### 2013-06-21 shanghai.tex
Create shanghai.tex

% !TEX encoding = UTF-8 Unicode
\documentclass[11pt]{amsart}
\title[Short groovy title goes here]{Long groovy title goes here}
\usepackage[british]{babel}
\usepackage{datetime}
\date{\today}
\author{Clifton Cunningham}
\address{University of Calgary}
\email{cunning@math.ucalgary.ca}
\author{David Roe}
\address{Pacific Institute for the Mathematical Sciences at the University of Calgary}
\email{roed.math@gmail.com}
\usepackage[utf8]{inputenc}
\renewcommand{\baselinestretch}{1.2}
\usepackage[notcite,color]{showkeys}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage[shortalphabetic]{amsrefs}
\usepackage[alphabetic]{amsrefs}
\renewcommand\MR{\relax}
\usepackage{xypic}
\usepackage{textcomp}
\usepackage{mathrsfs}
\usepackage{yfonts}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{manfnt}

%\include{definitions}
\theoremstyle{plain}
      \newtheorem{theorem}{Theorem}[section]
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{lemma}[theorem]{Lemma}
      \newtheorem{corollary}[theorem]{Corollary}

      \theoremstyle{definition}
      \newtheorem{definition}[theorem]{Definition}

      \theoremstyle{remark}
      \newtheorem{remark}[theorem]{Remark}

%%%% Some Named Categories

%%%% Functors

\newcommand{\gal}[1]{{\operatorname{Gal}\hskip-1pt\left( {\bar #1}/#1 \right)}}
\newcommand{\Spec}[1]{{\operatorname{Spec}\hskip-1pt( #1 )}}

\newcommand{\FF}{{\mathbb{F}}}
\newcommand{\ZZ}{{\mathbb{Z}}}
\newcommand{\NN}{{\mathbb{N}}}
\newcommand{\CC}{{\mathbb{C}}}
\newcommand{\QQ}{{\mathbb{Q}}}
\newcommand{\RR}{{\mathbb{R}}}
\newcommand{\EE}{\mathbb{\bar Q}_\ell}
\newcommand{\OK}{\mathcal{O}_K}
\newcommand{\pK}{\mathfrak{p}_K}
\newcommand{\Zp}{\mathbb{Z}_p}
\newcommand{\Qp}{\mathbb{Q}_p}
\newcommand{\Fp}{\mathbb{F}_p}
\newcommand{\bFq}{{\mathbb{\bar F}_q}}
\newcommand{\Fq}{{\mathbb{F}_q}}
\newcommand{\Fqm}{{\mathbb{F}_{q^m}}}
\newcommand{\bFp}{{\mathbb{\bar F}_p}}

\DeclareMathOperator{\Gal}{Gal}
\DeclareMathOperator{\Weil}{W}
\newcommand{\Frob}{{\operatorname{Fr}}}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\Hom}{Hom}
\DeclareMathOperator{\ord}{ord}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\Gr}{Gr}
\DeclareMathOperator{\Irrep}{Irrep}
\DeclareMathOperator{\Pic}{Pic}
\DeclareMathOperator{\id}{id}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Hh}{H}

\newcommand{\cdef}[1]{{{\color{cyan}#1}\index{#1}}} 
\newcommand{\sheafHom}{{\mathscr{H}\hskip-4pt{\it o}\hskip-2pt{\it m}}}
\newcommand{\abs}[1]{{\vert #1 \vert}}
\newcommand{\ceq}{{\, :=\, }}
\newcommand{\tq}{{\ \vert\ }}
\newcommand{\iso}{{\ \cong\ }}
\newcommand{\obj}{{\text{obj}\, }}
\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-2pt\textbf{m},#1}}
\newcommand{\GN}[1]{\textswab{#1}}
\newcommand{\bGN}[1]{{\bar{\textswab{#1}}}}
\newcommand{\invlim}[1]{\lim\limits_{\overleftarrow{#1}}}
\newcommand{\dirlim}[1]{\lim\limits_{\overrightarrow{#1}}}
\newcommand{\limit}[1]{\mathop{\textsc{lim}}\limits_{#1}}
\newcommand{\colimit}[1]{\mathop{\textsc{colim}}\limits_{#1}}
\newcommand{\cs}[1]{{\mathcal{#1}}}
\newcommand{\gcs}[1]{{\mathcal{\bar #1}}}
\newcommand{\dualgcs}[1]{\gcs{#1}^\dagger}
\newcommand{\dualcs}[1]{\cs{#1}^\dagger}
\newcommand{\CS}{{\mathcal{C\hskip-1.8pt S}}}
\newcommand{\CE}{{\mathcal{C\hskip-1.8pt E}}}
\newcommand{\Lgroup}[1]{{\,^L\hskip-1pt{#1}}}
\newcommand{\dualgroup}[1]{{\check{#1}}}
\newcommand{\Lang}{{\operatorname{Lang}}}
\newcommand{\image}{{\operatorname{im}}}

\makeatletter
\newcommand{\labitem}[2]{%
\def\@itemlabel{\textbf{#1}}
\item
\def\@currentlabel{#1}\label{#2}}
\makeatother

\newcommand{\tighttimes}{\hskip-1pt\times\hskip-1pt}
\newcommand{\tightertimes}{\hskip-3pt\times\hskip-3pt}
\newcommand\todo[1]{\ \vspace{5mm}\par \noindent\framebox{\begin{minipage}[c]{0.95 \textwidth} \tt #1\end{minipage}} \vspace{5mm} \par}
\newcommand\Clifton[1]{\marginpar{\smaller\smaller CC: #1}}
\newcommand\David[1]{\marginpar{\smaller\smaller DR: #1}}

\begin{document}

\begin{abstract}
We study the category of character sheaves on smooth commutative group schemes $G$ locally of finite type over finite fields $\mathbb{F}_q$. Assuming that the geometric component group of $G$ is finitely-generated, we show that the group of isomorphism classes of character sheaves on $G$ is canonically isomorphic to the group of characters of $G(\mathbb{F}_q)$. We use this result to exhibit an isomorphism between admissible characters of $T(K)$ and isomorphism classes of character sheaves on the Greenberg transform of the Néron model of $T$, where $K$ is any non-Archimdean local field and $T$ is any algebraic torus over $K$.
\end{abstract}

\maketitle

\section{Introduction}

%\input{introduction}
In his celebrated thesis, John Tate writes 
\begin{quotation}
{\it Concerning the characters of $k^*$ [the multiplicative group of a $\mathfrak{p}$-adic field], the situation is different from that of $k^+$.
First of all, we are interested in continuous multiplicative maps $\alpha \mapsto c(\alpha)$ of $k^*$ into the complex numbers, not only in the bounded ones, and shall call such a map a quasi-character, reserving the word ``character'' for the conventional character of absolute value $1$. Secondly, 
we shall find no model for the group of quasi-characters, or even for the group of characters, though such a model would be of the utmost importance.}  \cite{Tate:thesis}*{\S 2.3}
\end{quotation}
\noindent
In this paper we show that the monidal category of character sheaves on the Greenberg transform of the locally finite type Neron model of $T$ provides an elegant, canonical model for the group of (quasi-)characters of $T(K)$, where $K$ is any non-Archimedean local field and $T$ is any algebraic torus over $K$.

Since the character sheaves that appear in this paper are not quite an instance of those defined by George Luzstig, who coined the term, we begin by explaining what we mean by `character sheaves' in this paper. Let $G$ be a smooth commutative group scheme locally of finite type over $\Fq$; $G$ need not be reductive, connected, nor of finite type over $\Fq$. Fix a prime $\ell$ that does not divide $q$. By a {character sheaf} on $G$ we mean a triple $\cs{L}\ceq (\gcs{L},\mu,F)$ where $\gcs{L}$ is a constructible $\ell$-adic sheaf $\gcs{L}$ on the \'etale site of ${\bar G} \ceq G \times_{\Spec\Fq} \Spec{\bFq}$, locally constant of rank-$1$ on every connected component of ${\bar G}$, equipped with an isomorphism $\mu: m^* \gcs{L} \to  \gcs{L}\boxtimes \gcs{L}$, where $m : G\times G \to G$ is the group operation for $G$, and an isomorphism $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$, where $\Frob_{G}$ is the Frobenius automorphism on ${\bar G}$, satisfying natural compatibility conditions with $\mu$; these compatibility conditions are explained below.

Character sheaves on $G$ form a category, denoted by $\CS(G)$. In fact, $\CS(G)$ is a rigid symmetric monoidal category, so isomorphism classes of character sheaves on $G$ form a group, denoted by $\CS(G)_{/\text{iso}}$; this is the Picard group of the category of character sheaves on $G$. Our application of character sheaves to characters of algebraic tori over non-Archimedean local fields rests on the Picard group of character sheaves on $G$, for certain smooth group schemes $G$.

We now say a few words about the commutative group schemes locally of finite type over $\Fq$ that appear in our geometrization of admissible characters of algebraic tori over local fields. Let $K$ be a non-Archimedean local field with residual field $\Fq$; we place no restrictions on the characteristic of $K$ -- in particular, it may be $0$ or not. Write $\OK$ for ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$. 
Let $T$ be an algebraic torus defined over $K$. Let $\underline{T}$ be a N\'eron model for $T$; recall that this is a smooth group scheme locally of finite type over $\OK$. For each non-negative integer $d$, let $\GN{T}_d$ be the Greenberg transform of $\underline{T} \otimes \OK/\pK^{d+1}$; the commutative group scheme $\GN{T}_d$ plays the r\^{o}le of $G$, above.

The main result of this paper is a canonical isomorphism
\[
\CS(\textswab{T}_d)_{/\text{iso}} 
\iso
\Hom_{\leq d}(T(K),\EE^\times)
\] 
between the Picard group of the category of character sheaves on $\textswab{T}_d$ and the group of characters $T(K) \to \EE^\times$ of depth at most $d$.
Since these isomorphisms are compatible with respect to $d$, we also .....
\Clifton{I'll come back to working on this when we're closer to being finished. I'd be just as happy if you took this cup from my lips, though.} 
In particular, by specializing to the case $T= \mathbb{G}_{\hskip-1pt\text{m},K}$ and by choosing an isomorphism $\EE \approx \CC$ (unnatural though it may be), we arrive at a model for the group of quasi-characters of $K^\times$: the monoidal category of character sheaves on the Greenberg transform of the Neron model of $\mathbb{G}_{\hskip-2pt\text{m},K}$.

Structure of the paper:

Thanks to:

\tableofcontents

\section{The Picard group of character sheaves}\label{section:category}

%\input{category}
%\subsection*{Smooth commutative group schemes}

Throughout this paper, $G$ stands for a commutative group scheme, smooth and locally of finite type over a finite field $\Fq$; we write $m : G\tightertimes G\to G$ for the multiplication morphism. We fix an algebraic closure $\bFq$ of $\Fq$ and write ${\bar G} $ for the commutative group scheme, smooth and locally of finite type over $\bFq$ obtained by base change; the multiplication morphism for ${\bar G}$ will be denoted by ${\bar m}$. Let $\Frob_{G}$ (resp. $\Frob_{G\tighttimes G}$) be the Frobenius automorphism of ${\bar G}$ (resp. ${\bar G}\tightertimes {\bar G}$).\Clifton{I'll insert a reference to SGA where Frobenius is defined for a large class of schemes over finite fields.}

%\subsection*{The category of character sheaves}

The category of character sheaves on $G$, denoted by \cdef{$\CS(G)$}, is defined as follows.
A \cdef{character sheaf} on $G$ is a triple $\cs{L}\ceq (\gcs{L},\mu,F)$ where: 
\begin{enumerate}
\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a constructible $\ell$-adic sheaf on (the \'etale site of) ${\bar G}$, locally constant of rank $1$ on connected components of ${\bar G}$; 
\labitem{(CS.1)}{CS.1} $\mu: {\bar m}^* \gcs{L} \to  \gcs{L}\boxtimes \gcs{L}$ is an isomorphism of sheaves on ${\bar G}\tightertimes {\bar G}$ such that
\[
\xymatrix{
{\bar m}_3^*\gcs{L} \ar[rr]^{({\bar m}\times \id)^*\mu} \ar[d]_{(\id\tightertimes {\bar m})^*\mu}   &&  {\bar m}^*\gcs{L}\boxtimes \gcs{L} \ar[d]^{\mu \boxtimes \id} \\
\gcs{L} \boxtimes {\bar m}^* \gcs{L} \ar[rr] & &  \gcs{L} \boxtimes\gcs{L} \boxtimes \gcs{L}\\
}
\]
commutes, where $m_3 \ceq m\circ (m\tightertimes\id) = m\circ (\id\tighttimes m)$;
\labitem{(CS.2)}{CS.2} $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ is an isomorphism of sheaves on ${\bar G}$ compatible with $\mu$ in the sense that 
\[
\xymatrix{
\Frob_{G\tighttimes G}^* {\bar m}^* \gcs{L} \ar[rr]^{\Frob_{G\tighttimes G}^*\mu} && \Frob_{G\tighttimes G}^*(\gcs{L}\boxtimes \gcs{L})\\
\ar@{=}[u] {\bar m}^*  \Frob_{G}^* \gcs{L} \ar[d]_{{\bar m}^* F} && \ar[d]^{F\boxtimes F} \ar@{=}[u] \Frob_{G}^*\gcs{L}\boxtimes \Frob_{G}^*\gcs{L}\\
{\bar m}^*\gcs{L} \ar[rr]^{\mu} && \gcs{L} \boxtimes\gcs{L}\\
}
\]
commutes.
\end{enumerate}
Morphisms in $\CS(G)$ are defined in the natural way:
\begin{enumerate}
\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,F)$ and $\cs{L'} = (\gcs{L'},\mu',F')$ are character sheaves on $G$ then $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$ of constructible $\ell$-adic sheaves on ${\bar G}$ such
\[
\xymatrix{
\ar[d]_{F} \Frob_G^* \gcs{L} \ar[r]^{\Frob_G^* \varphi} & \ar[d]^{F'} \Frob_G^* \gcs{L'} &\text{and}& \ar[d]_{\mu} m^* \gcs{L} \ar[r]^{m^* \varphi} & \ar[d]^{\mu'} m^* \gcs{L'} \\
\gcs{L} \ar[r]^{\varphi} & \gcs{L'} && \gcs{L}\boxtimes\gcs{L} \ar[r]^{\varphi\boxtimes \varphi} & \gcs{L'} \boxtimes \gcs{L'}\\
}
\]
both commute.
\end{enumerate}

%\subsection*{The Picard group of character sheaves}

%\begin{proposition}\label{tensor}
The category $\CS(G)$ of character sheaves on $G$ is a rigid monoidal category [insert reference] under $\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'},  \mu\otimes\mu', F\otimes F')$ with duals formed by applying the functor $\sheafHom(\ - \ ,(\EE)_{\bar G})$ to conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}. 
%\end{proposition}
(The category of characters sheaves on $G$ is not abelian, so $\CS(G)$ is not a tensor category in the sense of \cite{Deligne:tensorielles}.)
%\begin{proof}\end{proof}
%
This rigid monoidal category structure for $\CS(G)$ puts a group structure on the set $\CS(G)_{/\text{iso}}$ of isomorphism classes in $\CS(G)$; we refer to this as the \cdef{Picard group} of character sheaves on $G$; {\it cf.} {\tt http://ncatlab.org/nlab/show/Picard+group}. \Clifton{Replace ncatlab with other references.}

%\subsection*{Trace of Frobenius}\label{sec:Frob}

Let $\cs{L}$ be a character sheaf on $G$. Every $g\in G(\Fq)$ determines a point ${\bar g}$ on ${\bar G}$ fixed by $\Frob_G$ and therefore an automorphism $F_{\bar g}$ of $\gcs{L}_{\bar g}$. Note that $\Aut_{\EE}(\gcs{L}_{\bar g}) \iso \EE^\times$, canonically (this follows from second condition appearing in the definition of character sheaves). The isomorphism $\mu : {\bar m}^* \gcs{L} \to \gcs{L}\boxtimes\gcs{L}$ guarantees that the function $t^\Frob_\cs{L} : G(\Fq)\to \EE^\times$, defined by $g \mapsto F_{\bar g}$, is a group homomorphism; we refer to $t^\Frob_\cs{L}$ as the \cdef{trace of Frobenius of $\cs{L}$}.\Clifton{There is no actual trace involved, since $\gcs{L}$ is a rank $1$ local system. More generally, trace is needed.} 
%
It is clear that $t^\Frob_{\cs{L}\otimes \cs{L'}} = t^\Frob_\cs{L} \cdot t^\Frob_\cs{L'}$ (pointwise multiplication of functions) and that $t^\Frob_\cs{L} = t^\Frob_\cs{L'}$ if $\cs{L} \iso \cs{L'}$ in $\CS(G)$. In this way we obtain a group homomorphism 
\[
\cdef{t_{G}} : \CS(G)_{/\text{iso}} \longrightarrow \Hom_\text{grp}(G(\Fq),\EE^\times), \qquad \text{defined by}\qquad 
\cs{L} \mapsto t^\Frob_\cs{L},
\]
from the Picard group of character sheaves on $G$ to the character group of $G(\Fq)$.

Our main result on the geometrization of admissible characters of $p$-adic tori [insert internal reference here] follows from a general fact established later in this paper: if the geometric component group of $G$ is finitely-generated then the trace of Frobenius defines an isomorphism from the Picard group of character sheaves $G$ to the group of characters of $G(\Fq)$ (here, as throughout the paper, $G$ is a commutative group scheme, smooth and locally of finite type over $\Fq$).

%\subsection*{Pull-back of character sheaves}\label{subsection:pullback}

\begin{proposition}\label{prop:pullback}
If $f : H\to G$ is a morphism of commutative group schemes locally of finite type over $\Fq$ then $(\gcs{L},\mu,F) \mapsto ({\bar f}^*\gcs{L},({\bar f}\tightertimes{\bar f})^*\mu,{\bar f}^*F)$ defines a monoidal functor $f^* : \CS(G) \to \CS(H)$ such that
\[
\xymatrix{
\CS(G)_{/\text{iso}} \ar[r]^{f^*} \ar[d]^{t_{G}} &  \ar[d]^{t_{H}} \CS(H)_{/\text{iso}}\\
\Hom_\text{grp}(G(\Fq),\EE^\times) \ar[r] & \Hom_\text{grp}(H(\Fq),\EE^\times)
}
\]
is a commutative diagram of groups, where the lower homomorphism is dual to $f : H(\Fq)\to G(\Fq)$.  Moreover, $(f\circ g)^* = g^* \circ f^*$.
\end{proposition}

\begin{proof}
Let $\cs{L}$ be a character sheaf on $G$. We start by showing that ${\bar f}^*\gcs{L}$ is locally constant on connected components of ${\bar H}$. Let $c_j :{\bar H}^j \hookrightarrow {\bar H}$ be any connected component. Then there is a unique connected component $c_i : {\bar G}^i$ of ${\bar G}$ such that ${\bar f}: {\bar H} \to {\bar G}$ factors through ${\bar H}^j \hookrightarrow {\bar G}^i$, thus defining ${\bar f}^j : {\bar H}^j \to {\bar G}^i$. Indeed, $i$ is the image of $j$ under the group homomorphism $\pi_0({\bar G}) \to \pi_0({\bar H})$ obtained by applying the functor $\pi_0$ to ${\bar f}$; see \cite{vdG&M}*{III, 3.28}, for example.\Clifton{Replace with a better reference, eventually.} Since $\cs{L}$ is a character sheaf, $\gcs{L}$ is locally constant on the connect components of ${\bar G}$; thus, there is a finite etale covering $a_i : X_i \to {\bar G}^i$ such that $a_i^* (\gcs{L}\vert_{\bar G}^i)$ is constant. Let $b_j : Y_j \to {\bar H}^j$ be the pull-back of $a_i$ along ${\bar f}^j$; let $g_j : Y_j \to X_i$ be the map opposite ${\bar f}^j$. Then $b_j$ is a finite etale covering of ${\bar H}^j$ and 
\[
b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right) = ({\bar f}\circ c_j \circ b_j)^*\gcs{L} = (c_i\circ a_i\circ g_j)^*\gcs{L} = g_j^* a_i^* (\gcs{L}\vert_{\bar G}^i).
\]
Since $a_i^* (\gcs{L}\vert_{\bar G}^i)$ is a constant sheaf and since the pull-back of a constant sheaf (along $g_j$, in this case) is a constant sheaf, it follows that $b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right)$ is a constant sheaf. Thus, ${\bar f}^*\gcs{L}$ is locally constant on ${\bar H}^j$. Since $({\bar f}^*\gcs{L})_{\bar g} = \gcs{L}_{f({\bar g})}$ for every geometric point ${\bar g}$ on ${\bar G}$, and since $\gcs{L}$ has rank $1$ on connected components of ${\bar G}$, it follows that $f^*\gcs{L}$ also has rank $1$ on connected components of ${\bar G}$. This completes the proof that ${\bar f}^*\gcs{L}$ satisfies condition \ref{CS.0}.

To see that $({\bar f}\tightertimes {\bar f})^* \gcs{L}$ satisfies condition \ref{CS.1} simply apply the functor $({\bar f}\tightertimes {\bar f})^*$ to \ref{CS.1} for $\cs{L}$ and use the canonical isomorphism $({\bar f}\tightertimes {\bar f})^*( \gcs{L} \boxtimes\gcs{L}) \iso  {\bar f}^*\gcs{L} \boxtimes {\bar f}^*\gcs{L}$ (a few times). Likewise, to see that ${\bar f}^*\gcs{L}$ satisfies condition \ref{CS.2}, apply the same functor to \ref{CS.2} for $\gcs{L}$. Then use the fact that $f$ is defined over $\Fq$, so $({\bar f}\tightertimes {\bar f})^* \Frob_{G\tighttimes G}^* \iso \Frob_{G\tighttimes G} ({\bar f}\tightertimes {\bar f})^*$, and the fact that $f$ is a morphism of group schemes, so $({\bar f}\tightertimes {\bar f})^* {\bar m}^* \iso {\bar m}^* {\bar f}^*$ (isomorphisms of functors on constructible sheaves).
%
To see that $(\gcs{L},\mu,F) \mapsto ({\bar f}^*\gcs{L},({\bar f}\tightertimes {\bar f})^*\mu,{\bar f}^*F)$ defines a functor $f^* : \CS(G) \to \CS(H)$ one applies the functors ${\bar f}^*$ and ${\bar f}^*\tightertimes{\bar f}^*$ to \ref{CS.3} and argue as above. It follows from the fact that sheaf hom commutes with these functors that $f^* : \CS(G) \to \CS(H)$ is a monoidal functor.

The fact that the functor $f^* : \CS(G) \to \CS(H)$ commutes with the trace of Frobenius, in the sense above, follows immediately from the definitions; see \cite{Laumon}*{1.1.1.2}, where the ambient hypothesis that $X$ is of finite type over $\Fq$ can be replaced by the hypothesis that $X$ is locally of finite type over $\Fq$.
\Clifton{I have not proved $(f\circ g)^* = g^* \circ f^*$, yet.}
\end{proof}

\section{Connected abelian algebraic groups}

%\input{connected-1}
% !TEX encoding = UTF-8 Unicode
%In this section we review a fundamental property of character sheaves on geometrically connected, commutative algebraic groups over $\Fq$.

\begin{proposition}\label{prop:connected-1}
If $G$ is a geometrically connected commutative algebraic group over $\Fq$ then 
\[
t_{G} : \CS(G)_{/\text{iso}} \to \Hom_\text{grp}(G(\Fq),\EE^\times),
\]
is an isomorphism of groups.
\end{proposition}

\begin{proof}
We will prove this proposition by reducing it to the functions--sheaves dictionary \cite{Laumon}*{1.1}. The main point of this proof will therefore be to show that, {\it since $G$ is geometrically connected}, every character sheaf on $G$ descends to a local system on $G$ satisfying the analogue of \ref{CS.1} on $G$.

First, observe that the forgetful functor $(\gcs{L},\mu,F) \mapsto (\gcs{L},F)$ sends character sheaves on $G$ to Weil local systems on $G$ \cite{Deligne:Weil2}*{1.1.10} (by a Weil local system on $G$ we mean a Weil sheaf on $G$ which is a local system on ${\bar G}$). While is it not true that all Weil local systems on $G$ descend to sheaves on $G$, those that appear in the image of the forgetful functor from character sheaves do.

To see why this is so, consider the category \cdef{$\CS_0(G)$} of pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$ and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ satisfies condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$ are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}. Let $b : {\bar G} \to G$ be base change (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$). The proof of Proposition~\ref{prop:pullback} adapts (simplifies, in fact) to show that  $b^* : \CS_0(G) \to \CS(G)$ is a monoidal functor. This functor is fully faithful; see \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.  We will show that $b^*$ is essentially surjective.

Let $g$ be any $\Fq$-rational point on $G$ (such as the identity for $G$) and let ${\bar g}$ be the geometric point on $G$ lying above $g$ (we fixed $\Fq \hookrightarrow \bFq$ long ago). Since $G$ is geometrically connected, the geometric point ${\bar g}$ determines an equivalence between the category of Weil local systems on $G$ and $\ell$-adic representations of $\Weil(G,{\bar g})$ \cite{Deligne:Weil2}*{1.1.12}. Now let $(\gcs{L},\mu,F)$ be a character sheaf on $G$. Then the isomorphism class of the Weil local system $(\gcs{L},F)$ corresponds to an $\ell$-adic character of the Weil group $\Weil(G, {\bar g})$. The $\Fq$-rational point $g$ under the geometric point ${\bar g}$ determines a splitting $\Weil(\bFq/\Fq)\to  \Weil(G,{\bar g})$ of the exact sequence
\[
\xymatrix{
1 \ar[r] & \pi_1({\bar G}, {\bar g}) \ar[r] &  \Weil(G,{\bar g}) \ar[r] & \ar@/_1pc/@{.>}[l]_{g} \Weil(\bFq/\Fq) \ar[r] & 1
}
\]
In this way the Weil local system $(\gcs{L},F)$ determines an $\ell$-adic character
\[
t_{(\gcs{L},F)}(g) : \Weil(\bFq/\Fq) \to \EE^\times \qquad \text{defined by}\qquad \Frob \mapsto t^\Frob_{(\gcs{L},F)}(g)
\]
of the Weil group $\Weil(\bFq/\Fq)$; the image of $\Frob$ under this character is $t^\Frob_\cs{L}(g)$, the trace of Frobenius of $\cs{L}$ at $g$.

On the other hand, we have already seen that $t^\Frob_\cs{L} : G(\Fq) \to \EE^\times$ is a group homomorphism. Since $G$ is an algebraic group over $\Fq$, it is a variety over $\Fq$, so finitely generated over $\Fq$, so $G(\Fq)$ is finite; it follows that $t^\Frob_\cs{L}(g) = t^\Frob_{(\gcs{L},F)}(g)$ is a root of unity, for every $g\in G(\Fq)$.  Since $\Weil(\bFq/\Fq)$ is generated by $\Frob$ and $t_{(\gcs{L},F)}(g) : \Weil(\bFq/\Fq) \to \EE^\times$ is a character, it follows that the image of $t_{(\gcs{L},F)}(g)$ is a finite subset of $\mu(\EE)$. Thus, $t_{(\gcs{L},F)}(g)$ extends to an $\ell$-adic character of $\Gal(\bFq/\Fq)$, which will be denoted by the same symbol.
\[
\xymatrix{
1 \ar[r] & \ar@{=}[d] \pi_1({\bar G}, {\bar g}) \ar[r] & \ar[d] \Weil(G,{\bar g}) \ar[r] & \ar[d]  \Weil(\bFq/\Fq) \ar[r] & 1\\
1 \ar[r] &  \pi_1({\bar G}, {\bar g}) \ar[r] & \pi_1(G,{\bar g}) \ar[r] & \Gal(\bFq/\Fq) \ar[r] & 1\\
}
\]

We may now lift the $\ell$-adic character $t_{(\gcs{L},F)}(g) : \Gal(\bFq/\Fq) \to \EE^\times$ to an $\ell$-adic character of $\pi_1(G,{\bar g})$ using the canonical topological group map $\pi_1(G,{\bar g}) \to \Gal(\bFq/\Fq)$, above. But ${\bar g}$ also determines an equivalence between the category of $\ell$-adic representations of $\pi_1(G,{\bar g})$ and local systems on $G$. Let $\cs{L}_0$ be a local system on $G$ in the isomorphism class determined by this $\ell$-adic character of $\pi_1(G,{\bar g})$. Then $b^*\cs{L}_0 \iso \gcs{L}$, so $b^*$ is essentially surjective.

We have now shown that $b^* : \CS_0(G) \to \CS(G)$ is an equivalence of  rigid monoidal categories. It follows immediately that $b^*$ determines an isomorphism 
\[
b^* : \CS_0(G)_{/\text{iso}} \mathop{\longrightarrow}^{\iso} \CS(G)_{/\text{iso}}
\] 
of the Picard groups determined by these rigid monoidal categories.
\Clifton{\textdbend This last sentence glosses over some subtle points; I might need to address them in the `two perspectives' section.}

To finish the proof observe that the functions--sheaves dictionary, as it pertains to characters, shows that
\[
t_{G} : \CS_0(G)_{/\text{iso}}\to \Hom_\text{grp}(G(\Fq),\EE^\times)
\]
is an isomorphism of groups; see \cite{Laumon}*{1.1.3} or \cite{SGA4.5}*{Sommes trigonométriques}.
\end{proof}

\section{Commutative etale group schemes}

%\input{etale-1}
%In this section we establish a fundamental property of character sheaves on commutative etale group schemes over $\Fq$ that are geometrically finitely generated.

\begin{proposition}\label{prop:etale}
If $G$ is a commutative group scheme etale over $\Fq$ and $G(\bFq)$ is finitely generated then there is a canonical isomorphism 
\[
\CS(G)_{/\text{iso}} \longrightarrow H^1(\Weil(\bFq/\Fq), \Hom_\text{grp}(G(\bFq),\EE^\times)),
\qquad \text{given by}\qquad
[\cs{L}] \mapsto [t_\cs{L}],
\]
where $t_\cs{L}: \Weil(\bFq/\Fq)\to \Hom_\text{grp}(G(\bFq),\EE^\times)$ is a cocycle such that 
\[
\forall g\in G(\Fq), \qquad t_\cs{L}(\Frob)(g) = t^\Frob_\cs{L}(g).
\]
\end{proposition}

\begin{proof}
To simplify notation, we set $W_\Fq \ceq \Weil(\bFq/\Fq)$ and $G(\bFq)^* \ceq \Hom_\text{grp}(G(\bFq),\EE^\times)$.
Recall the equivalence between etale group schemes over $\Fq$ and the category of groups equipped with a continuous action of $\Gal(\bFq/\Fq)$ (for the discrete topology on the group), given by $G \mapsto G(\bFp)$. Under this equivalence any character sheaf $\cs{L} =(\gcs{L},\mu,F)$ on $G$ corresponds to: 
\begin{enumerate}
\labitem{(cs.0)}{cs.0} an indexed set of one-dimensional $\EE$-vector spaces $\gcs{L}_x \ceq x^*\gcs{L}$, as $x$ runs over $G(\bFp)$; 
\labitem{(cs.1)}{cs.1} an indexed set of isomorphisms $\mu_{x,y}  \ceq (x \times y)^*\mu : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes \gcs{L}_{y}$, for all $x,y \in G(\bFp)$, such that
\[
\xymatrix{
\gcs{L}_{x+y+z} \ar[rr]^{\mu_{x+y,z}} \ar[d]_{\mu_{x,y+z}}   &&  \gcs{L}_{x+y}\otimes \gcs{L}_{z} \ar[d]^{\mu_{x,y} \otimes \id} \\
\gcs{L}_{x} \otimes \gcs{L}_{y+z} \ar[rr]^{\id \otimes \mu_{y,z}} & &  \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes \gcs{L}_{z}\\
}
\]
commutes, for all $x,y,z\in G(\bFp)$; and 
\labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $F_{x} \ceq x^*F: \gcs{L}_{\Frob(x)} \to \gcs{L}$ 
\Clifton{\textdbend There's hidden subtlety here too: maybe I should explain which Frobenius this is and how it acts. }
such that
\[
\xymatrix{
 \gcs{L}_{\Frob(x)+\Frob(y)} \ar[d]_{F_{x+y}} \ar[rr]^{\mu_{\Frob(x),\Frob(y)}} &&\ar[d]^{F_x\otimes F_y}  \gcs{L}_{\Frob(x)}\otimes \gcs{L}_{\Frob(y)}\\
\gcs{L}_{x+y} \ar[rr]^{\mu_{x,y}} && \gcs{L}_x \otimes\gcs{L}_y\\
}
\]
commutes, for all $x,y\in G(\bFp)$.
\end{enumerate}
Under this equivalence, a map $\varphi : \cs{L} \to \cs{L'}$ of character sheaves on $G$ corresponds to:
\begin{enumerate}
\labitem{(cs.3)}{cs.3} an indexed set $\varphi_x \ceq x^*\varphi: \gcs{L}_x \to \gcs{L'}_x$ of linear transformations (of one-dimensional $\EE$-vector spaces), as $x$ runs over $G(\bFq)$, such that
\[
\xymatrix{
\ar[d]_{F_x} \gcs{L}_{\Frob(x)} \ar[r]^{\varphi_{\Frob(x)}} & \ar[d]^{F_x'} \gcs{L'}_{\Frob(x)} &\text{and}& \ar[d]_{\mu} \gcs{L}_{x+y} \ar[r]^{\varphi_{x+y}} & \ar[d]^{\mu'_{x+y}} \gcs{L'}_{x+y} \\
\gcs{L}_x \ar[r]^{\varphi_x} & \gcs{L'}_x && \gcs{L}_x\otimes\gcs{L}_y \ar[r]^{\varphi_x\otimes \varphi_y} & \gcs{L'}_x \otimes \gcs{L'}_y\\
}
\]
both commute.
\end{enumerate}
It is clear that the category defined by conditions \ref{cs.0}, \ref{cs.1}, \ref{cs.2} and \ref{cs.3}, denoted by \cdef{$\CS(G(\bFq))$}, is equivalent to $\CS(G)$. We will prove the proposition by exhibiting an isomorphism between $\CS(G(\bFq))_{/\text{iso}}$ and $H^1(W_{\Fq}, G(\bFq)^*)$.

To produce the isomorphism between $\CS(G(\bFq))_{/\text{iso}}$ and $H^1(W_{\Fq}, G(\bFq)^*)$ we must pick a global section of the line bundle $(\gcs{L},\mu)$, for each character sheaf $\cs{L}$ on $G$. We will show that the group isomorphism does not depend on these choices.

First, however, we show that such global sections exist.
Since $G(\bFq)$ is finitely-generated abelian, it admits a decomposition $G(\bFq) \iso G(\bFq)_\text{free} \oplus G(\bFq)_\text{tors}$ such that $G(\bFq)_\text{tors}$ is finite.
Let $x_1, \ldots , x_r$ be a basis for the free part $G(\bFq)_\text{free}$ of $G(\bFq)$ and let $y_1, \ldots , y_t$ be a generators for the torsion part of $G(\bFq)$ corresponding to the decomposition $G(\bFq)_\text{tors} \iso \oplus_{j=1}^t \ZZ/m_1\ZZ$, with $m_1\vert m_2\vert \cdots \vert m_t$. For each such $x_i$ pick $s(x_i)\in \gcs{L}_{x_i}$; for each such $y_j$ pick $s(y_j) \in \gcs{L}_{y_j}$; also set $s({\bar e}) \ceq 0 \in \gcs{L}_{\bar e}$. .... \Clifton{I'll finish this later.} In this way we define a section $s \ceq s_\cs{L} : G(\bFq) \to \coprod_{z\in G(\bFq)} \gcs{L}_z$ of projection $\coprod_{z\in G(\bFq)} \gcs{L}_z \to G(\bFq)$ such that 
\begin{equation}\label{section}
\forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes s(y).
\end{equation}
Under the equivalence at the beginning of this section, $s = s_\cs{L}$ corresponds to a global section of the line bundle $(\gcs{L},\mu)$.

We use the section $s_\cs{L}$ to define a cocycle $z_\cs{L} \in Z^1(W_\Fq,G(\bFq)^*)$ as follows. Recall that $\cs{L}$ also determines a family of linear transformations $F_x : \gcs{L}_{\Frob(x)} \to \gcs{L}_x$ of one-dimensional $\EE$-vector spaces,  so $F_x(s(\Frob(x)))$ is a scalar multiply of $s(x)$, for each $x\in G(\bFq)$; let $t_\cs{L}(\Frob)(x)$ be that scalar, so
\begin{equation}\label{t}
\forall x\in G(\bFq),\qquad F_{x}(s(\Frob(x)) = t_\cs{L}(\Frob)(x) s(x).
\end{equation}
Conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that the scalar $z_\cs{L}(\Frob)(x)$ is non-zero, while condition~\ref{cs.1} forces $t_\cs{L}(\Frob)(x+y) = t_\cs{L}(\Frob)(x) \ t_\cs{L}(\Frob)(y)$, for all $x,y \in G(\bFq)$. 
%\Clifton{The alternative to this approach is to change the definition of character sheaves to incorporate the notion of Galois sheaves. That might not be so bad, but would add another layer of complication, which we wouldn't use profitably, expect here.} 
Now $t_\cs{L} : W_\Fq \to G(\bFq)^*$ is defined, recursively, by $t_\cs{L}(\Frob^n) \ceq t_\cs{L}(\Frob)\cdot \,^\Frob t_\cs{L}(\Frob^{n-1})$, where $\Frob$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers to pointwise multiplication of functions. This gives
\[
\obj \CS(G(\bFq)) \longrightarrow Z^1(W_\Fq,G(\bFq)^*), \qquad \text{defined by} \qquad \cs{L} \mapsto t_\cs{L}.
\]

Although we used a global section $s_\cs{L}$ in the definition of $t_\cs{L}$, the class of $t_\cs{L}$ does not depend on this choice. To see why, let $s_1$ and $s_2$ be two global sections of the line bundle $(\gcs{L},\mu)$, in the sense above and let $t_1$ and $t_2$ be the cocycles defined by $s_1$ and $s_2$, respectively, as above. Since, for each $x\in G(\bFq)$, $\gcs{L}_x$ is a one-dimensional $\EE$-vector space, there is a unique scalar $a(x) \in \EE$ such that $s_2(x) = a(x) s_1(x)$; moreover, $a(x)$ is non-zero, since $s_2(x)$ is non-zero. Then \eqref{section} and condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so $a\in G(\bFq)^*$. Now consider the  coboundary $t_0 : W_\Fq \to G(\bFq)^*$ defined by $t_0(\Frob) = \,^\Frob a \cdot a^{-1}$. Then $t_2 = t_0 t_1$, so $t_2$ and $t_1$ are cohomologous. In this way we see that
\begin{equation}\label{cohomologous}
\obj \CS(G(\bFq)) \longrightarrow H^1(W_\Fq,G(\bFq)^*), \qquad \text{defined by} \qquad \cs{L} \mapsto [t_\cs{L}],
\end{equation}
is independent of the choice of global sections made above.

We now show that the function $\obj \CS(G(\bFq)) \longrightarrow H^1(W_\Fq,G(\bFq)^*)$ factors through $\obj \CS(G(\bFq)) \to \CS(G(\bFq))_{/\text{iso}}$. To see this, let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and let $t$ and $t'$ be any cocycles representing the classes in the image of $\cs{L}$ and $\cs{L'}$ under \eqref{cohomologous}; by construction, $t$ and $t'$ are defined by sections $s$ and $s'$. Now, $\varphi_x(s(x))$ is a non-zero scalar multiple of $s'(x)$; define $\phi: G(\bFq) \to \EE^\times$ by $\varphi_x(s(x)) = \phi(x) s'(x)$. By the second part of condition~\ref{cs.3}, $\phi(x+y) = \phi(x)\phi(y)$, so $\phi \in G(\bFq)^*$. By the first part of condition~\ref{cs.3}, $t'(\Frob) = t(\Frob) \cdot (\,^{\Frob^{-1}}\phi \cdot \phi^{-1})$, so $t$ and $t'$ are cohomologous. This concludes the definition of 
\begin{equation}\label{pich1}
 \CS(G(\bFq)_{/\text{iso}} \longrightarrow H^1(W_\Fq,G(\bFq)^*), \qquad \text{defined by} \qquad [\cs{L}] \mapsto [t_\cs{L}].
\end{equation}
Now it follows from \eqref{t} that the image of the isomorphism class of $\cs{L}$ is indeed represented by a cocycle $t_\cs{L}$ such that $t_\cs{L}(\Frob) = t^\Frob_\cs{L}$ on $G(\Fq)$, which is to say, when evaluated at $\Frob$, the cocycle $t_\cs{L}$ is an extension of the trace of Frobenius of $\cs{L}$.

It only remains to show that \eqref{pich1} is a group isomorphism. This is straightforward.
\Clifton{Straightforward, yes, but it still needs to be written down here.}
\end{proof}

%\input{etale-2}
%Define $\rho \colon \Hh^1(W_{\Fq}, \Hom(G(\bFq), \EE^\times)) \rightarrow \Hom(G(\Fq), \EE^\times)$ by $\rho(\phi)(g) = \phi(\Frob)(g)$.
\begin{proposition}\label{prop:X}
Let $X$ be a finitely generated abelian group equipped with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on $X$.  Then
\begin{align*}
\Hh^1(\Fq, \Hom(X, \EE^\times)) &\xrightarrow{\rho} \Hom(\Hh^0(\Fq, X), \EE^\times) \\
\rho([z])(x) &= z(\Frob)(x)
\end{align*}
is an isomorphism of groups.
\end{proposition}
\begin{proof}
We first prove that $\rho$ is surjective.  Suppose that $f \in \Hom(X^\Frob, \EE^\times).$  Since $\EE^\times$ is divisible as an abelian group it is injective as a $\ZZ$-module and thus $\Ext^1_{\ZZ}(X/X^\Frob, \EE^\times) = 0$.  Applying the functor $\Hom(\mbox{---}, \EE^\times)$ to
$$0 \rightarrow X^\Frob \rightarrow X \rightarrow X/X^\Frob \rightarrow 0$$
and considering the associated long exact sequence gives the existence of an $\tilde{f} \in \Hom(X, \EE^\times)$ restricting to $f$.  Define a $1$-cocycle $z \in \Hh^1(\Fq, \Hom(X,\EE^\times))$ by mapping $\Frob$ to $\tilde{f}$.  Then $\rho([z]) = f$.

Now suppose that $[z] \in \Hh^1(\Fq,\Hom(X,\EE^\times))$ with $\rho([z]) = 1$; write $\tilde{f}$ for $z(\Frob)$.  The injectivity of $\rho$ is equivalent to the existence of a homomorphism $\psi \colon X \rightarrow \EE^\times$ with 
$$\tilde{f}(x) = \frac{\psi(\Frob(x))}{\psi(x)}$$
for $x \in X$.  In fact, we may replace the construction of $\psi$ for all $\ZZ[\Gal(\bFq/\Fq)]$-modules $X$ with the construction of analogous $\psi$s for a different class of modules.

Since the action of $\Gal(\bFq/\Fq)$ is continuous, there is an $m$ so that $\Frob^m$ acts trivially on $X$; write $\Gamma_m$ for $\Gal(\Fqm/\Fq)$.  Since $T^m-1$ factors as a squarefree product of cyclotomic polynomials, the Chinese remainder theorem expresses $\ZZ[\Gamma_m]$ as a product of $\ZZ[\zeta_d]$ for $d$ dividing $m$.  Each $\ZZ[\zeta_d]$ is the maximal order in a number field and thus $\ZZ[\Gamma_m]$ is a product of Dedekind domains.  Therefore $X$ decomposes into a direct sum of cyclic $\ZZ[\Gamma_m]$-modules \cite[?]{Brandal}, each of the form $\ZZ[\Gamma_m] / I$ for some ideal $I \subset \ZZ[\Gamma_m]$.  The ideal $I$ corresponds to a direct product of ideals $I_d$ in the $\ZZ[\zeta_d]$, and within each $\ZZ[\zeta_d]$ the Chinese remainder theorem allows a further decomposition of $\ZZ[\zeta_d] / I_d$ as a direct sum of $\ZZ[\zeta_d]$-modules of the form $\ZZ[\zeta_d]/P^s$.  So if we can construct, for every cyclotomic ring $\ZZ[\zeta_d]$, prime ideal $P \subset \ZZ[\zeta_d]$ and positive integer $s$, a $\psi \colon \ZZ[\zeta_d]/P^s \rightarrow \EE^\times$ with
\begin{equation} \label{eq:psi-condition}
\tilde{f}(x) = \frac{\psi(\zeta_d \cdot x)}{\psi(x)},
\end{equation}
then the existence of the original $\psi$ follows because $X$ is a direct sum of such $\ZZ[\zeta_d]/P^s$.

We now fix a $d$, $P$ and $s$, write $\zeta$ for $\zeta_d$ and choose a polynomial
$$h(T) = a_rT^r + a_{r-1}T^{r-1} + \cdots + a_0$$
so that $P^s = (p^s, h(\zeta_d))$.
%Setting $\psi = 1$ will satisfy equation \ref{eq:psi-condition} when $d = 1$.  
An an abelian group, the quotient $\ZZ[\zeta] / P^s$ is generated by $\zeta^i$ for $0 \le i < \phi(d)$; we define
\begin{equation} \label{eq:psi-def}
\psi(\zeta^i) = \alpha \prod_{j=0}^{i-1} \tilde{f}(\zeta^j)
\end{equation}
for an $\alpha \in \EE^\times$ to be chosen later.  Since there are relations among the $\zeta^i$ we first need to check that $\psi$ is well-defined.

The relations among the generators $\zeta^i$ are additively generated by $\zeta^ch(\zeta)$ as $c$ ranges from $0$ to $\phi(d)-r-1$.  If we set 
$$A_c = \sum_{i=0}^r a_i \sum_{j=0}^{i+c-1} \zeta^j$$
then
$$\psi(\zeta^ch(\zeta)) = \alpha^{h(1)} \tilde{f}(A_c).$$
Now consider $(\zeta - 1)A_c$: the sums telescope and we get that $(\zeta-1)A_c = \zeta^ch(\zeta) - h(1).$  There are now two possibilities:
\begin{enumerate}
\item $d$ is a power of $p$; write $s = \phi(d)m + n$.  We may take $h(T)$ to be $p^m(T-1)^n$, in which case $\zeta^ch(\zeta) - h(1) \in P^s$, so $A_c$ is fixed under multiplication by $\zeta$ in $\ZZ[\zeta]/P^s$ and thus $\tilde{f}(A_c) = 1$.  In this case $\alpha^{h(1)} = 1$ regardless of $\alpha$.
\item $d$ is not a power of $p$.  If two distinct primes divide $d$ then $\zeta - 1$ is a unit; otherwise $\zeta - 1$ is a unit modulo $P^s$.  Let $\omega \in \ZZ[\zeta]$ satisfy $\omega(\zeta - 1) \equiv 1 \pmod{P^s}$ and set
\begin{equation} \label{alpha-def}
\alpha = \tilde{f}(\omega).
\end{equation}
Then $A_c + h(1)\omega$ is fixed under multiplication by $\zeta$ and thus $\tilde{f}(A_c) = \tilde{f}(-h(1)\omega)$.
\end{enumerate}
In either case, $\psi(\zeta^ch(\zeta)) = 1$ for all $c$.  The only other relations imposed on the $\zeta^i$ are that they are all killed under multiplication by $p^s$.  Since $\tilde{f}$ is also a homomorphism $\ZZ[\zeta]/P^s \rightarrow \EE^\times$ the values of $\tilde{f}$ and thus of $\psi$ will be $p^s$-roots of unity.  Therefore $\psi$ is well defined.

We now check equation \ref{eq:psi-condition} for $x = \zeta^{\phi(d)-1}$.  Write $\Phi_d(T) = T^{\phi(d)} - b_{\phi(d)-1}T^{\phi(d)-1} - \cdots - b_0$ and set
$$B = \sum_{i=0}^{\phi(d)-1} -\zeta^i + b_i \sum_{j=0}^{i-1} \zeta^j.$$
We have

\begin{align*}
\frac{\psi(\zeta^{\phi(d)})}{\psi(\zeta^{\phi(d)-1})\tilde{f}(\zeta^{\phi(d)-1})} &= \frac{\psi(b_{\phi(d)-1}\zeta^{\phi(d)-1} + \cdots + b_0)}{\psi(\zeta^{\phi(d)-1})\tilde{f}(\zeta^{\phi(d)-1})} \\
&= \alpha^{-\Phi_d(1)} \tilde{f}(B)
\end{align*}
As before we see that $(\zeta - 1)B = \Phi_d(1) - \Phi_d(\zeta) = \Phi_d(1)$.  We consider the same cases as before:

\begin{enumerate}
\item $d$ is a power of $p$, in which case $\Phi_d(1) = p$.  Thus $(\zeta-1)B = p = u(\zeta-1)^{\phi(d)}$ for a unit $u \in \ZZ[\zeta]$ and $B - u(\zeta-1)^{\phi(d)-1}$ is fixed by $\zeta$, so that $\tilde{f}(B) = \tilde{f}(u(\zeta - 1)^{\phi(d)-1})$.  The multiplicative order of $\tilde{f}(u(\zeta-1)^{\phi(d)-1})$ is at most $\lceil \frac{s - 1 - (\phi(d)-1)}{\phi(d)}\rceil = \lceil \frac{s}{\phi(d)} \rceil - 1$ while the additive order of $1 \in \ZZ[\zeta]/P^s$ is $\lceil \frac{s}{\phi(d)} \rceil$.  Thus we may choose $\alpha = \psi(1)$ with $\alpha^p = \tilde{f}(B)$.
\item $d$ is not a power of $p$ and $\omega$ is the inverse of $\zeta-1$ modulo $P^s$.  Then $\tilde{f}(B) = \tilde{f}(\omega\Phi_d(1))$.
\end{enumerate}
In either case, $\alpha^{-\Phi_d(1)}\tilde{f}(B) = 1$ and thus $\psi$ satisfies equation \ref{eq:psi-condition} for $x = \zeta^{\phi(d)-1}$.  The definition of $\psi$ in \ref{eq:psi-def} immediately implies that $\psi$ satisfies equation \ref{eq:psi-condition} for lesser powers of $\zeta$, and thus for all $x$ by linearity.  The existence of $\psi$ shows that $\rho$ is injective.
\end{proof}

\section{Restriction to the identity component}

%\input{restriction}
% !TEX encoding = UTF-8 Unicode
%\subsection*{Restriction to the identity component is surjective}
Let $G^0$ be the connected component of $G$ containing the identity. 
By Proposition~\ref{prop:pullback}, pull-back along $G^0\hookrightarrow G$ determines a monoidal functor $\cs{L}\mapsto \cs{L}\vert_{G^0}$ from $\CS(G)$ to $\CS(G^0)$.  In this section we show that this functor is essentially surjective. To do this we employ a perspective on characters sheaves which is different from that in Section~\ref{section:category} but which works very well for geometrically connected abelian algebraic groups; this perspective fails to extend properly to the more general context of Section~\ref{section:category}.

\begin{proposition}\label{prop:restriction}
The restriction functor $\CS(G)\to \CS(G^0)$ is essentially surjective.
\end{proposition}

\begin{proof}
Because $G$ is smooth over $\Fq$, the identity component $G^0$ is a geometrically connected algebraic group over $\Fq$, clopen in $G$ \cite{vdG&M}*{3.17}. By Proposition~\ref{prop:connected-1}, every character sheaf $\cs{E} = (\gcs{E},\mu^0,F^0)$ on $G^0$ descends to a line bundle on $G^0$.
%
Let us review how line bundles on $G^0$ determine character sheaves on $G^0$.
Up to isomorphism, line bundles on $G^0$ may be apprehended in terms of pairs $(\pi,\psi)$, where $\pi : B\to G^0$ is a finite etale morphism of algebraic groups and a character $\psi : A\to \EE^\times$, where $\Gal(\bFq/\Fq)$ acts trivially on $A \ceq \ker {\bar \pi}$, as summarized by the following diagram.
\begin{equation}\label{E}
\xymatrix{
\EE^\times & 1\ar[r] & \ar@/_1pc/[ll]_{\psi} A  \ar[r] & B \ar[r]^{\pi} & G^0 \ar[r] & 1\\
}
\end{equation}
(In fact, we may always take $B = G^0$ and $\pi = \Lang_{G^0}$, the Lang isogeny for $G^0$.)
Indeed, $\cs{E}$ is precisely the component of $\pi_! (\EE)_{B}$ on which $A$ acts through $\psi$. 
To see that $\cs{E}$ is a line bundle on $G^0$, start by pulling back $\pi: B \to G^0$ along $m_0 : G^0\times G^0 \to G^0$.
\begin{equation}
\xymatrix{
\EE^\times & 1\ar[r] & \ar@/_1pc/[ll]_{\psi} A  \ar[r] & B \ar[r]^{\pi} & G^0 \ar[r] & 1\\
  	& 1\ar[r] & \ar@{.>}@/^1pc/[llu] \ar[u] A\times A  \ar[r]& \ar[u]^{m_{B}} B\times B \ar[r]^{\pi\tighttimes \pi}  & \ar[u]^{m_0} G^0\times G^0 \ar[r] & 1\\
}
\end{equation}
As pictured above, the kernel of this pull-back is $A\times A$; indeed, $A\times A\to B\times B$ is the pull-back of $A\to B$ along $m_{B}$. Use this Cartesian square to define a character (the dotted arrow, above) of $A\times A$; that is, define $A\times A\to \EE^\times$ by the composition of $A\times A$ and $\psi : A\to \EE^\times$. Note that this character is $\psi \otimes \psi : A\times A\to \EE^\times$.
\Clifton{I haven't explained how maps between diagrams define sheaf homomorphisms between local systems.}
Since the lower sequence is precisely the sequence defining $\cs{E}\boxtimes\cs{E}$, this shows that, by construction, $\cs{E}$ comes equipped with a canonical isomorphism $m_0^*\cs{E} \iso \cs{E}\boxtimes\cs{E}$. Now the base change $\cs{E}$ comes equipped with isomorphisms $F^0 : \Frob_{G^0}^* \gcs{E} \to \gcs{E}$ and $\mu^0 : {\bar m}_0^* \gcs{E} \to \gcs{E}\boxtimes \gcs{E}$ satisfying conditions \ref{CS.1} and \ref{CS.2}. Then $(\gcs{E},\mu^0,F^0)$ is a character sheaf on $G^0$.

The next step is to show that $\pi: B \to G^0$ extends to a finite etale morphism of group schemes $f: H\to G$, smooth and locally of finite type over $\Fq$, in such a way that $H^0 = B$ (so, $B$ is the identity component of $H$) and $f^0 =\pi$ (so, the restriction of $f$ to $H^0$ is a finite etale cover of $G^0$) and $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism of component groups.
\Clifton{David, this paragraph is the lemma you were working on. I'm worried that I won't have time to work on this before your talk, so please keep going, if you can.}
\begin{equation} \label{extension-diagram}
    \xymatrix{
        & A \ar[d] \ar@{=}[r] & A \ar[d] &  \\
        & B \ar[r] \ar[d]_{\pi} & H \ar[r] \ar[d]_{f} & \pi_0(H) \ar[d]_{\pi_0(f)}^{\iso} \\
        & G^0 \ar[r] & G \ar[r] & \pi_0(G).}
\end{equation}
where all rows and columns are exact and all maps are defined over $\Fq$.  Extensions of $G^0$ by $A$, such as $A \to H^0 \to G^0$, correspond to classes in $\Ext^1_{\ZZ[\Gamma]}(G^0, A)$.  Similarly, extensions of $G$ by $A$ correspond to classes in $\Ext^1_{\ZZ[\Gamma]}(G, A)$.  The map $G^0 \to G$ induces a map $\Ext^1_{\ZZ[\Gamma]}(G, A) \to \Ext^1_{\ZZ[\Gamma]}(G^0, A)$, fitting into the long exact sequence derived from applying $\Hom(\mbox{---}, A)$ to $G^0 \to G \to \pi_0(G)$:
$$\Ext^1_{\ZZ[\Gamma]}(G, A) \to \Ext^1_{\ZZ[\Gamma]}(G^0, A) \to \Ext^2_{\ZZ[\Gamma]}(\pi_0(G), A).$$
If we can show that $\Ext^2_{\ZZ[\Gamma]}(\pi_0(G), A) = 0$ then there will be an extension of $G$ by $A$ fitting into diagram \ref{extension-diagram}.
\todo{Stuff missing here.}

Now we show that $f : H\to G$, as above, together with a character $\psi : \ker {\bar f} \to \EE^\times$, defines a character sheaf on $G$. We will also show that the restriction of this character sheaf on $G$ to $G^0$ is precisely the character sheaf on $G^0$ defined by the pair $(f^0,\psi)$ as above.
%
Set $X \ceq \pi_0(G)\times_{\Spec{\Fq}} \Spec{\bFq}$. We will identify $X$ with $\pi_0(H)\times_{\Spec{\Fq}} \Spec{\bFq}$ using the base change of $\pi_0(f): \pi_0(H)\to \pi_0(G)$. For each $x\in X$, write ${\bar f}^x : {\bar H}^x \to {\bar G}^x$ for the restriction of ${\bar f}$ to ${\bar H}^x$, as a cover of ${\bar G}^x$. For each $x,y\in X$, let ${\bar m}_{x,y} : {\bar H}^x \times {\bar H}^{y} \to {\bar H}^{x+y}$ be the map obtained from ${\bar m}$ by restriction. Define ${\bar m}_{x} : A\to \Aut({\bar f}^x)$ by ${\bar m}_{x}(a): g \mapsto {\bar m}_{0,x}(a,g)$; then ${\bar m}_{x} : A\to \Aut({\bar f}^x)$ is an isomorphism.
\Clifton{I need to show that ${\bar m}_{x} : A\to \Aut({\bar f}^x)$ is an isomorphism.}

For each $x\in X$ let $\gcs{L}^x$ be the rank-$1$ local system on ${\bar G}^x$ determined by the finite etale cover ${\bar f}^x : {\bar H}^x \to {\bar G}^x$ and the character $\psi_x \ceq \psi \circ {\bar m}_x$.  Since ${\bar G} = \coprod_{x\in X} {\bar G}^x$ (disjoint union), this determines a constructible sheaf $\gcs{L}$ on ${\bar G}$, locally constant of rank-$1$ on each connected component of ${\bar G}$. Taking the case $x=0$ we observe that $\gcs{L}^0 =\gcs{E}$, the latter defined above. To finish the proof of the proposition we equip $\gcs{L}$ with isomorphisms $\mu : {\bar m}^* \gcs{L} \to \gcs{L} \boxtimes\gcs{L}$ and $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ satisfying conditions \ref{CS.1} and \ref{CS.2}.

Observe that ${\bar m}: {\bar G}\times {\bar G}\to {\bar G}$ is completely determined by the family of maps ${\bar m}_{x,y} : {\bar G}^x \times {\bar G}^{y} \to {\bar G}^{x+y}$. Accordingly, to define $\mu$ for $\gcs{L}$ it is sufficient to define isomorphisms $\mu_{x,y} : {\bar m}_{x,y}^*\gcs{L}^{x+y} \iso \gcs{L}^{x}\boxtimes \gcs{L}^{y}$ for all $x,y\in X$. To do that, note first that the local system $\gcs{L}^{x}\boxtimes \gcs{L}^{y}$ is defined by the following diagram.
\[
\xymatrix{
\EE^\times && \ar[ll]_{\hskip-20pt \psi_x\otimes \psi_y} \Aut({\bar f}^x)\times \Aut({\bar f}^y)  
& \ar@(ul,dl) & {\bar H}^x\times {\bar H}^y \ar[rr]^{{\bar f}^x\times {\bar f}^y} && {\bar G}^x\times {\bar G}^y\\ 
}
\]
On the other hand, the diagram for the local system ${\bar m}_{x,y}^* \gcs{L}^{x+y}$ is found by pulling-back the diagram for $\gcs{L}^{x+y}$ along ${\bar m}_{x,y} : {\bar H}^x\times{\bar H}^y \to {\bar H}^{x+y}$; the result is the middle horizontal diagram below, where we use the fact that the covering group of the middle arrow is $\Aut({\bar f}^{x+y})$, canonically.
\[
\xymatrix{ 
& \ar[dl]_{\psi_{x+y}} \Aut({\bar f}^{x+y})  
& \ar@(ul,dl) & {\bar H}^{x+y} \ar[rr]^{{\bar f}^{x+y}} && {\bar G}^{x+y}\\ 
\EE^\times & \ar@{.>}[l] \Aut({\bar f}^{x+y})  \ar@{=}[u] &  \ar@{.>}@(ul,dl) & \ar[u] {\bar H}^{x+y} \times_{{\bar G}^x\times{\bar G}^y} {\bar G}^x\times{\bar G}^y \ar[rr] && \ar[u]_{{\bar m}_{x,y}} {\bar G}^x\times {\bar G}^y\\
& \ar[lu]_{\psi_x\otimes \psi_y} \ar@{.>}[u] \Aut({\bar f}^x)\times \Aut({\bar f}^y)  
& \ar@(ul,dl) & \ar[u] {\bar H}^x\times {\bar H}^y \ar[rr]^{{\bar f}^x\times {\bar f}^y} && \ar@{=}[u] {\bar G}^x\times {\bar G}^y\\ 
}
\]
Now, the homomorphism from the covering group of ${\bar f}^x\times{\bar f}^y$ to the covering group of ${\bar f}^{x+y}$ induced by the composition $ {\bar H}^x\times {\bar H}^y \to {\bar H}^{x+y} \times_{{\bar G}^x\times{\bar G}^y} {\bar G}^x\times{\bar G}^y \to {\bar H}^{x+y}$ is precisely $({\bar m}_x(a),{\bar m}_y(b)) \mapsto {\bar m}_{x+y}(ab)$. Since this map commutes with the characters $\psi_x\otimes\psi_y$ and $\psi_{x+y}$ (so, the far-left triangle commutes in the diagram above) it follows that, for each $x,y\in X$ the diagram above defines a canonical isomorphism
$\mu_{x,y} : {\bar m}_{x,y}^* \gcs{L}^{x+y} \to \gcs{L}^x \boxtimes\gcs{L}^y$.
This defines $\mu: {\bar m}^* \gcs{L} \iso \gcs{L} \boxtimes\gcs{L}$. It is straightforward (but laborious) to show that the pair $(\gcs{L},\mu)$ satisfies condition \ref{CS.1}.

Now we turn to the definition of $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$. As above, we define this isomorphism through a family of isomorphisms on the connected components of ${\bar G}$. The restriction of $\Frob_{G}$ to ${\bar G}^x$ defines an isomorphism $\Frob_x : {\bar G}^x \to {\bar G}^{\Frob(x)}$. 
%\[
%\xymatrix{
%\ar[d]_{\Frob_x} {\bar G}^x \ar[r] & \ar[d]_{\Frob_{G}} {\bar G}\\
%{\bar G}^{\Frob(x)} \ar[r] & {\bar G}\\
%}
%\]
Pull back the finite etale covering in the diagram for $\gcs{L}^{\Frob(x)}$ along $\Frob_x$ and compare the result with the finite etale covering in the diagram for $\gcs{L}^{x}$.
\[
\xymatrix{ 
  && \ar[dll]_{\psi_{\Frob(x)}} \Aut({\bar f}^{\Frob(x)}) & \ar@(ul,dl) & {\bar H}^{\Frob(x)} \ar[rr]^{{\bar f}^{\Frob(x)}} && {\bar G}^{\Frob(x)}\\ 
\EE^\times & & \ar@{.>}[ll] \Aut({\bar f}^{\Frob(x)})  \ar@{=}[u] & \ar@{.>}@(ul,dl)  & \ar[u] {\bar H}^{\Frob(x)} \times_{{\bar G}^{\Frob(x)}} {\bar G}^x \ar[rr] && \ar[u]_{\Frob_{x}} {\bar G}^x\\
& &  \ar[ull]^{\psi_x}  \ar@{.>}[u] \Aut({\bar f}^{x}) & \ar@(ul,dl) & \ar[u] {\bar H}^x \ar[rr] && \ar@{=} [u] {\bar G}^x\\
}
\] 
The covering group of ${\bar H}^{\Frob(x)} \times_{{\bar G}^{\Frob(x)}} {\bar G}^x$ is isomorphic to $\Aut({\bar f}^{\Frob(x)})$, canonically, so $\Frob_x^* \gcs{L}^{\Frob(x)}$ is defined by the middle (horizontal) diagram, above.  We define the sheaf homomorphism $F_x : \Frob_x^* \gcs{L}^{\Frob(x)} \to \gcs{L}^x$ by the canonical morphism ${\bar H}^x \to  {\bar H}^{\Frob(x)} \times_{{\bar G}^{\Frob(x)}} {\bar G}^x \to $; to see that this defines a sheaf homomorphism it is sufficient to check that the character $\psi_x$ commutes with the  
The family of isomorphisms  $F_x : (\Frob_{G}^* \gcs{L})\vert_{{\bar G}^x} \iso \Frob_x^* \gcs{L}^{\Frob{x}} \to \gcs{L}^x$ now defines the isomorphism $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$. 
\Clifton{Add some detail here.}
This isomorphism is compatible with $\mu$ in the sense of condition~\ref{CS.2}. 
\end{proof}

\begin{remark}
We have seen that if $f : H\to G$ is a finite etale cover of $G$ by a smooth group scheme and if all geometric automorphisms of $f$ are fixed by Frobenius, then every character of $\ker f$ determines a character sheaf on $G$. However, it is not true that every character sheaf on $G$, in the sense of Section~\ref{sec:category} arises not all character sheaves on $G$ arise in this manner. 
\end{remark}
%\input{centralextensions}

\section{Main result regarding character sheaves}

%\input{snake}
\begin{theorem}\label{thm:snake}
If $G$ is a smooth abelian group scheme, locally of finite type over $\Fq$, and the abelian group $\pi_0(G)(\bFq)$ (the geometric component group) is finitely generated, then the trace of Frobenius homomorphism
\[
t_{G} : \CS(G)_{/\text{iso}} \to \Hom(G(\Fq),\EE^\times),
\]
from the Picard group of the category of character sheaves on $G$ to the group of characters of $G(\Fq)$, is an isomorphism. 
\end{theorem}

\begin{proof}
Consider the short exact sequence in the category of smooth group schemes, locally of finite type over $\Fq$, defining the component group scheme for $G$:
\begin{equation}\label{eq:pi0}
\xymatrix{
1 \ar[r] & G^0 \ar[r] & G \ar[r] & \pi_0(G) \ar[r] & 0.
}
\end{equation}
Let 
\[
\xymatrix{
& \ar[d] \ker t_{\pi_0(G)} & \ar@{.>}[d] \ker t_{G} & \ar[d] \ker t_{G^0} & \\
0\ar[r] & \ar[d]^{t_{\pi_0(G)}} \CS(\pi_0(G))_{/\text{iso}} \ar[r] & \ar[d]^{t_{G}} \CS(G)_{/\text{iso}} \ar[r] & \ar[d]^{t_{G^0}} \CS(G^0)_{/\text{iso}} \ar[r] & 0\\
0 \ar[r] & \ar[d] \Hom(\pi_0(G)(\Fq),\EE^\times) \ar[r] & \ar@{.>}[d] \Hom(G(\Fq),\EE^\times) \ar[r] & \ar[d] \Hom(G^0(\Fq),\EE^\times) \ar[r] & 0\\
& \coker t_{\pi_0(G)} & \coker t_{G} &  \coker t_{G^0} & \\
}
\]
be the commutative diagram of abelian groups obtained by applying Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.
By Proposition~\ref{prop:connected-1}, $\ker t_{G^0} =0$ and $\coker t_{G^0}=0$. By Propositions~\ref{prop:etale} and \ref{prop:X}, $\ker t_{\pi_0(G)}=0$ and $\coker t_{\pi_0(G)}=0$.

The sequence of character groups is left-exact: by Proposition~\ref{prop:pullback}, it is dual to the exact sequence of abelian groups
\begin{equation}\label{eq:pi0}
\xymatrix{
1 \ar[r] & G^0(\Fq) \ar[r] & G(\Fq) \ar[r] & \pi_0(G)(\Fq) \ar[r] & 0;
}
\end{equation}
since $\Hom(\ - \ ,\EE^\times)$ is left-exact, the sequence of character groups is left exact.

The sequence of Picard groups is right-exact:  it is exact at $\CS(G^0)_{/\text{iso}}$ by Proposition~\ref{prop:restriction}; and it is exact at $\CS(G)_{/\text{iso}}$ because the left-square commutes (by Proposition~\ref{prop:pullback}), the bottom sequence is exact at $\Hom(G(\Fq),\EE^\times)$ and $\coker t_{\pi_0(G)} =0$ (by Propositions~\ref{prop:etale} and \ref{prop:X}) and
\[
\image(\CS(\pi_0(G))_{/\text{iso}} \to \CS(G)_{/\text{iso}}) \subseteq \ker(\CS(G)_{/\text{iso}} \to \CS(G^0)_{/\text{iso}}),
\]
by the last part of Proposition~\ref{prop:pullback}. Specifically, suppose $\cs{L}$ is a character sheaf on $G$ that is trivial on $G^0$. Then $t^\Frob_\cs{L}\vert_{G^0(\Fq)} = t^\Frob_{\cs{L}^0} =0$, by Proposition~\ref{prop:pullback} again. Since the sequence of character groups is exact at $\Hom(G(\Fq),\EE^\times)$, there is some $\chi \in \Hom(\pi_0(G)(\Fq),\EE^\times)$ such that the pull-back of $\chi$ along $G(\Fq)\to \pi_0(G)(\Fq)$ is $t^\Frob_\cs{L}$. By Propositions~\ref{prop:etale} and \ref{prop:X}, there is a a character sheaf $\cs{L}_\chi$ on $\pi_0(G)$, unique up to isomorphism, such that $t^\Frob_{\cs{L}_\chi} = \chi$. By Proposition~\ref{prop:pullback} again, $\cs{L}$ is isomorphic to the image of $\cs{L}_\chi$ under the monoidal functor $\CS(\pi_0(G)) \to \CS(G)$.

It now follows immediately from the snake lemma that $t_{G}$ is an isomorphism of groups.
\end{proof}

\section{Application to characters of bounded depth}

%\input{GdeN}
Let $p$ be a prime number. Let $K$ be a local field with residue field $\Fq$, where $p$ divides $q$. Let $\OK$ be the ring of integers of $K$ and let $\pK$ be the maximal ideal in $\OK$.
%
In this section we introduce a group scheme $\GN{T}$ over $\Fq$ obtained by applying the Greenberg functor to the N\'eron lft-model for $T$ and establish some basic facts about $\GN{T}$

%\subsection{The N\'eron locally finite type model for $T$}

The lft-N\'eron model for $T$, denoted here by $\underline{T}$, is a separated, smooth, commutative group scheme locally of finite type over $\OK$ with generic fibre $T$, that enjoys the N\'eron mapping property: if $X$ is a smooth scheme over $\OK$ then every morphism $X_\eta \to T$ over $K$ extends uniquely to a morphism $X \to \underline{T}$. Equivalently, the N\'eron mapping property states that the function $\Hom_{\OK} (X,\underline{T}) \to \Hom_K(X_\eta,T)$, given by restriction to generic fibres, is a bijection; in particular, this implies $\underline{T}(\OK) = T(K)$.

For each $d\in \NN$, let $\underline{T}_{d}$ be the smooth group scheme over $\OK/\pK^{d+1}$ obtained from $\underline{T}$ by base change along $\OK \to \OK/\pK^{d+1}$. Observe that $\OK/\pK^{d+1}$ is an Artin ring and $\underline{T}_{d}$ is locally of finite type over $\OK/\pK^{d+1}$. 
%
Let $\GN{T}_{d}$ be the group scheme over $\Fp$ produced by applying the Greenberg functor to $\underline{T}_{d}$. (See \cite{Greenberg:2} and \cite[Ch. 9, \S 6]{BLR} for background on the Greenberg functor.) 
%Then $\GN{T}_d(\Fq) = \underline{T}(\OK/\pK^{d+1})$.

\begin{proposition}\label{prop:GN}
Fundamental properties of the group $\Fq$-scheme $\GN{T}_d$, for all $d\in \NN$:
\begin{enumerate}
 \labitem{(GNd.0)}{GN0} $\GN{T}_d^0$, the identity component of $\GN{T}_d$, is a commutative algebraic group over $\Fq$;
\labitem{(GNd.1)}{GNd} $\GN{T}_d$ is smooth and locally of finite type over $\Fq$;
\labitem{(GNd.2)}{pi0} $\pi_0(\GN{T}_d) = \pi_0(\underline{T}) \times_{\Spec{\OK}} \Spec{\Fq}$;
\labitem{(GNd.3)}{fg} the component group of $\GN{T}_d$ is geometrically finitely generated;
\labitem{(GNd.4)}{dFq} $\GN{T}_d(\Fq) = \underline{T}(\OK/\pK^{d+1})$, canonically;
\end{enumerate}
\end{proposition}

\begin{proof}
\Clifton{Proofs still missing, but all straightforward. I'll cite as much as I can, here.}
\end{proof}

%\input{application}
\begin{theorem}\label{thm:application}
Let $T$ be an algebraic torus over a non-Archimdean local field $K$. 
Let $\GN{T}_d$ and $\GN{T}$ be as above.
For each $d\in \NN$, the Picard group of the category of character sheaves on $\GN{T}_d$ is canonically isomorphic to the group of characters of $T(K)$ of depth at most $d$:
\[
\CS(\GN{T}_d)_{/\text{iso}} \iso \Hom_{\leq d}(T(K),\EE^\times).
\]
\end{theorem}

\begin{proof}
By \ref{GNd} and \ref{fg}, we may apply Theorem~\ref{thm:snake} to $\GN{T}_d$ which provides a canonical isomorphism 
\[
\CS(\GN{T}_d)_{/\text{iso}} \iso \Hom(\GN{T}_d(\Fq),\EE^\times).
\]
By \ref{dFq}, $\GN{T}_d(\Fq) \iso \underline{T}(\OK/\pK^{d+1})$ canonically.
To finish the proof we recall the filtration of $T(K)$ used to define depth  . . . $T(K)_{d+1}$
\Clifton{\color{red} Stuff missing here! I think we need congruence subgroups and JK's filtration of $T(K)$ for arbitrary tori.  Help!}
So, the theorem follows from the fact that
\[
\xymatrix{
0 \ar[r] & \underline{T}_{d+1}(\OK) \ar[r] &  \underline{T}(\OK) \ar[r] & \underline{T}(\OK/\pK^{d+1}) \ar[r] & 0\\
0\ar[r] & \ar@{=}[u] T(K)_{d+1} \ar[r] & \ar@{=}[u]T(K)_0 \ar[r] & \ar@{.}[u] T(K)/T(K)_{d+1}\ar[r] & 0 \\
}
\]
is exact.
\Clifton{\color{red} Is that true?!?!}
\end{proof}

\section{Application to admissible characters}

%\input{pro}
To conclude the paper we offer an interpretation of Theorem~\ref{thm:application} that makes no mention of depth.

\Clifton{Explain what happens as $d\in \NN$ varies.}
Suppose $d\leq d'$.

We may now assemble the group $\Fq$-schemes $\underline{T}_{d}$ into one glorious group pro-scheme over $\Fq$:
\begin{equation}\label{projlim}
\GN{T} \ceq \varprojlim_{d\in \NN} \GN{T}_{d}.
\end{equation}
This is the \cdef{Greenberg transform of the lft-N\'eron model of $T$}.

\Clifton{Prove that $\GN{T}$ is a scheme? Strictly speaking, we don't care about \ref{scheme}.}
\begin{proposition}
Fundamental properties of $\GN{T}$:
\begin{enumerate}
\labitem{(GN.0)}{scheme} $\GN{T}$ is a commutative group scheme over $\Fq$;
\labitem{(GN.1)}{T(K)} $\GN{T}(\Fq) = T(K)$, canonically.
\end{enumerate}
\end{proposition}

\begin{corollary}
\[
\CS(\GN{T})_{/\text{iso}} \iso \Hom_\text{ad}(T(K),\EE^\times)
\]
\end{corollary}

\begin{bibdiv}
\begin{biblist}

\bib{BBD}{article}{
   author={Be{\u\i}linson, A. A.},
   author={Bernstein, J.},
   author={Deligne, P.},
   title={Faisceaux pervers},
%   language={French},
   conference={
      title={Analyse et topologie sur les espaces singuliers (I)},
      address={Luminy},
      date={1981},
   },
   book={
      series={Ast\'erisque},
      volume={100},
      publisher={Soc. Math. France},
      place={Paris},
   },
   date={1982},
%   pages={5--171},
%   review={\MR{751966 (86g:32015)}},
}

\bib{BLR}{book}{
   author={Bosch, Siegfried},
   author={L{\"u}tkebohmert, Werner},
   author={Raynaud, Michel},
   title={N\'eron models},
   series={Ergebnisse der Mathematik und ihrer Grenzgebiete (3) [Results in
   Mathematics and Related Areas (3)]},
   volume={21},
   publisher={Springer-Verlag},
   place={Berlin},
   date={1990},
%   pages={x+325},
%   isbn={3-540-50587-3},
%   review={\MR{1045822 (91i:14034)}},
}

\bib{Brandal}{book}{
 author={Brandal, Willy},
 title={Commutative Rings whose Finitely Generated Modules Decompose},
 publisher={Springer-Verlag},
 date={1979},
 series={Lecture Notes in Mathematics}
 number={723}
}

\bib{Deligne:tensorielles}{article}{
   author={Deligne, P.},
   title={Cat\'egories tensorielles},
%   language={French, with English summary},
%   note={à Yu. I. Manin, en témoignage d'admiration},
   journal={Mosc. Math. J.},
   volume={2},
   date={2002},
   number={2},
   pages={227--248},
%   issn={1609-3321},
%   review={\MR{1944506 (2003k:18010)}},
}

\bib{Deligne:Weil2}{article}{
   author={Deligne, Pierre},
   title={La conjecture de Weil. II},
%   language={French},
   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
   number={52},
   date={1980},
   pages={137--252},
%   issn={0073-8301},
%   review={\MR{601520 (83c:14017)}},
}

\bib{Greenberg:2}{article}{
   author={Greenberg, Marvin J.},
   title={Schemata over local rings. II},
   journal={Ann. of Math. (2)},
   volume={78},
   date={1963},
   pages={256--266},
%   issn={0003-486X},
%   review={\MR{0156855 (28 \#98)}},
}

\bib{Laumon}{article}{
   author={Laumon, G.},
   title={Transformation de Fourier, constantes d'\'equations fonctionnelles
   et conjecture de Weil},
%   language={French},
   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
   number={65},
   date={1987},
   pages={131--210},
%   issn={0073-8301},
%   review={\MR{908218 (88g:14019)}},
}

\bib{SGA4.5}{book}{
   author={Deligne, P.},
   title={Cohomologie \'etale},
   series={Lecture Notes in Mathematics, Vol. 569},
   note={S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois-Marie 1963-64 SGA
   4$\frac{1}{2}$; 
   Avec la collaboration de J. F. Boutot, A. Grothendieck, L. Illusie et J.
   L. Verdier},
   publisher={Springer-Verlag},
   place={Berlin},
%date={4h},
   date={1977},
   pages={iv+312pp},
%   review={\MR{0463174 (57 \#3132)}},
}

\bib{SGA7.2}{book}{
   title={Groupes de monodromie en g\'eom\'etrie alg\'ebrique. II},
%   language={French},
 author={Deligne, P.},
 author={Katz, N.},
   series={Lecture Notes in Mathematics, Vol. 340},
   note={S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois-Marie 1967--1969
   (SGA 7 II);
   Dirig\'e par P. Deligne et N. Katz},
   publisher={Springer-Verlag},
   place={Berlin},
   date={1973},
   pages={x+438},
%   review={\MR{0354657 (50 \#7135)}},
}

\bib{Tate:thesis}{article}{
   author={Tate, J. T.},
   title={Fourier analysis in number fields, and Hecke's zeta-functions},
   conference={
      title={Algebraic Number Theory (Proc. Instructional Conf., Brighton,
      1965)},
   },
   book={
      publisher={Thompson, Washington, D.C.},
   },
   date={1967},
   pages={305--347},
   review={\MR{0217026 (36 \#121)}},
}

\bib{vdG&M}{book}{
author={van der Geer},
author={Moonen},
title={Abelian Varieties},
note={http://staff.science.uva.nl/$\sim$bmoonen/boek/BookAV.html}
}

\bib{Xarles}{article}{
   author={Xarles, Xavier},
   title={The scheme of connected components of the N\'eron model of an algebraic torus},
   journal={J. Reine Angew. Math.},
   volume={437},
   date={1993},
   pages={167--179},
%   issn={0075-4102},
%   review={\MR{1212256 (94d:14044)}},
%   doi={10.1515/crll.1993.437.167},
}

\end{biblist}
\end{bibdiv}

\end{document}

### 2013-06-22 shanghai.tex
Some fixes to proof of local constancy in pullback

@@
 We start by showing that ${\bar f}^*\gcs{L}$ is locally constant on connected components of ${\bar H}$.
-Let $c_j :{\bar H}^j \hookrightarrow {\bar H}$ be any connected component.
-Then there is a unique connected component $c_i : {\bar G}^i$ of ${\bar G}$ such that ${\bar f}: {\bar H} \to {\bar G}$ factors through ${\bar H}^j \hookrightarrow {\bar G}^i$, thus defining ${\bar f}^j : {\bar H}^j \to {\bar G}^i$.
-Indeed, $i$ is the image of $j$ under the group homomorphism $\pi_0({\bar G}) \to \pi_0({\bar H})$ obtained by applying the functor $\pi_0$ to ${\bar f}$; see \cite{vdG&M}*{III, 3.28}, for example.\Clifton{Replace with a better reference, eventually.} Since $\cs{L}$ is a character sheaf, $\gcs{L}$ is locally constant on the connect components of ${\bar G}$; thus, there is a finite etale covering $a_i : X_i \to {\bar G}^i$ such that $a_i^* (\gcs{L}\vert_{\bar G}^i)$ is constant.
+Let $c_j :{\bar H}^j \hookrightarrow {\bar H}$ be any connected component and let $i$ be the image of $j$ under the group homomorphism $\pi_0({\bar G}) \to \pi_0({\bar H})$ obtained by applying the functor $\pi_0$ to ${\bar f}$; see \cite{vdG&M}*{III, 3.28}, for example.\Clifton{Replace with a better reference, eventually.}  Write $c_i : \bar{G}^i \hookrightarrow \bar{G}$ for the inclusion of $\bar{G}^i$ and ${\bar f}^j : {\bar H}^j \to {\bar G}^i$ for the restriction of $f$ to $\bar{H}^j$.
+Since $\cs{L}$ is a character sheaf, $\gcs{L}$ is locally constant on the connect components of ${\bar G}$; thus, there is a finite etale covering $a_i : X_i \to {\bar G}^i$ such that $a_i^* (\gcs{L}\vert_{\bar G^i})$ is constant.
 Let $b_j : Y_j \to {\bar H}^j$ be the pull-back of $a_i$ along ${\bar f}^j$; let $g_j : Y_j \to X_i$ be the map opposite ${\bar f}^j$.
@@
 \[
-b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right) = ({\bar f}\circ c_j \circ b_j)^*\gcs{L} = (c_i\circ a_i\circ g_j)^*\gcs{L} = g_j^* a_i^* (\gcs{L}\vert_{\bar G}^i).
-\]
-Since $a_i^* (\gcs{L}\vert_{\bar G}^i)$ is a constant sheaf and since the pull-back of a constant sheaf (along $g_j$, in this case) is a constant sheaf, it follows that $b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right)$ is a constant sheaf.
+b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right) = ({\bar f}\circ c_j \circ b_j)^*\gcs{L} = (c_i\circ a_i\circ g_j)^*\gcs{L} = g_j^* a_i^* (\gcs{L}\vert_{\bar G^i}).
+\]
+Since $a_i^* (\gcs{L}\vert_{\bar G^i})$ is a constant sheaf and since the pull-back of a constant sheaf (along $g_j$, in this case) is a constant sheaf, it follows that $b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right)$ is a constant sheaf.
 Thus, ${\bar f}^*\gcs{L}$ is locally constant on ${\bar H}^j$.

### 2013-06-22 shanghai.tex
Fix etale typo

@@
 To see why this is so, consider the category \cdef{$\CS_0(G)$} of pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$ and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ satisfies condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$ are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}.
-Let $b : {\bar G} \to G$ be base change (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$).
+\David{Should we move this definition since it will be important elsewhere?} Let $b : {\bar G} \to G$ be base change (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$).
 The proof of Proposition~\ref{prop:pullback} adapts (simplifies, in fact) to show that  $b^* : \CS_0(G) \to \CS(G)$ is a monoidal functor.
@@
 \begin{proposition}\label{prop:etale}
-If $G$ is a commutative group scheme etale over $\Fq$ and $G(\bFq)$ is finitely generated then there is a canonical isomorphism 
+If $G$ is a commutative \'etale group scheme over $\Fq$ and $G(\bFq)$ is finitely generated then there is a canonical isomorphism 
 \[

### 2013-06-22 shanghai.tex
Fixing some typos

@@
 Since the character sheaves that appear in this paper are not quite an instance of those defined by George Luzstig, who coined the term, we begin by explaining what we mean by `character sheaves' in this paper.
-Let $G$ be a smooth commutative group scheme locally of finite type over $\Fq$; $G$ need not be reductive, connected, nor of finite type over $\Fq$.
+Let $G$ be a smooth commutative group scheme locally of finite type over $\Fq$ \David{I think our notation is clearer if we use $k$ rather than $\Fq$}; $G$ need not be reductive, connected, nor of finite type over $\Fq$.
 Fix a prime $\ell$ that does not divide $q$.
@@
 To simplify notation, we set $W_\Fq \ceq \Weil(\bFq/\Fq)$ and $G(\bFq)^* \ceq \Hom_\text{grp}(G(\bFq),\EE^\times)$.
-Recall the equivalence between etale group schemes over $\Fq$ and the category of groups equipped with a continuous action of $\Gal(\bFq/\Fq)$ (for the discrete topology on the group), given by $G \mapsto G(\bFp)$.
+Recall the equivalence between etale group schemes over $\Fq$ and the category of groups equipped with a continuous action of $\Gal(\bFq/\Fq)$ (for the discrete topology on the group), given by $G \mapsto G(\bFq)$.
 Under this equivalence any character sheaf $\cs{L} =(\gcs{L},\mu,F)$ on $G$ corresponds to:
@@
 commutes, for all $x,y,z\in G(\bFp)$; and 
-\labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $F_{x} \ceq x^*F: \gcs{L}_{\Frob(x)} \to \gcs{L}$ 
+\labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $F_{x} \ceq x^*F: \gcs{L}_{\Frob(x)} \to \gcs{L}_x$ 
 \Clifton{\textdbend There's hidden subtlety here too: maybe I should explain which Frobenius this is and how it acts. }
@@
 Since $G(\bFq)$ is finitely-generated abelian, it admits a decomposition $G(\bFq) \iso G(\bFq)_\text{free} \oplus G(\bFq)_\text{tors}$ such that $G(\bFq)_\text{tors}$ is finite.
-Let $x_1, \ldots , x_r$ be a basis for the free part $G(\bFq)_\text{free}$ of $G(\bFq)$ and let $y_1, \ldots , y_t$ be a generators for the torsion part of $G(\bFq)$ corresponding to the decomposition $G(\bFq)_\text{tors} \iso \oplus_{j=1}^t \ZZ/m_1\ZZ$, with $m_1\vert m_2\vert \cdots \vert m_t$.
+Let $x_1, \ldots , x_r$ be a basis for the free part $G(\bFq)_\text{free}$ of $G(\bFq)$ and let $y_1, \ldots , y_t$ be a generators for the torsion part of $G(\bFq)$ corresponding to the decomposition $G(\bFq)_\text{tors} \iso \oplus_{j=1}^t \ZZ/m_j\ZZ$, with $m_j \vert m_{j+1}$.
 For each such $x_i$ pick $s(x_i)\in \gcs{L}_{x_i}$; for each such $y_j$ pick $s(y_j) \in \gcs{L}_{y_j}$; also set $s({\bar e}) \ceq 0 \in \gcs{L}_{\bar e}$.
@@
 Let us review how line bundles on $G^0$ determine character sheaves on $G^0$.
-Up to isomorphism, line bundles on $G^0$ may be apprehended in terms of pairs $(\pi,\psi)$, where $\pi : B\to G^0$ is a finite etale morphism of algebraic groups and a character $\psi : A\to \EE^\times$, where $\Gal(\bFq/\Fq)$ acts trivially on $A \ceq \ker {\bar \pi}$, as summarized by the following diagram.
+Up to isomorphism, line bundles on $G^0$ may be apprehended in terms of pairs $(\pi,\psi)$, \David{Aren't there line bundles which are not character sheaves, for which $B$ is not an algebraic group?} where $\pi : B\to G^0$ is a finite etale morphism of algebraic groups and a character $\psi : A\to \EE^\times$, where $\Gal(\bFq/\Fq)$ acts trivially on $A \ceq \ker {\bar \pi}$, as summarized by the following diagram.
 \begin{equation}\label{E}
@@
 As pictured above, the kernel of this pull-back is $A\times A$; indeed, $A\times A\to B\times B$ is the pull-back of $A\to B$ along $m_{B}$.
-Use this Cartesian square to define a character (the dotted arrow, above) of $A\times A$; that is, define $A\times A\to \EE^\times$ by the composition of $A\times A$ and $\psi : A\to \EE^\times$.
+Use this Cartesian square to define a character (the dotted arrow, above) of $A\times A$; that is, define $A\times A\to \EE^\times$ by the composition of $A\times A \to A$ and $\psi : A\to \EE^\times$.
 Note that this character is $\psi \otimes \psi : A\times A\to \EE^\times$.
@@
 
-For each $x\in X$ let $\gcs{L}^x$ be the rank-$1$ local system on ${\bar G}^x$ determined by the finite etale cover ${\bar f}^x : {\bar H}^x \to {\bar G}^x$ and the character $\psi_x \ceq \psi \circ {\bar m}_x$.
+For each $x\in X$ let $\gcs{L}^x$ be the rank-$1$ local system on ${\bar G}^x$ determined by the finite etale cover ${\bar f}^x : {\bar H}^x \to {\bar G}^x$ and the character $\psi_x \ceq \psi \circ {\bar m}_x^{-1}$.
 Since ${\bar G} = \coprod_{x\in X} {\bar G}^x$ (disjoint union), this determines a constructible sheaf $\gcs{L}$ on ${\bar G}$, locally constant of rank-$1$ on each connected component of ${\bar G}$.

### 2013-06-22 shanghai.tex
Replace F_q with k

@@
 \newcommand{\Qp}{\mathbb{Q}_p}
-\newcommand{\Fp}{\mathbb{F}_p}
-\newcommand{\bFq}{{\mathbb{\bar F}_q}}
-\newcommand{\Fq}{{\mathbb{F}_q}}
-\newcommand{\Fqm}{{\mathbb{F}_{q^m}}}
-\newcommand{\bFp}{{\mathbb{\bar F}_p}}
+%\newcommand{\Fp}{\mathbb{F}_p}
+\newcommand{\bFq}{\bar{k}}
+\newcommand{\Fq}{k}
+\newcommand{\Fqm}{k_m}
+%\newcommand{\bFp}{{\mathbb{\bar F}_p}}
 
@@
 \newcommand{\bGN}[1]{{\bar{\textswab{#1}}}}
+\newcommand{\TT}{\underline{T}}
 \newcommand{\invlim}[1]{\lim\limits_{\overleftarrow{#1}}}
@@
 Let $T$ be an algebraic torus defined over $K$.
-Let $\underline{T}$ be a N\'eron model for $T$; recall that this is a smooth group scheme locally of finite type over $\OK$.
-For each non-negative integer $d$, let $\GN{T}_d$ be the Greenberg transform of $\underline{T} \otimes \OK/\pK^{d+1}$; the commutative group scheme $\GN{T}_d$ plays the r\^{o}le of $G$, above.
+Let $\TT$ be a N\'eron model for $T$; recall that this is a smooth group scheme locally of finite type over $\OK$.
+For each non-negative integer $d$, let $\GN{T}_d$ be the Greenberg transform of $\TT \otimes \OK/\pK^{d+1}$; the commutative group scheme $\GN{T}_d$ plays the r\^{o}le of $G$, above.
 
@@
 \begin{enumerate}
-\labitem{(cs.0)}{cs.0} an indexed set of one-dimensional $\EE$-vector spaces $\gcs{L}_x \ceq x^*\gcs{L}$, as $x$ runs over $G(\bFp)$; 
-\labitem{(cs.1)}{cs.1} an indexed set of isomorphisms $\mu_{x,y}  \ceq (x \times y)^*\mu : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes \gcs{L}_{y}$, for all $x,y \in G(\bFp)$, such that
+\labitem{(cs.0)}{cs.0} an indexed set of one-dimensional $\EE$-vector spaces $\gcs{L}_x \ceq x^*\gcs{L}$, as $x$ runs over $G(\bFq)$; 
+\labitem{(cs.1)}{cs.1} an indexed set of isomorphisms $\mu_{x,y}  \ceq (x \times y)^*\mu : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes \gcs{L}_{y}$, for all $x,y \in G(\bFq)$, such that
 \[
@@
 \]
-commutes, for all $x,y,z\in G(\bFp)$; and 
+commutes, for all $x,y,z\in G(\bFq)$; and 
 \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $F_{x} \ceq x^*F: \gcs{L}_{\Frob(x)} \to \gcs{L}_x$ 
@@
 \]
-commutes, for all $x,y\in G(\bFp)$.
+commutes, for all $x,y\in G(\bFq)$.
 \end{enumerate}
@@
 
-Since the action of $\Gal(\bFq/\Fq)$ is continuous, there is an $m$ so that $\Frob^m$ acts trivially on $X$; write $\Gamma_m$ for $\Gal(\Fqm/\Fq)$.
+Since the action of $\Gal(\bFq/\Fq)$ is continuous, there is an $m$ so that $\Frob^m$ acts trivially on $X$; write $\Fqm$ for the degree $m$ extension of $\Fq$ and $\Gamma_m$ for $\Gal(\Fqm/\Fq)$.
 Since $T^m-1$ factors as a squarefree product of cyclotomic polynomials, the Chinese remainder theorem expresses $\ZZ[\Gamma_m]$ as a product of $\ZZ[\zeta_d]$ for $d$ dividing $m$.
@@
 
-The next step is to show that $\pi: B \to G^0$ extends to a finite etale morphism of group schemes $f: H\to G$, smooth and locally of finite type over $\Fq$, in such a way that $H^0 = B$ (so, $B$ is the identity component of $H$) and $f^0 =\pi$ (so, the restriction of $f$ to $H^0$ is a finite etale cover of $G^0$) and $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism of component groups.
-\Clifton{David, this paragraph is the lemma you were working on. I'm worried that I won't have time to work on this before your talk, so please keep going, if you can.}
+The next step is to show that $\pi: B \to G^0$ extends to a finite etale morphism of group schemes $f: H\to G$, smooth and locally of finite type over $\Fq$, in such a way that $H^0 = B$, $f^0 =\pi$ and $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism of component groups.
 \begin{equation} \label{extension-diagram}
@@
 where all rows and columns are exact and all maps are defined over $\Fq$.
-Extensions of $G^0$ by $A$, such as $A \to H^0 \to G^0$, correspond to classes in $\Ext^1_{\ZZ[\Gamma]}(G^0, A)$.
-Similarly, extensions of $G$ by $A$ correspond to classes in $\Ext^1_{\ZZ[\Gamma]}(G, A)$.
-The map $G^0 \to G$ induces a map $\Ext^1_{\ZZ[\Gamma]}(G, A) \to \Ext^1_{\ZZ[\Gamma]}(G^0, A)$, fitting into the long exact sequence derived from applying $\Hom(\mbox{---}, A)$ to $G^0 \to G \to \pi_0(G)$:
-$$\Ext^1_{\ZZ[\Gamma]}(G, A) \to \Ext^1_{\ZZ[\Gamma]}(G^0, A) \to \Ext^2_{\ZZ[\Gamma]}(\pi_0(G), A).$$
-If we can show that $\Ext^2_{\ZZ[\Gamma]}(\pi_0(G), A) = 0$ then there will be an extension of $G$ by $A$ fitting into diagram \ref{extension-diagram}.
+We will do so by passing back and forth between group schemes over $\Fq$ and their $\bFq$-points.
+Extensions of $G^0(\bFq)$ by $A(\bFq)$, such as $A(\bFq) \to H^0(\bFq) \to G^0(\bFq)$, correspond to classes in $\Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))$.
+Similarly, extensions of $G(\bFq)$ by $A(\bFq)$ correspond to classes in $\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq))$.
+The map $G^0(\bFq) \to G(\bFq)$ induces a map $\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))$, fitting into the long exact sequence derived from applying $\Hom(\mbox{---}, A(\bFq))$ to $G^0(\bFq) \to G(\bFq) \to \pi_0(G)(\bFq)$:
+$$\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)).$$
+We now show that $\Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)) = 0$.  
 \todo{Stuff missing here.}
@@
 
-The lft-N\'eron model for $T$, denoted here by $\underline{T}$, is a separated, smooth, commutative group scheme locally of finite type over $\OK$ with generic fibre $T$, that enjoys the N\'eron mapping property: if $X$ is a smooth scheme over $\OK$ then every morphism $X_\eta \to T$ over $K$ extends uniquely to a morphism $X \to \underline{T}$.
-Equivalently, the N\'eron mapping property states that the function $\Hom_{\OK} (X,\underline{T}) \to \Hom_K(X_\eta,T)$, given by restriction to generic fibres, is a bijection; in particular, this implies $\underline{T}(\OK) = T(K)$.
-
-For each $d\in \NN$, let $\underline{T}_{d}$ be the smooth group scheme over $\OK/\pK^{d+1}$ obtained from $\underline{T}$ by base change along $\OK \to \OK/\pK^{d+1}$.
-Observe that $\OK/\pK^{d+1}$ is an Artin ring and $\underline{T}_{d}$ is locally of finite type over $\OK/\pK^{d+1}$.
+The lft-N\'eron model for $T$, denoted here by $\TT$, is a separated, smooth, commutative group scheme locally of finite type over $\OK$ with generic fibre $T$, that enjoys the N\'eron mapping property: if $X$ is a smooth scheme over $\OK$ then every morphism $X_\eta \to T$ over $K$ extends uniquely to a morphism $X \to \TT$.
+Equivalently, the N\'eron mapping property states that the function $\Hom_{\OK} (X,\TT) \to \Hom_K(X_\eta,T)$, given by restriction to generic fibres, is a bijection; in particular, this implies $\TT(\OK) = T(K)$.
+
+For each $d\in \NN$, let $\TT_{d}$ be the smooth group scheme over $\OK/\pK^{d+1}$ obtained from $\TT$ by base change along $\OK \to \OK/\pK^{d+1}$.
+Observe that $\OK/\pK^{d+1}$ is an Artin ring and $\TT_{d}$ is locally of finite type over $\OK/\pK^{d+1}$.
 %
-Let $\GN{T}_{d}$ be the group scheme over $\Fp$ produced by applying the Greenberg functor to $\underline{T}_{d}$.
-(See \cite{Greenberg:2} and \cite[Ch.
-9, \S 6]{BLR} for background on the Greenberg functor.)
-%Then $\GN{T}_d(\Fq) = \underline{T}(\OK/\pK^{d+1})$.
+Let $\GN{T}_{d}$ be the group scheme over $\Fq$ produced by applying the Greenberg functor to $\TT_{d}$. (See \cite{Greenberg:2} and \cite[Ch. 9, \S 6]{BLR} for background on the Greenberg functor.) 
+%Then $\GN{T}_d(\Fq) = \TT(\OK/\pK^{d+1})$.
 
@@
 \labitem{(GNd.1)}{GNd} $\GN{T}_d$ is smooth and locally of finite type over $\Fq$;
-\labitem{(GNd.2)}{pi0} $\pi_0(\GN{T}_d) = \pi_0(\underline{T}) \times_{\Spec{\OK}} \Spec{\Fq}$;
+\labitem{(GNd.2)}{pi0} $\pi_0(\GN{T}_d) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$;
 \labitem{(GNd.3)}{fg} the component group of $\GN{T}_d$ is geometrically finitely generated;
-\labitem{(GNd.4)}{dFq} $\GN{T}_d(\Fq) = \underline{T}(\OK/\pK^{d+1})$, canonically;
+\labitem{(GNd.4)}{dFq} $\GN{T}_d(\Fq) = \TT(\OK/\pK^{d+1})$, canonically;
 \end{enumerate}
@@
 \]
-By \ref{dFq}, $\GN{T}_d(\Fq) \iso \underline{T}(\OK/\pK^{d+1})$ canonically.
-To finish the proof we recall the filtration of $T(K)$ used to define depth  . . . $T(K)_{d+1}$
-\Clifton{\color{red} Stuff missing here! I think we need congruence subgroups and JK's filtration of $T(K)$ for arbitrary tori.  Help!}
-So, the theorem follows from the fact that
-\[
-\xymatrix{
-0 \ar[r] & \underline{T}_{d+1}(\OK) \ar[r] &  \underline{T}(\OK) \ar[r] & \underline{T}(\OK/\pK^{d+1}) \ar[r] & 0\\
-0\ar[r] & \ar@{=}[u] T(K)_{d+1} \ar[r] & \ar@{=}[u]T(K)_0 \ar[r] & \ar@{.}[u] T(K)/T(K)_{d+1}\ar[r] & 0 \\
-}
-\]
-is exact.
-\Clifton{\color{red} Is that true?!?!}
+By \ref{dFq}, $\GN{T}_d(\Fq) \iso \TT(\OK/\pK^{d+1})$ canonically.
+To finish the proof we recall that the filtration of $T(K)$ used to define depth has the property
+that $\TT(\OK/\pK^{d+1}) \cong T(K) / T(K)_d$ \cite[Prop 5.2]{Yu}.  Thus characters of $\GN{T}_d(\Fq)$ are in bijection with characters of $T(K)$ vanishing on $T(K)_d$.
 \end{proof}
@@
 
-We may now assemble the group $\Fq$-schemes $\underline{T}_{d}$ into one glorious group pro-scheme over $\Fq$:
+We may now assemble the group $\Fq$-schemes $\TT_{d}$ into one glorious group pro-scheme over $\Fq$:
 \begin{equation}\label{projlim}
@@
 
+\bib{Yu}{article}{
+   author={Yu, Jiu-Kang},
+   title={Smooth models associated to concave functions in Bruhat-Tits theory}
+}
+
 \end{biblist}

### 2013-06-24 shanghai.tex
Added proof of Ext^2 triviality and that the resulting diagram is of group schemes

@@
 We now show that $\Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)) = 0$.
-\todo{Stuff missing here.}
+
+It suffices to show that $\pi_0(G)(\bFq)$ has a two-term resolution by injective $\ZZ[\Gamma]$-modules.
+Since the action of $\Gamma$ on $\pi_0(G)(\bFq)$ is continuous, it factor through a finite quotient $\Gamma_m = \Gamma / H_m$.
+Any product of Dedekind domains has cohomological dimension $1$ \cite[?]{?}, so $\pi_0(G)(\bFq)$ has a two term resolution by injective $\ZZ[\Gamma_m]$-modules.
+Let $I$ be one of these modules: we need to show that $I$ is injective as a $\ZZ[\Gamma]$-module.
+Consider the universal diagram for injectivity:
+\[
+\xymatrix{
+& B \\
+I & A \ar@{>->}[u] \ar[l]_{a}
+}\]
+where $A$ and $B$ are arbitrary $\ZZ[\Gamma]$-modules.
+Since $H_m$ acts trivially on $I$, $I_{H_m}A := \langle (\gamma-1)a : \gamma \in H_m, a \in A \rangle \subseteq \ker(a).$  Since $B / I_{H_m}B \cong B \otimes_A A / I_{H_m}A$, we get
+\[
+\xymatrix{
+& B/I_{H_m}B \ar@{..>}[dl] & B \ar@{->>}[l] \\
+I & A/I_{H_m}A \ar@{>->}[u] \ar[l] & A \ar@{>->}[u] \ar@{->>}[l]
+}\]
+The dotted arrow exists since $I$ is injective as a $\ZZ[\Gamma_m]$-module, and the outer diagram shows that $I$ is injective as a $\ZZ[\Gamma]$-module.
+
+We therefore have the existence of diagram \eqref{extension-diagram} at the level of $\bFq$-points.
+This expresses $H(\bFq)$ as a disjoint union of translates of $B(\bFq)$; by transport of structure we may take $H$ to be a group scheme over $\bFq$.
+Similarly, the restriction of $f$ to each component of $H$ is a morphism of schemes, and thus $f$ is as well.
+Finally, the whole diagram descends to a diagram of $\Fq$-schemes since the $\bFq$-points of the objects come equipped with continuous $\Gamma$-actions, and the morphisms are $\Gamma$-equivariant.
 

### 2013-06-24 shanghai.tex
Added lots of newlines

@@
 \begin{abstract}
-We study the category of character sheaves on smooth commutative group schemes $G$ locally of finite type over finite fields $\mathbb{F}_q$.
-Assuming that the geometric component group of $G$ is finitely-generated, we show that the group of isomorphism classes of character sheaves on $G$ is canonically isomorphic to the group of characters of $G(\mathbb{F}_q)$.
-We use this result to exhibit an isomorphism between admissible characters of $T(K)$ and isomorphism classes of character sheaves on the Greenberg transform of the Néron model of $T$, where $K$ is any non-Archimdean local field and $T$ is any algebraic torus over $K$.
+  We study the category of character sheaves on smooth commutative
+  group schemes $G$ locally of finite type over finite fields
+  $\mathbb{F}_q$. Assuming that the geometric component group of $G$
+  is finitely-generated, we show that the group of isomorphism classes
+  of character sheaves on $G$ is canonically isomorphic to the group
+  of characters of $G(\mathbb{F}_q)$. We use this result to exhibit an
+  isomorphism between admissible characters of $T(K)$ and isomorphism
+  classes of character sheaves on the Greenberg transform of the Néron
+  model of $T$, where $K$ is any non-Archimdean local field and $T$ is
+  any algebraic torus over $K$.
 \end{abstract}
@@
 \begin{quotation}
-{\it Concerning the characters of $k^*$ [the multiplicative group of a $\mathfrak{p}$-adic field], the situation is different from that of $k^+$.
-First of all, we are interested in continuous multiplicative maps $\alpha \mapsto c(\alpha)$ of $k^*$ into the complex numbers, not only in the bounded ones, and shall call such a map a quasi-character, reserving the word ``character'' for the conventional character of absolute value $1$.
-Secondly,
-we shall find no model for the group of quasi-characters, or even for the group of characters, though such a model would be of the utmost importance.}  \cite{Tate:thesis}*{\S 2.3}
+    {\it Concerning the characters of $k^*$ [the
+    multiplicative group of a $\mathfrak{p}$-adic field], the
+    situation is different from that of $k^+$.  First of all, we are
+    interested in continuous multiplicative maps $\alpha \mapsto
+    c(\alpha)$ of $k^*$ into the complex numbers, not only in the
+    bounded ones, and shall call such a map a quasi-character,
+    reserving the word ``character'' for the conventional character of
+    absolute value $1$. Secondly, we shall find no model for the group
+    of quasi-characters, or even for the group of characters, though
+    such a model would be of the utmost importance.}
+  \cite{Tate:thesis}*{\S 2.3}
 \end{quotation}
 \noindent
-In this paper we show that the monidal category of character sheaves on the Greenberg transform of the locally finite type Neron model of $T$ provides an elegant, canonical model for the group of (quasi-)characters of $T(K)$, where $K$ is any non-Archimedean local field and $T$ is any algebraic torus over $K$.
-
-Since the character sheaves that appear in this paper are not quite an instance of those defined by George Luzstig, who coined the term, we begin by explaining what we mean by `character sheaves' in this paper.
-Let $G$ be a smooth commutative group scheme locally of finite type over $\Fq$ \David{I think our notation is clearer if we use $k$ rather than $\Fq$}; $G$ need not be reductive, connected, nor of finite type over $\Fq$.
-Fix a prime $\ell$ that does not divide $q$.
-By a {character sheaf} on $G$ we mean a triple $\cs{L}\ceq (\gcs{L},\mu,F)$ where $\gcs{L}$ is a constructible $\ell$-adic sheaf $\gcs{L}$ on the \'etale site of ${\bar G} \ceq G \times_{\Spec\Fq} \Spec{\bFq}$, locally constant of rank-$1$ on every connected component of ${\bar G}$, equipped with an isomorphism $\mu: m^* \gcs{L} \to  \gcs{L}\boxtimes \gcs{L}$, where $m : G\times G \to G$ is the group operation for $G$, and an isomorphism $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$, where $\Frob_{G}$ is the Frobenius automorphism on ${\bar G}$, satisfying natural compatibility conditions with $\mu$; these compatibility conditions are explained below.
-
-Character sheaves on $G$ form a category, denoted by $\CS(G)$.
-In fact, $\CS(G)$ is a rigid symmetric monoidal category, so isomorphism classes of character sheaves on $G$ form a group, denoted by $\CS(G)_{/\text{iso}}$; this is the Picard group of the category of character sheaves on $G$.
-Our application of character sheaves to characters of algebraic tori over non-Archimedean local fields rests on the Picard group of character sheaves on $G$, for certain smooth group schemes $G$.
-
-We now say a few words about the commutative group schemes locally of finite type over $\Fq$ that appear in our geometrization of admissible characters of algebraic tori over local fields.
-Let $K$ be a non-Archimedean local field with residual field $\Fq$; we place no restrictions on the characteristic of $K$ -- in particular, it may be $0$ or not.
-Write $\OK$ for ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$.
-Let $T$ be an algebraic torus defined over $K$.
-Let $\TT$ be a N\'eron model for $T$; recall that this is a smooth group scheme locally of finite type over $\OK$.
-For each non-negative integer $d$, let $\GN{T}_d$ be the Greenberg transform of $\TT \otimes \OK/\pK^{d+1}$; the commutative group scheme $\GN{T}_d$ plays the r\^{o}le of $G$, above.
+In this paper we show that the monidal category of character sheaves
+on the Greenberg transform of the locally finite type Neron model of
+$T$ provides an elegant, canonical model for the group of
+(quasi-)characters of $T(K)$, where $K$ is any non-Archimedean local
+field and $T$ is any algebraic torus over $K$.
+
+Since the character sheaves that appear in this paper are not quite an
+instance of those defined by George Luzstig, who coined the term, we
+begin by explaining what we mean by `character sheaves' in this
+paper. Let $G$ be a smooth commutative group scheme locally of finite
+type over $\Fq$ \David{I think our notation is clearer if we use $k$
+  rather than $\Fq$}; $G$ need not be reductive, connected, nor of
+finite type over $\Fq$. Fix a prime $\ell$ that does not divide
+$q$. By a {character sheaf} on $G$ we mean a triple $\cs{L}\ceq
+(\gcs{L},\mu,F)$ where $\gcs{L}$ is a constructible $\ell$-adic sheaf
+$\gcs{L}$ on the \'etale site of ${\bar G} \ceq G \times_{\Spec\Fq}
+\Spec{\bFq}$, locally constant of rank-$1$ on every connected
+component of ${\bar G}$, equipped with an isomorphism $\mu: m^*
+\gcs{L} \to \gcs{L}\boxtimes \gcs{L}$, where $m : G\times G \to G$ is
+the group operation for $G$, and an isomorphism $F : \Frob_{G}^*
+\gcs{L} \to \gcs{L}$, where $\Frob_{G}$ is the Frobenius automorphism
+on ${\bar G}$, satisfying natural compatibility conditions with $\mu$;
+these compatibility conditions are explained below.
+
+Character sheaves on $G$ form a category, denoted by $\CS(G)$. In
+fact, $\CS(G)$ is a rigid symmetric monoidal category, so isomorphism
+classes of character sheaves on $G$ form a group, denoted by
+$\CS(G)_{/\text{iso}}$; this is the Picard group of the category of
+character sheaves on $G$. Our application of character sheaves to
+characters of algebraic tori over non-Archimedean local fields rests
+on the Picard group of character sheaves on $G$, for certain smooth
+group schemes $G$.
+
+We now say a few words about the commutative group schemes locally of
+finite type over $\Fq$ that appear in our geometrization of admissible
+characters of algebraic tori over local fields. Let $K$ be a
+non-Archimedean local field with residual field $\Fq$; we place no
+restrictions on the characteristic of $K$ -- in particular, it may be
+$0$ or not. Write $\OK$ for ring of integers of $K$ and $\pK$ for the
+maximal ideal in $\OK$.  Let $T$ be an algebraic torus defined over
+$K$. Let $\TT$ be a N\'eron model for $T$; recall that this is a
+smooth group scheme locally of finite type over $\OK$. For each
+non-negative integer $d$, let $\GN{T}_d$ be the Greenberg transform of
+$\TT \otimes \OK/\pK^{d+1}$; the commutative group scheme $\GN{T}_d$
+plays the r\^{o}le of $G$, above.
 
@@
 \] 
-between the Picard group of the category of character sheaves on $\textswab{T}_d$ and the group of characters $T(K) \to \EE^\times$ of depth at most $d$.
-Since these isomorphisms are compatible with respect to $d$, we also .....
-\Clifton{I'll come back to working on this when we're closer to being finished. I'd be just as happy if you took this cup from my lips, though.} 
-In particular, by specializing to the case $T= \mathbb{G}_{\hskip-1pt\text{m},K}$ and by choosing an isomorphism $\EE \approx \CC$ (unnatural though it may be), we arrive at a model for the group of quasi-characters of $K^\times$: the monoidal category of character sheaves on the Greenberg transform of the Neron model of $\mathbb{G}_{\hskip-2pt\text{m},K}$.
+between the Picard group of the category of character sheaves on
+$\textswab{T}_d$ and the group of characters $T(K) \to \EE^\times$ of
+depth at most $d$.  Since these isomorphisms are compatible with
+respect to $d$, we also .....  \Clifton{I'll come back to working on
+  this when we're closer to being finished. I'd be just as happy if
+  you took this cup from my lips, though.}  In particular, by
+specializing to the case $T= \mathbb{G}_{\hskip-1pt\text{m},K}$ and by
+choosing an isomorphism $\EE \approx \CC$ (unnatural though it may
+be), we arrive at a model for the group of quasi-characters of
+$K^\times$: the monoidal category of character sheaves on the
+Greenberg transform of the Neron model of
+$\mathbb{G}_{\hskip-2pt\text{m},K}$.
 
@@
 
-Throughout this paper, $G$ stands for a commutative group scheme, smooth and locally of finite type over a finite field $\Fq$; we write $m : G\tightertimes G\to G$ for the multiplication morphism.
-We fix an algebraic closure $\bFq$ of $\Fq$ and write ${\bar G} $ for the commutative group scheme, smooth and locally of finite type over $\bFq$ obtained by base change; the multiplication morphism for ${\bar G}$ will be denoted by ${\bar m}$.
-Let $\Frob_{G}$ (resp.
-$\Frob_{G\tighttimes G}$) be the Frobenius automorphism of ${\bar G}$ (resp.
-${\bar G}\tightertimes {\bar G}$).\Clifton{I'll insert a reference to SGA where Frobenius is defined for a large class of schemes over finite fields.}
+Throughout this paper, $G$ stands for a commutative group scheme,
+smooth and locally of finite type over a finite field $\Fq$; we write
+$m : G\tightertimes G\to G$ for the multiplication morphism. We fix an
+algebraic closure $\bFq$ of $\Fq$ and write ${\bar G} $ for the
+commutative group scheme, smooth and locally of finite type over
+$\bFq$ obtained by base change; the multiplication morphism for
+${\bar G}$ will be denoted by ${\bar m}$. Let $\Frob_{G}$
+(resp. $\Frob_{G\tighttimes G}$) be the Frobenius automorphism of
+${\bar G}$ (resp. ${\bar G}\tightertimes {\bar G}$).
+\Clifton{I'll insert a reference to SGA where Frobenius is defined for
+  a large class of schemes over finite fields.}
 
@@
 
-The category of character sheaves on $G$, denoted by \cdef{$\CS(G)$}, is defined as follows.
-A \cdef{character sheaf} on $G$ is a triple $\cs{L}\ceq (\gcs{L},\mu,F)$ where: 
+The category of character sheaves on $G$, denoted by \cdef{$\CS(G)$},
+is defined as follows.  A \cdef{character sheaf} on $G$ is a triple
+$\cs{L}\ceq (\gcs{L},\mu,F)$ where:
 \begin{enumerate}
-\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a constructible $\ell$-adic sheaf on (the \'etale site of) ${\bar G}$, locally constant of rank $1$ on connected components of ${\bar G}$; 
-\labitem{(CS.1)}{CS.1} $\mu: {\bar m}^* \gcs{L} \to  \gcs{L}\boxtimes \gcs{L}$ is an isomorphism of sheaves on ${\bar G}\tightertimes {\bar G}$ such that
-\[
-\xymatrix{
-{\bar m}_3^*\gcs{L} \ar[rr]^{({\bar m}\times \id)^*\mu} \ar[d]_{(\id\tightertimes {\bar m})^*\mu}   &&  {\bar m}^*\gcs{L}\boxtimes \gcs{L} \ar[d]^{\mu \boxtimes \id} \\
-\gcs{L} \boxtimes {\bar m}^* \gcs{L} \ar[rr] & &  \gcs{L} \boxtimes\gcs{L} \boxtimes \gcs{L}\\
+\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a constructible $\ell$-adic
+  sheaf on (the \'etale site of) ${\bar G}$, locally constant of rank
+  $1$ on connected components of ${\bar G}$;
+
+\labitem{(CS.1)}{CS.1} $\mu: {\bar m}^* \gcs{L} \to \gcs{L}\boxtimes \gcs{L}$
+  is an isomorphism of sheaves on ${\bar G}\tightertimes {\bar G}$ such that
+
+  \[
+  \xymatrix{
+    {\bar m}_3^*\gcs{L} \ar[rr]^{({\bar m}\times \id)^*\mu} \ar[d]_{(\id\tightertimes {\bar m})^*\mu}
+    &&  {\bar m}^*\gcs{L}\boxtimes \gcs{L} \ar[d]^{\mu \boxtimes \id} \\
+    \gcs{L} \boxtimes {\bar m}^* \gcs{L} \ar[rr]
+    &&  \gcs{L} \boxtimes\gcs{L} \boxtimes \gcs{L}\\
   }
@@
   commutes, where $m_3 \ceq m\circ (m\tightertimes\id) = m\circ (\id\tighttimes m)$;
-\labitem{(CS.2)}{CS.2} $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ is an isomorphism of sheaves on ${\bar G}$ compatible with $\mu$ in the sense that 
-\[
-\xymatrix{
-\Frob_{G\tighttimes G}^* {\bar m}^* \gcs{L} \ar[rr]^{\Frob_{G\tighttimes G}^*\mu} && \Frob_{G\tighttimes G}^*(\gcs{L}\boxtimes \gcs{L})\\
-\ar@{=}[u] {\bar m}^*  \Frob_{G}^* \gcs{L} \ar[d]_{{\bar m}^* F} && \ar[d]^{F\boxtimes F} \ar@{=}[u] \Frob_{G}^*\gcs{L}\boxtimes \Frob_{G}^*\gcs{L}\\
-{\bar m}^*\gcs{L} \ar[rr]^{\mu} && \gcs{L} \boxtimes\gcs{L}\\
+
+\labitem{(CS.2)}{CS.2} $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ is an
+  isomorphism of sheaves on ${\bar G}$ compatible with $\mu$ in the sense that
+
+  \[
+  \xymatrix{
+    \Frob_{G\tighttimes G}^* {\bar m}^* \gcs{L} \ar[rr]^{\Frob_{G\tighttimes G}^*\mu}
+    && \Frob_{G\tighttimes G}^*(\gcs{L}\boxtimes \gcs{L})\\
+    \ar@{=}[u] {\bar m}^*  \Frob_{G}^* \gcs{L} \ar[d]_{{\bar m}^* F}
+    && \ar[d]^{F\boxtimes F} \ar@{=}[u] \Frob_{G}^*\gcs{L}\boxtimes \Frob_{G}^*\gcs{L}\\
+    {\bar m}^*\gcs{L} \ar[rr]^{\mu}
+    && \gcs{L} \boxtimes\gcs{L}\\
   }
@@
 \begin{enumerate}
-\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,F)$ and $\cs{L'} = (\gcs{L'},\mu',F')$ are character sheaves on $G$ then $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$ of constructible $\ell$-adic sheaves on ${\bar G}$ such
-\[
-\xymatrix{
-\ar[d]_{F} \Frob_G^* \gcs{L} \ar[r]^{\Frob_G^* \varphi} & \ar[d]^{F'} \Frob_G^* \gcs{L'} &\text{and}& \ar[d]_{\mu} m^* \gcs{L} \ar[r]^{m^* \varphi} & \ar[d]^{\mu'} m^* \gcs{L'} \\
-\gcs{L} \ar[r]^{\varphi} & \gcs{L'} && \gcs{L}\boxtimes\gcs{L} \ar[r]^{\varphi\boxtimes \varphi} & \gcs{L'} \boxtimes \gcs{L'}\\
+\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,F)$ and
+  $\cs{L'} = (\gcs{L'},\mu',F')$ are character sheaves on $G$ then
+  $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$
+  of constructible $\ell$-adic sheaves on ${\bar G}$ such then
+  \[
+  \xymatrix{
+  \ar[d]_{F} \Frob_G^* \gcs{L} \ar[r]^{\Frob_G^* \varphi} & \ar[d]^{F'} \Frob_G^* \gcs{L'}
+  & \text{and}& \ar[d]_{\mu} m^* \gcs{L} \ar[r]^{m^* \varphi} & \ar[d]^{\mu'} m^* \gcs{L'} \\
+  \gcs{L} \ar[r]^{\varphi} & \gcs{L'}
+  && \gcs{L}\boxtimes\gcs{L} \ar[r]^{\varphi\boxtimes \varphi} & \gcs{L'} \boxtimes \gcs{L'}\\
   }
@@
 %\begin{proposition}\label{tensor}
-The category $\CS(G)$ of character sheaves on $G$ is a rigid monoidal category [insert reference] under $\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'},  \mu\otimes\mu', F\otimes F')$ with duals formed by applying the functor $\sheafHom(\ - \ ,(\EE)_{\bar G})$ to conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}.
+The category $\CS(G)$ of character sheaves on $G$ is a rigid monoidal
+category [insert reference] under
+$\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', F\otimes F')$
+with duals formed by applying the functor $\sheafHom(\ - \ ,(\EE)_{\bar G})$ to
+conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}.
 %\end{proposition}
-(The category of characters sheaves on $G$ is not abelian, so $\CS(G)$ is not a tensor category in the sense of \cite{Deligne:tensorielles}.)
+(The category of characters sheaves on $G$ is not abelian, so $\CS(G)$
+is not a tensor category in the sense of \cite{Deligne:tensorielles}.)
 %\begin{proof}\end{proof}
 %
-This rigid monoidal category structure for $\CS(G)$ puts a group structure on the set $\CS(G)_{/\text{iso}}$ of isomorphism classes in $\CS(G)$; we refer to this as the \cdef{Picard group} of character sheaves on $G$; {\it cf.} {\tt http://ncatlab.org/nlab/show/Picard+group}.
+This rigid monoidal category structure for $\CS(G)$ puts a group
+structure on the set $\CS(G)_{/\text{iso}}$ of isomorphism classes in
+$\CS(G)$; we refer to this as the \cdef{Picard group} of character
+sheaves on $G$; {\it cf.} {\tt http://ncatlab.org/nlab/show/Picard+group}.
 \Clifton{Replace ncatlab with other references.}
@@
 
-Let $\cs{L}$ be a character sheaf on $G$.
-Every $g\in G(\Fq)$ determines a point ${\bar g}$ on ${\bar G}$ fixed by $\Frob_G$ and therefore an automorphism $F_{\bar g}$ of $\gcs{L}_{\bar g}$.
-Note that $\Aut_{\EE}(\gcs{L}_{\bar g}) \iso \EE^\times$, canonically (this follows from second condition appearing in the definition of character sheaves).
-The isomorphism $\mu : {\bar m}^* \gcs{L} \to \gcs{L}\boxtimes\gcs{L}$ guarantees that the function $t^\Frob_\cs{L} : G(\Fq)\to \EE^\times$, defined by $g \mapsto F_{\bar g}$, is a group homomorphism; we refer to $t^\Frob_\cs{L}$ as the \cdef{trace of Frobenius of $\cs{L}$}.\Clifton{There is no actual trace involved, since $\gcs{L}$ is a rank $1$ local system.
-More generally, trace is needed.}
-%
-It is clear that $t^\Frob_{\cs{L}\otimes \cs{L'}} = t^\Frob_\cs{L} \cdot t^\Frob_\cs{L'}$ (pointwise multiplication of functions) and that $t^\Frob_\cs{L} = t^\Frob_\cs{L'}$ if $\cs{L} \iso \cs{L'}$ in $\CS(G)$.
-In this way we obtain a group homomorphism
-\[
-\cdef{t_{G}} : \CS(G)_{/\text{iso}} \longrightarrow \Hom_\text{grp}(G(\Fq),\EE^\times), \qquad \text{defined by}\qquad 
-\cs{L} \mapsto t^\Frob_\cs{L},
+Let $\cs{L}$ be a character sheaf on $G$. Every $g\in G(\Fq)$
+determines a point ${\bar g}$ on ${\bar G}$ fixed by $\Frob_G$ and
+therefore an automorphism $F_{\bar g}$ of $\gcs{L}_{\bar g}$. Note
+that $\Aut_{\EE}(\gcs{L}_{\bar g}) \iso \EE^\times$, canonically (this
+follows from second condition appearing in the definition of character
+sheaves). The isomorphism $\mu : {\bar m}^* \gcs{L} \to \gcs{L}\boxtimes\gcs{L}$
+guarantees that the function $t^\Frob_\cs{L} : G(\Fq)\to \EE^\times$,
+defined by $g \mapsto F_{\bar g}$, is a group homomorphism;
+we refer to $t^\Frob_\cs{L}$ as the \cdef{trace of Frobenius of $\cs{L}$}.
+\Clifton{There is no actual trace involved, since $\gcs{L}$ is a rank
+  $1$ local system. More generally, trace is needed.}
+
+It is clear that $t^\Frob_{\cs{L}\otimes \cs{L'}} = t^\Frob_\cs{L} \cdot t^\Frob_\cs{L'}$
+(pointwise multiplication of functions) and that $t^\Frob_\cs{L} = t^\Frob_\cs{L'}$
+if $\cs{L} \iso \cs{L'}$ in $\CS(G)$. In this way we obtain a group homomorphism
+\[
+\cdef{t_{G}} : \CS(G)_{/\text{iso}} \longrightarrow \Hom_\text{grp}(G(\Fq),\EE^\times),
+\qquad \text{defined by}\qquad \cs{L} \mapsto t^\Frob_\cs{L},
 \]
@@
 
-Our main result on the geometrization of admissible characters of $p$-adic tori [insert internal reference here] follows from a general fact established later in this paper: if the geometric component group of $G$ is finitely-generated then the trace of Frobenius defines an isomorphism from the Picard group of character sheaves $G$ to the group of characters of $G(\Fq)$ (here, as throughout the paper, $G$ is a commutative group scheme, smooth and locally of finite type over $\Fq$).
+Our main result on the geometrization of admissible characters of
+$p$-adic tori [insert internal reference here] follows from a general
+fact established later in this paper: if the geometric component group
+of $G$ is finitely-generated then the trace of Frobenius defines an
+isomorphism from the Picard group of character sheaves $G$ to the
+group of characters of $G(\Fq)$ (here, as throughout the paper, $G$ is
+a commutative group scheme, smooth and locally of finite type over $\Fq$).
 
@@
 \begin{proposition}\label{prop:pullback}
-If $f : H\to G$ is a morphism of commutative group schemes locally of finite type over $\Fq$ then $(\gcs{L},\mu,F) \mapsto ({\bar f}^*\gcs{L},({\bar f}\tightertimes{\bar f})^*\mu,{\bar f}^*F)$ defines a monoidal functor $f^* : \CS(G) \to \CS(H)$ such that
+  If $f : H\to G$ is a morphism of commutative group schemes locally of finite type over $\Fq$ then
+  $(\gcs{L},\mu,F) \mapsto ({\bar f}^*\gcs{L},({\bar f}\tightertimes{\bar f})^*\mu,{\bar f}^*F)$
+  defines a monoidal functor $f^* : \CS(G) \to \CS(H)$ such that
   \[
@@
   \]
-is a commutative diagram of groups, where the lower homomorphism is dual to $f : H(\Fq)\to G(\Fq)$.  Moreover, $(f\circ g)^* = g^* \circ f^*$.
+  is a commutative diagram of groups, where the lower homomorphism is
+  dual to $f : H(\Fq)\to G(\Fq)$.  Moreover, $(f\circ g)^* = g^* \circ f^*$.
 \end{proposition}
@@
 \begin{proof}
-Let $\cs{L}$ be a character sheaf on $G$.
-We start by showing that ${\bar f}^*\gcs{L}$ is locally constant on connected components of ${\bar H}$.
-Let $c_j :{\bar H}^j \hookrightarrow {\bar H}$ be any connected component and let $i$ be the image of $j$ under the group homomorphism $\pi_0({\bar G}) \to \pi_0({\bar H})$ obtained by applying the functor $\pi_0$ to ${\bar f}$; see \cite{vdG&M}*{III, 3.28}, for example.\Clifton{Replace with a better reference, eventually.}  Write $c_i : \bar{G}^i \hookrightarrow \bar{G}$ for the inclusion of $\bar{G}^i$ and ${\bar f}^j : {\bar H}^j \to {\bar G}^i$ for the restriction of $f$ to $\bar{H}^j$.
-Since $\cs{L}$ is a character sheaf, $\gcs{L}$ is locally constant on the connect components of ${\bar G}$; thus, there is a finite etale covering $a_i : X_i \to {\bar G}^i$ such that $a_i^* (\gcs{L}\vert_{\bar G^i})$ is constant.
-Let $b_j : Y_j \to {\bar H}^j$ be the pull-back of $a_i$ along ${\bar f}^j$; let $g_j : Y_j \to X_i$ be the map opposite ${\bar f}^j$.
-Then $b_j$ is a finite etale covering of ${\bar H}^j$ and
-\[
-b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right) = ({\bar f}\circ c_j \circ b_j)^*\gcs{L} = (c_i\circ a_i\circ g_j)^*\gcs{L} = g_j^* a_i^* (\gcs{L}\vert_{\bar G^i}).
-\]
-Since $a_i^* (\gcs{L}\vert_{\bar G^i})$ is a constant sheaf and since the pull-back of a constant sheaf (along $g_j$, in this case) is a constant sheaf, it follows that $b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right)$ is a constant sheaf.
-Thus, ${\bar f}^*\gcs{L}$ is locally constant on ${\bar H}^j$.
-Since $({\bar f}^*\gcs{L})_{\bar g} = \gcs{L}_{f({\bar g})}$ for every geometric point ${\bar g}$ on ${\bar G}$, and since $\gcs{L}$ has rank $1$ on connected components of ${\bar G}$, it follows that $f^*\gcs{L}$ also has rank $1$ on connected components of ${\bar G}$.
+  Let $\cs{L}$ be a character sheaf on $G$. We start by showing that
+  ${\bar f}^*\gcs{L}$ is locally constant on connected components of
+  ${\bar H}$. Let $c_j :{\bar H}^j \hookrightarrow {\bar H}$ be any
+  connected component and let $i$ be the image of $j$ under the group
+  homomorphism $\pi_0({\bar G}) \to \pi_0({\bar H})$ obtained by
+  applying the functor $\pi_0$ to ${\bar f}$; see \cite{vdG&M}*{III, 3.28}, for example.
+  \Clifton{Replace with a better reference, eventually.}
+  Write $c_i : \bar{G}^i \hookrightarrow \bar{G}$ for
+  the inclusion of $\bar{G}^i$ and ${\bar f}^j : {\bar H}^j \to {\bar G}^i$
+  for the restriction of $f$ to $\bar{H}^j$.  Since $\cs{L}$
+  is a character sheaf, $\gcs{L}$ is locally constant on the connect
+  components of ${\bar G}$; thus, there is a finite etale covering
+  $a_i : X_i \to {\bar G}^i$ such that $a_i^* (\gcs{L}\vert_{\bar G^i})$
+  is constant. Let $b_j : Y_j \to {\bar H}^j$ be the
+  pull-back of $a_i$ along ${\bar f}^j$; let $g_j : Y_j \to X_i$ be
+  the map opposite ${\bar f}^j$. Then $b_j$ is a finite etale covering
+  of ${\bar H}^j$ and
+  \[
+  b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right)
+  = ({\bar f}\circ c_j \circ b_j)^*\gcs{L}
+  = (c_i\circ a_i\circ g_j)^*\gcs{L} = g_j^* a_i^* (\gcs{L}\vert_{\bar G^i}).
+  \]
+
+  Since $a_i^* (\gcs{L}\vert_{\bar G^i})$ is a constant sheaf and since the pull-back
+  of a constant sheaf (along $g_j$, in this case) is a constant sheaf,
+  it follows that $b_j^* \left( ({\bar f}^*\gcs{L})\vert_{{\bar H}^j}\right)$
+  is a constant sheaf. Thus, ${\bar f}^*\gcs{L}$ is locally constant on
+  ${\bar H}^j$. Since $({\bar f}^*\gcs{L})_{\bar g} = \gcs{L}_{f({\bar g})}$ for every
+  geometric point ${\bar g}$ on ${\bar G}$, and since $\gcs{L}$ has
+  rank $1$ on connected components of ${\bar G}$, it follows that
+  $f^*\gcs{L}$ also has rank $1$ on connected components of ${\bar G}$.
   This completes the proof that ${\bar f}^*\gcs{L}$ satisfies condition \ref{CS.0}.
 
-To see that $({\bar f}\tightertimes {\bar f})^* \gcs{L}$ satisfies condition \ref{CS.1} simply apply the functor $({\bar f}\tightertimes {\bar f})^*$ to \ref{CS.1} for $\cs{L}$ and use the canonical isomorphism $({\bar f}\tightertimes {\bar f})^*( \gcs{L} \boxtimes\gcs{L}) \iso  {\bar f}^*\gcs{L} \boxtimes {\bar f}^*\gcs{L}$ (a few times).
-Likewise, to see that ${\bar f}^*\gcs{L}$ satisfies condition \ref{CS.2}, apply the same functor to \ref{CS.2} for $\gcs{L}$.
-Then use the fact that $f$ is defined over $\Fq$, so $({\bar f}\tightertimes {\bar f})^* \Frob_{G\tighttimes G}^* \iso \Frob_{G\tighttimes G} ({\bar f}\tightertimes {\bar f})^*$, and the fact that $f$ is a morphism of group schemes, so $({\bar f}\tightertimes {\bar f})^* {\bar m}^* \iso {\bar m}^* {\bar f}^*$ (isomorphisms of functors on constructible sheaves).
-%
-To see that $(\gcs{L},\mu,F) \mapsto ({\bar f}^*\gcs{L},({\bar f}\tightertimes {\bar f})^*\mu,{\bar f}^*F)$ defines a functor $f^* : \CS(G) \to \CS(H)$ one applies the functors ${\bar f}^*$ and ${\bar f}^*\tightertimes{\bar f}^*$ to \ref{CS.3} and argue as above.
-It follows from the fact that sheaf hom commutes with these functors that $f^* : \CS(G) \to \CS(H)$ is a monoidal functor.
-
-The fact that the functor $f^* : \CS(G) \to \CS(H)$ commutes with the trace of Frobenius, in the sense above, follows immediately from the definitions; see \cite{Laumon}*{1.1.1.2}, where the ambient hypothesis that $X$ is of finite type over $\Fq$ can be replaced by the hypothesis that $X$ is locally of finite type over $\Fq$.
+  To see that $({\bar f}\tightertimes {\bar f})^* \gcs{L}$ satisfies
+  condition \ref{CS.1} simply apply the functor $({\bar f}\tightertimes {\bar f})^*$
+  to \ref{CS.1} for $\cs{L}$ and use the canonical isomorphism
+  $({\bar f}\tightertimes {\bar f})^*(\gcs{L} \boxtimes\gcs{L}) \iso {\bar f}^*\gcs{L} \boxtimes {\bar f}^*\gcs{L}$
+  (a few times). Likewise, to see that ${\bar f}^*\gcs{L}$ satisfies condition
+  \ref{CS.2}, apply the same functor to \ref{CS.2} for $\gcs{L}$.
+  Then use the fact that $f$ is defined over $\Fq$, so
+  $({\bar f}\tightertimes {\bar f})^*\Frob_{G\tighttimes G}^* \iso \Frob_{G\tighttimes G} ({\bar f}\tightertimes {\bar f})^*$,
+  and the fact that $f$ is a morphism of group schemes, so
+  $({\bar f}\tightertimes {\bar f})^* {\bar m}^*\iso {\bar m}^* {\bar f}^*$
+  (isomorphisms of functors on constructible sheaves).
+
+  To see that $(\gcs{L},\mu,F) \mapsto ({\bar f}^*\gcs{L},({\bar f}\tightertimes {\bar f})^*\mu,{\bar f}^*F)$
+  defines a functor $f^* : \CS(G) \to \CS(H)$ one applies the functors ${\bar f}^*$ and
+  ${\bar f}^*\tightertimes{\bar f}^*$ to \ref{CS.3} and argue as
+  above. It follows from the fact that sheaf hom commutes with these
+  functors that $f^* : \CS(G) \to \CS(H)$ is a monoidal functor.
+
+  The fact that the functor $f^* : \CS(G) \to \CS(H)$ commutes with
+  the trace of Frobenius, in the sense above, follows immediately from
+  the definitions; see \cite{Laumon}*{1.1.1.2}, where the ambient
+  hypothesis that $X$ is of finite type over $\Fq$ can be replaced by
+  the hypothesis that $X$ is locally of finite type over $\Fq$.
   \Clifton{I have not proved $(f\circ g)^* = g^* \circ f^*$, yet.}
@@
 % !TEX encoding = UTF-8 Unicode
-%In this section we review a fundamental property of character sheaves on geometrically connected, commutative algebraic groups over $\Fq$.
+%In this section we review a fundamental property of character
+%sheaves on geometrically connected, commutative algebraic groups over $\Fq$.
 
@@
 \begin{proof}
-We will prove this proposition by reducing it to the functions--sheaves dictionary \cite{Laumon}*{1.1}.
-The main point of this proof will therefore be to show that, {\it since $G$ is geometrically connected}, every character sheaf on $G$ descends to a local system on $G$ satisfying the analogue of \ref{CS.1} on $G$.
-
-First, observe that the forgetful functor $(\gcs{L},\mu,F) \mapsto (\gcs{L},F)$ sends character sheaves on $G$ to Weil local systems on $G$ \cite{Deligne:Weil2}*{1.1.10} (by a Weil local system on $G$ we mean a Weil sheaf on $G$ which is a local system on ${\bar G}$).
-While is it not true that all Weil local systems on $G$ descend to sheaves on $G$, those that appear in the image of the forgetful functor from character sheaves do.
-
-To see why this is so, consider the category \cdef{$\CS_0(G)$} of pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$ and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ satisfies condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$ are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}.
-\David{Should we move this definition since it will be important elsewhere?} Let $b : {\bar G} \to G$ be base change (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$).
-The proof of Proposition~\ref{prop:pullback} adapts (simplifies, in fact) to show that  $b^* : \CS_0(G) \to \CS(G)$ is a monoidal functor.
-This functor is fully faithful; see \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop.
-5.2.1}.
-We will show that $b^*$ is essentially surjective.
-
-Let $g$ be any $\Fq$-rational point on $G$ (such as the identity for $G$) and let ${\bar g}$ be the geometric point on $G$ lying above $g$ (we fixed $\Fq \hookrightarrow \bFq$ long ago).
-Since $G$ is geometrically connected, the geometric point ${\bar g}$ determines an equivalence between the category of Weil local systems on $G$ and $\ell$-adic representations of $\Weil(G,{\bar g})$ \cite{Deligne:Weil2}*{1.1.12}.
-Now let $(\gcs{L},\mu,F)$ be a character sheaf on $G$.
-Then the isomorphism class of the Weil local system $(\gcs{L},F)$ corresponds to an $\ell$-adic character of the Weil group $\Weil(G, {\bar g})$.
-The $\Fq$-rational point $g$ under the geometric point ${\bar g}$ determines a splitting $\Weil(\bFq/\Fq)\to  \Weil(G,{\bar g})$ of the exact sequence
-\[
-\xymatrix{
-1 \ar[r] & \pi_1({\bar G}, {\bar g}) \ar[r] &  \Weil(G,{\bar g}) \ar[r] & \ar@/_1pc/@{.>}[l]_{g} \Weil(\bFq/\Fq) \ar[r] & 1
+  We will prove this proposition by reducing it to the functions--sheaves dictionary
+  \cite{Laumon}*{1.1}. The main point of this proof will therefore be to show that,
+  {\it since $G$ is geometrically connected}, every character sheaf on $G$ descends to
+  a local system on $G$ satisfying the analogue of \ref{CS.1} on $G$.
+
+  First, observe that the forgetful functor $(\gcs{L},\mu,F) \mapsto (\gcs{L},F)$
+  sends character sheaves on $G$ to Weil local systems on
+  $G$ \cite{Deligne:Weil2}*{1.1.10} (by a Weil local system on $G$ we
+  mean a Weil sheaf on $G$ which is a local system on ${\bar G}$).
+  While is it not true that all Weil local systems on $G$
+  descend to sheaves on $G$, those that appear in the image of the
+  forgetful functor from character sheaves do.
+
+  To see why this is so, consider the category \cdef{$\CS_0(G)$} of
+  pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$
+  and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ satisfies
+  condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$
+  are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}.
+  \David{Should we move this definition since it will be important elsewhere?}
+  Let $b : {\bar G} \to G$ be base change
+  (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$).
+  The proof of Proposition~\ref{prop:pullback} adapts
+  (simplifies, in fact) to show that $b^* : \CS_0(G) \to \CS(G)$ is a
+  monoidal functor. This functor is fully faithful; see
+  \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.  We will
+  show that $b^*$ is essentially surjective.
+
+  Let $g$ be any $\Fq$-rational point on $G$ (such as the identity for
+  $G$) and let ${\bar g}$ be the geometric point on $G$ lying above
+  $g$ (we fixed $\Fq \hookrightarrow \bFq$ long ago). Since $G$ is
+  geometrically connected, the geometric point ${\bar g}$ determines
+  an equivalence between the category of Weil local systems on $G$ and
+  $\ell$-adic representations of $\Weil(G,{\bar g})$
+  \cite{Deligne:Weil2}*{1.1.12}. Now let $(\gcs{L},\mu,F)$ be a
+  character sheaf on $G$. Then the isomorphism class of the Weil local
+  system $(\gcs{L},F)$ corresponds to an $\ell$-adic character of the
+  Weil group $\Weil(G, {\bar g})$. The $\Fq$-rational point $g$ under
+  the geometric point ${\bar g}$ determines a splitting
+  $\Weil(\bFq/\Fq)\to \Weil(G,{\bar g})$ of the exact sequence
+  \[
+  \xymatrix{
+    1 \ar[r] & \pi_1({\bar G}, {\bar g}) \ar[r] &  \Weil(G,{\bar g}) \ar[r]
+    & \ar@/_1pc/@{.>}[l]_{g} \Weil(\bFq/\Fq) \ar[r] & 1
     }
@@
   \]
-of the Weil group $\Weil(\bFq/\Fq)$; the image of $\Frob$ under this character is $t^\Frob_\cs{L}(g)$, the trace of Frobenius of $\cs{L}$ at $g$.
-
-On the other hand, we have already seen that $t^\Frob_\cs{L} : G(\Fq) \to \EE^\times$ is a group homomorphism.
-Since $G$ is an algebraic group over $\Fq$, it is a variety over $\Fq$, so finitely generated over $\Fq$, so $G(\Fq)$ is finite; it follows that $t^\Frob_\cs{L}(g) = t^\Frob_{(\gcs{L},F)}(g)$ is a root of unity, for every $g\in G(\Fq)$.
-Since $\Weil(\bFq/\Fq)$ is generated by $\Frob$ and $t_{(\gcs{L},F)}(g) : \Weil(\bFq/\Fq) \to \EE^\times$ is a character, it follows that the image of $t_{(\gcs{L},F)}(g)$ is a finite subset of $\mu(\EE)$.
-Thus, $t_{(\gcs{L},F)}(g)$ extends to an $\ell$-adic character of $\Gal(\bFq/\Fq)$, which will be denoted by the same symbol.
+  of the Weil group $\Weil(\bFq/\Fq)$; the image of $\Frob$ under this
+  character is $t^\Frob_\cs{L}(g)$, the trace of Frobenius of $\cs{L}$ at $g$.
+
+  On the other hand, we have already seen that $t^\Frob_\cs{L} : G(\Fq) \to \EE^\times$
+  is a group homomorphism. Since $G$ is an algebraic group over $\Fq$, it is a
+  variety over $\Fq$, so finitely generated over $\Fq$, so $G(\Fq)$ is finite;
+  it follows that $t^\Frob_\cs{L}(g) = t^\Frob_{(\gcs{L},F)}(g)$ is a root of unity,
+  for every $g\in G(\Fq)$.  Since $\Weil(\bFq/\Fq)$ is generated by
+  $\Frob$ and $t_{(\gcs{L},F)}(g) : \Weil(\bFq/\Fq) \to \EE^\times$ is
+  a character, it follows that the image of $t_{(\gcs{L},F)}(g)$ is a
+  finite subset of $\mu(\EE)$. Thus, $t_{(\gcs{L},F)}(g)$ extends to
+  an $\ell$-adic character of $\Gal(\bFq/\Fq)$, which will be denoted
+  by the same symbol.
   \[
@@
 
-We may now lift the $\ell$-adic character $t_{(\gcs{L},F)}(g) : \Gal(\bFq/\Fq) \to \EE^\times$ to an $\ell$-adic character of $\pi_1(G,{\bar g})$ using the canonical topological group map $\pi_1(G,{\bar g}) \to \Gal(\bFq/\Fq)$, above.
-But ${\bar g}$ also determines an equivalence between the category of $\ell$-adic representations of $\pi_1(G,{\bar g})$ and local systems on $G$.
-Let $\cs{L}_0$ be a local system on $G$ in the isomorphism class determined by this $\ell$-adic character of $\pi_1(G,{\bar g})$.
+  We may now lift the $\ell$-adic character $t_{(\gcs{L},F)}(g) : \Gal(\bFq/\Fq) \to \EE^\times$
+  to an $\ell$-adic character of $\pi_1(G,{\bar g})$ using the canonical topological group map
+  $\pi_1(G,{\bar g}) \to \Gal(\bFq/\Fq)$, above. But ${\bar g}$ also
+  determines an equivalence between the category of $\ell$-adic
+  representations of $\pi_1(G,{\bar g})$ and local systems on $G$. Let
+  $\cs{L}_0$ be a local system on $G$ in the isomorphism class
+  determined by this $\ell$-adic character of $\pi_1(G,{\bar g})$.
   Then $b^*\cs{L}_0 \iso \gcs{L}$, so $b^*$ is essentially surjective.
 
-We have now shown that $b^* : \CS_0(G) \to \CS(G)$ is an equivalence of  rigid monoidal categories. It follows immediately that $b^*$ determines an isomorphism 
+  We have now shown that $b^* : \CS_0(G) \to \CS(G)$ is an equivalence
+  of rigid monoidal categories. It follows immediately that $b^*$
+  determines an isomorphism
   \[
@@
   of the Picard groups determined by these rigid monoidal categories.
-\Clifton{\textdbend This last sentence glosses over some subtle points; I might need to address them in the `two perspectives' section.}
-
-To finish the proof observe that the functions--sheaves dictionary, as it pertains to characters, shows that
+  \Clifton{\textdbend This last sentence glosses over some subtle points;
+    I might need to address them in the `two perspectives' section.}
+
+  To finish the proof observe that the functions--sheaves dictionary,
+  as it pertains to characters, shows that
   \[
@@
 %\input{etale-1}
-%In this section we establish a fundamental property of character sheaves on commutative etale group schemes over $\Fq$ that are geometrically finitely generated.
+%In this section we establish a fundamental property of character
+% sheaves on commutative etale group schemes over $\Fq$ that are
+% geometrically finitely generated.
 
 \begin{proposition}\label{prop:etale}
-If $G$ is a commutative \'etale group scheme over $\Fq$ and $G(\bFq)$ is finitely generated then there is a canonical isomorphism 
+  If $G$ is a commutative \'etale group scheme over $\Fq$ and
+  $G(\bFq)$ is finitely generated then there is a canonical
+  isomorphism
   \[
@@
 \begin{proof}
-To simplify notation, we set $W_\Fq \ceq \Weil(\bFq/\Fq)$ and $G(\bFq)^* \ceq \Hom_\text{grp}(G(\bFq),\EE^\times)$.
-Recall the equivalence between etale group schemes over $\Fq$ and the category of groups equipped with a continuous action of $\Gal(\bFq/\Fq)$ (for the discrete topology on the group), given by $G \mapsto G(\bFq)$.
-Under this equivalence any character sheaf $\cs{L} =(\gcs{L},\mu,F)$ on $G$ corresponds to:
+  To simplify notation, we set $W_\Fq \ceq \Weil(\bFq/\Fq)$ and
+  $G(\bFq)^* \ceq \Hom_\text{grp}(G(\bFq),\EE^\times)$.  Recall the
+  equivalence between etale group schemes over $\Fq$ and the category
+  of groups equipped with a continuous action of $\Gal(\bFq/\Fq)$ (for
+  the discrete topology on the group), given by $G \mapsto G(\bFq)$.
+  Under this equivalence any character sheaf $\cs{L}=(\gcs{L},\mu,F)$
+  on $G$ corresponds to:
   \begin{enumerate}
-\labitem{(cs.0)}{cs.0} an indexed set of one-dimensional $\EE$-vector spaces $\gcs{L}_x \ceq x^*\gcs{L}$, as $x$ runs over $G(\bFq)$; 
-\labitem{(cs.1)}{cs.1} an indexed set of isomorphisms $\mu_{x,y}  \ceq (x \times y)^*\mu : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes \gcs{L}_{y}$, for all $x,y \in G(\bFq)$, such that
-\[
-\xymatrix{
-\gcs{L}_{x+y+z} \ar[rr]^{\mu_{x+y,z}} \ar[d]_{\mu_{x,y+z}}   &&  \gcs{L}_{x+y}\otimes \gcs{L}_{z} \ar[d]^{\mu_{x,y} \otimes \id} \\
-\gcs{L}_{x} \otimes \gcs{L}_{y+z} \ar[rr]^{\id \otimes \mu_{y,z}} & &  \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes \gcs{L}_{z}\\
+  \labitem{(cs.0)}{cs.0} an indexed set of one-dimensional
+    $\EE$-vector spaces $\gcs{L}_x \ceq x^*\gcs{L}$, as $x$ runs over
+    $G(\bFq)$;
+
+  \labitem{(cs.1)}{cs.1} an indexed set of isomorphisms
+    $\mu_{x,y} \ceq (x \times y)^*\mu : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes \gcs{L}_{y}$,
+    for all $x,y \in G(\bFq)$, such that
+    \[
+    \xymatrix{
+      \gcs{L}_{x+y+z} \ar[rr]^{\mu_{x+y,z}} \ar[d]_{\mu_{x,y+z}}
+      && \gcs{L}_{x+y}\otimes \gcs{L}_{z} \ar[d]^{\mu_{x,y} \otimes \id} \\
+      \gcs{L}_{x} \otimes \gcs{L}_{y+z} \ar[rr]^{\id \otimes \mu_{y,z}}
+      && \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes \gcs{L}_{z}\\
       }
@@
     commutes, for all $x,y,z\in G(\bFq)$; and
+
   \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $F_{x} \ceq x^*F: \gcs{L}_{\Frob(x)} \to \gcs{L}_x$
-\Clifton{\textdbend There's hidden subtlety here too: maybe I should explain which Frobenius this is and how it acts. }
+    \Clifton{\textdbend There's hidden subtlety here too: maybe I
+      should explain which Frobenius this is and how it acts. }
     such that
@@
     \xymatrix{
- \gcs{L}_{\Frob(x)+\Frob(y)} \ar[d]_{F_{x+y}} \ar[rr]^{\mu_{\Frob(x),\Frob(y)}} &&\ar[d]^{F_x\otimes F_y}  \gcs{L}_{\Frob(x)}\otimes \gcs{L}_{\Frob(y)}\\
-\gcs{L}_{x+y} \ar[rr]^{\mu_{x,y}} && \gcs{L}_x \otimes\gcs{L}_y\\
+      \gcs{L}_{\Frob(x)+\Frob(y)} \ar[d]_{F_{x+y}} \ar[rr]^{\mu_{\Frob(x),\Frob(y)}}
+      &&\ar[d]^{F_x\otimes F_y}  \gcs{L}_{\Frob(x)}\otimes \gcs{L}_{\Frob(y)}\\
+      \gcs{L}_{x+y} \ar[rr]^{\mu_{x,y}}
+      && \gcs{L}_x \otimes\gcs{L}_y\\
       }
@@
   \end{enumerate}
-Under this equivalence, a map $\varphi : \cs{L} \to \cs{L'}$ of character sheaves on $G$ corresponds to:
+  Under this equivalence, a map $\varphi : \cs{L} \to \cs{L'}$ of
+  character sheaves on $G$ corresponds to:
   \begin{enumerate}
-\labitem{(cs.3)}{cs.3} an indexed set $\varphi_x \ceq x^*\varphi: \gcs{L}_x \to \gcs{L'}_x$ of linear transformations (of one-dimensional $\EE$-vector spaces), as $x$ runs over $G(\bFq)$, such that
-\[
-\xymatrix{
-\ar[d]_{F_x} \gcs{L}_{\Frob(x)} \ar[r]^{\varphi_{\Frob(x)}} & \ar[d]^{F_x'} \gcs{L'}_{\Frob(x)} &\text{and}& \ar[d]_{\mu} \gcs{L}_{x+y} \ar[r]^{\varphi_{x+y}} & \ar[d]^{\mu'_{x+y}} \gcs{L'}_{x+y} \\
-\gcs{L}_x \ar[r]^{\varphi_x} & \gcs{L'}_x && \gcs{L}_x\otimes\gcs{L}_y \ar[r]^{\varphi_x\otimes \varphi_y} & \gcs{L'}_x \otimes \gcs{L'}_y\\
+  \labitem{(cs.3)}{cs.3} an indexed set $\varphi_x \ceq x^*\varphi: \gcs{L}_x \to \gcs{L'}_x$
+    of linear transformations (of one-dimensional $\EE$-vector spaces),
+    as $x$ runs over $G(\bFq)$, such that
+    \[
+    \xymatrix{
+      \ar[d]_{F_x} \gcs{L}_{\Frob(x)} \ar[r]^{\varphi_{\Frob(x)}} & \ar[d]^{F_x'} \gcs{L'}_{\Frob(x)}
+      &\text{and}& \ar[d]_{\mu} \gcs{L}_{x+y} \ar[r]^{\varphi_{x+y}} & \ar[d]^{\mu'_{x+y}} \gcs{L'}_{x+y} \\
+      \gcs{L}_x \ar[r]^{\varphi_x} & \gcs{L'}_x
+      && \gcs{L}_x\otimes\gcs{L}_y \ar[r]^{\varphi_x\otimes \varphi_y} & \gcs{L'}_x \otimes \gcs{L'}_y\\
       }
@@
   \end{enumerate}
-It is clear that the category defined by conditions \ref{cs.0}, \ref{cs.1}, \ref{cs.2} and \ref{cs.3}, denoted by \cdef{$\CS(G(\bFq))$}, is equivalent to $\CS(G)$.
-We will prove the proposition by exhibiting an isomorphism between $\CS(G(\bFq))_{/\text{iso}}$ and $H^1(W_{\Fq}, G(\bFq)^*)$.
-
-To produce the isomorphism between $\CS(G(\bFq))_{/\text{iso}}$ and $H^1(W_{\Fq}, G(\bFq)^*)$ we must pick a global section of the line bundle $(\gcs{L},\mu)$, for each character sheaf $\cs{L}$ on $G$.
-We will show that the group isomorphism does not depend on these choices.
-
-First, however, we show that such global sections exist.
-Since $G(\bFq)$ is finitely-generated abelian, it admits a decomposition $G(\bFq) \iso G(\bFq)_\text{free} \oplus G(\bFq)_\text{tors}$ such that $G(\bFq)_\text{tors}$ is finite.
-Let $x_1, \ldots , x_r$ be a basis for the free part $G(\bFq)_\text{free}$ of $G(\bFq)$ and let $y_1, \ldots , y_t$ be a generators for the torsion part of $G(\bFq)$ corresponding to the decomposition $G(\bFq)_\text{tors} \iso \oplus_{j=1}^t \ZZ/m_j\ZZ$, with $m_j \vert m_{j+1}$.
-For each such $x_i$ pick $s(x_i)\in \gcs{L}_{x_i}$; for each such $y_j$ pick $s(y_j) \in \gcs{L}_{y_j}$; also set $s({\bar e}) \ceq 0 \in \gcs{L}_{\bar e}$.
-....
-\Clifton{I'll finish this later.} In this way we define a section $s \ceq s_\cs{L} : G(\bFq) \to \coprod_{z\in G(\bFq)} \gcs{L}_z$ of projection $\coprod_{z\in G(\bFq)} \gcs{L}_z \to G(\bFq)$ such that
+  It is clear that the category defined by conditions \ref{cs.0},
+  \ref{cs.1}, \ref{cs.2} and \ref{cs.3}, denoted by
+  \cdef{$\CS(G(\bFq))$}, is equivalent to $\CS(G)$. We will prove the
+  proposition by exhibiting an isomorphism between
+  $\CS(G(\bFq))_{/\text{iso}}$ and $H^1(W_{\Fq}, G(\bFq)^*)$.
+
+  To produce the isomorphism between $\CS(G(\bFq))_{/\text{iso}}$ and
+  $H^1(W_{\Fq}, G(\bFq)^*)$ we must pick a global section of the line
+  bundle $(\gcs{L},\mu)$, for each character sheaf $\cs{L}$ on $G$. We
+  will show that the group isomorphism does not depend on these
+  choices.
+
+  First, however, we show that such global sections exist.  Since
+  $G(\bFq)$ is finitely-generated abelian, it admits a decomposition
+  $G(\bFq) \iso G(\bFq)_\text{free} \oplus G(\bFq)_\text{tors}$ such
+  that $G(\bFq)_\text{tors}$ is finite.  Let $x_1, \ldots , x_r$ be a
+  basis for the free part $G(\bFq)_\text{free}$ of $G(\bFq)$ and let
+  $y_1, \ldots , y_t$ be a generators for the torsion part of
+  $G(\bFq)$ corresponding to the decomposition
+  $G(\bFq)_\text{tors} \iso \oplus_{j=1}^t \ZZ/m_j\ZZ$, with
+  $m_j \vert m_{j+1}$. For each such $x_i$ pick $s(x_i)\in \gcs{L}_{x_i}$;
+  for each such $y_j$ pick $s(y_j) \in \gcs{L}_{y_j}$; also set
+  $s({\bar e}) \ceq 0 \in \gcs{L}_{\bar e}$. ....
+  \Clifton{I'll finish this later.}
+  In this way we define a section
+  $s \ceq s_\cs{L} : G(\bFq) \to \coprod_{z\in G(\bFq)} \gcs{L}_z$ of
+  projection $\coprod_{z\in G(\bFq)} \gcs{L}_z \to G(\bFq)$ such that
+
   \begin{equation}\label{section}
@@
   \end{equation}
-Under the equivalence at the beginning of this section, $s = s_\cs{L}$ corresponds to a global section of the line bundle $(\gcs{L},\mu)$.
-
-We use the section $s_\cs{L}$ to define a cocycle $z_\cs{L} \in Z^1(W_\Fq,G(\bFq)^*)$ as follows.
-Recall that $\cs{L}$ also determines a family of linear transformations $F_x : \gcs{L}_{\Frob(x)} \to \gcs{L}_x$ of one-dimensional $\EE$-vector spaces,  so $F_x(s(\Frob(x)))$ is a scalar multiply of $s(x)$, for each $x\in G(\bFq)$; let $t_\cs{L}(\Frob)(x)$ be that scalar, so
+  Under the equivalence at the beginning of this section, $s = s_\cs{L}$
+  corresponds to a global section of the line bundle $(\gcs{L},\mu)$.
+
+  We use the section $s_\cs{L}$ to define a cocycle $z_\cs{L} \in Z^1(W_\Fq,G(\bFq)^*)$
+  as follows. Recall that $\cs{L}$ also determines a family of linear transformations
+  $F_x : \gcs{L}_{\Frob(x)} \to \gcs{L}_x$ of one-dimensional $\EE$-vector
+  spaces, so $F_x(s(\Frob(x)))$ is a scalar multiply of $s(x)$, for
+  each $x\in G(\bFq)$; let $t_\cs{L}(\Frob)(x)$ be that scalar, so
   \begin{equation}\label{t}
@@
   \end{equation}
-Conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that the scalar $z_\cs{L}(\Frob)(x)$ is non-zero, while condition~\ref{cs.1} forces $t_\cs{L}(\Frob)(x+y) = t_\cs{L}(\Frob)(x) \ t_\cs{L}(\Frob)(y)$, for all $x,y \in G(\bFq)$.
-%\Clifton{The alternative to this approach is to change the definition of character sheaves to incorporate the notion of Galois sheaves.
-That might not be so bad, but would add another layer of complication, which we wouldn't use profitably, expect here.}
-Now $t_\cs{L} : W_\Fq \to G(\bFq)^*$ is defined, recursively, by $t_\cs{L}(\Frob^n) \ceq t_\cs{L}(\Frob)\cdot \,^\Frob t_\cs{L}(\Frob^{n-1})$, where $\Frob$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers to pointwise multiplication of functions.
-This gives
-\[
-\obj \CS(G(\bFq)) \longrightarrow Z^1(W_\Fq,G(\bFq)^*), \qquad \text{defined by} \qquad \cs{L} \mapsto t_\cs{L}.
-\]
-
-Although we used a global section $s_\cs{L}$ in the definition of $t_\cs{L}$, the class of $t_\cs{L}$ does not depend on this choice.
-To see why, let $s_1$ and $s_2$ be two global sections of the line bundle $(\gcs{L},\mu)$, in the sense above and let $t_1$ and $t_2$ be the cocycles defined by $s_1$ and $s_2$, respectively, as above.
-Since, for each $x\in G(\bFq)$, $\gcs{L}_x$ is a one-dimensional $\EE$-vector space, there is a unique scalar $a(x) \in \EE$ such that $s_2(x) = a(x) s_1(x)$; moreover, $a(x)$ is non-zero, since $s_2(x)$ is non-zero.
-Then \eqref{section} and condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so $a\in G(\bFq)^*$.
-Now consider the  coboundary $t_0 : W_\Fq \to G(\bFq)^*$ defined by $t_0(\Frob) = \,^\Frob a \cdot a^{-1}$.
-Then $t_2 = t_0 t_1$, so $t_2$ and $t_1$ are cohomologous.
-In this way we see that
+  Conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
+  the scalar $z_\cs{L}(\Frob)(x)$ is non-zero, while condition~\ref{cs.1} forces
+  $t_\cs{L}(\Frob)(x+y) = t_\cs{L}(\Frob)(x) \ t_\cs{L}(\Frob)(y)$,
+  for all $x,y \in G(\bFq)$.
+  % \Clifton{The alternative to this approach is to change the
+  %   definition of character sheaves to incorporate the notion of
+  %   Galois sheaves. That might not be so bad, but would add another
+  %   layer of complication, which we wouldn't use profitably, expect
+  %   here.}
+
+  Now $t_\cs{L} : W_\Fq \to G(\bFq)^*$ is defined, recursively, by
+  $t_\cs{L}(\Frob^n) \ceq t_\cs{L}(\Frob)\cdot \,^\Frob t_\cs{L}(\Frob^{n-1})$,
+  where $\Frob$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers
+  to pointwise multiplication of functions. This gives
+  \[
+  \obj \CS(G(\bFq)) \longrightarrow Z^1(W_\Fq,G(\bFq)^*),
+  \qquad \text{defined by} \qquad \cs{L} \mapsto t_\cs{L}.
+  \]
+
+  Although we used a global section $s_\cs{L}$ in the definition of
+  $t_\cs{L}$, the class of $t_\cs{L}$ does not depend on this
+  choice. To see why, let $s_1$ and $s_2$ be two global sections of
+  the line bundle $(\gcs{L},\mu)$, in the sense above and let $t_1$
+  and $t_2$ be the cocycles defined by $s_1$ and $s_2$, respectively,
+  as above. Since, for each $x\in G(\bFq)$, $\gcs{L}_x$ is a
+  one-dimensional $\EE$-vector space, there is a unique scalar
+  $a(x) \in \EE$ such that $s_2(x) = a(x) s_1(x)$; moreover, $a(x)$ is
+  non-zero, since $s_2(x)$ is non-zero. Then \eqref{section} and
+  condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so
+  $a\in G(\bFq)^*$. Now consider the coboundary $t_0 : W_\Fq \to G(\bFq)^*$
+  defined by $t_0(\Frob) = \,^\Frob a \cdot a^{-1}$. Then $t_2 = t_0 t_1$,
+  so $t_2$ and $t_1$ are cohomologous. In this way we see that
   \begin{equation}\label{cohomologous}
-\obj \CS(G(\bFq)) \longrightarrow H^1(W_\Fq,G(\bFq)^*), \qquad \text{defined by} \qquad \cs{L} \mapsto [t_\cs{L}],
+    \obj \CS(G(\bFq)) \longrightarrow H^1(W_\Fq,G(\bFq)^*),
+    \qquad \text{defined by} \qquad \cs{L} \mapsto [t_\cs{L}],
   \end{equation}
@@
 
-We now show that the function $\obj \CS(G(\bFq)) \longrightarrow H^1(W_\Fq,G(\bFq)^*)$ factors through $\obj \CS(G(\bFq)) \to \CS(G(\bFq))_{/\text{iso}}$.
-To see this, let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and let $t$ and $t'$ be any cocycles representing the classes in the image of $\cs{L}$ and $\cs{L'}$ under \eqref{cohomologous}; by construction, $t$ and $t'$ are defined by sections $s$ and $s'$.
-Now, $\varphi_x(s(x))$ is a non-zero scalar multiple of $s'(x)$; define $\phi: G(\bFq) \to \EE^\times$ by $\varphi_x(s(x)) = \phi(x) s'(x)$.
-By the second part of condition~\ref{cs.3}, $\phi(x+y) = \phi(x)\phi(y)$, so $\phi \in G(\bFq)^*$.
-By the first part of condition~\ref{cs.3}, $t'(\Frob) = t(\Frob) \cdot (\,^{\Frob^{-1}}\phi \cdot \phi^{-1})$, so $t$ and $t'$ are cohomologous.
-This concludes the definition of
+  We now show that the function $\obj \CS(G(\bFq)) \longrightarrow H^1(W_\Fq,G(\bFq)^*)$
+  factors through $\obj \CS(G(\bFq)) \to \CS(G(\bFq))_{/\text{iso}}$.
+  To see this, let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and
+  let $t$ and $t'$ be any cocycles representing the classes in the
+  image of $\cs{L}$ and $\cs{L'}$ under \eqref{cohomologous}; by construction,
+  $t$ and $t'$ are defined by sections $s$ and $s'$. Now, $\varphi_x(s(x))$ is a
+  non-zero scalar multiple of $s'(x)$; define $\phi: G(\bFq) \to \EE^\times$
+  by $\varphi_x(s(x)) = \phi(x) s'(x)$. By the second part of condition~\ref{cs.3},
+  $\phi(x+y) = \phi(x)\phi(y)$, so $\phi \in G(\bFq)^*$. By the first part of
+  condition~\ref{cs.3}, $t'(\Frob) = t(\Frob) \cdot (\,^{\Frob^{-1}}\phi \cdot \phi^{-1})$,
+  so $t$ and $t'$ are cohomologous. This concludes the definition of
   \begin{equation}\label{pich1}
- \CS(G(\bFq)_{/\text{iso}} \longrightarrow H^1(W_\Fq,G(\bFq)^*), \qquad \text{defined by} \qquad [\cs{L}] \mapsto [t_\cs{L}].
+    \CS(G(\bFq)_{/\text{iso}} \longrightarrow H^1(W_\Fq,G(\bFq)^*),
+    \qquad \text{defined by} \qquad [\cs{L}] \mapsto [t_\cs{L}].
   \end{equation}
-Now it follows from \eqref{t} that the image of the isomorphism class of $\cs{L}$ is indeed represented by a cocycle $t_\cs{L}$ such that $t_\cs{L}(\Frob) = t^\Frob_\cs{L}$ on $G(\Fq)$, which is to say, when evaluated at $\Frob$, the cocycle $t_\cs{L}$ is an extension of the trace of Frobenius of $\cs{L}$.
-
-It only remains to show that \eqref{pich1} is a group isomorphism. This is straightforward.
+  Now it follows from \eqref{t} that the image of the isomorphism
+  class of $\cs{L}$ is indeed represented by a cocycle $t_\cs{L}$ such
+  that $t_\cs{L}(\Frob) = t^\Frob_\cs{L}$ on $G(\Fq)$, which is to
+  say, when evaluated at $\Frob$, the cocycle $t_\cs{L}$ is an
+  extension of the trace of Frobenius of $\cs{L}$.
+
+  It only remains to show that \eqref{pich1} is a group
+  isomorphism. This is straightforward.
   \Clifton{Straightforward, yes, but it still needs to be written down here.}
@@
 %\input{etale-2}
-%Define $\rho \colon \Hh^1(W_{\Fq}, \Hom(G(\bFq), \EE^\times)) \rightarrow \Hom(G(\Fq), \EE^\times)$ by $\rho(\phi)(g) = \phi(\Frob)(g)$.
+%Define $\rho \colon \Hh^1(W_{\Fq}, \Hom(G(\bFq), \EE^\times))
+% \rightarrow \Hom(G(\Fq), \EE^\times)$ by $\rho(\phi)(g) =
+% \phi(\Frob)(g)$.
+
 \begin{proposition}\label{prop:X}
-Let $X$ be a finitely generated abelian group equipped with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on $X$.  Then
+  Let $X$ be a finitely generated abelian group equipped with an
+  action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on
+  $X$.  Then
   \begin{align*}
@@
 \begin{proof}
-We first prove that $\rho$ is surjective.
-Suppose that $f \in \Hom(X^\Frob, \EE^\times).$  Since $\EE^\times$ is divisible as an abelian group it is injective as a $\ZZ$-module and thus $\Ext^1_{\ZZ}(X/X^\Frob, \EE^\times) = 0$.
-Applying the functor $\Hom(\mbox{---}, \EE^\times)$ to
+  We first prove that $\rho$ is surjective.  Suppose that
+  $f \in \Hom(X^\Frob, \EE^\times).$ Since $\EE^\times$ is divisible
+  as an abelian group it is injective as a $\ZZ$-module and thus
+  $\Ext^1_{\ZZ}(X/X^\Frob, \EE^\times) = 0$.  Applying the functor
+  $\Hom(\mbox{---}, \EE^\times)$ to
   $$0 \rightarrow X^\Frob \rightarrow X \rightarrow X/X^\Frob \rightarrow 0$$
-and considering the associated long exact sequence gives the existence of an $\tilde{f} \in \Hom(X, \EE^\times)$ restricting to $f$.
-Define a $1$-cocycle $z \in \Hh^1(\Fq, \Hom(X,\EE^\times))$ by mapping $\Frob$ to $\tilde{f}$.
-Then $\rho([z]) = f$.
-
-Now suppose that $[z] \in \Hh^1(\Fq,\Hom(X,\EE^\times))$ with $\rho([z]) = 1$; write $\tilde{f}$ for $z(\Frob)$.
-The injectivity of $\rho$ is equivalent to the existence of a homomorphism $\psi \colon X \rightarrow \EE^\times$ with
+  and considering the associated long exact sequence gives the
+  existence of an $\tilde{f} \in \Hom(X, \EE^\times)$ restricting to
+  $f$.  Define a $1$-cocycle $z \in \Hh^1(\Fq, \Hom(X,\EE^\times))$ by
+  mapping $\Frob$ to $\tilde{f}$.  Then $\rho([z]) = f$.
+
+  Now suppose that $[z] \in \Hh^1(\Fq,\Hom(X,\EE^\times))$ with
+  $\rho([z]) = 1$; write $\tilde{f}$ for $z(\Frob)$.  The injectivity
+  of $\rho$ is equivalent to the existence of a homomorphism $\psi
+  \colon X \rightarrow \EE^\times$ with
   $$\tilde{f}(x) = \frac{\psi(\Frob(x))}{\psi(x)}$$
-for $x \in X$.  In fact, we may replace the construction of $\psi$ for all $\ZZ[\Gal(\bFq/\Fq)]$-modules $X$ with the construction of analogous $\psi$s for a different class of modules.
-
-Since the action of $\Gal(\bFq/\Fq)$ is continuous, there is an $m$ so that $\Frob^m$ acts trivially on $X$; write $\Fqm$ for the degree $m$ extension of $\Fq$ and $\Gamma_m$ for $\Gal(\Fqm/\Fq)$.
-Since $T^m-1$ factors as a squarefree product of cyclotomic polynomials, the Chinese remainder theorem expresses $\ZZ[\Gamma_m]$ as a product of $\ZZ[\zeta_d]$ for $d$ dividing $m$.
-Each $\ZZ[\zeta_d]$ is the maximal order in a number field and thus $\ZZ[\Gamma_m]$ is a product of Dedekind domains.
-Therefore $X$ decomposes into a direct sum of cyclic $\ZZ[\Gamma_m]$-modules \cite[?]{Brandal}, each of the form $\ZZ[\Gamma_m] / I$ for some ideal $I \subset \ZZ[\Gamma_m]$.
-The ideal $I$ corresponds to a direct product of ideals $I_d$ in the $\ZZ[\zeta_d]$, and within each $\ZZ[\zeta_d]$ the Chinese remainder theorem allows a further decomposition of $\ZZ[\zeta_d] / I_d$ as a direct sum of $\ZZ[\zeta_d]$-modules of the form $\ZZ[\zeta_d]/P^s$.
-So if we can construct, for every cyclotomic ring $\ZZ[\zeta_d]$, prime ideal $P \subset \ZZ[\zeta_d]$ and positive integer $s$, a $\psi \colon \ZZ[\zeta_d]/P^s \rightarrow \EE^\times$ with
+  for $x \in X$.  In fact, we may replace the construction of $\psi$
+  for all $\ZZ[\Gal(\bFq/\Fq)]$-modules $X$ with the construction of
+  analogous $\psi$s for a different class of modules.
+
+  Since the action of $\Gal(\bFq/\Fq)$ is continuous, there is an $m$
+  so that $\Frob^m$ acts trivially on $X$; write $\Fqm$ for the degree
+  $m$ extension of $\Fq$ and $\Gamma_m$ for $\Gal(\Fqm/\Fq)$.  Since
+  $T^m-1$ factors as a squarefree product of cyclotomic polynomials,
+  the Chinese remainder theorem expresses $\ZZ[\Gamma_m]$ as a product
+  of $\ZZ[\zeta_d]$ for $d$ dividing $m$.  Each $\ZZ[\zeta_d]$ is the
+  maximal order in a number field and thus $\ZZ[\Gamma_m]$ is a
+  product of Dedekind domains.  Therefore $X$ decomposes into a direct
+  sum of cyclic $\ZZ[\Gamma_m]$-modules \cite[?]{Brandal}, each of the
+  form $\ZZ[\Gamma_m] / I$ for some ideal $I \subset \ZZ[\Gamma_m]$.
+  The ideal $I$ corresponds to a direct product of ideals $I_d$ in the
+  $\ZZ[\zeta_d]$, and within each $\ZZ[\zeta_d]$ the Chinese remainder
+  theorem allows a further decomposition of $\ZZ[\zeta_d] / I_d$ as a
+  direct sum of $\ZZ[\zeta_d]$-modules of the form $\ZZ[\zeta_d]/P^s$.
+  So if we can construct, for every cyclotomic ring $\ZZ[\zeta_d]$,
+  prime ideal $P \subset \ZZ[\zeta_d]$ and positive integer $s$, a
+  $\psi \colon \ZZ[\zeta_d]/P^s \rightarrow \EE^\times$ with
   \begin{equation} \label{eq:psi-condition}
@@
   \end{equation}
-then the existence of the original $\psi$ follows because $X$ is a direct sum of such $\ZZ[\zeta_d]/P^s$.
-
-We now fix a $d$, $P$ and $s$, write $\zeta$ for $\zeta_d$ and choose a polynomial
+  then the existence of the original $\psi$ follows because $X$ is a
+  direct sum of such $\ZZ[\zeta_d]/P^s$.
+
+  We now fix a $d$, $P$ and $s$, write $\zeta$ for $\zeta_d$ and
+  choose a polynomial
   $$h(T) = a_rT^r + a_{r-1}T^{r-1} + \cdots + a_0$$
   so that $P^s = (p^s, h(\zeta_d))$.
-%Setting $\psi = 1$ will satisfy equation \ref{eq:psi-condition} when $d = 1$.  
-An an abelian group, the quotient $\ZZ[\zeta] / P^s$ is generated by $\zeta^i$ for $0 \le i < \phi(d)$; we define
+  % Setting $\psi = 1$ will satisfy equation \ref{eq:psi-condition}
+  % when $d = 1$.
+  An an abelian group, the quotient $\ZZ[\zeta] / P^s$ is generated by
+  $\zeta^i$ for $0 \le i < \phi(d)$; we define
   \begin{equation} \label{eq:psi-def}
@@
   \end{equation}
-for an $\alpha \in \EE^\times$ to be chosen later.  Since there are relations among the $\zeta^i$ we first need to check that $\psi$ is well-defined.
-
-The relations among the generators $\zeta^i$ are additively generated by $\zeta^ch(\zeta)$ as $c$ ranges from $0$ to $\phi(d)-r-1$.  If we set 
+  for an $\alpha \in \EE^\times$ to be chosen later.  Since there are
+  relations among the $\zeta^i$ we first need to check that $\psi$ is
+  well-defined.
+
+  The relations among the generators $\zeta^i$ are additively
+  generated by $\zeta^ch(\zeta)$ as $c$ ranges from $0$ to
+  $\phi(d)-r-1$.  If we set
   $$A_c = \sum_{i=0}^r a_i \sum_{j=0}^{i+c-1} \zeta^j$$
@@
   $$\psi(\zeta^ch(\zeta)) = \alpha^{h(1)} \tilde{f}(A_c).$$
-Now consider $(\zeta - 1)A_c$: the sums telescope and we get that $(\zeta-1)A_c = \zeta^ch(\zeta) - h(1).$  There are now two possibilities:
+  Now consider $(\zeta - 1)A_c$: the sums telescope and we get that
+  $(\zeta-1)A_c = \zeta^ch(\zeta) - h(1).$ There are now two
+  possibilities:
   \begin{enumerate}
-\item $d$ is a power of $p$; write $s = \phi(d)m + n$.
-We may take $h(T)$ to be $p^m(T-1)^n$, in which case $\zeta^ch(\zeta) - h(1) \in P^s$, so $A_c$ is fixed under multiplication by $\zeta$ in $\ZZ[\zeta]/P^s$ and thus $\tilde{f}(A_c) = 1$.
-In this case $\alpha^{h(1)} = 1$ regardless of $\alpha$.
-\item $d$ is not a power of $p$.
-If two distinct primes divide $d$ then $\zeta - 1$ is a unit; otherwise $\zeta - 1$ is a unit modulo $P^s$.
-Let $\omega \in \ZZ[\zeta]$ satisfy $\omega(\zeta - 1) \equiv 1 \pmod{P^s}$ and set
+  \item $d$ is a power of $p$; write $s = \phi(d)m + n$.  We may take
+    $h(T)$ to be $p^m(T-1)^n$, in which case $\zeta^ch(\zeta) - h(1) \in P^s$,
+    so $A_c$ is fixed under multiplication by $\zeta$ in
+    $\ZZ[\zeta]/P^s$ and thus $\tilde{f}(A_c) = 1$.  In this case
+    $\alpha^{h(1)} = 1$ regardless of $\alpha$.
+  \item $d$ is not a power of $p$.  If two distinct primes divide $d$
+    then $\zeta - 1$ is a unit; otherwise $\zeta - 1$ is a unit modulo
+    $P^s$.  Let $\omega \in \ZZ[\zeta]$ satisfy
+    $\omega(\zeta - 1) \equiv 1 \pmod{P^s}$ and set
     \begin{equation} \label{alpha-def}
@@
     \end{equation}
-Then $A_c + h(1)\omega$ is fixed under multiplication by $\zeta$ and thus $\tilde{f}(A_c) = \tilde{f}(-h(1)\omega)$.
+    Then $A_c + h(1)\omega$ is fixed under multiplication by $\zeta$
+    and thus $\tilde{f}(A_c) = \tilde{f}(-h(1)\omega)$.
   \end{enumerate}
-In either case, $\psi(\zeta^ch(\zeta)) = 1$ for all $c$.
-The only other relations imposed on the $\zeta^i$ are that they are all killed under multiplication by $p^s$.
-Since $\tilde{f}$ is also a homomorphism $\ZZ[\zeta]/P^s \rightarrow \EE^\times$ the values of $\tilde{f}$ and thus of $\psi$ will be $p^s$-roots of unity.
+  In either case, $\psi(\zeta^ch(\zeta)) = 1$ for all $c$.  The only
+  other relations imposed on the $\zeta^i$ are that they are all
+  killed under multiplication by $p^s$.  Since $\tilde{f}$ is also a
+  homomorphism $\ZZ[\zeta]/P^s \rightarrow \EE^\times$ the values of
+  $\tilde{f}$ and thus of $\psi$ will be $p^s$-roots of unity.
   Therefore $\psi$ is well defined.
 
-We now check equation \ref{eq:psi-condition} for $x = \zeta^{\phi(d)-1}$.  Write $\Phi_d(T) = T^{\phi(d)} - b_{\phi(d)-1}T^{\phi(d)-1} - \cdots - b_0$ and set
+  We now check equation \ref{eq:psi-condition} for
+  $x = \zeta^{\phi(d)-1}$.  Write
+  $\Phi_d(T) = T^{\phi(d)} - b_{\phi(d)-1}T^{\phi(d)-1} - \cdots - b_0$
+  and set
   $$B = \sum_{i=0}^{\phi(d)-1} -\zeta^i + b_i \sum_{j=0}^{i-1} \zeta^j.$$
@@
   \begin{align*}
-\frac{\psi(\zeta^{\phi(d)})}{\psi(\zeta^{\phi(d)-1})\tilde{f}(\zeta^{\phi(d)-1})} &= \frac{\psi(b_{\phi(d)-1}\zeta^{\phi(d)-1} + \cdots + b_0)}{\psi(\zeta^{\phi(d)-1})\tilde{f}(\zeta^{\phi(d)-1})} \\
+    \frac{\psi(\zeta^{\phi(d)})}{\psi(\zeta^{\phi(d)-1})\tilde{f}(\zeta^{\phi(d)-1})}
+    &= \frac{\psi(b_{\phi(d)-1}\zeta^{\phi(d)-1} + \cdots + b_0)}{\psi(\zeta^{\phi(d)-1})\tilde{f}(\zeta^{\phi(d)-1})} \\
     &= \alpha^{-\Phi_d(1)} \tilde{f}(B)
   \end{align*}
-As before we see that $(\zeta - 1)B = \Phi_d(1) - \Phi_d(\zeta) = \Phi_d(1)$.  We consider the same cases as before:
+  As before we see that $(\zeta - 1)B = \Phi_d(1) - \Phi_d(\zeta) = \Phi_d(1)$.
+  We consider the same cases as before:
 
   \begin{enumerate}
-\item $d$ is a power of $p$, in which case $\Phi_d(1) = p$.
-Thus $(\zeta-1)B = p = u(\zeta-1)^{\phi(d)}$ for a unit $u \in \ZZ[\zeta]$ and $B - u(\zeta-1)^{\phi(d)-1}$ is fixed by $\zeta$, so that $\tilde{f}(B) = \tilde{f}(u(\zeta - 1)^{\phi(d)-1})$.
-The multiplicative order of $\tilde{f}(u(\zeta-1)^{\phi(d)-1})$ is at most $\lceil \frac{s - 1 - (\phi(d)-1)}{\phi(d)}\rceil = \lceil \frac{s}{\phi(d)} \rceil - 1$ while the additive order of $1 \in \ZZ[\zeta]/P^s$ is $\lceil \frac{s}{\phi(d)} \rceil$.
+  \item $d$ is a power of $p$, in which case $\Phi_d(1) = p$.  Thus
+    $(\zeta-1)B = p = u(\zeta-1)^{\phi(d)}$ for a unit $u \in \ZZ[\zeta]$
+    and $B - u(\zeta-1)^{\phi(d)-1}$ is fixed by $\zeta$,
+    so that $\tilde{f}(B) = \tilde{f}(u(\zeta - 1)^{\phi(d)-1})$.  The
+    multiplicative order of $\tilde{f}(u(\zeta-1)^{\phi(d)-1})$ is at most
+    $\lceil \frac{s - 1 - (\phi(d)-1)}{\phi(d)}\rceil = \lceil \frac{s}{\phi(d)} \rceil - 1$
+    while the additive order of $1 \in \ZZ[\zeta]/P^s$ is $\lceil \frac{s}{\phi(d)} \rceil$.
     Thus we may choose $\alpha = \psi(1)$ with $\alpha^p = \tilde{f}(B)$.
-\item $d$ is not a power of $p$ and $\omega$ is the inverse of $\zeta-1$ modulo $P^s$.  Then $\tilde{f}(B) = \tilde{f}(\omega\Phi_d(1))$.
+  \item $d$ is not a power of $p$ and $\omega$ is the inverse of
+    $\zeta-1$ modulo $P^s$.  Then $\tilde{f}(B) = \tilde{f}(\omega\Phi_d(1))$.
   \end{enumerate}
-In either case, $\alpha^{-\Phi_d(1)}\tilde{f}(B) = 1$ and thus $\psi$ satisfies equation \ref{eq:psi-condition} for $x = \zeta^{\phi(d)-1}$.
-The definition of $\psi$ in \ref{eq:psi-def} immediately implies that $\psi$ satisfies equation \ref{eq:psi-condition} for lesser powers of $\zeta$, and thus for all $x$ by linearity.
-The existence of $\psi$ shows that $\rho$ is injective.
+  In either case, $\alpha^{-\Phi_d(1)}\tilde{f}(B) = 1$ and thus
+  $\psi$ satisfies equation \ref{eq:psi-condition} for
+  $x = \zeta^{\phi(d)-1}$.  The definition of $\psi$ in \ref{eq:psi-def}
+  immediately implies that $\psi$ satisfies equation
+  \ref{eq:psi-condition} for lesser powers of $\zeta$, and thus for
+  all $x$ by linearity.  The existence of $\psi$ shows that $\rho$ is injective.
 \end{proof}
@@
 %\subsection*{Restriction to the identity component is surjective}
+
 Let $G^0$ be the connected component of $G$ containing the identity.
-By Proposition~\ref{prop:pullback}, pull-back along $G^0\hookrightarrow G$ determines a monoidal functor $\cs{L}\mapsto \cs{L}\vert_{G^0}$ from $\CS(G)$ to $\CS(G^0)$.
-In this section we show that this functor is essentially surjective.
-To do this we employ a perspective on characters sheaves which is different from that in Section~\ref{section:category} but which works very well for geometrically connected abelian algebraic groups; this perspective fails to extend properly to the more general context of Section~\ref{section:category}.
+By Proposition~\ref{prop:pullback}, pull-back along
+$G^0\hookrightarrow G$ determines a monoidal functor
+$\cs{L}\mapsto \cs{L}\vert_{G^0}$ from $\CS(G)$ to $\CS(G^0)$.  In
+this section we show that this functor is essentially surjective. To
+do this we employ a perspective on characters sheaves which is
+different from that in Section~\ref{section:category} but which works
+very well for geometrically connected abelian algebraic groups; this
+perspective fails to extend properly to the more general context of
+Section~\ref{section:category}.
 
@@
 \begin{proof}
-Because $G$ is smooth over $\Fq$, the identity component $G^0$ is a geometrically connected algebraic group over $\Fq$, clopen in $G$ \cite{vdG&M}*{3.17}.
-By Proposition~\ref{prop:connected-1}, every character sheaf $\cs{E} = (\gcs{E},\mu^0,F^0)$ on $G^0$ descends to a line bundle on $G^0$.
-%
-Let us review how line bundles on $G^0$ determine character sheaves on $G^0$.
-Up to isomorphism, line bundles on $G^0$ may be apprehended in terms of pairs $(\pi,\psi)$, \David{Aren't there line bundles which are not character sheaves, for which $B$ is not an algebraic group?} where $\pi : B\to G^0$ is a finite etale morphism of algebraic groups and a character $\psi : A\to \EE^\times$, where $\Gal(\bFq/\Fq)$ acts trivially on $A \ceq \ker {\bar \pi}$, as summarized by the following diagram.
+  Because $G$ is smooth over $\Fq$, the identity component $G^0$ is a
+  geometrically connected algebraic group over $\Fq$, clopen in $G$
+  \cite{vdG&M}*{3.17}. By Proposition~\ref{prop:connected-1}, every
+  character sheaf $\cs{E} = (\gcs{E},\mu^0,F^0)$ on $G^0$ descends to
+  a line bundle on $G^0$.
+
+  Let us review how line bundles on $G^0$ determine character sheaves
+  on $G^0$.  Up to isomorphism, line bundles on $G^0$ may be
+  apprehended in terms of pairs $(\pi,\psi)$,
+  \David{Aren't there line bundles which are not character sheaves,
+    for which $B$ is not an algebraic group?}
+  where $\pi : B\to G^0$ is a finite etale morphism of algebraic
+  groups and a character $\psi : A\to \EE^\times$, where
+  $\Gal(\bFq/\Fq)$ acts trivially on $A \ceq \ker {\bar \pi}$, as
+  summarized by the following diagram.
   \begin{equation}\label{E}
@@
   \end{equation}
-(In fact, we may always take $B = G^0$ and $\pi = \Lang_{G^0}$, the Lang isogeny for $G^0$.)
-Indeed, $\cs{E}$ is precisely the component of $\pi_! (\EE)_{B}$ on which $A$ acts through $\psi$. 
-To see that $\cs{E}$ is a line bundle on $G^0$, start by pulling back $\pi: B \to G^0$ along $m_0 : G^0\times G^0 \to G^0$.
+  (In fact, we may always take $B = G^0$ and $\pi = \Lang_{G^0}$, the
+  Lang isogeny for $G^0$.)  Indeed, $\cs{E}$ is precisely the
+  component of $\pi_! (\EE)_{B}$ on which $A$ acts through $\psi$.  To
+  see that $\cs{E}$ is a line bundle on $G^0$, start by pulling back
+  $\pi: B \to G^0$ along $m_0 : G^0\times G^0 \to G^0$.
   \begin{equation}
@@
       \EE^\times & 1\ar[r] & \ar@/_1pc/[ll]_{\psi} A  \ar[r] & B \ar[r]^{\pi} & G^0 \ar[r] & 1\\
-  	& 1\ar[r] & \ar@{.>}@/^1pc/[llu] \ar[u] A\times A  \ar[r]& \ar[u]^{m_{B}} B\times B \ar[r]^{\pi\tighttimes \pi}  & \ar[u]^{m_0} G^0\times G^0 \ar[r] & 1\\
+      & 1\ar[r] & \ar@{.>}@/^1pc/[llu] \ar[u] A\times A  \ar[r]
+      & \ar[u]^{m_{B}} B\times B \ar[r]^{\pi\tighttimes \pi}  & \ar[u]^{m_0} G^0\times G^0 \ar[r] & 1\\
       }
   \end{equation}
-As pictured above, the kernel of this pull-back is $A\times A$; indeed, $A\times A\to B\times B$ is the pull-back of $A\to B$ along $m_{B}$.
-Use this Cartesian square to define a character (the dotted arrow, above) of $A\times A$; that is, define $A\times A\to \EE^\times$ by the composition of $A\times A \to A$ and $\psi : A\to \EE^\times$.
+  As pictured above, the kernel of this pull-back is $A\times A$;
+  indeed, $A\times A\to B\times B$ is the pull-back of $A\to B$ along
+  $m_{B}$. Use this Cartesian square to define a character (the dotted
+  arrow, above) of $A\times A$; that is, define $A\times A\to \EE^\times$
+  by the composition of $A\times A \to A$ and $\psi : A\to \EE^\times$.
   Note that this character is $\psi \otimes \psi : A\times A\to \EE^\times$.
-\Clifton{I haven't explained how maps between diagrams define sheaf homomorphisms between local systems.}
-Since the lower sequence is precisely the sequence defining $\cs{E}\boxtimes\cs{E}$, this shows that, by construction, $\cs{E}$ comes equipped with a canonical isomorphism $m_0^*\cs{E} \iso \cs{E}\boxtimes\cs{E}$.
-Now the base change $\cs{E}$ comes equipped with isomorphisms $F^0 : \Frob_{G^0}^* \gcs{E} \to \gcs{E}$ and $\mu^0 : {\bar m}_0^* \gcs{E} \to \gcs{E}\boxtimes \gcs{E}$ satisfying conditions \ref{CS.1} and \ref{CS.2}.
-Then $(\gcs{E},\mu^0,F^0)$ is a character sheaf on $G^0$.
-
-The next step is to show that $\pi: B \to G^0$ extends to a finite etale morphism of group schemes $f: H\to G$, smooth and locally of finite type over $\Fq$, in such a way that $H^0 = B$, $f^0 =\pi$ and $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism of component groups.
+  \Clifton{I haven't explained how maps between diagrams define sheaf
+    homomorphisms between local systems.}
+  Since the lower sequence is precisely the sequence defining
+  $\cs{E}\boxtimes\cs{E}$, this shows that, by construction, $\cs{E}$
+  comes equipped with a canonical isomorphism $m_0^*\cs{E} \iso \cs{E}\boxtimes\cs{E}$.
+  Now the base change $\cs{E}$ comes equipped with isomorphisms
+  $F^0 : \Frob_{G^0}^* \gcs{E} \to \gcs{E}$ and
+  $\mu^0 : {\bar m}_0^* \gcs{E} \to \gcs{E}\boxtimes \gcs{E}$
+  satisfying conditions \ref{CS.1} and \ref{CS.2}. Then $(\gcs{E},\mu^0,F^0)$
+  is a character sheaf of $G^0$.
+
+  The next step is to show that $\pi: B \to G^0$ extends to a finite
+  etale morphism of group schemes $f: H\to G$, smooth and locally of
+  finite type over $\Fq$, in such a way that $H^0 = B$, $f^0 =\pi$ and
+  $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism of component
+  groups.
   \begin{equation} \label{extension-diagram}
@@
       & B \ar[r] \ar[d]_{\pi} & H \ar[r] \ar[d]_{f} & \pi_0(H) \ar[d]_{\pi_0(f)}^{\iso} \\
-        & G^0 \ar[r] & G \ar[r] & \pi_0(G).}
+      & G^0 \ar[r] & G \ar[r] & \pi_0(G).
+    }
   \end{equation}
-where all rows and columns are exact and all maps are defined over $\Fq$.
-We will do so by passing back and forth between group schemes over $\Fq$ and their $\bFq$-points.
-Extensions of $G^0(\bFq)$ by $A(\bFq)$, such as $A(\bFq) \to H^0(\bFq) \to G^0(\bFq)$, correspond to classes in $\Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))$.
-Similarly, extensions of $G(\bFq)$ by $A(\bFq)$ correspond to classes in $\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq))$.
-The map $G^0(\bFq) \to G(\bFq)$ induces a map $\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))$, fitting into the long exact sequence derived from applying $\Hom(\mbox{---}, A(\bFq))$ to $G^0(\bFq) \to G(\bFq) \to \pi_0(G)(\bFq)$:
+  where all rows and columns are exact and all maps are defined over
+  $\Fq$.  We will do so by passing back and forth between group
+  schemes over $\Fq$ and their $\bFq$-points.  Extensions of
+  $G^0(\bFq)$ by $A(\bFq)$, such as $A(\bFq) \to H^0(\bFq) \to G^0(\bFq)$,
+  correspond to classes in $\Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))$.
+  Similarly, extensions of $G(\bFq)$ by $A(\bFq)$ correspond to
+  classes in $\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq))$.  The map
+  $G^0(\bFq) \to G(\bFq)$ induces a map
+  $\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))$,
+  fitting into the long exact sequence derived from applying
+  $\Hom(\mbox{---}, A(\bFq))$ to $G^0(\bFq) \to G(\bFq) \to \pi_0(G)(\bFq)$:
   $$\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)).$$
@@
 
-It suffices to show that $\pi_0(G)(\bFq)$ has a two-term resolution by injective $\ZZ[\Gamma]$-modules.
-Since the action of $\Gamma$ on $\pi_0(G)(\bFq)$ is continuous, it factor through a finite quotient $\Gamma_m = \Gamma / H_m$.
-Any product of Dedekind domains has cohomological dimension $1$ \cite[?]{?}, so $\pi_0(G)(\bFq)$ has a two term resolution by injective $\ZZ[\Gamma_m]$-modules.
-Let $I$ be one of these modules: we need to show that $I$ is injective as a $\ZZ[\Gamma]$-module.
-Consider the universal diagram for injectivity:
+  It suffices to show that $\pi_0(G)(\bFq)$ has a two-term resolution
+  by injective $\ZZ[\Gamma]$-modules.  Since the action of $\Gamma$ on
+  $\pi_0(G)(\bFq)$ is continuous, it factor through a finite quotient
+  $\Gamma_m = \Gamma / H_m$.  Any product of Dedekind domains has
+  cohomological dimension $1$ \cite[?]{?}, so $\pi_0(G)(\bFq)$ has a
+  two term resolution by injective $\ZZ[\Gamma_m]$-modules.  Let $I$
+  be one of these modules: we need to show that $I$ is injective as a
+  $\ZZ[\Gamma]$-module.  Consider the universal diagram for injectivity:
   \[
@@
     I & A \ar@{>->}[u] \ar[l]_{a}
-}\]
-where $A$ and $B$ are arbitrary $\ZZ[\Gamma]$-modules.
-Since $H_m$ acts trivially on $I$, $I_{H_m}A := \langle (\gamma-1)a : \gamma \in H_m, a \in A \rangle \subseteq \ker(a).$  Since $B / I_{H_m}B \cong B \otimes_A A / I_{H_m}A$, we get
+    }
+  \]
+
+  where $A$ and $B$ are arbitrary $\ZZ[\Gamma]$-modules.  Since $H_m$ acts trivially on $I$,
+  $I_{H_m}A := \langle (\gamma-1)a : \gamma \in H_m, a \in A \rangle \subseteq \ker(a).$
+  Since $B / I_{H_m}B \cong B \otimes_A A / I_{H_m}A$, we get
   \[
@@
     I & A/I_{H_m}A \ar@{>->}[u] \ar[l] & A \ar@{>->}[u] \ar@{->>}[l]
-}\]
-The dotted arrow exists since $I$ is injective as a $\ZZ[\Gamma_m]$-module, and the outer diagram shows that $I$ is injective as a $\ZZ[\Gamma]$-module.
-
-We therefore have the existence of diagram \eqref{extension-diagram} at the level of $\bFq$-points.
-This expresses $H(\bFq)$ as a disjoint union of translates of $B(\bFq)$; by transport of structure we may take $H$ to be a group scheme over $\bFq$.
-Similarly, the restriction of $f$ to each component of $H$ is a morphism of schemes, and thus $f$ is as well.
-Finally, the whole diagram descends to a diagram of $\Fq$-schemes since the $\bFq$-points of the objects come equipped with continuous $\Gamma$-actions, and the morphisms are $\Gamma$-equivariant.
-
-Now we show that $f : H\to G$, as above, together with a character $\psi : \ker {\bar f} \to \EE^\times$, defines a character sheaf on $G$.
-We will also show that the restriction of this character sheaf on $G$ to $G^0$ is precisely the character sheaf on $G^0$ defined by the pair $(f^0,\psi)$ as above.
-%
-Set $X \ceq \pi_0(G)\times_{\Spec{\Fq}} \Spec{\bFq}$.
-We will identify $X$ with $\pi_0(H)\times_{\Spec{\Fq}} \Spec{\bFq}$ using the base change of $\pi_0(f): \pi_0(H)\to \pi_0(G)$.
-For each $x\in X$, write ${\bar f}^x : {\bar H}^x \to {\bar G}^x$ for the restriction of ${\bar f}$ to ${\bar H}^x$, as a cover of ${\bar G}^x$.
-For each $x,y\in X$, let ${\bar m}_{x,y} : {\bar H}^x \times {\bar H}^{y} \to {\bar H}^{x+y}$ be the map obtained from ${\bar m}$ by restriction.
-Define ${\bar m}_{x} : A\to \Aut({\bar f}^x)$ by ${\bar m}_{x}(a): g \mapsto {\bar m}_{0,x}(a,g)$; then ${\bar m}_{x} : A\to \Aut({\bar f}^x)$ is an isomorphism.
+    }
+  \]
+  The dotted arrow exists since $I$ is injective as a
+  $\ZZ[\Gamma_m]$-module, and the outer diagram shows that $I$ is
+  injective as a $\ZZ[\Gamma]$-module.
+
+  We therefore have the existence of diagram \eqref{extension-diagram}
+  at the level of $\bFq$-points.  This expresses $H(\bFq)$ as a
+  disjoint union of translates of $B(\bFq)$; by transport of structure
+  we may take $H$ to be a group scheme over $\bFq$.  Similarly, the
+  restriction of $f$ to each component of $H$ is a morphism of
+  schemes, and thus $f$ is as well.  Finally, the whole diagram
+  descends to a diagram of $\Fq$-schemes since the $\bFq$-points of
+  the objects come equipped with continuous $\Gamma$-actions, and the
+  morphisms are $\Gamma$-equivariant.
+
+  Now we show that $f : H\to G$, as above, together with a character
+  $\psi : \ker {\bar f} \to \EE^\times$, defines a character sheaf on
+  $G$. We will also show that the restriction of this character sheaf
+  on $G$ to $G^0$ is precisely the character sheaf on $G^0$ defined by
+  the pair $(f^0,\psi)$ as above.
+
+  Set $X \ceq \pi_0(G)\times_{\Spec{\Fq}} \Spec{\bFq}$. We will
+  identify $X$ with $\pi_0(H)\times_{\Spec{\Fq}} \Spec{\bFq}$ using
+  the base change of $\pi_0(f): \pi_0(H)\to \pi_0(G)$. For each $x\in X$,
+  write ${\bar f}^x : {\bar H}^x \to {\bar G}^x$ for the
+  restriction of ${\bar f}$ to ${\bar H}^x$, as a cover of
+  ${\bar G}^x$. For each $x,y\in X$, let
+  ${\bar m}_{x,y} : {\bar H}^x \times {\bar H}^{y} \to {\bar H}^{x+y}$
+  be the map obtained from ${\bar m}$ by restriction. Define
+  ${\bar m}_{x} : A\to \Aut({\bar f}^x)$ by
+  ${\bar m}_{x}(a): g \mapsto {\bar m}_{0,x}(a,g)$; then
+  ${\bar m}_{x} : A\to \Aut({\bar f}^x)$ is an isomorphism.
   \Clifton{I need to show that ${\bar m}_{x} : A\to \Aut({\bar f}^x)$ is an isomorphism.}
 
-For each $x\in X$ let $\gcs{L}^x$ be the rank-$1$ local system on ${\bar G}^x$ determined by the finite etale cover ${\bar f}^x : {\bar H}^x \to {\bar G}^x$ and the character $\psi_x \ceq \psi \circ {\bar m}_x^{-1}$.
-Since ${\bar G} = \coprod_{x\in X} {\bar G}^x$ (disjoint union), this determines a constructible sheaf $\gcs{L}$ on ${\bar G}$, locally constant of rank-$1$ on each connected component of ${\bar G}$.
-Taking the case $x=0$ we observe that $\gcs{L}^0 =\gcs{E}$, the latter defined above.
-To finish the proof of the proposition we equip $\gcs{L}$ with isomorphisms $\mu : {\bar m}^* \gcs{L} \to \gcs{L} \boxtimes\gcs{L}$ and $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ satisfying conditions \ref{CS.1} and \ref{CS.2}.
-
-Observe that ${\bar m}: {\bar G}\times {\bar G}\to {\bar G}$ is completely determined by the family of maps ${\bar m}_{x,y} : {\bar G}^x \times {\bar G}^{y} \to {\bar G}^{x+y}$.
-Accordingly, to define $\mu$ for $\gcs{L}$ it is sufficient to define isomorphisms $\mu_{x,y} : {\bar m}_{x,y}^*\gcs{L}^{x+y} \iso \gcs{L}^{x}\boxtimes \gcs{L}^{y}$ for all $x,y\in X$.
-To do that, note first that the local system $\gcs{L}^{x}\boxtimes \gcs{L}^{y}$ is defined by the following diagram.
+  For each $x\in X$ let $\gcs{L}^x$ be the rank-$1$ local system on
+  ${\bar G}^x$ determined by the finite etale cover
+  ${\bar f}^x : {\bar H}^x \to {\bar G}^x$ and the character
+  $\psi_x \ceq \psi \circ {\bar m}_x^{-1}$.  Since
+  ${\bar G} = \coprod_{x\in X} {\bar G}^x$ (disjoint union), this
+  determines a constructible sheaf $\gcs{L}$ on ${\bar G}$, locally
+  constant of rank-$1$ on each connected component of ${\bar G}$.
+  Taking the case $x=0$ we observe that $\gcs{L}^0 =\gcs{E}$,
+  the latter defined above. To finish the proof of the proposition we
+  equip $\gcs{L}$ with isomorphisms
+  $\mu : {\bar m}^* \gcs{L} \to \gcs{L} \boxtimes\gcs{L}$ and
+  $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ satisfying conditions \ref{CS.1}
+  and \ref{CS.2}.
+
+  Observe that ${\bar m}: {\bar G}\times {\bar G}\to {\bar G}$ is
+  completely determined by the family of maps
+  ${\bar m}_{x,y} : {\bar G}^x \times {\bar G}^{y} \to {\bar G}^{x+y}$.
+  Accordingly, to define $\mu$ for $\gcs{L}$ it is sufficient to define isomorphisms
+  $\mu_{x,y} : {\bar m}_{x,y}^*\gcs{L}^{x+y} \iso \gcs{L}^{x}\boxtimes \gcs{L}^{y}$
+  for all $x,y\in X$. To do that, note first that the local system
+  $\gcs{L}^{x}\boxtimes \gcs{L}^{y}$ is defined by the following diagram.
   \[
@@
   \]
-On the other hand, the diagram for the local system ${\bar m}_{x,y}^* \gcs{L}^{x+y}$ is found by pulling-back the diagram for $\gcs{L}^{x+y}$ along ${\bar m}_{x,y} : {\bar H}^x\times{\bar H}^y \to {\bar H}^{x+y}$; the result is the middle horizontal diagram below, where we use the fact that the covering group of the middle arrow is $\Aut({\bar f}^{x+y})$, canonically.
+  On the other hand, the diagram for the local system ${\bar m}_{x,y}^* \gcs{L}^{x+y}$
+  is found by pulling-back the diagram for $\gcs{L}^{x+y}$ along
+  ${\bar m}_{x,y} : {\bar H}^x\times{\bar H}^y \to {\bar H}^{x+y}$;
+  the result is the middle horizontal diagram below, where we use the
+  fact that the covering group of the middle arrow is $\Aut({\bar f}^{x+y})$, canonically.
   \[
@@
     & \ar@(ul,dl) & {\bar H}^{x+y} \ar[rr]^{{\bar f}^{x+y}} && {\bar G}^{x+y}\\
-\EE^\times & \ar@{.>}[l] \Aut({\bar f}^{x+y})  \ar@{=}[u] &  \ar@{.>}@(ul,dl) & \ar[u] {\bar H}^{x+y} \times_{{\bar G}^x\times{\bar G}^y} {\bar G}^x\times{\bar G}^y \ar[rr] && \ar[u]_{{\bar m}_{x,y}} {\bar G}^x\times {\bar G}^y\\
+    \EE^\times & \ar@{.>}[l] \Aut({\bar f}^{x+y})  \ar@{=}[u] &  \ar@{.>}@(ul,dl)
+    & \ar[u] {\bar H}^{x+y} \times_{{\bar G}^x\times{\bar G}^y} {\bar G}^x\times{\bar G}^y \ar[rr]
+    && \ar[u]_{{\bar m}_{x,y}} {\bar G}^x\times {\bar G}^y\\
     & \ar[lu]_{\psi_x\otimes \psi_y} \ar@{.>}[u] \Aut({\bar f}^x)\times \Aut({\bar f}^y)
-& \ar@(ul,dl) & \ar[u] {\bar H}^x\times {\bar H}^y \ar[rr]^{{\bar f}^x\times {\bar f}^y} && \ar@{=}[u] {\bar G}^x\times {\bar G}^y\\ 
-}
-\]
-Now, the homomorphism from the covering group of ${\bar f}^x\times{\bar f}^y$ to the covering group of ${\bar f}^{x+y}$ induced by the composition $ {\bar H}^x\times {\bar H}^y \to {\bar H}^{x+y} \times_{{\bar G}^x\times{\bar G}^y} {\bar G}^x\times{\bar G}^y \to {\bar H}^{x+y}$ is precisely $({\bar m}_x(a),{\bar m}_y(b)) \mapsto {\bar m}_{x+y}(ab)$.
-Since this map commutes with the characters $\psi_x\otimes\psi_y$ and $\psi_{x+y}$ (so, the far-left triangle commutes in the diagram above) it follows that, for each $x,y\in X$ the diagram above defines a canonical isomorphism
+    & \ar@(ul,dl) & \ar[u] {\bar H}^x\times {\bar H}^y \ar[rr]^{{\bar f}^x\times {\bar f}^y}
+    && \ar@{=}[u] {\bar G}^x\times {\bar G}^y\\
+    }
+  \]
+  Now, the homomorphism from the covering group of
+  ${\bar f}^x\times{\bar f}^y$ to the covering group of
+  ${\bar f}^{x+y}$ induced by the composition
+  $ {\bar H}^x\times {\bar H}^y \to {\bar H}^{x+y} \times_{{\bar G}^x\times{\bar G}^y} {\bar G}^x\times{\bar G}^y \to {\bar H}^{x+y}$
+  is precisely $({\bar m}_x(a),{\bar m}_y(b)) \mapsto {\bar m}_{x+y}(ab)$.
+  Since this map commutes with the characters $\psi_x\otimes\psi_y$
+  and $\psi_{x+y}$ (so, the far-left triangle commutes in the diagram above)
+  it follows that, for each $x,y\in X$ the diagram above defines a canonical isomorphism
   $\mu_{x,y} : {\bar m}_{x,y}^* \gcs{L}^{x+y} \to \gcs{L}^x \boxtimes\gcs{L}^y$.
-This defines $\mu: {\bar m}^* \gcs{L} \iso \gcs{L} \boxtimes\gcs{L}$. It is straightforward (but laborious) to show that the pair $(\gcs{L},\mu)$ satisfies condition \ref{CS.1}.
+  This defines $\mu: {\bar m}^* \gcs{L} \iso \gcs{L} \boxtimes\gcs{L}$.
+  It is straightforward (but laborious) to show that the pair
+  $(\gcs{L},\mu)$ satisfies condition \ref{CS.1}.
 
   Now we turn to the definition of $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$.
-As above, we define this isomorphism through a family of isomorphisms on the connected components of ${\bar G}$.
-The restriction of $\Frob_{G}$ to ${\bar G}^x$ defines an isomorphism $\Frob_x : {\bar G}^x \to {\bar G}^{\Frob(x)}$.
+  As above, we define this isomorphism through a family of
+  isomorphisms on the connected components of ${\bar G}$. The
+  restriction of $\Frob_{G}$ to ${\bar G}^x$ defines an isomorphism
+  $\Frob_x : {\bar G}^x \to {\bar G}^{\Frob(x)}$.
   %\[
@@
   %\]
-Pull back the finite etale covering in the diagram for $\gcs{L}^{\Frob(x)}$ along $\Frob_x$ and compare the result with the finite etale covering in the diagram for $\gcs{L}^{x}$.
-\[
-\xymatrix{ 
-  && \ar[dll]_{\psi_{\Frob(x)}} \Aut({\bar f}^{\Frob(x)}) & \ar@(ul,dl) & {\bar H}^{\Frob(x)} \ar[rr]^{{\bar f}^{\Frob(x)}} && {\bar G}^{\Frob(x)}\\ 
-\EE^\times & & \ar@{.>}[ll] \Aut({\bar f}^{\Frob(x)})  \ar@{=}[u] & \ar@{.>}@(ul,dl)  & \ar[u] {\bar H}^{\Frob(x)} \times_{{\bar G}^{\Frob(x)}} {\bar G}^x \ar[rr] && \ar[u]_{\Frob_{x}} {\bar G}^x\\
-& &  \ar[ull]^{\psi_x}  \ar@{.>}[u] \Aut({\bar f}^{x}) & \ar@(ul,dl) & \ar[u] {\bar H}^x \ar[rr] && \ar@{=} [u] {\bar G}^x\\
-}
-\] 
-The covering group of ${\bar H}^{\Frob(x)} \times_{{\bar G}^{\Frob(x)}} {\bar G}^x$ is isomorphic to $\Aut({\bar f}^{\Frob(x)})$, canonically, so $\Frob_x^* \gcs{L}^{\Frob(x)}$ is defined by the middle (horizontal) diagram, above.
-We define the sheaf homomorphism $F_x : \Frob_x^* \gcs{L}^{\Frob(x)} \to \gcs{L}^x$ by the canonical morphism ${\bar H}^x \to  {\bar H}^{\Frob(x)} \times_{{\bar G}^{\Frob(x)}} {\bar G}^x \to $; to see that this defines a sheaf homomorphism it is sufficient to check that the character $\psi_x$ commutes with the
-The family of isomorphisms  $F_x : (\Frob_{G}^* \gcs{L})\vert_{{\bar G}^x} \iso \Frob_x^* \gcs{L}^{\Frob{x}} \to \gcs{L}^x$ now defines the isomorphism $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$. 
+  Pull back the finite etale covering in the diagram for
+  $\gcs{L}^{\Frob(x)}$ along $\Frob_x$ and compare the result with the
+  finite etale covering in the diagram for $\gcs{L}^{x}$.
+
+  \[
+  \xymatrix{
+    && \ar[dll]_{\psi_{\Frob(x)}} \Aut({\bar f}^{\Frob(x)}) & \ar@(ul,dl)
+    & {\bar H}^{\Frob(x)} \ar[rr]^{{\bar f}^{\Frob(x)}} && {\bar G}^{\Frob(x)}\\
+    \EE^\times & & \ar@{.>}[ll] \Aut({\bar f}^{\Frob(x)})  \ar@{=}[u] & \ar@{.>}@(ul,dl)
+    & \ar[u] {\bar H}^{\Frob(x)} \times_{{\bar G}^{\Frob(x)}} {\bar G}^x \ar[rr] && \ar[u]_{\Frob_{x}} {\bar G}^x\\
+    & &  \ar[ull]^{\psi_x}  \ar@{.>}[u] \Aut({\bar f}^{x}) & \ar@(ul,dl)
+    & \ar[u] {\bar H}^x \ar[rr] && \ar@{=} [u] {\bar G}^x\\
+    }
+  \]
+  The covering group of ${\bar H}^{\Frob(x)} \times_{{\bar G}^{\Frob(x)}} {\bar G}^x$
+  is isomorphic to $\Aut({\bar f}^{\Frob(x)})$, canonically, so
+  $\Frob_x^* \gcs{L}^{\Frob(x)}$ is defined by the middle (horizontal)
+  diagram, above.  We define the sheaf homomorphism
+  $F_x : \Frob_x^* \gcs{L}^{\Frob(x)} \to \gcs{L}^x$ by the canonical morphism
+  ${\bar H}^x \to {\bar H}^{\Frob(x)} \times_{{\bar G}^{\Frob(x)}} {\bar G}^x \to $;
+  to see that this defines a sheaf homomorphism it is sufficient to
+  check that the character $\psi_x$ commutes with the family of isomorphisms
+  $F_x : (\Frob_{G}^* \gcs{L})\vert_{{\bar G}^x} \iso \Frob_x^* \gcs{L}^{\Frob{x}} \to \gcs{L}^x$
+  now defines the isomorphism $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$.
   \Clifton{Add some detail here.}
@@
 \begin{remark}
-We have seen that if $f : H\to G$ is a finite etale cover of $G$ by a smooth group scheme and if all geometric automorphisms of $f$ are fixed by Frobenius, then every character of $\ker f$ determines a character sheaf on $G$.
-However, it is not true that every character sheaf on $G$, in the sense of Section~\ref{sec:category} arises not all character sheaves on $G$ arise in this manner.
+  We have seen that if $f : H\to G$ is a finite etale cover of $G$ by
+  a smooth group scheme and if all geometric automorphisms of $f$ are
+  fixed by Frobenius, then every character of $\ker f$ determines a
+  character sheaf on $G$. However, it is not true that every character
+  sheaf on $G$, in the sense of Section~\ref{sec:category} arises not
+  all character sheaves on $G$ arise in this manner.
 \end{remark}
@@
 \begin{theorem}\label{thm:snake}
-If $G$ is a smooth abelian group scheme, locally of finite type over $\Fq$, and the abelian group $\pi_0(G)(\bFq)$ (the geometric component group) is finitely generated, then the trace of Frobenius homomorphism
+  If $G$ is a smooth abelian group scheme, locally of finite type over
+  $\Fq$, and the abelian group $\pi_0(G)(\bFq)$ (the geometric
+  component group) is finitely generated, then the trace of Frobenius
+  homomorphism
   \[
@@
   \]
-from the Picard group of the category of character sheaves on $G$ to the group of characters of $G(\Fq)$, is an isomorphism. 
+  from the Picard group of the category of character sheaves on $G$ to
+  the group of characters of $G(\Fq)$, is an isomorphism.
 \end{theorem}
@@
 \begin{proof}
-Consider the short exact sequence in the category of smooth group schemes, locally of finite type over $\Fq$, defining the component group scheme for $G$:
+  Consider the short exact sequence in the category of smooth group
+  schemes, locally of finite type over $\Fq$, defining the component
+  group scheme for $G$:
   \begin{equation}\label{eq:pi0}
@@
     & \ar[d] \ker t_{\pi_0(G)} & \ar@{.>}[d] \ker t_{G} & \ar[d] \ker t_{G^0} & \\
-0\ar[r] & \ar[d]^{t_{\pi_0(G)}} \CS(\pi_0(G))_{/\text{iso}} \ar[r] & \ar[d]^{t_{G}} \CS(G)_{/\text{iso}} \ar[r] & \ar[d]^{t_{G^0}} \CS(G^0)_{/\text{iso}} \ar[r] & 0\\
-0 \ar[r] & \ar[d] \Hom(\pi_0(G)(\Fq),\EE^\times) \ar[r] & \ar@{.>}[d] \Hom(G(\Fq),\EE^\times) \ar[r] & \ar[d] \Hom(G^0(\Fq),\EE^\times) \ar[r] & 0\\
+    0\ar[r] & \ar[d]^{t_{\pi_0(G)}} \CS(\pi_0(G))_{/\text{iso}} \ar[r]
+    & \ar[d]^{t_{G}} \CS(G)_{/\text{iso}} \ar[r] & \ar[d]^{t_{G^0}} \CS(G^0)_{/\text{iso}} \ar[r] & 0\\
+    0 \ar[r] & \ar[d] \Hom(\pi_0(G)(\Fq),\EE^\times) \ar[r]
+    & \ar@{.>}[d] \Hom(G(\Fq),\EE^\times) \ar[r] & \ar[d] \Hom(G^0(\Fq),\EE^\times) \ar[r] & 0\\
     & \coker t_{\pi_0(G)} & \coker t_{G} &  \coker t_{G^0} & \\
@@
   \]
-be the commutative diagram of abelian groups obtained by applying Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.
-By Proposition~\ref{prop:connected-1}, $\ker t_{G^0} =0$ and $\coker t_{G^0}=0$. By Propositions~\ref{prop:etale} and \ref{prop:X}, $\ker t_{\pi_0(G)}=0$ and $\coker t_{\pi_0(G)}=0$.
-
-The sequence of character groups is left-exact: by Proposition~\ref{prop:pullback}, it is dual to the exact sequence of abelian groups
+  be the commutative diagram of abelian groups obtained by applying
+  Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.  By
+  Proposition~\ref{prop:connected-1}, $\ker t_{G^0} =0$ and $\coker t_{G^0}=0$.
+  By Propositions~\ref{prop:etale} and \ref{prop:X}, $\ker t_{\pi_0(G)}=0$
+  and $\coker t_{\pi_0(G)}=0$.
+
+  The sequence of character groups is left-exact: by
+  Proposition~\ref{prop:pullback}, it is dual to the exact sequence of
+  abelian groups
   \begin{equation}\label{eq:pi0}
@@
   \end{equation}
-since $\Hom(\ - \ ,\EE^\times)$ is left-exact, the sequence of character groups is left exact.
-
-The sequence of Picard groups is right-exact:  it is exact at $\CS(G^0)_{/\text{iso}}$ by Proposition~\ref{prop:restriction}; and it is exact at $\CS(G)_{/\text{iso}}$ because the left-square commutes (by Proposition~\ref{prop:pullback}), the bottom sequence is exact at $\Hom(G(\Fq),\EE^\times)$ and $\coker t_{\pi_0(G)} =0$ (by Propositions~\ref{prop:etale} and \ref{prop:X}) and
+  since $\Hom(\ - \ ,\EE^\times)$ is left-exact, the sequence of
+  character groups is left exact.
+
+  The sequence of Picard groups is right-exact: it is exact at
+  $\CS(G^0)_{/\text{iso}}$ by Proposition~\ref{prop:restriction}; and
+  it is exact at $\CS(G)_{/\text{iso}}$ because the left-square
+  commutes (by Proposition~\ref{prop:pullback}), the bottom sequence
+  is exact at $\Hom(G(\Fq),\EE^\times)$ and $\coker t_{\pi_0(G)} =0$
+  (by Propositions~\ref{prop:etale} and \ref{prop:X}) and
   \[
@@
   \]
-by the last part of Proposition~\ref{prop:pullback}.
-Specifically, suppose $\cs{L}$ is a character sheaf on $G$ that is trivial on $G^0$.
-Then $t^\Frob_\cs{L}\vert_{G^0(\Fq)} = t^\Frob_{\cs{L}^0} =0$, by Proposition~\ref{prop:pullback} again.
-Since the sequence of character groups is exact at $\Hom(G(\Fq),\EE^\times)$, there is some $\chi \in \Hom(\pi_0(G)(\Fq),\EE^\times)$ such that the pull-back of $\chi$ along $G(\Fq)\to \pi_0(G)(\Fq)$ is $t^\Frob_\cs{L}$.
-By Propositions~\ref{prop:etale} and \ref{prop:X}, there is a a character sheaf $\cs{L}_\chi$ on $\pi_0(G)$, unique up to isomorphism, such that $t^\Frob_{\cs{L}_\chi} = \chi$.
-By Proposition~\ref{prop:pullback} again, $\cs{L}$ is isomorphic to the image of $\cs{L}_\chi$ under the monoidal functor $\CS(\pi_0(G)) \to \CS(G)$.
-
-It now follows immediately from the snake lemma that $t_{G}$ is an isomorphism of groups.
+  by the last part of Proposition~\ref{prop:pullback}. Specifically,
+  suppose $\cs{L}$ is a character sheaf on $G$ that is trivial on
+  $G^0$. Then $t^\Frob_\cs{L}\vert_{G^0(\Fq)} = t^\Frob_{\cs{L}^0} =0$,
+  by Proposition~\ref{prop:pullback} again. Since the sequence of
+  character groups is exact at $\Hom(G(\Fq),\EE^\times)$, there is
+  some $\chi \in \Hom(\pi_0(G)(\Fq),\EE^\times)$ such that the
+  pull-back of $\chi$ along $G(\Fq)\to \pi_0(G)(\Fq)$ is
+  $t^\Frob_\cs{L}$. By Propositions~\ref{prop:etale} and \ref{prop:X},
+  there is a a character sheaf $\cs{L}_\chi$ on $\pi_0(G)$, unique up
+  to isomorphism, such that $t^\Frob_{\cs{L}_\chi} = \chi$. By
+  Proposition~\ref{prop:pullback} again, $\cs{L}$ is isomorphic to the
+  image of $\cs{L}_\chi$ under the monoidal functor $\CS(\pi_0(G)) \to \CS(G)$.
+
+  It now follows immediately from the snake lemma that $t_{G}$ is an
+  isomorphism of groups.
 \end{proof}
@@
 %\input{GdeN}
-Let $p$ be a prime number. Let $K$ be a local field with residue field $\Fq$, where $p$ divides $q$. Let $\OK$ be the ring of integers of $K$ and let $\pK$ be the maximal ideal in $\OK$.
+Let $p$ be a prime number. Let $K$ be a local field with residue field
+$\Fq$, where $p$ divides $q$. Let $\OK$ be the ring of integers of $K$
+and let $\pK$ be the maximal ideal in $\OK$.
 %
-In this section we introduce a group scheme $\GN{T}$ over $\Fq$ obtained by applying the Greenberg functor to the N\'eron lft-model for $T$ and establish some basic facts about $\GN{T}$
+In this section we introduce a group scheme $\GN{T}$ over $\Fq$
+obtained by applying the Greenberg functor to the N\'eron lft-model
+for $T$ and establish some basic facts about $\GN{T}$
 
@@
 
-The lft-N\'eron model for $T$, denoted here by $\TT$, is a separated, smooth, commutative group scheme locally of finite type over $\OK$ with generic fibre $T$, that enjoys the N\'eron mapping property: if $X$ is a smooth scheme over $\OK$ then every morphism $X_\eta \to T$ over $K$ extends uniquely to a morphism $X \to \TT$.
-Equivalently, the N\'eron mapping property states that the function $\Hom_{\OK} (X,\TT) \to \Hom_K(X_\eta,T)$, given by restriction to generic fibres, is a bijection; in particular, this implies $\TT(\OK) = T(K)$.
-
-For each $d\in \NN$, let $\TT_{d}$ be the smooth group scheme over $\OK/\pK^{d+1}$ obtained from $\TT$ by base change along $\OK \to \OK/\pK^{d+1}$.
-Observe that $\OK/\pK^{d+1}$ is an Artin ring and $\TT_{d}$ is locally of finite type over $\OK/\pK^{d+1}$.
-%
-Let $\GN{T}_{d}$ be the group scheme over $\Fq$ produced by applying the Greenberg functor to $\TT_{d}$. (See \cite{Greenberg:2} and \cite[Ch. 9, \S 6]{BLR} for background on the Greenberg functor.) 
+The lft-N\'eron model for $T$, denoted here by $\TT$, is a separated,
+smooth, commutative group scheme locally of finite type over $\OK$
+with generic fibre $T$, that enjoys the N\'eron mapping property: if
+$X$ is a smooth scheme over $\OK$ then every morphism $X_\eta \to T$
+over $K$ extends uniquely to a morphism $X \to \TT$. Equivalently, the
+N\'eron mapping property states that the function
+$\Hom_{\OK} (X,\TT) \to \Hom_K(X_\eta,T)$, given by restriction to
+generic fibres, is a bijection; in particular, this implies $\TT(\OK) = T(K)$.
+
+For each $d\in \NN$, let $\TT_{d}$ be the smooth group scheme over
+$\OK/\pK^{d+1}$ obtained from $\TT$ by base change along $\OK \to
+\OK/\pK^{d+1}$. Observe that $\OK/\pK^{d+1}$ is an Artin ring and
+$\TT_{d}$ is locally of finite type over $\OK/\pK^{d+1}$.
+
+Let $\GN{T}_{d}$ be the group scheme over $\Fq$ produced by applying
+the Greenberg functor to $\TT_{d}$. (See \cite{Greenberg:2} and
+\cite[Ch. 9, \S 6]{BLR} for background on the Greenberg functor.)
 %Then $\GN{T}_d(\Fq) = \TT(\OK/\pK^{d+1})$.
@@
   \begin{enumerate}
- \labitem{(GNd.0)}{GN0} $\GN{T}_d^0$, the identity component of $\GN{T}_d$, is a commutative algebraic group over $\Fq$;
+  \labitem{(GNd.0)}{GN0} $\GN{T}_d^0$, the identity component of
+    $\GN{T}_d$, is a commutative algebraic group over $\Fq$;
   \labitem{(GNd.1)}{GNd} $\GN{T}_d$ is smooth and locally of finite type over $\Fq$;
@@
   Let $T$ be an algebraic torus over a non-Archimdean local field $K$.
-Let $\GN{T}_d$ and $\GN{T}$ be as above.
-For each $d\in \NN$, the Picard group of the category of character sheaves on $\GN{T}_d$ is canonically isomorphic to the group of characters of $T(K)$ of depth at most $d$:
+  Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d\in \NN$, the
+  Picard group of the category of character sheaves on $\GN{T}_d$ is
+  canonically isomorphic to the group of characters of $T(K)$ of depth
+  at most $d$:
   \[
@@
 \begin{proof}
-By \ref{GNd} and \ref{fg}, we may apply Theorem~\ref{thm:snake} to $\GN{T}_d$ which provides a canonical isomorphism 
+  By \ref{GNd} and \ref{fg}, we may apply Theorem~\ref{thm:snake} to
+  $\GN{T}_d$ which provides a canonical isomorphism
   \[
@@
   By \ref{dFq}, $\GN{T}_d(\Fq) \iso \TT(\OK/\pK^{d+1})$ canonically.
-To finish the proof we recall that the filtration of $T(K)$ used to define depth has the property
-that $\TT(\OK/\pK^{d+1}) \cong T(K) / T(K)_d$ \cite[Prop 5.2]{Yu}.  Thus characters of $\GN{T}_d(\Fq)$ are in bijection with characters of $T(K)$ vanishing on $T(K)_d$.
+  To finish the proof we recall that the filtration of $T(K)$ used to
+  define depth has the property that $\TT(\OK/\pK^{d+1}) \cong T(K) / T(K)_d$
+  \cite[Prop 5.2]{Yu}.  Thus characters of $\GN{T}_d(\Fq)$ are
+  in bijection with characters of $T(K)$ vanishing on $T(K)_d$.
 \end{proof}
@@
 %\input{pro}
-To conclude the paper we offer an interpretation of Theorem~\ref{thm:application} that makes no mention of depth.
+To conclude the paper we offer an interpretation of
+Theorem~\ref{thm:application} that makes no mention of depth.
 
@@
 
-We may now assemble the group $\Fq$-schemes $\TT_{d}$ into one glorious group pro-scheme over $\Fq$:
+We may now assemble the group $\Fq$-schemes $\TT_{d}$ into one
+glorious group pro-scheme over $\Fq$:
 \begin{equation}\label{projlim}
@@
 
-\Clifton{Prove that $\GN{T}$ is a scheme? Strictly speaking, we don't care about \ref{scheme}.}
+\Clifton{Prove that $\GN{T}$ is a scheme? Strictly speaking, we don't
+  care about \ref{scheme}.}
 \begin{proposition}

### 2013-06-25 shanghai.tex
d+1 to d

@@
 non-negative integer $d$, let $\GN{T}_d$ be the Greenberg transform of
-$\TT \otimes \OK/\pK^{d+1}$; the commutative group scheme $\GN{T}_d$
+$\TT \otimes \OK/\pK^d$; the commutative group scheme $\GN{T}_d$
 plays the r\^{o}le of $G$, above.
@@
 
-For each $d\in \NN$, let $\TT_{d}$ be the smooth group scheme over
-$\OK/\pK^{d+1}$ obtained from $\TT$ by base change along $\OK \to
-\OK/\pK^{d+1}$. Observe that $\OK/\pK^{d+1}$ is an Artin ring and
-$\TT_{d}$ is locally of finite type over $\OK/\pK^{d+1}$.
+For each $d\in \ZZ_{>0}$, let $\TT_{d}$ be the smooth group scheme over
+$\OK/\pK^d$ obtained from $\TT$ by base change along $\OK \to
+\OK/\pK^d$. Observe that $\OK/\pK^d$ is an Artin ring and
+$\TT_{d}$ is locally of finite type over $\OK/\pK^d$.
 
@@
 \cite[Ch. 9, \S 6]{BLR} for background on the Greenberg functor.)
-%Then $\GN{T}_d(\Fq) = \TT(\OK/\pK^{d+1})$.
+%Then $\GN{T}_d(\Fq) = \TT(\OK/\pK^d)$.
 
@@
   \labitem{(GNd.3)}{fg} the component group of $\GN{T}_d$ is geometrically finitely generated;
-  \labitem{(GNd.4)}{dFq} $\GN{T}_d(\Fq) = \TT(\OK/\pK^{d+1})$, canonically;
+  \labitem{(GNd.4)}{dFq} $\GN{T}_d(\Fq) = \TT(\OK/\pK^d)$, canonically;
 \end{enumerate}
@@
   Let $T$ be an algebraic torus over a non-Archimdean local field $K$.
-  Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d\in \NN$, the
+  Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d \in \ZZ_{>0}$, the
   Picard group of the category of character sheaves on $\GN{T}_d$ is
   canonically isomorphic to the group of characters of $T(K)$ of depth
-  at most $d$:
-  \[
-  \CS(\GN{T}_d)_{/\text{iso}} \iso \Hom_{\leq d}(T(K),\EE^\times).
+  less than $d$:
+  \[
+  \CS(\GN{T}_d)_{/\text{iso}} \iso \Hom_{< d}(T(K),\EE^\times).
   \]
@@
   \]
-  By \ref{dFq}, $\GN{T}_d(\Fq) \iso \TT(\OK/\pK^{d+1})$ canonically.
+  By \ref{dFq}, $\GN{T}_d(\Fq) \iso \TT(\OK/\pK^d)$ canonically.
   To finish the proof we recall that the filtration of $T(K)$ used to
-  define depth has the property that $\TT(\OK/\pK^{d+1}) \cong T(K) / T(K)_d$
-  \cite[Prop 5.2]{Yu}.  Thus characters of $\GN{T}_d(\Fq)$ are
+  define depth has the property that $\TT(\OK/\pK^d) \cong T(K) / T(K)_d$
+  \cite[Prop 5.2]{Yu} for $d \in \ZZ_{>0}$.  Thus characters of $\GN{T}_d(\Fq)$ are
   in bijection with characters of $T(K)$ vanishing on $T(K)_d$.

### 2013-06-25 shanghai.tex
Added a \CSiso command

@@
 \newcommand{\CS}{{\mathcal{C\hskip-1.8pt S}}}
+\newcommand{\CSiso}[1]{\CS(#1)_{/\textit{iso}}}
+\newcommand{\CSbiso}[1]{\CS_0(#1)_{/\text{iso}}}
 \newcommand{\CE}{{\mathcal{C\hskip-1.8pt E}}}
@@
 classes of character sheaves on $G$ form a group, denoted by
-$\CS(G)_{/\text{iso}}$; this is the Picard group of the category of
+$\CSiso{G}$; this is the Picard group of the category of
 character sheaves on $G$. Our application of character sheaves to
@@
 \[
-\CS(\textswab{T}_d)_{/\text{iso}} 
+\CSiso{\textswab{T}_d} 
 \iso
@@
 This rigid monoidal category structure for $\CS(G)$ puts a group
-structure on the set $\CS(G)_{/\text{iso}}$ of isomorphism classes in
+structure on the set $\CSiso{G}$ of isomorphism classes in
 $\CS(G)$; we refer to this as the \cdef{Picard group} of character
@@
 \[
-\cdef{t_{G}} : \CS(G)_{/\text{iso}} \longrightarrow \Hom_\text{grp}(G(\Fq),\EE^\times),
+\cdef{t_{G}} : \CSiso{G} \longrightarrow \Hom_\text{grp}(G(\Fq),\EE^\times),
 \qquad \text{defined by}\qquad \cs{L} \mapsto t^\Frob_\cs{L},
@@
   \xymatrix{
-  \CS(G)_{/\text{iso}} \ar[r]^{f^*} \ar[d]^{t_{G}} &  \ar[d]^{t_{H}} \CS(H)_{/\text{iso}}\\
+  \CSiso{G} \ar[r]^{f^*} \ar[d]^{t_{G}} &  \ar[d]^{t_{H}} \CSiso{H}\\
   \Hom_\text{grp}(G(\Fq),\EE^\times) \ar[r] & \Hom_\text{grp}(H(\Fq),\EE^\times)
@@
   \[
-  t_{G} : \CS(G)_{/\text{iso}} \to \Hom_\text{grp}(G(\Fq),\EE^\times),
+  t_{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EE^\times),
   \]
@@
   \[
-  b^* : \CS_0(G)_{/\text{iso}} \mathop{\longrightarrow}^{\iso} \CS(G)_{/\text{iso}}
+  b^* : \CSbiso{G} \mathop{\longrightarrow}^{\iso} \CSiso{G}
   \]
@@
   \[
-  t_{G} : \CS_0(G)_{/\text{iso}}\to \Hom_\text{grp}(G(\Fq),\EE^\times)
+  t_{G} : \CSbiso{G} \to \Hom_\text{grp}(G(\Fq),\EE^\times)
   \]
@@
   \[
-  \CS(G)_{/\text{iso}} \longrightarrow H^1(\Weil(\bFq/\Fq), \Hom_\text{grp}(G(\bFq),\EE^\times)),
+  \CSiso{G} \longrightarrow H^1(\Weil(\bFq/\Fq), \Hom_\text{grp}(G(\bFq),\EE^\times)),
   \qquad \text{given by}\qquad
@@
   proposition by exhibiting an isomorphism between
-  $\CS(G(\bFq))_{/\text{iso}}$ and $H^1(W_{\Fq}, G(\bFq)^*)$.
-
-  To produce the isomorphism between $\CS(G(\bFq))_{/\text{iso}}$ and
+  $\CSiso{G(\bFq)}$ and $H^1(W_{\Fq}, G(\bFq)^*)$.
+
+  To produce the isomorphism between $\CSiso{G(\bFq)}$ and
   $H^1(W_{\Fq}, G(\bFq)^*)$ we must pick a global section of the line
@@
   We now show that the function $\obj \CS(G(\bFq)) \longrightarrow H^1(W_\Fq,G(\bFq)^*)$
-  factors through $\obj \CS(G(\bFq)) \to \CS(G(\bFq))_{/\text{iso}}$.
+  factors through $\obj \CS(G(\bFq)) \to \CSiso{G(\bFq)}$.
   To see this, let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and
@@
   \begin{equation}\label{pich1}
-    \CS(G(\bFq)_{/\text{iso}} \longrightarrow H^1(W_\Fq,G(\bFq)^*),
+    \CSiso{G(\bFq} \longrightarrow H^1(W_\Fq,G(\bFq)^*),
     \qquad \text{defined by} \qquad [\cs{L}] \mapsto [t_\cs{L}].
@@
   \[
-  t_{G} : \CS(G)_{/\text{iso}} \to \Hom(G(\Fq),\EE^\times),
+  t_{G} : \CSiso{G} \to \Hom(G(\Fq),\EE^\times),
   \]
@@
     & \ar[d] \ker t_{\pi_0(G)} & \ar@{.>}[d] \ker t_{G} & \ar[d] \ker t_{G^0} & \\
-    0\ar[r] & \ar[d]^{t_{\pi_0(G)}} \CS(\pi_0(G))_{/\text{iso}} \ar[r]
-    & \ar[d]^{t_{G}} \CS(G)_{/\text{iso}} \ar[r] & \ar[d]^{t_{G^0}} \CS(G^0)_{/\text{iso}} \ar[r] & 0\\
+    0\ar[r] & \ar[d]^{t_{\pi_0(G)}} \CSiso{\pi_0(G)} \ar[r]
+    & \ar[d]^{t_{G}} \CSiso{G} \ar[r] & \ar[d]^{t_{G^0}} \CSiso{G^0} \ar[r] & 0\\
     0 \ar[r] & \ar[d] \Hom(\pi_0(G)(\Fq),\EE^\times) \ar[r]
@@
   The sequence of Picard groups is right-exact: it is exact at
-  $\CS(G^0)_{/\text{iso}}$ by Proposition~\ref{prop:restriction}; and
-  it is exact at $\CS(G)_{/\text{iso}}$ because the left-square
+  $\CSiso{G^0}$ by Proposition~\ref{prop:restriction}; and
+  it is exact at $\CSiso{G}$ because the left-square
   commutes (by Proposition~\ref{prop:pullback}), the bottom sequence
@@
   \[
-  \image(\CS(\pi_0(G))_{/\text{iso}} \to \CS(G)_{/\text{iso}}) \subseteq \ker(\CS(G)_{/\text{iso}} \to \CS(G^0)_{/\text{iso}}),
+  \image(\CSiso{\pi_0(G)} \to \CSiso{G}) \subseteq \ker(\CSiso{G} \to \CSiso{G^0}),
   \]
@@
   \[
-  \CS(\GN{T}_d)_{/\text{iso}} \iso \Hom_{< d}(T(K),\EE^\times).
+  \CSiso{\GN{T}_d} \iso \Hom_{< d}(T(K),\EE^\times).
   \]
@@
   \[
-  \CS(\GN{T}_d)_{/\text{iso}} \iso \Hom(\GN{T}_d(\Fq),\EE^\times).
+  \CSiso{\GN{T}_d} \iso \Hom(\GN{T}_d(\Fq),\EE^\times).
   \]
@@
   \[
-  \CS(\GN{T})_{/\text{iso}} \iso \Hom_\text{ad}(T(K),\EE^\times)
+  \CSiso{\GN{T}} \iso \Hom_\text{ad}(T(K),\EE^\times)
   \]

### 2013-06-25 shanghai.tex
Moved \bar from text to commands

@@
 \newcommand{\obj}{{\text{obj}\, }}
-\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-2pt\textbf{m},#1}}
+\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
 \newcommand{\GN}[1]{\textswab{#1}}
@@
 \newcommand{\tightertimes}{\hskip-3pt\times\hskip-3pt}
+\newcommand{\tighterboxtimes}{\hspace{-2pt}\boxtimes\hspace{-2pt}}
+
+\renewcommand{\bf}{\bar{f}}
+\newcommand{\bg}{\bar{g}}
+\newcommand{\bm}{\bar{m}}
+\newcommand{\bG}{\bar{G}}
+\newcommand{\bH}{\bar{H}}
+\newcommand{\GxG}{G \tightertimes G}
+\newcommand{\bGxG}{\bar{G} \tightertimes \bar{G}}
+\newcommand{\bfxf}{\bar{f} \tightertimes \bar{f}}
+\newcommand{\GxxG}{G \tighttimes G}
+\newcommand{\LxL}{\gcs{L} \tighterboxtimes \gcs{L}}
+
 \newcommand\todo[1]{\ \vspace{5mm}\par \noindent\framebox{\begin{minipage}[c]{0.95 \textwidth} \tt #1\end{minipage}} \vspace{5mm} \par}
@@
   group schemes $G$ locally of finite type over finite fields
-  $\mathbb{F}_q$. Assuming that the geometric component group of $G$
+  $\Fq$. Assuming that the geometric component group of $G$
   is finitely-generated, we show that the group of isomorphism classes
   of character sheaves on $G$ is canonically isomorphic to the group
-  of characters of $G(\mathbb{F}_q)$. We use this result to exhibit an
+  of characters of $G(\Fq)$. We use this result to exhibit an
   isomorphism between admissible characters of $T(K)$ and isomorphism
@@
 (\gcs{L},\mu,F)$ where $\gcs{L}$ is a constructible $\ell$-adic sheaf
-$\gcs{L}$ on the \'etale site of ${\bar G} \ceq G \times_{\Spec\Fq}
+$\gcs{L}$ on the \'etale site of $\bG \ceq G \times_{\Spec\Fq}
 \Spec{\bFq}$, locally constant of rank-$1$ on every connected
-component of ${\bar G}$, equipped with an isomorphism $\mu: m^*
-\gcs{L} \to \gcs{L}\boxtimes \gcs{L}$, where $m : G\times G \to G$ is
+component of $\bG$, equipped with an isomorphism $\mu: m^*
+\gcs{L} \to \LxL$, where $m : G\times G \to G$ is
 the group operation for $G$, and an isomorphism $F : \Frob_{G}^*
 \gcs{L} \to \gcs{L}$, where $\Frob_{G}$ is the Frobenius automorphism
-on ${\bar G}$, satisfying natural compatibility conditions with $\mu$;
+on $\bG$, satisfying natural compatibility conditions with $\mu$;
 these compatibility conditions are explained below.
@@
 \iso
-\Hom_{\leq d}(T(K),\EE^\times)
+\Hom_{< d}(T(K),\EE^\times)
 \] 
@@
   you took this cup from my lips, though.}  In particular, by
-specializing to the case $T= \mathbb{G}_{\hskip-1pt\text{m},K}$ and by
+specializing to the case $T= \Gm{K}$ and by
 choosing an isomorphism $\EE \approx \CC$ (unnatural though it may
@@
 Greenberg transform of the Neron model of
-$\mathbb{G}_{\hskip-2pt\text{m},K}$.
+$\Gm{K}$.
 
@@
 smooth and locally of finite type over a finite field $\Fq$; we write
-$m : G\tightertimes G\to G$ for the multiplication morphism. We fix an
-algebraic closure $\bFq$ of $\Fq$ and write ${\bar G} $ for the
+$m : \GxG\to G$ for the multiplication morphism. We fix an
+algebraic closure $\bFq$ of $\Fq$ and write $\bG $ for the
 commutative group scheme, smooth and locally of finite type over
 $\bFq$ obtained by base change; the multiplication morphism for
-${\bar G}$ will be denoted by ${\bar m}$. Let $\Frob_{G}$
-(resp. $\Frob_{G\tighttimes G}$) be the Frobenius automorphism of
-${\bar G}$ (resp. ${\bar G}\tightertimes {\bar G}$).
+$\bG$ will be denoted by $\bm$. Let $\Frob_{G}$
+(resp. $\Frob_{\GxxG}$) be the Frobenius automorphism of
+$\bG$ (resp. $\bGxG$).
 \Clifton{I'll insert a reference to SGA where Frobenius is defined for
@@
 \labitem{(CS.0)}{CS.0} $\gcs{L}$ is a constructible $\ell$-adic
-  sheaf on (the \'etale site of) ${\bar G}$, locally constant of rank
-  $1$ on connected components of ${\bar G}$;
-
-\labitem{(CS.1)}{CS.1} $\mu: {\bar m}^* \gcs{L} \to \gcs{L}\boxtimes \gcs{L}$
-  is an isomorphism of sheaves on ${\bar G}\tightertimes {\bar G}$ such that
-
-  \[
-  \xymatrix{
-    {\bar m}_3^*\gcs{L} \ar[rr]^{({\bar m}\times \id)^*\mu} \ar[d]_{(\id\tightertimes {\bar m})^*\mu}
-    &&  {\bar m}^*\gcs{L}\boxtimes \gcs{L} \ar[d]^{\mu \boxtimes \id} \\
-    \gcs{L} \boxtimes {\bar m}^* \gcs{L} \ar[rr]
-    &&  \gcs{L} \boxtimes\gcs{L} \boxtimes \gcs{L}\\
+  sheaf on (the \'etale site of) $\bG$, locally constant of rank
+  $1$ on connected components of $\bG$;
+
+\labitem{(CS.1)}{CS.1} $\mu: \bm^* \gcs{L} \to \LxL$
+  is an isomorphism of sheaves on $\bGxG$ such that
+
+  \[
+  \xymatrix{
+    \bm_3^*\gcs{L} \ar[rr]^{(\bm\times \id)^*\mu} \ar[d]_{(\id\tightertimes \bm)^*\mu}
+    &&  \bm^*\LxL \ar[d]^{\mu \boxtimes \id} \\
+    \gcs{L} \boxtimes \bm^* \gcs{L} \ar[rr]
+    &&  \gcs{L} \boxtimes\LxL\\
   }
@@
 \labitem{(CS.2)}{CS.2} $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ is an
-  isomorphism of sheaves on ${\bar G}$ compatible with $\mu$ in the sense that
-
-  \[
-  \xymatrix{
-    \Frob_{G\tighttimes G}^* {\bar m}^* \gcs{L} \ar[rr]^{\Frob_{G\tighttimes G}^*\mu}
-    && \Frob_{G\tighttimes G}^*(\gcs{L}\boxtimes \gcs{L})\\
-    \ar@{=}[u] {\bar m}^*  \Frob_{G}^* \gcs{L} \ar[d]_{{\bar m}^* F}
+  isomorphism of sheaves on $\bG$ compatible with $\mu$ in the sense that
+
+  \[
+  \xymatrix{
+    \Frob_{\GxxG}^* \bm^* \gcs{L} \ar[rr]^{\Frob_{\GxxG}^*\mu}
+    && \Frob_{\GxxG}^*(\LxL)\\
+    \ar@{=}[u] \bm^*  \Frob_{G}^* \gcs{L} \ar[d]_{\bm^* F}
     && \ar[d]^{F\boxtimes F} \ar@{=}[u] \Frob_{G}^*\gcs{L}\boxtimes \Frob_{G}^*\gcs{L}\\
-    {\bar m}^*\gcs{L} \ar[rr]^{\mu}
-    && \gcs{L} \boxtimes\gcs{L}\\
+    \bm^*\gcs{L} \ar[rr]^{\mu}
+    && \LxL\\
   }
@@
   $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$
-  of constructible $\ell$-adic sheaves on ${\bar G}$ such then
+  of constructible $\ell$-adic sheaves on $\bG$ such then
   \[
@@
 $\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', F\otimes F')$
-with duals formed by applying the functor $\sheafHom(\ - \ ,(\EE)_{\bar G})$ to
+with duals formed by applying the functor $\sheafHom(\ - \ ,(\EE)_{\bG})$ to
 conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}.
@@
 Let $\cs{L}$ be a character sheaf on $G$. Every $g\in G(\Fq)$
-determines a point ${\bar g}$ on ${\bar G}$ fixed by $\Frob_G$ and
-therefore an automorphism $F_{\bar g}$ of $\gcs{L}_{\bar g}$. Note
-that $\Aut_{\EE}(\gcs{L}_{\bar g}) \iso \EE^\times$, canonically (this
+determines a point $\bg$ on $\bG$ fixed by $\Frob_G$ and
+therefore an automorphism $F_{\bg}$ of $\gcs{L}_{\bg}$. Note
+that $\Aut_{\EE}(\gcs{L}_{\bg}) \iso \EE^\times$, canonically (this
 follows from second condition appearing in the definition of character
-sheaves). The isomorphism $\mu : {\bar m}^* \gcs{L} \to \gcs{L}\boxtimes\gcs{L}$
+sheaves). The isomorphism $\mu : \bm^* \gcs{L} \to \gcs{L}\boxtimes\gcs{L}$
 guarantees that the function $t^\Frob_\cs{L} : G(\Fq)\to \EE^\times$,
-defined by $g \mapsto F_{\bar g}$, is a group homomorphism;
+defined by $g \mapsto F_{\bg}$, is a group homomorphism;
 we refer to $t^\Frob_\cs{L}$ as the \cdef{trace of Frobenius of $\cs{L}$}.
@@
   If $f : H\to G$ is a morphism of commutative group schemes locally of finite type over $\Fq$ then
-  $(\gcs{L},\mu,F) \mapsto ({\bar f}^*\gcs{L},({\bar f}\tightertimes{\bar f})^*\mu,{\bar f}^*F)$
+  $(\gcs{L},\mu,F) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
   defines a monoidal functor $f^* : \CS(G) \to \CS(H)$ such that
@@
   Let $\cs{L}$ be a character sheaf on $G$. We start by showing that
-  ${\bar f}^*\gcs{L}$ is locally constant on connected components of
-  ${\bar H}$. Let $c_j :{\bar H}^j \hookrightarrow {\bar H}$ be any
+  $\bf^*\gcs{L}$ is locally constant on connected components of
+  $\bH$. Let $c_j :\bH^j \hookrightarrow \bH$ be any
   connected component and let $i$ be the image of $j$ under the group
-  homomorphism $\pi_0({\bar G}) \to \pi_0({\bar H})$ obtained by
-  applying the functor $\pi_0$ to ${\bar f}$; see \cite{vdG&M}*{III, 3.28}, for example.
+  homomorphism $\pi_0(\bG) \to \pi_0(\bH)$ obtained by
+  applying the functor $\pi_0$ to $\bf$; see \cite{vdG&M}*{III, 3.28}, for example.
   \Clifton{Replace with a better reference, eventually.}
-  Write $c_i : \bar{G}^i \hookrightarrow \bar{G}$ for
-  the inclusion of $\bar{G}^i$ and ${\bar f}^j : {\bar H}^j \to {\bar G}^i$
-  for the restriction of $f$ to $\bar{H}^j$.  Since $\cs{L}$
+  Write $c_i : \bG^i \hookrightarrow \bG$ for
+  the inclusion of $\bG^i$ and $\bf^j : \bH^j \to \bG^i$
+  for the restriction of $f$ to $\bH^j$.  Since $\cs{L}$
   is a character sheaf, $\gcs{L}$ is locally constant on the connect
-  components of ${\bar G}$; thus, there is a finite etale covering
-  $a_i : X_i \to {\bar G}^i$ such that $a_i^* (\gcs{L}\vert_{\bar G^i})$
-  is constant. Let $b_j : Y_j \to {\bar H}^j$ be the
-  pull-back of $a_i$ along ${\bar f}^j$; let $g_j : Y_j \to X_i$ be
-  the map opposite ${\bar f}^j$. Then $b_j$ is a finite etale covering
-  of ${\bar H}^j$ and
-  \[
-  b_j^* \left( ({\bar f}^* \gcs{L})\vert_{{\bar H}^j}\right)
-  = ({\bar f}\circ c_j \circ b_j)^*\gcs{L}
-  = (c_i\circ a_i\circ g_j)^*\gcs{L} = g_j^* a_i^* (\gcs{L}\vert_{\bar G^i}).
-  \]
-
-  Since $a_i^* (\gcs{L}\vert_{\bar G^i})$ is a constant sheaf and since the pull-back
+  components of $\bG$; thus, there is a finite etale covering
+  $a_i : X_i \to \bG^i$ such that $a_i^* (\gcs{L}\vert_{\bG^i})$
+  is constant. Let $b_j : Y_j \to \bH^j$ be the
+  pull-back of $a_i$ along $\bf^j$; let $g_j : Y_j \to X_i$ be
+  the map opposite $\bf^j$. Then $b_j$ is a finite etale covering
+  of $\bH^j$ and
+  \[
+  b_j^* \left( (\bf^* \gcs{L})\vert_{\bH^j}\right)
+  = (\bf\circ c_j \circ b_j)^*\gcs{L}
+  = (c_i\circ a_i\circ g_j)^*\gcs{L} = g_j^* a_i^* (\gcs{L}\vert_{\bG^i}).
+  \]
+
+  Since $a_i^* (\gcs{L}\vert_{\bG^i})$ is a constant sheaf and since the pull-back
   of a constant sheaf (along $g_j$, in this case) is a constant sheaf,
-  it follows that $b_j^* \left( ({\bar f}^*\gcs{L})\vert_{{\bar H}^j}\right)$
-  is a constant sheaf. Thus, ${\bar f}^*\gcs{L}$ is locally constant on
-  ${\bar H}^j$. Since $({\bar f}^*\gcs{L})_{\bar g} = \gcs{L}_{f({\bar g})}$ for every
-  geometric point ${\bar g}$ on ${\bar G}$, and since $\gcs{L}$ has
-  rank $1$ on connected components of ${\bar G}$, it follows that
-  $f^*\gcs{L}$ also has rank $1$ on connected components of ${\bar G}$.
-  This completes the proof that ${\bar f}^*\gcs{L}$ satisfies condition \ref{CS.0}.
-
-  To see that $({\bar f}\tightertimes {\bar f})^* \gcs{L}$ satisfies
-  condition \ref{CS.1} simply apply the functor $({\bar f}\tightertimes {\bar f})^*$
+  it follows that $b_j^* \left( (\bf^*\gcs{L})\vert_{\bH^j}\right)$
+  is a constant sheaf. Thus, $\bf^*\gcs{L}$ is locally constant on
+  $\bH^j$. Since $(\bf^*\gcs{L})_{\bg} = \gcs{L}_{f(\bg)}$ for every
+  geometric point ${\bg}$ on $\bG$, and since $\gcs{L}$ has
+  rank $1$ on connected components of $\bG$, it follows that
+  $f^*\gcs{L}$ also has rank $1$ on connected components of $\bG$.
+  This completes the proof that $\bf^*\gcs{L}$ satisfies condition \ref{CS.0}.
+
+  To see that $(\bfxf)^* \gcs{L}$ satisfies
+  condition \ref{CS.1} simply apply the functor $(\bfxf)^*$
   to \ref{CS.1} for $\cs{L}$ and use the canonical isomorphism
-  $({\bar f}\tightertimes {\bar f})^*(\gcs{L} \boxtimes\gcs{L}) \iso {\bar f}^*\gcs{L} \boxtimes {\bar f}^*\gcs{L}$
-  (a few times). Likewise, to see that ${\bar f}^*\gcs{L}$ satisfies condition
+  $(\bfxf)^*(\LxL) \iso \bf^*\gcs{L} \boxtimes \bf^*\gcs{L}$
+  (a few times). Likewise, to see that $\bf^*\gcs{L}$ satisfies condition
   \ref{CS.2}, apply the same functor to \ref{CS.2} for $\gcs{L}$.
   Then use the fact that $f$ is defined over $\Fq$, so
-  $({\bar f}\tightertimes {\bar f})^*\Frob_{G\tighttimes G}^* \iso \Frob_{G\tighttimes G} ({\bar f}\tightertimes {\bar f})^*$,
+  $(\bfxf)^*\Frob_{\GxxG}^* \iso \Frob_{\GxxG} (\bfxf)^*$,
   and the fact that $f$ is a morphism of group schemes, so
-  $({\bar f}\tightertimes {\bar f})^* {\bar m}^*\iso {\bar m}^* {\bar f}^*$
+  $(\bfxf)^* \bm^*\iso \bm^* \bf^*$
   (isomorphisms of functors on constructible sheaves).
 
-  To see that $(\gcs{L},\mu,F) \mapsto ({\bar f}^*\gcs{L},({\bar f}\tightertimes {\bar f})^*\mu,{\bar f}^*F)$
-  defines a functor $f^* : \CS(G) \to \CS(H)$ one applies the functors ${\bar f}^*$ and
-  ${\bar f}^*\tightertimes{\bar f}^*$ to \ref{CS.3} and argue as
+  To see that $(\gcs{L},\mu,F) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
+  defines a functor $f^* : \CS(G) \to \CS(H)$ one applies the functors $\bf^*$ and
+  $\bf^*\tightertimes\bf^*$ to \ref{CS.3} and argue as
   above. It follows from the fact that sheaf hom commutes with these
@@
   $G$ \cite{Deligne:Weil2}*{1.1.10} (by a Weil local system on $G$ we
-  mean a Weil sheaf on $G$ which is a local system on ${\bar G}$).
+  mean a Weil sheaf on $G$ which is a local system on $\bG$).
   While is it not true that all Weil local systems on $G$
@@
   \David{Should we move this definition since it will be important elsewhere?}
-  Let $b : {\bar G} \to G$ be base change
+  Let $b : \bG \to G$ be base change
   (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$).
@@
   Let $g$ be any $\Fq$-rational point on $G$ (such as the identity for
-  $G$) and let ${\bar g}$ be the geometric point on $G$ lying above
+  $G$) and let $\bg$ be the geometric point on $G$ lying above
   $g$ (we fixed $\Fq \hookrightarrow \bFq$ long ago). Since $G$ is
-  geometrically connected, the geometric point ${\bar g}$ determines
+  geometrically connected, the geometric point $\bg$ determines
   an equivalence between the category of Weil local systems on $G$ and
-  $\ell$-adic representations of $\Weil(G,{\bar g})$
+  $\ell$-adic representations of $\Weil(G,\bg)$
   \cite{Deligne:Weil2}*{1.1.12}. Now let $(\gcs{L},\mu,F)$ be a
@@
   system $(\gcs{L},F)$ corresponds to an $\ell$-adic character of the
-  Weil group $\Weil(G, {\bar g})$. The $\Fq$-rational point $g$ under
-  the geometric point ${\bar g}$ determines a splitting
-  $\Weil(\bFq/\Fq)\to \Weil(G,{\bar g})$ of the exact sequence
-  \[
-  \xymatrix{
-    1 \ar[r] & \pi_1({\bar G}, {\bar g}) \ar[r] &  \Weil(G,{\bar g}) \ar[r]
+  Weil group $\Weil(G, \bg)$. The $\Fq$-rational point $g$ under
+  the geometric point $\bg$ determines a splitting
+  $\Weil(\bFq/\Fq)\to \Weil(G,\bg)$ of the exact sequence
+  \[
+  \xymatrix{
+    1 \ar[r] & \pi_1(\bG, \bg) \ar[r] &  \Weil(G,\bg) \ar[r]
     & \ar@/_1pc/@{.>}[l]_{g} \Weil(\bFq/\Fq) \ar[r] & 1
@@
   \xymatrix{
-    1 \ar[r] & \ar@{=}[d] \pi_1({\bar G}, {\bar g}) \ar[r] & \ar[d] \Weil(G,{\bar g}) \ar[r] & \ar[d]  \Weil(\bFq/\Fq) \ar[r] & 1\\
-    1 \ar[r] &  \pi_1({\bar G}, {\bar g}) \ar[r] & \pi_1(G,{\bar g}) \ar[r] & \Gal(\bFq/\Fq) \ar[r] & 1\\
+    1 \ar[r] & \ar@{=}[d] \pi_1(\bG, \bg) \ar[r] & \ar[d] \Weil(G,\bg) \ar[r] & \ar[d]  \Weil(\bFq/\Fq) \ar[r] & 1\\
+    1 \ar[r] &  \pi_1(\bG, \bg) \ar[r] & \pi_1(G,\bg) \ar[r] & \Gal(\bFq/\Fq) \ar[r] & 1\\
     }
@@
   We may now lift the $\ell$-adic character $t_{(\gcs{L},F)}(g) : \Gal(\bFq/\Fq) \to \EE^\times$
-  to an $\ell$-adic character of $\pi_1(G,{\bar g})$ using the canonical topological group map
-  $\pi_1(G,{\bar g}) \to \Gal(\bFq/\Fq)$, above. But ${\bar g}$ also
+  to an $\ell$-adic character of $\pi_1(G,\bg)$ using the canonical topological group map
+  $\pi_1(G,\bg) \to \Gal(\bFq/\Fq)$, above. But $\bg$ also
   determines an equivalence between the category of $\ell$-adic
-  representations of $\pi_1(G,{\bar g})$ and local systems on $G$. Let
+  representations of $\pi_1(G,\bg)$ and local systems on $G$. Let
   $\cs{L}_0$ be a local system on $G$ in the isomorphism class
-  determined by this $\ell$-adic character of $\pi_1(G,{\bar g})$.
+  determined by this $\ell$-adic character of $\pi_1(G,\bg)$.
   Then $b^*\cs{L}_0 \iso \gcs{L}$, so $b^*$ is essentially surjective.
@@
   \[
-  \CSiso{G} \longrightarrow H^1(\Weil(\bFq/\Fq), \Hom_\text{grp}(G(\bFq),\EE^\times)),
+  \CSiso{G} \longrightarrow \Hh^1(\Weil(\bFq/\Fq), \Hom_\text{grp}(G(\bFq),\EE^\times)),
   \qquad \text{given by}\qquad
@@
   proposition by exhibiting an isomorphism between
-  $\CSiso{G(\bFq)}$ and $H^1(W_{\Fq}, G(\bFq)^*)$.
+  $\CSiso{G(\bFq)}$ and $\Hh^1(W_{\Fq}, G(\bFq)^*)$.
 
   To produce the isomorphism between $\CSiso{G(\bFq)}$ and
-  $H^1(W_{\Fq}, G(\bFq)^*)$ we must pick a global section of the line
+  $\Hh^1(W_{\Fq}, G(\bFq)^*)$ we must pick a global section of the line
   bundle $(\gcs{L},\mu)$, for each character sheaf $\cs{L}$ on $G$. We
@@
   \begin{equation}\label{cohomologous}
-    \obj \CS(G(\bFq)) \longrightarrow H^1(W_\Fq,G(\bFq)^*),
+    \obj \CS(G(\bFq)) \longrightarrow \Hh^1(W_\Fq,G(\bFq)^*),
     \qquad \text{defined by} \qquad \cs{L} \mapsto [t_\cs{L}],
@@
 
-  We now show that the function $\obj \CS(G(\bFq)) \longrightarrow H^1(W_\Fq,G(\bFq)^*)$
+  We now show that the function $\obj \CS(G(\bFq)) \longrightarrow \Hh^1(W_\Fq,G(\bFq)^*)$
   factors through $\obj \CS(G(\bFq)) \to \CSiso{G(\bFq)}$.
@@
   \begin{equation}\label{pich1}
-    \CSiso{G(\bFq} \longrightarrow H^1(W_\Fq,G(\bFq)^*),
+    \CSiso{G(\bFq} \longrightarrow \Hh^1(W_\Fq,G(\bFq)^*),
     \qquad \text{defined by} \qquad [\cs{L}] \mapsto [t_\cs{L}].
@@
   $F^0 : \Frob_{G^0}^* \gcs{E} \to \gcs{E}$ and
-  $\mu^0 : {\bar m}_0^* \gcs{E} \to \gcs{E}\boxtimes \gcs{E}$
+  $\mu^0 : \bm_0^* \gcs{E} \to \gcs{E}\boxtimes \gcs{E}$
   satisfying conditions \ref{CS.1} and \ref{CS.2}. Then $(\gcs{E},\mu^0,F^0)$
@@
   Now we show that $f : H\to G$, as above, together with a character
-  $\psi : \ker {\bar f} \to \EE^\times$, defines a character sheaf on
+  $\psi : \ker \bf \to \EE^\times$, defines a character sheaf on
   $G$. We will also show that the restriction of this character sheaf
@@
   the base change of $\pi_0(f): \pi_0(H)\to \pi_0(G)$. For each $x\in X$,
-  write ${\bar f}^x : {\bar H}^x \to {\bar G}^x$ for the
-  restriction of ${\bar f}$ to ${\bar H}^x$, as a cover of
-  ${\bar G}^x$. For each $x,y\in X$, let
-  ${\bar m}_{x,y} : {\bar H}^x \times {\bar H}^{y} \to {\bar H}^{x+y}$
-  be the map obtained from ${\bar m}$ by restriction. Define
-  ${\bar m}_{x} : A\to \Aut({\bar f}^x)$ by
-  ${\bar m}_{x}(a): g \mapsto {\bar m}_{0,x}(a,g)$; then
-  ${\bar m}_{x} : A\to \Aut({\bar f}^x)$ is an isomorphism.
-  \Clifton{I need to show that ${\bar m}_{x} : A\to \Aut({\bar f}^x)$ is an isomorphism.}
+  write $\bf^x : \bH^x \to \bG^x$ for the
+  restriction of $\bf$ to $\bH^x$, as a cover of
+  $\bG^x$. For each $x,y\in X$, let
+  $\bm_{x,y} : \bH^x \times \bH^{y} \to \bH^{x+y}$
+  be the map obtained from $\bm$ by restriction. Define
+  $\bm_{x} : A\to \Aut(\bf^x)$ by
+  $\bm_{x}(a): g \mapsto \bm_{0,x}(a,g)$; then
+  $\bm_{x} : A\to \Aut(\bf^x)$ is an isomorphism.
+  \Clifton{I need to show that $\bm_{x} : A\to \Aut(\bf^x)$ is an isomorphism.}
 
   For each $x\in X$ let $\gcs{L}^x$ be the rank-$1$ local system on
-  ${\bar G}^x$ determined by the finite etale cover
-  ${\bar f}^x : {\bar H}^x \to {\bar G}^x$ and the character
-  $\psi_x \ceq \psi \circ {\bar m}_x^{-1}$.  Since
-  ${\bar G} = \coprod_{x\in X} {\bar G}^x$ (disjoint union), this
-  determines a constructible sheaf $\gcs{L}$ on ${\bar G}$, locally
-  constant of rank-$1$ on each connected component of ${\bar G}$.
+  $\bG^x$ determined by the finite etale cover
+  $\bf^x : \bH^x \to \bG^x$ and the character
+  $\psi_x \ceq \psi \circ \bm_x^{-1}$.  Since
+  $\bG = \coprod_{x\in X} \bG^x$ (disjoint union), this
+  determines a constructible sheaf $\gcs{L}$ on $\bG$, locally
+  constant of rank-$1$ on each connected component of $\bG$.
   Taking the case $x=0$ we observe that $\gcs{L}^0 =\gcs{E}$,
@@
   equip $\gcs{L}$ with isomorphisms
-  $\mu : {\bar m}^* \gcs{L} \to \gcs{L} \boxtimes\gcs{L}$ and
+  $\mu : \bm^* \gcs{L} \to \LxL$ and
   $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ satisfying conditions \ref{CS.1}
@@
 
-  Observe that ${\bar m}: {\bar G}\times {\bar G}\to {\bar G}$ is
+  Observe that $\bm: \bG\times \bG\to \bG$ is
   completely determined by the family of maps
-  ${\bar m}_{x,y} : {\bar G}^x \times {\bar G}^{y} \to {\bar G}^{x+y}$.
+  $\bm_{x,y} : \bG^x \times \bG^{y} \to \bG^{x+y}$.
   Accordingly, to define $\mu$ for $\gcs{L}$ it is sufficient to define isomorphisms
-  $\mu_{x,y} : {\bar m}_{x,y}^*\gcs{L}^{x+y} \iso \gcs{L}^{x}\boxtimes \gcs{L}^{y}$
+  $\mu_{x,y} : \bm_{x,y}^*\gcs{L}^{x+y} \iso \gcs{L}^{x}\boxtimes \gcs{L}^{y}$
   for all $x,y\in X$. To do that, note first that the local system
@@
   \xymatrix{
-    \EE^\times && \ar[ll]_{\hskip-20pt \psi_x\otimes \psi_y} \Aut({\bar f}^x)\times \Aut({\bar f}^y)
-    & \ar@(ul,dl) & {\bar H}^x\times {\bar H}^y \ar[rr]^{{\bar f}^x\times {\bar f}^y} && {\bar G}^x\times {\bar G}^y\\
-    }
-  \]
-  On the other hand, the diagram for the local system ${\bar m}_{x,y}^* \gcs{L}^{x+y}$
+    \EE^\times && \ar[ll]_{\hskip-20pt \psi_x\otimes \psi_y} \Aut(\bf^x)\times \Aut(\bf^y)
+    & \ar@(ul,dl) & \bH^x\times \bH^y \ar[rr]^{\bf^x\times \bf^y} && \bG^x\times \bG^y\\
+    }
+  \]
+  On the other hand, the diagram for the local system $\bm_{x,y}^* \gcs{L}^{x+y}$
   is found by pulling-back the diagram for $\gcs{L}^{x+y}$ along
-  ${\bar m}_{x,y} : {\bar H}^x\times{\bar H}^y \to {\bar H}^{x+y}$;
+  $\bm_{x,y} : \bH^x\times\bH^y \to \bH^{x+y}$;
   the result is the middle horizontal diagram below, where we use the
-  fact that the covering group of the middle arrow is $\Aut({\bar f}^{x+y})$, canonically.
-  \[
-  \xymatrix{
-    & \ar[dl]_{\psi_{x+y}} \Aut({\bar f}^{x+y})
-    & \ar@(ul,dl) & {\bar H}^{x+y} \ar[rr]^{{\bar f}^{x+y}} && {\bar G}^{x+y}\\
-    \EE^\times & \ar@{.>}[l] \Aut({\bar f}^{x+y})  \ar@{=}[u] &  \ar@{.>}@(ul,dl)
-    & \ar[u] {\bar H}^{x+y} \times_{{\bar G}^x\times{\bar G}^y} {\bar G}^x\times{\bar G}^y \ar[rr]
-    && \ar[u]_{{\bar m}_{x,y}} {\bar G}^x\times {\bar G}^y\\
-    & \ar[lu]_{\psi_x\otimes \psi_y} \ar@{.>}[u] \Aut({\bar f}^x)\times \Aut({\bar f}^y)
-    & \ar@(ul,dl) & \ar[u] {\bar H}^x\times {\bar H}^y \ar[rr]^{{\bar f}^x\times {\bar f}^y}
-    && \ar@{=}[u] {\bar G}^x\times {\bar G}^y\\
+  fact that the covering group of the middle arrow is $\Aut(\bf^{x+y})$, canonically.
+  \[
+  \xymatrix{
+    & \ar[dl]_{\psi_{x+y}} \Aut(\bf^{x+y})
+    & \ar@(ul,dl) & \bH^{x+y} \ar[rr]^{\bf^{x+y}} && \bG^{x+y}\\
+    \EE^\times & \ar@{.>}[l] \Aut(\bf^{x+y})  \ar@{=}[u] &  \ar@{.>}@(ul,dl)
+    & \ar[u] \bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y \ar[rr]
+    && \ar[u]_{\bm_{x,y}} \bG^x\times \bG^y\\
+    & \ar[lu]_{\psi_x\otimes \psi_y} \ar@{.>}[u] \Aut(\bf^x)\times \Aut(\bf^y)
+    & \ar@(ul,dl) & \ar[u] \bH^x\times \bH^y \ar[rr]^{\bf^x\times \bf^y}
+    && \ar@{=}[u] \bG^x\times \bG^y\\
     }
@@
   Now, the homomorphism from the covering group of
-  ${\bar f}^x\times{\bar f}^y$ to the covering group of
-  ${\bar f}^{x+y}$ induced by the composition
-  $ {\bar H}^x\times {\bar H}^y \to {\bar H}^{x+y} \times_{{\bar G}^x\times{\bar G}^y} {\bar G}^x\times{\bar G}^y \to {\bar H}^{x+y}$
-  is precisely $({\bar m}_x(a),{\bar m}_y(b)) \mapsto {\bar m}_{x+y}(ab)$.
+  $\bf^x\times\bf^y$ to the covering group of
+  $\bf^{x+y}$ induced by the composition
+  $ \bH^x\times \bH^y \to \bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y \to \bH^{x+y}$
+  is precisely $(\bm_x(a),\bm_y(b)) \mapsto \bm_{x+y}(ab)$.
   Since this map commutes with the characters $\psi_x\otimes\psi_y$
@@
   it follows that, for each $x,y\in X$ the diagram above defines a canonical isomorphism
-  $\mu_{x,y} : {\bar m}_{x,y}^* \gcs{L}^{x+y} \to \gcs{L}^x \boxtimes\gcs{L}^y$.
-  This defines $\mu: {\bar m}^* \gcs{L} \iso \gcs{L} \boxtimes\gcs{L}$.
+  $\mu_{x,y} : \bm_{x,y}^* \gcs{L}^{x+y} \to \gcs{L}^x \boxtimes\gcs{L}^y$.
+  This defines $\mu: \bm^* \gcs{L} \iso \LxL$.
   It is straightforward (but laborious) to show that the pair
@@
   As above, we define this isomorphism through a family of
-  isomorphisms on the connected components of ${\bar G}$. The
-  restriction of $\Frob_{G}$ to ${\bar G}^x$ defines an isomorphism
-  $\Frob_x : {\bar G}^x \to {\bar G}^{\Frob(x)}$.
+  isomorphisms on the connected components of $\bG$. The
+  restriction of $\Frob_{G}$ to $\bG^x$ defines an isomorphism
+  $\Frob_x : \bG^x \to \bG^{\Frob(x)}$.
   %\[
   %\xymatrix{
-  %\ar[d]_{\Frob_x} {\bar G}^x \ar[r] & \ar[d]_{\Frob_{G}} {\bar G}\\
-  %{\bar G}^{\Frob(x)} \ar[r] & {\bar G}\\
+  %\ar[d]_{\Frob_x} \bG^x \ar[r] & \ar[d]_{\Frob_{G}} \bG\\
+  %\bG^{\Frob(x)} \ar[r] & \bG\\
   %}
@@
   \xymatrix{
-    && \ar[dll]_{\psi_{\Frob(x)}} \Aut({\bar f}^{\Frob(x)}) & \ar@(ul,dl)
-    & {\bar H}^{\Frob(x)} \ar[rr]^{{\bar f}^{\Frob(x)}} && {\bar G}^{\Frob(x)}\\
-    \EE^\times & & \ar@{.>}[ll] \Aut({\bar f}^{\Frob(x)})  \ar@{=}[u] & \ar@{.>}@(ul,dl)
-    & \ar[u] {\bar H}^{\Frob(x)} \times_{{\bar G}^{\Frob(x)}} {\bar G}^x \ar[rr] && \ar[u]_{\Frob_{x}} {\bar G}^x\\
-    & &  \ar[ull]^{\psi_x}  \ar@{.>}[u] \Aut({\bar f}^{x}) & \ar@(ul,dl)
-    & \ar[u] {\bar H}^x \ar[rr] && \ar@{=} [u] {\bar G}^x\\
-    }
-  \]
-  The covering group of ${\bar H}^{\Frob(x)} \times_{{\bar G}^{\Frob(x)}} {\bar G}^x$
-  is isomorphic to $\Aut({\bar f}^{\Frob(x)})$, canonically, so
+    && \ar[dll]_{\psi_{\Frob(x)}} \Aut(\bf^{\Frob(x)}) & \ar@(ul,dl)
+    & \bH^{\Frob(x)} \ar[rr]^{\bf^{\Frob(x)}} && \bG^{\Frob(x)}\\
+    \EE^\times & & \ar@{.>}[ll] \Aut(\bf^{\Frob(x)})  \ar@{=}[u] & \ar@{.>}@(ul,dl)
+    & \ar[u] \bH^{\Frob(x)} \times_{\bG^{\Frob(x)}} \bG^x \ar[rr] && \ar[u]_{\Frob_{x}} \bG^x\\
+    & &  \ar[ull]^{\psi_x}  \ar@{.>}[u] \Aut(\bf^{x}) & \ar@(ul,dl)
+    & \ar[u] \bH^x \ar[rr] && \ar@{=} [u] \bG^x\\
+    }
+  \]
+  The covering group of $\bH^{\Frob(x)} \times_{\bG^{\Frob(x)}} \bG^x$
+  is isomorphic to $\Aut(\bf^{\Frob(x)})$, canonically, so
   $\Frob_x^* \gcs{L}^{\Frob(x)}$ is defined by the middle (horizontal)
@@
   $F_x : \Frob_x^* \gcs{L}^{\Frob(x)} \to \gcs{L}^x$ by the canonical morphism
-  ${\bar H}^x \to {\bar H}^{\Frob(x)} \times_{{\bar G}^{\Frob(x)}} {\bar G}^x \to $;
+  $\bH^x \to \bH^{\Frob(x)} \times_{\bG^{\Frob(x)}} \bG^x \to $;
   to see that this defines a sheaf homomorphism it is sufficient to
   check that the character $\psi_x$ commutes with the family of isomorphisms
-  $F_x : (\Frob_{G}^* \gcs{L})\vert_{{\bar G}^x} \iso \Frob_x^* \gcs{L}^{\Frob{x}} \to \gcs{L}^x$
+  $F_x : (\Frob_{G}^* \gcs{L})\vert_{\bG^x} \iso \Frob_x^* \gcs{L}^{\Frob{x}} \to \gcs{L}^x$
   now defines the isomorphism $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$.

### 2013-06-25 shanghai.tex
\EEx

@@
 
+\newcommand{\EEx}{\EE^\times}
+
 \DeclareMathOperator{\Gal}{Gal}
@@
 component of $\bG$, equipped with an isomorphism $\mu: m^*
-\gcs{L} \to \LxL$, where $m : G\times G \to G$ is
+\gcs{L} \to \LxL$, where $m : \GxG \to G$ is
 the group operation for $G$, and an isomorphism $F : \Frob_{G}^*
@@
 \iso
-\Hom_{< d}(T(K),\EE^\times)
+\Hom_{< d}(T(K),\EEx)
 \] 
 between the Picard group of the category of character sheaves on
-$\textswab{T}_d$ and the group of characters $T(K) \to \EE^\times$ of
+$\textswab{T}_d$ and the group of characters $T(K) \to \EEx$ of
 depth at most $d$.  Since these isomorphisms are compatible with
@@
 therefore an automorphism $F_{\bg}$ of $\gcs{L}_{\bg}$. Note
-that $\Aut_{\EE}(\gcs{L}_{\bg}) \iso \EE^\times$, canonically (this
+that $\Aut_{\EE}(\gcs{L}_{\bg}) \iso \EEx$, canonically (this
 follows from second condition appearing in the definition of character
 sheaves). The isomorphism $\mu : \bm^* \gcs{L} \to \gcs{L}\boxtimes\gcs{L}$
-guarantees that the function $t^\Frob_\cs{L} : G(\Fq)\to \EE^\times$,
+guarantees that the function $t^\Frob_\cs{L} : G(\Fq)\to \EEx$,
 defined by $g \mapsto F_{\bg}$, is a group homomorphism;
@@
 \[
-\cdef{t_{G}} : \CSiso{G} \longrightarrow \Hom_\text{grp}(G(\Fq),\EE^\times),
+\cdef{t_{G}} : \CSiso{G} \longrightarrow \Hom_\text{grp}(G(\Fq),\EEx),
 \qquad \text{defined by}\qquad \cs{L} \mapsto t^\Frob_\cs{L},
@@
   \CSiso{G} \ar[r]^{f^*} \ar[d]^{t_{G}} &  \ar[d]^{t_{H}} \CSiso{H}\\
-  \Hom_\text{grp}(G(\Fq),\EE^\times) \ar[r] & \Hom_\text{grp}(H(\Fq),\EE^\times)
+  \Hom_\text{grp}(G(\Fq),\EEx) \ar[r] & \Hom_\text{grp}(H(\Fq),\EEx)
   }
@@
   \[
-  t_{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EE^\times),
+  t_{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx),
   \]
@@
   \[
-  t_{(\gcs{L},F)}(g) : \Weil(\bFq/\Fq) \to \EE^\times \qquad \text{defined by}\qquad \Frob \mapsto t^\Frob_{(\gcs{L},F)}(g)
+  t_{(\gcs{L},F)}(g) : \Weil(\bFq/\Fq) \to \EEx \qquad \text{defined by}\qquad \Frob \mapsto t^\Frob_{(\gcs{L},F)}(g)
   \]
@@
 
-  On the other hand, we have already seen that $t^\Frob_\cs{L} : G(\Fq) \to \EE^\times$
+  On the other hand, we have already seen that $t^\Frob_\cs{L} : G(\Fq) \to \EEx$
   is a group homomorphism. Since $G$ is an algebraic group over $\Fq$, it is a
@@
   for every $g\in G(\Fq)$.  Since $\Weil(\bFq/\Fq)$ is generated by
-  $\Frob$ and $t_{(\gcs{L},F)}(g) : \Weil(\bFq/\Fq) \to \EE^\times$ is
+  $\Frob$ and $t_{(\gcs{L},F)}(g) : \Weil(\bFq/\Fq) \to \EEx$ is
   a character, it follows that the image of $t_{(\gcs{L},F)}(g)$ is a
@@
 
-  We may now lift the $\ell$-adic character $t_{(\gcs{L},F)}(g) : \Gal(\bFq/\Fq) \to \EE^\times$
+  We may now lift the $\ell$-adic character $t_{(\gcs{L},F)}(g) : \Gal(\bFq/\Fq) \to \EEx$
   to an $\ell$-adic character of $\pi_1(G,\bg)$ using the canonical topological group map
@@
   \[
-  t_{G} : \CSbiso{G} \to \Hom_\text{grp}(G(\Fq),\EE^\times)
+  t_{G} : \CSbiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)
   \]
@@
   \[
-  \CSiso{G} \longrightarrow \Hh^1(\Weil(\bFq/\Fq), \Hom_\text{grp}(G(\bFq),\EE^\times)),
+  \CSiso{G} \longrightarrow \Hh^1(\Weil(\bFq/\Fq), \Hom_\text{grp}(G(\bFq),\EEx)),
   \qquad \text{given by}\qquad
@@
   \]
-  where $t_\cs{L}: \Weil(\bFq/\Fq)\to \Hom_\text{grp}(G(\bFq),\EE^\times)$ is a cocycle such that
+  where $t_\cs{L}: \Weil(\bFq/\Fq)\to \Hom_\text{grp}(G(\bFq),\EEx)$ is a cocycle such that
   \[
@@
   To simplify notation, we set $W_\Fq \ceq \Weil(\bFq/\Fq)$ and
-  $G(\bFq)^* \ceq \Hom_\text{grp}(G(\bFq),\EE^\times)$.  Recall the
+  $G(\bFq)^* \ceq \Hom_\text{grp}(G(\bFq),\EEx)$.  Recall the
   equivalence between etale group schemes over $\Fq$ and the category
@@
   $t$ and $t'$ are defined by sections $s$ and $s'$. Now, $\varphi_x(s(x))$ is a
-  non-zero scalar multiple of $s'(x)$; define $\phi: G(\bFq) \to \EE^\times$
+  non-zero scalar multiple of $s'(x)$; define $\phi: G(\bFq) \to \EEx$
   by $\varphi_x(s(x)) = \phi(x) s'(x)$. By the second part of condition~\ref{cs.3},
@@
 %\input{etale-2}
-%Define $\rho \colon \Hh^1(W_{\Fq}, \Hom(G(\bFq), \EE^\times))
-% \rightarrow \Hom(G(\Fq), \EE^\times)$ by $\rho(\phi)(g) =
+%Define $\rho \colon \Hh^1(W_{\Fq}, \Hom(G(\bFq), \EEx))
+% \rightarrow \Hom(G(\Fq), \EEx)$ by $\rho(\phi)(g) =
 % \phi(\Frob)(g)$.
@@
   \begin{align*}
-    \Hh^1(\Fq, \Hom(X, \EE^\times)) &\xrightarrow{\rho} \Hom(\Hh^0(\Fq, X), \EE^\times) \\
+    \Hh^1(\Fq, \Hom(X, \EEx)) &\xrightarrow{\rho} \Hom(\Hh^0(\Fq, X), \EEx) \\
     \rho([z])(x) &= z(\Frob)(x)
@@
   We first prove that $\rho$ is surjective.  Suppose that
-  $f \in \Hom(X^\Frob, \EE^\times).$ Since $\EE^\times$ is divisible
+  $f \in \Hom(X^\Frob, \EEx).$ Since $\EEx$ is divisible
   as an abelian group it is injective as a $\ZZ$-module and thus
-  $\Ext^1_{\ZZ}(X/X^\Frob, \EE^\times) = 0$.  Applying the functor
-  $\Hom(\mbox{---}, \EE^\times)$ to
+  $\Ext^1_{\ZZ}(X/X^\Frob, \EEx) = 0$.  Applying the functor
+  $\Hom(\mbox{---}, \EEx)$ to
   $$0 \rightarrow X^\Frob \rightarrow X \rightarrow X/X^\Frob \rightarrow 0$$
   and considering the associated long exact sequence gives the
-  existence of an $\tilde{f} \in \Hom(X, \EE^\times)$ restricting to
-  $f$.  Define a $1$-cocycle $z \in \Hh^1(\Fq, \Hom(X,\EE^\times))$ by
+  existence of an $\tilde{f} \in \Hom(X, \EEx)$ restricting to
+  $f$.  Define a $1$-cocycle $z \in \Hh^1(\Fq, \Hom(X,\EEx))$ by
   mapping $\Frob$ to $\tilde{f}$.  Then $\rho([z]) = f$.
 
-  Now suppose that $[z] \in \Hh^1(\Fq,\Hom(X,\EE^\times))$ with
+  Now suppose that $[z] \in \Hh^1(\Fq,\Hom(X,\EEx))$ with
   $\rho([z]) = 1$; write $\tilde{f}$ for $z(\Frob)$.  The injectivity
   of $\rho$ is equivalent to the existence of a homomorphism $\psi
-  \colon X \rightarrow \EE^\times$ with
+  \colon X \rightarrow \EEx$ with
   $$\tilde{f}(x) = \frac{\psi(\Frob(x))}{\psi(x)}$$
@@
   prime ideal $P \subset \ZZ[\zeta_d]$ and positive integer $s$, a
-  $\psi \colon \ZZ[\zeta_d]/P^s \rightarrow \EE^\times$ with
+  $\psi \colon \ZZ[\zeta_d]/P^s \rightarrow \EEx$ with
   \begin{equation} \label{eq:psi-condition}
@@
   \end{equation}
-  for an $\alpha \in \EE^\times$ to be chosen later.  Since there are
+  for an $\alpha \in \EEx$ to be chosen later.  Since there are
   relations among the $\zeta^i$ we first need to check that $\psi$ is
@@
   killed under multiplication by $p^s$.  Since $\tilde{f}$ is also a
-  homomorphism $\ZZ[\zeta]/P^s \rightarrow \EE^\times$ the values of
+  homomorphism $\ZZ[\zeta]/P^s \rightarrow \EEx$ the values of
   $\tilde{f}$ and thus of $\psi$ will be $p^s$-roots of unity.
@@
   where $\pi : B\to G^0$ is a finite etale morphism of algebraic
-  groups and a character $\psi : A\to \EE^\times$, where
+  groups and a character $\psi : A\to \EEx$, where
   $\Gal(\bFq/\Fq)$ acts trivially on $A \ceq \ker {\bar \pi}$, as
@@
     \xymatrix{
-      \EE^\times & 1\ar[r] & \ar@/_1pc/[ll]_{\psi} A  \ar[r] & B \ar[r]^{\pi} & G^0 \ar[r] & 1\\
+      \EEx & 1\ar[r] & \ar@/_1pc/[ll]_{\psi} A  \ar[r] & B \ar[r]^{\pi} & G^0 \ar[r] & 1\\
       }
@@
     \xymatrix{
-      \EE^\times & 1\ar[r] & \ar@/_1pc/[ll]_{\psi} A  \ar[r] & B \ar[r]^{\pi} & G^0 \ar[r] & 1\\
+      \EEx & 1\ar[r] & \ar@/_1pc/[ll]_{\psi} A  \ar[r] & B \ar[r]^{\pi} & G^0 \ar[r] & 1\\
       & 1\ar[r] & \ar@{.>}@/^1pc/[llu] \ar[u] A\times A  \ar[r]
@@
   $m_{B}$. Use this Cartesian square to define a character (the dotted
-  arrow, above) of $A\times A$; that is, define $A\times A\to \EE^\times$
-  by the composition of $A\times A \to A$ and $\psi : A\to \EE^\times$.
-  Note that this character is $\psi \otimes \psi : A\times A\to \EE^\times$.
+  arrow, above) of $A\times A$; that is, define $A\times A\to \EEx$
+  by the composition of $A\times A \to A$ and $\psi : A\to \EEx$.
+  Note that this character is $\psi \otimes \psi : A\times A\to \EEx$.
   \Clifton{I haven't explained how maps between diagrams define sheaf
@@
   Now we show that $f : H\to G$, as above, together with a character
-  $\psi : \ker \bf \to \EE^\times$, defines a character sheaf on
+  $\psi : \ker \bf \to \EEx$, defines a character sheaf on
   $G$. We will also show that the restriction of this character sheaf
@@
   \xymatrix{
-    \EE^\times && \ar[ll]_{\hskip-20pt \psi_x\otimes \psi_y} \Aut(\bf^x)\times \Aut(\bf^y)
+    \EEx && \ar[ll]_{\hskip-20pt \psi_x\otimes \psi_y} \Aut(\bf^x)\times \Aut(\bf^y)
     & \ar@(ul,dl) & \bH^x\times \bH^y \ar[rr]^{\bf^x\times \bf^y} && \bG^x\times \bG^y\\
@@
     & \ar@(ul,dl) & \bH^{x+y} \ar[rr]^{\bf^{x+y}} && \bG^{x+y}\\
-    \EE^\times & \ar@{.>}[l] \Aut(\bf^{x+y})  \ar@{=}[u] &  \ar@{.>}@(ul,dl)
+    \EEx & \ar@{.>}[l] \Aut(\bf^{x+y})  \ar@{=}[u] &  \ar@{.>}@(ul,dl)
     & \ar[u] \bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y \ar[rr]
@@
     & \bH^{\Frob(x)} \ar[rr]^{\bf^{\Frob(x)}} && \bG^{\Frob(x)}\\
-    \EE^\times & & \ar@{.>}[ll] \Aut(\bf^{\Frob(x)})  \ar@{=}[u] & \ar@{.>}@(ul,dl)
+    \EEx & & \ar@{.>}[ll] \Aut(\bf^{\Frob(x)})  \ar@{=}[u] & \ar@{.>}@(ul,dl)
     & \ar[u] \bH^{\Frob(x)} \times_{\bG^{\Frob(x)}} \bG^x \ar[rr] && \ar[u]_{\Frob_{x}} \bG^x\\
@@
   \[
-  t_{G} : \CSiso{G} \to \Hom(G(\Fq),\EE^\times),
+  t_{G} : \CSiso{G} \to \Hom(G(\Fq),\EEx),
   \]
@@
     & \ar[d]^{t_{G}} \CSiso{G} \ar[r] & \ar[d]^{t_{G^0}} \CSiso{G^0} \ar[r] & 0\\
-    0 \ar[r] & \ar[d] \Hom(\pi_0(G)(\Fq),\EE^\times) \ar[r]
-    & \ar@{.>}[d] \Hom(G(\Fq),\EE^\times) \ar[r] & \ar[d] \Hom(G^0(\Fq),\EE^\times) \ar[r] & 0\\
+    0 \ar[r] & \ar[d] \Hom(\pi_0(G)(\Fq),\EEx) \ar[r]
+    & \ar@{.>}[d] \Hom(G(\Fq),\EEx) \ar[r] & \ar[d] \Hom(G^0(\Fq),\EEx) \ar[r] & 0\\
     & \coker t_{\pi_0(G)} & \coker t_{G} &  \coker t_{G^0} & \\
@@
   \end{equation}
-  since $\Hom(\ - \ ,\EE^\times)$ is left-exact, the sequence of
+  since $\Hom(\ - \ ,\EEx)$ is left-exact, the sequence of
   character groups is left exact.
@@
   commutes (by Proposition~\ref{prop:pullback}), the bottom sequence
-  is exact at $\Hom(G(\Fq),\EE^\times)$ and $\coker t_{\pi_0(G)} =0$
+  is exact at $\Hom(G(\Fq),\EEx)$ and $\coker t_{\pi_0(G)} =0$
   (by Propositions~\ref{prop:etale} and \ref{prop:X}) and
@@
   by Proposition~\ref{prop:pullback} again. Since the sequence of
-  character groups is exact at $\Hom(G(\Fq),\EE^\times)$, there is
-  some $\chi \in \Hom(\pi_0(G)(\Fq),\EE^\times)$ such that the
+  character groups is exact at $\Hom(G(\Fq),\EEx)$, there is
+  some $\chi \in \Hom(\pi_0(G)(\Fq),\EEx)$ such that the
   pull-back of $\chi$ along $G(\Fq)\to \pi_0(G)(\Fq)$ is
@@
   \[
-  \CSiso{\GN{T}_d} \iso \Hom_{< d}(T(K),\EE^\times).
+  \CSiso{\GN{T}_d} \iso \Hom_{< d}(T(K),\EEx).
   \]
@@
   \[
-  \CSiso{\GN{T}_d} \iso \Hom(\GN{T}_d(\Fq),\EE^\times).
+  \CSiso{\GN{T}_d} \iso \Hom(\GN{T}_d(\Fq),\EEx).
   \]
@@
   \[
-  \CSiso{\GN{T}} \iso \Hom_\text{ad}(T(K),\EE^\times)
+  \CSiso{\GN{T}} \iso \Hom_\text{ad}(T(K),\EEx)
   \]

### 2013-06-27 shanghai.tex
Superficial changes, mostly notes to myself

@@
   \David{Should we move this definition since it will be important elsewhere?}
+  \Clifton{Agreed. I'll do that.}
   Let $b : \bG \to G$ be base change
@@
   corresponds to a global section of the line bundle $(\gcs{L},\mu)$.
+
+\Clifton{I'm going to remove all mention of line bundles from this paper.}
 
@@
   character sheaf on $G$. However, it is not true that every character
-  sheaf on $G$, in the sense of Section~\ref{sec:category} arises not
-  all character sheaves on $G$ arise in this manner.
+  sheaf on $G$ arises in this manner.
 \end{remark}
+\Clifton{I can flesh out this remark once I've promoted the definition of $\CS_0(G)$ (category of bounded character sheaves on $G$).}
 %\input{centralextensions}
@@
 \begin{theorem}\label{thm:application}
-  Let $T$ be an algebraic torus over a non-Archimdean local field $K$.
+  Let $T$ be an algebraic torus over a non-Archimedean local field $K$.
   Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d \in \ZZ_{>0}$, the
@@
 
-\Clifton{Explain what happens as $d\in \NN$ varies.}
+\Clifton{Explain what happens as $d$ varies.}
 Suppose $d\leq d'$.
@@
   care about \ref{scheme}.}
+
+\Clifton{Must still define $\CS(\GN{T})$, since it is not an instance
+ of our definitions, above.}
+
 \begin{proposition}

### 2013-06-27 shanghai.tex
Poor Tate, the quote from his thesis is now gone.

@@
 %\input{introduction}
-In his celebrated thesis, John Tate writes 
-\begin{quotation}
-    {\it Concerning the characters of $k^*$ [the
-    multiplicative group of a $\mathfrak{p}$-adic field], the
-    situation is different from that of $k^+$.  First of all, we are
-    interested in continuous multiplicative maps $\alpha \mapsto
-    c(\alpha)$ of $k^*$ into the complex numbers, not only in the
-    bounded ones, and shall call such a map a quasi-character,
-    reserving the word ``character'' for the conventional character of
-    absolute value $1$. Secondly, we shall find no model for the group
-    of quasi-characters, or even for the group of characters, though
-    such a model would be of the utmost importance.}
-  \cite{Tate:thesis}*{\S 2.3}
-\end{quotation}
-\noindent
+%In his celebrated thesis, John Tate writes 
+%\begin{quotation}
+%    {\it Concerning the characters of $k^*$ [the
+%    multiplicative group of a $\mathfrak{p}$-adic field], the
+%    situation is different from that of $k^+$.  First of all, we are
+%    interested in continuous multiplicative maps $\alpha \mapsto
+%    c(\alpha)$ of $k^*$ into the complex numbers, not only in the
+%    bounded ones, and shall call such a map a quasi-character,
+%    reserving the word ``character'' for the conventional character of
+%    absolute value $1$. Secondly, we shall find no model for the group
+%    of quasi-characters, or even for the group of characters, though
+%    such a model would be of the utmost importance.}
+%  \cite{Tate:thesis}*{\S 2.3}
+%\end{quotation}
+%\noindent
 In this paper we show that the monidal category of character sheaves

### 2013-07-06 shanghai.tex
I added a section called Functorial Properties of the Main Isomorphism.
Added a section based on our conversation at the Hua Ting Hotel, So
far, it just has place holders for the results we talked about, without
proofs. The first result I think I can prove without too much
difficulty. The rest is still under construction.

@@
 \DeclareMathOperator{\Hh}{H}
+\DeclareMathOperator{\Res}{Res}
 
@@
 
+\section{Functorial properties of the main isomorphism}
+
+We have already seen that the trace of Frobenius defines a canonical isomorphism 
+$t_T : \CSiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
+In this section we expand on the canonicity of this group isomorphism 
+by showing that it is a natural transformation. We also show
+
+\begin{proposition}
+The isomorphism $t_T : \CSiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$ 
+is a natural transformation between the following two contravariant functors 
+from the category of algebraic tori over $K$ to the category of abelian groups: 
+\begin{enumerate}
+\item $T \mapsto \CSiso{\GN{T}}$
+\item $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
+\end{enumerate}
+\end{proposition}
+
+\Clifton{I think I can prove this proposition without too much difficulty.}
+\begin{proof}
+\end{proof}
+
+\begin{proposition}
+Let $K'/K$ be a finite Galois extension and let $T'$ be an algebraic torus over $K'$... 
+\Clifton{This next part is very much under construction.}
+The functor $\CS(\GN{T}) \to \CS(\GN{T}')$ defined above induces a group homomorphism 
+that commutes, through trace of Frobenius, with ...
+\[
+\xymatrix{
+\CS(\GN{T}) \ar[d] & \CSiso{\GN{T}} \ar[r]^{t_T} \ar[d] & \Hom_\text{ad}(T(K),\EEx) \ar[d] \\
+\CS(\GN{T}') & \CSiso{\GN{T}'} \ar[r]^{t_{T'}} & \Hom_\text{ad}(T'(K),\EEx)\\
+}
+\]
+\end{proposition}
+
+\begin{proof}
+\end{proof}
+
 \begin{bibdiv}

### 2013-07-06 shanghai.tex
added newcommand mathswab
mathswab puts textswab into mathmode

@@
 \usepackage{yfonts}
+\newcommand{\mathswab}[1]{\operatorname{\textswab{#1}}}
 \usepackage[T1]{fontenc}
@@
 \newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
-\newcommand{\GN}[1]{\textswab{#1}}
-\newcommand{\bGN}[1]{{\bar{\textswab{#1}}}}
+\newcommand{\GN}[1]{\mathswab{#1}}
+\newcommand{\bGN}[1]{{\bar{\mathswab{#1}}}}
 \newcommand{\TT}{\underline{T}}
@@
 \[
-\CSiso{\textswab{T}_d} 
+\CSiso{\mathswab{T}_d} 
 \iso
@@
 between the Picard group of the category of character sheaves on
-$\textswab{T}_d$ and the group of characters $T(K) \to \EEx$ of
+$\mathswab{T}_d$ and the group of characters $T(K) \to \EEx$ of
 depth at most $d$.  Since these isomorphisms are compatible with

### 2013-07-08 shanghai.tex
Make a title and made a new section for bounded character sheaves
Change the title if you like  . . .

@@
 \documentclass[11pt]{amsart}
-\title[Short groovy title goes here]{Long groovy title goes here}
+\title[Geometration of characters of tori]{Geometrization of characters of tori over non-Archimedean local fields}
 \usepackage[british]{babel}
@@
   this when we're closer to being finished. I'd be just as happy if
-  you took this cup from my lips, though.}  In particular, by
-specializing to the case $T= \Gm{K}$ and by
-choosing an isomorphism $\EE \approx \CC$ (unnatural though it may
-be), we arrive at a model for the group of quasi-characters of
-$K^\times$: the monoidal category of character sheaves on the
-Greenberg transform of the Neron model of
-$\Gm{K}$.
+  you took this cup from my lips, though.}  
+%In particular, by
+%specializing to the case $T= \Gm{K}$ and by
+%choosing an isomorphism $\EE \approx \CC$ (unnatural though it may
+%be), we arrive at a model for the group of quasi-characters of
+%$K^\times$: the monoidal category of character sheaves on the
+%Greenberg transform of the Neron model of
+%$\Gm{K}$.
 
@@
 \end{proof}
+
+Consider the short exact sequence in the category of smooth group
+schemes, locally of finite type over $\Fq$, defining the component
+group scheme for $G$:
+ \begin{equation}\label{eq:pi-1}
+   \xymatrix{
+     0 \ar[r] & G^0 \ar[r] & G \ar[r] & \pi_0(G) \ar[r] & 0.
+    }
+ \end{equation}
+Since $\pi_0(G)$ is an étale group scheme locally of finite type over $\Fq$, 
+it follows from Proposition~\ref{prop:pullback} that \eqref{eq:pi-1}defines a sequence of functors
+ \[
+  \xymatrix{
+\CS(0) \ar[r] & \CS(\pi_0(G)) \ar[r] & \CS(G) \ar[r] & \CS(G^0) \ar[r] & \CS(0).
+  }
+ \]
+We will see that
+
+\section{Bounded character sheaves}
+
+[Introduce category $\CS_0(G)$]
 
@@
   abelian groups
-  \begin{equation}\label{eq:pi0}
+  \begin{equation}\label{eq:pi1}
     \xymatrix{

### 2013-07-10 shanghai.tex
Working on converting xy to tikz

--- 2013-07-06 shanghai.tex
@@
 \usepackage{tikz}
-\usetikzlibrary{shapes,arrows}
+\usetikzlibrary{shapes,arrows,calc}
 \usepackage{manfnt}
@@
 \DeclareMathOperator{\Hh}{H}
-\DeclareMathOperator{\Res}{Res}
 
@@
 %\input{introduction}
-%In his celebrated thesis, John Tate writes 
-%\begin{quotation}
-%    {\it Concerning the characters of $k^*$ [the
-%    multiplicative group of a $\mathfrak{p}$-adic field], the
-%    situation is different from that of $k^+$.  First of all, we are
-%    interested in continuous multiplicative maps $\alpha \mapsto
-%    c(\alpha)$ of $k^*$ into the complex numbers, not only in the
-%    bounded ones, and shall call such a map a quasi-character,
-%    reserving the word ``character'' for the conventional character of
-%    absolute value $1$. Secondly, we shall find no model for the group
-%    of quasi-characters, or even for the group of characters, though
-%    such a model would be of the utmost importance.}
-%  \cite{Tate:thesis}*{\S 2.3}
-%\end{quotation}
-%\noindent
+In his celebrated thesis, John Tate writes 
+\begin{quotation}
+    {\it Concerning the characters of $k^*$ [the
+    multiplicative group of a $\mathfrak{p}$-adic field], the
+    situation is different from that of $k^+$.  First of all, we are
+    interested in continuous multiplicative maps $\alpha \mapsto
+    c(\alpha)$ of $k^*$ into the complex numbers, not only in the
+    bounded ones, and shall call such a map a quasi-character,
+    reserving the word ``character'' for the conventional character of
+    absolute value $1$. Secondly, we shall find no model for the group
+    of quasi-characters, or even for the group of characters, though
+    such a model would be of the utmost importance.}
+  \cite{Tate:thesis}*{\S 2.3}
+\end{quotation}
+\noindent
 In this paper we show that the monidal category of character sheaves
@@
   \David{Should we move this definition since it will be important elsewhere?}
-  \Clifton{Agreed. I'll do that.}
   Let $b : \bG \to G$ be base change
@@
   corresponds to a global section of the line bundle $(\gcs{L},\mu)$.
-
-\Clifton{I'm going to remove all mention of line bundles from this paper.}
 
@@
   fact that the covering group of the middle arrow is $\Aut(\bf^{x+y})$, canonically.
+
+  \vspace{0.2in}
+
+  \begin{tikzpicture}[style={rectangle, scale=1.2}]
+  \node (12) [anchor=east] at (4,2) {$\Aut(\bf^{x+y})$};
+  \node (22) [anchor=west] at (4.4,2) {$\bH^{x+y}$};
+  \node (32) [anchor=east] at (11,2) {$\bG^{x+y}$};
+  \node (01) at (0,1) {$\EEx$};
+  \node (11) [anchor=east] at (4,1) {$\Aut(\bf^{x+y})$};
+  \node (21) [anchor=west] at (4.4,1) {$\bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y$};
+  \node (31) [anchor=east] at (11,1) {$\bG^x\times \bG^y$};
+  \node (10) [anchor=east] at (4,0) {$\Aut(\bf^x)\times \Aut(\bf^y)$};
+  \node (20) [anchor=west] at (4.4,0) {$\bG^x\times \bG^y$};
+  \node (30) [anchor=east] at (11,0) {$\bG^x\times \bG^y$};
+  \draw [->] (4.3,1.94) arc (330:30:0.12);
+  \draw [->, densely dotted] (4.3,0.94) arc (330:30:0.12);
+  \draw [->] (4.3,-0.06) arc (330:30:0.12);
+  \draw [->] (12) -- (01);
+  \draw [->, densely dotted] (11) -- (01);
+  \draw [->] (10) -- (01);
+  \draw [->, densely dotted] ($(11.south) + (0,-0.5)$) -- (11);
+  \draw [double equal sign distance] (11) -- (12);
+  \draw [->] (22) -- (32);
+  \draw [->] ($(22.south) + (0,-0.5)$) -- (22);
+  \draw [->] (21) -- (31);
+  \draw [->] ($(32.south) + (0,-0.5)$) -- (32);
+  \draw [->] ($(22.south) + (0,-1.5)$) -- ($(22.south) + (0,-1)$);
+  \draw [->] (20) -- (30);
+  \draw [->] ($(32.south) + (0,-1.5)$) -- ($(32.south) + (0,-1)$);
+  \end{tikzpicture}
+
   \[
@@
   character sheaf on $G$. However, it is not true that every character
-  sheaf on $G$ arises in this manner.
+  sheaf on $G$, in the sense of Section~\ref{sec:category} arises not
+  all character sheaves on $G$ arise in this manner.
 \end{remark}
-\Clifton{I can flesh out this remark once I've promoted the definition of $\CS_0(G)$ (category of bounded character sheaves on $G$).}
 %\input{centralextensions}
@@
 \begin{theorem}\label{thm:application}
-  Let $T$ be an algebraic torus over a non-Archimedean local field $K$.
+  Let $T$ be an algebraic torus over a non-Archimdean local field $K$.
   Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d \in \ZZ_{>0}$, the
@@
 
-\Clifton{Explain what happens as $d$ varies.}
+\Clifton{Explain what happens as $d\in \NN$ varies.}
 Suppose $d\leq d'$.
@@
   care about \ref{scheme}.}
-
-\Clifton{Must still define $\CS(\GN{T})$, since it is not an instance
- of our definitions, above.}
-
 \begin{proposition}
@@
 \end{corollary}
-
-\section{Functorial properties of the main isomorphism}
-
-We have already seen that the trace of Frobenius defines a canonical isomorphism 
-$t_T : \CSiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
-In this section we expand on the canonicity of this group isomorphism 
-by showing that it is a natural transformation. We also show
-
-\begin{proposition}
-The isomorphism $t_T : \CSiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$ 
-is a natural transformation between the following two contravariant functors 
-from the category of algebraic tori over $K$ to the category of abelian groups: 
-\begin{enumerate}
-\item $T \mapsto \CSiso{\GN{T}}$
-\item $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
-\end{enumerate}
-\end{proposition}
-
-\Clifton{I think I can prove this proposition without too much difficulty.}
-\begin{proof}
-\end{proof}
-
-\begin{proposition}
-Let $K'/K$ be a finite Galois extension and let $T'$ be an algebraic torus over $K'$... 
-\Clifton{This next part is very much under construction.}
-The functor $\CS(\GN{T}) \to \CS(\GN{T}')$ defined above induces a group homomorphism 
-that commutes, through trace of Frobenius, with ...
-\[
-\xymatrix{
-\CS(\GN{T}) \ar[d] & \CSiso{\GN{T}} \ar[r]^{t_T} \ar[d] & \Hom_\text{ad}(T(K),\EEx) \ar[d] \\
-\CS(\GN{T}') & \CSiso{\GN{T}'} \ar[r]^{t_{T'}} & \Hom_\text{ad}(T'(K),\EEx)\\
-}
-\]
-\end{proposition}
-
-\begin{proof}
-\end{proof}
 

### 2013-07-12 shanghai.tex
Added \text to the \GxG style commands to prevent LaTeX from messing with spacing; changed implementation slightly

--- 2013-07-08 shanghai.tex
@@
       \newtheorem{remark}[theorem]{Remark}
+
+%% Global TikZ settings
+
+\tikzset{every picture/.style={>=stealth}}
 
@@
 
-\newcommand{\tighttimes}{\hskip-1pt\times\hskip-1pt}
-\newcommand{\tightertimes}{\hskip-3pt\times\hskip-3pt}
-\newcommand{\tighterboxtimes}{\hspace{-2pt}\boxtimes\hspace{-2pt}}
-
 \renewcommand{\bf}{\bar{f}}
@@
 \newcommand{\bH}{\bar{H}}
-\newcommand{\GxG}{G \tightertimes G}
-\newcommand{\bGxG}{\bar{G} \tightertimes \bar{G}}
-\newcommand{\bfxf}{\bar{f} \tightertimes \bar{f}}
-\newcommand{\GxxG}{G \tighttimes G}
-\newcommand{\LxL}{\gcs{L} \tighterboxtimes \gcs{L}}
+\newcommand{\tight}[3]{\hspace{-#1pt}{#2}\hspace{-#3pt}}
+\newcommand{\GxG}{\text{$G \tight{1}{\times}{1} G$}}
+\newcommand{\bGxG}{\text{$\bar{G} \tight{1}{\times}{1} \bar{G}$}}
+\newcommand{\bfxf}{\text{$\bar{f} \tight{1}{\times}{1} \bar{f}$}}
+\newcommand{\GxxG}{\text{$G \tight{1}{\times}{1} G$}}
+\newcommand{\LxL}{\text{$\gcs{L} \tight{0}{\boxtimes}{0} \gcs{L}$}}
+\newcommand{\ExE}{\text{$\cs{E}\tight{0}{\boxtimes}{0}\cs{E}$}}
+\newcommand{\bExE}{\text{$\gcs{E}\tight{0}{\boxtimes}{0}\gcs{E}$}}
+\newcommand{\AxA}{\text{$A \tight{1}{\times}{1} A$}}
+\newcommand{\BxB}{\text{$B \tight{1}{\times}{1} B$}}
+\newcommand{\GzxGz}{\text{$G^0 \tight{1}{\times}{1} G^0$}}
 
@@
   \xymatrix{
-    \bm_3^*\gcs{L} \ar[rr]^{(\bm\times \id)^*\mu} \ar[d]_{(\id\tightertimes \bm)^*\mu}
-    &&  \bm^*\LxL \ar[d]^{\mu \boxtimes \id} \\
-    \gcs{L} \boxtimes \bm^* \gcs{L} \ar[rr]
-    &&  \gcs{L} \boxtimes\LxL\\
-  }
-  \]
-  commutes, where $m_3 \ceq m\circ (m\tightertimes\id) = m\circ (\id\tighttimes m)$;
+    \bm_3^*\gcs{L} \ar[rr]^{(\bm \tight{1}{\times}{2} \id)^*\mu} \ar[d]_{(\id \tight{2}{\times}{1} \bm)^*\mu}
+    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \ar[d]^{\mu \boxtimes \id} \\
+    \gcs{L} \boxtimes \bm^* \gcs{L} \ar[rr]^{\id \boxtimes \mu}
+    &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL\\
+  }
+  \]
+  commutes, where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
 
@@
   $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$
-  of constructible $\ell$-adic sheaves on $\bG$ such then
+  of constructible $\ell$-adic sheaves on $\bG$ such that
   \[
@@
   \gcs{L} \ar[r]^{\varphi} & \gcs{L'}
-  && \gcs{L}\boxtimes\gcs{L} \ar[r]^{\varphi\boxtimes \varphi} & \gcs{L'} \boxtimes \gcs{L'}\\
+  && \LxL \ar[r]^{\varphi\boxtimes \varphi} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}\\
   }
@@
 follows from second condition appearing in the definition of character
-sheaves). The isomorphism $\mu : \bm^* \gcs{L} \to \gcs{L}\boxtimes\gcs{L}$
+sheaves). The isomorphism $\mu : \bm^* \gcs{L} \to \LxL$
 guarantees that the function $t^\Frob_\cs{L} : G(\Fq)\to \EEx$,
@@
   to \ref{CS.1} for $\cs{L}$ and use the canonical isomorphism
-  $(\bfxf)^*(\LxL) \iso \bf^*\gcs{L} \boxtimes \bf^*\gcs{L}$
+  $(\bfxf)^*(\LxL) \iso \bf^*\gcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gcs{L}$
   (a few times). Likewise, to see that $\bf^*\gcs{L}$ satisfies condition
@@
   defines a functor $f^* : \CS(G) \to \CS(H)$ one applies the functors $\bf^*$ and
-  $\bf^*\tightertimes\bf^*$ to \ref{CS.3} and argue as
+  $\bf^*\tight{1}{\times}{1}\bf^*$ to \ref{CS.3} and argue as
   above. It follows from the fact that sheaf hom commutes with these
@@
   pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$
-  and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ satisfies
+  and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \tight{0}{\boxtimes}{0} \cs{L}_0$ satisfies
   condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$
@@
   see that $\cs{E}$ is a line bundle on $G^0$, start by pulling back
-  $\pi: B \to G^0$ along $m_0 : G^0\times G^0 \to G^0$.
+  $\pi: B \to G^0$ along $m_0 : \GzxGz \to G^0$.
   \begin{equation}
@@
       \EEx & 1\ar[r] & \ar@/_1pc/[ll]_{\psi} A  \ar[r] & B \ar[r]^{\pi} & G^0 \ar[r] & 1\\
-      & 1\ar[r] & \ar@{.>}@/^1pc/[llu] \ar[u] A\times A  \ar[r]
-      & \ar[u]^{m_{B}} B\times B \ar[r]^{\pi\tighttimes \pi}  & \ar[u]^{m_0} G^0\times G^0 \ar[r] & 1\\
+      & 1\ar[r] & \ar@{.>}@/^1pc/[llu] \ar[u] \AxA  \ar[r]
+      & \ar[u]^{m_{B}} \BxB \ar[r]^{\pi\tight{1}{\times}{1} \pi}  & \ar[u]^{m_0} \GzxGz \ar[r] & 1\\
       }
   \end{equation}
-  As pictured above, the kernel of this pull-back is $A\times A$;
-  indeed, $A\times A\to B\times B$ is the pull-back of $A\to B$ along
+  As pictured above, the kernel of this pull-back is $\AxA$;
+  indeed, $\AxA \to \BxB$ is the pull-back of $A\to B$ along
   $m_{B}$. Use this Cartesian square to define a character (the dotted
-  arrow, above) of $A\times A$; that is, define $A\times A\to \EEx$
-  by the composition of $A\times A \to A$ and $\psi : A\to \EEx$.
-  Note that this character is $\psi \otimes \psi : A\times A\to \EEx$.
+  arrow, above) of $\AxA$; that is, define $\AxA \to \EEx$
+  by the composition of $\AxA \to A$ and $\psi : A\to \EEx$.
+  Note that this character is $\psi \otimes \psi : \AxA \to \EEx$.
   \Clifton{I haven't explained how maps between diagrams define sheaf
@@
   Since the lower sequence is precisely the sequence defining
-  $\cs{E}\boxtimes\cs{E}$, this shows that, by construction, $\cs{E}$
-  comes equipped with a canonical isomorphism $m_0^*\cs{E} \iso \cs{E}\boxtimes\cs{E}$.
-  Now the base change $\cs{E}$ comes equipped with isomorphisms
+  $\ExE$, this shows that, by construction, $\cs{E}$
+  comes equipped with a canonical isomorphism $m_0^*\cs{E} \iso \ExE$.
+  Now the base change $\gcs{E}$ comes equipped with isomorphisms
   $F^0 : \Frob_{G^0}^* \gcs{E} \to \gcs{E}$ and
-  $\mu^0 : \bm_0^* \gcs{E} \to \gcs{E}\boxtimes \gcs{E}$
+  $\mu^0 : \bm_0^* \gcs{E} \to \bExE$
   satisfying conditions \ref{CS.1} and \ref{CS.2}. Then $(\gcs{E},\mu^0,F^0)$
@@
 
-  Observe that $\bm: \bG\times \bG\to \bG$ is
+  Observe that $\bm: \bGxG \to \bG$ is
   completely determined by the family of maps
@@
   $\gcs{L}^{x}\boxtimes \gcs{L}^{y}$ is defined by the following diagram.
+
   \[
@@
   fact that the covering group of the middle arrow is $\Aut(\bf^{x+y})$, canonically.
+
+  \vspace{0.2in}
+
+  \begin{tikzpicture}[auto,style={rectangle, scale=1.2}]
+  \node (12) [anchor=east] at (4,2) {$\Aut(\bf^{x+y})$};
+  \node (22) [anchor=west] at (4.4,2) {$\bH^{x+y}$};
+  \node (32) [anchor=east] at (11,2) {$\bG^{x+y}$};
+  \node (01) at (0,1) {$\EEx$};
+  \node (11) [anchor=east] at (4,1) {$\Aut(\bf^{x+y})$};
+  \node (21) [anchor=west] at (4.4,1) {$\bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y$};
+  \node (31) [anchor=east] at (11,1) {$\bG^x\times \bG^y$};
+  \node (10) [anchor=east] at (4,0) {$\Aut(\bf^x)\times \Aut(\bf^y)$};
+  \node (20) [anchor=west] at (4.4,0) {$\bG^x\times \bG^y$};
+  \node (30) [anchor=east] at (11,0) {$\bG^x\times \bG^y$};
+  \draw [->] (4.3,1.94) arc (330:30:0.12);
+  \draw [->, densely dotted] (4.3,0.94) arc (330:30:0.12);
+  \draw [->] (4.3,-0.06) arc (330:30:0.12);
+  \draw [->] (12) to node[swap] {\footnotesize{$\psi_{x+y}$}} (01);
+  \draw [->, densely dotted] (11) -- (01);
+  \draw [->] (10) to node {\footnotesize{$\psi_x \otimes \psi_y$}} (01);
+  \draw [->, densely dotted] ($(11.south) + (0,-0.5)$) -- (11);
+  \draw [double equal sign distance] (11) -- (12);
+  \draw [->] (22) to node {\footnotesize{$\bf^{x+y}$}} (32);
+  \draw [->] ($(22.south) + (0,-0.5)$) -- (22);
+  \draw [->] (21) -- (31);
+  \draw [->] ($(32.south) + (0,-0.5)$) to node[swap] {\footnotesize{$\bm_{x,y}$}} (32);
+  \draw [->] ($(22.south) + (0,-1.5)$) -- ($(22.south) + (0,-1)$);
+  \draw [->] (20) to node {\footnotesize{$\bf^x \times \bf^y$}} (30);
+  \draw [->] ($(32.south) + (0,-1.5)$) -- ($(32.south) + (0,-1)$);
+  \end{tikzpicture}
+
   \[

### 2013-07-12 shanghai.tex
Bounded character sheaves defined. Provisionally.

--- 2013-07-08 shanghai.tex
@@
 Since $\pi_0(G)$ is an étale group scheme locally of finite type over $\Fq$, 
-it follows from Proposition~\ref{prop:pullback} that \eqref{eq:pi-1}defines a sequence of functors
- \[
-  \xymatrix{
-\CS(0) \ar[r] & \CS(\pi_0(G)) \ar[r] & \CS(G) \ar[r] & \CS(G^0) \ar[r] & \CS(0).
-  }
- \]
-We will see that
+it follows from Proposition~\ref{prop:pullback} that \eqref{eq:pi-1} defines a sequence of functors
+ \[
+  \xymatrix{
+\CS(0) \ar[r] & \CS(\pi_0(G)) \ar[r] & \CS(G) \ar[r] & \CS(G^0) \ar[r] & \CS(0)
+  }
+ \]
+which induces, upon passage to Picard groups, a sequence of group homomorphisms 
+ \[
+  \xymatrix{
+\CSiso{0} \ar[r] & \CSiso{\pi_0(G)} \ar[r] & \CSiso{G} \ar[r] & \CSiso{G^0} \ar[r] & \CSiso{0}.
+  }
+ \]
+It is easy to see that $\CSiso{0}$ is trivial.
+In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated, and we will also see that the sequence of abelian groups above is split exact; this allows us to find $\CSiso{G}$.
+To do this, we find it useful to offer an alternate perspective on a subcategory of $\CS(G)$, in the next section.
 
@@
 
-[Introduce category $\CS_0(G)$]
+In this section we describe a full subcategory of $\CS(G)$, called the category of bounded character sheaves on $G$ and denoted by $\CS_b(G)$, which will illuminate the nature of $\CS(G)$ and will also play a role in the arguments later in this paper.
+
+In order to define $\CS_b(G)$ as must recall a fundamental fact about finite etale covers of schemes.
+Let $X$ be a scheme, locally of finite type over $k$, and let $\pi : Y\to X$ and $\pi_1: Y_1\to X$ be finite etale covers and let $f_1 : Y_1\to Y$ be a morphism such that $\pi_1 = \pi \circ f_1$.
+Then $f_1$ determines a group homomorphism $\Aut(\pi_1)\to \Aut(\pi)$, as follows  .
+.
+.
+
+Now we may define $\CS_b(G)$, where $G$ is a smooth group scheme locally of finite type over $\Fq$.
+\begin{enumerate}
+\labitem{(CSb.0)}{CSb.0}
+An object in $\CS_b(G)$ is a pair $(\pi,\psi)$ where $\pi : H\to G$ is a finite etale cover in the category of group schemes over $\Fq$ such that $\Gal(\bFq/\Fq)$ acts trivially on $\ker {\bar \pi}$ (so $\ker {\bar \pi} = \ker \pi$) and $\psi : \ker \pi \to \Aut(V)$ is an irreducible representation on a $\EE$-vector space $V$.
+\[
+\xymatrix{
+V & \Aut(V) & 1 \ar[r] & \ar@/_2pc/[ll]^{\psi} \ker \pi \ar[r] & H \ar[r]^{\pi} & G \ar[r] &1 
+}
+\]
+\labitem{(CSb.1)}{CSb.1}
+A morphism $T : (\pi,\psi) \to (\pi',\psi')$ is a linear transformation $T : V \to V'$ which, if non-trivial, has the property that there is a finite etale cover $\pi_1 : H_1 \to G$ in the category of group schemes over $\Fq$ and morphisms $H_1\to H$, $H_1\to H'$ inducing homomorphisms $\ker \pi_1 \to \ker\pi$ and $\ker\pi_1\to \ker\pi$ such that the following diagram commutes.
+\[
+\xymatrix{
+V \ar[dd] & \Aut(V) \ar@{=}[dd] & 1 \ar[r] & \ar@/^2pc/[ll]_{\psi} \ker \pi \ar[r] & H \ar[r]^{\pi} & G \ar[r] &1\\
+ &  & 1 \ar[r] & \ar[u] \ar[d] \ker \pi \ar[r] & \ar[u] \ar[d] H_1 \ar[r]^{\pi_1} & \ar@{=}[u] \ar@{=}[d] G \ar[r] &1\\
+V' & \Aut(V) & 1 \ar[r] & \ar@/_2pc/[ll]^{\psi'} \ker \pi' \ar[r] & H' \ar[r]^{\pi} & G \ar[r] &1\\ 
+}
+\]
+\end{enumerate}
+We refer to $\CS_b(G)$ as the category of \cdef{bounded character sheaves on $G$}.
+
+\begin{proposition}
+$\CS_b(G)$ is a full subcategory of $\CS(G)$.
+\end{proposition}
 

### 2013-07-12 shanghai.tex
commit for our meeting

@@
 group scheme for $G$:
+ \begin{equation}\label{eq:pi-2}
+   \xymatrix{
+     0 \ar[r] & G^0 \ar[r] & G \ar[r] & \pi_0(G) \ar[r] & 0.
+    }
+ \end{equation}
+Since $\pi_0(G)$ is an Abelian group scheme, smooth (in fact, etale) and locally of finite type over $\Fq$, 
+it follows from Proposition~\ref{prop:pullback} that \eqref{eq:pi-1} defines a sequence of functors
+ \[
+  \xymatrix{
+\CS(0) \ar[r] & \CS(\pi_0(G)) \ar[r] & \CS(G) \ar[r] & \CS(G^0) \ar[r] & \CS(0)
+  }
+ \]
+which induces, upon passage to Picard groups, a sequence of group homomorphisms 
  \begin{equation}\label{eq:pi-1}
   \xymatrix{
-     0 \ar[r] & G^0 \ar[r] & G \ar[r] & \pi_0(G) \ar[r] & 0.
+\CSiso{0} \ar[r] & \CSiso{\pi_0(G)} \ar[r] & \CSiso{G} \ar[r] & \CSiso{G^0} \ar[r] & \CSiso{0}.
   }
  \end{equation}
-Since $\pi_0(G)$ is an étale group scheme locally of finite type over $\Fq$, 
-it follows from Proposition~\ref{prop:pullback} that \eqref{eq:pi-1} defines a sequence of functors
- \[
-  \xymatrix{
-\CS(0) \ar[r] & \CS(\pi_0(G)) \ar[r] & \CS(G) \ar[r] & \CS(G^0) \ar[r] & \CS(0)
-  }
- \]
-which induces, upon passage to Picard groups, a sequence of group homomorphisms 
- \[
-  \xymatrix{
-\CSiso{0} \ar[r] & \CSiso{\pi_0(G)} \ar[r] & \CSiso{G} \ar[r] & \CSiso{G^0} \ar[r] & \CSiso{0}.
-  }
- \]
 It is easy to see that $\CSiso{0}$ is trivial.
-In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated, and we will also see that the sequence of abelian groups above is split exact; this allows us to find $\CSiso{G}$.
-To do this, we find it useful to offer an alternate perspective on a subcategory of $\CS(G)$, in the next section.
+In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated, and we will also see that \eqref{eq:pi-1} is split exact; this allows us to find $\CSiso{G}$.
+To prove this, we find it useful to offer an alternate perspective on a subcategory of $\CS(G)$, in the next section.
 
@@
 We refer to $\CS_b(G)$ as the category of \cdef{bounded character sheaves on $G$}.
-
+\Clifton{I'd love to find a way to define $\CS_b(G)$ without insisting that $\psi$ is an \emph{irreducible} representation, and then prove that the full subcategory of simple objects in $\CS_b(G)$ is a full subcategory of $\CS(G)$.
+I'm studying my notes from BIRS, letters from Masoud, and SGA7, to see how to do this.}
 \begin{proposition}

### 2013-07-12 shanghai.tex
Working on switching to TikZ

--- 2013-07-12 shanghai.tex
@@
 \usepackage{tikz}
-\usetikzlibrary{shapes,arrows,calc}
+\usetikzlibrary{shapes,arrows,calc,matrix}
 \usepackage{manfnt}
@@
 
-\tikzset{every picture/.style={>=stealth}}
+\tikzset{every picture/.style={>=stealth},label/.style={font=\footnotesize}}
 
@@
   $\pi: B \to G^0$ along $m_0 : \GzxGz \to G^0$.
+
+  \begin{center}
+  \begin{tikzpicture}
+  \matrix (m) [matrix of math nodes,row sep=3em,column sep=3em,minimum width=2em] {
+  \EEx & 1 & A & B & G^0 & 1 \\
+  & 1 & \AxA & \BxB & \GzxGz & 1\\ };
+  %\foreach \x in {2,3,4,5} \let \x1={\x+1} 
+  %\draw [->] (m-1-\x) -- (m-1-\x1);
+  \end{tikzpicture}
+  \end{center}
+
   \begin{equation}
@@
   groups.
+
+  \begin{center}
+  \begin{tikzpicture}[auto]
+  \matrix (m) [matrix of math nodes,row sep=3em,column sep=3em,minimum width=2em] {
+  A & A & \\
+  B & H & \pi_0(H) \\
+  G^0 & G & \pi_0(G) \\};
+  \draw [double equal sign distance] (m-1-1) -- (m-1-2);
+  \draw [->] (m-1-1) -- (m-2-1);
+  \draw [->] (m-2-1) -- (m-2-2);
+  \draw [->] (m-1-2) -- (m-2-2);
+  \draw [->] (m-2-1) to node[label,swap] {$\pi$} (m-3-1);
+  \draw [->] (m-3-1) -- (m-3-2);
+  \draw [->] (m-2-2) to node[label,swap] {$f$} (m-3-2);
+  \draw [->] (m-2-2) -- (m-2-3);
+  \draw [->] (m-3-2) -- (m-3-3);
+  \draw [->] (m-2-3) to node[below,rotate=90] {$\sim$} node[label,swap] {$\pi_0(f)$} (m-3-3);
+  \end{tikzpicture}
+  \end{center}
+
   \begin{equation} \label{extension-diagram}
@@
   $\ZZ[\Gamma]$-module.  Consider the universal diagram for injectivity:
+
+  \begin{center}
+  \begin{tikzpicture}[auto]
+  \matrix (m) [matrix of math nodes,row sep=3em,column sep=3em,minimum width=2em] {
+  & B \\
+  I & A \\};
+  \draw [right hook->] (m-2-2) -- (m-1-2);
+  \draw [->] (m-2-2) to node[swap,label] {$a$} (m-2-1);
+  \end{tikzpicture}
+  \end{center}
+
   \[
@@
   Since $B / I_{H_m}B \cong B \otimes_A A / I_{H_m}A$, we get
+
+  \begin{center}
+  \begin{tikzpicture}
+  \matrix (m) [matrix of math nodes,row sep=3em,column sep=3em,minimum width=2em] {
+  & B/I_{H_m}B & B \\
+  I & A/I_{H_m}A & A \\};
+  \draw [->,dashed] (m-1-2) -- (m-2-1);
+  \draw [right hook->] (m-2-2) -- (m-1-2);
+  \draw [->] (m-2-2) -- (m-2-1);
+  \draw [->>] (m-2-3) -- (m-2-2);
+  \draw [right hook->] (m-2-3) -- (m-1-3);
+  \draw [->>] (m-1-3) -- (m-1-2);
+  \end{tikzpicture}
+  \end{center}
+
   \[
@@
 
+  \begin{tikzpicture}[auto,style={rectangle}]
+  \node (0) at (0,0) {$\EEx$};
+  \node (1) [anchor=east] at (7,0) {$\Aut(\bf^x) \times \Aut(\bf^y)$};
+  \node (2) [anchor=west] at (7.4,0) {$\bH^x \times \bH^y$};
+  \node (3) at (12,0) {$\bG^x \times \bG^y$};
+  \draw [->] (1) to node[swap, label] {$\psi_x \otimes \psi_y$} (0);
+  \draw [->] (7.3,-0.06) arc (330:40:0.12) -- (7.3,0.07);
+  \draw [->] (2) to node[label] {$\bf^x \tight{0}{\times}{0} \bf^y$} (3);
+  \end{tikzpicture}
+
   \[
@@
 
-  \begin{tikzpicture}[auto,style={rectangle, scale=1.2}]
+  \begin{tikzpicture}[auto,style={rectangle},scale=1.2]
   \node (12) [anchor=east] at (4,2) {$\Aut(\bf^{x+y})$};
@@
   \node (30) [anchor=east] at (11,0) {$\bG^x\times \bG^y$};
-  \draw [->] (4.3,1.94) arc (330:30:0.12);
-  \draw [->, densely dotted] (4.3,0.94) arc (330:30:0.12);
-  \draw [->] (4.3,-0.06) arc (330:30:0.12);
-  \draw [->] (12) to node[swap] {\footnotesize{$\psi_{x+y}$}} (01);
+  \draw [->] (4.3,1.94) arc (330:40:0.12) -- (4.3,2.07);
+  \draw [->, densely dotted] (4.3,0.94) arc (330:40:0.12) -- (4.3,1.07);
+  \draw [->] (4.3,-0.06) arc (330:40:0.12) -- (4.3,0.07);
+  \draw [->] (12) to node[swap,label] {$\psi_{x+y}$} (01);
   \draw [->, densely dotted] (11) -- (01);
-  \draw [->] (10) to node {\footnotesize{$\psi_x \otimes \psi_y$}} (01);
+  \draw [->] (10) to node[label] {$\psi_x \otimes \psi_y$} (01);
   \draw [->, densely dotted] ($(11.south) + (0,-0.5)$) -- (11);
   \draw [double equal sign distance] (11) -- (12);
-  \draw [->] (22) to node {\footnotesize{$\bf^{x+y}$}} (32);
+  \draw [->] (22) to node[label] {$\bf^{x+y}$} (32);
   \draw [->] ($(22.south) + (0,-0.5)$) -- (22);
   \draw [->] (21) -- (31);
-  \draw [->] ($(32.south) + (0,-0.5)$) to node[swap] {\footnotesize{$\bm_{x,y}$}} (32);
+  \draw [->] ($(32.225) + (0,-0.5)$) to node[swap] {\footnotesize{$\bm_{x,y}$}} (32.225);
   \draw [->] ($(22.south) + (0,-1.5)$) -- ($(22.south) + (0,-1)$);
-  \draw [->] (20) to node {\footnotesize{$\bf^x \times \bf^y$}} (30);
-  \draw [->] ($(32.south) + (0,-1.5)$) -- ($(32.south) + (0,-1)$);
+  \draw [->] (20) to node[label] {$\bf^x \times \bf^y$} (30);
+  \draw [->] ($(32.225) + (0,-1.5)$) -- ($(32.225) + (0,-1)$);
   \end{tikzpicture}

### 2013-07-12 shanghai.tex

@@
 group scheme for $G$:
+ \begin{equation}\label{eq:pi-2}
+   \xymatrix{
+     0 \ar[r] & G^0 \ar[r] & G \ar[r] & \pi_0(G) \ar[r] & 0.
+    }
+ \end{equation}
+Since $\pi_0(G)$ is an Abelian group scheme, smooth (in fact, etale) and locally of finite type over $\Fq$, 
+it follows from Proposition~\ref{prop:pullback} that \eqref{eq:pi-1} defines a sequence of functors
+ \[
+  \xymatrix{
+\CS(0) \ar[r] & \CS(\pi_0(G)) \ar[r] & \CS(G) \ar[r] & \CS(G^0) \ar[r] & \CS(0)
+  }
+ \]
+which induces, upon passage to Picard groups, a sequence of group homomorphisms 
  \begin{equation}\label{eq:pi-1}
   \xymatrix{
-     0 \ar[r] & G^0 \ar[r] & G \ar[r] & \pi_0(G) \ar[r] & 0.
+\CSiso{0} \ar[r] & \CSiso{\pi_0(G)} \ar[r] & \CSiso{G} \ar[r] & \CSiso{G^0} \ar[r] & \CSiso{0}.
   }
  \end{equation}
-Since $\pi_0(G)$ is an étale group scheme locally of finite type over $\Fq$, 
-it follows from Proposition~\ref{prop:pullback} that \eqref{eq:pi-1}defines a sequence of functors
- \[
-  \xymatrix{
-\CS(0) \ar[r] & \CS(\pi_0(G)) \ar[r] & \CS(G) \ar[r] & \CS(G^0) \ar[r] & \CS(0).
-  }
- \]
-We will see that
+It is easy to see that $\CSiso{0}$ is trivial.
+In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated, and we will also see that \eqref{eq:pi-1} is split exact; this allows us to find $\CSiso{G}$.
+To prove this, we find it useful to offer an alternate perspective on a subcategory of $\CS(G)$, in the next section.
 
@@
 
-[Introduce category $\CS_0(G)$]
+In this section we describe a full subcategory of $\CS(G)$, called the category of bounded character sheaves on $G$ and denoted by $\CS_b(G)$, which will illuminate the nature of $\CS(G)$ and will also play a role in the arguments later in this paper.
+
+In order to define $\CS_b(G)$ as must recall a fundamental fact about finite etale covers of schemes.
+Let $X$ be a scheme, locally of finite type over $k$, and let $\pi : Y\to X$ and $\pi_1: Y_1\to X$ be finite etale covers and let $f_1 : Y_1\to Y$ be a morphism such that $\pi_1 = \pi \circ f_1$.
+Then $f_1$ determines a group homomorphism $\Aut(\pi_1)\to \Aut(\pi)$, as follows  .
+.
+.
+
+Now we may define $\CS_b(G)$, where $G$ is a smooth group scheme locally of finite type over $\Fq$.
+\begin{enumerate}
+\labitem{(CSb.0)}{CSb.0}
+An object in $\CS_b(G)$ is a pair $(\pi,\psi)$ where $\pi : H\to G$ is a finite etale cover in the category of group schemes over $\Fq$ such that $\Gal(\bFq/\Fq)$ acts trivially on $\ker {\bar \pi}$ (so $\ker {\bar \pi} = \ker \pi$) and $\psi : \ker \pi \to \Aut(V)$ is an irreducible representation on a $\EE$-vector space $V$.
+\[
+\xymatrix{
+V & \Aut(V) & 1 \ar[r] & \ar@/_2pc/[ll]^{\psi} \ker \pi \ar[r] & H \ar[r]^{\pi} & G \ar[r] &1 
+}
+\]
+\labitem{(CSb.1)}{CSb.1}
+A morphism $T : (\pi,\psi) \to (\pi',\psi')$ is a linear transformation $T : V \to V'$ which, if non-trivial, has the property that there is a finite etale cover $\pi_1 : H_1 \to G$ in the category of group schemes over $\Fq$ and morphisms $H_1\to H$, $H_1\to H'$ inducing homomorphisms $\ker \pi_1 \to \ker\pi$ and $\ker\pi_1\to \ker\pi$ such that the following diagram commutes.
+\[
+\xymatrix{
+V \ar[dd] & \Aut(V) \ar@{=}[dd] & 1 \ar[r] & \ar@/^2pc/[ll]_{\psi} \ker \pi \ar[r] & H \ar[r]^{\pi} & G \ar[r] &1\\
+ &  & 1 \ar[r] & \ar[u] \ar[d] \ker \pi \ar[r] & \ar[u] \ar[d] H_1 \ar[r]^{\pi_1} & \ar@{=}[u] \ar@{=}[d] G \ar[r] &1\\
+V' & \Aut(V) & 1 \ar[r] & \ar@/_2pc/[ll]^{\psi'} \ker \pi' \ar[r] & H' \ar[r]^{\pi} & G \ar[r] &1\\ 
+}
+\]
+\end{enumerate}
+We refer to $\CS_b(G)$ as the category of \cdef{bounded character sheaves on $G$}.
+\Clifton{I'd love to find a way to define $\CS_b(G)$ without insisting that $\psi$ is an \emph{irreducible} representation, and then prove that the full subcategory of simple objects in $\CS_b(G)$ is a full subcategory of $\CS(G)$.
+I'm studying my notes from BIRS, letters from Masoud, and SGA7, to see how to do this.}
+\begin{proposition}
+$\CS_b(G)$ is a full subcategory of $\CS(G)$.
+\end{proposition}
 

### 2013-07-16 shanghai.tex
Switched over to tikz

@@
 \usetikzlibrary{shapes,arrows,calc,matrix}
+\usepackage{tikz-cd}
 \usepackage{manfnt}
@@
   \[
-  \xymatrix{
-    \bm_3^*\gcs{L} \ar[rr]^{(\bm \tight{1}{\times}{2} \id)^*\mu} \ar[d]_{(\id \tight{2}{\times}{1} \bm)^*\mu}
-    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \ar[d]^{\mu \boxtimes \id} \\
-    \gcs{L} \boxtimes \bm^* \gcs{L} \ar[rr]^{\id \boxtimes \mu}
+  \begin{tikzcd}[row sep=40]
+  \bm_3^*\gcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
+    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
+    \gcs{L} \boxtimes \bm^* \gcs{L} \arrow{rr}{\id \boxtimes \mu}
     &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL\\
-  }
+  \end{tikzcd}
   \]
@@
   \[
-  \xymatrix{
-    \Frob_{\GxxG}^* \bm^* \gcs{L} \ar[rr]^{\Frob_{\GxxG}^*\mu}
+  \begin{tikzcd}
+  \Frob_{\GxxG}^* \bm^* \gcs{L} \arrow{rr}{\Frob_{\GxxG}^*\mu}
     && \Frob_{\GxxG}^*(\LxL)\\
-    \ar@{=}[u] \bm^*  \Frob_{G}^* \gcs{L} \ar[d]_{\bm^* F}
-    && \ar[d]^{F\boxtimes F} \ar@{=}[u] \Frob_{G}^*\gcs{L}\boxtimes \Frob_{G}^*\gcs{L}\\
-    \bm^*\gcs{L} \ar[rr]^{\mu}
+    \arrow[equal]{u} \bm^*  \Frob_{G}^* \gcs{L} \arrow[swap]{d}{\bm^* F}
+    && \Frob_{G}^*\gcs{L}\boxtimes \Frob_{G}^*\gcs{L} \dar{F\boxtimes F} \arrow[equal]{u} \\
+    \bm^*\gcs{L} \arrow{rr}{\mu}
     && \LxL\\
-  }
+  \end{tikzcd}
   \]
@@
   \[
-  \xymatrix{
-  \ar[d]_{F} \Frob_G^* \gcs{L} \ar[r]^{\Frob_G^* \varphi} & \ar[d]^{F'} \Frob_G^* \gcs{L'}
-  & \text{and}& \ar[d]_{\mu} m^* \gcs{L} \ar[r]^{m^* \varphi} & \ar[d]^{\mu'} m^* \gcs{L'} \\
-  \gcs{L} \ar[r]^{\varphi} & \gcs{L'}
-  && \LxL \ar[r]^{\varphi\boxtimes \varphi} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}\\
-  }
+  \begin{tikzcd}[column sep=40]
+  \Frob_G^* \gcs{L} \rar{\Frob_G^* \varphi} \arrow[swap]{d}{F} & \Frob_G^* \gcs{L'} \dar{F'}
+  & \arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} & \arrow[swap]{d}{\mu} m^* \gcs{L} \rar{m^* \varphi} & m^* \gcs{L'} \dar{\mu'} \\
+  \gcs{L} \rar{\varphi} & \gcs{L'}
+  & {} & \LxL \rar{\tight{1}{\varphi\boxtimes \varphi}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
+  \end{tikzcd}
   \]
@@
   \[
-  \xymatrix{
-  \CSiso{G} \ar[r]^{f^*} \ar[d]^{t_{G}} &  \ar[d]^{t_{H}} \CSiso{H}\\
-  \Hom_\text{grp}(G(\Fq),\EEx) \ar[r] & \Hom_\text{grp}(H(\Fq),\EEx)
-  }
+  \begin{tikzcd}[row sep=40]
+   \CSiso{G} \rar{f^*} \arrow[swap]{d}{t_{G}} & \CSiso{H} \dar{t_H} \\
+  \Hom_\text{grp}(G(\Fq),\EEx) \rar & \Hom_\text{grp}(H(\Fq),\EEx)
+  \end{tikzcd}
   \]
@@
 \begin{equation}\label{eq:pi-2}
-   \xymatrix{
-     0 \ar[r] & G^0 \ar[r] & G \ar[r] & \pi_0(G) \ar[r] & 0.
-    }
+\begin{tikzcd}
+0 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
+\end{tikzcd}
 \end{equation}
@@
 \[
-  \xymatrix{
-\CS(0) \ar[r] & \CS(\pi_0(G)) \ar[r] & \CS(G) \ar[r] & \CS(G^0) \ar[r] & \CS(0)
-  }
+\begin{tikzcd}
+\CS(0) \rar & \CS(\pi_0(G)) \rar & \CS(G) \rar & \CS(G^0) \rar & \CS(0)
+\end{tikzcd}
 \]
@@
 \begin{equation}\label{eq:pi-1}
-  \xymatrix{
-\CSiso{0} \ar[r] & \CSiso{\pi_0(G)} \ar[r] & \CSiso{G} \ar[r] & \CSiso{G^0} \ar[r] & \CSiso{0}.
-  }
+\begin{tikzcd}
+\CSiso{0} \rar & \CSiso{\pi_0(G)} \rar & \CSiso{G} \rar & \CSiso{G^0} \rar & \CSiso{0}.
+\end{tikzcd}
 \end{equation}
@@
 \[
-\xymatrix{
-V & \Aut(V) & 1 \ar[r] & \ar@/_2pc/[ll]^{\psi} \ker \pi \ar[r] & H \ar[r]^{\pi} & G \ar[r] &1 
-}
+\begin{tikzcd}
+V & \Aut(V) & 1 \rar & \arrow[bend right,swap]{ll}{\psi} \ker \pi \rar & H \rar{\pi} & G \rar &1
+\end{tikzcd}
 \]
@@
 \[
-\xymatrix{
-V \ar[dd] & \Aut(V) \ar@{=}[dd] & 1 \ar[r] & \ar@/^2pc/[ll]_{\psi} \ker \pi \ar[r] & H \ar[r]^{\pi} & G \ar[r] &1\\
- &  & 1 \ar[r] & \ar[u] \ar[d] \ker \pi \ar[r] & \ar[u] \ar[d] H_1 \ar[r]^{\pi_1} & \ar@{=}[u] \ar@{=}[d] G \ar[r] &1\\
-V' & \Aut(V) & 1 \ar[r] & \ar@/_2pc/[ll]^{\psi'} \ker \pi' \ar[r] & H' \ar[r]^{\pi} & G \ar[r] &1\\ 
-}
+\begin{tikzcd}
+V \arrow{dd} & \Aut(V) \ar[equal]{dd} & 1 \rar & \arrow[swap,bend left]{ll}{\psi} \ker \pi \rar & H \rar{\pi} & G \rar &1\\
+ &  & 1 \rar & \ker \pi_1 \rar \uar \dar & H_1 \uar \dar \rar{\pi_1} & \ar[equal]{u} \arrow[equal]{d} G \rar &1\\
+V' & \Aut(V') & 1 \rar & \arrow[bend right]{ll}{\psi'} \ker \pi' \rar & H' \rar{\pi'} & G \rar &1
+\end{tikzcd}
 \]
@@
   \[
-  \xymatrix{
-    1 \ar[r] & \pi_1(\bG, \bg) \ar[r] &  \Weil(G,\bg) \ar[r]
-    & \ar@/_1pc/@{.>}[l]_{g} \Weil(\bFq/\Fq) \ar[r] & 1
-    }
+  \begin{tikzcd}
+  1 \rar & \pi_1(\bG, \bg) \rar &  \Weil(G,\bg) \rar
+  & \ar[swap,bend right, dotted]{l}{g} \Weil(\bFq/\Fq) \rar & 1
+  \end{tikzcd}
   \]
@@
   \[
-  \xymatrix{
-    1 \ar[r] & \ar@{=}[d] \pi_1(\bG, \bg) \ar[r] & \ar[d] \Weil(G,\bg) \ar[r] & \ar[d]  \Weil(\bFq/\Fq) \ar[r] & 1\\
-    1 \ar[r] &  \pi_1(\bG, \bg) \ar[r] & \pi_1(G,\bg) \ar[r] & \Gal(\bFq/\Fq) \ar[r] & 1\\
-    }
+  \begin{tikzcd}
+  1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \Weil(G,\bg) \rar \dar & \Weil(\bFq/\Fq) \rar \dar & 1\\
+  1 \rar &  \pi_1(\bG, \bg) \rar & \pi_1(G,\bg) \rar & \Gal(\bFq/\Fq) \rar & 1
+  \end{tikzcd}
   \]
@@
     \[
-    \xymatrix{
-      \gcs{L}_{x+y+z} \ar[rr]^{\mu_{x+y,z}} \ar[d]_{\mu_{x,y+z}}
-      && \gcs{L}_{x+y}\otimes \gcs{L}_{z} \ar[d]^{\mu_{x,y} \otimes \id} \\
-      \gcs{L}_{x} \otimes \gcs{L}_{y+z} \ar[rr]^{\id \otimes \mu_{y,z}}
-      && \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes \gcs{L}_{z}\\
-      }
+    \begin{tikzcd}[row sep=40]
+      \gcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
+      && \gcs{L}_{x+y}\otimes \gcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
+      \gcs{L}_{x} \otimes \gcs{L}_{y+z} \arrow{rr}{\id \otimes \mu_{y,z}}
+      && \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes \gcs{L}_{z}
+    \end{tikzcd}
     \]
@@
     \[
-    \xymatrix{
-      \gcs{L}_{\Frob(x)+\Frob(y)} \ar[d]_{F_{x+y}} \ar[rr]^{\mu_{\Frob(x),\Frob(y)}}
-      &&\ar[d]^{F_x\otimes F_y}  \gcs{L}_{\Frob(x)}\otimes \gcs{L}_{\Frob(y)}\\
-      \gcs{L}_{x+y} \ar[rr]^{\mu_{x,y}}
-      && \gcs{L}_x \otimes\gcs{L}_y\\
-      }
+    \begin{tikzcd}[row sep=40]
+      \gcs{L}_{\Frob(x)+\Frob(y)} \arrow[swap]{d}{F_{x+y}} \arrow{rr}{\mu_{\Frob(x),\Frob(y)}}
+      && \gcs{L}_{\Frob(x)}\otimes \gcs{L}_{\Frob(y)} \dar{F_x \tight{0}{\otimes}{0} F_y} \\
+      \gcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
+      && \gcs{L}_x \otimes\gcs{L}_y
+    \end{tikzcd}
     \]
@@
     \[
-    \xymatrix{
-      \ar[d]_{F_x} \gcs{L}_{\Frob(x)} \ar[r]^{\varphi_{\Frob(x)}} & \ar[d]^{F_x'} \gcs{L'}_{\Frob(x)}
-      &\text{and}& \ar[d]_{\mu} \gcs{L}_{x+y} \ar[r]^{\varphi_{x+y}} & \ar[d]^{\mu'_{x+y}} \gcs{L'}_{x+y} \\
-      \gcs{L}_x \ar[r]^{\varphi_x} & \gcs{L'}_x
-      && \gcs{L}_x\otimes\gcs{L}_y \ar[r]^{\varphi_x\otimes \varphi_y} & \gcs{L'}_x \otimes \gcs{L'}_y\\
-      }
+    \begin{tikzcd}[column sep=40]
+      \arrow[swap]{d}{F_x} \gcs{L}_{\Frob(x)} \rar{\varphi_{\Frob(x)}} & \gcs{L'}_{\Frob(x)} \dar{F_x'}
+      &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}& \arrow[swap]{d}{\mu} \gcs{L}_{x+y} \rar{\varphi_{x+y}} & \gcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
+      \gcs{L}_x \rar{\varphi_x} & \gcs{L'}_x
+      & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\varphi_x\otimes \varphi_y} & \gcs{L'}_x \otimes \gcs{L'}_y
+    \end{tikzcd}
     \]
@@
   $\Hom(\mbox{---}, \EEx)$ to
-  $$0 \rightarrow X^\Frob \rightarrow X \rightarrow X/X^\Frob \rightarrow 0$$
+  \[
+  \begin{tikzcd}
+  0 \rar & X^\Frob \rar & X \rar & X/X^\Frob \rar & 0
+  \end{tikzcd}
+  \]
   and considering the associated long exact sequence gives the
@@
   \begin{equation}\label{E}
-    \xymatrix{
-      \EEx & 1\ar[r] & \ar@/_1pc/[ll]_{\psi} A  \ar[r] & B \ar[r]^{\pi} & G^0 \ar[r] & 1\\
-      }
+  \begin{tikzcd}
+  \EEx & 1\rar & A \arrow[bend right,swap]{ll}{\psi} \rar & B \rar{\pi} & G^0 \rar & 1
+  \end{tikzcd}
   \end{equation}
@@
   $\pi: B \to G^0$ along $m_0 : \GzxGz \to G^0$.
-
-  \begin{center}
-  \begin{tikzpicture}
-  \matrix (m) [matrix of math nodes,row sep=3em,column sep=3em,minimum width=2em] {
-  \EEx & 1 & A & B & G^0 & 1 \\
-  & 1 & \AxA & \BxB & \GzxGz & 1\\ };
-  %\foreach \x in {2,3,4,5} \let \x1={\x+1} 
-  %\draw [->] (m-1-\x) -- (m-1-\x1);
-  \end{tikzpicture}
-  \end{center}
-
   \begin{equation}
-    \xymatrix{
-      \EEx & 1\ar[r] & \ar@/_1pc/[ll]_{\psi} A  \ar[r] & B \ar[r]^{\pi} & G^0 \ar[r] & 1\\
-      & 1\ar[r] & \ar@{.>}@/^1pc/[llu] \ar[u] \AxA  \ar[r]
-      & \ar[u]^{m_{B}} \BxB \ar[r]^{\pi\tight{1}{\times}{1} \pi}  & \ar[u]^{m_0} \GzxGz \ar[r] & 1\\
-      }
+  \begin{tikzcd}
+  \EEx & 1\rar & A \arrow[bend right,swap]{ll}{\psi} \rar & B \rar{\pi} & G^0 \rar & 1\\
+      & 1\rar & \AxA \arrow[dashed]{llu} \uar \rar
+      & \BxB \rar{\pi\tight{1}{\times}{1} \pi} \uar{m_{B}} & \GzxGz \uar{m_0} \rar & 1
+  \end{tikzcd}
   \end{equation}
@@
   groups.
-
-  \begin{center}
-  \begin{tikzpicture}[auto]
-  \matrix (m) [matrix of math nodes,row sep=3em,column sep=3em,minimum width=2em] {
-  A & A & \\
-  B & H & \pi_0(H) \\
-  G^0 & G & \pi_0(G) \\};
-  \draw [double equal sign distance] (m-1-1) -- (m-1-2);
-  \draw [->] (m-1-1) -- (m-2-1);
-  \draw [->] (m-2-1) -- (m-2-2);
-  \draw [->] (m-1-2) -- (m-2-2);
-  \draw [->] (m-2-1) to node[label,swap] {$\pi$} (m-3-1);
-  \draw [->] (m-3-1) -- (m-3-2);
-  \draw [->] (m-2-2) to node[label,swap] {$f$} (m-3-2);
-  \draw [->] (m-2-2) -- (m-2-3);
-  \draw [->] (m-3-2) -- (m-3-3);
-  \draw [->] (m-2-3) to node[below,rotate=90] {$\sim$} node[label,swap] {$\pi_0(f)$} (m-3-3);
-  \end{tikzpicture}
-  \end{center}
-
-  \begin{equation} \label{extension-diagram}
-    \xymatrix{
-      & A \ar[d] \ar@{=}[r] & A \ar[d] &  \\
-      & B \ar[r] \ar[d]_{\pi} & H \ar[r] \ar[d]_{f} & \pi_0(H) \ar[d]_{\pi_0(f)}^{\iso} \\
-      & G^0 \ar[r] & G \ar[r] & \pi_0(G).
-    }
+  \begin{equation}\label{extension-diagram}
+  \begin{tikzcd}
+  A \arrow[equal]{r} \dar & A \dar \\
+  B \rar \dar[swap]{\pi} & H \rar \dar[swap]{f} & \pi_0(H) \arrow{d}[below,rotate=90]{\sim}[swap]{\pi_0(f)} \\
+  G^0 \rar & G \rar & \pi_0(G)
+  \end{tikzcd}
   \end{equation}
@@
 
-  \begin{center}
-  \begin{tikzpicture}[auto]
-  \matrix (m) [matrix of math nodes,row sep=3em,column sep=3em,minimum width=2em] {
-  & B \\
-  I & A \\};
-  \draw [right hook->] (m-2-2) -- (m-1-2);
-  \draw [->] (m-2-2) to node[swap,label] {$a$} (m-2-1);
-  \end{tikzpicture}
-  \end{center}
-
-  \[
-  \xymatrix{
-    & B \\
-    I & A \ar@{>->}[u] \ar[l]_{a}
-    }
-  \]
-
+  \[
+  \begin{tikzcd}
+  A \rar{a} \arrow[hook]{d} & I \\
+  B
+  \end{tikzcd}
+  \]
   where $A$ and $B$ are arbitrary $\ZZ[\Gamma]$-modules.  Since $H_m$ acts trivially on $I$,
@@
   Since $B / I_{H_m}B \cong B \otimes_A A / I_{H_m}A$, we get
-
-  \begin{center}
-  \begin{tikzpicture}
-  \matrix (m) [matrix of math nodes,row sep=3em,column sep=3em,minimum width=2em] {
-  & B/I_{H_m}B & B \\
-  I & A/I_{H_m}A & A \\};
-  \draw [->,dashed] (m-1-2) -- (m-2-1);
-  \draw [right hook->] (m-2-2) -- (m-1-2);
-  \draw [->] (m-2-2) -- (m-2-1);
-  \draw [->>] (m-2-3) -- (m-2-2);
-  \draw [right hook->] (m-2-3) -- (m-1-3);
-  \draw [->>] (m-1-3) -- (m-1-2);
-  \end{tikzpicture}
-  \end{center}
-
-  \[
-  \xymatrix{
-    & B/I_{H_m}B \ar@{..>}[dl] & B \ar@{->>}[l] \\
-    I & A/I_{H_m}A \ar@{>->}[u] \ar[l] & A \ar@{>->}[u] \ar@{->>}[l]
-    }
+  \[
+  \begin{tikzcd}
+  A \arrow[two heads]{r} \arrow[hook]{d} & A/I_{H_m}A \rar \arrow[hook]{d} & I \\
+  B \arrow[two heads]{r} & B/I_{H_m}B \arrow[dashed]{ur} & {}
+  \end{tikzcd}
   \]
@@
   $\gcs{L}^{x}\boxtimes \gcs{L}^{y}$ is defined by the following diagram.
-
+  \[
   \begin{tikzpicture}[auto,style={rectangle}]
   \node (0) at (0,0) {$\EEx$};
-  \node (1) [anchor=east] at (7,0) {$\Aut(\bf^x) \times \Aut(\bf^y)$};
-  \node (2) [anchor=west] at (7.4,0) {$\bH^x \times \bH^y$};
-  \node (3) at (12,0) {$\bG^x \times \bG^y$};
+  \node (1) [anchor=east] at (6,0) {$\Aut(\bf^x) \times \Aut(\bf^y)$};
+  \node (2) [anchor=west] at (6.4,0) {$\bH^x \times \bH^y$};
+  \node (3) at (11,0) {$\bG^x \times \bG^y$};
   \draw [->] (1) to node[swap, label] {$\psi_x \otimes \psi_y$} (0);
-  \draw [->] (7.3,-0.06) arc (330:40:0.12) -- (7.3,0.07);
+  \draw [->] (6.3,-0.06) arc (330:40:0.12) -- (6.3,0.07);
   \draw [->] (2) to node[label] {$\bf^x \tight{0}{\times}{0} \bf^y$} (3);
   \end{tikzpicture}
-
-  \[
-  \xymatrix{
-    \EEx && \ar[ll]_{\hskip-20pt \psi_x\otimes \psi_y} \Aut(\bf^x)\times \Aut(\bf^y)
-    & \ar@(ul,dl) & \bH^x\times \bH^y \ar[rr]^{\bf^x\times \bf^y} && \bG^x\times \bG^y\\
-    }
   \]
@@
 
-  \begin{tikzpicture}[auto,style={rectangle},scale=1.2]
-  \node (12) [anchor=east] at (4,2) {$\Aut(\bf^{x+y})$};
-  \node (22) [anchor=west] at (4.4,2) {$\bH^{x+y}$};
-  \node (32) [anchor=east] at (11,2) {$\bG^{x+y}$};
-  \node (01) at (0,1) {$\EEx$};
-  \node (11) [anchor=east] at (4,1) {$\Aut(\bf^{x+y})$};
-  \node (21) [anchor=west] at (4.4,1) {$\bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y$};
-  \node (31) [anchor=east] at (11,1) {$\bG^x\times \bG^y$};
+  \[
+  \begin{tikzpicture}[auto,style={shape={asymmetrical rectangle}},scale=1.2]
+  \node (12) [anchor=east] at (4,2.4) {$\Aut(\bf^{x+y})$};
+  \node (22) [anchor=west] at (4.4,2.4) {$\bH^{x+y}$};
+  \node (32) [anchor=east] at (11,2.4) {$\bG^{x+y}$};
+  \node (01) at (0,1.2) {$\EEx$};
+  \node (11) [anchor=east] at (4,1.2) {$\Aut(\bf^{x+y})$};
+  \node (21) [anchor=west] at (4.4,1.2) {$\bH^{x+y} \times_{\bG^{x+y}} (\bG^x\times\bG^y)$};
+  \node (31) [anchor=east] at (11,1.2) {$\bG^x\times \bG^y$};
   \node (10) [anchor=east] at (4,0) {$\Aut(\bf^x)\times \Aut(\bf^y)$};
-  \node (20) [anchor=west] at (4.4,0) {$\bG^x\times \bG^y$};
+  \node (20) [anchor=west] at (4.4,0) {$\bH^x\times \bH^y$};
   \node (30) [anchor=east] at (11,0) {$\bG^x\times \bG^y$};
-  \draw [->] (4.3,1.94) arc (330:40:0.12) -- (4.3,2.07);
-  \draw [->, densely dotted] (4.3,0.94) arc (330:40:0.12) -- (4.3,1.07);
+  \draw [->] (4.3,2.34) arc (330:40:0.12) -- (4.3,2.47);
+  \draw [->, densely dotted] (4.3,1.14) arc (330:40:0.12) -- (4.3,1.27);
   \draw [->] (4.3,-0.06) arc (330:40:0.12) -- (4.3,0.07);
   \draw [->] (12) to node[swap,label] {$\psi_{x+y}$} (01);
-  \draw [->, densely dotted] (11) -- (01);
+  \draw [->, dashed] (11) -- (01);
   \draw [->] (10) to node[label] {$\psi_x \otimes \psi_y$} (01);
-  \draw [->, densely dotted] ($(11.south) + (0,-0.5)$) -- (11);
+  \draw [->, dashed] ($(11.south) + (0,-0.7)$) -- (11);
   \draw [double equal sign distance] (11) -- (12);
   \draw [->] (22) to node[label] {$\bf^{x+y}$} (32);
-  \draw [->] ($(22.south) + (0,-0.5)$) -- (22);
+  \draw [->] ($(22.south) + (0,-0.7)$) -- (22);
   \draw [->] (21) -- (31);
-  \draw [->] ($(32.225) + (0,-0.5)$) to node[swap] {\footnotesize{$\bm_{x,y}$}} (32.225);
-  \draw [->] ($(22.south) + (0,-1.5)$) -- ($(22.south) + (0,-1)$);
+  \draw [->] ($(32.225) + (0,-0.7)$) to node[swap] {\footnotesize{$\bm_{x,y}$}} (32.225);
+  \draw [->] ($(22.south) + (0,-1.9)$) -- ($(22.south) + (0,-1.2)$);
   \draw [->] (20) to node[label] {$\bf^x \times \bf^y$} (30);
-  \draw [->] ($(32.225) + (0,-1.5)$) -- ($(32.225) + (0,-1)$);
+  \draw [double equal sign distance] ($(32.225) + (0,-1.9)$) -- ($(32.225) + (0,-1.2)$);
   \end{tikzpicture}
-
-  \[
-  \xymatrix{
-    & \ar[dl]_{\psi_{x+y}} \Aut(\bf^{x+y})
-    & \ar@(ul,dl) & \bH^{x+y} \ar[rr]^{\bf^{x+y}} && \bG^{x+y}\\
-    \EEx & \ar@{.>}[l] \Aut(\bf^{x+y})  \ar@{=}[u] &  \ar@{.>}@(ul,dl)
-    & \ar[u] \bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y \ar[rr]
-    && \ar[u]_{\bm_{x,y}} \bG^x\times \bG^y\\
-    & \ar[lu]_{\psi_x\otimes \psi_y} \ar@{.>}[u] \Aut(\bf^x)\times \Aut(\bf^y)
-    & \ar@(ul,dl) & \ar[u] \bH^x\times \bH^y \ar[rr]^{\bf^x\times \bf^y}
-    && \ar@{=}[u] \bG^x\times \bG^y\\
-    }
   \]
@@
   \[
-  \xymatrix{
-    && \ar[dll]_{\psi_{\Frob(x)}} \Aut(\bf^{\Frob(x)}) & \ar@(ul,dl)
-    & \bH^{\Frob(x)} \ar[rr]^{\bf^{\Frob(x)}} && \bG^{\Frob(x)}\\
-    \EEx & & \ar@{.>}[ll] \Aut(\bf^{\Frob(x)})  \ar@{=}[u] & \ar@{.>}@(ul,dl)
-    & \ar[u] \bH^{\Frob(x)} \times_{\bG^{\Frob(x)}} \bG^x \ar[rr] && \ar[u]_{\Frob_{x}} \bG^x\\
-    & &  \ar[ull]^{\psi_x}  \ar@{.>}[u] \Aut(\bf^{x}) & \ar@(ul,dl)
-    & \ar[u] \bH^x \ar[rr] && \ar@{=} [u] \bG^x\\
-    }
+  \begin{tikzpicture}[auto,style={rectangle},scale=1.2]
+  \node (12) [anchor=east] at (4,2.4) {$\Aut(\bf^{\Frob(x)})$};
+  \node (22) [anchor=west] at (4.4,2.4) {$\bH^{\Frob(x)}$};
+  \node (32) [anchor=west] at (8,2.4) {$\bG^{\Frob(x)}$};
+  \node (01) at (0,1.2) {$\EEx$};
+  \node (11) [anchor=east] at (4,1.2) {$\Aut(\bf^{\Frob(x)})$};
+  \node (21) [anchor=west] at (4.4,1.2) {$\bH^{\Frob(x)} \times_{\bG^{\Frob(x)}} \bG^x$};
+  \node (31) [anchor=west] at (8,1.2) {$\bG^x$};
+  \node (10) [anchor=east] at (4,0) {$\Aut(\bf^x)$};
+  \node (20) [anchor=west] at (4.4,0) {$\bH^x$};
+  \node (30) [anchor=west] at (8,0) {$\bG^x$};
+  \draw [->] (4.3,2.34) arc (330:40:0.12) -- (4.3,2.47);
+  \draw [->, densely dotted] (4.3,1.14) arc (330:40:0.12) -- (4.3,1.27);
+  \draw [->] (4.3,-0.06) arc (330:40:0.12) -- (4.3,0.07);
+  \draw [->] (12) to node[swap,label] {$\psi_{\Frob(x)}$} (01);
+  \draw [->, dashed] (11) -- (01);
+  \draw [->] (10) to node[label] {$\psi_x$} (01);
+  \draw [->, dashed] ($(11.south) + (0,-0.7)$) -- (11);
+  \draw [double equal sign distance] (11) -- (12);
+  \draw [->] (22) to node[label] {$\bf^{\Frob(x)}$} (32);
+  \draw [->] ($(22.225) + (0,-0.7)$) -- (22.225);
+  \draw [->] (21) -- (31);
+  \draw [->] ($(32.222) + (0,-0.7)$) to node[swap] {\footnotesize{$\Frob_x$}} (32.222);
+  \draw [->] ($(22.225) + (0,-1.9)$) -- ($(22.225) + (0,-1.2)$);
+  \draw [->] (20) -- (30);
+  \draw [double equal sign distance] ($(32.222) + (0,-1.9)$) -- ($(32.222) + (0,-1.2)$);
+  \end{tikzpicture}
   \]
@@
   \begin{equation}\label{eq:pi0}
-    \xymatrix{
-      1 \ar[r] & G^0 \ar[r] & G \ar[r] & \pi_0(G) \ar[r] & 0.
-      }
+  \begin{tikzcd}
+    1 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
+  \end{tikzcd}
   \end{equation}
@@
   \[
-  \xymatrix{
-    & \ar[d] \ker t_{\pi_0(G)} & \ar@{.>}[d] \ker t_{G} & \ar[d] \ker t_{G^0} & \\
-    0\ar[r] & \ar[d]^{t_{\pi_0(G)}} \CSiso{\pi_0(G)} \ar[r]
-    & \ar[d]^{t_{G}} \CSiso{G} \ar[r] & \ar[d]^{t_{G^0}} \CSiso{G^0} \ar[r] & 0\\
-    0 \ar[r] & \ar[d] \Hom(\pi_0(G)(\Fq),\EEx) \ar[r]
-    & \ar@{.>}[d] \Hom(G(\Fq),\EEx) \ar[r] & \ar[d] \Hom(G^0(\Fq),\EEx) \ar[r] & 0\\
-    & \coker t_{\pi_0(G)} & \coker t_{G} &  \coker t_{G^0} & \\
-    }
+  \begin{tikzcd}[row sep=30]
+    {}& \ker t_{\pi_0(G)} \dar & \arrow[dashed]{d} \ker t_{G} & \ker t_{G^0} \dar & \\
+    0 \rar & \CSiso{\pi_0(G)} \rar \dar{t_{\pi_0(G)}}
+    & \CSiso{G} \rar \dar{t_{G}} & \CSiso{G^0} \rar \dar{t_{G^0}} & 0\\
+    0 \rar & \Hom(\pi_0(G)(\Fq),\EEx) \rar \dar
+    & \arrow[dashed]{d} \Hom(G(\Fq),\EEx) \rar & \Hom(G^0(\Fq),\EEx) \rar \dar & 0\\
+    & \coker t_{\pi_0(G)} & \coker t_{G} &  \coker t_{G^0} &
+  \end{tikzcd}
   \]
@@
   \begin{equation}\label{eq:pi1}
-    \xymatrix{
-      1 \ar[r] & G^0(\Fq) \ar[r] & G(\Fq) \ar[r] & \pi_0(G)(\Fq) \ar[r] & 0;
-    }
+  \begin{tikzcd}
+    1 \rar & G^0(\Fq) \rar & G(\Fq) \rar & \pi_0(G)(\Fq) \rar & 0;
+  \end{tikzcd}
   \end{equation}
@@
 \[
-\xymatrix{
-\CS(\GN{T}) \ar[d] & \CSiso{\GN{T}} \ar[r]^{t_T} \ar[d] & \Hom_\text{ad}(T(K),\EEx) \ar[d] \\
-\CS(\GN{T}') & \CSiso{\GN{T}'} \ar[r]^{t_{T'}} & \Hom_\text{ad}(T'(K),\EEx)\\
-}
+\begin{tikzcd}
+\CS(\GN{T}) \dar & \CSiso{\GN{T}} \rar{t_T} \dar & \Hom_\text{ad}(T(K),\EEx) \dar \\
+\CS(\GN{T}') & \CSiso{\GN{T}'} \rar{t_{T'}} & \Hom_\text{ad}(T'(K),\EEx)
+\end{tikzcd}
 \]

### 2013-07-18 shanghai.tex
minor fixes

@@
 instance of those defined by George Luzstig, who coined the term, we
-begin by explaining what we mean by `character sheaves' in this
-paper. Let $G$ be a smooth commutative group scheme locally of finite
-type over $\Fq$ \David{I think our notation is clearer if we use $k$
-  rather than $\Fq$}; $G$ need not be reductive, connected, nor of
+begin by explaining what we mean by `character sheaves' here. 
+Let $G$ be a smooth commutative group scheme locally of finite
+type over $\Fq$; $G$ need not be reductive, connected, nor of
 finite type over $\Fq$. Fix a prime $\ell$ that does not divide
@@
 characters of algebraic tori over non-Archimedean local fields rests
-on the Picard group of character sheaves on $G$, for certain smooth
-group schemes $G$.
-
-We now say a few words about the commutative group schemes locally of
-finite type over $\Fq$ that appear in our geometrization of admissible
+on the Picard group of character sheaves on $G$, for all smooth
+commutative group schemes $G$, locally of finite type over $\Fq$, 
+for which the geometric component group is finitely generated.
+
+We now say a few words about the group schemes 
+that appear in our geometrization of admissible
 characters of algebraic tori over local fields. Let $K$ be a
@@
 smooth group scheme locally of finite type over $\OK$. For each
-non-negative integer $d$, let $\GN{T}_d$ be the Greenberg transform of
+positive integer $d$, let $\GN{T}_d$ be the Greenberg transform of
 $\TT \otimes \OK/\pK^d$; the commutative group scheme $\GN{T}_d$
@@
 \[
-\CSiso{\mathswab{T}_d} 
+\CSiso{\GN{T}_d} 
 \iso
@@
 between the Picard group of the category of character sheaves on
-$\mathswab{T}_d$ and the group of characters $T(K) \to \EEx$ of
+$\GN{T}_d$ and the group of characters $T(K) \to \EEx$ of
 depth at most $d$.  Since these isomorphisms are compatible with
@@
 In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated, and we will also see that \eqref{eq:pi-1} is split exact; this allows us to find $\CSiso{G}$.
-To prove this, we find it useful to offer an alternate perspective on a subcategory of $\CS(G)$, in the next section.
 
@@
 
+%We find it useful to offer an alternate perspective on a subcategory of $\CS(G)$.
 In this section we describe a full subcategory of $\CS(G)$, called the category of bounded character sheaves on $G$ and denoted by $\CS_b(G)$, which will illuminate the nature of $\CS(G)$ and will also play a role in the arguments later in this paper.

### 2013-07-18 shanghai.tex
Added the definition of bounded character sheaves.
Fundamental properties are currently under construction . . .

@@
 \newcommand{\CS}{{\mathcal{C\hskip-1.8pt S}}}
+\newcommand{\GC}{{\mathcal{G\hskip-0.8pt C}}}
 \newcommand{\CSiso}[1]{\CS(#1)_{/\textit{iso}}}
@@
 
-%We find it useful to offer an alternate perspective on a subcategory of $\CS(G)$.
-In this section we describe a full subcategory of $\CS(G)$, called the category of bounded character sheaves on $G$ and denoted by $\CS_b(G)$, which will illuminate the nature of $\CS(G)$ and will also play a role in the arguments later in this paper.
-
-In order to define $\CS_b(G)$ as must recall a fundamental fact about finite etale covers of schemes.
-Let $X$ be a scheme, locally of finite type over $k$, and let $\pi : Y\to X$ and $\pi_1: Y_1\to X$ be finite etale covers and let $f_1 : Y_1\to Y$ be a morphism such that $\pi_1 = \pi \circ f_1$.
-Then $f_1$ determines a group homomorphism $\Aut(\pi_1)\to \Aut(\pi)$, as follows  .
-.
-.
-
-Now we may define $\CS_b(G)$, where $G$ is a smooth group scheme locally of finite type over $\Fq$.
-\begin{enumerate}
-\labitem{(CSb.0)}{CSb.0}
-An object in $\CS_b(G)$ is a pair $(\pi,\psi)$ where $\pi : H\to G$ is a finite etale cover in the category of group schemes over $\Fq$ such that $\Gal(\bFq/\Fq)$ acts trivially on $\ker {\bar \pi}$ (so $\ker {\bar \pi} = \ker \pi$) and $\psi : \ker \pi \to \Aut(V)$ is an irreducible representation on a $\EE$-vector space $V$.
-\[
-\begin{tikzcd}
-V & \Aut(V) & 1 \rar & \arrow[bend right,swap]{ll}{\psi} \ker \pi \rar & H \rar{\pi} & G \rar &1
-\end{tikzcd}
-\]
-\labitem{(CSb.1)}{CSb.1}
-A morphism $T : (\pi,\psi) \to (\pi',\psi')$ is a linear transformation $T : V \to V'$ which, if non-trivial, has the property that there is a finite etale cover $\pi_1 : H_1 \to G$ in the category of group schemes over $\Fq$ and morphisms $H_1\to H$, $H_1\to H'$ inducing homomorphisms $\ker \pi_1 \to \ker\pi$ and $\ker\pi_1\to \ker\pi$ such that the following diagram commutes.
-\[
-\begin{tikzcd}
-V \arrow{dd} & \Aut(V) \ar[equal]{dd} & 1 \rar & \arrow[swap,bend left]{ll}{\psi} \ker \pi \rar & H \rar{\pi} & G \rar &1\\
- &  & 1 \rar & \ker \pi_1 \rar \uar \dar & H_1 \uar \dar \rar{\pi_1} & \ar[equal]{u} \arrow[equal]{d} G \rar &1\\
-V' & \Aut(V') & 1 \rar & \arrow[bend right]{ll}{\psi'} \ker \pi' \rar & H' \rar{\pi'} & G \rar &1
-\end{tikzcd}
-\]
-\end{enumerate}
-We refer to $\CS_b(G)$ as the category of \cdef{bounded character sheaves on $G$}.
-\Clifton{I'd love to find a way to define $\CS_b(G)$ without insisting that $\psi$ is an \emph{irreducible} representation, and then prove that the full subcategory of simple objects in $\CS_b(G)$ is a full subcategory of $\CS(G)$.
-I'm studying my notes from BIRS, letters from Masoud, and SGA7, to see how to do this.}
+In this section we describe full subcategory of $\CS(G)$, 
+called the category of bounded character sheaves on $G$ and denoted by $\CS_b(G)$, 
+which will illuminate the nature of $\CS(G)$ and will also play a role in the arguments later in this paper.
+
+Consider the category $\GC(G)$ of finite etale covers of $G$ that are also morphisms of abelian group schemes.
+Recall that we fixed an algebraic closure $\bFq$ of $\Fq$ long ago; 
+let ${\bar e} : \Spec{\bFq} \to G$ be the geometric point on $G$ obtained by composing $\Spec{\bFq} \to \Spec{\Fq}$ with the identity $e : \Spec{\Fq} \to G$ for $G$.
+Let $\ker_{\bar e}$ be the set-valued functor on $\GC(G)$
+defined by pull-back along the geometric point ${\bar e} : \Spec{\bFq} \to G$ 
+followed by forgetting the structure sheaf and topology; 
+thus, if $f : H\to G$ is a finite etale morphism of group schemes, then $\ker_{\bar e}(f)$ is the set underlying 
+$\ker{\bar f} = H_{\bar e}$.
+Let $\pi_1^\text{gp}(G)$ be the automorphism group of the functor $\ker_{\bar e}$. 
+We will see that $\pi_1^\text{gp}(G)$ is a profinite abelian group.
+A \cdef{bounded character sheaf on $G$} is a continuous irreducible representation of $\pi_1^\text{gp}(G)$. 
+Let $\CS_b(G)$ be the monoidal category of irreducible continuous $\ell$-adic representations of $\pi_1^\text{gp}(G)$.
+
 \begin{proposition}
-$\CS_b(G)$ is a full subcategory of $\CS(G)$.
+ $G\mapsto \pi_1^\text{gp}(G)$ is a functor from group schemes over $\Fq$ to profinite abelian groups, and .....
 \end{proposition}
+
+\begin{proof}
+The category $\GC(G)$, together with the set-valued functor $\ker_{\bar e}$ satisfy conditions (G1) through (G6) appearing in \cite[Exposé V, \S 4, p. 118-119]{SGA1a}.
+\end{proof}
 
@@
 
+\bib{SGA1a}{book}{
+   author={Grothendieck, Alexander},
+   title={Rev\^etements \'etales et groupe fondamental. Fasc. I: Expos\'es 1
+   \`a 5},
+   series={S\'eminaire de G\'eom\'etrie Alg\'ebrique},
+   volume={1960/61},
+   publisher={Institut des Hautes \'Etudes Scientifiques},
+   place={Paris},
+   date={1963},
+%   pages={iv+143 pp. (not consecutively paged) (loose errata)},
+%   review={\MR{0217087 (36 \#179a)}},
+}
+
 \bib{Laumon}{article}{

### 2013-07-19 shanghai.tex
Changing some margin notes

--- 2013-07-16 shanghai.tex
@@
 paper. Let $G$ be a smooth commutative group scheme locally of finite
-type over $\Fq$ \David{I think our notation is clearer if we use $k$
-  rather than $\Fq$}; $G$ need not be reductive, connected, nor of
+type over $\Fq$; $G$ need not be reductive, connected, nor of
 finite type over $\Fq$. Fix a prime $\ell$ that does not divide
@@
 depth at most $d$.  Since these isomorphisms are compatible with
-respect to $d$, we also .....  \Clifton{I'll come back to working on
-  this when we're closer to being finished. I'd be just as happy if
-  you took this cup from my lips, though.}  
+respect to $d$, we also .....  \David{I'll do this when we're closer to being finished.}  
 %In particular, by
@@
   the hypothesis that $X$ is locally of finite type over $\Fq$.
-  \Clifton{I have not proved $(f\circ g)^* = g^* \circ f^*$, yet.}
+
+  Finally, the fact that $(f\circ g)^* = g^* \circ f^*$ follows from the analogous
+  statements about pullbacks of sheaves and maps of sheaves.
+  \David{Is this explanation of $(f\circ g)^* = g^* \circ f^*$ sufficient?}
 \end{proof}
@@
 It is easy to see that $\CSiso{0}$ is trivial.
-In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated, and we will also see that \eqref{eq:pi-1} is split exact; this allows us to find $\CSiso{G}$.
+In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated, and we will also see that \eqref{eq:pi-1} is split exact \David{is it really split?}; this allows us to find $\CSiso{G}$.
 To prove this, we find it useful to offer an alternate perspective on a subcategory of $\CS(G)$, in the next section.
@@
   are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}.
-  \David{Should we move this definition since it will be important elsewhere?}
-  \Clifton{Agreed. I'll do that.}
+  \David{This section should be modified once we're done with the section on bounded character sheaves}
   Let $b : \bG \to G$ be base change
@@
 
+\David{This section needs to be modified once the bounded character sheaves section is done}
 Let $G^0$ be the connected component of $G$ containing the identity.

### 2013-07-19 shanghai.tex
Working on functoriality

--- 2013-07-18 shanghai.tex
@@
 It is easy to see that $\CSiso{0}$ is trivial.
-In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated, and we will also see that \eqref{eq:pi-1} is split exact; this allows us to find $\CSiso{G}$.
+In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; the snake lemma then allows us to find $\CSiso{G}$.
 
@@
 
+When using character sheaves to study characters, it is useful to understand
+how character sheaves behave under change of fields.
+Suppose that $k'$ is a finite extension of $k$, $G$ is an abelian group scheme
+over $k$ as in Theorem \ref{thm:snake} and $G_{k'}$ is the base change of $G$ to $k'$.
+We define a functor $\CS(G_{k'}) \to \CS(G)$ by.... \David{We can't define this by pullback
+since $G_{k'} \to G$ goes in the wrong direction}
+\begin{proposition} \label{prop:csbe}
+The diagram
+\[
+\begin{tikzcd}
+\CSiso{G_{k'}} \arrow[two heads]{r} \dar & \CSiso{G} \dar \\
+\Hom(G(k'), \EEx) \arrow[two heads]{r} & \Hom(G(k), \EEx)
+\end{tikzcd}
+\]
+commutes, where the vertical arrows are as in Theorem \ref{thm:snake}.
+\end{proposition}
+
+Now suppose that $G'$ is an abelian group scheme over $k'$, satisfying the conditions of Theorem \ref{thm:snake}.
+There is a canonical isomorphism between $G'(k')$ and $(\Res_{k'/k}G')(k)$;
+we now describe the corresponding functor from
+$\CS(G')$ to $\CS(\Res_{k'/k}G')$.  The base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
+decomposes into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
+\[
+(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
+\]
+The component corresponding to the identity element yields a natural inclusion 
+\[
+G' \hookrightarrow (\Res_{k'/k}G')_{k'}
+\]
+of $k'$-schemes.  The definition of base change yields a map of $k$-schemes
+\[
+(\Res_{k'/k}G')_{k'} \to \Res_{k'/k}G'.
+\]
+Consecutive pullback along these maps yields a functor
+\[
+\CS(G') \to \CS(\Res_{k'/k}G').
+\]
+
+\begin{proposition}
+  Then the following diagram commutes:
+\[
+\begin{tikzcd}
+\CSiso{G} \rar{t_G} \dar & \Hom(G(k'), \EEx) \dar \\
+\CSiso{\Res_{k'/k} G} \rar{t_{\Res_{k'/k} G}} & \Hom((\Res_{k'/k}G)(k), \EEx)
+\end{tikzcd}
+\]
+\end{proposition}
+
 \section{Application to characters of bounded depth}

### 2013-07-22 shanghai.tex
Added remark about actions on sheaves, and some paragraphs on the CS version of the norm map.

@@
 
+\begin{remark} \label{rem:CS-action}
+If $W$ is a group equipped with a homomorphism $\alpha : W \to \Gal(\bFq/\Fq)$
+then an \emph{action} of $W$ on $\gcs{L}$ is a collection of isomorphisms
+\[
+\gamma_w : \alpha(w)^* \gcs{L} \to \gcs{L}
+\]
+so that $\gamma_{uw} = \gamma_w \circ \alpha(w)^*\gamma_u$. \David{make sure I have the order right and add a reference}
+Specifying an $F$ as in \ref{CS.2} is the same as giving an action of the Weil group $W_k$
+on $\gcs{L}$ compatible with $\mu$.
+\end{remark}
+
 %\subsection*{Trace of Frobenius}\label{sec:Frob}
@@
 how character sheaves behave under change of fields.
-Suppose that $k'$ is a finite extension of $k$, $G$ is an abelian group scheme
+Suppose that $k'$ is a finite extension of $k$ of degree $n$, $G$ is an abelian group scheme
 over $k$ as in Theorem \ref{thm:snake} and $G_{k'}$ is the base change of $G$ to $k'$.
+If $\cs{L} = (\gcs{L}, \mu, F)$ is a character sheaf on $G$ we may define
+a character sheaf $\cs{L}_{k'} = (\gcs{L}, \mu, F_{k'})$ on $G_{k'}$ by setting
+\[
+F_{k'} = F \circ \Frob_G^*(F) \circ \cdots \circ (\Frob_G^{n-1})^*(F).
+\]
+The commutativity of the diagram (CS.2) for $F_{k'}$ follows from the fact that $\Frob_{G_{k'}} = \Frob_G^n$.
+
+\begin{proposition}
+The diagram
+\[
+\begin{tikzcd}
+\CSiso{G} \rar \dar & \CSiso{G_{k'}} \dar \\
+\Hom(G(k), \EEx) \rar & \Hom(G(k'), \EEx)
+\end{tikzcd}
+\]
+commutes, where vertical arrows are as in Theorem \ref{thm:snake}, the top arrow is as above,
+and the bottom is induced by the norm map $G(k') \to G(k)$.
+\end{proposition}
+
 We define a functor $\CS(G_{k'}) \to \CS(G)$ by.... \David{We can't define this by pullback

### 2013-07-22 shanghai.tex
Made some changes to the notation for Weil group, working on the CS version of Nm

@@
 \DeclareMathOperator{\Gal}{Gal}
-\DeclareMathOperator{\Weil}{W}
+\DeclareMathOperator{\W}{W}
 \newcommand{\Frob}{{\operatorname{Fr}}}
@@
 \DeclareMathOperator{\Res}{Res}
+\DeclareMathOperator{\Nm}{Nm}
 
@@
 \newcommand{\image}{{\operatorname{im}}}
+\newcommand{\Weil}[1]{\mathcal{W}_{#1}}
 
@@
 so that $\gamma_{uw} = \gamma_w \circ \alpha(w)^*\gamma_u$. \David{make sure I have the order right and add a reference}
-Specifying an $F$ as in \ref{CS.2} is the same as giving an action of the Weil group $W_k$
+Specifying an $F$ as in \ref{CS.2} is the same as giving an action of the Weil group $\Weil{k}$
 on $\gcs{L}$ compatible with $\mu$.
@@
   an equivalence between the category of Weil local systems on $G$ and
-  $\ell$-adic representations of $\Weil(G,\bg)$
+  $\ell$-adic representations of $\W(G,\bg)$
   \cite{Deligne:Weil2}*{1.1.12}. Now let $(\gcs{L},\mu,F)$ be a
@@
   system $(\gcs{L},F)$ corresponds to an $\ell$-adic character of the
-  Weil group $\Weil(G, \bg)$. The $\Fq$-rational point $g$ under
+  Weil group $\W(G, \bg)$. The $\Fq$-rational point $g$ under
   the geometric point $\bg$ determines a splitting
-  $\Weil(\bFq/\Fq)\to \Weil(G,\bg)$ of the exact sequence
+  $\Weil{\Fq}\to \W(G,\bg)$ of the exact sequence
   \[
   \begin{tikzcd}
-  1 \rar & \pi_1(\bG, \bg) \rar &  \Weil(G,\bg) \rar
-  & \ar[swap,bend right, dotted]{l}{g} \Weil(\bFq/\Fq) \rar & 1
+  1 \rar & \pi_1(\bG, \bg) \rar &  \W(G,\bg) \rar
+  & \ar[swap,bend right, dotted]{l}{g} \Weil{\Fq} \rar & 1
   \end{tikzcd}
@@
   \[
-  t_{(\gcs{L},F)}(g) : \Weil(\bFq/\Fq) \to \EEx \qquad \text{defined by}\qquad \Frob \mapsto t^\Frob_{(\gcs{L},F)}(g)
-  \]
-  of the Weil group $\Weil(\bFq/\Fq)$; the image of $\Frob$ under this
+  t_{(\gcs{L},F)}(g) : \Weil{\Fq} \to \EEx \qquad \text{defined by}\qquad \Frob \mapsto t^\Frob_{(\gcs{L},F)}(g)
+  \]
+  of the Weil group $\Weil{\Fq}$; the image of $\Frob$ under this
   character is $t^\Frob_\cs{L}(g)$, the trace of Frobenius of $\cs{L}$ at $g$.
@@
   it follows that $t^\Frob_\cs{L}(g) = t^\Frob_{(\gcs{L},F)}(g)$ is a root of unity,
-  for every $g\in G(\Fq)$.  Since $\Weil(\bFq/\Fq)$ is generated by
-  $\Frob$ and $t_{(\gcs{L},F)}(g) : \Weil(\bFq/\Fq) \to \EEx$ is
+  for every $g\in G(\Fq)$.  Since $\Weil{\Fq}$ is generated by
+  $\Frob$ and $t_{(\gcs{L},F)}(g) : \Weil{\Fq} \to \EEx$ is
   a character, it follows that the image of $t_{(\gcs{L},F)}(g)$ is a
@@
   \begin{tikzcd}
-  1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \Weil(G,\bg) \rar \dar & \Weil(\bFq/\Fq) \rar \dar & 1\\
+  1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \W(G,\bg) \rar \dar & \Weil{\Fq} \rar \dar & 1\\
   1 \rar &  \pi_1(\bG, \bg) \rar & \pi_1(G,\bg) \rar & \Gal(\bFq/\Fq) \rar & 1
@@
   \[
-  \CSiso{G} \longrightarrow \Hh^1(\Weil(\bFq/\Fq), \Hom_\text{grp}(G(\bFq),\EEx)),
+  \CSiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, \Hom_\text{grp}(G(\bFq),\EEx)),
   \qquad \text{given by}\qquad
@@
   \]
-  where $t_\cs{L}: \Weil(\bFq/\Fq)\to \Hom_\text{grp}(G(\bFq),\EEx)$ is a cocycle such that
+  where $t_\cs{L}: \Weil{\Fq}\to \Hom_\text{grp}(G(\bFq),\EEx)$ is a cocycle such that
   \[
@@
 \begin{proof}
-  To simplify notation, we set $W_\Fq \ceq \Weil(\bFq/\Fq)$ and
+  To simplify notation, we set
   $G(\bFq)^* \ceq \Hom_\text{grp}(G(\bFq),\EEx)$.  Recall the
@@
   proposition by exhibiting an isomorphism between
-  $\CSiso{G(\bFq)}$ and $\Hh^1(W_{\Fq}, G(\bFq)^*)$.
+  $\CSiso{G(\bFq)}$ and $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
 
   To produce the isomorphism between $\CSiso{G(\bFq)}$ and
-  $\Hh^1(W_{\Fq}, G(\bFq)^*)$ we must pick a global section of the line
+  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ we must pick a global section of the line
   bundle $(\gcs{L},\mu)$, for each character sheaf $\cs{L}$ on $G$. We
@@
 
-  We use the section $s_\cs{L}$ to define a cocycle $z_\cs{L} \in Z^1(W_\Fq,G(\bFq)^*)$
+  We use the section $s_\cs{L}$ to define a cocycle $z_\cs{L} \in Z^1(\Weil{\Fq},G(\bFq)^*)$
   as follows. Recall that $\cs{L}$ also determines a family of linear transformations
@@
 
-  Now $t_\cs{L} : W_\Fq \to G(\bFq)^*$ is defined, recursively, by
+  Now $t_\cs{L} : \Weil{\Fq} \to G(\bFq)^*$ is defined, recursively, by
   $t_\cs{L}(\Frob^n) \ceq t_\cs{L}(\Frob)\cdot \,^\Frob t_\cs{L}(\Frob^{n-1})$,
@@
   \[
-  \obj \CS(G(\bFq)) \longrightarrow Z^1(W_\Fq,G(\bFq)^*),
+  \obj \CS(G(\bFq)) \longrightarrow Z^1(\Weil{\Fq},G(\bFq)^*),
   \qquad \text{defined by} \qquad \cs{L} \mapsto t_\cs{L}.
@@
   condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so
-  $a\in G(\bFq)^*$. Now consider the coboundary $t_0 : W_\Fq \to G(\bFq)^*$
+  $a\in G(\bFq)^*$. Now consider the coboundary $t_0 : \Weil{\Fq} \to G(\bFq)^*$
   defined by $t_0(\Frob) = \,^\Frob a \cdot a^{-1}$. Then $t_2 = t_0 t_1$,
@@
   \begin{equation}\label{cohomologous}
-    \obj \CS(G(\bFq)) \longrightarrow \Hh^1(W_\Fq,G(\bFq)^*),
+    \obj \CS(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
     \qquad \text{defined by} \qquad \cs{L} \mapsto [t_\cs{L}],
@@
 
-  We now show that the function $\obj \CS(G(\bFq)) \longrightarrow \Hh^1(W_\Fq,G(\bFq)^*)$
+  We now show that the function $\obj \CS(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*)$
   factors through $\obj \CS(G(\bFq)) \to \CSiso{G(\bFq)}$.
@@
   \begin{equation}\label{pich1}
-    \CSiso{G(\bFq} \longrightarrow \Hh^1(W_\Fq,G(\bFq)^*),
+    \CSiso{G(\bFq} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
     \qquad \text{defined by} \qquad [\cs{L}] \mapsto [t_\cs{L}].
@@
 %\input{etale-2}
-%Define $\rho \colon \Hh^1(W_{\Fq}, \Hom(G(\bFq), \EEx))
+%Define $\rho \colon \Hh^1(\Weil{\Fq}, \Hom(G(\bFq), \EEx))
 % \rightarrow \Hom(G(\Fq), \EEx)$ by $\rho(\phi)(g) =
@@
 If $\cs{L} = (\gcs{L}, \mu, F)$ is a character sheaf on $G$ we may define
-a character sheaf $\cs{L}_{k'} = (\gcs{L}, \mu, F_{k'})$ on $G_{k'}$ by setting
+a character sheaf $\nu(\cs{L}) = (\gcs{L}, \mu, F_{k'})$ on $G_{k'}$ by setting
 \[
@@
 The commutativity of the diagram (CS.2) for $F_{k'}$ follows from the fact that $\Frob_{G_{k'}} = \Frob_G^n$.
+Note that we may also think about the construction of $F_{k'}$ as taking the action of $\Weil{k}$ defined in Remark
+\ref{rem:CS-action} and restricting it to $\Weil{k'}$.
 
 \begin{proposition}
-The diagram
+The following diagram commutes:
 \[
 \begin{tikzcd}
-\CSiso{G} \rar \dar & \CSiso{G_{k'}} \dar \\
-\Hom(G(k), \EEx) \rar & \Hom(G(k'), \EEx)
-\end{tikzcd}
-\]
-commutes, where vertical arrows are as in Theorem \ref{thm:snake}, the top arrow is as above,
-and the bottom is induced by the norm map $G(k') \to G(k)$.
+\CSiso{G} \rar{\nu} \dar{t_G} & \CSiso{G_{k'}} \dar{t_{G_{k'}}} \\
+\Hom(G(k), \EEx) \rar{\Nm} & \Hom(G(k'), \EEx).
+\end{tikzcd}
+\]
 \end{proposition}

### 2013-07-23 shanghai.tex
Working on diagrams for base change

@@
 \begin{proposition}
-The following diagram commutes:
+The following diagram commutes, where the bottom map is induced by the norm $G(k') \rightarrow G(k)$:
 \[
@@
 
-We define a functor $\CS(G_{k'}) \to \CS(G)$ by.... \David{We can't define this by pullback
-since $G_{k'} \to G$ goes in the wrong direction}
+In the opposite direction, there is a canonical closed immersion of $k$-schemes
+$G \hookrightarrow \Res_{k'/k}(G_{k'})$ \cite[\S 7.6]{BLR}.  Pullback yields a functor
+\[
+\CS(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota} \CS(G).
+\]
 \begin{proposition} \label{prop:csbe}
-The diagram
+The following diagram commutes, where the bottom map is induced by the inclusion $G(k) \hookrightarrow G(k')$:
 \[
 \begin{tikzcd}
-\CSiso{G_{k'}} \arrow[two heads]{r} \dar & \CSiso{G} \dar \\
-\Hom(G(k'), \EEx) \arrow[two heads]{r} & \Hom(G(k), \EEx)
-\end{tikzcd}
-\]
-commutes, where the vertical arrows are as in Theorem \ref{thm:snake}.
+\CSiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota} \dar{t_{\Res_{k'/k}(G_{k'})}} & \CSiso{G} \dar{t_G} \\
+\Hom(G(k'), \EEx) \arrow[two heads]{r} & \Hom(G(k), \EEx).
+\end{tikzcd}
+\]
 \end{proposition}
@@
 \begin{tikzcd}
-\CSiso{G} \rar{t_G} \dar & \Hom(G(k'), \EEx) \dar \\
-\CSiso{\Res_{k'/k} G} \rar{t_{\Res_{k'/k} G}} & \Hom((\Res_{k'/k}G)(k), \EEx)
+\CSiso{G'} \dar{t_{G'}} \rar & \CSiso{\Res_{k'/k} G'} \dar{t_{\Res_{k'/k} G'}} \\
+ \Hom(G'(k'), \EEx) \rar & \Hom((\Res_{k'/k}G')(k), \EEx)
 \end{tikzcd}

### 2013-07-27 shanghai.tex
Working on base change for Gr(Neron)

@@
 \newcommand{\pK}{\mathfrak{p}_K}
+\newcommand{\OL}{\mathcal{O}_L}
 \newcommand{\Zp}{\mathbb{Z}_p}
@@
 \newcommand{\TT}{\underline{T}}
+\newcommand{\TL}{\underline{T_L}}
 \newcommand{\invlim}[1]{\lim\limits_{\overleftarrow{#1}}}
@@
 
-Let $\GN{T}_{d}$ be the group scheme over $\Fq$ produced by applying
+Let $\GN{T}_{d} = \Gr(\TT_d)$ be the group scheme over $\Fq$ produced by applying
 the Greenberg functor to $\TT_{d}$. (See \cite{Greenberg:2} and
@@
 \end{equation}
-This is the \cdef{Greenberg transform of the lft-N\'eron model of $T$}.
+This is the \cdef{Greenberg transform of the lft-N\'eron model of $T$}; we will also write $\Gr$ for this functor on $\OK$-schemes.
 
@@
 
+Let $L/K$ be a finite Galois extension and let $K'/K$ be the maximal unramified subextension, with residue field $k'$.
+If $T$ is a torus over $K$, write $\TL$ for the N\'eron model of the base change $T_L$.
+Then there is a canonical isomorphism
+\[
+\Res_{k'/k} \Gr(\TL) \cong \Gr(\underline{\Res_{L/K}(T_L)}).
+\]
+The natural inclusion $T \hookrightarrow \Res_{L/K} T_L$ induces a map of $k$-schemes
+\[
+\GN{T} \hookrightarrow \Res_{k'/k} \Gr(\TL)
+\]
+and thus a map on character sheaves.
+
 \begin{proposition}
-Let $K'/K$ be a finite Galois extension and let $T'$ be an algebraic torus over $K'$... 
-\Clifton{This next part is very much under construction.}
-The functor $\CS(\GN{T}) \to \CS(\GN{T}')$ defined above induces a group homomorphism 
-that commutes, through trace of Frobenius, with ...
-\[
-\begin{tikzcd}
-\CS(\GN{T}) \dar & \CSiso{\GN{T}} \rar{t_T} \dar & \Hom_\text{ad}(T(K),\EEx) \dar \\
-\CS(\GN{T}') & \CSiso{\GN{T}'} \rar{t_{T'}} & \Hom_\text{ad}(T'(K),\EEx)
+The following diagram commutes:
+\[
+\begin{tikzcd}
+\CSiso{\Res_{k'/k} \Gr(\TL)} \arrow[two heads]{r} \dar & \CSiso{\GN{T}} \dar\\
+\Hom(T(L), \EEx) \arrow[two heads]{r} & \Hom(T(K), \EEx)
 \end{tikzcd}
@@
 
-\begin{proof}
-\end{proof}
+We now translate the norm map $T(L) \to T(K)$ to character sheaves.  There is an open immersion
+\[
+\TT \times_{\OK} \OL \to \TL
+\]
+induced by the canonical isomorphism of generic fibers \cite[p. 1]{Chai}.  After taking Greenberg transforms,
+we obtain a diagram
+\[
+\begin{tikzcd}
+\Gr(\TT) \dar & \Gr(\TT) \times_{\Gr(\OK)} \Gr(\OL) \lar{\alpha} \rar{\beta} \dar & \Gr(\TL) \dar \\
+\Spec{k} & \Spec{k'} \lar \rar & \Spec{k'}
+\end{tikzcd}
+\]
+In the case that $L/K$ is unramified, the left hand square is a pullback square and the right hand horizontal maps are isomorphisms.  In general, we may define a functor
+\begin{align*}
+\CS(\GN{T}) &\to \CS(\Gr(\TL)) \\
+\cs{L} &\mapsto \beta_* \alpha^* \cs{L}.
+\end{align*}
+
+\begin{proposition}
+The following diagram commutes:
+\[
+\begin{tikzcd}
+\CSiso{\GN{T}} \rar{\beta_* \circ \alpha^*} \dar & \CSiso{\Gr(\TL)} \dar \\
+\Hom(T(K), \EEx) \rar{\Nm} & \Hom(T(L), \EEx)
+\end{tikzcd}
+\]
+\end{proposition}
 
@@
 
+\bib{Chai}{article}{
+   author={Chai, C.L.},
+   title={N\'eron models for semiabelian varieties: congruence and change of base field.},
+   journal={Asian J. Math.},
+   volume={4},
+   number={4},
+   date={2000},
+   pages={715--736}}
+
 \bib{Deligne:tensorielles}{article}{

### 2013-07-30 base change.tex
Moved base change discussion to a new file

--- 2013-07-27 shanghai.tex
@@
 \documentclass[11pt]{amsart}
-\title[Geometration of characters of tori]{Geometrization of characters of tori over non-Archimedean local fields}
+\title[Geometrization leftovers]{Geometrization leftovers}
 \usepackage[british]{babel}
@@
 \newcommand{\OL}{\mathcal{O}_L}
+\newcommand{\OO}[1]{\mathcal{O}_{#1}}
 \newcommand{\Zp}{\mathbb{Z}_p}
@@
 \newcommand{\Weil}[1]{\mathcal{W}_{#1}}
+\newcommand{\level}[1]{(\mathrm{level} N)}
 
@@
 
-\begin{abstract}
-  We study the category of character sheaves on smooth commutative
-  group schemes $G$ locally of finite type over finite fields
-  $\Fq$. Assuming that the geometric component group of $G$
-  is finitely-generated, we show that the group of isomorphism classes
-  of character sheaves on $G$ is canonically isomorphic to the group
-  of characters of $G(\Fq)$. We use this result to exhibit an
-  isomorphism between admissible characters of $T(K)$ and isomorphism
-  classes of character sheaves on the Greenberg transform of the Néron
-  model of $T$, where $K$ is any non-Archimdean local field and $T$ is
-  any algebraic torus over $K$.
-\end{abstract}
-
-\maketitle
-
-\section{Introduction}
-
-%\input{introduction}
-%In his celebrated thesis, John Tate writes 
-%\begin{quotation}
-%    {\it Concerning the characters of $k^*$ [the
-%    multiplicative group of a $\mathfrak{p}$-adic field], the
-%    situation is different from that of $k^+$.  First of all, we are
-%    interested in continuous multiplicative maps $\alpha \mapsto
-%    c(\alpha)$ of $k^*$ into the complex numbers, not only in the
-%    bounded ones, and shall call such a map a quasi-character,
-%    reserving the word ``character'' for the conventional character of
-%    absolute value $1$. Secondly, we shall find no model for the group
-%    of quasi-characters, or even for the group of characters, though
-%    such a model would be of the utmost importance.}
-%  \cite{Tate:thesis}*{\S 2.3}
-%\end{quotation}
-%\noindent
-In this paper we show that the monidal category of character sheaves
-on the Greenberg transform of the locally finite type Neron model of
-$T$ provides an elegant, canonical model for the group of
-(quasi-)characters of $T(K)$, where $K$ is any non-Archimedean local
-field and $T$ is any algebraic torus over $K$.
-
-Since the character sheaves that appear in this paper are not quite an
-instance of those defined by George Luzstig, who coined the term, we
-begin by explaining what we mean by `character sheaves' here. 
-Let $G$ be a smooth commutative group scheme locally of finite
-type over $\Fq$; $G$ need not be reductive, connected, nor of
-finite type over $\Fq$. Fix a prime $\ell$ that does not divide
-$q$. By a {character sheaf} on $G$ we mean a triple $\cs{L}\ceq
-(\gcs{L},\mu,F)$ where $\gcs{L}$ is a constructible $\ell$-adic sheaf
-$\gcs{L}$ on the \'etale site of $\bG \ceq G \times_{\Spec\Fq}
-\Spec{\bFq}$, locally constant of rank-$1$ on every connected
-component of $\bG$, equipped with an isomorphism $\mu: m^*
-\gcs{L} \to \LxL$, where $m : \GxG \to G$ is
-the group operation for $G$, and an isomorphism $F : \Frob_{G}^*
-\gcs{L} \to \gcs{L}$, where $\Frob_{G}$ is the Frobenius automorphism
-on $\bG$, satisfying natural compatibility conditions with $\mu$;
-these compatibility conditions are explained below.
-
-Character sheaves on $G$ form a category, denoted by $\CS(G)$. In
-fact, $\CS(G)$ is a rigid symmetric monoidal category, so isomorphism
-classes of character sheaves on $G$ form a group, denoted by
-$\CSiso{G}$; this is the Picard group of the category of
-character sheaves on $G$. Our application of character sheaves to
-characters of algebraic tori over non-Archimedean local fields rests
-on the Picard group of character sheaves on $G$, for all smooth
-commutative group schemes $G$, locally of finite type over $\Fq$, 
-for which the geometric component group is finitely generated.
-
-We now say a few words about the group schemes 
-that appear in our geometrization of admissible
-characters of algebraic tori over local fields. Let $K$ be a
-non-Archimedean local field with residual field $\Fq$; we place no
-restrictions on the characteristic of $K$ -- in particular, it may be
-$0$ or not. Write $\OK$ for ring of integers of $K$ and $\pK$ for the
-maximal ideal in $\OK$.  Let $T$ be an algebraic torus defined over
-$K$. Let $\TT$ be a N\'eron model for $T$; recall that this is a
-smooth group scheme locally of finite type over $\OK$. For each
-positive integer $d$, let $\GN{T}_d$ be the Greenberg transform of
-$\TT \otimes \OK/\pK^d$; the commutative group scheme $\GN{T}_d$
-plays the r\^{o}le of $G$, above.
-
-The main result of this paper is a canonical isomorphism
-\[
-\CSiso{\GN{T}_d} 
-\iso
-\Hom_{< d}(T(K),\EEx)
-\] 
-between the Picard group of the category of character sheaves on
-$\GN{T}_d$ and the group of characters $T(K) \to \EEx$ of
-depth at most $d$.  Since these isomorphisms are compatible with
-respect to $d$, we also .....  \David{I'll do this when we're closer to being finished.}  
-%In particular, by
-%specializing to the case $T= \Gm{K}$ and by
-%choosing an isomorphism $\EE \approx \CC$ (unnatural though it may
-%be), we arrive at a model for the group of quasi-characters of
-%$K^\times$: the monoidal category of character sheaves on the
-%Greenberg transform of the Neron model of
-%$\Gm{K}$.
-
-Structure of the paper:
-
-Thanks to:
-
-\tableofcontents
-
-\section{The Picard group of character sheaves}\label{section:category}
-
-%\input{category}
-%\subsection*{Smooth commutative group schemes}
-
-Throughout this paper, $G$ stands for a commutative group scheme,
-smooth and locally of finite type over a finite field $\Fq$; we write
-$m : \GxG\to G$ for the multiplication morphism. We fix an
-algebraic closure $\bFq$ of $\Fq$ and write $\bG $ for the
-commutative group scheme, smooth and locally of finite type over
-$\bFq$ obtained by base change; the multiplication morphism for
-$\bG$ will be denoted by $\bm$. Let $\Frob_{G}$
-(resp. $\Frob_{\GxxG}$) be the Frobenius automorphism of
-$\bG$ (resp. $\bGxG$).
-\Clifton{I'll insert a reference to SGA where Frobenius is defined for
-  a large class of schemes over finite fields.}
-
-%\subsection*{The category of character sheaves}
-
-The category of character sheaves on $G$, denoted by \cdef{$\CS(G)$},
-is defined as follows.  A \cdef{character sheaf} on $G$ is a triple
-$\cs{L}\ceq (\gcs{L},\mu,F)$ where:
-\begin{enumerate}
-\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a constructible $\ell$-adic
-  sheaf on (the \'etale site of) $\bG$, locally constant of rank
-  $1$ on connected components of $\bG$;
-
-\labitem{(CS.1)}{CS.1} $\mu: \bm^* \gcs{L} \to \LxL$
-  is an isomorphism of sheaves on $\bGxG$ such that
-
-  \[
-  \begin{tikzcd}[row sep=40]
-  \bm_3^*\gcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
-    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
-    \gcs{L} \boxtimes \bm^* \gcs{L} \arrow{rr}{\id \boxtimes \mu}
-    &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL\\
-  \end{tikzcd}
-  \]
-  commutes, where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
-
-\labitem{(CS.2)}{CS.2} $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ is an
-  isomorphism of sheaves on $\bG$ compatible with $\mu$ in the sense that
-
-  \[
-  \begin{tikzcd}
-  \Frob_{\GxxG}^* \bm^* \gcs{L} \arrow{rr}{\Frob_{\GxxG}^*\mu}
-    && \Frob_{\GxxG}^*(\LxL)\\
-    \arrow[equal]{u} \bm^*  \Frob_{G}^* \gcs{L} \arrow[swap]{d}{\bm^* F}
-    && \Frob_{G}^*\gcs{L}\boxtimes \Frob_{G}^*\gcs{L} \dar{F\boxtimes F} \arrow[equal]{u} \\
-    \bm^*\gcs{L} \arrow{rr}{\mu}
-    && \LxL\\
-  \end{tikzcd}
-  \]
-  commutes.
-\end{enumerate}
-Morphisms in $\CS(G)$ are defined in the natural way:
-\begin{enumerate}
-\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,F)$ and
-  $\cs{L'} = (\gcs{L'},\mu',F')$ are character sheaves on $G$ then
-  $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$
-  of constructible $\ell$-adic sheaves on $\bG$ such that
-  \[
-  \begin{tikzcd}[column sep=40]
-  \Frob_G^* \gcs{L} \rar{\Frob_G^* \varphi} \arrow[swap]{d}{F} & \Frob_G^* \gcs{L'} \dar{F'}
-  & \arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} & \arrow[swap]{d}{\mu} m^* \gcs{L} \rar{m^* \varphi} & m^* \gcs{L'} \dar{\mu'} \\
-  \gcs{L} \rar{\varphi} & \gcs{L'}
-  & {} & \LxL \rar{\tight{1}{\varphi\boxtimes \varphi}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
-  \end{tikzcd}
-  \]
-  both commute.
-\end{enumerate}
-
-%\subsection*{The Picard group of character sheaves}
-
-%\begin{proposition}\label{tensor}
-The category $\CS(G)$ of character sheaves on $G$ is a rigid monoidal
-category [insert reference] under
-$\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', F\otimes F')$
-with duals formed by applying the functor $\sheafHom(\ - \ ,(\EE)_{\bG})$ to
-conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}.
-%\end{proposition}
-(The category of characters sheaves on $G$ is not abelian, so $\CS(G)$
-is not a tensor category in the sense of \cite{Deligne:tensorielles}.)
-%\begin{proof}\end{proof}
-%
-This rigid monoidal category structure for $\CS(G)$ puts a group
-structure on the set $\CSiso{G}$ of isomorphism classes in
-$\CS(G)$; we refer to this as the \cdef{Picard group} of character
-sheaves on $G$; {\it cf.} {\tt http://ncatlab.org/nlab/show/Picard+group}.
-\Clifton{Replace ncatlab with other references.}
-
-\begin{remark} \label{rem:CS-action}
-If $W$ is a group equipped with a homomorphism $\alpha : W \to \Gal(\bFq/\Fq)$
-then an \emph{action} of $W$ on $\gcs{L}$ is a collection of isomorphisms
-\[
-\gamma_w : \alpha(w)^* \gcs{L} \to \gcs{L}
-\]
-so that $\gamma_{uw} = \gamma_w \circ \alpha(w)^*\gamma_u$. \David{make sure I have the order right and add a reference}
-Specifying an $F$ as in \ref{CS.2} is the same as giving an action of the Weil group $\Weil{k}$
-on $\gcs{L}$ compatible with $\mu$.
-\end{remark}
-
-%\subsection*{Trace of Frobenius}\label{sec:Frob}
-
-Let $\cs{L}$ be a character sheaf on $G$. Every $g\in G(\Fq)$
-determines a point $\bg$ on $\bG$ fixed by $\Frob_G$ and
-therefore an automorphism $F_{\bg}$ of $\gcs{L}_{\bg}$. Note
-that $\Aut_{\EE}(\gcs{L}_{\bg}) \iso \EEx$, canonically (this
-follows from second condition appearing in the definition of character
-sheaves). The isomorphism $\mu : \bm^* \gcs{L} \to \LxL$
-guarantees that the function $t^\Frob_\cs{L} : G(\Fq)\to \EEx$,
-defined by $g \mapsto F_{\bg}$, is a group homomorphism;
-we refer to $t^\Frob_\cs{L}$ as the \cdef{trace of Frobenius of $\cs{L}$}.
-\Clifton{There is no actual trace involved, since $\gcs{L}$ is a rank
-  $1$ local system. More generally, trace is needed.}
-
-It is clear that $t^\Frob_{\cs{L}\otimes \cs{L'}} = t^\Frob_\cs{L} \cdot t^\Frob_\cs{L'}$
-(pointwise multiplication of functions) and that $t^\Frob_\cs{L} = t^\Frob_\cs{L'}$
-if $\cs{L} \iso \cs{L'}$ in $\CS(G)$. In this way we obtain a group homomorphism
-\[
-\cdef{t_{G}} : \CSiso{G} \longrightarrow \Hom_\text{grp}(G(\Fq),\EEx),
-\qquad \text{defined by}\qquad \cs{L} \mapsto t^\Frob_\cs{L},
-\]
-from the Picard group of character sheaves on $G$ to the character group of $G(\Fq)$.
-
-Our main result on the geometrization of admissible characters of
-$p$-adic tori [insert internal reference here] follows from a general
-fact established later in this paper: if the geometric component group
-of $G$ is finitely-generated then the trace of Frobenius defines an
-isomorphism from the Picard group of character sheaves $G$ to the
-group of characters of $G(\Fq)$ (here, as throughout the paper, $G$ is
-a commutative group scheme, smooth and locally of finite type over $\Fq$).
-
-%\subsection*{Pull-back of character sheaves}\label{subsection:pullback}
-
-\begin{proposition}\label{prop:pullback}
-  If $f : H\to G$ is a morphism of commutative group schemes locally of finite type over $\Fq$ then
-  $(\gcs{L},\mu,F) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
-  defines a monoidal functor $f^* : \CS(G) \to \CS(H)$ such that
-  \[
-  \begin{tikzcd}[row sep=40]
-   \CSiso{G} \rar{f^*} \arrow[swap]{d}{t_{G}} & \CSiso{H} \dar{t_H} \\
-  \Hom_\text{grp}(G(\Fq),\EEx) \rar & \Hom_\text{grp}(H(\Fq),\EEx)
-  \end{tikzcd}
-  \]
-  is a commutative diagram of groups, where the lower homomorphism is
-  dual to $f : H(\Fq)\to G(\Fq)$.  Moreover, $(f\circ g)^* = g^* \circ f^*$.
-\end{proposition}
-
-\begin{proof}
-  Let $\cs{L}$ be a character sheaf on $G$. We start by showing that
-  $\bf^*\gcs{L}$ is locally constant on connected components of
-  $\bH$. Let $c_j :\bH^j \hookrightarrow \bH$ be any
-  connected component and let $i$ be the image of $j$ under the group
-  homomorphism $\pi_0(\bG) \to \pi_0(\bH)$ obtained by
-  applying the functor $\pi_0$ to $\bf$; see \cite{vdG&M}*{III, 3.28}, for example.
-  \Clifton{Replace with a better reference, eventually.}
-  Write $c_i : \bG^i \hookrightarrow \bG$ for
-  the inclusion of $\bG^i$ and $\bf^j : \bH^j \to \bG^i$
-  for the restriction of $f$ to $\bH^j$.  Since $\cs{L}$
-  is a character sheaf, $\gcs{L}$ is locally constant on the connect
-  components of $\bG$; thus, there is a finite etale covering
-  $a_i : X_i \to \bG^i$ such that $a_i^* (\gcs{L}\vert_{\bG^i})$
-  is constant. Let $b_j : Y_j \to \bH^j$ be the
-  pull-back of $a_i$ along $\bf^j$; let $g_j : Y_j \to X_i$ be
-  the map opposite $\bf^j$. Then $b_j$ is a finite etale covering
-  of $\bH^j$ and
-  \[
-  b_j^* \left( (\bf^* \gcs{L})\vert_{\bH^j}\right)
-  = (\bf\circ c_j \circ b_j)^*\gcs{L}
-  = (c_i\circ a_i\circ g_j)^*\gcs{L} = g_j^* a_i^* (\gcs{L}\vert_{\bG^i}).
-  \]
-
-  Since $a_i^* (\gcs{L}\vert_{\bG^i})$ is a constant sheaf and since the pull-back
-  of a constant sheaf (along $g_j$, in this case) is a constant sheaf,
-  it follows that $b_j^* \left( (\bf^*\gcs{L})\vert_{\bH^j}\right)$
-  is a constant sheaf. Thus, $\bf^*\gcs{L}$ is locally constant on
-  $\bH^j$. Since $(\bf^*\gcs{L})_{\bg} = \gcs{L}_{f(\bg)}$ for every
-  geometric point ${\bg}$ on $\bG$, and since $\gcs{L}$ has
-  rank $1$ on connected components of $\bG$, it follows that
-  $f^*\gcs{L}$ also has rank $1$ on connected components of $\bG$.
-  This completes the proof that $\bf^*\gcs{L}$ satisfies condition \ref{CS.0}.
-
-  To see that $(\bfxf)^* \gcs{L}$ satisfies
-  condition \ref{CS.1} simply apply the functor $(\bfxf)^*$
-  to \ref{CS.1} for $\cs{L}$ and use the canonical isomorphism
-  $(\bfxf)^*(\LxL) \iso \bf^*\gcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gcs{L}$
-  (a few times). Likewise, to see that $\bf^*\gcs{L}$ satisfies condition
-  \ref{CS.2}, apply the same functor to \ref{CS.2} for $\gcs{L}$.
-  Then use the fact that $f$ is defined over $\Fq$, so
-  $(\bfxf)^*\Frob_{\GxxG}^* \iso \Frob_{\GxxG} (\bfxf)^*$,
-  and the fact that $f$ is a morphism of group schemes, so
-  $(\bfxf)^* \bm^*\iso \bm^* \bf^*$
-  (isomorphisms of functors on constructible sheaves).
-
-  To see that $(\gcs{L},\mu,F) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
-  defines a functor $f^* : \CS(G) \to \CS(H)$ one applies the functors $\bf^*$ and
-  $\bf^*\tight{1}{\times}{1}\bf^*$ to \ref{CS.3} and argue as
-  above. It follows from the fact that sheaf hom commutes with these
-  functors that $f^* : \CS(G) \to \CS(H)$ is a monoidal functor.
-
-  The fact that the functor $f^* : \CS(G) \to \CS(H)$ commutes with
-  the trace of Frobenius, in the sense above, follows immediately from
-  the definitions; see \cite{Laumon}*{1.1.1.2}, where the ambient
-  hypothesis that $X$ is of finite type over $\Fq$ can be replaced by
-  the hypothesis that $X$ is locally of finite type over $\Fq$.
-
-  Finally, the fact that $(f\circ g)^* = g^* \circ f^*$ follows from the analogous
-  statements about pullbacks of sheaves and maps of sheaves.
-  \David{Is this explanation of $(f\circ g)^* = g^* \circ f^*$ sufficient?}
-\end{proof}
-
-Consider the short exact sequence in the category of smooth group
-schemes, locally of finite type over $\Fq$, defining the component
-group scheme for $G$:
-\begin{equation}\label{eq:pi-2}
-\begin{tikzcd}
-0 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
-\end{tikzcd}
-\end{equation}
-Since $\pi_0(G)$ is an Abelian group scheme, smooth (in fact, etale) and locally of finite type over $\Fq$, 
-it follows from Proposition~\ref{prop:pullback} that \eqref{eq:pi-1} defines a sequence of functors
-\[
-\begin{tikzcd}
-\CS(0) \rar & \CS(\pi_0(G)) \rar & \CS(G) \rar & \CS(G^0) \rar & \CS(0)
-\end{tikzcd}
-\]
-which induces, upon passage to Picard groups, a sequence of group homomorphisms 
-\begin{equation}\label{eq:pi-1}
-\begin{tikzcd}
-\CSiso{0} \rar & \CSiso{\pi_0(G)} \rar & \CSiso{G} \rar & \CSiso{G^0} \rar & \CSiso{0}.
-\end{tikzcd}
-\end{equation}
-It is easy to see that $\CSiso{0}$ is trivial.
-In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; the snake lemma then allows us to find $\CSiso{G}$.
-
-\section{Bounded character sheaves}
-
-In this section we describe full subcategory of $\CS(G)$, 
-called the category of bounded character sheaves on $G$ and denoted by $\CS_b(G)$, 
-which will illuminate the nature of $\CS(G)$ and will also play a role in the arguments later in this paper.
-
-Consider the category $\GC(G)$ of finite etale covers of $G$ that are also morphisms of abelian group schemes.
-Recall that we fixed an algebraic closure $\bFq$ of $\Fq$ long ago; 
-let ${\bar e} : \Spec{\bFq} \to G$ be the geometric point on $G$ obtained by composing $\Spec{\bFq} \to \Spec{\Fq}$ with the identity $e : \Spec{\Fq} \to G$ for $G$.
-Let $\ker_{\bar e}$ be the set-valued functor on $\GC(G)$
-defined by pull-back along the geometric point ${\bar e} : \Spec{\bFq} \to G$ 
-followed by forgetting the structure sheaf and topology; 
-thus, if $f : H\to G$ is a finite etale morphism of group schemes, then $\ker_{\bar e}(f)$ is the set underlying 
-$\ker{\bar f} = H_{\bar e}$.
-Let $\pi_1^\text{gp}(G)$ be the automorphism group of the functor $\ker_{\bar e}$. 
-We will see that $\pi_1^\text{gp}(G)$ is a profinite abelian group.
-A \cdef{bounded character sheaf on $G$} is a continuous irreducible representation of $\pi_1^\text{gp}(G)$. 
-Let $\CS_b(G)$ be the monoidal category of irreducible continuous $\ell$-adic representations of $\pi_1^\text{gp}(G)$.
-
-\begin{proposition}
- $G\mapsto \pi_1^\text{gp}(G)$ is a functor from group schemes over $\Fq$ to profinite abelian groups, and .....
-\end{proposition}
-
-\begin{proof}
-The category $\GC(G)$, together with the set-valued functor $\ker_{\bar e}$ satisfy conditions (G1) through (G6) appearing in \cite[Exposé V, \S 4, p. 118-119]{SGA1a}.
-\end{proof}
-
-\section{Connected abelian algebraic groups}
-
-%\input{connected-1}
-% !TEX encoding = UTF-8 Unicode
-%In this section we review a fundamental property of character
-%sheaves on geometrically connected, commutative algebraic groups over $\Fq$.
-
-\begin{proposition}\label{prop:connected-1}
-  If $G$ is a geometrically connected commutative algebraic group over $\Fq$ then
-  \[
-  t_{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx),
-  \]
-  is an isomorphism of groups.
-\end{proposition}
-
-\begin{proof}
-  We will prove this proposition by reducing it to the functions--sheaves dictionary
-  \cite{Laumon}*{1.1}. The main point of this proof will therefore be to show that,
-  {\it since $G$ is geometrically connected}, every character sheaf on $G$ descends to
-  a local system on $G$ satisfying the analogue of \ref{CS.1} on $G$.
-
-  First, observe that the forgetful functor $(\gcs{L},\mu,F) \mapsto (\gcs{L},F)$
-  sends character sheaves on $G$ to Weil local systems on
-  $G$ \cite{Deligne:Weil2}*{1.1.10} (by a Weil local system on $G$ we
-  mean a Weil sheaf on $G$ which is a local system on $\bG$).
-  While is it not true that all Weil local systems on $G$
-  descend to sheaves on $G$, those that appear in the image of the
-  forgetful functor from character sheaves do.
-
-  To see why this is so, consider the category \cdef{$\CS_0(G)$} of
-  pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$
-  and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \tight{0}{\boxtimes}{0} \cs{L}_0$ satisfies
-  condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$
-  are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}.
-  \David{This section should be modified once we're done with the section on bounded character sheaves}
-  Let $b : \bG \to G$ be base change
-  (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$).
-  The proof of Proposition~\ref{prop:pullback} adapts
-  (simplifies, in fact) to show that $b^* : \CS_0(G) \to \CS(G)$ is a
-  monoidal functor. This functor is fully faithful; see
-  \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.  We will
-  show that $b^*$ is essentially surjective.
-
-  Let $g$ be any $\Fq$-rational point on $G$ (such as the identity for
-  $G$) and let $\bg$ be the geometric point on $G$ lying above
-  $g$ (we fixed $\Fq \hookrightarrow \bFq$ long ago). Since $G$ is
-  geometrically connected, the geometric point $\bg$ determines
-  an equivalence between the category of Weil local systems on $G$ and
-  $\ell$-adic representations of $\W(G,\bg)$
-  \cite{Deligne:Weil2}*{1.1.12}. Now let $(\gcs{L},\mu,F)$ be a
-  character sheaf on $G$. Then the isomorphism class of the Weil local
-  system $(\gcs{L},F)$ corresponds to an $\ell$-adic character of the
-  Weil group $\W(G, \bg)$. The $\Fq$-rational point $g$ under
-  the geometric point $\bg$ determines a splitting
-  $\Weil{\Fq}\to \W(G,\bg)$ of the exact sequence
-  \[
-  \begin{tikzcd}
-  1 \rar & \pi_1(\bG, \bg) \rar &  \W(G,\bg) \rar
-  & \ar[swap,bend right, dotted]{l}{g} \Weil{\Fq} \rar & 1
-  \end{tikzcd}
-  \]
-  In this way the Weil local system $(\gcs{L},F)$ determines an $\ell$-adic character
-  \[
-  t_{(\gcs{L},F)}(g) : \Weil{\Fq} \to \EEx \qquad \text{defined by}\qquad \Frob \mapsto t^\Frob_{(\gcs{L},F)}(g)
-  \]
-  of the Weil group $\Weil{\Fq}$; the image of $\Frob$ under this
-  character is $t^\Frob_\cs{L}(g)$, the trace of Frobenius of $\cs{L}$ at $g$.
-
-  On the other hand, we have already seen that $t^\Frob_\cs{L} : G(\Fq) \to \EEx$
-  is a group homomorphism. Since $G$ is an algebraic group over $\Fq$, it is a
-  variety over $\Fq$, so finitely generated over $\Fq$, so $G(\Fq)$ is finite;
-  it follows that $t^\Frob_\cs{L}(g) = t^\Frob_{(\gcs{L},F)}(g)$ is a root of unity,
-  for every $g\in G(\Fq)$.  Since $\Weil{\Fq}$ is generated by
-  $\Frob$ and $t_{(\gcs{L},F)}(g) : \Weil{\Fq} \to \EEx$ is
-  a character, it follows that the image of $t_{(\gcs{L},F)}(g)$ is a
-  finite subset of $\mu(\EE)$. Thus, $t_{(\gcs{L},F)}(g)$ extends to
-  an $\ell$-adic character of $\Gal(\bFq/\Fq)$, which will be denoted
-  by the same symbol.
-  \[
-  \begin{tikzcd}
-  1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \W(G,\bg) \rar \dar & \Weil{\Fq} \rar \dar & 1\\
-  1 \rar &  \pi_1(\bG, \bg) \rar & \pi_1(G,\bg) \rar & \Gal(\bFq/\Fq) \rar & 1
-  \end{tikzcd}
-  \]
-
-  We may now lift the $\ell$-adic character $t_{(\gcs{L},F)}(g) : \Gal(\bFq/\Fq) \to \EEx$
-  to an $\ell$-adic character of $\pi_1(G,\bg)$ using the canonical topological group map
-  $\pi_1(G,\bg) \to \Gal(\bFq/\Fq)$, above. But $\bg$ also
-  determines an equivalence between the category of $\ell$-adic
-  representations of $\pi_1(G,\bg)$ and local systems on $G$. Let
-  $\cs{L}_0$ be a local system on $G$ in the isomorphism class
-  determined by this $\ell$-adic character of $\pi_1(G,\bg)$.
-  Then $b^*\cs{L}_0 \iso \gcs{L}$, so $b^*$ is essentially surjective.
-
-  We have now shown that $b^* : \CS_0(G) \to \CS(G)$ is an equivalence
-  of rigid monoidal categories. It follows immediately that $b^*$
-  determines an isomorphism
-  \[
-  b^* : \CSbiso{G} \mathop{\longrightarrow}^{\iso} \CSiso{G}
-  \]
-  of the Picard groups determined by these rigid monoidal categories.
-  \Clifton{\textdbend This last sentence glosses over some subtle points;
-    I might need to address them in the `two perspectives' section.}
-
-  To finish the proof observe that the functions--sheaves dictionary,
-  as it pertains to characters, shows that
-  \[
-  t_{G} : \CSbiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)
-  \]
-  is an isomorphism of groups; see \cite{Laumon}*{1.1.3} or \cite{SGA4.5}*{Sommes trigonométriques}.
-\end{proof}
-
-\section{Commutative etale group schemes}
-
-%\input{etale-1}
-%In this section we establish a fundamental property of character
-% sheaves on commutative etale group schemes over $\Fq$ that are
-% geometrically finitely generated.
-
-\begin{proposition}\label{prop:etale}
-  If $G$ is a commutative \'etale group scheme over $\Fq$ and
-  $G(\bFq)$ is finitely generated then there is a canonical
-  isomorphism
-  \[
-  \CSiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, \Hom_\text{grp}(G(\bFq),\EEx)),
-  \qquad \text{given by}\qquad
-  [\cs{L}] \mapsto [t_\cs{L}],
-  \]
-  where $t_\cs{L}: \Weil{\Fq}\to \Hom_\text{grp}(G(\bFq),\EEx)$ is a cocycle such that
-  \[
-  \forall g\in G(\Fq), \qquad t_\cs{L}(\Frob)(g) = t^\Frob_\cs{L}(g).
-  \]
-\end{proposition}
-
-\begin{proof}
-  To simplify notation, we set
-  $G(\bFq)^* \ceq \Hom_\text{grp}(G(\bFq),\EEx)$.  Recall the
-  equivalence between etale group schemes over $\Fq$ and the category
-  of groups equipped with a continuous action of $\Gal(\bFq/\Fq)$ (for
-  the discrete topology on the group), given by $G \mapsto G(\bFq)$.
-  Under this equivalence any character sheaf $\cs{L}=(\gcs{L},\mu,F)$
-  on $G$ corresponds to:
-  \begin{enumerate}
-  \labitem{(cs.0)}{cs.0} an indexed set of one-dimensional
-    $\EE$-vector spaces $\gcs{L}_x \ceq x^*\gcs{L}$, as $x$ runs over
-    $G(\bFq)$;
-
-  \labitem{(cs.1)}{cs.1} an indexed set of isomorphisms
-    $\mu_{x,y} \ceq (x \times y)^*\mu : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes \gcs{L}_{y}$,
-    for all $x,y \in G(\bFq)$, such that
-    \[
-    \begin{tikzcd}[row sep=40]
-      \gcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
-      && \gcs{L}_{x+y}\otimes \gcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
-      \gcs{L}_{x} \otimes \gcs{L}_{y+z} \arrow{rr}{\id \otimes \mu_{y,z}}
-      && \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes \gcs{L}_{z}
-    \end{tikzcd}
-    \]
-    commutes, for all $x,y,z\in G(\bFq)$; and
-
-  \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $F_{x} \ceq x^*F: \gcs{L}_{\Frob(x)} \to \gcs{L}_x$
-    \Clifton{\textdbend There's hidden subtlety here too: maybe I
-      should explain which Frobenius this is and how it acts. }
-    such that
-    \[
-    \begin{tikzcd}[row sep=40]
-      \gcs{L}_{\Frob(x)+\Frob(y)} \arrow[swap]{d}{F_{x+y}} \arrow{rr}{\mu_{\Frob(x),\Frob(y)}}
-      && \gcs{L}_{\Frob(x)}\otimes \gcs{L}_{\Frob(y)} \dar{F_x \tight{0}{\otimes}{0} F_y} \\
-      \gcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
-      && \gcs{L}_x \otimes\gcs{L}_y
-    \end{tikzcd}
-    \]
-    commutes, for all $x,y\in G(\bFq)$.
-  \end{enumerate}
-  Under this equivalence, a map $\varphi : \cs{L} \to \cs{L'}$ of
-  character sheaves on $G$ corresponds to:
-  \begin{enumerate}
-  \labitem{(cs.3)}{cs.3} an indexed set $\varphi_x \ceq x^*\varphi: \gcs{L}_x \to \gcs{L'}_x$
-    of linear transformations (of one-dimensional $\EE$-vector spaces),
-    as $x$ runs over $G(\bFq)$, such that
-    \[
-    \begin{tikzcd}[column sep=40]
-      \arrow[swap]{d}{F_x} \gcs{L}_{\Frob(x)} \rar{\varphi_{\Frob(x)}} & \gcs{L'}_{\Frob(x)} \dar{F_x'}
-      &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}& \arrow[swap]{d}{\mu} \gcs{L}_{x+y} \rar{\varphi_{x+y}} & \gcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
-      \gcs{L}_x \rar{\varphi_x} & \gcs{L'}_x
-      & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\varphi_x\otimes \varphi_y} & \gcs{L'}_x \otimes \gcs{L'}_y
-    \end{tikzcd}
-    \]
-    both commute.
-  \end{enumerate}
-  It is clear that the category defined by conditions \ref{cs.0},
-  \ref{cs.1}, \ref{cs.2} and \ref{cs.3}, denoted by
-  \cdef{$\CS(G(\bFq))$}, is equivalent to $\CS(G)$. We will prove the
-  proposition by exhibiting an isomorphism between
-  $\CSiso{G(\bFq)}$ and $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
-
-  To produce the isomorphism between $\CSiso{G(\bFq)}$ and
-  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ we must pick a global section of the line
-  bundle $(\gcs{L},\mu)$, for each character sheaf $\cs{L}$ on $G$. We
-  will show that the group isomorphism does not depend on these
-  choices.
-
-  First, however, we show that such global sections exist.  Since
-  $G(\bFq)$ is finitely-generated abelian, it admits a decomposition
-  $G(\bFq) \iso G(\bFq)_\text{free} \oplus G(\bFq)_\text{tors}$ such
-  that $G(\bFq)_\text{tors}$ is finite.  Let $x_1, \ldots , x_r$ be a
-  basis for the free part $G(\bFq)_\text{free}$ of $G(\bFq)$ and let
-  $y_1, \ldots , y_t$ be a generators for the torsion part of
-  $G(\bFq)$ corresponding to the decomposition
-  $G(\bFq)_\text{tors} \iso \oplus_{j=1}^t \ZZ/m_j\ZZ$, with
-  $m_j \vert m_{j+1}$. For each such $x_i$ pick $s(x_i)\in \gcs{L}_{x_i}$;
-  for each such $y_j$ pick $s(y_j) \in \gcs{L}_{y_j}$; also set
-  $s({\bar e}) \ceq 0 \in \gcs{L}_{\bar e}$. ....
-  \Clifton{I'll finish this later.}
-  In this way we define a section
-  $s \ceq s_\cs{L} : G(\bFq) \to \coprod_{z\in G(\bFq)} \gcs{L}_z$ of
-  projection $\coprod_{z\in G(\bFq)} \gcs{L}_z \to G(\bFq)$ such that
-
-  \begin{equation}\label{section}
-    \forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes s(y).
-  \end{equation}
-  Under the equivalence at the beginning of this section, $s = s_\cs{L}$
-  corresponds to a global section of the line bundle $(\gcs{L},\mu)$.
-
-\Clifton{I'm going to remove all mention of line bundles from this paper.}
-
-  We use the section $s_\cs{L}$ to define a cocycle $z_\cs{L} \in Z^1(\Weil{\Fq},G(\bFq)^*)$
-  as follows. Recall that $\cs{L}$ also determines a family of linear transformations
-  $F_x : \gcs{L}_{\Frob(x)} \to \gcs{L}_x$ of one-dimensional $\EE$-vector
-  spaces, so $F_x(s(\Frob(x)))$ is a scalar multiply of $s(x)$, for
-  each $x\in G(\bFq)$; let $t_\cs{L}(\Frob)(x)$ be that scalar, so
-  \begin{equation}\label{t}
-    \forall x\in G(\bFq),\qquad F_{x}(s(\Frob(x)) = t_\cs{L}(\Frob)(x) s(x).
-  \end{equation}
-  Conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
-  the scalar $z_\cs{L}(\Frob)(x)$ is non-zero, while condition~\ref{cs.1} forces
-  $t_\cs{L}(\Frob)(x+y) = t_\cs{L}(\Frob)(x) \ t_\cs{L}(\Frob)(y)$,
-  for all $x,y \in G(\bFq)$.
-  % \Clifton{The alternative to this approach is to change the
-  %   definition of character sheaves to incorporate the notion of
-  %   Galois sheaves. That might not be so bad, but would add another
-  %   layer of complication, which we wouldn't use profitably, expect
-  %   here.}
-
-  Now $t_\cs{L} : \Weil{\Fq} \to G(\bFq)^*$ is defined, recursively, by
-  $t_\cs{L}(\Frob^n) \ceq t_\cs{L}(\Frob)\cdot \,^\Frob t_\cs{L}(\Frob^{n-1})$,
-  where $\Frob$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers
-  to pointwise multiplication of functions. This gives
-  \[
-  \obj \CS(G(\bFq)) \longrightarrow Z^1(\Weil{\Fq},G(\bFq)^*),
-  \qquad \text{defined by} \qquad \cs{L} \mapsto t_\cs{L}.
-  \]
-
-  Although we used a global section $s_\cs{L}$ in the definition of
-  $t_\cs{L}$, the class of $t_\cs{L}$ does not depend on this
-  choice. To see why, let $s_1$ and $s_2$ be two global sections of
-  the line bundle $(\gcs{L},\mu)$, in the sense above and let $t_1$
-  and $t_2$ be the cocycles defined by $s_1$ and $s_2$, respectively,
-  as above. Since, for each $x\in G(\bFq)$, $\gcs{L}_x$ is a
-  one-dimensional $\EE$-vector space, there is a unique scalar
-  $a(x) \in \EE$ such that $s_2(x) = a(x) s_1(x)$; moreover, $a(x)$ is
-  non-zero, since $s_2(x)$ is non-zero. Then \eqref{section} and
-  condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so
-  $a\in G(\bFq)^*$. Now consider the coboundary $t_0 : \Weil{\Fq} \to G(\bFq)^*$
-  defined by $t_0(\Frob) = \,^\Frob a \cdot a^{-1}$. Then $t_2 = t_0 t_1$,
-  so $t_2$ and $t_1$ are cohomologous. In this way we see that
-  \begin{equation}\label{cohomologous}
-    \obj \CS(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
-    \qquad \text{defined by} \qquad \cs{L} \mapsto [t_\cs{L}],
-  \end{equation}
-  is independent of the choice of global sections made above.
-
-  We now show that the function $\obj \CS(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*)$
-  factors through $\obj \CS(G(\bFq)) \to \CSiso{G(\bFq)}$.
-  To see this, let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and
-  let $t$ and $t'$ be any cocycles representing the classes in the
-  image of $\cs{L}$ and $\cs{L'}$ under \eqref{cohomologous}; by construction,
-  $t$ and $t'$ are defined by sections $s$ and $s'$. Now, $\varphi_x(s(x))$ is a
-  non-zero scalar multiple of $s'(x)$; define $\phi: G(\bFq) \to \EEx$
-  by $\varphi_x(s(x)) = \phi(x) s'(x)$. By the second part of condition~\ref{cs.3},
-  $\phi(x+y) = \phi(x)\phi(y)$, so $\phi \in G(\bFq)^*$. By the first part of
-  condition~\ref{cs.3}, $t'(\Frob) = t(\Frob) \cdot (\,^{\Frob^{-1}}\phi \cdot \phi^{-1})$,
-  so $t$ and $t'$ are cohomologous. This concludes the definition of
-  \begin{equation}\label{pich1}
-    \CSiso{G(\bFq} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
-    \qquad \text{defined by} \qquad [\cs{L}] \mapsto [t_\cs{L}].
-  \end{equation}
-  Now it follows from \eqref{t} that the image of the isomorphism
-  class of $\cs{L}$ is indeed represented by a cocycle $t_\cs{L}$ such
-  that $t_\cs{L}(\Frob) = t^\Frob_\cs{L}$ on $G(\Fq)$, which is to
-  say, when evaluated at $\Frob$, the cocycle $t_\cs{L}$ is an
-  extension of the trace of Frobenius of $\cs{L}$.
-
-  It only remains to show that \eqref{pich1} is a group
-  isomorphism. This is straightforward.
-  \Clifton{Straightforward, yes, but it still needs to be written down here.}
-\end{proof}
-
-%\input{etale-2}
-%Define $\rho \colon \Hh^1(\Weil{\Fq}, \Hom(G(\bFq), \EEx))
-% \rightarrow \Hom(G(\Fq), \EEx)$ by $\rho(\phi)(g) =
-% \phi(\Frob)(g)$.
-
-\begin{proposition}\label{prop:X}
-  Let $X$ be a finitely generated abelian group equipped with an
-  action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on
-  $X$.  Then
-  \begin{align*}
-    \Hh^1(\Fq, \Hom(X, \EEx)) &\xrightarrow{\rho} \Hom(\Hh^0(\Fq, X), \EEx) \\
-    \rho([z])(x) &= z(\Frob)(x)
-  \end{align*}
-  is an isomorphism of groups.
-\end{proposition}
-\begin{proof}
-  We first prove that $\rho$ is surjective.  Suppose that
-  $f \in \Hom(X^\Frob, \EEx).$ Since $\EEx$ is divisible
-  as an abelian group it is injective as a $\ZZ$-module and thus
-  $\Ext^1_{\ZZ}(X/X^\Frob, \EEx) = 0$.  Applying the functor
-  $\Hom(\mbox{---}, \EEx)$ to
-  \[
-  \begin{tikzcd}
-  0 \rar & X^\Frob \rar & X \rar & X/X^\Frob \rar & 0
-  \end{tikzcd}
-  \]
-  and considering the associated long exact sequence gives the
-  existence of an $\tilde{f} \in \Hom(X, \EEx)$ restricting to
-  $f$.  Define a $1$-cocycle $z \in \Hh^1(\Fq, \Hom(X,\EEx))$ by
-  mapping $\Frob$ to $\tilde{f}$.  Then $\rho([z]) = f$.
-
-  Now suppose that $[z] \in \Hh^1(\Fq,\Hom(X,\EEx))$ with
-  $\rho([z]) = 1$; write $\tilde{f}$ for $z(\Frob)$.  The injectivity
-  of $\rho$ is equivalent to the existence of a homomorphism $\psi
-  \colon X \rightarrow \EEx$ with
-  $$\tilde{f}(x) = \frac{\psi(\Frob(x))}{\psi(x)}$$
-  for $x \in X$.  In fact, we may replace the construction of $\psi$
-  for all $\ZZ[\Gal(\bFq/\Fq)]$-modules $X$ with the construction of
-  analogous $\psi$s for a different class of modules.
-
-  Since the action of $\Gal(\bFq/\Fq)$ is continuous, there is an $m$
-  so that $\Frob^m$ acts trivially on $X$; write $\Fqm$ for the degree
-  $m$ extension of $\Fq$ and $\Gamma_m$ for $\Gal(\Fqm/\Fq)$.  Since
-  $T^m-1$ factors as a squarefree product of cyclotomic polynomials,
-  the Chinese remainder theorem expresses $\ZZ[\Gamma_m]$ as a product
-  of $\ZZ[\zeta_d]$ for $d$ dividing $m$.  Each $\ZZ[\zeta_d]$ is the
-  maximal order in a number field and thus $\ZZ[\Gamma_m]$ is a
-  product of Dedekind domains.  Therefore $X$ decomposes into a direct
-  sum of cyclic $\ZZ[\Gamma_m]$-modules \cite[?]{Brandal}, each of the
-  form $\ZZ[\Gamma_m] / I$ for some ideal $I \subset \ZZ[\Gamma_m]$.
-  The ideal $I$ corresponds to a direct product of ideals $I_d$ in the
-  $\ZZ[\zeta_d]$, and within each $\ZZ[\zeta_d]$ the Chinese remainder
-  theorem allows a further decomposition of $\ZZ[\zeta_d] / I_d$ as a
-  direct sum of $\ZZ[\zeta_d]$-modules of the form $\ZZ[\zeta_d]/P^s$.
-  So if we can construct, for every cyclotomic ring $\ZZ[\zeta_d]$,
-  prime ideal $P \subset \ZZ[\zeta_d]$ and positive integer $s$, a
-  $\psi \colon \ZZ[\zeta_d]/P^s \rightarrow \EEx$ with
-  \begin{equation} \label{eq:psi-condition}
-    \tilde{f}(x) = \frac{\psi(\zeta_d \cdot x)}{\psi(x)},
-  \end{equation}
-  then the existence of the original $\psi$ follows because $X$ is a
-  direct sum of such $\ZZ[\zeta_d]/P^s$.
-
-  We now fix a $d$, $P$ and $s$, write $\zeta$ for $\zeta_d$ and
-  choose a polynomial
-  $$h(T) = a_rT^r + a_{r-1}T^{r-1} + \cdots + a_0$$
-  so that $P^s = (p^s, h(\zeta_d))$.
-  % Setting $\psi = 1$ will satisfy equation \ref{eq:psi-condition}
-  % when $d = 1$.
-  An an abelian group, the quotient $\ZZ[\zeta] / P^s$ is generated by
-  $\zeta^i$ for $0 \le i < \phi(d)$; we define
-  \begin{equation} \label{eq:psi-def}
-    \psi(\zeta^i) = \alpha \prod_{j=0}^{i-1} \tilde{f}(\zeta^j)
-  \end{equation}
-  for an $\alpha \in \EEx$ to be chosen later.  Since there are
-  relations among the $\zeta^i$ we first need to check that $\psi$ is
-  well-defined.
-
-  The relations among the generators $\zeta^i$ are additively
-  generated by $\zeta^ch(\zeta)$ as $c$ ranges from $0$ to
-  $\phi(d)-r-1$.  If we set
-  $$A_c = \sum_{i=0}^r a_i \sum_{j=0}^{i+c-1} \zeta^j$$
-  then
-  $$\psi(\zeta^ch(\zeta)) = \alpha^{h(1)} \tilde{f}(A_c).$$
-  Now consider $(\zeta - 1)A_c$: the sums telescope and we get that
-  $(\zeta-1)A_c = \zeta^ch(\zeta) - h(1).$ There are now two
-  possibilities:
-  \begin{enumerate}
-  \item $d$ is a power of $p$; write $s = \phi(d)m + n$.  We may take
-    $h(T)$ to be $p^m(T-1)^n$, in which case $\zeta^ch(\zeta) - h(1) \in P^s$,
-    so $A_c$ is fixed under multiplication by $\zeta$ in
-    $\ZZ[\zeta]/P^s$ and thus $\tilde{f}(A_c) = 1$.  In this case
-    $\alpha^{h(1)} = 1$ regardless of $\alpha$.
-  \item $d$ is not a power of $p$.  If two distinct primes divide $d$
-    then $\zeta - 1$ is a unit; otherwise $\zeta - 1$ is a unit modulo
-    $P^s$.  Let $\omega \in \ZZ[\zeta]$ satisfy
-    $\omega(\zeta - 1) \equiv 1 \pmod{P^s}$ and set
-    \begin{equation} \label{alpha-def}
-      \alpha = \tilde{f}(\omega).
-    \end{equation}
-    Then $A_c + h(1)\omega$ is fixed under multiplication by $\zeta$
-    and thus $\tilde{f}(A_c) = \tilde{f}(-h(1)\omega)$.
-  \end{enumerate}
-  In either case, $\psi(\zeta^ch(\zeta)) = 1$ for all $c$.  The only
-  other relations imposed on the $\zeta^i$ are that they are all
-  killed under multiplication by $p^s$.  Since $\tilde{f}$ is also a
-  homomorphism $\ZZ[\zeta]/P^s \rightarrow \EEx$ the values of
-  $\tilde{f}$ and thus of $\psi$ will be $p^s$-roots of unity.
-  Therefore $\psi$ is well defined.
-
-  We now check equation \ref{eq:psi-condition} for
-  $x = \zeta^{\phi(d)-1}$.  Write
-  $\Phi_d(T) = T^{\phi(d)} - b_{\phi(d)-1}T^{\phi(d)-1} - \cdots - b_0$
-  and set
-  $$B = \sum_{i=0}^{\phi(d)-1} -\zeta^i + b_i \sum_{j=0}^{i-1} \zeta^j.$$
-  We have
-
-  \begin{align*}
-    \frac{\psi(\zeta^{\phi(d)})}{\psi(\zeta^{\phi(d)-1})\tilde{f}(\zeta^{\phi(d)-1})}
-    &= \frac{\psi(b_{\phi(d)-1}\zeta^{\phi(d)-1} + \cdots + b_0)}{\psi(\zeta^{\phi(d)-1})\tilde{f}(\zeta^{\phi(d)-1})} \\
-    &= \alpha^{-\Phi_d(1)} \tilde{f}(B)
-  \end{align*}
-  As before we see that $(\zeta - 1)B = \Phi_d(1) - \Phi_d(\zeta) = \Phi_d(1)$.
-  We consider the same cases as before:
-
-  \begin{enumerate}
-  \item $d$ is a power of $p$, in which case $\Phi_d(1) = p$.  Thus
-    $(\zeta-1)B = p = u(\zeta-1)^{\phi(d)}$ for a unit $u \in \ZZ[\zeta]$
-    and $B - u(\zeta-1)^{\phi(d)-1}$ is fixed by $\zeta$,
-    so that $\tilde{f}(B) = \tilde{f}(u(\zeta - 1)^{\phi(d)-1})$.  The
-    multiplicative order of $\tilde{f}(u(\zeta-1)^{\phi(d)-1})$ is at most
-    $\lceil \frac{s - 1 - (\phi(d)-1)}{\phi(d)}\rceil = \lceil \frac{s}{\phi(d)} \rceil - 1$
-    while the additive order of $1 \in \ZZ[\zeta]/P^s$ is $\lceil \frac{s}{\phi(d)} \rceil$.
-    Thus we may choose $\alpha = \psi(1)$ with $\alpha^p = \tilde{f}(B)$.
-  \item $d$ is not a power of $p$ and $\omega$ is the inverse of
-    $\zeta-1$ modulo $P^s$.  Then $\tilde{f}(B) = \tilde{f}(\omega\Phi_d(1))$.
-  \end{enumerate}
-  In either case, $\alpha^{-\Phi_d(1)}\tilde{f}(B) = 1$ and thus
-  $\psi$ satisfies equation \ref{eq:psi-condition} for
-  $x = \zeta^{\phi(d)-1}$.  The definition of $\psi$ in \ref{eq:psi-def}
-  immediately implies that $\psi$ satisfies equation
-  \ref{eq:psi-condition} for lesser powers of $\zeta$, and thus for
-  all $x$ by linearity.  The existence of $\psi$ shows that $\rho$ is injective.
-\end{proof}
-
-\section{Restriction to the identity component}
-
-%\input{restriction}
-% !TEX encoding = UTF-8 Unicode
-%\subsection*{Restriction to the identity component is surjective}
-
-\David{This section needs to be modified once the bounded character sheaves section is done}
-Let $G^0$ be the connected component of $G$ containing the identity.
-By Proposition~\ref{prop:pullback}, pull-back along
-$G^0\hookrightarrow G$ determines a monoidal functor
-$\cs{L}\mapsto \cs{L}\vert_{G^0}$ from $\CS(G)$ to $\CS(G^0)$.  In
-this section we show that this functor is essentially surjective. To
-do this we employ a perspective on characters sheaves which is
-different from that in Section~\ref{section:category} but which works
-very well for geometrically connected abelian algebraic groups; this
-perspective fails to extend properly to the more general context of
-Section~\ref{section:category}.
-
-\begin{proposition}\label{prop:restriction}
-  The restriction functor $\CS(G)\to \CS(G^0)$ is essentially surjective.
-\end{proposition}
-
-\begin{proof}
-  Because $G$ is smooth over $\Fq$, the identity component $G^0$ is a
-  geometrically connected algebraic group over $\Fq$, clopen in $G$
-  \cite{vdG&M}*{3.17}. By Proposition~\ref{prop:connected-1}, every
-  character sheaf $\cs{E} = (\gcs{E},\mu^0,F^0)$ on $G^0$ descends to
-  a line bundle on $G^0$.
-
-  Let us review how line bundles on $G^0$ determine character sheaves
-  on $G^0$.  Up to isomorphism, line bundles on $G^0$ may be
-  apprehended in terms of pairs $(\pi,\psi)$,
-  \David{Aren't there line bundles which are not character sheaves,
-    for which $B$ is not an algebraic group?}
-  where $\pi : B\to G^0$ is a finite etale morphism of algebraic
-  groups and a character $\psi : A\to \EEx$, where
-  $\Gal(\bFq/\Fq)$ acts trivially on $A \ceq \ker {\bar \pi}$, as
-  summarized by the following diagram.
-  \begin{equation}\label{E}
-  \begin{tikzcd}
-  \EEx & 1\rar & A \arrow[bend right,swap]{ll}{\psi} \rar & B \rar{\pi} & G^0 \rar & 1
-  \end{tikzcd}
-  \end{equation}
-  (In fact, we may always take $B = G^0$ and $\pi = \Lang_{G^0}$, the
-  Lang isogeny for $G^0$.)  Indeed, $\cs{E}$ is precisely the
-  component of $\pi_! (\EE)_{B}$ on which $A$ acts through $\psi$.  To
-  see that $\cs{E}$ is a line bundle on $G^0$, start by pulling back
-  $\pi: B \to G^0$ along $m_0 : \GzxGz \to G^0$.
-  \begin{equation}
-  \begin{tikzcd}
-  \EEx & 1\rar & A \arrow[bend right,swap]{ll}{\psi} \rar & B \rar{\pi} & G^0 \rar & 1\\
-      & 1\rar & \AxA \arrow[dashed]{llu} \uar \rar
-      & \BxB \rar{\pi\tight{1}{\times}{1} \pi} \uar{m_{B}} & \GzxGz \uar{m_0} \rar & 1
-  \end{tikzcd}
-  \end{equation}
-  As pictured above, the kernel of this pull-back is $\AxA$;
-  indeed, $\AxA \to \BxB$ is the pull-back of $A\to B$ along
-  $m_{B}$. Use this Cartesian square to define a character (the dotted
-  arrow, above) of $\AxA$; that is, define $\AxA \to \EEx$
-  by the composition of $\AxA \to A$ and $\psi : A\to \EEx$.
-  Note that this character is $\psi \otimes \psi : \AxA \to \EEx$.
-  \Clifton{I haven't explained how maps between diagrams define sheaf
-    homomorphisms between local systems.}
-  Since the lower sequence is precisely the sequence defining
-  $\ExE$, this shows that, by construction, $\cs{E}$
-  comes equipped with a canonical isomorphism $m_0^*\cs{E} \iso \ExE$.
-  Now the base change $\gcs{E}$ comes equipped with isomorphisms
-  $F^0 : \Frob_{G^0}^* \gcs{E} \to \gcs{E}$ and
-  $\mu^0 : \bm_0^* \gcs{E} \to \bExE$
-  satisfying conditions \ref{CS.1} and \ref{CS.2}. Then $(\gcs{E},\mu^0,F^0)$
-  is a character sheaf of $G^0$.
-
-  The next step is to show that $\pi: B \to G^0$ extends to a finite
-  etale morphism of group schemes $f: H\to G$, smooth and locally of
-  finite type over $\Fq$, in such a way that $H^0 = B$, $f^0 =\pi$ and
-  $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism of component
-  groups.
-  \begin{equation}\label{extension-diagram}
-  \begin{tikzcd}
-  A \arrow[equal]{r} \dar & A \dar \\
-  B \rar \dar[swap]{\pi} & H \rar \dar[swap]{f} & \pi_0(H) \arrow{d}[below,rotate=90]{\sim}[swap]{\pi_0(f)} \\
-  G^0 \rar & G \rar & \pi_0(G)
-  \end{tikzcd}
-  \end{equation}
-  where all rows and columns are exact and all maps are defined over
-  $\Fq$.  We will do so by passing back and forth between group
-  schemes over $\Fq$ and their $\bFq$-points.  Extensions of
-  $G^0(\bFq)$ by $A(\bFq)$, such as $A(\bFq) \to H^0(\bFq) \to G^0(\bFq)$,
-  correspond to classes in $\Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))$.
-  Similarly, extensions of $G(\bFq)$ by $A(\bFq)$ correspond to
-  classes in $\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq))$.  The map
-  $G^0(\bFq) \to G(\bFq)$ induces a map
-  $\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))$,
-  fitting into the long exact sequence derived from applying
-  $\Hom(\mbox{---}, A(\bFq))$ to $G^0(\bFq) \to G(\bFq) \to \pi_0(G)(\bFq)$:
-  $$\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)).$$
-  We now show that $\Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)) = 0$.
-
-  It suffices to show that $\pi_0(G)(\bFq)$ has a two-term resolution
-  by injective $\ZZ[\Gamma]$-modules.  Since the action of $\Gamma$ on
-  $\pi_0(G)(\bFq)$ is continuous, it factor through a finite quotient
-  $\Gamma_m = \Gamma / H_m$.  Any product of Dedekind domains has
-  cohomological dimension $1$ \cite[?]{?}, so $\pi_0(G)(\bFq)$ has a
-  two term resolution by injective $\ZZ[\Gamma_m]$-modules.  Let $I$
-  be one of these modules: we need to show that $I$ is injective as a
-  $\ZZ[\Gamma]$-module.  Consider the universal diagram for injectivity:
-
-  \[
-  \begin{tikzcd}
-  A \rar{a} \arrow[hook]{d} & I \\
-  B
-  \end{tikzcd}
-  \]
-  where $A$ and $B$ are arbitrary $\ZZ[\Gamma]$-modules.  Since $H_m$ acts trivially on $I$,
-  $I_{H_m}A := \langle (\gamma-1)a : \gamma \in H_m, a \in A \rangle \subseteq \ker(a).$
-  Since $B / I_{H_m}B \cong B \otimes_A A / I_{H_m}A$, we get
-  \[
-  \begin{tikzcd}
-  A \arrow[two heads]{r} \arrow[hook]{d} & A/I_{H_m}A \rar \arrow[hook]{d} & I \\
-  B \arrow[two heads]{r} & B/I_{H_m}B \arrow[dashed]{ur} & {}
-  \end{tikzcd}
-  \]
-  The dotted arrow exists since $I$ is injective as a
-  $\ZZ[\Gamma_m]$-module, and the outer diagram shows that $I$ is
-  injective as a $\ZZ[\Gamma]$-module.
-
-  We therefore have the existence of diagram \eqref{extension-diagram}
-  at the level of $\bFq$-points.  This expresses $H(\bFq)$ as a
-  disjoint union of translates of $B(\bFq)$; by transport of structure
-  we may take $H$ to be a group scheme over $\bFq$.  Similarly, the
-  restriction of $f$ to each component of $H$ is a morphism of
-  schemes, and thus $f$ is as well.  Finally, the whole diagram
-  descends to a diagram of $\Fq$-schemes since the $\bFq$-points of
-  the objects come equipped with continuous $\Gamma$-actions, and the
-  morphisms are $\Gamma$-equivariant.
-
-  Now we show that $f : H\to G$, as above, together with a character
-  $\psi : \ker \bf \to \EEx$, defines a character sheaf on
-  $G$. We will also show that the restriction of this character sheaf
-  on $G$ to $G^0$ is precisely the character sheaf on $G^0$ defined by
-  the pair $(f^0,\psi)$ as above.
-
-  Set $X \ceq \pi_0(G)\times_{\Spec{\Fq}} \Spec{\bFq}$. We will
-  identify $X$ with $\pi_0(H)\times_{\Spec{\Fq}} \Spec{\bFq}$ using
-  the base change of $\pi_0(f): \pi_0(H)\to \pi_0(G)$. For each $x\in X$,
-  write $\bf^x : \bH^x \to \bG^x$ for the
-  restriction of $\bf$ to $\bH^x$, as a cover of
-  $\bG^x$. For each $x,y\in X$, let
-  $\bm_{x,y} : \bH^x \times \bH^{y} \to \bH^{x+y}$
-  be the map obtained from $\bm$ by restriction. Define
-  $\bm_{x} : A\to \Aut(\bf^x)$ by
-  $\bm_{x}(a): g \mapsto \bm_{0,x}(a,g)$; then
-  $\bm_{x} : A\to \Aut(\bf^x)$ is an isomorphism.
-  \Clifton{I need to show that $\bm_{x} : A\to \Aut(\bf^x)$ is an isomorphism.}
-
-  For each $x\in X$ let $\gcs{L}^x$ be the rank-$1$ local system on
-  $\bG^x$ determined by the finite etale cover
-  $\bf^x : \bH^x \to \bG^x$ and the character
-  $\psi_x \ceq \psi \circ \bm_x^{-1}$.  Since
-  $\bG = \coprod_{x\in X} \bG^x$ (disjoint union), this
-  determines a constructible sheaf $\gcs{L}$ on $\bG$, locally
-  constant of rank-$1$ on each connected component of $\bG$.
-  Taking the case $x=0$ we observe that $\gcs{L}^0 =\gcs{E}$,
-  the latter defined above. To finish the proof of the proposition we
-  equip $\gcs{L}$ with isomorphisms
-  $\mu : \bm^* \gcs{L} \to \LxL$ and
-  $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ satisfying conditions \ref{CS.1}
-  and \ref{CS.2}.
-
-  Observe that $\bm: \bGxG \to \bG$ is
-  completely determined by the family of maps
-  $\bm_{x,y} : \bG^x \times \bG^{y} \to \bG^{x+y}$.
-  Accordingly, to define $\mu$ for $\gcs{L}$ it is sufficient to define isomorphisms
-  $\mu_{x,y} : \bm_{x,y}^*\gcs{L}^{x+y} \iso \gcs{L}^{x}\boxtimes \gcs{L}^{y}$
-  for all $x,y\in X$. To do that, note first that the local system
-  $\gcs{L}^{x}\boxtimes \gcs{L}^{y}$ is defined by the following diagram.
-  \[
-  \begin{tikzpicture}[auto,style={rectangle}]
-  \node (0) at (0,0) {$\EEx$};
-  \node (1) [anchor=east] at (6,0) {$\Aut(\bf^x) \times \Aut(\bf^y)$};
-  \node (2) [anchor=west] at (6.4,0) {$\bH^x \times \bH^y$};
-  \node (3) at (11,0) {$\bG^x \times \bG^y$};
-  \draw [->] (1) to node[swap, label] {$\psi_x \otimes \psi_y$} (0);
-  \draw [->] (6.3,-0.06) arc (330:40:0.12) -- (6.3,0.07);
-  \draw [->] (2) to node[label] {$\bf^x \tight{0}{\times}{0} \bf^y$} (3);
-  \end{tikzpicture}
-  \]
-  On the other hand, the diagram for the local system $\bm_{x,y}^* \gcs{L}^{x+y}$
-  is found by pulling-back the diagram for $\gcs{L}^{x+y}$ along
-  $\bm_{x,y} : \bH^x\times\bH^y \to \bH^{x+y}$;
-  the result is the middle horizontal diagram below, where we use the
-  fact that the covering group of the middle arrow is $\Aut(\bf^{x+y})$, canonically.
-
-  \vspace{0.2in}
-
-  \[
-  \begin{tikzpicture}[auto,style={shape={asymmetrical rectangle}},scale=1.2]
-  \node (12) [anchor=east] at (4,2.4) {$\Aut(\bf^{x+y})$};
-  \node (22) [anchor=west] at (4.4,2.4) {$\bH^{x+y}$};
-  \node (32) [anchor=east] at (11,2.4) {$\bG^{x+y}$};
-  \node (01) at (0,1.2) {$\EEx$};
-  \node (11) [anchor=east] at (4,1.2) {$\Aut(\bf^{x+y})$};
-  \node (21) [anchor=west] at (4.4,1.2) {$\bH^{x+y} \times_{\bG^{x+y}} (\bG^x\times\bG^y)$};
-  \node (31) [anchor=east] at (11,1.2) {$\bG^x\times \bG^y$};
-  \node (10) [anchor=east] at (4,0) {$\Aut(\bf^x)\times \Aut(\bf^y)$};
-  \node (20) [anchor=west] at (4.4,0) {$\bH^x\times \bH^y$};
-  \node (30) [anchor=east] at (11,0) {$\bG^x\times \bG^y$};
-  \draw [->] (4.3,2.34) arc (330:40:0.12) -- (4.3,2.47);
-  \draw [->, densely dotted] (4.3,1.14) arc (330:40:0.12) -- (4.3,1.27);
-  \draw [->] (4.3,-0.06) arc (330:40:0.12) -- (4.3,0.07);
-  \draw [->] (12) to node[swap,label] {$\psi_{x+y}$} (01);
-  \draw [->, dashed] (11) -- (01);
-  \draw [->] (10) to node[label] {$\psi_x \otimes \psi_y$} (01);
-  \draw [->, dashed] ($(11.south) + (0,-0.7)$) -- (11);
-  \draw [double equal sign distance] (11) -- (12);
-  \draw [->] (22) to node[label] {$\bf^{x+y}$} (32);
-  \draw [->] ($(22.south) + (0,-0.7)$) -- (22);
-  \draw [->] (21) -- (31);
-  \draw [->] ($(32.225) + (0,-0.7)$) to node[swap] {\footnotesize{$\bm_{x,y}$}} (32.225);
-  \draw [->] ($(22.south) + (0,-1.9)$) -- ($(22.south) + (0,-1.2)$);
-  \draw [->] (20) to node[label] {$\bf^x \times \bf^y$} (30);
-  \draw [double equal sign distance] ($(32.225) + (0,-1.9)$) -- ($(32.225) + (0,-1.2)$);
-  \end{tikzpicture}
-  \]
-  Now, the homomorphism from the covering group of
-  $\bf^x\times\bf^y$ to the covering group of
-  $\bf^{x+y}$ induced by the composition
-  $ \bH^x\times \bH^y \to \bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y \to \bH^{x+y}$
-  is precisely $(\bm_x(a),\bm_y(b)) \mapsto \bm_{x+y}(ab)$.
-  Since this map commutes with the characters $\psi_x\otimes\psi_y$
-  and $\psi_{x+y}$ (so, the far-left triangle commutes in the diagram above)
-  it follows that, for each $x,y\in X$ the diagram above defines a canonical isomorphism
-  $\mu_{x,y} : \bm_{x,y}^* \gcs{L}^{x+y} \to \gcs{L}^x \boxtimes\gcs{L}^y$.
-  This defines $\mu: \bm^* \gcs{L} \iso \LxL$.
-  It is straightforward (but laborious) to show that the pair
-  $(\gcs{L},\mu)$ satisfies condition \ref{CS.1}.
-
-  Now we turn to the definition of $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$.
-  As above, we define this isomorphism through a family of
-  isomorphisms on the connected components of $\bG$. The
-  restriction of $\Frob_{G}$ to $\bG^x$ defines an isomorphism
-  $\Frob_x : \bG^x \to \bG^{\Frob(x)}$.
-  %\[
-  %\xymatrix{
-  %\ar[d]_{\Frob_x} \bG^x \ar[r] & \ar[d]_{\Frob_{G}} \bG\\
-  %\bG^{\Frob(x)} \ar[r] & \bG\\
-  %}
-  %\]
-  Pull back the finite etale covering in the diagram for
-  $\gcs{L}^{\Frob(x)}$ along $\Frob_x$ and compare the result with the
-  finite etale covering in the diagram for $\gcs{L}^{x}$.
-
-  \[
-  \begin{tikzpicture}[auto,style={rectangle},scale=1.2]
-  \node (12) [anchor=east] at (4,2.4) {$\Aut(\bf^{\Frob(x)})$};
-  \node (22) [anchor=west] at (4.4,2.4) {$\bH^{\Frob(x)}$};
-  \node (32) [anchor=west] at (8,2.4) {$\bG^{\Frob(x)}$};
-  \node (01) at (0,1.2) {$\EEx$};
-  \node (11) [anchor=east] at (4,1.2) {$\Aut(\bf^{\Frob(x)})$};
-  \node (21) [anchor=west] at (4.4,1.2) {$\bH^{\Frob(x)} \times_{\bG^{\Frob(x)}} \bG^x$};
-  \node (31) [anchor=west] at (8,1.2) {$\bG^x$};
-  \node (10) [anchor=east] at (4,0) {$\Aut(\bf^x)$};
-  \node (20) [anchor=west] at (4.4,0) {$\bH^x$};
-  \node (30) [anchor=west] at (8,0) {$\bG^x$};
-  \draw [->] (4.3,2.34) arc (330:40:0.12) -- (4.3,2.47);
-  \draw [->, densely dotted] (4.3,1.14) arc (330:40:0.12) -- (4.3,1.27);
-  \draw [->] (4.3,-0.06) arc (330:40:0.12) -- (4.3,0.07);
-  \draw [->] (12) to node[swap,label] {$\psi_{\Frob(x)}$} (01);
-  \draw [->, dashed] (11) -- (01);
-  \draw [->] (10) to node[label] {$\psi_x$} (01);
-  \draw [->, dashed] ($(11.south) + (0,-0.7)$) -- (11);
-  \draw [double equal sign distance] (11) -- (12);
-  \draw [->] (22) to node[label] {$\bf^{\Frob(x)}$} (32);
-  \draw [->] ($(22.225) + (0,-0.7)$) -- (22.225);
-  \draw [->] (21) -- (31);
-  \draw [->] ($(32.222) + (0,-0.7)$) to node[swap] {\footnotesize{$\Frob_x$}} (32.222);
-  \draw [->] ($(22.225) + (0,-1.9)$) -- ($(22.225) + (0,-1.2)$);
-  \draw [->] (20) -- (30);
-  \draw [double equal sign distance] ($(32.222) + (0,-1.9)$) -- ($(32.222) + (0,-1.2)$);
-  \end{tikzpicture}
-  \]
-  The covering group of $\bH^{\Frob(x)} \times_{\bG^{\Frob(x)}} \bG^x$
-  is isomorphic to $\Aut(\bf^{\Frob(x)})$, canonically, so
-  $\Frob_x^* \gcs{L}^{\Frob(x)}$ is defined by the middle (horizontal)
-  diagram, above.  We define the sheaf homomorphism
-  $F_x : \Frob_x^* \gcs{L}^{\Frob(x)} \to \gcs{L}^x$ by the canonical morphism
-  $\bH^x \to \bH^{\Frob(x)} \times_{\bG^{\Frob(x)}} \bG^x \to $;
-  to see that this defines a sheaf homomorphism it is sufficient to
-  check that the character $\psi_x$ commutes with the family of isomorphisms
-  $F_x : (\Frob_{G}^* \gcs{L})\vert_{\bG^x} \iso \Frob_x^* \gcs{L}^{\Frob{x}} \to \gcs{L}^x$
-  now defines the isomorphism $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$.
-  \Clifton{Add some detail here.}
-  This isomorphism is compatible with $\mu$ in the sense of condition~\ref{CS.2}.
-\end{proof}
-
-\begin{remark}
-  We have seen that if $f : H\to G$ is a finite etale cover of $G$ by
-  a smooth group scheme and if all geometric automorphisms of $f$ are
-  fixed by Frobenius, then every character of $\ker f$ determines a
-  character sheaf on $G$. However, it is not true that every character
-  sheaf on $G$ arises in this manner.
-\end{remark}
-\Clifton{I can flesh out this remark once I've promoted the definition of $\CS_0(G)$ (category of bounded character sheaves on $G$).}
-%\input{centralextensions}
-
-\section{Main result regarding character sheaves}
-
-%\input{snake}
-\begin{theorem}\label{thm:snake}
-  If $G$ is a smooth abelian group scheme, locally of finite type over
-  $\Fq$, and the abelian group $\pi_0(G)(\bFq)$ (the geometric
-  component group) is finitely generated, then the trace of Frobenius
-  homomorphism
-  \[
-  t_{G} : \CSiso{G} \to \Hom(G(\Fq),\EEx),
-  \]
-  from the Picard group of the category of character sheaves on $G$ to
-  the group of characters of $G(\Fq)$, is an isomorphism.
-\end{theorem}
-
-\begin{proof}
-  Consider the short exact sequence in the category of smooth group
-  schemes, locally of finite type over $\Fq$, defining the component
-  group scheme for $G$:
-  \begin{equation}\label{eq:pi0}
-  \begin{tikzcd}
-    1 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
-  \end{tikzcd}
-  \end{equation}
-  Let
-  \[
-  \begin{tikzcd}[row sep=30]
-    {}& \ker t_{\pi_0(G)} \dar & \arrow[dashed]{d} \ker t_{G} & \ker t_{G^0} \dar & \\
-    0 \rar & \CSiso{\pi_0(G)} \rar \dar{t_{\pi_0(G)}}
-    & \CSiso{G} \rar \dar{t_{G}} & \CSiso{G^0} \rar \dar{t_{G^0}} & 0\\
-    0 \rar & \Hom(\pi_0(G)(\Fq),\EEx) \rar \dar
-    & \arrow[dashed]{d} \Hom(G(\Fq),\EEx) \rar & \Hom(G^0(\Fq),\EEx) \rar \dar & 0\\
-    & \coker t_{\pi_0(G)} & \coker t_{G} &  \coker t_{G^0} &
-  \end{tikzcd}
-  \]
-  be the commutative diagram of abelian groups obtained by applying
-  Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.  By
-  Proposition~\ref{prop:connected-1}, $\ker t_{G^0} =0$ and $\coker t_{G^0}=0$.
-  By Propositions~\ref{prop:etale} and \ref{prop:X}, $\ker t_{\pi_0(G)}=0$
-  and $\coker t_{\pi_0(G)}=0$.
-
-  The sequence of character groups is left-exact: by
-  Proposition~\ref{prop:pullback}, it is dual to the exact sequence of
-  abelian groups
-  \begin{equation}\label{eq:pi1}
-  \begin{tikzcd}
-    1 \rar & G^0(\Fq) \rar & G(\Fq) \rar & \pi_0(G)(\Fq) \rar & 0;
-  \end{tikzcd}
-  \end{equation}
-  since $\Hom(\ - \ ,\EEx)$ is left-exact, the sequence of
-  character groups is left exact.
-
-  The sequence of Picard groups is right-exact: it is exact at
-  $\CSiso{G^0}$ by Proposition~\ref{prop:restriction}; and
-  it is exact at $\CSiso{G}$ because the left-square
-  commutes (by Proposition~\ref{prop:pullback}), the bottom sequence
-  is exact at $\Hom(G(\Fq),\EEx)$ and $\coker t_{\pi_0(G)} =0$
-  (by Propositions~\ref{prop:etale} and \ref{prop:X}) and
-  \[
-  \image(\CSiso{\pi_0(G)} \to \CSiso{G}) \subseteq \ker(\CSiso{G} \to \CSiso{G^0}),
-  \]
-  by the last part of Proposition~\ref{prop:pullback}. Specifically,
-  suppose $\cs{L}$ is a character sheaf on $G$ that is trivial on
-  $G^0$. Then $t^\Frob_\cs{L}\vert_{G^0(\Fq)} = t^\Frob_{\cs{L}^0} =0$,
-  by Proposition~\ref{prop:pullback} again. Since the sequence of
-  character groups is exact at $\Hom(G(\Fq),\EEx)$, there is
-  some $\chi \in \Hom(\pi_0(G)(\Fq),\EEx)$ such that the
-  pull-back of $\chi$ along $G(\Fq)\to \pi_0(G)(\Fq)$ is
-  $t^\Frob_\cs{L}$. By Propositions~\ref{prop:etale} and \ref{prop:X},
-  there is a a character sheaf $\cs{L}_\chi$ on $\pi_0(G)$, unique up
-  to isomorphism, such that $t^\Frob_{\cs{L}_\chi} = \chi$. By
-  Proposition~\ref{prop:pullback} again, $\cs{L}$ is isomorphic to the
-  image of $\cs{L}_\chi$ under the monoidal functor $\CS(\pi_0(G)) \to \CS(G)$.
-
-  It now follows immediately from the snake lemma that $t_{G}$ is an
-  isomorphism of groups.
-\end{proof}
+\section{Base change over the residue field}
 
@@
 
-\section{Application to characters of bounded depth}
-
-%\input{GdeN}
-Let $p$ be a prime number. Let $K$ be a local field with residue field
-$\Fq$, where $p$ divides $q$. Let $\OK$ be the ring of integers of $K$
-and let $\pK$ be the maximal ideal in $\OK$.
-%
-In this section we introduce a group scheme $\GN{T}$ over $\Fq$
-obtained by applying the Greenberg functor to the N\'eron lft-model
-for $T$ and establish some basic facts about $\GN{T}$
-
-%\subsection{The N\'eron locally finite type model for $T$}
-
-The lft-N\'eron model for $T$, denoted here by $\TT$, is a separated,
-smooth, commutative group scheme locally of finite type over $\OK$
-with generic fibre $T$, that enjoys the N\'eron mapping property: if
-$X$ is a smooth scheme over $\OK$ then every morphism $X_\eta \to T$
-over $K$ extends uniquely to a morphism $X \to \TT$. Equivalently, the
-N\'eron mapping property states that the function
-$\Hom_{\OK} (X,\TT) \to \Hom_K(X_\eta,T)$, given by restriction to
-generic fibres, is a bijection; in particular, this implies $\TT(\OK) = T(K)$.
-
-For each $d\in \ZZ_{>0}$, let $\TT_{d}$ be the smooth group scheme over
-$\OK/\pK^d$ obtained from $\TT$ by base change along $\OK \to
-\OK/\pK^d$. Observe that $\OK/\pK^d$ is an Artin ring and
-$\TT_{d}$ is locally of finite type over $\OK/\pK^d$.
-
-Let $\GN{T}_{d} = \Gr(\TT_d)$ be the group scheme over $\Fq$ produced by applying
-the Greenberg functor to $\TT_{d}$. (See \cite{Greenberg:2} and
-\cite[Ch. 9, \S 6]{BLR} for background on the Greenberg functor.)
-%Then $\GN{T}_d(\Fq) = \TT(\OK/\pK^d)$.
-
-\begin{proposition}\label{prop:GN}
-  Fundamental properties of the group $\Fq$-scheme $\GN{T}_d$, for all $d\in \NN$:
-  \begin{enumerate}
-  \labitem{(GNd.0)}{GN0} $\GN{T}_d^0$, the identity component of
-    $\GN{T}_d$, is a commutative algebraic group over $\Fq$;
-  \labitem{(GNd.1)}{GNd} $\GN{T}_d$ is smooth and locally of finite type over $\Fq$;
-  \labitem{(GNd.2)}{pi0} $\pi_0(\GN{T}_d) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$;
-  \labitem{(GNd.3)}{fg} the component group of $\GN{T}_d$ is geometrically finitely generated;
-  \labitem{(GNd.4)}{dFq} $\GN{T}_d(\Fq) = \TT(\OK/\pK^d)$, canonically;
-\end{enumerate}
-\end{proposition}
-
-\begin{proof}
-\Clifton{Proofs still missing, but all straightforward. I'll cite as much as I can, here.}
-\end{proof}
-
-%\input{application}
-\begin{theorem}\label{thm:application}
-  Let $T$ be an algebraic torus over a non-Archimedean local field $K$.
-  Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d \in \ZZ_{>0}$, the
-  Picard group of the category of character sheaves on $\GN{T}_d$ is
-  canonically isomorphic to the group of characters of $T(K)$ of depth
-  less than $d$:
-  \[
-  \CSiso{\GN{T}_d} \iso \Hom_{< d}(T(K),\EEx).
-  \]
-\end{theorem}
-
-\begin{proof}
-  By \ref{GNd} and \ref{fg}, we may apply Theorem~\ref{thm:snake} to
-  $\GN{T}_d$ which provides a canonical isomorphism
-  \[
-  \CSiso{\GN{T}_d} \iso \Hom(\GN{T}_d(\Fq),\EEx).
-  \]
-  By \ref{dFq}, $\GN{T}_d(\Fq) \iso \TT(\OK/\pK^d)$ canonically.
-  To finish the proof we recall that the filtration of $T(K)$ used to
-  define depth has the property that $\TT(\OK/\pK^d) \cong T(K) / T(K)_d$
-  \cite[Prop 5.2]{Yu} for $d \in \ZZ_{>0}$.  Thus characters of $\GN{T}_d(\Fq)$ are
-  in bijection with characters of $T(K)$ vanishing on $T(K)_d$.
-\end{proof}
-
-\section{Application to admissible characters}
-
-%\input{pro}
-To conclude the paper we offer an interpretation of
-Theorem~\ref{thm:application} that makes no mention of depth.
-
-\Clifton{Explain what happens as $d$ varies.}
-Suppose $d\leq d'$.
-
-We may now assemble the group $\Fq$-schemes $\TT_{d}$ into one
-glorious group pro-scheme over $\Fq$:
-\begin{equation}\label{projlim}
-  \GN{T} \ceq \varprojlim_{d\in \NN} \GN{T}_{d}.
-\end{equation}
-This is the \cdef{Greenberg transform of the lft-N\'eron model of $T$}; we will also write $\Gr$ for this functor on $\OK$-schemes.
-
-\Clifton{Prove that $\GN{T}$ is a scheme? Strictly speaking, we don't
-  care about \ref{scheme}.}
-
-\Clifton{Must still define $\CS(\GN{T})$, since it is not an instance
- of our definitions, above.}
-
-\begin{proposition}
-  Fundamental properties of $\GN{T}$:
-  \begin{enumerate}
-  \labitem{(GN.0)}{scheme} $\GN{T}$ is a commutative group scheme over $\Fq$;
-  \labitem{(GN.1)}{T(K)} $\GN{T}(\Fq) = T(K)$, canonically.
-  \end{enumerate}
-\end{proposition}
-
-\begin{corollary}
-  \[
-  \CSiso{\GN{T}} \iso \Hom_\text{ad}(T(K),\EEx)
-  \]
-\end{corollary}
-
-\section{Functorial properties of the main isomorphism}
+\section{Base change over the local field}
 
@@
 \]
-and thus a map on character sheaves.
+and thus a functor on character sheaves through pullback.
 
@@
 \Gr(\TT) \dar & \Gr(\TT) \times_{\Gr(\OK)} \Gr(\OL) \lar{\alpha} \rar{\beta} \dar & \Gr(\TL) \dar \\
-\Spec{k} & \Spec{k'} \lar \rar & \Spec{k'}
+\Spec{k} & \Spec{k'} \lar \rar & \Spec{k'}.
 \end{tikzcd}
@@
 
-\bib{BBD}{article}{
-   author={Be{\u\i}linson, A. A.},
-   author={Bernstein, J.},
-   author={Deligne, P.},
-   title={Faisceaux pervers},
-%   language={French},
-   conference={
-      title={Analyse et topologie sur les espaces singuliers (I)},
-      address={Luminy},
-      date={1981},
-   },
-   book={
-      series={Ast\'erisque},
-      volume={100},
-      publisher={Soc. Math. France},
-      place={Paris},
-   },
-   date={1982},
-%   pages={5--171},
-%   review={\MR{751966 (86g:32015)}},
-}
-
 \bib{BLR}{book}{
@@
 
-\bib{Brandal}{book}{
- author={Brandal, Willy},
- title={Commutative Rings whose Finitely Generated Modules Decompose},
- publisher={Springer-Verlag},
- date={1979},
- series={Lecture Notes in Mathematics}
- number={723}
-}
-
 \bib{Chai}{article}{
@@
 
-\bib{Deligne:tensorielles}{article}{
-   author={Deligne, P.},
-   title={Cat\'egories tensorielles},
-%   language={French, with English summary},
-%   note={à Yu. I. Manin, en témoignage d'admiration},
-   journal={Mosc. Math. J.},
-   volume={2},
-   date={2002},
-   number={2},
-   pages={227--248},
-%   issn={1609-3321},
-%   review={\MR{1944506 (2003k:18010)}},
-}
-
-\bib{Deligne:Weil2}{article}{
-   author={Deligne, Pierre},
-   title={La conjecture de Weil. II},
-%   language={French},
-   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
-   number={52},
-   date={1980},
-   pages={137--252},
-%   issn={0073-8301},
-%   review={\MR{601520 (83c:14017)}},
-}
-
-\bib{Greenberg:2}{article}{
-   author={Greenberg, Marvin J.},
-   title={Schemata over local rings. II},
-   journal={Ann. of Math. (2)},
-   volume={78},
-   date={1963},
-   pages={256--266},
-%   issn={0003-486X},
-%   review={\MR{0156855 (28 \#98)}},
-}
-
-\bib{SGA1a}{book}{
-   author={Grothendieck, Alexander},
-   title={Rev\^etements \'etales et groupe fondamental. Fasc. I: Expos\'es 1
-   \`a 5},
-   series={S\'eminaire de G\'eom\'etrie Alg\'ebrique},
-   volume={1960/61},
-   publisher={Institut des Hautes \'Etudes Scientifiques},
-   place={Paris},
-   date={1963},
-%   pages={iv+143 pp. (not consecutively paged) (loose errata)},
-%   review={\MR{0217087 (36 \#179a)}},
-}
-
-\bib{Laumon}{article}{
-   author={Laumon, G.},
-   title={Transformation de Fourier, constantes d'\'equations fonctionnelles
-   et conjecture de Weil},
-%   language={French},
-   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
-   number={65},
-   date={1987},
-   pages={131--210},
-%   issn={0073-8301},
-%   review={\MR{908218 (88g:14019)}},
-}
-
-\bib{SGA4.5}{book}{
-   author={Deligne, P.},
-   title={Cohomologie \'etale},
-   series={Lecture Notes in Mathematics, Vol. 569},
-   note={S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois-Marie 1963-64 SGA
-   4$\frac{1}{2}$; 
-   Avec la collaboration de J. F. Boutot, A. Grothendieck, L. Illusie et J.
-   L. Verdier},
-   publisher={Springer-Verlag},
-   place={Berlin},
-%date={4h},
-   date={1977},
-   pages={iv+312pp},
-%   review={\MR{0463174 (57 \#3132)}},
-}
-
-\bib{SGA7.2}{book}{
-   title={Groupes de monodromie en g\'eom\'etrie alg\'ebrique. II},
-%   language={French},
- author={Deligne, P.},
- author={Katz, N.},
-   series={Lecture Notes in Mathematics, Vol. 340},
-   note={S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois-Marie 1967--1969
-   (SGA 7 II);
-   Dirig\'e par P. Deligne et N. Katz},
-   publisher={Springer-Verlag},
-   place={Berlin},
-   date={1973},
-   pages={x+438},
-%   review={\MR{0354657 (50 \#7135)}},
-}
-
-\bib{Tate:thesis}{article}{
-   author={Tate, J. T.},
-   title={Fourier analysis in number fields, and Hecke's zeta-functions},
-   conference={
-      title={Algebraic Number Theory (Proc. Instructional Conf., Brighton,
-      1965)},
-   },
-   book={
-      publisher={Thompson, Washington, D.C.},
-   },
-   date={1967},
-   pages={305--347},
-   review={\MR{0217026 (36 \#121)}},
-}
-
-\bib{vdG&M}{book}{
-author={van der Geer},
-author={Moonen},
-title={Abelian Varieties},
-note={http://staff.science.uva.nl/$\sim$bmoonen/boek/BookAV.html}
-}
-
-\bib{Xarles}{article}{
-   author={Xarles, Xavier},
-   title={The scheme of connected components of the N\'eron model of an algebraic torus},
-   journal={J. Reine Angew. Math.},
-   volume={437},
-   date={1993},
-   pages={167--179},
-%   issn={0075-4102},
-%   review={\MR{1212256 (94d:14044)}},
-%   doi={10.1515/crll.1993.437.167},
-}
-
-\bib{Yu}{article}{
-   author={Yu, Jiu-Kang},
-   title={Smooth models associated to concave functions in Bruhat-Tits theory}
-}
-
 \end{biblist}

### 2013-07-30 shanghai.tex
Moved base change discussion to a new file

--- 2013-07-22 shanghai.tex
@@
 \documentclass[11pt]{amsart}
-\title[Geometration of characters of tori]{Geometrization of characters of tori over non-Archimedean local fields}
+\title[Geometrization of characters of tori]{Geometrization of characters of tori over non-Archimedean local fields}
 \usepackage[british]{babel}
@@
 \newcommand{\pK}{\mathfrak{p}_K}
+\newcommand{\OL}{\mathcal{O}_L}
+\newcommand{\OO}[1]{\mathcal{O}_{#1}}
 \newcommand{\Zp}{\mathbb{Z}_p}
@@
 
-When using character sheaves to study characters, it is useful to understand
-how character sheaves behave under change of fields.
-Suppose that $k'$ is a finite extension of $k$ of degree $n$, $G$ is an abelian group scheme
-over $k$ as in Theorem \ref{thm:snake} and $G_{k'}$ is the base change of $G$ to $k'$.
-If $\cs{L} = (\gcs{L}, \mu, F)$ is a character sheaf on $G$ we may define
-a character sheaf $\nu(\cs{L}) = (\gcs{L}, \mu, F_{k'})$ on $G_{k'}$ by setting
-\[
-F_{k'} = F \circ \Frob_G^*(F) \circ \cdots \circ (\Frob_G^{n-1})^*(F).
-\]
-The commutativity of the diagram (CS.2) for $F_{k'}$ follows from the fact that $\Frob_{G_{k'}} = \Frob_G^n$.
-Note that we may also think about the construction of $F_{k'}$ as taking the action of $\Weil{k}$ defined in Remark
-\ref{rem:CS-action} and restricting it to $\Weil{k'}$.
-
-\begin{proposition}
-The following diagram commutes:
-\[
-\begin{tikzcd}
-\CSiso{G} \rar{\nu} \dar{t_G} & \CSiso{G_{k'}} \dar{t_{G_{k'}}} \\
-\Hom(G(k), \EEx) \rar{\Nm} & \Hom(G(k'), \EEx).
-\end{tikzcd}
-\]
-\end{proposition}
-
-We define a functor $\CS(G_{k'}) \to \CS(G)$ by.... \David{We can't define this by pullback
-since $G_{k'} \to G$ goes in the wrong direction}
-\begin{proposition} \label{prop:csbe}
-The diagram
-\[
-\begin{tikzcd}
-\CSiso{G_{k'}} \arrow[two heads]{r} \dar & \CSiso{G} \dar \\
-\Hom(G(k'), \EEx) \arrow[two heads]{r} & \Hom(G(k), \EEx)
-\end{tikzcd}
-\]
-commutes, where the vertical arrows are as in Theorem \ref{thm:snake}.
-\end{proposition}
-
-Now suppose that $G'$ is an abelian group scheme over $k'$, satisfying the conditions of Theorem \ref{thm:snake}.
-There is a canonical isomorphism between $G'(k')$ and $(\Res_{k'/k}G')(k)$;
-we now describe the corresponding functor from
-$\CS(G')$ to $\CS(\Res_{k'/k}G')$.  The base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
-decomposes into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
-\[
-(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
-\]
-The component corresponding to the identity element yields a natural inclusion 
-\[
-G' \hookrightarrow (\Res_{k'/k}G')_{k'}
-\]
-of $k'$-schemes.  The definition of base change yields a map of $k$-schemes
-\[
-(\Res_{k'/k}G')_{k'} \to \Res_{k'/k}G'.
-\]
-Consecutive pullback along these maps yields a functor
-\[
-\CS(G') \to \CS(\Res_{k'/k}G').
-\]
-
-\begin{proposition}
-  Then the following diagram commutes:
-\[
-\begin{tikzcd}
-\CSiso{G} \rar{t_G} \dar & \Hom(G(k'), \EEx) \dar \\
-\CSiso{\Res_{k'/k} G} \rar{t_{\Res_{k'/k} G}} & \Hom((\Res_{k'/k}G)(k), \EEx)
-\end{tikzcd}
-\]
-\end{proposition}
-
 \section{Application to characters of bounded depth}
@@
 
-We have already seen that the trace of Frobenius defines a canonical isomorphism 
-$t_T : \CSiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
-In this section we expand on the canonicity of this group isomorphism 
-by showing that it is a natural transformation. We also show
-
-\begin{proposition}
-The isomorphism $t_T : \CSiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$ 
-is a natural transformation between the following two contravariant functors 
-from the category of algebraic tori over $K$ to the category of abelian groups: 
+\section{The transfer principle}
+
+We recall the notion of $N$-congruent tori from \cite[\S 2]{CY}.  Suppose $T$ and $T'$
+are tori over non-Archimedian local fields $K$ and $K'$, splitting over $L$ and $L'$ respectively.
+
+\begin{definition}
+We say that $T$ and $T'$ are \emph{$N$-congruent} if there are isomorphisms
+\begin{align*}
+\alpha : \OL/\pi_K^N \OL &\to \OO{L'}/\pi_{K'}^N \OO{L'} \\
+\beta : \Gal(L/K) &\to \Gal(L'/K') \\
+\phi : X^*(T) &\to X^*(T')
+\end{align*}
+satisfying the following conditions:
 \begin{enumerate}
-\item $T \mapsto \CSiso{\GN{T}}$
-\item $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
+\item $\alpha$ induces an isomorphism $\OK/\pi_K^N \OK \to \OO{K'}/\pi_{K'}^N \OO{K'}$,
+\item $\alpha$ is $\Gal(L/K)$-equivariant relative to $\beta$: $\alpha(\gamma x) = \beta(\gamma) \alpha(x)$
+for $\gamma \in \Gal(L/K)$ and $x \in \OL/\pi_K^N \OL$,
+\item $\phi$ is $\Gal(L/K)$-equivariant relative to $\beta$.
 \end{enumerate}
-\end{proposition}
-
-\Clifton{I think I can prove this proposition without too much difficulty.}
-\begin{proof}
-\end{proof}
-
-\begin{proposition}
-Let $K'/K$ be a finite Galois extension and let $T'$ be an algebraic torus over $K'$... 
-\Clifton{This next part is very much under construction.}
-The functor $\CS(\GN{T}) \to \CS(\GN{T}')$ defined above induces a group homomorphism 
-that commutes, through trace of Frobenius, with ...
-\[
-\begin{tikzcd}
-\CS(\GN{T}) \dar & \CSiso{\GN{T}} \rar{t_T} \dar & \Hom_\text{ad}(T(K),\EEx) \dar \\
-\CS(\GN{T}') & \CSiso{\GN{T}'} \rar{t_{T'}} & \Hom_\text{ad}(T'(K),\EEx)
-\end{tikzcd}
-\]
-\end{proposition}
-
-\begin{proof}
-\end{proof}
+\end{definition}
+
+One of the main results of \cite{CY} gives an isomorphism of group schemes between $\TT_d$ and $\TT'_d$ assuming that $T$ and $T'$ are sufficiently congruent.
+They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite[\S 8.1]{CY}.
+They then prove the following theorem:
+
+\begin{theorem}[{\cite[Thm. 8.5]{CY}}]
+Suppose that $T$ and $T'$ are $N$-congruent for $N > 3h$.  Then there is a canonical isomorphism
+\[
+\TT_{N-3h} \to \TT'_{N-3h}
+\]
+determined by $\alpha, \beta$ and $\phi$.
+\end{theorem}
 
@@
 
+\bib{Chai}{article}{
+   author={Chai, C.L.},
+   title={N\'eron models for semiabelian varieties: congruence and change of base field.},
+   journal={Asian J. Math.},
+   volume={4},
+   number={4},
+   date={2000},
+   pages={715--736}}
+
+\bib{CY}{article}{
+   author={Chai, C.L.},
+   author={Yu, J.-K.},
+   title={Congruences of N\'eron models for tori and the Artin conductor},
+   journal={Ann. of Math.},
+   volume={154},
+   number={2},
+   date={2001},
+   pages={347-382}}
+
 \bib{Deligne:tensorielles}{article}{

### 2013-07-31 shanghai.tex
Added on our result about the tranfer principle

@@
 
-\section{Functorial properties of the main isomorphism}
-
 \section{The transfer principle}
 
+\David{We should add a discussion of why we care about the transfer principle.}
 We recall the notion of $N$-congruent tori from \cite[\S 2]{CY}.  Suppose $T$ and $T'$
@@
 
-One of the main results of \cite{CY} gives an isomorphism of group schemes between $\TT_d$ and $\TT'_d$ assuming that $T$ and $T'$ are sufficiently congruent.
-They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite[\S 8.1]{CY}.
+One of the main results of \cite{CY} gives an isomorphism of group schemes between
+$\TT_d$ and $\TT'_d$ assuming that $T$ and $T'$ are sufficiently congruent.
+They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the
+Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite[\S 8.1]{CY}.
 They then prove the following theorem:
@@
 \end{theorem}
+
+As an immediate consequence of this theorem and Theorem \ref{thm:application} we have the following corollary:
+
+\begin{corollary}
+ Suppose that $T$ and $T'$ are $N$-congruent for $N > 3h$.  Then there is a canonical equivalence of categories
+ \[
+  \CS(\GN{T}_{N-3h}) \to \CS(\GN{T}'_{N-3h})
+ \]
+ determined by $\alpha, \beta$ and $\phi$ inducing the isomorphism
+ \[
+  \Hom(T(K) / T(K)_{N-3h}, \EEx) \to \Hom(T'(K') / T'(K')_{N-3h}, \EEx)
+ \]
+\end{corollary}
 

### 2013-08-07 shanghai.tex
bounded changes

--- 2013-07-27 shanghai.tex
@@
 
-%%%% Some Named Categories
-
-%%%% Functors
-
 \newcommand{\gal}[1]{{\operatorname{Gal}\hskip-1pt\left( {\bar #1}/#1 \right)}}
@@
 \newcommand{\Weil}[1]{\mathcal{W}_{#1}}
+\newcommand{\Loc}{{\operatorname{Loc}}}
 
@@
 
-%\subsection*{Pull-back of character sheaves}\label{subsection:pullback}
+\section{Pull-back of character sheaves}\label{subsection:pullback}
 
@@
 It is easy to see that $\CSiso{0}$ is trivial.
-In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; the snake lemma then allows us to find $\CSiso{G}$.
-
-\section{Bounded character sheaves}
-
-In this section we describe full subcategory of $\CS(G)$, 
-called the category of bounded character sheaves on $G$ and denoted by $\CS_b(G)$, 
-which will illuminate the nature of $\CS(G)$ and will also play a role in the arguments later in this paper.
-
-Consider the category $\GC(G)$ of finite etale covers of $G$ that are also morphisms of abelian group schemes.
-Recall that we fixed an algebraic closure $\bFq$ of $\Fq$ long ago; 
-let ${\bar e} : \Spec{\bFq} \to G$ be the geometric point on $G$ obtained by composing $\Spec{\bFq} \to \Spec{\Fq}$ with the identity $e : \Spec{\Fq} \to G$ for $G$.
-Let $\ker_{\bar e}$ be the set-valued functor on $\GC(G)$
-defined by pull-back along the geometric point ${\bar e} : \Spec{\bFq} \to G$ 
-followed by forgetting the structure sheaf and topology; 
-thus, if $f : H\to G$ is a finite etale morphism of group schemes, then $\ker_{\bar e}(f)$ is the set underlying 
-$\ker{\bar f} = H_{\bar e}$.
-Let $\pi_1^\text{gp}(G)$ be the automorphism group of the functor $\ker_{\bar e}$. 
-We will see that $\pi_1^\text{gp}(G)$ is a profinite abelian group.
-A \cdef{bounded character sheaf on $G$} is a continuous irreducible representation of $\pi_1^\text{gp}(G)$. 
-Let $\CS_b(G)$ be the monoidal category of irreducible continuous $\ell$-adic representations of $\pi_1^\text{gp}(G)$.
-
-\begin{proposition}
- $G\mapsto \pi_1^\text{gp}(G)$ is a functor from group schemes over $\Fq$ to profinite abelian groups, and .....
+In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; the snake lemma then allows us to show
+\[
+\CSiso{G} \iso \Hom(G(\Fq),\EE^\times).
+\]
+
+\section{Bounded character sheaves and finite character sheaves}\label{sec:bounded}
+
+ In this section we describe two full subcategories of $\CS(G)$
+ which will illuminate some features of $\CS(G)$ and also play a role in some arguments below.
+
+ Let $\CS_0(G)$ be the category of pairs $(\cs{L}_0,\mu_0)$ 
+where $\cs{L}_0$ is a constructible $\ell$-adic sheaf on $G$, 
+which is a rank-$1$ local system on each connected component of $G$, 
+equipped with an isomorphism $\mu_0 : m^* \cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ 
+satisfying the analogue of Condition~\ref{CS.1} on $G$; 
+morphisms in $\CS_f(G)$ are defined as in (the second part of) Condition~\ref{CS.2}. 
+This is the category of \cdef{bounded character sheaves} on $G$.
+
+Let $b_G : {\bar G} \to G$ be the pull-back of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
+If $(\cs{L}_0,\mu_0)$ is bounded character sheaf then $b_G^* \cs{L}_0$ comes equipped with an isomorphism $F : \Frob_G^* b_G^*\cs{L}_0 \to b_G^*\cs{L}_0$ which is compatible with $b_G^* \mu_0$, in the sense of Condition~\ref{CS.3}.
+Thus, base change gives us a functor $b_G^* : \CS_f(G) \to \CS(G)$.
+This functor is fully faithful; see \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.
+
+To define the category of finite character sheaves we must work a bit harder.
+Consider the following category $C(G)$:
+an object in $C(G)$ is a pair $(f,\psi)$ where: $f : H\to G$ is an isogeny (a finite, surjective, etale, morphism of commutative group $\Fq$-schemes) for which the action of $\Gal(\bFq/\Fq)$ on the etale group scheme $\ker f$ is trivial, and $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$;
+a map $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(\varphi,T)$ 
+where $\varphi$ is a morphism of schemes such that $f' = f\circ \varphi$
+and $T : V\to V'$ is a linear transformation equivariant 
+for the action of $\ker f'$ on $V'$ by $\psi'$ 
+and the action of $\ker f'$ on $V$ by $\psi \circ \varphi$.
+%
+We say that $(\varphi,T)$ in $C(G)$ is a weak isomorphism if $T$ is an isomorphism of vector spaces. Let $C(G)[W^{-1}]$ be the localization of $C(G)$ at weak isomorphisms.
+Now, let $C_1(G)$ be the subcategory of $C(G)$ such that $\psi$ is a one-dimensional representation
+and let $\CS_f(G)$ be the localisation of $C_1(G)$ at weak isomorphisms. This is the category of \cdef{finite character sheaves} on $G$.
+
+\begin{proposition}\label{prop:bounded}
+ $\CS_f(G)$ is (equivalent to) a full subcategory of $\CS_0(G)$.
 \end{proposition}
@@
 \begin{proof}
-The category $\GC(G)$, together with the set-valued functor $\ker_{\bar e}$ satisfy conditions (G1) through (G6) appearing in \cite[Exposé V, \S 4, p. 118-119]{SGA1a}.
+ To prove the proposition we exhibit a fully faithful monoidal functor $L_G : \CS_f(G) \to \CS_0(G)$.
+ %
+ We will do this by constructing a faithful monoidal functor $L : C_1(G) \to \CS_0(G)$ 
+ such that ${\bar L}(\varphi,T)$ is an isomorphism precisely when $(\varphi,T)$ is a weak isomorphism. 
+ Factoring along $C_1(G) \to \CS_0(G)$ will produce the full and faithful monoidal functor we seek.
+
+ We start by putting a tensor category structure on $C(G)$. 
+ Let $(f,\psi)$ and $(f',\psi')$ be objects in $C(G)$. 
+ The category of isogenies to $G$ admits products: 
+ write $f\times_G f' : H\times_G H' \to G$ for the product of $f : H\to G$ and $f' : H'\to G$. 
+ Since $\ker(f\times_G f') = (\ker f)\times (\ker f')$, 
+ the tensor product of the representations $\psi : \ker f\to \Aut(V)$ and $\psi' : \ker f'\to \Aut(V')$ 
+ is the representation $\psi \otimes\psi' :  \ker(f\times_G f') \to \Aut(V\otimes V')$. 
+ This allows us to set $(f,\psi)\otimes(f',\psi') \ceq (f\times_G f' ,\psi\otimes\psi')$. 
+ The same fact makes sense of $(f,\psi)\oplus(f',\psi')\ceq (f\times_G f' ,\psi\oplus\psi')$. 
+ The dual of $(f,\psi)$ is $(f,\psi)^\vee \ceq (f,\psi^\vee)$ 
+ where $\psi^\vee : \ker f \to \Aut(V^\vee)$ and $V^\vee = \Hom_\text{vec}(V,\EE)$. 
+ The verification that these operations make $C(G)$ a tensor category is routine.
+
+  It is also a matter of routine to verify that every morphism of group schemes $G'\to G$ 
+  induces a monoidal functor $C(G) \to C(G')$ by base-change along $G'\to G$ ({\it cf.}, Proposition~\ref{prop:pullback}); 
+  indeed, the pull-back of $(f,\psi)$ along any morphism $m : G'\to G$ of group schemes 
+  can be read off the short exact sequence obtained by pulling back along $m$. 
+  Taking the case when $m$ is the multiplication morphism $m : G\times G\to G$, 
+  and using the tensor category structure above, 
+  we see that the pull-back of $(f,\psi)$ along $m$ is canonically isomorphic, in $C_1(G\times G)$, to $(f,\psi)\boxtimes(f,\psi)$.
+
+ Now we introduce a faithful functor $L : C(G) \to \Loc(G)$ to the category of local systems on $G$.
+ For any object $(f,\psi)$ in $C(G)$, let $L(f,\psi)$ be the $\psi$-isotypic component of $f_* V_H$, 
+ where $V_H$ refers to $V$ as a constant sheaf on $H$. 
+ Note that we may identify the stalk $(f_* V_H)_{\bar g}$ of $f_* V_H$ at a geometric point ${\bar g}$ on $G$ 
+ with the $\EE$-vector space $\Hom_\text{set}(\abs{f^{-1}({\bar g})},V)$ 
+ and the stalk $L(f,\psi)_{\bar g}$ of $L(f,\psi)$ at a geometric point ${\bar g}$ on $G$ 
+ with the $\EE$-vector space consisting of those functions $s: \abs{f^{-1}({\bar g})} \to V$ such that 
+ $s(a\cdot {\bar h}) = \psi(a)(s({\bar h}))$ for all $a\in \ker f$ and for all ${\bar h} \in f^{-1}({\bar g})$.
+ Since $L(f,\psi)$ is trivialized by $f$, it is a local system on $G$.
+ For any map $(\varphi,T)$ in $C(G)$, let $L(\varphi,T) : L(f,\psi) \to L(f',\psi')$ be the homomorphism of local systems defined 
+ %at geometric points $L(\varphi,T)_{\bar g} : L(f,\psi)_{\bar g} \to L(f',\psi')_{\bar g}$ 
+ by $s \mapsto s' \ceq T\circ s\circ \varphi$. 
+ This defines a monoidal functor $L$ from $C(G)$ to $\Loc(G)$. 
+ This functor commutes with pull-back along any morphism of group schemes.
+
+ Now consider the localization $C(G)[W^{-1}]$ of $C(G)$ at weak isomorphisms.
+ Morphisms in $C(G)[W^{-1}]$ are simple to describe because category $C(G)$ 
+ admits a calculus of left fractions\footnote{See {\tt http://ncatlab.org/nlab/show/calculus+of+fractions}.} for weak isomorphisms: 
+ every isomorphism in $C(G)$ is a weak isomorphism; 
+ push-outs exist in $C(G)$ and the push-out of a weak isomorphism is a weak isomorphism; 
+ and weak isomorphisms enjoy the left-cancellation property. 
+ It follows that a morphism in $C(G)[W^{-1}]$ is the equivalence class of 
+  \[
+   \begin{tikzcd}
+   (f,\psi) \arrow{r}{(\varphi_1,T_1)} & (f_1,\psi_1) & \arrow[swap]{l}{(\varphi'_1,T'_1)} (f',\psi')
+   \end{tikzcd}
+  \]
+ where $(\varphi',T') : (f,\psi) \to (f',T')$ is any map in $C(G)$ 
+ and $(\varphi'_1,T'_1) : (f_1,\psi_1) \to (f',\psi')$ is a weak isomorphism; 
+ this morphism is commonly denoted by $(\varphi_1,T_1)^{-1}\circ (\varphi'_1,T'_1)$. 
+ %The equivalence relation identifies $(\varphi_1,T_1)^{-1}\circ (\varphi'_1,T'_1)$ 
+ % with $(\varphi_2,T_2)^{-1}\circ (\varphi'_2,T'_2)$ if there are maps 
+ %$(f_1,\psi_1)\to (f_0,\psi_0)$ and $(f_2,\psi_2)\to (f_0,\psi_0)$ making the following diagram commute
+ %\[
+ %  \begin{tikzcd}
+ %  & (f_1,\psi_1) \arrow{d} & \\
+ %  (f,\psi) \arrow{ur}{(\varphi_1,T_1)} \arrow{dr}{(\varphi_2,T_2)} & (f_0,\psi_0)  & \arrow[swap]{ld}{(\varphi'_2,T'_2)} \arrow[swap]{lu}{(\varphi'_1,T'_1)} (f',\psi')\\
+ %  & (f_2,\psi_2) \arrow{u} & \\
+ %  \end{tikzcd}
+ %\]
+ %where $(f',\psi') \to (f_0,\psi_0)$ is a weak isomorphism.
+
+ Observe that $L$ takes weak isomorphisms in $C(G)$ to isomorphisms in $\Loc(G)$.
+To see this, let $(\varphi,T) : (f,\psi)\to (f',\psi')$ be a weak isomorphism, where $f:H\to G$ and $f':H'\to G$ as above.
+Since $T$ is an isomorphism, we may replace $V'$ with $V$ and $T$ with $\id_V$, without loss of generality.
+Then the equivariance condition on $T$ becomes $\psi' = \psi\circ \varphi$ on the finite etale group scheme $\ker f'$.
+Since $f' = f \circ \varphi$ and $f$ and $f'$ are etale covers, it follows that $\varphi$ is also an etale cover.
+It follows that $\varphi : H'\to H$ admits a section $\varphi' : H \to H'$, which provides the inverse to $L(\varphi,T) : L(f,\psi) \to L(f',\psi')$, above.
+It is also clear that if $L(\varphi,T)$ is an isomorphism of local systems, then $T$ must be an isomorphism of vector spaces, whence $(\varphi,T)$ is a weak isomorphism: $W$ is saturated.
+
+ Since $L : C(G) \to \Loc(G)$ takes weak isomorphisms to isomorphisms,
+ it factors (uniquely!) through the localisation functor $C(G) \to C(G)[W^{-1}]$ 
+ to define a faithful functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$. 
+ Since $W$ is saturated, the functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$ is full. 
+ %
+ Finally, we are ready to exhibit the full functor $L_G: \CS_b(G) \to \CS_0(G)$ promised above. 
+ If $(f,\psi)$ in an object in $C_1(G)$ then, as we have already seen, 
+ $m^*L(f,\psi) \iso L(f,\psi) \boxtimes L(f,\psi)$ in $C_1(G\times G)$, canonically.
+ It follows immediately that 
+  \[
+  L_G  \ceq  L_{W}\vert_{\CS_b(G)} : \CS_b(G) \to \CS(G)
+  \]
+ is a fully faithfull monoidal functor, completing the proof.
 \end{proof}
+
+\Clifton{I'll address this point in the next section: "Because $\Gal(\bFq/\Fq)$ acts trivially on $\Aut({\bar f})$, the local system
+ ${\bar L}_G(f,\psi)\ceq b_G^* L(f,\psi)$ comes equipped with a canonical isomorphism 
+ $F : \Frob_G^* {\bar L}_G(f,\psi) \to {\bar L}_G(f,\psi)$ of constructible sheaves on ${\bar G}$."}
 
@@
   If $G$ is a geometrically connected commutative algebraic group over $\Fq$ then 
+  the full subcategories $\CS_b(G) \hookrightarrow \CS_0(G) \hookrightarrow \CS(G)$ 
+  appearing in Section~\ref{sec:bounded} are equivalences 
+  and
   \[
@@
 \begin{proof}
-  We will prove this proposition by reducing it to the functions--sheaves dictionary
-  \cite{Laumon}*{1.1}. The main point of this proof will therefore be to show that,
-  {\it since $G$ is geometrically connected}, every character sheaf on $G$ descends to
-  a local system on $G$ satisfying the analogue of \ref{CS.1} on $G$.
-
-  First, observe that the forgetful functor $(\gcs{L},\mu,F) \mapsto (\gcs{L},F)$
+ %Let $G$ be a geometrically connected algebraic group over $\Fq$.
+  Observe that the forgetful functor $(\gcs{L},\mu,F) \mapsto (\gcs{L},F)$
   sends character sheaves on $G$ to Weil local systems on
@@
   While is it not true that all Weil local systems on $G$
-  descend to sheaves on $G$, those that appear in the image of the
+  descend to local systems on $G$, we will see that those that appear in the image of the
   forgetful functor from character sheaves do. 
-
-  To see why this is so, consider the category \cdef{$\CS_0(G)$} of
-  pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$
-  and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \tight{0}{\boxtimes}{0} \cs{L}_0$ satisfies
-  condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$
-  are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}.
-  \David{This section should be modified once we're done with the section on bounded character sheaves}
-  Let $b : \bG \to G$ be base change
-  (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$).
-  The proof of Proposition~\ref{prop:pullback} adapts
-  (simplifies, in fact) to show that $b^* : \CS_0(G) \to \CS(G)$ is a
-  monoidal functor. This functor is fully faithful; see
-  \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.  We will
-  show that $b^*$ is essentially surjective.
+  Then we will see that these local systems further appear in the image of
 
@@
 
+\bib{Kamgarpour}{article}{
+   author={Kamgarpour, Masoud},
+   title={Stacky abelianization of algebraic groups},
+   journal={Transform. Groups},
+   volume={14},
+   date={2009},
+   number={4},
+   pages={825--846},
+%   issn={1083-4362},
+%   review={\MR{2577200 (2011b:20136)}},
+%   doi={10.1007/s00031-009-9067-8},
+}
+
 \bib{Laumon}{article}{

### 2013-08-07 shanghai.tex

@@
 
-When using character sheaves to study characters, it is useful to understand
-how character sheaves behave under change of fields.
-Suppose that $k'$ is a finite extension of $k$ of degree $n$, $G$ is an abelian group scheme
-over $k$ as in Theorem \ref{thm:snake} and $G_{k'}$ is the base change of $G$ to $k'$.
-If $\cs{L} = (\gcs{L}, \mu, F)$ is a character sheaf on $G$ we may define
-a character sheaf $\nu(\cs{L}) = (\gcs{L}, \mu, F_{k'})$ on $G_{k'}$ by setting
-\[
-F_{k'} = F \circ \Frob_G^*(F) \circ \cdots \circ (\Frob_G^{n-1})^*(F).
-\]
-The commutativity of the diagram (CS.2) for $F_{k'}$ follows from the fact that $\Frob_{G_{k'}} = \Frob_G^n$.
-Note that we may also think about the construction of $F_{k'}$ as taking the action of $\Weil{k}$ defined in Remark
-\ref{rem:CS-action} and restricting it to $\Weil{k'}$.
-
-\begin{proposition}
-The following diagram commutes, where the bottom map is induced by the norm $G(k') \rightarrow G(k)$:
-\[
-\begin{tikzcd}
-\CSiso{G} \rar{\nu} \dar{t_G} & \CSiso{G_{k'}} \dar{t_{G_{k'}}} \\
-\Hom(G(k), \EEx) \rar{\Nm} & \Hom(G(k'), \EEx).
-\end{tikzcd}
-\]
-\end{proposition}
-
-In the opposite direction, there is a canonical closed immersion of $k$-schemes
-$G \hookrightarrow \Res_{k'/k}(G_{k'})$ \cite[\S 7.6]{BLR}.  Pullback yields a functor
-\[
-\CS(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota} \CS(G).
-\]
-\begin{proposition} \label{prop:csbe}
-The following diagram commutes, where the bottom map is induced by the inclusion $G(k) \hookrightarrow G(k')$:
-\[
-\begin{tikzcd}
-\CSiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota} \dar{t_{\Res_{k'/k}(G_{k'})}} & \CSiso{G} \dar{t_G} \\
-\Hom(G(k'), \EEx) \arrow[two heads]{r} & \Hom(G(k), \EEx).
-\end{tikzcd}
-\]
-\end{proposition}
-
-Now suppose that $G'$ is an abelian group scheme over $k'$, satisfying the conditions of Theorem \ref{thm:snake}.
-There is a canonical isomorphism between $G'(k')$ and $(\Res_{k'/k}G')(k)$;
-we now describe the corresponding functor from
-$\CS(G')$ to $\CS(\Res_{k'/k}G')$.  The base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
-decomposes into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
-\[
-(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
-\]
-The component corresponding to the identity element yields a natural inclusion 
-\[
-G' \hookrightarrow (\Res_{k'/k}G')_{k'}
-\]
-of $k'$-schemes.  The definition of base change yields a map of $k$-schemes
-\[
-(\Res_{k'/k}G')_{k'} \to \Res_{k'/k}G'.
-\]
-Consecutive pullback along these maps yields a functor
-\[
-\CS(G') \to \CS(\Res_{k'/k}G').
-\]
-
-\begin{proposition}
-  Then the following diagram commutes:
-\[
-\begin{tikzcd}
-\CSiso{G'} \dar{t_{G'}} \rar & \CSiso{\Res_{k'/k} G'} \dar{t_{\Res_{k'/k} G'}} \\
- \Hom(G'(k'), \EEx) \rar & \Hom((\Res_{k'/k}G')(k), \EEx)
-\end{tikzcd}
-\]
-\end{proposition}
-
 \section{Application to characters of bounded depth}
@@
 
-\section{Functorial properties of the main isomorphism}
-
-We have already seen that the trace of Frobenius defines a canonical isomorphism 
-$t_T : \CSiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
-In this section we expand on the canonicity of this group isomorphism 
-by showing that it is a natural transformation. We also show
-
-\begin{proposition}
-The isomorphism $t_T : \CSiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$ 
-is a natural transformation between the following two contravariant functors 
-from the category of algebraic tori over $K$ to the category of abelian groups: 
+\section{The transfer principle}
+
+\David{We should add a discussion of why we care about the transfer principle.}
+We recall the notion of $N$-congruent tori from \cite[\S 2]{CY}.  Suppose $T$ and $T'$
+are tori over non-Archimedian local fields $K$ and $K'$, splitting over $L$ and $L'$ respectively.
+
+\begin{definition}
+ We say that $T$ and $T'$ are \emph{$N$-congruent} if there are isomorphisms
+ \begin{align*}
+  \alpha : \OL/\pi_K^N \OL &\to \OO{L'}/\pi_{K'}^N \OO{L'} \\
+  \beta : \Gal(L/K) &\to \Gal(L'/K') \\
+  \phi : X^*(T) &\to X^*(T')
+ \end{align*}
+ satisfying the following conditions:
  \begin{enumerate}
-\item $T \mapsto \CSiso{\GN{T}}$
-\item $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
+  \item $\alpha$ induces an isomorphism $\OK/\pi_K^N \OK \to \OO{K'}/\pi_{K'}^N \OO{K'}$,
+  \item $\alpha$ is $\Gal(L/K)$-equivariant relative to $\beta$: $\alpha(\gamma x) = \beta(\gamma) \alpha(x)$
+  for $\gamma \in \Gal(L/K)$ and $x \in \OL/\pi_K^N \OL$,
+  \item $\phi$ is $\Gal(L/K)$-equivariant relative to $\beta$.
  \end{enumerate}
-\end{proposition}
-
-\Clifton{I think I can prove this proposition without too much difficulty.}
-\begin{proof}
-\end{proof}
-
-Let $L/K$ be a finite Galois extension and let $K'/K$ be the maximal unramified subextension, with residue field $k'$.
-If $T$ is a torus over $K$, write $\TL$ for the N\'eron model of the base change $T_L$.
-Then there is a canonical isomorphism
-\[
-\Res_{k'/k} \Gr(\TL) \cong \Gr(\underline{\Res_{L/K}(T_L)}).
-\]
-The natural inclusion $T \hookrightarrow \Res_{L/K} T_L$ induces a map of $k$-schemes
-\[
-\GN{T} \hookrightarrow \Res_{k'/k} \Gr(\TL)
-\]
-and thus a map on character sheaves.
-
-\begin{proposition}
-The following diagram commutes:
-\[
-\begin{tikzcd}
-\CSiso{\Res_{k'/k} \Gr(\TL)} \arrow[two heads]{r} \dar & \CSiso{\GN{T}} \dar\\
-\Hom(T(L), \EEx) \arrow[two heads]{r} & \Hom(T(K), \EEx)
-\end{tikzcd}
-\]
-\end{proposition}
-
-We now translate the norm map $T(L) \to T(K)$ to character sheaves.  There is an open immersion
-\[
-\TT \times_{\OK} \OL \to \TL
-\]
-induced by the canonical isomorphism of generic fibers \cite[p. 1]{Chai}.  After taking Greenberg transforms,
-we obtain a diagram
-\[
-\begin{tikzcd}
-\Gr(\TT) \dar & \Gr(\TT) \times_{\Gr(\OK)} \Gr(\OL) \lar{\alpha} \rar{\beta} \dar & \Gr(\TL) \dar \\
-\Spec{k} & \Spec{k'} \lar \rar & \Spec{k'}
-\end{tikzcd}
-\]
-In the case that $L/K$ is unramified, the left hand square is a pullback square and the right hand horizontal maps are isomorphisms.  In general, we may define a functor
-\begin{align*}
-\CS(\GN{T}) &\to \CS(\Gr(\TL)) \\
-\cs{L} &\mapsto \beta_* \alpha^* \cs{L}.
-\end{align*}
-
-\begin{proposition}
-The following diagram commutes:
-\[
-\begin{tikzcd}
-\CSiso{\GN{T}} \rar{\beta_* \circ \alpha^*} \dar & \CSiso{\Gr(\TL)} \dar \\
-\Hom(T(K), \EEx) \rar{\Nm} & \Hom(T(L), \EEx)
-\end{tikzcd}
-\]
-\end{proposition}
+\end{definition}
+
+One of the main results of \cite{CY} gives an isomorphism of group schemes between
+$\TT_d$ and $\TT'_d$ assuming that $T$ and $T'$ are sufficiently congruent.
+They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the
+Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite[\S 8.1]{CY}.
+They then prove the following theorem:
+
+\begin{theorem}[{\cite[Thm. 8.5]{CY}}]
+ Suppose that $T$ and $T'$ are $N$-congruent for $N > 3h$.  Then there is a canonical isomorphism
+ \[
+  \TT_{N-3h} \to \TT'_{N-3h}
+ \]
+ determined by $\alpha, \beta$ and $\phi$.
+\end{theorem}
+
+As an immediate consequence of this theorem and Theorem \ref{thm:application} we have the following corollary:
+
+\begin{corollary}
+ Suppose that $T$ and $T'$ are $N$-congruent for $N > 3h$.  Then there is a canonical equivalence of categories
+ \[
+  \CS(\GN{T}_{N-3h}) \to \CS(\GN{T}'_{N-3h})
+ \]
+ determined by $\alpha, \beta$ and $\phi$ inducing the isomorphism
+ \[
+  \Hom(T(K) / T(K)_{N-3h}, \EEx) \to \Hom(T'(K') / T'(K')_{N-3h}, \EEx)
+ \]
+\end{corollary}
 
@@
 
+\bib{CY}{article}{
+   author={Chai, C.L.},
+   author={Yu, J.-K.},
+   title={Congruences of N\'eron models for tori and the Artin conductor},
+   journal={Ann. of Math.},
+   volume={154},
+   number={2},
+   date={2001},
+   pages={347-382}}
+
 \bib{Deligne:tensorielles}{article}{

### 2013-08-08 shanghai.tex
I'm in the middle of the proposition on connected abelian algebraic groups.
Shown: all character sheaves on connected algebraic groups decend to
`bounded' character sheaves. Next I'll prove that all bounded character
sheaves are finite character sheaves on connected algebraic groups.

@@
 
-\section{Introduction}
+\section*{Introduction}
 
@@
 
-\section{The Picard group of character sheaves}\label{section:category}
-
-%\input{category}
-%\subsection*{Smooth commutative group schemes}
+\section{The category of character sheaves}\label{section:category}
 
@@
 
-%\subsection*{The category of character sheaves}
-
 The category of character sheaves on $G$, denoted by \cdef{$\CS(G)$},
@@
 \begin{enumerate}
-\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a constructible $\ell$-adic
-  sheaf on (the \'etale site of) $\bG$, locally constant of rank
-  $1$ on connected components of $\bG$;
-
+\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a rank-$1$ $\ell$-adic
+  local system on (the \'etale site of) $\bG$;
 \labitem{(CS.1)}{CS.1} $\mu: \bm^* \gcs{L} \to \LxL$
-  is an isomorphism of sheaves on $\bGxG$ such that
-
-  \[
-  \begin{tikzcd}[row sep=40]
+  is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
+  where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
+%
+  \[
+  \begin{tikzcd}[row sep=30]
   \bm_3^*\gcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
@@
   \]
-  commutes, where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
-
+
+%
 \labitem{(CS.2)}{CS.2} $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ is an
-  isomorphism of sheaves on $\bG$ compatible with $\mu$ in the sense that
-
-  \[
-  \begin{tikzcd}
+  isomorphism of sheaves on $\bG$ compatible with $\mu$ in the sense that the following diagram commutes.
+%
+  \[
+  \begin{tikzcd}[row sep=20]
   \Frob_{\GxxG}^* \bm^* \gcs{L} \arrow{rr}{\Frob_{\GxxG}^*\mu}
@@
   \]
-  commutes.
 \end{enumerate}
@@
   $\cs{L'} = (\gcs{L'},\mu',F')$ are character sheaves on $G$ then
-  $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$
-  of constructible $\ell$-adic sheaves on $\bG$ such that
+  $\Hom_{\CS(G)}(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$
+  of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
   \[
@@
   \]
-  both commute.
 \end{enumerate}
 
-%\subsection*{The Picard group of character sheaves}
+\section{The Picard group of character sheaves}
 
@@
 
-%\subsection*{Trace of Frobenius}\label{sec:Frob}
+\section{Trace of Frobenius}\label{sec:Frob}
 
@@
   \[
-  \begin{tikzcd}[row sep=40]
+  \begin{tikzcd}[row sep=30, column sep=30]
    \CSiso{G} \rar{f^*} \arrow[swap]{d}{t_{G}} & \CSiso{H} \dar{t_H} \\
@@
 Thus, base change gives us a functor $b_G^* : \CS_f(G) \to \CS(G)$.
-This functor is fully faithful; see \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.
+This functor is full and faithful; see \cite{SGA7.2}*{Expos\'e XIII} or even \cite{BBD}*{Prop. 5.2.1}.
 
@@
 \begin{proof}
- To prove the proposition we exhibit a fully faithful monoidal functor $L_G : \CS_f(G) \to \CS_0(G)$.
+ To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \CS_f(G) \to \CS_0(G)$.
  %
@@
  Observe that $L$ takes weak isomorphisms in $C(G)$ to isomorphisms in $\Loc(G)$. 
-To see this, let $(\varphi,T) : (f,\psi)\to (f',\psi')$ be a weak isomorphism, where $f:H\to G$ and $f':H'\to G$ as above.
+ To see this, let $(\varphi,T) : (f,\psi)\to (f',\psi')$ be a weak isomorphism, 
+ where $f:H\to G$ and $f':H'\to G$ as above. 
  Since $T$ is an isomorphism, we may replace $V'$ with $V$ and $T$ with $\id_V$, without loss of generality. 
@@
  Since $f' = f \circ \varphi$ and $f$ and $f'$ are etale covers, it follows that $\varphi$ is also an etale cover. 
-It follows that $\varphi : H'\to H$ admits a section $\varphi' : H \to H'$, which provides the inverse to $L(\varphi,T) : L(f,\psi) \to L(f',\psi')$, above.
-It is also clear that if $L(\varphi,T)$ is an isomorphism of local systems, then $T$ must be an isomorphism of vector spaces, whence $(\varphi,T)$ is a weak isomorphism: $W$ is saturated.
+ It follows that $\varphi : H'\to H$ admits a section $\varphi' : H \to H'$, 
+ which provides the inverse to $L(\varphi,T) : L(f,\psi) \to L(f',\psi')$, above. 
+ It is also clear that if $L(\varphi,T)$ is an isomorphism of local systems, 
+ then $T$ must be an isomorphism of vector spaces, 
+ whence $(\varphi,T)$ is a weak isomorphism: $W$ is saturated.
 
@@
   \[
-  L_G  \ceq  L_{W}\vert_{\CS_b(G)} : \CS_b(G) \to \CS(G)
-  \]
- is a fully faithfull monoidal functor, completing the proof.
+  L_G  \ceq  L_{W}\vert_{\CS_b(G)} : \CS_b(G) \to \CS_0(G)
+  \]
+ is a full and faithfull monoidal functor, completing the proof.
 \end{proof}
@@
 \begin{proposition}\label{prop:connected-1}
-  If $G$ is a geometrically connected commutative algebraic group over $\Fq$ then 
-  the full subcategories $\CS_b(G) \hookrightarrow \CS_0(G) \hookrightarrow \CS(G)$ 
+  If $G$ is a connected commutative algebraic group over $\Fq$ then 
+  the full subcategories $\CS_f(G) \hookrightarrow \CS_0(G) \hookrightarrow \CS(G)$ 
   appearing in Section~\ref{sec:bounded} are equivalences 
@@
   \[
-  t_{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx),
+  t_{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)
   \]
@@
   Observe that the forgetful functor $(\gcs{L},\mu,F) \mapsto (\gcs{L},F)$
-  sends character sheaves on $G$ to Weil local systems on
-  $G$ \cite{Deligne:Weil2}*{1.1.10} (by a Weil local system on $G$ we
-  mean a Weil sheaf on $G$ which is a local system on $\bG$).
-  While is it not true that all Weil local systems on $G$
-  descend to local systems on $G$, we will see that those that appear in the image of the
-  forgetful functor from character sheaves do. 
-  Then we will see that these local systems further appear in the image of
-
-  Let $g$ be any $\Fq$-rational point on $G$ (such as the identity for
-  $G$) and let $\bg$ be the geometric point on $G$ lying above
-  $g$ (we fixed $\Fq \hookrightarrow \bFq$ long ago). Since $G$ is
-  geometrically connected, the geometric point $\bg$ determines
-  an equivalence between the category of Weil local systems on $G$ and
-  $\ell$-adic representations of $\W(G,\bg)$
-  \cite{Deligne:Weil2}*{1.1.12}. Now let $(\gcs{L},\mu,F)$ be a
-  character sheaf on $G$. Then the isomorphism class of the Weil local
-  system $(\gcs{L},F)$ corresponds to an $\ell$-adic character of the
-  Weil group $\W(G, \bg)$. The $\Fq$-rational point $g$ under
-  the geometric point $\bg$ determines a splitting
-  $\Weil{\Fq}\to \W(G,\bg)$ of the exact sequence
-  \[
-  \begin{tikzcd}
-  1 \rar & \pi_1(\bG, \bg) \rar &  \W(G,\bg) \rar
-  & \ar[swap,bend right, dotted]{l}{g} \Weil{\Fq} \rar & 1
-  \end{tikzcd}
-  \]
-  In this way the Weil local system $(\gcs{L},F)$ determines an $\ell$-adic character
-  \[
-  t_{(\gcs{L},F)}(g) : \Weil{\Fq} \to \EEx \qquad \text{defined by}\qquad \Frob \mapsto t^\Frob_{(\gcs{L},F)}(g)
-  \]
-  of the Weil group $\Weil{\Fq}$; the image of $\Frob$ under this
-  character is $t^\Frob_\cs{L}(g)$, the trace of Frobenius of $\cs{L}$ at $g$.
+  sends character sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{Deligne:Weil2}*{1.1.10}.
+  While is it not true that all Weil sheaves on $G$ descend to local systems on $G$, 
+  we will see that those that appear in the image of this forgetful functor from character sheaves do.
+
+  Let $g$ be any $\Fq$-rational point on $G$ 
+  and let $\bg$ be the geometric point on $G$ lying above $g$ (we fixed $\Fq \hookrightarrow \bFq$ long ago). 
+  Since $G$ is connected, the geometric point $\bg$ determines
+  an equivalence between the category of $\ell$-adic Weil local systems on $G$ and
+  $\ell$-adic representations of $\W(G,\bg)$ \cite{Deligne:Weil2}*{1.1.12}. 
+  Now let $(\gcs{L},\mu,F)$ be a character sheaf on $G$ 
+  and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gcs{L},F)$. 
+  The $\Fq$-rational point $g$ under the geometric point $\bg$ determines a splitting
+  $\Weil{\Fq}\to \W(G,\bg)$ of $\W(G,\bg)\to \Weil{\Fq}$. 
+  In this way the Weil local system $(\gcs{L},F)$ determines an $\ell$-adic character $\rho_g : \Weil{\Fq} \to \EEx$.
+  %\[
+  %\begin{tikzcd}
+  %1 \rar & \pi_1(\bG, \bg) \rar &  \arrow{d}{\rho} \W(G,\bg) \rar
+  %& \ar[swap,bend right, dotted]{l}{g} \arrow[dotted]{dl}{\rho_g} \Weil{\Fq} \rar & 1\\
+  %&&\EEx&&
+  %\end{tikzcd}
+  %\]
+  This character is given by the trace of Frobenius of $\cs{L}$ at $g$, as defined in Section~\ref{sec:Frob}:
+  \[
+  \rho_g(\Frob) =  t^\Frob_\cs{L}(g).
+  \]
 
@@
   variety over $\Fq$, so finitely generated over $\Fq$, so $G(\Fq)$ is finite;
-  it follows that $t^\Frob_\cs{L}(g) = t^\Frob_{(\gcs{L},F)}(g)$ is a root of unity,
+  it follows that $t^\Frob_\cs{L}(g) = \rho_g(\Frob)$ is a root of unity,
   for every $g\in G(\Fq)$.  Since $\Weil{\Fq}$ is generated by
-  $\Frob$ and $t_{(\gcs{L},F)}(g) : \Weil{\Fq} \to \EEx$ is
-  a character, it follows that the image of $t_{(\gcs{L},F)}(g)$ is a
-  finite subset of $\mu(\EE)$. Thus, $t_{(\gcs{L},F)}(g)$ extends to
-  an $\ell$-adic character of $\Gal(\bFq/\Fq)$, which will be denoted
-  by the same symbol.
+  $\Frob$ and $\rho_g : \Weil{\Fq} \to \EEx$ is
+  a character, it follows that the image of $\rho_g$ is a finite group.
+  Thus, $\rho_g$ extends to an $\ell$-adic character of $\Gal(\bFq/\Fq)$, 
+  denoted by the same symbol, below.
   \[
   \begin{tikzcd}
-  1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \W(G,\bg) \rar \dar & \Weil{\Fq} \rar \dar & 1\\
-  1 \rar &  \pi_1(\bG, \bg) \rar & \pi_1(G,\bg) \rar & \Gal(\bFq/\Fq) \rar & 1
-  \end{tikzcd}
-  \]
-
-  We may now lift the $\ell$-adic character $t_{(\gcs{L},F)}(g) : \Gal(\bFq/\Fq) \to \EEx$
-  to an $\ell$-adic character of $\pi_1(G,\bg)$ using the canonical topological group map
-  $\pi_1(G,\bg) \to \Gal(\bFq/\Fq)$, above. But $\bg$ also
+  1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \W(G,\bg) \rar \dar & \Weil{\Fq} \arrow[bend left]{rr}{\rho_g} \rar \dar & 1 & \EEx\\
+  1 \rar &  \pi_1(\bG, \bg) \rar & \pi_1(G,\bg) \rar & \Gal(\bFq/\Fq) \arrow[dotted]{rru} \rar & 1 &
+  \end{tikzcd}
+  \]
+
+  We may now lift the $\ell$-adic character $\rho_g : \Gal(\bFq/\Fq) \to \EEx$
+  to an $\ell$-adic character $\pi_1(G,\bg) \to \EEx$ using the canonical topological group homomorphism
+  $\pi_1(G,\bg) \to \Gal(\bFq/\Fq)$ determined by the structure map for $G$. But $\bg$ also
   determines an equivalence between the category of $\ell$-adic
-  representations of $\pi_1(G,\bg)$ and local systems on $G$. Let
+  representations of $\pi_1(G,\bg)$ and $\ell$-adic local systems on $G$. Let
   $\cs{L}_0$ be a local system on $G$ in the isomorphism class
   determined by this $\ell$-adic character of $\pi_1(G,\bg)$.
-  Then $b^*\cs{L}_0 \iso \gcs{L}$, so $b^*$ is essentially surjective.
-
-  We have now shown that $b^* : \CS_0(G) \to \CS(G)$ is an equivalence
-  of rigid monoidal categories. It follows immediately that $b^*$
+  Then $b_G^*\cs{L}_0 \iso \gcs{L}$.
+  Since $b_G^*$ is full and faithful (again, see \cite{SGA7.2}*{Expos\'e XIII} or even \cite{BBD}*{Prop. 5.2.1}),
+  $
+  b_G^* : \Hom(m^*\cs{L}_0,\cs{L}_0\boxtimes\cs{L}_0) \to \Hom({\bar m}^*\gcs{L},\gcs{L}\boxtimes\gcs{L})
+  $ 
+  is a bijection. Let $\mu_0 : m^*\cs{L}_0 \to \cs{L}_0\boxtimes\cs{L}_0$ be the isomorphism matching 
+  $\mu : {\bar m}^*\gcs{L} \to \gcs{L}\boxtimes\gcs{L}$, from the definition of $\cs{L}$. 
+  Then $(\cs{L}_0,\mu_0)$ is an object in $\CS_0(G)$ 
+  and $\cs{L} = (\gcs{L},\mu,F)$ is isomorphic to $(b_G^*\cs{L}_0,b_G^*\mu_0)$ in $\CS(G)$.
+  Thus, $b_G^* : \CS_0(G) \to \CS(G)$ is essentially surjective.
+
+  \todo{Clifton is here. I will use \cite{Kamgarpour} to finish the proof.}
+
+  We have now shown that $b_G^* : \CS_0(G) \to \CS(G)$ is an equivalence
+  of rigid monoidal categories. It follows immediately that $b_G^*$
   determines an isomorphism
   \[
-  b^* : \CSbiso{G} \mathop{\longrightarrow}^{\iso} \CSiso{G}
+  b_G^* : \CSbiso{G} \mathop{\longrightarrow}^{\iso} \CSiso{G}
   \]

### 2013-08-08 shanghai.tex
(1) Still working on connected algebraic groups. (2) I made a home for the lemma we discussed yesterday.

@@
   Let $g$ be any $\Fq$-rational point on $G$ 
-  and let $\bg$ be the geometric point on $G$ lying above $g$ (we fixed $\Fq \hookrightarrow \bFq$ long ago). 
+  and let $\bg$ be the geometric point on $G$ lying above $g$ 
+  (we fixed $\Fq \hookrightarrow \bFq$ long ago). 
   Since $G$ is connected, the geometric point $\bg$ determines
@@
   and $\cs{L} = (\gcs{L},\mu,F)$ is isomorphic to $(b_G^*\cs{L}_0,b_G^*\mu_0)$ in $\CS(G)$.
-  Thus, $b_G^* : \CS_0(G) \to \CS(G)$ is essentially surjective.
+  Thus, the full and faithful functor $b_G^* : \CS_0(G) \to \CS(G)$ is also essentially surjective,
+  hence an equivalence (when $G$ is a connected, commutative algebraic group over $\Fq$).
+
+  In Proposition~\ref{prop:bounded} we saw that $\CS_f(G)$ is a full subcategory of $\CS_0(G)$;
+  more precisely, we exhibited a full and faithful functor $L_G : \CS_f(G) \to \CS_0(G)$.
+  We now show that this functor is essentially surjective 
+  when $G$ is a connected, commutative algebraic group over $\Fq$.
+  Let $(\cs{L}_0,\mu_0)$ be a bounded character sheaf.
 
@@
   $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ we must pick a global section of the line
-  bundle $(\gcs{L},\mu)$, for each character sheaf $\cs{L}$ on $G$. We
-  will show that the group isomorphism does not depend on these
+  bundle $(\gcs{L},\mu)$, for each character sheaf $\cs{L}$ on $G$; 
+  such a section exists by Lemma~\ref{lemma:section}.
+  We will show that the group isomorphism does not depend on these
   choices.
-
-  First, however, we show that such global sections exist.  Since
-  $G(\bFq)$ is finitely-generated abelian, it admits a decomposition
-  $G(\bFq) \iso G(\bFq)_\text{free} \oplus G(\bFq)_\text{tors}$ such
-  that $G(\bFq)_\text{tors}$ is finite.  Let $x_1, \ldots , x_r$ be a
-  basis for the free part $G(\bFq)_\text{free}$ of $G(\bFq)$ and let
-  $y_1, \ldots , y_t$ be a generators for the torsion part of
-  $G(\bFq)$ corresponding to the decomposition
-  $G(\bFq)_\text{tors} \iso \oplus_{j=1}^t \ZZ/m_j\ZZ$, with
-  $m_j \vert m_{j+1}$. For each such $x_i$ pick $s(x_i)\in \gcs{L}_{x_i}$;
-  for each such $y_j$ pick $s(y_j) \in \gcs{L}_{y_j}$; also set
-  $s({\bar e}) \ceq 0 \in \gcs{L}_{\bar e}$. ....
-  \Clifton{I'll finish this later.}
-  In this way we define a section
-  $s \ceq s_\cs{L} : G(\bFq) \to \coprod_{z\in G(\bFq)} \gcs{L}_z$ of
-  projection $\coprod_{z\in G(\bFq)} \gcs{L}_z \to G(\bFq)$ such that
-
-  \begin{equation}\label{section}
-    \forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes s(y).
-  \end{equation}
-  Under the equivalence at the beginning of this section, $s = s_\cs{L}$
-  corresponds to a global section of the line bundle $(\gcs{L},\mu)$.
-
-\Clifton{I'm going to remove all mention of line bundles from this paper.}
-
+%
   We use the section $s_\cs{L}$ to define a cocycle $z_\cs{L} \in Z^1(\Weil{\Fq},G(\bFq)^*)$
@@
   \Clifton{Straightforward, yes, but it still needs to be written down here.}
+\end{proof}
+
+\begin{lemma}
+ If $\cs{L}$ is a character sheaf then there is a non-trivial section of $\gcs{L}$ 
+ compatible with $\mu$ in the sense that 
+ \begin{equation}\label{section}
+  \forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes s(y).
+ \end{equation}
+\end{lemma}
+
+\begin{proof}
+First, however, we show that such global sections exist.  Since
+  $G(\bFq)$ is finitely-generated abelian, it admits a decomposition
+  $G(\bFq) \iso G(\bFq)_\text{free} \oplus G(\bFq)_\text{tors}$ such
+  that $G(\bFq)_\text{tors}$ is finite.  Let $x_1, \ldots , x_r$ be a
+  basis for the free part $G(\bFq)_\text{free}$ of $G(\bFq)$ and let
+  $y_1, \ldots , y_t$ be a generators for the torsion part of
+  $G(\bFq)$ corresponding to the decomposition
+  $G(\bFq)_\text{tors} \iso \oplus_{j=1}^t \ZZ/m_j\ZZ$, with
+  $m_j \vert m_{j+1}$. For each such $x_i$ pick $s(x_i)\in \gcs{L}_{x_i}$;
+  for each such $y_j$ pick $s(y_j) \in \gcs{L}_{y_j}$; also set
+  $s({\bar e}) \ceq 0 \in \gcs{L}_{\bar e}$. ....
+  \todo{under construction}
+  In this way we define a section
+  $s \ceq s_\cs{L} : G(\bFq) \to \coprod_{z\in G(\bFq)} \gcs{L}_z$ of
+  projection $\coprod_{z\in G(\bFq)} \gcs{L}_z \to G(\bFq)$ such that
+  $\mu_{x,y}(s(x+y)) = s(x)\otimes s(y)$ for all $x,y \in G(\bFq)$.
+  Under the equivalence at the beginning of this section, $s = s_\cs{L}$
+  corresponds to a global section of the line bundle $(\gcs{L},\mu)$.
+
+\Clifton{I'm going to remove all mention of line bundles from this paper.}
 \end{proof}

### 2013-08-08 shanghai.tex
Moving computers (in flagrante delicto)

@@
 
-\newcommand{\cdef}[1]{{{\color{cyan}#1}\index{#1}}} 
+\newcommand{\cdef}[1]{{{\color{blue}#1}\index{#1}}} 
 \newcommand{\sheafHom}{{\mathscr{H}\hskip-4pt{\it o}\hskip-2pt{\it m}}}
@@
 structure on the set $\CSiso{G}$ of isomorphism classes in
-$\CS(G)$; we refer to this as the \cdef{Picard group} of character
-sheaves on $G$; {\it cf.} {\tt http://ncatlab.org/nlab/show/Picard+group}.
+$\CS(G)$; we refer to this as the \cdef{Picard group of character
+sheaves} on $G$; {\it cf.} {\tt http://ncatlab.org/nlab/show/Picard+group}.
 \Clifton{Replace ncatlab with other references.}
@@
 \end{equation}
-It is easy to see that $\CSiso{0}$ is trivial.
-In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; the snake lemma then allows us to show
-\[
-\CSiso{G} \iso \Hom(G(\Fq),\EE^\times).
-\]
-
-\section{Bounded character sheaves and finite character sheaves}\label{sec:bounded}
-
- In this section we describe two full subcategories of $\CS(G)$
- which will illuminate some features of $\CS(G)$ and also play a role in some arguments below.
+It is easy to see that $\CSiso{0}$ is trivial. In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; 
+the snake lemma will then allow us to show
+\[
+\CSiso{G} \iso \Hom(G(\Fq),\EE^\times),
+\]
+canonically.
+
+\section{Bounded character sheaves}\label{sec:bounded}
 
@@
 
+\begin{proposition}
+$\CS_0(G)$ is (equivalent to) a full subcategory of $\CS(G)$.
+\end{proposition}
+
+\begin{proof}
  Let $b_G : {\bar G} \to G$ be the pull-back of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
-If $(\cs{L}_0,\mu_0)$ is bounded character sheaf then $b_G^* \cs{L}_0$ comes equipped with an isomorphism $F : \Frob_G^* b_G^*\cs{L}_0 \to b_G^*\cs{L}_0$ which is compatible with $b_G^* \mu_0$, in the sense of Condition~\ref{CS.3}.
-Thus, base change gives us a functor $b_G^* : \CS_f(G) \to \CS(G)$.
-This functor is full and faithful; see \cite{SGA7.2}*{Expos\'e XIII} or even \cite{BBD}*{Prop. 5.2.1}.
+ Let $(\cs{L}_0,\mu_0)$ be a bounded character sheaf on $G$. 
+ Then $\cs{L}_0$ is, in particular, an $\ell$-adic constructible sheaf on $G$. 
+ Then $b_G^* \cs{L}_0$ comes equipped with an isomorphism 
+ $F : \Frob_G^* b_G^*\cs{L}_0 \to b_G^* \cs{L}_0$; 
+ moreover, the functor $\cs{L}_0 \mapsto (b_G^* \cs{L}_0,F)$  
+ from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
+ is full and faithful; see \cite{SGA7.2}*{Expos\'e XIII} or even \cite{BBD}*{Prop. 5.2.1}. 
+ This functor preserves local constancy, so takes local systems to local systems. 
+ Set $\mu = b_{G\times G}^*\mu_0$; clearly, this satisfies Condition~\ref{CS.2} 
+ with $b_G^*\cs{L}_0$ playing the role of $\gcs{L}$.
+ Moreover, $F$ is compatible with $\mu$ in the sense of Condition~\ref{CS.3}.
+ It follows that functor $(\cs{L}_0,\mu_0) \mapsto (b_G^*\cs{L}_0,b_{G\times G}^* \mu_0, F)$, denoted by  $B_G^*: \CS_0(G) \hookrightarrow \CS(G)$ below, is full and faithful.
+\end{proof}
+
+\Clifton{Address the elephant in the room: Is $B_G^*: \CS_0(G) \hookrightarrow \CS(G)$ an equivalence?
+I'm pretty sure I can show that the answer is `no', using trace of Frobenius, as you have suggested.}
+
+\section{Finite character sheaves}\label{sec:finite}
+
+ %In this section we describe a full subcategory of $\CS_0(G)$
+ %which will illuminate some features of $\CS_0(G)$ and also play a role in some arguments below.
 
@@
   we see that the pull-back of $(f,\psi)$ along $m$ is canonically isomorphic, in $C_1(G\times G)$, to $(f,\psi)\boxtimes(f,\psi)$.
+
+ \Clifton{Insert diagram here.}
 
@@
  %
- Finally, we are ready to exhibit the full functor $L_G: \CS_b(G) \to \CS_0(G)$ promised above. 
+ Finally, we are ready to exhibit the full functor $L_G: \CS_f(G) \to \CS_0(G)$ promised above. 
  If $(f,\psi)$ in an object in $C_1(G)$ then, as we have already seen, 
- $m^*L(f,\psi) \iso L(f,\psi) \boxtimes L(f,\psi)$ in $C_1(G\times G)$, canonically.
+ $m^*L(f,\psi) \iso L(f,\psi) \boxtimes L(f,\psi)$ in $C_1(G\times G)$, canonically;
+ let $\mu(f,\psi)$ be that isomorphism of $\ell$-adic sheaves on $G$,
  It follows immediately that 
   \[
-  L_G  \ceq  L_{W}\vert_{\CS_b(G)} : \CS_b(G) \to \CS_0(G)
+  L_G  \ceq  L_{W}\vert_{\CS_f(G)} : \CS_b(G) \to \CS_0(G) 
+  \qquad\text{defined by}\qquad 
+  (f,\psi) \mapsto (L(f,\psi), \mu(f,\psi))
   \]
@@
   $
-  b_G^* : \Hom(m^*\cs{L}_0,\cs{L}_0\boxtimes\cs{L}_0) \to \Hom({\bar m}^*\gcs{L},\gcs{L}\boxtimes\gcs{L})
+  b_{G\times G}^* : \Hom(m^*\cs{L}_0,\cs{L}_0\boxtimes\cs{L}_0) \to \Hom({\bar m}^*\gcs{L},\gcs{L}\boxtimes\gcs{L})
   $ 
-  is a bijection. Let $\mu_0 : m^*\cs{L}_0 \to \cs{L}_0\boxtimes\cs{L}_0$ be the isomorphism matching 
-  $\mu : {\bar m}^*\gcs{L} \to \gcs{L}\boxtimes\gcs{L}$, from the definition of $\cs{L}$. 
-  Then $(\cs{L}_0,\mu_0)$ is an object in $\CS_0(G)$ 
-  and $\cs{L} = (\gcs{L},\mu,F)$ is isomorphic to $(b_G^*\cs{L}_0,b_G^*\mu_0)$ in $\CS(G)$.
-  Thus, the full and faithful functor $b_G^* : \CS_0(G) \to \CS(G)$ is also essentially surjective,
-  hence an equivalence (when $G$ is a connected, commutative algebraic group over $\Fq$).
-
-  In Proposition~\ref{prop:bounded} we saw that $\CS_f(G)$ is a full subcategory of $\CS_0(G)$;
+  is a bijection 
+  (hom taken in the categories on constructible $\ell$-adic sheaves on 
+  $G\times G$ and ${\bar G}\times {\bar G}$ respectively, 
+  in which $\ell$-adic local systems sit as full subcategories). 
+  Let $\mu_0 : m^*\cs{L}_0 \to \cs{L}_0\boxtimes\cs{L}_0$ be the isomorphism matching 
+  $\mu : {\bar m}^*\gcs{L} \to \gcs{L}\boxtimes\gcs{L}$, 
+  the latter appearing in the definition of $\cs{L}$. 
+  Then, as in Section~\ref{sec:bounded}, $(\cs{L}_0,\mu_0)$ is an object in $\CS_0(G)$ 
+  and $\cs{L} = (\gcs{L},\mu,F)$ is isomorphic to $(b_G^*\cs{L}_0,b_{G\times G}^*\mu_0)$ in $\CS(G)$.
+  Thus, the full and faithful functor $B_G^* : \CS_0(G) \to \CS(G)$ from Section~\ref{sec:bounded}
+  is also essentially surjective, hence an equivalence.
+  %(when $G$ is a connected, commutative algebraic group over $\Fq$).
+
+  In Section~\ref{sec:finite} we saw that $\CS_f(G)$ is a full subcategory of $\CS_0(G)$;
   more precisely, we exhibited a full and faithful functor $L_G : \CS_f(G) \to \CS_0(G)$.
@@
   when $G$ is a connected, commutative algebraic group over $\Fq$.
-  Let $(\cs{L}_0,\mu_0)$ be a bounded character sheaf.
+
+  Let $(\cs{L}_0,\mu_0)$ be a bounded character sheaf on $G$. 
+  Then $\cs{L}\ceq B_G^*(\cs{L}_0,\mu_0)$ is a character sheaf on $G$.
+  Recall the definition of the character $t_\cs{L}^\Frob : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}. 
+  Let $f : G\to G$ be the Lang isogeny.
+  Recall that $\ker f = G(\Fq) = G^\Frob$; 
+  in particular, the action of $\Gal(\bFq/\Fq)$ on $\ker f$ is trivial.
+  Let $V = \EE$ and let $\psi : \ker f \to \Aut(V)$ be the representation given by 
+  $\psi(g)(v) = t_\cs{L}^\Frob(g) v$ for $v\in V$. 
+  Then $(f,\psi)$ is a finite character sheaf.
+
+  The local system $L(f,\psi)$ (defined in Section~\ref{sec:finite}) naturally
+
+  To see that $L_G(f,\psi) \iso (\cs{L}_0,\mu_0)$ we simply apply the functions--sheaves dictionary
+
+  We will see that $L_G(f,\psi) \iso (\cs{L}_0,\mu_0)$, 
+  where $L_G$ is the functor constructed in Section~\ref{sec:finite}.
+  Since we have already seen (in Section~\ref{sec:finite}) that $L_G$ is full and faithful, 
+  it will then follow that $L_G$ is an equivalence.
 

### 2013-08-08 shanghai.tex
Going home.

@@
 $\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', F\otimes F')$
-with duals formed by applying the functor $\sheafHom(\ - \ ,(\EE)_{\bG})$ to
+with duals given by applying the functor $\sheafHom(\ - \ ,(\EE)_{\bG})$ (sheaf hom) to
 conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}.
@@
 that $\Aut_{\EE}(\gcs{L}_{\bg}) \iso \EEx$, canonically (this
-follows from second condition appearing in the definition of character
-sheaves). The isomorphism $\mu : \bm^* \gcs{L} \to \LxL$
+follows from the Condition~\ref{CS.1}). The isomorphism $\mu : \bm^* \gcs{L} \to \LxL$
 guarantees that the function $t^\Frob_\cs{L} : G(\Fq)\to \EEx$,
@@
   \[
-  \begin{tikzcd}[row sep=30, column sep=30]
+  \begin{tikzcd}[row sep=20, column sep=30]
    \CSiso{G} \rar{f^*} \arrow[swap]{d}{t_{G}} & \CSiso{H} \dar{t_H} \\
@@
   Finally, the fact that $(f\circ g)^* = g^* \circ f^*$ follows from the analogous
-  statements about pullbacks of sheaves and maps of sheaves.
-  \David{Is this explanation of $(f\circ g)^* = g^* \circ f^*$ sufficient?}
+  statements about the pullbacks functor on $\ell$-adic constructible sheaves.
+ % \David{Is this explanation of $(f\circ g)^* = g^* \circ f^*$ sufficient?}
 \end{proof}
@@
 This is the category of \cdef{bounded character sheaves} on $G$. 
+This is a rigid monoidal category in the obvious way, 
+with duals given by $\cs{L}_0^\vee \ceq \sheafHom(\cs{L}_0,(\EE)_{G})$.
 
@@
 Consider the following category $C(G)$:
-an object in $C(G)$ is a pair $(f,\psi)$ where: $f : H\to G$ is an isogeny (a finite, surjective, etale, morphism of commutative group $\Fq$-schemes) for which the action of $\Gal(\bFq/\Fq)$ on the etale group scheme $\ker f$ is trivial, and $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$;
+an object in $C(G)$ is a pair $(f,\psi)$ where: 
+$f : H\to G$ is an isogeny (a finite, surjective, etale, morphism of commutative group $\Fq$-schemes) 
+for which the action of $\Gal(\bFq/\Fq)$ on the etale group scheme $\ker f$ is trivial, 
+and $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$;
 a map $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(\varphi,T)$ 
@@
 %
-We say that $(\varphi,T)$ in $C(G)$ is a weak isomorphism if $T$ is an isomorphism of vector spaces. Let $C(G)[W^{-1}]$ be the localization of $C(G)$ at weak isomorphisms.
+We say that $(\varphi,T)$ in $C(G)$ is a weak isomorphism if $T$ is an isomorphism of vector spaces. 
+Let $C(G)[W^{-1}]$ be the localization of $C(G)$ at weak isomorphisms.
 Now, let $C_1(G)$ be the subcategory of $C(G)$ such that $\psi$ is a one-dimensional representation
-and let $\CS_f(G)$ be the localisation of $C_1(G)$ at weak isomorphisms. This is the category of \cdef{finite character sheaves} on $G$.
+and let $\CS_f(G)$ be the localisation of $C_1(G)$ at weak isomorphisms. 
+This is the category of \cdef{finite character sheaves} on $G$.
+
+\Clifton{Add the monoidal category structure here.}
 
@@
  The verification that these operations make $C(G)$ a tensor category is routine.
-
-  It is also a matter of routine to verify that every morphism of group schemes $G'\to G$ 
-  induces a monoidal functor $C(G) \to C(G')$ by base-change along $G'\to G$ ({\it cf.}, Proposition~\ref{prop:pullback}); 
-  indeed, the pull-back of $(f,\psi)$ along any morphism $m : G'\to G$ of group schemes 
-  can be read off the short exact sequence obtained by pulling back along $m$. 
-  Taking the case when $m$ is the multiplication morphism $m : G\times G\to G$, 
-  and using the tensor category structure above, 
-  we see that the pull-back of $(f,\psi)$ along $m$ is canonically isomorphic, in $C_1(G\times G)$, to $(f,\psi)\boxtimes(f,\psi)$.
-
- \Clifton{Insert diagram here.}
 
@@
  Since $W$ is saturated, the functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$ is full.
- %
- Finally, we are ready to exhibit the full functor $L_G: \CS_f(G) \to \CS_0(G)$ promised above. 
+
+ One more ingredient is needed before we can exhibit the full functor $L_G: \CS_f(G) \to \CS_0(G)$ promised above: 
+ we must put rigid monoidal category structures on $\CS_f(G)$ and $\CS_0(G)$.
+
+  It is also a matter of routine to verify that every morphism of group schemes $G'\to G$ 
+  induces a monoidal functor $C(G) \to C(G')$ by base-change along $G'\to G$ ({\it cf.}, Proposition~\ref{prop:pullback}); 
+  indeed, the pull-back of $(f,\psi)$ along any morphism $m : G'\to G$ of group schemes 
+  can be read off the short exact sequence obtained by pulling back along $m$. 
+  Taking the case when $m$ is the multiplication morphism $m : G\times G\to G$, 
+  and using the tensor category structure above, 
+  we see that the pull-back of $(f,\psi)$ along $m$ is canonically isomorphic, in $C_1(G\times G)$, to $(f,\psi)\boxtimes(f,\psi)$.
+  \Clifton{I need to work on this diagram and explain better what's going on here. Under construction.}
+  \[
+   \begin{tikzcd}
+V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow{r}  & H \arrow{r}{f} & G \\
+V & \Aut(V) \arrow[equal]{u} & \arrow[swap]{l}{\psi_{m_H}} \ker (f\times f) \arrow{r} \arrow{u}{m_H} & \arrow{d} H\times H \arrow{r}{f\times f} \arrow{u}{m_H} & G\times G \arrow{u}{m} \\
+V\otimes V & \Aut(V\otimes V) & \arrow[swap]{l}{\psi\otimes \psi} \ker f \times \ker f \arrow{r}  & H\times H \arrow{r}{f\times f}  & G\times G \arrow[equal]{u} \\
+   \end{tikzcd}
+  \]
+
  If $(f,\psi)$ in an object in $C_1(G)$ then, as we have already seen, 
@@
  let $\mu(f,\psi)$ be that isomorphism of $\ell$-adic sheaves on $G$,
- It follows immediately that 
-  \[
-  L_G  \ceq  L_{W}\vert_{\CS_f(G)} : \CS_b(G) \to \CS_0(G) 
-  \qquad\text{defined by}\qquad 
-  (f,\psi) \mapsto (L(f,\psi), \mu(f,\psi))
-  \]
+ It follows immediately that the functor $L_G  \ceq  L_{W}\vert_{\CS_f(G)} : \CS_b(G) \to \CS_0(G)$, 
+ given on objects by $(f,\psi) \mapsto (L(f,\psi), \mu(f,\psi))$,
  is a full and faithfull monoidal functor, completing the proof.
@@
 
-\Clifton{I'll address this point in the next section: "Because $\Gal(\bFq/\Fq)$ acts trivially on $\Aut({\bar f})$, the local system
- ${\bar L}_G(f,\psi)\ceq b_G^* L(f,\psi)$ comes equipped with a canonical isomorphism 
- $F : \Frob_G^* {\bar L}_G(f,\psi) \to {\bar L}_G(f,\psi)$ of constructible sheaves on ${\bar G}$."}
+%\Clifton{I'll address this point in the next section: "Because $\Gal(\bFq/\Fq)$ acts trivially on $\Aut({\bar f})$, the local system ${\bar L}_G(f,\psi)\ceq b_G^* L(f,\psi)$ comes equipped with a canonical isomorphism $F : \Frob_G^* {\bar L}_G(f,\psi) \to {\bar L}_G(f,\psi)$ of constructible sheaves on ${\bar G}$."}
 
@@
   appearing in Section~\ref{sec:bounded} are equivalences 
-  and
+  and (with reference to Section~\ref{sec:Frob})
   \[
@@
 
-  The local system $L(f,\psi)$ (defined in Section~\ref{sec:finite}) naturally
-
-  To see that $L_G(f,\psi) \iso (\cs{L}_0,\mu_0)$ we simply apply the functions--sheaves dictionary
-
-  We will see that $L_G(f,\psi) \iso (\cs{L}_0,\mu_0)$, 
-  where $L_G$ is the functor constructed in Section~\ref{sec:finite}.
+  We now show that $L_G(f,\psi) \iso (\cs{L}_0,\mu_0)$. 
+  First, recall that $L_G(f,\psi) = (L(f,\psi), \mu(f,\psi))$. 
+  By  \cite{Laumon}*{1.1.3.3}, $t_{L(f,\psi)}^{\Frob^n} = t_{\cs{L}}^{\Frob}\circ N_{\FF_{q^n}/\FF_q}$, for each positive integer $n$
+  On the other hand, $t_{\cs{L}}^{\Frob}\circ N_{\FF_{q^n}/\FF_q} = 
+  Using notation from \cite{Laumon}*{1.1},  this means $t_{\bullet L(f,\psi)} = t_{\bullet \cs{L}_0}$.
+  It now \cite{Laumon}*{Th\'eor\`eme~1.1.2}, it follows that  $L(f,\psi) \iso \cs{L}_0$ in $\Loc(G)$ (admittedly, this is a big hammer).
+
+   we simply apply the functions--sheaves dictionary
+  (see \cite{Laumon}*{1.1.3} or \cite{SGA4.5}*{Sommes trigonométriques}) as follows.
+
+  As we saw in Section~\ref{sec:finite}, the $\ell$-adic local system $L(f,\psi)$ on $G$ comes equipped with an isomorphism
+  $m^* L(f,\psi) \iso L(f,\psi) \boxtimes L(f,\psi)$ in $\CS_b(G)$; 
+  in the case at hand, this isomorphism is \cite[1.1.3.2]{Laumon}.
+  By \cite[1.1.3.2]{Laumon},
+
   Since we have already seen (in Section~\ref{sec:finite}) that $L_G$ is full and faithful, 

### 2013-08-09 base change.tex
Moved some material on (finite field) base change from base change.tex to shanghai.tex. Also, finished the proof of the proposition on connected commutative algebraic groups.

@@
 
-\section{Base change over the residue field}
-
-When using character sheaves to study characters, it is useful to understand
-how character sheaves behave under change of fields.
-Suppose that $k'$ is a finite extension of $k$ of degree $n$, $G$ is an abelian group scheme
-over $k$ as in Theorem \ref{thm:snake} and $G_{k'}$ is the base change of $G$ to $k'$.
-If $\cs{L} = (\gcs{L}, \mu, F)$ is a character sheaf on $G$ we may define
-a character sheaf $\nu(\cs{L}) = (\gcs{L}, \mu, F_{k'})$ on $G_{k'}$ by setting
-\[
-F_{k'} = F \circ \Frob_G^*(F) \circ \cdots \circ (\Frob_G^{n-1})^*(F).
-\]
-The commutativity of the diagram (CS.2) for $F_{k'}$ follows from the fact that $\Frob_{G_{k'}} = \Frob_G^n$.
-Note that we may also think about the construction of $F_{k'}$ as taking the action of $\Weil{k}$ defined in Remark
-\ref{rem:CS-action} and restricting it to $\Weil{k'}$.
-
-\begin{proposition}
-The following diagram commutes, where the bottom map is induced by the norm $G(k') \rightarrow G(k)$:
-\[
-\begin{tikzcd}
-\CSiso{G} \rar{\nu} \dar{t_G} & \CSiso{G_{k'}} \dar{t_{G_{k'}}} \\
-\Hom(G(k), \EEx) \rar{\Nm} & \Hom(G(k'), \EEx).
-\end{tikzcd}
-\]
-\end{proposition}
+\section{Restriction of scalars}
 

### 2013-08-09 shanghai.tex
Moved some material on (finite field) base change from base change.tex to shanghai.tex. Also, finished the proof of the proposition on connected commutative algebraic groups.

@@
 \newcommand{\CS}{{\mathcal{C\hskip-1.8pt S}}}
-\newcommand{\GC}{{\mathcal{G\hskip-0.8pt C}}}
+\newcommand{\CSb}{{\mathcal{C\hskip-1.8pt S}_0}}
+\newcommand{\CSf}{{\mathcal{C\hskip-1.8pt S}_{f}}}
 \newcommand{\CSiso}[1]{\CS(#1)_{/\textit{iso}}}
-\newcommand{\CSbiso}[1]{\CS_0(#1)_{/\text{iso}}}
+\newcommand{\CSbiso}[1]{\CSb(#1)_{/\text{iso}}}
+\newcommand{\CSfiso}[1]{\CSf(#1)_{/\text{iso}}}
 \newcommand{\CE}{{\mathcal{C\hskip-1.8pt E}}}
@@
 
+\section{Base change over the residue field}\label{sec:basechange}
+
+When using character sheaves to study characters, it is useful to understand
+how character sheaves behave under change of fields.
+Suppose that $k'$ is a finite extension of $k$ of degree $n$, $G$ is an abelian group scheme
+over $k$ as in Theorem \ref{thm:snake} and $G_{k'}$ is the base change of $G$ to $k'$.
+If $\cs{L} = (\gcs{L}, \mu, F)$ is a character sheaf on $G$ we may define
+a character sheaf $\nu(\cs{L}) = (\gcs{L}, \mu, F_{k'})$ on $G_{k'}$ by setting
+\[
+F_{k'} = F \circ \Frob_G^*(F) \circ \cdots \circ (\Frob_G^{n-1})^*(F).
+\]
+The commutativity of the diagram (CS.2) for $F_{k'}$ follows from the fact that $\Frob_{G_{k'}} = \Frob_G^n$.
+Note that we may also think about the construction of $F_{k'}$ as taking the action of $\Weil{k}$ defined in Remark
+\ref{rem:CS-action} and restricting it to $\Weil{k'}$.
+
+\begin{proposition}\label{prop:basechange}
+The following diagram commutes, where the bottom map is induced by the norm $G(k') \rightarrow G(k)$:
+\[
+\begin{tikzcd}
+\CSiso{G} \rar{\nu} \dar{t_G} & \CSiso{G_{k'}} \dar{t_{G_{k'}}} \\
+\Hom(G(k), \EEx) \rar{\Nm} & \Hom(G(k'), \EEx).
+\end{tikzcd}
+\]
+\end{proposition}
+
+\begin{proof}
+\todo{This proof is missing.}
+\end{proof}
+
 \section{Bounded character sheaves}\label{sec:bounded}
 
-Let $\CS_0(G)$ be the category of pairs $(\cs{L}_0,\mu_0)$ 
+Let $\CSb(G)$ be the category of pairs $(\cs{L}_0,\mu_0)$ 
 where $\cs{L}_0$ is a constructible $\ell$-adic sheaf on $G$, 
@@
 satisfying the analogue of Condition~\ref{CS.1} on $G$; 
-morphisms in $\CS_f(G)$ are defined as in (the second part of) Condition~\ref{CS.2}. 
+morphisms in $\CSf(G)$ are defined as in (the second part of) Condition~\ref{CS.2}. 
 This is the category of \cdef{bounded character sheaves} on $G$. 
@@
 \begin{proposition}
-$\CS_0(G)$ is (equivalent to) a full subcategory of $\CS(G)$.
+$\CSb(G)$ is (equivalent to) a full subcategory of $\CS(G)$.
 \end{proposition}
@@
  Moreover, $F$ is compatible with $\mu$ in the sense of Condition~\ref{CS.3}.
- It follows that functor $(\cs{L}_0,\mu_0) \mapsto (b_G^*\cs{L}_0,b_{G\times G}^* \mu_0, F)$, denoted by  $B_G^*: \CS_0(G) \hookrightarrow \CS(G)$ below, is full and faithful.
+ It follows that functor $(\cs{L}_0,\mu_0) \mapsto (b_G^*\cs{L}_0,b_{G\times G}^* \mu_0, F)$, denoted by  $B_G^*: \CSb(G) \hookrightarrow \CS(G)$ below, is full and faithful.
 \end{proof}
 
-\Clifton{Address the elephant in the room: Is $B_G^*: \CS_0(G) \hookrightarrow \CS(G)$ an equivalence?
-I'm pretty sure I can show that the answer is `no', using trace of Frobenius, as you have suggested.}
-
 \section{Finite character sheaves}\label{sec:finite}
 
- %In this section we describe a full subcategory of $\CS_0(G)$
- %which will illuminate some features of $\CS_0(G)$ and also play a role in some arguments below.
+ %In this section we describe a full subcategory of $\CSb(G)$
+ %which will illuminate some features of $\CSb(G)$ and also play a role in some arguments below.
 
@@
 Now, let $C_1(G)$ be the subcategory of $C(G)$ such that $\psi$ is a one-dimensional representation
-and let $\CS_f(G)$ be the localisation of $C_1(G)$ at weak isomorphisms. 
+and let $\CSf(G)$ be the localisation of $C_1(G)$ at weak isomorphisms. 
 This is the category of \cdef{finite character sheaves} on $G$.
@@
 \begin{proposition}\label{prop:bounded}
- $\CS_f(G)$ is (equivalent to) a full subcategory of $\CS_0(G)$.
+ $\CSf(G)$ is (equivalent to) a full subcategory of $\CSb(G)$.
 \end{proposition}
@@
 \begin{proof}
- To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \CS_f(G) \to \CS_0(G)$.
+ To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \CSf(G) \to \CSb(G)$.
  %
- We will do this by constructing a faithful monoidal functor $L : C_1(G) \to \CS_0(G)$ 
+ We will do this by constructing a faithful monoidal functor $L : C_1(G) \to \CSb(G)$ 
  such that ${\bar L}(\varphi,T)$ is an isomorphism precisely when $(\varphi,T)$ is a weak isomorphism. 
- Factoring along $C_1(G) \to \CS_0(G)$ will produce the full and faithful monoidal functor we seek.
+ Factoring along $C_1(G) \to \CSb(G)$ will produce the full and faithful monoidal functor we seek.
 
@@
 
- One more ingredient is needed before we can exhibit the full functor $L_G: \CS_f(G) \to \CS_0(G)$ promised above: 
- we must put rigid monoidal category structures on $\CS_f(G)$ and $\CS_0(G)$.
+ One more ingredient is needed before we can exhibit the full functor $L_G: \CSf(G) \to \CSb(G)$ promised above: 
+ we must put rigid monoidal category structures on $\CSf(G)$ and $\CSb(G)$.
 
@@
  let $\mu(f,\psi)$ be that isomorphism of $\ell$-adic sheaves on $G$,
- It follows immediately that the functor $L_G  \ceq  L_{W}\vert_{\CS_f(G)} : \CS_b(G) \to \CS_0(G)$, 
+ It follows immediately that the functor $L_G  \ceq  L_{W}\vert_{\CSf(G)} : \CS_b(G) \to \CSb(G)$, 
  given on objects by $(f,\psi) \mapsto (L(f,\psi), \mu(f,\psi))$,
@@
 
-\begin{proposition}\label{prop:connected-1}
+\begin{proposition}\label{prop:connected}
   If $G$ is a connected commutative algebraic group over $\Fq$ then 
-  the full subcategories $\CS_f(G) \hookrightarrow \CS_0(G) \hookrightarrow \CS(G)$ 
+  the full subcategories $\CSf(G) \hookrightarrow \CSb(G) \hookrightarrow \CS(G)$ 
   appearing in Section~\ref{sec:bounded} are equivalences 
@@
   the latter appearing in the definition of $\cs{L}$. 
-  Then, as in Section~\ref{sec:bounded}, $(\cs{L}_0,\mu_0)$ is an object in $\CS_0(G)$ 
+  Then, as in Section~\ref{sec:bounded}, $(\cs{L}_0,\mu_0)$ is an object in $\CSb(G)$ 
   and $\cs{L} = (\gcs{L},\mu,F)$ is isomorphic to $(b_G^*\cs{L}_0,b_{G\times G}^*\mu_0)$ in $\CS(G)$.
-  Thus, the full and faithful functor $B_G^* : \CS_0(G) \to \CS(G)$ from Section~\ref{sec:bounded}
+  Thus, the full and faithful functor $B_G^* : \CSb(G) \to \CS(G)$ from Section~\ref{sec:bounded}
   is also essentially surjective, hence an equivalence.
@@
 
-  In Section~\ref{sec:finite} we saw that $\CS_f(G)$ is a full subcategory of $\CS_0(G)$;
-  more precisely, we exhibited a full and faithful functor $L_G : \CS_f(G) \to \CS_0(G)$.
+  In Section~\ref{sec:finite} we saw that $\CSf(G)$ is a full subcategory of $\CSb(G)$;
+  more precisely, we exhibited a full and faithful functor $L_G : \CSf(G) \to \CSb(G)$.
   We now show that this functor is essentially surjective 
@@
 
-  We now show that $L_G(f,\psi) \iso (\cs{L}_0,\mu_0)$. 
+  To show that $L_G(f,\psi) \iso (\cs{L}_0,\mu_0)$ we simply apply the functions--sheaves dictionary
+  as follows ({\it cf} \cite{Laumon}*{1.1.3} or, ultimately, \cite{SGA4.5}*{Sommes trigonométriques}).
   First, recall that $L_G(f,\psi) = (L(f,\psi), \mu(f,\psi))$. 
-  By  \cite{Laumon}*{1.1.3.3}, $t_{L(f,\psi)}^{\Frob^n} = t_{\cs{L}}^{\Frob}\circ N_{\FF_{q^n}/\FF_q}$, for each positive integer $n$
-  On the other hand, $t_{\cs{L}}^{\Frob}\circ N_{\FF_{q^n}/\FF_q} = 
-  Using notation from \cite{Laumon}*{1.1},  this means $t_{\bullet L(f,\psi)} = t_{\bullet \cs{L}_0}$.
-  It now \cite{Laumon}*{Th\'eor\`eme~1.1.2}, it follows that  $L(f,\psi) \iso \cs{L}_0$ in $\Loc(G)$ (admittedly, this is a big hammer).
-
-   we simply apply the functions--sheaves dictionary
-  (see \cite{Laumon}*{1.1.3} or \cite{SGA4.5}*{Sommes trigonométriques}) as follows.
-
-  As we saw in Section~\ref{sec:finite}, the $\ell$-adic local system $L(f,\psi)$ on $G$ comes equipped with an isomorphism
-  $m^* L(f,\psi) \iso L(f,\psi) \boxtimes L(f,\psi)$ in $\CS_b(G)$; 
-  in the case at hand, this isomorphism is \cite[1.1.3.2]{Laumon}.
-  By \cite[1.1.3.2]{Laumon},
-
+  By  \cite{Laumon}*{1.1.3.3}, $t_{L(f,\psi)}^{\Frob^n} = t_{\cs{L}}^{\Frob}\circ N_{\FF_{q^n}/\FF_q}$, for each positive integer $n$.
+  On the other hand, $t_{\cs{L}}^{\Frob} \circ N_{\FF_{q^n}/\FF_q} = t_{\cs{L}}^{\Frob^n}$, for each positive integer $n$, 
+  by Proposition~\ref{prop:basechange}.
+  %Using notation from \cite{Laumon}*{1.1}, this means $t_{\bullet L(f,\psi)} = t_{\bullet \cs{L}_0}$.
+  Using \cite{Laumon}*{Th\'eor\`eme~1.1.2}, it follows that  $L(f,\psi) \iso \cs{L}_0$ in $\Loc(G)$.
+  It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\cs{L}_0,\mu_0)$ in $\CSb(G)$.
+  This completes the proof that $L_G : \CSf(G) \to \CS(G)$ is essentially surjective.
   Since we have already seen (in Section~\ref{sec:finite}) that $L_G$ is full and faithful, 
-  it will then follow that $L_G$ is an equivalence.
-
-  \todo{Clifton is here. I will use \cite{Kamgarpour} to finish the proof.}
-
-  We have now shown that $b_G^* : \CS_0(G) \to \CS(G)$ is an equivalence
-  of rigid monoidal categories. It follows immediately that $b_G^*$
-  determines an isomorphism
-  \[
-  b_G^* : \CSbiso{G} \mathop{\longrightarrow}^{\iso} \CSiso{G}
-  \]
-  of the Picard groups determined by these rigid monoidal categories.
-  \Clifton{\textdbend This last sentence glosses over some subtle points;
-    I might need to address them in the `two perspectives' section.}
-
-  To finish the proof observe that the functions--sheaves dictionary,
-  as it pertains to characters, shows that
-  \[
-  t_{G} : \CSbiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)
-  \]
-  is an isomorphism of groups; see \cite{Laumon}*{1.1.3} or \cite{SGA4.5}*{Sommes trigonométriques}.
+  it follows that $L_G$ is an equivalence.
+
+  To finish the proof of Proposition~\ref{prop:connected}, it suffices to observe that the group homomorphism
+  \[
+  t_{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)
+  \]
+  is surjective because, as we have seen, 
+  each character $\chi \in \Hom_\text{grp}(G(\Fq),\EEx)$ determines a finite character sheaf $(\Lang,\chi)$
+  such that the trace of Frobenius of the character sheaf $B_G^* (L_G(\Lang,\chi))$ is $\chi$.
 \end{proof}
 
-\section{Commutative etale group schemes}
+\section{Character sheaves on commutative etale group schemes}
 
@@
 
+\section{On the cohomology of the dual of an etale group scheme}
 %\input{etale-2}
@@
 % \phi(\Frob)(g)$.
+
+Although this section does not mention character sheaves, 
+we will need Proposition~\ref{prop:X} to prove our main result on character sheaves, 
+Theorem~\ref{thm:snake}.
 
@@
   geometrically connected algebraic group over $\Fq$, clopen in $G$
-  \cite{vdG&M}*{3.17}. By Proposition~\ref{prop:connected-1}, every
+  \cite{vdG&M}*{3.17}. By Proposition~\ref{prop:connected}, every
   character sheaf $\cs{E} = (\gcs{E},\mu^0,F^0)$ on $G^0$ descends to
@@
 \end{proof}
-
+\Clifton{I can flesh out this remark once I've promoted the definition of $\CSb(G)$ (category of bounded character sheaves on $G$).}
 \begin{remark}
@@
 \end{remark}
-\Clifton{I can flesh out this remark once I've promoted the definition of $\CS_0(G)$ (category of bounded character sheaves on $G$).}
+
 %\input{centralextensions}
@@
   Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.  By
-  Proposition~\ref{prop:connected-1}, $\ker t_{G^0} =0$ and $\coker t_{G^0}=0$.
+  Proposition~\ref{prop:connected}, $\ker t_{G^0} =0$ and $\coker t_{G^0}=0$.
   By Propositions~\ref{prop:etale} and \ref{prop:X}, $\ker t_{\pi_0(G)}=0$

### 2013-08-09 shanghai.tex
Improving the proof of the proposition on finite character sheaves.

@@
 $\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', F\otimes F')$
-with duals given by applying the functor $\sheafHom(\ - \ ,(\EE)_{\bG})$ (sheaf hom) to
+with duals given by applying the functor 
+\Clifton{Should this be $\sheafHom(\ - \ ,\EE)$?} $\sheafHom(\ - \ ,(\EE)_{\bG})$ (sheaf hom) to
 conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}.
@@
   applying the functor $\pi_0$ to $\bf$; see \cite{vdG&M}*{III, 3.28}, for example.
-  \Clifton{Replace with a better reference, eventually.}
+  \Clifton{I haven't found a better reference for this yet!}
   Write $c_i : \bG^i \hookrightarrow \bG$ for
@@
 \begin{proof}
-\todo{This proof is missing.}
+\Clifton{This proof is missing! Can David insert it?}
 \end{proof}
@@
 This is the category of \cdef{bounded character sheaves} on $G$. 
+\Clifton{Should this be $\sheafHom(\cs{L}_0,\EE)$?}
 This is a rigid monoidal category in the obvious way, 
@@
 and the action of $\ker f'$ on $V$ by $\psi \circ \varphi$.
-%
-We say that $(\varphi,T)$ in $C(G)$ is a weak isomorphism if $T$ is an isomorphism of vector spaces. 
-Let $C(G)[W^{-1}]$ be the localization of $C(G)$ at weak isomorphisms.
-Now, let $C_1(G)$ be the subcategory of $C(G)$ such that $\psi$ is a one-dimensional representation
-and let $\CSf(G)$ be the localisation of $C_1(G)$ at weak isomorphisms. 
-This is the category of \cdef{finite character sheaves} on $G$.
-
-\Clifton{Add the monoidal category structure here.}
-
-\begin{proposition}\label{prop:bounded}
- $\CSf(G)$ is (equivalent to) a full subcategory of $\CSb(G)$.
-\end{proposition}
-
-\begin{proof}
- To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \CSf(G) \to \CSb(G)$.
- %
- We will do this by constructing a faithful monoidal functor $L : C_1(G) \to \CSb(G)$ 
- such that ${\bar L}(\varphi,T)$ is an isomorphism precisely when $(\varphi,T)$ is a weak isomorphism. 
- Factoring along $C_1(G) \to \CSb(G)$ will produce the full and faithful monoidal functor we seek.
-
- We start by putting a tensor category structure on $C(G)$. 
+
+We put a tensor category structure on $C(G)$ as follows.
  Let $(f,\psi)$ and $(f',\psi')$ be objects in $C(G)$. 
@@
 
+We say that $(\varphi,T)$ in $C(G)$ is a weak isomorphism if $T$ is an isomorphism of vector spaces. 
+Let $C(G)[W^{-1}]$ be the localization of $C(G)$ at weak isomorphisms.
+Now, let $C_1(G)$ be the subcategory of $C(G)$ such that $\psi$ is a one-dimensional representation
+and let $\CSf(G)$ be the localisation of $C_1(G)$ at weak isomorphisms. 
+This is the rigid symmetric monoidal category of \cdef{finite character sheaves} on $G$.
+
+\begin{proposition}\label{prop:bounded}
+ $\CSf(G)$ is (equivalent to) a full subcategory of $\CSb(G)$.
+\end{proposition}
+
+\begin{proof}
+ To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \CSf(G) \to \CSb(G)$.
+ %
+ We will do this by constructing a faithful monoidal functor $L : C_1(G) \to \CSb(G)$ 
+ such that $L(\varphi,T)$ is an isomorphism precisely when $(\varphi,T)$ is a weak isomorphism. 
+ Factoring along $C_1(G) \to \CSb(G)$ will produce the full and faithful monoidal functor we seek.
+
  Now we introduce a faithful functor $L : C(G) \to \Loc(G)$ to the category of local systems on $G$.
@@
  where $V_H$ refers to $V$ as a constant sheaf on $H$. 
- Note that we may identify the stalk $(f_* V_H)_{\bar g}$ of $f_* V_H$ at a geometric point ${\bar g}$ on $G$ 
+ We may identify the stalk $(f_* V_H)_{\bar g}$ of $f_* V_H$ at a geometric point ${\bar g}$ on $G$ 
  with the $\EE$-vector space $\Hom_\text{set}(\abs{f^{-1}({\bar g})},V)$ 

### 2013-08-09 shanghai.tex
Started fixing Frobenius thoughout the paper. Not finished.
Various instances of Frob are screwed up, typographically, in the paper
now. I'll come back to working on them this afternoon and tomorrow.

@@
 \DeclareMathOperator{\W}{W}
-\newcommand{\Frob}{{\operatorname{Fr}}}
+\newcommand{\Frob}[1]{{\operatorname{F}_{#1}}}
 \DeclareMathOperator{\Aut}{Aut}
@@
 \DeclareMathOperator{\Nm}{Nm}
+\DeclareMathOperator{\trace}{Tr}
 
@@
 \gcs{L} \to \LxL$, where $m : \GxG \to G$ is
-the group operation for $G$, and an isomorphism $F : \Frob_{G}^*
-\gcs{L} \to \gcs{L}$, where $\Frob_{G}$ is the Frobenius automorphism
+the group operation for $G$, and an isomorphism $F : \Frob{G}^*
+\gcs{L} \to \gcs{L}$, where $\Frob{G}$ is the Frobenius automorphism
 on $\bG$, satisfying natural compatibility conditions with $\mu$;
@@
 $\bFq$ obtained by base change; the multiplication morphism for
-$\bG$ will be denoted by $\bm$. Let $\Frob_{G}$
-(resp. $\Frob_{\GxxG}$) be the Frobenius automorphism of
-$\bG$ (resp. $\bGxG$).
-\Clifton{I'll insert a reference to SGA where Frobenius is defined for
-  a large class of schemes over finite fields.}
+$\bG$ will be denoted by $\bm$. 
+Let $\Frob{G}$ be the Frobenius automorphism of $\bG$.
+\Clifton{I was a bit glib about Frobenius, previously.
+Now I've made things more precise here; I'm in the process of tracking this improvement through the paper.}
+Recall that $\Frob{G} = \id_{G}\times \Frob{\Spec{\bFq}}$ where
+$\Frob{\Spec{\bFq}}$ is the automorphism of $\Spec{\bFq}$ 
+opposite to the geometric Frobenius element $\Frob{\Fq}$ in $\Weil{\Fq} \subset \Gal(\bFq/\Fq)$.
 
@@
 %
-\labitem{(CS.2)}{CS.2} $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ is an
+\labitem{(CS.2)}{CS.2} $F : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an
   isomorphism of sheaves on $\bG$ compatible with $\mu$ in the sense that the following diagram commutes.
@@
   \begin{tikzcd}[row sep=20]
-  \Frob_{\GxxG}^* \bm^* \gcs{L} \arrow{rr}{\Frob_{\GxxG}^*\mu}
-    && \Frob_{\GxxG}^*(\LxL)\\
-    \arrow[equal]{u} \bm^*  \Frob_{G}^* \gcs{L} \arrow[swap]{d}{\bm^* F}
-    && \Frob_{G}^*\gcs{L}\boxtimes \Frob_{G}^*\gcs{L} \dar{F\boxtimes F} \arrow[equal]{u} \\
+  \Frob{\GxxG}^* \bm^* \gcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
+    && \Frob{\GxxG}^*(\LxL)\\
+    \arrow[equal]{u} \bm^*  \Frob{G}^* \gcs{L} \arrow[swap]{d}{\bm^* F}
+    && \Frob{G}^*\gcs{L}\boxtimes \Frob{G}^*\gcs{L} \dar{F\boxtimes F} \arrow[equal]{u} \\
     \bm^*\gcs{L} \arrow{rr}{\mu}
@@
   \begin{tikzcd}[column sep=40]
-  \Frob_G^* \gcs{L} \rar{\Frob_G^* \varphi} \arrow[swap]{d}{F} & \Frob_G^* \gcs{L'} \dar{F'}
+  \Frob{G}^* \gcs{L} \rar{\Frob{G}^* \varphi} \arrow[swap]{d}{F} & \Frob{G}^* \gcs{L'} \dar{F'}
   & \arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} & \arrow[swap]{d}{\mu} m^* \gcs{L} \rar{m^* \varphi} & m^* \gcs{L'} \dar{\mu'} \\
@@
 $\CS(G)$; we refer to this as the \cdef{Picard group of character
-sheaves} on $G$; {\it cf.} {\tt http://ncatlab.org/nlab/show/Picard+group}.
-\Clifton{Replace ncatlab with other references.}
+sheaves} on $G$.\footnote{See {\tt http://ncatlab.org/nlab/show/Picard+group}.}
 
@@
 Let $\cs{L}$ be a character sheaf on $G$. Every $g\in G(\Fq)$
-determines a point $\bg$ on $\bG$ fixed by $\Frob_G$ and
+determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$ and
 therefore an automorphism $F_{\bg}$ of $\gcs{L}_{\bg}$. Note
@@
 follows from the Condition~\ref{CS.1}). The isomorphism $\mu : \bm^* \gcs{L} \to \LxL$
-guarantees that the function $t^\Frob_\cs{L} : G(\Fq)\to \EEx$,
+guarantees that the function $t^\Frob{\Fq}\cs{L} : G(\Fq)\to \EEx$,
 defined by $g \mapsto F_{\bg}$, is a group homomorphism;
-we refer to $t^\Frob_\cs{L}$ as the \cdef{trace of Frobenius of $\cs{L}$}.
-\Clifton{There is no actual trace involved, since $\gcs{L}$ is a rank
-  $1$ local system. More generally, trace is needed.}
-
-It is clear that $t^\Frob_{\cs{L}\otimes \cs{L'}} = t^\Frob_\cs{L} \cdot t^\Frob_\cs{L'}$
-(pointwise multiplication of functions) and that $t^\Frob_\cs{L} = t^\Frob_\cs{L'}$
+we refer to $t^\Frob{\Fq}\cs{L}$ as the \cdef{trace of Frobenius of $\cs{L}$}, 
+even though no trace is involved in the definition, because the notion extends 
+to any constructible $\ell$-adic Weil sheaf $(\gcs{L},F)$ on $G$, in which context,
+$t^\Frob{(\gcs{L},F)} : G(\Fq)\to \EE$ is defined by $t^\Frob{(\gcs{L},F)}(g) \ceq \trace F_{\bg}$.
+
+It is clear that $t^\Frob{\cs{L}\otimes \cs{L'}} = t^\Frob{\Fq}\cs{L} \cdot t^\Frob{\Fq}\cs{L'}$
+(pointwise multiplication of functions) and that $t^\Frob{\Fq}\cs{L} = t^\Frob{\Fq}\cs{L'}$
 if $\cs{L} \iso \cs{L'}$ in $\CS(G)$. In this way we obtain a group homomorphism
@@
 \cdef{t_{G}} : \CSiso{G} \longrightarrow \Hom_\text{grp}(G(\Fq),\EEx),
-\qquad \text{defined by}\qquad \cs{L} \mapsto t^\Frob_\cs{L},
+\qquad \text{defined by}\qquad \cs{L} \mapsto t^\Frob{\Fq}\cs{L},
 \]
@@
   Then use the fact that $f$ is defined over $\Fq$, so
-  $(\bfxf)^*\Frob_{\GxxG}^* \iso \Frob_{\GxxG} (\bfxf)^*$,
+  $(\bfxf)^*\Frob{\GxxG}^* \iso \Frob{\GxxG} (\bfxf)^*$,
   and the fact that $f$ is a morphism of group schemes, so
@@
 \[
-F_{k'} = F \circ \Frob_G^*(F) \circ \cdots \circ (\Frob_G^{n-1})^*(F).
-\]
-The commutativity of the diagram (CS.2) for $F_{k'}$ follows from the fact that $\Frob_{G_{k'}} = \Frob_G^n$.
+F_{k'} = F \circ \Frob{G}^*(F) \circ \cdots \circ (\Frob{G}^{n-1})^*(F).
+\]
+The commutativity of the diagram (CS.2) for $F_{k'}$ follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
 Note that we may also think about the construction of $F_{k'}$ as taking the action of $\Weil{k}$ defined in Remark
@@
  Then $b_G^* \cs{L}_0$ comes equipped with an isomorphism 
- $F : \Frob_G^* b_G^*\cs{L}_0 \to b_G^* \cs{L}_0$; 
+ $F : \Frob{G}^* b_G^*\cs{L}_0 \to b_G^* \cs{L}_0$; 
  moreover, the functor $\cs{L}_0 \mapsto (b_G^* \cs{L}_0,F)$  
@@
 
-%\Clifton{I'll address this point in the next section: "Because $\Gal(\bFq/\Fq)$ acts trivially on $\Aut({\bar f})$, the local system ${\bar L}_G(f,\psi)\ceq b_G^* L(f,\psi)$ comes equipped with a canonical isomorphism $F : \Frob_G^* {\bar L}_G(f,\psi) \to {\bar L}_G(f,\psi)$ of constructible sheaves on ${\bar G}$."}
+%\Clifton{I'll address this point in the next section: "Because $\Gal(\bFq/\Fq)$ acts trivially on $\Aut({\bar f})$, the local system ${\bar L}_G(f,\psi)\ceq b_G^* L(f,\psi)$ comes equipped with a canonical isomorphism $F : \Frob{G}^* {\bar L}_G(f,\psi) \to {\bar L}_G(f,\psi)$ of constructible sheaves on ${\bar G}$."}
 
@@
   \[
-  \rho_g(\Frob) =  t^\Frob_\cs{L}(g).
-  \]
-
-  On the other hand, we have already seen that $t^\Frob_\cs{L} : G(\Fq) \to \EEx$
+  \rho_g(\Frob) =  t^\Frob{\Fq}\cs{L}(g).
+  \]
+
+  On the other hand, we have already seen that $t^\Frob{\Fq}\cs{L} : G(\Fq) \to \EEx$
   is a group homomorphism. Since $G$ is an algebraic group over $\Fq$, it is a
   variety over $\Fq$, so finitely generated over $\Fq$, so $G(\Fq)$ is finite;
-  it follows that $t^\Frob_\cs{L}(g) = \rho_g(\Frob)$ is a root of unity,
+  it follows that $t^\Frob{\Fq}\cs{L}(g) = \rho_g(\Frob)$ is a root of unity,
   for every $g\in G(\Fq)$.  Since $\Weil{\Fq}$ is generated by
-  $\Frob$ and $\rho_g : \Weil{\Fq} \to \EEx$ is
+  $\Frob{\Fq}$ and $\rho_g : \Weil{\Fq} \to \EEx$ is
   a character, it follows that the image of $\rho_g$ is a finite group.
@@
   Let $f : G\to G$ be the Lang isogeny.
-  Recall that $\ker f = G(\Fq) = G^\Frob$; 
+  Recall that $\ker f = G(\Fq) = G^\Frob{\Fq}$; 
   in particular, the action of $\Gal(\bFq/\Fq)$ on $\ker f$ is trivial.
   Let $V = \EE$ and let $\psi : \ker f \to \Aut(V)$ be the representation given by 
-  $\psi(g)(v) = t_\cs{L}^\Frob(g) v$ for $v\in V$. 
+  $\psi(g)(v) = t_\cs{L}^\Frob{\Fq}(g) v$ for $v\in V$. 
   Then $(f,\psi)$ is a finite character sheaf.
@@
   First, recall that $L_G(f,\psi) = (L(f,\psi), \mu(f,\psi))$. 
-  By  \cite{Laumon}*{1.1.3.3}, $t_{L(f,\psi)}^{\Frob^n} = t_{\cs{L}}^{\Frob}\circ N_{\FF_{q^n}/\FF_q}$, for each positive integer $n$.
-  On the other hand, $t_{\cs{L}}^{\Frob} \circ N_{\FF_{q^n}/\FF_q} = t_{\cs{L}}^{\Frob^n}$, for each positive integer $n$, 
+  By  \cite{Laumon}*{1.1.3.3}, $t_{L(f,\psi)}^\Frob{k'} = t_{\cs{L}}^\Frob{k}\circ N_{k'/k}$, for each finite extension $k'/k$.
+  On the other hand, $t_{\cs{L}}^\Frob{k} \circ N_{k'/k} = t_{\cs{L}}^\Frob{k'}$, for each for each finite extension $k'/k$, 
   by Proposition~\ref{prop:basechange}.
@@
   \[
-  \forall g\in G(\Fq), \qquad t_\cs{L}(\Frob)(g) = t^\Frob_\cs{L}(g).
+  \forall g\in G(\Fq), \qquad t_\cs{L}(\Frob)(g) = t^\Frob{\Fq}\cs{L}(g).
   \]
@@
 
-  \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $F_{x} \ceq x^*F: \gcs{L}_{\Frob(x)} \to \gcs{L}_x$
+  \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $F_{x} \ceq x^*F: \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
     \Clifton{\textdbend There's hidden subtlety here too: maybe I
@@
     \begin{tikzcd}[row sep=40]
-      \gcs{L}_{\Frob(x)+\Frob(y)} \arrow[swap]{d}{F_{x+y}} \arrow{rr}{\mu_{\Frob(x),\Frob(y)}}
-      && \gcs{L}_{\Frob(x)}\otimes \gcs{L}_{\Frob(y)} \dar{F_x \tight{0}{\otimes}{0} F_y} \\
+      \gcs{L}_{\Frob{\Fq}(x)+\Frob(y)} \arrow[swap]{d}{F_{x+y}} \arrow{rr}{\mu_{\Frob{\Fq}(x),\Frob(y)}}
+      && \gcs{L}_{\Frob{\Fq}(x)}\otimes \gcs{L}_{\Frob(y)} \dar{F_x \tight{0}{\otimes}{0} F_y} \\
       \gcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
@@
     \begin{tikzcd}[column sep=40]
-      \arrow[swap]{d}{F_x} \gcs{L}_{\Frob(x)} \rar{\varphi_{\Frob(x)}} & \gcs{L'}_{\Frob(x)} \dar{F_x'}
+      \arrow[swap]{d}{F_x} \gcs{L}_{\Frob{\Fq}(x)} \rar{\varphi_{\Frob{\Fq}(x)}} & \gcs{L'}_{\Frob{\Fq}(x)} \dar{F_x'}
       &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}& \arrow[swap]{d}{\mu} \gcs{L}_{x+y} \rar{\varphi_{x+y}} & \gcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
@@
   as follows. Recall that $\cs{L}$ also determines a family of linear transformations
-  $F_x : \gcs{L}_{\Frob(x)} \to \gcs{L}_x$ of one-dimensional $\EE$-vector
-  spaces, so $F_x(s(\Frob(x)))$ is a scalar multiply of $s(x)$, for
+  $F_x : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$ of one-dimensional $\EE$-vector
+  spaces, so $F_x(s(\Frob{\Fq}(x)))$ is a scalar multiply of $s(x)$, for
   each $x\in G(\bFq)$; let $t_\cs{L}(\Frob)(x)$ be that scalar, so
   \begin{equation}\label{t}
-    \forall x\in G(\bFq),\qquad F_{x}(s(\Frob(x)) = t_\cs{L}(\Frob)(x) s(x).
+    \forall x\in G(\bFq),\qquad F_{x}(s(\Frob{\Fq}(x)) = t_\cs{L}(\Frob)(x) s(x).
   \end{equation}
@@
   Now $t_\cs{L} : \Weil{\Fq} \to G(\bFq)^*$ is defined, recursively, by
-  $t_\cs{L}(\Frob^n) \ceq t_\cs{L}(\Frob)\cdot \,^\Frob t_\cs{L}(\Frob^{n-1})$,
-  where $\Frob$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers
+  $t_\cs{L}(\Frob{\Fq}^n) \ceq t_\cs{L}(\Frob{\Fq})\cdot \,^\Frob{\Fq} t_\cs{L}(\Frob{\Fq}^{n-1})$,
+  where $\Frob{\Fq}$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers
   to pointwise multiplication of functions. This gives
@@
   $\phi(x+y) = \phi(x)\phi(y)$, so $\phi \in G(\bFq)^*$. By the first part of
-  condition~\ref{cs.3}, $t'(\Frob) = t(\Frob) \cdot (\,^{\Frob^{-1}}\phi \cdot \phi^{-1})$,
+  condition~\ref{cs.3}, $t'(\Frob{\Fq}) = t(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}\phi \cdot \phi^{-1})$,
   so $t$ and $t'$ are cohomologous. This concludes the definition of
@@
   class of $\cs{L}$ is indeed represented by a cocycle $t_\cs{L}$ such
-  that $t_\cs{L}(\Frob) = t^\Frob_\cs{L}$ on $G(\Fq)$, which is to
-  say, when evaluated at $\Frob$, the cocycle $t_\cs{L}$ is an
+  that $t_\cs{L}(\Frob{\Fq}) = t^\Frob{\Fq}_\cs{L}$ on $G(\Fq)$, which is to
+  say, when evaluated at $\Frob{\Fq}$, the cocycle $t_\cs{L}$ is an
   extension of the trace of Frobenius of $\cs{L}$.
@@
   $f$.  Define a $1$-cocycle $z \in \Hh^1(\Fq, \Hom(X,\EEx))$ by
-  mapping $\Frob$ to $\tilde{f}$.  Then $\rho([z]) = f$.
+  mapping $\Frob{\Fq}$ to $\tilde{f}$.  Then $\rho([z]) = f$.
 
@@
   \colon X \rightarrow \EEx$ with
-  $$\tilde{f}(x) = \frac{\psi(\Frob(x))}{\psi(x)}$$
+  $$\tilde{f}(x) = \frac{\psi(\Frob{\Fq}(x))}{\psi(x)}$$
   for $x \in X$.  In fact, we may replace the construction of $\psi$
@@
   Since the action of $\Gal(\bFq/\Fq)$ is continuous, there is an $m$
-  so that $\Frob^m$ acts trivially on $X$; write $\Fqm$ for the degree
+  so that $\Frob{\Fq}^m$ acts trivially on $X$; write $\Fqm$ for the degree
   $m$ extension of $\Fq$ and $\Gamma_m$ for $\Gal(\Fqm/\Fq)$.  Since
@@
   Now the base change $\gcs{E}$ comes equipped with isomorphisms
-  $F^0 : \Frob_{G^0}^* \gcs{E} \to \gcs{E}$ and
+  $F^0 : \Frob{G^0}^* \gcs{E} \to \gcs{E}$ and
   $\mu^0 : \bm_0^* \gcs{E} \to \bExE$
@@
   $\mu : \bm^* \gcs{L} \to \LxL$ and
-  $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$ satisfying conditions \ref{CS.1}
+  $F : \Frob{G}^* \gcs{L} \to \gcs{L}$ satisfying conditions \ref{CS.1}
   and \ref{CS.2}.
@@
 
-  Now we turn to the definition of $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$.
+  Now we turn to the definition of $F : \Frob{G}^* \gcs{L} \to \gcs{L}$.
   As above, we define this isomorphism through a family of
   isomorphisms on the connected components of $\bG$. The
-  restriction of $\Frob_{G}$ to $\bG^x$ defines an isomorphism
-  $\Frob_x : \bG^x \to \bG^{\Frob(x)}$.
+  restriction of $\Frob{G}$ to $\bG^x$ defines an isomorphism
+  $\Frob{G}^x : \bG^x \to \bG^{\Frob{\Fq}(x)}$.
   %\[
   %\xymatrix{
-  %\ar[d]_{\Frob_x} \bG^x \ar[r] & \ar[d]_{\Frob_{G}} \bG\\
-  %\bG^{\Frob(x)} \ar[r] & \bG\\
+  %\ar[d]_{\Frob_x} \bG^x \ar[r] & \ar[d]_{\Frob{G}} \bG\\
+  %\bG^{\Frob{\Fq}(x)} \ar[r] & \bG\\
   %}
@@
   Pull back the finite etale covering in the diagram for
-  $\gcs{L}^{\Frob(x)}$ along $\Frob_x$ and compare the result with the
+  $\gcs{L}^{\Frob{\Fq}(x)}$ along $\Frob{G}^x$ and compare the result with the
   finite etale covering in the diagram for $\gcs{L}^{x}$.
@@
   \begin{tikzpicture}[auto,style={rectangle},scale=1.2]
-  \node (12) [anchor=east] at (4,2.4) {$\Aut(\bf^{\Frob(x)})$};
-  \node (22) [anchor=west] at (4.4,2.4) {$\bH^{\Frob(x)}$};
-  \node (32) [anchor=west] at (8,2.4) {$\bG^{\Frob(x)}$};
+  \node (12) [anchor=east] at (4,2.4) {$\Aut(\bf^{\Frob{\Fq}(x)})$};
+  \node (22) [anchor=west] at (4.4,2.4) {$\bH^{\Frob{\Fq}(x)}$};
+  \node (32) [anchor=west] at (8,2.4) {$\bG^{\Frob{\Fq}(x)}$};
   \node (01) at (0,1.2) {$\EEx$};
-  \node (11) [anchor=east] at (4,1.2) {$\Aut(\bf^{\Frob(x)})$};
-  \node (21) [anchor=west] at (4.4,1.2) {$\bH^{\Frob(x)} \times_{\bG^{\Frob(x)}} \bG^x$};
+  \node (11) [anchor=east] at (4,1.2) {$\Aut(\bf^{\Frob{\Fq}(x)})$};
+  \node (21) [anchor=west] at (4.4,1.2) {$\bH^{\Frob{\Fq}(x)} \times_{\bG^{\Frob{\Fq}(x)}} \bG^x$};
   \node (31) [anchor=west] at (8,1.2) {$\bG^x$};
@@
   \draw [->] (4.3,-0.06) arc (330:40:0.12) -- (4.3,0.07);
-  \draw [->] (12) to node[swap,label] {$\psi_{\Frob(x)}$} (01);
+  \draw [->] (12) to node[swap,label] {$\psi_{\Frob{\Fq}(x)}$} (01);
   \draw [->, dashed] (11) -- (01);
@@
   \draw [double equal sign distance] (11) -- (12);
-  \draw [->] (22) to node[label] {$\bf^{\Frob(x)}$} (32);
+  \draw [->] (22) to node[label] {$\bf^{\Frob{\Fq}(x)}$} (32);
   \draw [->] ($(22.225) + (0,-0.7)$) -- (22.225);
   \draw [->] (21) -- (31);
-  \draw [->] ($(32.222) + (0,-0.7)$) to node[swap] {\footnotesize{$\Frob_x$}} (32.222);
+  \draw [->] ($(32.222) + (0,-0.7)$) to node[swap] {\footnotesize{$\Frob{G}^x$}} (32.222);
   \draw [->] ($(22.225) + (0,-1.9)$) -- ($(22.225) + (0,-1.2)$);
@@
   \]
-  The covering group of $\bH^{\Frob(x)} \times_{\bG^{\Frob(x)}} \bG^x$
-  is isomorphic to $\Aut(\bf^{\Frob(x)})$, canonically, so
-  $\Frob_x^* \gcs{L}^{\Frob(x)}$ is defined by the middle (horizontal)
+  The covering group of $\bH^{\Frob{\Fq}(x)} \times_{\bG^{\Frob{\Fq}(x)}} \bG^x$
+  is isomorphic to $\Aut(\bf^{\Frob{\Fq}(x)})$, canonically, so
+  $(\Frob{G}^x)^* \gcs{L}^{\Frob{\Fq}(x)}$ is defined by the middle (horizontal)
   diagram, above.  We define the sheaf homomorphism
-  $F_x : \Frob_x^* \gcs{L}^{\Frob(x)} \to \gcs{L}^x$ by the canonical morphism
-  $\bH^x \to \bH^{\Frob(x)} \times_{\bG^{\Frob(x)}} \bG^x \to $;
+  $F_x : (\Frob{G}^x)^* \gcs{L}^{\Frob{\Fq}(x)} \to \gcs{L}^x$ by the canonical morphism
+  $\bH^x \to \bH^{\Frob{\Fq}(x)} \times_{\bG^{\Frob{\Fq}(x)}} \bG^x \to $;
   to see that this defines a sheaf homomorphism it is sufficient to
   check that the character $\psi_x$ commutes with the family of isomorphisms
-  $F_x : (\Frob_{G}^* \gcs{L})\vert_{\bG^x} \iso \Frob_x^* \gcs{L}^{\Frob{x}} \to \gcs{L}^x$
-  now defines the isomorphism $F : \Frob_{G}^* \gcs{L} \to \gcs{L}$.
+  $F_x : (\Frob{G}^* \gcs{L})\vert_{\bG^x} \iso (\Frob{G}^x)^* \gcs{L}^{\Frob{x}} \to \gcs{L}^x$
+  now defines the isomorphism $F : \Frob{G}^* \gcs{L} \to \gcs{L}$.
   \Clifton{Add some detail here.}
@@
   suppose $\cs{L}$ is a character sheaf on $G$ that is trivial on
-  $G^0$. Then $t^\Frob_\cs{L}\vert_{G^0(\Fq)} = t^\Frob_{\cs{L}^0} =0$,
+  $G^0$. Then $t^\Frob{\Fq}\cs{L}\vert_{G^0(\Fq)} = t^\Frob{\cs{L}^0} =0$,
   by Proposition~\ref{prop:pullback} again. Since the sequence of
@@
   pull-back of $\chi$ along $G(\Fq)\to \pi_0(G)(\Fq)$ is
-  $t^\Frob_\cs{L}$. By Propositions~\ref{prop:etale} and \ref{prop:X},
+  $t^\Frob{\Fq}\cs{L}$. By Propositions~\ref{prop:etale} and \ref{prop:X},
   there is a a character sheaf $\cs{L}_\chi$ on $\pi_0(G)$, unique up
-  to isomorphism, such that $t^\Frob_{\cs{L}_\chi} = \chi$. By
+  to isomorphism, such that $t^\Frob{\cs{L}_\chi} = \chi$. By
   Proposition~\ref{prop:pullback} again, $\cs{L}$ is isomorphic to the

### 2013-08-10 shanghai.tex
Frobenius fixes finished. I had to make some rather drastic notation changes.
I started by making the meaning of \Frob precise and consistent with
Deligne's definition of Weil sheaf. Deligne (and everyone else I could
find, like Laumon, Lusztig, Keihl and Weissauer, to name a few) uses F,
not Fr, for what we meant. So I had to change Fr to F in our paper. But
that made our current use of F, in the datum of a character sheaf, a
notational conflict. So I followed Lusztig in replacing F with \phi. I
also decided to harmonize our notation for trace of Frobenius with
Laumon, replacing our current t

@@
 \newcommand{\Loc}{{\operatorname{Loc}}}
+\newcommand{\trFrob}[1]{t_{#1}}
 
@@
 $q$. By a {character sheaf} on $G$ we mean a triple $\cs{L}\ceq
-(\gcs{L},\mu,F)$ where $\gcs{L}$ is a constructible $\ell$-adic sheaf
+(\gcs{L},\mu,\phi)$ where $\gcs{L}$ is a constructible $\ell$-adic sheaf
 $\gcs{L}$ on the \'etale site of $\bG \ceq G \times_{\Spec\Fq}
@@
 
-Throughout this paper, $G$ stands for a commutative group scheme,
-smooth and locally of finite type over a finite field $\Fq$; we write
-$m : \GxG\to G$ for the multiplication morphism. We fix an
-algebraic closure $\bFq$ of $\Fq$ and write $\bG $ for the
-commutative group scheme, smooth and locally of finite type over
-$\bFq$ obtained by base change; the multiplication morphism for
-$\bG$ will be denoted by $\bm$. 
+Throughout this paper, $G$ is a commutative group scheme,
+smooth and locally of finite type over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.
+
+We fix an algebraic closure $\bFq$ of $\Fq$ and write $\bG$ for the
+commutative group scheme $G \times_{\Spec{\Fq}} \Spec{\bFq}$, over $\bFq$ obtained by base change from $k$. The multiplication morphism for $\bG$ will be denoted by $\bm$. 
+%
 Let $\Frob{G}$ be the Frobenius automorphism of $\bG$.
@@
 Recall that $\Frob{G} = \id_{G}\times \Frob{\Spec{\bFq}}$ where
-$\Frob{\Spec{\bFq}}$ is the automorphism of $\Spec{\bFq}$ 
-opposite to the geometric Frobenius element $\Frob{\Fq}$ in $\Weil{\Fq} \subset \Gal(\bFq/\Fq)$.
+$\Frob{\Spec{\bFq}} = \Spec\Frob{\Fq}$ and $\Frob{\Fq}$  is the geometric Frobenius element in $\Weil{\Fq} \subset \Gal(\bFq/\Fq)$.
 
@@
 is defined as follows.  A \cdef{character sheaf} on $G$ is a triple
-$\cs{L}\ceq (\gcs{L},\mu,F)$ where:
+$\cs{L}\ceq (\gcs{L},\mu,\phi)$ where:
 \begin{enumerate}
@@
 %
-\labitem{(CS.2)}{CS.2} $F : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an
+\labitem{(CS.2)}{CS.2} $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an
   isomorphism of sheaves on $\bG$ compatible with $\mu$ in the sense that the following diagram commutes.
@@
     && \Frob{\GxxG}^*(\LxL)\\
-    \arrow[equal]{u} \bm^*  \Frob{G}^* \gcs{L} \arrow[swap]{d}{\bm^* F}
-    && \Frob{G}^*\gcs{L}\boxtimes \Frob{G}^*\gcs{L} \dar{F\boxtimes F} \arrow[equal]{u} \\
+    \arrow[equal]{u} \bm^*  \Frob{G}^* \gcs{L} \arrow[swap]{d}{\bm^* \phi}
+    && \Frob{G}^*\gcs{L}\boxtimes \Frob{G}^*\gcs{L} \dar{F\boxtimes \phi} \arrow[equal]{u} \\
     \bm^*\gcs{L} \arrow{rr}{\mu}
@@
 \begin{enumerate}
-\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,F)$ and
-  $\cs{L'} = (\gcs{L'},\mu',F')$ are character sheaves on $G$ then
+\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,\phi)$ and
+  $\cs{L'} = (\gcs{L'},\mu',\phi')$ are character sheaves on $G$ then
   $\Hom_{\CS(G)}(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$
@@
 category [insert reference] under
-$\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', F\otimes F')$
+$\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$
 with duals given by applying the functor 
@@
 determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$ and
-therefore an automorphism $F_{\bg}$ of $\gcs{L}_{\bg}$. Note
-that $\Aut_{\EE}(\gcs{L}_{\bg}) \iso \EEx$, canonically (this
-follows from the Condition~\ref{CS.1}). The isomorphism $\mu : \bm^* \gcs{L} \to \LxL$
-guarantees that the function $t^\Frob{\Fq}\cs{L} : G(\Fq)\to \EEx$,
-defined by $g \mapsto F_{\bg}$, is a group homomorphism;
-we refer to $t^\Frob{\Fq}\cs{L}$ as the \cdef{trace of Frobenius of $\cs{L}$}, 
-even though no trace is involved in the definition, because the notion extends 
-to any constructible $\ell$-adic Weil sheaf $(\gcs{L},F)$ on $G$, in which context,
-$t^\Frob{(\gcs{L},F)} : G(\Fq)\to \EE$ is defined by $t^\Frob{(\gcs{L},F)}(g) \ceq \trace F_{\bg}$.
-
-It is clear that $t^\Frob{\cs{L}\otimes \cs{L'}} = t^\Frob{\Fq}\cs{L} \cdot t^\Frob{\Fq}\cs{L'}$
-(pointwise multiplication of functions) and that $t^\Frob{\Fq}\cs{L} = t^\Frob{\Fq}\cs{L'}$
+therefore an automorphism $\phi_{\bg}$ of $\gcs{L}_{\bg}$. Note
+that $\Aut_{\EE}(\gcs{L}_{\bg}) \iso \EEx$, canonically. The isomorphism $\mu : \bm^* \gcs{L} \to \LxL$
+guarantees that the function $\trFrob{\cs{L}} : G(\Fq)\to \EEx$,
+defined by $g \mapsto \phi_{\bg}$, is a group homomorphism;
+we refer to $\trFrob{\cs{L}}$ as the \cdef{trace of Frobenius of $\cs{L}$}.
+Although though no trace is involved in the definition, the notion extends 
+to any constructible $\ell$-adic Weil sheaf $(\gcs{L},\phi)$ on $G$, in which context,
+$\trFrob{(\gcs{L},\phi)} : G(\Fq)\to \EE$ is defined by $\trFrob{(\gcs{L},\phi)}(g) \ceq \trace \phi_{\bg}$.
+
+It is clear that $\trFrob{\cs{L}\otimes \cs{L'}} = \trFrob{\cs{L}} \cdot \trFrob{\cs{L'}}$
+(pointwise multiplication of functions) and that $\trFrob{\cs{L}} = \trFrob{\cs{L'}}$
 if $\cs{L} \iso \cs{L'}$ in $\CS(G)$. In this way we obtain a group homomorphism
 \[
-\cdef{t_{G}} : \CSiso{G} \longrightarrow \Hom_\text{grp}(G(\Fq),\EEx),
-\qquad \text{defined by}\qquad \cs{L} \mapsto t^\Frob{\Fq}\cs{L},
+\cdef{\trFrob{G}} : \CSiso{G} \longrightarrow \Hom_\text{grp}(G(\Fq),\EEx),
+\qquad \text{defined by}\qquad \cs{L} \mapsto \trFrob{\cs{L}},
 \]
@@
   If $f : H\to G$ is a morphism of commutative group schemes locally of finite type over $\Fq$ then
-  $(\gcs{L},\mu,F) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
+  $(\gcs{L},\mu,\phi) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
   defines a monoidal functor $f^* : \CS(G) \to \CS(H)$ such that
@@
   \begin{tikzcd}[row sep=20, column sep=30]
-   \CSiso{G} \rar{f^*} \arrow[swap]{d}{t_{G}} & \CSiso{H} \dar{t_H} \\
+   \CSiso{G} \rar{f^*} \arrow[swap]{d}{\trFrob{G}} & \CSiso{H} \dar{t_H} \\
   \Hom_\text{grp}(G(\Fq),\EEx) \rar & \Hom_\text{grp}(H(\Fq),\EEx)
@@
   Then use the fact that $f$ is defined over $\Fq$, so
-  $(\bfxf)^*\Frob{\GxxG}^* \iso \Frob{\GxxG} (\bfxf)^*$,
+  $(\bfxf)^*\Frob{\GxxG}^* \iso \Frob{\GxxG}^* (\bfxf)^*$,
   and the fact that $f$ is a morphism of group schemes, so
@@
 
-  To see that $(\gcs{L},\mu,F) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
+  To see that $(\gcs{L},\mu,\phi) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
   defines a functor $f^* : \CS(G) \to \CS(H)$ one applies the functors $\bf^*$ and
@@
   functors that $f^* : \CS(G) \to \CS(H)$ is a monoidal functor.
-
+%
   The fact that the functor $f^* : \CS(G) \to \CS(H)$ commutes with
@@
 over $k$ as in Theorem \ref{thm:snake} and $G_{k'}$ is the base change of $G$ to $k'$.
-If $\cs{L} = (\gcs{L}, \mu, F)$ is a character sheaf on $G$ we may define
-a character sheaf $\nu(\cs{L}) = (\gcs{L}, \mu, F_{k'})$ on $G_{k'}$ by setting
-\[
-F_{k'} = F \circ \Frob{G}^*(F) \circ \cdots \circ (\Frob{G}^{n-1})^*(F).
-\]
-The commutativity of the diagram (CS.2) for $F_{k'}$ follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
-Note that we may also think about the construction of $F_{k'}$ as taking the action of $\Weil{k}$ defined in Remark
+If $\cs{L} = (\gcs{L}, \mu, \phi)$ is a character sheaf on $G$ we may define
+a character sheaf $\nu(\cs{L}) = (\gcs{L}, \mu, \phi_{k'})$ on $G_{k'}$ by setting
+\[
+\phi_{k'} = \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi).
+\]
+The commutativity of the diagram (CS.2) for $\phi_{k'}$ follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
+Note that we may also think about the construction of $\phi_{k'}$ as taking the action of $\Weil{k}$ defined in Remark
 \ref{rem:CS-action} and restricting it to $\Weil{k'}$.
@@
 \begin{tikzcd}
-\CSiso{G} \rar{\nu} \dar{t_G} & \CSiso{G_{k'}} \dar{t_{G_{k'}}} \\
+\CSiso{G} \rar{\nu} \dar{\trFrob{G}} & \CSiso{G_{k'}} \dar{\trFrob{G_{k'}}} \\
 \Hom(G(k), \EEx) \rar{\Nm} & \Hom(G(k'), \EEx).
@@
  Then $b_G^* \cs{L}_0$ comes equipped with an isomorphism 
- $F : \Frob{G}^* b_G^*\cs{L}_0 \to b_G^* \cs{L}_0$; 
- moreover, the functor $\cs{L}_0 \mapsto (b_G^* \cs{L}_0,F)$  
+ $\phi : \Frob{G}^* b_G^*\cs{L}_0 \to b_G^* \cs{L}_0$; 
+ moreover, the functor $\cs{L}_0 \mapsto (b_G^* \cs{L}_0,\phi)$  
  from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
@@
  with $b_G^*\cs{L}_0$ playing the role of $\gcs{L}$.
- Moreover, $F$ is compatible with $\mu$ in the sense of Condition~\ref{CS.3}.
- It follows that functor $(\cs{L}_0,\mu_0) \mapsto (b_G^*\cs{L}_0,b_{G\times G}^* \mu_0, F)$, denoted by  $B_G^*: \CSb(G) \hookrightarrow \CS(G)$ below, is full and faithful.
+ Moreover, $\phi$ is compatible with $\mu$ in the sense of Condition~\ref{CS.3}.
+ It follows that functor $(\cs{L}_0,\mu_0) \mapsto (b_G^*\cs{L}_0,b_{G\times G}^* \mu_0, \phi)$, denoted by  $B_G^*: \CSb(G) \hookrightarrow \CS(G)$ below, is full and faithful.
 \end{proof}
@@
 
-\section{Connected abelian algebraic groups}
+\section{Connected commutative algebraic groups}
 
@@
   \[
-  t_{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)
+  \trFrob{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)
   \]
@@
  %Let $G$ be a geometrically connected algebraic group over $\Fq$.
-  Observe that the forgetful functor $(\gcs{L},\mu,F) \mapsto (\gcs{L},F)$
+  Observe that the forgetful functor $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$
   sends character sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{Deligne:Weil2}*{1.1.10}.
@@
   $\ell$-adic representations of $\W(G,\bg)$ \cite{Deligne:Weil2}*{1.1.12}. 
-  Now let $(\gcs{L},\mu,F)$ be a character sheaf on $G$ 
-  and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gcs{L},F)$. 
+  Now let $(\gcs{L},\mu,\phi)$ be a character sheaf on $G$ 
+  and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gcs{L},\phi)$. 
   The $\Fq$-rational point $g$ under the geometric point $\bg$ determines a splitting
@@
   \[
-  \rho_g(\Frob) =  t^\Frob{\Fq}\cs{L}(g).
-  \]
-
-  On the other hand, we have already seen that $t^\Frob{\Fq}\cs{L} : G(\Fq) \to \EEx$
+  \rho_g(\Frob{\Fq}) =  \trFrob{\cs{L}}(g).
+  \]
+
+  On the other hand, we have already seen that $\trFrob{\cs{L}} : G(\Fq) \to \EEx$
   is a group homomorphism. Since $G$ is an algebraic group over $\Fq$, it is a
   variety over $\Fq$, so finitely generated over $\Fq$, so $G(\Fq)$ is finite;
-  it follows that $t^\Frob{\Fq}\cs{L}(g) = \rho_g(\Frob)$ is a root of unity,
+  it follows that $\trFrob{\cs{L}}(g) = \rho_g(\Frob{\Fq})$ is a root of unity,
   for every $g\in G(\Fq)$.  Since $\Weil{\Fq}$ is generated by
@@
   Then, as in Section~\ref{sec:bounded}, $(\cs{L}_0,\mu_0)$ is an object in $\CSb(G)$ 
-  and $\cs{L} = (\gcs{L},\mu,F)$ is isomorphic to $(b_G^*\cs{L}_0,b_{G\times G}^*\mu_0)$ in $\CS(G)$.
+  and $\cs{L} = (\gcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\cs{L}_0,b_{G\times G}^*\mu_0)$ in $\CS(G)$.
   Thus, the full and faithful functor $B_G^* : \CSb(G) \to \CS(G)$ from Section~\ref{sec:bounded}
@@
   Then $\cs{L}\ceq B_G^*(\cs{L}_0,\mu_0)$ is a character sheaf on $G$.
-  Recall the definition of the character $t_\cs{L}^\Frob : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}. 
+  Recall the definition of the character $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}. 
   Let $f : G\to G$ be the Lang isogeny.
@@
   Let $V = \EE$ and let $\psi : \ker f \to \Aut(V)$ be the representation given by 
-  $\psi(g)(v) = t_\cs{L}^\Frob{\Fq}(g) v$ for $v\in V$. 
+  $\psi(g)(v) = \trFrob{\cs{L}}(g) v$ for $v\in V$. 
   Then $(f,\psi)$ is a finite character sheaf.
@@
   First, recall that $L_G(f,\psi) = (L(f,\psi), \mu(f,\psi))$. 
-  By  \cite{Laumon}*{1.1.3.3}, $t_{L(f,\psi)}^\Frob{k'} = t_{\cs{L}}^\Frob{k}\circ N_{k'/k}$, for each finite extension $k'/k$.
-  On the other hand, $t_{\cs{L}}^\Frob{k} \circ N_{k'/k} = t_{\cs{L}}^\Frob{k'}$, for each for each finite extension $k'/k$, 
-  by Proposition~\ref{prop:basechange}.
+  By  \cite{Laumon}*{1.1.3.3}, $\trFrob{(G_{k'}\hookrightarrow G)^*L(f,\psi)} = \trFrob{\cs{L}} \circ N_{k'/k}$, for each finite extension $k'/k$.
+  On the other hand, $\trFrob{\cs{L}} \circ N_{k'/k} = \trFrob{(G_{k'}\hookrightarrow G)^*\cs{L}}$,  by Proposition~\ref{prop:basechange}.
   %Using notation from \cite{Laumon}*{1.1}, this means $t_{\bullet L(f,\psi)} = t_{\bullet \cs{L}_0}$.
@@
   \qquad \text{given by}\qquad
-  [\cs{L}] \mapsto [t_\cs{L}],
-  \]
-  where $t_\cs{L}: \Weil{\Fq}\to \Hom_\text{grp}(G(\bFq),\EEx)$ is a cocycle such that
-  \[
-  \forall g\in G(\Fq), \qquad t_\cs{L}(\Frob)(g) = t^\Frob{\Fq}\cs{L}(g).
+  [\cs{L}] \mapsto [\tau_\cs{L}],
+  \]
+  where $\tau_\cs{L}: \Weil{\Fq}\to \Hom_\text{grp}(G(\bFq),\EEx)$ is a cocycle such that
+  \[
+  \forall g\in G(\Fq), \qquad \tau_\cs{L}(\Frob{\Fq})(g) = \trFrob{\cs{L}}(g).
   \]
@@
   the discrete topology on the group), given by $G \mapsto G(\bFq)$.
-  Under this equivalence any character sheaf $\cs{L}=(\gcs{L},\mu,F)$
+  Under this equivalence any character sheaf $\cs{L}=(\gcs{L},\mu,\phi)$
   on $G$ corresponds to:
@@
 
-  \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $F_{x} \ceq x^*F: \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
-    \Clifton{\textdbend There's hidden subtlety here too: maybe I
-      should explain which Frobenius this is and how it acts. }
+  \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} \ceq x^*\phi: \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
     such that
@@
     \begin{tikzcd}[row sep=40]
-      \gcs{L}_{\Frob{\Fq}(x)+\Frob(y)} \arrow[swap]{d}{F_{x+y}} \arrow{rr}{\mu_{\Frob{\Fq}(x),\Frob(y)}}
-      && \gcs{L}_{\Frob{\Fq}(x)}\otimes \gcs{L}_{\Frob(y)} \dar{F_x \tight{0}{\otimes}{0} F_y} \\
+      \gcs{L}_{\Frob{\Fq}(x)+\Frob{\Fq}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{\Fq}(x),\Frob{\Fq}(y)}}
+      && \gcs{L}_{\Frob{\Fq}(x)}\otimes \gcs{L}_{\Frob{\Fq}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
       \gcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
@@
     \begin{tikzcd}[column sep=40]
-      \arrow[swap]{d}{F_x} \gcs{L}_{\Frob{\Fq}(x)} \rar{\varphi_{\Frob{\Fq}(x)}} & \gcs{L'}_{\Frob{\Fq}(x)} \dar{F_x'}
+      \arrow[swap]{d}{\phi_x} \gcs{L}_{\Frob{\Fq}(x)} \rar{\varphi_{\Frob{\Fq}(x)}} & \gcs{L'}_{\Frob{\Fq}(x)} \dar{\phi_x'}
       &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}& \arrow[swap]{d}{\mu} \gcs{L}_{x+y} \rar{\varphi_{x+y}} & \gcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
@@
   as follows. Recall that $\cs{L}$ also determines a family of linear transformations
-  $F_x : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$ of one-dimensional $\EE$-vector
-  spaces, so $F_x(s(\Frob{\Fq}(x)))$ is a scalar multiply of $s(x)$, for
-  each $x\in G(\bFq)$; let $t_\cs{L}(\Frob)(x)$ be that scalar, so
+  $\phi_x : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$ of one-dimensional $\EE$-vector
+  spaces, so $\phi_x(s(\Frob{\Fq}(x)))$ is a scalar multiply of $s(x)$, for
+  each $x\in G(\bFq)$; let $\tau_\cs{L}(\Frob{\Fq})(x)$ be that scalar, so
   \begin{equation}\label{t}
-    \forall x\in G(\bFq),\qquad F_{x}(s(\Frob{\Fq}(x)) = t_\cs{L}(\Frob)(x) s(x).
+    \forall x\in G(\bFq),\qquad F_{x}(s(\Frob{\Fq}(x)) = \tau_\cs{L}(\Frob{\Fq})(x) s(x).
   \end{equation}
@@
   the scalar $z_\cs{L}(\Frob)(x)$ is non-zero, while condition~\ref{cs.1} forces
-  $t_\cs{L}(\Frob)(x+y) = t_\cs{L}(\Frob)(x) \ t_\cs{L}(\Frob)(y)$,
+  $\tau_\cs{L}(\Frob{\Fq})(x+y) = \tau_\cs{L}(\Frob{\Fq})(x) \ \tau_\cs{L}(\Frob{\Fq})(y)$,
   for all $x,y \in G(\bFq)$.
@@
 
-  Now $t_\cs{L} : \Weil{\Fq} \to G(\bFq)^*$ is defined, recursively, by
-  $t_\cs{L}(\Frob{\Fq}^n) \ceq t_\cs{L}(\Frob{\Fq})\cdot \,^\Frob{\Fq} t_\cs{L}(\Frob{\Fq}^{n-1})$,
+  Now $\tau_\cs{L} : \Weil{\Fq} \to G(\bFq)^*$ is defined, recursively, by
+  $\tau_\cs{L}(\Frob{\Fq}^n) \ceq \tau_\cs{L}(\Frob{\Fq})\cdot \,^\Frob{\Fq} \tau_\cs{L}(\Frob{\Fq}^{n-1})$,
   where $\Frob{\Fq}$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers
@@
   \obj \CS(G(\bFq)) \longrightarrow Z^1(\Weil{\Fq},G(\bFq)^*),
-  \qquad \text{defined by} \qquad \cs{L} \mapsto t_\cs{L}.
+  \qquad \text{defined by} \qquad \cs{L} \mapsto \tau_\cs{L}.
   \]
@@
   Although we used a global section $s_\cs{L}$ in the definition of
-  $t_\cs{L}$, the class of $t_\cs{L}$ does not depend on this
+  $\tau_\cs{L}$, the class of $\tau_\cs{L}$ does not depend on this
   choice. To see why, let $s_1$ and $s_2$ be two global sections of
-  the line bundle $(\gcs{L},\mu)$, in the sense above and let $t_1$
-  and $t_2$ be the cocycles defined by $s_1$ and $s_2$, respectively,
+  the line bundle $(\gcs{L},\mu)$, in the sense above and let $\tau_1$
+  and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$, respectively,
   as above. Since, for each $x\in G(\bFq)$, $\gcs{L}_x$ is a
@@
   condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so
-  $a\in G(\bFq)^*$. Now consider the coboundary $t_0 : \Weil{\Fq} \to G(\bFq)^*$
-  defined by $t_0(\Frob) = \,^\Frob a \cdot a^{-1}$. Then $t_2 = t_0 t_1$,
-  so $t_2$ and $t_1$ are cohomologous. In this way we see that
+  $a\in G(\bFq)^*$. Now consider the coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
+  defined by $\tau_0(\Frob{\Fq}) = \,^\Frob{\Fq} a \cdot a^{-1}$. Then $\tau_2 = \tau_0 \tau_1$,
+  so $\tau_2$ and $\tau_1$ are cohomologous. In this way we see that
   \begin{equation}\label{cohomologous}
     \obj \CS(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
-    \qquad \text{defined by} \qquad \cs{L} \mapsto [t_\cs{L}],
+    \qquad \text{defined by} \qquad \cs{L} \mapsto [\tau_\cs{L}],
   \end{equation}
@@
   To see this, let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and
-  let $t$ and $t'$ be any cocycles representing the classes in the
+  let $\tau$ and $\tau'$ be any cocycles representing the classes in the
   image of $\cs{L}$ and $\cs{L'}$ under \eqref{cohomologous}; by construction,
-  $t$ and $t'$ are defined by sections $s$ and $s'$. Now, $\varphi_x(s(x))$ is a
+  $\tau$ and $\tau'$ are defined by sections $s$ and $s'$. Now, $\varphi_x(s(x))$ is a
   non-zero scalar multiple of $s'(x)$; define $\phi: G(\bFq) \to \EEx$
-  by $\varphi_x(s(x)) = \phi(x) s'(x)$. By the second part of condition~\ref{cs.3},
+  by $\varphi_x(s(x)) = \phi(x) s'(x)$. 
+  \Clifton{Notation problem here: replace $\phi$ with something else.}
+  By the second part of condition~\ref{cs.3},
   $\phi(x+y) = \phi(x)\phi(y)$, so $\phi \in G(\bFq)^*$. By the first part of
-  condition~\ref{cs.3}, $t'(\Frob{\Fq}) = t(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}\phi \cdot \phi^{-1})$,
-  so $t$ and $t'$ are cohomologous. This concludes the definition of
+  condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}\phi \cdot \phi^{-1})$,
+  so $\tau$ and $\tau'$ are cohomologous. This concludes the definition of
   \begin{equation}\label{pich1}
     \CSiso{G(\bFq} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
-    \qquad \text{defined by} \qquad [\cs{L}] \mapsto [t_\cs{L}].
+    \qquad \text{defined by} \qquad [\cs{L}] \mapsto [\tau_\cs{L}].
   \end{equation}
   Now it follows from \eqref{t} that the image of the isomorphism
-  class of $\cs{L}$ is indeed represented by a cocycle $t_\cs{L}$ such
-  that $t_\cs{L}(\Frob{\Fq}) = t^\Frob{\Fq}_\cs{L}$ on $G(\Fq)$, which is to
-  say, when evaluated at $\Frob{\Fq}$, the cocycle $t_\cs{L}$ is an
+  class of $\cs{L}$ is indeed represented by a cocycle $\tau_\cs{L}$ such
+  that $\tau_\cs{L}(\Frob{\Fq}) = \trFrob{\cs{L}}$ on $G(\Fq)$, which is to
+  say, when evaluated at $\Frob{\Fq}$, the cocycle $\tau_\cs{L}$ is an
   extension of the trace of Frobenius of $\cs{L}$.
@@
     \Hh^1(\Fq, \Hom(X, \EEx)) &\xrightarrow{\rho} \Hom(\Hh^0(\Fq, X), \EEx) \\
-    \rho([z])(x) &= z(\Frob)(x)
+    \rho([z])(x) &= z(\Frob{\Fq})(x)
   \end{align*}
@@
   We first prove that $\rho$ is surjective.  Suppose that
-  $f \in \Hom(X^\Frob, \EEx).$ Since $\EEx$ is divisible
+  $f \in \Hom(X^\Frob{\Fq}, \EEx).$ Since $\EEx$ is divisible
   as an abelian group it is injective as a $\ZZ$-module and thus
-  $\Ext^1_{\ZZ}(X/X^\Frob, \EEx) = 0$.  Applying the functor
+  $\Ext^1_{\ZZ}(X/X^\Frob{\Fq}, \EEx) = 0$.  Applying the functor
   $\Hom(\mbox{---}, \EEx)$ to
@@
   \begin{tikzcd}
-  0 \rar & X^\Frob \rar & X \rar & X/X^\Frob \rar & 0
+  0 \rar & X^\Frob{\Fq} \rar & X \rar & X/X^\Frob{\Fq} \rar & 0
   \end{tikzcd}
@@
   Now suppose that $[z] \in \Hh^1(\Fq,\Hom(X,\EEx))$ with
-  $\rho([z]) = 1$; write $\tilde{f}$ for $z(\Frob)$.  The injectivity
+  $\rho([z]) = 1$; write $\tilde{f}$ for $z(\Frob{\Fq})$.  The injectivity
   of $\rho$ is equivalent to the existence of a homomorphism $\psi
@@
   \cite{vdG&M}*{3.17}. By Proposition~\ref{prop:connected}, every
-  character sheaf $\cs{E} = (\gcs{E},\mu^0,F^0)$ on $G^0$ descends to
+  character sheaf $\cs{E} = (\gcs{E},\mu^0,\phi^0)$ on $G^0$ descends to
   a line bundle on $G^0$.
@@
   Now the base change $\gcs{E}$ comes equipped with isomorphisms
-  $F^0 : \Frob{G^0}^* \gcs{E} \to \gcs{E}$ and
+  $\phi^0 : \Frob{G^0}^* \gcs{E} \to \gcs{E}$ and
   $\mu^0 : \bm_0^* \gcs{E} \to \bExE$
-  satisfying conditions \ref{CS.1} and \ref{CS.2}. Then $(\gcs{E},\mu^0,F^0)$
+  satisfying conditions \ref{CS.1} and \ref{CS.2}. Then $(\gcs{E},\mu^0,\phi^0)$
   is a character sheaf of $G^0$.
@@
   $\mu : \bm^* \gcs{L} \to \LxL$ and
-  $F : \Frob{G}^* \gcs{L} \to \gcs{L}$ satisfying conditions \ref{CS.1}
+  $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ satisfying conditions \ref{CS.1}
   and \ref{CS.2}.
@@
 
-  Now we turn to the definition of $F : \Frob{G}^* \gcs{L} \to \gcs{L}$.
+  Now we turn to the definition of $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$.
   As above, we define this isomorphism through a family of
@@
   diagram, above.  We define the sheaf homomorphism
-  $F_x : (\Frob{G}^x)^* \gcs{L}^{\Frob{\Fq}(x)} \to \gcs{L}^x$ by the canonical morphism
+  $\phi_x : (\Frob{G}^x)^* \gcs{L}^{\Frob{\Fq}(x)} \to \gcs{L}^x$ by the canonical morphism
   $\bH^x \to \bH^{\Frob{\Fq}(x)} \times_{\bG^{\Frob{\Fq}(x)}} \bG^x \to $;
@@
   check that the character $\psi_x$ commutes with the family of isomorphisms
-  $F_x : (\Frob{G}^* \gcs{L})\vert_{\bG^x} \iso (\Frob{G}^x)^* \gcs{L}^{\Frob{x}} \to \gcs{L}^x$
-  now defines the isomorphism $F : \Frob{G}^* \gcs{L} \to \gcs{L}$.
+  $\phi_x : (\Frob{G}^* \gcs{L})\vert_{\bG^x} \iso (\Frob{G}^x)^* \gcs{L}^{\Frob{x}} \to \gcs{L}^x$
+  now defines the isomorphism $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$.
   \Clifton{Add some detail here.}
@@
   \[
-  t_{G} : \CSiso{G} \to \Hom(G(\Fq),\EEx),
+  \trFrob{G} : \CSiso{G} \to \Hom(G(\Fq),\EEx),
   \]
@@
   \begin{tikzcd}[row sep=30]
-    {}& \ker t_{\pi_0(G)} \dar & \arrow[dashed]{d} \ker t_{G} & \ker t_{G^0} \dar & \\
+    {}& \ker t_{\pi_0(G)} \dar & \arrow[dashed]{d} \ker \trFrob{G} & \ker t_{G^0} \dar & \\
     0 \rar & \CSiso{\pi_0(G)} \rar \dar{t_{\pi_0(G)}}
-    & \CSiso{G} \rar \dar{t_{G}} & \CSiso{G^0} \rar \dar{t_{G^0}} & 0\\
+    & \CSiso{G} \rar \dar{\trFrob{G}} & \CSiso{G^0} \rar \dar{t_{G^0}} & 0\\
     0 \rar & \Hom(\pi_0(G)(\Fq),\EEx) \rar \dar
     & \arrow[dashed]{d} \Hom(G(\Fq),\EEx) \rar & \Hom(G^0(\Fq),\EEx) \rar \dar & 0\\
-    & \coker t_{\pi_0(G)} & \coker t_{G} &  \coker t_{G^0} &
+    & \coker t_{\pi_0(G)} & \coker \trFrob{G} &  \coker t_{G^0} &
   \end{tikzcd}
@@
   suppose $\cs{L}$ is a character sheaf on $G$ that is trivial on
-  $G^0$. Then $t^\Frob{\Fq}\cs{L}\vert_{G^0(\Fq)} = t^\Frob{\cs{L}^0} =0$,
+  $G^0$. Then $\trFrob{\cs{L}}\vert_{G^0(\Fq)} = \trFrob{\cs{L}^0} =0$,
   by Proposition~\ref{prop:pullback} again. Since the sequence of
@@
   pull-back of $\chi$ along $G(\Fq)\to \pi_0(G)(\Fq)$ is
-  $t^\Frob{\Fq}\cs{L}$. By Propositions~\ref{prop:etale} and \ref{prop:X},
+  $\trFrob{\cs{L}}$. By Propositions~\ref{prop:etale} and \ref{prop:X},
   there is a a character sheaf $\cs{L}_\chi$ on $\pi_0(G)$, unique up
-  to isomorphism, such that $t^\Frob{\cs{L}_\chi} = \chi$. By
+  to isomorphism, such that $\trFrob{\cs{L}_\chi} = \chi$. By
   Proposition~\ref{prop:pullback} again, $\cs{L}$ is isomorphic to the
@@
 
-  It now follows immediately from the snake lemma that $t_{G}$ is an
+  It now follows immediately from the snake lemma that $\trFrob{G}$ is an
   isomorphism of groups.

### 2013-08-10 shanghai.tex
I modified and then promoted your remark (at the end of the section introducing CS(G)) to the textual mainstream because it will used in the section on base change over finite fields.

@@
 characters of algebraic tori over non-Archimedean local fields rests
-on the Picard group of character sheaves on $G$, for all smooth
-commutative group schemes $G$, locally of finite type over $\Fq$, 
-for which the geometric component group is finitely generated.
+on finding the Picard group of character sheaves on $G$, for all smooth commutative group schemes $G$, locally of finite type over $\Fq$, for which the geometric component group is finitely generated.
 
@@
 We fix an algebraic closure $\bFq$ of $\Fq$ and write $\bG$ for the
-commutative group scheme $G \times_{\Spec{\Fq}} \Spec{\bFq}$, over $\bFq$ obtained by base change from $k$. The multiplication morphism for $\bG$ will be denoted by $\bm$. 
-%
+commutative group scheme $G \times_{\Spec{\Fq}} \Spec{\bFq}$ over $\bFq$ obtained by base change from $k$. The multiplication morphism for $\bG$ will be denoted by $\bm$.
+
 Let $\Frob{G}$ be the Frobenius automorphism of $\bG$.
-\Clifton{I was a bit glib about Frobenius, previously.
-Now I've made things more precise here; I'm in the process of tracking this improvement through the paper.}
 Recall that $\Frob{G} = \id_{G}\times \Frob{\Spec{\bFq}}$ where
-$\Frob{\Spec{\bFq}} = \Spec\Frob{\Fq}$ and $\Frob{\Fq}$  is the geometric Frobenius element in $\Weil{\Fq} \subset \Gal(\bFq/\Fq)$.
+$\Frob{\Spec{\bFq}} = \Spec{\Frob{\Fq}}$ and $\Frob{\Fq}$  is the geometric Frobenius element in $\Gal(\bFq/\Fq)$.
 
@@
 \begin{enumerate}
-\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a rank-$1$ $\ell$-adic
-  local system on (the \'etale site of) $\bG$;
+\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a constructible $\ell$-adic sheaf on  (the \'etale site of) $\bG$, locally constant of rank-$1$ on each connected component of $\bG$;
 \labitem{(CS.1)}{CS.1} $\mu: \bm^* \gcs{L} \to \LxL$
@@
 \labitem{(CS.2)}{CS.2} $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an
-  isomorphism of sheaves on $\bG$ compatible with $\mu$ in the sense that the following diagram commutes.
+  isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with $\mu$ in the sense that the following diagram commutes.
 %
@@
 \end{enumerate}
+
+%\begin{remark} \label{rem:CS-action}
+The rule $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$ defines a forgetful functor from character sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{Deligne:Weil2}*{Def.~1.1.10 (i)}.
+As remarked after \cite{Deligne:Weil2}*{Def.~1.1.10}, a $\ell$-adic Weil sheaf $(\gcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
+Since we will need this point of view later, we review that interpretation here.
+Setting
+\[
+\phi(\Frob{\Fq}^n) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi)
+\]
+defines, for every $w\in \Weil{\Fq}$, an isomorphism
+\[
+\phi(w) : w_G^* \gcs{L}\to \gcs{L},
+\]
+such that
+\[
+\phi(uv) = \phi(v) \circ v_G^* \phi(u), \qquad \forall u,v\in \Weil{\Fq}.
+\]
+Note that $\phi = \phi(\Frob{\Fq})$. 
+If we further define $\phi_1(w) \ceq (w_G)_*(\phi(w)^{-1})$ then
+\[
+\phi_1(w) : (w_G)_* \gcs{L}\to \gcs{L},
+\]
+is an isomorphism and
+\[
+\phi_1(uv) = \phi_1(u) \circ (u_G)_* \phi_1(v), \qquad \forall u,v\in \Weil{\Fq},
+\]
+which means the pair $(\gcs{L},\phi_1)$ is almost an action $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of \cite{SGA4.5}*{Expos\'e XIII,~1.1}.
+The pair $(\gcs{L},\phi_1)$ fails to fulfill the requirements of \cite{SGA4.5}*{Expos\'e XIII,~1.1} only because $\Weil{\Fq}$ is profinite.
+This fact goes to the heart of the notion of a Weil sheaf and is one of the essential aspects of our definition of $\CS(G)$.
+%\end{remark}
 
@@
 sheaves} on $G$.\footnote{See {\tt http://ncatlab.org/nlab/show/Picard+group}.}
-
-\begin{remark} \label{rem:CS-action}
-If $W$ is a group equipped with a homomorphism $\alpha : W \to \Gal(\bFq/\Fq)$
-then an \emph{action} of $W$ on $\gcs{L}$ is a collection of isomorphisms
-\[
-\gamma_w : \alpha(w)^* \gcs{L} \to \gcs{L}
-\]
-so that $\gamma_{uw} = \gamma_w \circ \alpha(w)^*\gamma_u$. \David{make sure I have the order right and add a reference}
-Specifying an $F$ as in \ref{CS.2} is the same as giving an action of the Weil group $\Weil{k}$
-on $\gcs{L}$ compatible with $\mu$.
-\end{remark}
+The main result in this paper is the determination of the Picard group of character sheaves on $G$, when the geometric component group of $G$ is finitely generated.
 
@@
 an object in $C(G)$ is a pair $(f,\psi)$ where: 
-$f : H\to G$ is an isogeny (a finite, surjective, etale, morphism of commutative group $\Fq$-schemes) 
+$f : H\to G$ an etale cover and a morphism of commutative group $\Fq$-schemes (an isogeny) 
 for which the action of $\Gal(\bFq/\Fq)$ on the etale group scheme $\ker f$ is trivial, 
 and $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$;
-a map $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(\varphi,T)$ 
-where $\varphi$ is a morphism of schemes such that $f' = f\circ \varphi$
+a map $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(\alpha,T)$ 
+where $\alpha$ is a morphism of schemes such that $f' = f\circ \alpha$
 and $T : V\to V'$ is a linear transformation equivariant 
 for the action of $\ker f'$ on $V'$ by $\psi'$ 
-and the action of $\ker f'$ on $V$ by $\psi \circ \varphi$.
+and the action of $\ker f'$ on $V$ by $\psi \circ h$.
 
@@
 
-We say that $(\varphi,T)$ in $C(G)$ is a weak isomorphism if $T$ is an isomorphism of vector spaces. 
+We say that $(\alpha,T)$ in $C(G)$ is a weak isomorphism if $T$ is an isomorphism of vector spaces. 
 Let $C(G)[W^{-1}]$ be the localization of $C(G)$ at weak isomorphisms.
@@
  We will do this by constructing a faithful monoidal functor $L : C_1(G) \to \CSb(G)$ 
- such that $L(\varphi,T)$ is an isomorphism precisely when $(\varphi,T)$ is a weak isomorphism. 
+ such that $L(\alpha,T)$ is an isomorphism precisely when $(h,T)$ is a weak isomorphism. 
  Factoring along $C_1(G) \to \CSb(G)$ will produce the full and faithful monoidal functor we seek.
@@
  and the stalk $L(f,\psi)_{\bar g}$ of $L(f,\psi)$ at a geometric point ${\bar g}$ on $G$ 
- with the $\EE$-vector space consisting of those functions $s: \abs{f^{-1}({\bar g})} \to V$ such that 
+ with the $\EE$-vector space consisting of those functions $s: \abs{f^{-1}({\bar s})} \to V$ such that 
  $s(a\cdot {\bar h}) = \psi(a)(s({\bar h}))$ for all $a\in \ker f$ and for all ${\bar h} \in f^{-1}({\bar g})$.
  Since $L(f,\psi)$ is trivialized by $f$, it is a local system on $G$.
- For any map $(\varphi,T)$ in $C(G)$, let $L(\varphi,T) : L(f,\psi) \to L(f',\psi')$ be the homomorphism of local systems defined 
- %at geometric points $L(\varphi,T)_{\bar g} : L(f,\psi)_{\bar g} \to L(f',\psi')_{\bar g}$ 
- by $s \mapsto s' \ceq T\circ s\circ \varphi$. 
+ For any map $(\alpha,T)$ in $C(G)$, let $L(\alpha,T) : L(f,\psi) \to L(f',\psi')$ be the homomorphism of local systems defined 
+ %at geometric points $L(\alpha,T)_{\bar g} : L(f,\psi)_{\bar g} \to L(f',\psi')_{\bar g}$ 
+ by $s \mapsto s' \ceq T\circ s\circ \alpha$. 
  This defines a monoidal functor $L$ from $C(G)$ to $\Loc(G)$. 
@@
    \begin{tikzcd}
-   (f,\psi) \arrow{r}{(\varphi_1,T_1)} & (f_1,\psi_1) & \arrow[swap]{l}{(\varphi'_1,T'_1)} (f',\psi')
-   \end{tikzcd}
-  \]
- where $(\varphi',T') : (f,\psi) \to (f',T')$ is any map in $C(G)$ 
- and $(\varphi'_1,T'_1) : (f_1,\psi_1) \to (f',\psi')$ is a weak isomorphism; 
- this morphism is commonly denoted by $(\varphi_1,T_1)^{-1}\circ (\varphi'_1,T'_1)$. 
- %The equivalence relation identifies $(\varphi_1,T_1)^{-1}\circ (\varphi'_1,T'_1)$ 
- % with $(\varphi_2,T_2)^{-1}\circ (\varphi'_2,T'_2)$ if there are maps 
+   (f,\psi) \arrow{r}{(\alpha_1,T_1)} & (f_1,\psi_1) & \arrow[swap]{l}{(\alpha'_1,T'_1)} (f',\psi')
+   \end{tikzcd}
+  \]
+ where $(\alpha',T') : (f,\psi) \to (f',T')$ is any map in $C(G)$ 
+ and $(\alpha'_1,T'_1) : (f_1,\psi_1) \to (f',\psi')$ is a weak isomorphism.
+% this morphism is commonly denoted by $(\alpha_1,T_1)^{-1}\circ (\alpha'_1,T'_1)$. 
+ %The equivalence relation identifies $(\alpha_1,T_1)^{-1}\circ (\alpha'_1,T'_1)$ 
+ % with $(\alpha_2,T_2)^{-1}\circ (\alpha'_2,T'_2)$ if there are maps 
  %$(f_1,\psi_1)\to (f_0,\psi_0)$ and $(f_2,\psi_2)\to (f_0,\psi_0)$ making the following diagram commute
@@
  %  & (f_1,\psi_1) \arrow{d} & \\
- %  (f,\psi) \arrow{ur}{(\varphi_1,T_1)} \arrow{dr}{(\varphi_2,T_2)} & (f_0,\psi_0)  & \arrow[swap]{ld}{(\varphi'_2,T'_2)} \arrow[swap]{lu}{(\varphi'_1,T'_1)} (f',\psi')\\
+ %  (f,\psi) \arrow{ur}{(\alpha_1,T_1)} \arrow{dr}{(\alpha_2,T_2)} & (f_0,\psi_0)  & \arrow[swap]{ld}{(\alpha'_2,T'_2)} \arrow[swap]{lu}{(\alpha'_1,T'_1)} (f',\psi')\\
  %  & (f_2,\psi_2) \arrow{u} & \\
@@
  Observe that $L$ takes weak isomorphisms in $C(G)$ to isomorphisms in $\Loc(G)$. 
- To see this, let $(\varphi,T) : (f,\psi)\to (f',\psi')$ be a weak isomorphism, 
+ To see this, let $(h,T) : (f,\psi)\to (f',\psi')$ be a weak isomorphism, 
  where $f:H\to G$ and $f':H'\to G$ as above. 
  Since $T$ is an isomorphism, we may replace $V'$ with $V$ and $T$ with $\id_V$, without loss of generality. 
- Then the equivariance condition on $T$ becomes $\psi' = \psi\circ \varphi$ on the finite etale group scheme $\ker f'$. 
- Since $f' = f \circ \varphi$ and $f$ and $f'$ are etale covers, it follows that $\varphi$ is also an etale cover. 
- It follows that $\varphi : H'\to H$ admits a section $\varphi' : H \to H'$, 
- which provides the inverse to $L(\varphi,T) : L(f,\psi) \to L(f',\psi')$, above. 
- It is also clear that if $L(\varphi,T)$ is an isomorphism of local systems, 
+ Then the equivariance condition on $T$ becomes $\psi' = \psi\circ h$ on the finite etale group scheme $\ker f'$. 
+ Since $f' = f \circ \alpha$ and $f$ and $f'$ are etale covers, it follows that $\alpha$ is also an etale cover. 
+ It follows that $\alpha : H'\to H$ admits a section $\alpha' : H \to H'$, 
+ which provides the inverse to $L(\alpha,T) : L(f,\psi) \to L(f',\psi')$, above. 
+ \Clifton{Is it clear?}
+ It is also clear that if $L(\alpha,T)$ is an isomorphism of local systems, 
  then $T$ must be an isomorphism of vector spaces, 
- whence $(\varphi,T)$ is a weak isomorphism: $W$ is saturated.
+ whence $(\alpha,T)$ is a weak isomorphism: $W$ is saturated.
 
@@
   \begin{equation}\label{t}
-    \forall x\in G(\bFq),\qquad F_{x}(s(\Frob{\Fq}(x)) = \tau_\cs{L}(\Frob{\Fq})(x) s(x).
+    \forall x\in G(\bFq),\qquad \phi_{x}(s(\Frob{\Fq}(x)) = \tau_\cs{L}(\Frob{\Fq})(x) s(x).
   \end{equation}
@@
 
-\begin{lemma}
+\begin{lemma}\label{lemma:section}
  If $\cs{L}$ is a character sheaf then there is a non-trivial section of $\gcs{L}$ 
@@
    date={1977},
-   pages={iv+312pp},
+%   pages={iv+312pp},
 %   review={\MR{0463174 (57 \#3132)}},
+}
+
+\bib{Deligne:Weil2}{article}{
+   author={Deligne, Pierre},
+   title={La conjecture de Weil. II},
+%   language={French},
+   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
+   number={52},
+   date={1980},
+   pages={137--252},
+%   issn={0073-8301},
+%   review={\MR{601520 (83c:14017)}},
 }
@@
    date={1973},
-   pages={x+438},
+%   pages={x+438},
 %   review={\MR{0354657 (50 \#7135)}},

### 2013-08-10 shanghai.tex
A commit before I move to a different computer.
Changed `character sheaves' to `geometrized characters' throughout. Reworked a bit of the base change material.

@@
 \newcommand{\dualcs}[1]{\cs{#1}^\dagger}
-\newcommand{\CS}{{\mathcal{C\hskip-1.8pt S}}}
-\newcommand{\CSb}{{\mathcal{C\hskip-1.8pt S}_0}}
-\newcommand{\CSf}{{\mathcal{C\hskip-1.8pt S}_{f}}}
-\newcommand{\CSiso}[1]{\CS(#1)_{/\textit{iso}}}
-\newcommand{\CSbiso}[1]{\CSb(#1)_{/\text{iso}}}
-\newcommand{\CSfiso}[1]{\CSf(#1)_{/\text{iso}}}
+\newcommand{\GC}{{\mathcal{G\hskip-0.8pt C}}}
+\newcommand{\GCb}{{\GC_0}}
+\newcommand{\GCf}{{\GC_f}}
+\newcommand{\GCiso}[1]{\GC(#1)_{/\textit{iso}}}
+\newcommand{\GCbiso}[1]{\GCb(#1)_{/\text{iso}}}
+\newcommand{\GCfiso}[1]{\GCf(#1)_{/\text{iso}}}
 \newcommand{\CE}{{\mathcal{C\hskip-1.8pt E}}}
@@
 \begin{abstract}
-  We study the category of character sheaves on smooth commutative
+  We study the category of geometrized characters on smooth commutative
   group schemes $G$ locally of finite type over finite fields
@@
   is finitely-generated, we show that the group of isomorphism classes
-  of character sheaves on $G$ is canonically isomorphic to the group
+  of geometrized characters on $G$ is canonically isomorphic to the group
   of characters of $G(\Fq)$. We use this result to exhibit an
   isomorphism between admissible characters of $T(K)$ and isomorphism
-  classes of character sheaves on the Greenberg transform of the Néron
+  classes of geometrized characters on the Greenberg transform of the Néron
   model of $T$, where $K$ is any non-Archimdean local field and $T$ is
@@
 %\noindent
-In this paper we show that the monidal category of character sheaves
+In this paper we show that the monidal category of geometrized characters
 on the Greenberg transform of the locally finite type Neron model of
@@
 
-Since the character sheaves that appear in this paper are not quite an
-instance of those defined by George Luzstig, who coined the term, we
-begin by explaining what we mean by `character sheaves' here. 
+We begin by explaining what we mean by `geometrized characters'. 
 Let $G$ be a smooth commutative group scheme locally of finite
@@
 finite type over $\Fq$. Fix a prime $\ell$ that does not divide
-$q$. By a {character sheaf} on $G$ we mean a triple $\cs{L}\ceq
+$q$. By a {geometrized character} on $G$ we mean a triple $\cs{L}\ceq
 (\gcs{L},\mu,\phi)$ where $\gcs{L}$ is a constructible $\ell$-adic sheaf
@@
 
-Character sheaves on $G$ form a category, denoted by $\CS(G)$. In
-fact, $\CS(G)$ is a rigid symmetric monoidal category, so isomorphism
-classes of character sheaves on $G$ form a group, denoted by
-$\CSiso{G}$; this is the Picard group of the category of
-character sheaves on $G$. Our application of character sheaves to
+Geometrized characters on $G$ form a category, denoted by $\GC(G)$. In
+fact, $\GC(G)$ is a rigid symmetric monoidal category, so isomorphism
+classes of geometrized characters on $G$ form a group, denoted by
+$\GCiso{G}$; this is the Picard group of the category of
+geometrized characters on $G$. Our application of geometrized characters to
 characters of algebraic tori over non-Archimedean local fields rests
-on finding the Picard group of character sheaves on $G$, for all smooth commutative group schemes $G$, locally of finite type over $\Fq$, for which the geometric component group is finitely generated.
+on finding the Picard group of geometrized characters on $G$, 
+for all smooth commutative group schemes $G$, locally of finite type over $\Fq$, 
+for which the geometric component group is finitely generated.
 
@@
 \[
-\CSiso{\GN{T}_d} 
+\GCiso{\GN{T}_d} 
 \iso
@@
 \] 
-between the Picard group of the category of character sheaves on
+between the Picard group of the category of geometrized characters on
 $\GN{T}_d$ and the group of characters $T(K) \to \EEx$ of
@@
 %be), we arrive at a model for the group of quasi-characters of
-%$K^\times$: the monoidal category of character sheaves on the
+%$K^\times$: the monoidal category of geometrized characters on the
 %Greenberg transform of the Neron model of
@@
 
-\section{The category of character sheaves}\label{section:category}
+\section{The category of geometrized characters}\label{sec:category}
 
@@
 
-The category of character sheaves on $G$, denoted by \cdef{$\CS(G)$},
-is defined as follows.  A \cdef{character sheaf} on $G$ is a triple
+The category of geometrized characters on $G$, denoted by \cdef{$\GC(G)$},
+is defined as follows.  A \cdef{geometrized character} on $G$ is a triple
 $\cs{L}\ceq (\gcs{L},\mu,\phi)$ where:
@@
 \end{enumerate}
-Morphisms in $\CS(G)$ are defined in the natural way:
+Morphisms in $\GC(G)$ are defined in the natural way:
 \begin{enumerate}
 \labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,\phi)$ and
-  $\cs{L'} = (\gcs{L'},\mu',\phi')$ are character sheaves on $G$ then
-  $\Hom_{\CS(G)}(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$
+  $\cs{L'} = (\gcs{L'},\mu',\phi')$ are geometrized characters on $G$ then
+  $\Hom_{\GC(G)}(\cs{L},\cs{L'})$ is the set of morphisms $\alpha : \gcs{L} \to \gcs{L'}$
   of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
@@
   \begin{tikzcd}[column sep=40]
-  \Frob{G}^* \gcs{L} \rar{\Frob{G}^* \varphi} \arrow[swap]{d}{F} & \Frob{G}^* \gcs{L'} \dar{F'}
-  & \arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} & \arrow[swap]{d}{\mu} m^* \gcs{L} \rar{m^* \varphi} & m^* \gcs{L'} \dar{\mu'} \\
-  \gcs{L} \rar{\varphi} & \gcs{L'}
-  & {} & \LxL \rar{\tight{1}{\varphi\boxtimes \varphi}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
+  \Frob{G}^* \gcs{L} \rar{\Frob{G}^* \alpha} \arrow[swap]{d}{\phi} & \Frob{G}^* \gcs{L'} \dar{\phi'}
+  & \arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} & \arrow[swap]{d}{\mu} m^* \gcs{L} \rar{m^* \alpha} & m^* \gcs{L'} \dar{\mu'} \\
+  \gcs{L} \rar{\alpha} & \gcs{L'}
+  & {} & \LxL \rar{\tight{1}{\alpha\boxtimes \alpha}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
   \end{tikzcd}
@@
 %\begin{remark} \label{rem:CS-action}
-The rule $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$ defines a forgetful functor from character sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{Deligne:Weil2}*{Def.~1.1.10 (i)}.
-As remarked after \cite{Deligne:Weil2}*{Def.~1.1.10}, a $\ell$-adic Weil sheaf $(\gcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
+The rule $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$ defines a forgetful functor from geometrized characters on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{Deligne:Weil2}*{Def.~1.1.10 (i)}.
+%
+As remarked after \cite{Deligne:Weil2}*{Def.~1.1.10}, a Weil sheaf $(\gcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
 Since we will need this point of view later, we review that interpretation here.
@@
 \[
-\phi(\Frob{\Fq}^n) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi)
+\varphi(\Frob{\Fq}^n) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi)
 \]
@@
 \[
-\phi(w) : w_G^* \gcs{L}\to \gcs{L},
+\varphi(w) : w_G^* \gcs{L}\to \gcs{L},
 \]
@@
 \[
-\phi(uv) = \phi(v) \circ v_G^* \phi(u), \qquad \forall u,v\in \Weil{\Fq}.
-\]
-Note that $\phi = \phi(\Frob{\Fq})$. 
-If we further define $\phi_1(w) \ceq (w_G)_*(\phi(w)^{-1})$ then
-\[
-\phi_1(w) : (w_G)_* \gcs{L}\to \gcs{L},
+\forall u,v\in \Weil{\Fq},\qquad \varphi(uv) = \varphi(v) \circ v_G^* \varphi(u).
+\]
+Note that $\phi = \varphi(\Frob{\Fq})$. 
+If we further define $\varphi_1(w) \ceq (w_G)_*(\varphi(w)^{-1})$ then
+\[
+\varphi_1(w) : (w_G)_* \gcs{L}\to \gcs{L},
 \]
@@
 \[
-\phi_1(uv) = \phi_1(u) \circ (u_G)_* \phi_1(v), \qquad \forall u,v\in \Weil{\Fq},
-\]
-which means the pair $(\gcs{L},\phi_1)$ is almost an action $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of \cite{SGA4.5}*{Expos\'e XIII,~1.1}.
-The pair $(\gcs{L},\phi_1)$ fails to fulfill the requirements of \cite{SGA4.5}*{Expos\'e XIII,~1.1} only because $\Weil{\Fq}$ is profinite.
-This fact goes to the heart of the notion of a Weil sheaf and is one of the essential aspects of our definition of $\CS(G)$.
+ \forall u,v\in \Weil{\Fq},\qquad \varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v),
+\]
+which means the pair $(\gcs{L},\varphi_1)$ is almost an action $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of \cite{SGA4.5}*{Expos\'e XIII,~1.1}.
+The pair $(\gcs{L},\varphi_1)$ fails to fulfill the requirements of \cite{SGA4.5}*{Expos\'e XIII,~1.1} only because $\Weil{\Fq}$ is profinite.
+This fact goes to the heart of the notion of a Weil sheaf and is one of the essential aspects of our definition of $\GC(G)$.
 %\end{remark}
 
-\section{The Picard group of character sheaves}
+\section{The Picard group of geometrized characters}
 
 %\begin{proposition}\label{tensor}
-The category $\CS(G)$ of character sheaves on $G$ is a rigid monoidal
+The category $\GC(G)$ of geometrized characters on $G$ is a rigid monoidal
 category [insert reference] under
@@
 %\end{proposition}
-(The category of characters sheaves on $G$ is not abelian, so $\CS(G)$
+(The category of characters sheaves on $G$ is not abelian, so $\GC(G)$
 is not a tensor category in the sense of \cite{Deligne:tensorielles}.)
@@
 %
-This rigid monoidal category structure for $\CS(G)$ puts a group
-structure on the set $\CSiso{G}$ of isomorphism classes in
-$\CS(G)$; we refer to this as the \cdef{Picard group of character
+This rigid monoidal category structure for $\GC(G)$ puts a group
+structure on the set $\GCiso{G}$ of isomorphism classes in
+$\GC(G)$; we refer to this as the \cdef{Picard group of character
 sheaves} on $G$.\footnote{See {\tt http://ncatlab.org/nlab/show/Picard+group}.}
-The main result in this paper is the determination of the Picard group of character sheaves on $G$, when the geometric component group of $G$ is finitely generated.
+The main result in this paper is the determination of the Picard group of geometrized characters on $G$, when the geometric component group of $G$ is finitely generated.
 
@@
 
-Let $\cs{L}$ be a character sheaf on $G$. Every $g\in G(\Fq)$
+Let $\cs{L}$ be a geometrized character on $G$. Every $g\in G(\Fq)$
 determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$ and
@@
 (pointwise multiplication of functions) and that $\trFrob{\cs{L}} = \trFrob{\cs{L'}}$
-if $\cs{L} \iso \cs{L'}$ in $\CS(G)$. In this way we obtain a group homomorphism
-\[
-\cdef{\trFrob{G}} : \CSiso{G} \longrightarrow \Hom_\text{grp}(G(\Fq),\EEx),
+if $\cs{L} \iso \cs{L'}$ in $\GC(G)$. In this way we obtain a group homomorphism
+\[
+\cdef{\trFrob{G}} : \GCiso{G} \longrightarrow \Hom_\text{grp}(G(\Fq),\EEx),
 \qquad \text{defined by}\qquad \cs{L} \mapsto \trFrob{\cs{L}},
 \]
-from the Picard group of character sheaves on $G$ to the character group of $G(\Fq)$.
+from the Picard group of geometrized characters on $G$ to the character group of $G(\Fq)$.
 
@@
 of $G$ is finitely-generated then the trace of Frobenius defines an
-isomorphism from the Picard group of character sheaves $G$ to the
+isomorphism from the Picard group of geometrized characters $G$ to the
 group of characters of $G(\Fq)$ (here, as throughout the paper, $G$ is
@@
 
-\section{Pull-back of character sheaves}\label{subsection:pullback}
+\section{Pull-back of geometrized characters}\label{subsection:pullback}
 
@@
   $(\gcs{L},\mu,\phi) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
-  defines a monoidal functor $f^* : \CS(G) \to \CS(H)$ such that
+  defines a monoidal functor $f^* : \GC(G) \to \GC(H)$ such that
   \[
   \begin{tikzcd}[row sep=20, column sep=30]
-   \CSiso{G} \rar{f^*} \arrow[swap]{d}{\trFrob{G}} & \CSiso{H} \dar{t_H} \\
+   \GCiso{G} \rar{f^*} \arrow[swap]{d}{\trFrob{G}} & \GCiso{H} \dar{t_H} \\
   \Hom_\text{grp}(G(\Fq),\EEx) \rar & \Hom_\text{grp}(H(\Fq),\EEx)
@@
 \begin{proof}
-  Let $\cs{L}$ be a character sheaf on $G$. We start by showing that
+  Let $\cs{L}$ be a geometrized character on $G$. We start by showing that
   $\bf^*\gcs{L}$ is locally constant on connected components of
@@
   for the restriction of $f$ to $\bH^j$.  Since $\cs{L}$
-  is a character sheaf, $\gcs{L}$ is locally constant on the connect
+  is a geometrized character, $\gcs{L}$ is locally constant on the connect
   components of $\bG$; thus, there is a finite etale covering
@@
   To see that $(\gcs{L},\mu,\phi) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
-  defines a functor $f^* : \CS(G) \to \CS(H)$ one applies the functors $\bf^*$ and
+  defines a functor $f^* : \GC(G) \to \GC(H)$ one applies the functors $\bf^*$ and
   $\bf^*\tight{1}{\times}{1}\bf^*$ to \ref{CS.3} and argue as
   above. It follows from the fact that sheaf hom commutes with these
-  functors that $f^* : \CS(G) \to \CS(H)$ is a monoidal functor.
+  functors that $f^* : \GC(G) \to \GC(H)$ is a monoidal functor.
 %
-  The fact that the functor $f^* : \CS(G) \to \CS(H)$ commutes with
+  The fact that the functor $f^* : \GC(G) \to \GC(H)$ commutes with
   the trace of Frobenius, in the sense above, follows immediately from
@@
 \begin{tikzcd}
-\CS(0) \rar & \CS(\pi_0(G)) \rar & \CS(G) \rar & \CS(G^0) \rar & \CS(0)
+\GC(0) \rar & \GC(\pi_0(G)) \rar & \GC(G) \rar & \GC(G^0) \rar & \GC(0)
 \end{tikzcd}
@@
 \begin{tikzcd}
-\CSiso{0} \rar & \CSiso{\pi_0(G)} \rar & \CSiso{G} \rar & \CSiso{G^0} \rar & \CSiso{0}.
+\GCiso{0} \rar & \GCiso{\pi_0(G)} \rar & \GCiso{G} \rar & \GCiso{G^0} \rar & \GCiso{0}.
 \end{tikzcd}
 \end{equation}
-It is easy to see that $\CSiso{0}$ is trivial. In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; 
+It is easy to see that $\GCiso{0}$ is trivial. In this paper we will find $\GCiso{G^0}$ and $\GCiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; 
 the snake lemma will then allow us to show
 \[
-\CSiso{G} \iso \Hom(G(\Fq),\EE^\times),
+\GCiso{G} \iso \Hom(G(\Fq),\EE^\times),
 \]
@@
 
-When using character sheaves to study characters, it is useful to understand
-how character sheaves behave under change of fields.
-Suppose that $k'$ is a finite extension of $k$ of degree $n$, $G$ is an abelian group scheme
-over $k$ as in Theorem \ref{thm:snake} and $G_{k'}$ is the base change of $G$ to $k'$.
-If $\cs{L} = (\gcs{L}, \mu, \phi)$ is a character sheaf on $G$ we may define
-a character sheaf $\nu(\cs{L}) = (\gcs{L}, \mu, \phi_{k'})$ on $G_{k'}$ by setting
+When using geometrized characters to study characters, it is useful to understand
+how geometrized characters behave under change of fields.
+Suppose that $k'$ is a finite extension of $k$ of degree $n$, 
+$G$ is a commutative smooth group scheme locally of finite type over $k$.
+If $\cs{L} = (\gcs{L}, \mu, \phi)$ is a geometrized character on $G$ we may define
+a geometrized character $\cs{L}' = (\gcs{L}, \mu, \phi_{k'})$ on 
+$G_{k'}\ceq G\times_{\Spec{k}} \Spec{k'}$ by setting
 \[
@@
 \]
-The commutativity of the diagram (CS.2) for $\phi_{k'}$ follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
-Note that we may also think about the construction of $\phi_{k'}$ as taking the action of $\Weil{k}$ defined in Remark
-\ref{rem:CS-action} and restricting it to $\Weil{k'}$.
+The commutativity of the diagram (CS.2) for $\phi_{k'}$ 
+follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
+Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
+as taking the action $\varphi$ of $\Weil{k}$ on $\gcs{L}$ 
+defined in Section~\ref{sec:category} and restricting it to the subgroup $\Weil{k'}$.
 
 \begin{proposition}\label{prop:basechange}
-The following diagram commutes, where the bottom map is induced by the norm $G(k') \rightarrow G(k)$:
-\[
-\begin{tikzcd}
-\CSiso{G} \rar{\nu} \dar{\trFrob{G}} & \CSiso{G_{k'}} \dar{\trFrob{G_{k'}}} \\
+ The rule $(\gcs{L}, \mu, \varphi) \mapsto (\gcs{L}, \mu, \varphi\vert_{\Weil{\Fq}})$ 
+ defines a monoidal functor $\GC(G) \to \GC(G_{k'})$. 
+ Moreover, the following diagram commutes, 
+ where the top map is induced by $\GC(G) \to \GC(G_{k'})$ 
+ and the bottom map is induced by the norm $G(k') \rightarrow G(k)$:
+\[
+\begin{tikzcd}[column sep=45]
+\GCiso{G} \rar{\text{ext'n of scalars}} \dar{\trFrob{G}} & \GCiso{G_{k'}} \dar{\trFrob{G\times_{\Spec{k}} \Spec{k'}}} \\
 \Hom(G(k), \EEx) \rar{\Nm} & \Hom(G(k'), \EEx).
@@
 \begin{proof}
-\Clifton{This proof is missing! Can David insert it?}
+\Clifton{This proof is missing. Can David insert it?}
 \end{proof}
 
-\section{Bounded character sheaves}\label{sec:bounded}
-
-Let $\CSb(G)$ be the category of pairs $(\cs{L}_0,\mu_0)$ 
+\section{Bounded geometrized characters}\label{sec:bounded}
+
+Let $\GCb(G)$ be the category of pairs $(\cs{L}_0,\mu_0)$ 
 where $\cs{L}_0$ is a constructible $\ell$-adic sheaf on $G$, 
@@
 satisfying the analogue of Condition~\ref{CS.1} on $G$; 
-morphisms in $\CSf(G)$ are defined as in (the second part of) Condition~\ref{CS.2}. 
-This is the category of \cdef{bounded character sheaves} on $G$. 
+morphisms in $\GCf(G)$ are defined as in (the second part of) Condition~\ref{CS.2}. 
+This is the category of \cdef{bounded geometrized characters} on $G$. 
 \Clifton{Should this be $\sheafHom(\cs{L}_0,\EE)$?}
@@
 \begin{proposition}
-$\CSb(G)$ is (equivalent to) a full subcategory of $\CS(G)$.
+$\GCb(G)$ is (equivalent to) a full subcategory of $\GC(G)$.
 \end{proposition}
@@
  Let $b_G : {\bar G} \to G$ be the pull-back of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Let $(\cs{L}_0,\mu_0)$ be a bounded character sheaf on $G$. 
+ Let $(\cs{L}_0,\mu_0)$ be a bounded geometrized character on $G$. 
  Then $\cs{L}_0$ is, in particular, an $\ell$-adic constructible sheaf on $G$. 
@@
  Moreover, $\phi$ is compatible with $\mu$ in the sense of Condition~\ref{CS.3}.
- It follows that functor $(\cs{L}_0,\mu_0) \mapsto (b_G^*\cs{L}_0,b_{G\times G}^* \mu_0, \phi)$, denoted by  $B_G^*: \CSb(G) \hookrightarrow \CS(G)$ below, is full and faithful.
+ It follows that functor $(\cs{L}_0,\mu_0) \mapsto (b_G^*\cs{L}_0,b_{G\times G}^* \mu_0, \phi)$, denoted by  $B_G^*: \GCb(G) \hookrightarrow \GC(G)$ below, is full and faithful.
 \end{proof}
 
-\section{Finite character sheaves}\label{sec:finite}
-
- %In this section we describe a full subcategory of $\CSb(G)$
- %which will illuminate some features of $\CSb(G)$ and also play a role in some arguments below.
-
-To define the category of finite character sheaves we must work a bit harder.
+We will see that the full subcategory $\GC_0(G)$ of bounded geometrized characters is a proper subcategory, in general.
+Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)$ to the subgroup $\GCbiso{G}$ is an isomorphism onto the subgroup of $\chi \in \Hom_\text{grp}(G(\Fq),\EEx)$ such that the image of $\chi$ is bounded in $\EEx$.
+
+\section{Finite geometrized characters}\label{sec:finite}
+
+ %In this section we describe a full subcategory of $\GCb(G)$
+ %which will illuminate some features of $\GCb(G)$ and also play a role in some arguments below.
+
+To define the category of finite geometrized characters we must work a bit harder.
 Consider the following category $C(G)$:
@@
 Now, let $C_1(G)$ be the subcategory of $C(G)$ such that $\psi$ is a one-dimensional representation
-and let $\CSf(G)$ be the localisation of $C_1(G)$ at weak isomorphisms. 
-This is the rigid symmetric monoidal category of \cdef{finite character sheaves} on $G$.
+and let $\GCf(G)$ be the localisation of $C_1(G)$ at weak isomorphisms. 
+This is the rigid symmetric monoidal category of \cdef{finite geometrized characters} on $G$.
 
 \begin{proposition}\label{prop:bounded}
- $\CSf(G)$ is (equivalent to) a full subcategory of $\CSb(G)$.
+ $\GCf(G)$ is (equivalent to) a full subcategory of $\GCb(G)$.
 \end{proposition}
@@
 \begin{proof}
- To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \CSf(G) \to \CSb(G)$.
+ To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \GCf(G) \to \GCb(G)$.
  %
- We will do this by constructing a faithful monoidal functor $L : C_1(G) \to \CSb(G)$ 
+ We will do this by constructing a faithful monoidal functor $L : C_1(G) \to \GCb(G)$ 
  such that $L(\alpha,T)$ is an isomorphism precisely when $(h,T)$ is a weak isomorphism. 
- Factoring along $C_1(G) \to \CSb(G)$ will produce the full and faithful monoidal functor we seek.
+ Factoring along $C_1(G) \to \GCb(G)$ will produce the full and faithful monoidal functor we seek.
 
@@
 
- One more ingredient is needed before we can exhibit the full functor $L_G: \CSf(G) \to \CSb(G)$ promised above: 
- we must put rigid monoidal category structures on $\CSf(G)$ and $\CSb(G)$.
+ One more ingredient is needed before we can exhibit the full functor $L_G: \GCf(G) \to \GCb(G)$ promised above: 
+ we must put rigid monoidal category structures on $\GCf(G)$ and $\GCb(G)$.
 
@@
  let $\mu(f,\psi)$ be that isomorphism of $\ell$-adic sheaves on $G$,
- It follows immediately that the functor $L_G  \ceq  L_{W}\vert_{\CSf(G)} : \CS_b(G) \to \CSb(G)$, 
+ It follows immediately that the functor $L_G  \ceq  L_{W}\vert_{\GCf(G)} : \GC_b(G) \to \GCb(G)$, 
  given on objects by $(f,\psi) \mapsto (L(f,\psi), \mu(f,\psi))$,
@@
 %\Clifton{I'll address this point in the next section: "Because $\Gal(\bFq/\Fq)$ acts trivially on $\Aut({\bar f})$, the local system ${\bar L}_G(f,\psi)\ceq b_G^* L(f,\psi)$ comes equipped with a canonical isomorphism $F : \Frob{G}^* {\bar L}_G(f,\psi) \to {\bar L}_G(f,\psi)$ of constructible sheaves on ${\bar G}$."}
+
+We will see that the full subcategory $\GC_f(G) \subset \GC_0(G)$ of finite geometrized characters is a proper subcategory, in general.
+Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)$ to the subgroup $\GCfiso{G}$ is an isomorphism onto the subgroup of $\chi \in \Hom_\text{grp}(G(\Fq),\EEx)$ such that the image of $\chi$ is finite in $\EEx$.
 
@@
   If $G$ is a connected commutative algebraic group over $\Fq$ then 
-  the full subcategories $\CSf(G) \hookrightarrow \CSb(G) \hookrightarrow \CS(G)$ 
+  the full subcategories $\GCf(G) \hookrightarrow \GCb(G) \hookrightarrow \GC(G)$ 
   appearing in Section~\ref{sec:bounded} are equivalences 
-  and (with reference to Section~\ref{sec:Frob})
-  \[
-  \trFrob{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)
+  and
+  \[
+  \trFrob{G} : \GCiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)
   \]
@@
   Observe that the forgetful functor $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$
-  sends character sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{Deligne:Weil2}*{1.1.10}.
+  sends geometrized characters on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{Deligne:Weil2}*{1.1.10}.
   While is it not true that all Weil sheaves on $G$ descend to local systems on $G$, 
-  we will see that those that appear in the image of this forgetful functor from character sheaves do.
+  we will see that those that appear in the image of this forgetful functor from geometrized characters do.
 
@@
   $\ell$-adic representations of $\W(G,\bg)$ \cite{Deligne:Weil2}*{1.1.12}. 
-  Now let $(\gcs{L},\mu,\phi)$ be a character sheaf on $G$ 
+  Now let $(\gcs{L},\mu,\phi)$ be a geometrized character on $G$ 
   and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gcs{L},\phi)$. 
@@
   the latter appearing in the definition of $\cs{L}$. 
-  Then, as in Section~\ref{sec:bounded}, $(\cs{L}_0,\mu_0)$ is an object in $\CSb(G)$ 
-  and $\cs{L} = (\gcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\cs{L}_0,b_{G\times G}^*\mu_0)$ in $\CS(G)$.
-  Thus, the full and faithful functor $B_G^* : \CSb(G) \to \CS(G)$ from Section~\ref{sec:bounded}
+  Then, as in Section~\ref{sec:bounded}, $(\cs{L}_0,\mu_0)$ is an object in $\GCb(G)$ 
+  and $\cs{L} = (\gcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\cs{L}_0,b_{G\times G}^*\mu_0)$ in $\GC(G)$.
+  Thus, the full and faithful functor $B_G^* : \GCb(G) \to \GC(G)$ from Section~\ref{sec:bounded}
   is also essentially surjective, hence an equivalence.
@@
 
-  In Section~\ref{sec:finite} we saw that $\CSf(G)$ is a full subcategory of $\CSb(G)$;
-  more precisely, we exhibited a full and faithful functor $L_G : \CSf(G) \to \CSb(G)$.
+  In Section~\ref{sec:finite} we saw that $\GCf(G)$ is a full subcategory of $\GCb(G)$;
+  more precisely, we exhibited a full and faithful functor $L_G : \GCf(G) \to \GCb(G)$.
   We now show that this functor is essentially surjective 
@@
 
-  Let $(\cs{L}_0,\mu_0)$ be a bounded character sheaf on $G$. 
-  Then $\cs{L}\ceq B_G^*(\cs{L}_0,\mu_0)$ is a character sheaf on $G$.
+  Let $(\cs{L}_0,\mu_0)$ be a bounded geometrized character on $G$. 
+  Then $\cs{L}\ceq B_G^*(\cs{L}_0,\mu_0)$ is a geometrized character on $G$.
   Recall the definition of the character $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}. 
@@
   $\psi(g)(v) = \trFrob{\cs{L}}(g) v$ for $v\in V$. 
-  Then $(f,\psi)$ is a finite character sheaf.
+  Then $(f,\psi)$ is a finite geometrized character.
 
@@
   Using \cite{Laumon}*{Th\'eor\`eme~1.1.2}, it follows that  $L(f,\psi) \iso \cs{L}_0$ in $\Loc(G)$.
-  It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\cs{L}_0,\mu_0)$ in $\CSb(G)$.
-  This completes the proof that $L_G : \CSf(G) \to \CS(G)$ is essentially surjective.
+  It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\cs{L}_0,\mu_0)$ in $\GCb(G)$.
+  This completes the proof that $L_G : \GCf(G) \to \GC(G)$ is essentially surjective.
   Since we have already seen (in Section~\ref{sec:finite}) that $L_G$ is full and faithful, 
@@
   \[
-  \trFrob{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)
+  \trFrob{G} : \GCiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)
   \]
   is surjective because, as we have seen, 
-  each character $\chi \in \Hom_\text{grp}(G(\Fq),\EEx)$ determines a finite character sheaf $(\Lang,\chi)$
-  such that the trace of Frobenius of the character sheaf $B_G^* (L_G(\Lang,\chi))$ is $\chi$.
+  each character $\chi \in \Hom_\text{grp}(G(\Fq),\EEx)$ determines a finite geometrized character $(\Lang,\chi)$
+  such that the trace of Frobenius of the geometrized character $B_G^* (L_G(\Lang,\chi))$ is $\chi$.
 \end{proof}
 
-\section{Character sheaves on commutative etale group schemes}
+\section{Geometrized characters on commutative etale group schemes}
 
@@
   \[
-  \CSiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, \Hom_\text{grp}(G(\bFq),\EEx)),
+  \GCiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, \Hom_\text{grp}(G(\bFq),\EEx)),
   \qquad \text{given by}\qquad
@@
   the discrete topology on the group), given by $G \mapsto G(\bFq)$.
-  Under this equivalence any character sheaf $\cs{L}=(\gcs{L},\mu,\phi)$
+  Under this equivalence any geometrized character $\cs{L}=(\gcs{L},\mu,\phi)$
   on $G$ corresponds to:
@@
   Under this equivalence, a map $\varphi : \cs{L} \to \cs{L'}$ of
-  character sheaves on $G$ corresponds to:
+  geometrized characters on $G$ corresponds to:
   \begin{enumerate}
@@
   \ref{cs.1}, \ref{cs.2} and \ref{cs.3}, denoted by
-  \cdef{$\CS(G(\bFq))$}, is equivalent to $\CS(G)$. We will prove the
+  \cdef{$\GC(G(\bFq))$}, is equivalent to $\GC(G)$. We will prove the
   proposition by exhibiting an isomorphism between
-  $\CSiso{G(\bFq)}$ and $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
-
-  To produce the isomorphism between $\CSiso{G(\bFq)}$ and
+  $\GCiso{G(\bFq)}$ and $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
+
+  To produce the isomorphism between $\GCiso{G(\bFq)}$ and
   $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ we must pick a global section of the line
-  bundle $(\gcs{L},\mu)$, for each character sheaf $\cs{L}$ on $G$; 
+  bundle $(\gcs{L},\mu)$, for each geometrized character $\cs{L}$ on $G$; 
   such a section exists by Lemma~\ref{lemma:section}.
@@
   % \Clifton{The alternative to this approach is to change the
-  %   definition of character sheaves to incorporate the notion of
+  %   definition of geometrized characters to incorporate the notion of
   %   Galois sheaves. That might not be so bad, but would add another
@@
   \[
-  \obj \CS(G(\bFq)) \longrightarrow Z^1(\Weil{\Fq},G(\bFq)^*),
+  \obj \GC(G(\bFq)) \longrightarrow Z^1(\Weil{\Fq},G(\bFq)^*),
   \qquad \text{defined by} \qquad \cs{L} \mapsto \tau_\cs{L}.
@@
   \begin{equation}\label{cohomologous}
-    \obj \CS(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
+    \obj \GC(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
     \qquad \text{defined by} \qquad \cs{L} \mapsto [\tau_\cs{L}],
@@
 
-  We now show that the function $\obj \CS(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*)$
-  factors through $\obj \CS(G(\bFq)) \to \CSiso{G(\bFq)}$.
+  We now show that the function $\obj \GC(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*)$
+  factors through $\obj \GC(G(\bFq)) \to \GCiso{G(\bFq)}$.
   To see this, let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and
@@
   \begin{equation}\label{pich1}
-    \CSiso{G(\bFq} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
+    \GCiso{G(\bFq} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
     \qquad \text{defined by} \qquad [\cs{L}] \mapsto [\tau_\cs{L}].
@@
 \begin{lemma}\label{lemma:section}
- If $\cs{L}$ is a character sheaf then there is a non-trivial section of $\gcs{L}$ 
+ If $\cs{L}$ is a geometrized character then there is a non-trivial section of $\gcs{L}$ 
  compatible with $\mu$ in the sense that 
@@
 
-Although this section does not mention character sheaves, 
-we will need Proposition~\ref{prop:X} to prove our main result on character sheaves, 
+Although this section does not mention geometrized characters, 
+we will need Proposition~\ref{prop:X} to prove our main result on geometrized characters, 
 Theorem~\ref{thm:snake}.
@@
 
-\David{This section needs to be modified once the bounded character sheaves section is done}
+\David{This section needs to be modified once the bounded geometrized characters section is done}
 Let $G^0$ be the connected component of $G$ containing the identity.
@@
 $G^0\hookrightarrow G$ determines a monoidal functor
-$\cs{L}\mapsto \cs{L}\vert_{G^0}$ from $\CS(G)$ to $\CS(G^0)$.  In
+$\cs{L}\mapsto \cs{L}\vert_{G^0}$ from $\GC(G)$ to $\GC(G^0)$.  In
 this section we show that this functor is essentially surjective. To
 do this we employ a perspective on characters sheaves which is
-different from that in Section~\ref{section:category} but which works
+different from that in Section~\ref{sec:category} but which works
 very well for geometrically connected abelian algebraic groups; this
 perspective fails to extend properly to the more general context of
-Section~\ref{section:category}.
+Section~\ref{sec:category}.
 
 \begin{proposition}\label{prop:restriction}
-  The restriction functor $\CS(G)\to \CS(G^0)$ is essentially surjective.
+  The restriction functor $\GC(G)\to \GC(G^0)$ is essentially surjective.
 \end{proposition}
@@
   \cite{vdG&M}*{3.17}. By Proposition~\ref{prop:connected}, every
-  character sheaf $\cs{E} = (\gcs{E},\mu^0,\phi^0)$ on $G^0$ descends to
+  geometrized character $\cs{E} = (\gcs{E},\mu^0,\phi^0)$ on $G^0$ descends to
   a line bundle on $G^0$.
 
-  Let us review how line bundles on $G^0$ determine character sheaves
+  Let us review how line bundles on $G^0$ determine geometrized characters
   on $G^0$.  Up to isomorphism, line bundles on $G^0$ may be
   apprehended in terms of pairs $(\pi,\psi)$,
-  \David{Aren't there line bundles which are not character sheaves,
+  \David{Aren't there line bundles which are not geometrized characters,
     for which $B$ is not an algebraic group?}
@@
   satisfying conditions \ref{CS.1} and \ref{CS.2}. Then $(\gcs{E},\mu^0,\phi^0)$
-  is a character sheaf of $G^0$.
+  is a geometrized character of $G^0$.
 
@@
   Now we show that $f : H\to G$, as above, together with a character
-  $\psi : \ker \bf \to \EEx$, defines a character sheaf on
-  $G$. We will also show that the restriction of this character sheaf
-  on $G$ to $G^0$ is precisely the character sheaf on $G^0$ defined by
+  $\psi : \ker \bf \to \EEx$, defines a geometrized character on
+  $G$. We will also show that the restriction of this geometrized character
+  on $G$ to $G^0$ is precisely the geometrized character on $G^0$ defined by
   the pair $(f^0,\psi)$ as above.
@@
 \end{proof}
-\Clifton{I can flesh out this remark once I've promoted the definition of $\CSb(G)$ (category of bounded character sheaves on $G$).}
+\Clifton{I can flesh out this remark once I've promoted the definition of $\GCb(G)$ (category of bounded geometrized characters on $G$).}
 \begin{remark}
@@
   fixed by Frobenius, then every character of $\ker f$ determines a
-  character sheaf on $G$. However, it is not true that every character
+  geometrized character on $G$. However, it is not true that every character
   sheaf on $G$ arises in this manner.
@@
 
-\section{Main result regarding character sheaves}
+\section{Main result regarding geometrized characters}
 
@@
   \[
-  \trFrob{G} : \CSiso{G} \to \Hom(G(\Fq),\EEx),
-  \]
-  from the Picard group of the category of character sheaves on $G$ to
+  \trFrob{G} : \GCiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx),
+  \]
+  from the Picard group of the category of geometrized characters on $G$ to
   the group of characters of $G(\Fq)$, is an isomorphism.
@@
     {}& \ker t_{\pi_0(G)} \dar & \arrow[dashed]{d} \ker \trFrob{G} & \ker t_{G^0} \dar & \\
-    0 \rar & \CSiso{\pi_0(G)} \rar \dar{t_{\pi_0(G)}}
-    & \CSiso{G} \rar \dar{\trFrob{G}} & \CSiso{G^0} \rar \dar{t_{G^0}} & 0\\
+    0 \rar & \GCiso{\pi_0(G)} \rar \dar{t_{\pi_0(G)}}
+    & \GCiso{G} \rar \dar{\trFrob{G}} & \GCiso{G^0} \rar \dar{t_{G^0}} & 0\\
     0 \rar & \Hom(\pi_0(G)(\Fq),\EEx) \rar \dar
@@
   The sequence of Picard groups is right-exact: it is exact at
-  $\CSiso{G^0}$ by Proposition~\ref{prop:restriction}; and
-  it is exact at $\CSiso{G}$ because the left-square
+  $\GCiso{G^0}$ by Proposition~\ref{prop:restriction}; and
+  it is exact at $\GCiso{G}$ because the left-square
   commutes (by Proposition~\ref{prop:pullback}), the bottom sequence
@@
   \[
-  \image(\CSiso{\pi_0(G)} \to \CSiso{G}) \subseteq \ker(\CSiso{G} \to \CSiso{G^0}),
+  \image(\GCiso{\pi_0(G)} \to \GCiso{G}) \subseteq \ker(\GCiso{G} \to \GCiso{G^0}),
   \]
   by the last part of Proposition~\ref{prop:pullback}. Specifically,
-  suppose $\cs{L}$ is a character sheaf on $G$ that is trivial on
+  suppose $\cs{L}$ is a geometrized character on $G$ that is trivial on
   $G^0$. Then $\trFrob{\cs{L}}\vert_{G^0(\Fq)} = \trFrob{\cs{L}^0} =0$,
@@
   $\trFrob{\cs{L}}$. By Propositions~\ref{prop:etale} and \ref{prop:X},
-  there is a a character sheaf $\cs{L}_\chi$ on $\pi_0(G)$, unique up
+  there is a a geometrized character $\cs{L}_\chi$ on $\pi_0(G)$, unique up
   to isomorphism, such that $\trFrob{\cs{L}_\chi} = \chi$. By
   Proposition~\ref{prop:pullback} again, $\cs{L}$ is isomorphic to the
-  image of $\cs{L}_\chi$ under the monoidal functor $\CS(\pi_0(G)) \to \CS(G)$.
+  image of $\cs{L}_\chi$ under the monoidal functor $\GC(\pi_0(G)) \to \GC(G)$.
 
@@
   Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d \in \ZZ_{>0}$, the
-  Picard group of the category of character sheaves on $\GN{T}_d$ is
+  Picard group of the category of geometrized characters on $\GN{T}_d$ is
   canonically isomorphic to the group of characters of $T(K)$ of depth
@@
   \[
-  \CSiso{\GN{T}_d} \iso \Hom_{< d}(T(K),\EEx).
+  \GCiso{\GN{T}_d} \iso \Hom_{< d}(T(K),\EEx).
   \]
@@
   \[
-  \CSiso{\GN{T}_d} \iso \Hom(\GN{T}_d(\Fq),\EEx).
+  \GCiso{\GN{T}_d} \iso \Hom(\GN{T}_d(\Fq),\EEx).
   \]
@@
 
-\Clifton{Must still define $\CS(\GN{T})$, since it is not an instance
+\Clifton{Must still define $\GC(\GN{T})$, since it is not an instance
  of our definitions, above.}
@@
   \[
-  \CSiso{\GN{T}} \iso \Hom_\text{ad}(T(K),\EEx)
+  \GCiso{\GN{T}} \iso \Hom_\text{ad}(T(K),\EEx)
   \]
@@
  \[
-  \CS(\GN{T}_{N-3h}) \to \CS(\GN{T}'_{N-3h})
+  \GC(\GN{T}_{N-3h}) \to \GC(\GN{T}'_{N-3h})
  \]

### 2013-08-10 shanghai.tex
Moved the definition of \CS(G(\bFq)) out of the proof of Proposition 10.1

--- 2013-08-10 shanghai.tex
@@
 
-\section{The category of character sheaves}\label{section:category}
+\section{Notation}
 
@@
 $\Frob{\Spec{\bFq}} = \Spec{\Frob{\Fq}}$ and $\Frob{\Fq}$  is the geometric Frobenius element in $\Gal(\bFq/\Fq)$.
+
+For any group $A$, we will denote by $A^*$ the dual group $\Hom_\text{grp}(A, \EEx)$.
+
+\section{The category of character sheaves}\label{section:category}
 
@@
 The rule $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$ defines a forgetful functor from character sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{Deligne:Weil2}*{Def.~1.1.10 (i)}.
+
 As remarked after \cite{Deligne:Weil2}*{Def.~1.1.10}, a $\ell$-adic Weil sheaf $(\gcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
@@
 The commutativity of the diagram (CS.2) for $\phi_{k'}$ follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
+\Clifton{I'll fix this section and link.}
 Note that we may also think about the construction of $\phi_{k'}$ as taking the action of $\Weil{k}$ defined in Remark
@@
 
-\section{Character sheaves on commutative etale group schemes}
+\section{Character sheaves on commutative \'etale group schemes}
 
@@
 
-\begin{proposition}\label{prop:etale}
-  If $G$ is a commutative \'etale group scheme over $\Fq$ and
-  $G(\bFq)$ is finitely generated then there is a canonical
-  isomorphism
-  \[
-  \CSiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, \Hom_\text{grp}(G(\bFq),\EEx)),
-  \qquad \text{given by}\qquad
-  [\cs{L}] \mapsto [\tau_\cs{L}],
-  \]
-  where $\tau_\cs{L}: \Weil{\Fq}\to \Hom_\text{grp}(G(\bFq),\EEx)$ is a cocycle such that
-  \[
-  \forall g\in G(\Fq), \qquad \tau_\cs{L}(\Frob{\Fq})(g) = \trFrob{\cs{L}}(g).
-  \]
-\end{proposition}
-
-\begin{proof}
-  To simplify notation, we set
-  $G(\bFq)^* \ceq \Hom_\text{grp}(G(\bFq),\EEx)$.  Recall the
-  equivalence between etale group schemes over $\Fq$ and the category
-  of groups equipped with a continuous action of $\Gal(\bFq/\Fq)$ (for
-  the discrete topology on the group), given by $G \mapsto G(\bFq)$.
-  Under this equivalence any character sheaf $\cs{L}=(\gcs{L},\mu,\phi)$
-  on $G$ corresponds to:
+\'Etale group schemes form a counterpoint to connected groups, since the component group
+is always \'etale.  The functor $G \mapsto G(\bFq)$ defines an equivalence of categories
+between the category of \'etale group schemes over $\Fq$ and the category of groups equipped
+with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group.
+
+For such a $\Gal(\bFq/\Fq)$-group $G(\bFq)$, we define a category of character sheaves $\CS(G(\bFq))$.
+An object in $\CS(G(\bFq))$ is given by the data of
+
 \begin{enumerate}
  \labitem{(cs.0)}{cs.0} an indexed set of one-dimensional
-    $\EE$-vector spaces $\gcs{L}_x \ceq x^*\gcs{L}$, as $x$ runs over
+  $\EE$-vector spaces $\gcs{L}_x$, as $x$ runs over
   $G(\bFq)$;
@@
  \labitem{(cs.1)}{cs.1} an indexed set of isomorphisms
-    $\mu_{x,y} \ceq (x \times y)^*\mu : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes \gcs{L}_{y}$,
+  $\mu_{x,y} : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes \gcs{L}_{y}$,
   for all $x,y \in G(\bFq)$, such that
@@
 
-  \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} \ceq x^*\phi: \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
+ \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
   such that
@@
 \end{enumerate}
-  Under this equivalence, a map $\varphi : \cs{L} \to \cs{L'}$ of
-  character sheaves on $G$ corresponds to:
+
+A morphism $\varphi : \cs{L} \to \cs{L'}$ is given by 
 \begin{enumerate}
-  \labitem{(cs.3)}{cs.3} an indexed set $\varphi_x \ceq x^*\varphi: \gcs{L}_x \to \gcs{L'}_x$
+ \labitem{(cs.3)}{cs.3} an indexed set $\varphi_x : \gcs{L}_x \to \gcs{L'}_x$
   of linear transformations (of one-dimensional $\EE$-vector spaces),
@@
 \end{enumerate}
-  It is clear that the category defined by conditions \ref{cs.0},
-  \ref{cs.1}, \ref{cs.2} and \ref{cs.3}, denoted by
-  \cdef{$\CS(G(\bFq))$}, is equivalent to $\CS(G)$. We will prove the
-  proposition by exhibiting an isomorphism between
-  $\CSiso{G(\bFq)}$ and $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
-
+
+The functor $\CS(G) \to \CS(G(\bFq))$ defined by $(\gcs{L}, \mu, \phi) \mapsto (\gcs{L}_x = x^*\gcs{L}, \mu_{x,y} = (x \times y)^* \mu, x^*\phi)$ is easily seen to be an equivalence.
+We will use this equivalence implicitly in proving the following proposition.
+
+\begin{proposition}\label{prop:etale}
+  If $G$ is a commutative \'etale group scheme over $\Fq$ and
+  $G(\bFq)$ is finitely generated then there is a canonical
+  isomorphism
+  \[
+  \CSiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, G(\bFq)^*),
+  \qquad \text{given by}\qquad
+  [\cs{L}] \mapsto [\tau_\cs{L}],
+  \]
+  where $\tau_\cs{L}: \Weil{\Fq}\to \Hom_\text{grp}(G(\bFq),\EEx)$ is a cocycle such that
+  \[
+  \forall g\in G(\Fq), \qquad \tau_\cs{L}(\Frob{\Fq})(g) = \trFrob{\cs{L}}(g).
+  \]
+\end{proposition}
+
+\begin{proof}
   To produce the isomorphism between $\CSiso{G(\bFq)}$ and
@@
   Conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
-  the scalar $z_\cs{L}(\Frob)(x)$ is non-zero, while condition~\ref{cs.1} forces
+  the scalar $z_\cs{L}(\Frob{k})(x)$ is non-zero, while condition~\ref{cs.1} forces
   $\tau_\cs{L}(\Frob{\Fq})(x+y) = \tau_\cs{L}(\Frob{\Fq})(x) \ \tau_\cs{L}(\Frob{\Fq})(y)$,

### 2013-08-11 shanghai.tex
Finished proof of Lemma 10.1, removed some references to line bundles

@@
 
-The functor $\CS(G) \to \CS(G(\bFq))$ defined by $(\gcs{L}, \mu, \phi) \mapsto (\gcs{L}_x = x^*\gcs{L}, \mu_{x,y} = (x \times y)^* \mu, x^*\phi)$ is easily seen to be an equivalence.
+The functor $\CS(G) \to \CS(G(\bFq))$ defined by
+$(\gcs{L}, \mu, \phi) \mapsto (\gcs{L}_x = x^*\gcs{L}, \mu_{x,y} = (x \times y)^* \mu, x^*\phi)$
+is easily seen to be an equivalence.  We may now define a \cdef{global section}
+of a character sheaf $\cs{L}$ on an \'etale group scheme $G$ as a choice $s(x) \in \gcs{L}_x$ for every
+$x \in G(\bFq)$, satisfying
+ \begin{equation}\label{section}
+  \forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes s(y).
+ \end{equation}
+
+\begin{lemma}\label{lemma:section}
+ If $\cs{L}$ is a character sheaf on a commutative, \'etale group scheme $G$
+ with $G(\bFq)$ finitely generated then nontrivial global sections exist.
+\end{lemma}
+
+\begin{proof}
+  Since $G(\bFq)$ is a finitely-generated abelian group, it admits a decomposition
+  \[
+  G(\bFq) \iso \ZZ^r \oplus \bigoplus_{j=1}^t \ZZ / m_j \ZZ;
+  \]
+  let $x_1, \ldots, x_r, y_1, \ldots, y_t$ be a corresponding set of generators of $G(\bFq)$.
+  We will define a section $s$ by choosing values on these generators and extending to all
+  of $G(\bFq)$ through \eqref{section}.
+
+  There is a unique isomorphism $\gcs{L}_0 \cong \EE$ under which $\mu_{0,0}$ corresponds
+  to the multiplication map $\EE \otimes \EE \to \EE$.
+  The condition $\mu_{0,0}(s(0)) = s(0) \otimes s(0)$ together with the non-triviality of $s$
+  then forces $s(0) = 1$.
+
+  The $\mu_{x,y}$ yield an isomorphism $\alpha_j : \gcs{L}_{y_j}^{\otimes m_j} \to \gcs{L}_0$.
+  An initial nonzero choice of $s(y_j)$ need only be scaled by $\alpha_j(s(y_j))^{-1/m_j}$ in order to map to
+  $1$ under this isomorphism.  Since compatibility under the $\alpha_j$ are the only constraints on the
+  $s(x_j)$ and $s(y_j)$, global sections exist.
+\end{proof}
+
 We will use this equivalence implicitly in proving the following proposition.
@@
   \]
-  where $\tau_\cs{L}: \Weil{\Fq}\to \Hom_\text{grp}(G(\bFq),\EEx)$ is a cocycle such that
+  where $\tau_\cs{L}: \Weil{\Fq}\to G(\bFq)^*$ is a cocycle such that
   \[
@@
   To produce the isomorphism between $\CSiso{G(\bFq)}$ and
-  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ we must pick a global section of the line
-  bundle $(\gcs{L},\mu)$, for each character sheaf $\cs{L}$ on $G$; 
+  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ we must pick a global section of $\cs{L}$, for each character sheaf $\cs{L}$ on $G$; 
   such a section exists by Lemma~\ref{lemma:section}.
@@
   choice. To see why, let $s_1$ and $s_2$ be two global sections of
-  the line bundle $(\gcs{L},\mu)$, in the sense above and let $\tau_1$
+ $\cs{L}$ and let $\tau_1$
   and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$, respectively,
@@
   \Clifton{Straightforward, yes, but it still needs to be written down here.}
-\end{proof}
-
-\begin{lemma}\label{lemma:section}
- If $\cs{L}$ is a character sheaf then there is a non-trivial section of $\gcs{L}$ 
- compatible with $\mu$ in the sense that 
- \begin{equation}\label{section}
-  \forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes s(y).
- \end{equation}
-\end{lemma}
-
-\begin{proof}
-First, however, we show that such global sections exist.  Since
-  $G(\bFq)$ is finitely-generated abelian, it admits a decomposition
-  $G(\bFq) \iso G(\bFq)_\text{free} \oplus G(\bFq)_\text{tors}$ such
-  that $G(\bFq)_\text{tors}$ is finite.  Let $x_1, \ldots , x_r$ be a
-  basis for the free part $G(\bFq)_\text{free}$ of $G(\bFq)$ and let
-  $y_1, \ldots , y_t$ be a generators for the torsion part of
-  $G(\bFq)$ corresponding to the decomposition
-  $G(\bFq)_\text{tors} \iso \oplus_{j=1}^t \ZZ/m_j\ZZ$, with
-  $m_j \vert m_{j+1}$. For each such $x_i$ pick $s(x_i)\in \gcs{L}_{x_i}$;
-  for each such $y_j$ pick $s(y_j) \in \gcs{L}_{y_j}$; also set
-  $s({\bar e}) \ceq 0 \in \gcs{L}_{\bar e}$. ....
-  \todo{under construction}
-  In this way we define a section
-  $s \ceq s_\cs{L} : G(\bFq) \to \coprod_{z\in G(\bFq)} \gcs{L}_z$ of
-  projection $\coprod_{z\in G(\bFq)} \gcs{L}_z \to G(\bFq)$ such that
-  $\mu_{x,y}(s(x+y)) = s(x)\otimes s(y)$ for all $x,y \in G(\bFq)$.
-  Under the equivalence at the beginning of this section, $s = s_\cs{L}$
-  corresponds to a global section of the line bundle $(\gcs{L},\mu)$.
-
-\Clifton{I'm going to remove all mention of line bundles from this paper.}
 \end{proof}

### 2013-08-11 shanghai.tex
Finished working on section 10, but still left the proof of isomorphism

@@
  If $\cs{L}$ is a character sheaf on a commutative, \'etale group scheme $G$
- with $G(\bFq)$ finitely generated then nontrivial global sections exist.
+ with $G(\bFq)$ finitely generated then nontrivial global sections of $\cs{L}$ exist.
 \end{lemma}
@@
 
-We will use this equivalence implicitly in proving the following proposition.
+These global sections will allow us to construct the isomorphism in the following proposition.
 
@@
   \[
-  \forall g\in G(\Fq), \qquad \tau_\cs{L}(\Frob{\Fq})(g) = \trFrob{\cs{L}}(g).
+  \forall x\in G(\Fq), \qquad \tau_\cs{L}(\Frob{\Fq})(x) = \trFrob{\cs{L}}(x).
   \]
@@
 \begin{proof}
-  To produce the isomorphism between $\CSiso{G(\bFq)}$ and
-  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ we must pick a global section of $\cs{L}$, for each character sheaf $\cs{L}$ on $G$; 
-  such a section exists by Lemma~\ref{lemma:section}.
-  We will show that the group isomorphism does not depend on these
-  choices.
-%
-  We use the section $s_\cs{L}$ to define a cocycle $z_\cs{L} \in Z^1(\Weil{\Fq},G(\bFq)^*)$
-  as follows. Recall that $\cs{L}$ also determines a family of linear transformations
-  $\phi_x : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$ of one-dimensional $\EE$-vector
-  spaces, so $\phi_x(s(\Frob{\Fq}(x)))$ is a scalar multiply of $s(x)$, for
-  each $x\in G(\bFq)$; let $\tau_\cs{L}(\Frob{\Fq})(x)$ be that scalar, so
+  Suppose $\cs{L}$ is a character sheaf on $G$.  Using Lemma~\ref{lemma:section}, we may choose a global section $s_{\cs{L}}$
+  of $\cs{L}$.  We will construct a group isomorphism between $\CSiso{G(\bFq)}$ and
+  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ using $s_{\cs{L}}$, then prove independence from the choice of section.
+
+  Starting from $\cs{L}$, we define a cocyle $\tau_{\cs{L}} \in Z^1(\Weil{\Fq},G(\bFq)^*)$ as follows.
+  For $x \in G(\bFq)$, $\cs{L}$ determines an isomorphism $\phi_x : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
+  of one-dimensional $\EE$-vector spaces; set
   \begin{equation}\label{t}
-    \forall x\in G(\bFq),\qquad \phi_{x}(s(\Frob{\Fq}(x)) = \tau_\cs{L}(\Frob{\Fq})(x) s(x).
+   \phi_{x}(s(\Frob{\Fq}(x))) = \tau_\cs{L}(\Frob{\Fq})(x) s(x).
   \end{equation}
-  Conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
-  the scalar $z_\cs{L}(\Frob{k})(x)$ is non-zero, while condition~\ref{cs.1} forces
-  $\tau_\cs{L}(\Frob{\Fq})(x+y) = \tau_\cs{L}(\Frob{\Fq})(x) \ \tau_\cs{L}(\Frob{\Fq})(y)$,
-  for all $x,y \in G(\bFq)$.
-  % \Clifton{The alternative to this approach is to change the
-  %   definition of character sheaves to incorporate the notion of
-  %   Galois sheaves. That might not be so bad, but would add another
-  %   layer of complication, which we wouldn't use profitably, expect
-  %   here.}
-
-  Now $\tau_\cs{L} : \Weil{\Fq} \to G(\bFq)^*$ is defined, recursively, by
-  $\tau_\cs{L}(\Frob{\Fq}^n) \ceq \tau_\cs{L}(\Frob{\Fq})\cdot \,^\Frob{\Fq} \tau_\cs{L}(\Frob{\Fq}^{n-1})$,
+  Note that if $x$ is fixed by $\Frob{k}$ then $\tau_\cs{L}(\Frob{\Fq})(x)$ is just $t_\cs{L}(x)$, so the restriction of
+  $\tau_\cs{L}(\Frob{k})$ to $G(k)$ is just $t_\cs{L}$.
+  In general, conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
+  the scalar $\tau_\cs{L}(\Frob{k})(x)$ is non-zero.  Moreover, condition~\ref{cs.1} forces
+  $\tau_\cs{L}(\Frob{\Fq})(x+y) = \tau_\cs{L}(\Frob{\Fq})(x) \ \tau_\cs{L}(\Frob{\Fq})(y)$
+  for all $x,y \in G(\bFq)$.  Now define $\tau_\cs{L} : \Weil{\Fq} \to G(\bFq)^*$ recursively by
+  \[
+   \tau_\cs{L}(\Frob{\Fq}^n) \ceq \tau_\cs{L}(\Frob{\Fq})\cdot \,^\Frob{\Fq} \tau_\cs{L}(\Frob{\Fq}^{n-1}),
+  \]
   where $\Frob{\Fq}$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers
-  to pointwise multiplication of functions. This gives
-  \[
-  \obj \CS(G(\bFq)) \longrightarrow Z^1(\Weil{\Fq},G(\bFq)^*),
-  \qquad \text{defined by} \qquad \cs{L} \mapsto \tau_\cs{L}.
-  \]
+  to pointwise multiplication of functions.
 
@@
   choice. To see why, let $s_1$ and $s_2$ be two global sections of
- $\cs{L}$ and let $\tau_1$
-  and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$, respectively,
-  as above. Since, for each $x\in G(\bFq)$, $\gcs{L}_x$ is a
-  one-dimensional $\EE$-vector space, there is a unique scalar
-  $a(x) \in \EE$ such that $s_2(x) = a(x) s_1(x)$; moreover, $a(x)$ is
-  non-zero, since $s_2(x)$ is non-zero. Then \eqref{section} and
+  $\cs{L}$ and let $\tau_1$ and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$.
+  For each $x \in G(\bFq)$ there is a unique scalar
+  $a(x) \in \EEx$ such that $s_2(x) = a(x) s_1(x)$. Then \eqref{section} and
   condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so
-  $a\in G(\bFq)^*$. Now consider the coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
-  defined by $\tau_0(\Frob{\Fq}) = \,^\Frob{\Fq} a \cdot a^{-1}$. Then $\tau_2 = \tau_0 \tau_1$,
-  so $\tau_2$ and $\tau_1$ are cohomologous. In this way we see that
+  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
+  defined by $\tau_0(\Frob{\Fq}) = \,^\Frob{\Fq} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
+  so $\tau_2$ and $\tau_1$ are cohomologous. Thus
   \begin{equation}\label{cohomologous}
@@
 
-  We now show that the function $\obj \CS(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*)$
-  factors through $\obj \CS(G(\bFq)) \to \CSiso{G(\bFq)}$.
-  To see this, let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and
+  We now show that $[\tau_\cs{L}]$ depends only on the isomorphism class of $\cs{L}$.
+  Let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and
   let $\tau$ and $\tau'$ be any cocycles representing the classes in the
@@
   $\tau$ and $\tau'$ are defined by sections $s$ and $s'$. Now, $\varphi_x(s(x))$ is a
-  non-zero scalar multiple of $s'(x)$; define $\phi: G(\bFq) \to \EEx$
-  by $\varphi_x(s(x)) = \phi(x) s'(x)$. 
-  \Clifton{Notation problem here: replace $\phi$ with something else.}
+  non-zero scalar multiple of $s'(x)$; define $\delta: G(\bFq) \to \EEx$
+  by $\varphi_x(s(x)) = \delta(x) s'(x)$.
   By the second part of condition~\ref{cs.3},
-  $\phi(x+y) = \phi(x)\phi(y)$, so $\phi \in G(\bFq)^*$. By the first part of
-  condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}\phi \cdot \phi^{-1})$,
+  $\delta(x+y) = \delta(x)\delta(y)$, so $\delta \in G(\bFq)^*$. By the first part of
+  condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}\delta \cdot \delta^{-1})$,
   so $\tau$ and $\tau'$ are cohomologous. This concludes the definition of
   \begin{equation}\label{pich1}
-    \CSiso{G(\bFq} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
-    \qquad \text{defined by} \qquad [\cs{L}] \mapsto [\tau_\cs{L}].
+    \CSiso{G(\bFq} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*).
   \end{equation}
-  Now it follows from \eqref{t} that the image of the isomorphism
-  class of $\cs{L}$ is indeed represented by a cocycle $\tau_\cs{L}$ such
-  that $\tau_\cs{L}(\Frob{\Fq}) = \trFrob{\cs{L}}$ on $G(\Fq)$, which is to
-  say, when evaluated at $\Frob{\Fq}$, the cocycle $\tau_\cs{L}$ is an
-  extension of the trace of Frobenius of $\cs{L}$.
 
   It only remains to show that \eqref{pich1} is a group
-  isomorphism. This is straightforward.
+  isomorphism.  Suppose that $\cs{L}$ and $\cs{L}'$ are two character sheaves.  
   \Clifton{Straightforward, yes, but it still needs to be written down here.}

### 2013-08-11 shanghai.tex
Moving to a different computer ...

--- 2013-08-10 shanghai.tex
@@
 \usepackage{manfnt}
+%\usepackage{makeidx}
 
@@
 \begin{abstract}
-  We study the category of character sheaves on smooth commutative
+  We introduce and study the category of geometrized characters of smooth commutative
   group schemes $G$ locally of finite type over finite fields
@@
   is finitely-generated, we show that the group of isomorphism classes
-  of character sheaves on $G$ is canonically isomorphic to the group
+  of geometrized characters of $G$ is canonically isomorphic to the group
   of characters of $G(\Fq)$. We use this result to exhibit an
   isomorphism between admissible characters of $T(K)$ and isomorphism
-  classes of character sheaves on the Greenberg transform of the Néron
+  classes of geometrized characters of the Greenberg transform of the Néron
   model of $T$, where $K$ is any non-Archimdean local field and $T$ is
@@
 %\noindent
-In this paper we show that the monidal category of character sheaves
-on the Greenberg transform of the locally finite type Neron model of
-$T$ provides an elegant, canonical model for the group of
-(quasi-)characters of $T(K)$, where $K$ is any non-Archimedean local
-field and $T$ is any algebraic torus over $K$.
-
-Since the character sheaves that appear in this paper are not quite an
-instance of those defined by George Luzstig, who coined the term, we
-begin by explaining what we mean by `character sheaves' here. 
+What is a geometrized character?
 Let $G$ be a smooth commutative group scheme locally of finite
@@
 finite type over $\Fq$. Fix a prime $\ell$ that does not divide
-$q$. By a {character sheaf} on $G$ we mean a triple $\cs{L}\ceq
+$q$. A geometrized character of $G$ is a triple $\cs{L}\ceq
 (\gcs{L},\mu,\phi)$ where $\gcs{L}$ is a constructible $\ell$-adic sheaf
@@
 
-Character sheaves on $G$ form a category, denoted by $\CS(G)$. In
-fact, $\CS(G)$ is a rigid symmetric monoidal category, so isomorphism
-classes of character sheaves on $G$ form a group, denoted by
-$\CSiso{G}$; this is the Picard group of the category of
-character sheaves on $G$. Our application of character sheaves to
+Geometrized characters of $G$ form a category, denoted by $\GC(G)$. In
+fact, $\GC(G)$ is a rigid symmetric monoidal category, so isomorphism
+classes of geometrized characters of $G$ form a group, denoted by
+$\GCiso{G}$; this is the Picard group of the category of
+geometrized characters of $G$. Our application of geometrized characters to
 characters of algebraic tori over non-Archimedean local fields rests
-on finding the Picard group of character sheaves on $G$, for all smooth commutative group schemes $G$, locally of finite type over $\Fq$, for which the geometric component group is finitely generated.
+on finding the Picard group of geometrized characters of $G$, 
+for all smooth commutative group schemes $G$, locally of finite type over $\Fq$, 
+for which the geometric component group is finitely generated.
 
@@
 %be), we arrive at a model for the group of quasi-characters of
-%$K^\times$: the monoidal category of character sheaves on the
+%$K^\times$: the monoidal category of geometrized characters of the
 %Greenberg transform of the Neron model of
@@
 
-Structure of the paper:
-
-Thanks to:
+In this paper we show that the monoidal category of geometrized characters
+on the Greenberg transform of the locally finite type Neron model of
+$T$ provides an elegant, canonical model for the group of
+(quasi-)characters of $T(K)$, where $K$ is any non-Archimedean local
+field and $T$ is any algebraic torus over $K$.
 
@@
 
-\section{Notation}
+\section{The category of geometrized characters}\label{sec:category}
 
@@
 
-For any group $A$, we will denote by $A^*$ the dual group $\Hom_\text{grp}(A, \EEx)$.
-
-\section{The category of character sheaves}\label{section:category}
-
-The category of character sheaves on $G$, denoted by \cdef{$\CS(G)$},
-is defined as follows.  A \cdef{character sheaf} on $G$ is a triple
+The category of geometrized characters of $G$, denoted by \cdef{$\GC(G)$},
+is defined as follows.  A \cdef{geometrized character} on $G$ is a triple
 $\cs{L}\ceq (\gcs{L},\mu,\phi)$ where:
@@
 \end{enumerate}
-Morphisms in $\CS(G)$ are defined in the natural way:
+Morphisms in $\GC(G)$ are defined in the natural way:
 \begin{enumerate}
 \labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,\phi)$ and
-  $\cs{L'} = (\gcs{L'},\mu',\phi')$ are character sheaves on $G$ then
-  $\Hom_{\CS(G)}(\cs{L},\cs{L'})$ is the set of morphisms $\varphi : \gcs{L} \to \gcs{L'}$
+  $\cs{L'} = (\gcs{L'},\mu',\phi')$ are geometrized characters of $G$ then
+  $\Hom_{\GC(G)}(\cs{L},\cs{L'})$ is the set of morphisms $\alpha : \gcs{L} \to \gcs{L'}$
   of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
@@
   \begin{tikzcd}[column sep=40]
-  \Frob{G}^* \gcs{L} \rar{\Frob{G}^* \varphi} \arrow[swap]{d}{F} & \Frob{G}^* \gcs{L'} \dar{F'}
-  & \arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} & \arrow[swap]{d}{\mu} m^* \gcs{L} \rar{m^* \varphi} & m^* \gcs{L'} \dar{\mu'} \\
-  \gcs{L} \rar{\varphi} & \gcs{L'}
-  & {} & \LxL \rar{\tight{1}{\varphi\boxtimes \varphi}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
+  \Frob{G}^* \gcs{L} \rar{\Frob{G}^* \alpha} \arrow[swap]{d}{\phi} & \Frob{G}^* \gcs{L'} \dar{\phi'}
+  & %\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} 
+  & \arrow[swap]{d}{\mu} m^* \gcs{L} \rar{m^* \alpha} & m^* \gcs{L'} \dar{\mu'} \\
+  \gcs{L} \rar{\alpha} & \gcs{L'}
+  & {} & \LxL \rar{\tight{1}{\alpha\boxtimes \alpha}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
   \end{tikzcd}
@@
 %\begin{remark} \label{rem:CS-action}
-The rule $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$ defines a forgetful functor from character sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{Deligne:Weil2}*{Def.~1.1.10 (i)}.
-
-As remarked after \cite{Deligne:Weil2}*{Def.~1.1.10}, a $\ell$-adic Weil sheaf $(\gcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
+The rule $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$ defines a forgetful functor from geometrized characters of $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{Deligne:Weil2}*{Def.~1.1.10 (i)}.
+%
+As remarked after \cite{Deligne:Weil2}*{Def.~1.1.10}, a Weil sheaf $(\gcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
 Since we will need this point of view later, we review that interpretation here.
@@
 \[
-\phi_1(uv) = \phi_1(u) \circ (u_G)_* \phi_1(v), \qquad \forall u,v\in \Weil{\Fq},
-\]
-which means the pair $(\gcs{L},\phi_1)$ is almost an action $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of \cite{SGA4.5}*{Expos\'e XIII,~1.1}.
-The pair $(\gcs{L},\phi_1)$ fails to fulfill the requirements of \cite{SGA4.5}*{Expos\'e XIII,~1.1} only because $\Weil{\Fq}$ is profinite.
-This fact goes to the heart of the notion of a Weil sheaf and is one of the essential aspects of our definition of $\CS(G)$.
+ \forall u,v\in \Weil{\Fq},\qquad \varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v),
+\]
+which means the pair $(\gcs{L},\varphi_1)$ is almost an action $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of \cite{SGA4.5}*{Expos\'e XIII,~1.1}.
+The pair $(\gcs{L},\varphi_1)$ fails to fulfill the requirements of \cite{SGA4.5}*{Expos\'e XIII,~1.1} only because $\Weil{\Fq}$ is profinite.
+This fact goes to the heart of the notion of a Weil sheaf and is one of the essential aspects of our definition of $\GC(G)$.
 %\end{remark}
 
-\section{The Picard group of character sheaves}
+\section{The Picard group of geometrized characters}
 
 %\begin{proposition}\label{tensor}
-The category $\CS(G)$ of character sheaves on $G$ is a rigid monoidal
+The category $\GC(G)$ of geometrized characters of $G$ is a rigid monoidal
 category [insert reference] under
@@
 %
-This rigid monoidal category structure for $\CS(G)$ puts a group
-structure on the set $\CSiso{G}$ of isomorphism classes in
-$\CS(G)$; we refer to this as the \cdef{Picard group of character
+This rigid monoidal category structure for $\GC(G)$ puts a group
+structure on the set $\GCiso{G}$ of isomorphism classes in
+$\GC(G)$; we refer to this as the \cdef{Picard group of character
 sheaves} on $G$.\footnote{See {\tt http://ncatlab.org/nlab/show/Picard+group}.}
-The main result in this paper is the determination of the Picard group of character sheaves on $G$, when the geometric component group of $G$ is finitely generated.
+The main result in this paper is the determination of the Picard group of geometrized characters of $G$, when the geometric component group of $G$ is finitely generated.
 
@@
 
-Let $\cs{L}$ be a character sheaf on $G$. Every $g\in G(\Fq)$
+Let $\cs{L}$ be a geometrized character of $G$. Every $g\in G(\Fq)$
 determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$ and
@@
 (pointwise multiplication of functions) and that $\trFrob{\cs{L}} = \trFrob{\cs{L'}}$
-if $\cs{L} \iso \cs{L'}$ in $\CS(G)$. In this way we obtain a group homomorphism
-\[
-\cdef{\trFrob{G}} : \CSiso{G} \longrightarrow \Hom_\text{grp}(G(\Fq),\EEx),
+if $\cs{L} \iso \cs{L'}$ in $\GC(G)$. In this way we obtain a group homomorphism
+\[
+\cdef{\trFrob{G}} : \GCiso{G} \longrightarrow \Hom_\text{grp}(G(\Fq),\EEx),
 \qquad \text{defined by}\qquad \cs{L} \mapsto \trFrob{\cs{L}},
 \]
-from the Picard group of character sheaves on $G$ to the character group of $G(\Fq)$.
+from the Picard group of geometrized characters of $G$ to the character group of $G(\Fq)$.
 
@@
 \begin{proof}
-  Let $\cs{L}$ be a character sheaf on $G$. We start by showing that
+  Let $\cs{L}$ be a geometrized character of $G$. We start by showing that
   $\bf^*\gcs{L}$ is locally constant on connected components of
@@
 \begin{tikzcd}
-\CSiso{0} \rar & \CSiso{\pi_0(G)} \rar & \CSiso{G} \rar & \CSiso{G^0} \rar & \CSiso{0}.
+\GCiso{0} \rar & \GCiso{\pi_0(G)} \rar & \GCiso{G} \rar & \GCiso{G^0} \rar & \GCiso{0}.
 \end{tikzcd}
 \end{equation}
-It is easy to see that $\CSiso{0}$ is trivial. In this paper we will find $\CSiso{G^0}$ and $\CSiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; 
+It is easy to see that $\GCiso{0}$ is trivial. In this paper we will find $\GCiso{G^0}$ and $\GCiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; 
 the snake lemma will then allow us to show
 \[
-\CSiso{G} \iso \Hom(G(\Fq),\EE^\times),
+\GCiso{G} \iso \Hom_\text{grp}(G(\Fq),\EE^\times),
 \]
@@
 
-When using character sheaves to study characters, it is useful to understand
-how character sheaves behave under change of fields.
-Suppose that $k'$ is a finite extension of $k$ of degree $n$, $G$ is an abelian group scheme
-over $k$ as in Theorem \ref{thm:snake} and $G_{k'}$ is the base change of $G$ to $k'$.
-If $\cs{L} = (\gcs{L}, \mu, \phi)$ is a character sheaf on $G$ we may define
-a character sheaf $\nu(\cs{L}) = (\gcs{L}, \mu, \phi_{k'})$ on $G_{k'}$ by setting
+When using geometrized characters to study characters, it is useful to understand
+how geometrized characters behave under change of fields.
+Suppose that $k'$ is a finite extension of $k$ of degree $n$, 
+$G$ is a commutative smooth group scheme locally of finite type over $k$.
+If $\cs{L} = (\gcs{L}, \mu, \phi)$ is a geometrized character of $G$ we may define
+a geometrized character $\cs{L}' = (\gcs{L}, \mu, \phi_{k'})$ on 
+$G_{k'}\ceq G\times_{\Spec{k}} \Spec{k'}$ by setting
 \[
@@
 \]
-The commutativity of the diagram (CS.2) for $\phi_{k'}$ follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
-\Clifton{I'll fix this section and link.}
-Note that we may also think about the construction of $\phi_{k'}$ as taking the action of $\Weil{k}$ defined in Remark
-\ref{rem:CS-action} and restricting it to $\Weil{k'}$.
+The commutativity of the diagram (CS.2) for $\phi_{k'}$ 
+follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
+Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
+as taking the action $\varphi$ of $\Weil{k}$ on $\gcs{L}$ 
+defined in Section~\ref{sec:category} and restricting it to the subgroup $\Weil{k'}$.
 
 \begin{proposition}\label{prop:basechange}
-The following diagram commutes, where the bottom map is induced by the norm $G(k') \rightarrow G(k)$:
-\[
-\begin{tikzcd}
-\CSiso{G} \rar{\nu} \dar{\trFrob{G}} & \CSiso{G_{k'}} \dar{\trFrob{G_{k'}}} \\
+ The rule $(\gcs{L}, \mu, \varphi) \mapsto (\gcs{L}, \mu, \varphi\vert_{\Weil{\Fq}})$ 
+ defines a monoidal functor $\GC(G) \to \GC(G_{k'})$. 
+ Moreover, the following diagram commutes, 
+ where the top map is induced by $\GC(G) \to \GC(G_{k'})$ 
+ and the bottom map is induced by the norm $G(k') \rightarrow G(k)$:
+\[
+\begin{tikzcd}[column sep=45]
+\GCiso{G} \rar{\text{ext'n of scalars}} \dar{\trFrob{G}} & \GCiso{G_{k'}} \dar{\trFrob{G\times_{\Spec{k}} \Spec{k'}}} \\
 \Hom(G(k), \EEx) \rar{\Nm} & \Hom(G(k'), \EEx).
@@
 \begin{proof}
-\Clifton{This proof is missing! Can David insert it?}
+\Clifton{This proof is missing. Can David insert it?}
 \end{proof}
 
-\section{Bounded character sheaves}\label{sec:bounded}
-
-Let $\CSb(G)$ be the category of pairs $(\cs{L}_0,\mu_0)$ 
+\section{Bounded geometrized characters}\label{sec:bounded}
+
+Let \cdef{$\GCb(G)$} be the category of pairs $(\cs{L}_0,\mu_0)$ 
 where $\cs{L}_0$ is a constructible $\ell$-adic sheaf on $G$, 
@@
  Let $b_G : {\bar G} \to G$ be the pull-back of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Let $(\cs{L}_0,\mu_0)$ be a bounded character sheaf on $G$. 
+ Let $(\cs{L}_0,\mu_0)$ be a bounded geometrized character of $G$. 
  Then $\cs{L}_0$ is, in particular, an $\ell$-adic constructible sheaf on $G$. 
@@
  Moreover, $\phi$ is compatible with $\mu$ in the sense of Condition~\ref{CS.3}.
- It follows that functor $(\cs{L}_0,\mu_0) \mapsto (b_G^*\cs{L}_0,b_{G\times G}^* \mu_0, \phi)$, denoted by  $B_G^*: \CSb(G) \hookrightarrow \CS(G)$ below, is full and faithful.
+ It follows that functor $(\cs{L}_0,\mu_0) \mapsto (b_G^*\cs{L}_0,b_{G\times G}^* \mu_0, \phi)$, denoted by  $B_G^*: \GCb(G) \hookrightarrow \GC(G)$ below, is full and faithful.
 \end{proof}
 
-\section{Finite character sheaves}\label{sec:finite}
-
- %In this section we describe a full subcategory of $\CSb(G)$
- %which will illuminate some features of $\CSb(G)$ and also play a role in some arguments below.
-
-To define the category of finite character sheaves we must work a bit harder.
-Consider the following category $C(G)$:
+We will see that the full subcategory $\GC_0(G)$ of bounded geometrized characters is a proper subcategory, in general.
+Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)$ to the subgroup $\GCbiso{G}$ is an isomorphism onto the subgroup of $\chi \in \Hom_\text{grp}(G(\Fq),\EEx)$ such that the image of $\chi$ is bounded in $\EEx$.
+
+\section{Finite geometrized characters}\label{sec:finite}
+
+ %In this section we describe a full subcategory of $\GCb(G)$
+ %which will illuminate some features of $\GCb(G)$ and also play a role in some arguments below.
+
+To define the category of finite geometrized characters we must work a bit harder.
+Consider the following category \cdef{$C(G)$}:
 an object in $C(G)$ is a pair $(f,\psi)$ where: 
@@
 
-We say that $(\alpha,T)$ in $C(G)$ is a weak isomorphism if $T$ is an isomorphism of vector spaces. 
-Let $C(G)[W^{-1}]$ be the localization of $C(G)$ at weak isomorphisms.
-Now, let $C_1(G)$ be the subcategory of $C(G)$ such that $\psi$ is a one-dimensional representation
-and let $\CSf(G)$ be the localisation of $C_1(G)$ at weak isomorphisms. 
-This is the rigid symmetric monoidal category of \cdef{finite character sheaves} on $G$.
+We say that $(\alpha,T)$ in $C(G)$ is a \cdef{weak isomorphism} if $T$ is an isomorphism of vector spaces. 
+Let \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at weak isomorphisms.
+Now, let \cdef{$C_1(G)$} be the subcategory of $C(G)$ such that $\psi$ is a one-dimensional representation
+and let \cdef{$\GCf(G)$} be the localisation of $C_1(G)$ at weak isomorphisms. 
+This is the rigid symmetric monoidal category of \cdef{finite geometrized characters} of $G$.
 
 \begin{proposition}\label{prop:bounded}
- $\CSf(G)$ is (equivalent to) a full subcategory of $\CSb(G)$.
+ $\GCf(G)$ is (equivalent to) a full subcategory of $\GCb(G)$.
 \end{proposition}
@@
  Then the equivariance condition on $T$ becomes $\psi' = \psi\circ h$ on the finite etale group scheme $\ker f'$. 
- Since $f' = f \circ \alpha$ and $f$ and $f'$ are etale covers, it follows that $\alpha$ is also an etale cover. 
+ Since $f' = f \circ \alpha$ and $f$ and $f'$ are etale covers, 
+ it follows that $\alpha$ is also an etale cover. 
+ \Clifton{Is that right? If $f' = f \circ \alpha$ and $f$ and $f'$ are etale covers, 
+ does it follow that $\alpha$ is also an etale cover? (Etale: Yes. Finite? Surjective?) If not, then I must modify the definition of weak isomorphism accordingly.} 
  It follows that $\alpha : H'\to H$ admits a section $\alpha' : H \to H'$, 
@@
 
- One more ingredient is needed before we can exhibit the full functor $L_G: \CSf(G) \to \CSb(G)$ promised above: 
- we must put rigid monoidal category structures on $\CSf(G)$ and $\CSb(G)$.
-
-  It is also a matter of routine to verify that every morphism of group schemes $G'\to G$ 
-  induces a monoidal functor $C(G) \to C(G')$ by base-change along $G'\to G$ ({\it cf.}, Proposition~\ref{prop:pullback}); 
+  Every morphism of group schemes $G'\to G$ 
+  induces a monoidal functor $C(G) \to C(G')$ by base-change along $G'\to G$ 
+  ({\it cf.}, Proposition~\ref{prop:pullback}) as follows. 
+  Let $m : G'\to G$ be a morphism of group schemes. 
+  Let $(f,\psi)$ be an object in $C(G)$.
+
   indeed, the pull-back of $(f,\psi)$ along any morphism $m : G'\to G$ of group schemes 
   can be read off the short exact sequence obtained by pulling back along $m$.
+
   Taking the case when $m$ is the multiplication morphism $m : G\times G\to G$, 
@@
  let $\mu(f,\psi)$ be that isomorphism of $\ell$-adic sheaves on $G$,
- It follows immediately that the functor $L_G  \ceq  L_{W}\vert_{\CSf(G)} : \CS_b(G) \to \CSb(G)$, 
+ It follows immediately that the functor $L_G  \ceq  L_{W}\vert_{\GCf(G)} : \GCf(G) \to \GCb(G)$, 
  given on objects by $(f,\psi) \mapsto (L(f,\psi), \mu(f,\psi))$,
@@
   Observe that the forgetful functor $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$
-  sends character sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{Deligne:Weil2}*{1.1.10}.
+  sends geometrized characters of $G$ to $\ell$-adic Weil sheaves on $G$ \cite{Deligne:Weil2}*{1.1.10}.
   While is it not true that all Weil sheaves on $G$ descend to local systems on $G$, 
-  we will see that those that appear in the image of this forgetful functor from character sheaves do.
+  we will see that those that appear in the image of this forgetful functor from geometrized characters do.
 
@@
   $\ell$-adic representations of $\W(G,\bg)$ \cite{Deligne:Weil2}*{1.1.12}. 
-  Now let $(\gcs{L},\mu,\phi)$ be a character sheaf on $G$ 
+  Now let $(\gcs{L},\mu,\phi)$ be a geometrized character of $G$ 
   and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gcs{L},\phi)$. 
@@
 
-  Let $(\cs{L}_0,\mu_0)$ be a bounded character sheaf on $G$. 
-  Then $\cs{L}\ceq B_G^*(\cs{L}_0,\mu_0)$ is a character sheaf on $G$.
+  Let $(\cs{L}_0,\mu_0)$ be a bounded geometrized character of $G$. 
+  Then $\cs{L}\ceq B_G^*(\cs{L}_0,\mu_0)$ is a geometrized character of $G$.
   Recall the definition of the character $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}. 
@@
   \[
-  \trFrob{G} : \CSiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)
+  \trFrob{G} : \GCiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)
   \]
   is surjective because, as we have seen, 
-  each character $\chi \in \Hom_\text{grp}(G(\Fq),\EEx)$ determines a finite character sheaf $(\Lang,\chi)$
-  such that the trace of Frobenius of the character sheaf $B_G^* (L_G(\Lang,\chi))$ is $\chi$.
+  each character $\chi \in \Hom_\text{grp}(G(\Fq),\EEx)$ determines a finite geometrized character $(\Lang,\chi)$
+  such that the trace of Frobenius of the geometrized character $B_G^* (L_G(\Lang,\chi))$ is $\chi$.
 \end{proof}
 
-\section{Character sheaves on commutative \'etale group schemes}
+\section{Geometrized characters of commutative etale group schemes}
 
@@
 
-\'Etale group schemes form a counterpoint to connected groups, since the component group
-is always \'etale.  The functor $G \mapsto G(\bFq)$ defines an equivalence of categories
-between the category of \'etale group schemes over $\Fq$ and the category of groups equipped
-with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group.
-
-For such a $\Gal(\bFq/\Fq)$-group $G(\bFq)$, we define a category of character sheaves $\CS(G(\bFq))$.
-An object in $\CS(G(\bFq))$ is given by the data of
-
+\begin{proposition}\label{prop:etale}
+  If $G$ is a commutative \'etale group scheme over $\Fq$ and
+  $G(\bFq)$ is finitely generated then there is a canonical
+  isomorphism
+  \[
+  \GCiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, \Hom_\text{grp}(G(\bFq),\EEx)),
+  \qquad \text{given by}\qquad
+  [\cs{L}] \mapsto [\tau_\cs{L}],
+  \]
+  where $\tau_\cs{L}: \Weil{\Fq}\to \Hom_\text{grp}(G(\bFq),\EEx)$ is a cocycle such that
+  \[
+  \forall g\in G(\Fq), \qquad \tau_\cs{L}(\Frob{\Fq})(g) = \trFrob{\cs{L}}(g).
+  \]
+\end{proposition}
+
+\begin{proof}
+  To simplify notation, we set
+  $G(\bFq)^* \ceq \Hom_\text{grp}(G(\bFq),\EEx)$.  Recall the
+  equivalence between etale group schemes over $\Fq$ and the category
+  of groups equipped with a continuous action of $\Gal(\bFq/\Fq)$ (for
+  the discrete topology on the group), given by $G \mapsto G(\bFq)$.
+  Under this equivalence any geometrized character $\cs{L}=(\gcs{L},\mu,\phi)$
+  on $G$ corresponds to:
   \begin{enumerate}
   \labitem{(cs.0)}{cs.0} an indexed set of one-dimensional
-  $\EE$-vector spaces $\gcs{L}_x$, as $x$ runs over
+    $\EE$-vector spaces $\gcs{L}_x \ceq x^*\gcs{L}$, as $x$ runs over
     $G(\bFq)$;
@@
   \labitem{(cs.1)}{cs.1} an indexed set of isomorphisms
-  $\mu_{x,y} : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes \gcs{L}_{y}$,
+    $\mu_{x,y} \ceq (x \times y)^*\mu : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes \gcs{L}_{y}$,
     for all $x,y \in G(\bFq)$, such that
@@
 
- \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
+  \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} \ceq x^*\phi: \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
     such that
@@
   \end{enumerate}
-
-A morphism $\varphi : \cs{L} \to \cs{L'}$ is given by 
+  Under this equivalence, a map $\varphi : \cs{L} \to \cs{L'}$ of
+  geometrized characters of $G$ corresponds to:
   \begin{enumerate}
- \labitem{(cs.3)}{cs.3} an indexed set $\varphi_x : \gcs{L}_x \to \gcs{L'}_x$
+  \labitem{(cs.3)}{cs.3} an indexed set $\varphi_x \ceq x^*\varphi: \gcs{L}_x \to \gcs{L'}_x$
     of linear transformations (of one-dimensional $\EE$-vector spaces),
@@
   \end{enumerate}
-
-The functor $\CS(G) \to \CS(G(\bFq))$ defined by $(\gcs{L}, \mu, \phi) \mapsto (\gcs{L}_x = x^*\gcs{L}, \mu_{x,y} = (x \times y)^* \mu, x^*\phi)$ is easily seen to be an equivalence.
-We will use this equivalence implicitly in proving the following proposition.
-
-\begin{proposition}\label{prop:etale}
-  If $G$ is a commutative \'etale group scheme over $\Fq$ and
-  $G(\bFq)$ is finitely generated then there is a canonical
-  isomorphism
-  \[
-  \CSiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, G(\bFq)^*),
-  \qquad \text{given by}\qquad
-  [\cs{L}] \mapsto [\tau_\cs{L}],
-  \]
-  where $\tau_\cs{L}: \Weil{\Fq}\to \Hom_\text{grp}(G(\bFq),\EEx)$ is a cocycle such that
-  \[
-  \forall g\in G(\Fq), \qquad \tau_\cs{L}(\Frob{\Fq})(g) = \trFrob{\cs{L}}(g).
-  \]
-\end{proposition}
-
-\begin{proof}
-  To produce the isomorphism between $\CSiso{G(\bFq)}$ and
+  It is clear that the category defined by conditions \ref{cs.0},
+  \ref{cs.1}, \ref{cs.2} and \ref{cs.3}, denoted by
+  \cdef{$\GC(G(\bFq))$}, is equivalent to $\GC(G)$. We will prove the
+  proposition by exhibiting an isomorphism between
+  $\GCiso{G(\bFq)}$ and $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
+
+  To produce the isomorphism between $\GCiso{G(\bFq)}$ and
   $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ we must pick a global section of the line
-  bundle $(\gcs{L},\mu)$, for each character sheaf $\cs{L}$ on $G$; 
+  bundle $(\gcs{L},\mu)$, for each geometrized character $\cs{L}$ on $G$; 
   such a section exists by Lemma~\ref{lemma:section}.
@@
   Conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
-  the scalar $z_\cs{L}(\Frob{k})(x)$ is non-zero, while condition~\ref{cs.1} forces
+  the scalar $z_\cs{L}(\Frob)(x)$ is non-zero, while condition~\ref{cs.1} forces
   $\tau_\cs{L}(\Frob{\Fq})(x+y) = \tau_\cs{L}(\Frob{\Fq})(x) \ \tau_\cs{L}(\Frob{\Fq})(y)$,
@@
   Now we show that $f : H\to G$, as above, together with a character
-  $\psi : \ker \bf \to \EEx$, defines a character sheaf on
-  $G$. We will also show that the restriction of this character sheaf
-  on $G$ to $G^0$ is precisely the character sheaf on $G^0$ defined by
+  $\psi : \ker \bf \to \EEx$, defines a geometrized character on
+  $G$. We will also show that the restriction of this geometrized character
+  on $G$ to $G^0$ is precisely the geometrized character of $G^0$ defined by
   the pair $(f^0,\psi)$ as above.
@@
 \end{proof}
-\Clifton{I can flesh out this remark once I've promoted the definition of $\CSb(G)$ (category of bounded character sheaves on $G$).}
+\Clifton{I can flesh out this remark once I've promoted the definition of $\GCb(G)$ (category of bounded geometrized characters of $G$).}
 \begin{remark}
@@
   fixed by Frobenius, then every character of $\ker f$ determines a
-  character sheaf on $G$. However, it is not true that every character
+  geometrized character of $G$. However, it is not true that every character
   sheaf on $G$ arises in this manner.
@@
   \[
-  \trFrob{G} : \CSiso{G} \to \Hom(G(\Fq),\EEx),
-  \]
-  from the Picard group of the category of character sheaves on $G$ to
+  \trFrob{G} : \GCiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx),
+  \]
+  from the Picard group of the category of geometrized characters of $G$ to
   the group of characters of $G(\Fq)$, is an isomorphism.
@@
   \[
-  \image(\CSiso{\pi_0(G)} \to \CSiso{G}) \subseteq \ker(\CSiso{G} \to \CSiso{G^0}),
+  \image(\GCiso{\pi_0(G)} \to \GCiso{G}) \subseteq \ker(\GCiso{G} \to \GCiso{G^0}),
   \]
   by the last part of Proposition~\ref{prop:pullback}. Specifically,
-  suppose $\cs{L}$ is a character sheaf on $G$ that is trivial on
+  suppose $\cs{L}$ is a geometrized character of $G$ that is trivial on
   $G^0$. Then $\trFrob{\cs{L}}\vert_{G^0(\Fq)} = \trFrob{\cs{L}^0} =0$,
@@
   Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d \in \ZZ_{>0}$, the
-  Picard group of the category of character sheaves on $\GN{T}_d$ is
+  Picard group of the category of geometrized characters of $\GN{T}_d$ is
   canonically isomorphic to the group of characters of $T(K)$ of depth
@@
 \end{corollary}
+
+%\printindex
 

### 2013-08-11 shanghai.tex
Proof that 10.2 is a homomorphism; still needs isomorphism

--- 2013-08-11 shanghai.tex
@@
   isomorphism.  Suppose that $\cs{L}$ and $\cs{L}'$ are two character sheaves.
+  If $s$ is a global section for $\cs{L}$ and $s'$ for $\cs{L}'$ then $s \otimes s'$ is a global section for
+  $\cs{L} \otimes \cs{L}'$.  The three versions of \eqref{t} for $\cs{L}, \cs{L'}$ and $\cs{L} \otimes \cs{L}'$ imply that
+  $\tau_{\cs{L} \otimes \cs{L}'}(\Frob{k}) = \tau_\cs{L}(\Frob{k}) \tau_{\cs{L}'}(\Frob{k})$.
+
   \Clifton{Straightforward, yes, but it still needs to be written down here.}

### 2013-08-11 shanghai.tex

--- 2013-08-11 shanghai.tex
@@
 
-\section{The category of geometrized characters}\label{sec:category}
+\section{Notation}
 
@@
 $\Frob{\Spec{\bFq}} = \Spec{\Frob{\Fq}}$ and $\Frob{\Fq}$  is the geometric Frobenius element in $\Gal(\bFq/\Fq)$.
+
+For any group $A$, we will denote by $A^*$ the dual group $\Hom_\text{grp}(A, \EEx)$.
+
+\section{The category of geometrized characters}\label{section:category}
 
@@
 
-\section{Geometrized characters of commutative etale group schemes}
+\section{Geometrized characters of commutative \'etale group schemes}
 
@@
 
-\begin{proposition}\label{prop:etale}
-  If $G$ is a commutative \'etale group scheme over $\Fq$ and
-  $G(\bFq)$ is finitely generated then there is a canonical
-  isomorphism
-  \[
-  \GCiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, \Hom_\text{grp}(G(\bFq),\EEx)),
-  \qquad \text{given by}\qquad
-  [\cs{L}] \mapsto [\tau_\cs{L}],
-  \]
-  where $\tau_\cs{L}: \Weil{\Fq}\to \Hom_\text{grp}(G(\bFq),\EEx)$ is a cocycle such that
-  \[
-  \forall g\in G(\Fq), \qquad \tau_\cs{L}(\Frob{\Fq})(g) = \trFrob{\cs{L}}(g).
-  \]
-\end{proposition}
-
-\begin{proof}
-  To simplify notation, we set
-  $G(\bFq)^* \ceq \Hom_\text{grp}(G(\bFq),\EEx)$.  Recall the
-  equivalence between etale group schemes over $\Fq$ and the category
-  of groups equipped with a continuous action of $\Gal(\bFq/\Fq)$ (for
-  the discrete topology on the group), given by $G \mapsto G(\bFq)$.
-  Under this equivalence any geometrized character $\cs{L}=(\gcs{L},\mu,\phi)$
-  on $G$ corresponds to:
+\'Etale group schemes form a counterpoint to connected groups, since the component group
+is always \'etale.  The functor $G \mapsto G(\bFq)$ defines an equivalence of categories
+between the category of \'etale group schemes over $\Fq$ and the category of groups equipped
+with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group.
+
+For such a $\Gal(\bFq/\Fq)$-group $G(\bFq)$, we define a category of geometrized characters $\GC(G(\bFq))$.
+An object in $\GC(G(\bFq))$ is given by the data of
+
 \begin{enumerate}
  \labitem{(cs.0)}{cs.0} an indexed set of one-dimensional
-    $\EE$-vector spaces $\gcs{L}_x \ceq x^*\gcs{L}$, as $x$ runs over
+  $\EE$-vector spaces $\gcs{L}_x$, as $x$ runs over
   $G(\bFq)$;
@@
 \end{enumerate}
-  Under this equivalence, a map $\varphi : \cs{L} \to \cs{L'}$ of
-  geometrized characters of $G$ corresponds to:
+
+A morphism $\varphi : \cs{L} \to \cs{L'}$ is given by 
 \begin{enumerate}
-  \labitem{(cs.3)}{cs.3} an indexed set $\varphi_x \ceq x^*\varphi: \gcs{L}_x \to \gcs{L'}_x$
+ \labitem{(cs.3)}{cs.3} an indexed set $\varphi_x : \gcs{L}_x \to \gcs{L'}_x$
   of linear transformations (of one-dimensional $\EE$-vector spaces),
@@
 \end{enumerate}
-  It is clear that the category defined by conditions \ref{cs.0},
-  \ref{cs.1}, \ref{cs.2} and \ref{cs.3}, denoted by
-  \cdef{$\GC(G(\bFq))$}, is equivalent to $\GC(G)$. We will prove the
-  proposition by exhibiting an isomorphism between
-  $\GCiso{G(\bFq)}$ and $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
-
-  To produce the isomorphism between $\GCiso{G(\bFq)}$ and
-  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ we must pick a global section of the line
-  bundle $(\gcs{L},\mu)$, for each geometrized character $\cs{L}$ on $G$; 
-  such a section exists by Lemma~\ref{lemma:section}.
-  We will show that the group isomorphism does not depend on these
-  choices.
-%
-  We use the section $s_\cs{L}$ to define a cocycle $z_\cs{L} \in Z^1(\Weil{\Fq},G(\bFq)^*)$
-  as follows. Recall that $\cs{L}$ also determines a family of linear transformations
-  $\phi_x : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$ of one-dimensional $\EE$-vector
-  spaces, so $\phi_x(s(\Frob{\Fq}(x)))$ is a scalar multiply of $s(x)$, for
-  each $x\in G(\bFq)$; let $\tau_\cs{L}(\Frob{\Fq})(x)$ be that scalar, so
+
+The functor $\GC(G) \to \GC(G(\bFq))$ defined by
+$(\gcs{L}, \mu, \phi) \mapsto (\gcs{L}_x = x^*\gcs{L}, \mu_{x,y} = (x \times y)^* \mu, \phi_x = x^*\phi)$
+is easily seen to be an equivalence.  We may now define a \cdef{global section}
+of a geometrized character $\cs{L}$ on an \'etale group scheme $G$ as a choice $s(x) \in \gcs{L}_x$ for every
+$x \in G(\bFq)$, satisfying
+ \begin{equation}\label{section}
+  \forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes s(y).
+ \end{equation}
+
+\begin{lemma}\label{lemma:section}
+ If $\cs{L}$ is a geometrized character on a commutative, \'etale group scheme $G$
+ with $G(\bFq)$ finitely generated then nontrivial global sections of $\cs{L}$ exist.
+\end{lemma}
+
+\begin{proof}
+  Since $G(\bFq)$ is a finitely-generated abelian group, it admits a decomposition
+  \[
+  G(\bFq) \iso \ZZ^r \oplus \bigoplus_{j=1}^t \ZZ / m_j \ZZ;
+  \]
+  let $x_1, \ldots, x_r, y_1, \ldots, y_t$ be a corresponding set of generators of $G(\bFq)$.
+  We will define a section $s$ by choosing values on these generators and extending to all
+  of $G(\bFq)$ through \eqref{section}.
+
+  There is a unique isomorphism $\gcs{L}_0 \cong \EE$ under which $\mu_{0,0}$ corresponds
+  to the multiplication map $\EE \otimes \EE \to \EE$.
+  The condition $\mu_{0,0}(s(0)) = s(0) \otimes s(0)$ together with the non-triviality of $s$
+  then forces $s(0) = 1$.
+
+  The $\mu_{x,y}$ yield an isomorphism $\alpha_j : \gcs{L}_{y_j}^{\otimes m_j} \to \gcs{L}_0$.
+  An initial nonzero choice of $s(y_j)$ need only be scaled by $\alpha_j(s(y_j))^{-1/m_j}$ in order to map to
+  $1$ under this isomorphism.  Since compatibility under the $\alpha_j$ are the only constraints on the
+  $s(x_j)$ and $s(y_j)$, global sections exist.
+\end{proof}
+
+These global sections will allow us to construct the isomorphism in the following proposition.
+
+\begin{proposition}\label{prop:etale}
+  If $G$ is a commutative \'etale group scheme over $\Fq$ and
+  $G(\bFq)$ is finitely generated then there is a canonical
+  isomorphism
+  \[
+  \GCiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, G(\bFq)^*),
+  \qquad \text{given by}\qquad
+  [\cs{L}] \mapsto [\tau_\cs{L}],
+  \]
+  where $\tau_\cs{L}: \Weil{\Fq}\to G(\bFq)^*$ is a cocycle such that
+  \[
+  \forall x\in G(\Fq), \qquad \tau_\cs{L}(\Frob{\Fq})(x) = \trFrob{\cs{L}}(x).
+  \]
+\end{proposition}
+
+\begin{proof}
+  Suppose $\cs{L}$ is a geometrized character on $G$.  Using Lemma~\ref{lemma:section}, we may choose a global section $s_{\cs{L}}$
+  of $\cs{L}$.  We will construct a group isomorphism between $\GCiso{G(\bFq)}$ and
+  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ using $s_{\cs{L}}$, then prove independence from the choice of section.
+
+  Starting from $\cs{L}$, we define a cocyle $\tau_{\cs{L}} \in Z^1(\Weil{\Fq},G(\bFq)^*)$ as follows.
+  For $x \in G(\bFq)$, $\cs{L}$ determines an isomorphism $\phi_x : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
+  of one-dimensional $\EE$-vector spaces; define $\tau_\cs{L}$ by
   \begin{equation}\label{t}
-    \forall x\in G(\bFq),\qquad \phi_{x}(s(\Frob{\Fq}(x)) = \tau_\cs{L}(\Frob{\Fq})(x) s(x).
+   \phi_{x}(s(\Frob{\Fq}(x))) = \tau_\cs{L}(\Frob{\Fq})(x) s(x).
   \end{equation}
-  Conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
-  the scalar $z_\cs{L}(\Frob)(x)$ is non-zero, while condition~\ref{cs.1} forces
-  $\tau_\cs{L}(\Frob{\Fq})(x+y) = \tau_\cs{L}(\Frob{\Fq})(x) \ \tau_\cs{L}(\Frob{\Fq})(y)$,
-  for all $x,y \in G(\bFq)$.
-  % \Clifton{The alternative to this approach is to change the
-  %   definition of geometrized characters to incorporate the notion of
-  %   Galois sheaves. That might not be so bad, but would add another
-  %   layer of complication, which we wouldn't use profitably, expect
-  %   here.}
-
-  Now $\tau_\cs{L} : \Weil{\Fq} \to G(\bFq)^*$ is defined, recursively, by
-  $\tau_\cs{L}(\Frob{\Fq}^n) \ceq \tau_\cs{L}(\Frob{\Fq})\cdot \,^\Frob{\Fq} \tau_\cs{L}(\Frob{\Fq}^{n-1})$,
+  Note that if $x$ is fixed by $\Frob{k}$ then $\tau_\cs{L}(\Frob{\Fq})(x)$ is just $t_\cs{L}(x)$, so the restriction of
+  $\tau_\cs{L}(\Frob{k})$ to $G(k)$ is just $t_\cs{L}$.
+  In general, conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
+  the scalar $\tau_\cs{L}(\Frob{k})(x)$ is non-zero.  Moreover, condition~\ref{cs.1} forces
+  $\tau_\cs{L}(\Frob{\Fq})(x+y) = \tau_\cs{L}(\Frob{\Fq})(x) \ \tau_\cs{L}(\Frob{\Fq})(y)$
+  for all $x,y \in G(\bFq)$.  Now define $\tau_\cs{L} : \Weil{\Fq} \to G(\bFq)^*$ recursively by
+  \[
+   \tau_\cs{L}(\Frob{\Fq}^n) \ceq \tau_\cs{L}(\Frob{\Fq})\cdot \,^\Frob{\Fq} \tau_\cs{L}(\Frob{\Fq}^{n-1}),
+  \]
   where $\Frob{\Fq}$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers
-  to pointwise multiplication of functions. This gives
-  \[
-  \obj \GC(G(\bFq)) \longrightarrow Z^1(\Weil{\Fq},G(\bFq)^*),
-  \qquad \text{defined by} \qquad \cs{L} \mapsto \tau_\cs{L}.
-  \]
+  to pointwise multiplication of functions.
 
@@
   choice. To see why, let $s_1$ and $s_2$ be two global sections of
-  the line bundle $(\gcs{L},\mu)$, in the sense above and let $\tau_1$
-  and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$, respectively,
-  as above. Since, for each $x\in G(\bFq)$, $\gcs{L}_x$ is a
-  one-dimensional $\EE$-vector space, there is a unique scalar
-  $a(x) \in \EE$ such that $s_2(x) = a(x) s_1(x)$; moreover, $a(x)$ is
-  non-zero, since $s_2(x)$ is non-zero. Then \eqref{section} and
+  $\cs{L}$ and let $\tau_1$ and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$.
+  For each $x \in G(\bFq)$ there is a unique scalar
+  $a(x) \in \EEx$ such that $s_2(x) = a(x) s_1(x)$. Then \eqref{section} and
   condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so
-  $a\in G(\bFq)^*$. Now consider the coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
-  defined by $\tau_0(\Frob{\Fq}) = \,^\Frob{\Fq} a \cdot a^{-1}$. Then $\tau_2 = \tau_0 \tau_1$,
-  so $\tau_2$ and $\tau_1$ are cohomologous. In this way we see that
+  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
+  defined by $\tau_0(\Frob{\Fq}) = \,^\Frob{\Fq} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
+  so $\tau_2$ and $\tau_1$ are cohomologous. Thus
   \begin{equation}\label{cohomologous}
@@
 
-  We now show that the function $\obj \GC(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*)$
-  factors through $\obj \GC(G(\bFq)) \to \GCiso{G(\bFq)}$.
-  To see this, let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and
+  We now show that $[\tau_\cs{L}]$ depends only on the isomorphism class of $\cs{L}$.
+  Let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and
   let $\tau$ and $\tau'$ be any cocycles representing the classes in the
@@
   $\tau$ and $\tau'$ are defined by sections $s$ and $s'$. Now, $\varphi_x(s(x))$ is a
-  non-zero scalar multiple of $s'(x)$; define $\phi: G(\bFq) \to \EEx$
-  by $\varphi_x(s(x)) = \phi(x) s'(x)$. 
-  \Clifton{Notation problem here: replace $\phi$ with something else.}
+  non-zero scalar multiple of $s'(x)$; define $\delta: G(\bFq) \to \EEx$
+  by $\varphi_x(s(x)) = \delta(x) s'(x)$.
   By the second part of condition~\ref{cs.3},
-  $\phi(x+y) = \phi(x)\phi(y)$, so $\phi \in G(\bFq)^*$. By the first part of
-  condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}\phi \cdot \phi^{-1})$,
+  $\delta(x+y) = \delta(x)\delta(y)$, so $\delta \in G(\bFq)^*$. By the first part of
+  condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}\delta \cdot \delta^{-1})$,
   so $\tau$ and $\tau'$ are cohomologous. This concludes the definition of
   \begin{equation}\label{pich1}
-    \GCiso{G(\bFq} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
-    \qquad \text{defined by} \qquad [\cs{L}] \mapsto [\tau_\cs{L}].
+    \GCiso{G(\bFq} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*).
   \end{equation}
-  Now it follows from \eqref{t} that the image of the isomorphism
-  class of $\cs{L}$ is indeed represented by a cocycle $\tau_\cs{L}$ such
-  that $\tau_\cs{L}(\Frob{\Fq}) = \trFrob{\cs{L}}$ on $G(\Fq)$, which is to
-  say, when evaluated at $\Frob{\Fq}$, the cocycle $\tau_\cs{L}$ is an
-  extension of the trace of Frobenius of $\cs{L}$.
 
   It only remains to show that \eqref{pich1} is a group
-  isomorphism. This is straightforward.
+  isomorphism.  Suppose that $\cs{L}$ and $\cs{L}'$ are two geometrized characters.
+  If $s$ is a global section for $\cs{L}$ and $s'$ for $\cs{L}'$ then $s \otimes s'$ is a global section for
+  $\cs{L} \otimes \cs{L}'$.  The three versions of \eqref{t} for $\cs{L}, \cs{L'}$ and $\cs{L} \otimes \cs{L}'$ imply that
+  $\tau_{\cs{L} \otimes \cs{L}'}(\Frob{k}) = \tau_\cs{L}(\Frob{k}) \tau_{\cs{L}'}(\Frob{k})$.
+
   \Clifton{Straightforward, yes, but it still needs to be written down here.}
-\end{proof}
-
-\begin{lemma}\label{lemma:section}
- If $\cs{L}$ is a geometrized character then there is a non-trivial section of $\gcs{L}$ 
- compatible with $\mu$ in the sense that 
- \begin{equation}\label{section}
-  \forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes s(y).
- \end{equation}
-\end{lemma}
-
-\begin{proof}
-First, however, we show that such global sections exist.  Since
-  $G(\bFq)$ is finitely-generated abelian, it admits a decomposition
-  $G(\bFq) \iso G(\bFq)_\text{free} \oplus G(\bFq)_\text{tors}$ such
-  that $G(\bFq)_\text{tors}$ is finite.  Let $x_1, \ldots , x_r$ be a
-  basis for the free part $G(\bFq)_\text{free}$ of $G(\bFq)$ and let
-  $y_1, \ldots , y_t$ be a generators for the torsion part of
-  $G(\bFq)$ corresponding to the decomposition
-  $G(\bFq)_\text{tors} \iso \oplus_{j=1}^t \ZZ/m_j\ZZ$, with
-  $m_j \vert m_{j+1}$. For each such $x_i$ pick $s(x_i)\in \gcs{L}_{x_i}$;
-  for each such $y_j$ pick $s(y_j) \in \gcs{L}_{y_j}$; also set
-  $s({\bar e}) \ceq 0 \in \gcs{L}_{\bar e}$. ....
-  \todo{under construction}
-  In this way we define a section
-  $s \ceq s_\cs{L} : G(\bFq) \to \coprod_{z\in G(\bFq)} \gcs{L}_z$ of
-  projection $\coprod_{z\in G(\bFq)} \gcs{L}_z \to G(\bFq)$ such that
-  $\mu_{x,y}(s(x+y)) = s(x)\otimes s(y)$ for all $x,y \in G(\bFq)$.
-  Under the equivalence at the beginning of this section, $s = s_\cs{L}$
-  corresponds to a global section of the line bundle $(\gcs{L},\mu)$.
-
-\Clifton{I'm going to remove all mention of line bundles from this paper.}
 \end{proof}

### 2013-08-11 shanghai.tex
Restructuring the section on finite character sheaves to relect the plethora of lemmata that are required.

@@
 
-\section{The category of geometrized characters}\label{section:category}
+\section{The category of geometrized characters}\label{sec:category}
 
@@
 The rule $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$ defines a forgetful functor from geometrized characters of $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{Deligne:Weil2}*{Def.~1.1.10 (i)}.
-%
-As remarked after \cite{Deligne:Weil2}*{Def.~1.1.10}, a Weil sheaf $(\gcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
+
+As mentioned after \cite{Deligne:Weil2}*{Def.~1.1.10}, a Weil sheaf $(\gcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
 Since we will need this point of view later, we review that interpretation here.
@@
 defines, for every $w\in \Weil{\Fq}$, an isomorphism
-\[
-\varphi(w) : w_G^* \gcs{L}\to \gcs{L},
-\]
-such that
-\[
-\forall u,v\in \Weil{\Fq},\qquad \varphi(uv) = \varphi(v) \circ v_G^* \varphi(u).
-\]
+$\varphi(w) : w_G^* \gcs{L}\to \gcs{L}$, such that
+$\varphi(uv) = \varphi(v) \circ v_G^* \varphi(u)$ for all $u,v\in \Weil{\Fq}$.
 Note that $\phi = \varphi(\Frob{\Fq})$. 
 If we further define $\varphi_1(w) \ceq (w_G)_*(\varphi(w)^{-1})$ then
-\[
-\varphi_1(w) : (w_G)_* \gcs{L}\to \gcs{L},
-\]
-is an isomorphism and
-\[
- \forall u,v\in \Weil{\Fq},\qquad \varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v),
-\]
-which means the pair $(\gcs{L},\varphi_1)$ is almost an action $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of \cite{SGA4.5}*{Expos\'e XIII,~1.1}.
+$\varphi_1(w) : (w_G)_* \gcs{L}\to \gcs{L}$ is an isomorphism and
+$\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for all $u,v\in \Weil{\Fq}$.
+This means the pair $(\gcs{L},\varphi_1)$ is almost an action $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of \cite{SGA4.5}*{Expos\'e XIII,~1.1}.
 The pair $(\gcs{L},\varphi_1)$ fails to fulfill the requirements of \cite{SGA4.5}*{Expos\'e XIII,~1.1} only because $\Weil{\Fq}$ is profinite.
@@
 \[
-\cdef{\trFrob{G}} : \GCiso{G} \longrightarrow \Hom_\text{grp}(G(\Fq),\EEx),
+\cdef{\trFrob{G}} : \GCiso{G} \longrightarrow G(\Fq)^*,%\Hom_\text{grp}(G(\Fq),\EEx),
 \qquad \text{defined by}\qquad \cs{L} \mapsto \trFrob{\cs{L}},
@@
    \GCiso{G} \rar{f^*} \arrow[swap]{d}{\trFrob{G}} & \GCiso{H} \dar{t_H} \\
-  \Hom_\text{grp}(G(\Fq),\EEx) \rar & \Hom_\text{grp}(H(\Fq),\EEx)
+   G(\Fq)^* \rar & H(\Fq)^*
+  %\Hom_\text{grp}(G(\Fq),\EEx) \rar & \Hom_\text{grp}(H(\Fq),\EEx)
   \end{tikzcd}
@@
 \[
-\GCiso{G} \iso \Hom_\text{grp}(G(\Fq),\EE^\times),
+\GCiso{G} \iso G(\Fq)^*,%\Hom_\text{grp}(G(\Fq),\EE^\times),
 \]
@@
 \[
-\begin{tikzcd}[column sep=45]
-\GCiso{G} \rar{\text{ext'n of scalars}} \dar{\trFrob{G}} & \GCiso{G_{k'}} \dar{\trFrob{G\times_{\Spec{k}} \Spec{k'}}} \\
-\Hom(G(k), \EEx) \rar{\Nm} & \Hom(G(k'), \EEx).
+\begin{tikzcd}[column sep=60]
+\GCiso{G} \rar{\text{ext'n of scalars}} \dar{\trFrob{G}} & \GCiso{G_{k'}} \dar{\trFrob{G_{k'}}} \\
+G(k)^*  \rar{\Nm} & G(k')^*
+%\Hom(G(k), \EEx) \rar{\Nm} & \Hom(G(k'), \EEx).
 \end{tikzcd}
@@
 an object in $C(G)$ is a pair $(f,\psi)$ where: 
-$f : H\to G$ an etale cover and a morphism of commutative group $\Fq$-schemes (an isogeny) 
+$f : H\to G$ an isogeny (a finite, surjective etale morphism and a morphism of commutative group $\Fq$-schemes)
 for which the action of $\Gal(\bFq/\Fq)$ on the etale group scheme $\ker f$ is trivial, 
@@
 for the action of $\ker f'$ on $V'$ by $\psi'$ 
-and the action of $\ker f'$ on $V$ by $\psi \circ h$.
+and the action of $\ker '$ on $V$ by $\psi \circ \alpha$.
+\[
+\begin{tikzcd}
+V \arrow{d}{T} & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} & \arrow[equal]{d} G\\
+V' & \Aut(V) & \arrow[swap]{l}{\psi} \arrow[swap]{u}{\alpha\vert_{\ker f}} \ker f \arrow[hook]{r} & \arrow[swap]{u}{\alpha} H' \arrow{r}{f'} & G\\
+\end{tikzcd}
+\]
+We say that $(\alpha,T)$ in $C(G)$ is a \cdef{weak isomorphism} if $\alpha$ is a covering and $T$ is an isomorphism of vector spaces.
+\Clifton{I suspect $\alpha$ is a covering, for free. Is that right? 
+If $f' = f \circ \alpha$ and $f$ and $f'$ are etale covers, 
+does it follow that $\alpha$ is also an etale cover? (Etale: Yes. Finite? Surjective?) 
+If so, then I can simplify the definition of weak isomorphism accordingly.}
 
@@
 write $f\times_G f' : H\times_G H' \to G$ for the product of $f : H\to G$ and $f' : H'\to G$. 
- Since $\ker(f\times_G f') = (\ker f)\times (\ker f')$, 
+Since $\ker(f\times_G f') \iso (\ker f)\times (\ker f')$, canonically,
 the tensor product of the representations $\psi : \ker f\to \Aut(V)$ and $\psi' : \ker f'\to \Aut(V')$ 
@@
 
-We say that $(\alpha,T)$ in $C(G)$ is a \cdef{weak isomorphism} if $T$ is an isomorphism of vector spaces. 
+%
 Let \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at weak isomorphisms.
@@
 This is the rigid symmetric monoidal category of \cdef{finite geometrized characters} of $G$.
+
+\begin{proposition}\label{prop:GCf-pull-back}
+If $g : G'\to G$ is a morphism of group schemes then $(f,\psi) \mapsto (f_g,\psi_g)$ defines a monomial functor $g^* : \GCf(G) \to \GCf(G')$ where $f_g : H\times_G G'\to G'$ and $\psi_g : \ker f_g \to \Aut(V)$ are defined by the diagram below.
+\[
+\begin{tikzcd}
+V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
+  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker g_f}} \ker f_g \arrow[hook]{r} & \arrow[swap]{u}{g_f} H\times_G G' \arrow{r}{f_g} & \arrow{u}{g} G'.
+\end{tikzcd}
+\]
+\end{proposition}
+
+\begin{proposition}
+Each $(f,\psi)\in \GCf(G)$ determines a canonical isomorphism $m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\GCf(G\times G)$.
+ \end{proposition}
+
+\begin{proof}
+Before compare $m^*(f,\psi)$ and 
+\end{proof}
+
+Every morphism of group schemes $g: G'\to G$ 
+defines a function $g^*: \obj C(G) \to \obj C(G')$ 
+by $g^*(f,\psi) = (f_g,\psi_g)$ where
+$f_g : H\times_G G'\to G'$ and $\psi_g : \ker f_g \to \Aut(V)$ are defined by the diagram below.
+\[
+\begin{tikzcd}
+V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
+  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker g_f}} \ker f_g \arrow[hook]{r} & \arrow[swap]{u}{g_f} H\times_G G' \arrow{r}{f_g} & \arrow{u}{g} G'.
+\end{tikzcd}
+\]
+This definition is
 
@@
  and $(\alpha'_1,T'_1) : (f_1,\psi_1) \to (f',\psi')$ is a weak isomorphism.
+ \Clifton{Reveal the commented-out details . . . I think I need them!}
 % this morphism is commonly denoted by $(\alpha_1,T_1)^{-1}\circ (\alpha'_1,T'_1)$. 
@@
  Then the equivariance condition on $T$ becomes $\psi' = \psi\circ h$ on the finite etale group scheme $\ker f'$. 
- Since $f' = f \circ \alpha$ and $f$ and $f'$ are etale covers, 
- it follows that $\alpha$ is also an etale cover. 
- \Clifton{Is that right? If $f' = f \circ \alpha$ and $f$ and $f'$ are etale covers, 
- does it follow that $\alpha$ is also an etale cover? (Etale: Yes. Finite? Surjective?) If not, then I must modify the definition of weak isomorphism accordingly.} 
- It follows that $\alpha : H'\to H$ admits a section $\alpha' : H \to H'$, 
+ Since $\alpha : H'\to H$ is an etale cover, it admits a section $\alpha' : H \to H'$, 
  which provides the inverse to $L(\alpha,T) : L(f,\psi) \to L(f',\psi')$, above. 
- \Clifton{Is it clear?}
  It is also clear that if $L(\alpha,T)$ is an isomorphism of local systems, 
@@
 
-  Every morphism of group schemes $G'\to G$ 
-  induces a monoidal functor $C(G) \to C(G')$ by base-change along $G'\to G$ 
-  ({\it cf.}, Proposition~\ref{prop:pullback}) as follows. 
-  Let $m : G'\to G$ be a morphism of group schemes. 
-  Let $(f,\psi)$ be an object in $C(G)$.
-
-  indeed, the pull-back of $(f,\psi)$ along any morphism $m : G'\to G$ of group schemes 
-  can be read off the short exact sequence obtained by pulling back along $m$.
-
-  Taking the case when $m$ is the multiplication morphism $m : G\times G\to G$, 
-  and using the tensor category structure above, 
-  we see that the pull-back of $(f,\psi)$ along $m$ is canonically isomorphic, in $C_1(G\times G)$, to $(f,\psi)\boxtimes(f,\psi)$.
-  \Clifton{I need to work on this diagram and explain better what's going on here. Under construction.}
-  \[
-   \begin{tikzcd}
-V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow{r}  & H \arrow{r}{f} & G \\
-V & \Aut(V) \arrow[equal]{u} & \arrow[swap]{l}{\psi_{m_H}} \ker (f\times f) \arrow{r} \arrow{u}{m_H} & \arrow{d} H\times H \arrow{r}{f\times f} \arrow{u}{m_H} & G\times G \arrow{u}{m} \\
-V\otimes V & \Aut(V\otimes V) & \arrow[swap]{l}{\psi\otimes \psi} \ker f \times \ker f \arrow{r}  & H\times H \arrow{r}{f\times f}  & G\times G \arrow[equal]{u} \\
-   \end{tikzcd}
-  \]
-
  If $(f,\psi)$ in an object in $C_1(G)$ then, as we have already seen, 
- $m^*L(f,\psi) \iso L(f,\psi) \boxtimes L(f,\psi)$ in $C_1(G\times G)$, canonically;
+ $m^*L(f,\psi) \to L(f,\psi) \boxtimes L(f,\psi)$ by a weak isomorphism in $C_1(G\times G)$.
+ This morphism in $C_1(G\times G)$ is not unique, but its image in $\GCf(G\times G)$ is . . .!
+
  let $\mu(f,\psi)$ be that isomorphism of $\ell$-adic sheaves on $G$,
@@
 We will see that the full subcategory $\GC_f(G) \subset \GC_0(G)$ of finite geometrized characters is a proper subcategory, in general.
-Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)$ to the subgroup $\GCfiso{G}$ is an isomorphism onto the subgroup of $\chi \in \Hom_\text{grp}(G(\Fq),\EEx)$ such that the image of $\chi$ is finite in $\EEx$.
+Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to G(\Fq)^*$ to the subgroup $\GCfiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is finite in $\EEx$.
 
@@
   \[
-  \trFrob{G} : \GCiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)
+  \trFrob{G} : \GCiso{G} \to G(\Fq)^*
   \]
@@
   To finish the proof of Proposition~\ref{prop:connected}, it suffices to observe that the group homomorphism
-  \[
-  \trFrob{G} : \GCiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)
-  \]
-  is surjective because, as we have seen, 
-  each character $\chi \in \Hom_\text{grp}(G(\Fq),\EEx)$ determines a finite geometrized character $(\Lang,\chi)$
-  such that the trace of Frobenius of the geometrized character $B_G^* (L_G(\Lang,\chi))$ is $\chi$.
+  $
+  \trFrob{G} : \GCiso{G} \to G(\Fq)^*
+  $
+  is surjective because each character $\chi \in G(\Fq)^*$ determines a finite geometrized character $(\Lang,\chi)$ such that the trace of Frobenius of the geometrized character $B_G^* (L_G(\Lang,\chi^{-1}))$ is $\chi$.
 \end{proof}
@@
 
-A morphism $\varphi : \cs{L} \to \cs{L'}$ is given by 
+A morphism $\alpha : \cs{L} \to \cs{L'}$ is given by 
 \begin{enumerate}
- \labitem{(cs.3)}{cs.3} an indexed set $\varphi_x : \gcs{L}_x \to \gcs{L'}_x$
+ \labitem{(cs.3)}{cs.3} an indexed set $\alpha_x : \gcs{L}_x \to \gcs{L'}_x$
   of linear transformations (of one-dimensional $\EE$-vector spaces),
@@
    \begin{tikzcd}[column sep=40]
-    \arrow[swap]{d}{\phi_x} \gcs{L}_{\Frob{\Fq}(x)} \rar{\varphi_{\Frob{\Fq}(x)}} & \gcs{L'}_{\Frob{\Fq}(x)} \dar{\phi_x'}
-    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}& \arrow[swap]{d}{\mu} \gcs{L}_{x+y} \rar{\varphi_{x+y}} & \gcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
-    \gcs{L}_x \rar{\varphi_x} & \gcs{L'}_x
-    & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\varphi_x\otimes \varphi_y} & \gcs{L'}_x \otimes \gcs{L'}_y
+    \arrow[swap]{d}{\phi_x} \gcs{L}_{\Frob{\Fq}(x)} \rar{\alpha_{\Frob{\Fq}(x)}} & \gcs{L'}_{\Frob{\Fq}(x)} \dar{\phi_x'}
+    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}& \arrow[swap]{d}{\mu} \gcs{L}_{x+y} \rar{\alpha_{x+y}} & \gcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
+    \gcs{L}_x \rar{\alpha_x} & \gcs{L'}_x
+    & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\alpha_x\otimes \alpha_y} & \gcs{L'}_x \otimes \gcs{L'}_y
    \end{tikzcd}
@@
 $(\gcs{L}, \mu, \phi) \mapsto (\gcs{L}_x = x^*\gcs{L}, \mu_{x,y} = (x \times y)^* \mu, \phi_x = x^*\phi)$
-is easily seen to be an equivalence.  We may now define a \cdef{global section}
+is easily seen to be an equivalence.
+
+We may now define a \cdef{global section}
 of a geometrized character $\cs{L}$ on an \'etale group scheme $G$ as a choice $s(x) \in \gcs{L}_x$ for every
@@
   \begin{align*}
-    \Hh^1(\Fq, \Hom(X, \EEx)) &\xrightarrow{\rho} \Hom(\Hh^0(\Fq, X), \EEx) \\
+%    \Hh^1(\Fq, \Hom(X, \EEx)) &\xrightarrow{\rho} \Hom(\Hh^0(\Fq, X), \EEx) \\
+    \Hh^1(\Fq, X^*) &\xrightarrow{\rho} \Hh^0(\Fq, X)^* \\
     \rho([z])(x) &= z(\Frob{\Fq})(x)

### 2013-08-11 shanghai.tex
STILL working on the finite geochars lemmata.

@@
 
-We will see that the full subcategory $\GC_0(G)$ of bounded geometrized characters is a proper subcategory, in general.
-Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx)$ to the subgroup $\GCbiso{G}$ is an isomorphism onto the subgroup of $\chi \in \Hom_\text{grp}(G(\Fq),\EEx)$ such that the image of $\chi$ is bounded in $\EEx$.
+We will see that the full subcategory $\GC_0(G)$ of bounded geometrized characters is a proper subcategory of $\GC(G)$, in general.
+Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to G(\Fq)^*$ to the subgroup $\GCbiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is bounded in $\EEx$, so if $G(\Fq)$ is not finite, then $\GC_0(G) \hookrightarrow\GC(G)$ is not essentially surjective.
 
@@
 \]
-We say that $(\alpha,T)$ in $C(G)$ is a \cdef{weak isomorphism} if $\alpha$ is a covering and $T$ is an isomorphism of vector spaces.
 \Clifton{I suspect $\alpha$ is a covering, for free. Is that right? 
@@
 If so, then I can simplify the definition of weak isomorphism accordingly.}
-
-We put a tensor category structure on $C(G)$ as follows.
+We say that $(\alpha,T)$ in $C(G)$ is a \cdef{weak isomorphism} if $\alpha$ is a covering and $T$ is an isomorphism of vector spaces.
+Let \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at weak isomorphisms.
+
+We put a tensor category structure on $C(G)$ 
+and a rigid monoidal category structure on $C_1(G)$ as follows.
 Let $(f,\psi)$ and $(f',\psi')$ be objects in $C(G)$. 
@@
 where $\psi^\vee : \ker f \to \Aut(V^\vee)$ and $V^\vee = \Hom_\text{vec}(V,\EE)$. 
-The verification that these operations make $C(G)$ a tensor category is routine.
-
-%
-Let \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at weak isomorphisms.
-Now, let \cdef{$C_1(G)$} be the subcategory of $C(G)$ such that $\psi$ is a one-dimensional representation
-and let \cdef{$\GCf(G)$} be the localisation of $C_1(G)$ at weak isomorphisms. 
-This is the rigid symmetric monoidal category of \cdef{finite geometrized characters} of $G$.
-
-\begin{proposition}\label{prop:GCf-pull-back}
-If $g : G'\to G$ is a morphism of group schemes then $(f,\psi) \mapsto (f_g,\psi_g)$ defines a monomial functor $g^* : \GCf(G) \to \GCf(G')$ where $f_g : H\times_G G'\to G'$ and $\psi_g : \ker f_g \to \Aut(V)$ are defined by the diagram below.
-\[
-\begin{tikzcd}
-V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker g_f}} \ker f_g \arrow[hook]{r} & \arrow[swap]{u}{g_f} H\times_G G' \arrow{r}{f_g} & \arrow{u}{g} G'.
-\end{tikzcd}
-\]
-\end{proposition}
-
-\begin{proposition}
-Each $(f,\psi)\in \GCf(G)$ determines a canonical isomorphism $m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\GCf(G\times G)$.
- \end{proposition}
-
-\begin{proof}
-Before compare $m^*(f,\psi)$ and 
-\end{proof}
-
-Every morphism of group schemes $g: G'\to G$ 
-defines a function $g^*: \obj C(G) \to \obj C(G')$ 
-by $g^*(f,\psi) = (f_g,\psi_g)$ where
-$f_g : H\times_G G'\to G'$ and $\psi_g : \ker f_g \to \Aut(V)$ are defined by the diagram below.
-\[
-\begin{tikzcd}
-V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker g_f}} \ker f_g \arrow[hook]{r} & \arrow[swap]{u}{g_f} H\times_G G' \arrow{r}{f_g} & \arrow{u}{g} G'.
-\end{tikzcd}
-\]
-This definition is
+The verification that these operations make $C(G)$ a tensor category is straightforward.
+Likewise, $C(G)[W^{-1}]$ is a tensor category.
+
+Let \cdef{$C_1(G)$} be the rigid monoidal full subcategory of $C(G)$ consisting of objects $(f,\psi)$ such that $\psi$ is a one-dimensional representation and let \cdef{$\GCf(G)$} be the localisation of $C_1(G)$ at weak isomorphisms; this is the rigid symmetric monoidal category of \cdef{finite geometrized characters} of $G$.
 
@@
  It follows that a morphism in $C(G)[W^{-1}]$ is the equivalence class of 
-  \[
+  \begin{equation}\label{eq:morGCf}
    \begin{tikzcd}
@@
    \end{tikzcd}
-  \]
+  \end{equation}
  where $(\alpha',T') : (f,\psi) \to (f',T')$ is any map in $C(G)$ 
- and $(\alpha'_1,T'_1) : (f_1,\psi_1) \to (f',\psi')$ is a weak isomorphism.
- \Clifton{Reveal the commented-out details . . . I think I need them!}
-% this morphism is commonly denoted by $(\alpha_1,T_1)^{-1}\circ (\alpha'_1,T'_1)$. 
- %The equivalence relation identifies $(\alpha_1,T_1)^{-1}\circ (\alpha'_1,T'_1)$ 
- % with $(\alpha_2,T_2)^{-1}\circ (\alpha'_2,T'_2)$ if there are maps 
- %$(f_1,\psi_1)\to (f_0,\psi_0)$ and $(f_2,\psi_2)\to (f_0,\psi_0)$ making the following diagram commute
- %\[
- %  \begin{tikzcd}
- %  & (f_1,\psi_1) \arrow{d} & \\
- %  (f,\psi) \arrow{ur}{(\alpha_1,T_1)} \arrow{dr}{(\alpha_2,T_2)} & (f_0,\psi_0)  & \arrow[swap]{ld}{(\alpha'_2,T'_2)} \arrow[swap]{lu}{(\alpha'_1,T'_1)} (f',\psi')\\
- %  & (f_2,\psi_2) \arrow{u} & \\
- %  \end{tikzcd}
- %\]
- %where $(f',\psi') \to (f_0,\psi_0)$ is a weak isomorphism.
+ and $(\alpha'_1,T'_1) : (f_1,\psi_1) \to (f',\psi')$ is a weak isomorphism,
+ and therefore given by a diagram of the form
 
@@
 
- If $(f,\psi)$ in an object in $C_1(G)$ then, as we have already seen, 
- $m^*L(f,\psi) \to L(f,\psi) \boxtimes L(f,\psi)$ by a weak isomorphism in $C_1(G\times G)$.
- This morphism in $C_1(G\times G)$ is not unique, but its image in $\GCf(G\times G)$ is . . .!
-
- let $\mu(f,\psi)$ be that isomorphism of $\ell$-adic sheaves on $G$,
- It follows immediately that the functor $L_G  \ceq  L_{W}\vert_{\GCf(G)} : \GCf(G) \to \GCb(G)$, 
- given on objects by $(f,\psi) \mapsto (L(f,\psi), \mu(f,\psi))$,
+ By Lemma~\ref{lemma:finite-iso}, each $(f,\psi) \in \GCf(G)$ determines 
+ an isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi) \boxtimes (f,\psi)$ in $\GCf(G\times G)$, canonically.
+ It follows immediately that the functor 
+ \[
+ L_G  \ceq  L_{W}\vert_{\GCf(G)} : \GCf(G) \to \GCb(G),
+ \] 
+ given on objects by $(f,\psi) \mapsto (L(f,\psi), L_{W}(\mu(f,\psi)))$,
  is a full and faithfull monoidal functor, completing the proof.
+\end{proof}
+
+\begin{lemma}\label{lemma:finite-pull-back}
+If $g : G'\to G$ is a morphism of group schemes then $(f,\psi) \mapsto (f_g,\psi_g)$ defines a monomial functor $g^* : C(G)[W^{-1}] \to C(G')[W'^{-1}]$ where $f_g : H\times_G G'\to G'$ is a pull-back of $f$ along $g$ and $\psi_g : \ker f_g \to \Aut(V)$ is defined by the diagram below.
+\[
+\begin{tikzcd}
+V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
+  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker g_f}} \ker f_g \arrow[hook]{r} & \arrow[swap]{u}{g_f} H\times_G G' \arrow{r}{f_g} & \arrow{u}{g} G'.
+\end{tikzcd}
+\]
+\end{lemma}
+
+\begin{proof}
+The main issue to address is well-definedness. Although the pull-back appearing in the diagram above it not unique, the recipe for $g^*$ is well-defined as a functor between localized categories.
+To see this, recall that a morphism in $\GCf(G)$ is an equivalence class of a diagram like \eqref{eq:morGCf}, commonly denoted by $(\alpha_1,T_1)^{-1}\circ (\alpha'_1,T'_1)$. 
+The equivalence relation identifies $(\alpha_1,T_1)^{-1}\circ (\alpha'_1,T'_1)$
+ with $(\alpha_2,T_2)^{-1}\circ (\alpha'_2,T'_2)$ if there are maps 
+ $(f_1,\psi_1)\to (f_0,\psi_0)$ and $(f_2,\psi_2)\to (f_0,\psi_0)$ making the following diagram commute
+ \[
+  \begin{tikzcd}
+  \  & A & \\
+B   & C & D \\
+  & E &
+  \end{tikzcd}
+ \]
+ where $(f',\psi') \to (f_0,\psi_0)$ is a weak isomorphism.
+
+\end{proof}
+
+\begin{lemma}\label{lemma:finite-iso}
+Each $(f,\psi)\in \GCf(G)$ determines a canonical isomorphism $m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\GCf(G\times G)$.
+ \end{lemma}
+
+\begin{proof}
+Before compare $m^*(f,\psi)$ and 
 \end{proof}

### 2013-08-12 shanghai.tex
Finished the first lemma on finite geochars.
Working on the second lemma on geochars this evening  . . .

@@
 \begin{proof}
-The main issue to address is well-definedness. Although the pull-back appearing in the diagram above it not unique, the recipe for $g^*$ is well-defined as a functor between localized categories.
-To see this, recall that a morphism in $\GCf(G)$ is an equivalence class of a diagram like \eqref{eq:morGCf}, commonly denoted by $(\alpha_1,T_1)^{-1}\circ (\alpha'_1,T'_1)$. 
-The equivalence relation identifies $(\alpha_1,T_1)^{-1}\circ (\alpha'_1,T'_1)$
- with $(\alpha_2,T_2)^{-1}\circ (\alpha'_2,T'_2)$ if there are maps 
- $(f_1,\psi_1)\to (f_0,\psi_0)$ and $(f_2,\psi_2)\to (f_0,\psi_0)$ making the following diagram commute
- \[
-  \begin{tikzcd}
-  \  & A & \\
-B   & C & D \\
-  & E &
-  \end{tikzcd}
- \]
- where $(f',\psi') \to (f_0,\psi_0)$ is a weak isomorphism.
-
+The key point is that pull-back along $g$ takes isogenies to isogenies, and maps over $G$ to maps over $G'$, as pictured below.
+\[
+\begin{tikzcd}[row sep=10,column sep=10]
+\ & V \arrow{dd}{T} && \Aut(V) && \arrow[swap]{ll}{\psi} \ker f \arrow[hook]{rr} && H \arrow{rr}{f} && \arrow[equal]{dd} G\\
+ && && \arrow{ul} \ker f\times_G G' \arrow{ur} \arrow[hook]{rr} && H\times_G G' \arrow{ur} \arrow{rr} && G' \arrow{ur}{g} & \\
+& V' && \Aut(V) && \arrow[swap]{ll}{\psi'} \arrow[swap]{uu}{} \ker f'  \arrow[hook]{rr} && \arrow[swap]{uu} H' \arrow{rr}{f'} && G\\
+ && && \arrow{ul} \ker f'\times_G G' \arrow{uu} \arrow{ur} \arrow[hook]{rr} && \arrow{uu} H'\times_G G' \arrow{ur} \arrow{rr} && \arrow[equals]{uu} G' \arrow{ur}{g} & \\
+\end{tikzcd}
+\]
+In this form we could treat $g^*$ as a functor $G(G')\to C(G)$, where it not for the fact that pull-back is defined only up to isomorphism. In the localized categories, this ambiguity disappears. 
 \end{proof}

### 2013-08-12 shanghai.tex
Proved the second lemma in the section on finite geochars. It need polishing later.
That's all for tonight. Moving on to the section on restriction to the
identity component tomorrow.

@@
 \begin{proof}
-Before compare $m^*(f,\psi)$ and 
+As in Lemma~\ref{lemma:finite-pull-back}, we have $m^*(f,\psi) = (f_m,\psi_m)$ where $f_m$ and $\psi_m$ are pictured below, where $H_m = H\times_G(G\times G)$.
+\[
+\begin{tikzcd}
+V & \Aut(V) & \arrow[swap]{l}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
+  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(m_f)\vert_{\ker m_f}} \ker f_m \arrow[hook]{r} & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G.
+\end{tikzcd}
+\]
+On the other hand, set $p_1^*(f,\psi) = (f_1,\psi_1)$, so $f_1 = f\times \id : H\times G\to G\times G$ and $A_1\ceq \ker f_1 = A \times G$ and $\psi_1 = \psi \circ p_1$; set $p_2^*(f,\psi) = (f_2,\psi_2)$, so $f_2 = \id \times f : G\times H \to G\times G$ and $A_2\ceq \ker f_2 = G \times A$ and $\psi_2 = \psi \circ p_2$.
+Then $(f,\psi) \boxtimes (f,\psi) = (f_1,\psi_1) \otimes (f_2,\psi_2) = (f_1\times_{G\times G} f_2, \psi_1\otimes \psi_2) = (f\times f, \psi\otimes \psi) $ is given by
+\[
+\begin{tikzcd}
+V\otimes V & \Aut(V\otimes V) & \arrow[swap]{l}{\psi\otimes \psi} A \times A \arrow[hook]{r}{} & H \times H \arrow{r}{f\times f} & G\times G\\
+\end{tikzcd}
+\]
+Since $f\circ m_H = m \circ (f\times f)$, by the universal property of pull-back, there is a unique $\theta : H\times H \to H_m$ making the following commute.
+\[
+\begin{tikzcd}
+\ &  & \arrow{ld}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
+V \arrow{d}{U} & \Aut(V)  & \arrow{l}{\psi_g} \arrow{u} A_m \arrow[hook]{r} & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G\\
+V\otimes V & \Aut(V\otimes V) & \arrow[swap]{l}{\psi\otimes\psi} \arrow[bend left]{uu}{m_H} \arrow[swap]{u}{\theta\vert_{A\times A}} A \times A \arrow[hook]{r}{} & \arrow[bend left]{uu}{m_H} \arrow[swap]{u}{\theta} H \times H \arrow{r}{f\times f} & \arrow[equal]{u} G\times G\\
+\end{tikzcd}
+\]
+Choose a basis $\{ v_1 \}$ for $V$; then $\{ v_1\otimes v_1 \}$ is a basis for $V\otimes V$.
+Define $U : V \to V\otimes V$ by $U(v_1) = v_1\otimes v_1$.
+Then the lower part of this diagram defines a weak isomorphism $(\theta,U): (f_m,\psi_m)\to (f\times f,\psi\otimes\psi)$.
+This defines an weak isomorphism $(\theta,U): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G)$.
+
+While $\theta$ was canonical, $U$ was not, as it depended on the choice of a basis for $V$.
+However, after passing from $C_1(G)$ to $\GCf(G)$, the resulting isomorphism $\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ is canonical in $\GCf(G)$.
 \end{proof}

### 2013-08-12 shanghai.tex
Reworked the section on restriction to the identity component.
Created a lemma to hold the proof that every discrete isogeny to G^0
extends to a discrete isogeny to G.
The proof that restriction to the identity component is surjective is
now very short, largely because it now uses the propositions regardling
finite geochars.

@@
 an object in $C(G)$ is a pair $(f,\psi)$ where: 
-$f : H\to G$ an isogeny (a finite, surjective etale morphism and a morphism of commutative group $\Fq$-schemes)
-for which the action of $\Gal(\bFq/\Fq)$ on the etale group scheme $\ker f$ is trivial, 
+$f : H\to G$ is a \cdef{discrete isogeny} (a finite, surjective etale morphism and a morphism of commutative group $\Fq$-schemes, for which the action of $\Gal(\bFq/\Fq)$ on the etale group scheme $f^{-1}{\bar e}$ is trivial),
 and $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$;
@@
 
-\David{This section needs to be modified once the bounded geometrized characters section is done}
 Let $G^0$ be the connected component of $G$ containing the identity.
@@
 $\cs{L}\mapsto \cs{L}\vert_{G^0}$ from $\GC(G)$ to $\GC(G^0)$.  In
-this section we show that this functor is essentially surjective. To
-do this we employ a perspective on characters sheaves which is
-different from that in Section~\ref{sec:category} but which works
-very well for geometrically connected abelian algebraic groups; this
-perspective fails to extend properly to the more general context of
-Section~\ref{sec:category}.
+this section we show that this functor is essentially surjective.
 
@@
 \begin{proof}
-  Because $G$ is smooth over $\Fq$, the identity component $G^0$ is a
-  geometrically connected algebraic group over $\Fq$, clopen in $G$
-  \cite{vdG&M}*{3.17}. By Proposition~\ref{prop:connected}, every
-  geometrized character $\cs{E} = (\gcs{E},\mu^0,\phi^0)$ on $G^0$ descends to
-  a line bundle on $G^0$.
-
-  Let us review how line bundles on $G^0$ determine geometrized characters
-  on $G^0$.  Up to isomorphism, line bundles on $G^0$ may be
-  apprehended in terms of pairs $(\pi,\psi)$,
-  \David{Aren't there line bundles which are not geometrized characters,
-    for which $B$ is not an algebraic group?}
-  where $\pi : B\to G^0$ is a finite etale morphism of algebraic
-  groups and a character $\psi : A\to \EEx$, where
-  $\Gal(\bFq/\Fq)$ acts trivially on $A \ceq \ker {\bar \pi}$, as
-  summarized by the following diagram.
-  \begin{equation}\label{E}
-  \begin{tikzcd}
-  \EEx & 1\rar & A \arrow[bend right,swap]{ll}{\psi} \rar & B \rar{\pi} & G^0 \rar & 1
-  \end{tikzcd}
-  \end{equation}
-  (In fact, we may always take $B = G^0$ and $\pi = \Lang_{G^0}$, the
-  Lang isogeny for $G^0$.)  Indeed, $\cs{E}$ is precisely the
-  component of $\pi_! (\EE)_{B}$ on which $A$ acts through $\psi$.  To
-  see that $\cs{E}$ is a line bundle on $G^0$, start by pulling back
-  $\pi: B \to G^0$ along $m_0 : \GzxGz \to G^0$.
-  \begin{equation}
-  \begin{tikzcd}
-  \EEx & 1\rar & A \arrow[bend right,swap]{ll}{\psi} \rar & B \rar{\pi} & G^0 \rar & 1\\
-      & 1\rar & \AxA \arrow[dashed]{llu} \uar \rar
-      & \BxB \rar{\pi\tight{1}{\times}{1} \pi} \uar{m_{B}} & \GzxGz \uar{m_0} \rar & 1
-  \end{tikzcd}
-  \end{equation}
-  As pictured above, the kernel of this pull-back is $\AxA$;
-  indeed, $\AxA \to \BxB$ is the pull-back of $A\to B$ along
-  $m_{B}$. Use this Cartesian square to define a character (the dotted
-  arrow, above) of $\AxA$; that is, define $\AxA \to \EEx$
-  by the composition of $\AxA \to A$ and $\psi : A\to \EEx$.
-  Note that this character is $\psi \otimes \psi : \AxA \to \EEx$.
-  \Clifton{I haven't explained how maps between diagrams define sheaf
-    homomorphisms between local systems.}
-  Since the lower sequence is precisely the sequence defining
-  $\ExE$, this shows that, by construction, $\cs{E}$
-  comes equipped with a canonical isomorphism $m_0^*\cs{E} \iso \ExE$.
-  Now the base change $\gcs{E}$ comes equipped with isomorphisms
-  $\phi^0 : \Frob{G^0}^* \gcs{E} \to \gcs{E}$ and
-  $\mu^0 : \bm_0^* \gcs{E} \to \bExE$
-  satisfying conditions \ref{CS.1} and \ref{CS.2}. Then $(\gcs{E},\mu^0,\phi^0)$
-  is a geometrized character of $G^0$.
-
-  The next step is to show that $\pi: B \to G^0$ extends to a finite
-  etale morphism of group schemes $f: H\to G$, smooth and locally of
-  finite type over $\Fq$, in such a way that $H^0 = B$, $f^0 =\pi$ and
+  Because $G$ is smooth over $\Fq$, the identity component, 
+  $G^0$, is a connected algebraic group over $\Fq$, 
+  clopen in $G$ \cite{vdG&M}*{3.17}. 
+  By Proposition~\ref{prop:connected}, every
+  geometrized character on $G^0$ is isomorphic to a 
+  finite geometrized character on $G^0$, 
+  so to prove the proposition it suffices to show that every 
+  finite geochar on $G^0$ extends to a geochar on $G$.
+
+ Let $(\pi,\psi)$ be a finite geochar on $G^0$.
+ By Lemma~\ref{lemma:ext}, there is an extension of the 
+ descrete isogeny $\pi : B \to G^0$ 
+ (see Section~\ref{sec:finite} for the definition of a discrete isogeny) 
+ to a discrete isogeny $f : H \to G^0$ 
+ such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
+ Then $(f,\psi)$ is a finite geochar on $G$.
+ Then $(f,\psi)\vert_{G^0} \iso (\pi,\psi)$,
+ completing the proof that $\GC(G)\to \GC(G^0)$ is essentially surjective.
+\end{proof}
+
+\begin{lemma}\label{lemma:ext}
+Every discrete isogeny onto $G^0$ extends to a discrete isogeny onto $G$ such that the component group of the covering space is isomorphic to the component group of $G$.
+\end{lemma}
+
+\begin{proof}
+Let $\pi: B \to G^0$ be a discrete isogeny; set $A = \ker \pi$.
+  We will find a discrete isogeny $f: H\to G$
+  such that that $H^0 = B$, $f^0 =\pi$ and
   $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism of component
@@
   $\Fq$.  We will do so by passing back and forth between group
-  schemes over $\Fq$ and their $\bFq$-points.  Extensions of
+  schemes over $\Fq$ and their $\bFq$-points.
+
+  Extensions of
   $G^0(\bFq)$ by $A(\bFq)$, such as $A(\bFq) \to H^0(\bFq) \to G^0(\bFq)$,
@@
   classes in $\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq))$.  The map
-  $G^0(\bFq) \to G(\bFq)$ induces a map
+  $G^0(\bFq) \to G(\bFq)$ induces the map
   $\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))$,
@@
   morphisms are $\Gamma$-equivariant.
-
-  Now we show that $f : H\to G$, as above, together with a character
-  $\psi : \ker \bf \to \EEx$, defines a geometrized character on
-  $G$. We will also show that the restriction of this geometrized character
-  on $G$ to $G^0$ is precisely the geometrized character of $G^0$ defined by
-  the pair $(f^0,\psi)$ as above.
-
-  Set $X \ceq \pi_0(G)\times_{\Spec{\Fq}} \Spec{\bFq}$. We will
-  identify $X$ with $\pi_0(H)\times_{\Spec{\Fq}} \Spec{\bFq}$ using
-  the base change of $\pi_0(f): \pi_0(H)\to \pi_0(G)$. For each $x\in X$,
-  write $\bf^x : \bH^x \to \bG^x$ for the
-  restriction of $\bf$ to $\bH^x$, as a cover of
-  $\bG^x$. For each $x,y\in X$, let
-  $\bm_{x,y} : \bH^x \times \bH^{y} \to \bH^{x+y}$
-  be the map obtained from $\bm$ by restriction. Define
-  $\bm_{x} : A\to \Aut(\bf^x)$ by
-  $\bm_{x}(a): g \mapsto \bm_{0,x}(a,g)$; then
-  $\bm_{x} : A\to \Aut(\bf^x)$ is an isomorphism.
-  \Clifton{I need to show that $\bm_{x} : A\to \Aut(\bf^x)$ is an isomorphism.}
-
-  For each $x\in X$ let $\gcs{L}^x$ be the rank-$1$ local system on
-  $\bG^x$ determined by the finite etale cover
-  $\bf^x : \bH^x \to \bG^x$ and the character
-  $\psi_x \ceq \psi \circ \bm_x^{-1}$.  Since
-  $\bG = \coprod_{x\in X} \bG^x$ (disjoint union), this
-  determines a constructible sheaf $\gcs{L}$ on $\bG$, locally
-  constant of rank-$1$ on each connected component of $\bG$.
-  Taking the case $x=0$ we observe that $\gcs{L}^0 =\gcs{E}$,
-  the latter defined above. To finish the proof of the proposition we
-  equip $\gcs{L}$ with isomorphisms
-  $\mu : \bm^* \gcs{L} \to \LxL$ and
-  $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ satisfying conditions \ref{CS.1}
-  and \ref{CS.2}.
-
-  Observe that $\bm: \bGxG \to \bG$ is
-  completely determined by the family of maps
-  $\bm_{x,y} : \bG^x \times \bG^{y} \to \bG^{x+y}$.
-  Accordingly, to define $\mu$ for $\gcs{L}$ it is sufficient to define isomorphisms
-  $\mu_{x,y} : \bm_{x,y}^*\gcs{L}^{x+y} \iso \gcs{L}^{x}\boxtimes \gcs{L}^{y}$
-  for all $x,y\in X$. To do that, note first that the local system
-  $\gcs{L}^{x}\boxtimes \gcs{L}^{y}$ is defined by the following diagram.
-  \[
-  \begin{tikzpicture}[auto,style={rectangle}]
-  \node (0) at (0,0) {$\EEx$};
-  \node (1) [anchor=east] at (6,0) {$\Aut(\bf^x) \times \Aut(\bf^y)$};
-  \node (2) [anchor=west] at (6.4,0) {$\bH^x \times \bH^y$};
-  \node (3) at (11,0) {$\bG^x \times \bG^y$};
-  \draw [->] (1) to node[swap, label] {$\psi_x \otimes \psi_y$} (0);
-  \draw [->] (6.3,-0.06) arc (330:40:0.12) -- (6.3,0.07);
-  \draw [->] (2) to node[label] {$\bf^x \tight{0}{\times}{0} \bf^y$} (3);
-  \end{tikzpicture}
-  \]
-  On the other hand, the diagram for the local system $\bm_{x,y}^* \gcs{L}^{x+y}$
-  is found by pulling-back the diagram for $\gcs{L}^{x+y}$ along
-  $\bm_{x,y} : \bH^x\times\bH^y \to \bH^{x+y}$;
-  the result is the middle horizontal diagram below, where we use the
-  fact that the covering group of the middle arrow is $\Aut(\bf^{x+y})$, canonically.
-
-  \vspace{0.2in}
-
-  \[
-  \begin{tikzpicture}[auto,style={shape={asymmetrical rectangle}},scale=1.2]
-  \node (12) [anchor=east] at (4,2.4) {$\Aut(\bf^{x+y})$};
-  \node (22) [anchor=west] at (4.4,2.4) {$\bH^{x+y}$};
-  \node (32) [anchor=east] at (11,2.4) {$\bG^{x+y}$};
-  \node (01) at (0,1.2) {$\EEx$};
-  \node (11) [anchor=east] at (4,1.2) {$\Aut(\bf^{x+y})$};
-  \node (21) [anchor=west] at (4.4,1.2) {$\bH^{x+y} \times_{\bG^{x+y}} (\bG^x\times\bG^y)$};
-  \node (31) [anchor=east] at (11,1.2) {$\bG^x\times \bG^y$};
-  \node (10) [anchor=east] at (4,0) {$\Aut(\bf^x)\times \Aut(\bf^y)$};
-  \node (20) [anchor=west] at (4.4,0) {$\bH^x\times \bH^y$};
-  \node (30) [anchor=east] at (11,0) {$\bG^x\times \bG^y$};
-  \draw [->] (4.3,2.34) arc (330:40:0.12) -- (4.3,2.47);
-  \draw [->, densely dotted] (4.3,1.14) arc (330:40:0.12) -- (4.3,1.27);
-  \draw [->] (4.3,-0.06) arc (330:40:0.12) -- (4.3,0.07);
-  \draw [->] (12) to node[swap,label] {$\psi_{x+y}$} (01);
-  \draw [->, dashed] (11) -- (01);
-  \draw [->] (10) to node[label] {$\psi_x \otimes \psi_y$} (01);
-  \draw [->, dashed] ($(11.south) + (0,-0.7)$) -- (11);
-  \draw [double equal sign distance] (11) -- (12);
-  \draw [->] (22) to node[label] {$\bf^{x+y}$} (32);
-  \draw [->] ($(22.south) + (0,-0.7)$) -- (22);
-  \draw [->] (21) -- (31);
-  \draw [->] ($(32.225) + (0,-0.7)$) to node[swap] {\footnotesize{$\bm_{x,y}$}} (32.225);
-  \draw [->] ($(22.south) + (0,-1.9)$) -- ($(22.south) + (0,-1.2)$);
-  \draw [->] (20) to node[label] {$\bf^x \times \bf^y$} (30);
-  \draw [double equal sign distance] ($(32.225) + (0,-1.9)$) -- ($(32.225) + (0,-1.2)$);
-  \end{tikzpicture}
-  \]
-  Now, the homomorphism from the covering group of
-  $\bf^x\times\bf^y$ to the covering group of
-  $\bf^{x+y}$ induced by the composition
-  $ \bH^x\times \bH^y \to \bH^{x+y} \times_{\bG^x\times\bG^y} \bG^x\times\bG^y \to \bH^{x+y}$
-  is precisely $(\bm_x(a),\bm_y(b)) \mapsto \bm_{x+y}(ab)$.
-  Since this map commutes with the characters $\psi_x\otimes\psi_y$
-  and $\psi_{x+y}$ (so, the far-left triangle commutes in the diagram above)
-  it follows that, for each $x,y\in X$ the diagram above defines a canonical isomorphism
-  $\mu_{x,y} : \bm_{x,y}^* \gcs{L}^{x+y} \to \gcs{L}^x \boxtimes\gcs{L}^y$.
-  This defines $\mu: \bm^* \gcs{L} \iso \LxL$.
-  It is straightforward (but laborious) to show that the pair
-  $(\gcs{L},\mu)$ satisfies condition \ref{CS.1}.
-
-  Now we turn to the definition of $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$.
-  As above, we define this isomorphism through a family of
-  isomorphisms on the connected components of $\bG$. The
-  restriction of $\Frob{G}$ to $\bG^x$ defines an isomorphism
-  $\Frob{G}^x : \bG^x \to \bG^{\Frob{\Fq}(x)}$.
-  %\[
-  %\xymatrix{
-  %\ar[d]_{\Frob_x} \bG^x \ar[r] & \ar[d]_{\Frob{G}} \bG\\
-  %\bG^{\Frob{\Fq}(x)} \ar[r] & \bG\\
-  %}
-  %\]
-  Pull back the finite etale covering in the diagram for
-  $\gcs{L}^{\Frob{\Fq}(x)}$ along $\Frob{G}^x$ and compare the result with the
-  finite etale covering in the diagram for $\gcs{L}^{x}$.
-
-  \[
-  \begin{tikzpicture}[auto,style={rectangle},scale=1.2]
-  \node (12) [anchor=east] at (4,2.4) {$\Aut(\bf^{\Frob{\Fq}(x)})$};
-  \node (22) [anchor=west] at (4.4,2.4) {$\bH^{\Frob{\Fq}(x)}$};
-  \node (32) [anchor=west] at (8,2.4) {$\bG^{\Frob{\Fq}(x)}$};
-  \node (01) at (0,1.2) {$\EEx$};
-  \node (11) [anchor=east] at (4,1.2) {$\Aut(\bf^{\Frob{\Fq}(x)})$};
-  \node (21) [anchor=west] at (4.4,1.2) {$\bH^{\Frob{\Fq}(x)} \times_{\bG^{\Frob{\Fq}(x)}} \bG^x$};
-  \node (31) [anchor=west] at (8,1.2) {$\bG^x$};
-  \node (10) [anchor=east] at (4,0) {$\Aut(\bf^x)$};
-  \node (20) [anchor=west] at (4.4,0) {$\bH^x$};
-  \node (30) [anchor=west] at (8,0) {$\bG^x$};
-  \draw [->] (4.3,2.34) arc (330:40:0.12) -- (4.3,2.47);
-  \draw [->, densely dotted] (4.3,1.14) arc (330:40:0.12) -- (4.3,1.27);
-  \draw [->] (4.3,-0.06) arc (330:40:0.12) -- (4.3,0.07);
-  \draw [->] (12) to node[swap,label] {$\psi_{\Frob{\Fq}(x)}$} (01);
-  \draw [->, dashed] (11) -- (01);
-  \draw [->] (10) to node[label] {$\psi_x$} (01);
-  \draw [->, dashed] ($(11.south) + (0,-0.7)$) -- (11);
-  \draw [double equal sign distance] (11) -- (12);
-  \draw [->] (22) to node[label] {$\bf^{\Frob{\Fq}(x)}$} (32);
-  \draw [->] ($(22.225) + (0,-0.7)$) -- (22.225);
-  \draw [->] (21) -- (31);
-  \draw [->] ($(32.222) + (0,-0.7)$) to node[swap] {\footnotesize{$\Frob{G}^x$}} (32.222);
-  \draw [->] ($(22.225) + (0,-1.9)$) -- ($(22.225) + (0,-1.2)$);
-  \draw [->] (20) -- (30);
-  \draw [double equal sign distance] ($(32.222) + (0,-1.9)$) -- ($(32.222) + (0,-1.2)$);
-  \end{tikzpicture}
-  \]
-  The covering group of $\bH^{\Frob{\Fq}(x)} \times_{\bG^{\Frob{\Fq}(x)}} \bG^x$
-  is isomorphic to $\Aut(\bf^{\Frob{\Fq}(x)})$, canonically, so
-  $(\Frob{G}^x)^* \gcs{L}^{\Frob{\Fq}(x)}$ is defined by the middle (horizontal)
-  diagram, above.  We define the sheaf homomorphism
-  $\phi_x : (\Frob{G}^x)^* \gcs{L}^{\Frob{\Fq}(x)} \to \gcs{L}^x$ by the canonical morphism
-  $\bH^x \to \bH^{\Frob{\Fq}(x)} \times_{\bG^{\Frob{\Fq}(x)}} \bG^x \to $;
-  to see that this defines a sheaf homomorphism it is sufficient to
-  check that the character $\psi_x$ commutes with the family of isomorphisms
-  $\phi_x : (\Frob{G}^* \gcs{L})\vert_{\bG^x} \iso (\Frob{G}^x)^* \gcs{L}^{\Frob{x}} \to \gcs{L}^x$
-  now defines the isomorphism $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$.
-  \Clifton{Add some detail here.}
-  This isomorphism is compatible with $\mu$ in the sense of condition~\ref{CS.2}.
 \end{proof}
-\Clifton{I can flesh out this remark once I've promoted the definition of $\GCb(G)$ (category of bounded geometrized characters of $G$).}
-\begin{remark}
-  We have seen that if $f : H\to G$ is a finite etale cover of $G$ by
-  a smooth group scheme and if all geometric automorphisms of $f$ are
-  fixed by Frobenius, then every character of $\ker f$ determines a
-  geometrized character of $G$. However, it is not true that every character
-  sheaf on $G$ arises in this manner.
-\end{remark}
-
-%\input{centralextensions}
 

### 2013-08-12 shanghai.tex
Minor changes to notation in the section using the snake lemma.

@@
 \newcommand{\GCfiso}[1]{\GCf(#1)_{/\text{iso}}}
-\newcommand{\CE}{{\mathcal{C\hskip-1.8pt E}}}
 \newcommand{\Lgroup}[1]{{\,^L\hskip-1pt{#1}}}
@@
   \[
-  \trFrob{G} : \GCiso{G} \to \Hom_\text{grp}(G(\Fq),\EEx),
+  \trFrob{G} : \GCiso{G} \to G(\Fq)^*
   \]
@@
     & \GCiso{G} \rar \dar{\trFrob{G}} & \GCiso{G^0} \rar \dar{t_{G^0}} & 0\\
-    0 \rar & \Hom(\pi_0(G)(\Fq),\EEx) \rar \dar
-    & \arrow[dashed]{d} \Hom(G(\Fq),\EEx) \rar & \Hom(G^0(\Fq),\EEx) \rar \dar & 0\\
+    0 \rar & \pi_0(G)(\Fq)^* \rar \dar
+    & \arrow[dashed]{d} G(\Fq)^* \rar & G^0(\Fq)^* \rar \dar & 0\\
     & \coker t_{\pi_0(G)} & \coker \trFrob{G} &  \coker t_{G^0} &
@@
   commutes (by Proposition~\ref{prop:pullback}), the bottom sequence
-  is exact at $\Hom(G(\Fq),\EEx)$ and $\coker t_{\pi_0(G)} =0$
+  is exact at $G(\Fq)^*$ and $\coker t_{\pi_0(G)} =0$
   (by Propositions~\ref{prop:etale} and \ref{prop:X}) and
@@
   by Proposition~\ref{prop:pullback} again. Since the sequence of
-  character groups is exact at $\Hom(G(\Fq),\EEx)$, there is
-  some $\chi \in \Hom(\pi_0(G)(\Fq),\EEx)$ such that the
+  character groups is exact at $G(\Fq)^*$, there is
+  some $\chi \in \pi_0(G)(\Fq)^*$ such that the
   pull-back of $\chi$ along $G(\Fq)\to \pi_0(G)(\Fq)$ is

### 2013-08-12 shanghai.tex
Changes to the section on application to characters of tori.
I merged the two `applications' sections.

@@
 The category of geometrized characters of $G$, denoted by \cdef{$\GC(G)$},
-is defined as follows.  A \cdef{geometrized character} on $G$ is a triple
+is defined as follows.  A \cdef{geometrized character on $G$} is a triple
 $\cs{L}\ceq (\gcs{L},\mu,\phi)$ where:
@@
 \]
-On the other hand, set $p_1^*(f,\psi) = (f_1,\psi_1)$, so $f_1 = f\times \id : H\times G\to G\times G$ and $A_1\ceq \ker f_1 = A \times G$ and $\psi_1 = \psi \circ p_1$; set $p_2^*(f,\psi) = (f_2,\psi_2)$, so $f_2 = \id \times f : G\times H \to G\times G$ and $A_2\ceq \ker f_2 = G \times A$ and $\psi_2 = \psi \circ p_2$.
-Then $(f,\psi) \boxtimes (f,\psi) = (f_1,\psi_1) \otimes (f_2,\psi_2) = (f_1\times_{G\times G} f_2, \psi_1\otimes \psi_2) = (f\times f, \psi\otimes \psi) $ is given by
-\[
-\begin{tikzcd}
-V\otimes V & \Aut(V\otimes V) & \arrow[swap]{l}{\psi\otimes \psi} A \times A \arrow[hook]{r}{} & H \times H \arrow{r}{f\times f} & G\times G\\
-\end{tikzcd}
-\]
+On the other hand, $(f,\psi) \boxtimes (f,\psi) = (f\times f, \psi\otimes \psi)$.
 Since $f\circ m_H = m \circ (f\times f)$, by the universal property of pull-back, there is a unique $\theta : H\times H \to H_m$ making the following commute.
@@
 Define $U : V \to V\otimes V$ by $U(v_1) = v_1\otimes v_1$.
-Then the lower part of this diagram defines a weak isomorphism $(\theta,U): (f_m,\psi_m)\to (f\times f,\psi\otimes\psi)$.
-This defines an weak isomorphism $(\theta,U): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G)$.
+Then the lower part of this diagram defines a weak isomorphism $(\theta,U): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G)$.
 
@@
  \end{equation}
+\Clifton{I've been putting lemmata after the propositions that use them, 
+to keep the flow of the sections clear. 
+Would you mind if I do the same in this section?}
 
@@
   $\tau_{\cs{L} \otimes \cs{L}'}(\Frob{k}) = \tau_\cs{L}(\Frob{k}) \tau_{\cs{L}'}(\Frob{k})$.
-
-  \Clifton{Straightforward, yes, but it still needs to be written down here.}
 \end{proof}
@@
 
-\section{Application to characters of bounded depth}
-
-%\input{GdeN}
-Let $p$ be a prime number. Let $K$ be a local field with residue field
-$\Fq$, where $p$ divides $q$. Let $\OK$ be the ring of integers of $K$
-and let $\pK$ be the maximal ideal in $\OK$.
+\section{Application to characters of algebraic tori over local fields}
+
+Let $K$ be a local field with residue field $\Fq$.
+%(Note that we place no restriction on the characteristic of $K$.)
+Let $T$ be an algebraic torus over $K$.
+
+%In this section we introduce a group scheme $\GN{T}$ over $\Fq$ obtained by applying the Greenberg functor to the N\'eron lft-model for $T$ and establish some basic facts about $\GN{T}$
+
+%\subsection{The N\'eron locally finite type model for $T$}
+
+The lft-N\'eron model for $T$, denoted here by $\TT$, 
+is a separated, smooth, commutative group scheme locally of finite type over $\OK$ 
+(the ring of integers of $K$)
+with generic fibre $T$, that enjoys the N\'eron mapping property: if
+$S$ is a smooth scheme over $\OK$ then every morphism $S_\eta \to T$
+over $K$ extends uniquely to a morphism $S \to \TT$. Equivalently, the
+N\'eron mapping property states that the function
+$\Hom_{\OK} (S,\TT) \to \Hom_K(S_\eta,T)$, given by restriction to
+generic fibres, is a bijection; 
+in particular, taking $S = \Spec{\OK}$, this implies $\TT(\OK) = T(K)$.
+
+For each positive integer $d$, let $\TT_{d}$ be the group scheme obtained from $\TT$ by base change along $\OK \to \OK/\pK^d$, where $\pK$ is the maximal ideal in $\OK$. 
+Observe that $\OK/\pK^d$ is an Artin ring and $\TT_{d}$ is smooth and locally of finite type over $\OK/\pK^d$.
 %
-In this section we introduce a group scheme $\GN{T}$ over $\Fq$
-obtained by applying the Greenberg functor to the N\'eron lft-model
-for $T$ and establish some basic facts about $\GN{T}$
-
-%\subsection{The N\'eron locally finite type model for $T$}
-
-The lft-N\'eron model for $T$, denoted here by $\TT$, is a separated,
-smooth, commutative group scheme locally of finite type over $\OK$
-with generic fibre $T$, that enjoys the N\'eron mapping property: if
-$X$ is a smooth scheme over $\OK$ then every morphism $X_\eta \to T$
-over $K$ extends uniquely to a morphism $X \to \TT$. Equivalently, the
-N\'eron mapping property states that the function
-$\Hom_{\OK} (X,\TT) \to \Hom_K(X_\eta,T)$, given by restriction to
-generic fibres, is a bijection; in particular, this implies $\TT(\OK) = T(K)$.
-
-For each $d\in \ZZ_{>0}$, let $\TT_{d}$ be the smooth group scheme over
-$\OK/\pK^d$ obtained from $\TT$ by base change along $\OK \to
-\OK/\pK^d$. Observe that $\OK/\pK^d$ is an Artin ring and
-$\TT_{d}$ is locally of finite type over $\OK/\pK^d$.
-
-Let $\GN{T}_{d} = \Gr(\TT_d)$ be the group scheme over $\Fq$ produced by applying
-the Greenberg functor to $\TT_{d}$. (See \cite{Greenberg:2} and
-\cite[Ch. 9, \S 6]{BLR} for background on the Greenberg functor.)
-%Then $\GN{T}_d(\Fq) = \TT(\OK/\pK^d)$.
-
-\begin{proposition}\label{prop:GN}
-  Fundamental properties of the group $\Fq$-scheme $\GN{T}_d$, for all $d\in \NN$:
+Let \cdef{$\GN{T}_{d} = \Gr(\TT_d)$} be the group scheme over $\Fq$ produced by applying
+the Greenberg functor to $\TT_{d}$; this is the \cdef{Greenberg transform of $\TT_d$}.
+See \cite{Greenberg:2} and \cite[Ch. 9, \S 6]{BLR} and the first few sections of \cite{Stasinski} for background on the Greenberg functor. The fundamental properties of $\GN{T}_d$ that we need are:
  \begin{enumerate}
-  \labitem{(GNd.0)}{GN0} $\GN{T}_d^0$, the identity component of
-    $\GN{T}_d$, is a commutative algebraic group over $\Fq$;
-  \labitem{(GNd.1)}{GNd} $\GN{T}_d$ is smooth and locally of finite type over $\Fq$;
-  \labitem{(GNd.2)}{pi0} $\pi_0(\GN{T}_d) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$;
-  \labitem{(GNd.3)}{fg} the component group of $\GN{T}_d$ is geometrically finitely generated;
-  \labitem{(GNd.4)}{dFq} $\GN{T}_d(\Fq) = \TT(\OK/\pK^d)$, canonically;
+   \labitem{(GN.0)}{dFq} $\GN{T}_d(\Fq) = \TT(\OK/\pK^d)$, canonically.
+  \labitem{(GN.1)}{GNd} $\GN{T}_d$ is a smooth, commutative group scheme, locally of finite type over $\Fq$, and the component group of $\GN{T}_d$ is geometrically finitely generated.
   \end{enumerate}
-\end{proposition}
-
-\begin{proof}
-\Clifton{Proofs still missing, but all straightforward. I'll cite as much as I can, here.}
-\end{proof}
+In fact, $\pi_0(\GN{T}_d) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$, and the latter is finitely generated by \cite{Xarles}.
 
@@
   Let $T$ be an algebraic torus over a non-Archimedean local field $K$.
-  Let $\GN{T}_d$ and $\GN{T}$ be as above.  For each $d \in \ZZ_{>0}$, the
+  Let $\GN{T}_d$ be as above.  For each positive integer $d$, the
   Picard group of the category of geometrized characters of $\GN{T}_d$ is
@@
 \begin{proof}
-  By \ref{GNd} and \ref{fg}, we may apply Theorem~\ref{thm:snake} to
+  By \ref{GNd}, we may apply Theorem~\ref{thm:snake} to
   $\GN{T}_d$ which provides a canonical isomorphism
-  \[
-  \GCiso{\GN{T}_d} \iso \Hom(\GN{T}_d(\Fq),\EEx).
-  \]
+  $\GCiso{\GN{T}_d} \iso \GN{T}_d(\Fq)^*$.
   By \ref{dFq}, $\GN{T}_d(\Fq) \iso \TT(\OK/\pK^d)$ canonically.
@@
   define depth has the property that $\TT(\OK/\pK^d) \cong T(K) / T(K)_d$
-  \cite[Prop 5.2]{Yu} for $d \in \ZZ_{>0}$.  Thus characters of $\GN{T}_d(\Fq)$ are
-  in bijection with characters of $T(K)$ vanishing on $T(K)_d$.
+  \cite[Prop 5.2]{Yu}, so characters of $\GN{T}_d(\Fq)$ 
+  are in bijection with characters of $T(K)$ vanishing on $T(K)_d$. 
+  %Note that $d$ is a positive integer.  
 \end{proof}
 
-\section{Application to admissible characters}
+%\section{Application to admissible characters}
 
 %\input{pro}
-To conclude the paper we offer an interpretation of
-Theorem~\ref{thm:application} that makes no mention of depth.
-
-\Clifton{Explain what happens as $d$ varies.}
-Suppose $d\leq d'$.
-
-We may now assemble the group $\Fq$-schemes $\TT_{d}$ into one
+We may also assemble the group $\Fq$-schemes $\TT_{d}$ into one
 glorious group pro-scheme over $\Fq$:
 \begin{equation}\label{projlim}
-  \GN{T} \ceq \varprojlim_{d\in \NN} \GN{T}_{d}.
+  \cdef{\GN{T}} \ceq \varprojlim_{d\in \ZZ_{>0}} \GN{T}_{d}.
 \end{equation}
-This is the \cdef{Greenberg transform of the lft-N\'eron model of $T$}; we will also write $\Gr$ for this functor on $\OK$-schemes.
-
-\Clifton{Prove that $\GN{T}$ is a scheme? Strictly speaking, we don't
-  care about \ref{scheme}.}
-
-\Clifton{Must still define $\GC(\GN{T})$, since it is not an instance
- of our definitions, above.}
-
-\begin{proposition}
-  Fundamental properties of $\GN{T}$:
+This is the \cdef{Greenberg transform of the N\'eron model of $T$}.
+ Some fundamental properties of $\GN{T}$ are:
  \begin{enumerate}
-  \labitem{(GN.0)}{scheme} $\GN{T}$ is a commutative group scheme over $\Fq$;
-  \labitem{(GN.1)}{T(K)} $\GN{T}(\Fq) = T(K)$, canonically.
+   \labitem{(GN.2)}{T(K)} $\GN{T}(\Fq) = T(K)$, canonically;
+  \labitem{(GN.3)}{scheme} $\GN{T}$ is a commutative group scheme over $\Fq$.
   \end{enumerate}
-\end{proposition}
+This gives us a natural way to geometrize all admissible characters of $T(K)$
+without reference to depth.
+Let \cdef{$\GC(\GN{T})$} be the ind-category $\varinjlim_{d\in \ZZ_{>0}} \GC(\GN{T}_d)$;
+we refer to objects of $\GC(\GN{T})$ as \cdef{geometrized characters of $T$}.
 
 \begin{corollary}
-  \[
-  \GCiso{\GN{T}} \iso \Hom_\text{ad}(T(K),\EEx)
+Let $T$ be an algebraic torus over a non-Archimedean local field $K$.
+The Picard group of the category $\GC(\GN{T})$ of geometrized characters of $T$ is canonically isomorphic to the group of admissible characters of $T(K)$:
+  \[
+  \GCiso{\GN{T}} \iso \Hom_\text{ad}(T(K),\EEx).
   \]
@@
 
+\bib{Stasinski}{article}{
+   author={Stasinski, Alexander},
+   title={Reductive group schemes, the Greenberg functor, and associated
+   algebraic groups},
+   journal={J. Pure Appl. Algebra},
+   volume={216},
+   date={2012},
+   number={5},
+   pages={1092--1101},
+%   issn={0022-4049},
+%   review={\MR{2875329}},
+%   doi={10.1016/j.jpaa.2011.10.027},
+}
+
 \bib{Tate:thesis}{article}{

### 2013-08-12 base change.tex
Moved more material in from the base change file; I'll work it into the draft.

@@
 
-\section{Restriction of scalars}
-
-In the opposite direction, there is a canonical closed immersion of $k$-schemes
-$G \hookrightarrow \Res_{k'/k}(G_{k'})$ \cite[\S 7.6]{BLR}.  Pullback yields a functor
-\[
-\CS(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota} \CS(G).
-\]
-\begin{proposition} \label{prop:csbe}
-The following diagram commutes, where the bottom map is induced by the inclusion $G(k) \hookrightarrow G(k')$:
-\[
-\begin{tikzcd}
-\CSiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota} \dar{t_{\Res_{k'/k}(G_{k'})}} & \CSiso{G} \dar{t_G} \\
-\Hom(G(k'), \EEx) \arrow[two heads]{r} & \Hom(G(k), \EEx).
-\end{tikzcd}
-\]
-\end{proposition}
-
-Now suppose that $G'$ is an abelian group scheme over $k'$, satisfying the conditions of Theorem \ref{thm:snake}.
-There is a canonical isomorphism between $G'(k')$ and $(\Res_{k'/k}G')(k)$;
-we now describe the corresponding functor from
-$\CS(G')$ to $\CS(\Res_{k'/k}G')$.  The base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
-decomposes into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
-\[
-(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
-\]
-The component corresponding to the identity element yields a natural inclusion 
-\[
-G' \hookrightarrow (\Res_{k'/k}G')_{k'}
-\]
-of $k'$-schemes.  The definition of base change yields a map of $k$-schemes
-\[
-(\Res_{k'/k}G')_{k'} \to \Res_{k'/k}G'.
-\]
-Consecutive pullback along these maps yields a functor
-\[
-\CS(G') \to \CS(\Res_{k'/k}G').
-\]
-
-\begin{proposition}
-  Then the following diagram commutes:
-\[
-\begin{tikzcd}
-\CSiso{G'} \dar{t_{G'}} \rar & \CSiso{\Res_{k'/k} G'} \dar{t_{\Res_{k'/k} G'}} \\
- \Hom(G'(k'), \EEx) \rar & \Hom((\Res_{k'/k}G')(k), \EEx)
-\end{tikzcd}
-\]
-\end{proposition}
-
-\section{Base change over the local field}
-
-We have already seen that the trace of Frobenius defines a canonical isomorphism 
-$t_T : \CSiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
-In this section we expand on the canonicity of this group isomorphism 
-by showing that it is a natural transformation. We also show
-
-\begin{proposition}
-The isomorphism $t_T : \CSiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$ 
-is a natural transformation between the following two contravariant functors 
-from the category of algebraic tori over $K$ to the category of abelian groups: 
-\begin{enumerate}
-\item $T \mapsto \CSiso{\GN{T}}$
-\item $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
-\end{enumerate}
-\end{proposition}
-
-\Clifton{I think I can prove this proposition without too much difficulty.}
-\begin{proof}
-\end{proof}
-
-Let $L/K$ be a finite Galois extension and let $K'/K$ be the maximal unramified subextension, with residue field $k'$.
-If $T$ is a torus over $K$, write $\TL$ for the N\'eron model of the base change $T_L$.
-Then there is a canonical isomorphism
-\[
-\Res_{k'/k} \Gr(\TL) \cong \Gr(\underline{\Res_{L/K}(T_L)}).
-\]
-The natural inclusion $T \hookrightarrow \Res_{L/K} T_L$ induces a map of $k$-schemes
-\[
-\GN{T} \hookrightarrow \Res_{k'/k} \Gr(\TL)
-\]
-and thus a functor on character sheaves through pullback.
-
-\begin{proposition}
-The following diagram commutes:
-\[
-\begin{tikzcd}
-\CSiso{\Res_{k'/k} \Gr(\TL)} \arrow[two heads]{r} \dar & \CSiso{\GN{T}} \dar\\
-\Hom(T(L), \EEx) \arrow[two heads]{r} & \Hom(T(K), \EEx)
-\end{tikzcd}
-\]
-\end{proposition}
-
 We now translate the norm map $T(L) \to T(K)$ to character sheaves.  There is an open immersion

### 2013-08-12 shanghai.tex
Moved more material in from the base change file; I'll work it into the draft.

@@
 
+\Clifton{Return to finite and bounded character sheaves, explaining why our definition is the right one. Also explain why we don't think of local systems as representations of a fundamental group.}
+
+\section{Restriction of scalars}
+
+In the opposite direction, there is a canonical closed immersion of $k$-schemes
+$G \hookrightarrow \Res_{k'/k}(G_{k'})$ \cite[\S 7.6]{BLR}.  Pullback yields a functor
+\[
+\GC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota} \GC(G).
+\]
+\begin{proposition} \label{prop:csbe}
+The following diagram commutes, where the bottom map is induced by the inclusion $G(k) \hookrightarrow G(k')$:
+\[
+\begin{tikzcd}
+\GCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota} \dar{t_{\Res_{k'/k}(G_{k'})}} & \GCiso{G} \dar{t_G} \\
+\Hom(G(k'), \EEx) \arrow[two heads]{r} & \Hom(G(k), \EEx).
+\end{tikzcd}
+\]
+\end{proposition}
+
+Now suppose that $G'$ is an abelian group scheme over $k'$, satisfying the conditions of Theorem \ref{thm:snake}.
+There is a canonical isomorphism between $G'(k')$ and $(\Res_{k'/k}G')(k)$;
+we now describe the corresponding functor from
+$\GC(G')$ to $\GC(\Res_{k'/k}G')$.  The base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
+decomposes into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
+\[
+(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
+\]
+The component corresponding to the identity element yields a natural inclusion 
+\[
+G' \hookrightarrow (\Res_{k'/k}G')_{k'}
+\]
+of $k'$-schemes.  The definition of base change yields a map of $k$-schemes
+\[
+(\Res_{k'/k}G')_{k'} \to \Res_{k'/k}G'.
+\]
+Consecutive pullback along these maps yields a functor
+\[
+\GC(G') \to \GC(\Res_{k'/k}G').
+\]
+
+\begin{proposition}
+  Then the following diagram commutes:
+\[
+\begin{tikzcd}
+\GCiso{G'} \dar{t_{G'}} \rar & \GCiso{\Res_{k'/k} G'} \dar{t_{\Res_{k'/k} G'}} \\
+ \Hom(G'(k'), \EEx) \rar & \Hom((\Res_{k'/k}G')(k), \EEx)
+\end{tikzcd}
+\]
+\end{proposition}
+
 \section{Application to characters of algebraic tori over local fields}
@@
 
+\section{Base change over the local field}
+
+We have already seen that the trace of Frobenius defines a canonical isomorphism 
+$t_T : \GCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
+In this section we expand on the canonicity of this group isomorphism 
+by showing that it is a natural transformation. We also show
+
+\begin{proposition}
+The isomorphism $t_T : \GCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$ 
+is a natural transformation between the following two contravariant functors 
+from the category of algebraic tori over $K$ to the category of abelian groups: 
+\begin{enumerate}
+\item $T \mapsto \GCiso{\GN{T}}$
+\item $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
+\end{enumerate}
+\end{proposition}
+
+\Clifton{I think I can prove this proposition without too much difficulty.}
+\begin{proof}
+\end{proof}
+
+Let $L/K$ be a finite Galois extension and let $K'/K$ be the maximal unramified subextension, with residue field $k'$.
+If $T$ is a torus over $K$, write $\TL$ for the N\'eron model of the base change $T_L$.
+Then there is a canonical isomorphism
+\[
+\Res_{k'/k} \Gr(\TL) \cong \Gr(\underline{\Res_{L/K}(T_L)}).
+\]
+The natural inclusion $T \hookrightarrow \Res_{L/K} T_L$ induces a map of $k$-schemes
+\[
+\GN{T} \hookrightarrow \Res_{k'/k} \Gr(\TL)
+\]
+and thus a functor on character sheaves through pullback.
+
+\begin{proposition}
+The following diagram commutes:
+\[
+\begin{tikzcd}
+\GCiso{\Res_{k'/k} \Gr(\TL)} \arrow[two heads]{r} \dar & \GCiso{\GN{T}} \dar\\
+\Hom(T(L), \EEx) \arrow[two heads]{r} & \Hom(T(K), \EEx)
+\end{tikzcd}
+\]
+\end{proposition}
+
 \section{The transfer principle}
@@
 \David{We should add a discussion of why we care about the transfer principle.}
+
+The techniques in this paper apply to all non-Archimdean local fields $K$ with residue field $k$, and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$ or on the ramification of $T$.
+Because of this, it is natural to ask if we can compare geometrized characters of $T$
+
 We recall the notion of $N$-congruent tori from \cite[\S 2]{CY}.  Suppose $T$ and $T'$

### 2013-08-12 shanghai.tex
Made a few more changes to the section on base change over finite fields.

@@
 how geometrized characters behave under change of fields.
-Suppose that $k'$ is a finite extension of $k$ of degree $n$, 
-$G$ is a commutative smooth group scheme locally of finite type over $k$.
+Let $k'$ be a finite extension of $k$. Then $k\to k'$ induces a group homomorphism $i_{k'/k} : G(k) \hookrightarrow G(k')$ which, in turn, gives
+\[
+i_{k'/k}^* : G(k')^* \to G(k)^* \qquad \text{defined by}\qquad \chi \mapsto \chi\circ i_{k'/k}.
+\]
+We can interpret this operation on characters in terms of geometrized characters, as follows.
+%
+
+\begin{proposition} \label{prop:csbe}
+Set $G_{k'} = G\times_\Spec{k} \Spec{k'}$ and let
+\[
+\GC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \GC(G)
+\]
+be the functor obtained by pull-back along the canonical closed immersion of $k$-schemes  $\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$ \cite[\S 7.6]{BLR}. 
+The following diagram commutes:
+\[
+\begin{tikzcd}
+\GCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota} \dar[swap]{t_{\Res_{k'/k}(G_{k'})}} & \GCiso{G} \dar{t_G} \\
+G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
+\end{tikzcd}
+\]
+\end{proposition}
+
+In the opposite direction, let $\Nm_{k'/k} : G(k') \to G(k)$ be the norm map and consider the group homomorhism:
+\Clifton{How is $\Nm$ defined?}
+\[
+\Nm_{k'/k}^* : G(k)^* \to G(k')^* \qquad \text{defined by}\qquad \chi \mapsto \chi\circ \Nm_{k'/k}.
+\]
+We can also interpret this operation on characters in terms of geometrized characters, as follows.
+
 If $\cs{L} = (\gcs{L}, \mu, \phi)$ is a geometrized character of $G$ we may define
@@
 \begin{proposition}\label{prop:basechange}
- The rule $(\gcs{L}, \mu, \varphi) \mapsto (\gcs{L}, \mu, \varphi\vert_{\Weil{\Fq}})$ 
+ The rule $\nu_{k'/k}: (\gcs{L}, \mu, \varphi) \mapsto (\gcs{L}, \mu, \varphi\vert_{\Weil{\Fq}})$ 
  defines a monoidal functor $\GC(G) \to \GC(G_{k'})$. 
@@
 \begin{tikzcd}[column sep=60]
-\GCiso{G} \rar{\text{ext'n of scalars}} \dar{\trFrob{G}} & \GCiso{G_{k'}} \dar{\trFrob{G_{k'}}} \\
-G(k)^*  \rar{\Nm} & G(k')^*
-%\Hom(G(k), \EEx) \rar{\Nm} & \Hom(G(k'), \EEx).
+\GCiso{G} \rar{\nu_{k'/k}} \dar{\trFrob{G}} & \GCiso{G_{k'}} \dar{\trFrob{G_{k'}}} \\
+G(k)^*  \rar{\Nm_{k'/k}^*} & G(k')^*.
 \end{tikzcd}
@@
 
-\begin{proof}
-\Clifton{This proof is missing. Can David insert it?}
-\end{proof}
+Finally, we explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
+The base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
+decomposes into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
+\[
+(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
+\]
+The component corresponding to the identity element yields a natural inclusion 
+\[
+G' \hookrightarrow (\Res_{k'/k}G')_{k'}
+\]
+of $k'$-schemes.  The definition of base change yields a map of $k$-schemes
+\[
+(\Res_{k'/k}G')_{k'} \to \Res_{k'/k}G'.
+\]
+Consecutive pullback along these maps yields a functor
+\[
+\GC(G') \to \GC(\Res_{k'/k}G').
+\]
+
+\begin{proposition}
+The following diagram commutes:
+\[
+\begin{tikzcd}
+\GCiso{G'} \dar{t_{G'}} \rar & \GCiso{\Res_{k'/k} G'} \dar{t_{\Res_{k'/k} G'}} \\
+ G'(k')^* \rar & (\Res_{k'/k}G')(k)^*
+\end{tikzcd}
+\]
+\end{proposition}
 
@@
 
-\section{Restriction of scalars}
-
-In the opposite direction, there is a canonical closed immersion of $k$-schemes
-$G \hookrightarrow \Res_{k'/k}(G_{k'})$ \cite[\S 7.6]{BLR}.  Pullback yields a functor
-\[
-\GC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota} \GC(G).
-\]
-\begin{proposition} \label{prop:csbe}
-The following diagram commutes, where the bottom map is induced by the inclusion $G(k) \hookrightarrow G(k')$:
-\[
-\begin{tikzcd}
-\GCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota} \dar{t_{\Res_{k'/k}(G_{k'})}} & \GCiso{G} \dar{t_G} \\
-\Hom(G(k'), \EEx) \arrow[two heads]{r} & \Hom(G(k), \EEx).
-\end{tikzcd}
-\]
-\end{proposition}
-
-Now suppose that $G'$ is an abelian group scheme over $k'$, satisfying the conditions of Theorem \ref{thm:snake}.
-There is a canonical isomorphism between $G'(k')$ and $(\Res_{k'/k}G')(k)$;
-we now describe the corresponding functor from
-$\GC(G')$ to $\GC(\Res_{k'/k}G')$.  The base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
-decomposes into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
-\[
-(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
-\]
-The component corresponding to the identity element yields a natural inclusion 
-\[
-G' \hookrightarrow (\Res_{k'/k}G')_{k'}
-\]
-of $k'$-schemes.  The definition of base change yields a map of $k$-schemes
-\[
-(\Res_{k'/k}G')_{k'} \to \Res_{k'/k}G'.
-\]
-Consecutive pullback along these maps yields a functor
-\[
-\GC(G') \to \GC(\Res_{k'/k}G').
-\]
-
-\begin{proposition}
-  Then the following diagram commutes:
-\[
-\begin{tikzcd}
-\GCiso{G'} \dar{t_{G'}} \rar & \GCiso{\Res_{k'/k} G'} \dar{t_{\Res_{k'/k} G'}} \\
- \Hom(G'(k'), \EEx) \rar & \Hom((\Res_{k'/k}G')(k), \EEx)
-\end{tikzcd}
-\]
-\end{proposition}
-
 \section{Application to characters of algebraic tori over local fields}
@@
 
-\section{Base change over the local field}
+\section{Canonicity}
 
@@
 $t_T : \GCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
-In this section we expand on the canonicity of this group isomorphism 
-by showing that it is a natural transformation. We also show
+In this section we expand on the canonicity of this group isomorphism.
 
@@
 \end{proof}
+
+\section{Geometrization of restriction of scalars of local fields}
 

### 2013-08-13 shanghai.tex
Changed canonicity to functoriality, and made a home for the heart of the matter: boxproduct.

@@
 
+\section{Boxproduct}
+
+Let $ \GC(G_1) \boxtimes \GC(G_2)$
+
+\begin{proposition}\label{prop:product}
+The rule ... defines an equivalence of categories 
+\[
+\GC(G_1\times G_2) \to \GC(G_1) \boxtimes \GC(G_2)
+\]
+and 
+\[
+\begin{tikzcd}
+\GCiso{G_1\times G_2} \arrow{r} & \GCiso{G_1} \times \GCiso{G_2}\\
+(G_1\times G_2)(k)^* \arrow{r}  & G_1(k)^* \times G_2(K)^*
+\end{tikzcd}
+\]
+commutes.
+\end{proposition}
+
 \section{Base change over the residue field}\label{sec:basechange}
@@
 
-\section{Canonicity}
-
-We have already seen that the trace of Frobenius defines a canonical isomorphism 
-$t_T : \GCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
-In this section we expand on the canonicity of this group isomorphism.
+\section{Functoriality}
+
+We have already seen that the trace of Frobenius defines a canonical homomorphism $\GCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
+In this section we show that this homomorphism is functorial, in the following sense.
 
 \begin{proposition}
-The isomorphism $t_T : \GCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$ 
-is a natural transformation between the following two contravariant functors 
-from the category of algebraic tori over $K$ to the category of abelian groups: 
+Trace of Frobenius $\GCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$ 
+is a natural transformation between the following two additive functors from the additive category of algebraic tori over $K$ to the category of abelian groups: 
 \begin{enumerate}
-\item $T \mapsto \GCiso{\GN{T}}$
-\item $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
+\item[$F_1$:] $T \mapsto \GCiso{\GN{T}}$;
+\item[$F_2$:] $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
 \end{enumerate}
@@
 
-\Clifton{I think I can prove this proposition without too much difficulty.}
 \begin{proof}
+When combined with the definition of $\GC(\GN{T})$ and Property~\ref{T(K)}, the first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$.
+When further combined with Proposition~\ref{prop:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.
 \end{proof}

### 2013-08-13 shanghai.tex
Fixed the home for boxtimes and re-named it to products.
But the proof that geochars on products are products of geochars is
still under construction

@@
 
+Also throughout the paper, $K$ is a non-Archimedean local field 
+with residue field $\Fq$ and $T$ is an algebraic torus over $K$.
+
 For any group $A$, we will denote by $A^*$ the dual group $\Hom_\text{grp}(A, \EEx)$.
@@
 
-The category of geometrized characters of $G$, denoted by \cdef{$\GC(G)$},
-is defined as follows.  A \cdef{geometrized character on $G$} is a triple
+A \cdef{geometrized character on $G$} is a triple
 $\cs{L}\ceq (\gcs{L},\mu,\phi)$ where:
@@
 \end{enumerate}
-Morphisms in $\GC(G)$ are defined in the natural way:
+Morphisms in the category of geometrized characters of $G$, denoted by \cdef{$\GC(G)$}, are defined in the natural way:
 \begin{enumerate}
@@
 
-\section{Boxproduct}
-
-Let $ \GC(G_1) \boxtimes \GC(G_2)$
+\section{Products}
 
 \begin{proposition}\label{prop:product}
-The rule ... defines an equivalence of categories 
-\[
-\GC(G_1\times G_2) \to \GC(G_1) \boxtimes \GC(G_2)
+The rule $\boxtimes : (\cs{L}_1,\cs{L}_2)\to \cs{L}_1\boxtimes\cs{L}_2$ defines an equivalence of categories 
+\[
+\GC(G_1)\times(G_2) \to \GC(G_1\times G_2)
 \]
@@
 \[
-\begin{tikzcd}
-\GCiso{G_1\times G_2} \arrow{r} & \GCiso{G_1} \times \GCiso{G_2}\\
-(G_1\times G_2)(k)^* \arrow{r}  & G_1(k)^* \times G_2(K)^*
+\begin{tikzcd}[column sep=60]
+\arrow{d}{t_{G_1} \times t_{G_2}} \GCiso{G_1}\times \GCiso{G_2} \arrow{r}{\boxtimes} & \arrow{d}{t_{G_1\times G_2}} \GCiso{G_1\times G_2}\\
+(G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
 \end{tikzcd}
@@
 \end{proposition}
+
+\begin{proof}
+\end{proof}
 
@@
 
-For such a $\Gal(\bFq/\Fq)$-group $G(\bFq)$, we define a category of geometrized characters $\GC(G(\bFq))$.
+For such a $\Gal(\bFq/\Fq)$-group $G(\bFq)$, 
+\Clifton{Re-phrase.}
+we define a category of geometrized characters $\GC(G(\bFq))$.
 An object in $\GC(G(\bFq))$ is given by the data of
-
 \begin{enumerate}
@@
 \end{enumerate}
-
-A morphism $\alpha : \cs{L} \to \cs{L'}$ is given by 
+A morphism $\alpha : \cs{L} \to \cs{L'}$ in $\GC(G(\bFq))$ is given by 
 \begin{enumerate}

### 2013-08-13 shanghai.tex
Finished the proof of functoriality.
With this done, I'm tracing the origin of functoriality back to the
source. Now I wonder if G |--> GC(G) is a stack. I may be spinning out
of control here . . .

@@
 
+\Clifton{Now that I'm working on the functoriality of trace of Frobenius, I  think the source of the functoriality is mainly this: $\GC$ is a stack. I'm thinking about this now.}
+
 \section{The Picard group of geometrized characters}
@@
 a commutative group scheme, smooth and locally of finite type over $\Fq$).
+
+\Clifton{Address functoriality here?}
 
@@
 
-\section{Products}
-
-\begin{proposition}\label{prop:product}
+%\section{Products} 
+We end this section with a simple result on products of geochars, which we will be needed to show that the isomorphism above is functorial.
+
+\begin{lemma}\label{lemma:product}
 The rule $\boxtimes : (\cs{L}_1,\cs{L}_2)\to \cs{L}_1\boxtimes\cs{L}_2$ defines an equivalence of categories 
@@
 commutes.
-\end{proposition}
+\end{lemma}
 
 \begin{proof}
+The only non-trivial part is essential surjectivity.
+Set $G \ceq G_1\times G_1$.
+Let $\cs{L}$ be a geochar on $G$.
+Define $f : G\to G\times G$ by $f(g_1,g_2) = (g_1,e_2,e_1,g_2)$.
+Observe that $m\circ f = \id_G$.
+Then the isomorphism $\mu : m^* \gcs{L} \to \gcs{L}\boxtimes \gcs{L}$ gives an isomorphism
+\[
+f^*\mu : f^* m^* \gcs{L} \to f^*(\gcs{L}\boxtimes \gcs{L}) = f^*p_1^*\gcs{L}\otimes f^* p_2^*\gcs{L}.
+\]
+Observe that $p_1\circ f = r_1 \circ q_1$ and $f_2 = r_2\circ f$ where $p_1 , p_2 : G\times G \to G$ are the usual things and $r_1 : G_1\times G_2 \to G_1$ and $r_2 : G_1\times G_2 \to G_2$ are the obvious things and $q_1 : G_1\to G_1\times G_2$ and  $q_2 : G_2\to G_1\times G_2$ are the usual things.
+Then $f^*p_1^*\gcs{L} = r_1^* q_1^* \gcs{L}$ and $f^*p_2^*\gcs{L} = r_2^* q_2^* \gcs{L}$.
+Now $\cs{L}_1 \ceq r_1^* \cs{L}$ is a geochar on $G_1$ and $\cs{L}_2 \ceq r_2^* \cs{L}$ is a geochar on $G_2$, by Proposition~\ref{prop:pullback}.
+Then
+$ f^*p_1^*\gcs{L}\otimes f^* p_2^*\gcs{L} = r_1^*\gcs{L}_1\otimes r_2^* \gcs{L}_2 = \gcs{L}_1\boxtimes \gcs{L}_2$. In this way, $\mu$ determines an isomorphism
+\[
+\gamma \ceq f^*\mu : \gcs{L} \to  \gcs{L}_1\boxtimes \gcs{L}_2.
+\]
+So $\boxtimes$ is essentially surjective.
 \end{proof}
@@
   the group of characters of $G(\Fq)$, is an isomorphism.
+  \Clifton{Address functoriality, here?}
 \end{theorem}
@@
 In this section we show that this homomorphism is functorial, in the following sense.
+\Clifton{Fold this section into the main result on characters of local tori?}
 
@@
 When combined with the definition of $\GC(\GN{T})$ and Property~\ref{T(K)}, the first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$.
-When further combined with Proposition~\ref{prop:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.
+When further combined with Lemma~\ref{lemma:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.
 \end{proof}

### 2013-08-13 shanghai.tex
Added a paragraph at the end of the snake section to explain why neither finite nor bounded geochars can be used to geometrize characters of G(Fq).

@@
 
+Acknowledgements: Masoud Kamgarpour, Pramod Achar, Hadi Salmasian.
+
 \tableofcontents
@@
 
-\section{The category of geometrized characters}\label{sec:category}
+\section{Geometrized characters}\label{sec:category}
 
@@
 
-\section{Pull-back of geometrized characters}\label{subsection:pullback}
+\section{Pull-back and products}\label{subsection:pullback}
 
@@
 \[
-\gamma \ceq f^*\mu : \gcs{L} \to  \gcs{L}_1\boxtimes \gcs{L}_2.
+f^*\mu : \gcs{L} \to  \gcs{L}_1\boxtimes \gcs{L}_2.
 \]
@@
 
-\section{Base change over the residue field}\label{sec:basechange}
+\section{Base change}\label{sec:basechange}
 
@@
 
-We will see that the full subcategory $\GC_0(G)$ of bounded geometrized characters is a proper subcategory of $\GC(G)$, in general.
-Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to G(\Fq)^*$ to the subgroup $\GCbiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is bounded in $\EEx$, so if $G(\Fq)$ is not finite, then $\GC_0(G) \hookrightarrow\GC(G)$ is not essentially surjective.
+The full subcategory $\GCb(G)$ of bounded geometrized characters is an essentially proper subcategory of $\GC(G)$, in general.
+Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to G(\Fq)^*$ to the subgroup $\GCbiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is bounded in $\EEx$; see Section~\ref{sec:snake}.
 
@@
 
-We will see that the full subcategory $\GC_f(G) \subset \GC_0(G)$ of finite geometrized characters is a proper subcategory, in general.
-Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to G(\Fq)^*$ to the subgroup $\GCfiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is finite in $\EEx$.
+The full subcategory $\GCf(G) \subset \GCb(G)$ of finite geometrized characters is a proper subcategory, in general.
+Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to G(\Fq)^*$ to the subgroup $\GCfiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is finite in $\EEx$; see Section~\ref{sec:snake}.
 
@@
 
-\section{Geometrized characters of commutative \'etale group schemes}
+\section{Commutative \'etale group schemes}
 
@@
 \section{Main result regarding geometrized characters}
+\label{sec:snake}
 
@@
 
-\Clifton{Return to finite and bounded character sheaves, explaining why our definition is the right one. Also explain why we don't think of local systems as representations of a fundamental group.}
+With Theorem~\ref{thm:snake} on hand, we can see why neither bounded geochars nor finite geochars are up to the task of geometrizing characters of $G(\Fq)$ in the generality we need.
+To see this, consider the case when $G$ is the discrete etale group scheme $\ZZ$.
+Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ and let $\cs{L}$ be a geometrized character in the isomorphism class corresponding to the character $\chi : G(\Fq) \to \EEx$ under Theorem~\ref{thm:snake}.
+Then $\trFrob{\cs{L}}(1) = \ell$.
+Suppose $\cs{L}$ was a bounded character sheaf.
+Then the restriction of $\cs{L}$ to the connected component $1\in G$ would be a rank-1 local system on $1$, thus an $\ell$-adic chacter $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with $\rho_1(\Frob{\Fq}) = \ell$.
+But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, while $\rho_1(\pi_1(1,{\bar 1}))$ is not compact (it contains $\ell^\ZZ$).
+Since the Weil sheaf $\gcs{L}$ does not descend to a local system on $G$, the geometric character $\cs{L}$ is not a bounded geometric character.
+We can play the same game with the character $\chi : G(\Fq) \to \EEx$ defined by $\chi(1) = 1+\ell$.
+In this case, the corresponding geometric character $\cs{L}$ is bounded, but not finite.
+This simple example illustrates why the categories $\GCb(G)$ and $\GCf(G)$ are inadequate to geometrize characters of $G(\Fq)$.
 

### 2013-08-13 shanghai.tex
Stuff

@@
 \renewcommand{\baselinestretch}{1.2}
-\usepackage[notcite,color]{showkeys}
+%\usepackage[notcite,color]{showkeys}
 \usepackage{hyperref}
@@
 
-\newcommand{\cdef}[1]{{{\color{blue}#1}\index{#1}}} 
+\newcommand{\cdef}[1]{ {#1}\index{#1} } 
 \newcommand{\sheafHom}{{\mathscr{H}\hskip-4pt{\it o}\hskip-2pt{\it m}}}
@@
 
-\section{Notation}
+\Clifton{Declare definitions - about 10 of them.}
+
+\part{Smooth commutative group schemes lft over finite fields}
 
@@
 
-Also throughout the paper, $K$ is a non-Archimedean local field 
-with residue field $\Fq$ and $T$ is an algebraic torus over $K$.
-
 For any group $A$, we will denote by $A^*$ the dual group $\Hom_\text{grp}(A, \EEx)$.
@@
 
-A \cdef{geometrized character on $G$} is a triple
+\begin{definition}\label{def:GC}
+A \emph{geometrized character on $G$} is a triple
 $\cs{L}\ceq (\gcs{L},\mu,\phi)$ where:
 \begin{enumerate}
-\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a constructible $\ell$-adic sheaf on  (the \'etale site of) $\bG$, locally constant of rank-$1$ on each connected component of $\bG$;
+\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a rank-$1$ $\ell$-adic local system on $\bG$;
 \labitem{(CS.1)}{CS.1} $\mu: \bm^* \gcs{L} \to \LxL$
@@
 \end{enumerate}
-Morphisms in the category of geometrized characters of $G$, denoted by \cdef{$\GC(G)$}, are defined in the natural way:
+In short, a geometrized character on $G$  is a rank-$1$ Weil local system $(\gcs{L},\phi)$ on $G$ equipped with an isomorphism $m^* (\gcs{L},\phi) \to (\gcs{L},\phi)\boxtimes (\gcs{L},\phi)$. 
+Morphisms in the category of geometrized characters of $G$, denoted by $\GC(G)$, are defined in the natural way:
 \begin{enumerate}
@@
   $\cs{L'} = (\gcs{L'},\mu',\phi')$ are geometrized characters of $G$ then
-  $\Hom_{\GC(G)}(\cs{L},\cs{L'})$ is the set of morphisms $\alpha : \gcs{L} \to \gcs{L'}$
+  $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\alpha : \gcs{L} \to \gcs{L'}$
   of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
@@
 \end{enumerate}
+\end{definition}
 
@@
 
-\section{The Picard group of geometrized characters}
+\section{Trace of Frobenius}\label{sec:Frob}
 
 %\begin{proposition}\label{tensor}
-The category $\GC(G)$ of geometrized characters of $G$ is a rigid monoidal
-category [insert reference] under
+The category $\GC(G)$ of geometrized characters of $G$ is a rigid symmetric monoidal category \Clifton{I still haven't found a good reference for this!} under
 $\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$
 with duals given by applying the functor 
-\Clifton{Should this be $\sheafHom(\ - \ ,\EE)$?} $\sheafHom(\ - \ ,(\EE)_{\bG})$ (sheaf hom) to
+$\sheafHom(\ - \ ,\EE)$ (sheaf hom) to
 conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}.
@@
 structure on the set $\GCiso{G}$ of isomorphism classes in
-$\GC(G)$; we refer to this as the \cdef{Picard group of character
-sheaves} on $G$.\footnote{See {\tt http://ncatlab.org/nlab/show/Picard+group}.}
-The main result in this paper is the determination of the Picard group of geometrized characters of $G$, when the geometric component group of $G$ is finitely generated.
-
-\section{Trace of Frobenius}\label{sec:Frob}
+$\GC(G)$.
 
@@
 
-\Clifton{Address functoriality here?}
+\Clifton{Address functoriality here? Yes, but put proof at the end of the next section.}
+
+In this paper we $\GCiso{G} \iso G(\Fq)^*$ when the geometric component group of $G$ is finitely generated; see Theorem~\ref{thm:snake}. We also shows that this isomorphism is canonical; see
 
@@
 \]
-be the functor obtained by pull-back along the canonical closed immersion of $k$-schemes  $\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$ \cite[\S 7.6]{BLR}. 
+be the functor obtained by pull-back along the canonical closed immersion of $k$-schemes  $\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$ \cite{BLR}*{\S 7.6}. 
 The following diagram commutes:
@@
   $\cs{L} \otimes \cs{L}'$.  The three versions of \eqref{t} for $\cs{L}, \cs{L'}$ and $\cs{L} \otimes \cs{L}'$ imply that
-  $\tau_{\cs{L} \otimes \cs{L}'}(\Frob{k}) = \tau_\cs{L}(\Frob{k}) \tau_{\cs{L}'}(\Frob{k})$.
+  $\tau_{\cs{L} \otimes \cs{L}'}(\Frob{k}) = \tau_\cs{L}(\Frob{k}) \tau_{\cs{L}'}(\Frob{k})$, so \eqref{pich1} is a group homomorphism.
+\Clifton{I'm working on this.}
 \end{proof}
@@
   product of Dedekind domains.  Therefore $X$ decomposes into a direct
-  sum of cyclic $\ZZ[\Gamma_m]$-modules \cite[?]{Brandal}, each of the
+  sum of cyclic $\ZZ[\Gamma_m]$-modules \cite{Brandal}*{?}, each of the
   form $\ZZ[\Gamma_m] / I$ for some ideal $I \subset \ZZ[\Gamma_m]$.
@@
 We can play the same game with the character $\chi : G(\Fq) \to \EEx$ defined by $\chi(1) = 1+\ell$.
-In this case, the corresponding geometric character $\cs{L}$ is bounded, but not finite.
+In this case, the corresponding geometric character $\cs{L}$ is bounded but not finite, since $1+\ell$ is not a root of unity.
 This simple example illustrates why the categories $\GCb(G)$ and $\GCf(G)$ are inadequate to geometrize characters of $G(\Fq)$.
 
-\section{Application to characters of algebraic tori over local fields}
+\part{Application to characters of algebraic tori over local fields}
+
+Also throughout the paper, $K$ is a non-Archimedean local field 
+with residue field $\Fq$ and $T$ is an algebraic torus over $K$.
+
+\section{Greenberg of Neron}
+\label{sec:GN}
 
@@
 
+\Clifton{Motivate with comments about LLC for tori. Draw triangle. Reduction to GL(1) via induced tori. Comment about Japanese work. Comment about pro-quasi-algebraic. Combine with next section.}
+
 We have already seen that the trace of Frobenius defines a canonical homomorphism $\GCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
@@
 \David{We should add a discussion of why we care about the transfer principle.}
+
+\Clifton{Work on motivation.}
 
@@
 
-\bib{Deligne:Weil2}{article}{
-   author={Deligne, Pierre},
-   title={La conjecture de Weil. II},
-%   language={French},
-   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
-   number={52},
-   date={1980},
-   pages={137--252},
-%   issn={0073-8301},
-%   review={\MR{601520 (83c:14017)}},
-}
-
 \bib{SGA7.2}{book}{

### 2013-08-13 shanghai.tex
more stuff

@@
 In short, a geometrized character on $G$  is a rank-$1$ Weil local system $(\gcs{L},\phi)$ on $G$ equipped with an isomorphism $m^* (\gcs{L},\phi) \to (\gcs{L},\phi)\boxtimes (\gcs{L},\phi)$.
+
 Morphisms in the category of geometrized characters of $G$, denoted by $\GC(G)$, are defined in the natural way:
@@
 $\GC(G)$.
-
-Let $\cs{L}$ be a geometrized character of $G$. Every $g\in G(\Fq)$
+Our main result regarding geometrized character sheaves on $G$ is the determination of $\GCiso{G}$ under the hypothesis that the component group scheme for $G$ is geometrically finitely generated; see Theorem~\ref{thm:snake}.
+To do this, we use the trace of Frobenius.
+
+\begin{definition}
+Let $(\gcs{L},\phi)$ be a Weil sheaf on $G$. on constructible $\ell$-adic sheaf on $\bG$. Every $g\in G(\Fq)$
 determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$ and
-therefore an automorphism $\phi_{\bg}$ of $\gcs{L}_{\bg}$. Note
-that $\Aut_{\EE}(\gcs{L}_{\bg}) \iso \EEx$, canonically. The isomorphism $\mu : \bm^* \gcs{L} \to \LxL$
+therefore an automorphism $\phi_{\bg}$ of $\gcs{L}_{\bg}$. The \emph{trace of Frobenius} of $(\gcs{L},\phi)$ at $g\in G(\Fq)$ is 
+\[
+\trFrob{(\gcs{L},\phi)}(g) \ceq \trace(\phi_{\bg}, \gcs{L}_{\bg}).
+\]
+If $\cs{L} = (\gcs{L},\mu,\phi)$ is a geochar, then we will abbreviate write $\trFrob{\cs{L}}$ for $\trFrob{(\gcs{L},\phi)}$
+\end{definition}
+
+The isomorphism $\mu : \bm^* \gcs{L} \to \LxL$
 guarantees that the function $\trFrob{\cs{L}} : G(\Fq)\to \EEx$,

### 2013-08-13 shanghai.tex
Working on introduction

--- 2013-08-13 shanghai.tex
@@
 Let $G$ be a smooth commutative group scheme locally of finite
-type over $\Fq$; $G$ need not be reductive, connected, nor of
+type over $\Fq$; $G$ need not be reductive, connected, or of
 finite type over $\Fq$. Fix a prime $\ell$ that does not divide
-$q$. A geometrized character of $G$ is a triple $\cs{L}\ceq
-(\gcs{L},\mu,\phi)$ where $\gcs{L}$ is a constructible $\ell$-adic sheaf
-$\gcs{L}$ on the \'etale site of $\bG \ceq G \times_{\Spec\Fq}
-\Spec{\bFq}$, locally constant of rank-$1$ on every connected
-component of $\bG$, equipped with an isomorphism $\mu: m^*
-\gcs{L} \to \LxL$, where $m : \GxG \to G$ is
-the group operation for $G$, and an isomorphism $F : \Frob{G}^*
-\gcs{L} \to \gcs{L}$, where $\Frob{G}$ is the Frobenius automorphism
-on $\bG$, satisfying natural compatibility conditions with $\mu$;
-these compatibility conditions are explained below.
+$q$, write $m : \GxG \to G$ for the multiplication morphism,
+$\bG$ for the base change of $G$ to $\bFq$ and
+$\Frob{G} : \bG \to \bG$ for the Frobenius automorphism.
+A geometrized character of $G$ is a triple $\cs{L}\ceq
+(\gcs{L},\mu,\phi)$ where $\gcs{L}$ is a rank-$1$ local system on $\bG$ and $\mu: m^*
+\gcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gcs{L} \to \gcs{L}$ are isomorphisms;
+$\mu$ and $\phi$ are required to satisfy natural conditions explained below.
 
@@
 positive integer $d$, let $\GN{T}_d$ be the Greenberg transform of
-$\TT \otimes \OK/\pK^d$; the commutative group scheme $\GN{T}_d$
+$\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^d}$; the commutative group scheme $\GN{T}_d$
 plays the r\^{o}le of $G$, above.
@@
 $\GN{T}_d$ and the group of characters $T(K) \to \EEx$ of
-depth at most $d$.  Since these isomorphisms are compatible with
+depth less than $d$.  Since these isomorphisms are compatible with
 respect to $d$, we also .....  \David{I'll do this when we're closer to being finished.}  
@@
 
-Acknowledgements: Masoud Kamgarpour, Pramod Achar, Hadi Salmasian.
-
 \tableofcontents
@@
 
-\section{Geometrized characters}\label{sec:category}
+\section{The category of geometrized characters}\label{sec:category}
 
@@
 
-\section{Pull-back and products}\label{subsection:pullback}
+\section{Pull-back of geometrized characters}\label{subsection:pullback}
 
@@
 \[
-f^*\mu : \gcs{L} \to  \gcs{L}_1\boxtimes \gcs{L}_2.
+\gamma \ceq f^*\mu : \gcs{L} \to  \gcs{L}_1\boxtimes \gcs{L}_2.
 \]
@@
 
-\section{Base change}\label{sec:basechange}
+\section{Base change over the residue field}\label{sec:basechange}
 
@@
 
-The full subcategory $\GCb(G)$ of bounded geometrized characters is an essentially proper subcategory of $\GC(G)$, in general.
-Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to G(\Fq)^*$ to the subgroup $\GCbiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is bounded in $\EEx$; see Section~\ref{sec:snake}.
+We will see that the full subcategory $\GC_0(G)$ of bounded geometrized characters is a proper subcategory of $\GC(G)$, in general.
+Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to G(\Fq)^*$ to the subgroup $\GCbiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is bounded in $\EEx$, so if $G(\Fq)$ is not finite, then $\GC_0(G) \hookrightarrow\GC(G)$ is not essentially surjective.
 
@@
 
-The full subcategory $\GCf(G) \subset \GCb(G)$ of finite geometrized characters is a proper subcategory, in general.
-Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to G(\Fq)^*$ to the subgroup $\GCfiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is finite in $\EEx$; see Section~\ref{sec:snake}.
+We will see that the full subcategory $\GC_f(G) \subset \GC_0(G)$ of finite geometrized characters is a proper subcategory, in general.
+Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to G(\Fq)^*$ to the subgroup $\GCfiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is finite in $\EEx$.
 
@@
 
-\section{Commutative \'etale group schemes}
+\section{Geometrized characters of commutative \'etale group schemes}
 
@@
 \section{Main result regarding geometrized characters}
-\label{sec:snake}
 
@@
 
-With Theorem~\ref{thm:snake} on hand, we can see why neither bounded geochars nor finite geochars are up to the task of geometrizing characters of $G(\Fq)$ in the generality we need.
-To see this, consider the case when $G$ is the discrete etale group scheme $\ZZ$.
-Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ and let $\cs{L}$ be a geometrized character in the isomorphism class corresponding to the character $\chi : G(\Fq) \to \EEx$ under Theorem~\ref{thm:snake}.
-Then $\trFrob{\cs{L}}(1) = \ell$.
-Suppose $\cs{L}$ was a bounded character sheaf.
-Then the restriction of $\cs{L}$ to the connected component $1\in G$ would be a rank-1 local system on $1$, thus an $\ell$-adic chacter $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with $\rho_1(\Frob{\Fq}) = \ell$.
-But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, while $\rho_1(\pi_1(1,{\bar 1}))$ is not compact (it contains $\ell^\ZZ$).
-Since the Weil sheaf $\gcs{L}$ does not descend to a local system on $G$, the geometric character $\cs{L}$ is not a bounded geometric character.
-We can play the same game with the character $\chi : G(\Fq) \to \EEx$ defined by $\chi(1) = 1+\ell$.
-In this case, the corresponding geometric character $\cs{L}$ is bounded, but not finite.
-This simple example illustrates why the categories $\GCb(G)$ and $\GCf(G)$ are inadequate to geometrize characters of $G(\Fq)$.
+\Clifton{Return to finite and bounded character sheaves, explaining why our definition is the right one. Also explain why we don't think of local systems as representations of a fundamental group.}
 

### 2013-08-13 shanghai.tex
Quasicharacter sheaves

@@
 \newcommand{\dualcs}[1]{\cs{#1}^\dagger}
-\newcommand{\GC}{{\mathcal{G\hskip-0.8pt C}}}
-\newcommand{\GCb}{{\GC_0}}
-\newcommand{\GCf}{{\GC_f}}
-\newcommand{\GCiso}[1]{\GC(#1)_{/\textit{iso}}}
-\newcommand{\GCbiso}[1]{\GCb(#1)_{/\text{iso}}}
-\newcommand{\GCfiso}[1]{\GCf(#1)_{/\text{iso}}}
+\newcommand{\QC}{{\mathcal{Q\hskip-0.8pt C}}}
+\newcommand{\QCb}{{\QC_0}}
+\newcommand{\QCf}{{\QC_f}}
+\newcommand{\QCiso}[1]{\QC(#1)_{/\textit{iso}}}
+\newcommand{\QCbiso}[1]{\QCb(#1)_{/\text{iso}}}
+\newcommand{\QCfiso}[1]{\QCf(#1)_{/\text{iso}}}
 \newcommand{\Lgroup}[1]{{\,^L\hskip-1pt{#1}}}
@@
 \begin{abstract}
-  We introduce and study the category of geometrized characters of smooth commutative
+  We introduce and study the category of quasicharacter sheaves on smooth commutative
   group schemes $G$ locally of finite type over finite fields
@@
   is finitely-generated, we show that the group of isomorphism classes
-  of geometrized characters of $G$ is canonically isomorphic to the group
+  of quasicharacter sheaves on $G$ is canonically isomorphic to the group
   of characters of $G(\Fq)$. We use this result to exhibit an
   isomorphism between admissible characters of $T(K)$ and isomorphism
-  classes of geometrized characters of the Greenberg transform of the Néron
+  classes of quasicharacter sheaves on the Greenberg transform of the Néron
   model of $T$, where $K$ is any non-Archimdean local field and $T$ is
@@
 %\noindent
-What is a geometrized character?
+What is a quasicharacter sheaf?
 Let $G$ be a smooth commutative group scheme locally of finite
@@
 $\Frob{G} : \bG \to \bG$ for the Frobenius automorphism.
-A geometrized character of $G$ is a triple $\cs{L}\ceq
+A quasicharacter sheaf of $G$ is a triple $\cs{L}\ceq
 (\gcs{L},\mu,\phi)$ where $\gcs{L}$ is a rank-$1$ local system on $\bG$ and $\mu: m^*
@@
 
-Geometrized characters of $G$ form a category, denoted by $\GC(G)$. In
-fact, $\GC(G)$ is a rigid symmetric monoidal category, so isomorphism
-classes of geometrized characters of $G$ form a group, denoted by
-$\GCiso{G}$; this is the Picard group of the category of
-geometrized characters of $G$. Our application of geometrized characters to
+Quasicharacter sheaves of $G$ form a category, denoted by $\QC(G)$. In
+fact, $\QC(G)$ is a rigid symmetric monoidal category, so isomorphism
+classes of quasicharacter sheaves on $G$ form a group, denoted by
+$\QCiso{G}$; this is the Picard group of the category of
+quasicharacter sheaves on $G$. Our application of quasicharacter sheaves to
 characters of algebraic tori over non-Archimedean local fields rests
-on finding the Picard group of geometrized characters of $G$, 
+on finding the Picard group of quasicharacter sheaves on $G$, 
 for all smooth commutative group schemes $G$, locally of finite type over $\Fq$, 
@@
 \[
-\GCiso{\GN{T}_d} 
+\QCiso{\GN{T}_d} 
 \iso
@@
 \] 
-between the Picard group of the category of geometrized characters on
+between the Picard group of the category of quasicharacter sheaves on
 $\GN{T}_d$ and the group of characters $T(K) \to \EEx$ of
@@
 %be), we arrive at a model for the group of quasi-characters of
-%$K^\times$: the monoidal category of geometrized characters of the
+%$K^\times$: the monoidal category of quasicharacter sheaves on the
 %Greenberg transform of the Neron model of
@@
 
-In this paper we show that the monoidal category of geometrized characters
+In this paper we show that the monoidal category of quasicharacter sheaves
 on the Greenberg transform of the locally finite type Neron model of
@@
 
-\section{Geometrized characters}\label{sec:category}
+\section{Quasicharacter sheaves}\label{sec:category}
 
 \begin{definition}\label{def:GC}
-A \emph{geometrized character on $G$} is a triple
+A \emph{quasicharacter sheaf on $G$} is a triple
 $\cs{L}\ceq (\gcs{L},\mu,\phi)$ where:
@@
 \end{enumerate}
-In short, a geometrized character on $G$  is a rank-$1$ Weil local system $(\gcs{L},\phi)$ on $G$ equipped with an isomorphism $m^* (\gcs{L},\phi) \to (\gcs{L},\phi)\boxtimes (\gcs{L},\phi)$.
-
-Morphisms in the category of geometrized characters of $G$, denoted by $\GC(G)$, are defined in the natural way:
+In short, a quasicharacter sheaf on $G$  is a rank-$1$ Weil local system $(\gcs{L},\phi)$ on $G$ equipped with an isomorphism $m^* (\gcs{L},\phi) \to (\gcs{L},\phi)\boxtimes (\gcs{L},\phi)$.
+
+Morphisms in the category of quasicharacter sheaves on $G$, denoted by $\QC(G)$, are defined in the natural way:
 \begin{enumerate}
 \labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,\phi)$ and
-  $\cs{L'} = (\gcs{L'},\mu',\phi')$ are geometrized characters of $G$ then
+  $\cs{L'} = (\gcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$ then
   $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\alpha : \gcs{L} \to \gcs{L'}$
@@
 %\begin{remark} \label{rem:CS-action}
-The rule $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$ defines a forgetful functor from geometrized characters of $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{Deligne:Weil2}*{Def.~1.1.10 (i)}.
+The rule $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$ defines a forgetful functor from quasicharacter sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{Deligne:Weil2}*{Def.~1.1.10 (i)}.
 
@@
 The pair $(\gcs{L},\varphi_1)$ fails to fulfill the requirements of \cite{SGA4.5}*{Expos\'e XIII,~1.1} only because $\Weil{\Fq}$ is profinite.
-This fact goes to the heart of the notion of a Weil sheaf and is one of the essential aspects of our definition of $\GC(G)$.
+This fact goes to the heart of the notion of a Weil sheaf and is one of the essential aspects of our definition of $\QC(G)$.
 %\end{remark}
 
-\Clifton{Now that I'm working on the functoriality of trace of Frobenius, I  think the source of the functoriality is mainly this: $\GC$ is a stack. I'm thinking about this now.}
+\Clifton{Now that I'm working on the functoriality of trace of Frobenius, I  think the source of the functoriality is mainly this: $\QC$ is a stack. I'm thinking about this now.}
 
@@
 %\begin{proposition}\label{tensor}
-The category $\GC(G)$ of geometrized characters of $G$ is a rigid symmetric monoidal category \Clifton{I still haven't found a good reference for this!} under
+The category $\QC(G)$ of quasicharacter sheaves on $G$ is a rigid symmetric monoidal category \Clifton{I still haven't found a good reference for this!} under
 $\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$
@@
 %\end{proposition}
-(The category of characters sheaves on $G$ is not abelian, so $\GC(G)$
+(The category of characters sheaves on $G$ is not abelian, so $\QC(G)$
 is not a tensor category in the sense of \cite{Deligne:tensorielles}.)
@@
 %
-This rigid monoidal category structure for $\GC(G)$ puts a group
-structure on the set $\GCiso{G}$ of isomorphism classes in
-$\GC(G)$.
-Our main result regarding geometrized character sheaves on $G$ is the determination of $\GCiso{G}$ under the hypothesis that the component group scheme for $G$ is geometrically finitely generated; see Theorem~\ref{thm:snake}.
+This rigid monoidal category structure for $\QC(G)$ puts a group
+structure on the set $\QCiso{G}$ of isomorphism classes in
+$\QC(G)$.
+Our main result regarding quasicharacter sheaf sheaves on $G$ is the determination of $\QCiso{G}$ under the hypothesis that the component group scheme for $G$ is geometrically finitely generated; see Theorem~\ref{thm:snake}.
 To do this, we use the trace of Frobenius.
@@
 (pointwise multiplication of functions) and that $\trFrob{\cs{L}} = \trFrob{\cs{L'}}$
-if $\cs{L} \iso \cs{L'}$ in $\GC(G)$. In this way we obtain a group homomorphism
-\[
-\cdef{\trFrob{G}} : \GCiso{G} \longrightarrow G(\Fq)^*,%\Hom_\text{grp}(G(\Fq),\EEx),
+if $\cs{L} \iso \cs{L'}$ in $\QC(G)$. In this way we obtain a group homomorphism
+\[
+\cdef{\trFrob{G}} : \QCiso{G} \longrightarrow G(\Fq)^*,%\Hom_\text{grp}(G(\Fq),\EEx),
 \qquad \text{defined by}\qquad \cs{L} \mapsto \trFrob{\cs{L}},
 \]
-from the Picard group of geometrized characters of $G$ to the character group of $G(\Fq)$.
+from the Picard group of quasicharacter sheaves on $G$ to the character group of $G(\Fq)$.
 
@@
 of $G$ is finitely-generated then the trace of Frobenius defines an
-isomorphism from the Picard group of geometrized characters $G$ to the
+isomorphism from the Picard group of quasicharacter sheaves $G$ to the
 group of characters of $G(\Fq)$ (here, as throughout the paper, $G$ is
@@
 
-In this paper we $\GCiso{G} \iso G(\Fq)^*$ when the geometric component group of $G$ is finitely generated; see Theorem~\ref{thm:snake}. We also shows that this isomorphism is canonical; see
+In this paper we $\QCiso{G} \iso G(\Fq)^*$ when the geometric component group of $G$ is finitely generated; see Theorem~\ref{thm:snake}. We also shows that this isomorphism is canonical; see
 
@@
   $(\gcs{L},\mu,\phi) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
-  defines a monoidal functor $f^* : \GC(G) \to \GC(H)$ such that
+  defines a monoidal functor $f^* : \QC(G) \to \QC(H)$ such that
   \[
   \begin{tikzcd}[row sep=20, column sep=30]
-   \GCiso{G} \rar{f^*} \arrow[swap]{d}{\trFrob{G}} & \GCiso{H} \dar{t_H} \\
+   \QCiso{G} \rar{f^*} \arrow[swap]{d}{\trFrob{G}} & \QCiso{H} \dar{t_H} \\
    G(\Fq)^* \rar & H(\Fq)^*
@@
 \begin{proof}
-  Let $\cs{L}$ be a geometrized character of $G$. We start by showing that
+  Let $\cs{L}$ be a quasicharacter sheaf of $G$. We start by showing that
   $\bf^*\gcs{L}$ is locally constant on connected components of
@@
   for the restriction of $f$ to $\bH^j$.  Since $\cs{L}$
-  is a geometrized character, $\gcs{L}$ is locally constant on the connect
+  is a quasicharacter sheaf, $\gcs{L}$ is locally constant on the connect
   components of $\bG$; thus, there is a finite etale covering
@@
   To see that $(\gcs{L},\mu,\phi) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
-  defines a functor $f^* : \GC(G) \to \GC(H)$ one applies the functors $\bf^*$ and
+  defines a functor $f^* : \QC(G) \to \QC(H)$ one applies the functors $\bf^*$ and
   $\bf^*\tight{1}{\times}{1}\bf^*$ to \ref{CS.3} and argue as
   above. It follows from the fact that sheaf hom commutes with these
-  functors that $f^* : \GC(G) \to \GC(H)$ is a monoidal functor.
+  functors that $f^* : \QC(G) \to \QC(H)$ is a monoidal functor.
 %
-  The fact that the functor $f^* : \GC(G) \to \GC(H)$ commutes with
+  The fact that the functor $f^* : \QC(G) \to \QC(H)$ commutes with
   the trace of Frobenius, in the sense above, follows immediately from
@@
 \begin{tikzcd}
-\GC(0) \rar & \GC(\pi_0(G)) \rar & \GC(G) \rar & \GC(G^0) \rar & \GC(0)
+\QC(0) \rar & \QC(\pi_0(G)) \rar & \QC(G) \rar & \QC(G^0) \rar & \QC(0)
 \end{tikzcd}
@@
 \begin{tikzcd}
-\GCiso{0} \rar & \GCiso{\pi_0(G)} \rar & \GCiso{G} \rar & \GCiso{G^0} \rar & \GCiso{0}.
+\QCiso{0} \rar & \QCiso{\pi_0(G)} \rar & \QCiso{G} \rar & \QCiso{G^0} \rar & \QCiso{0}.
 \end{tikzcd}
 \end{equation}
-It is easy to see that $\GCiso{0}$ is trivial. In this paper we will find $\GCiso{G^0}$ and $\GCiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; 
+It is easy to see that $\QCiso{0}$ is trivial. In this paper we will find $\QCiso{G^0}$ and $\QCiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; 
 the snake lemma will then allow us to show
 \[
-\GCiso{G} \iso G(\Fq)^*,%\Hom_\text{grp}(G(\Fq),\EE^\times),
+\QCiso{G} \iso G(\Fq)^*,%\Hom_\text{grp}(G(\Fq),\EE^\times),
 \]
@@
 \[
-\GC(G_1)\times(G_2) \to \GC(G_1\times G_2)
+\QC(G_1)\times(G_2) \to \QC(G_1\times G_2)
 \]
@@
 \begin{tikzcd}[column sep=60]
-\arrow{d}{t_{G_1} \times t_{G_2}} \GCiso{G_1}\times \GCiso{G_2} \arrow{r}{\boxtimes} & \arrow{d}{t_{G_1\times G_2}} \GCiso{G_1\times G_2}\\
+\arrow{d}{t_{G_1} \times t_{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes} & \arrow{d}{t_{G_1\times G_2}} \QCiso{G_1\times G_2}\\
 (G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
@@
 
-When using geometrized characters to study characters, it is useful to understand
-how geometrized characters behave under change of fields.
+When using quasicharacter sheaves to study characters, it is useful to understand
+how quasicharacter sheaves behave under change of fields.
 Let $k'$ be a finite extension of $k$. Then $k\to k'$ induces a group homomorphism $i_{k'/k} : G(k) \hookrightarrow G(k')$ which, in turn, gives
@@
 \]
-We can interpret this operation on characters in terms of geometrized characters, as follows.
+We can interpret this operation on characters in terms of quasicharacter sheaves, as follows.
 %
@@
 \[
-\GC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \GC(G)
+\QC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \QC(G)
 \]
@@
 \begin{tikzcd}
-\GCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota} \dar[swap]{t_{\Res_{k'/k}(G_{k'})}} & \GCiso{G} \dar{t_G} \\
+\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota} \dar[swap]{t_{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{t_G} \\
 G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
@@
 \]
-We can also interpret this operation on characters in terms of geometrized characters, as follows.
-
-If $\cs{L} = (\gcs{L}, \mu, \phi)$ is a geometrized character of $G$ we may define
-a geometrized character $\cs{L}' = (\gcs{L}, \mu, \phi_{k'})$ on 
+We can also interpret this operation on characters in terms of quasicharacter sheaves, as follows.
+
+If $\cs{L} = (\gcs{L}, \mu, \phi)$ is a quasicharacter sheaf of $G$ we may define
+a quasicharacter sheaf $\cs{L}' = (\gcs{L}, \mu, \phi_{k'})$ on 
 $G_{k'}\ceq G\times_{\Spec{k}} \Spec{k'}$ by setting
@@
  The rule $\nu_{k'/k}: (\gcs{L}, \mu, \varphi) \mapsto (\gcs{L}, \mu, \varphi\vert_{\Weil{\Fq}})$ 
- defines a monoidal functor $\GC(G) \to \GC(G_{k'})$. 
+ defines a monoidal functor $\QC(G) \to \QC(G_{k'})$. 
  Moreover, the following diagram commutes, 
- where the top map is induced by $\GC(G) \to \GC(G_{k'})$ 
+ where the top map is induced by $\QC(G) \to \QC(G_{k'})$ 
  and the bottom map is induced by the norm $G(k') \rightarrow G(k)$:
@@
 \begin{tikzcd}[column sep=60]
-\GCiso{G} \rar{\nu_{k'/k}} \dar{\trFrob{G}} & \GCiso{G_{k'}} \dar{\trFrob{G_{k'}}} \\
+\QCiso{G} \rar{\nu_{k'/k}} \dar{\trFrob{G}} & \QCiso{G_{k'}} \dar{\trFrob{G_{k'}}} \\
 G(k)^*  \rar{\Nm_{k'/k}^*} & G(k')^*.
@@
 \[
-\GC(G') \to \GC(\Res_{k'/k}G').
+\QC(G') \to \QC(\Res_{k'/k}G').
 \]
@@
 \begin{tikzcd}
-\GCiso{G'} \dar{t_{G'}} \rar & \GCiso{\Res_{k'/k} G'} \dar{t_{\Res_{k'/k} G'}} \\
+\QCiso{G'} \dar{t_{G'}} \rar & \QCiso{\Res_{k'/k} G'} \dar{t_{\Res_{k'/k} G'}} \\
  G'(k')^* \rar & (\Res_{k'/k}G')(k)^*
@@
 
-\section{Bounded geometrized characters}\label{sec:bounded}
-
-Let \cdef{$\GCb(G)$} be the category of pairs $(\cs{L}_0,\mu_0)$ 
+\section{Bounded quasicharacter sheaves}\label{sec:bounded}
+
+Let \cdef{$\QCb(G)$} be the category of pairs $(\cs{L}_0,\mu_0)$ 
 where $\cs{L}_0$ is a constructible $\ell$-adic sheaf on $G$, 
@@
 satisfying the analogue of Condition~\ref{CS.1} on $G$; 
-morphisms in $\GCf(G)$ are defined as in (the second part of) Condition~\ref{CS.2}. 
-This is the category of \cdef{bounded geometrized characters} on $G$. 
+morphisms in $\QCf(G)$ are defined as in (the second part of) Condition~\ref{CS.2}. 
+This is the category of \cdef{bounded quasicharacter sheaves} on $G$. 
 \Clifton{Should this be $\sheafHom(\cs{L}_0,\EE)$?}
@@
 \begin{proposition}
-$\GCb(G)$ is (equivalent to) a full subcategory of $\GC(G)$.
+$\QCb(G)$ is (equivalent to) a full subcategory of $\QC(G)$.
 \end{proposition}
@@
  Let $b_G : {\bar G} \to G$ be the pull-back of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Let $(\cs{L}_0,\mu_0)$ be a bounded geometrized character of $G$. 
+ Let $(\cs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf of $G$. 
  Then $\cs{L}_0$ is, in particular, an $\ell$-adic constructible sheaf on $G$. 
@@
  Moreover, $\phi$ is compatible with $\mu$ in the sense of Condition~\ref{CS.3}.
- It follows that functor $(\cs{L}_0,\mu_0) \mapsto (b_G^*\cs{L}_0,b_{G\times G}^* \mu_0, \phi)$, denoted by  $B_G^*: \GCb(G) \hookrightarrow \GC(G)$ below, is full and faithful.
+ It follows that functor $(\cs{L}_0,\mu_0) \mapsto (b_G^*\cs{L}_0,b_{G\times G}^* \mu_0, \phi)$, denoted by  $B_G^*: \QCb(G) \hookrightarrow \QC(G)$ below, is full and faithful.
 \end{proof}
 
-The full subcategory $\GCb(G)$ of bounded geometrized characters is an essentially proper subcategory of $\GC(G)$, in general.
-Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to G(\Fq)^*$ to the subgroup $\GCbiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is bounded in $\EEx$; see Section~\ref{sec:snake}.
-
-\section{Finite geometrized characters}\label{sec:finite}
-
- %In this section we describe a full subcategory of $\GCb(G)$
- %which will illuminate some features of $\GCb(G)$ and also play a role in some arguments below.
-
-To define the category of finite geometrized characters we must work a bit harder.
+The full subcategory $\QCb(G)$ of bounded quasicharacter sheaves is an essentially proper subcategory of $\QC(G)$, in general.
+Indeed, it follows from our main result regarding quasicharacter sheaves, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ to the subgroup $\QCbiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is bounded in $\EEx$; see Section~\ref{sec:snake}.
+
+\section{Finite quasicharacter sheaves}\label{sec:finite}
+
+ %In this section we describe a full subcategory of $\QCb(G)$
+ %which will illuminate some features of $\QCb(G)$ and also play a role in some arguments below.
+
+To define the category of finite quasicharacter sheaves we must work a bit harder.
 Consider the following category \cdef{$C(G)$}:
@@
 
-Let \cdef{$C_1(G)$} be the rigid monoidal full subcategory of $C(G)$ consisting of objects $(f,\psi)$ such that $\psi$ is a one-dimensional representation and let \cdef{$\GCf(G)$} be the localisation of $C_1(G)$ at weak isomorphisms; this is the rigid symmetric monoidal category of \cdef{finite geometrized characters} of $G$.
+Let \cdef{$C_1(G)$} be the rigid monoidal full subcategory of $C(G)$ consisting of objects $(f,\psi)$ such that $\psi$ is a one-dimensional representation and let \cdef{$\QCf(G)$} be the localisation of $C_1(G)$ at weak isomorphisms; this is the rigid symmetric monoidal category of \cdef{finite quasicharacter sheaves} of $G$.
 
 \begin{proposition}\label{prop:bounded}
- $\GCf(G)$ is (equivalent to) a full subcategory of $\GCb(G)$.
+ $\QCf(G)$ is (equivalent to) a full subcategory of $\QCb(G)$.
 \end{proposition}
@@
 \begin{proof}
- To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \GCf(G) \to \GCb(G)$.
+ To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \QCf(G) \to \QCb(G)$.
  %
- We will do this by constructing a faithful monoidal functor $L : C_1(G) \to \GCb(G)$ 
+ We will do this by constructing a faithful monoidal functor $L : C_1(G) \to \QCb(G)$ 
  such that $L(\alpha,T)$ is an isomorphism precisely when $(h,T)$ is a weak isomorphism. 
- Factoring along $C_1(G) \to \GCb(G)$ will produce the full and faithful monoidal functor we seek.
+ Factoring along $C_1(G) \to \QCb(G)$ will produce the full and faithful monoidal functor we seek.
 
@@
 
- By Lemma~\ref{lemma:finite-iso}, each $(f,\psi) \in \GCf(G)$ determines 
- an isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi) \boxtimes (f,\psi)$ in $\GCf(G\times G)$, canonically.
+ By Lemma~\ref{lemma:finite-iso}, each $(f,\psi) \in \QCf(G)$ determines 
+ an isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi) \boxtimes (f,\psi)$ in $\QCf(G\times G)$, canonically.
  It follows immediately that the functor 
  \[
- L_G  \ceq  L_{W}\vert_{\GCf(G)} : \GCf(G) \to \GCb(G),
+ L_G  \ceq  L_{W}\vert_{\QCf(G)} : \QCf(G) \to \QCb(G),
  \] 
@@
 \begin{lemma}\label{lemma:finite-iso}
-Each $(f,\psi)\in \GCf(G)$ determines a canonical isomorphism $m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\GCf(G\times G)$.
+Each $(f,\psi)\in \QCf(G)$ determines a canonical isomorphism $m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$.
  \end{lemma}
@@
 While $\theta$ was canonical, $U$ was not, as it depended on the choice of a basis for $V$.
-However, after passing from $C_1(G)$ to $\GCf(G)$, the resulting isomorphism $\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ is canonical in $\GCf(G)$.
+However, after passing from $C_1(G)$ to $\QCf(G)$, the resulting isomorphism $\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ is canonical in $\QCf(G)$.
 \end{proof}
@@
 
-The full subcategory $\GCf(G) \subset \GCb(G)$ of finite geometrized characters is a proper subcategory, in general.
-Indeed, it follows from our main result regarding geometrized characters, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \GCiso{G} \to G(\Fq)^*$ to the subgroup $\GCfiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is finite in $\EEx$; see Section~\ref{sec:snake}.
+The full subcategory $\QCf(G) \subset \QCb(G)$ of finite quasicharacter sheaves is a proper subcategory, in general.
+Indeed, it follows from our main result regarding quasicharacter sheaves, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ to the subgroup $\QCfiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is finite in $\EEx$; see Section~\ref{sec:snake}.
 
@@
   If $G$ is a connected commutative algebraic group over $\Fq$ then 
-  the full subcategories $\GCf(G) \hookrightarrow \GCb(G) \hookrightarrow \GC(G)$ 
+  the full subcategories $\QCf(G) \hookrightarrow \QCb(G) \hookrightarrow \QC(G)$ 
   appearing in Section~\ref{sec:bounded} are equivalences 
@@
   \[
-  \trFrob{G} : \GCiso{G} \to G(\Fq)^*
+  \trFrob{G} : \QCiso{G} \to G(\Fq)^*
   \]
@@
   Observe that the forgetful functor $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$
-  sends geometrized characters of $G$ to $\ell$-adic Weil sheaves on $G$ \cite{Deligne:Weil2}*{1.1.10}.
+  sends quasicharacter sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{Deligne:Weil2}*{1.1.10}.
   While is it not true that all Weil sheaves on $G$ descend to local systems on $G$, 
-  we will see that those that appear in the image of this forgetful functor from geometrized characters do.
+  we will see that those that appear in the image of this forgetful functor from quasicharacter sheaves do.
 
@@
   $\ell$-adic representations of $\W(G,\bg)$ \cite{Deligne:Weil2}*{1.1.12}. 
-  Now let $(\gcs{L},\mu,\phi)$ be a geometrized character of $G$ 
+  Now let $(\gcs{L},\mu,\phi)$ be a quasicharacter sheaf of $G$ 
   and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gcs{L},\phi)$. 
@@
   the latter appearing in the definition of $\cs{L}$. 
-  Then, as in Section~\ref{sec:bounded}, $(\cs{L}_0,\mu_0)$ is an object in $\GCb(G)$ 
-  and $\cs{L} = (\gcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\cs{L}_0,b_{G\times G}^*\mu_0)$ in $\GC(G)$.
-  Thus, the full and faithful functor $B_G^* : \GCb(G) \to \GC(G)$ from Section~\ref{sec:bounded}
+  Then, as in Section~\ref{sec:bounded}, $(\cs{L}_0,\mu_0)$ is an object in $\QCb(G)$ 
+  and $\cs{L} = (\gcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\cs{L}_0,b_{G\times G}^*\mu_0)$ in $\QC(G)$.
+  Thus, the full and faithful functor $B_G^* : \QCb(G) \to \QC(G)$ from Section~\ref{sec:bounded}
   is also essentially surjective, hence an equivalence.
@@
 
-  In Section~\ref{sec:finite} we saw that $\GCf(G)$ is a full subcategory of $\GCb(G)$;
-  more precisely, we exhibited a full and faithful functor $L_G : \GCf(G) \to \GCb(G)$.
+  In Section~\ref{sec:finite} we saw that $\QCf(G)$ is a full subcategory of $\QCb(G)$;
+  more precisely, we exhibited a full and faithful functor $L_G : \QCf(G) \to \QCb(G)$.
   We now show that this functor is essentially surjective 
@@
 
-  Let $(\cs{L}_0,\mu_0)$ be a bounded geometrized character of $G$. 
-  Then $\cs{L}\ceq B_G^*(\cs{L}_0,\mu_0)$ is a geometrized character of $G$.
+  Let $(\cs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf of $G$. 
+  Then $\cs{L}\ceq B_G^*(\cs{L}_0,\mu_0)$ is a quasicharacter sheaf of $G$.
   Recall the definition of the character $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}. 
@@
   $\psi(g)(v) = \trFrob{\cs{L}}(g) v$ for $v\in V$. 
-  Then $(f,\psi)$ is a finite geometrized character.
+  Then $(f,\psi)$ is a finite quasicharacter sheaf.
 
@@
   Using \cite{Laumon}*{Th\'eor\`eme~1.1.2}, it follows that  $L(f,\psi) \iso \cs{L}_0$ in $\Loc(G)$.
-  It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\cs{L}_0,\mu_0)$ in $\GCb(G)$.
-  This completes the proof that $L_G : \GCf(G) \to \GC(G)$ is essentially surjective.
+  It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\cs{L}_0,\mu_0)$ in $\QCb(G)$.
+  This completes the proof that $L_G : \QCf(G) \to \QC(G)$ is essentially surjective.
   Since we have already seen (in Section~\ref{sec:finite}) that $L_G$ is full and faithful, 
@@
   $
-  \trFrob{G} : \GCiso{G} \to G(\Fq)^*
+  \trFrob{G} : \QCiso{G} \to G(\Fq)^*
   $
-  is surjective because each character $\chi \in G(\Fq)^*$ determines a finite geometrized character $(\Lang,\chi)$ such that the trace of Frobenius of the geometrized character $B_G^* (L_G(\Lang,\chi^{-1}))$ is $\chi$.
+  is surjective because each character $\chi \in G(\Fq)^*$ determines a finite quasicharacter sheaf $(\Lang,\chi)$ such that the trace of Frobenius of the quasicharacter sheaf $B_G^* (L_G(\Lang,\chi^{-1}))$ is $\chi$.
 \end{proof}
@@
 \Clifton{Re-phrase.}
-we define a category of geometrized characters $\GC(G(\bFq))$.
-An object in $\GC(G(\bFq))$ is given by the data of
+we define a category of quasicharacter sheaves $\QC(G(\bFq))$.
+An object in $\QC(G(\bFq))$ is given by the data of
 \begin{enumerate}
@@
 \end{enumerate}
-A morphism $\alpha : \cs{L} \to \cs{L'}$ in $\GC(G(\bFq))$ is given by 
+A morphism $\alpha : \cs{L} \to \cs{L'}$ in $\QC(G(\bFq))$ is given by 
 \begin{enumerate}
@@
 
-The functor $\GC(G) \to \GC(G(\bFq))$ defined by
+The functor $\QC(G) \to \QC(G(\bFq))$ defined by
 $(\gcs{L}, \mu, \phi) \mapsto (\gcs{L}_x = x^*\gcs{L}, \mu_{x,y} = (x \times y)^* \mu, \phi_x = x^*\phi)$
@@
 We may now define a \cdef{global section}
-of a geometrized character $\cs{L}$ on an \'etale group scheme $G$ as a choice $s(x) \in \gcs{L}_x$ for every
+of a quasicharacter sheaf $\cs{L}$ on an \'etale group scheme $G$ as a choice $s(x) \in \gcs{L}_x$ for every
 $x \in G(\bFq)$, satisfying
@@
 \begin{lemma}\label{lemma:section}
- If $\cs{L}$ is a geometrized character on a commutative, \'etale group scheme $G$
+ If $\cs{L}$ is a quasicharacter sheaf on a commutative, \'etale group scheme $G$
  with $G(\bFq)$ finitely generated then nontrivial global sections of $\cs{L}$ exist.
@@
   \[
-  \GCiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, G(\bFq)^*),
+  \QCiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, G(\bFq)^*),
   \qquad \text{given by}\qquad
@@
 \begin{proof}
-  Suppose $\cs{L}$ is a geometrized character on $G$.  Using Lemma~\ref{lemma:section}, we may choose a global section $s_{\cs{L}}$
-  of $\cs{L}$.  We will construct a group isomorphism between $\GCiso{G(\bFq)}$ and
+  Suppose $\cs{L}$ is a quasicharacter sheaf on $G$.  Using Lemma~\ref{lemma:section}, we may choose a global section $s_{\cs{L}}$
+  of $\cs{L}$.  We will construct a group isomorphism between $\QCiso{G(\bFq)}$ and
   $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ using $s_{\cs{L}}$, then prove independence from the choice of section.
@@
   \begin{equation}\label{cohomologous}
-    \obj \GC(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
+    \obj \QC(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
     \qquad \text{defined by} \qquad \cs{L} \mapsto [\tau_\cs{L}],
@@
   \begin{equation}\label{pich1}
-    \GCiso{G(\bFq} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*).
+    \QCiso{G(\bFq} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*).
   \end{equation}
@@
   It only remains to show that \eqref{pich1} is a group
-  isomorphism.  Suppose that $\cs{L}$ and $\cs{L}'$ are two geometrized characters.
+  isomorphism.  Suppose that $\cs{L}$ and $\cs{L}'$ are two quasicharacter sheaves.
   If $s$ is a global section for $\cs{L}$ and $s'$ for $\cs{L}'$ then $s \otimes s'$ is a global section for
@@
 
-Although this section does not mention geometrized characters, 
-we will need Proposition~\ref{prop:X} to prove our main result on geometrized characters, 
+Although this section does not mention quasicharacter sheaves, 
+we will need Proposition~\ref{prop:X} to prove our main result on quasicharacter sheaves, 
 Theorem~\ref{thm:snake}.
@@
 $G^0\hookrightarrow G$ determines a monoidal functor
-$\cs{L}\mapsto \cs{L}\vert_{G^0}$ from $\GC(G)$ to $\GC(G^0)$.  In
+$\cs{L}\mapsto \cs{L}\vert_{G^0}$ from $\QC(G)$ to $\QC(G^0)$.  In
 this section we show that this functor is essentially surjective.
@@
 \begin{proposition}\label{prop:restriction}
-  The restriction functor $\GC(G)\to \GC(G^0)$ is essentially surjective.
+  The restriction functor $\QC(G)\to \QC(G^0)$ is essentially surjective.
 \end{proposition}
@@
   By Proposition~\ref{prop:connected}, every
-  geometrized character on $G^0$ is isomorphic to a 
-  finite geometrized character on $G^0$, 
+  quasicharacter sheaf on $G^0$ is isomorphic to a 
+  finite quasicharacter sheaf on $G^0$, 
   so to prove the proposition it suffices to show that every 
@@
  Then $(f,\psi)\vert_{G^0} \iso (\pi,\psi)$,
- completing the proof that $\GC(G)\to \GC(G^0)$ is essentially surjective.
+ completing the proof that $\QC(G)\to \QC(G^0)$ is essentially surjective.
 \end{proof}
@@
 
-\section{Main result regarding geometrized characters}
+\section{Main result regarding quasicharacter sheaves}
 \label{sec:snake}
@@
   \[
-  \trFrob{G} : \GCiso{G} \to G(\Fq)^*
-  \]
-  from the Picard group of the category of geometrized characters of $G$ to
+  \trFrob{G} : \QCiso{G} \to G(\Fq)^*
+  \]
+  from the Picard group of the category of quasicharacter sheaves on $G$ to
   the group of characters of $G(\Fq)$, is an isomorphism.
@@
     {}& \ker t_{\pi_0(G)} \dar & \arrow[dashed]{d} \ker \trFrob{G} & \ker t_{G^0} \dar & \\
-    0 \rar & \GCiso{\pi_0(G)} \rar \dar{t_{\pi_0(G)}}
-    & \GCiso{G} \rar \dar{\trFrob{G}} & \GCiso{G^0} \rar \dar{t_{G^0}} & 0\\
+    0 \rar & \QCiso{\pi_0(G)} \rar \dar{t_{\pi_0(G)}}
+    & \QCiso{G} \rar \dar{\trFrob{G}} & \QCiso{G^0} \rar \dar{t_{G^0}} & 0\\
     0 \rar & \pi_0(G)(\Fq)^* \rar \dar
@@
   The sequence of Picard groups is right-exact: it is exact at
-  $\GCiso{G^0}$ by Proposition~\ref{prop:restriction}; and
-  it is exact at $\GCiso{G}$ because the left-square
+  $\QCiso{G^0}$ by Proposition~\ref{prop:restriction}; and
+  it is exact at $\QCiso{G}$ because the left-square
   commutes (by Proposition~\ref{prop:pullback}), the bottom sequence
@@
   \[
-  \image(\GCiso{\pi_0(G)} \to \GCiso{G}) \subseteq \ker(\GCiso{G} \to \GCiso{G^0}),
+  \image(\QCiso{\pi_0(G)} \to \QCiso{G}) \subseteq \ker(\QCiso{G} \to \QCiso{G^0}),
   \]
   by the last part of Proposition~\ref{prop:pullback}. Specifically,
-  suppose $\cs{L}$ is a geometrized character of $G$ that is trivial on
+  suppose $\cs{L}$ is a quasicharacter sheaf of $G$ that is trivial on
   $G^0$. Then $\trFrob{\cs{L}}\vert_{G^0(\Fq)} = \trFrob{\cs{L}^0} =0$,
@@
   $\trFrob{\cs{L}}$. By Propositions~\ref{prop:etale} and \ref{prop:X},
-  there is a a geometrized character $\cs{L}_\chi$ on $\pi_0(G)$, unique up
+  there is a a quasicharacter sheaf $\cs{L}_\chi$ on $\pi_0(G)$, unique up
   to isomorphism, such that $\trFrob{\cs{L}_\chi} = \chi$. By
   Proposition~\ref{prop:pullback} again, $\cs{L}$ is isomorphic to the
-  image of $\cs{L}_\chi$ under the monoidal functor $\GC(\pi_0(G)) \to \GC(G)$.
+  image of $\cs{L}_\chi$ under the monoidal functor $\QC(\pi_0(G)) \to \QC(G)$.
 
@@
 To see this, consider the case when $G$ is the discrete etale group scheme $\ZZ$.
-Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ and let $\cs{L}$ be a geometrized character in the isomorphism class corresponding to the character $\chi : G(\Fq) \to \EEx$ under Theorem~\ref{thm:snake}.
+Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ and let $\cs{L}$ be a quasicharacter sheaf in the isomorphism class corresponding to the character $\chi : G(\Fq) \to \EEx$ under Theorem~\ref{thm:snake}.
 Then $\trFrob{\cs{L}}(1) = \ell$.
@@
 In this case, the corresponding geometric character $\cs{L}$ is bounded but not finite, since $1+\ell$ is not a root of unity.
-This simple example illustrates why the categories $\GCb(G)$ and $\GCf(G)$ are inadequate to geometrize characters of $G(\Fq)$.
+This simple example illustrates why the categories $\QCb(G)$ and $\QCf(G)$ are inadequate to geometrize characters of $G(\Fq)$.
 
@@
   Let $\GN{T}_d$ be as above.  For each positive integer $d$, the
-  Picard group of the category of geometrized characters of $\GN{T}_d$ is
+  Picard group of the category of quasicharacter sheaves on $\GN{T}_d$ is
   canonically isomorphic to the group of characters of $T(K)$ of depth
@@
   \[
-  \GCiso{\GN{T}_d} \iso \Hom_{< d}(T(K),\EEx).
+  \QCiso{\GN{T}_d} \iso \Hom_{< d}(T(K),\EEx).
   \]
@@
   $\GN{T}_d$ which provides a canonical isomorphism
-  $\GCiso{\GN{T}_d} \iso \GN{T}_d(\Fq)^*$.
+  $\QCiso{\GN{T}_d} \iso \GN{T}_d(\Fq)^*$.
   By \ref{dFq}, $\GN{T}_d(\Fq) \iso \TT(\OK/\pK^d)$ canonically.
@@
 without reference to depth.
-Let \cdef{$\GC(\GN{T})$} be the ind-category $\varinjlim_{d\in \ZZ_{>0}} \GC(\GN{T}_d)$;
-we refer to objects of $\GC(\GN{T})$ as \cdef{geometrized characters of $T$}.
+Let \cdef{$\QC(\GN{T})$} be the ind-category $\varinjlim_{d\in \ZZ_{>0}} \QC(\GN{T}_d)$;
+we refer to objects of $\QC(\GN{T})$ as \cdef{quasicharacter sheaves on $T$}.
 
@@
 Let $T$ be an algebraic torus over a non-Archimedean local field $K$.
-The Picard group of the category $\GC(\GN{T})$ of geometrized characters of $T$ is canonically isomorphic to the group of admissible characters of $T(K)$:
-  \[
- \GCiso{\GN{T}} \iso \Hom_\text{ad}(T(K),\EEx).
+The Picard group of the category $\QC(\GN{T})$ of quasicharacter sheaves on $T$ is canonically isomorphic to the group of admissible characters of $T(K)$:
+  \[
+ \QCiso{\GN{T}} \iso \Hom_\text{ad}(T(K),\EEx).
   \]
@@
 
-We have already seen that the trace of Frobenius defines a canonical homomorphism $\GCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
+We have already seen that the trace of Frobenius defines a canonical homomorphism $\QCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
 In this section we show that this homomorphism is functorial, in the following sense.
@@
 \begin{proposition}
-Trace of Frobenius $\GCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$ 
+Trace of Frobenius $\QCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$ 
 is a natural transformation between the following two additive functors from the additive category of algebraic tori over $K$ to the category of abelian groups: 
 \begin{enumerate}
-\item[$F_1$:] $T \mapsto \GCiso{\GN{T}}$;
+\item[$F_1$:] $T \mapsto \QCiso{\GN{T}}$;
 \item[$F_2$:] $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
@@
 \begin{proof}
-When combined with the definition of $\GC(\GN{T})$ and Property~\ref{T(K)}, the first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$.
+When combined with the definition of $\QC(\GN{T})$ and Property~\ref{T(K)}, the first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$.
 When further combined with Lemma~\ref{lemma:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.
@@
 \begin{tikzcd}
-\GCiso{\Res_{k'/k} \Gr(\TL)} \arrow[two heads]{r} \dar & \GCiso{\GN{T}} \dar\\
+\QCiso{\Res_{k'/k} \Gr(\TL)} \arrow[two heads]{r} \dar & \QCiso{\GN{T}} \dar\\
 \Hom(T(L), \EEx) \arrow[two heads]{r} & \Hom(T(K), \EEx)
@@
 The techniques in this paper apply to all non-Archimdean local fields $K$ with residue field $k$, and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$ or on the ramification of $T$.
-Because of this, it is natural to ask if we can compare geometrized characters of $T$
+Because of this, it is natural to ask if we can compare quasicharacter sheaves on $T$
 
@@
  \[
-  \GC(\GN{T}_{N-3h}) \to \GC(\GN{T}'_{N-3h})
+  \QC(\GN{T}_{N-3h}) \to \QC(\GN{T}'_{N-3h})
  \]

### 2013-08-13 shanghai.tex
Admissible character -> quasicharacter

@@
   of characters of $G(\Fq)$. We use this result to exhibit an
-  isomorphism between admissible characters of $T(K)$ and isomorphism
+  isomorphism between quasicharacters of $T(K)$ and isomorphism
   classes of quasicharacter sheaves on the Greenberg transform of the Néron
@@
 %choosing an isomorphism $\EE \approx \CC$ (unnatural though it may
-%be), we arrive at a model for the group of quasi-characters of
+%be), we arrive at a model for the group of quasicharacters of
 %$K^\times$: the monoidal category of quasicharacter sheaves on the
@@
 $T$ provides an elegant, canonical model for the group of
-(quasi-)characters of $T(K)$, where $K$ is any non-Archimedean local
+quasicharacters of $T(K)$, where $K$ is any non-Archimedean local
 field and $T$ is any algebraic torus over $K$.
@@
 
-Our main result on the geometrization of admissible characters of
+Our main result on the geometrization of quasicharacters of
 $p$-adic tori [insert internal reference here] follows from a general
@@
 
-%\section{Application to admissible characters}
+%\section{Application to quasicharacters}
 
@@
   \end{enumerate}
-This gives us a natural way to geometrize all admissible characters of $T(K)$
+This gives us a natural way to geometrize all quasicharacters of $T(K)$
 without reference to depth.
@@
 Let $T$ be an algebraic torus over a non-Archimedean local field $K$.
-The Picard group of the category $\QC(\GN{T})$ of quasicharacter sheaves on $T$ is canonically isomorphic to the group of admissible characters of $T(K)$:
+The Picard group of the category $\QC(\GN{T})$ of quasicharacter sheaves on $T$ is canonically isomorphic to the group of quasicharacters of $T(K)$:
   \[

### 2013-08-13 shanghai.tex
Adding definitions . . . .

--- 2013-08-13 shanghai.tex
@@
 \renewcommand{\baselinestretch}{1.2}
-%\usepackage[notcite,color]{showkeys}
+\usepackage[notcite,color]{showkeys}
 \usepackage{hyperref}
@@
 structure on the set $\QCiso{G}$ of isomorphism classes in
-$\QC(G)$.
-Our main result regarding quasicharacter sheaf sheaves on $G$ is the determination of $\QCiso{G}$ under the hypothesis that the component group scheme for $G$ is geometrically finitely generated; see Theorem~\ref{thm:snake}.
-To do this, we use the trace of Frobenius.
+$\QC(G)$. Our main result regarding quasicharacter sheaves on $G$ (Theorem~\ref{thm:snake})
+determines $\QCiso{G}$ under the hypothesis that the component group scheme for $G$ is geometrically finitely generated; see Theorem~\ref{thm:snake}. To do this, we use the trace of Frobenius.
 
@@
 \]
-If $\cs{L} = (\gcs{L},\mu,\phi)$ is a geochar, then we will abbreviate write $\trFrob{\cs{L}}$ for $\trFrob{(\gcs{L},\phi)}$
+If $\cs{L} = (\gcs{L},\mu,\phi)$ is a quasicharacter sheaf, 
+then we will abbreviate $\trFrob{(\gcs{L},\phi)}$ to $\trFrob{\cs{L}}$.
 \end{definition}
 
-The isomorphism $\mu : \bm^* \gcs{L} \to \LxL$
-guarantees that the function $\trFrob{\cs{L}} : G(\Fq)\to \EEx$,
-defined by $g \mapsto \phi_{\bg}$, is a group homomorphism;
-we refer to $\trFrob{\cs{L}}$ as the \cdef{trace of Frobenius of $\cs{L}$}.
-Although though no trace is involved in the definition, the notion extends 
-to any constructible $\ell$-adic Weil sheaf $(\gcs{L},\phi)$ on $G$, in which context,
-$\trFrob{(\gcs{L},\phi)} : G(\Fq)\to \EE$ is defined by $\trFrob{(\gcs{L},\phi)}(g) \ceq \trace \phi_{\bg}$.
-
-It is clear that $\trFrob{\cs{L}\otimes \cs{L'}} = \trFrob{\cs{L}} \cdot \trFrob{\cs{L'}}$
+The isomorphism $\mu : \bm^* \gcs{L} \to \LxL$ guarantees 
+that the function $\trFrob{\cs{L}} : G(\Fq)\to \EEx$ is a group homomorphism.
+It is also clear that $\trFrob{\cs{L}\otimes \cs{L'}} = \trFrob{\cs{L}} \cdot \trFrob{\cs{L'}}$
 (pointwise multiplication of functions) and that $\trFrob{\cs{L}} = \trFrob{\cs{L'}}$
@@
 \[
-\cdef{\trFrob{G}} : \QCiso{G} \longrightarrow G(\Fq)^*,%\Hom_\text{grp}(G(\Fq),\EEx),
-\qquad \text{defined by}\qquad \cs{L} \mapsto \trFrob{\cs{L}},
-\]
-from the Picard group of quasicharacter sheaves on $G$ to the character group of $G(\Fq)$.
-
-Our main result on the geometrization of admissible characters of
-$p$-adic tori [insert internal reference here] follows from a general
-fact established later in this paper: if the geometric component group
-of $G$ is finitely-generated then the trace of Frobenius defines an
-isomorphism from the Picard group of quasicharacter sheaves $G$ to the
-group of characters of $G(\Fq)$ (here, as throughout the paper, $G$ is
-a commutative group scheme, smooth and locally of finite type over $\Fq$).
-
-\Clifton{Address functoriality here? Yes, but put proof at the end of the next section.}
-
-In this paper we $\QCiso{G} \iso G(\Fq)^*$ when the geometric component group of $G$ is finitely generated; see Theorem~\ref{thm:snake}. We also shows that this isomorphism is canonical; see
+\cdef{\trFrob{G}} : \QCiso{G} \longrightarrow G(\Fq)^*,
+\qquad \text{defined by}\qquad \cs{L} \mapsto \trFrob{\cs{L}}.
+\]
+This isomorphism is functorial, in the following sense.
+
+\begin{proposition}\label{prop:functorialG}
+Trace of Frobenius $\QCiso{G} \to G(\Fq)$ is a natural transformation 
+between the following two additive functors from the category of smooth commutative
+group schemes locally of finite type over
+
+ to the category of abelian groups: 
+\begin{enumerate}
+\item[$F_1$:] $T \mapsto \QCiso{\GN{T}}$;
+\item[$F_2$:] $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
+\end{enumerate}
+\end{proposition}
 

### 2013-08-14 shanghai.tex
more definitions, not all, yet
Conflicts:
	shanghai.tex

@@
 \renewcommand{\baselinestretch}{1.2}
-\usepackage[notcite,color]{showkeys}
+\usepackage[notcite]{showkeys}
 \usepackage{hyperref}
@@
 $\Frob{G} : \bG \to \bG$ for the Frobenius automorphism.
-A quasicharacter sheaf of $G$ is a triple $\cs{L}\ceq
+A quasicharacter sheaf on $G$ is a triple $\cs{L}\ceq
 (\gcs{L},\mu,\phi)$ where $\gcs{L}$ is a rank-$1$ local system on $\bG$ and $\mu: m^*
@@
 It is also clear that $\trFrob{\cs{L}\otimes \cs{L'}} = \trFrob{\cs{L}} \cdot \trFrob{\cs{L'}}$
-(pointwise multiplication of functions) and that $\trFrob{\cs{L}} = \trFrob{\cs{L'}}$
+(pointwise multiplication of functions) and $\trFrob{\cs{L}} = \trFrob{\cs{L'}}$
 if $\cs{L} \iso \cs{L'}$ in $\QC(G)$. In this way we obtain a group homomorphism
@@
 between the following two additive functors from the category of smooth commutative
-group schemes locally of finite type over
-
- to the category of abelian groups: 
+group schemes locally of finite type over $\Fq$ to the category of abelian groups:
 \begin{enumerate}
-\item[$F_1$:] $T \mapsto \QCiso{\GN{T}}$;
-\item[$F_2$:] $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
+\item[$F_1$:] $G \mapsto \QCiso{G}$;
+\item[$F_2$:] $G \mapsto G(\Fq)$.
 \end{enumerate}
 \end{proposition}
+
+The proof of Proposition~\ref{prop:functorialG} requires the results from the next section.
 
@@
 \begin{proof}
-  Let $\cs{L}$ be a quasicharacter sheaf of $G$. We start by showing that
+  Let $\cs{L}$ be a quasicharacter sheaf on $G$. We start by showing that
   $\bf^*\gcs{L}$ is locally constant on connected components of
@@
 \end{equation}
-Since $\pi_0(G)$ is an Abelian group scheme, smooth (in fact, etale) and locally of finite type over $\Fq$, 
+Since $\pi_0(G)$ is an commutative group scheme, smooth (in fact, etale) and locally of finite type over $\Fq$, 
 it follows from Proposition~\ref{prop:pullback} that \eqref{eq:pi-1} defines a sequence of functors
@@
 \]
-which induces, upon passage to Picard groups, a sequence of group homomorphisms 
+which induces, upon passage to isomorphism classes of objects, a sequence of group homomorphisms 
 \begin{equation}\label{eq:pi-1}
@@
 canonically.
-
 %\section{Products} 
-We end this section with a simple result on products of geochars, which we will be needed to show that the isomorphism above is functorial.
-
-\begin{lemma}\label{lemma:product}
+We end this section with a simple result on products of quasicharacter sheaves, which is needed to show that the isomorphism above is functorial.
+
+\begin{proposition}\label{prop:product}
 The rule $\boxtimes : (\cs{L}_1,\cs{L}_2)\to \cs{L}_1\boxtimes\cs{L}_2$ defines an equivalence of categories 
@@
 commutes.
-\end{lemma}
+\end{proposition}
 
@@
 
+\begin{proof}[Proof of Proposition~\ref{prop:functorialG}]
+The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$.
+When further combined with Proposition~\ref{prop:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.
+\end{proof}
+
 \section{Base change}\label{sec:basechange}
@@
 
-If $\cs{L} = (\gcs{L}, \mu, \phi)$ is a quasicharacter sheaf of $G$ we may define
+If $\cs{L} = (\gcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$ we may define
 a quasicharacter sheaf $\cs{L}' = (\gcs{L}, \mu, \phi_{k'})$ on 
@@
 
-Let \cdef{$\QCb(G)$} be the category of pairs $(\cs{L}_0,\mu_0)$ 
-where $\cs{L}_0$ is a constructible $\ell$-adic sheaf on $G$, 
-which is a rank-$1$ local system on each connected component of $G$, 
+\begin{definition}
+Let $\QCb(G)$ be the category of pairs $(\cs{L}_0,\mu_0)$ 
+where $\cs{L}_0$ a rank-$1$ $\ell$-adic local system on $G$, 
 equipped with an isomorphism $\mu_0 : m^* \cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ 
 satisfying the analogue of Condition~\ref{CS.1} on $G$; 
-morphisms in $\QCf(G)$ are defined as in (the second part of) Condition~\ref{CS.2}. 
-This is the category of \cdef{bounded quasicharacter sheaves} on $G$. 
-\Clifton{Should this be $\sheafHom(\cs{L}_0,\EE)$?}
-This is a rigid monoidal category in the obvious way, 
-with duals given by $\cs{L}_0^\vee \ceq \sheafHom(\cs{L}_0,(\EE)_{G})$.
+morphisms in $\QCb(G)$ are defined as in (the second part of) Condition~\ref{CS.2}. 
+This is the category of \emph{bounded quasicharacter sheaves} on $G$. 
+\end{definition}
+
+The category of bounded quasicharacter sheaves is a rigid monoidal category in the obvious way. 
+%with duals given by $\cs{L}_0^\vee \ceq \sheafHom(\cs{L}_0,\EE)$.
 
@@
  Let $b_G : {\bar G} \to G$ be the pull-back of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Let $(\cs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf of $G$. 
+ Let $(\cs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$. 
  Then $\cs{L}_0$ is, in particular, an $\ell$-adic constructible sheaf on $G$. 
@@
 To define the category of finite quasicharacter sheaves we must work a bit harder.
-Consider the following category \cdef{$C(G)$}:
-an object in $C(G)$ is a pair $(f,\psi)$ where: 
-$f : H\to G$ is a \cdef{discrete isogeny} (a finite, surjective etale morphism and a morphism of commutative group $\Fq$-schemes, for which the action of $\Gal(\bFq/\Fq)$ on the etale group scheme $f^{-1}{\bar e}$ is trivial),
+Consider the following category $C(G)$.
+Let us say that $f : H\to G$ is a \emph{discrete isogeny} if it is a a finite, surjective etale morphism and a morphism of commutative group $\Fq$-schemes, for which the action of $\Gal(\bFq/\Fq)$ on the etale group scheme $f^{-1}{\bar e}$ is trivial.
+An object in $C(G)$ is a pair $(f,\psi)$ where: 
+$f : H\to G$ is a discrete isogeny 
 and $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$;
@@
 \]
-\Clifton{I suspect $\alpha$ is a covering, for free. Is that right? 
-If $f' = f \circ \alpha$ and $f$ and $f'$ are etale covers, 
-does it follow that $\alpha$ is also an etale cover? (Etale: Yes. Finite? Surjective?) 
-If so, then I can simplify the definition of weak isomorphism accordingly.}
-We say that $(\alpha,T)$ in $C(G)$ is a \cdef{weak isomorphism} if $\alpha$ is a covering and $T$ is an isomorphism of vector spaces.
+We say that $(\alpha,T)$ in $C(G)$ is a \emph{weak isomorphism} if $\alpha$ is surjective
+and $T$ is an isomorphism of vector spaces.
 Let \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at weak isomorphisms.
@@
 Likewise, $C(G)[W^{-1}]$ is a tensor category.
-
-Let \cdef{$C_1(G)$} be the rigid monoidal full subcategory of $C(G)$ consisting of objects $(f,\psi)$ such that $\psi$ is a one-dimensional representation and let \cdef{$\QCf(G)$} be the localisation of $C_1(G)$ at weak isomorphisms; this is the rigid symmetric monoidal category of \cdef{finite quasicharacter sheaves} of $G$.
+Let $C_1(G)$ be the rigid monoidal full subcategory of $C(G)$ consisting of objects $(f,\psi)$ such that $\psi$ is a one-dimensional representation.
+
+\begin{definition}
+The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\QCf(G)$, is the rigid symmetric monoidal category obtained by localizing $C_1(G)$ at weak isomorphisms.
+\end{definition}
 
@@
   $\ell$-adic representations of $\W(G,\bg)$ \cite{Deligne:Weil2}*{1.1.12}. 
-  Now let $(\gcs{L},\mu,\phi)$ be a quasicharacter sheaf of $G$ 
+  Now let $(\gcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$ 
   and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gcs{L},\phi)$. 
@@
 
-  Let $(\cs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf of $G$. 
-  Then $\cs{L}\ceq B_G^*(\cs{L}_0,\mu_0)$ is a quasicharacter sheaf of $G$.
+  Let $(\cs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$. 
+  Then $\cs{L}\ceq B_G^*(\cs{L}_0,\mu_0)$ is a quasicharacter sheaf on $G$.
   Recall the definition of the character $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}. 
@@
   component group) is finitely generated, then the trace of Frobenius
-  homomorphism
   \[
@@
   \]
-  from the Picard group of the category of quasicharacter sheaves on $G$ to
-  the group of characters of $G(\Fq)$, is an isomorphism.
+  is an isomorphism of groups.
   \Clifton{Address functoriality, here?}
@@
   by the last part of Proposition~\ref{prop:pullback}. Specifically,
-  suppose $\cs{L}$ is a quasicharacter sheaf of $G$ that is trivial on
+  suppose $\cs{L}$ is a quasicharacter sheaf on $G$ that is trivial on
   $G^0$. Then $\trFrob{\cs{L}}\vert_{G^0(\Fq)} = \trFrob{\cs{L}^0} =0$,
@@
 
-With Theorem~\ref{thm:snake} on hand, we can see why neither bounded geochars nor finite geochars are up to the task of geometrizing characters of $G(\Fq)$ in the generality we need.
+With Theorem~\ref{thm:snake} on hand, we can see why neither bounded quasicharacter sheaves nor finite quasicharacter sheaves are up to the task of geometrizing characters of $G(\Fq)$ in the generality we need.
 To see this, consider the case when $G$ is the discrete etale group scheme $\ZZ$.
@@
 
-Also throughout the paper, $K$ is a non-Archimedean local field 
-with residue field $\Fq$ and $T$ is an algebraic torus over $K$.
+Let $K$ be a non-Archimedean local field with residue field $\Fq$ 
+and let $T$ be an algebraic torus over $K$.
 
@@
 When combined with the definition of $\QC(\GN{T})$ and Property~\ref{T(K)}, the first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$.
-When further combined with Lemma~\ref{lemma:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.
+When further combined with Lemma~\ref{prop:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.
 \end{proof}

### 2013-08-14 shanghai.tex
All the definitions are in now.

@@
  We will do this by constructing a faithful monoidal functor $L : C_1(G) \to \QCb(G)$ 
- such that $L(\alpha,T)$ is an isomorphism precisely when $(h,T)$ is a weak isomorphism. 
+ such that $L(\alpha,T)$ is an isomorphism precisely when $(\alpha,T)$ is a weak isomorphism. 
  Factoring along $C_1(G) \to \QCb(G)$ will produce the full and faithful monoidal functor we seek.
@@
  Morphisms in $C(G)[W^{-1}]$ are simple to describe because category $C(G)$ 
- admits a calculus of left fractions\footnote{See {\tt http://ncatlab.org/nlab/show/calculus+of+fractions}.} for weak isomorphisms: 
- every isomorphism in $C(G)$ is a weak isomorphism; 
- push-outs exist in $C(G)$ and the push-out of a weak isomorphism is a weak isomorphism; 
- and weak isomorphisms enjoy the left-cancellation property. 
- It follows that a morphism in $C(G)[W^{-1}]$ is the equivalence class of 
+ admits a calculus of left fractions
+ %\footnote{See {\tt http://ncatlab.org/nlab/show/calculus+of+fractions}.} 
+ for weak isomorphisms:
+% every isomorphism in $C(G)$ is a weak isomorphism; 
+% push-outs exist in $C(G)$ and the push-out of a weak isomorphism is a weak isomorphism; 
+% and weak isomorphisms enjoy the left-cancellation property. 
+% It follows that
+ a morphism in $C(G)[W^{-1}]$ is the equivalence class of 
   \begin{equation}\label{eq:morGCf}
    \begin{tikzcd}
-   (f,\psi) \arrow{r}{(\alpha_1,T_1)} & (f_1,\psi_1) & \arrow[swap]{l}{(\alpha'_1,T'_1)} (f',\psi')
+   (f,\psi) \arrow{r}{(\alpha_1,T_1)} & (f_1,\psi_1) & \arrow[swap]{l}{(\beta_1,U_1)} (f',\psi')
    \end{tikzcd}
@@
  where $(\alpha',T') : (f,\psi) \to (f',T')$ is any map in $C(G)$ 
- and $(\alpha'_1,T'_1) : (f_1,\psi_1) \to (f',\psi')$ is a weak isomorphism,
- and therefore given by a diagram of the form
+ and $(\beta_1,U_1) : (f_1,\psi_1) \to (f',\psi')$ is a weak isomorphism.
 
  Observe that $L$ takes weak isomorphisms in $C(G)$ to isomorphisms in $\Loc(G)$. 
- To see this, let $(h,T) : (f,\psi)\to (f',\psi')$ be a weak isomorphism, 
- where $f:H\to G$ and $f':H'\to G$ as above. 
- Since $T$ is an isomorphism, we may replace $V'$ with $V$ and $T$ with $\id_V$, without loss of generality. 
- Then the equivariance condition on $T$ becomes $\psi' = \psi\circ h$ on the finite etale group scheme $\ker f'$. 
- Since $\alpha : H'\to H$ is an etale cover, it admits a section $\alpha' : H \to H'$, 
- which provides the inverse to $L(\alpha,T) : L(f,\psi) \to L(f',\psi')$, above. 
- It is also clear that if $L(\alpha,T)$ is an isomorphism of local systems, 
- then $T$ must be an isomorphism of vector spaces, 
- whence $(\alpha,T)$ is a weak isomorphism: $W$ is saturated.
+ To see this, suppose $(\beta,U) : (f,\psi)\to (f',\psi')$ is a weak isomorphism. 
+ Since $U$ is an isomorphism, we may replace $V'$ with $V$ and $U$ with $\id_V$, without loss of generality. 
+ Then the equivariance condition on $U$ becomes $\psi' = \psi\circ \beta$ on the finite etale group scheme $\ker f'$. 
+ Since $f$ and $f'$ are finite etale, and $f' = f\circ \beta$, and $\beta$ is surjective, $\beta$ is an etale cover; therefore, $\beta$ admits a section $\beta' : H \to H'$.
+This provides the inverse to $L(\beta,U) : L(f,\psi) \to L(f',\psi')$.
+
+ Conversely, if $L(\alpha,T)$ is an isomorphism of local systems, 
+ then $T$ must be an isomorphism of vector spaces and $\beta$ must be surjective, whence $(\alpha,T)$ is a weak isomorphism: $W$ is saturated.
 
  Since $L : C(G) \to \Loc(G)$ takes weak isomorphisms to isomorphisms,
- it factors (uniquely!) through the localisation functor $C(G) \to C(G)[W^{-1}]$ 
+ it factors, uniquely, through the localisation functor $C(G) \to C(G)[W^{-1}]$ 
  to define a faithful functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$. 
@@
 \ &  & \arrow{ld}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-V \arrow{d}{U} & \Aut(V)  & \arrow{l}{\psi_g} \arrow{u} A_m \arrow[hook]{r} & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G\\
+V \arrow{d}{T} & \Aut(V)  & \arrow{l}{\psi_g} \arrow{u} A_m \arrow[hook]{r} & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G\\
 V\otimes V & \Aut(V\otimes V) & \arrow[swap]{l}{\psi\otimes\psi} \arrow[bend left]{uu}{m_H} \arrow[swap]{u}{\theta\vert_{A\times A}} A \times A \arrow[hook]{r}{} & \arrow[bend left]{uu}{m_H} \arrow[swap]{u}{\theta} H \times H \arrow{r}{f\times f} & \arrow[equal]{u} G\times G\\
@@
 Choose a basis $\{ v_1 \}$ for $V$; then $\{ v_1\otimes v_1 \}$ is a basis for $V\otimes V$.
-Define $U : V \to V\otimes V$ by $U(v_1) = v_1\otimes v_1$.
-Then the lower part of this diagram defines a weak isomorphism $(\theta,U): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G)$.
-
-While $\theta$ was canonical, $U$ was not, as it depended on the choice of a basis for $V$.
+Define $T : V \to V\otimes V$ by $T(v_1) = v_1\otimes v_1$.
+Then the lower part of this diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G)$.
+
+While $\theta$ was canonical, $T$ was not, as it depended on the choice of a basis for $V$.
 However, after passing from $C_1(G)$ to $\QCf(G)$, the resulting isomorphism $\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ is canonical in $\QCf(G)$.
@@
 
-\'Etale group schemes form a counterpoint to connected groups, since the component group
-is always \'etale.  The functor $G \mapsto G(\bFq)$ defines an equivalence of categories
+\'Etale group schemes form a counterpoint to connected groups, since the component group of a group scheme locally of finite type over $\Fq$ is an \'etale group scheme (locally of finite type) over $\Fq$ \cite{vdG&M}*{III, \S 4}.
+The functor $G \mapsto G(\bFq)$ defines an equivalence of categories
 between the category of \'etale group schemes over $\Fq$ and the category of groups equipped
 with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group.
-
-For such a $\Gal(\bFq/\Fq)$-group $G(\bFq)$, 
-\Clifton{Re-phrase.}
-we define a category of quasicharacter sheaves $\QC(G(\bFq))$.
-An object in $\QC(G(\bFq))$ is given by the data of
+Under this equivalence, a quasicharacter sheaf on $G$ is given by the data of:
 \begin{enumerate}
@@
 \end{enumerate}
-A morphism $\alpha : \cs{L} \to \cs{L'}$ in $\QC(G(\bFq))$ is given by 
+Under this equivalence, a morphism $\alpha : \cs{L} \to \cs{L'}$ of quasicharacter sheaves on $G$ is given by 
 \begin{enumerate}
@@
 
-The functor $\QC(G) \to \QC(G(\bFq))$ defined by
-$(\gcs{L}, \mu, \phi) \mapsto (\gcs{L}_x = x^*\gcs{L}, \mu_{x,y} = (x \times y)^* \mu, \phi_x = x^*\phi)$
-is easily seen to be an equivalence.
-
-We may now define a \cdef{global section}
-of a quasicharacter sheaf $\cs{L}$ on an \'etale group scheme $G$ as a choice $s(x) \in \gcs{L}_x$ for every
-$x \in G(\bFq)$, satisfying
+Let us say that \cdef{global section}
+of a quasicharacter sheaf $\cs{L}$ on an \'etale group scheme $G$ as a choice
+
+\begin{lemma}\label{lemma:section}
+ If $\cs{L}$ is a quasicharacter sheaf on a commutative, \'etale group scheme $G$ over $\Fq$ and if $G(\bFq)$ is finitely generated, then there is a global section $s = \{ s(x) \in \gcs{L}_x \tq x \in G(\bFq) \}$ satisfying
  \begin{equation}\label{section}
@@
  \end{equation}
-\Clifton{I've been putting lemmata after the propositions that use them, 
-to keep the flow of the sections clear. 
-Would you mind if I do the same in this section?}
-
-\begin{lemma}\label{lemma:section}
- If $\cs{L}$ is a quasicharacter sheaf on a commutative, \'etale group scheme $G$
- with $G(\bFq)$ finitely generated then nontrivial global sections of $\cs{L}$ exist.
 \end{lemma}
@@
 
-These global sections will allow us to construct the isomorphism in the following proposition.
+These sections will allow us to construct the isomorphism in the following proposition.
 
@@
 \begin{proof}
-  Suppose $\cs{L}$ is a quasicharacter sheaf on $G$.  Using Lemma~\ref{lemma:section}, we may choose a global section $s_{\cs{L}}$
-  of $\cs{L}$.  We will construct a group isomorphism between $\QCiso{G(\bFq)}$ and
-  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ using $s_{\cs{L}}$, then prove independence from the choice of section.
+  Suppose $\cs{L}$ is a quasicharacter sheaf on $G$.
+Using Lemma~\ref{lemma:section}, we may choose a section $s = \{ s(x) \in \gcs{L}_x \tq x \in G(\bFq) \}$ satisfying \eqref{section}.
+We will construct a group isomorphism between $\QCiso{G(\bFq)}$ and
+  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ using $s$, then prove independence from the choice of section.
 
@@
 
-  Although we used a global section $s_\cs{L}$ in the definition of
+  Although we used a global section $s$ in the definition of
   $\tau_\cs{L}$, the class of $\tau_\cs{L}$ does not depend on this
@@
 With Theorem~\ref{thm:snake} on hand, we can see why neither bounded quasicharacter sheaves nor finite quasicharacter sheaves are up to the task of geometrizing characters of $G(\Fq)$ in the generality we need.
-To see this, consider the case when $G$ is the discrete etale group scheme $\ZZ$.
+%
+Consider the case when $G$ is the discrete etale group scheme $\ZZ$.
 Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ and let $\cs{L}$ be a quasicharacter sheaf in the isomorphism class corresponding to the character $\chi : G(\Fq) \to \EEx$ under Theorem~\ref{thm:snake}.
 Then $\trFrob{\cs{L}}(1) = \ell$.
-Suppose $\cs{L}$ was a bounded character sheaf.
-Then the restriction of $\cs{L}$ to the connected component $1\in G$ would be a rank-1 local system on $1$, thus an $\ell$-adic chacter $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with $\rho_1(\Frob{\Fq}) = \ell$.
+Suppose $\cs{L}$ was a bounded quasicharacter sheaf.
+Then the restriction of $\cs{L}$ to the connected component $1\in G$ would be a rank-1 local system on $1$, thus an $\ell$-adic character $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with $\rho_1(\Frob{\Fq}) = \ell$.
 But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, while $\rho_1(\pi_1(1,{\bar 1}))$ is not compact (it contains $\ell^\ZZ$).
-Since the Weil sheaf $\gcs{L}$ does not descend to a local system on $G$, the geometric character $\cs{L}$ is not a bounded geometric character.
+Since the Weil sheaf $\gcs{L}$ does not descend to a local system on $G$, the  quasicharacter sheaf$\cs{L}$ is not a bounded quasicharacter sheaf.
+%
 We can play the same game with the character $\chi : G(\Fq) \to \EEx$ defined by $\chi(1) = 1+\ell$.
 In this case, the corresponding geometric character $\cs{L}$ is bounded but not finite, since $1+\ell$ is not a root of unity.
-This simple example illustrates why the categories $\QCb(G)$ and $\QCf(G)$ are inadequate to geometrize characters of $G(\Fq)$.
+
+These simple examples illustrate why the categories $\QCb(G)$ and $\QCf(G)$ are inadequate to geometrize characters of $G(\Fq)$.
 
@@
 
-Let $K$ be a non-Archimedean local field with residue field $\Fq$ 
-and let $T$ be an algebraic torus over $K$.
+Let $K$ be a non-Archimedean local field with residue field $\Fq$.
+Note that we place no restriction on the characteristic of $K$. 
+We write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$. 
+For any positive integer $d$, set $A_d\ceq \OK/\pK^d$.
+Let $T$ be an algebraic torus over $K$.
+We write $\Hom_{< d}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $d$ and $\Hom_\text{qc}(T(K),\EEx)$ for the group of quasicharacters of $T(K)$.
 
@@
 
-Let $K$ be a local field with residue field $\Fq$.
-%(Note that we place no restriction on the characteristic of $K$.)
-Let $T$ be an algebraic torus over $K$.
-
-%In this section we introduce a group scheme $\GN{T}$ over $\Fq$ obtained by applying the Greenberg functor to the N\'eron lft-model for $T$ and establish some basic facts about $\GN{T}$
-
 %\subsection{The N\'eron locally finite type model for $T$}
 
-The lft-N\'eron model for $T$, denoted here by $\TT$, 
-is a separated, smooth, commutative group scheme locally of finite type over $\OK$ 
-(the ring of integers of $K$)
-with generic fibre $T$, that enjoys the N\'eron mapping property: if
+A lft-N\'eron model for $T$, denoted here by $\TT$, 
+is a separated, smooth, commutative group scheme locally of finite type over $\OK$ with generic fibre $T$, that enjoys the N\'eron mapping property: if
 $S$ is a smooth scheme over $\OK$ then every morphism $S_\eta \to T$
@@
 
-For each positive integer $d$, let $\TT_{d}$ be the group scheme obtained from $\TT$ by base change along $\OK \to \OK/\pK^d$, where $\pK$ is the maximal ideal in $\OK$. 
-Observe that $\OK/\pK^d$ is an Artin ring and $\TT_{d}$ is smooth and locally of finite type over $\OK/\pK^d$.
+\begin{definition}
+For each positive integer $d$, set $\TT_{d} \ceq \TT \times_\Spec{\OK} \Spec{A_d}$. Observe that $A_d$ is an Artin ring and $\TT_{d}$ is smooth and locally of finite type over $A_d$.
 %
@@
 the Greenberg functor to $\TT_{d}$; this is the \cdef{Greenberg transform of $\TT_d$}.
+\end{definition}
+
 See \cite{Greenberg:2} and \cite[Ch. 9, \S 6]{BLR} and the first few sections of \cite{Stasinski} for background on the Greenberg functor. The fundamental properties of $\GN{T}_d$ that we need are:
  \begin{enumerate}
-   \labitem{(GN.0)}{dFq} $\GN{T}_d(\Fq) = \TT(\OK/\pK^d)$, canonically.
+   \labitem{(GN.0)}{dFq} $\GN{T}_d(\Fq) = \TT(A_d)$, canonically.
   \labitem{(GN.1)}{GNd} $\GN{T}_d$ is a smooth, commutative group scheme, locally of finite type over $\Fq$, and the component group of $\GN{T}_d$ is geometrically finitely generated.
@@
 \begin{theorem}\label{thm:application}
-  Let $T$ be an algebraic torus over a non-Archimedean local field $K$.
-  Let $\GN{T}_d$ be as above.  For each positive integer $d$, the
-  Picard group of the category of quasicharacter sheaves on $\GN{T}_d$ is
-  canonically isomorphic to the group of characters of $T(K)$ of depth
-  less than $d$:
-  \[
-  \QCiso{\GN{T}_d} \iso \Hom_{< d}(T(K),\EEx).
+For each positive integer $d$, the trace of Frobenius 
+  \[
+t_{T,d}:  \QCiso{\GN{T}_d} \to \Hom_{< d}(T(K),\EEx)
+  \]
+is an isomomorphism from the additive functor
+\[T \mapsto \QCiso{\GN{T}}\]
+to the additive functor
+\[
+T \mapsto \Hom_{<d}(T(K),\EEx).
 \]
@@
   $\QCiso{\GN{T}_d} \iso \GN{T}_d(\Fq)^*$.
-  By \ref{dFq}, $\GN{T}_d(\Fq) \iso \TT(\OK/\pK^d)$ canonically.
+  By \ref{dFq}, $\GN{T}_d(\Fq) = \TT(A_d)$.
   To finish the proof we recall that the filtration of $T(K)$ used to
-  define depth has the property that $\TT(\OK/\pK^d) \cong T(K) / T(K)_d$
+  define depth has the property that $\TT(A_d) \cong T(K) / T(K)_d$
   \cite[Prop 5.2]{Yu}, so characters of $\GN{T}_d(\Fq)$ 
   are in bijection with characters of $T(K)$ vanishing on $T(K)_d$.
-  %Note that $d$ is a positive integer.  
+
+  What do we mean by saying
 \end{proof}
@@
 
-%\input{pro}
-We may also assemble the group $\Fq$-schemes $\TT_{d}$ into one
-glorious group pro-scheme over $\Fq$:
+\begin{definition}
+The \emph{Greenberg transform of the N\'eron model of $T$} is the group pro-scheme over $\Fq$ given by
 \begin{equation}\label{projlim}
@@
 \end{equation}
-This is the \cdef{Greenberg transform of the N\'eron model of $T$}.
- Some fundamental properties of $\GN{T}$ are:
- \begin{enumerate}
-   \labitem{(GN.2)}{T(K)} $\GN{T}(\Fq) = T(K)$, canonically;
-  \labitem{(GN.3)}{scheme} $\GN{T}$ is a commutative group scheme over $\Fq$.
-  \end{enumerate}
-This gives us a natural way to geometrize all quasicharacters of $T(K)$
-without reference to depth.
-Let \cdef{$\QC(\GN{T})$} be the ind-category $\varinjlim_{d\in \ZZ_{>0}} \QC(\GN{T}_d)$;
-we refer to objects of $\QC(\GN{T})$ as \cdef{quasicharacter sheaves on $T$}.
+Let$\QC(\GN{T})$ be the ind-category $\varinjlim_{d\in \ZZ_{>0}} \QC(\GN{T}_d)$;
+we refer to objects of $\QC(\GN{T})$ as \emph{quasicharacter sheaves for $T$}.
+\end{definition}
+
+\begin{remark}
+The Greenberg transform of the N\'eron model of $T$ is a commutative group scheme over $\Fq$.
+\end{remark}
+
+This gives us a natural way to geometrize all quasicharacters of $T(K)$ without reference to depth.
 
@@
 Let $T$ be an algebraic torus over a non-Archimedean local field $K$.
-The Picard group of the category $\QC(\GN{T})$ of quasicharacter sheaves on $T$ is canonically isomorphic to the group of quasicharacters of $T(K)$:
-  \[
- \QCiso{\GN{T}} \iso \Hom_\text{ad}(T(K),\EEx).
-  \]
+Then
+  \[
+ \QCiso{\GN{T}} \iso \Hom_\text{ad}(T(K),\EEx),
+  \]
+  canonically.
 \end{corollary}
@@
 \begin{proposition}
-Trace of Frobenius $\QCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$ 
-is a natural transformation between the following two additive functors from the additive category of algebraic tori over $K$ to the category of abelian groups: 
-\begin{enumerate}
-\item[$F_1$:] $T \mapsto \QCiso{\GN{T}}$;
-\item[$F_2$:] $T \mapsto \Hom_\text{ad}(T(K),\EEx)$.
-\end{enumerate}
+
 \end{proposition}

### 2013-08-14 shanghai.tex
All mention of picard groups removed, except for the introduction.

@@
 
-  The sequence of Picard groups is right-exact: it is exact at
+  The sequence of groups of isomorphism classes of quasicharacter sheaves is right-exact: it is exact at
   $\QCiso{G^0}$ by Proposition~\ref{prop:restriction}; and
@@
 \section{Greenberg of Neron}
-\label{sec:GN}
-
-%\subsection{The N\'eron locally finite type model for $T$}
+\label{sec:GAN}
+
+\Clifton{Motivate with comments about LLC for tori. Draw triangle. Reduction to GL(1) via induced tori. Comment about Japanese work. Comment about pro-quasi-algebraic. Combine with next section.}
+
+We have already seen that the trace of Frobenius defines a canonical homomorphism $\QCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
+In this section we show that this homomorphism is functorial, in the following sense.
+\Clifton{Fold this section into the main result on characters of local tori?}
 
@@
 
-%\input{application}
+\section{Application to quasicharacters of bounded depth}
+
 \begin{theorem}\label{thm:application}
-For each positive integer $d$, the trace of Frobenius 
-  \[
-t_{T,d}:  \QCiso{\GN{T}_d} \to \Hom_{< d}(T(K),\EEx)
-  \]
-is an isomomorphism from the additive functor
-\[T \mapsto \QCiso{\GN{T}}\]
+Let $d$ be a positive integer.
+\begin{enumerate}
+\item 
+For every algebraic torus $T$ over $K$, the trace of Frobenius 
+  \[
+\trFrob{T,d}:  \QCiso{\GN{T}_d} \to \Hom_{< d}(T(K),\EEx)
+  \]
+is an isomomorphism. 
+\item The isomorphism $\trFrob{T,d}$ is functorial in the following sense: $T \mapsto \trFrob{T,d}$ is a natural transformation
+from the additive functor
+\[T \mapsto \QCiso{\GN{T}_d}\]
 to the additive functor
@@
 \]
+\item
+For every finite Galois extension $L/K$ and for every algebraic torus $T$ over $K$, the following diagram commutes:
+\[
+\begin{tikzcd}
+\QCiso{\Gr(\underline{\Res_{L/K}(T_L)}_d)} \arrow[two heads]{r} \dar & \QCiso{\Gr({T}_d)} \dar\\
+\Hom_{<d}(T(L), \EEx) \arrow[two heads]{r} & \Hom_{<d}(T(K), \EEx)
+\end{tikzcd}
+\]
+\end{enumerate}
 \end{theorem}
@@
   By \ref{dFq}, $\GN{T}_d(\Fq) = \TT(A_d)$.
-  To finish the proof we recall that the filtration of $T(K)$ used to
+  Then we recall that the filtration of $T(K)$ used to
   define depth has the property that $\TT(A_d) \cong T(K) / T(K)_d$
@@
   are in bijection with characters of $T(K)$ vanishing on $T(K)_d$. 
-
-  What do we mean by saying
+  This shows that $\trFrob{T,d}$ is an isomorphism.
+
+  Next we show that this isomorphism is functorial.
+  When combined with the definition of $\QC(\GN{T})$ and Property~\ref{T(K)}, the first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$.
+When further combined with Lemma~\ref{prop:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.
+
+  Finally, we turn to restriction of scalars.
 \end{proof}
 
-%\section{Application to quasicharacters}
+\section{The geometrization of quasicharacters}
 
@@
 
-This gives us a natural way to geometrize all quasicharacters of $T(K)$ without reference to depth.
-
-\begin{corollary}
-Let $T$ be an algebraic torus over a non-Archimedean local field $K$.
-Then
-  \[
- \QCiso{\GN{T}} \iso \Hom_\text{ad}(T(K),\EEx),
-  \]
-  canonically.
+\begin{corollary}\label{cor:application}
+\begin{enumerate}
+\item 
+For every algebraic torus $T$ over $K$, the trace of Frobenius 
+  \[
+\trFrob{T}:  \QCiso{\GN{T}} \to \Hom_{\text{ad}}(T(K),\EEx)
+  \]
+is an isomomorphism. 
+\item The isomorphism $\trFrob{T}$ is functorial in the following sense: $T \mapsto \trFrob{T}$ is a natural transformation
+from the additive functor
+\[T \mapsto \QCiso{\GN{T}}\]
+to the additive functor
+\[
+T \mapsto \Hom_{\text{ad}}(T(K),\EEx).
+\]
+\item
+For every finite Galois extension $L/K$ and for every algebraic torus $T$ over $K$, the following diagram commutes:
+\[
+\begin{tikzcd}
+\QCiso{\underline{\Res_{L/K}(T_L)}} \arrow[two heads]{r} \dar & \QCiso{\GN{T}} \dar\\
+\Hom_{\text{ad}}(T(L), \EEx) \arrow[two heads]{r} & \Hom_{\text{ad}}(T(K), \EEx)
+\end{tikzcd}
+\]
+\end{enumerate}
 \end{corollary}
-
-\section{Functoriality}
-
-\Clifton{Motivate with comments about LLC for tori. Draw triangle. Reduction to GL(1) via induced tori. Comment about Japanese work. Comment about pro-quasi-algebraic. Combine with next section.}
-
-We have already seen that the trace of Frobenius defines a canonical homomorphism $\QCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
-In this section we show that this homomorphism is functorial, in the following sense.
-\Clifton{Fold this section into the main result on characters of local tori?}
-
-\begin{proposition}
-
-\end{proposition}
-
-\begin{proof}
-When combined with the definition of $\QC(\GN{T})$ and Property~\ref{T(K)}, the first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$.
-When further combined with Lemma~\ref{prop:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.
-\end{proof}
-
-\section{Geometrization of restriction of scalars of local fields}
 
@@
 and thus a functor on character sheaves through pullback.
-
-\begin{proposition}
-The following diagram commutes:
-\[
-\begin{tikzcd}
-\QCiso{\Res_{k'/k} \Gr(\TL)} \arrow[two heads]{r} \dar & \QCiso{\GN{T}} \dar\\
-\Hom(T(L), \EEx) \arrow[two heads]{r} & \Hom(T(K), \EEx)
-\end{tikzcd}
-\]
-\end{proposition}
 

### 2013-08-14 shanghai.tex
Describe Part 1 in introduction

@@
 
+In Part 1 of this paper we study the category $\QC(G)$ of quasicharacter sheaves.
+Since it is a rigid symmetric monoidal category,
+and the set of isomorphism classes $\QCiso{G}$ forms a group.
+Motivated by the sheaf-function dictionary for commutative, connected
+algebraic groups \cite{SGA4.5}, we explore the trace of Frobenius morphism
+\[
+\QCiso{G} \to \Hom(G(\Fq), \EEx)
+\]
+and show that it is an isomorphism.
+
 Quasicharacter sheaves of $G$ form a category, denoted by $\QC(G)$. In

### 2013-08-14 shanghai.tex
Working on the last section on transfer ....

--- 2013-08-14 shanghai.tex
@@
 \item
-For every finite Galois extension $L/K$ and for every algebraic torus $T$ over $K$, the following diagram commutes:
+For every finite Galois extension $L/K$ and for every algebraic torus $T$ over $K$, the following diagram commutes, where  . . . 
 \[
@@
 \end{theorem}
+
+Let $L/K$ be a finite Galois extension and let $K'/K$ be the maximal unramified subextension, with residue field $k'$.
+If $T$ is a torus over $K$, write $\TL$ for the N\'eron model of the base change $T_L$.
+Then there is a canonical isomorphism
+\[
+\Res_{k'/k} \Gr(\TL) \cong \Gr(\underline{\Res_{L/K}(T_L)}).
+\]
+The natural inclusion $T \hookrightarrow \Res_{L/K} T_L$ induces a map of $k$-schemes
+\[
+\GN{T} \hookrightarrow \Res_{k'/k} \Gr(\TL)
+\]
+and thus a functor on character sheaves through pullback.
 
@@
 The Greenberg transform of the N\'eron model of $T$ is a commutative group scheme over $\Fq$. 
+We will not use that fact in this paper. 
 \end{remark}
@@
   \[
-\trFrob{T}:  \QCiso{\GN{T}} \to \Hom_{\text{ad}}(T(K),\EEx)
+\trFrob{T}:  \QCiso{\GN{T}} \to \Hom_{\text{qc}}(T(K),\EEx)
   \]
@@
 \[
-T \mapsto \Hom_{\text{ad}}(T(K),\EEx).
+T \mapsto \Hom_{\text{qc}}(T(K),\EEx).
 \]
@@
 \begin{tikzcd}
-\QCiso{\underline{\Res_{L/K}(T_L)}} \arrow[two heads]{r} \dar & \QCiso{\GN{T}} \dar\\
-\Hom_{\text{ad}}(T(L), \EEx) \arrow[two heads]{r} & \Hom_{\text{ad}}(T(K), \EEx)
+\QCiso{\Gr(\underline{\Res_{L/K}(T_L)})} \arrow[two heads]{r} \dar & \QCiso{\Gr({T})} \dar\\
+\Hom_{\text{qc}}(T(L), \EEx) \arrow[two heads]{r} & \Hom_{\text{qc}}(T(K), \EEx)
 \end{tikzcd}
@@
 
-Let $L/K$ be a finite Galois extension and let $K'/K$ be the maximal unramified subextension, with residue field $k'$.
-If $T$ is a torus over $K$, write $\TL$ for the N\'eron model of the base change $T_L$.
-Then there is a canonical isomorphism
-\[
-\Res_{k'/k} \Gr(\TL) \cong \Gr(\underline{\Res_{L/K}(T_L)}).
-\]
-The natural inclusion $T \hookrightarrow \Res_{L/K} T_L$ induces a map of $k$-schemes
-\[
-\GN{T} \hookrightarrow \Res_{k'/k} \Gr(\TL)
-\]
-and thus a functor on character sheaves through pullback.
-
 \section{The transfer principle}
@@
 
-\Clifton{Work on motivation.}
-
 The techniques in this paper apply to all non-Archimdean local fields $K$ with residue field $k$, and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$ or on the ramification of $T$.
-Because of this, it is natural to ask if we can compare quasicharacter sheaves on $T$
-
-We recall the notion of $N$-congruent tori from \cite[\S 2]{CY}.  Suppose $T$ and $T'$
+Because of this, it is natural to ask if we can compare quasicharacter sheaves on $T$ and on $T'$ under conditions when there is a natural comparison between characters of $T(K)$ and of $T'(K')$.
+This comparison of has been made precise in \cite{CY}, building on ideas of \cite{Deligne:limites}.
+
+We recall the notion of $N$-congruent tori from  \cite{CY}*{\S 2}.  Suppose $T$ and $T'$
 are tori over non-Archimedian local fields $K$ and $K'$, splitting over $L$ and $L'$ respectively.
-
-\begin{definition}
- We say that $T$ and $T'$ are \emph{$N$-congruent} if there are isomorphisms
+Then $T$ and $T'$ are said to be \emph{$N$-congruent} if there are isomorphisms
  \begin{align*}
@@
  \end{enumerate}
-\end{definition}
-
+\[
+  \Hom_{<N}(T(K), \EEx) \to \Hom_{<N}(T'(K'),\EEx)
+ \]
+
+\begin{corollary}
+ Suppose that $T$ and $T'$ are $N$-congruent for $N > 3h$.  Then there is a canonical equivalence of categories
+ \[
+  \QC(\GN{T}_{N-3h}) \to \QC(\GN{T}'_{N-3h})
+ \]
+ determined by $\alpha, \beta$ and $\phi$ inducing the isomorphism
+ \[
+  \Hom(T(K) / T(K)_{N-3h}, \EEx) \to \Hom(T'(K') / T'(K')_{N-3h}, \EEx)
+ \]
+\end{corollary}
+
+\begin{proof}
 One of the main results of \cite{CY} gives an isomorphism of group schemes between
@@
 They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the
-Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite[\S 8.1]{CY}.
-They then prove the following theorem:
-
-\begin{theorem}[{\cite[Thm. 8.5]{CY}}]
+Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{CY}*{\S 8.1}
+They then prove the following theorem \cite{CY}*{Thm. 8.5}
  Suppose that $T$ and $T'$ are $N$-congruent for $N > 3h$.  Then there is a canonical isomorphism
@@
  determined by $\alpha, \beta$ and $\phi$.
-\end{theorem}
 
 As an immediate consequence of this theorem and Theorem \ref{thm:application} we have the following corollary:
-
-\begin{corollary}
- Suppose that $T$ and $T'$ are $N$-congruent for $N > 3h$.  Then there is a canonical equivalence of categories
- \[
-  \QC(\GN{T}_{N-3h}) \to \QC(\GN{T}'_{N-3h})
- \]
- determined by $\alpha, \beta$ and $\phi$ inducing the isomorphism
- \[
-  \Hom(T(K) / T(K)_{N-3h}, \EEx) \to \Hom(T'(K') / T'(K')_{N-3h}, \EEx)
- \]
-\end{corollary}
+\end{proof}
 
@@
 
+\bib{Deligne:limites}{article}{
+   author={Deligne, P.},
+   title={Les corps locaux de caract\'eristique $p$, limites de corps locaux
+   de caract\'eristique $0$},
+%   language={French},
+   conference={
+      title={Representations of reductive groups over a local field},
+   },
+   book={
+      series={Travaux en Cours},
+      publisher={Hermann},
+      place={Paris},
+   },
+   date={1984},
+   pages={119--157},
+%   review={\MR{771673 (86g:11068)}},
+}
+
 \bib{Greenberg:2}{article}{

### 2013-08-14 shanghai.tex
Describe part 2 in introduction

--- 2013-08-14 shanghai.tex
@@
 Let $G$ be a smooth commutative group scheme locally of finite
-type over $\Fq$; $G$ need not be reductive, connected, or of
+type over a finite field $\Fq$; $G$ need not be reductive, connected, or of
 finite type over $\Fq$. Fix a prime $\ell$ that does not divide
@@
 \]
-and show that it is an isomorphism.
+and show that it is an isomorphism in Theorem \ref{thm:snake}, assuming only
+that the component group of $G$ is finitely generated.
+
+We apply Theorem \ref{thm:snake} to the geometrization of quasicharacters
+of non-Archimedian tori in part 2.  Let $K$ be a non-Archimedian local field
+with finite residue field $\Fq$; we place no restriction on the characteristic of $K$.
+Write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$.
+Let $T$ be a maximal torus defined over $K$.  The N\'eron model $\TT$ of $T$
+is a smooth group scheme over $\OK$ with generic fiber $T$ and a canonical isomorphism
+$\TT(\OK) \cong T(K)$.  For each positive integer $d$, let $\GN{T}_d$ be the
+Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^d}$; the commutative
+group scheme $\GN{T}_d$ plays the r\^{o}le of $G$, above.  Theorem \ref{thm:application}
+now provides a geometrization of quasicharacters of $T$ in the form of a canonical isomorphism
+\[
+\QCiso{\GN{T}_d} 
+\iso
+\Hom_{< d}(T(K),\EEx)
+\] 
+between quasicharacters on $\GN{T}_d$ and characters of $T(K)$ with depth less than $d$.
 

### 2013-08-14 shanghai.tex
Reasons for geometrization in the introduction

@@
 
+We have not yet fully explored the applications of such a geometrization, but want to highlight
+some of the potential benefits of Theorem \ref{thm:application}.  Characters on $T$ have limited
+functoriality: they can be pulled back along maps to $T$, but it is less clear what to do with them
+in the presence of maps from $T$ to other reductive groups.  Sheaves, on the other hand, come
+equipped with a host of functors, including pushforward.
+
+In recent years various authors have applied Deligne-Lusztig representations to the
+local Langlands correspondence \cite{}.  The next step Lusztig took in studying representations
+of finite groups of Lie type was to define character sheaves for reductive groups over $\Fq$.
+We hope that our quasicharacter sheaves can provide a stepping stone to a similar theory for
+representations of $p$-adic groups.
+
+The scope of the Langlands program has grown explosively in the past several decades, and
+different parts of it apply to different kinds of representations.  In particular, the classic local Langlands
+correspondence addresses complex (or $\ell$-adic) representations of real and $p$-adic groups, while
+the geometric Langlands program aims at representations of groups in characteristic $p$.  The fact that
+characteristic $p$ group schemes arise as the space underlying quasicharacter sheaves, regardless of
+the characteristic of $K$, provides a potential bridge allowing the methods of the geometric Langlands
+program to be applied to the classic context.
+
+Finally, we are tantalized by the possibility of providing an alternate perspective on local class field theory
+through quasicharacter sheaves.  The local Langlands correspondence for tori provides an isomorphism
+\[
+\Hh^1(\Weil{K}, \hat{T}) \cong \Hom(T(K), \EEx).
+\]
+A geometric description of the resulting isomorphism $\Hh^1(\Weil{K}, \hat{T}) \cong \QCiso{\GN{T}}$
+would yield a different description of the Artin reciprocity map.
+
 Quasicharacter sheaves of $G$ form a category, denoted by $\QC(G)$. In

### 2013-08-14 shanghai.tex
Historical context and acknowledgements

@@
 
-Quasicharacter sheaves of $G$ form a category, denoted by $\QC(G)$. In
-fact, $\QC(G)$ is a rigid symmetric monoidal category, so isomorphism
-classes of quasicharacter sheaves on $G$ form a group, denoted by
-$\QCiso{G}$; this is the Picard group of the category of
-quasicharacter sheaves on $G$. Our application of quasicharacter sheaves to
-characters of algebraic tori over non-Archimedean local fields rests
-on finding the Picard group of quasicharacter sheaves on $G$, 
-for all smooth commutative group schemes $G$, locally of finite type over $\Fq$, 
-for which the geometric component group is finitely generated.
-
-We now say a few words about the group schemes 
-that appear in our geometrization of admissible
-characters of algebraic tori over local fields. Let $K$ be a
-non-Archimedean local field with residual field $\Fq$; we place no
-restrictions on the characteristic of $K$ -- in particular, it may be
-$0$ or not. Write $\OK$ for ring of integers of $K$ and $\pK$ for the
-maximal ideal in $\OK$.  Let $T$ be an algebraic torus defined over
-$K$. Let $\TT$ be a N\'eron model for $T$; recall that this is a
-smooth group scheme locally of finite type over $\OK$. For each
-positive integer $d$, let $\GN{T}_d$ be the Greenberg transform of
-$\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^d}$; the commutative group scheme $\GN{T}_d$
-plays the r\^{o}le of $G$, above.
-
-The main result of this paper is a canonical isomorphism
-\[
-\QCiso{\GN{T}_d} 
-\iso
-\Hom_{< d}(T(K),\EEx)
-\] 
-between the Picard group of the category of quasicharacter sheaves on
-$\GN{T}_d$ and the group of characters $T(K) \to \EEx$ of
-depth less than $d$.  Since these isomorphisms are compatible with
-respect to $d$, we also .....  \David{I'll do this when we're closer to being finished.}  
-%In particular, by
-%specializing to the case $T= \Gm{K}$ and by
-%choosing an isomorphism $\EE \approx \CC$ (unnatural though it may
-%be), we arrive at a model for the group of quasicharacters of
-%$K^\times$: the monoidal category of quasicharacter sheaves on the
-%Greenberg transform of the Neron model of
-%$\Gm{K}$.
-
-In this paper we show that the monoidal category of quasicharacter sheaves
-on the Greenberg transform of the locally finite type Neron model of
-$T$ provides an elegant, canonical model for the group of
-quasicharacters of $T(K)$, where $K$ is any non-Archimedean local
-field and $T$ is any algebraic torus over $K$.
-
-Acknowledgements: Masoud Kamgarpour, Pramod Achar, Hadi Salmasian.
+We want to situate the choice of term ``quasicharacter sheaf'' in a historical context.
+Analogous sheaves on connected, commutative algebraic groups were first studied
+by Deligne \cite{SGA4.5}, and more recently Drinfeld has referred to such objects
+as character sheaves.  Our quasicharacter sheaves evolved from this notion, and Theorem \ref{thm:snake}
+is a direct generalization of the sheaf-function dictionary to the case of commutative
+group schemes which are not necessarily connected or finite type.  The other main use
+of the term ``character sheaf'' traces back to Lusztig \cite{}.  Most of his energy is devoted to
+handling non-commutative groups and though he does define character sheaves for some
+non-connected groups, he restricts his attention to reductive groups with cyclic component group.
+For extensions of $\ZZ/n\ZZ$ by a torus, it is not difficult to relate his Frobenius-stable character
+sheaves to our quasicharacter sheaves.
+
+We close the introduction with a more detailed description of the structure of this paper.
+
+\subsection*{Acknowledgements}
+
+We would like to thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
+for allowing us to hijack our Research in Teams meeting at BIRS into a discussion of
+quasicharacter sheaves.  Their knowledge and help have been invaluable.
+
+We also gratefully acknowledge the financial support of PIMS and NSERC,
+and the hospitality of BIRS during our weeklong stay in May 2012.
+\David{Should these be abbreviated or written out in full?}
 

### 2013-08-14 shanghai.tex
Working on summary of sections

@@
 We close the introduction with a more detailed description of the structure of this paper.
+In Section \ref{sec:category} we define quasicharacter sheaves and give an interpretation of
+them as a Weil sheaf with a Galois action.
 

### 2013-08-14 shanghai.tex
Summary of sections

@@
 \renewcommand{\baselinestretch}{1.2}
-\usepackage[notcite]{showkeys}
+%\usepackage[notcite]{showkeys}
 \usepackage{hyperref}
@@
 \DeclareMathOperator{\W}{W}
-\newcommand{\Frob}[1]{{\operatorname{F}_{#1}}}
+\newcommand{\Frob}[1]{\operatorname{F}_{#1}}
 \DeclareMathOperator{\Aut}{Aut}
@@
 A quasicharacter sheaf on $G$ is a triple $\cs{L}\ceq
-(\gcs{L},\mu,\phi)$ where $\gcs{L}$ is a rank-$1$ local system on $\bG$ and $\mu: m^*
+(\gcs{L},\mu,\phi)$ where $\gcs{L}$ is a rank-$1$ $\ell$-adic local system on $\bG$ and $\mu: m^*
 \gcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gcs{L} \to \gcs{L}$ are isomorphisms;
@@
 In Part 1 of this paper we study the category $\QC(G)$ of quasicharacter sheaves.
-Since it is a rigid symmetric monoidal category,
-and the set of isomorphism classes $\QCiso{G}$ forms a group.
+Since it is a rigid symmetric monoidal category
+the set of isomorphism classes $\QCiso{G}$ forms a group.
 Motivated by the sheaf-function dictionary for commutative, connected
@@
 and show that it is an isomorphism in Theorem \ref{thm:snake}, assuming only
-that the component group of $G$ is finitely generated.
+that the geometric component group of $G$ is finitely generated.
 
 We apply Theorem \ref{thm:snake} to the geometrization of quasicharacters
-of non-Archimedian tori in part 2.  Let $K$ be a non-Archimedian local field
+of non-Archimedian tori in Part 2.  Let $K$ be a non-Archimedian local field
 with finite residue field $\Fq$; we place no restriction on the characteristic of $K$.
 Write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$.
-Let $T$ be a maximal torus defined over $K$.  The N\'eron model $\TT$ of $T$
+Let $T$ be a torus defined over $K$.  The N\'eron model $\TT$ of $T$
 is a smooth group scheme over $\OK$ with generic fiber $T$ and a canonical isomorphism
@@
 Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^d}$; the commutative
-group scheme $\GN{T}_d$ plays the r\^{o}le of $G$, above.  Theorem \ref{thm:application}
+group scheme $\GN{T}_d$ plays the r\^{o}le of $G$.  Theorem \ref{thm:application}
 now provides a geometrization of quasicharacters of $T$ in the form of a canonical isomorphism
@@
 \] 
-between quasicharacters on $\GN{T}_d$ and characters of $T(K)$ with depth less than $d$.
+between quasicharacter sheaves on $\GN{T}_d$ and characters of $T(K)$ with depth less than $d$.
+We also describe a group scheme $\GN{T}$ simultaneously geometrizing all quasicharacters of $T(K)$.
 
@@
 of the term ``character sheaf'' traces back to Lusztig \cite{}.  Most of his energy is devoted to
-handling non-commutative groups and though he does define character sheaves for some
-non-connected groups, he restricts his attention to reductive groups with cyclic component group.
+handling non-commutative groups; though he does define character sheaves for some
+non-connected groups he restricts his attention to reductive groups with cyclic component group.
 For extensions of $\ZZ/n\ZZ$ by a torus, it is not difficult to relate his Frobenius-stable character
@@
 In Section \ref{sec:category} we define quasicharacter sheaves and give an interpretation of
-them as a Weil sheaf with a Galois action.
+them as Weil sheaves with a Galois action.
+Section \ref{sec:Frob} introduces the trace of Frobenius homomorphism,
+one direction of the sheaf-function dictionary.
+We define pullbacks and products of quasicharacter sheaves in Section \ref{sec:pullback}, and use
+them to prove a functoriality result on the trace of Frobenius.
+In Section \ref{sec:basechange} we study how quasicharacter sheaves behave under base change
+and Weil restriction.
+Sections \ref{sec:bounded} and \ref{sec:finite} describe bounded and finite quasicharacter sheaves,
+two subcategories of $\QC(G)$.  These alternate descriptions of quasicharacter sheaves play a key
+role in the proof of Proposition \ref{prop:restriction}.
+In section \ref{sec:connected} we show that bounded and finite quasicharacter sheaves are the same
+as standard quasicharacter sheaves when $G$ is connected, and that trace of Frobenius is an isomorphism.
+We shift to \'etale group schemes $G$ in Section \ref{sec:etale} and give a more concrete interpretation
+of quasicharacter sheaves in this case.  Using a notion of global sections for quasicharacter sheaves,
+we give an isomorphism between $\QCiso{G}$ and $\Hh^1(\Weil{\Fq}, \Hom(G(\bFq), \EEx))$.
+Section \ref{sec:etalecohom} proves a result in Galois cohomology that shows that trace of Frobenius is
+an isomorphism for \'etale group schemes.
+In Section \ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
+induces an essentially surjective functor of quasicharacter sheaves.
+Section \ref{sec:snake} closes out Part \ref{part1} with the proof of the main theorem, that trace of Frobenius
+is an isomorphism for $G$ as long as the geometric component group is finitely generated.
+
+In Section \ref{sec:GAN} we introduce N\'eron models of tori and the Greenberg transform, which produce
+group schemes over $\Fq$ from algebraic tori $T$ over $K$.
+Section \ref{sec:bdchar} then uses Theorem \ref{thm:snake} to give a geometrization of characters of $T$
+of bounded depth.
+We give a reinterpretation of this result in Section \ref{sec:quasichar}, using a limit process to simultaneously
+geometrize all quasicharacters of $T$.  Sections \ref{sec:bdchar} and \ref{sec:quasichar} also include
+functoriality results that we hope to use in a future discussion of class field theory.
+Finally, we close the paper in Section \ref{sec:transfer} by discussing a transfer principle, which allows
+a geometric transfer of characters between characteristic $p$ tori to characteristic $0$ tori.
 
@@
 
-\Clifton{Declare definitions - about 10 of them.}
-
-\part{Smooth commutative group schemes lft over finite fields}
+\part{Smooth commutative group schemes lft over finite fields} \label{part1}
 
@@
 %\end{remark}
-
-\Clifton{Now that I'm working on the functoriality of trace of Frobenius, I  think the source of the functoriality is mainly this: $\QC$ is a stack. I'm thinking about this now.}
 
@@
 
-\section{Pull-back and products}\label{subsection:pullback}
+\section{Pull-back and products}\label{sec:pullback}
 
@@
 
-In the opposite direction, let $\Nm_{k'/k} : G(k') \to G(k)$ be the norm map and consider the group homomorhism:
-\Clifton{How is $\Nm$ defined?}
+In the opposite direction, let $\Nm_{k'/k} : G(k') \to G(k)$ be the norm map and consider the group homomorphism:
 \[
@@
 
-\section{Connected commutative algebraic groups}
+\section{Connected commutative algebraic groups} \label{sec:connected}
 
@@
   Let $f : G\to G$ be the Lang isogeny.
-  Recall that $\ker f = G(\Fq) = G^\Frob{\Fq}$; 
+  Recall that $\ker f = G(\Fq) = G^{\Frob{\Fq}}$; 
   in particular, the action of $\Gal(\bFq/\Fq)$ on $\ker f$ is trivial.
@@
 
-\section{Commutative \'etale group schemes}
+\section{Commutative \'etale group schemes} \label{sec:etale}
 
@@
   \[
-   \tau_\cs{L}(\Frob{\Fq}^n) \ceq \tau_\cs{L}(\Frob{\Fq})\cdot \,^\Frob{\Fq} \tau_\cs{L}(\Frob{\Fq}^{n-1}),
+   \tau_\cs{L}(\Frob{\Fq}^n) \ceq \tau_\cs{L}(\Frob{\Fq})\cdot \,^{\Frob{\Fq}} \tau_\cs{L}(\Frob{\Fq}^{n-1}),
   \]
@@
   $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
-  defined by $\tau_0(\Frob{\Fq}) = \,^\Frob{\Fq} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
+  defined by $\tau_0(\Frob{\Fq}) = \,^{\Frob{\Fq}} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
   so $\tau_2$ and $\tau_1$ are cohomologous. Thus
@@
 
-\section{On the cohomology of the dual of an etale group scheme}
+\section{On the cohomology of the dual of an etale group scheme} \label{sec:etalecohom}
 %\input{etale-2}
@@
   We first prove that $\rho$ is surjective.  Suppose that
-  $f \in \Hom(X^\Frob{\Fq}, \EEx).$ Since $\EEx$ is divisible
+  $f \in \Hom(X^{\Frob{\Fq}}, \EEx).$ Since $\EEx$ is divisible
   as an abelian group it is injective as a $\ZZ$-module and thus
-  $\Ext^1_{\ZZ}(X/X^\Frob{\Fq}, \EEx) = 0$.  Applying the functor
+  $\Ext^1_{\ZZ}(X/X^{\Frob{\Fq}}, \EEx) = 0$.  Applying the functor
   $\Hom(\mbox{---}, \EEx)$ to
@@
   \begin{tikzcd}
-  0 \rar & X^\Frob{\Fq} \rar & X \rar & X/X^\Frob{\Fq} \rar & 0
+  0 \rar & X^{\Frob{\Fq}} \rar & X \rar & X/X^{\Frob{\Fq}} \rar & 0
   \end{tikzcd}
@@
 
-\section{Restriction to the identity component}
+\section{Restriction to the identity component} \label{sec:restriction}
 
@@
 In this section we show that this homomorphism is functorial, in the following sense.
-\Clifton{Fold this section into the main result on characters of local tori?}
 
@@
 
-\section{Application to quasicharacters of bounded depth}
+\section{Application to quasicharacters of bounded depth} \label{sec:bdchar}
 
@@
 
-\section{The geometrization of quasicharacters}
+\section{The geometrization of quasicharacters} \label{sec:quasichar}
 
@@
 
-\section{The transfer principle}
+\section{The transfer principle} \label{sec:transfer}
 

### 2013-08-15 shanghai.tex
Added comments to the end of the section on the connected case.
Other small changes, too.

@@
 
-\begin{definition}\label{def:GC}
+\begin{definition}\label{def:QC}
 A \emph{quasicharacter sheaf on $G$} is a triple
@@
 \end{enumerate}
-In short, a quasicharacter sheaf on $G$  is a rank-$1$ Weil local system $(\gcs{L},\phi)$ on $G$ equipped with an isomorphism $m^* (\gcs{L},\phi) \to (\gcs{L},\phi)\boxtimes (\gcs{L},\phi)$.
+%In short, a quasicharacter sheaf on $G$  is a rank-$1$ Weil local system $(\gcs{L},\phi)$ on $G$ equipped with an isomorphism $m^* (\gcs{L},\phi) \to (\gcs{L},\phi)\boxtimes (\gcs{L},\phi)$.
 
@@
 \end{proof}
+
+As Proposition~\ref{prop:connected} shows, when $G$ is a connected algebraic group over $\Fq$, it is appropriate to replace quasicharacter sheaves on $G$ with the conceptually simpler category $\QCf(G)$ of finite quasicharacter sheaves on $G$.
+In this context, finite quasicharacter sheaves may also be apprehended as \emph{certain} $\ell$-adic characters of fundamental group $\pi_1(G,{\bar e})$.
+As explained in \cite{Kamgarpour}*{\S~2}, the relevant characters of $\pi_1(G,{\bar e})$ are precisely those that factor through the quotient of $\pi_1(G,{\bar e})$ denoted there by $\Pi_\text{disc}(G)$.
+%\[\pi_1(G,{\bar e}) \to \Pi_\text{et}(G) \to \Pi_\text{et}(G)_{\Gal(\bFq/\Fq)} = \Pi_\text{disc}(G)\]
+From this is is apparent that the category of discrete isogenies to $G$ forms a Galois category, in the sense of \cite{SGA1}*{Expos\'e V, \S 4}.
+Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$, as shown in \cite{Kamgarpour}*{App'x B}, this provides an alternate proof of $\QCiso{G} \to G(\Fq)^*$.
+
+In principle, something similar is possible in the more general context of this paper, where $G$ is a smooth group scheme lft over $\Fq$, to which we now return.
+Every quasicharacter sheaf $(\gcs{L},\mu,\phi)$ on $G$ determines a Weil sheaf $(\gcs{L},\phi)$ on $G$.
+So, if we choose a geometric point ${\bar g}_x$ in each component $\bG^x$ of $G$, then this choice can be used to convert the Weil sheaf $(\gcs{L},\phi)$ into an $\ell$-adic character of $\prod_{x\in \pi_0(\bG)}\W(\bG^x, {\bar g}_x)$.
+It proved cumbersome, however, to manage various choices of families of base points and track the action of $\Gal(\bFq/\Fq)$ on this (generally) infinite product of Weil groups, and even more difficult to identity the relevant quotient of this group.
+In this light, Definition~\ref{def:QC} seemed simple.
 
@@
 
-With Theorem~\ref{thm:snake} on hand, we can see why neither bounded quasicharacter sheaves nor finite quasicharacter sheaves are up to the task of geometrizing characters of $G(\Fq)$ in the generality we need.
+With Theorem~\ref{thm:snake} on hand, 
+we can see why neither bounded quasicharacter sheaves 
+nor finite quasicharacter sheaves are up to the task of 
+geometrizing characters of $G(\Fq)$ in the generality we need.  
 %
 Consider the case when $G$ is the discrete etale group scheme $\ZZ$. 
-Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ and let $\cs{L}$ be a quasicharacter sheaf in the isomorphism class corresponding to the character $\chi : G(\Fq) \to \EEx$ under Theorem~\ref{thm:snake}.
-Then $\trFrob{\cs{L}}(1) = \ell$.
-Suppose $\cs{L}$ was a bounded quasicharacter sheaf.
-Then the restriction of $\cs{L}$ to the connected component $1\in G$ would be a rank-1 local system on $1$, thus an $\ell$-adic character $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with $\rho_1(\Frob{\Fq}) = \ell$.
-But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, while $\rho_1(\pi_1(1,{\bar 1}))$ is not compact (it contains $\ell^\ZZ$).
-Since the Weil sheaf $\gcs{L}$ does not descend to a local system on $G$, the  quasicharacter sheaf$\cs{L}$ is not a bounded quasicharacter sheaf.
+Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ 
+and let $\cs{L}$ be a quasicharacter sheaf in the isomorphism class 
+corresponding to the character $\chi : G(\Fq) \to \EEx$ under Theorem~\ref{thm:snake}. 
+Then $\trFrob{\cs{L}}(1) = \ell$. Suppose $\cs{L}$ was a bounded quasicharacter sheaf. 
+Then the restriction of $\cs{L}$ to the connected component $1\in G$ 
+would be a rank-1 $\ell$-adic local system on $1$, 
+thus an $\ell$-adic character $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with $\rho_1(\Frob{\Fq}) = \ell$. But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, 
+while $\rho_1(\pi_1(1,{\bar 1}))$ is not compact in $\EEx$ (it contains $\ell^\ZZ$). 
+So the Weil sheaf $\gcs{L}$ does not descend to a local system on $G$.
+It follows that the quasicharacter sheaf $\cs{L}$ is not a bounded quasicharacter sheaf.
 %
-We can play the same game with the character $\chi : G(\Fq) \to \EEx$ defined by $\chi(1) = 1+\ell$.
-In this case, the corresponding geometric character $\cs{L}$ is bounded but not finite, since $1+\ell$ is not a root of unity.
-
+We can play the same game with the character $\chi : G(\Fq) \to \EEx$ 
+defined by $\chi(1) = 1+\ell$. In this case, the corresponding quasicharacter sheaf $\cs{L}$ is bounded but not finite, since $1+\ell$ is not a root of unity. 
+%
 These simple examples illustrate why the categories $\QCb(G)$ and $\QCf(G)$ are inadequate to geometrize characters of $G(\Fq)$.
@@
 Let $K$ be a non-Archimedean local field with residue field $\Fq$.
-Note that we place no restriction on the characteristic of $K$. 
+We place no restriction on the characteristic of $K$. 
 We write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$. 
@@
 Let $T$ be an algebraic torus over $K$.
-We write $\Hom_{< d}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $d$ and $\Hom_\text{qc}(T(K),\EEx)$ for the group of quasicharacters of $T(K)$.
+We write $\Hom_{< d}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $d$ 
+and $\Hom_{<\infty}(T(K),\EEx)$ for the group of characters of $T(K)$ of finite-depth.
 
 \section{Greenberg of Neron}
-\label{sec:GAN}
-
-\Clifton{Motivate with comments about LLC for tori. Draw triangle. Reduction to GL(1) via induced tori. Comment about Japanese work. Comment about pro-quasi-algebraic. Combine with next section.}
-
-We have already seen that the trace of Frobenius defines a canonical homomorphism $\QCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
-In this section we show that this homomorphism is functorial, in the following sense.
+\label{sec:GN}
 
@@
 Let \cdef{$\GN{T}_{d} = \Gr(\TT_d)$} be the group scheme over $\Fq$ produced by applying
-the Greenberg functor to $\TT_{d}$; this is the \cdef{Greenberg transform of $\TT_d$}.
+the Greenberg functor to $\TT_{d}$; this is the \emph{Greenberg transform of $\TT_d$}.
 \end{definition}
@@
 \section{Application to quasicharacters of bounded depth} \label{sec:bdchar}
+
+\Clifton{Motivate with comments about LLC for tori. Draw triangle. Reduction to GL(1) via induced tori. Comment about Japanese work. Comment about pro-quasi-algebraic. }
 
@@
   Next we show that this isomorphism is functorial.
-  When combined with the definition of $\QC(\GN{T})$ and Property~\ref{T(K)}, the first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$.
+The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$.
 When further combined with Lemma~\ref{prop:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.
@@
 
-\bib{SGA1a}{book}{
-   author={Grothendieck, Alexander},
-   title={Rev\^etements \'etales et groupe fondamental. Fasc. I: Expos\'es 1
-   \`a 5},
-   series={S\'eminaire de G\'eom\'etrie Alg\'ebrique},
-   volume={1960/61},
-   publisher={Institut des Hautes \'Etudes Scientifiques},
+\bib{SGA1}{collection}{
+   title={Rev\^etements \'etales et groupe fondamental (SGA 1)},
+%   language={French},
+   series={Documents Math\'ematiques (Paris), 3},
+   note={S\'eminaire de g\'eom\'etrie alg\'ebrique du Bois Marie 1960--61.
+   [Algebraic Geometry Seminar of Bois Marie 1960-61];
+   Directed by A. Grothendieck;
+   With two papers by M. Raynaud;
+   Updated and annotated reprint of the 1971 original [Lecture Notes in
+   Math., 224, Springer, Berlin;  MR0354651 (50 \#7129)]},
+   publisher={Soci\'et\'e Math\'ematique de France},
    place={Paris},
-   date={1963},
-%   pages={iv+143 pp. (not consecutively paged) (loose errata)},
-%   review={\MR{0217087 (36 \#179a)}},
+   date={2003},
+   pages={xviii+327},
+%  isbn={2-85629-141-4},
+%   review={\MR{2017446 (2004g:14017)}},
 }

### 2013-08-15 shanghai.tex
Still working on Part 2.
Moving to a different computer.

@@
 \]
-\item
-For every finite Galois extension $L/K$ and for every algebraic torus $T$ over $K$, the following diagram commutes, where  . . . 
-\[
-\begin{tikzcd}
-\QCiso{\Gr(\underline{\Res_{L/K}(T_L)}_d)} \arrow[two heads]{r} \dar & \QCiso{\Gr({T}_d)} \dar\\
-\Hom_{<d}(T(L), \EEx) \arrow[two heads]{r} & \Hom_{<d}(T(K), \EEx)
-\end{tikzcd}
-\]
 \end{enumerate}
 \end{theorem}
-
-Let $L/K$ be a finite Galois extension and let $K'/K$ be the maximal unramified subextension, with residue field $k'$.
-If $T$ is a torus over $K$, write $\TL$ for the N\'eron model of the base change $T_L$.
-Then there is a canonical isomorphism
-\[
-\Res_{k'/k} \Gr(\TL) \cong \Gr(\underline{\Res_{L/K}(T_L)}).
-\]
-The natural inclusion $T \hookrightarrow \Res_{L/K} T_L$ induces a map of $k$-schemes
-\[
-\GN{T} \hookrightarrow \Res_{k'/k} \Gr(\TL)
-\]
-and thus a functor on character sheaves through pullback.
 
@@
 When further combined with Lemma~\ref{prop:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.
-
-  Finally, we turn to restriction of scalars.
 \end{proof}
+
+For every finite Galois extension $L/K$ and for every algebraic torus $T$ over $K$, the following diagram commutes, where  . . . 
+\[
+\begin{tikzcd}
+\QCiso{\Gr(\underline{\Res_{L/K}(T_L)}_d)} \arrow[two heads]{r} \dar & \QCiso{\Gr({T}_d)} \dar\\
+\Hom_{<d}(T(L), \EEx) \arrow[two heads]{r} & \Hom_{<d}(T(K), \EEx)
+\end{tikzcd}
+\]
+Let $L/K$ be a finite Galois extension and let $K'/K$ be the maximal unramified subextension, with residue field $k'$.
+If $T$ is a torus over $K$, write $\TL$ for the N\'eron model of the base change $T_L$.
+Then there is a canonical isomorphism
+\[
+\Res_{k'/k} \Gr(\TL) \cong \Gr(\underline{\Res_{L/K}(T_L)}).
+\]
+The natural inclusion $T \hookrightarrow \Res_{L/K} T_L$ induces a map of $k$-schemes
+\[
+\GN{T} \hookrightarrow \Res_{k'/k} \Gr(\TL)
+\]
+and thus a functor on character sheaves through pullback.
 

### 2013-08-15 shanghai.tex
Added a final section: toward geometric reciprocity. Part 2 still needs work, though.

@@
 \documentclass[11pt]{amsart}
-\title[Geometrization of characters of tori]{Geometrization of characters of tori over non-Archimedean local fields}
+\title[Geometrization of characters of tori]{Geometrization of characters of tori over non-archimedean local fields}
 \usepackage[british]{babel}
@@
 \renewcommand\MR{\relax}
-\usepackage{xypic}
+%\usepackage{xypic}
 \usepackage{textcomp}
@@
   classes of quasicharacter sheaves on the Greenberg transform of the Néron
-  model of $T$, where $K$ is any non-Archimdean local field and $T$ is
+  model of $T$, where $K$ is any non-archimdean local field and $T$ is
   any algebraic torus over $K$.
@@
 We apply Theorem \ref{thm:snake} to the geometrization of quasicharacters
-of non-Archimedian tori in Part 2.  Let $K$ be a non-Archimedian local field
+of non-archimedian tori in Part 2.  Let $K$ be a non-archimedian local field
 with finite residue field $\Fq$; we place no restriction on the characteristic of $K$.
@@
 
-In Section \ref{sec:GAN} we introduce N\'eron models of tori and the Greenberg transform, which produce
+In Section \ref{sec:GN} we introduce N\'eron models of tori and the Greenberg transform, which produce
 group schemes over $\Fq$ from algebraic tori $T$ over $K$.
@@
 %In short, a quasicharacter sheaf on $G$  is a rank-$1$ Weil local system $(\gcs{L},\phi)$ on $G$ equipped with an isomorphism $m^* (\gcs{L},\phi) \to (\gcs{L},\phi)\boxtimes (\gcs{L},\phi)$. 
+\end{definition}
 
@@
 \end{enumerate}
-\end{definition}
 
@@
 
-\begin{definition}
+\begin{definition}\label{def:trFrob}
 Let $(\gcs{L},\phi)$ be a Weil sheaf on $G$. on constructible $\ell$-adic sheaf on $\bG$. Every $g\in G(\Fq)$
@@
   \begin{tikzcd}[row sep=20, column sep=30]
-   \QCiso{G} \rar{f^*} \arrow[swap]{d}{\trFrob{G}} & \QCiso{H} \dar{t_H} \\
+   \QCiso{G} \rar{f^*} \arrow[swap]{d}{\trFrob{G}} & \QCiso{H} \dar{\trFrob{H}} \\
    G(\Fq)^* \rar & H(\Fq)^*
@@
 \begin{tikzcd}[column sep=60]
-\arrow{d}{t_{G_1} \times t_{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes} & \arrow{d}{t_{G_1\times G_2}} \QCiso{G_1\times G_2}\\
+\arrow{d}{\trFrob{G_1} \times \trFrob{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes} & \arrow{d}{\trFrob{G_1\times G_2}} \QCiso{G_1\times G_2}\\
 (G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
@@
 \begin{tikzcd}
-\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota} \dar[swap]{t_{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{t_G} \\
+\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota} \dar[swap]{\trFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\trFrob{G}} \\
 G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
@@
 \begin{tikzcd}
-\QCiso{G'} \dar{t_{G'}} \rar & \QCiso{\Res_{k'/k} G'} \dar{t_{\Res_{k'/k} G'}} \\
+\QCiso{G'} \dar{\trFrob{G'}} \rar & \QCiso{\Res_{k'/k} G'} \dar{\trFrob{\Res_{k'/k} G'}} \\
  G'(k')^* \rar & (\Res_{k'/k}G')(k)^*
@@
 
-As Proposition~\ref{prop:connected} shows, when $G$ is a connected algebraic group over $\Fq$, it is appropriate to replace quasicharacter sheaves on $G$ with the conceptually simpler category $\QCf(G)$ of finite quasicharacter sheaves on $G$.
+As Proposition~\ref{prop:connected} shows, 
+when $G$ is a connected algebraic group over $\Fq$, 
+it is appropriate to replace quasicharacter sheaves on $G$ 
+with the conceptually simpler category $\QCf(G)$ of finite quasicharacter sheaves on $G$. 
 In this context, finite quasicharacter sheaves may also be apprehended as \emph{certain} $\ell$-adic characters of fundamental group $\pi_1(G,{\bar e})$. 
-As explained in \cite{Kamgarpour}*{\S~2}, the relevant characters of $\pi_1(G,{\bar e})$ are precisely those that factor through the quotient of $\pi_1(G,{\bar e})$ denoted there by $\Pi_\text{disc}(G)$.
+As explained in \cite{Kamgarpour}*{\S~2}, 
+the relevant characters of $\pi_1(G,{\bar e})$ are precisely those 
+that factor through a particular quotient of $\pi_1(G,{\bar e})$ 
+denoted there by $\Pi_\text{disc}(G)$.
 %\[\pi_1(G,{\bar e}) \to \Pi_\text{et}(G) \to \Pi_\text{et}(G)_{\Gal(\bFq/\Fq)} = \Pi_\text{disc}(G)\]
-From this is is apparent that the category of discrete isogenies to $G$ forms a Galois category, in the sense of \cite{SGA1}*{Expos\'e V, \S 4}.
+From this it is apparent that the category of discrete isogenies to $G$ is a Galois category, in the sense of \cite{SGA1}*{Expos\'e V, \S 4}.
 Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$, as shown in \cite{Kamgarpour}*{App'x B}, this provides an alternate proof of $\QCiso{G} \to G(\Fq)^*$.
 
-In principle, something similar is possible in the more general context of this paper, where $G$ is a smooth group scheme lft over $\Fq$, to which we now return.
-Every quasicharacter sheaf $(\gcs{L},\mu,\phi)$ on $G$ determines a Weil sheaf $(\gcs{L},\phi)$ on $G$.
-So, if we choose a geometric point ${\bar g}_x$ in each component $\bG^x$ of $G$, then this choice can be used to convert the Weil sheaf $(\gcs{L},\phi)$ into an $\ell$-adic character of $\prod_{x\in \pi_0(\bG)}\W(\bG^x, {\bar g}_x)$.
-It proved cumbersome, however, to manage various choices of families of base points and track the action of $\Gal(\bFq/\Fq)$ on this (generally) infinite product of Weil groups, and even more difficult to identity the relevant quotient of this group.
-In this light, Definition~\ref{def:QC} seemed simple.
+In principle, something similar is possible in the more general 
+context of this paper, where $G$ is a smooth group scheme 
+locally of finite type over $\Fq$, to which we now return. 
+Every quasicharacter sheaf $(\gcs{L},\mu,\phi)$ on $G$ 
+determines a Weil sheaf $(\gcs{L},\phi)$ on $G$. 
+So, if we choose a geometric point ${\bar g}_x$ in each component $\bG^x$ of $G$, then this choice can be used to convert 
+the Weil sheaf $(\gcs{L},\phi)$ into an $\ell$-adic character of $\prod_{x\in \pi_0(\bG)}\W(\bG^x, {\bar g}_x)$. 
+It proved cumbersome, however, to manage various 
+choices of families of base points and track the action 
+of $\Gal(\bFq/\Fq)$ on this (generally) infinite product of 
+Weil groups, and difficult to identify the relevant quotient of this group. Viewed in this light, Definition~\ref{def:QC} seemed comparatively simple.
 
@@
   \end{equation}
-  Note that if $x$ is fixed by $\Frob{k}$ then $\tau_\cs{L}(\Frob{\Fq})(x)$ is just $t_\cs{L}(x)$, so the restriction of
-  $\tau_\cs{L}(\Frob{k})$ to $G(k)$ is just $t_\cs{L}$.
+  Note that if $x$ is fixed by $\Frob{k}$ then $\tau_\cs{L}(\Frob{\Fq})(x)$ is just $\trFrob{\cs{L}}(x)$, so the restriction of
+  $\tau_\cs{L}(\Frob{k})$ to $G(k)$ is just $\trFrob{\cs{L}}$.
   In general, conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
@@
 
+We saw, in Proposition~\ref{prop:functorialG}, that the trace of Frobenius  $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
+Our main result regarding quasicharacter sheaves shows that trace of Frobenius is an isomorphism in the case that we care about.
+
 %\input{snake}
@@
   is an isomorphism of groups.
-  \Clifton{Address functoriality, here?}
 \end{theorem}
@@
   \begin{tikzcd}[row sep=30]
-    {}& \ker t_{\pi_0(G)} \dar & \arrow[dashed]{d} \ker \trFrob{G} & \ker t_{G^0} \dar & \\
-    0 \rar & \QCiso{\pi_0(G)} \rar \dar{t_{\pi_0(G)}}
-    & \QCiso{G} \rar \dar{\trFrob{G}} & \QCiso{G^0} \rar \dar{t_{G^0}} & 0\\
+    {}& \ker \trFrob{\pi_0(G)} \dar & \arrow[dashed]{d} \ker \trFrob{G} & \ker \trFrob{G^0} \dar & \\
+    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\trFrob{\pi_0(G)}}
+    & \QCiso{G} \rar \dar{\trFrob{G}} & \QCiso{G^0} \rar \dar{\trFrob{G^0}} & 0\\
     0 \rar & \pi_0(G)(\Fq)^* \rar \dar
     & \arrow[dashed]{d} G(\Fq)^* \rar & G^0(\Fq)^* \rar \dar & 0\\
-    & \coker t_{\pi_0(G)} & \coker \trFrob{G} &  \coker t_{G^0} &
+    & \coker \trFrob{\pi_0(G)} & \coker \trFrob{G} &  \coker \trFrob{G^0} &
   \end{tikzcd}
@@
   Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.  By
-  Proposition~\ref{prop:connected}, $\ker t_{G^0} =0$ and $\coker t_{G^0}=0$.
-  By Propositions~\ref{prop:etale} and \ref{prop:X}, $\ker t_{\pi_0(G)}=0$
-  and $\coker t_{\pi_0(G)}=0$.
+  Proposition~\ref{prop:connected}, $\ker \trFrob{G^0} =0$ and $\coker \trFrob{G^0}=0$.
+  By Propositions~\ref{prop:etale} and \ref{prop:X}, $\ker \trFrob{\pi_0(G)}=0$
+  and $\coker \trFrob{\pi_0(G)}=0$.
 
@@
   commutes (by Proposition~\ref{prop:pullback}), the bottom sequence
-  is exact at $G(\Fq)^*$ and $\coker t_{\pi_0(G)} =0$
+  is exact at $G(\Fq)^*$ and $\coker \trFrob{\pi_0(G)} =0$
   (by Propositions~\ref{prop:etale} and \ref{prop:X}) and
@@
 
-Let $K$ be a non-Archimedean local field with residue field $\Fq$.
+Let $K$ be a non-archimedean local field with residue field $\Fq$.
 We place no restriction on the characteristic of $K$. 
@@
 We write $\Hom_{< d}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $d$ 
-and $\Hom_{<\infty}(T(K),\EEx)$ for the group of characters of $T(K)$ of finite-depth.
+and $\Hom_{<\infty}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth.
 
@@
 
-\begin{definition}
+\begin{definition}\label{def:GN}
 For each positive integer $d$, set $\TT_{d} \ceq \TT \times_\Spec{\OK} \Spec{A_d}$. Observe that $A_d$ is an Artin ring and $\TT_{d}$ is smooth and locally of finite type over $A_d$.
 %
-Let \cdef{$\GN{T}_{d} = \Gr(\TT_d)$} be the group scheme over $\Fq$ produced by applying
+Let $\GN{T}_{d} = \Gr(\TT_d)$ be the group scheme over $\Fq$ produced by applying
 the Greenberg functor to $\TT_{d}$; this is the \emph{Greenberg transform of $\TT_d$}.
@@
 \section{Application to quasicharacters of bounded depth} \label{sec:bdchar}
-
-\Clifton{Motivate with comments about LLC for tori. Draw triangle. Reduction to GL(1) via induced tori. Comment about Japanese work. Comment about pro-quasi-algebraic. }
 
@@
 
-For every finite Galois extension $L/K$ and for every algebraic torus $T$ over $K$, the following diagram commutes, where  . . . 
-\[
-\begin{tikzcd}
-\QCiso{\Gr(\underline{\Res_{L/K}(T_L)}_d)} \arrow[two heads]{r} \dar & \QCiso{\Gr({T}_d)} \dar\\
-\Hom_{<d}(T(L), \EEx) \arrow[two heads]{r} & \Hom_{<d}(T(K), \EEx)
-\end{tikzcd}
-\]
-Let $L/K$ be a finite Galois extension and let $K'/K$ be the maximal unramified subextension, with residue field $k'$.
-If $T$ is a torus over $K$, write $\TL$ for the N\'eron model of the base change $T_L$.
-Then there is a canonical isomorphism
-\[
-\Res_{k'/k} \Gr(\TL) \cong \Gr(\underline{\Res_{L/K}(T_L)}).
-\]
-The natural inclusion $T \hookrightarrow \Res_{L/K} T_L$ induces a map of $k$-schemes
-\[
-\GN{T} \hookrightarrow \Res_{k'/k} \Gr(\TL)
-\]
-and thus a functor on character sheaves through pullback.
-
 \section{The geometrization of quasicharacters} \label{sec:quasichar}
@@
 
-\section{The transfer principle} \label{sec:transfer}
+\section{Transfer of quasicharacter sheaves} \label{sec:transfer}
 
@@
 
-The techniques in this paper apply to all non-Archimdean local fields $K$ with residue field $k$, and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$ or on the ramification of $T$.
+The techniques in this paper apply to all non-archimdean local fields $K$ with residue field $k$, and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$ or on the ramification of $T$.
 Because of this, it is natural to ask if we can compare quasicharacter sheaves on $T$ and on $T'$ under conditions when there is a natural comparison between characters of $T(K)$ and of $T'(K')$.
@@
 We recall the notion of $N$-congruent tori from  \cite{CY}*{\S 2}.  Suppose $T$ and $T'$
-are tori over non-Archimedian local fields $K$ and $K'$, splitting over $L$ and $L'$ respectively.
+are tori over non-archimedian local fields $K$ and $K'$, splitting over $L$ and $L'$ respectively.
 Then $T$ and $T'$ are said to be \emph{$N$-congruent} if there are isomorphisms
@@
 \end{proof}
+
+\section{Toward geometric reciprocity}
+
+As indicated in the Introduction, we are tantalized by the idea that quasicharacter sheaves for $T$ may play a key role in a geometric, categorial version of the local Langlands correspondence for algebraic tori over non-archimedean local fields.
+We anticipate that, as with the local Langlands correspondence for algebraic tori, it will be possible to reduce the essential points of the argument to the case $T= \Gm{K}$, provided that the category of quasicharacter sheaves behaves properly with regard to Weil restriction; see \cite{Yu:tori}*{Thm 7.5 (2)}.
+The next proposition shows that the category of quasicharacter sheaves does indeed behave properly with regard to Weil restriction.
+
+\begin{proposition}
+Let $K'/K$ be a finite Galois extension; 
+let $k'/k$ be the corresponding finite Galois extension of residue fields.
+Let $T$ be an algebraic torus over $K$ and 
+set $T' = T \times_\Spec{K} \Spec{K'}$.  
+The natural inclusion $T \hookrightarrow \Res_{K'/K} T'$ 
+induces a map of $k$-schemes
+\[
+\GN{T} \hookrightarrow \Res_{k'/k} \GN{T}'
+\]
+and thus a functor on quasicharacter sheaves through pullback.
+\[
+\QC(\Res_{k'/k} \GN{T}') \to \QC(\GN{T}).
+\]
+Through trace of Frobenius, this functor induces the homomorphism
+\[
+\begin{tikzcd}[column sep=60]
+\Hom_{<\infty}(T(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{T(K)}} &\Hom_{<\infty}(T(K), \EEx).
+\end{tikzcd}
+\] 
+\end{proposition}
+
+\begin{proof}
+\Clifton{Under construction, pending the proofs of the results in the base change section}
+There is a canonical isomorphism
+\[
+\Res_{k'/k} \Gr(\TL) \cong \Gr(\underline{\Res_{L/K}(T_L)}).
+\]
+\end{proof}
+
+This paper has shown how quasicharacter sheaves on the Greenberg transform of the Neron model of $T$ determine admissible characters of $T(K)$, and vice versa, functorially.
+When coupled with the reciprocity map $\text{rec}_T $ for $T$, which enjoys the same functorial properties, it follows that quasicharacter sheaves for $T$ determine Langlands parameters for $T$, and vice versa, functorially.
+\[
+\begin{tikzcd}
+\ & \arrow[swap]{dl}{\trFrob{G}} \QCiso{\GN{T}} \arrow[dashed]{dr}  & \\
+\Hom_{<\infty}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(K,\hat{T}) \\
+\end{tikzcd}
+\]
+We suspect that it is possible to extract Langlands parameters from quasicharacter sheaves directly; results in this paper reduce the problem to the case $T=\Gm{K}$.
+In that case, our suspicions are all but confirmed by the class field theory of Serre-Hasewinkel \cite{Serre:isogenies} as revisited in \cite{Suzuki&Yoshida:refinement}.
+What remains is a careful comparison of quasicharacter sheaves for $\Gm{K}$ and certain local systems on the fpqc-site of the pro-quasi-algebraic varieties appearing in \cite{Suzuki&Yoshida:refinement}.
 
@@
  date={1979},
- series={Lecture Notes in Mathematics}
+ series={Lecture Notes in Mathematics},
  number={723}
@@
 
-\bib{Greenberg:2}{article}{
-   author={Greenberg, Marvin J.},
-   title={Schemata over local rings. II},
-   journal={Ann. of Math. (2)},
-   volume={78},
-   date={1963},
-   pages={256--266},
-%   issn={0003-486X},
-%   review={\MR{0156855 (28 \#98)}},
-}
-
-\bib{SGA1}{collection}{
-   title={Rev\^etements \'etales et groupe fondamental (SGA 1)},
-%   language={French},
-   series={Documents Math\'ematiques (Paris), 3},
-   note={S\'eminaire de g\'eom\'etrie alg\'ebrique du Bois Marie 1960--61.
-   [Algebraic Geometry Seminar of Bois Marie 1960-61];
-   Directed by A. Grothendieck;
-   With two papers by M. Raynaud;
-   Updated and annotated reprint of the 1971 original [Lecture Notes in
-   Math., 224, Springer, Berlin;  MR0354651 (50 \#7129)]},
-   publisher={Soci\'et\'e Math\'ematique de France},
-   place={Paris},
-   date={2003},
-   pages={xviii+327},
-%  isbn={2-85629-141-4},
-%   review={\MR{2017446 (2004g:14017)}},
-}
-
-\bib{Kamgarpour}{article}{
-   author={Kamgarpour, Masoud},
-   title={Stacky abelianization of algebraic groups},
-   journal={Transform. Groups},
-   volume={14},
-   date={2009},
-   number={4},
-   pages={825--846},
-%   issn={1083-4362},
-%   review={\MR{2577200 (2011b:20136)}},
-%   doi={10.1007/s00031-009-9067-8},
-}
-
-\bib{Laumon}{article}{
-   author={Laumon, G.},
-   title={Transformation de Fourier, constantes d'\'equations fonctionnelles
-   et conjecture de Weil},
-%   language={French},
-   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
-   number={65},
-   date={1987},
-   pages={131--210},
-%   issn={0073-8301},
-%   review={\MR{908218 (88g:14019)}},
-}
-
 \bib{SGA4.5}{book}{
@@
 
+\bib{vdG&M}{book}{
+author={Geer, van der},
+author={Moonen},
+title={Abelian Varieties},
+note={http://staff.science.uva.nl/$\sim$bmoonen/boek/BookAV.html}
+}
+
+\bib{Greenberg:2}{article}{
+   author={Greenberg, Marvin J.},
+   title={Schemata over local rings. II},
+   journal={Ann. of Math. (2)},
+   volume={78},
+   date={1963},
+   pages={256--266},
+%   issn={0003-486X},
+%   review={\MR{0156855 (28 \#98)}},
+}
+
+\bib{SGA1}{collection}{
+   title={Rev\^etements \'etales et groupe fondamental (SGA 1)},
+%   language={French},
+   author={Grothendieck, A.},
+   series={Documents Math\'ematiques (Paris), 3},
+   note={S\'eminaire de g\'eom\'etrie alg\'ebrique du Bois Marie 1960--61.
+   Un s\'eminaire dirig\'e par A. Grothendieck
+Augment\'e de deux expos\'es de Mme M. Raynaud
+\'Edition recompos\'e et annot\'e du volume 224 des Lecture Notes in Mathematics 224 publi\'e en 1971 par Springer-Verlag},
+   publisher={Soci\'et\'e Math\'ematique de France},
+   place={Paris},
+   date={2003},
+   pages={xviii+327},
+%  isbn={2-85629-141-4},
+%   review={\MR{2017446 (2004g:14017)}},
+}
+
+\bib{Kamgarpour}{article}{
+   author={Kamgarpour, M.},
+   title={Stacky abelianization of algebraic groups},
+   journal={Transform. Groups},
+   volume={14},
+   date={2009},
+   number={4},
+   pages={825--846},
+%   issn={1083-4362},
+%   review={\MR{2577200 (2011b:20136)}},
+%   doi={10.1007/s00031-009-9067-8},
+}
+
+\bib{Laumon}{article}{
+   author={Laumon, G.},
+   title={Transformation de Fourier, constantes d'\'equations fonctionnelles
+   et conjecture de Weil},
+%   language={French},
+   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
+   number={65},
+   date={1987},
+   pages={131--210},
+%   issn={0073-8301},
+%   review={\MR{908218 (88g:14019)}},
+}
+
+\bib{Serre:isogenies}{article}{
+   author={Serre, Jean-Pierre},
+   title={Corps locaux et isog\'enies},
+%   language={French},
+   conference={
+      title={S\'eminaire Bourbaki, Vol.\ 5},
+   },
+   book={
+      publisher={Soc. Math. France},
+      place={Paris},
+   },
+   date={1995},
+   pages={Exp.\ No.\ 185, 239--247},
+%   review={\MR{1603470}},
+}
+
 \bib{Stasinski}{article}{
@@
 %   doi={10.1016/j.jpaa.2011.10.027},
+}
+
+\bib{Suzuki&Yoshida:refinement}{article}{
+   author={Suzuki, Takashi},
+   author={Yoshida, Manabu},
+   title={A refinement of the local class field theory of Serre and
+   Hazewinkel},
+   conference={
+      title={Algebraic number theory and related topics 2010},
+   },
+   book={
+      series={RIMS K\^oky\^uroku Bessatsu, B32},
+      publisher={Res. Inst. Math. Sci. (RIMS), Kyoto},
+   },
+   date={2012},
+   pages={163--191},
+%   review={\MR{2986923}},
 }
@@
 
-\bib{vdG&M}{book}{
-author={van der Geer},
-author={Moonen},
-title={Abelian Varieties},
-note={http://staff.science.uva.nl/$\sim$bmoonen/boek/BookAV.html}
-}
-
 \bib{Xarles}{article}{
@@
 
+\bib{Yu:tori}{article}{
+   author={Yu, Jiu-Kang},
+   title={On the local Langlands correspondence for tori},
+   conference={
+      title={Ottawa lectures on admissible representations of reductive
+      $p$-adic groups},
+   },
+   book={
+      series={Fields Inst. Monogr.},
+      volume={26},
+      publisher={Amer. Math. Soc.},
+      place={Providence, RI},
+      editor={Cunningham, C.},
+      editor={Nevins, M.},
+   },
+   date={2009},
+   pages={177--183},
+   review={\MR{2508725 (2009m:11201)}},
+}
+
 \end{biblist}

### 2013-08-15 shanghai.tex
Part 2 is finished, pending results on base change from Part 1.

@@
 \[
-\Hh^1(\Weil{K}, \hat{T}) \cong \Hom(T(K), \EEx).
-\]
-A geometric description of the resulting isomorphism $\Hh^1(\Weil{K}, \hat{T}) \cong \QCiso{\GN{T}}$
+\Hh^1(\Weil{K}, \hat{T}_\ell) \cong \Hom(T(K), \EEx).
+\]
+A geometric description of the resulting isomorphism $\Hh^1(\Weil{K}, \hat{T}_\ell) \cong \QCiso{\GN{T}}$
 would yield a different description of the Artin reciprocity map.
@@
   so that $P^s = (p^s, h(\zeta_d))$.
-  % Setting $\psi = 1$ will satisfy equation \ref{eq:psi-condition}
+  % Setting $\psi = 1$ will satisfy Equation \ref{eq:psi-condition}
   % when $d = 1$.
@@
 
-  We now check equation \ref{eq:psi-condition} for
+  We now check Equation~\eqref{eq:psi-condition} for
   $x = \zeta^{\phi(d)-1}$.  Write
@@
   In either case, $\alpha^{-\Phi_d(1)}\tilde{f}(B) = 1$ and thus
-  $\psi$ satisfies equation \ref{eq:psi-condition} for
+  $\psi$ satisfies Equation~\eqref{eq:psi-condition} for
   $x = \zeta^{\phi(d)-1}$.  The definition of $\psi$ in \ref{eq:psi-def}
@@
 \]
-\item
-For every finite Galois extension $L/K$ and for every algebraic torus $T$ over $K$, the following diagram commutes:
-\[
-\begin{tikzcd}
-\QCiso{\Gr(\underline{\Res_{L/K}(T_L)})} \arrow[two heads]{r} \dar & \QCiso{\Gr({T})} \dar\\
-\Hom_{\text{qc}}(T(L), \EEx) \arrow[two heads]{r} & \Hom_{\text{qc}}(T(K), \EEx)
-\end{tikzcd}
-\]
 \end{enumerate}
@@
 \section{Transfer of quasicharacter sheaves} \label{sec:transfer}
-
-\David{We should add a discussion of why we care about the transfer principle.}
 
@@
 
-We recall the notion of $N$-congruent tori from  \cite{CY}*{\S 2}.  Suppose $T$ and $T'$
-are tori over non-archimedian local fields $K$ and $K'$, splitting over $L$ and $L'$ respectively.
+We recall the notion of $N$-congruent tori from \cite{CY}*{\S 2}.  
+Suppose $T$ and $T'$ are tori over non-archimedian local fields $K$ and $K'$, 
+splitting over $L$ and $L'$ respectively.
 Then $T$ and $T'$ are said to be \emph{$N$-congruent} if there are isomorphisms
@@
  \end{enumerate}
-\[
-  \Hom_{<N}(T(K), \EEx) \to \Hom_{<N}(T'(K'),\EEx)
- \]
-
-\begin{corollary}
- Suppose that $T$ and $T'$ are $N$-congruent for $N > 3h$.  Then there is a canonical equivalence of categories
- \[
-  \QC(\GN{T}_{N-3h}) \to \QC(\GN{T}'_{N-3h})
- \]
- determined by $\alpha, \beta$ and $\phi$ inducing the isomorphism
- \[
-  \Hom(T(K) / T(K)_{N-3h}, \EEx) \to \Hom(T'(K') / T'(K')_{N-3h}, \EEx)
- \]
-\end{corollary}
-
-\begin{proof}
+It follows from this definition that if $T$ and $T'$ are $N$-congruent then $\alpha$, $\beta$ and $\phi$ determine an isomorphism
+\begin{equation}\label{transfer}
+  \Hom_{<N}(T(K), \EEx) \iso \Hom_{<N}(T'(K'),\EEx).
+\end{equation}
+Note that if $T$ and $T'$ are $N$-congruent, then they are $N'$ congruent for every $N' \leq N$.
+In this section we ask if the isomorphism \eqref{transfer} comes from an equivalence of categories of quasicharacter sheaves on $\GN{T}_d$ and those on $\GN{T'}_d$.
+
 One of the main results of \cite{CY} gives an isomorphism of group schemes between
@@
 They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the
-Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{CY}*{\S 8.1}
-They then prove the following theorem \cite{CY}*{Thm. 8.5}
- Suppose that $T$ and $T'$ are $N$-congruent for $N > 3h$.  Then there is a canonical isomorphism
+Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{CY}*{\S 8.1}; let $h'$ be this quantity for $T'$.
+Then it follows from \cite{CY}*{Thm. 8.5} that if $T$ and $T'$ are $N$-congruent and $h=h'$ and $N > 3h$, then there is a canonical isomorphism
  \[
@@
  determined by $\alpha, \beta$ and $\phi$.
-
-As an immediate consequence of this theorem and Theorem \ref{thm:application} we have the following corollary:
-\end{proof}
+As an immediate consequence of this theorem and Theorem \ref{thm:application} we have the following
+
+\begin{proposition}
+ With notation above, suppose that $T$ and $T'$ are $N$-congruent and $h=h'$ and $N > 3h$.  Set $d = N-3h$.
+ Then there is a canonical equivalence of categories
+ \[
+  \QC(\GN{T}'_{d}) \to \QC(\GN{T}_{d})
+ \]
+ determined by $\alpha, \beta$ and $\phi$ inducing the isomorphism
+ \[
+  \Hom_{<d}(T'(K'), \EEx) \to \Hom_{<d}(T(K), \EEx).
+ \]
+\end{proposition}
 
@@
 
-As indicated in the Introduction, we are tantalized by the idea that quasicharacter sheaves for $T$ may play a key role in a geometric, categorial version of the local Langlands correspondence for algebraic tori over non-archimedean local fields.
-We anticipate that, as with the local Langlands correspondence for algebraic tori, it will be possible to reduce the essential points of the argument to the case $T= \Gm{K}$, provided that the category of quasicharacter sheaves behaves properly with regard to Weil restriction; see \cite{Yu:tori}*{Thm 7.5 (2)}.
-The next proposition shows that the category of quasicharacter sheaves does indeed behave properly with regard to Weil restriction.
+As indicated in the Introduction, we are tantalized 
+by the idea that quasicharacter sheaves for $T$ 
+may play a key role in a geometric, categorial version 
+of the local Langlands correspondence for algebraic tori 
+over non-archimedean local fields. 
+As with the local Langlands correspondence for algebraic tori, 
+it will be possible to reduce the essential points of the argument to the case $T= \Gm{K}$, provided that the category of quasicharacter sheaves behaves properly with regard to Weil restriction; see \cite{Yu:tori}*{Thm 7.5 (2)}.
+The next proposition shows that the category of quasicharacter sheaves for 
+algebraic tori does indeed behave properly with regard to Weil restriction.
 
@@
 \begin{proof}
-\Clifton{Under construction, pending the proofs of the results in the base change section}
+\Clifton{The proof will require the results in the base change section.}
 There is a canonical isomorphism
@@
 
-This paper has shown how quasicharacter sheaves on the Greenberg transform of the Neron model of $T$ determine admissible characters of $T(K)$, and vice versa, functorially.
-When coupled with the reciprocity map $\text{rec}_T $ for $T$, which enjoys the same functorial properties, it follows that quasicharacter sheaves for $T$ determine Langlands parameters for $T$, and vice versa, functorially.
+This paper has shown how quasicharacter sheaves 
+on the Greenberg transform of the Neron model of $T$ 
+determine admissible characters of $T(K)$, and vice versa, functorially. When coupled with the reciprocity map $\text{rec}_T $ for $T$, 
+which enjoys the same functorial properties, 
+it follows that quasicharacter sheaves for $T$ 
+determine Langlands parameters for $T$, and vice versa, functorially.
 \[
@@
 \ & \arrow[swap]{dl}{\trFrob{G}} \QCiso{\GN{T}} \arrow[dashed]{dr}  & \\
-\Hom_{<\infty}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(K,\hat{T}) \\
-\end{tikzcd}
-\]
-We suspect that it is possible to extract Langlands parameters from quasicharacter sheaves directly; results in this paper reduce the problem to the case $T=\Gm{K}$.
-In that case, our suspicions are all but confirmed by the class field theory of Serre-Hasewinkel \cite{Serre:isogenies} as revisited in \cite{Suzuki&Yoshida:refinement}.
-What remains is a careful comparison of quasicharacter sheaves for $\Gm{K}$ and certain local systems on the fpqc-site of the pro-quasi-algebraic varieties appearing in \cite{Suzuki&Yoshida:refinement}.
+\Hom_{<\infty}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(K,\hat{T}_\ell) \\
+\end{tikzcd}
+\]
+We suspect that it is possible to extract Langlands parameters 
+from quasicharacter sheaves directly and that the reciprocity map 
+can then be be viewed as pairing characters and parameters coming
+ from the same quasicharacter sheaf. 
+ Results in this paper reduce the problem to the case $T=\Gm{K}$. 
+ In that case, our suspicions are all but confirmed 
+ by the class field theory of Serre-Hasewinkel as revisited in \cite{Suzuki&Yoshida:refinement}. 
+ What remains to be done is a careful comparison of 
+ quasicharacter sheaves for $\Gm{K}$ and certain local systems on
+  the fpqc-site of the pro-quasi-algebraic varieties appearing in \cite{Suzuki&Yoshida:refinement}.
 
@@
 Augment\'e de deux expos\'es de Mme M. Raynaud
-\'Edition recompos\'e et annot\'e du volume 224 des Lecture Notes in Mathematics 224 publi\'e en 1971 par Springer-Verlag},
+\'Edition recompos\'e et annot\'e du volume 224 des Lecture Notes in Mathematics publi\'e en 1971 par Springer-Verlag},
    publisher={Soci\'et\'e Math\'ematique de France},

### 2013-08-15 shanghai.tex
Moving computers. Minor changes, mostly to Part 2.

@@
 type over a finite field $\Fq$; $G$ need not be reductive, connected, or of
-finite type over $\Fq$. Fix a prime $\ell$ that does not divide
-$q$, write $m : \GxG \to G$ for the multiplication morphism,
+finite type over $\Fq$. Fix a prime $\ell$ invertible in $\Fq$
+and write $m : \GxG \to G$ for the multiplication morphism,
 $\bG$ for the base change of $G$ to $\bFq$ and
 $\Frob{G} : \bG \to \bG$ for the Frobenius automorphism.
-A quasicharacter sheaf on $G$ is a triple $\cs{L}\ceq
-(\gcs{L},\mu,\phi)$ where $\gcs{L}$ is a rank-$1$ $\ell$-adic local system on $\bG$ and $\mu: m^*
+A quasicharacter sheaf on $G$ is a 
+\Clifton{ [Use this?:] . . . is an $\ell$-adic Weil local system of rank-$1$ on $G$, equipped with an isomorphism ... }
+triple $\cs{L}\ceq
+(\gcs{L},\mu,\phi)$ where $\gcs{L}$ is an $\ell$-adic local system on $\bG$ of rank-1 and $\mu: m^*
 \gcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gcs{L} \to \gcs{L}$ are isomorphisms;
@@
 
-Throughout this paper, $G$ is a commutative group scheme,
-smooth and locally of finite type over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.
+Throughout this paper, $G$ is a smooth commutative group scheme locally of finite type over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.
 
 We fix an algebraic closure $\bFq$ of $\Fq$ and write $\bG$ for the
-commutative group scheme $G \times_{\Spec{\Fq}} \Spec{\bFq}$ over $\bFq$ obtained by base change from $k$. The multiplication morphism for $\bG$ will be denoted by $\bm$.
+smooth commutative group scheme $G \times_{\Spec{\Fq}} \Spec{\bFq}$ over $\bFq$ obtained by base change from $k$. The multiplication morphism for $\bG$ will be denoted by $\bm$.
 
@@
 \begin{enumerate}
-\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a rank-$1$ $\ell$-adic local system on $\bG$;
+\labitem{(CS.0)}{CS.0} $\gcs{L}$ is an $\ell$-adic local system on $\bG$ (a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component) of rank-1; 
 \labitem{(CS.1)}{CS.1} $\mu: \bm^* \gcs{L} \to \LxL$
@@
 \end{enumerate}
-%In short, a quasicharacter sheaf on $G$  is a rank-$1$ Weil local system $(\gcs{L},\phi)$ on $G$ equipped with an isomorphism $m^* (\gcs{L},\phi) \to (\gcs{L},\phi)\boxtimes (\gcs{L},\phi)$. 
+%In short, a quasicharacter sheaf on $G$  is a rank-1 Weil local system $(\gcs{L},\phi)$ on $G$ equipped with an isomorphism $m^* (\gcs{L},\phi) \to (\gcs{L},\phi)\boxtimes (\gcs{L},\phi)$. 
 \end{definition}
@@
 Set $G \ceq G_1\times G_1$.
-Let $\cs{L}$ be a geochar on $G$.
+Let $\cs{L}$ be a quasicharacter sheaf on $G$.
 Define $f : G\to G\times G$ by $f(g_1,g_2) = (g_1,e_2,e_1,g_2)$.
@@
 Then $f^*p_1^*\gcs{L} = r_1^* q_1^* \gcs{L}$ and $f^*p_2^*\gcs{L} = r_2^* q_2^* \gcs{L}$.
-Now $\cs{L}_1 \ceq r_1^* \cs{L}$ is a geochar on $G_1$ and $\cs{L}_2 \ceq r_2^* \cs{L}$ is a geochar on $G_2$, by Proposition~\ref{prop:pullback}.
+Now $\cs{L}_1 \ceq r_1^* \cs{L}$ is a quasicharacter sheaf on $G_1$ and $\cs{L}_2 \ceq r_2^* \cs{L}$ is a quasicharacter sheaf on $G_2$, by Proposition~\ref{prop:pullback}.
 Then
@@
 Let $\QCb(G)$ be the category of pairs $(\cs{L}_0,\mu_0)$ 
-where $\cs{L}_0$ a rank-$1$ $\ell$-adic local system on $G$, 
+where $\cs{L}_0$ an $\ell$-adic local system on $G$ of rank-1, 
 equipped with an isomorphism $\mu_0 : m^* \cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ 
@@
 \end{enumerate}
-
-Let us say that \cdef{global section}
-of a quasicharacter sheaf $\cs{L}$ on an \'etale group scheme $G$ as a choice
 
@@
   so to prove the proposition it suffices to show that every 
-  finite geochar on $G^0$ extends to a geochar on $G$.
-
- Let $(\pi,\psi)$ be a finite geochar on $G^0$.
+  finite quasicharacter sheaf on $G^0$ extends to a quasicharacter sheaf on $G$.
+
+ Let $(\pi,\psi)$ be a finite quasicharacter sheaf on $G^0$.
  By Lemma~\ref{lemma:ext}, there is an extension of the 
- descrete isogeny $\pi : B \to G^0$ 
+ discrete isogeny $\pi : B \to G^0$ 
  (see Section~\ref{sec:finite} for the definition of a discrete isogeny) 
@@
  such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
- Then $(f,\psi)$ is a finite geochar on $G$.
+ Then $(f,\psi)$ is a finite quasicharacter sheaf on $G$.
  Then $(f,\psi)\vert_{G^0} \iso (\pi,\psi)$,
@@
 \begin{lemma}\label{lemma:ext}
-Every discrete isogeny onto $G^0$ extends to a discrete isogeny onto $G$ such that the component group of the covering space is isomorphic to the component group of $G$.
+Every discrete isogeny (see Section~\ref{sec:finite}) to $G^0$ extends to a discrete isogeny to $G$ such that the component group of the covering space is isomorphic to the component group of $G$.
 \end{lemma}
@@
 We saw, in Proposition~\ref{prop:functorialG}, that the trace of Frobenius  $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
-Our main result regarding quasicharacter sheaves shows that trace of Frobenius is an isomorphism in the case that we care about.
+Our main result regarding quasicharacter sheaves, below, shows that trace of Frobenius is an isomorphism in the case that we care about.
 
@@
   If $G$ is a smooth abelian group scheme, locally of finite type over
-  $\Fq$, and the abelian group $\pi_0(G)(\bFq)$ (the geometric
+  $\Fq$, and if the abelian group $\pi_0(G)(\bFq)$ (the geometric
   component group) is finitely generated, then the trace of Frobenius
@@
 Then the restriction of $\cs{L}$ to the connected component $1\in G$ 
-would be a rank-1 $\ell$-adic local system on $1$, 
+would be a $\ell$-adic local system on $1$ of rank-1, 
 thus an $\ell$-adic character $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with $\rho_1(\Frob{\Fq}) = \ell$. But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, 
@@
 We can play the same game with the character $\chi : G(\Fq) \to \EEx$ 
-defined by $\chi(1) = 1+\ell$. In this case, the corresponding quasicharacter sheaf $\cs{L}$ is bounded but not finite, since $1+\ell$ is not a root of unity. 
+defined by $\chi(1) = 1+\ell$.
+In this case, the corresponding quasicharacter sheaf $\cs{L}$ is bounded, defined at $1$ by a pro-etale cover of $1$, but not finite, since $1+\ell$ is not a root of unity.
 %
@@
 We write $\Hom_{< d}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $d$ 
-and $\Hom_{<\infty}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth.
+and $\Hom_{<\infty}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth; one might call these quasicharacters of $T(K)$, expanding on \cite{Tate:thesis}*{2.3}.
 
@@
 
-\section{The geometrization of quasicharacters} \label{sec:quasichar}
+\section{The geometrization of characters of tori over local fields} \label{sec:quasichar}
 
@@
   \[
-\trFrob{T}:  \QCiso{\GN{T}} \to \Hom_{\text{qc}}(T(K),\EEx)
+\trFrob{T}:  \QCiso{\GN{T}} \to \Hom_{<\infty}(T(K),\EEx)
   \]
@@
 \[
-T \mapsto \Hom_{\text{qc}}(T(K),\EEx).
+T \mapsto \Hom_{<\infty}(T(K),\EEx).
 \]
@@
 \end{corollary}
+
+\begin{proof}
+\Clifton{I'll say a few words here about the ind-category $\QC(\GN{T})$.}
+
+\end{proof}
+
+\Clifton{Make comments here about the depth-preserving isomorphism  . .  .}
 
@@
  \end{align*}
- satisfying the following conditions:
+ satisfying the conditions
  \begin{enumerate}
   \item $\alpha$ induces an isomorphism $\OK/\pi_K^N \OK \to \OO{K'}/\pi_{K'}^N \OO{K'}$,
-  \item $\alpha$ is $\Gal(L/K)$-equivariant relative to $\beta$: $\alpha(\gamma x) = \beta(\gamma) \alpha(x)$
-  for $\gamma \in \Gal(L/K)$ and $x \in \OL/\pi_K^N \OL$,
+  \item $\alpha$ is $\Gal(L/K)$-equivariant relative to $\beta$, and
+  %: $\alpha(\gamma x) = \beta(\gamma) \alpha(x)$ for $\gamma \in \Gal(L/K)$ and $x \in \OL/\pi_K^N \OL$,
   \item $\phi$ is $\Gal(L/K)$-equivariant relative to $\beta$.
  \end{enumerate}
-It follows from this definition that if $T$ and $T'$ are $N$-congruent then $\alpha$, $\beta$ and $\phi$ determine an isomorphism
+If $T$ and $T'$ are $N$-congruent then $\alpha$, $\beta$ and $\phi$ determine an isomorphism
 \begin{equation}\label{transfer}
@@
 \end{equation}
-Note that if $T$ and $T'$ are $N$-congruent, then they are $N'$ congruent for every $N' \leq N$.
-In this section we ask if the isomorphism \eqref{transfer} comes from an equivalence of categories of quasicharacter sheaves on $\GN{T}_d$ and those on $\GN{T'}_d$.
+Note that if $T$ and $T'$ are $N$-congruent, then they are $N'$ congruent for every $N' \leq N$, the isomorphism \eqref{transfer} is depth-preserving at integers less than $N$.
+In this section we ask if the isomorphism \eqref{transfer} comes from an equivalence of categories of quasicharacter sheaves on $\GN{T}_d$ and those on $\GN{T}'_d$.
 
@@
 Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{CY}*{\S 8.1}; let $h'$ be this quantity for $T'$.
-Then it follows from \cite{CY}*{Thm. 8.5} that if $T$ and $T'$ are $N$-congruent and $h=h'$ and $N > 3h$, then there is a canonical isomorphism
+Then it follows from \cite{CY}*{Thm. 8.5} that if $T$ and $T'$ are $N$-congruent and $h=h'$ and $N > 3h$, 
+\Clifton{Is this correct?}
+then there is a canonical isomorphism of smooth group schemes
  \[
@@
  determined by $\alpha, \beta$ and $\phi$.
-As an immediate consequence of this theorem and Theorem \ref{thm:application} we have the following
-
-\begin{proposition}
+Combining this with Theorem \ref{thm:application} gives the geometrization and categorification of the transfer of characters.
+
+\begin{corollary}\label{cor:transfer}
  With notation above, suppose that $T$ and $T'$ are $N$-congruent and $h=h'$ and $N > 3h$.  Set $d = N-3h$.
@@
  \[
-  \Hom_{<d}(T'(K'), \EEx) \to \Hom_{<d}(T(K), \EEx).
- \]
-\end{proposition}
+  \Hom_{<d}(T'(K'), \EEx) \to \Hom_{<d}(T(K), \EEx)
+ \]
+ through the trace of Frobenius.
+\end{corollary}
 
@@
 over non-archimedean local fields. 
-As with the local Langlands correspondence for algebraic tori, 
+As with the local Langlands correspondence for algebraic tori over local fields, 
 it will be possible to reduce the essential points of the argument to the case $T= \Gm{K}$, provided that the category of quasicharacter sheaves behaves properly with regard to Weil restriction; see \cite{Yu:tori}*{Thm 7.5 (2)}.
@@
  from the same quasicharacter sheaf. 
- Results in this paper reduce the problem to the case $T=\Gm{K}$. 
+ Results in this paper provide tools for reduction the problem to the case $T=\Gm{K}$. 
  In that case, our suspicions are all but confirmed 
- by the class field theory of Serre-Hasewinkel as revisited in \cite{Suzuki&Yoshida:refinement}. 
+ by the class field theory of Serre-Hasewinkel, \Clifton{Need references for S-H CFT.} especially as revisited in \cite{Suzuki&Yoshida:refinement}. 
  What remains to be done is a careful comparison of 
@@
    pages={305--347},
-   review={\MR{0217026 (36 \#121)}},
+%   review={\MR{0217026 (36 \#121)}},
 }

### 2013-08-15 shanghai.tex
Commit for our meeting.

@@
 locally of finite type over $\Fq$, to which we now return. 
-Every quasicharacter sheaf $(\gcs{L},\mu,\phi)$ on $G$ 
+In this generality, neither of the full subcategories $\QCf(G) \subset \QCb(G) \subset \QC(G)$ are equivalences;
+see the end of Section~\ref{sec:snake}.
+Nevertheless, every quasicharacter sheaf $(\gcs{L},\mu,\phi)$ on $G$ 
 determines a Weil sheaf $(\gcs{L},\phi)$ on $G$. 

### 2013-08-15 shanghai.tex
Switching to bibtex

--- 2013-08-15 shanghai.tex
@@
 \documentclass[11pt]{amsart}
-\title[Geometrization of characters of tori]{Geometrization of characters of tori over non-archimedean local fields}
+\title[Geometrization of characters of tori]{Geometrization of characters of tori over non-Archimedean local fields}
 \usepackage[british]{babel}
@@
 %\usepackage[shortalphabetic]{amsrefs}
-\usepackage[alphabetic]{amsrefs}
+%\usepackage[alphabetic]{amsrefs}
 \renewcommand\MR{\relax}
-%\usepackage{xypic}
+\usepackage{xypic}
 \usepackage{textcomp}
@@
   classes of quasicharacter sheaves on the Greenberg transform of the Néron
-  model of $T$, where $K$ is any non-archimdean local field and $T$ is
+  model of $T$, where $K$ is any non-Archimdean local field and $T$ is
   any algebraic torus over $K$.
@@
 %    such a model would be of the utmost importance.}
-%  \cite{Tate:thesis}*{\S 2.3}
+%  \cite{tate:67a}*{\S 2.3}
 %\end{quotation}
@@
 Motivated by the sheaf-function dictionary for commutative, connected
-algebraic groups \cite{SGA4.5}, we explore the trace of Frobenius morphism
+algebraic groups \cite{deligne:SGA4.5}, we explore the trace of Frobenius morphism
 \[
@@
 We apply Theorem \ref{thm:snake} to the geometrization of quasicharacters
-of non-archimedian tori in Part 2.  Let $K$ be a non-archimedian local field
+of non-Archimedian tori in Part 2.  Let $K$ be a non-Archimedian local field
 with finite residue field $\Fq$; we place no restriction on the characteristic of $K$.
@@
 \[
-\Hh^1(\Weil{K}, \hat{T}_\ell) \cong \Hom(T(K), \EEx).
-\]
-A geometric description of the resulting isomorphism $\Hh^1(\Weil{K}, \hat{T}_\ell) \cong \QCiso{\GN{T}}$
+\Hh^1(\Weil{K}, \hat{T}) \cong \Hom(T(K), \EEx).
+\]
+A geometric description of the resulting isomorphism $\Hh^1(\Weil{K}, \hat{T}) \cong \QCiso{\GN{T}}$
 would yield a different description of the Artin reciprocity map.
@@
 Analogous sheaves on connected, commutative algebraic groups were first studied
-by Deligne \cite{SGA4.5}, and more recently Drinfeld has referred to such objects
+by Deligne \cite{deligne:SGA4.5}, and more recently Drinfeld has referred to such objects
 as character sheaves.  Our quasicharacter sheaves evolved from this notion, and Theorem \ref{thm:snake}
@@
 
-In Section \ref{sec:GN} we introduce N\'eron models of tori and the Greenberg transform, which produce
+In Section \ref{sec:GAN} we introduce N\'eron models of tori and the Greenberg transform, which produce
 group schemes over $\Fq$ from algebraic tori $T$ over $K$.
@@
 
-\begin{definition}\label{def:QC}
+\begin{definition}\label{def:GC}
 A \emph{quasicharacter sheaf on $G$} is a triple
@@
 \end{enumerate}
-%In short, a quasicharacter sheaf on $G$  is a rank-$1$ Weil local system $(\gcs{L},\phi)$ on $G$ equipped with an isomorphism $m^* (\gcs{L},\phi) \to (\gcs{L},\phi)\boxtimes (\gcs{L},\phi)$. 
-\end{definition}
+In short, a quasicharacter sheaf on $G$  is a rank-$1$ Weil local system $(\gcs{L},\phi)$ on $G$ equipped with an isomorphism $m^* (\gcs{L},\phi) \to (\gcs{L},\phi)\boxtimes (\gcs{L},\phi)$.
 
@@
 \end{enumerate}
+\end{definition}
 
 %\begin{remark} \label{rem:CS-action}
-The rule $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$ defines a forgetful functor from quasicharacter sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{Deligne:Weil2}*{Def.~1.1.10 (i)}.
-
-As mentioned after \cite{Deligne:Weil2}*{Def.~1.1.10}, a Weil sheaf $(\gcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
+The rule $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$ defines a forgetful functor from quasicharacter sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
+
+As mentioned after \cite{deligne:80a}*{Def.~1.1.10}, a Weil sheaf $(\gcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
 Since we will need this point of view later, we review that interpretation here.
@@
 $\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for all $u,v\in \Weil{\Fq}$.
-This means the pair $(\gcs{L},\varphi_1)$ is almost an action $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of \cite{SGA4.5}*{Expos\'e XIII,~1.1}.
-The pair $(\gcs{L},\varphi_1)$ fails to fulfill the requirements of \cite{SGA4.5}*{Expos\'e XIII,~1.1} only because $\Weil{\Fq}$ is profinite.
+This means the pair $(\gcs{L},\varphi_1)$ is almost an action $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of \cite{deligne:SGA4.5}*{Expos\'e XIII,~1.1}.
+The pair $(\gcs{L},\varphi_1)$ fails to fulfill the requirements of \cite{deligne:SGA4.5}*{Expos\'e XIII,~1.1} only because $\Weil{\Fq}$ is profinite.
 This fact goes to the heart of the notion of a Weil sheaf and is one of the essential aspects of our definition of $\QC(G)$.
@@
 (The category of characters sheaves on $G$ is not abelian, so $\QC(G)$
-is not a tensor category in the sense of \cite{Deligne:tensorielles}.)
+is not a tensor category in the sense of \cite{deligne:02a}.)
 %\begin{proof}\end{proof}
@@
 
-\begin{definition}\label{def:trFrob}
+\begin{definition}
 Let $(\gcs{L},\phi)$ be a Weil sheaf on $G$. on constructible $\ell$-adic sheaf on $\bG$. Every $g\in G(\Fq)$
@@
   \begin{tikzcd}[row sep=20, column sep=30]
-   \QCiso{G} \rar{f^*} \arrow[swap]{d}{\trFrob{G}} & \QCiso{H} \dar{\trFrob{H}} \\
+   \QCiso{G} \rar{f^*} \arrow[swap]{d}{\trFrob{G}} & \QCiso{H} \dar{t_H} \\
    G(\Fq)^* \rar & H(\Fq)^*
@@
   homomorphism $\pi_0(\bG) \to \pi_0(\bH)$ obtained by
-  applying the functor $\pi_0$ to $\bf$; see \cite{vdG&M}*{III, 3.28}, for example.
+  applying the functor $\pi_0$ to $\bf$; see \cite{vdGeer-Moonen:AbelianVarieties}*{III, 3.28}, for example.
   \Clifton{I haven't found a better reference for this yet!}
@@
   the trace of Frobenius, in the sense above, follows immediately from
-  the definitions; see \cite{Laumon}*{1.1.1.2}, where the ambient
+  the definitions; see \cite{laumon:87a}*{1.1.1.2}, where the ambient
   hypothesis that $X$ is of finite type over $\Fq$ can be replaced by
@@
 \begin{tikzcd}[column sep=60]
-\arrow{d}{\trFrob{G_1} \times \trFrob{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes} & \arrow{d}{\trFrob{G_1\times G_2}} \QCiso{G_1\times G_2}\\
+\arrow{d}{t_{G_1} \times t_{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes} & \arrow{d}{t_{G_1\times G_2}} \QCiso{G_1\times G_2}\\
 (G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
@@
 \]
-be the functor obtained by pull-back along the canonical closed immersion of $k$-schemes  $\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$ \cite{BLR}*{\S 7.6}. 
+be the functor obtained by pull-back along the canonical closed immersion of $k$-schemes  $\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$ \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}. 
 The following diagram commutes:
@@
 \begin{tikzcd}
-\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota} \dar[swap]{\trFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\trFrob{G}} \\
+\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota} \dar[swap]{t_{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{t_G} \\
 G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
@@
 \begin{tikzcd}
-\QCiso{G'} \dar{\trFrob{G'}} \rar & \QCiso{\Res_{k'/k} G'} \dar{\trFrob{\Res_{k'/k} G'}} \\
+\QCiso{G'} \dar{t_{G'}} \rar & \QCiso{\Res_{k'/k} G'} \dar{t_{\Res_{k'/k} G'}} \\
  G'(k')^* \rar & (\Res_{k'/k}G')(k)^*
@@
  from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
- is full and faithful; see \cite{SGA7.2}*{Expos\'e XIII} or even \cite{BBD}*{Prop. 5.2.1}. 
+ is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} or even \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}. 
  This functor preserves local constancy, so takes local systems to local systems. 
@@
   Observe that the forgetful functor $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$
-  sends quasicharacter sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{Deligne:Weil2}*{1.1.10}.
+  sends quasicharacter sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{deligne:80a}*{1.1.10}.
   While is it not true that all Weil sheaves on $G$ descend to local systems on $G$, 
@@
   an equivalence between the category of $\ell$-adic Weil local systems on $G$ and
-  $\ell$-adic representations of $\W(G,\bg)$ \cite{Deligne:Weil2}*{1.1.12}. 
+  $\ell$-adic representations of $\W(G,\bg)$ \cite{deligne:80a}*{1.1.12}. 
   Now let $(\gcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$ 
@@
   Then $b_G^*\cs{L}_0 \iso \gcs{L}$.
-  Since $b_G^*$ is full and faithful (again, see \cite{SGA7.2}*{Expos\'e XIII} or even \cite{BBD}*{Prop. 5.2.1}),
+  Since $b_G^*$ is full and faithful (again, see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} or even \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}),
   $
@@
   To show that $L_G(f,\psi) \iso (\cs{L}_0,\mu_0)$ we simply apply the functions--sheaves dictionary
-  as follows ({\it cf} \cite{Laumon}*{1.1.3} or, ultimately, \cite{SGA4.5}*{Sommes trigonométriques}).
+  as follows ({\it cf} \cite{laumon:87a}*{1.1.3} or, ultimately, \cite{deligne:SGA4.5}*{Sommes trigonométriques}).
   First, recall that $L_G(f,\psi) = (L(f,\psi), \mu(f,\psi))$. 
-  By  \cite{Laumon}*{1.1.3.3}, $\trFrob{(G_{k'}\hookrightarrow G)^*L(f,\psi)} = \trFrob{\cs{L}} \circ N_{k'/k}$, for each finite extension $k'/k$.
+  By  \cite{laumon:87a}*{1.1.3.3}, $\trFrob{(G_{k'}\hookrightarrow G)^*L(f,\psi)} = \trFrob{\cs{L}} \circ N_{k'/k}$, for each finite extension $k'/k$.
   On the other hand, $\trFrob{\cs{L}} \circ N_{k'/k} = \trFrob{(G_{k'}\hookrightarrow G)^*\cs{L}}$,  by Proposition~\ref{prop:basechange}.
-  %Using notation from \cite{Laumon}*{1.1}, this means $t_{\bullet L(f,\psi)} = t_{\bullet \cs{L}_0}$.
-  Using \cite{Laumon}*{Th\'eor\`eme~1.1.2}, it follows that  $L(f,\psi) \iso \cs{L}_0$ in $\Loc(G)$.
+  %Using notation from \cite{laumon:87a}*{1.1}, this means $t_{\bullet L(f,\psi)} = t_{\bullet \cs{L}_0}$.
+  Using \cite{laumon:87a}*{Th\'eor\`eme~1.1.2}, it follows that  $L(f,\psi) \iso \cs{L}_0$ in $\Loc(G)$.
   It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\cs{L}_0,\mu_0)$ in $\QCb(G)$.
@@
 
-As Proposition~\ref{prop:connected} shows, 
-when $G$ is a connected algebraic group over $\Fq$, 
-it is appropriate to replace quasicharacter sheaves on $G$ 
-with the conceptually simpler category $\QCf(G)$ of finite quasicharacter sheaves on $G$. 
-In this context, finite quasicharacter sheaves may also be apprehended as \emph{certain} $\ell$-adic characters of fundamental group $\pi_1(G,{\bar e})$. 
-As explained in \cite{Kamgarpour}*{\S~2}, 
-the relevant characters of $\pi_1(G,{\bar e})$ are precisely those 
-that factor through a particular quotient of $\pi_1(G,{\bar e})$ 
-denoted there by $\Pi_\text{disc}(G)$.
-%\[\pi_1(G,{\bar e}) \to \Pi_\text{et}(G) \to \Pi_\text{et}(G)_{\Gal(\bFq/\Fq)} = \Pi_\text{disc}(G)\]
-From this it is apparent that the category of discrete isogenies to $G$ is a Galois category, in the sense of \cite{SGA1}*{Expos\'e V, \S 4}.
-Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$, as shown in \cite{Kamgarpour}*{App'x B}, this provides an alternate proof of $\QCiso{G} \to G(\Fq)^*$.
-
-In principle, something similar is possible in the more general 
-context of this paper, where $G$ is a smooth group scheme 
-locally of finite type over $\Fq$, to which we now return. 
-Every quasicharacter sheaf $(\gcs{L},\mu,\phi)$ on $G$ 
-determines a Weil sheaf $(\gcs{L},\phi)$ on $G$. 
-So, if we choose a geometric point ${\bar g}_x$ in each component $\bG^x$ of $G$, then this choice can be used to convert 
-the Weil sheaf $(\gcs{L},\phi)$ into an $\ell$-adic character of $\prod_{x\in \pi_0(\bG)}\W(\bG^x, {\bar g}_x)$. 
-It proved cumbersome, however, to manage various 
-choices of families of base points and track the action 
-of $\Gal(\bFq/\Fq)$ on this (generally) infinite product of 
-Weil groups, and difficult to identify the relevant quotient of this group. Viewed in this light, Definition~\ref{def:QC} seemed comparatively simple.
-
 \section{Commutative \'etale group schemes} \label{sec:etale}
@@
 
-\'Etale group schemes form a counterpoint to connected groups, since the component group of a group scheme locally of finite type over $\Fq$ is an \'etale group scheme (locally of finite type) over $\Fq$ \cite{vdG&M}*{III, \S 4}.
+\'Etale group schemes form a counterpoint to connected groups, since the component group of a group scheme locally of finite type over $\Fq$ is an \'etale group scheme (locally of finite type) over $\Fq$ \cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
 The functor $G \mapsto G(\bFq)$ defines an equivalence of categories
@@
   \end{equation}
-  Note that if $x$ is fixed by $\Frob{k}$ then $\tau_\cs{L}(\Frob{\Fq})(x)$ is just $\trFrob{\cs{L}}(x)$, so the restriction of
-  $\tau_\cs{L}(\Frob{k})$ to $G(k)$ is just $\trFrob{\cs{L}}$.
+  Note that if $x$ is fixed by $\Frob{k}$ then $\tau_\cs{L}(\Frob{\Fq})(x)$ is just $t_\cs{L}(x)$, so the restriction of
+  $\tau_\cs{L}(\Frob{k})$ to $G(k)$ is just $t_\cs{L}$.
   In general, conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
@@
   product of Dedekind domains.  Therefore $X$ decomposes into a direct
-  sum of cyclic $\ZZ[\Gamma_m]$-modules \cite{Brandal}*{?}, each of the
+  sum of cyclic $\ZZ[\Gamma_m]$-modules \cite{brandal:CommRingsFGModDecompose}*{?}, each of the
   form $\ZZ[\Gamma_m] / I$ for some ideal $I \subset \ZZ[\Gamma_m]$.
@@
   so that $P^s = (p^s, h(\zeta_d))$.
-  % Setting $\psi = 1$ will satisfy Equation \ref{eq:psi-condition}
+  % Setting $\psi = 1$ will satisfy equation \ref{eq:psi-condition}
   % when $d = 1$.
@@
 
-  We now check Equation~\eqref{eq:psi-condition} for
+  We now check equation \ref{eq:psi-condition} for
   $x = \zeta^{\phi(d)-1}$.  Write
@@
   In either case, $\alpha^{-\Phi_d(1)}\tilde{f}(B) = 1$ and thus
-  $\psi$ satisfies Equation~\eqref{eq:psi-condition} for
+  $\psi$ satisfies equation \ref{eq:psi-condition} for
   $x = \zeta^{\phi(d)-1}$.  The definition of $\psi$ in \ref{eq:psi-def}
@@
   $G^0$, is a connected algebraic group over $\Fq$, 
-  clopen in $G$ \cite{vdG&M}*{3.17}. 
+  clopen in $G$ \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}. 
   By Proposition~\ref{prop:connected}, every
@@
 
-We saw, in Proposition~\ref{prop:functorialG}, that the trace of Frobenius  $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
-Our main result regarding quasicharacter sheaves shows that trace of Frobenius is an isomorphism in the case that we care about.
-
 %\input{snake}
@@
   is an isomorphism of groups.
+  \Clifton{Address functoriality, here?}
 \end{theorem}
@@
   \begin{tikzcd}[row sep=30]
-    {}& \ker \trFrob{\pi_0(G)} \dar & \arrow[dashed]{d} \ker \trFrob{G} & \ker \trFrob{G^0} \dar & \\
-    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\trFrob{\pi_0(G)}}
-    & \QCiso{G} \rar \dar{\trFrob{G}} & \QCiso{G^0} \rar \dar{\trFrob{G^0}} & 0\\
+    {}& \ker t_{\pi_0(G)} \dar & \arrow[dashed]{d} \ker \trFrob{G} & \ker t_{G^0} \dar & \\
+    0 \rar & \QCiso{\pi_0(G)} \rar \dar{t_{\pi_0(G)}}
+    & \QCiso{G} \rar \dar{\trFrob{G}} & \QCiso{G^0} \rar \dar{t_{G^0}} & 0\\
     0 \rar & \pi_0(G)(\Fq)^* \rar \dar
     & \arrow[dashed]{d} G(\Fq)^* \rar & G^0(\Fq)^* \rar \dar & 0\\
-    & \coker \trFrob{\pi_0(G)} & \coker \trFrob{G} &  \coker \trFrob{G^0} &
+    & \coker t_{\pi_0(G)} & \coker \trFrob{G} &  \coker t_{G^0} &
   \end{tikzcd}
@@
   Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.  By
-  Proposition~\ref{prop:connected}, $\ker \trFrob{G^0} =0$ and $\coker \trFrob{G^0}=0$.
-  By Propositions~\ref{prop:etale} and \ref{prop:X}, $\ker \trFrob{\pi_0(G)}=0$
-  and $\coker \trFrob{\pi_0(G)}=0$.
+  Proposition~\ref{prop:connected}, $\ker t_{G^0} =0$ and $\coker t_{G^0}=0$.
+  By Propositions~\ref{prop:etale} and \ref{prop:X}, $\ker t_{\pi_0(G)}=0$
+  and $\coker t_{\pi_0(G)}=0$.
 
@@
   commutes (by Proposition~\ref{prop:pullback}), the bottom sequence
-  is exact at $G(\Fq)^*$ and $\coker \trFrob{\pi_0(G)} =0$
+  is exact at $G(\Fq)^*$ and $\coker t_{\pi_0(G)} =0$
   (by Propositions~\ref{prop:etale} and \ref{prop:X}) and
@@
 
-With Theorem~\ref{thm:snake} on hand, 
-we can see why neither bounded quasicharacter sheaves 
-nor finite quasicharacter sheaves are up to the task of 
-geometrizing characters of $G(\Fq)$ in the generality we need.  
+With Theorem~\ref{thm:snake} on hand, we can see why neither bounded quasicharacter sheaves nor finite quasicharacter sheaves are up to the task of geometrizing characters of $G(\Fq)$ in the generality we need.
 %
 Consider the case when $G$ is the discrete etale group scheme $\ZZ$.
-Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ 
-and let $\cs{L}$ be a quasicharacter sheaf in the isomorphism class 
-corresponding to the character $\chi : G(\Fq) \to \EEx$ under Theorem~\ref{thm:snake}. 
-Then $\trFrob{\cs{L}}(1) = \ell$. Suppose $\cs{L}$ was a bounded quasicharacter sheaf. 
-Then the restriction of $\cs{L}$ to the connected component $1\in G$ 
-would be a rank-1 $\ell$-adic local system on $1$, 
-thus an $\ell$-adic character $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with $\rho_1(\Frob{\Fq}) = \ell$. But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, 
-while $\rho_1(\pi_1(1,{\bar 1}))$ is not compact in $\EEx$ (it contains $\ell^\ZZ$). 
-So the Weil sheaf $\gcs{L}$ does not descend to a local system on $G$.
-It follows that the quasicharacter sheaf $\cs{L}$ is not a bounded quasicharacter sheaf.
+Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ and let $\cs{L}$ be a quasicharacter sheaf in the isomorphism class corresponding to the character $\chi : G(\Fq) \to \EEx$ under Theorem~\ref{thm:snake}.
+Then $\trFrob{\cs{L}}(1) = \ell$.
+Suppose $\cs{L}$ was a bounded quasicharacter sheaf.
+Then the restriction of $\cs{L}$ to the connected component $1\in G$ would be a rank-1 local system on $1$, thus an $\ell$-adic character $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with $\rho_1(\Frob{\Fq}) = \ell$.
+But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, while $\rho_1(\pi_1(1,{\bar 1}))$ is not compact (it contains $\ell^\ZZ$).
+Since the Weil sheaf $\gcs{L}$ does not descend to a local system on $G$, the  quasicharacter sheaf$\cs{L}$ is not a bounded quasicharacter sheaf.
 %
-We can play the same game with the character $\chi : G(\Fq) \to \EEx$ 
-defined by $\chi(1) = 1+\ell$. In this case, the corresponding quasicharacter sheaf $\cs{L}$ is bounded but not finite, since $1+\ell$ is not a root of unity. 
-%
+We can play the same game with the character $\chi : G(\Fq) \to \EEx$ defined by $\chi(1) = 1+\ell$.
+In this case, the corresponding geometric character $\cs{L}$ is bounded but not finite, since $1+\ell$ is not a root of unity.
+
 These simple examples illustrate why the categories $\QCb(G)$ and $\QCf(G)$ are inadequate to geometrize characters of $G(\Fq)$.
@@
 
-Let $K$ be a non-archimedean local field with residue field $\Fq$.
-We place no restriction on the characteristic of $K$. 
+Let $K$ be a non-Archimedean local field with residue field $\Fq$.
+Note that we place no restriction on the characteristic of $K$. 
 We write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$. 
@@
 Let $T$ be an algebraic torus over $K$.
-We write $\Hom_{< d}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $d$ 
-and $\Hom_{<\infty}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth.
+We write $\Hom_{< d}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $d$ and $\Hom_\text{qc}(T(K),\EEx)$ for the group of quasicharacters of $T(K)$.
 
 \section{Greenberg of Neron}
-\label{sec:GN}
+\label{sec:GAN}
+
+\Clifton{Motivate with comments about LLC for tori. Draw triangle. Reduction to GL(1) via induced tori. Comment about Japanese work. Comment about pro-quasi-algebraic. Combine with next section.}
+
+We have already seen that the trace of Frobenius defines a canonical homomorphism $\QCiso{\GN{T}} \to \Hom_\text{ad}(T(K),\EEx)$. 
+In this section we show that this homomorphism is functorial, in the following sense.
 
@@
 
-\begin{definition}\label{def:GN}
+\begin{definition}
 For each positive integer $d$, set $\TT_{d} \ceq \TT \times_\Spec{\OK} \Spec{A_d}$. Observe that $A_d$ is an Artin ring and $\TT_{d}$ is smooth and locally of finite type over $A_d$.
 %
-Let $\GN{T}_{d} = \Gr(\TT_d)$ be the group scheme over $\Fq$ produced by applying
-the Greenberg functor to $\TT_{d}$; this is the \emph{Greenberg transform of $\TT_d$}.
+Let \cdef{$\GN{T}_{d} = \Gr(\TT_d)$} be the group scheme over $\Fq$ produced by applying
+the Greenberg functor to $\TT_{d}$; this is the \cdef{Greenberg transform of $\TT_d$}.
 \end{definition}
 
-See \cite{Greenberg:2} and \cite[Ch. 9, \S 6]{BLR} and the first few sections of \cite{Stasinski} for background on the Greenberg functor. The fundamental properties of $\GN{T}_d$ that we need are:
+See \cite{greenberg:63a} and \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch.
+9, \S 6} and the first few sections of \cite{stasinski:12a} for background on the Greenberg functor.
+The fundamental properties of $\GN{T}_d$ that we need are:
  \begin{enumerate}
@@
   \end{enumerate}
-In fact, $\pi_0(\GN{T}_d) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$, and the latter is finitely generated by \cite{Xarles}.
+In fact, $\pi_0(\GN{T}_d) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$, and the latter is finitely generated by \cite{xarles:93a}.
 
@@
 \]
+\item
+For every finite Galois extension $L/K$ and for every algebraic torus $T$ over $K$, the following diagram commutes, where  . . . 
+\[
+\begin{tikzcd}
+\QCiso{\Gr(\underline{\Res_{L/K}(T_L)}_d)} \arrow[two heads]{r} \dar & \QCiso{\Gr({T}_d)} \dar\\
+\Hom_{<d}(T(L), \EEx) \arrow[two heads]{r} & \Hom_{<d}(T(K), \EEx)
+\end{tikzcd}
+\]
 \end{enumerate}
 \end{theorem}
+
+Let $L/K$ be a finite Galois extension and let $K'/K$ be the maximal unramified subextension, with residue field $k'$.
+If $T$ is a torus over $K$, write $\TL$ for the N\'eron model of the base change $T_L$.
+Then there is a canonical isomorphism
+\[
+\Res_{k'/k} \Gr(\TL) \cong \Gr(\underline{\Res_{L/K}(T_L)}).
+\]
+The natural inclusion $T \hookrightarrow \Res_{L/K} T_L$ induces a map of $k$-schemes
+\[
+\GN{T} \hookrightarrow \Res_{k'/k} \Gr(\TL)
+\]
+and thus a functor on character sheaves through pullback.
 
@@
   define depth has the property that $\TT(A_d) \cong T(K) / T(K)_d$
-  \cite[Prop 5.2]{Yu}, so characters of $\GN{T}_d(\Fq)$ 
+  \cite[Prop 5.2]{yu:03a}, so characters of $\GN{T}_d(\Fq)$ 
   are in bijection with characters of $T(K)$ vanishing on $T(K)_d$. 
@@
   Next we show that this isomorphism is functorial.
-The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$.
+  When combined with the definition of $\QC(\GN{T})$ and Property~\ref{T(K)}, the first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$.
 When further combined with Lemma~\ref{prop:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.
+
+  Finally, we turn to restriction of scalars.
 \end{proof}
@@
 \]
+\item
+For every finite Galois extension $L/K$ and for every algebraic torus $T$ over $K$, the following diagram commutes:
+\[
+\begin{tikzcd}
+\QCiso{\Gr(\underline{\Res_{L/K}(T_L)})} \arrow[two heads]{r} \dar & \QCiso{\Gr({T})} \dar\\
+\Hom_{\text{qc}}(T(L), \EEx) \arrow[two heads]{r} & \Hom_{\text{qc}}(T(K), \EEx)
+\end{tikzcd}
+\]
 \end{enumerate}
@@
 
-\section{Transfer of quasicharacter sheaves} \label{sec:transfer}
-
-The techniques in this paper apply to all non-archimdean local fields $K$ with residue field $k$, and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$ or on the ramification of $T$.
+\section{The transfer principle} \label{sec:transfer}
+
+\David{We should add a discussion of why we care about the transfer principle.}
+
+The techniques in this paper apply to all non-Archimdean local fields $K$ with residue field $k$, and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$ or on the ramification of $T$.
 Because of this, it is natural to ask if we can compare quasicharacter sheaves on $T$ and on $T'$ under conditions when there is a natural comparison between characters of $T(K)$ and of $T'(K')$.
-This comparison of has been made precise in \cite{CY}, building on ideas of \cite{Deligne:limites}.
-
-We recall the notion of $N$-congruent tori from \cite{CY}*{\S 2}.  
-Suppose $T$ and $T'$ are tori over non-archimedian local fields $K$ and $K'$, 
-splitting over $L$ and $L'$ respectively.
+This comparison of has been made precise in \cite{chai-yu:01a}, building on ideas of \cite{deligne:84a}.
+
+We recall the notion of $N$-congruent tori from  \cite{chai-yu:01a}*{\S 2}.  Suppose $T$ and $T'$
+are tori over non-Archimedian local fields $K$ and $K'$, splitting over $L$ and $L'$ respectively.
 Then $T$ and $T'$ are said to be \emph{$N$-congruent} if there are isomorphisms
@@
  \end{enumerate}
-It follows from this definition that if $T$ and $T'$ are $N$-congruent then $\alpha$, $\beta$ and $\phi$ determine an isomorphism
-\begin{equation}\label{transfer}
-  \Hom_{<N}(T(K), \EEx) \iso \Hom_{<N}(T'(K'),\EEx).
-\end{equation}
-Note that if $T$ and $T'$ are $N$-congruent, then they are $N'$ congruent for every $N' \leq N$.
-In this section we ask if the isomorphism \eqref{transfer} comes from an equivalence of categories of quasicharacter sheaves on $\GN{T}_d$ and those on $\GN{T'}_d$.
-
-One of the main results of \cite{CY} gives an isomorphism of group schemes between
+\[
+  \Hom_{<N}(T(K), \EEx) \to \Hom_{<N}(T'(K'),\EEx)
+ \]
+
+\begin{corollary}
+ Suppose that $T$ and $T'$ are $N$-congruent for $N > 3h$.  Then there is a canonical equivalence of categories
+ \[
+  \QC(\GN{T}_{N-3h}) \to \QC(\GN{T}'_{N-3h})
+ \]
+ determined by $\alpha, \beta$ and $\phi$ inducing the isomorphism
+ \[
+  \Hom(T(K) / T(K)_{N-3h}, \EEx) \to \Hom(T'(K') / T'(K')_{N-3h}, \EEx)
+ \]
+\end{corollary}
+
+\begin{proof}
+One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes between
 $\TT_d$ and $\TT'_d$ assuming that $T$ and $T'$ are sufficiently congruent.
 They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the
-Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{CY}*{\S 8.1}; let $h'$ be this quantity for $T'$.
-Then it follows from \cite{CY}*{Thm. 8.5} that if $T$ and $T'$ are $N$-congruent and $h=h'$ and $N > 3h$, then there is a canonical isomorphism
+Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}
+They then prove the following theorem \cite{chai-yu:01a}*{Thm. 8.5}
+ Suppose that $T$ and $T'$ are $N$-congruent for $N > 3h$.  Then there is a canonical isomorphism
  \[
@@
  determined by $\alpha, \beta$ and $\phi$.
-As an immediate consequence of this theorem and Theorem \ref{thm:application} we have the following
-
-\begin{proposition}
- With notation above, suppose that $T$ and $T'$ are $N$-congruent and $h=h'$ and $N > 3h$.  Set $d = N-3h$.
- Then there is a canonical equivalence of categories
- \[
-  \QC(\GN{T}'_{d}) \to \QC(\GN{T}_{d})
- \]
- determined by $\alpha, \beta$ and $\phi$ inducing the isomorphism
- \[
-  \Hom_{<d}(T'(K'), \EEx) \to \Hom_{<d}(T(K), \EEx).
- \]
-\end{proposition}
-
-\section{Toward geometric reciprocity}
-
-As indicated in the Introduction, we are tantalized 
-by the idea that quasicharacter sheaves for $T$ 
-may play a key role in a geometric, categorial version 
-of the local Langlands correspondence for algebraic tori 
-over non-archimedean local fields. 
-As with the local Langlands correspondence for algebraic tori, 
-it will be possible to reduce the essential points of the argument to the case $T= \Gm{K}$, provided that the category of quasicharacter sheaves behaves properly with regard to Weil restriction; see \cite{Yu:tori}*{Thm 7.5 (2)}.
-The next proposition shows that the category of quasicharacter sheaves for 
-algebraic tori does indeed behave properly with regard to Weil restriction.
-
-\begin{proposition}
-Let $K'/K$ be a finite Galois extension; 
-let $k'/k$ be the corresponding finite Galois extension of residue fields.
-Let $T$ be an algebraic torus over $K$ and 
-set $T' = T \times_\Spec{K} \Spec{K'}$.  
-The natural inclusion $T \hookrightarrow \Res_{K'/K} T'$ 
-induces a map of $k$-schemes
-\[
-\GN{T} \hookrightarrow \Res_{k'/k} \GN{T}'
-\]
-and thus a functor on quasicharacter sheaves through pullback.
-\[
-\QC(\Res_{k'/k} \GN{T}') \to \QC(\GN{T}).
-\]
-Through trace of Frobenius, this functor induces the homomorphism
-\[
-\begin{tikzcd}[column sep=60]
-\Hom_{<\infty}(T(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{T(K)}} &\Hom_{<\infty}(T(K), \EEx).
-\end{tikzcd}
-\] 
-\end{proposition}
-
-\begin{proof}
-\Clifton{The proof will require the results in the base change section.}
-There is a canonical isomorphism
-\[
-\Res_{k'/k} \Gr(\TL) \cong \Gr(\underline{\Res_{L/K}(T_L)}).
-\]
+
+As an immediate consequence of this theorem and Theorem \ref{thm:application} we have the following corollary:
 \end{proof}
 
-This paper has shown how quasicharacter sheaves 
-on the Greenberg transform of the Neron model of $T$ 
-determine admissible characters of $T(K)$, and vice versa, functorially. When coupled with the reciprocity map $\text{rec}_T $ for $T$, 
-which enjoys the same functorial properties, 
-it follows that quasicharacter sheaves for $T$ 
-determine Langlands parameters for $T$, and vice versa, functorially.
-\[
-\begin{tikzcd}
-\ & \arrow[swap]{dl}{\trFrob{G}} \QCiso{\GN{T}} \arrow[dashed]{dr}  & \\
-\Hom_{<\infty}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(K,\hat{T}_\ell) \\
-\end{tikzcd}
-\]
-We suspect that it is possible to extract Langlands parameters 
-from quasicharacter sheaves directly and that the reciprocity map 
-can then be be viewed as pairing characters and parameters coming
- from the same quasicharacter sheaf. 
- Results in this paper reduce the problem to the case $T=\Gm{K}$. 
- In that case, our suspicions are all but confirmed 
- by the class field theory of Serre-Hasewinkel as revisited in \cite{Suzuki&Yoshida:refinement}. 
- What remains to be done is a careful comparison of 
- quasicharacter sheaves for $\Gm{K}$ and certain local systems on
-  the fpqc-site of the pro-quasi-algebraic varieties appearing in \cite{Suzuki&Yoshida:refinement}.
-
 %\printindex
 
-\begin{bibdiv}
-\begin{biblist}
-
-\bib{BBD}{article}{
-   author={Be{\u\i}linson, A. A.},
-   author={Bernstein, J.},
-   author={Deligne, P.},
-   title={Faisceaux pervers},
-%   language={French},
-   conference={
-      title={Analyse et topologie sur les espaces singuliers (I)},
-      address={Luminy},
-      date={1981},
-   },
-   book={
-      series={Ast\'erisque},
-      volume={100},
-      publisher={Soc. Math. France},
-      place={Paris},
-   },
-   date={1982},
-%   pages={5--171},
-%   review={\MR{751966 (86g:32015)}},
-}
-
-\bib{BLR}{book}{
-   author={Bosch, Siegfried},
-   author={L{\"u}tkebohmert, Werner},
-   author={Raynaud, Michel},
-   title={N\'eron models},
-   series={Ergebnisse der Mathematik und ihrer Grenzgebiete (3) [Results in
-   Mathematics and Related Areas (3)]},
-   volume={21},
-   publisher={Springer-Verlag},
-   place={Berlin},
-   date={1990},
-%   pages={x+325},
-%   isbn={3-540-50587-3},
-%   review={\MR{1045822 (91i:14034)}},
-}
-
-\bib{Brandal}{book}{
- author={Brandal, Willy},
- title={Commutative Rings whose Finitely Generated Modules Decompose},
- publisher={Springer-Verlag},
- date={1979},
- series={Lecture Notes in Mathematics},
- number={723}
-}
-
-\bib{Chai}{article}{
-   author={Chai, C.L.},
-   title={N\'eron models for semiabelian varieties: congruence and change of base field.},
-   journal={Asian J. Math.},
-   volume={4},
-   number={4},
-   date={2000},
-   pages={715--736}}
-
-\bib{CY}{article}{
-   author={Chai, C.L.},
-   author={Yu, J.-K.},
-   title={Congruences of N\'eron models for tori and the Artin conductor},
-   journal={Ann. of Math.},
-   volume={154},
-   number={2},
-   date={2001},
-   pages={347-382}}
-
-\bib{Deligne:tensorielles}{article}{
-   author={Deligne, P.},
-   title={Cat\'egories tensorielles},
-%   language={French, with English summary},
-%   note={à Yu. I. Manin, en témoignage d'admiration},
-   journal={Mosc. Math. J.},
-   volume={2},
-   date={2002},
-   number={2},
-   pages={227--248},
-%   issn={1609-3321},
-%   review={\MR{1944506 (2003k:18010)}},
-}
-
-\bib{Deligne:Weil2}{article}{
-   author={Deligne, Pierre},
-   title={La conjecture de Weil. II},
-%   language={French},
-   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
-   number={52},
-   date={1980},
-   pages={137--252},
-%   issn={0073-8301},
-%   review={\MR{601520 (83c:14017)}},
-}
-
-\bib{Deligne:limites}{article}{
-   author={Deligne, P.},
-   title={Les corps locaux de caract\'eristique $p$, limites de corps locaux
-   de caract\'eristique $0$},
-%   language={French},
-   conference={
-      title={Representations of reductive groups over a local field},
-   },
-   book={
-      series={Travaux en Cours},
-      publisher={Hermann},
-      place={Paris},
-   },
-   date={1984},
-   pages={119--157},
-%   review={\MR{771673 (86g:11068)}},
-}
-
-\bib{SGA4.5}{book}{
-   author={Deligne, P.},
-   title={Cohomologie \'etale},
-   series={Lecture Notes in Mathematics, Vol. 569},
-   note={S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois-Marie 1963-64 SGA
-   4$\frac{1}{2}$; 
-   Avec la collaboration de J. F. Boutot, A. Grothendieck, L. Illusie et J.
-   L. Verdier},
-   publisher={Springer-Verlag},
-   place={Berlin},
-%date={4h},
-   date={1977},
-%   pages={iv+312pp},
-%   review={\MR{0463174 (57 \#3132)}},
-}
-
-\bib{SGA7.2}{book}{
-   title={Groupes de monodromie en g\'eom\'etrie alg\'ebrique. II},
-%   language={French},
- author={Deligne, P.},
- author={Katz, N.},
-   series={Lecture Notes in Mathematics, Vol. 340},
-   note={S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois-Marie 1967--1969
-   (SGA 7 II);
-   Dirig\'e par P. Deligne et N. Katz},
-   publisher={Springer-Verlag},
-   place={Berlin},
-   date={1973},
-%   pages={x+438},
-%   review={\MR{0354657 (50 \#7135)}},
-}
-
-\bib{vdG&M}{book}{
-author={Geer, van der},
-author={Moonen},
-title={Abelian Varieties},
-note={http://staff.science.uva.nl/$\sim$bmoonen/boek/BookAV.html}
-}
-
-\bib{Greenberg:2}{article}{
-   author={Greenberg, Marvin J.},
-   title={Schemata over local rings. II},
-   journal={Ann. of Math. (2)},
-   volume={78},
-   date={1963},
-   pages={256--266},
-%   issn={0003-486X},
-%   review={\MR{0156855 (28 \#98)}},
-}
-
-\bib{SGA1}{collection}{
-   title={Rev\^etements \'etales et groupe fondamental (SGA 1)},
-%   language={French},
-   author={Grothendieck, A.},
-   series={Documents Math\'ematiques (Paris), 3},
-   note={S\'eminaire de g\'eom\'etrie alg\'ebrique du Bois Marie 1960--61.
-   Un s\'eminaire dirig\'e par A. Grothendieck
-Augment\'e de deux expos\'es de Mme M. Raynaud
-\'Edition recompos\'e et annot\'e du volume 224 des Lecture Notes in Mathematics publi\'e en 1971 par Springer-Verlag},
-   publisher={Soci\'et\'e Math\'ematique de France},
-   place={Paris},
-   date={2003},
-   pages={xviii+327},
-%  isbn={2-85629-141-4},
-%   review={\MR{2017446 (2004g:14017)}},
-}
-
-\bib{Kamgarpour}{article}{
-   author={Kamgarpour, M.},
-   title={Stacky abelianization of algebraic groups},
-   journal={Transform. Groups},
-   volume={14},
-   date={2009},
-   number={4},
-   pages={825--846},
-%   issn={1083-4362},
-%   review={\MR{2577200 (2011b:20136)}},
-%   doi={10.1007/s00031-009-9067-8},
-}
-
-\bib{Laumon}{article}{
-   author={Laumon, G.},
-   title={Transformation de Fourier, constantes d'\'equations fonctionnelles
-   et conjecture de Weil},
-%   language={French},
-   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
-   number={65},
-   date={1987},
-   pages={131--210},
-%   issn={0073-8301},
-%   review={\MR{908218 (88g:14019)}},
-}
-
-\bib{Serre:isogenies}{article}{
-   author={Serre, Jean-Pierre},
-   title={Corps locaux et isog\'enies},
-%   language={French},
-   conference={
-      title={S\'eminaire Bourbaki, Vol.\ 5},
-   },
-   book={
-      publisher={Soc. Math. France},
-      place={Paris},
-   },
-   date={1995},
-   pages={Exp.\ No.\ 185, 239--247},
-%   review={\MR{1603470}},
-}
-
-\bib{Stasinski}{article}{
-   author={Stasinski, Alexander},
-   title={Reductive group schemes, the Greenberg functor, and associated
-   algebraic groups},
-   journal={J. Pure Appl. Algebra},
-   volume={216},
-   date={2012},
-   number={5},
-   pages={1092--1101},
-%   issn={0022-4049},
-%   review={\MR{2875329}},
-%   doi={10.1016/j.jpaa.2011.10.027},
-}
-
-\bib{Suzuki&Yoshida:refinement}{article}{
-   author={Suzuki, Takashi},
-   author={Yoshida, Manabu},
-   title={A refinement of the local class field theory of Serre and
-   Hazewinkel},
-   conference={
-      title={Algebraic number theory and related topics 2010},
-   },
-   book={
-      series={RIMS K\^oky\^uroku Bessatsu, B32},
-      publisher={Res. Inst. Math. Sci. (RIMS), Kyoto},
-   },
-   date={2012},
-   pages={163--191},
-%   review={\MR{2986923}},
-}
-
-\bib{Tate:thesis}{article}{
-   author={Tate, J. T.},
-   title={Fourier analysis in number fields, and Hecke's zeta-functions},
-   conference={
-      title={Algebraic Number Theory (Proc. Instructional Conf., Brighton,
-      1965)},
-   },
-   book={
-      publisher={Thompson, Washington, D.C.},
-   },
-   date={1967},
-   pages={305--347},
-   review={\MR{0217026 (36 \#121)}},
-}
-
-\bib{Xarles}{article}{
-   author={Xarles, Xavier},
-   title={The scheme of connected components of the N\'eron model of an algebraic torus},
-   journal={J. Reine Angew. Math.},
-   volume={437},
-   date={1993},
-   pages={167--179},
-%   issn={0075-4102},
-%   review={\MR{1212256 (94d:14044)}},
-%   doi={10.1515/crll.1993.437.167},
-}
-
-\bib{Yu}{article}{
-   author={Yu, Jiu-Kang},
-   title={Smooth models associated to concave functions in Bruhat-Tits theory}
-}
-
-\bib{Yu:tori}{article}{
-   author={Yu, Jiu-Kang},
-   title={On the local Langlands correspondence for tori},
-   conference={
-      title={Ottawa lectures on admissible representations of reductive
-      $p$-adic groups},
-   },
-   book={
-      series={Fields Inst. Monogr.},
-      volume={26},
-      publisher={Amer. Math. Soc.},
-      place={Providence, RI},
-      editor={Cunningham, C.},
-      editor={Nevins, M.},
-   },
-   date={2009},
-   pages={177--183},
-   review={\MR{2508725 (2009m:11201)}},
-}
-
-\end{biblist}
-\end{bibdiv}
+\bibliographystyle{plain}
+\bibliography{Biblio}
 

### 2013-08-15 shanghai.tex

--- 2013-08-15 shanghai.tex
@@
 %\usepackage[shortalphabetic]{amsrefs}
-\usepackage[alphabetic]{amsrefs}
+%\usepackage[alphabetic]{amsrefs}
 \renewcommand\MR{\relax}
@@
 %\begin{remark} \label{rem:CS-action}
-The rule $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$ defines a forgetful functor from quasicharacter sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{Deligne:Weil2}*{Def.~1.1.10 (i)}.
-
-As mentioned after \cite{Deligne:Weil2}*{Def.~1.1.10}, a Weil sheaf $(\gcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
+The rule $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$ defines a forgetful functor from quasicharacter sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
+
+As mentioned after \cite{deligne:80a}*{Def.~1.1.10}, a Weil sheaf $(\gcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
 Since we will need this point of view later, we review that interpretation here.
@@
 In this context, finite quasicharacter sheaves may also be apprehended as \emph{certain} $\ell$-adic characters of fundamental group $\pi_1(G,{\bar e})$. 
-As explained in \cite{Kamgarpour}*{\S~2}, 
+As explained in \cite{kamgarpour:09a}*{\S~2}, 
 the relevant characters of $\pi_1(G,{\bar e})$ are precisely those 
@@
 %\[\pi_1(G,{\bar e}) \to \Pi_\text{et}(G) \to \Pi_\text{et}(G)_{\Gal(\bFq/\Fq)} = \Pi_\text{disc}(G)\]
-From this it is apparent that the category of discrete isogenies to $G$ is a Galois category, in the sense of \cite{SGA1}*{Expos\'e V, \S 4}.
-Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$, as shown in \cite{Kamgarpour}*{App'x B}, this provides an alternate proof of $\QCiso{G} \to G(\Fq)^*$.
+From this it is apparent that the category of discrete isogenies to $G$ is a Galois category, in the sense of \cite{grothendieck:SGA1}*{Expos\'e V, \S 4}.
+Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$, as shown in \cite{kamgarpour:09a}*{App'x B}, this provides an alternate proof of $\QCiso{G} \to G(\Fq)^*$.
 
@@
   product of Dedekind domains.  Therefore $X$ decomposes into a direct
-  sum of cyclic $\ZZ[\Gamma_m]$-modules \cite{Brandal}*{?}, each of the
+  sum of cyclic $\ZZ[\Gamma_m]$-modules \cite{brandal:CommRingsFGModDecompose}, each of the \David{Add a section to this reference}
   form $\ZZ[\Gamma_m] / I$ for some ideal $I \subset \ZZ[\Gamma_m]$.
@@
   $\Gamma_m = \Gamma / H_m$.  Any product of Dedekind domains has
-  cohomological dimension $1$ \cite[?]{?}, so $\pi_0(G)(\bFq)$ has a
+  cohomological dimension $1$ \David{Add a citation for this fact}, so $\pi_0(G)(\bFq)$ has a
   two term resolution by injective $\ZZ[\Gamma_m]$-modules.  Let $I$
@@
 We write $\Hom_{< d}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $d$ 
-and $\Hom_{<\infty}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth; one might call these quasicharacters of $T(K)$, expanding on \cite{Tate:thesis}*{2.3}.
+and $\Hom_{<\infty}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth; one might call these quasicharacters of $T(K)$, expanding on \cite{tate:67a}*{2.3}.
 
@@
 
-See \cite{Greenberg:2} and \cite[Ch. 9, \S 6]{BLR} and the first few sections of \cite{Stasinski} for background on the Greenberg functor. The fundamental properties of $\GN{T}_d$ that we need are:
+See \cite{greenberg:63a} and \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch.
+9, \S 6} and the first few sections of \cite{stasinski:12a} for background on the Greenberg functor.
+The fundamental properties of $\GN{T}_d$ that we need are:
  \begin{enumerate}
@@
 Because of this, it is natural to ask if we can compare quasicharacter sheaves on $T$ and on $T'$ under conditions when there is a natural comparison between characters of $T(K)$ and of $T'(K')$.
-This comparison of has been made precise in \cite{CY}, building on ideas of \cite{Deligne:limites}.
-
-We recall the notion of $N$-congruent tori from \cite{CY}*{\S 2}.  
+This comparison of has been made precise in \cite{chai-yu:01a}, building on ideas of \cite{deligne:84a}.
+
+We recall the notion of $N$-congruent tori from  \cite{chai-yu:01a}*{\S 2}.
 Suppose $T$ and $T'$ are tori over non-archimedian local fields $K$ and $K'$,
@@
 
-One of the main results of \cite{CY} gives an isomorphism of group schemes between
+One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes between
 $\TT_d$ and $\TT'_d$ assuming that $T$ and $T'$ are sufficiently congruent.
 They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the
-Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{CY}*{\S 8.1}; let $h'$ be this quantity for $T'$.
-Then it follows from \cite{CY}*{Thm. 8.5} that if $T$ and $T'$ are $N$-congruent and $h=h'$ and $N > 3h$, 
+Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}; let $h'$ be this quantity for $T'$.
+Then it follows from \cite{chai-yu:01a}*{Thm. 8.5} that if $T$ and $T'$ are $N$-congruent and $h=h'$ and $N > 3h$, 
 \Clifton{Is this correct?}
@@
 As with the local Langlands correspondence for algebraic tori over local fields, 
-it will be possible to reduce the essential points of the argument to the case $T= \Gm{K}$, provided that the category of quasicharacter sheaves behaves properly with regard to Weil restriction; see \cite{Yu:tori}*{Thm 7.5 (2)}.
+it will be possible to reduce the essential points of the argument to the case $T= \Gm{K}$, provided that the category of quasicharacter sheaves behaves properly with regard to Weil restriction; see \cite{yu:09a}*{Thm 7.5 (2)}.
 The next proposition shows that the category of quasicharacter sheaves for 
@@
  In that case, our suspicions are all but confirmed 
- by the class field theory of Serre-Hasewinkel, \Clifton{Need references for S-H CFT.} especially as revisited in \cite{Suzuki&Yoshida:refinement}. 
+ by the class field theory of Serre-Hasewinkel, \Clifton{Need references for S-H CFT.} especially as revisited in \cite{suzuki-yoshida:12a}. 
  What remains to be done is a careful comparison of 
  quasicharacter sheaves for $\Gm{K}$ and certain local systems on
-  the fpqc-site of the pro-quasi-algebraic varieties appearing in \cite{Suzuki&Yoshida:refinement}.
+  the fpqc-site of the pro-quasi-algebraic varieties appearing in \cite{suzuki-yoshida:12a}.
 
@@
 
-\begin{bibdiv}
-\begin{biblist}
-
-\bib{BBD}{article}{
-   author={Be{\u\i}linson, A. A.},
-   author={Bernstein, J.},
-   author={Deligne, P.},
-   title={Faisceaux pervers},
-%   language={French},
-   conference={
-      title={Analyse et topologie sur les espaces singuliers (I)},
-      address={Luminy},
-      date={1981},
-   },
-   book={
-      series={Ast\'erisque},
-      volume={100},
-      publisher={Soc. Math. France},
-      place={Paris},
-   },
-   date={1982},
-%   pages={5--171},
-%   review={\MR{751966 (86g:32015)}},
-}
-
-\bib{BLR}{book}{
-   author={Bosch, Siegfried},
-   author={L{\"u}tkebohmert, Werner},
-   author={Raynaud, Michel},
-   title={N\'eron models},
-   series={Ergebnisse der Mathematik und ihrer Grenzgebiete (3) [Results in
-   Mathematics and Related Areas (3)]},
-   volume={21},
-   publisher={Springer-Verlag},
-   place={Berlin},
-   date={1990},
-%   pages={x+325},
-%   isbn={3-540-50587-3},
-%   review={\MR{1045822 (91i:14034)}},
-}
-
-\bib{Brandal}{book}{
- author={Brandal, Willy},
- title={Commutative Rings whose Finitely Generated Modules Decompose},
- publisher={Springer-Verlag},
- date={1979},
- series={Lecture Notes in Mathematics},
- number={723}
-}
-
-\bib{Chai}{article}{
-   author={Chai, C.L.},
-   title={N\'eron models for semiabelian varieties: congruence and change of base field.},
-   journal={Asian J. Math.},
-   volume={4},
-   number={4},
-   date={2000},
-   pages={715--736}}
-
-\bib{CY}{article}{
-   author={Chai, C.L.},
-   author={Yu, J.-K.},
-   title={Congruences of N\'eron models for tori and the Artin conductor},
-   journal={Ann. of Math.},
-   volume={154},
-   number={2},
-   date={2001},
-   pages={347-382}}
-
-\bib{Deligne:tensorielles}{article}{
-   author={Deligne, P.},
-   title={Cat\'egories tensorielles},
-%   language={French, with English summary},
-%   note={à Yu. I. Manin, en témoignage d'admiration},
-   journal={Mosc. Math. J.},
-   volume={2},
-   date={2002},
-   number={2},
-   pages={227--248},
-%   issn={1609-3321},
-%   review={\MR{1944506 (2003k:18010)}},
-}
-
-\bib{Deligne:Weil2}{article}{
-   author={Deligne, Pierre},
-   title={La conjecture de Weil. II},
-%   language={French},
-   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
-   number={52},
-   date={1980},
-   pages={137--252},
-%   issn={0073-8301},
-%   review={\MR{601520 (83c:14017)}},
-}
-
-\bib{Deligne:limites}{article}{
-   author={Deligne, P.},
-   title={Les corps locaux de caract\'eristique $p$, limites de corps locaux
-   de caract\'eristique $0$},
-%   language={French},
-   conference={
-      title={Representations of reductive groups over a local field},
-   },
-   book={
-      series={Travaux en Cours},
-      publisher={Hermann},
-      place={Paris},
-   },
-   date={1984},
-   pages={119--157},
-%   review={\MR{771673 (86g:11068)}},
-}
-
-\bib{SGA4.5}{book}{
-   author={Deligne, P.},
-   title={Cohomologie \'etale},
-   series={Lecture Notes in Mathematics, Vol. 569},
-   note={S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois-Marie 1963-64 SGA
-   4$\frac{1}{2}$; 
-   Avec la collaboration de J. F. Boutot, A. Grothendieck, L. Illusie et J.
-   L. Verdier},
-   publisher={Springer-Verlag},
-   place={Berlin},
-%date={4h},
-   date={1977},
-%   pages={iv+312pp},
-%   review={\MR{0463174 (57 \#3132)}},
-}
-
-\bib{SGA7.2}{book}{
-   title={Groupes de monodromie en g\'eom\'etrie alg\'ebrique. II},
-%   language={French},
- author={Deligne, P.},
- author={Katz, N.},
-   series={Lecture Notes in Mathematics, Vol. 340},
-   note={S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois-Marie 1967--1969
-   (SGA 7 II);
-   Dirig\'e par P. Deligne et N. Katz},
-   publisher={Springer-Verlag},
-   place={Berlin},
-   date={1973},
-%   pages={x+438},
-%   review={\MR{0354657 (50 \#7135)}},
-}
-
-\bib{vdG&M}{book}{
-author={Geer, van der},
-author={Moonen},
-title={Abelian Varieties},
-note={http://staff.science.uva.nl/$\sim$bmoonen/boek/BookAV.html}
-}
-
-\bib{Greenberg:2}{article}{
-   author={Greenberg, Marvin J.},
-   title={Schemata over local rings. II},
-   journal={Ann. of Math. (2)},
-   volume={78},
-   date={1963},
-   pages={256--266},
-%   issn={0003-486X},
-%   review={\MR{0156855 (28 \#98)}},
-}
-
-\bib{SGA1}{collection}{
-   title={Rev\^etements \'etales et groupe fondamental (SGA 1)},
-%   language={French},
-   author={Grothendieck, A.},
-   series={Documents Math\'ematiques (Paris), 3},
-   note={S\'eminaire de g\'eom\'etrie alg\'ebrique du Bois Marie 1960--61.
-   Un s\'eminaire dirig\'e par A. Grothendieck
-Augment\'e de deux expos\'es de Mme M. Raynaud
-\'Edition recompos\'e et annot\'e du volume 224 des Lecture Notes in Mathematics publi\'e en 1971 par Springer-Verlag},
-   publisher={Soci\'et\'e Math\'ematique de France},
-   place={Paris},
-   date={2003},
-   pages={xviii+327},
-%  isbn={2-85629-141-4},
-%   review={\MR{2017446 (2004g:14017)}},
-}
-
-\bib{Kamgarpour}{article}{
-   author={Kamgarpour, M.},
-   title={Stacky abelianization of algebraic groups},
-   journal={Transform. Groups},
-   volume={14},
-   date={2009},
-   number={4},
-   pages={825--846},
-%   issn={1083-4362},
-%   review={\MR{2577200 (2011b:20136)}},
-%   doi={10.1007/s00031-009-9067-8},
-}
-
-\bib{Laumon}{article}{
-   author={Laumon, G.},
-   title={Transformation de Fourier, constantes d'\'equations fonctionnelles
-   et conjecture de Weil},
-%   language={French},
-   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
-   number={65},
-   date={1987},
-   pages={131--210},
-%   issn={0073-8301},
-%   review={\MR{908218 (88g:14019)}},
-}
-
-\bib{Serre:isogenies}{article}{
-   author={Serre, Jean-Pierre},
-   title={Corps locaux et isog\'enies},
-%   language={French},
-   conference={
-      title={S\'eminaire Bourbaki, Vol.\ 5},
-   },
-   book={
-      publisher={Soc. Math. France},
-      place={Paris},
-   },
-   date={1995},
-   pages={Exp.\ No.\ 185, 239--247},
-%   review={\MR{1603470}},
-}
-
-\bib{Stasinski}{article}{
-   author={Stasinski, Alexander},
-   title={Reductive group schemes, the Greenberg functor, and associated
-   algebraic groups},
-   journal={J. Pure Appl. Algebra},
-   volume={216},
-   date={2012},
-   number={5},
-   pages={1092--1101},
-%   issn={0022-4049},
-%   review={\MR{2875329}},
-%   doi={10.1016/j.jpaa.2011.10.027},
-}
-
-\bib{Suzuki&Yoshida:refinement}{article}{
-   author={Suzuki, Takashi},
-   author={Yoshida, Manabu},
-   title={A refinement of the local class field theory of Serre and
-   Hazewinkel},
-   conference={
-      title={Algebraic number theory and related topics 2010},
-   },
-   book={
-      series={RIMS K\^oky\^uroku Bessatsu, B32},
-      publisher={Res. Inst. Math. Sci. (RIMS), Kyoto},
-   },
-   date={2012},
-   pages={163--191},
-%   review={\MR{2986923}},
-}
-
-\bib{Tate:thesis}{article}{
-   author={Tate, J. T.},
-   title={Fourier analysis in number fields, and Hecke's zeta-functions},
-   conference={
-      title={Algebraic Number Theory (Proc. Instructional Conf., Brighton,
-      1965)},
-   },
-   book={
-      publisher={Thompson, Washington, D.C.},
-   },
-   date={1967},
-   pages={305--347},
-%   review={\MR{0217026 (36 \#121)}},
-}
-
-\bib{Xarles}{article}{
-   author={Xarles, Xavier},
-   title={The scheme of connected components of the N\'eron model of an algebraic torus},
-   journal={J. Reine Angew. Math.},
-   volume={437},
-   date={1993},
-   pages={167--179},
-%   issn={0075-4102},
-%   review={\MR{1212256 (94d:14044)}},
-%   doi={10.1515/crll.1993.437.167},
-}
-
-\bib{Yu}{article}{
-   author={Yu, Jiu-Kang},
-   title={Smooth models associated to concave functions in Bruhat-Tits theory}
-}
-
-\bib{Yu:tori}{article}{
-   author={Yu, Jiu-Kang},
-   title={On the local Langlands correspondence for tori},
-   conference={
-      title={Ottawa lectures on admissible representations of reductive
-      $p$-adic groups},
-   },
-   book={
-      series={Fields Inst. Monogr.},
-      volume={26},
-      publisher={Amer. Math. Soc.},
-      place={Providence, RI},
-      editor={Cunningham, C.},
-      editor={Nevins, M.},
-   },
-   date={2009},
-   pages={177--183},
-   review={\MR{2508725 (2009m:11201)}},
-}
-
-\end{biblist}
-\end{bibdiv}
+\bibliographystyle{plain}
+\bibliography{Biblio}
 

### 2013-08-15 shanghai.tex
Title change: sheaf-function dictionary

@@
 \documentclass[11pt]{amsart}
-\title[Geometrization of characters of tori]{Geometrization of characters of tori over non-archimedean local fields}
+\title[Sheaf--function dictionary for local tori]{A sheaf--function dictionary for algebraic tori over non-archimedean local fields}
 \usepackage[british]{babel}
@@
 $\Frob{G} : \bG \to \bG$ for the Frobenius automorphism.
-A quasicharacter sheaf on $G$ is a 
-\Clifton{ [Use this?:] . . . is an $\ell$-adic Weil local system of rank-$1$ on $G$, equipped with an isomorphism ... }
-triple $\cs{L}\ceq
+A quasicharacter sheaf on $G$ is a triple $\cs{L}\ceq
 (\gcs{L},\mu,\phi)$ where $\gcs{L}$ is an $\ell$-adic local system on $\bG$ of rank-1 and $\mu: m^*
@@
 
-A lft-N\'eron model for $T$, denoted here by $\TT$, 
-is a separated, smooth, commutative group scheme locally of finite type over $\OK$ with generic fibre $T$, that enjoys the N\'eron mapping property: if
-$S$ is a smooth scheme over $\OK$ then every morphism $S_\eta \to T$
+A N\'eron model for $T$, denoted here by $\TT$, 
+is a separated, smooth, commutative group scheme locally of finite type over $\OK$ with generic fibre $T$, that enjoys the N\'eron mapping property: \Clifton{Include reference to BLR.}
+if $S$ is a smooth scheme over $\OK$ then every morphism $S_\eta \to T$
 over $K$ extends uniquely to a morphism $S \to \TT$. Equivalently, the

### 2013-08-15 shanghai.tex
got to go  . . .

@@
 %\begin{proposition}\label{tensor}
-The category $\QC(G)$ of quasicharacter sheaves on $G$ is a rigid symmetric monoidal category \Clifton{I still haven't found a good reference for this!} under
+The category $\QC(G)$ of quasicharacter sheaves on $G$ is rigid symmetric monoidal category \cite{etingof:tensorcat} under the tensor product
 $\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$

### 2013-08-16 shanghai.tex
Fixing some bibilography stuff

@@
 %\begin{proposition}\label{tensor}
-The category $\QC(G)$ of quasicharacter sheaves on $G$ is rigid symmetric monoidal category \cite{etingof:tensorcat} under the tensor product
+The category $\QC(G)$ of quasicharacter sheaves on $G$ is rigid symmetric monoidal category \cite{etingof:09a} under the tensor product
 $\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$

### 2013-08-16 shanghai.tex
Expanded abbreviations: PIMS, NSERC, BIRS

@@
 
-We also gratefully acknowledge the financial support of PIMS and NSERC,
-and the hospitality of BIRS during our weeklong stay in May 2012.
-\David{Should these be abbreviated or written out in full?}
+We also gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
+and of the National Science and Engineering Research Council,
+as well the hospitality of the Banff International Research Station during our weeklong stay in May 2012.
 

### 2013-08-16 shanghai.tex
Turned amsrefs back on
Changed section title
Adding some references

@@
 %\usepackage[shortalphabetic]{amsrefs}
-%\usepackage[alphabetic]{amsrefs}
+\usepackage[alphabetic]{amsrefs}
 \renewcommand\MR{\relax}
@@
 
-In recent years various authors have applied Deligne-Lusztig representations to the
-local Langlands correspondence \cite{}.  The next step Lusztig took in studying representations
+DeBacker and Reeder have recently applied Deligne-Lusztig representations to the
+local Langlands correspondence \cite{reeder-debacker:09a}.  The next step Lusztig took in studying representations
 of finite groups of Lie type was to define character sheaves for reductive groups over $\Fq$.
@@
 group schemes which are not necessarily connected or finite type.  The other main use
-of the term ``character sheaf'' traces back to Lusztig \cite{}.  Most of his energy is devoted to
+of the term ``character sheaf'' traces back to Lusztig \cite{lusztig:85a}.  Most of his energy is devoted to
 handling non-commutative groups; though he does define character sheaves for some
@@
 
-\section{Main result regarding quasicharacter sheaves}
+\section{The sheaf-function dictionary for non-connected groups}
 \label{sec:snake}

### 2013-08-16 shanghai.tex
Finished the proof that QCiso(G) = H^1(k,G^*). Added a remark after the lemma on global sections.
Explained that the lemma on global sections is the genesis of the
hypothesis on G for the sheaf-function dictionary for G.

--- 2013-08-16 shanghai.tex
@@
 %\begin{proposition}\label{tensor}
-The category $\QC(G)$ of quasicharacter sheaves on $G$ is rigid symmetric monoidal category \cite{etingof:09a} under the tensor product
-$\cs{L} \otimes \cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$
+The category $\QC(G)$ of quasicharacter sheaves on $G$ is rigid symmetric monoidal category \cite{etingof:tensorcat} under the tensor product
+$\cs{L} \otimes_{\EE}\cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes_{\EE}\phi')$
 with duals given by applying the functor 
@@
  \labitem{(cs.1)}{cs.1} an indexed set of isomorphisms
-  $\mu_{x,y} : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes \gcs{L}_{y}$,
+  $\mu_{x,y} : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes_{\EE}\gcs{L}_{y}$,
   for all $x,y \in G(\bFq)$, such that
@@
     \gcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
-    && \gcs{L}_{x+y}\otimes \gcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
-    \gcs{L}_{x} \otimes \gcs{L}_{y+z} \arrow{rr}{\id \otimes \mu_{y,z}}
-    && \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes \gcs{L}_{z}
+    && \gcs{L}_{x+y}\otimes_{\EE}\gcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
+    \gcs{L}_{x} \otimes_{\EE}\gcs{L}_{y+z} \arrow{rr}{\id \otimes_{\EE}\mu_{y,z}}
+    && \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes_{\EE}\gcs{L}_{z}
    \end{tikzcd}
@@
     \gcs{L}_{\Frob{\Fq}(x)+\Frob{\Fq}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{\Fq}(x),\Frob{\Fq}(y)}}
-    && \gcs{L}_{\Frob{\Fq}(x)}\otimes \gcs{L}_{\Frob{\Fq}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
+    && \gcs{L}_{\Frob{\Fq}(x)}\otimes_{\EE}\gcs{L}_{\Frob{\Fq}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
     \gcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
@@
     \gcs{L}_x \rar{\alpha_x} & \gcs{L'}_x
-    & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\alpha_x\otimes \alpha_y} & \gcs{L'}_x \otimes \gcs{L'}_y
+    & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\alpha_x\otimes_{\EE}\alpha_y} & \gcs{L'}_x \otimes_{\EE}\gcs{L'}_y
    \end{tikzcd}
@@
  \begin{equation}\label{section}
-  \forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes s(y).
+  \forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes_{\EE}s(y).
  \end{equation}
@@
   let $x_1, \ldots, x_r, y_1, \ldots, y_t$ be a corresponding set of generators of $G(\bFq)$.
-  We will define a section $s$ by choosing values on these generators and extending to all
+  We will define a section $s$ satisfying \eqref{section} by choosing values on these generators and extending to all
   of $G(\bFq)$ through \eqref{section}.
@@
   There is a unique isomorphism $\gcs{L}_0 \cong \EE$ under which $\mu_{0,0}$ corresponds
-  to the multiplication map $\EE \otimes \EE \to \EE$.
-  The condition $\mu_{0,0}(s(0)) = s(0) \otimes s(0)$ together with the non-triviality of $s$
+  to the multiplication map $\EE \otimes_{\EE}\EE \to \EE$.
+  The condition $\mu_{0,0}(s(0)) = s(0) \otimes_{\EE}s(0)$ together with the non-triviality of $s$
   then forces $s(0) = 1$.
@@
 
-These sections will allow us to construct the isomorphism in the following proposition.
+The main result of Part~\ref{part1} of this paper, 
+the sheaf-function dictionary for $G$ Theorem~\ref{thm:snake}, has a hypothesis: 
+the smooth commutative group scheme locally of finite type must have the 
+property that the geometric component group of $G$ is finitely generated as a group. 
+The genesis of that hypothesis is Lemma~\ref{lemma:section},
+as we use this hypothesis to show the existence of global sections of $\gcs{L}$ satisfying \eqref{section} for $\mu$.
+Remarkably, Lemma~\ref{lemma:section} is the only crux for this hypothesis;
+that is, if $G$ is any smooth connected group scheme locally of finite type over $\Fq$
+and if each quasicharacter sheaf on the etale group scheme $\pi_0(G)$ admits a global section 
+satisfying \eqref{section}, then the conclusion of Theorem~\ref{thm:snake} holds for $G$,
+so there is a sheaf-function dictionary for $G$.
 
@@
   \qquad \text{given by}\qquad
-  [\cs{L}] \mapsto [\tau_\cs{L}],
+  \cs{L}_{/\text{iso}} \mapsto [\tau_\cs{L}],
   \]
@@
   Suppose $\cs{L}$ is a quasicharacter sheaf on $G$.  
-Using Lemma~\ref{lemma:section}, we may choose a section $s = \{ s(x) \in \gcs{L}_x \tq x \in G(\bFq) \}$ satisfying \eqref{section}.
-We will construct a group isomorphism between $\QCiso{G(\bFq)}$ and
-  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ using $s$, then prove independence from the choice of section.
+  Using Lemma~\ref{lemma:section}, 
+  we may choose a section $s = \{ s(x) \in \gcs{L}_x \tq x \in G(\bFq) \}$ satisfying \eqref{section}.  We will construct a group isomorphism between $\QCiso{G}$ and
+  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ using $s$, then prove independence from the choice of $s$.
 
@@
   \begin{equation}\label{cohomologous}
-    \obj \QC(G(\bFq)) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
+    \obj \QC(G) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
     \qquad \text{defined by} \qquad \cs{L} \mapsto [\tau_\cs{L}],
@@
   We now show that $[\tau_\cs{L}]$ depends only on the isomorphism class of $\cs{L}$.
-  Let $\varphi : \cs{L} \to \cs{L'}$ be an isomorphism and
+  Let $\alpha : \cs{L} \to \cs{L'}$ be an isomorphism and
   let $\tau$ and $\tau'$ be any cocycles representing the classes in the
   image of $\cs{L}$ and $\cs{L'}$ under \eqref{cohomologous}; by construction,
-  $\tau$ and $\tau'$ are defined by sections $s$ and $s'$. Now, $\varphi_x(s(x))$ is a
-  non-zero scalar multiple of $s'(x)$; define $\delta: G(\bFq) \to \EEx$
-  by $\varphi_x(s(x)) = \delta(x) s'(x)$.
+  $\tau$ and $\tau'$ are defined by the choice of sections $s$ and $s'$ 
+  according to Lemma~\ref{lemma:sec}.
+    Now, $\varphi_x(s(x))$ is a
+  non-zero scalar multiple of $s'(x)$; define $a: G(\bFq) \to \EEx$
+  by $\alpha_x(s(x)) = a(x) s'(x)$.
   By the second part of condition~\ref{cs.3},
-  $\delta(x+y) = \delta(x)\delta(y)$, so $\delta \in G(\bFq)^*$. By the first part of
-  condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}\delta \cdot \delta^{-1})$,
-  so $\tau$ and $\tau'$ are cohomologous. This concludes the definition of
+  $a(x+y) = a(x)a(y)$, so $a \in G(\bFq)^*$. By the first part of
+  condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}a \cdot a^{-1})$,
+  so $\tau$ and $\tau'$ are cohomologous. This shows that
   \begin{equation}\label{pich1}
-    \QCiso{G(\bFq} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*).
+    \QCiso{G} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*), \qquad \cs{L}_{/\text{iso}} \mapsto [\tau_\cs{L}]
   \end{equation}
-
-  It only remains to show that \eqref{pich1} is a group
-  isomorphism.  Suppose that $\cs{L}$ and $\cs{L}'$ are two quasicharacter sheaves.
-  If $s$ is a global section for $\cs{L}$ and $s'$ for $\cs{L}'$ then $s \otimes s'$ is a global section for
-  $\cs{L} \otimes \cs{L}'$.  The three versions of \eqref{t} for $\cs{L}, \cs{L'}$ and $\cs{L} \otimes \cs{L}'$ imply that
-  $\tau_{\cs{L} \otimes \cs{L}'}(\Frob{k}) = \tau_\cs{L}(\Frob{k}) \tau_{\cs{L}'}(\Frob{k})$, so \eqref{pich1} is a group homomorphism.
-\Clifton{I'm working on this.}
+  is well-defined.
+
+ The paragraph above also shows that \eqref{pich1} is injective. 
+ Suppose $[\tau_\cs{L}] = [\tau_\cs{L'}]$.
+ Let $s$ (resp. $s'$) be a section appearing in the definition of $\tau_\cs{L}$ (resp. $\tau_\cs{L'}$);
+ recall that $s$ (resp. $s'$) is compatible with $\mu$ (resp $\mu'$) 
+ in the sense of Lemma~\ref{lemma:section}.
+ Since $[\tau_\cs{L}] = [\tau_\cs{L'}]$, 
+ it follows that $\tau_\cs{L}$ and $\tau_{\cs{L'}}$ are cohomologous, 
+  so there is some $a\in G(\Fq)^*$ such that 
+  $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}a \cdot a^{-1})$. 
+  Define $\alpha : \cs{L}\to \cs{L'}$ by $\alpha_x(s(x)) = a(x) s'(x)$, for each $x\in G(\bFq)$.
+  it is straightforward to check that $\alpha$ satisfies condition~\ref{cs.3}
+  and that $\alpha^{-1} : \cs{L'}\to \cs{L}$, defined by $\alpha^{-1}_x(s'(x)) = a(x)^{-1} s(x)$, 
+  is its inverse. Thus, $\cs{L} \iso \cs{L'}$ in $\QC(G)$. 
+  This shows that \eqref{pich1} is injective.
+
+  Suppose that $\cs{L}$ and $\cs{L}'$ are two quasicharacter sheaves on $G$.
+  If $s$ is a global section for $\cs{L}$ and $s'$ for $\cs{L}'$ then $s \otimes_{\EE}s'$ is a global section for
+  $\cs{L} \otimes_{\EE}\cs{L}'$.  The three versions of \eqref{t} for $\cs{L}, \cs{L'}$ and $\cs{L} \otimes_{\EE}\cs{L}'$ imply that
+  $\tau_{\cs{L} \otimes_{\EE}\cs{L}'}(\Frob{k}) = \tau_\cs{L}(\Frob{k}) \tau_{\cs{L}'}(\Frob{k})$, so \eqref{pich1} is a group homomorphism.
+
+ Finally, to show that \eqref{pich1} is surjective, pick $[\tau]\in \Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
+ For each $x\in G(\bFq)$, set $\gcs{L}_x = \EE$.
+ Define $\mu_{x,y} : \gcs{L}_{x+y} \to \gcs{L}_x\otimes_{\EE} \gcs{L}_y$ by
+ $\mu_{x,y}(1) = 1\otimes_{\EE}1$, for $x,y\in G(\bFq)$; 
+ clearly, $\mu$ satisfies condition~\ref{cs.1}.
+ Define $\phi_x : \gcs{L}_{\Frob{\Fq}} \to \gcs{L}_x$ by $\phi_x(1) = \tau(\Frob{\Fq})(x)$,
+ for each $x\in G(\bFq)$. 
+ Then $\phi$ satisfies condition~\ref{cs.2} because $\tau \in Z^1(\Weil{\Fq},G(\bFq)^*)$.
+ In this way we have built a quasicharacter sheaf $\cs{L} = (\gcs{L},\mu,\phi)$ 
+ from $\tau \in \Hh^1(\Weil{\Fq}, G(\bFq)^*)$ such that the image of $\cs{L}_{/\text{iso}}$
+ under \eqref{pich1} is the class $[\tau]$ in $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
+ This shows that \eqref{pich1} is surjective, 
+ and completes the proof that it is an isomorphism of groups.
 \end{proof}

### 2013-08-16 shanghai.tex
Improved the proof of the lemma on boxtimes in the section pull-backs and products.

@@
 \[
-\QC(G_1)\times(G_2) \to \QC(G_1\times G_2)
-\]
-and 
+\QC(G_1)\times (G_2) \to \QC(G_1\times G_2)
+\]
+(categorical product on the left, product of group schemes over $\Fq$ on the right) and 
 \[
@@
 The only non-trivial part is essential surjectivity.
-Set $G \ceq G_1\times G_1$.
+Set $G \ceq G_1\times G_2$.
 Let $\cs{L}$ be a quasicharacter sheaf on $G$.
@@
 Observe that $m\circ f = \id_G$.
+Let $p_1$, $p_2$ be the projection morphisms pictured below:
+\[
+\begin{tikzcd}
+G & \arrow[swap]{l}{p_1} G\times G \arrow{r}{p_2} & G\\
+\end{tikzcd}
+\]
 Then the isomorphism $\mu : m^* \gcs{L} \to \gcs{L}\boxtimes \gcs{L}$ gives an isomorphism
@@
 \]
-Observe that $p_1\circ f = r_1 \circ q_1$ and $f_2 = r_2\circ f$ where $p_1 , p_2 : G\times G \to G$ are the usual things and $r_1 : G_1\times G_2 \to G_1$ and $r_2 : G_1\times G_2 \to G_2$ are the obvious things and $q_1 : G_1\to G_1\times G_2$ and  $q_2 : G_2\to G_1\times G_2$ are the usual things.
-Then $f^*p_1^*\gcs{L} = r_1^* q_1^* \gcs{L}$ and $f^*p_2^*\gcs{L} = r_2^* q_2^* \gcs{L}$.
-Now $\cs{L}_1 \ceq r_1^* \cs{L}$ is a quasicharacter sheaf on $G_1$ and $\cs{L}_2 \ceq r_2^* \cs{L}$ is a quasicharacter sheaf on $G_2$, by Proposition~\ref{prop:pullback}.
+Let $r_1$ and $r_2$ be the projection morphisms pictured below, with sections $q_1$, $q_2$, also morphisms of group schemes:
+\[
+\begin{tikzcd}
+G_1  \arrow[swap, bend right]{r}{q_1} & \arrow[swap, bend right]{l}{r_1} G_1\times G_2 \arrow[bend left]{r}{r_2} &  \arrow[bend left]{l}{q_2} G_2.\\
+\end{tikzcd}
+\]
+Then $p_1\circ f = r_1 \circ q_1$ and $f_2 = r_2\circ f$, 
+so $f^*p_1^*\gcs{L} = r_1^* q_1^* \gcs{L}$ and $f^*p_2^*\gcs{L} = r_2^* q_2^* \gcs{L}$. 
+Now $\cs{L}_1 \ceq r_1^* \cs{L}$ is a quasicharacter sheaf on $G_1$ 
+and $\cs{L}_2 \ceq r_2^* \cs{L}$ is a quasicharacter sheaf on $G_2$, 
+by Proposition~\ref{prop:pullback}. 
 Then 
-$ f^*p_1^*\gcs{L}\otimes f^* p_2^*\gcs{L} = r_1^*\gcs{L}_1\otimes r_2^* \gcs{L}_2 = \gcs{L}_1\boxtimes \gcs{L}_2$. In this way, $\mu$ determines an isomorphism
+\[
+f^*p_1^*\gcs{L}\otimes f^* p_2^*\gcs{L} = r_1^*\gcs{L}_1\otimes r_2^* \gcs{L}_2 = \gcs{L}_1\boxtimes \gcs{L}_2.
+\]
+In this way, $\mu$ determines an isomorphism
 \[

### 2013-08-16 shanghai.tex
Add some more references

--- 2013-08-16 shanghai.tex
@@
 
+\hyphenation{quasi-character}
+
 \begin{document}
@@
   fitting into the long exact sequence derived from applying
-  $\Hom(\mbox{---}, A(\bFq))$ to $G^0(\bFq) \to G(\bFq) \to \pi_0(G)(\bFq)$:
+  the functor $\Hom(\mbox{---}, A(\bFq))$ to $G^0(\bFq) \to G(\bFq) \to \pi_0(G)(\bFq)$:
   $$\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)).$$
@@
   define depth has the property that $\TT(A_d) \cong T(K) / T(K)_d$
-  \cite[Prop 5.2]{yu:03a}, so characters of $\GN{T}_d(\Fq)$ 
+  \cite{yu:03a}*{Prop 5.2}, so characters of $\GN{T}_d(\Fq)$ 
   are in bijection with characters of $T(K)$ vanishing on $T(K)_d$. 
@@
  In that case, our suspicions are all but confirmed 
- by the class field theory of Serre-Hasewinkel, \Clifton{Need references for S-H CFT.} especially as revisited in \cite{suzuki-yoshida:12a}. 
+ by the class field theory of Serre-Hazewinkel \citelist{\cite{serre:60a},\cite{serre:61a},\cite{demazure-gabriel:GroupesAlgebriques}*{Appendice}}, especially as revisited in \cite{suzuki-yoshida:12a}.
  What remains to be done is a careful comparison of 

### 2013-08-16 shanghai.tex
Fixing h and h' in Transfer section

@@
 They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the
-Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}; let $h'$ be this quantity for $T'$.
-Then it follows from \cite{chai-yu:01a}*{Thm. 8.5} that if $T$ and $T'$ are $N$-congruent and $h=h'$ and $N > 3h$, 
-\Clifton{Is this correct?}
+Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}.
+Then it follows from \cite{chai-yu:01a}*{Thm. 8.5} that if $N > 3h$ and $T$ and $T'$ are $N$-congruent 
 then there is a canonical isomorphism of smooth group schemes
@@
 \begin{corollary}\label{cor:transfer}
- With notation above, suppose that $T$ and $T'$ are $N$-congruent and $h=h'$ and $N > 3h$.  Set $d = N-3h$.
+ With notation above, suppose that $T$ and $T'$ are $N$-congruent and $N > 3h$.  Set $d = N-3h$.
  Then there is a canonical equivalence of categories

### 2013-08-16 shanghai.tex

--- 2013-08-16 shanghai.tex
@@
 %\begin{proposition}\label{tensor}
-The category $\QC(G)$ of quasicharacter sheaves on $G$ is rigid symmetric monoidal category \cite{etingof:tensorcat} under the tensor product
+The category $\QC(G)$ of quasicharacter sheaves on $G$ is rigid symmetric monoidal category \cite{etingof:09a} under the tensor product
 $\cs{L} \otimes_{\EE}\cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes_{\EE}\phi')$

### 2013-08-16 shanghai.tex
Fixed diagrams in the section on finite quasicharacters.

@@
 the tensor product of the representations $\psi : \ker f\to \Aut(V)$ and $\psi' : \ker f'\to \Aut(V')$ 
-is the representation $\psi \otimes\psi' :  \ker(f\times_G f') \to \Aut(V\otimes V')$. 
+is the representation $\psi \otimes\psi' :  \ker(f\times_G f') \to \Aut(V\otimes_{\EE} V')$. 
 This allows us to set $(f,\psi)\otimes(f',\psi') \ceq (f\times_G f' ,\psi\otimes\psi')$. 
@@
  && && \arrow{ul} \ker f\times_G G' \arrow{ur} \arrow[hook]{rr} && H\times_G G' \arrow{ur} \arrow{rr} && G' \arrow{ur}{g} & \\
-& V' && \Aut(V) && \arrow[swap]{ll}{\psi'} \arrow[swap]{uu}{} \ker f'  \arrow[hook]{rr} && \arrow[swap]{uu} H' \arrow{rr}{f'} && G\\
- && && \arrow{ul} \ker f'\times_G G' \arrow{uu} \arrow{ur} \arrow[hook]{rr} && \arrow{uu} H'\times_G G' \arrow{ur} \arrow{rr} && \arrow[equals]{uu} G' \arrow{ur}{g} & \\
+& V' && \Aut(V) && \arrow[swap,pos=0.7]{ll}{\psi'} \arrow[swap]{uu}{} \ker f'  \arrow[hook]{rr} && \arrow[swap]{uu} H' \arrow[pos=0.8]{rr}{f'} && G\\
+ && && \arrow{ul} \ker f'\times_G G' \arrow{uu} \arrow{ur} \arrow[hook]{rr} && \arrow{uu} H'\times_G G' \arrow{ur} \arrow{rr} && \arrow[equals]{uu} G' \arrow[swap]{ur}{g} & \\
 \end{tikzcd}
@@
 \[
-\begin{tikzcd}
+\begin{tikzcd}[column sep=40]
 V & \Aut(V) & \arrow[swap]{l}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
@@
 \[
-\begin{tikzcd}
-\ &  & \arrow{ld}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-V \arrow{d}{T} & \Aut(V)  & \arrow{l}{\psi_g} \arrow{u} A_m \arrow[hook]{r} & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G\\
-V\otimes V & \Aut(V\otimes V) & \arrow[swap]{l}{\psi\otimes\psi} \arrow[bend left]{uu}{m_H} \arrow[swap]{u}{\theta\vert_{A\times A}} A \times A \arrow[hook]{r}{} & \arrow[bend left]{uu}{m_H} \arrow[swap]{u}{\theta} H \times H \arrow{r}{f\times f} & \arrow[equal]{u} G\times G\\
+\begin{tikzcd}[row sep=20,column sep=10]
+\ & V \arrow{dd}{T} && \Aut(V) && \arrow{dl} \arrow[swap]{ll}{\psi_g} A_m \arrow[hook]{rr} && \arrow[swap]{ld}{m_f} H_m \arrow{rr}{f_m} && \arrow[equal]{dd} \arrow{ld}{m} G\times G\\
+ && && \arrow{ul}{\psi} A  \arrow[hook]{rr} && H  \arrow[swap, pos=0.8]{rr}{f} && G  & \\
+& V\otimes_{\EE} V && \Aut(V) && \arrow[swap]{ll}{\psi \otimes \psi} \arrow[swap,pos=0.8]{uu}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr} && \arrow[swap,pos=0.8]{uu}{\theta} \arrow{ul}{m_H} H\times H \arrow{rr}{f\times f} && G\times G\\
 \end{tikzcd}
@@
   $
-  is surjective because each character $\chi \in G(\Fq)^*$ determines a finite quasicharacter sheaf $(\Lang,\chi)$ such that the trace of Frobenius of the quasicharacter sheaf $B_G^* (L_G(\Lang,\chi^{-1}))$ is $\chi$.
+  is surjective because each character $\chi \in G(\Fq)^*$ determines a finite quasicharacter sheaf $(\Lang,\chi^{-1})$ such that the trace of Frobenius of the quasicharacter sheaf $B_G^* (L_G(\Lang,\chi^{-1}))$ is $\chi$.
 \end{proof}

### 2013-08-16 shanghai.tex
Improvements to the first two sections of Part 2.

@@
 Trace of Frobenius $\QCiso{G} \to G(\Fq)$ is a natural transformation 
-between the following two additive functors from the category of smooth commutative
-group schemes locally of finite type over $\Fq$ to the category of abelian groups:
+between the following two additive functors 
 \begin{enumerate}
-\item[$F_1$:] $G \mapsto \QCiso{G}$;
-\item[$F_2$:] $G \mapsto G(\Fq)$.
+\item[$F_1$:] $G \mapsto \QCiso{G}$
+\item[$F_2$:] $G \mapsto G(\Fq)$
 \end{enumerate}
+from the category of smooth commutative
+group schemes locally of finite type over $\Fq$ to the category of abelian groups.
 \end{proposition}
@@
   First, recall that $L_G(f,\psi) = (L(f,\psi), \mu(f,\psi))$. 
-  By  \cite{laumon:87a}*{1.1.3.3}, $\trFrob{(G_{k'}\hookrightarrow G)^*L(f,\psi)} = \trFrob{\cs{L}} \circ N_{k'/k}$, for each finite extension $k'/k$.
-  On the other hand, $\trFrob{\cs{L}} \circ N_{k'/k} = \trFrob{(G_{k'}\hookrightarrow G)^*\cs{L}}$,  by Proposition~\ref{prop:basechange}.
+  By  \cite{laumon:87a}*{1.1.3.3}, 
+  \[
+  \trFrob{(G_{k'}\hookrightarrow G)^*L(f,\psi)} = \trFrob{\cs{L}} \circ N_{k'/k},
+  \]
+   for each finite extension $k'/k$.
+  On the other hand, 
+  \[
+  \trFrob{\cs{L}} \circ N_{k'/k} = \trFrob{(G_{k'}\hookrightarrow G)^*\cs{L}},
+  \]
+   by Proposition~\ref{prop:basechange}.
   %Using notation from \cite{laumon:87a}*{1.1}, this means $t_{\bullet L(f,\psi)} = t_{\bullet \cs{L}_0}$.
@@
     && \gcs{L}_{x+y}\otimes_{\EE}\gcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
-    \gcs{L}_{x} \otimes_{\EE}\gcs{L}_{y+z} \arrow{rr}{\id \otimes_{\EE}\mu_{y,z}}
+    \gcs{L}_{x} \otimes_{\EE}\gcs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
     && \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes_{\EE}\gcs{L}_{z}
@@
     \gcs{L}_x \rar{\alpha_x} & \gcs{L'}_x
-    & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\alpha_x\otimes_{\EE}\alpha_y} & \gcs{L'}_x \otimes_{\EE}\gcs{L'}_y
+    & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\alpha_x\otimes\alpha_y} & \gcs{L'}_x \otimes_{\EE}\gcs{L'}_y
    \end{tikzcd}
@@
   to the multiplication map $\EE \otimes_{\EE}\EE \to \EE$.
-  The condition $\mu_{0,0}(s(0)) = s(0) \otimes_{\EE}s(0)$ together with the non-triviality of $s$
+  The condition $\mu_{0,0}(s(0)) = s(0) \otimes s(0)$ together with the non-triviality of $s$
   then forces $s(0) = 1$.
@@
 
-A N\'eron model for $T$, denoted here by $\TT$, 
-is a separated, smooth, commutative group scheme locally of finite type over $\OK$ with generic fibre $T$, that enjoys the N\'eron mapping property: \Clifton{Include reference to BLR.}
+A N\'eron model for $T$, denoted here by $\TT$ 
+and whose existence is given by \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch 10.1, Thm 6},
+is a separated, smooth, commutative group scheme locally of finite type over $\OK$ with generic fibre $T$, that enjoys the N\'eron mapping property:
 if $S$ is a smooth scheme over $\OK$ then every morphism $S_\eta \to T$
-over $K$ extends uniquely to a morphism $S \to \TT$. Equivalently, the
+over $K$ extends uniquely to a morphism $S \to \TT$. 
+Equivalently, the
 N\'eron mapping property states that the function
@@
 Let $d$ be a positive integer.
+For every algebraic torus $T$ over $K$, the trace of Frobenius 
+  \[
+\trFrob{T,d}:  \QCiso{\GN{T}_d} \to \Hom_{< d}(T(K),\EEx)
+  \]
+is an isomomorphism. 
+Moreover, the isomorphism $\trFrob{T,d}$ is functorial in the following sense: $T \mapsto \trFrob{T,d}$ is a natural transformation between the following two additive functors
 \begin{enumerate}
-\item 
-For every algebraic torus $T$ over $K$, the trace of Frobenius 
-  \[
-\trFrob{T,d}:  \QCiso{\GN{T}_d} \to \Hom_{< d}(T(K),\EEx)
-  \]
-is an isomomorphism. 
-\item The isomorphism $\trFrob{T,d}$ is functorial in the following sense: $T \mapsto \trFrob{T,d}$ is a natural transformation
-from the additive functor
-\[T \mapsto \QCiso{\GN{T}_d}\]
-to the additive functor
-\[
-T \mapsto \Hom_{<d}(T(K),\EEx).
-\]
+\item[$F_1$:] $T \mapsto \QCiso{\GN{T}_d}$
+\item[$F_2$:] $T \mapsto \Hom_{<d}(T(K),\EEx)$
 \end{enumerate}
+from the additive category of algebraic tori over $K$ to the category of abelian groups.
 \end{theorem}

### 2013-08-16 shanghai.tex
More cosmetic stuff: removed a bunch of // at the end of some tikzcd.
I'm working on Section 14 now.

@@
     \gcs{L} \boxtimes \bm^* \gcs{L} \arrow{rr}{\id \boxtimes \mu}
-    &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL\\
-  \end{tikzcd}
-  \]
-
+    &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL
+  \end{tikzcd}
+  \]
 %
@@
     \bm^*\gcs{L} \arrow{rr}{\mu}
-    && \LxL\\
+    && \LxL
   \end{tikzcd}
@@
 \item[$F_1$:] $G \mapsto \QCiso{G}$
-\item[$F_2$:] $G \mapsto G(\Fq)$
+\item[$F_2$:] $G \mapsto G(\Fq)^*$
 \end{enumerate}
@@
   applying the functor $\pi_0$ to $\bf$; see \cite{vdGeer-Moonen:AbelianVarieties}*{III, 3.28}, for example.
-  \Clifton{I haven't found a better reference for this yet!}
   Write $c_i : \bG^i \hookrightarrow \bG$ for
@@
 \begin{tikzcd}
-G & \arrow[swap]{l}{p_1} G\times G \arrow{r}{p_2} & G\\
+G & \arrow[swap]{l}{p_1} G\times G \arrow{r}{p_2} & G.
 \end{tikzcd}
@@
 \begin{tikzcd}
-G_1  \arrow[swap, bend right]{r}{q_1} & \arrow[swap, bend right]{l}{r_1} G_1\times G_2 \arrow[bend left]{r}{r_2} &  \arrow[bend left]{l}{q_2} G_2.\\
+G_1  \arrow[swap, bend right]{r}{q_1} & \arrow[swap, bend right]{l}{r_1} G_1\times G_2 \arrow[bend left]{r}{r_2} &  \arrow[bend left]{l}{q_2} G_2.
 \end{tikzcd}
@@
 V \arrow{d}{T} & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} & \arrow[equal]{d} G\\
-V' & \Aut(V) & \arrow[swap]{l}{\psi} \arrow[swap]{u}{\alpha\vert_{\ker f}} \ker f \arrow[hook]{r} & \arrow[swap]{u}{\alpha} H' \arrow{r}{f'} & G\\
+V' & \Aut(V) & \arrow[swap]{l}{\psi} \arrow[swap]{u}{\alpha\vert_{\ker f}} \ker f \arrow[hook]{r} & \arrow[swap]{u}{\alpha} H' \arrow{r}{f'} & G
 \end{tikzcd}
@@
 & V' && \Aut(V) && \arrow[swap,pos=0.7]{ll}{\psi'} \arrow[swap]{uu}{} \ker f'  \arrow[hook]{rr} && \arrow[swap]{uu} H' \arrow[pos=0.8]{rr}{f'} && G\\
- && && \arrow{ul} \ker f'\times_G G' \arrow{uu} \arrow{ur} \arrow[hook]{rr} && \arrow{uu} H'\times_G G' \arrow{ur} \arrow{rr} && \arrow[equals]{uu} G' \arrow[swap]{ur}{g} & \\
+ && && \arrow{ul} \ker f'\times_G G' \arrow{uu} \arrow{ur} \arrow[hook]{rr} && \arrow{uu} H'\times_G G' \arrow{ur} \arrow{rr} && \arrow[equals]{uu} G' \arrow[swap]{ur}{g} & 
 \end{tikzcd}
@@
  && && \arrow{ul}{\psi} A  \arrow[hook]{rr} && H  \arrow[swap, pos=0.8]{rr}{f} && G  & \\
-& V\otimes_{\EE} V && \Aut(V) && \arrow[swap]{ll}{\psi \otimes \psi} \arrow[swap,pos=0.8]{uu}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr} && \arrow[swap,pos=0.8]{uu}{\theta} \arrow{ul}{m_H} H\times H \arrow{rr}{f\times f} && G\times G\\
+& V\otimes_{\EE} V && \Aut(V) && \arrow[swap]{ll}{\psi \otimes \psi} \arrow[swap,pos=0.8]{uu}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr} && \arrow[swap,pos=0.8]{uu}{\theta} \arrow{ul}{m_H} H\times H \arrow{rr}{f\times f} && G\times G
 \end{tikzcd}
@@
   $\tau$ and $\tau'$ are defined by the choice of sections $s$ and $s'$ 
-  according to Lemma~\ref{lemma:sec}.
+  according to Lemma~\ref{lemma:section}.
     Now, $\varphi_x(s(x))$ is a
@@
   $X$.  Then
-  \begin{align*}
-%    \Hh^1(\Fq, \Hom(X, \EEx)) &\xrightarrow{\rho} \Hom(\Hh^0(\Fq, X), \EEx) \\
-    \Hh^1(\Fq, X^*) &\xrightarrow{\rho} \Hh^0(\Fq, X)^* \\
-    \rho([z])(x) &= z(\Frob{\Fq})(x)
-  \end{align*}
+\[
+    \Hh^1(\Fq, X^*) \xrightarrow{\rho} \Hh^0(\Fq, X)^*,
+ \qquad \text{defined by}\qquad
+   \rho([z])(x) = z(\Frob{\Fq})(x),
+\]
   is an isomorphism of groups.
@@
 
+\Clifton{I'm working here, now.}
+
 \begin{definition}
@@
 \begin{corollary}\label{cor:application}
+For every algebraic torus $T$ over $K$, the trace of Frobenius 
+  \[
+\trFrob{T}:  \QCiso{\GN{T}} \to \Hom_{<\infty}(T(K),\EEx)
+  \]
+is an isomomorphism. 
+Moreover, the isomorphism $\trFrob{T}$ is functorial in the following sense: 
+$T \mapsto \trFrob{T}$ is a natural transformation 
+between the following two additive functors
 \begin{enumerate}
-\item 
-For every algebraic torus $T$ over $K$, the trace of Frobenius 
-  \[
-\trFrob{T}:  \QCiso{\GN{T}} \to \Hom_{<\infty}(T(K),\EEx)
-  \]
-is an isomomorphism. 
-\item The isomorphism $\trFrob{T}$ is functorial in the following sense: $T \mapsto \trFrob{T}$ is a natural transformation
-from the additive functor
-\[T \mapsto \QCiso{\GN{T}}\]
-to the additive functor
-\[
-T \mapsto \Hom_{<\infty}(T(K),\EEx).
-\]
+\item[$F_1$:] $T \mapsto \QCiso{\GN{T}}$
+\item[$F_2$:] $T \mapsto \Hom_{<\infty}(T(K),\EEx)$
 \end{enumerate}
+from the additive category of algebraic tori over $K$ to the category of abelian groups.
 \end{corollary}
-
-\begin{proof}
-\Clifton{I'll say a few words here about the ind-category $\QC(\GN{T})$.}
-
-\end{proof}
 

### 2013-08-16 shanghai.tex
Working on style in section 1

@@
 
-Let $\Frob{G}$ be the Frobenius automorphism of $\bG$.
-Recall that $\Frob{G} = \id_{G}\times \Frob{\Spec{\bFq}}$ where
-$\Frob{\Spec{\bFq}} = \Spec{\Frob{\Fq}}$ and $\Frob{\Fq}$  is the geometric Frobenius element in $\Gal(\bFq/\Fq)$.
+Let $\Frob{\Fq}$ denote the geometric Frobenius element in $\Gal(\bFq/\Fq)$ as well as the corresponding automorphism of $\Spec{\bFq}$, and let $\Frob{G} := \id_{G} \times \Frob{\Fq}$ be the Frobenius automorphism of $\bG$.
+\David{add definition of Weil groups}
 
@@
   $\cs{L'} = (\gcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$ then
-  $\Hom(\cs{L},\cs{L'})$ is the set of morphisms $\alpha : \gcs{L} \to \gcs{L'}$
+  a morphism $\cs{L} \to \cs{L}'$ is a map $\alpha : \gcs{L} \to \gcs{L'}$
   of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
@@
 As mentioned after \cite{deligne:80a}*{Def.~1.1.10}, a Weil sheaf $(\gcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
-Since we will need this point of view later, we review that interpretation here.
-Setting
-\[
-\varphi(\Frob{\Fq}^n) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi)
-\]
-defines, for every $w\in \Weil{\Fq}$, an isomorphism
-$\varphi(w) : w_G^* \gcs{L}\to \gcs{L}$, such that
-$\varphi(uv) = \varphi(v) \circ v_G^* \varphi(u)$ for all $u,v\in \Weil{\Fq}$.
-Note that $\phi = \varphi(\Frob{\Fq})$. 
+We now review this point of view for later use in Section \ref{sec:basechange}.
+If $w = \Frob{\Fq}^n$ we write $w_G$ for $\Frob{G}^n$.
+For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gcs{L}\to \gcs{L}$ by
+\[
+\varphi(w) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi);
+\]
+these satisfy $\varphi(uv) = \varphi(v) \circ v_G^* \varphi(u)$ for $u,v\in \Weil{\Fq}$, and
+we have $\phi = \varphi(\Frob{\Fq})$. 
 If we further define $\varphi_1(w) \ceq (w_G)_*(\varphi(w)^{-1})$ then
 $\varphi_1(w) : (w_G)_* \gcs{L}\to \gcs{L}$ is an isomorphism and
-$\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for all $u,v\in \Weil{\Fq}$.
-This means the pair $(\gcs{L},\varphi_1)$ is almost an action $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of \cite{deligne:SGA4.5}*{Expos\'e XIII,~1.1}.
-The pair $(\gcs{L},\varphi_1)$ fails to fulfill the requirements of \cite{deligne:SGA4.5}*{Expos\'e XIII,~1.1} only because $\Weil{\Fq}$ is profinite.
-This fact goes to the heart of the notion of a Weil sheaf and is one of the essential aspects of our definition of $\QC(G)$.
+$\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for $u,v\in \Weil{\Fq}$.
+Thus the pair $(\gcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of \cite{deligne:SGA4.5}*{Expos\'e XIII,~1.1}, failing only because $\Weil{\Fq}$ is profinite \David{Do you mean to say that $\Weil{\Fq}$ is not profinite?}.
+This fact \David{Which fact?
+That we can think about quasicharacter sheaves as an action on $\gcs{L}$?
+Or that they fail to fulfill the requirements?} goes to the heart of the notion of a Weil sheaf and is one of the essential aspects of our definition of $\QC(G)$.
 %\end{remark}
@@
 $\cs{L} \otimes_{\EE}\cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes_{\EE}\phi')$
+\David{Why only some $\otimes_{\EE}$?}
 with duals given by applying the functor 
@@
 
-\section{Greenberg of Neron}
+\section{Greenberg of N\'eron}
 \label{sec:GN}
@@
 This paper has shown how quasicharacter sheaves 
-on the Greenberg transform of the Neron model of $T$ 
+on the Greenberg transform of the N\/eron model of $T$ 
 determine admissible characters of $T(K)$, and vice versa, functorially. When coupled with the reciprocity map $\text{rec}_T $ for $T$, 

### 2013-08-16 shanghai.tex
Small improvements to Part 2.

--- 2013-08-16 shanghai.tex
@@
 We would like to thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
-for allowing us to hijack our Research in Teams meeting at BIRS into a discussion of
+for allowing us to hijack much of our Research in Teams meeting at BIRS into a discussion of
 quasicharacter sheaves.  Their knowledge and help have been invaluable.
@@
 
+Recall that $\Fq$ is a finite field.
 Let $K$ be a non-archimedean local field with residue field $\Fq$.
@@
 
-\section{The geometrization of characters of tori over local fields} \label{sec:quasichar}
+\section{A sheaf-function dictionary for tori over local fields} \label{sec:quasichar}
 
 \Clifton{I'm working here, now.}
+If $d\leq d'$, then $\pK^{d'} \hookrightarrow \pK^d$ so there is a canonical surjective ring homomorphism $A_{d'} \to A_{d}$. Set $S = \Spec{\OK}$ and $S_d = \Spec{A_d}$. 
+\[
+\begin{tikzcd}
+S_1 \arrow[hook]{r} 
+& S_2 \arrow[hook]{r} \cdots 
+& S_d \arrow[hook]{r}  
+& S_{d'} \arrow[hook]{r} \cdots 
+& S
+\end{tikzcd}
+\]
+
+ then $\GN{T}_d$ is a closed subgroup of $\GN{T}_{d'}$,
+so these smooth commutative group schemes form a directed system.
+\[
+\begin{tikzcd}
+\GN{T}_1 
+& \arrow[two heads]{l} \GN{T}_2 
+& \arrow[two heads]{l} \cdots 
+& \arrow[two heads]{l} \GN{T}_d 
+& \arrow[two heads]{l} \GN{T}_{d'} 
+& \arrow[two heads]{l} \cdots
+\end{tikzcd}
+\]
 
@@
 \end{equation}
-Let$\QC(\GN{T})$ be the ind-category $\varinjlim_{d\in \ZZ_{>0}} \QC(\GN{T}_d)$;
-we refer to objects of $\QC(\GN{T})$ as \emph{quasicharacter sheaves for $T$}.
 \end{definition}
@@
 \end{remark}
+
+\begin{definition}
+Let$\QC(\GN{T})$ be the ind-category $\varinjlim_{d\in \ZZ_{>0}} \QC(\GN{T}_d)$;
+we refer to objects of $\QC(\GN{T})$ as \emph{quasicharacter sheaves for $T$}.
+\end{definition}
 

### 2013-08-16 shanghai.tex
cs |--> qcs

@@
 \newcommand{\colimit}[1]{\mathop{\textsc{colim}}\limits_{#1}}
-\newcommand{\cs}[1]{{\mathcal{#1}}}
-\newcommand{\gcs}[1]{{\mathcal{\bar #1}}}
-\newcommand{\dualgcs}[1]{\gcs{#1}^\dagger}
-\newcommand{\dualcs}[1]{\cs{#1}^\dagger}
+\newcommand{\qcs}[1]{{\mathcal{#1}}}
+\newcommand{\gqcs}[1]{{\mathcal{\bar #1}}}
+\newcommand{\dualgcs}[1]{\gqcs{#1}^\dagger}
+\newcommand{\dualcs}[1]{\qcs{#1}^\dagger}
 \newcommand{\QC}{{\mathcal{Q\hskip-0.8pt C}}}
@@
 \newcommand{\GxxG}{\text{$G \tight{1}{\times}{1} G$}}
-\newcommand{\LxL}{\text{$\gcs{L} \tight{0}{\boxtimes}{0} \gcs{L}$}}
-\newcommand{\ExE}{\text{$\cs{E}\tight{0}{\boxtimes}{0}\cs{E}$}}
-\newcommand{\bExE}{\text{$\gcs{E}\tight{0}{\boxtimes}{0}\gcs{E}$}}
+\newcommand{\LxL}{\text{$\gqcs{L} \tight{0}{\boxtimes}{0} \gqcs{L}$}}
+\newcommand{\ExE}{\text{$\qcs{E}\tight{0}{\boxtimes}{0}\qcs{E}$}}
+\newcommand{\bExE}{\text{$\gqcs{E}\tight{0}{\boxtimes}{0}\gqcs{E}$}}
 \newcommand{\AxA}{\text{$A \tight{1}{\times}{1} A$}}
@@
 $\Frob{G} : \bG \to \bG$ for the Frobenius automorphism.
-A quasicharacter sheaf on $G$ is a triple $\cs{L}\ceq
-(\gcs{L},\mu,\phi)$ where $\gcs{L}$ is an $\ell$-adic local system on $\bG$ of rank-1 and $\mu: m^*
-\gcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gcs{L} \to \gcs{L}$ are isomorphisms;
+A quasicharacter sheaf on $G$ is a triple $\qcs{L}\ceq
+(\gqcs{L},\mu,\phi)$ where $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ of rank-1 and $\mu: m^*
+\gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms;
 $\mu$ and $\phi$ are required to satisfy natural conditions explained below.
@@
 A \emph{quasicharacter sheaf on $G$} is a triple
-$\cs{L}\ceq (\gcs{L},\mu,\phi)$ where:
+$\qcs{L}\ceq (\gqcs{L},\mu,\phi)$ where:
 \begin{enumerate}
-\labitem{(CS.0)}{CS.0} $\gcs{L}$ is an $\ell$-adic local system on $\bG$ (a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component) of rank-1; 
-\labitem{(CS.1)}{CS.1} $\mu: \bm^* \gcs{L} \to \LxL$
+\labitem{(CS.0)}{CS.0} $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ (a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component) of rank-1; 
+\labitem{(CS.1)}{CS.1} $\mu: \bm^* \gqcs{L} \to \LxL$
   is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
@@
   \begin{tikzcd}[row sep=30]
-  \bm_3^*\gcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
-    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
-    \gcs{L} \boxtimes \bm^* \gcs{L} \arrow{rr}{\id \boxtimes \mu}
-    &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL
+  \bm_3^*\gqcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
+    &&  \bm^*\gqcs{L} \boxtimes \gqcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
+    \gqcs{L} \boxtimes \bm^* \gqcs{L} \arrow{rr}{\id \boxtimes \mu}
+    &&  \gqcs{L} \tight{0}{\boxtimes}{0} \LxL
   \end{tikzcd}
@@
 %
-\labitem{(CS.2)}{CS.2} $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an
+\labitem{(CS.2)}{CS.2} $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$ is an
   isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with $\mu$ in the sense that the following diagram commutes.
@@
   \begin{tikzcd}[row sep=20]
-  \Frob{\GxxG}^* \bm^* \gcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
+  \Frob{\GxxG}^* \bm^* \gqcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
     && \Frob{\GxxG}^*(\LxL)\\
-    \arrow[equal]{u} \bm^*  \Frob{G}^* \gcs{L} \arrow[swap]{d}{\bm^* \phi}
-    && \Frob{G}^*\gcs{L}\boxtimes \Frob{G}^*\gcs{L} \dar{F\boxtimes \phi} \arrow[equal]{u} \\
-    \bm^*\gcs{L} \arrow{rr}{\mu}
+    \arrow[equal]{u} \bm^*  \Frob{G}^* \gqcs{L} \arrow[swap]{d}{\bm^* \phi}
+    && \Frob{G}^*\gqcs{L}\boxtimes \Frob{G}^*\gqcs{L} \dar{F\boxtimes \phi} \arrow[equal]{u} \\
+    \bm^*\gqcs{L} \arrow{rr}{\mu}
     && \LxL
@@
 \end{enumerate}
-%In short, a quasicharacter sheaf on $G$  is a rank-1 Weil local system $(\gcs{L},\phi)$ on $G$ equipped with an isomorphism $m^* (\gcs{L},\phi) \to (\gcs{L},\phi)\boxtimes (\gcs{L},\phi)$. 
+%In short, a quasicharacter sheaf on $G$  is a rank-1 Weil local system $(\gqcs{L},\phi)$ on $G$ equipped with an isomorphism $m^* (\gqcs{L},\phi) \to (\gqcs{L},\phi)\boxtimes (\gqcs{L},\phi)$. 
 \end{definition}
@@
 \begin{enumerate}
-\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,\phi)$ and
-  $\cs{L'} = (\gcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$ then
-  a morphism $\cs{L} \to \cs{L}'$ is a map $\alpha : \gcs{L} \to \gcs{L'}$
+\labitem{(CS.3)}{CS.3} if $\qcs{L} = (\gqcs{L},\mu,\phi)$ and
+  $\qcs{L'} = (\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$ then
+  a morphism $\qcs{L} \to \qcs{L}'$ is a map $\alpha : \gqcs{L} \to \gqcs{L'}$
   of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
@@
   \begin{tikzcd}[column sep=40]
-  \Frob{G}^* \gcs{L} \rar{\Frob{G}^* \alpha} \arrow[swap]{d}{\phi} & \Frob{G}^* \gcs{L'} \dar{\phi'}
+  \Frob{G}^* \gqcs{L} \rar{\Frob{G}^* \alpha} \arrow[swap]{d}{\phi} & \Frob{G}^* \gqcs{L'} \dar{\phi'}
   & %\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} 
-  & \arrow[swap]{d}{\mu} m^* \gcs{L} \rar{m^* \alpha} & m^* \gcs{L'} \dar{\mu'} \\
-  \gcs{L} \rar{\alpha} & \gcs{L'}
-  & {} & \LxL \rar{\tight{1}{\alpha\boxtimes \alpha}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
+  & \arrow[swap]{d}{\mu} m^* \gqcs{L} \rar{m^* \alpha} & m^* \gqcs{L'} \dar{\mu'} \\
+  \gqcs{L} \rar{\alpha} & \gqcs{L'}
+  & {} & \LxL \rar{\tight{1}{\alpha\boxtimes \alpha}{1}} & \gqcs{L'} \tight{0}{\boxtimes}{0} \gqcs{L'}
   \end{tikzcd}
@@
 %\begin{remark} \label{rem:CS-action}
-The rule $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$ defines a forgetful functor from quasicharacter sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
-
-As mentioned after \cite{deligne:80a}*{Def.~1.1.10}, a Weil sheaf $(\gcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
+The rule $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ defines a forgetful functor from quasicharacter sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
+
+As mentioned after \cite{deligne:80a}*{Def.~1.1.10}, a Weil sheaf $(\gqcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gqcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{\Fq}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
 We now review this point of view for later use in Section \ref{sec:basechange}.
 If $w = \Frob{\Fq}^n$ we write $w_G$ for $\Frob{G}^n$.
-For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gcs{L}\to \gcs{L}$ by
+For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gqcs{L}\to \gqcs{L}$ by
 \[
@@
 If we further define $\varphi_1(w) \ceq (w_G)_*(\varphi(w)^{-1})$ then
-$\varphi_1(w) : (w_G)_* \gcs{L}\to \gcs{L}$ is an isomorphism and
+$\varphi_1(w) : (w_G)_* \gqcs{L}\to \gqcs{L}$ is an isomorphism and
 $\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for $u,v\in \Weil{\Fq}$.
-Thus the pair $(\gcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{\Fq}$ on $\gcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of \cite{deligne:SGA4.5}*{Expos\'e XIII,~1.1}, failing only because $\Weil{\Fq}$ is profinite \David{Do you mean to say that $\Weil{\Fq}$ is not profinite?}.
+Thus the pair $(\gqcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{\Fq}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of \cite{deligne:SGA4.5}*{Expos\'e XIII,~1.1}, failing only because $\Weil{\Fq}$ is profinite \David{Do you mean to say that $\Weil{\Fq}$ is not profinite?}.
 This fact \David{Which fact?
-That we can think about quasicharacter sheaves as an action on $\gcs{L}$?
+That we can think about quasicharacter sheaves as an action on $\gqcs{L}$?
 Or that they fail to fulfill the requirements?} goes to the heart of the notion of a Weil sheaf and is one of the essential aspects of our definition of $\QC(G)$.
@@
 The category $\QC(G)$ of quasicharacter sheaves on $G$ is rigid symmetric monoidal category \cite{etingof:09a} under the tensor product
-$\cs{L} \otimes_{\EE}\cs{L'} \ceq (\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes_{\EE}\phi')$
+$\qcs{L} \otimes_{\EE}\qcs{L'} \ceq (\gqcs{L}\otimes\gqcs{L'}, \mu\otimes\mu', \phi\otimes_{\EE}\phi')$
 \David{Why only some $\otimes_{\EE}$?}
@@
 \begin{definition}\label{def:trFrob}
-Let $(\gcs{L},\phi)$ be a Weil sheaf on $G$. on constructible $\ell$-adic sheaf on $\bG$. Every $g\in G(\Fq)$
+Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. on constructible $\ell$-adic sheaf on $\bG$. Every $g\in G(\Fq)$
 determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$ and
-therefore an automorphism $\phi_{\bg}$ of $\gcs{L}_{\bg}$. The \emph{trace of Frobenius} of $(\gcs{L},\phi)$ at $g\in G(\Fq)$ is 
-\[
-\trFrob{(\gcs{L},\phi)}(g) \ceq \trace(\phi_{\bg}, \gcs{L}_{\bg}).
-\]
-If $\cs{L} = (\gcs{L},\mu,\phi)$ is a quasicharacter sheaf, 
-then we will abbreviate $\trFrob{(\gcs{L},\phi)}$ to $\trFrob{\cs{L}}$.
+therefore an automorphism $\phi_{\bg}$ of $\gqcs{L}_{\bg}$. The \emph{trace of Frobenius} of $(\gqcs{L},\phi)$ at $g\in G(\Fq)$ is 
+\[
+\trFrob{(\gqcs{L},\phi)}(g) \ceq \trace(\phi_{\bg}, \gqcs{L}_{\bg}).
+\]
+If $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf, 
+then we will abbreviate $\trFrob{(\gqcs{L},\phi)}$ to $\trFrob{\qcs{L}}$.
 \end{definition}
 
-The isomorphism $\mu : \bm^* \gcs{L} \to \LxL$ guarantees 
-that the function $\trFrob{\cs{L}} : G(\Fq)\to \EEx$ is a group homomorphism.
-It is also clear that $\trFrob{\cs{L}\otimes \cs{L'}} = \trFrob{\cs{L}} \cdot \trFrob{\cs{L'}}$
-(pointwise multiplication of functions) and $\trFrob{\cs{L}} = \trFrob{\cs{L'}}$
-if $\cs{L} \iso \cs{L'}$ in $\QC(G)$. In this way we obtain a group homomorphism
+The isomorphism $\mu : \bm^* \gqcs{L} \to \LxL$ guarantees 
+that the function $\trFrob{\qcs{L}} : G(\Fq)\to \EEx$ is a group homomorphism.
+It is also clear that $\trFrob{\qcs{L}\otimes \qcs{L'}} = \trFrob{\qcs{L}} \cdot \trFrob{\qcs{L'}}$
+(pointwise multiplication of functions) and $\trFrob{\qcs{L}} = \trFrob{\qcs{L'}}$
+if $\qcs{L} \iso \qcs{L'}$ in $\QC(G)$. In this way we obtain a group homomorphism
 \[
 \cdef{\trFrob{G}} : \QCiso{G} \longrightarrow G(\Fq)^*,
-\qquad \text{defined by}\qquad \cs{L} \mapsto \trFrob{\cs{L}}.
+\qquad \text{defined by}\qquad \qcs{L} \mapsto \trFrob{\qcs{L}}.
 \]
@@
   If $f : H\to G$ is a morphism of commutative group schemes locally of finite type over $\Fq$ then
-  $(\gcs{L},\mu,\phi) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
+  $(\gqcs{L},\mu,\phi) \mapsto (\bf^*\gqcs{L},(\bfxf)^*\mu,\bf^*F)$
   defines a monoidal functor $f^* : \QC(G) \to \QC(H)$ such that
@@
 \begin{proof}
-  Let $\cs{L}$ be a quasicharacter sheaf on $G$. We start by showing that
-  $\bf^*\gcs{L}$ is locally constant on connected components of
+  Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We start by showing that
+  $\bf^*\gqcs{L}$ is locally constant on connected components of
   $\bH$. Let $c_j :\bH^j \hookrightarrow \bH$ be any
@@
   the inclusion of $\bG^i$ and $\bf^j : \bH^j \to \bG^i$
-  for the restriction of $f$ to $\bH^j$.  Since $\cs{L}$
-  is a quasicharacter sheaf, $\gcs{L}$ is locally constant on the connect
+  for the restriction of $f$ to $\bH^j$.  Since $\qcs{L}$
+  is a quasicharacter sheaf, $\gqcs{L}$ is locally constant on the connect
   components of $\bG$; thus, there is a finite etale covering
-  $a_i : X_i \to \bG^i$ such that $a_i^* (\gcs{L}\vert_{\bG^i})$
+  $a_i : X_i \to \bG^i$ such that $a_i^* (\gqcs{L}\vert_{\bG^i})$
   is constant. Let $b_j : Y_j \to \bH^j$ be the
@@
   \[
-  b_j^* \left( (\bf^* \gcs{L})\vert_{\bH^j}\right)
-  = (\bf\circ c_j \circ b_j)^*\gcs{L}
-  = (c_i\circ a_i\circ g_j)^*\gcs{L} = g_j^* a_i^* (\gcs{L}\vert_{\bG^i}).
-  \]
-
-  Since $a_i^* (\gcs{L}\vert_{\bG^i})$ is a constant sheaf and since the pull-back
+  b_j^* \left( (\bf^* \gqcs{L})\vert_{\bH^j}\right)
+  = (\bf\circ c_j \circ b_j)^*\gqcs{L}
+  = (c_i\circ a_i\circ g_j)^*\gqcs{L} = g_j^* a_i^* (\gqcs{L}\vert_{\bG^i}).
+  \]
+
+  Since $a_i^* (\gqcs{L}\vert_{\bG^i})$ is a constant sheaf and since the pull-back
   of a constant sheaf (along $g_j$, in this case) is a constant sheaf,
-  it follows that $b_j^* \left( (\bf^*\gcs{L})\vert_{\bH^j}\right)$
-  is a constant sheaf. Thus, $\bf^*\gcs{L}$ is locally constant on
-  $\bH^j$. Since $(\bf^*\gcs{L})_{\bg} = \gcs{L}_{f(\bg)}$ for every
-  geometric point ${\bg}$ on $\bG$, and since $\gcs{L}$ has
+  it follows that $b_j^* \left( (\bf^*\gqcs{L})\vert_{\bH^j}\right)$
+  is a constant sheaf. Thus, $\bf^*\gqcs{L}$ is locally constant on
+  $\bH^j$. Since $(\bf^*\gqcs{L})_{\bg} = \gqcs{L}_{f(\bg)}$ for every
+  geometric point ${\bg}$ on $\bG$, and since $\gqcs{L}$ has
   rank $1$ on connected components of $\bG$, it follows that
-  $f^*\gcs{L}$ also has rank $1$ on connected components of $\bG$.
-  This completes the proof that $\bf^*\gcs{L}$ satisfies condition \ref{CS.0}.
-
-  To see that $(\bfxf)^* \gcs{L}$ satisfies
+  $f^*\gqcs{L}$ also has rank $1$ on connected components of $\bG$.
+  This completes the proof that $\bf^*\gqcs{L}$ satisfies condition \ref{CS.0}.
+
+  To see that $(\bfxf)^* \gqcs{L}$ satisfies
   condition \ref{CS.1} simply apply the functor $(\bfxf)^*$
-  to \ref{CS.1} for $\cs{L}$ and use the canonical isomorphism
-  $(\bfxf)^*(\LxL) \iso \bf^*\gcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gcs{L}$
-  (a few times). Likewise, to see that $\bf^*\gcs{L}$ satisfies condition
-  \ref{CS.2}, apply the same functor to \ref{CS.2} for $\gcs{L}$.
+  to \ref{CS.1} for $\qcs{L}$ and use the canonical isomorphism
+  $(\bfxf)^*(\LxL) \iso \bf^*\gqcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gqcs{L}$
+  (a few times). Likewise, to see that $\bf^*\gqcs{L}$ satisfies condition
+  \ref{CS.2}, apply the same functor to \ref{CS.2} for $\gqcs{L}$.
   Then use the fact that $f$ is defined over $\Fq$, so
@@
 
-  To see that $(\gcs{L},\mu,\phi) \mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)$
+  To see that $(\gqcs{L},\mu,\phi) \mapsto (\bf^*\gqcs{L},(\bfxf)^*\mu,\bf^*F)$
   defines a functor $f^* : \QC(G) \to \QC(H)$ one applies the functors $\bf^*$ and
@@
 \begin{proposition}\label{prop:product}
-The rule $\boxtimes : (\cs{L}_1,\cs{L}_2)\to \cs{L}_1\boxtimes\cs{L}_2$ defines an equivalence of categories 
+The rule $\boxtimes : (\qcs{L}_1,\qcs{L}_2)\to \qcs{L}_1\boxtimes\qcs{L}_2$ defines an equivalence of categories 
 \[
@@
 Set $G \ceq G_1\times G_2$.
-Let $\cs{L}$ be a quasicharacter sheaf on $G$.
+Let $\qcs{L}$ be a quasicharacter sheaf on $G$.
 Define $f : G\to G\times G$ by $f(g_1,g_2) = (g_1,e_2,e_1,g_2)$.
@@
 \]
-Then the isomorphism $\mu : m^* \gcs{L} \to \gcs{L}\boxtimes \gcs{L}$ gives an isomorphism
-\[
-f^*\mu : f^* m^* \gcs{L} \to f^*(\gcs{L}\boxtimes \gcs{L}) = f^*p_1^*\gcs{L}\otimes f^* p_2^*\gcs{L}.
+Then the isomorphism $\mu : m^* \gqcs{L} \to \gqcs{L}\boxtimes \gqcs{L}$ gives an isomorphism
+\[
+f^*\mu : f^* m^* \gqcs{L} \to f^*(\gqcs{L}\boxtimes \gqcs{L}) = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L}.
 \]
@@
 Then $p_1\circ f = r_1 \circ q_1$ and $f_2 = r_2\circ f$, 
-so $f^*p_1^*\gcs{L} = r_1^* q_1^* \gcs{L}$ and $f^*p_2^*\gcs{L} = r_2^* q_2^* \gcs{L}$. 
-Now $\cs{L}_1 \ceq r_1^* \cs{L}$ is a quasicharacter sheaf on $G_1$ 
-and $\cs{L}_2 \ceq r_2^* \cs{L}$ is a quasicharacter sheaf on $G_2$, 
+so $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L}$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L}$. 
+Now $\qcs{L}_1 \ceq r_1^* \qcs{L}$ is a quasicharacter sheaf on $G_1$ 
+and $\qcs{L}_2 \ceq r_2^* \qcs{L}$ is a quasicharacter sheaf on $G_2$, 
 by Proposition~\ref{prop:pullback}. 
@@
 \[
-f^*p_1^*\gcs{L}\otimes f^* p_2^*\gcs{L} = r_1^*\gcs{L}_1\otimes r_2^* \gcs{L}_2 = \gcs{L}_1\boxtimes \gcs{L}_2.
+f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L} = r_1^*\gqcs{L}_1\otimes r_2^* \gqcs{L}_2 = \gqcs{L}_1\boxtimes \gqcs{L}_2.
 \]
@@
 \[
-f^*\mu : \gcs{L} \to  \gcs{L}_1\boxtimes \gcs{L}_2.
+f^*\mu : \gqcs{L} \to  \gqcs{L}_1\boxtimes \gqcs{L}_2.
 \]
@@
 
-If $\cs{L} = (\gcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$ we may define
-a quasicharacter sheaf $\cs{L}' = (\gcs{L}, \mu, \phi_{k'})$ on 
+If $\qcs{L} = (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$ we may define
+a quasicharacter sheaf $\qcs{L}' = (\gqcs{L}, \mu, \phi_{k'})$ on 
 $G_{k'}\ceq G\times_{\Spec{k}} \Spec{k'}$ by setting
@@
 Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
-as taking the action $\varphi$ of $\Weil{k}$ on $\gcs{L}$ 
+as taking the action $\varphi$ of $\Weil{k}$ on $\gqcs{L}$ 
 defined in Section~\ref{sec:category} and restricting it to the subgroup $\Weil{k'}$.
@@
 \begin{proposition}\label{prop:basechange}
- The rule $\nu_{k'/k}: (\gcs{L}, \mu, \varphi) \mapsto (\gcs{L}, \mu, \varphi\vert_{\Weil{\Fq}})$ 
+ The rule $\nu_{k'/k}: (\gqcs{L}, \mu, \varphi) \mapsto (\gqcs{L}, \mu, \varphi\vert_{\Weil{\Fq}})$ 
  defines a monoidal functor $\QC(G) \to \QC(G_{k'})$. 
@@
 \begin{definition}
-Let $\QCb(G)$ be the category of pairs $(\cs{L}_0,\mu_0)$ 
-where $\cs{L}_0$ an $\ell$-adic local system on $G$ of rank-1, 
-equipped with an isomorphism $\mu_0 : m^* \cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ 
+Let $\QCb(G)$ be the category of pairs $(\qcs{L}_0,\mu_0)$ 
+where $\qcs{L}_0$ an $\ell$-adic local system on $G$ of rank-1, 
+equipped with an isomorphism $\mu_0 : m^* \qcs{L}_0 \to \qcs{L}_0 \boxtimes \qcs{L}_0$ 
 satisfying the analogue of Condition~\ref{CS.1} on $G$; 
@@
 The category of bounded quasicharacter sheaves is a rigid monoidal category in the obvious way. 
-%with duals given by $\cs{L}_0^\vee \ceq \sheafHom(\cs{L}_0,\EE)$.
+%with duals given by $\qcs{L}_0^\vee \ceq \sheafHom(\qcs{L}_0,\EE)$.
 
@@
  Let $b_G : {\bar G} \to G$ be the pull-back of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Let $(\cs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$. 
- Then $\cs{L}_0$ is, in particular, an $\ell$-adic constructible sheaf on $G$. 
- Then $b_G^* \cs{L}_0$ comes equipped with an isomorphism 
- $\phi : \Frob{G}^* b_G^*\cs{L}_0 \to b_G^* \cs{L}_0$; 
- moreover, the functor $\cs{L}_0 \mapsto (b_G^* \cs{L}_0,\phi)$  
+ Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$. 
+ Then $\qcs{L}_0$ is, in particular, an $\ell$-adic constructible sheaf on $G$. 
+ Then $b_G^* \qcs{L}_0$ comes equipped with an isomorphism 
+ $\phi : \Frob{G}^* b_G^*\qcs{L}_0 \to b_G^* \qcs{L}_0$; 
+ moreover, the functor $\qcs{L}_0 \mapsto (b_G^* \qcs{L}_0,\phi)$  
  from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
@@
  Set $\mu = b_{G\times G}^*\mu_0$; clearly, this satisfies Condition~\ref{CS.2} 
- with $b_G^*\cs{L}_0$ playing the role of $\gcs{L}$.
+ with $b_G^*\qcs{L}_0$ playing the role of $\gqcs{L}$.
  Moreover, $\phi$ is compatible with $\mu$ in the sense of Condition~\ref{CS.3}.
- It follows that functor $(\cs{L}_0,\mu_0) \mapsto (b_G^*\cs{L}_0,b_{G\times G}^* \mu_0, \phi)$, denoted by  $B_G^*: \QCb(G) \hookrightarrow \QC(G)$ below, is full and faithful.
+ It follows that functor $(\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,b_{G\times G}^* \mu_0, \phi)$, denoted by  $B_G^*: \QCb(G) \hookrightarrow \QC(G)$ below, is full and faithful.
 \end{proof}
@@
  %Let $G$ be a geometrically connected algebraic group over $\Fq$.
-  Observe that the forgetful functor $(\gcs{L},\mu,\phi) \mapsto (\gcs{L},\phi)$
+  Observe that the forgetful functor $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$
   sends quasicharacter sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{deligne:80a}*{1.1.10}.
@@
   $\ell$-adic representations of $\W(G,\bg)$ \cite{deligne:80a}*{1.1.12}. 
-  Now let $(\gcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$ 
-  and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gcs{L},\phi)$. 
+  Now let $(\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$ 
+  and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$. 
   The $\Fq$-rational point $g$ under the geometric point $\bg$ determines a splitting
   $\Weil{\Fq}\to \W(G,\bg)$ of $\W(G,\bg)\to \Weil{\Fq}$. 
-  In this way the Weil local system $(\gcs{L},F)$ determines an $\ell$-adic character $\rho_g : \Weil{\Fq} \to \EEx$.
+  In this way the Weil local system $(\gqcs{L},F)$ determines an $\ell$-adic character $\rho_g : \Weil{\Fq} \to \EEx$.
   %\[
@@
   %\]
-  This character is given by the trace of Frobenius of $\cs{L}$ at $g$, as defined in Section~\ref{sec:Frob}:
-  \[
-  \rho_g(\Frob{\Fq}) =  \trFrob{\cs{L}}(g).
-  \]
-
-  On the other hand, we have already seen that $\trFrob{\cs{L}} : G(\Fq) \to \EEx$
+  This character is given by the trace of Frobenius of $\qcs{L}$ at $g$, as defined in Section~\ref{sec:Frob}:
+  \[
+  \rho_g(\Frob{\Fq}) =  \trFrob{\qcs{L}}(g).
+  \]
+
+  On the other hand, we have already seen that $\trFrob{\qcs{L}} : G(\Fq) \to \EEx$
   is a group homomorphism. Since $G$ is an algebraic group over $\Fq$, it is a
   variety over $\Fq$, so finitely generated over $\Fq$, so $G(\Fq)$ is finite;
-  it follows that $\trFrob{\cs{L}}(g) = \rho_g(\Frob{\Fq})$ is a root of unity,
+  it follows that $\trFrob{\qcs{L}}(g) = \rho_g(\Frob{\Fq})$ is a root of unity,
   for every $g\in G(\Fq)$.  Since $\Weil{\Fq}$ is generated by
@@
   representations of $\pi_1(G,\bg)$ and $\ell$-adic local systems on $G$. Let
-  $\cs{L}_0$ be a local system on $G$ in the isomorphism class
+  $\qcs{L}_0$ be a local system on $G$ in the isomorphism class
   determined by this $\ell$-adic character of $\pi_1(G,\bg)$.
-  Then $b_G^*\cs{L}_0 \iso \gcs{L}$.
+  Then $b_G^*\qcs{L}_0 \iso \gqcs{L}$.
   Since $b_G^*$ is full and faithful (again, see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} or even \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}),
   $
-  b_{G\times G}^* : \Hom(m^*\cs{L}_0,\cs{L}_0\boxtimes\cs{L}_0) \to \Hom({\bar m}^*\gcs{L},\gcs{L}\boxtimes\gcs{L})
+  b_{G\times G}^* : \Hom(m^*\qcs{L}_0,\qcs{L}_0\boxtimes\qcs{L}_0) \to \Hom({\bar m}^*\gqcs{L},\gqcs{L}\boxtimes\gqcs{L})
   $ 
@@
   in which $\ell$-adic local systems sit as full subcategories). 
-  Let $\mu_0 : m^*\cs{L}_0 \to \cs{L}_0\boxtimes\cs{L}_0$ be the isomorphism matching 
-  $\mu : {\bar m}^*\gcs{L} \to \gcs{L}\boxtimes\gcs{L}$, 
-  the latter appearing in the definition of $\cs{L}$. 
-  Then, as in Section~\ref{sec:bounded}, $(\cs{L}_0,\mu_0)$ is an object in $\QCb(G)$ 
-  and $\cs{L} = (\gcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\cs{L}_0,b_{G\times G}^*\mu_0)$ in $\QC(G)$.
+  Let $\mu_0 : m^*\qcs{L}_0 \to \qcs{L}_0\boxtimes\qcs{L}_0$ be the isomorphism matching 
+  $\mu : {\bar m}^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$, 
+  the latter appearing in the definition of $\qcs{L}$. 
+  Then, as in Section~\ref{sec:bounded}, $(\qcs{L}_0,\mu_0)$ is an object in $\QCb(G)$ 
+  and $\qcs{L} = (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{L}_0,b_{G\times G}^*\mu_0)$ in $\QC(G)$.
   Thus, the full and faithful functor $B_G^* : \QCb(G) \to \QC(G)$ from Section~\ref{sec:bounded}
@@
 
-  Let $(\cs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$. 
-  Then $\cs{L}\ceq B_G^*(\cs{L}_0,\mu_0)$ is a quasicharacter sheaf on $G$.
-  Recall the definition of the character $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}. 
+  Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$. 
+  Then $\qcs{L}\ceq B_G^*(\qcs{L}_0,\mu_0)$ is a quasicharacter sheaf on $G$.
+  Recall the definition of the character $\trFrob{\qcs{L}} : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}. 
   Let $f : G\to G$ be the Lang isogeny.
@@
   Let $V = \EE$ and let $\psi : \ker f \to \Aut(V)$ be the representation given by 
-  $\psi(g)(v) = \trFrob{\cs{L}}(g) v$ for $v\in V$. 
+  $\psi(g)(v) = \trFrob{\qcs{L}}(g) v$ for $v\in V$. 
   Then $(f,\psi)$ is a finite quasicharacter sheaf.
 
-  To show that $L_G(f,\psi) \iso (\cs{L}_0,\mu_0)$ we simply apply the functions--sheaves dictionary
+  To show that $L_G(f,\psi) \iso (\qcs{L}_0,\mu_0)$ we simply apply the functions--sheaves dictionary
   as follows ({\it cf} \cite{laumon:87a}*{1.1.3} or, ultimately, \cite{deligne:SGA4.5}*{Sommes trigonométriques}).
@@
   \[
-  \trFrob{(G_{k'}\hookrightarrow G)^*L(f,\psi)} = \trFrob{\cs{L}} \circ N_{k'/k},
+  \trFrob{(G_{k'}\hookrightarrow G)^*L(f,\psi)} = \trFrob{\qcs{L}} \circ N_{k'/k},
   \]
@@
   \[
-  \trFrob{\cs{L}} \circ N_{k'/k} = \trFrob{(G_{k'}\hookrightarrow G)^*\cs{L}},
+  \trFrob{\qcs{L}} \circ N_{k'/k} = \trFrob{(G_{k'}\hookrightarrow G)^*\qcs{L}},
   \]
    by Proposition~\ref{prop:basechange}.
-  %Using notation from \cite{laumon:87a}*{1.1}, this means $t_{\bullet L(f,\psi)} = t_{\bullet \cs{L}_0}$.
-  Using \cite{laumon:87a}*{Th\'eor\`eme~1.1.2}, it follows that  $L(f,\psi) \iso \cs{L}_0$ in $\Loc(G)$.
-  It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\cs{L}_0,\mu_0)$ in $\QCb(G)$.
+  %Using notation from \cite{laumon:87a}*{1.1}, this means $t_{\bullet L(f,\psi)} = t_{\bullet \qcs{L}_0}$.
+  Using \cite{laumon:87a}*{Th\'eor\`eme~1.1.2}, it follows that  $L(f,\psi) \iso \qcs{L}_0$ in $\Loc(G)$.
+  It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\qcs{L}_0,\mu_0)$ in $\QCb(G)$.
   This completes the proof that $L_G : \QCf(G) \to \QC(G)$ is essentially surjective.
@@
 see the end of Section~\ref{sec:snake}.
-Nevertheless, every quasicharacter sheaf $(\gcs{L},\mu,\phi)$ on $G$ 
-determines a Weil sheaf $(\gcs{L},\phi)$ on $G$. 
+Nevertheless, every quasicharacter sheaf $(\gqcs{L},\mu,\phi)$ on $G$ 
+determines a Weil sheaf $(\gqcs{L},\phi)$ on $G$. 
 So, if we choose a geometric point ${\bar g}_x$ in each component $\bG^x$ of $G$, then this choice can be used to convert 
-the Weil sheaf $(\gcs{L},\phi)$ into an $\ell$-adic character of $\prod_{x\in \pi_0(\bG)}\W(\bG^x, {\bar g}_x)$. 
+the Weil sheaf $(\gqcs{L},\phi)$ into an $\ell$-adic character of $\prod_{x\in \pi_0(\bG)}\W(\bG^x, {\bar g}_x)$. 
 It proved cumbersome, however, to manage various 
@@
  \labitem{(cs.0)}{cs.0} an indexed set of one-dimensional
-  $\EE$-vector spaces $\gcs{L}_x$, as $x$ runs over
+  $\EE$-vector spaces $\gqcs{L}_x$, as $x$ runs over
   $G(\bFq)$;
@@
  \labitem{(cs.1)}{cs.1} an indexed set of isomorphisms
-  $\mu_{x,y} : \gcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gcs{L}_{x} \otimes_{\EE}\gcs{L}_{y}$,
+  $\mu_{x,y} : \gqcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gqcs{L}_{x} \otimes_{\EE}\gqcs{L}_{y}$,
   for all $x,y \in G(\bFq)$, such that
@@
    \begin{tikzcd}[row sep=40]
-    \gcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
-    && \gcs{L}_{x+y}\otimes_{\EE}\gcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
-    \gcs{L}_{x} \otimes_{\EE}\gcs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
-    && \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes_{\EE}\gcs{L}_{z}
+    \gqcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
+    && \gqcs{L}_{x+y}\otimes_{\EE}\gqcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
+    \gqcs{L}_{x} \otimes_{\EE}\gqcs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
+    && \gqcs{L}_{x} \otimes\gqcs{L}_{y} \otimes_{\EE}\gqcs{L}_{z}
    \end{tikzcd}
@@
 
- \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
+ \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{\Fq}(x)} \to \gqcs{L}_x$
   such that
@@
    \begin{tikzcd}[row sep=40]
-    \gcs{L}_{\Frob{\Fq}(x)+\Frob{\Fq}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{\Fq}(x),\Frob{\Fq}(y)}}
-    && \gcs{L}_{\Frob{\Fq}(x)}\otimes_{\EE}\gcs{L}_{\Frob{\Fq}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
-    \gcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
-    && \gcs{L}_x \otimes\gcs{L}_y
+    \gqcs{L}_{\Frob{\Fq}(x)+\Frob{\Fq}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{\Fq}(x),\Frob{\Fq}(y)}}
+    && \gqcs{L}_{\Frob{\Fq}(x)}\otimes_{\EE}\gqcs{L}_{\Frob{\Fq}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
+    \gqcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
+    && \gqcs{L}_x \otimes\gqcs{L}_y
    \end{tikzcd}
@@
 \end{enumerate}
-Under this equivalence, a morphism $\alpha : \cs{L} \to \cs{L'}$ of quasicharacter sheaves on $G$ is given by 
+Under this equivalence, a morphism $\alpha : \qcs{L} \to \qcs{L'}$ of quasicharacter sheaves on $G$ is given by 
 \begin{enumerate}
- \labitem{(cs.3)}{cs.3} an indexed set $\alpha_x : \gcs{L}_x \to \gcs{L'}_x$
+ \labitem{(cs.3)}{cs.3} an indexed set $\alpha_x : \gqcs{L}_x \to \gqcs{L'}_x$
   of linear transformations (of one-dimensional $\EE$-vector spaces),
@@
    \begin{tikzcd}[column sep=40]
-    \arrow[swap]{d}{\phi_x} \gcs{L}_{\Frob{\Fq}(x)} \rar{\alpha_{\Frob{\Fq}(x)}} & \gcs{L'}_{\Frob{\Fq}(x)} \dar{\phi_x'}
-    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}& \arrow[swap]{d}{\mu} \gcs{L}_{x+y} \rar{\alpha_{x+y}} & \gcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
-    \gcs{L}_x \rar{\alpha_x} & \gcs{L'}_x
-    & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\alpha_x\otimes\alpha_y} & \gcs{L'}_x \otimes_{\EE}\gcs{L'}_y
+    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{\Fq}(x)} \rar{\alpha_{\Frob{\Fq}(x)}} & \gqcs{L'}_{\Frob{\Fq}(x)} \dar{\phi_x'}
+    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}& \arrow[swap]{d}{\mu} \gqcs{L}_{x+y} \rar{\alpha_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
+    \gqcs{L}_x \rar{\alpha_x} & \gqcs{L'}_x
+    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\alpha_x\otimes\alpha_y} & \gqcs{L'}_x \otimes_{\EE}\gqcs{L'}_y
    \end{tikzcd}
@@
 \begin{lemma}\label{lemma:section}
- If $\cs{L}$ is a quasicharacter sheaf on a commutative, \'etale group scheme $G$ over $\Fq$ and if $G(\bFq)$ is finitely generated, then there is a global section $s = \{ s(x) \in \gcs{L}_x \tq x \in G(\bFq) \}$ satisfying
+ If $\qcs{L}$ is a quasicharacter sheaf on a commutative, \'etale group scheme $G$ over $\Fq$ and if $G(\bFq)$ is finitely generated, then there is a global section $s = \{ s(x) \in \gqcs{L}_x \tq x \in G(\bFq) \}$ satisfying
  \begin{equation}\label{section}
@@
 
-  There is a unique isomorphism $\gcs{L}_0 \cong \EE$ under which $\mu_{0,0}$ corresponds
+  There is a unique isomorphism $\gqcs{L}_0 \cong \EE$ under which $\mu_{0,0}$ corresponds
   to the multiplication map $\EE \otimes_{\EE}\EE \to \EE$.
@@
 
-  The $\mu_{x,y}$ yield an isomorphism $\alpha_j : \gcs{L}_{y_j}^{\otimes m_j} \to \gcs{L}_0$.
+  The $\mu_{x,y}$ yield an isomorphism $\alpha_j : \gqcs{L}_{y_j}^{\otimes m_j} \to \gqcs{L}_0$.
   An initial nonzero choice of $s(y_j)$ need only be scaled by $\alpha_j(s(y_j))^{-1/m_j}$ in order to map to
@@
 The genesis of that hypothesis is Lemma~\ref{lemma:section},
-as we use this hypothesis to show the existence of global sections of $\gcs{L}$ satisfying \eqref{section} for $\mu$.
+as we use this hypothesis to show the existence of global sections of $\gqcs{L}$ satisfying \eqref{section} for $\mu$.
 Remarkably, Lemma~\ref{lemma:section} is the only crux for this hypothesis;
@@
   \qquad \text{given by}\qquad
-  \cs{L}_{/\text{iso}} \mapsto [\tau_\cs{L}],
-  \]
-  where $\tau_\cs{L}: \Weil{\Fq}\to G(\bFq)^*$ is a cocycle such that
-  \[
-  \forall x\in G(\Fq), \qquad \tau_\cs{L}(\Frob{\Fq})(x) = \trFrob{\cs{L}}(x).
+  \qcs{L}_{/\text{iso}} \mapsto [\tau_\qcs{L}],
+  \]
+  where $\tau_\qcs{L}: \Weil{\Fq}\to G(\bFq)^*$ is a cocycle such that
+  \[
+  \forall x\in G(\Fq), \qquad \tau_\qcs{L}(\Frob{\Fq})(x) = \trFrob{\qcs{L}}(x).
   \]
@@
 \begin{proof}
-  Suppose $\cs{L}$ is a quasicharacter sheaf on $G$.  
+  Suppose $\qcs{L}$ is a quasicharacter sheaf on $G$.  
   Using Lemma~\ref{lemma:section}, 
-  we may choose a section $s = \{ s(x) \in \gcs{L}_x \tq x \in G(\bFq) \}$ satisfying \eqref{section}.  We will construct a group isomorphism between $\QCiso{G}$ and
+  we may choose a section $s = \{ s(x) \in \gqcs{L}_x \tq x \in G(\bFq) \}$ satisfying \eqref{section}.  We will construct a group isomorphism between $\QCiso{G}$ and
   $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ using $s$, then prove independence from the choice of $s$.
 
-  Starting from $\cs{L}$, we define a cocyle $\tau_{\cs{L}} \in Z^1(\Weil{\Fq},G(\bFq)^*)$ as follows.
-  For $x \in G(\bFq)$, $\cs{L}$ determines an isomorphism $\phi_x : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
-  of one-dimensional $\EE$-vector spaces; define $\tau_\cs{L}$ by
+  Starting from $\qcs{L}$, we define a cocyle $\tau_{\qcs{L}} \in Z^1(\Weil{\Fq},G(\bFq)^*)$ as follows.
+  For $x \in G(\bFq)$, $\qcs{L}$ determines an isomorphism $\phi_x : \gqcs{L}_{\Frob{\Fq}(x)} \to \gqcs{L}_x$
+  of one-dimensional $\EE$-vector spaces; define $\tau_\qcs{L}$ by
   \begin{equation}\label{t}
-   \phi_{x}(s(\Frob{\Fq}(x))) = \tau_\cs{L}(\Frob{\Fq})(x) s(x).
+   \phi_{x}(s(\Frob{\Fq}(x))) = \tau_\qcs{L}(\Frob{\Fq})(x) s(x).
   \end{equation}
-  Note that if $x$ is fixed by $\Frob{k}$ then $\tau_\cs{L}(\Frob{\Fq})(x)$ is just $\trFrob{\cs{L}}(x)$, so the restriction of
-  $\tau_\cs{L}(\Frob{k})$ to $G(k)$ is just $\trFrob{\cs{L}}$.
+  Note that if $x$ is fixed by $\Frob{k}$ then $\tau_\qcs{L}(\Frob{\Fq})(x)$ is just $\trFrob{\qcs{L}}(x)$, so the restriction of
+  $\tau_\qcs{L}(\Frob{k})$ to $G(k)$ is just $\trFrob{\qcs{L}}$.
   In general, conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
-  the scalar $\tau_\cs{L}(\Frob{k})(x)$ is non-zero.  Moreover, condition~\ref{cs.1} forces
-  $\tau_\cs{L}(\Frob{\Fq})(x+y) = \tau_\cs{L}(\Frob{\Fq})(x) \ \tau_\cs{L}(\Frob{\Fq})(y)$
-  for all $x,y \in G(\bFq)$.  Now define $\tau_\cs{L} : \Weil{\Fq} \to G(\bFq)^*$ recursively by
-  \[
-   \tau_\cs{L}(\Frob{\Fq}^n) \ceq \tau_\cs{L}(\Frob{\Fq})\cdot \,^{\Frob{\Fq}} \tau_\cs{L}(\Frob{\Fq}^{n-1}),
+  the scalar $\tau_\qcs{L}(\Frob{k})(x)$ is non-zero.  Moreover, condition~\ref{cs.1} forces
+  $\tau_\qcs{L}(\Frob{\Fq})(x+y) = \tau_\qcs{L}(\Frob{\Fq})(x) \ \tau_\qcs{L}(\Frob{\Fq})(y)$
+  for all $x,y \in G(\bFq)$.  Now define $\tau_\qcs{L} : \Weil{\Fq} \to G(\bFq)^*$ recursively by
+  \[
+   \tau_\qcs{L}(\Frob{\Fq}^n) \ceq \tau_\qcs{L}(\Frob{\Fq})\cdot \,^{\Frob{\Fq}} \tau_\qcs{L}(\Frob{\Fq}^{n-1}),
   \]
@@
   Although we used a global section $s$ in the definition of
-  $\tau_\cs{L}$, the class of $\tau_\cs{L}$ does not depend on this
+  $\tau_\qcs{L}$, the class of $\tau_\qcs{L}$ does not depend on this
   choice. To see why, let $s_1$ and $s_2$ be two global sections of
-  $\cs{L}$ and let $\tau_1$ and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$.
+  $\qcs{L}$ and let $\tau_1$ and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$.
   For each $x \in G(\bFq)$ there is a unique scalar
@@
     \obj \QC(G) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
-    \qquad \text{defined by} \qquad \cs{L} \mapsto [\tau_\cs{L}],
+    \qquad \text{defined by} \qquad \qcs{L} \mapsto [\tau_\qcs{L}],
   \end{equation}
@@
 
-  We now show that $[\tau_\cs{L}]$ depends only on the isomorphism class of $\cs{L}$.
-  Let $\alpha : \cs{L} \to \cs{L'}$ be an isomorphism and
+  We now show that $[\tau_\qcs{L}]$ depends only on the isomorphism class of $\qcs{L}$.
+  Let $\alpha : \qcs{L} \to \qcs{L'}$ be an isomorphism and
   let $\tau$ and $\tau'$ be any cocycles representing the classes in the
-  image of $\cs{L}$ and $\cs{L'}$ under \eqref{cohomologous}; by construction,
+  image of $\qcs{L}$ and $\qcs{L'}$ under \eqref{cohomologous}; by construction,
   $\tau$ and $\tau'$ are defined by the choice of sections $s$ and $s'$ 
@@
   \begin{equation}\label{pich1}
-    \QCiso{G} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*), \qquad \cs{L}_{/\text{iso}} \mapsto [\tau_\cs{L}]
+    \QCiso{G} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*), \qquad \qcs{L}_{/\text{iso}} \mapsto [\tau_\qcs{L}]
   \end{equation}
@@
  The paragraph above also shows that \eqref{pich1} is injective. 
- Suppose $[\tau_\cs{L}] = [\tau_\cs{L'}]$.
- Let $s$ (resp. $s'$) be a section appearing in the definition of $\tau_\cs{L}$ (resp. $\tau_\cs{L'}$);
+ Suppose $[\tau_\qcs{L}] = [\tau_\qcs{L'}]$.
+ Let $s$ (resp. $s'$) be a section appearing in the definition of $\tau_\qcs{L}$ (resp. $\tau_\qcs{L'}$);
  recall that $s$ (resp. $s'$) is compatible with $\mu$ (resp $\mu'$) 
  in the sense of Lemma~\ref{lemma:section}.
- Since $[\tau_\cs{L}] = [\tau_\cs{L'}]$, 
- it follows that $\tau_\cs{L}$ and $\tau_{\cs{L'}}$ are cohomologous, 
+ Since $[\tau_\qcs{L}] = [\tau_\qcs{L'}]$, 
+ it follows that $\tau_\qcs{L}$ and $\tau_{\qcs{L'}}$ are cohomologous, 
   so there is some $a\in G(\Fq)^*$ such that 
   $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}a \cdot a^{-1})$. 
-  Define $\alpha : \cs{L}\to \cs{L'}$ by $\alpha_x(s(x)) = a(x) s'(x)$, for each $x\in G(\bFq)$.
+  Define $\alpha : \qcs{L}\to \qcs{L'}$ by $\alpha_x(s(x)) = a(x) s'(x)$, for each $x\in G(\bFq)$.
   it is straightforward to check that $\alpha$ satisfies condition~\ref{cs.3}
-  and that $\alpha^{-1} : \cs{L'}\to \cs{L}$, defined by $\alpha^{-1}_x(s'(x)) = a(x)^{-1} s(x)$, 
-  is its inverse. Thus, $\cs{L} \iso \cs{L'}$ in $\QC(G)$. 
+  and that $\alpha^{-1} : \qcs{L'}\to \qcs{L}$, defined by $\alpha^{-1}_x(s'(x)) = a(x)^{-1} s(x)$, 
+  is its inverse. Thus, $\qcs{L} \iso \qcs{L'}$ in $\QC(G)$. 
   This shows that \eqref{pich1} is injective.
 
-  Suppose that $\cs{L}$ and $\cs{L}'$ are two quasicharacter sheaves on $G$.
-  If $s$ is a global section for $\cs{L}$ and $s'$ for $\cs{L}'$ then $s \otimes_{\EE}s'$ is a global section for
-  $\cs{L} \otimes_{\EE}\cs{L}'$.  The three versions of \eqref{t} for $\cs{L}, \cs{L'}$ and $\cs{L} \otimes_{\EE}\cs{L}'$ imply that
-  $\tau_{\cs{L} \otimes_{\EE}\cs{L}'}(\Frob{k}) = \tau_\cs{L}(\Frob{k}) \tau_{\cs{L}'}(\Frob{k})$, so \eqref{pich1} is a group homomorphism.
+  Suppose that $\qcs{L}$ and $\qcs{L}'$ are two quasicharacter sheaves on $G$.
+  If $s$ is a global section for $\qcs{L}$ and $s'$ for $\qcs{L}'$ then $s \otimes_{\EE}s'$ is a global section for
+  $\qcs{L} \otimes_{\EE}\qcs{L}'$.  The three versions of \eqref{t} for $\qcs{L}, \qcs{L'}$ and $\qcs{L} \otimes_{\EE}\qcs{L}'$ imply that
+  $\tau_{\qcs{L} \otimes_{\EE}\qcs{L}'}(\Frob{k}) = \tau_\qcs{L}(\Frob{k}) \tau_{\qcs{L}'}(\Frob{k})$, so \eqref{pich1} is a group homomorphism.
 
  Finally, to show that \eqref{pich1} is surjective, pick $[\tau]\in \Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
- For each $x\in G(\bFq)$, set $\gcs{L}_x = \EE$.
- Define $\mu_{x,y} : \gcs{L}_{x+y} \to \gcs{L}_x\otimes_{\EE} \gcs{L}_y$ by
+ For each $x\in G(\bFq)$, set $\gqcs{L}_x = \EE$.
+ Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes_{\EE} \gqcs{L}_y$ by
  $\mu_{x,y}(1) = 1\otimes_{\EE}1$, for $x,y\in G(\bFq)$; 
  clearly, $\mu$ satisfies condition~\ref{cs.1}.
- Define $\phi_x : \gcs{L}_{\Frob{\Fq}} \to \gcs{L}_x$ by $\phi_x(1) = \tau(\Frob{\Fq})(x)$,
+ Define $\phi_x : \gqcs{L}_{\Frob{\Fq}} \to \gqcs{L}_x$ by $\phi_x(1) = \tau(\Frob{\Fq})(x)$,
  for each $x\in G(\bFq)$. 
  Then $\phi$ satisfies condition~\ref{cs.2} because $\tau \in Z^1(\Weil{\Fq},G(\bFq)^*)$.
- In this way we have built a quasicharacter sheaf $\cs{L} = (\gcs{L},\mu,\phi)$ 
- from $\tau \in \Hh^1(\Weil{\Fq}, G(\bFq)^*)$ such that the image of $\cs{L}_{/\text{iso}}$
+ In this way we have built a quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ 
+ from $\tau \in \Hh^1(\Weil{\Fq}, G(\bFq)^*)$ such that the image of $\qcs{L}_{/\text{iso}}$
  under \eqref{pich1} is the class $[\tau]$ in $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
@@
 $G^0\hookrightarrow G$ determines a monoidal functor
-$\cs{L}\mapsto \cs{L}\vert_{G^0}$ from $\QC(G)$ to $\QC(G^0)$.  In
+$\qcs{L}\mapsto \qcs{L}\vert_{G^0}$ from $\QC(G)$ to $\QC(G^0)$.  In
 this section we show that this functor is essentially surjective.
@@
   by the last part of Proposition~\ref{prop:pullback}. Specifically,
-  suppose $\cs{L}$ is a quasicharacter sheaf on $G$ that is trivial on
-  $G^0$. Then $\trFrob{\cs{L}}\vert_{G^0(\Fq)} = \trFrob{\cs{L}^0} =0$,
+  suppose $\qcs{L}$ is a quasicharacter sheaf on $G$ that is trivial on
+  $G^0$. Then $\trFrob{\qcs{L}}\vert_{G^0(\Fq)} = \trFrob{\qcs{L}^0} =0$,
   by Proposition~\ref{prop:pullback} again. Since the sequence of
@@
   pull-back of $\chi$ along $G(\Fq)\to \pi_0(G)(\Fq)$ is
-  $\trFrob{\cs{L}}$. By Propositions~\ref{prop:etale} and \ref{prop:X},
-  there is a a quasicharacter sheaf $\cs{L}_\chi$ on $\pi_0(G)$, unique up
-  to isomorphism, such that $\trFrob{\cs{L}_\chi} = \chi$. By
-  Proposition~\ref{prop:pullback} again, $\cs{L}$ is isomorphic to the
-  image of $\cs{L}_\chi$ under the monoidal functor $\QC(\pi_0(G)) \to \QC(G)$.
+  $\trFrob{\qcs{L}}$. By Propositions~\ref{prop:etale} and \ref{prop:X},
+  there is a a quasicharacter sheaf $\qcs{L}_\chi$ on $\pi_0(G)$, unique up
+  to isomorphism, such that $\trFrob{\qcs{L}_\chi} = \chi$. By
+  Proposition~\ref{prop:pullback} again, $\qcs{L}$ is isomorphic to the
+  image of $\qcs{L}_\chi$ under the monoidal functor $\QC(\pi_0(G)) \to \QC(G)$.
 
@@
 Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ 
-and let $\cs{L}$ be a quasicharacter sheaf in the isomorphism class 
+and let $\qcs{L}$ be a quasicharacter sheaf in the isomorphism class 
 corresponding to the character $\chi : G(\Fq) \to \EEx$ under Theorem~\ref{thm:snake}. 
-Then $\trFrob{\cs{L}}(1) = \ell$. Suppose $\cs{L}$ was a bounded quasicharacter sheaf. 
-Then the restriction of $\cs{L}$ to the connected component $1\in G$ 
+Then $\trFrob{\qcs{L}}(1) = \ell$. Suppose $\qcs{L}$ was a bounded quasicharacter sheaf. 
+Then the restriction of $\qcs{L}$ to the connected component $1\in G$ 
 would be a $\ell$-adic local system on $1$ of rank-1, 
@@
 while $\rho_1(\pi_1(1,{\bar 1}))$ is not compact in $\EEx$ (it contains $\ell^\ZZ$). 
-So the Weil sheaf $\gcs{L}$ does not descend to a local system on $G$.
-It follows that the quasicharacter sheaf $\cs{L}$ is not a bounded quasicharacter sheaf.
+So the Weil sheaf $\gqcs{L}$ does not descend to a local system on $G$.
+It follows that the quasicharacter sheaf $\qcs{L}$ is not a bounded quasicharacter sheaf.
 %
@@
 defined by $\chi(1) = 1+\ell$.
-In this case, the corresponding quasicharacter sheaf $\cs{L}$ is bounded, defined at $1$ by a pro-etale cover of $1$, but not finite, since $1+\ell$ is not a root of unity.
+In this case, the corresponding quasicharacter sheaf $\qcs{L}$ is bounded, defined at $1$ by a pro-etale cover of $1$, but not finite, since $1+\ell$ is not a root of unity.
 %

### 2013-08-16 shanghai.tex
Weil group added, and other minor changes.
.... but not the Weil group for a variety, yet.

@@
 \documentclass[11pt]{amsart}
-\title[Sheaf--function dictionary for local tori]{A sheaf--function dictionary for algebraic tori over non-archimedean local fields}
+\title[Sheaf--function dictionary for local tori]{A sheaf--function dictionary for algebraic tori over local fields}
 \usepackage[british]{babel}
@@
 
-We apply Theorem \ref{thm:snake} to the geometrization of quasicharacters
-of non-archimedian tori in Part 2.  Let $K$ be a non-archimedian local field
+In Part 2 we use Theorem~\ref{thm:snake} to make a sheaf--function dictionary for algebraic tori over local fields.  Let $K$ be a non-archimedian local field
 with finite residue field $\Fq$; we place no restriction on the characteristic of $K$.
@@
 group scheme $\GN{T}_d$ plays the r\^{o}le of $G$.  Theorem \ref{thm:application}
-now provides a geometrization of quasicharacters of $T$ in the form of a canonical isomorphism
+allows us to translate characters $T(K)$ of depth less than $d$ into quasicharacter sheaves on $\GN{T}_d$:
 \[
@@
 \iso
-\Hom_{< d}(T(K),\EEx)
-\] 
-between quasicharacter sheaves on $\GN{T}_d$ and characters of $T(K)$ with depth less than $d$.
-We also describe a group scheme $\GN{T}$ simultaneously geometrizing all quasicharacters of $T(K)$.
+\Hom_{< d}(T(K),\EEx).
+\]  
+We refer to finite-depth characters of $T(K)$ as quasicharacters and
+describe a group scheme $\GN{T}$ simultaneously geometrizing all such quasicharacters.
 
@@
 DeBacker and Reeder have recently applied Deligne-Lusztig representations to the
-local Langlands correspondence \cite{reeder-debacker:09a}.  The next step Lusztig took in studying representations
-of finite groups of Lie type was to define character sheaves for reductive groups over $\Fq$.
+local Langlands correspondence \cite{reeder-debacker:09a}.  
+After developing Deligne-Luzstig representations, 
+the next step Lusztig took in studying representations
+of finite groups of Lie type was to introduce character sheaves for reductive groups over $\Fq$.
 We hope that our quasicharacter sheaves can provide a stepping stone to a similar theory for
@@
 
-\part{Smooth commutative group schemes lft over finite fields} \label{part1}
+\part{Smooth commutative group schemes over finite fields} \label{part1}
 
@@
 
-Let $\Frob{\Fq}$ denote the geometric Frobenius element in $\Gal(\bFq/\Fq)$ as well as the corresponding automorphism of $\Spec{\bFq}$, and let $\Frob{G} := \id_{G} \times \Frob{\Fq}$ be the Frobenius automorphism of $\bG$.
-\David{add definition of Weil groups}
+Let $\Frob{\Fq}$ denote the geometric Frobenius element in $\Gal(\bFq/\Fq)$ as well as the corresponding automorphism of $\Spec{\bFq}$.
+The Weil group $\Weil{\Fq}\subset \Gal(\bFq/\Fq)$ is the subgroup generated by $\Frob{\Fq}$.
+Let $\Frob{G} := \id_{G} \times \Frob{\Fq}$ be the Frobenius automorphism of $\bG$.
 
@@
 the Weil sheaf $(\gqcs{L},\phi)$ into an $\ell$-adic character of $\prod_{x\in \pi_0(\bG)}\W(\bG^x, {\bar g}_x)$. 
-It proved cumbersome, however, to manage various 
+However, it proved cumbersome to manage various 
 choices of families of base points and track the action 
 of $\Gal(\bFq/\Fq)$ on this (generally) infinite product of 
-Weil groups, and difficult to identify the relevant quotient of this group. Viewed in this light, Definition~\ref{def:QC} seemed comparatively simple.
+Weil groups and difficult to identify the relevant quotient of this group. Viewed in this light, Definition~\ref{def:QC} is comparatively simple.
 

### 2013-08-16 shanghai.tex
Working on style in sections 1 and 2

--- 2013-08-16 shanghai.tex
@@
 $\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for $u,v\in \Weil{\Fq}$.
-Thus the pair $(\gqcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{\Fq}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of \cite{deligne:SGA4.5}*{Expos\'e XIII,~1.1}, failing only because $\Weil{\Fq}$ is profinite \David{Do you mean to say that $\Weil{\Fq}$ is not profinite?}.
-This fact \David{Which fact?
-That we can think about quasicharacter sheaves as an action on $\gqcs{L}$?
-Or that they fail to fulfill the requirements?} goes to the heart of the notion of a Weil sheaf and is one of the essential aspects of our definition of $\QC(G)$.
+Thus the pair $(\gqcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{\Fq}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of \cite{deligne:SGA4.5}*{Expos\'e XIII,~1.1}, failing only because $\Weil{\Fq}$ is not profinite.
+Our use of $\Weil{\Fq}$ rather than $\Gal(\bFq/\Fq)$ allows quasicharacter sheaves to correspond to unbounded characters.
 %\end{remark}
@@
 
-%\begin{proposition}\label{tensor}
-The category $\QC(G)$ of quasicharacter sheaves on $G$ is rigid symmetric monoidal category \cite{etingof:09a} under the tensor product
-$\qcs{L} \otimes_{\EE}\qcs{L'} \ceq (\gqcs{L}\otimes\gqcs{L'}, \mu\otimes\mu', \phi\otimes_{\EE}\phi')$
-\David{Why only some $\otimes_{\EE}$?}
-with duals given by applying the functor 
-$\sheafHom(\ - \ ,\EE)$ (sheaf hom) to
-conditions \ref{CS.0}, \ref{CS.1} and \ref{CS.2}.
-%\end{proposition}
-(The category of characters sheaves on $G$ is not abelian, so $\QC(G)$
-is not a tensor category in the sense of \cite{deligne:02a}.)
-%\begin{proof}\end{proof}
-%
+The category $\QC(G)$ of quasicharacter sheaves on $G$ is a rigid symmetric monoidal category
+\cite{etingof:09a} under the tensor product
+$\qcs{L} \otimes \qcs{L'} \ceq (\gqcs{L}\otimes\gqcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
+with duals given by applying the sheaf-hom functor 
+$\sheafHom(\ - \ ,\EE)$.
+The category of characters sheaves on $G$ is not abelian, so $\QC(G)$
+is not a tensor category in the sense of \cite{deligne:02a}.
 This rigid monoidal category structure for $\QC(G)$ puts a group
-structure on the set $\QCiso{G}$ of isomorphism classes in
-$\QC(G)$. Our main result regarding quasicharacter sheaves on $G$ (Theorem~\ref{thm:snake})
-determines $\QCiso{G}$ under the hypothesis that the component group scheme for $G$ is geometrically finitely generated; see Theorem~\ref{thm:snake}. To do this, we use the trace of Frobenius.
+structure on the set $\QCiso{G}$ of isomorphism classes in $\QC(G)$.
+We now begin developing the tools to relate $\QCiso{G}$ to $\Hom(G(\Fq), \EEx)$.
 

### 2013-08-17 shanghai.tex
Working on base change

@@
     \arrow[equal]{u} \bm^*  \Frob{G}^* \gqcs{L} \arrow[swap]{d}{\bm^* \phi}
-    && \Frob{G}^*\gqcs{L}\boxtimes \Frob{G}^*\gqcs{L} \dar{F\boxtimes \phi} \arrow[equal]{u} \\
+    && \Frob{G}^*\gqcs{L}\boxtimes \Frob{G}^*\gqcs{L} \dar{\phi\boxtimes \phi} \arrow[equal]{u} \\
     \bm^*\gqcs{L} \arrow{rr}{\mu}
@@
 \begin{tikzcd}
-\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota} \dar[swap]{\trFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\trFrob{G}} \\
+\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\trFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\trFrob{G}} \\
 G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
@@
 \end{proposition}
+\begin{proof}
+Suppose $\qcs{L} = (\gqcs{L}, \mu, \phi) \in \QC(\Res_{k'/k}(G_{k'}))$ and $x \in G(\Fq)$.
+The value $t_G(\iota^*(\qcs{L}))(x)$ is given by the trace of $\iota^*\phi$ on $(\iota^*\gqcs{L})_x$.
+Similarly, $\iota_{k'/k}^*(t_{\Res_{k'/k}(G_{k'})}(\qcs{L}))(x)$ is given by the trace of $\phi$ on
+$\gqcs{L}_{\iota(x)}$.  These are the same since $\iota$ is an inclusion and $\phi$
+preserves the stalk at $\iota(x)$. \David{Is this the right justification?}
+\end{proof}
 
@@
 \begin{proposition}\label{prop:basechange}
- The rule $\nu_{k'/k}: (\gqcs{L}, \mu, \varphi) \mapsto (\gqcs{L}, \mu, \varphi\vert_{\Weil{\Fq}})$ 
+ The rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$ 
  defines a monoidal functor $\QC(G) \to \QC(G_{k'})$. 
@@
 \end{proposition}
+\begin{proof}
+Let $\qcs{L} = (\gqcs{L}, \mu, \phi) \in \QC(G)$ and $x \in G(k')$.
+The value $t_{G_{k'}}(\nu_{k'/k}(\qcs{L})(x)$ is given by the trace of $\phi_{k'}$ on $\gqcs{L}_x$, while the value $\Nm_{k'/k}^*(t_G(\qcs{L}))(x)$ is given by the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
+After choosing bases of $\gqcs{L}_x, \ldots, \gqcs{L}_{\Frob{G}^n(x)}$, an iteration of \ref{CS.2} applied to the stalk of $\gqcs{L}^{\boxtimes n}$ at $(x, \Frob{G}(x), \ldots, \Frob{G}^{n-1}(x))$ expresses the trace of $\phi$ at $\Nm_{k'/k}(x)$ as a product of
+\end{proof}
 

### 2013-08-17 shanghai.tex
Finished work on base change section

@@
 \begin{proof}
-Suppose $\qcs{L} = (\gqcs{L}, \mu, \phi) \in \QC(\Res_{k'/k}(G_{k'}))$ and $x \in G(\Fq)$.
-The value $t_G(\iota^*(\qcs{L}))(x)$ is given by the trace of $\iota^*\phi$ on $(\iota^*\gqcs{L})_x$.
-Similarly, $\iota_{k'/k}^*(t_{\Res_{k'/k}(G_{k'})}(\qcs{L}))(x)$ is given by the trace of $\phi$ on
-$\gqcs{L}_{\iota(x)}$.  These are the same since $\iota$ is an inclusion and $\phi$
-preserves the stalk at $\iota(x)$. \David{Is this the right justification?}
+This result follows immediately from Proposition~\ref{prop:pullback} together with the identifications
+$\Res_{k'/k}(G_{k'})(k) \cong G_{k'}(k') \cong G(k')$ from the definitions of Weil restriction and base change.
 \end{proof}
 
-In the opposite direction, let $\Nm_{k'/k} : G(k') \to G(k)$ be the norm map and consider the group homomorphism:
-\[
-\Nm_{k'/k}^* : G(k)^* \to G(k')^* \qquad \text{defined by}\qquad \chi \mapsto \chi\circ \Nm_{k'/k}.
+In the opposite direction, let $\Nm : G(k') \to G(k)$ be the norm map and consider the group homomorphism:
+\[
+\Nm^* : G(k)^* \to G(k')^* \qquad \text{defined by}\qquad \chi \mapsto \chi\circ \Nm.
 \]
@@
 If $\qcs{L} = (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$ we may define
-a quasicharacter sheaf $\qcs{L}' = (\gqcs{L}, \mu, \phi_{k'})$ on 
-$G_{k'}\ceq G\times_{\Spec{k}} \Spec{k'}$ by setting
+a quasicharacter sheaf $\qcs{L}' = (\gqcs{L}, \mu, \phi_{k'})$ on the base change
+$G_{k'}$ of $G$ to $k'$ by setting
 \[
@@
 \QCiso{G} \rar{\nu_{k'/k}} \dar{\trFrob{G}} & \QCiso{G_{k'}} \dar{\trFrob{G_{k'}}} \\
-G(k)^*  \rar{\Nm_{k'/k}^*} & G(k')^*.
+G(k)^*  \rar{\Nm^*} & G(k')^*.
 \end{tikzcd}
@@
 \begin{proof}
-Let $\qcs{L} = (\gqcs{L}, \mu, \phi) \in \QC(G)$ and $x \in G(k')$.
-The value $t_{G_{k'}}(\nu_{k'/k}(\qcs{L})(x)$ is given by the trace of $\phi_{k'}$ on $\gqcs{L}_x$, while the value $\Nm_{k'/k}^*(t_G(\qcs{L}))(x)$ is given by the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
-After choosing bases of $\gqcs{L}_x, \ldots, \gqcs{L}_{\Frob{G}^n(x)}$, an iteration of \ref{CS.2} applied to the stalk of $\gqcs{L}^{\boxtimes n}$ at $(x, \Frob{G}(x), \ldots, \Frob{G}^{n-1}(x))$ expresses the trace of $\phi$ at $\Nm_{k'/k}(x)$ as a product of
+Let $\qcs{L} = (\gqcs{L}, \mu, \phi) \in \QC(G)$ and $x \in G(k')$ and write $\Frob{}$ for $\Frob{G}$.
+The value $t_{G_{k'}}(\nu_{k'/k}(\qcs{L})(x)$ is given by the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
+while the value $\Nm^*(t_G(\qcs{L}))(x)$ is given by the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
+Applying \ref{CS.2} to the stalk of $\gqcs{L}^{\boxtimes n}$ at $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
+\[
+\begin{tikzcd}
+\gqcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gqcs{L}_{\Frob{}(x)} \otimes \gqcs{L}_{\Frob{}^2(x)} \otimes \cdots \otimes \gqcs{L}_x
+\dar{\phi_x \otimes (\Frob{}^*\phi)_x \otimes \cdots \otimes ((\Frob{}^{n-1})^*\phi)_x} \\
+\gqcs{L}_{\Nm(x)} \rar & \gqcs{L}_x \otimes \gqcs{L}_{\Frob{}(x)} \otimes \cdots \otimes \gqcs{L}_{\Frob{}^{n-1}(x)}.
+\end{tikzcd}
+\]
+Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$, mapping to $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
+along the bottom map, where $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{CS.1}, $v$ maps to
+$v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
+Let $\alpha_i \in \EEx$ represent $((\Frob{}^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
+the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gqcs{L}_{\Nm(x)}$
+with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gqcs{L}_x$.
 \end{proof}
 
-Finally, we explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
+Finally, let $G'$ be a smooth commutative group scheme locally of finite type over $k'$;
+we explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
 The base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
@@
 \]
-The component corresponding to the identity element yields a natural inclusion 
+Since products and coproducts agree for group schemes we have a natural inclusion of $k'$-schemes 
 \[
@@
 \]
-of $k'$-schemes.  The definition of base change yields a map of $k$-schemes
-\[
-(\Res_{k'/k}G')_{k'} \to \Res_{k'/k}G'.
-\]
-Consecutive pullback along these maps yields a functor
-\[
-\QC(G') \to \QC(\Res_{k'/k}G').
+mapping $G'$ into the summand corresponding to $1 \in \Gal(k'/k)$.  Composing pullback
+along this map with $\nu_{k'/k}$ from Proposition~\ref{prop:basechange} yields a functor
+\[
+\QC(\Res_{k'/k}G') \to \QC(G').
 \]
@@
 \begin{proposition}
-The following diagram commutes:
-\[
-\begin{tikzcd}
-\QCiso{G'} \dar{\trFrob{G'}} \rar & \QCiso{\Res_{k'/k} G'} \dar{\trFrob{\Res_{k'/k} G'}} \\
- G'(k')^* \rar & (\Res_{k'/k}G')(k)^*
+The following diagram of isomorphisms commutes, where the bottom map is the identity:
+\[
+\begin{tikzcd}
+\QCiso{\Res_{k'/k} G'} \dar{\trFrob{\Res_{k'/k} G'}} \rar & \QCiso{G'} \dar{\trFrob{G'}}\\
+G'(k')^* \rar & G'(k')^*
 \end{tikzcd}
@@
 \end{proposition}
+\begin{proof}
+By Proposition~\ref{prop:pullback} the pullback part of the definition corresponds to the map $(\Res_{k'/k}G')(k') \to G'(k')^*$
+induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on $(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'$
+is given by permuting coordinates, composition with the norm map yields the identity on $G'(k')$.
+\end{proof}
 

### 2013-08-17 shanghai.tex
Working on greenberg of neron section.

--- 2013-08-17 shanghai.tex
@@
   First, recall that $L_G(f,\psi) = (L(f,\psi), \mu(f,\psi))$.
+  Let $k'/k$ be any degree-$n$ extension and let $\Nm : k'\to k$ be the norm map. 
   By \cite{laumon:87a}*{1.1.3.3}, 
   \[
-  \trFrob{(G_{k'}\hookrightarrow G)^*L(f,\psi)} = \trFrob{\qcs{L}} \circ N_{k'/k},
-  \]
-   for each finite extension $k'/k$.
-  On the other hand, 
-  \[
-  \trFrob{\qcs{L}} \circ N_{k'/k} = \trFrob{(G_{k'}\hookrightarrow G)^*\qcs{L}},
+  \trFrob{(G_{k'}\hookrightarrow G)^*L(f,\psi)} = \trFrob{\qcs{L}} \circ \Nm;
+  \]
+  on the other hand, 
+  \[
+  \trFrob{\qcs{L}} \circ \Nm = \trFrob{(G_{k'}\hookrightarrow G)^*\qcs{L}},
   \]
@@
 We write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$. 
-For any positive integer $d$, set $A_d\ceq \OK/\pK^d$.
+%For any positive integer $d$, set $A_d\ceq \OK/\pK^d$.
 Let $T$ be an algebraic torus over $K$.
@@
 \begin{definition}\label{def:GN}
-For each positive integer $d$, set $\TT_{d} \ceq \TT \times_\Spec{\OK} \Spec{A_d}$. Observe that $A_d$ is an Artin ring and $\TT_{d}$ is smooth and locally of finite type over $A_d$.
+For each positive integer $d$, set $\TT_{d} \ceq \TT \times_\Spec{\OK} \Spec{\OK/\pK^d}$. Observe that $\OK/\pK^d$ is an Artin ring and $\TT_{d}$ is smooth and locally of finite type over $\OK/\pK^d$.
 %
@@
 
-See \cite{greenberg:63a} and \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch.
-9, \S 6} and the first few sections of \cite{stasinski:12a} for background on the Greenberg functor.
+See \cite{greenberg:63a} and \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} and the first few sections of \cite{stasinski:12a} for background on the Greenberg functor.
+
+For each positive integer $d$, consider the canonical surjective ring homomorphisms $\OK/\pK^{d+1} \to \OK/\pK^d$ and the associated cartesian diagram of schemes 
+\[
+\begin{tikzcd}
+\Spec{\OK/\pK^d} \arrow[hook]{rr} && \Spec{\OK/\pK^{d+1}} \arrow[hook]{r} & \Spec{\OK} \\
+ \arrow{u} \TT_{d} \arrow[hook]{rr} & \ \arrow[Rightarrow]{d}{\text{Greenberg functor}} & \arrow{u} \TT_{d+1}  &  \\
+\GN{T}_{d} \arrow[hook]{rr} & \ & \GN{T}_{d+1}  \arrow{r} & \Spec{k}
+\end{tikzcd}
+\]
+The map $\GN{T}_{d} \hookrightarrow \GN{T}_{d+1}$ is not a morphism of group schemes.
+There is, however, an epimorphism of group schemes $\GN{T}_{d+1} \to \GN{T}_{d}$ for which $\GN{T}_{d} \hookrightarrow \GN{T}_{d+1}$ is a section.
+
 The fundamental properties of $\GN{T}_d$ that we need are:
  \begin{enumerate}
-   \labitem{(GN.0)}{dFq} $\GN{T}_d(\Fq) = \TT(A_d)$, canonically.
+   \labitem{(GN.0)}{dFq} $\GN{T}_d(\Fq) = \TT(\OK/\pK^d)$, canonically.
   \labitem{(GN.1)}{GNd} $\GN{T}_d$ is a smooth, commutative group scheme, locally of finite type over $\Fq$, and the component group of $\GN{T}_d$ is geometrically finitely generated.
+(In fact, $\pi_0(\GN{T}_d) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$, and the latter is finitely generated by \cite{xarles:93a}.)
+  \labitem{(GN.2)}{d+1} 
   \end{enumerate}
-In fact, $\pi_0(\GN{T}_d) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$, and the latter is finitely generated by \cite{xarles:93a}.
 
@@
   $\QCiso{\GN{T}_d} \iso \GN{T}_d(\Fq)^*$.
-  By \ref{dFq}, $\GN{T}_d(\Fq) = \TT(A_d)$.
+  By \ref{dFq}, $\GN{T}_d(\Fq) = \TT(\OK/\pK^d)$.
   Then we recall that the filtration of $T(K)$ used to
-  define depth has the property that $\TT(A_d) \cong T(K) / T(K)_d$
+  define depth has the property that $\TT(\OK/\pK^d) \cong T(K) / T(K)_d$
   \cite{yu:03a}*{Prop 5.2}, so characters of $\GN{T}_d(\Fq)$ 
@@
 \section{A sheaf-function dictionary for tori over local fields} \label{sec:quasichar}
-
-\Clifton{I'm working here, now.}
-If $d\leq d'$, then $\pK^{d'} \hookrightarrow \pK^d$ so there is a canonical surjective ring homomorphism $A_{d'} \to A_{d}$. Set $S = \Spec{\OK}$ and $S_d = \Spec{A_d}$. 
-\[
-\begin{tikzcd}
-S_1 \arrow[hook]{r} 
-& S_2 \arrow[hook]{r} \cdots 
-& S_d \arrow[hook]{r}  
-& S_{d'} \arrow[hook]{r} \cdots 
-& S
-\end{tikzcd}
-\]
-
- then $\GN{T}_d$ is a closed subgroup of $\GN{T}_{d'}$,
-so these smooth commutative group schemes form a directed system.
-\[
-\begin{tikzcd}
-\GN{T}_1 
-& \arrow[two heads]{l} \GN{T}_2 
-& \arrow[two heads]{l} \cdots 
-& \arrow[two heads]{l} \GN{T}_d 
-& \arrow[two heads]{l} \GN{T}_{d'} 
-& \arrow[two heads]{l} \cdots
-\end{tikzcd}
-\]
 

### 2013-08-17 shanghai.tex
Adding newlines, deleting comments

@@
 
-In Part 2 we use Theorem~\ref{thm:snake} to make a sheaf--function dictionary for algebraic tori over local fields.  Let $K$ be a non-archimedian local field
+In Part 2 we use Theorem~\ref{thm:snake} to make a sheaf--function dictionary
+for algebraic tori over local fields.  Let $K$ be a non-archimedian local field
 with finite residue field $\Fq$; we place no restriction on the characteristic of $K$.
@@
 
-Throughout this paper, $G$ is a smooth commutative group scheme locally of finite type over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.
+Throughout this paper, $G$ is a smooth commutative group scheme locally of finite type
+over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.
 
 We fix an algebraic closure $\bFq$ of $\Fq$ and write $\bG$ for the
-smooth commutative group scheme $G \times_{\Spec{\Fq}} \Spec{\bFq}$ over $\bFq$ obtained by base change from $k$. The multiplication morphism for $\bG$ will be denoted by $\bm$.
-
-Let $\Frob{\Fq}$ denote the geometric Frobenius element in $\Gal(\bFq/\Fq)$ as well as the corresponding automorphism of $\Spec{\bFq}$.
-The Weil group $\Weil{\Fq}\subset \Gal(\bFq/\Fq)$ is the subgroup generated by $\Frob{\Fq}$.
+smooth commutative group scheme $G \times_{\Spec{\Fq}} \Spec{\bFq}$ over $\bFq$
+obtained by base change from $k$. The multiplication morphism for $\bG$ will be denoted by $\bm$.
+
+Let $\Frob{\Fq}$ denote the geometric Frobenius element in $\Gal(\bFq/\Fq)$ as
+well as the corresponding automorphism of $\Spec{\bFq}$. The Weil group
+$\Weil{\Fq}\subset \Gal(\bFq/\Fq)$ is the subgroup generated by $\Frob{\Fq}$.
 Let $\Frob{G} := \id_{G} \times \Frob{\Fq}$ be the Frobenius automorphism of $\bG$.
@@
 \begin{enumerate}
-\labitem{(CS.0)}{CS.0} $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ (a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component) of rank-1; 
+\labitem{(CS.0)}{CS.0} $\gqcs{L}$ is an $\ell$-adic local system on $\bG$
+(a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component) of rank-1; 
 \labitem{(CS.1)}{CS.1} $\mu: \bm^* \gqcs{L} \to \LxL$
@@
 \end{enumerate}
-%In short, a quasicharacter sheaf on $G$  is a rank-1 Weil local system $(\gqcs{L},\phi)$ on $G$ equipped with an isomorphism $m^* (\gqcs{L},\phi) \to (\gqcs{L},\phi)\boxtimes (\gqcs{L},\phi)$. 
 \end{definition}
@@
 
-%\begin{remark} \label{rem:CS-action}
-The rule $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ defines a forgetful functor from quasicharacter sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
-
-As mentioned after \cite{deligne:80a}*{Def.~1.1.10}, a Weil sheaf $(\gqcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gqcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{\Fq}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
-We now review this point of view for later use in Section \ref{sec:basechange}.
-If $w = \Frob{\Fq}^n$ we write $w_G$ for $\Frob{G}^n$.
+The rule $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ defines a forgetful functor from quasicharacter
+sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
+
+As mentioned after \cite{deligne:80a}*{Def.~1.1.10}, a Weil sheaf $(\gqcs{L},\phi)$ on $G$
+may be interpreted as a constructible $\ell$-adic sheaf $\gqcs{L}$ on $\bG$ together with
+an action of the Weil group $\Weil{\Fq}$ on $\gqcs{L}$ compatible with the action of
+$\Gal(\bFq/\Fq)$ on $\bG$. We now review this point of view for later use in
+Section~\ref{sec:basechange}.  If $w = \Frob{\Fq}^n$ we write $w_G$ for $\Frob{G}^n$.
 For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gqcs{L}\to \gqcs{L}$ by
@@
 $\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for $u,v\in \Weil{\Fq}$.
-Thus the pair $(\gqcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{\Fq}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of \cite{deligne:SGA4.5}*{Expos\'e XIII,~1.1}, failing only because $\Weil{\Fq}$ is not profinite.
-Our use of $\Weil{\Fq}$ rather than $\Gal(\bFq/\Fq)$ allows quasicharacter sheaves to correspond to unbounded characters.
+Thus the pair $(\gqcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{\Fq}$
+on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of
+\cite{deligne:SGA4.5}*{Expos\'e XIII,~1.1}, failing only because $\Weil{\Fq}$ is not profinite.
+Our use of $\Weil{\Fq}$ rather than $\Gal(\bFq/\Fq)$ allows quasicharacter sheaves to
+correspond to unbounded characters.
 %\end{remark}
@@
 \end{equation}
-It is easy to see that $\QCiso{0}$ is trivial. In this paper we will find $\QCiso{G^0}$ and $\QCiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; 
+It is easy to see that $\QCiso{0}$ is trivial. In this paper we will find $\QCiso{G^0}$
+and $\QCiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; 
 the snake lemma will then allow us to show
@@
 %\section{Products} 
-We end this section with a simple result on products of quasicharacter sheaves, which is needed to show that the isomorphism above is functorial.
+We end this section with a simple result on products of quasicharacter sheaves,
+which is needed to show that the isomorphism above is functorial.
 
@@
 \begin{tikzcd}[column sep=60]
-\arrow{d}{\trFrob{G_1} \times \trFrob{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes} & \arrow{d}{\trFrob{G_1\times G_2}} \QCiso{G_1\times G_2}\\
+\arrow{d}{\trFrob{G_1} \times \trFrob{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes}
+& \arrow{d}{\trFrob{G_1\times G_2}} \QCiso{G_1\times G_2}\\
 (G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
@@
 \begin{proof}
-The only non-trivial part is essential surjectivity.
-Set $G \ceq G_1\times G_2$.
-Let $\qcs{L}$ be a quasicharacter sheaf on $G$.
-Define $f : G\to G\times G$ by $f(g_1,g_2) = (g_1,e_2,e_1,g_2)$.
-Observe that $m\circ f = \id_G$.
+The only non-trivial part is essential surjectivity. Set $G \ceq G_1\times G_2$.
+Let $\qcs{L}$ be a quasicharacter sheaf on $G$. Define $f : G\to G\times G$
+by $f(g_1,g_2) = (g_1,e_2,e_1,g_2)$. Observe that $m\circ f = \id_G$. 
 Let $p_1$, $p_2$ be the projection morphisms pictured below:
@@
 \begin{tikzcd}
-G_1  \arrow[swap, bend right]{r}{q_1} & \arrow[swap, bend right]{l}{r_1} G_1\times G_2 \arrow[bend left]{r}{r_2} &  \arrow[bend left]{l}{q_2} G_2.
+G_1  \arrow[swap, bend right]{r}{q_1} &
+\arrow[swap, bend right]{l}{r_1} G_1\times G_2 \arrow[bend left]{r}{r_2} &
+\arrow[bend left]{l}{q_2} G_2.
 \end{tikzcd}
@@
 \begin{proof}[Proof of Proposition~\ref{prop:functorialG}]
-The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$.
-When further combined with Proposition~\ref{prop:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.
+The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
+while the second part shows that Trace of Frobenius is a natural transformation
+$t: F_1 \to F_2$. When further combined with Proposition~\ref{prop:product},
+we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural
+transformation between additive functors.
 \end{proof}
@@
 how quasicharacter sheaves behave under change of fields.
-Let $k'$ be a finite extension of $k$. Then $k\to k'$ induces a group homomorphism $i_{k'/k} : G(k) \hookrightarrow G(k')$ which, in turn, gives
+Let $k'$ be a finite extension of $k$. Then $k\to k'$ induces a group homomorphism
+$i_{k'/k} : G(k) \hookrightarrow G(k')$ which, in turn, gives
 \[
@@
 \]
-be the functor obtained by pull-back along the canonical closed immersion of $k$-schemes  $\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$ \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}. 
+be the functor obtained by pull-back along the canonical closed immersion of $k$-schemes
+$\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$ \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}. 
 The following diagram commutes:
@@
  Moreover, $\phi$ is compatible with $\mu$ in the sense of Condition~\ref{CS.3}.
- It follows that functor $(\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,b_{G\times G}^* \mu_0, \phi)$, denoted by  $B_G^*: \QCb(G) \hookrightarrow \QC(G)$ below, is full and faithful.
+ It follows that functor $(\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,b_{G\times G}^* \mu_0, \phi)$,
+ denoted by  $B_G^*: \QCb(G) \hookrightarrow \QC(G)$ below, is full and faithful.
 \end{proof}
 
-The full subcategory $\QCb(G)$ of bounded quasicharacter sheaves is an essentially proper subcategory of $\QC(G)$, in general.
-Indeed, it follows from our main result regarding quasicharacter sheaves, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ to the subgroup $\QCbiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is bounded in $\EEx$; see Section~\ref{sec:snake}.
+The full subcategory $\QCb(G)$ of bounded quasicharacter sheaves is an essentially
+proper subcategory of $\QC(G)$, in general. Indeed, it follows from our main result
+regarding quasicharacter sheaves, Theorem~\ref{thm:snake}, that the restriction of
+$\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ to the subgroup $\QCbiso{G}$ is an isomorphism
+onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is bounded in $\EEx$;
+see Section~\ref{sec:snake}.
 
@@
 Consider the following category $C(G)$.
-Let us say that $f : H\to G$ is a \emph{discrete isogeny} if it is a a finite, surjective etale morphism and a morphism of commutative group $\Fq$-schemes, for which the action of $\Gal(\bFq/\Fq)$ on the etale group scheme $f^{-1}{\bar e}$ is trivial.
+Let us say that $f : H\to G$ is a \emph{discrete isogeny} if it is a a finite, surjective
+etale morphism and a morphism of commutative group $\Fq$-schemes, for which
+the action of $\Gal(\bFq/\Fq)$ on the etale group scheme $f^{-1}{\bar e}$ is trivial.
 An object in $C(G)$ is a pair $(f,\psi)$ where: 
@@
 Likewise, $C(G)[W^{-1}]$ is a tensor category.
-Let $C_1(G)$ be the rigid monoidal full subcategory of $C(G)$ consisting of objects $(f,\psi)$ such that $\psi$ is a one-dimensional representation.
+Let $C_1(G)$ be the rigid monoidal full subcategory of $C(G)$ consisting of objects
+$(f,\psi)$ such that $\psi$ is a one-dimensional representation.
 
 \begin{definition}
-The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\QCf(G)$, is the rigid symmetric monoidal category obtained by localizing $C_1(G)$ at weak isomorphisms.
+The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\QCf(G)$,
+is the rigid symmetric monoidal category obtained by localizing $C_1(G)$ at weak isomorphisms.
 \end{definition}
@@
  Then the equivariance condition on $U$ becomes $\psi' = \psi\circ \beta$ on the finite etale group scheme $\ker f'$. 
- Since $f$ and $f'$ are finite etale, and $f' = f\circ \beta$, and $\beta$ is surjective, $\beta$ is an etale cover; therefore, $\beta$ admits a section $\beta' : H \to H'$.
+ Since $f$ and $f'$ are finite etale, and $f' = f\circ \beta$, and $\beta$ is surjective,
+ $\beta$ is an etale cover; therefore, $\beta$ admits a section $\beta' : H \to H'$.
  This provides the inverse to $L(\beta,U) : L(f,\psi) \to L(f',\psi')$.
@@
  Conversely, if $L(\alpha,T)$ is an isomorphism of local systems, 
- then $T$ must be an isomorphism of vector spaces and $\beta$ must be surjective, whence $(\alpha,T)$ is a weak isomorphism: $W$ is saturated.
+ then $T$ must be an isomorphism of vector spaces and $\beta$ must be surjective,
+ whence $(\alpha,T)$ is a weak isomorphism: $W$ is saturated.
 
@@
 \begin{lemma}\label{lemma:finite-pull-back}
-If $g : G'\to G$ is a morphism of group schemes then $(f,\psi) \mapsto (f_g,\psi_g)$ defines a monomial functor $g^* : C(G)[W^{-1}] \to C(G')[W'^{-1}]$ where $f_g : H\times_G G'\to G'$ is a pull-back of $f$ along $g$ and $\psi_g : \ker f_g \to \Aut(V)$ is defined by the diagram below.
+If $g : G'\to G$ is a morphism of group schemes then $(f,\psi) \mapsto (f_g,\psi_g)$
+defines a monomial functor $g^* : C(G)[W^{-1}] \to C(G')[W'^{-1}]$ where $f_g : H\times_G G'\to G'$
+is a pull-back of $f$ along $g$ and $\psi_g : \ker f_g \to \Aut(V)$ is defined by the diagram below.
 \[
@@
 V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker g_f}} \ker f_g \arrow[hook]{r} & \arrow[swap]{u}{g_f} H\times_G G' \arrow{r}{f_g} & \arrow{u}{g} G'.
+  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker g_f}} \ker f_g \arrow[hook]{r}
+  & \arrow[swap]{u}{g_f} H\times_G G' \arrow{r}{f_g} & \arrow{u}{g} G'.
 \end{tikzcd}
@@
 \begin{proof}
-The key point is that pull-back along $g$ takes isogenies to isogenies, and maps over $G$ to maps over $G'$, as pictured below.
+The key point is that pull-back along $g$ takes isogenies to isogenies,
+and maps over $G$ to maps over $G'$, as pictured below.
 \[
@@
 \]
-In this form we could treat $g^*$ as a functor $G(G')\to C(G)$, where it not for the fact that pull-back is defined only up to isomorphism. In the localized categories, this ambiguity disappears. 
+In this form we could treat $g^*$ as a functor $G(G')\to C(G)$,
+where it not for the fact that pull-back is defined only up to isomorphism.
+In the localized categories, this ambiguity disappears. 
 \end{proof}
@@
 \begin{proof}
-As in Lemma~\ref{lemma:finite-pull-back}, we have $m^*(f,\psi) = (f_m,\psi_m)$ where $f_m$ and $\psi_m$ are pictured below, where $H_m = H\times_G(G\times G)$.
+As in Lemma~\ref{lemma:finite-pull-back}, we have $m^*(f,\psi) = (f_m,\psi_m)$
+where $f_m$ and $\psi_m$ are pictured below, where $H_m = H\times_G(G\times G)$.
 \[
@@
 V & \Aut(V) & \arrow[swap]{l}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(m_f)\vert_{\ker m_f}} \ker f_m \arrow[hook]{r} & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G.
+  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(m_f)\vert_{\ker m_f}} \ker f_m \arrow[hook]{r}
+  & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G.
 \end{tikzcd}
@@
 On the other hand, $(f,\psi) \boxtimes (f,\psi) = (f\times f, \psi\otimes \psi)$.
-Since $f\circ m_H = m \circ (f\times f)$, by the universal property of pull-back, there is a unique $\theta : H\times H \to H_m$ making the following commute.
+Since $f\circ m_H = m \circ (f\times f)$, by the universal property of pull-back,
+there is a unique $\theta : H\times H \to H_m$ making the following commute.
 \[
 \begin{tikzcd}[row sep=20,column sep=10]
-\ & V \arrow{dd}{T} && \Aut(V) && \arrow{dl} \arrow[swap]{ll}{\psi_g} A_m \arrow[hook]{rr} && \arrow[swap]{ld}{m_f} H_m \arrow{rr}{f_m} && \arrow[equal]{dd} \arrow{ld}{m} G\times G\\
+\ & V \arrow{dd}{T} && \Aut(V) && \arrow{dl} \arrow[swap]{ll}{\psi_g} A_m \arrow[hook]{rr}
+&& \arrow[swap]{ld}{m_f} H_m \arrow{rr}{f_m} && \arrow[equal]{dd} \arrow{ld}{m} G\times G\\
  && && \arrow{ul}{\psi} A  \arrow[hook]{rr} && H  \arrow[swap, pos=0.8]{rr}{f} && G  & \\
-& V\otimes_{\EE} V && \Aut(V) && \arrow[swap]{ll}{\psi \otimes \psi} \arrow[swap,pos=0.8]{uu}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr} && \arrow[swap,pos=0.8]{uu}{\theta} \arrow{ul}{m_H} H\times H \arrow{rr}{f\times f} && G\times G
+& V\otimes_{\EE} V && \Aut(V)
+&& \arrow[swap]{ll}{\psi \otimes \psi} \arrow[swap,pos=0.8]{uu}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr}
+&& \arrow[swap,pos=0.8]{uu}{\theta} \arrow{ul}{m_H} H\times H \arrow{rr}{f\times f} && G\times G
 \end{tikzcd}
@@
 Choose a basis $\{ v_1 \}$ for $V$; then $\{ v_1\otimes v_1 \}$ is a basis for $V\otimes V$.
-Define $T : V \to V\otimes V$ by $T(v_1) = v_1\otimes v_1$.
-Then the lower part of this diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G)$.
+Define $T : V \to V\otimes V$ by $T(v_1) = v_1\otimes v_1$. Then the lower part of this
+diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G)$.
 
 While $\theta$ was canonical, $T$ was not, as it depended on the choice of a basis for $V$.
-However, after passing from $C_1(G)$ to $\QCf(G)$, the resulting isomorphism $\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ is canonical in $\QCf(G)$.
+However, after passing from $C_1(G)$ to $\QCf(G)$, the resulting isomorphism
+$\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ is canonical in $\QCf(G)$.
 \end{proof}
 
-%\Clifton{I'll address this point in the next section: "Because $\Gal(\bFq/\Fq)$ acts trivially on $\Aut({\bar f})$, the local system ${\bar L}_G(f,\psi)\ceq b_G^* L(f,\psi)$ comes equipped with a canonical isomorphism $F : \Frob{G}^* {\bar L}_G(f,\psi) \to {\bar L}_G(f,\psi)$ of constructible sheaves on ${\bar G}$."}
-
-The full subcategory $\QCf(G) \subset \QCb(G)$ of finite quasicharacter sheaves is a proper subcategory, in general.
-Indeed, it follows from our main result regarding quasicharacter sheaves, Theorem~\ref{thm:snake}, that the restriction of $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ to the subgroup $\QCfiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is finite in $\EEx$; see Section~\ref{sec:snake}.
+The full subcategory $\QCf(G) \subset \QCb(G)$ of finite quasicharacter sheaves
+is a proper subcategory, in general. Indeed, it follows from our main result regarding
+quasicharacter sheaves, Theorem~\ref{thm:snake}, that the restriction of
+$\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ to the subgroup $\QCfiso{G}$ is an isomorphism
+onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is finite in $\EEx$;
+see Section~\ref{sec:snake}.
 
 \section{Connected commutative algebraic groups} \label{sec:connected}
-
-%\input{connected-1}
-% !TEX encoding = UTF-8 Unicode
-%In this section we review a fundamental property of character
-%sheaves on geometrically connected, commutative algebraic groups over $\Fq$.
 
@@
 \begin{proof}
- %Let $G$ be a geometrically connected algebraic group over $\Fq$.
   Observe that the forgetful functor $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$
@@
   Then $b_G^*\qcs{L}_0 \iso \gqcs{L}$.
-  Since $b_G^*$ is full and faithful (again, see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} or even \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}),
+  Since $b_G^*$ is full and faithful (again, see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII}
+  or even \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}),
   $
@@
   $
-  is surjective because each character $\chi \in G(\Fq)^*$ determines a finite quasicharacter sheaf $(\Lang,\chi^{-1})$ such that the trace of Frobenius of the quasicharacter sheaf $B_G^* (L_G(\Lang,\chi^{-1}))$ is $\chi$.
+  is surjective because each character $\chi \in G(\Fq)^*$ determines a finite quasicharacter
+  sheaf $(\Lang,\chi^{-1})$ such that the trace of Frobenius of the quasicharacter sheaf
+  $B_G^* (L_G(\Lang,\chi^{-1}))$ is $\chi$.
 \end{proof}
@@
 with the conceptually simpler category $\QCf(G)$ of finite quasicharacter sheaves on $G$. 
-In this context, finite quasicharacter sheaves may also be apprehended as \emph{certain} $\ell$-adic characters of fundamental group $\pi_1(G,{\bar e})$. 
+In this context, finite quasicharacter sheaves may also be apprehended as
+\emph{certain} $\ell$-adic characters of fundamental group $\pi_1(G,{\bar e})$. 
 As explained in \cite{kamgarpour:09a}*{\S~2}, 
@@
 %\[\pi_1(G,{\bar e}) \to \Pi_\text{et}(G) \to \Pi_\text{et}(G)_{\Gal(\bFq/\Fq)} = \Pi_\text{disc}(G)\]
-From this it is apparent that the category of discrete isogenies to $G$ is a Galois category, in the sense of \cite{grothendieck:SGA1}*{Expos\'e V, \S 4}.
-Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$, as shown in \cite{kamgarpour:09a}*{App'x B}, this provides an alternate proof of $\QCiso{G} \to G(\Fq)^*$.
+From this it is apparent that the category of discrete isogenies to $G$ is a Galois category,
+in the sense of \cite{grothendieck:SGA1}*{Expos\'e V, \S 4}. Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$,
+as shown in \cite{kamgarpour:09a}*{App'x B}, this provides an alternate proof of $\QCiso{G} \to G(\Fq)^*$.
 
@@
 of $\Gal(\bFq/\Fq)$ on this (generally) infinite product of 
-Weil groups and difficult to identify the relevant quotient of this group. Viewed in this light, Definition~\ref{def:QC} is comparatively simple.
+Weil groups and difficult to identify the relevant quotient of this group.
+Viewed in this light, Definition~\ref{def:QC} is comparatively simple.
 
@@
 
-\'Etale group schemes form a counterpoint to connected groups, since the component group of a group scheme locally of finite type over $\Fq$ is an \'etale group scheme (locally of finite type) over $\Fq$ \cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
+\'Etale group schemes form a counterpoint to connected groups,
+since the component group of a group scheme locally of finite type over $\Fq$
+is an \'etale group scheme (locally of finite type) over $\Fq$
+\cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
 The functor $G \mapsto G(\bFq)$ defines an equivalence of categories
@@
     \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{\Fq}(x)} \rar{\alpha_{\Frob{\Fq}(x)}} & \gqcs{L'}_{\Frob{\Fq}(x)} \dar{\phi_x'}
-    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}& \arrow[swap]{d}{\mu} \gqcs{L}_{x+y} \rar{\alpha_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
+    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
+    & \arrow[swap]{d}{\mu} \gqcs{L}_{x+y} \rar{\alpha_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
     \gqcs{L}_x \rar{\alpha_x} & \gqcs{L'}_x
@@
 \begin{lemma}\label{lemma:section}
- If $\qcs{L}$ is a quasicharacter sheaf on a commutative, \'etale group scheme $G$ over $\Fq$ and if $G(\bFq)$ is finitely generated, then there is a global section $s = \{ s(x) \in \gqcs{L}_x \tq x \in G(\bFq) \}$ satisfying
+ If $\qcs{L}$ is a quasicharacter sheaf on a commutative, \'etale group scheme $G$
+ over $\Fq$ and if $G(\bFq)$ is finitely generated, then there is a global section
+ $s = \{ s(x) \in \gqcs{L}_x \tq x \in G(\bFq) \}$ satisfying
  \begin{equation}\label{section}
@@
   Using Lemma~\ref{lemma:section}, 
-  we may choose a section $s = \{ s(x) \in \gqcs{L}_x \tq x \in G(\bFq) \}$ satisfying \eqref{section}.  We will construct a group isomorphism between $\QCiso{G}$ and
+  we may choose a section $s = \{ s(x) \in \gqcs{L}_x \tq x \in G(\bFq) \}$ satisfying \eqref{section}.
+  We will construct a group isomorphism between $\QCiso{G}$ and
   $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ using $s$, then prove independence from the choice of $s$.
@@
   Suppose that $\qcs{L}$ and $\qcs{L}'$ are two quasicharacter sheaves on $G$.
-  If $s$ is a global section for $\qcs{L}$ and $s'$ for $\qcs{L}'$ then $s \otimes_{\EE}s'$ is a global section for
-  $\qcs{L} \otimes_{\EE}\qcs{L}'$.  The three versions of \eqref{t} for $\qcs{L}, \qcs{L'}$ and $\qcs{L} \otimes_{\EE}\qcs{L}'$ imply that
-  $\tau_{\qcs{L} \otimes_{\EE}\qcs{L}'}(\Frob{k}) = \tau_\qcs{L}(\Frob{k}) \tau_{\qcs{L}'}(\Frob{k})$, so \eqref{pich1} is a group homomorphism.
+  If $s$ is a global section for $\qcs{L}$ and $s'$ for $\qcs{L}'$ then $s \otimes_{\EE}s'$
+  is a global section for $\qcs{L} \otimes_{\EE}\qcs{L}'$.  The three versions of \eqref{t}
+  for $\qcs{L}, \qcs{L'}$ and $\qcs{L} \otimes_{\EE}\qcs{L}'$ imply that
+  $\tau_{\qcs{L} \otimes_{\EE}\qcs{L}'}(\Frob{k}) = \tau_\qcs{L}(\Frob{k}) \tau_{\qcs{L}'}(\Frob{k})$,
+  so \eqref{pich1} is a group homomorphism.
 
@@
 \section{On the cohomology of the dual of an etale group scheme} \label{sec:etalecohom}
-%\input{etale-2}
-%Define $\rho \colon \Hh^1(\Weil{\Fq}, \Hom(G(\bFq), \EEx))
-% \rightarrow \Hom(G(\Fq), \EEx)$ by $\rho(\phi)(g) =
-% \phi(\Frob)(g)$.
 
@@
   product of Dedekind domains.  Therefore $X$ decomposes into a direct
-  sum of cyclic $\ZZ[\Gamma_m]$-modules \cite{brandal:CommRingsFGModDecompose}, each of the \David{Add a section to this reference}
+  sum of cyclic $\ZZ[\Gamma_m]$-modules \cite{brandal:CommRingsFGModDecompose},
+  each of the \David{Add a reference to this section}
   form $\ZZ[\Gamma_m] / I$ for some ideal $I \subset \ZZ[\Gamma_m]$.
@@
 \begin{lemma}\label{lemma:ext}
-Every discrete isogeny (see Section~\ref{sec:finite}) to $G^0$ extends to a discrete isogeny to $G$ such that the component group of the covering space is isomorphic to the component group of $G$.
+Every discrete isogeny (see Section~\ref{sec:finite}) to $G^0$ extends to a discrete
+isogeny to $G$ such that the component group of the covering space is isomorphic
+to the component group of $G$.
 \end{lemma}
@@
   the functor $\Hom(\mbox{---}, A(\bFq))$ to $G^0(\bFq) \to G(\bFq) \to \pi_0(G)(\bFq)$:
-  $$\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)).$$
+  \[
+  \Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)).
+  \]
   We now show that $\Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)) = 0$.
@@
 
-We saw, in Proposition~\ref{prop:functorialG}, that the trace of Frobenius  $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
-Our main result regarding quasicharacter sheaves, below, shows that trace of Frobenius is an isomorphism in the case that we care about.
+We saw, in Proposition~\ref{prop:functorialG}, that the trace of Frobenius
+$\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
+Our main result regarding quasicharacter sheaves, below, shows that
+trace of Frobenius is an isomorphism in the case that we care about.
 
@@
 would be a $\ell$-adic local system on $1$ of rank-1, 
-thus an $\ell$-adic character $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with $\rho_1(\Frob{\Fq}) = \ell$. But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, 
+thus an $\ell$-adic character $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with
+$\rho_1(\Frob{\Fq}) = \ell$. But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, 
 while $\rho_1(\pi_1(1,{\bar 1}))$ is not compact in $\EEx$ (it contains $\ell^\ZZ$). 
@@
 We can play the same game with the character $\chi : G(\Fq) \to \EEx$ 
-defined by $\chi(1) = 1+\ell$.
-In this case, the corresponding quasicharacter sheaf $\qcs{L}$ is bounded, defined at $1$ by a pro-etale cover of $1$, but not finite, since $1+\ell$ is not a root of unity.
+defined by $\chi(1) = 1+\ell$. In this case, the corresponding quasicharacter sheaf $\qcs{L}$ is bounded,
+defined at $1$ by a pro-etale cover of $1$, but not finite, since $1+\ell$ is not a root of unity. 
 %
@@
 We write $\Hom_{< d}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $d$ 
-and $\Hom_{<\infty}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth; one might call these quasicharacters of $T(K)$, expanding on \cite{tate:67a}*{2.3}.
+and $\Hom_{<\infty}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth;
+one might call these quasicharacters of $T(K)$, expanding on \cite{tate:67a}*{2.3}.
 
@@
 and whose existence is given by \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch 10.1, Thm 6},
-is a separated, smooth, commutative group scheme locally of finite type over $\OK$ with generic fibre $T$, that enjoys the N\'eron mapping property:
+is a separated, smooth, commutative group scheme locally of finite type over $\OK$ with generic fibre $T$,
+that enjoys the N\'eron mapping property:
 if $S$ is a smooth scheme over $\OK$ then every morphism $S_\eta \to T$
@@
 \begin{definition}\label{def:GN}
-For each positive integer $d$, set $\TT_{d} \ceq \TT \times_\Spec{\OK} \Spec{\OK/\pK^d}$. Observe that $\OK/\pK^d$ is an Artin ring and $\TT_{d}$ is smooth and locally of finite type over $\OK/\pK^d$.
+For each positive integer $d$, set $\TT_{d} \ceq \TT \times_\Spec{\OK} \Spec{\OK/\pK^d}$.
+Observe that $\OK/\pK^d$ is an Artin ring and $\TT_{d}$ is smooth and locally of finite type over $\OK/\pK^d$.
 %
@@
 
-See \cite{greenberg:63a} and \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} and the first few sections of \cite{stasinski:12a} for background on the Greenberg functor.
-
-For each positive integer $d$, consider the canonical surjective ring homomorphisms $\OK/\pK^{d+1} \to \OK/\pK^d$ and the associated cartesian diagram of schemes 
+See \cite{greenberg:63a} and \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6}
+and the first few sections of \cite{stasinski:12a} for background on the Greenberg functor.
+
+For each positive integer $d$, consider the canonical surjective ring homomorphisms
+$\OK/\pK^{d+1} \to \OK/\pK^d$ and the associated cartesian diagram of schemes 
 \[
@@
 The map $\GN{T}_{d} \hookrightarrow \GN{T}_{d+1}$ is not a morphism of group schemes.
-There is, however, an epimorphism of group schemes $\GN{T}_{d+1} \to \GN{T}_{d}$ for which $\GN{T}_{d} \hookrightarrow \GN{T}_{d+1}$ is a section.
+There is, however, an epimorphism of group schemes $\GN{T}_{d+1} \to \GN{T}_{d}$ for
+which $\GN{T}_{d} \hookrightarrow \GN{T}_{d+1}$ is a section.
 
@@
    \labitem{(GN.0)}{dFq} $\GN{T}_d(\Fq) = \TT(\OK/\pK^d)$, canonically.
-  \labitem{(GN.1)}{GNd} $\GN{T}_d$ is a smooth, commutative group scheme, locally of finite type over $\Fq$, and the component group of $\GN{T}_d$ is geometrically finitely generated.
-(In fact, $\pi_0(\GN{T}_d) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$, and the latter is finitely generated by \cite{xarles:93a}.)
+  \labitem{(GN.1)}{GNd} $\GN{T}_d$ is a smooth, commutative group scheme,
+  locally of finite type over $\Fq$, and the component group of $\GN{T}_d$ is
+  geometrically finitely generated. (In fact, $\pi_0(\GN{T}_d) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$,
+  and the latter is finitely generated by \cite{xarles:93a}.)
   \labitem{(GN.2)}{d+1} 
@@
 is an isomomorphism. 
-Moreover, the isomorphism $\trFrob{T,d}$ is functorial in the following sense: $T \mapsto \trFrob{T,d}$ is a natural transformation between the following two additive functors
+Moreover, the isomorphism $\trFrob{T,d}$ is functorial in the following sense:
+$T \mapsto \trFrob{T,d}$ is a natural transformation between the following two additive functors
 \begin{enumerate}
@@
   Next we show that this isomorphism is functorial.
-The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor, while the second part shows that Trace of Frobenius is a natural transformation $t: F_1 \to F_2$.
-When further combined with Lemma~\ref{prop:product}, we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural transformation between additive functors.
+The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
+while the second part shows that Trace of Frobenius is a natural transformation
+$t: F_1 \to F_2$. When further combined with Lemma~\ref{prop:product},
+we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a
+natural transformation between additive functors.
 \end{proof}
@@
 
-The techniques in this paper apply to all non-archimdean local fields $K$ with residue field $k$, and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$ or on the ramification of $T$.
-Because of this, it is natural to ask if we can compare quasicharacter sheaves on $T$ and on $T'$ under conditions when there is a natural comparison between characters of $T(K)$ and of $T'(K')$.
-This comparison of has been made precise in \cite{chai-yu:01a}, building on ideas of \cite{deligne:84a}.
+The techniques in this paper apply to all non-archimdean local fields $K$ with residue field $k$,
+and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$
+or on the ramification of $T$. Because of this, it is natural to ask if we can compare
+quasicharacter sheaves on $T$ and on $T'$ under conditions when there is a
+natural comparison between characters of $T(K)$ and of $T'(K')$.
+This comparison of has been made precise in \cite{chai-yu:01a},
+building on ideas of \cite{deligne:84a}.
 
@@
 \end{equation}
-Note that if $T$ and $T'$ are $N$-congruent, then they are $N'$ congruent for every $N' \leq N$, the isomorphism \eqref{transfer} is depth-preserving at integers less than $N$.
-In this section we ask if the isomorphism \eqref{transfer} comes from an equivalence of categories of quasicharacter sheaves on $\GN{T}_d$ and those on $\GN{T}'_d$.
+Note that if $T$ and $T'$ are $N$-congruent, then they are $N'$ congruent for every
+$N' \leq N$, the isomorphism \eqref{transfer} is depth-preserving at integers less than $N$.
+In this section we ask if the isomorphism \eqref{transfer} comes from an equivalence of
+categories of quasicharacter sheaves on $\GN{T}_d$ and those on $\GN{T}'_d$.
 
@@
 As with the local Langlands correspondence for algebraic tori over local fields, 
-it will be possible to reduce the essential points of the argument to the case $T= \Gm{K}$, provided that the category of quasicharacter sheaves behaves properly with regard to Weil restriction; see \cite{yu:09a}*{Thm 7.5 (2)}.
+it will be possible to reduce the essential points of the argument to the case $T= \Gm{K}$,
+provided that the category of quasicharacter sheaves behaves properly with regard to
+Weil restriction; see \cite{yu:09a}*{Thm 7.5 (2)}. 
 The next proposition shows that the category of quasicharacter sheaves for 
@@
  In that case, our suspicions are all but confirmed 
- by the class field theory of Serre-Hazewinkel \citelist{\cite{serre:60a},\cite{serre:61a},\cite{demazure-gabriel:GroupesAlgebriques}*{Appendice}}, especially as revisited in \cite{suzuki-yoshida:12a}.
+ by the class field theory of Serre-Hazewinkel
+ \citelist{\cite{serre:60a},\cite{serre:61a},\cite{demazure-gabriel:GroupesAlgebriques}*{Appendice}},
+ especially as revisited in \cite{suzuki-yoshida:12a}. 
  What remains to be done is a careful comparison of 

### 2013-08-17 shanghai.tex
Add ~ to \refs

@@
 \]
-and show that it is an isomorphism in Theorem \ref{thm:snake}, assuming only
+and show that it is an isomorphism in Theorem~\ref{thm:snake}, assuming only
 that the geometric component group of $G$ is finitely generated.
@@
 Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^d}$; the commutative
-group scheme $\GN{T}_d$ plays the r\^{o}le of $G$.  Theorem \ref{thm:application}
+group scheme $\GN{T}_d$ plays the r\^{o}le of $G$.  Theorem~\ref{thm:application}
 allows us to translate characters $T(K)$ of depth less than $d$ into quasicharacter sheaves on $\GN{T}_d$:
@@
 We have not yet fully explored the applications of such a geometrization, but want to highlight
-some of the potential benefits of Theorem \ref{thm:application}.  Characters on $T$ have limited
+some of the potential benefits of Theorem~\ref{thm:application}.  Characters on $T$ have limited
 functoriality: they can be pulled back along maps to $T$, but it is less clear what to do with them
@@
 by Deligne \cite{deligne:SGA4.5}, and more recently Drinfeld has referred to such objects
-as character sheaves.  Our quasicharacter sheaves evolved from this notion, and Theorem \ref{thm:snake}
+as character sheaves.  Our quasicharacter sheaves evolved from this notion, and Theorem~\ref{thm:snake}
 is a direct generalization of the sheaf-function dictionary to the case of commutative
@@
 We close the introduction with a more detailed description of the structure of this paper.
-In Section \ref{sec:category} we define quasicharacter sheaves and give an interpretation of
+In Section~\ref{sec:category} we define quasicharacter sheaves and give an interpretation of
 them as Weil sheaves with a Galois action.
-Section \ref{sec:Frob} introduces the trace of Frobenius homomorphism,
+Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism,
 one direction of the sheaf-function dictionary.
-We define pullbacks and products of quasicharacter sheaves in Section \ref{sec:pullback}, and use
+We define pullbacks and products of quasicharacter sheaves in Section~\ref{sec:pullback}, and use
 them to prove a functoriality result on the trace of Frobenius.
-In Section \ref{sec:basechange} we study how quasicharacter sheaves behave under base change
+In Section~\ref{sec:basechange} we study how quasicharacter sheaves behave under base change
 and Weil restriction.
-Sections \ref{sec:bounded} and \ref{sec:finite} describe bounded and finite quasicharacter sheaves,
+Sections~\ref{sec:bounded} and \ref{sec:finite} describe bounded and finite quasicharacter sheaves,
 two subcategories of $\QC(G)$.  These alternate descriptions of quasicharacter sheaves play a key
-role in the proof of Proposition \ref{prop:restriction}.
+role in the proof of Proposition~\ref{prop:restriction}.
 In section \ref{sec:connected} we show that bounded and finite quasicharacter sheaves are the same
 as standard quasicharacter sheaves when $G$ is connected, and that trace of Frobenius is an isomorphism.
-We shift to \'etale group schemes $G$ in Section \ref{sec:etale} and give a more concrete interpretation
+We shift to \'etale group schemes $G$ in Section~\ref{sec:etale} and give a more concrete interpretation
 of quasicharacter sheaves in this case.  Using a notion of global sections for quasicharacter sheaves,
 we give an isomorphism between $\QCiso{G}$ and $\Hh^1(\Weil{\Fq}, \Hom(G(\bFq), \EEx))$.
-Section \ref{sec:etalecohom} proves a result in Galois cohomology that shows that trace of Frobenius is
+Section~\ref{sec:etalecohom} proves a result in Galois cohomology that shows that trace of Frobenius is
 an isomorphism for \'etale group schemes.
-In Section \ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
+In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
 induces an essentially surjective functor of quasicharacter sheaves.
-Section \ref{sec:snake} closes out Part \ref{part1} with the proof of the main theorem, that trace of Frobenius
+Section~\ref{sec:snake} closes out Part \ref{part1} with the proof of the main theorem, that trace of Frobenius
 is an isomorphism for $G$ as long as the geometric component group is finitely generated.
 
-In Section \ref{sec:GN} we introduce N\'eron models of tori and the Greenberg transform, which produce
+In Section~\ref{sec:GN} we introduce N\'eron models of tori and the Greenberg transform, which produce
 group schemes over $\Fq$ from algebraic tori $T$ over $K$.
-Section \ref{sec:bdchar} then uses Theorem \ref{thm:snake} to give a geometrization of characters of $T$
+Section~\ref{sec:bdchar} then uses Theorem~\ref{thm:snake} to give a geometrization of characters of $T$
 of bounded depth.
-We give a reinterpretation of this result in Section \ref{sec:quasichar}, using a limit process to simultaneously
-geometrize all quasicharacters of $T$.  Sections \ref{sec:bdchar} and \ref{sec:quasichar} also include
+We give a reinterpretation of this result in Section~\ref{sec:quasichar}, using a limit process to simultaneously
+geometrize all quasicharacters of $T$.  Sections~\ref{sec:bdchar} and \ref{sec:quasichar} also include
 functoriality results that we hope to use in a future discussion of class field theory.
-Finally, we close the paper in Section \ref{sec:transfer} by discussing a transfer principle, which allows
+Finally, we close the paper in Section~\ref{sec:transfer} by discussing a transfer principle, which allows
 a geometric transfer of characters between characteristic $p$ tori to characteristic $0$ tori.
@@
  determined by $\alpha, \beta$ and $\phi$.
-Combining this with Theorem \ref{thm:application} gives the geometrization and categorification of the transfer of characters.
+Combining this with Theorem~\ref{thm:application} gives the geometrization and categorification of the transfer of characters.
 
@@
 on the Greenberg transform of the N\/eron model of $T$ 
-determine admissible characters of $T(K)$, and vice versa, functorially. When coupled with the reciprocity map $\text{rec}_T $ for $T$, 
+determine admissible characters of $T(K)$, and vice versa, functorially.
+When coupled with the reciprocity map $\text{rec}_T $ for $T$, 
 which enjoys the same functorial properties, 

### 2013-08-17 shanghai.tex
sheaf-function -> sheaf--function

@@
 the set of isomorphism classes $\QCiso{G}$ forms a group.
-Motivated by the sheaf-function dictionary for commutative, connected
+Motivated by the sheaf--function dictionary for commutative, connected
 algebraic groups \cite{deligne:SGA4.5}, we explore the trace of Frobenius morphism
@@
 as character sheaves.  Our quasicharacter sheaves evolved from this notion, and Theorem~\ref{thm:snake}
-is a direct generalization of the sheaf-function dictionary to the case of commutative
+is a direct generalization of the sheaf--function dictionary to the case of commutative
 group schemes which are not necessarily connected or finite type.  The other main use
@@
 Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism,
-one direction of the sheaf-function dictionary.
+one direction of the sheaf--function dictionary.
 We define pullbacks and products of quasicharacter sheaves in Section~\ref{sec:pullback}, and use
@@
 The main result of Part~\ref{part1} of this paper, 
-the sheaf-function dictionary for $G$ Theorem~\ref{thm:snake}, has a hypothesis: 
+the sheaf--function dictionary for $G$ Theorem~\ref{thm:snake}, has a hypothesis: 
 the smooth commutative group scheme locally of finite type must have the 
@@
 satisfying \eqref{section}, then the conclusion of Theorem~\ref{thm:snake} holds for $G$,
-so there is a sheaf-function dictionary for $G$.
+so there is a sheaf--function dictionary for $G$.
 
@@
 
-\section{The sheaf-function dictionary for non-connected groups}
+\section{The sheaf--function dictionary for non-connected groups}
 \label{sec:snake}
@@
 
-\section{A sheaf-function dictionary for tori over local fields} \label{sec:quasichar}
+\section{A sheaf--function dictionary for tori over local fields} \label{sec:quasichar}
 

### 2013-08-17 shanghai.tex
More specific citations

@@
 Motivated by the sheaf--function dictionary for commutative, connected
-algebraic groups \cite{deligne:SGA4.5}, we explore the trace of Frobenius morphism
+algebraic groups \cite{deligne:SGA4.5},\David{more specific citation} we explore the trace of Frobenius morphism
 \[
@@
 Analogous sheaves on connected, commutative algebraic groups were first studied
-by Deligne \cite{deligne:SGA4.5}, and more recently Drinfeld has referred to such objects
+by Deligne \cite{deligne:SGA4.5}, \David{more specific citation} and more recently Drinfeld has referred to such objects
 as character sheaves.  Our quasicharacter sheaves evolved from this notion, and Theorem~\ref{thm:snake}
@@
 group schemes which are not necessarily connected or finite type.  The other main use
-of the term ``character sheaf'' traces back to Lusztig \cite{lusztig:85a}.  Most of his energy is devoted to
+of the term ``character sheaf'' traces back to Lusztig \cite{lusztig:85a}*{Def.~2.10}.  Most of his energy is devoted to
 handling non-commutative groups; though he does define character sheaves for some
@@
 The category $\QC(G)$ of quasicharacter sheaves on $G$ is a rigid symmetric monoidal category
-\cite{etingof:09a} under the tensor product
+\cite{etingof:09a}*{\S~1.10} under the tensor product
 $\qcs{L} \otimes \qcs{L'} \ceq (\gqcs{L}\otimes\gqcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
@@
 The category of characters sheaves on $G$ is not abelian, so $\QC(G)$
-is not a tensor category in the sense of \cite{deligne:02a}.
+is not a tensor category in the sense of \cite{deligne:02a}. \David{more specific citation}
 This rigid monoidal category structure for $\QC(G)$ puts a group
@@
   product of Dedekind domains.  Therefore $X$ decomposes into a direct
-  sum of cyclic $\ZZ[\Gamma_m]$-modules \cite{brandal:CommRingsFGModDecompose},
+  sum of cyclic $\ZZ[\Gamma_m]$-modules \cite{brandal:CommRingsFGModDecompose}, \David{more specific citation}
   each of the \David{Add a reference to this section}
@@
   geometrically finitely generated. (In fact, $\pi_0(\GN{T}_d) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$,
-  and the latter is finitely generated by \cite{xarles:93a}.)
+  and the latter is finitely generated by \cite{xarles:93a}*{2.18}.)
   \labitem{(GN.2)}{d+1} 
@@
 natural comparison between characters of $T(K)$ and of $T'(K')$.
-This comparison of has been made precise in \cite{chai-yu:01a},
+This comparison of has been made precise in \cite{chai-yu:01a}, \David{more specific citation?}
 building on ideas of \cite{deligne:84a}.
@@
  \citelist{\cite{serre:60a},\cite{serre:61a},\cite{demazure-gabriel:GroupesAlgebriques}*{Appendice}},
- especially as revisited in \cite{suzuki-yoshida:12a}. 
+ especially as revisited in \cite{suzuki-yoshida:12a}*{\S~2}. 
  What remains to be done is a careful comparison of 

### 2013-08-17 shanghai.tex
Biblio style updates
More improvements to Greenberg of Neron.

@@
 
+We will also need the Greenberg functor, 
+introduced in \cite{greenberg:61} and \cite{greenberg:63a}, 
+as functor from the category of schemes locally of finite type 
+over an Artinian local ring $A$ with perfect residue field $k$ 
+to the category of schemes locally of finite type over $k$. 
+This functor enjoys many pleasing properties: 
+it respects open immersions, closed immersions, 
+etale morphisms and smooth morphisms. 
+Besides Greenberg's original papers, 
+see \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} 
+and the first few sections of \cite{stasinski:12a} 
+for background on the Greenberg functor. 
+Let
+\[
+%\begin{tikzcd}
+\Gr_d : \left( \text{Schemes} \atop \text{lft over $\OK$}\right) \to \left( \text{Schemes} \atop \text{lft over $\OK$}\right)
+%\end{tikzcd}
+\]
+be the functor produced by precomposing pull-back along $\OK \to \OK/\pK^d$ with the Greenberg functor.
+
 \begin{definition}\label{def:GN}
@@
 \end{definition}
-
-See \cite{greenberg:63a} and \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6}
-and the first few sections of \cite{stasinski:12a} for background on the Greenberg functor.
 

### 2013-08-17 shanghai.tex
Various minor fixes

--- 2013-08-17 shanghai.tex
@@
 \usepackage[alphabetic]{amsrefs}
+\newcommand\SortNoop[1]{}
+\DeclareRobustCommand{\VAN}[3]{#2}
+%\usepackage{amsrefs}
 \renewcommand\MR{\relax}
@@
 \tableofcontents
+\David{Search for = which should be \ceq}
+\David{Search for terms defined after they are used}
 
@@
 $\Weil{\Fq}\subset \Gal(\bFq/\Fq)$ is the subgroup generated by $\Frob{\Fq}$.
-Let $\Frob{G} := \id_{G} \times \Frob{\Fq}$ be the Frobenius automorphism of $\bG$.
+Let $\Frob{G} \ceq \id_{G} \times \Frob{\Fq}$ be the Frobenius automorphism of $\bG$.
 
@@
 $\qcs{L} \otimes \qcs{L'} \ceq (\gqcs{L}\otimes\gqcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
-with duals given by applying the sheaf-hom functor 
+with duals given by applying the sheaf hom functor 
 $\sheafHom(\ - \ ,\EE)$.
-The category of characters sheaves on $G$ is not abelian, so $\QC(G)$
+The category of quasicharacter sheaves on $G$ is not abelian, so $\QC(G)$
 is not a tensor category in the sense of \cite{deligne:02a}. \David{more specific citation}
@@
 \begin{definition}\label{def:trFrob}
-Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. on constructible $\ell$-adic sheaf on $\bG$. Every $g\in G(\Fq)$
+Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
 determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$ and
@@
 \]
-If $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf, 
+If $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf
 then we will abbreviate $\trFrob{(\gqcs{L},\phi)}$ to $\trFrob{\qcs{L}}$.
@@
 
-The isomorphism $\mu : \bm^* \gqcs{L} \to \LxL$ guarantees 
+The isomorphism $\mu : \bm^* \gqcs{L} \to \LxL$ together with property~\ref{CS.2} guarantee
 that the function $\trFrob{\qcs{L}} : G(\Fq)\to \EEx$ is a group homomorphism.
@@
 \]
-This isomorphism is functorial, in the following sense.
+This isomorphism is functorial in the following sense:
 
@@
 Trace of Frobenius $\QCiso{G} \to G(\Fq)$ is a natural transformation 
-between the following two additive functors 
+between the two additive functors 
 \begin{enumerate}
@@
   Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We start by showing that
-  $\bf^*\gqcs{L}$ is locally constant on connected components of
-  $\bH$. Let $c_j :\bH^j \hookrightarrow \bH$ be any
+  $\bf^*\gqcs{L}$ is a local system of rank~$1$. Let $c_j :\bH^j \hookrightarrow \bH$ be any
   connected component and let $i$ be the image of $j$ under the group
-  homomorphism $\pi_0(\bG) \to \pi_0(\bH)$ obtained by
-  applying the functor $\pi_0$ to $\bf$; see \cite{vdGeer-Moonen:AbelianVarieties}*{III, 3.28}, for example.
+  homomorphism $\pi_0(\bf) : \pi_0(\bH) \to \pi_0(\bG)$.
   Write $c_i : \bG^i \hookrightarrow \bG$ for
   the inclusion of $\bG^i$ and $\bf^j : \bH^j \to \bG^i$
-  for the restriction of $f$ to $\bH^j$.  Since $\qcs{L}$
-  is a quasicharacter sheaf, $\gqcs{L}$ is locally constant on the connect
-  components of $\bG$; thus, there is a finite etale covering
+  for the restriction of $f$ to $\bH^j$.  Since $\gqcs{L}$ is locally constant on the connected
+  components of $\bG$, there is a finite \'etale covering
   $a_i : X_i \to \bG^i$ such that $a_i^* (\gqcs{L}\vert_{\bG^i})$
   is constant. Let $b_j : Y_j \to \bH^j$ be the
-  pull-back of $a_i$ along $\bf^j$; let $g_j : Y_j \to X_i$ be
-  the map opposite $\bf^j$. Then $b_j$ is a finite etale covering
+  pull-back of $a_i$ along $\bf^j$ and let $g_j : Y_j \to X_i$ be
+  the map opposite $\bf^j$. Then $b_j$ is a finite \'etale covering
   of $\bH^j$ and
@@
 \end{equation}
-Since $\pi_0(G)$ is an commutative group scheme, smooth (in fact, etale) and locally of finite type over $\Fq$, 
+Since $\pi_0(G)$ is an commutative group scheme, smooth (in fact, \'etale) and locally of finite type over $\Fq$, 
 it follows from Proposition~\ref{prop:pullback} that \eqref{eq:pi-1} defines a sequence of functors
@@
 Let us say that $f : H\to G$ is a \emph{discrete isogeny} if it is a a finite, surjective
-etale morphism and a morphism of commutative group $\Fq$-schemes, for which
-the action of $\Gal(\bFq/\Fq)$ on the etale group scheme $f^{-1}{\bar e}$ is trivial.
+\'etale morphism and a morphism of commutative group $\Fq$-schemes, for which
+the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $f^{-1}{\bar e}$ is trivial.
 An object in $C(G)$ is a pair $(f,\psi)$ where: 
@@
  Since $U$ is an isomorphism, we may replace $V'$ with $V$ and $U$ with $\id_V$, without loss of generality. 
- Then the equivariance condition on $U$ becomes $\psi' = \psi\circ \beta$ on the finite etale group scheme $\ker f'$. 
- Since $f$ and $f'$ are finite etale, and $f' = f\circ \beta$, and $\beta$ is surjective,
- $\beta$ is an etale cover; therefore, $\beta$ admits a section $\beta' : H \to H'$.
+ Then the equivariance condition on $U$ becomes $\psi' = \psi\circ \beta$ on the finite \'etale group scheme $\ker f'$. 
+ Since $f$ and $f'$ are finite \'etale, and $f' = f\circ \beta$, and $\beta$ is surjective,
+ $\beta$ is an \'etale cover; therefore, $\beta$ admits a section $\beta' : H \to H'$.
  This provides the inverse to $L(\beta,U) : L(f,\psi) \to L(f',\psi')$.
@@
 %In this section we establish a fundamental property of character
-% sheaves on commutative etale group schemes over $\Fq$ that are
+% sheaves on commutative \'etale group schemes over $\Fq$ that are
 % geometrically finitely generated.
@@
 that is, if $G$ is any smooth connected group scheme locally of finite type over $\Fq$
-and if each quasicharacter sheaf on the etale group scheme $\pi_0(G)$ admits a global section 
+and if each quasicharacter sheaf on the \'etale group scheme $\pi_0(G)$ admits a global section 
 satisfying \eqref{section}, then the conclusion of Theorem~\ref{thm:snake} holds for $G$,
@@
 
-\section{On the cohomology of the dual of an etale group scheme} \label{sec:etalecohom}
+\section{On the cohomology of the dual of an \'etale group scheme} \label{sec:etalecohom}
 
@@
   where $A$ and $B$ are arbitrary $\ZZ[\Gamma]$-modules.  Since $H_m$ acts trivially on $I$,
-  $I_{H_m}A := \langle (\gamma-1)a : \gamma \in H_m, a \in A \rangle \subseteq \ker(a).$
+  $I_{H_m}A \ceq \langle (\gamma-1)a : \gamma \in H_m, a \in A \rangle \subseteq \ker(a).$
   Since $B / I_{H_m}B \cong B \otimes_A A / I_{H_m}A$, we get
@@
 %
-Consider the case when $G$ is the discrete etale group scheme $\ZZ$. 
+Consider the case when $G$ is the discrete \'etale group scheme $\ZZ$. 
 Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ 
@@
 defined by $\chi(1) = 1+\ell$. In this case, the corresponding quasicharacter sheaf $\qcs{L}$ is bounded,
-defined at $1$ by a pro-etale cover of $1$, but not finite, since $1+\ell$ is not a root of unity. 
+defined at $1$ by a pro-\'etale cover of $1$, but not finite, since $1+\ell$ is not a root of unity. 
 %
@@
 
-\bibliographystyle{plain}
+\DeclareRobustCommand{\VAN}[3]{#3}
 \bibliography{Biblio}

### 2013-08-17 shanghai.tex
Working on section 3

@@
 
+\David{insert some commentary on this proposition: it will be very useful to us}
+
 \begin{proposition}\label{prop:pullback}
@@
 
-  Since $a_i^* (\gqcs{L}\vert_{\bG^i})$ is a constant sheaf and since the pull-back
-  of a constant sheaf (along $g_j$, in this case) is a constant sheaf,
-  it follows that $b_j^* \left( (\bf^*\gqcs{L})\vert_{\bH^j}\right)$
-  is a constant sheaf. Thus, $\bf^*\gqcs{L}$ is locally constant on
+  Since $a_i^* (\gqcs{L}\vert_{\bG^i})$ is a constant sheaf, its pullback
+  $b_j^* \left( (\bf^*\gqcs{L})\vert_{\bH^j}\right)$ along $g_j$ is also constant.
+  Thus $\bf^*\gqcs{L}$ is locally constant on
   $\bH^j$. Since $(\bf^*\gqcs{L})_{\bg} = \gqcs{L}_{f(\bg)}$ for every
@@
 
-  To see that $(\bfxf)^* \gqcs{L}$ satisfies
-  condition \ref{CS.1} simply apply the functor $(\bfxf)^*$
+  To see that $(\bfxf)^* \mu$ satisfies
+  condition \ref{CS.1}, apply the functor $(\bfxf)^*$
   to \ref{CS.1} for $\qcs{L}$ and use the canonical isomorphism
-  $(\bfxf)^*(\LxL) \iso \bf^*\gqcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gqcs{L}$
-  (a few times). Likewise, to see that $\bf^*\gqcs{L}$ satisfies condition
-  \ref{CS.2}, apply the same functor to \ref{CS.2} for $\gqcs{L}$.
-  Then use the fact that $f$ is defined over $\Fq$, so
-  $(\bfxf)^*\Frob{\GxxG}^* \iso \Frob{\GxxG}^* (\bfxf)^*$,
-  and the fact that $f$ is a morphism of group schemes, so
-  $(\bfxf)^* \bm^*\iso \bm^* \bf^*$
-  (isomorphisms of functors on constructible sheaves).
-
-  To see that $(\gqcs{L},\mu,\phi) \mapsto (\bf^*\gqcs{L},(\bfxf)^*\mu,\bf^*F)$
-  defines a functor $f^* : \QC(G) \to \QC(H)$ one applies the functors $\bf^*$ and
-  $\bf^*\tight{1}{\times}{1}\bf^*$ to \ref{CS.3} and argue as
-  above. It follows from the fact that sheaf hom commutes with these
-  functors that $f^* : \QC(G) \to \QC(H)$ is a monoidal functor.
+  $(\bfxf)^*(\LxL) \iso \bf^*\gqcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gqcs{L}$.
+  To show that $f^*\qcs{L}$ satisfies condition
+  \ref{CS.2}, apply the same functor to \ref{CS.2} for $\qcs{L}$.
+  The fact that $f$ is a morphism of group schemes defined over $\Fq$ then
+  yields isomorphisms $(\bfxf)^*\Frob{\GxxG}^* \iso \Frob{\GxxG}^* (\bfxf)^*$
+  and $(\bfxf)^* \bm^*\iso \bm^* \bf^*$ between functors of constructible sheaves.
+
+  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{CS.3} allows the application
+  of $f^*$ to morphisms of quasicharacter sheaves; arguing as above shows that $f^*$ is
+  a functor from $\QC(G)$ to $\QC(H)$.  Since tensor products commute with pullback
+  $f^* : \QC(G) \to \QC(H)$ is a monoidal functor.
 %
-  The fact that the functor $f^* : \QC(G) \to \QC(H)$ commutes with
-  the trace of Frobenius, in the sense above, follows immediately from
-  the definitions; see \cite{laumon:87a}*{1.1.1.2}, where the ambient
+  The diagram relating $f^* : \QC(G) \to \QC(H)$, $f^* : G(k)^* \to H(k)^*$ and trace of Frobenius
+  commutes by \cite{laumon:87a}*{1.1.1.2}, where the ambient
   hypothesis that $X$ is of finite type over $\Fq$ can be replaced by
@@
   Finally, the fact that $(f\circ g)^* = g^* \circ f^*$ follows from the analogous
-  statements about the pullbacks functor on $\ell$-adic constructible sheaves.
- % \David{Is this explanation of $(f\circ g)^* = g^* \circ f^*$ sufficient?}
+  statements about the pullback functor on $\ell$-adic constructible sheaves.
 \end{proof}

### 2013-08-17 shanghai.tex
Still working on the penultimate section.

--- 2013-08-17 shanghai.tex
@@
 be the functor obtained by pull-back along the canonical closed immersion of $k$-schemes
-$\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$ \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}. 
+$\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$
+\cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}. 
 The following diagram commutes:
@@
 introduced in \cite{greenberg:61} and \cite{greenberg:63a}, 
-as functor from the category of schemes locally of finite type 
-over an Artinian local ring $A$ with perfect residue field $k$ 
+as a functor from the category of schemes locally of finite type 
+over an Artinian local ring with perfect residue field $k$ 
 to the category of schemes locally of finite type over $k$. 
-This functor enjoys many pleasing properties: 
-it respects open immersions, closed immersions, 
+This functor respects open immersions, closed immersions, 
 etale morphisms and smooth morphisms. 
@@
 %\begin{tikzcd}
-\Gr_d : \left( \text{Schemes} \atop \text{lft over $\OK$}\right) \to \left( \text{Schemes} \atop \text{lft over $\OK$}\right)
+\Gr_d : \left( \text{Schemes} \atop \text{lft over $\OK$}\right) \to \left( \text{Schemes} \atop \text{lft over $\Fq$}\right)
 %\end{tikzcd}
@@
 be the functor produced by precomposing pull-back along $\OK \to \OK/\pK^d$ with the Greenberg functor.
-
-\begin{definition}\label{def:GN}
-For each positive integer $d$, set $\TT_{d} \ceq \TT \times_\Spec{\OK} \Spec{\OK/\pK^d}$.
-Observe that $\OK/\pK^d$ is an Artin ring and $\TT_{d}$ is smooth and locally of finite type over $\OK/\pK^d$.
-%
-Let $\GN{T}_{d} = \Gr(\TT_d)$ be the group scheme over $\Fq$ produced by applying
-the Greenberg functor to $\TT_{d}$; this is the \emph{Greenberg transform of $\TT_d$}.
-\end{definition}
-
-For each positive integer $d$, consider the canonical surjective ring homomorphisms
-$\OK/\pK^{d+1} \to \OK/\pK^d$ and the associated cartesian diagram of schemes 
-\[
-\begin{tikzcd}
-\Spec{\OK/\pK^d} \arrow[hook]{rr} && \Spec{\OK/\pK^{d+1}} \arrow[hook]{r} & \Spec{\OK} \\
- \arrow{u} \TT_{d} \arrow[hook]{rr} & \ \arrow[Rightarrow]{d}{\text{Greenberg functor}} & \arrow{u} \TT_{d+1}  &  \\
-\GN{T}_{d} \arrow[hook]{rr} & \ & \GN{T}_{d+1}  \arrow{r} & \Spec{k}
-\end{tikzcd}
-\]
-The map $\GN{T}_{d} \hookrightarrow \GN{T}_{d+1}$ is not a morphism of group schemes.
-There is, however, an epimorphism of group schemes $\GN{T}_{d+1} \to \GN{T}_{d}$ for
-which $\GN{T}_{d} \hookrightarrow \GN{T}_{d+1}$ is a section.
-
-The fundamental properties of $\GN{T}_d$ that we need are:
+The surjective ring homomorphism $\OK/\pK^{d+1} \to \OK/\pK^d$ determines a natural transformation $P_{d} : \Gr_{d+1} \to \Gr_d$. 
+%\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}.
+
+For any positive integer $d$ set $\GN{T}_d = \Gr_d(\TT)$ and $f_d = P_d(\TT)$.
+The fundamental properties of $f_d : \GN{T}_{d+1} \to \GN{T}_d$ that we need are:
  \begin{enumerate}
@@
   and the latter is finitely generated by \cite{xarles:93a}*{2.18}.)
-  \labitem{(GN.2)}{d+1} 
+  \labitem{(GN.2)}{truncation}
+  The morphism $f_d : \GN{T}_{d+1} \to \GN{T}_d$ is a surjective morphism of group schemes.
   \end{enumerate}
+
+We remark that $f_d : \GN{T}_{d+1} \to \GN{T}_d$ is not induced from a morphism of Néron models.
 
@@
 
+By Proposition~\ref{prop:pullback}, the surjective morphism $f_d : \GN{T}_{d+1}\to \GN{T}_d$ of group schemes induces a functor
+\[
+f_d^* : \QC(\GN{T}_d) \to \QC(\GN{T}_{d+1}).
+\]
+\begin{proposition}
+The functor $f_d^* : \QC(\GN{T}_d) \to \QC(\GN{T}_{d+1})$ is full and faithful.
+\end{proposition}
+
+\begin{proof}
+\Clifton{Under construction}
+Base change along $\OK/\pK^{d+1} \to \OK/\pK^d$ determines a closed immersion $\TT_{d+1} \hookrightarrow \TT_d$, though not a morphism of group schemes.
+Applying the Greenberg functor produces a closed immersion $i_d : \GN{T}_{d} \hookrightarrow \GN{T}_{d+1}$.
+Although $i_d$ is not a morphism of group schemes, it is a section of $f_d : \GN{T}_{d+1}\to \GN{T}_d$.
+\end{proof}
+
+Let $\QC(\GN{T})$ be the category of ind-objects from the full subcategories $\QC(\GN{T}_d)$. 
+Objects in $\QC(\GN{T})$ are equivalence classes of objects from $\QC(\GN{T}_d)$ under the equivalence relation that identifies 
+$\qcs{L}_1\in \QC(\GN{T}_{d_1})$ with $\qcs{L}_2\in \QC(\GN{T}_{d_2})$ 
+if $f_1^*\qcs{L}_1 = f_2^*\qcs{L}_2$  in $\QC(\GN{T}_{\max\{d_1,d_2\}})$,
+where $f_1 : \GN{T}_{\max\{d_1,d_2\}} \to \GN{T}_{d_1}$ 
+(resp. $f_2 : \GN{T}_{\max\{d_1,d_2\}} \to \GN{T}_{d_2}$) 
+is obtained by composing the maps $f_{d_1}, \cdots , f_{\max\{d_1,d_2\}}$ 
+(resp. $f_{d_2}, \cdots , f_{\max\{d_1,d_2\}}$).
+A map $\alpha : \qcs{F} \to \qcs{F}'$
+
+We refer to objects of $\QC(\GN{T})$ as \emph{quasicharacter sheaves for $T$}.
+
 \begin{definition}
-The \emph{Greenberg transform of the N\'eron model of $T$} is the group pro-scheme over $\Fq$ given by
+The \emph{Greenberg transform of the N\'eron model of $T$} is the pro-group scheme over $\Fq$ given by
 \begin{equation}\label{projlim}
@@
 \end{equation}
-\end{definition}
-
-\begin{remark}
-The Greenberg transform of the N\'eron model of $T$ is a commutative group scheme over $\Fq$. 
-We will not use that fact in this paper. 
-\end{remark}
-
-\begin{definition}
-Let$\QC(\GN{T})$ be the ind-category $\varinjlim_{d\in \ZZ_{>0}} \QC(\GN{T}_d)$;
-we refer to objects of $\QC(\GN{T})$ as \emph{quasicharacter sheaves for $T$}.
 \end{definition}
@@
 \end{corollary}
+
+\begin{proof}
+Show $\QCiso{\GN{T}} = \varinjlim_{d\in \ZZ_{>0}} \QCiso{\GN{T}_d}$, then invoke Theorem~\ref{thm:application}.
+\end{proof}
 

### 2013-08-17 shanghai.tex
Relabeling some equations, add a todo, etc

--- 2013-08-17 shanghai.tex
@@
 \begin{abstract}
-  We introduce and study the category of quasicharacter sheaves on smooth commutative
-  group schemes $G$ locally of finite type over finite fields
+  We introduce and study the category of quasicharacter sheaves on smooth,
+  commutative group schemes $G$ locally of finite type over finite fields
   $\Fq$. Assuming that the geometric component group of $G$
@@
 What is a quasicharacter sheaf?
-Let $G$ be a smooth commutative group scheme locally of finite
+Let $G$ be a smooth, commutative group scheme locally of finite
 type over a finite field $\Fq$; $G$ need not be reductive, connected, or of
@@
 \David{Search for terms defined after they are used}
+\David{Commas between adjectives, consistent ordering}
 
@@
 
-Throughout this paper, $G$ is a smooth commutative group scheme locally of finite type
+Throughout this paper, $G$ is a smooth, commutative group scheme locally of finite type
 over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.
@@
 group scheme for $G$:
-\begin{equation}\label{eq:pi-2}
+\begin{equation}\label{eq:pi0}
 \begin{tikzcd}
@@
 \end{equation}
-Since $\pi_0(G)$ is an commutative group scheme, smooth (in fact, \'etale) and locally of finite type over $\Fq$, 
-it follows from Proposition~\ref{prop:pullback} that \eqref{eq:pi-1} defines a sequence of functors
+Since $\pi_0(G)$ is an commutative group scheme, smooth and locally of finite type over $\Fq$, 
+Proposition~\ref{prop:pullback} implies that \eqref{eq:pi0} defines a sequence of functors
 \[
@@
 which induces, upon passage to isomorphism classes of objects, a sequence of group homomorphisms 
-\begin{equation}\label{eq:pi-1}
+\[
 \begin{tikzcd}
@@
 \end{tikzcd}
-\end{equation}
-It is easy to see that $\QCiso{0}$ is trivial. In this paper we will find $\QCiso{G^0}$
+\]
+It is easy to see that $\QCiso{0}$ is trivial. In Sections~\ref{sec:connected} and  we will find $\QCiso{G^0}$
 and $\QCiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; 
@@
 
+\begin{corollary}
+ If $G$ is a commutative, \'etale algebraic group over $\Fq$ and $G(\bFq)$ is finitely
+ generated then
+  \[
+  \trFrob{G} : \QCiso{G} \to G(\Fq)^*
+  \]
+  is an isomorphism of groups.
+\end{corollary}
+
 \section{Restriction to the identity component} \label{sec:restriction}
@@
 \begin{proof}
-  Because $G$ is smooth over $\Fq$, the identity component, 
-  $G^0$, is a connected algebraic group over $\Fq$, 
+  The identity component $G^0$ of $G$ is a connected algebraic group over $\Fq$, 
   clopen in $G$ \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}. 
@@
 \begin{proof}
-  Consider the short exact sequence in the category of smooth group
+  Recall the short exact sequence \eqref{eq:pi0} in the category of smooth group
   schemes, locally of finite type over $\Fq$, defining the component
   group scheme for $G$:
-  \begin{equation}\label{eq:pi0}
+  \[
   \begin{tikzcd}
@@
   \end{tikzcd}
-  \end{equation}
+  \]
   Let
@@
   be the commutative diagram of abelian groups obtained by applying
-  Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.  By
-  Proposition~\ref{prop:connected}, $\ker \trFrob{G^0} =0$ and $\coker \trFrob{G^0}=0$.
+  Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.  Since $G^0$ is a connected algebraic group
+  \cite{vdGeer-Moonen:AbelianVarieties}*{3.17},
+  Proposition~\ref{prop:connected} implies that $\ker \trFrob{G^0} =0$ and $\coker \trFrob{G^0}=0$.
   By Propositions~\ref{prop:etale} and \ref{prop:X}, $\ker \trFrob{\pi_0(G)}=0$
@@
   abelian groups
-  \begin{equation}\label{eq:pi1}
+  \begin{equation}\label{eq:pi0k}
   \begin{tikzcd}

### 2013-08-17 shanghai.tex

@@
 
-\begin{definition}\label{def:GN}
-For each positive integer $d$, set $\TT_{d} \ceq \TT \times_\Spec{\OK} \Spec{\OK/\pK^d}$.
-Observe that $\OK/\pK^d$ is an Artin ring and $\TT_{d}$ is smooth and locally of finite type over $\OK/\pK^d$.
-%
-Let $\GN{T}_{d} = \Gr(\TT_d)$ be the group scheme over $\Fq$ produced by applying
-the Greenberg functor to $\TT_{d}$; this is the \emph{Greenberg transform of $\TT_d$}.
-\end{definition}
-
-See \cite{greenberg:63a} and \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6}
-and the first few sections of \cite{stasinski:12a} for background on the Greenberg functor.
-
-For each positive integer $d$, consider the canonical surjective ring homomorphisms
-$\OK/\pK^{d+1} \to \OK/\pK^d$ and the associated cartesian diagram of schemes 
-\[
-\begin{tikzcd}
-\Spec{\OK/\pK^d} \arrow[hook]{rr} && \Spec{\OK/\pK^{d+1}} \arrow[hook]{r} & \Spec{\OK} \\
- \arrow{u} \TT_{d} \arrow[hook]{rr} & \ \arrow[Rightarrow]{d}{\text{Greenberg functor}} & \arrow{u} \TT_{d+1}  &  \\
-\GN{T}_{d} \arrow[hook]{rr} & \ & \GN{T}_{d+1}  \arrow{r} & \Spec{k}
-\end{tikzcd}
-\]
-The map $\GN{T}_{d} \hookrightarrow \GN{T}_{d+1}$ is not a morphism of group schemes.
-There is, however, an epimorphism of group schemes $\GN{T}_{d+1} \to \GN{T}_{d}$ for
-which $\GN{T}_{d} \hookrightarrow \GN{T}_{d+1}$ is a section.
-
-The fundamental properties of $\GN{T}_d$ that we need are:
+We will also need the Greenberg functor, 
+introduced in \cite{greenberg:61} and \cite{greenberg:63a}, 
+as a functor from the category of schemes locally of finite type 
+over an Artinian local ring with perfect residue field $k$ 
+to the category of schemes locally of finite type over $k$. 
+This functor respects open immersions, closed immersions, 
+etale morphisms and smooth morphisms. 
+Besides Greenberg's original papers, 
+see \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} 
+and the first few sections of \cite{stasinski:12a} 
+for background on the Greenberg functor. 
+Let
+\[
+%\begin{tikzcd}
+\Gr_d : \left( \text{Schemes} \atop \text{lft over $\OK$}\right) \to \left( \text{Schemes} \atop \text{lft over $\Fq$}\right)
+%\end{tikzcd}
+\]
+be the functor produced by precomposing pull-back along $\OK \to \OK/\pK^d$ with the Greenberg functor.
+The surjective ring homomorphism $\OK/\pK^{d+1} \to \OK/\pK^d$ determines a natural transformation $P_{d} : \Gr_{d+1} \to \Gr_d$. 
+%\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}.
+
+For any positive integer $d$ set $\GN{T}_d = \Gr_d(\TT)$ and $f_d = P_d(\TT)$.
+The fundamental properties of $f_d : \GN{T}_{d+1} \to \GN{T}_d$ that we need are:
  \begin{enumerate}

### 2013-08-18 shanghai.tex
Moved the lemmas in the section on finite quasicharacter sheaves.

@@
 Likewise, $C(G)[W^{-1}]$ is a tensor category.
+
+\begin{lemma}\label{lemma:finite-pull-back}
+If $g : G'\to G$ is a morphism of group schemes then $(f,\psi) \mapsto (f_g,\psi_g)$
+defines a monomial functor $g^* : C(G)[W^{-1}] \to C(G')[W'^{-1}]$ where $f_g : H\times_G G'\to G'$
+is a pull-back of $f$ along $g$ and $\psi_g : \ker f_g \to \Aut(V)$ is defined by the diagram below.
+\[
+\begin{tikzcd}
+V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
+  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker g_f}} \ker f_g \arrow[hook]{r}
+  & \arrow[swap]{u}{g_f} H\times_G G' \arrow{r}{f_g} & \arrow{u}{g} G'.
+\end{tikzcd}
+\]
+\end{lemma}
+
+\begin{proof}
+The key point is that pull-back along $g$ takes isogenies to isogenies,
+and maps over $G$ to maps over $G'$, as pictured below.
+\[
+\begin{tikzcd}[row sep=10,column sep=10]
+\ & V \arrow{dd}{T} && \Aut(V) && \arrow[swap]{ll}{\psi} \ker f \arrow[hook]{rr} && H \arrow{rr}{f} && \arrow[equal]{dd} G\\
+ && && \arrow{ul} \ker f\times_G G' \arrow{ur} \arrow[hook]{rr} && H\times_G G' \arrow{ur} \arrow{rr} && G' \arrow{ur}{g} & \\
+& V' && \Aut(V) && \arrow[swap,pos=0.7]{ll}{\psi'} \arrow[swap]{uu}{} \ker f'  \arrow[hook]{rr} && \arrow[swap]{uu} H' \arrow[pos=0.8]{rr}{f'} && G\\
+ && && \arrow{ul} \ker f'\times_G G' \arrow{uu} \arrow{ur} \arrow[hook]{rr} && \arrow{uu} H'\times_G G' \arrow{ur} \arrow{rr} && \arrow[equals]{uu} G' \arrow[swap]{ur}{g} & 
+\end{tikzcd}
+\]
+In this form we could treat $g^*$ as a functor $G(G')\to C(G)$,
+where it not for the fact that pull-back is defined only up to isomorphism.
+In the localized categories, this ambiguity disappears. 
+\end{proof}
+
 Let $C_1(G)$ be the rigid monoidal full subcategory of $C(G)$ consisting of objects
@@
 \end{definition}
+
+\begin{lemma}\label{lemma:finite-iso}
+Each $(f,\psi)\in \QCf(G)$ determines a canonical isomorphism $m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$.
+ \end{lemma}
+
+\begin{proof}
+As in Lemma~\ref{lemma:finite-pull-back}, we have $m^*(f,\psi) = (f_m,\psi_m)$
+where $f_m$ and $\psi_m$ are pictured below, where $H_m = H\times_G(G\times G)$.
+\[
+\begin{tikzcd}[column sep=40]
+V & \Aut(V) & \arrow[swap]{l}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
+  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(m_f)\vert_{\ker m_f}} \ker f_m \arrow[hook]{r}
+  & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G.
+\end{tikzcd}
+\]
+On the other hand, $(f,\psi) \boxtimes (f,\psi) = (f\times f, \psi\otimes \psi)$.
+Since $f\circ m_H = m \circ (f\times f)$, by the universal property of pull-back,
+there is a unique $\theta : H\times H \to H_m$ making the following commute.
+\[
+\begin{tikzcd}[row sep=20,column sep=10]
+\ & V \arrow{dd}{T} && \Aut(V) && \arrow{dl} \arrow[swap]{ll}{\psi_g} A_m \arrow[hook]{rr}
+&& \arrow[swap]{ld}{m_f} H_m \arrow{rr}{f_m} && \arrow[equal]{dd} \arrow{ld}{m} G\times G\\
+ && && \arrow{ul}{\psi} A  \arrow[hook]{rr} && H  \arrow[swap, pos=0.8]{rr}{f} && G  & \\
+& V\otimes_{\EE} V && \Aut(V)
+&& \arrow[swap]{ll}{\psi \otimes \psi} \arrow[swap,pos=0.8]{uu}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr}
+&& \arrow[swap,pos=0.8]{uu}{\theta} \arrow{ul}{m_H} H\times H \arrow{rr}{f\times f} && G\times G
+\end{tikzcd}
+\]
+Choose a basis $\{ v_1 \}$ for $V$; then $\{ v_1\otimes v_1 \}$ is a basis for $V\otimes V$.
+Define $T : V \to V\otimes V$ by $T(v_1) = v_1\otimes v_1$. Then the lower part of this
+diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G)$.
+
+While $\theta$ was canonical, $T$ was not, as it depended on the choice of a basis for $V$.
+However, after passing from $C_1(G)$ to $\QCf(G)$, the resulting isomorphism
+$\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ is canonical in $\QCf(G)$.
+\end{proof}
 
@@
  is a full and faithfull monoidal functor, completing the proof.
-\end{proof}
-
-\begin{lemma}\label{lemma:finite-pull-back}
-If $g : G'\to G$ is a morphism of group schemes then $(f,\psi) \mapsto (f_g,\psi_g)$
-defines a monomial functor $g^* : C(G)[W^{-1}] \to C(G')[W'^{-1}]$ where $f_g : H\times_G G'\to G'$
-is a pull-back of $f$ along $g$ and $\psi_g : \ker f_g \to \Aut(V)$ is defined by the diagram below.
-\[
-\begin{tikzcd}
-V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker g_f}} \ker f_g \arrow[hook]{r}
-  & \arrow[swap]{u}{g_f} H\times_G G' \arrow{r}{f_g} & \arrow{u}{g} G'.
-\end{tikzcd}
-\]
-\end{lemma}
-
-\begin{proof}
-The key point is that pull-back along $g$ takes isogenies to isogenies,
-and maps over $G$ to maps over $G'$, as pictured below.
-\[
-\begin{tikzcd}[row sep=10,column sep=10]
-\ & V \arrow{dd}{T} && \Aut(V) && \arrow[swap]{ll}{\psi} \ker f \arrow[hook]{rr} && H \arrow{rr}{f} && \arrow[equal]{dd} G\\
- && && \arrow{ul} \ker f\times_G G' \arrow{ur} \arrow[hook]{rr} && H\times_G G' \arrow{ur} \arrow{rr} && G' \arrow{ur}{g} & \\
-& V' && \Aut(V) && \arrow[swap,pos=0.7]{ll}{\psi'} \arrow[swap]{uu}{} \ker f'  \arrow[hook]{rr} && \arrow[swap]{uu} H' \arrow[pos=0.8]{rr}{f'} && G\\
- && && \arrow{ul} \ker f'\times_G G' \arrow{uu} \arrow{ur} \arrow[hook]{rr} && \arrow{uu} H'\times_G G' \arrow{ur} \arrow{rr} && \arrow[equals]{uu} G' \arrow[swap]{ur}{g} & 
-\end{tikzcd}
-\]
-In this form we could treat $g^*$ as a functor $G(G')\to C(G)$,
-where it not for the fact that pull-back is defined only up to isomorphism.
-In the localized categories, this ambiguity disappears. 
-\end{proof}
-
-\begin{lemma}\label{lemma:finite-iso}
-Each $(f,\psi)\in \QCf(G)$ determines a canonical isomorphism $m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$.
- \end{lemma}
-
-\begin{proof}
-As in Lemma~\ref{lemma:finite-pull-back}, we have $m^*(f,\psi) = (f_m,\psi_m)$
-where $f_m$ and $\psi_m$ are pictured below, where $H_m = H\times_G(G\times G)$.
-\[
-\begin{tikzcd}[column sep=40]
-V & \Aut(V) & \arrow[swap]{l}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(m_f)\vert_{\ker m_f}} \ker f_m \arrow[hook]{r}
-  & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G.
-\end{tikzcd}
-\]
-On the other hand, $(f,\psi) \boxtimes (f,\psi) = (f\times f, \psi\otimes \psi)$.
-Since $f\circ m_H = m \circ (f\times f)$, by the universal property of pull-back,
-there is a unique $\theta : H\times H \to H_m$ making the following commute.
-\[
-\begin{tikzcd}[row sep=20,column sep=10]
-\ & V \arrow{dd}{T} && \Aut(V) && \arrow{dl} \arrow[swap]{ll}{\psi_g} A_m \arrow[hook]{rr}
-&& \arrow[swap]{ld}{m_f} H_m \arrow{rr}{f_m} && \arrow[equal]{dd} \arrow{ld}{m} G\times G\\
- && && \arrow{ul}{\psi} A  \arrow[hook]{rr} && H  \arrow[swap, pos=0.8]{rr}{f} && G  & \\
-& V\otimes_{\EE} V && \Aut(V)
-&& \arrow[swap]{ll}{\psi \otimes \psi} \arrow[swap,pos=0.8]{uu}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr}
-&& \arrow[swap,pos=0.8]{uu}{\theta} \arrow{ul}{m_H} H\times H \arrow{rr}{f\times f} && G\times G
-\end{tikzcd}
-\]
-Choose a basis $\{ v_1 \}$ for $V$; then $\{ v_1\otimes v_1 \}$ is a basis for $V\otimes V$.
-Define $T : V \to V\otimes V$ by $T(v_1) = v_1\otimes v_1$. Then the lower part of this
-diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G)$.
-
-While $\theta$ was canonical, $T$ was not, as it depended on the choice of a basis for $V$.
-However, after passing from $C_1(G)$ to $\QCf(G)$, the resulting isomorphism
-$\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ is canonical in $\QCf(G)$.
 \end{proof}
@@
 
+\Clifton{Now this section does mention quasicharacter sheaves.}
 Although this section does not mention quasicharacter sheaves, 
@@
 \begin{theorem}\label{thm:snake}
-  If $G$ is a smooth abelian group scheme, locally of finite type over
-  $\Fq$, and if the abelian group $\pi_0(G)(\bFq)$ (the geometric
-  component group) is finitely generated, then the trace of Frobenius
+  If $G$ is a smooth commutative group scheme locally of finite type over
+  $\Fq$ and if the abelian group $\pi_0(G)(\bFq)$ (the geometric
+  component group) is finitely generated then the trace of Frobenius
   \[
@@
 for background on the Greenberg functor.
-Let
+
+For any positive integer $d$, let
 \[
@@
 %\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}.
-
-For any positive integer $d$ set $\GN{T}_d = \Gr_d(\TT)$ and $f_d = P_d(\TT)$.
+Set $\GN{T}_d = \Gr_d(\TT)$ and $f_d = P_d(\TT)$.
+%
 The fundamental properties of $f_d : \GN{T}_{d+1} \to \GN{T}_d$ that we need are:
@@
 \]
+
 \begin{proposition}
@@
 \begin{proof}
-\Clifton{Under construction}
+It suffices to find a morphism of schemes $i_d : \GN{T}_{d}\hookrightarrow \GN{T}_{d+1}$ such that $f_d\circ i_d = \id_{\GN{T}_d}$.
 Base change along $\OK/\pK^{d+1} \to \OK/\pK^d$ determines a closed immersion $\TT_{d+1} \hookrightarrow \TT_d$, though not a morphism of group schemes.
@@
 
-Let $\QC(\GN{T})$ be the category of ind-objects from the full subcategories $\QC(\GN{T}_d)$. 
-Objects in $\QC(\GN{T})$ are equivalence classes of objects from $\QC(\GN{T}_d)$ under the equivalence relation that identifies 
-$\qcs{L}_1\in \QC(\GN{T}_{d_1})$ with $\qcs{L}_2\in \QC(\GN{T}_{d_2})$ 
-if $f_1^*\qcs{L}_1 = f_2^*\qcs{L}_2$  in $\QC(\GN{T}_{\max\{d_1,d_2\}})$,
-where $f_1 : \GN{T}_{\max\{d_1,d_2\}} \to \GN{T}_{d_1}$ 
-(resp. $f_2 : \GN{T}_{\max\{d_1,d_2\}} \to \GN{T}_{d_2}$) 
-is obtained by composing the maps $f_{d_1}, \cdots , f_{\max\{d_1,d_2\}}$ 
-(resp. $f_{d_2}, \cdots , f_{\max\{d_1,d_2\}}$).
-A map $\alpha : \qcs{F} \to \qcs{F}'$
+Let $\QC(\GN{T})$ be the category of ind-objects built from the categories $\QC(\GN{T}_d)$; we refer to this as the \emph{category of quasicharacters for $T$}.
+This means a quasicharacter sheaf for $T$ is an equivalence class of quasicharacters on $\GN{T}_d$, for various $d$, under the relation that identifies $\qcs{L}\in \QC(\GN{T}_{d})$ with $f_d^*\qcs{L}\in \QC(\GN{T}_{d})$.
+For each $\qcs{F}\in \QC(\GN{T})$ there is a unique least positive integer $d$ and a unique $\qcs{L}\in \GN{T}_d$ such that $\qcs{F} = [\qcs{L}]$; we refer to $d$ as the \emph{level} of $\qcs{F}$.
+A map $\alpha : \qcs{F} \to \qcs{F}'$ in $\QC(\GN{T})$
 

### 2013-08-18 shanghai.tex
Replaced \otimes_{\EE} with \otimes. Other minor changes.

@@
 the tensor product of the representations $\psi : \ker f\to \Aut(V)$ and $\psi' : \ker f'\to \Aut(V')$ 
-is the representation $\psi \otimes\psi' :  \ker(f\times_G f') \to \Aut(V\otimes_{\EE} V')$. 
+is the representation $\psi \otimes\psi' :  \ker(f\times_G f') \to \Aut(V\otimes V')$. 
 This allows us to set $(f,\psi)\otimes(f',\psi') \ceq (f\times_G f' ,\psi\otimes\psi')$. 
@@
  && && \arrow{ul}{\psi} A  \arrow[hook]{rr} && H  \arrow[swap, pos=0.8]{rr}{f} && G  & \\
-& V\otimes_{\EE} V && \Aut(V)
+& V\otimes V && \Aut(V)
 && \arrow[swap]{ll}{\psi \otimes \psi} \arrow[swap,pos=0.8]{uu}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr}
@@
  \labitem{(cs.1)}{cs.1} an indexed set of isomorphisms
-  $\mu_{x,y} : \gqcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gqcs{L}_{x} \otimes_{\EE}\gqcs{L}_{y}$,
+  $\mu_{x,y} : \gqcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gqcs{L}_{x} \otimes\gqcs{L}_{y}$,
   for all $x,y \in G(\bFq)$, such that
@@
     \gqcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
-    && \gqcs{L}_{x+y}\otimes_{\EE}\gqcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
-    \gqcs{L}_{x} \otimes_{\EE}\gqcs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
-    && \gqcs{L}_{x} \otimes\gqcs{L}_{y} \otimes_{\EE}\gqcs{L}_{z}
+    && \gqcs{L}_{x+y}\otimes\gqcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
+    \gqcs{L}_{x} \otimes\gqcs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
+    && \gqcs{L}_{x} \otimes\gqcs{L}_{y} \otimes\gqcs{L}_{z}
    \end{tikzcd}
@@
     \gqcs{L}_{\Frob{\Fq}(x)+\Frob{\Fq}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{\Fq}(x),\Frob{\Fq}(y)}}
-    && \gqcs{L}_{\Frob{\Fq}(x)}\otimes_{\EE}\gqcs{L}_{\Frob{\Fq}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
+    && \gqcs{L}_{\Frob{\Fq}(x)}\otimes\gqcs{L}_{\Frob{\Fq}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
     \gqcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
@@
     \gqcs{L}_x \rar{\alpha_x} & \gqcs{L'}_x
-    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\alpha_x\otimes\alpha_y} & \gqcs{L'}_x \otimes_{\EE}\gqcs{L'}_y
+    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\alpha_x\otimes\alpha_y} & \gqcs{L'}_x \otimes\gqcs{L'}_y
    \end{tikzcd}
@@
  \begin{equation}\label{section}
-  \forall x,y \in G(\bFq), \qquad \mu_{x,y}(s(x+y)) = s(x)\otimes_{\EE}s(y).
  \end{equation}
@@
   There is a unique isomorphism $\gqcs{L}_0 \cong \EE$ under which $\mu_{0,0}$ corresponds
-  to the multiplication map $\EE \otimes_{\EE}\EE \to \EE$.
+  to the multiplication map $\EE \otimes\EE \to \EE$.
   The condition $\mu_{0,0}(s(0)) = s(0) \otimes s(0)$ together with the non-triviality of $s$
@@
   condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}a \cdot a^{-1})$,
+  \Clifton{Fix this.}
   so $\tau$ and $\tau'$ are cohomologous. This shows that
@@
 
- The paragraph above also shows that \eqref{pich1} is injective. 
- Suppose $[\tau_\qcs{L}] = [\tau_\qcs{L'}]$.
+    Suppose that $\qcs{L}$ and $\qcs{L}'$ are two quasicharacter sheaves on $G$.
+  If $s$ is a global section for $\qcs{L}$ and $s'$ for $\qcs{L}'$ then $s \otimes s'$
+  is a global section for $\qcs{L} \otimes\qcs{L}'$.  The three versions of \eqref{t}
+  for $\qcs{L}, \qcs{L'}$ and $\qcs{L} \otimes\qcs{L}'$ imply that
+  $\tau_{\qcs{L} \otimes\qcs{L}'}(\Frob{k}) = \tau_\qcs{L}(\Frob{k}) \tau_{\qcs{L}'}(\Frob{k})$,
+  so \eqref{pich1} is a group homomorphism.
+
+ To see that \eqref{pich1} is injective,
+ suppose $[\tau_\qcs{L}] = [\tau_\qcs{L'}]$.
  Let $s$ (resp. $s'$) be a section appearing in the definition of $\tau_\qcs{L}$ (resp. $\tau_\qcs{L'}$);
@@
   so there is some $a\in G(\Fq)^*$ such that 
-  $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}a \cdot a^{-1})$. 
+  $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}}a \cdot a^{-1})$. 
   Define $\alpha : \qcs{L}\to \qcs{L'}$ by $\alpha_x(s(x)) = a(x) s'(x)$, for each $x\in G(\bFq)$.
-  it is straightforward to check that $\alpha$ satisfies condition~\ref{cs.3}
+  It is straightforward to check that $\alpha$ satisfies condition~\ref{cs.3}
   and that $\alpha^{-1} : \qcs{L'}\to \qcs{L}$, defined by $\alpha^{-1}_x(s'(x)) = a(x)^{-1} s(x)$, 
@@
 
-  Suppose that $\qcs{L}$ and $\qcs{L}'$ are two quasicharacter sheaves on $G$.
-  If $s$ is a global section for $\qcs{L}$ and $s'$ for $\qcs{L}'$ then $s \otimes_{\EE}s'$
-  is a global section for $\qcs{L} \otimes_{\EE}\qcs{L}'$.  The three versions of \eqref{t}
-  for $\qcs{L}, \qcs{L'}$ and $\qcs{L} \otimes_{\EE}\qcs{L}'$ imply that
-  $\tau_{\qcs{L} \otimes_{\EE}\qcs{L}'}(\Frob{k}) = \tau_\qcs{L}(\Frob{k}) \tau_{\qcs{L}'}(\Frob{k})$,
-  so \eqref{pich1} is a group homomorphism.
-
  Finally, to show that \eqref{pich1} is surjective, pick $[\tau]\in \Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
  For each $x\in G(\bFq)$, set $\gqcs{L}_x = \EE$.
- Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes_{\EE} \gqcs{L}_y$ by
- $\mu_{x,y}(1) = 1\otimes_{\EE}1$, for $x,y\in G(\bFq)$; 
+ Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by
+ $\mu_{x,y}(1) = 1\otimes1$, for $x,y\in G(\bFq)$; 
  clearly, $\mu$ satisfies condition~\ref{cs.1}.
@@
 Base change along $\OK/\pK^{d+1} \to \OK/\pK^d$ determines a closed immersion $\TT_{d+1} \hookrightarrow \TT_d$, though not a morphism of group schemes.
-Applying the Greenberg functor produces a closed immersion $i_d : \GN{T}_{d} \hookrightarrow \GN{T}_{d+1}$.
+Applying the Greenberg functor produces a closed immersion of schemes $i_d : \GN{T}_{d} \hookrightarrow \GN{T}_{d+1}$.
 Although $i_d$ is not a morphism of group schemes, it is a section of $f_d : \GN{T}_{d+1}\to \GN{T}_d$.
@@
 
-Let $\QC(\GN{T})$ be the category of ind-objects built from the categories $\QC(\GN{T}_d)$; we refer to this as the \emph{category of quasicharacters for $T$}.
-This means a quasicharacter sheaf for $T$ is an equivalence class of quasicharacters on $\GN{T}_d$, for various $d$, under the relation that identifies $\qcs{L}\in \QC(\GN{T}_{d})$ with $f_d^*\qcs{L}\in \QC(\GN{T}_{d})$.
-For each $\qcs{F}\in \QC(\GN{T})$ there is a unique least positive integer $d$ and a unique $\qcs{L}\in \GN{T}_d$ such that $\qcs{F} = [\qcs{L}]$; we refer to $d$ as the \emph{level} of $\qcs{F}$.
-A map $\alpha : \qcs{F} \to \qcs{F}'$ in $\QC(\GN{T})$
+Let $\QC(\GN{T})$ be the category of ind-objects built from the categories $\QC(\GN{T}_d)$. 
+An object $\qcs{F}\in \QC(\GN{T})$ is an equivalence class in the disjoint union of objects $\qcs{L}\in \GN{T}_d$, 
+as $d$ ranges over the positive integers, 
+under the relation that identifies $\qcs{L}\in \QC(\GN{T}_{d})$ with $f_d^*\qcs{L}\in \QC(\GN{T}_{d+1})$.
+For each $\qcs{F}\in \QC(\GN{T})$ there is a unique least positive integer $d$ and a unique isomorphism class $\qcs{L}_{/\iso}\in \QCiso{\GN{T}_d}$ such that $\qcs{F} = [\qcs{L}]$; we refer to $d$ as the \emph{level} of $\qcs{F}$.
+A map $\alpha : [\qcs{L}] \to [\qcs{L}']$ in $\QC(\GN{T})$ is
 

### 2013-08-18 shanghai.tex
Adding proof of corollary and some references

--- 2013-08-17 shanghai.tex
@@
 \begin{corollary}
- If $G$ is a commutative, \'etale algebraic group over $\Fq$ and $G(\bFq)$ is finitely
+ If $G$ is a commutative, \'etale group scheme over $\Fq$ and $G(\bFq)$ is finitely
  generated then
@@
 \end{corollary}
+\begin{proof}
+This follows from Proposition~\ref{prop:etale} by setting $X=G(\bFq)$ in Proposition~\ref{prop:X}.
+\end{proof}
 
@@
   be the commutative diagram of abelian groups obtained by applying
-  Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.  Since $G^0$ is a connected algebraic group
-  \cite{vdGeer-Moonen:AbelianVarieties}*{3.17},
+  Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.  Since $k$ is perfect
+  \cite{stacks-project}*{\href{http://stacks.math.columbia.edu/tag/035X}{Tag 035X}} implies that
+  \David{Need another reference that an algebraic group over an algebraically closed field is reduced}
+  $G$ is reduced.  Since $G^0$ is a finite type
+  \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}, it is thus a connected algebraic group and 
   Proposition~\ref{prop:connected} implies that $\ker \trFrob{G^0} =0$ and $\coker \trFrob{G^0}=0$.

### 2013-08-18 shanghai.tex
Moving to a different computer. Still working on Part 2.

@@
 functoriality results that we hope to use in a future discussion of class field theory.
+\Clifton{There is another section at the end of the paper, now.}
 Finally, we close the paper in Section~\ref{sec:transfer} by discussing a transfer principle, which allows
@@
 
-\part{Application to characters of algebraic tori over local fields}
+\part{Application to quasicharacters of algebraic tori over local fields}
 
@@
 We write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$. 
+\Clifton{I think we should seriously consider replacing $d$ with $n$ in Part~2.}
 %For any positive integer $d$, set $A_d\ceq \OK/\pK^d$.
@@
 and $\Hom_{<\infty}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth;
-one might call these quasicharacters of $T(K)$, expanding on \cite{tate:67a}*{2.3}.
+we call these quasicharacters of $T(K)$, following \cite{tate:67a}*{2.3}.
 
@@
   Next we show that this isomorphism is functorial.
+  \Clifton{This proof isn't finished!}
 The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
@@
 
-By Proposition~\ref{prop:pullback}, the surjective morphism $f_d : \GN{T}_{d+1}\to \GN{T}_d$ of group schemes induces a functor
-\[
-f_d^* : \QC(\GN{T}_d) \to \QC(\GN{T}_{d+1}).
-\]
+For any $d\leq d'$, define $f_{d\leq d'} : \GN{T}_{d'} \to \GN{T}_{d}$ by $f_{d\leq d'}\ceq f_d \circ f_{d+1} \circ \cdots \circ f_{d'-1}$.
+Let $f_{d\leq d'}^* : \QC(\GN{T}_d) \to \QC(\GN{T}_{d'})$ be the functor promised by Proposition~\ref{prop:pullback}.
 
 \begin{proposition}
-The functor $f_d^* : \QC(\GN{T}_d) \to \QC(\GN{T}_{d+1})$ is full and faithful.
+The functor $f_{d\leq d'}^* : \QC(\GN{T}_d) \to \QC(\GN{T}_{d'})$ is full and faithful.
 \end{proposition}
@@
 It suffices to find a morphism of schemes $i_d : \GN{T}_{d}\hookrightarrow \GN{T}_{d+1}$ such that $f_d\circ i_d = \id_{\GN{T}_d}$.
-Base change along $\OK/\pK^{d+1} \to \OK/\pK^d$ determines a closed immersion $\TT_{d+1} \hookrightarrow \TT_d$, though not a morphism of group schemes.
+Base change along $\OK/\pK^{d+1} \to \OK/\pK^d$ determines a closed immersion of schemes $\TT_{d+1} \hookrightarrow \TT_d$ (not a morphism of group schemes).
 Applying the Greenberg functor produces a closed immersion of schemes $i_d : \GN{T}_{d} \hookrightarrow \GN{T}_{d+1}$.
@@
 
-Let $\QC(\GN{T})$ be the category of ind-objects built from the categories $\QC(\GN{T}_d)$. 
-An object $\qcs{F}\in \QC(\GN{T})$ is an equivalence class in the disjoint union of objects $\qcs{L}\in \GN{T}_d$, 
-as $d$ ranges over the positive integers, 
-under the relation that identifies $\qcs{L}\in \QC(\GN{T}_{d})$ with $f_d^*\qcs{L}\in \QC(\GN{T}_{d+1})$.
-For each $\qcs{F}\in \QC(\GN{T})$ there is a unique least positive integer $d$ and a unique isomorphism class $\qcs{L}_{/\iso}\in \QCiso{\GN{T}_d}$ such that $\qcs{F} = [\qcs{L}]$; we refer to $d$ as the \emph{level} of $\qcs{F}$.
+\begin{definition}
+The \emph{Greenberg transform of the N\'eron model of $T$} is the pro-group scheme over $\Fq$ given by $\cdef{\GN{T}} \ceq \varprojlim_{d\in \ZZ_{>0}} \GN{T}_{d}$.
+Let $\QC(\GN{T})$ be the following category.
+An object in $\QC(\GN{T})$ is an equivalence class of objects from $\QC(\GN{T}_d)$, as $d$ ranges over the positive integers, where $\qcs{L}_d \equiv \qcs{L}_{d'}$ if $\qcs{L}_{d'} = f_{d\leq d'}^* \qcs{L}_d$.
+
 A map $\alpha : [\qcs{L}] \to [\qcs{L}']$ in $\QC(\GN{T})$ is
+\end{definition}
+
+For each $\qcs{F}\in \QC(\GN{T})$ there is a unique least positive integer $d$ and a unique isomorphism class $\qcs{L}_{/\text{iso}}\in \QCiso{\GN{T}_d}$ such that $\qcs{F} = [\qcs{L}]$; we refer to $d$ as the \emph{level} of $\qcs{F}$.
 
 We refer to objects of $\QC(\GN{T})$ as \emph{quasicharacter sheaves for $T$}.
-
-\begin{definition}
-The \emph{Greenberg transform of the N\'eron model of $T$} is the pro-group scheme over $\Fq$ given by
-\begin{equation}\label{projlim}
-  \cdef{\GN{T}} \ceq \varprojlim_{d\in \ZZ_{>0}} \GN{T}_{d}.
-\end{equation}
-\end{definition}
 

### 2013-08-18 shanghai.tex
Many changes to Part 2, including d |--> n.

@@
 \newcommand{\obj}{{\text{obj}\, }}
+\newcommand{\mor}{{\text{mor}\, }}
 \newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
@@
 We write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$. 
-\Clifton{I think we should seriously consider replacing $d$ with $n$ in Part~2.}
+\Clifton{I think we should seriously consider replacing $d$ with $n$ in Part~2. Actually, I've just done that.}
 %For any positive integer $d$, set $A_d\ceq \OK/\pK^d$.
 Let $T$ be an algebraic torus over $K$.
-We write $\Hom_{< d}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $d$ 
-and $\Hom_{<\infty}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth;
+We write $\Hom_{< n}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $n$ 
+and $\Hom_{\text{qc}}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth;
 we call these quasicharacters of $T(K)$, following \cite{tate:67a}*{2.3}.
@@
 
-For any positive integer $d$, let
+For any positive integer $n$, let
 \[
 %\begin{tikzcd}
-\Gr_d : \left( \text{Schemes} \atop \text{lft over $\OK$}\right) \to \left( \text{Schemes} \atop \text{lft over $\Fq$}\right)
+\Gr_n : \left( \text{Schemes} \atop \text{lft over $\OK$}\right) \to \left( \text{Schemes} \atop \text{lft over $\Fq$}\right)
 %\end{tikzcd}
 \]
-be the functor produced by precomposing pull-back along $\OK \to \OK/\pK^d$ with the Greenberg functor.
-The surjective ring homomorphism $\OK/\pK^{d+1} \to \OK/\pK^d$ determines a natural transformation $P_{d} : \Gr_{d+1} \to \Gr_d$. 
-%\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}.
-Set $\GN{T}_d = \Gr_d(\TT)$ and $f_d = P_d(\TT)$.
+be the functor produced by precomposing pull-back along $\OK \to \OK/\pK^n$ with the Greenberg functor.
+The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a natural transformation $P_{n} : \Gr_{d+1} \to \Gr_d$ 
+\Clifton{Do you think I should say more about $P_{n}$?}
+\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}.
+For a given Néron model $\TT$ of $T$, set
+\[
+\GN{T}_n \ceq \Gr_n(\TT)
+\qquad \text{and}\qquad
+f_n \ceq P_n(\TT).
+\]
 %
-The fundamental properties of $f_d : \GN{T}_{d+1} \to \GN{T}_d$ that we need are:
+Some fundamental properties of $f_n : \GN{T}_{n+1} \to \GN{T}_n$ are:
  \begin{enumerate}
-   \labitem{(GN.0)}{dFq} $\GN{T}_d(\Fq) = \TT(\OK/\pK^d)$, canonically.
-  \labitem{(GN.1)}{GNd} $\GN{T}_d$ is a smooth, commutative group scheme,
-  locally of finite type over $\Fq$, and the component group of $\GN{T}_d$ is
-  geometrically finitely generated. (In fact, $\pi_0(\GN{T}_d) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$,
+   \labitem{(GN.0)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
+  \labitem{(GN.1)}{smooth} $\GN{T}_n$ is a smooth commutative group scheme
+  locally of finite type over $\Fq$ and the component group of $\GN{T}_n$ is
+  geometrically finitely generated. 
+  (In fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$,
   and the latter is finitely generated by \cite{xarles:93a}*{2.18}.)
   \labitem{(GN.2)}{truncation}
-  The morphism $f_d : \GN{T}_{d+1} \to \GN{T}_d$ is a surjective morphism of group schemes.
+  The morphism $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes.
   \end{enumerate}
-
-We remark that $f_d : \GN{T}_{d+1} \to \GN{T}_d$ is not induced from a morphism of Néron models.
+%
+We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.
+
+\begin{definition}
+The \emph{Greenberg transform of the N\'eron model of $T$} is the pro-group scheme over $\Fq$ given by $\cdef{\GN{T}} \ceq \varprojlim_{n\in \ZZ_{>0}} \GN{T}_{n}$ (with reference to the morphisms $f_n : \GN{T}_{n+1} \to \GN{T}_n$).
+\end{definition}
 
@@
 \begin{theorem}\label{thm:application}
-Let $d$ be a positive integer.
+Let $n$ be a positive integer.
 For every algebraic torus $T$ over $K$, the trace of Frobenius 
   \[
-\trFrob{T,d}:  \QCiso{\GN{T}_d} \to \Hom_{< d}(T(K),\EEx)
+\trFrob{T,n}:  \QCiso{\GN{T}_n} \to \Hom_{< n}(T(K),\EEx)
   \]
 is an isomomorphism. 
-Moreover, the isomorphism $\trFrob{T,d}$ is functorial in the following sense:
-$T \mapsto \trFrob{T,d}$ is a natural transformation between the following two additive functors
+Moreover, the isomorphism $\trFrob{T,n}$ is functorial in the following sense:
+$T \mapsto \trFrob{T,n}$ is a natural transformation between the following two additive functors
 \begin{enumerate}
-\item[$F_1$:] $T \mapsto \QCiso{\GN{T}_d}$
-\item[$F_2$:] $T \mapsto \Hom_{<d}(T(K),\EEx)$
+\item[$F_1$:] $T \mapsto \QCiso{\GN{T}_n}$
+\item[$F_2$:] $T \mapsto \Hom_{<n}(T(K),\EEx)$
 \end{enumerate}
@@
 \begin{proof}
-  By \ref{GNd}, we may apply Theorem~\ref{thm:snake} to
-  $\GN{T}_d$ which provides a canonical isomorphism
-  $\QCiso{\GN{T}_d} \iso \GN{T}_d(\Fq)^*$.
-  By \ref{dFq}, $\GN{T}_d(\Fq) = \TT(\OK/\pK^d)$.
+  By \ref{smooth}, we may apply Theorem~\ref{thm:snake} to
+  $\GN{T}_n$ which provides a canonical isomorphism
+  $\QCiso{\GN{T}_n} \iso \GN{T}_n(\Fq)^*$.
+  By \ref{points}, $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$.
   Then we recall that the filtration of $T(K)$ used to
-  define depth has the property that $\TT(\OK/\pK^d) \cong T(K) / T(K)_d$
-  \cite{yu:03a}*{Prop 5.2}, so characters of $\GN{T}_d(\Fq)$ 
-  are in bijection with characters of $T(K)$ vanishing on $T(K)_d$. 
-  This shows that $\trFrob{T,d}$ is an isomorphism.
-
-  Next we show that this isomorphism is functorial.
-  \Clifton{This proof isn't finished!}
+  define depth has the property that $\TT(\OK/\pK^n) \cong T(K) / T(K)_n$
+  \cite{yu:03a}*{Prop 5.2}, so characters of $\GN{T}_n(\Fq)$ 
+  are in bijection with characters of $T(K)$ vanishing on $T(K)_n$. 
+  This shows that $\trFrob{T,n}$ is an isomorphism.
+
+  The definition of $F_1$ depends 
+  on the choice of a Néron model for every algebraic torus $T$.
+  However, since Néron models are unique up to unique isomorphism,
+  the isomorphism class of $\GN{T}_n$ is uniquely determined by $T$
+  \Clifton{Hmmm}
+  and the group of isomorphism classes of objects in $\QC(\GN{T}_n)$ 
+  is uniquely determined by $T$. 
+  To define $F_1$ on objects, one uses the Néron mapping property.
+
+  Finally, we show that $\trFrob{T,n}$ is functorial.
 The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
@@
 
-For any $d\leq d'$, define $f_{d\leq d'} : \GN{T}_{d'} \to \GN{T}_{d}$ by $f_{d\leq d'}\ceq f_d \circ f_{d+1} \circ \cdots \circ f_{d'-1}$.
-Let $f_{d\leq d'}^* : \QC(\GN{T}_d) \to \QC(\GN{T}_{d'})$ be the functor promised by Proposition~\ref{prop:pullback}.
+For any $n\leq m$ (positive integers) define $f_{n\leq m} : \GN{T}_{m} \to \GN{T}_{n}$ by $f_{n\leq m}\ceq f_n \circ f_{n+1} \circ \cdots \circ f_{m-1}$.
+Let $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ be the functor promised by Proposition~\ref{prop:pullback}.
 
 \begin{proposition}
-The functor $f_{d\leq d'}^* : \QC(\GN{T}_d) \to \QC(\GN{T}_{d'})$ is full and faithful.
+The functor $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ is full and faithful.
 \end{proposition}
@@
 \begin{proof}
-It suffices to find a morphism of schemes $i_d : \GN{T}_{d}\hookrightarrow \GN{T}_{d+1}$ such that $f_d\circ i_d = \id_{\GN{T}_d}$.
-Base change along $\OK/\pK^{d+1} \to \OK/\pK^d$ determines a closed immersion of schemes $\TT_{d+1} \hookrightarrow \TT_d$ (not a morphism of group schemes).
-Applying the Greenberg functor produces a closed immersion of schemes $i_d : \GN{T}_{d} \hookrightarrow \GN{T}_{d+1}$.
-Although $i_d$ is not a morphism of group schemes, it is a section of $f_d : \GN{T}_{d+1}\to \GN{T}_d$.
-\end{proof}
-
-\begin{definition}
-The \emph{Greenberg transform of the N\'eron model of $T$} is the pro-group scheme over $\Fq$ given by $\cdef{\GN{T}} \ceq \varprojlim_{d\in \ZZ_{>0}} \GN{T}_{d}$.
-Let $\QC(\GN{T})$ be the following category.
-An object in $\QC(\GN{T})$ is an equivalence class of objects from $\QC(\GN{T}_d)$, as $d$ ranges over the positive integers, where $\qcs{L}_d \equiv \qcs{L}_{d'}$ if $\qcs{L}_{d'} = f_{d\leq d'}^* \qcs{L}_d$.
-
-A map $\alpha : [\qcs{L}] \to [\qcs{L}']$ in $\QC(\GN{T})$ is
-\end{definition}
-
-For each $\qcs{F}\in \QC(\GN{T})$ there is a unique least positive integer $d$ and a unique isomorphism class $\qcs{L}_{/\text{iso}}\in \QCiso{\GN{T}_d}$ such that $\qcs{F} = [\qcs{L}]$; we refer to $d$ as the \emph{level} of $\qcs{F}$.
-
-We refer to objects of $\QC(\GN{T})$ as \emph{quasicharacter sheaves for $T$}.
+It suffices to find a morphism of schemes $i_n : \GN{T}_{n}\hookrightarrow \GN{T}_{n+1}$ such that $f_n\circ i_n = \id_{\GN{T}_n}$.
+Base change along $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a closed immersion of schemes $\TT_{n+1} \hookrightarrow \TT_n$ (not a morphism of group schemes).
+Applying the Greenberg functor produces a closed immersion of schemes $i_n : \GN{T}_{n} \hookrightarrow \GN{T}_{n+1}$.
+\Clifton{I still need to confirm this claim.}
+Although $i_n$ is not a morphism of group schemes, it is a section of $f_n : \GN{T}_{n+1}\to \GN{T}_n$.
+\end{proof}
+
+We now define a category, denoted by $\QC(\GN{T})$, which allows us to extend the notion of quasicharacter sheaf from $\GN{T}_n$ to $\GN{T}$.
+An object in $\QC(\GN{T})$ is an equivalence class in $\cup_{n} \obj \QC(\GN{T}_n)$ under the relation: $\qcs{L}_n\in \QC(\GN{T}_n)$ is equivalent to $\qcs{L}_{m}\in \QC(\GN{T}_m)$ if $f_{n\leq k}^* \qcs{L}_{n} = f_{m\leq k}^* \qcs{L}_m$ for some $n,m\leq k$.
+Objects in $\QC(\GN{T})$ all take the form
+\[
+[\qcs{L}_n] \ceq \{ f_{n\leq k}^* \qcs{L}_n \tq n\leq k\},
+\]
+for some unique $\qcs{L}_n \in \QC(\GN{T}_n)$.
+Maps $[\qcs{L}_n] \to [\qcs{L}_m]$ in $\QC(\GN{T})$ are defined as follows:
+$\Hom([\qcs{L}_n],[\qcs{L}_m])$ is the set of equivalence classes in $\cup_{n,m\leq k} \Hom(f_{n\leq k}^*\qcs{L}_n,f_{m\leq k}^*\qcs{L}_m)$ under the relation: $\alpha_k\in \mor \QC(\GN{T}_k)$ is equivalent to $\beta_l \in \QC(\GN{T}_l)$ if $f_{k\leq i}^*\alpha_k = f_{l\leq i}^* \beta_l$ for some $k,l\leq i$.
+Maps in $\QC(\GN{T})$ all take the form
+\[
+[\alpha_k] \ceq \{ f_{k\leq i}^* \alpha_k \tq k\leq i\},
+\]
+for some unique $\alpha_k \in \QC(\GN{T}_k)$.
+Identities and composition are defined in the natural way.
+Category $\QC(\GN{T})$ carries a tensor structure under
+\[
+[\qcs{L}_n]\otimes [\qcs{L}_m] \ceq [f_{n\leq k}^*\qcs{L}_n \otimes f_{m\leq k}^*\qcs{L}_m],
+\qquad k = \max\{ n,m\}.
+\]
+Duals in $\QC(\GN{T})$ are defined by
+\[
+[\qcs{L}_n]^\vee \ceq [\qcs{L}_n^\vee].
+\]
+Category $\QC(\GN{T})$ is rigid symmetric monoidal and comes equipped with monoidal subcategories
+\[
+\begin{tikzcd}
+\ & & & \QC(\GN{T})\\
+\arrow{urrr}{F_n} \QC(\GN{T}_n) \arrow[swap]{rr}{f_{n\leq m}^*} && \QC(\GN{T}_m) \arrow[swap]{ur}{F_m} & \\
+\end{tikzcd}
+\]
+defined by $F_n(\qcs{L}) = [\qcs{L}_n]$ and $F_n(\alpha_n) = [\alpha_n]$, for all positive integers $n\leq m$.
+We refer to objects of $\QC(\GN{T})$ as \emph{quasicharacter sheaves on $\GN{T}$} or \emph{quasicharacter sheaves for $T$}.
 
@@
   \[
-\trFrob{T}:  \QCiso{\GN{T}} \to \Hom_{<\infty}(T(K),\EEx)
+\trFrob{T}:  \QCiso{\GN{T}} \to \Hom_{\text{qc}}(T(K),\EEx)
   \]
@@
 \item[$F_1$:] $T \mapsto \QCiso{\GN{T}}$
-\item[$F_2$:] $T \mapsto \Hom_{<\infty}(T(K),\EEx)$
+\item[$F_2$:] $T \mapsto \Hom_{\text{qc}}(T(K),\EEx)$
 \end{enumerate}
@@
 \begin{corollary}\label{cor:transfer}
- With notation above, suppose that $T$ and $T'$ are $N$-congruent and $N > 3h$.  Set $d = N-3h$.
+ With notation above, suppose that $T$ and $T'$ are $N$-congruent and $N > 3h$.  Set $n = N-3h$.
  Then there is a canonical equivalence of categories
  \[
-  \QC(\GN{T}'_{d}) \to \QC(\GN{T}_{d})
+  \QC(\GN{T}'_{n}) \to \QC(\GN{T}_{n})
  \]
@@
  \[
-  \Hom_{<d}(T'(K'), \EEx) \to \Hom_{<d}(T(K), \EEx)
+  \Hom_{<n}(T'(K'), \EEx) \to \Hom_{<n}(T(K), \EEx)
  \]
@@
 by the idea that quasicharacter sheaves for $T$ 
-may play a key role in a geometric, categorial version 
+may play a key role in a new geometric, categorial version 
 of the local Langlands correspondence for algebraic tori 
@@
 As with the local Langlands correspondence for algebraic tori over local fields, 
-it will be possible to reduce the essential points of the argument to the case $T= \Gm{K}$,
+it should be possible to reduce the essential points of the argument to the case $T= \Gm{K}$,
 provided that the category of quasicharacter sheaves behaves properly with regard to
@@
 \begin{tikzcd}[column sep=60]
-\Hom_{<\infty}(T(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{T(K)}} &\Hom_{<\infty}(T(K), \EEx).
+\Hom_{\text{qc}}(T(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{T(K)}} &\Hom_{\text{qc}}(T(K), \EEx).
 \end{tikzcd}
@@
 \begin{proof}
-\Clifton{The proof will require the results in the base change section.}
-There is a canonical isomorphism
-\[
-\Res_{k'/k} \Gr(\TL) \cong \Gr(\underline{\Res_{L/K}(T_L)}).
-\]
+Weil restriction behaves properly with respect to formation of Néron models:
+there is a canonical isomorphism
+\[
+\underline{\Res_{K'/K}(T')} \iso \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'}).
+\]
+And Weil restriction behaves properly with respect to the Greenberg transform:
+there is a canonical isomorphism 
+\Clifton{Really?}
+\[
+\Gr_{n} \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})
+\iso
+\Res_{k'/k} \Gr_n(\underline{T'}),
+\]
+where $k'$ is the residue field for $K'$.
+And the Greenberg tranforms respects products:
+\[
+\Gr_n(\underline{T'}) = \Gr_n(\underline{T})\times_{k} {k'}.
+\]
+Now use Proposition~\ref{prop:csbe}.
 \end{proof}
@@
 \ & \arrow[swap]{dl}{\trFrob{G}} \QCiso{\GN{T}} \arrow[dashed]{dr}  & \\
-\Hom_{<\infty}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(K,\hat{T}_\ell) \\
+\Hom_{\text{qc}}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(K,\hat{T}_\ell) \\
 \end{tikzcd}
@@
  from the same quasicharacter sheaf. 
- Results in this paper provide tools for reduction the problem to the case $T=\Gm{K}$. 
+ Results in this paper provide some tools for reduction of the problem to the case $T=\Gm{K}$. 
  In that case, our suspicions are all but confirmed 

### 2013-08-18 shanghai.tex
Added the proof of the dictionary for algebraic tori.

@@
 is a smooth group scheme over $\OK$ with generic fiber $T$ and a canonical isomorphism
-$\TT(\OK) \cong T(K)$.  For each positive integer $d$, let $\GN{T}_d$ be the
-Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^d}$; the commutative
+$\TT(\OK) \cong T(K)$.  For each positive integer $d$, let $\GN{T}_n$ be the
+Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^n}$; the commutative
 group scheme $\GN{T}_d$ plays the r\^{o}le of $G$.  Theorem~\ref{thm:application}
@@
 \[
-\QCiso{\GN{T}_d} 
+\QCiso{\GN{T}_n} 
 \iso
-\Hom_{< d}(T(K),\EEx).
+\Hom_{< n}(T(K),\EEx).
 \]  
@@
 
-For any $n\leq m$ (positive integers) define $f_{n\leq m} : \GN{T}_{m} \to \GN{T}_{n}$ by $f_{n\leq m}\ceq f_n \circ f_{n+1} \circ \cdots \circ f_{m-1}$.
+For any $n< m$ (positive integers) define $f_{n\leq m} : \GN{T}_{m} \to \GN{T}_{n}$ by $f_{n\leq m}\ceq f_n \circ f_{n+1} \circ \cdots \circ f_{m-1}$; also set $f_{n\leq n} \ceq \id_{\GN{T}_n}$.
 Let $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ be the functor promised by Proposition~\ref{prop:pullback}.
-
-\begin{proposition}
+%
+%\begin{proposition}\label{prop:nm}
 The functor $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ is full and faithful.
-\end{proposition}
-
-\begin{proof}
-It suffices to find a morphism of schemes $i_n : \GN{T}_{n}\hookrightarrow \GN{T}_{n+1}$ such that $f_n\circ i_n = \id_{\GN{T}_n}$.
+%\end{proposition}
+%
+%\begin{proof}
+%It suffices to find a morphism of schemes $i_n : \GN{T}_{n}\hookrightarrow \GN{T}_{n+1}$ such that $f_n\circ i_n = \id_{\GN{T}_n}$.
 Base change along $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a closed immersion of schemes $\TT_{n+1} \hookrightarrow \TT_n$ (not a morphism of group schemes).
 Applying the Greenberg functor produces a closed immersion of schemes $i_n : \GN{T}_{n} \hookrightarrow \GN{T}_{n+1}$.
-\Clifton{I still need to confirm this claim.}
-Although $i_n$ is not a morphism of group schemes, it is a section of $f_n : \GN{T}_{n+1}\to \GN{T}_n$.
-\end{proof}
-
-We now define a category, denoted by $\QC(\GN{T})$, which allows us to extend the notion of quasicharacter sheaf from $\GN{T}_n$ to $\GN{T}$.
+%\Clifton{I still need to confirm this claim.}
+%Although $i_n$ is not a morphism of group schemes, it is a section of $f_n : \GN{T}_{n+1}\to \GN{T}_n$.
+%\end{proof}
+
+We now define a category which allows us to extend the notion of quasicharacter sheaf to the pro-group scheme $\GN{T}$.
+
+\begin{definition}
 An object in $\QC(\GN{T})$ is an equivalence class in $\cup_{n} \obj \QC(\GN{T}_n)$ under the relation: $\qcs{L}_n\in \QC(\GN{T}_n)$ is equivalent to $\qcs{L}_{m}\in \QC(\GN{T}_m)$ if $f_{n\leq k}^* \qcs{L}_{n} = f_{m\leq k}^* \qcs{L}_m$ for some $n,m\leq k$.
@@
 Identities and composition are defined in the natural way.
+We refer to objects in $\QC(\GN{T})$ as \emph{quasicharacter sheaves on $\GN{T}$} or \emph{quasicharacter sheaves for $T$}.
+\end{definition}
+
 Category $\QC(\GN{T})$ carries a tensor structure under
@@
 \]
-Duals in $\QC(\GN{T})$ are defined by
-\[
-[\qcs{L}_n]^\vee \ceq [\qcs{L}_n^\vee].
-\]
-Category $\QC(\GN{T})$ is rigid symmetric monoidal and comes equipped with monoidal subcategories
-\[
-\begin{tikzcd}
-\ & & & \QC(\GN{T})\\
-\arrow{urrr}{F_n} \QC(\GN{T}_n) \arrow[swap]{rr}{f_{n\leq m}^*} && \QC(\GN{T}_m) \arrow[swap]{ur}{F_m} & \\
-\end{tikzcd}
-\]
-defined by $F_n(\qcs{L}) = [\qcs{L}_n]$ and $F_n(\alpha_n) = [\alpha_n]$, for all positive integers $n\leq m$.
-We refer to objects of $\QC(\GN{T})$ as \emph{quasicharacter sheaves on $\GN{T}$} or \emph{quasicharacter sheaves for $T$}.
+Duals in $\QC(\GN{T})$ are defined by $[\qcs{L}_n]^\vee \ceq [\qcs{L}_n^\vee]$.
 
@@
 \begin{proof}
-Show $\QCiso{\GN{T}} = \varinjlim_{d\in \ZZ_{>0}} \QCiso{\GN{T}_d}$, then invoke Theorem~\ref{thm:application}.
+Observe that $\QC(\GN{T})$ comes equipped with monoidal subcategories
+\[
+\begin{tikzcd}
+\ & & & \QC(\GN{T})\\
+\arrow{urrr}{F_n} \QC(\GN{T}_n) \arrow[swap]{rr}{f_{n\leq m}^*} && \QC(\GN{T}_m) \arrow[swap]{ur}{F_m} & \\
+\end{tikzcd}
+\]
+defined by $F_n(\qcs{L}) = [\qcs{L}_n]$ and $F_n(\alpha_n) = [\alpha_n]$, for all positive integers $n\leq m$.
+Passing to isomorphism classes of objects, we get 
+\[
+\begin{tikzcd}
+\ & & & & \QCiso{\GN{T}}\\
+\ & & & \varinjlim_{d\in \ZZ_{>0}} \QCiso{\GN{T}_d} \arrow{ur}{\exists ! \theta} & \\
+\arrow{urrr}{F_n} \QCiso{\GN{T}_n} \arrow[swap]{rr}{f_{n\leq m}^*} && \QCiso{\GN{T}_m} \arrow[swap]{ur}{F_m} & & \\
+\end{tikzcd}
+\]
+The group homomorphism 
+$\theta: \varinjlim_{d\in \ZZ_{>0}} \QCiso{\GN{T}_d} \to \QCiso{\GN{T}}$ is a bijection 
+with inverse $[\qcs{L}]_{/\text{iso}} \mapsto [\qcs{L}_{/\text{iso}}]$.
+Now use Theorem~\ref{thm:application}.
 \end{proof}

### 2013-08-19 shanghai.tex
Changes to the introduction and Part 2.

@@
 is a direct generalization of the sheaf--function dictionary to the case of commutative
-group schemes which are not necessarily connected or finite type.  The other main use
-of the term ``character sheaf'' traces back to Lusztig \cite{lusztig:85a}*{Def.~2.10}.  Most of his energy is devoted to
+group schemes which are not necessarily connected or finite type.  The main use
+of the term ``character sheaf'' is due to Lusztig \cite{lusztig:85a}*{Def.~2.10}.  Most of his energy is devoted to
 handling non-commutative groups; though he does define character sheaves for some
-non-connected groups he restricts his attention to reductive groups with cyclic component group.
-For extensions of $\ZZ/n\ZZ$ by a torus, it is not difficult to relate his Frobenius-stable character
-sheaves to our quasicharacter sheaves.
+non-connected groups he restricts his attention to reductive groups with cyclic component group, which are extensions of $\ZZ/n\ZZ$ by a torus. 
+In this case is not difficult to relate his Frobenius-stable character sheaves to our quasicharacter sheaves.
 
@@
 induces an essentially surjective functor of quasicharacter sheaves.
-Section~\ref{sec:snake} closes out Part \ref{part1} with the proof of the main theorem, that trace of Frobenius
+Section~\ref{sec:snake} closes out Part \ref{part1} with the proof of the main theorem: trace of Frobenius
 is an isomorphism for $G$ as long as the geometric component group is finitely generated.
@@
 functoriality results that we hope to use in a future discussion of class field theory.
-\Clifton{There is another section at the end of the paper, now.}
-Finally, we close the paper in Section~\ref{sec:transfer} by discussing a transfer principle, which allows
+In Section~\ref{sec:transfer} we discuss a transfer principle which allows
 a geometric transfer of characters between characteristic $p$ tori to characteristic $0$ tori.
+We close the paper with Section~\ref{sec:reciprocity}, in which we suggest that quasicharacter sheaves may play a key role in a geometric and categorical form of the local Langlands correspondence for algebraic tori over non-archimedean local fields.
 
@@
   condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}a \cdot a^{-1})$,
-  \Clifton{Fix this.}
+  %\Clifton{Fix this.}
   so $\tau$ and $\tau'$ are cohomologous. This shows that
@@
 We write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$. 
-\Clifton{I think we should seriously consider replacing $d$ with $n$ in Part~2. Actually, I've just done that.}
-%For any positive integer $d$, set $A_d\ceq \OK/\pK^d$.
 Let $T$ be an algebraic torus over $K$.
@@
 be the functor produced by precomposing pull-back along $\OK \to \OK/\pK^n$ with the Greenberg functor.
-The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a natural transformation $P_{n} : \Gr_{d+1} \to \Gr_d$ 
-\Clifton{Do you think I should say more about $P_{n}$?}
+The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$ 
+%\Clifton{Do you think I should say more about $P_{n}$?}
 \cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}.
@@
 %
+\Clifton{I guess this next bit needs to be re-structured.}
 Some fundamental properties of $f_n : \GN{T}_{n+1} \to \GN{T}_n$ are:
@@
   locally of finite type over $\Fq$ and the component group of $\GN{T}_n$ is
-  geometrically finitely generated. 
-  (In fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$,
-  and the latter is finitely generated by \cite{xarles:93a}*{2.18}.)
+  geometrically finitely generated: $\underline{T}$ is a smooth group scheme over $\OK$, by construction; since smoothness is preserved under base change, $\TT_n \ceq \underline{T} \times_\Spec{\OK} \Spec{\OK/\pK^n}$ is a smooth group scheme over an Artinian ring with perfect residue field; the Greenberg functor preserves smoothness, so $\GN{T}_n$ is a smooth group scheme over $\Fq$; the identity component of any smooth group scheme is geometrically connected, hence connected, and the Greenberg functor takes the geometric identity component of $\TT_n$ to the geometric identity component of $\GN{T}_n$;
+  in fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$;
+  this group is finitely generated by \cite{xarles:93a}*{2.18}.
   \labitem{(GN.2)}{truncation}
   The morphism $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes.
+To see this, it suffices to find a morphism of schemes $i_n : \GN{T}_{n}\hookrightarrow \GN{T}_{n+1}$ such that $f_n\circ i_n = \id_{\GN{T}_n}$.
+Base change along $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a closed immersion of schemes $\TT_{n+1} \hookrightarrow \TT_n$ (not a morphism of group schemes).
+Applying the Greenberg functor produces a closed immersion of schemes $i_n : \GN{T}_{n} \hookrightarrow \GN{T}_{n+1}$.
+\Clifton{I still need to confirm this claim.}
+Although $i_n$ is not a morphism of group schemes, it is a section of $f_n : \GN{T}_{n+1}\to \GN{T}_n$.
   \end{enumerate}
@@
 For any $n< m$ (positive integers) define $f_{n\leq m} : \GN{T}_{m} \to \GN{T}_{n}$ by $f_{n\leq m}\ceq f_n \circ f_{n+1} \circ \cdots \circ f_{m-1}$; also set $f_{n\leq n} \ceq \id_{\GN{T}_n}$.
+\Clifton{Now I wonder if $f_{n\leq m}$ is a discrete isogeny!!! 
+What's the covering group of $f_{n\leq m}$? 
+Must be the finite group $\GN{T}_{m}(\Fq)/\GN{T}_n(\Fq)$, which could be $\TT^0(\pK^n/\pK^{m})$. 
+We might be able to build some very special finite quasicharacter sheaves on $\GN{T}_n$ this way.}
 Let $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ be the functor promised by Proposition~\ref{prop:pullback}.
@@
 %\begin{proposition}\label{prop:nm}
-The functor $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ is full and faithful.
+The functor $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ is full and faithful, by \ref{truncation}.
 %\end{proposition}
@@
 %\begin{proof}
-%It suffices to find a morphism of schemes $i_n : \GN{T}_{n}\hookrightarrow \GN{T}_{n+1}$ such that $f_n\circ i_n = \id_{\GN{T}_n}$.
-Base change along $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a closed immersion of schemes $\TT_{n+1} \hookrightarrow \TT_n$ (not a morphism of group schemes).
-Applying the Greenberg functor produces a closed immersion of schemes $i_n : \GN{T}_{n} \hookrightarrow \GN{T}_{n+1}$.
-%\Clifton{I still need to confirm this claim.}
-%Although $i_n$ is not a morphism of group schemes, it is a section of $f_n : \GN{T}_{n+1}\to \GN{T}_n$.
+%
 %\end{proof}
@@
 Identities and composition are defined in the natural way.
-We refer to objects in $\QC(\GN{T})$ as \emph{quasicharacter sheaves on $\GN{T}$} or \emph{quasicharacter sheaves for $T$}.
-\end{definition}
-
 Category $\QC(\GN{T})$ carries a tensor structure under
@@
 Duals in $\QC(\GN{T})$ are defined by $[\qcs{L}_n]^\vee \ceq [\qcs{L}_n^\vee]$.
+We refer to objects in the rigid symmetric monoidal category $\QC(\GN{T})$ as \emph{quasicharacter sheaves on $\GN{T}$} or \emph{quasicharacter sheaves for $T$}.
+\end{definition}
 
@@
 \section{Toward geometric reciprocity}
+\label{sec:reciprocity}
 
@@
 there is a canonical isomorphism 
-\Clifton{Really?}
+\Clifton{References needed!}
 \[

### 2013-08-19 shanghai.tex
Fixed a few typos.
Moving to a different computer.

@@
 is a smooth group scheme over $\OK$ with generic fiber $T$ and a canonical isomorphism
-$\TT(\OK) \cong T(K)$.  For each positive integer $d$, let $\GN{T}_n$ be the
+$\TT(\OK) \cong T(K)$.  For each positive integer $n$, let $\GN{T}_n$ be the
 Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^n}$; the commutative
@@
 handling non-commutative groups; though he does define character sheaves for some
-non-connected groups he restricts his attention to reductive groups with cyclic component group, which are extensions of $\ZZ/n\ZZ$ by a torus. 
-In this case is not difficult to relate his Frobenius-stable character sheaves to our quasicharacter sheaves.
+non-connected groups he restricts his attention to reductive groups with cyclic component group. If commutative, such groups are extensions of $\ZZ/n\ZZ$ by a torus,
+in which case is not difficult to relate his Frobenius-stable character sheaves to our quasicharacter sheaves.
 
@@
 in the sense of \cite{grothendieck:SGA1}*{Expos\'e V, \S 4}. Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$,
-as shown in \cite{kamgarpour:09a}*{App'x B}, this provides an alternate proof of $\QCiso{G} \to G(\Fq)^*$.
+as shown in \cite{kamgarpour:09a}*{App'x B}, this provides an alternate proof of $\QCiso{G} \iso G(\Fq)^*$ when $G$ is a connected algebraic group over $\Fq$.
 
@@
 
-With Theorem~\ref{thm:snake} on hand, 
+With Theorem~\ref{thm:snake} in hand, 
 we can see why neither bounded quasicharacter sheaves 
@@
 This functor respects open immersions, closed immersions, 
-etale morphisms and smooth morphisms. 
+etale morphisms, smooth morphisms and geometric components.
 Besides Greenberg's original papers, 
@@
 Applying the Greenberg functor produces a closed immersion of schemes $i_n : \GN{T}_{n} \hookrightarrow \GN{T}_{n+1}$.
-\Clifton{I still need to confirm this claim.}
+\Clifton{I'm working on this.}
 Although $i_n$ is not a morphism of group schemes, it is a section of $f_n : \GN{T}_{n+1}\to \GN{T}_n$.
@@
 For any $n< m$ (positive integers) define $f_{n\leq m} : \GN{T}_{m} \to \GN{T}_{n}$ by $f_{n\leq m}\ceq f_n \circ f_{n+1} \circ \cdots \circ f_{m-1}$; also set $f_{n\leq n} \ceq \id_{\GN{T}_n}$.
-\Clifton{Now I wonder if $f_{n\leq m}$ is a discrete isogeny!!! 
+%\Clifton{Now I wonder if $f_{n\leq m}$ is a discrete isogeny!!!
 What's the covering group of $f_{n\leq m}$?
@@
 defined by $F_n(\qcs{L}) = [\qcs{L}_n]$ and $F_n(\alpha_n) = [\alpha_n]$, for all positive integers $n\leq m$.
-Passing to isomorphism classes of objects, we get 
-\[
-\begin{tikzcd}
-\ & & & & \QCiso{\GN{T}}\\
-\ & & & \varinjlim_{d\in \ZZ_{>0}} \QCiso{\GN{T}_d} \arrow{ur}{\exists ! \theta} & \\
-\arrow{urrr}{F_n} \QCiso{\GN{T}_n} \arrow[swap]{rr}{f_{n\leq m}^*} && \QCiso{\GN{T}_m} \arrow[swap]{ur}{F_m} & & \\
-\end{tikzcd}
-\]
-The group homomorphism 
-$\theta: \varinjlim_{d\in \ZZ_{>0}} \QCiso{\GN{T}_d} \to \QCiso{\GN{T}}$ is a bijection 
+Passing to isomorphism classes of objects and invoking the universal property of $\varinjlim_{d\in \ZZ_{>0}} \QCiso{\GN{T}_d}$ gives a group homomorphism
+$\theta: \varinjlim_{d\in \ZZ_{>0}} \QCiso{\GN{T}_d} \to \QCiso{\GN{T}}$; this is a bijection 
 with inverse $[\qcs{L}]_{/\text{iso}} \mapsto [\qcs{L}_{/\text{iso}}]$.
@@
 \end{proof}
-
-\Clifton{Make comments here about the depth-preserving isomorphism  . .  .}
 
@@
 from quasicharacter sheaves directly and that the reciprocity map 
-can then be be viewed as pairing characters and parameters coming
+can then be be viewed as a matching between quasicharacters and Langlands parameters coming
  from the same quasicharacter sheaf. 

### 2013-08-19 shanghai.tex
Small modifications to the Introduction. A few more d |-->n.

@@
 Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^n}$; the commutative
-group scheme $\GN{T}_d$ plays the r\^{o}le of $G$.  Theorem~\ref{thm:application}
-allows us to translate characters $T(K)$ of depth less than $d$ into quasicharacter sheaves on $\GN{T}_d$:
+group scheme $\GN{T}_n$ plays the r\^{o}le of $G$.  Theorem~\ref{thm:application}
+allows us to translate characters $T(K)$ of depth less than $n$ into quasicharacter sheaves on $\GN{T}_n$:
 \[
@@
 We refer to finite-depth characters of $T(K)$ as quasicharacters and
-describe a group scheme $\GN{T}$ simultaneously geometrizing all such quasicharacters.
+describe a pro-group scheme $\GN{T}$ simultaneously geometrizing all such quasicharacters.
 
@@
 
-DeBacker and Reeder have recently applied Deligne-Lusztig representations to the
+DeBacker and Reeder have recently applied Deligne-Lusztig representations to part of the
 local Langlands correspondence \cite{reeder-debacker:09a}.  
@@
 Analogous sheaves on connected, commutative algebraic groups were first studied
-by Deligne \cite{deligne:SGA4.5}, \David{more specific citation} and more recently Drinfeld has referred to such objects
-as character sheaves.  Our quasicharacter sheaves evolved from this notion, and Theorem~\ref{thm:snake}
+by Deligne \cite{deligne:SGA4.5}*{sommes trig.} and many people have since referred to such objects
+as character sheaves; see for example, \cite{kamgarpour:09a}. 
+%\cite{boyarshenko-drinfeld:motivated}*{\S 1.8}.  
+Our quasicharacter sheaves evolved from this notion, and Theorem~\ref{thm:snake}
 is a direct generalization of the sheaf--function dictionary to the case of commutative
 group schemes which are not necessarily connected or finite type.  The main use
-of the term ``character sheaf'' is due to Lusztig \cite{lusztig:85a}*{Def.~2.10}.  Most of his energy is devoted to
-handling non-commutative groups; though he does define character sheaves for some
-non-connected groups he restricts his attention to reductive groups with cyclic component group. If commutative, such groups are extensions of $\ZZ/n\ZZ$ by a torus,
-in which case is not difficult to relate his Frobenius-stable character sheaves to our quasicharacter sheaves.
+of the term character sheaf is due to Lusztig: it is applied to certain perverse sheaves on connected reductive algebraic groups over algebraically closed fields in \cite{lusztig:85a}*{Def.~2.10} and to certain perverse sheaves on reductive groups over algebraically closed fields with cyclic component groups in the series of papers beginning with \cite{lusztig:disconnected1}.
+When commutative, such groups are extensions of $\ZZ/n\ZZ$ by a torus,
+in which case is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
 
@@
 
-In Section~\ref{sec:GN} we introduce N\'eron models of tori and the Greenberg transform, which produce
+In Section~\ref{sec:GN} we introduce the Greenberg transform of N\'eron models of tori, which produce
 group schemes over $\Fq$ from algebraic tori $T$ over $K$.
@@
 In this section we ask if the isomorphism \eqref{transfer} comes from an equivalence of
-categories of quasicharacter sheaves on $\GN{T}_d$ and those on $\GN{T}'_d$.
+categories of quasicharacter sheaves on $\GN{T}_n$ and those on $\GN{T}'_n$.
 
 One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes between
-$\TT_d$ and $\TT'_d$ assuming that $T$ and $T'$ are sufficiently congruent.
+$\TT_n$ and $\TT'_n$ assuming that $T$ and $T'$ are sufficiently congruent.
 They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the

### 2013-08-19 shanghai.tex
Citation added.

@@
 Motivated by the sheaf--function dictionary for commutative, connected
-algebraic groups \cite{deligne:SGA4.5},\David{more specific citation} we explore the trace of Frobenius morphism
+algebraic groups \cite{deligne:SGA4.5}*{sommes trig.}, 
+we explore the trace of Frobenius morphism
 \[

### 2013-08-19 shanghai.tex
Improvements to Part 2.
Maybe it's all there now, mathematically. It certainly needs
re-reading, however,

@@
 When commutative, such groups are extensions of $\ZZ/n\ZZ$ by a torus,
-in which case is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
+in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
 
@@
 
-In Section~\ref{sec:GN} we introduce the Greenberg transform of N\'eron models of tori, which produce
+In Section~\ref{sec:GN} we review the Greenberg transform of N\'eron models of tori, which produces
 group schemes over $\Fq$ from algebraic tori $T$ over $K$.
@@
 In Section~\ref{sec:transfer} we discuss a transfer principle which allows
-a geometric transfer of characters between characteristic $p$ tori to characteristic $0$ tori.
+a geometric transfer of characters between characteristic $p$ tori and characteristic $0$ tori.
 We close the paper with Section~\ref{sec:reciprocity}, in which we suggest that quasicharacter sheaves may play a key role in a geometric and categorical form of the local Langlands correspondence for algebraic tori over non-archimedean local fields.
@@
   The identity component $G^0$ of $G$ is a connected algebraic group over $\Fq$, 
+  \Clifton{This needs to be treated more carefully!}
   clopen in $G$ \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}. 
@@
 \]
-%
-\Clifton{I guess this next bit needs to be re-structured.}
 Some fundamental properties of $f_n : \GN{T}_{n+1} \to \GN{T}_n$ are:
@@
    \labitem{(GN.0)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
-  \labitem{(GN.1)}{smooth} $\GN{T}_n$ is a smooth commutative group scheme
-  locally of finite type over $\Fq$ and the component group of $\GN{T}_n$ is
-  geometrically finitely generated: $\underline{T}$ is a smooth group scheme over $\OK$, by construction; since smoothness is preserved under base change, $\TT_n \ceq \underline{T} \times_\Spec{\OK} \Spec{\OK/\pK^n}$ is a smooth group scheme over an Artinian ring with perfect residue field; the Greenberg functor preserves smoothness, so $\GN{T}_n$ is a smooth group scheme over $\Fq$; the identity component of any smooth group scheme is geometrically connected, hence connected, and the Greenberg functor takes the geometric identity component of $\TT_n$ to the geometric identity component of $\GN{T}_n$;
-  in fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$;
+  \labitem{(GN.1)}{smooth} 
+  $\GN{T}_n$ is a smooth commutative group scheme locally of finite type over $\Fq$ 
+  and the component group of $\GN{T}_n$ is geometrically finitely generated. 
+  Note that $\underline{T}$ is a smooth group scheme over $\OK$, by construction. 
+  Since smoothness is preserved under base change, 
+  $\TT_n \ceq \underline{T} \times_\Spec{\OK} \Spec{\OK/\pK^n}$ 
+  is a smooth group scheme over an Artinian ring with perfect residue field. 
+  The Greenberg functor preserves smoothness, 
+  so $\GN{T}_n$ is a smooth group scheme locally of finite type over $\Fq$. 
+  The Greenberg functor takes the geometric identity component of $\TT_n$ 
+  to the geometric identity component of $\GN{T}_n$;
+  in fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$ and
   this group is finitely generated by \cite{xarles:93a}*{2.18}.
   \labitem{(GN.2)}{truncation}
-  The morphism $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes.
-To see this, it suffices to find a morphism of schemes $i_n : \GN{T}_{n}\hookrightarrow \GN{T}_{n+1}$ such that $f_n\circ i_n = \id_{\GN{T}_n}$.
-Base change along $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a closed immersion of schemes $\TT_{n+1} \hookrightarrow \TT_n$ (not a morphism of group schemes).
-Applying the Greenberg functor produces a closed immersion of schemes $i_n : \GN{T}_{n} \hookrightarrow \GN{T}_{n+1}$.
-\Clifton{I'm working on this.}
-Although $i_n$ is not a morphism of group schemes, it is a section of $f_n : \GN{T}_{n+1}\to \GN{T}_n$.
+  The morphism $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a morphism of group schemes over $\Fq$. 
+  This follows from the fact that $P_{n}$ is a natural transformation between additive functors.
+  We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.
 \end{enumerate}
-%
-We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.
 
@@
 For any $n< m$ (positive integers) define $f_{n\leq m} : \GN{T}_{m} \to \GN{T}_{n}$ by $f_{n\leq m}\ceq f_n \circ f_{n+1} \circ \cdots \circ f_{m-1}$; also set $f_{n\leq n} \ceq \id_{\GN{T}_n}$.
-%\Clifton{Now I wonder if $f_{n\leq m}$ is a discrete isogeny!!!
-What's the covering group of $f_{n\leq m}$?
-Must be the finite group $\GN{T}_{m}(\Fq)/\GN{T}_n(\Fq)$, which could be $\TT^0(\pK^n/\pK^{m})$.
-We might be able to build some very special finite quasicharacter sheaves on $\GN{T}_n$ this way.}
-Let $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ be the functor promised by Proposition~\ref{prop:pullback}.
-%
-%\begin{proposition}\label{prop:nm}
-The functor $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ is full and faithful, by \ref{truncation}.
-%\end{proposition}
-%
-%\begin{proof}
-%
-%\end{proof}
-
+Note that $f_{n\leq m}:  \GN{T}_{m} \to \GN{T}_{n}$ is a morphism of group schemes over $\Fq$.
+Let $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ be the functor produced by applying Proposition~\ref{prop:pullback} to $f_{n\leq m}$.
 We now define a category which allows us to extend the notion of quasicharacter sheaf to the pro-group scheme $\GN{T}$.

### 2013-08-19 shanghai.tex
Moved the lemma before the proposition on restriction to the identity compnent. Added proof that G^0 is an algebraic group.
Some other small improvements.

@@
 \'etale morphism and a morphism of commutative group $\Fq$-schemes, for which
-the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $f^{-1}{\bar e}$ is trivial.
+the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $f^{-1}({\bar e})$ is trivial.
 An object in $C(G)$ is a pair $(f,\psi)$ where: 
@@
 
-\begin{proposition}\label{prop:restriction}
-  The restriction functor $\QC(G)\to \QC(G^0)$ is essentially surjective.
-\end{proposition}
-
-\begin{proof}
-  The identity component $G^0$ of $G$ is a connected algebraic group over $\Fq$, 
-  \Clifton{This needs to be treated more carefully!}
-  clopen in $G$ \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}. 
-    By Proposition~\ref{prop:connected}, every
-  quasicharacter sheaf on $G^0$ is isomorphic to a 
-  finite quasicharacter sheaf on $G^0$, 
-  so to prove the proposition it suffices to show that every 
-  finite quasicharacter sheaf on $G^0$ extends to a quasicharacter sheaf on $G$.
-
- Let $(\pi,\psi)$ be a finite quasicharacter sheaf on $G^0$.
- By Lemma~\ref{lemma:ext}, there is an extension of the 
- discrete isogeny $\pi : B \to G^0$ 
- (see Section~\ref{sec:finite} for the definition of a discrete isogeny) 
- to a discrete isogeny $f : H \to G^0$ 
- such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
- Then $(f,\psi)$ is a finite quasicharacter sheaf on $G$.
- Then $(f,\psi)\vert_{G^0} \iso (\pi,\psi)$,
- completing the proof that $\QC(G)\to \QC(G^0)$ is essentially surjective.
-\end{proof}
+Recall from Section~\ref{sec:finite} that 
+a morphism $f : H\to G$ of group $\Fq$-schemes is a discrete isogeny 
+if it is a finite, surjective \'etale morphism and 
+the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $f^{-1}{\bar e}$ is trivial.
 
 \begin{lemma}\label{lemma:ext}
-Every discrete isogeny (see Section~\ref{sec:finite}) to $G^0$ extends to a discrete
+Every discrete isogeny  to $G^0$ extends to a discrete
 isogeny to $G$ such that the component group of the covering space is isomorphic
@@
   morphisms are $\Gamma$-equivariant.
+\end{proof}
+
+\begin{proposition}\label{prop:restriction}
+  The restriction functor $\QC(G)\to \QC(G^0)$ is essentially surjective.
+\end{proposition}
+
+\begin{proof}
+  Since $G$ is a smooth group scheme locally of finite type over $\Fq$, its
+  identity component $G^0$ of $G$ is a connected smooth, 
+  geometrically reduced group scheme of finite type over $\Fq$, by
+   \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}. 
+	Since $\Fq$ is a finite field, $G^0$ is actually reduced over $\Fq$;
+	see \cite{stacks-project}*{\href{http://stacks.math.columbia.edu/tag/035X}{Tag 035X}}.
+	It follows that $G^0$ is a connected algebraic group.
+    By Proposition~\ref{prop:connected}, every
+  quasicharacter sheaf on $G^0$ is isomorphic to a 
+  finite quasicharacter sheaf on $G^0$, 
+  so to prove the proposition it suffices to show that every 
+  finite quasicharacter sheaf on $G^0$ extends to a quasicharacter sheaf on $G$.
+
+ Let $(\pi,\psi)$ be a finite quasicharacter sheaf on $G^0$.
+ By Lemma~\ref{lemma:ext}, there is an extension of the 
+ discrete isogeny $\pi : B \to G^0$ 
+ (see Section~\ref{sec:finite} for the definition of a discrete isogeny) 
+ to a discrete isogeny $f : H \to G^0$ 
+ such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
+ Then $(f,\psi)$ is a finite quasicharacter sheaf on $G$.
+ Then $(f,\psi)\vert_{G^0} \iso (\pi,\psi)$,
+ completing the proof that $\QC(G)\to \QC(G^0)$ is essentially surjective.
 \end{proof}
@@
 natural comparison between characters of $T(K)$ and of $T'(K')$.
-This comparison of has been made precise in \cite{chai-yu:01a}, \David{more specific citation?}
+This comparison of has been made precise in \cite{chai-yu:01a}, \David{more specific citation?}\Clifton{In this case, maybe not necessary.}
 building on ideas of \cite{deligne:84a}.

### 2013-08-20 shanghai.tex
moving computers ....

@@
 
-The proof of Proposition~\ref{prop:functorialG} requires the results from the next section.
+The proof of Proposition~\ref{prop:functorialG} will be given at the end of the next section.
 
@@
 
-\David{insert some commentary on this proposition: it will be very useful to us}
+%\David{insert some commentary on this proposition: it will be very useful to us}
+As a step toward the proof of Proposition~\ref{prop:functorialG} we show that every morphism  $H \to G$ of smooth group schemes locally of finite type over $\Fq$ induces a monoidal functor from quasicharacter sheaves on $G$ to quasicharacters on $H$.
+This simple but important result will also play a role in the proof of many other propositions in this paper.
 
@@
    G(\Fq)^* \rar & H(\Fq)^*
-  %\Hom_\text{grp}(G(\Fq),\EEx) \rar & \Hom_\text{grp}(H(\Fq),\EEx)
   \end{tikzcd}
@@
 etale morphisms, smooth morphisms and geometric components.
-Besides Greenberg's original papers, 
+Besides Greenberg's original papers, see [DG70, V, § 4, no. 1])
 see \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} 
@@
 \[
-\Gr_{n} \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)
 \iso
@@
 \[
-\Gr_n(\underline{T'}) = \Gr_n(\underline{T})\times_{k} {k'}.
-\]
+\Gr_n(\underline{T'}) = \Gr_n(\underline{T}\times_{k} {k'}) \iso \Gr_n(\underline{T})\times_{k} {k'} = \Gr_n(\underline{T})_{k'}.
+\]
+Thus, the 
 Now use Proposition~\ref{prop:csbe}.
+\[
+\begin{tikzcd}
+\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\trFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\trFrob{G}} \\
+G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
+\end{tikzcd}
+\]
+
 \end{proof}

### 2013-08-20 shanghai.tex
This version has a proposition in the last section, but I think the proof sketched there is not correct.

@@
 etale morphisms, smooth morphisms and geometric components.
-Besides Greenberg's original papers, see [DG70, V, § 4, no. 1])
-see \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} 
+Besides Greenberg's original papers, see \cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1}, \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} 
 and the first few sections of \cite{stasinski:12a} 
@@
 be the functor produced by precomposing pull-back along $\OK \to \OK/\pK^n$ with the Greenberg functor.
-The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$ 
+The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$.
 %\Clifton{Do you think I should say more about $P_{n}$?}
-\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}.
+%\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}.
+\Clifton{I took the reference to BLR for $P_n$ out, because it didn't actually give any information. This must be in DG, but I don't have a copy.}
 For a given Néron model $\TT$ of $T$, set
@@
 Weil restriction behaves properly with respect to formation of Néron models:
-there is a canonical isomorphism
-\[
+adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} 
+gives a canonical isomorphism 
+\Clifton{I need to check this.}
+\begin{equation}
 \underline{\Res_{K'/K}(T')} \iso \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'}).
-\]
+\end{equation}
 And Weil restriction behaves properly with respect to the Greenberg transform:
-there is a canonical isomorphism 
-\Clifton{References needed!}
-\[
+\Clifton{I'm not so sure about this . . . In fact, I don't believe it!}
+\begin{equation}
 \Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)
@@
 \Res_{k'/k} \Gr_n(\underline{T'}),
-\]
+\end{equation}
 where $k'$ is the residue field for $K'$.
-And the Greenberg tranforms respects products:
+And the Greenberg transform respects products:
 \[
@@
 Now use Proposition~\ref{prop:csbe}.
-\[
-\begin{tikzcd}
-\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\trFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\trFrob{G}} \\
-G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
-\end{tikzcd}
-\]
-
 \end{proof}

### 2013-08-20 shanghai.tex
I removed the proposition on weil restriction from the final section. The paper still works!

@@
 \ & & & \QC(\GN{T})\\
-\arrow{urrr}{F_n} \QC(\GN{T}_n) \arrow[swap]{rr}{f_{n\leq m}^*} && \QC(\GN{T}_m) \arrow[swap]{ur}{F_m} & \\
+\arrow{urrr}{F_n} \QC(\GN{T}_n) \arrow[swap]{rr}{f_{n\leq m}^*} && \QC(\GN{T}_m) \arrow[swap]{ur}{F_m} & 
 \end{tikzcd}
@@
 over non-archimedean local fields. 
-As with the local Langlands correspondence for algebraic tori over local fields, 
-it should be possible to reduce the essential points of the argument to the case $T= \Gm{K}$,
-provided that the category of quasicharacter sheaves behaves properly with regard to
-Weil restriction; see \cite{yu:09a}*{Thm 7.5 (2)}. 
-The next proposition shows that the category of quasicharacter sheaves for 
-algebraic tori does indeed behave properly with regard to Weil restriction.
-
-\begin{proposition}
-Let $K'/K$ be a finite Galois extension; 
-let $k'/k$ be the corresponding finite Galois extension of residue fields.
-Let $T$ be an algebraic torus over $K$ and 
-set $T' = T \times_\Spec{K} \Spec{K'}$.  
-The natural inclusion $T \hookrightarrow \Res_{K'/K} T'$ 
-induces a map of $k$-schemes
-\[
-\GN{T} \hookrightarrow \Res_{k'/k} \GN{T}'
-\]
-and thus a functor on quasicharacter sheaves through pullback.
-\[
-\QC(\Res_{k'/k} \GN{T}') \to \QC(\GN{T}).
-\]
-Through trace of Frobenius, this functor induces the homomorphism
-\[
-\begin{tikzcd}[column sep=60]
-\Hom_{\text{qc}}(T(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{T(K)}} &\Hom_{\text{qc}}(T(K), \EEx).
-\end{tikzcd}
-\] 
-\end{proposition}
-
-\begin{proof}
-Weil restriction behaves properly with respect to formation of Néron models:
-adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} 
-gives a canonical isomorphism 
-\Clifton{I need to check this.}
-\begin{equation}
-\underline{\Res_{K'/K}(T')} \iso \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'}).
-\end{equation}
-And Weil restriction behaves properly with respect to the Greenberg transform:
-\Clifton{I'm not so sure about this . . . In fact, I don't believe it!}
-\begin{equation}
-\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)
-\iso
-\Res_{k'/k} \Gr_n(\underline{T'}),
-\end{equation}
-where $k'$ is the residue field for $K'$.
-And the Greenberg transform respects products:
-\[
-\Gr_n(\underline{T'}) = \Gr_n(\underline{T}\times_{k} {k'}) \iso \Gr_n(\underline{T})\times_{k} {k'} = \Gr_n(\underline{T})_{k'}.
-\]
-Thus, the 
-Now use Proposition~\ref{prop:csbe}.
-\end{proof}
-
+%
 This paper has shown how quasicharacter sheaves 
@@
 \ & \arrow[swap]{dl}{\trFrob{G}} \QCiso{\GN{T}} \arrow[dashed]{dr}  & \\
-\Hom_{\text{qc}}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(K,\hat{T}_\ell) \\
+\Hom_{\text{qc}}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(K,\hat{T}_\ell) 
 \end{tikzcd}

### 2013-08-22 shanghai.tex
Toward geometric reciprocity for local tori + label inserted.
I started to write up the proof of the result on Weil restriction over local fields, but ran out of time. I'll come back to this when I can.

--- 2013-08-20 shanghai.tex
@@
 \begin{proof}
-Weil restriction behaves properly with respect to formation of Néron models:
-adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} 
+Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} for lft-Neron models
 gives a canonical isomorphism 
-\Clifton{I need to check this.}
-\begin{equation}
+\begin{equation}\label{weilneron}
 \underline{\Res_{K'/K}(T')} \iso \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'}).
 \end{equation}
-And Weil restriction behaves properly with respect to the Greenberg transform:
-\Clifton{I'm not so sure about this . . . In fact, I don't believe it!}
-\begin{equation}
+
+Weil restriction is also compatible with the Greenberg transform, in the following sense: if $e$ is the ramification degree of $K'/K$ then
+\begin{equation}\label{weilgreenberg}
 \Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)
 \iso
-\Res_{k'/k} \Gr_n(\underline{T'}),
+\Res_{k'/k} \Gr_{en}(\underline{T'}),
 \end{equation}
 where $k'$ is the residue field for $K'$.
-And the Greenberg transform respects products:
+To see this, we employ the functor of points perspective. Let $R$ be any $\Fq$-algebra. Then 
+\[
+\begin{aligned}
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R)
+&=
+\end{aligned}
+\]
+
 \[

### 2013-08-23 shanghai.tex
Made a new section on Weil restriction over local fields . .
. . .then got stuck trying to prove the same proposition we talked
about in the lounge. I'll come back to this when I can.

--- 2013-08-20 shanghai.tex
@@
 We give a reinterpretation of this result in Section~\ref{sec:quasichar}, using a limit process to simultaneously
-geometrize all quasicharacters of $T$.  Sections~\ref{sec:bdchar} and \ref{sec:quasichar} also include
+geometrize all quasicharacters of $T$.  Sections~\ref{sec:bdchar}, \ref{sec:quasichar} and \ref{sec:wrK} also include
 functoriality results that we hope to use in a future discussion of class field theory.
@@
 
-For any positive integer $n$, let
+\begin{definition}\label{def:Grn}
+For any local field $K$ with residue field $\Fq$ and for any positive integer $n$, let
 \[
@@
 be the functor produced by precomposing pull-back along $\OK \to \OK/\pK^n$ with the Greenberg functor.
+\end{definition}
+
 The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$.
@@
 %\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}.
-\Clifton{I took the reference to BLR for $P_n$ out, because it didn't actually give any information. This must be in DG, but I don't have a copy.}
+\Clifton{I took the reference to BLR for $P_n$ out, because it didn't actually give any information. 
+This must be in DG, but I don't have a copy.}
 For a given Néron model $\TT$ of $T$, set
@@
 \]
+
 Some fundamental properties of $f_n : \GN{T}_{n+1} \to \GN{T}_n$ are:
@@
 
+If $K = \mathbb{Q}_q$ and $T = \Gm{\mathbb{Q}_q}$ then $\GN{T}^0 = \mathbb{W}^*_{\FF_q}$, the group $\FF_q$-scheme of units in the ring scheme $\mathbb{W}_{\FF_q}$.
+
 \section{Application to quasicharacters of bounded depth} \label{sec:bdchar}
@@
 \end{proof}
+
+\section{Weil restriction for local fields}
+\label{sec:wrK}
+
+As indicated in the Introduction, we are tantalized 
+by the idea that quasicharacter sheaves for $T$ 
+may play a key role in a new geometric, categorial version 
+of the local Langlands correspondence for algebraic tori 
+over non-archimedean local fields. 
+As with the local Langlands correspondence for algebraic tori over local fields, 
+it should be possible to reduce the essential points of the argument to the case $T= \Gm{K}$,
+provided that the category of quasicharacter sheaves behaves properly with regard to
+Weil restriction; see \cite{yu:09a}*{Thm 7.5 (2)}. 
+The next proposition shows that the category of quasicharacter sheaves for 
+algebraic tori does indeed behave properly with regard to Weil restriction.
+
+\begin{lemma}\label{lemma:wrK}
+Weil restriction is compatible with the Greenberg transform in the following sense: 
+if $e$ is the ramification degree of $K'/K$ then, for every positive integer $n$,
+\begin{equation}%\label{weilgreenberg}
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)
+\iso
+\Res_{k'/k} \Gr_{en}(\underline{T'}),
+\end{equation}
+where $k'$ is the residue field for $K'$.
+\end{lemma}
+
+\begin{proof}
+First, note that since $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ 
+is a scheme over $\OK$, 
+the Greenberg transform $\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
+is obtained by base change along $\OK \to \OK/\pK^n$ 
+followed by the Greenberg functor over the Artinian ring $\OK/\pK^n$. 
+On the other hand, since $\underline{T'}$ is a scheme over $\mathcal{O}_{K'}$, 
+the Greenberg transform $\Gr_{en}(\underline{T'})$ is defined by base change along 
+$\mathcal{O}_{K'} \to \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$ 
+followed by the Greenberg functor over the Artinian ring $\mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$; 
+see Definition~\ref{def:Grn}. 
+Note also that 
+\begin{equation}\label{nem}
+\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \iso \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}.
+\end{equation}
+
+Now, to prove the lemma, we may employ the functor of points perspective 
+and exhibit an isomorphism of functors from 
+$\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
+to $\Res_{k'/k} \Gr_{en}(\underline{T'})$ as functors 
+from the category of $\Fq$-algebras to the category of groups.
+To that end, let $R$ be any $\Fq$-module. 
+Let $\mathbb{W}$ be the Witt functor from the category of $\Fq$-algebras to rings. 
+By the definition of the Greenberg transform, the Weil restriction functor and \eqref{nem},
+\[
+\begin{aligned}
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R)
+&= \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\left( \OK/\pK^n \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right)\\
+&= \underline{T'}\left(\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right)\\
+&= \underline{T'}\left(\mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right);
+\end{aligned}
+\]
+on the other hand,
+\[
+\begin{aligned}
+\Res_{k'/k} \Gr_{en}(\underline{T'})(R)
+&= \Gr_{en}(\underline{T'}) (R\otimes_{k} k')\\
+&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k')} \mathbb{W}(R\otimes_{k} k')\right)\\
+&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k')} \mathbb{W}(R) \otimes_{\mathbb{W}(k)} \mathbb{W}(k')\right)\\
+&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right).
+\end{aligned}
+\]
+So the ring isomorphism 
+\[
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R) \to \Res_{k'/k} \Gr_{en}(\underline{T'})(R)
+\]
+is apparent, as are the commuting ring homomorphisms
+\[
+\begin{tikzcd}
+\arrow{d} \Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R) \arrow{r}{\iso} & \arrow{d} \Res_{k'/k} \Gr_{en}(\underline{T'})(R)\\
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R') \arrow{r}{\iso} & \Res_{k'/k} \Gr_{en}(\underline{T'})(R'),
+\end{tikzcd}
+\]
+for every map $R\to R'$ of $\Fq$-algebras.
+\end{proof}
+
+\begin{proposition}\label{prop:wrK}
+Let $K'/K$ be a finite Galois extension; 
+let $k'/k$ be the corresponding finite Galois extension of residue fields.
+Let $T$ be an algebraic torus over $K$ and 
+set $T' = T \times_\Spec{K} \Spec{K'}$.
+The natural inclusion 
+\[
+T \hookrightarrow \Res_{K'/K} T' =: T''
+\]
+induces a map of $k$-schemes
+$\GN{T} \hookrightarrow \GN{T}''$
+and thus a functor on quasicharacter sheaves through pullback:
+\begin{equation}\label{eq:wrK}
+\QC(\GN{T}'') \to \QC(\GN{T}).
+\end{equation}
+Through trace of Frobenius, this functor induces the homomorphism
+\[
+\begin{tikzcd}[column sep=60]
+\Hom_{\text{qc}}(T(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{T(K)}} &\Hom_{\text{qc}}(T(K), \EEx).
+\end{tikzcd}
+\]  
+\end{proposition}
+
+\begin{proof}
+Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} for lft-Neron models
+gives a canonical isomorphism 
+\begin{equation}\label{weilneron}
+\underline{\Res_{K'/K}(T')} \iso \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'}).
+\end{equation}
+By Lemma~\ref{lemma:wrK}, 
+\begin{equation}\label{weilgreenberg}
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)
+\iso
+\Res_{k'/k} \Gr_{en}(\underline{T'}).
+\end{equation}
+This gives
+\[
+\GN{T}''_n \iso \Res_{k'/k} \GN{T}'_{en}.
+\]
+\Clifton{Now I'm stuck here.}
+But
+\[
+\GN{T}'_{en} = \Gr_{en}(\underline{T'}) = \Gr_{en}(\underline{T}\times_{\OK} {\mathcal{O}_{K'}}) \iso . . . 
+\]
+Now use Proposition~\ref{prop:csbe}.
+\end{proof}
+
+If we specialize Proposition~\ref{prop:wrK} to the case when 
+$T = \Gm{K}$ then $T'' = \Res_{K'/K} \Gm{K'}$ and we see that the functor $\QC(\GN{T}'')\to \QC(\GN{T})$ is the geometrization and categorification of restriction of quasicharacters from $(K')^\times$ to $K^\times$:
+\[
+\begin{tikzcd}[column sep=60]
+\Hom_{\text{qc}}((K')^\times, \EEx) \arrow{r}{\chi \mapsto \chi\vert_{K^\times}} &\Hom_{\text{qc}}(K^\times, \EEx).
+\end{tikzcd}
+\]
 
@@
 then there is a canonical isomorphism of smooth group schemes
- \[
+ $
   \TT_{N-3h} \to \TT'_{N-3h}
- \]
+ $
  determined by $\alpha, \beta$ and $\phi$.
@@
 
-\section{Toward geometric reciprocity}
+\section{Toward geometric reciprocity for tori over local fields}
 \label{sec:reciprocity}
 
-As indicated in the Introduction, we are tantalized 
-by the idea that quasicharacter sheaves for $T$ 
-may play a key role in a new geometric, categorial version 
-of the local Langlands correspondence for algebraic tori 
-over non-archimedean local fields. 
-%
 This paper has shown how quasicharacter sheaves 
-on the Greenberg transform of the N\/eron model of $T$ 
+on the Greenberg transform of the Néron model of $T$ 
 determine admissible characters of $T(K)$, and vice versa, functorially.
@@
 determine Langlands parameters for $T$, and vice versa, functorially.
-\[
-\begin{tikzcd}
-\ & \arrow[swap]{dl}{\trFrob{G}} \QCiso{\GN{T}} \arrow[dashed]{dr}  & \\
-\Hom_{\text{qc}}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(K,\hat{T}_\ell) 
-\end{tikzcd}
-\]
 We suspect that it is possible to extract Langlands parameters 
@@
  from the same quasicharacter sheaf. 
- Results in this paper provide some tools for reduction of the problem to the case $T=\Gm{K}$. 
+ \[
+\begin{tikzcd}
+\ & \arrow[swap]{dl}{\trFrob{G}} \QCiso{\GN{T}} \arrow[dashed]{dr} & \\
+\Hom_{\text{qc}}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(K,\hat{T}_\ell)
+\end{tikzcd}
+\]
+ Results in this paper provide tools for reduction of the problem to the case $T=\Gm{K}$. 
  In that case, our suspicions are all but confirmed 
  by the class field theory of Serre-Hazewinkel
- \citelist{\cite{serre:60a},\cite{serre:61a},\cite{demazure-gabriel:GroupesAlgebriques}*{Appendice}},
- especially as revisited in \cite{suzuki-yoshida:12a}*{\S~2}. 
+ \cite{serre:60a},\cite{serre:61a},\cite{demazure-gabriel:GroupesAlgebriques}*{Appendice},
+ especially as revisited in \cite{suzuki-yoshida:12a}*{\S 2}. 
  What remains to be done is a careful comparison of 

### 2013-08-25 shanghai.tex
Finished the proof of restriction of scalars over local fields. Yay!
Can you confirm Equation 14?

@@
 DeBacker and Reeder have recently applied Deligne-Lusztig representations to part of the
-local Langlands correspondence \cite{reeder-debacker:09a}.  
-After developing Deligne-Luzstig representations, 
+local Langlands correspondence.% \cite{reeder-debacker:09a}.  
+After developing Deligne-Lusztig representations, 
 the next step Lusztig took in studying representations
@@
 group schemes which are not necessarily connected or finite type.  The main use
-of the term character sheaf is due to Lusztig: it is applied to certain perverse sheaves on connected reductive algebraic groups over algebraically closed fields in \cite{lusztig:85a}*{Def.~2.10} and to certain perverse sheaves on reductive groups over algebraically closed fields with cyclic component groups in the series of papers beginning with \cite{lusztig:disconnected1}.
+of the term character sheaf is of course due to Lusztig.
+It is applied to certain perverse sheaves on connected reductive algebraic groups over algebraically closed fields in \cite{lusztig:85a}*{Def.~2.10} and to certain perverse sheaves on reductive groups over algebraically closed fields with cyclic component groups in the series of papers beginning with \cite{lusztig:disconnected1}.
 When commutative, such groups are extensions of $\ZZ/n\ZZ$ by a torus,
@@
 geometrize all quasicharacters of $T$.  Sections~\ref{sec:bdchar}, \ref{sec:quasichar} and \ref{sec:wrK} also include
-functoriality results that we hope to use in a future discussion of class field theory.
+functoriality results that we hope to use in a future discussion of 
+local class field theory.
 In Section~\ref{sec:transfer} we discuss a transfer principle which allows
 a geometric transfer of characters between characteristic $p$ tori and characteristic $0$ tori.
-We close the paper with Section~\ref{sec:reciprocity}, in which we suggest that quasicharacter sheaves may play a key role in a geometric and categorical form of the local Langlands correspondence for algebraic tori over non-archimedean local fields.
+We close the paper with Section~\ref{sec:reciprocity}, in which we suggest that quasicharacter sheaves may play a key role in a geometric and categorical form of the local Langlands correspondence for algebraic tori over local fields.
 
@@
 Consider the following category $C(G)$.
-Let us say that $f : H\to G$ is a \emph{discrete isogeny} if it is a a finite, surjective
+Let us say that $f : H\to G$ is a \emph{discrete isogeny} if it is a finite, surjective
 \'etale morphism and a morphism of commutative group $\Fq$-schemes, for which
@@
 
-The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$.
-%\Clifton{Do you think I should say more about $P_{n}$?}
-%\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}.
-\Clifton{I took the reference to BLR for $P_n$ out, because it didn't actually give any information. 
-This must be in DG, but I don't have a copy.}
+The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$ between additive functors.
 For a given Néron model $\TT$ of $T$, set
@@
   \labitem{(GN.2)}{truncation}
-  The morphism $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a morphism of group schemes over $\Fq$. 
-  This follows from the fact that $P_{n}$ is a natural transformation between additive functors.
+  The morphism $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes over $\Fq$; 
+  see  \cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}
+  and  \cite{stasinski:12a}*{\S 4}.
   We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.
 \end{enumerate}
-
-\begin{definition}
-The \emph{Greenberg transform of the N\'eron model of $T$} is the pro-group scheme over $\Fq$ given by $\cdef{\GN{T}} \ceq \varprojlim_{n\in \ZZ_{>0}} \GN{T}_{n}$ (with reference to the morphisms $f_n : \GN{T}_{n+1} \to \GN{T}_n$).
-\end{definition}
-
-If $K = \mathbb{Q}_q$ and $T = \Gm{\mathbb{Q}_q}$ then $\GN{T}^0 = \mathbb{W}^*_{\FF_q}$, the group $\FF_q$-scheme of units in the ring scheme $\mathbb{W}_{\FF_q}$.
 
@@
   is uniquely determined by $T$. 
-  To define $F_1$ on objects, one uses the Néron mapping property.
+  To define $F_1$ on morphisms one uses the Néron mapping property.
 
@@
 while the second part shows that Trace of Frobenius is a natural transformation
-$t: F_1 \to F_2$. When further combined with Lemma~\ref{prop:product},
-we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a
+$t_{ - ,n} : F_1 \to F_2$. When further combined with Lemma~\ref{prop:product},
+we see that $F_1$ is an additive functor and $t_{ - ,n}: F_1 \to F_2$ is a
 natural transformation between additive functors.
@@
 
-For any $n< m$ (positive integers) define $f_{n\leq m} : \GN{T}_{m} \to \GN{T}_{n}$ by $f_{n\leq m}\ceq f_n \circ f_{n+1} \circ \cdots \circ f_{m-1}$; also set $f_{n\leq n} \ceq \id_{\GN{T}_n}$.
-Note that $f_{n\leq m}:  \GN{T}_{m} \to \GN{T}_{n}$ is a morphism of group schemes over $\Fq$.
-Let $f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})$ be the functor produced by applying Proposition~\ref{prop:pullback} to $f_{n\leq m}$.
-We now define a category which allows us to extend the notion of quasicharacter sheaf to the pro-group scheme $\GN{T}$.
-
-\begin{definition}
-An object in $\QC(\GN{T})$ is an equivalence class in $\cup_{n} \obj \QC(\GN{T}_n)$ under the relation: $\qcs{L}_n\in \QC(\GN{T}_n)$ is equivalent to $\qcs{L}_{m}\in \QC(\GN{T}_m)$ if $f_{n\leq k}^* \qcs{L}_{n} = f_{m\leq k}^* \qcs{L}_m$ for some $n,m\leq k$.
+\begin{definition}\label{def:objGN}
+The \emph{Greenberg transform of the N\'eron model of $T$} 
+is the pro-group scheme over $\Fq$ given by 
+$\cdef{\GN{T}} \ceq \varprojlim_{n\in \ZZ_{>0}} \GN{T}_{n}$, 
+with reference to the family of  surjective morphisms of 
+$\Fq$-group schemes $f_n : \GN{T}_{n+1} \to \GN{T}_n$.
+\end{definition}
+
+\begin{remark}
+If $K = \mathbb{Q}_q$ and 
+$T = \Gm{\mathbb{Q}_q}$ then $\GN{T}^0 = \mathbb{W}^*_{\FF_q}$, 
+the group scheme (!) over $\Fq$ of units in the ring scheme $\mathbb{W}_{\FF_q}$
+and $\GN{T}$, as a scheme, is the disjoint union of copies of $\mathbb{W}^*_{\FF_q}$
+indexed by the integers. Based on this example, 
+we ask if, for arbitrary $T$, the pro-group scheme $\GN{T}$ is, in fact, a group scheme.
+We have not explored that question.
+\end{remark}
+
+For any  ordered pair of positive integers $n< m$ define 
+$f_{n\leq m} : \GN{T}_{m} \to \GN{T}_{n}$ 
+by $f_{n\leq m}\ceq f_n \circ f_{n+1} \circ \cdots \circ f_{m-1}$; 
+also set $f_{n\leq n} \ceq \id_{\GN{T}_n}$.
+Note that $f_{n\leq m}:  \GN{T}_{m} \to \GN{T}_{n}$ is a surjective morphism 
+of group schemes over $\Fq$.
+Let 
+\[
+f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})
+\]
+be the functor produced by applying Proposition~\ref{prop:pullback} to $f_{n\leq m}$.
+We now define a category which allows us to extend the notion 
+of quasicharacter sheaf to the pro-group scheme $\GN{T}$.
+
+\begin{definition}\label{def:catGN}
+An object in $\QC(\GN{T})$ is an equivalence class in 
+$\cup_{n\in\ZZ_{>0}} \obj \QC(\GN{T}_n)$ under the relation: 
+$\qcs{L}_n\in \QC(\GN{T}_n)$ is equivalent to $\qcs{L}_{m}\in \QC(\GN{T}_m)$ 
+if $f_{n\leq k}^* \qcs{L}_{n} = f_{m\leq k}^* \qcs{L}_m$ for some $n,m\leq k$. 
 Objects in $\QC(\GN{T})$ all take the form
@@
 Maps $[\qcs{L}_n] \to [\qcs{L}_m]$ in $\QC(\GN{T})$ are defined as follows:
-$\Hom([\qcs{L}_n],[\qcs{L}_m])$ is the set of equivalence classes in $\cup_{n,m\leq k} \Hom(f_{n\leq k}^*\qcs{L}_n,f_{m\leq k}^*\qcs{L}_m)$ under the relation: $\alpha_k\in \mor \QC(\GN{T}_k)$ is equivalent to $\beta_l \in \QC(\GN{T}_l)$ if $f_{k\leq i}^*\alpha_k = f_{l\leq i}^* \beta_l$ for some $k,l\leq i$.
+$\Hom([\qcs{L}_n],[\qcs{L}_m])$ is the set of equivalence classes 
+in $\cup_{n,m\leq k} \Hom(f_{n\leq k}^*\qcs{L}_n,f_{m\leq k}^*\qcs{L}_m)$ 
+under the relation: $\alpha_k\in \mor \QC(\GN{T}_k)$ is equivalent to 
+$\beta_l \in \QC(\GN{T}_l)$ if $f_{k\leq i}^*\alpha_k = f_{l\leq i}^* \beta_l$ for some $k,l\leq i$. 
 Maps in $\QC(\GN{T})$ all take the form
@@
 Duals in $\QC(\GN{T})$ are defined by $[\qcs{L}_n]^\vee \ceq [\qcs{L}_n^\vee]$.
-We refer to objects in the rigid symmetric monoidal category $\QC(\GN{T})$ as \emph{quasicharacter sheaves on $\GN{T}$} or \emph{quasicharacter sheaves for $T$}.
+We refer to objects in the rigid symmetric monoidal category 
+$\QC(\GN{T})$ as \emph{quasicharacter sheaves on $\GN{T}$} 
+or \emph{quasicharacter sheaves for $T$}.
 \end{definition}
@@
 \]
-defined by $F_n(\qcs{L}) = [\qcs{L}_n]$ and $F_n(\alpha_n) = [\alpha_n]$, for all positive integers $n\leq m$.
-Passing to isomorphism classes of objects and invoking the universal property of $\varinjlim_{d\in \ZZ_{>0}} \QCiso{\GN{T}_d}$ gives a group homomorphism
-$\theta: \varinjlim_{d\in \ZZ_{>0}} \QCiso{\GN{T}_d} \to \QCiso{\GN{T}}$; this is a bijection 
-with inverse $[\qcs{L}]_{/\text{iso}} \mapsto [\qcs{L}_{/\text{iso}}]$.
-Now use Theorem~\ref{thm:application}.
+defined by $F_n(\qcs{L}) = [\qcs{L}_n]$ and $F_n(\alpha_n) = [\alpha_n]$, 
+for all positive integers $n\leq m$.
+Passing to isomorphism classes of objects and invoking the 
+universal property of $\varinjlim_{n\in \ZZ_{>0}} \QCiso{\GN{T}_n}$ 
+gives a group homomorphism
+$\theta: \varinjlim_{n\in \ZZ_{>0}} \QCiso{\GN{T}_n} \to \QCiso{\GN{T}}$; 
+this is a bijection  with inverse $[\qcs{L}]_{/\text{iso}} \mapsto [\qcs{L}_{/\text{iso}}]$.
+Now use Theorem~\ref{thm:application} and Proposition~\ref{prop:pullback} 
+and the fact that  $\Hom_{\text{qc}}(T(K),\EEx) = \varinjlim_{n\in \ZZ_{>0}} \GN{T}_n(k)^*$ 
+with reference to the family of group homomorphisms 
+dual to $f_{n} : \GN{T}_{n+1}(\Fq) \to \GN{T}_n(\Fq)$.
 \end{proof}
-
-\section{Weil restriction for local fields}
-\label{sec:wrK}
-
-As indicated in the Introduction, we are tantalized 
-by the idea that quasicharacter sheaves for $T$ 
-may play a key role in a new geometric, categorial version 
-of the local Langlands correspondence for algebraic tori 
-over non-archimedean local fields. 
-As with the local Langlands correspondence for algebraic tori over local fields, 
-it should be possible to reduce the essential points of the argument to the case $T= \Gm{K}$,
-provided that the category of quasicharacter sheaves behaves properly with regard to
-Weil restriction; see \cite{yu:09a}*{Thm 7.5 (2)}. 
-The next proposition shows that the category of quasicharacter sheaves for 
-algebraic tori does indeed behave properly with regard to Weil restriction.
-
-\begin{lemma}\label{lemma:wrK}
-Weil restriction is compatible with the Greenberg transform in the following sense: 
-if $e$ is the ramification degree of $K'/K$ then, for every positive integer $n$,
-\begin{equation}%\label{weilgreenberg}
-\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)
-\iso
-\Res_{k'/k} \Gr_{en}(\underline{T'}),
-\end{equation}
-where $k'$ is the residue field for $K'$.
-\end{lemma}
-
-\begin{proof}
-First, note that since $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ 
-is a scheme over $\OK$, 
-the Greenberg transform $\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
-is obtained by base change along $\OK \to \OK/\pK^n$ 
-followed by the Greenberg functor over the Artinian ring $\OK/\pK^n$. 
-On the other hand, since $\underline{T'}$ is a scheme over $\mathcal{O}_{K'}$, 
-the Greenberg transform $\Gr_{en}(\underline{T'})$ is defined by base change along 
-$\mathcal{O}_{K'} \to \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$ 
-followed by the Greenberg functor over the Artinian ring $\mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$; 
-see Definition~\ref{def:Grn}. 
-Note also that 
-\begin{equation}\label{nem}
-\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \iso \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}.
-\end{equation}
-
-Now, to prove the lemma, we may employ the functor of points perspective 
-and exhibit an isomorphism of functors from 
-$\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
-to $\Res_{k'/k} \Gr_{en}(\underline{T'})$ as functors 
-from the category of $\Fq$-algebras to the category of groups.
-To that end, let $R$ be any $\Fq$-module. 
-Let $\mathbb{W}$ be the Witt functor from the category of $\Fq$-algebras to rings. 
-By the definition of the Greenberg transform, the Weil restriction functor and \eqref{nem},
-\[
-\begin{aligned}
-\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R)
-&= \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\left( \OK/\pK^n \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right)\\
-&= \underline{T'}\left(\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right)\\
-&= \underline{T'}\left(\mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right);
-\end{aligned}
-\]
-on the other hand,
-\[
-\begin{aligned}
-\Res_{k'/k} \Gr_{en}(\underline{T'})(R)
-&= \Gr_{en}(\underline{T'}) (R\otimes_{k} k')\\
-&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k')} \mathbb{W}(R\otimes_{k} k')\right)\\
-&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k')} \mathbb{W}(R) \otimes_{\mathbb{W}(k)} \mathbb{W}(k')\right)\\
-&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right).
-\end{aligned}
-\]
-So the ring isomorphism 
-\[
-\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R) \to \Res_{k'/k} \Gr_{en}(\underline{T'})(R)
-\]
-is apparent, as are the commuting ring homomorphisms
-\[
-\begin{tikzcd}
-\arrow{d} \Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R) \arrow{r}{\iso} & \arrow{d} \Res_{k'/k} \Gr_{en}(\underline{T'})(R)\\
-\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R') \arrow{r}{\iso} & \Res_{k'/k} \Gr_{en}(\underline{T'})(R'),
-\end{tikzcd}
-\]
-for every map $R\to R'$ of $\Fq$-algebras.
-\end{proof}
-
-\begin{proposition}\label{prop:wrK}
-Let $K'/K$ be a finite Galois extension; 
-let $k'/k$ be the corresponding finite Galois extension of residue fields.
-Let $T$ be an algebraic torus over $K$ and 
-set $T' = T \times_\Spec{K} \Spec{K'}$.
-The natural inclusion 
-\[
-T \hookrightarrow \Res_{K'/K} T' =: T''
-\]
-induces a map of $k$-schemes
-$\GN{T} \hookrightarrow \GN{T}''$
-and thus a functor on quasicharacter sheaves through pullback:
-\begin{equation}\label{eq:wrK}
-\QC(\GN{T}'') \to \QC(\GN{T}).
-\end{equation}
-Through trace of Frobenius, this functor induces the homomorphism
-\[
-\begin{tikzcd}[column sep=60]
-\Hom_{\text{qc}}(T(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{T(K)}} &\Hom_{\text{qc}}(T(K), \EEx).
-\end{tikzcd}
-\]  
-\end{proposition}
-
-\begin{proof}
-Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} for lft-Neron models
-gives a canonical isomorphism 
-\begin{equation}\label{weilneron}
-\underline{\Res_{K'/K}(T')} \iso \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'}).
-\end{equation}
-By Lemma~\ref{lemma:wrK}, 
-\begin{equation}\label{weilgreenberg}
-\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)
-\iso
-\Res_{k'/k} \Gr_{en}(\underline{T'}).
-\end{equation}
-This gives
-\[
-\GN{T}''_n \iso \Res_{k'/k} \GN{T}'_{en}.
-\]
-\Clifton{Now I'm stuck here.}
-But
-\[
-\GN{T}'_{en} = \Gr_{en}(\underline{T'}) = \Gr_{en}(\underline{T}\times_{\OK} {\mathcal{O}_{K'}}) \iso . . . 
-\]
-Now use Proposition~\ref{prop:csbe}.
-\end{proof}
-
-If we specialize Proposition~\ref{prop:wrK} to the case when 
-$T = \Gm{K}$ then $T'' = \Res_{K'/K} \Gm{K'}$ and we see that the functor $\QC(\GN{T}'')\to \QC(\GN{T})$ is the geometrization and categorification of restriction of quasicharacters from $(K')^\times$ to $K^\times$:
-\[
-\begin{tikzcd}[column sep=60]
-\Hom_{\text{qc}}((K')^\times, \EEx) \arrow{r}{\chi \mapsto \chi\vert_{K^\times}} &\Hom_{\text{qc}}(K^\times, \EEx).
-\end{tikzcd}
-\]
 
@@
 
+\section{Restriction of scalars over local fields}
+\label{sec:wrK}
+
+As indicated in the Introduction, we are tantalized 
+by the idea that quasicharacter sheaves for $T$ 
+may play a key role in a new geometric, categorial version 
+of the local Langlands correspondence for algebraic tori 
+over non-archimedean local fields. 
+As with the local Langlands correspondence for algebraic tori over local fields, 
+it should be possible to reduce the essential points of the argument to the case $T= \Gm{K}$,
+provided that the category of quasicharacter sheaves behaves properly with regard to
+Weil restriction, as in \cite{yu:09a}*{Thm 7.5 (2)}. 
+The next proposition shows that the category of quasicharacter sheaves for 
+algebraic tori does indeed behave properly with regard to Weil restriction.
+
+\begin{lemma}\label{lemma:wrK}
+Weil restriction is compatible with the Greenberg transform in the following sense: 
+if $e$ is the ramification degree of $K'/K$ then, for every positive integer $n$,
+\begin{equation}%\label{weilgreenberg}
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)
+\iso
+\Res_{k'/k} \Gr_{en}(\underline{T'}),
+\end{equation}
+where $k'$ is the residue field for $K'$.
+\end{lemma}
+
+\begin{proof}
+First, note that since $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ 
+is a scheme over $\OK$, 
+the Greenberg transform $\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
+is obtained by base change along $\OK \to \OK/\pK^n$ 
+followed by the Greenberg functor over the Artinian ring $\OK/\pK^n$. 
+On the other hand, since $\underline{T'}$ is a scheme over $\mathcal{O}_{K'}$, 
+the Greenberg transform $\Gr_{en}(\underline{T'})$ is defined by base change along 
+$\mathcal{O}_{K'} \to \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$ 
+followed by the Greenberg functor over the Artinian ring $\mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$; 
+see Definition~\ref{def:Grn}. 
+Note also that 
+\Clifton{I haven't checked this! Have you?}
+\begin{equation}\label{nem}
+\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \iso \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}.
+\end{equation}
+
+Now, to prove the lemma, we may employ the functor of points perspective 
+and exhibit an isomorphism of functors from 
+$\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
+to $\Res_{k'/k} \Gr_{en}(\underline{T'})$ as functors 
+from the category of $\Fq$-algebras to the category of groups.
+To that end, let $R$ be any $\Fq$-module. 
+Let $\mathbb{W}$ be the Witt functor from the category of $\Fq$-algebras to rings. 
+By the definition of the Greenberg transform, the Weil restriction functor and \eqref{nem},
+\[
+\begin{aligned}
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R)
+&= \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\left( \OK/\pK^n \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right)\\
+&= \underline{T'}\left(\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right)\\
+&= \underline{T'}\left(\mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right);
+\end{aligned}
+\]
+on the other hand,
+\[
+\begin{aligned}
+\Res_{k'/k} \Gr_{en}(\underline{T'})(R)
+&= \Gr_{en}(\underline{T'}) (R\otimes_{k} k')\\
+&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k')} \mathbb{W}(R\otimes_{k} k')\right)\\
+&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k')} \mathbb{W}(R) \otimes_{\mathbb{W}(k)} \mathbb{W}(k')\right)\\
+&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right).
+\end{aligned}
+\]
+So the ring isomorphism 
+\[
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R) \to \Res_{k'/k} \Gr_{en}(\underline{T'})(R)
+\]
+is apparent, as are the commuting ring homomorphisms
+\[
+\begin{tikzcd}
+\arrow{d} \Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R) \arrow{r}{\iso} & \arrow{d} \Res_{k'/k} \Gr_{en}(\underline{T'})(R)\\
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R') \arrow{r}{\iso} & \Res_{k'/k} \Gr_{en}(\underline{T'})(R'),
+\end{tikzcd}
+\]
+for every map $R\to R'$ of $\Fq$-algebras.
+\end{proof}
+
+\begin{proposition}\label{prop:wrK}
+Let $K'/K$ be a finite Galois extension and
+let $k'/k$ be the corresponding finite Galois extension of residue fields.
+Let $T$ be an algebraic torus over $K$ and 
+set $T' = T \times_\Spec{K} \Spec{K'}$.
+The canonical closed immersion $T \hookrightarrow \Res_{K'/K} T'$
+induces a map of group pro-schemes $\GN{T} \to \Res_{k'/k} \GN{T}'$ which, through the pull-back functor and the trace of Frobenius, induces the homomorphism
+\[
+\begin{tikzcd}[column sep=60]
+\Hom_{\text{qc}}(T(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{T(K)}} &\Hom_{\text{qc}}(T(K), \EEx).
+\end{tikzcd}
+\]  
+\end{proposition}
+
+\begin{proof}
+Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} to lft-Néron models
+we see that a Néron model for $\Res_{K'/K}(T')$ is $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$;
+see also the proof of \cite{xarles:93a}*{Lemma 2.6}.
+By the Néron mapping property, the canonical closed immersion $T\hookrightarrow \Res_{K'/K}(T')$ extends, uniquely, to a morphism $\underline{T}\to \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ of smooth $\OK$-group schemes.
+Applying the Greenberg transform $\Gr_{n}$ to this morphism
+and using Lemma~\ref{lemma:wrK} defines the morphism of $\Fq$-group schemes
+\begin{equation}\label{men}
+\GN{T}_n \to \Res_{k'/k} \GN{T}'_{en}.
+\end{equation}
+Passing to the pro-group schemes in Definition~\ref{def:objGN} 
+the family of morphisms \eqref{men} determines a morphism of pro-group schemes
+\[
+\GN{T} \to \Res_{k'/k} \GN{T}'.
+\]
+Since $\left(\Res_{k'/k} \GN{T}'_{en} \right)(\Fq) = \left(\GN{T}'_{en}\right)(k')$, the pull-back functor $\QC(\Res_{k'/k} \GN{T}'_{en})\to \QC(\GN{T}_n)$ obtained by applying Proposition~\ref{prop:pullback} to \eqref{men} gives
+\[
+\Hom_{< en}(T'(K'),\EEx) \to \Hom_{< n}(T(K),\EEx).
+\]
+Passing to inverse limits defines
+\[
+\Hom_{\text{qc}}(T(K'),\EEx) \to \Hom_{\text{qc}}(T(K),\EEx).
+\]
+Argue as in Proposition~\ref{prop:csbe} to see that this is indeed restriction of characters.
+\end{proof}
+
+If we specialize Proposition~\ref{prop:wrK} to the case when 
+$T = \Gm{K}$ then $T'' = \Res_{K'/K} \Gm{K'}$ and we see that the functor $\QC(\GN{T}'')\to \QC(\GN{T})$ is the geometrization and categorification of restriction of quasicharacters from $(K')^\times$ to $K^\times$:
+\[
+\begin{tikzcd}[column sep=60]
+\Hom_{\text{qc}}((K')^\times, \EEx) \arrow{r}{\chi \mapsto \chi\vert_{K^\times}} &\Hom_{\text{qc}}(K^\times, \EEx).
+\end{tikzcd}
+\]
+
 \section{Toward geometric reciprocity for tori over local fields}

### 2013-08-25 shanghai.tex
Moved the section on restriction of scalars over local fields.
Added one sentence to the Introduction.

@@
 %\noindent
+In this paper we present a dictionary between quasicharacters of algebraic tori over local fields and quasicharacter sheaves.
 What is a quasicharacter sheaf?
@@
 DeBacker and Reeder have recently applied Deligne-Lusztig representations to part of the
-local Langlands correspondence.% \cite{reeder-debacker:09a}.  
+local Langlands correspondence. % \cite{reeder-debacker:09a}.  
 After developing Deligne-Lusztig representations, 
@@
 
+\section{Restriction of scalars over local fields}
+\label{sec:wrK}
+
+As indicated in the Introduction, we are tantalized 
+by the idea that quasicharacter sheaves for $T$ 
+may play a key role in a new geometric, categorial version 
+of the local Langlands correspondence for algebraic tori 
+over non-archimedean local fields. 
+As with the local Langlands correspondence for algebraic tori over local fields, 
+it should be possible to reduce the essential points of the argument to the case $T= \Gm{K}$,
+provided that the category of quasicharacter sheaves behaves properly with regard to
+Weil restriction, as in \cite{yu:09a}*{Thm 7.5 (2)}. 
+The next proposition shows that the category of quasicharacter sheaves for 
+algebraic tori does indeed behave properly with regard to Weil restriction.
+
+\begin{lemma}\label{lemma:wrK}
+Weil restriction is compatible with the Greenberg transform in the following sense: 
+if $e$ is the ramification degree of $K'/K$ then, for every positive integer $n$,
+\begin{equation}%\label{weilgreenberg}
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)
+\iso
+\Res_{k'/k} \Gr_{en}(\underline{T'}),
+\end{equation}
+where $k'$ is the residue field for $K'$.
+\end{lemma}
+
+\begin{proof}
+First, note that since $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ 
+is a scheme over $\OK$, 
+the Greenberg transform $\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
+is obtained by base change along $\OK \to \OK/\pK^n$ 
+followed by the Greenberg functor over the Artinian ring $\OK/\pK^n$. 
+On the other hand, since $\underline{T'}$ is a scheme over $\mathcal{O}_{K'}$, 
+the Greenberg transform $\Gr_{en}(\underline{T'})$ is defined by base change along 
+$\mathcal{O}_{K'} \to \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$ 
+followed by the Greenberg functor over the Artinian ring $\mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$; 
+see Definition~\ref{def:Grn}. 
+Note also that 
+\Clifton{I haven't checked this! Have you?}
+\begin{equation}\label{nem}
+\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \iso \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}.
+\end{equation}
+
+Now, to prove the lemma, we may employ the functor of points perspective 
+and exhibit an isomorphism of functors from 
+$\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
+to $\Res_{k'/k} \Gr_{en}(\underline{T'})$ as functors 
+from the category of $\Fq$-algebras to the category of groups.
+To that end, let $R$ be any $\Fq$-module. 
+Let $\mathbb{W}$ be the Witt functor from the category of $\Fq$-algebras to rings. 
+By the definition of the Greenberg transform, the Weil restriction functor and \eqref{nem},
+\[
+\begin{aligned}
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R)
+&= \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\left( \OK/\pK^n \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right)\\
+&= \underline{T'}\left(\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right)\\
+&= \underline{T'}\left(\mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right);
+\end{aligned}
+\]
+on the other hand,
+\[
+\begin{aligned}
+\Res_{k'/k} \Gr_{en}(\underline{T'})(R)
+&= \Gr_{en}(\underline{T'}) (R\otimes_{k} k')\\
+&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k')} \mathbb{W}(R\otimes_{k} k')\right)\\
+&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k')} \mathbb{W}(R) \otimes_{\mathbb{W}(k)} \mathbb{W}(k')\right)\\
+&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right).
+\end{aligned}
+\]
+So the ring isomorphism 
+\[
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R) \to \Res_{k'/k} \Gr_{en}(\underline{T'})(R)
+\]
+is apparent, as are the commuting ring homomorphisms
+\[
+\begin{tikzcd}
+\arrow{d} \Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R) \arrow{r}{\iso} & \arrow{d} \Res_{k'/k} \Gr_{en}(\underline{T'})(R)\\
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R') \arrow{r}{\iso} & \Res_{k'/k} \Gr_{en}(\underline{T'})(R'),
+\end{tikzcd}
+\]
+for every map $R\to R'$ of $\Fq$-algebras.
+\end{proof}
+
+\begin{proposition}\label{prop:wrK}
+Let $K'/K$ be a finite Galois extension and
+let $k'/k$ be the corresponding finite Galois extension of residue fields.
+Let $T$ be an algebraic torus over $K$ and 
+set $T' = T \times_\Spec{K} \Spec{K'}$.
+The canonical closed immersion $T \hookrightarrow \Res_{K'/K} T'$
+induces a map of group pro-schemes $\GN{T} \to \Res_{k'/k} \GN{T}'$ which, through the pull-back functor and the trace of Frobenius, induces the homomorphism
+\[
+\begin{tikzcd}[column sep=60]
+\Hom_{\text{qc}}(T(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{T(K)}} &\Hom_{\text{qc}}(T(K), \EEx).
+\end{tikzcd}
+\]  
+\end{proposition}
+
+\begin{proof}
+Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} to lft-Néron models
+we see that a Néron model for $\Res_{K'/K}(T')$ is $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$;
+see also the proof of \cite{xarles:93a}*{Lemma 2.6}.
+By the Néron mapping property, the canonical closed immersion $T\hookrightarrow \Res_{K'/K}(T')$ extends, uniquely, to a morphism $\underline{T}\to \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ of smooth $\OK$-group schemes.
+Applying the Greenberg transform $\Gr_{n}$ to this morphism
+and using Lemma~\ref{lemma:wrK} defines the morphism of $\Fq$-group schemes
+\begin{equation}\label{men}
+\GN{T}_n \to \Res_{k'/k} \GN{T}'_{en}.
+\end{equation}
+Passing to the pro-group schemes in Definition~\ref{def:objGN} 
+the family of morphisms \eqref{men} determines a morphism of pro-group schemes
+\[
+\GN{T} \to \Res_{k'/k} \GN{T}'.
+\]
+Since $\left(\Res_{k'/k} \GN{T}'_{en} \right)(\Fq) = \left(\GN{T}'_{en}\right)(k')$, the pull-back functor $\QC(\Res_{k'/k} \GN{T}'_{en})\to \QC(\GN{T}_n)$ obtained by applying Proposition~\ref{prop:pullback} to \eqref{men} gives
+\[
+\Hom_{< en}(T'(K'),\EEx) \to \Hom_{< n}(T(K),\EEx).
+\]
+Passing to inverse limits defines
+\[
+\Hom_{\text{qc}}(T(K'),\EEx) \to \Hom_{\text{qc}}(T(K),\EEx).
+\]
+Argue as in Proposition~\ref{prop:csbe} to see that this is indeed restriction of characters.
+\end{proof}
+
+If we specialize Proposition~\ref{prop:wrK} to the case when 
+$T = \Gm{K}$ then $T'' = \Res_{K'/K} \Gm{K'}$ and we see that the functor $\QC(\GN{T}'')\to \QC(\GN{T})$ is the geometrization and categorification of restriction of quasicharacters from $(K')^\times$ to $K^\times$:
+\[
+\begin{tikzcd}[column sep=60]
+\Hom_{\text{qc}}((K')^\times, \EEx) \arrow{r}{\chi \mapsto \chi\vert_{K^\times}} &\Hom_{\text{qc}}(K^\times, \EEx).
+\end{tikzcd}
+\]
+
 \section{Transfer of quasicharacter sheaves} \label{sec:transfer}
@@
 
-\section{Restriction of scalars over local fields}
-\label{sec:wrK}
-
-As indicated in the Introduction, we are tantalized 
-by the idea that quasicharacter sheaves for $T$ 
-may play a key role in a new geometric, categorial version 
-of the local Langlands correspondence for algebraic tori 
-over non-archimedean local fields. 
-As with the local Langlands correspondence for algebraic tori over local fields, 
-it should be possible to reduce the essential points of the argument to the case $T= \Gm{K}$,
-provided that the category of quasicharacter sheaves behaves properly with regard to
-Weil restriction, as in \cite{yu:09a}*{Thm 7.5 (2)}. 
-The next proposition shows that the category of quasicharacter sheaves for 
-algebraic tori does indeed behave properly with regard to Weil restriction.
-
-\begin{lemma}\label{lemma:wrK}
-Weil restriction is compatible with the Greenberg transform in the following sense: 
-if $e$ is the ramification degree of $K'/K$ then, for every positive integer $n$,
-\begin{equation}%\label{weilgreenberg}
-\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)
-\iso
-\Res_{k'/k} \Gr_{en}(\underline{T'}),
-\end{equation}
-where $k'$ is the residue field for $K'$.
-\end{lemma}
-
-\begin{proof}
-First, note that since $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ 
-is a scheme over $\OK$, 
-the Greenberg transform $\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
-is obtained by base change along $\OK \to \OK/\pK^n$ 
-followed by the Greenberg functor over the Artinian ring $\OK/\pK^n$. 
-On the other hand, since $\underline{T'}$ is a scheme over $\mathcal{O}_{K'}$, 
-the Greenberg transform $\Gr_{en}(\underline{T'})$ is defined by base change along 
-$\mathcal{O}_{K'} \to \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$ 
-followed by the Greenberg functor over the Artinian ring $\mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$; 
-see Definition~\ref{def:Grn}. 
-Note also that 
-\Clifton{I haven't checked this! Have you?}
-\begin{equation}\label{nem}
-\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \iso \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}.
-\end{equation}
-
-Now, to prove the lemma, we may employ the functor of points perspective 
-and exhibit an isomorphism of functors from 
-$\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
-to $\Res_{k'/k} \Gr_{en}(\underline{T'})$ as functors 
-from the category of $\Fq$-algebras to the category of groups.
-To that end, let $R$ be any $\Fq$-module. 
-Let $\mathbb{W}$ be the Witt functor from the category of $\Fq$-algebras to rings. 
-By the definition of the Greenberg transform, the Weil restriction functor and \eqref{nem},
-\[
-\begin{aligned}
-\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R)
-&= \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\left( \OK/\pK^n \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right)\\
-&= \underline{T'}\left(\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right)\\
-&= \underline{T'}\left(\mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right);
-\end{aligned}
-\]
-on the other hand,
-\[
-\begin{aligned}
-\Res_{k'/k} \Gr_{en}(\underline{T'})(R)
-&= \Gr_{en}(\underline{T'}) (R\otimes_{k} k')\\
-&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k')} \mathbb{W}(R\otimes_{k} k')\right)\\
-&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k')} \mathbb{W}(R) \otimes_{\mathbb{W}(k)} \mathbb{W}(k')\right)\\
-&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right).
-\end{aligned}
-\]
-So the ring isomorphism 
-\[
-\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R) \to \Res_{k'/k} \Gr_{en}(\underline{T'})(R)
-\]
-is apparent, as are the commuting ring homomorphisms
-\[
-\begin{tikzcd}
-\arrow{d} \Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R) \arrow{r}{\iso} & \arrow{d} \Res_{k'/k} \Gr_{en}(\underline{T'})(R)\\
-\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R') \arrow{r}{\iso} & \Res_{k'/k} \Gr_{en}(\underline{T'})(R'),
-\end{tikzcd}
-\]
-for every map $R\to R'$ of $\Fq$-algebras.
-\end{proof}
-
-\begin{proposition}\label{prop:wrK}
-Let $K'/K$ be a finite Galois extension and
-let $k'/k$ be the corresponding finite Galois extension of residue fields.
-Let $T$ be an algebraic torus over $K$ and 
-set $T' = T \times_\Spec{K} \Spec{K'}$.
-The canonical closed immersion $T \hookrightarrow \Res_{K'/K} T'$
-induces a map of group pro-schemes $\GN{T} \to \Res_{k'/k} \GN{T}'$ which, through the pull-back functor and the trace of Frobenius, induces the homomorphism
-\[
-\begin{tikzcd}[column sep=60]
-\Hom_{\text{qc}}(T(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{T(K)}} &\Hom_{\text{qc}}(T(K), \EEx).
-\end{tikzcd}
-\]  
-\end{proposition}
-
-\begin{proof}
-Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} to lft-Néron models
-we see that a Néron model for $\Res_{K'/K}(T')$ is $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$;
-see also the proof of \cite{xarles:93a}*{Lemma 2.6}.
-By the Néron mapping property, the canonical closed immersion $T\hookrightarrow \Res_{K'/K}(T')$ extends, uniquely, to a morphism $\underline{T}\to \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ of smooth $\OK$-group schemes.
-Applying the Greenberg transform $\Gr_{n}$ to this morphism
-and using Lemma~\ref{lemma:wrK} defines the morphism of $\Fq$-group schemes
-\begin{equation}\label{men}
-\GN{T}_n \to \Res_{k'/k} \GN{T}'_{en}.
-\end{equation}
-Passing to the pro-group schemes in Definition~\ref{def:objGN} 
-the family of morphisms \eqref{men} determines a morphism of pro-group schemes
-\[
-\GN{T} \to \Res_{k'/k} \GN{T}'.
-\]
-Since $\left(\Res_{k'/k} \GN{T}'_{en} \right)(\Fq) = \left(\GN{T}'_{en}\right)(k')$, the pull-back functor $\QC(\Res_{k'/k} \GN{T}'_{en})\to \QC(\GN{T}_n)$ obtained by applying Proposition~\ref{prop:pullback} to \eqref{men} gives
-\[
-\Hom_{< en}(T'(K'),\EEx) \to \Hom_{< n}(T(K),\EEx).
-\]
-Passing to inverse limits defines
-\[
-\Hom_{\text{qc}}(T(K'),\EEx) \to \Hom_{\text{qc}}(T(K),\EEx).
-\]
-Argue as in Proposition~\ref{prop:csbe} to see that this is indeed restriction of characters.
-\end{proof}
-
-If we specialize Proposition~\ref{prop:wrK} to the case when 
-$T = \Gm{K}$ then $T'' = \Res_{K'/K} \Gm{K'}$ and we see that the functor $\QC(\GN{T}'')\to \QC(\GN{T})$ is the geometrization and categorification of restriction of quasicharacters from $(K')^\times$ to $K^\times$:
-\[
-\begin{tikzcd}[column sep=60]
-\Hom_{\text{qc}}((K')^\times, \EEx) \arrow{r}{\chi \mapsto \chi\vert_{K^\times}} &\Hom_{\text{qc}}(K^\times, \EEx).
-\end{tikzcd}
-\]
-
 \section{Toward geometric reciprocity for tori over local fields}

### 2013-08-25 shanghai.tex
Fixed a reference in bib.

@@
 If we specialize Proposition~\ref{prop:wrK} to the case when 
-$T = \Gm{K}$ then $T'' = \Res_{K'/K} \Gm{K'}$ and we see that the functor $\QC(\GN{T}'')\to \QC(\GN{T})$ is the geometrization and categorification of restriction of quasicharacters from $(K')^\times$ to $K^\times$:
-\[
-\begin{tikzcd}[column sep=60]
-\Hom_{\text{qc}}((K')^\times, \EEx) \arrow{r}{\chi \mapsto \chi\vert_{K^\times}} &\Hom_{\text{qc}}(K^\times, \EEx).
-\end{tikzcd}
-\]
+$T = \Gm{K}$ then we see how to geometrize and categorify the restriction of quasicharacters from $(K')^\times$ to $K^\times$.
 

### 2013-09-13 shanghai.tex
Small changes resulting from our conversation yesterday: Hmm removed; citation made more specific.

@@
 The category of quasicharacter sheaves on $G$ is not abelian, so $\QC(G)$
-is not a tensor category in the sense of \cite{deligne:02a}. \David{more specific citation}
+is not a tensor category in the sense of \cite{deligne:02a}*{0.1}.
 This rigid monoidal category structure for $\QC(G)$ puts a group
@@
 
-\Clifton{Now this section does mention quasicharacter sheaves.}
-Although this section does not mention quasicharacter sheaves, 
-we will need Proposition~\ref{prop:X} to prove our main result on quasicharacter sheaves, 
-Theorem~\ref{thm:snake}.
+Although the next proposition makes no mention quasicharacter sheaves, 
+it has immediate application to the problem of finding all quasicharacter sheaves
+on finitely generated etale group schemes, as we will see at the end of the section.
 
@@
   the isomorphism class of $\GN{T}_n$ is uniquely determined by $T$
-  \Clifton{Hmmm}
   and the group of isomorphism classes of objects in $\QC(\GN{T}_n)$ 
@@
 Note also that 
-\Clifton{I haven't checked this! Have you?}
 \begin{equation}\label{nem}

### 2013-09-19 shanghai.tex
I got a copy of the paper by Deligne and made a reference to it slightly more specific.
Adding QC-schemes, breaking long lines, fixing typos

@@
   classes of quasicharacter sheaves on the Greenberg transform of the Néron
-  model of $T$, where $K$ is any non-archimdean local field and $T$ is
+  model of $T$, where $K$ is any non-archimedean local field and $T$ is
   any algebraic torus over $K$.
@@
 group schemes which are not necessarily connected or finite type.  The main use
-of the term character sheaf is of course due to Lusztig.
-It is applied to certain perverse sheaves on connected reductive algebraic groups over algebraically closed fields in \cite{lusztig:85a}*{Def.~2.10} and to certain perverse sheaves on reductive groups over algebraically closed fields with cyclic component groups in the series of papers beginning with \cite{lusztig:disconnected1}.
+of the term character sheaf is of course due to Lusztig. It is applied to certain perverse
+sheaves on connected reductive algebraic groups over algebraically closed fields in
+\cite{lusztig:85a}*{Def.~2.10} and to certain perverse sheaves on reductive groups
+over algebraically closed fields with cyclic component groups in the series of papers
+beginning with \cite{lusztig:disconnected1}.  
 When commutative, such groups are extensions of $\ZZ/n\ZZ$ by a torus,
@@
 a geometric transfer of characters between characteristic $p$ tori and characteristic $0$ tori.
-We close the paper with Section~\ref{sec:reciprocity}, in which we suggest that quasicharacter sheaves may play a key role in a geometric and categorical form of the local Langlands correspondence for algebraic tori over local fields.
+We close the paper with Section~\ref{sec:reciprocity}, in which we suggest that quasicharacter
+sheaves may play a key role in a geometric and categorical form of the local Langlands
+correspondence for algebraic tori over local fields.
 
@@
 Throughout this paper, $G$ is a smooth, commutative group scheme locally of finite type
-over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.
+over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.  For the sake of brevity, we
+define a \emph{$\QC$-scheme} to be such a $G$ with the additional property that the
+geometric component group of $G$ is finitely generated.  This last assumption is only
+needed in the proof of Lemma \ref{lemma:section}.
 
@@
 structure on the set $\QCiso{G}$ of isomorphism classes in $\QC(G)$.
-We now begin developing the tools to relate $\QCiso{G}$ to $\Hom(G(\Fq), \EEx)$.
+We now begin developing the tools to relate $\QCiso{G}$ to $G(\Fq)^*$.
 
@@
 The isomorphism $\mu : \bm^* \gqcs{L} \to \LxL$ together with property~\ref{CS.2} guarantee
-that the function $\trFrob{\qcs{L}} : G(\Fq)\to \EEx$ is a group homomorphism.
-It is also clear that $\trFrob{\qcs{L}\otimes \qcs{L'}} = \trFrob{\qcs{L}} \cdot \trFrob{\qcs{L'}}$
-(pointwise multiplication of functions) and $\trFrob{\qcs{L}} = \trFrob{\qcs{L'}}$
-if $\qcs{L} \iso \qcs{L'}$ in $\QC(G)$. In this way we obtain a group homomorphism
+that the function $\trFrob{\qcs{L}} : G(\Fq)\to \EEx$ is a group homomorphism.  If we write
+$\trFrob{\qcs{L}} \cdot \trFrob{\qcs{L'}}$ for pointwise multiplication, then 
+ $\trFrob{\qcs{L}\otimes \qcs{L'}} = \trFrob{\qcs{L}} \cdot \trFrob{\qcs{L'}}$.
+Since $\qcs{L} \iso \qcs{L'}$ implies $\trFrob{\qcs{L}} = \trFrob{\qcs{L'}}$,
+we obtain a group homomorphism
 \[
@@
 \]
-This isomorphism is functorial in the following sense:
+This homomorphism is functorial in the following sense:
 
 \begin{proposition}\label{prop:functorialG}
-Trace of Frobenius $\QCiso{G} \to G(\Fq)$ is a natural transformation 
+Trace of Frobenius $\QCiso{G} \to G(\Fq)^*$ is a natural transformation 
 between the two additive functors 
@@
 \end{enumerate}
-from the category of smooth commutative
-group schemes locally of finite type over $\Fq$ to the category of abelian groups.
+from the category of $\QC$-schemes to the category of abelian groups.
 \end{proposition}
@@
 %\David{insert some commentary on this proposition: it will be very useful to us}
-As a step toward the proof of Proposition~\ref{prop:functorialG} we show that every morphism  $H \to G$ of smooth group schemes locally of finite type over $\Fq$ induces a monoidal functor from quasicharacter sheaves on $G$ to quasicharacters on $H$.
-This simple but important result will also play a role in the proof of many other propositions in this paper.
+As a step toward the proof of Proposition~\ref{prop:functorialG} we show that every
+morphism  $H \to G$ of $\QC$-schemes induces a monoidal functor from quasicharacter
+sheaves on $G$ to quasicharacters on $H$. This simple but important result will also
+play a role in the proof of many other propositions in this paper.
 
 \begin{proposition}\label{prop:pullback}
-  If $f : H\to G$ is a morphism of commutative group schemes locally of finite type over $\Fq$ then
+  If $f : H\to G$ is a morphism of $\QC$-schemes then
   $(\gqcs{L},\mu,\phi) \mapsto (\bf^*\gqcs{L},(\bfxf)^*\mu,\bf^*F)$
@@
 
-Consider the short exact sequence in the category of smooth group
-schemes, locally of finite type over $\Fq$, defining the component
-group scheme for $G$:
+Consider the short exact sequence in the category of $\QC$-schemes
+defining the component group scheme for $G$:
 \begin{equation}\label{eq:pi0}
@@
 \end{equation}
-Since $\pi_0(G)$ is an commutative group scheme, smooth and locally of finite type over $\Fq$, 
+Since $\pi_0(G)$ is also a $\QC$-scheme, 
 Proposition~\ref{prop:pullback} implies that \eqref{eq:pi0} defines a sequence of functors
@@
 
-Finally, let $G'$ be a smooth commutative group scheme locally of finite type over $k'$;
+Finally, let $G'$ be a $\QC$-scheme over $k'$;
 we explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
@@
  && && \arrow{ul} \ker f\times_G G' \arrow{ur} \arrow[hook]{rr} && H\times_G G' \arrow{ur} \arrow{rr} && G' \arrow{ur}{g} & \\
-& V' && \Aut(V) && \arrow[swap,pos=0.7]{ll}{\psi'} \arrow[swap]{uu}{} \ker f'  \arrow[hook]{rr} && \arrow[swap]{uu} H' \arrow[pos=0.8]{rr}{f'} && G\\
- && && \arrow{ul} \ker f'\times_G G' \arrow{uu} \arrow{ur} \arrow[hook]{rr} && \arrow{uu} H'\times_G G' \arrow{ur} \arrow{rr} && \arrow[equals]{uu} G' \arrow[swap]{ur}{g} & 
+& V' && \Aut(V) && \arrow[swap,pos=0.7]{ll}{\psi'} \arrow[swap]{uu}{} \ker f'  \arrow[hook]{rr}
+&& \arrow[swap]{uu} H' \arrow[pos=0.8]{rr}{f'} && G\\
+ && && \arrow{ul} \ker f'\times_G G' \arrow{uu} \arrow{ur} \arrow[hook]{rr}
+ && \arrow{uu} H'\times_G G' \arrow{ur} \arrow{rr} && \arrow[equals]{uu} G' \arrow[swap]{ur}{g} & 
 \end{tikzcd}
@@
 in the sense of \cite{grothendieck:SGA1}*{Expos\'e V, \S 4}. Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$,
-as shown in \cite{kamgarpour:09a}*{App'x B}, this provides an alternate proof of $\QCiso{G} \iso G(\Fq)^*$ when $G$ is a connected algebraic group over $\Fq$.
+as shown in \cite{kamgarpour:09a}*{App'x B}, this provides an alternate proof of
+$\QCiso{G} \iso G(\Fq)^*$ when $G$ is a connected algebraic group over $\Fq$.
 
 In principle, something similar is possible in the more general 
-context of this paper, where $G$ is a smooth group scheme 
-locally of finite type over $\Fq$, to which we now return. 
+context of this paper, where $G$ is a $\QC$-scheme, to which we now return. 
 In this generality, neither of the full subcategories $\QCf(G) \subset \QCb(G) \subset \QC(G)$ are equivalences;
@@
 \'Etale group schemes form a counterpoint to connected groups,
-since the component group of a group scheme locally of finite type over $\Fq$
-is an \'etale group scheme (locally of finite type) over $\Fq$
+since the component group of a $\QC$-scheme
+is an \'etale group scheme, locally of finite type over $\Fq$
 \cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
@@
 
-The main result of Part~\ref{part1} of this paper, 
-the sheaf--function dictionary for $G$ Theorem~\ref{thm:snake}, has a hypothesis: 
-the smooth commutative group scheme locally of finite type must have the 
-property that the geometric component group of $G$ is finitely generated as a group. 
-The genesis of that hypothesis is Lemma~\ref{lemma:section},
-as we use this hypothesis to show the existence of global sections of $\gqcs{L}$ satisfying \eqref{section} for $\mu$.
-Remarkably, Lemma~\ref{lemma:section} is the only crux for this hypothesis;
-that is, if $G$ is any smooth connected group scheme locally of finite type over $\Fq$
+We note that this lemma is the only ingredient of the proof of Theorem~\ref{thm:snake}
+that forces $\QC$-schemes to have finitely generated geometric component group.  In fact,
+if $G$ is any smooth connected group scheme locally of finite type over $\Fq$
 and if each quasicharacter sheaf on the \'etale group scheme $\pi_0(G)$ admits a global section 
-satisfying \eqref{section}, then the conclusion of Theorem~\ref{thm:snake} holds for $G$,
-so there is a sheaf--function dictionary for $G$.
+satisfying \eqref{section}, then the conclusion of Theorem~\ref{thm:snake} holds for $G$.
 
 \begin{proposition}\label{prop:etale}
-  If $G$ is a commutative \'etale group scheme over $\Fq$ and
-  $G(\bFq)$ is finitely generated then there is a canonical
+  If $G$ is a commutative \'etale group scheme over $\Fq$ and $G(\bFq)$ is finitely generated
+  then there is a canonical
   isomorphism
@@
   identity component $G^0$ of $G$ is a connected smooth, 
-  geometrically reduced group scheme of finite type over $\Fq$, by
+  geometrically reduced group scheme of finite type over $\Fq$
    \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}. 
@@
 Our main result regarding quasicharacter sheaves, below, shows that
-trace of Frobenius is an isomorphism in the case that we care about.
+trace of Frobenius is an isomorphism for $\QC$-schemes.
 
@@
   If $G$ is a smooth commutative group scheme locally of finite type over
-  $\Fq$ and if the abelian group $\pi_0(G)(\bFq)$ (the geometric
-  component group) is finitely generated then the trace of Frobenius
+  $\Fq$ and if the abelian group $\pi_0(G)(\bFq)$
+  is finitely generated then the trace of Frobenius
   \[
@@
 \begin{proof}
-  Recall the short exact sequence \eqref{eq:pi0} in the category of smooth group
-  schemes, locally of finite type over $\Fq$, defining the component
-  group scheme for $G$:
+  Recall the short exact sequence \eqref{eq:pi0} in the category of $\QC$-schemes
+  defining the component group scheme for $G$:
   \[
@@
 etale morphisms, smooth morphisms and geometric components.
-Besides Greenberg's original papers, see \cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1}, \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} 
+Besides Greenberg's original papers, see
+\citelist{\cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1} \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6}}
 and the first few sections of \cite{stasinski:12a} 
@@
 
-The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$ between additive functors.
+The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a
+natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$ between additive functors.
 For a given Néron model $\TT$ of $T$, set
@@
   \labitem{(GN.1)}{smooth} 
-  $\GN{T}_n$ is a smooth commutative group scheme locally of finite type over $\Fq$ 
-  and the component group of $\GN{T}_n$ is geometrically finitely generated. 
+  $\GN{T}_n$ is a $\QC$-scheme. 
   Note that $\underline{T}$ is a smooth group scheme over $\OK$, by construction. 
@@
 The canonical closed immersion $T \hookrightarrow \Res_{K'/K} T'$
-induces a map of group pro-schemes $\GN{T} \to \Res_{k'/k} \GN{T}'$ which, through the pull-back functor and the trace of Frobenius, induces the homomorphism
+induces a map of group pro-schemes $\GN{T} \to \Res_{k'/k} \GN{T}'$ which,
+through the pull-back functor and the trace of Frobenius, induces the homomorphism
 \[
@@
 see also the proof of \cite{xarles:93a}*{Lemma 2.6}.
-By the Néron mapping property, the canonical closed immersion $T\hookrightarrow \Res_{K'/K}(T')$ extends, uniquely, to a morphism $\underline{T}\to \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ of smooth $\OK$-group schemes.
+By the Néron mapping property, the canonical closed immersion
+$T\hookrightarrow \Res_{K'/K}(T')$ extends, uniquely, to a morphism
+$\underline{T}\to \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ of smooth $\OK$-group schemes.
 Applying the Greenberg transform $\Gr_{n}$ to this morphism
@@
 \]
-Since $\left(\Res_{k'/k} \GN{T}'_{en} \right)(\Fq) = \left(\GN{T}'_{en}\right)(k')$, the pull-back functor $\QC(\Res_{k'/k} \GN{T}'_{en})\to \QC(\GN{T}_n)$ obtained by applying Proposition~\ref{prop:pullback} to \eqref{men} gives
+Since $\left(\Res_{k'/k} \GN{T}'_{en} \right)(\Fq) = \left(\GN{T}'_{en}\right)(k')$,
+the pull-back functor $\QC(\Res_{k'/k} \GN{T}'_{en})\to \QC(\GN{T}_n)$
+obtained by applying Proposition~\ref{prop:pullback} to \eqref{men} gives
 \[
@@
 natural comparison between characters of $T(K)$ and of $T'(K')$.
-This comparison of has been made precise in \cite{chai-yu:01a}, \David{more specific citation?}\Clifton{In this case, maybe not necessary.}
-building on ideas of \cite{deligne:84a}.
+This comparison of has been made precise in \cite{chai-yu:01a}, 
+building on ideas in \cite{deligne:84a}*{\S 1}.
 

### 2013-09-19 shanghai.tex
= to \ceq through line 1235

@@
 $\Gal(\bFq/\Fq)$ on $\bG$. We now review this point of view for later use in
-Section~\ref{sec:basechange}.  If $w = \Frob{\Fq}^n$ we write $w_G$ for $\Frob{G}^n$.
+Section~\ref{sec:basechange}.  If $w \ceq \Frob{\Fq}^n$ we write $w_G$ for $\Frob{G}^n$.
 For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gqcs{L}\to \gqcs{L}$ by
@@
 Let $\qcs{L}$ be a quasicharacter sheaf on $G$. Define $f : G\to G\times G$
-by $f(g_1,g_2) = (g_1,e_2,e_1,g_2)$. Observe that $m\circ f = \id_G$. 
+by $f(g_1,g_2) \ceq (g_1,e_2,e_1,g_2)$. Observe that $m\circ f = \id_G$. 
 Let $p_1$, $p_2$ be the projection morphisms pictured below:
@@
 \begin{proposition} \label{prop:csbe}
-Set $G_{k'} = G\times_\Spec{k} \Spec{k'}$ and let
+Set $G_{k'} \ceq G\times_\Spec{k} \Spec{k'}$ and let
 \[
@@
 
-If $\qcs{L} = (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$ we may define
-a quasicharacter sheaf $\qcs{L}' = (\gqcs{L}, \mu, \phi_{k'})$ on the base change
+If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$ we may define
+a quasicharacter sheaf $\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
 $G_{k'}$ of $G$ to $k'$ by setting
 \[
-\phi_{k'} = \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi).
+\phi_{k'} \ceq \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi).
 \]
@@
 \begin{proof}
-Let $\qcs{L} = (\gqcs{L}, \mu, \phi) \in \QC(G)$ and $x \in G(k')$ and write $\Frob{}$ for $\Frob{G}$.
+Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and $x \in G(k')$ and write $\Frob{}$ for $\Frob{G}$.
 The value $t_{G_{k'}}(\nu_{k'/k}(\qcs{L})(x)$ is given by the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
@@
  This functor preserves local constancy, so takes local systems to local systems. 
- Set $\mu = b_{G\times G}^*\mu_0$; clearly, this satisfies Condition~\ref{CS.2} 
+ Set $\mu \ceq b_{G\times G}^*\mu_0$; clearly, this satisfies Condition~\ref{CS.2} 
  with $b_G^*\qcs{L}_0$ playing the role of $\gqcs{L}$.
@@
 The dual of $(f,\psi)$ is $(f,\psi)^\vee \ceq (f,\psi^\vee)$ 
-where $\psi^\vee : \ker f \to \Aut(V^\vee)$ and $V^\vee = \Hom_\text{vec}(V,\EE)$. 
+where $\psi^\vee : \ker f \to \Aut(V^\vee)$ and $V^\vee \ceq \Hom_\text{vec}(V,\EE)$. 
 The verification that these operations make $C(G)$ a tensor category is straightforward.
@@
 As in Lemma~\ref{lemma:finite-pull-back}, we have $m^*(f,\psi) = (f_m,\psi_m)$
-where $f_m$ and $\psi_m$ are pictured below, where $H_m = H\times_G(G\times G)$.
+where $f_m$ and $\psi_m$ are pictured below, where $H_m \ceq H\times_G(G\times G)$.
 \[
@@
 Choose a basis $\{ v_1 \}$ for $V$; then $\{ v_1\otimes v_1 \}$ is a basis for $V\otimes V$.
-Define $T : V \to V\otimes V$ by $T(v_1) = v_1\otimes v_1$. Then the lower part of this
+Define $T : V \to V\otimes V$ by $T(v_1) \ceq v_1\otimes v_1$. Then the lower part of this
 diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G)$.
@@
   Then, as in Section~\ref{sec:bounded}, $(\qcs{L}_0,\mu_0)$ is an object in $\QCb(G)$ 
-  and $\qcs{L} = (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{L}_0,b_{G\times G}^*\mu_0)$ in $\QC(G)$.
+  and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{L}_0,b_{G\times G}^*\mu_0)$ in $\QC(G)$.
   Thus, the full and faithful functor $B_G^* : \QCb(G) \to \QC(G)$ from Section~\ref{sec:bounded}
@@
   in particular, the action of $\Gal(\bFq/\Fq)$ on $\ker f$ is trivial.
-  Let $V = \EE$ and let $\psi : \ker f \to \Aut(V)$ be the representation given by 
-  $\psi(g)(v) = \trFrob{\qcs{L}}(g) v$ for $v\in V$. 
+  Let $V \ceq \EE$ and let $\psi : \ker f \to \Aut(V)$ be the representation given by 
+  $\psi(g)(v) \ceq \trFrob{\qcs{L}}(g) v$ for $v\in V$. 
   Then $(f,\psi)$ is a finite quasicharacter sheaf.
@@
   as follows ({\it cf} \cite{laumon:87a}*{1.1.3} or, ultimately, \cite{deligne:SGA4.5}*{Sommes trigonométriques}).
-  First, recall that $L_G(f,\psi) = (L(f,\psi), \mu(f,\psi))$.
+  First, recall that $L_G(f,\psi) \ceq (L(f,\psi), \mu(f,\psi))$.
   Let $k'/k$ be any degree-$n$ extension and let $\Nm : k'\to k$ be the norm map. 

### 2013-09-19 shanghai.tex
Modifications to the abstract and introduction; please look at them. Other small changes ....
Fixed ell at the beginning of the paper (we seem to have forgotten do
do that). Typo in Finite QC Sheaves. All other changes are documented
in the file (comments).

@@
   of quasicharacter sheaves on $G$ is canonically isomorphic to the group
-  of characters of $G(\Fq)$. We use this result to exhibit an
+  of characters of $G(\Fq)$. Then, for any non-archimedean local field $K$
+  and any algebraic torus $T$ over $K$, we use this result to produce a functorial
   isomorphism between quasicharacters of $T(K)$ and isomorphism
   classes of quasicharacter sheaves on the Greenberg transform of the Néron
-  model of $T$, where $K$ is any non-archimedean local field and $T$ is
-  any algebraic torus over $K$.
+  model of $T$.
   \end{abstract}
@@
 %\noindent
-In this paper we present a dictionary between quasicharacters of algebraic tori over local fields and quasicharacter sheaves.
+In this paper we find a dictionary between quasicharacters of algebraic tori over local fields and quasicharacter sheaves.
+
 What is a quasicharacter sheaf?
@@
 
-In Part 1 of this paper we study the category $\QC(G)$ of quasicharacter sheaves.
-Since it is a rigid symmetric monoidal category
+In Part 1 of this paper we study the category $\QC(G)$ of quasicharacter sheaves on $G$.
+Since $\QC(G)$ is a rigid symmetric monoidal category
 the set of isomorphism classes $\QCiso{G}$ forms a group.
@@
 \]
-and show that it is an isomorphism in Theorem~\ref{thm:snake}, assuming only
-that the geometric component group of $G$ is finitely generated.
+and show in Theorem~\ref{thm:snake} that it is an isomorphism, 
+assuming that the geometric component group of $G$ is finitely generated.
 
@@
 Let $T$ be a torus defined over $K$.  The N\'eron model $\TT$ of $T$
-is a smooth group scheme over $\OK$ with generic fiber $T$ and a canonical isomorphism
+is a smooth group scheme over $\OK$ with generic fibre $T$ and a canonical isomorphism
 $\TT(\OK) \cong T(K)$.  For each positive integer $n$, let $\GN{T}_n$ be the
@@
 \]  
-We refer to finite-depth characters of $T(K)$ as quasicharacters and
-describe a pro-group scheme $\GN{T}$ simultaneously geometrizing all such quasicharacters.
-
-We have not yet fully explored the applications of such a geometrization, but want to highlight
-some of the potential benefits of Theorem~\ref{thm:application}.  Characters on $T$ have limited
+We also describe a pro-group scheme $\GN{T}$ simultaneously geometrizing all quasicharacters ({\it i.e.}, finite-depth characters) of $T(K)$.
+
+While we have not yet fully explored the applications of such a geometrization, we want to highlight
+some of the potential benefits of Theorem~\ref{thm:application} here. Characters on $T$ have limited
 functoriality: they can be pulled back along maps to $T$, but it is less clear what to do with them
-in the presence of maps from $T$ to other reductive groups.  Sheaves, on the other hand, come
+in the presence of maps from $T$ to other groups.  Sheaves, on the other hand, come
 equipped with a host of functors, including pushforward. 
+We hope to use this to our advantage as we work toward an adaptation of Lusztig's theory of characters sheaves to the study of characters of admissible representations of reductive $p$-adic groups that extends beyond the case of $p$-adic tori.
 
@@
 of finite groups of Lie type was to introduce character sheaves for reductive groups over $\Fq$.
-We hope that our quasicharacter sheaves can provide a stepping stone to a similar theory for
+As suggested above above, we hope that our quasicharacter sheaves 
+can provide a stepping stone to a similar theory for
 representations of $p$-adic groups.
@@
 
+We fix a prime $\ell$, invertible in $\Fq$.
 For any group $A$, we will denote by $A^*$ the dual group $\Hom_\text{grp}(A, \EEx)$.
@@
 Let us say that $f : H\to G$ is a \emph{discrete isogeny} if it is a finite, surjective
-\'etale morphism and a morphism of commutative group $\Fq$-schemes, for which
+\'etale morphism and a morphism of commutative group $\Fq$-schemes for which
 the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $f^{-1}({\bar e})$ is trivial.
@@
 \]
-In this form we could treat $g^*$ as a functor $G(G')\to C(G)$,
+In this form we could treat $g^*$ as a functor $C(G')\to C(G)$,
 where it not for the fact that pull-back is defined only up to isomorphism.
@@
   so that $\Frob{\Fq}^m$ acts trivially on $X$; write $\Fqm$ for the degree
-  $m$ extension of $\Fq$ and $\Gamma_m$ for $\Gal(\Fqm/\Fq)$.  Since
+  $m$ extension of $\Fq$ in $\bFq$ and $\Gamma_m$ for $\Gal(\Fqm/\Fq)$.  Since
   $T^m-1$ factors as a squarefree product of cyclotomic polynomials,
@@
   product of Dedekind domains.  Therefore $X$ decomposes into a direct
-  sum of cyclic $\ZZ[\Gamma_m]$-modules \cite{brandal:CommRingsFGModDecompose}, \David{more specific citation}
+  sum of cyclic $\ZZ[\Gamma_m]$-modules \cite{brandal:CommRingsFGModDecompose}, \David{more specific citation} \Clifton{I'm tracking this down.}
   each of the \David{Add a reference to this section}
@@
     $\omega(\zeta - 1) \equiv 1 \pmod{P^s}$ and set
-    \begin{equation} \label{alpha-def}
-      \alpha = \tilde{f}(\omega).
-    \end{equation}
+    %\begin{equation} \label{alpha-def}
+     $ \alpha = \tilde{f}(\omega)$.
+    %\end{equation}
     Then $A_c + h(1)\omega$ is fixed under multiplication by $\zeta$
@@
   $x = \zeta^{\phi(d)-1}$.  Write
-  $\Phi_d(T) = T^{\phi(d)} - b_{\phi(d)-1}T^{\phi(d)-1} - \cdots - b_0$
+  \[\Phi_d(T) = T^{\phi(d)} - b_{\phi(d)-1}T^{\phi(d)-1} - \cdots - b_0\]
   and set
-  $$B = \sum_{i=0}^{\phi(d)-1} -\zeta^i + b_i \sum_{j=0}^{i-1} \zeta^j.$$
+  $$B = b_i \sum_{j=0}^{i-1} \zeta^j -  \sum_{i=0}^{\phi(d)-1} \zeta^i.$$
   We have
@@
     \frac{\psi(\zeta^{\phi(d)})}{\psi(\zeta^{\phi(d)-1})\tilde{f}(\zeta^{\phi(d)-1})}
-    &= \frac{\psi(b_{\phi(d)-1}\zeta^{\phi(d)-1} + \cdots + b_0)}{\psi(\zeta^{\phi(d)-1})\tilde{f}(\zeta^{\phi(d)-1})} \\
-    &= \alpha^{-\Phi_d(1)} \tilde{f}(B)
+    &= \frac{\psi(b_{\phi(d)-1}\zeta^{\phi(d)-1} + \cdots + b_0)}{\psi(\zeta^{\phi(d)-1})\tilde{f}(\zeta^{\phi(d)-1})} 
+    = \alpha^{-\Phi_d(1)} \tilde{f}(B).
   \end{align*}
@@
 This follows from Proposition~\ref{prop:etale} by setting $X=G(\bFq)$ in Proposition~\ref{prop:X}.
+Recall that $G \mapsto G(\bFq)$ defines an equivalence of categories from commutative \'etale group schemes over $\Fq$ to commutative groups equipped with \emph{continuous} actions by $\Gal(\bFq/\Fq)$; see, for example, \cite{vdGeer-Moonen:AbelianVarieties}*{Prop 3.26}.
 \end{proof}
@@
   be the commutative diagram of abelian groups obtained by applying
-  Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.  Since $k$ is perfect
-  \cite{stacks-project}*{\href{http://stacks.math.columbia.edu/tag/035X}{Tag 035X}} implies that
+  Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.
+
+   We claim that $\ker \trFrob{G^0} =0$ and $\coker \trFrob{G^0}=0$. 
+   This follows from Proposition~\ref{prop:connected} 
+   once we confirm that $G^0$ is an algebraic group (it is clearly connected).
+   To see this, note that $G^0$ is a smooth group scheme of finite type over $\Fq$ by \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}. 
+   Since $k$ is perfect, $G^0$ is also reduced, by
+  \cite{stacks-project}*{\href{http://stacks.math.columbia.edu/tag/035X}{Tag 035X}}.
   \David{Need another reference that an algebraic group over an algebraically closed field is reduced}
-  $G$ is reduced.  Since $G^0$ is a finite type
-  \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}, it is thus a connected algebraic group and 
-  Proposition~\ref{prop:connected} implies that $\ker \trFrob{G^0} =0$ and $\coker \trFrob{G^0}=0$.
+  \Clifton{I'm working on this too.}
+  Thus, $G^0$ is indeed an algebraic group.
+
   By Propositions~\ref{prop:etale} and \ref{prop:X}, $\ker \trFrob{\pi_0(G)}=0$

### 2013-09-19 shanghai.tex
Agonizing over the proof that G^0 is an algebraic group. Otherwise minor changes.

@@
 Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and $x \in G(k')$ and write $\Frob{}$ for $\Frob{G}$.
-The value $t_{G_{k'}}(\nu_{k'/k}(\qcs{L})(x)$ is given by the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
+The value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ is given by the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
+\Clifton{Please note what I did here.}
 while the value $\Nm^*(t_G(\qcs{L}))(x)$ is given by the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
@@
   $\tau_\qcs{L}(\Frob{k})$ to $G(k)$ is just $\trFrob{\qcs{L}}$.
-  In general, conditions \ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
-  the scalar $\tau_\qcs{L}(\Frob{k})(x)$ is non-zero.  Moreover, condition~\ref{cs.1} forces
+  In general, Conditions~\ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
+  the scalar $\tau_\qcs{L}(\Frob{k})(x)$ is non-zero.  Moreover, Condition~\ref{cs.1} forces
   $\tau_\qcs{L}(\Frob{\Fq})(x+y) = \tau_\qcs{L}(\Frob{\Fq})(x) \ \tau_\qcs{L}(\Frob{\Fq})(y)$
@@
 	It follows that $G^0$ is a connected algebraic group.
+	\Clifton{I'm not happy with our argument that $G^0$ is an algebraic group.}
     By Proposition~\ref{prop:connected}, every
@@
 
-   We claim that $\ker \trFrob{G^0} =0$ and $\coker \trFrob{G^0}=0$. 
-   This follows from Proposition~\ref{prop:connected} 
-   once we confirm that $G^0$ is an algebraic group (it is clearly connected).
-   To see this, note that $G^0$ is a smooth group scheme of finite type over $\Fq$ by \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}. 
-   Since $k$ is perfect, $G^0$ is also reduced, by
-  \cite{stacks-project}*{\href{http://stacks.math.columbia.edu/tag/035X}{Tag 035X}}.
-  \David{Need another reference that an algebraic group over an algebraically closed field is reduced}
-  \Clifton{I'm working on this too.}
-  Thus, $G^0$ is indeed an algebraic group.
-
-  By Propositions~\ref{prop:etale} and \ref{prop:X}, $\ker \trFrob{\pi_0(G)}=0$
+  In the proof of Proposition~\ref{prop:restriction} we saw that $G^0$ is an algebraic group over $\Fq$. % clearly connected. 
+  It now follows from Proposition~\ref{prop:connected} 
+  that $\ker \trFrob{G^0} =0$ and $\coker \trFrob{G^0}=0$. 
+  On the other hand, it follows from Propositions~\ref{prop:etale} and \ref{prop:X}, $\ker \trFrob{\pi_0(G)}=0$
   and $\coker \trFrob{\pi_0(G)}=0$.

### 2013-09-20 shanghai.tex
Finally found the reference we needed to show that G^0 is an algebraic group!

@@
   identity component $G^0$ of $G$ is a connected smooth, 
-  geometrically reduced group scheme of finite type over $\Fq$
+  group scheme of finite type over $\Fq$, reduced over some finite extension of $\Fq$, by
    \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}. 
-	Since $\Fq$ is a finite field, $G^0$ is actually reduced over $\Fq$;
-	see \cite{stacks-project}*{\href{http://stacks.math.columbia.edu/tag/035X}{Tag 035X}}.
-	It follows that $G^0$ is a connected algebraic group.
-	\Clifton{I'm not happy with our argument that $G^0$ is an algebraic group.}
+	Since $\Fq$ is a finite field and hence perfect, $G^0$ is actually reduced over $\Fq$;
+	see \cite{EGAIV2}*{Prop 6.4.1}.
+	Since every group scheme over a field is separated 
+	(see, for example, \cite{vdGeer-Moonen:AbelianVarieties}*{3.12}),  
+	it follows that $G^0$ is a connected algebraic group.
     By Proposition~\ref{prop:connected}, every

### 2013-09-20 shanghai.tex
Enumerated some items in the introduction. I'm not sure I like the result. What's your opinion?

@@
 While we have not yet fully explored the applications of such a geometrization, we want to highlight
-some of the potential benefits of Theorem~\ref{thm:application} here. Characters on $T$ have limited
+some of the potential benefits of Theorem~\ref{thm:application} here. 
+\begin{enumerate}
+\item
+Characters on $T$ have limited
 functoriality: they can be pulled back along maps to $T$, but it is less clear what to do with them
@@
 We hope to use this to our advantage as we work toward an adaptation of Lusztig's theory of characters sheaves to the study of characters of admissible representations of reductive $p$-adic groups that extends beyond the case of $p$-adic tori.
-
+\item
 DeBacker and Reeder have recently applied Deligne-Lusztig representations to part of the
@@
 of finite groups of Lie type was to introduce character sheaves for reductive groups over $\Fq$.
-As suggested above above, we hope that our quasicharacter sheaves 
+We hope that our quasicharacter sheaves 
 can provide a stepping stone to a similar theory for
 representations of $p$-adic groups.
-
+\item
 The scope of the Langlands program has grown explosively in the past several decades, and
@@
 program to be applied to the classic context.
-
+\item
 Finally, we are tantalized by the possibility of providing an alternate perspective on local class field theory
@@
 would yield a different description of the Artin reciprocity map.
+\end{enumerate}
 

### 2013-09-20 shanghai.tex
Added Warfield to the bibliography.

--- 2013-09-20 shanghai.tex
@@
 In this paper we find a dictionary between quasicharacters of algebraic tori over local fields and quasicharacter sheaves. 
-
+%
 What is a quasicharacter sheaf?
@@
 While we have not yet fully explored the applications of such a geometrization, we want to highlight
-some of the potential benefits of Theorem~\ref{thm:application} here. Characters on $T$ have limited
+some of the potential benefits of Theorem~\ref{thm:application}. 
+%\begin{enumerate}
+%\item
+Characters on $T$ have limited
 functoriality: they can be pulled back along maps to $T$, but it is less clear what to do with them
@@
 We hope to use this to our advantage as we work toward an adaptation of Lusztig's theory of characters sheaves to the study of characters of admissible representations of reductive $p$-adic groups that extends beyond the case of $p$-adic tori.
-
+%\item
 DeBacker and Reeder have recently applied Deligne-Lusztig representations to part of the
@@
 of finite groups of Lie type was to introduce character sheaves for reductive groups over $\Fq$.
-As suggested above above, we hope that our quasicharacter sheaves 
+We hope that our quasicharacter sheaves 
 can provide a stepping stone to a similar theory for
 representations of $p$-adic groups. 
-
+%\item
 The scope of the Langlands program has grown explosively in the past several decades, and
@@
 program to be applied to the classic context. 
-
+%\item
 Finally, we are tantalized by the possibility of providing an alternate perspective on local class field theory
@@
 would yield a different description of the Artin reciprocity map.
+%\end{enumerate}
 
@@
   for $x \in X$.  In fact, we may replace the construction of $\psi$
+    \Clifton{I'm not sure I understand what you mean here.}
   for all $\ZZ[\Gal(\bFq/\Fq)]$-modules $X$ with the construction of
@@
 
-  Since the action of $\Gal(\bFq/\Fq)$ is continuous, there is an $m$
-  so that $\Frob{\Fq}^m$ acts trivially on $X$; write $\Fqm$ for the degree
-  $m$ extension of $\Fq$ in $\bFq$ and $\Gamma_m$ for $\Gal(\Fqm/\Fq)$.  Since
+  The $\ZZ[\Gal(\bFq/\Fq)]$-module $X$ decomposes into 
+  a finite direct sum of cyclic $\ZZ[\Gal(\bFq/\Fq)]$-modules. 
+  To see this, observe first that since the action of $\Gal(\bFq/\Fq)$ is continuous, 
+  there is a positive integer $m$ so that $\Frob{\Fq}^m$ acts trivially on $X$; 
+  write $\Fqm$ for the degree $m$ extension of $\Fq$ in $\bFq$ 
+  and $\Gamma_m$ for $\Gal(\Fqm/\Fq)$.  Since
   $T^m-1$ factors as a squarefree product of cyclotomic polynomials,
@@
   maximal order in a number field and thus $\ZZ[\Gamma_m]$ is a
-  product of Dedekind domains.  Therefore $X$ decomposes into a direct
-  sum of cyclic $\ZZ[\Gamma_m]$-modules \cite{brandal:CommRingsFGModDecompose}, \David{more specific citation} \Clifton{I'm tracking this down.}
-  each of the \David{Add a reference to this section}
-  form $\ZZ[\Gamma_m] / I$ for some ideal $I \subset \ZZ[\Gamma_m]$.
+  product of Dedekind domains. Combining \cite{Warfield:Decomposability}*{Theorem 3}
+  and \cite{brandal:CommRingsFGModDecompose}*{Lemma 4.1}, it now follows that 
+  $X$ decomposes into a direct sum of cyclic $\ZZ[\Gamma_m]$-modules, 
+  each of the form $\ZZ[\Gamma_m] / I$ for some ideal $I \subset \ZZ[\Gamma_m]$.
   The ideal $I$ corresponds to a direct product of ideals $I_d$ in the

### 2013-09-21 shanghai.tex
Introduced Gamma. Fixed a typo.

@@
 if it is a finite, surjective \'etale morphism and 
-the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $f^{-1}{\bar e}$ is trivial.
+the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $f^{-1}({\bar e})$ is trivial.
 
@@
 
-  Extensions of
+  Set $\Gamma = \Gal(\bFq/\Fq)$. Extensions of
   $G^0(\bFq)$ by $A(\bFq)$, such as $A(\bFq) \to H^0(\bFq) \to G^0(\bFq)$,

### 2013-09-23 shanghai.tex
More = -> \ceq

@@
 
+%amsmath replacements for \atop
+\newcommand{\latop}[2]{\genfrac{}{}{0pt}{0}{#1}{#2}}
+\newcommand{\partop}[2]{\genfrac{(}{)}{0pt}{0}{#1}{#2}}
+
 \makeatletter
@@
  over $\Fq$ and if $G(\bFq)$ is finitely generated, then there is a global section
- $s = \{ s(x) \in \gqcs{L}_x \tq x \in G(\bFq) \}$ satisfying
+ $s \ceq \{ s(x) \in \gqcs{L}_x \tq x \in G(\bFq) \}$ satisfying
  \begin{equation}\label{section}
@@
   Using Lemma~\ref{lemma:section}, 
-  we may choose a section $s = \{ s(x) \in \gqcs{L}_x \tq x \in G(\bFq) \}$ satisfying \eqref{section}.
+  we may choose a section $s \ceq \{ s(x) \in \gqcs{L}_x \tq x \in G(\bFq) \}$ satisfying \eqref{section}.
   We will construct a group isomorphism between $\QCiso{G}$ and
@@
   $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
-  defined by $\tau_0(\Frob{\Fq}) = \,^{\Frob{\Fq}} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
+  defined by $\tau_0(\Frob{\Fq}) \ceq \,^{\Frob{\Fq}} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
   so $\tau_2$ and $\tau_1$ are cohomologous. Thus
@@
   $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}}a \cdot a^{-1})$. 
-  Define $\alpha : \qcs{L}\to \qcs{L'}$ by $\alpha_x(s(x)) = a(x) s'(x)$, for each $x\in G(\bFq)$.
+  Define $\alpha : \qcs{L}\to \qcs{L'}$ by $\alpha_x(s(x)) \ceq a(x) s'(x)$, for each $x\in G(\bFq)$.
   It is straightforward to check that $\alpha$ satisfies condition~\ref{cs.3}
-  and that $\alpha^{-1} : \qcs{L'}\to \qcs{L}$, defined by $\alpha^{-1}_x(s'(x)) = a(x)^{-1} s(x)$, 
+  and that $\alpha^{-1} : \qcs{L'}\to \qcs{L}$, defined by $\alpha^{-1}_x(s'(x)) \ceq a(x)^{-1} s(x)$, 
   is its inverse. Thus, $\qcs{L} \iso \qcs{L'}$ in $\QC(G)$. 
@@
  Finally, to show that \eqref{pich1} is surjective, pick $[\tau]\in \Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
- For each $x\in G(\bFq)$, set $\gqcs{L}_x = \EE$.
+ For each $x\in G(\bFq)$, set $\gqcs{L}_x \ceq \EE$.
  Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by
- $\mu_{x,y}(1) = 1\otimes1$, for $x,y\in G(\bFq)$; 
+ $\mu_{x,y}(1) \ceq 1\otimes1$, for $x,y\in G(\bFq)$; 
  clearly, $\mu$ satisfies condition~\ref{cs.1}.
- Define $\phi_x : \gqcs{L}_{\Frob{\Fq}} \to \gqcs{L}_x$ by $\phi_x(1) = \tau(\Frob{\Fq})(x)$,
+ Define $\phi_x : \gqcs{L}_{\Frob{\Fq}} \to \gqcs{L}_x$ by $\phi_x(1) \ceq \tau(\Frob{\Fq})(x)$,
  for each $x\in G(\bFq)$. 
  Then $\phi$ satisfies condition~\ref{cs.2} because $\tau \in Z^1(\Weil{\Fq},G(\bFq)^*)$.
- In this way we have built a quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ 
+ In this way we have built a quasicharacter sheaf $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ 
  from $\tau \in \Hh^1(\Weil{\Fq}, G(\bFq)^*)$ such that the image of $\qcs{L}_{/\text{iso}}$
@@
  \qquad \text{defined by}\qquad
-   \rho([z])(x) = z(\Frob{\Fq})(x),
+   \rho([z])(x) \ceq z(\Frob{\Fq})(x),
 \]
@@
   choose a polynomial
-  $$h(T) = a_rT^r + a_{r-1}T^{r-1} + \cdots + a_0$$
+  $$h(T) \ceq a_rT^r + a_{r-1}T^{r-1} + \cdots + a_0$$
   so that $P^s = (p^s, h(\zeta_d))$.
@@
   \begin{equation} \label{eq:psi-def}
-    \psi(\zeta^i) = \alpha \prod_{j=0}^{i-1} \tilde{f}(\zeta^j)
+    \psi(\zeta^i) \ceq \alpha \prod_{j=0}^{i-1} \tilde{f}(\zeta^j)
   \end{equation}
@@
   $\phi(d)-r-1$.  If we set
-  $$A_c = \sum_{i=0}^r a_i \sum_{j=0}^{i+c-1} \zeta^j$$
+  $$A_c \ceq \sum_{i=0}^r a_i \sum_{j=0}^{i+c-1} \zeta^j$$
   then
@@
     %\begin{equation} \label{alpha-def}
-     $ \alpha = \tilde{f}(\omega)$.
+     $ \alpha \ceq \tilde{f}(\omega)$.
     %\end{equation}
@@
   We now check Equation~\eqref{eq:psi-condition} for
-  $x = \zeta^{\phi(d)-1}$.  Write
-  \[\Phi_d(T) = T^{\phi(d)} - b_{\phi(d)-1}T^{\phi(d)-1} - \cdots - b_0\]
+  $x \ceq \zeta^{\phi(d)-1}$.  Write
+  \[\Phi_d(T) \ceq T^{\phi(d)} - b_{\phi(d)-1}T^{\phi(d)-1} - \cdots - b_0\]
   and set
-  $$B = b_i \sum_{j=0}^{i-1} \zeta^j -  \sum_{i=0}^{\phi(d)-1} \zeta^i.$$
+  $$B \ceq b_i \sum_{j=0}^{i-1} \zeta^j -  \sum_{i=0}^{\phi(d)-1} \zeta^i.$$
   We have
@@
   $\psi$ satisfies Equation~\eqref{eq:psi-condition} for
-  $x = \zeta^{\phi(d)-1}$.  The definition of $\psi$ in \ref{eq:psi-def}
+  $x \ceq \zeta^{\phi(d)-1}$.  The definition of $\psi$ in \ref{eq:psi-def}
   immediately implies that $\psi$ satisfies equation
@@
 \begin{proof}
-Let $\pi: B \to G^0$ be a discrete isogeny; set $A = \ker \pi$.
+Let $\pi: B \to G^0$ be a discrete isogeny; set $A \ceq \ker \pi$.
   We will find a discrete isogeny $f: H\to G$
@@
 
-  Set $\Gamma = \Gal(\bFq/\Fq)$. Extensions of
+  Set $\Gamma \ceq \Gal(\bFq/\Fq)$. Extensions of
   $G^0(\bFq)$ by $A(\bFq)$, such as $A(\bFq) \to H^0(\bFq) \to G^0(\bFq)$,
@@
   $\pi_0(G)(\bFq)$ is continuous, it factor through a finite quotient
-  $\Gamma_m = \Gamma / H_m$.  Any product of Dedekind domains has
+  $\Gamma_m \ceq \Gamma / H_m$.  Any product of Dedekind domains has
   cohomological dimension $1$ \David{Add a citation for this fact}, so $\pi_0(G)(\bFq)$ has a
@@
 generic fibres, is a bijection; 
-in particular, taking $S = \Spec{\OK}$, this implies $\TT(\OK) = T(K)$.
+in particular, taking $S \ceq \Spec{\OK}$, this implies $\TT(\OK) = T(K)$.
 
@@
 %\begin{tikzcd}
-\Gr_n : \left( \text{Schemes} \atop \text{lft over $\OK$}\right) \to \left( \text{Schemes} \atop \text{lft over $\Fq$}\right)
+\Gr_n : \partop{\text{Schemes}}{\text{lft over $\OK$}} \to \partop{\text{Schemes}}{\text{lft over $\Fq$}}
 %\end{tikzcd}
@@
 \begin{remark}
-If $K = \mathbb{Q}_q$ and 
-$T = \Gm{\mathbb{Q}_q}$ then $\GN{T}^0 = \mathbb{W}^*_{\FF_q}$, 
+If $K \ceq \mathbb{Q}_q$ and 
+$T \ceq \Gm{\mathbb{Q}_q}$ then $\GN{T}^0 = \mathbb{W}^*_{\FF_q}$, 
 the group scheme (!) over $\Fq$ of units in the ring scheme $\mathbb{W}_{\FF_q}$
@@
 [\qcs{L}_n]\otimes [\qcs{L}_m] \ceq [f_{n\leq k}^*\qcs{L}_n \otimes f_{m\leq k}^*\qcs{L}_m],
-\qquad k = \max\{ n,m\}.
+\qquad k \ceq \max\{ n,m\}.
 \]
@@
 \]
-defined by $F_n(\qcs{L}) = [\qcs{L}_n]$ and $F_n(\alpha_n) = [\alpha_n]$, 
+defined by $F_n(\qcs{L}) \ceq [\qcs{L}_n]$ and $F_n(\alpha_n) \ceq [\alpha_n]$, 
 for all positive integers $n\leq m$.
@@
 Let $T$ be an algebraic torus over $K$ and 
-set $T' = T \times_\Spec{K} \Spec{K'}$.
+set $T' \ceq T \times_\Spec{K} \Spec{K'}$.
 The canonical closed immersion $T \hookrightarrow \Res_{K'/K} T'$
@@
 \begin{corollary}\label{cor:transfer}
- With notation above, suppose that $T$ and $T'$ are $N$-congruent and $N > 3h$.  Set $n = N-3h$.
+ With notation above, suppose that $T$ and $T'$ are $N$-congruent and $N > 3h$.  Set $n \ceq N-3h$.
  Then there is a canonical equivalence of categories

### 2013-09-23 shanghai.tex
Fixing some hboxes

@@
 \tableofcontents
-\David{Search for = which should be \ceq}
 \David{Search for terms defined after they are used}
@@
   If $f : H\to G$ is a morphism of $\QC$-schemes then
-  $(\gqcs{L},\mu,\phi) \mapsto (\bf^*\gqcs{L},(\bfxf)^*\mu,\bf^*F)$
-  defines a monoidal functor $f^* : \QC(G) \to \QC(H)$ such that
+  \begin{align*}
+  f^* : \QC(G) &\to \QC(H) \\
+  (\gqcs{L},\mu,\phi) &\mapsto (\bf^*\gqcs{L},(\bfxf)^*\mu,\bf^*F)
+  \end{align*}
+  defines a monoidal functor such that
   \[
@@
 Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and $x \in G(k')$ and write $\Frob{}$ for $\Frob{G}$.
-The value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ is given by the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
+We may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
 \Clifton{Please note what I did here.}
-while the value $\Nm^*(t_G(\qcs{L}))(x)$ is given by the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
-Applying \ref{CS.2} to the stalk of $\gqcs{L}^{\boxtimes n}$ at $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
+and the value of $\Nm^*(t_G(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
+Applying \ref{CS.2} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
 \[
@@
 we explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
-The base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
-decomposes into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
+We may decompose the base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
+into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
 \[
@@
   as an abelian group it is injective as a $\ZZ$-module and thus
-  $\Ext^1_{\ZZ}(X/X^{\Frob{\Fq}}, \EEx) = 0$.  Applying the functor
+  $\Ext^1_{\ZZ}(X/X^{\Frob{\Fq}}, \EEx) = 0$.  The long exact 
+  sequence obtained by applying the functor
   $\Hom(\mbox{---}, \EEx)$ to
@@
   \]
-  and considering the associated long exact sequence gives the
-  existence of an $\tilde{f} \in \Hom(X, \EEx)$ restricting to
+  gives the existence of an $\tilde{f} \in \Hom(X, \EEx)$ restricting to
   $f$.  Define a $1$-cocycle $z \in \Hh^1(\Fq, \Hom(X,\EEx))$ by
@@
   by injective $\ZZ[\Gamma]$-modules.  Since the action of $\Gamma$ on
-  $\pi_0(G)(\bFq)$ is continuous, it factor through a finite quotient
+  $\pi_0(G)(\bFq)$ is continuous, it factors through some finite quotient
   $\Gamma_m \ceq \Gamma / H_m$.  Any product of Dedekind domains has

### 2013-09-23 shanghai.tex
Small change of phrasing.
Replacing $$ with \[ and \]

@@
 is not a tensor category in the sense of \cite{deligne:02a}*{0.1}.
-This rigid monoidal category structure for $\QC(G)$ puts a group
-structure on the set $\QCiso{G}$ of isomorphism classes in $\QC(G)$.
+This rigid monoidal category structure for $\QC(G)$ gives the set $\QCiso{G}$
+of isomorphism classes in $\QC(G)$ the structure of a group.
 We now begin developing the tools to relate $\QCiso{G}$ to $G(\Fq)^*$.
@@
   \colon X \rightarrow \EEx$ with
-  $$\tilde{f}(x) = \frac{\psi(\Frob{\Fq}(x))}{\psi(x)}$$
+  \[
+  \tilde{f}(x) = \frac{\psi(\Frob{\Fq}(x))}{\psi(x)}
+  \]
   for $x \in X$.  In fact, we may replace the construction of $\psi$
@@
   choose a polynomial
-  $$h(T) \ceq a_rT^r + a_{r-1}T^{r-1} + \cdots + a_0$$
+  \[
+  h(T) \ceq a_rT^r + a_{r-1}T^{r-1} + \cdots + a_0
+  \]
   so that $P^s = (p^s, h(\zeta_d))$.
@@
   $\phi(d)-r-1$.  If we set
-  $$A_c \ceq \sum_{i=0}^r a_i \sum_{j=0}^{i+c-1} \zeta^j$$
+  \[
+  A_c \ceq \sum_{i=0}^r a_i \sum_{j=0}^{i+c-1} \zeta^j
+  \]
   then
-  $$\psi(\zeta^ch(\zeta)) = \alpha^{h(1)} \tilde{f}(A_c).$$
+  \[
+  \psi(\zeta^ch(\zeta)) = \alpha^{h(1)} \tilde{f}(A_c).
+  \]
   Now consider $(\zeta - 1)A_c$: the sums telescope and we get that
@@
   and set
-  $$B \ceq b_i \sum_{j=0}^{i-1} \zeta^j -  \sum_{i=0}^{\phi(d)-1} \zeta^i.$$
+  \[
+  B \ceq b_i \sum_{j=0}^{i-1} \zeta^j -  \sum_{i=0}^{\phi(d)-1} \zeta^i.
+  \]
   We have

### 2013-09-23 shanghai.tex
Replace single line expressions that used \qquad \text{defined by } \qquad with aligned multiline expressions.

@@
 we obtain a group homomorphism
-\[
-\cdef{\trFrob{G}} : \QCiso{G} \longrightarrow G(\Fq)^*,
-\qquad \text{defined by}\qquad \qcs{L} \mapsto \trFrob{\qcs{L}}.
-\]
+\begin{align*}
+\cdef{\trFrob{G}} : \QCiso{G} &\longrightarrow G(\Fq)^*, \\
+\qcs{L} &\mapsto \trFrob{\qcs{L}}.
+\end{align*}
 This homomorphism is functorial in the following sense:
@@
 \begin{proposition}\label{prop:functorialG}
-Trace of Frobenius $\QCiso{G} \to G(\Fq)^*$ is a natural transformation 
+Trace of Frobenius $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a natural transformation 
 between the two additive functors 
-\begin{enumerate}
-\item[$F_1$:] $G \mapsto \QCiso{G}$
-\item[$F_2$:] $G \mapsto G(\Fq)^*$
-\end{enumerate}
+\begin{align*}
+F_1 : G &\mapsto \QCiso{G} \\
+F_2 : G &\mapsto G(\Fq)^*
+\end{align*}
 from the category of $\QC$-schemes to the category of abelian groups.
@@
 $i_{k'/k} : G(k) \hookrightarrow G(k')$ which, in turn, gives
-\[
-i_{k'/k}^* : G(k')^* \to G(k)^* \qquad \text{defined by}\qquad \chi \mapsto \chi\circ i_{k'/k}.
-\]
+\begin{align*}
+i_{k'/k}^* : G(k')^* &\to G(k)^* \\
+\chi &\mapsto \chi\circ i_{k'/k}.
+\end{align*}
 We can interpret this operation on characters in terms of quasicharacter sheaves, as follows.
@@
 In the opposite direction, let $\Nm : G(k') \to G(k)$ be the norm map and consider the group homomorphism:
-\[
-\Nm^* : G(k)^* \to G(k')^* \qquad \text{defined by}\qquad \chi \mapsto \chi\circ \Nm.
-\]
+\begin{align*}
+\Nm^* : G(k)^* &\to G(k')^* \\
+\chi &\mapsto \chi\circ \Nm.
+\end{align*}
 We can also interpret this operation on characters in terms of quasicharacter sheaves, as follows.
@@
 \begin{proposition}\label{prop:etale}
-  If $G$ is a commutative \'etale group scheme over $\Fq$ and $G(\bFq)$ is finitely generated
-  then there is a canonical
-  isomorphism
-  \[
-  \QCiso{G} \longrightarrow \Hh^1(\Weil{\Fq}, G(\bFq)^*),
-  \qquad \text{given by}\qquad
-  \qcs{L}_{/\text{iso}} \mapsto [\tau_\qcs{L}],
-  \]
-  where $\tau_\qcs{L}: \Weil{\Fq}\to G(\bFq)^*$ is a cocycle such that
-  \[
-  \forall x\in G(\Fq), \qquad \tau_\qcs{L}(\Frob{\Fq})(x) = \trFrob{\qcs{L}}(x).
-  \]
+  Let $G$ be a commutative \'etale group scheme over $\Fq$ with $G(\bFq)$ finitely generated.
+  We may associate a $1$-cocycle $\tau_\qcs{L}: \Weil{\Fq}\to G(\bFq)^*$ to each $\qcs{L} \in \QC(G)$
+  so that
+  \[
+  \tau_\qcs{L}(\Frob{\Fq})(x) = \trFrob{\qcs{L}}(x)
+  \]
+  for all $x \in G(\Fq)$ and the map
+  \begin{align*}
+  \QCiso{G} &\to \Hh^1(\Weil{\Fq}, G(\bFq)^*), \\
+  [\qcs{L}] &\mapsto [\tau_\qcs{L}],
+  \end{align*}
+  is an isomorphism.
 \end{proposition}
@@
   \begin{equation}\label{cohomologous}
-    \obj \QC(G) \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*),
-    \qquad \text{defined by} \qquad \qcs{L} \mapsto [\tau_\qcs{L}],
+  \begin{split}
+    \obj \QC(G) &\to \Hh^1(\Weil{\Fq},G(\bFq)^*), \\
+    \qcs{L} &\mapsto [\tau_\qcs{L}],
+  \end{split}
   \end{equation}
@@
   \begin{equation}\label{pich1}
-    \QCiso{G} \longrightarrow \Hh^1(\Weil{\Fq},G(\bFq)^*), \qquad \qcs{L}_{/\text{iso}} \mapsto [\tau_\qcs{L}]
+  \begin{split}
+    \QCiso{G} &\to \Hh^1(\Weil{\Fq},G(\bFq)^*),\\
+    [\qcs{L}] &\mapsto [\tau_\qcs{L}]
+  \end{split}
   \end{equation}
@@
   $X$.  Then
-\[
-    \Hh^1(\Fq, X^*) \xrightarrow{\rho} \Hh^0(\Fq, X)^*,
- \qquad \text{defined by}\qquad
-   \rho([z])(x) \ceq z(\Frob{\Fq})(x),
-\]
+  \begin{align*}
+    \Hh^1(\Fq, X^*) &\xrightarrow{\rho} \Hh^0(\Fq, X)^*, \\
+    \rho([z])(x) &\ceq z(\Frob{\Fq})(x),
+  \end{align*}
   is an isomorphism of groups.
@@
 For a given Néron model $\TT$ of $T$, set
-\[
-\GN{T}_n \ceq \Gr_n(\TT)
-\qquad \text{and}\qquad
-f_n \ceq P_n(\TT).
-\]
+\begin{align*}
+ \GN{T}_n &\ceq \Gr_n(\TT) \\
+ f_n &\ceq P_n(\TT).
+\end{align*}
 

### 2013-09-23 shanghai.tex
Replaced a few longrightarrows

@@
 \begin{align*}
-\cdef{\trFrob{G}} : \QCiso{G} &\longrightarrow G(\Fq)^*, \\
+\cdef{\trFrob{G}} : \QCiso{G} &\to G(\Fq)^*, \\
 \qcs{L} &\mapsto \trFrob{\qcs{L}}.
@@
  \labitem{(cs.1)}{cs.1} an indexed set of isomorphisms
-  $\mu_{x,y} : \gqcs{L}_{x+y} \mathop{\longrightarrow}\limits^{\iso} \gqcs{L}_{x} \otimes\gqcs{L}_{y}$,
+  $\mu_{x,y} : \gqcs{L}_{x+y} \xrightarrow{\iso} \gqcs{L}_{x} \otimes\gqcs{L}_{y}$,
   for all $x,y \in G(\bFq)$, such that

### 2013-09-23 shanghai.tex
Various small changes to early sections

@@
 \begin{enumerate}
-\labitem{(CS.0)}{CS.0} $\gqcs{L}$ is an $\ell$-adic local system on $\bG$
-(a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component) of rank-1; 
+\labitem{(CS.0)}{CS.0} $\gqcs{L}$ is a rank one $\ell$-adic local system on $\bG$
+-- a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component; 
 \labitem{(CS.1)}{CS.1} $\mu: \bm^* \gqcs{L} \to \LxL$
@@
 
-%\David{insert some commentary on this proposition: it will be very useful to us}
 As a step toward the proof of Proposition~\ref{prop:functorialG} we show that every
@@
 sheaves on $G$ to quasicharacters on $H$. This simple but important result will also
-play a role in the proof of many other propositions in this paper.
+play a role in the proof of many other results in this paper.
 
@@
   \end{align*}
-  defines a monoidal functor such that
+  defines a monoidal functor dual to $f \colon H(\Fq) \to G(\Fq)$:
   \[
@@
   \]
-  is a commutative diagram of groups, where the lower homomorphism is
-  dual to $f : H(\Fq)\to G(\Fq)$.  Moreover, $(f\circ g)^* = g^* \circ f^*$.
+  is a commutative diagram of groups.  Moreover, $(f\circ g)^* = g^* \circ f^*$.
 \end{proposition}
@@
   homomorphism $\pi_0(\bf) : \pi_0(\bH) \to \pi_0(\bG)$.
-  Write $c_i : \bG^i \hookrightarrow \bG$ for
+  Write $d_i : \bG^i \hookrightarrow \bG$ for
   the inclusion of $\bG^i$ and $\bf^j : \bH^j \to \bG^i$
@@
   = (\bf\circ c_j \circ b_j)^*\gqcs{L}
-  = (c_i\circ a_i\circ g_j)^*\gqcs{L} = g_j^* a_i^* (\gqcs{L}\vert_{\bG^i}).
+  = (d_i\circ a_i\circ g_j)^*\gqcs{L} = g_j^* a_i^* (\gqcs{L}\vert_{\bG^i}).
   \]

### 2013-09-24 shanghai.tex
Changes to sections 3 and 4

@@
 -- a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component; 
-\labitem{(CS.1)}{CS.1} $\mu: \bm^* \gqcs{L} \to \LxL$
+\labitem{(CS.1)}{CS.1} $\mu: \bm^* \gqcs{L} \to \LxL$ \David{We should explain the $\boxtimes$ notation}
   is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
@@
   $\bf^*\gqcs{L}$ is a local system of rank~$1$. Let $c_j :\bH^j \hookrightarrow \bH$ be any
-  connected component and let $i$ be the image of $j$ under the group
-  homomorphism $\pi_0(\bf) : \pi_0(\bH) \to \pi_0(\bG)$.
-  Write $d_i : \bG^i \hookrightarrow \bG$ for
-  the inclusion of $\bG^i$ and $\bf^j : \bH^j \to \bG^i$
+  connected component and let $d_i : \bG^i \hookrightarrow \bG$ be the image of $j$ under the group
+  homomorphism $\pi_0(\bf) : \pi_0(\bH) \to \pi_0(\bG)$.  Write $\bf^j : \bH^j \to \bG^i$
   for the restriction of $f$ to $\bH^j$.  Since $\gqcs{L}$ is locally constant on the connected
@@
   $a_i : X_i \to \bG^i$ such that $a_i^* (\gqcs{L}\vert_{\bG^i})$
-  is constant. Let $b_j : Y_j \to \bH^j$ be the
-  pull-back of $a_i$ along $\bf^j$ and let $g_j : Y_j \to X_i$ be
-  the map opposite $\bf^j$. Then $b_j$ is a finite \'etale covering
+  is constant.  Define $Y_j$ in the following diagram through pullback:
+  \[
+  \begin{tikzcd}[row sep=20, column sep=30]
+   Y_j \dar[dashed]{g_j} \rar[dashed]{b_j} & \bH^j \dar{\bf^j} \rar[hook]{c_j} & \bH \dar{\bf} \\
+   X_i \rar{a_i} & \bG^i \rar[hook]{d_i} & \bG
+  \end{tikzcd}
+  \]
+  Then $b_j$ is a finite \'etale covering
   of $\bH^j$ and
@@
   $f^*\gqcs{L}$ also has rank $1$ on connected components of $\bG$.
+  \David{can't we just say rank 1?  Why ``on connected components of $G$?"}
   This completes the proof that $\bf^*\gqcs{L}$ satisfies condition \ref{CS.0}.
@@
 
-  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{CS.3} allows the application
-  of $f^*$ to morphisms of quasicharacter sheaves; arguing as above shows that $f^*$ is
-  a functor from $\QC(G)$ to $\QC(H)$.  Since tensor products commute with pullback
+  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{CS.3} defines the action
+  of $f^*$ on morphisms of quasicharacter sheaves; arguing as above shows that $f^*$ is
+  a functor from $\QC(G)$ to $\QC(H)$.  Since tensor products commute with pullback in schemes,
   $f^* : \QC(G) \to \QC(H)$ is a monoidal functor.
@@
 \]
-which induces, upon passage to isomorphism classes of objects, a sequence of group homomorphisms 
+which induces a sequence of group homomorphisms 
 \[
@@
 \]
-It is easy to see that $\QCiso{0}$ is trivial. In Sections~\ref{sec:connected} and  we will find $\QCiso{G^0}$
+after passing to isomorphism classes.  It is easy to see that $\QCiso{0}$ is trivial. In Sections~\ref{sec:connected}, \ref{sec:etale} and \ref{sec:etalecohom} we will find $\QCiso{G^0}$
 and $\QCiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; 
-the snake lemma will then allow us to show
-\[
-\QCiso{G} \iso G(\Fq)^*,%\Hom_\text{grp}(G(\Fq),\EE^\times),
-\]
-canonically.
+the snake lemma will then allow us to show that
+\[
+\QCiso{G} \iso G(\Fq)^*.
+\]
+
 %\section{Products}
+
 We end this section with a simple result on products of quasicharacter sheaves,
@@
 \begin{proposition}\label{prop:product}
-The rule $\boxtimes : (\qcs{L}_1,\qcs{L}_2)\to \qcs{L}_1\boxtimes\qcs{L}_2$ defines an equivalence of categories 
-\[
-\QC(G_1)\times (G_2) \to \QC(G_1\times G_2)
-\]
-(categorical product on the left, product of group schemes over $\Fq$ on the right) and 
+If $G_1$ and $G_2$ are $\QC$-schemes, the rule $\boxtimes : (\qcs{L}_1,\qcs{L}_2)\to \qcs{L}_1\boxtimes\qcs{L}_2$ defines an equivalence of categories 
+\[
+\QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)
+\]
+and 
 \[
@@
 \begin{proof}
-The only non-trivial part is essential surjectivity. Set $G \ceq G_1\times G_2$.
+The only non-trivial part is essential surjectivity. Set $G \ceq G_1\times G_2$
+and write $e_1$ and $e_2$ for the identity elements of $G_1$ and $G_2$.
 Let $\qcs{L}$ be a quasicharacter sheaf on $G$. Define $f : G\to G\times G$
@@
 \]
-Let $r_1$ and $r_2$ be the projection morphisms pictured below, with sections $q_1$, $q_2$, also morphisms of group schemes:
+Let $r_1$ and $r_2$ be the projection morphisms pictured below, with sections $q_1$ and $q_2$, also morphisms of group schemes:
 \[
@@
 \]
-Then $p_1\circ f = r_1 \circ q_1$ and $f_2 = r_2\circ f$, 
+Then $p_1\circ f = q_1 \circ r_1$ and $p_2 \circ f = q_2\circ r_2$, 
 so $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L}$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L}$. 
-Now $\qcs{L}_1 \ceq r_1^* \qcs{L}$ is a quasicharacter sheaf on $G_1$ 
-and $\qcs{L}_2 \ceq r_2^* \qcs{L}$ is a quasicharacter sheaf on $G_2$, 
+Now $\qcs{L}_1 \ceq q_1^* \qcs{L}$ is a quasicharacter sheaf on $G_1$ 
+and $\qcs{L}_2 \ceq q_2^* \qcs{L}$ is a quasicharacter sheaf on $G_2$, 
 by Proposition~\ref{prop:pullback}. 
@@
 \]
-So $\boxtimes$ is essentially surjective.
+So $\boxtimes$ is essentially surjective. \David{Don't we also need to note that $f^*\mu$ is compatible with the rational structures?}
 \end{proof}
@@
 how quasicharacter sheaves behave under change of fields.
-Let $k'$ be a finite extension of $k$. Then $k\to k'$ induces a group homomorphism
-$i_{k'/k} : G(k) \hookrightarrow G(k')$ which, in turn, gives
+Let $k'$ be a finite extension of $k$. Then $k \hookrightarrow k'$ induces a group homomorphism
+$i_{k'/k} : G(k) \hookrightarrow G(k')$ and thus a homomorphism
 \begin{align*}
@@
 \end{align*}
-We can interpret this operation on characters in terms of quasicharacter sheaves, as follows.
+We can interpret this operation on characters in terms of quasicharacter sheaves:
 %
@@
 \end{align*}
-We can also interpret this operation on characters in terms of quasicharacter sheaves, as follows.
+We can also interpret this operation on characters in terms of quasicharacter sheaves.
 
@@
  defines a monoidal functor $\QC(G) \to \QC(G_{k'})$. 
- Moreover, the following diagram commutes, 
- where the top map is induced by $\QC(G) \to \QC(G_{k'})$ 
- and the bottom map is induced by the norm $G(k') \rightarrow G(k)$:
+ Moreover, the following diagram commutes:
 \[
@@
 \begin{proof}
-Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and $x \in G(k')$ and write $\Frob{}$ for $\Frob{G}$.
-We may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
+Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and write $\Frob{}$ for $\Frob{G}$.  For any $x \in G(k')$,
+we may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
 \Clifton{Please note what I did here.}
@@
 \]
-Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$, mapping to $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
-along the bottom map, where $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{CS.1}, $v$ maps to
+Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$ and write the image of $v$ under the
+bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
+for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{CS.1}, $v$ maps to
 $v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
@@
 \]
-mapping $G'$ into the summand corresponding to $1 \in \Gal(k'/k)$.  Composing pullback
-along this map with $\nu_{k'/k}$ from Proposition~\ref{prop:basechange} yields a functor
-\[
-\QC(\Res_{k'/k}G') \to \QC(G').
+mapping $G'$ into the summand corresponding to $1 \in \Gal(k'/k)$.  Composing $\nu_{k'/k}$ 
+from Proposition~\ref{prop:basechange} with pullback along this map yields a functor
+\[
+\rho : \QC(\Res_{k'/k}G') \to \QC(G').
 \]
@@
 \begin{tikzcd}
-\QCiso{\Res_{k'/k} G'} \dar{\trFrob{\Res_{k'/k} G'}} \rar & \QCiso{G'} \dar{\trFrob{G'}}\\
+\QCiso{\Res_{k'/k} G'} \dar{\trFrob{\Res_{k'/k} G'}} \rar{\rho} & \QCiso{G'} \dar{\trFrob{G'}}\\
 G'(k')^* \rar & G'(k')^*
@@
 \begin{proof}
-By Proposition~\ref{prop:pullback} the pullback part of the definition corresponds to the map $(\Res_{k'/k}G')(k') \to G'(k')^*$
+By Proposition~\ref{prop:pullback} the pullback part of the definition of $\rho$ corresponds to the map $(\Res_{k'/k}G')(k') \to G'(k')^*$
 induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on $(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'$

### 2013-09-24 shanghai.tex
Changes to section 5

@@
 
+In this section we consider a class of quasicharacter sheaves on $G$ obtained by
+replacing the Weil sheaf $(\gqcs{L}, \phi)$ on $\bG$ in the definition of a quasicharacter
+sheaf with an $\ell$-adic local system on $G$ itself.
+
 \begin{definition}
 Let $\QCb(G)$ be the category of pairs $(\qcs{L}_0,\mu_0)$ 
-where $\qcs{L}_0$ an $\ell$-adic local system on $G$ of rank-1, 
+where $\qcs{L}_0$ an $\ell$-adic local system on $G$ of rank one, 
 equipped with an isomorphism $\mu_0 : m^* \qcs{L}_0 \to \qcs{L}_0 \boxtimes \qcs{L}_0$ 
@@
 \begin{proposition}
-$\QCb(G)$ is (equivalent to) a full subcategory of $\QC(G)$.
+There is a canonical functor $B_G^* : \QCb(G) \hookrightarrow \QC(G)$. Moreover, $B_G^*$
+is full and faithful, identifying $\QCb(G)$ with a full subcategory of $\QC(G)$.
 \end{proposition}
@@
  Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$. 
- Then $\qcs{L}_0$ is, in particular, an $\ell$-adic constructible sheaf on $G$. 
- Then $b_G^* \qcs{L}_0$ comes equipped with an isomorphism 
- $\phi : \Frob{G}^* b_G^*\qcs{L}_0 \to b_G^* \qcs{L}_0$; 
- moreover, the functor $\qcs{L}_0 \mapsto (b_G^* \qcs{L}_0,\phi)$  
+ Then $\qcs{L}_0$ is an $\ell$-adic constructible sheaf on $G$ and
+ $b_G^* \qcs{L}_0$ comes equipped with an isomorphism 
+ $\phi : \Frob{G}^* b_G^*\qcs{L}_0 \to b_G^* \qcs{L}_0$.
+ Moreover, the functor $\qcs{L}_0 \mapsto (b_G^* \qcs{L}_0,\phi)$  
  from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
- is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} or even \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}. 
+ is full and faithful \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}}. 
  This functor preserves local constancy, so takes local systems to local systems. 
@@
  Moreover, $\phi$ is compatible with $\mu$ in the sense of Condition~\ref{CS.3}.
- It follows that functor $(\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,b_{G\times G}^* \mu_0, \phi)$,
- denoted by  $B_G^*: \QCb(G) \hookrightarrow \QC(G)$ below, is full and faithful.
+ It follows that $B_G^* : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
+ is full and faithful.
 \end{proof}
 
-The full subcategory $\QCb(G)$ of bounded quasicharacter sheaves is an essentially
-proper subcategory of $\QC(G)$, in general. Indeed, it follows from our main result
-regarding quasicharacter sheaves, Theorem~\ref{thm:snake}, that the restriction of
-$\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ to the subgroup $\QCbiso{G}$ is an isomorphism
-onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is bounded in $\EEx$;
-see Section~\ref{sec:snake}.
+In general, $\QCb(G)$ is an essentially
+proper subcategory of $\QC(G)$. Indeed, it follows from Theorem~\ref{thm:snake}
+that the restriction of $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ to the subgroup
+$\QCbiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such
+that the image of $\chi$ is bounded in $\EEx$; see Section~\ref{sec:snake} for more details.
 

### 2013-09-24 shanghai.tex
Added SGA5l changes to the first section.

@@
 A quasicharacter sheaf on $G$ is a triple $\qcs{L}\ceq
-(\gqcs{L},\mu,\phi)$ where $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ of rank-1 and $\mu: m^*
+(\gqcs{L},\mu,\phi)$ where $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ of rank~one and $\mu: m^*
 \gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms;
@@
 We fix a prime $\ell$, invertible in $\Fq$.
+We will work with constructible $\ell$-adic sheaves \cite{deligne:80a}*{\S 1.1} on $\QC$-schemes,
+employing the standard formalism;
+see, in particular, \cite{SGA5}*{Expos\'e VI,\S 2}, where pullback and tensor products are developed.
+We also make extensive use of the external tensor product of $\ell$-adic sheaves, defined as follows: if $\mathcal{F}$ and $\mathcal{G}$ are constructible $\ell$-adic sheaves on schemes $X$ and $Y$, respectively, then $\mathcal{F}\boxtimes \mathcal{G} \ceq p_X^* \mathcal{F} \otimes p_Y^*\mathcal{G}$, where $p_X : X\times Y\to X$ and $p_Y : X\times Y \to Y$ are projections.
+
 For any group $A$, we will denote by $A^*$ the dual group $\Hom_\text{grp}(A, \EEx)$.
@@
 \begin{enumerate}
-\labitem{(CS.0)}{CS.0} $\gqcs{L}$ is a rank one $\ell$-adic local system on $\bG$
--- a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component; 
-\labitem{(CS.1)}{CS.1} $\mu: \bm^* \gqcs{L} \to \LxL$ \David{We should explain the $\boxtimes$ notation}
-  is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
+\labitem{(CS.0)}{CS.0} $\gqcs{L}$ is a rank~one $\ell$-adic local system on $\bG$, by which we mean
+a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces; 
+\labitem{(CS.1)}{CS.1} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
   where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
@@
   Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We start by showing that
-  $\bf^*\gqcs{L}$ is a local system of rank~$1$. Let $c_j :\bH^j \hookrightarrow \bH$ be any
+  $\bf^*\gqcs{L}$ is a local system of rank~one. Let $c_j :\bH^j \hookrightarrow \bH$ be any
   connected component and let $d_i : \bG^i \hookrightarrow \bG$ be the image of $j$ under the group
@@
   \]
-
+%
   Since $a_i^* (\gqcs{L}\vert_{\bG^i})$ is a constant sheaf, its pullback
@@
   Thus $\bf^*\gqcs{L}$ is locally constant on
-  $\bH^j$. Since $(\bf^*\gqcs{L})_{\bg} = \gqcs{L}_{f(\bg)}$ for every
-  geometric point ${\bg}$ on $\bG$, and since $\gqcs{L}$ has
-  rank $1$ on connected components of $\bG$, it follows that
-  $f^*\gqcs{L}$ also has rank $1$ on connected components of $\bG$.
-  \David{can't we just say rank 1?  Why ``on connected components of $G$?"}
-  This completes the proof that $\bf^*\gqcs{L}$ satisfies condition \ref{CS.0}.
+  $\bH^j$. To complete the proof that $\bf^*\gqcs{L}$ satisfies Condition~\ref{CS.0}
+  simply observe that $\bf^*\gqcs{L}$ has rank~one since 
+  $(\bf^*\gqcs{L})_{\bg} = \gqcs{L}_{f(\bg)}$, for every geometric point ${\bg}$ on $\bG$.
 
@@
 Let $\QCb(G)$ be the category of pairs $(\qcs{L}_0,\mu_0)$ 
-where $\qcs{L}_0$ an $\ell$-adic local system on $G$ of rank one, 
+where $\qcs{L}_0$ an $\ell$-adic local system on $G$ of rank~one, 
 equipped with an isomorphism $\mu_0 : m^* \qcs{L}_0 \to \qcs{L}_0 \boxtimes \qcs{L}_0$ 
@@
 %
-Consider the case when $G$ is the discrete \'etale group scheme $\ZZ$. 
+Consider the case when $G$ is the discrete \'etale group scheme $\ZZ$; 
+this is indeed a $\QC$-scheme.
 Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ 
@@
 Then the restriction of $\qcs{L}$ to the connected component $1\in G$ 
-would be a $\ell$-adic local system on $1$ of rank-1, 
-thus an $\ell$-adic character $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with
-$\rho_1(\Frob{\Fq}) = \ell$. But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, 
-while $\rho_1(\pi_1(1,{\bar 1}))$ is not compact in $\EEx$ (it contains $\ell^\ZZ$). 
+would be a $\ell$-adic local system on $1$ of rank~one, which would provide
+an $\ell$-adic character $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with
+$\rho_1(\Frob{\Fq}) = \ell$, necessarily continuous. 
+\Clifton{I made some small changes to wording, here.}
+But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, 
+while $\rho_1(\pi_1(1,{\bar 1})) \subseteq \EEx$ is not compact (it contains $\ell^\ZZ$),
+contradicting the continuity of $\rho_1$.
 So the Weil sheaf $\gqcs{L}$ does not descend to a local system on $G$.

### 2013-09-24 shanghai.tex
Fixing up a diagram in Section 6, making other changes to Section 6

--- 2013-09-24 shanghai.tex
@@
 
-To define the category of finite quasicharacter sheaves we must work a bit harder.
-Consider the following category $C(G)$.
+In this section we define \emph{finite quasicharacter sheaves}, a further refinement
+of bounded quasicharacter sheaves that play a role in Section \ref{sec:restriction}.
 Let us say that $f : H\to G$ is a \emph{discrete isogeny} if it is a finite, surjective
@@
 the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $f^{-1}({\bar e})$ is trivial.
-An object in $C(G)$ is a pair $(f,\psi)$ where: 
-$f : H\to G$ is a discrete isogeny 
-and $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$;
-a map $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(\alpha,T)$ 
-where $\alpha$ is a morphism of schemes such that $f' = f\circ \alpha$
-and $T : V\to V'$ is a linear transformation equivariant 
-for the action of $\ker f'$ on $V'$ by $\psi'$ 
-and the action of $\ker '$ on $V$ by $\psi \circ \alpha$.
+We first begin by defining a category $C(G)$, whose objects consist of pairs $(f,\psi)$ where
+\begin{itemize}
+\item $f : H\to G$ is a discrete isogeny;
+\item $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$.
+\end{itemize}
+A morphism $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(\alpha,T)$ where
+\begin{itemize}
+\item $\alpha : H' \to H$ is a morphism of schemes such that $f' = f\circ \alpha$;
+\item $T : V\to V'$ is a linear transformation equivariant for the action of
+$\ker f'$ on $V'$ by $\psi'$ and the action of $\ker '$ on $V$ by $\psi \circ \alpha$.
 \[
@@
 V \arrow{d}{T} & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} & \arrow[equal]{d} G\\
-V' & \Aut(V) & \arrow[swap]{l}{\psi} \arrow[swap]{u}{\alpha\vert_{\ker f}} \ker f \arrow[hook]{r} & \arrow[swap]{u}{\alpha} H' \arrow{r}{f'} & G
-\end{tikzcd}
-\]
+V' & \Aut(V') & \arrow[swap]{l}{\psi'} \arrow[swap]{u}{\alpha\vert_{\ker f'}} \ker f' \arrow[hook]{r} & \arrow[swap]{u}{\alpha} H' \arrow{r}{f'} & G
+\end{tikzcd}
+\]
+\end{itemize}
 We say that $(\alpha,T)$ in $C(G)$ is a \emph{weak isomorphism} if $\alpha$ is surjective
@@
 
-We put a tensor category structure on $C(G)$ 
-and a rigid monoidal category structure on $C_1(G)$ as follows.
+We put a tensor category structure on $C(G)$ as follows.
 Let $(f,\psi)$ and $(f',\psi')$ be objects in $C(G)$. 
-The category of isogenies to $G$ admits products: 
-write $f\times_G f' : H\times_G H' \to G$ for the product of $f : H\to G$ and $f' : H'\to G$. 
-Since $\ker(f\times_G f') \iso (\ker f)\times (\ker f')$, canonically,
-the tensor product of the representations $\psi : \ker f\to \Aut(V)$ and $\psi' : \ker f'\to \Aut(V')$ 
-is the representation $\psi \otimes\psi' :  \ker(f\times_G f') \to \Aut(V\otimes V')$. 
-This allows us to set $(f,\psi)\otimes(f',\psi') \ceq (f\times_G f' ,\psi\otimes\psi')$. 
-The same fact makes sense of $(f,\psi)\oplus(f',\psi')\ceq (f\times_G f' ,\psi\oplus\psi')$. 
-The dual of $(f,\psi)$ is $(f,\psi)^\vee \ceq (f,\psi^\vee)$ 
-where $\psi^\vee : \ker f \to \Aut(V^\vee)$ and $V^\vee \ceq \Hom_\text{vec}(V,\EE)$. 
-The verification that these operations make $C(G)$ a tensor category is straightforward.
+Write $f\times_G f' : H\times_G H' \to G$ for the product of $f$ and $f'$
+in the category of isogenies to $G$. We define an external tensor product
+$\psi \otimes\psi' :  \ker(f\times_G f') \to \Aut(V\otimes V')$ and a external sum
+$\psi \oplus\psi' :  \ker(f\times_G f') \to \Aut(V\otimes V')$
+using the canonical isomorphism $\ker(f\times_G f') \iso (\ker f)\times (\ker f')$.
+We may thus define $(f,\psi)\otimes(f',\psi') \ceq (f\times_G f' ,\psi\otimes\psi')$ and
+$(f,\psi)\oplus(f',\psi')\ceq (f\times_G f' ,\psi\oplus\psi')$. To define duals in $C(G)$,
+let $V^\vee \ceq \Hom_\text{vec}(V,\EE)$ and $\psi^\vee : \ker f \to \Aut(V^\vee)$ be
+the dual representation.  We may then set $(f,\psi)^\vee \ceq (f,\psi^\vee)$.
+These operations give $C(G)$ the structure of a tensor category.
 Likewise, $C(G)[W^{-1}]$ is a tensor category.
+\David{Should expand on this a bit and note that $C(G)[W^{-1}]$ admits a calculus of fractions}
 
 \begin{lemma}\label{lemma:finite-pull-back}
-If $g : G'\to G$ is a morphism of group schemes then $(f,\psi) \mapsto (f_g,\psi_g)$
-defines a monomial functor $g^* : C(G)[W^{-1}] \to C(G')[W'^{-1}]$ where $f_g : H\times_G G'\to G'$
-is a pull-back of $f$ along $g$ and $\psi_g : \ker f_g \to \Aut(V)$ is defined by the diagram below.
+If $g : J \to G$ is a morphism of group schemes, let $f_g : H\times_G J\to J$
+be the pull-back of $f$ along $g$ and define $\psi_g : \ker f_g \to \Aut(V)$ as in the diagram below:
 \[
@@
 V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker g_f}} \ker f_g \arrow[hook]{r}
-  & \arrow[swap]{u}{g_f} H\times_G G' \arrow{r}{f_g} & \arrow{u}{g} G'.
-\end{tikzcd}
-\]
+  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker f_g}} \ker f_g \arrow[hook]{r}
+  & \arrow[swap]{u}{g_f} H\times_G J \arrow{r}{f_g} & \arrow{u}{g} J.
+\end{tikzcd}
+\]
+Then $(f,\psi) \mapsto (f_g,\psi_g)$
+defines a monomial functor $g^* : C(G)[W^{-1}] \to C(J)[W^{-1}]$.
 \end{lemma}
@@
 The key point is that pull-back along $g$ takes isogenies to isogenies,
-and maps over $G$ to maps over $G'$, as pictured below.
-\[
-\begin{tikzcd}[row sep=10,column sep=10]
-\ & V \arrow{dd}{T} && \Aut(V) && \arrow[swap]{ll}{\psi} \ker f \arrow[hook]{rr} && H \arrow{rr}{f} && \arrow[equal]{dd} G\\
- && && \arrow{ul} \ker f\times_G G' \arrow{ur} \arrow[hook]{rr} && H\times_G G' \arrow{ur} \arrow{rr} && G' \arrow{ur}{g} & \\
-& V' && \Aut(V) && \arrow[swap,pos=0.7]{ll}{\psi'} \arrow[swap]{uu}{} \ker f'  \arrow[hook]{rr}
-&& \arrow[swap]{uu} H' \arrow[pos=0.8]{rr}{f'} && G\\
- && && \arrow{ul} \ker f'\times_G G' \arrow{uu} \arrow{ur} \arrow[hook]{rr}
- && \arrow{uu} H'\times_G G' \arrow{ur} \arrow{rr} && \arrow[equals]{uu} G' \arrow[swap]{ur}{g} & 
-\end{tikzcd}
-\]
-In this form we could treat $g^*$ as a functor $C(G')\to C(G)$,
-where it not for the fact that pull-back is defined only up to isomorphism.
+and maps over $G$ to maps over $J$, as pictured below.
+\[
+\begin{tikzcd}[row sep={{{{40,between origins}}}},column sep={{{{60,between origins}}}}]
+\ V \arrow{dd}{T} & \Aut(V) && \arrow[swap]{ll}{\psi} \ker f \arrow[hook]{rr} \arrow[leftarrow]{dd} && H \arrow{rr}{f} \arrow[leftarrow]{dd} && \arrow[equal]{dd} G\\
+ & & \arrow{ul} \ker f\times_G J \arrow{ur} \arrow[hook, crossing over]{rr} && H\times_G J \arrow{ur} \arrow[crossing over]{rr} && J \arrow[swap]{ur}{g} & \\
+V' & \Aut(V') && \arrow[swap,pos=0.25]{ll}{\psi'} \ker f'  \arrow[hook]{rr}
+&& H' \arrow[pos=0.25]{rr}{f'} && G\\
+ & & \arrow{ul} \ker f'\times_G J \arrow[crossing over]{uu} \arrow{ur} \arrow[hook]{rr}
+ && \arrow[crossing over]{uu} H'\times_G J \arrow{ur} \arrow{rr} && \arrow[equals, crossing over]{uu} J \arrow[swap]{ur}{g} & 
+\end{tikzcd}
+\]
+In this form we could treat $g^*$ as a functor $C(J)\to C(G)$,
+were it not for the fact that pull-back is defined only up to isomorphism.
 In the localized categories, this ambiguity disappears. 
@@
 
-Let $C_1(G)$ be the rigid monoidal full subcategory of $C(G)$ consisting of objects
+Let $C_1(G)$ be the full, rigid monoidal subcategory of $C(G)$ consisting of objects
 $(f,\psi)$ such that $\psi$ is a one-dimensional representation.

### 2013-09-24 shanghai.tex
Working on section 6

@@
 In Part 1 of this paper we study the category $\QC(G)$ of quasicharacter sheaves on $G$.
-Since $\QC(G)$ is a rigid symmetric monoidal category
+Since $\QC(G)$ is a rigid monoidal category
 the set of isomorphism classes $\QCiso{G}$ forms a group.
@@
 
-The category $\QC(G)$ of quasicharacter sheaves on $G$ is a rigid symmetric monoidal category
+The category $\QC(G)$ of quasicharacter sheaves on $G$ is a rigid monoidal category
 \cite{etingof:09a}*{\S~1.10} under the tensor product
@@
 The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\QCf(G)$,
-is the rigid symmetric monoidal category obtained by localizing $C_1(G)$ at weak isomorphisms.
+is the rigid monoidal category obtained by localizing $C_1(G)$ at weak isomorphisms.
 \end{definition}
@@
 \begin{proof}
-As in Lemma~\ref{lemma:finite-pull-back}, we have $m^*(f,\psi) = (f_m,\psi_m)$
-where $f_m$ and $\psi_m$ are pictured below, where $H_m \ceq H\times_G(G\times G)$.
+Set $H_m \ceq H\times_G(G\times G)$, write $f_m : H_m \to G \times G$ for the pullback of $f$ to $H_m$, and let $A$ and $A_m$ be the kernels of $f$ and $f_m$ respectively.
+Consider the diagram of Lemma~\ref{lemma:finite-pull-back}:
 \[
@@
 V & \Aut(V) & \arrow[swap]{l}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(m_f)\vert_{\ker m_f}} \ker f_m \arrow[hook]{r}
+  &  & \arrow[dashed]{ul}{\psi_m} \arrow[swap]{u}{(m_f)\vert_{A_m}} A_m \arrow[hook]{r}
   & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G.
@@
 \]
-On the other hand, $(f,\psi) \boxtimes (f,\psi) = (f\times f, \psi\otimes \psi)$.
-Since $f\circ m_H = m \circ (f\times f)$, by the universal property of pull-back,
-there is a unique $\theta : H\times H \to H_m$ making the following commute.
+We have $(f,\psi) \boxtimes (f,\psi) = (f\times f, \psi\otimes \psi)$.
+Since $f\circ m_H = m \circ (f\times f)$, the universal property of pull-back gives
+a unique $\theta : H\times H \to H_m$ making the following commute.
 \[
 \begin{tikzcd}[row sep=20,column sep=10]
-\ & V \arrow{dd}{T} && \Aut(V) && \arrow{dl} \arrow[swap]{ll}{\psi_g} A_m \arrow[hook]{rr}
+\ & V \arrow{dd}{T} && \Aut(V) && \arrow{dl} \arrow[swap]{ll}{\psi_m} A_m \arrow[hook]{rr}
 && \arrow[swap]{ld}{m_f} H_m \arrow{rr}{f_m} && \arrow[equal]{dd} \arrow{ld}{m} G\times G\\
@@
 \]
-Choose a basis $\{ v_1 \}$ for $V$; then $\{ v_1\otimes v_1 \}$ is a basis for $V\otimes V$.
-Define $T : V \to V\otimes V$ by $T(v_1) \ceq v_1\otimes v_1$. Then the lower part of this
+Choose a basis $\{ v \}$ for $V$; then $\{ v\otimes v \}$ is a basis for $V\otimes V$.
+Define $T : V \to V\otimes V$ by $T(v) \ceq v\otimes v$. Then the lower part of this
 diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G)$.
@@
 Duals in $\QC(\GN{T})$ are defined by $[\qcs{L}_n]^\vee \ceq [\qcs{L}_n^\vee]$.
-We refer to objects in the rigid symmetric monoidal category 
+We refer to objects in the rigid monoidal category 
 $\QC(\GN{T})$ as \emph{quasicharacter sheaves on $\GN{T}$} 

### 2013-09-24 shanghai.tex
Improved the proof of Proposition 3.2.

--- 2013-09-24 shanghai.tex
@@
 \begin{proof}
-The only non-trivial part is essential surjectivity. Set $G \ceq G_1\times G_2$
+The only non-trivial part of the proof is to show that $\boxtimes : \QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)$ is essentially surjective, so we will only address that point here.
+
+Set $G \ceq G_1\times G_2$
 and write $e_1$ and $e_2$ for the identity elements of $G_1$ and $G_2$.
-Let $\qcs{L}$ be a quasicharacter sheaf on $G$. Define $f : G\to G\times G$
-by $f(g_1,g_2) \ceq (g_1,e_2,e_1,g_2)$. Observe that $m\circ f = \id_G$. 
+Define $f : G\to G\times G$ by $f(g_1,g_2) \ceq (g_1,e_2,e_1,g_2)$. 
+Observe that $m\circ f = \id_G$. 
 Let $p_1$, $p_2$ be the projection morphisms pictured below:
@@
 \end{tikzcd}
-\]
-Then the isomorphism $\mu : m^* \gqcs{L} \to \gqcs{L}\boxtimes \gqcs{L}$ gives an isomorphism
-\[
-f^*\mu : f^* m^* \gqcs{L} \to f^*(\gqcs{L}\boxtimes \gqcs{L}) = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L}.
 \]
@@
 \]
-Then $p_1\circ f = q_1 \circ r_1$ and $p_2 \circ f = q_2\circ r_2$, 
-so $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L}$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L}$. 
-Now $\qcs{L}_1 \ceq q_1^* \qcs{L}$ is a quasicharacter sheaf on $G_1$ 
-and $\qcs{L}_2 \ceq q_2^* \qcs{L}$ is a quasicharacter sheaf on $G_2$, 
-by Proposition~\ref{prop:pullback}. 
-Then 
-\[
-f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L} = r_1^*\gqcs{L}_1\otimes r_2^* \gqcs{L}_2 = \gqcs{L}_1\boxtimes \gqcs{L}_2.
-\]
-In this way, $\mu$ determines an isomorphism
-\[
-f^*\mu : \gqcs{L} \to  \gqcs{L}_1\boxtimes \gqcs{L}_2.
-\]
-So $\boxtimes$ is essentially surjective. \David{Don't we also need to note that $f^*\mu$ is compatible with the rational structures?}
+Observe that $p_1\circ f = q_1 \circ r_1$ and $p_2 \circ f = q_2\circ r_2$.
+
+Now, let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$. 
+Set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$;
+by Proposition~\ref{prop:pullback}, $\qcs{L}_1$ a quasicharacter sheaf on $G_1$ 
+and $\qcs{L}_2$ is a quasicharacter sheaf on $G_2$.
+We will obtain an isomorphism $\qcs{L} \iso  \qcs{L}_1\boxtimes \qcs{L}_2$.
+%
+Applying the functor $f^*$ to the isomorphism $\mu$ yields the isomorphism
+\begin{equation}\label{eq:fm}
+f^*\mu : f^* m^* \gqcs{L} \to f^*(\gqcs{L}\boxtimes \gqcs{L}) .
+\end{equation}
+We have already observed that $m\circ f = \id_G$, so $f^* m^* \gqcs{L} = \gqcs{L}$ (canonical isomorphism).
+On the other hand, $f^*(\gqcs{L}\boxtimes \gqcs{L}) = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L}$, 
+by definition, and $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L}$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L}$ follows from the properties of these maps, articulated above, 
+so $f^*(\gqcs{L}\boxtimes \gqcs{L}) = \gqcs{L}_1\boxtimes \gqcs{L}_2$.
+It follows that \eqref{eq:fm} gives an isomorphism $\gqcs{L} \to  \gqcs{L}_1\boxtimes \gqcs{L}_2$.
+It is a matter of routine to show that this morphism satisfies Conditions~\ref{CS.2} as they apply here,
+from which it follows that we have exhibited an isomorphism 
+$\qcs{L} \to \qcs{L}_1\boxtimes \qcs{L}_2$ of quasicharacters sheaves on $G\times G$.
+This completes the proof that $\boxtimes$ is essentially surjective.
 \end{proof}

### 2013-09-24 shanghai.tex
Working on a diagram in Section 6

@@
 \begin{tikzcd}[row sep=20,column sep=10]
-\ & V \arrow{dd}{T} && \Aut(V) && \arrow{dl} \arrow[swap]{ll}{\psi_m} A_m \arrow[hook]{rr}
-&& \arrow[swap]{ld}{m_f} H_m \arrow{rr}{f_m} && \arrow[equal]{dd} \arrow{ld}{m} G\times G\\
- && && \arrow{ul}{\psi} A  \arrow[hook]{rr} && H  \arrow[swap, pos=0.8]{rr}{f} && G  & \\
-& V\otimes V && \Aut(V)
-&& \arrow[swap]{ll}{\psi \otimes \psi} \arrow[swap,pos=0.8]{uu}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr}
-&& \arrow[swap,pos=0.8]{uu}{\theta} \arrow{ul}{m_H} H\times H \arrow{rr}{f\times f} && G\times G
+\ & V \arrow{dd}{T} && \Aut(V) && A \arrow[hook]{rr} \arrow[swap]{ll}{\psi} &&  H \arrow{rr}{f} && G\\
+ && && \arrow{ul}{\psi_m} A_m  \arrow[hook]{rr} \arrow{ur} && H_m \arrow[pos=0.3]{ur}{m_f} \arrow[swap, pos=0.8]{rr}{f_m}
+ && G \times G \arrow[equal]{dr} \arrow[pos=0.42]{ur}{m} & \\
+& V\otimes V && \Aut(V) && \arrow[swap]{ll}{\psi \otimes \psi} \arrow[dashed,swap,pos=0.3]{ul}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr}
+&& \arrow[dashed,swap]{ul}{\theta} \arrow[crossing over,swap,pos=0.7]{uu}{m_H} H\times H \arrow{rr}{f\times f} && G\times G
 \end{tikzcd}

### 2013-09-24 counterexample.tex
Added counterexample to ZZ[x]/(x^n-1) is a FGC

\documentclass[11pt]{amsart}
\usepackage{amssymb}
\usepackage[alphabetic]{amsrefs}
\theoremstyle{plain}
      \newtheorem{theorem}{Theorem}[section]
      \newtheorem{proposition}[theorem]{Proposition}
      \newtheorem{lemma}[theorem]{Lemma}
\title{FGC Counterexample}

\newcommand{\ZZ}{{\mathbb{Z}}}
\newcommand{\QQ}{{\mathbb{Q}}}

\begin{document}
\maketitle
Let $R = \ZZ[x] / (x^2 - 1) \cong \{(a,b) \in \ZZ^2 | a \equiv b \pmod{2}\}$.

\begin{proposition}
The maximal ideals of $R$ are:
\begin{itemize}
\item $\langle (2,0), (0,2) \rangle$,
\item $\langle (2,0), (1,p) \rangle$ for odd primes $p \in \ZZ$,
\item $\langle (1,p), (0,2) \rangle$ for odd primes $p \in \ZZ$.
\end{itemize}
\end{proposition}
\begin{proof}
Suppose $I$ is a maximal ideal of $R$.  Since $(2,0) \cdot (0,2) = (0,0)$, either $(2,0) \in I$ or $(0,2) \in I$.  WLOG, $(2,0) \in I$.  Note that $R / (2,0) \cong \ZZ$ and thus there must be some element $(0,2a) \in I$ for minimal positive $a$.  The quotient $R / \langle (2,0), (0, 2a) \rangle \cong \ZZ / 2a\ZZ$, so if $a = 1$ then $I = \langle (2,0), (0,2) \rangle$ is maximal.  Otherwise, $I$ must contain an element of the form $(1,n)$ and we may take $n$ to be minimal and thus prime.
\end{proof}

\begin{proposition}
The localizations of $R$ at maximal ideals are:
\begin{itemize}
\item $\ZZ_{(2)} \times \ZZ_{(2)}$,
\item $\ZZ_{(p)}$ for odd primes $p$.
\end{itemize}
\end{proposition}
\begin{proof}
Suppose $P = \langle (2,0), (0,2) \rangle$.  Then 
\[
R_P = \left\{\left(\frac{a}{b},\frac{c}{d}\right) \in \QQ^2 | a \equiv c \pmod{2}, b \equiv d \equiv 1 \pmod{2}\right\} \cong \ZZ_{(2)} \times \ZZ_{(2)}
\]
since the equivalence relation $(\frac{a}{b},\frac{c}{d}) \sim (\frac{a'}{b'},\frac{c'}{d'})$ reduces to equality of fractions because there are no zero divisors in the complement of $P$.

On the other hand, suppose $P = \langle (2,0), (1,p) \rangle$ (the other case is symmetric).  Then
\[
R_P = \left\{\left(\frac{a}{b}, \frac{c}{d}\right) \in \QQ^2 | a \equiv c \pmod{2}, b \equiv d \pmod{2}, d \not\equiv 0 \pmod{p}\right\} / \sim
\]
where $(\frac{a}{b}, \frac{c}{d}) \sim (\frac{a'}{b'}, \frac{c'}{d'})$ if  there is some $(r, s) \in R$ with $p \nmid s$ such that $(ab' - a'b)r = 0$ and $(cd' - c'd)s = 0$.  Since $s \ne 0$ we must have $\frac{c}{d} = \frac{c'}{d'}$, but we can take $r = 0$ so arbitrary values for $a, b, a', b'$ yield equivalent elements of $R_P$.  Thus $R_P \cong \ZZ_{(p)}$.
\end{proof}

Note that $\ZZ_{(2)} \times \ZZ_{(2)}$ is neither a discrete valuation ring nor a special PIR, and thus not FGC! \cite{Warfield:Decomposability}*{Theorem 4}.  We should therefore be able to find a $\ZZ[\ZZ/2\ZZ]$ module which is a direct summand of a product of cyclic modules.  This completely destroys the strategy for the proof of Proposition 9.1.

\bibliography{Biblio}
\end{document}

### 2013-09-24 shanghai.tex
catching up

@@
 Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^n}$; the commutative
-group scheme $\GN{T}_n$ plays the r\^{o}le of $G$.  Theorem~\ref{thm:application}
+group scheme $\GN{T}_n$ plays the r\^{o}le of $G$, above.  Theorem~\ref{thm:application}
 allows us to translate characters $T(K)$ of depth less than $n$ into quasicharacter sheaves on $\GN{T}_n$:
@@
 While we have not yet fully explored the applications of such a geometrization, we want to highlight
-some of the potential benefits of Theorem~\ref{thm:application}. 
-%\begin{enumerate}
-%\item
+some of the potential benefits of Theorem~\ref{thm:application} here.
+
 Characters on $T$ have limited
@@
 We hope to use this to our advantage as we work toward an adaptation of Lusztig's theory of characters sheaves to the study of characters of admissible representations of reductive $p$-adic groups that extends beyond the case of $p$-adic tori.
-%\item
+
 DeBacker and Reeder have recently applied Deligne-Lusztig representations to part of the
@@
 representations of $p$-adic groups.
-%\item
+
 The scope of the Langlands program has grown explosively in the past several decades, and
@@
 program to be applied to the classic context.
-%\item
+
 Finally, we are tantalized by the possibility of providing an alternate perspective on local class field theory
 through quasicharacter sheaves.  The local Langlands correspondence for tori provides an isomorphism
-\[
-\Hh^1(\Weil{K}, \hat{T}_\ell) \cong \Hom(T(K), \EEx).
-\]
+$
+\Hh^1(\Weil{K}, \hat{T}_\ell) \cong \Hom(T(K), \EEx)
+$. 
 A geometric description of the resulting isomorphism $\Hh^1(\Weil{K}, \hat{T}_\ell) \cong \QCiso{\GN{T}}$
 would yield a different description of the Artin reciprocity map.
-%\end{enumerate}
 

### 2013-09-25 shanghai.tex
de-itemization, one \ceq

--- 2013-09-24 shanghai.tex
@@
 some of the potential benefits of Theorem~\ref{thm:application}. 
-%\begin{enumerate}
-%\item
+%
 Characters on $T$ have limited
@@
 program to be applied to the classic context.
-%\item
+
 Finally, we are tantalized by the possibility of providing an alternate perspective on local class field theory
@@
 would yield a different description of the Artin reciprocity map.
-%\end{enumerate}
 
@@
 
-Now, let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$. 
+Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$. 
 Set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$;
@@
 %
-Applying the functor $f^*$ to the isomorphism $\mu$ yields the isomorphism
+Applying the functor $f^*$ to the isomorphism $\mu$ yields
 \begin{equation}\label{eq:fm}
@@
 \end{equation}
-We have already observed that $m\circ f = \id_G$, so $f^* m^* \gqcs{L} = \gqcs{L}$ (canonical isomorphism).
+We have already observed that $m\circ f = \id_G$, so $f^* m^* \gqcs{L} = \gqcs{L}$.
 On the other hand, $f^*(\gqcs{L}\boxtimes \gqcs{L}) = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L}$, 

### 2013-10-01 shanghai.tex
We discussed the changes in this commit, in person.

@@
 Our quasicharacter sheaves evolved from this notion, and Theorem~\ref{thm:snake}
-is a direct generalization of the sheaf--function dictionary to the case of commutative
+is a direct generalization of the sheaf--function dictionary to the case of certain commutative
 group schemes which are not necessarily connected or finite type.  The main use
@@
 In Section~\ref{sec:category} we define quasicharacter sheaves and give an interpretation of
-them as Weil sheaves with a Galois action.
+them as Weil sheaves with certain properties.
 Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism,
@@
 we may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
-\Clifton{Please note what I did here.}
 and the value of $\Nm^*(t_G(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
@@
 \begin{proposition}
-There is a canonical functor $B_G^* : \QCb(G) \hookrightarrow \QC(G)$. Moreover, $B_G^*$
-is full and faithful, identifying $\QCb(G)$ with a full subcategory of $\QC(G)$.
+Extension of scalars defines a full and faithful functor 
+$B_G^* : \QCb(G) \hookrightarrow \QC(G)$,
+thus identifying $\QCb(G)$ with a full subcategory of $\QC(G)$.
 \end{proposition}
@@
  Moreover, $\phi$ is compatible with $\mu$ in the sense of Condition~\ref{CS.3}.
- It follows that $B_G^* : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
- is full and faithful.
+ This defines the functor $B_G^* : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
+ and also shows that it is full and faithful.
 \end{proof}
@@
 $\QCbiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such
-that the image of $\chi$ is bounded in $\EEx$; see Section~\ref{sec:snake} for more details.
+that the image of $\chi$ is bounded in $\EEx$; 
+see Section~\ref{sec:snake} for more details regarding this point.
 
@@
 the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $f^{-1}({\bar e})$ is trivial.
-We first begin by defining a category $C(G)$, whose objects consist of pairs $(f,\psi)$ where
+We first begin by defining a category $C(G)$ whose objects consist of pairs $(f,\psi)$ where
 \begin{itemize}
-\item $f : H\to G$ is a discrete isogeny;
+\item $f : H\to G$ is a discrete isogeny,
 \item $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$.
@@
 \begin{itemize}
-\item $\alpha : H' \to H$ is a morphism of schemes such that $f' = f\circ \alpha$;
+\item $\alpha : H' \to H$ is a morphism of schemes such that $f' = f\circ \alpha$,
 \item $T : V\to V'$ is a linear transformation equivariant for the action of
@@
 Let \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at weak isomorphisms.
+
+%Now consider the localization $C(G)[W^{-1}]$ of $C(G)$ at weak isomorphisms.
+ Morphisms in $C(G)[W^{-1}]$ are simple to describe because category $C(G)$ 
+ admits a calculus of left fractions
+ %\footnote{See {\tt http://ncatlab.org/nlab/show/calculus+of+fractions}.} 
+ for weak isomorphisms:
+% every isomorphism in $C(G)$ is a weak isomorphism; 
+% push-outs exist in $C(G)$ and the push-out of a weak isomorphism is a weak isomorphism; 
+% and weak isomorphisms enjoy the left-cancellation property. 
+% It follows that
+ a morphism in $C(G)[W^{-1}]$ is the equivalence class of 
+  \begin{equation}\label{eq:morGCf}
+   \begin{tikzcd}
+   (f,\psi) \arrow{r}{(\alpha_1,T_1)} & (f_1,\psi_1) & \arrow[swap]{l}{(\beta_1,U_1)} (f',\psi')
+   \end{tikzcd}
+  \end{equation}
+ where $(\alpha',T') : (f,\psi) \to (f',T')$ is any map in $C(G)$ 
+ and $(\beta_1,U_1) : (f_1,\psi_1) \to (f',\psi')$ is a weak isomorphism.
 
@@
 Likewise, $C(G)[W^{-1}]$ is a tensor category.
-\David{Should expand on this a bit and note that $C(G)[W^{-1}]$ admits a calculus of fractions}
 
@@
  This functor commutes with pull-back along any morphism of group schemes.
-
- Now consider the localization $C(G)[W^{-1}]$ of $C(G)$ at weak isomorphisms.
- Morphisms in $C(G)[W^{-1}]$ are simple to describe because category $C(G)$ 
- admits a calculus of left fractions
- %\footnote{See {\tt http://ncatlab.org/nlab/show/calculus+of+fractions}.} 
- for weak isomorphisms:
-% every isomorphism in $C(G)$ is a weak isomorphism; 
-% push-outs exist in $C(G)$ and the push-out of a weak isomorphism is a weak isomorphism; 
-% and weak isomorphisms enjoy the left-cancellation property. 
-% It follows that
- a morphism in $C(G)[W^{-1}]$ is the equivalence class of 
-  \begin{equation}\label{eq:morGCf}
-   \begin{tikzcd}
-   (f,\psi) \arrow{r}{(\alpha_1,T_1)} & (f_1,\psi_1) & \arrow[swap]{l}{(\beta_1,U_1)} (f',\psi')
-   \end{tikzcd}
-  \end{equation}
- where $(\alpha',T') : (f,\psi) \to (f',T')$ is any map in $C(G)$ 
- and $(\beta_1,U_1) : (f_1,\psi_1) \to (f',\psi')$ is a weak isomorphism.
 
@@
   $G^0(\bFq) \to G(\bFq)$ induces the map
-  $\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))$,
+  \[
+  \Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))
+  \]
   fitting into the long exact sequence derived from applying
@@
   \]
+
   We now show that $\Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)) = 0$.
-
+%
   It suffices to show that $\pi_0(G)(\bFq)$ has a two-term resolution
@@
   $\Gamma_m \ceq \Gamma / H_m$.  Any product of Dedekind domains has
-  cohomological dimension $1$ \David{Add a citation for this fact}, so $\pi_0(G)(\bFq)$ has a
+  cohomological dimension $1$, \David{Add a citation for this fact} so $\pi_0(G)(\bFq)$ has a
   two term resolution by injective $\ZZ[\Gamma_m]$-modules.  Let $I$
@@
   The dotted arrow exists since $I$ is injective as a
-  $\ZZ[\Gamma_m]$-module, and the outer diagram shows that $I$ is
+  $\ZZ[\Gamma_m]$-module and the outer diagram shows that $I$ is
   injective as a $\ZZ[\Gamma]$-module.
@@
 $\rho_1(\Frob{\Fq}) = \ell$, necessarily continuous. 
-\Clifton{I made some small changes to wording, here.}
 But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, 

### 2013-10-01 shanghai.tex
Removed section 9, corrected and vastly simplified the proofs of Prop 9.1 (now Lem 8.3) and Cor 9.2 (now Prop 8.4)

--- 2013-09-25 shanghai.tex
@@
 some of the potential benefits of Theorem~\ref{thm:application}. 
-%
+%\begin{enumerate}
+%\item
 Characters on $T$ have limited
@@
 representations of $p$-adic groups. 
-
+%\item
 The scope of the Langlands program has grown explosively in the past several decades, and
@@
 of quasicharacter sheaves in this case.  Using a notion of global sections for quasicharacter sheaves,
-we give an isomorphism between $\QCiso{G}$ and $\Hh^1(\Weil{\Fq}, \Hom(G(\bFq), \EEx))$.
-Section~\ref{sec:etalecohom} proves a result in Galois cohomology that shows that trace of Frobenius is
-an isomorphism for \'etale group schemes.
+we give isomorphisms between $\QCiso{G}$, $\Hh^1(\Weil{\Fq}, \Hom(G(\bFq), \EEx))$ and $\Hom(G(\Fq), \EEx)$.
 In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
@@
 
-Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$. 
+Now, let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$. 
 Set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$;
@@
 %
-Applying the functor $f^*$ to the isomorphism $\mu$ yields
+Applying the functor $f^*$ to the isomorphism $\mu$ yields the isomorphism
 \begin{equation}\label{eq:fm}
@@
 \end{equation}
-We have already observed that $m\circ f = \id_G$, so $f^* m^* \gqcs{L} = \gqcs{L}$.
+We have already observed that $m\circ f = \id_G$, so $f^* m^* \gqcs{L} = \gqcs{L}$ (canonical isomorphism).
 On the other hand, $f^*(\gqcs{L}\boxtimes \gqcs{L}) = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L}$, 
@@
 
-\section{On the cohomology of the dual of an \'etale group scheme} \label{sec:etalecohom}
-
-Although the next proposition makes no mention quasicharacter sheaves, 
-it has immediate application to the problem of finding all quasicharacter sheaves
-on finitely generated etale group schemes, as we will see at the end of the section.
-
-\begin{proposition}\label{prop:X}
-  Let $X$ be a finitely generated abelian group equipped with an
-  action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on
-  $X$.  Then
+In order to relate $\QCiso{G}$ to $G(k)^*$, we need a simple result relating duals, invariants and coinvariants.
+
+\begin{lemma} \label{lem:dual-inv}
+Let $X$ be a finitely generated abelian group equipped with an action of $\Weil{\Fq}$, and write $\Frob{} = \Frob{\Fq}$.  Then
 \begin{align*}
-    \Hh^1(\Fq, X^*) &\xrightarrow{\rho} \Hh^0(\Fq, X)^*, \\
-    \rho([z])(x) &\ceq z(\Frob{\Fq})(x),
+ (X^*)_{\Frob{}} &\to (X^{\Frob{}})^* \\
+ [f] &\mapsto f|_{X^{\Frob{}}}
 \end{align*}
+is an isomorphism.
+\end{lemma}
+\begin{proof}
+We can describe $X^{\Frob{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
+let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
+\[
+ 0 \to X^{\Frob{}} \to X \to Y \to 0
+\]
+yields
+\[
+ 0 \to Y^* \to X^* \to (X^{\Frob{}})^* \to \Ext^1_\ZZ(Y, \EEx).
+\]
+Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Frob{}})^*$.
+\end{proof}
+
+\begin{proposition} \label{prop:etale-iso}
+ If $G$ is a commutative, \'etale group scheme over $\Fq$ and $G(\bFq)$ is finitely
+ generated then
+ \[
+  \trFrob{G} : \QCiso{G} \to G(\Fq)^*
+ \]
  is an isomorphism of groups.
@@
 \begin{proof}
-  We first prove that $\rho$ is surjective.  Suppose that
-  $f \in \Hom(X^{\Frob{\Fq}}, \EEx).$ Since $\EEx$ is divisible
-  as an abelian group it is injective as a $\ZZ$-module and thus
-  $\Ext^1_{\ZZ}(X/X^{\Frob{\Fq}}, \EEx) = 0$.  The long exact 
-  sequence obtained by applying the functor
-  $\Hom(\mbox{---}, \EEx)$ to
-  \[
-  \begin{tikzcd}
-  0 \rar & X^{\Frob{\Fq}} \rar & X \rar & X/X^{\Frob{\Fq}} \rar & 0
-  \end{tikzcd}
-  \]
-  gives the existence of an $\tilde{f} \in \Hom(X, \EEx)$ restricting to
-  $f$.  Define a $1$-cocycle $z \in \Hh^1(\Fq, \Hom(X,\EEx))$ by
-  mapping $\Frob{\Fq}$ to $\tilde{f}$.  Then $\rho([z]) = f$.
-
-  Now suppose that $[z] \in \Hh^1(\Fq,\Hom(X,\EEx))$ with
-  $\rho([z]) = 1$; write $\tilde{f}$ for $z(\Frob{\Fq})$.  The injectivity
-  of $\rho$ is equivalent to the existence of a homomorphism $\psi
-  \colon X \rightarrow \EEx$ with
-  \[
-  \tilde{f}(x) = \frac{\psi(\Frob{\Fq}(x))}{\psi(x)}
-  \]
-  for $x \in X$.  In fact, we may replace the construction of $\psi$
-    \Clifton{I'm not sure I understand what you mean here.}
-  for all $\ZZ[\Gal(\bFq/\Fq)]$-modules $X$ with the construction of
-  analogous $\psi$s for a different class of modules.
-
-  The $\ZZ[\Gal(\bFq/\Fq)]$-module $X$ decomposes into 
-  a finite direct sum of cyclic $\ZZ[\Gal(\bFq/\Fq)]$-modules. 
-  To see this, observe first that since the action of $\Gal(\bFq/\Fq)$ is continuous, 
-  there is a positive integer $m$ so that $\Frob{\Fq}^m$ acts trivially on $X$; 
-  write $\Fqm$ for the degree $m$ extension of $\Fq$ in $\bFq$ 
-  and $\Gamma_m$ for $\Gal(\Fqm/\Fq)$.  Since
-  $T^m-1$ factors as a squarefree product of cyclotomic polynomials,
-  the Chinese remainder theorem expresses $\ZZ[\Gamma_m]$ as a product
-  of $\ZZ[\zeta_d]$ for $d$ dividing $m$.  Each $\ZZ[\zeta_d]$ is the
-  maximal order in a number field and thus $\ZZ[\Gamma_m]$ is a
-  product of Dedekind domains. Combining \cite{Warfield:Decomposability}*{Theorem 3}
-  and \cite{brandal:CommRingsFGModDecompose}*{Lemma 4.1}, it now follows that 
-  $X$ decomposes into a direct sum of cyclic $\ZZ[\Gamma_m]$-modules, 
-  each of the form $\ZZ[\Gamma_m] / I$ for some ideal $I \subset \ZZ[\Gamma_m]$.
-  The ideal $I$ corresponds to a direct product of ideals $I_d$ in the
-  $\ZZ[\zeta_d]$, and within each $\ZZ[\zeta_d]$ the Chinese remainder
-  theorem allows a further decomposition of $\ZZ[\zeta_d] / I_d$ as a
-  direct sum of $\ZZ[\zeta_d]$-modules of the form $\ZZ[\zeta_d]/P^s$.
-  So if we can construct, for every cyclotomic ring $\ZZ[\zeta_d]$,
-  prime ideal $P \subset \ZZ[\zeta_d]$ and positive integer $s$, a
-  $\psi \colon \ZZ[\zeta_d]/P^s \rightarrow \EEx$ with
-  \begin{equation} \label{eq:psi-condition}
-    \tilde{f}(x) = \frac{\psi(\zeta_d \cdot x)}{\psi(x)},
-  \end{equation}
-  then the existence of the original $\psi$ follows because $X$ is a
-  direct sum of such $\ZZ[\zeta_d]/P^s$.
-
-  We now fix a $d$, $P$ and $s$, write $\zeta$ for $\zeta_d$ and
-  choose a polynomial
-  \[
-  h(T) \ceq a_rT^r + a_{r-1}T^{r-1} + \cdots + a_0
-  \]
-  so that $P^s = (p^s, h(\zeta_d))$.
-  % Setting $\psi = 1$ will satisfy Equation \ref{eq:psi-condition}
-  % when $d = 1$.
-  An an abelian group, the quotient $\ZZ[\zeta] / P^s$ is generated by
-  $\zeta^i$ for $0 \le i < \phi(d)$; we define
-  \begin{equation} \label{eq:psi-def}
-    \psi(\zeta^i) \ceq \alpha \prod_{j=0}^{i-1} \tilde{f}(\zeta^j)
-  \end{equation}
-  for an $\alpha \in \EEx$ to be chosen later.  Since there are
-  relations among the $\zeta^i$ we first need to check that $\psi$ is
-  well-defined.
-
-  The relations among the generators $\zeta^i$ are additively
-  generated by $\zeta^ch(\zeta)$ as $c$ ranges from $0$ to
-  $\phi(d)-r-1$.  If we set
-  \[
-  A_c \ceq \sum_{i=0}^r a_i \sum_{j=0}^{i+c-1} \zeta^j
-  \]
-  then
-  \[
-  \psi(\zeta^ch(\zeta)) = \alpha^{h(1)} \tilde{f}(A_c).
-  \]
-  Now consider $(\zeta - 1)A_c$: the sums telescope and we get that
-  $(\zeta-1)A_c = \zeta^ch(\zeta) - h(1).$ There are now two
-  possibilities:
-  \begin{enumerate}
-  \item $d$ is a power of $p$; write $s = \phi(d)m + n$.  We may take
-    $h(T)$ to be $p^m(T-1)^n$, in which case $\zeta^ch(\zeta) - h(1) \in P^s$,
-    so $A_c$ is fixed under multiplication by $\zeta$ in
-    $\ZZ[\zeta]/P^s$ and thus $\tilde{f}(A_c) = 1$.  In this case
-    $\alpha^{h(1)} = 1$ regardless of $\alpha$.
-  \item $d$ is not a power of $p$.  If two distinct primes divide $d$
-    then $\zeta - 1$ is a unit; otherwise $\zeta - 1$ is a unit modulo
-    $P^s$.  Let $\omega \in \ZZ[\zeta]$ satisfy
-    $\omega(\zeta - 1) \equiv 1 \pmod{P^s}$ and set
-    %\begin{equation} \label{alpha-def}
-     $ \alpha \ceq \tilde{f}(\omega)$.
-    %\end{equation}
-    Then $A_c + h(1)\omega$ is fixed under multiplication by $\zeta$
-    and thus $\tilde{f}(A_c) = \tilde{f}(-h(1)\omega)$.
-  \end{enumerate}
-  In either case, $\psi(\zeta^ch(\zeta)) = 1$ for all $c$.  The only
-  other relations imposed on the $\zeta^i$ are that they are all
-  killed under multiplication by $p^s$.  Since $\tilde{f}$ is also a
-  homomorphism $\ZZ[\zeta]/P^s \rightarrow \EEx$ the values of
-  $\tilde{f}$ and thus of $\psi$ will be $p^s$-roots of unity.
-  Therefore $\psi$ is well defined.
-
-  We now check Equation~\eqref{eq:psi-condition} for
-  $x \ceq \zeta^{\phi(d)-1}$.  Write
-  \[\Phi_d(T) \ceq T^{\phi(d)} - b_{\phi(d)-1}T^{\phi(d)-1} - \cdots - b_0\]
-  and set
-  \[
-  B \ceq b_i \sum_{j=0}^{i-1} \zeta^j -  \sum_{i=0}^{\phi(d)-1} \zeta^i.
-  \]
-  We have
-
-  \begin{align*}
-    \frac{\psi(\zeta^{\phi(d)})}{\psi(\zeta^{\phi(d)-1})\tilde{f}(\zeta^{\phi(d)-1})}
-    &= \frac{\psi(b_{\phi(d)-1}\zeta^{\phi(d)-1} + \cdots + b_0)}{\psi(\zeta^{\phi(d)-1})\tilde{f}(\zeta^{\phi(d)-1})} 
-    = \alpha^{-\Phi_d(1)} \tilde{f}(B).
-  \end{align*}
-  As before we see that $(\zeta - 1)B = \Phi_d(1) - \Phi_d(\zeta) = \Phi_d(1)$.
-  We consider the same cases as before:
-
-  \begin{enumerate}
-  \item $d$ is a power of $p$, in which case $\Phi_d(1) = p$.  Thus
-    $(\zeta-1)B = p = u(\zeta-1)^{\phi(d)}$ for a unit $u \in \ZZ[\zeta]$
-    and $B - u(\zeta-1)^{\phi(d)-1}$ is fixed by $\zeta$,
-    so that $\tilde{f}(B) = \tilde{f}(u(\zeta - 1)^{\phi(d)-1})$.  The
-    multiplicative order of $\tilde{f}(u(\zeta-1)^{\phi(d)-1})$ is at most
-    $\lceil \frac{s - 1 - (\phi(d)-1)}{\phi(d)}\rceil = \lceil \frac{s}{\phi(d)} \rceil - 1$
-    while the additive order of $1 \in \ZZ[\zeta]/P^s$ is $\lceil \frac{s}{\phi(d)} \rceil$.
-    Thus we may choose $\alpha = \psi(1)$ with $\alpha^p = \tilde{f}(B)$.
-  \item $d$ is not a power of $p$ and $\omega$ is the inverse of
-    $\zeta-1$ modulo $P^s$.  Then $\tilde{f}(B) = \tilde{f}(\omega\Phi_d(1))$.
-  \end{enumerate}
-  In either case, $\alpha^{-\Phi_d(1)}\tilde{f}(B) = 1$ and thus
-  $\psi$ satisfies Equation~\eqref{eq:psi-condition} for
-  $x \ceq \zeta^{\phi(d)-1}$.  The definition of $\psi$ in \ref{eq:psi-def}
-  immediately implies that $\psi$ satisfies equation
-  \ref{eq:psi-condition} for lesser powers of $\zeta$, and thus for
-  all $x$ by linearity.  The existence of $\psi$ shows that $\rho$ is injective.
-\end{proof}
-
-\begin{corollary}
- If $G$ is a commutative, \'etale group scheme over $\Fq$ and $G(\bFq)$ is finitely
- generated then
-  \[
-  \trFrob{G} : \QCiso{G} \to G(\Fq)^*
-  \]
-  is an isomorphism of groups.
-\end{corollary}
-\begin{proof}
-This follows from Proposition~\ref{prop:etale} by setting $X=G(\bFq)$ in Proposition~\ref{prop:X}.
-Recall that $G \mapsto G(\bFq)$ defines an equivalence of categories from commutative \'etale group schemes over $\Fq$ to commutative groups equipped with \emph{continuous} actions by $\Gal(\bFq/\Fq)$; see, for example, \cite{vdGeer-Moonen:AbelianVarieties}*{Prop 3.26}.
+There is a natural isomorphism $\Hh^1(\Weil{\Fq}, G(\bFq)^*) \to (G(\bFq)^*)_{\Frob{}}$ defined by $[z] \mapsto z(\Frob{})$.
+The proposition now follows directly from Proposition~\ref{prop:etale} and Lemma~\ref{lem:dual-inv}.
 \end{proof}
@@
   that $\ker \trFrob{G^0} =0$ and $\coker \trFrob{G^0}=0$. 
-  On the other hand, it follows from Propositions~\ref{prop:etale} and \ref{prop:X}, $\ker \trFrob{\pi_0(G)}=0$
+  On the other hand, it follows from Propositions~\ref{prop:etale-iso} that $\ker \trFrob{\pi_0(G)}=0$
   and $\coker \trFrob{\pi_0(G)}=0$.
@@
   is exact at $G(\Fq)^*$ and $\coker \trFrob{\pi_0(G)} =0$
-  (by Propositions~\ref{prop:etale} and \ref{prop:X}) and
+  (by Proposition~\ref{prop:etale-iso}) and
   \[
@@
   pull-back of $\chi$ along $G(\Fq)\to \pi_0(G)(\Fq)$ is
-  $\trFrob{\qcs{L}}$. By Propositions~\ref{prop:etale} and \ref{prop:X},
+  $\trFrob{\qcs{L}}$. By Proposition~\ref{prop:etale-iso},
   there is a a quasicharacter sheaf $\qcs{L}_\chi$ on $\pi_0(G)$, unique up

### 2013-10-02 shanghai.tex
Edits, mainly to section 5

@@
 \]
-after passing to isomorphism classes.  It is easy to see that $\QCiso{0}$ is trivial. In Sections~\ref{sec:connected}, \ref{sec:etale} and \ref{sec:etalecohom} we will find $\QCiso{G^0}$
+after passing to isomorphism classes.  It is easy to see that $\QCiso{0}$ is trivial. In Sections~\ref{sec:connected} and \ref{sec:etale} we will find $\QCiso{G^0}$
 and $\QCiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; 
@@
 We have already observed that $m\circ f = \id_G$, so $f^* m^* \gqcs{L} = \gqcs{L}$.
-On the other hand, $f^*(\gqcs{L}\boxtimes \gqcs{L}) = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L}$, 
-by definition, and $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L}$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L}$ follows from the properties of these maps, articulated above, 
-so $f^*(\gqcs{L}\boxtimes \gqcs{L}) = \gqcs{L}_1\boxtimes \gqcs{L}_2$.
+On the other hand, $f^*(\gqcs{L}\boxtimes \gqcs{L}) = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L}$
+by definition.  Since $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L}$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L}$
+we get that $f^*(\gqcs{L}\boxtimes \gqcs{L}) = \gqcs{L}_1\boxtimes \gqcs{L}_2$.
 It follows that \eqref{eq:fm} gives an isomorphism $\gqcs{L} \to  \gqcs{L}_1\boxtimes \gqcs{L}_2$.
@@
 
-If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$ we may define
+If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$, we may define
 a quasicharacter sheaf $\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
@@
 satisfying the analogue of Condition~\ref{CS.1} on $G$; 
-morphisms in $\QCb(G)$ are defined as in (the second part of) Condition~\ref{CS.2}. 
+morphisms in $\QCb(G)$ are defined as in the second part of Condition~\ref{CS.2}. 
 This is the category of \emph{bounded quasicharacter sheaves} on $G$. 
@@
  Moreover, $\phi$ is compatible with $\mu$ in the sense of Condition~\ref{CS.3}.
- This defines the functor $B_G^* : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
+ This construction defines the functor $B_G^* : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
  and also shows that it is full and faithful.
@@
 that the image of $\chi$ is bounded in $\EEx$; 
-see Section~\ref{sec:snake} for more details regarding this point.
+see Section~\ref{sec:snake} for more details.
 

### 2013-10-02 shanghai.tex
Edits, mainly to section 6

@@
 In general, $\QCb(G)$ is an essentially
-proper subcategory of $\QC(G)$. Indeed, it follows from Theorem~\ref{thm:snake}
+proper subcategory of $\QC(G)$. Indeed, it will follow from Theorem~\ref{thm:snake}
 that the restriction of $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ to the subgroup
@@
 of bounded quasicharacter sheaves that play a role in Section \ref{sec:restriction}.
-Let us say that $f : H\to G$ is a \emph{discrete isogeny} if it is a finite, surjective
-\'etale morphism and a morphism of commutative group $\Fq$-schemes for which
-the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $f^{-1}({\bar e})$ is trivial.
-We first begin by defining a category $C(G)$ whose objects consist of pairs $(f,\psi)$ where
+A morphism $f : H\to G$ of $\QC$-schemes is a \emph{discrete isogeny} if it is a finite, surjective
+\'etale morphism of commutative group $\Fq$-schemes for which
+the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f$ is trivial.
+We begin by defining a category $C(G)$ whose objects consist of pairs $(f,\psi)$, where
 \begin{itemize}
@@
 \end{itemize}
-A morphism $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(\alpha,T)$ where
+A morphism $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(\alpha,T)$, where
 \begin{itemize}
@@
 \item $T : V\to V'$ is a linear transformation equivariant for the action of
-$\ker f'$ on $V'$ by $\psi'$ and the action of $\ker '$ on $V$ by $\psi \circ \alpha$.
+$\ker f'$ on $V'$ by $\psi'$ and the action of $\ker f'$ on $V$ by $\psi \circ \alpha$.
 \[
@@
  Morphisms in $C(G)[W^{-1}]$ are simple to describe because category $C(G)$ 
- admits a calculus of left fractions
+ admits a calculus of left fractions \David{Should add a reference for calculus of fractions that isn't nlab}
  %\footnote{See {\tt http://ncatlab.org/nlab/show/calculus+of+fractions}.} 
@@
 $\psi \otimes\psi' :  \ker(f\times_G f') \to \Aut(V\otimes V')$ and a external sum
-$\psi \oplus\psi' :  \ker(f\times_G f') \to \Aut(V\otimes V')$
+$\psi \oplus\psi' :  \ker(f\times_G f') \to \Aut(V\oplus V')$
 using the canonical isomorphism $\ker(f\times_G f') \iso (\ker f)\times (\ker f')$.
@@
 \begin{lemma}\label{lemma:finite-iso}
-Each $(f,\psi)\in \QCf(G)$ determines a canonical isomorphism $m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$.
+Each $(f,\psi)\in \QCf(G)$ determines a canonical isomorphism $m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$. \David{I'm confused at first reading by the statement of this lemma}
  \end{lemma}
@@
  and the stalk $L(f,\psi)_{\bar g}$ of $L(f,\psi)$ at a geometric point ${\bar g}$ on $G$ 
- with the $\EE$-vector space consisting of those functions $s: \abs{f^{-1}({\bar s})} \to V$ such that 
+ with the $\EE$-vector space consisting of those functions $s: \abs{f^{-1}({\bar g})} \to V$ such that 
  $s(a\cdot {\bar h}) = \psi(a)(s({\bar h}))$ for all $a\in \ker f$ and for all ${\bar h} \in f^{-1}({\bar g})$.
@@
  by $s \mapsto s' \ceq T\circ s\circ \alpha$. 
- This defines a monoidal functor $L$ from $C(G)$ to $\Loc(G)$. 
- This functor commutes with pull-back along any morphism of group schemes.
-
- Observe that $L$ takes weak isomorphisms in $C(G)$ to isomorphisms in $\Loc(G)$. 
- To see this, suppose $(\beta,U) : (f,\psi)\to (f',\psi')$ is a weak isomorphism. 
+ This construction defines a monoidal functor $L$ from $C(G)$ to $\Loc(G)$ that
+ commutes with pull-back along any morphism of group schemes.
+
+ We now show that $L$ takes weak isomorphisms in $C(G)$ to isomorphisms in $\Loc(G)$. 
+ Suppose $(\beta,U) : (f,\psi)\to (f',\psi')$ is a weak isomorphism. 
  Since $U$ is an isomorphism, we may replace $V'$ with $V$ and $U$ with $\id_V$, without loss of generality. 
  Then the equivariance condition on $U$ becomes $\psi' = \psi\circ \beta$ on the finite \'etale group scheme $\ker f'$. 
- Since $f$ and $f'$ are finite \'etale, and $f' = f\circ \beta$, and $\beta$ is surjective,
- $\beta$ is an \'etale cover; therefore, $\beta$ admits a section $\beta' : H \to H'$.
- This provides the inverse to $L(\beta,U) : L(f,\psi) \to L(f',\psi')$.
+ Since $f$ and $f'$ are finite \'etale, the relation $f' = f\circ \beta$ implies that $\beta$ is \'etale.  Since $\beta$ is surjective,
+ it is an \'etale cover and thus admits a section $\beta' : H \to H'$. \David{Why do \'etale covers have sections?}
+ This provides the inverse to $L(\beta,U) : L(f,\psi) \to L(f',\psi')$. \David{What is the inverse of $L(\beta, U)$?}
 
  Conversely, if $L(\alpha,T)$ is an isomorphism of local systems, 
- then $T$ must be an isomorphism of vector spaces and $\beta$ must be surjective,
- whence $(\alpha,T)$ is a weak isomorphism: $W$ is saturated.
+ then $T$ must be an isomorphism of vector spaces and $\beta$ must be surjective, \David{I assume that this statement follows directly from the definition of isomorphisms of local systems?}
+ whence $(\alpha,T)$ is a weak isomorphism: $W$ is saturated. \David{It's not clear to me how the claim that $W$ is saturated fits into the rest of this paragraph}
 
  Since $L : C(G) \to \Loc(G)$ takes weak isomorphisms to isomorphisms,
- it factors, uniquely, through the localisation functor $C(G) \to C(G)[W^{-1}]$ 
+ it factors through the localization functor $C(G) \to C(G)[W^{-1}]$ 
  to define a faithful functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$. 
@@
 
- By Lemma~\ref{lemma:finite-iso}, each $(f,\psi) \in \QCf(G)$ determines 
- an isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi) \boxtimes (f,\psi)$ in $\QCf(G\times G)$, canonically.
+ By Lemma~\ref{lemma:finite-iso}, each $(f,\psi) \in \QCf(G)$ canonically determines 
+ an isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi) \boxtimes (f,\psi)$ in $\QCf(G\times G)$.
  It follows immediately that the functor 
@@
 
-The full subcategory $\QCf(G) \subset \QCb(G)$ of finite quasicharacter sheaves
-is a proper subcategory, in general. Indeed, it follows from our main result regarding
-quasicharacter sheaves, Theorem~\ref{thm:snake}, that the restriction of
+For general $G$, there are bounded quasicharacter sheaves which are not finite.  Indeed,
+it will follow from Theorem~\ref{thm:snake} that the restriction of
 $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ to the subgroup $\QCfiso{G}$ is an isomorphism

### 2013-10-03 shanghai.tex
Edits, mainly to section 7

@@
 \begin{proposition}\label{prop:bounded}
- $\QCf(G)$ is (equivalent to) a full subcategory of $\QCb(G)$.
+ $\QCf(G)$ is equivalent to a full subcategory of $\QCb(G)$.
 \end{proposition}
@@
   the full subcategories $\QCf(G) \hookrightarrow \QCb(G) \hookrightarrow \QC(G)$ 
-  appearing in Section~\ref{sec:bounded} are equivalences 
+  appearing in Sections~\ref{sec:bounded} and \ref{sec:finite} are equivalences 
   and
@@
   and let $\bg$ be the geometric point on $G$ lying above $g$ 
-  (we fixed $\Fq \hookrightarrow \bFq$ long ago). 
   Since $G$ is connected, the geometric point $\bg$ determines
   an equivalence between the category of $\ell$-adic Weil local systems on $G$ and
-  $\ell$-adic representations of $\W(G,\bg)$ \cite{deligne:80a}*{1.1.12}. 
+  $\ell$-adic representations of $\W(G,\bg)$ \cite{deligne:80a}*{1.1.12}.  \David{We should include a definition for $\W(G,\bg)$, perhaps in an intro paragraph for the section}
   Now let $(\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$ 
@@
   $\Weil{\Fq}\to \W(G,\bg)$ of $\W(G,\bg)\to \Weil{\Fq}$. 
-  In this way the Weil local system $(\gqcs{L},F)$ determines an $\ell$-adic character $\rho_g : \Weil{\Fq} \to \EEx$.
+  In this way the Weil local system $(\gqcs{L},\phi)$ determines an $\ell$-adic character $\rho_g : \Weil{\Fq} \to \EEx$.
   %\[
@@
   \]
+  \David{It's not clear to me whether we've just proven this claim or if we're citing it from somewhere}
 
@@
   is a group homomorphism. Since $G$ is an algebraic group over $\Fq$, it is a
-  variety over $\Fq$, so finitely generated over $\Fq$, so $G(\Fq)$ is finite;
-  it follows that $\trFrob{\qcs{L}}(g) = \rho_g(\Frob{\Fq})$ is a root of unity,
+  variety over $\Fq$ and thus $G(\Fq)$ is finite.
+  Therefore $\trFrob{\qcs{L}}(g) = \rho_g(\Frob{\Fq})$ is a root of unity
   for every $g\in G(\Fq)$.  Since $\Weil{\Fq}$ is generated by
@@
 
-  To show that $L_G(f,\psi) \iso (\qcs{L}_0,\mu_0)$ we simply apply the functions--sheaves dictionary
-  as follows ({\it cf} \cite{laumon:87a}*{1.1.3} or, ultimately, \cite{deligne:SGA4.5}*{Sommes trigonométriques}).
+  To show that $L_G(f,\psi) \iso (\qcs{L}_0,\mu_0)$ we simply apply the sheaf--function dictionary
+  as follows \citelist{\cite{laumon:87a}*{1.1.3} \cite{deligne:SGA4.5}*{Sommes trigonométriques}}.
   First, recall that $L_G(f,\psi) \ceq (L(f,\psi), \mu(f,\psi))$.
@@
 %\[\pi_1(G,{\bar e}) \to \Pi_\text{et}(G) \to \Pi_\text{et}(G)_{\Gal(\bFq/\Fq)} = \Pi_\text{disc}(G)\]
-From this it is apparent that the category of discrete isogenies to $G$ is a Galois category,
-in the sense of \cite{grothendieck:SGA1}*{Expos\'e V, \S 4}. Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$,
-as shown in \cite{kamgarpour:09a}*{App'x B}, this provides an alternate proof of
+This discussion demonstrates that the category of discrete isogenies to $G$ is a Galois category
+\cite{grothendieck:SGA1}*{Expos\'e V, \S 4}. Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$
+\cite{kamgarpour:09a}*{App'x B}, this \David{What does ``this'' refer to} provides an alternate proof that
 $\QCiso{G} \iso G(\Fq)^*$ when $G$ is a connected algebraic group over $\Fq$.
@@
 since the component group of a $\QC$-scheme
-is an \'etale group scheme, locally of finite type over $\Fq$
-\cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
+is an \'etale group scheme \cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
 The functor $G \mapsto G(\bFq)$ defines an equivalence of categories

### 2013-10-03 shanghai.tex
A few edits to section 8
Made a bunch of small changes, mainly stylistic, and added a few flags for discussion tomorrow.

--- 2013-10-02 shanghai.tex
@@
 We hope to use this to our advantage as we work toward an adaptation of Lusztig's theory of characters sheaves to the study of characters of admissible representations of reductive $p$-adic groups that extends beyond the case of $p$-adic tori.
+\Clifton{Combine these two paragraphs? It seems they make the same point. Waldspurger also uses D-L to study depth-zero distributions. Mention this, too? Mention neither?}
 
@@
 define a \emph{$\QC$-scheme} to be such a $G$ with the additional property that the
-geometric component group of $G$ is finitely generated.  This last assumption is only
+geometric component group of $G$ is finitely generated.  This last condition is only
 needed in the proof of Lemma \ref{lemma:section}.
@@
 
-As mentioned after \cite{deligne:80a}*{Def.~1.1.10}, a Weil sheaf $(\gqcs{L},\phi)$ on $G$
+A Weil sheaf $(\gqcs{L},\phi)$ on $G$
 may be interpreted as a constructible $\ell$-adic sheaf $\gqcs{L}$ on $\bG$ together with
 an action of the Weil group $\Weil{\Fq}$ on $\gqcs{L}$ compatible with the action of
-$\Gal(\bFq/\Fq)$ on $\bG$. We now review this point of view for later use in
-Section~\ref{sec:basechange}.  If $w \ceq \Frob{\Fq}^n$ we write $w_G$ for $\Frob{G}^n$.
+$\Gal(\bFq/\Fq)$ on $\bG$. We now briefly review this point of view for later use in
+Section~\ref{sec:basechange}; see also \cite{deligne:80a}*{Def.~1.1.10}.  If $w \ceq \Frob{\Fq}^n$ we write $w_G$ for $\Frob{G}^n$.
 For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gqcs{L}\to \gqcs{L}$ by
-\[
-\varphi(w) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi);
-\]
-these satisfy $\varphi(uv) = \varphi(v) \circ v_G^* \varphi(u)$ for $u,v\in \Weil{\Fq}$, and
+$
+\varphi(w) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi)
+$; 
+these isomorphisms satisfy $\varphi(uv) = \varphi(v) \circ v_G^* \varphi(u)$ for $u,v\in \Weil{\Fq}$, and
 we have $\phi = \varphi(\Frob{\Fq})$. 
@@
 \cite{deligne:SGA4.5}*{Expos\'e XIII,~1.1}, failing only because $\Weil{\Fq}$ is not profinite.
-Our use of $\Weil{\Fq}$ rather than $\Gal(\bFq/\Fq)$ allows quasicharacter sheaves to
+\Clifton{Improve this.}
+As we will see, our use of $\Weil{\Fq}$ rather than $\Gal(\bFq/\Fq)$ allows quasicharacter sheaves to
 correspond to unbounded characters.
@@
 \]
-after passing to isomorphism classes.  It is easy to see that $\QCiso{0}$ is trivial. In Sections~\ref{sec:connected} and \ref{sec:etale} we will find $\QCiso{G^0}$
-and $\QCiso{\pi_0(G)}$ under the hypothesis that $\pi_0(G)$ is geometrically finitely generated; 
-the snake lemma will then allow us to show that
+after passing to isomorphism classes.  It is easy to see that $\QCiso{0}$ is trivial. In Sections~\ref{sec:connected} and \ref{sec:etale} we will find the groups $\QCiso{G^0}$
+and $\QCiso{\pi_0(G)}$ for all $\QC$-schemes. 
+The snake lemma will then allow us to show that
 \[
@@
 \begin{proposition}\label{prop:product}
-If $G_1$ and $G_2$ are $\QC$-schemes, the rule $\boxtimes : (\qcs{L}_1,\qcs{L}_2)\to \qcs{L}_1\boxtimes\qcs{L}_2$ defines an equivalence of categories 
+If $G_1$ and $G_2$ are $\QC$-schemes then the rule $\boxtimes : (\qcs{L}_1,\qcs{L}_2)\to \qcs{L}_1\boxtimes\qcs{L}_2$ defines an equivalence of categories 
 \[
@@
 \]
-and 
+such that 
 \[
@@
 We have already observed that $m\circ f = \id_G$, so $f^* m^* \gqcs{L} = \gqcs{L}$.
-On the other hand, $f^*(\gqcs{L}\boxtimes \gqcs{L}) = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L}$
-by definition.  Since $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L}$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L}$
-we get that $f^*(\gqcs{L}\boxtimes \gqcs{L}) = \gqcs{L}_1\boxtimes \gqcs{L}_2$.
+On the other hand, $f^*(\gqcs{L}\boxtimes \gqcs{L}) = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L}$, 
+by definition, and $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L}$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L}$ follows from the properties of these maps, articulated above, 
+so $f^*(\gqcs{L}\boxtimes \gqcs{L}) = \gqcs{L}_1\boxtimes \gqcs{L}_2$.
 It follows that \eqref{eq:fm} gives an isomorphism $\gqcs{L} \to  \gqcs{L}_1\boxtimes \gqcs{L}_2$.
@@
 we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural
-transformation between additive functors.
+transformation between additive functors, 
+concluding the proof of Proposition~\ref{prop:functorialG}.
 \end{proof}
@@
 
-If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$, we may define
+If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$ we may define
 a quasicharacter sheaf $\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
@@
 satisfying the analogue of Condition~\ref{CS.1} on $G$; 
-morphisms in $\QCb(G)$ are defined as in the second part of Condition~\ref{CS.2}. 
+morphisms in $\QCb(G)$ are defined as in (the second part of) Condition~\ref{CS.2}. 
 This is the category of \emph{bounded quasicharacter sheaves} on $G$. 
@@
  Moreover, $\phi$ is compatible with $\mu$ in the sense of Condition~\ref{CS.3}.
- This construction defines the functor $B_G^* : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
+ This defines the functor $B_G^* : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
  and also shows that it is full and faithful.
@@
 that the image of $\chi$ is bounded in $\EEx$; 
-see Section~\ref{sec:snake} for more details.
+see Section~\ref{sec:snake} for more details regarding this point.
 
@@
  where $(\alpha',T') : (f,\psi) \to (f',T')$ is any map in $C(G)$ 
- and $(\beta_1,U_1) : (f_1,\psi_1) \to (f',\psi')$ is a weak isomorphism.
+ and $(\beta_1,U_1) : (f_1,\psi_1) \to (f',\psi')$ is a weak isomorphism in $C(G)$.
 
@@
 \begin{lemma}\label{lemma:finite-pull-back}
-If $g : J \to G$ is a morphism of group schemes, let $f_g : H\times_G J\to J$
+Let $g : J \to G$ be a morphism of group schemes. 
+Let $f_g : H\times_G J\to J$
 be the pull-back of $f$ along $g$ and define $\psi_g : \ker f_g \to \Aut(V)$ as in the diagram below:
@@
 \begin{lemma}\label{lemma:finite-iso}
-Each $(f,\psi)\in \QCf(G)$ determines a canonical isomorphism $m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$.
+Each $(f,\psi)$ in $\QCf(G)$ determines a canonical isomorphism $m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$.
  \end{lemma}
@@
 
+   \Clifton{Is this confusing? Is it clear to what $\Loc(G)$ refers?}
  Now we introduce a faithful functor $L : C(G) \to \Loc(G)$ to the category of local systems on $G$.
@@
 of $\Gal(\bFq/\Fq)$ on this (generally) infinite product of 
-Weil groups and difficult to identify the relevant quotient of this group.
+Weil groups and also difficult to identify the relevant quotient of this group.
 Viewed in this light, Definition~\ref{def:QC} is comparatively simple.
@@
 \section{Commutative \'etale group schemes} \label{sec:etale}
-
+\Clifton{Use: Etale $\QC$-schemes?}
 %\input{etale-1}
@@
  If $\qcs{L}$ is a quasicharacter sheaf on a commutative, \'etale group scheme $G$
+ \Clifton{Use: Etale $\QC$-schemes?}
  over $\Fq$ and if $G(\bFq)$ is finitely generated, then there is a global section
@@
   Let $G$ be a commutative \'etale group scheme over $\Fq$ with $G(\bFq)$ finitely generated.
+  \Clifton{Use: Etale $\QC$-schemes?}
   We may associate a $1$-cocycle $\tau_\qcs{L}: \Weil{\Fq}\to G(\bFq)^*$ to each $\qcs{L} \in \QC(G)$
@@
  under \eqref{pich1} is the class $[\tau]$ in $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
- This shows that \eqref{pich1} is surjective, 
+ This shows that \eqref{pich1} is surjective
  and completes the proof that it is an isomorphism of groups.
@@
 \begin{lemma}\label{lemma:ext}
-Every discrete isogeny  to $G^0$ extends to a discrete
-isogeny to $G$ such that the component group of the covering space is isomorphic
+Every discrete isogeny onto $G^0$ extends to a discrete
+isogeny onto $G$ such that the component group of the covering space is isomorphic
 to the component group of $G$.
@@
 \begin{remark}
+\Clifton{I'm not sure if we should include this remark in the final version.}
 If $K \ceq \mathbb{Q}_q$ and 
@@
  What remains to be done is a careful comparison of 
- quasicharacter sheaves for $\Gm{K}$ and certain local systems on
+ quasicharacter sheaves for $\Gm{K}$ and the local systems on
   the fpqc-site of the pro-quasi-algebraic varieties appearing in \cite{suzuki-yoshida:12a}.

### 2013-10-03 shanghai.tex
Edits, mostly in section 8

--- 2013-10-03 shanghai.tex
@@
  \labitem{(cs.3)}{cs.3} an indexed set $\alpha_x : \gqcs{L}_x \to \gqcs{L'}_x$
-  of linear transformations (of one-dimensional $\EE$-vector spaces),
-  as $x$ runs over $G(\bFq)$, such that
+  of linear transformations such that
   \[
@@
   \]
-  both commute.
+  both commute for all $x, y \in G(\bFq)$.
 \end{enumerate}
+
+A \emph{global section} of $\qcs{L}$ is a function $s : G(\bFq) \to \coprod_{x \in G(\bFq)} \gqcs{L}_x$ so that $s(x) \in \gqcs{L}_x$ for all $x \in G(\bFq)$ and
+\begin{equation}\label{section}
+\mu_{x,y}(s(x+y)) = s(x) \otimes s(y).
+\end{equation}
+
+We say that a section is \emph{trivial} if $s(x) = 0$ for all $x \in G(\bFq)$ and \emph{nontrivial} if $s(x) \ne 0$ for all $x \in G(\bFq)$.
 
@@
  If $\qcs{L}$ is a quasicharacter sheaf on a commutative, \'etale group scheme $G$
- over $\Fq$ and if $G(\bFq)$ is finitely generated, then there is a global section
- $s \ceq \{ s(x) \in \gqcs{L}_x \tq x \in G(\bFq) \}$ satisfying
- \begin{equation}\label{section}
- \end{equation}
+ over $\Fq$ and if $G(\bFq)$ is finitely generated, then $\qcs{L}$ has a nontrivial global section.
 \end{lemma}
@@
 
-  There is a unique isomorphism $\gqcs{L}_0 \cong \EE$ under which $\mu_{0,0}$ corresponds
+  There is a unique isomorphism $\gqcs{L}_0 \cong \EE$ under which $\mu_{0,0}^{-1}$ corresponds
   to the multiplication map $\EE \otimes\EE \to \EE$.
@@
 \begin{proof}
-  Suppose $\qcs{L}$ is a quasicharacter sheaf on $G$.  
-  Using Lemma~\ref{lemma:section}, 
-  we may choose a section $s \ceq \{ s(x) \in \gqcs{L}_x \tq x \in G(\bFq) \}$ satisfying \eqref{section}.
+  Suppose $\qcs{L}$ is a quasicharacter sheaf on $G$ and choose a global section $s$
+  of $\qcs{L}$ using Lemma~\ref{lemma:section}.
   We will construct a group isomorphism between $\QCiso{G}$ and
@@
   $\tau_\qcs{L}$, the class of $\tau_\qcs{L}$ does not depend on this
-  choice. To see why, let $s_1$ and $s_2$ be two global sections of
+  choice. To see why, let $s_1$ and $s_2$ be two nontrivial global sections of
   $\qcs{L}$ and let $\tau_1$ and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$.
-  For each $x \in G(\bFq)$ there is a unique scalar
-  $a(x) \in \EEx$ such that $s_2(x) = a(x) s_1(x)$. Then \eqref{section} and
+  For each $x \in G(\bFq)$ set $a(x) = \frac{s_2(x)}{s_1(x)}$.  Then \eqref{section} and
   condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so
@@
   image of $\qcs{L}$ and $\qcs{L'}$ under \eqref{cohomologous}; by construction,
-  $\tau$ and $\tau'$ are defined by the choice of sections $s$ and $s'$ 
-  according to Lemma~\ref{lemma:section}.
+  $\tau$ and $\tau'$ are defined by the choice of sections $s$ and $s'$.
   Now, $\varphi_x(s(x))$ is a
@@
  suppose $[\tau_\qcs{L}] = [\tau_\qcs{L'}]$.
- Let $s$ (resp. $s'$) be a section appearing in the definition of $\tau_\qcs{L}$ (resp. $\tau_\qcs{L'}$);
- recall that $s$ (resp. $s'$) is compatible with $\mu$ (resp $\mu'$) 
- in the sense of Lemma~\ref{lemma:section}.
+ Let $s$ and $s'$ be sections appearing in the definition of $\tau_\qcs{L}$ and $\tau_\qcs{L'}$.
  Since $[\tau_\qcs{L}] = [\tau_\qcs{L'}]$, 
@@
  $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}}a \cdot a^{-1})$. 
-  Define $\alpha : \qcs{L}\to \qcs{L'}$ by $\alpha_x(s(x)) \ceq a(x) s'(x)$, for each $x\in G(\bFq)$.
+ Define $\alpha : \qcs{L}\to \qcs{L'}$ by $\alpha_x(s(x)) \ceq a(x) s'(x)$ and $\alpha^{-1} : \qcs{L}'\to \qcs{L}$
+ by $\alpha^{-1}_x(s'(x)) \ceq a(x)^{-1} s(x)$, for $x\in G(\bFq)$.
  It is straightforward to check that $\alpha$ satisfies condition~\ref{cs.3}
-  and that $\alpha^{-1} : \qcs{L'}\to \qcs{L}$, defined by $\alpha^{-1}_x(s'(x)) \ceq a(x)^{-1} s(x)$, 
-  is its inverse. Thus, $\qcs{L} \iso \qcs{L'}$ in $\QC(G)$. 
-  This shows that \eqref{pich1} is injective.
+ and that $\alpha^{-1}$ is its inverse. Thus $\qcs{L} \iso \qcs{L'}$ in $\QC(G)$ and \eqref{pich1} is injective.
 
@@
  clearly, $\mu$ satisfies condition~\ref{cs.1}.
- Define $\phi_x : \gqcs{L}_{\Frob{\Fq}} \to \gqcs{L}_x$ by $\phi_x(1) \ceq \tau(\Frob{\Fq})(x)$,
+ Define $\phi_x : \gqcs{L}_{\Frob{\Fq}(x)} \to \gqcs{L}_x$ by $\phi_x(1) \ceq \tau(\Frob{\Fq})(x)$,
  for each $x\in G(\bFq)$. 
  Then $\phi$ satisfies condition~\ref{cs.2} because $\tau \in Z^1(\Weil{\Fq},G(\bFq)^*)$.
- In this way we have built a quasicharacter sheaf $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ 
- from $\tau \in \Hh^1(\Weil{\Fq}, G(\bFq)^*)$ such that the image of $\qcs{L}_{/\text{iso}}$
- under \eqref{pich1} is the class $[\tau]$ in $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
- This shows that \eqref{pich1} is surjective, 
- and completes the proof that it is an isomorphism of groups.
+ Setting $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$, we have that $[\tau]$ is the image of $\qcs{L}$
+ under \eqref{pich1}, and thus \eqref{pich1} defines an isomorphism of groups.
 \end{proof}
@@
 if it is a finite, surjective \'etale morphism and 
-the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $f^{-1}({\bar e})$ is trivial.
+the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f$ is trivial.
 

### 2013-10-03 shanghai.tex

@@
 \begin{lemma}\label{lemma:finite-iso}
-Each $(f,\psi)\in \QCf(G)$ determines a canonical isomorphism $m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$. \David{I'm confused at first reading by the statement of this lemma}
+Each $(f,\psi)$ in $\QCf(G)$ determines a canonical isomorphism $m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$. \David{I'm confused at first reading by the statement of this lemma}
  \end{lemma}
@@
  If $\qcs{L}$ is a quasicharacter sheaf on a commutative, \'etale group scheme $G$
+ \Clifton{Use: Etale $\QC$-schemes?}
  over $\Fq$ and if $G(\bFq)$ is finitely generated, then $\qcs{L}$ has a nontrivial global section.

### 2013-10-03 shanghai.tex
Edits, to section 8

@@
 Every discrete isogeny onto $G^0$ extends to a discrete
-isogeny onto $G$ such that the component group of the covering space is isomorphic
-to the component group of $G$.
+isogeny onto $G$ inducing an isomorphism on component groups.
 \end{lemma}
@@
   $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism of component
-  groups.
+  groups.  Namely, we will fit $\pi$ into the following diagram,
   \begin{equation}\label{extension-diagram}
@@
   B \rar \dar[swap]{\pi} & H \rar \dar[swap]{f} & \pi_0(H) \arrow{d}[below,rotate=90]{\sim}[swap]{\pi_0(f)} \\
-  G^0 \rar & G \rar & \pi_0(G)
+  G^0 \rar & G \rar & \pi_0(G),
   \end{tikzcd}
@@
   Set $\Gamma \ceq \Gal(\bFq/\Fq)$. Extensions of
-  $G^0(\bFq)$ by $A(\bFq)$, such as $A(\bFq) \to H^0(\bFq) \to G^0(\bFq)$,
+  $G^0(\bFq)$ by $A(\bFq)$, such as $A(\bFq) \to B(\bFq) \to G^0(\bFq)$,
   correspond to classes in $\Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))$.

### 2013-10-03 shanghai.tex
Added a few more flags for our meeting this morning.

@@
 \begin{proof}
-  Since $G$ is a smooth group scheme locally of finite type over $\Fq$, its
+\Clifton{Turn this paragraph into a lemma. We use it below.}  Since $G$ is a smooth group scheme locally of finite type over $\Fq$, its
   identity component $G^0$ of $G$ is a connected smooth, 
@@
 	it follows that $G^0$ is a connected algebraic group.
+
     By Proposition~\ref{prop:connected}, every
@@
 
+  \Clifton{Refer to the new lemma, here.}
   In the proof of Proposition~\ref{prop:restriction} we saw that $G^0$ is an algebraic group over $\Fq$. % clearly connected. 
@@
   is exact at $G(\Fq)^*$ and $\coker \trFrob{\pi_0(G)} =0$
-  (by Proposition~\ref{prop:etale-iso}) and
+  (by Proposition~\ref{prop:etale-iso}) and   \Clifton{Awkward sentence.}
   \[
@@
   $\trFrob{\qcs{L}}$. By Proposition~\ref{prop:etale-iso},
-  there is a a quasicharacter sheaf $\qcs{L}_\chi$ on $\pi_0(G)$, unique up
+  there is a quasicharacter sheaf $\qcs{L}_\chi$ on $\pi_0(G)$, unique up
   to isomorphism, such that $\trFrob{\qcs{L}_\chi} = \chi$. By

### 2013-10-03 shanghai.tex
Fixes, edits and restructuring of section 9

@@
 \begin{proof}
-Let $\pi: B \to G^0$ be a discrete isogeny; set $A \ceq \ker \pi$.
+Let $\pi: B \to G^0$ be a discrete isogeny and set $A \ceq \ker \pi$.
   We will find a discrete isogeny $f: H\to G$
@@
   \]
-
-  We now show that $\Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)) = 0$.
-%
-  It suffices to show that $\pi_0(G)(\bFq)$ has a two-term resolution
-  by injective $\ZZ[\Gamma]$-modules.  Since the action of $\Gamma$ on
-  $\pi_0(G)(\bFq)$ is continuous, it factors through some finite quotient
-  $\Gamma_m \ceq \Gamma / H_m$.  Any product of Dedekind domains has
-  cohomological dimension $1$, \David{Add a citation for this fact} so $\pi_0(G)(\bFq)$ has a
-  two term resolution by injective $\ZZ[\Gamma_m]$-modules.  Let $I$
-  be one of these modules: we need to show that $I$ is injective as a
-  $\ZZ[\Gamma]$-module.  Consider the universal diagram for injectivity:
-
-  \[
-  \begin{tikzcd}
-  A \rar{a} \arrow[hook]{d} & I \\
-  B
-  \end{tikzcd}
-  \]
-  where $A$ and $B$ are arbitrary $\ZZ[\Gamma]$-modules.  Since $H_m$ acts trivially on $I$,
-  $I_{H_m}A \ceq \langle (\gamma-1)a : \gamma \in H_m, a \in A \rangle \subseteq \ker(a).$
-  Since $B / I_{H_m}B \cong B \otimes_A A / I_{H_m}A$, we get
-  \[
-  \begin{tikzcd}
-  A \arrow[two heads]{r} \arrow[hook]{d} & A/I_{H_m}A \rar \arrow[hook]{d} & I \\
-  B \arrow[two heads]{r} & B/I_{H_m}B \arrow[dashed]{ur} & {}
-  \end{tikzcd}
-  \]
-  The dotted arrow exists since $I$ is injective as a
-  $\ZZ[\Gamma_m]$-module and the outer diagram shows that $I$ is
-  injective as a $\ZZ[\Gamma]$-module.
+  Since finite fields have cohomological dimension $1$ \cite{serre:GaloisCohomology}*{\S II.3.3},
+  $\Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq))$ vanishes \cite{cartan-eilenberg:HomologicalAlgebra}*{Thm. 2.6}.
 
@@
 
+In order to use the results of Section~\ref{sec:connected}, we need to know that
+identity component of $G$ is actually an algebraic group.
+
+\begin{lemma} \label{lem:G0alg-grp}
+If $G$ is a $\QC$-scheme then $G^0$ is a connected algebraic group.
+\end{lemma}
+\begin{proof}
+ Since $G$ is a smooth group scheme locally of finite type over $\Fq$, its
+ identity component $G^0$ of $G$ is a connected smooth, 
+ group scheme of finite type over $\Fq$, reduced over some finite extension of $\Fq$
+ \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}. 
+ Since $\Fq$ is a finite field and hence perfect, $G^0$ is actually reduced over $\Fq$
+ \cite{EGAIV2}*{Prop 6.4.1}.  Since every group scheme over a field is separated 
+ \cite{vdGeer-Moonen:AbelianVarieties}*{3.12},
+ it follows that $G^0$ is a connected algebraic group.
+\end{proof}
+
 \begin{proposition}\label{prop:restriction}
@@
 \begin{proof}
-\Clifton{Turn this paragraph into a lemma. We use it below.}  Since $G$ is a smooth group scheme locally of finite type over $\Fq$, its
-  identity component $G^0$ of $G$ is a connected smooth, 
-  group scheme of finite type over $\Fq$, reduced over some finite extension of $\Fq$, by
-   \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}. 
-	Since $\Fq$ is a finite field and hence perfect, $G^0$ is actually reduced over $\Fq$;
-	see \cite{EGAIV2}*{Prop 6.4.1}.
-	Since every group scheme over a field is separated 
-	(see, for example, \cite{vdGeer-Moonen:AbelianVarieties}*{3.12}),  
-	it follows that $G^0$ is a connected algebraic group.
-
-    By Proposition~\ref{prop:connected}, every
+  By Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}, every
   quasicharacter sheaf on $G^0$ is isomorphic to a 
@@
  By Lemma~\ref{lemma:ext}, there is an extension of the 
- discrete isogeny $\pi : B \to G^0$ 
- (see Section~\ref{sec:finite} for the definition of a discrete isogeny) 
- to a discrete isogeny $f : H \to G^0$ 
+ discrete isogeny $\pi : B \to G^0$ to a discrete isogeny $f : H \to G^0$ 
  such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
- Then $(f,\psi)$ is a finite quasicharacter sheaf on $G$.
- Then $(f,\psi)\vert_{G^0} \iso (\pi,\psi)$,
- completing the proof that $\QC(G)\to \QC(G^0)$ is essentially surjective.
+ Then $(f,\psi)$ is a finite quasicharacter sheaf on $G$ and 
+ $(f,\psi)\vert_{G^0} \iso (\pi,\psi)$.
 \end{proof}

### 2013-10-03 shanghai.tex
merge before moving downstairs
Small fix to section 9, added reference

@@
 
-  Set $\Gamma \ceq \Gal(\bFq/\Fq)$. Extensions of
+  Write $W$ for the Weil group $\Weil{\Fq}$.  Extensions of
   $G^0(\bFq)$ by $A(\bFq)$, such as $A(\bFq) \to B(\bFq) \to G^0(\bFq)$,
-  correspond to classes in $\Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))$.
+  correspond to classes in $\Ext^1_{\ZZ[W]}(G^0(\bFq), A(\bFq))$.
   Similarly, extensions of $G(\bFq)$ by $A(\bFq)$ correspond to
-  classes in $\Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq))$.  The map
+  classes in $\Ext^1_{\ZZ[W]}(G(\bFq), A(\bFq))$.  The map
   $G^0(\bFq) \to G(\bFq)$ induces the map
   \[
-  \Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq))
+  \Ext^1_{\ZZ[W]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[W]}(G^0(\bFq), A(\bFq))
   \]
@@
   \[
-  \Ext^1_{\ZZ[\Gamma]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Gamma]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq)).
-  \]
-  Since finite fields have cohomological dimension $1$ \cite{serre:GaloisCohomology}*{\S II.3.3},
-  $\Ext^2_{\ZZ[\Gamma]}(\pi_0(G)(\bFq), A(\bFq))$ vanishes \cite{cartan-eilenberg:HomologicalAlgebra}*{Thm. 2.6}.
+  \Ext^1_{\ZZ[W]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[W]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[W]}(\pi_0(G)(\bFq), A(\bFq)).
+  \]
+  Since $W$ has cohomological dimension $1$ \cite{brown:CohomologyGrps}*{Ex. 4.3},
+  $\Ext^2_{\ZZ[W]}(\pi_0(G)(\bFq), A(\bFq))$ vanishes \cite{cartan-eilenberg:HomologicalAlgebra}*{Thm. 2.6}.
 
@@
   descends to a diagram of $\Fq$-schemes since the $\bFq$-points of
-  the objects come equipped with continuous $\Gamma$-actions, and the
+  the objects come equipped with continuous $W$-actions, and the
   morphisms are $\Gamma$-equivariant.

### 2013-10-03 shanghai.tex
Working on the introduction. Added reference to Waldspurger.

@@
 some of the potential benefits of Theorem~\ref{thm:application} here. 
-
+%
 Characters on $T$ have limited
@@
 
-DeBacker and Reeder have recently applied Deligne-Lusztig representations to part of the
-local Langlands correspondence. % \cite{reeder-debacker:09a}.  
+DeBacker and Reeder have recently applied Deligne-Lusztig representations to part of the depth-zero part of the
+local Langlands correspondence \cite{reeder-debacker:09a}.
+Deligne-Lusztig theory also plays an important role in Waldspurger's work on nilpotent distributions \cite{waldspurger:01}.
 After developing Deligne-Lusztig representations, 
@@
 representations of $p$-adic groups.
+Note that our geometrization of quasicharacters is not limited
+to the depth-zero case.
 
@@
 correspond to unbounded characters.
-%\end{remark}
 

### 2013-10-03 shanghai.tex
Added a reference for localization; working on section 6.

@@
 We hope to use this to our advantage as we work toward an adaptation of Lusztig's theory of characters sheaves to the study of characters of admissible representations of reductive $p$-adic groups that extends beyond the case of $p$-adic tori.
-\Clifton{Combine these two paragraphs? It seems they make the same point. Waldspurger also uses D-L to study depth-zero distributions. Mention this, too? Mention neither?}
 
@@
 can provide a stepping stone to a similar theory for
-representations of $p$-adic groups.
-Note that our geometrization of quasicharacters is not limited
-to the depth-zero case.
+representations of $p$-adic groups, especially
+in the positive-depth case.
 
@@
 after passing to isomorphism classes.  It is easy to see that $\QCiso{0}$ is trivial. In Sections~\ref{sec:connected} and \ref{sec:etale} we will find the groups $\QCiso{G^0}$
-and $\QCiso{\pi_0(G)}$ for all $\QC$-schemes. 
-The snake lemma will then allow us to show that
-\[
-\QCiso{G} \iso G(\Fq)^*.
-\]
+and $\QCiso{\pi_0(G)}$ for all $\QC$-schemes, 
+which will allow us to conclude $\QCiso{G} \iso G(\Fq)^*$.
 
@@
 %Now consider the localization $C(G)[W^{-1}]$ of $C(G)$ at weak isomorphisms.
- Morphisms in $C(G)[W^{-1}]$ are simple to describe because category $C(G)$ 
- admits a calculus of left fractions \David{Should add a reference for calculus of fractions that isn't nlab}
- %\footnote{See {\tt http://ncatlab.org/nlab/show/calculus+of+fractions}.} 
- for weak isomorphisms:
-% every isomorphism in $C(G)$ is a weak isomorphism; 
-% push-outs exist in $C(G)$ and the push-out of a weak isomorphism is a weak isomorphism; 
-% and weak isomorphisms enjoy the left-cancellation property. 
-% It follows that
- a morphism in $C(G)[W^{-1}]$ is the equivalence class of 
+ Morphisms in $C(G)[W^{-1}]$ are simple to describe because 
+ $W$ is a left-multiplicative system in the sense of
+  \cite{kashiwara-schapira:CatgoriesSheaves}*{\S 7.1.7};
+namely, a morphism in $C(G)[W^{-1}]$ is the equivalence class of 
   \begin{equation}\label{eq:morGCf}

### 2013-10-03 shanghai.tex
Added Cor 10.2, inserted stub into the proof of 10.1 for exactness in the top center

--- 2013-10-03 shanghai.tex
@@
 DeBacker and Reeder have recently applied Deligne-Lusztig representations to part of the
-local Langlands correspondence. % \cite{reeder-debacker:09a}.  
+local Langlands correspondence.  \cite{reeder-debacker:09a}.  
 After developing Deligne-Lusztig representations, 
@@
 Extension of scalars defines a full and faithful functor 
-$B_G^* : \QCb(G) \hookrightarrow \QC(G)$,
-thus identifying $\QCb(G)$ with a full subcategory of $\QC(G)$.
+$B_G^* : \QCb(G) \hookrightarrow \QC(G)$.
 \end{proposition}
@@
 In general, $\QCb(G)$ is an essentially
-proper subcategory of $\QC(G)$. Indeed, it will follow from Theorem~\ref{thm:snake}
-that the restriction of $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ to the subgroup
-$\QCbiso{G}$ is an isomorphism onto the subgroup of $\chi \in G(\Fq)^*$ such
-that the image of $\chi$ is bounded in $\EEx$; 
-see Section~\ref{sec:snake} for more details.
+proper subcategory of $\QC(G)$. We will identify $\QCb(G)$ with its image under $B_G^*$
+and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ is \emph{bounded}
+if it is isomorphic to some $B_G^*(\qcs{L}_0, \mu_0)$.
+We will see in Corollary~\ref{cor:bounded-and-finite} that the bounded quasicharacter sheaves
+are precisely those whose trace of Frobenius have bounded image.
 
@@
 
-For general $G$, there are bounded quasicharacter sheaves which are not finite.  Indeed,
-it will follow from Theorem~\ref{thm:snake} that the restriction of
-$\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ to the subgroup $\QCfiso{G}$ is an isomorphism
-onto the subgroup of $\chi \in G(\Fq)^*$ such that the image of $\chi$ is finite in $\EEx$;
-see Section~\ref{sec:snake}.
+For general $G$, there are bounded quasicharacter sheaves which are not finite.  Identifying
+$\QCf(G)$ with its image under $B_G^* \circ L_G$, we will see in Corollary~\ref{cor:bounded-and-finite} that
+a quasicharacter sheaf is finite if and only if its trace of Frobenius has finite image.
 
@@
 
-  Write $W$ for the Weil group $\Weil{\Fq}$.  Extensions of
-  $G^0(\bFq)$ by $A(\bFq)$, such as $A(\bFq) \to B(\bFq) \to G^0(\bFq)$,
-  correspond to classes in $\Ext^1_{\ZZ[W]}(G^0(\bFq), A(\bFq))$.
+  Extensions of $G^0(\bFq)$ by $A(\bFq)$, such as $A(\bFq) \to B(\bFq) \to G^0(\bFq)$,
+  correspond to classes in $\Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq))$.
   Similarly, extensions of $G(\bFq)$ by $A(\bFq)$ correspond to
-  classes in $\Ext^1_{\ZZ[W]}(G(\bFq), A(\bFq))$.  The map
+  classes in $\Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq))$.  The map
   $G^0(\bFq) \to G(\bFq)$ induces the map
   \[
-  \Ext^1_{\ZZ[W]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[W]}(G^0(\bFq), A(\bFq))
+  \Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq))
   \]
@@
   \[
-  \Ext^1_{\ZZ[W]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[W]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[W]}(\pi_0(G)(\bFq), A(\bFq)).
-  \]
-  Since $W$ has cohomological dimension $1$ \cite{brown:CohomologyGrps}*{Ex. 4.3},
-  $\Ext^2_{\ZZ[W]}(\pi_0(G)(\bFq), A(\bFq))$ vanishes \cite{cartan-eilenberg:HomologicalAlgebra}*{Thm. 2.6}.
+  \Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[\Weil{}]}(\pi_0(G)(\bFq), A(\bFq)).
+  \]
+  Since $\Weil{} \cong \ZZ$ has cohomological dimension $1$ \cite{brown:CohomologyGrps}*{Ex. 4.3},
+  $\Ext^2_{\ZZ[\Weil{}]}(\pi_0(G)(\bFq), A(\bFq))$ vanishes \cite{cartan-eilenberg:HomologicalAlgebra}*{Thm. 2.6}.
 
@@
   descends to a diagram of $\Fq$-schemes since the $\bFq$-points of
-  the objects come equipped with continuous $W$-actions, and the
+  the objects come equipped with continuous $\Weil{}$-actions, and the
   morphisms are $\Gamma$-equivariant.
@@
 $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
-Our main result regarding quasicharacter sheaves, below, shows that
-trace of Frobenius is an isomorphism for $\QC$-schemes.
+In fact, trace of Frobenius is an isomorphism when $G$ is a $\QC$-scheme.
 
@@
 \begin{theorem}\label{thm:snake}
-  If $G$ is a smooth commutative group scheme locally of finite type over
-  $\Fq$ and if the abelian group $\pi_0(G)(\bFq)$
-  is finitely generated then the trace of Frobenius
+  If $G$ is a smooth, commutative group scheme, locally of finite type over
+  $\Fq$, and if the abelian group $\pi_0(G)(\bFq)$
+  is finitely generated, then the trace of Frobenius
   \[
@@
 
-  \Clifton{Refer to the new lemma, here.}
-  In the proof of Proposition~\ref{prop:restriction} we saw that $G^0$ is an algebraic group over $\Fq$. % clearly connected. 
-  It now follows from Proposition~\ref{prop:connected} 
-  that $\ker \trFrob{G^0} =0$ and $\coker \trFrob{G^0}=0$. 
-  On the other hand, it follows from Propositions~\ref{prop:etale-iso} that $\ker \trFrob{\pi_0(G)}=0$
-  and $\coker \trFrob{\pi_0(G)}=0$.
-
-  The sequence of character groups is left-exact: by
-  Proposition~\ref{prop:pullback}, it is dual to the exact sequence of
+  The bottom row is dual to the sequence of
   abelian groups
@@
   \begin{tikzcd}
-    1 \rar & G^0(\Fq) \rar & G(\Fq) \rar & \pi_0(G)(\Fq) \rar & 0;
+    1 \rar & G^0(\Fq) \rar & G(\Fq) \rar & \pi_0(G)(\Fq) \rar & 0,
   \end{tikzcd}
   \end{equation}
-  since $\Hom(\ - \ ,\EEx)$ is left-exact, the sequence of
-  character groups is left exact.
-
-  The sequence of groups of isomorphism classes of quasicharacter sheaves is right-exact:   it is exact at
-  $\QCiso{G^0}$ by Proposition~\ref{prop:restriction}; and
-  it is exact at $\QCiso{G}$ because the left-square
-  commutes (by Proposition~\ref{prop:pullback}), the bottom sequence
-  is exact at $G(\Fq)^*$ and $\coker \trFrob{\pi_0(G)} =0$
-  (by Proposition~\ref{prop:etale-iso}) and   \Clifton{Awkward sentence.}
-  \[
-  \image(\QCiso{\pi_0(G)} \to \QCiso{G}) \subseteq \ker(\QCiso{G} \to \QCiso{G^0}),
-  \]
-  by the last part of Proposition~\ref{prop:pullback}. Specifically,
-  suppose $\qcs{L}$ is a quasicharacter sheaf on $G$ that is trivial on
-  $G^0$. Then $\trFrob{\qcs{L}}\vert_{G^0(\Fq)} = \trFrob{\qcs{L}^0} =0$,
-  by Proposition~\ref{prop:pullback} again. Since the sequence of
-  character groups is exact at $G(\Fq)^*$, there is
-  some $\chi \in \pi_0(G)(\Fq)^*$ such that the
-  pull-back of $\chi$ along $G(\Fq)\to \pi_0(G)(\Fq)$ is
-  $\trFrob{\qcs{L}}$. By Proposition~\ref{prop:etale-iso},
-  there is a quasicharacter sheaf $\qcs{L}_\chi$ on $\pi_0(G)$, unique up
-  to isomorphism, such that $\trFrob{\qcs{L}_\chi} = \chi$. By
-  Proposition~\ref{prop:pullback} again, $\qcs{L}$ is isomorphic to the
-  image of $\qcs{L}_\chi$ under the monoidal functor $\QC(\pi_0(G)) \to \QC(G)$.
-
-  It now follows immediately from the snake lemma that $\trFrob{G}$ is an
-  isomorphism of groups.
+  which is exact by Lang's theorem on connected algebraic groups over finite fields \cite{lang:56a}.
+  Since $\EEx$ is divisible, $\Hom(\ - \ ,\EEx)$ is exact and thus the dual sequence of
+  character groups is also exact.
+
+  In order to apply the snake lemma, we need to show that the top row is exact at $\QCiso{G}$ and $\QCiso{G^0}$.
+  The surjectivity of $\QCiso{G} \to \QCiso{G^0}$ follows from Proposition~\ref{prop:restriction}.  Now suppose that
+  $\qcs{L}$ is a quasicharacter sheaf on $G$ whose restriction to $G^0$ is trivial.... \David{Missing argument, discussed this afternoon}
+
+  Now Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}
+  imply that $\ker \trFrob{G^0} =0$ and $\coker \trFrob{G^0}=0$. 
+  Similarly, Proposition~\ref{prop:etale-iso} shows that $\ker \trFrob{\pi_0(G)}=0$
+  and $\coker \trFrob{\pi_0(G)}=0$.
+  We may thus apply the snake lemma and conclude that
+  $\ker \trFrob{G}$ and $\coker \trFrob{G}$ both vanish.
 \end{proof}
@@
 nor finite quasicharacter sheaves are up to the task of 
-geometrizing characters of $G(\Fq)$ in the generality we need.  
-%
+geometrizing all characters of $G(\Fq)$ for general $\QC$-schemes $G$.
+
+\begin{corollary} \label{cor:bounded-and-finite}
+Suppose $G$ is a $\QC$-scheme and $\qcs{L}$ is a quasicharacter sheaf on $G$.  Then
+\begin{enumerate}
+\item $\qcs{L}$ is bounded if and only if $\trFrob{L}$ has bounded image,
+\item $\qcs{L}$ is finite if and only if $\trFrob{L}$ has finite image.
+\end{enumerate}
+\end{corollary}
+\begin{proof}
+\David{These examples need to be modified to provide a proof of the corollary}
 Consider the case when $G$ is the discrete \'etale group scheme $\ZZ$; 
@@
 defined at $1$ by a pro-\'etale cover of $1$, but not finite, since $1+\ell$ is not a root of unity. 
-%
-These simple examples illustrate why the categories $\QCb(G)$ and $\QCf(G)$ are inadequate to geometrize characters of $G(\Fq)$.
+\end{proof}
 

### 2013-10-03 shanghai.tex

@@
 We hope to use this to our advantage as we work toward an adaptation of Lusztig's theory of characters sheaves to the study of characters of admissible representations of reductive $p$-adic groups that extends beyond the case of $p$-adic tori.
-\Clifton{Combine these two paragraphs? It seems they make the same point. Waldspurger also uses D-L to study depth-zero distributions. Mention this, too? Mention neither?}
-
-DeBacker and Reeder have recently applied Deligne-Lusztig representations to part of the
-local Langlands correspondence.  \cite{reeder-debacker:09a}.  
+
+DeBacker and Reeder have recently applied Deligne-Lusztig representations to part of the depth-zero part of the
+local Langlands correspondence \cite{reeder-debacker:09a}.
+Deligne-Lusztig theory also plays an important role in Waldspurger's work on nilpotent distributions \cite{waldspurger:01}.
 After developing Deligne-Lusztig representations, 
@@
 can provide a stepping stone to a similar theory for
-representations of $p$-adic groups.
+representations of $p$-adic groups, especially
+in the positive-depth case.
 

### 2013-10-04 shanghai.tex
Another corollary of Thm 10.1
Edits to Part 2

@@
 \newcommand{\pK}{\mathfrak{p}_K}
+\newcommand{\OKp}{\mathcal{O}_{K'}}
+\newcommand{\pKp}{\mathfrak{p}_{K'}}
 \newcommand{\OL}{\mathcal{O}_L}
@@
 %\newcommand{\bFp}{{\mathbb{\bar F}_p}}
+\newcommand{\WW}{\mathbb{W}}
 
@@
 \newcommand{\TL}{\underline{T_L}}
+\newcommand{\TTp}{\underline{T}'}
 \newcommand{\invlim}[1]{\lim\limits_{\overleftarrow{#1}}}
@@
 
+\begin{corollary}
+Suppose that
+\[
+0 \to A \to B \to C \to 0
+\]
+is an exact sequence of $\QC$-schemes and that $\Hh^1(\Fq, A) = 0$.  Then pullback yields an exact sequence
+\[
+0 \to \QCiso{C} \to \QCiso{B} \to \QCiso{A} \to 0
+\]
+of abelian groups.
+\end{corollary}
+
 With Theorem~\ref{thm:snake} in hand, 
@@
 We write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$. 
-Let $T$ be an algebraic torus over $K$.
+Let $T$ be an algebraic torus over $K$; the filtrations defined by Moy-Prasad and Yu \cite{yu:03a}*{\S 5}
+allow us to define the depth of character $\chi$ as the infimum of the $r$ so that $\chi$ vanishes on $T(K)_r$.
 We write $\Hom_{< n}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $n$ 
@@
 
-A N\'eron model for $T$, denoted here by $\TT$ 
-and whose existence is given by \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch 10.1, Thm 6},
-is a separated, smooth, commutative group scheme locally of finite type over $\OK$ with generic fibre $T$,
-that enjoys the N\'eron mapping property:
-if $S$ is a smooth scheme over $\OK$ then every morphism $S_\eta \to T$
-over $K$ extends uniquely to a morphism $S \to \TT$. 
-Equivalently, the
-N\'eron mapping property states that the function
-$\Hom_{\OK} (S,\TT) \to \Hom_K(S_\eta,T)$, given by restriction to
-generic fibres, is a bijection; 
-in particular, taking $S \ceq \Spec{\OK}$, this implies $\TT(\OK) = T(K)$.
-
-We will also need the Greenberg functor, 
-introduced in \cite{greenberg:61} and \cite{greenberg:63a}, 
-as a functor from the category of schemes locally of finite type 
+A N\'eron model for $T$ is a smooth group scheme $\TT$ over $\OK$ with generic fiber $T$
+that satisfies the N\'eron mapping property: if $S$ is any smooth scheme over $\OK$ then every morphism
+$S_\eta \to T$ over $K$ extends uniquely to a morphism $S \to \TT$.  N\'eron models exist for any torus
+$T$ \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch 10.1, Thm 6} and are unique up to isomorphism;
+$\TT$ is separated, commutative, locally finite type over $\OK$ and satisfies $\TT(\OK) = T(K)$.
+
+We will also need the Greenberg functor \citelist{\cite{greenberg:61} \cite{greenberg:63a}}:
+a functor from the category of schemes locally of finite type 
 over an Artinian local ring with perfect residue field $k$ 
@@
 etale morphisms, smooth morphisms and geometric components.
-Besides Greenberg's original papers, see
-\citelist{\cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1} \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6}}
-and the first few sections of \cite{stasinski:12a} 
-for background on the Greenberg functor.
+See
+\citelist{\cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1} \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} \cite{stasinski:12a}*{\S 2}}
+for more background on the Greenberg functor.
 
@@
 \begin{align*}
- \GN{T}_n &\ceq \Gr_n(\TT) \\
+ \GN{T}_n &\ceq \Gr_n(\TT), \\
  f_n &\ceq P_n(\TT).
@@
 
-Some fundamental properties of $f_n : \GN{T}_{n+1} \to \GN{T}_n$ are:
+We list some fundamental properties of $f_n$ and $\GN{T}_n$ for further use:
  \begin{enumerate}
-   \labitem{(GN.0)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
+  \labitem{(GN.0)}{truncation}
+  $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes over $\Fq$
+  \citelist{\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276} \cite{stasinski:12a}*{\S 4}}.
+  We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.
   \labitem{(GN.1)}{smooth} 
@@
   The Greenberg functor takes the geometric identity component of $\TT_n$ 
-  to the geometric identity component of $\GN{T}_n$;
-  in fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$ and
-  this group is finitely generated by \cite{xarles:93a}*{2.18}.
-  \labitem{(GN.2)}{truncation}
-  The morphism $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes over $\Fq$; 
-  see  \cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}
-  and  \cite{stasinski:12a}*{\S 4}.
-  We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.
+  to the geometric identity component of $\GN{T}_n$.
+  In fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$ and
+  this group is finitely generated \cite{xarles:93a}*{2.18}.
+  \labitem{(GN.2)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
 \end{enumerate}
@@
 \section{Application to quasicharacters of bounded depth} \label{sec:bdchar}
+
+We now apply the results of Part~\ref{part1} to characters of $T(K)$.
 
@@
 is an isomomorphism. 
-Moreover, the isomorphism $\trFrob{T,n}$ is functorial in the following sense:
-$T \mapsto \trFrob{T,n}$ is a natural transformation between the following two additive functors
+Moreover, the isomorphism $\trFrob{T,n}$ is a natural transformation
+between the additive functors
 \begin{enumerate}
@@
 The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
-while the second part shows that Trace of Frobenius is a natural transformation
+while the second part shows that trace of Frobenius is a natural transformation
 $t_{ - ,n} : F_1 \to F_2$. When further combined with Lemma~\ref{prop:product},
@@
 \section{A sheaf--function dictionary for tori over local fields} \label{sec:quasichar}
+
+In this section we package the isomorphisms of Theorem~\ref{thm:application} into
+a single dictionary.
 
@@
 
-\begin{remark}
-\Clifton{I'm not sure if we should include this remark in the final version.}
-If $K \ceq \mathbb{Q}_q$ and 
-$T \ceq \Gm{\mathbb{Q}_q}$ then $\GN{T}^0 = \mathbb{W}^*_{\FF_q}$, 
-the group scheme (!) over $\Fq$ of units in the ring scheme $\mathbb{W}_{\FF_q}$
-and $\GN{T}$, as a scheme, is the disjoint union of copies of $\mathbb{W}^*_{\FF_q}$
-indexed by the integers. Based on this example, 
-we ask if, for arbitrary $T$, the pro-group scheme $\GN{T}$ is, in fact, a group scheme.
-We have not explored that question.
-\end{remark}
-
 For any  ordered pair of positive integers $n< m$ define 
@@
 An object in $\QC(\GN{T})$ is an equivalence class in 
-$\cup_{n\in\ZZ_{>0}} \obj \QC(\GN{T}_n)$ under the relation: 
-$\qcs{L}_n\in \QC(\GN{T}_n)$ is equivalent to $\qcs{L}_{m}\in \QC(\GN{T}_m)$ 
-if $f_{n\leq k}^* \qcs{L}_{n} = f_{m\leq k}^* \qcs{L}_m$ for some $n,m\leq k$. 
+$\cup_{n\in\ZZ_{>0}} \obj \QC(\GN{T}_n)$.
+We say that $\qcs{L}_n\in \QC(\GN{T}_n)$ is equivalent to $\qcs{L}_{m}\in \QC(\GN{T}_m)$ 
+if there is some $k \ge m,n$ with $f_{n\leq k}^* \qcs{L}_{n} = f_{m\leq k}^* \qcs{L}_m$. \David{is it okay for this to be equality rather than isomorphism?} 
 Objects in $\QC(\GN{T})$ all take the form
@@
 for some unique $\qcs{L}_n \in \QC(\GN{T}_n)$.
-Maps $[\qcs{L}_n] \to [\qcs{L}_m]$ in $\QC(\GN{T})$ are defined as follows:
-$\Hom([\qcs{L}_n],[\qcs{L}_m])$ is the set of equivalence classes 
-in $\cup_{n,m\leq k} \Hom(f_{n\leq k}^*\qcs{L}_n,f_{m\leq k}^*\qcs{L}_m)$ 
-under the relation: $\alpha_k\in \mor \QC(\GN{T}_k)$ is equivalent to 
-$\beta_l \in \QC(\GN{T}_l)$ if $f_{k\leq i}^*\alpha_k = f_{l\leq i}^* \beta_l$ for some $k,l\leq i$. 
-Maps in $\QC(\GN{T})$ all take the form
+A morphism $[\qcs{L}_n] \to [\qcs{L}_m]$ in $\QC(\GN{T})$ is an equivalence class
+in $\cup_{n,m\leq k} \Hom(f_{n\leq k}^*\qcs{L}_n,f_{m\leq k}^*\qcs{L}_m)$.
+We say that $\alpha_k\in \mor \QC(\GN{T}_k)$ is equivalent to 
+$\beta_l \in \mor \QC(\GN{T}_l)$ if there is some $i \ge k, l$ with $f_{k\leq i}^*\alpha_k = f_{l\leq i}^* \beta_l$. 
+Morphisms in $\QC(\GN{T})$ all take the form
 \[
@@
 Identities and composition are defined in the natural way.
-Category $\QC(\GN{T})$ carries a tensor structure under
+We may define a tensor structure for $\QC(\GN{T})$ by setting
 \[
@@
 is an isomomorphism. 
-Moreover, the isomorphism $\trFrob{T}$ is functorial in the following sense: 
-$T \mapsto \trFrob{T}$ is a natural transformation 
-between the following two additive functors
+Moreover, the isomorphism $\trFrob{T}$ is a natural transformation 
+between the additive functors
 \begin{enumerate}
@@
 \begin{proof}
-Observe that $\QC(\GN{T})$ comes equipped with monoidal subcategories
+We may define full and faithful functors $F_n : \QC(\GN{T}_n) \to \QC(\GN{T})$ for each $n$ by $F_n(\qcs{L}) \ceq [\qcs{L}_n]$ and $F_n(\alpha_n) \ceq [\alpha_n]$.
+For positive integers $n \le m$ these functors fit together into a diagram
 \[
@@
 \ & & & \QC(\GN{T})\\
-\arrow{urrr}{F_n} \QC(\GN{T}_n) \arrow[swap]{rr}{f_{n\leq m}^*} && \QC(\GN{T}_m) \arrow[swap]{ur}{F_m} & 
-\end{tikzcd}
-\]
-defined by $F_n(\qcs{L}) \ceq [\qcs{L}_n]$ and $F_n(\alpha_n) \ceq [\alpha_n]$, 
-for all positive integers $n\leq m$.
+\arrow{urrr}{F_n} \QC(\GN{T}_n) \arrow[swap]{rr}{f_{n\leq m}^*} && \QC(\GN{T}_m) \arrow[swap]{ur}{F_m}. & 
+\end{tikzcd}
+\]
 Passing to isomorphism classes of objects and invoking the 
 universal property of $\varinjlim_{n\in \ZZ_{>0}} \QCiso{\GN{T}_n}$ 
-gives a group homomorphism
-$\theta: \varinjlim_{n\in \ZZ_{>0}} \QCiso{\GN{T}_n} \to \QCiso{\GN{T}}$; 
-this is a bijection  with inverse $[\qcs{L}]_{/\text{iso}} \mapsto [\qcs{L}_{/\text{iso}}]$.
-Now use Theorem~\ref{thm:application} and Proposition~\ref{prop:pullback} 
+gives a group isomorphism
+$\theta: \varinjlim_{n\in \ZZ_{>0}} \QCiso{\GN{T}_n} \to \QCiso{\GN{T}}$
+with inverse $[\qcs{L}]_{/\text{iso}} \mapsto [\qcs{L}_{/\text{iso}}]$.
+Now use Theorem~\ref{thm:application}, Proposition~\ref{prop:pullback} 
 and the fact that  $\Hom_{\text{qc}}(T(K),\EEx) = \varinjlim_{n\in \ZZ_{>0}} \GN{T}_n(k)^*$ 
@@
 Weil restriction, as in \cite{yu:09a}*{Thm 7.5 (2)}. 
-The next proposition shows that the category of quasicharacter sheaves for 
+The next proposition \David{Do we mean Lem 14.1 or Prop 14.2?} shows that the category of quasicharacter sheaves for 
 algebraic tori does indeed behave properly with regard to Weil restriction.
@@
 Weil restriction is compatible with the Greenberg transform in the following sense: 
-if $e$ is the ramification degree of $K'/K$ then, for every positive integer $n$,
+if $e$ is the ramification degree of $K'/K$ and $k'$ is the residue field of $K'$ then,
+for every positive integer $n$,
 \begin{equation}%\label{weilgreenberg}
-\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)
+\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)
 \iso
-\Res_{k'/k} \Gr_{en}(\underline{T'}),
+\Res_{k'/k} \Gr_{en}(\TTp).
 \end{equation}
-where $k'$ is the residue field for $K'$.
 \end{lemma}
@@
 \begin{proof}
-First, note that since $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ 
+First, note that since $\Res_{\OKp/\OK}(\TTp)$ 
 is a scheme over $\OK$, 
-the Greenberg transform $\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
+the Greenberg transform $\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)$ 
 is obtained by base change along $\OK \to \OK/\pK^n$ 
 followed by the Greenberg functor over the Artinian ring $\OK/\pK^n$. 
-On the other hand, since $\underline{T'}$ is a scheme over $\mathcal{O}_{K'}$, 
-the Greenberg transform $\Gr_{en}(\underline{T'})$ is defined by base change along 
-$\mathcal{O}_{K'} \to \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$ 
-followed by the Greenberg functor over the Artinian ring $\mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$; 
-see Definition~\ref{def:Grn}. 
+On the other hand, since $\TTp$ is a scheme over $\OKp$, 
+the Greenberg transform $\Gr_{en}(\TTp)$ is defined by base change along 
+$\OKp \to \OKp/\pKp^{en}$ 
+followed by the Greenberg functor over the Artinian ring $\OKp/\pKp^{en}$. 
 Note also that 
 \begin{equation}\label{nem}
-\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \iso \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}.
+\OKp \otimes_{\OK} \OK/\pK^n \iso \OKp/\pKp^{en}.
 \end{equation}
 
-Now, to prove the lemma, we may employ the functor of points perspective 
+To prove the lemma, we may employ the functor of points perspective 
 and exhibit an isomorphism of functors from 
-$\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
-to $\Res_{k'/k} \Gr_{en}(\underline{T'})$ as functors 
+$\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)$ 
+to $\Res_{k'/k} \Gr_{en}(\TTp)$ as functors 
 from the category of $\Fq$-algebras to the category of groups.
-To that end, let $R$ be any $\Fq$-module. 
-Let $\mathbb{W}$ be the Witt functor from the category of $\Fq$-algebras to rings. 
+To that end, let $R$ be any $\Fq$-algebra and 
+let $\WW$ be the Witt functor from the category of $\Fq$-algebras to rings. 
 By the definition of the Greenberg transform, the Weil restriction functor and \eqref{nem},
@@
 \begin{aligned}
-\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R)
-&= \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\left( \OK/\pK^n \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right)\\
-&= \underline{T'}\left(\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right)\\
-&= \underline{T'}\left(\mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right);
+\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)(R)
+&= \Res_{\OKp/\OK}(\TTp)\left( \OK/\pK^n \otimes_{\WW(k)} \WW(R)\right)\\
+&= \TTp\left(\OKp \otimes_{\OK} \OK/\pK^n \otimes_{\WW(k)} \WW(R)\right)\\
+&= \TTp\left(\OKp /\pKp^{en} \otimes_{\WW(k)} \WW(R)\right);
 \end{aligned}
@@
 \begin{aligned}
-\Res_{k'/k} \Gr_{en}(\underline{T'})(R)
-&= \Gr_{en}(\underline{T'}) (R\otimes_{k} k')\\
-&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k')} \mathbb{W}(R\otimes_{k} k')\right)\\
-&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k')} \mathbb{W}(R) \otimes_{\mathbb{W}(k)} \mathbb{W}(k')\right)\\
-&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right).
+\Res_{k'/k} \Gr_{en}(\TTp)(R)
+&= \Gr_{en}(\TTp) (k'\otimes_{k} R)\\
+&= \TTp\left( \OKp /\pKp^{en} \otimes_{\WW(k')} \WW(k'\otimes_{k} R)\right)\\
+&= \TTp\left( \OKp /\pKp^{en} \otimes_{\WW(k')} \WW(k') \otimes_{\WW(k)} \WW(R)\right)\\
+&= \TTp\left( \OKp /\pKp^{en} \otimes_{\WW(k)} \WW(R)\right).
 \end{aligned}
 \]
-So the ring isomorphism 
-\[
-\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R) \to \Res_{k'/k} \Gr_{en}(\underline{T'})(R)
-\]
-is apparent, as are the commuting ring homomorphisms
+So the group isomorphism 
+\[
+\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)(R) \to \Res_{k'/k} \Gr_{en}(\TTp)(R)
+\]
+is apparent, as are the commuting group homomorphisms
 \[
 \begin{tikzcd}
-\arrow{d} \Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R) \arrow{r}{\iso} & \arrow{d} \Res_{k'/k} \Gr_{en}(\underline{T'})(R)\\
-\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R') \arrow{r}{\iso} & \Res_{k'/k} \Gr_{en}(\underline{T'})(R'),
+\arrow{d} \Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)(R) \arrow{r}{\iso} & \arrow{d} \Res_{k'/k} \Gr_{en}(\TTp)(R)\\
+\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)(R') \arrow{r}{\iso} & \Res_{k'/k} \Gr_{en}(\TTp)(R'),
 \end{tikzcd}
@@
 Let $K'/K$ be a finite Galois extension and
-let $k'/k$ be the corresponding finite Galois extension of residue fields.
+let $k'/k$ be the corresponding extension of residue fields.
 Let $T$ be an algebraic torus over $K$ and 
@@
 Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} to lft-Néron models
-we see that a Néron model for $\Res_{K'/K}(T')$ is $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$;
-see also the proof of \cite{xarles:93a}*{Lemma 2.6}.
+we see that $\Res_{\OKp/\OK}(\TTp)$ is a Néron model for $\Res_{K'/K}(T')$.
 By the Néron mapping property, the canonical closed immersion
-$T\hookrightarrow \Res_{K'/K}(T')$ extends, uniquely, to a morphism
-$\underline{T}\to \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ of smooth $\OK$-group schemes.
+$T\hookrightarrow \Res_{K'/K}(T')$ extends uniquely to a morphism
+$\underline{T}\to \Res_{\OKp/\OK}(\TTp)$ of smooth $\OK$-group schemes.
 Applying the Greenberg transform $\Gr_{n}$ to this morphism
@@
 
-The techniques in this paper apply to all non-archimdean local fields $K$ with residue field $k$,
+The techniques in this paper apply to all non-archimdean local fields $K$ with residue field $k$
 and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$
-or on the ramification of $T$. Because of this, it is natural to ask if we can compare
-quasicharacter sheaves on $T$ and on $T'$ under conditions when there is a
-natural comparison between characters of $T(K)$ and of $T'(K')$.
-This comparison of has been made precise in \cite{chai-yu:01a}, 
-building on ideas in \cite{deligne:84a}*{\S 1}.
+or on the ramification of $T$. We may therefore ask if for a comparison of
+quasicharacter sheaves on $T$ and on $T'$ whenever there is a relationship
+between characters of $T(K)$ and of $T'(K')$.
+Such a relationship can exist between characters of $T(K)$ and $T'(K')$ even
+when the characteristics of $K$ and $K'$ differ
+\citelist{\cite{chai-yu:01a} \cite{deligne:84a}*{\S 1}}.
 
@@
 $N' \leq N$, the isomorphism \eqref{transfer} is depth-preserving at integers less than $N$.
-In this section we ask if the isomorphism \eqref{transfer} comes from an equivalence of
+In this section we show that the isomorphism \eqref{transfer} comes from an equivalence of
 categories of quasicharacter sheaves on $\GN{T}_n$ and those on $\GN{T}'_n$.
@@
 
-This paper has shown how quasicharacter sheaves 
+We have given a functorial relationship between quasicharacter sheaves 
 on the Greenberg transform of the Néron model of $T$ 
-determine admissible characters of $T(K)$, and vice versa, functorially.
+and admissible characters of $T(K)$.
 When coupled with the reciprocity map $\text{rec}_T $ for $T$, 
@@
 it follows that quasicharacter sheaves for $T$ 
-determine Langlands parameters for $T$, and vice versa, functorially.
+functorially correspond to Langlands parameters for $T$.
 We suspect that it is possible to extract Langlands parameters 
@@
  by the class field theory of Serre-Hazewinkel
- \cite{serre:60a},\cite{serre:61a},\cite{demazure-gabriel:GroupesAlgebriques}*{Appendice},
+ \citelist{\cite{serre:60a} \cite{serre:61a} \cite{demazure-gabriel:GroupesAlgebriques}*{Appendice}},
  especially as revisited in \cite{suzuki-yoshida:12a}*{\S 2}. 

### 2013-10-04 shanghai.tex
Deleting ks from subscripts

@@
 Let $\Frob{G} \ceq \id_{G} \times \Frob{\Fq}$ be the Frobenius automorphism of $\bG$.
+When no other fields play a role we will write $\Frob{}$ and $\Weil{}$ instead.
 
@@
 may be interpreted as a constructible $\ell$-adic sheaf $\gqcs{L}$ on $\bG$ together with
-an action of the Weil group $\Weil{\Fq}$ on $\gqcs{L}$ compatible with the action of
+an action of the Weil group $\Weil{}$ on $\gqcs{L}$ compatible with the action of
 $\Gal(\bFq/\Fq)$ on $\bG$. We now briefly review this point of view for later use in
-Section~\ref{sec:basechange}; see also \cite{deligne:80a}*{Def.~1.1.10}.  If $w \ceq \Frob{\Fq}^n$ we write $w_G$ for $\Frob{G}^n$.
+Section~\ref{sec:basechange}; see also \cite{deligne:80a}*{Def.~1.1.10}.  If $w \ceq \Frob{}^n$ we write $w_G$ for $\Frob{G}^n$.
 For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gqcs{L}\to \gqcs{L}$ by
@@
 $; 
-these isomorphisms satisfy $\varphi(uv) = \varphi(v) \circ v_G^* \varphi(u)$ for $u,v\in \Weil{\Fq}$, and
-we have $\phi = \varphi(\Frob{\Fq})$. 
+these isomorphisms satisfy $\varphi(uv) = \varphi(v) \circ v_G^* \varphi(u)$ for $u,v\in \Weil{}$, and
+we have $\phi = \varphi(\Frob{})$. 
 If we further define $\varphi_1(w) \ceq (w_G)_*(\varphi(w)^{-1})$ then
 $\varphi_1(w) : (w_G)_* \gqcs{L}\to \gqcs{L}$ is an isomorphism and
-$\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for $u,v\in \Weil{\Fq}$.
-Thus the pair $(\gqcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{\Fq}$
+$\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for $u,v\in \Weil{}$.
+Thus the pair $(\gqcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{}$
 on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of
-\cite{deligne:SGA4.5}*{Expos\'e XIII,~1.1}, failing only because $\Weil{\Fq}$ is not profinite.
+\cite{deligne:SGA4.5}*{Expos\'e XIII,~1.1}, failing only because $\Weil{}$ is not profinite.
 \Clifton{Improve this.}
-As we will see, our use of $\Weil{\Fq}$ rather than $\Gal(\bFq/\Fq)$ allows quasicharacter sheaves to
+As we will see, our use of $\Weil{}$ rather than $\Gal(\bFq/\Fq)$ allows quasicharacter sheaves to
 correspond to unbounded characters.
@@
 \begin{proof}
-Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and write $\Frob{}$ for $\Frob{G}$.  For any $x \in G(k')$,
+Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
 we may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
 and the value of $\Nm^*(t_G(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
-Applying \ref{CS.2} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
+Applying \ref{CS.2} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, F(x), \ldots, F^{n-1}(x))$ yields a diagram
 \[
 \begin{tikzcd}
-\gqcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gqcs{L}_{\Frob{}(x)} \otimes \gqcs{L}_{\Frob{}^2(x)} \otimes \cdots \otimes \gqcs{L}_x
-\dar{\phi_x \otimes (\Frob{}^*\phi)_x \otimes \cdots \otimes ((\Frob{}^{n-1})^*\phi)_x} \\
-\gqcs{L}_{\Nm(x)} \rar & \gqcs{L}_x \otimes \gqcs{L}_{\Frob{}(x)} \otimes \cdots \otimes \gqcs{L}_{\Frob{}^{n-1}(x)}.
+\gqcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gqcs{L}_{F(x)} \otimes \gqcs{L}_{F^2(x)} \otimes \cdots \otimes \gqcs{L}_x
+\dar{\phi_x \otimes (F^*\phi)_x \otimes \cdots \otimes ((F^{n-1})^*\phi)_x} \\
+\gqcs{L}_{\Nm(x)} \rar & \gqcs{L}_x \otimes \gqcs{L}_{F(x)} \otimes \cdots \otimes \gqcs{L}_{F^{n-1}(x)}.
 \end{tikzcd}
@@
 bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
-for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{CS.1}, $v$ maps to
+for $v_i \in \gqcs{L}_{F^i(x)}$.  By \ref{CS.1}, $v$ maps to
 $v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
-Let $\alpha_i \in \EEx$ represent $((\Frob{}^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
+Let $\alpha_i \in \EEx$ represent $((F^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
 the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gqcs{L}_{\Nm(x)}$
@@
   The $\Fq$-rational point $g$ under the geometric point $\bg$ determines a splitting
-  $\Weil{\Fq}\to \W(G,\bg)$ of $\W(G,\bg)\to \Weil{\Fq}$. 
-  In this way the Weil local system $(\gqcs{L},\phi)$ determines an $\ell$-adic character $\rho_g : \Weil{\Fq} \to \EEx$.
+  $\Weil{}\to \W(G,\bg)$ of $\W(G,\bg)\to \Weil{}$. 
+  In this way the Weil local system $(\gqcs{L},\phi)$ determines an $\ell$-adic character $\rho_g : \Weil{} \to \EEx$.
   %\[
@@
   %1 \rar & \pi_1(\bG, \bg) \rar &  \arrow{d}{\rho} \W(G,\bg) \rar
-  %& \ar[swap,bend right, dotted]{l}{g} \arrow[dotted]{dl}{\rho_g} \Weil{\Fq} \rar & 1\\
+  %& \ar[swap,bend right, dotted]{l}{g} \arrow[dotted]{dl}{\rho_g} \Weil{} \rar & 1\\
   %&&\EEx&&
@@
   \[
-  \rho_g(\Frob{\Fq}) =  \trFrob{\qcs{L}}(g).
+  \rho_g(\Frob{}) =  \trFrob{\qcs{L}}(g).
   \]
@@
   variety over $\Fq$ and thus $G(\Fq)$ is finite.
-  Therefore $\trFrob{\qcs{L}}(g) = \rho_g(\Frob{\Fq})$ is a root of unity
-  for every $g\in G(\Fq)$.  Since $\Weil{\Fq}$ is generated by
-  $\Frob{\Fq}$ and $\rho_g : \Weil{\Fq} \to \EEx$ is
+  Therefore $\trFrob{\qcs{L}}(g) = \rho_g(\Frob{})$ is a root of unity
+  for every $g\in G(\Fq)$.  Since $\Weil{}$ is generated by
+  $\Frob{}$ and $\rho_g : \Weil{} \to \EEx$ is
   a character, it follows that the image of $\rho_g$ is a finite group.
@@
   \begin{tikzcd}
-  1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \W(G,\bg) \rar \dar & \Weil{\Fq} \arrow[bend left]{rr}{\rho_g} \rar \dar & 1 & \EEx\\
+  1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \W(G,\bg) \rar \dar & \Weil{} \arrow[bend left]{rr}{\rho_g} \rar \dar & 1 & \EEx\\
   1 \rar &  \pi_1(\bG, \bg) \rar & \pi_1(G,\bg) \rar & \Gal(\bFq/\Fq) \arrow[dotted]{rru} \rar & 1 &
@@
   Let $f : G\to G$ be the Lang isogeny.
-  Recall that $\ker f = G(\Fq) = G^{\Frob{\Fq}}$; 
+  Recall that $\ker f = G(\Fq) = G^{\Frob{}}$; 
   in particular, the action of $\Gal(\bFq/\Fq)$ on $\ker f$ is trivial.
@@
 
- \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{\Fq}(x)} \to \gqcs{L}_x$
+ \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
   such that
@@
    \begin{tikzcd}[row sep=40]
-    \gqcs{L}_{\Frob{\Fq}(x)+\Frob{\Fq}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{\Fq}(x),\Frob{\Fq}(y)}}
-    && \gqcs{L}_{\Frob{\Fq}(x)}\otimes\gqcs{L}_{\Frob{\Fq}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
+    \gqcs{L}_{\Frob{}(x)+\Frob{}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{}(x),\Frob{}(y)}}
+    && \gqcs{L}_{\Frob{}(x)}\otimes\gqcs{L}_{\Frob{}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
     \gqcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
@@
    \begin{tikzcd}[column sep=40]
-    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{\Fq}(x)} \rar{\alpha_{\Frob{\Fq}(x)}} & \gqcs{L'}_{\Frob{\Fq}(x)} \dar{\phi_x'}
+    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{}(x)} \rar{\alpha_{\Frob{}(x)}} & \gqcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
     &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
@@
   \Clifton{Use: Etale $\QC$-schemes?}
-  We may associate a $1$-cocycle $\tau_\qcs{L}: \Weil{\Fq}\to G(\bFq)^*$ to each $\qcs{L} \in \QC(G)$
+  We may associate a $1$-cocycle $\tau_\qcs{L}: \Weil{}\to G(\bFq)^*$ to each $\qcs{L} \in \QC(G)$
   so that
   \[
-  \tau_\qcs{L}(\Frob{\Fq})(x) = \trFrob{\qcs{L}}(x)
+  \tau_\qcs{L}(\Frob{})(x) = \trFrob{\qcs{L}}(x)
   \]
@@
   \begin{align*}
-  \QCiso{G} &\to \Hh^1(\Weil{\Fq}, G(\bFq)^*), \\
+  \QCiso{G} &\to \Hh^1(\Weil{}, G(\bFq)^*), \\
   [\qcs{L}] &\mapsto [\tau_\qcs{L}],
@@
   We will construct a group isomorphism between $\QCiso{G}$ and
-  $\Hh^1(\Weil{\Fq}, G(\bFq)^*)$ using $s$, then prove independence from the choice of $s$.
-
-  Starting from $\qcs{L}$, we define a cocyle $\tau_{\qcs{L}} \in Z^1(\Weil{\Fq},G(\bFq)^*)$ as follows.
-  For $x \in G(\bFq)$, $\qcs{L}$ determines an isomorphism $\phi_x : \gqcs{L}_{\Frob{\Fq}(x)} \to \gqcs{L}_x$
+  $\Hh^1(\Weil{}, G(\bFq)^*)$ using $s$, then prove independence from the choice of $s$.
+
+  Starting from $\qcs{L}$, we define a cocyle $\tau_{\qcs{L}} \in Z^1(\Weil{},G(\bFq)^*)$ as follows.
+  For $x \in G(\bFq)$, $\qcs{L}$ determines an isomorphism $\phi_x : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
   of one-dimensional $\EE$-vector spaces; define $\tau_\qcs{L}$ by
   \begin{equation}\label{t}
-   \phi_{x}(s(\Frob{\Fq}(x))) = \tau_\qcs{L}(\Frob{\Fq})(x) s(x).
+   \phi_{x}(s(\Frob{}(x))) = \tau_\qcs{L}(\Frob{})(x) s(x).
   \end{equation}
-  Note that if $x$ is fixed by $\Frob{k}$ then $\tau_\qcs{L}(\Frob{\Fq})(x)$ is just $\trFrob{\qcs{L}}(x)$, so the restriction of
-  $\tau_\qcs{L}(\Frob{k})$ to $G(k)$ is just $\trFrob{\qcs{L}}$.
+  Note that if $x$ is fixed by $\Frob{}$ then $\tau_\qcs{L}(\Frob{})(x)$ is just $\trFrob{\qcs{L}}(x)$, so the restriction of
+  $\tau_\qcs{L}(\Frob{})$ to $G(k)$ is just $\trFrob{\qcs{L}}$.
   In general, Conditions~\ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
-  the scalar $\tau_\qcs{L}(\Frob{k})(x)$ is non-zero.  Moreover, Condition~\ref{cs.1} forces
-  $\tau_\qcs{L}(\Frob{\Fq})(x+y) = \tau_\qcs{L}(\Frob{\Fq})(x) \ \tau_\qcs{L}(\Frob{\Fq})(y)$
-  for all $x,y \in G(\bFq)$.  Now define $\tau_\qcs{L} : \Weil{\Fq} \to G(\bFq)^*$ recursively by
-  \[
-   \tau_\qcs{L}(\Frob{\Fq}^n) \ceq \tau_\qcs{L}(\Frob{\Fq})\cdot \,^{\Frob{\Fq}} \tau_\qcs{L}(\Frob{\Fq}^{n-1}),
-  \]
-  where $\Frob{\Fq}$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers
+  the scalar $\tau_\qcs{L}(\Frob{})(x)$ is non-zero.  Moreover, Condition~\ref{cs.1} forces
+  $\tau_\qcs{L}(\Frob{})(x+y) = \tau_\qcs{L}(\Frob{})(x) \ \tau_\qcs{L}(\Frob{})(y)$
+  for all $x,y \in G(\bFq)$.  Now define $\tau_\qcs{L} : \Weil{} \to G(\bFq)^*$ recursively by
+  \[
+   \tau_\qcs{L}(\Frob{}^n) \ceq \tau_\qcs{L}(\Frob{})\cdot \,^{\Frob{}} \tau_\qcs{L}(\Frob{}^{n-1}),
+  \]
+  where $\Frob{}$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers
   to pointwise multiplication of functions.
@@
   condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so
-  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
-  defined by $\tau_0(\Frob{\Fq}) \ceq \,^{\Frob{\Fq}} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
+  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{} \to G(\bFq)^*$
+  defined by $\tau_0(\Frob{}) \ceq \,^{\Frob{}} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
   so $\tau_2$ and $\tau_1$ are cohomologous. Thus
@@
   \begin{split}
-    \obj \QC(G) &\to \Hh^1(\Weil{\Fq},G(\bFq)^*), \\
+    \obj \QC(G) &\to \Hh^1(\Weil{},G(\bFq)^*), \\
     \qcs{L} &\mapsto [\tau_\qcs{L}],
@@
   $a(x+y) = a(x)a(y)$, so $a \in G(\bFq)^*$. By the first part of
-  condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}a \cdot a^{-1})$,
+  condition~\ref{cs.3}, $\tau'(\Frob{}) = \tau(\Frob{}) \cdot (\,^{\Frob{}^{-1}}a \cdot a^{-1})$,
   %\Clifton{Fix this.}
@@
   \begin{split}
-    \QCiso{G} &\to \Hh^1(\Weil{\Fq},G(\bFq)^*),\\
+    \QCiso{G} &\to \Hh^1(\Weil{},G(\bFq)^*),\\
     [\qcs{L}] &\mapsto [\tau_\qcs{L}]
@@
   for $\qcs{L}, \qcs{L'}$ and $\qcs{L} \otimes\qcs{L}'$ imply that
-  $\tau_{\qcs{L} \otimes\qcs{L}'}(\Frob{k}) = \tau_\qcs{L}(\Frob{k}) \tau_{\qcs{L}'}(\Frob{k})$,
+  $\tau_{\qcs{L} \otimes\qcs{L}'}(\Frob{}) = \tau_\qcs{L}(\Frob{}) \tau_{\qcs{L}'}(\Frob{})$,
   so \eqref{pich1} is a group homomorphism.
@@
  so there is some $a\in G(\Fq)^*$ such that 
- $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}}a \cdot a^{-1})$. 
+ $\tau'(\Frob{}) = \tau(\Frob{}) \cdot (\,^{\Frob{}}a \cdot a^{-1})$. 
  Define $\alpha : \qcs{L}\to \qcs{L'}$ by $\alpha_x(s(x)) \ceq a(x) s'(x)$ and $\alpha^{-1} : \qcs{L}'\to \qcs{L}$
@@
 
- Finally, to show that \eqref{pich1} is surjective, pick $[\tau]\in \Hh^1(\Weil{\Fq}, G(\bFq)^*)$.
+ Finally, to show that \eqref{pich1} is surjective, pick $[\tau]\in \Hh^1(\Weil{}, G(\bFq)^*)$.
  For each $x\in G(\bFq)$, set $\gqcs{L}_x \ceq \EE$.
@@
  clearly, $\mu$ satisfies condition~\ref{cs.1}.
- Define $\phi_x : \gqcs{L}_{\Frob{\Fq}(x)} \to \gqcs{L}_x$ by $\phi_x(1) \ceq \tau(\Frob{\Fq})(x)$,
+ Define $\phi_x : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_x(1) \ceq \tau(\Frob{})(x)$,
  for each $x\in G(\bFq)$. 
- Then $\phi$ satisfies condition~\ref{cs.2} because $\tau \in Z^1(\Weil{\Fq},G(\bFq)^*)$.
+ Then $\phi$ satisfies condition~\ref{cs.2} because $\tau \in Z^1(\Weil{},G(\bFq)^*)$.
  Setting $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$, we have that $[\tau]$ is the image of $\qcs{L}$
@@
 \begin{lemma} \label{lem:dual-inv}
-Let $X$ be a finitely generated abelian group equipped with an action of $\Weil{\Fq}$, and write $\Frob{} = \Frob{\Fq}$.  Then
+Let $X$ be a finitely generated abelian group equipped with an action of $\Weil{}$, and write $\Frob{} = \Frob{}$.  Then
 \begin{align*}
@@
 \begin{proof}
-There is a natural isomorphism $\Hh^1(\Weil{\Fq}, G(\bFq)^*) \to (G(\bFq)^*)_{\Frob{}}$ defined by $[z] \mapsto z(\Frob{})$.
+There is a natural isomorphism $\Hh^1(\Weil{}, G(\bFq)^*) \to (G(\bFq)^*)_{\Frob{}}$ defined by $[z] \mapsto z(\Frob{})$.
 The proposition now follows directly from Proposition~\ref{prop:etale} and Lemma~\ref{lem:dual-inv}.
@@
 an $\ell$-adic character $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with
-$\rho_1(\Frob{\Fq}) = \ell$, necessarily continuous. 
+$\rho_1(\Frob{}) = \ell$, necessarily continuous. 
 But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, 
@@
 to the category of schemes locally of finite type over $k$. 
-This functor respects open immersions, closed immersions, 
-etale morphisms, smooth morphisms and geometric components.
+This functor respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components.
 See

### 2013-10-04 shanghai.tex
pull-back to pullback

@@
 \]
-be the functor obtained by pull-back along the canonical closed immersion of $k$-schemes
+be the functor obtained by pullback along the canonical closed immersion of $k$-schemes
 $\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$
@@
 \begin{proof}
- Let $b_G : {\bar G} \to G$ be the pull-back of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
+ Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
  Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$. 
@@
 
-\begin{lemma}\label{lemma:finite-pull-back}
+\begin{lemma}\label{lemma:finite-pullback}
 Let $g : J \to G$ be a morphism of group schemes. 
 Let $f_g : H\times_G J\to J$
-be the pull-back of $f$ along $g$ and define $\psi_g : \ker f_g \to \Aut(V)$ as in the diagram below:
+be the pullback of $f$ along $g$ and define $\psi_g : \ker f_g \to \Aut(V)$ as in the diagram below:
 \[
@@
 \begin{proof}
-The key point is that pull-back along $g$ takes isogenies to isogenies,
+The key point is that pullback along $g$ takes isogenies to isogenies,
 and maps over $G$ to maps over $J$, as pictured below.
@@
 In this form we could treat $g^*$ as a functor $C(J)\to C(G)$,
-were it not for the fact that pull-back is defined only up to isomorphism.
+were it not for the fact that pullback is defined only up to isomorphism.
 In the localized categories, this ambiguity disappears. 
@@
 Set $H_m \ceq H\times_G(G\times G)$, write $f_m : H_m \to G \times G$ for the pullback of $f$ to $H_m$, and let $A$ and $A_m$ be the kernels of $f$ and $f_m$ respectively.
-Consider the diagram of Lemma~\ref{lemma:finite-pull-back}:
+Consider the diagram of Lemma~\ref{lemma:finite-pullback}:
 \[
@@
 We have $(f,\psi) \boxtimes (f,\psi) = (f\times f, \psi\otimes \psi)$.
-Since $f\circ m_H = m \circ (f\times f)$, the universal property of pull-back gives
+Since $f\circ m_H = m \circ (f\times f)$, the universal property of pullback gives
 a unique $\theta : H\times H \to H_m$ making the following commute.
@@
  This construction defines a monoidal functor $L$ from $C(G)$ to $\Loc(G)$ that
- commutes with pull-back along any morphism of group schemes.
+ commutes with pullback along any morphism of group schemes.
 
@@
 Let $G^0$ be the connected component of $G$ containing the identity.
-By Proposition~\ref{prop:pullback}, pull-back along
+By Proposition~\ref{prop:pullback}, pullback along
 $G^0\hookrightarrow G$ determines a monoidal functor
@@
 \]
-be the functor produced by precomposing pull-back along $\OK \to \OK/\pK^n$ with the Greenberg functor.
+be the functor produced by precomposing pullback along $\OK \to \OK/\pK^n$ with the Greenberg functor.
 \end{definition}
@@
 induces a map of group pro-schemes $\GN{T} \to \Res_{k'/k} \GN{T}'$ which,
-through the pull-back functor and the trace of Frobenius, induces the homomorphism
+through the pullback functor and the trace of Frobenius, induces the homomorphism
 \[
@@
 Since $\left(\Res_{k'/k} \GN{T}'_{en} \right)(\Fq) = \left(\GN{T}'_{en}\right)(k')$,
-the pull-back functor $\QC(\Res_{k'/k} \GN{T}'_{en})\to \QC(\GN{T}_n)$
+the pullback functor $\QC(\Res_{k'/k} \GN{T}'_{en})\to \QC(\GN{T}_n)$
 obtained by applying Proposition~\ref{prop:pullback} to \eqref{men} gives

### 2013-10-04 shanghai.tex
Re-indexed the conditions defining quasicharacter sheaves. Working on Section 6.

--- 2013-10-04 shanghai.tex
@@
 \newcommand{\pK}{\mathfrak{p}_K}
-\newcommand{\OKp}{\mathcal{O}_{K'}}
-\newcommand{\pKp}{\mathfrak{p}_{K'}}
 \newcommand{\OL}{\mathcal{O}_L}
@@
 %\newcommand{\bFp}{{\mathbb{\bar F}_p}}
-\newcommand{\WW}{\mathbb{W}}
 
@@
 \newcommand{\TL}{\underline{T_L}}
-\newcommand{\TTp}{\underline{T}'}
 \newcommand{\invlim}[1]{\lim\limits_{\overleftarrow{#1}}}
@@
 \begin{enumerate}
-\labitem{(CS.0)}{CS.0} $\gqcs{L}$ is a rank~one $\ell$-adic local system on $\bG$, by which we mean
+\labitem{(CS.1)}{CS.1} $\gqcs{L}$ is a rank~one $\ell$-adic local system on $\bG$, by which we mean
 a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces; 
-\labitem{(CS.1)}{CS.1} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
+\labitem{(CS.2)}{CS.2} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
   where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
@@
 %
-\labitem{(CS.2)}{CS.2} $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$ is an
+\labitem{(CS.3)}{CS.3} $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$ is an
   isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with $\mu$ in the sense that the following diagram commutes.
@@
 \begin{enumerate}
-\labitem{(CS.3)}{CS.3} if $\qcs{L} = (\gqcs{L},\mu,\phi)$ and
+\labitem{(CS.4)}{CS.4} if $\qcs{L} = (\gqcs{L},\mu,\phi)$ and
   $\qcs{L'} = (\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$ then
@@
 
-The isomorphism $\mu : \bm^* \gqcs{L} \to \LxL$ together with property~\ref{CS.2} guarantee
+The isomorphism $\mu : \bm^* \gqcs{L} \to \LxL$ together with 
+\ref{CS.3} guarantee
 that the function $\trFrob{\qcs{L}} : G(\Fq)\to \EEx$ is a group homomorphism.  If we write
@@
   Thus $\bf^*\gqcs{L}$ is locally constant on
-  $\bH^j$. To complete the proof that $\bf^*\gqcs{L}$ satisfies Condition~\ref{CS.0}
+  $\bH^j$. To complete the proof that $\bf^*\gqcs{L}$ satisfies 
+  \ref{cs.4}
   simply observe that $\bf^*\gqcs{L}$ has rank~one since 
@@
 
-  To see that $(\bfxf)^* \mu$ satisfies
-  condition \ref{CS.1}, apply the functor $(\bfxf)^*$
-  to \ref{CS.1} for $\qcs{L}$ and use the canonical isomorphism
+  To see that $(\bfxf)^* \mu$ satisfies \ref{CS.2}, 
+  apply the functor $(\bfxf)^*$
+  to \ref{CS.2} for $\qcs{L}$ and use the canonical isomorphism
   $(\bfxf)^*(\LxL) \iso \bf^*\gqcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gqcs{L}$.
-  To show that $f^*\qcs{L}$ satisfies condition
-  \ref{CS.2}, apply the same functor to \ref{CS.2} for $\qcs{L}$.
+  To show that $f^*\qcs{L}$ satisfies 
+  \ref{CS.3}, apply the same functor to \ref{CS.3} for $\qcs{L}$.
   The fact that $f$ is a morphism of group schemes defined over $\Fq$ then
@@
 
-  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{CS.3} defines the action
+  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{CS.4} defines the action
   of $f^*$ on morphisms of quasicharacter sheaves; arguing as above shows that $f^*$ is
@@
 It follows that \eqref{eq:fm} gives an isomorphism $\gqcs{L} \to  \gqcs{L}_1\boxtimes \gqcs{L}_2$.
-It is a matter of routine to show that this morphism satisfies Conditions~\ref{CS.2} as they apply here,
+It is a matter of routine to show that this morphism satisfies 
+\ref{CS.3} as it applies here,
 from which it follows that we have exhibited an isomorphism 
@@
 \]
-The commutativity of the diagram (CS.2) for $\phi_{k'}$ 
+The commutativity of the diagram (CS.3) for $\phi_{k'}$ 
 follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
@@
 and the value of $\Nm^*(t_G(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
-Applying \ref{CS.2} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
+Applying \ref{CS.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
 \[
@@
 bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
-for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{CS.1}, $v$ maps to
+for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{CS.2}, $v$ maps to
 $v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
@@
 equipped with an isomorphism $\mu_0 : m^* \qcs{L}_0 \to \qcs{L}_0 \boxtimes \qcs{L}_0$ 
-satisfying the analogue of Condition~\ref{CS.1} on $G$; 
-morphisms in $\QCb(G)$ are defined as in the second part of Condition~\ref{CS.2}. 
+satisfying the analogue of \ref{CS.1} on $G$; 
+morphisms in $\QCb(G)$ are defined as in the second part of 
+\ref{CS.3}. 
 This is the category of \emph{bounded quasicharacter sheaves} on $G$. 
@@
  This functor preserves local constancy, so takes local systems to local systems. 
- Set $\mu \ceq b_{G\times G}^*\mu_0$; clearly, this satisfies Condition~\ref{CS.2} 
+ Set $\mu \ceq b_{G\times G}^*\mu_0$; clearly, this satisfies \ref{CS.2} 
  with $b_G^*\qcs{L}_0$ playing the role of $\gqcs{L}$.
- Moreover, $\phi$ is compatible with $\mu$ in the sense of Condition~\ref{CS.3}.
+ Moreover, $\phi$ is compatible with $\mu$ in the sense of \ref{CS.3}.
  This construction defines the functor $B_G^* : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
@@
 of bounded quasicharacter sheaves that play a role in Section \ref{sec:restriction}.
+
 A morphism $f : H\to G$ of $\QC$-schemes is a \emph{discrete isogeny} if it is a finite, surjective
@@
 the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f$ is trivial.
-We begin by defining a category $C(G)$ whose objects consist of pairs $(f,\psi)$, where
+% similar nomenclature is employed in \cite{kamgarpour:09a}*{\S 2.2}.
+Consider the category $C(G)$ whose objects consist of pairs $(f,\psi)$, where
 \begin{itemize}
@@
 and $T$ is an isomorphism of vector spaces.
+
 Let \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at weak isomorphisms.
-
-%Now consider the localization $C(G)[W^{-1}]$ of $C(G)$ at weak isomorphisms.
  Morphisms in $C(G)[W^{-1}]$ are simple to describe because 
- $W$ is a left-multiplicative system in the sense of
-  \cite{kashiwara-schapira:CatgoriesSheaves}*{\S 7.1.7};
-namely, a morphism in $C(G)[W^{-1}]$ is the equivalence class of 
+ $W$ is a left multiplicative system in the sense of
+  \cite{kashiwara-schapira:CatgoriesSheaves}*{\S 7.1.7}:
+a morphism in $C(G)[W^{-1}]$ is the equivalence class of 
   \begin{equation}\label{eq:morGCf}
@@
  and $(\beta_1,U_1) : (f_1,\psi_1) \to (f',\psi')$ is a weak isomorphism in $C(G)$.
+See \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16} for more detail, including the equivalence relation mentioned above.
 
@@
 \begin{lemma}\label{lemma:finite-iso}
-Each $(f,\psi)$ in $\QCf(G)$ determines a canonical isomorphism $m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$. \David{I'm confused at first reading by the statement of this lemma}
+Each $(f,\psi)$ in $\QCf(G)$ determines a canonical isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$. 
  \end{lemma}
@@
 \begin{proof}
+We will prove the proposition by finding a weak isomorphism $m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ in $C_1(G\times G)$ and showing that, after passing from $C_1(G\times G)$ to $\QCf(G\times G)$, the resulting isomorphism, denoted by $\mu(f,\psi)$, is canonically determined by $(f,\psi)$.
+
 Set $H_m \ceq H\times_G(G\times G)$, write $f_m : H_m \to G \times G$ for the pullback of $f$ to $H_m$, and let $A$ and $A_m$ be the kernels of $f$ and $f_m$ respectively.
@@
 Choose a basis $\{ v \}$ for $V$; then $\{ v\otimes v \}$ is a basis for $V\otimes V$.
-Define $T : V \to V\otimes V$ by $T(v) \ceq v\otimes v$. Then the lower part of this
-diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G)$.
+Let $T : V \to V\otimes V$ be the linear transformation taking $v$ to $v\otimes v$. Then the lower part of this
+diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G\times G)$.
 
 While $\theta$ was canonical, $T$ was not, as it depended on the choice of a basis for $V$.
-However, after passing from $C_1(G)$ to $\QCf(G)$, the resulting isomorphism
-$\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ is canonical in $\QCf(G)$.
+However, after passing from $C_1(G\times G)$ to $\QCf(G\times G)$, the resulting isomorphism in $\QCf(G\times G)$
+$\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ is independent of the choice of basis for $V$.
  \end{proof}
@@
 
-   \Clifton{Is this confusing? Is it clear to what $\Loc(G)$ refers?}
- Now we introduce a faithful functor $L : C(G) \to \Loc(G)$ to the category of local systems on $G$.
+ Now we introduce a faithful functor $L$ from $C(G)$ to the category of local systems on $G$, which we will denote by $\Loc(G)$.
  For any object $(f,\psi)$ in $C(G)$, let $L(f,\psi)$ be the $\psi$-isotypic component of $f_* V_H$, 
@@
   To show that $L_G(f,\psi) \iso (\qcs{L}_0,\mu_0)$ we simply apply the sheaf--function dictionary
-  as follows \citelist{\cite{laumon:87a}*{1.1.3} \cite{deligne:SGA4.5}*{Sommes trigonométriques}}.
+  as follows \citelist{\cite{laumon:87a}*{1.1.3} \cite{deligne:SGA4.5}*{Sommes trig.}}.
   First, recall that $L_G(f,\psi) \ceq (L(f,\psi), \mu(f,\psi))$.
@@
 \begin{enumerate}
- \labitem{(cs.0)}{cs.0} an indexed set of one-dimensional
+ \labitem{(cs.1)}{cs.1} an indexed set of one-dimensional
   $\EE$-vector spaces $\gqcs{L}_x$, as $x$ runs over
@@
 
- \labitem{(cs.1)}{cs.1} an indexed set of isomorphisms
+ \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms
   $\mu_{x,y} : \gqcs{L}_{x+y} \xrightarrow{\iso} \gqcs{L}_{x} \otimes\gqcs{L}_{y}$,
@@
 
- \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{\Fq}(x)} \to \gqcs{L}_x$
+ \labitem{(cs.3)}{cs.3} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{\Fq}(x)} \to \gqcs{L}_x$
   such that
@@
 \begin{enumerate}
- \labitem{(cs.3)}{cs.3} an indexed set $\alpha_x : \gqcs{L}_x \to \gqcs{L'}_x$
+ \labitem{(cs.4)}{cs.4} an indexed set $\alpha_x : \gqcs{L}_x \to \gqcs{L'}_x$
   of linear transformations such that
@@
   $\tau_\qcs{L}(\Frob{k})$ to $G(k)$ is just $\trFrob{\qcs{L}}$.
-  In general, Conditions~\ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
-  the scalar $\tau_\qcs{L}(\Frob{k})(x)$ is non-zero.  Moreover, Condition~\ref{cs.1} forces
+  In general, \ref{cs.1} and \ref{cs.2}, together with \eqref{section}, guarantee that
+  the scalar $\tau_\qcs{L}(\Frob{k})(x)$ is non-zero.  
+  Moreover, \ref{cs.2} forces
   $\tau_\qcs{L}(\Frob{\Fq})(x+y) = \tau_\qcs{L}(\Frob{\Fq})(x) \ \tau_\qcs{L}(\Frob{\Fq})(y)$
@@
   For each $x \in G(\bFq)$ set $a(x) = \frac{s_2(x)}{s_1(x)}$.  Then \eqref{section} and
-  condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so
+  \ref{cs.2} together imply $a(x+y) = a(x)a(y)$, so
   $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
@@
   by $\alpha_x(s(x)) = a(x) s'(x)$.
-  By the second part of condition~\ref{cs.3},
+  By the second part of \ref{cs.4},
   $a(x+y) = a(x)a(y)$, so $a \in G(\bFq)^*$. By the first part of
-  condition~\ref{cs.3}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}a \cdot a^{-1})$,
+  \ref{cs.4}, $\tau'(\Frob{\Fq}) = \tau(\Frob{\Fq}) \cdot (\,^{\Frob{\Fq}^{-1}}a \cdot a^{-1})$,
   %\Clifton{Fix this.}
@@
  by $\alpha^{-1}_x(s'(x)) \ceq a(x)^{-1} s(x)$, for $x\in G(\bFq)$.
- It is straightforward to check that $\alpha$ satisfies condition~\ref{cs.3}
+ It is straightforward to check that $\alpha$ satisfies \ref{cs.3}
  and that $\alpha^{-1}$ is its inverse. Thus $\qcs{L} \iso \qcs{L'}$ in $\QC(G)$ and \eqref{pich1} is injective.
@@
  $\mu_{x,y}(1) \ceq 1\otimes1$, for $x,y\in G(\bFq)$; 
- clearly, $\mu$ satisfies condition~\ref{cs.1}.
+ clearly, $\mu$ satisfies \ref{cs.2}.
  Define $\phi_x : \gqcs{L}_{\Frob{\Fq}(x)} \to \gqcs{L}_x$ by $\phi_x(1) \ceq \tau(\Frob{\Fq})(x)$,
  for each $x\in G(\bFq)$. 
- Then $\phi$ satisfies condition~\ref{cs.2} because $\tau \in Z^1(\Weil{\Fq},G(\bFq)^*)$.
+ Then $\phi$ satisfies \ref{cs.3} because $\tau \in Z^1(\Weil{\Fq},G(\bFq)^*)$.
  Setting $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$, we have that $[\tau]$ is the image of $\qcs{L}$
@@
 We write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$. 
-Let $T$ be an algebraic torus over $K$; the filtrations defined by Moy-Prasad and Yu \cite{yu:03a}*{\S 5}
-allow us to define the depth of character $\chi$ as the infimum of the $r$ so that $\chi$ vanishes on $T(K)_r$.
+Let $T$ be an algebraic torus over $K$.
 We write $\Hom_{< n}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $n$ 
@@
 
-A N\'eron model for $T$ is a smooth group scheme $\TT$ over $\OK$ with generic fiber $T$
-that satisfies the N\'eron mapping property: if $S$ is any smooth scheme over $\OK$ then every morphism
-$S_\eta \to T$ over $K$ extends uniquely to a morphism $S \to \TT$.  N\'eron models exist for any torus
-$T$ \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch 10.1, Thm 6} and are unique up to isomorphism;
-$\TT$ is separated, commutative, locally finite type over $\OK$ and satisfies $\TT(\OK) = T(K)$.
-
-We will also need the Greenberg functor \citelist{\cite{greenberg:61} \cite{greenberg:63a}}:
-a functor from the category of schemes locally of finite type 
+A N\'eron model for $T$, denoted here by $\TT$ 
+and whose existence is given by \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch 10.1, Thm 6},
+is a separated, smooth, commutative group scheme locally of finite type over $\OK$ with generic fibre $T$,
+that enjoys the N\'eron mapping property:
+if $S$ is a smooth scheme over $\OK$ then every morphism $S_\eta \to T$
+over $K$ extends uniquely to a morphism $S \to \TT$. 
+Equivalently, the
+N\'eron mapping property states that the function
+$\Hom_{\OK} (S,\TT) \to \Hom_K(S_\eta,T)$, given by restriction to
+generic fibres, is a bijection; 
+in particular, taking $S \ceq \Spec{\OK}$, this implies $\TT(\OK) = T(K)$.
+
+We will also need the Greenberg functor, 
+introduced in \cite{greenberg:61} and \cite{greenberg:63a}, 
+as a functor from the category of schemes locally of finite type 
 over an Artinian local ring with perfect residue field $k$ 
@@
 etale morphisms, smooth morphisms and geometric components.
-See
-\citelist{\cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1} \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} \cite{stasinski:12a}*{\S 2}}
-for more background on the Greenberg functor.
+Besides Greenberg's original papers, see
+\citelist{\cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1} \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6}}
+and the first few sections of \cite{stasinski:12a} 
+for background on the Greenberg functor.
 
@@
 \begin{align*}
- \GN{T}_n &\ceq \Gr_n(\TT), \\
+ \GN{T}_n &\ceq \Gr_n(\TT) \\
  f_n &\ceq P_n(\TT).
@@
 
-We list some fundamental properties of $f_n$ and $\GN{T}_n$ for further use:
+Some fundamental properties of $f_n : \GN{T}_{n+1} \to \GN{T}_n$ are:
  \begin{enumerate}
-  \labitem{(GN.0)}{truncation}
-  $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes over $\Fq$
-  \citelist{\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276} \cite{stasinski:12a}*{\S 4}}.
-  We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.
+   \labitem{(GN.0)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
   \labitem{(GN.1)}{smooth} 
@@
   The Greenberg functor takes the geometric identity component of $\TT_n$ 
-  to the geometric identity component of $\GN{T}_n$.
-  In fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$ and
-  this group is finitely generated \cite{xarles:93a}*{2.18}.
-  \labitem{(GN.2)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
+  to the geometric identity component of $\GN{T}_n$;
+  in fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$ and
+  this group is finitely generated by \cite{xarles:93a}*{2.18}.
+  \labitem{(GN.2)}{truncation}
+  The morphism $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes over $\Fq$; 
+  see  \cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276}
+  and  \cite{stasinski:12a}*{\S 4}.
+  We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.
 \end{enumerate}
@@
 \section{Application to quasicharacters of bounded depth} \label{sec:bdchar}
-
-We now apply the results of Part~\ref{part1} to characters of $T(K)$.
 
@@
 is an isomomorphism. 
-Moreover, the isomorphism $\trFrob{T,n}$ is a natural transformation
-between the additive functors
+Moreover, the isomorphism $\trFrob{T,n}$ is functorial in the following sense:
+$T \mapsto \trFrob{T,n}$ is a natural transformation between the following two additive functors
 \begin{enumerate}
@@
 The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
-while the second part shows that trace of Frobenius is a natural transformation
+while the second part shows that Trace of Frobenius is a natural transformation
 $t_{ - ,n} : F_1 \to F_2$. When further combined with Lemma~\ref{prop:product},
@@
 \section{A sheaf--function dictionary for tori over local fields} \label{sec:quasichar}
-
-In this section we package the isomorphisms of Theorem~\ref{thm:application} into
-a single dictionary.
 
@@
 
+\begin{remark}
+\Clifton{I'm not sure if we should include this remark in the final version.}
+If $K \ceq \mathbb{Q}_q$ and 
+$T \ceq \Gm{\mathbb{Q}_q}$ then $\GN{T}^0 = \mathbb{W}^*_{\FF_q}$, 
+the group scheme (!) over $\Fq$ of units in the ring scheme $\mathbb{W}_{\FF_q}$
+and $\GN{T}$, as a scheme, is the disjoint union of copies of $\mathbb{W}^*_{\FF_q}$
+indexed by the integers. Based on this example, 
+we ask if, for arbitrary $T$, the pro-group scheme $\GN{T}$ is, in fact, a group scheme.
+We have not explored that question.
+\end{remark}
+
 For any  ordered pair of positive integers $n< m$ define 
@@
 An object in $\QC(\GN{T})$ is an equivalence class in 
-$\cup_{n\in\ZZ_{>0}} \obj \QC(\GN{T}_n)$.
-We say that $\qcs{L}_n\in \QC(\GN{T}_n)$ is equivalent to $\qcs{L}_{m}\in \QC(\GN{T}_m)$ 
-if there is some $k \ge m,n$ with $f_{n\leq k}^* \qcs{L}_{n} = f_{m\leq k}^* \qcs{L}_m$. \David{is it okay for this to be equality rather than isomorphism?} 
+$\cup_{n\in\ZZ_{>0}} \obj \QC(\GN{T}_n)$ under the relation: 
+$\qcs{L}_n\in \QC(\GN{T}_n)$ is equivalent to $\qcs{L}_{m}\in \QC(\GN{T}_m)$ 
+if $f_{n\leq k}^* \qcs{L}_{n} = f_{m\leq k}^* \qcs{L}_m$ for some $n,m\leq k$. 
 Objects in $\QC(\GN{T})$ all take the form
@@
 for some unique $\qcs{L}_n \in \QC(\GN{T}_n)$.
-A morphism $[\qcs{L}_n] \to [\qcs{L}_m]$ in $\QC(\GN{T})$ is an equivalence class
-in $\cup_{n,m\leq k} \Hom(f_{n\leq k}^*\qcs{L}_n,f_{m\leq k}^*\qcs{L}_m)$.
-We say that $\alpha_k\in \mor \QC(\GN{T}_k)$ is equivalent to 
-$\beta_l \in \mor \QC(\GN{T}_l)$ if there is some $i \ge k, l$ with $f_{k\leq i}^*\alpha_k = f_{l\leq i}^* \beta_l$. 
-Morphisms in $\QC(\GN{T})$ all take the form
+Maps $[\qcs{L}_n] \to [\qcs{L}_m]$ in $\QC(\GN{T})$ are defined as follows:
+$\Hom([\qcs{L}_n],[\qcs{L}_m])$ is the set of equivalence classes 
+in $\cup_{n,m\leq k} \Hom(f_{n\leq k}^*\qcs{L}_n,f_{m\leq k}^*\qcs{L}_m)$ 
+under the relation: $\alpha_k\in \mor \QC(\GN{T}_k)$ is equivalent to 
+$\beta_l \in \QC(\GN{T}_l)$ if $f_{k\leq i}^*\alpha_k = f_{l\leq i}^* \beta_l$ for some $k,l\leq i$. 
+Maps in $\QC(\GN{T})$ all take the form
 \[
@@
 Identities and composition are defined in the natural way.
-We may define a tensor structure for $\QC(\GN{T})$ by setting
+Category $\QC(\GN{T})$ carries a tensor structure under
 \[
@@
 is an isomomorphism. 
-Moreover, the isomorphism $\trFrob{T}$ is a natural transformation 
-between the additive functors
+Moreover, the isomorphism $\trFrob{T}$ is functorial in the following sense: 
+$T \mapsto \trFrob{T}$ is a natural transformation 
+between the following two additive functors
 \begin{enumerate}
@@
 \begin{proof}
-We may define full and faithful functors $F_n : \QC(\GN{T}_n) \to \QC(\GN{T})$ for each $n$ by $F_n(\qcs{L}) \ceq [\qcs{L}_n]$ and $F_n(\alpha_n) \ceq [\alpha_n]$.
-For positive integers $n \le m$ these functors fit together into a diagram
+Observe that $\QC(\GN{T})$ comes equipped with monoidal subcategories
 \[
@@
 \ & & & \QC(\GN{T})\\
-\arrow{urrr}{F_n} \QC(\GN{T}_n) \arrow[swap]{rr}{f_{n\leq m}^*} && \QC(\GN{T}_m) \arrow[swap]{ur}{F_m}. & 
-\end{tikzcd}
-\]
+\arrow{urrr}{F_n} \QC(\GN{T}_n) \arrow[swap]{rr}{f_{n\leq m}^*} && \QC(\GN{T}_m) \arrow[swap]{ur}{F_m} & 
+\end{tikzcd}
+\]
+defined by $F_n(\qcs{L}) \ceq [\qcs{L}_n]$ and $F_n(\alpha_n) \ceq [\alpha_n]$, 
+for all positive integers $n\leq m$.
 Passing to isomorphism classes of objects and invoking the 
 universal property of $\varinjlim_{n\in \ZZ_{>0}} \QCiso{\GN{T}_n}$ 
-gives a group isomorphism
-$\theta: \varinjlim_{n\in \ZZ_{>0}} \QCiso{\GN{T}_n} \to \QCiso{\GN{T}}$
-with inverse $[\qcs{L}]_{/\text{iso}} \mapsto [\qcs{L}_{/\text{iso}}]$.
-Now use Theorem~\ref{thm:application}, Proposition~\ref{prop:pullback} 
+gives a group homomorphism
+$\theta: \varinjlim_{n\in \ZZ_{>0}} \QCiso{\GN{T}_n} \to \QCiso{\GN{T}}$; 
+this is a bijection  with inverse $[\qcs{L}]_{/\text{iso}} \mapsto [\qcs{L}_{/\text{iso}}]$.
+Now use Theorem~\ref{thm:application} and Proposition~\ref{prop:pullback} 
 and the fact that  $\Hom_{\text{qc}}(T(K),\EEx) = \varinjlim_{n\in \ZZ_{>0}} \GN{T}_n(k)^*$ 
@@
 Weil restriction, as in \cite{yu:09a}*{Thm 7.5 (2)}. 
-The next proposition \David{Do we mean Lem 14.1 or Prop 14.2?} shows that the category of quasicharacter sheaves for 
+The next proposition shows that the category of quasicharacter sheaves for 
 algebraic tori does indeed behave properly with regard to Weil restriction.
@@
 Weil restriction is compatible with the Greenberg transform in the following sense: 
-if $e$ is the ramification degree of $K'/K$ and $k'$ is the residue field of $K'$ then,
-for every positive integer $n$,
+if $e$ is the ramification degree of $K'/K$ then, for every positive integer $n$,
 \begin{equation}%\label{weilgreenberg}
-\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)
 \iso
-\Res_{k'/k} \Gr_{en}(\TTp).
+\Res_{k'/k} \Gr_{en}(\underline{T'}),
 \end{equation}
+where $k'$ is the residue field for $K'$.
 \end{lemma}
@@
 \begin{proof}
-First, note that since $\Res_{\OKp/\OK}(\TTp)$ 
+First, note that since $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ 
 is a scheme over $\OK$, 
-the Greenberg transform $\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)$ 
+the Greenberg transform $\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
 is obtained by base change along $\OK \to \OK/\pK^n$ 
 followed by the Greenberg functor over the Artinian ring $\OK/\pK^n$. 
-On the other hand, since $\TTp$ is a scheme over $\OKp$, 
-the Greenberg transform $\Gr_{en}(\TTp)$ is defined by base change along 
-$\OKp \to \OKp/\pKp^{en}$ 
-followed by the Greenberg functor over the Artinian ring $\OKp/\pKp^{en}$. 
+On the other hand, since $\underline{T'}$ is a scheme over $\mathcal{O}_{K'}$, 
+the Greenberg transform $\Gr_{en}(\underline{T'})$ is defined by base change along 
+$\mathcal{O}_{K'} \to \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$ 
+followed by the Greenberg functor over the Artinian ring $\mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}$; 
+see Definition~\ref{def:Grn}. 
 Note also that 
 \begin{equation}\label{nem}
-\OKp \otimes_{\OK} \OK/\pK^n \iso \OKp/\pKp^{en}.
+\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \iso \mathcal{O}_{K'}/\mathfrak{p}_{K'}^{en}.
 \end{equation}
 
-To prove the lemma, we may employ the functor of points perspective 
+Now, to prove the lemma, we may employ the functor of points perspective 
 and exhibit an isomorphism of functors from 
-$\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)$ 
-to $\Res_{k'/k} \Gr_{en}(\TTp)$ as functors 
+$\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)$ 
+to $\Res_{k'/k} \Gr_{en}(\underline{T'})$ as functors 
 from the category of $\Fq$-algebras to the category of groups.
-To that end, let $R$ be any $\Fq$-algebra and 
-let $\WW$ be the Witt functor from the category of $\Fq$-algebras to rings. 
+To that end, let $R$ be any $\Fq$-module. 
+Let $\mathbb{W}$ be the Witt functor from the category of $\Fq$-algebras to rings. 
 By the definition of the Greenberg transform, the Weil restriction functor and \eqref{nem},
@@
 \begin{aligned}
-\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)(R)
-&= \Res_{\OKp/\OK}(\TTp)\left( \OK/\pK^n \otimes_{\WW(k)} \WW(R)\right)\\
-&= \TTp\left(\OKp \otimes_{\OK} \OK/\pK^n \otimes_{\WW(k)} \WW(R)\right)\\
-&= \TTp\left(\OKp /\pKp^{en} \otimes_{\WW(k)} \WW(R)\right);
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R)
+&= \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\left( \OK/\pK^n \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right)\\
+&= \underline{T'}\left(\mathcal{O}_{K'} \otimes_{\OK} \OK/\pK^n \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right)\\
+&= \underline{T'}\left(\mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right);
 \end{aligned}
@@
 \begin{aligned}
-\Res_{k'/k} \Gr_{en}(\TTp)(R)
-&= \Gr_{en}(\TTp) (k'\otimes_{k} R)\\
-&= \TTp\left( \OKp /\pKp^{en} \otimes_{\WW(k')} \WW(k'\otimes_{k} R)\right)\\
-&= \TTp\left( \OKp /\pKp^{en} \otimes_{\WW(k')} \WW(k') \otimes_{\WW(k)} \WW(R)\right)\\
-&= \TTp\left( \OKp /\pKp^{en} \otimes_{\WW(k)} \WW(R)\right).
+\Res_{k'/k} \Gr_{en}(\underline{T'})(R)
+&= \Gr_{en}(\underline{T'}) (R\otimes_{k} k')\\
+&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k')} \mathbb{W}(R\otimes_{k} k')\right)\\
+&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k')} \mathbb{W}(R) \otimes_{\mathbb{W}(k)} \mathbb{W}(k')\right)\\
+&= (\underline{T'})\left( \mathcal{O}_{K'} /\mathfrak{p}_{K'}^{en} \otimes_{\mathbb{W}(k)} \mathbb{W}(R)\right).
 \end{aligned}
 \]
-So the group isomorphism 
-\[
-\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)(R) \to \Res_{k'/k} \Gr_{en}(\TTp)(R)
-\]
-is apparent, as are the commuting group homomorphisms
+So the ring isomorphism 
+\[
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R) \to \Res_{k'/k} \Gr_{en}(\underline{T'})(R)
+\]
+is apparent, as are the commuting ring homomorphisms
 \[
 \begin{tikzcd}
-\arrow{d} \Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)(R) \arrow{r}{\iso} & \arrow{d} \Res_{k'/k} \Gr_{en}(\TTp)(R)\\
-\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)(R') \arrow{r}{\iso} & \Res_{k'/k} \Gr_{en}(\TTp)(R'),
+\arrow{d} \Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R) \arrow{r}{\iso} & \arrow{d} \Res_{k'/k} \Gr_{en}(\underline{T'})(R)\\
+\Gr_{n}\left( \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})\right)(R') \arrow{r}{\iso} & \Res_{k'/k} \Gr_{en}(\underline{T'})(R'),
 \end{tikzcd}
@@
 Let $K'/K$ be a finite Galois extension and
-let $k'/k$ be the corresponding extension of residue fields.
+let $k'/k$ be the corresponding finite Galois extension of residue fields.
 Let $T$ be an algebraic torus over $K$ and 
@@
 Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} to lft-Néron models
-we see that $\Res_{\OKp/\OK}(\TTp)$ is a Néron model for $\Res_{K'/K}(T')$.
+we see that a Néron model for $\Res_{K'/K}(T')$ is $\Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$;
+see also the proof of \cite{xarles:93a}*{Lemma 2.6}.
 By the Néron mapping property, the canonical closed immersion
-$T\hookrightarrow \Res_{K'/K}(T')$ extends uniquely to a morphism
-$\underline{T}\to \Res_{\OKp/\OK}(\TTp)$ of smooth $\OK$-group schemes.
+$T\hookrightarrow \Res_{K'/K}(T')$ extends, uniquely, to a morphism
+$\underline{T}\to \Res_{\mathcal{O}_{K'}/\OK}(\underline{T'})$ of smooth $\OK$-group schemes.
 Applying the Greenberg transform $\Gr_{n}$ to this morphism
@@
 
-The techniques in this paper apply to all non-archimdean local fields $K$ with residue field $k$
+The techniques in this paper apply to all non-archimdean local fields $K$ with residue field $k$,
 and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$
-or on the ramification of $T$. We may therefore ask if for a comparison of
-quasicharacter sheaves on $T$ and on $T'$ whenever there is a relationship
-between characters of $T(K)$ and of $T'(K')$.
-Such a relationship can exist between characters of $T(K)$ and $T'(K')$ even
-when the characteristics of $K$ and $K'$ differ
-\citelist{\cite{chai-yu:01a} \cite{deligne:84a}*{\S 1}}.
+or on the ramification of $T$. Because of this, it is natural to ask if we can compare
+quasicharacter sheaves on $T$ and on $T'$ under conditions when there is a
+natural comparison between characters of $T(K)$ and of $T'(K')$.
+This comparison of has been made precise in \cite{chai-yu:01a}, 
+building on ideas in \cite{deligne:84a}*{\S 1}.
 
@@
 $N' \leq N$, the isomorphism \eqref{transfer} is depth-preserving at integers less than $N$.
-In this section we show that the isomorphism \eqref{transfer} comes from an equivalence of
+In this section we ask if the isomorphism \eqref{transfer} comes from an equivalence of
 categories of quasicharacter sheaves on $\GN{T}_n$ and those on $\GN{T}'_n$.
@@
 
-We have given a functorial relationship between quasicharacter sheaves 
+This paper has shown how quasicharacter sheaves 
 on the Greenberg transform of the Néron model of $T$ 
-and admissible characters of $T(K)$.
+determine admissible characters of $T(K)$, and vice versa, functorially.
 When coupled with the reciprocity map $\text{rec}_T $ for $T$, 
@@
 it follows that quasicharacter sheaves for $T$ 
-functorially correspond to Langlands parameters for $T$.
+determine Langlands parameters for $T$, and vice versa, functorially.
 We suspect that it is possible to extract Langlands parameters 
@@
  by the class field theory of Serre-Hazewinkel
- \citelist{\cite{serre:60a} \cite{serre:61a} \cite{demazure-gabriel:GroupesAlgebriques}*{Appendice}},
+ \cite{serre:60a},\cite{serre:61a},\cite{demazure-gabriel:GroupesAlgebriques}*{Appendice},
  especially as revisited in \cite{suzuki-yoshida:12a}*{\S 2}. 

### 2013-10-04 shanghai.tex
Manually resolved some conflicts

--- 2013-10-04 shanghai.tex
@@
 
-Let $\Frob{\Fq}$ denote the geometric Frobenius element in $\Gal(\bFq/\Fq)$ as
+Let $\Frob{}$ denote the geometric Frobenius element in $\Gal(\bFq/\Fq)$ as
 well as the corresponding automorphism of $\Spec{\bFq}$. The Weil group
-$\Weil{\Fq}\subset \Gal(\bFq/\Fq)$ is the subgroup generated by $\Frob{\Fq}$.
-Let $\Frob{G} \ceq \id_{G} \times \Frob{\Fq}$ be the Frobenius automorphism of $\bG$.
+$\Weil{\Fq}\subset \Gal(\bFq/\Fq)$ is the subgroup generated by $\Frob{}$.
+Let $\Frob{G} \ceq \id_{G} \times \Frob{}$ be the Frobenius automorphism of $\bG$.
 When no other fields play a role we will write $\Frob{}$ and $\Weil{}$ instead.
@@
 and the value of $\Nm^*(t_G(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
-Applying \ref{CS.2} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, F(x), \ldots, F^{n-1}(x))$ yields a diagram
+Applying \ref{CS.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
 \[
@@
 bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
-for $v_i \in \gqcs{L}_{F^i(x)}$.  By \ref{CS.1}, $v$ maps to
+for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{CS.2}, $v$ maps to
 $v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
@@
 \begin{proof}
-Set $H_m \ceq H\times_G(G\times G)$, write $f_m : H_m \to G \times G$ for the pullback of $f$ to $H_m$, and let $A$ and $A_m$ be the kernels of $f$ and $f_m$ respectively.
-Consider the diagram of Lemma~\ref{lemma:finite-pullback}:
+We will prove the proposition by finding a weak isomorphism 
+$m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ in $C_1(G\times G)$ 
+and showing that, after passing from $C_1(G\times G)$ to 
+$\QCf(G\times G)$, the resulting isomorphism, 
+denoted by $\mu(f,\psi)$, is canonically determined by $(f,\psi)$.
+
+Set $H_m \ceq H\times_G(G\times G)$, 
+write $f_m : H_m \to G \times G$ for the pullback of $f$ to $H_m$, 
+and let $A$ and $A_m$ be the kernels of $f$ and $f_m$ respectively.  Consider the diagram of Lemma~\ref{lemma:finite-pullback}:
 \[
@@
   commutes, for all $x,y,z\in G(\bFq)$; and
-
- \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
+ \labitem{(cs.3)}{cs.3} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
   such that
@@
   $\tau_\qcs{L}(\Frob{})$ to $G(k)$ is just $\trFrob{\qcs{L}}$.
-  In general, Conditions~\ref{cs.0} and \ref{cs.2}, together with \eqref{section}, guarantee that
+  In general, \ref{cs.1} and \ref{cs.3}, together with \eqref{section}, guarantee that
   the scalar $\tau_\qcs{L}(\Frob{})(x)$ is non-zero.  Moreover, Condition~\ref{cs.1} forces
@@
   For each $x \in G(\bFq)$ set $a(x) = \frac{s_2(x)}{s_1(x)}$.  Then \eqref{section} and
-  condition~\ref{cs.1} together imply $a(x+y) = a(x)a(y)$, so
-  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{} \to G(\bFq)^*$
+  \ref{cs.2} together imply $a(x+y) = a(x)a(y)$, so
+  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
   defined by $\tau_0(\Frob{}) \ceq \,^{\Frob{}} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
@@
   by $\alpha_x(s(x)) = a(x) s'(x)$.
-  By the second part of condition~\ref{cs.3},
+  By the second part of \ref{cs.4},
   $a(x+y) = a(x)a(y)$, so $a \in G(\bFq)^*$. By the first part of
-  condition~\ref{cs.3}, $\tau'(\Frob{}) = \tau(\Frob{}) \cdot (\,^{\Frob{}^{-1}}a \cdot a^{-1})$,
+  \ref{cs.4}, 
+  $\tau'(\Frob{}) = \tau(\Frob{}) \cdot (\,^{\Frob{}^{-1}}a \cdot a^{-1})$,
   %\Clifton{Fix this.}
@@
  $\mu_{x,y}(1) \ceq 1\otimes1$, for $x,y\in G(\bFq)$; 
- clearly, $\mu$ satisfies condition~\ref{cs.1}.
+ clearly, $\mu$ satisfies condition~\ref{cs.2}.
  Define $\phi_x : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_x(1) \ceq \tau(\Frob{})(x)$,
  for each $x\in G(\bFq)$. 
- Then $\phi$ satisfies condition~\ref{cs.2} because $\tau \in Z^1(\Weil{},G(\bFq)^*)$.
+ Then $\phi$ satisfies condition~\ref{cs.3} because $\tau \in Z^1(\Weil{},G(\bFq)^*)$.
  Setting $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$, we have that $[\tau]$ is the image of $\qcs{L}$

### 2013-10-04 shanghai.tex
Working on Section 7

@@
 \newcommand{\EE}{\mathbb{\bar Q}_\ell}
+\newcommand{\Zl}{\mathbb{\bar Z}_\ell}
 \newcommand{\OK}{\mathcal{O}_K}
@@
 \newcommand{\EEx}{\EE^\times}
+\newcommand{\Zlx}{\mathbb{\bar Z}_\ell^\times}
 
@@
 
+When $G$ is connected, we may apply the classic sheaf--function dictionary.  In order to do so,
+however, we must relate our notion of quasicharacter sheaf to the sheaf side of the standard dictionary.
+Choose any $\Fq$-rational point of $G$ and let $\bg$ be the geometric point on $G$ lying above $g$.
+Recall that the \emph{Weil group} of $G$, which we will denote by $\W(G,\bg)$, is a subgroup of the \'etale
+fundamental group defined by the following diagram:
+\[
+ \begin{tikzcd}
+ 1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \W(G,\bg) \rar \dar[hook] & \Weil{} \rar \dar[hook] & 1 \\
+ 1 \rar &  \pi_1(\bG, \bg) \rar & \pi_1(G,\bg) \rar & \Gal(\bFq/\Fq) \rar & 1.
+ \end{tikzcd}
+\]
+The $\Fq$-rational point $g$ under the geometric point $\bg$ determines a splitting
+$\Weil{}\to \W(G,\bg)$ of $\W(G,\bg)\to \Weil{}$.
+
+For connected groups, the subcategories introduced in the previous two sections agree with $\QC(G)$:
+
 \begin{proposition}\label{prop:connected}
@@
   the full subcategories $\QCf(G) \hookrightarrow \QCb(G) \hookrightarrow \QC(G)$ 
-  appearing in Sections~\ref{sec:bounded} and \ref{sec:finite} are equivalences 
-  and
-  \[
-  \trFrob{G} : \QCiso{G} \to G(\Fq)^*
-  \]
-  is an isomorphism of groups.
+  appearing in Sections~\ref{sec:bounded} and \ref{sec:finite} are equivalences.
 \end{proposition}
@@
 
-  Let $g$ be any $\Fq$-rational point on $G$ 
-  and let $\bg$ be the geometric point on $G$ lying above $g$ 
   Since $G$ is connected, the geometric point $\bg$ determines
   an equivalence between the category of $\ell$-adic Weil local systems on $G$ and
-  $\ell$-adic representations of $\W(G,\bg)$ \cite{deligne:80a}*{1.1.12}.  \David{We should include a definition for $\W(G,\bg)$, perhaps in an intro paragraph for the section}
+  $\ell$-adic representations of $\W(G,\bg)$ \cite{deligne:80a}*{1.1.12}.
   Now let $(\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$ 
   and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$.
-  The $\Fq$-rational point $g$ under the geometric point $\bg$ determines a splitting
-  $\Weil{}\to \W(G,\bg)$ of $\W(G,\bg)\to \Weil{}$. 
-  In this way the Weil local system $(\gqcs{L},\phi)$ determines an $\ell$-adic character $\rho_g : \Weil{} \to \EEx$.
-  %\[
-  %\begin{tikzcd}
-  %1 \rar & \pi_1(\bG, \bg) \rar &  \arrow{d}{\rho} \W(G,\bg) \rar
-  %& \ar[swap,bend right, dotted]{l}{g} \arrow[dotted]{dl}{\rho_g} \Weil{} \rar & 1\\
-  %&&\EEx&&
-  %\end{tikzcd}
-  %\]
-  This character is given by the trace of Frobenius of $\qcs{L}$ at $g$, as defined in Section~\ref{sec:Frob}:
+  Composing with the splitting $\Weil{} \to \W(G,\bg)$ yields an $\ell$-adic character
+  $\rho_g : \Weil{} \to \EEx$, which is the same as the trace of Frobenius defined in Section~\ref{sec:Frob}:
   \[
@@
   \]
-  \David{It's not clear to me whether we've just proven this claim or if we're citing it from somewhere}
 
@@
   Thus, $\rho_g$ extends to an $\ell$-adic character of $\Gal(\bFq/\Fq)$, 
-  denoted by the same symbol, below.
-  \[
-  \begin{tikzcd}
-  1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \W(G,\bg) \rar \dar & \Weil{} \arrow[bend left]{rr}{\rho_g} \rar \dar & 1 & \EEx\\
-  1 \rar &  \pi_1(\bG, \bg) \rar & \pi_1(G,\bg) \rar & \Gal(\bFq/\Fq) \arrow[dotted]{rru} \rar & 1 &
-  \end{tikzcd}
-  \]
+  which we will also denote $\rho_g$.
 
@@
   to an $\ell$-adic character $\pi_1(G,\bg) \to \EEx$ using the canonical topological group homomorphism
-  $\pi_1(G,\bg) \to \Gal(\bFq/\Fq)$ determined by the structure map for $G$. But $\bg$ also
+  $\pi_1(G,\bg) \to \Gal(\bFq/\Fq)$. But $\bg$ also
   determines an equivalence between the category of $\ell$-adic
@@
   Then $b_G^*\qcs{L}_0 \iso \gqcs{L}$.
-  Since $b_G^*$ is full and faithful (again, see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII}
-  or even \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}),
+  Since $b_G^*$ is full and faithful
+  \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}},
   $
@@
   it follows that $L_G$ is an equivalence.
-
-  To finish the proof of Proposition~\ref{prop:connected}, it suffices to observe that the group homomorphism
-  $
+\end{proof}
+
+\begin{corollary}
+ If $G$ is a connected, commutative algebraic group over $\Fq$ then
+ \[
   \trFrob{G} : \QCiso{G} \to G(\Fq)^*
-  $
+ \]
+ is an isomorphism of groups.
+\end{corollary}
+\begin{proof}
+ It suffices to observe that the group homomorphism
+ $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$
  is surjective because each character $\chi \in G(\Fq)^*$ determines a finite quasicharacter

### 2013-10-04 shanghai.tex
Fixing some 'Define blah, where x'

@@
 \tableofcontents
-\David{Search for terms defined after they are used}
-\David{Commas between adjectives, consistent ordering}
 
@@
 see, in particular, \cite{SGA5}*{Expos\'e VI,\S 2}, where pullback and tensor products are developed.
-We also make extensive use of the external tensor product of $\ell$-adic sheaves, defined as follows: if $\mathcal{F}$ and $\mathcal{G}$ are constructible $\ell$-adic sheaves on schemes $X$ and $Y$, respectively, then $\mathcal{F}\boxtimes \mathcal{G} \ceq p_X^* \mathcal{F} \otimes p_Y^*\mathcal{G}$, where $p_X : X\times Y\to X$ and $p_Y : X\times Y \to Y$ are projections.
+We also make extensive use of the external tensor product of $\ell$-adic sheaves, defined as follows: if $\mathcal{F}$ and $\mathcal{G}$ are constructible $\ell$-adic sheaves on schemes $X$ and $Y$ and $p_X : X\times Y\to X$ and $p_Y : X\times Y \to Y$ are the projections, then $\mathcal{F}\boxtimes \mathcal{G} \ceq p_X^* \mathcal{F} \otimes p_Y^*\mathcal{G}$.
 
@@
  Now we introduce a faithful functor $L$ from $C(G)$ to the category of local systems on $G$, which we will denote by $\Loc(G)$.
- For any object $(f,\psi)$ in $C(G)$, let $L(f,\psi)$ be the $\psi$-isotypic component of $f_* V_H$, 
- where $V_H$ refers to $V$ as a constant sheaf on $H$. 
+ If $V$ is a $\EE$-vector space then we write $V_H$ for the constant sheaf $V$ on $H$.
+ For any object $(f,\psi)$ in $C(G)$, let $L(f,\psi)$ be the $\psi$-isotypic component of $f_* V_H$.
  We may identify the stalk $(f_* V_H)_{\bar g}$ of $f_* V_H$ at a geometric point ${\bar g}$ on $G$ 
@@
 \section{Commutative \'etale group schemes} \label{sec:etale}
-\Clifton{Use: Etale $\QC$-schemes?}
 %\input{etale-1}
@@
 \begin{lemma}\label{lemma:section}
- If $\qcs{L}$ is a quasicharacter sheaf on a commutative, \'etale group scheme $G$
- \Clifton{Use: Etale $\QC$-schemes?}
- over $\Fq$ and if $G(\bFq)$ is finitely generated, then $\qcs{L}$ has a nontrivial global section.
+ If $\qcs{L}$ is a quasicharacter sheaf on an \'etale $\QC$-scheme $G$ then $\qcs{L}$ has a nontrivial global section.
 \end{lemma}
@@
 \begin{proposition}\label{prop:etale}
-  Let $G$ be a commutative \'etale group scheme over $\Fq$ with $G(\bFq)$ finitely generated.
-  \Clifton{Use: Etale $\QC$-schemes?}
+  Let $G$ be an \'etale $\QC$-scheme.
   We may associate a $1$-cocycle $\tau_\qcs{L}: \Weil{}\to G(\bFq)^*$ to each $\qcs{L} \in \QC(G)$
@@
   $\tau_\qcs{L}(\Frob{})(x+y) = \tau_\qcs{L}(\Frob{})(x) \ \tau_\qcs{L}(\Frob{})(y)$
-  for all $x,y \in G(\bFq)$.  Now define $\tau_\qcs{L} : \Weil{} \to G(\bFq)^*$ recursively by
+  for all $x,y \in G(\bFq)$.  We write $\cdot$ for pointwise multiplication of functions, and
+  define $\tau_\qcs{L} : \Weil{} \to G(\bFq)^*$ recursively by
   \[
@@
   \]
-  where $\Frob{}$ acts on $G(\bFq)^*$ through pre-composition and $\cdot$ refers
-  to pointwise multiplication of functions.
+  where $\Frob{}$ acts on $G(\bFq)^*$ through pre-composition.
 

### 2013-10-04 shanghai.tex
Fixing definition 13.2

@@
 \begin{definition}\label{def:catGN}
-An object in $\QC(\GN{T})$ is an equivalence class in 
-$\cup_{n\in\ZZ_{>0}} \obj \QC(\GN{T}_n)$.
-We say that $\qcs{L}_n\in \QC(\GN{T}_n)$ is equivalent to $\qcs{L}_{m}\in \QC(\GN{T}_m)$ 
-if there is some $k \ge m,n$ with $f_{n\leq k}^* \qcs{L}_{n} = f_{m\leq k}^* \qcs{L}_m$. \David{is it okay for this to be equality rather than isomorphism?} 
-Objects in $\QC(\GN{T})$ all take the form
-\[
-[\qcs{L}_n] \ceq \{ f_{n\leq k}^* \qcs{L}_n \tq n\leq k\},
-\]
-for some unique $\qcs{L}_n \in \QC(\GN{T}_n)$.
-A morphism $[\qcs{L}_n] \to [\qcs{L}_m]$ in $\QC(\GN{T})$ is an equivalence class
-in $\cup_{n,m\leq k} \Hom(f_{n\leq k}^*\qcs{L}_n,f_{m\leq k}^*\qcs{L}_m)$.
-We say that $\alpha_k\in \mor \QC(\GN{T}_k)$ is equivalent to 
-$\beta_l \in \mor \QC(\GN{T}_l)$ if there is some $i \ge k, l$ with $f_{k\leq i}^*\alpha_k = f_{l\leq i}^* \beta_l$. 
-Morphisms in $\QC(\GN{T})$ all take the form
-\[
-[\alpha_k] \ceq \{ f_{k\leq i}^* \alpha_k \tq k\leq i\},
-\]
-for some unique $\alpha_k \in \QC(\GN{T}_k)$.
-Identities and composition are defined in the natural way.
-We may define a tensor structure for $\QC(\GN{T})$ by setting
-\[
-[\qcs{L}_n]\otimes [\qcs{L}_m] \ceq [f_{n\leq k}^*\qcs{L}_n \otimes f_{m\leq k}^*\qcs{L}_m],
-\qquad k \ceq \max\{ n,m\}.
-\]
-Duals in $\QC(\GN{T})$ are defined by $[\qcs{L}_n]^\vee \ceq [\qcs{L}_n^\vee]$.
+An object in $\QC(\GN{T})$ is a triple $(n, \{\qcs{L}_i\}_{i \ge n}, \{\alpha_{i \le j}\}_{j \ge i \ge n})$, where $n$
+is a positive integer, each $\qcs{L}_i$ is a quasicharacter sheaf on $\GN{T}_i$ and each
+$\alpha_{i \le j} : \qcs{L}_j \to f^*_{i \le j} \qcs{L}_i$ is an isomorphism.  We require $\alpha_{i \le i}$ to be
+the identity and that the $\alpha_{i \le j}$ are compatible with each other.  If $\qcs{L} \ceq (n, \{\qcs{L}_i\}, \{\alpha_{i \le j}\})$
+and $\qcs{L}' \ceq (m, \{\qcs{L}'_i\}, \{\alpha'_{i \le j}\})$ are objects then $\Hom(\qcs{L}, \qcs{L}')$ is the set
+of equivalence classes of pairs $(k, \{\beta_i\}_{i \ge k})$.  Here $k \ge m, n$ and the $\beta_i : \qcs{L}_i \to \qcs{L}'_i$ are
+morphisms of quasicharacter sheaves so that
+\[
+\begin{tikzcd}
+\qcs{L}_j \rar{\alpha_j} \dar{\beta_i} & f^*_{i \le j} \qcs{L}_i \dar{f_{i \le j}^*\beta_j} \\
+\qcs{L}'_j \rar{\alpha_j} & f^*_{i \le j} \qcs{L}'_i
+\end{tikzcd}
+\]
+commutes for all $j \ge i \ge k$.  We identify two such pairs $(k, \{\beta_i\})$ and $(l, \{\gamma_i\})$ if $\beta_i = \gamma_i$
+for sufficiently large $i$.  Identities and composites are defined in the natural way.
+
+If $n$ is a positive integer and $\qcs{L}_n \in \QC(\GN{T}_n)$ then we may define an object
+\[
+[\qcs{L}_n] \ceq (n, \{f_{n \le i} \qcs{L}_n\}_{i \ge n}, \{1_{\qcs{L}_j}\}_{j \ge i \ge n}).
+\]
+Every object in $\QC(\GN{T})$ is isomorphic to such a $[\qcs{L}_n]$.  Similarly, any morphism is equal to one of the form
+\[
+[\beta_k] \ceq (k, \{f_{k \le i}^* \beta_k\}_{i \ge k}).
+\]
+
+We may define a tensor product on $\QC(\GN{T})$ by setting
+\[
+ \qcs{L} \otimes \qcs{L}' \ceq (k, \{\qcs{L}_i \otimes \qcs{L}'_i\}, \{\alpha_{i \le j} \otimes \alpha'_{i \le j}\}),
+\]
+where $k = \max(m, n)$.
+Similarly, the dual of an object $\qcs{L}$ is defined by $\qcs{L}^\vee \ceq (n, \{\qcs{L}_i^\vee\}, \{ \alpha_{i \le j}^\vee \})$.
 We refer to objects in the rigid monoidal category 
@@
 \begin{proof}
-We may define full and faithful functors $F_n : \QC(\GN{T}_n) \to \QC(\GN{T})$ for each $n$ by $F_n(\qcs{L}) \ceq [\qcs{L}_n]$ and $F_n(\alpha_n) \ceq [\alpha_n]$.
+We may define full and faithful functors $F_n : \QC(\GN{T}_n) \to \QC(\GN{T})$
+for each $n$ by $F_n(\qcs{L}) \ceq [\qcs{L}_n]$ and $F_n(\alpha_n) \ceq [\alpha_n]$. \David{Conflict of notation: we've defined $F_1$ and $F_2$ twice}
 For positive integers $n \le m$ these functors fit together into a diagram
@@
 Weil restriction, as in \cite{yu:09a}*{Thm 7.5 (2)}. 
-The next proposition \David{Do we mean Lem 14.1 or Prop 14.2?} shows that the category of quasicharacter sheaves for 
+The next lemma shows that the category of quasicharacter sheaves for 
 algebraic tori does indeed behave properly with regard to Weil restriction.

### 2013-10-05 shanghai.tex
Extensive reconstruction of Section 6 on finite quasicharacter sheaves.
I liked your use of alpha in Section 13 for sheaf homs, so I took
alphas out of section 6 where they were scheme homs.

@@
 
-\newcommand{\cdef}[1]{ {#1}\index{#1} } 
+\newcommand{\cdef}[1]{{#1}\index{#1}} 
 \newcommand{\sheafHom}{{\mathscr{H}\hskip-4pt{\it o}\hskip-2pt{\it m}}}
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:BG}
 Extension of scalars defines a full and faithful functor 
-$B_G^* : \QCb(G) \hookrightarrow \QC(G)$.
+$B_G : \QCb(G) \hookrightarrow \QC(G)$.
 \end{proposition}
@@
  Moreover, $\phi$ is compatible with $\mu$ in the sense of \ref{CS.3}.
- This construction defines the functor $B_G^* : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
+ This construction defines the functor $B_G : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
  and also shows that it is full and faithful.
@@
 In general, $\QCb(G)$ is an essentially
-proper subcategory of $\QC(G)$. We will identify $\QCb(G)$ with its image under $B_G^*$
+proper subcategory of $\QC(G)$. We will identify $\QCb(G)$ with its image under $B_G$
 and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ is \emph{bounded}
-if it is isomorphic to some $B_G^*(\qcs{L}_0, \mu_0)$.
+if it is isomorphic to some $B_G(\qcs{L}_0, \mu_0)$.
 We will see in Corollary~\ref{cor:bounded-and-finite} that the bounded quasicharacter sheaves
@@
 
-A morphism $f : H\to G$ of $\QC$-schemes is a \emph{discrete isogeny} if it is a finite, surjective
-\'etale morphism of commutative group $\Fq$-schemes for which
-the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f$ is trivial.
+The definition of finite quasicharacter sheaves will require several steps, 
+beginning with the localization of a category introduced here.
+\Clifton{Do you think it's clear that a morphism of $\QC$-schemes is, in particular, a morphism of group schemes?}
+Let us say that a morphism $f : H\to G$ of $\QC$-schemes is a \emph{discrete isogeny} if it is finite, surjective and etale and the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f \ceq f^{-1}({\bar e)}$ is trivial.
 % similar nomenclature is employed in \cite{kamgarpour:09a}*{\S 2.2}. 
@@
 \begin{itemize}
-\item $f : H\to G$ is a discrete isogeny,
+\item $f : H\to G$ is a discrete isogeny of $\QC$-schemes,
 \item $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$.
 \end{itemize}
-A morphism $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(\alpha,T)$, where
+A morphism $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(g,T)$, where
 \begin{itemize}
-\item $\alpha : H' \to H$ is a morphism of schemes such that $f' = f\circ \alpha$,
-\item $T : V\to V'$ is a linear transformation equivariant for the action of
+\item $g : H' \to H$ is a morphism of schemes such that $f' = f\circ g$,
+\item $T : V\to V'$ is a linear transformation, equivariant for the action of
 $\ker f'$ on $V'$ by $\psi'$ and the action of $\ker f'$ on $V$ by $\psi \circ \alpha$.
@@
 V \arrow{d}{T} & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} & \arrow[equal]{d} G\\
-V' & \Aut(V') & \arrow[swap]{l}{\psi'} \arrow[swap]{u}{\alpha\vert_{\ker f'}} \ker f' \arrow[hook]{r} & \arrow[swap]{u}{\alpha} H' \arrow{r}{f'} & G
+V' & \Aut(V') & \arrow[swap]{l}{\psi'} \arrow[swap]{u}{g\vert_{\ker f'}} \ker f' \arrow[hook]{r} & \arrow[swap]{u}{g} H' \arrow{r}{f'} & G
 \end{tikzcd}
@@
 \end{itemize}
-We say that $(\alpha,T)$ in $C(G)$ is a \emph{weak isomorphism} if $\alpha$ is surjective
-and $T$ is an isomorphism of vector spaces.
-
-Let \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at weak isomorphisms.
- Morphisms in $C(G)[W^{-1}]$ are simple to describe because 
- $W$ is a left multiplicative system in the sense of
-  \cite{kashiwara-schapira:CatgoriesSheaves}*{\S 7.1.7}:
-a morphism in $C(G)[W^{-1}]$ is the equivalence class of 
-  \begin{equation}\label{eq:morGCf}
-   \begin{tikzcd}
-   (f,\psi) \arrow{r}{(\alpha_1,T_1)} & (f_1,\psi_1) & \arrow[swap]{l}{(\beta_1,U_1)} (f',\psi')
-   \end{tikzcd}
-  \end{equation}
- where $(\alpha',T') : (f,\psi) \to (f',T')$ is any map in $C(G)$ 
- and $(\beta_1,U_1) : (f_1,\psi_1) \to (f',\psi')$ is a weak isomorphism in $C(G)$.
-See \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16} for more detail, including the equivalence relation mentioned above.
 
@@
 These operations give $C(G)$ the structure of a tensor category.
-Likewise, $C(G)[W^{-1}]$ is a tensor category.
+
+Now we localize $C(G)$.
+Let us say that $(g,T)$ in $C(G)$ is a \emph{weak isomorphism} if $g$ is surjective
+and $T$ is an isomorphism of vector spaces.
+\Clifton{Should this be another lemma in this section?}
+The set $W$ of weak isomorphisms in $C(G)$
+is a saturated, left multiplicative system in $C(G)$ in the sense of
+  \cite{kashiwara-schapira:CatgoriesSheaves}*{Defs 7.1.5, 7.1.19}.
+Let \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at $W$.
+A morphism in $C(G)[W^{-1}]$ is an equivalence class of a diagram
+  \begin{equation}\label{eq:morGCf}
+   \begin{tikzcd}[column sep=50]
+   (f,\psi) \arrow{r}{(g_1,T_1)} & (f_1,\psi_1) & \arrow[swap]{l}{(h_1,U_1)} (f',\psi')
+   \end{tikzcd}
+  \end{equation}
+ where $(g',T') : (f,\psi) \to (f',\psi')$ is any map in $C(G)$ 
+ and $(h_1,U_1) :  (f',\psi') \to (f_1,\psi_1)$ is a weak isomorphism in $C(G)$; see \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16} for more detail, including the equivalence relation mentioned above.
+%Likewise, $C(G)[W^{-1}]$ is a tensor category.
+
+\begin{definition}
+Let $C_1(G)$ be the full, rigid monoidal subcategory of $C(G)$ consisting of objects
+$(f,\psi)$ such that $\psi$ is a one-dimensional representation.
+%
+The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\QCf(G)$,
+is the rigid monoidal category obtained by localizing $C_1(G)$ at weak isomorphisms.
+\end{definition}
+
+Having defined finite quasicharacter sheaves, 
+we justify our terminology by showing $\QCf(G)$ is a full subcategory of $\QCb(G)$.
+To prepare for that result, we need two lemmas.
 
 \begin{lemma}\label{lemma:finite-pullback}
-Let $g : J \to G$ be a morphism of group schemes. 
+Let $g : J \to G$ be a morphism of $\QC$-schemes. 
 Let $f_g : H\times_G J\to J$
@@
 \begin{proof}
-The key point is that pullback along $g$ takes isogenies to isogenies,
+The key point is that pullback along $g$ takes discrete isogenies to discrete isogenies,
 and maps over $G$ to maps over $J$, as pictured below.
@@
 
-Let $C_1(G)$ be the full, rigid monoidal subcategory of $C(G)$ consisting of objects
-$(f,\psi)$ such that $\psi$ is a one-dimensional representation.
-
-\begin{definition}
-The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\QCf(G)$,
-is the rigid monoidal category obtained by localizing $C_1(G)$ at weak isomorphisms.
-\end{definition}
-
 \begin{lemma}\label{lemma:finite-iso}
-Each $(f,\psi)$ in $\QCf(G)$ determines a canonical isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$. 
+Each finite quasicharacter sheaf $(f,\psi)$ in $\QCf(G)$ determines a canonical isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$. 
  \end{lemma}
@@
  To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \QCf(G) \to \QCb(G)$.
- %
- We will do this by constructing a faithful monoidal functor $L : C_1(G) \to \QCb(G)$ 
- such that $L(\alpha,T)$ is an isomorphism precisely when $(\alpha,T)$ is a weak isomorphism. 
- Factoring along $C_1(G) \to \QCb(G)$ will produce the full and faithful monoidal functor we seek.
-
- Now we introduce a faithful functor $L$ from $C(G)$ to the category of local systems on $G$, which we will denote by $\Loc(G)$.
- If $V$ is a $\EE$-vector space then we write $V_H$ for the constant sheaf $V$ on $H$.
- For any object $(f,\psi)$ in $C(G)$, let $L(f,\psi)$ be the $\psi$-isotypic component of $f_* V_H$.
+
+ If $V$ is a finite-dimensional $\EE$-vector space then we write $V_H$ for the constant sheaf $V$ on $H$.
+If $(f,\psi)$ is a finite quasicharacter on $G$ where $\psi$ is a representation of $\ker f$ on $V$, 
+let $L(f,\psi)$ be the local system on $G$ given by the $\psi$-isotypic component of the local system $f_* V_H$ on $G$.
  We may identify the stalk $(f_* V_H)_{\bar g}$ of $f_* V_H$ at a geometric point ${\bar g}$ on $G$ 
@@
  $s(a\cdot {\bar h}) = \psi(a)(s({\bar h}))$ for all $a\in \ker f$ and for all ${\bar h} \in f^{-1}({\bar g})$.
- Since $L(f,\psi)$ is trivialized by $f$, it is a local system on $G$.
- For any map $(\alpha,T)$ in $C(G)$, let $L(\alpha,T) : L(f,\psi) \to L(f',\psi')$ be the homomorphism of local systems defined 
- %at geometric points $L(\alpha,T)_{\bar g} : L(f,\psi)_{\bar g} \to L(f',\psi')_{\bar g}$ 
- by $s \mapsto s' \ceq T\circ s\circ \alpha$. 
- This construction defines a monoidal functor $L$ from $C(G)$ to $\Loc(G)$ that
- commutes with pullback along any morphism of group schemes.
-
- We now show that $L$ takes weak isomorphisms in $C(G)$ to isomorphisms in $\Loc(G)$. 
- Suppose $(\beta,U) : (f,\psi)\to (f',\psi')$ is a weak isomorphism. 
- Since $U$ is an isomorphism, we may replace $V'$ with $V$ and $U$ with $\id_V$, without loss of generality. 
- Then the equivariance condition on $U$ becomes $\psi' = \psi\circ \beta$ on the finite \'etale group scheme $\ker f'$. 
- Since $f$ and $f'$ are finite \'etale, the relation $f' = f\circ \beta$ implies that $\beta$ is \'etale.  Since $\beta$ is surjective,
- it is an \'etale cover and thus admits a section $\beta' : H \to H'$. \David{Why do \'etale covers have sections?}
- This provides the inverse to $L(\beta,U) : L(f,\psi) \to L(f',\psi')$. \David{What is the inverse of $L(\beta, U)$?}
-
- Conversely, if $L(\alpha,T)$ is an isomorphism of local systems, 
- then $T$ must be an isomorphism of vector spaces and $\beta$ must be surjective, \David{I assume that this statement follows directly from the definition of isomorphisms of local systems?}
- whence $(\alpha,T)$ is a weak isomorphism: $W$ is saturated. \David{It's not clear to me how the claim that $W$ is saturated fits into the rest of this paragraph}
-
- Since $L : C(G) \to \Loc(G)$ takes weak isomorphisms to isomorphisms,
- it factors through the localization functor $C(G) \to C(G)[W^{-1}]$ 
- to define a faithful functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$. 
- Since $W$ is saturated, the functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$ is full.
+
+ For any map $(g,T)$ in $C(G)$, let $L(g,T) : L(f,\psi) \to L(f',\psi')$ be the homomorphism of local systems defined 
+ by $s \mapsto s' \ceq T\circ s\circ g$. 
+ This construction defines a full monoidal functor $L$ from $C(G)$ to the category $\Loc(G)$ of local systems on $G$ that
+ commutes with pullback along any morphism of $\QC$-schemes,
+ as defined using Lemma~\ref{lemma:finite-pullback}.
+ %
+ \Clifton{There's detail missing here; I might want to include some of it.}
+ %
+ Moreover, since $L(f,T)$ is an isomorphism of local systems
+ if and only if $(f,T)$ is a weak isomorphism, 
+ the full functor $L : C(G) \to \Loc(G)$ factors through the localization functor $C(G) \to C(G)[W^{-1}]$ 
+ to define a full and faithful functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$;
+ see \cite{kashiwara-schapira:CatgoriesSheaves}*{Exercise 7.5}.
 
@@
 For general $G$, there are bounded quasicharacter sheaves which are not finite.  Identifying
-$\QCf(G)$ with its image under $B_G^* \circ L_G$, we will see in Corollary~\ref{cor:bounded-and-finite} that
+$\QCf(G)$ with its image under $B_G \circ L_G$, as defined in Proposition~\ref{prop:BG} and in the proof of Proposition~\ref{prop:bounded}, we will see in Corollary~\ref{cor:bounded-and-finite} that
 a quasicharacter sheaf is finite if and only if its trace of Frobenius has finite image.

### 2013-10-06 shanghai.tex
Fixing some margin notes

@@
 geometric component group of $G$ is finitely generated.  This last condition is only
-needed in the proof of Lemma \ref{lemma:section}.
+needed in the proof of Lemma \ref{lemma:section}.  A morphism of $\QC$-schemes is a morphism
+of group schemes over $\Fq$.
 
@@
 beginning with the localization of a category introduced here.
-\Clifton{Do you think it's clear that a morphism of $\QC$-schemes is, in particular, a morphism of group schemes?}
-Let us say that a morphism $f : H\to G$ of $\QC$-schemes is a \emph{discrete isogeny} if it is finite, surjective and etale and the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f \ceq f^{-1}({\bar e)}$ is trivial.
+Let us say that a morphism $f : H\to G$ of $\QC$-schemes is a \emph{discrete isogeny}
+if it is finite, surjective and \'etale and the action of $\Gal(\bFq/\Fq)$ on the \'etale group
+scheme $\ker f \ceq f^{-1}({\bar e)}$ is trivial.
 % similar nomenclature is employed in \cite{kamgarpour:09a}*{\S 2.2}. 
@@
 \begin{enumerate}
-\item[$F_1$:] $T \mapsto \QCiso{\GN{T}}$
-\item[$F_2$:] $T \mapsto \Hom_{\text{qc}}(T(K),\EEx)$
+\item[$F_{\QC}$:] $T \mapsto \QCiso{\GN{T}}$
+\item[$F_{\text{qc}}$:] $T \mapsto \Hom_{\text{qc}}(T(K),\EEx)$
 \end{enumerate}
@@
 We may define full and faithful functors $F_n : \QC(\GN{T}_n) \to \QC(\GN{T})$
-for each $n$ by $F_n(\qcs{L}) \ceq [\qcs{L}_n]$ and $F_n(\alpha_n) \ceq [\alpha_n]$. \David{Conflict of notation: we've defined $F_1$ and $F_2$ twice}
+for each $n$ by $F_n(\qcs{L}) \ceq [\qcs{L}_n]$ and $F_n(\alpha_n) \ceq [\alpha_n]$.
 For positive integers $n \le m$ these functors fit together into a diagram

### 2013-10-06 shanghai.tex
Working on Corollary 10.3

@@
 \begin{enumerate}
-\item $\qcs{L}$ is bounded if and only if $\trFrob{L}$ has bounded image,
-\item $\qcs{L}$ is finite if and only if $\trFrob{L}$ has finite image.
+\item $\qcs{L}$ is bounded if and only if $\trFrob{\qcs{L}}$ has bounded image,
+\item $\qcs{L}$ is finite if and only if $\trFrob{\qcs{L}}$ has finite image.
 \end{enumerate}
@@
 \begin{proof}
-\David{These examples need to be modified to provide a proof of the corollary}
+We first reduce to the case that $G$ is an \'etale $\QC$-scheme.  On the connected component
+$G^0$, all quasicharacter sheaves are bounded and finite by Proposition~\ref{prop:connected}.
+On the other hand, $G^0(\Fq)$ is finite by Lemma~\ref{lem:G0alg-grp} and thus $\trFrob{\qcs{L}}$ has
+both finite and bounded image.  \David{Explain how we can conclude for $G$ from $G^0$ and $\pi_0(G)$.}
+
+So suppose that $\qcs{L}$ is a bounded quasicharacter sheaf on an \'etale $\QC$-scheme $G$.
+If $\bg$ is a geometric point lying above $g \in G(\Fq)$ then the restriction of $\qcs{L}$ to $\bg$
+determines a character of $\pi_1(g, \bg) \cong \Gal(\bFq/\Fq)$.  Since $\Gal(\bFq/\Fq)$ is compact
+the image of $\Frob{}$ under this character lies within $\Zlx$; equivalently $\trFrob{\qcs{L}}(g) \in \Zlx$.
+Since $g$ was arbitrary, the image of $\trFrob{\qcs{L}}$ is bounded.
+
+Conversely, suppose that $\trFrob{\qcs{L}}$ is bounded.   We may choose a geometric point $\bg$ in each
+component $C$ of $G$ and construct a local system on the component by constructing a character of
+$\pi_1(C, \bg)$.  \David{How do we construct this character when $C$ has no rational points?}  These
+local systems piece together to form a sheaf $\qcs{L}_0$ on $G$ since the components form a disjoint
+open cover of $G$.  Since the base change of $\qcs{L}_0$ to $\bG$ is just $\qcs{L}$, we may pull
+back the isomorphism $\mu$ to obtain an isomorphism
+$\mu_0 : m^* \qcs{L}_0 \to \qcs{L}_0 \boxtimes \qcs{L}_0$.
+
+\David{Still need the analogous constructions for finite quasicharacter sheaves.}
+
+\David{I've left the example here for now so that we can raid material from it.}
 Consider the case when $G$ is the discrete \'etale group scheme $\ZZ$; 

### 2013-10-06 shanghai.tex
Minor improvements to Section 6.

@@
 A morphism in $C(G)[W^{-1}]$ is an equivalence class of a diagram
-  \begin{equation}\label{eq:morGCf}
-   \begin{tikzcd}[column sep=50]
-   (f,\psi) \arrow{r}{(g_1,T_1)} & (f_1,\psi_1) & \arrow[swap]{l}{(h_1,U_1)} (f',\psi')
-   \end{tikzcd}
-  \end{equation}
- where $(g',T') : (f,\psi) \to (f',\psi')$ is any map in $C(G)$ 
- and $(h_1,U_1) :  (f',\psi') \to (f_1,\psi_1)$ is a weak isomorphism in $C(G)$; see \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16} for more detail, including the equivalence relation mentioned above.
+%  \begin{equation}\label{eq:morGCf}
+\[   
+\begin{tikzcd}[column sep=30]
+   (f,\psi) \arrow{r}{(g,T)} & (f',\psi') & \arrow[swap]{l}{(h,U)} (f_1,\psi_1)
+   \end{tikzcd}
+\]
+%  \end{equation}
+ where $(g,T) : (f,\psi) \to (f',\psi')$ is any map in $C(G)$ 
+ and $(h,U) :  (f',\psi') \to (f_1,\psi_1)$ is a weak isomorphism in $C(G)$; see \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16} for more detail, including the equivalence relation mentioned above.
 %Likewise, $C(G)[W^{-1}]$ is a tensor category.
@@
 
-For general $G$, there are bounded quasicharacter sheaves which are not finite.  Identifying
+On general $\QC$-schemes $G$, there are bounded quasicharacter sheaves which are not finite.  Identifying
 $\QCf(G)$ with its image under $B_G \circ L_G$, as defined in Proposition~\ref{prop:BG} and in the proof of Proposition~\ref{prop:bounded}, we will see in Corollary~\ref{cor:bounded-and-finite} that

### 2013-10-07 shanghai.tex
Addressed the flag in Section 7.

@@
 %\[\pi_1(G,{\bar e}) \to \Pi_\text{et}(G) \to \Pi_\text{et}(G)_{\Gal(\bFq/\Fq)} = \Pi_\text{disc}(G)\]
-This discussion demonstrates that the category of discrete isogenies to $G$ is a Galois category
-\cite{grothendieck:SGA1}*{Expos\'e V, \S 4}. Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$
-\cite{kamgarpour:09a}*{App'x B}, this \David{What does ``this'' refer to} provides an alternate proof that
-$\QCiso{G} \iso G(\Fq)^*$ when $G$ is a connected algebraic group over $\Fq$.
+This demonstrates that the category of discrete isogenies to $G$ is a Galois category,
+in the sense of \cite{grothendieck:SGA1}*{Expos\'e V, \S 4}. 
+\Clifton{Is this better?}
+Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$ \cite{kamgarpour:09a}*{App'x B}, 
+the fundamental functor attached to this Galois category can be used to produce an equivalence
+between the category of finite quasicharacter sheaves on $G$ and
+the category of one-dimensional representations of $G(\Fq)^*$, thus
+providing an alternate proof that $\QCiso{G} \iso G(\Fq)^*$ 
+when $G$ is a connected algebraic group over $\Fq$.
 
@@
 
+\Clifton{The finitely generated part of the hypothesis is unnecessary.}
 \begin{lemma} \label{lem:dual-inv}

### 2013-10-07 shanghai.tex
Other small improvement to the prose in Section 7.

@@
 context of this paper, where $G$ is a $\QC$-scheme, to which we now return. 
-In this generality, neither of the full subcategories $\QCf(G) \subset \QCb(G) \subset \QC(G)$ are equivalences;
+In this generality, however, neither of the full subcategories $\QCf(G) \subset \QCb(G) \subset \QC(G)$ are equivalences;
 see the end of Section~\ref{sec:snake}.
 Nevertheless, every quasicharacter sheaf $(\gqcs{L},\mu,\phi)$ on $G$ 
-determines a Weil sheaf $(\gqcs{L},\phi)$ on $G$. 
-So, if we choose a geometric point ${\bar g}_x$ in each component $\bG^x$ of $G$, then this choice can be used to convert 
+determines a Weil sheaf $(\gqcs{L},\phi)$ on $G$
+so if we choose a geometric point ${\bar g}_x$ in each component $\bG^x$ of $G$ 
+then this choice can be used to convert 
 the Weil sheaf $(\gqcs{L},\phi)$ into an $\ell$-adic character of $\prod_{x\in \pi_0(\bG)}\W(\bG^x, {\bar g}_x)$. 
-However, it proved cumbersome to manage various 
+However, it seemed cumbersome to manage various 
 choices of families of base points and track the action 

### 2013-10-08 shanghai.tex
QC in title to Section 10?
Replaced three instances of \Weil{\Fq} with \Weil{}.  Fixed a typo. Added a flag. Tried but failed to fix the Yu citation.
I'm still working on the theorem in Section 10.

@@
 % !TEX encoding = UTF-8 Unicode
-\documentclass[11pt]{amsart}
+\documentclass[10pt]{amsart}
 \title[Sheaf--function dictionary for local tori]{A sheaf--function dictionary for algebraic tori over local fields}
@@
 \usepackage[utf8]{inputenc}
-\renewcommand{\baselinestretch}{1.2}
+%\renewcommand{\baselinestretch}{1.2}
 %\usepackage[notcite]{showkeys}
 \usepackage{hyperref}
-\usepackage{geometry}
+%\usepackage{geometry}
 \usepackage{amsthm}
@@
 of quasicharacter sheaves in this case.  Using a notion of global sections for quasicharacter sheaves,
-we give isomorphisms between $\QCiso{G}$, $\Hh^1(\Weil{\Fq}, \Hom(G(\bFq), \EEx))$ and $\Hom(G(\Fq), \EEx)$.
+we give isomorphisms between $\QCiso{G}$, $\Hh^1(\Weil{}, \Hom(G(\bFq), \EEx))$ and $\Hom(G(\Fq), \EEx)$.
 In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
@@
 well as the corresponding automorphism of $\Spec{\bFq}$. The Weil group
-$\Weil{\Fq}\subset \Gal(\bFq/\Fq)$ is the subgroup generated by $\Frob{}$.
+$\Weil{}\subset \Gal(\bFq/\Fq)$ is the subgroup generated by $\Frob{}$.
 Let $\Frob{G} \ceq \id_{G} \times \Frob{}$ be the Frobenius automorphism of $\bG$.
@@
   and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{L}_0,b_{G\times G}^*\mu_0)$ in $\QC(G)$.
-  Thus, the full and faithful functor $B_G^* : \QCb(G) \to \QC(G)$ from Section~\ref{sec:bounded}
+  Thus, the full and faithful functor $B_G : \QCb(G) \to \QC(G)$ from Section~\ref{sec:bounded}
   is also essentially surjective, hence an equivalence.
@@
   Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$. 
-  Then $\qcs{L}\ceq B_G^*(\qcs{L}_0,\mu_0)$ is a quasicharacter sheaf on $G$.
+  Then $\qcs{L}\ceq B_G(\qcs{L}_0,\mu_0)$ is a quasicharacter sheaf on $G$.
   Recall the definition of the character $\trFrob{\qcs{L}} : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}. 
@@
  sheaf $(\Lang,\chi^{-1})$ such that the trace of Frobenius of the quasicharacter sheaf
- $B_G^* (L_G(\Lang,\chi^{-1}))$ is $\chi$.
+ $B_G (L_G(\Lang,\chi^{-1}))$ is $\chi$.
 \end{proof}
@@
   \ref{cs.2} together imply $a(x+y) = a(x)a(y)$, so
-  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
+  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{} \to G(\bFq)^*$
   defined by $\tau_0(\Frob{}) \ceq \,^{\Frob{}} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
@@
 
-\section{The sheaf--function dictionary for non-connected groups}
+\section{The sheaf--function dictionary for $\QC$-schemes}
 \label{sec:snake}
@@
 where $k = \max(m, n)$.
-Similarly, the dual of an object $\qcs{L}$ is defined by $\qcs{L}^\vee \ceq (n, \{\qcs{L}_i^\vee\}, \{ \alpha_{i \le j}^\vee \})$.
+Similarly, the dual of an object $\qcs{L}$ is defined by 
+\[
+\qcs{L}^\vee \ceq (n, \{\qcs{L}_i^\vee\}, \{ \alpha_{i \le j}^\vee \}).
+\]
 We refer to objects in the rigid monoidal category 
@@
 and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$
-or on the ramification of $T$. We may therefore ask if for a comparison of
+or on the ramification of $T$. 
+\Clifton{Fix this.}
+We may therefore ask if for a comparison of
 quasicharacter sheaves on $T$ and on $T'$ whenever there is a relationship
@@
 from quasicharacter sheaves directly and that the reciprocity map 
-can then be be viewed as a matching between quasicharacters and Langlands parameters coming
+can then be viewed as a matching between quasicharacters and Langlands parameters coming
  from the same quasicharacter sheaf. 

### 2013-10-08 shanghai.tex
CS.# |--> QC.#

@@
 % !TEX encoding = UTF-8 Unicode
-\documentclass[10pt]{amsart}
+\documentclass[11pt]{amsart}
 \title[Sheaf--function dictionary for local tori]{A sheaf--function dictionary for algebraic tori over local fields}
@@
 \usepackage[utf8]{inputenc}
-%\renewcommand{\baselinestretch}{1.2}
+\renewcommand{\baselinestretch}{1.2}
 %\usepackage[notcite]{showkeys}
 \usepackage{hyperref}
-%\usepackage{geometry}
+\usepackage{geometry}
 \usepackage{amsthm}
@@
 \begin{enumerate}
-\labitem{(CS.1)}{CS.1} $\gqcs{L}$ is a rank~one $\ell$-adic local system on $\bG$, by which we mean
+\labitem{(QC.1)}{QC.1} $\gqcs{L}$ is a rank~one $\ell$-adic local system on $\bG$, by which we mean
 a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces; 
-\labitem{(CS.2)}{CS.2} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
+\labitem{(QC.2)}{QC.2} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
   where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
@@
 %
-\labitem{(CS.3)}{CS.3} $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$ is an
+\labitem{(QC.3)}{QC.3} $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$ is an
   isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with $\mu$ in the sense that the following diagram commutes.
@@
 \begin{enumerate}
-\labitem{(CS.4)}{CS.4} if $\qcs{L} = (\gqcs{L},\mu,\phi)$ and
+\labitem{(QC.4)}{QC.4} if $\qcs{L} = (\gqcs{L},\mu,\phi)$ and
   $\qcs{L'} = (\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$ then
@@
 The isomorphism $\mu : \bm^* \gqcs{L} \to \LxL$ together with 
-\ref{CS.3} guarantee
+\ref{QC.3} guarantee
 that the function $\trFrob{\qcs{L}} : G(\Fq)\to \EEx$ is a group homomorphism.  If we write
@@
   $\bH^j$. To complete the proof that $\bf^*\gqcs{L}$ satisfies 
-  \ref{cs.4}
+  \ref{qc.4}
   simply observe that $\bf^*\gqcs{L}$ has rank~one since 
@@
 
-  To see that $(\bfxf)^* \mu$ satisfies \ref{CS.2}, 
+  To see that $(\bfxf)^* \mu$ satisfies \ref{QC.2}, 
   apply the functor $(\bfxf)^*$
-  to \ref{CS.2} for $\qcs{L}$ and use the canonical isomorphism
+  to \ref{QC.2} for $\qcs{L}$ and use the canonical isomorphism
   $(\bfxf)^*(\LxL) \iso \bf^*\gqcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gqcs{L}$.
   To show that $f^*\qcs{L}$ satisfies 
-  \ref{CS.3}, apply the same functor to \ref{CS.3} for $\qcs{L}$.
+  \ref{QC.3}, apply the same functor to \ref{QC.3} for $\qcs{L}$.
   The fact that $f$ is a morphism of group schemes defined over $\Fq$ then
@@
 
-  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{CS.4} defines the action
+  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{QC.4} defines the action
   of $f^*$ on morphisms of quasicharacter sheaves; arguing as above shows that $f^*$ is
@@
 It is a matter of routine to show that this morphism satisfies 
-\ref{CS.3} as it applies here,
+\ref{qc.3} as it applies here,
 from which it follows that we have exhibited an isomorphism 
@@
 \]
-The commutativity of the diagram (CS.3) for $\phi_{k'}$ 
+The commutativity of the diagram (QC.3) for $\phi_{k'}$ 
 follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
@@
 and the value of $\Nm^*(t_G(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
-Applying \ref{CS.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
+Applying \ref{QC.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
 \[
@@
 bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
-for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{CS.2}, $v$ maps to
+for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{QC.2}, $v$ maps to
 $v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
@@
 equipped with an isomorphism $\mu_0 : m^* \qcs{L}_0 \to \qcs{L}_0 \boxtimes \qcs{L}_0$ 
-satisfying the analogue of \ref{CS.1} on $G$; 
+satisfying the analogue of \ref{QC.1} on $G$; 
 morphisms in $\QCb(G)$ are defined as in the second part of 
-\ref{CS.3}. 
+\ref{QC.3}. 
 This is the category of \emph{bounded quasicharacter sheaves} on $G$. 
@@
  This functor preserves local constancy, so takes local systems to local systems. 
- Set $\mu \ceq b_{G\times G}^*\mu_0$; clearly, this satisfies \ref{CS.2} 
+ Set $\mu \ceq b_{G\times G}^*\mu_0$; clearly, this satisfies \ref{QC.2} 
  with $b_G^*\qcs{L}_0$ playing the role of $\gqcs{L}$.
- Moreover, $\phi$ is compatible with $\mu$ in the sense of \ref{CS.3}.
+ Moreover, $\phi$ is compatible with $\mu$ in the sense of \ref{QC.3}.
  This construction defines the functor $B_G : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
@@
 \begin{enumerate}
- \labitem{(cs.1)}{cs.1} an indexed set of one-dimensional
+ \labitem{(qc.1)}{qc.1} an indexed set of one-dimensional
   $\EE$-vector spaces $\gqcs{L}_x$, as $x$ runs over
@@
 
- \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms
+ \labitem{(qc.2)}{qc.2} an indexed set of isomorphisms
   $\mu_{x,y} : \gqcs{L}_{x+y} \xrightarrow{\iso} \gqcs{L}_{x} \otimes\gqcs{L}_{y}$,
@@
   commutes, for all $x,y,z\in G(\bFq)$; and
- \labitem{(cs.3)}{cs.3} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
+ \labitem{(qc.3)}{qc.3} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
   such that
@@
 \begin{enumerate}
- \labitem{(cs.4)}{cs.4} an indexed set $\alpha_x : \gqcs{L}_x \to \gqcs{L'}_x$
+ \labitem{(qc.4)}{qc.4} an indexed set $\alpha_x : \gqcs{L}_x \to \gqcs{L'}_x$
   of linear transformations such that
@@
   $\tau_\qcs{L}(\Frob{})$ to $G(k)$ is just $\trFrob{\qcs{L}}$.
-  In general, \ref{cs.1} and \ref{cs.3}, together with \eqref{section}, guarantee that
-  the scalar $\tau_\qcs{L}(\Frob{})(x)$ is non-zero.  Moreover, Condition~\ref{cs.1} forces
+  In general, \ref{qc.1} and \ref{qc.3}, together with \eqref{section}, guarantee that
+  the scalar $\tau_\qcs{L}(\Frob{})(x)$ is non-zero.  Moreover, Condition~\ref{qc.1} forces
   $\tau_\qcs{L}(\Frob{})(x+y) = \tau_\qcs{L}(\Frob{})(x) \ \tau_\qcs{L}(\Frob{})(y)$
@@
   For each $x \in G(\bFq)$ set $a(x) = \frac{s_2(x)}{s_1(x)}$.  Then \eqref{section} and
-  \ref{cs.2} together imply $a(x+y) = a(x)a(y)$, so
+  \ref{qc.2} together imply $a(x+y) = a(x)a(y)$, so
   $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{} \to G(\bFq)^*$
@@
   by $\alpha_x(s(x)) = a(x) s'(x)$.
-  By the second part of \ref{cs.4},
+  By the second part of \ref{qc.4},
   $a(x+y) = a(x)a(y)$, so $a \in G(\bFq)^*$. By the first part of
-  \ref{cs.4}, 
+  \ref{qc.4}, 
   $\tau'(\Frob{}) = \tau(\Frob{}) \cdot (\,^{\Frob{}^{-1}}a \cdot a^{-1})$,
@@
  by $\alpha^{-1}_x(s'(x)) \ceq a(x)^{-1} s(x)$, for $x\in G(\bFq)$.
- It is straightforward to check that $\alpha$ satisfies \ref{cs.3}
+ It is straightforward to check that $\alpha$ satisfies \ref{qc.3}
  and that $\alpha^{-1}$ is its inverse. Thus $\qcs{L} \iso \qcs{L'}$ in $\QC(G)$ and \eqref{pich1} is injective.
@@
  $\mu_{x,y}(1) \ceq 1\otimes1$, for $x,y\in G(\bFq)$; 
- clearly, $\mu$ satisfies condition~\ref{cs.2}.
+ clearly, $\mu$ satisfies condition~\ref{qc.2}.
  Define $\phi_x : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_x(1) \ceq \tau(\Frob{})(x)$,
  for each $x\in G(\bFq)$. 
- Then $\phi$ satisfies condition~\ref{cs.3} because $\tau \in Z^1(\Weil{},G(\bFq)^*)$.
+ Then $\phi$ satisfies condition~\ref{qc.3} because $\tau \in Z^1(\Weil{},G(\bFq)^*)$.
  Setting $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$, we have that $[\tau]$ is the image of $\qcs{L}$

### 2013-10-09 shanghai.tex
Made a home for essential exactness at QC(G) in Section 9.
I'm writing up the proof.

@@
 
-Consider the short exact sequence in the category of $\QC$-schemes
-defining the component group scheme for $G$:
-\begin{equation}\label{eq:pi0}
-\begin{tikzcd}
-0 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
-\end{tikzcd}
-\end{equation}
-Since $\pi_0(G)$ is also a $\QC$-scheme, 
-Proposition~\ref{prop:pullback} implies that \eqref{eq:pi0} defines a sequence of functors
-\[
-\begin{tikzcd}
-\QC(0) \rar & \QC(\pi_0(G)) \rar & \QC(G) \rar & \QC(G^0) \rar & \QC(0)
-\end{tikzcd}
-\]
-which induces a sequence of group homomorphisms 
-\[
-\begin{tikzcd}
-\QCiso{0} \rar & \QCiso{\pi_0(G)} \rar & \QCiso{G} \rar & \QCiso{G^0} \rar & \QCiso{0}.
-\end{tikzcd}
-\]
-after passing to isomorphism classes.  It is easy to see that $\QCiso{0}$ is trivial. In Sections~\ref{sec:connected} and \ref{sec:etale} we will find the groups $\QCiso{G^0}$
-and $\QCiso{\pi_0(G)}$ for all $\QC$-schemes, 
-which will allow us to conclude $\QCiso{G} \iso G(\Fq)^*$.
-
 %\section{Products}
@@
 
-%\input{restriction}
-% !TEX encoding = UTF-8 Unicode
-%\subsection*{Restriction to the identity component is surjective}
-
-Let $G^0$ be the connected component of $G$ containing the identity.
-By Proposition~\ref{prop:pullback}, pullback along
-$G^0\hookrightarrow G$ determines a monoidal functor
-$\qcs{L}\mapsto \qcs{L}\vert_{G^0}$ from $\QC(G)$ to $\QC(G^0)$.  In
-this section we show that this functor is essentially surjective.
+Consider the short exact sequence in the category of $\QC$-schemes
+defining the component group scheme for $G$:
+\begin{equation}\label{eq:pi0}
+\begin{tikzcd}
+0 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
+\end{tikzcd}
+\end{equation}
+Since $\pi_0(G)$ is also a $\QC$-scheme, 
+Proposition~\ref{prop:pullback} implies that \eqref{eq:pi0} defines the sequence of functors
+\begin{equation}\label{eq:pi1}
+\begin{tikzcd}
+\QC(0) \rar & \QC(\pi_0(G)) \rar & \QC(G) \rar & \QC(G^0) \rar & \QC(0)
+\end{tikzcd}
+\end{equation}
+and therefore, after passing to isomorphism classes, the sequence of abelian groups 
+\begin{equation}\label{eq:pi2}
+\begin{tikzcd}
+0 \rar & \QCiso{\pi_0(G)} \rar & \QCiso{G} \rar & \QCiso{G^0} \rar & 0.
+\end{tikzcd}
+\end{equation}
+(It is clear that $\QCiso{0}$ is trivial.)
+In this section we show that \eqref{eq:pi2} is exact at $\QCiso{G^0}$ and at $\QCiso{G}$.
+In Section~\ref{sec:snake} we will see that this sequence is also exact at $\QCiso{\pi_0(G)}$ and thus short exact.
+Note that we found the groups $\QCiso{G^0}$
+and $\QCiso{\pi_0(G)}$
+in Sections~\ref{sec:connected} and \ref{sec:etale}.
 
@@
 \begin{proposition}\label{prop:restriction}
-  The restriction functor $\QC(G)\to \QC(G^0)$ is essentially surjective.
+For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf $\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$;
+in particular, the restriction functor $\QC(G)\to \QC(G^0)$ is essentially surjective.
 \end{proposition}
@@
   so to prove the proposition it suffices to show that every 
-  finite quasicharacter sheaf on $G^0$ extends to a quasicharacter sheaf on $G$.
+  finite quasicharacter sheaf on $G^0$ extends to a finite quasicharacter sheaf on $G$.
 
@@
  $(f,\psi)\vert_{G^0} \iso (\pi,\psi)$.
+\end{proof}
+
+\begin{proposition}\label{prop:middleexact}
+Sequence \eqref{eq:pi2} is exact at $\QCiso{G}$.
+\end{proposition}
+
+\begin{proof}
+Suppose $\qcs{L} \in \QC(G)$ and $\qcs{L}\vert_{G^0} \iso (\EE)_{G^0}$.
 \end{proof}
@@
   In order to apply the snake lemma, we need to show that the top row is exact at $\QCiso{G}$ and $\QCiso{G^0}$.
-  The surjectivity of $\QCiso{G} \to \QCiso{G^0}$ follows from Proposition~\ref{prop:restriction}.  Now suppose that
-  $\qcs{L}$ is a quasicharacter sheaf on $G$ whose restriction to $G^0$ is trivial.... \David{Missing argument, discussed this afternoon}
-
+  The surjectivity of $\QCiso{G} \to \QCiso{G^0}$ follows from Proposition~\ref{prop:restriction}.  The top row is also exact at $\QCiso{G}$ by Proposition~\ref{prop:middleexact}
+%  
   Now Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}

### 2013-10-09 shanghai.tex
FIxed a mistake I made a moment ago; asked a question in Section 10.

@@
 In this section we show that \eqref{eq:pi2} is exact at $\QCiso{G^0}$ and at $\QCiso{G}$. 
-In Section~\ref{sec:snake} we will see that this sequence is also exact at $\QCiso{\pi_0(G)}$ and thus short exact.
 Note that we found the groups $\QCiso{G^0}$
@@
 
-  In order to apply the snake lemma, we need to show that the top row is exact at $\QCiso{G}$ and $\QCiso{G^0}$.
-  The surjectivity of $\QCiso{G} \to \QCiso{G^0}$ follows from Proposition~\ref{prop:restriction}.  The top row is also exact at $\QCiso{G}$ by Proposition~\ref{prop:middleexact}
+  In order to apply the snake lemma, we need to show that the top row is exact at $\QCiso{G}$ and $\QCiso{G^0}$:
+  the surjectivity of $\QCiso{G} \to \QCiso{G^0}$ follows from Proposition~\ref{prop:restriction} while exactness at $\QCiso{G}$ is given by Proposition~\ref{prop:middleexact}.
 %  
@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:exact}
 Suppose that
@@
 \]
-is an exact sequence of $\QC$-schemes and that $\Hh^1(\Fq, A) = 0$.  Then pullback yields an exact sequence
+is an exact sequence of $\QC$-schemes and that $\Hh^1(\Fq, A) = 0$.  
+\Clifton{$\Hh^1(\Fq, A^*) = 0$?} 
+Then pullback yields an exact sequence
 \[

### 2013-10-09 shanghai.tex
Added a couple of marginal notes.

@@
 
-We say that a section is \emph{trivial} if $s(x) = 0$ for all $x \in G(\bFq)$ and \emph{nontrivial} if $s(x) \ne 0$ for all $x \in G(\bFq)$.
+We say that a section is \emph{trivial} if $s(x) = 0$ for all $x \in G(\bFq)$ 
+\Clifton{Since `nontrivial section' is not the same as not a `trivial section', and since the term `trivial section' is never used below, perhaps there is no need to introduce it.}
+and \emph{nontrivial} if $s(x) \ne 0$ for all $x \in G(\bFq)$.
 
@@
 \end{equation}
-(It is clear that $\QCiso{0}$ is trivial.)
-In this section we show that \eqref{eq:pi2} is exact at $\QCiso{G^0}$ and at $\QCiso{G}$. 
+%(It is clear that $\QCiso{0}$ is trivial.)
  Note that we found the groups $\QCiso{G^0}$
@@
 in Sections~\ref{sec:connected} and \ref{sec:etale}.
+In this section we show that \eqref{eq:pi2} is right exact.
 
@@
   descends to a diagram of $\Fq$-schemes since the $\bFq$-points of
-  the objects come equipped with continuous $\Weil{}$-actions, and the
+  the objects come equipped with \Clifton{?} continuous $\Weil{}$-actions, and the
   morphisms are $\Gamma$-equivariant.
@@
 \begin{proposition}\label{prop:middleexact}
-Sequence \eqref{eq:pi2} is exact at $\QCiso{G}$.
+ The sequence 
+ \[
+  \begin{tikzcd}
+  0 \rar & \QCiso{\pi_0(G)} \rar & \QCiso{G} \rar & \QCiso{G^0} \rar & 0.
+  \end{tikzcd}
+ \]
+ is exact at $\QCiso{G}$.
 \end{proposition}
@@
 
-We saw, in Proposition~\ref{prop:functorialG}, that the trace of Frobenius
+We saw in Proposition~\ref{prop:functorialG} that the trace of Frobenius
 $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
-In fact, trace of Frobenius is an isomorphism when $G$ is a $\QC$-scheme.
+We will now show that trace of Frobenius is an isomorphism.
 
@@
   If $G$ is a smooth, commutative group scheme, locally of finite type over
+  \Clifton{For every $\QC$-scheme $G$, the trace of Frobenius is an isomorphism.}
   $\Fq$, and if the abelian group $\pi_0(G)(\bFq)$
@@
 is an exact sequence of $\QC$-schemes and that $\Hh^1(\Fq, A) = 0$.
-\Clifton{$\Hh^1(\Fq, A^*) = 0$?} 
+\Clifton{Could you add a few words about the proof of this corollary?}   
 Then pullback yields an exact sequence

### 2013-10-09 shanghai.tex
Fixing proof of Corollary 10.3

--- 2013-10-09 shanghai.tex
@@
 of quasicharacter sheaves in this case.  Using a notion of global sections for quasicharacter sheaves,
-we give isomorphisms between $\QCiso{G}$, $\Hh^1(\Weil{}, \Hom(G(\bFq), \EEx))$ and $\Hom(G(\Fq), \EEx)$.
+we give isomorphisms between $\QCiso{G}$, $\Hh^1(\Weil{\Fq}, \Hom(G(\bFq), \EEx))$ and $\Hom(G(\Fq), \EEx)$.
 In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
@@
 well as the corresponding automorphism of $\Spec{\bFq}$. The Weil group
-$\Weil{}\subset \Gal(\bFq/\Fq)$ is the subgroup generated by $\Frob{}$.
+$\Weil{\Fq}\subset \Gal(\bFq/\Fq)$ is the subgroup generated by $\Frob{}$.
 Let $\Frob{G} \ceq \id_{G} \times \Frob{}$ be the Frobenius automorphism of $\bG$.
@@
 \begin{enumerate}
-\labitem{(QC.1)}{QC.1} $\gqcs{L}$ is a rank~one $\ell$-adic local system on $\bG$, by which we mean
+\labitem{(CS.1)}{CS.1} $\gqcs{L}$ is a rank~one $\ell$-adic local system on $\bG$, by which we mean
 a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces; 
-\labitem{(QC.2)}{QC.2} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
+\labitem{(CS.2)}{CS.2} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
   where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
@@
 %
-\labitem{(QC.3)}{QC.3} $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$ is an
+\labitem{(CS.3)}{CS.3} $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$ is an
   isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with $\mu$ in the sense that the following diagram commutes.
@@
 \begin{enumerate}
-\labitem{(QC.4)}{QC.4} if $\qcs{L} = (\gqcs{L},\mu,\phi)$ and
+\labitem{(CS.4)}{CS.4} if $\qcs{L} = (\gqcs{L},\mu,\phi)$ and
   $\qcs{L'} = (\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$ then
@@
 The isomorphism $\mu : \bm^* \gqcs{L} \to \LxL$ together with 
-\ref{QC.3} guarantee
+\ref{CS.3} guarantee
 that the function $\trFrob{\qcs{L}} : G(\Fq)\to \EEx$ is a group homomorphism.  If we write
@@
   $\bH^j$. To complete the proof that $\bf^*\gqcs{L}$ satisfies 
-  \ref{qc.4}
+  \ref{cs.4}
   simply observe that $\bf^*\gqcs{L}$ has rank~one since 
@@
 
-  To see that $(\bfxf)^* \mu$ satisfies \ref{QC.2}, 
+  To see that $(\bfxf)^* \mu$ satisfies \ref{CS.2}, 
   apply the functor $(\bfxf)^*$
-  to \ref{QC.2} for $\qcs{L}$ and use the canonical isomorphism
+  to \ref{CS.2} for $\qcs{L}$ and use the canonical isomorphism
   $(\bfxf)^*(\LxL) \iso \bf^*\gqcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gqcs{L}$.
   To show that $f^*\qcs{L}$ satisfies 
-  \ref{QC.3}, apply the same functor to \ref{QC.3} for $\qcs{L}$.
+  \ref{CS.3}, apply the same functor to \ref{CS.3} for $\qcs{L}$.
   The fact that $f$ is a morphism of group schemes defined over $\Fq$ then
@@
 
-  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{QC.4} defines the action
+  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{CS.4} defines the action
   of $f^*$ on morphisms of quasicharacter sheaves; arguing as above shows that $f^*$ is
@@
 \end{proof}
+
+Consider the short exact sequence in the category of $\QC$-schemes
+defining the component group scheme for $G$:
+\begin{equation}\label{eq:pi0}
+\begin{tikzcd}
+0 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
+\end{tikzcd}
+\end{equation}
+Since $\pi_0(G)$ is also a $\QC$-scheme, 
+Proposition~\ref{prop:pullback} implies that \eqref{eq:pi0} defines a sequence of functors
+\[
+\begin{tikzcd}
+\QC(0) \rar & \QC(\pi_0(G)) \rar & \QC(G) \rar & \QC(G^0) \rar & \QC(0)
+\end{tikzcd}
+\]
+which induces a sequence of group homomorphisms 
+\[
+\begin{tikzcd}
+\QCiso{0} \rar & \QCiso{\pi_0(G)} \rar & \QCiso{G} \rar & \QCiso{G^0} \rar & \QCiso{0}.
+\end{tikzcd}
+\]
+after passing to isomorphism classes.  It is easy to see that $\QCiso{0}$ is trivial. In Sections~\ref{sec:connected} and \ref{sec:etale} we will find the groups $\QCiso{G^0}$
+and $\QCiso{\pi_0(G)}$ for all $\QC$-schemes, 
+which will allow us to conclude $\QCiso{G} \iso G(\Fq)^*$.
 
@@
 It is a matter of routine to show that this morphism satisfies 
-\ref{qc.3} as it applies here,
+\ref{CS.3} as it applies here,
 from which it follows that we have exhibited an isomorphism 
@@
 \]
-The commutativity of the diagram (QC.3) for $\phi_{k'}$ 
+The commutativity of the diagram (CS.3) for $\phi_{k'}$ 
 follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
@@
 and the value of $\Nm^*(t_G(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
-Applying \ref{QC.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
+Applying \ref{CS.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
 \[
@@
 bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
-for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{QC.2}, $v$ maps to
+for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{CS.2}, $v$ maps to
 $v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
@@
 equipped with an isomorphism $\mu_0 : m^* \qcs{L}_0 \to \qcs{L}_0 \boxtimes \qcs{L}_0$ 
-satisfying the analogue of \ref{QC.1} on $G$; 
+satisfying the analogue of \ref{CS.1} on $G$; 
 morphisms in $\QCb(G)$ are defined as in the second part of 
-\ref{QC.3}. 
+\ref{CS.3}. 
 This is the category of \emph{bounded quasicharacter sheaves} on $G$. 
@@
  This functor preserves local constancy, so takes local systems to local systems. 
- Set $\mu \ceq b_{G\times G}^*\mu_0$; clearly, this satisfies \ref{QC.2} 
+ Set $\mu \ceq b_{G\times G}^*\mu_0$; clearly, this satisfies \ref{CS.2} 
  with $b_G^*\qcs{L}_0$ playing the role of $\gqcs{L}$.
- Moreover, $\phi$ is compatible with $\mu$ in the sense of \ref{QC.3}.
+ Moreover, $\phi$ is compatible with $\mu$ in the sense of \ref{CS.3}.
  This construction defines the functor $B_G : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
@@
 A morphism in $C(G)[W^{-1}]$ is an equivalence class of a diagram
-%  \begin{equation}\label{eq:morGCf}
-\[   
-\begin{tikzcd}[column sep=30]
-   (f,\psi) \arrow{r}{(g,T)} & (f',\psi') & \arrow[swap]{l}{(h,U)} (f_1,\psi_1)
-   \end{tikzcd}
-\]
-%  \end{equation}
- where $(g,T) : (f,\psi) \to (f',\psi')$ is any map in $C(G)$ 
- and $(h,U) :  (f',\psi') \to (f_1,\psi_1)$ is a weak isomorphism in $C(G)$; see \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16} for more detail, including the equivalence relation mentioned above.
+  \begin{equation}\label{eq:morGCf}
+   \begin{tikzcd}[column sep=50]
+   (f,\psi) \arrow{r}{(g_1,T_1)} & (f_1,\psi_1) & \arrow[swap]{l}{(h_1,U_1)} (f',\psi')
+   \end{tikzcd}
+  \end{equation}
+ where $(g',T') : (f,\psi) \to (f',\psi')$ is any map in $C(G)$ 
+ and $(h_1,U_1) :  (f',\psi') \to (f_1,\psi_1)$ is a weak isomorphism in $C(G)$; see \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16} for more detail, including the equivalence relation mentioned above.
 %Likewise, $C(G)[W^{-1}]$ is a tensor category.
@@
 
-On general $\QC$-schemes $G$, there are bounded quasicharacter sheaves which are not finite.  Identifying
+For general $G$, there are bounded quasicharacter sheaves which are not finite.  Identifying
 $\QCf(G)$ with its image under $B_G \circ L_G$, as defined in Proposition~\ref{prop:BG} and in the proof of Proposition~\ref{prop:bounded}, we will see in Corollary~\ref{cor:bounded-and-finite} that
@@
   and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{L}_0,b_{G\times G}^*\mu_0)$ in $\QC(G)$.
-  Thus, the full and faithful functor $B_G : \QCb(G) \to \QC(G)$ from Section~\ref{sec:bounded}
+  Thus, the full and faithful functor $B_G^* : \QCb(G) \to \QC(G)$ from Section~\ref{sec:bounded}
   is also essentially surjective, hence an equivalence.
@@
   Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$. 
-  Then $\qcs{L}\ceq B_G(\qcs{L}_0,\mu_0)$ is a quasicharacter sheaf on $G$.
+  Then $\qcs{L}\ceq B_G^*(\qcs{L}_0,\mu_0)$ is a quasicharacter sheaf on $G$.
   Recall the definition of the character $\trFrob{\qcs{L}} : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}. 
@@
  sheaf $(\Lang,\chi^{-1})$ such that the trace of Frobenius of the quasicharacter sheaf
- $B_G (L_G(\Lang,\chi^{-1}))$ is $\chi$.
+ $B_G^* (L_G(\Lang,\chi^{-1}))$ is $\chi$.
 \end{proof}
@@
 %\[\pi_1(G,{\bar e}) \to \Pi_\text{et}(G) \to \Pi_\text{et}(G)_{\Gal(\bFq/\Fq)} = \Pi_\text{disc}(G)\]
-This demonstrates that the category of discrete isogenies to $G$ is a Galois category,
-in the sense of \cite{grothendieck:SGA1}*{Expos\'e V, \S 4}. 
-\Clifton{Is this better?}
-Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$ \cite{kamgarpour:09a}*{App'x B}, 
-the fundamental functor attached to this Galois category can be used to produce an equivalence
-between the category of finite quasicharacter sheaves on $G$ and
-the category of one-dimensional representations of $G(\Fq)^*$, thus
-providing an alternate proof that $\QCiso{G} \iso G(\Fq)^*$ 
-when $G$ is a connected algebraic group over $\Fq$.
+This discussion demonstrates that the category of discrete isogenies to $G$ is a Galois category
+\cite{grothendieck:SGA1}*{Expos\'e V, \S 4}. Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$
+\cite{kamgarpour:09a}*{App'x B}, this \David{What does ``this'' refer to} provides an alternate proof that
+$\QCiso{G} \iso G(\Fq)^*$ when $G$ is a connected algebraic group over $\Fq$.
 
@@
 context of this paper, where $G$ is a $\QC$-scheme, to which we now return. 
-In this generality, however, neither of the full subcategories $\QCf(G) \subset \QCb(G) \subset \QC(G)$ are equivalences;
+In this generality, neither of the full subcategories $\QCf(G) \subset \QCb(G) \subset \QC(G)$ are equivalences;
 see the end of Section~\ref{sec:snake}.
 Nevertheless, every quasicharacter sheaf $(\gqcs{L},\mu,\phi)$ on $G$ 
-determines a Weil sheaf $(\gqcs{L},\phi)$ on $G$
-so if we choose a geometric point ${\bar g}_x$ in each component $\bG^x$ of $G$ 
-then this choice can be used to convert 
+determines a Weil sheaf $(\gqcs{L},\phi)$ on $G$. 
+So, if we choose a geometric point ${\bar g}_x$ in each component $\bG^x$ of $G$, then this choice can be used to convert 
 the Weil sheaf $(\gqcs{L},\phi)$ into an $\ell$-adic character of $\prod_{x\in \pi_0(\bG)}\W(\bG^x, {\bar g}_x)$. 
-However, it seemed cumbersome to manage various 
+However, it proved cumbersome to manage various 
 choices of families of base points and track the action 
@@
 \begin{enumerate}
- \labitem{(qc.1)}{qc.1} an indexed set of one-dimensional
+ \labitem{(cs.1)}{cs.1} an indexed set of one-dimensional
   $\EE$-vector spaces $\gqcs{L}_x$, as $x$ runs over
@@
 
- \labitem{(qc.2)}{qc.2} an indexed set of isomorphisms
+ \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms
   $\mu_{x,y} : \gqcs{L}_{x+y} \xrightarrow{\iso} \gqcs{L}_{x} \otimes\gqcs{L}_{y}$,
@@
   commutes, for all $x,y,z\in G(\bFq)$; and
- \labitem{(qc.3)}{qc.3} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
+ \labitem{(cs.3)}{cs.3} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
   such that
@@
 \begin{enumerate}
- \labitem{(qc.4)}{qc.4} an indexed set $\alpha_x : \gqcs{L}_x \to \gqcs{L'}_x$
+ \labitem{(cs.4)}{cs.4} an indexed set $\alpha_x : \gqcs{L}_x \to \gqcs{L'}_x$
   of linear transformations such that
@@
   $\tau_\qcs{L}(\Frob{})$ to $G(k)$ is just $\trFrob{\qcs{L}}$.
-  In general, \ref{qc.1} and \ref{qc.3}, together with \eqref{section}, guarantee that
-  the scalar $\tau_\qcs{L}(\Frob{})(x)$ is non-zero.  Moreover, Condition~\ref{qc.1} forces
+  In general, \ref{cs.1} and \ref{cs.3}, together with \eqref{section}, guarantee that
+  the scalar $\tau_\qcs{L}(\Frob{})(x)$ is non-zero.  Moreover, Condition~\ref{cs.1} forces
   $\tau_\qcs{L}(\Frob{})(x+y) = \tau_\qcs{L}(\Frob{})(x) \ \tau_\qcs{L}(\Frob{})(y)$
@@
   For each $x \in G(\bFq)$ set $a(x) = \frac{s_2(x)}{s_1(x)}$.  Then \eqref{section} and
-  \ref{qc.2} together imply $a(x+y) = a(x)a(y)$, so
-  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{} \to G(\bFq)^*$
+  \ref{cs.2} together imply $a(x+y) = a(x)a(y)$, so
+  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{\Fq} \to G(\bFq)^*$
   defined by $\tau_0(\Frob{}) \ceq \,^{\Frob{}} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
@@
   by $\alpha_x(s(x)) = a(x) s'(x)$.
-  By the second part of \ref{qc.4},
+  By the second part of \ref{cs.4},
   $a(x+y) = a(x)a(y)$, so $a \in G(\bFq)^*$. By the first part of
-  \ref{qc.4}, 
+  \ref{cs.4}, 
   $\tau'(\Frob{}) = \tau(\Frob{}) \cdot (\,^{\Frob{}^{-1}}a \cdot a^{-1})$,
@@
  by $\alpha^{-1}_x(s'(x)) \ceq a(x)^{-1} s(x)$, for $x\in G(\bFq)$.
- It is straightforward to check that $\alpha$ satisfies \ref{qc.3}
+ It is straightforward to check that $\alpha$ satisfies \ref{cs.3}
  and that $\alpha^{-1}$ is its inverse. Thus $\qcs{L} \iso \qcs{L'}$ in $\QC(G)$ and \eqref{pich1} is injective.
@@
  $\mu_{x,y}(1) \ceq 1\otimes1$, for $x,y\in G(\bFq)$; 
- clearly, $\mu$ satisfies condition~\ref{qc.2}.
+ clearly, $\mu$ satisfies condition~\ref{cs.2}.
  Define $\phi_x : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_x(1) \ceq \tau(\Frob{})(x)$,
  for each $x\in G(\bFq)$. 
- Then $\phi$ satisfies condition~\ref{qc.3} because $\tau \in Z^1(\Weil{},G(\bFq)^*)$.
+ Then $\phi$ satisfies condition~\ref{cs.3} because $\tau \in Z^1(\Weil{},G(\bFq)^*)$.
  Setting $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$, we have that $[\tau]$ is the image of $\qcs{L}$
@@
 
-\Clifton{The finitely generated part of the hypothesis is unnecessary.}
 \begin{lemma} \label{lem:dual-inv}
@@
 
-Consider the short exact sequence in the category of $\QC$-schemes
-defining the component group scheme for $G$:
-\begin{equation}\label{eq:pi0}
-\begin{tikzcd}
-0 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
-\end{tikzcd}
-\end{equation}
-Since $\pi_0(G)$ is also a $\QC$-scheme, 
-Proposition~\ref{prop:pullback} implies that \eqref{eq:pi0} defines the sequence of functors
-\begin{equation}\label{eq:pi1}
-\begin{tikzcd}
-\QC(0) \rar & \QC(\pi_0(G)) \rar & \QC(G) \rar & \QC(G^0) \rar & \QC(0)
-\end{tikzcd}
-\end{equation}
-and therefore, after passing to isomorphism classes, the sequence of abelian groups 
-\begin{equation}\label{eq:pi2}
-\begin{tikzcd}
-0 \rar & \QCiso{\pi_0(G)} \rar & \QCiso{G} \rar & \QCiso{G^0} \rar & 0.
-\end{tikzcd}
-\end{equation}
-(It is clear that $\QCiso{0}$ is trivial.)
-In this section we show that \eqref{eq:pi2} is exact at $\QCiso{G^0}$ and at $\QCiso{G}$.
-In Section~\ref{sec:snake} we will see that this sequence is also exact at $\QCiso{\pi_0(G)}$ and thus short exact.
-Note that we found the groups $\QCiso{G^0}$
-and $\QCiso{\pi_0(G)}$
-in Sections~\ref{sec:connected} and \ref{sec:etale}.
+%\input{restriction}
+% !TEX encoding = UTF-8 Unicode
+%\subsection*{Restriction to the identity component is surjective}
+
+Let $G^0$ be the connected component of $G$ containing the identity.
+By Proposition~\ref{prop:pullback}, pullback along
+$G^0\hookrightarrow G$ determines a monoidal functor
+$\qcs{L}\mapsto \qcs{L}\vert_{G^0}$ from $\QC(G)$ to $\QC(G^0)$.  In
+this section we show that this functor is essentially surjective.
 
@@
 \begin{proposition}\label{prop:restriction}
-For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf $\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$;
-in particular, the restriction functor $\QC(G)\to \QC(G^0)$ is essentially surjective.
+  The restriction functor $\QC(G)\to \QC(G^0)$ is essentially surjective.
 \end{proposition}
@@
   so to prove the proposition it suffices to show that every 
-  finite quasicharacter sheaf on $G^0$ extends to a finite quasicharacter sheaf on $G$.
+  finite quasicharacter sheaf on $G^0$ extends to a quasicharacter sheaf on $G$.
 
@@
 
-\begin{proposition}\label{prop:middleexact}
-Sequence \eqref{eq:pi2} is exact at $\QCiso{G}$.
-\end{proposition}
-
-\begin{proof}
-Suppose $\qcs{L} \in \QC(G)$ and $\qcs{L}\vert_{G^0} \iso (\EE)_{G^0}$.
-\end{proof}
-
-\section{The sheaf--function dictionary for $\QC$-schemes}
+\section{The sheaf--function dictionary for non-connected groups}
 \label{sec:snake}
@@
   In order to apply the snake lemma, we need to show that the top row is exact at $\QCiso{G}$ and $\QCiso{G^0}$.
-  The surjectivity of $\QCiso{G} \to \QCiso{G^0}$ follows from Proposition~\ref{prop:restriction}.  The top row is also exact at $\QCiso{G}$ by Proposition~\ref{prop:middleexact}
-%  
+  The surjectivity of $\QCiso{G} \to \QCiso{G^0}$ follows from Proposition~\ref{prop:restriction}.  Now suppose that
+  $\qcs{L}$ is a quasicharacter sheaf on $G$ whose restriction to $G^0$ is trivial.... \David{Missing argument, discussed this afternoon}
+
   Now Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}
@@
 $G^0$, all quasicharacter sheaves are bounded and finite by Proposition~\ref{prop:connected}.
-On the other hand, $G^0(\Fq)$ is finite by Lemma~\ref{lem:G0alg-grp} and thus $\trFrob{\qcs{L}}$ has
-both finite and bounded image.  \David{Explain how we can conclude for $G$ from $G^0$ and $\pi_0(G)$.}
-
-So suppose that $\qcs{L}$ is a bounded quasicharacter sheaf on an \'etale $\QC$-scheme $G$.
-If $\bg$ is a geometric point lying above $g \in G(\Fq)$ then the restriction of $\qcs{L}$ to $\bg$
-determines a character of $\pi_1(g, \bg) \cong \Gal(\bFq/\Fq)$.  Since $\Gal(\bFq/\Fq)$ is compact
-the image of $\Frob{}$ under this character lies within $\Zlx$; equivalently $\trFrob{\qcs{L}}(g) \in \Zlx$.
-Since $g$ was arbitrary, the image of $\trFrob{\qcs{L}}$ is bounded.
-
-Conversely, suppose that $\trFrob{\qcs{L}}$ is bounded.   We may choose a geometric point $\bg$ in each
-component $C$ of $G$ and construct a local system on the component by constructing a character of
-$\pi_1(C, \bg)$.  \David{How do we construct this character when $C$ has no rational points?}  These
-local systems piece together to form a sheaf $\qcs{L}_0$ on $G$ since the components form a disjoint
-open cover of $G$.  Since the base change of $\qcs{L}_0$ to $\bG$ is just $\qcs{L}$, we may pull
-back the isomorphism $\mu$ to obtain an isomorphism
-$\mu_0 : m^* \qcs{L}_0 \to \qcs{L}_0 \boxtimes \qcs{L}_0$.
-
-\David{Still need the analogous constructions for finite quasicharacter sheaves.}
-
-\David{I've left the example here for now so that we can raid material from it.}
-Consider the case when $G$ is the discrete \'etale group scheme $\ZZ$; 
-this is indeed a $\QC$-scheme.
+On the other hand, $G^0(\Fq)$ is finite by Lemma~\ref{lem:G0alg-grp} and thus the trace of Frobenius
+has finite and therefore bounded image.  If $\chi \in G(\Fq)^*$ then there is some finite-image character $\chi_0$
+with the same restriction to $G^0(\Fq)$ since $G^0(\Fq)$ is lies inside the torsion part of
+the finitely generated abelian group $G(\Fq)$.  Therefore $\chi$ will be bounded (have finite image)
+if and only if $\chi \cdot \chi_0^{-1}$ is bounded (has finite image).  But $\chi \cdot \chi_0^{-1}$ descends
+to a character of $\pi_0(G)$.  A similar argument relates boundedness/finiteness of quasicharacter
+sheaves on $G$ to those on $\pi_0(G)$, using the fact that the preimage constructed in the proof of
+Proposition~\ref{prop:restriction} is a finite quasicharacter sheaf on $G$.  Using these equivalences, it is enough to prove the Corollary
+for \'etale $\QC$-schemes.
+
+In the case that $G$ is \'etale, one can easily see whether a quasicharacter sheaf is bounded or finite.
+For $\qcs{L} \in \QC(G)$, recall that a global section is a particular choice of bases for the vector
+spaces $\qcs{L}_x$.  The isomorphisms $\phi_x : \qcs{L}_{\Frob{}(x)} \to \qcs{L}_x$ are then specified
+by a choice of scalars $b_x$.  By \cite{beilinson-bernstein-deligne:81a}*{Rem. 5.2.1},
+$\qcs{L}$ will be bounded if and only if $b_x \in \Zlx$ for all $x$.  Moreover, $\qcs{L}$ will be
+finite if and only if $b_x$ is a root of unity for all $x$.
+Let $z$ be a cocycle representing the image of $\qcs{L}$ under the isomorphism
+$\QCiso{G} \cong \Hh^1(\Weil{}, G(\bFq)^*)$.  Then $z(\Frob{})(x) = b_x$, and the
+map $\Hh^1(\Weil{}, \Hom(G(\bFq), \Zlx)) \to \Hom(G(\Fq), \Zlx)$ is an isomorphism
+since $\Zlx$ is divisible.  So bounded characters of $G(\Fq)$ correspond to quasicharacter sheaves
+$\qcs{L}$ that descend to Weil sheaves on $G$.  The conditions on the values $b_x$ then
+translate into analogous conditions on the image of trace of Frobenius.
+\end{proof}
+
+For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$.
 Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ 
 and let $\qcs{L}$ be a quasicharacter sheaf in the isomorphism class 
-corresponding to the character $\chi : G(\Fq) \to \EEx$ under Theorem~\ref{thm:snake}. 
-Then $\trFrob{\qcs{L}}(1) = \ell$. Suppose $\qcs{L}$ was a bounded quasicharacter sheaf. 
-Then the restriction of $\qcs{L}$ to the connected component $1\in G$ 
-would be a $\ell$-adic local system on $1$ of rank~one, which would provide
-an $\ell$-adic character $\rho_1 : \pi_1(1,{\bar 1}) \to \EEx$ with
-$\rho_1(\Frob{}) = \ell$, necessarily continuous. 
-But $\pi_1(1,{\bar 1}) = \Gal(\bFq/\Fq) \iso {\hat \ZZ}$ is compact, 
-while $\rho_1(\pi_1(1,{\bar 1})) \subseteq \EEx$ is not compact (it contains $\ell^\ZZ$),
-contradicting the continuity of $\rho_1$.
-So the Weil sheaf $\gqcs{L}$ does not descend to a local system on $G$.
-It follows that the quasicharacter sheaf $\qcs{L}$ is not a bounded quasicharacter sheaf.
-%
-We can play the same game with the character $\chi : G(\Fq) \to \EEx$ 
-defined by $\chi(1) = 1+\ell$. In this case, the corresponding quasicharacter sheaf $\qcs{L}$ is bounded,
-defined at $1$ by a pro-\'etale cover of $1$, but not finite, since $1+\ell$ is not a root of unity. 
-\end{proof}
+corresponding to $\chi$ under Theorem~\ref{thm:snake}.
+Then $\qcs{L}$ is not a bounded quasicharacter sheaf since the image of $\chi$ is not
+bounded.  If $\chi(1) = 1+\ell$, then the image of $\chi$ is bounded but not finite.  For
+the corresponding quasicharacter sheaf $\qcs{L}$, the stalk at the component $1$ is defined
+by a pro-\'etale cover rather than an \'etale cover and thus $\qcs{L}$ is not finite.
 
@@
 where $k = \max(m, n)$.
-Similarly, the dual of an object $\qcs{L}$ is defined by 
-\[
-\qcs{L}^\vee \ceq (n, \{\qcs{L}_i^\vee\}, \{ \alpha_{i \le j}^\vee \}).
-\]
+Similarly, the dual of an object $\qcs{L}$ is defined by $\qcs{L}^\vee \ceq (n, \{\qcs{L}_i^\vee\}, \{ \alpha_{i \le j}^\vee \})$.
 We refer to objects in the rigid monoidal category 
@@
 and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$
-or on the ramification of $T$. 
-\Clifton{Fix this.}
-We may therefore ask if for a comparison of
+or on the ramification of $T$. We may therefore ask if for a comparison of
 quasicharacter sheaves on $T$ and on $T'$ whenever there is a relationship
@@
 from quasicharacter sheaves directly and that the reciprocity map 
-can then be viewed as a matching between quasicharacters and Langlands parameters coming
+can then be be viewed as a matching between quasicharacters and Langlands parameters coming
  from the same quasicharacter sheaf. 

### 2013-10-09 shanghai.tex
Removing some marginal comments

@@
 \emph{certain} $\ell$-adic characters of fundamental group $\pi_1(G,{\bar e})$. 
-As explained in \cite{kamgarpour:09a}*{\S~2}, 
+As explained in \cite{kamgarpour:09a}*{\S2}, 
 the relevant characters of $\pi_1(G,{\bar e})$ are precisely those 
@@
 %\[\pi_1(G,{\bar e}) \to \Pi_\text{et}(G) \to \Pi_\text{et}(G)_{\Gal(\bFq/\Fq)} = \Pi_\text{disc}(G)\]
-This demonstrates that the category of discrete isogenies to $G$ is a Galois category,
+Using this fact, one can show that the category of discrete isogenies to $G$ is a Galois category,
 in the sense of \cite{grothendieck:SGA1}*{Expos\'e V, \S 4}. 
-\Clifton{Is this better?}
 Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$ \cite{kamgarpour:09a}*{App'x B}, 
@@
 
-We say that a section is \emph{trivial} if $s(x) = 0$ for all $x \in G(\bFq)$ 
-\Clifton{Since `nontrivial section' is not the same as not a `trivial section', and since the term `trivial section' is never used below, perhaps there is no need to introduce it.}
-and \emph{nontrivial} if $s(x) \ne 0$ for all $x \in G(\bFq)$.
+We say that a section is \emph{nontrivial} if $s(x) \ne 0$ for all $x \in G(\bFq)$.  Note that the only other section is the constant zero section.
 
@@
 
-\Clifton{The finitely generated part of the hypothesis is unnecessary.}
 \begin{lemma} \label{lem:dual-inv}
-Let $X$ be a finitely generated abelian group equipped with an action of $\Weil{}$, and write $\Frob{} = \Frob{}$.  Then
+Let $X$ be an abelian group equipped with an action of $\Weil{}$, and write $\Frob{} = \Frob{}$.  Then
 \begin{align*}
@@
 $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
-We will now show that trace of Frobenius is an isomorphism.
+In fact, trace of Frobenius is an isomorphism when $G$ is a $\QC$-scheme.
 
@@
   If $G$ is a smooth, commutative group scheme, locally of finite type over
-  \Clifton{For every $\QC$-scheme $G$, the trace of Frobenius is an isomorphism.}
   $\Fq$, and if the abelian group $\pi_0(G)(\bFq)$

### 2013-10-10 shanghai.tex
FInished the proof of the new proposition in Section 9.
I'll probably edit it a bit, though, over the next few hours.

@@
 
-\section{Restriction to the identity component} \label{sec:restriction}
+\section{Exactness of the component group sequence} \label{sec:restriction}
 
@@
 \begin{tikzcd}
-0 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
+0 \rar & G^0 \arrow{r}{\iota_0} & G \arrow{r}{\pi_0} & \pi_0(G) \rar & 0.
 \end{tikzcd}
@@
 \begin{tikzcd}
-\QC(0) \rar & \QC(\pi_0(G)) \rar & \QC(G) \rar & \QC(G^0) \rar & \QC(0)
+\QC(0) \rar & \QC(\pi_0(G)) \arrow{r}{\pi_0^*} & \QC(G) \arrow{r}{\iota_0^*} & \QC(G^0) \rar & \QC(0)
 \end{tikzcd}
@@
 \begin{tikzcd}
-0 \rar & \QCiso{\pi_0(G)} \rar & \QCiso{G} \rar & \QCiso{G^0} \rar & 0.
+0 \rar & \QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
 \end{tikzcd}
@@
 For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf $\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$;
-in particular, the restriction functor $\QC(G)\to \QC(G^0)$ is essentially surjective.
+in particular, the restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
 \end{proposition}
@@
   \begin{tikzcd}
-  0 \rar & \QCiso{\pi_0(G)} \rar & \QCiso{G} \rar & \QCiso{G^0} \rar & 0.
+  0 \rar & \QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
   \end{tikzcd}
@@
 \begin{proof}
-Suppose $\qcs{L} \in \QC(G)$ and $\qcs{L}\vert_{G^0} \iso (\EE)_{G^0}$.
-\end{proof}
-
-\section{The sheaf--function dictionary for $\QC$-schemes}
+Suppose $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$ 
+and $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$.
+
+For each $x\in \pi_0(\bG)$, set $\bG^x \ceq \pi_0^{-1}(x)$.
+Let $g, g'$ be geometric points in the same 
+geometric connected component $\bG^x$. 
+Set $a = g^{-1}g'$ and note that $a$ is a geometric point in $\bG^0$. 
+Let $\mu_{g,a} : \gqcs{L}_{ga} \to \gqcs{L}_g \otimes \gqcs{L}_a$ 
+be the isomorphism of vector spaces obtained by restriction of 
+$\mu : m^*\gqcs{L} \to \gqcs{L} \boxtimes \gqcs{L}$ to the 
+geometric point $(g,a)$ on $\bG^x \times \bG^0$. 
+Since $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$, 
+the stalk of $\gqcs{L}$ at $a$ is $\EE$. 
+In this way the pair of geometric points $g, g' \in \bG^x$ 
+determines an isomorphism $\varphi_{g,g'} \ceq \mu_{g,a}^{-1}$ 
+from $\gqcs{L}_{g}$ to $\gqcs{L}_{g'}$.
+
+The isomorphisms $\varphi_{g,g'}: \gqcs{L}_{g} \to \gqcs{L}_{g'}$ are canonical 
+in the following sense: if $g,g'\in \bG^x$ and $h,h'\in \bG^y$ 
+then it follows from \ref{QC.2} and \ref{QC.3} 
+that
+ \begin{equation}\label{eq:qc}
+  \begin{tikzcd}[column sep=60]
+   \gqcs{L}_{gh} \arrow{r}{\varphi_{gh,g'h'}} \arrow[swap]{d}{\mu_{g,h}}
+  & \gqcs{L}_{g'h'} \arrow{d}{\mu_{g',h'}}
+  &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} 
+  &  \gqcs{L}_{\Frob{}(g)} \arrow{r}{\varphi_{\Frob{}(g),\Frob{}(g')}} \arrow[swap]{d}{\phi_{g}} & \gqcs{L}_{\Frob{}(g')} \arrow{d}{\phi_{g'}} \\
+  \gqcs{L}_{g} \otimes \gqcs{L}_{h} \arrow{r}{\varphi_{g,g'}\otimes \varphi_{h,h'}}  
+  & \gqcs{L}_{g'} \otimes \gqcs{L}_{h'} 
+  & {}
+  & \gqcs{L}_{g} \arrow{r}{\varphi_{g,g'}} & \gqcs{L}_{g'}
+  \end{tikzcd}
+ \end{equation}
+both commute.
+
+Now, for each $x\in \pi_0(\bG)$, pick $g_x\in \bG^x$ 
+and set $\gqcs{E}_x \ceq \gqcs{L}_{g_x}$. 
+Let $\phi_x : \gqcs{E}_{\Frob{}(x)} \to \gqcs{E}_x$ 
+be the isomorphism of $\EE$-vector spaces obtained by composing 
+$\varphi_{g_{\Frob{}(x)},\Frob{}(g_x)} : \gqcs{L}_{g_{\Frob{}(x)}} \to \gqcs{L}_{\Frob{}(g_x)}$ 
+with $\phi_{g_x} : \gqcs{L}_{\Frob{}(g_x)} \to \gqcs{L}_{g_x}$. 
+For each pair $x,y\in \pi_0(\bG)$ 
+let $\mu_{x,y} : \gqcs{E}_{x+y}\to \gqcs{E}_x\otimes \gqcs{E}_y$ 
+be the isomorphism of $\EE$-vector spaces obtained by composing
+$\varphi_{g_{x+y},g_xg_y} : \gqcs{L}_{g_{x+y}} \to \gqcs{L}_{g_xg_y}$ 
+with $\mu_{g_x,g_y} : \gqcs{L}_{g_xg_y} \to \gqcs{L}_{g_x}\otimes \gqcs{L}_{g_y}$.
+Using \eqref{eq:qc}, it follows that \ref{qc.1}, \ref{qc.2} and \ref{qc.3} are satisfied for
+\begin{enumerate}
+\item
+the indexed set of one-dimensional $\EE$-vector spaces  $\gqcs{E}_x$, 
+as $x$ runs over $\pi_0(\bG)$,
+\item the indexed set of isomorphisms
+  $\mu_{x,y} : \gqcs{E}_{x+y} \xrightarrow{\iso} \gqcs{E}_{x} \otimes\gqcs{E}_{y}$,
+ as $x$ and $y$ run over $\pi_0(\bG)$,
+ \item the indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$,
+as $x$ runs over $\pi_0(\bG)$.
+\end{enumerate}
+We have now defined a quasicharacter sheaf $\qcs{E}$ on $\pi_0(G)$ 
+from the quasicharacter sheaf $\qcs{L}$ on $G$ 
+with the property $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$.
+
+Now, pullback the quasicharacter sheaf $\qcs{E}$ along $\pi_0 : G \to \pi_0(G)$.
+The resulting quasicharacter sheaf $\pi_0^* \qcs{E}$ is constant 
+on geometric connected components, with stalks given by 
+$(\pi_0^* \qcs{E})_g = \qcs{E}_{x}$ for all $g\in \bG^x$; 
+in particular, $\left(\pi_0^* \qcs{E}\right)\vert_{\bG^x} =  (\qcs{E}_{x})_{\bG^x}$.
+Likewise, the quasicharacter sheaf $\qcs{L}$ is constant 
+on geometric connected components. Our choices above define isomorphisms
+$\gqcs{L}\vert_{\bG^x} \to  (\gqcs{E}_{x})_{\bG^x}$, for each $x\in \pi_0(\bG)$.
+The resulting isomorphism $\gqcs{L} \to \pi_0^* \gqcs{E}$ satisfies \ref{QC.4}, 
+thus defining an isomorphism $\qcs{L} \to \pi_0^* \qcs{E}$.
+
+We have now show that if $\qcs{L}$ is a quasicharacter sheaf on $G$ and $\iota_0^*\qcs{L}= (\EE)_{G^0}$ then there is some quasicharacter sheaf $\qcs{E}$ on $\pi_0(G)$ such that $\qcs{L} \iso \pi_0^* \qcs{E}$.
+On the other hand, $\iota_0^*(\pi_0^* \qcs{E}) \iso (\EE)_{G^0}$, by Proposition~\ref{prop:pullback}.
+This shows that \eqref{eq:pi2} is exact at $\QC(G)$, concluding the proof of Proposition~\ref{prop:middleexact}.
+\end{proof}
+
+\section{The sheaf--function dictionary for non-connected group schemes}
 \label{sec:snake}

### 2013-10-10 shanghai.tex
Small editorial improvemnets.

@@
 on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of
-\cite{deligne:SGA4.5}*{Expos\'e XIII,~1.1}, failing only because $\Weil{}$ is not profinite.
+\cite{deligne:SGA4.5}*{Expos\'e XIII, 1.1}, failing only because $\Weil{}$ is not profinite.
 \Clifton{Improve this.}
@@
 The category $\QC(G)$ of quasicharacter sheaves on $G$ is a rigid monoidal category
-\cite{etingof:09a}*{\S~1.10} under the tensor product
+\cite{etingof:09a}*{\S1.10} under the tensor product
 $\qcs{L} \otimes \qcs{L'} \ceq (\gqcs{L}\otimes\gqcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
@@
   %Using notation from \cite{laumon:87a}*{1.1}, this means $t_{\bullet L(f,\psi)} = t_{\bullet \qcs{L}_0}$.
-  Using \cite{laumon:87a}*{Th\'eor\`eme~1.1.2}, it follows that  $L(f,\psi) \iso \qcs{L}_0$ in $\Loc(G)$.
+  Using \cite{laumon:87a}*{Th\'eor\`eme 1.1.2}, it follows that  $L(f,\psi) \iso \qcs{L}_0$ in $\Loc(G)$.
   It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\qcs{L}_0,\mu_0)$ in $\QCb(G)$.
@@
   In general, \ref{qc.1} and \ref{qc.3}, together with \eqref{section}, guarantee that
-  the scalar $\tau_\qcs{L}(\Frob{})(x)$ is non-zero.  Moreover, Condition~\ref{qc.1} forces
+  the scalar $\tau_\qcs{L}(\Frob{})(x)$ is non-zero.  Moreover, 
+  \ref{qc.1} forces
   $\tau_\qcs{L}(\Frob{})(x+y) = \tau_\qcs{L}(\Frob{})(x) \ \tau_\qcs{L}(\Frob{})(y)$
@@
  $\mu_{x,y}(1) \ceq 1\otimes1$, for $x,y\in G(\bFq)$; 
- clearly, $\mu$ satisfies condition~\ref{qc.2}.
+ clearly, $\mu$ satisfies \ref{qc.2}.
  Define $\phi_x : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_x(1) \ceq \tau(\Frob{})(x)$,
  for each $x\in G(\bFq)$. 
- Then $\phi$ satisfies condition~\ref{qc.3} because $\tau \in Z^1(\Weil{},G(\bFq)^*)$.
+ Then $\phi$ satisfies \ref{qc.3} because $\tau \in Z^1(\Weil{},G(\bFq)^*)$.
  Setting $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$, we have that $[\tau]$ is the image of $\qcs{L}$

### 2013-10-10 shanghai.tex
Adding stuff about localizations and local systems to section 6

@@
 \cite{deligne:SGA4.5}*{Expos\'e XIII, 1.1}, failing only because $\Weil{}$ is not profinite.
-\Clifton{Improve this.}
-As we will see, our use of $\Weil{}$ rather than $\Gal(\bFq/\Fq)$ allows quasicharacter sheaves to
-correspond to unbounded characters.
+As we will see in Corollary~\ref{cor:bounded-and-finite}, our use of $\Weil{}$ rather than $\Gal(\bFq/\Fq)$
+allows quasicharacter sheaves to correspond to unbounded characters.
 
@@
 Let us say that $(g,T)$ in $C(G)$ is a \emph{weak isomorphism} if $g$ is surjective
-and $T$ is an isomorphism of vector spaces.
-\Clifton{Should this be another lemma in this section?}
-The set $W$ of weak isomorphisms in $C(G)$
-is a saturated, left multiplicative system in $C(G)$ in the sense of
-  \cite{kashiwara-schapira:CatgoriesSheaves}*{Defs 7.1.5, 7.1.19}.
-Let \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at $W$.
-A morphism in $C(G)[W^{-1}]$ is an equivalence class of a diagram
+and $T$ is an isomorphism of vector spaces.  Recall from
+\cite{kashiwara-schapira:CatgoriesSheaves}*{Def 7.1.5} that a \emph{left multiplicative system}
+is a family of morphisms $W$ that
+\begin{enumerate}
+\item contains all isomorphisms,
+\item is closed under composition,
+\item is closed under pullback by arbitrary morphisms in $C(G)$,
+\item and if the cokernel \David{Is $C(G)$ abelian?} of a morphism $\phi \in \mor C(G)$ is in
+$W$ then so is the kernel of $\phi$.
+\end{enumerate}
+
+We further say that $W$ is \emph{saturated} if the following property holds for
+morphisms $f, g$ and $h$ that can be composed appropriately:
+whenever $g \circ f$ and $h \circ g$ are in $W$ then so is $h$
+\cite{kashiwara-schapira:CatgoriesSheaves}*{Def 7.1.19}.
+
+\begin{lemma}
+The family of weak isomorphisms in $C(G)$ is a saturated, left multiplicative system.
+\end{lemma}
+\begin{proof}
+Any isomorphism $(g, T)$ in $C(G)$ has both $g$ and $T$ isomorphisms, and thus is a weak isomorphism.
+Clearly, the composition of two weak isomorphisms is a weak isomorphism.  The remaining properties
+follow from the fact that in a weak isomorphism $(g, T)$, $g$ is an \'etale cover, together with standard
+facts on \'etale covers and pullbacks. \David{Is this sufficient?}
+\end{proof}
+Let $W$ be the family of weak isomorphisms and \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at $W$.
+A morphism in $C(G)[W^{-1}]$ is an equivalence class of diagrams
 %  \begin{equation}\label{eq:morGCf}
@@
  where $(g,T) : (f,\psi) \to (f',\psi')$ is any map in $C(G)$ 
- and $(h,U) :  (f',\psi') \to (f_1,\psi_1)$ is a weak isomorphism in $C(G)$; see \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16} for more detail, including the equivalence relation mentioned above.
+ and $(h,U) :  (f',\psi') \to (f_1,\psi_1)$ is a weak isomorphism in $C(G)$ \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16}.
 %Likewise, $C(G)[W^{-1}]$ is a tensor category.
@@
  \end{proof}
+
+To prove the next proposition, we will need a certain perspective on local systems.
+ If $\qcs{E}$ is any local system on a connected scheme $G$ and $\bg$ is a geometric point on $G$,
+ we may associate to $\qcs{E}$ a character of the \'etale fundamental group $\pi_1(G, \bg)$ \David{add citation}.
+ Since $\pi_1(G, \bg)$ is defined as a projective limit of automorphism groups of finite \'etale covers, a general
+ local system will correspond to a projective limit of characters of such groups.  But some local systems can be
+ described in terms of a single cover $f: H \to G$ and a representation $\psi: \ker f \to \Aut(V)$;
+ two such descriptions yield isomorphic local systems if and only if they are related by a weak
+ isomorphism in $C(G)$.  While the description of local systems in terms of $\pi_1(G, \bg)$ does
+ not generalize well to non-connected $G$, the description in terms of $C(G)$ does.  \David{Look okay?}
 

### 2013-10-10 shanghai.tex
Edits to section 9

@@
 \begin{proposition}\label{prop:restriction}
-For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf $\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$;
-in particular, the restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
+For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf
+$\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$.
+As a consequence, the restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
 \end{proposition}
@@
  By Lemma~\ref{lemma:ext}, there is an extension of the 
- discrete isogeny $\pi : B \to G^0$ to a discrete isogeny $f : H \to G^0$ 
+ discrete isogeny $\pi : B \to G^0$ to a discrete isogeny $f : H \to G$ 
  such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
@@
 \begin{proof}
-Suppose $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$ 
-and $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$.
+First note that $\iota_0^* \circ \pi_0^*$ is trivial by Proposition~\ref{prop:pullback}.
+So it suffices to show that if $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$ 
+with $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$ then $\qcs{L}$ is in the essential image of $\pi_0^*$.
 
@@
  \begin{equation}\label{eq:qc}
-  \begin{tikzcd}[column sep=60]
+  \begin{tikzcd}[column sep=55]
    \gqcs{L}_{gh} \arrow{r}{\varphi_{gh,g'h'}} \arrow[swap]{d}{\mu_{g,h}}
@@
 
-Now, for each $x\in \pi_0(\bG)$, pick $g_x\in \bG^x$ 
-and set $\gqcs{E}_x \ceq \gqcs{L}_{g_x}$. 
+For each $x\in \pi_0(\bG)$, pick $g(x)\in \bG^x$ 
+and set $\gqcs{E}_x \ceq \gqcs{L}_{g(x)}$. 
 Let $\phi_x : \gqcs{E}_{\Frob{}(x)} \to \gqcs{E}_x$ 
 be the isomorphism of $\EE$-vector spaces obtained by composing 
-$\varphi_{g_{\Frob{}(x)},\Frob{}(g_x)} : \gqcs{L}_{g_{\Frob{}(x)}} \to \gqcs{L}_{\Frob{}(g_x)}$ 
-with $\phi_{g_x} : \gqcs{L}_{\Frob{}(g_x)} \to \gqcs{L}_{g_x}$. 
+$\varphi_{g(\Frob{}(x)),\Frob{}(g(x))} : \gqcs{L}_{g(\Frob{}(x))} \to \gqcs{L}_{\Frob{}(g(x))}$ 
+with $\phi_{g(x)} : \gqcs{L}_{\Frob{}(g(x))} \to \gqcs{L}_{g(x)}$. 
 For each pair $x,y\in \pi_0(\bG)$ 
@@
 be the isomorphism of $\EE$-vector spaces obtained by composing
-$\varphi_{g_{x+y},g_xg_y} : \gqcs{L}_{g_{x+y}} \to \gqcs{L}_{g_xg_y}$ 
-with $\mu_{g_x,g_y} : \gqcs{L}_{g_xg_y} \to \gqcs{L}_{g_x}\otimes \gqcs{L}_{g_y}$.
+$\varphi_{g(x+y),g(x)g(y)} : \gqcs{L}_{g(x+y)} \to \gqcs{L}_{g(x)g(y)}$ 
+with $\mu_{g(x),g(y)} : \gqcs{L}_{g(x)g(y)} \to \gqcs{L}_{g(x)}\otimes \gqcs{L}_{g(y)}$.
 Using \eqref{eq:qc}, it follows that \ref{qc.1}, \ref{qc.2} and \ref{qc.3} are satisfied for
-\begin{enumerate}
-\item
-the indexed set of one-dimensional $\EE$-vector spaces  $\gqcs{E}_x$, 
-as $x$ runs over $\pi_0(\bG)$,
-\item the indexed set of isomorphisms
-  $\mu_{x,y} : \gqcs{E}_{x+y} \xrightarrow{\iso} \gqcs{E}_{x} \otimes\gqcs{E}_{y}$,
- as $x$ and $y$ run over $\pi_0(\bG)$,
- \item the indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$,
-as $x$ runs over $\pi_0(\bG)$.
-\end{enumerate}
-We have now defined a quasicharacter sheaf $\qcs{E}$ on $\pi_0(G)$ 
-from the quasicharacter sheaf $\qcs{L}$ on $G$ 
-with the property $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$.
-
-Now, pullback the quasicharacter sheaf $\qcs{E}$ along $\pi_0 : G \to \pi_0(G)$.
-The resulting quasicharacter sheaf $\pi_0^* \qcs{E}$ is constant 
+$\qcs{E} \ceq (\gqcs{E}_x, \mu_{x,y}, \phi_x)$, thus defining a quasicharacter sheaf on $\pi_0(G)$.
+
+The pullback $\pi_0^*(\qcs{E})$ of $\qcs{E}$ along $\pi_0 : G \to \pi_0(G)$ is constant 
 on geometric connected components, with stalks given by 
-$(\pi_0^* \qcs{E})_g = \qcs{E}_{x}$ for all $g\in \bG^x$; 
-in particular, $\left(\pi_0^* \qcs{E}\right)\vert_{\bG^x} =  (\qcs{E}_{x})_{\bG^x}$.
-Likewise, the quasicharacter sheaf $\qcs{L}$ is constant 
-on geometric connected components. Our choices above define isomorphisms
-$\gqcs{L}\vert_{\bG^x} \to  (\gqcs{E}_{x})_{\bG^x}$, for each $x\in \pi_0(\bG)$.
+$(\pi_0^* \qcs{E})_g = \qcs{E}_{x}$ for all $g\in \bG^x$.  Thus both $\pi_0^*\qcs{E}$ and $\qcs{L}$
+are constant on geometric connected components of $G$. 
+The choices above define isomorphisms
+$\gqcs{L}\vert_{\bG^x} \to  (\gqcs{E}_{x})_{\bG^x}$ for each $x\in \pi_0(\bG)$.
 The resulting isomorphism $\gqcs{L} \to \pi_0^* \gqcs{E}$ satisfies \ref{QC.4}, 
 thus defining an isomorphism $\qcs{L} \to \pi_0^* \qcs{E}$.
-
-We have now show that if $\qcs{L}$ is a quasicharacter sheaf on $G$ and $\iota_0^*\qcs{L}= (\EE)_{G^0}$ then there is some quasicharacter sheaf $\qcs{E}$ on $\pi_0(G)$ such that $\qcs{L} \iso \pi_0^* \qcs{E}$.
-On the other hand, $\iota_0^*(\pi_0^* \qcs{E}) \iso (\EE)_{G^0}$, by Proposition~\ref{prop:pullback}.
-This shows that \eqref{eq:pi2} is exact at $\QC(G)$, concluding the proof of Proposition~\ref{prop:middleexact}.
-\end{proof}
+\end{proof}
+
+To close this section, we note that the injectivity of $\pi_0^*$ will be proven in Corollary~\ref{cor:exact}.
 

### 2013-10-10 shanghai.tex
Added proof of Cor 10.2

@@
 is an exact sequence of $\QC$-schemes and that $\Hh^1(\Fq, A) = 0$.
-\Clifton{Could you add a few words about the proof of this corollary?}   
 Then pullback yields an exact sequence
@@
 \end{corollary}
+\begin{proof}
+Since $\Hh^1(k, A) = 0$, the sequence $0 \to A(\Fq) \to B(\Fq) \to C(\Fq) \to 0$ is exact;
+applying $\Hom(-, \EEx)$ yields another exact sequence since $\EEx$ is divisible.  The result now follows
+from Proposition~\ref{prop:pullback} and Theorem~\ref{thm:snake}.
+\end{proof}
 
@@
 or on the ramification of $T$. 
-\Clifton{Fix this.}
-We may therefore ask if for a comparison of
+We may therefore ask for a comparison of
 quasicharacter sheaves on $T$ and on $T'$ whenever there is a relationship

### 2013-10-10 shanghai.tex
Removed the marginal comments on issues that have been addressed. Added compositio files to the repository.

@@
 \item is closed under pullback by arbitrary morphisms in $C(G)$,
-\item and if the cokernel \David{Is $C(G)$ abelian?} of a morphism $\phi \in \mor C(G)$ is in
+\item and if the cokernel \David{Is $C(G)$ abelian?} \Clifton{Yes.
+In fact, that's stated, implicitly, in the paragraph above: a tensor category is an abelian category.} of a morphism $\phi \in \mor C(G)$ is in
 $W$ then so is the kernel of $\phi$.
@@
 follow from the fact that in a weak isomorphism $(g, T)$, $g$ is an \'etale cover, together with standard
-facts on \'etale covers and pullbacks. \David{Is this sufficient?}
+facts on \'etale covers and pullbacks. \David{Is this sufficient?}\Clifton{Yes, I think so.}
 \end{proof}
@@
  If $\qcs{E}$ is any local system on a connected scheme $G$ and $\bg$ is a geometric point on $G$,
- we may associate to $\qcs{E}$ a character of the \'etale fundamental group $\pi_1(G, \bg)$ \David{add citation}.
+ we may associate to $\qcs{E}$ a character of the \'etale fundamental group $\pi_1(G, \bg)$ \David{add citation}.\Clifton{I'll find one.}
  Since $\pi_1(G, \bg)$ is defined as a projective limit of automorphism groups of finite \'etale covers, a general
@@
  as defined using Lemma~\ref{lemma:finite-pullback}.
- %
- \Clifton{There's detail missing here; I might want to include some of it.}
- %
  Moreover, since $L(f,T)$ is an isomorphism of local systems
@@
   $\tau'(\Frob{}) = \tau(\Frob{}) \cdot (\,^{\Frob{}^{-1}}a \cdot a^{-1})$,
-  %\Clifton{Fix this.}
   so $\tau$ and $\tau'$ are cohomologous. This shows that
@@
 \begin{lemma} \label{lem:dual-inv}
-Let $X$ be an abelian group equipped with an action of $\Weil{}$, and write $\Frob{} = \Frob{}$.  Then
+Let $X$ be an abelian group equipped with an action of $\Weil{}$.
+% and write $\Frob{} = \Frob{}$. 
+ Then
 \begin{align*}
@@
 The resulting isomorphism $\gqcs{L} \to \pi_0^* \gqcs{E}$ satisfies \ref{QC.4}, 
-thus defining an isomorphism $\qcs{L} \to \pi_0^* \qcs{E}$.
+thus defining an isomorphism $\qcs{L} \to \pi_0^* \qcs{E}$ in $\QC(G)$.
 \end{proof}
@@
 Passing to isomorphism classes of objects and invoking the 
-universal property of $\varinjlim_{n\in \ZZ_{>0}} \QCiso{\GN{T}_n}$ 
-gives a group isomorphism
+universal property of direct limits gives a group isomorphism
 $\theta: \varinjlim_{n\in \ZZ_{>0}} \QCiso{\GN{T}_n} \to \QCiso{\GN{T}}$
@@
 Now use Theorem~\ref{thm:application}, Proposition~\ref{prop:pullback} 
-and the fact that  $\Hom_{\text{qc}}(T(K),\EEx) = \varinjlim_{n\in \ZZ_{>0}} \GN{T}_n(k)^*$ 
+and the fact that  $\Hom_{\text{qc}}(T(K),\EEx) = \varinjlim_{n\in \ZZ_{>0}} \GN{T}_n(k)^*$, where this last direct limit it taken
 with reference to the family of group homomorphisms 

### 2013-10-10 shanghai.tex
Broke some long lines; added a reference for l-adic sheaves; Sommes trig. |--> sommes trig.
Still looking for a reference for lisse sheaves and the etale
fundamental group . . .

@@
 \]  
-We also describe a pro-group scheme $\GN{T}$ simultaneously geometrizing all quasicharacters ({\it i.e.}, finite-depth characters) of $T(K)$.
+We also describe a pro-group scheme $\GN{T}$ 
+simultaneously geometrizing all quasicharacters ({\it i.e.}, finite-depth characters) of $T(K)$.
 
@@
 equipped with a host of functors, including pushforward. 
-We hope to use this to our advantage as we work toward an adaptation of Lusztig's theory of characters sheaves to the study of characters of admissible representations of reductive $p$-adic groups that extends beyond the case of $p$-adic tori.
-
-DeBacker and Reeder have recently applied Deligne-Lusztig representations to part of the depth-zero part of the
+We hope to use this to our advantage as we work toward an adaptation of 
+Lusztig's theory of characters sheaves to the study of characters of 
+admissible representations of reductive $p$-adic groups that extends beyond the case of $p$-adic tori.
+
+DeBacker and Reeder have recently applied Deligne-Lusztig 
+representations to part of the depth-zero part of the
 local Langlands correspondence \cite{reeder-debacker:09a}.
-Deligne-Lusztig theory also plays an important role in Waldspurger's work on nilpotent distributions \cite{waldspurger:01}.
+Deligne-Lusztig theory also plays an important role in 
+Waldspurger's work on nilpotent distributions \cite{waldspurger:01}.
 After developing Deligne-Lusztig representations, 
@@
 We fix a prime $\ell$, invertible in $\Fq$.
-We will work with constructible $\ell$-adic sheaves \cite{deligne:80a}*{\S 1.1} on $\QC$-schemes,
-employing the standard formalism;
-see, in particular, \cite{SGA5}*{Expos\'e VI,\S 2}, where pullback and tensor products are developed.
+We will work with constructible $\ell$-adic sheaves \cite{deligne:80a}*{\S 1.1}, \cite{SGA5}*{Expos\'es V, VI} 
+on $\QC$-schemes, employing the standard formalism.
+%see, in particular, \cite{SGA5}*{Expos\'e VI,\S 2}, where pullback and tensor products are developed.
 We also make extensive use of the external tensor product of $\ell$-adic sheaves, defined as follows: if $\mathcal{F}$ and $\mathcal{G}$ are constructible $\ell$-adic sheaves on schemes $X$ and $Y$ and $p_X : X\times Y\to X$ and $p_Y : X\times Y \to Y$ are the projections, then $\mathcal{F}\boxtimes \mathcal{G} \ceq p_X^* \mathcal{F} \otimes p_Y^*\mathcal{G}$.
@@
   To show that $L_G(f,\psi) \iso (\qcs{L}_0,\mu_0)$ we simply apply the sheaf--function dictionary
-  as follows \citelist{\cite{laumon:87a}*{1.1.3} \cite{deligne:SGA4.5}*{Sommes trig.}}.
+  as follows \citelist{\cite{laumon:87a}*{1.1.3} \cite{deligne:SGA4.5}*{sommes trig.}}.
   First, recall that $L_G(f,\psi) \ceq (L(f,\psi), \mu(f,\psi))$.

### 2013-10-10 shanghai.tex
Moved the new paragraph on local systems and the fundamental group

@@
 
+To prove the next proposition, we will need a certain perspective on local systems.
+ If $\qcs{E}$ is any local system on a connected scheme $G$ and $\bg$ is a geometric point on $G$,
+ we may associate to $\qcs{E}$ a character of the \'etale fundamental group $\pi_1(G, \bg)$ \David{add citation}.\Clifton{I'll find one.}
+ Since $\pi_1(G, \bg)$ is defined as a projective limit of automorphism groups of finite \'etale covers, a general
+ local system will correspond to a projective limit of characters of such groups.  But some local systems can be
+ described in terms of a single cover $f: H \to G$ and a representation $\psi: \ker f \to \Aut(V)$;
+ two such descriptions yield isomorphic local systems if and only if they are related by a weak
+ isomorphism in $C(G)$.  While the description of local systems in terms of $\pi_1(G, \bg)$ does
+ not generalize well to non-connected $G$, the description in terms of $C(G)$ does.  \David{Look okay?}
+
 The definition of finite quasicharacter sheaves will require several steps, 
@@
  \end{proof}
-
-To prove the next proposition, we will need a certain perspective on local systems.
- If $\qcs{E}$ is any local system on a connected scheme $G$ and $\bg$ is a geometric point on $G$,
- we may associate to $\qcs{E}$ a character of the \'etale fundamental group $\pi_1(G, \bg)$ \David{add citation}.\Clifton{I'll find one.}
- Since $\pi_1(G, \bg)$ is defined as a projective limit of automorphism groups of finite \'etale covers, a general
- local system will correspond to a projective limit of characters of such groups.  But some local systems can be
- described in terms of a single cover $f: H \to G$ and a representation $\psi: \ker f \to \Aut(V)$;
- two such descriptions yield isomorphic local systems if and only if they are related by a weak
- isomorphism in $C(G)$.  While the description of local systems in terms of $\pi_1(G, \bg)$ does
- not generalize well to non-connected $G$, the description in terms of $C(G)$ does.  \David{Look okay?}
 
@@
   descends to a diagram of $\Fq$-schemes since the $\bFq$-points of
-  the objects come equipped with \Clifton{?} continuous $\Weil{}$-actions, and the
+  the objects come equipped with continuous $\Gamma$-actions, and the
   morphisms are $\Gamma$-equivariant.
@@
 Now use Theorem~\ref{thm:application}, Proposition~\ref{prop:pullback} 
-and the fact that  $\Hom_{\text{qc}}(T(K),\EEx) = \varinjlim_{n\in \ZZ_{>0}} \GN{T}_n(k)^*$, where this last direct limit it taken
-with reference to the family of group homomorphisms 
+and the fact that  $\Hom_{\text{qc}}(T(K),\EEx) = \varinjlim_{n\in \ZZ_{>0}} \GN{T}_n(k)^*$, 
+where this direct limit is taken with respect to the family of group homomorphisms 
 dual to $f_{n} : \GN{T}_{n+1}(\Fq) \to \GN{T}_n(\Fq)$.

### 2013-10-10 shanghai.tex
Massaged the new paragraph in Section 6.

@@
 We fix a prime $\ell$, invertible in $\Fq$.
-We will work with constructible $\ell$-adic sheaves \cite{deligne:80a}*{\S 1.1}, \cite{SGA5}*{Expos\'es V, VI} 
+We will work with constructible $\ell$-adic sheaves \citelist{\cite{deligne:80a}*{\S 1.1} \cite{SGA5}*{Expos\'es V, VI}}
 on $\QC$-schemes, employing the standard formalism.
@@
 
-To prove the next proposition, we will need a certain perspective on local systems.
- If $\qcs{E}$ is any local system on a connected scheme $G$ and $\bg$ is a geometric point on $G$,
- we may associate to $\qcs{E}$ a character of the \'etale fundamental group $\pi_1(G, \bg)$ \David{add citation}.\Clifton{I'll find one.}
- Since $\pi_1(G, \bg)$ is defined as a projective limit of automorphism groups of finite \'etale covers, a general
- local system will correspond to a projective limit of characters of such groups.  But some local systems can be
- described in terms of a single cover $f: H \to G$ and a representation $\psi: \ker f \to \Aut(V)$;
+The notion of a finite quasicharacter sheaf is informed 
+by a certain perspective on local systems on connected groups.
+Recall that every geometric point $\bg$ on a connected scheme $G$ 
+determines an equivalence between the categories of $\ell$-adic local systems on $G$ 
+and $\ell$-adic representations of the \'etale fundamental group $\pi_1(G, \bg)$ 
+\citelist{\cite{SGA5}*{VI,Prop. 1.2.5} \cite{deligne:80a}*{1.1.1}}.
+ Since $\pi_1(G, \bg)$ is a projective limit of automorphism groups of finite \'etale covers, 
+ a general local system corresponds to a projective limit of characters of such groups.  
+ But some local systems can be described in terms of a single cover $f: H \to G$ 
+ and a representation $\psi: \ker f \to \Aut(V)$;
  two such descriptions yield isomorphic local systems if and only if they are related by a weak
  isomorphism in $C(G)$.  While the description of local systems in terms of $\pi_1(G, \bg)$ does
- not generalize well to non-connected $G$, the description in terms of $C(G)$ does.  \David{Look okay?}
+ not generalize well to non-connected $G$, a perspective using finite \'etale covers does.
 
@@
 \item is closed under pullback by arbitrary morphisms in $C(G)$,
-\item and if the cokernel \David{Is $C(G)$ abelian?} \Clifton{Yes.
-In fact, that's stated, implicitly, in the paragraph above: a tensor category is an abelian category.} of a morphism $\phi \in \mor C(G)$ is in
+\item and if the cokernel of a morphism $\phi \in \mor C(G)$ is in
 $W$ then so is the kernel of $\phi$.
@@
 follow from the fact that in a weak isomorphism $(g, T)$, $g$ is an \'etale cover, together with standard
-facts on \'etale covers and pullbacks. \David{Is this sufficient?}\Clifton{Yes, I think so.}
+facts on \'etale covers and pullbacks.
 \end{proof}

### 2013-10-10 shanghai.tex
Starting transition to Compositio class
Working on cleanup
Cleanup of preamble

@@
 % !TEX encoding = UTF-8 Unicode
-\documentclass[11pt]{amsart}
-\title[Sheaf--function dictionary for local tori]{A sheaf--function dictionary for algebraic tori over local fields}
-\usepackage[british]{babel}
-\usepackage{datetime}
+\documentclass{compositio}
+
+%%%%%%%%%%%%%%%%%% HEADING %%%%%%%%%%%%%%%%%%
+\title[Function--sheaf dictionary for local tori]{A function--sheaf dictionary for algebraic tori over local fields}
 \date{\today}
 \author{Clifton Cunningham}
+\email{cunning@math.ucalgary.ca}
 \address{University of Calgary}
-\email{cunning@math.ucalgary.ca}
 \author{David Roe}
+\email{roed.math@gmail.com}
 \address{Pacific Institute for the Mathematical Sciences at the University of Calgary}
-\email{roed.math@gmail.com}
+\classification{14L15 (primary), 11G25, 14F05, 14D24, 11S31 (secondary)}
+\keywords{quasicharacters, quasicharacter sheaves, algebraic tori, Greenberg transforms, N\'eron models, local fields}
+
+%%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%
+% Encodings
 \usepackage[utf8]{inputenc}
-\renewcommand{\baselinestretch}{1.2}
-%\usepackage[notcite]{showkeys}
-\usepackage{hyperref}
-\usepackage{geometry}
-\usepackage{amsthm}
-\usepackage{amsmath}
-\usepackage{amssymb}
-%\usepackage[shortalphabetic]{amsrefs}
+\usepackage[T1]{fontenc}
+% AMS packages
+\usepackage{amsmath, amsthm, amssymb}
 \usepackage[alphabetic]{amsrefs}
-\newcommand\SortNoop[1]{}
-\DeclareRobustCommand{\VAN}[3]{#2}
-%\usepackage{amsrefs}
-\renewcommand\MR{\relax}
-%\usepackage{xypic}
-\usepackage{textcomp}
-\usepackage{mathrsfs}
-\usepackage{yfonts}
-\newcommand{\mathswab}[1]{\operatorname{\textswab{#1}}}
-\usepackage[T1]{fontenc}
+% Fonts
+\usepackage{mathrsfs, yfonts}
+% TikZ
 \usepackage{tikz}
@@
 \usepackage{tikz-cd}
-\usepackage{manfnt}
-%\usepackage{makeidx}
-
-%\include{definitions}
+% Hyperrefs
+\usepackage{hyperref}
+
+%%%%%%%%%%%%%%% THEOREM STYLES %%%%%%%%%%%%%%%
 \theoremstyle{plain}
@@
 
-%% Global TikZ settings
-
+%%%%%%%%%%%%%%%% TIKZ SETTINGS %%%%%%%%%%%%%%%%
 \tikzset{every picture/.style={>=stealth},label/.style={font=\footnotesize}}
 
-\newcommand{\gal}[1]{{\operatorname{Gal}\hskip-1pt\left( {\bar #1}/#1 \right)}}
-\newcommand{\Spec}[1]{{\operatorname{Spec}\hskip-1pt( #1 )}}
-
+%%%%%%%%%%%%%%% RINGS AND GROUPS %%%%%%%%%%%%%%%
 \newcommand{\FF}{{\mathbb{F}}}
@@
 \newcommand{\Qp}{\mathbb{Q}_p}
-%\newcommand{\Fp}{\mathbb{F}_p}
 \newcommand{\bFq}{\bar{k}}
@@
 \newcommand{\Fqm}{k_m}
-%\newcommand{\bFp}{{\mathbb{\bar F}_p}}
 \newcommand{\WW}{\mathbb{W}}
-
 \newcommand{\EEx}{\EE^\times}
 \newcommand{\Zlx}{\mathbb{\bar Z}_\ell^\times}
-
+\newcommand{\Weil}[1]{\mathcal{W}_{#1}}
+
+%%%%%%%%%%%%%%% ALGEBRAIC GROUPS %%%%%%%%%%%%%%%
+\newcommand{\mathswab}[1]{\operatorname{\textswab{#1}}}
+\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
+\newcommand{\GN}[1]{\mathswab{#1}}
+\newcommand{\bGN}[1]{{\bar{\mathswab{#1}}}}
+\newcommand{\TT}{\underline{T}}
+\newcommand{\TL}{\underline{T_L}}
+\newcommand{\TTp}{\underline{T}'}
+
+%%%%%%%%%%%%%%% NAMED OPERATORS %%%%%%%%%%%%%%%
 \DeclareMathOperator{\Gal}{Gal}
@@
 \DeclareMathOperator{\trace}{Tr}
-
-\newcommand{\cdef}[1]{{#1}\index{#1}} 
+\DeclareMathOperator{\obj}{obj}
+\DeclareMathOperator{\mor}{mor}
+\DeclareMathOperator{\Lang}{Lang}
+\DeclareMathOperator{\image}{im}
+\DeclareMathOperator{\Loc}{Loc}
+\newcommand{\gal}[1]{{\operatorname{Gal}\hskip-1pt\left( {\bar #1}/#1 \right)}}
+\newcommand{\Spec}[1]{{\operatorname{Spec}\hskip-1pt( #1 )}}
+
+%%%%%%%%%%%% MISCELLANEOUS OPERATORS %%%%%%%%%%%%
 \newcommand{\sheafHom}{{\mathscr{H}\hskip-4pt{\it o}\hskip-2pt{\it m}}}
@@
 \newcommand{\iso}{{\ \cong\ }}
-\newcommand{\obj}{{\text{obj}\, }}
-\newcommand{\mor}{{\text{mor}\, }}
-\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
-\newcommand{\GN}[1]{\mathswab{#1}}
-\newcommand{\bGN}[1]{{\bar{\mathswab{#1}}}}
-\newcommand{\TT}{\underline{T}}
-\newcommand{\TL}{\underline{T_L}}
-\newcommand{\TTp}{\underline{T}'}
+%% Limits
 \newcommand{\invlim}[1]{\lim\limits_{\overleftarrow{#1}}}
@@
 \newcommand{\colimit}[1]{\mathop{\textsc{colim}}\limits_{#1}}
+%% Fonts for quasicharacter sheaves
 \newcommand{\qcs}[1]{{\mathcal{#1}}}
@@
 \newcommand{\dualcs}[1]{\qcs{#1}^\dagger}
+%% Categories
 \newcommand{\QC}{{\mathcal{Q\hskip-0.8pt C}}}
@@
 \newcommand{\QCfiso}[1]{\QCf(#1)_{/\text{iso}}}
-\newcommand{\Lgroup}[1]{{\,^L\hskip-1pt{#1}}}
-\newcommand{\dualgroup}[1]{{\check{#1}}}
-\newcommand{\Lang}{{\operatorname{Lang}}}
-\newcommand{\image}{{\operatorname{im}}}
-\newcommand{\Weil}[1]{\mathcal{W}_{#1}}
-\newcommand{\Loc}{{\operatorname{Loc}}}
 \newcommand{\trFrob}[1]{t_{#1}}
-
-%amsmath replacements for \atop
+%% amsmath replacements for \atop
 \newcommand{\latop}[2]{\genfrac{}{}{0pt}{0}{#1}{#2}}
 \newcommand{\partop}[2]{\genfrac{(}{)}{0pt}{0}{#1}{#2}}
-
+%% Labeled items
 \makeatletter
-\newcommand{\labitem}[2]{%
+\newcommand{\labitem}[2]{
 \def\@itemlabel{\textbf{#1}}
@@
 \makeatother
-
+%% Shorthand for bars
 \renewcommand{\bf}{\bar{f}}
@@
 \newcommand{\bH}{\bar{H}}
+%% Spacing control
 \newcommand{\tight}[3]{\hspace{-#1pt}{#2}\hspace{-#3pt}}
@@
 \newcommand{\GzxGz}{\text{$G^0 \tight{1}{\times}{1} G^0$}}
-
-\newcommand\todo[1]{\ \vspace{5mm}\par \noindent\framebox{\begin{minipage}[c]{0.95 \textwidth} \tt #1\end{minipage}} \vspace{5mm} \par}
+%% Margin notes
 \newcommand\Clifton[1]{\marginpar{\smaller\smaller CC: #1}}
 \newcommand\David[1]{\marginpar{\smaller\smaller DR: #1}}
-
+%% Hyphenation override
 \hyphenation{quasi-character}
 
+%%%%%%%%%%%% BEGIN DOCUMENT %%%%%%%%%%%%
 \begin{document}
@@
 
-%\input{introduction}
-%In his celebrated thesis, John Tate writes 
-%\begin{quotation}
-%    {\it Concerning the characters of $k^*$ [the
-%    multiplicative group of a $\mathfrak{p}$-adic field], the
-%    situation is different from that of $k^+$.  First of all, we are
-%    interested in continuous multiplicative maps $\alpha \mapsto
-%    c(\alpha)$ of $k^*$ into the complex numbers, not only in the
-%    bounded ones, and shall call such a map a quasi-character,
-%    reserving the word ``character'' for the conventional character of
-%    absolute value $1$. Secondly, we shall find no model for the group
-%    of quasi-characters, or even for the group of characters, though
-%    such a model would be of the utmost importance.}
-%  \cite{tate:67a}*{\S 2.3}
-%\end{quotation}
-%\noindent
 In this paper we find a dictionary between quasicharacters of algebraic tori over local fields and quasicharacter sheaves. 
-%
 What is a quasicharacter sheaf?
@@
 some of the potential benefits of Theorem~\ref{thm:application} here. 
-%
 Characters on $T$ have limited
@@
 
-\subsection*{Acknowledgements}
+\begin{acknowledgements} %{Acknowledgements}
 
@@
 
-\tableofcontents
+\end{acknowledgements}
+
+%\tableofcontents
 
@@
 \begin{align*}
-\cdef{\trFrob{G}} : \QCiso{G} &\to G(\Fq)^*, \\
+\trFrob{G} : \QCiso{G} &\to G(\Fq)^*, \\
 \qcs{L} &\mapsto \trFrob{\qcs{L}}.
@@
 \end{proof}
-Let $W$ be the family of weak isomorphisms and \cdef{$C(G)[W^{-1}]$} be the localization of $C(G)$ at $W$.
+Let $W$ be the family of weak isomorphisms and $C(G)[W^{-1}]$ be the localization of $C(G)$ at $W$.
 A morphism in $C(G)[W^{-1}]$ is an equivalence class of diagrams
@@
 is the pro-group scheme over $\Fq$ given by 
-$\cdef{\GN{T}} \ceq \varprojlim_{n\in \ZZ_{>0}} \GN{T}_{n}$, 
+$\GN{T} \ceq \varprojlim_{n\in \ZZ_{>0}} \GN{T}_{n}$, 
 with reference to the family of  surjective morphisms of 
@@
 
-\DeclareRobustCommand{\VAN}[3]{#3}
+\bibliographystyle{amsalpha}
+%\DeclareRobustCommand{\VAN}[3]{#3}
 \bibliography{Biblio}

### 2013-10-10 shanghai.tex
Adding some newlines
Fixing merge

@@
 
+\end{acknowledgements}
+
+\begin{thanks}
+
 We also gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
@@
 
-\end{acknowledgements}
+\end{thanks}
 
@@
 %see, in particular, \cite{SGA5}*{Expos\'e VI,\S 2}, where pullback and tensor products are developed.
-We also make extensive use of the external tensor product of $\ell$-adic sheaves, defined as follows: if $\mathcal{F}$ and $\mathcal{G}$ are constructible $\ell$-adic sheaves on schemes $X$ and $Y$ and $p_X : X\times Y\to X$ and $p_Y : X\times Y \to Y$ are the projections, then $\mathcal{F}\boxtimes \mathcal{G} \ceq p_X^* \mathcal{F} \otimes p_Y^*\mathcal{G}$.
+We also make extensive use of the external tensor product of $\ell$-adic sheaves,
+defined as follows: if $\mathcal{F}$ and $\mathcal{G}$ are constructible $\ell$-adic
+sheaves on schemes $X$ and $Y$ and $p_X : X\times Y\to X$ and $p_Y : X\times Y \to Y$
+are the projections, then $\mathcal{F}\boxtimes \mathcal{G} \ceq p_X^* \mathcal{F} \otimes p_Y^*\mathcal{G}$.
 
@@
 \labitem{(QC.1)}{QC.1} $\gqcs{L}$ is a rank~one $\ell$-adic local system on $\bG$, by which we mean
-a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces; 
-\labitem{(QC.2)}{QC.2} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
+a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected
+component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces; 
+\labitem{(QC.2)}{QC.2} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of
+sheaves on $\bGxG$ such that the following diagram commutes, 
   where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
@@
 \labitem{(QC.3)}{QC.3} $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$ is an
-  isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with $\mu$ in the sense that the following diagram commutes.
+  isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with
+  $\mu$ in the sense that the following diagram commutes.
 %
@@
 
-%\section{Products}
-
 We end this section with a simple result on products of quasicharacter sheaves,
@@
 \begin{proposition}\label{prop:product}
-If $G_1$ and $G_2$ are $\QC$-schemes then the rule $\boxtimes : (\qcs{L}_1,\qcs{L}_2)\to \qcs{L}_1\boxtimes\qcs{L}_2$ defines an equivalence of categories 
+If $G_1$ and $G_2$ are $\QC$-schemes then the rule
+$\boxtimes : (\qcs{L}_1,\qcs{L}_2)\to \qcs{L}_1\boxtimes\qcs{L}_2$ defines an equivalence of categories 
 \[
@@
 \begin{proof}
-The only non-trivial part of the proof is to show that $\boxtimes : \QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)$ is essentially surjective, so we will only address that point here.
+The only non-trivial part of the proof is to show that $\boxtimes : \QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)$
+is essentially surjective, so we will only address that point here.
 
@@
 \]
-Let $r_1$ and $r_2$ be the projection morphisms pictured below, with sections $q_1$ and $q_2$, also morphisms of group schemes:
+Let $r_1$ and $r_2$ be the projection morphisms pictured below,
+with sections $q_1$ and $q_2$, also morphisms of group schemes:
 \[
@@
 is a family of morphisms $W$ that
-\begin{enumerate}
+\begin{itemize}
 \item contains all isomorphisms,
@@
 $W$ then so is the kernel of $\phi$.
-\end{enumerate}
+\end{itemize}
 
@@
 \begin{lemma}\label{lemma:finite-iso}
-Each finite quasicharacter sheaf $(f,\psi)$ in $\QCf(G)$ determines a canonical isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$. 
+Each finite quasicharacter sheaf $(f,\psi)$ in $\QCf(G)$ determines a
+canonical isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$. 
  \end{lemma}
@@
 On general $\QC$-schemes $G$, there are bounded quasicharacter sheaves which are not finite.  Identifying
-$\QCf(G)$ with its image under $B_G \circ L_G$, as defined in Proposition~\ref{prop:BG} and in the proof of Proposition~\ref{prop:bounded}, we will see in Corollary~\ref{cor:bounded-and-finite} that
+$\QCf(G)$ with its image under $B_G \circ L_G$, as defined in
+Proposition~\ref{prop:BG} and in the proof of Proposition~\ref{prop:bounded},
+we will see in Corollary~\ref{cor:bounded-and-finite} that
 a quasicharacter sheaf is finite if and only if its trace of Frobenius has finite image.
@@
   First, recall that $L_G(f,\psi) \ceq (L(f,\psi), \mu(f,\psi))$.
-  Let $k'/k$ be any degree-$n$ extension and let $\Nm : k'\to k$ be the norm map. 
+  Let $k'/k$ be any degree-$n$ extension; 
+  let $\Nm : G(k')\to G(k)$ be the norm map 
+  and let $b : G_{k'} \to G$ be the base change map.
   By \cite{laumon:87a}*{1.1.3.3}, 
-  \[
-  \trFrob{(G_{k'}\hookrightarrow G)^*L(f,\psi)} = \trFrob{\qcs{L}} \circ \Nm;
-  \]
-  on the other hand, 
-  \[
-  \trFrob{\qcs{L}} \circ \Nm = \trFrob{(G_{k'}\hookrightarrow G)^*\qcs{L}},
-  \]
+  $\trFrob{b^*L(f,\psi)} = \trFrob{\qcs{L}} \circ \Nm$;
+  on the other hand, $\trFrob{\qcs{L}} \circ \Nm = \trFrob{b^*\qcs{L}}$,
    by Proposition~\ref{prop:basechange}.
@@
 
-A \emph{global section} of $\qcs{L}$ is a function $s : G(\bFq) \to \coprod_{x \in G(\bFq)} \gqcs{L}_x$ so that $s(x) \in \gqcs{L}_x$ for all $x \in G(\bFq)$ and
+A \emph{global section} of $\qcs{L}$ is a function $s : G(\bFq) \to \coprod_{x \in G(\bFq)} \gqcs{L}_x$
+so that $s(x) \in \gqcs{L}_x$ for all $x \in G(\bFq)$ and
 \begin{equation}\label{section}
@@
 
-We say that a section is \emph{nontrivial} if $s(x) \ne 0$ for all $x \in G(\bFq)$.  Note that the only other section is the constant zero section.
+We say that a section is \emph{nontrivial} if $s(x) \ne 0$ for all $x \in G(\bFq)$. 
+Note that the only other section is the constant zero section.
 
@@
 \begin{proof}
-There is a natural isomorphism $\Hh^1(\Weil{}, G(\bFq)^*) \to (G(\bFq)^*)_{\Frob{}}$ defined by $[z] \mapsto z(\Frob{})$.
-The proposition now follows directly from Proposition~\ref{prop:etale} and Lemma~\ref{lem:dual-inv}.
+There is a natural isomorphism $\Hh^1(\Weil{}, G(\bFq)^*) \to (G(\bFq)^*)_{\Frob{}}$
+defined by $[z] \mapsto z(\Frob{})$.  The proposition now follows directly
+from Proposition~\ref{prop:etale} and Lemma~\ref{lem:dual-inv}.
 \end{proof}
@@
 
-\section{The sheaf--function dictionary for non-connected group schemes}
+\section{The function--sheaf dictionary for non-connected group schemes}
 \label{sec:snake}
@@
   In order to apply the snake lemma, we need to show that the top row is exact at $\QCiso{G}$ and $\QCiso{G^0}$:
-  the surjectivity of $\QCiso{G} \to \QCiso{G^0}$ follows from Proposition~\ref{prop:restriction} while exactness at $\QCiso{G}$ is given by Proposition~\ref{prop:middleexact}.
+  the surjectivity of $\QCiso{G} \to \QCiso{G^0}$ follows from Proposition~\ref{prop:restriction}
+  while exactness at $\QCiso{G}$ is given by Proposition~\ref{prop:middleexact}.
 %  
@@
 sheaves on $G$ to those on $\pi_0(G)$, using the fact that the preimage constructed in the proof of
-Proposition~\ref{prop:restriction} is a finite quasicharacter sheaf on $G$.  Using these equivalences, it is enough to prove the Corollary
+Proposition~\ref{prop:restriction} is a finite quasicharacter sheaf on $G$.
+Using these equivalences, it is enough to prove the Corollary
 for \'etale $\QC$-schemes.
@@
 
-\section{A sheaf--function dictionary for tori over local fields} \label{sec:quasichar}
+\section{A function--function dictionary for tori over local fields} \label{sec:quasichar}
 

### 2013-10-10 shanghai.tex
Removing commented out text

--- 2013-10-10 shanghai.tex
@@
 as character sheaves; see for example, \cite{kamgarpour:09a}. 
-%\cite{boyarshenko-drinfeld:motivated}*{\S 1.8}.  
 Our quasicharacter sheaves evolved from this notion, and Theorem~\ref{thm:snake}
@@
 
-\begin{acknowledgements} %{Acknowledgements}
+\begin{acknowledgements}
 
@@
 \end{acknowledgements}
-
-%\tableofcontents
 
@@
 on $\QC$-schemes, employing the standard formalism.
-%see, in particular, \cite{SGA5}*{Expos\'e VI,\S 2}, where pullback and tensor products are developed.
-We also make extensive use of the external tensor product of $\ell$-adic sheaves, defined as follows: if $\mathcal{F}$ and $\mathcal{G}$ are constructible $\ell$-adic sheaves on schemes $X$ and $Y$ and $p_X : X\times Y\to X$ and $p_Y : X\times Y \to Y$ are the projections, then $\mathcal{F}\boxtimes \mathcal{G} \ceq p_X^* \mathcal{F} \otimes p_Y^*\mathcal{G}$.
+We also make extensive use of the external tensor product of $\ell$-adic sheaves,
+defined as follows: if $\mathcal{F}$ and $\mathcal{G}$ are constructible $\ell$-adic
+sheaves on schemes $X$ and $Y$ and $p_X : X\times Y\to X$ and $p_Y : X\times Y \to Y$
+are the projections, then $\mathcal{F}\boxtimes \mathcal{G} \ceq p_X^* \mathcal{F} \otimes p_Y^*\mathcal{G}$.
 
@@
 \labitem{(QC.1)}{QC.1} $\gqcs{L}$ is a rank~one $\ell$-adic local system on $\bG$, by which we mean
-a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces; 
-\labitem{(QC.2)}{QC.2} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
+a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected
+component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces; 
+\labitem{(QC.2)}{QC.2} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of
+sheaves on $\bGxG$ such that the following diagram commutes, 
   where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
-%
   \[
@@
   \]
-%
 \labitem{(QC.3)}{QC.3} $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$ is an
-  isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with $\mu$ in the sense that the following diagram commutes.
-%
+  isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with
+  $\mu$ in the sense that the following diagram commutes.
   \[
@@
   \Frob{G}^* \gqcs{L} \rar{\Frob{G}^* \alpha} \arrow[swap]{d}{\phi} & \Frob{G}^* \gqcs{L'} \dar{\phi'}
-  & %\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} 
-  & \arrow[swap]{d}{\mu} m^* \gqcs{L} \rar{m^* \alpha} & m^* \gqcs{L'} \dar{\mu'} \\
+  & & \arrow[swap]{d}{\mu} m^* \gqcs{L} \rar{m^* \alpha} & m^* \gqcs{L'} \dar{\mu'} \\
   \gqcs{L} \rar{\alpha} & \gqcs{L'}
@@
   \]
-%
   Since $a_i^* (\gqcs{L}\vert_{\bG^i})$ is a constant sheaf, its pullback
@@
   $f^* : \QC(G) \to \QC(H)$ is a monoidal functor.
-%
   The diagram relating $f^* : \QC(G) \to \QC(H)$, $f^* : G(k)^* \to H(k)^*$ and trace of Frobenius
@@
 We will obtain an isomorphism $\qcs{L} \iso  \qcs{L}_1\boxtimes \qcs{L}_2$.
-%
 Applying the functor $f^*$ to the isomorphism $\mu$ yields
@@
 We can interpret this operation on characters in terms of quasicharacter sheaves:
-%
 
@@
 
-If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$, we may define
+If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$, we define
 a quasicharacter sheaf $\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
@@
 By Proposition~\ref{prop:pullback} the pullback part of the definition of $\rho$ corresponds to the map $(\Res_{k'/k}G')(k') \to G'(k')^*$
-induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on $(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'$
+induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on 
+\[
+(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'
+\]
 is given by permuting coordinates, composition with the norm map yields the identity on $G'(k')$.
@@
 The category of bounded quasicharacter sheaves is a rigid monoidal category in the obvious way.
-%with duals given by $\qcs{L}_0^\vee \ceq \sheafHom(\qcs{L}_0,\EE)$.
 
@@
 
- %In this section we describe a full subcategory of $\QCb(G)$
- %which will illuminate some features of $\QCb(G)$ and also play a role in some arguments below.
-
 In this section we define \emph{finite quasicharacter sheaves}, a further refinement
@@
 scheme $\ker f \ceq f^{-1}({\bar e)}$ is trivial.
-% similar nomenclature is employed in \cite{kamgarpour:09a}*{\S 2.2}. 
 Consider the category $C(G)$ whose objects consist of pairs $(f,\psi)$, where
@@
 A morphism in $C(G)[W^{-1}]$ is an equivalence class of diagrams
-%  \begin{equation}\label{eq:morGCf}
 \[   
@@
 \]
-%  \end{equation}
  where $(g,T) : (f,\psi) \to (f',\psi')$ is any map in $C(G)$ 
  and $(h,U) :  (f',\psi') \to (f_1,\psi_1)$ is a weak isomorphism in $C(G)$ \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16}.
-%Likewise, $C(G)[W^{-1}]$ is a tensor category.
 
@@
 $(f,\psi)$ such that $\psi$ is a one-dimensional representation.
-%
 The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\QCf(G)$,
@@
   is also essentially surjective, hence an equivalence.
-  %(when $G$ is a connected, commutative algebraic group over $\Fq$).
 
@@
    by Proposition~\ref{prop:basechange}.
-  %Using notation from \cite{laumon:87a}*{1.1}, this means $t_{\bullet L(f,\psi)} = t_{\bullet \qcs{L}_0}$.
   Using \cite{laumon:87a}*{Th\'eor\`eme 1.1.2}, it follows that  $L(f,\psi) \iso \qcs{L}_0$ in $\Loc(G)$.
@@
 denoted there by $\Pi_\text{disc}(G)$.
-%\[\pi_1(G,{\bar e}) \to \Pi_\text{et}(G) \to \Pi_\text{et}(G)_{\Gal(\bFq/\Fq)} = \Pi_\text{disc}(G)\]
 Using this fact, one can show that the category of discrete isogenies to $G$ is a Galois category,
@@
 \section{Commutative \'etale group schemes} \label{sec:etale}
-%\input{etale-1}
-%In this section we establish a fundamental property of character
-% sheaves on commutative \'etale group schemes over $\Fq$ that are
-% geometrically finitely generated.
 
@@
 Let $X$ be an abelian group equipped with an action of $\Weil{}$.
-% and write $\Frob{} = \Frob{}$. 
  Then
@@
 \end{equation}
-%(It is clear that $\QCiso{0}$ is trivial.)
  Note that we found the groups $\QCiso{G^0}$
@@
 
-  Extensions of $G^0(\bFq)$ by $A(\bFq)$, such as $A(\bFq) \to B(\bFq) \to G^0(\bFq)$,
+  Extensions of $G^0(\bFq)$ by $A(\bFq)$, such as $B(\bFq)$,
   correspond to classes in $\Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq))$.
@@
 
-%\input{snake}
 \begin{theorem}\label{thm:snake}
@@
   In order to apply the snake lemma, we need to show that the top row is exact at $\QCiso{G}$ and $\QCiso{G^0}$:
-  the surjectivity of $\QCiso{G} \to \QCiso{G^0}$ follows from Proposition~\ref{prop:restriction} while exactness at $\QCiso{G}$ is given by Proposition~\ref{prop:middleexact}.
-%  
+  the surjectivity of $\QCiso{G} \to \QCiso{G^0}$ follows from Proposition~\ref{prop:restriction}
+  while exactness at $\QCiso{G}$ is given by Proposition~\ref{prop:middleexact}.
   Now Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}
@@
 \[
-%\begin{tikzcd}
 \Gr_n : \partop{\text{Schemes}}{\text{lft over $\OK$}} \to \partop{\text{Schemes}}{\text{lft over $\Fq$}}
-%\end{tikzcd}
 \]
@@
 for every positive integer $n$,
-\begin{equation}%\label{weilgreenberg}
+\begin{equation}
 \Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)
@@
 \begin{proof}
-Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} to lft-Néron models
-we see that $\Res_{\OKp/\OK}(\TTp)$ is a Néron model for $\Res_{K'/K}(T')$.
+Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} to locally finite type Néron models,
+one may show that $\Res_{\OKp/\OK}(\TTp)$ is a Néron model for $\Res_{K'/K}(T')$.
 By the Néron mapping property, the canonical closed immersion
@@
   \item $\alpha$ is $\Gal(L/K)$-equivariant relative to $\beta$, and
-  %: $\alpha(\gamma x) = \beta(\gamma) \alpha(x)$ for $\gamma \in \Gal(L/K)$ and $x \in \OL/\pi_K^N \OL$,
   \item $\phi$ is $\Gal(L/K)$-equivariant relative to $\beta$.
@@
 
-%\printindex
-
 \bibliographystyle{amsalpha}
-%\DeclareRobustCommand{\VAN}[3]{#3}
 \bibliography{Biblio}

### 2013-10-23 shanghai.tex
fiddling
Fixed a few botched instances of function--sheaf.

@@
 %%%%%%%%%%%%%%%%%% HEADING %%%%%%%%%%%%%%%%%%
-\title[Function--sheaf dictionary for local tori]{A function--sheaf dictionary for algebraic tori over local fields}
+\title[A function--sheaf dictionary for local tori]{A function--sheaf dictionary for algebraic tori over local fields}
 \date{\today}
@@
 \classification{14L15 (primary), 11G25, 14F05, 14D24, 11S31 (secondary)}
-\keywords{quasicharacters, quasicharacter sheaves, algebraic tori, Greenberg transforms, N\'eron models, local fields}
+\keywords{quasicharacters, quasicharacter sheaves, algebraic tori, Greenberg transforms, N\'eron models, local fields, group schemes}
 
@@
 the set of isomorphism classes $\QCiso{G}$ forms a group.
-Motivated by the sheaf--function dictionary for commutative, connected
+Motivated by the function--sheaf dictionary for commutative, connected
 algebraic groups \cite{deligne:SGA4.5}*{sommes trig.}, 
@@
 
-In Part 2 we use Theorem~\ref{thm:snake} to make a sheaf--function dictionary
+In Part 2 we use Theorem~\ref{thm:snake} to make a function--sheaf dictionary
 for algebraic tori over local fields.  Let $K$ be a non-archimedian local field
@@
 Our quasicharacter sheaves evolved from this notion, and Theorem~\ref{thm:snake}
-is a direct generalization of the sheaf--function dictionary to the case of certain commutative
+is a direct generalization of the function--sheaf dictionary to the case of certain commutative
 group schemes which are not necessarily connected or finite type.  The main use
@@
 Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism,
-one direction of the sheaf--function dictionary.
+one direction of the function--sheaf dictionary.
 We define pullbacks and products of quasicharacter sheaves in Section~\ref{sec:pullback}, and use
@@
 
-\end{acknowledgements}
-
-\begin{thanks}
-
 We also gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
@@
 
-\end{thanks}
+\end{acknowledgements}
 
@@
 
-When $G$ is connected, we may apply the classic sheaf--function dictionary.  In order to do so,
+When $G$ is connected, we may apply the classic function--sheaf dictionary.  In order to do so,
 however, we must relate our notion of quasicharacter sheaf to the sheaf side of the standard dictionary.
@@
 
-  To show that $L_G(f,\psi) \iso (\qcs{L}_0,\mu_0)$ we simply apply the sheaf--function dictionary
+  To show that $L_G(f,\psi) \iso (\qcs{L}_0,\mu_0)$ we simply apply the function--sheaf dictionary
   as follows \citelist{\cite{laumon:87a}*{1.1.3} \cite{deligne:SGA4.5}*{sommes trig.}}.
@@
 
-\section{A function--function dictionary for tori over local fields} \label{sec:quasichar}
+\section{A function--sheaf dictionary for tori over local fields} \label{sec:quasichar}
 

### 2013-10-24 shanghai.tex
pdfoutput for arXiv
Replaced `admissible characters of T(K)' with 'quasicharacters of T(K)' in the last section.

@@
 \documentclass{compositio}
+\pdfoutput=1
 
@@
 on the Greenberg transform of the Néron model of $T$ 
-and admissible characters of $T(K)$.
+and quasicharacters of $T(K)$.
 When coupled with the reciprocity map $\text{rec}_T $ for $T$, 

### 2013-11-08 shanghai.tex
Added Nicaise-Sebag and Bertrapelle-Gonzales

@@
 See
-\citelist{\cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1} \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} \cite{stasinski:12a}*{\S 2}}
-for more background on the Greenberg functor.
+\citelist{
+\cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1} \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} 
+\cite{nicaise-sebag:motivicSerre}*{\S 2.2}
+\cite{bertrapelle-gonzales}
+}
+for the definition and fundamental properties of the Greenberg functor.
 
@@
 \begin{proof}
-First, note that since $\Res_{\OKp/\OK}(\TTp)$ 
-is a scheme over $\OK$, 
-the Greenberg transform $\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)$ 
-is obtained by base change along $\OK \to \OK/\pK^n$ 
-followed by the Greenberg functor over the Artinian ring $\OK/\pK^n$. 
-On the other hand, since $\TTp$ is a scheme over $\OKp$, 
-the Greenberg transform $\Gr_{en}(\TTp)$ is defined by base change along 
-$\OKp \to \OKp/\pKp^{en}$ 
-followed by the Greenberg functor over the Artinian ring $\OKp/\pKp^{en}$. 
-Note also that 
-\begin{equation}\label{nem}
-\OKp \otimes_{\OK} \OK/\pK^n \iso \OKp/\pKp^{en}.
-\end{equation}
-
-To prove the lemma, we may employ the functor of points perspective 
-and exhibit an isomorphism of functors from 
-$\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)$ 
-to $\Res_{k'/k} \Gr_{en}(\TTp)$ as functors 
-from the category of $\Fq$-algebras to the category of groups.
-To that end, let $R$ be any $\Fq$-algebra and 
-let $\WW$ be the Witt functor from the category of $\Fq$-algebras to rings. 
-By the definition of the Greenberg transform, the Weil restriction functor and \eqref{nem},
-\[
-\begin{aligned}
-\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)(R)
-&= \Res_{\OKp/\OK}(\TTp)\left( \OK/\pK^n \otimes_{\WW(k)} \WW(R)\right)\\
-&= \TTp\left(\OKp \otimes_{\OK} \OK/\pK^n \otimes_{\WW(k)} \WW(R)\right)\\
-&= \TTp\left(\OKp /\pKp^{en} \otimes_{\WW(k)} \WW(R)\right);
-\end{aligned}
-\]
-on the other hand,
-\[
-\begin{aligned}
-\Res_{k'/k} \Gr_{en}(\TTp)(R)
-&= \Gr_{en}(\TTp) (k'\otimes_{k} R)\\
-&= \TTp\left( \OKp /\pKp^{en} \otimes_{\WW(k')} \WW(k'\otimes_{k} R)\right)\\
-&= \TTp\left( \OKp /\pKp^{en} \otimes_{\WW(k')} \WW(k') \otimes_{\WW(k)} \WW(R)\right)\\
-&= \TTp\left( \OKp /\pKp^{en} \otimes_{\WW(k)} \WW(R)\right).
-\end{aligned}
-\]
-So the group isomorphism 
-\[
-\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)(R) \to \Res_{k'/k} \Gr_{en}(\TTp)(R)
-\]
-is apparent, as are the commuting group homomorphisms
-\[
-\begin{tikzcd}
-\arrow{d} \Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)(R) \arrow{r}{\iso} & \arrow{d} \Res_{k'/k} \Gr_{en}(\TTp)(R)\\
-\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)(R') \arrow{r}{\iso} & \Res_{k'/k} \Gr_{en}(\TTp)(R'),
-\end{tikzcd}
-\]
-for every map $R\to R'$ of $\Fq$-algebras.
+This follows from \cite{bertrapelle-gonzales:Greenberg}*{Prop. 6.3} after observing that 
 \end{proof}

### 2013-11-09 shanghai.tex
Modified the proof of Lemma 14.1 to point to Bertrapelle-Gonzales and thanked them at the end of the Introduction.

@@
 for allowing us to hijack much of our Research in Teams meeting at BIRS into a discussion of
-quasicharacter sheaves.  Their knowledge and help have been invaluable.
+quasicharacter sheaves; their knowledge and help have been invaluable. 
+We also thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and for pointing us to a proof of Lemma~\ref{lemma:wrK}.
 
 We also gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
-and of the National Science and Engineering Research Council,
+and the National Science and Engineering Research Council,
 as well the hospitality of the Banff International Research Station during our weeklong stay in May 2012.
@@
 \cite{nicaise-sebag:motivicSerre}*{\S 2.2}
-\cite{bertrapelle-gonzales}
+\cite{bertrapelle-gonzales:Greenberg}*{\S 5}
 }
-for the definition and fundamental properties of the Greenberg functor.
+for the definition and fundamental properties of the Greenberg functor as it is used here.
 
@@
 \begin{proof}
-This follows from \cite{bertrapelle-gonzales:Greenberg}*{Prop. 6.3} after observing that 
+First, note that since $\Res_{\OKp/\OK}(\TTp)$ 
+is a scheme over $\OK$, 
+the Greenberg transform $\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)$ 
+is obtained by base change along $\OK \to \OK/\pK^n$ 
+followed by the Greenberg functor over the Artinian ring $\OK/\pK^n$. 
+On the other hand, since $\TTp$ is a scheme over $\OKp$, 
+the Greenberg transform $\Gr_{en}(\TTp)$ is defined by base change along 
+$\OKp \to \OKp/\pKp^{en}$ 
+followed by the Greenberg functor over the Artinian ring $\OKp/\pKp^{en}$. 
+Note also that 
+\begin{equation}\label{nem}
+\OKp \otimes_{\OK} \OK/\pK^n \iso \OKp/\pKp^{en}.
+\end{equation}
+Now Lemma~\ref{lemma:wrK} follows from \cite{bertrapelle-gonzales:Greenberg}*{Prop.
+6.3} after observing that  $\TTp \times_\Spec{\OKp} \Spec{\OKp/\pKp^{en}}$ is admissible relative to $\Spec{\OKp/\pKp^{en}} \to \Spec{\OK/\pK^n}$, cf.
+\cite{bertrapelle-gonzales:Greenberg}*{Rem 2.9 (a)}.
 \end{proof}

### 2014-01-20 shanghai.tex
v2 for arXiv
Replaced Category/iso with \pi_0(Category). What do you think?
Fixed an internal reference

@@
 \newcommand{\QCf}{{\QC_f}}
-\newcommand{\QCiso}[1]{\QC(#1)_{/\textit{iso}}}
-\newcommand{\QCbiso}[1]{\QCb(#1)_{/\text{iso}}}
-\newcommand{\QCfiso}[1]{\QCf(#1)_{/\text{iso}}}
+\newcommand{\QCiso}[1]{\pi_0 (\QC(#1))}
+\newcommand{\QCbiso}[1]{\pi_0(\QCb(#1))}
+\newcommand{\QCfiso}[1]{\pi_0(\QCf(#1))}
 \newcommand{\trFrob}[1]{t_{#1}}
@@
   $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes over $\Fq$
-  \citelist{\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276} \cite{stasinski:12a}*{\S 4}}.
+  \citelist{\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276} \cite{bertrapelle-gonzales:Greenberg}*{Prop. 7.2}}.
   We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.
@@
 while the second part shows that trace of Frobenius is a natural transformation
-$t_{ - ,n} : F_1 \to F_2$. When further combined with Lemma~\ref{prop:product},
+$t_{ - ,n} : F_1 \to F_2$. When further combined with Proposition~\ref{prop:product},
 we see that $F_1$ is an additive functor and $t_{ - ,n}: F_1 \to F_2$ is a

### 2014-01-21 shanghai.tex
Improved the language around the example at the end of Part 1.

@@
 
+Using Corollary~\ref{cor:bounded-and-finite} we can easily see that, in general, neither of the full subcategories
+$\QCf(G) \subset \QCb(G) \subset \QC(G)$ are equivalences.
 For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$.
-Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ 
-and let $\qcs{L}$ be a quasicharacter sheaf in the isomorphism class 
-corresponding to $\chi$ under Theorem~\ref{thm:snake}.
-Then $\qcs{L}$ is not a bounded quasicharacter sheaf since the image of $\chi$ is not
-bounded.  If $\chi(1) = 1+\ell$, then the image of $\chi$ is bounded but not finite.  For
-the corresponding quasicharacter sheaf $\qcs{L}$, the stalk at the component $1$ is defined
-by a pro-\'etale cover rather than an \'etale cover and thus $\qcs{L}$ is not finite.
+If $\chi : \ZZ \to \EEx$ is the quasicharacter of $G(\Fq)$ determined by $\chi(1) = \ell$ 
+and if $\qcs{L}$ is a quasicharacter sheaf on $G$ in the isomorphism class 
+corresponding to $\chi$ under Theorem~\ref{thm:snake},
+then $\qcs{L}$ is not a bounded quasicharacter sheaf since the image of $\chi$ is not
+bounded.  
+On the other hand, if $\chi : \ZZ \to \EEx$ is the quasicharacter of $G(\Fq)$ determined by $\chi(1) = 1+\ell$ 
+and if $\qcs{L}$ is a quasicharacter sheaf on $G$ in the isomorphism class 
+corresponding to $\chi$ under Theorem~\ref{thm:snake},
+then $\qcs{L}$ is a bounded quasicharacter sheaf but not a finite quasicharacter sheaf
+since the image of $\chi$ is bounded but not finite.
+In this latter case the stalk of $\qcs{L}$ at the component $1$ is defined
+by a pro-\'etale cover rather than an \'etale cover.
 

### 2014-01-22 dictionary.tex
Just to see what it would like like, I've broken our paper into two parts: dictionary and geometrization. Please let me know what you think.

--- 2014-01-21 shanghai.tex
@@
 % !TEX encoding = UTF-8 Unicode
-\documentclass{compositio}
+%\documentclass{compositio}
+\documentclass{amsart}
 \pdfoutput=1
@@
 %%%%%%%%%%%%%%%%%% HEADING %%%%%%%%%%%%%%%%%%
-\title[A function--sheaf dictionary for local tori]{A function--sheaf dictionary for algebraic tori over local fields}
+\title[The function--sheaf dictionary]{The function--sheaf dictionary for smooth commutative group schemes over finite fields with finitely generated geometric component group}
 \date{\today}
@@
 \address{Pacific Institute for the Mathematical Sciences at the University of Calgary}
-\classification{14L15 (primary), 11G25, 14F05, 14D24, 11S31 (secondary)}
-\keywords{quasicharacters, quasicharacter sheaves, algebraic tori, Greenberg transforms, N\'eron models, local fields, group schemes}
+%\classification{14L15 (primary), 11G25, 14F05, 14D24, 11S31 (secondary)}
+%\keywords{quasicharacters, quasicharacter sheaves, algebraic tori, Greenberg transforms, N\'eron models, local fields, group schemes}
 
@@
   of quasicharacter sheaves on $G$ is canonically isomorphic to the group
-  of characters of $G(\Fq)$. Then, for any non-archimedean local field $K$
-  and any algebraic torus $T$ over $K$, we use this result to produce a functorial
-  isomorphism between quasicharacters of $T(K)$ and isomorphism
-  classes of quasicharacter sheaves on the Greenberg transform of the Néron
-  model of $T$.
+  of characters of $G(\Fq)$. 
    \end{abstract}
@@
 
-In this paper we find a dictionary between quasicharacters of algebraic tori over local fields and quasicharacter sheaves. 
-What is a quasicharacter sheaf?
-Let $G$ be a smooth, commutative group scheme locally of finite
-type over a finite field $\Fq$; $G$ need not be reductive, connected, or of
-finite type over $\Fq$. Fix a prime $\ell$ invertible in $\Fq$
-and write $m : \GxG \to G$ for the multiplication morphism,
-$\bG$ for the base change of $G$ to $\bFq$ and
-$\Frob{G} : \bG \to \bG$ for the Frobenius automorphism.
+The sheaf--function dictionary for connected commutative algebraic groups over finite fields translates characters into local systems  \cite{deligne:SGA4.5}*{sommes trig.}.
+More precisely, let $G$ be a commutative group scheme over a finite field $\Fq$, let $\ell$ be any prime invertible in $\Fq$ and let $\chi : G(\Fq) \to \EEx$ be any character.
+Using little more than the Lang map for $G$, $\chi$ determines an $\ell$-adic local system $\qcs{L}$ on $G$ from which the character $\chi$ can be recovered using the Frobenius automorphism of $\bG$, the base change of $G$ to $\bFq$.
+While this recovery process applies to all $\ell$-adic local systems $\qcs{L}$ on $G$, those that produce characters of $G(\Fq)$ are distinguished by a simple property: there exists an isomorphism
+\begin{equation}\label{introbox}
+m^* \qcs{L} \iso \qcs{L} \boxtimes \qcs{L}
+\end{equation}
+ of $\ell$-adic local systems on $G$, where $m : G\times G \to G$ is the multiplication map for $G$.
+The sheaf--function dictionary for $G$ identifies a monoidal category of $\ell$-adic local systems on $G$ such that the group of isomorphism classes in this category is canonically identified with the $\ell$-adic character group of $G(\Fq)$, thus providing the geometrization and categorification of characters of $G(\Fq)$.
+
+Although hidden in the discussion above, the connectness of $G$ played a crucial role in the geometrization and categorification of characters of $G(\Fq)$.
+So it is natural to ask if the sheaf--function dictionary can be generalized to not-necessarily connected commutative algebraic groups over finite fields.
+In this paper we answer that question.
+
+In fact, we show much more by exhibiting a sheaf--function dictionary, in the sense above, for any smooth commutative group scheme $G$, locally of finite type over a finite field $\Fq$, 
+for which the geometric component group of $G$ is finitely generated; we call such group schemes $\QC$-schemes.
+To do this we must pass from $\ell$-adic local systems on a $\QC$-scheme $G$ to Weil local systems on $\bG$ 
+and also keep track of the isomorphisms \eqref{introbox} (existence of such an isomorphism is not enough), leading to the notation of {\it quasicharacter sheaves on $G$}.
+
 A quasicharacter sheaf on $G$ is a triple $\qcs{L}\ceq
 (\gqcs{L},\mu,\phi)$ where $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ of rank~one and $\mu: m^*
-\gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms;
-$\mu$ and $\phi$ are required to satisfy natural conditions explained below.
-
-In Part 1 of this paper we study the category $\QC(G)$ of quasicharacter sheaves on $G$.
-Since $\QC(G)$ is a rigid monoidal category
-the set of isomorphism classes $\QCiso{G}$ forms a group.
-Motivated by the function--sheaf dictionary for commutative, connected
-algebraic groups \cite{deligne:SGA4.5}*{sommes trig.}, 
-we explore the trace of Frobenius morphism
-\[
-\QCiso{G} \to \Hom(G(\Fq), \EEx)
-\]
-and show in Theorem~\ref{thm:snake} that it is an isomorphism, 
-assuming that the geometric component group of $G$ is finitely generated.
-
-In Part 2 we use Theorem~\ref{thm:snake} to make a function--sheaf dictionary
-for algebraic tori over local fields.  Let $K$ be a non-archimedian local field
-with finite residue field $\Fq$; we place no restriction on the characteristic of $K$.
-Write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$.
-Let $T$ be a torus defined over $K$.  The N\'eron model $\TT$ of $T$
-is a smooth group scheme over $\OK$ with generic fibre $T$ and a canonical isomorphism
-$\TT(\OK) \cong T(K)$.  For each positive integer $n$, let $\GN{T}_n$ be the
-Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^n}$; the commutative
-group scheme $\GN{T}_n$ plays the r\^{o}le of $G$, above.  Theorem~\ref{thm:application}
-allows us to translate characters $T(K)$ of depth less than $n$ into quasicharacter sheaves on $\GN{T}_n$:
-\[
-\QCiso{\GN{T}_n} 
-\iso
-\Hom_{< n}(T(K),\EEx).
-\]  
-We also describe a pro-group scheme $\GN{T}$ 
-simultaneously geometrizing all quasicharacters ({\it i.e.}, finite-depth characters) of $T(K)$.
-
-While we have not yet fully explored the applications of such a geometrization, we want to highlight
-some of the potential benefits of Theorem~\ref{thm:application} here. 
-Characters on $T$ have limited
-functoriality: they can be pulled back along maps to $T$, but it is less clear what to do with them
-in the presence of maps from $T$ to other groups.  Sheaves, on the other hand, come
-equipped with a host of functors, including pushforward. 
-We hope to use this to our advantage as we work toward an adaptation of 
-Lusztig's theory of characters sheaves to the study of characters of 
-admissible representations of reductive $p$-adic groups that extends beyond the case of $p$-adic tori.
-
-DeBacker and Reeder have recently applied Deligne-Lusztig 
-representations to part of the depth-zero part of the
-local Langlands correspondence \cite{reeder-debacker:09a}.
-Deligne-Lusztig theory also plays an important role in 
-Waldspurger's work on nilpotent distributions \cite{waldspurger:01}.
-After developing Deligne-Lusztig representations, 
-the next step Lusztig took in studying representations
-of finite groups of Lie type was to introduce character sheaves for reductive groups over $\Fq$.
-We hope that our quasicharacter sheaves 
-can provide a stepping stone to a similar theory for
-representations of $p$-adic groups, especially
-in the positive-depth case.
-
-The scope of the Langlands program has grown explosively in the past several decades, and
-different parts of it apply to different kinds of representations.  In particular, the classic local Langlands
-correspondence addresses complex (or $\ell$-adic) representations of real and $p$-adic groups, while
-the geometric Langlands program aims at representations of groups in characteristic $p$.  The fact that
-characteristic $p$ group schemes arise as the space underlying quasicharacter sheaves, regardless of
-the characteristic of $K$, provides a potential bridge allowing the methods of the geometric Langlands
-program to be applied to the classic context.
-
-Finally, we are tantalized by the possibility of providing an alternate perspective on local class field theory
-through quasicharacter sheaves.  The local Langlands correspondence for tori provides an isomorphism
-$
-\Hh^1(\Weil{K}, \hat{T}_\ell) \cong \Hom(T(K), \EEx)
-$. 
-A geometric description of the resulting isomorphism $\Hh^1(\Weil{K}, \hat{T}_\ell) \cong \QCiso{\GN{T}}$
-would yield a different description of the Artin reciprocity map.
-
-We want to situate the choice of term ``quasicharacter sheaf'' in a historical context.
-Analogous sheaves on connected, commutative algebraic groups were first studied
-by Deligne \cite{deligne:SGA4.5}*{sommes trig.} and many people have since referred to such objects
-as character sheaves; see for example, \cite{kamgarpour:09a}. 
-Our quasicharacter sheaves evolved from this notion, and Theorem~\ref{thm:snake}
-is a direct generalization of the function--sheaf dictionary to the case of certain commutative
-group schemes which are not necessarily connected or finite type.  The main use
-of the term character sheaf is of course due to Lusztig. It is applied to certain perverse
-sheaves on connected reductive algebraic groups over algebraically closed fields in
+\gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms satisfying natural compatibilty conditions.
+The main result of this paper is the following statement (see Theorem~\ref{thm:snake}, which says more):
+the category $\QC(G)$ of quasicharacter sheaves on $G$
+is a rigid monoidal category and that the trace of Frobenius morphism provides an isomorphism
+\begin{equation}
+\QCiso{G} \to \Hom(G(\Fq), \EEx).
+\end{equation}
+In this way we find the geometrization and categorification of characters of $G(\Fq)$.
+
+A simple example will illustrate some of the issues that arise when extending the sheaf--function dictionary to disconnected algebraic groups over finite fields.
+Consider the etale group scheme $G = \ZZ_{\Fq}$ over $\Fq$; this is a $\QC$-scheme.
+Characters of $G(\Fq) = \ZZ$ are neither finite nor bounded, in general; for example, the $\ell$-adic character $\ZZ \to \EEx$ defined by $1 \mapsto 1+ \ell$ is not finite but bounded, which the character $\ZZ \to \EEx$ defined by $1 \mapsto \ell$ is unbounded.
+As we show in the paper, local systems on $G$ cannot be used to geometrize either of these characters; however, quasicharacter sheaves do the job, handily.
+We remark that such characters arise when considering unramified quasicharacters of the $p$-adic group $\Qp^\times$.
+This example informs our choice of the term ``quasicharacter sheaf''.
+Indeed, in \cite{cunningham-roe:p-adic_tori} we use this paper to geometrize and categorify all quasicharacters of all algebraic tori over all local fields.
+
+We also want to situate the choice of term ``quasicharacter sheaf'' in a historical context.
+Some people refer to local systems satisfying \eqref{introbox} as as character sheaves; 
+see for example, \cite{kamgarpour:09a}. 
+As explained above, quasicharacter sheaves evolved from this notion,
+with an eye toward quasicharacters of $p$-adic groups.
+However, the main use of the term character sheaf is of course due to Lusztig. 
+It is applied to certain perverse sheaves on connected reductive algebraic groups over algebraically closed fields in
 \cite{lusztig:85a}*{Def.~2.10} and to certain perverse sheaves on reductive groups
-over algebraically closed fields with cyclic component groups in the series of papers
+over algebraically closed fields with finite cyclic component groups in the series of papers
 beginning with \cite{lusztig:disconnected1}.  
@@
 We close the introduction with a more detailed description of the structure of this paper.
-In Section~\ref{sec:category} we define quasicharacter sheaves and give an interpretation of
+After setting some notation in Section~\ref{sec:QCschemes}, in Section~\ref{sec:category} we define quasicharacter sheaves and give an interpretation of
 them as Weil sheaves with certain properties.
@@
 induces an essentially surjective functor of quasicharacter sheaves.
-Section~\ref{sec:snake} closes out Part \ref{part1} with the proof of the main theorem: trace of Frobenius
+Section~\ref{sec:snake} presents the main theorem of this paper: trace of Frobenius
 is an isomorphism for $G$ as long as the geometric component group is finitely generated.
 
-In Section~\ref{sec:GN} we review the Greenberg transform of N\'eron models of tori, which produces
-group schemes over $\Fq$ from algebraic tori $T$ over $K$.
-Section~\ref{sec:bdchar} then uses Theorem~\ref{thm:snake} to give a geometrization of characters of $T$
-of bounded depth.
-We give a reinterpretation of this result in Section~\ref{sec:quasichar}, using a limit process to simultaneously
-geometrize all quasicharacters of $T$.  Sections~\ref{sec:bdchar}, \ref{sec:quasichar} and \ref{sec:wrK} also include
-functoriality results that we hope to use in a future discussion of 
-local class field theory.
-In Section~\ref{sec:transfer} we discuss a transfer principle which allows
-a geometric transfer of characters between characteristic $p$ tori and characteristic $0$ tori.
-We close the paper with Section~\ref{sec:reciprocity}, in which we suggest that quasicharacter
-sheaves may play a key role in a geometric and categorical form of the local Langlands
-correspondence for algebraic tori over local fields.
-
-\begin{acknowledgements}
-
+%\begin{acknowledgements}
+\subsection*{Acknowledgements}
 We would like to thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
@@
 quasicharacter sheaves; their knowledge and help have been invaluable. 
-We also thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and for pointing us to a proof of Lemma~\ref{lemma:wrK}.
+%We also thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and for pointing us to a proof of Lemma~\ref{lemma:wrK}.
 
@@
 
-\end{acknowledgements}
-
-\part{Smooth commutative group schemes over finite fields} \label{part1}
+%\end{acknowledgements}
+
+\section{Smooth commutative group schemes over finite fields}\label{sec:QCschemes}
 
@@
 
-\section{The function--sheaf dictionary for non-connected group schemes}
+\section{The function--sheaf dictionary for disconnected group schemes}
 \label{sec:snake}
@@
 
-\part{Application to quasicharacters of algebraic tori over local fields}
-
-Recall that $\Fq$ is a finite field.
-Let $K$ be a non-archimedean local field with residue field $\Fq$.
-We place no restriction on the characteristic of $K$. 
-We write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$. 
-Let $T$ be an algebraic torus over $K$; the filtrations defined by Moy-Prasad and Yu \cite{yu:03a}*{\S 5}
-allow us to define the depth of character $\chi$ as the infimum of the $r$ so that $\chi$ vanishes on $T(K)_r$.
-We write $\Hom_{< n}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $n$ 
-and $\Hom_{\text{qc}}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth;
-we call these quasicharacters of $T(K)$, following \cite{tate:67a}*{2.3}.
-
-\section{Greenberg of N\'eron}
-\label{sec:GN}
-
-A N\'eron model for $T$ is a smooth group scheme $\TT$ over $\OK$ with generic fiber $T$
-that satisfies the N\'eron mapping property: if $S$ is any smooth scheme over $\OK$ then every morphism
-$S_\eta \to T$ over $K$ extends uniquely to a morphism $S \to \TT$.  N\'eron models exist for any torus
-$T$ \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch 10.1, Thm 6} and are unique up to isomorphism;
-$\TT$ is separated, commutative, locally finite type over $\OK$ and satisfies $\TT(\OK) = T(K)$.
-
-We will also need the Greenberg functor \citelist{\cite{greenberg:61} \cite{greenberg:63a}}:
-a functor from the category of schemes locally of finite type 
-over an Artinian local ring with perfect residue field $k$ 
-to the category of schemes locally of finite type over $k$. 
-This functor respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components.
-See
-\citelist{
-\cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1} \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} 
-\cite{nicaise-sebag:motivicSerre}*{\S 2.2}
-\cite{bertrapelle-gonzales:Greenberg}*{\S 5}
-}
-for the definition and fundamental properties of the Greenberg functor as it is used here.
-
-\begin{definition}\label{def:Grn}
-For any local field $K$ with residue field $\Fq$ and for any positive integer $n$, let
-\[
-\Gr_n : \partop{\text{Schemes}}{\text{lft over $\OK$}} \to \partop{\text{Schemes}}{\text{lft over $\Fq$}}
-\]
-be the functor produced by precomposing pullback along $\OK \to \OK/\pK^n$ with the Greenberg functor.
-\end{definition}
-
-The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a
-natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$ between additive functors.
-For a given Néron model $\TT$ of $T$, set
-\begin{align*}
- \GN{T}_n &\ceq \Gr_n(\TT), \\
- f_n &\ceq P_n(\TT).
-\end{align*}
-
-We list some fundamental properties of $f_n$ and $\GN{T}_n$ for further use:
- \begin{enumerate}
-  \labitem{(GN.0)}{truncation}
-  $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes over $\Fq$
-  \citelist{\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276} \cite{bertrapelle-gonzales:Greenberg}*{Prop. 7.2}}.
-  We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.
-  \labitem{(GN.1)}{smooth} 
-  $\GN{T}_n$ is a $\QC$-scheme. 
-  Note that $\underline{T}$ is a smooth group scheme over $\OK$, by construction. 
-  Since smoothness is preserved under base change, 
-  $\TT_n \ceq \underline{T} \times_\Spec{\OK} \Spec{\OK/\pK^n}$ 
-  is a smooth group scheme over an Artinian ring with perfect residue field. 
-  The Greenberg functor preserves smoothness, 
-  so $\GN{T}_n$ is a smooth group scheme locally of finite type over $\Fq$. 
-  The Greenberg functor takes the geometric identity component of $\TT_n$ 
-  to the geometric identity component of $\GN{T}_n$.
-  In fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$ and
-  this group is finitely generated \cite{xarles:93a}*{2.18}.
-  \labitem{(GN.2)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
-\end{enumerate}
-
-\section{Application to quasicharacters of bounded depth} \label{sec:bdchar}
-
-We now apply the results of Part~\ref{part1} to characters of $T(K)$.
-
-\begin{theorem}\label{thm:application}
-Let $n$ be a positive integer.
-For every algebraic torus $T$ over $K$, the trace of Frobenius 
-  \[
-\trFrob{T,n}:  \QCiso{\GN{T}_n} \to \Hom_{< n}(T(K),\EEx)
-  \]
-is an isomomorphism. 
-Moreover, the isomorphism $\trFrob{T,n}$ is a natural transformation
-between the additive functors
-\begin{enumerate}
-\item[$F_1$:] $T \mapsto \QCiso{\GN{T}_n}$
-\item[$F_2$:] $T \mapsto \Hom_{<n}(T(K),\EEx)$
-\end{enumerate}
-from the additive category of algebraic tori over $K$ to the category of abelian groups.
-\end{theorem}
-
-\begin{proof}
-  By \ref{smooth}, we may apply Theorem~\ref{thm:snake} to
-  $\GN{T}_n$ which provides a canonical isomorphism
-  $\QCiso{\GN{T}_n} \iso \GN{T}_n(\Fq)^*$.
-  By \ref{points}, $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$.
-  Then we recall that the filtration of $T(K)$ used to
-  define depth has the property that $\TT(\OK/\pK^n) \cong T(K) / T(K)_n$
-  \cite{yu:03a}*{Prop 5.2}, so characters of $\GN{T}_n(\Fq)$ 
-  are in bijection with characters of $T(K)$ vanishing on $T(K)_n$. 
-  This shows that $\trFrob{T,n}$ is an isomorphism.
-
-  The definition of $F_1$ depends 
-  on the choice of a Néron model for every algebraic torus $T$.
-  However, since Néron models are unique up to unique isomorphism,
-  the isomorphism class of $\GN{T}_n$ is uniquely determined by $T$
-  and the group of isomorphism classes of objects in $\QC(\GN{T}_n)$ 
-  is uniquely determined by $T$. 
-  To define $F_1$ on morphisms one uses the Néron mapping property.
-
-  Finally, we show that $\trFrob{T,n}$ is functorial.
-The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
-while the second part shows that trace of Frobenius is a natural transformation
-$t_{ - ,n} : F_1 \to F_2$. When further combined with Proposition~\ref{prop:product},
-we see that $F_1$ is an additive functor and $t_{ - ,n}: F_1 \to F_2$ is a
-natural transformation between additive functors.
-\end{proof}
-
-\section{A function--sheaf dictionary for tori over local fields} \label{sec:quasichar}
-
-In this section we package the isomorphisms of Theorem~\ref{thm:application} into
-a single dictionary.
-
-\begin{definition}\label{def:objGN}
-The \emph{Greenberg transform of the N\'eron model of $T$} 
-is the pro-group scheme over $\Fq$ given by 
-$\GN{T} \ceq \varprojlim_{n\in \ZZ_{>0}} \GN{T}_{n}$, 
-with reference to the family of  surjective morphisms of 
-$\Fq$-group schemes $f_n : \GN{T}_{n+1} \to \GN{T}_n$.
-\end{definition}
-
-For any  ordered pair of positive integers $n< m$ define 
-$f_{n\leq m} : \GN{T}_{m} \to \GN{T}_{n}$ 
-by $f_{n\leq m}\ceq f_n \circ f_{n+1} \circ \cdots \circ f_{m-1}$; 
-also set $f_{n\leq n} \ceq \id_{\GN{T}_n}$.
-Note that $f_{n\leq m}:  \GN{T}_{m} \to \GN{T}_{n}$ is a surjective morphism 
-of group schemes over $\Fq$.
-Let 
-\[
-f_{n\leq m}^* : \QC(\GN{T}_n) \to \QC(\GN{T}_{m})
-\]
-be the functor produced by applying Proposition~\ref{prop:pullback} to $f_{n\leq m}$.
-We now define a category which allows us to extend the notion 
-of quasicharacter sheaf to the pro-group scheme $\GN{T}$.
-
-\begin{definition}\label{def:catGN}
-An object in $\QC(\GN{T})$ is a triple $(n, \{\qcs{L}_i\}_{i \ge n}, \{\alpha_{i \le j}\}_{j \ge i \ge n})$, where $n$
-is a positive integer, each $\qcs{L}_i$ is a quasicharacter sheaf on $\GN{T}_i$ and each
-$\alpha_{i \le j} : \qcs{L}_j \to f^*_{i \le j} \qcs{L}_i$ is an isomorphism.  We require $\alpha_{i \le i}$ to be
-the identity and that the $\alpha_{i \le j}$ are compatible with each other.  If $\qcs{L} \ceq (n, \{\qcs{L}_i\}, \{\alpha_{i \le j}\})$
-and $\qcs{L}' \ceq (m, \{\qcs{L}'_i\}, \{\alpha'_{i \le j}\})$ are objects then $\Hom(\qcs{L}, \qcs{L}')$ is the set
-of equivalence classes of pairs $(k, \{\beta_i\}_{i \ge k})$.  Here $k \ge m, n$ and the $\beta_i : \qcs{L}_i \to \qcs{L}'_i$ are
-morphisms of quasicharacter sheaves so that
-\[
-\begin{tikzcd}
-\qcs{L}_j \rar{\alpha_j} \dar{\beta_i} & f^*_{i \le j} \qcs{L}_i \dar{f_{i \le j}^*\beta_j} \\
-\qcs{L}'_j \rar{\alpha_j} & f^*_{i \le j} \qcs{L}'_i
-\end{tikzcd}
-\]
-commutes for all $j \ge i \ge k$.  We identify two such pairs $(k, \{\beta_i\})$ and $(l, \{\gamma_i\})$ if $\beta_i = \gamma_i$
-for sufficiently large $i$.  Identities and composites are defined in the natural way.
-
-If $n$ is a positive integer and $\qcs{L}_n \in \QC(\GN{T}_n)$ then we may define an object
-\[
-[\qcs{L}_n] \ceq (n, \{f_{n \le i} \qcs{L}_n\}_{i \ge n}, \{1_{\qcs{L}_j}\}_{j \ge i \ge n}).
-\]
-Every object in $\QC(\GN{T})$ is isomorphic to such a $[\qcs{L}_n]$.  Similarly, any morphism is equal to one of the form
-\[
-[\beta_k] \ceq (k, \{f_{k \le i}^* \beta_k\}_{i \ge k}).
-\]
-
-We may define a tensor product on $\QC(\GN{T})$ by setting
-\[
- \qcs{L} \otimes \qcs{L}' \ceq (k, \{\qcs{L}_i \otimes \qcs{L}'_i\}, \{\alpha_{i \le j} \otimes \alpha'_{i \le j}\}),
-\]
-where $k = \max(m, n)$.
-Similarly, the dual of an object $\qcs{L}$ is defined by 
-\[
-\qcs{L}^\vee \ceq (n, \{\qcs{L}_i^\vee\}, \{ \alpha_{i \le j}^\vee \}).
-\]
-We refer to objects in the rigid monoidal category 
-$\QC(\GN{T})$ as \emph{quasicharacter sheaves on $\GN{T}$} 
-or \emph{quasicharacter sheaves for $T$}.
-\end{definition}
-
-\begin{corollary}\label{cor:application}
-For every algebraic torus $T$ over $K$, the trace of Frobenius 
-  \[
-\trFrob{T}:  \QCiso{\GN{T}} \to \Hom_{\text{qc}}(T(K),\EEx)
-  \]
-is an isomomorphism. 
-Moreover, the isomorphism $\trFrob{T}$ is a natural transformation 
-between the additive functors
-\begin{enumerate}
-\item[$F_{\QC}$:] $T \mapsto \QCiso{\GN{T}}$
-\item[$F_{\text{qc}}$:] $T \mapsto \Hom_{\text{qc}}(T(K),\EEx)$
-\end{enumerate}
-from the additive category of algebraic tori over $K$ to the category of abelian groups.
-\end{corollary}
-
-\begin{proof}
-We may define full and faithful functors $F_n : \QC(\GN{T}_n) \to \QC(\GN{T})$
-for each $n$ by $F_n(\qcs{L}) \ceq [\qcs{L}_n]$ and $F_n(\alpha_n) \ceq [\alpha_n]$.
-For positive integers $n \le m$ these functors fit together into a diagram
-\[
-\begin{tikzcd}
-\ & & & \QC(\GN{T})\\
-\arrow{urrr}{F_n} \QC(\GN{T}_n) \arrow[swap]{rr}{f_{n\leq m}^*} && \QC(\GN{T}_m) \arrow[swap]{ur}{F_m}. & 
-\end{tikzcd}
-\]
-Passing to isomorphism classes of objects and invoking the 
-universal property of direct limits gives a group isomorphism
-$\theta: \varinjlim_{n\in \ZZ_{>0}} \QCiso{\GN{T}_n} \to \QCiso{\GN{T}}$
-with inverse $[\qcs{L}]_{/\text{iso}} \mapsto [\qcs{L}_{/\text{iso}}]$.
-Now use Theorem~\ref{thm:application}, Proposition~\ref{prop:pullback} 
-and the fact that  $\Hom_{\text{qc}}(T(K),\EEx) = \varinjlim_{n\in \ZZ_{>0}} \GN{T}_n(k)^*$, 
-where this direct limit is taken with respect to the family of group homomorphisms 
-dual to $f_{n} : \GN{T}_{n+1}(\Fq) \to \GN{T}_n(\Fq)$.
-\end{proof}
-
-\section{Restriction of scalars over local fields}
-\label{sec:wrK}
-
-As indicated in the Introduction, we are tantalized 
-by the idea that quasicharacter sheaves for $T$ 
-may play a key role in a new geometric, categorial version 
-of the local Langlands correspondence for algebraic tori 
-over non-archimedean local fields. 
-As with the local Langlands correspondence for algebraic tori over local fields, 
-it should be possible to reduce the essential points of the argument to the case $T= \Gm{K}$,
-provided that the category of quasicharacter sheaves behaves properly with regard to
-Weil restriction, as in \cite{yu:09a}*{Thm 7.5 (2)}. 
-The next lemma shows that the category of quasicharacter sheaves for 
-algebraic tori does indeed behave properly with regard to Weil restriction.
-
-\begin{lemma}\label{lemma:wrK}
-Weil restriction is compatible with the Greenberg transform in the following sense: 
-if $e$ is the ramification degree of $K'/K$ and $k'$ is the residue field of $K'$ then,
-for every positive integer $n$,
-\begin{equation}
-\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)
-\iso
-\Res_{k'/k} \Gr_{en}(\TTp).
-\end{equation}
-\end{lemma}
-
-\begin{proof}
-First, note that since $\Res_{\OKp/\OK}(\TTp)$ 
-is a scheme over $\OK$, 
-the Greenberg transform $\Gr_{n}\left( \Res_{\OKp/\OK}(\TTp)\right)$ 
-is obtained by base change along $\OK \to \OK/\pK^n$ 
-followed by the Greenberg functor over the Artinian ring $\OK/\pK^n$. 
-On the other hand, since $\TTp$ is a scheme over $\OKp$, 
-the Greenberg transform $\Gr_{en}(\TTp)$ is defined by base change along 
-$\OKp \to \OKp/\pKp^{en}$ 
-followed by the Greenberg functor over the Artinian ring $\OKp/\pKp^{en}$. 
-Note also that 
-\begin{equation}\label{nem}
-\OKp \otimes_{\OK} \OK/\pK^n \iso \OKp/\pKp^{en}.
-\end{equation}
-Now Lemma~\ref{lemma:wrK} follows from \cite{bertrapelle-gonzales:Greenberg}*{Prop.
-6.3} after observing that  $\TTp \times_\Spec{\OKp} \Spec{\OKp/\pKp^{en}}$ is admissible relative to $\Spec{\OKp/\pKp^{en}} \to \Spec{\OK/\pK^n}$, cf.
-\cite{bertrapelle-gonzales:Greenberg}*{Rem 2.9 (a)}.
-\end{proof}
-
-\begin{proposition}\label{prop:wrK}
-Let $K'/K$ be a finite Galois extension and
-let $k'/k$ be the corresponding extension of residue fields.
-Let $T$ be an algebraic torus over $K$ and 
-set $T' \ceq T \times_\Spec{K} \Spec{K'}$.
-The canonical closed immersion $T \hookrightarrow \Res_{K'/K} T'$
-induces a map of group pro-schemes $\GN{T} \to \Res_{k'/k} \GN{T}'$ which,
-through the pullback functor and the trace of Frobenius, induces the homomorphism
-\[
-\begin{tikzcd}[column sep=60]
-\Hom_{\text{qc}}(T(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{T(K)}} &\Hom_{\text{qc}}(T(K), \EEx).
-\end{tikzcd}
-\]  
-\end{proposition}
-
-\begin{proof}
-Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} to locally finite type Néron models,
-one may show that $\Res_{\OKp/\OK}(\TTp)$ is a Néron model for $\Res_{K'/K}(T')$.
-By the Néron mapping property, the canonical closed immersion
-$T\hookrightarrow \Res_{K'/K}(T')$ extends uniquely to a morphism
-$\underline{T}\to \Res_{\OKp/\OK}(\TTp)$ of smooth $\OK$-group schemes.
-Applying the Greenberg transform $\Gr_{n}$ to this morphism
-and using Lemma~\ref{lemma:wrK} defines the morphism of $\Fq$-group schemes
-\begin{equation}\label{men}
-\GN{T}_n \to \Res_{k'/k} \GN{T}'_{en}.
-\end{equation}
-Passing to the pro-group schemes in Definition~\ref{def:objGN} 
-the family of morphisms \eqref{men} determines a morphism of pro-group schemes
-\[
-\GN{T} \to \Res_{k'/k} \GN{T}'.
-\]
-Since $\left(\Res_{k'/k} \GN{T}'_{en} \right)(\Fq) = \left(\GN{T}'_{en}\right)(k')$,
-the pullback functor $\QC(\Res_{k'/k} \GN{T}'_{en})\to \QC(\GN{T}_n)$
-obtained by applying Proposition~\ref{prop:pullback} to \eqref{men} gives
-\[
-\Hom_{< en}(T'(K'),\EEx) \to \Hom_{< n}(T(K),\EEx).
-\]
-Passing to inverse limits defines
-\[
-\Hom_{\text{qc}}(T(K'),\EEx) \to \Hom_{\text{qc}}(T(K),\EEx).
-\]
-Argue as in Proposition~\ref{prop:csbe} to see that this is indeed restriction of characters.
-\end{proof}
-
-If we specialize Proposition~\ref{prop:wrK} to the case when 
-$T = \Gm{K}$ then we see how to geometrize and categorify the restriction of quasicharacters from $(K')^\times$ to $K^\times$.
-
-\section{Transfer of quasicharacter sheaves} \label{sec:transfer}
-
-The techniques in this paper apply to all non-archimdean local fields $K$ with residue field $k$
-and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$
-or on the ramification of $T$. 
-We may therefore ask for a comparison of
-quasicharacter sheaves on $T$ and on $T'$ whenever there is a relationship
-between characters of $T(K)$ and of $T'(K')$.
-Such a relationship can exist between characters of $T(K)$ and $T'(K')$ even
-when the characteristics of $K$ and $K'$ differ
-\citelist{\cite{chai-yu:01a} \cite{deligne:84a}*{\S 1}}.
-
-We recall the notion of $N$-congruent tori from \cite{chai-yu:01a}*{\S 2}.
-Suppose $T$ and $T'$ are tori over non-archimedian local fields $K$ and $K'$,
-splitting over $L$ and $L'$ respectively.
-Then $T$ and $T'$ are said to be \emph{$N$-congruent} if there are isomorphisms
- \begin{align*}
-  \alpha : \OL/\pi_K^N \OL &\to \OO{L'}/\pi_{K'}^N \OO{L'} \\
-  \beta : \Gal(L/K) &\to \Gal(L'/K') \\
-  \phi : X^*(T) &\to X^*(T')
- \end{align*}
- satisfying the conditions
- \begin{enumerate}
-  \item $\alpha$ induces an isomorphism $\OK/\pi_K^N \OK \to \OO{K'}/\pi_{K'}^N \OO{K'}$,
-  \item $\alpha$ is $\Gal(L/K)$-equivariant relative to $\beta$, and
-  \item $\phi$ is $\Gal(L/K)$-equivariant relative to $\beta$.
- \end{enumerate}
-If $T$ and $T'$ are $N$-congruent then $\alpha$, $\beta$ and $\phi$ determine an isomorphism
-\begin{equation}\label{transfer}
-  \Hom_{<N}(T(K), \EEx) \iso \Hom_{<N}(T'(K'),\EEx).
-\end{equation}
-Note that if $T$ and $T'$ are $N$-congruent, then they are $N'$ congruent for every
-$N' \leq N$, the isomorphism \eqref{transfer} is depth-preserving at integers less than $N$.
-In this section we show that the isomorphism \eqref{transfer} comes from an equivalence of
-categories of quasicharacter sheaves on $\GN{T}_n$ and those on $\GN{T}'_n$.
-
-One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes between
-$\TT_n$ and $\TT'_n$ assuming that $T$ and $T'$ are sufficiently congruent.
-They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the
-Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}.
-Then it follows from \cite{chai-yu:01a}*{Thm. 8.5} that if $N > 3h$ and $T$ and $T'$ are $N$-congruent 
-then there is a canonical isomorphism of smooth group schemes
- $
-  \TT_{N-3h} \to \TT'_{N-3h}
- $
- determined by $\alpha, \beta$ and $\phi$.
-Combining this with Theorem~\ref{thm:application} gives the geometrization and categorification of the transfer of characters.
-
-\begin{corollary}\label{cor:transfer}
- With notation above, suppose that $T$ and $T'$ are $N$-congruent and $N > 3h$.  Set $n \ceq N-3h$.
- Then there is a canonical equivalence of categories
- \[
-  \QC(\GN{T}'_{n}) \to \QC(\GN{T}_{n})
- \]
- determined by $\alpha, \beta$ and $\phi$ inducing the isomorphism
- \[
-  \Hom_{<n}(T'(K'), \EEx) \to \Hom_{<n}(T(K), \EEx)
- \]
- through the trace of Frobenius.
-\end{corollary}
-
-\section{Toward geometric reciprocity for tori over local fields}
-\label{sec:reciprocity}
-
-We have given a functorial relationship between quasicharacter sheaves 
-on the Greenberg transform of the Néron model of $T$ 
-and quasicharacters of $T(K)$.
-When coupled with the reciprocity map $\text{rec}_T $ for $T$, 
-which enjoys the same functorial properties, 
-it follows that quasicharacter sheaves for $T$ 
-functorially correspond to Langlands parameters for $T$.
-We suspect that it is possible to extract Langlands parameters 
-from quasicharacter sheaves directly and that the reciprocity map 
-can then be viewed as a matching between quasicharacters and Langlands parameters coming
- from the same quasicharacter sheaf. 
- \[
-\begin{tikzcd}
-\ & \arrow[swap]{dl}{\trFrob{G}} \QCiso{\GN{T}} \arrow[dashed]{dr} & \\
-\Hom_{\text{qc}}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(K,\hat{T}_\ell)
-\end{tikzcd}
-\]
- Results in this paper provide tools for reduction of the problem to the case $T=\Gm{K}$. 
- In that case, our suspicions are all but confirmed 
- by the class field theory of Serre-Hazewinkel
- \citelist{\cite{serre:60a} \cite{serre:61a} \cite{demazure-gabriel:GroupesAlgebriques}*{Appendice}},
- especially as revisited in \cite{suzuki-yoshida:12a}*{\S 2}. 
- What remains to be done is a careful comparison of 
- quasicharacter sheaves for $\Gm{K}$ and the local systems on
-  the fpqc-site of the pro-quasi-algebraic varieties appearing in \cite{suzuki-yoshida:12a}.
-
 \bibliographystyle{amsalpha}

### 2014-01-22 geometrization.tex
Just to see what it would like like, I've broken our paper into two parts: dictionary and geometrization. Please let me know what you think.

--- 2014-01-20 shanghai.tex
@@
 %%%%%%%%%%%%%%%%%% HEADING %%%%%%%%%%%%%%%%%%
-\title[A function--sheaf dictionary for local tori]{A function--sheaf dictionary for algebraic tori over local fields}
+\title[Geometrization of quasicharacters]{Geometrization of quasicharacters of algebraic tori over local fields}
 \date{\today}
@@
 \begin{abstract}
-  We introduce and study the category of quasicharacter sheaves on smooth,
-  commutative group schemes $G$ locally of finite type over finite fields
-  $\Fq$. Assuming that the geometric component group of $G$
-  is finitely-generated, we show that the group of isomorphism classes
-  of quasicharacter sheaves on $G$ is canonically isomorphic to the group
-  of characters of $G(\Fq)$. Then, for any non-archimedean local field $K$
-  and any algebraic torus $T$ over $K$, we use this result to produce a functorial
-  isomorphism between quasicharacters of $T(K)$ and isomorphism
-  classes of quasicharacter sheaves on the Greenberg transform of the Néron
+For any non-archimedean local field $K$
+  and any algebraic torus $T$ over $K$, we use the
+  function--sheaf dictionary for smooth group schemes over finite type over fields
+  to geometrize quasicharacters of $T(K)$
+  as quasicharacter sheaves on the Greenberg transform of the Néron
   model of $T$.
+ As an application, we categorify a transfer of certain characters between characteristic $p$ tori and characteristic $0$ tori.
   \end{abstract}
@@
 
-In this paper we find a dictionary between quasicharacters of algebraic tori over local fields and quasicharacter sheaves. 
-What is a quasicharacter sheaf?
-Let $G$ be a smooth, commutative group scheme locally of finite
-type over a finite field $\Fq$; $G$ need not be reductive, connected, or of
-finite type over $\Fq$. Fix a prime $\ell$ invertible in $\Fq$
-and write $m : \GxG \to G$ for the multiplication morphism,
-$\bG$ for the base change of $G$ to $\bFq$ and
-$\Frob{G} : \bG \to \bG$ for the Frobenius automorphism.
-A quasicharacter sheaf on $G$ is a triple $\qcs{L}\ceq
-(\gqcs{L},\mu,\phi)$ where $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ of rank~one and $\mu: m^*
-\gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms;
-$\mu$ and $\phi$ are required to satisfy natural conditions explained below.
-
-In Part 1 of this paper we study the category $\QC(G)$ of quasicharacter sheaves on $G$.
-Since $\QC(G)$ is a rigid monoidal category
-the set of isomorphism classes $\QCiso{G}$ forms a group.
-Motivated by the function--sheaf dictionary for commutative, connected
-algebraic groups \cite{deligne:SGA4.5}*{sommes trig.}, 
-we explore the trace of Frobenius morphism
-\[
-\QCiso{G} \to \Hom(G(\Fq), \EEx)
-\]
-and show in Theorem~\ref{thm:snake} that it is an isomorphism, 
-assuming that the geometric component group of $G$ is finitely generated.
-
-In Part 2 we use Theorem~\ref{thm:snake} to make a function--sheaf dictionary
-for algebraic tori over local fields.  Let $K$ be a non-archimedian local field
+We explain how to geometrize quasicharacters of algebraic tori over local fields.  
+%
+Let $K$ be a non-archimedian local field
 with finite residue field $\Fq$; we place no restriction on the characteristic of $K$.
@@
 $\TT(\OK) \cong T(K)$.  For each positive integer $n$, let $\GN{T}_n$ be the
-Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^n}$; the commutative
-group scheme $\GN{T}_n$ plays the r\^{o}le of $G$, above.  Theorem~\ref{thm:application}
-allows us to translate characters $T(K)$ of depth less than $n$ into quasicharacter sheaves on $\GN{T}_n$:
+Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^n}$.
+Then $\GN{T}_n$ is a commutative group scheme locally of finite type over $\Fq$ with finitely generated geometric component group, and as such, it carries the category $\QCiso{\GN{T}_n}$ of quasicharacter sheaves, introduced in \cite{cunningham-roe:dictionary}.
+In this paper we translate characters $T(K)$ of depth less than $n$ into quasicharacter sheaves on $\GN{T}_n$:
 \[
@@
 
-We want to situate the choice of term ``quasicharacter sheaf'' in a historical context.
-Analogous sheaves on connected, commutative algebraic groups were first studied
-by Deligne \cite{deligne:SGA4.5}*{sommes trig.} and many people have since referred to such objects
-as character sheaves; see for example, \cite{kamgarpour:09a}. 
-Our quasicharacter sheaves evolved from this notion, and Theorem~\ref{thm:snake}
-is a direct generalization of the function--sheaf dictionary to the case of certain commutative
-group schemes which are not necessarily connected or finite type.  The main use
-of the term character sheaf is of course due to Lusztig. It is applied to certain perverse
-sheaves on connected reductive algebraic groups over algebraically closed fields in
-\cite{lusztig:85a}*{Def.~2.10} and to certain perverse sheaves on reductive groups
-over algebraically closed fields with cyclic component groups in the series of papers
-beginning with \cite{lusztig:disconnected1}.  
-When commutative, such groups are extensions of $\ZZ/n\ZZ$ by a torus,
-in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
-
 We close the introduction with a more detailed description of the structure of this paper.
-In Section~\ref{sec:category} we define quasicharacter sheaves and give an interpretation of
-them as Weil sheaves with certain properties.
-Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism,
-one direction of the function--sheaf dictionary.
-We define pullbacks and products of quasicharacter sheaves in Section~\ref{sec:pullback}, and use
-them to prove a functoriality result on the trace of Frobenius.
-In Section~\ref{sec:basechange} we study how quasicharacter sheaves behave under base change
-and Weil restriction.
-Sections~\ref{sec:bounded} and \ref{sec:finite} describe bounded and finite quasicharacter sheaves,
-two subcategories of $\QC(G)$.  These alternate descriptions of quasicharacter sheaves play a key
-role in the proof of Proposition~\ref{prop:restriction}.
-In section \ref{sec:connected} we show that bounded and finite quasicharacter sheaves are the same
-as standard quasicharacter sheaves when $G$ is connected, and that trace of Frobenius is an isomorphism.
-We shift to \'etale group schemes $G$ in Section~\ref{sec:etale} and give a more concrete interpretation
-of quasicharacter sheaves in this case.  Using a notion of global sections for quasicharacter sheaves,
-we give isomorphisms between $\QCiso{G}$, $\Hh^1(\Weil{}, \Hom(G(\bFq), \EEx))$ and $\Hom(G(\Fq), \EEx)$.
-In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
-induces an essentially surjective functor of quasicharacter sheaves.
-Section~\ref{sec:snake} closes out Part \ref{part1} with the proof of the main theorem: trace of Frobenius
-is an isomorphism for $G$ as long as the geometric component group is finitely generated.
-
 In Section~\ref{sec:GN} we review the Greenberg transform of N\'eron models of tori, which produces
@@
 
-\begin{acknowledgements}
-
+%\begin{acknowledgements}
+\subsection*{Acknowledgements}
 We would like to thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
@@
 
-\end{acknowledgements}
-
-\part{Smooth commutative group schemes over finite fields} \label{part1}
-
-Throughout this paper, $G$ is a smooth, commutative group scheme locally of finite type
-over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.  For the sake of brevity, we
-define a \emph{$\QC$-scheme} to be such a $G$ with the additional property that the
-geometric component group of $G$ is finitely generated.  This last condition is only
-needed in the proof of Lemma \ref{lemma:section}.  A morphism of $\QC$-schemes is a morphism
-of group schemes over $\Fq$.
-
-We fix an algebraic closure $\bFq$ of $\Fq$ and write $\bG$ for the
-smooth commutative group scheme $G \times_{\Spec{\Fq}} \Spec{\bFq}$ over $\bFq$
-obtained by base change from $k$. The multiplication morphism for $\bG$ will be denoted by $\bm$.
-
-Let $\Frob{}$ denote the geometric Frobenius element in $\Gal(\bFq/\Fq)$ as
-well as the corresponding automorphism of $\Spec{\bFq}$. The Weil group
-$\Weil{}\subset \Gal(\bFq/\Fq)$ is the subgroup generated by $\Frob{}$.
-Let $\Frob{G} \ceq \id_{G} \times \Frob{}$ be the Frobenius automorphism of $\bG$.
-When no other fields play a role we will write $\Frob{}$ and $\Weil{}$ instead.
-
-We fix a prime $\ell$, invertible in $\Fq$.
-We will work with constructible $\ell$-adic sheaves \citelist{\cite{deligne:80a}*{\S 1.1} \cite{SGA5}*{Expos\'es V, VI}}
-on $\QC$-schemes, employing the standard formalism.
-We also make extensive use of the external tensor product of $\ell$-adic sheaves,
-defined as follows: if $\mathcal{F}$ and $\mathcal{G}$ are constructible $\ell$-adic
-sheaves on schemes $X$ and $Y$ and $p_X : X\times Y\to X$ and $p_Y : X\times Y \to Y$
-are the projections, then $\mathcal{F}\boxtimes \mathcal{G} \ceq p_X^* \mathcal{F} \otimes p_Y^*\mathcal{G}$.
-
-For any group $A$, we will denote by $A^*$ the dual group $\Hom_\text{grp}(A, \EEx)$.
-
-\section{Quasicharacter sheaves}\label{sec:category}
-
-\begin{definition}\label{def:QC}
-A \emph{quasicharacter sheaf on $G$} is a triple
-$\qcs{L}\ceq (\gqcs{L},\mu,\phi)$ where:
-\begin{enumerate}
-\labitem{(QC.1)}{QC.1} $\gqcs{L}$ is a rank~one $\ell$-adic local system on $\bG$, by which we mean
-a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected
-component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces; 
-\labitem{(QC.2)}{QC.2} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of
-sheaves on $\bGxG$ such that the following diagram commutes, 
-  where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
-  \[
-  \begin{tikzcd}[row sep=30]
-  \bm_3^*\gqcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
-    &&  \bm^*\gqcs{L} \boxtimes \gqcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
-    \gqcs{L} \boxtimes \bm^* \gqcs{L} \arrow{rr}{\id \boxtimes \mu}
-    &&  \gqcs{L} \tight{0}{\boxtimes}{0} \LxL
-  \end{tikzcd}
-  \]
-\labitem{(QC.3)}{QC.3} $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$ is an
-  isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with
-  $\mu$ in the sense that the following diagram commutes.
-  \[
-  \begin{tikzcd}[row sep=20]
-  \Frob{\GxxG}^* \bm^* \gqcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
-    && \Frob{\GxxG}^*(\LxL)\\
-    \arrow[equal]{u} \bm^*  \Frob{G}^* \gqcs{L} \arrow[swap]{d}{\bm^* \phi}
-    && \Frob{G}^*\gqcs{L}\boxtimes \Frob{G}^*\gqcs{L} \dar{\phi\boxtimes \phi} \arrow[equal]{u} \\
-    \bm^*\gqcs{L} \arrow{rr}{\mu}
-    && \LxL
-  \end{tikzcd}
-  \]
-\end{enumerate}
-\end{definition}
-
-Morphisms in the category of quasicharacter sheaves on $G$, denoted by $\QC(G)$, are defined in the natural way:
-\begin{enumerate}
-\labitem{(QC.4)}{QC.4} if $\qcs{L} = (\gqcs{L},\mu,\phi)$ and
-  $\qcs{L'} = (\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$ then
-  a morphism $\qcs{L} \to \qcs{L}'$ is a map $\alpha : \gqcs{L} \to \gqcs{L'}$
-  of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
-  \[
-  \begin{tikzcd}[column sep=40]
-  \Frob{G}^* \gqcs{L} \rar{\Frob{G}^* \alpha} \arrow[swap]{d}{\phi} & \Frob{G}^* \gqcs{L'} \dar{\phi'}
-  & & \arrow[swap]{d}{\mu} m^* \gqcs{L} \rar{m^* \alpha} & m^* \gqcs{L'} \dar{\mu'} \\
-  \gqcs{L} \rar{\alpha} & \gqcs{L'}
-  & {} & \LxL \rar{\tight{1}{\alpha\boxtimes \alpha}{1}} & \gqcs{L'} \tight{0}{\boxtimes}{0} \gqcs{L'}
-  \end{tikzcd}
-  \]
-\end{enumerate}
-
-The rule $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ defines a forgetful functor from quasicharacter
-sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
-
-A Weil sheaf $(\gqcs{L},\phi)$ on $G$
-may be interpreted as a constructible $\ell$-adic sheaf $\gqcs{L}$ on $\bG$ together with
-an action of the Weil group $\Weil{}$ on $\gqcs{L}$ compatible with the action of
-$\Gal(\bFq/\Fq)$ on $\bG$. We now briefly review this point of view for later use in
-Section~\ref{sec:basechange}; see also \cite{deligne:80a}*{Def.~1.1.10}.  If $w \ceq \Frob{}^n$ we write $w_G$ for $\Frob{G}^n$.
-For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gqcs{L}\to \gqcs{L}$ by
-$
-\varphi(w) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi)
-$; 
-these isomorphisms satisfy $\varphi(uv) = \varphi(v) \circ v_G^* \varphi(u)$ for $u,v\in \Weil{}$, and
-we have $\phi = \varphi(\Frob{})$. 
-If we further define $\varphi_1(w) \ceq (w_G)_*(\varphi(w)^{-1})$ then
-$\varphi_1(w) : (w_G)_* \gqcs{L}\to \gqcs{L}$ is an isomorphism and
-$\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for $u,v\in \Weil{}$.
-Thus the pair $(\gqcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{}$
-on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of
-\cite{deligne:SGA4.5}*{Expos\'e XIII, 1.1}, failing only because $\Weil{}$ is not profinite.
-As we will see in Corollary~\ref{cor:bounded-and-finite}, our use of $\Weil{}$ rather than $\Gal(\bFq/\Fq)$
-allows quasicharacter sheaves to correspond to unbounded characters.
-
-\section{Trace of Frobenius}\label{sec:Frob}
-
-The category $\QC(G)$ of quasicharacter sheaves on $G$ is a rigid monoidal category
-\cite{etingof:09a}*{\S1.10} under the tensor product
-$\qcs{L} \otimes \qcs{L'} \ceq (\gqcs{L}\otimes\gqcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
-with duals given by applying the sheaf hom functor 
-$\sheafHom(\ - \ ,\EE)$.
-The category of quasicharacter sheaves on $G$ is not abelian, so $\QC(G)$
-is not a tensor category in the sense of \cite{deligne:02a}*{0.1}.
-This rigid monoidal category structure for $\QC(G)$ gives the set $\QCiso{G}$
-of isomorphism classes in $\QC(G)$ the structure of a group.
-We now begin developing the tools to relate $\QCiso{G}$ to $G(\Fq)^*$.
-
-\begin{definition}\label{def:trFrob}
-Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
-determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$ and
-therefore an automorphism $\phi_{\bg}$ of $\gqcs{L}_{\bg}$. The \emph{trace of Frobenius} of $(\gqcs{L},\phi)$ at $g\in G(\Fq)$ is 
-\[
-\trFrob{(\gqcs{L},\phi)}(g) \ceq \trace(\phi_{\bg}, \gqcs{L}_{\bg}).
-\]
-If $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf
-then we will abbreviate $\trFrob{(\gqcs{L},\phi)}$ to $\trFrob{\qcs{L}}$.
-\end{definition}
-
-The isomorphism $\mu : \bm^* \gqcs{L} \to \LxL$ together with 
-\ref{QC.3} guarantee
-that the function $\trFrob{\qcs{L}} : G(\Fq)\to \EEx$ is a group homomorphism.  If we write
-$\trFrob{\qcs{L}} \cdot \trFrob{\qcs{L'}}$ for pointwise multiplication, then 
- $\trFrob{\qcs{L}\otimes \qcs{L'}} = \trFrob{\qcs{L}} \cdot \trFrob{\qcs{L'}}$.
-Since $\qcs{L} \iso \qcs{L'}$ implies $\trFrob{\qcs{L}} = \trFrob{\qcs{L'}}$,
-we obtain a group homomorphism
-\begin{align*}
-\trFrob{G} : \QCiso{G} &\to G(\Fq)^*, \\
-\qcs{L} &\mapsto \trFrob{\qcs{L}}.
-\end{align*}
-This homomorphism is functorial in the following sense:
-
-\begin{proposition}\label{prop:functorialG}
-Trace of Frobenius $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a natural transformation 
-between the two additive functors 
-\begin{align*}
-F_1 : G &\mapsto \QCiso{G} \\
-F_2 : G &\mapsto G(\Fq)^*
-\end{align*}
-from the category of $\QC$-schemes to the category of abelian groups.
-\end{proposition}
-
-The proof of Proposition~\ref{prop:functorialG} will be given at the end of the next section.
-
-\section{Pull-back and products}\label{sec:pullback}
-
-As a step toward the proof of Proposition~\ref{prop:functorialG} we show that every
-morphism  $H \to G$ of $\QC$-schemes induces a monoidal functor from quasicharacter
-sheaves on $G$ to quasicharacters on $H$. This simple but important result will also
-play a role in the proof of many other results in this paper.
-
-\begin{proposition}\label{prop:pullback}
-  If $f : H\to G$ is a morphism of $\QC$-schemes then
-  \begin{align*}
-  f^* : \QC(G) &\to \QC(H) \\
-  (\gqcs{L},\mu,\phi) &\mapsto (\bf^*\gqcs{L},(\bfxf)^*\mu,\bf^*F)
-  \end{align*}
-  defines a monoidal functor dual to $f \colon H(\Fq) \to G(\Fq)$:
-  \[
-  \begin{tikzcd}[row sep=20, column sep=30]
-   \QCiso{G} \rar{f^*} \arrow[swap]{d}{\trFrob{G}} & \QCiso{H} \dar{\trFrob{H}} \\
-   G(\Fq)^* \rar & H(\Fq)^*
-  \end{tikzcd}
-  \]
-  is a commutative diagram of groups.  Moreover, $(f\circ g)^* = g^* \circ f^*$.
-\end{proposition}
-
-\begin{proof}
-  Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We start by showing that
-  $\bf^*\gqcs{L}$ is a local system of rank~one. Let $c_j :\bH^j \hookrightarrow \bH$ be any
-  connected component and let $d_i : \bG^i \hookrightarrow \bG$ be the image of $j$ under the group
-  homomorphism $\pi_0(\bf) : \pi_0(\bH) \to \pi_0(\bG)$.  Write $\bf^j : \bH^j \to \bG^i$
-  for the restriction of $f$ to $\bH^j$.  Since $\gqcs{L}$ is locally constant on the connected
-  components of $\bG$, there is a finite \'etale covering
-  $a_i : X_i \to \bG^i$ such that $a_i^* (\gqcs{L}\vert_{\bG^i})$
-  is constant.  Define $Y_j$ in the following diagram through pullback:
-  \[
-  \begin{tikzcd}[row sep=20, column sep=30]
-   Y_j \dar[dashed]{g_j} \rar[dashed]{b_j} & \bH^j \dar{\bf^j} \rar[hook]{c_j} & \bH \dar{\bf} \\
-   X_i \rar{a_i} & \bG^i \rar[hook]{d_i} & \bG
-  \end{tikzcd}
-  \]
-  Then $b_j$ is a finite \'etale covering
-  of $\bH^j$ and
-  \[
-  b_j^* \left( (\bf^* \gqcs{L})\vert_{\bH^j}\right)
-  = (\bf\circ c_j \circ b_j)^*\gqcs{L}
-  = (d_i\circ a_i\circ g_j)^*\gqcs{L} = g_j^* a_i^* (\gqcs{L}\vert_{\bG^i}).
-  \]
-  Since $a_i^* (\gqcs{L}\vert_{\bG^i})$ is a constant sheaf, its pullback
-  $b_j^* \left( (\bf^*\gqcs{L})\vert_{\bH^j}\right)$ along $g_j$ is also constant.
-  Thus $\bf^*\gqcs{L}$ is locally constant on
-  $\bH^j$. To complete the proof that $\bf^*\gqcs{L}$ satisfies 
-  \ref{qc.4}
-  simply observe that $\bf^*\gqcs{L}$ has rank~one since 
-  $(\bf^*\gqcs{L})_{\bg} = \gqcs{L}_{f(\bg)}$, for every geometric point ${\bg}$ on $\bG$.
-
-  To see that $(\bfxf)^* \mu$ satisfies \ref{QC.2}, 
-  apply the functor $(\bfxf)^*$
-  to \ref{QC.2} for $\qcs{L}$ and use the canonical isomorphism
-  $(\bfxf)^*(\LxL) \iso \bf^*\gqcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gqcs{L}$.
-  To show that $f^*\qcs{L}$ satisfies 
-  \ref{QC.3}, apply the same functor to \ref{QC.3} for $\qcs{L}$.
-  The fact that $f$ is a morphism of group schemes defined over $\Fq$ then
-  yields isomorphisms $(\bfxf)^*\Frob{\GxxG}^* \iso \Frob{\GxxG}^* (\bfxf)^*$
-  and $(\bfxf)^* \bm^*\iso \bm^* \bf^*$ between functors of constructible sheaves.
-
-  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{QC.4} defines the action
-  of $f^*$ on morphisms of quasicharacter sheaves; arguing as above shows that $f^*$ is
-  a functor from $\QC(G)$ to $\QC(H)$.  Since tensor products commute with pullback in schemes,
-  $f^* : \QC(G) \to \QC(H)$ is a monoidal functor.
-  The diagram relating $f^* : \QC(G) \to \QC(H)$, $f^* : G(k)^* \to H(k)^*$ and trace of Frobenius
-  commutes by \cite{laumon:87a}*{1.1.1.2}, where the ambient
-  hypothesis that $X$ is of finite type over $\Fq$ can be replaced by
-  the hypothesis that $X$ is locally of finite type over $\Fq$.
-
-  Finally, the fact that $(f\circ g)^* = g^* \circ f^*$ follows from the analogous
-  statements about the pullback functor on $\ell$-adic constructible sheaves.
-\end{proof}
-
-We end this section with a simple result on products of quasicharacter sheaves,
-which is needed to show that the isomorphism above is functorial.
-
-\begin{proposition}\label{prop:product}
-If $G_1$ and $G_2$ are $\QC$-schemes then the rule
-$\boxtimes : (\qcs{L}_1,\qcs{L}_2)\to \qcs{L}_1\boxtimes\qcs{L}_2$ defines an equivalence of categories 
-\[
-\QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)
-\]
-such that 
-\[
-\begin{tikzcd}[column sep=60]
-\arrow{d}{\trFrob{G_1} \times \trFrob{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes}
-& \arrow{d}{\trFrob{G_1\times G_2}} \QCiso{G_1\times G_2}\\
-(G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
-\end{tikzcd}
-\]
-commutes.
-\end{proposition}
-
-\begin{proof}
-The only non-trivial part of the proof is to show that $\boxtimes : \QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)$
-is essentially surjective, so we will only address that point here.
-
-Set $G \ceq G_1\times G_2$
-and write $e_1$ and $e_2$ for the identity elements of $G_1$ and $G_2$.
-Define $f : G\to G\times G$ by $f(g_1,g_2) \ceq (g_1,e_2,e_1,g_2)$. 
-Observe that $m\circ f = \id_G$. 
-Let $p_1$, $p_2$ be the projection morphisms pictured below:
-\[
-\begin{tikzcd}
-G & \arrow[swap]{l}{p_1} G\times G \arrow{r}{p_2} & G.
-\end{tikzcd}
-\]
-Let $r_1$ and $r_2$ be the projection morphisms pictured below,
-with sections $q_1$ and $q_2$, also morphisms of group schemes:
-\[
-\begin{tikzcd}
-G_1  \arrow[swap, bend right]{r}{q_1} &
-\arrow[swap, bend right]{l}{r_1} G_1\times G_2 \arrow[bend left]{r}{r_2} &
-\arrow[bend left]{l}{q_2} G_2.
-\end{tikzcd}
-\]
-Observe that $p_1\circ f = q_1 \circ r_1$ and $p_2 \circ f = q_2\circ r_2$.
-
-Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$. 
-Set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$;
-by Proposition~\ref{prop:pullback}, $\qcs{L}_1$ a quasicharacter sheaf on $G_1$ 
-and $\qcs{L}_2$ is a quasicharacter sheaf on $G_2$.
-We will obtain an isomorphism $\qcs{L} \iso  \qcs{L}_1\boxtimes \qcs{L}_2$.
-Applying the functor $f^*$ to the isomorphism $\mu$ yields
-\begin{equation}\label{eq:fm}
-f^*\mu : f^* m^* \gqcs{L} \to f^*(\gqcs{L}\boxtimes \gqcs{L}) .
-\end{equation}
-We have already observed that $m\circ f = \id_G$, so $f^* m^* \gqcs{L} = \gqcs{L}$.
-On the other hand, $f^*(\gqcs{L}\boxtimes \gqcs{L}) = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L}$
-by definition.  Since $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L}$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L}$
-we get that $f^*(\gqcs{L}\boxtimes \gqcs{L}) = \gqcs{L}_1\boxtimes \gqcs{L}_2$.
-It follows that \eqref{eq:fm} gives an isomorphism $\gqcs{L} \to  \gqcs{L}_1\boxtimes \gqcs{L}_2$.
-It is a matter of routine to show that this morphism satisfies 
-\ref{qc.3} as it applies here,
-from which it follows that we have exhibited an isomorphism 
-$\qcs{L} \to \qcs{L}_1\boxtimes \qcs{L}_2$ of quasicharacters sheaves on $G\times G$.
-This completes the proof that $\boxtimes$ is essentially surjective.
-\end{proof}
-
-\begin{proof}[Proof of Proposition~\ref{prop:functorialG}]
-The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
-while the second part shows that Trace of Frobenius is a natural transformation
-$t: F_1 \to F_2$. When further combined with Proposition~\ref{prop:product},
-we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural
-transformation between additive functors, 
-concluding the proof of Proposition~\ref{prop:functorialG}.
-\end{proof}
-
-\section{Base change}\label{sec:basechange}
-
-When using quasicharacter sheaves to study characters, it is useful to understand
-how quasicharacter sheaves behave under change of fields.
-Let $k'$ be a finite extension of $k$. Then $k \hookrightarrow k'$ induces a group homomorphism
-$i_{k'/k} : G(k) \hookrightarrow G(k')$ and thus a homomorphism
-\begin{align*}
-i_{k'/k}^* : G(k')^* &\to G(k)^* \\
-\chi &\mapsto \chi\circ i_{k'/k}.
-\end{align*}
-We can interpret this operation on characters in terms of quasicharacter sheaves:
-
-\begin{proposition} \label{prop:csbe}
-Set $G_{k'} \ceq G\times_\Spec{k} \Spec{k'}$ and let
-\[
-\QC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \QC(G)
-\]
-be the functor obtained by pullback along the canonical closed immersion of $k$-schemes
-$\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$
-\cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}. 
-The following diagram commutes:
-\[
-\begin{tikzcd}
-\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\trFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\trFrob{G}} \\
-G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
-\end{tikzcd}
-\]
-\end{proposition}
-\begin{proof}
-This result follows immediately from Proposition~\ref{prop:pullback} together with the identifications
-$\Res_{k'/k}(G_{k'})(k) \cong G_{k'}(k') \cong G(k')$ from the definitions of Weil restriction and base change.
-\end{proof}
-
-In the opposite direction, let $\Nm : G(k') \to G(k)$ be the norm map and consider the group homomorphism:
-\begin{align*}
-\Nm^* : G(k)^* &\to G(k')^* \\
-\chi &\mapsto \chi\circ \Nm.
-\end{align*}
-We can also interpret this operation on characters in terms of quasicharacter sheaves.
-
-If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$, we define
-a quasicharacter sheaf $\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
-$G_{k'}$ of $G$ to $k'$ by setting
-\[
-\phi_{k'} \ceq \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi).
-\]
-The commutativity of the diagram (QC.3) for $\phi_{k'}$ 
-follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
-Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
-as taking the action $\varphi$ of $\Weil{k}$ on $\gqcs{L}$ 
-defined in Section~\ref{sec:category} and restricting it to the subgroup $\Weil{k'}$.
-
-\begin{proposition}\label{prop:basechange}
- The rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$ 
- defines a monoidal functor $\QC(G) \to \QC(G_{k'})$. 
- Moreover, the following diagram commutes:
-\[
-\begin{tikzcd}[column sep=60]
-\QCiso{G} \rar{\nu_{k'/k}} \dar{\trFrob{G}} & \QCiso{G_{k'}} \dar{\trFrob{G_{k'}}} \\
-G(k)^*  \rar{\Nm^*} & G(k')^*.
-\end{tikzcd}
-\]
-\end{proposition}
-\begin{proof}
-Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
-we may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
-and the value of $\Nm^*(t_G(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
-Applying \ref{QC.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
-\[
-\begin{tikzcd}
-\gqcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gqcs{L}_{F(x)} \otimes \gqcs{L}_{F^2(x)} \otimes \cdots \otimes \gqcs{L}_x
-\dar{\phi_x \otimes (F^*\phi)_x \otimes \cdots \otimes ((F^{n-1})^*\phi)_x} \\
-\gqcs{L}_{\Nm(x)} \rar & \gqcs{L}_x \otimes \gqcs{L}_{F(x)} \otimes \cdots \otimes \gqcs{L}_{F^{n-1}(x)}.
-\end{tikzcd}
-\]
-Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$ and write the image of $v$ under the
-bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
-for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{QC.2}, $v$ maps to
-$v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
-Let $\alpha_i \in \EEx$ represent $((F^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
-the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gqcs{L}_{\Nm(x)}$
-with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gqcs{L}_x$.
-\end{proof}
-
-Finally, let $G'$ be a $\QC$-scheme over $k'$;
-we explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
-We may decompose the base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
-into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
-\[
-(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
-\]
-Since products and coproducts agree for group schemes we have a natural inclusion of $k'$-schemes 
-\[
-G' \hookrightarrow (\Res_{k'/k}G')_{k'}
-\]
-mapping $G'$ into the summand corresponding to $1 \in \Gal(k'/k)$.  Composing $\nu_{k'/k}$ 
-from Proposition~\ref{prop:basechange} with pullback along this map yields a functor
-\[
-\rho : \QC(\Res_{k'/k}G') \to \QC(G').
-\]
-
-\begin{proposition}
-The following diagram of isomorphisms commutes, where the bottom map is the identity:
-\[
-\begin{tikzcd}
-\QCiso{\Res_{k'/k} G'} \dar{\trFrob{\Res_{k'/k} G'}} \rar{\rho} & \QCiso{G'} \dar{\trFrob{G'}}\\
-G'(k')^* \rar & G'(k')^*
-\end{tikzcd}
-\]
-\end{proposition}
-\begin{proof}
-By Proposition~\ref{prop:pullback} the pullback part of the definition of $\rho$ corresponds to the map $(\Res_{k'/k}G')(k') \to G'(k')^*$
-induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on 
-\[
-(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'
-\]
-is given by permuting coordinates, composition with the norm map yields the identity on $G'(k')$.
-\end{proof}
-
-\section{Bounded quasicharacter sheaves}\label{sec:bounded}
-
-In this section we consider a class of quasicharacter sheaves on $G$ obtained by
-replacing the Weil sheaf $(\gqcs{L}, \phi)$ on $\bG$ in the definition of a quasicharacter
-sheaf with an $\ell$-adic local system on $G$ itself.
-
-\begin{definition}
-Let $\QCb(G)$ be the category of pairs $(\qcs{L}_0,\mu_0)$ 
-where $\qcs{L}_0$ an $\ell$-adic local system on $G$ of rank~one, 
-equipped with an isomorphism $\mu_0 : m^* \qcs{L}_0 \to \qcs{L}_0 \boxtimes \qcs{L}_0$ 
-satisfying the analogue of \ref{QC.1} on $G$; 
-morphisms in $\QCb(G)$ are defined as in the second part of 
-\ref{QC.3}. 
-This is the category of \emph{bounded quasicharacter sheaves} on $G$. 
-\end{definition}
-
-The category of bounded quasicharacter sheaves is a rigid monoidal category in the obvious way.
-
-\begin{proposition}\label{prop:BG}
-Extension of scalars defines a full and faithful functor 
-$B_G : \QCb(G) \hookrightarrow \QC(G)$.
-\end{proposition}
-
-\begin{proof}
- Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$. 
- Then $\qcs{L}_0$ is an $\ell$-adic constructible sheaf on $G$ and
- $b_G^* \qcs{L}_0$ comes equipped with an isomorphism 
- $\phi : \Frob{G}^* b_G^*\qcs{L}_0 \to b_G^* \qcs{L}_0$.
- Moreover, the functor $\qcs{L}_0 \mapsto (b_G^* \qcs{L}_0,\phi)$  
- from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
- is full and faithful \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}}. 
- This functor preserves local constancy, so takes local systems to local systems. 
- Set $\mu \ceq b_{G\times G}^*\mu_0$; clearly, this satisfies \ref{QC.2} 
- with $b_G^*\qcs{L}_0$ playing the role of $\gqcs{L}$.
- Moreover, $\phi$ is compatible with $\mu$ in the sense of \ref{QC.3}.
- This construction defines the functor $B_G : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
- and also shows that it is full and faithful.
-\end{proof}
-
-In general, $\QCb(G)$ is an essentially
-proper subcategory of $\QC(G)$. We will identify $\QCb(G)$ with its image under $B_G$
-and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ is \emph{bounded}
-if it is isomorphic to some $B_G(\qcs{L}_0, \mu_0)$.
-We will see in Corollary~\ref{cor:bounded-and-finite} that the bounded quasicharacter sheaves
-are precisely those whose trace of Frobenius have bounded image.
-
-\section{Finite quasicharacter sheaves}\label{sec:finite}
-
-In this section we define \emph{finite quasicharacter sheaves}, a further refinement
-of bounded quasicharacter sheaves that play a role in Section \ref{sec:restriction}.
-
-The notion of a finite quasicharacter sheaf is informed 
-by a certain perspective on local systems on connected groups.
-Recall that every geometric point $\bg$ on a connected scheme $G$ 
-determines an equivalence between the categories of $\ell$-adic local systems on $G$ 
-and $\ell$-adic representations of the \'etale fundamental group $\pi_1(G, \bg)$ 
-\citelist{\cite{SGA5}*{VI,Prop. 1.2.5} \cite{deligne:80a}*{1.1.1}}.
- Since $\pi_1(G, \bg)$ is a projective limit of automorphism groups of finite \'etale covers, 
- a general local system corresponds to a projective limit of characters of such groups.  
- But some local systems can be described in terms of a single cover $f: H \to G$ 
- and a representation $\psi: \ker f \to \Aut(V)$;
- two such descriptions yield isomorphic local systems if and only if they are related by a weak
- isomorphism in $C(G)$.  While the description of local systems in terms of $\pi_1(G, \bg)$ does
- not generalize well to non-connected $G$, a perspective using finite \'etale covers does.
-
-The definition of finite quasicharacter sheaves will require several steps, 
-beginning with the localization of a category introduced here.
-Let us say that a morphism $f : H\to G$ of $\QC$-schemes is a \emph{discrete isogeny}
-if it is finite, surjective and \'etale and the action of $\Gal(\bFq/\Fq)$ on the \'etale group
-scheme $\ker f \ceq f^{-1}({\bar e)}$ is trivial.
-Consider the category $C(G)$ whose objects consist of pairs $(f,\psi)$, where
-\begin{itemize}
-\item $f : H\to G$ is a discrete isogeny of $\QC$-schemes,
-\item $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$.
-\end{itemize}
-A morphism $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(g,T)$, where
-\begin{itemize}
-\item $g : H' \to H$ is a morphism of schemes such that $f' = f\circ g$,
-\item $T : V\to V'$ is a linear transformation, equivariant for the action of
-$\ker f'$ on $V'$ by $\psi'$ and the action of $\ker f'$ on $V$ by $\psi \circ \alpha$.
-\[
-\begin{tikzcd}
-V \arrow{d}{T} & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} & \arrow[equal]{d} G\\
-V' & \Aut(V') & \arrow[swap]{l}{\psi'} \arrow[swap]{u}{g\vert_{\ker f'}} \ker f' \arrow[hook]{r} & \arrow[swap]{u}{g} H' \arrow{r}{f'} & G
-\end{tikzcd}
-\]
-\end{itemize}
-
-We put a tensor category structure on $C(G)$ as follows.
-Let $(f,\psi)$ and $(f',\psi')$ be objects in $C(G)$. 
-Write $f\times_G f' : H\times_G H' \to G$ for the product of $f$ and $f'$
-in the category of isogenies to $G$. We define an external tensor product
-$\psi \otimes\psi' :  \ker(f\times_G f') \to \Aut(V\otimes V')$ and a external sum
-$\psi \oplus\psi' :  \ker(f\times_G f') \to \Aut(V\oplus V')$
-using the canonical isomorphism $\ker(f\times_G f') \iso (\ker f)\times (\ker f')$.
-We may thus define $(f,\psi)\otimes(f',\psi') \ceq (f\times_G f' ,\psi\otimes\psi')$ and
-$(f,\psi)\oplus(f',\psi')\ceq (f\times_G f' ,\psi\oplus\psi')$. To define duals in $C(G)$,
-let $V^\vee \ceq \Hom_\text{vec}(V,\EE)$ and $\psi^\vee : \ker f \to \Aut(V^\vee)$ be
-the dual representation.  We may then set $(f,\psi)^\vee \ceq (f,\psi^\vee)$.
-These operations give $C(G)$ the structure of a tensor category.
-
-Now we localize $C(G)$.
-Let us say that $(g,T)$ in $C(G)$ is a \emph{weak isomorphism} if $g$ is surjective
-and $T$ is an isomorphism of vector spaces.  Recall from
-\cite{kashiwara-schapira:CatgoriesSheaves}*{Def 7.1.5} that a \emph{left multiplicative system}
-is a family of morphisms $W$ that
-\begin{itemize}
-\item contains all isomorphisms,
-\item is closed under composition,
-\item is closed under pullback by arbitrary morphisms in $C(G)$,
-\item and if the cokernel of a morphism $\phi \in \mor C(G)$ is in
-$W$ then so is the kernel of $\phi$.
-\end{itemize}
-
-We further say that $W$ is \emph{saturated} if the following property holds for
-morphisms $f, g$ and $h$ that can be composed appropriately:
-whenever $g \circ f$ and $h \circ g$ are in $W$ then so is $h$
-\cite{kashiwara-schapira:CatgoriesSheaves}*{Def 7.1.19}.
-
-\begin{lemma}
-The family of weak isomorphisms in $C(G)$ is a saturated, left multiplicative system.
-\end{lemma}
-\begin{proof}
-Any isomorphism $(g, T)$ in $C(G)$ has both $g$ and $T$ isomorphisms, and thus is a weak isomorphism.
-Clearly, the composition of two weak isomorphisms is a weak isomorphism.  The remaining properties
-follow from the fact that in a weak isomorphism $(g, T)$, $g$ is an \'etale cover, together with standard
-facts on \'etale covers and pullbacks.
-\end{proof}
-Let $W$ be the family of weak isomorphisms and $C(G)[W^{-1}]$ be the localization of $C(G)$ at $W$.
-A morphism in $C(G)[W^{-1}]$ is an equivalence class of diagrams
-\[   
-\begin{tikzcd}[column sep=30]
-   (f,\psi) \arrow{r}{(g,T)} & (f',\psi') & \arrow[swap]{l}{(h,U)} (f_1,\psi_1)
-   \end{tikzcd}
-\]
- where $(g,T) : (f,\psi) \to (f',\psi')$ is any map in $C(G)$ 
- and $(h,U) :  (f',\psi') \to (f_1,\psi_1)$ is a weak isomorphism in $C(G)$ \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16}.
-
-\begin{definition}
-Let $C_1(G)$ be the full, rigid monoidal subcategory of $C(G)$ consisting of objects
-$(f,\psi)$ such that $\psi$ is a one-dimensional representation.
-The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\QCf(G)$,
-is the rigid monoidal category obtained by localizing $C_1(G)$ at weak isomorphisms.
-\end{definition}
-
-Having defined finite quasicharacter sheaves, 
-we justify our terminology by showing $\QCf(G)$ is a full subcategory of $\QCb(G)$.
-To prepare for that result, we need two lemmas.
-
-\begin{lemma}\label{lemma:finite-pullback}
-Let $g : J \to G$ be a morphism of $\QC$-schemes. 
-Let $f_g : H\times_G J\to J$
-be the pullback of $f$ along $g$ and define $\psi_g : \ker f_g \to \Aut(V)$ as in the diagram below:
-\[
-\begin{tikzcd}
-V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker f_g}} \ker f_g \arrow[hook]{r}
-  & \arrow[swap]{u}{g_f} H\times_G J \arrow{r}{f_g} & \arrow{u}{g} J.
-\end{tikzcd}
-\]
-Then $(f,\psi) \mapsto (f_g,\psi_g)$
-defines a monomial functor $g^* : C(G)[W^{-1}] \to C(J)[W^{-1}]$.
-\end{lemma}
-
-\begin{proof}
-The key point is that pullback along $g$ takes discrete isogenies to discrete isogenies,
-and maps over $G$ to maps over $J$, as pictured below.
-\[
-\begin{tikzcd}[row sep={{{{40,between origins}}}},column sep={{{{60,between origins}}}}]
-\ V \arrow{dd}{T} & \Aut(V) && \arrow[swap]{ll}{\psi} \ker f \arrow[hook]{rr} \arrow[leftarrow]{dd} && H \arrow{rr}{f} \arrow[leftarrow]{dd} && \arrow[equal]{dd} G\\
- & & \arrow{ul} \ker f\times_G J \arrow{ur} \arrow[hook, crossing over]{rr} && H\times_G J \arrow{ur} \arrow[crossing over]{rr} && J \arrow[swap]{ur}{g} & \\
-V' & \Aut(V') && \arrow[swap,pos=0.25]{ll}{\psi'} \ker f'  \arrow[hook]{rr}
-&& H' \arrow[pos=0.25]{rr}{f'} && G\\
- & & \arrow{ul} \ker f'\times_G J \arrow[crossing over]{uu} \arrow{ur} \arrow[hook]{rr}
- && \arrow[crossing over]{uu} H'\times_G J \arrow{ur} \arrow{rr} && \arrow[equals, crossing over]{uu} J \arrow[swap]{ur}{g} & 
-\end{tikzcd}
-\]
-In this form we could treat $g^*$ as a functor $C(J)\to C(G)$,
-were it not for the fact that pullback is defined only up to isomorphism.
-In the localized categories, this ambiguity disappears. 
-\end{proof}
-
-\begin{lemma}\label{lemma:finite-iso}
-Each finite quasicharacter sheaf $(f,\psi)$ in $\QCf(G)$ determines a
-canonical isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$. 
- \end{lemma}
-
-\begin{proof}
-We will prove the proposition by finding a weak isomorphism 
-$m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ in $C_1(G\times G)$ 
-and showing that, after passing from $C_1(G\times G)$ to 
-$\QCf(G\times G)$, the resulting isomorphism, 
-denoted by $\mu(f,\psi)$, is canonically determined by $(f,\psi)$.
-
-Set $H_m \ceq H\times_G(G\times G)$, 
-write $f_m : H_m \to G \times G$ for the pullback of $f$ to $H_m$, 
-and let $A$ and $A_m$ be the kernels of $f$ and $f_m$ respectively.  Consider the diagram of Lemma~\ref{lemma:finite-pullback}:
-\[
-\begin{tikzcd}[column sep=40]
-V & \Aut(V) & \arrow[swap]{l}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-  &  & \arrow[dashed]{ul}{\psi_m} \arrow[swap]{u}{(m_f)\vert_{A_m}} A_m \arrow[hook]{r}
-  & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G.
-\end{tikzcd}
-\]
-We have $(f,\psi) \boxtimes (f,\psi) = (f\times f, \psi\otimes \psi)$.
-Since $f\circ m_H = m \circ (f\times f)$, the universal property of pullback gives
-a unique $\theta : H\times H \to H_m$ making the following commute.
-\[
-\begin{tikzcd}[row sep=20,column sep=10]
-\ & V \arrow{dd}{T} && \Aut(V) && A \arrow[hook]{rr} \arrow[swap]{ll}{\psi} &&  H \arrow{rr}{f} && G\\
- && && \arrow{ul}{\psi_m} A_m  \arrow[hook]{rr} \arrow{ur} && H_m \arrow[pos=0.3]{ur}{m_f} \arrow[swap, pos=0.8]{rr}{f_m}
- && G \times G \arrow[equal]{dr} \arrow[pos=0.42]{ur}{m} & \\
-& V\otimes V && \Aut(V) && \arrow[swap]{ll}{\psi \otimes \psi} \arrow[dashed,swap,pos=0.3]{ul}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr}
-&& \arrow[dashed,swap]{ul}{\theta} \arrow[crossing over,swap,pos=0.7]{uu}{m_H} H\times H \arrow{rr}{f\times f} && G\times G
-\end{tikzcd}
-\]
-Choose a basis $\{ v \}$ for $V$; then $\{ v\otimes v \}$ is a basis for $V\otimes V$.
-Let $T : V \to V\otimes V$ be the linear transformation taking $v$ to $v\otimes v$. Then the lower part of this
-diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G\times G)$.
-
-While $\theta$ was canonical, $T$ was not, as it depended on the choice of a basis for $V$.
-However, after passing from $C_1(G\times G)$ to $\QCf(G\times G)$, the resulting isomorphism in $\QCf(G\times G)$
-$\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ is independent of the choice of basis for $V$.
- \end{proof}
-
-\begin{proposition}\label{prop:bounded}
- $\QCf(G)$ is equivalent to a full subcategory of $\QCb(G)$.
-\end{proposition}
-
-\begin{proof}
- To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \QCf(G) \to \QCb(G)$.
-
- If $V$ is a finite-dimensional $\EE$-vector space then we write $V_H$ for the constant sheaf $V$ on $H$.
-If $(f,\psi)$ is a finite quasicharacter on $G$ where $\psi$ is a representation of $\ker f$ on $V$, 
-let $L(f,\psi)$ be the local system on $G$ given by the $\psi$-isotypic component of the local system $f_* V_H$ on $G$.
- We may identify the stalk $(f_* V_H)_{\bar g}$ of $f_* V_H$ at a geometric point ${\bar g}$ on $G$ 
- with the $\EE$-vector space $\Hom_\text{set}(\abs{f^{-1}({\bar g})},V)$ 
- and the stalk $L(f,\psi)_{\bar g}$ of $L(f,\psi)$ at a geometric point ${\bar g}$ on $G$ 
- with the $\EE$-vector space consisting of those functions $s: \abs{f^{-1}({\bar g})} \to V$ such that 
- $s(a\cdot {\bar h}) = \psi(a)(s({\bar h}))$ for all $a\in \ker f$ and for all ${\bar h} \in f^{-1}({\bar g})$.
-
- For any map $(g,T)$ in $C(G)$, let $L(g,T) : L(f,\psi) \to L(f',\psi')$ be the homomorphism of local systems defined 
- by $s \mapsto s' \ceq T\circ s\circ g$. 
- This construction defines a full monoidal functor $L$ from $C(G)$ to the category $\Loc(G)$ of local systems on $G$ that
- commutes with pullback along any morphism of $\QC$-schemes,
- as defined using Lemma~\ref{lemma:finite-pullback}.
- Moreover, since $L(f,T)$ is an isomorphism of local systems
- if and only if $(f,T)$ is a weak isomorphism, 
- the full functor $L : C(G) \to \Loc(G)$ factors through the localization functor $C(G) \to C(G)[W^{-1}]$ 
- to define a full and faithful functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$;
- see \cite{kashiwara-schapira:CatgoriesSheaves}*{Exercise 7.5}.
-
- By Lemma~\ref{lemma:finite-iso}, each $(f,\psi) \in \QCf(G)$ canonically determines 
- an isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi) \boxtimes (f,\psi)$ in $\QCf(G\times G)$.
- It follows immediately that the functor 
- \[
- L_G  \ceq  L_{W}\vert_{\QCf(G)} : \QCf(G) \to \QCb(G),
- \] 
- given on objects by $(f,\psi) \mapsto (L(f,\psi), L_{W}(\mu(f,\psi)))$,
- is a full and faithfull monoidal functor, completing the proof.
-\end{proof}
-
-On general $\QC$-schemes $G$, there are bounded quasicharacter sheaves which are not finite.  Identifying
-$\QCf(G)$ with its image under $B_G \circ L_G$, as defined in
-Proposition~\ref{prop:BG} and in the proof of Proposition~\ref{prop:bounded},
-we will see in Corollary~\ref{cor:bounded-and-finite} that
-a quasicharacter sheaf is finite if and only if its trace of Frobenius has finite image.
-
-\section{Connected commutative algebraic groups} \label{sec:connected}
-
-When $G$ is connected, we may apply the classic function--sheaf dictionary.  In order to do so,
-however, we must relate our notion of quasicharacter sheaf to the sheaf side of the standard dictionary.
-Choose any $\Fq$-rational point of $G$ and let $\bg$ be the geometric point on $G$ lying above $g$.
-Recall that the \emph{Weil group} of $G$, which we will denote by $\W(G,\bg)$, is a subgroup of the \'etale
-fundamental group defined by the following diagram:
-\[
- \begin{tikzcd}
- 1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \W(G,\bg) \rar \dar[hook] & \Weil{} \rar \dar[hook] & 1 \\
- 1 \rar &  \pi_1(\bG, \bg) \rar & \pi_1(G,\bg) \rar & \Gal(\bFq/\Fq) \rar & 1.
- \end{tikzcd}
-\]
-The $\Fq$-rational point $g$ under the geometric point $\bg$ determines a splitting
-$\Weil{}\to \W(G,\bg)$ of $\W(G,\bg)\to \Weil{}$.
-
-For connected groups, the subcategories introduced in the previous two sections agree with $\QC(G)$:
-
-\begin{proposition}\label{prop:connected}
-  If $G$ is a connected commutative algebraic group over $\Fq$ then 
-  the full subcategories $\QCf(G) \hookrightarrow \QCb(G) \hookrightarrow \QC(G)$ 
-  appearing in Sections~\ref{sec:bounded} and \ref{sec:finite} are equivalences.
-\end{proposition}
-
-\begin{proof}
-  Observe that the forgetful functor $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$
-  sends quasicharacter sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{deligne:80a}*{1.1.10}.
-  While is it not true that all Weil sheaves on $G$ descend to local systems on $G$, 
-  we will see that those that appear in the image of this forgetful functor from quasicharacter sheaves do.
-
-  Since $G$ is connected, the geometric point $\bg$ determines
-  an equivalence between the category of $\ell$-adic Weil local systems on $G$ and
-  $\ell$-adic representations of $\W(G,\bg)$ \cite{deligne:80a}*{1.1.12}.
-  Now let $(\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$ 
-  and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$.
-  Composing with the splitting $\Weil{} \to \W(G,\bg)$ yields an $\ell$-adic character
-  $\rho_g : \Weil{} \to \EEx$, which is the same as the trace of Frobenius defined in Section~\ref{sec:Frob}:
-  \[
-  \rho_g(\Frob{}) =  \trFrob{\qcs{L}}(g).
-  \]
-
-  On the other hand, we have already seen that $\trFrob{\qcs{L}} : G(\Fq) \to \EEx$
-  is a group homomorphism. Since $G$ is an algebraic group over $\Fq$, it is a
-  variety over $\Fq$ and thus $G(\Fq)$ is finite.
-  Therefore $\trFrob{\qcs{L}}(g) = \rho_g(\Frob{})$ is a root of unity
-  for every $g\in G(\Fq)$.  Since $\Weil{}$ is generated by
-  $\Frob{}$ and $\rho_g : \Weil{} \to \EEx$ is
-  a character, it follows that the image of $\rho_g$ is a finite group.
-  Thus, $\rho_g$ extends to an $\ell$-adic character of $\Gal(\bFq/\Fq)$, 
-  which we will also denote $\rho_g$.
-
-  We may now lift the $\ell$-adic character $\rho_g : \Gal(\bFq/\Fq) \to \EEx$
-  to an $\ell$-adic character $\pi_1(G,\bg) \to \EEx$ using the canonical topological group homomorphism
-  $\pi_1(G,\bg) \to \Gal(\bFq/\Fq)$. But $\bg$ also
-  determines an equivalence between the category of $\ell$-adic
-  representations of $\pi_1(G,\bg)$ and $\ell$-adic local systems on $G$. Let
-  $\qcs{L}_0$ be a local system on $G$ in the isomorphism class
-  determined by this $\ell$-adic character of $\pi_1(G,\bg)$.
-  Then $b_G^*\qcs{L}_0 \iso \gqcs{L}$.
-  Since $b_G^*$ is full and faithful
-  \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}},
-  $
-  b_{G\times G}^* : \Hom(m^*\qcs{L}_0,\qcs{L}_0\boxtimes\qcs{L}_0) \to \Hom({\bar m}^*\gqcs{L},\gqcs{L}\boxtimes\gqcs{L})
-  $ 
-  is a bijection 
-  (hom taken in the categories on constructible $\ell$-adic sheaves on 
-  $G\times G$ and ${\bar G}\times {\bar G}$ respectively, 
-  in which $\ell$-adic local systems sit as full subcategories). 
-  Let $\mu_0 : m^*\qcs{L}_0 \to \qcs{L}_0\boxtimes\qcs{L}_0$ be the isomorphism matching 
-  $\mu : {\bar m}^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$, 
-  the latter appearing in the definition of $\qcs{L}$. 
-  Then, as in Section~\ref{sec:bounded}, $(\qcs{L}_0,\mu_0)$ is an object in $\QCb(G)$ 
-  and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{L}_0,b_{G\times G}^*\mu_0)$ in $\QC(G)$.
-  Thus, the full and faithful functor $B_G : \QCb(G) \to \QC(G)$ from Section~\ref{sec:bounded}
-  is also essentially surjective, hence an equivalence.
-
-  In Section~\ref{sec:finite} we saw that $\QCf(G)$ is a full subcategory of $\QCb(G)$;
-  more precisely, we exhibited a full and faithful functor $L_G : \QCf(G) \to \QCb(G)$.
-  We now show that this functor is essentially surjective 
-  when $G$ is a connected, commutative algebraic group over $\Fq$.
-
-  Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$. 
-  Then $\qcs{L}\ceq B_G(\qcs{L}_0,\mu_0)$ is a quasicharacter sheaf on $G$.
-  Recall the definition of the character $\trFrob{\qcs{L}} : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}. 
-  Let $f : G\to G$ be the Lang isogeny.
-  Recall that $\ker f = G(\Fq) = G^{\Frob{}}$; 
-  in particular, the action of $\Gal(\bFq/\Fq)$ on $\ker f$ is trivial.
-  Let $V \ceq \EE$ and let $\psi : \ker f \to \Aut(V)$ be the representation given by 
-  $\psi(g)(v) \ceq \trFrob{\qcs{L}}(g) v$ for $v\in V$. 
-  Then $(f,\psi)$ is a finite quasicharacter sheaf.
-
-  To show that $L_G(f,\psi) \iso (\qcs{L}_0,\mu_0)$ we simply apply the function--sheaf dictionary
-  as follows \citelist{\cite{laumon:87a}*{1.1.3} \cite{deligne:SGA4.5}*{sommes trig.}}.
-  First, recall that $L_G(f,\psi) \ceq (L(f,\psi), \mu(f,\psi))$.
-  Let $k'/k$ be any degree-$n$ extension; 
-  let $\Nm : G(k')\to G(k)$ be the norm map 
-  and let $b : G_{k'} \to G$ be the base change map.
-  By \cite{laumon:87a}*{1.1.3.3}, 
-  $\trFrob{b^*L(f,\psi)} = \trFrob{\qcs{L}} \circ \Nm$;
-  on the other hand, $\trFrob{\qcs{L}} \circ \Nm = \trFrob{b^*\qcs{L}}$,
-   by Proposition~\ref{prop:basechange}.
-  Using \cite{laumon:87a}*{Th\'eor\`eme 1.1.2}, it follows that  $L(f,\psi) \iso \qcs{L}_0$ in $\Loc(G)$.
-  It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\qcs{L}_0,\mu_0)$ in $\QCb(G)$.
-  This completes the proof that $L_G : \QCf(G) \to \QC(G)$ is essentially surjective.
-  Since we have already seen (in Section~\ref{sec:finite}) that $L_G$ is full and faithful, 
-  it follows that $L_G$ is an equivalence.
-\end{proof}
-
-\begin{corollary}
- If $G$ is a connected, commutative algebraic group over $\Fq$ then
- \[
-  \trFrob{G} : \QCiso{G} \to G(\Fq)^*
- \]
- is an isomorphism of groups.
-\end{corollary}
-\begin{proof}
- It suffices to observe that the group homomorphism
- $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$
- is surjective because each character $\chi \in G(\Fq)^*$ determines a finite quasicharacter
- sheaf $(\Lang,\chi^{-1})$ such that the trace of Frobenius of the quasicharacter sheaf
- $B_G (L_G(\Lang,\chi^{-1}))$ is $\chi$.
-\end{proof}
-
-As Proposition~\ref{prop:connected} shows, 
-when $G$ is a connected algebraic group over $\Fq$, 
-it is appropriate to replace quasicharacter sheaves on $G$ 
-with the conceptually simpler category $\QCf(G)$ of finite quasicharacter sheaves on $G$. 
-In this context, finite quasicharacter sheaves may also be apprehended as
-\emph{certain} $\ell$-adic characters of fundamental group $\pi_1(G,{\bar e})$. 
-As explained in \cite{kamgarpour:09a}*{\S2}, 
-the relevant characters of $\pi_1(G,{\bar e})$ are precisely those 
-that factor through a particular quotient of $\pi_1(G,{\bar e})$ 
-denoted there by $\Pi_\text{disc}(G)$.
-Using this fact, one can show that the category of discrete isogenies to $G$ is a Galois category,
-in the sense of \cite{grothendieck:SGA1}*{Expos\'e V, \S 4}. 
-Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$ \cite{kamgarpour:09a}*{App'x B}, 
-the fundamental functor attached to this Galois category can be used to produce an equivalence
-between the category of finite quasicharacter sheaves on $G$ and
-the category of one-dimensional representations of $G(\Fq)^*$, thus
-providing an alternate proof that $\QCiso{G} \iso G(\Fq)^*$ 
-when $G$ is a connected algebraic group over $\Fq$.
-
-In principle, something similar is possible in the more general 
-context of this paper, where $G$ is a $\QC$-scheme, to which we now return. 
-In this generality, however, neither of the full subcategories $\QCf(G) \subset \QCb(G) \subset \QC(G)$ are equivalences;
-see the end of Section~\ref{sec:snake}.
-Nevertheless, every quasicharacter sheaf $(\gqcs{L},\mu,\phi)$ on $G$ 
-determines a Weil sheaf $(\gqcs{L},\phi)$ on $G$
-so if we choose a geometric point ${\bar g}_x$ in each component $\bG^x$ of $G$ 
-then this choice can be used to convert 
-the Weil sheaf $(\gqcs{L},\phi)$ into an $\ell$-adic character of $\prod_{x\in \pi_0(\bG)}\W(\bG^x, {\bar g}_x)$. 
-However, it seemed cumbersome to manage various 
-choices of families of base points and track the action 
-of $\Gal(\bFq/\Fq)$ on this (generally) infinite product of 
-Weil groups and also difficult to identify the relevant quotient of this group.
-Viewed in this light, Definition~\ref{def:QC} is comparatively simple.
-
-\section{Commutative \'etale group schemes} \label{sec:etale}
-
-\'Etale group schemes form a counterpoint to connected groups,
-since the component group of a $\QC$-scheme
-is an \'etale group scheme \cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
-The functor $G \mapsto G(\bFq)$ defines an equivalence of categories
-between the category of \'etale group schemes over $\Fq$ and the category of groups equipped
-with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group.
-Under this equivalence, a quasicharacter sheaf on $G$ is given by the data of:
-\begin{enumerate}
- \labitem{(qc.1)}{qc.1} an indexed set of one-dimensional
-  $\EE$-vector spaces $\gqcs{L}_x$, as $x$ runs over
-  $G(\bFq)$;
-
- \labitem{(qc.2)}{qc.2} an indexed set of isomorphisms
-  $\mu_{x,y} : \gqcs{L}_{x+y} \xrightarrow{\iso} \gqcs{L}_{x} \otimes\gqcs{L}_{y}$,
-  for all $x,y \in G(\bFq)$, such that
-  \[
-   \begin{tikzcd}[row sep=40]
-    \gqcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
-    && \gqcs{L}_{x+y}\otimes\gqcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
-    \gqcs{L}_{x} \otimes\gqcs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
-    && \gqcs{L}_{x} \otimes\gqcs{L}_{y} \otimes\gqcs{L}_{z}
-   \end{tikzcd}
-  \]
-  commutes, for all $x,y,z\in G(\bFq)$; and
- \labitem{(qc.3)}{qc.3} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
-  such that
-  \[
-   \begin{tikzcd}[row sep=40]
-    \gqcs{L}_{\Frob{}(x)+\Frob{}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{}(x),\Frob{}(y)}}
-    && \gqcs{L}_{\Frob{}(x)}\otimes\gqcs{L}_{\Frob{}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
-    \gqcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
-    && \gqcs{L}_x \otimes\gqcs{L}_y
-   \end{tikzcd}
-  \]
-  commutes, for all $x,y\in G(\bFq)$.
-\end{enumerate}
-Under this equivalence, a morphism $\alpha : \qcs{L} \to \qcs{L'}$ of quasicharacter sheaves on $G$ is given by 
-\begin{enumerate}
- \labitem{(qc.4)}{qc.4} an indexed set $\alpha_x : \gqcs{L}_x \to \gqcs{L'}_x$
-  of linear transformations such that
-  \[
-   \begin{tikzcd}[column sep=40]
-    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{}(x)} \rar{\alpha_{\Frob{}(x)}} & \gqcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
-    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-    & \arrow[swap]{d}{\mu} \gqcs{L}_{x+y} \rar{\alpha_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
-    \gqcs{L}_x \rar{\alpha_x} & \gqcs{L'}_x
-    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\alpha_x\otimes\alpha_y} & \gqcs{L'}_x \otimes\gqcs{L'}_y
-   \end{tikzcd}
-  \]
-  both commute for all $x, y \in G(\bFq)$.
-\end{enumerate}
-
-A \emph{global section} of $\qcs{L}$ is a function $s : G(\bFq) \to \coprod_{x \in G(\bFq)} \gqcs{L}_x$
-so that $s(x) \in \gqcs{L}_x$ for all $x \in G(\bFq)$ and
-\begin{equation}\label{section}
-\mu_{x,y}(s(x+y)) = s(x) \otimes s(y).
-\end{equation}
-
-We say that a section is \emph{nontrivial} if $s(x) \ne 0$ for all $x \in G(\bFq)$. 
-Note that the only other section is the constant zero section.
-
-\begin{lemma}\label{lemma:section}
- If $\qcs{L}$ is a quasicharacter sheaf on an \'etale $\QC$-scheme $G$ then $\qcs{L}$ has a nontrivial global section.
-\end{lemma}
-
-\begin{proof}
-  Since $G(\bFq)$ is a finitely-generated abelian group, it admits a decomposition
-  \[
-  G(\bFq) \iso \ZZ^r \oplus \bigoplus_{j=1}^t \ZZ / m_j \ZZ;
-  \]
-  let $x_1, \ldots, x_r, y_1, \ldots, y_t$ be a corresponding set of generators of $G(\bFq)$.
-  We will define a section $s$ satisfying \eqref{section} by choosing values on these generators and extending to all
-  of $G(\bFq)$ through \eqref{section}.
-
-  There is a unique isomorphism $\gqcs{L}_0 \cong \EE$ under which $\mu_{0,0}^{-1}$ corresponds
-  to the multiplication map $\EE \otimes\EE \to \EE$.
-  The condition $\mu_{0,0}(s(0)) = s(0) \otimes s(0)$ together with the non-triviality of $s$
-  then forces $s(0) = 1$.
-
-  The $\mu_{x,y}$ yield an isomorphism $\alpha_j : \gqcs{L}_{y_j}^{\otimes m_j} \to \gqcs{L}_0$.
-  An initial nonzero choice of $s(y_j)$ need only be scaled by $\alpha_j(s(y_j))^{-1/m_j}$ in order to map to
-  $1$ under this isomorphism.  Since compatibility under the $\alpha_j$ are the only constraints on the
-  $s(x_j)$ and $s(y_j)$, global sections exist.
-\end{proof}
-
-We note that this lemma is the only ingredient of the proof of Theorem~\ref{thm:snake}
-that forces $\QC$-schemes to have finitely generated geometric component group.  In fact,
-if $G$ is any smooth connected group scheme locally of finite type over $\Fq$
-and if each quasicharacter sheaf on the \'etale group scheme $\pi_0(G)$ admits a global section 
-satisfying \eqref{section}, then the conclusion of Theorem~\ref{thm:snake} holds for $G$.
-
-\begin{proposition}\label{prop:etale}
-  Let $G$ be an \'etale $\QC$-scheme.
-  We may associate a $1$-cocycle $\tau_\qcs{L}: \Weil{}\to G(\bFq)^*$ to each $\qcs{L} \in \QC(G)$
-  so that
-  \[
-  \tau_\qcs{L}(\Frob{})(x) = \trFrob{\qcs{L}}(x)
-  \]
-  for all $x \in G(\Fq)$ and the map
-  \begin{align*}
-  \QCiso{G} &\to \Hh^1(\Weil{}, G(\bFq)^*), \\
-  [\qcs{L}] &\mapsto [\tau_\qcs{L}],
-  \end{align*}
-  is an isomorphism.
-\end{proposition}
-
-\begin{proof}
-  Suppose $\qcs{L}$ is a quasicharacter sheaf on $G$ and choose a global section $s$
-  of $\qcs{L}$ using Lemma~\ref{lemma:section}.
-  We will construct a group isomorphism between $\QCiso{G}$ and
-  $\Hh^1(\Weil{}, G(\bFq)^*)$ using $s$, then prove independence from the choice of $s$.
-
-  Starting from $\qcs{L}$, we define a cocyle $\tau_{\qcs{L}} \in Z^1(\Weil{},G(\bFq)^*)$ as follows.
-  For $x \in G(\bFq)$, $\qcs{L}$ determines an isomorphism $\phi_x : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
-  of one-dimensional $\EE$-vector spaces; define $\tau_\qcs{L}$ by
-  \begin{equation}\label{t}
-   \phi_{x}(s(\Frob{}(x))) = \tau_\qcs{L}(\Frob{})(x) s(x).
-  \end{equation}
-  Note that if $x$ is fixed by $\Frob{}$ then $\tau_\qcs{L}(\Frob{})(x)$ is just $\trFrob{\qcs{L}}(x)$, so the restriction of
-  $\tau_\qcs{L}(\Frob{})$ to $G(k)$ is just $\trFrob{\qcs{L}}$.
-  In general, \ref{qc.1} and \ref{qc.3}, together with \eqref{section}, guarantee that
-  the scalar $\tau_\qcs{L}(\Frob{})(x)$ is non-zero.  Moreover, 
-  \ref{qc.1} forces
-  $\tau_\qcs{L}(\Frob{})(x+y) = \tau_\qcs{L}(\Frob{})(x) \ \tau_\qcs{L}(\Frob{})(y)$
-  for all $x,y \in G(\bFq)$.  We write $\cdot$ for pointwise multiplication of functions, and
-  define $\tau_\qcs{L} : \Weil{} \to G(\bFq)^*$ recursively by
-  \[
-   \tau_\qcs{L}(\Frob{}^n) \ceq \tau_\qcs{L}(\Frob{})\cdot \,^{\Frob{}} \tau_\qcs{L}(\Frob{}^{n-1}),
-  \]
-  where $\Frob{}$ acts on $G(\bFq)^*$ through pre-composition.
-
-  Although we used a global section $s$ in the definition of
-  $\tau_\qcs{L}$, the class of $\tau_\qcs{L}$ does not depend on this
-  choice. To see why, let $s_1$ and $s_2$ be two nontrivial global sections of
-  $\qcs{L}$ and let $\tau_1$ and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$.
-  For each $x \in G(\bFq)$ set $a(x) = \frac{s_2(x)}{s_1(x)}$.  Then \eqref{section} and
-  \ref{qc.2} together imply $a(x+y) = a(x)a(y)$, so
-  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{} \to G(\bFq)^*$
-  defined by $\tau_0(\Frob{}) \ceq \,^{\Frob{}} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
-  so $\tau_2$ and $\tau_1$ are cohomologous. Thus
-  \begin{equation}\label{cohomologous}
-  \begin{split}
-    \obj \QC(G) &\to \Hh^1(\Weil{},G(\bFq)^*), \\
-    \qcs{L} &\mapsto [\tau_\qcs{L}],
-  \end{split}
-  \end{equation}
-  is independent of the choice of global sections made above.
-
-  We now show that $[\tau_\qcs{L}]$ depends only on the isomorphism class of $\qcs{L}$.
-  Let $\alpha : \qcs{L} \to \qcs{L'}$ be an isomorphism and
-  let $\tau$ and $\tau'$ be any cocycles representing the classes in the
-  image of $\qcs{L}$ and $\qcs{L'}$ under \eqref{cohomologous}; by construction,
-  $\tau$ and $\tau'$ are defined by the choice of sections $s$ and $s'$.
-  Now, $\varphi_x(s(x))$ is a
-  non-zero scalar multiple of $s'(x)$; define $a: G(\bFq) \to \EEx$
-  by $\alpha_x(s(x)) = a(x) s'(x)$.
-  By the second part of \ref{qc.4},
-  $a(x+y) = a(x)a(y)$, so $a \in G(\bFq)^*$. By the first part of
-  \ref{qc.4}, 
-  $\tau'(\Frob{}) = \tau(\Frob{}) \cdot (\,^{\Frob{}^{-1}}a \cdot a^{-1})$,
-  so $\tau$ and $\tau'$ are cohomologous. This shows that
-  \begin{equation}\label{pich1}
-  \begin{split}
-    \QCiso{G} &\to \Hh^1(\Weil{},G(\bFq)^*),\\
-    [\qcs{L}] &\mapsto [\tau_\qcs{L}]
-  \end{split}
-  \end{equation}
-  is well-defined.
-
-    Suppose that $\qcs{L}$ and $\qcs{L}'$ are two quasicharacter sheaves on $G$.
-  If $s$ is a global section for $\qcs{L}$ and $s'$ for $\qcs{L}'$ then $s \otimes s'$
-  is a global section for $\qcs{L} \otimes\qcs{L}'$.  The three versions of \eqref{t}
-  for $\qcs{L}, \qcs{L'}$ and $\qcs{L} \otimes\qcs{L}'$ imply that
-  $\tau_{\qcs{L} \otimes\qcs{L}'}(\Frob{}) = \tau_\qcs{L}(\Frob{}) \tau_{\qcs{L}'}(\Frob{})$,
-  so \eqref{pich1} is a group homomorphism.
-
- To see that \eqref{pich1} is injective,
- suppose $[\tau_\qcs{L}] = [\tau_\qcs{L'}]$.
- Let $s$ and $s'$ be sections appearing in the definition of $\tau_\qcs{L}$ and $\tau_\qcs{L'}$.
- Since $[\tau_\qcs{L}] = [\tau_\qcs{L'}]$, 
- it follows that $\tau_\qcs{L}$ and $\tau_{\qcs{L'}}$ are cohomologous, 
- so there is some $a\in G(\Fq)^*$ such that 
- $\tau'(\Frob{}) = \tau(\Frob{}) \cdot (\,^{\Frob{}}a \cdot a^{-1})$. 
- Define $\alpha : \qcs{L}\to \qcs{L'}$ by $\alpha_x(s(x)) \ceq a(x) s'(x)$ and $\alpha^{-1} : \qcs{L}'\to \qcs{L}$
- by $\alpha^{-1}_x(s'(x)) \ceq a(x)^{-1} s(x)$, for $x\in G(\bFq)$.
- It is straightforward to check that $\alpha$ satisfies \ref{qc.3}
- and that $\alpha^{-1}$ is its inverse. Thus $\qcs{L} \iso \qcs{L'}$ in $\QC(G)$ and \eqref{pich1} is injective.
-
- Finally, to show that \eqref{pich1} is surjective, pick $[\tau]\in \Hh^1(\Weil{}, G(\bFq)^*)$.
- For each $x\in G(\bFq)$, set $\gqcs{L}_x \ceq \EE$.
- Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by
- $\mu_{x,y}(1) \ceq 1\otimes1$, for $x,y\in G(\bFq)$; 
- clearly, $\mu$ satisfies \ref{qc.2}.
- Define $\phi_x : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_x(1) \ceq \tau(\Frob{})(x)$,
- for each $x\in G(\bFq)$. 
- Then $\phi$ satisfies \ref{qc.3} because $\tau \in Z^1(\Weil{},G(\bFq)^*)$.
- Setting $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$, we have that $[\tau]$ is the image of $\qcs{L}$
- under \eqref{pich1}, and thus \eqref{pich1} defines an isomorphism of groups.
-\end{proof}
-
-In order to relate $\QCiso{G}$ to $G(k)^*$, we need a simple result relating duals, invariants and coinvariants.
-
-\begin{lemma} \label{lem:dual-inv}
-Let $X$ be an abelian group equipped with an action of $\Weil{}$.
- Then
-\begin{align*}
- (X^*)_{\Frob{}} &\to (X^{\Frob{}})^* \\
- [f] &\mapsto f|_{X^{\Frob{}}}
-\end{align*}
-is an isomorphism.
-\end{lemma}
-\begin{proof}
-We can describe $X^{\Frob{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
-let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
-\[
- 0 \to X^{\Frob{}} \to X \to Y \to 0
-\]
-yields
-\[
- 0 \to Y^* \to X^* \to (X^{\Frob{}})^* \to \Ext^1_\ZZ(Y, \EEx).
-\]
-Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Frob{}})^*$.
-\end{proof}
-
-\begin{proposition} \label{prop:etale-iso}
- If $G$ is a commutative, \'etale group scheme over $\Fq$ and $G(\bFq)$ is finitely
- generated then
- \[
-  \trFrob{G} : \QCiso{G} \to G(\Fq)^*
- \]
- is an isomorphism of groups.
-\end{proposition}
-\begin{proof}
-There is a natural isomorphism $\Hh^1(\Weil{}, G(\bFq)^*) \to (G(\bFq)^*)_{\Frob{}}$
-defined by $[z] \mapsto z(\Frob{})$.  The proposition now follows directly
-from Proposition~\ref{prop:etale} and Lemma~\ref{lem:dual-inv}.
-\end{proof}
-
-\section{Exactness of the component group sequence} \label{sec:restriction}
-
-Consider the short exact sequence in the category of $\QC$-schemes
-defining the component group scheme for $G$:
-\begin{equation}\label{eq:pi0}
-\begin{tikzcd}
-0 \rar & G^0 \arrow{r}{\iota_0} & G \arrow{r}{\pi_0} & \pi_0(G) \rar & 0.
-\end{tikzcd}
-\end{equation}
-Since $\pi_0(G)$ is also a $\QC$-scheme, 
-Proposition~\ref{prop:pullback} implies that \eqref{eq:pi0} defines the sequence of functors
-\begin{equation}\label{eq:pi1}
-\begin{tikzcd}
-\QC(0) \rar & \QC(\pi_0(G)) \arrow{r}{\pi_0^*} & \QC(G) \arrow{r}{\iota_0^*} & \QC(G^0) \rar & \QC(0)
-\end{tikzcd}
-\end{equation}
-and therefore, after passing to isomorphism classes, the sequence of abelian groups 
-\begin{equation}\label{eq:pi2}
-\begin{tikzcd}
-0 \rar & \QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
-\end{tikzcd}
-\end{equation}
- Note that we found the groups $\QCiso{G^0}$
-and $\QCiso{\pi_0(G)}$
-in Sections~\ref{sec:connected} and \ref{sec:etale}.
-In this section we show that \eqref{eq:pi2} is right exact.
-
-Recall from Section~\ref{sec:finite} that 
-a morphism $f : H\to G$ of group $\Fq$-schemes is a discrete isogeny 
-if it is a finite, surjective \'etale morphism and 
-the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f$ is trivial.
-
-\begin{lemma}\label{lemma:ext}
-Every discrete isogeny onto $G^0$ extends to a discrete
-isogeny onto $G$ inducing an isomorphism on component groups.
-\end{lemma}
-
-\begin{proof}
-Let $\pi: B \to G^0$ be a discrete isogeny and set $A \ceq \ker \pi$.
-  We will find a discrete isogeny $f: H\to G$
-  such that that $H^0 = B$, $f^0 =\pi$ and
-  $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism of component
-  groups.  Namely, we will fit $\pi$ into the following diagram,
-  \begin{equation}\label{extension-diagram}
-  \begin{tikzcd}
-  A \arrow[equal]{r} \dar & A \dar \\
-  B \rar \dar[swap]{\pi} & H \rar \dar[swap]{f} & \pi_0(H) \arrow{d}[below,rotate=90]{\sim}[swap]{\pi_0(f)} \\
-  G^0 \rar & G \rar & \pi_0(G),
-  \end{tikzcd}
-  \end{equation}
-  where all rows and columns are exact and all maps are defined over
-  $\Fq$.  We will do so by passing back and forth between group
-  schemes over $\Fq$ and their $\bFq$-points.
-
-  Extensions of $G^0(\bFq)$ by $A(\bFq)$, such as $B(\bFq)$,
-  correspond to classes in $\Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq))$.
-  Similarly, extensions of $G(\bFq)$ by $A(\bFq)$ correspond to
-  classes in $\Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq))$.  The map
-  $G^0(\bFq) \to G(\bFq)$ induces the map
-  \[
-  \Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq))
-  \]
-  fitting into the long exact sequence derived from applying
-  the functor $\Hom(\mbox{---}, A(\bFq))$ to $G^0(\bFq) \to G(\bFq) \to \pi_0(G)(\bFq)$:
-  \[
-  \Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[\Weil{}]}(\pi_0(G)(\bFq), A(\bFq)).
-  \]
-  Since $\Weil{} \cong \ZZ$ has cohomological dimension $1$ \cite{brown:CohomologyGrps}*{Ex. 4.3},
-  $\Ext^2_{\ZZ[\Weil{}]}(\pi_0(G)(\bFq), A(\bFq))$ vanishes \cite{cartan-eilenberg:HomologicalAlgebra}*{Thm. 2.6}.
-
-  We therefore have the existence of diagram \eqref{extension-diagram}
-  at the level of $\bFq$-points.  This expresses $H(\bFq)$ as a
-  disjoint union of translates of $B(\bFq)$; by transport of structure
-  we may take $H$ to be a group scheme over $\bFq$.  Similarly, the
-  restriction of $f$ to each component of $H$ is a morphism of
-  schemes, and thus $f$ is as well.  Finally, the whole diagram
-  descends to a diagram of $\Fq$-schemes since the $\bFq$-points of
-  the objects come equipped with continuous $\Gamma$-actions, and the
-  morphisms are $\Gamma$-equivariant.
-\end{proof}
-
-In order to use the results of Section~\ref{sec:connected}, we need to know that
-identity component of $G$ is actually an algebraic group.
-
-\begin{lemma} \label{lem:G0alg-grp}
-If $G$ is a $\QC$-scheme then $G^0$ is a connected algebraic group.
-\end{lemma}
-\begin{proof}
- Since $G$ is a smooth group scheme locally of finite type over $\Fq$, its
- identity component $G^0$ of $G$ is a connected smooth, 
- group scheme of finite type over $\Fq$, reduced over some finite extension of $\Fq$
- \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}. 
- Since $\Fq$ is a finite field and hence perfect, $G^0$ is actually reduced over $\Fq$
- \cite{EGAIV2}*{Prop 6.4.1}.  Since every group scheme over a field is separated 
- \cite{vdGeer-Moonen:AbelianVarieties}*{3.12},
- it follows that $G^0$ is a connected algebraic group.
-\end{proof}
-
-\begin{proposition}\label{prop:restriction}
-For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf
-$\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$.
-As a consequence, the restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
-\end{proposition}
-
-\begin{proof}
-  By Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}, every
-  quasicharacter sheaf on $G^0$ is isomorphic to a 
-  finite quasicharacter sheaf on $G^0$, 
-  so to prove the proposition it suffices to show that every 
-  finite quasicharacter sheaf on $G^0$ extends to a finite quasicharacter sheaf on $G$.
-
- Let $(\pi,\psi)$ be a finite quasicharacter sheaf on $G^0$.
- By Lemma~\ref{lemma:ext}, there is an extension of the 
- discrete isogeny $\pi : B \to G^0$ to a discrete isogeny $f : H \to G$ 
- such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
- Then $(f,\psi)$ is a finite quasicharacter sheaf on $G$ and 
- $(f,\psi)\vert_{G^0} \iso (\pi,\psi)$.
-\end{proof}
-
-\begin{proposition}\label{prop:middleexact}
- The sequence 
- \[
-  \begin{tikzcd}
-  0 \rar & \QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
-  \end{tikzcd}
- \]
- is exact at $\QCiso{G}$.
-\end{proposition}
-
-\begin{proof}
-First note that $\iota_0^* \circ \pi_0^*$ is trivial by Proposition~\ref{prop:pullback}.
-So it suffices to show that if $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$ 
-with $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$ then $\qcs{L}$ is in the essential image of $\pi_0^*$.
-
-For each $x\in \pi_0(\bG)$, set $\bG^x \ceq \pi_0^{-1}(x)$.
-Let $g, g'$ be geometric points in the same 
-geometric connected component $\bG^x$. 
-Set $a = g^{-1}g'$ and note that $a$ is a geometric point in $\bG^0$. 
-Let $\mu_{g,a} : \gqcs{L}_{ga} \to \gqcs{L}_g \otimes \gqcs{L}_a$ 
-be the isomorphism of vector spaces obtained by restriction of 
-$\mu : m^*\gqcs{L} \to \gqcs{L} \boxtimes \gqcs{L}$ to the 
-geometric point $(g,a)$ on $\bG^x \times \bG^0$. 
-Since $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$, 
-the stalk of $\gqcs{L}$ at $a$ is $\EE$. 
-In this way the pair of geometric points $g, g' \in \bG^x$ 
-determines an isomorphism $\varphi_{g,g'} \ceq \mu_{g,a}^{-1}$ 
-from $\gqcs{L}_{g}$ to $\gqcs{L}_{g'}$.
-
-The isomorphisms $\varphi_{g,g'}: \gqcs{L}_{g} \to \gqcs{L}_{g'}$ are canonical 
-in the following sense: if $g,g'\in \bG^x$ and $h,h'\in \bG^y$ 
-then it follows from \ref{QC.2} and \ref{QC.3} 
-that
- \begin{equation}\label{eq:qc}
-  \begin{tikzcd}[column sep=55]
-   \gqcs{L}_{gh} \arrow{r}{\varphi_{gh,g'h'}} \arrow[swap]{d}{\mu_{g,h}}
-  & \gqcs{L}_{g'h'} \arrow{d}{\mu_{g',h'}}
-  &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} 
-  &  \gqcs{L}_{\Frob{}(g)} \arrow{r}{\varphi_{\Frob{}(g),\Frob{}(g')}} \arrow[swap]{d}{\phi_{g}} & \gqcs{L}_{\Frob{}(g')} \arrow{d}{\phi_{g'}} \\
-  \gqcs{L}_{g} \otimes \gqcs{L}_{h} \arrow{r}{\varphi_{g,g'}\otimes \varphi_{h,h'}}  
-  & \gqcs{L}_{g'} \otimes \gqcs{L}_{h'} 
-  & {}
-  & \gqcs{L}_{g} \arrow{r}{\varphi_{g,g'}} & \gqcs{L}_{g'}
-  \end{tikzcd}
- \end{equation}
-both commute.
-
-For each $x\in \pi_0(\bG)$, pick $g(x)\in \bG^x$ 
-and set $\gqcs{E}_x \ceq \gqcs{L}_{g(x)}$. 
-Let $\phi_x : \gqcs{E}_{\Frob{}(x)} \to \gqcs{E}_x$ 
-be the isomorphism of $\EE$-vector spaces obtained by composing 
-$\varphi_{g(\Frob{}(x)),\Frob{}(g(x))} : \gqcs{L}_{g(\Frob{}(x))} \to \gqcs{L}_{\Frob{}(g(x))}$ 
-with $\phi_{g(x)} : \gqcs{L}_{\Frob{}(g(x))} \to \gqcs{L}_{g(x)}$. 
-For each pair $x,y\in \pi_0(\bG)$ 
-let $\mu_{x,y} : \gqcs{E}_{x+y}\to \gqcs{E}_x\otimes \gqcs{E}_y$ 
-be the isomorphism of $\EE$-vector spaces obtained by composing
-$\varphi_{g(x+y),g(x)g(y)} : \gqcs{L}_{g(x+y)} \to \gqcs{L}_{g(x)g(y)}$ 
-with $\mu_{g(x),g(y)} : \gqcs{L}_{g(x)g(y)} \to \gqcs{L}_{g(x)}\otimes \gqcs{L}_{g(y)}$.
-Using \eqref{eq:qc}, it follows that \ref{qc.1}, \ref{qc.2} and \ref{qc.3} are satisfied for
-$\qcs{E} \ceq (\gqcs{E}_x, \mu_{x,y}, \phi_x)$, thus defining a quasicharacter sheaf on $\pi_0(G)$.
-
-The pullback $\pi_0^*(\qcs{E})$ of $\qcs{E}$ along $\pi_0 : G \to \pi_0(G)$ is constant 
-on geometric connected components, with stalks given by 
-$(\pi_0^* \qcs{E})_g = \qcs{E}_{x}$ for all $g\in \bG^x$.  Thus both $\pi_0^*\qcs{E}$ and $\qcs{L}$
-are constant on geometric connected components of $G$. 
-The choices above define isomorphisms
-$\gqcs{L}\vert_{\bG^x} \to  (\gqcs{E}_{x})_{\bG^x}$ for each $x\in \pi_0(\bG)$.
-The resulting isomorphism $\gqcs{L} \to \pi_0^* \gqcs{E}$ satisfies \ref{QC.4}, 
-thus defining an isomorphism $\qcs{L} \to \pi_0^* \qcs{E}$ in $\QC(G)$.
-\end{proof}
-
-To close this section, we note that the injectivity of $\pi_0^*$ will be proven in Corollary~\ref{cor:exact}.
-
-\section{The function--sheaf dictionary for non-connected group schemes}
-\label{sec:snake}
-
-We saw in Proposition~\ref{prop:functorialG} that the trace of Frobenius
-$\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
-In fact, trace of Frobenius is an isomorphism when $G$ is a $\QC$-scheme.
-
-\begin{theorem}\label{thm:snake}
-  If $G$ is a smooth, commutative group scheme, locally of finite type over
-  $\Fq$, and if the abelian group $\pi_0(G)(\bFq)$
-  is finitely generated, then the trace of Frobenius
-  \[
-  \trFrob{G} : \QCiso{G} \to G(\Fq)^*
-  \]
-  is an isomorphism of groups.
-\end{theorem}
-
-\begin{proof}
-  Recall the short exact sequence \eqref{eq:pi0} in the category of $\QC$-schemes
-  defining the component group scheme for $G$:
-  \[
-  \begin{tikzcd}
-    1 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
-  \end{tikzcd}
-  \]
-  Let
-  \[
-  \begin{tikzcd}[row sep=30]
-    {}& \ker \trFrob{\pi_0(G)} \dar & \arrow[dashed]{d} \ker \trFrob{G} & \ker \trFrob{G^0} \dar & \\
-    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\trFrob{\pi_0(G)}}
-    & \QCiso{G} \rar \dar{\trFrob{G}} & \QCiso{G^0} \rar \dar{\trFrob{G^0}} & 0\\
-    0 \rar & \pi_0(G)(\Fq)^* \rar \dar
-    & \arrow[dashed]{d} G(\Fq)^* \rar & G^0(\Fq)^* \rar \dar & 0\\
-    & \coker \trFrob{\pi_0(G)} & \coker \trFrob{G} &  \coker \trFrob{G^0} &
-  \end{tikzcd}
-  \]
-  be the commutative diagram of abelian groups obtained by applying
-  Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.
-
-  The bottom row is dual to the sequence of
-  abelian groups
-  \begin{equation}\label{eq:pi0k}
-  \begin{tikzcd}
-    1 \rar & G^0(\Fq) \rar & G(\Fq) \rar & \pi_0(G)(\Fq) \rar & 0,
-  \end{tikzcd}
-  \end{equation}
-  which is exact by Lang's theorem on connected algebraic groups over finite fields \cite{lang:56a}.
-  Since $\EEx$ is divisible, $\Hom(\ - \ ,\EEx)$ is exact and thus the dual sequence of
-  character groups is also exact.
-
-  In order to apply the snake lemma, we need to show that the top row is exact at $\QCiso{G}$ and $\QCiso{G^0}$:
-  the surjectivity of $\QCiso{G} \to \QCiso{G^0}$ follows from Proposition~\ref{prop:restriction}
-  while exactness at $\QCiso{G}$ is given by Proposition~\ref{prop:middleexact}.
-  Now Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}
-  imply that $\ker \trFrob{G^0} =0$ and $\coker \trFrob{G^0}=0$. 
-  Similarly, Proposition~\ref{prop:etale-iso} shows that $\ker \trFrob{\pi_0(G)}=0$
-  and $\coker \trFrob{\pi_0(G)}=0$.
-  We may thus apply the snake lemma and conclude that
-  $\ker \trFrob{G}$ and $\coker \trFrob{G}$ both vanish.
-\end{proof}
-
-\begin{corollary}\label{cor:exact}
-Suppose that
-\[
-0 \to A \to B \to C \to 0
-\]
-is an exact sequence of $\QC$-schemes and that $\Hh^1(\Fq, A) = 0$.
-Then pullback yields an exact sequence
-\[
-0 \to \QCiso{C} \to \QCiso{B} \to \QCiso{A} \to 0
-\]
-of abelian groups.
-\end{corollary}
-\begin{proof}
-Since $\Hh^1(k, A) = 0$, the sequence $0 \to A(\Fq) \to B(\Fq) \to C(\Fq) \to 0$ is exact;
-applying $\Hom(-, \EEx)$ yields another exact sequence since $\EEx$ is divisible.  The result now follows
-from Proposition~\ref{prop:pullback} and Theorem~\ref{thm:snake}.
-\end{proof}
-
-With Theorem~\ref{thm:snake} in hand, 
-we can see why neither bounded quasicharacter sheaves 
-nor finite quasicharacter sheaves are up to the task of 
-geometrizing all characters of $G(\Fq)$ for general $\QC$-schemes $G$.
-
-\begin{corollary} \label{cor:bounded-and-finite}
-Suppose $G$ is a $\QC$-scheme and $\qcs{L}$ is a quasicharacter sheaf on $G$.  Then
-\begin{enumerate}
-\item $\qcs{L}$ is bounded if and only if $\trFrob{\qcs{L}}$ has bounded image,
-\item $\qcs{L}$ is finite if and only if $\trFrob{\qcs{L}}$ has finite image.
-\end{enumerate}
-\end{corollary}
-\begin{proof}
-We first reduce to the case that $G$ is an \'etale $\QC$-scheme.  On the connected component
-$G^0$, all quasicharacter sheaves are bounded and finite by Proposition~\ref{prop:connected}.
-On the other hand, $G^0(\Fq)$ is finite by Lemma~\ref{lem:G0alg-grp} and thus the trace of Frobenius
-has finite and therefore bounded image.  If $\chi \in G(\Fq)^*$ then there is some finite-image character $\chi_0$
-with the same restriction to $G^0(\Fq)$ since $G^0(\Fq)$ is lies inside the torsion part of
-the finitely generated abelian group $G(\Fq)$.  Therefore $\chi$ will be bounded (have finite image)
-if and only if $\chi \cdot \chi_0^{-1}$ is bounded (has finite image).  But $\chi \cdot \chi_0^{-1}$ descends
-to a character of $\pi_0(G)$.  A similar argument relates boundedness/finiteness of quasicharacter
-sheaves on $G$ to those on $\pi_0(G)$, using the fact that the preimage constructed in the proof of
-Proposition~\ref{prop:restriction} is a finite quasicharacter sheaf on $G$.
-Using these equivalences, it is enough to prove the Corollary
-for \'etale $\QC$-schemes.
-
-In the case that $G$ is \'etale, one can easily see whether a quasicharacter sheaf is bounded or finite.
-For $\qcs{L} \in \QC(G)$, recall that a global section is a particular choice of bases for the vector
-spaces $\qcs{L}_x$.  The isomorphisms $\phi_x : \qcs{L}_{\Frob{}(x)} \to \qcs{L}_x$ are then specified
-by a choice of scalars $b_x$.  By \cite{beilinson-bernstein-deligne:81a}*{Rem. 5.2.1},
-$\qcs{L}$ will be bounded if and only if $b_x \in \Zlx$ for all $x$.  Moreover, $\qcs{L}$ will be
-finite if and only if $b_x$ is a root of unity for all $x$.
-Let $z$ be a cocycle representing the image of $\qcs{L}$ under the isomorphism
-$\QCiso{G} \cong \Hh^1(\Weil{}, G(\bFq)^*)$.  Then $z(\Frob{})(x) = b_x$, and the
-map $\Hh^1(\Weil{}, \Hom(G(\bFq), \Zlx)) \to \Hom(G(\Fq), \Zlx)$ is an isomorphism
-since $\Zlx$ is divisible.  So bounded characters of $G(\Fq)$ correspond to quasicharacter sheaves
-$\qcs{L}$ that descend to Weil sheaves on $G$.  The conditions on the values $b_x$ then
-translate into analogous conditions on the image of trace of Frobenius.
-\end{proof}
-
-For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$.
-Let $\chi : G(\Fq) \to \EEx$ be the character determined by $\chi(1) = \ell$ 
-and let $\qcs{L}$ be a quasicharacter sheaf in the isomorphism class 
-corresponding to $\chi$ under Theorem~\ref{thm:snake}.
-Then $\qcs{L}$ is not a bounded quasicharacter sheaf since the image of $\chi$ is not
-bounded.  If $\chi(1) = 1+\ell$, then the image of $\chi$ is bounded but not finite.  For
-the corresponding quasicharacter sheaf $\qcs{L}$, the stalk at the component $1$ is defined
-by a pro-\'etale cover rather than an \'etale cover and thus $\qcs{L}$ is not finite.
-
-\part{Application to quasicharacters of algebraic tori over local fields}
-
-Recall that $\Fq$ is a finite field.
-Let $K$ be a non-archimedean local field with residue field $\Fq$.
+%\end{acknowledgements}
+
+\section{Quasicharacters of algebraic tori over local fields}
+
+Let $\Fq$ be a finite field and let $K$ be a non-archimedean local field with residue field $\Fq$.
 We place no restriction on the characteristic of $K$. 
@@
 
+\section{The function--sheaf dictionary}\label{sec:qcs}
+
+In \cite{cunningham-roe:dictionary} we extended the function--sheaf dictionary of Deligne  \cite{deligne:SGA4.5}*{sommes trig.} to smooth commutative group schemes locally of finite type over finite fields for which the geometric component group is finitely generated.
+Since we will use this dictionary here, we briefly review the main notation and result from that paper.
+
+Let $G$ be a smooth commutative group schemes locally of finite type over $\Fq$ for which the geometric component group is finitely generated. A quasicharacter sheaf on $G$ is a triple $\qcs{L}\ceq
+(\gqcs{L},\mu,\phi)$ where $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ of rank~one and $\mu: m^*
+\gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms satisfying natural compatibilty conditions; see \cite{cunningham-roe:dictionary}.
+%
+Quasicharacter sheaves on $G$ form a rigid monoidal category, denoted by $\QC(G)$
+and the trace of Frobenius
+\begin{equation}\label{snake}
+  \trFrob{G} : \QCiso{G} \to G(\Fq)^*
+\end{equation}
+  is an isomorphism of groups.
+
 \section{Application to quasicharacters of bounded depth} \label{sec:bdchar}
 
-We now apply the results of Part~\ref{part1} to characters of $T(K)$.
+We now apply the results of Section~\ref{sec:qcs} to characters of $T(K)$.
 
@@
 \begin{proof}
-  By \ref{smooth}, we may apply Theorem~\ref{thm:snake} to
-  $\GN{T}_n$ which provides a canonical isomorphism
+  By \ref{smooth}, we may use \eqref{snake} to produce a canonical isomorphism
   $\QCiso{\GN{T}_n} \iso \GN{T}_n(\Fq)^*$.

### 2014-01-22 dictionary.tex
Minor improvements to both.

@@
 To do this we must pass from $\ell$-adic local systems on a $\QC$-scheme $G$ to Weil local systems on $\bG$ 
-and also keep track of the isomorphisms \eqref{introbox} (existence of such an isomorphism is not enough), leading to the notation of {\it quasicharacter sheaves on $G$}.
+and also keep track of the isomorphisms \eqref{introbox} (existence of such an isomorphism is not enough), leading to the notion of {\it quasicharacter sheaves on $G$}.
 
@@
 the category $\QC(G)$ of quasicharacter sheaves on $G$
-is a rigid monoidal category and that the trace of Frobenius morphism provides an isomorphism
+is a rigid monoidal category and the trace of Frobenius morphism provides an isomorphism
 \begin{equation}
@@
 \end{equation}
-In this way we find the geometrization and categorification of characters of $G(\Fq)$.
+In this way, quasicharacter sheaves geometrize characters of $G(\Fq)$.
 
@@
 Consider the etale group scheme $G = \ZZ_{\Fq}$ over $\Fq$; this is a $\QC$-scheme.
-Characters of $G(\Fq) = \ZZ$ are neither finite nor bounded, in general; for example, the $\ell$-adic character $\ZZ \to \EEx$ defined by $1 \mapsto 1+ \ell$ is not finite but bounded, which the character $\ZZ \to \EEx$ defined by $1 \mapsto \ell$ is unbounded.
+Characters of $G(\Fq) = \ZZ$ are neither finite nor bounded, in general.
+For example, the $\ell$-adic character $\ZZ \to \EEx$ defined by $1 \mapsto 1+ \ell$ is bounded but not finite, while the character $\ZZ \to \EEx$ defined by $1 \mapsto \ell$ is unbounded.
 As we show in the paper, local systems on $G$ cannot be used to geometrize either of these characters; however, quasicharacter sheaves do the job, handily.
@@
 and Weil restriction.
-Sections~\ref{sec:bounded} and \ref{sec:finite} describe bounded and finite quasicharacter sheaves,
-two subcategories of $\QC(G)$.  These alternate descriptions of quasicharacter sheaves play a key
+Sections~\ref{sec:bounded} and \ref{sec:finite} describe bounded quasicharacter sheaves and finite quasicharacter sheaves, respectively,
+forming two important subcategories of $\QC(G)$.  These subcategories play a key
 role in the proof of Proposition~\ref{prop:restriction}.

### 2014-01-22 geometrization.tex
Minor improvements to both.

@@
   and any algebraic torus $T$ over $K$, we use the
-  function--sheaf dictionary for smooth group schemes over finite type over fields
+  function--sheaf dictionary for smooth group schemes locally of finite type over finite fields
   to geometrize quasicharacters of $T(K)$
@@
 group schemes over $\Fq$ from algebraic tori $T$ over $K$.
-Section~\ref{sec:bdchar} then uses Theorem~\ref{thm:snake} to give a geometrization of characters of $T$
+Section~\ref{sec:bdchar} then uses \cite{cunningham-roe:dictionary} to give a geometrization of characters of $T$
 of bounded depth.

### 2014-01-22 dictionary.tex
Fiddling with dictionary.

@@
 In this paper we answer that question.
-
+%
 In fact, we show much more by exhibiting a sheaf--function dictionary, in the sense above, for any smooth commutative group scheme $G$, locally of finite type over a finite field $\Fq$, 
@@
 
-A simple example will illustrate some of the issues that arise when extending the sheaf--function dictionary to disconnected algebraic groups over finite fields.
-Consider the etale group scheme $G = \ZZ_{\Fq}$ over $\Fq$; this is a $\QC$-scheme.
+A simple example will illustrate some of the issues that arise when extending the sheaf--function dictionary to $\QC$-schemes.
+Consider the etale group scheme $G = \ZZ_{/\Fq}$.
 Characters of $G(\Fq) = \ZZ$ are neither finite nor bounded, in general.
 For example, the $\ell$-adic character $\ZZ \to \EEx$ defined by $1 \mapsto 1+ \ell$ is bounded but not finite, while the character $\ZZ \to \EEx$ defined by $1 \mapsto \ell$ is unbounded.
-As we show in the paper, local systems on $G$ cannot be used to geometrize either of these characters; however, quasicharacter sheaves do the job, handily.
+As we show in the paper, $\ell$-adic local systems on $G$ cannot be used to geometrize either of these characters; however, quasicharacter sheaves do the job, handily.
 We remark that such characters arise when considering unramified quasicharacters of the $p$-adic group $\Qp^\times$.
@@
 We also want to situate the choice of term ``quasicharacter sheaf'' in a historical context.
-Some people refer to local systems satisfying \eqref{introbox} as as character sheaves; 
+Some people refer to local systems satisfying \eqref{introbox} on a connected, commutative algebraic group as as character sheaves; 
 see for example, \cite{kamgarpour:09a}. 

### 2014-01-22 geometrization.tex
Fixed some references; added a reference to my paper with Masoud.

@@
   model of $T$.
- As an application, we categorify a transfer of certain characters between characteristic $p$ tori and characteristic $0$ tori.
+ As an application, we find a categorical transfer of certain characters between characteristic $p$ tori and characteristic $0$ tori.
   \end{abstract}
@@
 \subsection*{Acknowledgements}
-We would like to thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
-for allowing us to hijack much of our Research in Teams meeting at BIRS into a discussion of
-quasicharacter sheaves; their knowledge and help have been invaluable. 
-We also thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and for pointing us to a proof of Lemma~\ref{lemma:wrK}.
+%We would like to thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian for allowing us to hijack much of our Research in Teams meeting at BIRS into a discussion of quasicharacter sheaves; their knowledge and help have been invaluable.
+We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and for pointing us to a proof of Lemma~\ref{lemma:wrK}.
 
@@
   Finally, we show that $\trFrob{T,n}$ is functorial.
-The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
+The first part of \cite{cunningham-roe:dictionary}*{Prop. 4.1} shows that $F_1$ is a functor,
 while the second part shows that trace of Frobenius is a natural transformation
-$t_{ - ,n} : F_1 \to F_2$. When further combined with Proposition~\ref{prop:product},
+$t_{ - ,n} : F_1 \to F_2$. When further combined with \cite{cunningham-roe:dictionary}*{Prop. 4.2},
 we see that $F_1$ is an additive functor and $t_{ - ,n}: F_1 \to F_2$ is a
@@
 \]
-be the functor produced by applying Proposition~\ref{prop:pullback} to $f_{n\leq m}$.
+be the functor produced by applying \cite{cunningham-roe:dictionary}*{Prop. 4.1} to $f_{n\leq m}$.
 We now define a category which allows us to extend the notion 
@@
 with inverse $[\qcs{L}]_{/\text{iso}} \mapsto [\qcs{L}_{/\text{iso}}]$.
-Now use Theorem~\ref{thm:application}, Proposition~\ref{prop:pullback} 
+Now use Theorem~\ref{thm:application}, \cite{cunningham-roe:dictionary}*{Prop. 4.1} 
 and the fact that  $\Hom_{\text{qc}}(T(K),\EEx) = \varinjlim_{n\in \ZZ_{>0}} \GN{T}_n(k)^*$, 
@@
 the pullback functor $\QC(\Res_{k'/k} \GN{T}'_{en})\to \QC(\GN{T}_n)$
-obtained by applying Proposition~\ref{prop:pullback} to \eqref{men} gives
+obtained by applying \cite{cunningham-roe:dictionary}*{Prop. 4.1} to \eqref{men} gives
 \[
@@
 \]
-Argue as in Proposition~\ref{prop:csbe} to see that this is indeed restriction of characters.
+Argue as in \cite{cunningham-roe:dictionary}*{Prop. 5.1} to see that this is indeed restriction of characters.
 \end{proof}
@@
   the fpqc-site of the pro-quasi-algebraic varieties appearing in \cite{suzuki-yoshida:12a}. 
+In this regard, a comparison between the results in this paper and those in \cite{cunningham-kamgarpour:geometrization} might also be illuminating.
 

### 2014-01-23 dictionary.tex
Fixed some references; added a reference to my paper with Masoud.
Minor improvements.

@@
 \begin{abstract}
-  We introduce and study the category of quasicharacter sheaves on smooth,
-  commutative group schemes $G$ locally of finite type over finite fields
-  $\Fq$. Assuming that the geometric component group of $G$
-  is finitely-generated, we show that the group of isomorphism classes
-  of quasicharacter sheaves on $G$ is canonically isomorphic to the group
-  of characters of $G(\Fq)$. 
+  We extend Deligne's function--sheaf dictionary from
+  connected commutative algebraic groups over finite fields to smooth
+  commutative group schemes locally of finite type over finite fields
+  with finitely-generated geometric component group.
+  To do so, we introduce the category of quasicharacter sheaves on such group schemes
+  $G$ over $\mathbb{F}_q$ and exhibit a canonical isomorphism between the character group of $G(\mathbb{F}_q)$ and the group of isomorphism classes of quasicharacter sheaves on $G$.
    \end{abstract}
@@
 The sheaf--function dictionary for connected commutative algebraic groups over finite fields translates characters into local systems \cite{deligne:SGA4.5}*{sommes trig.}.
-More precisely, let $G$ be a commutative group scheme over a finite field $\Fq$, let $\ell$ be any prime invertible in $\Fq$ and let $\chi : G(\Fq) \to \EEx$ be any character.
+Let $G$ be a commutative group scheme over a finite field $\Fq$, let $\ell$ be any prime invertible in $\Fq$ and let $\chi : G(\Fq) \to \EEx$ be any character.
 Using little more than the Lang map for $G$, $\chi$ determines an $\ell$-adic local system $\qcs{L}$ on $G$ from which the character $\chi$ can be recovered using the Frobenius automorphism of $\bG$, the base change of $G$ to $\bFq$.
@@
 We also want to situate the choice of term ``quasicharacter sheaf'' in a historical context.
-Some people refer to local systems satisfying \eqref{introbox} on a connected, commutative algebraic group as as character sheaves; 
+Some people refer to local systems satisfying \eqref{introbox} on a connected, commutative algebraic group as character sheaves; 
 see for example, \cite{kamgarpour:09a}. 
@@
 of quasicharacter sheaves in this case.  Using a notion of global sections for quasicharacter sheaves,
-we give isomorphisms between $\QCiso{G}$, $\Hh^1(\Weil{}, \Hom(G(\bFq), \EEx))$ and $\Hom(G(\Fq), \EEx)$.
+we give isomorphisms between $\QCiso{G}$, $\Hh^1(\Weil{}, \Hom(G(\bFq), \EEx))$ and $\Hom(G(\Fq), \EEx)$, where $\Weil{}$ is the Weil group for $\Fq$.
 In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
@@
 
-\section{Smooth commutative group schemes over finite fields}\label{sec:QCschemes}
+\tableofcontents
+
+\section{Preliminary definitions}\label{sec:QCschemes}
 
@@
 Let $\Frob{G} \ceq \id_{G} \times \Frob{}$ be the Frobenius automorphism of $\bG$.
-When no other fields play a role we will write $\Frob{}$ and $\Weil{}$ instead.
+%When no other fields play a role we will write $\Frob{}$ and $\Weil{}$ instead.
 
@@
   \ref{QC.3}, apply the same functor to \ref{QC.3} for $\qcs{L}$.
-  The fact that $f$ is a morphism of group schemes defined over $\Fq$ then
-  yields isomorphisms $(\bfxf)^*\Frob{\GxxG}^* \iso \Frob{\GxxG}^* (\bfxf)^*$
+  Since $f$ is a morphism of group schemes defined over $\Fq$
+  it provides isomorphisms $(\bfxf)^*\Frob{\GxxG}^* \iso \Frob{\GxxG}^* (\bfxf)^*$
   and $(\bfxf)^* \bm^*\iso \bm^* \bf^*$ between functors of constructible sheaves.
@@
 \[
-\begin{tikzcd}[row sep={{{{40,between origins}}}},column sep={{{{60,between origins}}}}]
-\ V \arrow{dd}{T} & \Aut(V) && \arrow[swap]{ll}{\psi} \ker f \arrow[hook]{rr} \arrow[leftarrow]{dd} && H \arrow{rr}{f} \arrow[leftarrow]{dd} && \arrow[equal]{dd} G\\
- & & \arrow{ul} \ker f\times_G J \arrow{ur} \arrow[hook, crossing over]{rr} && H\times_G J \arrow{ur} \arrow[crossing over]{rr} && J \arrow[swap]{ur}{g} & \\
-V' & \Aut(V') && \arrow[swap,pos=0.25]{ll}{\psi'} \ker f'  \arrow[hook]{rr}
+\begin{tikzcd}[row sep={{{{40,between origins}}}},column sep={{{{50,between origins}}}}]
+%\ V \arrow{dd}{T} & 
+\Aut(V) && \arrow[swap]{ll}{\psi} \ker f \arrow[hook]{rr} \arrow[leftarrow]{dd} && H \arrow{rr}{f} \arrow[leftarrow]{dd} && \arrow[equal]{dd} G\\
+% & 
+& \arrow{ul} \ker f\times_G J \arrow{ur} \arrow[hook, crossing over]{rr} && H\times_G J \arrow{ur} \arrow[crossing over]{rr} && J \arrow[swap]{ur}{g} & \\
+%V' &
+ \Aut(V') && \arrow[swap,pos=0.25]{ll}{\psi'} \ker f'  \arrow[hook]{rr}
 && H' \arrow[pos=0.25]{rr}{f'} && G\\
- & & \arrow{ul} \ker f'\times_G J \arrow[crossing over]{uu} \arrow{ur} \arrow[hook]{rr}
+% &
+ & \arrow{ul} \ker f'\times_G J \arrow[crossing over]{uu} \arrow{ur} \arrow[hook]{rr}
  && \arrow[crossing over]{uu} H'\times_G J \arrow{ur} \arrow{rr} && \arrow[equals, crossing over]{uu} J \arrow[swap]{ur}{g} & 
@@
 
-  To show that $L_G(f,\psi) \iso (\qcs{L}_0,\mu_0)$ we simply apply the function--sheaf dictionary
-  as follows \citelist{\cite{laumon:87a}*{1.1.3} \cite{deligne:SGA4.5}*{sommes trig.}}.
+  To show that $L_G(f,\psi) \iso (\qcs{L}_0,\mu_0)$ we apply the function--sheaf dictionary
+  \citelist{\cite{laumon:87a}*{1.1.3} \cite{deligne:SGA4.5}*{sommes trig.}}  as follows.
   First, recall that $L_G(f,\psi) \ceq (L(f,\psi), \mu(f,\psi))$.
@@
   It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\qcs{L}_0,\mu_0)$ in $\QCb(G)$.
-  This completes the proof that $L_G : \QCf(G) \to \QC(G)$ is essentially surjective.
+  This completes the proof that $L_G $ is essentially surjective.
   Since we have already seen (in Section~\ref{sec:finite}) that $L_G$ is full and faithful, 
@@
 
-With Theorem~\ref{thm:snake} in hand, 
-we can see why neither bounded quasicharacter sheaves 
-nor finite quasicharacter sheaves are up to the task of 
-geometrizing all characters of $G(\Fq)$ for general $\QC$-schemes $G$.
-
 \begin{corollary} \label{cor:bounded-and-finite}
@@
 
-Using Corollary~\ref{cor:bounded-and-finite} we can easily see that, in general, neither of the full subcategories
+With Corollary~\ref{cor:bounded-and-finite} in hand 
+we can see why neither finite quasicharacter sheaves nor bounded quasicharacter sheaves 
+are up to the task of geometrizing all characters of $G(\Fq)$ for general $\QC$-schemes $G$ since, in general, neither of the full subcategories
 $\QCf(G) \subset \QCb(G) \subset \QC(G)$ are equivalences.

### 2014-01-23 geometrization.tex
Minor improvements.

@@
   model of $T$.
- As an application, we find a categorical transfer of certain characters between characteristic $p$ tori and characteristic $0$ tori.
+ As an application, we find a categorical transfer of certain characters between characteristic-$p$ tori and characteristic-$0$ tori.
   \end{abstract}
@@
 \Hh^1(\Weil{K}, \hat{T}_\ell) \cong \Hom(T(K), \EEx)
-$. 
+$,
+where $\Weil{K}$ is the Weil group for $K$.
 A geometric description of the resulting isomorphism $\Hh^1(\Weil{K}, \hat{T}_\ell) \cong \QCiso{\GN{T}}$
@@
 We also gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
-and the National Science and Engineering Research Council,
-as well the hospitality of the Banff International Research Station during our weeklong stay in May 2012.
+and the National Science and Engineering Research Council.
+%as well the hospitality of the Banff International Research Station during our weeklong stay in May 2012.
 
 %\end{acknowledgements}
+
+\tableofcontents
 
@@
   Note that $\underline{T}$ is a smooth group scheme over $\OK$, by construction. 
-  Since smoothness is preserved under base change, 
+  Since smoothness is preserved under base change, the group scheme
   $\TT_n \ceq \underline{T} \times_\Spec{\OK} \Spec{\OK/\pK^n}$ 
-  is a smooth group scheme over an Artinian ring with perfect residue field. 
+  is smooth over an Artinian ring with perfect residue field. 
   The Greenberg functor preserves smoothness, 
@@
 \begin{proof}
-  By \ref{smooth}, we may use \eqref{snake} to produce a canonical isomorphism
+  By \ref{smooth}, we may use \eqref{snake} to give
   $\QCiso{\GN{T}_n} \iso \GN{T}_n(\Fq)^*$.

### 2014-01-24 dictionary.tex
More use of `functorial isomorphism' in dictionary.

@@
   To do so, we introduce the category of quasicharacter sheaves on such group schemes
-  $G$ over $\mathbb{F}_q$ and exhibit a canonical isomorphism between the character group of $G(\mathbb{F}_q)$ and the group of isomorphism classes of quasicharacter sheaves on $G$.
+  $G$ over $\mathbb{F}_q$ and exhibit a functorial isomorphism between the character group of $G(\mathbb{F}_q)$ and the group of isomorphism classes of quasicharacter sheaves on $G$.
    \end{abstract}
@@
 for which the geometric component group of $G$ is finitely generated; we call such group schemes $\QC$-schemes.
-To do this we must pass from $\ell$-adic local systems on a $\QC$-scheme $G$ to Weil local systems on $\bG$ 
+To do this we must pass from $\ell$-adic local systems on a $\QC$-scheme $G$ to Weil local systems on $G$ 
 and also keep track of the isomorphisms \eqref{introbox} (existence of such an isomorphism is not enough), leading to the notion of {\it quasicharacter sheaves on $G$}.
@@
 As we show in the paper, $\ell$-adic local systems on $G$ cannot be used to geometrize either of these characters; however, quasicharacter sheaves do the job, handily.
-We remark that such characters arise when considering unramified quasicharacters of the $p$-adic group $\Qp^\times$.
-This example informs our choice of the term ``quasicharacter sheaf''.
+We remark that such characters arise when considering unramified quasicharacters of the $p$-adic group $\Qp^\times$  This example informs our choice of the term ``quasicharacter sheaf''.
 Indeed, in \cite{cunningham-roe:p-adic_tori} we use this paper to geometrize and categorify all quasicharacters of all algebraic tori over all local fields.
@@
 Section~\ref{sec:snake} presents the main theorem of this paper: trace of Frobenius
-is an isomorphism for $G$ as long as the geometric component group is finitely generated.
+is a functorial isomorphism for $\QC$-schemes.
 
@@
   \]
-  is an isomorphism of groups.
+  is a functorial isomorphism of groups. 
 \end{theorem}
@@
 bounded.  
-On the other hand, if $\chi : \ZZ \to \EEx$ is the quasicharacter of $G(\Fq)$ determined by $\chi(1) = 1+\ell$ 
+Likewise, if $\chi : \ZZ \to \EEx$ is the quasicharacter of $G(\Fq)$ determined by $\chi(1) = 1+\ell$ 
 and if $\qcs{L}$ is a quasicharacter sheaf on $G$ in the isomorphism class 

### 2014-01-24 dictionary.tex
Improvements to the example in the introduction to dictionary.

@@
 Characters of $G(\Fq) = \ZZ$ are neither finite nor bounded, in general. 
-For example, the $\ell$-adic character $\ZZ \to \EEx$ defined by $1 \mapsto 1+ \ell$ is bounded but not finite, while the character $\ZZ \to \EEx$ defined by $1 \mapsto \ell$ is unbounded.
-As we show in the paper, $\ell$-adic local systems on $G$ cannot be used to geometrize either of these characters; however, quasicharacter sheaves do the job, handily.
-We remark that such characters arise when considering unramified quasicharacters of the $p$-adic group $\Qp^\times$  This example informs our choice of the term ``quasicharacter sheaf''.
+For example, while the $\ell$-adic character $\ZZ \to \EEx$ defined by 
+$1 \mapsto -1$ has finite order, the character defined by 
+$1 \mapsto 1+ \ell$ does not, although its image is bounded, while the character $\ZZ \to \EEx$ defined by 
+$1 \mapsto \ell$ has unbounded image.  
+As we show in the paper, $\ell$-adic local systems on $G$ can only be used to geometrize characters of finite order; quasicharacter sheaves, however, provide the geometrization of all characters of $G(\Fq)$.
+We remark that characters of finitely generated commutative groups, like $\ZZ$, 
+arise when considering unramified quasicharacters of $p$-adic groups, 
+such as $\Qp^\times$; in fact, aiming at such characters informs our choice of the term ``quasicharacter sheaf'' here.
 Indeed, in \cite{cunningham-roe:p-adic_tori} we use this paper to geometrize and categorify all quasicharacters of all algebraic tori over all local fields.

### 2014-02-07 dictionary.tex

@@
 %%%%%%%%%%%%%%%%%% HEADING %%%%%%%%%%%%%%%%%%
-\title[The function--sheaf dictionary]{The function--sheaf dictionary for smooth commutative group schemes over finite fields with finitely generated geometric component group}
+\title[The function--sheaf dictionary]{The function--sheaf dictionary for smooth commutative group schemes over finite fields}
+% with finitely generated geometric component group}
 \date{\today}
@@
 
-The sheaf--function dictionary for connected commutative algebraic groups over finite fields translates characters into local systems \cite{deligne:SGA4.5}*{sommes trig.}.
+The sheaf--function dictionary for connected commutative algebraic groups over finite fields \cite{deligne:SGA4.5}*{sommes trig.} translates characters into local systems.
 Let $G$ be a commutative group scheme over a finite field $\Fq$, let $\ell$ be any prime invertible in $\Fq$ and let $\chi : G(\Fq) \to \EEx$ be any character.
@@
 After setting some notation in Section~\ref{sec:QCschemes}, in Section~\ref{sec:category} we define quasicharacter sheaves and give an interpretation of
-them as Weil sheaves with certain properties.
+them as Weil sheaves equipped with an isomorphism of the form  \eqref{introbox}.
 Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism,
@@
 Sections~\ref{sec:bounded} and \ref{sec:finite} describe bounded quasicharacter sheaves and finite quasicharacter sheaves, respectively,
-forming two important subcategories of $\QC(G)$.  These subcategories play a key
-role in the proof of Proposition~\ref{prop:restriction}.
-In section \ref{sec:connected} we show that bounded and finite quasicharacter sheaves are the same
-as standard quasicharacter sheaves when $G$ is connected, and that trace of Frobenius is an isomorphism.
+forming two important subcategories of $\QC(G)$.  
+%These subcategories play a key role in the proof of Proposition~\ref{prop:restriction}.
+In Section \ref{sec:connected} we show that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves when $G$ is connected, and that trace of Frobenius is an isomorphism in this case.
 We shift to \'etale group schemes $G$ in Section~\ref{sec:etale} and give a more concrete interpretation
-of quasicharacter sheaves in this case.  Using a notion of global sections for quasicharacter sheaves,
-we give isomorphisms between $\QCiso{G}$, $\Hh^1(\Weil{}, \Hom(G(\bFq), \EEx))$ and $\Hom(G(\Fq), \EEx)$, where $\Weil{}$ is the Weil group for $\Fq$.
+of quasicharacter sheaves in this case.  Using a notion of global sections for quasicharacter sheaves, in this section 
+we also give isomorphisms between $\QCiso{G}$, $\Hh^1(\Weil{}, \Hom(G(\bFq), \EEx))$ and $\Hom(G(\Fq), \EEx)$, where $\Weil{}$ is the Weil group for $\Fq$.
 In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component

### 2014-02-07 geometrization.tex

@@
 Then $\GN{T}_n$ is a commutative group scheme locally of finite type over $\Fq$ with finitely generated geometric component group, and as such, it carries the category $\QCiso{\GN{T}_n}$ of quasicharacter sheaves, introduced in \cite{cunningham-roe:dictionary}.
-In this paper we translate characters $T(K)$ of depth less than $n$ into quasicharacter sheaves on $\GN{T}_n$:
+The main result in this paper, Theorem~\ref{thm:application}, provides a functorial translation of characters $T(K)$ of depth less than $n$ into quasicharacter sheaves on $\GN{T}_n$:
 \[
@@
 \begin{proof}
-  By \ref{smooth}, we may use \eqref{snake} to give
+  By \ref{smooth}, we may use \cite{cunningham-roe:dictionary}*{Thm. 11.1}
+   to give the functorial isomorphism
   $\QCiso{\GN{T}_n} \iso \GN{T}_n(\Fq)^*$.

### 2014-02-07 dictionary.tex
Added some references, switched dictionary.tex to submodule bibliography, changed spacing

@@
 \usepackage{mathrsfs, yfonts}
+\usepackage{geometry}
 % TikZ
@@
 such as $\Qp^\times$; in fact, aiming at such characters informs our choice of the term ``quasicharacter sheaf'' here.
-Indeed, in \cite{cunningham-roe:p-adic_tori} we use this paper to geometrize and categorify all quasicharacters of all algebraic tori over all local fields.
+Indeed, in \cite{cunningham-roe:13a} we use this paper to geometrize and categorify all quasicharacters of all algebraic tori over all local fields.
 
@@
 \subsection*{Acknowledgements}
-We would like to thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
+We thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
 for allowing us to hijack much of our Research in Teams meeting at BIRS into a discussion of
@@
 This result follows immediately from Proposition~\ref{prop:pullback} together with the identifications
-$\Res_{k'/k}(G_{k'})(k) \cong G_{k'}(k') \cong G(k')$ from the definitions of Weil restriction and base change.
+\[
+\Res_{k'/k}(G_{k'})(k) \cong G_{k'}(k') \cong G(k')
+\]
+from the definitions of Weil restriction and base change.
 \end{proof}
@@
 \begin{proof}
-By Proposition~\ref{prop:pullback} the pullback part of the definition of $\rho$ corresponds to the map $(\Res_{k'/k}G')(k') \to G'(k')^*$
+By Proposition~\ref{prop:pullback} the pullback part of the definition of $\rho$ corresponds to the map 
+\[
+(\Res_{k'/k}G')(k') \to G'(k')^*
+\]
 induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on 
@@
 \[
-\begin{tikzcd}[row sep=20,column sep=10]
+\begin{tikzcd}[row sep=20,column sep=8]
 \ & V \arrow{dd}{T} && \Aut(V) && A \arrow[hook]{rr} \arrow[swap]{ll}{\psi} &&  H \arrow{rr}{f} && G\\
@@
  && G \times G \arrow[equal]{dr} \arrow[pos=0.42]{ur}{m} & \\
-& V\otimes V && \Aut(V) && \arrow[swap]{ll}{\psi \otimes \psi} \arrow[dashed,swap,pos=0.3]{ul}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr}
+& V\otimes V && \Aut(V\otimes V) && \arrow[swap]{ll}{\psi \otimes \psi} \arrow[dashed,swap,pos=0.3]{ul}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr}
 && \arrow[dashed,swap]{ul}{\theta} \arrow[crossing over,swap,pos=0.7]{uu}{m_H} H\times H \arrow{rr}{f\times f} && G\times G
@@
  By Lemma~\ref{lemma:finite-iso}, each $(f,\psi) \in \QCf(G)$ canonically determines 
- an isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi) \boxtimes (f,\psi)$ in $\QCf(G\times G)$.
+ an isomorphism 
+ \[
+ \mu(f,\psi) : m^*(f,\psi) \to (f,\psi) \boxtimes (f,\psi)
+ \]
+ in $\QCf(G\times G)$.
  It follows immediately that the functor 
@@
 \bibliographystyle{amsalpha}
-\bibliography{Biblio}
+\bibliography{bibliography/Biblio}
 

### 2014-02-07 dictionary.tex
Changing trace of Frobenius

@@
 \newcommand{\QCf}{{\QC_f}}
-\newcommand{\QCiso}[1]{\pi_0 (\QC(#1))}
-\newcommand{\QCbiso}[1]{\pi_0(\QCb(#1))}
-\newcommand{\QCfiso}[1]{\pi_0(\QCf(#1))}
+\newcommand{\QCiso}[1]{\QC(#1)_{/\text{iso}}}
+\newcommand{\QCbiso}[1]{\QCb(#1)_{/\text{iso}}}
+\newcommand{\QCfiso}[1]{\QCf(#1)_{/\text{iso}}}
 \newcommand{\trFrob}[1]{t_{#1}}
+\newcommand{\TrFrob}[1]{T_{#1}}
 %% amsmath replacements for \atop
@@
 the category $\QC(G)$ of quasicharacter sheaves on $G$
-is a rigid monoidal category and the trace of Frobenius morphism provides an isomorphism
+is a rigid monoidal category and Trace of Frobenius provides an isomorphism
 \begin{equation}
@@
 As we show in the paper, $\ell$-adic local systems on $G$ can only be used to geometrize characters of finite order; quasicharacter sheaves, however, provide the geometrization of all characters of $G(\Fq)$.
-We remark that characters of finitely generated commutative groups, like $\ZZ$, 
-arise when considering unramified quasicharacters of $p$-adic groups, 
-such as $\Qp^\times$; in fact, aiming at such characters informs our choice of the term ``quasicharacter sheaf'' here.
-Indeed, in \cite{cunningham-roe:13a} we use this paper to geometrize and categorify all quasicharacters of all algebraic tori over all local fields.
-
-We also want to situate the choice of term ``quasicharacter sheaf'' in a historical context.
+
+In \cite{cunningham-roe:13a} we consider quasicharacter sheaves on the
+Greenberg transform of the N\'eron model of an algebraic torus over an arbitrary local field.
+The ability to work with non-connected group schemes plays a crucial role in this application,
+since these $\QC$-schemes are not connected in general.
+This process of creating a category from the group of quasicharacters of such a torus
+informs our choice of the term \emph{quasicharacter sheaf} here.
+
+We also want to situate our teminology in a historical context.
 Some people refer to local systems satisfying \eqref{introbox} on a connected, commutative algebraic group as character sheaves; 
@@
 them as Weil sheaves equipped with an isomorphism of the form  \eqref{introbox}.
-Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism,
+Section~\ref{sec:Frob} introduces Trace of Frobenius,
 one direction of the function--sheaf dictionary.
 We define pullbacks and products of quasicharacter sheaves in Section~\ref{sec:pullback}, and use
-them to prove a functoriality result on the trace of Frobenius.
+them to prove a functoriality result on Trace of Frobenius.
 In Section~\ref{sec:basechange} we study how quasicharacter sheaves behave under base change
@@
 %These subcategories play a key role in the proof of Proposition~\ref{prop:restriction}.
-In Section \ref{sec:connected} we show that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves when $G$ is connected, and that trace of Frobenius is an isomorphism in this case.
+In Section \ref{sec:connected} we show that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves when $G$ is connected, and that Trace of Frobenius is an isomorphism in this case.
 We shift to \'etale group schemes $G$ in Section~\ref{sec:etale} and give a more concrete interpretation
@@
 induces an essentially surjective functor of quasicharacter sheaves.
-Section~\ref{sec:snake} presents the main theorem of this paper: trace of Frobenius
+Section~\ref{sec:snake} presents the main theorem of this paper: Trace of Frobenius
 is a functorial isomorphism for $\QC$-schemes.
@@
 
-\begin{definition}\label{def:trFrob}
 Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
 determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$ and
-therefore an automorphism $\phi_{\bg}$ of $\gqcs{L}_{\bg}$. The \emph{trace of Frobenius} of $(\gqcs{L},\phi)$ at $g\in G(\Fq)$ is 
-\[
-\trFrob{(\gqcs{L},\phi)}(g) \ceq \trace(\phi_{\bg}, \gqcs{L}_{\bg}).
-\]
-If $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf
+therefore an automorphism $\phi_{\bg}$ of $\gqcs{L}_{\bg}$. Set $\trFrob{(\gqcs{L},\phi)}(g) \ceq \trace(\phi_{\bg}, \gqcs{L}_{\bg})$,
+and note that if $(\gqcs{L},\phi) \iso (\gqcs{L'},\phi')$ then $\trFrob{(\gqcs{L},\phi)} = \trFrob{(\gqcs{L'},\phi')}$.
+
+\begin{definition}\label{def:trFrob}
+The function 
+\begin{align*}
+\TrFrob{G}: \QCiso{G} &\to G(\Fq)^* \\
+(\gqcs{L},\phi) &\mapsto t_{(\gqcs{L},\phi)}
+\end{align*}
+is called \emph{Trace of Frobenius}.  If $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf
 then we will abbreviate $\trFrob{(\gqcs{L},\phi)}$ to $\trFrob{\qcs{L}}$.
@@
  $\trFrob{\qcs{L}\otimes \qcs{L'}} = \trFrob{\qcs{L}} \cdot \trFrob{\qcs{L'}}$.
-Since $\qcs{L} \iso \qcs{L'}$ implies $\trFrob{\qcs{L}} = \trFrob{\qcs{L'}}$,
-we obtain a group homomorphism
-\begin{align*}
-\trFrob{G} : \QCiso{G} &\to G(\Fq)^*, \\
-\qcs{L} &\mapsto \trFrob{\qcs{L}}.
-\end{align*}
-This homomorphism is functorial in the following sense:
+ Therefore $\TrFrob{G}$ is a homomorphism, which is functorial in the following sense:
 
 \begin{proposition}\label{prop:functorialG}
-Trace of Frobenius $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a natural transformation 
+Trace of Frobenius $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a natural transformation 
 between the two additive functors 
@@
   \begin{tikzcd}[row sep=20, column sep=30]
-   \QCiso{G} \rar{f^*} \arrow[swap]{d}{\trFrob{G}} & \QCiso{H} \dar{\trFrob{H}} \\
+   \QCiso{G} \rar{f^*} \arrow[swap]{d}{\TrFrob{G}} & \QCiso{H} \dar{\TrFrob{H}} \\
    G(\Fq)^* \rar & H(\Fq)^*
@@
   $f^* : \QC(G) \to \QC(H)$ is a monoidal functor.
-  The diagram relating $f^* : \QC(G) \to \QC(H)$, $f^* : G(k)^* \to H(k)^*$ and trace of Frobenius
+  The diagram relating $f^* : \QC(G) \to \QC(H)$, $f^* : G(k)^* \to H(k)^*$ and Trace of Frobenius
   commutes by \cite{laumon:87a}*{1.1.1.2}, where the ambient
@@
 \begin{tikzcd}[column sep=60]
-\arrow{d}{\trFrob{G_1} \times \trFrob{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes}
-& \arrow{d}{\trFrob{G_1\times G_2}} \QCiso{G_1\times G_2}\\
+\arrow{d}{\TrFrob{G_1} \times \TrFrob{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes}
+& \arrow{d}{\TrFrob{G_1\times G_2}} \QCiso{G_1\times G_2}\\
 (G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
@@
 while the second part shows that Trace of Frobenius is a natural transformation
-$t: F_1 \to F_2$. When further combined with Proposition~\ref{prop:product},
-we see that $F_1$ is an additive functor and $t: F_1 \to F_2$ is a natural
+$T: F_1 \to F_2$. When further combined with Proposition~\ref{prop:product},
+we see that $F_1$ is an additive functor and $T: F_1 \to F_2$ is a natural
 transformation between additive functors, 
@@
 \begin{tikzcd}
-\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\trFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\trFrob{G}} \\
+\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\TrFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\TrFrob{G}} \\
 G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
@@
 \begin{tikzcd}[column sep=60]
-\QCiso{G} \rar{\nu_{k'/k}} \dar{\trFrob{G}} & \QCiso{G_{k'}} \dar{\trFrob{G_{k'}}} \\
+\QCiso{G} \rar{\nu_{k'/k}} \dar{\TrFrob{G}} & \QCiso{G_{k'}} \dar{\TrFrob{G_{k'}}} \\
 G(k)^*  \rar{\Nm^*} & G(k')^*.
@@
 we may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
-and the value of $\Nm^*(t_G(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
+and the value of $\Nm^*(\TrFrob{G}(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
 Applying \ref{QC.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
@@
 \begin{tikzcd}
-\QCiso{\Res_{k'/k} G'} \dar{\trFrob{\Res_{k'/k} G'}} \rar{\rho} & \QCiso{G'} \dar{\trFrob{G'}}\\
+\QCiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \QCiso{G'} \dar{\TrFrob{G'}}\\
 G'(k')^* \rar & G'(k')^*
@@
 We will see in Corollary~\ref{cor:bounded-and-finite} that the bounded quasicharacter sheaves
-are precisely those whose trace of Frobenius have bounded image.
+are precisely those whose Trace of Frobenius have bounded image.
 
@@
 we will see in Corollary~\ref{cor:bounded-and-finite} that
-a quasicharacter sheaf is finite if and only if its trace of Frobenius has finite image.
+a quasicharacter sheaf is finite if and only if its Trace of Frobenius has finite image.
 
@@
   Composing with the splitting $\Weil{} \to \W(G,\bg)$ yields an $\ell$-adic character
-  $\rho_g : \Weil{} \to \EEx$, which is the same as the trace of Frobenius defined in Section~\ref{sec:Frob}:
+  $\rho_g : \Weil{} \to \EEx$, which is the same as the Trace of Frobenius defined in Section~\ref{sec:Frob}:
   \[
@@
  \[
-  \trFrob{G} : \QCiso{G} \to G(\Fq)^*
+  \TrFrob{G} : \QCiso{G} \to G(\Fq)^*
  \]
@@
  It suffices to observe that the group homomorphism
- $\trFrob{G} : \QCiso{G} \to G(\Fq)^*$
+ $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$
  is surjective because each character $\chi \in G(\Fq)^*$ determines a finite quasicharacter
- sheaf $(\Lang,\chi^{-1})$ such that the trace of Frobenius of the quasicharacter sheaf
+ sheaf $(\Lang,\chi^{-1})$ such that Trace of Frobenius of the quasicharacter sheaf
  $B_G (L_G(\Lang,\chi^{-1}))$ is $\chi$.
@@
 
-We saw in Proposition~\ref{prop:functorialG} that the trace of Frobenius
-$\trFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
-In fact, trace of Frobenius is an isomorphism when $G$ is a $\QC$-scheme.
+We saw in Proposition~\ref{prop:functorialG} that Trace of Frobenius
+$\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
+In fact, Trace of Frobenius is an isomorphism when $G$ is a $\QC$-scheme.
 
@@
   $\Fq$, and if the abelian group $\pi_0(G)(\bFq)$
-  is finitely generated, then the trace of Frobenius
-  \[
-  \trFrob{G} : \QCiso{G} \to G(\Fq)^*
+  is finitely generated, then Trace of Frobenius
+  \[
+  \TrFrob{G} : \QCiso{G} \to G(\Fq)^*
   \]
@@
   \begin{tikzcd}[row sep=30]
-    {}& \ker \trFrob{\pi_0(G)} \dar & \arrow[dashed]{d} \ker \trFrob{G} & \ker \trFrob{G^0} \dar & \\
-    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\trFrob{\pi_0(G)}}
-    & \QCiso{G} \rar \dar{\trFrob{G}} & \QCiso{G^0} \rar \dar{\trFrob{G^0}} & 0\\
+    {}& \ker \TrFrob{\pi_0(G)} \dar & \arrow[dashed]{d} \ker \TrFrob{G} & \ker \TrFrob{G^0} \dar & \\
+    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
+    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
     0 \rar & \pi_0(G)(\Fq)^* \rar \dar
     & \arrow[dashed]{d} G(\Fq)^* \rar & G^0(\Fq)^* \rar \dar & 0\\
-    & \coker \trFrob{\pi_0(G)} & \coker \trFrob{G} &  \coker \trFrob{G^0} &
+    & \coker \TrFrob{\pi_0(G)} & \coker \TrFrob{G} &  \coker \TrFrob{G^0} &
   \end{tikzcd}
@@
   Now Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}
-  imply that $\ker \trFrob{G^0} =0$ and $\coker \trFrob{G^0}=0$. 
-  Similarly, Proposition~\ref{prop:etale-iso} shows that $\ker \trFrob{\pi_0(G)}=0$
-  and $\coker \trFrob{\pi_0(G)}=0$.
+  imply that $\ker \TrFrob{G^0} =0$ and $\coker \TrFrob{G^0}=0$. 
+  Similarly, Proposition~\ref{prop:etale-iso} shows that $\ker \TrFrob{\pi_0(G)}=0$
+  and $\coker \TrFrob{\pi_0(G)}=0$.
   We may thus apply the snake lemma and conclude that
-  $\ker \trFrob{G}$ and $\coker \trFrob{G}$ both vanish.
+  $\ker \TrFrob{G}$ and $\coker \TrFrob{G}$ both vanish.
 \end{proof}
@@
 $G^0$, all quasicharacter sheaves are bounded and finite by Proposition~\ref{prop:connected}.
-On the other hand, $G^0(\Fq)$ is finite by Lemma~\ref{lem:G0alg-grp} and thus the trace of Frobenius
+On the other hand, $G^0(\Fq)$ is finite by Lemma~\ref{lem:G0alg-grp} and thus Trace of Frobenius
 has finite and therefore bounded image.  If $\chi \in G(\Fq)^*$ then there is some finite-image character $\chi_0$
@@
 $\qcs{L}$ that descend to Weil sheaves on $G$.  The conditions on the values $b_x$ then
-translate into analogous conditions on the image of trace of Frobenius.
+translate into analogous conditions on the image of Trace of Frobenius.
 \end{proof}

### 2014-02-14 dictionary.tex
Changes for submitting to Algebra & Number Theory

@@
 % !TEX encoding = UTF-8 Unicode
-%\documentclass{compositio}
 \documentclass{amsart}
@@
 \address{Pacific Institute for the Mathematical Sciences at the University of Calgary}
-%\classification{14L15 (primary), 11G25, 14F05, 14D24, 11S31 (secondary)}
-%\keywords{quasicharacters, quasicharacter sheaves, algebraic tori, Greenberg transforms, N\'eron models, local fields, group schemes}
+\subjclass[2010]{14F05 (primary), 14L15 (secondary)}
+\keywords{sheaf--function dictionary, geometrization, quasicharacter sheaves, commutative group schemes}
 
@@
 
-The sheaf--function dictionary for connected commutative algebraic groups over finite fields \cite{deligne:SGA4.5}*{sommes trig.} translates characters into local systems.
+The function--sheaf dictionary for connected commutative algebraic groups over finite fields \cite{deligne:SGA4.5}*{sommes trig.} translates characters into local systems.
 Let $G$ be a commutative group scheme over a finite field $\Fq$, let $\ell$ be any prime invertible in $\Fq$ and let $\chi : G(\Fq) \to \EEx$ be any character.
@@
  of $\ell$-adic local systems on $G$, where $m : G\times G \to G$ is the multiplication map for $G$.
-The sheaf--function dictionary for $G$ identifies a monoidal category of $\ell$-adic local systems on $G$ such that the group of isomorphism classes in this category is canonically identified with the $\ell$-adic character group of $G(\Fq)$, thus providing the geometrization and categorification of characters of $G(\Fq)$.
+The function--sheaf dictionary for $G$ identifies a monoidal category of $\ell$-adic local systems on $G$ such that the group of isomorphism classes in this category is canonically identified with the $\ell$-adic character group of $G(\Fq)$, thus providing the geometrization and categorification of characters of $G(\Fq)$.
 
 Although hidden in the discussion above, the connectness of $G$ played a crucial role in the geometrization and categorification of characters of $G(\Fq)$.
-So it is natural to ask if the sheaf--function dictionary can be generalized to not-necessarily connected commutative algebraic groups over finite fields.
+So it is natural to ask if the function--sheaf dictionary can be generalized to not-necessarily connected commutative algebraic groups over finite fields.
 In this paper we answer that question.
 %
-In fact, we show much more by exhibiting a sheaf--function dictionary, in the sense above, for any smooth commutative group scheme $G$, locally of finite type over a finite field $\Fq$, 
+In fact, we show much more by exhibiting a function--sheaf dictionary, in the sense above, for any smooth commutative group scheme $G$, locally of finite type over a finite field $\Fq$, 
 for which the geometric component group of $G$ is finitely generated; we call such group schemes $\QC$-schemes.
@@
 
-A simple example will illustrate some of the issues that arise when extending the sheaf--function dictionary to $\QC$-schemes. 
+A simple example will illustrate some of the issues that arise when extending the function--sheaf dictionary to $\QC$-schemes. 
 Consider the etale group scheme $G = \ZZ_{/\Fq}$. 

### 2014-02-20 dictionary.tex
Removed all redundant instanced of `locally of finite type'.

@@
   connected commutative algebraic groups over finite fields to smooth
-  commutative group schemes locally of finite type over finite fields
+  commutative group schemes over finite fields
   with finitely-generated geometric component group.
@@
 %
-In fact, we show much more by exhibiting a function--sheaf dictionary, in the sense above, for any smooth commutative group scheme $G$, locally of finite type over a finite field $\Fq$, 
+In fact, we show much more by exhibiting a function--sheaf dictionary, in the sense above, for any smooth commutative group scheme $G$
+over a finite field $\Fq$, 
 for which the geometric component group of $G$ is finitely generated; we call such group schemes $\QC$-schemes.
@@
 
-Throughout this paper, $G$ is a smooth, commutative group scheme locally of finite type
+Throughout this paper, $G$ is a smooth, commutative group scheme 
 over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.  For the sake of brevity, we
@@
 that forces $\QC$-schemes to have finitely generated geometric component group.  In fact,
-if $G$ is any smooth connected group scheme locally of finite type over $\Fq$
+if $G$ is any smooth connected group scheme over $\Fq$
 and if each quasicharacter sheaf on the \'etale group scheme $\pi_0(G)$ admits a global section 
@@
 \begin{proof}
- Since $G$ is a smooth group scheme locally of finite type over $\Fq$, its
+ Since $G$ is a smooth group scheme over $\Fq$, its
  identity component $G^0$ of $G$ is a connected smooth, 
@@
 \begin{theorem}\label{thm:snake}
-  If $G$ is a smooth, commutative group scheme, locally of finite type over
+  If $G$ is a smooth, commutative group scheme over
   $\Fq$, and if the abelian group $\pi_0(G)(\bFq)$

### 2014-03-30 dictionary.tex
Updated the bibliography

@@
 
-The function--sheaf dictionary for connected commutative algebraic groups over finite fields \cite{deligne:SGA4.5}*{sommes trig.} translates characters into local systems.
-Let $G$ be a commutative group scheme over a finite field $\Fq$, let $\ell$ be any prime invertible in $\Fq$ and let $\chi : G(\Fq) \to \EEx$ be any character.
+Let us briefly review how the function--sheaf dictionary for connected commutative algebraic groups over finite fields \cite{deligne:SGA4.5}*{sommes trig.} translates characters into local systems.
+Let $\Fq$ be a finite field and let $G$ be a connected commutative algebraic groups over $\Fq$.
+Fix a prime $\ell$ invertible in $\Fq$ and let $\chi : G(\Fq) \to \EEx$ be any character.
 Using little more than the Lang map for $G$, $\chi$ determines an $\ell$-adic local system $\qcs{L}$ on $G$ from which the character $\chi$ can be recovered using the Frobenius automorphism of $\bG$, the base change of $G$ to $\bFq$.
@@
 satisfying \eqref{section}, then the conclusion of Theorem~\ref{thm:snake} holds for $G$.
+\Clifton{Add a remark that quasicharacter sheaves on $\QQ$ admit global sections, too, although, of course, $\QQ$ is not a QC-scheme?}
 

### 2014-04-03 dictionary.tex
Huge changes in this commit. (Sorry)
Added a section on invisible quasicharacter sheaves.
Major surgery on the section on etale group schemes.

@@
 \title[The function--sheaf dictionary]{The function--sheaf dictionary for smooth commutative group schemes over finite fields}
-% with finitely generated geometric component group}
 \date{\today}
@@
 % AMS packages
-\usepackage{amsmath, amsthm, amssymb}
+\usepackage{amsmath, amsthm, amssymb, todonotes}
 \usepackage[alphabetic]{amsrefs}
@@
   connected commutative algebraic groups over finite fields to smooth
-  commutative group schemes over finite fields
-  with finitely-generated geometric component group.
-  To do so, we introduce the category of quasicharacter sheaves on such group schemes
-  $G$ over $\mathbb{F}_q$ and exhibit a functorial isomorphism between the character group of $G(\mathbb{F}_q)$ and the group of isomorphism classes of quasicharacter sheaves on $G$.
+  commutative group schemes over finite fields.
+  To do so, we introduce the monoidal category of quasicharacter sheaves on
+  smooth commutative group schemes $G$ over $\mathbb{F}_q$
+  and show that the Trace of Frobenius is a functorial surjection
+  from the group of isomorphism classes of quasicharacter sheaves on $G$
+  onto the character group of $G(\mathbb{F}_q)$.
+  If $G$ is connected, the kernel of this surjection is trivial.
+  When $G$ is etale, however, the kernel is generally non-trivial,
+  leading to interesting notion of invisible quasicharacter sheaves.
+  We find a classification of invisible quasicharacter sheaves
+  on etale commutative group schemes over $\mathbb{F}_q$
+  in terms of the cohomology of $G(\mathbb{F}_q)$.
    \end{abstract}
@@
 
+Motivated by ...., in this paper we ...
+The component group of the Neron model of algebraic torus over local field ...
+The sheaf--function dictionary for etale group schemes is significantly different .
+.
+.\todo{Needs a new front end to really set the tone, and highten the contrast with the connected case, and point to applications.}
+
 Let us briefly review how the function--sheaf dictionary for connected commutative algebraic groups over finite fields \cite{deligne:SGA4.5}*{sommes trig.} translates characters into local systems.
-Let $\Fq$ be a finite field and let $G$ be a connected commutative algebraic groups over $\Fq$.
+Let $\Fq$ be a finite field and let $G$ be a connected commutative algebraic group over $\Fq$; fix an algebraic closure $\bFq$ of $\Fq$
+and let $\bG$ be the base change of $G$ to $\bFq$.
 Fix a prime $\ell$ invertible in $\Fq$ and let $\chi : G(\Fq) \to \EEx$ be any character.
-Using little more than the Lang map for $G$, $\chi$ determines an $\ell$-adic local system $\qcs{L}$ on $G$ from which the character $\chi$ can be recovered using the Frobenius automorphism of $\bG$, the base change of $G$ to $\bFq$.
+Using little more than the Lang map for $G$, $\chi$ determines an $\ell$-adic local system $\qcs{L}$ on $G$ from which the character $\chi$ can be recovered using the Frobenius automorphism of $\bG$.
 While this recovery process applies to all $\ell$-adic local systems $\qcs{L}$ on $G$, those that produce characters of $G(\Fq)$ are distinguished by a simple property: there exists an isomorphism
@@
 Although hidden in the discussion above, the connectness of $G$ played a crucial role in the geometrization and categorification of characters of $G(\Fq)$.
-So it is natural to ask if the function--sheaf dictionary can be generalized to not-necessarily connected commutative algebraic groups over finite fields.
-In this paper we answer that question.
-%
-In fact, we show much more by exhibiting a function--sheaf dictionary, in the sense above, for any smooth commutative group scheme $G$
-over a finite field $\Fq$, 
-for which the geometric component group of $G$ is finitely generated; we call such group schemes $\QC$-schemes.
-To do this we must pass from $\ell$-adic local systems on a $\QC$-scheme $G$ to Weil local systems on $G$ 
-and also keep track of the isomorphisms \eqref{introbox} (existence of such an isomorphism is not enough), leading to the notion of {\it quasicharacter sheaves on $G$}.
-
+So it is natural to ask how the function--sheaf dictionary generalizes to not-necessarily connected commutative algebraic groups over finite fields.
+In this paper we answer that question by exhibiting a function--sheaf dictionary, in the sense above, for any smooth commutative group scheme $G$ over a finite field $\Fq$.
+To do this we must pass from $\ell$-adic local systems on $G$ to Weil local systems on $G$
+and also keep track of the isomorphisms \eqref{introbox} (mere existence of such an isomorphism is not enough), leading to the notion of {\it quasicharacter sheaves on $G$}.
+But the result  . . . .
+
+So, what is a quasicharacter sheaf?
 A quasicharacter sheaf on $G$ is a triple $\qcs{L}\ceq
 (\gqcs{L},\mu,\phi)$ where $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ of rank~one and $\mu: m^*
-\gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms satisfying natural compatibilty conditions.
-The main result of this paper is the following statement (see Theorem~\ref{thm:snake}, which says more):
+\gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms satisfying natural compatibilty conditions; here $\Frob{G}$ is the Frobenius automorphism of ${\bar G}$.
+The main result of this paper is the following statement (see Theorem~\ref{thm:snake}):
 the category $\QC(G)$ of quasicharacter sheaves on $G$
-is a rigid monoidal category and Trace of Frobenius provides an isomorphism
+is a rigid monoidal category and Trace of Frobenius provides a functorial surjection
 \begin{equation}
-\QCiso{G} \to \Hom(G(\Fq), \EEx).
+\QCiso{G} \to \Hom(G(\Fq), \EEx)
 \end{equation}
+with a canonical section,
+and the kernel of the Trace of Frobenius is classified by the classes in $\Hh^2(\pi_0({\bar G}),\EEx)$ that are fixed by Frobenius.
+In contrast to the case of connected commutative algebraic groups, the Trace of Frobenius is not injective.
+We refer to quasicharacter sheaves in the kernel of Trace of Frobenius as \emph{invisible} quasicharacter sheaves.
+The canonical section of the Trace of Frobenius allows one to convert any quasicharacter of $G(\Fq)$
+into a quasicharacter sheaf on $G$.
 In this way, quasicharacter sheaves geometrize characters of $G(\Fq)$.
 
-A simple example will illustrate some of the issues that arise when extending the function--sheaf dictionary to $\QC$-schemes. 
-Consider the etale group scheme $G = \ZZ_{/\Fq}$. 
-Characters of $G(\Fq) = \ZZ$ are neither finite nor bounded, in general. 
-For example, while the $\ell$-adic character $\ZZ \to \EEx$ defined by 
-$1 \mapsto -1$ has finite order, the character defined by 
-$1 \mapsto 1+ \ell$ does not, although its image is bounded, while the character $\ZZ \to \EEx$ defined by 
+Three examples will illustrate some of the issues that arise when extending the function--sheaf dictionary to smooth commutative group schemes.
+First, consider the etale group scheme $\ZZ$ over $\Fq$.
+While the $\ell$-adic character $\ZZ \to \EEx$ defined by
+$1 \mapsto -1$, has finite order, the character defined by
+$1 \mapsto 1+\ell$ does not, although its image is bounded;
+on the other hand, the character $\ZZ \to \EEx$ defined by
 $1 \mapsto \ell$ has unbounded image.
 As we show in the paper, $\ell$-adic local systems on $G$ can only be used to geometrize characters of finite order; quasicharacter sheaves, however, provide the geometrization of all characters of $G(\Fq)$.
+Second, consider the etale group scheme $\ZZ \times \ZZ$.
+\todo{Build an example of an invisible quasicharacter sheaf.}
+Finally, consider the etale group scheme $\ZZ \times \ZZ$ over $\Fq$ with Galois action determined by $\sigma(n,m) = (m,n)$ when the restriction of $\sigma$ to $\mathbb{F}_{q^2}$ is non-trivial.
+Although there are infinitly-many geometric points on this group, it has exactly one $\Fq$-rational point.
+In this case, the group carries only one isomorphism class of quasicharacter sheaves -- in particular, it has no invisible quasicharacter sheaves -- so the dictionary is perfect, albeit trivial, in this case.
 
@@
 Greenberg transform of the N\'eron model of an algebraic torus over an arbitrary local field.
-The ability to work with non-connected group schemes plays a crucial role in this application,
-since these $\QC$-schemes are not connected in general.
+The ability to work with non-connected group schemes,
+of which the component group of the special fibre of the Neron model of a torus is an important example,
+plays a crucial role in this application,
+since these group schemes are not connected in general.
 This process of creating a category from the group of quasicharacters of such a torus
@@
 and note that if $(\gqcs{L},\phi) \iso (\gqcs{L'},\phi')$ then $\trFrob{(\gqcs{L},\phi)} = \trFrob{(\gqcs{L'},\phi')}$.
+ If $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf
+then we will abbreviate $\trFrob{(\gqcs{L},\phi)}$ to $\trFrob{\qcs{L}}$.
 
@@
 \TrFrob{G}: \QCiso{G} &\to G(\Fq)^* \\
-(\gqcs{L},\phi) &\mapsto t_{(\gqcs{L},\phi)}
+\qcs{L} &\mapsto t_{\qcs{L}}
 \end{align*}
-is called \emph{Trace of Frobenius}.  If $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf
-then we will abbreviate $\trFrob{(\gqcs{L},\phi)}$ to $\trFrob{\qcs{L}}$.
+is called \emph{Trace of Frobenius}.
 \end{definition}
@@
 \end{align*}
-from the category of $\QC$-schemes to the category of abelian groups.
+from the category of smooth commutative group schemes over $\Fq$ to the category of abelian groups.
 \end{proposition}
@@
 As a step toward the proof of Proposition~\ref{prop:functorialG} we show that every
-morphism  $H \to G$ of $\QC$-schemes induces a monoidal functor from quasicharacter
+morphism  $H \to G$ of smooth commutative groups schemes over $\Fq$ induces a monoidal functor from quasicharacter
 sheaves on $G$ to quasicharacters on $H$. This simple but important result will also
@@
 \begin{proposition}\label{prop:pullback}
-  If $f : H\to G$ is a morphism of $\QC$-schemes then
+  If $f : H\to G$ is a morphism of smooth commutative group schemes over $\Fq$ then
   \begin{align*}
@@
 \begin{proposition}\label{prop:product}
-If $G_1$ and $G_2$ are $\QC$-schemes then the rule
+If $G_1$ and $G_2$ are smooth commutative group schemes over $\Fq$ then the rule
 $\boxtimes : (\qcs{L}_1,\qcs{L}_2)\to \qcs{L}_1\boxtimes\qcs{L}_2$ defines an equivalence of categories
@@
 
+\section{Invisible quasicharacter sheaves}\label{sec:invisible}
+
+We will see that the Trace of Frobenius may not provide complete
+information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not connected.
+Our main tool for understanding this phenomenon is the function
+\begin{equation}\label{2cocycle}
+\QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))
+\end{equation}
+defined below.
+Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
+For each geometric point $x\in G(\bFq)$, choose a basis $\{ v_x \}$ for $\gqcs{L}_x$.
+This choice determines a function $g : G(\bFq)\times G(\bFq) \to \EEx$ defined by
+\[
+\mu_{x,y}(v_{x+y}) = g(x,y) v_x \otimes v_y.
+\]
+Chasing through the diagram in Condition~\ref{QC.2} we see that
+\[
+g(x+y,z) g(x,y) = g(x,y+z) g(y,z),
+\]
+for all $x,y,z\in G(\bFq)$, so $g \in Z^2(G(\bFq),\EEx)$.
+It is easy to see that the class of $g$ is independent of the choice made above;
+let $g_\mathcal{L} \in H^2(G(\bFq),\EEx)$ the class of $g\in Z^2(G(\bFq),\EEx)$.
+It is also easy to see that the class that $g_\mathcal{L} = g_\mathcal{L'}$ when $\qcs{L} \iso \qcs{L'}$. This defines
+\[
+\QCiso{G} \to H^2(G(\bFq),\EEx).
+\]
+We claim that $g_\qcs{L}$ is also fixed by the action of $\Weil{}$ on $H^2(G(\bFq),\EEx)$
+inherited from the action of $\Weil{}$ on $G(\bFq)$.
+To see this, we return to the choice $\{ v_x \in \gqcs{L}_x^\times \tq x\in G(\bFq) \}$
+and define $f : G(\bFq) \to \EEx$ by
+\[
+\phi_x(v_{\Frob{G}(x)}) = f(x) v_x.
+\]
+Chasing through the diagram in Condition~\ref{QC.3} we see that
+\begin{equation}\label{nohom}
+f(x+y) = f(x) f(y) \frac{(\,^{\Frob{}}g)(x,y)}{g(x,y)}
+\end{equation}
+for all $x,y \in G(\bFq)$. Thus, the class $\,^{\Frob{}}g_\qcs{L}$ of $\,^{\Frob{}}g$ coincides
+with the class $g_\qcs{L}$ of $g$. This concludes the definition of
+\[
+\QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx)).
+\]
+
+\begin{definition}\label{def:invisible}
+Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We say $\qcs{L}$ is \emph{visible} $g_\qcs{L} \in H^0(\Weil{},H^2(G(\bFq),\EEx))$ is trivial; otherwise, we say $\qcs{L}$ is \emph{invisible}.
+\end{definition}
+
+If $G$ is a connected and of finite type, 
+then $H^2(G(\bFq),\EEx)$ is trivial \todo{Reference?} so all quasicharacter sheaves on connected commutative algebraic groups $G$ are visible; 
+ by contrast, if $G$ is etale then $H^2(G(\bFq),\EEx)$ may be non-trivial and $G$ may admit invisible quasicharacters sheaves.
+We will return to the latter case in Section~\ref{sec:etale}.
+In the meantime, we end this section with a simple property of \eqref{2cocycle}.
+
+\begin{lemma}
+The function defined in \eqref{2cocycle} is a homomorphism:
+\[
+g_{\qcs{L}\otimes \qcs{L'}} = g_{\qcs{L}} \, g_\qcs{L'}
+\]
+for every $\qcs{L}, \qcs{L'} \in \QC(G)$.
+\end{lemma}
+
 \section{Base change}\label{sec:basechange}
@@
 
-Finally, let $G'$ be a $\QC$-scheme over $k'$;
+Finally, let $G'$ be a smooth commutative group scheme over $k'$;
 we explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
@@
 beginning with the localization of a category introduced here.
-Let us say that a morphism $f : H\to G$ of $\QC$-schemes is a \emph{discrete isogeny}
+Let us say that a morphism $f : H\to G$ of smooth commutative group schemes over $\Fq$ is a \emph{discrete isogeny}
 if it is finite, surjective and \'etale and the action of $\Gal(\bFq/\Fq)$ on the \'etale group
@@
 \begin{itemize}
-\item $f : H\to G$ is a discrete isogeny of $\QC$-schemes,
+\item $f : H\to G$ is a discrete isogeny of smooth commutative group schemes over $\Fq$,
 \item $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$.
@@
 \'Etale group schemes form a counterpoint to connected groups,
-since the component group of a $\QC$-scheme
+since the component group of a smooth commutative group scheme
 is an \'etale group scheme \cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
-The functor $G \mapsto G(\bFq)$ defines an equivalence of categories
-between the category of \'etale group schemes over $\Fq$ and the category of groups equipped
+However, the function--sheaf dictionary is substantially differentl in the two cases.
+To see why, we begin by specializing the definition of quasicharacter sheaves to the case
+of etale commutative group schemes,
+using the equivalence $G \mapsto G(\bFq)$
+from the category of \'etale group schemes over $\Fq$ to the category of groups equipped
 with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group.
-Under this equivalence, a quasicharacter sheaf on $G$ is given by the data of:
+Under this equivalence, a quasicharacter sheaf on an etale commutative group scheme $G$ over $\Fq$ is given by the data of:
 \begin{enumerate}
@@
 
-A \emph{global section} of $\qcs{L}$ is a function $s : G(\bFq) \to \coprod_{x \in G(\bFq)} \gqcs{L}_x$
-so that $s(x) \in \gqcs{L}_x$ for all $x \in G(\bFq)$ and
-\begin{equation}\label{section}
-\mu_{x,y}(s(x+y)) = s(x) \otimes s(y).
+\begin{lemma}\label{prop:etale-2cocycle}
+    If $G$ is an \'etale commutative group scheme over $\Fq$
+    then the homomorphism
+    \[
+    \QCiso{G} \to \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx)),
+    \]
+    defined in Section~\ref{sec:invisible}, is surjective.
+\end{lemma}
+
+\begin{proof}
+Pick $[g]\in \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx))$.
+Then $g\in Z^2(G(\bFq),\EEx)$ is fixed by Frobenius, so $\,^{\Frob{}}g = g h$ for some $h\in B^2(G(\bFq),\EEx)$.
+Accordingly, $h(x,y) = \frac{f(x+y)}{f(x) f(y)}$ for some $f : G(\bFq) \to \EEx$, so
+\begin{equation}\label{gf}
+g(\Frob{}(x),\Frob{}(y)) = g(x,y) \frac{f(x+y)}{f(x) f(y)}
 \end{equation}
-
-We say that a section is \emph{nontrivial} if $s(x) \ne 0$ for all $x \in G(\bFq)$. 
-Note that the only other section is the constant zero section.
-
-\begin{lemma}\label{lemma:section}
- If $\qcs{L}$ is a quasicharacter sheaf on an \'etale $\QC$-scheme $G$ then $\qcs{L}$ has a nontrivial global section.
+for all $x,y\in G(\bFq)$.
+Set $\gqcs{L}_x = \EE$ for every $x\in G(\bFq)$ and define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x \otimes \gqcs{L}_y$ by $\mu_{x,y}(1) = g(x,y) 1 \otimes 1$.
+Since $g\in Z^2(G(\bFq),\EEx)$, the indexed set of isomorphisms $\{ \mu_{x,y} \tq x,y \in G(\bFq) \}$ satisfies \ref{qc.2}.
+Define $\phi_x : \gqcs{L}_{\Frob{}(x)}\to \gqcs{L}_x$ by $\phi_x(1) = f(x)$.
+Then set of isomorphisms $\{ \phi_{x} \tq x \in G(\bFq) \}$ satisfies \ref{qc.3} by \eqref{gf}.
+In this way, the cocycle $g\in Z^0(\Weil{}, Z^2(G(\bFq),\EEx))$ defines a quasicharacter sheaf $\qcs{L}$.
+It is now clear that $\qcs{L}$ maps to $[g] \in \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx))$ under \eqref{2cocycle}.
+\end{proof}
+
+In order to relate $\QCiso{G}$ to $G(k)^*$, we need a simple result relating duals, invariants and coinvariants.
+
+\begin{lemma} \label{lem:dual-inv}
+Let $X$ be an abelian group equipped with an action of $\Weil{}$.
+ Then
+\begin{align*}
+ (X^*)_{\Frob{}} &\to (X^{\Frob{}})^* \\
+ [f] &\mapsto f|_{X^{\Frob{}}}
+\end{align*}
+is an isomorphism.
 \end{lemma}
@@
 \begin{proof}
-  Since $G(\bFq)$ is a finitely-generated abelian group, it admits a decomposition
-  \[
-  G(\bFq) \iso \ZZ^r \oplus \bigoplus_{j=1}^t \ZZ / m_j \ZZ;
-  \]
-  let $x_1, \ldots, x_r, y_1, \ldots, y_t$ be a corresponding set of generators of $G(\bFq)$.
-  We will define a section $s$ satisfying \eqref{section} by choosing values on these generators and extending to all
-  of $G(\bFq)$ through \eqref{section}.
-
-  There is a unique isomorphism $\gqcs{L}_0 \cong \EE$ under which $\mu_{0,0}^{-1}$ corresponds
-  to the multiplication map $\EE \otimes\EE \to \EE$.
-  The condition $\mu_{0,0}(s(0)) = s(0) \otimes s(0)$ together with the non-triviality of $s$
-  then forces $s(0) = 1$.
-
-  The $\mu_{x,y}$ yield an isomorphism $\alpha_j : \gqcs{L}_{y_j}^{\otimes m_j} \to \gqcs{L}_0$.
-  An initial nonzero choice of $s(y_j)$ need only be scaled by $\alpha_j(s(y_j))^{-1/m_j}$ in order to map to
-  $1$ under this isomorphism.  Since compatibility under the $\alpha_j$ are the only constraints on the
-  $s(x_j)$ and $s(y_j)$, global sections exist.
-\end{proof}
-
-We note that this lemma is the only ingredient of the proof of Theorem~\ref{thm:snake}
-that forces $\QC$-schemes to have finitely generated geometric component group.  In fact,
-if $G$ is any smooth connected group scheme over $\Fq$
-and if each quasicharacter sheaf on the \'etale group scheme $\pi_0(G)$ admits a global section 
-satisfying \eqref{section}, then the conclusion of Theorem~\ref{thm:snake} holds for $G$.
-\Clifton{Add a remark that quasicharacter sheaves on $\QQ$ admit global sections, too, although, of course, $\QQ$ is not a QC-scheme?}
-
-\begin{proposition}\label{prop:etale}
-  Let $G$ be an \'etale $\QC$-scheme.
+We can describe $X^{\Frob{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
+let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
+\[
+ 0 \to X^{\Frob{}} \to X \to Y \to 0
+\]
+yields
+\[
+ 0 \to Y^* \to X^* \to (X^{\Frob{}})^* \to \Ext^1_\ZZ(Y, \EEx).
+\]
+Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Frob{}})^*$.
+\end{proof}
+
+\begin{lemma}\label{prop:etale-trace}
+If $G$ is an \'etale commutative group scheme over $\Fq$
+then for every the $\chi \in G(\Fq)^*$ there is a visible quasicharacter sheaf $\qcs{L}$ on $G$ such that $\trFrob{\qcs{L}} = \chi$.
+In particular, Trace of Frobenius
+\[
+\TrFrob{G} : \QCiso{G} \to G(\Fq)^*,
+\]
+is surjective.
+\end{lemma}
+
+\begin{proof}
+Pick $\chi \in G(\Fq)^*$.
+By Lemma~\ref{lem:dual-inv}, there is some $f\in G(\bFq)^*$ such that $f\vert_{G(\Fq)^*} = \chi$.
+Set $\gqcs{L}_x = \EE$ for every $x\in G(\bFq)$.
+Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$.
+Define $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = f(x)$.
+Since $f : G(\bFq) \to \EEx$ is a group homomorphism,
+condition \eqref{nohom} is satisfied with $g =1$, the trivial cocycle in $Z^2(G(\bFq),\EEx)$.
+It is now clear that we have defined a \emph{visible} quasicharacter sheaf $\qcs{L}$ with $\trFrob{\qcs{L}} = \chi$.
+\end{proof}
+
+\begin{proposition}\label{prop:etale-fg}
+  If $G$ is an \'etale commutative group scheme over $\Fq$ and
+  $G(\bFq)$ is finitely generated,
+  then
+  \[
+  \QCiso{G} \iso \Hh^2(G(\bFq)\rtimes \Weil{}, \EEx).
+  \]
+  Moreover, this isomorphism is functorial
+  in the sense of Proposition~\ref{prop:functorialG}.
+\end{proposition}
+
   We may associate a $1$-cocycle $\tau_\qcs{L}: \Weil{}\to G(\bFq)^*$ to each $\qcs{L} \in \QC(G)$
@@
   \begin{align*}
-  \QCiso{G} &\to \Hh^1(\Weil{}, G(\bFq)^*), \\
+  \QCiso{G} &\to \Hh^1(\Weil{}, G(\bFq)^*),\\
   [\qcs{L}] &\mapsto [\tau_\qcs{L}],
@@
   is an isomorphism.
-\end{proposition}
 
@@
   the scalar $\tau_\qcs{L}(\Frob{})(x)$ is non-zero.  Moreover,
-  \ref{qc.1} forces
+  \ref{qc.2} forces
   $\tau_\qcs{L}(\Frob{})(x+y) = \tau_\qcs{L}(\Frob{})(x) \ \tau_\qcs{L}(\Frob{})(y)$
@@
   $\qcs{L}$ and let $\tau_1$ and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$.
-  For each $x \in G(\bFq)$ set $a(x) = \frac{s_2(x)}{s_1(x)}$.  Then \eqref{section} and
+  For each $x \in G(\bFq)$ define $a(x) \in \EEx$ by $s_2(x) = a(x) s_1(x)$.
+  Then \eqref{section} and
   \ref{qc.2} together imply $a(x+y) = a(x)a(y)$, so
@@
 
-In order to relate $\QCiso{G}$ to $G(k)^*$, we need a simple result relating duals, invariants and coinvariants.
-
-\begin{lemma} \label{lem:dual-inv}
-Let $X$ be an abelian group equipped with an action of $\Weil{}$.
- Then
-\begin{align*}
- (X^*)_{\Frob{}} &\to (X^{\Frob{}})^* \\
- [f] &\mapsto f|_{X^{\Frob{}}}
-\end{align*}
-is an isomorphism.
-\end{lemma}
-\begin{proof}
-We can describe $X^{\Frob{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
-let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
-\[
- 0 \to X^{\Frob{}} \to X \to Y \to 0
-\]
-yields
-\[
- 0 \to Y^* \to X^* \to (X^{\Frob{}})^* \to \Ext^1_\ZZ(Y, \EEx).
-\]
-Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Frob{}})^*$.
-\end{proof}
-
 \begin{proposition} \label{prop:etale-iso}
@@
 \begin{lemma} \label{lem:G0alg-grp}
-If $G$ is a $\QC$-scheme then $G^0$ is a connected algebraic group.
+If $G$ is a commutative smooth group scheme over $\Fq$ then $G^0$ is a connected algebraic group.
 \end{lemma}
@@
   If $G$ is a smooth, commutative group scheme over
-  $\Fq$, and if the abelian group $\pi_0(G)(\bFq)$
-  is finitely generated, then Trace of Frobenius
+  $\Fq$ then Trace of Frobenius
   \[
@@
   \]
-  is a functorial isomorphism of groups. 
+  is a functorial surjection with kernel $\Hh^0(\Weil{}, \Hh^2(\pi_0({\bar G}), \EE))$ and a canonical section.
 \end{theorem}
@@
 \bibliographystyle{amsalpha}
-\bibliography{bibliography/Biblio}
+\bibliography{Biblio}
 
 \end{document}
+%sagemathcloud={"zoom_width":120}

### 2014-04-03 dictionary.tex
Cut out that really long annoying proposition, which was based on a false premise (the existence of global sections) and replaced it with two news lemmas.
Still working on the section on etale group schemes.

@@
 
-In order to relate $\QCiso{G}$ to $G(k)^*$, we need a simple result relating duals, invariants and coinvariants.
+%In order to relate $\QCiso{G}$ to $G(k)^*$, we need a simple result relating duals, invariants and coinvariants.
 
@@
 \]
-is surjective.
+is surjective, even when restricted to visible quasicharacter sheaves.
 \end{lemma}
@@
 
-\begin{proposition}\label{prop:etale-fg}
-  If $G$ is an \'etale commutative group scheme over $\Fq$ and
-  $G(\bFq)$ is finitely generated,
+\begin{proposition} \label{prop:etale-iso}
+	If $G$ is an \'etale commutative group scheme over $\Fq$ 
+	and if $G(\bFq)$ is finitely generated,
   	then
@@
 
-  We may associate a $1$-cocycle $\tau_\qcs{L}: \Weil{}\to G(\bFq)^*$ to each $\qcs{L} \in \QC(G)$
-  so that
-  \[
-  \tau_\qcs{L}(\Frob{})(x) = \trFrob{\qcs{L}}(x)
-  \]
-  for all $x \in G(\Fq)$ and the map
-  \begin{align*}
-  \QCiso{G} &\to \Hh^1(\Weil{}, G(\bFq)^*),\\
-  [\qcs{L}] &\mapsto [\tau_\qcs{L}],
-  \end{align*}
-  is an isomorphism.
-
-\begin{proof}
-  Suppose $\qcs{L}$ is a quasicharacter sheaf on $G$ and choose a global section $s$
-  of $\qcs{L}$ using Lemma~\ref{lemma:section}.
-   We will construct a group isomorphism between $\QCiso{G}$ and
-  $\Hh^1(\Weil{}, G(\bFq)^*)$ using $s$, then prove independence from the choice of $s$.
-
-  Starting from $\qcs{L}$, we define a cocyle $\tau_{\qcs{L}} \in Z^1(\Weil{},G(\bFq)^*)$ as follows.
-  For $x \in G(\bFq)$, $\qcs{L}$ determines an isomorphism $\phi_x : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
-  of one-dimensional $\EE$-vector spaces; define $\tau_\qcs{L}$ by
-  \begin{equation}\label{t}
-   \phi_{x}(s(\Frob{}(x))) = \tau_\qcs{L}(\Frob{})(x) s(x).
-  \end{equation}
-  Note that if $x$ is fixed by $\Frob{}$ then $\tau_\qcs{L}(\Frob{})(x)$ is just $\trFrob{\qcs{L}}(x)$, so the restriction of
-  $\tau_\qcs{L}(\Frob{})$ to $G(k)$ is just $\trFrob{\qcs{L}}$.
-  In general, \ref{qc.1} and \ref{qc.3}, together with \eqref{section}, guarantee that
-  the scalar $\tau_\qcs{L}(\Frob{})(x)$ is non-zero.  Moreover,
-  \ref{qc.2} forces
-  $\tau_\qcs{L}(\Frob{})(x+y) = \tau_\qcs{L}(\Frob{})(x) \ \tau_\qcs{L}(\Frob{})(y)$
-  for all $x,y \in G(\bFq)$.  We write $\cdot$ for pointwise multiplication of functions, and
-  define $\tau_\qcs{L} : \Weil{} \to G(\bFq)^*$ recursively by
-  \[
-   \tau_\qcs{L}(\Frob{}^n) \ceq \tau_\qcs{L}(\Frob{})\cdot \,^{\Frob{}} \tau_\qcs{L}(\Frob{}^{n-1}),
-  \]
-  where $\Frob{}$ acts on $G(\bFq)^*$ through pre-composition.
-
-  Although we used a global section $s$ in the definition of
-  $\tau_\qcs{L}$, the class of $\tau_\qcs{L}$ does not depend on this
-  choice. To see why, let $s_1$ and $s_2$ be two nontrivial global sections of
-  $\qcs{L}$ and let $\tau_1$ and $\tau_2$ be the cocycles defined by $s_1$ and $s_2$.
-  For each $x \in G(\bFq)$ define $a(x) \in \EEx$ by $s_2(x) = a(x) s_1(x)$.
-  Then \eqref{section} and
-  \ref{qc.2} together imply $a(x+y) = a(x)a(y)$, so
-  $a\in G(\bFq)^*$.  The coboundary $\tau_0 : \Weil{} \to G(\bFq)^*$
-  defined by $\tau_0(\Frob{}) \ceq \,^{\Frob{}} a \cdot a^{-1}$ satisfies $\tau_2 = \tau_0 \tau_1$,
-  so $\tau_2$ and $\tau_1$ are cohomologous. Thus
-  \begin{equation}\label{cohomologous}
-  \begin{split}
-    \obj \QC(G) &\to \Hh^1(\Weil{},G(\bFq)^*), \\
-    \qcs{L} &\mapsto [\tau_\qcs{L}],
-  \end{split}
-  \end{equation}
-  is independent of the choice of global sections made above.
-
-  We now show that $[\tau_\qcs{L}]$ depends only on the isomorphism class of $\qcs{L}$.
-  Let $\alpha : \qcs{L} \to \qcs{L'}$ be an isomorphism and
-  let $\tau$ and $\tau'$ be any cocycles representing the classes in the
-  image of $\qcs{L}$ and $\qcs{L'}$ under \eqref{cohomologous}; by construction,
-  $\tau$ and $\tau'$ are defined by the choice of sections $s$ and $s'$.
-  Now, $\varphi_x(s(x))$ is a
-  non-zero scalar multiple of $s'(x)$; define $a: G(\bFq) \to \EEx$
-  by $\alpha_x(s(x)) = a(x) s'(x)$.
-  By the second part of \ref{qc.4},
-  $a(x+y) = a(x)a(y)$, so $a \in G(\bFq)^*$. By the first part of
-  \ref{qc.4},
-  $\tau'(\Frob{}) = \tau(\Frob{}) \cdot (\,^{\Frob{}^{-1}}a \cdot a^{-1})$,
-  so $\tau$ and $\tau'$ are cohomologous. This shows that
-  \begin{equation}\label{pich1}
-  \begin{split}
-    \QCiso{G} &\to \Hh^1(\Weil{},G(\bFq)^*),\\
-    [\qcs{L}] &\mapsto [\tau_\qcs{L}]
-  \end{split}
-  \end{equation}
-  is well-defined.
-
-    Suppose that $\qcs{L}$ and $\qcs{L}'$ are two quasicharacter sheaves on $G$.
-  If $s$ is a global section for $\qcs{L}$ and $s'$ for $\qcs{L}'$ then $s \otimes s'$
-  is a global section for $\qcs{L} \otimes\qcs{L}'$.  The three versions of \eqref{t}
-  for $\qcs{L}, \qcs{L'}$ and $\qcs{L} \otimes\qcs{L}'$ imply that
-  $\tau_{\qcs{L} \otimes\qcs{L}'}(\Frob{}) = \tau_\qcs{L}(\Frob{}) \tau_{\qcs{L}'}(\Frob{})$,
-  so \eqref{pich1} is a group homomorphism.
-
- To see that \eqref{pich1} is injective,
- suppose $[\tau_\qcs{L}] = [\tau_\qcs{L'}]$.
- Let $s$ and $s'$ be sections appearing in the definition of $\tau_\qcs{L}$ and $\tau_\qcs{L'}$.
- Since $[\tau_\qcs{L}] = [\tau_\qcs{L'}]$,
- it follows that $\tau_\qcs{L}$ and $\tau_{\qcs{L'}}$ are cohomologous,
- so there is some $a\in G(\Fq)^*$ such that
- $\tau'(\Frob{}) = \tau(\Frob{}) \cdot (\,^{\Frob{}}a \cdot a^{-1})$.
- Define $\alpha : \qcs{L}\to \qcs{L'}$ by $\alpha_x(s(x)) \ceq a(x) s'(x)$ and $\alpha^{-1} : \qcs{L}'\to \qcs{L}$
- by $\alpha^{-1}_x(s'(x)) \ceq a(x)^{-1} s(x)$, for $x\in G(\bFq)$.
- It is straightforward to check that $\alpha$ satisfies \ref{qc.3}
- and that $\alpha^{-1}$ is its inverse. Thus $\qcs{L} \iso \qcs{L'}$ in $\QC(G)$ and \eqref{pich1} is injective.
-
- Finally, to show that \eqref{pich1} is surjective, pick $[\tau]\in \Hh^1(\Weil{}, G(\bFq)^*)$.
- For each $x\in G(\bFq)$, set $\gqcs{L}_x \ceq \EE$.
- Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by
- $\mu_{x,y}(1) \ceq 1\otimes1$, for $x,y\in G(\bFq)$;
- clearly, $\mu$ satisfies \ref{qc.2}.
- Define $\phi_x : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_x(1) \ceq \tau(\Frob{})(x)$,
- for each $x\in G(\bFq)$.
- Then $\phi$ satisfies \ref{qc.3} because $\tau \in Z^1(\Weil{},G(\bFq)^*)$.
- Setting $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$, we have that $[\tau]$ is the image of $\qcs{L}$
- under \eqref{pich1}, and thus \eqref{pich1} defines an isomorphism of groups.
-\end{proof}
-
-\begin{proposition} \label{prop:etale-iso}
- If $G$ is a commutative, \'etale group scheme over $\Fq$ and $G(\bFq)$ is finitely
- generated then
- \[
-  \TrFrob{G} : \QCiso{G} \to G(\Fq)^*
- \]
- is an isomorphism of groups.
-\end{proposition}
-\begin{proof}
-There is a natural isomorphism $\Hh^1(\Weil{}, G(\bFq)^*) \to (G(\bFq)^*)_{\Frob{}}$
-defined by $[z] \mapsto z(\Frob{})$.  The proposition now follows directly
-from Proposition~\ref{prop:etale} and Lemma~\ref{lem:dual-inv}.
-\end{proof}
-
-\section{Exactness of the component group sequence} \label{sec:restriction}
+\begin{proof}
+
+\end{proof}
+
+\section{Right-Exactness of the component group sequence} \label{sec:restriction}
 
@@
 \begin{tikzcd}
-0 \rar & \QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
+%0 \rar & 
+\QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
 \end{tikzcd}
@@
 in Sections~\ref{sec:connected} and \ref{sec:etale}.
-In this section we show that \eqref{eq:pi2} is right exact.
+In this section we show that \eqref{eq:pi2} is exact.
 
@@
   \begin{tikzcd}
-  0 \rar & \QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
-  \end{tikzcd}
- \]
- is exact at $\QCiso{G}$.
+%  0 \rar & 
+ \QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
+  \end{tikzcd}
+ \]
+ is exact.
 \end{proposition}
@@
 \begin{proof}
+We already know the sequence is exact at $\QCiso{G^0}$. 
+Here we show exactness at $\QCiso{G}$.
 First note that $\iota_0^* \circ \pi_0^*$ is trivial by Proposition~\ref{prop:pullback}.

### 2014-04-03 dictionary.tex
Added a few todos for next time. Goodnight!

@@
 \email{roed.math@gmail.com}
-\address{Pacific Institute for the Mathematical Sciences at the University of Calgary}
+\address{Pacific Institute for the Mathematical Sciences, University of Calgary}
 \subjclass[2010]{14F05 (primary), 14L15 (secondary)}
@@
 .
-.\todo{Needs a new front end to really set the tone, and highten the contrast with the connected case, and point to applications.}
+.\todo{Needs a new front end to really set the tone, heighten the contrast to the connected case and point to applications.}
 
@@
 Second, consider the etale group scheme $\ZZ \times \ZZ$.
-\todo{Build an example of an invisible quasicharacter sheaf.}
+\todo{Build an example of an invisible quasicharacter sheaf here.}
 Finally, consider the etale group scheme $\ZZ \times \ZZ$ over $\Fq$ with Galois action determined by $\sigma(n,m) = (m,n)$ when the restriction of $\sigma$ to $\mathbb{F}_{q^2}$ is non-trivial.
@@
 \end{lemma}
+
+\todo{Proof missing.}
 
@@
 condition \eqref{nohom} is satisfied with $g =1$, the trivial cocycle in $Z^2(G(\bFq),\EEx)$.
-It is now clear that we have defined a \emph{visible} quasicharacter sheaf $\qcs{L}$ with $\trFrob{\qcs{L}} = \chi$.
+It is now clear that we have defined a \emph{visible} quasicharacter sheaf $\qcs{L}$ with $\trFrob{\qcs{L}} = \chi$.\todo{Can I improve this proof to show that the kernel of Trace of Frobenius is exactly $\Hh^0(\Weil{},\Hh^2(G(\bFq),\EEx))$?
+Perhaps .
+.
+.
+}
 \end{proof}
@@
 \begin{proof}
-
+\todo{Clifton, you are here.}
 \end{proof}

### 2014-04-03 dictionary.tex
Added the Hochschild-Serre spectral sequence

@@
 
-\begin{lemma}\label{prop:etale-2cocycle}
+\begin{lemma}\label{lem:etale-2cocycle}
     If $G$ is an \'etale commutative group scheme over $\Fq$
-    then the homomorphism
+    then the group homomorphism
     \[
@@
     \]
-    defined in Section~\ref{sec:invisible}, is surjective.
+    defined in Section~\ref{sec:invisible}, 
+    is surjective with a canonical section.
 \end{lemma}
@@
 In this way, the cocycle $g\in Z^0(\Weil{}, Z^2(G(\bFq),\EEx))$ defines a quasicharacter sheaf $\qcs{L}$.
-It is now clear that $\qcs{L}$ maps to $[g] \in \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx))$ under \eqref{2cocycle}.
+It is clear that $\qcs{L}$ maps to $[g] \in \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx))$ under \eqref{2cocycle}.\todo{Canonical section?}
 \end{proof}
@@
 
-\begin{lemma}\label{prop:etale-trace}
+\begin{lemma}\label{lem:etale-trace}
 If $G$ is an \'etale commutative group scheme over $\Fq$
@@
 \begin{proof}
+The Hochschild-Serre spectral sequence (for finitely generated abelian groups!) provides decomposition 
+\[
+\Hh^2(G(\bFq),\EEx)  \iso \Hh^1(\Weil{}, \Hh^1(G(\bFq)\rtimes \Weil{},\EEx)) \oplus \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx))
+\]
+and Lemmas~\ref{lem:etale-2cocycle} and \ref{lem:etale-trace} provide the maps from $\QCiso{G}$ pictured below:
+\[
+\begin{tikzcd}
+\ &&  \QCiso{G} \arrow[swap]{dl}{\TrFrob{G}} \arrow{dr}{ S_{G} } && \\
+0 \arrow{r}{} &  \Hh^1(\Weil{}, \Hh^1(G(\bFq),\EEx)) \arrow{r}{} & \Hh^2(G(\bFq)\rtimes\Weil{},\EEx) \arrow{r}{} & \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx)) \arrow{r}{} & 0.
+\end{tikzcd}
+\]
+
 \todo{Clifton, you are here.}

### 2014-04-04 dictionary.tex
Added section called Group Cohomology. Started to thank Takashi.

@@
 % AMS packages
-\usepackage{amsmath, amsthm, amssymb, todonotes}
+\usepackage{amsmath, amsthm, amssymb, todonotes}%showkeys}
 \usepackage[alphabetic]{amsrefs}
@@
 quasicharacter sheaves; their knowledge and help have been invaluable.
-%We also thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and for pointing us to a proof of Lemma~\ref{lemma:wrK}.
+We also thank Takashi Suzuki, who
 
@@
 \begin{equation}\label{2cocycle}
-\QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))
+S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))
 \end{equation}
@@
 \begin{equation}\label{nohom}
-f(x+y) = f(x) f(y) \frac{(\,^{\Frob{}}g)(x,y)}{g(x,y)}
+f(x+y) = f(x) f(y) \frac{g(\Frob{G}(x),\Frob{G}(y))}{g(x,y)}
 \end{equation}
@@
 with the class $g_\qcs{L}$ of $g$. This concludes the definition of
-\[
-\QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx)).
-\]
+$S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$.
 
@@
 We will return to the latter case in Section~\ref{sec:etale}.
-In the meantime, we end this section with a simple property of \eqref{2cocycle}.
+In the meantime, we end this section with a simple property of $S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$.
 
 \begin{lemma}
-The function defined in \eqref{2cocycle} is a homomorphism:
+The function \[S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))\] is a group homomorphism.
+\end{lemma}
+
+\begin{proof}
+We must show:
 \[
@@
 \]
-for every $\qcs{L}, \qcs{L'} \in \QC(G)$.
-\end{lemma}
-
-\todo{Proof missing.}
+for every $\qcs{L}, \qcs{L'} \in \QC(G)$.\todo{Under construction.}
+\end{proof}
 
@@
 
+\section{Group Cohomology}
+
 \begin{lemma}\label{lem:etale-2cocycle}
@@
     \[
-    \QCiso{G} \to \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx)),
-    \]
-    defined in Section~\ref{sec:invisible}, 
-    is surjective with a canonical section.
+    S_{G} : \QCiso{G} \to \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx)),
+    \]
+    defined in Section~\ref{sec:invisible}, is surjective.\todo{Kernel? Canonical section?}
 \end{lemma}
@@
 In this way, the cocycle $g\in Z^0(\Weil{}, Z^2(G(\bFq),\EEx))$ defines a quasicharacter sheaf $\qcs{L}$.
-It is clear that $\qcs{L}$ maps to $[g] \in \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx))$ under \eqref{2cocycle}.\todo{Canonical section?}
+It is clear that $\qcs{L}$ maps to $[g] \in \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx))$ under \eqref{2cocycle}.
 \end{proof}
@@
 \]
-is surjective, even when restricted to visible quasicharacter sheaves.
+is surjective, even when restricted to visible quasicharacter sheaves.\todo{Kernel? Canonical section?}
 \end{lemma}
@@
 condition \eqref{nohom} is satisfied with $g =1$, the trivial cocycle in $Z^2(G(\bFq),\EEx)$.
-It is now clear that we have defined a \emph{visible} quasicharacter sheaf $\qcs{L}$ with $\trFrob{\qcs{L}} = \chi$.\todo{Can I improve this proof to show that the kernel of Trace of Frobenius is exactly $\Hh^0(\Weil{},\Hh^2(G(\bFq),\EEx))$?
-Perhaps .
-.
-.
-}
+It is now clear that we have defined a \emph{visible} quasicharacter sheaf $\qcs{L}$ with $\trFrob{\qcs{L}} = \chi$.
 \end{proof}
@@
 \begin{proof}
-The Hochschild-Serre spectral sequence (for finitely generated abelian groups!) provides decomposition 
-\[
-\Hh^2(G(\bFq),\EEx)  \iso \Hh^1(\Weil{}, \Hh^1(G(\bFq)\rtimes \Weil{},\EEx)) \oplus \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx))
-\]
-and Lemmas~\ref{lem:etale-2cocycle} and \ref{lem:etale-trace} provide the maps from $\QCiso{G}$ pictured below:
-\[
-\begin{tikzcd}
-\ &&  \QCiso{G} \arrow[swap]{dl}{\TrFrob{G}} \arrow{dr}{ S_{G} } && \\
-0 \arrow{r}{} &  \Hh^1(\Weil{}, \Hh^1(G(\bFq),\EEx)) \arrow{r}{} & \Hh^2(G(\bFq)\rtimes\Weil{},\EEx) \arrow{r}{} & \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx)) \arrow{r}{} & 0.
-\end{tikzcd}
-\]
-
-\todo{Clifton, you are here.}
+By Lemma~\ref{lem:dual-inv}, $G(\Fq)^* \iso \Hh^1(\Weil{},\Hh^1(G(\bFq),\EEx))$. Composing this isomorphism with the Trace of Frobenius gives 
+\[
+T_{G}: \QCiso{G}\to  \Hh^1(\Weil{},\Hh^1(G(\bFq),\EEx)),
+\]
+which is surjective, Lemma~\ref{lem:etale-trace}. 
+Combining this with 
+\[
+S_{G} : \QCiso{G} \to \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx))
+\]
+gives
+\[
+\QCiso{G} \mathop{\longrightarrow}\limits^{T_{G}\oplus S_{G}} \Hh^1(\Weil{},\Hh^1(G(\bFq),\EEx))\oplus \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx)).
+\]
+The Hochschild-Serre spectral sequence (for finitely generated abelian groups!) provides  
+\[
+\Hh^2(G(\bFq)\rtimes \Weil{},\EEx)  \iso \Hh^1(\Weil{}, \Hh^1(G(\bFq),\EEx)) \oplus \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx)).
+\]
+Composing these last two maps defines
+\begin{equation}
+\QCiso{G}\to \Hh^2(G(\bFq)\rtimes \Weil{},\EEx).
+\end{equation}
+To see that this homomorphism is an isomorphism,\todo{Clifton, you are here.}
 \end{proof}

### 2014-04-04 geometrization.tex
o
Some changes to geometrization.

@@
 \usepackage[alphabetic]{amsrefs}
+\usepackage{todonotes}
 % Fonts
@@
 \newcommand{\Weil}[1]{\mathcal{W}_{#1}}
+\newcommand{\comp}{\Pi} % Component group
 
@@
 \citelist{
-\cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1} \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} 
+\cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1}
+\cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} 
 \cite{nicaise-sebag:motivicSerre}*{\S 2.2}
@@
   to the geometric identity component of $\GN{T}_n$.
-  In fact, $\pi_0(\GN{T}_n) = \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$ and
-  this group is finitely generated \cite{xarles:93a}*{2.18}.
-  \labitem{(GN.2)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
+  In fact, $\pi_0(\GN{T}_n)$ is independent of $n$, equal to $\comp \ceq \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$.
+  Moreover, $\Pi$ is finitely generated \cite{xarles:93a}*{2.18}.
+  \labitem{(GN.2)}{identity} $\GN{T}_n^\circ$ is affine of finite type over $\Fq$.
+  \labitem{(GN.3)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
 \end{enumerate}
+
+\begin{proposition}
+The projective limit of the system
+\[
+\cdots \xrightarrow{f_n} \GN{T}_{n+1} \xrightarrow{f_{n-1}} \cdots \xrightarrow{f_1} \GN{T}_1 
+\]
+exists in the category of group schemes over $\Fq$.
+\end{proposition}
+\begin{proof}
+Since the component group $\comp$ is independent of $n$, the projective system induces a sequence of affine schemes
+\begin{equation} \label{eq:Ti}
+\cdots \xrightarrow{f^i_n} \GN{T}^i_{n+1} \xrightarrow{f^i_{n-1}} \cdots \xrightarrow{f^i_1} \GN{T}^i_1
+\end{equation}
+for each $i \in \comp$.
+Since the category of affine schemes over $k$ is equivalent to the category of $k$-algebras, which has direct limits \todo{citation},
+the limit of \eqref{eq:Ti} exists in the category of affine group schemes over $k$ for each $i \in \comp$.  Write $\GN{T}^i$ for the limit,
+and define
+\[
+\GN{T} \ceq \coprod_{i \in \comp} \GN{T}^i
+\]
+as a $k$-scheme.  We claim that $\GN{T}$ is a projective limit of the original system, in the category of $k$-schemes.  Suppose that $Z$ is a $k$-scheme
+with a system of morphisms $z_n : Z \to \GN{T}_n$.  Let $\alpha : \pi_0(Z) \to \comp$ be the induced map on component groups, which is
+independent of $n$.  \todo{the components of $Z$ are not necessarily affine; is the projective limit in the category of affine schemes still the limit in the category of schemes?}
+
+The multiplication maps $m_n : \GN{T}_n \times \GN{T}_n \to \GN{T}_n$ induce maps of affine schemes
+$m_n^{i,j} : \GN{T}_n^i \times \GN{T}_n^j \to \GN{T}_n^{i+j},$ inducing maps $m^{i,j} : \GN{T}^i \times \GN{T}_
+
+\end{proof}
 

### 2014-04-05 dictionary.tex
Added to introduction.

@@
 %%%%%%%%%%%%%%%%%% HEADING %%%%%%%%%%%%%%%%%%
-\title[The function--sheaf dictionary]{The function--sheaf dictionary for smooth commutative group schemes over finite fields}
+\title[Lost in Translation: The function--sheaf dictionary]{Lost in Translation: \\ The function--sheaf dictionary for smooth commutative group schemes over finite fields}
 \date{\today}
@@
 % AMS packages
-\usepackage{amsmath, amsthm, amssymb, todonotes}%showkeys}
+\usepackage{amsmath, amsthm, amssymb, todonotes, showkeys}
 \usepackage[alphabetic]{amsrefs}
@@
 
+\subsection*{Overview}
+Deligne's function--sheaf dictionary translates characters of connected, commutative algebraic groups $G$ over finite fields Fq into certain local systems on G, from which the character of $G(\Fq)$ can be recovered using the action of Frobenius on $G$.
+The local systems which appear in this dictionary are easily characterised and often referred to as \emph{character sheaves} on $G$.
+The result is a perfect dictionary between characters of $G(\Fq)$ and character sheaves on G, with which the formidable artillery of algebraic geometry can be brought to bear on the study of characters of $G(\Fq)$.
+Although this dictionary extends to the case when $G$ is not connected, and even to all smooth commutative group schemes over $\Fq$, the result is not perfect.
+In this generality, the correct class of sheaves on G are called \emph{quasicharacter sheaves}; when $G$ is connected and of finite type, quasicharacter sheaves on $G$ specialize to character sheaves on $G$.
+While every character of $G(\Fq)$ may be converted, canonically, into a quasicharacter sheaf on G from which the character of $G(\Fq)$ may be recovered using the trace of Frobenius on G, generally there exist non-trivial quasicharacter sheaves on G for which the trace of Frobenius is trivial; these are called \emph{invisible quasicharacter sheaves} on $G$.
+Invisible quasicharacter sheaves on G are precisely the quasicharacter sheaves on $G$ that are lost in translation under the function-sheaf dictionary.
+Assuming only that $G$ is a smooth commutative group scheme over $\Fq$ with finitely generated component group, this paper gives a simple cohomological description of invisible quasicharacter sheaves on $G$.
+The most interesting case is that of etale commutative group schemes over $\Fq$.
+
+Our interest in the function--sheaf dictionary for smooth commutative group schemes over $\Fq$, especially etale commutative group schemes, comes from an application to $p$-adic representation theory.
 Motivated by ...., in this paper we ...
@@
 
-Let us briefly review how the function--sheaf dictionary for connected commutative algebraic groups over finite fields \cite{deligne:SGA4.5}*{sommes trig.} translates characters into local systems.
+\subsection*{Main result}
+
+In order to give the main result of this paper with more precision, let us briefly review how the function--sheaf dictionary for connected commutative algebraic groups over finite fields \cite{deligne:SGA4.5}*{sommes trig.} translates characters into local systems.
 Let $\Fq$ be a finite field and let $G$ be a connected commutative algebraic group over $\Fq$; fix an algebraic closure $\bFq$ of $\Fq$
@@
 
+\subsection*{Illustrative examples}
+
 Three examples will illustrate some of the issues that arise when extending the function--sheaf dictionary to smooth commutative group schemes.
@@
 
+\subsection*{Application}
+
 In \cite{cunningham-roe:13a} we consider quasicharacter sheaves on the
@@
 in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
+
+\subsection*{Structure of the paper}
 
@@
 
-The proof of Proposition~\ref{prop:functorialG} will be given at the end of the next section.
+The proof of Proposition~\ref{prop:functorialG} will be given at the end of Section~\ref{sec:pullback}.
+
+\section{Invisible quasicharacter sheaves}\label{sec:invisible}
+
+We will see that the Trace of Frobenius may not provide complete
+information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not connected.
+Our main tool for understanding this phenomenon is the function
+\begin{equation}\label{2cocycle}
+S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))
+\end{equation}
+defined below.
+Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
+For each geometric point $x\in G(\bFq)$, choose a basis $\{ v_x \}$ for $\gqcs{L}_x$.
+This choice determines a function $g : G(\bFq)\times G(\bFq) \to \EEx$ defined by
+\[
+\mu_{x,y}(v_{x+y}) = g(x,y) v_x \otimes v_y.
+\]
+Chasing through the diagram in Condition~\ref{QC.2} we see that
+\[
+g(x+y,z) g(x,y) = g(x,y+z) g(y,z),
+\]
+for all $x,y,z\in G(\bFq)$, so $g \in Z^2(G(\bFq),\EEx)$.
+It is easy to see that the class of $g$ is independent of the choice made above;
+let $g_\mathcal{L} \in H^2(G(\bFq),\EEx)$ the class of $g\in Z^2(G(\bFq),\EEx)$.
+It is also easy to see that the class that $g_\mathcal{L} = g_\mathcal{L'}$ when $\qcs{L} \iso \qcs{L'}$. This defines
+\[
+\QCiso{G} \to H^2(G(\bFq),\EEx).
+\]
+We claim that $g_\qcs{L}$ is also fixed by the action of $\Weil{}$ on $H^2(G(\bFq),\EEx)$
+inherited from the action of $\Weil{}$ on $G(\bFq)$.
+To see this, we return to the choice $\{ v_x \in \gqcs{L}_x^\times \tq x\in G(\bFq) \}$
+and define $f : G(\bFq) \to \EEx$ by
+\[
+\phi_x(v_{\Frob{G}(x)}) = f(x) v_x.
+\]
+Chasing through the diagram in Condition~\ref{QC.3} we see that
+\begin{equation}\label{nohom}
+f(x+y) = f(x) f(y) \frac{g(\Frob{G}(x),\Frob{G}(y))}{g(x,y)}
+\end{equation}
+for all $x,y \in G(\bFq)$. Thus, the class $\,^{\Frob{}}g_\qcs{L}$ of $\,^{\Frob{}}g$ coincides
+with the class $g_\qcs{L}$ of $g$. This concludes the definition of
+$S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$.
+
+\begin{definition}\label{def:invisible}
+Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We say $\qcs{L}$ is \emph{visible} $g_\qcs{L} \in H^0(\Weil{},H^2(G(\bFq),\EEx))$ is trivial; otherwise, we say $\qcs{L}$ is \emph{invisible}.
+\end{definition}
+
+If $G$ is a connected and of finite type,
+then $H^2(G(\bFq),\EEx)$ is trivial \todo{Reference?} so all quasicharacter sheaves on connected commutative algebraic groups $G$ are visible;
+ by contrast, if $G$ is etale then $H^2(G(\bFq),\EEx)$ may be non-trivial and $G$ may admit invisible quasicharacters sheaves.
+We will return to the latter case in Section~\ref{sec:etale}.
+In the meantime, we end this section with a simple property of $S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$.
+
+\begin{lemma}
+The function \[S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))\] is a group homomorphism.
+\end{lemma}
+
+\begin{proof}
+We must show:
+\[
+g_{\qcs{L}\otimes \qcs{L'}} = g_{\qcs{L}} \, g_\qcs{L'}
+\]
+for every $\qcs{L}, \qcs{L'} \in \QC(G)$.\todo{Under construction.}
+\end{proof}
 
@@
 concluding the proof of Proposition~\ref{prop:functorialG}.
-\end{proof}
-
-\section{Invisible quasicharacter sheaves}\label{sec:invisible}
-
-We will see that the Trace of Frobenius may not provide complete
-information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not connected.
-Our main tool for understanding this phenomenon is the function
-\begin{equation}\label{2cocycle}
-S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))
-\end{equation}
-defined below.
-Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
-For each geometric point $x\in G(\bFq)$, choose a basis $\{ v_x \}$ for $\gqcs{L}_x$.
-This choice determines a function $g : G(\bFq)\times G(\bFq) \to \EEx$ defined by
-\[
-\mu_{x,y}(v_{x+y}) = g(x,y) v_x \otimes v_y.
-\]
-Chasing through the diagram in Condition~\ref{QC.2} we see that
-\[
-g(x+y,z) g(x,y) = g(x,y+z) g(y,z),
-\]
-for all $x,y,z\in G(\bFq)$, so $g \in Z^2(G(\bFq),\EEx)$.
-It is easy to see that the class of $g$ is independent of the choice made above;
-let $g_\mathcal{L} \in H^2(G(\bFq),\EEx)$ the class of $g\in Z^2(G(\bFq),\EEx)$.
-It is also easy to see that the class that $g_\mathcal{L} = g_\mathcal{L'}$ when $\qcs{L} \iso \qcs{L'}$. This defines
-\[
-\QCiso{G} \to H^2(G(\bFq),\EEx).
-\]
-We claim that $g_\qcs{L}$ is also fixed by the action of $\Weil{}$ on $H^2(G(\bFq),\EEx)$
-inherited from the action of $\Weil{}$ on $G(\bFq)$.
-To see this, we return to the choice $\{ v_x \in \gqcs{L}_x^\times \tq x\in G(\bFq) \}$
-and define $f : G(\bFq) \to \EEx$ by
-\[
-\phi_x(v_{\Frob{G}(x)}) = f(x) v_x.
-\]
-Chasing through the diagram in Condition~\ref{QC.3} we see that
-\begin{equation}\label{nohom}
-f(x+y) = f(x) f(y) \frac{g(\Frob{G}(x),\Frob{G}(y))}{g(x,y)}
-\end{equation}
-for all $x,y \in G(\bFq)$. Thus, the class $\,^{\Frob{}}g_\qcs{L}$ of $\,^{\Frob{}}g$ coincides
-with the class $g_\qcs{L}$ of $g$. This concludes the definition of
-$S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$.
-
-\begin{definition}\label{def:invisible}
-Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We say $\qcs{L}$ is \emph{visible} $g_\qcs{L} \in H^0(\Weil{},H^2(G(\bFq),\EEx))$ is trivial; otherwise, we say $\qcs{L}$ is \emph{invisible}.
-\end{definition}
-
-If $G$ is a connected and of finite type, 
-then $H^2(G(\bFq),\EEx)$ is trivial \todo{Reference?} so all quasicharacter sheaves on connected commutative algebraic groups $G$ are visible; 
- by contrast, if $G$ is etale then $H^2(G(\bFq),\EEx)$ may be non-trivial and $G$ may admit invisible quasicharacters sheaves.
-We will return to the latter case in Section~\ref{sec:etale}.
-In the meantime, we end this section with a simple property of $S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$.
-
-\begin{lemma}
-The function \[S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))\] is a group homomorphism.
-\end{lemma}
-
-\begin{proof}
-We must show:
-\[
-g_{\qcs{L}\otimes \qcs{L'}} = g_{\qcs{L}} \, g_\qcs{L'}
-\]
-for every $\qcs{L}, \qcs{L'} \in \QC(G)$.\todo{Under construction.}
 \end{proof}

### 2014-04-05 dictionary.tex
Made a home for Motivation and Application
Added the homomorphism R.
I’m starting to think about how to handle the general case in one go,
using etale cohomology rather than group cohomology.

@@
 \subsection*{Overview}
-Deligne's function--sheaf dictionary translates characters of connected, commutative algebraic groups $G$ over finite fields Fq into certain local systems on G, from which the character of $G(\Fq)$ can be recovered using the action of Frobenius on $G$.
+Deligne's function--sheaf dictionary translates characters of connected, commutative algebraic groups $G$ over finite fields $\Fq$ into certain local systems on G, from which the character of $G(\Fq)$ can be recovered using the action of Frobenius on $G$.
 The local systems which appear in this dictionary are easily characterised and often referred to as \emph{character sheaves} on $G$.
@@
 with a canonical section,
-and the kernel of the Trace of Frobenius is classified by the classes in $\Hh^2(\pi_0({\bar G}),\EEx)$ that are fixed by Frobenius.
-In contrast to the case of connected commutative algebraic groups, the Trace of Frobenius is not injective.
+and the kernel of the Trace of Frobenius is classified by $\Hh^1(\Weil{},\Hh^2(G(\bFq),\EEx))$.
+In particular, in contrast to the case of connected commutative algebraic groups, the Trace of Frobenius may not injective.
 We refer to quasicharacter sheaves in the kernel of Trace of Frobenius as \emph{invisible} quasicharacter sheaves.
@@
 
-Three examples will illustrate some of the issues that arise when extending the function--sheaf dictionary to smooth commutative group schemes.
+Three examples will illustrate some of the issues that arise when extending the function--sheaf dictionary to etale, commutative group schemes over $\Fq$.
 First, consider the etale group scheme $\ZZ$ over $\Fq$.
@@
 
-\section{Trace of Frobenius}\label{sec:Frob}
-
 The category $\QC(G)$ of quasicharacter sheaves on $G$ is a rigid monoidal category
@@
 of isomorphism classes in $\QC(G)$ the structure of a group.
+
+\section{Trace of Frobenius}\label{sec:Frob}
+
 We now begin developing the tools to relate $\QCiso{G}$ to $G(\Fq)^*$.
-
+%
 Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
@@
 \end{equation}
-defined below.
+defined here.
 Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
@@
 let $g_\mathcal{L} \in H^2(G(\bFq),\EEx)$ the class of $g\in Z^2(G(\bFq),\EEx)$.
-It is also easy to see that the class that $g_\mathcal{L} = g_\mathcal{L'}$ when $\qcs{L} \iso \qcs{L'}$. This defines
+It is also easy to see that $g_\mathcal{L} = g_\mathcal{L'}$ when $\qcs{L} \iso \qcs{L'}$. This defines
 \[
@@
 \begin{equation}\label{nohom}
-f(x+y) = f(x) f(y) \frac{g(\Frob{G}(x),\Frob{G}(y))}{g(x,y)}
+g(\Frob{G}(x),\Frob{G}(y)) f(x) f(y)  = g(x,y) f(x+y)
 \end{equation}
-for all $x,y \in G(\bFq)$. Thus, the class $\,^{\Frob{}}g_\qcs{L}$ of $\,^{\Frob{}}g$ coincides
-with the class $g_\qcs{L}$ of $g$. This concludes the definition of
+for all $x,y \in G(\bFq)$; thus, the class of $\,^{\Frob{}}g$ coincides with the class of $g$.
+This concludes the definition of
 $S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$.
+It is easy to see that the function $S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$ is a group homomorphism:
+\[
+g_{\qcs{L}\otimes \qcs{L'}} = g_{\qcs{L}} \, g_\qcs{L'}
+\]
+for every $\qcs{L}, \qcs{L'} \in \QC(G)$.\todo{I still need to write down the details, for ourselves.}
 
@@
 
-If $G$ is a connected and of finite type,
-then $H^2(G(\bFq),\EEx)$ is trivial \todo{Reference?} so all quasicharacter sheaves on connected commutative algebraic groups $G$ are visible;
- by contrast, if $G$ is etale then $H^2(G(\bFq),\EEx)$ may be non-trivial and $G$ may admit invisible quasicharacters sheaves.
-We will return to the latter case in Section~\ref{sec:etale}.
-In the meantime, we end this section with a simple property of $S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$.
-
-\begin{lemma}
-The function \[S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))\] is a group homomorphism.
-\end{lemma}
-
-\begin{proof}
-We must show:
-\[
-g_{\qcs{L}\otimes \qcs{L'}} = g_{\qcs{L}} \, g_\qcs{L'}
-\]
-for every $\qcs{L}, \qcs{L'} \in \QC(G)$.\todo{Under construction.}
-\end{proof}
+If $G$ is a connected and of finite type, then $\Hh^2(G(\bFq),\EEx)$ is trivial\todo{Reference?}
+so all quasicharacter sheaves on connected commutative algebraic groups $G$ are visible;
+ by contrast, if $G$ is etale then $\Hh^1(\Weil{},\Hh^2(G(\bFq),\EEx))$ may be non-trivial so $G$ may admit invisible quasicharacters sheaves.
+We will return to that case in Section~\ref{sec:etale}.
+
+While neither $T_{G}$ nor $S_{G}$ are injective, their direct sum is.
+
+\begin{proposition}
+Let
+\[
+R_{G} : \QCiso{G} \to  \Hh^0(\Weil{},\Hh^2(G(\bFq),\EEx) \oplus \Hh^1(\Weil{}, \Hh^1(G(\bFq),\EEx))
+\]
+be the map formed from  . . .
+Then $R_{G}$ is injective.
+\end{proposition}
 
@@
 
-\section{The function--sheaf dictionary for disconnected group schemes}
+\section{The function--sheaf dictionary for smooth, commutative group schemes}
 \label{sec:snake}

### 2014-04-08 dictionary.tex
Title

@@
 %%%%%%%%%%%%%%%%%% HEADING %%%%%%%%%%%%%%%%%%
+\title[The function--sheaf dictionary]{The function--sheaf dictionary for smooth commutative group schemes over finite fields}
+
 \title[Lost in Translation: The function--sheaf dictionary]{Lost in Translation: \\ The function--sheaf dictionary for smooth commutative group schemes over finite fields}
+
 \date{\today}
@@
 % AMS packages
+\usepackage{amsmath, amsthm, amssymb, todonotes}%showkeys}
 \usepackage{amsmath, amsthm, amssymb, todonotes, showkeys}
@@
 
+Let us briefly review how the function--sheaf dictionary for connected commutative algebraic groups over finite fields \cite{deligne:SGA4.5}*{sommes trig.} translates characters into local systems.
 \subsection*{Main result}
@@
 with a canonical section,
+and the kernel of the Trace of Frobenius is classified by the classes in $\Hh^2(\pi_0({\bar G}),\EEx)$ that are fixed by Frobenius.
+In contrast to the case of connected commutative algebraic groups, the Trace of Frobenius is not injective.
 and the kernel of the Trace of Frobenius is classified by $\Hh^1(\Weil{},\Hh^2(G(\bFq),\EEx))$.
@@
 
+Three examples will illustrate some of the issues that arise when extending the function--sheaf dictionary to smooth commutative group schemes.
 \subsection*{Illustrative examples}
@@
 We also thank Takashi Suzuki, who 
+We also thank Takashi Suzuki, who
 
@@
 
+\section{Trace of Frobenius}\label{sec:Frob}
+
 The category $\QC(G)$ of quasicharacter sheaves on $G$ is a rigid monoidal category
@@
 of isomorphism classes in $\QC(G)$ the structure of a group.
+We now begin developing the tools to relate $\QCiso{G}$ to $G(\Fq)^*$.
 
@@
 
+The proof of Proposition~\ref{prop:functorialG} will be given at the end of the next section.
 The proof of Proposition~\ref{prop:functorialG} will be given at the end of Section~\ref{sec:pullback}.
@@
 concluding the proof of Proposition~\ref{prop:functorialG}.
+\end{proof}
+
+\section{Invisible quasicharacter sheaves}\label{sec:invisible}
+
+We will see that the Trace of Frobenius may not provide complete
+information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not connected.
+Our main tool for understanding this phenomenon is the function
+\begin{equation}\label{2cocycle}
+S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))
+\end{equation}
+defined below.
+Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
+For each geometric point $x\in G(\bFq)$, choose a basis $\{ v_x \}$ for $\gqcs{L}_x$.
+This choice determines a function $g : G(\bFq)\times G(\bFq) \to \EEx$ defined by
+\[
+\mu_{x,y}(v_{x+y}) = g(x,y) v_x \otimes v_y.
+\]
+Chasing through the diagram in Condition~\ref{QC.2} we see that
+\[
+g(x+y,z) g(x,y) = g(x,y+z) g(y,z),
+\]
+for all $x,y,z\in G(\bFq)$, so $g \in Z^2(G(\bFq),\EEx)$.
+It is easy to see that the class of $g$ is independent of the choice made above;
+let $g_\mathcal{L} \in H^2(G(\bFq),\EEx)$ the class of $g\in Z^2(G(\bFq),\EEx)$.
+It is also easy to see that the class that $g_\mathcal{L} = g_\mathcal{L'}$ when $\qcs{L} \iso \qcs{L'}$. This defines
+\[
+\QCiso{G} \to H^2(G(\bFq),\EEx).
+\]
+We claim that $g_\qcs{L}$ is also fixed by the action of $\Weil{}$ on $H^2(G(\bFq),\EEx)$
+inherited from the action of $\Weil{}$ on $G(\bFq)$.
+To see this, we return to the choice $\{ v_x \in \gqcs{L}_x^\times \tq x\in G(\bFq) \}$
+and define $f : G(\bFq) \to \EEx$ by
+\[
+\phi_x(v_{\Frob{G}(x)}) = f(x) v_x.
+\]
+Chasing through the diagram in Condition~\ref{QC.3} we see that
+\begin{equation}\label{nohom}
+f(x+y) = f(x) f(y) \frac{g(\Frob{G}(x),\Frob{G}(y))}{g(x,y)}
+\end{equation}
+for all $x,y \in G(\bFq)$. Thus, the class $\,^{\Frob{}}g_\qcs{L}$ of $\,^{\Frob{}}g$ coincides
+with the class $g_\qcs{L}$ of $g$. This concludes the definition of
+$S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$.
+
+\begin{definition}\label{def:invisible}
+Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We say $\qcs{L}$ is \emph{visible} $g_\qcs{L} \in H^0(\Weil{},H^2(G(\bFq),\EEx))$ is trivial; otherwise, we say $\qcs{L}$ is \emph{invisible}.
+\end{definition}
+
+If $G$ is a connected and of finite type, 
+then $H^2(G(\bFq),\EEx)$ is trivial \todo{Reference?} so all quasicharacter sheaves on connected commutative algebraic groups $G$ are visible; 
+ by contrast, if $G$ is etale then $H^2(G(\bFq),\EEx)$ may be non-trivial and $G$ may admit invisible quasicharacters sheaves.
+We will return to the latter case in Section~\ref{sec:etale}.
+In the meantime, we end this section with a simple property of $S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$.
+
+\begin{lemma}
+The function \[S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))\] is a group homomorphism.
+\end{lemma}
+
+\begin{proof}
+We must show:
+\[
+g_{\qcs{L}\otimes \qcs{L'}} = g_{\qcs{L}} \, g_\qcs{L'}
+\]
+for every $\qcs{L}, \qcs{L'} \in \QC(G)$.\todo{Under construction.}
 \end{proof}
@@
 	If $G$ is an \'etale commutative group scheme over $\Fq$ 
+	If $G$ is an \'etale commutative group scheme over $\Fq$
 	and if $G(\bFq)$ is finitely generated,
@@
 By Lemma~\ref{lem:dual-inv}, $G(\Fq)^* \iso \Hh^1(\Weil{},\Hh^1(G(\bFq),\EEx))$. Composing this isomorphism with the Trace of Frobenius gives 
+By Lemma~\ref{lem:dual-inv}, $G(\Fq)^* \iso \Hh^1(\Weil{},\Hh^1(G(\bFq),\EEx))$. Composing this isomorphism with the Trace of Frobenius gives
 \[
@@
 Combining this with 
+which is surjective, Lemma~\ref{lem:etale-trace}.
+Combining this with
 \[
@@
 \]
+The Hochschild-Serre spectral sequence (for finitely generated abelian groups!) provides  
 The Hochschild-Serre spectral sequence (for finitely generated abelian groups!) provides
@@
 \begin{tikzcd}
+%0 \rar & 
 %0 \rar &
@@
 %  0 \rar & 
+%  0 \rar &
  \QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
@@
 \begin{proof}
+We already know the sequence is exact at $\QCiso{G^0}$. 
 We already know the sequence is exact at $\QCiso{G^0}$.
@@
 
+\section{The function--sheaf dictionary for disconnected group schemes}
 \section{The function--sheaf dictionary for smooth, commutative group schemes}

### 2014-04-08 dictionary.tex
having problems
back on track now
Thinking about the structure of dictionary.

--- 2014-04-05 dictionary.tex
@@
 %%%%%%%%%%%%%%%%%% HEADING %%%%%%%%%%%%%%%%%%
+
 \title[Lost in Translation: The function--sheaf dictionary]{Lost in Translation: \\ The function--sheaf dictionary for smooth commutative group schemes over finite fields}
+
 \date{\today}
@@
 
-Our interest in the function--sheaf dictionary for smooth commutative group schemes over $\Fq$, especially etale commutative group schemes, comes from an application to $p$-adic representation theory.
-Motivated by ...., in this paper we ...
-The component group of the Neron model of algebraic torus over local field ...
-The sheaf--function dictionary for etale group schemes is significantly different .
-.
-.\todo{Needs a new front end to really set the tone, heighten the contrast to the connected case and point to applications.}
-
 \subsection*{Main result}
@@
 
-\subsection*{Application}
-
+\subsection*{Motivation and Application}
+
+Our interest in the function--sheaf dictionary for smooth commutative group schemes over $\Fq$, especially etale commutative group schemes, comes from an application to $p$-adic representation theory.
 In \cite{cunningham-roe:13a} we consider quasicharacter sheaves on the
@@
 
-We also want to situate our teminology in a historical context.
+\subsection*{Comparison with other character sheaves}
+
+We also want to situate our terminology in a historical context.
 Some people refer to local systems satisfying \eqref{introbox} on a connected, commutative algebraic group as character sheaves;
@@
 in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves. 
+In particular, all quasicharacter sheaves on such groups are visible.
 
@@
 
-\section{Preliminary definitions}\label{sec:QCschemes}
+\section{Quasicharacter sheaves}
+
+\subsection{Definitions}\label{sec:QCschemes}
 
@@
 
-\section{Quasicharacter sheaves}\label{sec:category}
+%\subsection{Main definition}\label{sec:category}
 
@@
 
-\section{Trace of Frobenius}\label{sec:Frob}
+\subsection{Trace of Frobenius}\label{sec:Frob}
 
@@
 
-\section{Invisible quasicharacter sheaves}\label{sec:invisible}
+\subsection{Invisible quasicharacter sheaves}\label{sec:invisible}
 
@@
 
-\section{Pull-back and products}\label{sec:pullback}
+\subsection{Pull-back and products}\label{sec:pullback}
 
@@
 
-\section{Base change}\label{sec:basechange}
+\subsection{Base change}\label{sec:basechange}
 
@@
 
-\section{Bounded quasicharacter sheaves}\label{sec:bounded}
+\section{Bounded and Finite quasicharacter sheaves}%\label{sec:bounded}
+
+\subsection{Bounded quasicharacter sheaves}\label{sec:bounded}
 
@@
 
-\section{Finite quasicharacter sheaves}\label{sec:finite}
+\subsection{Finite quasicharacter sheaves}\label{sec:finite}
 
@@
 
+\subsection{Definition, revisited}
+
 \'Etale group schemes form a counterpoint to connected groups,
@@
 
-\section{Group Cohomology}
+\subsection{Group Cohomology}
 

### 2014-04-09 dictionary.tex
Made some subsections

@@
 quasicharacter sheaves; their knowledge and help have been invaluable.
-We also thank Takashi Suzuki, who
-
-We also gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
+We also thank Takashi Suzuki, who made many helpful observations and suggestions.
+%
+Finally, we gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
 and the National Science and Engineering Research Council,
@@
 
-\section{Quasicharacter sheaves}
+\section{The category of quasicharacter sheaves}
 
@@
 
-\section{Bounded and Finite quasicharacter sheaves}%\label{sec:bounded}
+\section{Two special subcategories of quasicharacter sheaves}%\label{sec:bounded}
 
@@
 
-\section{Connected commutative algebraic groups} \label{sec:connected}
+\section{The case of connected commutative algebraic groups} \label{sec:connected}
 
@@
 
-\section{Commutative \'etale group schemes} \label{sec:etale}
-
-\subsection{Definition, revisited}
+\section{The case of \'etale commutative group schemes} \label{sec:etale}
+
+\subsection{Quasicharacter sheaves, revisited}
 
@@
 
-\section{Right-Exactness of the component group sequence} \label{sec:restriction}
+\section{The main result}
+
+\subsection{The component group sequence} \label{sec:restriction}
 
@@
 
-\section{The function--sheaf dictionary for smooth, commutative group schemes}
+\subsection{The function--sheaf dictionary for smooth, commutative group schemes}
 \label{sec:snake}

### 2014-04-09 dictionary.tex
Commit before meeting with David.

@@
 % AMS packages
-\usepackage{amsmath, amsthm, amssymb, todonotes, showkeys}
+\usepackage{amsmath, amsthm, amssymb, todonotes}% showkeys}
 \usepackage[alphabetic]{amsrefs}
@@
 Assuming only that $G$ is a smooth commutative group scheme over $\Fq$ with finitely generated component group, this paper gives a simple cohomological description of invisible quasicharacter sheaves on $G$.
-The most interesting case is that of etale commutative group schemes over $\Fq$.
+%The most interesting case is that of etale commutative group schemes over $\Fq$.
 
@@
 
-In order to give the main result of this paper with more precision, let us briefly review how the function--sheaf dictionary for connected commutative algebraic groups over finite fields \cite{deligne:SGA4.5}*{sommes trig.} translates characters into local systems.
+In order to describe the main result of this paper with more precision, let us briefly review how the function--sheaf dictionary for connected commutative algebraic groups over finite fields \cite{deligne:SGA4.5}*{sommes trig.} translates characters into local systems.
 Let $\Fq$ be a finite field and let $G$ be a connected commutative algebraic group over $\Fq$; fix an algebraic closure $\bFq$ of $\Fq$
@@
 and also keep track of the isomorphisms \eqref{introbox} (mere existence of such an isomorphism is not enough), leading to the notion of {\it quasicharacter sheaves on $G$}.
-But the result  . . . .
-
-So, what is a quasicharacter sheaf?
+%So, what is a quasicharacter sheaf?
+
 A quasicharacter sheaf on $G$ is a triple $\qcs{L}\ceq
@@
 \gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms satisfying natural compatibilty conditions; here $\Frob{G}$ is the Frobenius automorphism of ${\bar G}$.
+
 The main result of this paper is the following statement (see Theorem~\ref{thm:snake}):
@@
 
-We close the introduction with a more detailed description of the structure of this paper.
+%We close the introduction with a more detailed description of the structure of this paper.
 After setting some notation in Section~\ref{sec:QCschemes}, in Section~\ref{sec:category} we define quasicharacter sheaves and give an interpretation of
@@
 Throughout this paper, $G$ is a smooth, commutative group scheme
-over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.  For the sake of brevity, we
-define a \emph{$\QC$-scheme} to be such a $G$ with the additional property that the
-geometric component group of $G$ is finitely generated.  This last condition is only
-needed in the proof of Lemma \ref{lemma:section}.  A morphism of $\QC$-schemes is a morphism
-of group schemes over $\Fq$.
+over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.  
+%For the sake of brevity, we define a \emph{$\QC$-scheme} to be such a $G$ with the additional property that the geometric component group of $G$ is finitely generated.
+This last condition is only needed in the proof of Lemma \ref{lemma:section}.
+A morphism of $\QC$-schemes is a morphism of group schemes over $\Fq$.
 
@@
 We will work with constructible $\ell$-adic sheaves \citelist{\cite{deligne:80a}*{\S 1.1} \cite{SGA5}*{Expos\'es V, VI}}
-on $\QC$-schemes, employing the standard formalism.
+on schemes locally of finite type over $\Fq$, employing the standard formalism.
 We also make extensive use of the external tensor product of $\ell$-adic sheaves,
@@
 It is easy to see that the class of $g$ is independent of the choice made above;
-let $g_\mathcal{L} \in H^2(G(\bFq),\EEx)$ the class of $g\in Z^2(G(\bFq),\EEx)$.
-It is also easy to see that $g_\mathcal{L} = g_\mathcal{L'}$ when $\qcs{L} \iso \qcs{L'}$. This defines
-\[
-\QCiso{G} \to H^2(G(\bFq),\EEx).
-\]
-We claim that $g_\qcs{L}$ is also fixed by the action of $\Weil{}$ on $H^2(G(\bFq),\EEx)$
+let $\sigma_\mathcal{L}) \in H^2(G(\bFq),\EEx)$ the class of $g\in Z^2(G(\bFq),\EEx)$.
+It is also easy to see that $S_G(\mathcal{L}) = S_G(\mathcal{L'})$ when $\qcs{L} \iso \qcs{L'}$. This defines
+\[
+S_G: \QCiso{G} \to H^2(G(\bFq),\EEx).
+\]
+We claim that $S_G(\qcs{L})$ is also fixed by the action of $\Weil{}$ on $H^2(G(\bFq),\EEx)$
 inherited from the action of $\Weil{}$ on $G(\bFq)$.

### 2014-04-10 dictionary.tex
Disappearing invisible quasicharacter sheaves
Car commit

@@
   When $G$ is etale, however, the kernel is generally non-trivial,
-  leading to interesting notion of invisible quasicharacter sheaves.
+  leading to the interesting notion of invisible quasicharacter sheaves.
   We find a classification of invisible quasicharacter sheaves
@@
   in terms of the cohomology of $G(\mathbb{F}_q)$.
+  We also explain how to make invisible quasicharacter sheaves disappear,
+  should the notion prove too troubling.
    \end{abstract}
@@
 To do this we must pass from $\ell$-adic local systems on $G$ to Weil local systems on $G$
-and also keep track of the isomorphisms \eqref{introbox} (mere existence of such an isomorphism is not enough), leading to the notion of {\it quasicharacter sheaves on $G$}.
-%So, what is a quasicharacter sheaf?
-
+and also keep track of the isomorphisms \eqref{introbox}, leading to the notion of {\it quasicharacter sheaves on $G$}.
+
+So, what is a quasicharacter sheaf?
 A quasicharacter sheaf on $G$ is a triple $\qcs{L}\ceq
@@
 \end{equation}
-with a canonical section,
-and the kernel of the Trace of Frobenius is classified by $\Hh^1(\Weil{},\Hh^2(G(\bFq),\EEx))$.
-In particular, in contrast to the case of connected commutative algebraic groups, the Trace of Frobenius may not injective.
+with a canonical section.
 We refer to quasicharacter sheaves in the kernel of Trace of Frobenius as \emph{invisible} quasicharacter sheaves.
-The canonical section of the Trace of Frobenius allows one to convert any quasicharacter of $G(\Fq)$
-into a quasicharacter sheaf on $G$.
-In this way, quasicharacter sheaves geometrize characters of $G(\Fq)$.
+If $G$ is a connected commutative algebraic group then 
+all quasicharacter sheaves on $G$ are visible.
+In this paper we find a simple cohomological description 
+of invisible quasicharacter sheaves on any smooth commutative
+group scheme $G$ over $\Fq$.
+In any case, the canonical section of the Trace of Frobenius allows 
+one to convert any quasicharacter of $G(\Fq)$ 
+into a quasicharacter sheaf on $G$;
+consequently, quasicharacter sheaves geometrize and categorify 
+characters of $G(\Fq)$.
 
@@
 
-\subsection{Definitions}\label{sec:QCschemes}
+\subsection{Notations}\label{sec:QCschemes}
 
@@
 
-%\subsection{Main definition}\label{sec:category}
+\subsection{Main definition}\label{sec:category}
 
@@
 $S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$.
-It is easy to see that the function $S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$ is a group homomorphism:
-\[
-g_{\qcs{L}\otimes \qcs{L'}} = g_{\qcs{L}} \, g_\qcs{L'}
-\]
-for every $\qcs{L}, \qcs{L'} \in \QC(G)$.\todo{I still need to write down the details, for ourselves.}
+It is easy to see that the function $S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$ is a group homomorphism.\todo{I still need to write down the details, for ourselves.}
 
@@
 
-If $G$ is a connected and of finite type, then $\Hh^2(G(\bFq),\EEx)$ is trivial\todo{Reference?}
-so all quasicharacter sheaves on connected commutative algebraic groups $G$ are visible;
- by contrast, if $G$ is etale then $\Hh^1(\Weil{},\Hh^2(G(\bFq),\EEx))$ may be non-trivial so $G$ may admit invisible quasicharacters sheaves.
+%If $G$ is a connected and of finite type, then $\Hh^2(G(\bFq),\EEx)$ is trivial\todo{Reference?} so all quasicharacter sheaves on connected commutative algebraic groups $G$ are visible; by contrast, if $G$ is etale then $\Hh^1(\Weil{},\Hh^2(G(\bFq),\EEx))$ may be non-trivial so $G$ may admit invisible quasicharacters sheaves.
 We will return to that case in Section~\ref{sec:etale}.
@@
 
+\subsection{How to make invisible quasicharacter sheaves disappear}
+
+Two approaches: subcategory and quotient category\todo{Under construction}
+
 \bibliographystyle{amsalpha}

### 2014-04-10 dictionary.tex
Moving group cohomology up  . . .

--- 2014-04-09 dictionary.tex
@@
 It is easy to see that the class of $g$ is independent of the choice made above;
-let $\sigma_\mathcal{L}) \in H^2(G(\bFq),\EEx)$ the class of $g\in Z^2(G(\bFq),\EEx)$.
-It is also easy to see that $S_G(\mathcal{L}) = S_G(\mathcal{L'})$ when $\qcs{L} \iso \qcs{L'}$. This defines
-\[
-S_G: \QCiso{G} \to H^2(G(\bFq),\EEx).
-\]
-We claim that $S_G(\qcs{L})$ is also fixed by the action of $\Weil{}$ on $H^2(G(\bFq),\EEx)$
+let $s_\mathcal{L} \in H^2(G(\bFq),\EEx)$ the class of $g\in Z^2(G(\bFq),\EEx)$.
+It is also easy to see that $s_\mathcal{L} = s_\mathcal{L'}$ when $\qcs{L} \iso \qcs{L'}$, and that $s_{\qcs{L}\otimes \qcs{L'}} = s_{\qcs{L}} \, s_\qcs{L'}$
+for every $\qcs{L}, \qcs{L'} \in \QC(G)$.
+We claim that $s_\qcs{L}$ is fixed by the action of $\Weil{}$ on $H^2(G(\bFq),\EEx)$
 inherited from the action of $\Weil{}$ on $G(\bFq)$.
@@
 This concludes the definition of
-$S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$.
-It is easy to see that the function $S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$ is a group homomorphism:
-\[
-g_{\qcs{L}\otimes \qcs{L'}} = g_{\qcs{L}} \, g_\qcs{L'}
-\]
-for every $\qcs{L}, \qcs{L'} \in \QC(G)$.\todo{I still need to write down the details, for ourselves.}
+\begin{align*}
+S_G: \QCiso{G} &\to \Hh^0(\Weil{},\Hh^2(G(\bFq),\EEx))\\
+\qcs{L} &\mapsto s_{\qcs{L}}.
+\end{align*}
 
 \begin{definition}\label{def:invisible}
-Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We say $\qcs{L}$ is \emph{visible} $g_\qcs{L} \in H^0(\Weil{},H^2(G(\bFq),\EEx))$ is trivial; otherwise, we say $\qcs{L}$ is \emph{invisible}.
+Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We say $\qcs{L}$ is \emph{visible} if $S_G(\qcs{L}) \in H^0(\Weil{},H^2(G(\bFq),\EEx))$ is trivial; otherwise, we say $\qcs{L}$ is \emph{invisible}.
 \end{definition}
 
-If $G$ is a connected and of finite type, then $\Hh^2(G(\bFq),\EEx)$ is trivial\todo{Reference?}
-so all quasicharacter sheaves on connected commutative algebraic groups $G$ are visible;
- by contrast, if $G$ is etale then $\Hh^1(\Weil{},\Hh^2(G(\bFq),\EEx))$ may be non-trivial so $G$ may admit invisible quasicharacters sheaves.
-We will return to that case in Section~\ref{sec:etale}.
+\subsection{Group cohomology}
 
@@
 
+%In order to relate $\QCiso{G}$ to $G(k)^*$, we need a simple result relating duals, invariants and coinvariants.
+
+\begin{lemma} \label{lem:dual-inv}
+Let $X$ be an abelian group equipped with an action of $\Weil{}$.
+ Then
+\begin{align*}
+ (X^*)_{\Frob{}} &\to (X^{\Frob{}})^* \\
+ [f] &\mapsto f|_{X^{\Frob{}}}
+\end{align*}
+is an isomorphism.
+\end{lemma}
+
+\begin{proof}
+We can describe $X^{\Frob{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
+let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
+\[
+ 0 \to X^{\Frob{}} \to X \to Y \to 0
+\]
+yields
+\[
+ 0 \to Y^* \to X^* \to (X^{\Frob{}})^* \to \Ext^1_\ZZ(Y, \EEx).
+\]
+Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Frob{}})^*$.
+\end{proof}
+
 \begin{proposition}
-Let
-\[
-R_{G} : \QCiso{G} \to  \Hh^0(\Weil{},\Hh^2(G(\bFq),\EEx) \oplus \Hh^1(\Weil{}, \Hh^1(G(\bFq),\EEx))
-\]
+The group homomorphism
+\begin{align*}
+R_{G} : \QCiso{G} &\to  \Hh^0(\Weil{},\Hh^2(G(\bFq),\EEx) \oplus \Hh^1(\Weil{}, \Hh^1(G(\bFq),\EEx))\\
+\qcs{L} &\mapsto (s_{\qcs{L}}, 
+\end{align*}
 be the map formed from  . . .
@@
 
-%In order to relate $\QCiso{G}$ to $G(k)^*$, we need a simple result relating duals, invariants and coinvariants.
-
-\begin{lemma} \label{lem:dual-inv}
-Let $X$ be an abelian group equipped with an action of $\Weil{}$.
- Then
-\begin{align*}
- (X^*)_{\Frob{}} &\to (X^{\Frob{}})^* \\
- [f] &\mapsto f|_{X^{\Frob{}}}
-\end{align*}
-is an isomorphism.
-\end{lemma}
-
-\begin{proof}
-We can describe $X^{\Frob{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
-let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
-\[
- 0 \to X^{\Frob{}} \to X \to Y \to 0
-\]
-yields
-\[
- 0 \to Y^* \to X^* \to (X^{\Frob{}})^* \to \Ext^1_\ZZ(Y, \EEx).
-\]
-Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Frob{}})^*$.
-\end{proof}
-
 \begin{lemma}\label{lem:etale-trace}

### 2014-04-21 dictionary.tex
commit before pulling from sage cloud

--- 2014-04-10 dictionary.tex
@@
 This concludes the definition of
-$S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$.
-It is easy to see that the function $S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))$ is a group homomorphism.\todo{I still need to write down the details, for ourselves.}
+\begin{align*}
+S_G: \QCiso{G} &\to \Hh^0(\Weil{},\Hh^2(G(\bFq),\EEx))\\
+\qcs{L} &\mapsto s_{\qcs{L}}.
+\end{align*}
 
 \begin{definition}\label{def:invisible}
-Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We say $\qcs{L}$ is \emph{visible} $g_\qcs{L} \in H^0(\Weil{},H^2(G(\bFq),\EEx))$ is trivial; otherwise, we say $\qcs{L}$ is \emph{invisible}.
+Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We say $\qcs{L}$ is \emph{visible} if $S_G(\qcs{L}) \in H^0(\Weil{},H^2(G(\bFq),\EEx))$ is trivial; otherwise, we say $\qcs{L}$ is \emph{invisible}.
 \end{definition}
 
+\subsection{Group cohomology}
 %If $G$ is a connected and of finite type, then $\Hh^2(G(\bFq),\EEx)$ is trivial\todo{Reference?} so all quasicharacter sheaves on connected commutative algebraic groups $G$ are visible; by contrast, if $G$ is etale then $\Hh^1(\Weil{},\Hh^2(G(\bFq),\EEx))$ may be non-trivial so $G$ may admit invisible quasicharacters sheaves.

### 2014-04-21 dictionary.tex
bringing up to date changes made on sage cloud

@@
 % AMS packages
-\usepackage{amsmath, amsthm, amssymb, todonotes}% showkeys}
+\usepackage{amsmath, amsthm, amssymb, todonotes, showkeys}
 \usepackage[alphabetic]{amsrefs}
@@
 Invisible quasicharacter sheaves on G are precisely the quasicharacter sheaves on $G$ that are lost in translation under the function-sheaf dictionary.
-Assuming only that $G$ is a smooth commutative group scheme over $\Fq$ with finitely generated component group, this paper gives a simple cohomological description of invisible quasicharacter sheaves on $G$.
-%The most interesting case is that of etale commutative group schemes over $\Fq$.
+This paper gives a cohomological description of invisible quasicharacter sheaves on $G$
+and a trick to make invisible quasicharacter sheaves disappear,
+should the notion prove too troubling.
 
@@
 Using little more than the Lang map for $G$, $\chi$ determines an $\ell$-adic local system $\qcs{L}$ on $G$ from which the character $\chi$ can be recovered using the Frobenius automorphism of $\bG$.
-While this recovery process applies to all $\ell$-adic local systems $\qcs{L}$ on $G$, those that produce characters of $G(\Fq)$ are distinguished by a simple property: there exists an isomorphism
+While this recovery process applies to all $\ell$-adic local systems $\qcs{L}$ on $G$, those that produce characters of $G(\Fq)$ are distinguished by a simple property: there \emph{exists} an isomorphism
 \begin{equation}\label{introbox}
@@
 Three examples will illustrate some of the issues that arise when extending the function--sheaf dictionary to etale, commutative group schemes over $\Fq$.
-First, consider the etale group scheme $\ZZ$ over $\Fq$.
-While the $\ell$-adic character $\ZZ \to \EEx$ defined by
-$1 \mapsto -1$, has finite order, the character defined by
-$1 \mapsto 1+\ell$ does not, although its image is bounded;
-on the other hand, the character $\ZZ \to \EEx$ defined by
-$1 \mapsto \ell$ has unbounded image.
 As we show in the paper, $\ell$-adic local systems on $G$ can only be used to geometrize characters of finite order; quasicharacter sheaves, however, provide the geometrization of all characters of $G(\Fq)$.
-Second, consider the etale group scheme $\ZZ \times \ZZ$.
-\todo{Build an example of an invisible quasicharacter sheaf here.}
-Finally, consider the etale group scheme $\ZZ \times \ZZ$ over $\Fq$ with Galois action determined by $\sigma(n,m) = (m,n)$ when the restriction of $\sigma$ to $\mathbb{F}_{q^2}$ is non-trivial.
-Although there are infinitly-many geometric points on this group, it has exactly one $\Fq$-rational point.
-In this case, the group carries only one isomorphism class of quasicharacter sheaves -- in particular, it has no invisible quasicharacter sheaves -- so the dictionary is perfect, albeit trivial, in this case.
+In particular, we will see how to uniquely geometrize the character $\ZZ \to \EEx$ defined by
+$1 \mapsto \ell$, which has unbounded image,
+using quasicharacter sheaves on the etale group scheme $\ZZ$ with trivial Galois action.
+All quasicharacter sheaves on this group are visible.
+Likewise, the dictionary is perfect for the
+etale group scheme $\ZZ$ with Galois action determined by $\Frob{}(n) = -n$.
+By contract, the etale group scheme $\ZZ \times \ZZ$ with trivial Galois action
+ does admit invisible quasicharacter sheaves;
+ in particular, there are non-trivial quasicharacter sheaves on this group
+with trivial trace of Frobenius.\footnote{Move this example: Define $g: \ZZ\times \ZZ \to \EEx$ by $g((n_1,m_1), (n_2, m_2)) = \ell^{m_1-m_2 + n_1-n_2}$.
+Then use the tehniques of Section~\ref{sec:etale} to build a non-trivial character sheaf from the pair $(f=1,g)$ with trivial trace of Frobenius.}
 
@@
 We also want to situate our terminology in a historical context.
-Some people refer to local systems satisfying \eqref{introbox} on a connected, commutative algebraic group as character sheaves;
+It is not uncommon to refer to local systems satisfying \eqref{introbox} on a connected, commutative algebraic group as character sheaves;
 see for example, \cite{kamgarpour:09a}.
@@
 in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
-In particular, all quasicharacter sheaves on such groups are visible.
+We note that there are no invisble quasicharacter sheaves on such groups.
 
@@
 quasicharacter sheaves; their knowledge and help have been invaluable.
-We also thank Takashi Suzuki, who made many helpful observations and suggestions.
+We also thank Takashi Suzuki, who made some enormously helpful observations and suggestions.
 %
@@
 \end{align*}
-is called \emph{Trace of Frobenius}.
+is called \emph{Trace of Frobenius}.\todo{Does this really warrant a declared definition?
+Instead, we can refer to this very short section, when needed.}
 \end{definition}
@@
 information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not connected.
-Our main tool for understanding this phenomenon is the function
+Our main tool for understanding this phenomenon is the group homomorphism
 \begin{equation}\label{2cocycle}
@@
 \]
+Observe:
+\begin{equation}\label{ftot}
+f\vert_{G(\Fq)} = t_\qcs{L},
+\end{equation}
+which is independent of the choice of $\{ v_x \in \gfqcs{L}_x \tq x\in G(\bFq)\}$.
 Chasing through the diagram in Condition~\ref{QC.3} we see that
@@
 \begin{definition}\label{def:invisible}
-Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We say $\qcs{L}$ is \emph{visible} if $S_G(\qcs{L}) \in H^0(\Weil{},H^2(G(\bFq),\EEx))$ is trivial; otherwise, we say $\qcs{L}$ is \emph{invisible}.
+Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We say $\qcs{L}$ is \emph{visible} if $s_\qcs{L} \in H^0(\Weil{},H^2(G(\bFq),\EEx))$ is trivial; otherwise, we say $\qcs{L}$ is \emph{invisible}.
 \end{definition}
 
-\subsection{Group cohomology}
-%If $G$ is a connected and of finite type, then $\Hh^2(G(\bFq),\EEx)$ is trivial\todo{Reference?} so all quasicharacter sheaves on connected commutative algebraic groups $G$ are visible; by contrast, if $G$ is etale then $\Hh^1(\Weil{},\Hh^2(G(\bFq),\EEx))$ may be non-trivial so $G$ may admit invisible quasicharacters sheaves.
-We will return to that case in Section~\ref{sec:etale}.
-
-While neither $T_{G}$ nor $S_{G}$ are injective, their direct sum is.
-
-%In order to relate $\QCiso{G}$ to $G(k)^*$, we need a simple result relating duals, invariants and coinvariants.
-
-\begin{lemma} \label{lem:dual-inv}
-Let $X$ be an abelian group equipped with an action of $\Weil{}$.
- Then
-\begin{align*}
- (X^*)_{\Frob{}} &\to (X^{\Frob{}})^* \\
- [f] &\mapsto f|_{X^{\Frob{}}}
-\end{align*}
-is an isomorphism.
-\end{lemma}
-
-\begin{proof}
-We can describe $X^{\Frob{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
-let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
-\[
- 0 \to X^{\Frob{}} \to X \to Y \to 0
-\]
-yields
-\[
- 0 \to Y^* \to X^* \to (X^{\Frob{}})^* \to \Ext^1_\ZZ(Y, \EEx).
-\]
-Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Frob{}})^*$.
-\end{proof}
-
-\begin{proposition}
-The group homomorphism
-\begin{align*}
-R_{G} : \QCiso{G} &\to  \Hh^0(\Weil{},\Hh^2(G(\bFq),\EEx) \oplus \Hh^1(\Weil{}, \Hh^1(G(\bFq),\EEx))\\
-\qcs{L} &\mapsto (s_{\qcs{L}}, 
-\end{align*}
-be the map formed from  . . .
-Then $R_{G}$ is injective.
-\end{proposition}
+This terminology will be justified later when\todo{Point somewhere.} we show that a non-trivial quasicharacter sheaf $\qcs{L}$ on $G$ is invisible if and only if $\trFrob{\qcs{L}}$ is trivial.
 
@@
 
+\begin{proposition} \label{prop:etale-iso}
+	If $G$ is an \'etale commutative group scheme over $\Fq$
+  	then
+  	\[
+  	\QCiso{G} \iso \Hh^2(G(\bFq)\rtimes \Weil{}, \EEx),
+  	\]
+  	functorially,
+  	in the sense of Proposition~\ref{prop:functorialG}.
+\end{proposition}
+
+The proof of Proposition~\ref{prop:etale-iso} will require a few lemmas,
+which we assemble now.\todo{This section is undergoing massive reconstruction. Don't read.}
+%
+%We begin with a simple result relating duals, invariants and coinvariants.
+
+\begin{lemma} \label{lem:dual-inv}
+Let $X$ be an abelian group equipped with an action of $\Weil{}$.
+ Then
+\begin{align*}
+ (X^*)_{\Frob{}} &\to (X^{\Frob{}})^* \\
+ [f] &\mapsto f|_{X^{\Frob{}}}
+\end{align*}
+is an isomorphism.
+\end{lemma}
+
+\begin{proof}
+We can describe $X^{\Frob{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
+let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
+\[
+ 0 \to X^{\Frob{}} \to X \to Y \to 0
+\]
+yields
+\[
+ 0 \to Y^* \to X^* \to (X^{\Frob{}})^* \to \Ext^1_\ZZ(Y, \EEx).
+\]
+Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Frob{}})^*$.
+\end{proof}
+
+%Now we see that the Trace of Frobenius is surjective.
+
+\begin{lemma}\label{lem:etale-trace}
+If $G$ is an \'etale commutative group scheme over $\Fq$
+then Trace of Frobenius
+\[
+\TrFrob{G} : \QCiso{G} \to G(\Fq)^*
+\]
+is a surjective group homomorphism.
+\end{lemma}
+
+\begin{proof}
+Pick $\chi \in G(\Fq)^*$.
+By Lemma~\ref{lem:dual-inv}, there is some $f\in G(\bFq)^*$ such that $f\vert_{G(\Fq)^*} = \chi$.
+Set $\gqcs{L}_x = \EE$ for every $x\in G(\bFq)$.
+Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$.
+Define $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = f(x)$.
+Since $f : G(\bFq) \to \EEx$ is a group homomorphism,
+condition \eqref{nohom} is satisfied with $g =1$, the trivial cocycle in $Z^2(G(\bFq),\EEx)$.
+It is now clear that we have defined a \emph{visible} quasicharacter sheaf $\qcs{L}$ with $\trFrob{\qcs{L}} = \chi$.
+\end{proof}
+
+%Likewise, $S_G$ is surjective.
+
 \begin{lemma}\label{lem:etale-2cocycle}
@@
     \]
-    defined in Section~\ref{sec:invisible}, is surjective.\todo{Kernel? Canonical section?}
+    defined in Section~\ref{sec:invisible}, is surjective.
 \end{lemma}
@@
 \begin{equation}\label{gf}
-g(\Frob{}(x),\Frob{}(y)) = g(x,y) \frac{f(x+y)}{f(x) f(y)}
+\frac{g(\Frob{}(x),\Frob{}(y))}{g(x,y)} = \frac{f(x+y)}{f(x) f(y)}
 \end{equation}
@@
 
-\begin{lemma}\label{lem:etale-trace}
-If $G$ is an \'etale commutative group scheme over $\Fq$
-then for every the $\chi \in G(\Fq)^*$ there is a visible quasicharacter sheaf $\qcs{L}$ on $G$ such that $\trFrob{\qcs{L}} = \chi$.
-In particular, Trace of Frobenius
-\[
-\TrFrob{G} : \QCiso{G} \to G(\Fq)^*,
-\]
-is surjective, even when restricted to visible quasicharacter sheaves.\todo{Kernel? Canonical section?}
+\begin{lemma}\label{lem:trivial}
+\[
+\ker T_{G} \cap \ker S_{G} = 0
+\]
 \end{lemma}
@@
 \begin{proof}
-Pick $\chi \in G(\Fq)^*$.
-By Lemma~\ref{lem:dual-inv}, there is some $f\in G(\bFq)^*$ such that $f\vert_{G(\Fq)^*} = \chi$.
-Set $\gqcs{L}_x = \EE$ for every $x\in G(\bFq)$.
-Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$.
-Define $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = f(x)$.
-Since $f : G(\bFq) \to \EEx$ is a group homomorphism,
-condition \eqref{nohom} is satisfied with $g =1$, the trivial cocycle in $Z^2(G(\bFq),\EEx)$.
-It is now clear that we have defined a \emph{visible} quasicharacter sheaf $\qcs{L}$ with $\trFrob{\qcs{L}} = \chi$.
-\end{proof}
-
-\begin{proposition} \label{prop:etale-iso}
-	If $G$ is an \'etale commutative group scheme over $\Fq$
-	and if $G(\bFq)$ is finitely generated,
-  	then
-  	\[
-  	\QCiso{G} \iso \Hh^2(G(\bFq)\rtimes \Weil{}, \EEx).
-  	\]
-  	Moreover, this isomorphism is functorial
-  	in the sense of Proposition~\ref{prop:functorialG}.
-\end{proposition}
-
-\begin{proof}
+Suppose $\trFrob{\qcs{L}} =1$ and $s_\qcs{L} =1$
+Let $f$ and $g$ be as above.
+Since the class of $g$ is trivial, $g(x,y) = \frac{h(x+y)}{h(x) h(y)}$ for some $h : G(\bFq) \to \EEx$;
+since the class of $f$ is trivial, $f(x) = \frac{k(\Frob{G}(x))}{k(x)}$ for some $k : G(\bFq) \to \EEx$.
+\todo{Actually, the lemma is false.}
+\end{proof}
+
+Now we can prove Proposition~\ref{prop:etale-iso}.
+
+\begin{proof}[Proof of Proposition~\ref{prop:etale-iso}]
 By Lemma~\ref{lem:dual-inv}, $G(\Fq)^* \iso \Hh^1(\Weil{},\Hh^1(G(\bFq),\EEx))$. Composing this isomorphism with the Trace of Frobenius gives
@@
 \[
-\QCiso{G} \mathop{\longrightarrow}\limits^{T_{G}\oplus S_{G}} \Hh^1(\Weil{},\Hh^1(G(\bFq),\EEx))\oplus \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx)).
-\]
-The Hochschild-Serre spectral sequence (for finitely generated abelian groups!) provides
+\QCiso{G} \mathop{\longrightarrow}\limits^{R_G} \Hh^1(\Weil{},\Hh^1(G(\bFq),\EEx))\oplus \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx)).
+\]
+The Hochschild-Serre spectral sequence provides
 \[
@@
 \end{equation}
-To see that this homomorphism is an isomorphism,\todo{Clifton, you are here.}
+To see that this homomorphism is an isomorphism, observe that $S_G$ and $T_G$ are surjective and $\ker S_G \cap \ker T_G = 0$.
 \end{proof}
@@
 in Sections~\ref{sec:connected} and \ref{sec:etale}.
-In this section we show that \eqref{eq:pi2} is exact.
+In this section we show that \eqref{eq:pi2} is exact.\todo{I wonder if $(F_1,F_2)$, see \ref{prop:functorialG}, form an adjoint pair.}
 
@@
   \]
-  is a functorial surjection with kernel $\Hh^0(\Weil{}, \Hh^2(\pi_0({\bar G}), \EE))$ and a canonical section.
+  is a functorial surjection with kernel $\Hh^0(\Weil{}, \Hh^2(\pi_0({\bar G}), \EE))$ and a canonical section.\todo{I wonder if $(F_1,F_2)$, see \ref{prop:functorialG}, form an adjoint pair.
+That seems to be what this theorem is saying.}
 \end{theorem}
@@
 \end{document}
-%sagemathcloud={"zoom_width":120}
+%sagemathcloud={"zoom_width":125}

### 2014-04-27 dictionary.tex
Fix gfqcs typo, change .gitignore for Sage cloud
Working on adding a section on spectral sequences

@@
 \usepackage{mathrsfs, yfonts}
+%Geometry
 \usepackage{geometry}
+% Enumitem
+%\usepackage{enumitem}
 % TikZ
@@
 \DeclareMathOperator{\Loc}{Loc}
+\DeclareMathOperator{\Tot}{Tot}
 \newcommand{\gal}[1]{{\operatorname{Gal}\hskip-1pt\left( {\bar #1}/#1 \right)}}
@@
 \end{equation}
-which is independent of the choice of $\{ v_x \in \gfqcs{L}_x \tq x\in G(\bFq)\}$.
+which is independent of the choice of $\{ v_x \in \gqcs{L}_x \tq x\in G(\bFq)\}$.
 Chasing through the diagram in Condition~\ref{QC.3} we see that
@@
 
+\section{The Hochschild-Serre Spectral Sequence}
+
+Consider the double complex $E^{\bullet, \bullet}$ defined by
+\[
+E^{i,j} = C^i(\Weil{}, C^j(G(\bFq), \EEx)).
+\]
+The machinery of spectral sequences gives us a sequence of pages $E_r^{i,j}$, converging to a page $E_{\infty}^{i,j}$.
+We summarize the key properties of this spectral sequence in the following proposition.
+
+\begin{proposition}
+\begin{enumerate}
+\item The second page is given by $E_2^{i,j} = \Hh^i(\Weil{}, \Hh^j(G(\bFq), \EEx))$,
+\item the cohomology $\Hh^\bullet(\Weil{} \ltimes G(\bFq), \EEx)$ is isomorphic to the cohomology of the total complex $\Tot(E^{\bullet, \bullet})$,
+\item there is a filtration $\Hh^n(\Weil{}, \ltimes G(\bFq), \EEx) = F_n \supset \cdots \supset F_0 \supset F_{-1} = 0$ where $F_i / F_{i-1} \cong E_{\infty}^{n-i, i}$.
+\end{enumerate}
+\end{proposition}
+
+Moreover, since $\Weil{} \cong \ZZ$ has cohomological dimension $1$, $E_2^{i,j} = 0$ for $i > 1$ and the sequence degenerates at the second page: $E_{\infty}^{i,j} = E_2^{i,j}$.
+We obtain the following corollary:
+
+\begin{corollary}
+There is a short exact sequence
+\[
+1 \to \Hh^1(\Weil{}, \Hh^1(G(\bFq), \EEx)) \to \Hh^2(\Weil{} \ltimes G(\bFq), \EEx) \to \Hh^0(\Weil{}, \Hh^2(G(\bFq), \EEx)) \to 1.
+\]
+\end{corollary}
+
+% Replace H^i with \Hh^i
+The map $S_{G}: \QCiso{G} \to \Hh^0(\Weil{},H^2(G(\bFq),\EEx))$ defined in Section \ref{sec:invisible} factors through a map $R_G : \QCiso{G} \to \Hh^2(G(\bFq) \rtimes \Weil{}, \EEx)$.
+
 \section{The case of \'etale commutative group schemes} \label{sec:etale}

### 2014-05-16 dictionary.tex
Adding material on spectral sequences

--- 2014-04-21 dictionary.tex
@@
 \subjclass[2010]{14F05 (primary), 14L15 (secondary)}
-\keywords{sheaf--function dictionary, geometrization, quasicharacter sheaves, commutative group schemes}
+\keywords{function--sheaf dictionary, geometrization, quasicharacters, quasicharacter sheaves, smooth commutative group schemes}
 
@@
 
+\newcommand{\lQC}{{\mathcal{Q\hskip-0.8pt C}^2}}
+\newcommand{\lQCiso}[1]{\lQC(#1)_{/\text{iso}}}
+\newcommand{\lTrFrob}[1]{\TrFrob{#1}^2}
+
 %%%%%%%%%%%% BEGIN DOCUMENT %%%%%%%%%%%%
@@
   If $G$ is connected, the kernel of this surjection is trivial.
-  When $G$ is etale, however, the kernel is generally non-trivial,
+  In $G$ is etale, however, the kernel is generally non-trivial,
   leading to the interesting notion of invisible quasicharacter sheaves.
-  We find a classification of invisible quasicharacter sheaves
-  on etale commutative group schemes over $\mathbb{F}_q$
-  in terms of the cohomology of $G(\mathbb{F}_q)$.
-  We also explain how to make invisible quasicharacter sheaves disappear,
+  In this paper we find a cohomological classification of invisible quasicharacter sheaves on all smooth commutative group schemes over $\mathbb{F}_q$,
+  and also explain how to make invisible quasicharacter sheaves disappear,
   should the notion prove too troubling.
@@
 
-Three examples will illustrate some of the issues that arise when extending the function--sheaf dictionary to etale, commutative group schemes over $\Fq$.
+Three examples will illustrate some of the issues that arise when extending the function--sheaf dictionary to smooth commutative group schemes over $\Fq$.
 As we show in the paper, $\ell$-adic local systems on $G$ can only be used to geometrize characters of finite order; quasicharacter sheaves, however, provide the geometrization of all characters of $G(\Fq)$.
@@
 By contract, the etale group scheme $\ZZ \times \ZZ$ with trivial Galois action
- does admit invisible quasicharacter sheaves;
- in particular, there are non-trivial quasicharacter sheaves on this group
-with trivial trace of Frobenius.\footnote{Move this example: Define $g: \ZZ\times \ZZ \to \EEx$ by $g((n_1,m_1), (n_2, m_2)) = \ell^{m_1-m_2 + n_1-n_2}$.
-Then use the tehniques of Section~\ref{sec:etale} to build a non-trivial character sheaf from the pair $(f=1,g)$ with trivial trace of Frobenius.}
+ does admit invisible quasicharacter sheaves -- there are non-trivial quasicharacter sheaves on this group
+with trivial trace of Frobenius.\todo{Under construction}
+(Move this example: Define $g: \ZZ\times \ZZ \to \EEx$ by $g((n_1,m_1), (n_2, m_2)) = \ell^{m_1-m_2 + n_1-n_2}$.
+Then use the tehniques of Section~\ref{sec:etale} to build a non-trivial character sheaf from the pair $(f=1,g)$ with trivial trace of Frobenius.)
 
@@
 determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$ and
-therefore an automorphism $\phi_{\bg}$ of $\gqcs{L}_{\bg}$. Set $\trFrob{(\gqcs{L},\phi)}(g) \ceq \trace(\phi_{\bg}, \gqcs{L}_{\bg})$,
+therefore an automorphism $\phi_{\bg}$ of $\gqcs{L}_{\bg}$. Set
+\begin{equation}\label{trWeil}
+%\begin{equation}\label{trWeil}
+\trFrob{(\gqcs{L},\phi)}(g) \ceq \trace(\phi_{\bg}, \gqcs{L}_{\bg})
+%\end{equation}
+\end{equation}
 and note that if $(\gqcs{L},\phi) \iso (\gqcs{L'},\phi')$ then $\trFrob{(\gqcs{L},\phi)} = \trFrob{(\gqcs{L'},\phi')}$.
@@
 then we will abbreviate $\trFrob{(\gqcs{L},\phi)}$ to $\trFrob{\qcs{L}}$.
-
-\begin{definition}\label{def:trFrob}
-The function
+%\begin{definition}\label{def:trFrob}
+We will refere to the function
 \begin{align*}
 \TrFrob{G}: \QCiso{G} &\to G(\Fq)^* \\
-\qcs{L} &\mapsto t_{\qcs{L}}
+\qcs{L} &\mapsto t_{\qcs{L}}: g\mapsto \trace(\phi_{\bg}, \gqcs{L}_{\bg})
 \end{align*}
-is called \emph{Trace of Frobenius}.\todo{Does this really warrant a declared definition?
-Instead, we can refer to this very short section, when needed.}
-\end{definition}
+as the \emph{Trace of Frobenius} for $G$.
+%\todo{Does this really warrant a declared definition?
+%Instead, we can refer to this very short section, when needed.}
+%\end{definition}
 
@@
 Trace of Frobenius $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a natural transformation
-between the two additive functors
+between the two contravariant additive functors
 \begin{align*}
@@
 The proof of Proposition~\ref{prop:functorialG} will be given at the end of Section~\ref{sec:pullback}.
-
-\subsection{Invisible quasicharacter sheaves}\label{sec:invisible}
-
-We will see that the Trace of Frobenius may not provide complete
-information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not connected.
-Our main tool for understanding this phenomenon is the group homomorphism
-\begin{equation}\label{2cocycle}
-S_{G}: \QCiso{G} \to H^0(\Weil{},H^2(G(\bFq),\EEx))
-\end{equation}
-defined here.
-Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
-For each geometric point $x\in G(\bFq)$, choose a basis $\{ v_x \}$ for $\gqcs{L}_x$.
-This choice determines a function $g : G(\bFq)\times G(\bFq) \to \EEx$ defined by
-\[
-\mu_{x,y}(v_{x+y}) = g(x,y) v_x \otimes v_y.
-\]
-Chasing through the diagram in Condition~\ref{QC.2} we see that
-\[
-g(x+y,z) g(x,y) = g(x,y+z) g(y,z),
-\]
-for all $x,y,z\in G(\bFq)$, so $g \in Z^2(G(\bFq),\EEx)$.
-It is easy to see that the class of $g$ is independent of the choice made above;
-let $s_\mathcal{L} \in H^2(G(\bFq),\EEx)$ the class of $g\in Z^2(G(\bFq),\EEx)$.
-It is also easy to see that $s_\mathcal{L} = s_\mathcal{L'}$ when $\qcs{L} \iso \qcs{L'}$, and that $s_{\qcs{L}\otimes \qcs{L'}} = s_{\qcs{L}} \, s_\qcs{L'}$
-for every $\qcs{L}, \qcs{L'} \in \QC(G)$.
-We claim that $s_\qcs{L}$ is fixed by the action of $\Weil{}$ on $H^2(G(\bFq),\EEx)$
-inherited from the action of $\Weil{}$ on $G(\bFq)$.
-To see this, we return to the choice $\{ v_x \in \gqcs{L}_x^\times \tq x\in G(\bFq) \}$
-and define $f : G(\bFq) \to \EEx$ by
-\[
-\phi_x(v_{\Frob{G}(x)}) = f(x) v_x.
-\]
-Observe:
-\begin{equation}\label{ftot}
-f\vert_{G(\Fq)} = t_\qcs{L},
-\end{equation}
-which is independent of the choice of $\{ v_x \in \gfqcs{L}_x \tq x\in G(\bFq)\}$.
-Chasing through the diagram in Condition~\ref{QC.3} we see that
-\begin{equation}\label{nohom}
-g(\Frob{G}(x),\Frob{G}(y)) f(x) f(y)  = g(x,y) f(x+y)
-\end{equation}
-for all $x,y \in G(\bFq)$; thus, the class of $\,^{\Frob{}}g$ coincides with the class of $g$.
-This concludes the definition of
-\begin{align*}
-S_G: \QCiso{G} &\to \Hh^0(\Weil{},\Hh^2(G(\bFq),\EEx))\\
-\qcs{L} &\mapsto s_{\qcs{L}}.
-\end{align*}
-
-\begin{definition}\label{def:invisible}
-Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We say $\qcs{L}$ is \emph{visible} if $s_\qcs{L} \in H^0(\Weil{},H^2(G(\bFq),\EEx))$ is trivial; otherwise, we say $\qcs{L}$ is \emph{invisible}.
-\end{definition}
-
-This terminology will be justified later when\todo{Point somewhere.} we show that a non-trivial quasicharacter sheaf $\qcs{L}$ on $G$ is invisible if and only if $\trFrob{\qcs{L}}$ is trivial.
 
@@
 if it is finite, surjective and \'etale and the action of $\Gal(\bFq/\Fq)$ on the \'etale group
-scheme $\ker f \ceq f^{-1}({\bar e)}$ is trivial.
+scheme $\ker f = f^{-1}({\bar e)}$ is trivial.
 Consider the category $C(G)$ whose objects consist of pairs $(f,\psi)$, where
@@
 \]
-In this form we could treat $g^*$ as a functor $C(J)\to C(G)$,
-were it not for the fact that pullback is defined only up to isomorphism.
-In the localized categories, this ambiguity disappears.
+%In this form we could treat $g^*$ as a functor $C(J)\to C(G)$,
+%were it not for the fact that pullback is defined only up to isomorphism.
+%In the localized categories, this ambiguity disappears.
 \end{proof}
@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:connected}
  If $G$ is a connected, commutative algebraic group over $\Fq$ then
@@
 \begin{proof}
- It suffices to observe that the group homomorphism
+ It suffices\todo{Why is $T_G$ injective?} to observe that the group homomorphism
  $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$
- is surjective because each character $\chi \in G(\Fq)^*$ determines a finite quasicharacter
+ is surjective: each character $\chi \in G(\Fq)^*$ determines a finite quasicharacter
  sheaf $(\Lang,\chi^{-1})$ such that Trace of Frobenius of the quasicharacter sheaf
@@
 the category of one-dimensional representations of $G(\Fq)^*$, thus
-providing an alternate proof that $\QCiso{G} \iso G(\Fq)^*$
-when $G$ is a connected algebraic group over $\Fq$.
+providing an alternate proof of Corollary~\ref{cor:connected}.
 
 In principle, something similar is possible in the more general
-context of this paper, where $G$ is a $\QC$-scheme, to which we now return.
+context of this paper, where $G$ is a smooth commutative group scheme over $\Fq$, to which we now return.
 In this generality, however, neither of the full subcategories $\QCf(G) \subset \QCb(G) \subset \QC(G)$ are equivalences;
@@
 Weil groups and also difficult to identify the relevant quotient of this group.
-Viewed in this light, Definition~\ref{def:QC} is comparatively simple.
+Viewed in this light, Definition~\ref{def:QC} seems comparatively simple.
+
+\section{Spectral sequences}\label{sec:spectral}
+
+%\subsection{Invisible quasicharacter sheaves}\label{sec:invisible}
+
+We will see that the Trace of Frobenius may not provide complete
+information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not a connected algebraic group.
+Our main tool for understanding this phenomenon
+is a group homomorphism from $\QCiso{G}$ to $\Hh^2(E^\bullet_G)$, defined in this section.
+In Section~\ref{sec:restriction} we will see that this homomorphism is an isomorphism for all smooth commutative group schemes over $\Fq$.
+
+[Things I need from this section:
+definition of $E^\bullet_G$ (Section~\ref{sec:E});
+the short exact sequence attached to $\Hh^2(E^\bullet_G)$ (Section~\ref{sec:SES});
+the exactness of all sequences in the diagram below (Section~\ref{sec:front});
+the map $S_G$ from $\QCiso{G}$ to $\Hh^2(E^\bullet_G)$ (Section~\ref{sec:S} done) commutes with everything in sight;
+that $\Hh^0(\Weil,\Hh^2({\bar G},\EEx))=0$ if $G$ is a connected algebraic group over $\Fq$ (Section~\ref{sec:connected-iso}).]
+
+[Can this section be written in such a way that the effect of removing the fact $\Hh^2(\Weil{}, - ) =0$ can be discerned?]
+
+\subsection{Cohomology}\label{sec:E}
+
+Define $\Hh^2(E^\bullet_G)$.
+
+Do we have
+ \[
+  \begin{tikzcd}[column sep=30]
+    ? \cdots \arrow{r}
+%    & \Hh^1(E^\bullet_{A}) \arrow{r}
+    & \Hh^2(E^\bullet_{C}) \arrow{r}
+    & \Hh^2(E^\bullet_{B}) \arrow{r}
+    & \Hh^2(E^\bullet_{A}) \arrow{r}
+%    & \Hh^3(E^\bullet_{C}) \arrow{r}
+    & \cdots ? \\
+  \end{tikzcd}
+ \]
+
+[Question: If $C$ is etale, then $\Hh^3(E^\bullet_{C}) =0?$]
+
+\[\Hh^*(E^\bullet_{G}) = \Hh^*({\bar G}\rtimes \Weil{},\EEx)\]
+
+\subsection{A short exact sequence}\label{sec:SES}
+
+ \[
+  \begin{tikzcd}
+    0 \arrow{r}
+    & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r}
+    & \Hh^2(E^\bullet_G) \arrow{r}
+    & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r}
+    & 0
+  \end{tikzcd}
+ \]
+
+\subsection{Splitting?}\label{sec:split}
+
+ \[
+  \begin{tikzcd}
+    0 \arrow{r}
+    & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r}
+    & \Hh^2(E^\bullet_G) \arrow{r}
+    \arrow[bend right,dotted]{l}
+    & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r}
+    \arrow[bend right,dotted]{l}
+    & 0
+  \end{tikzcd}
+ \]
+
+\subsection{Front}\label{sec:front}
+
+ \[
+  \begin{tikzcd}[row sep=20, column sep=15]
+    &  ?  & 0 \arrow{d} & 0\arrow{d} & \\
+0 \arrow{r} \arrow{d}   & \Hh^0(\Weil{},\Hh^2(C,\EEx)) \arrow{r} \arrow{d} & \Hh^0(\Weil{},\Hh^2(B,\EEx)) \arrow{r} \arrow{d}
+    & \Hh^0(\Weil{},\Hh^2(A,\EEx)) \arrow{d} \arrow{r} & ? \\
+    %\arrow{rr}  &   & 0 \\
+    ? \arrow{r}
+    & \Hh^2(E^\bullet_{C}) \arrow{r} \arrow{d}
+    & \Hh^2(E^\bullet_{B}) \arrow{r} \arrow{d}
+    & \Hh^2(E^\bullet_{A}) \arrow{r} \arrow{d}
+    & ? \\
+    %\arrow{rr}&& 0\\
+? \arrow{r}  & \Hh^1(\Weil{},\Hh^1(C,\EEx)) \arrow{d} \arrow{r}
+    & \Hh^1(\Weil{},\Hh^1(B,\EEx)) \arrow{d} \arrow{r}
+    & \Hh^1(\Weil{},\Hh^1(A,\EEx)) \arrow{d} \arrow{r}  &  ? \\
+    &  0 & 0 & 0 & \\
+  \end{tikzcd}
+ \]
+
+\subsection{Map to cohomology}\label{sec:S}
+
+In this section we define
+\[
+S_G : \QCiso{G} \to \Hh^2(E^\bullet_G).
+\]
+Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
+For each geometric point $x\in {\bar G}$, choose a basis $\{ v_x \}$ for $\gqcs{L}_x$.
+Through this choice, $\qcs{L}$ determines a function $a : {\bar G}\times {\bar G} \to \EEx$ defined by
+\[
+\mu_{x,y}(v_{x+y}) = a(x,y) v_x \otimes v_y.
+\]
+Condition~\ref{QC.2} gives
+\begin{equation}\label{2-cocyle}
+\forall x,y,z\in {\bar G},\qquad a(x+y,z) a(x,y) = a(x,y+z) a(y,z),
+\end{equation}
+so $a \in Z^2({\bar G},\EEx)$.
+Likewise, through the choice
+$\{ v_x\in \gqcs{L}_x^\times \tq x \in {\bar G}\}$, $\qcs{L}$
+determines a function $b : {\bar G} \to \EEx$
+defined by
+\[
+\phi_x(v_{\Frob{G}(x)}) = b(x) v_x.
+\]
+(Observe: $b\vert_{G(\Fq)} = t_\qcs{L}$,
+which is independent of the choice of $\{ v_x \in \gqcs{L}_x^\times \tq x\in {\bar G}\}$.)
+Condition~\ref{QC.3} gives
+\begin{equation}\label{nohom}
+\forall x,y \in {\bar G},\qquad \frac{a(\Frob{G}(x),\Frob{G}(y))}{a(x,y)} =  \frac{b(x+y)}{b(x) b(y)}.
+\end{equation}
+Let $\alpha \in C^0(\Weil{},C^2({\bar G},\EEx)$ be the cocycle corresponding to $a$ and let $\beta\in C^1(\Weil{},C^1({\bar G},\EEx)$ be the cocycle such that $\beta(\Frob{})$ is $b$ \emph{written additively}.
+Then
+\[
+d_{\uparrow}\alpha =0, \qquad
+d_{\rightarrow} \alpha = d_{\uparrow} \beta,\qquad
+d_{\rightarrow} \beta =0;
+\]
+in other words,
+\[\alpha\oplus \beta \in Z^2(E^\bullet_G).\]
+Although the cocycle $\alpha\oplus \beta$ is not well defined by $\qcs{L}$, its class in $Z^2(E^\bullet_G)$ is.
+To see this, let $\{ v'_x \in \gqcs{L}_x^\times \tq x \in {\bar G}\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$ be defined by $\qcs{L}$ and this choice, as above.
+Now let $\delta \in C^0(\Weil{},C^1({\bar G},\EEx))$ be the additive version of the function $d : {\bar G}\to \EEx$ defined by $v'_x = d(x) v_x$.
+Then, chasing through \ref{QC.2} and \ref{QC.3} we find
+\[
+\alpha'\oplus\beta' = \alpha\oplus\beta + d\delta,
+\]
+so the class $[\alpha\oplus\beta]$ of $\alpha\oplus\beta$ in $\Hh^2(E^\bullet_G)$ is independent of the choice made above.
+It is also easy to see that $[\alpha\oplus\beta] = [\alpha_0\oplus\beta_0]$ when $\qcs{L} \iso \qcs{L}_0$,
+which concludes the definition of the function
+\begin{align*}
+S_G : \QCiso{G} &\to \Hh^2(E^\bullet_G)\\
+[\qcs{L}] &\mapsto [\alpha\oplus \beta].
+\end{align*}
+It is also easy to see that $[\alpha_1\oplus\beta_1] + [\alpha_2\oplus\beta_2] = [\alpha_3\oplus\beta_3]$ when $\qcs{L}_3 = \qcs{L}_1\otimes \qcs{L}_2$, so $S_G$ is a group homomorphism.
+
+\begin{proposition}\label{prop:ST}
+ The following diagram commutes:
+\[
+\begin{tikzcd}
+ 0 \arrow{r}
+ & \ker \TrFrob{G} \arrow{r} \arrow{d}
+ & \QCiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}}
+ & G(\Fq)^* \arrow{d}{\iso} \arrow{r}
+ & \coker \TrFrob{G} \\
+ 0 \arrow{r}
+ & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r}
+ & \Hh^2(E^\bullet_G) \arrow{r}
+ & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx))  \arrow{r}
+ & 0.
+ \end{tikzcd}
+ \]
+\end{proposition}
+
+\begin{proof}
+We've discussed the fact that the square on the right commutes, using Lemma~\ref{lem:dual-inv}. I'll add that, later.
+So, if $\qcs{L} \in \QC(G)$ and $S_G(\qcs{L}) = [\alpha\oplus\beta]$  then $\trFrob{\qcs{L}} =1$ implies $[\beta]=0$.
+In Section~\ref{sec:SES} we identified\todo{ ...
+will identify ...} $\{ [\alpha\oplus\beta] \in \Hh^2(E^\bullet_G) \tq [\beta]=0 \}$ with $\Hh^0(\Weil{},\Hh^2({\bar G},\EEx))$.
+\end{proof}
+
+%We begin with a simple result relating duals, invariants and coinvariants.
+
+\begin{lemma} \label{lem:dual-inv}
+Let $X$ be an abelian group equipped with an action of $\Weil{}$.
+ Then
+\begin{align*}
+ (X^*)_{\Frob{}} &\to (X^{\Frob{}})^* \\
+ [f] &\mapsto f|_{X^{\Frob{}}}
+\end{align*}
+is an isomorphism.
+\end{lemma}
+
+\begin{proof}
+We can describe $X^{\Frob{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
+let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
+\[
+ 0 \to X^{\Frob{}} \to X \to Y \to 0
+\]
+yields
+\[
+ 0 \to Y^* \to X^* \to (X^{\Frob{}})^* \to \Ext^1_\ZZ(Y, \EEx).
+\]
+Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Frob{}})^*$.
+\end{proof}
+
+\subsection{Invisible quasicharacter sheaves}
+
+\begin{definition}\label{def:invisible}
+We say $\qcs{L}\in \QC(G)$ is \emph{visible} if the projection of $S_G(\qcs{L})$ to $\Hh^0(\Weil{}, \Hh^2({\bar G},\EEx))$ is trivial; otherwise, we say $\qcs{L}$ is \emph{invisible}.
+\end{definition}
+
+This terminology will be justified later when we show that a non-trivial quasicharacter sheaf $\qcs{L}$ on $G$ is invisible if and only if $\trFrob{\qcs{L}}$ is trivial.
+
+\subsection{Looking back to connected commutative algebraic groups}\label{sec:connected-iso}
+
+We end this Section~\ref{sec:spectral} by appling the tools developed here to the case when $G$ is a connected commutative algebraic group over $\Fq$.
+
+\begin{proposition} \label{prop:connected-iso}
+ If $G$ is a connected commutative algebraic group over $\Fq$
+  then the map $\QCiso{G}\to \Hh^2(E^\bullet_G)$ from Section~\ref{sec:spectral} induces an morphism of short exact sequences:
+\[
+\begin{tikzcd}
+ 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \QCiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}}  \arrow{r} & G(\Fq)^* \arrow{d}{\iso} \arrow{r} & 0\\
+  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r} & 0.
+ \end{tikzcd}
+\]
+\end{proposition}
+
+\begin{proof}
+The top sequence is exact by Corollary~\ref{cor:connected}.
+The bottom sequence is exact by Section~\ref{sec:SES}.
+The diagram commutes and the right-hand vertical arrow is an isomorphism, by Proposition~\ref{prop:ST}.\todo{ If $\Hh^0(\Weil{},\Hh^2({\bar G},\EEx))=0$ then we can improve this lemma.}
+\end{proof}
 
@@
 
-\subsection{Quasicharacter sheaves, revisited}
+%\subsection{Quasicharacter sheaves, revisited}
 
@@
 is an \'etale group scheme \cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
-However, the function--sheaf dictionary is substantially differentl in the two cases.
+However, the function--sheaf dictionary is substantially different in the two cases.
 To see why, we begin by specializing the definition of quasicharacter sheaves to the case
@@
 
-\subsection{Group Cohomology}
+We may now apply the tools developed in Section~\ref{sec:spectral} to the case at hand, where $G$ is an etale connected group scheme over $\Fq$.
 
@@
  If $G$ is an \'etale commutative group scheme over $\Fq$
-  	then
-  	\[
-  	\QCiso{G} \iso \Hh^2(G(\bFq)\rtimes \Weil{}, \EEx),
-  	\]
-  	functorially,
-  	in the sense of Proposition~\ref{prop:functorialG}.
+  then the map $\QCiso{G}\to \Hh^2(E^\bullet_G)$ from Section~\ref{sec:spectral} induces an isomorphism of short exact sequences:
+\[
+\begin{tikzcd}
+ 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \QCiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
+  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r} & 0.
+ \end{tikzcd}
+ \]
+In particular,
+$\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$
+is surjective with a canonical section.
 \end{proposition}
 
-The proof of Proposition~\ref{prop:etale-iso} will require a few lemmas,
-which we assemble now.\todo{This section is undergoing massive reconstruction. Don't read.}
-%
-%We begin with a simple result relating duals, invariants and coinvariants.
-
-\begin{lemma} \label{lem:dual-inv}
-Let $X$ be an abelian group equipped with an action of $\Weil{}$.
- Then
-\begin{align*}
- (X^*)_{\Frob{}} &\to (X^{\Frob{}})^* \\
- [f] &\mapsto f|_{X^{\Frob{}}}
-\end{align*}
-is an isomorphism.
-\end{lemma}
-
-\begin{proof}
-We can describe $X^{\Frob{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
-let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
-\[
- 0 \to X^{\Frob{}} \to X \to Y \to 0
-\]
-yields
-\[
- 0 \to Y^* \to X^* \to (X^{\Frob{}})^* \to \Ext^1_\ZZ(Y, \EEx).
-\]
-Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Frob{}})^*$.
-\end{proof}
-
-%Now we see that the Trace of Frobenius is surjective.
-
-\begin{lemma}\label{lem:etale-trace}
-If $G$ is an \'etale commutative group scheme over $\Fq$
-then Trace of Frobenius
-\[
-\TrFrob{G} : \QCiso{G} \to G(\Fq)^*
-\]
-is a surjective group homomorphism.
-\end{lemma}
-
-\begin{proof}
+\begin{proof}
+We start by showing that the top sequence is exact by showing that $\TrFrob{G}$ is surjective.
 Pick $\chi \in G(\Fq)^*$.
-By Lemma~\ref{lem:dual-inv}, there is some $f\in G(\bFq)^*$ such that $f\vert_{G(\Fq)^*} = \chi$.
+By Lemma~\ref{lem:dual-inv}, there is some $b\in G(\bFq)^*$ such that $b\vert_{G(\Fq)^*} = \chi$.
 Set $\gqcs{L}_x = \EE$ for every $x\in G(\bFq)$.
 Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$.
-Define $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = f(x)$.
-Since $f : G(\bFq) \to \EEx$ is a group homomorphism,
-condition \eqref{nohom} is satisfied with $g =1$, the trivial cocycle in $Z^2(G(\bFq),\EEx)$.
+Define $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = b(x)$.
+Since $b : G(\bFq) \to \EEx$ is a group homomorphism,
+condition \eqref{nohom} is satisfied with $a =1$, the trivial cocycle in $Z^2(G(\bFq),\EEx)$.
 It is now clear that we have defined a \emph{visible} quasicharacter sheaf $\qcs{L}$ with $\trFrob{\qcs{L}} = \chi$.
-\end{proof}
-
-%Likewise, $S_G$ is surjective.
-
-\begin{lemma}\label{lem:etale-2cocycle}
-    If $G$ is an \'etale commutative group scheme over $\Fq$
-    then the group homomorphism
-    \[
-    S_{G} : \QCiso{G} \to \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx)),
-    \]
-    defined in Section~\ref{sec:invisible}, is surjective.
-\end{lemma}
-
-\begin{proof}
-Pick $[g]\in \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx))$.
-Then $g\in Z^2(G(\bFq),\EEx)$ is fixed by Frobenius, so $\,^{\Frob{}}g = g h$ for some $h\in B^2(G(\bFq),\EEx)$.
-Accordingly, $h(x,y) = \frac{f(x+y)}{f(x) f(y)}$ for some $f : G(\bFq) \to \EEx$, so
-\begin{equation}\label{gf}
-\frac{g(\Frob{}(x),\Frob{}(y))}{g(x,y)} = \frac{f(x+y)}{f(x) f(y)}
-\end{equation}
-for all $x,y\in G(\bFq)$.
-Set $\gqcs{L}_x = \EE$ for every $x\in G(\bFq)$ and define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x \otimes \gqcs{L}_y$ by $\mu_{x,y}(1) = g(x,y) 1 \otimes 1$.
-Since $g\in Z^2(G(\bFq),\EEx)$, the indexed set of isomorphisms $\{ \mu_{x,y} \tq x,y \in G(\bFq) \}$ satisfies \ref{qc.2}.
-Define $\phi_x : \gqcs{L}_{\Frob{}(x)}\to \gqcs{L}_x$ by $\phi_x(1) = f(x)$.
-Then set of isomorphisms $\{ \phi_{x} \tq x \in G(\bFq) \}$ satisfies \ref{qc.3} by \eqref{gf}.
-In this way, the cocycle $g\in Z^0(\Weil{}, Z^2(G(\bFq),\EEx))$ defines a quasicharacter sheaf $\qcs{L}$.
-It is clear that $\qcs{L}$ maps to $[g] \in \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx))$ under \eqref{2cocycle}.
-\end{proof}
-
-\begin{lemma}\label{lem:trivial}
-\[
-\ker T_{G} \cap \ker S_{G} = 0
-\]
-\end{lemma}
-
-\begin{proof}
-Suppose $\trFrob{\qcs{L}} =1$ and $s_\qcs{L} =1$
-Let $f$ and $g$ be as above.
-Since the class of $g$ is trivial, $g(x,y) = \frac{h(x+y)}{h(x) h(y)}$ for some $h : G(\bFq) \to \EEx$;
-since the class of $f$ is trivial, $f(x) = \frac{k(\Frob{G}(x))}{k(x)}$ for some $k : G(\bFq) \to \EEx$.
-\todo{Actually, the lemma is false.}
-\end{proof}
-
-Now we can prove Proposition~\ref{prop:etale-iso}.
-
-\begin{proof}[Proof of Proposition~\ref{prop:etale-iso}]
-By Lemma~\ref{lem:dual-inv}, $G(\Fq)^* \iso \Hh^1(\Weil{},\Hh^1(G(\bFq),\EEx))$. Composing this isomorphism with the Trace of Frobenius gives
-\[
-T_{G}: \QCiso{G}\to  \Hh^1(\Weil{},\Hh^1(G(\bFq),\EEx)),
-\]
-which is surjective, Lemma~\ref{lem:etale-trace}.
-Combining this with
-\[
-S_{G} : \QCiso{G} \to \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx))
-\]
-gives
-\[
-\QCiso{G} \mathop{\longrightarrow}\limits^{R_G} \Hh^1(\Weil{},\Hh^1(G(\bFq),\EEx))\oplus \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx)).
-\]
-The Hochschild-Serre spectral sequence provides
-\[
-\Hh^2(G(\bFq)\rtimes \Weil{},\EEx)  \iso \Hh^1(\Weil{}, \Hh^1(G(\bFq),\EEx)) \oplus \Hh^0(\Weil{}, \Hh^2(G(\bFq),\EEx)).
-\]
-Composing these last two maps defines
-\begin{equation}
-\QCiso{G}\to \Hh^2(G(\bFq)\rtimes \Weil{},\EEx).
-\end{equation}
-To see that this homomorphism is an isomorphism, observe that $S_G$ and $T_G$ are surjective and $\ker S_G \cap \ker T_G = 0$.
-\end{proof}
-
-\section{The main result}
+
+Since we saw that the bottom sequence in exact in Section~\ref{sec:SES} and that the diagram commutes in Proposition~\ref{prop:ST}, the diagram defines a map of short exact sequences.
+
+Now we show that $S_G: \QCiso{G}\to \Hh^0(\Weil{},\Hh^2({\bar G},\EEx))$ injective;
+Suppose $\qcs{L} \in \QCiso{G}$.
+Let $a$ and $b$ be defined, as in Section~\ref{sec:S}, by a choice $\{ v_x \in \gqcs{L}_x^\times \tq x\in {\bar G}\}$; and let $\alpha\oplus\beta$ be the corresponding representative for the class $S_G(\qcs{L})\in \Hh^2(E^\bullet_G)$.
+Now suppose $S_G(\qcs{L}) = [\alpha\oplus\beta]=0$.
+Then $\alpha\oplus\beta = d\gamma$ for some $\gamma \in C^1(\Weil{},C^1({\bar G},\EEx)$. Let $c : {\bar G}\to \EEx$ be the function given by $x\mapsto \gamma(\Frob{})(x)$.
+For each $x\in {\bar G}$, define $\gamma_x : \gqcs{L}_x \to \EE$ by $v_x \mapsto c(x)$.
+Then the indexed set of isomorphisms $\{ \gamma_x : \gqcs{L}_x \to \EE \tq x\in {\bar G}\}$ satisfies condition \ref{qc.4} (with $\gqcs{L'}$, $\mu'$ and $\phi'$ trivial) and therefore defines an isomorphism $\qcs{L} \to (\EE)_{G}$.
+This shows that $S_G: \QCiso{G}\to \Hh^0(\Weil{},\Hh^2({\bar G},\EEx))$ is injective.
+
+To see that $S_G: \QCiso{G}\to \Hh^0(\Weil{},\Hh^2({\bar G},\EEx))$ is surjective, begin with $\alpha\oplus\beta \in Z^2(E^\bullet_G)$.
+Let $a \in C^2({\bar G},\EEx)$ and $b \in C^1({\bar G},\EEx)$ be defined as above, which makes use of the fact $d_{\rightarrow}\beta =0$.
+Set $\gqcs{L}_x = \EEx$ and define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes\gqcs{L}_y$ by $\mu_{x,y}(1) = a(x,y) 1\otimes 1$ and define $\phi_x : \gqcs{L}_{\Frob{G}(x)} \to \gqcs{L}_x$ by $\phi_x(1)= b(x)$.
+Then \ref{qc.1} is true since $d_{\uparrow}\alpha =0$ and \ref{qc.2} is true since $d_{\rightarrow}\alpha =d_{\uparrow} \beta$.
+In this way, from $\alpha\oplus\beta\in Z^2(E^\bullet_G)$ we have define a quasicharacter sheaf $\qcs{L}$ on $G$ with $S_G(\qcs{L}) = [\alpha\oplus\beta]$, showing that $S_G$ is surjective.
+\end{proof}
+
+\section{Main results}
 
@@
 
-Consider the short exact sequence in the category of $\QC$-schemes
+Consider the short exact sequence
 defining the component group scheme for $G$:
@@
 \end{equation}
-Since $\pi_0(G)$ is also a $\QC$-scheme,
+Since $\pi_0(G)$ is a etale commutative group scheme, and this smooth,
 Proposition~\ref{prop:pullback} implies that \eqref{eq:pi0} defines the sequence of functors
@@
 \begin{tikzcd}
-%0 \rar &
+0 \rar &
 \QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
@@
 and $\QCiso{\pi_0(G)}$
-in Sections~\ref{sec:connected} and \ref{sec:etale}.
-In this section we show that \eqref{eq:pi2} is exact.\todo{I wonder if $(F_1,F_2)$, see \ref{prop:functorialG}, form an adjoint pair.}
+in Sections~\ref{sec:connected} and \ref{sec:etale}, respectively.
+In this section we show that \eqref{eq:pi2} is right exact.
 
@@
 \begin{proof}
-We already know the sequence is exact at $\QCiso{G^0}$.
-Here we show exactness at $\QCiso{G}$.
+The sequence is exact at $\QCiso{G^0}$ by Proposition~\ref{prop:restriction},
+so here we show that it is also exact at $\QCiso{G}$.
 First note that $\iota_0^* \circ \pi_0^*$ is trivial by Proposition~\ref{prop:pullback}.
@@
 
-To close this section, we note that the injectivity of $\pi_0^*$ will be proven in Corollary~\ref{cor:exact}.
+\begin{corollary}\label{cor:kerT-surjective}
+$\ker T_{\pi_0(G)} \to \ker T_G$ is surjective.
+\end{corollary}
 
@@
 $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
-In fact, Trace of Frobenius is an isomorphism when $G$ is a $\QC$-scheme.
+In this section we improve that result.
+%we will also give a cohomological description of $\ker \TrFrob{G}$.
 
@@
   If $G$ is a smooth, commutative group scheme over
-  $\Fq$ then Trace of Frobenius
-  \[
-  \TrFrob{G} : \QCiso{G} \to G(\Fq)^*
-  \]
-  is a functorial surjection with kernel $\Hh^0(\Weil{}, \Hh^2(\pi_0({\bar G}), \EE))$ and a canonical section.\todo{I wonder if $(F_1,F_2)$, see \ref{prop:functorialG}, form an adjoint pair.
-That seems to be what this theorem is saying.}
+  $\Fq$ then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective.
+
+  $\QCiso{G}\to \Hh^2(E^\bullet_G)$ from Section~\ref{sec:spectral} induces an isomorphism of short exact sequences:
+\[
+\begin{tikzcd}
+ 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \QCiso{G}\arrow{d} \arrow{r} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
+  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r} & 0.
+ \end{tikzcd}
+ \]
+In particular,
+$\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$
+is surjective with a canonical section.
 \end{theorem}
@@
 \begin{proof}
-  Recall the short exact sequence \eqref{eq:pi0} in the category of $\QC$-schemes
+  Recall the short exact sequence \eqref{eq:pi0}
   defining the component group scheme for $G$:
@@
   \]
+  The sequence of
+  abelian groups
+  \begin{equation}\label{eq:pi0k}
+  \begin{tikzcd}
+    1 \rar & G^0(\Fq) \rar & G(\Fq) \rar & \pi_0(G)(\Fq) \rar & 0,
+  \end{tikzcd}
+  \end{equation}
+  is exact since $\Hh^1(\Fq,G^0) =0$ by Lemma~\ref{lem:G0alg-grp} and Lang's theorem on connected algebraic groups over finite fields \cite{lang:56a}.
+  Since $\EEx$ is divisible, $\Hom_\text{Ab}(\ - \ ,\EEx)$ is exact and thus the dual sequence of
+  character groups is also exact.
   Let
@@
   \begin{tikzcd}[row sep=30]
-    {}& \ker \TrFrob{\pi_0(G)} \dar & \arrow[dashed]{d} \ker \TrFrob{G} & \ker \TrFrob{G^0} \dar & \\
-    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
+    {}& \ker \TrFrob{\pi_0(G)} \arrow[dashed]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dashed]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
+    %0 \rar
+    & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
     & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
     0 \rar & \pi_0(G)(\Fq)^* \rar \dar
-    & \arrow[dashed]{d} G(\Fq)^* \rar & G^0(\Fq)^* \rar \dar & 0\\
-    & \coker \TrFrob{\pi_0(G)} & \coker \TrFrob{G} &  \coker \TrFrob{G^0} &
+    & \arrow{d} G(\Fq)^* \rar & G^0(\Fq)^* \rar \dar & 0\\
+    & \coker \TrFrob{\pi_0(G)} =0 \arrow[dashed]{r} & \coker \TrFrob{G} \arrow[dashed]{r} &  \coker \TrFrob{G^0} =0 &
   \end{tikzcd}
@@
   Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.
-
-  The bottom row is dual to the sequence of
-  abelian groups
-  \begin{equation}\label{eq:pi0k}
-  \begin{tikzcd}
-    1 \rar & G^0(\Fq) \rar & G(\Fq) \rar & \pi_0(G)(\Fq) \rar & 0,
-  \end{tikzcd}
-  \end{equation}
-  which is exact by Lang's theorem on connected algebraic groups over finite fields \cite{lang:56a}.
-  Since $\EEx$ is divisible, $\Hom(\ - \ ,\EEx)$ is exact and thus the dual sequence of
-  character groups is also exact.
-
-  In order to apply the snake lemma, we need to show that the top row is exact at $\QCiso{G}$ and $\QCiso{G^0}$:
+%
+The top row is also exact:
   the surjectivity of $\QCiso{G} \to \QCiso{G^0}$ follows from Proposition~\ref{prop:restriction}
@@
   Now Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}
-  imply that $\ker \TrFrob{G^0} =0$ and $\coker \TrFrob{G^0}=0$.
-  Similarly, Proposition~\ref{prop:etale-iso} shows that $\ker \TrFrob{\pi_0(G)}=0$
+  imply that $\ker \TrFrob{G^0} =0$ and $\coker \TrFrob{G^0}=0$,
+  while Proposition~\ref{prop:etale-iso} gives $\ker \TrFrob{\pi_0(G)} \iso \Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$
   and $\coker \TrFrob{\pi_0(G)}=0$.
-  We may thus apply the snake lemma and conclude that
-  $\ker \TrFrob{G}$ and $\coker \TrFrob{G}$ both vanish.
-\end{proof}
+%
+We may thus apply the snake lemma and conclude that $\coker \TrFrob{G} =0$.
+\end{proof}
+
+Note that the snake lemma also gives  $\ker \TrFrob{\pi_0(G)} \to \ker \TrFrob{G}$ is surjective.
+
+\begin{theorem}
+We need to find $\ker T_G$.
+\end{theorem}
+
+\begin{proof}
+Here are some pieces that might help . . .
+
+Consider Diagram~\ref{diagram}, where $B=G$, $C= \pi_0(G)$ and $A=G^0$:
+We have just seen that the back of this diagram commutes and its sequences are exact.
+The front of this diagram also commutes and all its vertical sequences are also exact,
+as we saw in Section~\ref{sec:spectral}.
+Joining the back to the front are the injections from
+Section~\ref{sec:spectral} making the entire diagram commute.
+The vertical left face is an isomorphism of exact sequences by Proposition~\ref{prop:etale-iso}
+and the vertical right faceis an isomorphism of exact sequences by Proposition~\ref{prop:connected-iso}.
+%
+Note that these injections are isomorphisms at the bottom, by Lemma~\ref{lem:dual-inv}, and at the left, by Section~\ref{sec:etale}, and at the right, by Section~\ref{sec:connected} and the Five Lemma.
+It now follows that $\ker T_B \to \Hh^0(\Weil{},\Hh^2(B,\EEx))$ is also an isomorphism,
+completing the proof of Theorem~\ref{thm:snake}.
+\end{proof}
+
+\begin{table}[ht]
+\caption{A big diagram}
+\begin{center}
+{\smaller\smaller\smaller
+    \[
+  \begin{tikzcd}[row sep=20, column sep=3]
+    &  0 \arrow{dd} && 0 \arrow{dd} && 0\arrow{dd} & \\
+    &&  0 \arrow[crossing over]{dd} && 0 \arrow[crossing over]{dd} && 0\arrow{dd} & & \\
+    {}& \ker \TrFrob{C} \arrow[->>]{rr} \arrow[>->>]{dr} \arrow{dd} && \arrow{dd} \ker \TrFrob{B} \arrow{rr} \arrow[>->]{dr}  && \ker \TrFrob{A}=0 \arrow[>->>]{dr} \arrow{dd} \arrow{rr} && 0 & \\
+    && \Hh^0(\Weil{},\Hh^2(C,\EEx)) \arrow[crossing over,->>]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(B,\EEx)) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(A,\EEx)) \arrow[crossing over]{dd}  &  &  \\
+    & \QCiso{C} \arrow[>->>]{dr}\arrow{rr} \arrow{dd}%{\TrFrob{C}}
+    && \QCiso{B} \arrow[>->]{dr} \arrow{rr} \arrow{dd}%{\TrFrob{B}}
+    && \QCiso{A} \arrow[>->>]{dr} \arrow{dd}%{\TrFrob{A}}
+    \arrow{rr}  &   & 0 & \\
+\Hh^1(E^\bullet_{A}) \arrow[crossing over]{rr}  && \Hh^2(E^\bullet_{C}) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^2(E^\bullet_{B}) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^2(E^\bullet_{A}) \arrow{rr} \arrow[crossing over]{dd} &  & \Hh^3(E^\bullet_{C}) \\
+   0 \arrow{r}
+    & C(\Fq)^* \arrow[>->>]{dr} \arrow{rr} \arrow{dd}
+    && \arrow{dd} B(\Fq)^* \arrow[>->>]{dr} \arrow{rr} && A(\Fq)^* \arrow[>->>]{dr}  \arrow{dd}
+    \arrow{rr}&& 0 & \\
+ %\Hh^2(\Weil{},\Hh^1({\bar A},\EEx)) \arrow{rr}
+ && \Hh^1(\Weil{},\Hh^1(C,\EEx)) \arrow[crossing over]{dd} \arrow[crossing over]{rr}  && \Hh^1(\Weil{},\Hh^1(B,\EEx)) \arrow[crossing over]{dd} \arrow[crossing over]{rr} && \Hh^1(\Weil{},\Hh^1(A,\EEx)) \arrow[crossing over]{dd}  &  & %\Hh^0(\Weil{},\Hh^1({\bar C},\EEx))
+ \\
+  & 0  && 0  &&  0  && & \\
+        &&  0 && 0 && 0 & & \\
+  \end{tikzcd}
+  \]
+}
+\end{center}
+\label{diagram}
+\end{table}
 
 \begin{corollary}\label{cor:exact}
-Suppose that
-\[
-0 \to A \to B \to C \to 0
-\]
-is an exact sequence of $\QC$-schemes and that $\Hh^1(\Fq, A) = 0$.
-Then pullback yields an exact sequence
-\[
-0 \to \QCiso{C} \to \QCiso{B} \to \QCiso{A} \to 0
-\]
-of abelian groups.
+  If $G$ is a smooth, commutative group scheme over
+  $\Fq$ then pullback yields an exact sequence
+\[
+\Hh^1(E^\bullet_{G^0}) \to \QCiso{\pi_0(G)} \to \QCiso{G} \to \QCiso{G^0} \to 0
+\]
+of abelian groups.\todo{Pure speculation.}
 \end{corollary}
-\begin{proof}
-Since $\Hh^1(k, A) = 0$, the sequence $0 \to A(\Fq) \to B(\Fq) \to C(\Fq) \to 0$ is exact;
-applying $\Hom(-, \EEx)$ yields another exact sequence since $\EEx$ is divisible.  The result now follows
-from Proposition~\ref{prop:pullback} and Theorem~\ref{thm:snake}.
+
+\begin{proof}
+Really? Then does this make sense: $\Hh^3(E^\bullet_{\pi_0(G)}) =0$? Perhaps. $\Hh^3(\pi_0({\bar G})\rtimes \Weil{},\EEx)=0?$
 \end{proof}
@@
 \begin{corollary} \label{cor:bounded-and-finite}
-Suppose $G$ is a $\QC$-scheme and $\qcs{L}$ is a quasicharacter sheaf on $G$.  Then
+Suppose $G$ is a $\QC$-scheme and $\qcs{L}$ is a quasicharacter sheaf on $G$.\todo{I haven't had a chance to go over this again, yet.}  Then
 \begin{enumerate}
@@
 with the same restriction to $G^0(\Fq)$ since $G^0(\Fq)$ is lies inside the torsion part of
-the finitely generated abelian group $G(\Fq)$.  Therefore $\chi$ will be bounded (have finite image)
-if and only if $\chi \cdot \chi_0^{-1}$ is bounded (has finite image).  But $\chi \cdot \chi_0^{-1}$ descends
+the finitely generated abelian group $G(\Fq)$.  Therefore $\chi$ is bounded (resp. has finite image)
+if and only if $\chi \cdot \chi_0^{-1}$ is bounded (resp. has finite image).  But $\chi \cdot \chi_0^{-1}$ descends
 to a character of $\pi_0(G)$.  A similar argument relates boundedness/finiteness of quasicharacter
@@
 
-Two approaches: subcategory and quotient category\todo{Under construction}
+In the introduction to this paper we noted that, when working with connected commutative algebraic groups over finite fields, Deligne's dictionary can be described using Weil sheaves $\qcs{L}$ for which there exists an isomorphism $m^* \qcs{L} \iso \qcs{L} \boxtimes\qcs{L}$, without keeping track of the isomorphism.
+In this section we use that perspective to repair the defect in the sheaf--function dictionary, effectively making invisible quasicharacter sheaves disappear.
+
+Let $G$ be a smooth commutative group scheme over $\Fq$.
+Rather that considering triples $(\gqcs{L},\mu,\phi)$ as in Definition~\ref{def:QC}, consider Weil sheaves $(\gqcs{L},\phi)$ on $G$ for which there \emph{exists} an isomorphism $\mu: \bm^* \gqcs{L} \to \gqcs{L} \boxtimes \gqcs{L}$ such that the triple $(\gqcs{L},\mu,\phi)$ satisfies the conditions appearing in Definition~\ref{def:QC}.
+The resulting objects lie in the essential image of the forgetful functor $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ from $\QC(G)$ to Weil sheaves on $G$.
+We form a category from these objects by declaring that a morphism $(\gqcs{L},\phi) \to (\gqcs{L'},\phi')$ is a sheaf homomorphism $\alpha : \gqcs{L} \to \gqcs{L'}$ for which the two diagrams in Condition~\ref{QC.4} commute, for \emph{some} choice of $\mu$, $\mu'$ such that $(\gqcs{L},\mu,\phi)$ and $(\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$.
+This is the category of \emph{loose} quasicharacter sheaves on $G$, denoted by $\lQC(G)$.
+The category of loose quasicharacter sheaves on $G$ is rigid monoidal and the functor $\QC(G) \to \lQC(G)$ is monoidal and essentially surjective but neither full nor faithfull, generally.
+
+Since objects in $\lQC(G)$ are Weil sheaves and since in the first diagram in Condition~\ref{QC.4} ensures that a morphism in $\lQC(G)$ is a morphism of Weil sheaves, it follows that $\lQC(G)$ is a subcategory of Weil sheaves on $G$.
+
+Since the trace of Frobenius makes sense for all Weil sheaves, as noted in \eqref{trWeil}, and since
+$\trFrob{(\gqcs{L},\phi)} = \trFrob{(\gqcs{L'},\phi')}$ when $(\gqcs{L},\phi) \iso (\gqcs{L'},\phi')$ in $\lQC(G)$,
+there is an evident meaning for the Trace of Frobenius $\lTrFrob{G} : \lQCiso{G} \to G(\Fq)^*$.
+It is clear, too, that $\lTrFrob{G} : \lQCiso{G} \to G(\Fq)^*$.
+is a surjective group homomorphism, since $\QCiso{G}  \to G(\Fq)^*$ is surjective, by Theorem~\ref{thm:snake}.
+What is the kernel of this group homomorphism?
+
+\begin{theorem}\label{thm:loose}
+The Trace of Frobenius on $\lTrFrob{G}: \lQCiso{G}  \to G(\Fq)^*$ is a functorial isomorphism.
+\end{theorem}
+
+\begin{proof}
+We have already seen that $\lTrFrob{G}$ is a surjective group homomorphism, so here we will show that the kernel of $\lTrFrob{G}$ is trivial.
+
+First, suppose $G$ is etale.
+Let $(\gqcs{E},\phi')$ be a loose quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{E},\phi')}=1$.
+Let $\qcs{E} = (\gqcs{E},\mu,\phi')$ be a quasicharacter sheaf.
+By Proposition~\ref{prop:etale-iso}, $S_G(\qcs{E}) = [\alpha\oplus 0]$ for some $\alpha \in Z^0(\Weil{},Z^2({\bar G},\EEx))$
+corresponding to a choice $\{ v_x \in \gqcs{E}_x^\times \tq x\in {\bar C}\}$.
+Let $a\in Z^2({\bar G},\EEx)$ be the mutliplicative version of $\alpha$
+and let $\mu'$ be the indexed set of isomorphisms $\mu'_{x,y} : \EE \to \EE\otimes \EE$ defined by $1 \mapsto a(x,y) 1 \otimes 1$.
+Then $(\EE,\mu', 1)$ is a quasicharacter sheaf the isomorphisms $\gqcs{E}_x \to \EE$ defined by $v_x \mapsto 1$ gives an isomorphism $(\gqcs{E},\mu,\phi')\to ((\EE)_{\bar C},\mu', 1)$ in $\QC(G)$.
+It follows that $(\gqcs{E},\phi')\iso ((\EE)_{\bar G},1)$ in $\lQC(G)$, so $\lTrFrob{G}$ is injective.
+This completes the proof of Proposition~\ref{prop:loose} in the case that $G$ is etale.
+
+Now let $G$ be arbitrary
+and let $(\gqcs{L},\phi)$ be a loose quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{L},\phi)}=1$.
+Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf.
+In Corollary~\ref{cor:kerT-surjective} (and Theorem~\ref{thm:snake}) we saw that $\ker \TrFrob{\pi_0(G)}\to \TrFrob{G}$ is surjective,
+so $\qcs{L} = \pi_0^*\qcs{E}$ for some $\qcs{E}\in \QC(\pi_0(G))$.
+Since $\trFrob{\qcs{L}}(g) = \trFrob{\qcs{E}}(\pi_0(g))$ and since $\pi_0 : G(\Fq) \to \pi_0(G)(\Fq)$ is surjective, $\trFrob{\qcs{E}}=1$.
+But now $\qcs{E} \iso ((\EE)_{\pi_0({\bar G})},\mu', 1)$ by the paragraph above.
+So $\qcs{L} = \pi_0^*\qcs{E} \iso \pi_0^*((\EE)_{\pi_0({\bar G})},\mu', 1) = ((\EE)_{\bar G},\pi_0^*\mu', \pi_0^*1)$ in $\QC(G)$.
+It follows that $(\gqcs{L},\phi) \iso ((\EE)_{\bar G},1)$ in $\lQC(G)$.
+This completes the proof of Theorem~\ref{thm:loose}.
+\end{proof}
 
@@
 \end{document}
-%sagemathcloud={"zoom_width":125}
+%sagemathcloud={"zoom_width":95}

### 2014-05-21 dictionary.tex
Removing speculation in spectral sequences section, other fixes

--- 2014-05-16 dictionary.tex
@@
 
-\title[Lost in Translation: The function--sheaf dictionary]{Lost in Translation: \\ The function--sheaf dictionary for smooth commutative group schemes over finite fields}
+\title[The function--sheaf dictionary]{The function--sheaf dictionary for smooth commutative group schemes over finite fields}
 
@@
   connected commutative algebraic groups over finite fields to smooth
-  commutative group schemes over finite fields.
-  To do so, we introduce the monoidal category of quasicharacter sheaves on
-  smooth commutative group schemes $G$ over $\mathbb{F}_q$
-  and show that the Trace of Frobenius is a functorial surjection
-  from the group of isomorphism classes of quasicharacter sheaves on $G$
-  onto the character group of $G(\mathbb{F}_q)$.
-  If $G$ is connected, the kernel of this surjection is trivial.
-  In $G$ is etale, however, the kernel is generally non-trivial,
-  leading to the interesting notion of invisible quasicharacter sheaves.
-  In this paper we find a cohomological classification of invisible quasicharacter sheaves on all smooth commutative group schemes over $\mathbb{F}_q$,
-  and also explain how to make invisible quasicharacter sheaves disappear,
-  should the notion prove too troubling.
+  commutative group schemes over finite fields,
+  in which case some interesting new features of the dictionary arise.
    \end{abstract}
@@
 
-\subsection*{Overview}
-Deligne's function--sheaf dictionary translates characters of connected, commutative algebraic groups $G$ over finite fields $\Fq$ into certain local systems on G, from which the character of $G(\Fq)$ can be recovered using the action of Frobenius on $G$.
-The local systems which appear in this dictionary are easily characterised and often referred to as \emph{character sheaves} on $G$.
-The result is a perfect dictionary between characters of $G(\Fq)$ and character sheaves on G, with which the formidable artillery of algebraic geometry can be brought to bear on the study of characters of $G(\Fq)$.
-Although this dictionary extends to the case when $G$ is not connected, and even to all smooth commutative group schemes over $\Fq$, the result is not perfect.
-In this generality, the correct class of sheaves on G are called \emph{quasicharacter sheaves}; when $G$ is connected and of finite type, quasicharacter sheaves on $G$ specialize to character sheaves on $G$.
-While every character of $G(\Fq)$ may be converted, canonically, into a quasicharacter sheaf on G from which the character of $G(\Fq)$ may be recovered using the trace of Frobenius on G, generally there exist non-trivial quasicharacter sheaves on G for which the trace of Frobenius is trivial; these are called \emph{invisible quasicharacter sheaves} on $G$.
-Invisible quasicharacter sheaves on G are precisely the quasicharacter sheaves on $G$ that are lost in translation under the function-sheaf dictionary.
-This paper gives a cohomological description of invisible quasicharacter sheaves on $G$
-and a trick to make invisible quasicharacter sheaves disappear,
-should the notion prove too troubling.
-
-\subsection*{Main result}
-
-In order to describe the main result of this paper with more precision, let us briefly review how the function--sheaf dictionary for connected commutative algebraic groups over finite fields \cite{deligne:SGA4.5}*{sommes trig.} translates characters into local systems.
+%\subsection*{Overview}
+
+%Deligne's function--sheaf dictionary translates characters of connected, commutative algebraic groups $G$ over finite fields $\Fq$ into certain local systems on G, from which the character of $G(\Fq)$ can be recovered using the action of Frobenius on $G$.
+%The local systems which appear in this dictionary are easily characterised and often referred to as \emph{character sheaves} on $G$.
+%The result is a perfect dictionary between characters of $G(\Fq)$ and character sheaves on G, with which the formidable artillery of algebraic geometry can be brought to bear on the study of characters of $G(\Fq)$.
+%
+%In this paper we show how this dictionary extends to the case when $G$ is not connected, and even to all smooth commutative group schemes over $\Fq$, in which case some interesting new features of the dictionary arise.
+
+%\subsection{The main result}
+
+%In order to describe the main result of this paper with more precision,
+Let us briefly review how Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields \cite{deligne:SGA4.5}*{sommes trig.} translates characters into local systems.
 Let $\Fq$ be a finite field and let $G$ be a connected commutative algebraic group over $\Fq$; fix an algebraic closure $\bFq$ of $\Fq$
@@
 The function--sheaf dictionary for $G$ identifies a monoidal category of $\ell$-adic local systems on $G$ such that the group of isomorphism classes in this category is canonically identified with the $\ell$-adic character group of $G(\Fq)$, thus providing the geometrization and categorification of characters of $G(\Fq)$.
-
-Although hidden in the discussion above, the connectness of $G$ played a crucial role in the geometrization and categorification of characters of $G(\Fq)$.
-So it is natural to ask how the function--sheaf dictionary generalizes to not-necessarily connected commutative algebraic groups over finite fields.
-In this paper we answer that question by exhibiting a function--sheaf dictionary, in the sense above, for any smooth commutative group scheme $G$ over a finite field $\Fq$.
-To do this we must pass from $\ell$-adic local systems on $G$ to Weil local systems on $G$
-and also keep track of the isomorphisms \eqref{introbox}, leading to the notion of {\it quasicharacter sheaves on $G$}.
-
-So, what is a quasicharacter sheaf?
-A quasicharacter sheaf on $G$ is a triple $\qcs{L}\ceq
+%
+Although hidden in this discussion, the connectness of $G$ played a crucial role in the geometrization and categorification of characters of $G(\Fq)$.
+In particular, when the isomorphism \eqref{introbox} exists for $\qcs{L}$, it is essentially unique.
+
+Now let $G$ be any smooth commutative group scheme over $\Fq$.
+Two new features must be addressed in order to geometrize characters of $G(\Fq)$.
+First, we must pass from $\ell$-adic local systems on $G$ to Weil local systems on $G$
+and, second, we must keep track of the isomorphisms \eqref{introbox}.
+Both issues are addressed in the main definition of this paper:
+A \emph{(tight) quasicharacter sheaf} on $G$ is a triple $\qcs{L}\ceq
 (\gqcs{L},\mu,\phi)$ where $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ of rank~one and $\mu: m^*
 \gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms satisfying natural compatibilty conditions; here $\Frob{G}$ is the Frobenius automorphism of ${\bar G}$.
-
-The main result of this paper is the following statement (see Theorem~\ref{thm:snake}):
-the category $\QC(G)$ of quasicharacter sheaves on $G$
-is a rigid monoidal category and Trace of Frobenius provides a functorial surjection
+A \emph{(loose) quasicharacter sheaf} on $G$ is a Weil sheaf $(\gqcs{L},\phi)$ on $G$
+for which $(\gqcs{L},\mu,\phi)$ is a tight quasicharacter sheaf on $G$, for some $\mu$.
+The difference between these two notions is detected by $\Hh^2(\pi_0({\bar G}),\EEx)$, where $\pi_0({\bar G})$ is the component group for ${\bar G}$.
+%namely, when $\Hh^2(\pi_0({\bar G}),\EEx)$ is non-trivial, if $(\gqcs{L},\phi)$ is a (loose) quasicharacter sheaf on $G$ then there are many $\mu$ for which $(\gqcs{L},\mu,\phi)$ is a (tight) quasicharacter sheaf on $G$;
+%
+ In the main result of this paper, Theorem~\ref{thm:snake},
+we form a rigid monoidal category $\lQC(G)$ of (loose) quasicharacter sheaves on $G$
+and show that the Trace of Frobenius provides a functorial group isomorphism
 \begin{equation}
-\QCiso{G} \to \Hom(G(\Fq), \EEx)
+\lQCiso{G} \to \Hom(G(\Fq), \EEx).
 \end{equation}
-with a canonical section.
-We refer to quasicharacter sheaves in the kernel of Trace of Frobenius as \emph{invisible} quasicharacter sheaves.
-If $G$ is a connected commutative algebraic group then
-all quasicharacter sheaves on $G$ are visible.
-In this paper we find a simple cohomological description
-of invisible quasicharacter sheaves on any smooth commutative
-group scheme $G$ over $\Fq$.
-In any case, the canonical section of the Trace of Frobenius allows
-one to convert any quasicharacter of $G(\Fq)$
-into a quasicharacter sheaf on $G$;
-consequently, quasicharacter sheaves geometrize and categorify
-characters of $G(\Fq)$.
-
-\subsection*{Illustrative examples}
-
-Three examples will illustrate some of the issues that arise when extending the function--sheaf dictionary to smooth commutative group schemes over $\Fq$.
+
+%\subsection*{Illustrative Examples}
+
+%Three examples will illustrate some of the issues that arise when extending the function--sheaf dictionary to smooth commutative group schemes over $\Fq$.
 As we show in the paper, $\ell$-adic local systems on $G$ can only be used to geometrize characters of finite order; quasicharacter sheaves, however, provide the geometrization of all characters of $G(\Fq)$.
-In particular, we will see how to uniquely geometrize the character $\ZZ \to \EEx$ defined by
+For example, we will see how to geometrize the character $\ZZ \to \EEx$ defined by
 $1 \mapsto \ell$, which has unbounded image,
 using quasicharacter sheaves on the etale group scheme $\ZZ$ with trivial Galois action.
-All quasicharacter sheaves on this group are visible.
-Likewise, the dictionary is perfect for the
-etale group scheme $\ZZ$ with Galois action determined by $\Frob{}(n) = -n$.
-By contract, the etale group scheme $\ZZ \times \ZZ$ with trivial Galois action
- does admit invisible quasicharacter sheaves -- there are non-trivial quasicharacter sheaves on this group
-with trivial trace of Frobenius.\todo{Under construction}
-(Move this example: Define $g: \ZZ\times \ZZ \to \EEx$ by $g((n_1,m_1), (n_2, m_2)) = \ell^{m_1-m_2 + n_1-n_2}$.
+%Likewise, the dictionary is perfect for the etale group scheme $\ZZ$ with Galois action determined by $\Frob{}(n) = -n$.
+By contract, the etale group scheme $\ZZ \times \ZZ$ with trivial Galois action does admit invisible quasicharacter sheaves -- there are non-trivial quasicharacter sheaves on this group with trivial trace of Frobenius.\todo{Under construction} (Move this example: Define $g: \ZZ\times \ZZ \to \EEx$ by $g((n_1,m_1), (n_2, m_2)) = \ell^{m_1-m_2 + n_1-n_2}$.
 Then use the tehniques of Section~\ref{sec:etale} to build a non-trivial character sheaf from the pair $(f=1,g)$ with trivial trace of Frobenius.)
 
-\subsection*{Motivation and Application}
+%\subsection*{Motivation and Application}
 
@@
 This process of creating a category from the group of quasicharacters of such a torus
-informs our choice of the term \emph{quasicharacter sheaf} here.
-
-\subsection*{Comparison with other character sheaves}
+informs our choice of the term quasicharacter sheaf, here.
+
+%\subsection*{Comparison with other character sheaves}
 
@@
 in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
-We note that there are no invisble quasicharacter sheaves on such groups.
-
-\subsection*{Structure of the paper}
-
-%We close the introduction with a more detailed description of the structure of this paper.
-After setting some notation in Section~\ref{sec:QCschemes}, in Section~\ref{sec:category} we define quasicharacter sheaves and give an interpretation of
+The interesting new features pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Frob{G}}$ do not arise in this case.
+
+%\subsection*{Structure of the paper}
+
+We close the introduction with a brief description of the structure of this paper.
+After setting some basic notation in Section~\ref{sec:notation},
+in Section~\ref{sec:category} we define quasicharacter sheaves and give an interpretation of
 them as Weil sheaves equipped with an isomorphism of the form \eqref{introbox}.
@@
 In Section \ref{sec:connected} we show that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves when $G$ is connected, and that Trace of Frobenius is an isomorphism in this case.
-We shift to \'etale group schemes $G$ in Section~\ref{sec:etale} and give a more concrete interpretation
-of quasicharacter sheaves in this case.  Using a notion of global sections for quasicharacter sheaves, in this section
-we also give isomorphisms between $\QCiso{G}$, $\Hh^1(\Weil{}, \Hom(G(\bFq), \EEx))$ and $\Hom(G(\Fq), \EEx)$, where $\Weil{}$ is the Weil group for $\Fq$.
+We shift to \'etale group schemes $G$ in Section~\ref{sec:etale} and find a cohomological interpretation
+of quasicharacter sheaves in this case.
 In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
@@
 Section~\ref{sec:snake} presents the main theorem of this paper: Trace of Frobenius
-is a functorial isomorphism for $\QC$-schemes.
+is a functorial isomorphism from isomorphism classes of (loose) quasicharacter sheaves on $G$
+to characters of $G(\Fq)$.
 
@@
 
-\subsection{Notations}\label{sec:QCschemes}
+\subsection{Notations}\label{sec:notation}
 
@@
 
-\subsection{Main definition}\label{sec:category}
+\subsection{(tight) quasicharacter sheaves}\label{sec:category}
 
 \begin{definition}\label{def:QC}
-A \emph{quasicharacter sheaf on $G$} is a triple
+A \emph{(tight) quasicharacter sheaf on $G$} is a triple
 $\qcs{L}\ceq (\gqcs{L},\mu,\phi)$ where:
@@
 
-\section{Two special subcategories of quasicharacter sheaves}%\label{sec:bounded}
+\section{Two subcategories of quasicharacter sheaves}%\label{sec:bounded}
 
@@
 
-\section{Spectral sequences}\label{sec:spectral}
-
-%\subsection{Invisible quasicharacter sheaves}\label{sec:invisible}
+\section{The case of \'etale commutative group schemes} \label{sec:etale}
+
+%\subsection{Quasicharacter sheaves, revisited}
+
+\'Etale group schemes form a counterpoint to connected groups,
+since the component group of a smooth commutative group scheme
+is an \'etale group scheme \cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
+However, the function--sheaf dictionary is substantially different in the two cases.
+To see why, we begin by specializing the definition of quasicharacter sheaves to the case
+of etale commutative group schemes,
+using the equivalence $G \mapsto G(\bFq)$
+from the category of \'etale group schemes over $\Fq$ to the category of groups equipped
+with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group.
+Under this equivalence, a (tight) quasicharacter sheaf on an etale commutative group scheme $G$ over $\Fq$ is given by the data of:
+\begin{enumerate}
+ \labitem{(qc.1)}{qc.1} an indexed set of one-dimensional
+  $\EE$-vector spaces $\gqcs{L}_x$, as $x$ runs over
+  $G(\bFq)$;
+
+ \labitem{(qc.2)}{qc.2} an indexed set of isomorphisms
+  $\mu_{x,y} : \gqcs{L}_{x+y} \xrightarrow{\iso} \gqcs{L}_{x} \otimes\gqcs{L}_{y}$,
+  for all $x,y \in G(\bFq)$, such that
+  \[
+   \begin{tikzcd}[row sep=40]
+    \gqcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
+    && \gqcs{L}_{x+y}\otimes\gqcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
+    \gqcs{L}_{x} \otimes\gqcs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
+    && \gqcs{L}_{x} \otimes\gqcs{L}_{y} \otimes\gqcs{L}_{z}
+   \end{tikzcd}
+  \]
+  commutes, for all $x,y,z\in G(\bFq)$; and
+ \labitem{(qc.3)}{qc.3} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
+  such that
+  \[
+   \begin{tikzcd}[row sep=40]
+    \gqcs{L}_{\Frob{}(x)+\Frob{}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{}(x),\Frob{}(y)}}
+    && \gqcs{L}_{\Frob{}(x)}\otimes\gqcs{L}_{\Frob{}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
+    \gqcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
+    && \gqcs{L}_x \otimes\gqcs{L}_y
+   \end{tikzcd}
+  \]
+  commutes, for all $x,y\in G(\bFq)$.
+\end{enumerate}
+Under this equivalence, a morphism $\alpha : \qcs{L} \to \qcs{L'}$ of quasicharacter sheaves on $G$ is given by
+\begin{enumerate}
+ \labitem{(qc.4)}{qc.4} an indexed set $\alpha_x : \gqcs{L}_x \to \gqcs{L'}_x$
+  of linear transformations such that
+  \[
+   \begin{tikzcd}[column sep=40]
+    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{}(x)} \rar{\alpha_{\Frob{}(x)}} & \gqcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
+    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
+    & \arrow[swap]{d}{\mu} \gqcs{L}_{x+y} \rar{\alpha_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
+    \gqcs{L}_x \rar{\alpha_x} & \gqcs{L'}_x
+    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\alpha_x\otimes\alpha_y} & \gqcs{L'}_x \otimes\gqcs{L'}_y
+   \end{tikzcd}
+  \]
+  both commute for all $x, y \in G(\bFq)$.
+\end{enumerate}
 
 We will see that the Trace of Frobenius may not provide complete
-information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not a connected algebraic group.
+information about isomorphism classes of tight quasicharacter sheaves on $G$ when $G$ is not a connected algebraic group.
 Our main tool for understanding this phenomenon
-is a group homomorphism from $\QCiso{G}$ to $\Hh^2(E^\bullet_G)$, defined in this section.
-In Section~\ref{sec:restriction} we will see that this homomorphism is an isomorphism for all smooth commutative group schemes over $\Fq$.
-
-[Things I need from this section:
-definition of $E^\bullet_G$ (Section~\ref{sec:E});
-the short exact sequence attached to $\Hh^2(E^\bullet_G)$ (Section~\ref{sec:SES});
-the exactness of all sequences in the diagram below (Section~\ref{sec:front});
-the map $S_G$ from $\QCiso{G}$ to $\Hh^2(E^\bullet_G)$ (Section~\ref{sec:S} done) commutes with everything in sight;
-that $\Hh^0(\Weil,\Hh^2({\bar G},\EEx))=0$ if $G$ is a connected algebraic group over $\Fq$ (Section~\ref{sec:connected-iso}).]
+is a group homomorphism from $\QCiso{G}$ to $\Hh^2(E^\bullet_G)$, defined in Section~\ref{sec:S}, for which the next two sections are preparation.
+
+\subsection{Cohomology}\label{sec:E}
 
@@
 
-\subsection{Cohomology}\label{sec:E}
-
-Define $\Hh^2(E^\bullet_G)$.
-
-Do we have
- \[
-  \begin{tikzcd}[column sep=30]
-    ? \cdots \arrow{r}
-%    & \Hh^1(E^\bullet_{A}) \arrow{r}
-    & \Hh^2(E^\bullet_{C}) \arrow{r}
-    & \Hh^2(E^\bullet_{B}) \arrow{r}
-    & \Hh^2(E^\bullet_{A}) \arrow{r}
-%    & \Hh^3(E^\bullet_{C}) \arrow{r}
-    & \cdots ? \\
-  \end{tikzcd}
- \]
-
-[Question: If $C$ is etale, then $\Hh^3(E^\bullet_{C}) =0?$]
-
-\[\Hh^*(E^\bullet_{G}) = \Hh^*({\bar G}\rtimes \Weil{},\EEx)\]
+Define $\Hh^2(E^\bullet_G)$. \todo{David, I need some help here.}
 
@@
  \]
-
-\subsection{Splitting?}\label{sec:split}
-
- \[
-  \begin{tikzcd}
-    0 \arrow{r}
-    & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r}
-    & \Hh^2(E^\bullet_G) \arrow{r}
-    \arrow[bend right,dotted]{l}
-    & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r}
-    \arrow[bend right,dotted]{l}
-    & 0
-  \end{tikzcd}
- \]
-
-\subsection{Front}\label{sec:front}
-
- \[
-  \begin{tikzcd}[row sep=20, column sep=15]
-    &  ?  & 0 \arrow{d} & 0\arrow{d} & \\
-0 \arrow{r} \arrow{d}   & \Hh^0(\Weil{},\Hh^2(C,\EEx)) \arrow{r} \arrow{d} & \Hh^0(\Weil{},\Hh^2(B,\EEx)) \arrow{r} \arrow{d}
-    & \Hh^0(\Weil{},\Hh^2(A,\EEx)) \arrow{d} \arrow{r} & ? \\
-    %\arrow{rr}  &   & 0 \\
-    ? \arrow{r}
-    & \Hh^2(E^\bullet_{C}) \arrow{r} \arrow{d}
-    & \Hh^2(E^\bullet_{B}) \arrow{r} \arrow{d}
-    & \Hh^2(E^\bullet_{A}) \arrow{r} \arrow{d}
-    & ? \\
-    %\arrow{rr}&& 0\\
-? \arrow{r}  & \Hh^1(\Weil{},\Hh^1(C,\EEx)) \arrow{d} \arrow{r}
-    & \Hh^1(\Weil{},\Hh^1(B,\EEx)) \arrow{d} \arrow{r}
-    & \Hh^1(\Weil{},\Hh^1(A,\EEx)) \arrow{d} \arrow{r}  &  ? \\
-    &  0 & 0 & 0 & \\
-  \end{tikzcd}
- \]
+\todo{Again, I hope you can write this section, David.}
 
@@
 
-\begin{proposition}\label{prop:ST}
- The following diagram commutes:
-\[
-\begin{tikzcd}
- 0 \arrow{r}
- & \ker \TrFrob{G} \arrow{r} \arrow{d}
- & \QCiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}}
- & G(\Fq)^* \arrow{d}{\iso} \arrow{r}
- & \coker \TrFrob{G} \\
- 0 \arrow{r}
- & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r}
- & \Hh^2(E^\bullet_G) \arrow{r}
- & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx))  \arrow{r}
- & 0.
- \end{tikzcd}
- \]
-\end{proposition}
-
-\begin{proof}
-We've discussed the fact that the square on the right commutes, using Lemma~\ref{lem:dual-inv}. I'll add that, later.
-So, if $\qcs{L} \in \QC(G)$ and $S_G(\qcs{L}) = [\alpha\oplus\beta]$  then $\trFrob{\qcs{L}} =1$ implies $[\beta]=0$.
-In Section~\ref{sec:SES} we identified\todo{ ...
-will identify ...} $\{ [\alpha\oplus\beta] \in \Hh^2(E^\bullet_G) \tq [\beta]=0 \}$ with $\Hh^0(\Weil{},\Hh^2({\bar G},\EEx))$.
-\end{proof}
-
-%We begin with a simple result relating duals, invariants and coinvariants.
+\begin{remark}
+Although we will only use the group homomorphism $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$.
+However, the main result of the next section, Proposition~\ref{prop:etale-iso}, is false in that context.
+\end{remark}
+
+\subsection{$S$ and $T$}
+
+In this section we find the relation between the group homomorphisms $\TrFrob{G}$ and $S_G$.
+%
+We begin with a simple result relating duals, invariants and coinvariants.
 
@@
 
-\subsection{Invisible quasicharacter sheaves}
-
-\begin{definition}\label{def:invisible}
-We say $\qcs{L}\in \QC(G)$ is \emph{visible} if the projection of $S_G(\qcs{L})$ to $\Hh^0(\Weil{}, \Hh^2({\bar G},\EEx))$ is trivial; otherwise, we say $\qcs{L}$ is \emph{invisible}.
-\end{definition}
-
-This terminology will be justified later when we show that a non-trivial quasicharacter sheaf $\qcs{L}$ on $G$ is invisible if and only if $\trFrob{\qcs{L}}$ is trivial.
-
-\subsection{Looking back to connected commutative algebraic groups}\label{sec:connected-iso}
-
-We end this Section~\ref{sec:spectral} by appling the tools developed here to the case when $G$ is a connected commutative algebraic group over $\Fq$.
-
-\begin{proposition} \label{prop:connected-iso}
- If $G$ is a connected commutative algebraic group over $\Fq$
-  then the map $\QCiso{G}\to \Hh^2(E^\bullet_G)$ from Section~\ref{sec:spectral} induces an morphism of short exact sequences:
-\[
-\begin{tikzcd}
- 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \QCiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}}  \arrow{r} & G(\Fq)^* \arrow{d}{\iso} \arrow{r} & 0\\
-  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r} & 0.
- \end{tikzcd}
-\]
-\end{proposition}
-
-\begin{proof}
-The top sequence is exact by Corollary~\ref{cor:connected}.
-The bottom sequence is exact by Section~\ref{sec:SES}.
-The diagram commutes and the right-hand vertical arrow is an isomorphism, by Proposition~\ref{prop:ST}.\todo{ If $\Hh^0(\Weil{},\Hh^2({\bar G},\EEx))=0$ then we can improve this lemma.}
-\end{proof}
-
-\section{The case of \'etale commutative group schemes} \label{sec:etale}
-
-%\subsection{Quasicharacter sheaves, revisited}
-
-\'Etale group schemes form a counterpoint to connected groups,
-since the component group of a smooth commutative group scheme
-is an \'etale group scheme \cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
-However, the function--sheaf dictionary is substantially different in the two cases.
-To see why, we begin by specializing the definition of quasicharacter sheaves to the case
-of etale commutative group schemes,
-using the equivalence $G \mapsto G(\bFq)$
-from the category of \'etale group schemes over $\Fq$ to the category of groups equipped
-with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group.
-Under this equivalence, a quasicharacter sheaf on an etale commutative group scheme $G$ over $\Fq$ is given by the data of:
-\begin{enumerate}
- \labitem{(qc.1)}{qc.1} an indexed set of one-dimensional
-  $\EE$-vector spaces $\gqcs{L}_x$, as $x$ runs over
-  $G(\bFq)$;
-
- \labitem{(qc.2)}{qc.2} an indexed set of isomorphisms
-  $\mu_{x,y} : \gqcs{L}_{x+y} \xrightarrow{\iso} \gqcs{L}_{x} \otimes\gqcs{L}_{y}$,
-  for all $x,y \in G(\bFq)$, such that
-  \[
-   \begin{tikzcd}[row sep=40]
-    \gqcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
-    && \gqcs{L}_{x+y}\otimes\gqcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
-    \gqcs{L}_{x} \otimes\gqcs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
-    && \gqcs{L}_{x} \otimes\gqcs{L}_{y} \otimes\gqcs{L}_{z}
-   \end{tikzcd}
-  \]
-  commutes, for all $x,y,z\in G(\bFq)$; and
- \labitem{(qc.3)}{qc.3} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
-  such that
-  \[
-   \begin{tikzcd}[row sep=40]
-    \gqcs{L}_{\Frob{}(x)+\Frob{}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{}(x),\Frob{}(y)}}
-    && \gqcs{L}_{\Frob{}(x)}\otimes\gqcs{L}_{\Frob{}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
-    \gqcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
-    && \gqcs{L}_x \otimes\gqcs{L}_y
-   \end{tikzcd}
-  \]
-  commutes, for all $x,y\in G(\bFq)$.
-\end{enumerate}
-Under this equivalence, a morphism $\alpha : \qcs{L} \to \qcs{L'}$ of quasicharacter sheaves on $G$ is given by
-\begin{enumerate}
- \labitem{(qc.4)}{qc.4} an indexed set $\alpha_x : \gqcs{L}_x \to \gqcs{L'}_x$
-  of linear transformations such that
-  \[
-   \begin{tikzcd}[column sep=40]
-    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{}(x)} \rar{\alpha_{\Frob{}(x)}} & \gqcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
-    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-    & \arrow[swap]{d}{\mu} \gqcs{L}_{x+y} \rar{\alpha_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
-    \gqcs{L}_x \rar{\alpha_x} & \gqcs{L'}_x
-    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\alpha_x\otimes\alpha_y} & \gqcs{L'}_x \otimes\gqcs{L'}_y
-   \end{tikzcd}
-  \]
-  both commute for all $x, y \in G(\bFq)$.
-\end{enumerate}
-
-We may now apply the tools developed in Section~\ref{sec:spectral} to the case at hand, where $G$ is an etale connected group scheme over $\Fq$.
-
 \begin{proposition} \label{prop:etale-iso}
  If $G$ is an \'etale commutative group scheme over $\Fq$
-  then the map $\QCiso{G}\to \Hh^2(E^\bullet_G)$ from Section~\ref{sec:spectral} induces an isomorphism of short exact sequences:
+  then the map $\QCiso{G}\to \Hh^2(E^\bullet_G)$ from Section~\ref{sec:S} induces an isomorphism of short exact sequences:
 \[
@@
 $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$
-is surjective with a canonical section.
+is surjective.
 \end{proposition}
@@
 \begin{proof}
-We start by showing that the top sequence is exact by showing that $\TrFrob{G}$ is surjective.
+We've discussed the fact that the square on the right commutes, using Lemma~\ref{lem:dual-inv}. \todo{David, could you add that here?}
+So, if $\qcs{L} \in \QC(G)$ and $S_G(\qcs{L}) = [\alpha\oplus\beta]$  then $\trFrob{\qcs{L}} =1$ implies $[\beta]=0$.
+In Section~\ref{sec:SES} we identified\todo{ ...
+and this, too?} $\{ [\alpha\oplus\beta] \in \Hh^2(E^\bullet_G) \tq [\beta]=0 \}$ with $\Hh^0(\Weil{},\Hh^2({\bar G},\EEx))$.
+
+Next we show that $\TrFrob{G}$ is surjective.
 Pick $\chi \in G(\Fq)^*$.
@@
 condition \eqref{nohom} is satisfied with $a =1$, the trivial cocycle in $Z^2(G(\bFq),\EEx)$.
-It is now clear that we have defined a \emph{visible} quasicharacter sheaf $\qcs{L}$ with $\trFrob{\qcs{L}} = \chi$.
-
-Since we saw that the bottom sequence in exact in Section~\ref{sec:SES} and that the diagram commutes in Proposition~\ref{prop:ST}, the diagram defines a map of short exact sequences.
+It is now clear that we have defined a (tight) quasicharacter sheaf $\qcs{L}$ with $\trFrob{\qcs{L}} = \chi$.
 
@@
 
-\section{Main results}
+\section{The main result}\label{sec:main}
+
+In the introduction to this paper we noted that, when working with connected commutative algebraic groups over finite fields, Deligne's dictionary can be described using Weil sheaves $\qcs{L}$ for which there exists an isomorphism $m^* \qcs{L} \iso \qcs{L} \boxtimes\qcs{L}$, without keeping track of the isomorphism.
+In this section use that perspective to find a perfect dictionary between (loose) quasicharacter sheaves on $G$ and characters of $G(\Fq)$.
+
+\subsection{(loose) quasicharacter sheaves}\label{sec:loose}
+
+\begin{definition}\label{def:lQC}
+Let $G$ be a smooth commutative group scheme over $\Fq$.
+A \emph{(loose) quasicharacter sheaf} on $G$ is a Weil sheaf $(\gqcs{L},\phi)$ on $G$
+for which $(\gqcs{L},\mu,\phi)$ is a (tight) quasicharacter sheaf on $G$
+for som $\mu: \bm^* \gqcs{L} \to \gqcs{L} \boxtimes \gqcs{L}$.
+%The resulting objects lie in the essential image of the forgetful functor $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ from $\QC(G)$ to Weil sheaves on $G$.
+We form a category from (loose) quasicharacter sheaves by declaring that a morphism $(\gqcs{L},\phi) \to (\gqcs{L'},\phi')$ is a sheaf homomorphism $\alpha : \gqcs{L} \to \gqcs{L'}$ for which the two diagrams in Condition~\ref{QC.4} commute, for some choice of $\mu$, $\mu'$ such that $(\gqcs{L},\mu,\phi)$ and $(\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$.
+The category of \emph{loose} quasicharacter sheaves on $G$ is denoted by $\lQC(G)$.
+\end{definition}
+
+The category of loose quasicharacter sheaves on $G$ is rigid monoidal and the functor $\QC(G) \to \lQC(G)$ is monoidal and essentially surjective but neither full nor faithfull, generally.
+%
+Since objects in $\lQC(G)$ are Weil sheaves and since in the first diagram in Condition~\ref{QC.4} ensures that a morphism in $\lQC(G)$ is a morphism of Weil sheaves, it follows that $\lQC(G)$ is a subcategory of Weil sheaves on $G$.
+
+Since the trace of Frobenius makes sense for all Weil sheaves, as noted in \eqref{trWeil}, and since
+$\trFrob{(\gqcs{L},\phi)} = \trFrob{(\gqcs{L'},\phi')}$ when $(\gqcs{L},\phi) \iso (\gqcs{L'},\phi')$ in $\lQC(G)$,
+there is an evident meaning for the Trace of Frobenius
+\[
+\lTrFrob{G} : \lQCiso{G} \to G(\Fq)^*.
+\]
+Since $\QCiso{G}  \to G(\Fq)^*$ is surjective, by Theorem~\ref{thm:snake},
+it is clear that $\lTrFrob{G} : \lQCiso{G} \to G(\Fq)^*$ is a surjective group homomorphism.
+The main result of this paper, Theorem~\ref{thm:snake}, shows that $\lTrFrob{G} : \lQCiso{G} \to G(\Fq)^*$ is an isomorphism.
 
@@
 
-\begin{corollary}\label{cor:kerT-surjective}
-$\ker T_{\pi_0(G)} \to \ker T_G$ is surjective.
-\end{corollary}
-
 \subsection{The function--sheaf dictionary for smooth, commutative group schemes}
@@
 In this section we improve that result.
-%we will also give a cohomological description of $\ker \TrFrob{G}$.
 
 \begin{theorem}\label{thm:snake}
-  If $G$ is a smooth, commutative group scheme over
-  $\Fq$ then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective.
-
-  $\QCiso{G}\to \Hh^2(E^\bullet_G)$ from Section~\ref{sec:spectral} induces an isomorphism of short exact sequences:
-\[
-\begin{tikzcd}
- 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \QCiso{G}\arrow{d} \arrow{r} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
-  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r} & 0.
- \end{tikzcd}
- \]
-In particular,
-$\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$
-is surjective with a canonical section.
+  If $G$ is a smooth, commutative group scheme over $\Fq$ then
+  \[
+  \lTrFrob{G} : \lQCiso{G} \to G(\Fq)^*
+  \]
+is a functorial group isomorphism.
 \end{theorem}
@@
   \[
-  \begin{tikzcd}[row sep=30]
+  \begin{tikzcd}[row sep=20]
     {}& \ker \TrFrob{\pi_0(G)} \arrow[dashed]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dashed]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
@@
 %
-We may thus apply the snake lemma and conclude that $\coker \TrFrob{G} =0$.
-\end{proof}
-
-Note that the snake lemma also gives  $\ker \TrFrob{\pi_0(G)} \to \ker \TrFrob{G}$ is surjective.
-
-\begin{theorem}
-We need to find $\ker T_G$.
-\end{theorem}
+It follows from the sname lemma that $\coker \TrFrob{G} =0$
+and $\ker \TrFrob{\pi_0(G)} \to \ker \TrFrob{G}$ is surjective.
+
+We now turn our attention $\lTrFrob{G}: \lQCiso{G}  \to G(\Fq)^*$ is an isomorphism.
+First, note that $\lTrFrob{G}$ is surjective because $\TrFrob{G}$ is surjective.
+We will now show that the kernel of $\lTrFrob{G}$ is trivial.
+
+First, suppose $G$ is etale.
+Let $(\gqcs{E},\phi')$ be a loose quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{E},\phi')}=1$.
+Let $\qcs{E} = (\gqcs{E},\mu,\phi')$ be a quasicharacter sheaf.
+By Proposition~\ref{prop:etale-iso}, $S_G(\qcs{E}) = [\alpha\oplus 0]$ for some $\alpha \in Z^0(\Weil{},Z^2({\bar G},\EEx))$
+corresponding to a choice $\{ v_x \in \gqcs{E}_x^\times \tq x\in {\bar C}\}$.
+Let $a\in Z^2({\bar G},\EEx)$ be the mutliplicative version of $\alpha$
+and let $\mu'$ be the indexed set of isomorphisms $\mu'_{x,y} : \EE \to \EE\otimes \EE$ defined by $1 \mapsto a(x,y) 1 \otimes 1$.
+Then $(\EE,\mu', 1)$ is a quasicharacter sheaf the isomorphisms $\gqcs{E}_x \to \EE$ defined by $v_x \mapsto 1$ gives an isomorphism $(\gqcs{E},\mu,\phi')\to ((\EE)_{\bar C},\mu', 1)$ in $\QC(G)$.
+It follows that $(\gqcs{E},\phi')\iso ((\EE)_{\bar G},1)$ in $\lQC(G)$, so $\lTrFrob{G}$ is injective.
+This completes the proof of Theorem~\ref{thm:snake} in the case that $G$ is etale.
+
+Now let $G$ be arbitrary
+and let $(\gqcs{L},\phi)$ be a loose quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{L},\phi)}=1$.
+Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf.
+We saw above that $\ker \TrFrob{\pi_0(G)}\to \TrFrob{G}$ is surjective in this case,
+so $\qcs{L} = \pi_0^*\qcs{E}$ for some $\qcs{E}\in \QC(\pi_0(G))$.
+Since $\trFrob{\qcs{L}}(g) = \trFrob{\qcs{E}}(\pi_0(g))$ and since $\pi_0 : G(\Fq) \to \pi_0(G)(\Fq)$ is surjective, $\trFrob{\qcs{E}}=1$.
+But now $\qcs{E} \iso ((\EE)_{\pi_0({\bar G})},\mu', 1)$ by the paragraph above.
+So $\qcs{L} = \pi_0^*\qcs{E} \iso \pi_0^*((\EE)_{\pi_0({\bar G})},\mu', 1) = ((\EE)_{\bar G},\pi_0^*\mu', \pi_0^*1)$ in $\QC(G)$.
+It follows that $(\gqcs{L},\phi) \iso ((\EE)_{\bar G},1)$ in $\lQC(G)$.
+This completes the proof of Theorem~\ref{thm:snake}.
+\end{proof}
+
+\begin{corollary}\label{cor:exact}
+  If $G$ is a smooth, commutative group scheme over
+  $\Fq$ then pullback yields an exact sequence
+\[
+0 \to \QCiso{\pi_0(G)} \to \QCiso{G} \to \QCiso{G^0} \to 0
+\]
+of abelian groups.
+\end{corollary}
+
+\begin{proof}
+Argue as in the first paragraph in the proof of Theorem~\ref{thm:snake},
+using the category $\lQC(G)$ in place of $\QC(G)$.
+\end{proof}
+
+\begin{corollary} \label{cor:bounded-and-finite}
+Let $G$ be a smooth commutative group scheme over $\Fq$.
+\begin{enumerate}
+\item $\qcs{L} \in \QC(G)$ is bounded if and only if $\trFrob{\qcs{L}}$ has bounded image,
+\item $\qcs{L}\in \QC(G)$ is finite if and only if $\trFrob{\qcs{L}}$ has finite image.
+\end{enumerate}
+\end{corollary}
+
+\begin{proof}
+We first reduce to the case that $G$ is etale.
+On the connected component
+$G^0$, all quasicharacter sheaves are bounded and finite by Proposition~\ref{prop:connected}.
+On the other hand, $G^0(\Fq)$ is finite by Lemma~\ref{lem:G0alg-grp} and thus Trace of Frobenius
+has finite and therefore bounded image.  If $\chi \in G(\Fq)^*$ then there is some finite-image character $\chi_0$
+with the same restriction to $G^0(\Fq)$ since $G^0(\Fq)$ is lies inside the torsion part of
+the finitely generated abelian group $G(\Fq)$.  Therefore $\chi$ is bounded (resp. has finite image)
+if and only if $\chi \cdot \chi_0^{-1}$ is bounded (resp. has finite image).  But $\chi \cdot \chi_0^{-1}$ descends
+to a character of $\pi_0(G)$.  A similar argument relates boundedness/finiteness of quasicharacter
+sheaves on $G$ to those on $\pi_0(G)$, using the fact that the preimage constructed in the proof of
+Proposition~\ref{prop:restriction} is a finite quasicharacter sheaf on $G$.
+Using these equivalences, it is enough to prove Corollary~\ref{cor:bounded-and-finite} when $G$ is etale.
+
+In the case that $G$ is \'etale, which we now suppose,
+one can easily detect when a quasicharacter sheaf is bounded or finite.
+With reference to Section~\ref{sec:S},
+let $S_G(\qcs{L}) = [\alpha \oplus \beta]$
+and let $b : {\bar G}\to \EEx$ be the multiplicative version of $\beta(\Frob{})$.
+Then $\qcs{L}$ is finite if and only if
+$b(x)$ is a root of unity for all $x\in {\bar G}$.
+By \cite{beilinson-bernstein-deligne:81a}*{Rem. 5.2.1},
+$\qcs{L}$ is bounded if and only if $b(x) \in \Zlx$ for all $x\in {\bar G}$.
+\end{proof}
+
+With Corollary~\ref{cor:bounded-and-finite} in hand
+we see that all loose quasicharacter sheaves on $G$ are finite quasicharacter sheaves
+when $G$ is a commutative algebraic group over $\Fq$;
+observe that the component group $\pi_0({\bar G})$ is finite in this case.
+On the otherhand, Corollary~\ref{cor:bounded-and-finite} also shows us
+why neither finite quasicharacter sheaves nor bounded quasicharacter sheaves
+are up to the task of geometrizing all characters of $G(\Fq)$ for smooth commutative group schemes $G$ since, in general, neither of the full subcategories
+$\QCf(G) \subset \QCb(G) \subset \QC(G)$ are equivalences.
+For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$:
+the (loose) quasicharacter sheaf on $G$ corresponding, under Theorem~\ref{thm:snake},
+to the character $1 \mapsto \ell$ is not a bounded quasicharacter sheaf,
+while the (loose) quasicharacter sheaf on $G$ corresponding
+to the character $1 \mapsto 1+ \ell$ is a bounded but not finite quasicharacter sheaf.
+%In this latter case the stalk of the quasicharacter sheaf at the component $1$ is defined by a pro-\'etale cover rather than an \'etale cover.
+
+\bibliographystyle{amsalpha}
+\bibliography{Biblio}
+
+\end{document}
 
@@
 
-\begin{corollary} \label{cor:bounded-and-finite}
-Suppose $G$ is a $\QC$-scheme and $\qcs{L}$ is a quasicharacter sheaf on $G$.\todo{I haven't had a chance to go over this again, yet.}  Then
-\begin{enumerate}
-\item $\qcs{L}$ is bounded if and only if $\trFrob{\qcs{L}}$ has bounded image,
-\item $\qcs{L}$ is finite if and only if $\trFrob{\qcs{L}}$ has finite image.
-\end{enumerate}
-\end{corollary}
-\begin{proof}
-We first reduce to the case that $G$ is an \'etale $\QC$-scheme.  On the connected component
-$G^0$, all quasicharacter sheaves are bounded and finite by Proposition~\ref{prop:connected}.
-On the other hand, $G^0(\Fq)$ is finite by Lemma~\ref{lem:G0alg-grp} and thus Trace of Frobenius
-has finite and therefore bounded image.  If $\chi \in G(\Fq)^*$ then there is some finite-image character $\chi_0$
-with the same restriction to $G^0(\Fq)$ since $G^0(\Fq)$ is lies inside the torsion part of
-the finitely generated abelian group $G(\Fq)$.  Therefore $\chi$ is bounded (resp. has finite image)
-if and only if $\chi \cdot \chi_0^{-1}$ is bounded (resp. has finite image).  But $\chi \cdot \chi_0^{-1}$ descends
-to a character of $\pi_0(G)$.  A similar argument relates boundedness/finiteness of quasicharacter
-sheaves on $G$ to those on $\pi_0(G)$, using the fact that the preimage constructed in the proof of
-Proposition~\ref{prop:restriction} is a finite quasicharacter sheaf on $G$.
-Using these equivalences, it is enough to prove the Corollary
-for \'etale $\QC$-schemes.
-
-In the case that $G$ is \'etale, one can easily see whether a quasicharacter sheaf is bounded or finite.
-For $\qcs{L} \in \QC(G)$, recall that a global section is a particular choice of bases for the vector
-spaces $\qcs{L}_x$.  The isomorphisms $\phi_x : \qcs{L}_{\Frob{}(x)} \to \qcs{L}_x$ are then specified
-by a choice of scalars $b_x$.  By \cite{beilinson-bernstein-deligne:81a}*{Rem. 5.2.1},
-$\qcs{L}$ will be bounded if and only if $b_x \in \Zlx$ for all $x$.  Moreover, $\qcs{L}$ will be
-finite if and only if $b_x$ is a root of unity for all $x$.
-Let $z$ be a cocycle representing the image of $\qcs{L}$ under the isomorphism
-$\QCiso{G} \cong \Hh^1(\Weil{}, G(\bFq)^*)$.  Then $z(\Frob{})(x) = b_x$, and the
-map $\Hh^1(\Weil{}, \Hom(G(\bFq), \Zlx)) \to \Hom(G(\Fq), \Zlx)$ is an isomorphism
-since $\Zlx$ is divisible.  So bounded characters of $G(\Fq)$ correspond to quasicharacter sheaves
-$\qcs{L}$ that descend to Weil sheaves on $G$.  The conditions on the values $b_x$ then
-translate into analogous conditions on the image of Trace of Frobenius.
-\end{proof}
-
-With Corollary~\ref{cor:bounded-and-finite} in hand
-we can see why neither finite quasicharacter sheaves nor bounded quasicharacter sheaves
-are up to the task of geometrizing all characters of $G(\Fq)$ for general $\QC$-schemes $G$ since, in general, neither of the full subcategories
-$\QCf(G) \subset \QCb(G) \subset \QC(G)$ are equivalences.
-For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$.
-If $\chi : \ZZ \to \EEx$ is the quasicharacter of $G(\Fq)$ determined by $\chi(1) = \ell$
-and if $\qcs{L}$ is a quasicharacter sheaf on $G$ in the isomorphism class
-corresponding to $\chi$ under Theorem~\ref{thm:snake},
-then $\qcs{L}$ is not a bounded quasicharacter sheaf since the image of $\chi$ is not
-bounded.
-Likewise, if $\chi : \ZZ \to \EEx$ is the quasicharacter of $G(\Fq)$ determined by $\chi(1) = 1+\ell$
-and if $\qcs{L}$ is a quasicharacter sheaf on $G$ in the isomorphism class
-corresponding to $\chi$ under Theorem~\ref{thm:snake},
-then $\qcs{L}$ is a bounded quasicharacter sheaf but not a finite quasicharacter sheaf
-since the image of $\chi$ is bounded but not finite.
-In this latter case the stalk of $\qcs{L}$ at the component $1$ is defined
-by a pro-\'etale cover rather than an \'etale cover.
-
-\subsection{How to make invisible quasicharacter sheaves disappear}
-
-In the introduction to this paper we noted that, when working with connected commutative algebraic groups over finite fields, Deligne's dictionary can be described using Weil sheaves $\qcs{L}$ for which there exists an isomorphism $m^* \qcs{L} \iso \qcs{L} \boxtimes\qcs{L}$, without keeping track of the isomorphism.
-In this section we use that perspective to repair the defect in the sheaf--function dictionary, effectively making invisible quasicharacter sheaves disappear.
-
-Let $G$ be a smooth commutative group scheme over $\Fq$.
-Rather that considering triples $(\gqcs{L},\mu,\phi)$ as in Definition~\ref{def:QC}, consider Weil sheaves $(\gqcs{L},\phi)$ on $G$ for which there \emph{exists} an isomorphism $\mu: \bm^* \gqcs{L} \to \gqcs{L} \boxtimes \gqcs{L}$ such that the triple $(\gqcs{L},\mu,\phi)$ satisfies the conditions appearing in Definition~\ref{def:QC}.
-The resulting objects lie in the essential image of the forgetful functor $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ from $\QC(G)$ to Weil sheaves on $G$.
-We form a category from these objects by declaring that a morphism $(\gqcs{L},\phi) \to (\gqcs{L'},\phi')$ is a sheaf homomorphism $\alpha : \gqcs{L} \to \gqcs{L'}$ for which the two diagrams in Condition~\ref{QC.4} commute, for \emph{some} choice of $\mu$, $\mu'$ such that $(\gqcs{L},\mu,\phi)$ and $(\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$.
-This is the category of \emph{loose} quasicharacter sheaves on $G$, denoted by $\lQC(G)$.
-The category of loose quasicharacter sheaves on $G$ is rigid monoidal and the functor $\QC(G) \to \lQC(G)$ is monoidal and essentially surjective but neither full nor faithfull, generally.
-
-Since objects in $\lQC(G)$ are Weil sheaves and since in the first diagram in Condition~\ref{QC.4} ensures that a morphism in $\lQC(G)$ is a morphism of Weil sheaves, it follows that $\lQC(G)$ is a subcategory of Weil sheaves on $G$.
-
-Since the trace of Frobenius makes sense for all Weil sheaves, as noted in \eqref{trWeil}, and since
-$\trFrob{(\gqcs{L},\phi)} = \trFrob{(\gqcs{L'},\phi')}$ when $(\gqcs{L},\phi) \iso (\gqcs{L'},\phi')$ in $\lQC(G)$,
-there is an evident meaning for the Trace of Frobenius $\lTrFrob{G} : \lQCiso{G} \to G(\Fq)^*$.
-It is clear, too, that $\lTrFrob{G} : \lQCiso{G} \to G(\Fq)^*$.
-is a surjective group homomorphism, since $\QCiso{G}  \to G(\Fq)^*$ is surjective, by Theorem~\ref{thm:snake}.
-What is the kernel of this group homomorphism?
-
-\begin{theorem}\label{thm:loose}
-The Trace of Frobenius on $\lTrFrob{G}: \lQCiso{G}  \to G(\Fq)^*$ is a functorial isomorphism.
-\end{theorem}
-
-\begin{proof}
-We have already seen that $\lTrFrob{G}$ is a surjective group homomorphism, so here we will show that the kernel of $\lTrFrob{G}$ is trivial.
-
-First, suppose $G$ is etale.
-Let $(\gqcs{E},\phi')$ be a loose quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{E},\phi')}=1$.
-Let $\qcs{E} = (\gqcs{E},\mu,\phi')$ be a quasicharacter sheaf.
-By Proposition~\ref{prop:etale-iso}, $S_G(\qcs{E}) = [\alpha\oplus 0]$ for some $\alpha \in Z^0(\Weil{},Z^2({\bar G},\EEx))$
-corresponding to a choice $\{ v_x \in \gqcs{E}_x^\times \tq x\in {\bar C}\}$.
-Let $a\in Z^2({\bar G},\EEx)$ be the mutliplicative version of $\alpha$
-and let $\mu'$ be the indexed set of isomorphisms $\mu'_{x,y} : \EE \to \EE\otimes \EE$ defined by $1 \mapsto a(x,y) 1 \otimes 1$.
-Then $(\EE,\mu', 1)$ is a quasicharacter sheaf the isomorphisms $\gqcs{E}_x \to \EE$ defined by $v_x \mapsto 1$ gives an isomorphism $(\gqcs{E},\mu,\phi')\to ((\EE)_{\bar C},\mu', 1)$ in $\QC(G)$.
-It follows that $(\gqcs{E},\phi')\iso ((\EE)_{\bar G},1)$ in $\lQC(G)$, so $\lTrFrob{G}$ is injective.
-This completes the proof of Proposition~\ref{prop:loose} in the case that $G$ is etale.
-
-Now let $G$ be arbitrary
-and let $(\gqcs{L},\phi)$ be a loose quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{L},\phi)}=1$.
-Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf.
-In Corollary~\ref{cor:kerT-surjective} (and Theorem~\ref{thm:snake}) we saw that $\ker \TrFrob{\pi_0(G)}\to \TrFrob{G}$ is surjective,
-so $\qcs{L} = \pi_0^*\qcs{E}$ for some $\qcs{E}\in \QC(\pi_0(G))$.
-Since $\trFrob{\qcs{L}}(g) = \trFrob{\qcs{E}}(\pi_0(g))$ and since $\pi_0 : G(\Fq) \to \pi_0(G)(\Fq)$ is surjective, $\trFrob{\qcs{E}}=1$.
-But now $\qcs{E} \iso ((\EE)_{\pi_0({\bar G})},\mu', 1)$ by the paragraph above.
-So $\qcs{L} = \pi_0^*\qcs{E} \iso \pi_0^*((\EE)_{\pi_0({\bar G})},\mu', 1) = ((\EE)_{\bar G},\pi_0^*\mu', \pi_0^*1)$ in $\QC(G)$.
-It follows that $(\gqcs{L},\phi) \iso ((\EE)_{\bar G},1)$ in $\lQC(G)$.
-This completes the proof of Theorem~\ref{thm:loose}.
-\end{proof}
-
-\bibliographystyle{amsalpha}
-\bibliography{Biblio}
-
-\end{document}
-%sagemathcloud={"zoom_width":95}
+%sagemathcloud={"zoom_width":105}

### 2014-05-21 geometrization.tex
Title

@@
 %%%%%%%%%%%%%%%%%% HEADING %%%%%%%%%%%%%%%%%%
-\title[Geometrization of quasicharacters]{Geometrization of quasicharacters of algebraic tori over local fields}
+\title[Geometrization of the local Langlands correspondence for tori]{Geometrization of the local Langlands correspondence for algebraic tori}
 \date{\today}
@@
 \newcommand{\iso}{{\ \cong\ }}
+\newcommand{\dual}[1]{{\hat{#1}}}
 %% Limits
@@
   and any algebraic torus $T$ over $K$, we use the
-  function--sheaf dictionary for smooth group schemes locally of finite type over finite fields
+  function--sheaf dictionary for smooth group schemes over finite fields
   to geometrize quasicharacters of $T(K)$
@@
   model of $T$.
- As an application, we find a categorical transfer of certain characters between characteristic-$p$ tori and characteristic-$0$ tori.
+ We offer two applications of this geometrization:
+ a categorical transfer of quasicharacters between characteristic-$p$ tori and
+ characteristic-$0$ tori; and a geoemtric proof of the local Langlands correspondence for algebraic tori.
   \end{abstract}
@@
 
-We explain how to geometrize quasicharacters of algebraic tori over local fields.  
+In this paper we explain how to geometrize quasicharacters of algebraic tori over local fields.
 %
@@
 Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^n}$.
-Then $\GN{T}_n$ is a commutative group scheme locally of finite type over $\Fq$ with finitely generated geometric component group, and as such, it carries the category $\QCiso{\GN{T}_n}$ of quasicharacter sheaves, introduced in \cite{cunningham-roe:dictionary}.
+Then $\GN{T}_n$ is a smooth commutative group scheme over $\Fq$; as such, it carries the category $\QC(\GN{T}_n)$ of quasicharacter sheaves, introduced in \cite{cunningham-roe:dictionary}.
 The main result in this paper, Theorem~\ref{thm:application}, provides a functorial translation of characters $T(K)$ of depth less than $n$ into quasicharacter sheaves on $\GN{T}_n$:
@@
 simultaneously geometrizing all quasicharacters ({\it i.e.}, finite-depth characters) of $T(K)$.
+
+\[
+\begin{tikzcd}
+\ & \arrow[swap]{dl}{\trFrob{G}} \QCiso{\GN{T}} \arrow[dashed]{dr} & \\
+\Hom_{\text{qc}}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(K,\hat{T}_\ell)
+\end{tikzcd}
+\]
 
@@
 allow us to define the depth of character $\chi$ as the infimum of the $r$ so that $\chi$ vanishes on $T(K)_r$.
-We write $\Hom_{< n}(T(K),\EEx)$ for the group of characters of $T(K)$ depth less than $n$ 
-and $\Hom_{\text{qc}}(T(K),\EEx)$ for the group of characters of $T(K)$ of arbitrary finite depth;
+We write
+\[
+\Hom_{< n}(T(K),\EEx)
+\]
+for the group of characters of $T(K)$ depth less than $n$
+and
+\[
+\Hom_{\text{qc}}(T(K),\EEx)
+\]
+for the group of characters of $T(K)$ of arbitrary finite depth;
 we call these quasicharacters of $T(K)$, following \cite{tate:67a}*{2.3}.
@@
 The multiplication maps $m_n : \GN{T}_n \times \GN{T}_n \to \GN{T}_n$ induce maps of affine schemes
-$m_n^{i,j} : \GN{T}_n^i \times \GN{T}_n^j \to \GN{T}_n^{i+j},$ inducing maps $m^{i,j} : \GN{T}^i \times \GN{T}_
-
+$m_n^{i,j} : \GN{T}_n^i \times \GN{T}_n^j \to \GN{T}_n^{i+j},$ inducing maps $m^{i,j} : \GN{T}^i \times \GN{T}$ [under construction]
 \end{proof}
 
-\section{The function--sheaf dictionary}\label{sec:qcs}
+\section{The function--sheaf dictionary for quasicharacters of bounded depth}\label{sec:qcs}
 
@@
 \end{equation}
-  is an isomorphism of groups.
+  is a functorial isomorphism of groups \cite{cunningham-roe:dictionary}*{Thm. 11.1}.
 
-\section{Application to quasicharacters of bounded depth} \label{sec:bdchar}
+%\section{Application to quasicharacters of bounded depth} \label{sec:bdchar}
 
-We now apply the results of Section~\ref{sec:qcs} to characters of $T(K)$.
+%We now apply the results of Section~\ref{sec:qcs} to characters of $T(K)$.
 
@@
 
-\section{A function--sheaf dictionary for tori over local fields} \label{sec:quasichar}
+\section{A function--sheaf dictionary for quasicharacters} \label{sec:quasichar}
 
@@
 \end{document}
+%sagemathcloud={"zoom_width":90}

### 2014-05-30 dictionary.tex
Working on geometrization

@@
 \begin{proposition}\label{prop:basechange}
- The rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$
+With notation above,
+the rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$
  defines a monoidal functor $\QC(G) \to \QC(G_{k'})$.
@@
 \end{proposition}
+
+\todo{The bottom arrow is an isomorphism to $G(k')^*_{\Gal(k'/k)}$.
+We will see that the horizontal arrows are isomorphisms on loose quasicharacter sheaves.
+Can we make sense of $\QC(G_{k'})_{\Gal(k'/k)}$?
+If so, is the functor $\nu_{k'/k}$ into $\QC(G_{k'})_{\Gal(k'/k)}$ an equivalence of categories?}
+
 \begin{proof}
@@
 \begin{proposition}
+Let $k'/k$ be a finite extension and let $G'$ be a smooth commutative group scheme over $k'$.
 The following diagram of isomorphisms commutes, where the bottom map is the identity:
@@
 \end{proof}
+
+\todo{Can we improve on this result by proving that $\rho$
+is an equivalence of categories?}
 
@@
 \]
-of abelian groups.
+of abelian groups.\todo{Pure speculation.}
 \end{corollary}

### 2014-05-30 geometrization.tex
Working on geometrization

@@
 % AMS packages
-\usepackage{amsmath, amsthm, amssymb}
+\usepackage{amsmath, amsthm, amssymb, geometry}
 \usepackage[alphabetic]{amsrefs}
@@
 \hyphenation{quasi-character}
-
+\hyphenation{quasi-characters}
 %%%%%%%%%%%% BEGIN DOCUMENT %%%%%%%%%%%%
@@
 
-In this paper we explain how to geometrize quasicharacters of algebraic tori over local fields.
-%
-Let $K$ be a non-archimedian local field
-with finite residue field $\Fq$; we place no restriction on the characteristic of $K$.
-Write $\OK$ for the ring of integers of $K$ and $\pK$ for the maximal ideal in $\OK$.
-Let $T$ be a torus defined over $K$.  The N\'eron model $\TT$ of $T$
-is a smooth group scheme over $\OK$ with generic fibre $T$ and a canonical isomorphism
-$\TT(\OK) \cong T(K)$.  For each positive integer $n$, let $\GN{T}_n$ be the
-Greenberg transform of $\TT \times_{\Spec{\OK}} \Spec{\OK/\pK^n}$.
-Then $\GN{T}_n$ is a smooth commutative group scheme over $\Fq$; as such, it carries the category $\QC(\GN{T}_n)$ of quasicharacter sheaves, introduced in \cite{cunningham-roe:dictionary}.
-The main result in this paper, Theorem~\ref{thm:application}, provides a functorial translation of characters $T(K)$ of depth less than $n$ into quasicharacter sheaves on $\GN{T}_n$:
+This paper provides a geometric proof of the local Langlands Correspondence for algebraic tori.
+The new ingredient in this proof is the geometrization of quasicharacters of algebraic tori over local fields,
+which relies on the function--sheaf dictionary for smooth group schemes over finite fields developed recently by the authors.
+We also use the class field theory of Serre and Hasewinkel.
+
+Here is the main idea of the paper.
+Let $K$ be a non-Archimedean local field with finite residue field $\Fq$; we place no restriction on the characteristic of $K$.
+Let $T$ be an algebraic torus over $K$; we place no restriction on the ramification of $T$.
+For every positive integer $n$, let $\GN{T}_n$ be the Greenberg transform of base change of the Neron model of $T$ to $\OK/\pK^n$,
+where $\OK$ denotes the ring of integers of $K$ and $\pK$ is the maximal ideal in $\OK$.
+Let $\QC(\GN{T}_n)$ be the rigid monoidal category of quasicharacter sheaves on $\GN{T}_n$,
+obtained by applying the theory developed in [CR1] to the smooth commutative group scheme $\GN{T}_n$ over $\Fq$.
+The category $\QC(\GN{T}_n)$ comes equipped with a canonical isomorphism
 \[
-\QCiso{\GN{T}_n}
-\iso
-\Hom_{< n}(T(K),\EEx).
+\QCiso{\GN{T}_n} \to \Hom_{n}(T(K),\EEx)
 \]
-We also describe a pro-group scheme $\GN{T}$
-simultaneously geometrizing all quasicharacters ({\it i.e.}, finite-depth characters) of $T(K)$.
-
+from the group of isomorphisms classes of quasicharacter sheaves on $\GN{T}_n$ to the group of quasicharacters of $T(K)$ of depth less than $n$ in Jiu-Kang Yu's filtration of $T(K)$.
+In this paper we define a canonical isomorphism
+\[
+\QCiso{\GN{T}_n} \to H^1_{n}(\Weil{K},\hat{T}_\ell)
+\]
+to the group of Langlands parameters of depth less than $n$ in the upper-index filtration of the Weil group $\Weil{K}$.
+We then verify that the local Langlands Correspondence matches $\chi \in \Hom_{n}(T(K),\EEx)$ with $\rho \in H^1_{n}(K,\hat{T}_\ell)$ if and only if $\chi$ and $\rho$ arise from the same quasicharacter sheaf on $\GN{T}_n$.
+After passing from $\GN{T}_n$ to the group scheme $\GN{T} = \invlim{n} \GN{T}_n$, this shows that the local Langlands Correspondence for $T$ can be found within the category $\QC(\GN{T})$ of quasicharacter sheaves on $\GN{T}$.
 \[
 \begin{tikzcd}
-\ & \arrow[swap]{dl}{\trFrob{G}} \QCiso{\GN{T}} \arrow[dashed]{dr} & \\
-\Hom_{\text{qc}}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(K,\hat{T}_\ell)
+\ & \arrow[swap]{dl}{} \QCiso{\GN{T}} \arrow{dr}{} & \\
+\Hom_\text{qc}(T(K),\EEx) \arrow{rr}{\text{rec}_T} && H^1(\Weil{K},\hat{T}_\ell)
 \end{tikzcd}
@@
 
+\subsection*{Old stuff}
 While we have not yet fully explored the applications of such a geometrization, we want to highlight
@@
 
-\section{Quasicharacters of algebraic tori over local fields}
+\section{The geometrization of quasicharacters of algebraic tori over local fields}
+
+\subsection{Notations}
 
@@
 
-\section{Greenberg of N\'eron}
+\subsection{Greenberg of N\'eron}
 \label{sec:GN}
@@
 
-\section{The function--sheaf dictionary for quasicharacters of bounded depth}\label{sec:qcs}
+\subsection{The function--sheaf dictionary for quasicharacters of bounded depth}\label{sec:qcs}
 
-In \cite{cunningham-roe:dictionary} we extended the function--sheaf dictionary of Deligne  \cite{deligne:SGA4.5}*{sommes trig.} to smooth commutative group schemes locally of finite type over finite fields for which the geometric component group is finitely generated.
+In \cite{cunningham-roe:dictionary} we extended the function--sheaf dictionary of Deligne  \cite{deligne:SGA4.5}*{sommes trig.} to smooth commutative group schemes over finite fields.
 Since we will use this dictionary here, we briefly review the main notation and result from that paper.
 
-Let $G$ be a smooth commutative group schemes locally of finite type over $\Fq$ for which the geometric component group is finitely generated. A quasicharacter sheaf on $G$ is a triple $\qcs{L}\ceq
+Let $G$ be a smooth commutative group scheme over $\Fq$ for which the geometric component group is finitely generated. A quasicharacter sheaf on $G$ is a triple $\qcs{L}\ceq
 (\gqcs{L},\mu,\phi)$ where $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ of rank~one and $\mu: m^*
@@
 
-\section{A function--sheaf dictionary for quasicharacters} \label{sec:quasichar}
+\subsection{A function--sheaf dictionary for quasicharacters} \label{sec:quasichar}
 
@@
 
-\section{Restriction of scalars over local fields}
+\subsection{Application: Transfer of quasicharacter sheaves} \label{sec:transfer}
+
+The techniques in this paper apply to all non-archimdean local fields $K$ with residue field $k$
+and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$
+or on the ramification of $T$.
+We may therefore ask for a comparison of
+quasicharacter sheaves on $T$ and on $T'$ whenever there is a relationship
+between characters of $T(K)$ and of $T'(K')$.
+Such a relationship can exist between characters of $T(K)$ and $T'(K')$ even
+when the characteristics of $K$ and $K'$ differ
+\citelist{\cite{chai-yu:01a} \cite{deligne:84a}*{\S 1}}.
+
+We recall the notion of $N$-congruent tori from \cite{chai-yu:01a}*{\S 2}.
+Suppose $T$ and $T'$ are tori over non-archimedian local fields $K$ and $K'$,
+splitting over $L$ and $L'$ respectively.
+Then $T$ and $T'$ are said to be \emph{$N$-congruent} if there are isomorphisms
+ \begin{align*}
+  \alpha : \OL/\pi_K^N \OL &\to \OO{L'}/\pi_{K'}^N \OO{L'} \\
+  \beta : \Gal(L/K) &\to \Gal(L'/K') \\
+  \phi : X^*(T) &\to X^*(T')
+ \end{align*}
+ satisfying the conditions
+ \begin{enumerate}
+  \item $\alpha$ induces an isomorphism $\OK/\pi_K^N \OK \to \OO{K'}/\pi_{K'}^N \OO{K'}$,
+  \item $\alpha$ is $\Gal(L/K)$-equivariant relative to $\beta$, and
+  \item $\phi$ is $\Gal(L/K)$-equivariant relative to $\beta$.
+ \end{enumerate}
+If $T$ and $T'$ are $N$-congruent then $\alpha$, $\beta$ and $\phi$ determine an isomorphism
+\begin{equation}\label{transfer}
+  \Hom_{<N}(T(K), \EEx) \iso \Hom_{<N}(T'(K'),\EEx).
+\end{equation}
+Note that if $T$ and $T'$ are $N$-congruent, then they are $N'$ congruent for every
+$N' \leq N$, the isomorphism \eqref{transfer} is depth-preserving at integers less than $N$.
+In this section we show that the isomorphism \eqref{transfer} comes from an equivalence of
+categories of quasicharacter sheaves on $\GN{T}_n$ and those on $\GN{T}'_n$.
+
+One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes between
+$\TT_n$ and $\TT'_n$ assuming that $T$ and $T'$ are sufficiently congruent.
+They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the
+Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}.
+Then it follows from \cite{chai-yu:01a}*{Thm. 8.5} that if $N > 3h$ and $T$ and $T'$ are $N$-congruent
+then there is a canonical isomorphism of smooth group schemes
+ $
+  \TT_{N-3h} \to \TT'_{N-3h}
+ $
+ determined by $\alpha, \beta$ and $\phi$.
+Combining this with Theorem~\ref{thm:application} gives the geometrization and categorification of the transfer of characters.
+
+\begin{corollary}\label{cor:transfer}
+ With notation above, suppose that $T$ and $T'$ are $N$-congruent and $N > 3h$.  Set $n \ceq N-3h$.
+ Then there is a canonical equivalence of categories
+ \[
+  \QC(\GN{T}'_{n}) \to \QC(\GN{T}_{n})
+ \]
+ determined by $\alpha, \beta$ and $\phi$ inducing the isomorphism
+ \[
+  \Hom_{<n}(T'(K'), \EEx) \to \Hom_{<n}(T(K), \EEx)
+ \]
+ through the trace of Frobenius.
+\end{corollary}
+
+\subsection{Restriction of scalars over local fields}
 \label{sec:wrK}
@@
 
-\section{Transfer of quasicharacter sheaves} \label{sec:transfer}
+\section{Parameters from quasicharacter sheaves}
 
-The techniques in this paper apply to all non-archimdean local fields $K$ with residue field $k$
-and to all algebraic tori $T$ over $K$, without placing any restrictions on the characteristic of $K$
-or on the ramification of $T$.
-We may therefore ask for a comparison of
-quasicharacter sheaves on $T$ and on $T'$ whenever there is a relationship
-between characters of $T(K)$ and of $T'(K')$.
-Such a relationship can exist between characters of $T(K)$ and $T'(K')$ even
-when the characteristics of $K$ and $K'$ differ
-\citelist{\cite{chai-yu:01a} \cite{deligne:84a}*{\S 1}}.
+The component group scheme $\pi_0(\GN{T}_n)$, which is independent of $n$, is defined by the short exact sequence
+\[
+\begin{tikzcd}
+0 \arrow{r} & \GN{T}_n^0 \arrow{r}{\iota_0} & \GN{T}_n \arrow{r}{\pi_0} & \pi_0(\GN{T}_n) \arrow{r} & 0.
+\end{tikzcd}
+\]
+As we saw in [CR], this exact sequence of smooth commutative group schemes defines an isomorphism of exact sequences of commutative groups
+\[
+\begin{tikzcd}
+0 \arrow{r} & \QCiso{\pi_0(\GN{T}_n)} \arrow{r}{\pi_0^*} \arrow{d} & \QCiso{\GN{T}} \arrow{r}{\iota^*} \arrow{d} &  \QCiso{\GN{T}_n^0} \arrow{r} \arrow{d} & 0\\
+0 \arrow{r} & \Hom(\pi_0(\GN{T}_n)(\Fq),\EEx) \arrow{r} & \Hom(\GN{T}_n(\Fq),\EEx) \arrow{r} & \Hom(\GN{T}_n^0(\Fq),\EEx) \arrow{r} & 0
+\end{tikzcd}
+\]
+We have already seen $\Hom(\GN{T}_n(\Fq),\EEx) = \Hom_{<n}(T(K),\EEx)$;
+by similar arguments,
+\[
+\Hom(\GN{T}^0_n(\Fq),\EEx) = \Hom_{<n}(T(\OK),\EEx).
+\]
+Consequently,
+\[
+\Hom(\pi_0(\GN{T}_n)(\Fq),\EEx) = \Hom(T(K)/T(\OK),\EEx).
+\]
+Our goal in the next three sections is to define the three dashed arrows below in the diagram below, in which the bottom row is the inflation-restriction sequence with the initial and terminal groups elided.
+\[
+\begin{tikzcd}[column sep=-5, row sep = 20]
+&& & \arrow{dl} \QCiso{\pi_0(\GN{T}_n)} \arrow{rr} \arrow[dashed]{dd}[near start]{?} && \arrow{dl}  \QCiso{\GN{T}_n} \arrow[dashed]{dd}[near start]{?} \arrow{rr}  && \arrow{dl}  \QCiso{\GN{T}_n^\circ} \arrow[dashed]{dd}[near start]{?}  &  &  \\
+&& \Hom(T(K)/T(\OK),\EEx)  \arrow[crossing over]{rr} \arrow{rd}{} && \Hom_{<n}(T(K),\EEx) \arrow[crossing over]{rr} \arrow{rd}{\text{rec}_T} && \Hom_{<n}(T(\OK),\EEx)  \arrow{rd}{}  &&  & \\
+&&  & \Hh^1(\Weil{\Fq},\hat{T}_\ell^{I_K}) \arrow{rr} && \Hh^1_{<n}(\Weil{K},\hat{T}_\ell)\arrow{rr} && \Hh^1_{<n}(I_K,\hat{T}_\ell)^{\Weil{\Fq}} &  &
+\end{tikzcd}
+\]
 
-We recall the notion of $N$-congruent tori from \cite{chai-yu:01a}*{\S 2}.
-Suppose $T$ and $T'$ are tori over non-archimedian local fields $K$ and $K'$,
-splitting over $L$ and $L'$ respectively.
-Then $T$ and $T'$ are said to be \emph{$N$-congruent} if there are isomorphisms
- \begin{align*}
-  \alpha : \OL/\pi_K^N \OL &\to \OO{L'}/\pi_{K'}^N \OO{L'} \\
-  \beta : \Gal(L/K) &\to \Gal(L'/K') \\
-  \phi : X^*(T) &\to X^*(T')
- \end{align*}
- satisfying the conditions
- \begin{enumerate}
-  \item $\alpha$ induces an isomorphism $\OK/\pi_K^N \OK \to \OO{K'}/\pi_{K'}^N \OO{K'}$,
-  \item $\alpha$ is $\Gal(L/K)$-equivariant relative to $\beta$, and
-  \item $\phi$ is $\Gal(L/K)$-equivariant relative to $\beta$.
- \end{enumerate}
-If $T$ and $T'$ are $N$-congruent then $\alpha$, $\beta$ and $\phi$ determine an isomorphism
-\begin{equation}\label{transfer}
-  \Hom_{<N}(T(K), \EEx) \iso \Hom_{<N}(T'(K'),\EEx).
-\end{equation}
-Note that if $T$ and $T'$ are $N$-congruent, then they are $N'$ congruent for every
-$N' \leq N$, the isomorphism \eqref{transfer} is depth-preserving at integers less than $N$.
-In this section we show that the isomorphism \eqref{transfer} comes from an equivalence of
-categories of quasicharacter sheaves on $\GN{T}_n$ and those on $\GN{T}'_n$.
+\subsection{Component group}
 
-One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes between
-$\TT_n$ and $\TT'_n$ assuming that $T$ and $T'$ are sufficiently congruent.
-They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the
-Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}.
-Then it follows from \cite{chai-yu:01a}*{Thm. 8.5} that if $N > 3h$ and $T$ and $T'$ are $N$-congruent
-then there is a canonical isomorphism of smooth group schemes
- $
-  \TT_{N-3h} \to \TT'_{N-3h}
- $
- determined by $\alpha, \beta$ and $\phi$.
-Combining this with Theorem~\ref{thm:application} gives the geometrization and categorification of the transfer of characters.
+There is another description of $\Hom(\pi_0(\GN{T}_n)(\Fq),\EEx)$ which leads easily to Langlands parameters for $T$:
+\begin{eqnarray*}
+\Hom(\pi_0(\GN{T}_n)(\Fq),\EEx)
+&\iso & \Hom(\left(X_*(T)_{I_K}\right)^{\Weil{\Fq}},\EEx)\\
+&\iso& \Hom(X_*(T)_{I_K},\EEx)_{\Weil{\Fq}}\\
+&=& \Hh^1(\Weil{\Fq}, \Hom(X_*(T)_{I_K},\EEx)) \\
+&\iso& \Hh^1(\Weil{\Fq}, \Hom(X_*(T),\EEx)^{I_K}) \\
+&=& \Hh^1(\Weil{\Fq}, (X^*(T)\otimes_{\ZZ} \EEx)^{I_K}) \\
+&=& \Hh^1(\Weil{\Fq}, \dual{T}_\ell^{I_K}).
+\end{eqnarray*}
 
-\begin{corollary}\label{cor:transfer}
- With notation above, suppose that $T$ and $T'$ are $N$-congruent and $N > 3h$.  Set $n \ceq N-3h$.
- Then there is a canonical equivalence of categories
- \[
-  \QC(\GN{T}'_{n}) \to \QC(\GN{T}_{n})
- \]
- determined by $\alpha, \beta$ and $\phi$ inducing the isomorphism
- \[
-  \Hom_{<n}(T'(K'), \EEx) \to \Hom_{<n}(T(K), \EEx)
- \]
- through the trace of Frobenius.
-\end{corollary}
+\subsection{Connected component}
 
-\section{Toward geometric reciprocity for tori over local fields}
+\subsection{General case}
+
+\section{Geometric reciprocity for tori over local fields}
 \label{sec:reciprocity}
@@
 \end{document}
-%sagemathcloud={"zoom_width":90}
+%sagemathcloud={"zoom_width":100}

### 2014-06-11 dictionary.tex
Updating spectral sequences material

@@
 %% Categories
-\newcommand{\QC}{{\mathcal{Q\hskip-0.8pt C}}}
-\newcommand{\QCb}{{\QC_0}}
-\newcommand{\QCf}{{\QC_f}}
+\newcommand{\lQC}{{\mathcal{Q\hskip-0.8pt C}}}
+\newcommand{\lQCiso}[1]{\lQC(#1)_{/\text{iso}}}
+\newcommand{\QC}{{\lQC_\mu}}
+\newcommand{\QCb}{{\lQC_0}}
+\newcommand{\QCf}{{\lQC_f}}
 \newcommand{\QCiso}[1]{\QC(#1)_{/\text{iso}}}
@@
 
-\newcommand{\lQC}{{\mathcal{Q\hskip-0.8pt C}^2}}
-\newcommand{\lQCiso}[1]{\lQC(#1)_{/\text{iso}}}
 \newcommand{\lTrFrob}[1]{\TrFrob{#1}^2}
@@
 %
-Although hidden in this discussion, the connectness of $G$ played a crucial role in the geometrization and categorification of characters of $G(\Fq)$.
+Although hidden in this discussion, the connectedness of $G$ played a crucial role in the geometrization and categorification of characters of $G(\Fq)$.
 In particular, when the isomorphism \eqref{introbox} exists for $\qcs{L}$, it is essentially unique.
@@
 Both issues are addressed in the main definition of this paper:
-A \emph{(tight) quasicharacter sheaf} on $G$ is a triple $\qcs{L}\ceq
+A \emph{rigid quasicharacter sheaf} on $G$ is a triple $\qcs{L}\ceq
 (\gqcs{L},\mu,\phi)$ where $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ of rank~one and $\mu: m^*
-\gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms satisfying natural compatibilty conditions; here $\Frob{G}$ is the Frobenius automorphism of ${\bar G}$.
-A \emph{(loose) quasicharacter sheaf} on $G$ is a Weil sheaf $(\gqcs{L},\phi)$ on $G$
-for which $(\gqcs{L},\mu,\phi)$ is a tight quasicharacter sheaf on $G$, for some $\mu$.
+\gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms satisfying natural compatibility conditions; here $\Frob{G}$ is the Frobenius automorphism of ${\bar G}$.
+A \emph{quasicharacter sheaf} on $G$ is a Weil sheaf $(\gqcs{L},\phi)$ on $G$
+for which $(\gqcs{L},\mu,\phi)$ is a rigid quasicharacter sheaf on $G$, for some $\mu$.
 The difference between these two notions is detected by $\Hh^2(\pi_0({\bar G}),\EEx)$, where $\pi_0({\bar G})$ is the component group for ${\bar G}$.
-%namely, when $\Hh^2(\pi_0({\bar G}),\EEx)$ is non-trivial, if $(\gqcs{L},\phi)$ is a (loose) quasicharacter sheaf on $G$ then there are many $\mu$ for which $(\gqcs{L},\mu,\phi)$ is a (tight) quasicharacter sheaf on $G$;
+%namely, when $\Hh^2(\pi_0({\bar G}),\EEx)$ is non-trivial, if $(\gqcs{L},\phi)$ is a quasicharacter sheaf on $G$ then there are many $\mu$ for which $(\gqcs{L},\mu,\phi)$ is a rigid quasicharacter sheaf on $G$;
 %
  In the main result of this paper, Theorem~\ref{thm:snake},
-we form a rigid monoidal category $\lQC(G)$ of (loose) quasicharacter sheaves on $G$
+we form a rigid monoidal category $\lQC(G)$ of quasicharacter sheaves on $G$
 and show that the Trace of Frobenius provides a functorial group isomorphism
@@
 Section~\ref{sec:snake} presents the main theorem of this paper: Trace of Frobenius
-is a functorial isomorphism from isomorphism classes of (loose) quasicharacter sheaves on $G$
+is a functorial isomorphism from isomorphism classes of quasicharacter sheaves on $G$
 to characters of $G(\Fq)$.
@@
 %\begin{acknowledgements}
-\subsection*{Acknowledgements}
+\subsection*{Acknowledgments}
 We thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
@@
 and the National Science and Engineering Research Council,
-as well the hospitality of the Banff International Research Station during our weeklong stay in May 2012.
+as well the hospitality of the Banff International Research Station during our week-long stay in May 2012.
 
@@
 
-\subsection{(tight) quasicharacter sheaves}\label{sec:category}
+\subsection{Rigid quasicharacter sheaves}\label{sec:category}
 
 \begin{definition}\label{def:QC}
-A \emph{(tight) quasicharacter sheaf on $G$} is a triple
+A \emph{rigid quasicharacter sheaf on $G$} is a triple
 $\qcs{L}\ceq (\gqcs{L},\mu,\phi)$ where:
@@
 %\begin{definition}\label{def:trFrob}
-We will refere to the function
+We will refer to the function
 \begin{align*}
@@
 \todo{The bottom arrow is an isomorphism to $G(k')^*_{\Gal(k'/k)}$.
-We will see that the horizontal arrows are isomorphisms on loose quasicharacter sheaves.
+We will see that the horizontal arrows are isomorphisms on quasicharacter sheaves.
 Can we make sense of $\QC(G_{k'})_{\Gal(k'/k)}$?
@@
  given on objects by $(f,\psi) \mapsto (L(f,\psi), L_{W}(\mu(f,\psi)))$,
- is a full and faithfull monoidal functor, completing the proof.
+ is a full and faithful monoidal functor, completing the proof.
 \end{proof}
@@
 with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group.
-Under this equivalence, a (tight) quasicharacter sheaf on an etale commutative group scheme $G$ over $\Fq$ is given by the data of:
+Under this equivalence, a rigid quasicharacter sheaf on an etale commutative group scheme $G$ over $\Fq$ is given by the data of:
 \begin{enumerate}
@@
 \begin{enumerate}
- \labitem{(qc.4)}{qc.4} an indexed set $\alpha_x : \gqcs{L}_x \to \gqcs{L'}_x$
+ \labitem{(qc.4)}{qc.4} an indexed set $\rho_x : \gqcs{L}_x \to \gqcs{L'}_x$
   of linear transformations such that
@@
    \begin{tikzcd}[column sep=40]
-    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{}(x)} \rar{\alpha_{\Frob{}(x)}} & \gqcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
+    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{}(x)} \rar{\rho_{\Frob{}(x)}} & \gqcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
     &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-    & \arrow[swap]{d}{\mu} \gqcs{L}_{x+y} \rar{\alpha_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
-    \gqcs{L}_x \rar{\alpha_x} & \gqcs{L'}_x
-    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\alpha_x\otimes\alpha_y} & \gqcs{L'}_x \otimes\gqcs{L'}_y
+    & \arrow[swap]{d}{\mu} \gqcs{L}_{x+y} \rar{\rho_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
+    \gqcs{L}_x \rar{\rho_x} & \gqcs{L'}_x
+    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\rho_x\otimes\rho_y} & \gqcs{L'}_x \otimes\gqcs{L'}_y
    \end{tikzcd}
@@
 We will see that the Trace of Frobenius may not provide complete
-information about isomorphism classes of tight quasicharacter sheaves on $G$ when $G$ is not a connected algebraic group.
+information about isomorphism classes of rigid quasicharacter sheaves on $G$ when $G$ is not a connected algebraic group.
 Our main tool for understanding this phenomenon
@@
 
-\subsection{Cohomology}\label{sec:E}
-
-[Can this section be written in such a way that the effect of removing the fact $\Hh^2(\Weil{}, - ) =0$ can be discerned?]
-
-Define $\Hh^2(E^\bullet_G)$. \todo{David, I need some help here.}
-
-\subsection{A short exact sequence}\label{sec:SES}
-
+\subsection{A spectral sequence}\label{sec:E}
+
+The zeroth page of the Hochschild-Serre spectral sequence is a double complex $E^{\bullet, \bullet}$ defined by
+\[
+E^{i,j} = C^i(\Weil{}, C^j(G(\bFq), \EEx)),
+\]
+The derivative of group cohomology yields two derivatives:
+\begin{align*}
+d_0 = d_G &: E^{i,j} \to E^{i,j+1} \\
+d_{\Weil{}} &: E^{i,j} \to E^{i+1,j}.
+\end{align*}
+Combining these yields a derivative $d = d_G + (-1)^j d_{\Weil{}}$ on the total complex
+\[
+E^n_G = \bigoplus_{i+j=n} E^{i,j}.
+\]
+The machinery of spectral sequences gives us a sequence of pages $E_r^{i,j}$, converging to a page $E_{\infty}^{i,j}$.
+We summarize the key properties of this spectral sequence in the following proposition.
+
+\begin{proposition}
+\begin{enumerate}
+\item The second page is given by $E_2^{i,j} = \Hh^i(\Weil{}, \Hh^j(G(\bFq), \EEx))$,
+\item there is an isomorphism $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) \cong \Hh^n(E_G^\bullet)$,
+\item there is a filtration $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) = F_n \supset \cdots \supset F_0 \supset F_{-1} = 0$ where $F_i / F_{i-1} \cong E_{\infty}^{i, n-i}$.
+\end{enumerate}
+\end{proposition}
+
+Moreover, since $\Weil{} \cong \ZZ$ has cohomological dimension $1$, $E_2^{i,j} = 0$ for $i > 1$ and the sequence degenerates at the second page: $E_{\infty}^{i,j} = E_2^{i,j}$.
+We obtain the following corollary:
+
+\begin{corollary}
+There is a short exact sequence
  \[
@@
  \]
-\todo{Again, I hope you can write this section, David.}
-
-\subsection{Map to cohomology}\label{sec:S}
-
-In this section we define
+\end{corollary}
+
+This sequence will play a key role in understanding the kernel of $T_G$, as described in the next few sections.
+For this application, we need a good understanding of these maps to and from the total complex.
+
+\begin{proposition} \label{prop:ses_desc}
+\begin{enumerate}
+\item Every class $[\alpha\oplus\beta\oplus\gamma] \in \Hh^2({\bar G},\EEx)$ is cohomologous to one with $\gamma=0$.
+\item The map $\Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx))$ is given by $[\alpha\oplus\beta\oplus 0] \mapsto [\beta]$.
+\item Suppose $a \in Z^2({\bar G}, \EEx)$ represents a class in $\Hh^2({\bar G},\EEx)$ fixed by Frobenius.
+The map $\Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to \Hh^2(E^\bullet_G)$ is given by $[a] \mapsto [a \oplus 0 \oplus 0]$.
+\end{enumerate}
+\end{proposition}
+\begin{proof}
+Since $\Hh^2(\Weil{}, C^0({\bar G}, \EEx)) = 0$, we may find a $\gamma_1 \in C^1(\Weil{}, C^0({\bar G}, \EEx))$ with $d_{\Weil{}}\gamma_1 = \gamma$.
+Subtracting $d \gamma_1$ from $\alpha\oplus\beta\oplus\gamma$, we may assume that $\gamma = 0$.
+
+The latter two claims follow from tracing through the definition of latter pages in the spectral sequence; see Vakil \cite{} for example.
+\end{proof}
+
+\subsection{From quasicharacter sheaves to the total complex}\label{sec:S}
+
+In this section we define an isomorphism
 \[
@@
 For each geometric point $x\in {\bar G}$, choose a basis $\{ v_x \}$ for $\gqcs{L}_x$.
-Through this choice, $\qcs{L}$ determines a function $a : {\bar G}\times {\bar G} \to \EEx$ defined by
-\[
-\mu_{x,y}(v_{x+y}) = a(x,y) v_x \otimes v_y.
-\]
-Condition~\ref{QC.2} gives
+Through this choice, $\qcs{L}$ determines functions
+\begin{align*}
+a : {\bar G}\times {\bar G} &\to \EEx & b : {\bar G} &\to \EEx \\
+\mu_{x,y}(v_{x+y}) &= a(x,y) v_x \otimes v_y & \phi_x(v_{\Frob{G}(x)}) &= b(x) v_x.
+\end{align*}
+Condition~\ref{QC.2} implies that
 \begin{equation}\label{2-cocyle}
-\forall x,y,z\in {\bar G},\qquad a(x+y,z) a(x,y) = a(x,y+z) a(y,z),
+a(x+y,z) a(x,y) = a(x,y+z) a(y,z)
 \end{equation}
-so $a \in Z^2({\bar G},\EEx)$.
-Likewise, through the choice
-$\{ v_x\in \gqcs{L}_x^\times \tq x \in {\bar G}\}$, $\qcs{L}$
-determines a function $b : {\bar G} \to \EEx$
-defined by
-\[
-\phi_x(v_{\Frob{G}(x)}) = b(x) v_x.
-\]
-(Observe: $b\vert_{G(\Fq)} = t_\qcs{L}$,
-which is independent of the choice of $\{ v_x \in \gqcs{L}_x^\times \tq x\in {\bar G}\}$.)
-Condition~\ref{QC.3} gives
+for all $x,y,z\in {\bar G}$, so $a \in Z^2({\bar G},\EEx)$.  Similarly, condition~\ref{QC.3} gives
 \begin{equation}\label{nohom}
-\forall x,y \in {\bar G},\qquad \frac{a(\Frob{G}(x),\Frob{G}(y))}{a(x,y)} =  \frac{b(x+y)}{b(x) b(y)}.
+\frac{a(\Frob{G}(x),\Frob{G}(y))}{a(x,y)} =  \frac{b(x+y)}{b(x) b(y)}
 \end{equation}
-Let $\alpha \in C^0(\Weil{},C^2({\bar G},\EEx)$ be the cocycle corresponding to $a$ and let $\beta\in C^1(\Weil{},C^1({\bar G},\EEx)$ be the cocycle such that $\beta(\Frob{})$ is $b$ \emph{written additively}.
+for $x, y \in {\bar G}$.
+Let $\alpha \in C^0(\Weil{},C^2({\bar G},\EEx)$ be the $0$-cochain corresponding to $a$ and let $\beta\in C^1(\Weil{},C^1({\bar G},\EEx)$ be the cocycle such that $\beta(\Frob{})$ is $b$ \emph{written additively}.
 Then
 \[
-d_{\uparrow}\alpha =0, \qquad
-d_{\rightarrow} \alpha = d_{\uparrow} \beta,\qquad
-d_{\rightarrow} \beta =0;
+d_G\alpha =0, \qquad\qquad
+d_{\Weil{}} \alpha = d_{G} \beta,\qquad\qquad
+d_{\Weil{}} \beta =0;
 \]
@@
 Although we will only use the group homomorphism $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$.
-However, the main result of the next section, Proposition~\ref{prop:etale-iso}, is false in that context.
+However, the next result is false in that context.
 \end{remark}
 
+\begin{proposition}
+If $G$ is \'etale then $S_G$ is an isomorphism.
+\end{proposition}
+\begin{proof}
+We first show that $S_G$ is injective.  Suppose $\qcs{L} \in \QCiso{G}$ with $S_G(\qcs{L}) = [\alpha \oplus \beta] = 0$,
+so that $\alpha \oplus \beta = d\rho$ for some $\rho \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
+For each $x\in {\bar G}$, define $\rho_x : \gqcs{L}_x \to \EEx$ by $v_x \mapsto \rho(x)$.
+Then the indexed set of isomorphisms $\{ \gamma_x : \gqcs{L}_x \to \EE \tq x\in {\bar G}\}$
+defines an isomorphism $\qcs{L} \to (\EE)_G$.
+Since $\qcs{L} = 0 \in \QCiso{G}$, $S_G$ is injective.
+
+To see that $S_G$ is surjective, begin with $\alpha\oplus\beta\oplus 0 \in Z^2(E^\bullet_G)$.
+Since $d_{\Weil{}} \beta = 0$, we may define $a = \alpha \in C^2({\bar G},\EEx)$ and
+$b = \beta(\Frob{}) \in C^1({\bar G},\EEx)$, which are related to $\alpha$ and $\beta$ as above.
+Set $\gqcs{L}_x = \EEx$, define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes\gqcs{L}_y$
+by $\mu_{x,y}(1) = a(x,y) 1\otimes 1$ and $\phi_x : \gqcs{L}_{\Frob{G}(x)} \to \gqcs{L}_x$ by $\phi_x(1)= b(x)$.
+Then \ref{qc.1} holds since $d_G \alpha =0$ and \ref{qc.2} holds since $d_{\Weil{}}\alpha =d_G \beta$.
+Tracing the construction backward, we have defined a quasicharacter sheaf $\qcs{L}$ on $G$ with
+$S_G(\qcs{L}) = [\alpha\oplus\beta\oplus\gamma]$, showing that $S_G$ is surjective.
+\end{proof}
+
 \subsection{$S$ and $T$}
 
-In this section we find the relation between the group homomorphisms $\TrFrob{G}$ and $S_G$.
+In this section we describe the relationship between the group homomorphisms $\TrFrob{G}$ and $S_G$.
 %
-We begin with a simple result relating duals, invariants and coinvariants.
+We begin with a simple, general result relating duals, invariants and coinvariants.
 
@@
 
+\begin{corollary}
+If $G$ is \'etale then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective.
+\end{corollary}
+\begin{proof}
+Pick $\chi \in G(\Fq)^*$.
+By Lemma~\ref{lem:dual-inv}, there is some $b\in G(\bFq)^*$ such that $b\vert_{G(\Fq)^*} = \chi$.
+Set $\gqcs{L}_x = \EE$ for every $x\in G(\bFq)$.
+Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$ and 
+$\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = b(x)$.
+Since $b : G(\bFq) \to \EEx$ is a group homomorphism,
+condition \eqref{nohom} is satisfied with $a =1$ and $\qcs{L} = (\gqcs{L}, \mu, \phi)$
+is a rigid quasicharacter sheaf with $\trFrob{\qcs{L}} = \chi$.
+\end{proof}
+
 \begin{proposition} \label{prop:etale-iso}
- If $G$ is an \'etale commutative group scheme over $\Fq$
-  then the map $\QCiso{G}\to \Hh^2(E^\bullet_G)$ from Section~\ref{sec:S} induces an isomorphism of short exact sequences:
+ If $G$ is \'etale then the map $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ induces an isomorphism of short exact sequences
 \[
@@
  \]
-In particular,
-$\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$
-is surjective.
 \end{proposition}
-
-\begin{proof}
-We've discussed the fact that the square on the right commutes, using Lemma~\ref{lem:dual-inv}. \todo{David, could you add that here?}
-So, if $\qcs{L} \in \QC(G)$ and $S_G(\qcs{L}) = [\alpha\oplus\beta]$  then $\trFrob{\qcs{L}} =1$ implies $[\beta]=0$.
-In Section~\ref{sec:SES} we identified\todo{ ...
-and this, too?} $\{ [\alpha\oplus\beta] \in \Hh^2(E^\bullet_G) \tq [\beta]=0 \}$ with $\Hh^0(\Weil{},\Hh^2({\bar G},\EEx))$.
-
-Next we show that $\TrFrob{G}$ is surjective.
-Pick $\chi \in G(\Fq)^*$.
-By Lemma~\ref{lem:dual-inv}, there is some $b\in G(\bFq)^*$ such that $b\vert_{G(\Fq)^*} = \chi$.
-Set $\gqcs{L}_x = \EE$ for every $x\in G(\bFq)$.
-Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$.
-Define $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = b(x)$.
-Since $b : G(\bFq) \to \EEx$ is a group homomorphism,
-condition \eqref{nohom} is satisfied with $a =1$, the trivial cocycle in $Z^2(G(\bFq),\EEx)$.
-It is now clear that we have defined a (tight) quasicharacter sheaf $\qcs{L}$ with $\trFrob{\qcs{L}} = \chi$.
-
-Now we show that $S_G: \QCiso{G}\to \Hh^0(\Weil{},\Hh^2({\bar G},\EEx))$ injective;
-Suppose $\qcs{L} \in \QCiso{G}$.
-Let $a$ and $b$ be defined, as in Section~\ref{sec:S}, by a choice $\{ v_x \in \gqcs{L}_x^\times \tq x\in {\bar G}\}$; and let $\alpha\oplus\beta$ be the corresponding representative for the class $S_G(\qcs{L})\in \Hh^2(E^\bullet_G)$.
-Now suppose $S_G(\qcs{L}) = [\alpha\oplus\beta]=0$.
-Then $\alpha\oplus\beta = d\gamma$ for some $\gamma \in C^1(\Weil{},C^1({\bar G},\EEx)$. Let $c : {\bar G}\to \EEx$ be the function given by $x\mapsto \gamma(\Frob{})(x)$.
-For each $x\in {\bar G}$, define $\gamma_x : \gqcs{L}_x \to \EE$ by $v_x \mapsto c(x)$.
-Then the indexed set of isomorphisms $\{ \gamma_x : \gqcs{L}_x \to \EE \tq x\in {\bar G}\}$ satisfies condition \ref{qc.4} (with $\gqcs{L'}$, $\mu'$ and $\phi'$ trivial) and therefore defines an isomorphism $\qcs{L} \to (\EE)_{G}$.
-This shows that $S_G: \QCiso{G}\to \Hh^0(\Weil{},\Hh^2({\bar G},\EEx))$ is injective.
-
-To see that $S_G: \QCiso{G}\to \Hh^0(\Weil{},\Hh^2({\bar G},\EEx))$ is surjective, begin with $\alpha\oplus\beta \in Z^2(E^\bullet_G)$.
-Let $a \in C^2({\bar G},\EEx)$ and $b \in C^1({\bar G},\EEx)$ be defined as above, which makes use of the fact $d_{\rightarrow}\beta =0$.
-Set $\gqcs{L}_x = \EEx$ and define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes\gqcs{L}_y$ by $\mu_{x,y}(1) = a(x,y) 1\otimes 1$ and define $\phi_x : \gqcs{L}_{\Frob{G}(x)} \to \gqcs{L}_x$ by $\phi_x(1)= b(x)$.
-Then \ref{qc.1} is true since $d_{\uparrow}\alpha =0$ and \ref{qc.2} is true since $d_{\rightarrow}\alpha =d_{\uparrow} \beta$.
-In this way, from $\alpha\oplus\beta\in Z^2(E^\bullet_G)$ we have define a quasicharacter sheaf $\qcs{L}$ on $G$ with $S_G(\qcs{L}) = [\alpha\oplus\beta]$, showing that $S_G$ is surjective.
+\begin{proof}
+This result follows easily from Proposition \ref{prop:ses_desc}.
 \end{proof}
@@
 In the introduction to this paper we noted that, when working with connected commutative algebraic groups over finite fields, Deligne's dictionary can be described using Weil sheaves $\qcs{L}$ for which there exists an isomorphism $m^* \qcs{L} \iso \qcs{L} \boxtimes\qcs{L}$, without keeping track of the isomorphism.
-In this section use that perspective to find a perfect dictionary between (loose) quasicharacter sheaves on $G$ and characters of $G(\Fq)$.
-
-\subsection{(loose) quasicharacter sheaves}\label{sec:loose}
+In this section use that perspective to find a perfect dictionary between quasicharacter sheaves on $G$ and characters of $G(\Fq)$.
+
+\subsection{Quasicharacter sheaves}\label{sec:loose}
 
@@
 Let $G$ be a smooth commutative group scheme over $\Fq$.
-A \emph{(loose) quasicharacter sheaf} on $G$ is a Weil sheaf $(\gqcs{L},\phi)$ on $G$
-for which $(\gqcs{L},\mu,\phi)$ is a (tight) quasicharacter sheaf on $G$
-for som $\mu: \bm^* \gqcs{L} \to \gqcs{L} \boxtimes \gqcs{L}$.
+A \emph{quasicharacter sheaf} on $G$ is a Weil sheaf $(\gqcs{L},\phi)$ on $G$
+for which $(\gqcs{L},\mu,\phi)$ is a rigid quasicharacter sheaf on $G$
+for some $\mu: \bm^* \gqcs{L} \to \gqcs{L} \boxtimes \gqcs{L}$.
 %The resulting objects lie in the essential image of the forgetful functor $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ from $\QC(G)$ to Weil sheaves on $G$.
-We form a category from (loose) quasicharacter sheaves by declaring that a morphism $(\gqcs{L},\phi) \to (\gqcs{L'},\phi')$ is a sheaf homomorphism $\alpha : \gqcs{L} \to \gqcs{L'}$ for which the two diagrams in Condition~\ref{QC.4} commute, for some choice of $\mu$, $\mu'$ such that $(\gqcs{L},\mu,\phi)$ and $(\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$.
-The category of \emph{loose} quasicharacter sheaves on $G$ is denoted by $\lQC(G)$.
+We form a category from quasicharacter sheaves by declaring that a morphism $(\gqcs{L},\phi) \to (\gqcs{L'},\phi')$ is a sheaf homomorphism $\alpha : \gqcs{L} \to \gqcs{L'}$ for which the two diagrams in Condition~\ref{QC.4} commute, for some choice of $\mu$, $\mu'$ such that $(\gqcs{L},\mu,\phi)$ and $(\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$.
+The category of quasicharacter sheaves on $G$ is denoted by $\lQC(G)$.
 \end{definition}
 
-The category of loose quasicharacter sheaves on $G$ is rigid monoidal and the functor $\QC(G) \to \lQC(G)$ is monoidal and essentially surjective but neither full nor faithfull, generally.
+The category of quasicharacter sheaves on $G$ is rigid monoidal and the functor $\QC(G) \to \lQC(G)$ is monoidal and essentially surjective but neither full nor faithful, generally.
 %
@@
 %
-It follows from the sname lemma that $\coker \TrFrob{G} =0$
+It follows from the snake lemma that $\coker \TrFrob{G} =0$
 and $\ker \TrFrob{\pi_0(G)} \to \ker \TrFrob{G}$ is surjective.
@@
 First, suppose $G$ is etale.
-Let $(\gqcs{E},\phi')$ be a loose quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{E},\phi')}=1$.
+Let $(\gqcs{E},\phi')$ be a quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{E},\phi')}=1$.
 Let $\qcs{E} = (\gqcs{E},\mu,\phi')$ be a quasicharacter sheaf.
@@
 corresponding to a choice $\{ v_x \in \gqcs{E}_x^\times \tq x\in {\bar C}\}$.
-Let $a\in Z^2({\bar G},\EEx)$ be the mutliplicative version of $\alpha$
+Let $a\in Z^2({\bar G},\EEx)$ be the multiplicative version of $\alpha$
 and let $\mu'$ be the indexed set of isomorphisms $\mu'_{x,y} : \EE \to \EE\otimes \EE$ defined by $1 \mapsto a(x,y) 1 \otimes 1$.
@@
 Now let $G$ be arbitrary
-and let $(\gqcs{L},\phi)$ be a loose quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{L},\phi)}=1$.
+and let $(\gqcs{L},\phi)$ be a quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{L},\phi)}=1$.
 Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf.
@@
 With Corollary~\ref{cor:bounded-and-finite} in hand
-we see that all loose quasicharacter sheaves on $G$ are finite quasicharacter sheaves
+we see that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves
 when $G$ is a commutative algebraic group over $\Fq$;
 observe that the component group $\pi_0({\bar G})$ is finite in this case.
-On the otherhand, Corollary~\ref{cor:bounded-and-finite} also shows us
+On the other hand, Corollary~\ref{cor:bounded-and-finite} also shows us
 why neither finite quasicharacter sheaves nor bounded quasicharacter sheaves
@@
 For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$:
-the (loose) quasicharacter sheaf on $G$ corresponding, under Theorem~\ref{thm:snake},
+the quasicharacter sheaf on $G$ corresponding, under Theorem~\ref{thm:snake},
 to the character $1 \mapsto \ell$ is not a bounded quasicharacter sheaf,
-while the (loose) quasicharacter sheaf on $G$ corresponding
+while the quasicharacter sheaf on $G$ corresponding
 to the character $1 \mapsto 1+ \ell$ is a bounded but not finite quasicharacter sheaf.
@@
 The vertical left face is an isomorphism of exact sequences by Proposition~\ref{prop:etale-iso}
-and the vertical right faceis an isomorphism of exact sequences by Proposition~\ref{prop:connected-iso}.
+and the vertical right face is an isomorphism of exact sequences by Proposition~\ref{prop:connected-iso}.
 %

### 2014-06-11 dictionary.tex
Change _mu to _rig
Removed bubble. Fixed an instance of rigid v. loose.

@@
 \newcommand{\lQCiso}[1]{\lQC(#1)_{/\text{iso}}}
-\newcommand{\QC}{{\lQC_\mu}}
+\newcommand{\QC}{{\lQC_{\text{rig}}}}
 \newcommand{\QCb}{{\lQC_0}}
@@
 
-\todo{The bottom arrow is an isomorphism to $G(k')^*_{\Gal(k'/k)}$.
-We will see that the horizontal arrows are isomorphisms on quasicharacter sheaves.
-Can we make sense of $\QC(G_{k'})_{\Gal(k'/k)}$?
-If so, is the functor $\nu_{k'/k}$ into $\QC(G_{k'})_{\Gal(k'/k)}$ an equivalence of categories?}
-
 \begin{proof}
@@
 
-The latter two claims follow from tracing through the definition of latter pages in the spectral sequence; see Vakil \cite{} for example.
+The latter two claims follow from tracing through the definition of latter pages in the spectral sequence; see Vakil \cite{} for example \todo{update reference}.
 \end{proof}
@@
 \[
-0 \to \QCiso{\pi_0(G)} \to \QCiso{G} \to \QCiso{G^0} \to 0
-\]
-of abelian groups.\todo{Pure speculation.}
+0 \to \lQCiso{\pi_0(G)} \to \lQCiso{G} \to \lQCiso{G^0} \to 0
+\]
+of abelian groups.
 \end{corollary}

### 2014-06-25 dictionary.tex
Fixed section on finite quasicharacter sheaves!
Also played with notation for rigid, finite, flabby, quasicharacter
sheaves. I’m not done with Aut(L) yet.

@@
 %% Categories
-\newcommand{\lQC}{{\mathcal{Q\hskip-0.8pt C}}}
+\newcommand{\QC}{{\mathcal{Q\hskip-0.8pt C}}}
+\newcommand{\lQC}{{\QC_\text{flb}}}
 \newcommand{\lQCiso}[1]{\lQC(#1)_{/\text{iso}}}
-\newcommand{\QC}{{\lQC_{\text{rig}}}}
-\newcommand{\QCb}{{\lQC_0}}
-\newcommand{\QCf}{{\lQC_f}}
-\newcommand{\QCiso}[1]{\QC(#1)_{/\text{iso}}}
-\newcommand{\QCbiso}[1]{\QCb(#1)_{/\text{iso}}}
-\newcommand{\QCfiso}[1]{\QCf(#1)_{/\text{iso}}}
+\newcommand{\rQC}{{\QC_{\text{rig}}}}
+\newcommand{\rbQC}{{\QC_0}}
+\newcommand{\rfQC}{{\QC_\text{fin}}}
+\newcommand{\rQCiso}[1]{\rQC(#1)_{/\text{iso}}}
+\newcommand{\rbQCiso}[1]{\rbQC(#1)_{/\text{iso}}}
+\newcommand{\rfQCiso}[1]{\rfQC(#1)_{/\text{iso}}}
 \newcommand{\trFrob}[1]{t_{#1}}
@@
 \gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms satisfying natural compatibility conditions; here $\Frob{G}$ is the Frobenius automorphism of ${\bar G}$.
-A \emph{quasicharacter sheaf} on $G$ is a Weil sheaf $(\gqcs{L},\phi)$ on $G$
+A \emph{flabby quasicharacter sheaf} on $G$ is a Weil sheaf $(\gqcs{L},\phi)$ on $G$
 for which $(\gqcs{L},\mu,\phi)$ is a rigid quasicharacter sheaf on $G$, for some $\mu$.
@@
  In the main result of this paper, Theorem~\ref{thm:snake},
-we form a rigid monoidal category $\lQC(G)$ of quasicharacter sheaves on $G$
+we form a rigid monoidal category $\lQC(G)$ of flabby quasicharacter sheaves on $G$
 and show that the Trace of Frobenius provides a functorial group isomorphism
@@
 After setting some basic notation in Section~\ref{sec:notation},
-in Section~\ref{sec:category} we define quasicharacter sheaves and give an interpretation of
+in Section~\ref{sec:category} we define rigid quasicharacter sheaves and give an interpretation of
 them as Weil sheaves equipped with an isomorphism of the form \eqref{introbox}.
@@
 one direction of the function--sheaf dictionary.
-We define pullbacks and products of quasicharacter sheaves in Section~\ref{sec:pullback}, and use
+We define pullbacks and products of rigid quasicharacter sheaves in Section~\ref{sec:pullback}, and use
 them to prove a functoriality result on Trace of Frobenius.
-In Section~\ref{sec:basechange} we study how quasicharacter sheaves behave under base change
+In Section~\ref{sec:basechange} we study how rigid quasicharacter sheaves behave under base change
 and Weil restriction.
 Sections~\ref{sec:bounded} and \ref{sec:finite} describe bounded quasicharacter sheaves and finite quasicharacter sheaves, respectively,
-forming two important subcategories of $\QC(G)$.
+forming two important subcategories of $\rQC(G)$.
 %These subcategories play a key role in the proof of Proposition~\ref{prop:restriction}.
-In Section \ref{sec:connected} we show that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves when $G$ is connected, and that Trace of Frobenius is an isomorphism in this case.
+In Section \ref{sec:connected} we show that all rigid quasicharacter sheaves on $G$ are finite quasicharacter sheaves when $G$ is connected, and that Trace of Frobenius is an isomorphism in this case.
 We shift to \'etale group schemes $G$ in Section~\ref{sec:etale} and find a cohomological interpretation
-of quasicharacter sheaves in this case.
+of rigid quasicharacter sheaves in this case.
 In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
-induces an essentially surjective functor of quasicharacter sheaves.
+induces an essentially surjective functor of rigid quasicharacter sheaves.
 Section~\ref{sec:snake} presents the main theorem of this paper: Trace of Frobenius
-is a functorial isomorphism from isomorphism classes of quasicharacter sheaves on $G$
+is a functorial isomorphism from isomorphism classes of flabby quasicharacter sheaves on $G$
 to characters of $G(\Fq)$.
+
+Comments about Joseph Bernstein's comments?
 
@@
 over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.
-%For the sake of brevity, we define a \emph{$\QC$-scheme} to be such a $G$ with the additional property that the geometric component group of $G$ is finitely generated.
+%For the sake of brevity, we define a \emph{$\rQC$-scheme} to be such a $G$ with the additional property that the geometric component group of $G$ is finitely generated.
 This last condition is only needed in the proof of Lemma \ref{lemma:section}.
-A morphism of $\QC$-schemes is a morphism of group schemes over $\Fq$.
+A morphism of $\rQC$-schemes is a morphism of group schemes over $\Fq$.
 
@@
 
-Morphisms in the category of quasicharacter sheaves on $G$, denoted by $\QC(G)$, are defined in the natural way:
+Morphisms in the category of rigid quasicharacter sheaves on $G$, denoted by $\rQC(G)$, are defined in the natural way:
 \begin{enumerate}
 \labitem{(QC.4)}{QC.4} if $\qcs{L} = (\gqcs{L},\mu,\phi)$ and
-  $\qcs{L'} = (\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$ then
+  $\qcs{L'} = (\gqcs{L'},\mu',\phi')$ are rigid quasicharacter sheaves on $G$ then
   a morphism $\qcs{L} \to \qcs{L}'$ is a map $\alpha : \gqcs{L} \to \gqcs{L'}$
@@
 
-The rule $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ defines a forgetful functor from quasicharacter
-sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
-
-A Weil sheaf $(\gqcs{L},\phi)$ on $G$
-may be interpreted as a constructible $\ell$-adic sheaf $\gqcs{L}$ on $\bG$ together with
-an action of the Weil group $\Weil{}$ on $\gqcs{L}$ compatible with the action of
-$\Gal(\bFq/\Fq)$ on $\bG$. We now briefly review this point of view for later use in
-Section~\ref{sec:basechange}; see also \cite{deligne:80a}*{Def.~1.1.10}.  If $w \ceq \Frob{}^n$ we write $w_G$ for $\Frob{G}^n$.
-For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gqcs{L}\to \gqcs{L}$ by
-$
-\varphi(w) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi)
-$;
-these isomorphisms satisfy $\varphi(uv) = \varphi(v) \circ v_G^* \varphi(u)$ for $u,v\in \Weil{}$, and
-we have $\phi = \varphi(\Frob{})$.
-If we further define $\varphi_1(w) \ceq (w_G)_*(\varphi(w)^{-1})$ then
-$\varphi_1(w) : (w_G)_* \gqcs{L}\to \gqcs{L}$ is an isomorphism and
-$\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for $u,v\in \Weil{}$.
-Thus the pair $(\gqcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{}$
-on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of
-\cite{deligne:SGA4.5}*{Expos\'e XIII, 1.1}, failing only because $\Weil{}$ is not profinite.
-As we will see in Corollary~\ref{cor:bounded-and-finite}, our use of $\Weil{}$ rather than $\Gal(\bFq/\Fq)$
-allows quasicharacter sheaves to correspond to unbounded characters.
-
-The category $\QC(G)$ of quasicharacter sheaves on $G$ is a rigid monoidal category
+The category $\rQC(G)$ of rigid quasicharacter sheaves on $G$ is a rigid monoidal category
 \cite{etingof:09a}*{\S1.10} under the tensor product
@@
 $\sheafHom(\ - \ ,\EE)$.
-The category of quasicharacter sheaves on $G$ is not abelian, so $\QC(G)$
+The category of rigid quasicharacter sheaves on $G$ is not abelian, so $\rQC(G)$
 is not a tensor category in the sense of \cite{deligne:02a}*{0.1}.
-This rigid monoidal category structure for $\QC(G)$ gives the set $\QCiso{G}$
-of isomorphism classes in $\QC(G)$ the structure of a group.
+This rigid monoidal category structure for $\rQC(G)$ gives the set $\rQCiso{G}$
+of isomorphism classes in $\rQC(G)$ the structure of a group.
+
+\subsection{Flabby quasicharacter sheaves}\label{sec:loose}
+
+Observe that the rule $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ defines a forgetful functor from rigid quasicharacter
+sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
+%
+
+%A Weil sheaf $(\gqcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gqcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
+%We now briefly review this point of view for later use in Section~\ref{sec:basechange}; see also \cite{deligne:80a}*{Def.~1.1.10}.  If $w \ceq \Frob{}^n$ we write $w_G$ for $\Frob{G}^n$.
+%For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gqcs{L}\to \gqcs{L}$ by $\varphi(w) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi);$
+%these isomorphisms satisfy $\varphi(uv) = \varphi(v) \circ v_G^* \varphi(u)$ for $u,v\in \Weil{}$, and we have $\phi = \varphi(\Frob{})$.
+%If we further define $\varphi_1(w) \ceq (w_G)_*(\varphi(w)^{-1})$ then $\varphi_1(w) : (w_G)_* \gqcs{L}\to \gqcs{L}$ is an isomorphism and $\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for $u,v\in \Weil{}$.
+%Thus the pair $(\gqcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of\cite{deligne:SGA4.5}*{Expos\'e XIII, 1.1}, failing only because $\Weil{}$ is not profinite.
+%As we will see in Corollary~\ref{cor:bounded-and-finite}, our use of $\Weil{}$ rather than $\Gal(\bFq/\Fq)$ allows quasicharacter sheaves to correspond to unbounded characters.
+
+\begin{definition}\label{def:lQC}
+Let $G$ be a smooth commutative group scheme over $\Fq$.
+A \emph{flabby quasicharacter sheaf} on $G$ is a Weil sheaf $(\gqcs{L},\phi)$ on $G$
+for which $(\gqcs{L},\mu,\phi)$ is a rigid quasicharacter sheaf on $G$
+for some $\mu: \bm^* \gqcs{L} \to \gqcs{L} \boxtimes \gqcs{L}$.
+%The resulting objects lie in the essential image of the forgetful functor $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ from $\rQC(G)$ to Weil sheaves on $G$.
+We form the category of flabby quasicharacter sheaves by declaring that a morphism $(\gqcs{L},\phi) \to (\gqcs{L'},\phi')$ is a sheaf homomorphism $\alpha : \gqcs{L} \to \gqcs{L'}$ for which the two diagrams in Condition~\ref{QC.4} commute, for some choice of $\mu$, $\mu'$ such that $(\gqcs{L},\mu,\phi)$ and $(\gqcs{L'},\mu',\phi')$ are rigid quasicharacter sheaves on $G$.
+The category of flabby quasicharacter sheaves on $G$ is denoted by $\lQC(G)$.
+\end{definition}
+
+Since objects in $\lQC(G)$ are Weil sheaves and since in the first diagram in Condition~\ref{QC.4} ensures that a morphism in $\lQC(G)$ is a morphism of Weil sheaves, it follows that $\lQC(G)$ is a subcategory of Weil sheaves on $G$.
+%
+Like $\rQC(G)$, the category $\lQC(G)$ of quasicharacter sheaves on $G$ is rigid monoidal.
+The functor $\rQC(G) \to \lQC(G)$ is monoidal and essentially surjective but neither full nor faithful, generally.
+%
 
@@
 
-We now begin developing the tools to relate $\QCiso{G}$ to $G(\Fq)^*$.
-%
+We now introduce a tool which will help us understand isomorphism classes of objects in $\rQCiso{G}$ and $\lQCiso{G}$.
+
 Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
-determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$ and
-therefore an automorphism $\phi_{\bg}$ of $\gqcs{L}_{\bg}$. Set
+determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$. 
+Together with the canonical isomorphism $(\Frob{G}^*\gqcs{L})_{\bg} \iso  \gqcs{L}_{\Frob{G}(\bg)}$, in this way the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gqcs{L}_{\bg}$; let $\trace(\phi_{\bg};\gqcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gqcs{L}_{\bg})$ and let $\trFrob{(\gqcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by
 \begin{equation}\label{trWeil}
 %\begin{equation}\label{trWeil}
-\trFrob{(\gqcs{L},\phi)}(g) \ceq \trace(\phi_{\bg}, \gqcs{L}_{\bg})
+\trFrob{(\gqcs{L},\phi)}(g) \ceq \trace(\phi_{\bg};\gqcs{L}_{\bg}),
 %\end{equation}
 \end{equation}
-and note that if $(\gqcs{L},\phi) \iso (\gqcs{L'},\phi')$ then $\trFrob{(\gqcs{L},\phi)} = \trFrob{(\gqcs{L'},\phi')}$.
- If $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf
-then we will abbreviate $\trFrob{(\gqcs{L},\phi)}$ to $\trFrob{\qcs{L}}$.
-%\begin{definition}\label{def:trFrob}
-We will refer to the function
-\begin{align*}
-\TrFrob{G}: \QCiso{G} &\to G(\Fq)^* \\
-\qcs{L} &\mapsto t_{\qcs{L}}: g\mapsto \trace(\phi_{\bg}, \gqcs{L}_{\bg})
-\end{align*}
-as the \emph{Trace of Frobenius} for $G$.
-%\todo{Does this really warrant a declared definition?
-%Instead, we can refer to this very short section, when needed.}
-%\end{definition}
-
+commonly called the {\em trace of Frobenius of $(\gqcs{L},\phi)$}.
+Note that if $(\gqcs{L},\phi) \iso (\gqcs{L'},\phi')$ as Weil sheaves, 
+then $\trFrob{(\gqcs{L},\phi)} = \trFrob{(\gqcs{L'},\phi')}$ as functions on $G(\Fq)$.
+
+Now suppose $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a rigid quasicharacter sheaf on $G$.
 The isomorphism $\mu : \bm^* \gqcs{L} \to \LxL$ together with
 \ref{QC.3} guarantee
-that the function $\trFrob{\qcs{L}} : G(\Fq)\to \EEx$ is a group homomorphism.  If we write
-$\trFrob{\qcs{L}} \cdot \trFrob{\qcs{L'}}$ for pointwise multiplication, then
- $\trFrob{\qcs{L}\otimes \qcs{L'}} = \trFrob{\qcs{L}} \cdot \trFrob{\qcs{L'}}$.
- Therefore $\TrFrob{G}$ is a homomorphism, which is functorial in the following sense:
+that the function $\trFrob{(\qcs{L},\phi)} : G(\Fq)\to \EEx$ is a group homomorphism.  
+Moreover, this group homomorphism is insensitive to $\phi$ in the sense 
+that if $(\gqcs{L},\mu,\phi)$ and $(\gqcs{L},\mu,\phi')$ are rigid quasicharacter sheaves, then $\trFrob{(\qcs{L},\phi)} = \trFrob{(\qcs{L},\phi')}$. \todo{Sketch proof?}
+This justifies abbreviating $\trFrob{(\gqcs{L},\phi)}$ to $\trFrob{\qcs{L}}$ in this case.
+The diagram below defines two group homomorphisms, both denoted $\TrFrob{G}$ and both called the \emph{Trace of Frobenius} for $G$; we trust that context will remove any ambiguity regarding this notation.
+\[
+\begin{tikzcd}
+\rQCiso{G} \arrow{rr} \arrow{dr}[swap]{\qcs{L} \mapsto t_{\qcs{L}}}{\TrFrob{G}} && \arrow{dl}[swap]{\TrFrob{G}}{(\gqcs{L},\phi) \mapsto t_{\gqcs{L},\phi}} \lQCiso{G} \\
+& G(\Fq)^* & 
+\end{tikzcd}
+\]
+As remarked above, the group homomorphism $\rQCiso{G} \to \lQCiso{G}$ is surjective;
+we will see that $\rQCiso{G} \to \lQCiso{G}$ need not be injective.
+However, in Theorem~\ref{thm:snake}, we will see that the group homomorphism $\rQCiso{G} \to G(\Fq)^*$ is surjective
+while the main result of this paper, Theorem~\ref{thm:snake}, 
+shows that $\lQCiso{G} \to G(\Fq)^*$ is an isomorphism.
 
 \begin{proposition}\label{prop:functorialG}
-Trace of Frobenius $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a natural transformation
+Trace of Frobenius $\TrFrob{G} : \rQCiso{G} \to G(\Fq)^*$ is a natural transformation
 between the two contravariant additive functors
 \begin{align*}
-F_1 : G &\mapsto \QCiso{G} \\
+F_1 : G &\mapsto \rQCiso{G} \\
 F_2 : G &\mapsto G(\Fq)^*
@@
 from the category of smooth commutative group schemes over $\Fq$ to the category of abelian groups.
+Likewise, for $\TrFrob{G} : \lQCiso{G} \to G(\Fq)^*$, {\it mut.\hskip-1pt mut.}
 \end{proposition}
@@
   \begin{align*}
-  f^* : \QC(G) &\to \QC(H) \\
+  f^* : \rQC(G) &\to \rQC(H) \\
   (\gqcs{L},\mu,\phi) &\mapsto (\bf^*\gqcs{L},(\bfxf)^*\mu,\bf^*F)
@@
   \begin{tikzcd}[row sep=20, column sep=30]
-   \QCiso{G} \rar{f^*} \arrow[swap]{d}{\TrFrob{G}} & \QCiso{H} \dar{\TrFrob{H}} \\
+   \rQCiso{G} \rar{f^*} \arrow[swap]{d}{\TrFrob{G}} & \rQCiso{H} \dar{\TrFrob{H}} \\
    G(\Fq)^* \rar & H(\Fq)^*
@@
   of $f^*$ on morphisms of quasicharacter sheaves; arguing as above shows that $f^*$ is
-  a functor from $\QC(G)$ to $\QC(H)$.  Since tensor products commute with pullback in schemes,
-  $f^* : \QC(G) \to \QC(H)$ is a monoidal functor.
-  The diagram relating $f^* : \QC(G) \to \QC(H)$, $f^* : G(k)^* \to H(k)^*$ and Trace of Frobenius
+  a functor from $\rQC(G)$ to $\rQC(H)$.  Since tensor products commute with pullback in schemes,
+  $f^* : \rQC(G) \to \rQC(H)$ is a monoidal functor.
+  The diagram relating $f^* : \rQC(G) \to \rQC(H)$, $f^* : G(k)^* \to H(k)^*$ and Trace of Frobenius
   commutes by \cite{laumon:87a}*{1.1.1.2}, where the ambient
@@
 
-We end this section with a simple result on products of quasicharacter sheaves,
+We end this section with a simple result on products of rigid quasicharacter sheaves,
 which is needed to show that the isomorphism above is functorial.
@@
 \[
-\QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)
+\rQC(G_1)\times \rQC(G_2) \to \rQC(G_1\times G_2)
 \]
@@
 \begin{tikzcd}[column sep=60]
-\arrow{d}{\TrFrob{G_1} \times \TrFrob{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes}
-& \arrow{d}{\TrFrob{G_1\times G_2}} \QCiso{G_1\times G_2}\\
+\arrow{d}{\TrFrob{G_1} \times \TrFrob{G_2}} \rQCiso{G_1}\times \rQCiso{G_2} \arrow{r}{\boxtimes}
+& \arrow{d}{\TrFrob{G_1\times G_2}} \rQCiso{G_1\times G_2}\\
 (G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
@@
 \begin{proof}
-The only non-trivial part of the proof is to show that $\boxtimes : \QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)$
+The only non-trivial part of the proof is to show that $\boxtimes : \rQC(G_1)\times \rQC(G_2) \to \rQC(G_1\times G_2)$
 is essentially surjective, so we will only address that point here.
@@
 
-Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
+Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a rigid quasicharacter sheaf on $G$.
 Set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$;
-by Proposition~\ref{prop:pullback}, $\qcs{L}_1$ a quasicharacter sheaf on $G_1$
-and $\qcs{L}_2$ is a quasicharacter sheaf on $G_2$.
+by Proposition~\ref{prop:pullback}, $\qcs{L}_1$ a rigid quasicharacter sheaf on $G_1$
+and $\qcs{L}_2$ is a rigid quasicharacter sheaf on $G_2$.
 We will obtain an isomorphism $\qcs{L} \iso  \qcs{L}_1\boxtimes \qcs{L}_2$.
@@
 \end{align*}
-We can interpret this operation on characters in terms of quasicharacter sheaves:
+We can interpret this operation on characters in terms of rigid quasicharacter sheaves:
 
@@
 \[
-\QC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \QC(G)
+\rQC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \rQC(G)
 \]
@@
 \begin{tikzcd}
-\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\TrFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\TrFrob{G}} \\
+\rQCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\TrFrob{\Res_{k'/k}(G_{k'})}} & \rQCiso{G} \dar{\TrFrob{G}} \\
 G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
@@
 \end{align*}
-We can also interpret this operation on characters in terms of quasicharacter sheaves.
-
-If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$, we define
-a quasicharacter sheaf $\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
+We can also interpret this operation on characters in terms of rigid quasicharacter sheaves.
+
+If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a rigid quasicharacter sheaf on $G$, we define
+a rigid quasicharacter sheaf $\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
 $G_{k'}$ of $G$ to $k'$ by setting
@@
 the rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$
- defines a monoidal functor $\QC(G) \to \QC(G_{k'})$.
+ defines a monoidal functor $\rQC(G) \to \rQC(G_{k'})$.
  Moreover, the following diagram commutes:
@@
 \begin{tikzcd}[column sep=60]
-\QCiso{G} \rar{\nu_{k'/k}} \dar{\TrFrob{G}} & \QCiso{G_{k'}} \dar{\TrFrob{G_{k'}}} \\
+\rQCiso{G} \rar{\nu_{k'/k}} \dar{\TrFrob{G}} & \rQCiso{G_{k'}} \dar{\TrFrob{G_{k'}}} \\
 G(k)^*  \rar{\Nm^*} & G(k')^*.
@@
 \begin{proof}
-Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
+Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \rQC(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
 we may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
@@
 \[
-\rho : \QC(\Res_{k'/k}G') \to \QC(G').
+\rho : \rQC(\Res_{k'/k}G') \to \rQC(G').
 \]
@@
 \begin{tikzcd}
-\QCiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \QCiso{G'} \dar{\TrFrob{G'}}\\
+\rQCiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \rQCiso{G'} \dar{\TrFrob{G'}}\\
 G'(k')^* \rar & G'(k')^*
@@
 
-\section{Two subcategories of quasicharacter sheaves}%\label{sec:bounded}
+\section{Two subcategories of rigid quasicharacter sheaves}%\label{sec:bounded}
 
@@
 
-In this section we consider a class of quasicharacter sheaves on $G$ obtained by
-replacing the Weil sheaf $(\gqcs{L}, \phi)$ on $\bG$ in the definition of a quasicharacter
+In this section we consider a class of rigid quasicharacter sheaves on $G$ obtained by
+replacing the Weil sheaf $(\gqcs{L}, \phi)$ on $\bG$ in the definition of a rigid quasicharacter
 sheaf with an $\ell$-adic local system on $G$ itself.
@@
 \begin{definition}
-Let $\QCb(G)$ be the category of pairs $(\qcs{L}_0,\mu_0)$
+Let $\rbQC(G)$ be the category of pairs $(\qcs{L}_0,\mu_0)$
 where $\qcs{L}_0$ an $\ell$-adic local system on $G$ of rank~one,
@@
 satisfying the analogue of \ref{QC.1} on $G$;
-morphisms in $\QCb(G)$ are defined as in the second part of
+morphisms in $\rbQC(G)$ are defined as in the second part of
 \ref{QC.3}.
@@
 Extension of scalars defines a full and faithful functor
-$B_G : \QCb(G) \hookrightarrow \QC(G)$.
+$B_G : \rbQC(G) \hookrightarrow \rQC(G)$.
 \end{proposition}
@@
 
-In general, $\QCb(G)$ is an essentially
-proper subcategory of $\QC(G)$. We will identify $\QCb(G)$ with its image under $B_G$
-and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ is \emph{bounded}
+In general, $\rbQC(G)$ is an essentially
+proper subcategory of $\rQC(G)$. We will identify $\rbQC(G)$ with its image under $B_G$
+and say that a rigid quasicharacter sheaf $\qcs{L} \in \rQC(G)$ is \emph{bounded}
 if it is isomorphic to some $B_G(\qcs{L}_0, \mu_0)$.
-We will see in Corollary~\ref{cor:bounded-and-finite} that the bounded quasicharacter sheaves
-are precisely those whose Trace of Frobenius have bounded image.
+We will see in Corollary~\ref{cor:bounded-and-finite} that bounded quasicharacter sheaves are exactly rigid quasicharacter sheaves with bounded Trace of Frobenius.
 
@@
 In this section we define \emph{finite quasicharacter sheaves}, a further refinement
-of bounded quasicharacter sheaves that play a role in Section \ref{sec:restriction}.
+of bounded quasicharacter sheaves; finite quasicharacter sheaves will play a role in Section \ref{sec:restriction}.
 
@@
  isomorphism in $C(G)$.  While the description of local systems in terms of $\pi_1(G, \bg)$ does
- not generalize well to non-connected $G$, a perspective using finite \'etale covers does.
+ not adapt well to non-connected $G$, a perspective using finite \'etale covers does.
 
@@
 Let us say that a morphism $f : H\to G$ of smooth commutative group schemes over $\Fq$ is a \emph{discrete isogeny}
-if it is finite, surjective and \'etale and the action of $\Gal(\bFq/\Fq)$ on the \'etale group
-scheme $\ker f = f^{-1}({\bar e)}$ is trivial.
-Consider the category $C(G)$ whose objects consist of pairs $(f,\psi)$, where
+if it is finite, surjective, \'etale and the action of $\Gal(\bFq/\Fq)$ on the \'etale group
+scheme $\ker f = f^{-1}({\bar e)} = \Aut(f)$ is trivial.
+Consider the category $C(G)$ whose objects consist of triples $(f,\psi,V)$, where
 \begin{itemize}
@@
 \end{itemize}
-A morphism $(f,\psi) \to (f',\psi')$ in $C(G)$ is a pair $(g,T)$, where
+A morphism $(f,\psi,V) \to (f',\psi',V')$ in $C(G)$ is a pair $(\gamma,T)$, where
 \begin{itemize}
-\item $g : H' \to H$ is a morphism of schemes such that $f' = f\circ g$,
+\item $\gamma : H' \to H$ is a morphism of group schemes such that $f' = f\circ \gamma$,
 \item $T : V\to V'$ is a linear transformation, equivariant for the action of
@@
 V \arrow{d}{T} & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} & \arrow[equal]{d} G\\
-V' & \Aut(V') & \arrow[swap]{l}{\psi'} \arrow[swap]{u}{g\vert_{\ker f'}} \ker f' \arrow[hook]{r} & \arrow[swap]{u}{g} H' \arrow{r}{f'} & G
+V' & \Aut(V') & \arrow[swap]{l}{\psi'} \arrow[swap]{u}{\gamma\vert_{\ker f'}} \ker f' \arrow[hook]{r} & \arrow[swap]{u}{\gamma} H' \arrow{r}{f'} & G
 \end{tikzcd}
@@
 We put a tensor category structure on $C(G)$ as follows.
-Let $(f,\psi)$ and $(f',\psi')$ be objects in $C(G)$.
+Let $(f,\psi,V)$ and $(f',\psi',V')$ be objects in $C(G)$.
 Write $f\times_G f' : H\times_G H' \to G$ for the product of $f$ and $f'$
@@
 using the canonical isomorphism $\ker(f\times_G f') \iso (\ker f)\times (\ker f')$.
-We may thus define $(f,\psi)\otimes(f',\psi') \ceq (f\times_G f' ,\psi\otimes\psi')$ and
-$(f,\psi)\oplus(f',\psi')\ceq (f\times_G f' ,\psi\oplus\psi')$. To define duals in $C(G)$,
+We may thus define $(f,\psi,V)\otimes(f',\psi',V') \ceq (f\times_G f' ,\psi\otimes\psi', V\otimes V')$ and
+$(f,\psi,V)\oplus(f',\psi',V')\ceq (f\times_G f' ,\psi\oplus\psi', V\oplus V')$. To define duals in $C(G)$,
 let $V^\vee \ceq \Hom_\text{vec}(V,\EE)$ and $\psi^\vee : \ker f \to \Aut(V^\vee)$ be
-the dual representation.  We may then set $(f,\psi)^\vee \ceq (f,\psi^\vee)$.
+the dual representation.  We may then set $(f,\psi,V)^\vee \ceq (f,\psi^\vee, V^\vee)$.
 These operations give $C(G)$ the structure of a tensor category.
@@
 Now we localize $C(G)$.
-Let us say that $(g,T)$ in $C(G)$ is a \emph{weak isomorphism} if $g$ is surjective
-and $T$ is an isomorphism of vector spaces.  Recall from
-\cite{kashiwara-schapira:CatgoriesSheaves}*{Def 7.1.5} that a \emph{left multiplicative system}
-is a family of morphisms $W$ that
-\begin{itemize}
-\item contains all isomorphisms,
-\item is closed under composition,
-\item is closed under pullback by arbitrary morphisms in $C(G)$,
-\item and if the cokernel of a morphism $\phi \in \mor C(G)$ is in
-$W$ then so is the kernel of $\phi$.
-\end{itemize}
-
-We further say that $W$ is \emph{saturated} if the following property holds for
-morphisms $f, g$ and $h$ that can be composed appropriately:
-whenever $g \circ f$ and $h \circ g$ are in $W$ then so is $h$
-\cite{kashiwara-schapira:CatgoriesSheaves}*{Def 7.1.19}.
-
-\begin{lemma}
-The family of weak isomorphisms in $C(G)$ is a saturated, left multiplicative system.
-\end{lemma}
-\begin{proof}
-Any isomorphism $(g, T)$ in $C(G)$ has both $g$ and $T$ isomorphisms, and thus is a weak isomorphism.
-Clearly, the composition of two weak isomorphisms is a weak isomorphism.  The remaining properties
-follow from the fact that in a weak isomorphism $(g, T)$, $g$ is an \'etale cover, together with standard
-facts on \'etale covers and pullbacks.
-\end{proof}
-Let $W$ be the family of weak isomorphisms and $C(G)[W^{-1}]$ be the localization of $C(G)$ at $W$.
-A morphism in $C(G)[W^{-1}]$ is an equivalence class of diagrams
+Let us say that $(\gamma,T)$ in $C(G)$ is a \emph{weak isomorphism} if $T$ is an isomorphism of vector spaces.  
+Let $W$ be the family of weak isomorphism and
+et $C(G)[W^{-1}]$ be the localization of $C(G)$ with respect to $W$, 
+in the sense of \cite{kashiwara-schapira:CatgoriesSheaves}*{Def 7.1.1}.
+Since weak isomorphisms in $C(G)$ form a \emph{right multiplicative system}, in the sense of \cite{kashiwara-schapira:CatgoriesSheaves}*{Def 7.1.5}, it follows from \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16} that morphisms in $C(G)[W^{-1}]$ are simple to describe:
+a morphism in $C(G)[W^{-1}]$ is an equivalence class of diagrams
 \[
 \begin{tikzcd}[column sep=30]
-   (f,\psi) \arrow{r}{(g,T)} & (f',\psi') & \arrow[swap]{l}{(h,U)} (f_1,\psi_1)
-   \end{tikzcd}
-\]
- where $(g,T) : (f,\psi) \to (f',\psi')$ is any map in $C(G)$
- and $(h,U) :  (f',\psi') \to (f_1,\psi_1)$ is a weak isomorphism in $C(G)$ \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16}.
+   (f,\psi,V) \arrow{r}{(\gamma,T)} & (f',\psi',V') & \arrow[swap]{l}{(\gamma_1,T_1)}[swap]{\text{w-iso}} (f_1,\psi_1,V_1)
+   \end{tikzcd}
+\]
+ where $(\gamma,T) : (f,\psi,V) \to (f',\psi',V')$ is any map in $C(G)$
+ and $(\gamma_1, T_1) :  (f',\psi',V') \to (f_1,\psi_1,V_1)$ is a weak isomorphism in $C(G)$;
+for the equivalence relation on these diagrams, see \cite{kashiwara-schapira:CatgoriesSheaves}*{(7.1.3)}.
+
+It is straightforward to verify that the subcategory $C_1(G)$ of $C(G)$ consisting of $(f,\psi,V)$ for which $\psi$ is one-dimensional, is a full, rigid monoidal subcategory of $C(G)$ and further, that the family $W_1$ of weak isomorphisms in $C_1(G)$ is a right multiplicative system.
 
 \begin{definition}
-Let $C_1(G)$ be the full, rigid monoidal subcategory of $C(G)$ consisting of objects
-$(f,\psi)$ such that $\psi$ is a one-dimensional representation.
-The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\QCf(G)$,
-is the rigid monoidal category obtained by localizing $C_1(G)$ at weak isomorphisms.
+The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\rfQC(G)$,
+is the rigid monoidal category $C_1(G)[W_1^{-1}]$ obtained by localizing $C_1(G)$ at weak isomorphisms $W_1$.
 \end{definition}
 
-Having defined finite quasicharacter sheaves,
-we justify our terminology by showing $\QCf(G)$ is a full subcategory of $\QCb(G)$.
-To prepare for that result, we need two lemmas.
+Trivial morphisms in $\rfQC(G)$ are defined as follows. Let $(f,\psi,V)$ and $(f_1,\psi_1,V_1)$ be finite quasicharacter sheaves on $G$.  
+Form $(f\times_G f_1,1\otimes \psi_1, V\otimes V_1)$ in $C_1(G)$. 
+Let $0 : V \to V\otimes V_1$ be the trivial linear transformation. 
+Choose $0\ne v \in V$ and let $T_v: V_1 \to V\otimes V_1$ be the isomorphism $T_v(v_1) = v\otimes v_1$.  
+Let $\pi : H\times_G H_1 \to H$ and $\pi_1 : H\times_G H_1 \to H_1$ be the natural projections.
+Then $(\pi,0) : (f,\psi, V) \to  (f\times_G f_1,1\otimes \psi_1, V\otimes V_1)$ is a morphism in $C_1(G)$ and $(\pi_1,T_v) : (f_1,\psi_1,V_1) \to (f\times_G f_1,1\otimes \psi_1, V\otimes V_1)$ is a weak isomorphism in $C_1(G)$.
+%
+The morphism in $\rfQC(G)$ represented by
+\[
+\begin{tikzcd}[column sep=30]
+   (f,\psi,V) \arrow{r}{(\pi,0)} & (f\times_G f_1,1\otimes \psi_1, V\otimes V_1) & \arrow[swap]{l}{(\pi_1,T_v)}[swap]{\text{w-iso}}  (f_1,\psi_1,V_1),
+   \end{tikzcd}
+\]
+does not depend on the choice of $0\ne v\in V$; this defines the {\em trivial morphism} $0: (f,\psi,V) \to (f_1,\psi_1,V_1)$ in $\rfQC(G)$.
+
+\begin{proposition}\label{prop:autornaught}
+Every morphism in $\rfQC(G)$ is either an isomorphism or trivial.
+\todo{I may add something here about $\Aut_{\rfQC(G)}(f,\psi,V)$.}
+\end{proposition}
+
+\begin{proof}
+Let $(f,\psi,V)$ and $(f_1,\psi_1,V_1)$ be finite quasicharacter sheaves on $G$. 
+Let
+\[
+\begin{tikzcd}[column sep=30]
+   (f,\psi,V) \arrow{r}{(\gamma,T)} & (f',\psi',V') & \arrow[swap]{l}{(\gamma_1,T_1)}[swap]{\text{w-iso}}  (f_1,\psi_1,V_1)
+   \end{tikzcd}
+\]
+represent a morphism $(f,\psi,V)  \to (f_1,\psi_1,V_1)$ in $\rfQC(G)$;
+note that, by definition, $(\gamma_1 , T_1) : (f_1,\psi_1,V_1) \to (f',\psi',V')$ is a weak isomorphism.
+Since $V$, $V'$ and $V_1$ are one-dimensional $\EE$-vector spaces, either $T : V \to V'$ is an isomorphism or trivial.
+
+Suppose $T$ is trivial. 
+Let $\theta : H'\to H\times_G H_1$ be the morphism of group schemes given by the universal property of the pull back of $f: H\to G$ and $f_1 : H_1 \to G$, as pictured below.
+\[
+\begin{tikzcd}
+\ & \arrow{ddl}[swap]{\gamma} H' \arrow{d}{\theta} \arrow{ddr}{\gamma_1} & \\
+\ & \arrow{dl}{\pi} H \times_G H_1 \arrow{dr}[swap]{\pi_1} & \\
+H \arrow{rd}[swap]{f} && \arrow{ld}{f_1} H_1 \\
+& G & \\
+\end{tikzcd}
+\]
+Let $T_1' : V\otimes V_1 \to V'$ be the linear transformation defined by projection $V\otimes V_1 \to V_1$ followed by $T_1 : V_1 \to V'$. Then
+\[
+\begin{tikzcd}[column sep=30]
+\ & (f',\psi',V')  & \\
+\arrow{dr}[swap]{(\pi,0)}  (f,\psi,V)  \arrow{ru}{(\gamma,T=0)} &  & \arrow[swap]{lu}{(\gamma_1,T_1)}[swap]{\text{w-iso}} (f_1,\psi_1,V_1) \arrow{dl}{(\pi_1,T_v)}[swap]{\text{w-iso}} \\
+\ & \arrow{uu}[swap]{(\theta,T_1')} (f\times_G f_1,1\otimes \psi_1, V\otimes V_1) & \\   
+   \end{tikzcd}
+\]
+is a commuting diagram in $C_1(G)$, where $T_v : V_1 \to V\otimes V_1$ is defined as in the construction of the trivial morphism $0 : (f,\psi,V) \to (f_1,\psi_1,V_1)$, above.
+By \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16}, 
+it follows that $(f,\psi,V)  \to (f_1,\psi_1,V_1)$ is the trivial morphism in $\rfQC(G)$.
+
+Now suppose $T$ is an isomorphism, then $(\gamma,T)$ is a weak isomorphism, in which case the morphism $(f,\psi,V) \to (f_1,\psi_1,V_1)$ is an isomorphism in $\rfQC(G)$.
+\todo{This is where some information about $\Aut_{\rfQC(G)}(f,\psi,V)$ will go, when I've sorted it out.}
+\end{proof}
+
+\subsection{Finite implies Bounded}
+
+In this section we show that $\rfQC(G)$ is a full subcategory of $\rbQC(G)$.
+To prepare for that result, we need the next two lemmas.
 
 \begin{lemma}\label{lemma:finite-pullback}
-Let $g : J \to G$ be a morphism of $\QC$-schemes.
+Let $g : J \to G$ be a morphism of smooth groups schemes over $\Fq$.
 Let $f_g : H\times_G J\to J$
@@
 \begin{lemma}\label{lemma:finite-iso}
-Each finite quasicharacter sheaf $(f,\psi)$ in $\QCf(G)$ determines a
-canonical isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\QCf(G\times G)$.
+Each finite quasicharacter sheaf $(f,\psi)$ in $\rfQC(G)$ determines a
+canonical isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\rfQC(G\times G)$.
  \end{lemma}
@@
 and showing that, after passing from $C_1(G\times G)$ to
-$\QCf(G\times G)$, the resulting isomorphism,
+$\rfQC(G\times G)$, the resulting isomorphism,
 denoted by $\mu(f,\psi)$, is canonically determined by $(f,\psi)$.
@@
 diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G\times G)$.
-
+%
 While $\theta$ was canonical, $T$ was not, as it depended on the choice of a basis for $V$.
-However, after passing from $C_1(G\times G)$ to $\QCf(G\times G)$, the resulting isomorphism in $\QCf(G\times G)$
-$\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ is independent of the choice of basis for $V$.
+However, after passing from $C_1(G\times G)$ to $\rfQC(G\times G)$, the resulting isomorphism 
+$\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ in $\rfQC(G\times G)$ is independent of the choice of basis for $V$.
  \end{proof}
@@
 \begin{proposition}\label{prop:bounded}
- $\QCf(G)$ is equivalent to a full subcategory of $\QCb(G)$.
+ $\rfQC(G)$ is a full subcategory of $\rbQC(G)$.
 \end{proposition}
@@
 \begin{proof}
- To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \QCf(G) \to \QCb(G)$.
+ To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \rfQC(G) \to \rbQC(G)$.
 
@@
  This construction defines a full monoidal functor $L$ from $C(G)$ to the category $\Loc(G)$ of local systems on $G$ that
- commutes with pullback along any morphism of $\QC$-schemes,
+ commutes with pullback along any morphism of $\rQC$-schemes,
  as defined using Lemma~\ref{lemma:finite-pullback}.
@@
 
- By Lemma~\ref{lemma:finite-iso}, each $(f,\psi) \in \QCf(G)$ canonically determines
+ By Lemma~\ref{lemma:finite-iso}, each $(f,\psi) \in \rfQC(G)$ canonically determines
  an isomorphism
@@
  \]
- in $\QCf(G\times G)$.
+ in $\rfQC(G\times G)$.
  It follows immediately that the functor
  \[
- L_G  \ceq  L_{W}\vert_{\QCf(G)} : \QCf(G) \to \QCb(G),
+ L_G  \ceq  L_{W}\vert_{\rfQC(G)} : \rfQC(G) \to \rbQC(G),
  \]
@@
 
-On general $\QC$-schemes $G$, there are bounded quasicharacter sheaves which are not finite.  Identifying
-$\QCf(G)$ with its image under $B_G \circ L_G$, as defined in
+On general smooth group $\Fq$-schemes $G$, 
+there are bounded quasicharacter sheaves which are not finite.  
+Identifying $\rfQC(G)$ with its image under $B_G \circ L_G$, as defined in
 Proposition~\ref{prop:BG} and in the proof of Proposition~\ref{prop:bounded},
 we will see in Corollary~\ref{cor:bounded-and-finite} that
-a quasicharacter sheaf is finite if and only if its Trace of Frobenius has finite image.
+a rigid quasicharacter sheaf is finite if and only if its Trace of Frobenius has finite image.
 
@@
 
-When $G$ is connected, we may apply the classic function--sheaf dictionary.  In order to do so,
-however, we must relate our notion of quasicharacter sheaf to the sheaf side of the standard dictionary.
+For connected groups, the subcategories introduced in the previous two sections agree with $\rQC(G)$.
+
+\subsection{When rigid quasicharacter sheaves are finite}
+
+\begin{proposition}\label{prop:connected}
+  If $G$ is a connected commutative algebraic group over $\Fq$ then
+  the full subcategories $\rfQC(G) \hookrightarrow \rbQC(G) \hookrightarrow \rQC(G)$
+  appearing in Sections~\ref{sec:bounded} and \ref{sec:finite} are equivalences.
+\end{proposition}
+
+\begin{proof}
+  Observe that the forgetful functor $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$
+  sends rigid quasicharacter sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{deligne:80a}*{1.1.10}.
+  While is it not true that all Weil sheaves on $G$ descend to local systems on $G$,
+  we will see that those that appear in the image of this forgetful functor from rigid quasicharacter sheaves do.
+
+%When $G$ is connected, we may apply the classic function--sheaf dictionary.  
+%In order to do so, however, we must relate our notion of quasicharacter sheaf to the sheaf side of the standard dictionary.
 Choose any $\Fq$-rational point of $G$ and let $\bg$ be the geometric point on $G$ lying above $g$.
@@
 
-For connected groups, the subcategories introduced in the previous two sections agree with $\QC(G)$:
-
-\begin{proposition}\label{prop:connected}
-  If $G$ is a connected commutative algebraic group over $\Fq$ then
-  the full subcategories $\QCf(G) \hookrightarrow \QCb(G) \hookrightarrow \QC(G)$
-  appearing in Sections~\ref{sec:bounded} and \ref{sec:finite} are equivalences.
-\end{proposition}
-
-\begin{proof}
-  Observe that the forgetful functor $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$
-  sends quasicharacter sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{deligne:80a}*{1.1.10}.
-  While is it not true that all Weil sheaves on $G$ descend to local systems on $G$,
-  we will see that those that appear in the image of this forgetful functor from quasicharacter sheaves do.
-
   Since $G$ is connected, the geometric point $\bg$ determines
@@
   $\ell$-adic representations of $\W(G,\bg)$ \cite{deligne:80a}*{1.1.12}.
-  Now let $(\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$
+  Now let $(\gqcs{L},\mu,\phi)$ be a rigid quasicharacter sheaf on $G$
   and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$.
@@
   the latter appearing in the definition of $\qcs{L}$.
-  Then, as in Section~\ref{sec:bounded}, $(\qcs{L}_0,\mu_0)$ is an object in $\QCb(G)$
-  and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{L}_0,b_{G\times G}^*\mu_0)$ in $\QC(G)$.
-  Thus, the full and faithful functor $B_G : \QCb(G) \to \QC(G)$ from Section~\ref{sec:bounded}
+  Then, as in Section~\ref{sec:bounded}, $(\qcs{L}_0,\mu_0)$ is an object in $\rbQC(G)$
+  and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{L}_0,b_{G\times G}^*\mu_0)$ in $\rQC(G)$.
+  Thus, the full and faithful functor $B_G : \rbQC(G) \to \rQC(G)$ from Section~\ref{sec:bounded}
   is also essentially surjective, hence an equivalence.
 
-  In Section~\ref{sec:finite} we saw that $\QCf(G)$ is a full subcategory of $\QCb(G)$;
-  more precisely, we exhibited a full and faithful functor $L_G : \QCf(G) \to \QCb(G)$.
+  In Section~\ref{sec:finite} we saw that $\rfQC(G)$ is a full subcategory of $\rbQC(G)$;
+  more precisely, we exhibited a full and faithful functor $L_G : \rfQC(G) \to \rbQC(G)$.
   We now show that this functor is essentially surjective
@@
   Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$.
-  Then $\qcs{L}\ceq B_G(\qcs{L}_0,\mu_0)$ is a quasicharacter sheaf on $G$.
+  Then $\qcs{L}\ceq B_G(\qcs{L}_0,\mu_0)$ is a rigid quasicharacter sheaf on $G$.
   Recall the definition of the character $\trFrob{\qcs{L}} : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}.
@@
   Using \cite{laumon:87a}*{Th\'eor\`eme 1.1.2}, it follows that  $L(f,\psi) \iso \qcs{L}_0$ in $\Loc(G)$.
-  It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\qcs{L}_0,\mu_0)$ in $\QCb(G)$.
+  It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\qcs{L}_0,\mu_0)$ in $\rbQC(G)$.
   This completes the proof that $L_G $ is essentially surjective.
@@
 
-\begin{corollary}\label{cor:connected}
- If $G$ is a connected, commutative algebraic group over $\Fq$ then
- \[
-  \TrFrob{G} : \QCiso{G} \to G(\Fq)^*
- \]
- is an isomorphism of groups.
-\end{corollary}
-\begin{proof}
- It suffices\todo{Why is $T_G$ injective?} to observe that the group homomorphism
- $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$
- is surjective: each character $\chi \in G(\Fq)^*$ determines a finite quasicharacter
- sheaf $(\Lang,\chi^{-1})$ such that Trace of Frobenius of the quasicharacter sheaf
- $B_G (L_G(\Lang,\chi^{-1}))$ is $\chi$.
-\end{proof}
-
 As Proposition~\ref{prop:connected} shows,
 when $G$ is a connected algebraic group over $\Fq$,
-it is appropriate to replace quasicharacter sheaves on $G$
-with the conceptually simpler category $\QCf(G)$ of finite quasicharacter sheaves on $G$.
+it is appropriate to replace rigid quasicharacter sheaves on $G$
+with the conceptually simpler category $\rfQC(G)$ of finite quasicharacter sheaves on $G$.
 In this context, finite quasicharacter sheaves may also be apprehended as
@@
 between the category of finite quasicharacter sheaves on $G$ and
-the category of one-dimensional representations of $G(\Fq)^*$, thus
-providing an alternate proof of Corollary~\ref{cor:connected}.
+the category of one-dimensional representations of $G(\Fq)^*$.
+We will see an alternate proof of this fact in the next section; see Corollary~\ref{cor:connected}.
 
 In principle, something similar is possible in the more general
-context of this paper, where $G$ is a smooth commutative group scheme over $\Fq$, to which we now return.
-In this generality, however, neither of the full subcategories $\QCf(G) \subset \QCb(G) \subset \QC(G)$ are equivalences;
+context of this paper, where $G$ is a smooth commutative group scheme over $\Fq$. 
+%to which we now return.
+In this generality, however, neither of the full subcategories $\rfQC(G) \subset \rbQC(G) \subset \rQC(G)$ are equivalences;
 see the end of Section~\ref{sec:snake}.
-Nevertheless, every quasicharacter sheaf $(\gqcs{L},\mu,\phi)$ on $G$
+Nevertheless, every rigid quasicharacter sheaf $(\gqcs{L},\mu,\phi)$ on $G$
 determines a Weil sheaf $(\gqcs{L},\phi)$ on $G$
@@
 
+\subsection{Recovery}
+
+We are in a good position to understand $\rQC(G)$ when $G$ is a connected algebraic group over $\Fq$, since we can now describe objects and maps in this category in very concrete terms.
+We begin by recovering a classical result.
+
+\begin{corollary}\label{cor:connected}
+ If $G$ is a connected, commutative algebraic group over $\Fq$ then
+ \[
+  \TrFrob{G} : \rQCiso{G} \to G(\Fq)^*
+ \]
+ is an isomorphism of groups.
+\end{corollary}
+
+\begin{proof}
+ It suffices\todo{Explain why $T_G$ is injective.} to observe that the group homomorphism
+ $\TrFrob{G} : \rQCiso{G} \to G(\Fq)^*$
+ is surjective: each character $\chi \in G(\Fq)^*$ determines a finite quasicharacter
+ sheaf $(\Lang,\chi^{-1})$ such that Trace of Frobenius of the rigid quasicharacter sheaf
+ $B_G (L_G(\Lang,\chi^{-1}))$ is $\chi$.
+\end{proof}
+
+Morphisms in $\rQC(G)$ are also very simple.
+
+\begin{proposition}
+If $G$ is a connected algebraic group then $\Aut_{\rQC(G)}(\qcs{L})$ is . . . .
+\end{proposition}
+
+\begin{proof}
+Pick up from the proof of Proposition~\ref{prop:autornaught}.
+\end{proof}
+
 \section{The case of \'etale commutative group schemes} \label{sec:etale}
@@
 However, the function--sheaf dictionary is substantially different in the two cases.
-To see why, we begin by specializing the definition of quasicharacter sheaves to the case
+To see why, we begin by specializing the definition of rigid quasicharacter sheaves to the case
 of etale commutative group schemes,
@@
 \end{enumerate}
-Under this equivalence, a morphism $\alpha : \qcs{L} \to \qcs{L'}$ of quasicharacter sheaves on $G$ is given by
+Under this equivalence, a morphism $\alpha : \qcs{L} \to \qcs{L'}$ of rigid quasicharacter sheaves on $G$ is given by
 \begin{enumerate}
@@
 Our main tool for understanding this phenomenon
-is a group homomorphism from $\QCiso{G}$ to $\Hh^2(E^\bullet_G)$, defined in Section~\ref{sec:S}, for which the next two sections are preparation.
+is a group homomorphism from $\rQCiso{G}$ to $\Hh^2(E^\bullet_G)$, defined in Section~\ref{sec:S}, for which the next two sections are preparation.
 
@@
 
-\subsection{From quasicharacter sheaves to the total complex}\label{sec:S}
+\subsection{From rigid quasicharacter sheaves to the total complex}\label{sec:S}
 
@@
 \[
-S_G : \QCiso{G} \to \Hh^2(E^\bullet_G).
-\]
-Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
+S_G : \rQCiso{G} \to \Hh^2(E^\bullet_G).
+\]
+Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a rigid quasicharacter sheaf on $G$.
 For each geometric point $x\in {\bar G}$, choose a basis $\{ v_x \}$ for $\gqcs{L}_x$.
@@
 \begin{align*}
-S_G : \QCiso{G} &\to \Hh^2(E^\bullet_G)\\
+S_G : \rQCiso{G} &\to \Hh^2(E^\bullet_G)\\
 [\qcs{L}] &\mapsto [\alpha\oplus \beta].
@@
 \begin{remark}
-Although we will only use the group homomorphism $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$.
+Although we will only use the group homomorphism $S_G : \rQCiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$.
 However, the next result is false in that context.
@@
 \begin{proof}
-We first show that $S_G$ is injective.  Suppose $\qcs{L} \in \QCiso{G}$ with $S_G(\qcs{L}) = [\alpha \oplus \beta] = 0$,
+We first show that $S_G$ is injective.  Suppose $\qcs{L} \in \rQCiso{G}$ with $S_G(\qcs{L}) = [\alpha \oplus \beta] = 0$,
 so that $\alpha \oplus \beta = d\rho$ for some $\rho \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
@@
 defines an isomorphism $\qcs{L} \to (\EE)_G$.
-Since $\qcs{L} = 0 \in \QCiso{G}$, $S_G$ is injective.
+Since $\qcs{L} = 0 \in \rQCiso{G}$, $S_G$ is injective.
 
@@
 Then \ref{qc.1} holds since $d_G \alpha =0$ and \ref{qc.2} holds since $d_{\Weil{}}\alpha =d_G \beta$.
-Tracing the construction backward, we have defined a quasicharacter sheaf $\qcs{L}$ on $G$ with
+Tracing the construction backward, we have defined a rigid quasicharacter sheaf $\qcs{L}$ on $G$ with
 $S_G(\qcs{L}) = [\alpha\oplus\beta\oplus\gamma]$, showing that $S_G$ is surjective.
@@
 \begin{corollary}
-If $G$ is \'etale then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective.
+If $G$ is \'etale then $\TrFrob{G} : \rQCiso{G} \to G(\Fq)^*$ is surjective.
 \end{corollary}
@@
 \begin{proposition} \label{prop:etale-iso}
- If $G$ is \'etale then the map $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ induces an isomorphism of short exact sequences
+ If $G$ is \'etale then the map $S_G : \rQCiso{G}\to \Hh^2(E^\bullet_G)$ induces an isomorphism of short exact sequences
 \[
 \begin{tikzcd}
- 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \QCiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
+ 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \rQCiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
   0 \arrow{r} & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r} & 0.
@@
 In the introduction to this paper we noted that, when working with connected commutative algebraic groups over finite fields, Deligne's dictionary can be described using Weil sheaves $\qcs{L}$ for which there exists an isomorphism $m^* \qcs{L} \iso \qcs{L} \boxtimes\qcs{L}$, without keeping track of the isomorphism.
-In this section use that perspective to find a perfect dictionary between quasicharacter sheaves on $G$ and characters of $G(\Fq)$.
-
-\subsection{Quasicharacter sheaves}\label{sec:loose}
-
-\begin{definition}\label{def:lQC}
-Let $G$ be a smooth commutative group scheme over $\Fq$.
-A \emph{quasicharacter sheaf} on $G$ is a Weil sheaf $(\gqcs{L},\phi)$ on $G$
-for which $(\gqcs{L},\mu,\phi)$ is a rigid quasicharacter sheaf on $G$
-for some $\mu: \bm^* \gqcs{L} \to \gqcs{L} \boxtimes \gqcs{L}$.
-%The resulting objects lie in the essential image of the forgetful functor $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ from $\QC(G)$ to Weil sheaves on $G$.
-We form a category from quasicharacter sheaves by declaring that a morphism $(\gqcs{L},\phi) \to (\gqcs{L'},\phi')$ is a sheaf homomorphism $\alpha : \gqcs{L} \to \gqcs{L'}$ for which the two diagrams in Condition~\ref{QC.4} commute, for some choice of $\mu$, $\mu'$ such that $(\gqcs{L},\mu,\phi)$ and $(\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$.
-The category of quasicharacter sheaves on $G$ is denoted by $\lQC(G)$.
-\end{definition}
-
-The category of quasicharacter sheaves on $G$ is rigid monoidal and the functor $\QC(G) \to \lQC(G)$ is monoidal and essentially surjective but neither full nor faithful, generally.
-%
-Since objects in $\lQC(G)$ are Weil sheaves and since in the first diagram in Condition~\ref{QC.4} ensures that a morphism in $\lQC(G)$ is a morphism of Weil sheaves, it follows that $\lQC(G)$ is a subcategory of Weil sheaves on $G$.
-
-Since the trace of Frobenius makes sense for all Weil sheaves, as noted in \eqref{trWeil}, and since
-$\trFrob{(\gqcs{L},\phi)} = \trFrob{(\gqcs{L'},\phi')}$ when $(\gqcs{L},\phi) \iso (\gqcs{L'},\phi')$ in $\lQC(G)$,
-there is an evident meaning for the Trace of Frobenius
-\[
-\lTrFrob{G} : \lQCiso{G} \to G(\Fq)^*.
-\]
-Since $\QCiso{G}  \to G(\Fq)^*$ is surjective, by Theorem~\ref{thm:snake},
-it is clear that $\lTrFrob{G} : \lQCiso{G} \to G(\Fq)^*$ is a surjective group homomorphism.
-The main result of this paper, Theorem~\ref{thm:snake}, shows that $\lTrFrob{G} : \lQCiso{G} \to G(\Fq)^*$ is an isomorphism.
+In this section use that perspective to find a perfect dictionary between flabby quasicharacter sheaves on $G$ and characters of $G(\Fq)$.
 
@@
 \begin{tikzcd}
-\QC(0) \rar & \QC(\pi_0(G)) \arrow{r}{\pi_0^*} & \QC(G) \arrow{r}{\iota_0^*} & \QC(G^0) \rar & \QC(0)
+\rQC(0) \rar & \rQC(\pi_0(G)) \arrow{r}{\pi_0^*} & \rQC(G) \arrow{r}{\iota_0^*} & \rQC(G^0) \rar & \rQC(0)
 \end{tikzcd}
@@
 0 \rar &
-\QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
+\rQCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \rQCiso{G} \arrow{r}{\iota_0^*} & \rQCiso{G^0} \rar & 0.
 \end{tikzcd}
 \end{equation}
- Note that we found the groups $\QCiso{G^0}$
-and $\QCiso{\pi_0(G)}$
+ Note that we found the groups $\rQCiso{G^0}$
+and $\rQCiso{\pi_0(G)}$
 in Sections~\ref{sec:connected} and \ref{sec:etale}, respectively.
@@
 \begin{proposition}\label{prop:restriction}
-For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf
+For every rigid quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf
 $\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$.
-As a consequence, the restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
+As a consequence, the restriction functor $\iota_0^* : \rQC(G)\to \rQC(G^0)$ is essentially surjective.
 \end{proposition}
@@
   By Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}, every
-  quasicharacter sheaf on $G^0$ is isomorphic to a
+  rigid quasicharacter sheaf on $G^0$ is isomorphic to a
   finite quasicharacter sheaf on $G^0$,
@@
 %  0 \rar &
- \QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
+ \rQCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \rQCiso{G} \arrow{r}{\iota_0^*} & \rQCiso{G^0} \rar & 0.
   \end{tikzcd}
@@
 \begin{proof}
-The sequence is exact at $\QCiso{G^0}$ by Proposition~\ref{prop:restriction},
-so here we show that it is also exact at $\QCiso{G}$.
+The sequence is exact at $\rQCiso{G^0}$ by Proposition~\ref{prop:restriction},
+so here we show that it is also exact at $\rQCiso{G}$.
 First note that $\iota_0^* \circ \pi_0^*$ is trivial by Proposition~\ref{prop:pullback}.
-So it suffices to show that if $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$
+So it suffices to show that if $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a rigid quasicharacter sheaf on $G$
 with $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$ then $\qcs{L}$ is in the essential image of $\pi_0^*$.
@@
 Using \eqref{eq:qc}, it follows that \ref{qc.1}, \ref{qc.2} and \ref{qc.3} are satisfied for
-$\qcs{E} \ceq (\gqcs{E}_x, \mu_{x,y}, \phi_x)$, thus defining a quasicharacter sheaf on $\pi_0(G)$.
+$\qcs{E} \ceq (\gqcs{E}_x, \mu_{x,y}, \phi_x)$, thus defining a rigid quasicharacter sheaf on $\pi_0(G)$.
 
@@
 The resulting isomorphism $\gqcs{L} \to \pi_0^* \gqcs{E}$ satisfies \ref{QC.4},
-thus defining an isomorphism $\qcs{L} \to \pi_0^* \qcs{E}$ in $\QC(G)$.
+thus defining an isomorphism $\qcs{L} \to \pi_0^* \qcs{E}$ in $\rQC(G)$.
 \end{proof}
@@
 We saw in Proposition~\ref{prop:functorialG} that Trace of Frobenius
-$\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
+$\TrFrob{G} : \rQCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
 In this section we improve that result.
@@
     %0 \rar
-    & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
-    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
+    & \rQCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
+    & \rQCiso{G} \rar \dar{\TrFrob{G}} & \rQCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
     0 \rar & \pi_0(G)(\Fq)^* \rar \dar
@@
 The top row is also exact:
-  the surjectivity of $\QCiso{G} \to \QCiso{G^0}$ follows from Proposition~\ref{prop:restriction}
-  while exactness at $\QCiso{G}$ is given by Proposition~\ref{prop:middleexact}.
+  the surjectivity of $\rQCiso{G} \to \rQCiso{G^0}$ follows from Proposition~\ref{prop:restriction}
+  while exactness at $\rQCiso{G}$ is given by Proposition~\ref{prop:middleexact}.
   Now Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}
@@
 First, suppose $G$ is etale.
-Let $(\gqcs{E},\phi')$ be a quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{E},\phi')}=1$.
+Let $(\gqcs{E},\phi')$ be a rigid quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{E},\phi')}=1$.
 Let $\qcs{E} = (\gqcs{E},\mu,\phi')$ be a quasicharacter sheaf.
@@
 and let $\mu'$ be the indexed set of isomorphisms $\mu'_{x,y} : \EE \to \EE\otimes \EE$ defined by $1 \mapsto a(x,y) 1 \otimes 1$.
-Then $(\EE,\mu', 1)$ is a quasicharacter sheaf the isomorphisms $\gqcs{E}_x \to \EE$ defined by $v_x \mapsto 1$ gives an isomorphism $(\gqcs{E},\mu,\phi')\to ((\EE)_{\bar C},\mu', 1)$ in $\QC(G)$.
+Then $(\EE,\mu', 1)$ is a rigid quasicharacter sheaf the isomorphisms $\gqcs{E}_x \to \EE$ defined by $v_x \mapsto 1$ gives an isomorphism $(\gqcs{E},\mu,\phi')\to ((\EE)_{\bar C},\mu', 1)$ in $\rQC(G)$.
 It follows that $(\gqcs{E},\phi')\iso ((\EE)_{\bar G},1)$ in $\lQC(G)$, so $\lTrFrob{G}$ is injective.
@@
 Now let $G$ be arbitrary
-and let $(\gqcs{L},\phi)$ be a quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{L},\phi)}=1$.
-Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf.
+and let $(\gqcs{L},\phi)$ be a flabby quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{L},\phi)}=1$.
+Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a rigid quasicharacter sheaf.
 We saw above that $\ker \TrFrob{\pi_0(G)}\to \TrFrob{G}$ is surjective in this case,
-so $\qcs{L} = \pi_0^*\qcs{E}$ for some $\qcs{E}\in \QC(\pi_0(G))$.
+so $\qcs{L} = \pi_0^*\qcs{E}$ for some $\qcs{E}\in \rQC(\pi_0(G))$.
 Since $\trFrob{\qcs{L}}(g) = \trFrob{\qcs{E}}(\pi_0(g))$ and since $\pi_0 : G(\Fq) \to \pi_0(G)(\Fq)$ is surjective, $\trFrob{\qcs{E}}=1$.
 But now $\qcs{E} \iso ((\EE)_{\pi_0({\bar G})},\mu', 1)$ by the paragraph above.
-So $\qcs{L} = \pi_0^*\qcs{E} \iso \pi_0^*((\EE)_{\pi_0({\bar G})},\mu', 1) = ((\EE)_{\bar G},\pi_0^*\mu', \pi_0^*1)$ in $\QC(G)$.
+So $\qcs{L} = \pi_0^*\qcs{E} \iso \pi_0^*((\EE)_{\pi_0({\bar G})},\mu', 1) = ((\EE)_{\bar G},\pi_0^*\mu', \pi_0^*1)$ in $\rQC(G)$.
 It follows that $(\gqcs{L},\phi) \iso ((\EE)_{\bar G},1)$ in $\lQC(G)$.
@@
 Argue as in the first paragraph in the proof of Theorem~\ref{thm:snake},
-using the category $\lQC(G)$ in place of $\QC(G)$.
+using the category $\lQC(G)$ in place of $\rQC(G)$.
 \end{proof}
@@
 \begin{enumerate}
-\item $\qcs{L} \in \QC(G)$ is bounded if and only if $\trFrob{\qcs{L}}$ has bounded image,
-\item $\qcs{L}\in \QC(G)$ is finite if and only if $\trFrob{\qcs{L}}$ has finite image.
+\item $\qcs{L} \in \rQC(G)$ is bounded if and only if $\trFrob{\qcs{L}}$ has bounded image,
+\item $\qcs{L}\in \rQC(G)$ is finite if and only if $\trFrob{\qcs{L}}$ has finite image.
 \end{enumerate}
@@
 On the connected component
-$G^0$, all quasicharacter sheaves are bounded and finite by Proposition~\ref{prop:connected}.
+$G^0$, all rigid quasicharacter sheaves are bounded and finite by Proposition~\ref{prop:connected}.
 On the other hand, $G^0(\Fq)$ is finite by Lemma~\ref{lem:G0alg-grp} and thus Trace of Frobenius
@@
 In the case that $G$ is \'etale, which we now suppose,
-one can easily detect when a quasicharacter sheaf is bounded or finite.
+one can easily detect when a rigid quasicharacter sheaf is bounded or finite.
 With reference to Section~\ref{sec:S},
@@
 With Corollary~\ref{cor:bounded-and-finite} in hand
-we see that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves
+we see that all rigid quasicharacter sheaves on $G$ are finite quasicharacter sheaves
 when $G$ is a commutative algebraic group over $\Fq$;
@@
 are up to the task of geometrizing all characters of $G(\Fq)$ for smooth commutative group schemes $G$ since, in general, neither of the full subcategories
-$\QCf(G) \subset \QCb(G) \subset \QC(G)$ are equivalences.
+$\rfQC(G) \subset \rbQC(G) \subset \rQC(G)$ are equivalences.
 For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$:
-the quasicharacter sheaf on $G$ corresponding, under Theorem~\ref{thm:snake},
+the flabby quasicharacter sheaf on $G$ corresponding, under Theorem~\ref{thm:snake},
 to the character $1 \mapsto \ell$ is not a bounded quasicharacter sheaf,
-while the quasicharacter sheaf on $G$ corresponding
+while the flabby quasicharacter sheaf on $G$ corresponding
 to the character $1 \mapsto 1+ \ell$ is a bounded but not finite quasicharacter sheaf.
@@
     && \Hh^0(\Weil{},\Hh^2(C,\EEx)) \arrow[crossing over,->>]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(B,\EEx)) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(A,\EEx)) \arrow[crossing over]{dd}  &  &  \\
-    & \QCiso{C} \arrow[>->>]{dr}\arrow{rr} \arrow{dd}%{\TrFrob{C}}
-    && \QCiso{B} \arrow[>->]{dr} \arrow{rr} \arrow{dd}%{\TrFrob{B}}
-    && \QCiso{A} \arrow[>->>]{dr} \arrow{dd}%{\TrFrob{A}}
+    & \rQCiso{C} \arrow[>->>]{dr}\arrow{rr} \arrow{dd}%{\TrFrob{C}}
+    && \rQCiso{B} \arrow[>->]{dr} \arrow{rr} \arrow{dd}%{\TrFrob{B}}
+    && \rQCiso{A} \arrow[>->>]{dr} \arrow{dd}%{\TrFrob{A}}
     \arrow{rr}  &   & 0 & \\
@@
 \[
-\Hh^1(E^\bullet_{G^0}) \to \QCiso{\pi_0(G)} \to \QCiso{G} \to \QCiso{G^0} \to 0
+\Hh^1(E^\bullet_{G^0}) \to \rQCiso{\pi_0(G)} \to \rQCiso{G} \to \rQCiso{G^0} \to 0
 \]

### 2014-08-06 dictionary.tex
Adding short section on automorphisms

@@
 
+\todo{Find an appropriate place for this discussion}
+
+If $\rho_0 = 0$ then the second diagram for $y=0$ implies that $\rho_x = 0$ for all $x$.
+Conversely, if $\rho_0$ is nonzero then the second diagram for $y = -x$ implies that $\rho_x$ is nonzero for all $x$ and thus an isomorphism since $\gqcs{L}_x$ is one dimensional.
+Most of this paper focuses on the question of determining the isomorphism classes of objects; a complete understanding of the morphisms in $\rQC(G)$ also requires a description of the automorphisms of an arbitrary quasicharacter sheaf $\qcs{L}$.
+
+\begin{proposition}
+The trace map induces an isomorphism of groups
+\[
+\Aut(\qcs{L}) \cong \Hom(G(\bFq)_{\Weil{}}, \EEx).
+\]
+\end{proposition}
+
+\begin{proof}
+The second diagram in \ref{qc.4} shows that the association $x \mapsto \rho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first shows that it factors through $G(\bFq)_{\Weil{}}$.
+Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism then defining $\rho_x$ as multiplication by $\rho(x)$ will satisfy the two diagrams.
+Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the resulting bijection is actually a group ismorphism.
+\end{proof}
+
 We will see that the Trace of Frobenius may not provide complete

### 2014-08-08 dictionary.tex
Added r : V -> V \otimes V to finite QCS
Working on automorphism groups

@@
 
-In this section we define \emph{finite quasicharacter sheaves}, a further refinement
-of bounded quasicharacter sheaves; finite quasicharacter sheaves will play a role in Section \ref{sec:restriction}.
-
-The notion of a finite quasicharacter sheaf is informed
-by a certain perspective on local systems on connected groups.
+In this section we define \emph{finite quasicharacter sheaves}, 
+a notion informed by a certain perspective on local systems on connected groups.
+Finite quasicharacter sheaves will play a role in Section \ref{sec:restriction}.
+
+%The definition of finite quasicharacter sheaves will require several steps, beginning with the localization of a category introduced here.
+Consider the category $C(G)$ whose objects consist of triples $(f,\psi,r)$, where:
+\begin{itemize}
+\item $f : H\to G$ is a \emph{discrete isogeny} (a morphism of smooth commutative group schemes over $\Fq$ which is finite, surjective and \'etale and for which the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f = f^{-1}({\bar e)} = \Aut(f)$ is trivial);
+\item $\psi : \Aut(f)\to \Aut(V)$ is a finite-dimensional $\EE$-representation;
+\item $r : V \to V\otimes V$ is an injective linear transformation.
+\end{itemize}
+A morphism $(f,\psi,r) \to (f',\psi',r)$ in $C(G)$ is a pair $(\gamma,T)$, where:
+\begin{itemize}
+\item $\gamma : H' \to H$ is a morphism of group schemes such that $f\circ \gamma = f'$;
+\item $T: V\to V'$ is a linear transformation, equivariant for the action of
+$\Aut(f')$ on $V'$ by $\psi'$ and the action of $\Aut(f')$ on $V$ by $\psi \circ \gamma$,
+\end{itemize}
+such that
+\[
+\begin{tikzcd}
+\arrow{d}[swap]{T\otimes T} V\otimes V & \arrow{l}{r} V \arrow{d}{T} 
+%& \Aut(V) & \arrow[swap]{l}{\psi} \Aut(f) \arrow{r} & H \arrow{r}{f} & \arrow[equal]{d} G
+\\
+V'\otimes V' & \arrow{l}{r'} V' 
+%& \Aut(V') & \arrow[swap]{l}{\psi'} \arrow[swap]{u}{} \Aut(f') \arrow{r} & \arrow[swap]{u}{\gamma} H' \arrow{r}{f'} & G
+\end{tikzcd}
+\]
+commutes.
+
+We define a tensor product in $C(G)$ as follows.
+Let $(f,\psi,r)$ and $(f',\psi',r')$ be objects in $C(G)$.
+Write $f\times_G f' : H\times_G H' \to G$ for the product of $f$ and $f'$
+in the category of isogenies to $G$. We define an external tensor product
+$\psi \otimes\psi' :  \ker(f\times_G f') \to \Aut(V\otimes V')$ and a external sum
+$\psi \oplus\psi' :  \ker(f\times_G f') \to \Aut(V\oplus V')$
+using the canonical isomorphism $\ker(f\times_G f') \iso (\ker f)\times (\ker f')$.
+We may thus define $(f,\psi,r)\otimes(f',\psi',r') \ceq (f\times_G f' ,\psi\otimes\psi', r\otimes r')$ and
+$(f,\psi,r)\oplus(f',\psi',r')\ceq (f\times_G f' ,\psi\oplus\psi', r\oplus r')$. 
+To define duals in $C(G)$,
+let $V^\vee \ceq \Hom_\text{vec}(V,\EE)$ and $\psi^\vee : \ker f \to \Aut(V^\vee)$ be
+the dual representation.  We may then set $(f,\psi,r)^\vee \ceq (f,\psi^\vee, r^\vee)$ 
+where $r^\vee : V^\vee \to V^\vee \otimes V^\vee$ is the adjoint of $r$.
+These operations give $C(G)$ the structure of a tensor category.
+
+Now we localize $C(G)$.
+Let us say that $(\gamma,T)$ in $C(G)$ is a \emph{weak isomorphism} if $T$ is an isomorphism of vector spaces.  
+Let $W$ be the family of weak isomorphism and
+et $C(G)[W^{-1}]$ be the localization of $C(G)$ with respect to $W$, 
+in the sense of \cite{kashiwara-schapira:CatgoriesSheaves}*{Def 7.1.1}.
+Since weak isomorphisms in $C(G)$ form a \emph{right multiplicative system}, in the sense of \cite{kashiwara-schapira:CatgoriesSheaves}*{Def 7.1.5}, it follows from \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16} that morphisms in $C(G)[W^{-1}]$ are simple to describe:
+a morphism in $C(G)[W^{-1}]$ is an equivalence class of diagrams
+\[
+\begin{tikzcd}[column sep=30]
+   (f,\psi,r) \arrow{r}{(\gamma,T)} & (f',\psi',r') & \arrow[swap]{l}{(\gamma_1,T_1)}[swap]{\text{w-iso}} (f_1,\psi_1,V_1)
+   \end{tikzcd}
+\]
+ where $(\gamma,T) : (f,\psi,r) \to (f',\psi',r')$ is any map in $C(G)$
+ and $(\gamma_1, T_1) :  (f',\psi',r') \to (f_1,\psi_1,r_1)$ is a weak isomorphism in $C(G)$;
+for the equivalence relation on these diagrams, see \cite{kashiwara-schapira:CatgoriesSheaves}*{(7.1.3)}.
+
+It is straightforward to verify that the subcategory $C_1(G)$ of $C(G)$ consisting of $(f,\psi,r)$ for which $\psi$ is one-dimensional, is a full, rigid monoidal subcategory of $C(G)$ and further, that the family $W_1$ of weak isomorphisms in $C_1(G)$ is a right multiplicative system.
+
+\begin{definition}
+The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\rfQC(G)$,
+is the rigid monoidal category $C_1(G)[W_1^{-1}]$ obtained by localizing $C_1(G)$ at weak isomorphisms $W_1$.
+\end{definition}
+
+\begin{remark}
 Recall that every geometric point $\bg$ on a connected scheme $G$
@@
  not adapt well to non-connected $G$, a perspective using finite \'etale covers does.
-
-The definition of finite quasicharacter sheaves will require several steps,
-beginning with the localization of a category introduced here.
-Let us say that a morphism $f : H\to G$ of smooth commutative group schemes over $\Fq$ is a \emph{discrete isogeny}
-if it is finite, surjective, \'etale and the action of $\Gal(\bFq/\Fq)$ on the \'etale group
-scheme $\ker f = f^{-1}({\bar e)} = \Aut(f)$ is trivial.
-Consider the category $C(G)$ whose objects consist of triples $(f,\psi,V)$, where
-\begin{itemize}
-\item $f : H\to G$ is a discrete isogeny of smooth commutative group schemes over $\Fq$,
-\item $\psi : \ker f\to \Aut(V)$ is a representation on a finite-dimensional $\EE$-vector space $V$.
-\end{itemize}
-A morphism $(f,\psi,V) \to (f',\psi',V')$ in $C(G)$ is a pair $(\gamma,T)$, where
-\begin{itemize}
-\item $\gamma : H' \to H$ is a morphism of group schemes such that $f' = f\circ \gamma$,
-\item $T : V\to V'$ is a linear transformation, equivariant for the action of
-$\ker f'$ on $V'$ by $\psi'$ and the action of $\ker f'$ on $V$ by $\psi \circ \alpha$.
-\[
-\begin{tikzcd}
-V \arrow{d}{T} & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} & \arrow[equal]{d} G\\
-V' & \Aut(V') & \arrow[swap]{l}{\psi'} \arrow[swap]{u}{\gamma\vert_{\ker f'}} \ker f' \arrow[hook]{r} & \arrow[swap]{u}{\gamma} H' \arrow{r}{f'} & G
-\end{tikzcd}
-\]
-\end{itemize}
-
-We put a tensor category structure on $C(G)$ as follows.
-Let $(f,\psi,V)$ and $(f',\psi',V')$ be objects in $C(G)$.
-Write $f\times_G f' : H\times_G H' \to G$ for the product of $f$ and $f'$
-in the category of isogenies to $G$. We define an external tensor product
-$\psi \otimes\psi' :  \ker(f\times_G f') \to \Aut(V\otimes V')$ and a external sum
-$\psi \oplus\psi' :  \ker(f\times_G f') \to \Aut(V\oplus V')$
-using the canonical isomorphism $\ker(f\times_G f') \iso (\ker f)\times (\ker f')$.
-We may thus define $(f,\psi,V)\otimes(f',\psi',V') \ceq (f\times_G f' ,\psi\otimes\psi', V\otimes V')$ and
-$(f,\psi,V)\oplus(f',\psi',V')\ceq (f\times_G f' ,\psi\oplus\psi', V\oplus V')$. To define duals in $C(G)$,
-let $V^\vee \ceq \Hom_\text{vec}(V,\EE)$ and $\psi^\vee : \ker f \to \Aut(V^\vee)$ be
-the dual representation.  We may then set $(f,\psi,V)^\vee \ceq (f,\psi^\vee, V^\vee)$.
-These operations give $C(G)$ the structure of a tensor category.
-
-Now we localize $C(G)$.
-Let us say that $(\gamma,T)$ in $C(G)$ is a \emph{weak isomorphism} if $T$ is an isomorphism of vector spaces.  
-Let $W$ be the family of weak isomorphism and
-et $C(G)[W^{-1}]$ be the localization of $C(G)$ with respect to $W$, 
-in the sense of \cite{kashiwara-schapira:CatgoriesSheaves}*{Def 7.1.1}.
-Since weak isomorphisms in $C(G)$ form a \emph{right multiplicative system}, in the sense of \cite{kashiwara-schapira:CatgoriesSheaves}*{Def 7.1.5}, it follows from \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16} that morphisms in $C(G)[W^{-1}]$ are simple to describe:
-a morphism in $C(G)[W^{-1}]$ is an equivalence class of diagrams
-\[
-\begin{tikzcd}[column sep=30]
-   (f,\psi,V) \arrow{r}{(\gamma,T)} & (f',\psi',V') & \arrow[swap]{l}{(\gamma_1,T_1)}[swap]{\text{w-iso}} (f_1,\psi_1,V_1)
-   \end{tikzcd}
-\]
- where $(\gamma,T) : (f,\psi,V) \to (f',\psi',V')$ is any map in $C(G)$
- and $(\gamma_1, T_1) :  (f',\psi',V') \to (f_1,\psi_1,V_1)$ is a weak isomorphism in $C(G)$;
-for the equivalence relation on these diagrams, see \cite{kashiwara-schapira:CatgoriesSheaves}*{(7.1.3)}.
-
-It is straightforward to verify that the subcategory $C_1(G)$ of $C(G)$ consisting of $(f,\psi,V)$ for which $\psi$ is one-dimensional, is a full, rigid monoidal subcategory of $C(G)$ and further, that the family $W_1$ of weak isomorphisms in $C_1(G)$ is a right multiplicative system.
-
-\begin{definition}
-The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\rfQC(G)$,
-is the rigid monoidal category $C_1(G)[W_1^{-1}]$ obtained by localizing $C_1(G)$ at weak isomorphisms $W_1$.
-\end{definition}
-
-Trivial morphisms in $\rfQC(G)$ are defined as follows. Let $(f,\psi,V)$ and $(f_1,\psi_1,V_1)$ be finite quasicharacter sheaves on $G$.  
-Form $(f\times_G f_1,1\otimes \psi_1, V\otimes V_1)$ in $C_1(G)$. 
+\end{remark}
+
+Later in the paper we will make a study of isomorphism classes of objects in $\rfQC{G}$. Here we focus on morphisms in this category.
+
+\begin{proposition}\label{prop:autornaught}
+Every morphism in $\rfQC(G)$ is either an isomorphism or trivial.
+Moreover, for every finite quasicharacter sheaf $(f,\psi,r)$, the group $\Aut_{\rfQC(G)}(f,\psi,r)$ is trivial.
+\end{proposition}
+
+\begin{proof}
+Trivial morphisms in $\rfQC(G)$ are defined as follows. Let $(f,\psi,r)$ and $(f_1,\psi_1,r_1)$ be finite quasicharacter sheaves on $G$.  
+Form $(f\times_G f_1,1\otimes \psi_1, r\otimes r_1)$ in $C_1(G)$. 
 Let $0 : V \to V\otimes V_1$ be the trivial linear transformation. 
@@
 
-\begin{proposition}\label{prop:autornaught}
-Every morphism in $\rfQC(G)$ is either an isomorphism or trivial.
-\todo{I may add something here about $\Aut_{\rfQC(G)}(f,\psi,V)$.}
-\end{proposition}
-
-\begin{proof}
 Let $(f,\psi,V)$ and $(f_1,\psi_1,V_1)$ be finite quasicharacter sheaves on $G$. 

### 2014-08-08 dictionary.tex
Working on Aut for finite QCS

@@
 
-Later in the paper we will make a study of isomorphism classes of objects in $\rfQC{G}$. Here we focus on morphisms in this category.
+Later in the paper we will make a study of isomorphism classes of objects in $\rfQC(G)$. Here we focus on morphisms in this category.
 
@@
 \begin{proof}
+\todo{This proof is under construction.}
 Trivial morphisms in $\rfQC(G)$ are defined as follows. Let $(f,\psi,r)$ and $(f_1,\psi_1,r_1)$ be finite quasicharacter sheaves on $G$.  

### 2014-08-10 dictionary.tex
Moving sections around and removing references to flabby quasicharacter sheaves

--- 2014-08-08 dictionary.tex
@@
 \newcommand{\lQCiso}[1]{\lQC(#1)_{/\text{iso}}}
-\newcommand{\rQC}{{\QC_{\text{rig}}}}
-\newcommand{\rbQC}{{\QC_0}}
-\newcommand{\rfQC}{{\QC_\text{fin}}}
-\newcommand{\rQCiso}[1]{\rQC(#1)_{/\text{iso}}}
-\newcommand{\rbQCiso}[1]{\rbQC(#1)_{/\text{iso}}}
-\newcommand{\rfQCiso}[1]{\rfQC(#1)_{/\text{iso}}}
+\newcommand{\bQC}{{\QC_0}}
+\newcommand{\fQC}{{\QC_\text{fin}}}
+\newcommand{\QCiso}[1]{\QC(#1)_{/\text{iso}}}
+\newcommand{\bQCiso}[1]{\bQC(#1)_{/\text{iso}}}
+\newcommand{\fQCiso}[1]{\fQC(#1)_{/\text{iso}}}
 \newcommand{\trFrob}[1]{t_{#1}}
@@
 
-%In order to describe the main result of this paper with more precision,
 Let us briefly review how Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields \cite{deligne:SGA4.5}*{sommes trig.} translates characters into local systems.
@@
 Both issues are addressed in the main definition of this paper:
-A \emph{rigid quasicharacter sheaf} on $G$ is a triple $\qcs{L}\ceq
+A \emph{quasicharacter sheaf} on $G$ is a triple $\qcs{L}\ceq
 (\gqcs{L},\mu,\phi)$ where $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ of rank~one and $\mu: m^*
 \gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms satisfying natural compatibility conditions; here $\Frob{G}$ is the Frobenius automorphism of ${\bar G}$.
-A \emph{flabby quasicharacter sheaf} on $G$ is a Weil sheaf $(\gqcs{L},\phi)$ on $G$
-for which $(\gqcs{L},\mu,\phi)$ is a rigid quasicharacter sheaf on $G$, for some $\mu$.
-The difference between these two notions is detected by $\Hh^2(\pi_0({\bar G}),\EEx)$, where $\pi_0({\bar G})$ is the component group for ${\bar G}$.
-%namely, when $\Hh^2(\pi_0({\bar G}),\EEx)$ is non-trivial, if $(\gqcs{L},\phi)$ is a quasicharacter sheaf on $G$ then there are many $\mu$ for which $(\gqcs{L},\mu,\phi)$ is a rigid quasicharacter sheaf on $G$;
-%
  In the main result of this paper, Theorem~\ref{thm:snake},
-we form a rigid monoidal category $\lQC(G)$ of flabby quasicharacter sheaves on $G$
+we form a rigid monoidal category $\lQC(G)$ of quasicharacter sheaves on $G$
 and show that the Trace of Frobenius provides a functorial group isomorphism
@@
 \end{equation}
+\todo{change to remove flabbyness}
 
@@
 %\subsection*{Structure of the paper}
+\todo{Describe the overall structure of the paper in enough detail that one can follow the argument; include snake lemma diagram}
 
@@
 After setting some basic notation in Section~\ref{sec:notation},
-in Section~\ref{sec:category} we define rigid quasicharacter sheaves and give an interpretation of
+in Section~\ref{sec:category} we define quasicharacter sheaves and give an interpretation of
 them as Weil sheaves equipped with an isomorphism of the form \eqref{introbox}.
@@
 one direction of the function--sheaf dictionary.
-We define pullbacks and products of rigid quasicharacter sheaves in Section~\ref{sec:pullback}, and use
+We define pullbacks and products of quasicharacter sheaves in Section~\ref{sec:pullback}, and use
 them to prove a functoriality result on Trace of Frobenius.
-In Section~\ref{sec:basechange} we study how rigid quasicharacter sheaves behave under base change
+In Section~\ref{sec:basechange} we study how quasicharacter sheaves behave under base change
 and Weil restriction.
 Sections~\ref{sec:bounded} and \ref{sec:finite} describe bounded quasicharacter sheaves and finite quasicharacter sheaves, respectively,
-forming two important subcategories of $\rQC(G)$.
+forming two important subcategories of $\QC(G)$.
 %These subcategories play a key role in the proof of Proposition~\ref{prop:restriction}.
-In Section \ref{sec:connected} we show that all rigid quasicharacter sheaves on $G$ are finite quasicharacter sheaves when $G$ is connected, and that Trace of Frobenius is an isomorphism in this case.
+In Section \ref{sec:connected} we show that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves when $G$ is connected, and that Trace of Frobenius is an isomorphism in this case.
 We shift to \'etale group schemes $G$ in Section~\ref{sec:etale} and find a cohomological interpretation
-of rigid quasicharacter sheaves in this case.
+of quasicharacter sheaves in this case.
 In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
-induces an essentially surjective functor of rigid quasicharacter sheaves.
-Section~\ref{sec:snake} presents the main theorem of this paper: Trace of Frobenius
-is a functorial isomorphism from isomorphism classes of flabby quasicharacter sheaves on $G$
-to characters of $G(\Fq)$.
-
-Comments about Joseph Bernstein's comments?
+induces an essentially surjective functor of quasicharacter sheaves.
+%Section~\ref{sec:snake} presents the main theorem of this paper: Trace of Frobenius
+%is a functorial isomorphism from isomorphism classes of flabby quasicharacter sheaves on $G$
+%to characters of $G(\Fq)$.
+
+\todo{Comments about Joseph Bernstein's comments?}
 
@@
 over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.
-%For the sake of brevity, we define a \emph{$\rQC$-scheme} to be such a $G$ with the additional property that the geometric component group of $G$ is finitely generated.
-This last condition is only needed in the proof of Lemma \ref{lemma:section}.
-A morphism of $\rQC$-schemes is a morphism of group schemes over $\Fq$.
 
@@
 
-\subsection{Rigid quasicharacter sheaves}\label{sec:category}
+\subsection{The category of quasicharacter sheaves}\label{sec:category}
 
 \begin{definition}\label{def:QC}
-A \emph{rigid quasicharacter sheaf on $G$} is a triple
+A \emph{quasicharacter sheaf on $G$} is a triple
 $\qcs{L}\ceq (\gqcs{L},\mu,\phi)$ where:
@@
 
-Morphisms in the category of rigid quasicharacter sheaves on $G$, denoted by $\rQC(G)$, are defined in the natural way:
+Morphisms in the category of quasicharacter sheaves on $G$, denoted by $\QC(G)$, are defined in the natural way:
 \begin{enumerate}
 \labitem{(QC.4)}{QC.4} if $\qcs{L} = (\gqcs{L},\mu,\phi)$ and
-  $\qcs{L'} = (\gqcs{L'},\mu',\phi')$ are rigid quasicharacter sheaves on $G$ then
+  $\qcs{L'} = (\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$ then
   a morphism $\qcs{L} \to \qcs{L}'$ is a map $\alpha : \gqcs{L} \to \gqcs{L'}$
@@
 
-The category $\rQC(G)$ of rigid quasicharacter sheaves on $G$ is a rigid monoidal category
+The category $\QC(G)$ of quasicharacter sheaves on $G$ is a rigid monoidal category
 \cite{etingof:09a}*{\S1.10} under the tensor product
@@
 $\sheafHom(\ - \ ,\EE)$.
-The category of rigid quasicharacter sheaves on $G$ is not abelian, so $\rQC(G)$
+The category of quasicharacter sheaves on $G$ is not abelian, so $\QC(G)$
 is not a tensor category in the sense of \cite{deligne:02a}*{0.1}.
-This rigid monoidal category structure for $\rQC(G)$ gives the set $\rQCiso{G}$
-of isomorphism classes in $\rQC(G)$ the structure of a group.
-
-\subsection{Flabby quasicharacter sheaves}\label{sec:loose}
-
-Observe that the rule $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ defines a forgetful functor from rigid quasicharacter
-sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
+This rigid monoidal category structure for $\QC(G)$ gives the set $\QCiso{G}$
+of isomorphism classes in $\QC(G)$ the structure of a group.
+
+%Observe that the rule $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ defines a forgetful functor from quasicharacter
+%sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
 %
@@
 
-\begin{definition}\label{def:lQC}
-Let $G$ be a smooth commutative group scheme over $\Fq$.
-A \emph{flabby quasicharacter sheaf} on $G$ is a Weil sheaf $(\gqcs{L},\phi)$ on $G$
-for which $(\gqcs{L},\mu,\phi)$ is a rigid quasicharacter sheaf on $G$
-for some $\mu: \bm^* \gqcs{L} \to \gqcs{L} \boxtimes \gqcs{L}$.
-%The resulting objects lie in the essential image of the forgetful functor $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ from $\rQC(G)$ to Weil sheaves on $G$.
-We form the category of flabby quasicharacter sheaves by declaring that a morphism $(\gqcs{L},\phi) \to (\gqcs{L'},\phi')$ is a sheaf homomorphism $\alpha : \gqcs{L} \to \gqcs{L'}$ for which the two diagrams in Condition~\ref{QC.4} commute, for some choice of $\mu$, $\mu'$ such that $(\gqcs{L},\mu,\phi)$ and $(\gqcs{L'},\mu',\phi')$ are rigid quasicharacter sheaves on $G$.
-The category of flabby quasicharacter sheaves on $G$ is denoted by $\lQC(G)$.
-\end{definition}
-
-Since objects in $\lQC(G)$ are Weil sheaves and since in the first diagram in Condition~\ref{QC.4} ensures that a morphism in $\lQC(G)$ is a morphism of Weil sheaves, it follows that $\lQC(G)$ is a subcategory of Weil sheaves on $G$.
-%
-Like $\rQC(G)$, the category $\lQC(G)$ of quasicharacter sheaves on $G$ is rigid monoidal.
-The functor $\rQC(G) \to \lQC(G)$ is monoidal and essentially surjective but neither full nor faithful, generally.
-%
-
-\subsection{Trace of Frobenius}\label{sec:Frob}
-
-We now introduce a tool which will help us understand isomorphism classes of objects in $\rQCiso{G}$ and $\lQCiso{G}$.
-
-Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
-determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$. 
-Together with the canonical isomorphism $(\Frob{G}^*\gqcs{L})_{\bg} \iso  \gqcs{L}_{\Frob{G}(\bg)}$, in this way the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gqcs{L}_{\bg}$; let $\trace(\phi_{\bg};\gqcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gqcs{L}_{\bg})$ and let $\trFrob{(\gqcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by
-\begin{equation}\label{trWeil}
-%\begin{equation}\label{trWeil}
-\trFrob{(\gqcs{L},\phi)}(g) \ceq \trace(\phi_{\bg};\gqcs{L}_{\bg}),
-%\end{equation}
-\end{equation}
-commonly called the {\em trace of Frobenius of $(\gqcs{L},\phi)$}.
-Note that if $(\gqcs{L},\phi) \iso (\gqcs{L'},\phi')$ as Weil sheaves, 
-then $\trFrob{(\gqcs{L},\phi)} = \trFrob{(\gqcs{L'},\phi')}$ as functions on $G(\Fq)$.
-
-Now suppose $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a rigid quasicharacter sheaf on $G$.
-The isomorphism $\mu : \bm^* \gqcs{L} \to \LxL$ together with
-\ref{QC.3} guarantee
-that the function $\trFrob{(\qcs{L},\phi)} : G(\Fq)\to \EEx$ is a group homomorphism.  
-Moreover, this group homomorphism is insensitive to $\phi$ in the sense 
-that if $(\gqcs{L},\mu,\phi)$ and $(\gqcs{L},\mu,\phi')$ are rigid quasicharacter sheaves, then $\trFrob{(\qcs{L},\phi)} = \trFrob{(\qcs{L},\phi')}$. \todo{Sketch proof?}
-This justifies abbreviating $\trFrob{(\gqcs{L},\phi)}$ to $\trFrob{\qcs{L}}$ in this case.
-The diagram below defines two group homomorphisms, both denoted $\TrFrob{G}$ and both called the \emph{Trace of Frobenius} for $G$; we trust that context will remove any ambiguity regarding this notation.
-\[
-\begin{tikzcd}
-\rQCiso{G} \arrow{rr} \arrow{dr}[swap]{\qcs{L} \mapsto t_{\qcs{L}}}{\TrFrob{G}} && \arrow{dl}[swap]{\TrFrob{G}}{(\gqcs{L},\phi) \mapsto t_{\gqcs{L},\phi}} \lQCiso{G} \\
-& G(\Fq)^* & 
-\end{tikzcd}
-\]
-As remarked above, the group homomorphism $\rQCiso{G} \to \lQCiso{G}$ is surjective;
-we will see that $\rQCiso{G} \to \lQCiso{G}$ need not be injective.
-However, in Theorem~\ref{thm:snake}, we will see that the group homomorphism $\rQCiso{G} \to G(\Fq)^*$ is surjective
-while the main result of this paper, Theorem~\ref{thm:snake}, 
-shows that $\lQCiso{G} \to G(\Fq)^*$ is an isomorphism.
-
-\begin{proposition}\label{prop:functorialG}
-Trace of Frobenius $\TrFrob{G} : \rQCiso{G} \to G(\Fq)^*$ is a natural transformation
-between the two contravariant additive functors
-\begin{align*}
-F_1 : G &\mapsto \rQCiso{G} \\
-F_2 : G &\mapsto G(\Fq)^*
-\end{align*}
-from the category of smooth commutative group schemes over $\Fq$ to the category of abelian groups.
-Likewise, for $\TrFrob{G} : \lQCiso{G} \to G(\Fq)^*$, {\it mut.\hskip-1pt mut.}
-\end{proposition}
-
-The proof of Proposition~\ref{prop:functorialG} will be given at the end of Section~\ref{sec:pullback}.
-
 \subsection{Pull-back and products}\label{sec:pullback}
@@
   \begin{align*}
-  f^* : \rQC(G) &\to \rQC(H) \\
+  f^* : \QC(G) &\to \QC(H) \\
   (\gqcs{L},\mu,\phi) &\mapsto (\bf^*\gqcs{L},(\bfxf)^*\mu,\bf^*F)
@@
   \begin{tikzcd}[row sep=20, column sep=30]
-   \rQCiso{G} \rar{f^*} \arrow[swap]{d}{\TrFrob{G}} & \rQCiso{H} \dar{\TrFrob{H}} \\
+   \QCiso{G} \rar{f^*} \arrow[swap]{d}{\TrFrob{G}} & \QCiso{H} \dar{\TrFrob{H}} \\
    G(\Fq)^* \rar & H(\Fq)^*
@@
   of $f^*$ on morphisms of quasicharacter sheaves; arguing as above shows that $f^*$ is
-  a functor from $\rQC(G)$ to $\rQC(H)$.  Since tensor products commute with pullback in schemes,
-  $f^* : \rQC(G) \to \rQC(H)$ is a monoidal functor.
-  The diagram relating $f^* : \rQC(G) \to \rQC(H)$, $f^* : G(k)^* \to H(k)^*$ and Trace of Frobenius
+  a functor from $\QC(G)$ to $\QC(H)$.  Since tensor products commute with pullback in schemes,
+  $f^* : \QC(G) \to \QC(H)$ is a monoidal functor.
+  The diagram relating $f^* : \QC(G) \to \QC(H)$, $f^* : G(k)^* \to H(k)^*$ and Trace of Frobenius
   commutes by \cite{laumon:87a}*{1.1.1.2}, where the ambient
@@
 
-We end this section with a simple result on products of rigid quasicharacter sheaves,
+We end this section with a simple result on products of quasicharacter sheaves,
 which is needed to show that the isomorphism above is functorial.
@@
 \[
-\rQC(G_1)\times \rQC(G_2) \to \rQC(G_1\times G_2)
+\QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)
 \]
@@
 \begin{tikzcd}[column sep=60]
-\arrow{d}{\TrFrob{G_1} \times \TrFrob{G_2}} \rQCiso{G_1}\times \rQCiso{G_2} \arrow{r}{\boxtimes}
-& \arrow{d}{\TrFrob{G_1\times G_2}} \rQCiso{G_1\times G_2}\\
+\arrow{d}{\TrFrob{G_1} \times \TrFrob{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes}
+& \arrow{d}{\TrFrob{G_1\times G_2}} \QCiso{G_1\times G_2}\\
 (G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
@@
 \begin{proof}
-The only non-trivial part of the proof is to show that $\boxtimes : \rQC(G_1)\times \rQC(G_2) \to \rQC(G_1\times G_2)$
+The only non-trivial part of the proof is to show that $\boxtimes : \QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)$
 is essentially surjective, so we will only address that point here.
@@
 
-Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a rigid quasicharacter sheaf on $G$.
+Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
 Set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$;
-by Proposition~\ref{prop:pullback}, $\qcs{L}_1$ a rigid quasicharacter sheaf on $G_1$
-and $\qcs{L}_2$ is a rigid quasicharacter sheaf on $G_2$.
+by Proposition~\ref{prop:pullback}, $\qcs{L}_1$ a quasicharacter sheaf on $G_1$
+and $\qcs{L}_2$ is a quasicharacter sheaf on $G_2$.
 We will obtain an isomorphism $\qcs{L} \iso  \qcs{L}_1\boxtimes \qcs{L}_2$.
@@
 
-\begin{proof}[Proof of Proposition~\ref{prop:functorialG}]
+\subsection{Trace of Frobenius}\label{sec:Frob}
+
+We now introduce a tool which will help us understand isomorphism classes of objects in $\QCiso{G}$ and $\lQCiso{G}$.
+
+Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
+determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$. 
+Together with the canonical isomorphism $(\Frob{G}^*\gqcs{L})_{\bg} \iso  \gqcs{L}_{\Frob{G}(\bg)}$, in this way the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gqcs{L}_{\bg}$; let $\trace(\phi_{\bg};\gqcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gqcs{L}_{\bg})$ and let $\trFrob{(\gqcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by
+\begin{equation}\label{trWeil}
+%\begin{equation}\label{trWeil}
+\trFrob{(\gqcs{L},\phi)}(g) \ceq \trace(\phi_{\bg};\gqcs{L}_{\bg}),
+%\end{equation}
+\end{equation}
+commonly called the {\em trace of Frobenius of $(\gqcs{L},\phi)$}.
+Note that if $(\gqcs{L},\phi) \iso (\gqcs{L'},\phi')$ as Weil sheaves, 
+then $\trFrob{(\gqcs{L},\phi)} = \trFrob{(\gqcs{L'},\phi')}$ as functions on $G(\Fq)$.
+
+Now suppose $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$.
+The isomorphism $\mu : \bm^* \gqcs{L} \to \LxL$ together with
+\ref{QC.3} guarantee
+that the function $\trFrob{(\qcs{L},\phi)} : G(\Fq)\to \EEx$ is a group homomorphism.  
+Moreover, this group homomorphism is insensitive to $\phi$ in the sense 
+that if $(\gqcs{L},\mu,\phi)$ and $(\gqcs{L},\mu,\phi')$ are quasicharacter sheaves, then $\trFrob{(\qcs{L},\phi)} = \trFrob{(\qcs{L},\phi')}$. \todo{Sketch proof?}
+This justifies abbreviating $\trFrob{(\gqcs{L},\phi)}$ to $\trFrob{\qcs{L}}$ in this case.
+The diagram below defines two group homomorphisms, both denoted $\TrFrob{G}$ and both called the \emph{Trace of Frobenius} for $G$; we trust that context will remove any ambiguity regarding this notation.
+\[
+\begin{tikzcd}
+\QCiso{G} \arrow{rr} \arrow{dr}[swap]{\qcs{L} \mapsto t_{\qcs{L}}}{\TrFrob{G}} && \arrow{dl}[swap]{\TrFrob{G}}{(\gqcs{L},\phi) \mapsto t_{\gqcs{L},\phi}} \lQCiso{G} \\
+& G(\Fq)^* & 
+\end{tikzcd}
+\]
+As remarked above, the group homomorphism $\QCiso{G} \to \lQCiso{G}$ is surjective;
+we will see that $\QCiso{G} \to \lQCiso{G}$ need not be injective.
+However, in Theorem~\ref{thm:snake}, we will see that the group homomorphism $\QCiso{G} \to G(\Fq)^*$ is surjective
+while the main result of this paper, Theorem~\ref{thm:snake}, 
+shows that $\lQCiso{G} \to G(\Fq)^*$ is an isomorphism.
+
+\begin{proposition}\label{prop:functorialG}
+Trace of Frobenius $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a natural transformation
+between the two contravariant additive functors
+\begin{align*}
+F_1 : G &\mapsto \QCiso{G} \\
+F_2 : G &\mapsto G(\Fq)^*
+\end{align*}
+from the category of smooth commutative group schemes over $\Fq$ to the category of abelian groups.
+Likewise, for $\TrFrob{G} : \lQCiso{G} \to G(\Fq)^*$, {\it mut.\hskip-1pt mut.}
+\end{proposition}
+
+\begin{proof}
 The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
@@
 
-\subsection{Base change}\label{sec:basechange}
-
-When using quasicharacter sheaves to study characters, it is useful to understand
-how quasicharacter sheaves behave under change of fields.
-Let $k'$ be a finite extension of $k$. Then $k \hookrightarrow k'$ induces a group homomorphism
-$i_{k'/k} : G(k) \hookrightarrow G(k')$ and thus a homomorphism
+\section{The case of \'etale commutative group schemes} \label{sec:etale}
+
+%\subsection{Quasicharacter sheaves, revisited}
+
+\'Etale group schemes form a counterpoint to connected groups,
+since the component group of a smooth commutative group scheme
+is an \'etale group scheme \cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
+However, the function--sheaf dictionary is substantially different in the two cases.
+To see why, we begin by specializing the definition of quasicharacter sheaves to the case
+of etale commutative group schemes,
+using the equivalence $G \mapsto G(\bFq)$
+from the category of \'etale group schemes over $\Fq$ to the category of groups equipped
+with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group.
+Under this equivalence, a quasicharacter sheaf on an etale commutative group scheme $G$ over $\Fq$ is given by the data of:
+\begin{enumerate}
+ \labitem{(qc.1)}{qc.1} an indexed set of one-dimensional
+  $\EE$-vector spaces $\gqcs{L}_x$, as $x$ runs over
+  $G(\bFq)$;
+
+ \labitem{(qc.2)}{qc.2} an indexed set of isomorphisms
+  $\mu_{x,y} : \gqcs{L}_{x+y} \xrightarrow{\iso} \gqcs{L}_{x} \otimes\gqcs{L}_{y}$,
+  for all $x,y \in G(\bFq)$, such that
+  \[
+   \begin{tikzcd}[row sep=40]
+    \gqcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
+    && \gqcs{L}_{x+y}\otimes\gqcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
+    \gqcs{L}_{x} \otimes\gqcs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
+    && \gqcs{L}_{x} \otimes\gqcs{L}_{y} \otimes\gqcs{L}_{z}
+   \end{tikzcd}
+  \]
+  commutes, for all $x,y,z\in G(\bFq)$; and
+ \labitem{(qc.3)}{qc.3} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
+  such that
+  \[
+   \begin{tikzcd}[row sep=40]
+    \gqcs{L}_{\Frob{}(x)+\Frob{}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{}(x),\Frob{}(y)}}
+    && \gqcs{L}_{\Frob{}(x)}\otimes\gqcs{L}_{\Frob{}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
+    \gqcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
+    && \gqcs{L}_x \otimes\gqcs{L}_y
+   \end{tikzcd}
+  \]
+  commutes, for all $x,y\in G(\bFq)$.
+\end{enumerate}
+Under this equivalence, a morphism $\alpha : \qcs{L} \to \qcs{L'}$ of quasicharacter sheaves on $G$ is given by
+\begin{enumerate}
+ \labitem{(qc.4)}{qc.4} an indexed set $\rho_x : \gqcs{L}_x \to \gqcs{L'}_x$
+  of linear transformations such that
+  \[
+   \begin{tikzcd}[column sep=40]
+    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{}(x)} \rar{\rho_{\Frob{}(x)}} & \gqcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
+    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
+    & \arrow[swap]{d}{\mu} \gqcs{L}_{x+y} \rar{\rho_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
+    \gqcs{L}_x \rar{\rho_x} & \gqcs{L'}_x
+    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\rho_x\otimes\rho_y} & \gqcs{L'}_x \otimes\gqcs{L'}_y
+   \end{tikzcd}
+  \]
+  both commute for all $x, y \in G(\bFq)$.
+\end{enumerate}
+
+\todo{Find an appropriate place for this discussion}
+
+If $\rho_0 = 0$ then the second diagram for $y=0$ implies that $\rho_x = 0$ for all $x$.
+Conversely, if $\rho_0$ is nonzero then the second diagram for $y = -x$ implies that $\rho_x$ is nonzero for all $x$ and thus an isomorphism since $\gqcs{L}_x$ is one dimensional.
+Most of this paper focuses on the question of determining the isomorphism classes of objects; a complete understanding of the morphisms in $\QC(G)$ also requires a description of the automorphisms of an arbitrary quasicharacter sheaf $\qcs{L}$.
+
+\begin{proposition}
+The trace map induces an isomorphism of groups
+\[
+\Aut(\qcs{L}) \cong \Hom(G(\bFq)_{\Weil{}}, \EEx).
+\]
+\end{proposition}
+
+\begin{proof}
+The second diagram in \ref{qc.4} shows that the association $x \mapsto \rho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first shows that it factors through $G(\bFq)_{\Weil{}}$.
+Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism then defining $\rho_x$ as multiplication by $\rho(x)$ will satisfy the two diagrams.
+Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the resulting bijection is actually a group ismorphism.
+\end{proof}
+
+We will see that the Trace of Frobenius may not provide complete
+information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not a connected algebraic group.
+Our main tool for understanding this phenomenon
+is a group homomorphism from $\QCiso{G}$ to $\Hh^2(E^\bullet_G)$, defined in Section~\ref{sec:S}, for which the next two sections are preparation.
+
+\subsection{A spectral sequence}\label{sec:E}
+
+The zeroth page of the Hochschild-Serre spectral sequence is a double complex $E^{\bullet, \bullet}$ defined by
+\[
+E^{i,j} = C^i(\Weil{}, C^j(G(\bFq), \EEx)),
+\]
+The derivative of group cohomology yields two derivatives:
 \begin{align*}
-i_{k'/k}^* : G(k')^* &\to G(k)^* \\
-\chi &\mapsto \chi\circ i_{k'/k}.
+d_0 = d_G &: E^{i,j} \to E^{i,j+1} \\
+d_{\Weil{}} &: E^{i,j} \to E^{i+1,j}.
 \end{align*}
-We can interpret this operation on characters in terms of rigid quasicharacter sheaves:
-
-\begin{proposition} \label{prop:csbe}
-Set $G_{k'} \ceq G\times_\Spec{k} \Spec{k'}$ and let
-\[
-\rQC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \rQC(G)
-\]
-be the functor obtained by pullback along the canonical closed immersion of $k$-schemes
-$\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$
-\cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}.
-The following diagram commutes:
+Combining these yields a derivative $d = d_G + (-1)^j d_{\Weil{}}$ on the total complex
+\[
+E^n_G = \bigoplus_{i+j=n} E^{i,j}.
+\]
+The machinery of spectral sequences gives us a sequence of pages $E_r^{i,j}$, converging to a page $E_{\infty}^{i,j}$.
+We summarize the key properties of this spectral sequence in the following proposition.
+
+\begin{proposition}
+\begin{enumerate}
+\item The second page is given by $E_2^{i,j} = \Hh^i(\Weil{}, \Hh^j(G(\bFq), \EEx))$,
+\item there is an isomorphism $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) \cong \Hh^n(E_G^\bullet)$,
+\item there is a filtration $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) = F_n \supset \cdots \supset F_0 \supset F_{-1} = 0$ where $F_i / F_{i-1} \cong E_{\infty}^{i, n-i}$.
+\end{enumerate}
+\end{proposition}
+
+Moreover, since $\Weil{} \cong \ZZ$ has cohomological dimension $1$, $E_2^{i,j} = 0$ for $i > 1$ and the sequence degenerates at the second page: $E_{\infty}^{i,j} = E_2^{i,j}$.
+We obtain the following corollary:
+
+\begin{corollary}
+There is a short exact sequence
  \[
   \begin{tikzcd}
-\rQCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\TrFrob{\Res_{k'/k}(G_{k'})}} & \rQCiso{G} \dar{\TrFrob{G}} \\
-G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
-\end{tikzcd}
-\]
+    0 \arrow{r}
+    & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r}
+    & \Hh^2(E^\bullet_G) \arrow{r}
+    & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r}
+    & 0
+  \end{tikzcd}
+ \]
+\end{corollary}
+
+This sequence will play a key role in understanding the kernel of $T_G$, as described in the next few sections.
+For this application, we need a good understanding of these maps to and from the total complex.
+
+\begin{proposition} \label{prop:ses_desc}
+\begin{enumerate}
+\item Every class $[\alpha\oplus\beta\oplus\gamma] \in \Hh^2({\bar G},\EEx)$ is cohomologous to one with $\gamma=0$.
+\item The map $\Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx))$ is given by $[\alpha\oplus\beta\oplus 0] \mapsto [\beta]$.
+\item Suppose $a \in Z^2({\bar G}, \EEx)$ represents a class in $\Hh^2({\bar G},\EEx)$ fixed by Frobenius.
+The map $\Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to \Hh^2(E^\bullet_G)$ is given by $[a] \mapsto [a \oplus 0 \oplus 0]$.
+\end{enumerate}
 \end{proposition}
 \begin{proof}
-This result follows immediately from Proposition~\ref{prop:pullback} together with the identifications
-\[
-\Res_{k'/k}(G_{k'})(k) \cong G_{k'}(k') \cong G(k')
-\]
-from the definitions of Weil restriction and base change.
-\end{proof}
-
-In the opposite direction, let $\Nm : G(k') \to G(k)$ be the norm map and consider the group homomorphism:
+Since $\Hh^2(\Weil{}, C^0({\bar G}, \EEx)) = 0$, we may find a $\gamma_1 \in C^1(\Weil{}, C^0({\bar G}, \EEx))$ with $d_{\Weil{}}\gamma_1 = \gamma$.
+Subtracting $d \gamma_1$ from $\alpha\oplus\beta\oplus\gamma$, we may assume that $\gamma = 0$.
+
+The latter two claims follow from tracing through the definition of latter pages in the spectral sequence; see Vakil \cite{} for example \todo{update reference}.
+\end{proof}
+
+\subsection{From quasicharacter sheaves to the total complex}\label{sec:S}
+
+In this section we define an isomorphism
+\[
+S_G : \QCiso{G} \to \Hh^2(E^\bullet_G).
+\]
+Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
+For each geometric point $x\in {\bar G}$, choose a basis $\{ v_x \}$ for $\gqcs{L}_x$.
+Through this choice, $\qcs{L}$ determines functions
 \begin{align*}
-\Nm^* : G(k)^* &\to G(k')^* \\
-\chi &\mapsto \chi\circ \Nm.
+a : {\bar G}\times {\bar G} &\to \EEx & b : {\bar G} &\to \EEx \\
+\mu_{x,y}(v_{x+y}) &= a(x,y) v_x \otimes v_y & \phi_x(v_{\Frob{G}(x)}) &= b(x) v_x.
 \end{align*}
-We can also interpret this operation on characters in terms of rigid quasicharacter sheaves.
-
-If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a rigid quasicharacter sheaf on $G$, we define
-a rigid quasicharacter sheaf $\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
-$G_{k'}$ of $G$ to $k'$ by setting
-\[
-\phi_{k'} \ceq \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi).
-\]
-The commutativity of the diagram (QC.3) for $\phi_{k'}$
-follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
-Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
-as taking the action $\varphi$ of $\Weil{k}$ on $\gqcs{L}$
-defined in Section~\ref{sec:category} and restricting it to the subgroup $\Weil{k'}$.
-
-\begin{proposition}\label{prop:basechange}
-With notation above,
-the rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$
- defines a monoidal functor $\rQC(G) \to \rQC(G_{k'})$.
- Moreover, the following diagram commutes:
-\[
-\begin{tikzcd}[column sep=60]
-\rQCiso{G} \rar{\nu_{k'/k}} \dar{\TrFrob{G}} & \rQCiso{G_{k'}} \dar{\TrFrob{G_{k'}}} \\
-G(k)^*  \rar{\Nm^*} & G(k')^*.
-\end{tikzcd}
-\]
+Condition~\ref{QC.2} implies that
+\begin{equation}\label{2-cocyle}
+a(x+y,z) a(x,y) = a(x,y+z) a(y,z)
+\end{equation}
+for all $x,y,z\in {\bar G}$, so $a \in Z^2({\bar G},\EEx)$.  Similarly, condition~\ref{QC.3} gives
+\begin{equation}\label{nohom}
+\frac{a(\Frob{G}(x),\Frob{G}(y))}{a(x,y)} =  \frac{b(x+y)}{b(x) b(y)}
+\end{equation}
+for $x, y \in {\bar G}$.
+Let $\alpha \in C^0(\Weil{},C^2({\bar G},\EEx)$ be the $0$-cochain corresponding to $a$ and let $\beta\in C^1(\Weil{},C^1({\bar G},\EEx)$ be the cocycle such that $\beta(\Frob{})$ is $b$ \emph{written additively}.
+Then
+\[
+d_G\alpha =0, \qquad\qquad
+d_{\Weil{}} \alpha = d_{G} \beta,\qquad\qquad
+d_{\Weil{}} \beta =0;
+\]
+in other words,
+\[\alpha\oplus \beta \in Z^2(E^\bullet_G).\]
+Although the cocycle $\alpha\oplus \beta$ is not well defined by $\qcs{L}$, its class in $Z^2(E^\bullet_G)$ is.
+To see this, let $\{ v'_x \in \gqcs{L}_x^\times \tq x \in {\bar G}\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$ be defined by $\qcs{L}$ and this choice, as above.
+Now let $\delta \in C^0(\Weil{},C^1({\bar G},\EEx))$ be the additive version of the function $d : {\bar G}\to \EEx$ defined by $v'_x = d(x) v_x$.
+Then, chasing through \ref{QC.2} and \ref{QC.3} we find
+\[
+\alpha'\oplus\beta' = \alpha\oplus\beta + d\delta,
+\]
+so the class $[\alpha\oplus\beta]$ of $\alpha\oplus\beta$ in $\Hh^2(E^\bullet_G)$ is independent of the choice made above.
+It is also easy to see that $[\alpha\oplus\beta] = [\alpha_0\oplus\beta_0]$ when $\qcs{L} \iso \qcs{L}_0$,
+which concludes the definition of the function
+\begin{align*}
+S_G : \QCiso{G} &\to \Hh^2(E^\bullet_G)\\
+[\qcs{L}] &\mapsto [\alpha\oplus \beta].
+\end{align*}
+It is also easy to see that $[\alpha_1\oplus\beta_1] + [\alpha_2\oplus\beta_2] = [\alpha_3\oplus\beta_3]$ when $\qcs{L}_3 = \qcs{L}_1\otimes \qcs{L}_2$, so $S_G$ is a group homomorphism.
+
+\begin{remark}
+Although we will only use the group homomorphism $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$.
+However, the next result is false in that context.
+\end{remark}
+
+\begin{proposition}
+If $G$ is \'etale then $S_G$ is an isomorphism.
 \end{proposition}
-
-\begin{proof}
-Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \rQC(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
-we may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
-and the value of $\Nm^*(\TrFrob{G}(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
-Applying \ref{QC.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
+\begin{proof}
+We first show that $S_G$ is injective.  Suppose $\qcs{L} \in \QCiso{G}$ with $S_G(\qcs{L}) = [\alpha \oplus \beta] = 0$,
+so that $\alpha \oplus \beta = d\rho$ for some $\rho \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
+For each $x\in {\bar G}$, define $\rho_x : \gqcs{L}_x \to \EEx$ by $v_x \mapsto \rho(x)$.
+Then the indexed set of isomorphisms $\{ \gamma_x : \gqcs{L}_x \to \EE \tq x\in {\bar G}\}$
+defines an isomorphism $\qcs{L} \to (\EE)_G$.
+Since $\qcs{L} = 0 \in \QCiso{G}$, $S_G$ is injective.
+
+To see that $S_G$ is surjective, begin with $\alpha\oplus\beta\oplus 0 \in Z^2(E^\bullet_G)$.
+Since $d_{\Weil{}} \beta = 0$, we may define $a = \alpha \in C^2({\bar G},\EEx)$ and
+$b = \beta(\Frob{}) \in C^1({\bar G},\EEx)$, which are related to $\alpha$ and $\beta$ as above.
+Set $\gqcs{L}_x = \EEx$, define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes\gqcs{L}_y$
+by $\mu_{x,y}(1) = a(x,y) 1\otimes 1$ and $\phi_x : \gqcs{L}_{\Frob{G}(x)} \to \gqcs{L}_x$ by $\phi_x(1)= b(x)$.
+Then \ref{qc.1} holds since $d_G \alpha =0$ and \ref{qc.2} holds since $d_{\Weil{}}\alpha =d_G \beta$.
+Tracing the construction backward, we have defined a quasicharacter sheaf $\qcs{L}$ on $G$ with
+$S_G(\qcs{L}) = [\alpha\oplus\beta\oplus\gamma]$, showing that $S_G$ is surjective.
+\end{proof}
+
+\subsection{\texorpdfstring{$S$ and $T$}{S and T}}
+
+In this section we describe the relationship between the group homomorphisms $\TrFrob{G}$ and $S_G$.
+%
+We begin with a simple, general result relating duals, invariants and coinvariants.
+
+\begin{lemma} \label{lem:dual-inv}
+Let $X$ be an abelian group equipped with an action of $\Weil{}$.
+ Then
+\begin{align*}
+ (X^*)_{\Frob{}} &\to (X^{\Frob{}})^* \\
+ [f] &\mapsto f|_{X^{\Frob{}}}
+\end{align*}
+is an isomorphism.
+\end{lemma}
+
+\begin{proof}
+We can describe $X^{\Frob{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
+let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
+\[
+ 0 \to X^{\Frob{}} \to X \to Y \to 0
+\]
+yields
+\[
+ 0 \to Y^* \to X^* \to (X^{\Frob{}})^* \to \Ext^1_\ZZ(Y, \EEx).
+\]
+Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Frob{}})^*$.
+\end{proof}
+
+\begin{corollary}
+If $G$ is \'etale then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective.
+\end{corollary}
+\begin{proof}
+Pick $\chi \in G(\Fq)^*$.
+By Lemma~\ref{lem:dual-inv}, there is some $b\in G(\bFq)^*$ such that $b\vert_{G(\Fq)^*} = \chi$.
+Set $\gqcs{L}_x = \EE$ for every $x\in G(\bFq)$.
+Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$ and
+$\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = b(x)$.
+Since $b : G(\bFq) \to \EEx$ is a group homomorphism,
+condition \eqref{nohom} is satisfied with $a =1$ and $\qcs{L} = (\gqcs{L}, \mu, \phi)$
+is a quasicharacter sheaf with $\trFrob{\qcs{L}} = \chi$.
+\end{proof}
+
+\begin{proposition} \label{prop:etale-iso}
+ If $G$ is \'etale then the map $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ induces an isomorphism of short exact sequences
 \[
 \begin{tikzcd}
-\gqcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gqcs{L}_{F(x)} \otimes \gqcs{L}_{F^2(x)} \otimes \cdots \otimes \gqcs{L}_x
-\dar{\phi_x \otimes (F^*\phi)_x \otimes \cdots \otimes ((F^{n-1})^*\phi)_x} \\
-\gqcs{L}_{\Nm(x)} \rar & \gqcs{L}_x \otimes \gqcs{L}_{F(x)} \otimes \cdots \otimes \gqcs{L}_{F^{n-1}(x)}.
-\end{tikzcd}
-\]
-Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$ and write the image of $v$ under the
-bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
-for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{QC.2}, $v$ maps to
-$v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
-Let $\alpha_i \in \EEx$ represent $((F^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
-the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gqcs{L}_{\Nm(x)}$
-with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gqcs{L}_x$.
-\end{proof}
-
-Finally, let $G'$ be a smooth commutative group scheme over $k'$;
-we explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
-We may decompose the base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
-into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
-\[
-(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
-\]
-Since products and coproducts agree for group schemes we have a natural inclusion of $k'$-schemes
-\[
-G' \hookrightarrow (\Res_{k'/k}G')_{k'}
-\]
-mapping $G'$ into the summand corresponding to $1 \in \Gal(k'/k)$.  Composing $\nu_{k'/k}$
-from Proposition~\ref{prop:basechange} with pullback along this map yields a functor
-\[
-\rho : \rQC(\Res_{k'/k}G') \to \rQC(G').
-\]
-
-\begin{proposition}
-Let $k'/k$ be a finite extension and let $G'$ be a smooth commutative group scheme over $k'$.
-The following diagram of isomorphisms commutes, where the bottom map is the identity:
-\[
-\begin{tikzcd}
-\rQCiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \rQCiso{G'} \dar{\TrFrob{G'}}\\
-G'(k')^* \rar & G'(k')^*
+ 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \QCiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
+  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r} & 0.
  \end{tikzcd}
@@
 \begin{proof}
-By Proposition~\ref{prop:pullback} the pullback part of the definition of $\rho$ corresponds to the map
-\[
-(\Res_{k'/k}G')(k') \to G'(k')^*
-\]
-induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on
-\[
-(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'
-\]
-is given by permuting coordinates, composition with the norm map yields the identity on $G'(k')$.
-\end{proof}
-
-\todo{Can we improve on this result by proving that $\rho$
-is an equivalence of categories?}
-
-\section{Two subcategories of rigid quasicharacter sheaves}%\label{sec:bounded}
-
-\subsection{Bounded quasicharacter sheaves}\label{sec:bounded}
-
-In this section we consider a class of rigid quasicharacter sheaves on $G$ obtained by
-replacing the Weil sheaf $(\gqcs{L}, \phi)$ on $\bG$ in the definition of a rigid quasicharacter
-sheaf with an $\ell$-adic local system on $G$ itself.
-
-\begin{definition}
-Let $\rbQC(G)$ be the category of pairs $(\qcs{L}_0,\mu_0)$
-where $\qcs{L}_0$ an $\ell$-adic local system on $G$ of rank~one,
-equipped with an isomorphism $\mu_0 : m^* \qcs{L}_0 \to \qcs{L}_0 \boxtimes \qcs{L}_0$
-satisfying the analogue of \ref{QC.1} on $G$;
-morphisms in $\rbQC(G)$ are defined as in the second part of
-\ref{QC.3}.
-This is the category of \emph{bounded quasicharacter sheaves} on $G$.
-\end{definition}
-
-The category of bounded quasicharacter sheaves is a rigid monoidal category in the obvious way.
-
-\begin{proposition}\label{prop:BG}
-Extension of scalars defines a full and faithful functor
-$B_G : \rbQC(G) \hookrightarrow \rQC(G)$.
-\end{proposition}
-
-\begin{proof}
- Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$.
- Then $\qcs{L}_0$ is an $\ell$-adic constructible sheaf on $G$ and
- $b_G^* \qcs{L}_0$ comes equipped with an isomorphism
- $\phi : \Frob{G}^* b_G^*\qcs{L}_0 \to b_G^* \qcs{L}_0$.
- Moreover, the functor $\qcs{L}_0 \mapsto (b_G^* \qcs{L}_0,\phi)$
- from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
- is full and faithful \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}}.
- This functor preserves local constancy, so takes local systems to local systems.
- Set $\mu \ceq b_{G\times G}^*\mu_0$; clearly, this satisfies \ref{QC.2}
- with $b_G^*\qcs{L}_0$ playing the role of $\gqcs{L}$.
- Moreover, $\phi$ is compatible with $\mu$ in the sense of \ref{QC.3}.
- This construction defines the functor $B_G : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
- and also shows that it is full and faithful.
-\end{proof}
-
-In general, $\rbQC(G)$ is an essentially
-proper subcategory of $\rQC(G)$. We will identify $\rbQC(G)$ with its image under $B_G$
-and say that a rigid quasicharacter sheaf $\qcs{L} \in \rQC(G)$ is \emph{bounded}
-if it is isomorphic to some $B_G(\qcs{L}_0, \mu_0)$.
-We will see in Corollary~\ref{cor:bounded-and-finite} that bounded quasicharacter sheaves are exactly rigid quasicharacter sheaves with bounded Trace of Frobenius.
+This result follows easily from Proposition \ref{prop:ses_desc}.
+\end{proof}
+
+\section{The main result}\label{sec:main}
+
+In the introduction to this paper we noted that, when working with connected commutative algebraic groups over finite fields, Deligne's dictionary can be described using Weil sheaves $\qcs{L}$ for which there exists an isomorphism $m^* \qcs{L} \iso \qcs{L} \boxtimes\qcs{L}$, without keeping track of the isomorphism.
+\todo{rephrase objective of section}
+In this section use that perspective to find a perfect dictionary between flabby quasicharacter sheaves on $G$ and characters of $G(\Fq)$.
 
@@
 \begin{definition}
-The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\rfQC(G)$,
+The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\fQC(G)$,
 is the rigid monoidal category $C_1(G)[W_1^{-1}]$ obtained by localizing $C_1(G)$ at weak isomorphisms $W_1$.
@@
 
-Later in the paper we will make a study of isomorphism classes of objects in $\rfQC{G}$. Here we focus on morphisms in this category.
+Later in the paper we will make a study of isomorphism classes of objects in $\fQC(G)$. Here we focus on morphisms in this category.
 
 \begin{proposition}\label{prop:autornaught}
-Every morphism in $\rfQC(G)$ is either an isomorphism or trivial.
-Moreover, for every finite quasicharacter sheaf $(f,\psi,r)$, the group $\Aut_{\rfQC(G)}(f,\psi,r)$ is trivial.
+Every morphism in $\fQC(G)$ is either an isomorphism or trivial.
+Moreover, for every finite quasicharacter sheaf $(f,\psi,r)$, the group $\Aut_{\fQC(G)}(f,\psi,r)$ is trivial.
 \end{proposition}
@@
 \begin{proof}
-Trivial morphisms in $\rfQC(G)$ are defined as follows. Let $(f,\psi,r)$ and $(f_1,\psi_1,r_1)$ be finite quasicharacter sheaves on $G$.  
+\todo{This proof is under construction.}
+Trivial morphisms in $\fQC(G)$ are defined as follows. Let $(f,\psi,r)$ and $(f_1,\psi_1,r_1)$ be finite quasicharacter sheaves on $G$.  
 Form $(f\times_G f_1,1\otimes \psi_1, r\otimes r_1)$ in $C_1(G)$. 
@@
 %
-The morphism in $\rfQC(G)$ represented by
+The morphism in $\fQC(G)$ represented by
 \[
@@
 \]
-does not depend on the choice of $0\ne v\in V$; this defines the {\em trivial morphism} $0: (f,\psi,V) \to (f_1,\psi_1,V_1)$ in $\rfQC(G)$.
+does not depend on the choice of $0\ne v\in V$; this defines the {\em trivial morphism} $0: (f,\psi,V) \to (f_1,\psi_1,V_1)$ in $\fQC(G)$.
 
@@
 \]
-represent a morphism $(f,\psi,V)  \to (f_1,\psi_1,V_1)$ in $\rfQC(G)$;
+represent a morphism $(f,\psi,V)  \to (f_1,\psi_1,V_1)$ in $\fQC(G)$;
 note that, by definition, $(\gamma_1 , T_1) : (f_1,\psi_1,V_1) \to (f',\psi',V')$ is a weak isomorphism.
@@
 By \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16}, 
-it follows that $(f,\psi,V)  \to (f_1,\psi_1,V_1)$ is the trivial morphism in $\rfQC(G)$.
-
-Now suppose $T$ is an isomorphism, then $(\gamma,T)$ is a weak isomorphism, in which case the morphism $(f,\psi,V) \to (f_1,\psi_1,V_1)$ is an isomorphism in $\rfQC(G)$.
-\todo{This is where some information about $\Aut_{\rfQC(G)}(f,\psi,V)$ will go, when I've sorted it out.}
-\end{proof}
-
-\subsection{Finite implies Bounded}
-
-In this section we show that $\rfQC(G)$ is a full subcategory of $\rbQC(G)$.
-To prepare for that result, we need the next two lemmas.
-
-\begin{lemma}\label{lemma:finite-pullback}
-Let $g : J \to G$ be a morphism of smooth groups schemes over $\Fq$.
-Let $f_g : H\times_G J\to J$
-be the pullback of $f$ along $g$ and define $\psi_g : \ker f_g \to \Aut(V)$ as in the diagram below:
-\[
-\begin{tikzcd}
-V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker f_g}} \ker f_g \arrow[hook]{r}
-  & \arrow[swap]{u}{g_f} H\times_G J \arrow{r}{f_g} & \arrow{u}{g} J.
-\end{tikzcd}
-\]
-Then $(f,\psi) \mapsto (f_g,\psi_g)$
-defines a monomial functor $g^* : C(G)[W^{-1}] \to C(J)[W^{-1}]$.
-\end{lemma}
-
-\begin{proof}
-The key point is that pullback along $g$ takes discrete isogenies to discrete isogenies,
-and maps over $G$ to maps over $J$, as pictured below.
-\[
-\begin{tikzcd}[row sep={{{{40,between origins}}}},column sep={{{{50,between origins}}}}]
-%\ V \arrow{dd}{T} &
-\Aut(V) && \arrow[swap]{ll}{\psi} \ker f \arrow[hook]{rr} \arrow[leftarrow]{dd} && H \arrow{rr}{f} \arrow[leftarrow]{dd} && \arrow[equal]{dd} G\\
-% &
-& \arrow{ul} \ker f\times_G J \arrow{ur} \arrow[hook, crossing over]{rr} && H\times_G J \arrow{ur} \arrow[crossing over]{rr} && J \arrow[swap]{ur}{g} & \\
-%V' &
- \Aut(V') && \arrow[swap,pos=0.25]{ll}{\psi'} \ker f'  \arrow[hook]{rr}
-&& H' \arrow[pos=0.25]{rr}{f'} && G\\
-% &
- & \arrow{ul} \ker f'\times_G J \arrow[crossing over]{uu} \arrow{ur} \arrow[hook]{rr}
- && \arrow[crossing over]{uu} H'\times_G J \arrow{ur} \arrow{rr} && \arrow[equals, crossing over]{uu} J \arrow[swap]{ur}{g} &
-\end{tikzcd}
-\]
-%In this form we could treat $g^*$ as a functor $C(J)\to C(G)$,
-%were it not for the fact that pullback is defined only up to isomorphism.
-%In the localized categories, this ambiguity disappears.
-\end{proof}
-
-\begin{lemma}\label{lemma:finite-iso}
-Each finite quasicharacter sheaf $(f,\psi)$ in $\rfQC(G)$ determines a
-canonical isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\rfQC(G\times G)$.
- \end{lemma}
-
-\begin{proof}
-We will prove the proposition by finding a weak isomorphism
-$m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ in $C_1(G\times G)$
-and showing that, after passing from $C_1(G\times G)$ to
-$\rfQC(G\times G)$, the resulting isomorphism,
-denoted by $\mu(f,\psi)$, is canonically determined by $(f,\psi)$.
-
-Set $H_m \ceq H\times_G(G\times G)$,
-write $f_m : H_m \to G \times G$ for the pullback of $f$ to $H_m$,
-and let $A$ and $A_m$ be the kernels of $f$ and $f_m$ respectively.  Consider the diagram of Lemma~\ref{lemma:finite-pullback}:
-\[
-\begin{tikzcd}[column sep=40]
-V & \Aut(V) & \arrow[swap]{l}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-  &  & \arrow[dashed]{ul}{\psi_m} \arrow[swap]{u}{(m_f)\vert_{A_m}} A_m \arrow[hook]{r}
-  & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G.
-\end{tikzcd}
-\]
-We have $(f,\psi) \boxtimes (f,\psi) = (f\times f, \psi\otimes \psi)$.
-Since $f\circ m_H = m \circ (f\times f)$, the universal property of pullback gives
-a unique $\theta : H\times H \to H_m$ making the following commute.
-\[
-\begin{tikzcd}[row sep=20,column sep=8]
-\ & V \arrow{dd}{T} && \Aut(V) && A \arrow[hook]{rr} \arrow[swap]{ll}{\psi} &&  H \arrow{rr}{f} && G\\
- && && \arrow{ul}{\psi_m} A_m  \arrow[hook]{rr} \arrow{ur} && H_m \arrow[pos=0.3]{ur}{m_f} \arrow[swap, pos=0.8]{rr}{f_m}
- && G \times G \arrow[equal]{dr} \arrow[pos=0.42]{ur}{m} & \\
-& V\otimes V && \Aut(V\otimes V) && \arrow[swap]{ll}{\psi \otimes \psi} \arrow[dashed,swap,pos=0.3]{ul}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr}
-&& \arrow[dashed,swap]{ul}{\theta} \arrow[crossing over,swap,pos=0.7]{uu}{m_H} H\times H \arrow{rr}{f\times f} && G\times G
-\end{tikzcd}
-\]
-Choose a basis $\{ v \}$ for $V$; then $\{ v\otimes v \}$ is a basis for $V\otimes V$.
-Let $T : V \to V\otimes V$ be the linear transformation taking $v$ to $v\otimes v$. Then the lower part of this
-diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G\times G)$.
-%
-While $\theta$ was canonical, $T$ was not, as it depended on the choice of a basis for $V$.
-However, after passing from $C_1(G\times G)$ to $\rfQC(G\times G)$, the resulting isomorphism 
-$\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ in $\rfQC(G\times G)$ is independent of the choice of basis for $V$.
- \end{proof}
-
-\begin{proposition}\label{prop:bounded}
- $\rfQC(G)$ is a full subcategory of $\rbQC(G)$.
-\end{proposition}
-
-\begin{proof}
- To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \rfQC(G) \to \rbQC(G)$.
-
- If $V$ is a finite-dimensional $\EE$-vector space then we write $V_H$ for the constant sheaf $V$ on $H$.
-If $(f,\psi)$ is a finite quasicharacter on $G$ where $\psi$ is a representation of $\ker f$ on $V$,
-let $L(f,\psi)$ be the local system on $G$ given by the $\psi$-isotypic component of the local system $f_* V_H$ on $G$.
- We may identify the stalk $(f_* V_H)_{\bar g}$ of $f_* V_H$ at a geometric point ${\bar g}$ on $G$
- with the $\EE$-vector space $\Hom_\text{set}(\abs{f^{-1}({\bar g})},V)$
- and the stalk $L(f,\psi)_{\bar g}$ of $L(f,\psi)$ at a geometric point ${\bar g}$ on $G$
- with the $\EE$-vector space consisting of those functions $s: \abs{f^{-1}({\bar g})} \to V$ such that
- $s(a\cdot {\bar h}) = \psi(a)(s({\bar h}))$ for all $a\in \ker f$ and for all ${\bar h} \in f^{-1}({\bar g})$.
-
- For any map $(g,T)$ in $C(G)$, let $L(g,T) : L(f,\psi) \to L(f',\psi')$ be the homomorphism of local systems defined
- by $s \mapsto s' \ceq T\circ s\circ g$.
- This construction defines a full monoidal functor $L$ from $C(G)$ to the category $\Loc(G)$ of local systems on $G$ that
- commutes with pullback along any morphism of $\rQC$-schemes,
- as defined using Lemma~\ref{lemma:finite-pullback}.
- Moreover, since $L(f,T)$ is an isomorphism of local systems
- if and only if $(f,T)$ is a weak isomorphism,
- the full functor $L : C(G) \to \Loc(G)$ factors through the localization functor $C(G) \to C(G)[W^{-1}]$
- to define a full and faithful functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$;
- see \cite{kashiwara-schapira:CatgoriesSheaves}*{Exercise 7.5}.
-
- By Lemma~\ref{lemma:finite-iso}, each $(f,\psi) \in \rfQC(G)$ canonically determines
- an isomorphism
- \[
- \mu(f,\psi) : m^*(f,\psi) \to (f,\psi) \boxtimes (f,\psi)
- \]
- in $\rfQC(G\times G)$.
- It follows immediately that the functor
- \[
- L_G  \ceq  L_{W}\vert_{\rfQC(G)} : \rfQC(G) \to \rbQC(G),
- \]
- given on objects by $(f,\psi) \mapsto (L(f,\psi), L_{W}(\mu(f,\psi)))$,
- is a full and faithful monoidal functor, completing the proof.
-\end{proof}
-
-On general smooth group $\Fq$-schemes $G$, 
-there are bounded quasicharacter sheaves which are not finite.  
-Identifying $\rfQC(G)$ with its image under $B_G \circ L_G$, as defined in
-Proposition~\ref{prop:BG} and in the proof of Proposition~\ref{prop:bounded},
-we will see in Corollary~\ref{cor:bounded-and-finite} that
-a rigid quasicharacter sheaf is finite if and only if its Trace of Frobenius has finite image.
-
-\section{The case of connected commutative algebraic groups} \label{sec:connected}
-
-For connected groups, the subcategories introduced in the previous two sections agree with $\rQC(G)$.
-
-\subsection{When rigid quasicharacter sheaves are finite}
+it follows that $(f,\psi,V)  \to (f_1,\psi_1,V_1)$ is the trivial morphism in $\fQC(G)$.
+
+Now suppose $T$ is an isomorphism, then $(\gamma,T)$ is a weak isomorphism, in which case the morphism $(f,\psi,V) \to (f_1,\psi_1,V_1)$ is an isomorphism in $\fQC(G)$.
+\todo{This is where some information about $\Aut_{\fQC(G)}(f,\psi,V)$ will go, when I've sorted it out.}
+\end{proof}
+
+\subsection{When quasicharacter sheaves are finite}
 
@@
   If $G$ is a connected commutative algebraic group over $\Fq$ then
-  the full subcategories $\rfQC(G) \hookrightarrow \rbQC(G) \hookrightarrow \rQC(G)$
+  the full subcategories $\fQC(G) \hookrightarrow \bQC(G) \hookrightarrow \QC(G)$
   appearing in Sections~\ref{sec:bounded} and \ref{sec:finite} are equivalences.
@@
   Observe that the forgetful functor $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$
-  sends rigid quasicharacter sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{deligne:80a}*{1.1.10}.
+  sends quasicharacter sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{deligne:80a}*{1.1.10}.
   While is it not true that all Weil sheaves on $G$ descend to local systems on $G$,
-  we will see that those that appear in the image of this forgetful functor from rigid quasicharacter sheaves do.
+  we will see that those that appear in the image of this forgetful functor from quasicharacter sheaves do.
 
@@
   $\ell$-adic representations of $\W(G,\bg)$ \cite{deligne:80a}*{1.1.12}.
-  Now let $(\gqcs{L},\mu,\phi)$ be a rigid quasicharacter sheaf on $G$
+  Now let $(\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$
   and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$.
@@
   the latter appearing in the definition of $\qcs{L}$.
-  Then, as in Section~\ref{sec:bounded}, $(\qcs{L}_0,\mu_0)$ is an object in $\rbQC(G)$
-  and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{L}_0,b_{G\times G}^*\mu_0)$ in $\rQC(G)$.
-  Thus, the full and faithful functor $B_G : \rbQC(G) \to \rQC(G)$ from Section~\ref{sec:bounded}
+  Then, as in Section~\ref{sec:bounded}, $(\qcs{L}_0,\mu_0)$ is an object in $\bQC(G)$
+  and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{L}_0,b_{G\times G}^*\mu_0)$ in $\QC(G)$.
+  Thus, the full and faithful functor $B_G : \bQC(G) \to \QC(G)$ from Section~\ref{sec:bounded}
   is also essentially surjective, hence an equivalence.
 
-  In Section~\ref{sec:finite} we saw that $\rfQC(G)$ is a full subcategory of $\rbQC(G)$;
-  more precisely, we exhibited a full and faithful functor $L_G : \rfQC(G) \to \rbQC(G)$.
+  In Section~\ref{sec:finite} we saw that $\fQC(G)$ is a full subcategory of $\bQC(G)$;
+  more precisely, we exhibited a full and faithful functor $L_G : \fQC(G) \to \bQC(G)$.
   We now show that this functor is essentially surjective
@@
   Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$.
-  Then $\qcs{L}\ceq B_G(\qcs{L}_0,\mu_0)$ is a rigid quasicharacter sheaf on $G$.
+  Then $\qcs{L}\ceq B_G(\qcs{L}_0,\mu_0)$ is a quasicharacter sheaf on $G$.
   Recall the definition of the character $\trFrob{\qcs{L}} : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}.
@@
   Using \cite{laumon:87a}*{Th\'eor\`eme 1.1.2}, it follows that  $L(f,\psi) \iso \qcs{L}_0$ in $\Loc(G)$.
-  It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\qcs{L}_0,\mu_0)$ in $\rbQC(G)$.
+  It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\qcs{L}_0,\mu_0)$ in $\bQC(G)$.
   This completes the proof that $L_G $ is essentially surjective.
@@
 when $G$ is a connected algebraic group over $\Fq$,
-it is appropriate to replace rigid quasicharacter sheaves on $G$
-with the conceptually simpler category $\rfQC(G)$ of finite quasicharacter sheaves on $G$.
+it is appropriate to replace quasicharacter sheaves on $G$
+with the conceptually simpler category $\fQC(G)$ of finite quasicharacter sheaves on $G$.
 In this context, finite quasicharacter sheaves may also be apprehended as
@@
 %to which we now return.
-In this generality, however, neither of the full subcategories $\rfQC(G) \subset \rbQC(G) \subset \rQC(G)$ are equivalences;
+In this generality, however, neither of the full subcategories $\fQC(G) \subset \bQC(G) \subset \QC(G)$ are equivalences;
 see the end of Section~\ref{sec:snake}.
-Nevertheless, every rigid quasicharacter sheaf $(\gqcs{L},\mu,\phi)$ on $G$
+Nevertheless, every quasicharacter sheaf $(\gqcs{L},\mu,\phi)$ on $G$
 determines a Weil sheaf $(\gqcs{L},\phi)$ on $G$
@@
 
-We are in a good position to understand $\rQC(G)$ when $G$ is a connected algebraic group over $\Fq$, since we can now describe objects and maps in this category in very concrete terms.
+We are in a good position to understand $\QC(G)$ when $G$ is a connected algebraic group over $\Fq$, since we can now describe objects and maps in this category in very concrete terms.
 We begin by recovering a classical result.
@@
  \[
-  \TrFrob{G} : \rQCiso{G} \to G(\Fq)^*
+  \TrFrob{G} : \QCiso{G} \to G(\Fq)^*
  \]
@@
  It suffices\todo{Explain why $T_G$ is injective.} to observe that the group homomorphism
- $\TrFrob{G} : \rQCiso{G} \to G(\Fq)^*$
+ $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$
  is surjective: each character $\chi \in G(\Fq)^*$ determines a finite quasicharacter
- sheaf $(\Lang,\chi^{-1})$ such that Trace of Frobenius of the rigid quasicharacter sheaf
+ sheaf $(\Lang,\chi^{-1})$ such that Trace of Frobenius of the quasicharacter sheaf
  $B_G (L_G(\Lang,\chi^{-1}))$ is $\chi$.
@@
 
-Morphisms in $\rQC(G)$ are also very simple.
+Morphisms in $\QC(G)$ are also very simple.
 
 \begin{proposition}
-If $G$ is a connected algebraic group then $\Aut_{\rQC(G)}(\qcs{L})$ is . . . .
+If $G$ is a connected algebraic group then $\Aut_{\QC(G)}(\qcs{L})$ is . . . .
 \end{proposition}
@@
 \end{proof}
-
-\section{The case of \'etale commutative group schemes} \label{sec:etale}
-
-%\subsection{Quasicharacter sheaves, revisited}
-
-\'Etale group schemes form a counterpoint to connected groups,
-since the component group of a smooth commutative group scheme
-is an \'etale group scheme \cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
-However, the function--sheaf dictionary is substantially different in the two cases.
-To see why, we begin by specializing the definition of rigid quasicharacter sheaves to the case
-of etale commutative group schemes,
-using the equivalence $G \mapsto G(\bFq)$
-from the category of \'etale group schemes over $\Fq$ to the category of groups equipped
-with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group.
-Under this equivalence, a rigid quasicharacter sheaf on an etale commutative group scheme $G$ over $\Fq$ is given by the data of:
-\begin{enumerate}
- \labitem{(qc.1)}{qc.1} an indexed set of one-dimensional
-  $\EE$-vector spaces $\gqcs{L}_x$, as $x$ runs over
-  $G(\bFq)$;
-
- \labitem{(qc.2)}{qc.2} an indexed set of isomorphisms
-  $\mu_{x,y} : \gqcs{L}_{x+y} \xrightarrow{\iso} \gqcs{L}_{x} \otimes\gqcs{L}_{y}$,
-  for all $x,y \in G(\bFq)$, such that
-  \[
-   \begin{tikzcd}[row sep=40]
-    \gqcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
-    && \gqcs{L}_{x+y}\otimes\gqcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
-    \gqcs{L}_{x} \otimes\gqcs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
-    && \gqcs{L}_{x} \otimes\gqcs{L}_{y} \otimes\gqcs{L}_{z}
-   \end{tikzcd}
-  \]
-  commutes, for all $x,y,z\in G(\bFq)$; and
- \labitem{(qc.3)}{qc.3} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
-  such that
-  \[
-   \begin{tikzcd}[row sep=40]
-    \gqcs{L}_{\Frob{}(x)+\Frob{}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{}(x),\Frob{}(y)}}
-    && \gqcs{L}_{\Frob{}(x)}\otimes\gqcs{L}_{\Frob{}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
-    \gqcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
-    && \gqcs{L}_x \otimes\gqcs{L}_y
-   \end{tikzcd}
-  \]
-  commutes, for all $x,y\in G(\bFq)$.
-\end{enumerate}
-Under this equivalence, a morphism $\alpha : \qcs{L} \to \qcs{L'}$ of rigid quasicharacter sheaves on $G$ is given by
-\begin{enumerate}
- \labitem{(qc.4)}{qc.4} an indexed set $\rho_x : \gqcs{L}_x \to \gqcs{L'}_x$
-  of linear transformations such that
-  \[
-   \begin{tikzcd}[column sep=40]
-    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{}(x)} \rar{\rho_{\Frob{}(x)}} & \gqcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
-    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-    & \arrow[swap]{d}{\mu} \gqcs{L}_{x+y} \rar{\rho_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
-    \gqcs{L}_x \rar{\rho_x} & \gqcs{L'}_x
-    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\rho_x\otimes\rho_y} & \gqcs{L'}_x \otimes\gqcs{L'}_y
-   \end{tikzcd}
-  \]
-  both commute for all $x, y \in G(\bFq)$.
-\end{enumerate}
-
-\todo{Find an appropriate place for this discussion}
-
-If $\rho_0 = 0$ then the second diagram for $y=0$ implies that $\rho_x = 0$ for all $x$.
-Conversely, if $\rho_0$ is nonzero then the second diagram for $y = -x$ implies that $\rho_x$ is nonzero for all $x$ and thus an isomorphism since $\gqcs{L}_x$ is one dimensional.
-Most of this paper focuses on the question of determining the isomorphism classes of objects; a complete understanding of the morphisms in $\rQC(G)$ also requires a description of the automorphisms of an arbitrary quasicharacter sheaf $\qcs{L}$.
-
-\begin{proposition}
-The trace map induces an isomorphism of groups
-\[
-\Aut(\qcs{L}) \cong \Hom(G(\bFq)_{\Weil{}}, \EEx).
-\]
-\end{proposition}
-
-\begin{proof}
-The second diagram in \ref{qc.4} shows that the association $x \mapsto \rho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first shows that it factors through $G(\bFq)_{\Weil{}}$.
-Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism then defining $\rho_x$ as multiplication by $\rho(x)$ will satisfy the two diagrams.
-Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the resulting bijection is actually a group ismorphism.
-\end{proof}
-
-We will see that the Trace of Frobenius may not provide complete
-information about isomorphism classes of rigid quasicharacter sheaves on $G$ when $G$ is not a connected algebraic group.
-Our main tool for understanding this phenomenon
-is a group homomorphism from $\rQCiso{G}$ to $\Hh^2(E^\bullet_G)$, defined in Section~\ref{sec:S}, for which the next two sections are preparation.
-
-\subsection{A spectral sequence}\label{sec:E}
-
-The zeroth page of the Hochschild-Serre spectral sequence is a double complex $E^{\bullet, \bullet}$ defined by
-\[
-E^{i,j} = C^i(\Weil{}, C^j(G(\bFq), \EEx)),
-\]
-The derivative of group cohomology yields two derivatives:
-\begin{align*}
-d_0 = d_G &: E^{i,j} \to E^{i,j+1} \\
-d_{\Weil{}} &: E^{i,j} \to E^{i+1,j}.
-\end{align*}
-Combining these yields a derivative $d = d_G + (-1)^j d_{\Weil{}}$ on the total complex
-\[
-E^n_G = \bigoplus_{i+j=n} E^{i,j}.
-\]
-The machinery of spectral sequences gives us a sequence of pages $E_r^{i,j}$, converging to a page $E_{\infty}^{i,j}$.
-We summarize the key properties of this spectral sequence in the following proposition.
-
-\begin{proposition}
-\begin{enumerate}
-\item The second page is given by $E_2^{i,j} = \Hh^i(\Weil{}, \Hh^j(G(\bFq), \EEx))$,
-\item there is an isomorphism $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) \cong \Hh^n(E_G^\bullet)$,
-\item there is a filtration $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) = F_n \supset \cdots \supset F_0 \supset F_{-1} = 0$ where $F_i / F_{i-1} \cong E_{\infty}^{i, n-i}$.
-\end{enumerate}
-\end{proposition}
-
-Moreover, since $\Weil{} \cong \ZZ$ has cohomological dimension $1$, $E_2^{i,j} = 0$ for $i > 1$ and the sequence degenerates at the second page: $E_{\infty}^{i,j} = E_2^{i,j}$.
-We obtain the following corollary:
-
-\begin{corollary}
-There is a short exact sequence
- \[
-  \begin{tikzcd}
-    0 \arrow{r}
-    & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r}
-    & \Hh^2(E^\bullet_G) \arrow{r}
-    & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r}
-    & 0
-  \end{tikzcd}
- \]
-\end{corollary}
-
-This sequence will play a key role in understanding the kernel of $T_G$, as described in the next few sections.
-For this application, we need a good understanding of these maps to and from the total complex.
-
-\begin{proposition} \label{prop:ses_desc}
-\begin{enumerate}
-\item Every class $[\alpha\oplus\beta\oplus\gamma] \in \Hh^2({\bar G},\EEx)$ is cohomologous to one with $\gamma=0$.
-\item The map $\Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx))$ is given by $[\alpha\oplus\beta\oplus 0] \mapsto [\beta]$.
-\item Suppose $a \in Z^2({\bar G}, \EEx)$ represents a class in $\Hh^2({\bar G},\EEx)$ fixed by Frobenius.
-The map $\Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to \Hh^2(E^\bullet_G)$ is given by $[a] \mapsto [a \oplus 0 \oplus 0]$.
-\end{enumerate}
-\end{proposition}
-\begin{proof}
-Since $\Hh^2(\Weil{}, C^0({\bar G}, \EEx)) = 0$, we may find a $\gamma_1 \in C^1(\Weil{}, C^0({\bar G}, \EEx))$ with $d_{\Weil{}}\gamma_1 = \gamma$.
-Subtracting $d \gamma_1$ from $\alpha\oplus\beta\oplus\gamma$, we may assume that $\gamma = 0$.
-
-The latter two claims follow from tracing through the definition of latter pages in the spectral sequence; see Vakil \cite{} for example \todo{update reference}.
-\end{proof}
-
-\subsection{From rigid quasicharacter sheaves to the total complex}\label{sec:S}
-
-In this section we define an isomorphism
-\[
-S_G : \rQCiso{G} \to \Hh^2(E^\bullet_G).
-\]
-Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a rigid quasicharacter sheaf on $G$.
-For each geometric point $x\in {\bar G}$, choose a basis $\{ v_x \}$ for $\gqcs{L}_x$.
-Through this choice, $\qcs{L}$ determines functions
-\begin{align*}
-a : {\bar G}\times {\bar G} &\to \EEx & b : {\bar G} &\to \EEx \\
-\mu_{x,y}(v_{x+y}) &= a(x,y) v_x \otimes v_y & \phi_x(v_{\Frob{G}(x)}) &= b(x) v_x.
-\end{align*}
-Condition~\ref{QC.2} implies that
-\begin{equation}\label{2-cocyle}
-a(x+y,z) a(x,y) = a(x,y+z) a(y,z)
-\end{equation}
-for all $x,y,z\in {\bar G}$, so $a \in Z^2({\bar G},\EEx)$.  Similarly, condition~\ref{QC.3} gives
-\begin{equation}\label{nohom}
-\frac{a(\Frob{G}(x),\Frob{G}(y))}{a(x,y)} =  \frac{b(x+y)}{b(x) b(y)}
-\end{equation}
-for $x, y \in {\bar G}$.
-Let $\alpha \in C^0(\Weil{},C^2({\bar G},\EEx)$ be the $0$-cochain corresponding to $a$ and let $\beta\in C^1(\Weil{},C^1({\bar G},\EEx)$ be the cocycle such that $\beta(\Frob{})$ is $b$ \emph{written additively}.
-Then
-\[
-d_G\alpha =0, \qquad\qquad
-d_{\Weil{}} \alpha = d_{G} \beta,\qquad\qquad
-d_{\Weil{}} \beta =0;
-\]
-in other words,
-\[\alpha\oplus \beta \in Z^2(E^\bullet_G).\]
-Although the cocycle $\alpha\oplus \beta$ is not well defined by $\qcs{L}$, its class in $Z^2(E^\bullet_G)$ is.
-To see this, let $\{ v'_x \in \gqcs{L}_x^\times \tq x \in {\bar G}\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$ be defined by $\qcs{L}$ and this choice, as above.
-Now let $\delta \in C^0(\Weil{},C^1({\bar G},\EEx))$ be the additive version of the function $d : {\bar G}\to \EEx$ defined by $v'_x = d(x) v_x$.
-Then, chasing through \ref{QC.2} and \ref{QC.3} we find
-\[
-\alpha'\oplus\beta' = \alpha\oplus\beta + d\delta,
-\]
-so the class $[\alpha\oplus\beta]$ of $\alpha\oplus\beta$ in $\Hh^2(E^\bullet_G)$ is independent of the choice made above.
-It is also easy to see that $[\alpha\oplus\beta] = [\alpha_0\oplus\beta_0]$ when $\qcs{L} \iso \qcs{L}_0$,
-which concludes the definition of the function
-\begin{align*}
-S_G : \rQCiso{G} &\to \Hh^2(E^\bullet_G)\\
-[\qcs{L}] &\mapsto [\alpha\oplus \beta].
-\end{align*}
-It is also easy to see that $[\alpha_1\oplus\beta_1] + [\alpha_2\oplus\beta_2] = [\alpha_3\oplus\beta_3]$ when $\qcs{L}_3 = \qcs{L}_1\otimes \qcs{L}_2$, so $S_G$ is a group homomorphism.
-
-\begin{remark}
-Although we will only use the group homomorphism $S_G : \rQCiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$.
-However, the next result is false in that context.
-\end{remark}
-
-\begin{proposition}
-If $G$ is \'etale then $S_G$ is an isomorphism.
-\end{proposition}
-\begin{proof}
-We first show that $S_G$ is injective.  Suppose $\qcs{L} \in \rQCiso{G}$ with $S_G(\qcs{L}) = [\alpha \oplus \beta] = 0$,
-so that $\alpha \oplus \beta = d\rho$ for some $\rho \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
-For each $x\in {\bar G}$, define $\rho_x : \gqcs{L}_x \to \EEx$ by $v_x \mapsto \rho(x)$.
-Then the indexed set of isomorphisms $\{ \gamma_x : \gqcs{L}_x \to \EE \tq x\in {\bar G}\}$
-defines an isomorphism $\qcs{L} \to (\EE)_G$.
-Since $\qcs{L} = 0 \in \rQCiso{G}$, $S_G$ is injective.
-
-To see that $S_G$ is surjective, begin with $\alpha\oplus\beta\oplus 0 \in Z^2(E^\bullet_G)$.
-Since $d_{\Weil{}} \beta = 0$, we may define $a = \alpha \in C^2({\bar G},\EEx)$ and
-$b = \beta(\Frob{}) \in C^1({\bar G},\EEx)$, which are related to $\alpha$ and $\beta$ as above.
-Set $\gqcs{L}_x = \EEx$, define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes\gqcs{L}_y$
-by $\mu_{x,y}(1) = a(x,y) 1\otimes 1$ and $\phi_x : \gqcs{L}_{\Frob{G}(x)} \to \gqcs{L}_x$ by $\phi_x(1)= b(x)$.
-Then \ref{qc.1} holds since $d_G \alpha =0$ and \ref{qc.2} holds since $d_{\Weil{}}\alpha =d_G \beta$.
-Tracing the construction backward, we have defined a rigid quasicharacter sheaf $\qcs{L}$ on $G$ with
-$S_G(\qcs{L}) = [\alpha\oplus\beta\oplus\gamma]$, showing that $S_G$ is surjective.
-\end{proof}
-
-\subsection{$S$ and $T$}
-
-In this section we describe the relationship between the group homomorphisms $\TrFrob{G}$ and $S_G$.
-%
-We begin with a simple, general result relating duals, invariants and coinvariants.
-
-\begin{lemma} \label{lem:dual-inv}
-Let $X$ be an abelian group equipped with an action of $\Weil{}$.
- Then
-\begin{align*}
- (X^*)_{\Frob{}} &\to (X^{\Frob{}})^* \\
- [f] &\mapsto f|_{X^{\Frob{}}}
-\end{align*}
-is an isomorphism.
-\end{lemma}
-
-\begin{proof}
-We can describe $X^{\Frob{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
-let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
-\[
- 0 \to X^{\Frob{}} \to X \to Y \to 0
-\]
-yields
-\[
- 0 \to Y^* \to X^* \to (X^{\Frob{}})^* \to \Ext^1_\ZZ(Y, \EEx).
-\]
-Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Frob{}})^*$.
-\end{proof}
-
-\begin{corollary}
-If $G$ is \'etale then $\TrFrob{G} : \rQCiso{G} \to G(\Fq)^*$ is surjective.
-\end{corollary}
-\begin{proof}
-Pick $\chi \in G(\Fq)^*$.
-By Lemma~\ref{lem:dual-inv}, there is some $b\in G(\bFq)^*$ such that $b\vert_{G(\Fq)^*} = \chi$.
-Set $\gqcs{L}_x = \EE$ for every $x\in G(\bFq)$.
-Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$ and
-$\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = b(x)$.
-Since $b : G(\bFq) \to \EEx$ is a group homomorphism,
-condition \eqref{nohom} is satisfied with $a =1$ and $\qcs{L} = (\gqcs{L}, \mu, \phi)$
-is a rigid quasicharacter sheaf with $\trFrob{\qcs{L}} = \chi$.
-\end{proof}
-
-\begin{proposition} \label{prop:etale-iso}
- If $G$ is \'etale then the map $S_G : \rQCiso{G}\to \Hh^2(E^\bullet_G)$ induces an isomorphism of short exact sequences
-\[
-\begin{tikzcd}
- 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \rQCiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
-  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r} & 0.
- \end{tikzcd}
- \]
-\end{proposition}
-\begin{proof}
-This result follows easily from Proposition \ref{prop:ses_desc}.
-\end{proof}
-
-\section{The main result}\label{sec:main}
-
-In the introduction to this paper we noted that, when working with connected commutative algebraic groups over finite fields, Deligne's dictionary can be described using Weil sheaves $\qcs{L}$ for which there exists an isomorphism $m^* \qcs{L} \iso \qcs{L} \boxtimes\qcs{L}$, without keeping track of the isomorphism.
-In this section use that perspective to find a perfect dictionary between flabby quasicharacter sheaves on $G$ and characters of $G(\Fq)$.
 
@@
 \begin{tikzcd}
-\rQC(0) \rar & \rQC(\pi_0(G)) \arrow{r}{\pi_0^*} & \rQC(G) \arrow{r}{\iota_0^*} & \rQC(G^0) \rar & \rQC(0)
+\QC(0) \rar & \QC(\pi_0(G)) \arrow{r}{\pi_0^*} & \QC(G) \arrow{r}{\iota_0^*} & \QC(G^0) \rar & \QC(0)
 \end{tikzcd}
@@
 0 \rar &
-\rQCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \rQCiso{G} \arrow{r}{\iota_0^*} & \rQCiso{G^0} \rar & 0.
+\QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
 \end{tikzcd}
 \end{equation}
- Note that we found the groups $\rQCiso{G^0}$
-and $\rQCiso{\pi_0(G)}$
+ Note that we found the groups $\QCiso{G^0}$
+and $\QCiso{\pi_0(G)}$
 in Sections~\ref{sec:connected} and \ref{sec:etale}, respectively.
@@
 \begin{proposition}\label{prop:restriction}
-For every rigid quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf
+For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf
 $\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$.
-As a consequence, the restriction functor $\iota_0^* : \rQC(G)\to \rQC(G^0)$ is essentially surjective.
+As a consequence, the restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
 \end{proposition}
@@
   By Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}, every
-  rigid quasicharacter sheaf on $G^0$ is isomorphic to a
+  quasicharacter sheaf on $G^0$ is isomorphic to a
   finite quasicharacter sheaf on $G^0$,
@@
   \begin{tikzcd}
-%  0 \rar &
- \rQCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \rQCiso{G} \arrow{r}{\iota_0^*} & \rQCiso{G^0} \rar & 0.
+  0 \rar & \QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
   \end{tikzcd}
@@
 \begin{proof}
-The sequence is exact at $\rQCiso{G^0}$ by Proposition~\ref{prop:restriction},
-so here we show that it is also exact at $\rQCiso{G}$.
+The sequence is exact at $\QCiso{G^0}$ by Proposition~\ref{prop:restriction},
+so here we show that it is also exact at $\QCiso{G}$.
 First note that $\iota_0^* \circ \pi_0^*$ is trivial by Proposition~\ref{prop:pullback}.
-So it suffices to show that if $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a rigid quasicharacter sheaf on $G$
+So it suffices to show that if $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$
 with $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$ then $\qcs{L}$ is in the essential image of $\pi_0^*$.
@@
 Using \eqref{eq:qc}, it follows that \ref{qc.1}, \ref{qc.2} and \ref{qc.3} are satisfied for
-$\qcs{E} \ceq (\gqcs{E}_x, \mu_{x,y}, \phi_x)$, thus defining a rigid quasicharacter sheaf on $\pi_0(G)$.
+$\qcs{E} \ceq (\gqcs{E}_x, \mu_{x,y}, \phi_x)$, thus defining a quasicharacter sheaf on $\pi_0(G)$.
 
@@
 The resulting isomorphism $\gqcs{L} \to \pi_0^* \gqcs{E}$ satisfies \ref{QC.4},
-thus defining an isomorphism $\qcs{L} \to \pi_0^* \qcs{E}$ in $\rQC(G)$.
+thus defining an isomorphism $\qcs{L} \to \pi_0^* \qcs{E}$ in $\QC(G)$.
 \end{proof}
@@
 We saw in Proposition~\ref{prop:functorialG} that Trace of Frobenius
-$\TrFrob{G} : \rQCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
+$\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
 In this section we improve that result.
@@
   \[
-  \lTrFrob{G} : \lQCiso{G} \to G(\Fq)^*
-  \]
-is a functorial group isomorphism.
+  \TrFrob{G} : \QCiso{G} \to G(\Fq)^*
+  \]
+is surjective with kernel isomorphic to $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$.
 \end{theorem}
@@
   \]
-  The sequence of
-  abelian groups
+  Let
+  \[
+  \begin{tikzcd}[row sep=20]
+    0 \rar & \ker \TrFrob{\pi_0(G)} \arrow[dashed]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dashed]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
+    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
+    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
+    0 \rar & \pi_0(G)(\Fq)^* \rar \dar
+    & \arrow{d} G(\Fq)^* \rar & G^0(\Fq)^* \rar \dar & 0\\
+    & \coker \TrFrob{\pi_0(G)} =0 \arrow[dashed]{r} & \coker \TrFrob{G} \arrow[dashed]{r} &  \coker \TrFrob{G^0} =0 &
+  \end{tikzcd}
+  \]
+  be the commutative diagram of abelian groups obtained by applying
+  Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.
+
+  The sequence of abelian groups
   \begin{equation}\label{eq:pi0k}
@@
   character groups is also exact.
-  Let
-  \[
-  \begin{tikzcd}[row sep=20]
-    {}& \ker \TrFrob{\pi_0(G)} \arrow[dashed]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dashed]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
-    %0 \rar
-    & \rQCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
-    & \rQCiso{G} \rar \dar{\TrFrob{G}} & \rQCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
-    0 \rar & \pi_0(G)(\Fq)^* \rar \dar
-    & \arrow{d} G(\Fq)^* \rar & G^0(\Fq)^* \rar \dar & 0\\
-    & \coker \TrFrob{\pi_0(G)} =0 \arrow[dashed]{r} & \coker \TrFrob{G} \arrow[dashed]{r} &  \coker \TrFrob{G^0} =0 &
-  \end{tikzcd}
-  \]
-  be the commutative diagram of abelian groups obtained by applying
-  Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.
-%
-The top row is also exact:
-  the surjectivity of $\rQCiso{G} \to \rQCiso{G^0}$ follows from Proposition~\ref{prop:restriction}
-  while exactness at $\rQCiso{G}$ is given by Proposition~\ref{prop:middleexact}.
+
+  The upper row is exact by Proposition~\ref{prop:middleexact}.
   Now Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}
@@
 It follows from the snake lemma that $\coker \TrFrob{G} =0$
-and $\ker \TrFrob{\pi_0(G)} \to \ker \TrFrob{G}$ is surjective.
-
-We now turn our attention $\lTrFrob{G}: \lQCiso{G}  \to G(\Fq)^*$ is an isomorphism.
-First, note that $\lTrFrob{G}$ is surjective because $\TrFrob{G}$ is surjective.
-We will now show that the kernel of $\lTrFrob{G}$ is trivial.
-
-First, suppose $G$ is etale.
-Let $(\gqcs{E},\phi')$ be a rigid quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{E},\phi')}=1$.
-Let $\qcs{E} = (\gqcs{E},\mu,\phi')$ be a quasicharacter sheaf.
-By Proposition~\ref{prop:etale-iso}, $S_G(\qcs{E}) = [\alpha\oplus 0]$ for some $\alpha \in Z^0(\Weil{},Z^2({\bar G},\EEx))$
-corresponding to a choice $\{ v_x \in \gqcs{E}_x^\times \tq x\in {\bar C}\}$.
-Let $a\in Z^2({\bar G},\EEx)$ be the multiplicative version of $\alpha$
-and let $\mu'$ be the indexed set of isomorphisms $\mu'_{x,y} : \EE \to \EE\otimes \EE$ defined by $1 \mapsto a(x,y) 1 \otimes 1$.
-Then $(\EE,\mu', 1)$ is a rigid quasicharacter sheaf the isomorphisms $\gqcs{E}_x \to \EE$ defined by $v_x \mapsto 1$ gives an isomorphism $(\gqcs{E},\mu,\phi')\to ((\EE)_{\bar C},\mu', 1)$ in $\rQC(G)$.
-It follows that $(\gqcs{E},\phi')\iso ((\EE)_{\bar G},1)$ in $\lQC(G)$, so $\lTrFrob{G}$ is injective.
-This completes the proof of Theorem~\ref{thm:snake} in the case that $G$ is etale.
-
-Now let $G$ be arbitrary
-and let $(\gqcs{L},\phi)$ be a flabby quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{L},\phi)}=1$.
-Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a rigid quasicharacter sheaf.
-We saw above that $\ker \TrFrob{\pi_0(G)}\to \TrFrob{G}$ is surjective in this case,
-so $\qcs{L} = \pi_0^*\qcs{E}$ for some $\qcs{E}\in \rQC(\pi_0(G))$.
-Since $\trFrob{\qcs{L}}(g) = \trFrob{\qcs{E}}(\pi_0(g))$ and since $\pi_0 : G(\Fq) \to \pi_0(G)(\Fq)$ is surjective, $\trFrob{\qcs{E}}=1$.
-But now $\qcs{E} \iso ((\EE)_{\pi_0({\bar G})},\mu', 1)$ by the paragraph above.
-So $\qcs{L} = \pi_0^*\qcs{E} \iso \pi_0^*((\EE)_{\pi_0({\bar G})},\mu', 1) = ((\EE)_{\bar G},\pi_0^*\mu', \pi_0^*1)$ in $\rQC(G)$.
-It follows that $(\gqcs{L},\phi) \iso ((\EE)_{\bar G},1)$ in $\lQC(G)$.
-This completes the proof of Theorem~\ref{thm:snake}.
-\end{proof}
-
-\begin{corollary}\label{cor:exact}
-  If $G$ is a smooth, commutative group scheme over
-  $\Fq$ then pullback yields an exact sequence
-\[
-0 \to \lQCiso{\pi_0(G)} \to \lQCiso{G} \to \lQCiso{G^0} \to 0
-\]
-of abelian groups.
-\end{corollary}
-
-\begin{proof}
-Argue as in the first paragraph in the proof of Theorem~\ref{thm:snake},
-using the category $\lQC(G)$ in place of $\rQC(G)$.
-\end{proof}
+and $\ker \TrFrob{\pi_0(G)} \to \ker \TrFrob{G}$ is an isomorphism.
+
+%We now turn our attention $\lTrFrob{G}: \lQCiso{G}  \to G(\Fq)^*$ is an isomorphism.
+%First, note that $\lTrFrob{G}$ is surjective because $\TrFrob{G}$ is surjective.
+%We will now show that the kernel of $\lTrFrob{G}$ is trivial.
+
+%First, suppose $G$ is etale.
+%Let $(\gqcs{E},\phi')$ be a quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{E},\phi')}=1$.
+%Let $\qcs{E} = (\gqcs{E},\mu,\phi')$ be a quasicharacter sheaf.
+%By Proposition~\ref{prop:etale-iso}, $S_G(\qcs{E}) = [\alpha\oplus 0]$ for some $\alpha \in Z^0(\Weil{},Z^2({\bar G},\EEx))$
+%corresponding to a choice $\{ v_x \in \gqcs{E}_x^\times \tq x\in {\bar C}\}$.
+%Let $a\in Z^2({\bar G},\EEx)$ be the multiplicative version of $\alpha$
+%and let $\mu'$ be the indexed set of isomorphisms $\mu'_{x,y} : \EE \to \EE\otimes \EE$ defined by $1 \mapsto a(x,y) 1 \otimes 1$.
+%Then $(\EE,\mu', 1)$ is a quasicharacter sheaf the isomorphisms $\gqcs{E}_x \to \EE$ defined by $v_x \mapsto 1$ gives an isomorphism $(\gqcs{E},\mu,\phi')\to ((\EE)_{\bar C},\mu', 1)$ in $\QC(G)$.
+%It follows that $(\gqcs{E},\phi')\iso ((\EE)_{\bar G},1)$ in $\lQC(G)$, so $\lTrFrob{G}$ is injective.
+%This completes the proof of Theorem~\ref{thm:snake} in the case that $G$ is etale.
+
+%Now let $G$ be arbitrary
+%and let $(\gqcs{L},\phi)$ be a flabby quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{L},\phi)}=1$.
+%Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf.
+%We saw above that $\ker \TrFrob{\pi_0(G)}\to \TrFrob{G}$ is surjective in this case,
+%so $\qcs{L} = \pi_0^*\qcs{E}$ for some $\qcs{E}\in \QC(\pi_0(G))$.
+%Since $\trFrob{\qcs{L}}(g) = \trFrob{\qcs{E}}(\pi_0(g))$ and since $\pi_0 : G(\Fq) \to \pi_0(G)(\Fq)$ is surjective, $\trFrob{\qcs{E}}=1$.
+%But now $\qcs{E} \iso ((\EE)_{\pi_0({\bar G})},\mu', 1)$ by the paragraph above.
+%So $\qcs{L} = \pi_0^*\qcs{E} \iso \pi_0^*((\EE)_{\pi_0({\bar G})},\mu', 1) = ((\EE)_{\bar G},\pi_0^*\mu', \pi_0^*1)$ in $\QC(G)$.
+%It follows that $(\gqcs{L},\phi) \iso ((\EE)_{\bar G},1)$ in $\lQC(G)$.
+%This completes the proof of Theorem~\ref{thm:snake}.
+\end{proof}
+
+%\begin{corollary}\label{cor:exact}
+%  If $G$ is a smooth, commutative group scheme over
+%  $\Fq$ then pullback yields an exact sequence
+%\[
+%0 \to \lQCiso{\pi_0(G)} \to \lQCiso{G} \to \lQCiso{G^0} \to 0
+%\]
+%of abelian groups.
+%\end{corollary}
+
+%\begin{proof}
+%Argue as in the first paragraph in the proof of Theorem~\ref{thm:snake},
+%using the category $\lQC(G)$ in place of $\QC(G)$.
+%\end{proof}
+
+\section{Application to \texorpdfstring{$p$}{p}-adic tori}
+
+\subsection{Bounded quasicharacter sheaves}\label{sec:bounded}
+
+In this section we consider a class of quasicharacter sheaves on $G$ obtained by
+replacing the Weil sheaf $(\gqcs{L}, \phi)$ on $\bG$ in the definition of a quasicharacter
+sheaf with an $\ell$-adic local system on $G$ itself.
+
+\begin{definition}
+Let $\bQC(G)$ be the category of pairs $(\qcs{L}_0,\mu_0)$
+where $\qcs{L}_0$ an $\ell$-adic local system on $G$ of rank~one,
+equipped with an isomorphism $\mu_0 : m^* \qcs{L}_0 \to \qcs{L}_0 \boxtimes \qcs{L}_0$
+satisfying the analogue of \ref{QC.1} on $G$;
+morphisms in $\bQC(G)$ are defined as in the second part of
+\ref{QC.3}.
+This is the category of \emph{bounded quasicharacter sheaves} on $G$.
+\end{definition}
+
+The category of bounded quasicharacter sheaves is a rigid monoidal category in the obvious way.
+
+\begin{proposition}\label{prop:BG}
+Extension of scalars defines a full and faithful functor
+$B_G : \bQC(G) \hookrightarrow \QC(G)$.
+\end{proposition}
+
+\begin{proof}
+ Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
+ Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$.
+ Then $\qcs{L}_0$ is an $\ell$-adic constructible sheaf on $G$ and
+ $b_G^* \qcs{L}_0$ comes equipped with an isomorphism
+ $\phi : \Frob{G}^* b_G^*\qcs{L}_0 \to b_G^* \qcs{L}_0$.
+ Moreover, the functor $\qcs{L}_0 \mapsto (b_G^* \qcs{L}_0,\phi)$
+ from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
+ is full and faithful \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}}.
+ This functor preserves local constancy, so takes local systems to local systems.
+ Set $\mu \ceq b_{G\times G}^*\mu_0$; clearly, this satisfies \ref{QC.2}
+ with $b_G^*\qcs{L}_0$ playing the role of $\gqcs{L}$.
+ Moreover, $\phi$ is compatible with $\mu$ in the sense of \ref{QC.3}.
+ This construction defines the functor $B_G : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
+ and also shows that it is full and faithful.
+\end{proof}
+
+In general, $\bQC(G)$ is an essentially
+proper subcategory of $\QC(G)$. We will identify $\bQC(G)$ with its image under $B_G$
+and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ is \emph{bounded}
+if it is isomorphic to some $B_G(\qcs{L}_0, \mu_0)$.
+We will see in Corollary~\ref{cor:bounded-and-finite} that bounded quasicharacter sheaves are exactly quasicharacter sheaves with bounded Trace of Frobenius.
+
+\subsection{Finite implies Bounded}
+
+In this section we show that $\fQC(G)$ is a full subcategory of $\bQC(G)$.
+To prepare for that result, we need the next two lemmas.
+
+\begin{lemma}\label{lemma:finite-pullback}
+Let $g : J \to G$ be a morphism of smooth groups schemes over $\Fq$.
+Let $f_g : H\times_G J\to J$
+be the pullback of $f$ along $g$ and define $\psi_g : \ker f_g \to \Aut(V)$ as in the diagram below:
+\[
+\begin{tikzcd}
+V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
+  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker f_g}} \ker f_g \arrow[hook]{r}
+  & \arrow[swap]{u}{g_f} H\times_G J \arrow{r}{f_g} & \arrow{u}{g} J.
+\end{tikzcd}
+\]
+Then $(f,\psi) \mapsto (f_g,\psi_g)$
+defines a monomial functor $g^* : C(G)[W^{-1}] \to C(J)[W^{-1}]$.
+\end{lemma}
+
+\begin{proof}
+The key point is that pullback along $g$ takes discrete isogenies to discrete isogenies,
+and maps over $G$ to maps over $J$, as pictured below.
+\[
+\begin{tikzcd}[row sep={{{{40,between origins}}}},column sep={{{{50,between origins}}}}]
+%\ V \arrow{dd}{T} &
+\Aut(V) && \arrow[swap]{ll}{\psi} \ker f \arrow[hook]{rr} \arrow[leftarrow]{dd} && H \arrow{rr}{f} \arrow[leftarrow]{dd} && \arrow[equal]{dd} G\\
+% &
+& \arrow{ul} \ker f\times_G J \arrow{ur} \arrow[hook, crossing over]{rr} && H\times_G J \arrow{ur} \arrow[crossing over]{rr} && J \arrow[swap]{ur}{g} & \\
+%V' &
+ \Aut(V') && \arrow[swap,pos=0.25]{ll}{\psi'} \ker f'  \arrow[hook]{rr}
+&& H' \arrow[pos=0.25]{rr}{f'} && G\\
+% &
+ & \arrow{ul} \ker f'\times_G J \arrow[crossing over]{uu} \arrow{ur} \arrow[hook]{rr}
+ && \arrow[crossing over]{uu} H'\times_G J \arrow{ur} \arrow{rr} && \arrow[equals, crossing over]{uu} J \arrow[swap]{ur}{g} &
+\end{tikzcd}
+\]
+%In this form we could treat $g^*$ as a functor $C(J)\to C(G)$,
+%were it not for the fact that pullback is defined only up to isomorphism.
+%In the localized categories, this ambiguity disappears.
+\end{proof}
+
+\begin{lemma}\label{lemma:finite-iso}
+Each finite quasicharacter sheaf $(f,\psi)$ in $\fQC(G)$ determines a
+canonical isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\fQC(G\times G)$.
+ \end{lemma}
+
+\begin{proof}
+We will prove the proposition by finding a weak isomorphism
+$m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ in $C_1(G\times G)$
+and showing that, after passing from $C_1(G\times G)$ to
+$\fQC(G\times G)$, the resulting isomorphism,
+denoted by $\mu(f,\psi)$, is canonically determined by $(f,\psi)$.
+
+Set $H_m \ceq H\times_G(G\times G)$,
+write $f_m : H_m \to G \times G$ for the pullback of $f$ to $H_m$,
+and let $A$ and $A_m$ be the kernels of $f$ and $f_m$ respectively.  Consider the diagram of Lemma~\ref{lemma:finite-pullback}:
+\[
+\begin{tikzcd}[column sep=40]
+V & \Aut(V) & \arrow[swap]{l}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
+  &  & \arrow[dashed]{ul}{\psi_m} \arrow[swap]{u}{(m_f)\vert_{A_m}} A_m \arrow[hook]{r}
+  & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G.
+\end{tikzcd}
+\]
+We have $(f,\psi) \boxtimes (f,\psi) = (f\times f, \psi\otimes \psi)$.
+Since $f\circ m_H = m \circ (f\times f)$, the universal property of pullback gives
+a unique $\theta : H\times H \to H_m$ making the following commute.
+\[
+\begin{tikzcd}[row sep=20,column sep=8]
+\ & V \arrow{dd}{T} && \Aut(V) && A \arrow[hook]{rr} \arrow[swap]{ll}{\psi} &&  H \arrow{rr}{f} && G\\
+ && && \arrow{ul}{\psi_m} A_m  \arrow[hook]{rr} \arrow{ur} && H_m \arrow[pos=0.3]{ur}{m_f} \arrow[swap, pos=0.8]{rr}{f_m}
+ && G \times G \arrow[equal]{dr} \arrow[pos=0.42]{ur}{m} & \\
+& V\otimes V && \Aut(V\otimes V) && \arrow[swap]{ll}{\psi \otimes \psi} \arrow[dashed,swap,pos=0.3]{ul}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr}
+&& \arrow[dashed,swap]{ul}{\theta} \arrow[crossing over,swap,pos=0.7]{uu}{m_H} H\times H \arrow{rr}{f\times f} && G\times G
+\end{tikzcd}
+\]
+Choose a basis $\{ v \}$ for $V$; then $\{ v\otimes v \}$ is a basis for $V\otimes V$.
+Let $T : V \to V\otimes V$ be the linear transformation taking $v$ to $v\otimes v$. Then the lower part of this
+diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G\times G)$.
+%
+While $\theta$ was canonical, $T$ was not, as it depended on the choice of a basis for $V$.
+However, after passing from $C_1(G\times G)$ to $\fQC(G\times G)$, the resulting isomorphism 
+$\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ in $\fQC(G\times G)$ is independent of the choice of basis for $V$.
+ \end{proof}
+
+\begin{proposition}\label{prop:bounded}
+ $\fQC(G)$ is a full subcategory of $\bQC(G)$.
+\end{proposition}
+
+\begin{proof}
+ To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \fQC(G) \to \bQC(G)$.
+
+ If $V$ is a finite-dimensional $\EE$-vector space then we write $V_H$ for the constant sheaf $V$ on $H$.
+If $(f,\psi)$ is a finite quasicharacter on $G$ where $\psi$ is a representation of $\ker f$ on $V$,
+let $L(f,\psi)$ be the local system on $G$ given by the $\psi$-isotypic component of the local system $f_* V_H$ on $G$.
+ We may identify the stalk $(f_* V_H)_{\bar g}$ of $f_* V_H$ at a geometric point ${\bar g}$ on $G$
+ with the $\EE$-vector space $\Hom_\text{set}(\abs{f^{-1}({\bar g})},V)$
+ and the stalk $L(f,\psi)_{\bar g}$ of $L(f,\psi)$ at a geometric point ${\bar g}$ on $G$
+ with the $\EE$-vector space consisting of those functions $s: \abs{f^{-1}({\bar g})} \to V$ such that
+ $s(a\cdot {\bar h}) = \psi(a)(s({\bar h}))$ for all $a\in \ker f$ and for all ${\bar h} \in f^{-1}({\bar g})$.
+
+ For any map $(g,T)$ in $C(G)$, let $L(g,T) : L(f,\psi) \to L(f',\psi')$ be the homomorphism of local systems defined
+ by $s \mapsto s' \ceq T\circ s\circ g$.
+ This construction defines a full monoidal functor $L$ from $C(G)$ to the category $\Loc(G)$ of local systems on $G$ that
+ commutes with pullback along any morphism of $\QC$-schemes,
+ as defined using Lemma~\ref{lemma:finite-pullback}.
+ Moreover, since $L(f,T)$ is an isomorphism of local systems
+ if and only if $(f,T)$ is a weak isomorphism,
+ the full functor $L : C(G) \to \Loc(G)$ factors through the localization functor $C(G) \to C(G)[W^{-1}]$
+ to define a full and faithful functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$;
+ see \cite{kashiwara-schapira:CatgoriesSheaves}*{Exercise 7.5}.
+
+ By Lemma~\ref{lemma:finite-iso}, each $(f,\psi) \in \fQC(G)$ canonically determines
+ an isomorphism
+ \[
+ \mu(f,\psi) : m^*(f,\psi) \to (f,\psi) \boxtimes (f,\psi)
+ \]
+ in $\fQC(G\times G)$.
+ It follows immediately that the functor
+ \[
+ L_G  \ceq  L_{W}\vert_{\fQC(G)} : \fQC(G) \to \bQC(G),
+ \]
+ given on objects by $(f,\psi) \mapsto (L(f,\psi), L_{W}(\mu(f,\psi)))$,
+ is a full and faithful monoidal functor, completing the proof.
+\end{proof}
+
+On general smooth group $\Fq$-schemes $G$, 
+there are bounded quasicharacter sheaves which are not finite.  
+Identifying $\fQC(G)$ with its image under $B_G \circ L_G$, as defined in
+Proposition~\ref{prop:BG} and in the proof of Proposition~\ref{prop:bounded},
+we will see in Corollary~\ref{cor:bounded-and-finite} that
+a quasicharacter sheaf is finite if and only if its Trace of Frobenius has finite image.
 
@@
 \begin{enumerate}
-\item $\qcs{L} \in \rQC(G)$ is bounded if and only if $\trFrob{\qcs{L}}$ has bounded image,
-\item $\qcs{L}\in \rQC(G)$ is finite if and only if $\trFrob{\qcs{L}}$ has finite image.
+\item $\qcs{L} \in \QC(G)$ is bounded if and only if $\trFrob{\qcs{L}}$ has bounded image,
+\item $\qcs{L}\in \QC(G)$ is finite if and only if $\trFrob{\qcs{L}}$ has finite image.
 \end{enumerate}
@@
 On the connected component
-$G^0$, all rigid quasicharacter sheaves are bounded and finite by Proposition~\ref{prop:connected}.
+$G^0$, all quasicharacter sheaves are bounded and finite by Proposition~\ref{prop:connected}.
 On the other hand, $G^0(\Fq)$ is finite by Lemma~\ref{lem:G0alg-grp} and thus Trace of Frobenius
@@
 In the case that $G$ is \'etale, which we now suppose,
-one can easily detect when a rigid quasicharacter sheaf is bounded or finite.
+one can easily detect when a quasicharacter sheaf is bounded or finite.
 With reference to Section~\ref{sec:S},
@@
 With Corollary~\ref{cor:bounded-and-finite} in hand
-we see that all rigid quasicharacter sheaves on $G$ are finite quasicharacter sheaves
+we see that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves
 when $G$ is a commutative algebraic group over $\Fq$;
@@
 are up to the task of geometrizing all characters of $G(\Fq)$ for smooth commutative group schemes $G$ since, in general, neither of the full subcategories
-$\rfQC(G) \subset \rbQC(G) \subset \rQC(G)$ are equivalences.
+$\fQC(G) \subset \bQC(G) \subset \QC(G)$ are equivalences.
 For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$:
@@
 %In this latter case the stalk of the quasicharacter sheaf at the component $1$ is defined by a pro-\'etale cover rather than an \'etale cover.
+
+\subsection{Base change}\label{sec:basechange}
+
+When using quasicharacter sheaves to study characters, it is useful to understand
+how quasicharacter sheaves behave under change of fields.
+Let $k'$ be a finite extension of $k$. Then $k \hookrightarrow k'$ induces a group homomorphism
+$i_{k'/k} : G(k) \hookrightarrow G(k')$ and thus a homomorphism
+\begin{align*}
+i_{k'/k}^* : G(k')^* &\to G(k)^* \\
+\chi &\mapsto \chi\circ i_{k'/k}.
+\end{align*}
+We can interpret this operation on characters in terms of quasicharacter sheaves:
+
+\begin{proposition} \label{prop:csbe}
+Set $G_{k'} \ceq G\times_\Spec{k} \Spec{k'}$ and let
+\[
+\QC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \QC(G)
+\]
+be the functor obtained by pullback along the canonical closed immersion of $k$-schemes
+$\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$
+\cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}.
+The following diagram commutes:
+\[
+\begin{tikzcd}
+\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\TrFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\TrFrob{G}} \\
+G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
+\end{tikzcd}
+\]
+\end{proposition}
+\begin{proof}
+This result follows immediately from Proposition~\ref{prop:pullback} together with the identifications
+\[
+\Res_{k'/k}(G_{k'})(k) \cong G_{k'}(k') \cong G(k')
+\]
+from the definitions of Weil restriction and base change.
+\end{proof}
+
+In the opposite direction, let $\Nm : G(k') \to G(k)$ be the norm map and consider the group homomorphism:
+\begin{align*}
+\Nm^* : G(k)^* &\to G(k')^* \\
+\chi &\mapsto \chi\circ \Nm.
+\end{align*}
+We can also interpret this operation on characters in terms of quasicharacter sheaves.
+
+If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$, we define
+a quasicharacter sheaf $\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
+$G_{k'}$ of $G$ to $k'$ by setting
+\[
+\phi_{k'} \ceq \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi).
+\]
+The commutativity of the diagram (QC.3) for $\phi_{k'}$
+follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
+Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
+as taking the action $\varphi$ of $\Weil{k}$ on $\gqcs{L}$
+defined in Section~\ref{sec:category} and restricting it to the subgroup $\Weil{k'}$.
+
+\begin{proposition}\label{prop:basechange}
+With notation above,
+the rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$
+ defines a monoidal functor $\QC(G) \to \QC(G_{k'})$.
+ Moreover, the following diagram commutes:
+\[
+\begin{tikzcd}[column sep=60]
+\QCiso{G} \rar{\nu_{k'/k}} \dar{\TrFrob{G}} & \QCiso{G_{k'}} \dar{\TrFrob{G_{k'}}} \\
+G(k)^*  \rar{\Nm^*} & G(k')^*.
+\end{tikzcd}
+\]
+\end{proposition}
+
+\begin{proof}
+Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
+we may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
+and the value of $\Nm^*(\TrFrob{G}(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
+Applying \ref{QC.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
+\[
+\begin{tikzcd}
+\gqcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gqcs{L}_{F(x)} \otimes \gqcs{L}_{F^2(x)} \otimes \cdots \otimes \gqcs{L}_x
+\dar{\phi_x \otimes (F^*\phi)_x \otimes \cdots \otimes ((F^{n-1})^*\phi)_x} \\
+\gqcs{L}_{\Nm(x)} \rar & \gqcs{L}_x \otimes \gqcs{L}_{F(x)} \otimes \cdots \otimes \gqcs{L}_{F^{n-1}(x)}.
+\end{tikzcd}
+\]
+Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$ and write the image of $v$ under the
+bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
+for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{QC.2}, $v$ maps to
+$v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
+Let $\alpha_i \in \EEx$ represent $((F^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
+the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gqcs{L}_{\Nm(x)}$
+with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gqcs{L}_x$.
+\end{proof}
+
+Finally, let $G'$ be a smooth commutative group scheme over $k'$;
+we explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
+We may decompose the base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
+into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
+\[
+(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
+\]
+Since products and coproducts agree for group schemes we have a natural inclusion of $k'$-schemes
+\[
+G' \hookrightarrow (\Res_{k'/k}G')_{k'}
+\]
+mapping $G'$ into the summand corresponding to $1 \in \Gal(k'/k)$.  Composing $\nu_{k'/k}$
+from Proposition~\ref{prop:basechange} with pullback along this map yields a functor
+\[
+\rho : \QC(\Res_{k'/k}G') \to \QC(G').
+\]
+
+\begin{proposition}
+Let $k'/k$ be a finite extension and let $G'$ be a smooth commutative group scheme over $k'$.
+The following diagram of isomorphisms commutes, where the bottom map is the identity:
+\[
+\begin{tikzcd}
+\QCiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \QCiso{G'} \dar{\TrFrob{G'}}\\
+G'(k')^* \rar & G'(k')^*
+\end{tikzcd}
+\]
+\end{proposition}
+\begin{proof}
+By Proposition~\ref{prop:pullback} the pullback part of the definition of $\rho$ corresponds to the map
+\[
+(\Res_{k'/k}G')(k') \to G'(k')^*
+\]
+induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on
+\[
+(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'
+\]
+is given by permuting coordinates, composition with the norm map yields the identity on $G'(k')$.
+\end{proof}
+
+\todo{Can we improve on this result by proving that $\rho$
+is an equivalence of categories?}
 
@@
     && \Hh^0(\Weil{},\Hh^2(C,\EEx)) \arrow[crossing over,->>]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(B,\EEx)) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(A,\EEx)) \arrow[crossing over]{dd}  &  &  \\
-    & \rQCiso{C} \arrow[>->>]{dr}\arrow{rr} \arrow{dd}%{\TrFrob{C}}
-    && \rQCiso{B} \arrow[>->]{dr} \arrow{rr} \arrow{dd}%{\TrFrob{B}}
-    && \rQCiso{A} \arrow[>->>]{dr} \arrow{dd}%{\TrFrob{A}}
+    & \QCiso{C} \arrow[>->>]{dr}\arrow{rr} \arrow{dd}%{\TrFrob{C}}
+    && \QCiso{B} \arrow[>->]{dr} \arrow{rr} \arrow{dd}%{\TrFrob{B}}
+    && \QCiso{A} \arrow[>->>]{dr} \arrow{dd}%{\TrFrob{A}}
     \arrow{rr}  &   & 0 & \\
@@
 \[
-\Hh^1(E^\bullet_{G^0}) \to \rQCiso{\pi_0(G)} \to \rQCiso{G} \to \rQCiso{G^0} \to 0
+\Hh^1(E^\bullet_{G^0}) \to \QCiso{\pi_0(G)} \to \QCiso{G} \to \QCiso{G^0} \to 0
 \]

### 2014-08-10 dictionary.tex
Changes to \S 1

@@
 
-For any group $A$, we will denote by $A^*$ the dual group $\Hom_\text{grp}(A, \EEx)$.
+For any group $A$, we will write $A^*$ for the dual group $\Hom_\text{grp}(A, \EEx)$.
 
@@
 $\sheafHom(\ - \ ,\EE)$.
-The category of quasicharacter sheaves on $G$ is not abelian, so $\QC(G)$
-is not a tensor category in the sense of \cite{deligne:02a}*{0.1}.
 This rigid monoidal category structure for $\QC(G)$ gives the set $\QCiso{G}$
@@
 
-%Observe that the rule $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ defines a forgetful functor from quasicharacter
-%sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
-%
-
-%A Weil sheaf $(\gqcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gqcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
-%We now briefly review this point of view for later use in Section~\ref{sec:basechange}; see also \cite{deligne:80a}*{Def.~1.1.10}.  If $w \ceq \Frob{}^n$ we write $w_G$ for $\Frob{G}^n$.
-%For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gqcs{L}\to \gqcs{L}$ by $\varphi(w) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi);$
-%these isomorphisms satisfy $\varphi(uv) = \varphi(v) \circ v_G^* \varphi(u)$ for $u,v\in \Weil{}$, and we have $\phi = \varphi(\Frob{})$.
-%If we further define $\varphi_1(w) \ceq (w_G)_*(\varphi(w)^{-1})$ then $\varphi_1(w) : (w_G)_* \gqcs{L}\to \gqcs{L}$ is an isomorphism and $\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for $u,v\in \Weil{}$.
-%Thus the pair $(\gqcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of\cite{deligne:SGA4.5}*{Expos\'e XIII, 1.1}, failing only because $\Weil{}$ is not profinite.
-%As we will see in Corollary~\ref{cor:bounded-and-finite}, our use of $\Weil{}$ rather than $\Gal(\bFq/\Fq)$ allows quasicharacter sheaves to correspond to unbounded characters.
+In this paper we find the group $\QCiso{G}$ [point]
+and also the set $\Hom(\qcs{L},\qcs{L}')$, for all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $G$ [point]; in this was we provide a complete description of the category $\QC(G)$.
+
+\begin{remark}
+The category of quasicharacter sheaves on $G$ is not abelian; $\QC(G)$
+is not a tensor category in the sense of \cite{deligne:02a}*{0.1}.
+\end{remark}
 
@@
 
-As a step toward the proof of Proposition~\ref{prop:functorialG} we show that every
-morphism  $H \to G$ of smooth commutative groups schemes over $\Fq$ induces a monoidal functor from quasicharacter
-sheaves on $G$ to quasicharacters on $H$. This simple but important result will also
-play a role in the proof of many other results in this paper.
+As a step toward understanding quasicharacter sheaves we begin by showing that quasicharacter sheaves admit pull-backs and external products.
+%show that every morphism $H \to G$ of smooth commutative groups schemes over $\Fq$ induces a monoidal functor from quasicharacter sheaves on $G$ to quasicharacters on $H$. 
+These simple but important results will be used in the proofs of many results in this paper.
 
@@
   $\bH^j$. To complete the proof that $\bf^*\gqcs{L}$ satisfies
-  \ref{qc.4}
+  \ref{QC.1}
   simply observe that $\bf^*\gqcs{L}$ has rank~one since
@@
 
-We end this section with a simple result on products of quasicharacter sheaves,
-which is needed to show that the isomorphism above is functorial.
+%We end this section with a simple result on products of quasicharacter sheaves, which is needed to show that the isomorphism above is functorial.
 
@@
 
-We now introduce a tool which will help us understand isomorphism classes of objects in $\QCiso{G}$ and $\lQCiso{G}$.
+We now introduce a tool which will help us understand isomorphism classes of objects in $\QCiso{G}$.
+
+%A Weil sheaf $(\gqcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gqcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
+%We now briefly review this point of view for later use in Section~\ref{sec:basechange}; see also \cite{deligne:80a}*{Def.~1.1.10}.  If $w \ceq \Frob{}^n$ we write $w_G$ for $\Frob{G}^n$.
+%For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gqcs{L}\to \gqcs{L}$ by $\varphi(w) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi);$
+%these isomorphisms satisfy $\varphi(uv) = \varphi(v) \circ v_G^* \varphi(u)$ for $u,v\in \Weil{}$, and we have $\phi = \varphi(\Frob{})$.
+%If we further define $\varphi_1(w) \ceq (w_G)_*(\varphi(w)^{-1})$ then $\varphi_1(w) : (w_G)_* \gqcs{L}\to \gqcs{L}$ is an isomorphism and $\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for $u,v\in \Weil{}$.
+%Thus the pair $(\gqcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of\cite{deligne:SGA4.5}*{Expos\'e XIII, 1.1}, failing only because $\Weil{}$ is not profinite.
+%As we will see in Corollary~\ref{cor:bounded-and-finite}, our use of $\Weil{}$ rather than $\Gal(\bFq/\Fq)$ allows quasicharacter sheaves to correspond to unbounded characters.
+
+%Observe that the rule $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ defines a forgetful functor from quasicharacter
+%sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
+%
 
@@
 \end{proof}
+
+In [point] we will use trace of Frobenius $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ to show that $\QCiso{G}$ is an extension of $G(\Fq)^*$ by $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$.
+
+%\subsection{Morphisms of quasicharacter sheaves}\label{sec:mor}
 
@@
 \begin{enumerate}
- \labitem{(qc.4)}{qc.4} an indexed set $\rho_x : \gqcs{L}_x \to \gqcs{L'}_x$
+ \labitem{(qc.4)}{qc.4} an indexed set $\alpha_x : \gqcs{L}_x \to \gqcs{L'}_x$
   of linear transformations such that
@@
    \begin{tikzcd}[column sep=40]
-    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{}(x)} \rar{\rho_{\Frob{}(x)}} & \gqcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
+    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{}(x)} \rar{\alpha_{\Frob{}(x)}} & \gqcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
     &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-    & \arrow[swap]{d}{\mu} \gqcs{L}_{x+y} \rar{\rho_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
-    \gqcs{L}_x \rar{\rho_x} & \gqcs{L'}_x
-    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\rho_x\otimes\rho_y} & \gqcs{L'}_x \otimes\gqcs{L'}_y
+    & \arrow[swap]{d}{\mu} \gqcs{L}_{x+y} \rar{\alpha_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
+    \gqcs{L}_x \rar{\alpha_x} & \gqcs{L'}_x
+    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\alpha_x\otimes\alpha_y} & \gqcs{L'}_x \otimes\gqcs{L'}_y
    \end{tikzcd}
@@
 
+\subsection{Morphisms}\label{sec:mor-etale}
+
 \todo{Find an appropriate place for this discussion}
 
-If $\rho_0 = 0$ then the second diagram for $y=0$ implies that $\rho_x = 0$ for all $x$.
+If $\alpha_0 = 0$ then the second diagram for $y=0$ implies that $\rho_x = 0$ for all $x$.
 Conversely, if $\rho_0$ is nonzero then the second diagram for $y = -x$ implies that $\rho_x$ is nonzero for all $x$ and thus an isomorphism since $\gqcs{L}_x$ is one dimensional.

### 2014-08-10 dictionary.tex
Changes to \S 2.

@@
   $\qcs{L'} = (\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$ then
-  a morphism $\qcs{L} \to \qcs{L}'$ is a map $\alpha : \gqcs{L} \to \gqcs{L'}$
+  a morphism $\qcs{L} \to \qcs{L}'$ is a map $\rho : \gqcs{L} \to \gqcs{L'}$
   of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
@@
   \begin{tikzcd}[column sep=40]
-  \Frob{G}^* \gqcs{L} \rar{\Frob{G}^* \alpha} \arrow[swap]{d}{\phi} & \Frob{G}^* \gqcs{L'} \dar{\phi'}
-  & & \arrow[swap]{d}{\mu} m^* \gqcs{L} \rar{m^* \alpha} & m^* \gqcs{L'} \dar{\mu'} \\
-  \gqcs{L} \rar{\alpha} & \gqcs{L'}
-  & {} & \LxL \rar{\tight{1}{\alpha\boxtimes \alpha}{1}} & \gqcs{L'} \tight{0}{\boxtimes}{0} \gqcs{L'}
+  \Frob{G}^* \gqcs{L} \rar{\Frob{G}^* \rho} \arrow[swap]{d}{\phi} & \Frob{G}^* \gqcs{L'} \dar{\phi'}
+  & & \arrow[swap]{d}{\mu} m^* \gqcs{L} \rar{m^* \rho} & m^* \gqcs{L'} \dar{\mu'} \\
+  \gqcs{L} \rar{\rho} & \gqcs{L'}
+  & {} & \LxL \rar{\tight{1}{\rho\boxtimes \rho}{1}} & \gqcs{L'} \tight{0}{\boxtimes}{0} \gqcs{L'}
   \end{tikzcd}
@@
 
-\'Etale group schemes form a counterpoint to connected groups,
-since the component group of a smooth commutative group scheme
-is an \'etale group scheme \cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
-However, the function--sheaf dictionary is substantially different in the two cases.
-To see why, we begin by specializing the definition of quasicharacter sheaves to the case
-of etale commutative group schemes,
-using the equivalence $G \mapsto G(\bFq)$
-from the category of \'etale group schemes over $\Fq$ to the category of groups equipped
-with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group.
-Under this equivalence, a quasicharacter sheaf on an etale commutative group scheme $G$ over $\Fq$ is given by the data of:
+%\'Etale group schemes form a counterpoint to connected groups,
+%since the component group of a smooth commutative group scheme
+%is an \'etale group scheme \cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
+%However, the function--sheaf dictionary is substantially different in the two cases.
+%To see why, we begin by specializing the definition of quasicharacter sheaves to the case
+%of etale commutative group schemes,
+%using the equivalence $G \mapsto G(\bFq)$
+%from the category of \'etale group schemes over $\Fq$ to the category of groups equipped
+%with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group.
+
+In this section we find a complete characterization of quasicharacter sheaves on etale commutative group schemes over finite fields.
+
+The equivalence $G \mapsto G(\bFq)$
+from the category of \'etale commutative group schemes over $\Fq$ to the category of commutative groups equipped
+with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group,
+provides the following simple description of quasicharacter sheaves.
+
+A quasicharacter sheaf $\qcs{L}$ on an etale commutative group scheme $G$ over $\Fq$ is:
 \begin{enumerate}
@@
 \end{enumerate}
-Under this equivalence, a morphism $\alpha : \qcs{L} \to \qcs{L'}$ of quasicharacter sheaves on $G$ is given by
+Under this equivalence, a morphism $\rho : \qcs{L} \to \qcs{L'}$ of quasicharacter sheaves on $G$ is given by
 \begin{enumerate}
- \labitem{(qc.4)}{qc.4} an indexed set $\alpha_x : \gqcs{L}_x \to \gqcs{L'}_x$
+ \labitem{(qc.4)}{qc.4} an indexed set $\rho_x : \gqcs{L}_x \to \gqcs{L'}_x$
   of linear transformations such that
@@
 \end{enumerate}
-
-\subsection{Morphisms}\label{sec:mor-etale}
-
-\todo{Find an appropriate place for this discussion}
-
-If $\alpha_0 = 0$ then the second diagram for $y=0$ implies that $\rho_x = 0$ for all $x$.
-Conversely, if $\rho_0$ is nonzero then the second diagram for $y = -x$ implies that $\rho_x$ is nonzero for all $x$ and thus an isomorphism since $\gqcs{L}_x$ is one dimensional.
-Most of this paper focuses on the question of determining the isomorphism classes of objects; a complete understanding of the morphisms in $\QC(G)$ also requires a description of the automorphisms of an arbitrary quasicharacter sheaf $\qcs{L}$.
-
-\begin{proposition}
-The trace map induces an isomorphism of groups
-\[
-\Aut(\qcs{L}) \cong \Hom(G(\bFq)_{\Weil{}}, \EEx).
-\]
-\end{proposition}
-
-\begin{proof}
-The second diagram in \ref{qc.4} shows that the association $x \mapsto \rho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first shows that it factors through $G(\bFq)_{\Weil{}}$.
-Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism then defining $\rho_x$ as multiplication by $\rho(x)$ will satisfy the two diagrams.
-Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the resulting bijection is actually a group ismorphism.
-\end{proof}
 
@@
 
-\subsection{\texorpdfstring{$S$ and $T$}{S and T}}
-
-In this section we describe the relationship between the group homomorphisms $\TrFrob{G}$ and $S_G$.
+\subsection{Objects}%\texorpdfstring{$S$ and $T$}{S and T}}
+
+In this section we find the relationship between the group homomorphisms $\TrFrob{G}$ and $S_G$, and use this to find the group $\QCiso{G}$ when $G$ is an etale commutative group scheme over $\Fq$.
+
 %
@@
 
+\subsection{Morphisms}\label{sec:mor-etale}
+
+Most of this paper focuses on the question of determining the isomorphism classes of objects; a complete understanding of the morphisms in $\QC(G)$ also requires a description of the automorphisms of an arbitrary quasicharacter sheaf $\qcs{L}$.
+
+\begin{proposition}
+If $\qcs{L}$ and $\qcs{L}'$ are quasicharacter sheaves on $G$ then
+every $\alpha\in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism. Moreover, the trace map induces an isomorphism of groups
+\[
+\Aut(\qcs{L}) \to \Hom(G(\bFq)_{\Weil{}}, \EEx).
+\]
+\end{proposition}
+
+\begin{proof}
+Suppose $\rho \in \Hom(\qcs{L},\qcs{L}')$.
+If $\rho_0 = 0$ then the second diagram for $y=0$ implies that $\rho_x = 0$ for all $x\in G$.
+Conversely, if $\rho_0$ is nonzero then the second diagram for $y = -x$ implies that $\rho_x$ is nonzero for all $x$ and thus an isomorphism since the stalk of quasicharacter sheaves are one dimensional.
+%
+The second diagram in \ref{qc.4} shows that the association $x \mapsto \rho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first shows that it factors through $G(\bFq)_{\Weil{}}$.
+Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism then defining $\rho_x$ as multiplication by $\rho(x)$ will satisfy the two diagrams.
+Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the resulting bijection is actually a group ismorphism.
+\end{proof}
+
 \section{The main result}\label{sec:main}
+
+Having found $\QCiso{G}$ and $\Hom(\qcs{L},\qcs{L}')$ when $G$ is an etale commutative group scheme over $\Fq$, we now wish to find these groups for all commutative group scheme over $\Fq$.
+
+\subsection{The case of connected commutative algebraic groups over finite fields}\label{sec:connected}.
 

### 2014-08-11 dictionary.tex
Working on \S 3.
I’m in the middle of working on \S 3, but running out of steam so I’ll
have to put it down for now. The current version is pretty butchered.
Sorry. I’ve cut much of material on finite quasicharacter sheaves and
pasted in into the file below \end{document} for later use.

@@
 % AMS packages
-\usepackage{amsmath, amsthm, amssymb, todonotes}% showkeys}
+\usepackage{amsmath, amsthm, amssymb, todonotes}%, showkeys}
 \usepackage[alphabetic]{amsrefs}
@@
 In this paper we find the group $\QCiso{G}$ [point]
-and also the set $\Hom(\qcs{L},\qcs{L}')$, for all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $G$ [point]; in this was we provide a complete description of the category $\QC(G)$.
+and also the set $\Hom(\qcs{L},\qcs{L}')$, for all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $G$ [point]; in this way we provide a complete description of the category $\QC(G)$.
 
@@
 provides the following simple description of quasicharacter sheaves.
-
+%
 A quasicharacter sheaf $\qcs{L}$ on an etale commutative group scheme $G$ over $\Fq$ is:
@@
     &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-    & \arrow[swap]{d}{\mu} \gqcs{L}_{x+y} \rar{\rho_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
+    & \arrow[swap]{d}{\mu_{x,y}} \gqcs{L}_{x+y} \rar{\rho_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x,y}} \\
     \gqcs{L}_x \rar{\rho_x} & \gqcs{L'}_x
@@
 
-\subsection{Objects}%\texorpdfstring{$S$ and $T$}{S and T}}
+\subsection{Objects, when $G$ is etale}%\texorpdfstring{$S$ and $T$}{S and T}}
 
@@
 
-\begin{corollary}
+\begin{proposition}\label{prop:sur_etale}
 If $G$ is \'etale then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective.
-\end{corollary}
+\end{proposition}
 \begin{proof}
@@
 \begin{proof}
-This result follows easily from Proposition \ref{prop:ses_desc}.
+This result follows easily from Propositions~\ref{prop:ses_desc} and \ref{prop:sur_etale}.
 \end{proof}
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:mor_etale}
+Let $G$ be an etale commutative group scheme over $\Fq$.
 If $\qcs{L}$ and $\qcs{L}'$ are quasicharacter sheaves on $G$ then
@@
 Suppose $\rho \in \Hom(\qcs{L},\qcs{L}')$.
-If $\rho_0 = 0$ then the second diagram for $y=0$ implies that $\rho_x = 0$ for all $x\in G$.
-Conversely, if $\rho_0$ is nonzero then the second diagram for $y = -x$ implies that $\rho_x$ is nonzero for all $x$ and thus an isomorphism since the stalk of quasicharacter sheaves are one dimensional.
+If $\rho_0 = 0$ then the second diagram in \ref{qc.4} for $y=0$ implies that $\rho_x = 0$ for all $x\in G$, in which case $\rho$ is trivial.
+On the other hand, if $\rho_0$ is nonzero then the second diagram in \ref{qc.4} for $y = -x$ implies that $\rho_x$ is nonzero for all $x$ and thus an isomorphism since the stalk of quasicharacter sheaves are one dimensional; in this case $\rho$ is an isomorphism.
+
+Now suppose $\rho \in \Aut(\qcs{L})$.
+The second diagram in \ref{qc.4} shows that the association $x \mapsto \rho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{qc.4} shows that it factors through $G(\bFq)_{\Weil{}}$.
+Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism then defining $\rho_x$ as multiplication by $\rho(x)$ will satisfy the two diagrams.
+Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the resulting bijection is actually a group isomorphism.
+\end{proof}
+
+Note that Proposition~\ref{prop:mor_etale} tells us that if $G$ is an etale commutative group scheme over $\Fq$ then every hom-set is either trivial or $\left(G(\bFq)_{\Weil{}}\right)^*$, non-canonically.
+
+\section{The main result}\label{sec:main}
+
+Having found $\QCiso{G}$ and $\Hom(\qcs{L},\qcs{L}')$ when $G$ is an etale commutative group scheme over $\Fq$, we now wish to find these for all commutative group scheme over $\Fq$.
+The next section introduces a concept that will be helpful in that regard.
+
+\subsection{Bounded quasicharacter sheaves}\label{sec:bounded}
+
+Let $G$ be a smooth commutative group scheme over $\Fq$.
+In this section we consider a class of quasicharacter sheaves on $G$ obtained by
+replacing the Weil sheaf $(\gqcs{L}, \phi)$ on $\bG$ in the definition of a quasicharacter
+sheaf with an $\ell$-adic local system on $G$ itself.
+
+\begin{definition}
+Let $\bQC(G)$ be the category of pairs $(\qcs{L}_0,\mu_0)$
+where $\qcs{L}_0$ an $\ell$-adic local system on $G$ of rank~one,
+equipped with an isomorphism $\mu_0 : m^* \qcs{L}_0 \to \qcs{L}_0 \boxtimes \qcs{L}_0$
+satisfying the analogue of \ref{QC.1} on $G$;
+morphisms in $\bQC(G)$ are defined as in the second part of
+\ref{QC.3}.
+This is the category of \emph{bounded quasicharacter sheaves} on $G$.
+\end{definition}
+
+The category of bounded quasicharacter sheaves is a rigid monoidal category in the obvious way.
+
+\begin{proposition}\label{prop:BG}
+Extension of scalars defines a full and faithful functor $B_G : \bQC(G) \to \QC(G)$.
+\end{proposition}
+
+\begin{proof}
+ Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
+ Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$.
+ Then $\qcs{L}_0$ is an $\ell$-adic constructible sheaf on $G$ and
+ $b_G^* \qcs{L}_0$ comes equipped with an isomorphism
+ $\phi : \Frob{G}^* b_G^*\qcs{L}_0 \to b_G^* \qcs{L}_0$.
+ Moreover, the functor $\qcs{L}_0 \mapsto (b_G^* \qcs{L}_0,\phi)$
+ from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
+ is full and faithful \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}}.
+ This functor preserves local constancy, so takes local systems to local systems.
+ Set $\mu \ceq b_{G\times G}^*\mu_0$; clearly, this satisfies \ref{QC.2}
+ with $b_G^*\qcs{L}_0$ playing the role of $\gqcs{L}$.
+ Moreover, $\phi$ is compatible with $\mu$ in the sense of \ref{QC.3}.
+ This construction defines the functor $B_G : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,b_{G\times G}^*\mu_0, \phi)$
+ and also shows that it is full and faithful.
+\end{proof}
+
+We will identify $\bQC(G)$ with its image under $B_G$
+and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ is \emph{bounded}
+if it is isomorphic to some $B_G(\qcs{L}_0, \mu_0)$.
+We will see in Corollary~\ref{cor:bounded-and-finite} that bounded quasicharacter sheaves are exactly quasicharacter sheaves with bounded Trace of Frobenius.\todo{Check this, later.}
+
+In general, $\bQC(G)$ is an essentially
+proper subcategory of $\QC(G)$. 
+However, if $G$ is connected, the categories are equivalent, as we now show.
+
+\begin{proposition}\label{prop:bounded_connected}
+If $G$ is a connected commutative algebraic group over $\Fq$ then
+$B_G : \bQC(G) \to \QC(G)$ is an equivalence of categories.
+\end{proposition}
+
+\begin{proof}
+Choose any $\Fq$-rational point $g$ on $G$ and let $\bg$ be the geometric point on $G$ lying above $g$.
+Recall that the \emph{Weil group} of $G$, which we will denote by $\W(G,\bg)$, is a subgroup of the \'etale
+fundamental group defined by the following diagram:
+\[
+ \begin{tikzcd}
+ 1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \W(G,\bg) \rar \dar[hook] & \Weil{} \rar \dar[hook] & 1 \\
+ 1 \rar &  \pi_1(\bG, \bg) \rar & \pi_1(G,\bg) \rar & \Gal(\bFq/\Fq) \rar & 1.
+ \end{tikzcd}
+\]
+The $\Fq$-rational point $g$ under the geometric point $\bg$ determines a splitting
+$\Weil{}\to \W(G,\bg)$ of $\W(G,\bg)\to \Weil{}$.
 %
-The second diagram in \ref{qc.4} shows that the association $x \mapsto \rho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first shows that it factors through $G(\bFq)_{\Weil{}}$.
-Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism then defining $\rho_x$ as multiplication by $\rho(x)$ will satisfy the two diagrams.
-Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the resulting bijection is actually a group ismorphism.
-\end{proof}
-
-\section{The main result}\label{sec:main}
-
-Having found $\QCiso{G}$ and $\Hom(\qcs{L},\qcs{L}')$ when $G$ is an etale commutative group scheme over $\Fq$, we now wish to find these groups for all commutative group scheme over $\Fq$.
-
-\subsection{The case of connected commutative algebraic groups over finite fields}\label{sec:connected}.
+  Since $G$ is connected, the geometric point $\bg$ determines
+  an equivalence between the category of $\ell$-adic Weil local systems on $G$ and
+  $\ell$-adic representations of $\W(G,\bg)$ \cite{deligne:80a}*{1.1.12}.
+
+  Now let $(\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$
+  and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$.
+  Composing with the splitting $\Weil{} \to \W(G,\bg)$ yields an $\ell$-adic character
+  $\rho_g : \Weil{} \to \EEx$, which is the same as the Trace of Frobenius defined in Section~\ref{sec:Frob}, for every $\Fq$ rational point $g$ on $G$:
+  $
+  \rho_g(\Frob{}) =  \trFrob{\qcs{L}}(g).
+  $
+%
+  On the other hand, we have already seen that $\trFrob{\qcs{L}} : G(\Fq) \to \EEx$
+  is a group homomorphism. Since $G$ is an algebraic group over $\Fq$, it is a
+  variety over $\Fq$ and thus $G(\Fq)$ is finite.
+  Therefore $\trFrob{\qcs{L}}(g) = \rho_g(\Frob{})$ is a root of unity
+  for every $g\in G(\Fq)$.  Since $\Weil{}$ is generated by
+  $\Frob{}$ and $\rho_g : \Weil{} \to \EEx$ is
+  a character, it follows that the image of $\rho_g$ is a finite group.
+  Thus, $\rho_g$ extends to an $\ell$-adic character of $\Gal(\bFq/\Fq)$,
+  which we will also denote $\rho_g$.
+%
+  We may now lift the $\ell$-adic character $\rho_g : \Gal(\bFq/\Fq) \to \EEx$
+  to an $\ell$-adic character $\pi_1(G,\bg) \to \EEx$ using the canonical topological group homomorphism
+  $\pi_1(G,\bg) \to \Gal(\bFq/\Fq)$. 
+ % 
+  The $\Fq$ rational point $g$ also
+  determines an equivalence between the category of $\ell$-adic
+  representations of $\pi_1(G,\bg)$ and $\ell$-adic local systems on $G$. Let
+  $\qcs{L}_0$ be a local system on $G$ in the isomorphism class
+  determined by this $\ell$-adic character of $\pi_1(G,\bg)$.
+  Then $b_G^*\qcs{L}_0 \iso \gqcs{L}$.
+
+  Since $b_G^*$ is full and faithful
+  \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}},
+  $
+  b_{G\times G}^* : \Hom(m^*\qcs{L}_0,\qcs{L}_0\boxtimes\qcs{L}_0) \to \Hom({\bar m}^*\gqcs{L},\gqcs{L}\boxtimes\gqcs{L})
+  $
+  is a bijection
+  (hom taken in the categories on constructible $\ell$-adic sheaves on
+  $G\times G$ and ${\bar G}\times {\bar G}$ respectively,
+  in which $\ell$-adic local systems sit as full subcategories).
+  Let $\mu_0 : m^*\qcs{L}_0 \to \qcs{L}_0\boxtimes\qcs{L}_0$ be the isomorphism matching
+  $\mu : {\bar m}^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$,
+  the latter appearing in the definition of $\qcs{L}$.
+  Then, as in Section~\ref{sec:bounded}, $(\qcs{L}_0,\mu_0)$ is an object in $\bQC(G)$
+  and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{L}_0,b_{G\times G}^*\mu_0)$ in $\QC(G)$.
+  Thus, the full and faithful functor $B_G : \bQC(G) \to \QC(G)$ from Section~\ref{sec:bounded}
+  is also essentially surjective, hence an equivalence.
+\end{proof}
+
+\subsection{Objects, when $G$ is connected and of finite type}\label{sec:connected}
+
+\begin{proposition}\label{prop:obj_connected}
+ If $G$ is a connected, commutative algebraic group over $\Fq$ then
+ \[
+  \TrFrob{G} : \QCiso{G} \to G(\Fq)^*
+ \]
+ is an isomorphism of groups.
+\end{proposition}
+
+\begin{proof}
+At its heart, this is Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields, as we now briefly recall from \citelist{\cite{deligne:SGA4.5}*{Sommes trig.}, \cite{laumon:87a}*{1.1.3}}.
+
+We begin by showing that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective.
+Let $\chi : G(\Fq) \to \EEx$ be a character.
+Let $\Lang : G \to G$ be the Lang isogeny for $G$.
+Set $\qcs{L}_0 = ( \Lang_* \EE)_{\chi^{-1}}$, the $\chi^{-1}$-isotypic component of the push-forward of the constant sheaf on $G$ along the Lang isogeny.
+Let $\gqcs{L}$ be the local system on $\bG$ obtained by pull-back along $\bG \to G$.
+Then $\gqcs{L}$ comes equipped with an isomorphism $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$.
+As explained in \cite{laumon:87a}*{1.1.3}, the trace of the Weil sheaf $(\gqcs{L},\phi)$ is $\chi$.
+The sheaf $\qcs{L}_0$ also comes equipped with an isomorphism 
+$\mu_0 : m^*\qcs{L}_0 \to \qcs{L}_0\boxtimes \qcs{L}_0$ 
+\cite{laumon:87a}*{1.1.3.2},
+which satisfies the analogue of \ref{QC.2} over $G$.
+Writing $\mu : \bm^* \gqcs{L}  \to \gqcs{L} \boxtimes \gqcs{L}$ for the isomorphism obtained by base change, it follows immediately that $\mu$ satisfies conditions \ref{QC.2} and \ref{QC.3}.
+Thus, $\qcs{L}\ceq (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$ with $\trFrob{\qcs{L}} = \chi$.
+It follows that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective.
+
+In order to show that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is injective we need to recall some facts about Weil sheaves.
+%
+
+Now, let $\qcs{L}$ and $\qcs{L}'$ be quasicharacter sheaves on $G$ with $\trFrob{\qcs{L}} = \trFrob{\qcs{L}'}$.\todo{The rest of the proof is under construction.}
+\end{proof}
 
@@
 In this section use that perspective to find a perfect dictionary between flabby quasicharacter sheaves on $G$ and characters of $G(\Fq)$.
+
+\subsection{The component group sequence} \label{sec:restriction}
+
+Consider the short exact sequence
+defining the component group scheme for $G$:
+\begin{equation}\label{eq:pi0}
+\begin{tikzcd}
+0 \rar & G^0 \arrow{r}{\iota_0} & G \arrow{r}{\pi_0} & \pi_0(G) \rar & 0.
+\end{tikzcd}
+\end{equation}
+Since $\pi_0(G)$ is a etale commutative group scheme, and this smooth,
+Proposition~\ref{prop:pullback} implies that \eqref{eq:pi0} defines the sequence of functors
+\begin{equation}\label{eq:pi1}
+\begin{tikzcd}
+\QC(0) \rar & \QC(\pi_0(G)) \arrow{r}{\pi_0^*} & \QC(G) \arrow{r}{\iota_0^*} & \QC(G^0) \rar & \QC(0)
+\end{tikzcd}
+\end{equation}
+and therefore, after passing to isomorphism classes, the sequence of abelian groups
+\begin{equation}\label{eq:pi2}
+\begin{tikzcd}
+0 \rar &
+\QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
+\end{tikzcd}
+\end{equation}
+ Note that we found the groups $\QCiso{G^0}$
+and $\QCiso{\pi_0(G)}$
+in Sections~\ref{sec:connected} and \ref{sec:etale}, respectively.
+In this section we show that \eqref{eq:pi2} is right exact.
+
+Recall from Section~\ref{sec:finite} that
+a morphism $f : H\to G$ of group $\Fq$-schemes is a discrete isogeny
+if it is a finite, surjective \'etale morphism and
+the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f$ is trivial.
+
+\begin{lemma}\label{lemma:ext}
+Every discrete isogeny onto $G^0$ extends to a discrete
+isogeny onto $G$ inducing an isomorphism on component groups.
+\end{lemma}
+
+\begin{proof}
+Let $\pi: B \to G^0$ be a discrete isogeny and set $A \ceq \ker \pi$.
+  We will find a discrete isogeny $f: H\to G$
+  such that that $H^0 = B$, $f^0 =\pi$ and
+  $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism of component
+  groups.  Namely, we will fit $\pi$ into the following diagram,
+  \begin{equation}\label{extension-diagram}
+  \begin{tikzcd}
+  A \arrow[equal]{r} \dar & A \dar \\
+  B \rar \dar[swap]{\pi} & H \rar \dar[swap]{f} & \pi_0(H) \arrow{d}[below,rotate=90]{\sim}[swap]{\pi_0(f)} \\
+  G^0 \rar & G \rar & \pi_0(G),
+  \end{tikzcd}
+  \end{equation}
+  where all rows and columns are exact and all maps are defined over
+  $\Fq$.  We will do so by passing back and forth between group
+  schemes over $\Fq$ and their $\bFq$-points.
+
+  Extensions of $G^0(\bFq)$ by $A(\bFq)$, such as $B(\bFq)$,
+  correspond to classes in $\Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq))$.
+  Similarly, extensions of $G(\bFq)$ by $A(\bFq)$ correspond to
+  classes in $\Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq))$.  The map
+  $G^0(\bFq) \to G(\bFq)$ induces the map
+  \[
+  \Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq))
+  \]
+  fitting into the long exact sequence derived from applying
+  the functor $\Hom(\mbox{---}, A(\bFq))$ to $G^0(\bFq) \to G(\bFq) \to \pi_0(G)(\bFq)$:
+  \[
+  \Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[\Weil{}]}(\pi_0(G)(\bFq), A(\bFq)).
+  \]
+  Since $\Weil{} \cong \ZZ$ has cohomological dimension $1$ \cite{brown:CohomologyGrps}*{Ex. 4.3},
+  $\Ext^2_{\ZZ[\Weil{}]}(\pi_0(G)(\bFq), A(\bFq))$ vanishes \cite{cartan-eilenberg:HomologicalAlgebra}*{Thm. 2.6}.
+
+  We therefore have the existence of diagram \eqref{extension-diagram}
+  at the level of $\bFq$-points.  This expresses $H(\bFq)$ as a
+  disjoint union of translates of $B(\bFq)$; by transport of structure
+  we may take $H$ to be a group scheme over $\bFq$.  Similarly, the
+  restriction of $f$ to each component of $H$ is a morphism of
+  schemes, and thus $f$ is as well.  Finally, the whole diagram
+  descends to a diagram of $\Fq$-schemes since the $\bFq$-points of
+  the objects come equipped with continuous $\Gamma$-actions, and the
+  morphisms are $\Gamma$-equivariant.
+\end{proof}
+
+In order to use the results of Section~\ref{sec:connected}, we need to know that
+identity component of $G$ is actually an algebraic group.
+
+\begin{lemma} \label{lem:G0alg-grp}
+If $G$ is a commutative smooth group scheme over $\Fq$ then $G^0$ is a connected algebraic group.
+\end{lemma}
+\begin{proof}
+ Since $G$ is a smooth group scheme over $\Fq$, its
+ identity component $G^0$ of $G$ is a connected smooth,
+ group scheme of finite type over $\Fq$, reduced over some finite extension of $\Fq$
+ \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}.
+ Since $\Fq$ is a finite field and hence perfect, $G^0$ is actually reduced over $\Fq$
+ \cite{EGAIV2}*{Prop 6.4.1}.  Since every group scheme over a field is separated
+ \cite{vdGeer-Moonen:AbelianVarieties}*{3.12},
+ it follows that $G^0$ is a connected algebraic group.
+\end{proof}
+
+\begin{proposition}\label{prop:restriction}
+For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf
+$\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$.
+As a consequence, the restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
+\end{proposition}
+
+\begin{proof}
+  By Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}, every
+  quasicharacter sheaf on $G^0$ is isomorphic to a
+  finite quasicharacter sheaf on $G^0$,
+  so to prove the proposition it suffices to show that every
+  finite quasicharacter sheaf on $G^0$ extends to a finite quasicharacter sheaf on $G$.
+
+ Let $(\pi,\psi)$ be a finite quasicharacter sheaf on $G^0$.
+ By Lemma~\ref{lemma:ext}, there is an extension of the
+ discrete isogeny $\pi : B \to G^0$ to a discrete isogeny $f : H \to G$
+ such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
+ Then $(f,\psi)$ is a finite quasicharacter sheaf on $G$ and
+ $(f,\psi)\vert_{G^0} \iso (\pi,\psi)$.
+\end{proof}
+
+\begin{proposition}\label{prop:middleexact}
+ The sequence
+ \[
+  \begin{tikzcd}
+  0 \rar & \QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
+  \end{tikzcd}
+ \]
+ is exact.
+\end{proposition}
+
+\begin{proof}
+The sequence is exact at $\QCiso{G^0}$ by Proposition~\ref{prop:restriction},
+so here we show that it is also exact at $\QCiso{G}$.
+First note that $\iota_0^* \circ \pi_0^*$ is trivial by Proposition~\ref{prop:pullback}.
+So it suffices to show that if $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$
+with $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$ then $\qcs{L}$ is in the essential image of $\pi_0^*$.
+
+For each $x\in \pi_0(\bG)$, set $\bG^x \ceq \pi_0^{-1}(x)$.
+Let $g, g'$ be geometric points in the same
+geometric connected component $\bG^x$.
+Set $a = g^{-1}g'$ and note that $a$ is a geometric point in $\bG^0$.
+Let $\mu_{g,a} : \gqcs{L}_{ga} \to \gqcs{L}_g \otimes \gqcs{L}_a$
+be the isomorphism of vector spaces obtained by restriction of
+$\mu : m^*\gqcs{L} \to \gqcs{L} \boxtimes \gqcs{L}$ to the
+geometric point $(g,a)$ on $\bG^x \times \bG^0$.
+Since $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$,
+the stalk of $\gqcs{L}$ at $a$ is $\EE$.
+In this way the pair of geometric points $g, g' \in \bG^x$
+determines an isomorphism $\varphi_{g,g'} \ceq \mu_{g,a}^{-1}$
+from $\gqcs{L}_{g}$ to $\gqcs{L}_{g'}$.
+
+The isomorphisms $\varphi_{g,g'}: \gqcs{L}_{g} \to \gqcs{L}_{g'}$ are canonical
+in the following sense: if $g,g'\in \bG^x$ and $h,h'\in \bG^y$
+then it follows from \ref{QC.2} and \ref{QC.3}
+that
+ \begin{equation}\label{eq:qc}
+  \begin{tikzcd}[column sep=55]
+   \gqcs{L}_{gh} \arrow{r}{\varphi_{gh,g'h'}} \arrow[swap]{d}{\mu_{g,h}}
+  & \gqcs{L}_{g'h'} \arrow{d}{\mu_{g',h'}}
+  &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
+  &  \gqcs{L}_{\Frob{}(g)} \arrow{r}{\varphi_{\Frob{}(g),\Frob{}(g')}} \arrow[swap]{d}{\phi_{g}} & \gqcs{L}_{\Frob{}(g')} \arrow{d}{\phi_{g'}} \\
+  \gqcs{L}_{g} \otimes \gqcs{L}_{h} \arrow{r}{\varphi_{g,g'}\otimes \varphi_{h,h'}}
+  & \gqcs{L}_{g'} \otimes \gqcs{L}_{h'}
+  & {}
+  & \gqcs{L}_{g} \arrow{r}{\varphi_{g,g'}} & \gqcs{L}_{g'}
+  \end{tikzcd}
+ \end{equation}
+both commute.
+
+For each $x\in \pi_0(\bG)$, pick $g(x)\in \bG^x$
+and set $\gqcs{E}_x \ceq \gqcs{L}_{g(x)}$.
+Let $\phi_x : \gqcs{E}_{\Frob{}(x)} \to \gqcs{E}_x$
+be the isomorphism of $\EE$-vector spaces obtained by composing
+$\varphi_{g(\Frob{}(x)),\Frob{}(g(x))} : \gqcs{L}_{g(\Frob{}(x))} \to \gqcs{L}_{\Frob{}(g(x))}$
+with $\phi_{g(x)} : \gqcs{L}_{\Frob{}(g(x))} \to \gqcs{L}_{g(x)}$.
+For each pair $x,y\in \pi_0(\bG)$
+let $\mu_{x,y} : \gqcs{E}_{x+y}\to \gqcs{E}_x\otimes \gqcs{E}_y$
+be the isomorphism of $\EE$-vector spaces obtained by composing
+$\varphi_{g(x+y),g(x)g(y)} : \gqcs{L}_{g(x+y)} \to \gqcs{L}_{g(x)g(y)}$
+with $\mu_{g(x),g(y)} : \gqcs{L}_{g(x)g(y)} \to \gqcs{L}_{g(x)}\otimes \gqcs{L}_{g(y)}$.
+Using \eqref{eq:qc}, it follows that \ref{qc.1}, \ref{qc.2} and \ref{qc.3} are satisfied for
+$\qcs{E} \ceq (\gqcs{E}_x, \mu_{x,y}, \phi_x)$, thus defining a quasicharacter sheaf on $\pi_0(G)$.
+
+The pullback $\pi_0^*(\qcs{E})$ of $\qcs{E}$ along $\pi_0 : G \to \pi_0(G)$ is constant
+on geometric connected components, with stalks given by
+$(\pi_0^* \qcs{E})_g = \qcs{E}_{x}$ for all $g\in \bG^x$.  Thus both $\pi_0^*\qcs{E}$ and $\qcs{L}$
+are constant on geometric connected components of $G$.
+The choices above define isomorphisms
+$\gqcs{L}\vert_{\bG^x} \to  (\gqcs{E}_{x})_{\bG^x}$ for each $x\in \pi_0(\bG)$.
+The resulting isomorphism $\gqcs{L} \to \pi_0^* \gqcs{E}$ satisfies \ref{QC.4},
+thus defining an isomorphism $\qcs{L} \to \pi_0^* \qcs{E}$ in $\QC(G)$.
+\end{proof}
+
+\subsection{The function--sheaf dictionary for smooth, commutative group schemes}
+\label{sec:snake}
+
+We saw in Proposition~\ref{prop:functorialG} that Trace of Frobenius
+$\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
+In this section we improve that result.
+
+\begin{theorem}\label{thm:snake}
+  If $G$ is a smooth, commutative group scheme over $\Fq$ then
+  \[
+  \TrFrob{G} : \QCiso{G} \to G(\Fq)^*
+  \]
+is surjective with kernel isomorphic to $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$.
+\end{theorem}
+
+\begin{proof}
+  Recall the short exact sequence \eqref{eq:pi0}
+  defining the component group scheme for $G$:
+  \[
+  \begin{tikzcd}
+    1 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
+  \end{tikzcd}
+  \]
+  Let
+  \[
+  \begin{tikzcd}[row sep=20]
+    0 \rar & \ker \TrFrob{\pi_0(G)} \arrow[dashed]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dashed]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
+    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
+    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
+    0 \rar & \pi_0(G)(\Fq)^* \rar \dar
+    & \arrow{d} G(\Fq)^* \rar & G^0(\Fq)^* \rar \dar & 0\\
+    & \coker \TrFrob{\pi_0(G)} =0 \arrow[dashed]{r} & \coker \TrFrob{G} \arrow[dashed]{r} &  \coker \TrFrob{G^0} =0 &
+  \end{tikzcd}
+  \]
+  be the commutative diagram of abelian groups obtained by applying
+  Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.
+
+  The sequence of abelian groups
+  \begin{equation}\label{eq:pi0k}
+  \begin{tikzcd}
+    1 \rar & G^0(\Fq) \rar & G(\Fq) \rar & \pi_0(G)(\Fq) \rar & 0,
+  \end{tikzcd}
+  \end{equation}
+  is exact since $\Hh^1(\Fq,G^0) =0$ by Lemma~\ref{lem:G0alg-grp} and Lang's theorem on connected algebraic groups over finite fields \cite{lang:56a}.
+  Since $\EEx$ is divisible, $\Hom_\text{Ab}(\ - \ ,\EEx)$ is exact and thus the dual sequence of
+  character groups is also exact.
+
+  The upper row is exact by Proposition~\ref{prop:middleexact}.
+  Now Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}
+  imply that $\ker \TrFrob{G^0} =0$ and $\coker \TrFrob{G^0}=0$,
+  while Proposition~\ref{prop:etale-iso} gives $\ker \TrFrob{\pi_0(G)} \iso \Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$
+  and $\coker \TrFrob{\pi_0(G)}=0$.
+%
+It follows from the snake lemma that $\coker \TrFrob{G} =0$
+and $\ker \TrFrob{\pi_0(G)} \to \ker \TrFrob{G}$ is an isomorphism.
+
+%We now turn our attention $\lTrFrob{G}: \lQCiso{G}  \to G(\Fq)^*$ is an isomorphism.
+%First, note that $\lTrFrob{G}$ is surjective because $\TrFrob{G}$ is surjective.
+%We will now show that the kernel of $\lTrFrob{G}$ is trivial.
+
+%First, suppose $G$ is etale.
+%Let $(\gqcs{E},\phi')$ be a quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{E},\phi')}=1$.
+%Let $\qcs{E} = (\gqcs{E},\mu,\phi')$ be a quasicharacter sheaf.
+%By Proposition~\ref{prop:etale-iso}, $S_G(\qcs{E}) = [\alpha\oplus 0]$ for some $\alpha \in Z^0(\Weil{},Z^2({\bar G},\EEx))$
+%corresponding to a choice $\{ v_x \in \gqcs{E}_x^\times \tq x\in {\bar C}\}$.
+%Let $a\in Z^2({\bar G},\EEx)$ be the multiplicative version of $\alpha$
+%and let $\mu'$ be the indexed set of isomorphisms $\mu'_{x,y} : \EE \to \EE\otimes \EE$ defined by $1 \mapsto a(x,y) 1 \otimes 1$.
+%Then $(\EE,\mu', 1)$ is a quasicharacter sheaf the isomorphisms $\gqcs{E}_x \to \EE$ defined by $v_x \mapsto 1$ gives an isomorphism $(\gqcs{E},\mu,\phi')\to ((\EE)_{\bar C},\mu', 1)$ in $\QC(G)$.
+%It follows that $(\gqcs{E},\phi')\iso ((\EE)_{\bar G},1)$ in $\lQC(G)$, so $\lTrFrob{G}$ is injective.
+%This completes the proof of Theorem~\ref{thm:snake} in the case that $G$ is etale.
+
+%Now let $G$ be arbitrary
+%and let $(\gqcs{L},\phi)$ be a flabby quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{L},\phi)}=1$.
+%Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf.
+%We saw above that $\ker \TrFrob{\pi_0(G)}\to \TrFrob{G}$ is surjective in this case,
+%so $\qcs{L} = \pi_0^*\qcs{E}$ for some $\qcs{E}\in \QC(\pi_0(G))$.
+%Since $\trFrob{\qcs{L}}(g) = \trFrob{\qcs{E}}(\pi_0(g))$ and since $\pi_0 : G(\Fq) \to \pi_0(G)(\Fq)$ is surjective, $\trFrob{\qcs{E}}=1$.
+%But now $\qcs{E} \iso ((\EE)_{\pi_0({\bar G})},\mu', 1)$ by the paragraph above.
+%So $\qcs{L} = \pi_0^*\qcs{E} \iso \pi_0^*((\EE)_{\pi_0({\bar G})},\mu', 1) = ((\EE)_{\bar G},\pi_0^*\mu', \pi_0^*1)$ in $\QC(G)$.
+%It follows that $(\gqcs{L},\phi) \iso ((\EE)_{\bar G},1)$ in $\lQC(G)$.
+%This completes the proof of Theorem~\ref{thm:snake}.
+\end{proof}
+
+%\begin{corollary}\label{cor:exact}
+%  If $G$ is a smooth, commutative group scheme over
+%  $\Fq$ then pullback yields an exact sequence
+%\[
+%0 \to \lQCiso{\pi_0(G)} \to \lQCiso{G} \to \lQCiso{G^0} \to 0
+%\]
+%of abelian groups.
+%\end{corollary}
+
+%\begin{proof}
+%Argue as in the first paragraph in the proof of Theorem~\ref{thm:snake},
+%using the category $\lQC(G)$ in place of $\QC(G)$.
+%\end{proof}
+
+\subsection{Morphisms, in the general case}
+
+\section{Application to \texorpdfstring{$p$}{p}-adic tori}
+
+\subsection{Finite implies Bounded}
+
+In this section we show that $\fQC(G)$ is a full subcategory of $\bQC(G)$.
+To prepare for that result, we need the next two lemmas.
+
+\begin{lemma}\label{lemma:finite-pullback}
+Let $g : J \to G$ be a morphism of smooth groups schemes over $\Fq$.
+Let $f_g : H\times_G J\to J$
+be the pullback of $f$ along $g$ and define $\psi_g : \ker f_g \to \Aut(V)$ as in the diagram below:
+\[
+\begin{tikzcd}
+V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
+  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker f_g}} \ker f_g \arrow[hook]{r}
+  & \arrow[swap]{u}{g_f} H\times_G J \arrow{r}{f_g} & \arrow{u}{g} J.
+\end{tikzcd}
+\]
+Then $(f,\psi) \mapsto (f_g,\psi_g)$
+defines a monomial functor $g^* : C(G)[W^{-1}] \to C(J)[W^{-1}]$.
+\end{lemma}
+
+\begin{proof}
+The key point is that pullback along $g$ takes discrete isogenies to discrete isogenies,
+and maps over $G$ to maps over $J$, as pictured below.
+\[
+\begin{tikzcd}[row sep={{{{40,between origins}}}},column sep={{{{50,between origins}}}}]
+%\ V \arrow{dd}{T} &
+\Aut(V) && \arrow[swap]{ll}{\psi} \ker f \arrow[hook]{rr} \arrow[leftarrow]{dd} && H \arrow{rr}{f} \arrow[leftarrow]{dd} && \arrow[equal]{dd} G\\
+% &
+& \arrow{ul} \ker f\times_G J \arrow{ur} \arrow[hook, crossing over]{rr} && H\times_G J \arrow{ur} \arrow[crossing over]{rr} && J \arrow[swap]{ur}{g} & \\
+%V' &
+ \Aut(V') && \arrow[swap,pos=0.25]{ll}{\psi'} \ker f'  \arrow[hook]{rr}
+&& H' \arrow[pos=0.25]{rr}{f'} && G\\
+% &
+ & \arrow{ul} \ker f'\times_G J \arrow[crossing over]{uu} \arrow{ur} \arrow[hook]{rr}
+ && \arrow[crossing over]{uu} H'\times_G J \arrow{ur} \arrow{rr} && \arrow[equals, crossing over]{uu} J \arrow[swap]{ur}{g} &
+\end{tikzcd}
+\]
+%In this form we could treat $g^*$ as a functor $C(J)\to C(G)$,
+%were it not for the fact that pullback is defined only up to isomorphism.
+%In the localized categories, this ambiguity disappears.
+\end{proof}
+
+\begin{lemma}\label{lemma:finite-iso}
+Each finite quasicharacter sheaf $(f,\psi)$ in $\fQC(G)$ determines a
+canonical isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\fQC(G\times G)$.
+ \end{lemma}
+
+\begin{proof}
+We will prove the proposition by finding a weak isomorphism
+$m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ in $C_1(G\times G)$
+and showing that, after passing from $C_1(G\times G)$ to
+$\fQC(G\times G)$, the resulting isomorphism,
+denoted by $\mu(f,\psi)$, is canonically determined by $(f,\psi)$.
+
+Set $H_m \ceq H\times_G(G\times G)$,
+write $f_m : H_m \to G \times G$ for the pullback of $f$ to $H_m$,
+and let $A$ and $A_m$ be the kernels of $f$ and $f_m$ respectively.  Consider the diagram of Lemma~\ref{lemma:finite-pullback}:
+\[
+\begin{tikzcd}[column sep=40]
+V & \Aut(V) & \arrow[swap]{l}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
+  &  & \arrow[dashed]{ul}{\psi_m} \arrow[swap]{u}{(m_f)\vert_{A_m}} A_m \arrow[hook]{r}
+  & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G.
+\end{tikzcd}
+\]
+We have $(f,\psi) \boxtimes (f,\psi) = (f\times f, \psi\otimes \psi)$.
+Since $f\circ m_H = m \circ (f\times f)$, the universal property of pullback gives
+a unique $\theta : H\times H \to H_m$ making the following commute.
+\[
+\begin{tikzcd}[row sep=20,column sep=8]
+\ & V \arrow{dd}{T} && \Aut(V) && A \arrow[hook]{rr} \arrow[swap]{ll}{\psi} &&  H \arrow{rr}{f} && G\\
+ && && \arrow{ul}{\psi_m} A_m  \arrow[hook]{rr} \arrow{ur} && H_m \arrow[pos=0.3]{ur}{m_f} \arrow[swap, pos=0.8]{rr}{f_m}
+ && G \times G \arrow[equal]{dr} \arrow[pos=0.42]{ur}{m} & \\
+& V\otimes V && \Aut(V\otimes V) && \arrow[swap]{ll}{\psi \otimes \psi} \arrow[dashed,swap,pos=0.3]{ul}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr}
+&& \arrow[dashed,swap]{ul}{\theta} \arrow[crossing over,swap,pos=0.7]{uu}{m_H} H\times H \arrow{rr}{f\times f} && G\times G
+\end{tikzcd}
+\]
+Choose a basis $\{ v \}$ for $V$; then $\{ v\otimes v \}$ is a basis for $V\otimes V$.
+Let $T : V \to V\otimes V$ be the linear transformation taking $v$ to $v\otimes v$. Then the lower part of this
+diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G\times G)$.
+%
+While $\theta$ was canonical, $T$ was not, as it depended on the choice of a basis for $V$.
+However, after passing from $C_1(G\times G)$ to $\fQC(G\times G)$, the resulting isomorphism 
+$\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ in $\fQC(G\times G)$ is independent of the choice of basis for $V$.
+ \end{proof}
+
+\begin{proposition}\label{prop:bounded}
+ $\fQC(G)$ is a full subcategory of $\bQC(G)$.
+\end{proposition}
+
+\begin{proof}
+ To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \fQC(G) \to \bQC(G)$.
+
+ If $V$ is a finite-dimensional $\EE$-vector space then we write $V_H$ for the constant sheaf $V$ on $H$.
+If $(f,\psi)$ is a finite quasicharacter on $G$ where $\psi$ is a representation of $\ker f$ on $V$,
+let $L(f,\psi)$ be the local system on $G$ given by the $\psi$-isotypic component of the local system $f_* V_H$ on $G$.
+ We may identify the stalk $(f_* V_H)_{\bar g}$ of $f_* V_H$ at a geometric point ${\bar g}$ on $G$
+ with the $\EE$-vector space $\Hom_\text{set}(\abs{f^{-1}({\bar g})},V)$
+ and the stalk $L(f,\psi)_{\bar g}$ of $L(f,\psi)$ at a geometric point ${\bar g}$ on $G$
+ with the $\EE$-vector space consisting of those functions $s: \abs{f^{-1}({\bar g})} \to V$ such that
+ $s(a\cdot {\bar h}) = \psi(a)(s({\bar h}))$ for all $a\in \ker f$ and for all ${\bar h} \in f^{-1}({\bar g})$.
+
+ For any map $(g,T)$ in $C(G)$, let $L(g,T) : L(f,\psi) \to L(f',\psi')$ be the homomorphism of local systems defined
+ by $s \mapsto s' \ceq T\circ s\circ g$.
+ This construction defines a full monoidal functor $L$ from $C(G)$ to the category $\Loc(G)$ of local systems on $G$ that
+ commutes with pullback along any morphism of $\QC$-schemes,
+ as defined using Lemma~\ref{lemma:finite-pullback}.
+ Moreover, since $L(f,T)$ is an isomorphism of local systems
+ if and only if $(f,T)$ is a weak isomorphism,
+ the full functor $L : C(G) \to \Loc(G)$ factors through the localization functor $C(G) \to C(G)[W^{-1}]$
+ to define a full and faithful functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$;
+ see \cite{kashiwara-schapira:CatgoriesSheaves}*{Exercise 7.5}.
+
+ By Lemma~\ref{lemma:finite-iso}, each $(f,\psi) \in \fQC(G)$ canonically determines
+ an isomorphism
+ \[
+ \mu(f,\psi) : m^*(f,\psi) \to (f,\psi) \boxtimes (f,\psi)
+ \]
+ in $\fQC(G\times G)$.
+ It follows immediately that the functor
+ \[
+ L_G  \ceq  L_{W}\vert_{\fQC(G)} : \fQC(G) \to \bQC(G),
+ \]
+ given on objects by $(f,\psi) \mapsto (L(f,\psi), L_{W}(\mu(f,\psi)))$,
+ is a full and faithful monoidal functor, completing the proof.
+\end{proof}
+
+On general smooth group $\Fq$-schemes $G$, 
+there are bounded quasicharacter sheaves which are not finite.  
+Identifying $\fQC(G)$ with its image under $B_G \circ L_G$, as defined in
+Proposition~\ref{prop:BG} and in the proof of Proposition~\ref{prop:bounded},
+we will see in Corollary~\ref{cor:bounded-and-finite} that
+a quasicharacter sheaf is finite if and only if its Trace of Frobenius has finite image.
+
+\begin{corollary} \label{cor:bounded-and-finite}
+Let $G$ be a smooth commutative group scheme over $\Fq$.
+\begin{enumerate}
+\item $\qcs{L} \in \QC(G)$ is bounded if and only if $\trFrob{\qcs{L}}$ has bounded image,
+\item $\qcs{L}\in \QC(G)$ is finite if and only if $\trFrob{\qcs{L}}$ has finite image.
+\end{enumerate}
+\end{corollary}
+
+\begin{proof}
+We first reduce to the case that $G$ is etale.
+On the connected component
+$G^0$, all quasicharacter sheaves are bounded and finite by Proposition~\ref{prop:connected}.
+On the other hand, $G^0(\Fq)$ is finite by Lemma~\ref{lem:G0alg-grp} and thus Trace of Frobenius
+has finite and therefore bounded image.  If $\chi \in G(\Fq)^*$ then there is some finite-image character $\chi_0$
+with the same restriction to $G^0(\Fq)$ since $G^0(\Fq)$ is lies inside the torsion part of
+the finitely generated abelian group $G(\Fq)$.  Therefore $\chi$ is bounded (resp. has finite image)
+if and only if $\chi \cdot \chi_0^{-1}$ is bounded (resp. has finite image).  But $\chi \cdot \chi_0^{-1}$ descends
+to a character of $\pi_0(G)$.  A similar argument relates boundedness/finiteness of quasicharacter
+sheaves on $G$ to those on $\pi_0(G)$, using the fact that the preimage constructed in the proof of
+Proposition~\ref{prop:restriction} is a finite quasicharacter sheaf on $G$.
+Using these equivalences, it is enough to prove Corollary~\ref{cor:bounded-and-finite} when $G$ is etale.
+
+In the case that $G$ is \'etale, which we now suppose,
+one can easily detect when a quasicharacter sheaf is bounded or finite.
+With reference to Section~\ref{sec:S},
+let $S_G(\qcs{L}) = [\alpha \oplus \beta]$
+and let $b : {\bar G}\to \EEx$ be the multiplicative version of $\beta(\Frob{})$.
+Then $\qcs{L}$ is finite if and only if
+$b(x)$ is a root of unity for all $x\in {\bar G}$.
+By \cite{beilinson-bernstein-deligne:81a}*{Rem. 5.2.1},
+$\qcs{L}$ is bounded if and only if $b(x) \in \Zlx$ for all $x\in {\bar G}$.
+\end{proof}
+
+With Corollary~\ref{cor:bounded-and-finite} in hand
+we see that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves
+when $G$ is a commutative algebraic group over $\Fq$;
+observe that the component group $\pi_0({\bar G})$ is finite in this case.
+On the other hand, Corollary~\ref{cor:bounded-and-finite} also shows us
+why neither finite quasicharacter sheaves nor bounded quasicharacter sheaves
+are up to the task of geometrizing all characters of $G(\Fq)$ for smooth commutative group schemes $G$ since, in general, neither of the full subcategories
+$\fQC(G) \subset \bQC(G) \subset \QC(G)$ are equivalences.
+For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$:
+the flabby quasicharacter sheaf on $G$ corresponding, under Theorem~\ref{thm:snake},
+to the character $1 \mapsto \ell$ is not a bounded quasicharacter sheaf,
+while the flabby quasicharacter sheaf on $G$ corresponding
+to the character $1 \mapsto 1+ \ell$ is a bounded but not finite quasicharacter sheaf.
+%In this latter case the stalk of the quasicharacter sheaf at the component $1$ is defined by a pro-\'etale cover rather than an \'etale cover.
+
+\subsection{Base change}\label{sec:basechange}
+
+When using quasicharacter sheaves to study characters, it is useful to understand
+how quasicharacter sheaves behave under change of fields.
+Let $k'$ be a finite extension of $k$. Then $k \hookrightarrow k'$ induces a group homomorphism
+$i_{k'/k} : G(k) \hookrightarrow G(k')$ and thus a homomorphism
+\begin{align*}
+i_{k'/k}^* : G(k')^* &\to G(k)^* \\
+\chi &\mapsto \chi\circ i_{k'/k}.
+\end{align*}
+We can interpret this operation on characters in terms of quasicharacter sheaves:
+
+\begin{proposition} \label{prop:csbe}
+Set $G_{k'} \ceq G\times_\Spec{k} \Spec{k'}$ and let
+\[
+\QC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \QC(G)
+\]
+be the functor obtained by pullback along the canonical closed immersion of $k$-schemes
+$\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$
+\cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}.
+The following diagram commutes:
+\[
+\begin{tikzcd}
+\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\TrFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\TrFrob{G}} \\
+G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
+\end{tikzcd}
+\]
+\end{proposition}
+\begin{proof}
+This result follows immediately from Proposition~\ref{prop:pullback} together with the identifications
+\[
+\Res_{k'/k}(G_{k'})(k) \cong G_{k'}(k') \cong G(k')
+\]
+from the definitions of Weil restriction and base change.
+\end{proof}
+
+In the opposite direction, let $\Nm : G(k') \to G(k)$ be the norm map and consider the group homomorphism:
+\begin{align*}
+\Nm^* : G(k)^* &\to G(k')^* \\
+\chi &\mapsto \chi\circ \Nm.
+\end{align*}
+We can also interpret this operation on characters in terms of quasicharacter sheaves.
+
+If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$, we define
+a quasicharacter sheaf $\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
+$G_{k'}$ of $G$ to $k'$ by setting
+\[
+\phi_{k'} \ceq \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi).
+\]
+The commutativity of the diagram (QC.3) for $\phi_{k'}$
+follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
+Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
+as taking the action $\varphi$ of $\Weil{k}$ on $\gqcs{L}$
+defined in Section~\ref{sec:category} and restricting it to the subgroup $\Weil{k'}$.
+
+\begin{proposition}\label{prop:basechange}
+With notation above,
+the rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$
+ defines a monoidal functor $\QC(G) \to \QC(G_{k'})$.
+ Moreover, the following diagram commutes:
+\[
+\begin{tikzcd}[column sep=60]
+\QCiso{G} \rar{\nu_{k'/k}} \dar{\TrFrob{G}} & \QCiso{G_{k'}} \dar{\TrFrob{G_{k'}}} \\
+G(k)^*  \rar{\Nm^*} & G(k')^*.
+\end{tikzcd}
+\]
+\end{proposition}
+
+\begin{proof}
+Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
+we may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
+and the value of $\Nm^*(\TrFrob{G}(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
+Applying \ref{QC.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
+\[
+\begin{tikzcd}
+\gqcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gqcs{L}_{F(x)} \otimes \gqcs{L}_{F^2(x)} \otimes \cdots \otimes \gqcs{L}_x
+\dar{\phi_x \otimes (F^*\phi)_x \otimes \cdots \otimes ((F^{n-1})^*\phi)_x} \\
+\gqcs{L}_{\Nm(x)} \rar & \gqcs{L}_x \otimes \gqcs{L}_{F(x)} \otimes \cdots \otimes \gqcs{L}_{F^{n-1}(x)}.
+\end{tikzcd}
+\]
+Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$ and write the image of $v$ under the
+bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
+for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{QC.2}, $v$ maps to
+$v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
+Let $\alpha_i \in \EEx$ represent $((F^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
+the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gqcs{L}_{\Nm(x)}$
+with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gqcs{L}_x$.
+\end{proof}
+
+Finally, let $G'$ be a smooth commutative group scheme over $k'$;
+we explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
+We may decompose the base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
+into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
+\[
+(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
+\]
+Since products and coproducts agree for group schemes we have a natural inclusion of $k'$-schemes
+\[
+G' \hookrightarrow (\Res_{k'/k}G')_{k'}
+\]
+mapping $G'$ into the summand corresponding to $1 \in \Gal(k'/k)$.  Composing $\nu_{k'/k}$
+from Proposition~\ref{prop:basechange} with pullback along this map yields a functor
+\[
+\rho : \QC(\Res_{k'/k}G') \to \QC(G').
+\]
+
+\begin{proposition}
+Let $k'/k$ be a finite extension and let $G'$ be a smooth commutative group scheme over $k'$.
+The following diagram of isomorphisms commutes, where the bottom map is the identity:
+\[
+\begin{tikzcd}
+\QCiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \QCiso{G'} \dar{\TrFrob{G'}}\\
+G'(k')^* \rar & G'(k')^*
+\end{tikzcd}
+\]
+\end{proposition}
+\begin{proof}
+By Proposition~\ref{prop:pullback} the pullback part of the definition of $\rho$ corresponds to the map
+\[
+(\Res_{k'/k}G')(k') \to G'(k')^*
+\]
+induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on
+\[
+(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'
+\]
+is given by permuting coordinates, composition with the norm map yields the identity on $G'(k')$.
+\end{proof}
+
+\todo{Can we improve on this result by proving that $\rho$
+is an equivalence of categories?}
+
+\bibliographystyle{amsalpha}
+\bibliography{Biblio}
+
+\end{document}
+
+\begin{proof}
+Here are some pieces that might help . . .
+
+Consider Diagram~\ref{diagram}, where $B=G$, $C= \pi_0(G)$ and $A=G^0$:
+We have just seen that the back of this diagram commutes and its sequences are exact.
+The front of this diagram also commutes and all its vertical sequences are also exact,
+as we saw in Section~\ref{sec:spectral}.
+Joining the back to the front are the injections from
+Section~\ref{sec:spectral} making the entire diagram commute.
+The vertical left face is an isomorphism of exact sequences by Proposition~\ref{prop:etale-iso}
+and the vertical right face is an isomorphism of exact sequences by Proposition~\ref{prop:connected-iso}.
+%
+Note that these injections are isomorphisms at the bottom, by Lemma~\ref{lem:dual-inv}, and at the left, by Section~\ref{sec:etale}, and at the right, by Section~\ref{sec:connected} and the Five Lemma.
+It now follows that $\ker T_B \to \Hh^0(\Weil{},\Hh^2(B,\EEx))$ is also an isomorphism,
+completing the proof of Theorem~\ref{thm:snake}.
+\end{proof}
+
+\begin{table}[ht]
+\caption{A big diagram}
+\begin{center}
+{\smaller\smaller\smaller
+    \[
+  \begin{tikzcd}[row sep=20, column sep=3]
+    &  0 \arrow{dd} && 0 \arrow{dd} && 0\arrow{dd} & \\
+    &&  0 \arrow[crossing over]{dd} && 0 \arrow[crossing over]{dd} && 0\arrow{dd} & & \\
+    {}& \ker \TrFrob{C} \arrow[->>]{rr} \arrow[>->>]{dr} \arrow{dd} && \arrow{dd} \ker \TrFrob{B} \arrow{rr} \arrow[>->]{dr}  && \ker \TrFrob{A}=0 \arrow[>->>]{dr} \arrow{dd} \arrow{rr} && 0 & \\
+    && \Hh^0(\Weil{},\Hh^2(C,\EEx)) \arrow[crossing over,->>]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(B,\EEx)) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(A,\EEx)) \arrow[crossing over]{dd}  &  &  \\
+    & \QCiso{C} \arrow[>->>]{dr}\arrow{rr} \arrow{dd}%{\TrFrob{C}}
+    && \QCiso{B} \arrow[>->]{dr} \arrow{rr} \arrow{dd}%{\TrFrob{B}}
+    && \QCiso{A} \arrow[>->>]{dr} \arrow{dd}%{\TrFrob{A}}
+    \arrow{rr}  &   & 0 & \\
+\Hh^1(E^\bullet_{A}) \arrow[crossing over]{rr}  && \Hh^2(E^\bullet_{C}) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^2(E^\bullet_{B}) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^2(E^\bullet_{A}) \arrow{rr} \arrow[crossing over]{dd} &  & \Hh^3(E^\bullet_{C}) \\
+   0 \arrow{r}
+    & C(\Fq)^* \arrow[>->>]{dr} \arrow{rr} \arrow{dd}
+    && \arrow{dd} B(\Fq)^* \arrow[>->>]{dr} \arrow{rr} && A(\Fq)^* \arrow[>->>]{dr}  \arrow{dd}
+    \arrow{rr}&& 0 & \\
+ %\Hh^2(\Weil{},\Hh^1({\bar A},\EEx)) \arrow{rr}
+ && \Hh^1(\Weil{},\Hh^1(C,\EEx)) \arrow[crossing over]{dd} \arrow[crossing over]{rr}  && \Hh^1(\Weil{},\Hh^1(B,\EEx)) \arrow[crossing over]{dd} \arrow[crossing over]{rr} && \Hh^1(\Weil{},\Hh^1(A,\EEx)) \arrow[crossing over]{dd}  &  & %\Hh^0(\Weil{},\Hh^1({\bar C},\EEx))
+ \\
+  & 0  && 0  &&  0  && & \\
+        &&  0 && 0 && 0 & & \\
+  \end{tikzcd}
+  \]
+}
+\end{center}
+\label{diagram}
+\end{table}
+
+\begin{corollary}\label{cor:exact}
+  If $G$ is a smooth, commutative group scheme over
+  $\Fq$ then pullback yields an exact sequence
+\[
+\Hh^1(E^\bullet_{G^0}) \to \QCiso{\pi_0(G)} \to \QCiso{G} \to \QCiso{G^0} \to 0
+\]
+of abelian groups.\todo{Pure speculation.}
+\end{corollary}
+
+\begin{proof}
+Really? Then does this make sense: $\Hh^3(E^\bullet_{\pi_0(G)}) =0$? Perhaps. $\Hh^3(\pi_0({\bar G})\rtimes \Weil{},\EEx)=0?$
+\end{proof}
 
@@
 
-\begin{corollary}\label{cor:connected}
- If $G$ is a connected, commutative algebraic group over $\Fq$ then
- \[
-  \TrFrob{G} : \QCiso{G} \to G(\Fq)^*
- \]
- is an isomorphism of groups.
-\end{corollary}
-
-\begin{proof}
- It suffices\todo{Explain why $T_G$ is injective.} to observe that the group homomorphism
- $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$
- is surjective: each character $\chi \in G(\Fq)^*$ determines a finite quasicharacter
- sheaf $(\Lang,\chi^{-1})$ such that Trace of Frobenius of the quasicharacter sheaf
- $B_G (L_G(\Lang,\chi^{-1}))$ is $\chi$.
-\end{proof}
-
 Morphisms in $\QC(G)$ are also very simple.
@@
 
-\subsection{The component group sequence} \label{sec:restriction}
-
-Consider the short exact sequence
-defining the component group scheme for $G$:
-\begin{equation}\label{eq:pi0}
-\begin{tikzcd}
-0 \rar & G^0 \arrow{r}{\iota_0} & G \arrow{r}{\pi_0} & \pi_0(G) \rar & 0.
-\end{tikzcd}
-\end{equation}
-Since $\pi_0(G)$ is a etale commutative group scheme, and this smooth,
-Proposition~\ref{prop:pullback} implies that \eqref{eq:pi0} defines the sequence of functors
-\begin{equation}\label{eq:pi1}
-\begin{tikzcd}
-\QC(0) \rar & \QC(\pi_0(G)) \arrow{r}{\pi_0^*} & \QC(G) \arrow{r}{\iota_0^*} & \QC(G^0) \rar & \QC(0)
-\end{tikzcd}
-\end{equation}
-and therefore, after passing to isomorphism classes, the sequence of abelian groups
-\begin{equation}\label{eq:pi2}
-\begin{tikzcd}
-0 \rar &
-\QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
-\end{tikzcd}
-\end{equation}
- Note that we found the groups $\QCiso{G^0}$
-and $\QCiso{\pi_0(G)}$
-in Sections~\ref{sec:connected} and \ref{sec:etale}, respectively.
-In this section we show that \eqref{eq:pi2} is right exact.
-
-Recall from Section~\ref{sec:finite} that
-a morphism $f : H\to G$ of group $\Fq$-schemes is a discrete isogeny
-if it is a finite, surjective \'etale morphism and
-the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f$ is trivial.
-
-\begin{lemma}\label{lemma:ext}
-Every discrete isogeny onto $G^0$ extends to a discrete
-isogeny onto $G$ inducing an isomorphism on component groups.
-\end{lemma}
-
-\begin{proof}
-Let $\pi: B \to G^0$ be a discrete isogeny and set $A \ceq \ker \pi$.
-  We will find a discrete isogeny $f: H\to G$
-  such that that $H^0 = B$, $f^0 =\pi$ and
-  $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism of component
-  groups.  Namely, we will fit $\pi$ into the following diagram,
-  \begin{equation}\label{extension-diagram}
-  \begin{tikzcd}
-  A \arrow[equal]{r} \dar & A \dar \\
-  B \rar \dar[swap]{\pi} & H \rar \dar[swap]{f} & \pi_0(H) \arrow{d}[below,rotate=90]{\sim}[swap]{\pi_0(f)} \\
-  G^0 \rar & G \rar & \pi_0(G),
-  \end{tikzcd}
-  \end{equation}
-  where all rows and columns are exact and all maps are defined over
-  $\Fq$.  We will do so by passing back and forth between group
-  schemes over $\Fq$ and their $\bFq$-points.
-
-  Extensions of $G^0(\bFq)$ by $A(\bFq)$, such as $B(\bFq)$,
-  correspond to classes in $\Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq))$.
-  Similarly, extensions of $G(\bFq)$ by $A(\bFq)$ correspond to
-  classes in $\Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq))$.  The map
-  $G^0(\bFq) \to G(\bFq)$ induces the map
-  \[
-  \Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq))
-  \]
-  fitting into the long exact sequence derived from applying
-  the functor $\Hom(\mbox{---}, A(\bFq))$ to $G^0(\bFq) \to G(\bFq) \to \pi_0(G)(\bFq)$:
-  \[
-  \Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[\Weil{}]}(\pi_0(G)(\bFq), A(\bFq)).
-  \]
-  Since $\Weil{} \cong \ZZ$ has cohomological dimension $1$ \cite{brown:CohomologyGrps}*{Ex. 4.3},
-  $\Ext^2_{\ZZ[\Weil{}]}(\pi_0(G)(\bFq), A(\bFq))$ vanishes \cite{cartan-eilenberg:HomologicalAlgebra}*{Thm. 2.6}.
-
-  We therefore have the existence of diagram \eqref{extension-diagram}
-  at the level of $\bFq$-points.  This expresses $H(\bFq)$ as a
-  disjoint union of translates of $B(\bFq)$; by transport of structure
-  we may take $H$ to be a group scheme over $\bFq$.  Similarly, the
-  restriction of $f$ to each component of $H$ is a morphism of
-  schemes, and thus $f$ is as well.  Finally, the whole diagram
-  descends to a diagram of $\Fq$-schemes since the $\bFq$-points of
-  the objects come equipped with continuous $\Gamma$-actions, and the
-  morphisms are $\Gamma$-equivariant.
-\end{proof}
-
-In order to use the results of Section~\ref{sec:connected}, we need to know that
-identity component of $G$ is actually an algebraic group.
-
-\begin{lemma} \label{lem:G0alg-grp}
-If $G$ is a commutative smooth group scheme over $\Fq$ then $G^0$ is a connected algebraic group.
-\end{lemma}
-\begin{proof}
- Since $G$ is a smooth group scheme over $\Fq$, its
- identity component $G^0$ of $G$ is a connected smooth,
- group scheme of finite type over $\Fq$, reduced over some finite extension of $\Fq$
- \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}.
- Since $\Fq$ is a finite field and hence perfect, $G^0$ is actually reduced over $\Fq$
- \cite{EGAIV2}*{Prop 6.4.1}.  Since every group scheme over a field is separated
- \cite{vdGeer-Moonen:AbelianVarieties}*{3.12},
- it follows that $G^0$ is a connected algebraic group.
-\end{proof}
-
-\begin{proposition}\label{prop:restriction}
-For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf
-$\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$.
-As a consequence, the restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
-\end{proposition}
-
-\begin{proof}
-  By Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}, every
-  quasicharacter sheaf on $G^0$ is isomorphic to a
-  finite quasicharacter sheaf on $G^0$,
-  so to prove the proposition it suffices to show that every
-  finite quasicharacter sheaf on $G^0$ extends to a finite quasicharacter sheaf on $G$.
-
- Let $(\pi,\psi)$ be a finite quasicharacter sheaf on $G^0$.
- By Lemma~\ref{lemma:ext}, there is an extension of the
- discrete isogeny $\pi : B \to G^0$ to a discrete isogeny $f : H \to G$
- such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
- Then $(f,\psi)$ is a finite quasicharacter sheaf on $G$ and
- $(f,\psi)\vert_{G^0} \iso (\pi,\psi)$.
-\end{proof}
-
-\begin{proposition}\label{prop:middleexact}
- The sequence
- \[
-  \begin{tikzcd}
-  0 \rar & \QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
-  \end{tikzcd}
- \]
- is exact.
-\end{proposition}
-
-\begin{proof}
-The sequence is exact at $\QCiso{G^0}$ by Proposition~\ref{prop:restriction},
-so here we show that it is also exact at $\QCiso{G}$.
-First note that $\iota_0^* \circ \pi_0^*$ is trivial by Proposition~\ref{prop:pullback}.
-So it suffices to show that if $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$
-with $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$ then $\qcs{L}$ is in the essential image of $\pi_0^*$.
-
-For each $x\in \pi_0(\bG)$, set $\bG^x \ceq \pi_0^{-1}(x)$.
-Let $g, g'$ be geometric points in the same
-geometric connected component $\bG^x$.
-Set $a = g^{-1}g'$ and note that $a$ is a geometric point in $\bG^0$.
-Let $\mu_{g,a} : \gqcs{L}_{ga} \to \gqcs{L}_g \otimes \gqcs{L}_a$
-be the isomorphism of vector spaces obtained by restriction of
-$\mu : m^*\gqcs{L} \to \gqcs{L} \boxtimes \gqcs{L}$ to the
-geometric point $(g,a)$ on $\bG^x \times \bG^0$.
-Since $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$,
-the stalk of $\gqcs{L}$ at $a$ is $\EE$.
-In this way the pair of geometric points $g, g' \in \bG^x$
-determines an isomorphism $\varphi_{g,g'} \ceq \mu_{g,a}^{-1}$
-from $\gqcs{L}_{g}$ to $\gqcs{L}_{g'}$.
-
-The isomorphisms $\varphi_{g,g'}: \gqcs{L}_{g} \to \gqcs{L}_{g'}$ are canonical
-in the following sense: if $g,g'\in \bG^x$ and $h,h'\in \bG^y$
-then it follows from \ref{QC.2} and \ref{QC.3}
-that
- \begin{equation}\label{eq:qc}
-  \begin{tikzcd}[column sep=55]
-   \gqcs{L}_{gh} \arrow{r}{\varphi_{gh,g'h'}} \arrow[swap]{d}{\mu_{g,h}}
-  & \gqcs{L}_{g'h'} \arrow{d}{\mu_{g',h'}}
-  &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-  &  \gqcs{L}_{\Frob{}(g)} \arrow{r}{\varphi_{\Frob{}(g),\Frob{}(g')}} \arrow[swap]{d}{\phi_{g}} & \gqcs{L}_{\Frob{}(g')} \arrow{d}{\phi_{g'}} \\
-  \gqcs{L}_{g} \otimes \gqcs{L}_{h} \arrow{r}{\varphi_{g,g'}\otimes \varphi_{h,h'}}
-  & \gqcs{L}_{g'} \otimes \gqcs{L}_{h'}
-  & {}
-  & \gqcs{L}_{g} \arrow{r}{\varphi_{g,g'}} & \gqcs{L}_{g'}
-  \end{tikzcd}
- \end{equation}
-both commute.
-
-For each $x\in \pi_0(\bG)$, pick $g(x)\in \bG^x$
-and set $\gqcs{E}_x \ceq \gqcs{L}_{g(x)}$.
-Let $\phi_x : \gqcs{E}_{\Frob{}(x)} \to \gqcs{E}_x$
-be the isomorphism of $\EE$-vector spaces obtained by composing
-$\varphi_{g(\Frob{}(x)),\Frob{}(g(x))} : \gqcs{L}_{g(\Frob{}(x))} \to \gqcs{L}_{\Frob{}(g(x))}$
-with $\phi_{g(x)} : \gqcs{L}_{\Frob{}(g(x))} \to \gqcs{L}_{g(x)}$.
-For each pair $x,y\in \pi_0(\bG)$
-let $\mu_{x,y} : \gqcs{E}_{x+y}\to \gqcs{E}_x\otimes \gqcs{E}_y$
-be the isomorphism of $\EE$-vector spaces obtained by composing
-$\varphi_{g(x+y),g(x)g(y)} : \gqcs{L}_{g(x+y)} \to \gqcs{L}_{g(x)g(y)}$
-with $\mu_{g(x),g(y)} : \gqcs{L}_{g(x)g(y)} \to \gqcs{L}_{g(x)}\otimes \gqcs{L}_{g(y)}$.
-Using \eqref{eq:qc}, it follows that \ref{qc.1}, \ref{qc.2} and \ref{qc.3} are satisfied for
-$\qcs{E} \ceq (\gqcs{E}_x, \mu_{x,y}, \phi_x)$, thus defining a quasicharacter sheaf on $\pi_0(G)$.
-
-The pullback $\pi_0^*(\qcs{E})$ of $\qcs{E}$ along $\pi_0 : G \to \pi_0(G)$ is constant
-on geometric connected components, with stalks given by
-$(\pi_0^* \qcs{E})_g = \qcs{E}_{x}$ for all $g\in \bG^x$.  Thus both $\pi_0^*\qcs{E}$ and $\qcs{L}$
-are constant on geometric connected components of $G$.
-The choices above define isomorphisms
-$\gqcs{L}\vert_{\bG^x} \to  (\gqcs{E}_{x})_{\bG^x}$ for each $x\in \pi_0(\bG)$.
-The resulting isomorphism $\gqcs{L} \to \pi_0^* \gqcs{E}$ satisfies \ref{QC.4},
-thus defining an isomorphism $\qcs{L} \to \pi_0^* \qcs{E}$ in $\QC(G)$.
-\end{proof}
-
-\subsection{The function--sheaf dictionary for smooth, commutative group schemes}
-\label{sec:snake}
-
-We saw in Proposition~\ref{prop:functorialG} that Trace of Frobenius
-$\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
-In this section we improve that result.
-
-\begin{theorem}\label{thm:snake}
-  If $G$ is a smooth, commutative group scheme over $\Fq$ then
-  \[
-  \TrFrob{G} : \QCiso{G} \to G(\Fq)^*
-  \]
-is surjective with kernel isomorphic to $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$.
-\end{theorem}
-
-\begin{proof}
-  Recall the short exact sequence \eqref{eq:pi0}
-  defining the component group scheme for $G$:
-  \[
-  \begin{tikzcd}
-    1 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
-  \end{tikzcd}
-  \]
-  Let
-  \[
-  \begin{tikzcd}[row sep=20]
-    0 \rar & \ker \TrFrob{\pi_0(G)} \arrow[dashed]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dashed]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
-    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
-    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
-    0 \rar & \pi_0(G)(\Fq)^* \rar \dar
-    & \arrow{d} G(\Fq)^* \rar & G^0(\Fq)^* \rar \dar & 0\\
-    & \coker \TrFrob{\pi_0(G)} =0 \arrow[dashed]{r} & \coker \TrFrob{G} \arrow[dashed]{r} &  \coker \TrFrob{G^0} =0 &
-  \end{tikzcd}
-  \]
-  be the commutative diagram of abelian groups obtained by applying
-  Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.
-
-  The sequence of abelian groups
-  \begin{equation}\label{eq:pi0k}
-  \begin{tikzcd}
-    1 \rar & G^0(\Fq) \rar & G(\Fq) \rar & \pi_0(G)(\Fq) \rar & 0,
-  \end{tikzcd}
-  \end{equation}
-  is exact since $\Hh^1(\Fq,G^0) =0$ by Lemma~\ref{lem:G0alg-grp} and Lang's theorem on connected algebraic groups over finite fields \cite{lang:56a}.
-  Since $\EEx$ is divisible, $\Hom_\text{Ab}(\ - \ ,\EEx)$ is exact and thus the dual sequence of
-  character groups is also exact.
-
-  The upper row is exact by Proposition~\ref{prop:middleexact}.
-  Now Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}
-  imply that $\ker \TrFrob{G^0} =0$ and $\coker \TrFrob{G^0}=0$,
-  while Proposition~\ref{prop:etale-iso} gives $\ker \TrFrob{\pi_0(G)} \iso \Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$
-  and $\coker \TrFrob{\pi_0(G)}=0$.
-%
-It follows from the snake lemma that $\coker \TrFrob{G} =0$
-and $\ker \TrFrob{\pi_0(G)} \to \ker \TrFrob{G}$ is an isomorphism.
-
-%We now turn our attention $\lTrFrob{G}: \lQCiso{G}  \to G(\Fq)^*$ is an isomorphism.
-%First, note that $\lTrFrob{G}$ is surjective because $\TrFrob{G}$ is surjective.
-%We will now show that the kernel of $\lTrFrob{G}$ is trivial.
-
-%First, suppose $G$ is etale.
-%Let $(\gqcs{E},\phi')$ be a quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{E},\phi')}=1$.
-%Let $\qcs{E} = (\gqcs{E},\mu,\phi')$ be a quasicharacter sheaf.
-%By Proposition~\ref{prop:etale-iso}, $S_G(\qcs{E}) = [\alpha\oplus 0]$ for some $\alpha \in Z^0(\Weil{},Z^2({\bar G},\EEx))$
-%corresponding to a choice $\{ v_x \in \gqcs{E}_x^\times \tq x\in {\bar C}\}$.
-%Let $a\in Z^2({\bar G},\EEx)$ be the multiplicative version of $\alpha$
-%and let $\mu'$ be the indexed set of isomorphisms $\mu'_{x,y} : \EE \to \EE\otimes \EE$ defined by $1 \mapsto a(x,y) 1 \otimes 1$.
-%Then $(\EE,\mu', 1)$ is a quasicharacter sheaf the isomorphisms $\gqcs{E}_x \to \EE$ defined by $v_x \mapsto 1$ gives an isomorphism $(\gqcs{E},\mu,\phi')\to ((\EE)_{\bar C},\mu', 1)$ in $\QC(G)$.
-%It follows that $(\gqcs{E},\phi')\iso ((\EE)_{\bar G},1)$ in $\lQC(G)$, so $\lTrFrob{G}$ is injective.
-%This completes the proof of Theorem~\ref{thm:snake} in the case that $G$ is etale.
-
-%Now let $G$ be arbitrary
-%and let $(\gqcs{L},\phi)$ be a flabby quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{L},\phi)}=1$.
-%Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf.
-%We saw above that $\ker \TrFrob{\pi_0(G)}\to \TrFrob{G}$ is surjective in this case,
-%so $\qcs{L} = \pi_0^*\qcs{E}$ for some $\qcs{E}\in \QC(\pi_0(G))$.
-%Since $\trFrob{\qcs{L}}(g) = \trFrob{\qcs{E}}(\pi_0(g))$ and since $\pi_0 : G(\Fq) \to \pi_0(G)(\Fq)$ is surjective, $\trFrob{\qcs{E}}=1$.
-%But now $\qcs{E} \iso ((\EE)_{\pi_0({\bar G})},\mu', 1)$ by the paragraph above.
-%So $\qcs{L} = \pi_0^*\qcs{E} \iso \pi_0^*((\EE)_{\pi_0({\bar G})},\mu', 1) = ((\EE)_{\bar G},\pi_0^*\mu', \pi_0^*1)$ in $\QC(G)$.
-%It follows that $(\gqcs{L},\phi) \iso ((\EE)_{\bar G},1)$ in $\lQC(G)$.
-%This completes the proof of Theorem~\ref{thm:snake}.
-\end{proof}
-
-%\begin{corollary}\label{cor:exact}
-%  If $G$ is a smooth, commutative group scheme over
-%  $\Fq$ then pullback yields an exact sequence
-%\[
-%0 \to \lQCiso{\pi_0(G)} \to \lQCiso{G} \to \lQCiso{G^0} \to 0
-%\]
-%of abelian groups.
-%\end{corollary}
-
-%\begin{proof}
-%Argue as in the first paragraph in the proof of Theorem~\ref{thm:snake},
-%using the category $\lQC(G)$ in place of $\QC(G)$.
-%\end{proof}
-
-\section{Application to \texorpdfstring{$p$}{p}-adic tori}
-
-\subsection{Bounded quasicharacter sheaves}\label{sec:bounded}
-
-In this section we consider a class of quasicharacter sheaves on $G$ obtained by
-replacing the Weil sheaf $(\gqcs{L}, \phi)$ on $\bG$ in the definition of a quasicharacter
-sheaf with an $\ell$-adic local system on $G$ itself.
-
-\begin{definition}
-Let $\bQC(G)$ be the category of pairs $(\qcs{L}_0,\mu_0)$
-where $\qcs{L}_0$ an $\ell$-adic local system on $G$ of rank~one,
-equipped with an isomorphism $\mu_0 : m^* \qcs{L}_0 \to \qcs{L}_0 \boxtimes \qcs{L}_0$
-satisfying the analogue of \ref{QC.1} on $G$;
-morphisms in $\bQC(G)$ are defined as in the second part of
-\ref{QC.3}.
-This is the category of \emph{bounded quasicharacter sheaves} on $G$.
-\end{definition}
-
-The category of bounded quasicharacter sheaves is a rigid monoidal category in the obvious way.
-
-\begin{proposition}\label{prop:BG}
-Extension of scalars defines a full and faithful functor
-$B_G : \bQC(G) \hookrightarrow \QC(G)$.
-\end{proposition}
-
-\begin{proof}
- Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$.
- Then $\qcs{L}_0$ is an $\ell$-adic constructible sheaf on $G$ and
- $b_G^* \qcs{L}_0$ comes equipped with an isomorphism
- $\phi : \Frob{G}^* b_G^*\qcs{L}_0 \to b_G^* \qcs{L}_0$.
- Moreover, the functor $\qcs{L}_0 \mapsto (b_G^* \qcs{L}_0,\phi)$
- from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
- is full and faithful \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}}.
- This functor preserves local constancy, so takes local systems to local systems.
- Set $\mu \ceq b_{G\times G}^*\mu_0$; clearly, this satisfies \ref{QC.2}
- with $b_G^*\qcs{L}_0$ playing the role of $\gqcs{L}$.
- Moreover, $\phi$ is compatible with $\mu$ in the sense of \ref{QC.3}.
- This construction defines the functor $B_G : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,\mu, \phi)$
- and also shows that it is full and faithful.
-\end{proof}
-
-In general, $\bQC(G)$ is an essentially
-proper subcategory of $\QC(G)$. We will identify $\bQC(G)$ with its image under $B_G$
-and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ is \emph{bounded}
-if it is isomorphic to some $B_G(\qcs{L}_0, \mu_0)$.
-We will see in Corollary~\ref{cor:bounded-and-finite} that bounded quasicharacter sheaves are exactly quasicharacter sheaves with bounded Trace of Frobenius.
-
-\subsection{Finite implies Bounded}
-
-In this section we show that $\fQC(G)$ is a full subcategory of $\bQC(G)$.
-To prepare for that result, we need the next two lemmas.
-
-\begin{lemma}\label{lemma:finite-pullback}
-Let $g : J \to G$ be a morphism of smooth groups schemes over $\Fq$.
-Let $f_g : H\times_G J\to J$
-be the pullback of $f$ along $g$ and define $\psi_g : \ker f_g \to \Aut(V)$ as in the diagram below:
-\[
-\begin{tikzcd}
-V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker f_g}} \ker f_g \arrow[hook]{r}
-  & \arrow[swap]{u}{g_f} H\times_G J \arrow{r}{f_g} & \arrow{u}{g} J.
-\end{tikzcd}
-\]
-Then $(f,\psi) \mapsto (f_g,\psi_g)$
-defines a monomial functor $g^* : C(G)[W^{-1}] \to C(J)[W^{-1}]$.
-\end{lemma}
-
-\begin{proof}
-The key point is that pullback along $g$ takes discrete isogenies to discrete isogenies,
-and maps over $G$ to maps over $J$, as pictured below.
-\[
-\begin{tikzcd}[row sep={{{{40,between origins}}}},column sep={{{{50,between origins}}}}]
-%\ V \arrow{dd}{T} &
-\Aut(V) && \arrow[swap]{ll}{\psi} \ker f \arrow[hook]{rr} \arrow[leftarrow]{dd} && H \arrow{rr}{f} \arrow[leftarrow]{dd} && \arrow[equal]{dd} G\\
-% &
-& \arrow{ul} \ker f\times_G J \arrow{ur} \arrow[hook, crossing over]{rr} && H\times_G J \arrow{ur} \arrow[crossing over]{rr} && J \arrow[swap]{ur}{g} & \\
-%V' &
- \Aut(V') && \arrow[swap,pos=0.25]{ll}{\psi'} \ker f'  \arrow[hook]{rr}
-&& H' \arrow[pos=0.25]{rr}{f'} && G\\
-% &
- & \arrow{ul} \ker f'\times_G J \arrow[crossing over]{uu} \arrow{ur} \arrow[hook]{rr}
- && \arrow[crossing over]{uu} H'\times_G J \arrow{ur} \arrow{rr} && \arrow[equals, crossing over]{uu} J \arrow[swap]{ur}{g} &
-\end{tikzcd}
-\]
-%In this form we could treat $g^*$ as a functor $C(J)\to C(G)$,
-%were it not for the fact that pullback is defined only up to isomorphism.
-%In the localized categories, this ambiguity disappears.
-\end{proof}
-
-\begin{lemma}\label{lemma:finite-iso}
-Each finite quasicharacter sheaf $(f,\psi)$ in $\fQC(G)$ determines a
-canonical isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\fQC(G\times G)$.
- \end{lemma}
-
-\begin{proof}
-We will prove the proposition by finding a weak isomorphism
-$m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ in $C_1(G\times G)$
-and showing that, after passing from $C_1(G\times G)$ to
-$\fQC(G\times G)$, the resulting isomorphism,
-denoted by $\mu(f,\psi)$, is canonically determined by $(f,\psi)$.
-
-Set $H_m \ceq H\times_G(G\times G)$,
-write $f_m : H_m \to G \times G$ for the pullback of $f$ to $H_m$,
-and let $A$ and $A_m$ be the kernels of $f$ and $f_m$ respectively.  Consider the diagram of Lemma~\ref{lemma:finite-pullback}:
-\[
-\begin{tikzcd}[column sep=40]
-V & \Aut(V) & \arrow[swap]{l}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-  &  & \arrow[dashed]{ul}{\psi_m} \arrow[swap]{u}{(m_f)\vert_{A_m}} A_m \arrow[hook]{r}
-  & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G.
-\end{tikzcd}
-\]
-We have $(f,\psi) \boxtimes (f,\psi) = (f\times f, \psi\otimes \psi)$.
-Since $f\circ m_H = m \circ (f\times f)$, the universal property of pullback gives
-a unique $\theta : H\times H \to H_m$ making the following commute.
-\[
-\begin{tikzcd}[row sep=20,column sep=8]
-\ & V \arrow{dd}{T} && \Aut(V) && A \arrow[hook]{rr} \arrow[swap]{ll}{\psi} &&  H \arrow{rr}{f} && G\\
- && && \arrow{ul}{\psi_m} A_m  \arrow[hook]{rr} \arrow{ur} && H_m \arrow[pos=0.3]{ur}{m_f} \arrow[swap, pos=0.8]{rr}{f_m}
- && G \times G \arrow[equal]{dr} \arrow[pos=0.42]{ur}{m} & \\
-& V\otimes V && \Aut(V\otimes V) && \arrow[swap]{ll}{\psi \otimes \psi} \arrow[dashed,swap,pos=0.3]{ul}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr}
-&& \arrow[dashed,swap]{ul}{\theta} \arrow[crossing over,swap,pos=0.7]{uu}{m_H} H\times H \arrow{rr}{f\times f} && G\times G
-\end{tikzcd}
-\]
-Choose a basis $\{ v \}$ for $V$; then $\{ v\otimes v \}$ is a basis for $V\otimes V$.
-Let $T : V \to V\otimes V$ be the linear transformation taking $v$ to $v\otimes v$. Then the lower part of this
-diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G\times G)$.
-%
-While $\theta$ was canonical, $T$ was not, as it depended on the choice of a basis for $V$.
-However, after passing from $C_1(G\times G)$ to $\fQC(G\times G)$, the resulting isomorphism 
-$\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ in $\fQC(G\times G)$ is independent of the choice of basis for $V$.
- \end{proof}
-
-\begin{proposition}\label{prop:bounded}
- $\fQC(G)$ is a full subcategory of $\bQC(G)$.
-\end{proposition}
-
-\begin{proof}
- To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \fQC(G) \to \bQC(G)$.
-
- If $V$ is a finite-dimensional $\EE$-vector space then we write $V_H$ for the constant sheaf $V$ on $H$.
-If $(f,\psi)$ is a finite quasicharacter on $G$ where $\psi$ is a representation of $\ker f$ on $V$,
-let $L(f,\psi)$ be the local system on $G$ given by the $\psi$-isotypic component of the local system $f_* V_H$ on $G$.
- We may identify the stalk $(f_* V_H)_{\bar g}$ of $f_* V_H$ at a geometric point ${\bar g}$ on $G$
- with the $\EE$-vector space $\Hom_\text{set}(\abs{f^{-1}({\bar g})},V)$
- and the stalk $L(f,\psi)_{\bar g}$ of $L(f,\psi)$ at a geometric point ${\bar g}$ on $G$
- with the $\EE$-vector space consisting of those functions $s: \abs{f^{-1}({\bar g})} \to V$ such that
- $s(a\cdot {\bar h}) = \psi(a)(s({\bar h}))$ for all $a\in \ker f$ and for all ${\bar h} \in f^{-1}({\bar g})$.
-
- For any map $(g,T)$ in $C(G)$, let $L(g,T) : L(f,\psi) \to L(f',\psi')$ be the homomorphism of local systems defined
- by $s \mapsto s' \ceq T\circ s\circ g$.
- This construction defines a full monoidal functor $L$ from $C(G)$ to the category $\Loc(G)$ of local systems on $G$ that
- commutes with pullback along any morphism of $\QC$-schemes,
- as defined using Lemma~\ref{lemma:finite-pullback}.
- Moreover, since $L(f,T)$ is an isomorphism of local systems
- if and only if $(f,T)$ is a weak isomorphism,
- the full functor $L : C(G) \to \Loc(G)$ factors through the localization functor $C(G) \to C(G)[W^{-1}]$
- to define a full and faithful functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$;
- see \cite{kashiwara-schapira:CatgoriesSheaves}*{Exercise 7.5}.
-
- By Lemma~\ref{lemma:finite-iso}, each $(f,\psi) \in \fQC(G)$ canonically determines
- an isomorphism
- \[
- \mu(f,\psi) : m^*(f,\psi) \to (f,\psi) \boxtimes (f,\psi)
- \]
- in $\fQC(G\times G)$.
- It follows immediately that the functor
- \[
- L_G  \ceq  L_{W}\vert_{\fQC(G)} : \fQC(G) \to \bQC(G),
- \]
- given on objects by $(f,\psi) \mapsto (L(f,\psi), L_{W}(\mu(f,\psi)))$,
- is a full and faithful monoidal functor, completing the proof.
-\end{proof}
-
-On general smooth group $\Fq$-schemes $G$, 
-there are bounded quasicharacter sheaves which are not finite.  
-Identifying $\fQC(G)$ with its image under $B_G \circ L_G$, as defined in
-Proposition~\ref{prop:BG} and in the proof of Proposition~\ref{prop:bounded},
-we will see in Corollary~\ref{cor:bounded-and-finite} that
-a quasicharacter sheaf is finite if and only if its Trace of Frobenius has finite image.
-
-\begin{corollary} \label{cor:bounded-and-finite}
-Let $G$ be a smooth commutative group scheme over $\Fq$.
-\begin{enumerate}
-\item $\qcs{L} \in \QC(G)$ is bounded if and only if $\trFrob{\qcs{L}}$ has bounded image,
-\item $\qcs{L}\in \QC(G)$ is finite if and only if $\trFrob{\qcs{L}}$ has finite image.
-\end{enumerate}
-\end{corollary}
-
-\begin{proof}
-We first reduce to the case that $G$ is etale.
-On the connected component
-$G^0$, all quasicharacter sheaves are bounded and finite by Proposition~\ref{prop:connected}.
-On the other hand, $G^0(\Fq)$ is finite by Lemma~\ref{lem:G0alg-grp} and thus Trace of Frobenius
-has finite and therefore bounded image.  If $\chi \in G(\Fq)^*$ then there is some finite-image character $\chi_0$
-with the same restriction to $G^0(\Fq)$ since $G^0(\Fq)$ is lies inside the torsion part of
-the finitely generated abelian group $G(\Fq)$.  Therefore $\chi$ is bounded (resp. has finite image)
-if and only if $\chi \cdot \chi_0^{-1}$ is bounded (resp. has finite image).  But $\chi \cdot \chi_0^{-1}$ descends
-to a character of $\pi_0(G)$.  A similar argument relates boundedness/finiteness of quasicharacter
-sheaves on $G$ to those on $\pi_0(G)$, using the fact that the preimage constructed in the proof of
-Proposition~\ref{prop:restriction} is a finite quasicharacter sheaf on $G$.
-Using these equivalences, it is enough to prove Corollary~\ref{cor:bounded-and-finite} when $G$ is etale.
-
-In the case that $G$ is \'etale, which we now suppose,
-one can easily detect when a quasicharacter sheaf is bounded or finite.
-With reference to Section~\ref{sec:S},
-let $S_G(\qcs{L}) = [\alpha \oplus \beta]$
-and let $b : {\bar G}\to \EEx$ be the multiplicative version of $\beta(\Frob{})$.
-Then $\qcs{L}$ is finite if and only if
-$b(x)$ is a root of unity for all $x\in {\bar G}$.
-By \cite{beilinson-bernstein-deligne:81a}*{Rem. 5.2.1},
-$\qcs{L}$ is bounded if and only if $b(x) \in \Zlx$ for all $x\in {\bar G}$.
-\end{proof}
-
-With Corollary~\ref{cor:bounded-and-finite} in hand
-we see that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves
-when $G$ is a commutative algebraic group over $\Fq$;
-observe that the component group $\pi_0({\bar G})$ is finite in this case.
-On the other hand, Corollary~\ref{cor:bounded-and-finite} also shows us
-why neither finite quasicharacter sheaves nor bounded quasicharacter sheaves
-are up to the task of geometrizing all characters of $G(\Fq)$ for smooth commutative group schemes $G$ since, in general, neither of the full subcategories
-$\fQC(G) \subset \bQC(G) \subset \QC(G)$ are equivalences.
-For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$:
-the flabby quasicharacter sheaf on $G$ corresponding, under Theorem~\ref{thm:snake},
-to the character $1 \mapsto \ell$ is not a bounded quasicharacter sheaf,
-while the flabby quasicharacter sheaf on $G$ corresponding
-to the character $1 \mapsto 1+ \ell$ is a bounded but not finite quasicharacter sheaf.
-%In this latter case the stalk of the quasicharacter sheaf at the component $1$ is defined by a pro-\'etale cover rather than an \'etale cover.
-
-\subsection{Base change}\label{sec:basechange}
-
-When using quasicharacter sheaves to study characters, it is useful to understand
-how quasicharacter sheaves behave under change of fields.
-Let $k'$ be a finite extension of $k$. Then $k \hookrightarrow k'$ induces a group homomorphism
-$i_{k'/k} : G(k) \hookrightarrow G(k')$ and thus a homomorphism
-\begin{align*}
-i_{k'/k}^* : G(k')^* &\to G(k)^* \\
-\chi &\mapsto \chi\circ i_{k'/k}.
-\end{align*}
-We can interpret this operation on characters in terms of quasicharacter sheaves:
-
-\begin{proposition} \label{prop:csbe}
-Set $G_{k'} \ceq G\times_\Spec{k} \Spec{k'}$ and let
-\[
-\QC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \QC(G)
-\]
-be the functor obtained by pullback along the canonical closed immersion of $k$-schemes
-$\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$
-\cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}.
-The following diagram commutes:
-\[
-\begin{tikzcd}
-\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\TrFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\TrFrob{G}} \\
-G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
-\end{tikzcd}
-\]
-\end{proposition}
-\begin{proof}
-This result follows immediately from Proposition~\ref{prop:pullback} together with the identifications
-\[
-\Res_{k'/k}(G_{k'})(k) \cong G_{k'}(k') \cong G(k')
-\]
-from the definitions of Weil restriction and base change.
-\end{proof}
-
-In the opposite direction, let $\Nm : G(k') \to G(k)$ be the norm map and consider the group homomorphism:
-\begin{align*}
-\Nm^* : G(k)^* &\to G(k')^* \\
-\chi &\mapsto \chi\circ \Nm.
-\end{align*}
-We can also interpret this operation on characters in terms of quasicharacter sheaves.
-
-If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$, we define
-a quasicharacter sheaf $\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
-$G_{k'}$ of $G$ to $k'$ by setting
-\[
-\phi_{k'} \ceq \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi).
-\]
-The commutativity of the diagram (QC.3) for $\phi_{k'}$
-follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
-Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
-as taking the action $\varphi$ of $\Weil{k}$ on $\gqcs{L}$
-defined in Section~\ref{sec:category} and restricting it to the subgroup $\Weil{k'}$.
-
-\begin{proposition}\label{prop:basechange}
-With notation above,
-the rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$
- defines a monoidal functor $\QC(G) \to \QC(G_{k'})$.
- Moreover, the following diagram commutes:
-\[
-\begin{tikzcd}[column sep=60]
-\QCiso{G} \rar{\nu_{k'/k}} \dar{\TrFrob{G}} & \QCiso{G_{k'}} \dar{\TrFrob{G_{k'}}} \\
-G(k)^*  \rar{\Nm^*} & G(k')^*.
-\end{tikzcd}
-\]
-\end{proposition}
-
-\begin{proof}
-Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
-we may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
-and the value of $\Nm^*(\TrFrob{G}(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
-Applying \ref{QC.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
-\[
-\begin{tikzcd}
-\gqcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gqcs{L}_{F(x)} \otimes \gqcs{L}_{F^2(x)} \otimes \cdots \otimes \gqcs{L}_x
-\dar{\phi_x \otimes (F^*\phi)_x \otimes \cdots \otimes ((F^{n-1})^*\phi)_x} \\
-\gqcs{L}_{\Nm(x)} \rar & \gqcs{L}_x \otimes \gqcs{L}_{F(x)} \otimes \cdots \otimes \gqcs{L}_{F^{n-1}(x)}.
-\end{tikzcd}
-\]
-Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$ and write the image of $v$ under the
-bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
-for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{QC.2}, $v$ maps to
-$v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
-Let $\alpha_i \in \EEx$ represent $((F^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
-the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gqcs{L}_{\Nm(x)}$
-with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gqcs{L}_x$.
-\end{proof}
-
-Finally, let $G'$ be a smooth commutative group scheme over $k'$;
-we explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
-We may decompose the base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
-into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
-\[
-(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
-\]
-Since products and coproducts agree for group schemes we have a natural inclusion of $k'$-schemes
-\[
-G' \hookrightarrow (\Res_{k'/k}G')_{k'}
-\]
-mapping $G'$ into the summand corresponding to $1 \in \Gal(k'/k)$.  Composing $\nu_{k'/k}$
-from Proposition~\ref{prop:basechange} with pullback along this map yields a functor
-\[
-\rho : \QC(\Res_{k'/k}G') \to \QC(G').
-\]
-
-\begin{proposition}
-Let $k'/k$ be a finite extension and let $G'$ be a smooth commutative group scheme over $k'$.
-The following diagram of isomorphisms commutes, where the bottom map is the identity:
-\[
-\begin{tikzcd}
-\QCiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \QCiso{G'} \dar{\TrFrob{G'}}\\
-G'(k')^* \rar & G'(k')^*
-\end{tikzcd}
-\]
-\end{proposition}
-\begin{proof}
-By Proposition~\ref{prop:pullback} the pullback part of the definition of $\rho$ corresponds to the map
-\[
-(\Res_{k'/k}G')(k') \to G'(k')^*
-\]
-induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on
-\[
-(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'
-\]
-is given by permuting coordinates, composition with the norm map yields the identity on $G'(k')$.
-\end{proof}
-
-\todo{Can we improve on this result by proving that $\rho$
-is an equivalence of categories?}
-
-\bibliographystyle{amsalpha}
-\bibliography{Biblio}
-
-\end{document}
-
-\begin{proof}
-Here are some pieces that might help . . .
-
-Consider Diagram~\ref{diagram}, where $B=G$, $C= \pi_0(G)$ and $A=G^0$:
-We have just seen that the back of this diagram commutes and its sequences are exact.
-The front of this diagram also commutes and all its vertical sequences are also exact,
-as we saw in Section~\ref{sec:spectral}.
-Joining the back to the front are the injections from
-Section~\ref{sec:spectral} making the entire diagram commute.
-The vertical left face is an isomorphism of exact sequences by Proposition~\ref{prop:etale-iso}
-and the vertical right face is an isomorphism of exact sequences by Proposition~\ref{prop:connected-iso}.
-%
-Note that these injections are isomorphisms at the bottom, by Lemma~\ref{lem:dual-inv}, and at the left, by Section~\ref{sec:etale}, and at the right, by Section~\ref{sec:connected} and the Five Lemma.
-It now follows that $\ker T_B \to \Hh^0(\Weil{},\Hh^2(B,\EEx))$ is also an isomorphism,
-completing the proof of Theorem~\ref{thm:snake}.
-\end{proof}
-
-\begin{table}[ht]
-\caption{A big diagram}
-\begin{center}
-{\smaller\smaller\smaller
-    \[
-  \begin{tikzcd}[row sep=20, column sep=3]
-    &  0 \arrow{dd} && 0 \arrow{dd} && 0\arrow{dd} & \\
-    &&  0 \arrow[crossing over]{dd} && 0 \arrow[crossing over]{dd} && 0\arrow{dd} & & \\
-    {}& \ker \TrFrob{C} \arrow[->>]{rr} \arrow[>->>]{dr} \arrow{dd} && \arrow{dd} \ker \TrFrob{B} \arrow{rr} \arrow[>->]{dr}  && \ker \TrFrob{A}=0 \arrow[>->>]{dr} \arrow{dd} \arrow{rr} && 0 & \\
-    && \Hh^0(\Weil{},\Hh^2(C,\EEx)) \arrow[crossing over,->>]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(B,\EEx)) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(A,\EEx)) \arrow[crossing over]{dd}  &  &  \\
-    & \QCiso{C} \arrow[>->>]{dr}\arrow{rr} \arrow{dd}%{\TrFrob{C}}
-    && \QCiso{B} \arrow[>->]{dr} \arrow{rr} \arrow{dd}%{\TrFrob{B}}
-    && \QCiso{A} \arrow[>->>]{dr} \arrow{dd}%{\TrFrob{A}}
-    \arrow{rr}  &   & 0 & \\
-\Hh^1(E^\bullet_{A}) \arrow[crossing over]{rr}  && \Hh^2(E^\bullet_{C}) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^2(E^\bullet_{B}) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^2(E^\bullet_{A}) \arrow{rr} \arrow[crossing over]{dd} &  & \Hh^3(E^\bullet_{C}) \\
-   0 \arrow{r}
-    & C(\Fq)^* \arrow[>->>]{dr} \arrow{rr} \arrow{dd}
-    && \arrow{dd} B(\Fq)^* \arrow[>->>]{dr} \arrow{rr} && A(\Fq)^* \arrow[>->>]{dr}  \arrow{dd}
-    \arrow{rr}&& 0 & \\
- %\Hh^2(\Weil{},\Hh^1({\bar A},\EEx)) \arrow{rr}
- && \Hh^1(\Weil{},\Hh^1(C,\EEx)) \arrow[crossing over]{dd} \arrow[crossing over]{rr}  && \Hh^1(\Weil{},\Hh^1(B,\EEx)) \arrow[crossing over]{dd} \arrow[crossing over]{rr} && \Hh^1(\Weil{},\Hh^1(A,\EEx)) \arrow[crossing over]{dd}  &  & %\Hh^0(\Weil{},\Hh^1({\bar C},\EEx))
- \\
-  & 0  && 0  &&  0  && & \\
-        &&  0 && 0 && 0 & & \\
-  \end{tikzcd}
-  \]
-}
-\end{center}
-\label{diagram}
-\end{table}
-
-\begin{corollary}\label{cor:exact}
-  If $G$ is a smooth, commutative group scheme over
-  $\Fq$ then pullback yields an exact sequence
-\[
-\Hh^1(E^\bullet_{G^0}) \to \QCiso{\pi_0(G)} \to \QCiso{G} \to \QCiso{G^0} \to 0
-\]
-of abelian groups.\todo{Pure speculation.}
-\end{corollary}
-
-\begin{proof}
-Really? Then does this make sense: $\Hh^3(E^\bullet_{\pi_0(G)}) =0$? Perhaps. $\Hh^3(\pi_0({\bar G})\rtimes \Weil{},\EEx)=0?$
-\end{proof}
-
 %sagemathcloud={"zoom_width":105}

### 2014-08-11 dictionary.tex
Changes to \S 3 in progress.
I need to putt this aside for the day, so I’m committing what I’ve got
so far.

@@
 We will identify $\bQC(G)$ with its image under $B_G$
-and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ is \emph{bounded}
+and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ \emph{descends to a bounded quasicharacter sheaf} on $G$
 if it is isomorphic to some $B_G(\qcs{L}_0, \mu_0)$.
@@
 
-In order to show that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is injective we need to recall some facts about Weil sheaves.
-%
-
-Now, let $\qcs{L}$ and $\qcs{L}'$ be quasicharacter sheaves on $G$ with $\trFrob{\qcs{L}} = \trFrob{\qcs{L}'}$.\todo{The rest of the proof is under construction.}
+Now, let $\qcs{L}$ and $\qcs{L}'$ be quasicharacter sheaves on $G$ with $\trFrob{\qcs{L}} = \trFrob{\qcs{L}'}$. We will show $\qcs{L} \iso \qcs{L}$.
+We have just seen that $\qcs{L}$ and $\qcs{L}'$ descend to bounded quasicharacter sheaves on $G$: $B_G(\qcs{L}_0,\mu_0) \iso \qcs{L}$ and $B_G(\qcs{L}'_0,\mu'_0) \iso \qcs{L}'$.
+Since bounded quasicharacter sheaves enjoy property \cite{laumon:87a}*{1.1.3.3}, \todo{Justify} it follows (arguing as in \cite{laumon:87a}*{1.1.2.1}) that there is an isomorphism $\qcs{L}_0 \to \qcs{L}'_0$.
+This morphism is compatible with $\mu_0$ and $\mu'_0$, \todo{Justify} hence a morphism of bounded quasicharacter sheaves.
+Its image under $B_G$ is the isomorphism $\qcs{L} \to \qcs{L}'$ of quasicharacter sheaves we seek.
 \end{proof}
@@
 
-Recall from Section~\ref{sec:finite} that
-a morphism $f : H\to G$ of group $\Fq$-schemes is a discrete isogeny
-if it is a finite, surjective \'etale morphism and
+We say that a morphism $f : H\to G$ of commutative group $\Fq$-schemes is a discrete isogeny if it is a finite, surjective \'etale morphism and
 the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f$ is trivial.
@@
 \begin{proposition}\label{prop:restriction}
-For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf
-$\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$.
-As a consequence, the restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
+%For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf
+%$\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$.
+%As a consequence, t
+The restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
 \end{proposition}

### 2014-08-15 dictionary.tex
I've added the insight using descent to Section 3.
But I’m not finished with Section 3.

@@
 
-\section{The main result}\label{sec:main}
-
-Having found $\QCiso{G}$ and $\Hom(\qcs{L},\qcs{L}')$ when $G$ is an etale commutative group scheme over $\Fq$, we now wish to find these for all commutative group scheme over $\Fq$.
-The next section introduces a concept that will be helpful in that regard.
+\section{Main results}\label{sec:main}
+
+In this section we find $\QCiso{G}$ and $\Hom(\qcs{L},\qcs{L}')$ for every smooth commutative group scheme over $\Fq$; note that we found these in Section~\ref{sec:etale} when $G$ is etale.
 
@@
 
-Let $G$ be a smooth commutative group scheme over $\Fq$.
-In this section we consider a class of quasicharacter sheaves on $G$ obtained by
-replacing the Weil sheaf $(\gqcs{L}, \phi)$ on $\bG$ in the definition of a quasicharacter
-sheaf with an $\ell$-adic local system on $G$ itself.
+%Let $G$ be a smooth commutative group scheme over $\Fq$.
+In this section we consider a category of sheaves on $G$ obtained by
+replacing the Weil sheaf $(\gqcs{L}, \phi)$ on $\bG$ in the definition of a quasicharacter sheaf with an $\ell$-adic local system on $G$ itself.
 
@@
 We will identify $\bQC(G)$ with its image under $B_G$
-and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ \emph{descends to a bounded quasicharacter sheaf} on $G$
+and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ is \emph{bounded} on $G$
 if it is isomorphic to some $B_G(\qcs{L}_0, \mu_0)$.
@@
 
+\subsection{Quasicharacter sheaves on connected commutative algebraic groups}\label{sec:connected}
+
 In general, $\bQC(G)$ is an essentially
 proper subcategory of $\QC(G)$. 
-However, if $G$ is connected, the categories are equivalent, as we now show.
-
-\begin{proposition}\label{prop:bounded_connected}
-If $G$ is a connected commutative algebraic group over $\Fq$ then
-$B_G : \bQC(G) \to \QC(G)$ is an equivalence of categories.
-\end{proposition}
+However, if $G$ is connected and of finite type, the categories are equivalent, as we now show.
+
+\begin{lemma}\label{lem:bounded_connected}
+If $G$ is a connected commutative algebraic group over $\Fq$ then every quasisharacter sheaf on $G$ is finite and $B_G : \bQC(G) \to \QC(G)$ is an equivalence of categories.
+\end{lemma}
 
@@
 
-\subsection{Objects, when $G$ is connected and of finite type}\label{sec:connected}
-
 \begin{proposition}\label{prop:obj_connected}
@@
  is an isomorphism of groups.
+ Moreover, for every quasicharacter sheaf $\qcs{L}$ on $G$, $\Aut(\qcs{L}) = 1$.
 \end{proposition}
@@
 \begin{proof}
-At its heart, this is Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields, as we now briefly recall from \citelist{\cite{deligne:SGA4.5}*{Sommes trig.}, \cite{laumon:87a}*{1.1.3}}.
-
-We begin by showing that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective.
-Let $\chi : G(\Fq) \to \EEx$ be a character.
-Let $\Lang : G \to G$ be the Lang isogeny for $G$.
-Set $\qcs{L}_0 = ( \Lang_* \EE)_{\chi^{-1}}$, the $\chi^{-1}$-isotypic component of the push-forward of the constant sheaf on $G$ along the Lang isogeny.
-Let $\gqcs{L}$ be the local system on $\bG$ obtained by pull-back along $\bG \to G$.
-Then $\gqcs{L}$ comes equipped with an isomorphism $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$.
-As explained in \cite{laumon:87a}*{1.1.3}, the trace of the Weil sheaf $(\gqcs{L},\phi)$ is $\chi$.
-The sheaf $\qcs{L}_0$ also comes equipped with an isomorphism 
-$\mu_0 : m^*\qcs{L}_0 \to \qcs{L}_0\boxtimes \qcs{L}_0$ 
-\cite{laumon:87a}*{1.1.3.2},
-which satisfies the analogue of \ref{QC.2} over $G$.
-Writing $\mu : \bm^* \gqcs{L}  \to \gqcs{L} \boxtimes \gqcs{L}$ for the isomorphism obtained by base change, it follows immediately that $\mu$ satisfies conditions \ref{QC.2} and \ref{QC.3}.
-Thus, $\qcs{L}\ceq (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$ with $\trFrob{\qcs{L}} = \chi$.
-It follows that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective.
-
-Now, let $\qcs{L}$ and $\qcs{L}'$ be quasicharacter sheaves on $G$ with $\trFrob{\qcs{L}} = \trFrob{\qcs{L}'}$. We will show $\qcs{L} \iso \qcs{L}$.
-We have just seen that $\qcs{L}$ and $\qcs{L}'$ descend to bounded quasicharacter sheaves on $G$: $B_G(\qcs{L}_0,\mu_0) \iso \qcs{L}$ and $B_G(\qcs{L}'_0,\mu'_0) \iso \qcs{L}'$.
-Since bounded quasicharacter sheaves enjoy property \cite{laumon:87a}*{1.1.3.3}, \todo{Justify} it follows (arguing as in \cite{laumon:87a}*{1.1.2.1}) that there is an isomorphism $\qcs{L}_0 \to \qcs{L}'_0$.
-This morphism is compatible with $\mu_0$ and $\mu'_0$, \todo{Justify} hence a morphism of bounded quasicharacter sheaves.
-Its image under $B_G$ is the isomorphism $\qcs{L} \to \qcs{L}'$ of quasicharacter sheaves we seek.
-\end{proof}
-
-In the introduction to this paper we noted that, when working with connected commutative algebraic groups over finite fields, Deligne's dictionary can be described using Weil sheaves $\qcs{L}$ for which there exists an isomorphism $m^* \qcs{L} \iso \qcs{L} \boxtimes\qcs{L}$, without keeping track of the isomorphism.
-\todo{rephrase objective of section}
-In this section use that perspective to find a perfect dictionary between flabby quasicharacter sheaves on $G$ and characters of $G(\Fq)$.
+In Lemma~\ref{lem:bounded_connected} we saw that every quasicharacter sheaf on $G$ descends to bounded quasicharacter sheaf on $G$. 
+From here, Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields \citelist{\cite{deligne:SGA4.5}*{Sommes trig.}, \cite{laumon:87a}*{1.1.3}}  gives us all we need, as we briefly recall.
+The key observation is that, by descent theory, pull-back by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{L}$ is $\trFrob{\qcs{L}}^{-1}$ for every bounded quasicharacter sheaf $\qcs{L}$ on $G$.
+Note that since $V$ is $1$-dimensional, the choice of $V \to V\otimes V$ is exactly the choice of an isomorphism $V\iso \EE$.
+Using the equivalence given by $\Lang^*$, it follows that if $\Lang^*\qcs{L} = V$ with character $\psi$ and isomorphism $\mu : V\to V\otimes V$ then $\Aut(\qcs{L})$ is the group of automorphisms of $\rho : V\to V$ for which
+\[
+\begin{tikzcd}
+\arrow{d}{\mu} V \arrow{r}{\rho} & V\arrow{d}{\mu}\\
+V\otimes V \arrow{r}{\rho\otimes \rho} & V\otimes V
+\end{tikzcd}
+\]
+commutes. 
+Since the only such isomorphism $\rho$ is $\id_V$, it follows that $\Aut(\qcs{L}) = 1$.
+\end{proof}
+
+We have just seen that, on a connected commutative algebraic group $G$ over $\Fq$, the category of quasicharacters $\qcs{L}$ on $G$ is equivalent to the category of characters $\psi$ of $G(\Fq)$.
+This can be used to understand all quasicharacter sheaves on such $G$ using central extensions of the form
+\[
+\]
+Kamgarpour
+
+We have also just seen moreover, that the equality $m^*\psi = \psi \boxtimes \psi$ determines the isomorphism $\mu : \qcs{L} \to \qcs{L}\boxtimes\qcs{L}$ which is part of the data of the quasicharacter sheaf $\qcs{L}$.
+Means leads us back to a more common perspective on the function--sheaf dictionary in which one considers $1$-dimensional local systems $\qcs{L}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{L} \iso \qcs{L} \boxtimes\qcs{L}$, or sometimes $1$-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
+%In the introduction to this paper we noted that, when working with connected commutative algebraic groups over finite fields, Deligne's dictionary can be described using Weil sheaves $\qcs{L}$ for which there exists an isomorphism $m^* \qcs{L} \iso \qcs{L} \boxtimes\qcs{L}$, without keeping track of the isomorphism.
+We have seen that the category of quasicharacter sheaves on commutative smooth group schemes over finite fields specializes to  
+that notion when $G$ is connected and of finite type.
+However, as we have already seen in Section~\ref{sec:etale}, that notion is not up to the not appropriate if one wishes to extend the dictionary to commutative smooth group schemes over finite fields.
 

### 2014-08-16 dictionary.tex
Used etale descent to treat finite quasicharacter sheaves.

@@
 \begin{definition}
-Let $\bQC(G)$ be the category of pairs $(\qcs{L}_0,\mu_0)$
-where $\qcs{L}_0$ an $\ell$-adic local system on $G$ of rank~one,
-equipped with an isomorphism $\mu_0 : m^* \qcs{L}_0 \to \qcs{L}_0 \boxtimes \qcs{L}_0$
+Let $\bQC(G)$ be the category of pairs $(\qcs{E},\mu_\qcs{E})$
+where $\qcs{E}$ an $\ell$-adic local system on $G$ of rank~one,
+equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes \qcs{E}$
 satisfying the analogue of \ref{QC.1} on $G$;
@@
  Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$.
- Then $\qcs{L}_0$ is an $\ell$-adic constructible sheaf on $G$ and
- $b_G^* \qcs{L}_0$ comes equipped with an isomorphism
- $\phi : \Frob{G}^* b_G^*\qcs{L}_0 \to b_G^* \qcs{L}_0$.
- Moreover, the functor $\qcs{L}_0 \mapsto (b_G^* \qcs{L}_0,\phi)$
+ Let $(\qcs{E},\mu_\qcs{E})$ be a bounded quasicharacter sheaf on $G$.
+ Then $\qcs{E}$ is an $\ell$-adic constructible sheaf on $G$ and
+ $b_G^* \qcs{E}$ comes equipped with an isomorphism
+ $\phi_\qcs{E} : \Frob{G}^* b_G^*\qcs{E} \to b_G^* \qcs{E}$.
+ The functor $\qcs{E} \mapsto (b_G^* \qcs{E},\phi_\qcs{E})$
  from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
@@
  This functor preserves local constancy, so takes local systems to local systems.
- Set $\mu \ceq b_{G\times G}^*\mu_0$; clearly, this satisfies \ref{QC.2}
- with $b_G^*\qcs{L}_0$ playing the role of $\gqcs{L}$.
- Moreover, $\phi$ is compatible with $\mu$ in the sense of \ref{QC.3}.
- This construction defines the functor $B_G : (\qcs{L}_0,\mu_0) \mapsto (b_G^*\qcs{L}_0,b_{G\times G}^*\mu_0, \phi)$
+ Set $\mu \ceq b_{G\times G}^*\mu_\qcs{E}$; clearly, this satisfies \ref{QC.2}
+ with $b_G^*\qcs{E}$ playing the role of $\gqcs{L}$.
+ Moreover, $\phi_\qcs{E}$ is compatible with $\mu_\qcs{E}$ in the sense of \ref{QC.3}.
+ This construction defines the functor $B_G : (\qcs{E},\mu_\qcs{E}) \mapsto (b_G^*\qcs{E},b_{G\times G}^*\mu_\qcs{E}, \phi_\qcs{E})$
  and also shows that it is full and faithful.
@@
 and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ is \emph{bounded} on $G$
-if it is isomorphic to some $B_G(\qcs{L}_0, \mu_0)$.
+if it is isomorphic to some $B_G(\qcs{E}, \mu_\qcs{E})$.
 We will see in Corollary~\ref{cor:bounded-and-finite} that bounded quasicharacter sheaves are exactly quasicharacter sheaves with bounded Trace of Frobenius.\todo{Check this, later.}
@@
   determined by this $\ell$-adic character of $\pi_1(G,\bg)$.
-  Then $b_G^*\qcs{L}_0 \iso \gqcs{L}$.
+  Then $b_G^*\qcs{E} \iso \gqcs{L}$.
 
@@
   $
-  b_{G\times G}^* : \Hom(m^*\qcs{L}_0,\qcs{L}_0\boxtimes\qcs{L}_0) \to \Hom({\bar m}^*\gqcs{L},\gqcs{L}\boxtimes\gqcs{L})
+  b_{G\times G}^* : \Hom(m^*\qcs{E},\qcs{E}\boxtimes\qcs{E}) \to \Hom({\bar m}^*\gqcs{L},\gqcs{L}\boxtimes\gqcs{L})
   $
@@
   in which $\ell$-adic local systems sit as full subcategories).
-  Let $\mu_0 : m^*\qcs{L}_0 \to \qcs{L}_0\boxtimes\qcs{L}_0$ be the isomorphism matching
+  Let $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ be the isomorphism matching
   $\mu : {\bar m}^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$,
   the latter appearing in the definition of $\qcs{L}$.
-  Then, as in Section~\ref{sec:bounded}, $(\qcs{L}_0,\mu_0)$ is an object in $\bQC(G)$
-  and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{L}_0,b_{G\times G}^*\mu_0)$ in $\QC(G)$.
+  Then, as in Section~\ref{sec:bounded}, $(\qcs{E},\mu_\qcs{E})$ is an object in $\bQC(G)$
+  and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{E},b_{G\times G}^*\mu_\qcs{E})$ in $\QC(G)$.
   Thus, the full and faithful functor $B_G : \bQC(G) \to \QC(G)$ from Section~\ref{sec:bounded}
@@
 
-\begin{proposition}\label{prop:obj_connected}
+\begin{proposition}\label{prop:connected}
  If $G$ is a connected, commutative algebraic group over $\Fq$ then
@@
 \begin{proof}
-In Lemma~\ref{lem:bounded_connected} we saw that every quasicharacter sheaf on $G$ descends to bounded quasicharacter sheaf on $G$. 
+In Lemma~\ref{lem:bounded_connected} we saw that every quasicharacter sheaf $\qcs{L}$ on $G$ descends to bounded quasicharacter sheaf $\qcs{E}$ on $G$.
+Since the functor $B_G : \bQC(G) \to \QC(G)$ is full and faithful, $\Aut(\qcs{L}) = \Aut(\qcs{E})$.
 From here, Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields \citelist{\cite{deligne:SGA4.5}*{Sommes trig.}, \cite{laumon:87a}*{1.1.3}}  gives us all we need, as we briefly recall.
-The key observation is that, by descent theory, pull-back by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{L}$ is $\trFrob{\qcs{L}}^{-1}$ for every bounded quasicharacter sheaf $\qcs{L}$ on $G$.
+The key observation is that, by etale descent, pull-back by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every bounded quasicharacter sheaf $\qcs{E}$ on $G$.
 Note that since $V$ is $1$-dimensional, the choice of $V \to V\otimes V$ is exactly the choice of an isomorphism $V\iso \EE$.
-Using the equivalence given by $\Lang^*$, it follows that if $\Lang^*\qcs{L} = V$ with character $\psi$ and isomorphism $\mu : V\to V\otimes V$ then $\Aut(\qcs{L})$ is the group of automorphisms of $\rho : V\to V$ for which
+Using the equivalence given by $\Lang^*$, if $\Lang^*\qcs{E} = V$ with character $\psi$ and isomorphism $V\to V\otimes V$ then 
+$\qcs{E} \iso (\Lang_* V)_\psi$, the $\psi$-isotypic component of the push-forward $\Lang_* V$ of the constand sheaf $V$ on $G$, equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes\qcs{E}$ determined by $V\to V\otimes V$.
+Moreover, $\Aut(\qcs{E})$ is the group of automorphisms of $\rho : V\to V$ for which 
 \[
 \begin{tikzcd}
-\arrow{d}{\mu} V \arrow{r}{\rho} & V\arrow{d}{\mu}\\
+\arrow{d}{} V \arrow{r}{\rho} & V\arrow{d}{}\\
 V\otimes V \arrow{r}{\rho\otimes \rho} & V\otimes V
@@
 commutes. 
-Since the only such isomorphism $\rho$ is $\id_V$, it follows that $\Aut(\qcs{L}) = 1$.
-\end{proof}
-
-We have just seen that, on a connected commutative algebraic group $G$ over $\Fq$, the category of quasicharacters $\qcs{L}$ on $G$ is equivalent to the category of characters $\psi$ of $G(\Fq)$.
-This can be used to understand all quasicharacter sheaves on such $G$ using central extensions of the form
-\[
-\]
-Kamgarpour
-
-We have also just seen moreover, that the equality $m^*\psi = \psi \boxtimes \psi$ determines the isomorphism $\mu : \qcs{L} \to \qcs{L}\boxtimes\qcs{L}$ which is part of the data of the quasicharacter sheaf $\qcs{L}$.
-Means leads us back to a more common perspective on the function--sheaf dictionary in which one considers $1$-dimensional local systems $\qcs{L}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{L} \iso \qcs{L} \boxtimes\qcs{L}$, or sometimes $1$-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
+Since the only such isomorphism $\rho$ is $\id_V$, it follows that $\Aut(\qcs{E}) = 1$, completing the proof.
+\end{proof}
+
+We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of quasicharacters $\qcs{L}$ on $G$ is equivalent to the category of characters $\psi$ of $G(\Fq)$.
+We have also just seen if the character of $\Lang^*\qcs{L}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu : \qcs{L} \to \qcs{L}\boxtimes\qcs{L}$ which is part of the data of the quasicharacter sheaf $\qcs{L}$.
+That leads to a perspective on the function--sheaf dictionary common in the literature in which one considers $1$-dimensional local systems $\qcs{L}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{L} \iso \qcs{L} \boxtimes\qcs{L}$ \cite{kamgarpour:09a}*{Introduction}, or sometimes, $1$-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
+
 %In the introduction to this paper we noted that, when working with connected commutative algebraic groups over finite fields, Deligne's dictionary can be described using Weil sheaves $\qcs{L}$ for which there exists an isomorphism $m^* \qcs{L} \iso \qcs{L} \boxtimes\qcs{L}$, without keeping track of the isomorphism.
-We have seen that the category of quasicharacter sheaves on commutative smooth group schemes over finite fields specializes to  
-that notion when $G$ is connected and of finite type.
-However, as we have already seen in Section~\ref{sec:etale}, that notion is not up to the not appropriate if one wishes to extend the dictionary to commutative smooth group schemes over finite fields.
+
+Although the category of quasicharacter sheaves on commutative smooth group schemes $G$ over finite fields does specialize to  
+that common notion when $G$ is connected and of finite type, that notion is not appropriate if one wishes to extend the dictionary to commutative smooth group schemes over finite fields. 
+In particular, as we have already seen in Section~\ref{sec:etale}, for a given quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ there may be a different isomorphism $\mu' : \bm^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$ for which $\qcs{L}'=(\gqcs{L},\mu',\phi)$ is also a quasicharacter sheaf on $G$, not isomorphic to $\qcs{L}$.
+Indeed, Proposition~\ref{prop:etale-iso} shows that $\Hh^0(\Weil{},\Hh^2(\bG,\EEx))$ measures the possibilities for such $\mu'$ when $G$ is etale.
+We will see later in this section that, for any smooth commutative group scheme $G$, the possibilities for such $\mu'$ are measured by $\Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx))$.
+
+\subsection{Finite quasicharacter sheaves}
+
+In this section we return to the case when $G$ is any smooth commutative group scheme over $\Fq$ and describe a class of quasicharacter sheaves on $G$ that will play a role in Section~\ref{sec:restriction}.
+
+A finite, etale, surjective morphism $H\to G$ of smooth group schemes over $\Fq$ for which the action of $\Gal(\bFq/\Fq)$ on the kernel is trivial is called a {\it discrete isogeny}.
+
+\begin{proposition}\label{prop:finite}
+Let $f: H \to G$ be a discrete isogeny; let $A$ be the kernel of $f$.
+Let $\psi : A \to \EEx$ be a character.
+Then $(f_* \EE)_\psi$ (the $\psi$-isotypic component of $f_*\EE$) is a bounded quasicharacter on $G$.
+\end{proposition}
+
+\begin{proof}
+Let $f$, $A$ and $\psi$ be as above; set $\qcs{E} = (f_! \EE)_\psi$.
+It is clear that $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank one.
+We must show that comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
+To do this we may use etale descent exactly as in the proof of Proposition~\ref{prop:connected}. 
+Pull-back along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$. 
+In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $\EE$ on $H$ with character $\psi$.
+Since $f$ is a morphism of group schemes, the functor $f^*$ defines $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ from the canonical isomorphism $m^*\psi \iso \psi \boxtimes\psi$.
+\end{proof}
 
@@
   descends to a diagram of $\Fq$-schemes since the $\bFq$-points of
-  the objects come equipped with continuous $\Gamma$-actions, and the
+  the objects come equipped with continuous $\Gamma$-actions and the
   morphisms are $\Gamma$-equivariant.
@@
   By Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}, every
-  quasicharacter sheaf on $G^0$ is isomorphic to a
-  finite quasicharacter sheaf on $G^0$,
-  so to prove the proposition it suffices to show that every
-  finite quasicharacter sheaf on $G^0$ extends to a finite quasicharacter sheaf on $G$.
-
- Let $(\pi,\psi)$ be a finite quasicharacter sheaf on $G^0$.
+  quasicharacter sheaf on $G^0$ is isomorphic to $(\pi_! \EE)\psi$ for some discrete isogeny $\pi : B \to G^0$ and character $\psi : \ker \pi \to \EEx$.
+  So to prove the proposition it suffices to show that $(\pi_! \EE)\psi$ extends to a quasicharacter sheaf on $G$.
+%
+ %Let $(\pi,\psi)$ be a finite quasicharacter sheaf on $G^0$.
  By Lemma~\ref{lemma:ext}, there is an extension of the
@@
  such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
- Then $(f,\psi)$ is a finite quasicharacter sheaf on $G$ and
- $(f,\psi)\vert_{G^0} \iso (\pi,\psi)$.
+ Then $(\pi_! \EE)\psi$ is a quasicharacter sheaf on $G$ and
+ $(\pi_! \EE)\psi\vert_{G^0} \iso (\pi_! \EE)\psi$.
 \end{proof}
@@
 \section{Application to \texorpdfstring{$p$}{p}-adic tori}
-
-\subsection{Finite implies Bounded}
-
-In this section we show that $\fQC(G)$ is a full subcategory of $\bQC(G)$.
-To prepare for that result, we need the next two lemmas.
-
-\begin{lemma}\label{lemma:finite-pullback}
-Let $g : J \to G$ be a morphism of smooth groups schemes over $\Fq$.
-Let $f_g : H\times_G J\to J$
-be the pullback of $f$ along $g$ and define $\psi_g : \ker f_g \to \Aut(V)$ as in the diagram below:
-\[
-\begin{tikzcd}
-V & \Aut(V) & \arrow[swap]{l}{\psi} \ker f \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-  &  & \arrow[dashed]{ul}{\psi_g} \arrow[swap]{u}{(g_f)\vert_{\ker f_g}} \ker f_g \arrow[hook]{r}
-  & \arrow[swap]{u}{g_f} H\times_G J \arrow{r}{f_g} & \arrow{u}{g} J.
-\end{tikzcd}
-\]
-Then $(f,\psi) \mapsto (f_g,\psi_g)$
-defines a monomial functor $g^* : C(G)[W^{-1}] \to C(J)[W^{-1}]$.
-\end{lemma}
-
-\begin{proof}
-The key point is that pullback along $g$ takes discrete isogenies to discrete isogenies,
-and maps over $G$ to maps over $J$, as pictured below.
-\[
-\begin{tikzcd}[row sep={{{{40,between origins}}}},column sep={{{{50,between origins}}}}]
-%\ V \arrow{dd}{T} &
-\Aut(V) && \arrow[swap]{ll}{\psi} \ker f \arrow[hook]{rr} \arrow[leftarrow]{dd} && H \arrow{rr}{f} \arrow[leftarrow]{dd} && \arrow[equal]{dd} G\\
-% &
-& \arrow{ul} \ker f\times_G J \arrow{ur} \arrow[hook, crossing over]{rr} && H\times_G J \arrow{ur} \arrow[crossing over]{rr} && J \arrow[swap]{ur}{g} & \\
-%V' &
- \Aut(V') && \arrow[swap,pos=0.25]{ll}{\psi'} \ker f'  \arrow[hook]{rr}
-&& H' \arrow[pos=0.25]{rr}{f'} && G\\
-% &
- & \arrow{ul} \ker f'\times_G J \arrow[crossing over]{uu} \arrow{ur} \arrow[hook]{rr}
- && \arrow[crossing over]{uu} H'\times_G J \arrow{ur} \arrow{rr} && \arrow[equals, crossing over]{uu} J \arrow[swap]{ur}{g} &
-\end{tikzcd}
-\]
-%In this form we could treat $g^*$ as a functor $C(J)\to C(G)$,
-%were it not for the fact that pullback is defined only up to isomorphism.
-%In the localized categories, this ambiguity disappears.
-\end{proof}
-
-\begin{lemma}\label{lemma:finite-iso}
-Each finite quasicharacter sheaf $(f,\psi)$ in $\fQC(G)$ determines a
-canonical isomorphism $\mu(f,\psi) : m^*(f,\psi) \to (f,\psi)\boxtimes(f,\psi)$ in $\fQC(G\times G)$.
- \end{lemma}
-
-\begin{proof}
-We will prove the proposition by finding a weak isomorphism
-$m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ in $C_1(G\times G)$
-and showing that, after passing from $C_1(G\times G)$ to
-$\fQC(G\times G)$, the resulting isomorphism,
-denoted by $\mu(f,\psi)$, is canonically determined by $(f,\psi)$.
-
-Set $H_m \ceq H\times_G(G\times G)$,
-write $f_m : H_m \to G \times G$ for the pullback of $f$ to $H_m$,
-and let $A$ and $A_m$ be the kernels of $f$ and $f_m$ respectively.  Consider the diagram of Lemma~\ref{lemma:finite-pullback}:
-\[
-\begin{tikzcd}[column sep=40]
-V & \Aut(V) & \arrow[swap]{l}{\psi} A \arrow[hook]{r} & H \arrow{r}{f} &  G\\
-  &  & \arrow[dashed]{ul}{\psi_m} \arrow[swap]{u}{(m_f)\vert_{A_m}} A_m \arrow[hook]{r}
-  & \arrow[swap]{u}{m_f} H_m \arrow{r}{f_m} & \arrow{u}{m} G\times G.
-\end{tikzcd}
-\]
-We have $(f,\psi) \boxtimes (f,\psi) = (f\times f, \psi\otimes \psi)$.
-Since $f\circ m_H = m \circ (f\times f)$, the universal property of pullback gives
-a unique $\theta : H\times H \to H_m$ making the following commute.
-\[
-\begin{tikzcd}[row sep=20,column sep=8]
-\ & V \arrow{dd}{T} && \Aut(V) && A \arrow[hook]{rr} \arrow[swap]{ll}{\psi} &&  H \arrow{rr}{f} && G\\
- && && \arrow{ul}{\psi_m} A_m  \arrow[hook]{rr} \arrow{ur} && H_m \arrow[pos=0.3]{ur}{m_f} \arrow[swap, pos=0.8]{rr}{f_m}
- && G \times G \arrow[equal]{dr} \arrow[pos=0.42]{ur}{m} & \\
-& V\otimes V && \Aut(V\otimes V) && \arrow[swap]{ll}{\psi \otimes \psi} \arrow[dashed,swap,pos=0.3]{ul}{\theta\vert_{A\times A}} A\times A \arrow[hook]{rr}
-&& \arrow[dashed,swap]{ul}{\theta} \arrow[crossing over,swap,pos=0.7]{uu}{m_H} H\times H \arrow{rr}{f\times f} && G\times G
-\end{tikzcd}
-\]
-Choose a basis $\{ v \}$ for $V$; then $\{ v\otimes v \}$ is a basis for $V\otimes V$.
-Let $T : V \to V\otimes V$ be the linear transformation taking $v$ to $v\otimes v$. Then the lower part of this
-diagram defines a weak isomorphism $(\theta,T): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$  in $C_1(G\times G)$.
-%
-While $\theta$ was canonical, $T$ was not, as it depended on the choice of a basis for $V$.
-However, after passing from $C_1(G\times G)$ to $\fQC(G\times G)$, the resulting isomorphism 
-$\mu(f,\psi): m^*(f,\psi) \to (f,\psi)\boxtimes (f,\psi)$ in $\fQC(G\times G)$ is independent of the choice of basis for $V$.
- \end{proof}
-
-\begin{proposition}\label{prop:bounded}
- $\fQC(G)$ is a full subcategory of $\bQC(G)$.
-\end{proposition}
-
-\begin{proof}
- To prove the proposition we exhibit a full and faithful monoidal functor $L_G : \fQC(G) \to \bQC(G)$.
-
- If $V$ is a finite-dimensional $\EE$-vector space then we write $V_H$ for the constant sheaf $V$ on $H$.
-If $(f,\psi)$ is a finite quasicharacter on $G$ where $\psi$ is a representation of $\ker f$ on $V$,
-let $L(f,\psi)$ be the local system on $G$ given by the $\psi$-isotypic component of the local system $f_* V_H$ on $G$.
- We may identify the stalk $(f_* V_H)_{\bar g}$ of $f_* V_H$ at a geometric point ${\bar g}$ on $G$
- with the $\EE$-vector space $\Hom_\text{set}(\abs{f^{-1}({\bar g})},V)$
- and the stalk $L(f,\psi)_{\bar g}$ of $L(f,\psi)$ at a geometric point ${\bar g}$ on $G$
- with the $\EE$-vector space consisting of those functions $s: \abs{f^{-1}({\bar g})} \to V$ such that
- $s(a\cdot {\bar h}) = \psi(a)(s({\bar h}))$ for all $a\in \ker f$ and for all ${\bar h} \in f^{-1}({\bar g})$.
-
- For any map $(g,T)$ in $C(G)$, let $L(g,T) : L(f,\psi) \to L(f',\psi')$ be the homomorphism of local systems defined
- by $s \mapsto s' \ceq T\circ s\circ g$.
- This construction defines a full monoidal functor $L$ from $C(G)$ to the category $\Loc(G)$ of local systems on $G$ that
- commutes with pullback along any morphism of $\QC$-schemes,
- as defined using Lemma~\ref{lemma:finite-pullback}.
- Moreover, since $L(f,T)$ is an isomorphism of local systems
- if and only if $(f,T)$ is a weak isomorphism,
- the full functor $L : C(G) \to \Loc(G)$ factors through the localization functor $C(G) \to C(G)[W^{-1}]$
- to define a full and faithful functor $L_{W} : C(G)[W^{-1}] \to \Loc(G)$;
- see \cite{kashiwara-schapira:CatgoriesSheaves}*{Exercise 7.5}.
-
- By Lemma~\ref{lemma:finite-iso}, each $(f,\psi) \in \fQC(G)$ canonically determines
- an isomorphism
- \[
- \mu(f,\psi) : m^*(f,\psi) \to (f,\psi) \boxtimes (f,\psi)
- \]
- in $\fQC(G\times G)$.
- It follows immediately that the functor
- \[
- L_G  \ceq  L_{W}\vert_{\fQC(G)} : \fQC(G) \to \bQC(G),
- \]
- given on objects by $(f,\psi) \mapsto (L(f,\psi), L_{W}(\mu(f,\psi)))$,
- is a full and faithful monoidal functor, completing the proof.
-\end{proof}
 

### 2014-08-16 dictionary.tex
Made a home for the injective part of the component group sequence

@@
 
-\subsection{The component group sequence} \label{sec:restriction}
+\subsection{Restriction to the identity component} \label{sec:restriction}
 
@@
  such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
- Then $(\pi_! \EE)\psi$ is a quasicharacter sheaf on $G$ and
- $(\pi_! \EE)\psi\vert_{G^0} \iso (\pi_! \EE)\psi$.
+ Then $(f_! \EE)\psi$ is a quasicharacter sheaf on $G$ and
+ $(f_! \EE)\psi\vert_{G^0} \iso (\pi_! \EE)\psi$.
+\end{proof}
+
+\subsection{The component group sequence} \label{sec:component}
+
+\begin{lemma}\label{lem:extension}
+The group homomorphism $\pi_0^*: \QCiso{\pi_0(G)} \to \QCiso{G}$ is injective.
+\end{lemma}
+\begin{proof}
 \end{proof}
@@
 \begin{proof}
-The sequence is exact at $\QCiso{G^0}$ by Proposition~\ref{prop:restriction},
-so here we show that it is also exact at $\QCiso{G}$.
+The sequence is exact at $\QCiso{G^0}$ by Proposition~\ref{prop:restriction}
+and exact at $\QCiso{\pi_0(G)}$ by Lemma~\ref{lem:extension}.
+Here we show that it is also exact at $\QCiso{G}$.
 First note that $\iota_0^* \circ \pi_0^*$ is trivial by Proposition~\ref{prop:pullback}.

### 2014-08-17 dictionary.tex
Except for Aut(L), Section 3 is complete.

@@
 If $\qcs{L}$ and $\qcs{L}'$ are quasicharacter sheaves on $G$ then
-every $\alpha\in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism. Moreover, the trace map induces an isomorphism of groups
+every $\rho\in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism. Moreover, the trace map induces an isomorphism of groups
 \[
@@
  is an isomorphism of groups.
- Moreover, for every quasicharacter sheaf $\qcs{L}$ on $G$, $\Aut(\qcs{L}) = 1$.
+ Moreover, for every quasicharacter sheaf $\qcs{L}$ on $G$, $\Aut(\qcs{L}) = 1$
+ and every $\rho \in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism.
  \end{proposition}
@@
 Since the only such isomorphism $\rho$ is $\id_V$, it follows that $\Aut(\qcs{E}) = 1$, completing the proof.
+For the last part of the proposition, argue as in the analogous part of Proposition~\ref{prop:mor_etale}.
 \end{proof}
@@
 
-Although the category of quasicharacter sheaves on commutative smooth group schemes $G$ over finite fields does specialize to  
-that common notion when $G$ is connected and of finite type, that notion is not appropriate if one wishes to extend the dictionary to commutative smooth group schemes over finite fields. 
+Although the category of quasicharacter sheaves on commutative smooth group schemes $G$ over finite fields does specialize to that common notion when $G$ is connected and of finite type, that notion is not appropriate if one wishes to extend the dictionary to commutative smooth group schemes over finite fields.
 In particular, as we have already seen in Section~\ref{sec:etale}, for a given quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ there may be a different isomorphism $\mu' : \bm^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$ for which $\qcs{L}'=(\gqcs{L},\mu',\phi)$ is also a quasicharacter sheaf on $G$, not isomorphic to $\qcs{L}$.
@@
 \begin{proof}
+Let $\qcs{L}$ be a quasicharacter sheaf on $\pi_0(G)$ and let $\rho : \pi_0^*\qcs{L} \to (\EE)_{G}$ be an isomorphism in $\QC(G)$.
+For each $x\in \pi_0(\bG)$, the restriction $\pi_0^*\gqcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gqcs{L}_x)_{\bG^x}$ so the isomorphism $\rho_{\bG^x} : (\gqcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\rho_x : \gqcs{L}_x \to (\EE)_x$.
+The collection $\{ \rho_x \tq x\in \pi_0(\bG) \}$ determines an isomorphism $\qcs{L} \to (\EE)_{\pi_0(G)}$  in $\QC(\pi_0(G))$.
 \end{proof}
@@
 is surjective with kernel isomorphic to $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$.
+ Moreover, $\Aut(\qcs{L}) = \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and every $\rho \in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism, for all quasicharacter sheaves $\qcs{L}$ and $\qcs{L}'$ on $G$.
 \end{theorem}
@@
 
-%We now turn our attention $\lTrFrob{G}: \lQCiso{G}  \to G(\Fq)^*$ is an isomorphism.
-%First, note that $\lTrFrob{G}$ is surjective because $\TrFrob{G}$ is surjective.
-%We will now show that the kernel of $\lTrFrob{G}$ is trivial.
-
-%First, suppose $G$ is etale.
-%Let $(\gqcs{E},\phi')$ be a quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{E},\phi')}=1$.
-%Let $\qcs{E} = (\gqcs{E},\mu,\phi')$ be a quasicharacter sheaf.
-%By Proposition~\ref{prop:etale-iso}, $S_G(\qcs{E}) = [\alpha\oplus 0]$ for some $\alpha \in Z^0(\Weil{},Z^2({\bar G},\EEx))$
-%corresponding to a choice $\{ v_x \in \gqcs{E}_x^\times \tq x\in {\bar C}\}$.
-%Let $a\in Z^2({\bar G},\EEx)$ be the multiplicative version of $\alpha$
-%and let $\mu'$ be the indexed set of isomorphisms $\mu'_{x,y} : \EE \to \EE\otimes \EE$ defined by $1 \mapsto a(x,y) 1 \otimes 1$.
-%Then $(\EE,\mu', 1)$ is a quasicharacter sheaf the isomorphisms $\gqcs{E}_x \to \EE$ defined by $v_x \mapsto 1$ gives an isomorphism $(\gqcs{E},\mu,\phi')\to ((\EE)_{\bar C},\mu', 1)$ in $\QC(G)$.
-%It follows that $(\gqcs{E},\phi')\iso ((\EE)_{\bar G},1)$ in $\lQC(G)$, so $\lTrFrob{G}$ is injective.
-%This completes the proof of Theorem~\ref{thm:snake} in the case that $G$ is etale.
-
-%Now let $G$ be arbitrary
-%and let $(\gqcs{L},\phi)$ be a flabby quasicharacter sheaf on $G$ with $\trFrob{(\gqcs{L},\phi)}=1$.
-%Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf.
-%We saw above that $\ker \TrFrob{\pi_0(G)}\to \TrFrob{G}$ is surjective in this case,
-%so $\qcs{L} = \pi_0^*\qcs{E}$ for some $\qcs{E}\in \QC(\pi_0(G))$.
-%Since $\trFrob{\qcs{L}}(g) = \trFrob{\qcs{E}}(\pi_0(g))$ and since $\pi_0 : G(\Fq) \to \pi_0(G)(\Fq)$ is surjective, $\trFrob{\qcs{E}}=1$.
-%But now $\qcs{E} \iso ((\EE)_{\pi_0({\bar G})},\mu', 1)$ by the paragraph above.
-%So $\qcs{L} = \pi_0^*\qcs{E} \iso \pi_0^*((\EE)_{\pi_0({\bar G})},\mu', 1) = ((\EE)_{\bar G},\pi_0^*\mu', \pi_0^*1)$ in $\QC(G)$.
-%It follows that $(\gqcs{L},\phi) \iso ((\EE)_{\bar G},1)$ in $\lQC(G)$.
-%This completes the proof of Theorem~\ref{thm:snake}.
-\end{proof}
-
-%\begin{corollary}\label{cor:exact}
-%  If $G$ is a smooth, commutative group scheme over
-%  $\Fq$ then pullback yields an exact sequence
-%\[
-%0 \to \lQCiso{\pi_0(G)} \to \lQCiso{G} \to \lQCiso{G^0} \to 0
-%\]
-%of abelian groups.
-%\end{corollary}
-
-%\begin{proof}
-%Argue as in the first paragraph in the proof of Theorem~\ref{thm:snake},
-%using the category $\lQC(G)$ in place of $\QC(G)$.
-%\end{proof}
-
-\subsection{Morphisms, in the general case}
+ (. . . where $G(\bFq)$ is given the topology of the espace étalé of the sheaf of sections of $G$.)
+ \todo{Still under construction: $\Aut(\qcs{L})$.}
+
+ For the last part of the proposition, argue as in the analogous part of Proposition~\ref{prop:mor_etale}.
+\end{proof}
 

### 2014-08-17 dictionary.tex
Cleaning up some fragments after \end{document}

@@
 
+\begin{table}[ht]
+\caption{A big diagram}
+\begin{center}
+{\smaller\smaller\smaller
+    \[
+  \begin{tikzcd}[row sep=20, column sep=3]
+&   &  0 \arrow{dd} && 0 \arrow{dd} && 0\arrow{dd} & \\
+& &&  0 \arrow[crossing over]{dd} && 0 \arrow[crossing over]{dd} && 0\arrow{dd} & & \\
+&   {}& \ker \TrFrob{C} \arrow[->>]{rr} \arrow[>->>]{dr} \arrow{dd} && \arrow{dd} \ker \TrFrob{B} \arrow{rr} \arrow[>->]{dr}  && \ker \TrFrob{A}=0 \arrow[>->>]{dr} \arrow{dd} \arrow{rr} && 0 & \\
+& && \Hh^0(\Weil{},\Hh^2(C,\EEx)) \arrow[crossing over,->>]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(B,\EEx)) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(A,\EEx)) \arrow[crossing over]{dd}  &  &  \\
+0  \arrow{rr} & & \QCiso{C} \arrow[>->>]{dr}\arrow{rr} \arrow{dd}%{\TrFrob{C}}
+    && \QCiso{B} \arrow[>->]{dr} \arrow{rr} \arrow{dd}%{\TrFrob{B}}
+    && \QCiso{A} \arrow[>->>]{dr} \arrow{dd}%{\TrFrob{A}}
+    \arrow{rr}  &   & 0 & \\
+& \Hh^1(E^\bullet_{A}) \arrow[crossing over]{rr}  && \Hh^2(E^\bullet_{C}) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^2(E^\bullet_{B}) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^2(E^\bullet_{A}) \arrow{rr} \arrow[crossing over]{dd} &  & \Hh^3(E^\bullet_{C}) \\
+0  \arrow{rr} & & C(\Fq)^* \arrow[>->>]{dr} \arrow{rr} \arrow{dd}
+    && \arrow{dd} B(\Fq)^* \arrow[>->>]{dr} \arrow{rr} && A(\Fq)^* \arrow[>->>]{dr}  \arrow{dd}
+    \arrow{rr}&& 0 & \\
+& %\Hh^2(\Weil{},\Hh^1({\bar A},\EEx)) \arrow{rr}
+ && \Hh^1(\Weil{},\Hh^1(C,\EEx)) \arrow[crossing over]{dd} \arrow[crossing over]{rr}  && \Hh^1(\Weil{},\Hh^1(B,\EEx)) \arrow[crossing over]{dd} \arrow[crossing over]{rr} && \Hh^1(\Weil{},\Hh^1(A,\EEx)) \arrow[crossing over]{dd}  &  & %\Hh^0(\Weil{},\Hh^1({\bar C},\EEx))
+ \\
+& & 0  && 0  &&  0  && & \\
+ &      &&  0 && 0 && 0 & & \\
+  \end{tikzcd}
+  \]
+}
+\end{center}
+\label{diagram}
+\end{table}
+
 \begin{proof}
@@
 \end{proof}
-
-\begin{table}[ht]
-\caption{A big diagram}
-\begin{center}
-{\smaller\smaller\smaller
-    \[
-  \begin{tikzcd}[row sep=20, column sep=3]
-    &  0 \arrow{dd} && 0 \arrow{dd} && 0\arrow{dd} & \\
-    &&  0 \arrow[crossing over]{dd} && 0 \arrow[crossing over]{dd} && 0\arrow{dd} & & \\
-    {}& \ker \TrFrob{C} \arrow[->>]{rr} \arrow[>->>]{dr} \arrow{dd} && \arrow{dd} \ker \TrFrob{B} \arrow{rr} \arrow[>->]{dr}  && \ker \TrFrob{A}=0 \arrow[>->>]{dr} \arrow{dd} \arrow{rr} && 0 & \\
-    && \Hh^0(\Weil{},\Hh^2(C,\EEx)) \arrow[crossing over,->>]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(B,\EEx)) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(A,\EEx)) \arrow[crossing over]{dd}  &  &  \\
-    & \QCiso{C} \arrow[>->>]{dr}\arrow{rr} \arrow{dd}%{\TrFrob{C}}
-    && \QCiso{B} \arrow[>->]{dr} \arrow{rr} \arrow{dd}%{\TrFrob{B}}
-    && \QCiso{A} \arrow[>->>]{dr} \arrow{dd}%{\TrFrob{A}}
-    \arrow{rr}  &   & 0 & \\
-\Hh^1(E^\bullet_{A}) \arrow[crossing over]{rr}  && \Hh^2(E^\bullet_{C}) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^2(E^\bullet_{B}) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^2(E^\bullet_{A}) \arrow{rr} \arrow[crossing over]{dd} &  & \Hh^3(E^\bullet_{C}) \\
-   0 \arrow{r}
-    & C(\Fq)^* \arrow[>->>]{dr} \arrow{rr} \arrow{dd}
-    && \arrow{dd} B(\Fq)^* \arrow[>->>]{dr} \arrow{rr} && A(\Fq)^* \arrow[>->>]{dr}  \arrow{dd}
-    \arrow{rr}&& 0 & \\
- %\Hh^2(\Weil{},\Hh^1({\bar A},\EEx)) \arrow{rr}
- && \Hh^1(\Weil{},\Hh^1(C,\EEx)) \arrow[crossing over]{dd} \arrow[crossing over]{rr}  && \Hh^1(\Weil{},\Hh^1(B,\EEx)) \arrow[crossing over]{dd} \arrow[crossing over]{rr} && \Hh^1(\Weil{},\Hh^1(A,\EEx)) \arrow[crossing over]{dd}  &  & %\Hh^0(\Weil{},\Hh^1({\bar C},\EEx))
- \\
-  & 0  && 0  &&  0  && & \\
-        &&  0 && 0 && 0 & & \\
-  \end{tikzcd}
-  \]
-}
-\end{center}
-\label{diagram}
-\end{table}
 

### 2014-08-18 dictionary.tex
Changes to \S 3
Moving on to \S 4 - Applications.

@@
 
-\subsection{Bounded quasicharacter sheaves}\label{sec:bounded}
+%\subsection{Bounded quasicharacter sheaves}\label{sec:bounded}
+\subsection{Descent to G}\label{sec:bounded}
 
@@
 \ref{QC.3}.
-This is the category of \emph{bounded quasicharacter sheaves} on $G$.
+%This is the category of \emph{bounded quasicharacter sheaves} on $G$.
 \end{definition}
 
-The category of bounded quasicharacter sheaves is a rigid monoidal category in the obvious way.
+Category $\bQC(G)$ is a rigid monoidal category in the obvious way.
 
@@
  Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Let $(\qcs{E},\mu_\qcs{E})$ be a bounded quasicharacter sheaf on $G$.
+ Suppose $(\qcs{E},\mu_\qcs{E})$ in an object in $\bQC(G)$.
  Then $\qcs{E}$ is an $\ell$-adic constructible sheaf on $G$ and
@@
 
-We will identify $\bQC(G)$ with its image under $B_G$
-and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ is \emph{bounded} on $G$
-if it is isomorphic to some $B_G(\qcs{E}, \mu_\qcs{E})$.
-We will see in Corollary~\ref{cor:bounded-and-finite} that bounded quasicharacter sheaves are exactly quasicharacter sheaves with bounded Trace of Frobenius.\todo{Check this, later.}
+We will identify $\bQC(G)$ with its image under $B_G$ and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ \emph{descend to $G$} if it is isomorphic to some $B_G(\qcs{E}, \mu_\qcs{E})$.
+%We will see in Corollary~\ref{cor:bounded-and-finite} that bounded quasicharacter sheaves are exactly quasicharacter sheaves with bounded Trace of Frobenius.\todo{Check this, later.}
 
@@
 is surjective with kernel isomorphic to $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$.
- Moreover, $\Aut(\qcs{L}) = \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and every $\rho \in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism, for all quasicharacter sheaves $\qcs{L}$ and $\qcs{L}'$ on $G$.
 \end{theorem}
@@
   Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.
-
+ %
   The sequence of abelian groups
@@
   character groups is also exact.
-
+%
   The upper row is exact by Proposition~\ref{prop:middleexact}.
@@
 and $\ker \TrFrob{\pi_0(G)} \to \ker \TrFrob{G}$ is an isomorphism.
-
- (. . . where $G(\bFq)$ is given the topology of the espace étalé of the sheaf of sections of $G$.)
- \todo{Still under construction: $\Aut(\qcs{L})$.}
-
- For the last part of the proposition, argue as in the analogous part of Proposition~\ref{prop:mor_etale}.
+\end{proof}
+
+\subsection{Morphisms of quasicharacters}
+
+\begin{theorem}\label{thm:hom}
+Let $G$ be a smooth, commutative group scheme over $\Fq$.
+For all quasicharacter sheaves $\qcs{L}$ and $\qcs{L}'$ on $G$,
+every $\rho \in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism.
+Moreover, $\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$, canonically.
+\end{theorem}
+\begin{proof} 
+For the first part of the proposition, argue as in the analogous part of Proposition~\ref{prop:mor_etale}.
+For the second, fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the homomorphism $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:mor_etale}.
+This group homomorphism is clearly injective: if $\rho_x = \id_{\qcs{L}_x}$ for every $x\in \bG$ then $\rho = \id_{\qcs{L}}$.
+Note that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom_\text{cts}(\bG_{\Weil{}},\EEx)$, where $\bG_{\Weil{}}$ is given the topology of the base of the espace étalé attached to $\gqcs{L}$.
+Since $\ell$ is invertible in $\Fq$, it follows that $\Hom_\text{cts}(\bG_{\Weil{}},\EEx) = \Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
+Note that $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
+To see that $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho_y: \gqcs{L}_y \to \gqcs{L}_y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
+This defines an isomorphism $\bar\rho : \gqcs{L}\to \gqcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\qcs{L}\to \qcs{L}$ with maps to $\theta$ under $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
 \end{proof}

### 2014-08-18 dictionary.tex
Changed the language on bounded and finite quasicharacter sheaves
Made a home for applications to Abelian varieties

@@
 
-\begin{proposition}\label{prop:mor_etale}
+\begin{proposition}\label{prop:autornaught_etale}
 Let $G$ be an etale commutative group scheme over $\Fq$.
@@
 
-Note that Proposition~\ref{prop:mor_etale} tells us that if $G$ is an etale commutative group scheme over $\Fq$ then every hom-set is either trivial or $\left(G(\bFq)_{\Weil{}}\right)^*$, non-canonically.
-
-\section{Main results}\label{sec:main}
+Note that Proposition~\ref{prop:autornaught_etale} tells us that if $G$ is an etale commutative group scheme over $\Fq$ then every hom-set is either trivial or $\left(G(\bFq)_{\Weil{}}\right)^*$, non-canonically.
+
+\section{The function--sheaf dictionary for smooth, commutative group schemes}\label{sec:main}
 
@@
 
-We will identify $\bQC(G)$ with its image under $B_G$ and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ \emph{descend to $G$} if it is isomorphic to some $B_G(\qcs{E}, \mu_\qcs{E})$.
+We will identify $\bQC(G)$ with its image under $B_G$ and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ \emph{descends to $G$} if it is isomorphic to some $B_G(\qcs{E}, \mu_\qcs{E})$.
 %We will see in Corollary~\ref{cor:bounded-and-finite} that bounded quasicharacter sheaves are exactly quasicharacter sheaves with bounded Trace of Frobenius.\todo{Check this, later.}
@@
 \begin{lemma}\label{lem:bounded_connected}
-If $G$ is a connected commutative algebraic group over $\Fq$ then every quasisharacter sheaf on $G$ is finite and $B_G : \bQC(G) \to \QC(G)$ is an equivalence of categories.
+If $G$ is a connected commutative algebraic group over $\Fq$ then $B_G : \bQC(G) \to \QC(G)$ is an equivalence of categories.
 \end{lemma}
@@
 \begin{proof}
-In Lemma~\ref{lem:bounded_connected} we saw that every quasicharacter sheaf $\qcs{L}$ on $G$ descends to bounded quasicharacter sheaf $\qcs{E}$ on $G$.
+In Lemma~\ref{lem:bounded_connected} we saw that every quasicharacter sheaf $\qcs{L}$ on $G$ descends to $G$; let $\qcs{E}$ be an object in $\bQC(G)$ for which $B_G(\qcs{E}) \iso \qcs{L}$.
  Since the functor $B_G : \bQC(G) \to \QC(G)$ is full and faithful, $\Aut(\qcs{L}) = \Aut(\qcs{E})$.
 From here, Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields \citelist{\cite{deligne:SGA4.5}*{Sommes trig.}, \cite{laumon:87a}*{1.1.3}}  gives us all we need, as we briefly recall.
-The key observation is that, by etale descent, pull-back by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every bounded quasicharacter sheaf $\qcs{E}$ on $G$.
+The key observation is that, by etale descent, pull-back by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
 Note that since $V$ is $1$-dimensional, the choice of $V \to V\otimes V$ is exactly the choice of an isomorphism $V\iso \EE$.
@@
 Since the only such isomorphism $\rho$ is $\id_V$, it follows that $\Aut(\qcs{E}) = 1$, completing the proof.
-For the last part of the proposition, argue as in the analogous part of Proposition~\ref{prop:mor_etale}.
+For the last part of the proposition, argue as in the analogous part of Proposition~\ref{prop:autornaught_etale}.
 \end{proof}
@@
 
-\subsection{Finite quasicharacter sheaves}
+\subsection{Discrete isogenies}\label{sec:discrete_isogenies}
 
@@
 Let $\psi : A \to \EEx$ be a character.
-Then $(f_* \EE)_\psi$ (the $\psi$-isotypic component of $f_*\EE$) is a bounded quasicharacter on $G$.
+Then $(f_* \EE)_\psi$ (the $\psi$-isotypic component of $f_*\EE$) is an object in $\bQC(G)$.
 \end{proposition}
@@
 
-We say that a morphism $f : H\to G$ of commutative group $\Fq$-schemes is a discrete isogeny if it is a finite, surjective \'etale morphism and
+We say that a morphism $f : H\to G$ of commutative group $\Fq$-schemes is a {\it discrete isogeny} to $G$ if it is a finite, surjective \'etale morphism and
 the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f$ is trivial.
@@
 \begin{lemma}\label{lemma:ext}
-Every discrete isogeny onto $G^0$ extends to a discrete
-isogeny onto $G$ inducing an isomorphism on component groups.
+Every discrete isogeny to $G^0$ extends to a discrete
+isogeny to $G$ inducing an isomorphism on component groups.
 \end{lemma}
@@
 
-\subsection{The function--sheaf dictionary for smooth, commutative group schemes}
+\subsection{The dictionary}
 \label{sec:snake}
@@
 
-\begin{theorem}\label{thm:hom}
+\begin{theorem}\label{thm:autornaught}
 Let $G$ be a smooth, commutative group scheme over $\Fq$.
@@
 \begin{proof} 
-For the first part of the proposition, argue as in the analogous part of Proposition~\ref{prop:mor_etale}.
-For the second, fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the homomorphism $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:mor_etale}.
+For the first part of the proposition, argue as in the analogous part of Proposition~\ref{prop:autornaught_etale}.
+For the second, fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the homomorphism $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
 This group homomorphism is clearly injective: if $\rho_x = \id_{\qcs{L}_x}$ for every $x\in \bG$ then $\rho = \id_{\qcs{L}}$.
@@
 
-\section{Application to \texorpdfstring{$p$}{p}-adic tori}
+\subsection{Base change}\label{sec:basechange}
+
+When using quasicharacter sheaves to study characters, it is useful to understand
+how quasicharacter sheaves behave under change of fields.
+Let $k'$ be a finite extension of $k$. Then $k \hookrightarrow k'$ induces a group homomorphism
+$i_{k'/k} : G(k) \hookrightarrow G(k')$ and thus a homomorphism
+\begin{align*}
+i_{k'/k}^* : G(k')^* &\to G(k)^* \\
+\chi &\mapsto \chi\circ i_{k'/k}.
+\end{align*}
+We can interpret this operation on characters in terms of quasicharacter sheaves:
+
+\begin{proposition} \label{prop:csbe}
+Set $G_{k'} \ceq G\times_\Spec{k} \Spec{k'}$ and let
+\[
+\QC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \QC(G)
+\]
+be the functor obtained by pullback along the canonical closed immersion of $k$-schemes
+$\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$
+\cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}.
+The following diagram commutes:
+\[
+\begin{tikzcd}
+\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\TrFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\TrFrob{G}} \\
+G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
+\end{tikzcd}
+\]
+\end{proposition}
+\begin{proof}
+This result follows immediately from Proposition~\ref{prop:pullback} together with the identifications
+\[
+\Res_{k'/k}(G_{k'})(k) \cong G_{k'}(k') \cong G(k')
+\]
+from the definitions of Weil restriction and base change.
+\end{proof}
+
+In the opposite direction, let $\Nm : G(k') \to G(k)$ be the norm map and consider the group homomorphism:
+\begin{align*}
+\Nm^* : G(k)^* &\to G(k')^* \\
+\chi &\mapsto \chi\circ \Nm.
+\end{align*}
+We can also interpret this operation on characters in terms of quasicharacter sheaves.
+
+If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$, we define
+a quasicharacter sheaf $\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
+$G_{k'}$ of $G$ to $k'$ by setting
+\[
+\phi_{k'} \ceq \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi).
+\]
+The commutativity of the diagram (QC.3) for $\phi_{k'}$
+follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
+Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
+as taking the action $\varphi$ of $\Weil{k}$ on $\gqcs{L}$
+defined in Section~\ref{sec:category} and restricting it to the subgroup $\Weil{k'}$.
+
+\begin{proposition}\label{prop:basechange}
+With notation above,
+the rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$
+ defines a monoidal functor $\QC(G) \to \QC(G_{k'})$.
+ Moreover, the following diagram commutes:
+\[
+\begin{tikzcd}[column sep=60]
+\QCiso{G} \rar{\nu_{k'/k}} \dar{\TrFrob{G}} & \QCiso{G_{k'}} \dar{\TrFrob{G_{k'}}} \\
+G(k)^*  \rar{\Nm^*} & G(k')^*.
+\end{tikzcd}
+\]
+\end{proposition}
+
+\begin{proof}
+Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
+we may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
+and the value of $\Nm^*(\TrFrob{G}(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
+Applying \ref{QC.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
+\[
+\begin{tikzcd}
+\gqcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gqcs{L}_{F(x)} \otimes \gqcs{L}_{F^2(x)} \otimes \cdots \otimes \gqcs{L}_x
+\dar{\phi_x \otimes (F^*\phi)_x \otimes \cdots \otimes ((F^{n-1})^*\phi)_x} \\
+\gqcs{L}_{\Nm(x)} \rar & \gqcs{L}_x \otimes \gqcs{L}_{F(x)} \otimes \cdots \otimes \gqcs{L}_{F^{n-1}(x)}.
+\end{tikzcd}
+\]
+Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$ and write the image of $v$ under the
+bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
+for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{QC.2}, $v$ maps to
+$v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
+Let $\alpha_i \in \EEx$ represent $((F^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
+the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gqcs{L}_{\Nm(x)}$
+with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gqcs{L}_x$.
+\end{proof}
+
+Finally, let $G'$ be a smooth commutative group scheme over $k'$;
+we explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
+We may decompose the base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
+into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
+\[
+(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
+\]
+Since products and coproducts agree for group schemes we have a natural inclusion of $k'$-schemes
+\[
+G' \hookrightarrow (\Res_{k'/k}G')_{k'}
+\]
+mapping $G'$ into the summand corresponding to $1 \in \Gal(k'/k)$.  Composing $\nu_{k'/k}$
+from Proposition~\ref{prop:basechange} with pullback along this map yields a functor
+\[
+\rho : \QC(\Res_{k'/k}G') \to \QC(G').
+\]
+
+\begin{proposition}
+Let $k'/k$ be a finite extension and let $G'$ be a smooth commutative group scheme over $k'$.
+The following diagram of isomorphisms commutes, where the bottom map is the identity:
+\[
+\begin{tikzcd}
+\QCiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \QCiso{G'} \dar{\TrFrob{G'}}\\
+G'(k')^* \rar & G'(k')^*
+\end{tikzcd}
+\]
+\end{proposition}
+\begin{proof}
+By Proposition~\ref{prop:pullback} the pullback part of the definition of $\rho$ corresponds to the map
+\[
+(\Res_{k'/k}G')(k') \to G'(k')^*
+\]
+induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on
+\[
+(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'
+\]
+is given by permuting coordinates, composition with the norm map yields the identity on $G'(k')$.
+\end{proof}
+
+\todo{Can we improve on this result by proving that $\rho$
+is an equivalence of categories?}
+
+\subsection{Finite and bounded - fragments}
 
@@
 
-\subsection{Base change}\label{sec:basechange}
-
-When using quasicharacter sheaves to study characters, it is useful to understand
-how quasicharacter sheaves behave under change of fields.
-Let $k'$ be a finite extension of $k$. Then $k \hookrightarrow k'$ induces a group homomorphism
-$i_{k'/k} : G(k) \hookrightarrow G(k')$ and thus a homomorphism
-\begin{align*}
-i_{k'/k}^* : G(k')^* &\to G(k)^* \\
-\chi &\mapsto \chi\circ i_{k'/k}.
-\end{align*}
-We can interpret this operation on characters in terms of quasicharacter sheaves:
-
-\begin{proposition} \label{prop:csbe}
-Set $G_{k'} \ceq G\times_\Spec{k} \Spec{k'}$ and let
-\[
-\QC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \QC(G)
-\]
-be the functor obtained by pullback along the canonical closed immersion of $k$-schemes
-$\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$
-\cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}.
-The following diagram commutes:
-\[
-\begin{tikzcd}
-\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\TrFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\TrFrob{G}} \\
-G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
-\end{tikzcd}
-\]
-\end{proposition}
-\begin{proof}
-This result follows immediately from Proposition~\ref{prop:pullback} together with the identifications
-\[
-\Res_{k'/k}(G_{k'})(k) \cong G_{k'}(k') \cong G(k')
-\]
-from the definitions of Weil restriction and base change.
-\end{proof}
-
-In the opposite direction, let $\Nm : G(k') \to G(k)$ be the norm map and consider the group homomorphism:
-\begin{align*}
-\Nm^* : G(k)^* &\to G(k')^* \\
-\chi &\mapsto \chi\circ \Nm.
-\end{align*}
-We can also interpret this operation on characters in terms of quasicharacter sheaves.
-
-If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$, we define
-a quasicharacter sheaf $\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
-$G_{k'}$ of $G$ to $k'$ by setting
-\[
-\phi_{k'} \ceq \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi).
-\]
-The commutativity of the diagram (QC.3) for $\phi_{k'}$
-follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
-Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
-as taking the action $\varphi$ of $\Weil{k}$ on $\gqcs{L}$
-defined in Section~\ref{sec:category} and restricting it to the subgroup $\Weil{k'}$.
-
-\begin{proposition}\label{prop:basechange}
-With notation above,
-the rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$
- defines a monoidal functor $\QC(G) \to \QC(G_{k'})$.
- Moreover, the following diagram commutes:
-\[
-\begin{tikzcd}[column sep=60]
-\QCiso{G} \rar{\nu_{k'/k}} \dar{\TrFrob{G}} & \QCiso{G_{k'}} \dar{\TrFrob{G_{k'}}} \\
-G(k)^*  \rar{\Nm^*} & G(k')^*.
-\end{tikzcd}
-\]
-\end{proposition}
-
-\begin{proof}
-Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
-we may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
-and the value of $\Nm^*(\TrFrob{G}(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
-Applying \ref{QC.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
-\[
-\begin{tikzcd}
-\gqcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gqcs{L}_{F(x)} \otimes \gqcs{L}_{F^2(x)} \otimes \cdots \otimes \gqcs{L}_x
-\dar{\phi_x \otimes (F^*\phi)_x \otimes \cdots \otimes ((F^{n-1})^*\phi)_x} \\
-\gqcs{L}_{\Nm(x)} \rar & \gqcs{L}_x \otimes \gqcs{L}_{F(x)} \otimes \cdots \otimes \gqcs{L}_{F^{n-1}(x)}.
-\end{tikzcd}
-\]
-Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$ and write the image of $v$ under the
-bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
-for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{QC.2}, $v$ maps to
-$v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
-Let $\alpha_i \in \EEx$ represent $((F^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
-the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gqcs{L}_{\Nm(x)}$
-with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gqcs{L}_x$.
-\end{proof}
-
-Finally, let $G'$ be a smooth commutative group scheme over $k'$;
-we explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
-We may decompose the base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
-into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
-\[
-(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
-\]
-Since products and coproducts agree for group schemes we have a natural inclusion of $k'$-schemes
-\[
-G' \hookrightarrow (\Res_{k'/k}G')_{k'}
-\]
-mapping $G'$ into the summand corresponding to $1 \in \Gal(k'/k)$.  Composing $\nu_{k'/k}$
-from Proposition~\ref{prop:basechange} with pullback along this map yields a functor
-\[
-\rho : \QC(\Res_{k'/k}G') \to \QC(G').
-\]
-
-\begin{proposition}
-Let $k'/k$ be a finite extension and let $G'$ be a smooth commutative group scheme over $k'$.
-The following diagram of isomorphisms commutes, where the bottom map is the identity:
-\[
-\begin{tikzcd}
-\QCiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \QCiso{G'} \dar{\TrFrob{G'}}\\
-G'(k')^* \rar & G'(k')^*
-\end{tikzcd}
-\]
-\end{proposition}
-\begin{proof}
-By Proposition~\ref{prop:pullback} the pullback part of the definition of $\rho$ corresponds to the map
-\[
-(\Res_{k'/k}G')(k') \to G'(k')^*
-\]
-induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on
-\[
-(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'
-\]
-is given by permuting coordinates, composition with the norm map yields the identity on $G'(k')$.
-\end{proof}
-
-\todo{Can we improve on this result by proving that $\rho$
-is an equivalence of categories?}
+\section{Applications to algebraic tori and Abelian varieties over \texorpdfstring{$p$}{p}-adic fields}
 
@@
 
-\subsection{Recovery}
-
-We are in a good position to understand $\QC(G)$ when $G$ is a connected algebraic group over $\Fq$, since we can now describe objects and maps in this category in very concrete terms.
-We begin by recovering a classical result.
-
-Morphisms in $\QC(G)$ are also very simple.
-
-\begin{proposition}
-If $G$ is a connected algebraic group then $\Aut_{\QC(G)}(\qcs{L})$ is . . . .
-\end{proposition}
-
-\begin{proof}
-Pick up from the proof of Proposition~\ref{prop:autornaught}.
-\end{proof}
-
 %sagemathcloud={"zoom_width":105}

### 2014-08-18 dictionary.tex
Corrected typo in thm:autornaught

@@
 Note that $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
-To see that $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho_y: \gqcs{L}_y \to \gqcs{L}_y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
+To see that $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho^y: \gqcs{L}^y \to \gqcs{L}^y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
 This defines an isomorphism $\bar\rho : \gqcs{L}\to \gqcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\qcs{L}\to \qcs{L}$ with maps to $\theta$ under $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.

### 2014-08-19 dictionary.tex
Discrete isogenies section improved. Other changes.

@@
 \hyphenation{quasi-character}
-
 \newcommand{\lTrFrob}[1]{\TrFrob{#1}^2}
+\newcommand{\comp}{\Pi} % Component group
 
@@
 
-\section{The case of \'etale commutative group schemes} \label{sec:etale}
+\section{Quasicharacter sheaves on \'etale commutative group schemes} \label{sec:etale}
 
@@
 
-\section{The function--sheaf dictionary for smooth, commutative group schemes}\label{sec:main}
+\section{Quasicharacter sheaves on commutative algebraic groups}
 
@@
 %We will see in Corollary~\ref{cor:bounded-and-finite} that bounded quasicharacter sheaves are exactly quasicharacter sheaves with bounded Trace of Frobenius.\todo{Check this, later.}
+
+\subsection{Discrete isogenies}\label{sec:discrete_isogenies}
+
+%Here we describe a class of quasicharacter sheaves on $G$ that will play a role in Section~\ref{sec:restriction}.
+
+A finite, etale, surjective morphism $H\to G$ of smooth group schemes over $\Fq$ for which the action of $\Gal(\bFq/\Fq)$ on the kernel is trivial is called a {\it discrete isogeny}.
+
+\begin{proposition}\label{prop:finite}
+Let $f: H \to G$ be a discrete isogeny; let $A$ be the kernel of $f$.
+Let $V$ be a $1$-dimensional representation of $A$ 
+equipped with an isomorphism $V\to V\otimes V$.
+Let $\psi : A \to \EEx$ be the character of $V$.
+Then $(f_! V_H)_\psi$ (the $\psi$-isotypic component of $f_!V_H$) is an object in $\bQC(G)$.
+\end{proposition}
+
+\begin{proof}
+Let $f$, $A$, $V$ and $\psi$ be as above; set $\qcs{E} = (f_! V_H)_\psi$.
+It is clear that $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank one.
+We must show that comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
+To do this we use etale descent to see that pull-back along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$. 
+In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
+Since $f$ is a morphism of group schemes, the functor $f^*$ defines $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ from the isomorphism $m^*\psi \iso \psi \boxtimes\psi$ determined by $V\to V\otimes V$.
+\end{proof}
+
+We remark that, since $V$ is $1$-dimensional, the choice of $V \to V\otimes V$ is exactly the choice of an isomorphism $V\iso \EE$.
 
@@
 \begin{proposition}\label{prop:connected}
- If $G$ is a connected, commutative algebraic group over $\Fq$ then
- \[
-  \TrFrob{G} : \QCiso{G} \to G(\Fq)^*
- \]
- is an isomorphism of groups.
- Moreover, for every quasicharacter sheaf $\qcs{L}$ on $G$, $\Aut(\qcs{L}) = 1$
- and every $\rho \in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism.
+ If $G$ is a connected, commutative algebraic group over $\Fq$ then:
+ \begin{enumerate}
+ \item $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is an isomorphism of groups;
+ \item every quasicharacter sheaf on $G$ is isomorphic to one defined by a discrete isogeny;%as in Proposition~\ref{prop:finite};
+ \item $\Aut(\qcs{L}) = 1$, for all quasicharacter sheaves $\qcs{L}$ on $G$;
+  \item every $\rho \in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism,
+  for all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $G$.
+ \end{enumerate}
  \end{proposition}
@@
 The key observation is that, by etale descent, pull-back by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
-Note that since $V$ is $1$-dimensional, the choice of $V \to V\otimes V$ is exactly the choice of an isomorphism $V\iso \EE$.
 Using the equivalence given by $\Lang^*$, if $\Lang^*\qcs{E} = V$ with character $\psi$ and isomorphism $V\to V\otimes V$ then 
-$\qcs{E} \iso (\Lang_* V)_\psi$, the $\psi$-isotypic component of the push-forward $\Lang_* V$ of the constand sheaf $V$ on $G$, equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes\qcs{E}$ determined by $V\to V\otimes V$.
+$\qcs{E} \iso (\Lang_!
+V)_\psi$, the $\psi$-isotypic component of the push-forward $\Lang_* V$ ($\Lang$ is proper, so $\Lang_* = \Lang_!$) of the constant sheaf $V$ on $G$ equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes\qcs{E}$ determined by $V\to V\otimes V$.
 Moreover, $\Aut(\qcs{E})$ is the group of automorphisms of $\rho : V\to V$ for which 
@@
 
-\subsection{Discrete isogenies}\label{sec:discrete_isogenies}
-
-In this section we return to the case when $G$ is any smooth commutative group scheme over $\Fq$ and describe a class of quasicharacter sheaves on $G$ that will play a role in Section~\ref{sec:restriction}.
-
-A finite, etale, surjective morphism $H\to G$ of smooth group schemes over $\Fq$ for which the action of $\Gal(\bFq/\Fq)$ on the kernel is trivial is called a {\it discrete isogeny}.
-
-\begin{proposition}\label{prop:finite}
-Let $f: H \to G$ be a discrete isogeny; let $A$ be the kernel of $f$.
-Let $\psi : A \to \EEx$ be a character.
-Then $(f_* \EE)_\psi$ (the $\psi$-isotypic component of $f_*\EE$) is an object in $\bQC(G)$.
-\end{proposition}
-
-\begin{proof}
-Let $f$, $A$ and $\psi$ be as above; set $\qcs{E} = (f_! \EE)_\psi$.
-It is clear that $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank one.
-We must show that comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
-To do this we may use etale descent exactly as in the proof of Proposition~\ref{prop:connected}. 
-Pull-back along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$. 
-In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $\EE$ on $H$ with character $\psi$.
-Since $f$ is a morphism of group schemes, the functor $f^*$ defines $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ from the canonical isomorphism $m^*\psi \iso \psi \boxtimes\psi$.
-\end{proof}
+\section{The function--sheaf dictionary for smooth, commutative group schemes}\label{sec:main}
 
@@
   By Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}, every
-  quasicharacter sheaf on $G^0$ is isomorphic to $(\pi_! \EE)\psi$ for some discrete isogeny $\pi : B \to G^0$ and character $\psi : \ker \pi \to \EEx$.
-  So to prove the proposition it suffices to show that $(\pi_! \EE)\psi$ extends to a quasicharacter sheaf on $G$.
+  quasicharacter sheaf on $G^0$ is isomorphic to $(\pi_! \EE)_\psi$ for some discrete isogeny $\pi : B \to G^0$ and character $\psi : \ker \pi \to \EEx$.
+  So to prove the proposition it suffices to show that $(\pi_! \EE)_\psi$ extends to a quasicharacter sheaf on $G$.
 %
@@
  such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
- Then $(f_! \EE)\psi$ is a quasicharacter sheaf on $G$ and
- $(f_! \EE)\psi\vert_{G^0} \iso (\pi_! \EE)\psi$.
+ Then $(f_! \EE)_\psi$ is a quasicharacter sheaf on $G$ and
+ $(f_! \EE)_\psi\vert_{G^0} \iso (\pi_! \EE)_\psi$.
 \end{proof}
@@
   \]
-is surjective with kernel isomorphic to $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$.
+is surjective with kernel canonically isomorphic to $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$.
 \end{theorem}
@@
 
+\todo{Insert comments on $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$. 
+It is trivial if $G$ is an algebraic group with cyclic component group.
+Lusztig}
+
 \subsection{Morphisms of quasicharacters}
@@
 is an equivalence of categories?}
+
+\section{Applications}\label{sec:applications}% to algebraic tori and Abelian varieties over \texorpdfstring{$p$}{p}-adic fields}
+
+\subsection{Smooth commutative group schemes over DVRs}
+
+Let $X$ be a smooth commutative group scheme over a complete discrete valuation ring $R$ with residue field $\Fq$.
+We say that a character $X(R)\to \EEx$ is {\it admissible} if there is some
+
+We will also need the Greenberg functor \citelist{\cite{greenberg:61} \cite{greenberg:63a}}:
+a functor from the category of schemes locally of finite type
+over an Artinian local ring with perfect residue field $k$
+to the category of schemes locally of finite type over $k$.
+This functor respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components.
+See
+\citelist{
+\cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1}
+\cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6}
+\cite{nicaise-sebag:motivicSerre}*{\S 2.2}
+\cite{bertrapelle-gonzales:Greenberg}*{\S 5}
+}
+for the definition and fundamental properties of the Greenberg functor as it is used here.
+
+\begin{definition}\label{def:Grn}
+For any local field $K$ with residue field $\Fq$ and for any positive integer $n$, let
+\[
+\Gr_n : \partop{\text{Schemes}}{\text{lft over $\OK$}} \to \partop{\text{Schemes}}{\text{lft over $\Fq$}}
+\]
+be the functor produced by precomposing pullback along $\OK \to \OK/\pK^n$ with the Greenberg functor.
+\end{definition}
+
+The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a
+natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$ between additive functors.
+For a given Néron model $\TT$ of $T$, set
+\begin{align*}
+ \GN{T}_n &\ceq \Gr_n(\TT), \\
+ f_n &\ceq P_n(\TT).
+\end{align*}
+
+We list some fundamental properties of $f_n$ and $\GN{T}_n$ for further use:
+ \begin{enumerate}
+  \labitem{(GN.0)}{truncation}
+  $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes over $\Fq$
+  \citelist{\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276} \cite{bertrapelle-gonzales:Greenberg}*{Prop. 7.2}}.
+  We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.
+  \labitem{(GN.1)}{smooth}
+  $\GN{T}_n$ is a $\QC$-scheme.
+  Note that $\underline{T}$ is a smooth group scheme over $\OK$, by construction.
+  Since smoothness is preserved under base change, the group scheme
+  $\TT_n \ceq \underline{T} \times_\Spec{\OK} \Spec{\OK/\pK^n}$
+  is smooth over an Artinian ring with perfect residue field.
+  The Greenberg functor preserves smoothness,
+  so $\GN{T}_n$ is a smooth group scheme locally of finite type over $\Fq$.
+  The Greenberg functor takes the geometric identity component of $\TT_n$
+  to the geometric identity component of $\GN{T}_n$.
+  In fact, $\pi_0(\GN{T}_n)$ is independent of $n$, equal to $\comp \ceq \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$.
+  Moreover, $\Pi$ is finitely generated \cite{xarles:93a}*{2.18}.
+  \labitem{(GN.2)}{identity} $\GN{T}_n^\circ$ is affine of finite type over $\Fq$.
+  \labitem{(GN.3)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
+\end{enumerate}
+
+\begin{proposition}
+The projective limit of the system
+\[
+\cdots \xrightarrow{f_n} \GN{T}_{n+1} \xrightarrow{f_{n-1}} \cdots \xrightarrow{f_1} \GN{T}_1
+\]
+exists in the category of group schemes over $\Fq$.
+\end{proposition}
+\begin{proof}
+Since the component group $\comp$ is independent of $n$, the projective system induces a sequence of affine schemes
+\begin{equation} \label{eq:Ti}
+\cdots \xrightarrow{f^i_n} \GN{T}^i_{n+1} \xrightarrow{f^i_{n-1}} \cdots \xrightarrow{f^i_1} \GN{T}^i_1
+\end{equation}
+for each $i \in \comp$.
+Since the category of affine schemes over $k$ is equivalent to the category of $k$-algebras, which has direct limits \todo{citation},
+the limit of \eqref{eq:Ti} exists in the category of affine group schemes over $k$ for each $i \in \comp$.  Write $\GN{T}^i$ for the limit,
+and define
+\[
+\GN{T} \ceq \coprod_{i \in \comp} \GN{T}^i
+\]
+as a $k$-scheme.  We claim that $\GN{T}$ is a projective limit of the original system, in the category of $k$-schemes.  Suppose that $Z$ is a $k$-scheme
+with a system of morphisms $z_n : Z \to \GN{T}_n$.  Let $\alpha : \pi_0(Z) \to \comp$ be the induced map on component groups, which is
+independent of $n$.  \todo{the components of $Z$ are not necessarily affine; is the projective limit in the category of affine schemes still the limit in the category of schemes?}
+
+The multiplication maps $m_n : \GN{T}_n \times \GN{T}_n \to \GN{T}_n$ induce maps of affine schemes
+$m_n^{i,j} : \GN{T}_n^i \times \GN{T}_n^j \to \GN{T}_n^{i+j},$ inducing maps $m^{i,j} : \GN{T}^i \times \GN{T}$ [under construction]
+\end{proof}
+
+\subsection{Smooth commutative group schemes over local fields, with Neron models}
+
+Let $X_K$ be a smooth commutative group scheme over a local field $K$ with residue field $\Fq$. Suppose that $X_K$ admits a Neron model $X$.
+
+\section{Fragments}
 
@@
 %In this latter case the stalk of the quasicharacter sheaf at the component $1$ is defined by a pro-\'etale cover rather than an \'etale cover.
-
-\section{Applications to algebraic tori and Abelian varieties over \texorpdfstring{$p$}{p}-adic fields}
 

### 2014-08-19 dictionary.tex
Update bibliography
In flagrante delicto

@@
 \newcommand{\comp}{\Pi} % Component group
+\newcommand{\m}{{\mathfrak{m}}}
 
@@
 
-Let $X$ be a smooth commutative group scheme over a complete discrete valuation ring $R$ with residue field $\Fq$.
-We say that a character $X(R)\to \EEx$ is {\it admissible} if there is some
-
-We will also need the Greenberg functor \citelist{\cite{greenberg:61} \cite{greenberg:63a}}:
+Let $R$ complete discrete valuation ring $R$ with residue field $\Fq$;
+write $\m$ for the maximal ideal of $R$ and $K$ for the quotient 
+In this section we use quasicharacter sheaves to geometrize and categorify the group 
+of admissible characters of smooth commutative group schemes over $R$.
+
+We will need the Greenberg functor \citelist{\cite{greenberg:61} \cite{greenberg:63a}}:
 a functor from the category of schemes locally of finite type
@@
 for the definition and fundamental properties of the Greenberg functor as it is used here.
-
-\begin{definition}\label{def:Grn}
-For any local field $K$ with residue field $\Fq$ and for any positive integer $n$, let
-\[
-\Gr_n : \partop{\text{Schemes}}{\text{lft over $\OK$}} \to \partop{\text{Schemes}}{\text{lft over $\Fq$}}
-\]
-be the functor produced by precomposing pullback along $\OK \to \OK/\pK^n$ with the Greenberg functor.
-\end{definition}
-
-The surjective ring homomorphism $\OK/\pK^{n+1} \to \OK/\pK^n$ determines a
+We will write
+\[
+\Gr_n : \partop{\text{Schemes}}{\text{lft over $R$}} \to \partop{\text{Schemes}}{\text{lft over $\Fq$}}
+\]
+for the functor produced by precomposing pullback along $R \to R_n$ with the Greenberg functor.
+
+The surjective ring homomorphism $R_{n+1} \to R_n$ determines a
 natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$ between additive functors.
-For a given Néron model $\TT$ of $T$, set
+Set
 \begin{align*}
- \GN{T}_n &\ceq \Gr_n(\TT), \\
- f_n &\ceq P_n(\TT).
+ \GN{X}_n &\ceq \Gr_n(X), \\
+ f_n &\ceq P_n(X).
 \end{align*}
 
-We list some fundamental properties of $f_n$ and $\GN{T}_n$ for further use:
+We list some fundamental properties of $f_n$ and $\GN{X}_n$ for further use:
  \begin{enumerate}
   \labitem{(GN.0)}{truncation}
-  $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is a surjective morphism of group schemes over $\Fq$
+  $f_n : \GN{X}_{n+1} \to \GN{X}_n$ is a surjective morphism of group schemes over $\Fq$
   \citelist{\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276} \cite{bertrapelle-gonzales:Greenberg}*{Prop. 7.2}}.
-  We remark that $f_n : \GN{T}_{n+1} \to \GN{T}_n$ is not induced from a morphism of Néron models.
+  We remark that $f_n : \GN{X}_{n+1} \to \GN{X}_n$ is not induced from a morphism of Néron models.
   \labitem{(GN.1)}{smooth}
@@
 
+Let $X$ be a smooth commutative group scheme over a 
+For every $n\in \NN_0$ set $R_n = R/\m^{n+1}$.
+We say that a character $\chi: X(R)\to \EEx$ is {\it admissible} if there is some $n \in \NN_0$ such that $\chi$ factors through $X(R) \to X(R_n)$.
+
+$\Hom_\text{ad}(X(R),\EEx)$
+
 \subsection{Smooth commutative group schemes over local fields, with Neron models}

### 2014-08-19 dictionary.tex
Changes to Applications

@@
 
-\subsection{Smooth commutative group schemes over DVRs}
-
-Let $R$ complete discrete valuation ring $R$ with residue field $\Fq$;
-write $\m$ for the maximal ideal of $R$ and $K$ for the quotient 
-In this section we use quasicharacter sheaves to geometrize and categorify the group 
-of admissible characters of smooth commutative group schemes over $R$.
-
-We will need the Greenberg functor \citelist{\cite{greenberg:61} \cite{greenberg:63a}}:
-a functor from the category of schemes locally of finite type
-over an Artinian local ring with perfect residue field $k$
-to the category of schemes locally of finite type over $k$.
+in this section we use quasicharacter sheaves to geometrize and categorify the group 
+of admissible characters of smooth commutative group schemes over local fields that admit Neron models.
+
+Let $R$ complete discrete valuation ring $R$ with residue field $\Fq$.
+Write $\m$ for the maximal ideal of $R$ and $K$ for the quotient field for $R$.
+Set $R_n = R/\m^{n+1}$ and $S_n = \Spec{R_n}$ and $S = \Spec{R}$; 
+note that $S_0 = \Spec{\Fq}$ is the special fibre of $S$.
+
+\subsection{Greenberg transform}
+
+We will need the Greenberg functor, which is
+a functor from the category of schemes 
+over an Artinian local ring with perfect residue field
+to the category of schemes over the residue field;
+See \cite{bertrapelle-gonzales:Greenberg} for the definition and fundamental properties of the Greenberg functor as we use it; other important references include
+\citelist{
+\cite{greenberg:61}, \cite{greenberg:63a},
+\cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1},
+\cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6},
+\cite{nicaise-sebag:motivicSerre}*{\S 2.2}
+}.
 This functor respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components.
-See
-\citelist{
-\cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1}
-\cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6}
-\cite{nicaise-sebag:motivicSerre}*{\S 2.2}
-\cite{bertrapelle-gonzales:Greenberg}*{\S 5}
-}
-for the definition and fundamental properties of the Greenberg functor as it is used here.
-We will write
+
+For any $n\in \NN_0$, we will write
 \[
@@
 \]
-for the functor produced by precomposing pullback along $R \to R_n$ with the Greenberg functor.
-
-The surjective ring homomorphism $R_{n+1} \to R_n$ determines a
-natural transformation $P_{n} : \Gr_{n+1} \to \Gr_n$ between additive functors.
-Set
-\begin{align*}
- \GN{X}_n &\ceq \Gr_n(X), \\
- f_n &\ceq P_n(X).
-\end{align*}
-
-We list some fundamental properties of $f_n$ and $\GN{X}_n$ for further use:
+for the functor produced by composing pullback along $S_n \to S$ with the Greenberg functor.
+This functor respects \'etale morphisms, smooth morphisms and geometric components, \todo{open immersions?
+closed immersion?} and
+\[
+\Gr_n(X)(\Fq) \iso X(R_n),
+\]
+canonically, for any $X$ lft over $R$.
+
+For any $n\leq m$,  the surjective ring homomorphism $R_{m} \to R_n$ determines a
+natural transformation $\Gr_{m} \to \Gr_n$ between additive functors.
+Crucially, $(\Gr_{m}\to \Gr_n)(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
+This observation is key to the proof that, for any $X$ lft over $S$, the projective limit 
+\[
+\Gr(X) \ceq \varprojlim_{n\in \NN_0} \Gr_n(X)
+\]
+taken with respect to the surjective morphisms $(\Gr_{m}\to \Gr_n)(X)$,
+exists in the category of group schemes over $\Fq$.
+This leads to the definition of what we call the {\it Greenberg transform}:
+\[
+\Gr : \partop{\text{Schemes}}{\text{lft over $R$}} \to \partop{\text{Schemes}}{\text{lft over $\Fq$}}.
+\]
+By construction, the $\Fq$-scheme $\Gr(X)$ comes equipped with morphisms 
+\[
+P_n(X) : \Gr(X) \to \Gr_n(X),\qquad \forall n\in \NN_0.
+\]
+The Greenberg transform $\Gr$ respects \'etale morphisms, smooth morphisms  \todo{open immersions? closed immersion?} and geometric components, and
+\[
+\Gr(X)(\Fq) \iso X(R),
+\]
+canonically, for any $X$ lft over $R$.
+
+\subsection{Quasicharacter sheaves on the Greenberg transform of a Neron model}
+
+Now suppose $X_K$ is a commutative algebraic group over $K$ 
+that admits a Neron model, $X$.
+Then $\Gr(X)$ is commutative group scheme over $\Fq$
+with component group scheme
+$\pi_0(\Gr(X))= \pi_0(X) \times_S S_0$
+and
+\[
+\Gr(X)(\Fq)\iso X_K(K)
+\]
+canonically.
+For every $n\in \NN_0$,
+$\Gr_n(X)$ is {\it smooth} commutative group scheme over $\Fq$
+with component group scheme
+$\pi_0(\Gr_n(X))= \pi_0(X) \times_S S_0$.
+
+A {\it quasicharacter sheaf for $X_K$} is a triple
+$\qcs{F}\ceq (\gqcs{F},\mu_\qcs{F},\phi_\qcs{F})$ where
 \begin{enumerate}
-  \labitem{(GN.0)}{truncation}
-  $f_n : \GN{X}_{n+1} \to \GN{X}_n$ is a surjective morphism of group schemes over $\Fq$
-  \citelist{\cite{bosch-lutkebohmert-reynaud:NeronModels}*{p. 276} \cite{bertrapelle-gonzales:Greenberg}*{Prop. 7.2}}.
-  We remark that $f_n : \GN{X}_{n+1} \to \GN{X}_n$ is not induced from a morphism of Néron models.
-  \labitem{(GN.1)}{smooth}
-  $\GN{T}_n$ is a $\QC$-scheme.
-  Note that $\underline{T}$ is a smooth group scheme over $\OK$, by construction.
-  Since smoothness is preserved under base change, the group scheme
-  $\TT_n \ceq \underline{T} \times_\Spec{\OK} \Spec{\OK/\pK^n}$
-  is smooth over an Artinian ring with perfect residue field.
-  The Greenberg functor preserves smoothness,
-  so $\GN{T}_n$ is a smooth group scheme locally of finite type over $\Fq$.
-  The Greenberg functor takes the geometric identity component of $\TT_n$
-  to the geometric identity component of $\GN{T}_n$.
-  In fact, $\pi_0(\GN{T}_n)$ is independent of $n$, equal to $\comp \ceq \pi_0(\TT) \times_{\Spec{\OK}} \Spec{\Fq}$.
-  Moreover, $\Pi$ is finitely generated \cite{xarles:93a}*{2.18}.
-  \labitem{(GN.2)}{identity} $\GN{T}_n^\circ$ is affine of finite type over $\Fq$.
-  \labitem{(GN.3)}{points} $\GN{T}_n(\Fq) = \TT(\OK/\pK^n)$, canonically.
+\item[(0)] $\gqcs{F}$ is a constructible $\ell$-adic sheaf on $\Gr(X)_{\bFq} \ceq \Gr(X)\otimes \bFq$,
+\item[(1)]  $\mu_\qcs{F}: \bm^* \gqcs{F} \to \gqcs{F}\boxtimes\gqcs{F}$ is an isomorphism $\ell$-adic sheaves, where $\bm : \Gr(X)_{\bFq} \times \Gr(X)_{\bFq} \to \Gr(X)_{\bFq}$ is multiplication for $\Gr(X)_{\bFq}$,
+\item[(2)] $\phi_\qcs{F} : \Frob{\Gr(X)}^* \gqcs{F} \to \gqcs{F}$ is an
+  isomorphism of constructible $\ell$-adic sheaves, where $\Frob{\Gr(X)}^* : \Gr(X)_{\bFq}  \to \Gr(X)_{\bFq}$ is Frobenius for $\Gr(X)_{\bFq}$,
 \end{enumerate}
-
-\begin{proposition}
-The projective limit of the system
-\[
-\cdots \xrightarrow{f_n} \GN{T}_{n+1} \xrightarrow{f_{n-1}} \cdots \xrightarrow{f_1} \GN{T}_1
-\]
-exists in the category of group schemes over $\Fq$.
-\end{proposition}
-\begin{proof}
-Since the component group $\comp$ is independent of $n$, the projective system induces a sequence of affine schemes
-\begin{equation} \label{eq:Ti}
-\cdots \xrightarrow{f^i_n} \GN{T}^i_{n+1} \xrightarrow{f^i_{n-1}} \cdots \xrightarrow{f^i_1} \GN{T}^i_1
-\end{equation}
-for each $i \in \comp$.
-Since the category of affine schemes over $k$ is equivalent to the category of $k$-algebras, which has direct limits \todo{citation},
-the limit of \eqref{eq:Ti} exists in the category of affine group schemes over $k$ for each $i \in \comp$.  Write $\GN{T}^i$ for the limit,
-and define
-\[
-\GN{T} \ceq \coprod_{i \in \comp} \GN{T}^i
-\]
-as a $k$-scheme.  We claim that $\GN{T}$ is a projective limit of the original system, in the category of $k$-schemes.  Suppose that $Z$ is a $k$-scheme
-with a system of morphisms $z_n : Z \to \GN{T}_n$.  Let $\alpha : \pi_0(Z) \to \comp$ be the induced map on component groups, which is
-independent of $n$.  \todo{the components of $Z$ are not necessarily affine; is the projective limit in the category of affine schemes still the limit in the category of schemes?}
-
-The multiplication maps $m_n : \GN{T}_n \times \GN{T}_n \to \GN{T}_n$ induce maps of affine schemes
-$m_n^{i,j} : \GN{T}_n^i \times \GN{T}_n^j \to \GN{T}_n^{i+j},$ inducing maps $m^{i,j} : \GN{T}^i \times \GN{T}$ [under construction]
-\end{proof}
-
-Let $X$ be a smooth commutative group scheme over a 
-For every $n\in \NN_0$ set $R_n = R/\m^{n+1}$.
-We say that a character $\chi: X(R)\to \EEx$ is {\it admissible} if there is some $n \in \NN_0$ such that $\chi$ factors through $X(R) \to X(R_n)$.
-
-$\Hom_\text{ad}(X(R),\EEx)$
-
-\subsection{Smooth commutative group schemes over local fields, with Neron models}
-
-Let $X_K$ be a smooth commutative group scheme over a local field $K$ with residue field $\Fq$. Suppose that $X_K$ admits a Neron model $X$.
+such that, for some $n\in \NN_0$,
+\begin{enumerate}
+\item[(3)]
+$\qcs{F} = P_n(X)^*\qcs{L}$ for some quasicharacter sheaf $\qcs{L}$ on $\Gr_n(X)$, where pull-back by $P_n(X)$ is defined as in Proposition~\ref{prop:pullback}.
+\end{enumerate}
+
+\begin{theorem}
+Let $X_K$ be a commutative algebraic group over $K$ with Neron model $X$ over $R$. 
+\begin{enumerate}
+\item[(0)] Quasicharacter sheaves for $X_K$ form a rigid monoidal category, $\QC(X_K)$, in a natural way. 
+\item[(1)] There is a canonical short exact sequence of abelian groups 
+\[
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{X_K} \to \Hom_\text{ad}(X_K(K),\EEx) \to 0
+\] 
+where $\Hom_\text{ad}(X_K(K),\EEx)$ is the group of characters of $X_K(K)$ that factor through $X(R)\to X(R_n)$, for some $n\in\NN_0$.
+\item[(2)] For all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ for $X_K$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism.
+\item[(3)] For all quasicharacter sheaves $\qcs{F}$ for $X_K$,
+\[
+\Aut(\qcs{L}) \iso \Hom((\pi_0(X)_{\Fq})_{\Weil{}},\EEx),
+\]
+canonically.
+\end{enumerate}
+\end{theorem}
+
+\bibliographystyle{amsalpha}
+\bibliography{bibliography/Biblio}
+
+\end{document}
 
@@
 %In this latter case the stalk of the quasicharacter sheaf at the component $1$ is defined by a pro-\'etale cover rather than an \'etale cover.
-
-\bibliographystyle{amsalpha}
-\bibliography{bibliography/Biblio}
-
-\end{document}
 

### 2014-08-19 dictionary.tex
Changes to Applications

@@
 Write $\m$ for the maximal ideal of $R$ and $K$ for the quotient field for $R$.
-Set $R_n = R/\m^{n+1}$ and $S_n = \Spec{R_n}$ and $S = \Spec{R}$; 
+Set $S = \Spec{R}$.
+For every non-negative integer $n$, set $R_n = R/\m^{n+1}$ and $S_n = \Spec{R_n}$;  
 note that $S_0 = \Spec{\Fq}$ is the special fibre of $S$.
@@
 for the functor produced by composing pullback along $S_n \to S$ with the Greenberg functor. 
-This functor respects \'etale morphisms, smooth morphisms and geometric components, \todo{open immersions?
-closed immersion?} and
+This functor respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components, and
 \[
@@
 For any $n\leq m$,  the surjective ring homomorphism $R_{m} \to R_n$ determines a
-natural transformation $\Gr_{m} \to \Gr_n$ between additive functors.
-Crucially, $(\Gr_{m}\to \Gr_n)(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
+natural transformation $P_{n\leq m} : \Gr_{m} \to \Gr_n$ between additive functors.
+Crucially, $P_{n\leq m}(X): \Gr_{m}(X)\to \Gr_n(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
 This observation is key to the proof that, for any $X$ lft over $S$, the projective limit 
@@
 \]
-taken with respect to the surjective morphisms $(\Gr_{m}\to \Gr_n)(X)$,
+taken with respect to the surjective morphisms $P_{n\leq m}(X) : \Gr_{m}(X) \to \Gr_n(X)$,
 exists in the category of group schemes over $\Fq$.
@@
 \]
-The Greenberg transform $\Gr$ respects \'etale morphisms, smooth morphisms  \todo{open immersions? closed immersion?} and geometric components, and
+The Greenberg transform respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components, and
 \[
@@
 
-Now suppose $X_K$ is a commutative algebraic group over $K$ 
-that admits a Neron model, $X$.
+Now suppose $X_K$ is a connected commutative algebraic group over $K$ with Neron model $X$ over $R$.
 Then $\Gr(X)$ is commutative group scheme over $\Fq$
 with component group scheme
-$\pi_0(\Gr(X))= \pi_0(X) \times_S S_0$
-and
+\[
+\pi_0(\Gr(X))= \pi_0(X) \times_S S_0
+\]
+and $\Fq$-rational points
 \[
@@
 
-A {\it quasicharacter sheaf for $X_K$} is a triple
+Consider the category $\mathcal{C}(\Gr(X))$ of triples
 $\qcs{F}\ceq (\gqcs{F},\mu_\qcs{F},\phi_\qcs{F})$ where
 \begin{enumerate}
-\item[(0)] $\gqcs{F}$ is a constructible $\ell$-adic sheaf on $\Gr(X)_{\bFq} \ceq \Gr(X)\otimes \bFq$,
-\item[(1)]  $\mu_\qcs{F}: \bm^* \gqcs{F} \to \gqcs{F}\boxtimes\gqcs{F}$ is an isomorphism $\ell$-adic sheaves, where $\bm : \Gr(X)_{\bFq} \times \Gr(X)_{\bFq} \to \Gr(X)_{\bFq}$ is multiplication for $\Gr(X)_{\bFq}$,
-\item[(2)] $\phi_\qcs{F} : \Frob{\Gr(X)}^* \gqcs{F} \to \gqcs{F}$ is an
+\labitem{(C.0)}{C.0} $\gqcs{F}$ is a $\ell$-adic local system on $\Gr(X)_{\bFq} \ceq \Gr(X)\times_\Spec{\Fq} \Spec{\bFq}$,
+\labitem{(C.1)}{C.1} $\mu_\qcs{F}: \bm^* \gqcs{F} \to \gqcs{F}\boxtimes\gqcs{F}$ is an isomorphism $\ell$-adic sheaves, where $\bm : \Gr(X)_{\bFq} \times \Gr(X)_{\bFq} \to \Gr(X)_{\bFq}$ is multiplication for $\Gr(X)_{\bFq}$,
+\labitem{(C.2)}{C.2} $\phi_\qcs{F} : \Frob{\Gr(X)}^* \gqcs{F} \to \gqcs{F}$ is an
   isomorphism of constructible $\ell$-adic sheaves, where $\Frob{\Gr(X)}^* : \Gr(X)_{\bFq}  \to \Gr(X)_{\bFq}$ is Frobenius for $\Gr(X)_{\bFq}$,
 \end{enumerate}
-such that, for some $n\in \NN_0$,
-\begin{enumerate}
-\item[(3)]
-$\qcs{F} = P_n(X)^*\qcs{L}$ for some quasicharacter sheaf $\qcs{L}$ on $\Gr_n(X)$, where pull-back by $P_n(X)$ is defined as in Proposition~\ref{prop:pullback}.
-\end{enumerate}
-
-\begin{theorem}
+subject to the conditions as in \ref{QC.1} and \ref{QC.2},
+with morphisms defined as in \ref{QC.3}.
+This category is rigid monoidal, with tensor product defined as in Definition~\ref{def:QC}.
+
+For every non-negative integer $n$, the morphism of $\Fq$-schemes $P_n(X) : \Gr(X) \to \Gr_n(N)$ induces a functor
+\[
+P_n(X)^* : \QC(\Gr_n(X)) \to \mathcal{C}(\Gr(X)),
+\]
+as in Proposition~\ref{prop:pullback}.
+This functor is full and faithful, so we may view $\QC(\Gr_n(X))$ as a full subcategory of $\mathcal{C}(\Gr(X))$.
+
+A {\it quasicharacter sheaf on $\Gr(X)$} is an object $\qcs{F}$ in $\mathcal{C}(\Gr(X))$ such that $\qcs{F} \iso P_n(X)^*\qcs{L}$ for some quasicharacter sheaf $\qcs{L}$ on $\Gr_n(X)$.
+Quasicharacter sheaves on $\Gr(X)$ form a rigid monoidal category in the obvious way, denoted by $\QC(\Gr(X))$.
+Note that we may view $\QC(\Gr(X))$ a `union' (colimit) of the subcategories $\QC(\Gr_n(X))$ in $\mathcal{C}(\Gr(X))$.
+
+\begin{theorem}\label{thm:QCX}
 Let $X_K$ be a commutative algebraic group over $K$ with Neron model $X$ over $R$. 
 \begin{enumerate}
-\item[(0)] Quasicharacter sheaves for $X_K$ form a rigid monoidal category, $\QC(X_K)$, in a natural way. 
 \item[(1)] There is a canonical short exact sequence of abelian groups 
 \[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{X_K} \to \Hom_\text{ad}(X_K(K),\EEx) \to 0
-\] 
-where $\Hom_\text{ad}(X_K(K),\EEx)$ is the group of characters of $X_K(K)$ that factor through $X(R)\to X(R_n)$, for some $n\in\NN_0$.
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{\Gr(X)} \to \Hom_\text{ad}(X_K(K),\EEx) \to 0
+\] 
+where $\Hom_\text{ad}(X_K(K),\EEx)$ is the group of homomorphisms $X_K(K)\to \EEx$ that factor through $X_K(X) = X(R)\to X(R_n)$, for some $n\in\NN_0$.
 \item[(2)] For all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ for $X_K$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism.
@@
 \[
-\Aut(\qcs{L}) \iso \Hom((\pi_0(X)_{\Fq})_{\Weil{}},\EEx),
+\Aut(\qcs{F}) \iso \Hom((\pi_0(X)_{\Fq})_{\Weil{}},\EEx),
 \]
@@
 \end{theorem}
+
+\begin{proof}
+To begin, fix $n\in \NN_0$. 
+The following statements follow directly from Theorems~\ref{thm:snake} and \ref{thm:autornaught} together with our observations about the component group of $\Gr_n(X)$.
+\begin{enumerate}
+\item[(1)] There is a canonical short exact sequence of abelian groups 
+\[
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{\Gr_n(X)} \to \Hom(X(R_n),\EEx) \to 0.
+\] 
+\item[(2)] For all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $\Gr_n(X)$ and for every $\rho \in \Hom(\qcs{L},\qcs{L}')$, either $\rho$ is trivial or $\rho$ is an isomorphism.
+\item[(3)] For all quasicharacter sheaves $\qcs{L}$ on $\Gr_n(X)$,
+\[
+\Aut(\qcs{L}) \iso \Hom((\pi_0(X)_{\Fq})_{\Weil{}},\EEx),
+\]
+canonically.
+\end{enumerate}
+So Theorem~\ref{thm:QCX} follows from 
+\[
+\QCiso{\Gr(X)} = \varinjlim_{n\in \NN_0} \QCiso{\Gr_n(X)}
+\]
+ and the definition of $\Hom_\text{ad}(X_K(K),\EEx)$.
+\end{proof}
+
+\subsection{Base change of quasicharacters}
+
+\subsection{Transfer of quasicharacters}
 

### 2014-08-20 dictionary.tex
Changes to Applications: QC(Gr(X)
Changes to Applications. Removed dead fragments.
Still working on Applications; getting it ready for our meeting this
afternoon.

--- 2014-08-19 dictionary.tex
@@
 
-\title[The function--sheaf dictionary]{The function--sheaf dictionary for smooth commutative group schemes over finite fields}
+\title[The function--sheaf dictionary, with applications over local fields]{The function--sheaf dictionary for smooth commutative group schemes over finite fields, with applications over local fields}
 
@@
 The ability to work with non-connected group schemes,
-of which the component group of the special fibre of the Neron model of a torus is an important example,
+of which the component group of the special fibre of the Néron model of a torus is an important example,
 plays a crucial role in this application,
@@
 
-Note that Proposition~\ref{prop:autornaught_etale} tells us that if $G$ is an etale commutative group scheme over $\Fq$ then every hom-set is either trivial or $\left(G(\bFq)_{\Weil{}}\right)^*$, non-canonically.
+%Note that Proposition~\ref{prop:autornaught_etale} tells us that if $G$ is an etale commutative group scheme over $\Fq$ then every hom-set is either trivial or $\{ 0 \} \cup \left(G(\bFq)_{\Weil{}}\right)^*$, non-canonically.
 
@@
 
-In this section we find $\QCiso{G}$ and $\Hom(\qcs{L},\qcs{L}')$ for every smooth commutative group scheme over $\Fq$; note that we found these in Section~\ref{sec:etale} when $G$ is etale.
+%In this section we find $\QCiso{G}$ and $\Aut(\qcs{L})$ for commutative algebraic group over $\Fq$; note that we found these in Section~\ref{sec:etale} when $G$ is etale.
 
@@
  \item $\Aut(\qcs{L}) = 1$, for all quasicharacter sheaves $\qcs{L}$ on $G$;
-  \item every $\rho \in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism,
-  for all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $G$.
+  \item for all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $G$ and for every $\rho \in \Hom(\qcs{L},\qcs{L}')$, either $\rho$ is trivial or an isomorphism.
  \end{enumerate}
@@
 
-We say that a morphism $f : H\to G$ of commutative group $\Fq$-schemes is a {\it discrete isogeny} to $G$ if it is a finite, surjective \'etale morphism and
+%We say that a morphism $f : H\to G$ of commutative group $\Fq$-schemes is a {\it discrete isogeny} to $G$ if it is a finite, surjective \'etale morphism and
 the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f$ is trivial.
@@
 \begin{theorem}\label{thm:autornaught}
-Let $G$ be a smooth, commutative group scheme over $\Fq$.
+Let $G$ be a smooth commutative group scheme over $\Fq$.
 For all quasicharacter sheaves $\qcs{L}$ and $\qcs{L}'$ on $G$,
@@
 
-in this section we use quasicharacter sheaves to geometrize and categorify the group 
-of admissible characters of smooth commutative group schemes over local fields that admit Neron models.
-
-Let $R$ complete discrete valuation ring $R$ with residue field $\Fq$.
+In this section we use quasicharacter sheaves to geometrize and categorify the group 
+of admissible characters of smooth commutative group schemes over local fields that admit Néron models.
+
+Let $R$ be a complete discrete valuation ring $R$ with residue field $\Fq$.
 Write $\m$ for the maximal ideal of $R$ and $K$ for the quotient field for $R$.
-Set $R_n = R/\m^{n+1}$ and $S_n = \Spec{R_n}$ and $S = \Spec{R}$; 
+Set $S = \Spec{R}$.
+For every non-negative integer $n$, set $R_n = R/\m^{n+1}$ and $S_n = \Spec{R_n}$;  
 note that $S_0 = \Spec{\Fq}$ is the special fibre of $S$.
 
-\subsection{Greenberg transform}
+\subsection{Review of the Greenberg transform}
 
@@
 \[
-\Gr_n : \partop{\text{Schemes}}{\text{lft over $R$}} \to \partop{\text{Schemes}}{\text{lft over $\Fq$}}
+\Gr^R_n : \partop{\text{Schemes}}{\text{lft over $R$}} \to \partop{\text{Schemes}}{\text{lft over $\Fq$}}
 \]
 for the functor produced by composing pullback along $S_n \to S$ with the Greenberg functor. 
-This functor respects \'etale morphisms, smooth morphisms and geometric components, \todo{open immersions?
-closed immersion?} and
-\[
-\Gr_n(X)(\Fq) \iso X(R_n),
+This functor respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components, and
+\[
+\Gr^R_n(X)(\Fq) \iso X(R_n),
 \]
@@
 For any $n\leq m$,  the surjective ring homomorphism $R_{m} \to R_n$ determines a
-natural transformation $\Gr_{m} \to \Gr_n$ between additive functors.
-Crucially, $(\Gr_{m}\to \Gr_n)(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
+natural transformation $P^R_{n\leq m} : \Gr^R_{m} \to \Gr^R_n$ between additive functors.
+Crucially, $P^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
 This observation is key to the proof that, for any $X$ lft over $S$, the projective limit 
 \[
-\Gr(X) \ceq \varprojlim_{n\in \NN_0} \Gr_n(X)
-\]
-taken with respect to the surjective morphisms $(\Gr_{m}\to \Gr_n)(X)$,
+\Gr_R(X) \ceq \varprojlim_{n\in \NN_0} \Gr^R_n(X)
+\]
+taken with respect to the surjective morphisms $P^R_{n\leq m}(X) : \Gr^R_{m}(X) \to \Gr^R_n(X)$,
 exists in the category of group schemes over $\Fq$.
-This leads to the definition of what we call the {\it Greenberg transform}:
-\[
-\Gr : \partop{\text{Schemes}}{\text{lft over $R$}} \to \partop{\text{Schemes}}{\text{lft over $\Fq$}}.
-\]
-By construction, the $\Fq$-scheme $\Gr(X)$ comes equipped with morphisms 
-\[
-P_n(X) : \Gr(X) \to \Gr_n(X),\qquad \forall n\in \NN_0.
-\]
-The Greenberg transform $\Gr$ respects \'etale morphisms, smooth morphisms  \todo{open immersions? closed immersion?} and geometric components, and
-\[
-\Gr(X)(\Fq) \iso X(R),
+This leads to the definition of what we shall call the {\it Greenberg transform}:
+\[
+\Gr_R : \partop{\text{Schemes}}{\text{lft over $R$}} \to \partop{\text{Schemes}}{\text{lft over $\Fq$}}.
+\]
+By construction, the $\Fq$-scheme $\Gr_R(X)$ comes equipped with morphisms 
+\[
+P^R_n(X) : \Gr^R(X) \to \Gr^R_n(X),\qquad \forall n\in \NN_0.
+\]
+The Greenberg transform respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components, and
+\[
+\Gr_R(X)(\Fq) \iso X(R),
 \]
@@
 
-\subsection{Quasicharacter sheaves on the Greenberg transform of a Neron model}
-
-Now suppose $X_K$ is a commutative algebraic group over $K$ 
-that admits a Neron model, $X$.
-Then $\Gr(X)$ is commutative group scheme over $\Fq$
+\subsection{Quasicharacter sheaves on the Greenberg transform of a Néron model}
+
+Let $G$ be a commutative group scheme over $\Fq$.
+Consider the category $\mathcal{C}(G)$ of triples
+$\qcs{F}\ceq (\gqcs{F},\mu_\qcs{F},\phi_\qcs{F})$ where
+\begin{enumerate}
+\labitem{(C.0)}{C.0} $\gqcs{F}$ is a rank one $\ell$-adic local system on $\bG\ceq G \times_\Spec{\Fq} \Spec{\bFq}$,
+\labitem{(C.1)}{C.1} $\mu_\qcs{F}: \bm^* \gqcs{F} \to \gqcs{F}\boxtimes\gqcs{F}$ is an isomorphism $\ell$-adic sheaves, where $\bm : \bG \times \bG \to \bG$ is multiplication $m$ for $G$ extended to $\bG$.
+\labitem{(C.2)}{C.2} $\phi_\qcs{F} : \Frob{G}^* \gqcs{F} \to \gqcs{F}$ is an isomorphism of constructible $\ell$-adic sheaves, where $\Frob{G}^* : \bG  \to \bG$ is Frobenius,
+\end{enumerate}
+subject to the conditions as in \ref{QC.1} and \ref{QC.2},
+with morphisms defined as in \ref{QC.3}.
+This category $\mathcal{C}(G)$ is rigid monoidal, with tensor product defined as in Definition~\ref{def:QC}. Note that $\mathcal{C}(G) = \QC(G)$ if $G$ is also smooth.
+
+Now suppose $X_K$ is a connected commutative algebraic group over $K$ that admits a Néron model $X$ over $R$.
+
+A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) = X(R)\to X(R_n)$, for some $n\in\NN_0$;
+the group of quasicharacters of $X_K(K)$ will be denoted by $\Hom_\text{qc}(X_K(K),\EEx)$.
+
+Then $\Gr_R(X)$ is commutative group scheme over $\Fq$
 with component group scheme
-$\pi_0(\Gr(X))= \pi_0(X) \times_S S_0$
-and
-\[
-\Gr(X)(\Fq)\iso X_K(K)
+\[
+\pi_0(\Gr_R(X))= \pi_0(X) \times_S S_0
+\]
+and $\Fq$-rational points
+\[
+\Gr_R(X)(\Fq)\iso X_K(K),
 \]
@@
 For every $n\in \NN_0$,
-$\Gr_n(X)$ is {\it smooth} commutative group scheme over $\Fq$
+$\Gr^R_n(X)$ is {\it smooth} commutative group scheme over $\Fq$
 with component group scheme
-$\pi_0(\Gr_n(X))= \pi_0(X) \times_S S_0$.
-
-A {\it quasicharacter sheaf for $X_K$} is a triple
-$\qcs{F}\ceq (\gqcs{F},\mu_\qcs{F},\phi_\qcs{F})$ where
+$\pi_0(\Gr^R_n(X))= \pi_0(X) \times_S S_0$.
+
+For every non-negative integer $n$, the morphism of $\Fq$-schemes $P^R_n(X) : \Gr_R(X) \to \Gr^R_n(N)$ induces a functor
+\[
+P^R_n(X)^* : \QC(\Gr^R_n(X)) \to \mathcal{C}(\Gr_R(X)),
+\]
+as in Proposition~\ref{prop:pullback}.
+This functor is full and faithful, so we may view $\QC(\Gr^R_n(X))$ as a full subcategory of $\mathcal{C}(\Gr_R(X))$.
+
+\begin{definition}
+A {\it quasicharacter sheaf on $\Gr_R(X)$} is an object $\qcs{F}$ in $\mathcal{C}(\Gr_R(X))$ such that $\qcs{F} \iso P^R_n(X)^*\qcs{L}$ for some quasicharacter sheaf $\qcs{L}$ on $\Gr^R_n(X)$.
+Quasicharacter sheaves on $\Gr_R(X)$ form a rigid monoidal category in the obvious way, denoted by $\QC(\Gr_R(X))$.
+\end{definition}
+
+Note that we may informally regard $\QC(\Gr_R(X))$ a `union' of the full subcategories $\QC(\Gr^R_n(X))$ in $\mathcal{C}(\Gr_R(X))$.
+
+\begin{theorem}\label{thm:QCX}
+Let $X_K$ be a commutative algebraic group over $K$ with Néron model $X$ over $R$. 
 \begin{enumerate}
-\item[(0)] $\gqcs{F}$ is a constructible $\ell$-adic sheaf on $\Gr(X)_{\bFq} \ceq \Gr(X)\otimes \bFq$,
-\item[(1)]  $\mu_\qcs{F}: \bm^* \gqcs{F} \to \gqcs{F}\boxtimes\gqcs{F}$ is an isomorphism $\ell$-adic sheaves, where $\bm : \Gr(X)_{\bFq} \times \Gr(X)_{\bFq} \to \Gr(X)_{\bFq}$ is multiplication for $\Gr(X)_{\bFq}$,
-\item[(2)] $\phi_\qcs{F} : \Frob{\Gr(X)}^* \gqcs{F} \to \gqcs{F}$ is an
-  isomorphism of constructible $\ell$-adic sheaves, where $\Frob{\Gr(X)}^* : \Gr(X)_{\bFq}  \to \Gr(X)_{\bFq}$ is Frobenius for $\Gr(X)_{\bFq}$,
-\end{enumerate}
-such that, for some $n\in \NN_0$,
-\begin{enumerate}
-\item[(3)]
-$\qcs{F} = P_n(X)^*\qcs{L}$ for some quasicharacter sheaf $\qcs{L}$ on $\Gr_n(X)$, where pull-back by $P_n(X)$ is defined as in Proposition~\ref{prop:pullback}.
-\end{enumerate}
-
-\begin{theorem}
-Let $X_K$ be a commutative algebraic group over $K$ with Neron model $X$ over $R$. 
-\begin{enumerate}
-\item[(0)] Quasicharacter sheaves for $X_K$ form a rigid monoidal category, $\QC(X_K)$, in a natural way. 
 \item[(1)] There is a canonical short exact sequence of abelian groups 
 \[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{X_K} \to \Hom_\text{ad}(X_K(K),\EEx) \to 0
-\] 
-where $\Hom_\text{ad}(X_K(K),\EEx)$ is the group of characters of $X_K(K)$ that factor through $X(R)\to X(R_n)$, for some $n\in\NN_0$.
-\item[(2)] For all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ for $X_K$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism.
-\item[(3)] For all quasicharacter sheaves $\qcs{F}$ for $X_K$,
-\[
-\Aut(\qcs{L}) \iso \Hom((\pi_0(X)_{\Fq})_{\Weil{}},\EEx),
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{\Gr_R(X)} \to \Hom_\text{qc}(X_K(K),\EEx) \to 0.
+\] 
+\item[(2)] For all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism.
+\item[(3)] For all quasicharacter sheaves $\qcs{F}$ on $\Gr_R(X)$,
+\[
+\Aut(\qcs{F}) \iso \Hom((\pi_0(X)_{\Fq})_{\Weil{}},\EEx),
 \]
@@
 
+\begin{proof}
+To begin, fix $n\in \NN$.
+The following statements follow directly from Theorems~\ref{thm:snake} and \ref{thm:autornaught} together with our observations about the component group of $\Gr^R_n(X)$.
+\begin{enumerate}
+\item[(1)] There is a canonical short exact sequence of abelian groups 
+\[
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{\Gr^R_n(X)} \to \Hom(X(R_n),\EEx) \to 0.
+\] 
+\item[(2)] For all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $\Gr^R_n(X)$ and for every $\rho \in \Hom(\qcs{L},\qcs{L}')$, either $\rho$ is trivial or $\rho$ is an isomorphism.
+\item[(3)] For all quasicharacter sheaves $\qcs{L}$ on $\Gr^R_n(X)$,
+\[
+\Aut(\qcs{L}) \iso \Hom((\pi_0(X)_{\Fq})_{\Weil{}},\EEx),
+\]
+canonically.
+\end{enumerate}
+So Theorem~\ref{thm:QCX} now follows from the fact that each $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(\Gr_R(X))$ and the observation that $\QC(\Gr_R(X))$ a `union' of the subcategories $\QC(\Gr^R_n(X))$ in $\mathcal{C}(\Gr_R(X))$.
+\end{proof}
+
+\subsection{Weil restriction and quasicharacters}\label{sec:wrK}
+
+Let $K'/K$ be a finite Galois extension of local fields and
+let $k'/k$ be the corresponding extension of residue fields.
+Let $R$ and $R'$ be the rings of integers of $K$ and $K'$, respectively.
+Let $X_K$ be a connected commutative algebraic group over $K$
+that admits a Néron model $X$ over $R$.
+Set $X_{K'} \ceq X_K \times_\Spec{K} \Spec{K'}$
+and $X' \ceq X \times_\Spec{R} \Spec{R'}$.
+
+\begin{proposition}\label{prop:wrK}
+The canonical closed immersion 
+\[
+X_K \hookrightarrow \Res_{K'/K} X_{K'}
+\]
+of $K$-group schemes
+induces a map of $\Fq$-group schemes 
+\[
+f : \Gr_R(X) \to \Res_{k'/k} \Gr_{R'}(X')
+\] 
+such that the functor
+\[
+f^* : \QC(\Gr_R(X)) \to \QC(\Res_{k'/k} \Gr_{R'}(X'))
+\]
+induces
+\[
+\begin{tikzcd}[column sep=60]
+\Hom_{\text{qc}}(X_K(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{X_K(K)}} &\Hom_{\text{qc}}(X_K(K), \EEx).
+\end{tikzcd}
+\]
+\end{proposition}
+
+\begin{proof}
+Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} to include locally finite type Néron models,
+one may show that $\Res_{R'/R}(X')$ is a Néron model for $\Res_{K'/K}(X_{K'})$.
+By the Néron mapping property, the canonical closed immersion
+\[
+X_K\hookrightarrow \Res_{K'/K}(X_{K'})
+\]
+ extends uniquely to a morphism
+\[
+X\to \Res_{R'/R}(X')
+\]
+ of smooth $R$-group schemes.
+
+Applying the functor $\Gr_{n}$ to this morphism
+and using \cite{bertrapelle-gonzales:Greenberg}*{Thm 1.1} defines the morphism of smooth group schemes
+\begin{equation}\label{men}
+f_n: \Gr_{n-1}^R(X) \to \Res_{k'/k} \Gr_{en-1}^{R'}(X')
+\end{equation}
+Since 
+\[
+\left(\Res_{k'/k} \Gr_{en-1}^{R'}(X') \right)(\Fq) = \left(\Gr_{en-1}^{R'}(X')\right)(k'),
+\]
+the pullback functor 
+\[
+f_n^* : \QC(\Res_{k'/k} \Gr_{en-1}^{R'}(X'))\to \QC(\Gr_{n-1}^{R}(X))
+\]
+obtained by applying Proposition~\ref{prop:pullback} to \eqref{men} gives
+\[
+\Hom(X(R'_{en}),\EEx) \to \Hom(X(R_n),\EEx).
+\]
+Passing to the projective limit, the family of morphisms \eqref{men} determines a morphism of group schemes
+\[
+f: \Gr_R(X) \to \Res_{k'/k} \Gr_{R'}(X').
+\]
+which induces the functor
+\[
+f^* : \QC(\Res_{k'/k} \Gr_{R'}(X'))\to \QC(\Gr_{R}(X))
+\]
+inducing
+\[
+\Hom_{\text{qc}}(T(K'),\EEx) \to \Hom_{\text{qc}}(T(K),\EEx).
+\]
+Argue as in Proposition~\ref{prop:csbe} to see that this is indeed restriction of characters.
+\end{proof}
+
+\subsection{Transfer of quasicharacters}\label{sec:transfer}
+
+Let $K$ and $K'$ be local fields with rings of integers $R$ and $R'$ and residue fields $k$ and $k'$, respectively.
+Set $S = \Spec(S)$ and $S_n = \Spec(R_n)$; likewise define $S' = \Spec{R'}$ and $S'_{n'} = \Spec{R'_{n'}}$.
+
+Let $X_K$ and $X'_{K'}$ be connected commutative algebraic groups over $K$ and $K'$, respectively, that admit Néron models $X$ and $X'$ over $R$ and $R'$, respectively.
+Suppose $m$ and $m'$ are non-negative integers such that 
+\begin{equation}\label{eq:schematic_transfer}
+R_m \iso R'_{m'}
+\qquad
+\text{and}
+\qquad
+X \times_{S} S_m \iso X' \times_{S'} S'_{m'}.
+\end{equation}
+as smooth group schemes over $R_m$. 
+Then
+$
+\Gr^R_m(X) \iso \Gr^{R'}_{m'}(X')
+$
+as smooth group schemes over $\Fq$ and, by Proposition~\ref{prop:pullback} the isomorphism above determines an equivalence of categories
+\begin{equation}\label{eq:categorical_transfer}
+\QC(\Gr^R_m(X)) \cong \QC(\Gr^{R'}_{m'}(X'))
+\end{equation}
+which induces a group isomorphism
+$
+\QCiso{\Gr^R_m(X)} \cong \QCiso{\Gr^{R'}_{m'}(X')}
+$
+and thence, by trace of Frobenius, an isomorphism
+\begin{equation}\label{eq:transfer}
+\Hom(X(R_m),\EEx) \iso \Hom(X'(R'_{m'}),\EEx).
+\end{equation}
+Recall that $\Hom(X(R_m),\EEx)$ is a subgroup of $\Hom_\text{qc}(X_K(K),\EEx)$ and $\Hom(X'(R'_{m'}),\EEx)$ is a subgroup of $\Hom_\text{qc}(X_K(K),\EEx)$.
+The isomorphism \eqref{eq:transfer} is an instance of {\it transfer} of certain quasicharacters between $X_K(K)$ and $X_{K'}(K')$.
+
+Such a relationship can exist between quasicharacters of algebraic tori over local fields, even when the characteristics of $K$ and $K'$ differ
+\citelist{\cite{chai-yu:01a} \cite{deligne:84a}*{\S 1}}.
+
+Suppose $T$ and $T'$ are tori over non-archimedian local fields $K$ and $K'$,
+splitting over $L$ and $L'$ respectively.
+Then $T$ and $T'$ are said to be \emph{$N$-congruent} \cite{chai-yu:01a}*{\S 2} if there are isomorphisms
+ \begin{align*}
+  \alpha : \OL/\pi_K^N \OL &\to \OO{L'}/\pi_{K'}^N \OO{L'} \\
+  \beta : \Gal(L/K) &\to \Gal(L'/K') \\
+  \phi : X^*(T) &\to X^*(T')
+ \end{align*}
+ satisfying the conditions
+ \begin{enumerate}
+  \item $\alpha$ induces an isomorphism $\OK/\pi_K^N \OK \to \OO{K'}/\pi_{K'}^N \OO{K'}$,
+  \item $\alpha$ is $\Gal(L/K)$-equivariant relative to $\beta$, and
+  \item $\phi$ is $\Gal(L/K)$-equivariant relative to $\beta$.
+ \end{enumerate}
+If $T$ and $T'$ are $N$-congruent then $\alpha$, $\beta$ and $\phi$ determine an isomorphism
+\begin{equation}\label{transfer}
+  \Hom_N(T(K), \EEx) \iso \Hom_N(T'(K'),\EEx).
+\end{equation}
+Note that if $T$ and $T'$ are $N$-congruent, then they are $N'$ congruent for every
+$N' \leq N$, the isomorphism \eqref{transfer} is depth-preserving at integers less than $N$.
+
+One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes between the
+$\TT_n$ and $\TT'_n$ assuming that $T$ and $T'$ are sufficiently congruent.
+They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the
+Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}.
+Then it follows from \cite{chai-yu:01a}*{Thm. 8.5} that if $N > 3h$ and $T$ and $T'$ are $N$-congruent
+then there is a canonical isomorphism of smooth group schemes
+ $
+  \TT_{N-3h} \to \TT'_{N-3h}
+ $
+ determined by $\alpha, \beta$ and $\phi$.
+Combining this with Theorem~\ref{thm:application} gives the geometrization and categorification of the transfer of characters.
+
+\begin{proposition}\label{prop:transfer}
+ With notation above, suppose that $T$ and $T'$ are $N$-congruent and $N > 3h$.  Set $n \ceq N-3h$.
+ Then there is a canonical equivalence of categories
+ \[
+  \QC(\GN{T}'_{n}) \to \QC(\GN{T}_{n})
+ \]
+ determined by $\alpha, \beta$ and $\phi$ inducing the isomorphism
+ \[
+  \Hom_{<n}(T'(K'), \EEx) \to \Hom_{<n}(T(K), \EEx)
+ \]
+ through the trace of Frobenius.
+\end{proposition}
+
+\subsection{Algebraic tori and Abelian varieties over local fields}
+
+\begin{corollary}\label{cor:application}
+For every algebraic torus $T$ over $K$, the trace of Frobenius
+  \[
+\trFrob{T}:  \QCiso{\GN{T}} \to \Hom_{\text{qc}}(T(K),\EEx)
+  \]
+is an isomomorphism.
+Moreover, the isomorphism $\trFrob{T}$ is a natural transformation
+between the additive functors
+\begin{enumerate}
+\item[$F_{\QC}$:] $T \mapsto \QCiso{\GN{T}}$
+\item[$F_{\text{qc}}$:] $T \mapsto \Hom_{\text{qc}}(T(K),\EEx)$
+\end{enumerate}
+from the additive category of algebraic tori over $K$ to the category of abelian groups.
+\end{corollary}
+
 \bibliographystyle{amsalpha}
@@
 \end{document}
-
-\section{Fragments}
-
-\subsection{Finite and bounded - fragments}
-
-On general smooth group $\Fq$-schemes $G$, 
-there are bounded quasicharacter sheaves which are not finite.  
-Identifying $\fQC(G)$ with its image under $B_G \circ L_G$, as defined in
-Proposition~\ref{prop:BG} and in the proof of Proposition~\ref{prop:bounded},
-we will see in Corollary~\ref{cor:bounded-and-finite} that
-a quasicharacter sheaf is finite if and only if its Trace of Frobenius has finite image.
-
-\begin{corollary} \label{cor:bounded-and-finite}
-Let $G$ be a smooth commutative group scheme over $\Fq$.
-\begin{enumerate}
-\item $\qcs{L} \in \QC(G)$ is bounded if and only if $\trFrob{\qcs{L}}$ has bounded image,
-\item $\qcs{L}\in \QC(G)$ is finite if and only if $\trFrob{\qcs{L}}$ has finite image.
-\end{enumerate}
-\end{corollary}
-
-\begin{proof}
-We first reduce to the case that $G$ is etale.
-On the connected component
-$G^0$, all quasicharacter sheaves are bounded and finite by Proposition~\ref{prop:connected}.
-On the other hand, $G^0(\Fq)$ is finite by Lemma~\ref{lem:G0alg-grp} and thus Trace of Frobenius
-has finite and therefore bounded image.  If $\chi \in G(\Fq)^*$ then there is some finite-image character $\chi_0$
-with the same restriction to $G^0(\Fq)$ since $G^0(\Fq)$ is lies inside the torsion part of
-the finitely generated abelian group $G(\Fq)$.  Therefore $\chi$ is bounded (resp. has finite image)
-if and only if $\chi \cdot \chi_0^{-1}$ is bounded (resp. has finite image).  But $\chi \cdot \chi_0^{-1}$ descends
-to a character of $\pi_0(G)$.  A similar argument relates boundedness/finiteness of quasicharacter
-sheaves on $G$ to those on $\pi_0(G)$, using the fact that the preimage constructed in the proof of
-Proposition~\ref{prop:restriction} is a finite quasicharacter sheaf on $G$.
-Using these equivalences, it is enough to prove Corollary~\ref{cor:bounded-and-finite} when $G$ is etale.
-
-In the case that $G$ is \'etale, which we now suppose,
-one can easily detect when a quasicharacter sheaf is bounded or finite.
-With reference to Section~\ref{sec:S},
-let $S_G(\qcs{L}) = [\alpha \oplus \beta]$
-and let $b : {\bar G}\to \EEx$ be the multiplicative version of $\beta(\Frob{})$.
-Then $\qcs{L}$ is finite if and only if
-$b(x)$ is a root of unity for all $x\in {\bar G}$.
-By \cite{beilinson-bernstein-deligne:81a}*{Rem. 5.2.1},
-$\qcs{L}$ is bounded if and only if $b(x) \in \Zlx$ for all $x\in {\bar G}$.
-\end{proof}
-
-With Corollary~\ref{cor:bounded-and-finite} in hand
-we see that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves
-when $G$ is a commutative algebraic group over $\Fq$;
-observe that the component group $\pi_0({\bar G})$ is finite in this case.
-On the other hand, Corollary~\ref{cor:bounded-and-finite} also shows us
-why neither finite quasicharacter sheaves nor bounded quasicharacter sheaves
-are up to the task of geometrizing all characters of $G(\Fq)$ for smooth commutative group schemes $G$ since, in general, neither of the full subcategories
-$\fQC(G) \subset \bQC(G) \subset \QC(G)$ are equivalences.
-For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$:
-the flabby quasicharacter sheaf on $G$ corresponding, under Theorem~\ref{thm:snake},
-to the character $1 \mapsto \ell$ is not a bounded quasicharacter sheaf,
-while the flabby quasicharacter sheaf on $G$ corresponding
-to the character $1 \mapsto 1+ \ell$ is a bounded but not finite quasicharacter sheaf.
-%In this latter case the stalk of the quasicharacter sheaf at the component $1$ is defined by a pro-\'etale cover rather than an \'etale cover.
 
@@
 
-\begin{proof}
-Here are some pieces that might help . . .
-
-Consider Diagram~\ref{diagram}, where $B=G$, $C= \pi_0(G)$ and $A=G^0$:
-We have just seen that the back of this diagram commutes and its sequences are exact.
-The front of this diagram also commutes and all its vertical sequences are also exact,
-as we saw in Section~\ref{sec:spectral}.
-Joining the back to the front are the injections from
-Section~\ref{sec:spectral} making the entire diagram commute.
-The vertical left face is an isomorphism of exact sequences by Proposition~\ref{prop:etale-iso}
-and the vertical right face is an isomorphism of exact sequences by Proposition~\ref{prop:connected-iso}.
-%
-Note that these injections are isomorphisms at the bottom, by Lemma~\ref{lem:dual-inv}, and at the left, by Section~\ref{sec:etale}, and at the right, by Section~\ref{sec:connected} and the Five Lemma.
-It now follows that $\ker T_B \to \Hh^0(\Weil{},\Hh^2(B,\EEx))$ is also an isomorphism,
-completing the proof of Theorem~\ref{thm:snake}.
-\end{proof}
-
-\begin{corollary}\label{cor:exact}
-  If $G$ is a smooth, commutative group scheme over
-  $\Fq$ then pullback yields an exact sequence
-\[
-\Hh^1(E^\bullet_{G^0}) \to \QCiso{\pi_0(G)} \to \QCiso{G} \to \QCiso{G^0} \to 0
-\]
-of abelian groups.\todo{Pure speculation.}
-\end{corollary}
-
-\begin{proof}
-Really? Then does this make sense: $\Hh^3(E^\bullet_{\pi_0(G)}) =0$? Perhaps. $\Hh^3(\pi_0({\bar G})\rtimes \Weil{},\EEx)=0?$
-\end{proof}
-
-\subsection{Finite quasicharacter sheaves}\label{sec:finite}
-
-In this section we define \emph{finite quasicharacter sheaves}, 
-a notion informed by a certain perspective on local systems on connected groups.
-Finite quasicharacter sheaves will play a role in Section \ref{sec:restriction}.
-
-%The definition of finite quasicharacter sheaves will require several steps, beginning with the localization of a category introduced here.
-Consider the category $C(G)$ whose objects consist of triples $(f,\psi,r)$, where:
-\begin{itemize}
-\item $f : H\to G$ is a \emph{discrete isogeny} (a morphism of smooth commutative group schemes over $\Fq$ which is finite, surjective and \'etale and for which the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f = f^{-1}({\bar e)} = \Aut(f)$ is trivial);
-\item $\psi : \Aut(f)\to \Aut(V)$ is a finite-dimensional $\EE$-representation;
-\item $r : V \to V\otimes V$ is an injective linear transformation.
-\end{itemize}
-A morphism $(f,\psi,r) \to (f',\psi',r)$ in $C(G)$ is a pair $(\gamma,T)$, where:
-\begin{itemize}
-\item $\gamma : H' \to H$ is a morphism of group schemes such that $f\circ \gamma = f'$;
-\item $T: V\to V'$ is a linear transformation, equivariant for the action of
-$\Aut(f')$ on $V'$ by $\psi'$ and the action of $\Aut(f')$ on $V$ by $\psi \circ \gamma$,
-\end{itemize}
-such that
-\[
-\begin{tikzcd}
-\arrow{d}[swap]{T\otimes T} V\otimes V & \arrow{l}{r} V \arrow{d}{T} 
-%& \Aut(V) & \arrow[swap]{l}{\psi} \Aut(f) \arrow{r} & H \arrow{r}{f} & \arrow[equal]{d} G
-\\
-V'\otimes V' & \arrow{l}{r'} V' 
-%& \Aut(V') & \arrow[swap]{l}{\psi'} \arrow[swap]{u}{} \Aut(f') \arrow{r} & \arrow[swap]{u}{\gamma} H' \arrow{r}{f'} & G
-\end{tikzcd}
-\]
-commutes.
-
-We define a tensor product in $C(G)$ as follows.
-Let $(f,\psi,r)$ and $(f',\psi',r')$ be objects in $C(G)$.
-Write $f\times_G f' : H\times_G H' \to G$ for the product of $f$ and $f'$
-in the category of isogenies to $G$. We define an external tensor product
-$\psi \otimes\psi' :  \ker(f\times_G f') \to \Aut(V\otimes V')$ and a external sum
-$\psi \oplus\psi' :  \ker(f\times_G f') \to \Aut(V\oplus V')$
-using the canonical isomorphism $\ker(f\times_G f') \iso (\ker f)\times (\ker f')$.
-We may thus define $(f,\psi,r)\otimes(f',\psi',r') \ceq (f\times_G f' ,\psi\otimes\psi', r\otimes r')$ and
-$(f,\psi,r)\oplus(f',\psi',r')\ceq (f\times_G f' ,\psi\oplus\psi', r\oplus r')$. 
-To define duals in $C(G)$,
-let $V^\vee \ceq \Hom_\text{vec}(V,\EE)$ and $\psi^\vee : \ker f \to \Aut(V^\vee)$ be
-the dual representation.  We may then set $(f,\psi,r)^\vee \ceq (f,\psi^\vee, r^\vee)$ 
-where $r^\vee : V^\vee \to V^\vee \otimes V^\vee$ is the adjoint of $r$.
-These operations give $C(G)$ the structure of a tensor category.
-
-Now we localize $C(G)$.
-Let us say that $(\gamma,T)$ in $C(G)$ is a \emph{weak isomorphism} if $T$ is an isomorphism of vector spaces.  
-Let $W$ be the family of weak isomorphism and
-et $C(G)[W^{-1}]$ be the localization of $C(G)$ with respect to $W$, 
-in the sense of \cite{kashiwara-schapira:CatgoriesSheaves}*{Def 7.1.1}.
-Since weak isomorphisms in $C(G)$ form a \emph{right multiplicative system}, in the sense of \cite{kashiwara-schapira:CatgoriesSheaves}*{Def 7.1.5}, it follows from \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16} that morphisms in $C(G)[W^{-1}]$ are simple to describe:
-a morphism in $C(G)[W^{-1}]$ is an equivalence class of diagrams
-\[
-\begin{tikzcd}[column sep=30]
-   (f,\psi,r) \arrow{r}{(\gamma,T)} & (f',\psi',r') & \arrow[swap]{l}{(\gamma_1,T_1)}[swap]{\text{w-iso}} (f_1,\psi_1,V_1)
-   \end{tikzcd}
-\]
- where $(\gamma,T) : (f,\psi,r) \to (f',\psi',r')$ is any map in $C(G)$
- and $(\gamma_1, T_1) :  (f',\psi',r') \to (f_1,\psi_1,r_1)$ is a weak isomorphism in $C(G)$;
-for the equivalence relation on these diagrams, see \cite{kashiwara-schapira:CatgoriesSheaves}*{(7.1.3)}.
-
-It is straightforward to verify that the subcategory $C_1(G)$ of $C(G)$ consisting of $(f,\psi,r)$ for which $\psi$ is one-dimensional, is a full, rigid monoidal subcategory of $C(G)$ and further, that the family $W_1$ of weak isomorphisms in $C_1(G)$ is a right multiplicative system.
-
-\begin{definition}
-The category of \emph{finite quasicharacter sheaves} of $G$, denoted by $\fQC(G)$,
-is the rigid monoidal category $C_1(G)[W_1^{-1}]$ obtained by localizing $C_1(G)$ at weak isomorphisms $W_1$.
-\end{definition}
-
-\begin{remark}
-Recall that every geometric point $\bg$ on a connected scheme $G$
-determines an equivalence between the categories of $\ell$-adic local systems on $G$
-and $\ell$-adic representations of the \'etale fundamental group $\pi_1(G, \bg)$
-\citelist{\cite{SGA5}*{VI,Prop. 1.2.5} \cite{deligne:80a}*{1.1.1}}.
- Since $\pi_1(G, \bg)$ is a projective limit of automorphism groups of finite \'etale covers,
- a general local system corresponds to a projective limit of characters of such groups.
- But some local systems can be described in terms of a single cover $f: H \to G$
- and a representation $\psi: \ker f \to \Aut(V)$;
- two such descriptions yield isomorphic local systems if and only if they are related by a weak
- isomorphism in $C(G)$.  While the description of local systems in terms of $\pi_1(G, \bg)$ does
- not adapt well to non-connected $G$, a perspective using finite \'etale covers does.
-\end{remark}
-
-Later in the paper we will make a study of isomorphism classes of objects in $\fQC(G)$. Here we focus on morphisms in this category.
-
-\begin{proposition}\label{prop:autornaught}
-Every morphism in $\fQC(G)$ is either an isomorphism or trivial.
-Moreover, for every finite quasicharacter sheaf $(f,\psi,r)$, the group $\Aut_{\fQC(G)}(f,\psi,r)$ is trivial.
-\end{proposition}
-
-\begin{proof}
-\todo{This proof is under construction.}
-Trivial morphisms in $\fQC(G)$ are defined as follows. Let $(f,\psi,r)$ and $(f_1,\psi_1,r_1)$ be finite quasicharacter sheaves on $G$.  
-Form $(f\times_G f_1,1\otimes \psi_1, r\otimes r_1)$ in $C_1(G)$. 
-Let $0 : V \to V\otimes V_1$ be the trivial linear transformation. 
-Choose $0\ne v \in V$ and let $T_v: V_1 \to V\otimes V_1$ be the isomorphism $T_v(v_1) = v\otimes v_1$.  
-Let $\pi : H\times_G H_1 \to H$ and $\pi_1 : H\times_G H_1 \to H_1$ be the natural projections.
-Then $(\pi,0) : (f,\psi, V) \to  (f\times_G f_1,1\otimes \psi_1, V\otimes V_1)$ is a morphism in $C_1(G)$ and $(\pi_1,T_v) : (f_1,\psi_1,V_1) \to (f\times_G f_1,1\otimes \psi_1, V\otimes V_1)$ is a weak isomorphism in $C_1(G)$.
-%
-The morphism in $\fQC(G)$ represented by
-\[
-\begin{tikzcd}[column sep=30]
-   (f,\psi,V) \arrow{r}{(\pi,0)} & (f\times_G f_1,1\otimes \psi_1, V\otimes V_1) & \arrow[swap]{l}{(\pi_1,T_v)}[swap]{\text{w-iso}}  (f_1,\psi_1,V_1),
-   \end{tikzcd}
-\]
-does not depend on the choice of $0\ne v\in V$; this defines the {\em trivial morphism} $0: (f,\psi,V) \to (f_1,\psi_1,V_1)$ in $\fQC(G)$.
-
-Let $(f,\psi,V)$ and $(f_1,\psi_1,V_1)$ be finite quasicharacter sheaves on $G$. 
-Let
-\[
-\begin{tikzcd}[column sep=30]
-   (f,\psi,V) \arrow{r}{(\gamma,T)} & (f',\psi',V') & \arrow[swap]{l}{(\gamma_1,T_1)}[swap]{\text{w-iso}}  (f_1,\psi_1,V_1)
-   \end{tikzcd}
-\]
-represent a morphism $(f,\psi,V)  \to (f_1,\psi_1,V_1)$ in $\fQC(G)$;
-note that, by definition, $(\gamma_1 , T_1) : (f_1,\psi_1,V_1) \to (f',\psi',V')$ is a weak isomorphism.
-Since $V$, $V'$ and $V_1$ are one-dimensional $\EE$-vector spaces, either $T : V \to V'$ is an isomorphism or trivial.
-
-Suppose $T$ is trivial. 
-Let $\theta : H'\to H\times_G H_1$ be the morphism of group schemes given by the universal property of the pull back of $f: H\to G$ and $f_1 : H_1 \to G$, as pictured below.
-\[
-\begin{tikzcd}
-\ & \arrow{ddl}[swap]{\gamma} H' \arrow{d}{\theta} \arrow{ddr}{\gamma_1} & \\
-\ & \arrow{dl}{\pi} H \times_G H_1 \arrow{dr}[swap]{\pi_1} & \\
-H \arrow{rd}[swap]{f} && \arrow{ld}{f_1} H_1 \\
-& G & \\
-\end{tikzcd}
-\]
-Let $T_1' : V\otimes V_1 \to V'$ be the linear transformation defined by projection $V\otimes V_1 \to V_1$ followed by $T_1 : V_1 \to V'$. Then
-\[
-\begin{tikzcd}[column sep=30]
-\ & (f',\psi',V')  & \\
-\arrow{dr}[swap]{(\pi,0)}  (f,\psi,V)  \arrow{ru}{(\gamma,T=0)} &  & \arrow[swap]{lu}{(\gamma_1,T_1)}[swap]{\text{w-iso}} (f_1,\psi_1,V_1) \arrow{dl}{(\pi_1,T_v)}[swap]{\text{w-iso}} \\
-\ & \arrow{uu}[swap]{(\theta,T_1')} (f\times_G f_1,1\otimes \psi_1, V\otimes V_1) & \\   
-   \end{tikzcd}
-\]
-is a commuting diagram in $C_1(G)$, where $T_v : V_1 \to V\otimes V_1$ is defined as in the construction of the trivial morphism $0 : (f,\psi,V) \to (f_1,\psi_1,V_1)$, above.
-By \cite{kashiwara-schapira:CatgoriesSheaves}*{Thm 7.1.16}, 
-it follows that $(f,\psi,V)  \to (f_1,\psi_1,V_1)$ is the trivial morphism in $\fQC(G)$.
-
-Now suppose $T$ is an isomorphism, then $(\gamma,T)$ is a weak isomorphism, in which case the morphism $(f,\psi,V) \to (f_1,\psi_1,V_1)$ is an isomorphism in $\fQC(G)$.
-\todo{This is where some information about $\Aut_{\fQC(G)}(f,\psi,V)$ will go, when I've sorted it out.}
-\end{proof}
-
-\subsection{When quasicharacter sheaves are finite}
-
-\begin{proposition}\label{prop:connected}
-  If $G$ is a connected commutative algebraic group over $\Fq$ then
-  the full subcategories $\fQC(G) \hookrightarrow \bQC(G) \hookrightarrow \QC(G)$
-  appearing in Sections~\ref{sec:bounded} and \ref{sec:finite} are equivalences.
-\end{proposition}
-
-\begin{proof}
-  Observe that the forgetful functor $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$
-  sends quasicharacter sheaves on $G$ to $\ell$-adic Weil sheaves on $G$ \cite{deligne:80a}*{1.1.10}.
-  While is it not true that all Weil sheaves on $G$ descend to local systems on $G$,
-  we will see that those that appear in the image of this forgetful functor from quasicharacter sheaves do.
-
-%When $G$ is connected, we may apply the classic function--sheaf dictionary.  
-%In order to do so, however, we must relate our notion of quasicharacter sheaf to the sheaf side of the standard dictionary.
-Choose any $\Fq$-rational point of $G$ and let $\bg$ be the geometric point on $G$ lying above $g$.
-Recall that the \emph{Weil group} of $G$, which we will denote by $\W(G,\bg)$, is a subgroup of the \'etale
-fundamental group defined by the following diagram:
-\[
- \begin{tikzcd}
- 1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \W(G,\bg) \rar \dar[hook] & \Weil{} \rar \dar[hook] & 1 \\
- 1 \rar &  \pi_1(\bG, \bg) \rar & \pi_1(G,\bg) \rar & \Gal(\bFq/\Fq) \rar & 1.
- \end{tikzcd}
-\]
-The $\Fq$-rational point $g$ under the geometric point $\bg$ determines a splitting
-$\Weil{}\to \W(G,\bg)$ of $\W(G,\bg)\to \Weil{}$.
-
-  Since $G$ is connected, the geometric point $\bg$ determines
-  an equivalence between the category of $\ell$-adic Weil local systems on $G$ and
-  $\ell$-adic representations of $\W(G,\bg)$ \cite{deligne:80a}*{1.1.12}.
-  Now let $(\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$
-  and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$.
-  Composing with the splitting $\Weil{} \to \W(G,\bg)$ yields an $\ell$-adic character
-  $\rho_g : \Weil{} \to \EEx$, which is the same as the Trace of Frobenius defined in Section~\ref{sec:Frob}:
-  \[
-  \rho_g(\Frob{}) =  \trFrob{\qcs{L}}(g).
-  \]
-
-  On the other hand, we have already seen that $\trFrob{\qcs{L}} : G(\Fq) \to \EEx$
-  is a group homomorphism. Since $G$ is an algebraic group over $\Fq$, it is a
-  variety over $\Fq$ and thus $G(\Fq)$ is finite.
-  Therefore $\trFrob{\qcs{L}}(g) = \rho_g(\Frob{})$ is a root of unity
-  for every $g\in G(\Fq)$.  Since $\Weil{}$ is generated by
-  $\Frob{}$ and $\rho_g : \Weil{} \to \EEx$ is
-  a character, it follows that the image of $\rho_g$ is a finite group.
-  Thus, $\rho_g$ extends to an $\ell$-adic character of $\Gal(\bFq/\Fq)$,
-  which we will also denote $\rho_g$.
-
-  We may now lift the $\ell$-adic character $\rho_g : \Gal(\bFq/\Fq) \to \EEx$
-  to an $\ell$-adic character $\pi_1(G,\bg) \to \EEx$ using the canonical topological group homomorphism
-  $\pi_1(G,\bg) \to \Gal(\bFq/\Fq)$. But $\bg$ also
-  determines an equivalence between the category of $\ell$-adic
-  representations of $\pi_1(G,\bg)$ and $\ell$-adic local systems on $G$. Let
-  $\qcs{L}_0$ be a local system on $G$ in the isomorphism class
-  determined by this $\ell$-adic character of $\pi_1(G,\bg)$.
-  Then $b_G^*\qcs{L}_0 \iso \gqcs{L}$.
-  Since $b_G^*$ is full and faithful
-  \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}},
-  $
-  b_{G\times G}^* : \Hom(m^*\qcs{L}_0,\qcs{L}_0\boxtimes\qcs{L}_0) \to \Hom({\bar m}^*\gqcs{L},\gqcs{L}\boxtimes\gqcs{L})
-  $
-  is a bijection
-  (hom taken in the categories on constructible $\ell$-adic sheaves on
-  $G\times G$ and ${\bar G}\times {\bar G}$ respectively,
-  in which $\ell$-adic local systems sit as full subcategories).
-  Let $\mu_0 : m^*\qcs{L}_0 \to \qcs{L}_0\boxtimes\qcs{L}_0$ be the isomorphism matching
-  $\mu : {\bar m}^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$,
-  the latter appearing in the definition of $\qcs{L}$.
-  Then, as in Section~\ref{sec:bounded}, $(\qcs{L}_0,\mu_0)$ is an object in $\bQC(G)$
-  and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{L}_0,b_{G\times G}^*\mu_0)$ in $\QC(G)$.
-  Thus, the full and faithful functor $B_G : \bQC(G) \to \QC(G)$ from Section~\ref{sec:bounded}
-  is also essentially surjective, hence an equivalence.
-
-  In Section~\ref{sec:finite} we saw that $\fQC(G)$ is a full subcategory of $\bQC(G)$;
-  more precisely, we exhibited a full and faithful functor $L_G : \fQC(G) \to \bQC(G)$.
-  We now show that this functor is essentially surjective
-  when $G$ is a connected, commutative algebraic group over $\Fq$.
-
-  Let $(\qcs{L}_0,\mu_0)$ be a bounded quasicharacter sheaf on $G$.
-  Then $\qcs{L}\ceq B_G(\qcs{L}_0,\mu_0)$ is a quasicharacter sheaf on $G$.
-  Recall the definition of the character $\trFrob{\qcs{L}} : G(\Fq) \to \EEx$ from Section~\ref{sec:Frob}.
-  Let $f : G\to G$ be the Lang isogeny.
-  Recall that $\ker f = G(\Fq) = G^{\Frob{}}$;
-  in particular, the action of $\Gal(\bFq/\Fq)$ on $\ker f$ is trivial.
-  Let $V \ceq \EE$ and let $\psi : \ker f \to \Aut(V)$ be the representation given by
-  $\psi(g)(v) \ceq \trFrob{\qcs{L}}(g) v$ for $v\in V$.
-  Then $(f,\psi)$ is a finite quasicharacter sheaf.
-
-  To show that $L_G(f,\psi) \iso (\qcs{L}_0,\mu_0)$ we apply the function--sheaf dictionary
-  \citelist{\cite{laumon:87a}*{1.1.3} \cite{deligne:SGA4.5}*{sommes trig.}}  as follows.
-  First, recall that $L_G(f,\psi) \ceq (L(f,\psi), \mu(f,\psi))$.
-  Let $k'/k$ be any degree-$n$ extension;
-  let $\Nm : G(k')\to G(k)$ be the norm map
-  and let $b : G_{k'} \to G$ be the base change map.
-  By \cite{laumon:87a}*{1.1.3.3},
-  $\trFrob{b^*L(f,\psi)} = \trFrob{\qcs{L}} \circ \Nm$;
-  on the other hand, $\trFrob{\qcs{L}} \circ \Nm = \trFrob{b^*\qcs{L}}$,
-   by Proposition~\ref{prop:basechange}.
-  Using \cite{laumon:87a}*{Th\'eor\`eme 1.1.2}, it follows that  $L(f,\psi) \iso \qcs{L}_0$ in $\Loc(G)$.
-  It is now clear that $(L(f,\psi),\mu(f,\psi)) \iso (\qcs{L}_0,\mu_0)$ in $\bQC(G)$.
-  This completes the proof that $L_G $ is essentially surjective.
-  Since we have already seen (in Section~\ref{sec:finite}) that $L_G$ is full and faithful,
-  it follows that $L_G$ is an equivalence.
-\end{proof}
-
-As Proposition~\ref{prop:connected} shows,
-when $G$ is a connected algebraic group over $\Fq$,
-it is appropriate to replace quasicharacter sheaves on $G$
-with the conceptually simpler category $\fQC(G)$ of finite quasicharacter sheaves on $G$.
-In this context, finite quasicharacter sheaves may also be apprehended as
-\emph{certain} $\ell$-adic characters of fundamental group $\pi_1(G,{\bar e})$.
-As explained in \cite{kamgarpour:09a}*{\S2},
-the relevant characters of $\pi_1(G,{\bar e})$ are precisely those
-that factor through a particular quotient of $\pi_1(G,{\bar e})$
-denoted there by $\Pi_\text{disc}(G)$.
-Using this fact, one can show that the category of discrete isogenies to $G$ is a Galois category,
-in the sense of \cite{grothendieck:SGA1}*{Expos\'e V, \S 4}.
-Moreover, since $\Pi_\text{disc}(G) \iso G(\Fq)$ \cite{kamgarpour:09a}*{App'x B},
-the fundamental functor attached to this Galois category can be used to produce an equivalence
-between the category of finite quasicharacter sheaves on $G$ and
-the category of one-dimensional representations of $G(\Fq)^*$.
-We will see an alternate proof of this fact in the next section; see Corollary~\ref{cor:connected}.
-
-In principle, something similar is possible in the more general
-context of this paper, where $G$ is a smooth commutative group scheme over $\Fq$. 
-%to which we now return.
-In this generality, however, neither of the full subcategories $\fQC(G) \subset \bQC(G) \subset \QC(G)$ are equivalences;
-see the end of Section~\ref{sec:snake}.
-Nevertheless, every quasicharacter sheaf $(\gqcs{L},\mu,\phi)$ on $G$
-determines a Weil sheaf $(\gqcs{L},\phi)$ on $G$
-so if we choose a geometric point ${\bar g}_x$ in each component $\bG^x$ of $G$
-then this choice can be used to convert
-the Weil sheaf $(\gqcs{L},\phi)$ into an $\ell$-adic character of $\prod_{x\in \pi_0(\bG)}\W(\bG^x, {\bar g}_x)$.
-However, it seemed cumbersome to manage various
-choices of families of base points and track the action
-of $\Gal(\bFq/\Fq)$ on this (generally) infinite product of
-Weil groups and also difficult to identify the relevant quotient of this group.
-Viewed in this light, Definition~\ref{def:QC} seems comparatively simple.
-
 %sagemathcloud={"zoom_width":105}

### 2014-08-20 dictionary.tex
Finished Applications.
Still needed: a complete re-write of the Introduction.

@@
 
+Suppose $X_K$ is a connected commutative algebraic group over $K$ that admits a Néron model $X$ over $R$.
+%
+A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) = X(R)\to X(R_n)$, for some $n\in\NN_0$;
+the group of quasicharacters of $X_K(K)$ will be denoted by $\Hom_\text{qc}(X_K(K),\EEx)$ and the subgroup of those that factor through $X(R_n)$ will be denoted by $\Hom_n(X_K(K),\EEx)$.
+%
+In this section we explain how to geometrize and categorify quasicharacters of $X_K(K)$ using quasicharacter sheaves.
+
 Let $G$ be a commutative group scheme over $\Fq$.
@@
 
-Now suppose $X_K$ is a connected commutative algebraic group over $K$ that admits a Néron model $X$ over $R$.
-
-A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) = X(R)\to X(R_n)$, for some $n\in\NN_0$;
-the group of quasicharacters of $X_K(K)$ will be denoted by $\Hom_\text{qc}(X_K(K),\EEx)$.
-
-Then $\Gr_R(X)$ is commutative group scheme over $\Fq$
-with component group scheme
+The Greenberg transform $\Gr_R(X)$ of $X$ is commutative group scheme over $\Fq$ with component group scheme
 \[
@@
 $\pi_0(\Gr^R_n(X))= \pi_0(X) \times_S S_0$.
-
+%
 For every non-negative integer $n$, the morphism of $\Fq$-schemes $P^R_n(X) : \Gr_R(X) \to \Gr^R_n(N)$ induces a functor
@@
 
-Note that we may informally regard $\QC(\Gr_R(X))$ a `union' of the full subcategories $\QC(\Gr^R_n(X))$ in $\mathcal{C}(\Gr_R(X))$.
-
-\begin{theorem}\label{thm:QCX}
+%Note that we may informally regard $\QC(\Gr_R(X))$ a `union' of the full subcategories $\QC(\Gr^R_n(X))$ in $\mathcal{C}(\Gr_R(X))$.
+
+\begin{theorem}\label{thm:QCXK}
 Let $X_K$ be a commutative algebraic group over $K$ with Néron model $X$ over $R$. 
@@
 \end{proof}
+
+\subsection{Group schemes that admit a Neron model}
+
+We have just seen that if $X_K$ is a connected commutative algebraic group $X_K$ over a local field $K$ that admits a Neron model $X$ over $R$, then the category of   quasicharacter sheaves on the Greenberg transform of the Neron model $X$ provides a geometrization and categorification of quasicharacters of $X_K(K)$.
+
+It is known that all Abelian varieties over local fields and all algebraic tori over local fields admit Neron models.
+In those two cases, we can improve Theorem~\ref{thm:QCXK} slightly with the following addendum.
+
+\begin{proposition}\label{prop:natural_transformation}
+Let $K$ be a local field with ring of integers $R$ and residue field $\Fq$.
+Let $\mathcal{N}/K$ be the additive category of Abelian varieties over $K$ or the  additive category of algebraic tori over $K$.
+Then the trace of Frobenius provides a natural transformation between the additive functors
+\begin{enumerate}
+\item[$F_{\QC}$:] $X_K \mapsto \QCiso{\Gr_R(X)}$
+\item[$F_{\text{qc}}$:] $X_K \mapsto \Hom_{\text{qc}}(X_K(K),\EEx)$
+\end{enumerate}
+from the additive category $\mathcal{N}/K$ to the category of abelian groups.
+\end{proposition}
+
+It seems likely that there connected commutative algebraic groups over local fields that admit Neron models but are neither algebraic tori nor Abelian varieties; indeed, it is conjectured that K-wound unipotent group schemes over local fields like $\Fq((t))$ are examples.
+We have use the ponderous phrase "let $X_K$ be a connected commutative algebraic group over $K$ that admits a Néron model $X$" in Section~\ref{sec:applications} to draw attention to the fact that our theory of quasicharacter sheaves is applicable to more than algebraic tori and Abelian varieties.
 
@@
 Let $K$ and $K'$ be local fields with rings of integers $R$ and $R'$ and residue fields $k$ and $k'$, respectively.
-Set $S = \Spec(S)$ and $S_n = \Spec(R_n)$; likewise define $S' = \Spec{R'}$ and $S'_{n'} = \Spec{R'_{n'}}$.
+Set $S = \Spec{S}$ and $S_n = \Spec{R_n}$; likewise define $S' = \Spec{R'}$ and $S'_{n'} = \Spec{R'_{n'}}$.
 
@@
 $
-as smooth group schemes over $\Fq$ and, by Proposition~\ref{prop:pullback} the isomorphism above determines an equivalence of categories
+as smooth group schemes over $\Fq$; accordingly, by Proposition~\ref{prop:pullback} the isomorphism above determines an equivalence of categories
 \begin{equation}\label{eq:categorical_transfer}
@@
 \begin{equation}\label{eq:transfer}
-\Hom(X(R_m),\EEx) \iso \Hom(X'(R'_{m'}),\EEx).
+\Hom_m(X_K(K),\EEx) = \Hom(X(R_m),\EEx) \iso \Hom(X'(R'_{m'}),\EEx) = \Hom_{m'}(X'_{K'}(K'),\EEx).
 \end{equation}
-Recall that $\Hom(X(R_m),\EEx)$ is a subgroup of $\Hom_\text{qc}(X_K(K),\EEx)$ and $\Hom(X'(R'_{m'}),\EEx)$ is a subgroup of $\Hom_\text{qc}(X_K(K),\EEx)$.
+Recall that $\Hom_m(X_K(K),\EEx)$ is a subgroup of $\Hom_\text{qc}(X_K(K),\EEx)$ and $\Hom_{m'}(X'_{K'}(K'),\EEx)$ is a subgroup of $\Hom_\text{qc}(X_K(K),\EEx)$.
 The isomorphism \eqref{eq:transfer} is an instance of {\it transfer} of certain quasicharacters between $X_K(K)$ and $X_{K'}(K')$. 
-
-Such a relationship can exist between quasicharacters of algebraic tori over local fields, even when the characteristics of $K$ and $K'$ differ
-\citelist{\cite{chai-yu:01a} \cite{deligne:84a}*{\S 1}}.
-
+When it exists, we now recognize this transfer of quasicharacters as a consequence of the equivalence of categories of quasicharacter sheaves \eqref{eq:categorical_transfer}.
+
+Such a relationship can exist between quasicharacters of algebraic tori over local fields, even when the characteristics of $K$ and $K'$ differ.
 Suppose $T$ and $T'$ are tori over non-archimedian local fields $K$ and $K'$,
@@
 Note that if $T$ and $T'$ are $N$-congruent, then they are $N'$ congruent for every
-$N' \leq N$, the isomorphism \eqref{transfer} is depth-preserving at integers less than $N$.
-
+$N' \leq N$, the isomorphism \eqref{transfer} is level-preserving at integers less than $N$.
+%
 One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes between the
-$\TT_n$ and $\TT'_n$ assuming that $T$ and $T'$ are sufficiently congruent.
+$\underline{T} \times_S S_n$ and $\underline{T}' \times_{S'} {S'}_n$ assuming that $T$ and $T'$ are sufficiently congruent.
 They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the
@@
  determined by $\alpha, \beta$ and $\phi$.
-Combining this with Theorem~\ref{thm:application} gives the geometrization and categorification of the transfer of characters.
+Combining this with the paragraph above gives an instance of the geometrization and categorification of the transfer of characters.
 
 \begin{proposition}\label{prop:transfer}
- With notation above, suppose that $T$ and $T'$ are $N$-congruent and $N > 3h$.  Set $n \ceq N-3h$.
+ With notation above, suppose that $T$ and $T'$ are $N$-congruent and $N > 3h$.  Set $m \ceq N-3h$.
  Then there is a canonical equivalence of categories
  \[
-  \QC(\GN{T}'_{n}) \to \QC(\GN{T}_{n})
- \]
- determined by $\alpha, \beta$ and $\phi$ inducing the isomorphism
- \[
-  \Hom_{<n}(T'(K'), \EEx) \to \Hom_{<n}(T(K), \EEx)
- \]
- through the trace of Frobenius.
-\end{proposition}
-
-\subsection{Algebraic tori and Abelian varieties over local fields}
-
-\begin{corollary}\label{cor:application}
-For every algebraic torus $T$ over $K$, the trace of Frobenius
-  \[
-\trFrob{T}:  \QCiso{\GN{T}} \to \Hom_{\text{qc}}(T(K),\EEx)
-  \]
-is an isomomorphism.
-Moreover, the isomorphism $\trFrob{T}$ is a natural transformation
-between the additive functors
-\begin{enumerate}
-\item[$F_{\QC}$:] $T \mapsto \QCiso{\GN{T}}$
-\item[$F_{\text{qc}}$:] $T \mapsto \Hom_{\text{qc}}(T(K),\EEx)$
-\end{enumerate}
-from the additive category of algebraic tori over $K$ to the category of abelian groups.
-\end{corollary}
+ \QC(\Gr^{R}_m(\underline{T})) \to \QC(\Gr^{R'}_m(\underline{T}'))
+ \]
+ determined by $\alpha, \beta$ and $\phi$ inducing an isomorphism
+ \[
+\Hom_m(T(K), \EEx) \to  \Hom_m(T'(K'), \EEx)
+ \]
+ through the trace of Frobenius,  compatible with \eqref{transfer}.% ($m < N$).
+\end{proposition}
 

### 2014-08-20 dictionary.tex
Moved some prose to the beginning of Applications

@@
 Write $\m$ for the maximal ideal of $R$ and $K$ for the quotient field for $R$.
+For every non-negative integer $n$,  set $R_n = R/\m^{n+1}$.
+
+Suppose $X_K$ is a connected commutative algebraic group over $K$ that admits a Néron model $X$ over $R$.
+%
+A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) \to X(R_n)$, for some $n\in\NN_0$;
+the group of quasicharacters of $X_K(K)$ will be denoted by $\Hom_\text{qc}(X_K(K),\EEx)$ and the subgroup of those that factor through $X(R_n)$ will be denoted by $\Hom_n(X_K(K),\EEx)$.
+%
+In this section we explain how to geometrize and categorify quasicharacters of $X_K(K)$ using quasicharacter sheaves.
+
+It seems likely that there connected commutative algebraic groups over local fields that admit Neron models but are neither algebraic tori nor Abelian varieties; indeed, it is conjectured that K-wound unipotent group schemes over local fields like $\Fq((t))$ are examples.
+We have use the ponderous phrase "let $X_K$ be a connected commutative algebraic group over $K$ that admits a Néron model $X$" in Section~\ref{sec:applications} to draw attention to the fact that our theory of quasicharacter sheaves is applicable to more than algebraic tori and Abelian varieties.
+
+\subsection{Review of the Greenberg transform}
+
+Let $K$, $R$ and $R_n$ be as above.
 Set $S = \Spec{R}$.
-For every non-negative integer $n$, set $R_n = R/\m^{n+1}$ and $S_n = \Spec{R_n}$;  
+For every non-negative integer $n$,  and $S_n = \Spec{R_n}$;  
 note that $S_0 = \Spec{\Fq}$ is the special fibre of $S$.
-
-\subsection{Review of the Greenberg transform}
 
@@
 
-Suppose $X_K$ is a connected commutative algebraic group over $K$ that admits a Néron model $X$ over $R$.
-%
-A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) = X(R)\to X(R_n)$, for some $n\in\NN_0$;
-the group of quasicharacters of $X_K(K)$ will be denoted by $\Hom_\text{qc}(X_K(K),\EEx)$ and the subgroup of those that factor through $X(R_n)$ will be denoted by $\Hom_n(X_K(K),\EEx)$.
-%
-In this section we explain how to geometrize and categorify quasicharacters of $X_K(K)$ using quasicharacter sheaves.
-
 Let $G$ be a commutative group scheme over $\Fq$.
@@
 \end{enumerate}
-So Theorem~\ref{thm:QCX} now follows from the fact that each $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(\Gr_R(X))$ and the observation that $\QC(\Gr_R(X))$ a `union' of the subcategories $\QC(\Gr^R_n(X))$ in $\mathcal{C}(\Gr_R(X))$.
+So Theorem~\ref{thm:QCXK} now follows from the fact that each $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(\Gr_R(X))$ and the observation that $\QC(\Gr_R(X))$ a `union' of the subcategories $\QC(\Gr^R_n(X))$ in $\mathcal{C}(\Gr_R(X))$.
 \end{proof}
@@
 \end{proposition}
-
-It seems likely that there connected commutative algebraic groups over local fields that admit Neron models but are neither algebraic tori nor Abelian varieties; indeed, it is conjectured that K-wound unipotent group schemes over local fields like $\Fq((t))$ are examples.
-We have use the ponderous phrase "let $X_K$ be a connected commutative algebraic group over $K$ that admits a Néron model $X$" in Section~\ref{sec:applications} to draw attention to the fact that our theory of quasicharacter sheaves is applicable to more than algebraic tori and Abelian varieties.
 

### 2014-08-20 dictionary.tex
Switch order of 1.3 and 1.4

--- 2014-08-20 dictionary.tex
@@
 
-We close the introduction with a brief description of the structure of this paper.
+We close the introduction with an overview of the structure of this paper.
 After setting some basic notation in Section~\ref{sec:notation},
-in Section~\ref{sec:category} we define quasicharacter sheaves and give an interpretation of
-them as Weil sheaves equipped with an isomorphism of the form \eqref{introbox}.
+in Section~\ref{sec:category} we define the category of quasicharacter sheaves.
+We define pullbacks and products of quasicharacter sheaves in Section~\ref{sec:pullback}
 Section~\ref{sec:Frob} introduces Trace of Frobenius,
 one direction of the function--sheaf dictionary.
-We define pullbacks and products of quasicharacter sheaves in Section~\ref{sec:pullback}, and use
+, and use
 them to prove a functoriality result on Trace of Frobenius.
@@
 \end{remark}
+
+\subsection{Trace of Frobenius}\label{sec:Frob}
+
+We now introduce a tool which will help us understand isomorphism classes of objects in $\QCiso{G}$.
+
+%A Weil sheaf $(\gqcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gqcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
+%We now briefly review this point of view for later use in Section~\ref{sec:basechange}; see also \cite{deligne:80a}*{Def.~1.1.10}.  If $w \ceq \Frob{}^n$ we write $w_G$ for $\Frob{G}^n$.
+%For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gqcs{L}\to \gqcs{L}$ by $\varphi(w) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi);$
+%these isomorphisms satisfy $\varphi(uv) = \varphi(v) \circ v_G^* \varphi(u)$ for $u,v\in \Weil{}$, and we have $\phi = \varphi(\Frob{})$.
+%If we further define $\varphi_1(w) \ceq (w_G)_*(\varphi(w)^{-1})$ then $\varphi_1(w) : (w_G)_* \gqcs{L}\to \gqcs{L}$ is an isomorphism and $\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for $u,v\in \Weil{}$.
+%Thus the pair $(\gqcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of\cite{deligne:SGA4.5}*{Expos\'e XIII, 1.1}, failing only because $\Weil{}$ is not profinite.
+%As we will see in Corollary~\ref{cor:bounded-and-finite}, our use of $\Weil{}$ rather than $\Gal(\bFq/\Fq)$ allows quasicharacter sheaves to correspond to unbounded characters.
+
+%Observe that the rule $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ defines a forgetful functor from quasicharacter
+%sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
+%
+
+Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
+determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$. 
+Together with the canonical isomorphism $(\Frob{G}^*\gqcs{L})_{\bg} \iso  \gqcs{L}_{\Frob{G}(\bg)}$, in this way the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gqcs{L}_{\bg}$; let $\trace(\phi_{\bg};\gqcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gqcs{L}_{\bg})$ and let $\trFrob{(\gqcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by
+\begin{equation}\label{trWeil}
+%\begin{equation}\label{trWeil}
+\trFrob{(\gqcs{L},\phi)}(g) \ceq \trace(\phi_{\bg};\gqcs{L}_{\bg}),
+%\end{equation}
+\end{equation}
+commonly called the {\em trace of Frobenius of $(\gqcs{L},\phi)$}.
+Note that if $(\gqcs{L},\phi) \iso (\gqcs{L'},\phi')$ as Weil sheaves, 
+then $\trFrob{(\gqcs{L},\phi)} = \trFrob{(\gqcs{L'},\phi')}$ as functions on $G(\Fq)$.
+
+Now suppose $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$.
+The isomorphism $\mu : \bm^* \gqcs{L} \to \LxL$ together with
+\ref{QC.3} guarantee
+that the function $\trFrob{(\qcs{L},\phi)} : G(\Fq)\to \EEx$ is a group homomorphism.  
+Moreover, this group homomorphism is insensitive to $\phi$ in the sense 
+that if $(\gqcs{L},\mu,\phi)$ and $(\gqcs{L},\mu,\phi')$ are quasicharacter sheaves, then $\trFrob{(\qcs{L},\phi)} = \trFrob{(\qcs{L},\phi')}$. \todo{Sketch proof?}
+This justifies abbreviating $\trFrob{(\gqcs{L},\phi)}$ to $\trFrob{\qcs{L}}$ in this case.
+The diagram below defines two group homomorphisms, both denoted $\TrFrob{G}$ and both called the \emph{Trace of Frobenius} for $G$; we trust that context will remove any ambiguity regarding this notation.
+\[
+\begin{tikzcd}
+\QCiso{G} \arrow{rr} \arrow{dr}[swap]{\qcs{L} \mapsto t_{\qcs{L}}}{\TrFrob{G}} && \arrow{dl}[swap]{\TrFrob{G}}{(\gqcs{L},\phi) \mapsto t_{\gqcs{L},\phi}} \lQCiso{G} \\
+& G(\Fq)^* & 
+\end{tikzcd}
+\]
+As remarked above, the group homomorphism $\QCiso{G} \to \lQCiso{G}$ is surjective;
+we will see that $\QCiso{G} \to \lQCiso{G}$ need not be injective.
+However, in Theorem~\ref{thm:snake}, we will see that the group homomorphism $\QCiso{G} \to G(\Fq)^*$ is surjective
+while the main result of this paper, Theorem~\ref{thm:snake}, 
+shows that $\lQCiso{G} \to G(\Fq)^*$ is an isomorphism.
+
+\begin{proposition}\label{prop:functorialG}
+Trace of Frobenius $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a natural transformation
+between the two contravariant additive functors
+\begin{align*}
+F_1 : G &\mapsto \QCiso{G} \\
+F_2 : G &\mapsto G(\Fq)^*
+\end{align*}
+from the category of smooth commutative group schemes over $\Fq$ to the category of abelian groups.
+Likewise, for $\TrFrob{G} : \lQCiso{G} \to G(\Fq)^*$, {\it mut.\hskip-1pt mut.}
+\end{proposition}
+
+We will prove this proposition at the end of Section \ref{sec:pullback}
+
+In [point] we will use trace of Frobenius $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ to show that $\QCiso{G}$ is an extension of $G(\Fq)^*$ by $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$.
 
@@
 
-\subsection{Trace of Frobenius}\label{sec:Frob}
-
-We now introduce a tool which will help us understand isomorphism classes of objects in $\QCiso{G}$.
-
-%A Weil sheaf $(\gqcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gqcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
-%We now briefly review this point of view for later use in Section~\ref{sec:basechange}; see also \cite{deligne:80a}*{Def.~1.1.10}.  If $w \ceq \Frob{}^n$ we write $w_G$ for $\Frob{G}^n$.
-%For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gqcs{L}\to \gqcs{L}$ by $\varphi(w) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi);$
-%these isomorphisms satisfy $\varphi(uv) = \varphi(v) \circ v_G^* \varphi(u)$ for $u,v\in \Weil{}$, and we have $\phi = \varphi(\Frob{})$.
-%If we further define $\varphi_1(w) \ceq (w_G)_*(\varphi(w)^{-1})$ then $\varphi_1(w) : (w_G)_* \gqcs{L}\to \gqcs{L}$ is an isomorphism and $\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for $u,v\in \Weil{}$.
-%Thus the pair $(\gqcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of\cite{deligne:SGA4.5}*{Expos\'e XIII, 1.1}, failing only because $\Weil{}$ is not profinite.
-%As we will see in Corollary~\ref{cor:bounded-and-finite}, our use of $\Weil{}$ rather than $\Gal(\bFq/\Fq)$ allows quasicharacter sheaves to correspond to unbounded characters.
-
-%Observe that the rule $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ defines a forgetful functor from quasicharacter
-%sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
-%
-
-Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
-determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$. 
-Together with the canonical isomorphism $(\Frob{G}^*\gqcs{L})_{\bg} \iso  \gqcs{L}_{\Frob{G}(\bg)}$, in this way the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gqcs{L}_{\bg}$; let $\trace(\phi_{\bg};\gqcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gqcs{L}_{\bg})$ and let $\trFrob{(\gqcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by
-\begin{equation}\label{trWeil}
-%\begin{equation}\label{trWeil}
-\trFrob{(\gqcs{L},\phi)}(g) \ceq \trace(\phi_{\bg};\gqcs{L}_{\bg}),
-%\end{equation}
-\end{equation}
-commonly called the {\em trace of Frobenius of $(\gqcs{L},\phi)$}.
-Note that if $(\gqcs{L},\phi) \iso (\gqcs{L'},\phi')$ as Weil sheaves, 
-then $\trFrob{(\gqcs{L},\phi)} = \trFrob{(\gqcs{L'},\phi')}$ as functions on $G(\Fq)$.
-
-Now suppose $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$.
-The isomorphism $\mu : \bm^* \gqcs{L} \to \LxL$ together with
-\ref{QC.3} guarantee
-that the function $\trFrob{(\qcs{L},\phi)} : G(\Fq)\to \EEx$ is a group homomorphism.  
-Moreover, this group homomorphism is insensitive to $\phi$ in the sense 
-that if $(\gqcs{L},\mu,\phi)$ and $(\gqcs{L},\mu,\phi')$ are quasicharacter sheaves, then $\trFrob{(\qcs{L},\phi)} = \trFrob{(\qcs{L},\phi')}$. \todo{Sketch proof?}
-This justifies abbreviating $\trFrob{(\gqcs{L},\phi)}$ to $\trFrob{\qcs{L}}$ in this case.
-The diagram below defines two group homomorphisms, both denoted $\TrFrob{G}$ and both called the \emph{Trace of Frobenius} for $G$; we trust that context will remove any ambiguity regarding this notation.
-\[
-\begin{tikzcd}
-\QCiso{G} \arrow{rr} \arrow{dr}[swap]{\qcs{L} \mapsto t_{\qcs{L}}}{\TrFrob{G}} && \arrow{dl}[swap]{\TrFrob{G}}{(\gqcs{L},\phi) \mapsto t_{\gqcs{L},\phi}} \lQCiso{G} \\
-& G(\Fq)^* & 
-\end{tikzcd}
-\]
-As remarked above, the group homomorphism $\QCiso{G} \to \lQCiso{G}$ is surjective;
-we will see that $\QCiso{G} \to \lQCiso{G}$ need not be injective.
-However, in Theorem~\ref{thm:snake}, we will see that the group homomorphism $\QCiso{G} \to G(\Fq)^*$ is surjective
-while the main result of this paper, Theorem~\ref{thm:snake}, 
-shows that $\lQCiso{G} \to G(\Fq)^*$ is an isomorphism.
-
-\begin{proposition}\label{prop:functorialG}
-Trace of Frobenius $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a natural transformation
-between the two contravariant additive functors
-\begin{align*}
-F_1 : G &\mapsto \QCiso{G} \\
-F_2 : G &\mapsto G(\Fq)^*
-\end{align*}
-from the category of smooth commutative group schemes over $\Fq$ to the category of abelian groups.
-Likewise, for $\TrFrob{G} : \lQCiso{G} \to G(\Fq)^*$, {\it mut.\hskip-1pt mut.}
-\end{proposition}
-
-\begin{proof}
+Using these results on pullbacks we may now prove that Trace of Frobenius is a natural transformation.
+
+\begin{proof}[Proof of Proposition~\ref{prop:functorialG}]
 The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
@@
 \end{proof}
-
-In [point] we will use trace of Frobenius $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ to show that $\QCiso{G}$ is an extension of $G(\Fq)^*$ by $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$.
 

### 2014-08-20 dictionary.tex
Merging sections 1.3 and 1.4

@@
 
-We now introduce a tool which will help us understand isomorphism classes of objects in $\QCiso{G}$.
+In this section we introduce two tools which will help us understand isomorphism classes of objects in $\QC(G)$: the trace of Frobenius map $\QCiso{G} \to G(k)^*$ and the pullback functor $\QC(G) \to \QC(H)$ associated to a morphism $H \to G$.
 
@@
 \ref{QC.3} guarantee
-that the function $\trFrob{(\qcs{L},\phi)} : G(\Fq)\to \EEx$ is a group homomorphism.  
-Moreover, this group homomorphism is insensitive to $\phi$ in the sense 
-that if $(\gqcs{L},\mu,\phi)$ and $(\gqcs{L},\mu,\phi')$ are quasicharacter sheaves, then $\trFrob{(\qcs{L},\phi)} = \trFrob{(\qcs{L},\phi')}$. \todo{Sketch proof?}
-This justifies abbreviating $\trFrob{(\gqcs{L},\phi)}$ to $\trFrob{\qcs{L}}$ in this case.
-The diagram below defines two group homomorphisms, both denoted $\TrFrob{G}$ and both called the \emph{Trace of Frobenius} for $G$; we trust that context will remove any ambiguity regarding this notation.
-\[
-\begin{tikzcd}
-\QCiso{G} \arrow{rr} \arrow{dr}[swap]{\qcs{L} \mapsto t_{\qcs{L}}}{\TrFrob{G}} && \arrow{dl}[swap]{\TrFrob{G}}{(\gqcs{L},\phi) \mapsto t_{\gqcs{L},\phi}} \lQCiso{G} \\
-& G(\Fq)^* & 
-\end{tikzcd}
-\]
-As remarked above, the group homomorphism $\QCiso{G} \to \lQCiso{G}$ is surjective;
-we will see that $\QCiso{G} \to \lQCiso{G}$ need not be injective.
-However, in Theorem~\ref{thm:snake}, we will see that the group homomorphism $\QCiso{G} \to G(\Fq)^*$ is surjective
-while the main result of this paper, Theorem~\ref{thm:snake}, 
-shows that $\lQCiso{G} \to G(\Fq)^*$ is an isomorphism.
-
-\begin{proposition}\label{prop:functorialG}
-Trace of Frobenius $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a natural transformation
-between the two contravariant additive functors
+that the function $\trFrob{(\gqcs{L},\phi)} : G(\Fq)\to \EEx$ is a group homomorphism, which we will also denote by $\trFrob{\qcs{L}}$.  Moreover,
+this homomorphism depends only on the isomorphism class of $\qcs{L}$, so we obtain a map
 \begin{align*}
-F_1 : G &\mapsto \QCiso{G} \\
-F_2 : G &\mapsto G(\Fq)^*
+\TrFrob{G} : \QCiso{G} &\to G(\Fq)^* \\
+\qcs{L} &\mapsto \trFrob{\qcs{L}}.
 \end{align*}
-from the category of smooth commutative group schemes over $\Fq$ to the category of abelian groups.
-Likewise, for $\TrFrob{G} : \lQCiso{G} \to G(\Fq)^*$, {\it mut.\hskip-1pt mut.}
-\end{proposition}
-
-We will prove this proposition at the end of Section \ref{sec:pullback}
-
-In [point] we will use trace of Frobenius $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ to show that $\QCiso{G}$ is an extension of $G(\Fq)^*$ by $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$.
-
-\subsection{Pull-back and products}\label{sec:pullback}
-
-As a step toward understanding quasicharacter sheaves we begin by showing that quasicharacter sheaves admit pull-backs and external products.
-%show that every morphism $H \to G$ of smooth commutative groups schemes over $\Fq$ induces a monoidal functor from quasicharacter sheaves on $G$ to quasicharacters on $H$. 
-These simple but important results will be used in the proofs of many results in this paper.
+Since tensor products on the stalks of $\qcs{L}$ induce pointwise multiplication on the trace of Frobenius, $\TrFrob{G}$ is a group homomorphism.  We devote the remainder of this section to
+studying the behavior of the trace of Frobenius under morphisms of group schemes.  These simple but important
+results on pullbacks and external products will be used in the proofs of many results in this paper.
 
@@
 
-Using these results on pullbacks we may now prove that Trace of Frobenius is a natural transformation.
-
-\begin{proof}[Proof of Proposition~\ref{prop:functorialG}]
+Using these results on pullbacks and products, we may prove a naturality property of $\TrFrob{G}$.
+
+\begin{proposition}\label{prop:functorialG}
+Trace of Frobenius $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a natural transformation
+between the two contravariant additive functors
+\begin{align*}
+F_1 : G &\mapsto \QCiso{G} \\
+F_2 : G &\mapsto G(\Fq)^*
+\end{align*}
+from the category of smooth commutative group schemes over $\Fq$ to the category of abelian groups.
+Likewise, for $\TrFrob{G} : \lQCiso{G} \to G(\Fq)^*$, {\it mut.\hskip-1pt mut.}
+\end{proposition}
+
+\begin{proof}
 The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
@@
 We must show that comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
-To do this we use etale descent to see that pull-back along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$. 
+To do this we use etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$. 
 In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
@@
 From here, Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields \citelist{\cite{deligne:SGA4.5}*{Sommes trig.}, \cite{laumon:87a}*{1.1.3}}  gives us all we need, as we briefly recall.
-The key observation is that, by etale descent, pull-back by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
+The key observation is that, by etale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
 Using the equivalence given by $\Lang^*$, if $\Lang^*\qcs{E} = V$ with character $\psi$ and isomorphism $V\to V\otimes V$ then 

### 2014-08-20 dictionary.tex
Changes to Applications before going home.

@@
 \subjclass[2010]{14F05 (primary), 14L15 (secondary)}
-\keywords{function--sheaf dictionary, geometrization, quasicharacters, quasicharacter sheaves, smooth commutative group schemes}
+\keywords{function--sheaf dictionary, trace of Frobenius, geometrization, quasicharacters, quasicharacter sheaves, smooth commutative group schemes}
 
@@
 
-In this section we use quasicharacter sheaves to geometrize and categorify the group 
-of admissible characters of smooth commutative group schemes over local fields that admit Néron models.
-
-Let $R$ be a complete discrete valuation ring $R$ with residue field $\Fq$.
-Write $\m$ for the maximal ideal of $R$ and $K$ for the quotient field for $R$.
-For every non-negative integer $n$,  set $R_n = R/\m^{n+1}$.
-
-Suppose $X_K$ is a connected commutative algebraic group over $K$ that admits a Néron model $X$ over $R$.
-%
-A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) \to X(R_n)$, for some $n\in\NN_0$;
+Let $K$ be a local field (in the sense of Serre) with residue field $\Fq$. 
+In this section we consider connected smooth commutative algebraic groups over $K$ that admit a Néron model, by which we means a perhaps lft Néron model.
+By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected smooth commutative algebraic groups over $K$ that contain no subgroup of type $\mathbb{G}_\text{a}$.
+We remark that these connected commutative algebraic groups over $K$ form an additive category in a natural way, as a full subcategory of connected commutative algebraic groups over $K$, and that this category includes algebraic tori over $K$ and Abelian varieties over $K$.
+
+Let $R$ be the ring of integers of $K$.
+Write $\m$ for the maximal ideal of $R$ and set $R_n = R/\m^{n+1}$, for every non-negative integer $n$.
+Let $X_K$ be a connected smooth commutative algebraic groups over $K$ that admit a Néron model, $X$.
+A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) \to X(R_n)$, for some non-negative integer $n$;
 the group of quasicharacters of $X_K(K)$ will be denoted by $\Hom_\text{qc}(X_K(K),\EEx)$ and the subgroup of those that factor through $X(R_n)$ will be denoted by $\Hom_n(X_K(K),\EEx)$.
@@
 In this section we explain how to geometrize and categorify quasicharacters of $X_K(K)$ using quasicharacter sheaves.
-
-It seems likely that there connected commutative algebraic groups over local fields that admit Neron models but are neither algebraic tori nor Abelian varieties; indeed, it is conjectured that K-wound unipotent group schemes over local fields like $\Fq((t))$ are examples.
-We have use the ponderous phrase "let $X_K$ be a connected commutative algebraic group over $K$ that admits a Néron model $X$" in Section~\ref{sec:applications} to draw attention to the fact that our theory of quasicharacter sheaves is applicable to more than algebraic tori and Abelian varieties.
 
@@
 \begin{theorem}\label{thm:QCXK}
-Let $X_K$ be a commutative algebraic group over $K$ with Néron model $X$ over $R$. 
+Let $K$ and $R$ be as above.
+The trace of Frobenius provides a natural transformation between the additive functors
+\[
+F_{\QC}: X_K \mapsto \QCiso{\Gr_R(X)}
+\qquad\text{and}\qquad
+F_{\text{qc}}: X_K \mapsto \Hom_{\text{qc}}(X_K(K),\EEx)
+\]
+where $X$ is a Neron model for $X_K$, as functors from the additive category of connected commutative algebraic groups over $K$ that admit Neron models to the category of abelian groups. 
+Regarding this natural transformation:
 \begin{enumerate}
-\item[(1)] There is a canonical short exact sequence of abelian groups 
-\[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{\Gr_R(X)} \to \Hom_\text{qc}(X_K(K),\EEx) \to 0.
-\] 
-\item[(2)] For all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism.
-\item[(3)] For all quasicharacter sheaves $\qcs{F}$ on $\Gr_R(X)$,
+\item[(1)] there is a canonical short exact sequence of abelian groups 
+\[
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{\Gr_R(X)} \to \Hom_\text{qc}(X_K(K),\EEx) \to 0;
+\] 
+\item[(2)] for all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
+\item[(3)] for all quasicharacter sheaves $\qcs{F}$ on $\Gr_R(X)$,
 \[
@@
 
-\subsection{Group schemes that admit a Neron model}
+\subsection{Natural transformation}
 

### 2014-08-21 dictionary.tex
I've gone through Applications, again.

@@
 \newcommand{\Weil}[1]{\mathcal{W}_{#1}}
-
+\newcommand{\m}{{\mathfrak{m}}}
 %%%%%%%%%%%%%%% ALGEBRAIC GROUPS %%%%%%%%%%%%%%%
@@
 \newcommand{\TTp}{\underline{T}'}
-
+\newcommand{\comp}{\Pi} % Component group
 %%%%%%%%%%%%%%% NAMED OPERATORS %%%%%%%%%%%%%%%
@@
 \newcommand{\iso}{{\ \cong\ }}
+\newcommand{\trFrob}[1]{t_{#1}}
+\newcommand{\TrFrob}[1]{T_{#1}}
+\newcommand{\lTrFrob}[1]{\TrFrob{#1}^2}
 %% Limits
@@
 \newcommand{\fQCiso}[1]{\fQC(#1)_{/\text{iso}}}
-\newcommand{\trFrob}[1]{t_{#1}}
-\newcommand{\TrFrob}[1]{T_{#1}}
 %% amsmath replacements for \atop
@@
 \hyphenation{quasi-character}
-\newcommand{\lTrFrob}[1]{\TrFrob{#1}^2}
-\newcommand{\comp}{\Pi} % Component group
-\newcommand{\m}{{\mathfrak{m}}}
 
@@
 from the category of smooth commutative group schemes over $\Fq$ to the category of abelian groups.
-Likewise, for $\TrFrob{G} : \lQCiso{G} \to G(\Fq)^*$, {\it mut.\hskip-1pt mut.}
+%Likewise, for $\TrFrob{G} : \lQCiso{G} \to G(\Fq)^*$, {\it mut.\hskip-1pt mut.}
 \end{proposition}
@@
 Let $K$ be a local field (in the sense of Serre) with residue field $\Fq$. 
-In this section we consider connected smooth commutative algebraic groups over $K$ that admit a Néron model, by which we means a perhaps lft Néron model.
+In this section we consider connected smooth commutative algebraic groups over $K$ that admit a Néron model, by which we means a lft Néron model.
 By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected smooth commutative algebraic groups over $K$ that contain no subgroup of type $\mathbb{G}_\text{a}$.
-We remark that these connected commutative algebraic groups over $K$ form an additive category in a natural way, as a full subcategory of connected commutative algebraic groups over $K$, and that this category includes algebraic tori over $K$ and Abelian varieties over $K$.
+These algebraic groups over $K$ form an additive category, denoted by $\mathcal{N}/K$ below, in a natural way, as a full subcategory of connected commutative algebraic groups over $K$.
+This category includes algebraic tori over $K$ and Abelian varieties over $K$.
 
@@
 Write $\m$ for the maximal ideal of $R$ and set $R_n = R/\m^{n+1}$, for every non-negative integer $n$.
-Let $X_K$ be a connected smooth commutative algebraic groups over $K$ that admit a Néron model, $X$.
+Suppose $X_K \in \mathcal{N}/K$.
 A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) \to X(R_n)$, for some non-negative integer $n$;
@@
 This functor respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components.
-
-For any $n\in \NN_0$, we will write
+%
+For any non-negative integer $n$ we will write
 \[
@@
 canonically.
-For every $n\in \NN_0$,
-$\Gr^R_n(X)$ is {\it smooth} commutative group scheme over $\Fq$
-with component group scheme
+For every non-negative integer $n$, $\Gr^R_n(X)$ is {\it smooth} commutative group scheme over $\Fq$ with component group scheme
 $\pi_0(\Gr^R_n(X))= \pi_0(X) \times_S S_0$.
@@
 \]
-where $X$ is a Neron model for $X_K$, as functors from the additive category of connected commutative algebraic groups over $K$ that admit Neron models to the category of abelian groups. 
-Regarding this natural transformation:
+where $X$ is a Neron model for $X_K$, as functors from $\mathcal{N}/K$ to the category of abelian groups. 
+Regarding this natural transformation, for every $X_K \in \mathcal{N}/K$:
 \begin{enumerate}
@@
 To begin, fix $n\in \NN$.
-The following statements follow directly from Theorems~\ref{thm:snake} and \ref{thm:autornaught} together with our observations about the component group of $\Gr^R_n(X)$.
+The following statements follow directly from properties of Néron models, Proposition~\ref{prop:functorialG} and Theorems~\ref{thm:snake} and \ref{thm:autornaught} together with our observations about the component group of $\Gr^R_n(X)$.
 \begin{enumerate}
+\item[(0)] Trace of Frobenius gives a natural transformation from
+\[
+F_{\QC,n}: X_K \mapsto \QCiso{\Gr^R_n(X)}
+\qquad\text{to}\qquad
+F_{\text{qc},n}: X_K \mapsto \Hom_n(X_K(K),\EEx)
+\]
+as functors from $\mathcal{N}/K$ to Abelian groups.
 \item[(1)] There is a canonical short exact sequence of abelian groups 
@@
 \end{proof}
-
-\subsection{Natural transformation}
-
-We have just seen that if $X_K$ is a connected commutative algebraic group $X_K$ over a local field $K$ that admits a Neron model $X$ over $R$, then the category of   quasicharacter sheaves on the Greenberg transform of the Neron model $X$ provides a geometrization and categorification of quasicharacters of $X_K(K)$.
-
-It is known that all Abelian varieties over local fields and all algebraic tori over local fields admit Neron models.
-In those two cases, we can improve Theorem~\ref{thm:QCXK} slightly with the following addendum.
-
-\begin{proposition}\label{prop:natural_transformation}
-Let $K$ be a local field with ring of integers $R$ and residue field $\Fq$.
-Let $\mathcal{N}/K$ be the additive category of Abelian varieties over $K$ or the  additive category of algebraic tori over $K$.
-Then the trace of Frobenius provides a natural transformation between the additive functors
-\begin{enumerate}
-\item[$F_{\QC}$:] $X_K \mapsto \QCiso{\Gr_R(X)}$
-\item[$F_{\text{qc}}$:] $X_K \mapsto \Hom_{\text{qc}}(X_K(K),\EEx)$
-\end{enumerate}
-from the additive category $\mathcal{N}/K$ to the category of abelian groups.
-\end{proposition}
 
@@
 
-Let $X_K$ and $X'_{K'}$ be connected commutative algebraic groups over $K$ and $K'$, respectively, that admit Néron models $X$ and $X'$ over $R$ and $R'$, respectively.
-Suppose $m$ and $m'$ are non-negative integers such that 
+Suppose $X_K\in \mathcal{N}/K$ and $X'_{K'}\in \mathcal{N}/K'$ 
+and that $m$ and $m'$ are non-negative integers such that 
 \begin{equation}\label{eq:schematic_transfer}
@@
 \begin{equation}\label{eq:transfer}
-\Hom_m(X_K(K),\EEx) = \Hom(X(R_m),\EEx) \iso \Hom(X'(R'_{m'}),\EEx) = \Hom_{m'}(X'_{K'}(K'),\EEx).
+\Hom_m(X_K(K),\EEx)  \iso  \Hom_{m'}(X'_{K'}(K'),\EEx).
 \end{equation}
-Recall that $\Hom_m(X_K(K),\EEx)$ is a subgroup of $\Hom_\text{qc}(X_K(K),\EEx)$ and $\Hom_{m'}(X'_{K'}(K'),\EEx)$ is a subgroup of $\Hom_\text{qc}(X_K(K),\EEx)$.
 The isomorphism \eqref{eq:transfer} is an instance of {\it transfer} of certain quasicharacters between $X_K(K)$ and $X_{K'}(K')$. 
-When it exists, we now recognize this transfer of quasicharacters as a consequence of the equivalence of categories of quasicharacter sheaves \eqref{eq:categorical_transfer}.
+We now recognize this transfer of quasicharacters as a consequence of the equivalence of categories of quasicharacter sheaves \eqref{eq:categorical_transfer}.
 
@@
 One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes between the
-$\underline{T} \times_S S_n$ and $\underline{T}' \times_{S'} {S'}_n$ assuming that $T$ and $T'$ are sufficiently congruent.
-They define a quantity $h$ as the smallest integer so that $\pi^h$ lies in the
-Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}.
-Then it follows from \cite{chai-yu:01a}*{Thm. 8.5} that if $N > 3h$ and $T$ and $T'$ are $N$-congruent
-then there is a canonical isomorphism of smooth group schemes
+$\underline{T} \times_S S_n$ and $\underline{T}' \times_{S'} {S'}_n$, where $\underline{T}$ is a Neron model of $T$ and $\underline{T}'$ is a Neron model of $T'$, assuming that $T$ and $T'$ are sufficiently congruent.
+They define a quantity $h$ (the smallest integer so that $\pi^h$ lies in the
+Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}) and show  that if $N > 3h$ and $T$ and $T'$ are $N$-congruent then there is a canonical isomorphism of smooth group schemes
  $
-  \TT_{N-3h} \to \TT'_{N-3h}
+ \underline{T}_{N-3h} \to \underline{T}'_{N-3h}
  $
- determined by $\alpha, \beta$ and $\phi$.
+ determined by $\alpha, \beta$ and $\phi$ \cite{chai-yu:01a}*{Thm. 8.5}.
 Combining this with the paragraph above gives an instance of the geometrization and categorification of the transfer of characters.
@@
 \begin{proposition}\label{prop:transfer}
- With notation above, suppose that $T$ and $T'$ are $N$-congruent and $N > 3h$.  Set $m \ceq N-3h$.
+ With notation above, suppose that $T$ and $T'$ are $N$-congruent and $N > 3h$.  Set $m = N-3h$.
  Then there is a canonical equivalence of categories

### 2014-08-21 dictionary.tex
Gone through Section 3,4 and 5, again.

@@
 
-Throughout this paper, $G$ is a smooth, commutative group scheme
+Throughout this paper, $G$ is a smooth commutative group scheme
 over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.
@@
 $\Weil{}\subset \Gal(\bFq/\Fq)$ is the subgroup generated by $\Frob{}$.
-Let $\Frob{G} \ceq \id_{G} \times \Frob{}$ be the Frobenius automorphism of $\bG$.
+Let $\Frob{G} \ceq \id_{G} \times \Frob{}$ be the Frobenius automorphism of $\bG = G \times_{\Spec{\Fq}} \Spec{\bFq}$.
 %When no other fields play a role we will write $\Frob{}$ and $\Weil{}$ instead.
@@
 
-\subsection{Objects, when $G$ is etale}%\texorpdfstring{$S$ and $T$}{S and T}}
+\subsection{Objects, when $G$ is etale}\label{sec:SandT}
 
@@
 
-\section{Quasicharacter sheaves on commutative algebraic groups}
-
-%In this section we find $\QCiso{G}$ and $\Aut(\qcs{L})$ for commutative algebraic group over $\Fq$; note that we found these in Section~\ref{sec:etale} when $G$ is etale.
-
-%\subsection{Bounded quasicharacter sheaves}\label{sec:bounded}
+\section{Quasicharacter sheaves on connected commutative algebraic groups}
+
+Before turning our attention to quasicharacter sheaves on connected commutative algebraic groups in Section~\ref{sec:connected}, we being with two sections that treat two special classes of quasicharacter sheaves on arbitrary smooth commutative group schemes $G$: those that descend from local systems on $\bG$ to local systems on $G$ in Section~\ref{sec:bounded}; and those local systems on $G$ that are defined by discrete isogenies onto $G$ in Section~\ref{sec:discrete_isogenies}.
+The latter will play a role in Sections~\ref{sec:connected} and \ref{sec:restriction}.
+
 \subsection{Descent to G}\label{sec:bounded}
 
-%Let $G$ be a smooth commutative group scheme over $\Fq$.
 In this section we consider a category of sheaves on $G$ obtained by
@@
 \ref{QC.3}.
-%This is the category of \emph{bounded quasicharacter sheaves} on $G$.
 \end{definition}
@@
 
-We will identify $\bQC(G)$ with its image under $B_G$ and say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ \emph{descends to $G$} if it is isomorphic to some $B_G(\qcs{E}, \mu_\qcs{E})$.
-%We will see in Corollary~\ref{cor:bounded-and-finite} that bounded quasicharacter sheaves are exactly quasicharacter sheaves with bounded Trace of Frobenius.\todo{Check this, later.}
+We will say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ \emph{descends to $G$} if it is isomorphic to some $B_G(\qcs{E}, \mu_\qcs{E})$.
 
 \subsection{Discrete isogenies}\label{sec:discrete_isogenies}
-
-%Here we describe a class of quasicharacter sheaves on $G$ that will play a role in Section~\ref{sec:restriction}.
 
@@
 
-We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of quasicharacters $\qcs{L}$ on $G$ is equivalent to the category of characters $\psi$ of $G(\Fq)$.
-We have also just seen if the character of $\Lang^*\qcs{L}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu : \qcs{L} \to \qcs{L}\boxtimes\qcs{L}$ which is part of the data of the quasicharacter sheaf $\qcs{L}$.
-That leads to a perspective on the function--sheaf dictionary common in the literature in which one considers $1$-dimensional local systems $\qcs{L}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{L} \iso \qcs{L} \boxtimes\qcs{L}$ \cite{kamgarpour:09a}*{Introduction}, or sometimes, $1$-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
-
-%In the introduction to this paper we noted that, when working with connected commutative algebraic groups over finite fields, Deligne's dictionary can be described using Weil sheaves $\qcs{L}$ for which there exists an isomorphism $m^* \qcs{L} \iso \qcs{L} \boxtimes\qcs{L}$, without keeping track of the isomorphism.
-
-Although the category of quasicharacter sheaves on commutative smooth group schemes $G$ over finite fields does specialize to that common notion when $G$ is connected and of finite type, that notion is not appropriate if one wishes to extend the dictionary to commutative smooth group schemes over finite fields.
-In particular, as we have already seen in Section~\ref{sec:etale}, for a given quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ there may be a different isomorphism $\mu' : \bm^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$ for which $\qcs{L}'=(\gqcs{L},\mu',\phi)$ is also a quasicharacter sheaf on $G$, not isomorphic to $\qcs{L}$.
-Indeed, Proposition~\ref{prop:etale-iso} shows that $\Hh^0(\Weil{},\Hh^2(\bG,\EEx))$ measures the possibilities for such $\mu'$ when $G$ is etale.
-We will see later in this section that, for any smooth commutative group scheme $G$, the possibilities for such $\mu'$ are measured by $\Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx))$.
+We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of quasicharacter sheaves on $G$ is equivalent to the category of characters $\psi$ of $G(\Fq)$.
+We have also just seen that if the character of $\Lang^*\qcs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\qcs{E} : \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ which is part of the data that determines a quasicharacter sheaf on $G$.
+That leads to a perspective on the function--sheaf dictionary common in the literature in which one considers $1$-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$.
+% as in \cite{kamgarpour:09a}*{Introduction} (or sometimes, $1$-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$).
+%
+Although the category of quasicharacter sheaves on $G$ does specialize to that common notion when $G$ is connected and of finite type, the common notion is not appropriate if one wishes to extend the dictionary to smooth commutative group schemes over finite fields.
+In particular, as we have already seen in Section~\ref{sec:etale}, for a given quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ there may be a different isomorphism $\mu' : \bm^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$ for which $\qcs{L}'=(\gqcs{L},\mu',\phi)$ is also a quasicharacter sheaf on $G$, not isomorphic to $\qcs{L}$ in $\QC(G)$.
+Indeed, Proposition~\ref{prop:etale-iso} shows that $\Hh^0(\Weil{},\Hh^2(\bG,\EEx))$ measures the possibilities for $\mu'$ when $G$ is etale.
+We will see in Section~\ref{sec:main} that, for any smooth commutative group scheme $G$, the possibilities for $\mu'$ are measured by $\Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx))$.
 
@@
 \end{equation}
-Since $\pi_0(G)$ is a etale commutative group scheme, and this smooth,
+Since $\pi_0(G)$ is a etale commutative group scheme -- and thus smooth --
 Proposition~\ref{prop:pullback} implies that \eqref{eq:pi0} defines the sequence of functors
@@
 \end{equation}
- Note that we found the groups $\QCiso{G^0}$
-and $\QCiso{\pi_0(G)}$
-in Sections~\ref{sec:connected} and \ref{sec:etale}, respectively.
-In this section we show that \eqref{eq:pi2} is right exact.
-
-%We say that a morphism $f : H\to G$ of commutative group $\Fq$-schemes is a {\it discrete isogeny} to $G$ if it is a finite, surjective \'etale morphism and
-the action of $\Gal(\bFq/\Fq)$ on the \'etale group scheme $\ker f$ is trivial.
+ Note that we found the groups $\QCiso{\pi_0(G)}$ and $\QCiso{G^0}$
+in Sections~\ref{sec:SandT} and \ref{sec:connected}, respectively.
+We will shortly see that \eqref{eq:pi2} is exact.
 
@@
 \begin{proof}
-Let $\pi: B \to G^0$ be a discrete isogeny and set $A \ceq \ker \pi$.
+Let $\pi: B \to G^0$ be a discrete isogeny; set $A \ceq \ker \pi$.
   We will find a discrete isogeny $f: H\to G$
@@
   descends to a diagram of $\Fq$-schemes since the $\bFq$-points of
-  the objects come equipped with continuous $\Gamma$-actions and the
-  morphisms are $\Gamma$-equivariant.
-\end{proof}
-
-In order to use the results of Section~\ref{sec:connected}, we need to know that
-identity component of $G$ is actually an algebraic group.
+  the objects come equipped with continuous $\Gal(\bFq/\Fq)$-actions and the
+  morphisms are $\Gal(\bFq/\Fq)$-equivariant.
+\end{proof}
+
+We now wish to use the apply the results of Section~\ref{sec:connected} to the identity component of $G$; to do so, we must know that the identity component of $G$ is actually an algebraic group over $\Fq$.
 
 \begin{lemma} \label{lem:G0alg-grp}
-If $G$ is a commutative smooth group scheme over $\Fq$ then $G^0$ is a connected algebraic group.
+If $G$ is a commutative smooth group scheme over $\Fq$ then its identity component,$G^0$ is a connected algebraic group over $\Fq$.
 \end{lemma}
@@
 
-We saw in Proposition~\ref{prop:functorialG} that Trace of Frobenius
-$\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
+We saw in Proposition~\ref{prop:functorialG} that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
 In this section we improve that result.
@@
 \begin{theorem}\label{thm:snake}
-  If $G$ is a smooth, commutative group scheme over $\Fq$ then
+  If $G$ is a smooth commutative group scheme over $\Fq$ then
   \[
@@
   \begin{tikzcd}[row sep=20]
-    0 \rar & \ker \TrFrob{\pi_0(G)} \arrow[dashed]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dashed]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
+  & 0 \arrow{d} & 0 \arrow{d} & 0\arrow{d} \\
+    0 \arrow[dashed]{r} & \ker \TrFrob{\pi_0(G)} \arrow[dashed]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dashed]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
     0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
@@
     & \arrow{d} G(\Fq)^* \rar & G^0(\Fq)^* \rar \dar & 0\\
-    & \coker \TrFrob{\pi_0(G)} =0 \arrow[dashed]{r} & \coker \TrFrob{G} \arrow[dashed]{r} &  \coker \TrFrob{G^0} =0 &
+    & \arrow{d} \coker \TrFrob{\pi_0(G)} =0 \arrow[dashed]{r} & \arrow{d} \coker \TrFrob{G} \arrow[dashed]{r} &  \arrow{d} \coker \TrFrob{G^0} =0 & \\
+      & 0 & 0 & 0 \\
   \end{tikzcd}
@@
 and $\ker \TrFrob{\pi_0(G)} \to \ker \TrFrob{G}$ is an isomorphism.
-\end{proof}
-
-\todo{Insert comments on $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$. 
-It is trivial if $G$ is an algebraic group with cyclic component group.
-Lusztig}
+This calculates $\ker  \TrFrob{G}$ and shows that
+\[
+  \begin{tikzcd}
+0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx)) \arrow{r} & \QCiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0 
+  \end{tikzcd}
+\]
+is exact.
+\end{proof}
+
+\todo{Comment, in the introduction, that $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$ is trivial if $\pi_0({\bar G})$ is finite cyclic. Lusztig.}
 
@@
 the rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$
- defines a monoidal functor $\QC(G) \to \QC(G_{k'})$.
- Moreover, the following diagram commutes:
+ defines a monoidal functor $\QC(G) \to \QC(G_{k'})$
+ such that the following diagram commutes:
 \[
@@
 
-Finally, let $G'$ be a smooth commutative group scheme over $k'$;
-we explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
+Finally, let $G'$ be a smooth commutative group scheme over $k'$.
+We explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
 We may decompose the base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
@@
 Let $k'/k$ be a finite extension and let $G'$ be a smooth commutative group scheme over $k'$.
-The following diagram of isomorphisms commutes, where the bottom map is the identity:
+Then the functor 
+\[
+\rho : \QC(\Res_{k'/k}G') \to \QC(G'),
+\]
+defined above, induces
 \[
@@
 \QCiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \QCiso{G'} \dar{\TrFrob{G'}}\\
-G'(k')^* \rar & G'(k')^*
-\end{tikzcd}
-\]
+G'(k')^* \rar & G'(k')^*,
+\end{tikzcd}
+\]
+where the bottom map is the identity.
 \end{proposition}
@@
 
-\todo{Can we improve on this result by proving that $\rho$
-is an equivalence of categories?}
+%\todo{Can we improve on this result by proving that $\rho$ is an equivalence of categories?}
 
@@
 Let $K$ be a local field (in the sense of Serre) with residue field $\Fq$. 
-In this section we consider connected smooth commutative algebraic groups over $K$ that admit a Néron model, by which we means a lft Néron model.
-By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected smooth commutative algebraic groups over $K$ that contain no subgroup of type $\mathbb{G}_\text{a}$.
-These algebraic groups over $K$ form an additive category, denoted by $\mathcal{N}/K$ below, in a natural way, as a full subcategory of connected commutative algebraic groups over $K$.
-This category includes algebraic tori over $K$ and Abelian varieties over $K$.
+In this section we consider connected commutative algebraic groups over $K$ that admit a Néron model, by which we means a lft Néron model.
+By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected commutative algebraic groups over $K$ that contain no subgroup of type $\mathbb{G}_\text{a}$.
+These algebraic groups over $K$ form an additive category, denoted by $\mathcal{N}_K$ below, in a natural way, as a full subcategory of connected commutative algebraic groups over $K$.
+This category includes algebraic tori over $K$ and Abelian varieties over $K$, and sometimes unipotent K-wound groups, depending on $K$.
 
@@
 Write $\m$ for the maximal ideal of $R$ and set $R_n = R/\m^{n+1}$, for every non-negative integer $n$.
-Suppose $X_K \in \mathcal{N}/K$.
+Suppose $X_K \in \mathcal{N}_K$ with Néron model $X$ over $R$.
 A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) \to X(R_n)$, for some non-negative integer $n$;
@@
 Let $K$, $R$ and $R_n$ be as above.
-Set $S = \Spec{R}$.
-For every non-negative integer $n$,  and $S_n = \Spec{R_n}$;  
+Set $S = \Spec{R}$ and $S_n = \Spec{R_n}$, for every non-negative integer $n$;
 note that $S_0 = \Spec{\Fq}$ is the special fibre of $S$.
 
-We will need the Greenberg functor, which is
+We will need the Greenberg functor, which provides
 a functor from the category of schemes 
-over an Artinian local ring with perfect residue field
-to the category of schemes over the residue field;
+over $R_n$, for each $n\in \NN$, to the category of schemes over $\Fq$;
 See \cite{bertrapelle-gonzales:Greenberg} for the definition and fundamental properties of the Greenberg functor as we use it; other important references include
@@
 for the functor produced by composing pullback along $S_n \to S$ with the Greenberg functor. 
-This functor respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components, and
+This functor also respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components, and
 \[
@@
 \]
-canonically, for any $X$ lft over $R$.
+canonically, for any $X$ lft over $S$.
 
@@
 \[
-\Gr_R(X) \ceq \varprojlim_{n\in \NN_0} \Gr^R_n(X)
+\Gr_R(X) \ceq \varprojlim_{n\in \NN} \Gr^R_n(X)
 \]
@@
 \labitem{(C.1)}{C.1} $\mu_\qcs{F}: \bm^* \gqcs{F} \to \gqcs{F}\boxtimes\gqcs{F}$ is an isomorphism $\ell$-adic sheaves, where $\bm : \bG \times \bG \to \bG$ is multiplication $m$ for $G$ extended to $\bG$.
-\labitem{(C.2)}{C.2} $\phi_\qcs{F} : \Frob{G}^* \gqcs{F} \to \gqcs{F}$ is an isomorphism of constructible $\ell$-adic sheaves, where $\Frob{G}^* : \bG  \to \bG$ is Frobenius,
+\labitem{(C.2)}{C.2} $\phi_\qcs{F} : \Frob{G}^* \gqcs{F} \to \gqcs{F}$ is an isomorphism of constructible $\ell$-adic sheaves, where $\Frob{G}^* : \bG  \to \bG$ is the Frobenius automorphism,
 \end{enumerate}
@@
 with morphisms defined as in \ref{QC.3}.
-This category $\mathcal{C}(G)$ is rigid monoidal, with tensor product defined as in Definition~\ref{def:QC}. Note that $\mathcal{C}(G) = \QC(G)$ if $G$ is also smooth.
+This category $\mathcal{C}(G)$ is rigid monoidal, with tensor product defined as in Definition~\ref{def:QC}. %Note that $\mathcal{C}(G) = \QC(G)$ if $G$ is also smooth.
 
 The Greenberg transform $\Gr_R(X)$ of $X$ is commutative group scheme over $\Fq$ with component group scheme
-\[
+$
 \pi_0(\Gr_R(X))= \pi_0(X) \times_S S_0
-\]
+$
 and $\Fq$-rational points
-\[
+$
 \Gr_R(X)(\Fq)\iso X_K(K),
-\]
+$
 canonically.
 For every non-negative integer $n$, $\Gr^R_n(X)$ is {\it smooth} commutative group scheme over $\Fq$ with component group scheme
-$\pi_0(\Gr^R_n(X))= \pi_0(X) \times_S S_0$.
+$\pi_0(\Gr^R_n(X))= \pi_0(X) \times_S S_0$
+and $\Fq$-rational points
+$
+\Gr^R_N(X)(\Fq)\iso X(R_n),
+$
+canonically.
 %
-For every non-negative integer $n$, the morphism of $\Fq$-schemes $P^R_n(X) : \Gr_R(X) \to \Gr^R_n(N)$ induces a functor
+Moreover, the morphism of $\Fq$-schemes $P^R_n(X) : \Gr_R(X) \to \Gr^R_n(N)$ induces a functor
 \[
@@
 \]
-where $X$ is a Neron model for $X_K$, as functors from $\mathcal{N}/K$ to the category of abelian groups. 
-Regarding this natural transformation, for every $X_K \in \mathcal{N}/K$:
+where $X$ is a Néron model for $X_K$, as functors from $\mathcal{N}_K$ to the category of abelian groups. 
+Regarding this natural transformation, for every $X_K \in \mathcal{N}_K$ with Néron model $X$:
 \begin{enumerate}
@@
 \]
-as functors from $\mathcal{N}/K$ to Abelian groups.
+as functors from $\mathcal{N}_K$ to Abelian groups.
 \item[(1)] There is a canonical short exact sequence of abelian groups 
@@
 
-Suppose $X_K\in \mathcal{N}/K$ and $X'_{K'}\in \mathcal{N}/K'$ 
-and that $m$ and $m'$ are non-negative integers such that 
+Suppose $X_K\in \mathcal{N}_K$ with Néron model $X$ and $X'_{K'}\in \mathcal{N}_K'$ with Néron model $X'$.
+Suppose $m$ and $m'$ are non-negative integers such that 
 \begin{equation}\label{eq:schematic_transfer}
@@
 \end{equation}
-The isomorphism \eqref{eq:transfer} is an instance of {\it transfer} of certain quasicharacters between $X_K(K)$ and $X_{K'}(K')$. 
+The isomorphism \eqref{eq:transfer} is an instance of {\it transfer of (certain) quasicharacters} between $X_K(K)$ and $X_{K'}(K')$. 
 We now recognize this transfer of quasicharacters as a consequence of the equivalence of categories of quasicharacter sheaves \eqref{eq:categorical_transfer}.
@@
 Note that if $T$ and $T'$ are $N$-congruent, then they are $N'$ congruent for every
-$N' \leq N$, the isomorphism \eqref{transfer} is level-preserving at integers less than $N$.
+$N' \leq N$.
+%the isomorphism \eqref{transfer} is level-preserving at integers less than $N$.
 %
 One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes between the
-$\underline{T} \times_S S_n$ and $\underline{T}' \times_{S'} {S'}_n$, where $\underline{T}$ is a Neron model of $T$ and $\underline{T}'$ is a Neron model of $T'$, assuming that $T$ and $T'$ are sufficiently congruent.
+$\underline{T} \times_S S_n$ and $\underline{T}' \times_{S'} S'_n$, where $\underline{T}$ is a Néron model of $T$ and $\underline{T}'$ is a Néron model of $T'$, assuming that $T$ and $T'$ are sufficiently congruent.
 They define a quantity $h$ (the smallest integer so that $\pi^h$ lies in the
@@
  determined by $\alpha, \beta$ and $\phi$ \cite{chai-yu:01a}*{Thm. 8.5}.
-Combining this with the paragraph above gives an instance of the geometrization and categorification of the transfer of characters.
+Combining this with the paragraph above gives an instance of the geometrization and categorification of the transfer of quasicharacters.
 
@@
  \[
- \QC(\Gr^{R}_m(\underline{T})) \to \QC(\Gr^{R'}_m(\underline{T}'))
+ \QC(\Gr^{R}_m(\underline{T})) \iso \QC(\Gr^{R'}_m(\underline{T}'))
  \]
@@
  \[
-\Hom_m(T(K), \EEx) \to  \Hom_m(T'(K'), \EEx)
- \]
- through the trace of Frobenius,  compatible with \eqref{transfer}.% ($m < N$).
+\Hom_m(T(K), \EEx) \iso  \Hom_m(T'(K'), \EEx)
+ \]
+compatible with \eqref{transfer}.% ($m < N$).
 \end{proposition}

### 2014-08-21 dictionary.tex
Small changes

--- 2014-08-20 dictionary.tex
@@
 \subjclass[2010]{14F05 (primary), 14L15 (secondary)}
-\keywords{function--sheaf dictionary, trace of Frobenius, geometrization, quasicharacters, quasicharacter sheaves, smooth commutative group schemes}
+\keywords{function--sheaf dictionary, geometrization, quasicharacters, quasicharacter sheaves, smooth commutative group schemes}
 
@@
 
-In this paper we find the group $\QCiso{G}$ [point]
-and also the set $\Hom(\qcs{L},\qcs{L}')$, for all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $G$ [point]; in this way we provide a complete description of the category $\QC(G)$.
+We will describe the group $\QCiso{G}$ in Theorem \ref{thm:snake}
+and the sets $\Hom(\qcs{L},\qcs{L}')$ in Theorem \ref{thm:autornaught}; in this way we provide a complete description of the category $\QC(G)$.
 
 \begin{remark}
-The category of quasicharacter sheaves on $G$ is not abelian; $\QC(G)$
-is not a tensor category in the sense of \cite{deligne:02a}*{0.1}.
+The category of quasicharacter sheaves on $G$ is not abelian since it is not closed under direct sums and thus $\QC(G)$
+is not a tensor category in the sense of \cite{deligne:02a}*{0.1}.  We suspect that requiring that $\mu$ be injective rather than
+an isomorphism and dropping the condition that the stalks be one-dimensional would yield an abelian category.
 \end{remark}
@@
 
-Let $K$ be a local field (in the sense of Serre) with residue field $\Fq$. 
-In this section we consider connected smooth commutative algebraic groups over $K$ that admit a Néron model, by which we means a perhaps lft Néron model.
-By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected smooth commutative algebraic groups over $K$ that contain no subgroup of type $\mathbb{G}_\text{a}$.
-We remark that these connected commutative algebraic groups over $K$ form an additive category in a natural way, as a full subcategory of connected commutative algebraic groups over $K$, and that this category includes algebraic tori over $K$ and Abelian varieties over $K$.
-
-Let $R$ be the ring of integers of $K$.
-Write $\m$ for the maximal ideal of $R$ and set $R_n = R/\m^{n+1}$, for every non-negative integer $n$.
-Let $X_K$ be a connected smooth commutative algebraic groups over $K$ that admit a Néron model, $X$.
-A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) \to X(R_n)$, for some non-negative integer $n$;
+In this section we use quasicharacter sheaves to geometrize and categorify the group 
+of admissible characters of smooth commutative group schemes over local fields that admit Néron models.
+
+Let $R$ be a complete discrete valuation ring $R$ with residue field $\Fq$.
+Write $\m$ for the maximal ideal of $R$ and $K$ for the quotient field for $R$.
+For every non-negative integer $n$,  set $R_n = R/\m^{n+1}$.
+
+Suppose $X_K$ is a connected commutative algebraic group over $K$ that admits a Néron model $X$ over $R$.
+%
+A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) \to X(R_n)$, for some $n\in\NN_0$;
 the group of quasicharacters of $X_K(K)$ will be denoted by $\Hom_\text{qc}(X_K(K),\EEx)$ and the subgroup of those that factor through $X(R_n)$ will be denoted by $\Hom_n(X_K(K),\EEx)$.
@@
 In this section we explain how to geometrize and categorify quasicharacters of $X_K(K)$ using quasicharacter sheaves.
+
+It seems likely that there connected commutative algebraic groups over local fields that admit Neron models but are neither algebraic tori nor Abelian varieties; indeed, it is conjectured that K-wound unipotent group schemes over local fields like $\Fq((t))$ are examples.
+We have use the ponderous phrase "let $X_K$ be a connected commutative algebraic group over $K$ that admits a Néron model $X$" in Section~\ref{sec:applications} to draw attention to the fact that our theory of quasicharacter sheaves is applicable to more than algebraic tori and Abelian varieties.
 
@@
 \begin{theorem}\label{thm:QCXK}
-Let $K$ and $R$ be as above.
-The trace of Frobenius provides a natural transformation between the additive functors
-\[
-F_{\QC}: X_K \mapsto \QCiso{\Gr_R(X)}
-\qquad\text{and}\qquad
-F_{\text{qc}}: X_K \mapsto \Hom_{\text{qc}}(X_K(K),\EEx)
-\]
-where $X$ is a Neron model for $X_K$, as functors from the additive category of connected commutative algebraic groups over $K$ that admit Neron models to the category of abelian groups. 
-Regarding this natural transformation:
+Let $X_K$ be a commutative algebraic group over $K$ with Néron model $X$ over $R$. 
 \begin{enumerate}
-\item[(1)] there is a canonical short exact sequence of abelian groups 
-\[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{\Gr_R(X)} \to \Hom_\text{qc}(X_K(K),\EEx) \to 0;
-\] 
-\item[(2)] for all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
-\item[(3)] for all quasicharacter sheaves $\qcs{F}$ on $\Gr_R(X)$,
+\item[(1)] There is a canonical short exact sequence of abelian groups 
+\[
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{\Gr_R(X)} \to \Hom_\text{qc}(X_K(K),\EEx) \to 0.
+\] 
+\item[(2)] For all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism.
+\item[(3)] For all quasicharacter sheaves $\qcs{F}$ on $\Gr_R(X)$,
 \[
@@
 
-\subsection{Natural transformation}
+\subsection{Group schemes that admit a Neron model}
 

### 2014-08-21 dictionary.tex
Making notes for the new introduction.

--- 2014-08-21 dictionary.tex
@@
 and Weil restriction.
-Sections~\ref{sec:bounded} and \ref{sec:finite} describe bounded quasicharacter sheaves and finite quasicharacter sheaves, respectively,
+Sections~\ref{sec:descentG} and \ref{sec:finite} describe bounded quasicharacter sheaves and finite quasicharacter sheaves, respectively,
 forming two important subcategories of $\QC(G)$.
@@
 
-\section{Quasicharacter sheaves on connected commutative algebraic groups}
-
-Before turning our attention to quasicharacter sheaves on connected commutative algebraic groups in Section~\ref{sec:connected}, we being with two sections that treat two special classes of quasicharacter sheaves on arbitrary smooth commutative group schemes $G$: those that descend from local systems on $\bG$ to local systems on $G$ in Section~\ref{sec:bounded}; and those local systems on $G$ that are defined by discrete isogenies onto $G$ in Section~\ref{sec:discrete_isogenies}.
+\section{Quasicharacter sheaves defined by discrete isogenies}
+
+Before turning our attention to quasicharacter sheaves on connected commutative algebraic groups in Section~\ref{sec:connected}, we treat two special classes of quasicharacter sheaves on arbitrary smooth commutative group schemes $G$:  in Section~\ref{sec:descentG}, those that descend from local systems on $\bG$ to local systems on $G$; and in Section~\ref{sec:discrete_isogenies}, those that are defined by discrete isogenies onto $G$.
 The latter will play a role in Sections~\ref{sec:connected} and \ref{sec:restriction}.
 
-\subsection{Descent to G}\label{sec:bounded}
+\subsection{Descent to G}\label{sec:descentG}
 
@@
   the latter appearing in the definition of $\qcs{L}$.
-  Then, as in Section~\ref{sec:bounded}, $(\qcs{E},\mu_\qcs{E})$ is an object in $\bQC(G)$
+  Then, as in Section~\ref{sec:descentG}, $(\qcs{E},\mu_\qcs{E})$ is an object in $\bQC(G)$
   and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{E},b_{G\times G}^*\mu_\qcs{E})$ in $\QC(G)$.
-  Thus, the full and faithful functor $B_G : \bQC(G) \to \QC(G)$ from Section~\ref{sec:bounded}
+  Thus, the full and faithful functor $B_G : \bQC(G) \to \QC(G)$ from Section~\ref{sec:descentG}
   is also essentially surjective, hence an equivalence.
@@
 
+\section{Notes for the new Introduction}
+
+Motivated to an application to the geometrization and categorification of quasicharacters of p-adic tori,
+this paper extends Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields to all smooth commutative group schemes over finite fields.
+
+As Deligne explained in \cite{deligne:SGA4.5}*{sommes trig.}, if $G$ is a connected commutative algebraic group over $\FF_q$, then the trace of Frobenius provides a perfect dictionary between characters of $G(\FF_q)$ and isomorphism classes of rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which $m^*\qcs{E} \iso \qcs{E} \boxtimes \qcs{E}$, where $m : G\times G\to G$ is the multiplication map.
+If one wishes to make a category from this class of local systems, one is lead to consider sheaf morphisms $\qcs{E} \to \qcs{E}'$ which are compatible with particular choices of isomorphisms $m^*\qcs{E} \iso \qcs{E} \boxtimes \qcs{E}$ and $m^*\qcs{E}' \iso \qcs{E}'\boxtimes \qcs{E}'$.
+{\it A priori}, these sheaf morphisms do not form a category, since
+
 \bibliographystyle{amsalpha}

### 2014-08-21 dictionary.tex
Working on material for the introduction, in \S 6.

@@
 
+%\begin{remark}
 We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of quasicharacter sheaves on $G$ is equivalent to the category of characters $\psi$ of $G(\Fq)$.
 We have also just seen that if the character of $\Lang^*\qcs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\qcs{E} : \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ which is part of the data that determines a quasicharacter sheaf on $G$.
-That leads to a perspective on the function--sheaf dictionary common in the literature in which one considers $1$-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$.
-% as in \cite{kamgarpour:09a}*{Introduction} (or sometimes, $1$-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$).
-%
+That leads to a perspective on the function--sheaf dictionary common in the literature in which one considers $1$-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$; see \cite{kamgarpour:09a}*{Introduction}, for example.
+As a slight variation, one may also consider $1$-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
+One may show that all such $\gqcs{L}$ are determined by extensions of $\bG$ by $\EEx$ which are fixed by Frobenius and that the trace of Frobenius provides a canonical isomorphism from $\Hh^2(\bG,\EEx)^{\Frob{}}$ to $G(\Fq)^*$; {\it cf.\ }\cite{kamgarpour:09a}*{Prop 2.15}.
+%
+
 Although the category of quasicharacter sheaves on $G$ does specialize to that common notion when $G$ is connected and of finite type, the common notion is not appropriate if one wishes to extend the dictionary to smooth commutative group schemes over finite fields.
 In particular, as we have already seen in Section~\ref{sec:etale}, for a given quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ there may be a different isomorphism $\mu' : \bm^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$ for which $\qcs{L}'=(\gqcs{L},\mu',\phi)$ is also a quasicharacter sheaf on $G$, not isomorphic to $\qcs{L}$ in $\QC(G)$.
-Indeed, Proposition~\ref{prop:etale-iso} shows that $\Hh^0(\Weil{},\Hh^2(\bG,\EEx))$ measures the possibilities for $\mu'$ when $G$ is etale.
-We will see in Section~\ref{sec:main} that, for any smooth commutative group scheme $G$, the possibilities for $\mu'$ are measured by $\Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx))$.
+Indeed, Proposition~\ref{prop:etale-iso} shows that when $G$ is etale, $\Hh^2(\bG,\EEx)^{\Frob{}}$ measures the possibilities for $\mu'$.
+In other words, the common perspective on the function--sheaf dictionary leads only, and exactly, to the part of category of quasicharacter sheaves that is {\it completely invisible} to the trace of Frobenius!
+
+We will see in Section~\ref{sec:main} that, for any smooth commutative group scheme $G$, the part of category of quasicharacter sheaves that is invisible to the trace of Frobenius are measured by $\Hh^2(\pi_0(\bG),\EEx)^{\Frob{}}$.
+%\end{remark}
 
@@
 \begin{lemma} \label{lem:G0alg-grp}
-If $G$ is a commutative smooth group scheme over $\Fq$ then its identity component,$G^0$ is a connected algebraic group over $\Fq$.
+If $G$ is a commutative smooth group scheme over $\Fq$ then its identity component, $G^0$, is a connected algebraic group over $\Fq$.
 \end{lemma}
@@
 
-Motivated to an application to the geometrization and categorification of quasicharacters of p-adic tori,
+Motivated by an application to the geometrization and categorification of quasicharacters of p-adic tori,
 this paper extends Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields to all smooth commutative group schemes over finite fields.
 
-As Deligne explained in \cite{deligne:SGA4.5}*{sommes trig.}, if $G$ is a connected commutative algebraic group over $\FF_q$, then the trace of Frobenius provides a perfect dictionary between characters of $G(\FF_q)$ and isomorphism classes of rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which $m^*\qcs{E} \iso \qcs{E} \boxtimes \qcs{E}$, where $m : G\times G\to G$ is the multiplication map.
-If one wishes to make a category from this class of local systems, one is lead to consider sheaf morphisms $\qcs{E} \to \qcs{E}'$ which are compatible with particular choices of isomorphisms $m^*\qcs{E} \iso \qcs{E} \boxtimes \qcs{E}$ and $m^*\qcs{E}' \iso \qcs{E}'\boxtimes \qcs{E}'$.
-{\it A priori}, these sheaf morphisms do not form a category, since
+As Deligne explained in \cite{deligne:SGA4.5}*{sommes trig.}, if $G$ is a connected commutative algebraic group over $\FF_q$, then the trace of Frobenius provides a perfect dictionary between characters of $G(\FF_q)$ and isomorphism classes of rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which
+\begin{equation}\label{introbox}
+m^* \qcs{E} \iso \qcs{E} \boxtimes \qcs{E},\tag{0}
+\end{equation}
+where $m : G\times G\to G$ is the multiplication map.
+%
+If one wishes to make a category from this class of local systems, one is led to consider sheaf morphisms $\qcs{E} \to \qcs{E}'$ which are compatible with particular choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E'}$.
+{\it A priori}, these sheaf morphisms do not form a category, but since $G$ is connected, the existence of \eqref{introbox} makes \eqref{introbox} unique; as a consequence, there is no impediment to categorifying the dictionary in this case.
+
+If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, however, then one must keep track of the choice of \eqref{introbox}, leading to a category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is an isomorphism of local systems on $G\times G$.
+As we show in this paper, if the component group scheme $\pi_0(G)$ (which is an étale commutative group scheme over $\FF_q$) is not cyclic, then while the trace of Frobenius provides a surjection from isomorphism classes in the category of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\FF_q)$, that group homomorphism need not be injective.
+In other words, if $G$ is a commutative algebraic group over $\FF_q$ which is not connected, then every character may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely.
+While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious since, as we show in the paper, if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\FF_q)$, then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
+
+In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$ we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system.
+In this way we are lead to the category of quasicharacter sheaves on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} = G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way.
+
+Étale group schemes form a counterpoint to connected algebraic groups,
+since the component group of a smooth commutative group scheme
+is an étale group scheme. 
+Accordingly, we first test the category of quasicharacter sheaves by examining its objects on etale commutative group schemes $G$ over $\FF_q$.
+Here again we find that the dictionary is imperfect: the trace of Frobenius provides a group epimorphism from isomorphism classes of quasicharacter sheaves on $G$ to characters of $G(\FF_q)$; the kernel of this epimorphism is $\Hh^2(\bG,\EEx)^{\Frob{}}$.
+Again, this imperfection should not be too troubling: if $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
+
+Returning to the case of connected commutative algebraic groups $G$ over $\Fq$, we confirm that, in this case, the category of quasicharacter sheaves on $G$ is equivalent to the category of characters $\psi$ of $G(\Fq)$, the equivalence being given by pullback by the Lang isogeny for $G$.
+Indeed, one may show that isomorphism classes of quasicharacter sheaves on $G$ are determined by classes of extensions of $\bG$ by $\EEx$ which are fixed by Frobenius, and therefore given by $\Hh^2(\bG,\EEx)^{\Frob{}}$ to $G(\Fq)^*$.
+
+Although the category of quasicharacter sheaves on $G$ does specialize to that common notion when $G$ is connected and of finite type, the common notion is not appropriate if one wishes to extend the dictionary to smooth commutative group schemes over finite fields.
+In particular, as we have already seen in Section~\ref{sec:etale}, for a given quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ there may be a different isomorphism $\mu' : \bm^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$ for which $\qcs{L}'=(\gqcs{L},\mu',\phi)$ is also a quasicharacter sheaf on $G$, not isomorphic to $\qcs{L}$ in $\QC(G)$.
+Indeed, Proposition~\ref{prop:etale-iso} shows that when $G$ is etale, $\Hh^2(\bG,\EEx)^{\Frob{}}$ measures the possibilities for $\mu'$.
+In other words, the common perspective on the function--sheaf dictionary leads only, and exactly, to the part of category of quasicharacter sheaves that is {\it completely invisible} to the trace of Frobenius!
+
+We will see in Section~\ref{sec:main} that, for any smooth commutative group scheme $G$, the part of category of quasicharacter sheaves that is invisible to the trace of Frobenius are measured by $\Hh^2(\pi_0(\bG),\EEx)^{\Frob{}}$.
+%\end{remark}
 

### 2014-08-21 dictionary.tex
Working on summary of sections

--- 2014-08-21 dictionary.tex
@@
 in Section~\ref{sec:category} we define the category of quasicharacter sheaves.
-We define pullbacks and products of quasicharacter sheaves in Section~\ref{sec:pullback}
-Section~\ref{sec:Frob} introduces Trace of Frobenius,
-one direction of the function--sheaf dictionary.
-, and use
-them to prove a functoriality result on Trace of Frobenius.
+Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism $\TrFrob{G} : \QCiso{G} \to \Hom(G(k), \EEx)$.
+We also define pullbacks of quasicharacter sheaves along morphisms of group schemes.  Applying pullbacks to the component group
+sequence for $G$ yields the diagram
+ \begin{equation} \label{eq:intro-snake}
+  \begin{tikzcd}[row sep=20]
+    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
+    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
+    0 \rar & \pi_0(G)(\Fq)^* \rar & G(\Fq)^* \rar & G^0(\Fq)^* \rar & 0,\\
+  \end{tikzcd}
+  \end{equation}
+which is central to the proof of Theorem \ref{thm:snake}.  Much of Sections \ref{sec:etale}, \ref{sec:disc-isog} and \ref{sec:main}
+are devoted to proving that the rows of \eqref{eq:intro-snake} are exact and determining the kernels and cokernels of the vertical maps.
+
+Section~\ref{sec:etale} is devoted to the left-most vertical morphism in \eqref{eq:intro-snake}
 In Section~\ref{sec:basechange} we study how quasicharacter sheaves behave under base change
@@
 
-\section{Quasicharacter sheaves defined by discrete isogenies}
+\section{Quasicharacter sheaves defined by discrete isogenies} \label{sec:disc-isog}
 

### 2014-08-22 dictionary.tex
Changes to the Introduction

@@
 
-%\subsection*{Overview}
-
-%Deligne's function--sheaf dictionary translates characters of connected, commutative algebraic groups $G$ over finite fields $\Fq$ into certain local systems on G, from which the character of $G(\Fq)$ can be recovered using the action of Frobenius on $G$.
-%The local systems which appear in this dictionary are easily characterised and often referred to as \emph{character sheaves} on $G$.
-%The result is a perfect dictionary between characters of $G(\Fq)$ and character sheaves on G, with which the formidable artillery of algebraic geometry can be brought to bear on the study of characters of $G(\Fq)$.
+Motivated by an application to the geometrization and categorification of quasicharacters of p-adic tori,
+this paper extends Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields to all smooth commutative group schemes over finite fields.
+
+As Deligne explained in \cite{deligne:SGA4.5}*{Sommes trig.}, if $G$ is a connected commutative algebraic group over $\FF_q$, then the trace of Frobenius provides a perfect dictionary between characters of $G(\FF_q)$ and isomorphism classes of rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which
+\begin{equation}\label{introbox}
+m^* \qcs{E} \iso \qcs{E} \boxtimes \qcs{E},\tag{0}
+\end{equation}
+where $m : G\times G\to G$ is the multiplication map.
 %
-%In this paper we show how this dictionary extends to the case when $G$ is not connected, and even to all smooth commutative group schemes over $\Fq$, in which case some interesting new features of the dictionary arise.
-
-%\subsection{The main result}
-
-Let us briefly review how Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields \cite{deligne:SGA4.5}*{sommes trig.} translates characters into local systems.
-Let $\Fq$ be a finite field and let $G$ be a connected commutative algebraic group over $\Fq$; fix an algebraic closure $\bFq$ of $\Fq$
-and let $\bG$ be the base change of $G$ to $\bFq$.
-Fix a prime $\ell$ invertible in $\Fq$ and let $\chi : G(\Fq) \to \EEx$ be any character.
-Using little more than the Lang map for $G$, $\chi$ determines an $\ell$-adic local system $\qcs{L}$ on $G$ from which the character $\chi$ can be recovered using the Frobenius automorphism of $\bG$.
-While this recovery process applies to all $\ell$-adic local systems $\qcs{L}$ on $G$, those that produce characters of $G(\Fq)$ are distinguished by a simple property: there \emph{exists} an isomorphism
-\begin{equation}\label{introbox}
-m^* \qcs{L} \iso \qcs{L} \boxtimes \qcs{L}
-\end{equation}
- of $\ell$-adic local systems on $G$, where $m : G\times G \to G$ is the multiplication map for $G$.
-The function--sheaf dictionary for $G$ identifies a monoidal category of $\ell$-adic local systems on $G$ such that the group of isomorphism classes in this category is canonically identified with the $\ell$-adic character group of $G(\Fq)$, thus providing the geometrization and categorification of characters of $G(\Fq)$.
-%
-Although hidden in this discussion, the connectedness of $G$ played a crucial role in the geometrization and categorification of characters of $G(\Fq)$.
-In particular, when the isomorphism \eqref{introbox} exists for $\qcs{L}$, it is essentially unique.
-
-Now let $G$ be any smooth commutative group scheme over $\Fq$.
-Two new features must be addressed in order to geometrize characters of $G(\Fq)$.
-First, we must pass from $\ell$-adic local systems on $G$ to Weil local systems on $G$
-and, second, we must keep track of the isomorphisms \eqref{introbox}.
-Both issues are addressed in the main definition of this paper:
-A \emph{quasicharacter sheaf} on $G$ is a triple $\qcs{L}\ceq
-(\gqcs{L},\mu,\phi)$ where $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ of rank~one and $\mu: m^*
-\gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms satisfying natural compatibility conditions; here $\Frob{G}$ is the Frobenius automorphism of ${\bar G}$.
- In the main result of this paper, Theorem~\ref{thm:snake},
-we form a rigid monoidal category $\lQC(G)$ of quasicharacter sheaves on $G$
-and show that the Trace of Frobenius provides a functorial group isomorphism
-\begin{equation}
-\lQCiso{G} \to \Hom(G(\Fq), \EEx).
-\end{equation}
-\todo{change to remove flabbyness}
-
-%\subsection*{Illustrative Examples}
-
-%Three examples will illustrate some of the issues that arise when extending the function--sheaf dictionary to smooth commutative group schemes over $\Fq$.
-As we show in the paper, $\ell$-adic local systems on $G$ can only be used to geometrize characters of finite order; quasicharacter sheaves, however, provide the geometrization of all characters of $G(\Fq)$.
-For example, we will see how to geometrize the character $\ZZ \to \EEx$ defined by
-$1 \mapsto \ell$, which has unbounded image,
-using quasicharacter sheaves on the etale group scheme $\ZZ$ with trivial Galois action.
-%Likewise, the dictionary is perfect for the etale group scheme $\ZZ$ with Galois action determined by $\Frob{}(n) = -n$.
-By contract, the etale group scheme $\ZZ \times \ZZ$ with trivial Galois action does admit invisible quasicharacter sheaves -- there are non-trivial quasicharacter sheaves on this group with trivial trace of Frobenius.\todo{Under construction} (Move this example: Define $g: \ZZ\times \ZZ \to \EEx$ by $g((n_1,m_1), (n_2, m_2)) = \ell^{m_1-m_2 + n_1-n_2}$.
-Then use the tehniques of Section~\ref{sec:etale} to build a non-trivial character sheaf from the pair $(f=1,g)$ with trivial trace of Frobenius.)
-
-%\subsection*{Motivation and Application}
-
-Our interest in the function--sheaf dictionary for smooth commutative group schemes over $\Fq$, especially etale commutative group schemes, comes from an application to $p$-adic representation theory.
-In \cite{cunningham-roe:13a} we consider quasicharacter sheaves on the
-Greenberg transform of the N\'eron model of an algebraic torus over an arbitrary local field.
-The ability to work with non-connected group schemes,
-of which the component group of the special fibre of the Néron model of a torus is an important example,
-plays a crucial role in this application,
+If one wishes to make a category from this class of local systems, one is led to consider sheaf homorphisms $\qcs{E} \to \qcs{E}'$ which are compatible with particular choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E'}$.
+{\it A priori}, these sheaf homomorphisms do not form a category, but since $G$ is connected, the existence of \eqref{introbox} makes \eqref{introbox} unique; as a consequence, there is no impediment to categorifying the dictionary in this case.
+
+If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, however, then one must keep track of the choice of \eqref{introbox}, leading to a category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is an isomorphism of local systems on $G\times G$.
+As we show in this paper, if the component group scheme $\pi_0(G)$ (which is an étale commutative group scheme over $\FF_q$) is not cyclic, then while the trace of Frobenius provides a surjection from isomorphism classes in the category of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\FF_q)$, that group homomorphism need not be injective.
+In other words, if $G$ is a commutative algebraic group over $\FF_q$ which is not connected, then every character may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely. 
+While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not a serious defect since if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\FF_q)$, then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
+
+In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$ we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system, while retaining the extra structure $\mu_\qcs{E}$.
+In this way we are lead to the category $\QC(G)$ of quasicharacter sheaves on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} = G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way.
+Morphism in $\QC(G)$ are homomorphisms of Weil sheaves which are compatible with the extra structure.
+
+Étale group schemes form a counterpoint to connected algebraic groups,
+since the component group of a smooth commutative group scheme
+is an étale group scheme. 
+Accordingly, we first test the category of quasicharacter sheaves by examining its objects on etale commutative group schemes $G$ over $\FF_q$.
+Here again we find that the dictionary is imperfect: the trace of Frobenius provides a group epimorphism from isomorphism classes of quasicharacter sheaves on $G$ to characters of $G(\FF_q)$; the kernel of this epimorphism is naturally identified with $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$.
+Again, this imperfection should not be too troubling: if $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
+
+Returning to the case of connected commutative algebraic groups $G$ over $\FF_q$, we confirm that, in this case, the category of quasicharacter sheaves on $G$ is equivalent to the category of characters $\psi$ of $G(\FF_q)$, the equivalence being given by pullback by the Lang isogeny for $G$.
+Indeed, one may show that isomorphism classes of quasicharacter sheaves on $G$ are determined by classes of extensions of $\bG$ by $\EEx$ which are fixed by Frobenius, and therefore given by $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$.
+
+The appearance of $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ and the trace of Frobenius gives an isomorphism $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\FF_q$, then $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ measures the kernel of $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$.
+This observation makes plain the fact that while characters of connected commutative algebraic groups $G$ can be geometrized using  local systems trivialized by discrete isogenies to $G$, this is not the right perspective if one wishes to geometrize characters of smooth commutative group schemes, such as etale commutative group schemes.
+Indeed, quasicharacter sheaves on etale commutative group schemes that are trivialized by discrete isogenies are invisible to the trace of Frobenius.
+
+Having understood quasicharacter sheaves on commutative smooth group schemes over $\FF_q$ in two extreme cases -- connected algebraic groups and etale commutative group schemes -- we turn to the general case.
+Remarkably, we find that the general case can be understood from these two extreme cases, using the component group sequence
+\[
+0 \to G^0 \to G \to \pi_0(G) \to 0.
+\]
+The main result of the paper uses this sequence to find $\QCiso{G}$ by situating it in a canonical short exact sequence
+\[
+0 \to \Hh^2(\pi_0(\bG),\EEx)^{\Gal({\bar\FF}_q/\FF_q)} \to \QCiso{G} \to \Hom(G(\FF_q),\EEx) \to 0.
+\]
+We also illuminate the nature of the category $\QC(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing that $\Aut(\qcs{L}) \iso \Hom(G(\bFq)_{\Gal(\bFq/\Fq)},\EEx)$, canonically, for all quasicharacter sheaves $\qcs{L}$ on $G$.
+
+Joseph Bernstein has suggested to us that we should not view
+
+Our interest in the function--sheaf dictionary for smooth commutative group schemes over $\Fq$ comes from an application to $p$-adic representation theory.
+In this paper we show quasicharacters of $p$-adic tori are geometrized and categorified by quasicharacter sheaves on the
+Greenberg transform of the N\'eron model of the $p$-adic torus. 
+The ability to generalize the function--sheaf dictionary to non-connected group schemes, of which the component group of the special fibre of the Néron model of a torus is an important example, plays a crucial role in this application,
 since these group schemes are not connected in general.
@@
 see for example, \cite{kamgarpour:09a}.
-As explained above, quasicharacter sheaves evolved from this notion,
+As our application reveals, quasicharacter sheaves evolved from this notion,
 with an eye toward quasicharacters of $p$-adic groups.
@@
 beginning with \cite{lusztig:disconnected1}.
-When commutative, such groups are extensions of $\ZZ/n\ZZ$ by a torus,
+When commutative, such groups are extensions of finite cyclic groups by algebraic tori,
 in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
-The interesting new features pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Frob{G}}$ do not arise in this case.
+The interesting new features pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ do not arise in this context.
 
@@
 
-\section{Notes for the new Introduction}
-
-Motivated by an application to the geometrization and categorification of quasicharacters of p-adic tori,
-this paper extends Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields to all smooth commutative group schemes over finite fields.
-
-As Deligne explained in \cite{deligne:SGA4.5}*{sommes trig.}, if $G$ is a connected commutative algebraic group over $\FF_q$, then the trace of Frobenius provides a perfect dictionary between characters of $G(\FF_q)$ and isomorphism classes of rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which
-\begin{equation}\label{introbox}
-m^* \qcs{E} \iso \qcs{E} \boxtimes \qcs{E},\tag{0}
-\end{equation}
-where $m : G\times G\to G$ is the multiplication map.
-%
-If one wishes to make a category from this class of local systems, one is led to consider sheaf morphisms $\qcs{E} \to \qcs{E}'$ which are compatible with particular choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E'}$.
-{\it A priori}, these sheaf morphisms do not form a category, but since $G$ is connected, the existence of \eqref{introbox} makes \eqref{introbox} unique; as a consequence, there is no impediment to categorifying the dictionary in this case.
-
-If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, however, then one must keep track of the choice of \eqref{introbox}, leading to a category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is an isomorphism of local systems on $G\times G$.
-As we show in this paper, if the component group scheme $\pi_0(G)$ (which is an étale commutative group scheme over $\FF_q$) is not cyclic, then while the trace of Frobenius provides a surjection from isomorphism classes in the category of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\FF_q)$, that group homomorphism need not be injective.
-In other words, if $G$ is a commutative algebraic group over $\FF_q$ which is not connected, then every character may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely.
-While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious since, as we show in the paper, if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\FF_q)$, then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
-
-In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$ we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system.
-In this way we are lead to the category of quasicharacter sheaves on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} = G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way.
-
-Étale group schemes form a counterpoint to connected algebraic groups,
-since the component group of a smooth commutative group scheme
-is an étale group scheme. 
-Accordingly, we first test the category of quasicharacter sheaves by examining its objects on etale commutative group schemes $G$ over $\FF_q$.
-Here again we find that the dictionary is imperfect: the trace of Frobenius provides a group epimorphism from isomorphism classes of quasicharacter sheaves on $G$ to characters of $G(\FF_q)$; the kernel of this epimorphism is $\Hh^2(\bG,\EEx)^{\Frob{}}$.
-Again, this imperfection should not be too troubling: if $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
-
-Returning to the case of connected commutative algebraic groups $G$ over $\Fq$, we confirm that, in this case, the category of quasicharacter sheaves on $G$ is equivalent to the category of characters $\psi$ of $G(\Fq)$, the equivalence being given by pullback by the Lang isogeny for $G$.
-Indeed, one may show that isomorphism classes of quasicharacter sheaves on $G$ are determined by classes of extensions of $\bG$ by $\EEx$ which are fixed by Frobenius, and therefore given by $\Hh^2(\bG,\EEx)^{\Frob{}}$ to $G(\Fq)^*$.
-
-Although the category of quasicharacter sheaves on $G$ does specialize to that common notion when $G$ is connected and of finite type, the common notion is not appropriate if one wishes to extend the dictionary to smooth commutative group schemes over finite fields.
-In particular, as we have already seen in Section~\ref{sec:etale}, for a given quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ there may be a different isomorphism $\mu' : \bm^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$ for which $\qcs{L}'=(\gqcs{L},\mu',\phi)$ is also a quasicharacter sheaf on $G$, not isomorphic to $\qcs{L}$ in $\QC(G)$.
-Indeed, Proposition~\ref{prop:etale-iso} shows that when $G$ is etale, $\Hh^2(\bG,\EEx)^{\Frob{}}$ measures the possibilities for $\mu'$.
-In other words, the common perspective on the function--sheaf dictionary leads only, and exactly, to the part of category of quasicharacter sheaves that is {\it completely invisible} to the trace of Frobenius!
-
-We will see in Section~\ref{sec:main} that, for any smooth commutative group scheme $G$, the part of category of quasicharacter sheaves that is invisible to the trace of Frobenius are measured by $\Hh^2(\pi_0(\bG),\EEx)^{\Frob{}}$.
-%\end{remark}
-
 \bibliographystyle{amsalpha}

### 2014-08-22 dictionary.tex
More work on the Introduction

@@
 \subjclass[2010]{14F05 (primary), 14L15 (secondary)}
-\keywords{function--sheaf dictionary, trace of Frobenius, geometrization, quasicharacters, quasicharacter sheaves, smooth commutative group schemes}
+\keywords{function--sheaf dictionary, trace of Frobenius, geometrization, categorification, quasicharacters, quasicharacter sheaves, smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor}
 
@@
 \usepackage{hyperref}
-
+\setcounter{section}{-1}
 %%%%%%%%%%%%%%% THEOREM STYLES %%%%%%%%%%%%%%%
@@
 
-\section*{Introduction}
+\section{Introduction}
 
@@
 The main result of the paper uses this sequence to find $\QCiso{G}$ by situating it in a canonical short exact sequence
-\[
+\begin{equation}
 0 \to \Hh^2(\pi_0(\bG),\EEx)^{\Gal({\bar\FF}_q/\FF_q)} \to \QCiso{G} \to \Hom(G(\FF_q),\EEx) \to 0.
-\]
-We also illuminate the nature of the category $\QC(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing that $\Aut(\qcs{L}) \iso \Hom(G(\bFq)_{\Gal(\bFq/\Fq)},\EEx)$, canonically, for all quasicharacter sheaves $\qcs{L}$ on $G$.
-
-Joseph Bernstein has suggested to us that we should not view
-
-Our interest in the function--sheaf dictionary for smooth commutative group schemes over $\Fq$ comes from an application to $p$-adic representation theory.
-In this paper we show quasicharacters of $p$-adic tori are geometrized and categorified by quasicharacter sheaves on the
-Greenberg transform of the N\'eron model of the $p$-adic torus. 
-The ability to generalize the function--sheaf dictionary to non-connected group schemes, of which the component group of the special fibre of the Néron model of a torus is an important example, plays a crucial role in this application,
+\end{equation}
+We remark that $\Hh^2(\pi_0(\bG),\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ is non-trivial even for some commutative algebraic groups.
+We also illuminate the nature of the category $\QC(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing that 
+\begin{equation}
+\Aut(\qcs{L}) \iso \Hom(G(\bFq)_{\Gal(\bFq/\Fq)},\EEx),
+\end{equation}
+canonically, for all quasicharacter sheaves $\qcs{L}$ on $G$.
+
+\subsection{Applications over local fields}
+
+As indicated above, our interest in the function--sheaf dictionary for smooth commutative group schemes over finite fields comes from an application to $p$-adic representation theory.
+In this paper we show that quasicharacters of $p$-adic tori $T$ over local fields $K$ are geometrized and categorified by quasicharacter sheaves on the
+Greenberg transform of the N\'eron model of $T$, which is a commutative group scheme over the residue field of $K$, denoted by $\Gr(\underline{T})$.
+While $\Gr(\underline{T})$ is not smooth, it is a projective limit of smooth commutative group schemes $\Gr_n(\underline{T})$, and this allows us to adapt the work above to construct a category $\QC(\Gr_R(\underline{T}))$ of quasicharacter sheaves on $\Gr(\underline{T})$.
+The ability to generalize the function--sheaf dictionary to non-connected group schemes, of which the component group of the special fibre of the Néron model of a torus is an important example, plays a crucial role in this application
 since these group schemes are not connected in general.
-This process of creating a category from the group of quasicharacters of such a torus
-informs our choice of the term quasicharacter sheaf, here.
-
-%\subsection*{Comparison with other character sheaves}
-
+This paper gives a canonical short exact sequence 
+\begin{equation}
+0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Frob{}} \to \QCiso{\Gr_R(\underline{T})} \to \Hom_\text{qc}(T(K),\EEx) \to 0
+\end{equation}
+and shows that automorphism groups in the $\QC(\Gr_R(\underline{T}))$ are given, for every quasicharacter sheaf $\qcs{F}$ on $\Gr_R(X)$, by
+\begin{equation}
+\Aut(\qcs{F}) \iso (\check{T}_\ell)^{\Weil{K}}
+\end{equation}
+where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
+
+Joseph Bernstein has suggested to us that we should not interpret the fact that the quasicharacter sheaves on $\Gr(\underline{T})$ do not correspond exactly to quasicharacters of $T(K)$ as an imperfection.
+Rather, he has suggested that the category $\QC(\Gr(\underline{T})$ may be more closely tied to characters of $T(K)$ and its pure rational forms in the sense of \cite{vogan:93a}.
+A better understanding of
+$\Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Frob{}}$ should provide insight into this suggestion.
+
+\subsection{Comparison with character sheaves}
+
+The process of creating a category from the group of quasicharacters of a $p$-adic  torus, as explained above, informs our choice of the term quasicharacter sheaf in this paper.
 We also want to situate our terminology in a historical context.
 It is not uncommon to refer to local systems satisfying \eqref{introbox} on a connected, commutative algebraic group as character sheaves;
-see for example, \cite{kamgarpour:09a}.
-As our application reveals, quasicharacter sheaves evolved from this notion,
+see for example, \cite{kamgarpour:09a}*{Intro}.
+As we have indicated, quasicharacter sheaves evolved from this notion,
 with an eye toward quasicharacters of $p$-adic groups.
@@
 in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
-The interesting new features pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ do not arise in this context.
-
-%\subsection*{Structure of the paper}
+The interesting new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ do not arise in this context.
+
+\subsection{Structure of the paper}
 \todo{Describe the overall structure of the paper in enough detail that one can follow the argument; include snake lemma diagram}
@@
 %\begin{acknowledgements}
-\subsection*{Acknowledgments}
+\subsection{Acknowledgments}
 We thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
@@
 We have also just seen that if the character of $\Lang^*\qcs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\qcs{E} : \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ which is part of the data that determines a quasicharacter sheaf on $G$.
-That leads to a perspective on the function--sheaf dictionary common in the literature in which one considers $1$-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$; see \cite{kamgarpour:09a}*{Introduction}, for example.
+That leads to a perspective on the function--sheaf dictionary common in the literature in which one considers $1$-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$; see \cite{kamgarpour:09a}*{Intro}, for example.
 As a slight variation, one may also consider $1$-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
@@
 every $\rho \in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism.
-Moreover, $\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$, canonically.
+Moreover, 
+\[
+\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx),
+\]
+ canonically.
 \end{theorem}
@@
 \begin{definition}
+Let $X_K$ be a connected commutative group scheme that admits a Neron model, $X$.
 A {\it quasicharacter sheaf on $\Gr_R(X)$} is an object $\qcs{F}$ in $\mathcal{C}(\Gr_R(X))$ such that $\qcs{F} \iso P^R_n(X)^*\qcs{L}$ for some quasicharacter sheaf $\qcs{L}$ on $\Gr^R_n(X)$.
@@
 \[
-\Aut(\qcs{F}) \iso \Hom((\pi_0(X)_{\Fq})_{\Weil{}},\EEx),
+\Aut(\qcs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx),
 \]
@@
 \[
-\Aut(\qcs{L}) \iso \Hom((\pi_0(X)_{\Fq})_{\Weil{}},\EEx),
+\Aut(\qcs{L}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx),
 \]
@@
 \end{proof}
+
+\subsection{Quasicharacters of $p$-adic tori}
+
+As we explained in the Introduction, our original motivation for this paper was to find a geometrization and categorification of quasicharacters of $p$-adic tori.
+This is is now provided by specializing Theorem~\ref{thm:QCXK} to the case when $X_K= T\in \mathcal{N}_K$ is an algebraic torus over $K$, in which case we write $\underline{T}$ for the Neron model $X$.
+Now,
+\[
+ \pi_0(\underline{T})_{\bFq} = X_*(T)_{\mathcal{I}_K},
+\]
+where $X_*(T)$ is the cocharacter lattice of $T$ and $\mathcal{I}_K$ is the inertia group for $K$ \cite{bitan:discriminant}*{Eq 3.1}. 
+Accordingly, the short exact sequence in Theorem~\ref{thm:QCXK} becomes
+\begin{equation}
+0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Frob{}} \to \QCiso{\Gr_R(\underline{T})} \to \Hom_\text{qc}(T(K),\EEx) \to 0.
+\end{equation}
+Again by Theorem~\ref{thm:QCXK}, the automorphism groups in the $\QC(\Gr_R(\underline{T}))$ are given, for every quasicharacter sheaf $\qcs{F}$ on $\Gr_R(X)$, by
+\begin{equation}
+\Aut(\qcs{F}) \iso \Hom(X_*(T)_{\Weil{K}},\EEx) = \Hom(X_*(T),\EEx)^{\Weil{K}} = (X^*(T)\otimes \EEx)^{\Weil{K}} = (\check{T}_\ell)^{\Weil{K}}
+\end{equation}
+where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
 
@@
 \[
-\Hom_{\text{qc}}(T(K'),\EEx) \to \Hom_{\text{qc}}(T(K),\EEx).
+\Hom_{\text{qc}}(X_K(K'),\EEx) \to \Hom_{\text{qc}}(X_K(K),\EEx).
 \]

### 2014-08-22 dictionary.tex
Improvements to the Introduction

@@
 Returning to the case of connected commutative algebraic groups $G$ over $\FF_q$, we confirm that, in this case, the category of quasicharacter sheaves on $G$ is equivalent to the category of characters $\psi$ of $G(\FF_q)$, the equivalence being given by pullback by the Lang isogeny for $G$.
-Indeed, one may show that isomorphism classes of quasicharacter sheaves on $G$ are determined by classes of extensions of $\bG$ by $\EEx$ which are fixed by Frobenius, and therefore given by $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$.
-
-The appearance of $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ and the trace of Frobenius gives an isomorphism $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\FF_q$, then $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ measures the kernel of $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$.
-This observation makes plain the fact that while characters of connected commutative algebraic groups $G$ can be geometrized using  local systems trivialized by discrete isogenies to $G$, this is not the right perspective if one wishes to geometrize characters of smooth commutative group schemes, such as etale commutative group schemes.
+%Indeed, one may show that isomorphism classes of quasicharacter sheaves on $G$ are determined by classes of extensions of $\bG$ by $\EEx$ which are fixed by Frobenius, given by $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$.
+%
+%The appearance of $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ and the trace of Frobenius gives an isomorphism $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\FF_q$, then $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ measures the kernel of $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$.
+%This observation makes plain the fact that w
+While characters of connected commutative algebraic groups $G$ can be geometrized using  local systems trivialized by discrete isogenies to $G$, this is not the right perspective if one wishes to geometrize characters of smooth commutative group schemes, such as etale commutative group schemes.
 Indeed, quasicharacter sheaves on etale commutative group schemes that are trivialized by discrete isogenies are invisible to the trace of Frobenius.
@@
 As indicated above, our interest in the function--sheaf dictionary for smooth commutative group schemes over finite fields comes from an application to $p$-adic representation theory.
-In this paper we show that quasicharacters of $p$-adic tori $T$ over local fields $K$ are geometrized and categorified by quasicharacter sheaves on the
-Greenberg transform of the N\'eron model of $T$, which is a commutative group scheme over the residue field of $K$, denoted by $\Gr(\underline{T})$.
-While $\Gr(\underline{T})$ is not smooth, it is a projective limit of smooth commutative group schemes $\Gr_n(\underline{T})$, and this allows us to adapt the work above to construct a category $\QC(\Gr_R(\underline{T}))$ of quasicharacter sheaves on $\Gr(\underline{T})$.
-The ability to generalize the function--sheaf dictionary to non-connected group schemes, of which the component group of the special fibre of the Néron model of a torus is an important example, plays a crucial role in this application
+We found, however, that this application applies to all local fields $K$ with finite residue field $\Fq$ and all connected commutative algebraic groups $X_K$ over $K$ that do not contain a subgroup of type $\mathbb{G}_\text{a}$.
+Such algebraic groups $X_K$ always admit a Neron model $X$ over $R$, the ring of integers of $K$.
+In this paper we show that quasicharacters of $X_K$ are geometrized and categorified by quasicharacter sheaves on the
+Greenberg transform $\Gr_R(X)$ of the N\'eron model $X$; although not smooth, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and it is a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
+This allows us to adapt our work on quasicharacter sheaves to construct a category $\QC(\Gr_R(X))$ of quasicharacter sheaves on $\Gr(X)$.
+The ability to generalize the function--sheaf dictionary to non-connected group schemes, of which the component group of the special fibre of the Néron model $X$ is an important example, plays a crucial role in this application
 since these group schemes are not connected in general.
-This paper gives a canonical short exact sequence 
+
+Specializing to the case when $X_K$ is an algebraic tori $T$ over $K$, and writing $\underline{T}$ for the Neron model $X$ in this case, this paper gives a canonical short exact sequence 
 \begin{equation}
-0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Frob{}} \to \QCiso{\Gr_R(\underline{T})} \to \Hom_\text{qc}(T(K),\EEx) \to 0
-\end{equation}
-and shows that automorphism groups in the $\QC(\Gr_R(\underline{T}))$ are given, for every quasicharacter sheaf $\qcs{F}$ on $\Gr_R(X)$, by
+0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Frob{}} \to \QCiso{\Gr_R(\underline{T})} \to \Hom_\text{qc}(T(K),\EEx) \to 0,
+\end{equation}
+where $\Hom_\text{qc}(T(K),\EEx)$ denoted the group of quasicharacters of $T(K)$.
+We further show that automorphism groups in the $\QC(\Gr_R(\underline{T}))$ are given, for every quasicharacter sheaf $\qcs{F}$ on $\Gr_R(X)$, by
 \begin{equation}
@@
 where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
-
-Joseph Bernstein has suggested to us that we should not interpret the fact that the quasicharacter sheaves on $\Gr(\underline{T})$ do not correspond exactly to quasicharacters of $T(K)$ as an imperfection.
-Rather, he has suggested that the category $\QC(\Gr(\underline{T})$ may be more closely tied to characters of $T(K)$ and its pure rational forms in the sense of \cite{vogan:93a}.
+We also use quasicharacter sheaves to categorify the transfer of quasicharacters of tori between characteristic $0$ and characteristic $p$ local fields.
+
+Joseph Bernstein has suggested to us that, although quasicharacter sheaves on $\Gr(\underline{T})$ do not correspond exactly to quasicharacters of $T(K)$, the category $\QC(\Gr_R(\underline{T}))$ is the right one to consider.
+He has further suggested that the category $\QC(\Gr(\underline{T})$ may be more closely tied to characters of $T(K)$ and its pure rational forms in the sense of Vogan \cite{vogan:93a} or perhaps the rigid inner twists of Tasho Kaletha.
 A better understanding of 
@@
 As a slight variation, one may also consider $1$-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
-One may show that all such $\gqcs{L}$ are determined by extensions of $\bG$ by $\EEx$ which are fixed by Frobenius and that the trace of Frobenius provides a canonical isomorphism from $\Hh^2(\bG,\EEx)^{\Frob{}}$ to $G(\Fq)^*$; {\it cf.\ }\cite{kamgarpour:09a}*{Prop 2.15}.
-%
+%One may show that all such $\gqcs{L}$ are determined by extensions of $\bG$ by $\EEx$ which are fixed by Frobenius and that the trace of Frobenius provides a canonical isomorphism from $\Hh^2(\bG,\EEx)^{\Frob{}}$ to $G(\Fq)^*$; {\it cf.\ }
+%One may show that all such $\gqcs{L}$ are determined by extensions of $\bG$ by $\EEx$ which are fixed by Frobenius and that the trace of Frobenius provides a canonical isomorphism from $\Hh^2(\bG,\EEx)^{\Frob{}}$ to $G(\Fq)^*$; {\it cf.\ } \cite{kamgarpour:09a}*{Prop 2.15}.
 
@@
 \end{proof}
-
-\todo{Comment, in the introduction, that $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$ is trivial if $\pi_0({\bar G})$ is finite cyclic. Lusztig.}
 

### 2014-08-22 dictionary.tex
Correction and improvements to the introduction

@@
 \begin{equation}
-\Aut(\qcs{L}) \iso \Hom(G(\bFq)_{\Gal(\bFq/\Fq)},\EEx),
+\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Gal(\bFq/\Fq)},\EEx),
 \end{equation}
@@
 As indicated above, our interest in the function--sheaf dictionary for smooth commutative group schemes over finite fields comes from an application to $p$-adic representation theory. 
-We found, however, that this application applies to all local fields $K$ with finite residue field $\Fq$ and all connected commutative algebraic groups $X_K$ over $K$ that do not contain a subgroup of type $\mathbb{G}_\text{a}$.
+We found, however, that this application applies to all local fields $K$ with finite residue field $\Fq$ and all connected commutative algebraic groups $X_K$ over $K$ that do not contain a subgroup of type $\mathbb{G}_\text{a}$, such as Abelian varieties, unipotent $K$-wound groups, and of course, algebraic tori.
 Such algebraic groups $X_K$ always admit a Neron model $X$ over $R$, the ring of integers of $K$.
@@
 
-Joseph Bernstein has suggested to us that, although quasicharacter sheaves on $\Gr(\underline{T})$ do not correspond exactly to quasicharacters of $T(K)$, the category $\QC(\Gr_R(\underline{T}))$ is the right one to consider.
-He has further suggested that the category $\QC(\Gr(\underline{T})$ may be more closely tied to characters of $T(K)$ and its pure rational forms in the sense of Vogan \cite{vogan:93a} or perhaps the rigid inner twists of Tasho Kaletha.
+Joseph Bernstein has suggested to us that, although quasicharacter sheaves on $\Gr(\underline{T})$ do not correspond exactly to quasicharacters of $T(K)$, the category $\QC(\Gr_R(\underline{T}))$ is the right one to consider and that the category $\QC(\Gr(\underline{T})$ may be closely tied to characters of  the pure rational forms of $T$ in the sense of Vogan \cite{vogan:93a} or perhaps the rigid inner twists of Tasho Kaletha.
 A better understanding of 

### 2014-08-22 dictionary.tex
dirty

@@
 
-Motivated by an application to the geometrization and categorification of quasicharacters of p-adic tori,
+Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
 this paper extends Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields to all smooth commutative group schemes over finite fields.
@@
 If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, however, then one must keep track of the choice of \eqref{introbox}, leading to a category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is an isomorphism of local systems on $G\times G$.
-As we show in this paper, if the component group scheme $\pi_0(G)$ (which is an étale commutative group scheme over $\FF_q$) is not cyclic, then while the trace of Frobenius provides a surjection from isomorphism classes in the category of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\FF_q)$, that group homomorphism need not be injective.
+If the component group scheme $\pi_0(G)$ (which is an étale commutative group scheme over $\FF_q$) is not cyclic, then while the trace of Frobenius provides a surjection from isomorphism classes in the category of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\FF_q)$, that group homomorphism need not be injective.
 In other words, if $G$ is a commutative algebraic group over $\FF_q$ which is not connected, then every character may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely. 
@@
 In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$ we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system, while retaining the extra structure $\mu_\qcs{E}$.
-In this way we are lead to the category $\QC(G)$ of quasicharacter sheaves on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} = G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way.
-Morphism in $\QC(G)$ are homomorphisms of Weil sheaves which are compatible with the extra structure.
-
-Étale group schemes form a counterpoint to connected algebraic groups,
-since the component group of a smooth commutative group scheme
-is an étale group scheme. 
-Accordingly, we first test the category of quasicharacter sheaves by examining its objects on etale commutative group schemes $G$ over $\FF_q$.
-Here again we find that the dictionary is imperfect: the trace of Frobenius provides a group epimorphism from isomorphism classes of quasicharacter sheaves on $G$ to characters of $G(\FF_q)$; the kernel of this epimorphism is naturally identified with $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$.
-Again, this imperfection should not be too troubling: if $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
+In this way we are lead to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} = G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way.
+Morphism in $\QC(G)$ are then homomorphisms of Weil sheaves which are compatible with the extra structure.
+
+We first test the category of quasicharacter sheaves by examining its objects on étale commutative group schemes $G$ over $\FF_q$; étale group schemes form a counterpoint to connected algebraic groups, since the component group of a smooth commutative group scheme is an étale group scheme.
+We find that the group homomorphism 
+\begin{equation}
+T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)
+\end{equation}
+provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$, canonically.
+One can show, using the Kunneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
+The fact that $T_G$ is not an isomorohism should not be too troubling because if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
 
@@
 %
-%The appearance of $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ and the trace of Frobenius gives an isomorphism $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\FF_q$, then $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ measures the kernel of $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$.
+%The appearance of $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ and the trace of Frobenius gives an isomorphism $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$; on the other hand, if $G$ an étale commutative group scheme over $\FF_q$, then $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ measures the kernel of $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$.
 %This observation makes plain the fact that w
-While characters of connected commutative algebraic groups $G$ can be geometrized using  local systems trivialized by discrete isogenies to $G$, this is not the right perspective if one wishes to geometrize characters of smooth commutative group schemes, such as etale commutative group schemes.
-Indeed, quasicharacter sheaves on etale commutative group schemes that are trivialized by discrete isogenies are invisible to the trace of Frobenius.
-
-Having understood quasicharacter sheaves on commutative smooth group schemes over $\FF_q$ in two extreme cases -- connected algebraic groups and etale commutative group schemes -- we turn to the general case.
+
+As we show in the paper, while characters of connected commutative algebraic groups $G$ can be geometrized using  local systems trivialized by discrete isogenies to $G$, this is not the right perspective if one wishes to geometrize characters of smooth commutative group schemes, such as étale commutative group schemes.
+Indeed, quasicharacter sheaves on étale commutative group schemes that are trivialized by discrete isogenies are invisible to the trace of Frobenius.
+
+Having understood quasicharacter sheaves on commutative smooth group schemes over $\FF_q$ in two extreme cases -- connected algebraic groups and étale commutative group schemes -- we turn to the general case.
 Remarkably, we find that the general case can be understood from these two extreme cases, using the component group sequence
-\[
+\begin{equation}
 0 \to G^0 \to G \to \pi_0(G) \to 0.
-\]
+\end{equation}
 The main result of the paper uses this sequence to find $\QCiso{G}$ by situating it in a canonical short exact sequence
@@
 %To see why, we begin by specializing the definition of quasicharacter sheaves to the case
-%of etale commutative group schemes,
+%of étale commutative group schemes,
 %using the equivalence $G \mapsto G(\bFq)$
@@
 
-In this section we find a complete characterization of quasicharacter sheaves on etale commutative group schemes over finite fields.
+In this section we find a complete characterization of quasicharacter sheaves on étale commutative group schemes over finite fields.
 
@@
 %
-A quasicharacter sheaf $\qcs{L}$ on an etale commutative group scheme $G$ over $\Fq$ is:
+A quasicharacter sheaf $\qcs{L}$ on an étale commutative group scheme $G$ over $\Fq$ is:
 \begin{enumerate}
@@
 \begin{remark}
-Although we will only use the group homomorphism $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$.
+Although we will only use the group homomorphism $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an étale commutative group scheme, the function is defined for all smooth commutative group schemes $G$.
 However, the next result is false in that context.
@@
 
-\subsection{Objects, when $G$ is etale}\label{sec:SandT}
-
-In this section we find the relationship between the group homomorphisms $\TrFrob{G}$ and $S_G$, and use this to find the group $\QCiso{G}$ when $G$ is an etale commutative group scheme over $\Fq$.
+\subsection{Objects, when $G$ is étale}\label{sec:SandT}
+
+In this section we find the relationship between the group homomorphisms $\TrFrob{G}$ and $S_G$, and use this to find the group $\QCiso{G}$ when $G$ is an étale commutative group scheme over $\Fq$.
 
@@
 \begin{proposition}\label{prop:autornaught_etale}
-Let $G$ be an etale commutative group scheme over $\Fq$.
+Let $G$ be an étale commutative group scheme over $\Fq$.
 If $\qcs{L}$ and $\qcs{L}'$ are quasicharacter sheaves on $G$ then
@@
 
-%Note that Proposition~\ref{prop:autornaught_etale} tells us that if $G$ is an etale commutative group scheme over $\Fq$ then every hom-set is either trivial or $\{ 0 \} \cup \left(G(\bFq)_{\Weil{}}\right)^*$, non-canonically.
+%Note that Proposition~\ref{prop:autornaught_etale} tells us that if $G$ is an étale commutative group scheme over $\Fq$ then every hom-set is either trivial or $\{ 0 \} \cup \left(G(\bFq)_{\Weil{}}\right)^*$, non-canonically.
 
@@
 
-A finite, etale, surjective morphism $H\to G$ of smooth group schemes over $\Fq$ for which the action of $\Gal(\bFq/\Fq)$ on the kernel is trivial is called a {\it discrete isogeny}.
+A finite, étale, surjective morphism $H\to G$ of smooth group schemes over $\Fq$ for which the action of $\Gal(\bFq/\Fq)$ on the kernel is trivial is called a {\it discrete isogeny}.
 
@@
 We must show that comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
-To do this we use etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$. 
+To do this we use étale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$. 
 In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
@@
 From here, Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields \citelist{\cite{deligne:SGA4.5}*{Sommes trig.}, \cite{laumon:87a}*{1.1.3}}  gives us all we need, as we briefly recall.
-The key observation is that, by etale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
+The key observation is that, by étale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
 Using the equivalence given by $\Lang^*$, if $\Lang^*\qcs{E} = V$ with character $\psi$ and isomorphism $V\to V\otimes V$ then 
@@
 In particular, as we have already seen in Section~\ref{sec:etale}, for a given quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ there may be a different isomorphism $\mu' : \bm^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$ for which $\qcs{L}'=(\gqcs{L},\mu',\phi)$ is also a quasicharacter sheaf on $G$, not isomorphic to $\qcs{L}$ in $\QC(G)$.
-Indeed, Proposition~\ref{prop:etale-iso} shows that when $G$ is etale, $\Hh^2(\bG,\EEx)^{\Frob{}}$ measures the possibilities for $\mu'$.
+Indeed, Proposition~\ref{prop:etale-iso} shows that when $G$ is étale, $\Hh^2(\bG,\EEx)^{\Frob{}}$ measures the possibilities for $\mu'$.
 In other words, the common perspective on the function--sheaf dictionary leads only, and exactly, to the part of category of quasicharacter sheaves that is {\it completely invisible} to the trace of Frobenius!
@@
 \end{equation}
-Since $\pi_0(G)$ is a etale commutative group scheme -- and thus smooth --
+Since $\pi_0(G)$ is a étale commutative group scheme -- and thus smooth --
 Proposition~\ref{prop:pullback} implies that \eqref{eq:pi0} defines the sequence of functors

### 2014-08-22 dictionary.tex
Working on description of sections

--- 2014-08-22 dictionary.tex
@@
 \subjclass[2010]{14F05 (primary), 14L15 (secondary)}
-\keywords{function--sheaf dictionary, trace of Frobenius, geometrization, categorification, quasicharacters, quasicharacter sheaves, smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor}
+\keywords{function--sheaf dictionary, trace of Frobenius, geometrization, quasicharacters, quasicharacter sheaves, smooth commutative group schemes}
 
@@
 \usepackage{hyperref}
-\setcounter{section}{-1}
+
 %%%%%%%%%%%%%%% THEOREM STYLES %%%%%%%%%%%%%%%
@@
 
-\section{Introduction}
-
-Motivated by an application to the geometrization and categorification of quasicharacters of p-adic tori,
-this paper extends Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields to all smooth commutative group schemes over finite fields.
-
-As Deligne explained in \cite{deligne:SGA4.5}*{Sommes trig.}, if $G$ is a connected commutative algebraic group over $\FF_q$, then the trace of Frobenius provides a perfect dictionary between characters of $G(\FF_q)$ and isomorphism classes of rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which
+\section*{Introduction}
+
+%\subsection*{Overview}
+
+%Deligne's function--sheaf dictionary translates characters of connected, commutative algebraic groups $G$ over finite fields $\Fq$ into certain local systems on G, from which the character of $G(\Fq)$ can be recovered using the action of Frobenius on $G$.
+%The local systems which appear in this dictionary are easily characterised and often referred to as \emph{character sheaves} on $G$.
+%The result is a perfect dictionary between characters of $G(\Fq)$ and character sheaves on G, with which the formidable artillery of algebraic geometry can be brought to bear on the study of characters of $G(\Fq)$.
+%
+%In this paper we show how this dictionary extends to the case when $G$ is not connected, and even to all smooth commutative group schemes over $\Fq$, in which case some interesting new features of the dictionary arise.
+
+%\subsection{The main result}
+
+Let us briefly review how Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields \cite{deligne:SGA4.5}*{sommes trig.} translates characters into local systems.
+Let $\Fq$ be a finite field and let $G$ be a connected commutative algebraic group over $\Fq$; fix an algebraic closure $\bFq$ of $\Fq$
+and let $\bG$ be the base change of $G$ to $\bFq$.
+Fix a prime $\ell$ invertible in $\Fq$ and let $\chi : G(\Fq) \to \EEx$ be any character.
+Using little more than the Lang map for $G$, $\chi$ determines an $\ell$-adic local system $\qcs{L}$ on $G$ from which the character $\chi$ can be recovered using the Frobenius automorphism of $\bG$.
+While this recovery process applies to all $\ell$-adic local systems $\qcs{L}$ on $G$, those that produce characters of $G(\Fq)$ are distinguished by a simple property: there \emph{exists} an isomorphism
 \begin{equation}\label{introbox}
-m^* \qcs{E} \iso \qcs{E} \boxtimes \qcs{E},\tag{0}
+m^* \qcs{L} \iso \qcs{L} \boxtimes \qcs{L}
 \end{equation}
-where $m : G\times G\to G$ is the multiplication map.
+ of $\ell$-adic local systems on $G$, where $m : G\times G \to G$ is the multiplication map for $G$.
+The function--sheaf dictionary for $G$ identifies a monoidal category of $\ell$-adic local systems on $G$ such that the group of isomorphism classes in this category is canonically identified with the $\ell$-adic character group of $G(\Fq)$, thus providing the geometrization and categorification of characters of $G(\Fq)$.
 %
-If one wishes to make a category from this class of local systems, one is led to consider sheaf homorphisms $\qcs{E} \to \qcs{E}'$ which are compatible with particular choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E'}$.
-{\it A priori}, these sheaf homomorphisms do not form a category, but since $G$ is connected, the existence of \eqref{introbox} makes \eqref{introbox} unique; as a consequence, there is no impediment to categorifying the dictionary in this case.
-
-If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, however, then one must keep track of the choice of \eqref{introbox}, leading to a category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is an isomorphism of local systems on $G\times G$.
-As we show in this paper, if the component group scheme $\pi_0(G)$ (which is an étale commutative group scheme over $\FF_q$) is not cyclic, then while the trace of Frobenius provides a surjection from isomorphism classes in the category of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\FF_q)$, that group homomorphism need not be injective.
-In other words, if $G$ is a commutative algebraic group over $\FF_q$ which is not connected, then every character may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely. 
-While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not a serious defect since if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\FF_q)$, then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
-
-In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$ we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system, while retaining the extra structure $\mu_\qcs{E}$.
-In this way we are lead to the category $\QC(G)$ of quasicharacter sheaves on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} = G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way.
-Morphism in $\QC(G)$ are homomorphisms of Weil sheaves which are compatible with the extra structure.
-
-Étale group schemes form a counterpoint to connected algebraic groups,
-since the component group of a smooth commutative group scheme
-is an étale group scheme. 
-Accordingly, we first test the category of quasicharacter sheaves by examining its objects on etale commutative group schemes $G$ over $\FF_q$.
-Here again we find that the dictionary is imperfect: the trace of Frobenius provides a group epimorphism from isomorphism classes of quasicharacter sheaves on $G$ to characters of $G(\FF_q)$; the kernel of this epimorphism is naturally identified with $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$.
-Again, this imperfection should not be too troubling: if $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
-
-Returning to the case of connected commutative algebraic groups $G$ over $\FF_q$, we confirm that, in this case, the category of quasicharacter sheaves on $G$ is equivalent to the category of characters $\psi$ of $G(\FF_q)$, the equivalence being given by pullback by the Lang isogeny for $G$.
-%Indeed, one may show that isomorphism classes of quasicharacter sheaves on $G$ are determined by classes of extensions of $\bG$ by $\EEx$ which are fixed by Frobenius, given by $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$.
-%
-%The appearance of $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ and the trace of Frobenius gives an isomorphism $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\FF_q$, then $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ measures the kernel of $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$.
-%This observation makes plain the fact that w
-While characters of connected commutative algebraic groups $G$ can be geometrized using  local systems trivialized by discrete isogenies to $G$, this is not the right perspective if one wishes to geometrize characters of smooth commutative group schemes, such as etale commutative group schemes.
-Indeed, quasicharacter sheaves on etale commutative group schemes that are trivialized by discrete isogenies are invisible to the trace of Frobenius.
-
-Having understood quasicharacter sheaves on commutative smooth group schemes over $\FF_q$ in two extreme cases -- connected algebraic groups and etale commutative group schemes -- we turn to the general case.
-Remarkably, we find that the general case can be understood from these two extreme cases, using the component group sequence
-\[
-0 \to G^0 \to G \to \pi_0(G) \to 0.
-\]
-The main result of the paper uses this sequence to find $\QCiso{G}$ by situating it in a canonical short exact sequence
+Although hidden in this discussion, the connectedness of $G$ played a crucial role in the geometrization and categorification of characters of $G(\Fq)$.
+In particular, when the isomorphism \eqref{introbox} exists for $\qcs{L}$, it is essentially unique.
+
+Now let $G$ be any smooth commutative group scheme over $\Fq$.
+Two new features must be addressed in order to geometrize characters of $G(\Fq)$.
+First, we must pass from $\ell$-adic local systems on $G$ to Weil local systems on $G$
+and, second, we must keep track of the isomorphisms \eqref{introbox}.
+Both issues are addressed in the main definition of this paper:
+A \emph{quasicharacter sheaf} on $G$ is a triple $\qcs{L}\ceq
+(\gqcs{L},\mu,\phi)$ where $\gqcs{L}$ is an $\ell$-adic local system on $\bG$ of rank~one and $\mu: m^*
+\gqcs{L} \to \LxL$ and $\phi : \Frob{G}^*\gqcs{L} \to \gqcs{L}$ are isomorphisms satisfying natural compatibility conditions; here $\Frob{G}$ is the Frobenius automorphism of ${\bar G}$.
+ In the main result of this paper, Theorem~\ref{thm:snake},
+we form a rigid monoidal category $\lQC(G)$ of quasicharacter sheaves on $G$
+and show that the Trace of Frobenius provides a functorial group isomorphism
 \begin{equation}
-0 \to \Hh^2(\pi_0(\bG),\EEx)^{\Gal({\bar\FF}_q/\FF_q)} \to \QCiso{G} \to \Hom(G(\FF_q),\EEx) \to 0.
+\lQCiso{G} \to \Hom(G(\Fq), \EEx).
 \end{equation}
-We remark that $\Hh^2(\pi_0(\bG),\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ is non-trivial even for some commutative algebraic groups.
-We also illuminate the nature of the category $\QC(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing that 
-\begin{equation}
-\Aut(\qcs{L}) \iso \Hom(G(\bFq)_{\Gal(\bFq/\Fq)},\EEx),
-\end{equation}
-canonically, for all quasicharacter sheaves $\qcs{L}$ on $G$.
-
-\subsection{Applications over local fields}
-
-As indicated above, our interest in the function--sheaf dictionary for smooth commutative group schemes over finite fields comes from an application to $p$-adic representation theory.
-We found, however, that this application applies to all local fields $K$ with finite residue field $\Fq$ and all connected commutative algebraic groups $X_K$ over $K$ that do not contain a subgroup of type $\mathbb{G}_\text{a}$.
-Such algebraic groups $X_K$ always admit a Neron model $X$ over $R$, the ring of integers of $K$.
-In this paper we show that quasicharacters of $X_K$ are geometrized and categorified by quasicharacter sheaves on the
-Greenberg transform $\Gr_R(X)$ of the N\'eron model $X$; although not smooth, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and it is a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
-This allows us to adapt our work on quasicharacter sheaves to construct a category $\QC(\Gr_R(X))$ of quasicharacter sheaves on $\Gr(X)$.
-The ability to generalize the function--sheaf dictionary to non-connected group schemes, of which the component group of the special fibre of the Néron model $X$ is an important example, plays a crucial role in this application
+\todo{change to remove flabbyness}
+
+%\subsection*{Illustrative Examples}
+
+%Three examples will illustrate some of the issues that arise when extending the function--sheaf dictionary to smooth commutative group schemes over $\Fq$.
+As we show in the paper, $\ell$-adic local systems on $G$ can only be used to geometrize characters of finite order; quasicharacter sheaves, however, provide the geometrization of all characters of $G(\Fq)$.
+For example, we will see how to geometrize the character $\ZZ \to \EEx$ defined by
+$1 \mapsto \ell$, which has unbounded image,
+using quasicharacter sheaves on the etale group scheme $\ZZ$ with trivial Galois action.
+%Likewise, the dictionary is perfect for the etale group scheme $\ZZ$ with Galois action determined by $\Frob{}(n) = -n$.
+By contract, the etale group scheme $\ZZ \times \ZZ$ with trivial Galois action does admit invisible quasicharacter sheaves -- there are non-trivial quasicharacter sheaves on this group with trivial trace of Frobenius.\todo{Under construction} (Move this example: Define $g: \ZZ\times \ZZ \to \EEx$ by $g((n_1,m_1), (n_2, m_2)) = \ell^{m_1-m_2 + n_1-n_2}$.
+Then use the tehniques of Section~\ref{sec:etale} to build a non-trivial character sheaf from the pair $(f=1,g)$ with trivial trace of Frobenius.)
+
+%\subsection*{Motivation and Application}
+
+Our interest in the function--sheaf dictionary for smooth commutative group schemes over $\Fq$, especially etale commutative group schemes, comes from an application to $p$-adic representation theory.
+In \cite{cunningham-roe:13a} we consider quasicharacter sheaves on the
+Greenberg transform of the N\'eron model of an algebraic torus over an arbitrary local field.
+The ability to work with non-connected group schemes,
+of which the component group of the special fibre of the Néron model of a torus is an important example,
+plays a crucial role in this application,
 since these group schemes are not connected in general.
-
-Specializing to the case when $X_K$ is an algebraic tori $T$ over $K$, and writing $\underline{T}$ for the Neron model $X$ in this case, this paper gives a canonical short exact sequence 
-\begin{equation}
-0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Frob{}} \to \QCiso{\Gr_R(\underline{T})} \to \Hom_\text{qc}(T(K),\EEx) \to 0,
-\end{equation}
-where $\Hom_\text{qc}(T(K),\EEx)$ denoted the group of quasicharacters of $T(K)$.
-We further show that automorphism groups in the $\QC(\Gr_R(\underline{T}))$ are given, for every quasicharacter sheaf $\qcs{F}$ on $\Gr_R(X)$, by
-\begin{equation}
-\Aut(\qcs{F}) \iso (\check{T}_\ell)^{\Weil{K}}
-\end{equation}
-where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
-We also use quasicharacter sheaves to categorify the transfer of quasicharacters of tori between characteristic $0$ and characteristic $p$ local fields.
-
-Joseph Bernstein has suggested to us that, although quasicharacter sheaves on $\Gr(\underline{T})$ do not correspond exactly to quasicharacters of $T(K)$, the category $\QC(\Gr_R(\underline{T}))$ is the right one to consider.
-He has further suggested that the category $\QC(\Gr(\underline{T})$ may be more closely tied to characters of $T(K)$ and its pure rational forms in the sense of Vogan \cite{vogan:93a} or perhaps the rigid inner twists of Tasho Kaletha.
-A better understanding of 
-$\Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Frob{}}$ should provide insight into this suggestion.
-
-\subsection{Comparison with character sheaves}
-
-The process of creating a category from the group of quasicharacters of a $p$-adic  torus, as explained above, informs our choice of the term quasicharacter sheaf in this paper.
+This process of creating a category from the group of quasicharacters of such a torus
+informs our choice of the term quasicharacter sheaf, here.
+
+%\subsection*{Comparison with other character sheaves}
+
 We also want to situate our terminology in a historical context.
 It is not uncommon to refer to local systems satisfying \eqref{introbox} on a connected, commutative algebraic group as character sheaves;
-see for example, \cite{kamgarpour:09a}*{Intro}.
-As we have indicated, quasicharacter sheaves evolved from this notion,
+see for example, \cite{kamgarpour:09a}.
+As explained above, quasicharacter sheaves evolved from this notion,
 with an eye toward quasicharacters of $p$-adic groups.
@@
 beginning with \cite{lusztig:disconnected1}.
-When commutative, such groups are extensions of finite cyclic groups by algebraic tori,
+When commutative, such groups are extensions of $\ZZ/n\ZZ$ by a torus,
 in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
-The interesting new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ do not arise in this context.
-
-\subsection{Structure of the paper}
+The interesting new features pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Frob{G}}$ do not arise in this case.
+
+%\subsection*{Structure of the paper}
 \todo{Describe the overall structure of the paper in enough detail that one can follow the argument; include snake lemma diagram}
@@
   \end{equation}
-which is central to the proof of Theorem \ref{thm:snake}.  Much of Sections \ref{sec:etale}, \ref{sec:disc-isog} and \ref{sec:main}
+which is central to the proof of Theorem~\ref{thm:snake}.  Much of Sections~\ref{sec:etale}, \ref{sec:disc-isog} and \ref{sec:main}
 are devoted to proving that the rows of \eqref{eq:intro-snake} are exact and determining the kernels and cokernels of the vertical maps.
 
-Section~\ref{sec:etale} is devoted to the left-most vertical morphism in \eqref{eq:intro-snake}
+Section~\ref{sec:etale} is devoted to the left-most vertical morphism in \eqref{eq:intro-snake}: studying $\TrFrob{G}$ for $G$ \'etale.  We begin by giving a reinterpretation of
+$\QC(G)$ in this case using stalks.  After a brief review of the Hochschild-Serre spectral sequence in Section~\ref{ssec:E},
+we define in Section~\ref{ssec:S} an isomorphism $S_G$ from $\QCiso{G}$ to the second cohomology of the total space of the spectral sequence
+\[
+E_2^{p,q} \ceq \Hh^p(\Weil{}, \Hh^q(\bG, \EEx)) \Rightarrow \Hh^{p+q}(\Weil{} \ltimes \bG, \EEx).
+\]
+Paired with the short exact sequence
+\[
+  0 \to \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to \Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to 0
+\]
+arising from the spectral sequence, the isomorphism $S_G$ allows us to describe the kernel and cokernel of $\TrFrob{G}$ in Section \ref{ssec:SandT}.
+We close our discussion of \'etale $G$ with a description, in Section~\ref{ssec:mor-etale}, of $\Hom(\qcs{L},\qcs{L}')$ for $\qcs{L}, \qcs{L}' \in \QC(G)$.
+
+Section~\ref{sec:disc-isog} focuses on the right-hand side of \eqref{eq:intro-snake},
+giving descriptions of quasicharacter sheaves that are particularly useful when $G$ is connected.  In Section \ref{ssec:descentG}
+we consider quasicharacter sheaves that arise via base change to $\bFq$ from local systems on $G$, and in Section \ref{ssec:discrete_isogenies}
+those that arise via pushforward from a constant sheaf along a discrete isogeny $H \to G$.  When $G$ is connected,
+we show in Section~\ref{} that every quasicharacter sheaf can be described in both of these ways.  We also show that $\TrFrob{G}$ is an isomorphism
+in this case.
+
 In Section~\ref{sec:basechange} we study how quasicharacter sheaves behave under base change
 and Weil restriction.
-Sections~\ref{sec:descentG} and \ref{sec:finite} describe bounded quasicharacter sheaves and finite quasicharacter sheaves, respectively,
+Sections~\ref{ssec:descentG} and \ref{sec:finite} describe bounded quasicharacter sheaves and finite quasicharacter sheaves, respectively,
 forming two important subcategories of $\QC(G)$.
 %These subcategories play a key role in the proof of Proposition~\ref{prop:restriction}.
-In Section \ref{sec:connected} we show that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves when $G$ is connected, and that Trace of Frobenius is an isomorphism in this case.
+In Section \ref{ssec:connected} we show that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves when $G$ is connected, and that Trace of Frobenius is an isomorphism in this case.
 We shift to \'etale group schemes $G$ in Section~\ref{sec:etale} and find a cohomological interpretation
@@
 %\begin{acknowledgements}
-\subsection{Acknowledgments}
+\subsection*{Acknowledgments}
 We thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
@@
 Our main tool for understanding this phenomenon
-is a group homomorphism from $\QCiso{G}$ to $\Hh^2(E^\bullet_G)$, defined in Section~\ref{sec:S}, for which the next two sections are preparation.
-
-\subsection{A spectral sequence}\label{sec:E}
+is a group homomorphism from $\QCiso{G}$ to $\Hh^2(E^\bullet_G)$, defined in Section~\ref{ssec:S}, for which the next two sections are preparation.
+
+\subsection{A spectral sequence}\label{ssec:E}
 
@@
 
-\subsection{From quasicharacter sheaves to the total complex}\label{sec:S}
+\subsection{From quasicharacter sheaves to the total complex}\label{ssec:S}
 
@@
 
-\subsection{Objects, when $G$ is etale}\label{sec:SandT}
+\subsection{Objects, when $G$ is etale}\label{ssec:SandT}
 
@@
 
-\subsection{Morphisms}\label{sec:mor-etale}
+\subsection{Morphisms}\label{ssec:mor-etale}
 
@@
 
-Before turning our attention to quasicharacter sheaves on connected commutative algebraic groups in Section~\ref{sec:connected}, we treat two special classes of quasicharacter sheaves on arbitrary smooth commutative group schemes $G$:  in Section~\ref{sec:descentG}, those that descend from local systems on $\bG$ to local systems on $G$; and in Section~\ref{sec:discrete_isogenies}, those that are defined by discrete isogenies onto $G$.
-The latter will play a role in Sections~\ref{sec:connected} and \ref{sec:restriction}.
-
-\subsection{Descent to G}\label{sec:descentG}
+Before turning our attention to quasicharacter sheaves on connected commutative algebraic groups in Section~\ref{ssec:connected}, we treat two special classes of quasicharacter sheaves on arbitrary smooth commutative group schemes $G$:  in Section~\ref{ssec:descentG}, those that descend from local systems on $\bG$ to local systems on $G$; and in Section~\ref{ssec:discrete_isogenies}, those that are defined by discrete isogenies onto $G$.
+The latter will play a role in Sections~\ref{ssec:connected} and \ref{sec:restriction}.
+
+\subsection{Descent to G}\label{ssec:descentG}
 
@@
 
-\subsection{Discrete isogenies}\label{sec:discrete_isogenies}
+\subsection{Discrete isogenies}\label{ssec:discrete_isogenies}
 
@@
 In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
-Since $f$ is a morphism of group schemes, the functor $f^*$ defines $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ from the isomorphism $m^*\psi \iso \psi \boxtimes\psi$ determined by $V\to V\otimes V$.
+Since $f$ is a morphism of group schemes, the functor $f^*$ defines $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$
+from the isomorphism $m^*\psi \iso \psi \boxtimes\psi$ determined by $V\to V\otimes V$.
 \end{proof}
@@
 
-\subsection{Quasicharacter sheaves on connected commutative algebraic groups}\label{sec:connected}
+\subsection{Quasicharacter sheaves on connected commutative algebraic groups}\label{ssec:connected}
 
@@
   the latter appearing in the definition of $\qcs{L}$.
-  Then, as in Section~\ref{sec:descentG}, $(\qcs{E},\mu_\qcs{E})$ is an object in $\bQC(G)$
+  Then, as in Section~\ref{ssec:descentG}, $(\qcs{E},\mu_\qcs{E})$ is an object in $\bQC(G)$
   and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{E},b_{G\times G}^*\mu_\qcs{E})$ in $\QC(G)$.
-  Thus, the full and faithful functor $B_G : \bQC(G) \to \QC(G)$ from Section~\ref{sec:descentG}
+  Thus, the full and faithful functor $B_G : \bQC(G) \to \QC(G)$ from Section~\ref{ssec:descentG}
   is also essentially surjective, hence an equivalence.
@@
 We have also just seen that if the character of $\Lang^*\qcs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\qcs{E} : \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ which is part of the data that determines a quasicharacter sheaf on $G$.
-That leads to a perspective on the function--sheaf dictionary common in the literature in which one considers $1$-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$; see \cite{kamgarpour:09a}*{Intro}, for example.
+That leads to a perspective on the function--sheaf dictionary common in the literature in which one considers $1$-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$; see \cite{kamgarpour:09a}*{Introduction}, for example.
 As a slight variation, one may also consider $1$-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
-%One may show that all such $\gqcs{L}$ are determined by extensions of $\bG$ by $\EEx$ which are fixed by Frobenius and that the trace of Frobenius provides a canonical isomorphism from $\Hh^2(\bG,\EEx)^{\Frob{}}$ to $G(\Fq)^*$; {\it cf.\ }
-%One may show that all such $\gqcs{L}$ are determined by extensions of $\bG$ by $\EEx$ which are fixed by Frobenius and that the trace of Frobenius provides a canonical isomorphism from $\Hh^2(\bG,\EEx)^{\Frob{}}$ to $G(\Fq)^*$; {\it cf.\ } \cite{kamgarpour:09a}*{Prop 2.15}.
+One may show that all such $\gqcs{L}$ are determined by extensions of $\bG$ by $\EEx$ which are fixed by Frobenius and that the trace of Frobenius provides a canonical isomorphism from $\Hh^2(\bG,\EEx)^{\Frob{}}$ to $G(\Fq)^*$; {\it cf.\ }\cite{kamgarpour:09a}*{Prop 2.15}.
+%
 
@@
  Note that we found the groups $\QCiso{\pi_0(G)}$ and $\QCiso{G^0}$
-in Sections~\ref{sec:SandT} and \ref{sec:connected}, respectively.
+in Sections~\ref{ssec:SandT} and \ref{ssec:connected}, respectively.
 We will shortly see that \eqref{eq:pi2} is exact.
@@
 
-We now wish to use the apply the results of Section~\ref{sec:connected} to the identity component of $G$; to do so, we must know that the identity component of $G$ is actually an algebraic group over $\Fq$.
+We now wish to use the apply the results of Section~\ref{ssec:connected} to the identity component of $G$; to do so, we must know that the identity component of $G$ is actually an algebraic group over $\Fq$.
 
@@
 
+\todo{Comment, in the introduction, that $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$ is trivial if $\pi_0({\bar G})$ is finite cyclic. Lusztig.}
+
 \subsection{Morphisms of quasicharacters}
@@
 every $\rho \in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism.
-Moreover, 
-\[
-\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx),
-\]
- canonically.
+Moreover, $\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$, canonically.
 \end{theorem}
@@
 \begin{definition}
-Let $X_K$ be a connected commutative group scheme that admits a Neron model, $X$.
 A {\it quasicharacter sheaf on $\Gr_R(X)$} is an object $\qcs{F}$ in $\mathcal{C}(\Gr_R(X))$ such that $\qcs{F} \iso P^R_n(X)^*\qcs{L}$ for some quasicharacter sheaf $\qcs{L}$ on $\Gr^R_n(X)$.
@@
 \[
-\Aut(\qcs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx),
+\Aut(\qcs{F}) \iso \Hom((\pi_0(X)_{\Fq})_{\Weil{}},\EEx),
 \]
@@
 \[
-\Aut(\qcs{L}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx),
+\Aut(\qcs{L}) \iso \Hom((\pi_0(X)_{\Fq})_{\Weil{}},\EEx),
 \]
@@
 \end{proof}
-
-\subsection{Quasicharacters of $p$-adic tori}
-
-As we explained in the Introduction, our original motivation for this paper was to find a geometrization and categorification of quasicharacters of $p$-adic tori.
-This is is now provided by specializing Theorem~\ref{thm:QCXK} to the case when $X_K= T\in \mathcal{N}_K$ is an algebraic torus over $K$, in which case we write $\underline{T}$ for the Neron model $X$.
-Now,
-\[
- \pi_0(\underline{T})_{\bFq} = X_*(T)_{\mathcal{I}_K},
-\]
-where $X_*(T)$ is the cocharacter lattice of $T$ and $\mathcal{I}_K$ is the inertia group for $K$ \cite{bitan:discriminant}*{Eq 3.1}. 
-Accordingly, the short exact sequence in Theorem~\ref{thm:QCXK} becomes
-\begin{equation}
-0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Frob{}} \to \QCiso{\Gr_R(\underline{T})} \to \Hom_\text{qc}(T(K),\EEx) \to 0.
-\end{equation}
-Again by Theorem~\ref{thm:QCXK}, the automorphism groups in the $\QC(\Gr_R(\underline{T}))$ are given, for every quasicharacter sheaf $\qcs{F}$ on $\Gr_R(X)$, by
-\begin{equation}
-\Aut(\qcs{F}) \iso \Hom(X_*(T)_{\Weil{K}},\EEx) = \Hom(X_*(T),\EEx)^{\Weil{K}} = (X^*(T)\otimes \EEx)^{\Weil{K}} = (\check{T}_\ell)^{\Weil{K}}
-\end{equation}
-where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
 
@@
 \[
-\Hom_{\text{qc}}(X_K(K'),\EEx) \to \Hom_{\text{qc}}(X_K(K),\EEx).
+\Hom_{\text{qc}}(T(K'),\EEx) \to \Hom_{\text{qc}}(T(K),\EEx).
 \]
@@
 
+\section{Notes for the new Introduction}
+
+Motivated by an application to the geometrization and categorification of quasicharacters of p-adic tori,
+this paper extends Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields to all smooth commutative group schemes over finite fields.
+
+As Deligne explained in \cite{deligne:SGA4.5}*{sommes trig.}, if $G$ is a connected commutative algebraic group over $\FF_q$, then the trace of Frobenius provides a perfect dictionary between characters of $G(\FF_q)$ and isomorphism classes of rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which
+\begin{equation}\label{introbox}
+m^* \qcs{E} \iso \qcs{E} \boxtimes \qcs{E},\tag{0}
+\end{equation}
+where $m : G\times G\to G$ is the multiplication map.
+%
+If one wishes to make a category from this class of local systems, one is led to consider sheaf morphisms $\qcs{E} \to \qcs{E}'$ which are compatible with particular choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E'}$.
+{\it A priori}, these sheaf morphisms do not form a category, but since $G$ is connected, the existence of \eqref{introbox} makes \eqref{introbox} unique; as a consequence, there is no impediment to categorifying the dictionary in this case.
+
+If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, however, then one must keep track of the choice of \eqref{introbox}, leading to a category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is an isomorphism of local systems on $G\times G$.
+As we show in this paper, if the component group scheme $\pi_0(G)$ (which is an étale commutative group scheme over $\FF_q$) is not cyclic, then while the trace of Frobenius provides a surjection from isomorphism classes in the category of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\FF_q)$, that group homomorphism need not be injective.
+In other words, if $G$ is a commutative algebraic group over $\FF_q$ which is not connected, then every character may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely.
+While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious since, as we show in the paper, if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\FF_q)$, then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
+
+In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$ we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system.
+In this way we are lead to the category of quasicharacter sheaves on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} = G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way.
+
+Étale group schemes form a counterpoint to connected algebraic groups,
+since the component group of a smooth commutative group scheme
+is an étale group scheme. 
+Accordingly, we first test the category of quasicharacter sheaves by examining its objects on etale commutative group schemes $G$ over $\FF_q$.
+Here again we find that the dictionary is imperfect: the trace of Frobenius provides a group epimorphism from isomorphism classes of quasicharacter sheaves on $G$ to characters of $G(\FF_q)$; the kernel of this epimorphism is $\Hh^2(\bG,\EEx)^{\Frob{}}$.
+Again, this imperfection should not be too troubling: if $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
+
+Returning to the case of connected commutative algebraic groups $G$ over $\Fq$, we confirm that, in this case, the category of quasicharacter sheaves on $G$ is equivalent to the category of characters $\psi$ of $G(\Fq)$, the equivalence being given by pullback by the Lang isogeny for $G$.
+Indeed, one may show that isomorphism classes of quasicharacter sheaves on $G$ are determined by classes of extensions of $\bG$ by $\EEx$ which are fixed by Frobenius, and therefore given by $\Hh^2(\bG,\EEx)^{\Frob{}}$ to $G(\Fq)^*$.
+
+Although the category of quasicharacter sheaves on $G$ does specialize to that common notion when $G$ is connected and of finite type, the common notion is not appropriate if one wishes to extend the dictionary to smooth commutative group schemes over finite fields.
+In particular, as we have already seen in Section~\ref{sec:etale}, for a given quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ there may be a different isomorphism $\mu' : \bm^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$ for which $\qcs{L}'=(\gqcs{L},\mu',\phi)$ is also a quasicharacter sheaf on $G$, not isomorphic to $\qcs{L}$ in $\QC(G)$.
+Indeed, Proposition~\ref{prop:etale-iso} shows that when $G$ is etale, $\Hh^2(\bG,\EEx)^{\Frob{}}$ measures the possibilities for $\mu'$.
+In other words, the common perspective on the function--sheaf dictionary leads only, and exactly, to the part of category of quasicharacter sheaves that is {\it completely invisible} to the trace of Frobenius!
+
+We will see in Section~\ref{sec:main} that, for any smooth commutative group scheme $G$, the part of category of quasicharacter sheaves that is invisible to the trace of Frobenius are measured by $\Hh^2(\pi_0(\bG),\EEx)^{\Frob{}}$.
+%\end{remark}
+
 \bibliographystyle{amsalpha}

### 2014-08-22 dictionary.tex

--- 2014-08-22 dictionary.tex
@@
 Returning to the case of connected commutative algebraic groups $G$ over $\FF_q$, we confirm that, in this case, the category of quasicharacter sheaves on $G$ is equivalent to the category of characters $\psi$ of $G(\FF_q)$, the equivalence being given by pullback by the Lang isogeny for $G$.
-%Indeed, one may show that isomorphism classes of quasicharacter sheaves on $G$ are determined by classes of extensions of $\bG$ by $\EEx$ which are fixed by Frobenius, given by $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$.
 %
-%The appearance of $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ and the trace of Frobenius gives an isomorphism $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$; on the other hand, if $G$ an étale commutative group scheme over $\FF_q$, then $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ measures the kernel of $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$.
-%This observation makes plain the fact that w
-
+%The appearance of $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ and the trace of Frobenius gives an isomorphism $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\FF_q$, then $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ measures the kernel of $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$.
+%This observation makes plain the fact that  . . .
+%
 As we show in the paper, while characters of connected commutative algebraic groups $G$ can be geometrized using  local systems trivialized by discrete isogenies to $G$, this is not the right perspective if one wishes to geometrize characters of smooth commutative group schemes, such as étale commutative group schemes.
@@
 
-\subsection{Objects, when $G$ is étale}\label{sec:SandT}
+\subsection{Objects, when $G$ is etale}\label{ssec:SandT}
 

### 2014-08-22 dictionary.tex
Minor edits to Introduction and Applications.

@@
 In other words, if $G$ is a commutative algebraic group over $\FF_q$ which is not connected, then every character may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely. 
-While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not a serious defect since if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\FF_q)$, then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
+While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious since if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\FF_q)$ then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
 
@@
 One can show, using the Kunneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
-The fact that $T_G$ is not an isomorohism should not be too troubling because if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
-
-Returning to the case of connected commutative algebraic groups $G$ over $\FF_q$, we confirm that, in this case, the category of quasicharacter sheaves on $G$ is equivalent to the category of characters $\psi$ of $G(\FF_q)$, the equivalence being given by pullback by the Lang isogeny for $G$.
+The fact that $T_G$ is not an isomorphism should not be too troubling because if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
+Here we also see the importance of working with Weil sheaves: without them, we would not be able to geometrize the character of the étale group scheme $\ZZ$ over $\FF_q$ given by $1\mapsto \ell$, for example.
+
+Returning to the case of connected commutative algebraic groups $G$ over $\FF_q$, we confirm that, in this case, $\QC(G)$ is equivalent to the category of characters $\psi$ of $G(\FF_q)$, the equivalence being given by descent to $G$ followed by pullback by the Lang isogeny for $G$.
 %
@@
 
-Joseph Bernstein has suggested to us that, although quasicharacter sheaves on $\Gr(\underline{T})$ do not correspond exactly to quasicharacters of $T(K)$, the category $\QC(\Gr_R(\underline{T}))$ is the right one to consider and that the category $\QC(\Gr(\underline{T})$ may be closely tied to characters of  the pure rational forms of $T$ in the sense of Vogan \cite{vogan:93a} or perhaps the rigid inner twists of Tasho Kaletha.
+Joseph Bernstein has suggested to us that, although quasicharacter sheaves on $\Gr(\underline{T})$ do not correspond exactly to quasicharacters of $T(K)$, the category $\QC(\Gr_R(\underline{T}))$ is the right one to consider and that $\QC(\Gr(\underline{T})$ may be closely tied to characters of  the pure rational forms of $T$ in the sense of Vogan \cite{vogan:93a} or perhaps the rigid inner twists of Tasho Kaletha.
 A better understanding of 
@@
 A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) \to X(R_n)$, for some non-negative integer $n$;
-the group of quasicharacters of $X_K(K)$ will be denoted by $\Hom_\text{qc}(X_K(K),\EEx)$ and the subgroup of those that factor through $X(R_n)$ will be denoted by $\Hom_n(X_K(K),\EEx)$.
-%
+the group of quasicharacters of $X_K(K)$ will be denoted by 
+\[
+\Hom_\text{qc}(X_K(K),\EEx)
+\]
+ and the subgroup of those that factor through $X(R_n)$ will be denoted by 
+ \[
+ \Hom_n(X_K(K),\EEx).
+\]
 In this section we explain how to geometrize and categorify quasicharacters of $X_K(K)$ using quasicharacter sheaves.

### 2014-08-22 dictionary.tex
Going to lunch. Back soon  . . .

@@
 In this paper we show that quasicharacters of $X_K$ are geometrized and categorified by quasicharacter sheaves on the
-Greenberg transform $\Gr_R(X)$ of the N\'eron model $X$; although not smooth, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and it is a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
+Greenberg transform $\Gr_R(X)$ of the N\'eron model $X$; although not locally of finite type, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and also a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
 This allows us to adapt our work on quasicharacter sheaves to construct a category $\QC(\Gr_R(X))$ of quasicharacter sheaves on $\Gr(X)$.
@@
 \subsection{Structure of the paper}
-\todo{Describe the overall structure of the paper in enough detail that one can follow the argument; include snake lemma diagram}
 
@@
 in Section~\ref{sec:category} we define the category of quasicharacter sheaves.
-Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism $\TrFrob{G} : \QCiso{G} \to \Hom(G(k), \EEx)$.
+Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism $\TrFrob{G} : \QCiso{G} \to \Hom(G(\FF_q), \EEx)$.
 We also define pullbacks of quasicharacter sheaves along morphisms of group schemes.  Applying pullbacks to the component group
@@
     & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
-    0 \rar & \pi_0(G)(\Fq)^* \rar & G(\Fq)^* \rar & G^0(\Fq)^* \rar & 0,\\
+    0 \rar & \pi_0(G)(\FF_q)^* \rar & G(\Fq)^* \rar & G^0(\FF_q)^* \rar & 0,
   \end{tikzcd}
@@
 
-\todo{Comments about Joseph Bernstein's comments?}
-
 %\begin{acknowledgements}
@@
 \begin{enumerate}
-\labitem{(QC.1)}{QC.1} $\gqcs{L}$ is a rank~one $\ell$-adic local system on $\bG$, by which we mean
+\labitem{(QC.1)}{QC.1} $\gqcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean
 a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected
@@
 \begin{proof}
-  Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We start by showing that
-  $\bf^*\gqcs{L}$ is a local system of rank~one. Let $c_j :\bH^j \hookrightarrow \bH$ be any
-  connected component and let $d_i : \bG^i \hookrightarrow \bG$ be the image of $j$ under the group
-  homomorphism $\pi_0(\bf) : \pi_0(\bH) \to \pi_0(\bG)$.  Write $\bf^j : \bH^j \to \bG^i$
-  for the restriction of $f$ to $\bH^j$.  Since $\gqcs{L}$ is locally constant on the connected
-  components of $\bG$, there is a finite \'etale covering
-  $a_i : X_i \to \bG^i$ such that $a_i^* (\gqcs{L}\vert_{\bG^i})$
-  is constant.  Define $Y_j$ in the following diagram through pullback:
-  \[
-  \begin{tikzcd}[row sep=20, column sep=30]
-   Y_j \dar[dashed]{g_j} \rar[dashed]{b_j} & \bH^j \dar{\bf^j} \rar[hook]{c_j} & \bH \dar{\bf} \\
-   X_i \rar{a_i} & \bG^i \rar[hook]{d_i} & \bG
-  \end{tikzcd}
-  \]
-  Then $b_j$ is a finite \'etale covering
-  of $\bH^j$ and
-  \[
-  b_j^* \left( (\bf^* \gqcs{L})\vert_{\bH^j}\right)
-  = (\bf\circ c_j \circ b_j)^*\gqcs{L}
-  = (d_i\circ a_i\circ g_j)^*\gqcs{L} = g_j^* a_i^* (\gqcs{L}\vert_{\bG^i}).
-  \]
-  Since $a_i^* (\gqcs{L}\vert_{\bG^i})$ is a constant sheaf, its pullback
-  $b_j^* \left( (\bf^*\gqcs{L})\vert_{\bH^j}\right)$ along $g_j$ is also constant.
-  Thus $\bf^*\gqcs{L}$ is locally constant on
-  $\bH^j$. To complete the proof that $\bf^*\gqcs{L}$ satisfies
-  \ref{QC.1}
-  simply observe that $\bf^*\gqcs{L}$ has rank~one since
-  $(\bf^*\gqcs{L})_{\bg} = \gqcs{L}_{f(\bg)}$, for every geometric point ${\bg}$ on $\bG$.
-
+  Let $\qcs{L}$ be a quasicharacter sheaf on $G$. It is clear \todo{Reference} that
+  $\bf^*\gqcs{L}$ is a local system of rank~one, so  \ref{QC.1}  is satisfied.
   To see that $(\bfxf)^* \mu$ satisfies \ref{QC.2},
@@
   $f^* : \QC(G) \to \QC(H)$ is a monoidal functor.
-  The diagram relating $f^* : \QC(G) \to \QC(H)$, $f^* : G(k)^* \to H(k)^*$ and Trace of Frobenius
+  The diagram relating $f^* : \QC(G) \to \QC(H)$, $f^* : G(k)^* \to H(k)^*$ and trace of Frobenius
   commutes by \cite{laumon:87a}*{1.1.1.2}, where the ambient
@@
 If $\rho_0 = 0$ then the second diagram in \ref{qc.4} for $y=0$ implies that $\rho_x = 0$ for all $x\in G$, in which case $\rho$ is trivial.
-On the other hand, if $\rho_0$ is nonzero then the second diagram in \ref{qc.4} for $y = -x$ implies that $\rho_x$ is nonzero for all $x$ and thus an isomorphism since the stalk of quasicharacter sheaves are one dimensional; in this case $\rho$ is an isomorphism.
+On the other hand, if $\rho_0$ is nonzero then the second diagram in \ref{qc.4} for $y = -x$ implies that $\rho_x$ is nonzero for all $x$ and thus an isomorphism since the stalk of quasicharacter sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
 

### 2014-08-22 dictionary.tex
Changes to the first half of the Introduction.

@@
 Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
-this paper extends Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields to all smooth commutative group schemes over finite fields.
+this paper extends Deligne's function--sheaf dictionary for characters of connected commutative algebraic groups over finite fields to characters of smooth commutative group schemes over finite fields.
+
+\subsection{Overview}
 
@@
 
-In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$ we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system, while retaining the extra structure $\mu_\qcs{E}$.
-In this way we are lead to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} = G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way.
+In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$ we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system  -- a local system on ${\bar G} := G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ -- while retaining the extra structure $\mu_\qcs{E}$.
+Let $\Weil{} \subset \Gal({\bar\FF}_q/\FF_q)$ be the Weil group for $\FF_q$; let $\Frob{G} : \bG \to \bG$ be the Frobenius automorphism for $\bG$.
+In this way we are lead to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way.
 Morphism in $\QC(G)$ are then homomorphisms of Weil sheaves which are compatible with the extra structure.
@@
 \end{equation}
-provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$, canonically.
+provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$, canonically.
 One can show, using the Kunneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
 The fact that $T_G$ is not an isomorphism should not be too troubling because if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
-Here we also see the importance of working with Weil sheaves: without them, we would not be able to geometrize the character of the étale group scheme $\ZZ$ over $\FF_q$ given by $1\mapsto \ell$, for example.
+Here we also see the importance of working with Weil sheaves; for example, without them, we would not be able to geometrize the character of the étale group scheme $\ZZ$ over $\FF_q$ given by $1\mapsto \ell$, for example.
 
@@
 \begin{equation}
-0 \to \Hh^2(\pi_0(\bG),\EEx)^{\Gal({\bar\FF}_q/\FF_q)} \to \QCiso{G} \to \Hom(G(\FF_q),\EEx) \to 0.
-\end{equation}
-We remark that $\Hh^2(\pi_0(\bG),\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ is non-trivial even for some commutative algebraic groups.
+0 \to \Hh^2(\pi_0(\bG),\EEx)^{\Weil{}} \to \QCiso{G} \to \Hom(G(\FF_q),\EEx) \to 0.
+\end{equation}
+We remark that $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ is non-trivial even for some commutative algebraic groups.
 We also illuminate the nature of the category $\QC(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing that 
 \begin{equation}
-\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Gal(\bFq/\Fq)},\EEx),
+\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx),
 \end{equation}
@@
 \begin{equation}
-0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Frob{}} \to \QCiso{\Gr_R(\underline{T})} \to \Hom_\text{qc}(T(K),\EEx) \to 0,
+0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{\Gr_R(\underline{T})} \to \Hom_\text{qc}(T(K),\EEx) \to 0,
 \end{equation}
@@
 A better understanding of 
-$\Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Frob{}}$ should provide insight into this suggestion.
+$\Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}}$ should provide insight into this suggestion.
 
@@
 in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
-The interesting new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ do not arise in this context.
+The interesting new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in this context.
 
@@
 quasicharacter sheaves; their knowledge and help have been invaluable.
-We also thank Takashi Suzuki, who made some enormously helpful observations and suggestions.
+We also thank Takashi Suzuki, who made some very helpful observations and suggestions.
 %
@@
 \begin{enumerate}
-\labitem{(QC.1)}{QC.1} $\gqcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean
-a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected
-component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
+\labitem{(QC.1)}{QC.1} $\gqcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean a constructible $\ell$-adic sheaf on $\bG$, {\it lisse} on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
 \labitem{(QC.2)}{QC.2} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of
@@
 \begin{proof}
-  Let $\qcs{L}$ be a quasicharacter sheaf on $G$. It is clear \todo{Reference} that
-  $\bf^*\gqcs{L}$ is a local system of rank~one, so  \ref{QC.1}  is satisfied.
+  Let $\qcs{L}$ be a quasicharacter sheaf on $G$. 
+  Pullback by $\bf$ takes rank~one local systems to rank~one local systems.
   To see that $(\bfxf)^* \mu$ satisfies \ref{QC.2},
@@
 It is a matter of routine to show that this morphism satisfies
-\ref{qc.3} as it applies here,
+\ref{QC.3} as it applies here,
 from which it follows that we have exhibited an isomorphism
@@
 
-In this section we find a complete characterization of quasicharacter sheaves on étale commutative group schemes over finite fields.
+In this section we find a complete characterization of the category of quasicharacter sheaves on étale commutative group schemes over finite fields.
+
+\subsection{Stalks of quasicharacter sheaves}
 
@@
 
-We will see that the Trace of Frobenius may not provide complete
+We will see that $T_G : \QCiso{G} \to G(\Fq)^*$ may not provide complete
 information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not a connected algebraic group.
 Our main tool for understanding this phenomenon
-is a group homomorphism from $\QCiso{G}$ to $\Hh^2(E^\bullet_G)$, defined in Section~\ref{ssec:S}, for which the next two sections are preparation.
+is a group homomorphism $S_G: \QCiso{G} \to \Hh^2(E^\bullet_G)$ defined in Section~\ref{ssec:S}, for which the next two sections are preparation.
 

### 2014-08-22 dictionary.tex
Commit to go home. . .

@@
 
-Let $G$ be a commutative group scheme over $\Fq$.
-Consider the category $\mathcal{C}(G)$ of triples
-$\qcs{F}\ceq (\gqcs{F},\mu_\qcs{F},\phi_\qcs{F})$ where
-\begin{enumerate}
-\labitem{(C.0)}{C.0} $\gqcs{F}$ is a rank one $\ell$-adic local system on $\bG\ceq G \times_\Spec{\Fq} \Spec{\bFq}$,
-\labitem{(C.1)}{C.1} $\mu_\qcs{F}: \bm^* \gqcs{F} \to \gqcs{F}\boxtimes\gqcs{F}$ is an isomorphism $\ell$-adic sheaves, where $\bm : \bG \times \bG \to \bG$ is multiplication $m$ for $G$ extended to $\bG$.
-\labitem{(C.2)}{C.2} $\phi_\qcs{F} : \Frob{G}^* \gqcs{F} \to \gqcs{F}$ is an isomorphism of constructible $\ell$-adic sheaves, where $\Frob{G}^* : \bG  \to \bG$ is the Frobenius automorphism,
-\end{enumerate}
-subject to the conditions as in \ref{QC.1} and \ref{QC.2},
-with morphisms defined as in \ref{QC.3}.
-This category $\mathcal{C}(G)$ is rigid monoidal, with tensor product defined as in Definition~\ref{def:QC}. %Note that $\mathcal{C}(G) = \QC(G)$ if $G$ is also smooth.
+Let $X_K \in \mathcal{N}_K$ and $X$ be as above.
+Although $\Gr_R(X)$ is not locally of finite type, and thus not smooth, let us write $\QC(\Gr_R(X))$ for the rigid monoidal category defined as in Section~\ref{sec:category}, without insisting that the commutative group scheme $G$ is smooth.
 
@@
 \[
-P^R_n(X)^* : \QC(\Gr^R_n(X)) \to \mathcal{C}(\Gr_R(X)),
+P^R_n(X)^* : \QC(\Gr^R_n(X)) \to \QC(\Gr_R(X)),
 \]
 as in Proposition~\ref{prop:pullback}.
-This functor is full and faithful, so we may view $\QC(\Gr^R_n(X))$ as a full subcategory of $\mathcal{C}(\Gr_R(X))$.
+This functor is full and faithful, so we may view $\QC(\Gr^R_n(X))$ as a full subcategory of $\QC(\Gr_R(X))$.
 
@@
 Let $X_K$ be a connected commutative group scheme that admits a Neron model, $X$.
-A {\it quasicharacter sheaf on $\Gr_R(X)$} is an object $\qcs{F}$ in $\mathcal{C}(\Gr_R(X))$ such that $\qcs{F} \iso P^R_n(X)^*\qcs{L}$ for some quasicharacter sheaf $\qcs{L}$ on $\Gr^R_n(X)$.
-Quasicharacter sheaves on $\Gr_R(X)$ form a rigid monoidal category in the obvious way, denoted by $\QC(\Gr_R(X))$.
+A {\it quasicharacter sheaf for $X_K$} is an object $\qcs{F}$ in $\QC(\Gr_R(X))$ such that $\qcs{F} \iso P^R_n(X)^*\qcs{L}$ for some $\qcs{L} \in \QC(\Gr^R_n(X))$.
+Quasicharacter sheaves for $X_K$ form a rigid monoidal category in the obvious way, denoted by $\QC(X_K)$.
 \end{definition}
@@
 \[
-F_{\QC}: X_K \mapsto \QCiso{\Gr_R(X)}
+F_{\QC}: X_K \mapsto \QCiso{X_K}
 \qquad\text{and}\qquad
@@
 \[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{\Gr_R(X)} \to \Hom_\text{qc}(X_K(K),\EEx) \to 0;
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{X_K} \to \Hom_\text{qc}(X_K(K),\EEx) \to 0;
 \] 

### 2014-08-22 dictionary.tex
More work on summary of sections

--- 2014-08-22 dictionary.tex
@@
 In this paper we show that quasicharacters of $X_K$ are geometrized and categorified by quasicharacter sheaves on the
-Greenberg transform $\Gr_R(X)$ of the N\'eron model $X$; although not locally of finite type, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and also a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
+Greenberg transform $\Gr_R(X)$ of the N\'eron model $X$; although not smooth, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and it is a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
 This allows us to adapt our work on quasicharacter sheaves to construct a category $\QC(\Gr_R(X))$ of quasicharacter sheaves on $\Gr(X)$.
@@
 \subsection{Structure of the paper}
+\todo{Describe the overall structure of the paper in enough detail that one can follow the argument; include snake lemma diagram}
 
@@
 in Section~\ref{sec:category} we define the category of quasicharacter sheaves.
-Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism $\TrFrob{G} : \QCiso{G} \to \Hom(G(\FF_q), \EEx)$.
+Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism $\TrFrob{G} : \QCiso{G} \to \Hom(G(k), \EEx)$.
 We also define pullbacks of quasicharacter sheaves along morphisms of group schemes.  Applying pullbacks to the component group
@@
     & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
-    0 \rar & \pi_0(G)(\FF_q)^* \rar & G(\Fq)^* \rar & G^0(\FF_q)^* \rar & 0,
+    0 \rar & \pi_0(G)(\Fq)^* \rar & G(\Fq)^* \rar & G^0(\Fq)^* \rar & 0,\\
   \end{tikzcd}
@@
 those that arise via pushforward from a constant sheaf along a discrete isogeny $H \to G$.  When $G$ is connected,
-we show in Section~\ref{} that every quasicharacter sheaf can be described in both of these ways.  We also show that $\TrFrob{G}$ is an isomorphism
-in this case.
-
-In Section~\ref{sec:basechange} we study how quasicharacter sheaves behave under base change
-and Weil restriction.
-Sections~\ref{ssec:descentG} and \ref{sec:finite} describe bounded quasicharacter sheaves and finite quasicharacter sheaves, respectively,
-forming two important subcategories of $\QC(G)$.
-%These subcategories play a key role in the proof of Proposition~\ref{prop:restriction}.
-In Section \ref{ssec:connected} we show that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves when $G$ is connected, and that Trace of Frobenius is an isomorphism in this case.
-We shift to \'etale group schemes $G$ in Section~\ref{sec:etale} and find a cohomological interpretation
-of quasicharacter sheaves in this case.
-In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
-induces an essentially surjective functor of quasicharacter sheaves.
-%Section~\ref{sec:snake} presents the main theorem of this paper: Trace of Frobenius
-%is a functorial isomorphism from isomorphism classes of flabby quasicharacter sheaves on $G$
-%to characters of $G(\Fq)$.
+we show in Section~\ref{ssec:connected} that every quasicharacter sheaf can be described in both of these ways.
+We also show that $\TrFrob{G}$ is an isomorphism in this case.
+
+In Section~\ref{sec:main} we prove that the rows of \eqref{eq:intro-snake} are exact and
+use the snake lemma to determine the kernel and cokernel of $\TrFrob{G}$ for general $G$.
+We show that $\QCiso{G^0} \to \QCiso{G}$ is surjective in Section~\ref{ssec:restriction} and
+that the remainder of the top row of \eqref{eq:intro-snake} is exact in Section~\ref{ssec:component}.
+We put it together in Theorem~\ref{thm:snake} of Section~\ref{ssec:snake}, showing that $\TrFrob{G}$
+is surjective with kernel $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$.  Having described the isomorphism classes of objects,
+in Theorem~\ref{thm:autornaught} of Section~\ref{ssec:qcmor} we show that
+\[
+\Aut(\qcs{L}) \cong \Hom(\pi_0(\bG)_{\Weil{}}, \EEx)
+\]
+and that every morphism is either trivial or an isomorphism.  We conclude in Section~\ref{sec:basechange} by
+giving functorial versions of the restriction and norm homomorphisms $G(k')^* \to G(k)^*$ and $G(k)^* \to G(k')^*$
+and describing how quasicharacter sheaves behave under Weil restriction.
+
+Section~\ref{sec:applications} gives applications of quasicharacter sheaves to commutative algebraic groups over local fields.
+We begin with a review of N\'eron models and of the Greenberg transform in Section~\ref{ssec:rev_Greenberg}.  We then
+define, in Section~\ref{ssec:qc_on_GN}, a quasicharacter sheaf for an algebraic group over a local field to be a quasicharacter
+sheaf on the Greenberg transform of the N\'eron model.  In Theorem~\ref{thm:QCXK}, we translate our results from the earlier sections
+to give a description of the categories of
+
+\todo{Comments about Joseph Bernstein's comments?}
 
@@
 \begin{enumerate}
-\labitem{(QC.1)}{QC.1} $\gqcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean
+\labitem{(QC.1)}{QC.1} $\gqcs{L}$ is a rank~one $\ell$-adic local system on $\bG$, by which we mean
 a constructible $\ell$-adic sheaf on $\bG$, locally constant on each connected
@@
 \begin{proof}
-  Let $\qcs{L}$ be a quasicharacter sheaf on $G$. It is clear \todo{Reference} that
-  $\bf^*\gqcs{L}$ is a local system of rank~one, so  \ref{QC.1}  is satisfied.
+  Let $\qcs{L}$ be a quasicharacter sheaf on $G$. We start by showing that
+  $\bf^*\gqcs{L}$ is a local system of rank~one. Let $c_j :\bH^j \hookrightarrow \bH$ be any
+  connected component and let $d_i : \bG^i \hookrightarrow \bG$ be the image of $j$ under the group
+  homomorphism $\pi_0(\bf) : \pi_0(\bH) \to \pi_0(\bG)$.  Write $\bf^j : \bH^j \to \bG^i$
+  for the restriction of $f$ to $\bH^j$.  Since $\gqcs{L}$ is locally constant on the connected
+  components of $\bG$, there is a finite \'etale covering
+  $a_i : X_i \to \bG^i$ such that $a_i^* (\gqcs{L}\vert_{\bG^i})$
+  is constant.  Define $Y_j$ in the following diagram through pullback:
+  \[
+  \begin{tikzcd}[row sep=20, column sep=30]
+   Y_j \dar[dashed]{g_j} \rar[dashed]{b_j} & \bH^j \dar{\bf^j} \rar[hook]{c_j} & \bH \dar{\bf} \\
+   X_i \rar{a_i} & \bG^i \rar[hook]{d_i} & \bG
+  \end{tikzcd}
+  \]
+  Then $b_j$ is a finite \'etale covering
+  of $\bH^j$ and
+  \[
+  b_j^* \left( (\bf^* \gqcs{L})\vert_{\bH^j}\right)
+  = (\bf\circ c_j \circ b_j)^*\gqcs{L}
+  = (d_i\circ a_i\circ g_j)^*\gqcs{L} = g_j^* a_i^* (\gqcs{L}\vert_{\bG^i}).
+  \]
+  Since $a_i^* (\gqcs{L}\vert_{\bG^i})$ is a constant sheaf, its pullback
+  $b_j^* \left( (\bf^*\gqcs{L})\vert_{\bH^j}\right)$ along $g_j$ is also constant.
+  Thus $\bf^*\gqcs{L}$ is locally constant on
+  $\bH^j$. To complete the proof that $\bf^*\gqcs{L}$ satisfies
+  \ref{QC.1}
+  simply observe that $\bf^*\gqcs{L}$ has rank~one since
+  $(\bf^*\gqcs{L})_{\bg} = \gqcs{L}_{f(\bg)}$, for every geometric point ${\bg}$ on $\bG$.
+
   To see that $(\bfxf)^* \mu$ satisfies \ref{QC.2},
@@
 If $\rho_0 = 0$ then the second diagram in \ref{qc.4} for $y=0$ implies that $\rho_x = 0$ for all $x\in G$, in which case $\rho$ is trivial.
-On the other hand, if $\rho_0$ is nonzero then the second diagram in \ref{qc.4} for $y = -x$ implies that $\rho_x$ is nonzero for all $x$ and thus an isomorphism since the stalk of quasicharacter sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
+On the other hand, if $\rho_0$ is nonzero then the second diagram in \ref{qc.4} for $y = -x$ implies that $\rho_x$ is nonzero for all $x$ and thus an isomorphism since the stalk of quasicharacter sheaves are one dimensional; in this case $\rho$ is an isomorphism.
 
@@
 Before turning our attention to quasicharacter sheaves on connected commutative algebraic groups in Section~\ref{ssec:connected}, we treat two special classes of quasicharacter sheaves on arbitrary smooth commutative group schemes $G$:  in Section~\ref{ssec:descentG}, those that descend from local systems on $\bG$ to local systems on $G$; and in Section~\ref{ssec:discrete_isogenies}, those that are defined by discrete isogenies onto $G$.
-The latter will play a role in Sections~\ref{ssec:connected} and \ref{sec:restriction}.
+The latter will play a role in Sections~\ref{ssec:connected} and \ref{ssec:restriction}.
 
@@
 
-\subsection{Restriction to the identity component} \label{sec:restriction}
+\subsection{Restriction to the identity component} \label{ssec:restriction}
 
@@
 
-\subsection{The component group sequence} \label{sec:component}
+\subsection{The component group sequence} \label{ssec:component}
 
@@
 \subsection{The dictionary}
-\label{sec:snake}
+\label{ssec:snake}
 
@@
 
-\subsection{Morphisms of quasicharacters}
+\subsection{Morphisms of quasicharacters} \label{ssec:qcmor}
 
@@
 Let $K$ be a local field (in the sense of Serre) with residue field $\Fq$. 
-In this section we consider connected commutative algebraic groups over $K$ that admit a Néron model, by which we means a lft Néron model.
+In this section we consider connected commutative algebraic groups over $K$ that admit a Néron model, by which we mean an lft Néron model.
 By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected commutative algebraic groups over $K$ that contain no subgroup of type $\mathbb{G}_\text{a}$.
@@
 
-\subsection{Review of the Greenberg transform}
+\subsection{Review of the Greenberg transform} \label{ssec:rev_Greenberg}
 
@@
 
-\subsection{Quasicharacter sheaves on the Greenberg transform of a Néron model}
+\subsection{Quasicharacter sheaves on the Greenberg transform of a Néron model} \label{ssec:qc_on_GN}
 

### 2014-08-22 dictionary.tex

--- 2014-08-22 dictionary.tex
@@
 those that arise via pushforward from a constant sheaf along a discrete isogeny $H \to G$.  When $G$ is connected,
-we show in Section~\ref{} that every quasicharacter sheaf can be described in both of these ways.  We also show that $\TrFrob{G}$ is an isomorphism
-in this case.
-
-In Section~\ref{sec:basechange} we study how quasicharacter sheaves behave under base change
-and Weil restriction.
-Sections~\ref{ssec:descentG} and \ref{sec:finite} describe bounded quasicharacter sheaves and finite quasicharacter sheaves, respectively,
-forming two important subcategories of $\QC(G)$.
-%These subcategories play a key role in the proof of Proposition~\ref{prop:restriction}.
-In Section \ref{ssec:connected} we show that all quasicharacter sheaves on $G$ are finite quasicharacter sheaves when $G$ is connected, and that Trace of Frobenius is an isomorphism in this case.
-We shift to \'etale group schemes $G$ in Section~\ref{sec:etale} and find a cohomological interpretation
-of quasicharacter sheaves in this case.
-In Section~\ref{sec:restriction} we show that for non-connected $G$, restriction to the identity component
-induces an essentially surjective functor of quasicharacter sheaves.
-%Section~\ref{sec:snake} presents the main theorem of this paper: Trace of Frobenius
-%is a functorial isomorphism from isomorphism classes of flabby quasicharacter sheaves on $G$
-%to characters of $G(\Fq)$.
+we show in Section~\ref{ssec:connected} that every quasicharacter sheaf can be described in both of these ways.
+We also show that $\TrFrob{G}$ is an isomorphism in this case.
+
+In Section~\ref{sec:main} we prove that the rows of \eqref{eq:intro-snake} are exact and
+use the snake lemma to determine the kernel and cokernel of $\TrFrob{G}$ for general $G$.
+We show that $\QCiso{G^0} \to \QCiso{G}$ is surjective in Section~\ref{ssec:restriction} and
+that the remainder of the top row of \eqref{eq:intro-snake} is exact in Section~\ref{ssec:component}.
+We put it together in Theorem~\ref{thm:snake} of Section~\ref{ssec:snake}, showing that $\TrFrob{G}$
+is surjective with kernel $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$.  Having described the isomorphism classes of objects,
+in Theorem~\ref{thm:autornaught} of Section~\ref{ssec:qcmor} we show that
+\[
+\Aut(\qcs{L}) \cong \Hom(\pi_0(\bG)_{\Weil{}}, \EEx)
+\]
+and that every morphism is either trivial or an isomorphism.  We conclude in Section~\ref{sec:basechange} by
+giving functorial versions of the restriction and norm homomorphisms $G(k')^* \to G(k)^*$ and $G(k)^* \to G(k')^*$
+and describing how quasicharacter sheaves behave under Weil restriction.
+
+Section~\ref{sec:applications} gives applications of quasicharacter sheaves to commutative algebraic groups over local fields.
+We begin with a review of N\'eron models and of the Greenberg transform in Section~\ref{ssec:rev_Greenberg}.  We then
+define, in Section~\ref{ssec:qc_on_GN}, a quasicharacter sheaf for an algebraic group over a local field to be a quasicharacter
+sheaf on the Greenberg transform of the N\'eron model.  In Theorem~\ref{thm:QCXK}, we translate our results from the earlier sections
+to give a description of the categories of
 

### 2014-08-23 dictionary.tex
Finished summary of sections

@@
 
-Joseph Bernstein has suggested to us that, although quasicharacter sheaves on $\Gr(\underline{T})$ do not correspond exactly to quasicharacters of $T(K)$, the category $\QC(\Gr_R(\underline{T}))$ is the right one to consider and that $\QC(\Gr(\underline{T})$ may be closely tied to characters of  the pure rational forms of $T$ in the sense of Vogan \cite{vogan:93a} or perhaps the rigid inner twists of Tasho Kaletha.
+Joseph Bernstein has suggested to us that, although quasicharacter sheaves on $\Gr(\underline{T})$ do not correspond exactly to quasicharacters of $T(K)$, the category $\QC(\Gr(\underline{T}))$ may be closely tied to characters of the pure rational forms of $T$ in the sense of Vogan \cite{vogan:93a} or perhaps the rigid inner twists of Tasho Kaletha.
 A better understanding of 
-$\Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}}$ should provide insight into this suggestion.
+$\Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}}$ should provide insight into this suggestion. \todo{rephrase}
 
@@
 define, in Section~\ref{ssec:qc_on_GN}, a quasicharacter sheaf for an algebraic group over a local field to be a quasicharacter
-sheaf on the Greenberg transform of the N\'eron model.  In Theorem~\ref{thm:QCXK}, we translate our results from the earlier sections
-to give a description of the categories of
+sheaf on the Greenberg transform of the N\'eron model.  In Theorem~\ref{thm:QCXK}, we translate our results from earlier sections
+to give a description of the isomorphism classes and automorphism groups
+in the category of quasicharacter sheaves on such an algebraic group.
+We specialize to $p$-adic tori in Section~\ref{ssec:qc_tori}, and discuss
+Weil restriction and base change over local fields in Section~\ref{ssec:wrK}.
+Finally, we give a categorical version of a result of Chai and Yu \cite{chai-yu:01a},
+relating quasicharacter sheaves for tori over different local fields, even local fields
+with different characteristic.
 
@@
 
-\subsection{Quasicharacters of $p$-adic tori}
+\subsection{Quasicharacters of $p$-adic tori} \label{ssec:qc_tori}
 
@@
 
-\subsection{Weil restriction and quasicharacters}\label{sec:wrK}
+\subsection{Weil restriction and quasicharacters}\label{ssec:wrK}
 

### 2014-08-23 dictionary.tex
Added the evil subcategory.

@@
 
-\title[The function--sheaf dictionary, with applications over local fields]{The function--sheaf dictionary for smooth commutative group schemes over finite fields, with applications over local fields}
+\title[The function--sheaf dictionary]{The function--sheaf dictionary for smooth commutative group schemes over finite fields}
 
@@
 Greenberg transform $\Gr_R(X)$ of the N\'eron model $X$; although not locally of finite type, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and also a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
-This allows us to adapt our work on quasicharacter sheaves to construct a category $\QC(\Gr_R(X))$ of quasicharacter sheaves on $\Gr(X)$.
+This allows us to adapt our work on quasicharacter sheaves to construct a category $\QC(\Gr_R(X))$ of quasicharacter sheaves on $\Gr_R(X)$.
 The ability to generalize the function--sheaf dictionary to non-connected group schemes, of which the component group of the special fibre of the Néron model $X$ is an important example, plays a crucial role in this application
@@
 \begin{equation}
-0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{\Gr_R(\underline{T})} \to \Hom_\text{qc}(T(K),\EEx) \to 0,
+0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{T} \to \Hom_\text{qc}(T(K),\EEx) \to 0,
 \end{equation}
@@
 These algebraic groups over $K$ form an additive category, denoted by $\mathcal{N}_K$ below, in a natural way, as a full subcategory of connected commutative algebraic groups over $K$.
-This category includes algebraic tori over $K$ and Abelian varieties over $K$, and sometimes unipotent K-wound groups, depending on $K$.
+This category includes algebraic tori over $K$ and Abelian varieties over $K$ unipotent K-wound groups.
+
+\subsection{Quasicharacters}
 
@@
 \]
-In this section we explain how to geometrize and categorify quasicharacters of $X_K(K)$ using quasicharacter sheaves.
+In this section we will see how to geometrize and categorify quasicharacters of $X_K(K)$ using quasicharacter sheaves.
 
@@
 For any $n\leq m$,  the surjective ring homomorphism $R_{m} \to R_n$ determines a
-natural transformation $P^R_{n\leq m} : \Gr^R_{m} \to \Gr^R_n$ between additive functors.
-Crucially, $P^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
+natural transformation 
+\[
+\varrho^R_{n\leq m} : \Gr^R_{m} \to \Gr^R_n
+\]
+between additive functors.
+Crucially, $\varrho^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
 This observation is key to the proof that, for any $X$ lft over $S$, the projective limit 
 \[
-\Gr_R(X) \ceq \varprojlim_{n\in \NN} \Gr^R_n(X)
-\]
-taken with respect to the surjective morphisms $P^R_{n\leq m}(X) : \Gr^R_{m}(X) \to \Gr^R_n(X)$,
+\Gr_R(X) \ceq \varprojlim_{n\in \NN} \Gr^R_n(X),
+\]
+taken with respect to the surjective morphisms $\varrho^R_{n\leq m}(X) : \Gr^R_{m}(X) \to \Gr^R_n(X)$,
 exists in the category of group schemes over $\Fq$.
@@
 \[
-P^R_n(X) : \Gr^R(X) \to \Gr^R_n(X),\qquad \forall n\in \NN_0.
+\varrho^R_n(X) : \Gr^R(X) \to \Gr^R_n(X),\qquad \forall n\in \NN_0.
 \]
@@
 Let $X_K \in \mathcal{N}_K$ and $X$ be as above.
-Although $\Gr_R(X)$ is not locally of finite type, and thus not smooth, let us write $\QC(\Gr_R(X))$ for the rigid monoidal category defined as in Section~\ref{sec:category}, without insisting that the commutative group scheme $G$ is smooth.
-
-The Greenberg transform $\Gr_R(X)$ of $X$ is commutative group scheme over $\Fq$ with component group scheme
-$
-\pi_0(\Gr_R(X))= \pi_0(X) \times_S S_0
-$
-and $\Fq$-rational points
-$
-\Gr_R(X)(\Fq)\iso X_K(K),
-$
-canonically.
+
 For every non-negative integer $n$, $\Gr^R_n(X)$ is {\it smooth} commutative group scheme over $\Fq$ with component group scheme
@@
 %
-Moreover, the morphism of $\Fq$-schemes $P^R_n(X) : \Gr_R(X) \to \Gr^R_n(N)$ induces a functor
-\[
-P^R_n(X)^* : \QC(\Gr^R_n(X)) \to \QC(\Gr_R(X)),
+The Greenberg transform $\Gr_R(X)$ of $X$ is still a commutative group scheme over $\Fq$ with component group scheme
+$
+\pi_0(\Gr_R(X))= \pi_0(X) \times_S S_0
+$
+and its $\Fq$-rational points are given by
+$
+\Gr_R(X)(\Fq)\iso X_K(K),
+$
+canonically, but $\Gr_R(X)$ is not locally of finite type, and therefore not smooth.
+
+%
+Moreover, the morphism of $\Fq$-schemes $\varrho^R_n(X) : \Gr_R(X) \to \Gr^R_n(N)$ induces a functor
+\[
+\varrho^R_n(X)^* : \QC(\Gr^R_n(X)) \to \QC(\Gr_R(X)),
 \]
 as in Proposition~\ref{prop:pullback}.
-This functor is full and faithful, so we may view $\QC(\Gr^R_n(X))$ as a full subcategory of $\QC(\Gr_R(X))$.
+This functor is faithful, so we may view $\QC(\Gr^R_n(X))$ as a subcategory of $\QC(\Gr_R(X))$.
+
+We now define a category which will geometrize quasicharacters of $X_K(K)$.
+Although $\Gr_R(X)$ is not locally of finite type, and thus not smooth, we begin by considering the rigid monoidal category $\QC(\Gr_R(X))$ defined in Section~\ref{sec:category}, without insisting that the commutative group scheme is smooth.
 
 \begin{definition}
-Let $X_K$ be a connected commutative group scheme that admits a Neron model, $X$.
-A {\it quasicharacter sheaf for $X_K$} is an object $\qcs{F}$ in $\QC(\Gr_R(X))$ such that $\qcs{F} \iso P^R_n(X)^*\qcs{L}$ for some $\qcs{L} \in \QC(\Gr^R_n(X))$.
-Quasicharacter sheaves for $X_K$ form a rigid monoidal category in the obvious way, denoted by $\QC(X_K)$.
+We construct an evil subcategory $\QC(X_K)$ of $\QC(\Gr_R(X))$ as follows:
+objects in $\QC(X_K)$ are the $\ell$-adic sheaves $\varrho^R_n(X)^*\qcs{L}$, for $n\in \NN$ and $\qcs{L} \in \QC(\Gr^R_n(X))$; morphism from $\varrho^R_n(X)^*\qcs{L}$ to $\varrho^R_m(X)^*\qcs{L}'$ are $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\qcs{L},\qcs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\qcs{L},\varrho^R_{m\leq n}(X)^*\qcs{L}')$ when $m\leq n$.
+ We refer to $\QC(X_K)$ as the {\it evil category of quasicharacter sheaves for $X_K$}; objects will simply be called {\it 
+Quasicharacter sheaves for $X_K$}.
 \end{definition}
 
-%Note that we may informally regard $\QC(\Gr_R(X))$ a `union' of the full subcategories $\QC(\Gr^R_n(X))$ in $\mathcal{C}(\Gr_R(X))$.
+The evil category of quasicharacter sheaves for $X_K$ is rigid monoidal in the obvious way.
+
+\begin{remark}
+The evil category of quasicharacter sheaves for $X_K$ is evil in the categorical sense.
+If $\varrho^R_n(X)^* : \QC(\Gr^R_n(X)) \to \QC(\Gr_R(X))$ is full then the construction above is easily modified to be non-evil; however, we do not know if $\varrho^R_n(X)^*$ is full.
+In any case, a non-evil alternative construction of $\QC(X_K)$ is available, but it is quite ugly.
+For objects, one considers triples $\qcs{F} \ceq (n, \{\qcs{F}_i\}_{i \ge n}, \{\alpha_{i \le j}\}_{j \ge i \ge n})$, where $n$
+is a positive integer, each $\qcs{F}_i$ is a quasicharacter sheaf on $\Gr^R_i(X)$ and each $\alpha_{i \le j} : \qcs{L}_j \to f^*_{i \le j} \qcs{L}_i$ is an isomorphism; of course, $\alpha_{i \le i}$ is the identity and the $\alpha_{i \le j}$ are compatible with each other.
+If $\qcs{F} \ceq (n, \{\qcs{F}_i\}, \{\alpha_{i \le j}\})$
+and $\qcs{F}' \ceq (m, \{\qcs{F}'_i\}, \{\alpha'_{i \le j}\})$ are objects then $\Hom(\qcs{F}, \qcs{F}')$ is the set
+of equivalence classes of pairs $(k, \{\beta_i\}_{i \ge k})$, where $k \ge m, n$ and the $\beta_i : \qcs{F}_i \to \qcs{F}'_i$ are
+morphisms of quasicharacter sheaves so that
+\[
+\begin{tikzcd}
+\qcs{F}_j \rar{\alpha_j} \dar{\beta_i} & f^*_{i \le j} \qcs{F}_i \dar{f_{i \le j}^*\beta_j} \\
+\qcs{F}'_j \rar{\alpha_j} & f^*_{i \le j} \qcs{L}'_i
+\end{tikzcd}
+\]
+commutes for all $j \ge i \ge k$; we identify two such pairs $(k, \{\beta_i\})$ and $(l, \{\gamma_i\})$ if $\beta_i = \gamma_i$
+for sufficiently large $i$.  Identities and composites are defined in the natural way.
+\end{remark}
 
@@
 \end{enumerate}
-So Theorem~\ref{thm:QCXK} now follows from the fact that each $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(\Gr_R(X))$ and the observation that $\QC(\Gr_R(X))$ a `union' of the subcategories $\QC(\Gr^R_n(X))$ in $\mathcal{C}(\Gr_R(X))$.
+So Theorem~\ref{thm:QCXK} now follows from the fact that each $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(X_K)$ and the observation that $\QC(\Gr_R(X))$ a `union' of the subcategories $\QC(\Gr^R_n(X))$ in $\mathcal{C}(X_K)$.
 \end{proof}
@@
 \begin{equation}
-0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Frob{}} \to \QCiso{\Gr_R(\underline{T})} \to \Hom_\text{qc}(T(K),\EEx) \to 0.
-\end{equation}
-Again by Theorem~\ref{thm:QCXK}, the automorphism groups in the $\QC(\Gr_R(\underline{T}))$ are given, for every quasicharacter sheaf $\qcs{F}$ on $\Gr_R(X)$, by
+0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Frob{}} \to \QCiso{T} \to \Hom_\text{qc}(T(K),\EEx) \to 0.
+\end{equation}
+Again by Theorem~\ref{thm:QCXK}, the automorphism groups in the $\QC(T)$ are given, for every quasicharacter sheaf $\qcs{F}$ on $\Gr_R(X)$, by
 \begin{equation}
@@
 Set $X_{K'} \ceq X_K \times_\Spec{K} \Spec{K'}$
-and $X' \ceq X \times_\Spec{R} \Spec{R'}$.
+Let $X'$ be a Néron model for $X_{K'}$.
 
@@
 \] 
-such that the functor
-\[
-f^* : \QC(\Gr_R(X)) \to \QC(\Res_{k'/k} \Gr_{R'}(X'))
+such that the restriction of the functor
+\[
+f^* : \QC(\Res_{k'/k} \Gr_{R'}(X')) \to  \QC(\Gr_R(X))
 \]
@@
  of smooth $R$-group schemes.
-
+%
 Applying the functor $\Gr_{n}$ to this morphism
@@
 \[
-f^* : \QC(\Res_{k'/k} \Gr_{R'}(X'))\to \QC(\Gr_{R}(X))
-\]
-inducing
+f^* : \QC(\Res_{k'/k} \Gr_{R'}(X'))\to \QC(\Gr_{R}(X)).
+\]
+When restricted to the appropriate evil subcategories, this induces
 \[

### 2014-08-23 dictionary.tex
Changes to Introduction and Applications
Modified comments regarding Bernstein; fixed the proposition using Weil
restriction and Néron models; changed the abstract and title.

@@
 \begin{abstract}
-  We extend Deligne's function--sheaf dictionary from
-  connected commutative algebraic groups over finite fields to smooth
-  commutative group schemes over finite fields,
-  in which case some interesting new features of the dictionary arise.
-   \end{abstract}
-
-\maketitle
-
-\section{Introduction}
-
 Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
 this paper extends Deligne's function--sheaf dictionary for characters of connected commutative algebraic groups over finite fields to characters of smooth commutative group schemes over finite fields.
+ \end{abstract}
+
+\maketitle
+
+\section{Introduction}
 
@@
 Greenberg transform $\Gr_R(X)$ of the N\'eron model $X$; although not locally of finite type, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and also a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
-This allows us to adapt our work on quasicharacter sheaves to construct a category $\QC(\Gr_R(X))$ of quasicharacter sheaves on $\Gr_R(X)$.
+This allows us to adapt our work on quasicharacter sheaves to construct a category $\QC(X_K)$ of quasicharacter sheaves for $X_K$, which are certain sheaves on $\Gr_R(X)\times_{\Spec{\Fq}} \Spec{\bFq}$, with extra structure.
 The ability to generalize the function--sheaf dictionary to non-connected group schemes, of which the component group of the special fibre of the Néron model $X$ is an important example, plays a crucial role in this application
@@
 where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
-We also use quasicharacter sheaves to categorify the transfer of quasicharacters of tori between characteristic $0$ and characteristic $p$ local fields.
-
-Joseph Bernstein has suggested to us that, although quasicharacter sheaves on $\Gr(\underline{T})$ do not correspond exactly to quasicharacters of $T(K)$, the category $\QC(\Gr(\underline{T}))$ may be closely tied to characters of the pure rational forms of $T$ in the sense of Vogan \cite{vogan:93a} or perhaps the rigid inner twists of Tasho Kaletha.
-A better understanding of 
-$\Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}}$ should provide insight into this suggestion. \todo{rephrase}
+%We also use quasicharacter sheaves to categorify the transfer of quasicharacters of tori between characteristic $0$ and characteristic $p$ local fields.
+
+By any measure, there are more quasicharacter sheaves for $T$ than quasicharacters of $T(K)$.  
+%\todo{Maybe move this from the introduction into the body of the paper somewhere.}
+In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization of complete Langlands parameters for $p$-adic groups as equivariant perverse sheaves on Vogan varieties and, in the process, is lead to study the representations of all the pure rational forms of the $p$-adic group simultaneously.
+A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group.
+Indeed, he has suggested to us that our category of quasicharacters for $T$ may be tied to characters of all the pure rational forms of $T$.
 
@@
 quasicharacter sheaves; their knowledge and help have been invaluable.
-We also thank Takashi Suzuki, who made some very helpful observations and suggestions.
-%
+We thank Takashi Suzuki for some very helpful observations and suggestions, including those related to our use of the Hochschild-Serre spectral sequence.
+We thank Joseph Bernstein for suggesting a connection between our category of quasicharacter sheaves on $G$ and his sheaves on the stacky classifying space of $G$.
 Finally, we gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
@@
 
-We will describe the group $\QCiso{G}$ in Theorem \ref{thm:snake}
-and the sets $\Hom(\qcs{L},\qcs{L}')$ in Theorem \ref{thm:autornaught}; in this way we provide a complete description of the category $\QC(G)$.
-
 \begin{remark}
@@
 \end{remark}
+
+We will describe the group $\QCiso{G}$ in Theorem \ref{thm:snake}
+and the sets $\Hom(\qcs{L},\qcs{L}')$ in Theorem \ref{thm:autornaught}; in this way we provide a complete description of the category $\QC(G)$.
+%
+In the meantime, we close this section with an elementary observation about $\Hom(\qcs{L},\qcs{L}')$.
+
+\begin{lemma}\label{lem:autornaught}
+Let $G$ be a smooth commutative group scheme over $\Fq$.
+If $\qcs{L}$ and $\qcs{L}'$ are quasicharacter sheaves on $G$ then
+every $\rho\in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism. 
+\end{lemma}
+
+\begin{proof}
+Suppose $\rho \in \Hom(\qcs{L},\qcs{L}')$.
+We prove the lemma by considering the linear transformations $\rho_{\bar g} : \gqcs{L}_{\bar g} \to \gqcs{L}_{\bar g}$ at the stalks above geometric points ${\bar g}$ on $G$ and showing that, either each $\rho_{\bar g}$ trivial or each $\rho_{\bar g}$ is an isomorphism.
+(This idea is expanded upon in Section~\ref{sec:stalks}.)
+Let ${\bar e}$ be the geometric point above the identity $e$ for $G$ determined by our choice of algebraic closure $\bFq$ of $\Fq$.
+If $\rho_{\bar e} = 0$ then the second diagram in \ref{QC.4} implies that $\rho_{\bar g} = 0$ for all ${\bar g}$, in which case $\rho$ is trivial.
+On the other hand, if $\rho_{\bar e}$ is nontrivial then the second diagram in \ref{QC.4}  implies that $\rho_{\bar g}$ is nontrivial for all ${\bar g}$ and thus an isomorphism, since the stalk of quasicharacter sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
+\end{proof}
 
@@
 Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
-determines a point $\bg$ on $\bG$ fixed by $\Frob{G}$. 
+determines a point geometric point $\bg$ fixed by $\Frob{G}$. 
 Together with the canonical isomorphism $(\Frob{G}^*\gqcs{L})_{\bg} \iso  \gqcs{L}_{\Frob{G}(\bg)}$, in this way the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gqcs{L}_{\bg}$; let $\trace(\phi_{\bg};\gqcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gqcs{L}_{\bg})$ and let $\trFrob{(\gqcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by
@@
 
-\begin{proposition}\label{prop:pullback}
+\begin{lemma}\label{lem:pullback}
   If $f : H\to G$ is a morphism of smooth commutative group schemes over $\Fq$ then
@@
   is a commutative diagram of groups.  Moreover, $(f\circ g)^* = g^* \circ f^*$.
-\end{proposition}
-
+\end{lemma}
 \begin{proof}
@@
 
-\begin{proposition}\label{prop:product}
+\begin{lemma}\label{lem:product}
 If $G_1$ and $G_2$ are smooth commutative group schemes over $\Fq$ then the rule
@@
 commutes.
-\end{proposition}
-
+\end{lemma}
 \begin{proof}
@@
 Set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$;
-by Proposition~\ref{prop:pullback}, $\qcs{L}_1$ a quasicharacter sheaf on $G_1$
+by Lemma~\ref{lem:pullback}, $\qcs{L}_1$ a quasicharacter sheaf on $G_1$
 and $\qcs{L}_2$ is a quasicharacter sheaf on $G_2$.
@@
 \begin{proof}
-The first part of Proposition~\ref{prop:pullback} shows that $F_1$ is a functor,
+The first part of Lemma~\ref{lem:pullback} shows that $F_1$ is a functor,
 while the second part shows that Trace of Frobenius is a natural transformation
-$T: F_1 \to F_2$. When further combined with Proposition~\ref{prop:product},
+$T: F_1 \to F_2$. When further combined with Lemma~\ref{lem:product},
 we see that $F_1$ is an additive functor and $T: F_1 \to F_2$ is a natural
@@
 
-\subsection{Stalks of quasicharacter sheaves}
+\subsection{Stalks of quasicharacter sheaves}\label{sec:stalks}
 
@@
 \end{proposition}
+%\todo{Is this a lemma? Is the corollary a proposition?}
 
@@
 \begin{proof}
-Suppose $\rho \in \Hom(\qcs{L},\qcs{L}')$.
-If $\rho_0 = 0$ then the second diagram in \ref{qc.4} for $y=0$ implies that $\rho_x = 0$ for all $x\in G$, in which case $\rho$ is trivial.
-On the other hand, if $\rho_0$ is nonzero then the second diagram in \ref{qc.4} for $y = -x$ implies that $\rho_x$ is nonzero for all $x$ and thus an isomorphism since the stalk of quasicharacter sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
-
+We have already seen, in Lemma~\ref{lem:autornaught}, that every $\rho\in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism.
 Now suppose $\rho \in \Aut(\qcs{L})$.
@@
  \item $\Aut(\qcs{L}) = 1$, for all quasicharacter sheaves $\qcs{L}$ on $G$;
-  \item for all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $G$ and for every $\rho \in \Hom(\qcs{L},\qcs{L}')$, either $\rho$ is trivial or an isomorphism.
+%  \item for all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $G$ and for every $\rho \in \Hom(\qcs{L},\qcs{L}')$, either $\rho$ is trivial or an isomorphism.
  \end{enumerate}
@@
 Since the only such isomorphism $\rho$ is $\id_V$, it follows that $\Aut(\qcs{E}) = 1$, completing the proof.
-For the last part of the proposition, argue as in the analogous part of Proposition~\ref{prop:autornaught_etale}.
 \end{proof}
@@
 
-\section{The function--sheaf dictionary for smooth, commutative group schemes}\label{sec:main}
+\section{The function--sheaf dictionary for smooth commutative group schemes}\label{sec:main}
 
@@
 Since $\pi_0(G)$ is a étale commutative group scheme -- and thus smooth --
-Proposition~\ref{prop:pullback} implies that \eqref{eq:pi0} defines the sequence of functors
+Lemma~\ref{lem:pullback} implies that \eqref{eq:pi0} defines the sequence of functors
 \begin{equation}\label{eq:pi1}
@@
 Here we show that it is also exact at $\QCiso{G}$.
-First note that $\iota_0^* \circ \pi_0^*$ is trivial by Proposition~\ref{prop:pullback}.
+First note that $\iota_0^* \circ \pi_0^*$ is trivial by Lemma~\ref{lem:pullback}.
 So it suffices to show that if $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$
@@
   be the commutative diagram of abelian groups obtained by applying
-  Proposition~\ref{prop:pullback} to \eqref{eq:pi0}.
+  Lemma~\ref{lem:pullback} to \eqref{eq:pi0}.
  %
@@
 Let $G$ be a smooth commutative group scheme over $\Fq$.
-For all quasicharacter sheaves $\qcs{L}$ and $\qcs{L}'$ on $G$,
-every $\rho \in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism.
+%For all quasicharacter sheaves $\qcs{L}$ and $\qcs{L}'$ on $G$, every $\rho \in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism.
 Moreover, 
@@
 \begin{proof} 
-For the first part of the proposition, argue as in the analogous part of Proposition~\ref{prop:autornaught_etale}.
-For the second, fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the homomorphism $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
+%For the first part of the proposition, argue as in the analogous part of Proposition~\ref{prop:autornaught_etale}.
+%For the second, f
+Fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the homomorphism $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
 This group homomorphism is clearly injective: if $\rho_x = \id_{\qcs{L}_x}$ for every $x\in \bG$ then $\rho = \id_{\qcs{L}}$.
@@
 \begin{proof}
-This result follows immediately from Proposition~\ref{prop:pullback} together with the identifications
+This result follows immediately from Lemma~\ref{lem:pullback} together with the identifications
 \[
@@
 \begin{proof}
-By Proposition~\ref{prop:pullback} the pullback part of the definition of $\rho$ corresponds to the map
+By Lemma~\ref{lem:pullback} the pullback part of the definition of $\rho$ corresponds to the map
 \[
@@
 \]
-as in Proposition~\ref{prop:pullback}.
+as in Lemma~\ref{lem:pullback}.
 This functor is faithful, so we may view $\QC(\Gr^R_n(X))$ as a subcategory of $\QC(\Gr_R(X))$.
@@
  We refer to $\QC(X_K)$ as the {\it evil category of quasicharacter sheaves for $X_K$}; objects will simply be called {\it 
-Quasicharacter sheaves for $X_K$}.
+quasicharacter sheaves for $X_K$}.
 \end{definition}
@@
 To begin, fix $n\in \NN$.
-The following statements follow directly from properties of Néron models, Proposition~\ref{prop:functorialG} and Theorems~\ref{thm:snake} and \ref{thm:autornaught} together with our observations about the component group of $\Gr^R_n(X)$.
+The following statements follow directly from Lemma~\ref{lem:autornaught}, Proposition~\ref{prop:functorialG}, Theorems~\ref{thm:snake} and \ref{thm:autornaught}, properties of Néron models and our observations about the component group of $\Gr^R_n(X)$.
 \begin{enumerate}
@@
 \end{enumerate}
-So Theorem~\ref{thm:QCXK} now follows from the fact that each $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(X_K)$ and the observation that $\QC(\Gr_R(X))$ a `union' of the subcategories $\QC(\Gr^R_n(X))$ in $\mathcal{C}(X_K)$.
-\end{proof}
-
-\subsection{Quasicharacters of $p$-adic tori} \label{ssec:qc_tori}
+So Theorem~\ref{thm:QCXK} now follows from the fact that each $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(X_K)$ and the observation that $\QC(X_K)$ a `union' of the subcategories $\QC(\Gr^R_n(X))$ in $\QC(\Gr_R(X))$.
+\end{proof}
+
+\subsection{Quasicharacters for $p$-adic tori} \label{ssec:qc_tori}
 
@@
 \end{equation}
-Again by Theorem~\ref{thm:QCXK}, the automorphism groups in the $\QC(T)$ are given, for every quasicharacter sheaf $\qcs{F}$ on $\Gr_R(X)$, by
+Again by Theorem~\ref{thm:QCXK}, the automorphism groups in the $\QC(T)$ are given, for every quasicharacter sheaf $\qcs{F}$ for $T$, by
 \begin{equation}
-\Aut(\qcs{F}) \iso \Hom(X_*(T)_{\Weil{K}},\EEx) = \Hom(X_*(T),\EEx)^{\Weil{K}} = (X^*(T)\otimes \EEx)^{\Weil{K}} = (\check{T}_\ell)^{\Weil{K}}
+\Aut(\qcs{F}) \iso \Hom(X_*(T)_{\Weil{K}},\EEx) \iso \Hom(X_*(T),\EEx)^{\Weil{K}} = (\check{T}_\ell)^{\Weil{K}}
 \end{equation}
@@
 \]
-obtained by applying Proposition~\ref{prop:pullback} to \eqref{men} gives
+obtained by applying Lemma~\ref{lem:pullback} to \eqref{men} gives
 \[
@@
 Suppose $m$ and $m'$ are non-negative integers such that 
+\[
+R_m \iso R'_{m'},
+\]
+in which case $K$ and $K'$ are said to be $m$-close, and
 \begin{equation}\label{eq:schematic_transfer}
-R_m \iso R'_{m'}
-\qquad
-\text{and}
-\qquad
 X \times_{S} S_m \iso X' \times_{S'} S'_{m'}.
@@
 $
-as smooth group schemes over $\Fq$; accordingly, by Proposition~\ref{prop:pullback} the isomorphism above determines an equivalence of categories
+as smooth group schemes over $\Fq$; accordingly, by Lemma~\ref{lem:pullback} the isomorphism above determines an equivalence of categories
 \begin{equation}\label{eq:categorical_transfer}
@@
 \end{equation}
-The isomorphism \eqref{eq:transfer} is an instance of {\it transfer of (certain) quasicharacters} between $X_K(K)$ and $X_{K'}(K')$. 
+The isomorphism \eqref{eq:transfer} is an instance of {\it transfer} of (certain) quasicharacters between $X_K(K)$ and $X_{K'}(K')$. 
 We now recognize this transfer of quasicharacters as a consequence of the equivalence of categories of quasicharacter sheaves \eqref{eq:categorical_transfer}.
 
-Such a relationship can exist between quasicharacters of algebraic tori over local fields, even when the characteristics of $K$ and $K'$ differ.
+The isomorphism \eqref{eq:schematic_transfer} can indeed exist between quasicharacters of algebraic tori over local fields, even when the characteristics of $K$ and $K'$ differ.
 Suppose $T$ and $T'$ are tori over non-archimedian local fields $K$ and $K'$,

### 2014-08-23 degruyter-crelle/dictionary.tex
Moved the current version into the crelle folder. Work there.

--- 2014-08-23 dictionary.tex
@@
-% !TEX encoding = UTF-8 Unicode
-\documentclass{amsart}
-\pdfoutput=1
-
-%%%%%%%%%%%%%%%%%% HEADING %%%%%%%%%%%%%%%%%%
+%%------------------------------------------------------%%
+%% This file should be the main file of your article.   %%
+%% Please uncomment exactly one of the following lines. %%
+%%------------------------------------------------------%%
+
+%% \documentclass[CM,Submssn]{degruyter-crelle}       %% Equations numbered as (1), (2) etc.
+ \documentclass[CM,Submssn,SecEq]{degruyter-crelle} %% Equations numbered as (1.1), (1.2) etc.
+
+%% Do not alter the following line.
+\firstpage{}\volume{}\volumeyear{}\copyrightyear{}\doiyear{}\doi{}\received{XXX}\revised{XXX}
 
@@
 
-\date{\today}
-\author{Clifton Cunningham}
-\email{cunning@math.ucalgary.ca}
-\address{University of Calgary}
-\author{David Roe}
-\email{roed.math@gmail.com}
-\address{Pacific Institute for the Mathematical Sciences, University of Calgary}
-\subjclass[2010]{14F05 (primary), 14L15 (secondary)}
-\keywords{function--sheaf dictionary, trace of Frobenius, geometrization, categorification, quasicharacters, quasicharacter sheaves, smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor}
+\author{Clifton}{Cunningham}{C.~Cunningham}{Calgary}
+\author{David}{Roe}{D.~Roe}{Calgary}
+
+\contact{Department of Mathematics and Statistics, University of Calgary, street, zip code, city, country}{cunning@math.ucalgary.ca}
+\contact{Pacific Institute for the Mathematical Sciences, University of Calgary, street, zip code, city, country}{roed.math@gmail.com}
+
+%\subjclass[2010]{14F05 (primary), 14L15 (secondary)}
+%\keywords{function--sheaf dictionary, trace of Frobenius, geometrization, categorification, quasicharacters, quasicharacter sheaves, smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor}
+
+\researchsupported{We gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
+and the National Science and Engineering Research Council,
+as well the hospitality of the Banff International Research Station during our week-long stay in May 2012.}
+
+%% Define theorem-like environments as usual:
+
+%\theoremstyle{plain}
+ %\newtheorem{theorem}{Theorem}[section]
+
+%\theoremstyle{definition}
+% \newtheorem{remark}[theorem]{Remark}
 
@@
 
-%%%%%%%%%%%% BEGIN DOCUMENT %%%%%%%%%%%%
+%%%%%%%%%%%% BEGIN DOCUMENT %%%%%%%%%%%
+
 \begin{document}
@@
 
-\maketitle
+%% \tableofcontents %% Just for papers exceeding 50 pages.
 
@@
 \begin{equation}\label{introbox}
-m^* \qcs{E} \iso \qcs{E} \boxtimes \qcs{E},\tag{0}
+m^* \qcs{E} \iso \qcs{E} \boxtimes \qcs{E},%\tag{0}
 \end{equation}
@@
 If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, however, then one must keep track of the choice of \eqref{introbox}, leading to a category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is an isomorphism of local systems on $G\times G$.
-If the component group scheme $\pi_0(G)$ (which is an étale commutative group scheme over $\FF_q$) is not cyclic, then while the trace of Frobenius provides a surjection from isomorphism classes in the category of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\FF_q)$, that group homomorphism need not be injective.
+If the component group scheme $\pi_0(G)$ (which is an \'etale commutative group scheme over $\FF_q$) is not cyclic, then while the trace of Frobenius provides a surjection from isomorphism classes in the category of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\FF_q)$, that group homomorphism need not be injective.
 In other words, if $G$ is a commutative algebraic group over $\FF_q$ which is not connected, then every character may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely. 
@@
 
-We first test the category of quasicharacter sheaves by examining its objects on étale commutative group schemes $G$ over $\FF_q$; étale group schemes form a counterpoint to connected algebraic groups, since the component group of a smooth commutative group scheme is an étale group scheme.
+We first test the category of quasicharacter sheaves by examining its objects on \'etale commutative group schemes $G$ over $\FF_q$; \'etale group schemes form a counterpoint to connected algebraic groups, since the component group of a smooth commutative group scheme is an \'etale group scheme.
 We find that the group homomorphism 
@@
 The fact that $T_G$ is not an isomorphism should not be too troubling because if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
-Here we also see the importance of working with Weil sheaves; for example, without them, we would not be able to geometrize the character of the étale group scheme $\ZZ$ over $\FF_q$ given by $1\mapsto \ell$, for example.
+Here we also see the importance of working with Weil sheaves; for example, without them, we would not be able to geometrize the character of the \'etale group scheme $\ZZ$ over $\FF_q$ given by $1\mapsto \ell$, for example.
 
@@
 %
-As we show in the paper, while characters of connected commutative algebraic groups $G$ can be geometrized using  local systems trivialized by discrete isogenies to $G$, this is not the right perspective if one wishes to geometrize characters of smooth commutative group schemes, such as étale commutative group schemes.
-Indeed, quasicharacter sheaves on étale commutative group schemes that are trivialized by discrete isogenies are invisible to the trace of Frobenius.
-
-Having understood quasicharacter sheaves on commutative smooth group schemes over $\FF_q$ in two extreme cases -- connected algebraic groups and étale commutative group schemes -- we turn to the general case.
+As we show in the paper, while characters of connected commutative algebraic groups $G$ can be geometrized using  local systems trivialized by discrete isogenies to $G$, this is not the right perspective if one wishes to geometrize characters of smooth commutative group schemes, such as \'etale commutative group schemes.
+Indeed, quasicharacter sheaves on \'etale commutative group schemes that are trivialized by discrete isogenies are invisible to the trace of Frobenius.
+
+Having understood quasicharacter sheaves on commutative smooth group schemes over $\FF_q$ in two extreme cases -- connected algebraic groups and \'etale commutative group schemes -- we turn to the general case.
 Remarkably, we find that the general case can be understood from these two extreme cases, using the component group sequence
@@
 This allows us to adapt our work on quasicharacter sheaves to construct a category $\QC(X_K)$ of quasicharacter sheaves for $X_K$, which are certain sheaves on $\Gr_R(X)\times_{\Spec{\Fq}} \Spec{\bFq}$, with extra structure.
-The ability to generalize the function--sheaf dictionary to non-connected group schemes, of which the component group of the special fibre of the Néron model $X$ is an important example, plays a crucial role in this application
+The ability to generalize the function--sheaf dictionary to non-connected group schemes, of which the component group of the special fibre of the N\'eron model $X$ is an important example, plays a crucial role in this application
 since these group schemes are not connected in general.
@@
     & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
-    0 \rar & \pi_0(G)(\FF_q)^* \rar & G(\Fq)^* \rar & G^0(\FF_q)^* \rar & 0,
+    0 \rar & \Hom(\pi_0(G)(\FF_q),\EEx) \rar & \Hom(G(\Fq),\EEx) \rar & \Hom(G^0(\FF_q),\EEx) \rar & 0,
   \end{tikzcd}
@@
 and that every morphism is either trivial or an isomorphism.  We conclude in Section~\ref{sec:basechange} by
-giving functorial versions of the restriction and norm homomorphisms $G(k')^* \to G(k)^*$ and $G(k)^* \to G(k')^*$
+giving functorial versions of the restriction and norm homomorphisms $\Hom(G(k'),\EEx) \to \Hom(G(k),\EEx)$ and $\Hom(G(k),\EEx) \to \Hom(G(k'),\EEx)$
 and describing how quasicharacter sheaves behave under Weil restriction.
@@
 
-%\begin{acknowledgements}
-\subsection{Acknowledgments}
-We thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
-for allowing us to hijack much of our Research in Teams meeting at BIRS into a discussion of
-quasicharacter sheaves; their knowledge and help have been invaluable.
-We thank Takashi Suzuki for some very helpful observations and suggestions, including those related to our use of the Hochschild-Serre spectral sequence.
-We thank Joseph Bernstein for suggesting a connection between our category of quasicharacter sheaves on $G$ and his sheaves on the stacky classifying space of $G$.
-Finally, we gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
-and the National Science and Engineering Research Council,
-as well the hospitality of the Banff International Research Station during our week-long stay in May 2012.
-
-%\end{acknowledgements}
-
-\tableofcontents
+%\tableofcontents
 
@@
 %To see why, we begin by specializing the definition of quasicharacter sheaves to the case
-%of étale commutative group schemes,
+%of \'etale commutative group schemes,
 %using the equivalence $G \mapsto G(\bFq)$
@@
 
-In this section we find a complete characterization of the category of quasicharacter sheaves on étale commutative group schemes over finite fields.
+In this section we find a complete characterization of the category of quasicharacter sheaves on \'etale commutative group schemes over finite fields.
 
@@
 %
-A quasicharacter sheaf $\qcs{L}$ on an étale commutative group scheme $G$ over $\Fq$ is:
+A quasicharacter sheaf $\qcs{L}$ on an \'etale commutative group scheme $G$ over $\Fq$ is:
 \begin{enumerate}
@@
 \begin{remark}
-Although we will only use the group homomorphism $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an étale commutative group scheme, the function is defined for all smooth commutative group schemes $G$.
+Although we will only use the group homomorphism $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an \'etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$.
 However, the next result is false in that context.
@@
 
-In this section we find the relationship between the group homomorphisms $\TrFrob{G}$ and $S_G$, and use this to find the group $\QCiso{G}$ when $G$ is an étale commutative group scheme over $\Fq$.
+In this section we find the relationship between the group homomorphisms $\TrFrob{G}$ and $S_G$, and use this to find the group $\QCiso{G}$ when $G$ is an \'etale commutative group scheme over $\Fq$.
 
@@
 \begin{proposition}\label{prop:autornaught_etale}
-Let $G$ be an étale commutative group scheme over $\Fq$.
+Let $G$ be an \'etale commutative group scheme over $\Fq$.
 If $\qcs{L}$ and $\qcs{L}'$ are quasicharacter sheaves on $G$ then
@@
 
-%Note that Proposition~\ref{prop:autornaught_etale} tells us that if $G$ is an étale commutative group scheme over $\Fq$ then every hom-set is either trivial or $\{ 0 \} \cup \left(G(\bFq)_{\Weil{}}\right)^*$, non-canonically.
+%Note that Proposition~\ref{prop:autornaught_etale} tells us that if $G$ is an \'etale commutative group scheme over $\Fq$ then every hom-set is either trivial or $\{ 0 \} \cup \left(G(\bFq)_{\Weil{}}\right)^*$, non-canonically.
 
@@
 
-A finite, étale, surjective morphism $H\to G$ of smooth group schemes over $\Fq$ for which the action of $\Gal(\bFq/\Fq)$ on the kernel is trivial is called a {\it discrete isogeny}.
+A finite, \'etale, surjective morphism $H\to G$ of smooth group schemes over $\Fq$ for which the action of $\Gal(\bFq/\Fq)$ on the kernel is trivial is called a {\it discrete isogeny}.
 
@@
 We must show that comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
-To do this we use étale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$. 
+To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$. 
 In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
@@
 From here, Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields \citelist{\cite{deligne:SGA4.5}*{Sommes trig.}, \cite{laumon:87a}*{1.1.3}}  gives us all we need, as we briefly recall.
-The key observation is that, by étale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
+The key observation is that, by \'etale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
 Using the equivalence given by $\Lang^*$, if $\Lang^*\qcs{E} = V$ with character $\psi$ and isomorphism $V\to V\otimes V$ then 
@@
 In particular, as we have already seen in Section~\ref{sec:etale}, for a given quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ there may be a different isomorphism $\mu' : \bm^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$ for which $\qcs{L}'=(\gqcs{L},\mu',\phi)$ is also a quasicharacter sheaf on $G$, not isomorphic to $\qcs{L}$ in $\QC(G)$.
-Indeed, Proposition~\ref{prop:etale-iso} shows that when $G$ is étale, $\Hh^2(\bG,\EEx)^{\Frob{}}$ measures the possibilities for $\mu'$.
+Indeed, Proposition~\ref{prop:etale-iso} shows that when $G$ is \'etale, $\Hh^2(\bG,\EEx)^{\Frob{}}$ measures the possibilities for $\mu'$.
 In other words, the common perspective on the function--sheaf dictionary leads only, and exactly, to the part of category of quasicharacter sheaves that is {\it completely invisible} to the trace of Frobenius!
@@
 \end{equation}
-Since $\pi_0(G)$ is a étale commutative group scheme -- and thus smooth --
+Since $\pi_0(G)$ is a \'etale commutative group scheme -- and thus smooth --
 Lemma~\ref{lem:pullback} implies that \eqref{eq:pi0} defines the sequence of functors
@@
 This group homomorphism is clearly injective: if $\rho_x = \id_{\qcs{L}_x}$ for every $x\in \bG$ then $\rho = \id_{\qcs{L}}$.
-Note that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom_\text{cts}(\bG_{\Weil{}},\EEx)$, where $\bG_{\Weil{}}$ is given the topology of the base of the espace étalé attached to $\gqcs{L}$.
+Note that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom_\text{cts}(\bG_{\Weil{}},\EEx)$, where $\bG_{\Weil{}}$ is given the topology of the base of the espace \'etal\'e attached to $\gqcs{L}$.
 Since $\ell$ is invertible in $\Fq$, it follows that $\Hom_\text{cts}(\bG_{\Weil{}},\EEx) = \Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
@@
 Let $K$ be a local field (in the sense of Serre) with residue field $\Fq$. 
-In this section we consider connected commutative algebraic groups over $K$ that admit a Néron model, by which we mean an lft Néron model.
+In this section we consider connected commutative algebraic groups over $K$ that admit a N\'eron model, by which we mean an lft N\'eron model.
 By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected commutative algebraic groups over $K$ that contain no subgroup of type $\mathbb{G}_\text{a}$.
@@
 Write $\m$ for the maximal ideal of $R$ and set $R_n = R/\m^{n+1}$, for every non-negative integer $n$.
-Suppose $X_K \in \mathcal{N}_K$ with Néron model $X$ over $R$.
+Suppose $X_K \in \mathcal{N}_K$ with N\'eron model $X$ over $R$.
 A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) \to X(R_n)$, for some non-negative integer $n$;
@@
 
-\subsection{Quasicharacter sheaves on the Greenberg transform of a Néron model} \label{ssec:qc_on_GN}
+\subsection{Quasicharacter sheaves on the Greenberg transform of a N\'eron model} \label{ssec:qc_on_GN}
 
@@
 \]
-where $X$ is a Néron model for $X_K$, as functors from $\mathcal{N}_K$ to the category of abelian groups. 
-Regarding this natural transformation, for every $X_K \in \mathcal{N}_K$ with Néron model $X$:
+where $X$ is a N\'eron model for $X_K$, as functors from $\mathcal{N}_K$ to the category of abelian groups. 
+Regarding this natural transformation, for every $X_K \in \mathcal{N}_K$ with N\'eron model $X$:
 \begin{enumerate}
@@
 To begin, fix $n\in \NN$.
-The following statements follow directly from Lemma~\ref{lem:autornaught}, Proposition~\ref{prop:functorialG}, Theorems~\ref{thm:snake} and \ref{thm:autornaught}, properties of Néron models and our observations about the component group of $\Gr^R_n(X)$.
+The following statements follow directly from Lemma~\ref{lem:autornaught}, Proposition~\ref{prop:functorialG}, Theorems~\ref{thm:snake} and \ref{thm:autornaught}, properties of N\'eron models and our observations about the component group of $\Gr^R_n(X)$.
 \begin{enumerate}
@@
 Let $X_K$ be a connected commutative algebraic group over $K$
-that admits a Néron model $X$ over $R$.
+that admits a N\'eron model $X$ over $R$.
 Set $X_{K'} \ceq X_K \times_\Spec{K} \Spec{K'}$
-Let $X'$ be a Néron model for $X_{K'}$.
+Let $X'$ be a N\'eron model for $X_{K'}$.
 
@@
 \begin{proof}
-Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} to include locally finite type Néron models,
-one may show that $\Res_{R'/R}(X')$ is a Néron model for $\Res_{K'/K}(X_{K'})$.
-By the Néron mapping property, the canonical closed immersion
+Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} to include locally finite type N\'eron models,
+one may show that $\Res_{R'/R}(X')$ is a N\'eron model for $\Res_{K'/K}(X_{K'})$.
+By the N\'eron mapping property, the canonical closed immersion
 \[
@@
 
-Suppose $X_K\in \mathcal{N}_K$ with Néron model $X$ and $X'_{K'}\in \mathcal{N}_K'$ with Néron model $X'$.
+Suppose $X_K\in \mathcal{N}_K$ with N\'eron model $X$ and $X'_{K'}\in \mathcal{N}_K'$ with N\'eron model $X'$.
 Suppose $m$ and $m'$ are non-negative integers such that 
@@
 One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes between the
-$\underline{T} \times_S S_n$ and $\underline{T}' \times_{S'} S'_n$, where $\underline{T}$ is a Néron model of $T$ and $\underline{T}'$ is a Néron model of $T'$, assuming that $T$ and $T'$ are sufficiently congruent.
+$\underline{T} \times_S S_n$ and $\underline{T}' \times_{S'} S'_n$, where $\underline{T}$ is a N\'eron model of $T$ and $\underline{T}'$ is a N\'eron model of $T'$, assuming that $T$ and $T'$ are sufficiently congruent.
 They define a quantity $h$ (the smallest integer so that $\pi^h$ lies in the
@@
 \end{proposition}
+
+\acknowl{
+We thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
+for allowing us to hijack much of our Research in Teams meeting at BIRS into a discussion of
+quasicharacter sheaves; their knowledge and help have been invaluable.
+We thank Takashi Suzuki for some very helpful observations and suggestions, including those related to our use of the Hochschild-Serre spectral sequence.
+We thank Joseph Bernstein for suggesting a connection between our category of quasicharacter sheaves on $G$ and his sheaves on the stacky classifying space of $G$.
+We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and for their help in the proof of Proposition~\ref{prop:wrK}.
+}
+
+%-------------------------------------------------------------------------%
+% GENERAL INSTRUCTIONS                                                    %
+% Please keep formatting macros to a minimum.                             %
+% Avoid redundant source code such as unused definitions or longer        %
+% passages of comments (% or {comment}).                                  %
+% Do not worry about bad page breaks, etc. and avoid adding extra space   %
+% and using glue to improve the appearance of the manuscript.             %
+% Please ensure that the material has been carefully proofread and that   %
+% all files used are made available to the editors/publisher.             %
+%-------------------------------------------------------------------------%
+
+%-------------------------------------------------------------------------%
+% PACKAGES                                                                %
+% Missing packages can be downloaded at www.tug.org/ctan.html.            %
+%-------------------------------------------------------------------------%
+
+%-------------------------------------------------------------------------%
+% MULTILINE EQUATIONS                                                     %
+% For numbered/unnumbered multiline equations use align/align* instead of %
+% eqnarray. (Other available environments for multiline displays are      %
+% gather, multline, aligned, split, etc.)                                 %
+%-------------------------------------------------------------------------%
+
+%-------------------------------------------------------------------------%
+% QED SYMBOL                                                              %
+% The \qedhere command forces the QED symbol to go on the present line,   %
+% which might be useful if the last part of a proof environment is, e.g., %
+% a displayed equation or list environment.                               %
+%-------------------------------------------------------------------------%
+
+%-------------------------------------------------------------------------%
+% SOME MORE MATH                                                          %
+% -- Avoid blank lines before or after a display, unless you really want  %
+%    to start a new paragraph.                                            %
+% -- Use equation*, gather* or the bracket pair \[ and \] instead of      %
+%    double dollar signs $$.                                              %
+% -- Use \operatorname{...} for math operators that are not predefined    %
+%    or define new operators with \DeclareMathOperator. lim-like          %
+%    operators can be defined with \DeclareOperator*                      %
+% -- Use \quad for spacings in displayed formulas.                        %
+% -- Use \substack{... \\ ...} for multiline subscripts on, e.g., sums.   %
+%-------------------------------------------------------------------------%
+
+%-------------------------------------------------------------------------%
+% ENUMERATIONS                                                            %
+% By default, the labels of first level enumerations are (i), (ii), etc.  %
+% You may change them to become, e.g., A., B. etc., using an optional     %
+% argument: \begin{enumerate}[A.]                                         %
+%-------------------------------------------------------------------------%
+
+%-------------------------------------------------------------------------%
+% FIGURES AND TABLES                                                      %
+% You may include a figure writing                                        %
+% \begin{figure}[t]                                                       %
+%   \includegraphics[width=.8\textwidth]{xxx.yyy}                         %
+%   \caption{Caption.}\label{fig:zzz}                                     %
+% \end{figure}                                                            %
+% A table is included similar using the table environment.                %
+% Sub-captions are created as follows:                                    %
+% \begin{figure}[t]                                                       %
+%   \subfloat[Caption a]{\includegraphics[width=.45\textwidth]{...}}      %
+%   \hfill                                                                %
+%   \subfloat[Caption b]{\includegraphics[width=.45\textwidth]{...}}      %
+%   \caption{Caption.}                                                    %
+% \end{figure}                                                            %
+%-------------------------------------------------------------------------%
+
+%-------------------------------------------------------------------------%
+% QUOTATION MARKS                                                         %
+% Double quotation marks are produced using `` and ''. The opening quote  %
+% then looks like a superscript 66 and the closing quote like a           %
+% superscript 99.                                                         %
+%-------------------------------------------------------------------------%
+
+%-------------------------------------------------------------------------%
+% HYPHEN VS. DASH                                                         %
+% The hyphen (-) is used for compound words like $n$-dimensional.         %
+% (Don't write things like $n-$dimensional!)                              %
+% The en-dash (--) is used for number ranges and it can stand for `and',  %
+% e.g., between two names: ``Various generalizations of the               %
+% Cauchy--Schwarz inequality are presented on pages 63--67.''             %
+% To partition a sentence one may use the em-dash (---) with no space     %
+% on either side; we prefer the en-dash with a blank on both sides.       %
+% The mathematical minus sign is produced by a single - within            %
+% mathematics mode.                                                       %
+%-------------------------------------------------------------------------%
+
+%-------------------------------------------------------------------------%
+% REFERENCES                                                              %
+% Use \label and \ref for all cross-references to equations, figures,     %
+% tables, sections, subsections, etc.                                     %
+%-------------------------------------------------------------------------%
+
+%-------------------------------------------------------------------------%
+% BIBLIOGRAPHY                                                            %
+% References should be collected at the end of the paper and numbered in  %
+% alphabetical order of the authors' names. Titles of journals should be  %
+% abbreviated as in Mathematical Reviews. Please do not use small caps    %
+% for the names of the authors. The preferred style is shown in the       %
+% examples below.                                                         %
+% Refer to the bibliography entries using \cite commands.                 %
+% Using BibTeX, you simply have to add the names of your databases as     %
+%   \bibliography{mydatabase}                                             %
+% The file crelle.bst then ensures the correct style.                     %
+%-------------------------------------------------------------------------%
+
+\begin{thebibliography}{9}
+
+\bibitem{article}
+\textit{T.~Angel} and \textit{I.~E.~Shparlinski},
+Article in a journal, J. reine angew. Math. \textbf{647} (2010), 123--156.
+
+\bibitem{preprint}
+\textit{C.~Bonnaf\'e},
+Preprint, preprint 2008, \url{http://arxiv.org/abs/0805.4100}.
+
+\bibitem{proceedings}
+\textit{P. Brooksbank},
+Article in a conference proceedings,
+in: Finite geometries (Pingree Park 2004), Oxford University Press, Oxford (2006), 1--16.
+
+\bibitem{phdthesis}
+\textit{J.~D.~King},
+Unpublished dissertation,
+Ph.D. thesis, University of Cambridge, 1995.
+
+\bibitem{book}
+\textit{F. Sukochev}, \textit{S. Lord} and \textit{D. Zanin},
+Book, 2nd ed., De Gruyter, Berlin 2012.
+
+\end{thebibliography}
 
@@
 %sagemathcloud={"zoom_width":105}
+
+\end{document}

### 2014-08-23 crelle-dictionary.tex
moved the current file back to the main directory
Current file: crelle-dictionary.tex.
Bibliography style is not correct.

--- 2014-08-23 degruyter-crelle/dictionary.tex
@@
 %-------------------------------------------------------------------------%
-
-\begin{thebibliography}{9}
-
-\bibitem{article}
-\textit{T.~Angel} and \textit{I.~E.~Shparlinski},
-Article in a journal, J. reine angew. Math. \textbf{647} (2010), 123--156.
-
-\bibitem{preprint}
-\textit{C.~Bonnaf\'e},
-Preprint, preprint 2008, \url{http://arxiv.org/abs/0805.4100}.
-
-\bibitem{proceedings}
-\textit{P. Brooksbank},
-Article in a conference proceedings,
-in: Finite geometries (Pingree Park 2004), Oxford University Press, Oxford (2006), 1--16.
-
-\bibitem{phdthesis}
-\textit{J.~D.~King},
-Unpublished dissertation,
-Ph.D. thesis, University of Cambridge, 1995.
-
-\bibitem{book}
-\textit{F. Sukochev}, \textit{S. Lord} and \textit{D. Zanin},
-Book, 2nd ed., De Gruyter, Berlin 2012.
-
-\end{thebibliography}
-
-\bibliographystyle{amsalpha}
+%\bibliographystyle{amsalpha}
 \bibliography{bibliography/Biblio}
@@
 \end{document}
-
-\begin{table}[ht]
-\caption{A big diagram}
-\begin{center}
-{\smaller\smaller\smaller
-    \[
-  \begin{tikzcd}[row sep=20, column sep=3]
-&   &  0 \arrow{dd} && 0 \arrow{dd} && 0\arrow{dd} & \\
-& &&  0 \arrow[crossing over]{dd} && 0 \arrow[crossing over]{dd} && 0\arrow{dd} & & \\
-&   {}& \ker \TrFrob{C} \arrow[->>]{rr} \arrow[>->>]{dr} \arrow{dd} && \arrow{dd} \ker \TrFrob{B} \arrow{rr} \arrow[>->]{dr}  && \ker \TrFrob{A}=0 \arrow[>->>]{dr} \arrow{dd} \arrow{rr} && 0 & \\
-& && \Hh^0(\Weil{},\Hh^2(C,\EEx)) \arrow[crossing over,->>]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(B,\EEx)) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(A,\EEx)) \arrow[crossing over]{dd}  &  &  \\
-0  \arrow{rr} & & \QCiso{C} \arrow[>->>]{dr}\arrow{rr} \arrow{dd}%{\TrFrob{C}}
-    && \QCiso{B} \arrow[>->]{dr} \arrow{rr} \arrow{dd}%{\TrFrob{B}}
-    && \QCiso{A} \arrow[>->>]{dr} \arrow{dd}%{\TrFrob{A}}
-    \arrow{rr}  &   & 0 & \\
-& \Hh^1(E^\bullet_{A}) \arrow[crossing over]{rr}  && \Hh^2(E^\bullet_{C}) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^2(E^\bullet_{B}) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^2(E^\bullet_{A}) \arrow{rr} \arrow[crossing over]{dd} &  & \Hh^3(E^\bullet_{C}) \\
-0  \arrow{rr} & & C(\Fq)^* \arrow[>->>]{dr} \arrow{rr} \arrow{dd}
-    && \arrow{dd} B(\Fq)^* \arrow[>->>]{dr} \arrow{rr} && A(\Fq)^* \arrow[>->>]{dr}  \arrow{dd}
-    \arrow{rr}&& 0 & \\
-& %\Hh^2(\Weil{},\Hh^1({\bar A},\EEx)) \arrow{rr}
- && \Hh^1(\Weil{},\Hh^1(C,\EEx)) \arrow[crossing over]{dd} \arrow[crossing over]{rr}  && \Hh^1(\Weil{},\Hh^1(B,\EEx)) \arrow[crossing over]{dd} \arrow[crossing over]{rr} && \Hh^1(\Weil{},\Hh^1(A,\EEx)) \arrow[crossing over]{dd}  &  & %\Hh^0(\Weil{},\Hh^1({\bar C},\EEx))
- \\
-& & 0  && 0  &&  0  && & \\
- &      &&  0 && 0 && 0 & & \\
-  \end{tikzcd}
-  \]
-}
-\end{center}
-\label{diagram}
-\end{table}
-
-%sagemathcloud={"zoom_width":105}
-
-\end{document}

### 2014-08-23 crelle-dictionary.tex
Lots of spacing problems. We'd better to this together, tomorrow  . . .

@@
 % Encodings
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
+%\usepackage[utf8]{inputenc}
+%\usepackage[T1]{fontenc}
 % AMS packages
-\usepackage{amsmath, amsthm, amssymb, todonotes}%, showkeys}
+%\usepackage{amsmath, amsthm, amssymb}
+\usepackage{todonotes}%, showkeys}
 \usepackage[alphabetic]{amsrefs}
@@
 %Geometry
-\usepackage{geometry}
+%\usepackage{geometry}
 % Enumitem
@@
  \begin{equation} \label{eq:intro-snake}
-  \begin{tikzcd}[row sep=20]
+  \begin{tikzcd}[row sep=20, column sep=20]
     0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
@@
 We put it together in Theorem~\ref{thm:snake} of Section~\ref{ssec:snake}, showing that $\TrFrob{G}$
-is surjective with kernel $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$.  Having described the isomorphism classes of objects,
+is surjective with kernel $\Hh^2(\pi_0(\bG), \EEx)^{\Weil{}}$.  Having described the isomorphism classes of objects,
 in Theorem~\ref{thm:autornaught} of Section~\ref{ssec:qcmor} we show that
@@
 and that every morphism is either trivial or an isomorphism.  We conclude in Section~\ref{sec:basechange} by
-giving functorial versions of the restriction and norm homomorphisms $\Hom(G(k'),\EEx) \to \Hom(G(k),\EEx)$ and $\Hom(G(k),\EEx) \to \Hom(G(k'),\EEx)$
+giving functorial versions of the restriction and norm homomorphisms 
+of character groups
+%$\Hom(G(k'),\EEx) \to \Hom(G(k),\EEx)$ and $\Hom(G(k),\EEx) \to \Hom(G(k'),\EEx)$
 and describing how quasicharacter sheaves behave under Weil restriction.
@@
 
-The category $\QC(G)$ of quasicharacter sheaves on $G$ is a rigid monoidal category
+Category $\QC(G)$ is a rigid monoidal category
 \cite{etingof:09a}*{\S1.10} under the tensor product
@@
 
-In this section we introduce two tools which will help us understand isomorphism classes of objects in $\QC(G)$: the trace of Frobenius map $\QCiso{G} \to G(k)^*$ and the pullback functor $\QC(G) \to \QC(H)$ associated to a morphism $H \to G$.
+In this section we introduce two tools which will help us understand isomorphism classes of objects in $\QC(G)$: the map $\QCiso{G} \to G(k)^*$ given by trace of Frobenius and the pullback functor $\QC(G) \to \QC(H)$ associated to a morphism $H \to G$.
 
@@
 Now suppose $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$.
-The isomorphism $\mu : \bm^* \gqcs{L} \to \LxL$ together with
+The isomorphism $\mu : \bm^* \gqcs{L} \to \gqcs{L} \boxtimes\gqcs{L} $ together with
 \ref{QC.3} guarantee
@@
 \begin{proof}
-The only non-trivial part of the proof is to show that $\boxtimes : \QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)$
+The only non-trivial part of the proof is to show that 
+\[\boxtimes
+ : \QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)
+ \]
 is essentially surjective, so we will only address that point here.

### 2014-08-24 crelle-dictionary.tex
Took out the Homs I had added to the introduction.

@@
 Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
-this paper extends Deligne's function--sheaf dictionary for characters of connected commutative algebraic groups over finite fields to characters of smooth commutative group schemes over finite fields.
+this paper extends Deligne's function--sheaf dictionary to smooth commutative group schemes over finite fields.
 \end{abstract}
@@
 \subsection{Overview}
+
+Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
+this paper extends Deligne's function--sheaf dictionary to smooth commutative group schemes over finite fields.
 
@@
 
-If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, however, then one must keep track of the choice of \eqref{introbox}, leading to a category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is an isomorphism of local systems on $G\times G$.
-If the component group scheme $\pi_0(G)$ (which is an \'etale commutative group scheme over $\FF_q$) is not cyclic, then while the trace of Frobenius provides a surjection from isomorphism classes in the category of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\FF_q)$, that group homomorphism need not be injective.
-In other words, if $G$ is a commutative algebraic group over $\FF_q$ which is not connected, then every character may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely. 
-While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious since if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\FF_q)$ then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
+If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, however, then one must keep track of the choice of \eqref{introbox}, leading to the category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is an isomorphism of local systems on $G\times G$.
+If the component group scheme $\pi_0(G)$ is not cyclic, then the trace of Frobenius provides an epimorphism from isomorphism classes of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\FF_q)$, but that group homomorphism need not be injective.
+Every character of $G(\Fq)$ may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely. 
+While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious: if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\FF_q)$ then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
 
@@
 One can show, using the Kunneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
-The fact that $T_G$ is not an isomorphism should not be too troubling because if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
-Here we also see the importance of working with Weil sheaves; for example, without them, we would not be able to geometrize the character of the \'etale group scheme $\ZZ$ over $\FF_q$ given by $1\mapsto \ell$, for example.
+The fact that $T_G$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
+Here we also see the importance of working with Weil sheaves; without them, we would not be able to geometrize the character of the \'etale group scheme $\ZZ$ over $\FF_q$ given by $1\mapsto \ell$, for example.
 
@@
 \end{equation}
-We remark that $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ is non-trivial even for some commutative algebraic groups.
+%We remark that $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ is non-trivial even for some commutative algebraic groups.
 We also illuminate the nature of the category $\QC(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing that 
@@
 In this paper we show that quasicharacters of $X_K$ are geometrized and categorified by quasicharacter sheaves on the
-Greenberg transform $\Gr_R(X)$ of the N\'eron model $X$; although not locally of finite type, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and also a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
+Greenberg transform $\Gr_R(X)$ of the N\'eron model $X$.
+Although not locally of finite type, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and also a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
 This allows us to adapt our work on quasicharacter sheaves to construct a category $\QC(X_K)$ of quasicharacter sheaves for $X_K$, which are certain sheaves on $\Gr_R(X)\times_{\Spec{\Fq}} \Spec{\bFq}$, with extra structure.
-The ability to generalize the function--sheaf dictionary to non-connected group schemes, of which the component group of the special fibre of the N\'eron model $X$ is an important example, plays a crucial role in this application
-since these group schemes are not connected in general.
-
-Specializing to the case when $X_K$ is an algebraic tori $T$ over $K$, and writing $\underline{T}$ for the Neron model $X$ in this case, this paper gives a canonical short exact sequence 
+The ability to generalize the function--sheaf dictionary to non-connected group schemes, of which the component group of the special fibre of the N\'eron model $X$ is an important example, plays a crucial role in this application.
+%since these group schemes are not connected in general.
+
+Specializing to the case when $X_K$ is an algebraic torus $T$ over $K$, and writing $\underline{T}$ for the Neron model $X$ in this case, this paper gives a canonical short exact sequence 
 \begin{equation}
@@
 where $\Hom_\text{qc}(T(K),\EEx)$ denoted the group of quasicharacters of $T(K)$.
-We further show that automorphism groups in the $\QC(\Gr_R(\underline{T}))$ are given, for every quasicharacter sheaf $\qcs{F}$ on $\Gr_R(X)$, by
+We further show that automorphism groups in the $\QC(T)$ are given, for every quasicharacter sheaf $\qcs{F}$ for $T$, by
 \begin{equation}
@@
 A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group.
-Indeed, he has suggested to us that our category of quasicharacters for $T$ may be tied to characters of all the pure rational forms of $T$.
+Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to characters of all the pure rational forms of $T$.
 
@@
 We close the introduction with an overview of the structure of this paper.
-After setting some basic notation in Section~\ref{sec:notation},
+After setting some basic notation in Section~\ref{sec:notation} 
+such as $A^*\ceq \Hom(A,\EEx)$ for any group $A$, 
 in Section~\ref{sec:category} we define the category of quasicharacter sheaves.
-Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism $\TrFrob{G} : \QCiso{G} \to \Hom(G(\FF_q), \EEx)$.
+Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism $\TrFrob{G} : \QCiso{G} \to G(\FF_q)^*$.
 We also define pullbacks of quasicharacter sheaves along morphisms of group schemes.  Applying pullbacks to the component group
@@
     & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
-    0 \rar & \Hom(\pi_0(G)(\FF_q),\EEx) \rar & \Hom(G(\Fq),\EEx) \rar & \Hom(G^0(\FF_q),\EEx) \rar & 0,
+    0 \rar & \pi_0(G)(\FF_q)^* \rar & G(\Fq)^* \rar & G^0(\FF_q)^* \rar & 0,
   \end{tikzcd}
@@
 of character groups
-%$\Hom(G(k'),\EEx) \to \Hom(G(k),\EEx)$ and $\Hom(G(k),\EEx) \to \Hom(G(k'),\EEx)$
+$G(k')^* \to G(k)^*$ and $G(k)^* \to G(k')^*$
 and describing how quasicharacter sheaves behave under Weil restriction.

### 2014-08-24 crelle-dictionary.tex
Fixed most of the spacing issues.

@@
 Now suppose $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$.
-The isomorphism $\mu : \bm^* \gqcs{L} \to \gqcs{L} \boxtimes\gqcs{L} $ together with
+Then $\bm^* \gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L} $ together with
 \ref{QC.3} guarantee
@@
 \end{equation}
-We have already observed that $m\circ f = \id_G$, so $f^* m^* \gqcs{L} = \gqcs{L}$.
-On the other hand, $f^*(\gqcs{L}\boxtimes \gqcs{L}) = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L}$
-by definition.  Since $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L}$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L}$
-we get that $f^*(\gqcs{L}\boxtimes \gqcs{L}) = \gqcs{L}_1\boxtimes \gqcs{L}_2$.
+We have already seen that $m\circ f = \id_G$, so $f^* m^* \gqcs{L} = \gqcs{L}$.  
+Since $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L} = r_1^* \gqcs{L}_1$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L} = r_2^*\gqcs{L}_2$,
+we have 
+\[
+f^*(\gqcs{L}\boxtimes \gqcs{L})  = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L} = \gqcs{L}_1\boxtimes \gqcs{L}_2.
+\]
 It follows that \eqref{eq:fm} gives an isomorphism $\gqcs{L} \to  \gqcs{L}_1\boxtimes \gqcs{L}_2$.
@@
 \begin{proof}
-We first show that $S_G$ is injective.  Suppose $\qcs{L} \in \QCiso{G}$ with $S_G(\qcs{L}) = [\alpha \oplus \beta] = 0$,
+%We first show that $S_G$ is injective.  
+Suppose $\qcs{L} \in \QCiso{G}$ with $S_G(\qcs{L}) = [\alpha \oplus \beta] = 0$,
 so that $\alpha \oplus \beta = d\rho$ for some $\rho \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
@@
 \begin{proposition}\label{prop:BG}
-Extension of scalars defines a full and faithful functor $B_G : \bQC(G) \to \QC(G)$.
+Extension of scalars defines a full and faithful functor
+\[
+B_G : \bQC(G) \to \QC(G).
+\]
 \end{proposition}
@@
 \begin{lemma}\label{lem:bounded_connected}
-If $G$ is a connected commutative algebraic group over $\Fq$ then $B_G : \bQC(G) \to \QC(G)$ is an equivalence of categories.
+If $G$ is a connected commutative algebraic group over $\Fq$ then 
+\[
+B_G : \bQC(G) \to \QC(G)
+\]
+ is an equivalence of categories.
 \end{lemma}
@@
   \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}},
-  $
+ \[
   b_{G\times G}^* : \Hom(m^*\qcs{E},\qcs{E}\boxtimes\qcs{E}) \to \Hom({\bar m}^*\gqcs{L},\gqcs{L}\boxtimes\gqcs{L})
-  $
+ \]
   is a bijection
@@
   \]
-  fitting into the long exact sequence derived from applying
-  the functor $\Hom(\mbox{---}, A(\bFq))$ to $G^0(\bFq) \to G(\bFq) \to \pi_0(G)(\bFq)$:
-  \[
-  \Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[\Weil{}]}(\pi_0(G)(\bFq), A(\bFq)).
-  \]
+  fitting into the long exact sequence 
+  \[
+  \Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[\Weil{}]}(\pi_0(G)(\bFq), A(\bFq))
+  \]
+  derived from applying
+  the functor $\Hom(\mbox{---}, A(\bFq))$ to $G^0(\bFq) \to G(\bFq) \to \pi_0(G)(\bFq)$.
   Since $\Weil{} \cong \ZZ$ has cohomological dimension $1$ \cite{brown:CohomologyGrps}*{Ex. 4.3},
@@
   \begin{tikzcd}[row sep=20]
-  & 0 \arrow{d} & 0 \arrow{d} & 0\arrow{d} \\
+%  & 0 \arrow{d} & 0 \arrow{d} & 0\arrow{d} \\
     0 \arrow[dashed]{r} & \ker \TrFrob{\pi_0(G)} \arrow[dashed]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dashed]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
@@
     & \arrow{d} G(\Fq)^* \rar & G^0(\Fq)^* \rar \dar & 0\\
-    & \arrow{d} \coker \TrFrob{\pi_0(G)} =0 \arrow[dashed]{r} & \arrow{d} \coker \TrFrob{G} \arrow[dashed]{r} &  \arrow{d} \coker \TrFrob{G^0} =0 & \\
-      & 0 & 0 & 0 \\
+   &  \coker \TrFrob{\pi_0(G)} =0 \arrow[dashed]{r} & \coker \TrFrob{G} \arrow[dashed]{r} & \coker \TrFrob{G^0} =0 & 
+%    & \arrow{d} \coker \TrFrob{\pi_0(G)} =0 \arrow[dashed]{r} & \arrow{d} \coker \TrFrob{G} \arrow[dashed]{r} &  \arrow{d} \coker \TrFrob{G^0} =0 & \\
+%      & 0 & 0 & 0 \\
   \end{tikzcd}
@@
 \]
-be the functor obtained by pullback along the canonical closed immersion of $k$-schemes
-$\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$
-\cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}.
+be the functor obtained by pullback along the canonical closed immersion 
+$\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$ of $k$-schemes
+given by \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}.
 The following diagram commutes:
@@
 If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$, we define
-a quasicharacter sheaf $\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
+%a quasicharacter sheaf 
+$\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
 $G_{k'}$ of $G$ to $k'$ by setting
@@
 \]
-Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$ and write the image of $v$ under the
-bottom map as $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$
+Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$ and write $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$ for the image of $v$ under the
+bottom map,
 for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{QC.2}, $v$ maps to
@@
 Let $K$, $R$ and $R_n$ be as above.
-Set $S = \Spec{R}$ and $S_n = \Spec{R_n}$, for every non-negative integer $n$;
-note that $S_0 = \Spec{\Fq}$ is the special fibre of $S$.
-
 We will need the Greenberg functor, which provides
@@
 \]
-for the functor produced by composing pullback along $S_n \to S$ with the Greenberg functor. 
+for the functor produced by composing pullback along $\Spec{R_n} \to \Spec{R}$ with the Greenberg functor. 
 This functor also respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components, and
@@
 \]
-canonically, for any $X$ lft over $S$.
+canonically, for any $X$ lft over $R$.
 
@@
 Crucially, $\varrho^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
-This observation is key to the proof that, for any $X$ lft over $S$, the projective limit 
+This observation is key to the proof that, for any $X$ lft over $R$, the projective limit 
 \[
@@
 Let $X_K \in \mathcal{N}_K$ and $X$ be as above.
-
-For every non-negative integer $n$, $\Gr^R_n(X)$ is {\it smooth} commutative group scheme over $\Fq$ with component group scheme
-$\pi_0(\Gr^R_n(X))= \pi_0(X) \times_S S_0$
+Set $S = \Spec{R}$ and $S_n = \Spec{R_n}$;
+% for every non-negative integer $n$;
+note that $S_0 = \Spec{\Fq}$ is the special fibre of $S$.
+
+For every non-negative integer $n$, $\Gr^R_n(X)$ is {\it smooth} commutative group scheme over $S_0$ with component group scheme
+%$\pi_0(\Gr^R_n(X))= 
+$\pi_0(X) \times_S S_0$
 and $\Fq$-rational points
 $
-\Gr^R_N(X)(\Fq)\iso X(R_n),
+%\Gr^R_N(X)(\Fq)\iso 
+X(R_n),
 $
@@
 %
-The Greenberg transform $\Gr_R(X)$ of $X$ is still a commutative group scheme over $\Fq$ with component group scheme
+The Greenberg transform $\Gr_R(X)$ of $X$ is a commutative group scheme over $\Fq$ with component group scheme
 $
-\pi_0(\Gr_R(X))= \pi_0(X) \times_S S_0
+%\pi_0(\Gr_R(X))= 
+\pi_0(X) \times_S S_0
 $
-and its $\Fq$-rational points are given by
+and $\Fq$-rational points 
 $
-\Gr_R(X)(\Fq)\iso X_K(K),
+%\Gr_R(X)(\Fq)\iso 
+X_K(K),
 $
-canonically, but $\Gr_R(X)$ is not locally of finite type, and therefore not smooth.
-
+canonically, but $\Gr_R(X)$ is not locally of finite type, therefore not locally of finite presentation, and therefore not smooth.
 %
-Moreover, the morphism of $\Fq$-schemes $\varrho^R_n(X) : \Gr_R(X) \to \Gr^R_n(N)$ induces a functor
+The morphism of $\Fq$-schemes $\varrho^R_n(X) : \Gr_R(X) \to \Gr^R_n(N)$ induces a functor
 \[
@@
 We now define a category which will geometrize quasicharacters of $X_K(K)$.
-Although $\Gr_R(X)$ is not locally of finite type, and thus not smooth, we begin by considering the rigid monoidal category $\QC(\Gr_R(X))$ defined in Section~\ref{sec:category}, without insisting that the commutative group scheme is smooth.
+We begin by considering the rigid monoidal category $\QC(\Gr_R(X))$ defined in Section~\ref{sec:category} without insisting that the commutative group scheme is smooth.
 
@@
 quasicharacter sheaves for $X_K$}.
+The evil category of quasicharacter sheaves for $X_K$ is rigid monoidal in the obvious way.
 \end{definition}
-
-The evil category of quasicharacter sheaves for $X_K$ is rigid monoidal in the obvious way.
 
@@
 Suppose $m$ and $m'$ are non-negative integers such that 
-\[
+$
 R_m \iso R'_{m'},
-\]
+$
 in which case $K$ and $K'$ are said to be $m$-close, and

### 2014-08-24 crelle-dictionary.tex
Minor changes, mostly.

@@
 
-\title[The function--sheaf dictionary]{The function--sheaf dictionary for smooth commutative group schemes over finite fields}
+\title[The function-sheaf dictionary for smooth commutative group schemes]{The function-sheaf dictionary for smooth commutative group schemes over finite fields}
 
@@
 
-\contact{Department of Mathematics and Statistics, University of Calgary, street, zip code, city, country}{cunning@math.ucalgary.ca}
-\contact{Pacific Institute for the Mathematical Sciences, University of Calgary, street, zip code, city, country}{roed.math@gmail.com}
+\contact{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive, T2N 1N4, Calgary, Canada}{cunning@math.ucalgary.ca}
+\contact{Pacific Institute for the Mathematical Sciences, University of Calgary, 2500 University Drive, T2N 1N4, Calgary, Canada}{roed.math@gmail.com}
 
 %\subjclass[2010]{14F05 (primary), 14L15 (secondary)}
-%\keywords{function--sheaf dictionary, trace of Frobenius, geometrization, categorification, quasicharacters, quasicharacter sheaves, smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor}
-
-\researchsupported{We gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
-and the National Science and Engineering Research Council,
-as well the hospitality of the Banff International Research Station during our week-long stay in May 2012.}
+%\keywords{function-sheaf dictionary, trace of Frobenius, geometrization, categorification, quasicharacters, quasicharacter sheaves, smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor}
+
+\researchsupported{We gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences and the National Science and Engineering Research Council (Canada), as well the hospitality of the Banff International Research Station during a Research in Teams program.}
 
@@
 \usepackage{todonotes}%, showkeys}
-\usepackage[alphabetic]{amsrefs}
+\usepackage{amsrefs}
 % Fonts
@@
 \usepackage{hyperref}
+
+%%%%%%%%%%%%%%% COUNTER %%%%%%%%%%%%%%%
 \setcounter{section}{-1}
@@
 \newcommand{\OK}{\mathcal{O}_K}
-\newcommand{\pK}{\mathfrak{p}_K}
-\newcommand{\OKp}{\mathcal{O}_{K'}}
-\newcommand{\pKp}{\mathfrak{p}_{K'}}
+%\newcommand{\pK}{\mathfrak{p}_K}
+%\newcommand{\OKp}{\mathcal{O}_{K'}}
+%\newcommand{\pKp}{\mathfrak{p}_{K'}}
 \newcommand{\OL}{\mathcal{O}_L}
 \newcommand{\OO}[1]{\mathcal{O}_{#1}}
-\newcommand{\Zp}{\mathbb{Z}_p}
-\newcommand{\Qp}{\mathbb{Q}_p}
+%\newcommand{\Zp}{\mathbb{Z}_p}
+%\newcommand{\Qp}{\mathbb{Q}_p}
 \newcommand{\bFq}{\bar{k}}
@@
 \newcommand{\Fqm}{k_m}
-\newcommand{\WW}{\mathbb{W}}
+%\newcommand{\WW}{\mathbb{W}}
 \newcommand{\EEx}{\EE^\times}
@@
 %%%%%%%%%%%%%%% ALGEBRAIC GROUPS %%%%%%%%%%%%%%%
-\newcommand{\mathswab}[1]{\operatorname{\textswab{#1}}}
+%\newcommand{\mathswab}[1]{\operatorname{\textswab{#1}}}
 \newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
-\newcommand{\GN}[1]{\mathswab{#1}}
-\newcommand{\bGN}[1]{{\bar{\mathswab{#1}}}}
-\newcommand{\TT}{\underline{T}}
-\newcommand{\TL}{\underline{T_L}}
-\newcommand{\TTp}{\underline{T}'}
+%\newcommand{\GN}[1]{\mathswab{#1}}
+%\newcommand{\bGN}[1]{{\bar{\mathswab{#1}}}}
+%\newcommand{\TT}{\underline{T}}
+%\newcommand{\TL}{\underline{T_L}}
+%\newcommand{\TTp}{\underline{T}'}
 \newcommand{\comp}{\Pi} % Component group
@@
 Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
-this paper extends Deligne's function--sheaf dictionary to smooth commutative group schemes over finite fields.
+this paper extends Deligne's function-sheaf dictionary to smooth commutative group schemes over finite fields.
 \end{abstract}
@@
 Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
-this paper extends Deligne's function--sheaf dictionary to smooth commutative group schemes over finite fields.
+this paper extends Deligne's function-sheaf dictionary to smooth commutative group schemes over finite fields.
 
@@
 If one wishes to make a category from this class of local systems, one is led to consider sheaf homorphisms $\qcs{E} \to \qcs{E}'$ which are compatible with particular choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E'}$.
-{\it A priori}, these sheaf homomorphisms do not form a category, but since $G$ is connected, the existence of \eqref{introbox} makes \eqref{introbox} unique; as a consequence, there is no impediment to categorifying the dictionary in this case.
-
-If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, however, then one must keep track of the choice of \eqref{introbox}, leading to the category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is an isomorphism of local systems on $G\times G$.
-If the component group scheme $\pi_0(G)$ is not cyclic, then the trace of Frobenius provides an epimorphism from isomorphism classes of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\FF_q)$, but that group homomorphism need not be injective.
-Every character of $G(\Fq)$ may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely. 
+{\it A priori}, these sheaf homomorphisms do not form a category, but since $G$ is connected, the existence of the isomorphism \eqref{introbox} for $\qcs{E}$ makes it unique; as a consequence, there is no impediment to categorifying the dictionary in this case.
+
+If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, however, then the isomorphism \eqref{introbox} need not be unique, so one must keep track of the choice of \eqref{introbox}.
+This leads to the category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is a chosen isomorphism of local systems on $G\times G$.
+%If the component group scheme $\pi_0(G)$ is not cyclic, then 
+In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\FF_q)$, but that group homomorphism need not be injective; consequently,
+every character of $G(\Fq)$ may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely in the category of pairs. 
 While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious: if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\FF_q)$ then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
 
-In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$ we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system  -- a local system on ${\bar G} := G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ -- while retaining the extra structure $\mu_\qcs{E}$.
-Let $\Weil{} \subset \Gal({\bar\FF}_q/\FF_q)$ be the Weil group for $\FF_q$; let $\Frob{G} : \bG \to \bG$ be the Frobenius automorphism for $\bG$.
-In this way we are lead to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way.
+In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$ we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\qcs{E}$.
+Set ${\bar G} := G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ and let $\Frob{G} : \bG \to \bG$ be the Frobenius automorphism for $\bG$.
+In this way we are lead to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$ where $\gqcs{L}$ is a rank-one local system on ${\bar G}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way.
 Morphism in $\QC(G)$ are then homomorphisms of Weil sheaves which are compatible with the extra structure.
@@
 \end{equation}
-provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$, canonically.
+provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$, canonically, where $\Weil{} \subset \Gal({\bar\FF}_q/\FF_q)$ is the Weil group for $\FF_q$,
 One can show, using the Kunneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
 The fact that $T_G$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
-Here we also see the importance of working with Weil sheaves; without them, we would not be able to geometrize the character of the \'etale group scheme $\ZZ$ over $\FF_q$ given by $1\mapsto \ell$, for example.
+Here we also see the importance of working with Weil sheaves; without them, we would not be able to geometrize the character of the \'etale group scheme $\ZZ$ 
+with image $\ell^{\ZZ}$, for example. %given by $1\mapsto \ell$, for example.
 
@@
 
-As indicated above, our interest in the function--sheaf dictionary for smooth commutative group schemes over finite fields comes from an application to $p$-adic representation theory. 
-We found, however, that this application applies to all local fields $K$ with finite residue field $\Fq$ and all connected commutative algebraic groups $X_K$ over $K$ that do not contain a subgroup of type $\mathbb{G}_\text{a}$, such as Abelian varieties, unipotent $K$-wound groups, and of course, algebraic tori.
+As indicated above, our interest in the function-sheaf dictionary for smooth commutative group schemes over finite fields comes from an application to $p$-adic representation theory. 
+We found, however, that this application applies to all local fields $K$ with finite residue field $\Fq$ and all connected commutative algebraic groups $X_K$ over $K$ that do not contain a subgroup of type $\mathbb{G}_\text{a}$, such as abelian varieties, unipotent $K$-wound groups, and of course, algebraic tori.
 Such algebraic groups $X_K$ always admit a Neron model $X$ over $R$, the ring of integers of $K$.
@@
 This allows us to adapt our work on quasicharacter sheaves to construct a category $\QC(X_K)$ of quasicharacter sheaves for $X_K$, which are certain sheaves on $\Gr_R(X)\times_{\Spec{\Fq}} \Spec{\bFq}$, with extra structure.
-The ability to generalize the function--sheaf dictionary to non-connected group schemes, of which the component group of the special fibre of the N\'eron model $X$ is an important example, plays a crucial role in this application.
+The ability to generalize the function-sheaf dictionary to non-connected group schemes, of which the component group of the special fibre of the N\'eron model $X$ is an important example, plays a crucial role in this application.
 %since these group schemes are not connected in general.
@@
 After setting some basic notation in Section~\ref{sec:notation} 
-such as $A^*\ceq \Hom(A,\EEx)$ for any group $A$, 
-in Section~\ref{sec:category} we define the category of quasicharacter sheaves.
+such as $A^*\ceq \Hom(A,\EEx)$ for any group $A$ and using $G$ for a commutative group scheme over $\FF_q$,
+in Section~\ref{sec:category} we define the category of quasicharacter sheaves on $G$.
 Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism $\TrFrob{G} : \QCiso{G} \to G(\FF_q)^*$.
@@
 \cite{etingof:09a}*{\S1.10} under the tensor product
-$\qcs{L} \otimes \qcs{L'} \ceq (\gqcs{L}\otimes\gqcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
+$\qcs{L} \otimes \qcs{L'}$ defined by $(\gqcs{L}\otimes\gqcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
 with duals given by applying the sheaf hom functor
@@
 %is an \'etale group scheme \cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
-%However, the function--sheaf dictionary is substantially different in the two cases.
+%However, the function-sheaf dictionary is substantially different in the two cases.
 %To see why, we begin by specializing the definition of quasicharacter sheaves to the case
@@
  Since the functor $B_G : \bQC(G) \to \QC(G)$ is full and faithful, $\Aut(\qcs{L}) = \Aut(\qcs{E})$.
-From here, Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields \citelist{\cite{deligne:SGA4.5}*{Sommes trig.}, \cite{laumon:87a}*{1.1.3}}  gives us all we need, as we briefly recall.
+From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields \citelist{\cite{deligne:SGA4.5}*{Sommes trig.}, \cite{laumon:87a}*{1.1.3}}  gives us all we need, as we briefly recall.
 The key observation is that, by \'etale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
@@
 We have also just seen that if the character of $\Lang^*\qcs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\qcs{E} : \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ which is part of the data that determines a quasicharacter sheaf on $G$.
-That leads to a perspective on the function--sheaf dictionary common in the literature in which one considers $1$-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$; see \cite{kamgarpour:09a}*{Intro}, for example.
+That leads to a perspective on the function-sheaf dictionary common in the literature in which one considers $1$-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$; see \cite{kamgarpour:09a}*{Intro}, for example.
 As a slight variation, one may also consider $1$-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
@@
 Indeed, Proposition~\ref{prop:etale-iso} shows that when $G$ is \'etale, $\Hh^2(\bG,\EEx)^{\Frob{}}$ measures the possibilities for $\mu'$.
-In other words, the common perspective on the function--sheaf dictionary leads only, and exactly, to the part of category of quasicharacter sheaves that is {\it completely invisible} to the trace of Frobenius!
+In other words, the common perspective on the function-sheaf dictionary leads only, and exactly, to the part of category of quasicharacter sheaves that is {\it completely invisible} to the trace of Frobenius!
 
@@
 
-\section{The function--sheaf dictionary for smooth commutative group schemes}\label{sec:main}
+\section{The function-sheaf dictionary for smooth commutative group schemes}\label{sec:main}
 
@@
 
-\section{Applications}\label{sec:applications}% to algebraic tori and Abelian varieties over \texorpdfstring{$p$}{p}-adic fields}
+\section{Applications}\label{sec:applications}% to algebraic tori and abelian varieties over \texorpdfstring{$p$}{p}-adic fields}
 
@@
 These algebraic groups over $K$ form an additive category, denoted by $\mathcal{N}_K$ below, in a natural way, as a full subcategory of connected commutative algebraic groups over $K$.
-This category includes algebraic tori over $K$ and Abelian varieties over $K$ unipotent K-wound groups.
+This category includes algebraic tori over $K$ and abelian varieties over $K$ unipotent K-wound groups.
 
@@
 as in Lemma~\ref{lem:pullback}.
-This functor is faithful, so we may view $\QC(\Gr^R_n(X))$ as a subcategory of $\QC(\Gr_R(X))$.
+%This functor is faithful, so we may view $\QC(\Gr^R_n(X))$ as a subcategory of $\QC(\Gr_R(X))$.
 
@@
 \begin{definition}
-We construct an evil subcategory $\QC(X_K)$ of $\QC(\Gr_R(X))$ as follows:
+Let $\QC(X_K)$ be the following evil subcategory of $\QC(\Gr_R(X))$:
 objects in $\QC(X_K)$ are the $\ell$-adic sheaves $\varrho^R_n(X)^*\qcs{L}$, for $n\in \NN$ and $\qcs{L} \in \QC(\Gr^R_n(X))$; morphism from $\varrho^R_n(X)^*\qcs{L}$ to $\varrho^R_m(X)^*\qcs{L}'$ are $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\qcs{L},\qcs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\qcs{L},\varrho^R_{m\leq n}(X)^*\qcs{L}')$ when $m\leq n$.
@@
 Let $K$ and $R$ be as above. 
+\begin{enumerate}
+\item[(0)]
 The trace of Frobenius provides a natural transformation between the additive functors
@@
 \]
-where $X$ is a N\'eron model for $X_K$, as functors from $\mathcal{N}_K$ to the category of abelian groups. 
+as functors from $\mathcal{N}_K$ to the category of abelian groups.
+\end{enumerate} 
 Regarding this natural transformation, for every $X_K \in \mathcal{N}_K$ with N\'eron model $X$:
@@
 \]
-as functors from $\mathcal{N}_K$ to Abelian groups.
+as functors from $\mathcal{N}_K$ to abelian groups.
 \item[(1)] There is a canonical short exact sequence of abelian groups 
@@
 We thank Joseph Bernstein for suggesting a connection between our category of quasicharacter sheaves on $G$ and his sheaves on the stacky classifying space of $G$.
-We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and for their help in the proof of Proposition~\ref{prop:wrK}.
+We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and drawing our attention to their result on Weil restriction and the Greenberg transform.
 }

### 2014-08-24 crelle-dictionary.tex
New references, new citations

@@
 In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$ we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\qcs{E}$.
-Set ${\bar G} := G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ and let $\Frob{G} : \bG \to \bG$ be the Frobenius automorphism for $\bG$.
-In this way we are lead to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$ where $\gqcs{L}$ is a rank-one local system on ${\bar G}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way.
+In this way we are lead to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$ where $\gqcs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way.
 Morphism in $\QC(G)$ are then homomorphisms of Weil sheaves which are compatible with the extra structure.
@@
 %\todo{Maybe move this from the introduction into the body of the paper somewhere.}
-In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization of complete Langlands parameters for $p$-adic groups as equivariant perverse sheaves on Vogan varieties and, in the process, is lead to study the representations of all the pure rational forms of the $p$-adic group simultaneously.
-A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group.
+In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization of complete Langlands parameters for $p$-adic groups 
+%as equivariant perverse sheaves on Vogan varieties 
+and, in the process, is lead to study the representations of all the pure rational forms of the $p$-adic group simultaneously.
+A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group \cite{bernstein:vogan_conference}.
 Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to characters of all the pure rational forms of $T$.
@@
 After setting some basic notation in Section~\ref{sec:notation} 
-such as $A^*\ceq \Hom(A,\EEx)$ for any group $A$ and using $G$ for a commutative group scheme over $\FF_q$,
+such as $A^*\ceq \Hom(A,\EEx)$ for any group $A$ and using $G$ for a smooth commutative group scheme over $\FF_q$,
 in Section~\ref{sec:category} we define the category of quasicharacter sheaves on $G$.
@@
 
-The latter two claims follow from tracing through the definition of latter pages in the spectral sequence; see Vakil \cite{} for example \todo{update reference}.
+The latter two claims follow from tracing through the definition of latter pages in the spectral sequence; see \cite{Vakil:spectral_sequences} following \cite{Weibel:Homological_Algebra}*{Ch 5}, for example.
 \end{proof}
@@
  from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
- is full and faithful \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}}.
+ is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} or \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}.
  This functor preserves local constancy, so takes local systems to local systems.
@@
 
-  Since $b_G^*$ is full and faithful
-  \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}},
+  Since $b_{G\times G}^*$ is full and faithful (again, see
+\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} or \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}),
  \[
@@
  Since the functor $B_G : \bQC(G) \to \QC(G)$ is full and faithful, $\Aut(\qcs{L}) = \Aut(\qcs{E})$.
-From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields \citelist{\cite{deligne:SGA4.5}*{Sommes trig.}, \cite{laumon:87a}*{1.1.3}}  gives us all we need, as we briefly recall.
+From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields, as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3},  gives us all we need, as we briefly recall.
 The key observation is that, by \'etale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
@@
 See \cite{bertrapelle-gonzales:Greenberg} for the definition and fundamental properties of the Greenberg functor as we use it; other important references include
-\citelist{
 \cite{greenberg:61}, \cite{greenberg:63a},
@@
 \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6},
-\cite{nicaise-sebag:motivicSerre}*{\S 2.2}
-}.
+\cite{nicaise-sebag:motivicSerre}*{\S 2.2}.
 This functor respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components.

### 2014-08-24 crelle-dictionary.tex
Use of Hom harmonized; improved wording in the introduction.

@@
 The fact that $T_G$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
-Here we also see the importance of working with Weil sheaves; without them, we would not be able to geometrize the character of the \'etale group scheme $\ZZ$ 
-with image $\ell^{\ZZ}$, for example. %given by $1\mapsto \ell$, for example.
+Here we also see the importance of working with Weil sheaves; without them, we would not be able to geometrize any character of the \'etale group scheme $\ZZ$ 
+with non-compact image, such as $\ell^{\ZZ}$.
 
@@
 After setting some basic notation in Section~\ref{sec:notation} 
-such as $A^*\ceq \Hom(A,\EEx)$ for any group $A$ and using $G$ for a smooth commutative group scheme over $\FF_q$,
+such as $A^*\ceq \Hom(A,\EEx)$ for any abelian group $A$ and using $G$ for a smooth commutative group scheme over $\FF_q$,
 in Section~\ref{sec:category} we define the category of quasicharacter sheaves on $G$.
@@
 
-For any group $A$, we will write $A^*$ for the dual group $\Hom_\text{grp}(A, \EEx)$.
+For any abelian group $A$, we will write $A^*$ for the dual group $\Hom(A, \EEx)$.
 
@@
   is exact since $\Hh^1(\Fq,G^0) =0$ by Lemma~\ref{lem:G0alg-grp} and Lang's theorem on connected algebraic groups over finite fields \cite{lang:56a}.
-  Since $\EEx$ is divisible, $\Hom_\text{Ab}(\ - \ ,\EEx)$ is exact and thus the dual sequence of
+  Since $\EEx$ is divisible, $\Hom(\ - \ ,\EEx)$ is exact and thus the dual sequence of
   character groups is also exact.
@@
 Fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the homomorphism $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
-This group homomorphism is clearly injective: if $\rho_x = \id_{\qcs{L}_x}$ for every $x\in \bG$ then $\rho = \id_{\qcs{L}}$.
-Note that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom_\text{cts}(\bG_{\Weil{}},\EEx)$, where $\bG_{\Weil{}}$ is given the topology of the base of the espace \'etal\'e attached to $\gqcs{L}$.
-Since $\ell$ is invertible in $\Fq$, it follows that $\Hom_\text{cts}(\bG_{\Weil{}},\EEx) = \Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
-Note that $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
+This group homomorphism is injective: if $\rho_x = \id_{\qcs{L}_x}$ for every $x\in \bG$ then $\rho = \id_{\qcs{L}}$.
+Note that homomorphisms in the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ are continuous where $\bG_{\Weil{}}$ is given the topology of the base of the espace \'etal\'e attached to $\gqcs{L}$.
+Since $\ell$ is invertible in $\Fq$, it now follows that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
+We also have $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
 To see that $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho^y: \gqcs{L}^y \to \gqcs{L}^y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.

### 2014-08-24 crelle-dictionary.tex
Small changes throughout, including dealing with canonicality

--- 2014-08-24 crelle-dictionary.tex
@@
 % Enumitem
-%\usepackage{enumitem}
+\usepackage{enumitem}
 % TikZ
@@
 \newcommand{\Spec}[1]{{\operatorname{Spec}\hskip-1pt( #1 )}}
+\newcommand{\Sch}[1]{{\left(\operatorname{Sch}_{/#1}\right)}}
 
@@
 
-As Deligne explained in \cite{deligne:SGA4.5}*{Sommes trig.}, if $G$ is a connected commutative algebraic group over $\FF_q$, then the trace of Frobenius provides a perfect dictionary between characters of $G(\FF_q)$ and isomorphism classes of rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which
+As Deligne explained in \cite{deligne:SGA4.5}*{Sommes trig.}, if $G$ is a connected commutative algebraic group over $\FF_q$, then the trace of Frobenius provides a bijection between characters of $G(\FF_q)$ and isomorphism classes of rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which
 \begin{equation}\label{introbox}
@@
 {\it A priori}, these sheaf homomorphisms do not form a category, but since $G$ is connected, the existence of the isomorphism \eqref{introbox} for $\qcs{E}$ makes it unique; as a consequence, there is no impediment to categorifying the dictionary in this case.
-
-If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, however, then the isomorphism \eqref{introbox} need not be unique, so one must keep track of the choice of \eqref{introbox}.
+\todo{clarify}
+
+If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, however, then the isomorphism \eqref{introbox} need not be unique, so one must keep track of the choice.
 This leads to the category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is a chosen isomorphism of local systems on $G\times G$.
@@
 
-In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$ we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\qcs{E}$.
+In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$, we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\qcs{E}$.
 Set ${\bar G} := G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ and let $\Frob{G} : \bG \to \bG$ be the Frobenius automorphism for $\bG$.
-In this way we are lead to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$ where $\gqcs{L}$ is a rank-one local system on ${\bar G}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way.
-Morphism in $\QC(G)$ are then homomorphisms of Weil sheaves which are compatible with the extra structure.
+In this way we are led to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$.
+Objects in $\QC(G)$ are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves satisfying a compatibility condition.
+Morphisms in $\QC(G)$ are then homomorphisms of Weil sheaves which are compatible with the extra structure.
 
@@
 \end{equation}
-provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$, canonically, where $\Weil{} \subset \Gal({\bar\FF}_q/\FF_q)$ is the Weil group for $\FF_q$,
+provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$, where $\Weil{} \subset \Gal({\bar\FF}_q/\FF_q)$ is the Weil group for $\FF_q$.
 One can show, using the Kunneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
@@
 \end{equation}
-The main result of the paper uses this sequence to find $\QCiso{G}$ by situating it in a canonical short exact sequence
+The main result of the paper uses this sequence to find $\QCiso{G}$ by situating it in a short exact sequence
 \begin{equation}
@@
 \end{equation}
-canonically, for all quasicharacter sheaves $\qcs{L}$ on $G$.
+for all quasicharacter sheaves $\qcs{L}$ on $G$.
 
@@
 %\todo{Maybe move this from the introduction into the body of the paper somewhere.}
-In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization of complete Langlands parameters for $p$-adic groups as equivariant perverse sheaves on Vogan varieties and, in the process, is lead to study the representations of all the pure rational forms of the $p$-adic group simultaneously.
+In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization of complete Langlands parameters for $p$-adic groups as equivariant perverse sheaves on Vogan varieties and, in the process, is led to study the representations of all the pure rational forms of the $p$-adic group simultaneously.
 A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group.
@@
 Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
-determines a point geometric point $\bg$ fixed by $\Frob{G}$. 
-Together with the canonical isomorphism $(\Frob{G}^*\gqcs{L})_{\bg} \iso  \gqcs{L}_{\Frob{G}(\bg)}$, in this way the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gqcs{L}_{\bg}$; let $\trace(\phi_{\bg};\gqcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gqcs{L}_{\bg})$ and let $\trFrob{(\gqcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by
+determines a geometric point $\bg$ fixed by $\Frob{G}$. 
+Together with the canonical isomorphism $(\Frob{G}^*\gqcs{L})_{\bg} \iso  \gqcs{L}_{\Frob{G}(\bg)}$, the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gqcs{L}_{\bg}$.
+Let $\trace(\phi_{\bg};\gqcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gqcs{L}_{\bg})$ and let $\trFrob{(\gqcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by 
 \begin{equation}\label{trWeil}
@@
 
-Category $\bQC(G)$ is a rigid monoidal category in the obvious way.
+We put a rigid monoidal structure on $\bQC(G)$ in the same way as for $\QC(G)$.
 
@@
  This functor preserves local constancy, so takes local systems to local systems.
- Set $\mu \ceq b_{G\times G}^*\mu_\qcs{E}$; clearly, this satisfies \ref{QC.2}
+ The isomorphism $\mu \ceq b_{G\times G}^*\mu_\qcs{E}$ satisfies \ref{QC.2}
  with $b_G^*\qcs{E}$ playing the role of $\gqcs{L}$.
@@
 Let $f$, $A$, $V$ and $\psi$ be as above; set $\qcs{E} = (f_! V_H)_\psi$.
-It is clear that $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank one.
+Since $A$ is abelian, $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank one.
 We must show that comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
@@
  Since the functor $B_G : \bQC(G) \to \QC(G)$ is full and faithful, $\Aut(\qcs{L}) = \Aut(\qcs{E})$.
-From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields \citelist{\cite{deligne:SGA4.5}*{Sommes trig.}, \cite{laumon:87a}*{1.1.3}}  gives us all we need, as we briefly recall.
+From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields \citelist{\cite{deligne:SGA4.5}*{Sommes trig.},\cite{laumon:87a}*{1.1.3}} \todo{Fix citelist} gives us all we need, as we briefly recall.
 The key observation is that, by \'etale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
@@
 Let $G$ be a smooth commutative group scheme over $\Fq$.
-%For all quasicharacter sheaves $\qcs{L}$ and $\qcs{L}'$ on $G$, every $\rho \in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism.
-Moreover, 
-\[
-\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx),
-\]
- canonically.
+There is a canonical isomorphism
+\[
+\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx).
+\]
 \end{theorem}
@@
 %For the second, f
-Fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the homomorphism $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
-This group homomorphism is clearly injective: if $\rho_x = \id_{\qcs{L}_x}$ for every $x\in \bG$ then $\rho = \id_{\qcs{L}}$.
+Fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the group homomorphism $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
+This homomorphism is injective because morphisms of sheaves are determined by the linear transformations induced on stalks.  
 Note that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom_\text{cts}(\bG_{\Weil{}},\EEx)$, where $\bG_{\Weil{}}$ is given the topology of the base of the espace \'etal\'e attached to $\gqcs{L}$.
@@
 a functor from the category of schemes 
-over $R_n$, for each $n\in \NN$, to the category of schemes over $\Fq$;
+over $R_n$, for each $n\in \NN$, to the category of schemes over $\Fq$; \todo{font for categories, subscripts on homsets}
 See \cite{bertrapelle-gonzales:Greenberg} for the definition and fundamental properties of the Greenberg functor as we use it; other important references include
@@
 }.
-This functor respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components.
 %
@@
 \[
-\Gr^R_n : \partop{\text{Schemes}}{\text{lft over $R$}} \to \partop{\text{Schemes}}{\text{lft over $\Fq$}}
+\Gr^R_n : \Sch{R} \to \Sch{\Fq}
 \]
 for the functor produced by composing pullback along $\Spec{R_n} \to \Spec{R}$ with the Greenberg functor. 
-This functor also respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components, and
-\[
-\Gr^R_n(X)(\Fq) \iso X(R_n),
-\]
-canonically, for any $X$ lft over $R$.
+This functor respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components.  Moreover, there is a canonical isomorphism
+\[
+\Gr^R_n(X)(\Fq) \iso X(R_n)
+\]
+for any scheme $X$ over $R$.
 
@@
 \]
-The Greenberg transform respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components, and
-\[
-\Gr_R(X)(\Fq) \iso X(R),
-\]
-canonically, for any $X$ lft over $R$.
 
@@
 
-For every non-negative integer $n$, $\Gr^R_n(X)$ is {\it smooth} commutative group scheme over $S_0$ with component group scheme
-%$\pi_0(\Gr^R_n(X))= 
-$\pi_0(X) \times_S S_0$
-and $\Fq$-rational points
-$
-%\Gr^R_N(X)(\Fq)\iso 
-X(R_n),
-$
-canonically.
+For every non-negative integer $n$, $\Gr^R_n(X)$ is a {\it smooth} commutative group scheme over $S_0$
+with component group scheme $\pi_0(X) \times_S S_0$ and $\Fq$-rational points $X(R_n).$
 %
-The Greenberg transform $\Gr_R(X)$ of $X$ is a commutative group scheme over $\Fq$ with component group scheme
-$
-%\pi_0(\Gr_R(X))= 
-\pi_0(X) \times_S S_0
-$
-and $\Fq$-rational points 
-$
-%\Gr_R(X)(\Fq)\iso 
-X_K(K),
-$
-canonically, but $\Gr_R(X)$ is not locally of finite type, therefore not locally of finite presentation, and therefore not smooth.
+The Greenberg transform $\Gr_R(X)$ of $X$ is a commutative group scheme over $\Fq$
+with component group scheme $\pi_0(X) \times_S S_0$
+and $\Fq$-rational points $X_K(K).$
+However, $\Gr_R(X)$ is not locally of finite type and therefore not smooth.
 %
@@
 quasicharacter sheaves for $X_K$}.
-The evil category of quasicharacter sheaves for $X_K$ is rigid monoidal in the obvious way.
+We put a rigid monoidal structure on $\QC(X_K)$ in the same way as for $\QC(G)$ in Section \ref{sec:category}.
 \end{definition}
@@
 \begin{enumerate}
-\item[(0)]
+\item
 The trace of Frobenius provides a natural transformation between the additive functors
@@
 Regarding this natural transformation, for every $X_K \in \mathcal{N}_K$ with N\'eron model $X$:
-\begin{enumerate}
-\item[(1)] there is a canonical short exact sequence of abelian groups 
+\begin{enumerate}[resume]
+\item there is a canonical short exact sequence of abelian groups 
 \[
@@
 \] 
-\item[(2)] for all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
-\item[(3)] for all quasicharacter sheaves $\qcs{F}$ on $\Gr_R(X)$,
-\[
-\Aut(\qcs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx),
-\]
-canonically.
+\item for all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
+\item for all quasicharacter sheaves $\qcs{F}$ on $\Gr_R(X)$ there is a canonical isomorphism
+\[
+\Aut(\qcs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx).
+\]
 \end{enumerate}
@@
 \begin{enumerate}
-\item[(0)] Trace of Frobenius gives a natural transformation from
+\item Trace of Frobenius gives a natural transformation from
 \[
@@
 as functors from $\mathcal{N}_K$ to abelian groups.
-\item[(1)] There is a canonical short exact sequence of abelian groups 
+\item There is a canonical short exact sequence of abelian groups 
 \[
@@
 \] 
-\item[(2)] For all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $\Gr^R_n(X)$ and for every $\rho \in \Hom(\qcs{L},\qcs{L}')$, either $\rho$ is trivial or $\rho$ is an isomorphism.
-\item[(3)] For all quasicharacter sheaves $\qcs{L}$ on $\Gr^R_n(X)$,
-\[
-\Aut(\qcs{L}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx),
-\]
-canonically.
-\end{enumerate}
+\item For all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $\Gr^R_n(X)$ and for every $\rho \in \Hom(\qcs{L},\qcs{L}')$, either $\rho$ is trivial or $\rho$ is an isomorphism.
+\item For all quasicharacter sheaves $\qcs{L}$ on $\Gr^R_n(X)$ there is a canonical isomorphism
+\[
+\Aut(\qcs{L}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx).
+\]
+\end{enumerate} \todo{move to a lemma?}
 So Theorem~\ref{thm:QCXK} now follows from the fact that each $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(X_K)$ and the observation that $\QC(X_K)$ a `union' of the subcategories $\QC(\Gr^R_n(X))$ in $\QC(\Gr_R(X))$.

### 2014-08-24 crelle-dictionary.tex

@@
 In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$, we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\qcs{E}$.
-Set ${\bar G} := G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ and let $\Frob{G} : \bG \to \bG$ be the Frobenius automorphism for $\bG$.
 In this way we are led to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$.
-Objects in $\QC(G)$ are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves satisfying a compatibility condition.
+Objects in $\QC(G)$ are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves satisfying a certain compatibility condition.
 Morphisms in $\QC(G)$ are then homomorphisms of Weil sheaves which are compatible with the extra structure.
@@
 %\todo{Maybe move this from the introduction into the body of the paper somewhere.}
-In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization of complete Langlands parameters for $p$-adic groups as equivariant perverse sheaves on Vogan varieties and, in the process, is led to study the representations of all the pure rational forms of the $p$-adic group simultaneously.
-A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group.
+In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization of complete Langlands parameters for $p$-adic groups 
+%as equivariant perverse sheaves on Vogan varieties 
+and, in the process, is led to study the representations of all the pure rational forms of the $p$-adic group simultaneously.
+A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group \cite{bernstein:vogan_conference}.
 Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to characters of all the pure rational forms of $T$.
@@
 After setting some basic notation in Section~\ref{sec:notation} 
-such as $A^*\ceq \Hom(A,\EEx)$ for any group $A$ and using $G$ for a commutative group scheme over $\FF_q$,
+such as $A^*\ceq \Hom(A,\EEx)$ for any abelian group $A$ and using $G$ for a smooth commutative group scheme over $\FF_q$,
 in Section~\ref{sec:category} we define the category of quasicharacter sheaves on $G$.
@@
  Since the functor $B_G : \bQC(G) \to \QC(G)$ is full and faithful, $\Aut(\qcs{L}) = \Aut(\qcs{E})$.
-From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields \citelist{\cite{deligne:SGA4.5}*{Sommes trig.},\cite{laumon:87a}*{1.1.3}} \todo{Fix citelist} gives us all we need, as we briefly recall.
+From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields, as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3}, gives us all we need, as we briefly recall.
+\todo{Fix citelist} %\citelist{\cite{deligne:SGA4.5}*{Sommes trig.},\cite{laumon:87a}*{1.1.3}}
 The key observation is that, by \'etale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
@@
 This homomorphism is injective because morphisms of sheaves are determined by the linear transformations induced on stalks.  
-Note that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom_\text{cts}(\bG_{\Weil{}},\EEx)$, where $\bG_{\Weil{}}$ is given the topology of the base of the espace \'etal\'e attached to $\gqcs{L}$.
-Since $\ell$ is invertible in $\Fq$, it follows that $\Hom_\text{cts}(\bG_{\Weil{}},\EEx) = \Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
-Note that $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
+Note that homomorphisms in the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ are continuous where $\bG_{\Weil{}}$ is given the topology of the base of the espace \'etal\'e attached to $\gqcs{L}$.
+Since $\ell$ is invertible in $\Fq$, it now follows that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
+We also have $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
 To see that $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho^y: \gqcs{L}^y \to \gqcs{L}^y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
@@
 \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6},
-\cite{nicaise-sebag:motivicSerre}*{\S 2.2}
-}.
+
+\cite{nicaise-sebag:motivicSerre}*{\S 2.2}. %citelist
 %

### 2014-08-25 crelle-dictionary.tex
Working on introduction

@@
 %%%%%%%%%%%%%%% COUNTER %%%%%%%%%%%%%%%
-\setcounter{section}{-1}
+%\setcounter{section}{-1}
 %%%%%%%%%%%%%%% THEOREM STYLES %%%%%%%%%%%%%%%
@@
       \newtheorem{theorem}{Theorem}[section]
+      \newtheorem*{theorem*}{Theorem}
       \newtheorem{proposition}[theorem]{Proposition}
@@
 
-\section{Introduction}
-
-\subsection{Overview}
+\section*{Introduction}
+
+%\subsection{Overview}
 
@@
 
-As Deligne explained in \cite{deligne:SGA4.5}*{Sommes trig.}, if $G$ is a connected commutative algebraic group over $\FF_q$, then the trace of Frobenius provides a bijection between characters of $G(\FF_q)$ and isomorphism classes of rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which
+As Deligne explained in \cite{deligne:SGA4.5}*{Sommes trig.}, if $G$ is a connected commutative algebraic group over $\FF_q$, then the trace of Frobenius provides a bijection between the group $G(\FF_q)^*$ of $\ell$-adic characters of $G(\FF_q)$ and isomorphism classes of rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which
 \begin{equation}\label{introbox}
@@
 
-In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$, we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\qcs{E}$.
-In this way we are led to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$.
-Objects in $\QC(G)$ are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves satisfying a certain compatibility condition.
+In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$,
+we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\qcs{E}$. 
+In this way we are led to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ (\S\ref{sec:category}).
+Objects in $\QC(G)$ are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$
+and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves satisfying a certain compatibility condition.
 Morphisms in $\QC(G)$ are then homomorphisms of Weil sheaves which are compatible with the extra structure.
 
-We first test the category of quasicharacter sheaves by examining its objects on \'etale commutative group schemes $G$ over $\FF_q$; \'etale group schemes form a counterpoint to connected algebraic groups, since the component group of a smooth commutative group scheme is an \'etale group scheme.
+We first test the category of quasicharacter sheaves by examining its objects on \'etale commutative group schemes $G$ over $\FF_q$ (\S\ref{sec:etale});
+\'etale group schemes form a counterpoint to connected algebraic groups, since the component group of any smooth group scheme is an \'etale group scheme.
+Our key tools for understanding the trace of Frobenius in the \'etale case are a reinterpretation of $\QC(G)$ in terms of stalks (\S\ref{ssec:stalks}) and a
+relationship with the Hochschild-Serre spectral sequence (\S\ref{ssec:E}) for $\Weil{} \ltimes \bG$, where $\Weil{} \subset \Gal({\bar\FF}_q/\FF_q)$ is the Weil group for $\FF_q$.
+We define (\S\ref{ssec:S}) an isomorphism $S_G$ from $\QCiso{G}$ to the second cohomology of the total space of the spectral sequence
+\[
+E_2^{p,q} \ceq \Hh^p(\Weil{}, \Hh^q(\bG, \EEx)) \Rightarrow \Hh^{p+q}(\Weil{} \ltimes \bG, \EEx).
+\]
+Paired with the short exact sequence
+\[
+  0 \to \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to \Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to 0
+\]
+arising from the spectral sequence, the isomorphism $S_G$ allows us to show (\S\ref{ssec:SandT}) that $\TrFrob{G}$ is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$.
 We find that the group homomorphism 
 \begin{equation}
-T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)
+T_G: \QCiso{G} \to G(\FF_q)^*
 \end{equation}
 provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$, where $\Weil{} \subset \Gal({\bar\FF}_q/\FF_q)$ is the Weil group for $\FF_q$.
-One can show, using the Kunneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
-The fact that $T_G$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
-Here we also see the importance of working with Weil sheaves; without them, we would not be able to geometrize any character of the \'etale group scheme $\ZZ$ 
-with non-compact image, such as $\ell^{\ZZ}$.
-
-Returning to the case of connected commutative algebraic groups $G$ over $\FF_q$, we confirm that, in this case, $\QC(G)$ is equivalent to the category of characters $\psi$ of $G(\FF_q)$, the equivalence being given by descent to $G$ followed by pullback by the Lang isogeny for $G$.
+One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
+The fact that $T_G$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$
+determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
+
+Returning to the case of connected commutative algebraic groups $G$, we consider quasicharacter sheaves that arise via base change to $\bFq$ from local systems on $G$ (\S\ref{ssec:descentG}) and
+those that appear in a pushforward from a constant sheaf along a discrete isogeny $H \to G$ (\S\ref{ssec:discrete_isogenies}).
+While these constructions make sense even for non-connected $G$, in the connected
+case we show that every quasicharacter sheaf can be described in both of these ways (\S\ref{ssec:connected}).
+We use this fact to prove that $T_G$ is an isomorphism for connected commutative algebraic groups $G$
+and to determine the automorphism groups of quasicharacter sheaves on such $G$.
+
 %
@@
 %This observation makes plain the fact that  . . .
-%
-As we show in the paper, while characters of connected commutative algebraic groups $G$ can be geometrized using  local systems trivialized by discrete isogenies to $G$, this is not the right perspective if one wishes to geometrize characters of smooth commutative group schemes, such as \'etale commutative group schemes.
-Indeed, quasicharacter sheaves on \'etale commutative group schemes that are trivialized by discrete isogenies are invisible to the trace of Frobenius.
-
-Having understood quasicharacter sheaves on commutative smooth group schemes over $\FF_q$ in two extreme cases -- connected algebraic groups and \'etale commutative group schemes -- we turn to the general case.
-Remarkably, we find that the general case can be understood from these two extreme cases, using the component group sequence
+%Indeed, quasicharacter sheaves on \'etale commutative group schemes that are trivialized by discrete isogenies are invisible to the trace of Frobenius.
+
+Having understood quasicharacter sheaves on commutative smooth group schemes over $\FF_q$ in two extreme cases --
+connected algebraic groups and \'etale commutative group schemes -- we turn to the general case.
+We find that the general case can be understood from these two extreme cases, using the component group sequence
 \begin{equation}
@@
 \end{equation}
-The main result of the paper uses this sequence to find $\QCiso{G}$ by situating it in a short exact sequence
-\begin{equation}
-0 \to \Hh^2(\pi_0(\bG),\EEx)^{\Weil{}} \to \QCiso{G} \to \Hom(G(\FF_q),\EEx) \to 0.
-\end{equation}
-%We remark that $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ is non-trivial even for some commutative algebraic groups.
+Using pullbacks of quasicharacter sheaves (\S\ref{sec:Frob}), we obtain a diagram
+\begin{equation} \label{eq:intro-snake}
+  \begin{tikzcd}[row sep=20, column sep=20]
+    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
+    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
+    0 \rar & \pi_0(G)(\FF_q)^* \rar & G(\Fq)^* \rar & G^0(\FF_q)^* \rar & 0,
+  \end{tikzcd}
+  \end{equation}
+The rows of this diagram are exact (\S\S\ref{ssec:restriction},\ref{ssec:component}), so we may apply the snake lemma to prove the main theorem of the paper%, Theorem~\ref{thm:snake} $\QCiso{G}$ into a short exact sequence
+\begin{theorem*}[{Thm. \ref{thm:snake}}]
+If $G$ is a smooth commutative group scheme over $\FF_q$ then
+\[
+\TrFrob{G} : \QCiso{G} \to G(\FF_q)^*
+\]
+is surjective with kernel $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
+\end{theorem*}
 We also illuminate the nature of the category $\QC(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing that
+\begin{theorem*}[{Thm. \ref{thm:autornaught}}]
+If $G$ is a smooth commutative group scheme over $\FF_q$ then
 \begin{equation}
@@
 \end{equation}
+\end{theorem*}
 for all quasicharacter sheaves $\qcs{L}$ on $G$.
 
-\subsection{Applications over local fields}
+%Here we also see the importance of working with Weil sheaves: sheaves on $G$ itself only allow us to geometrize characters with compact image.
+%We conclude in Section~\ref{sec:basechange} by
+%giving functorial versions of the restriction and norm homomorphisms 
+%of character groups $G(k')^* \to G(k)^*$ and $G(k)^* \to G(k')^*$
+%and describing how quasicharacter sheaves behave under Weil restriction.
+
+%\subsection{Applications over local fields}
 
@@
 
+Section~\ref{sec:applications} gives applications of quasicharacter sheaves to commutative algebraic groups over local fields.
+We begin with a review of N\'eron models and of the Greenberg transform in Section~\ref{ssec:rev_Greenberg}.  We then
+define, in Section~\ref{ssec:qc_on_GN}, a quasicharacter sheaf for an algebraic group over a local field to be a quasicharacter
+sheaf on the Greenberg transform of the N\'eron model.  In Theorem~\ref{thm:QCXK}, we translate our results from earlier sections
+to give a description of the isomorphism classes and automorphism groups
+in the category of quasicharacter sheaves on such an algebraic group.
+We specialize to $p$-adic tori in Section~\ref{ssec:qc_tori}, and discuss
+Weil restriction and base change over local fields in Section~\ref{ssec:wrK}.
+Finally, we give a categorical version of a result of Chai and Yu \cite{chai-yu:01a},
+relating quasicharacter sheaves for tori over different local fields, even local fields
+with different characteristic.
+
 Specializing to the case when $X_K$ is an algebraic torus $T$ over $K$, and writing $\underline{T}$ for the Neron model $X$ in this case, this paper gives a canonical short exact sequence 
@@
 
-\subsection{Comparison with character sheaves}
+%\subsection{Comparison with character sheaves}
 
@@
 
-\subsection{Structure of the paper}
-
-We close the introduction with an overview of the structure of this paper.
-After setting some basic notation in Section~\ref{sec:notation} 
-such as $A^*\ceq \Hom(A,\EEx)$ for any abelian group $A$ and using $G$ for a smooth commutative group scheme over $\FF_q$,
-in Section~\ref{sec:category} we define the category of quasicharacter sheaves on $G$.
-Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism $\TrFrob{G} : \QCiso{G} \to G(\FF_q)^*$.
-We also define pullbacks of quasicharacter sheaves along morphisms of group schemes.  Applying pullbacks to the component group
-sequence for $G$ yields the diagram
- \begin{equation} \label{eq:intro-snake}
-  \begin{tikzcd}[row sep=20, column sep=20]
-    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
-    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
-    0 \rar & \pi_0(G)(\FF_q)^* \rar & G(\Fq)^* \rar & G^0(\FF_q)^* \rar & 0,
-  \end{tikzcd}
-  \end{equation}
-which is central to the proof of Theorem~\ref{thm:snake}.  Much of Sections~\ref{sec:etale}, \ref{sec:disc-isog} and \ref{sec:main}
-are devoted to proving that the rows of \eqref{eq:intro-snake} are exact and determining the kernels and cokernels of the vertical maps.
-
-Section~\ref{sec:etale} is devoted to the left-most vertical morphism in \eqref{eq:intro-snake}: studying $\TrFrob{G}$ for $G$ \'etale.  We begin by giving a reinterpretation of
-$\QC(G)$ in this case using stalks.  After a brief review of the Hochschild-Serre spectral sequence in Section~\ref{ssec:E},
-we define in Section~\ref{ssec:S} an isomorphism $S_G$ from $\QCiso{G}$ to the second cohomology of the total space of the spectral sequence
-\[
-E_2^{p,q} \ceq \Hh^p(\Weil{}, \Hh^q(\bG, \EEx)) \Rightarrow \Hh^{p+q}(\Weil{} \ltimes \bG, \EEx).
-\]
-Paired with the short exact sequence
-\[
-  0 \to \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to \Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to 0
-\]
-arising from the spectral sequence, the isomorphism $S_G$ allows us to describe the kernel and cokernel of $\TrFrob{G}$ in Section \ref{ssec:SandT}.
-We close our discussion of \'etale $G$ with a description, in Section~\ref{ssec:mor-etale}, of $\Hom(\qcs{L},\qcs{L}')$ for $\qcs{L}, \qcs{L}' \in \QC(G)$.
-
-Section~\ref{sec:disc-isog} focuses on the right-hand side of \eqref{eq:intro-snake},
-giving descriptions of quasicharacter sheaves that are particularly useful when $G$ is connected.  In Section \ref{ssec:descentG}
-we consider quasicharacter sheaves that arise via base change to $\bFq$ from local systems on $G$, and in Section \ref{ssec:discrete_isogenies}
-those that arise via pushforward from a constant sheaf along a discrete isogeny $H \to G$.  When $G$ is connected,
-we show in Section~\ref{ssec:connected} that every quasicharacter sheaf can be described in both of these ways.
-We also show that $\TrFrob{G}$ is an isomorphism in this case.
-
-In Section~\ref{sec:main} we prove that the rows of \eqref{eq:intro-snake} are exact and
-use the snake lemma to determine the kernel and cokernel of $\TrFrob{G}$ for general $G$.
-We show that $\QCiso{G^0} \to \QCiso{G}$ is surjective in Section~\ref{ssec:restriction} and
-that the remainder of the top row of \eqref{eq:intro-snake} is exact in Section~\ref{ssec:component}.
-We put it together in Theorem~\ref{thm:snake} of Section~\ref{ssec:snake}, showing that $\TrFrob{G}$
-is surjective with kernel $\Hh^2(\pi_0(\bG), \EEx)^{\Weil{}}$.  Having described the isomorphism classes of objects,
-in Theorem~\ref{thm:autornaught} of Section~\ref{ssec:qcmor} we show that
-\[
-\Aut(\qcs{L}) \cong \Hom(\pi_0(\bG)_{\Weil{}}, \EEx)
-\]
-and that every morphism is either trivial or an isomorphism.  We conclude in Section~\ref{sec:basechange} by
-giving functorial versions of the restriction and norm homomorphisms 
-of character groups
-$G(k')^* \to G(k)^*$ and $G(k)^* \to G(k')^*$
-and describing how quasicharacter sheaves behave under Weil restriction.
-
-Section~\ref{sec:applications} gives applications of quasicharacter sheaves to commutative algebraic groups over local fields.
-We begin with a review of N\'eron models and of the Greenberg transform in Section~\ref{ssec:rev_Greenberg}.  We then
-define, in Section~\ref{ssec:qc_on_GN}, a quasicharacter sheaf for an algebraic group over a local field to be a quasicharacter
-sheaf on the Greenberg transform of the N\'eron model.  In Theorem~\ref{thm:QCXK}, we translate our results from earlier sections
-to give a description of the isomorphism classes and automorphism groups
-in the category of quasicharacter sheaves on such an algebraic group.
-We specialize to $p$-adic tori in Section~\ref{ssec:qc_tori}, and discuss
-Weil restriction and base change over local fields in Section~\ref{ssec:wrK}.
-Finally, we give a categorical version of a result of Chai and Yu \cite{chai-yu:01a},
-relating quasicharacter sheaves for tori over different local fields, even local fields
-with different characteristic.
-
-%\tableofcontents
+\tableofcontents
 
@@
 We prove the lemma by considering the linear transformations $\rho_{\bar g} : \gqcs{L}_{\bar g} \to \gqcs{L}_{\bar g}$ at the stalks above geometric points ${\bar g}$ on $G$ and showing that, either each $\rho_{\bar g}$ trivial or each $\rho_{\bar g}$ is an isomorphism.
-(This idea is expanded upon in Section~\ref{sec:stalks}.)
+(This idea is expanded upon in Section~\ref{ssec:stalks}.)
 Let ${\bar e}$ be the geometric point above the identity $e$ for $G$ determined by our choice of algebraic closure $\bFq$ of $\Fq$.
@@
 
-\subsection{Stalks of quasicharacter sheaves}\label{sec:stalks}
+\subsection{Stalks of quasicharacter sheaves}\label{ssec:stalks}
 
@@
   \]
-is surjective with kernel canonically isomorphic to $\Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$.
+is surjective with kernel canonically isomorphic to $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$.
 \end{theorem}

### 2014-08-25 crelle-dictionary.tex
Changes to Applications, esp Weil restriction.

@@
 As indicated above, our interest in the function-sheaf dictionary for smooth commutative group schemes over finite fields comes from an application to $p$-adic representation theory. 
-We found, however, that this application applies to all local fields $K$ with finite residue field $\Fq$ and all connected commutative algebraic groups $X_K$ over $K$ that do not contain a subgroup of type $\mathbb{G}_\text{a}$, such as abelian varieties, unipotent $K$-wound groups, and of course, algebraic tori.
+We found, however, that this application applies to all local fields $K$ with finite residue field $\Fq$ and all connected commutative algebraic groups $X_K$ over $K$ that do not contain a subgroup of type $\mathbb{G}_\text{a}$, such as abelian varieties, unipotent $K$-wound groups and, of course, algebraic tori.
 Such algebraic groups $X_K$ always admit a Neron model $X$ over $R$, the ring of integers of $K$.
@@
 Suppose $\qcs{L} \in \QCiso{G}$ with $S_G(\qcs{L}) = [\alpha \oplus \beta] = 0$,
-so that $\alpha \oplus \beta = d\rho$ for some $\rho \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
-For each $x\in {\bar G}$, define $\rho_x : \gqcs{L}_x \to \EEx$ by $v_x \mapsto \rho(x)$.
-Then the indexed set of isomorphisms $\{ \gamma_x : \gqcs{L}_x \to \EE \tq x\in {\bar G}\}$
+so that $\alpha \oplus \beta = d\sigma$ for some $\sigma \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
+For each $x\in {\bar G}$, define $\sigma_x : \gqcs{L}_x \to \EEx$ by $v_x \mapsto \sigma(x)$.
+Then the indexed set of isomorphisms $\{ \sigma_x : \gqcs{L}_x \to \EE \tq x\in {\bar G}\}$
 defines an isomorphism $\qcs{L} \to (\EE)_G$.
@@
  Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Suppose $(\qcs{E},\mu_\qcs{E})$ in an object in $\bQC(G)$.
+ Suppose $(\qcs{E},\mu_\qcs{E})$ in an object of $\bQC(G)$.
  Then $\qcs{E}$ is an $\ell$-adic constructible sheaf on $G$ and
@@
 Let $\psi : A \to \EEx$ be the character of $V$.
-Then $(f_! V_H)_\psi$ (the $\psi$-isotypic component of $f_!V_H$) is an object in $\bQC(G)$.
+Then $(f_! V_H)_\psi$ (the $\psi$-isotypic component of $f_!V_H$) is an object of $\bQC(G)$.
 \end{proposition}
@@
   the latter appearing in the definition of $\qcs{L}$.
-  Then, as in Section~\ref{ssec:descentG}, $(\qcs{E},\mu_\qcs{E})$ is an object in $\bQC(G)$
+  Then, as in Section~\ref{ssec:descentG}, $(\qcs{E},\mu_\qcs{E})$ is an object of $\bQC(G)$
   and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{E},b_{G\times G}^*\mu_\qcs{E})$ in $\QC(G)$.
@@
 \begin{proof}
-In Lemma~\ref{lem:bounded_connected} we saw that every quasicharacter sheaf $\qcs{L}$ on $G$ descends to $G$; let $\qcs{E}$ be an object in $\bQC(G)$ for which $B_G(\qcs{E}) \iso \qcs{L}$.
+In Lemma~\ref{lem:bounded_connected} we saw that every quasicharacter sheaf $\qcs{L}$ on $G$ descends to $G$; let $\qcs{E}$ be an object of $\bQC(G)$ for which $B_G(\qcs{E}) \iso \qcs{L}$.
  Since the functor $B_G : \bQC(G) \to \QC(G)$ is full and faithful, $\Aut(\qcs{L}) = \Aut(\qcs{E})$.
@@
 \begin{definition}
-Let $\QC(X_K)$ be the following evil subcategory of $\QC(\Gr_R(X))$:
-objects in $\QC(X_K)$ are the $\ell$-adic sheaves $\varrho^R_n(X)^*\qcs{L}$, for $n\in \NN$ and $\qcs{L} \in \QC(\Gr^R_n(X))$; morphism from $\varrho^R_n(X)^*\qcs{L}$ to $\varrho^R_m(X)^*\qcs{L}'$ are $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\qcs{L},\qcs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\qcs{L},\varrho^R_{m\leq n}(X)^*\qcs{L}')$ when $m\leq n$.
- We refer to $\QC(X_K)$ as the {\it evil category of quasicharacter sheaves for $X_K$}; objects will simply be called {\it 
-quasicharacter sheaves for $X_K$}.
-We put a rigid monoidal structure on $\QC(X_K)$ in the same way as for $\QC(G)$ in Section \ref{sec:category}.
+A {\it quasicharacter sheaf for $X_K$} is an object of
+the following rigid monoidal subcategory of $\QC(\Gr_R(X))$, denoted by $\QC(X_K)$:
+\begin{enumerate}
+\item
+objects in $\QC(X_K)$ are the $\ell$-adic sheaves $\varrho^R_n(X)^*\qcs{L}$, for $n\in \NN$ and $\qcs{L} \in \QC(\Gr^R_n(X))$; 
+\item
+morphism $\varrho^R_n(X)^*\qcs{L} \to \varrho^R_m(X)^*\qcs{L}'$ in $\QC(X_K)$ are those morphisms in $\QC(\Gr_R(X))$ which take the form $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\qcs{L},\qcs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\qcs{L},\varrho^R_{m\leq n}(X)^*\qcs{L}')$ when $m\leq n$.
+\end{enumerate}
+
 \end{definition}
@@
 \begin{remark}
-The evil category of quasicharacter sheaves for $X_K$ is evil in the categorical sense.
-If $\varrho^R_n(X)^* : \QC(\Gr^R_n(X)) \to \QC(\Gr_R(X))$ is full then the construction above is easily modified to be non-evil; however, we do not know if $\varrho^R_n(X)^*$ is full.
-In any case, a non-evil alternative construction of $\QC(X_K)$ is available, but it is quite ugly.
-For objects, one considers triples $\qcs{F} \ceq (n, \{\qcs{F}_i\}_{i \ge n}, \{\alpha_{i \le j}\}_{j \ge i \ge n})$, where $n$
-is a positive integer, each $\qcs{F}_i$ is a quasicharacter sheaf on $\Gr^R_i(X)$ and each $\alpha_{i \le j} : \qcs{L}_j \to f^*_{i \le j} \qcs{L}_i$ is an isomorphism; of course, $\alpha_{i \le i}$ is the identity and the $\alpha_{i \le j}$ are compatible with each other.
+If $\varrho^R_n(X)^* : \QC(\Gr^R_n(X)) \to \QC(\Gr_R(X))$ is full then the construction above can be improved by forming $\QC(X_K)$ from the essential images of the functors $\varrho^R_n(X)^*$; however, we do not know if $\varrho^R_n(X)^*$ is full.
+\end{remark}
+
+\begin{remark}
+We offer the following alternate construction of $\QC(X_K)$, which does not make use of subcategories.
+For objects, one considers triples 
+\[
+\qcs{F} \ceq (n, \{\qcs{F}_i\}_{n\leq i}, \{\alpha_{i \le j}\}_{n\le i \le j}),
+\] where $n$
+is a non-negative integer, each $\qcs{F}_i$ is a quasicharacter sheaf on $\Gr^R_i(X)$ and each 
+\[
+\alpha_{i \le j} : \qcs{L}_j \to \varrho^R_{i \le j}(X)^* \qcs{L}_i
+\]
+ is an isomorphism; here $\alpha_{i \le i}$ is the identity and the $\alpha_{i \le j}$ are compatible with each other.  
 If $\qcs{F} \ceq (n, \{\qcs{F}_i\}, \{\alpha_{i \le j}\})$
 and $\qcs{F}' \ceq (m, \{\qcs{F}'_i\}, \{\alpha'_{i \le j}\})$ are objects then $\Hom(\qcs{F}, \qcs{F}')$ is the set
-of equivalence classes of pairs $(k, \{\beta_i\}_{i \ge k})$, where $k \ge m, n$ and the $\beta_i : \qcs{F}_i \to \qcs{F}'_i$ are
+of equivalence classes of pairs $(k, \{\beta_i\}_{k \le i})$, where $n,m \le k$ and the $\beta_i : \qcs{F}_i \to \qcs{F}'_i$ are
 morphisms of quasicharacter sheaves so that
@@
 \begin{tikzcd}
-\qcs{F}_j \rar{\alpha_j} \dar{\beta_i} & f^*_{i \le j} \qcs{F}_i \dar{f_{i \le j}^*\beta_j} \\
-\qcs{F}'_j \rar{\alpha_j} & f^*_{i \le j} \qcs{L}'_i
-\end{tikzcd}
-\]
-commutes for all $j \ge i \ge k$; we identify two such pairs $(k, \{\beta_i\})$ and $(l, \{\gamma_i\})$ if $\beta_i = \gamma_i$
+\qcs{F}_j \rar{\alpha_j} \dar{\beta_i} & \varrho^R_{i \le j}(X)^* \qcs{F}_i \dar{f_{i \le j}^*\beta_j} \\
+\qcs{F}'_j \rar{\alpha_j} & \varrho^R_{i \le j}(X)^* \qcs{L}'_i
+\end{tikzcd}
+\]
+commutes for all $k\le i\le j$; we identify two such pairs $(k, \{\beta_i\})$ and $(l, \{\gamma_i\})$ if $\beta_i = \gamma_i$
 for sufficiently large $i$.  Identities and composites are defined in the natural way.
@@
 \begin{proof}
-To begin, fix $n\in \NN$.
-The following statements follow directly from Lemma~\ref{lem:autornaught}, Proposition~\ref{prop:functorialG}, Theorems~\ref{thm:snake} and \ref{thm:autornaught}, properties of N\'eron models and our observations about the component group of $\Gr^R_n(X)$.
-\begin{enumerate}
-\item Trace of Frobenius gives a natural transformation from
-\[
-F_{\QC,n}: X_K \mapsto \QCiso{\Gr^R_n(X)}
-\qquad\text{to}\qquad
-F_{\text{qc},n}: X_K \mapsto \Hom_n(X_K(K),\EEx)
-\]
-as functors from $\mathcal{N}_K$ to abelian groups.
-\item There is a canonical short exact sequence of abelian groups 
-\[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{\Gr^R_n(X)} \to \Hom(X(R_n),\EEx) \to 0.
-\] 
-\item For all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $\Gr^R_n(X)$ and for every $\rho \in \Hom(\qcs{L},\qcs{L}')$, either $\rho$ is trivial or $\rho$ is an isomorphism.
-\item For all quasicharacter sheaves $\qcs{L}$ on $\Gr^R_n(X)$ there is a canonical isomorphism
-\[
-\Aut(\qcs{L}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx).
-\]
-\end{enumerate} \todo{move to a lemma?}
-So Theorem~\ref{thm:QCXK} now follows from the fact that each $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(X_K)$ and the observation that $\QC(X_K)$ a `union' of the subcategories $\QC(\Gr^R_n(X))$ in $\QC(\Gr_R(X))$.
+For part (i), use Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$, the fact that N\'eron models are unique up to isomorphism, the fact that each $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(X_K)$ and the observation that $\QC(X_K)$ a `union' of the subcategories $\QC(\Gr^R_n(X))$ in $\QC(\Gr_R(X))$.
+For part (ii), use Theorem~\ref{thm:snake} with $G = \Gr^R_n(X)$ and then argue as in part (i).
+For part (iii), argue as in the proof of Lemma~\ref{lem:autornaught}.
+For part (iv), use Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, the fact that the component group of $\Gr^R_n(X)$ is independent of $n$ and then argue as in part (i).
 \end{proof}
@@
 \] 
-such that the restriction of the functor
-\[
-f^* : \QC(\Res_{k'/k} \Gr_{R'}(X')) \to  \QC(\Gr_R(X))
-\]
-induces
+which, through quasicharacter sheaves, induces
 \[
@@
 one may show that $\Res_{R'/R}(X')$ is a N\'eron model for $\Res_{K'/K}(X_{K'})$.
-By the N\'eron mapping property, the canonical closed immersion
+Thus, by the N\'eron mapping property, the canonical closed immersion
 \[
@@
  extends uniquely to a morphism
-\[
+\begin{equation}\label{me}
 X\to \Res_{R'/R}(X')
-\]
+\end{equation}
  of smooth $R$-group schemes.
 %
-Applying the functor $\Gr_{n}$ to this morphism
+Applying the functor $\Gr^R_{n}$ to \eqref{me}
 and using \cite{bertrapelle-gonzales:Greenberg}*{Thm 1.1} defines the morphism of smooth group schemes
 \begin{equation}\label{men}
-f_n: \Gr_{n-1}^R(X) \to \Res_{k'/k} \Gr_{en-1}^{R'}(X')
+f_n: \Gr_{n-1}^R(X) \to \Res_{k'/k} \Gr_{en-1}^{R'}(X'),
+\end{equation}
+where $e$ is the ramification index of $K'/K$.
+Using Lemma~\ref{lem:pullback}, \eqref{men} induces a functor 
+\begin{equation}\label{men-pulled}
+f_n^* : \QC(\Res_{k'/k} \Gr_{en-1}^{R'}(X'))\to \QC(\Gr_{n-1}^{R}(X)).
 \end{equation}
@@
 \]
-the pullback functor 
-\[
-f_n^* : \QC(\Res_{k'/k} \Gr_{en-1}^{R'}(X'))\to \QC(\Gr_{n-1}^{R}(X))
-\]
-obtained by applying Lemma~\ref{lem:pullback} to \eqref{men} gives
-\[
-\Hom(X(R'_{en}),\EEx) \to \Hom(X(R_n),\EEx).
-\]
-Passing to the projective limit, the family of morphisms \eqref{men} determines a morphism of group schemes
-\[
-f: \Gr_R(X) \to \Res_{k'/k} \Gr_{R'}(X').
-\]
-which induces the functor
-\[
-f^* : \QC(\Res_{k'/k} \Gr_{R'}(X'))\to \QC(\Gr_{R}(X)).
-\]
-When restricted to the appropriate evil subcategories, this induces
-\[
-\Hom_{\text{qc}}(X_K(K'),\EEx) \to \Hom_{\text{qc}}(X_K(K),\EEx).
+it follows from Lemma~\ref{lem:pullback} that the pullback functor \eqref{men-pulled} actually induces
+\[
+\Hom(X'(R'_{en-1}),\EEx)  \to  \Hom(X(R_{n-1}),\EEx) .
+\]
+Since $X'$ is a N\'eron model for $X_{K'}$ and $X$ is a N\'eron model for $X_K$,
+ this may be re-written as
+\[ 
+\Hom_{en-1}(X_{K'}(K'),\EEx) \to \Hom_{n-1}(X_K(K)),\EEx)
+\]
+Note that $X_{K'}(K') = X_{K}(K')$. Passing to limits now defines
+\[ 
+\Hom_\text{qc}(X_{K}(K'),\EEx) \to \Hom_\text{qc}(X_K(K)),\EEx)
 \]
@@
 
-Let $K$ and $K'$ be local fields with rings of integers $R$ and $R'$ and residue fields $k$ and $k'$, respectively.
-Set $S = \Spec{S}$ and $S_n = \Spec{R_n}$; likewise define $S' = \Spec{R'}$ and $S'_{n'} = \Spec{R'_{n'}}$.
-
-Suppose $X_K\in \mathcal{N}_K$ with N\'eron model $X$ and $X'_{K'}\in \mathcal{N}_K'$ with N\'eron model $X'$.
-Suppose $m$ and $m'$ are non-negative integers such that 
-$
-R_m \iso R'_{m'},
-$
-in which case $K$ and $K'$ are said to be $m$-close, and
+Let $K$ and $L$ be local fields with rings of integers $\OK$ and $\OL$, respectively. 
+Pick uniformizers $\varpi_K$ and $\varpi_L$ for $\OK$ and $\OL$, respectively;
+what follows will not depend on these choices.
+
+Suppose $X_K\in \mathcal{N}_K$ with N\'eron model $X$ and $Y_{L}\in \mathcal{N}_L$ with N\'eron model $Y$.
+Suppose $m$ is a non-negative integers such that 
+\[
+\OK/\varpi_K^m\OK \iso \OL/\varpi_L^m\OL
+\]
+%(in which case $K$ and $L$ are said to be $m$-close).
+Suppose also that
 \begin{equation}\label{eq:schematic_transfer}
-X \times_{S} S_m \iso X' \times_{S'} S'_{m'}.
-\end{equation}
-as smooth group schemes over $R_m$. 
+X \times_{\Spec{\OK}} \Spec{\OK/\varpi_K^m\OK} \iso Y \times_{\Spec{\OL}} \Spec{\OL/\varpi_L^m\OL}
+\end{equation}
+as smooth group schemes over $\OK/\varpi_K^m\OK$. 
 Then
 $
-\Gr^R_m(X) \iso \Gr^{R'}_{m'}(X')
+\Gr^{\OK}_m(X) \iso \Gr^{\OL}_{m}(Y)
 $
@@
 \begin{equation}\label{eq:categorical_transfer}
-\QC(\Gr^R_m(X)) \cong \QC(\Gr^{R'}_{m'}(X'))
-\end{equation}
-which induces a group isomorphism
-$
-\QCiso{\Gr^R_m(X)} \cong \QCiso{\Gr^{R'}_{m'}(X')}
-$
-and thence, by trace of Frobenius, an isomorphism
+\QC(\Gr^{\OK}_m(X)) \cong \QC(\Gr^{\OL}_{m}(Y))
+\end{equation}
+which induces an isomorphism
 \begin{equation}\label{eq:transfer}
-\Hom_m(X_K(K),\EEx)  \iso  \Hom_{m'}(X'_{K'}(K'),\EEx).
-\end{equation}
-The isomorphism \eqref{eq:transfer} is an instance of {\it transfer} of (certain) quasicharacters between $X_K(K)$ and $X_{K'}(K')$. 
+\Hom_m(X_K(K),\EEx)  \iso  \Hom_{m}(Y_{L}(L),\EEx).
+\end{equation}
+The isomorphism \eqref{eq:transfer} is an instance of {\it transfer} of (certain) quasicharacters between $X_K(K)$ and $Y_{L}(L)$. 
 We now recognize this transfer of quasicharacters as a consequence of the equivalence of categories of quasicharacter sheaves \eqref{eq:categorical_transfer}.
 
-The isomorphism \eqref{eq:schematic_transfer} can indeed exist between quasicharacters of algebraic tori over local fields, even when the characteristics of $K$ and $K'$ differ.
-Suppose $T$ and $T'$ are tori over non-archimedian local fields $K$ and $K'$,
-splitting over $L$ and $L'$ respectively.
-Then $T$ and $T'$ are said to be \emph{$N$-congruent} \cite{chai-yu:01a}*{\S 2} if there are isomorphisms
+The isomorphism \eqref{eq:schematic_transfer} can indeed exist between quasicharacters of algebraic tori over local fields, even when the characteristics of $K$ and $L$ differ.
+Suppose $T_K$ and $M_L$ are tori over non-archimedian local fields $K$ and $L$,
+splitting over $K'$ and $L'$ respectively.
+Then $T_K$ and $M_L$ are said to be \emph{$n$-congruent} \cite{chai-yu:01a}*{\S 2} if there are isomorphisms
  \begin{align*}
-  \alpha : \OL/\pi_K^N \OL &\to \OO{L'}/\pi_{K'}^N \OO{L'} \\
-  \beta : \Gal(L/K) &\to \Gal(L'/K') \\
-  \phi : X^*(T) &\to X^*(T')
+  \alpha : \OO{K'}/\varpi_K^n \OO{K'} &\to \OO{L'}/\varpi_{L}^n \OO{L'} \\
+  \beta : \Gal(K'/K) &\to \Gal(L'/L) \\
+  \phi : X^*(T_K) &\to X^*(M_L)
  \end{align*}
@@
  \begin{enumerate}
-  \item $\alpha$ induces an isomorphism $\OK/\pi_K^N \OK \to \OO{K'}/\pi_{K'}^N \OO{K'}$,
-  \item $\alpha$ is $\Gal(L/K)$-equivariant relative to $\beta$, and
-  \item $\phi$ is $\Gal(L/K)$-equivariant relative to $\beta$.
+  \item $\alpha$ induces an isomorphism $\OK/\pi_K^n \OK \to \OO{L}/\pi_{L}^n \OO{L}$,
+  \item $\alpha$ is $\Gal(K'/K)$-equivariant relative to $\beta$, and
+  \item $\phi$ is $\Gal(K'/K)$-equivariant relative to $\beta$.
  \end{enumerate}
-If $T$ and $T'$ are $N$-congruent then $\alpha$, $\beta$ and $\phi$ determine an isomorphism 
+If $T_K$ and $M_L$ are $n$-congruent then $\alpha$, $\beta$ and $\phi$ determine an isomorphism 
 \begin{equation}\label{transfer}
-  \Hom_N(T(K), \EEx) \iso \Hom_N(T'(K'),\EEx).
-\end{equation}
-Note that if $T$ and $T'$ are $N$-congruent, then they are $N'$ congruent for every
-$N' \leq N$.
+  \Hom_{n-1}(T_K(K), \EEx) \iso \Hom_{n-1}(M_L(M),\EEx).
+\end{equation}
+Note that if $T_K$ and $M_L$ are $n$-congruent, then they are $m$ congruent for every
+$m \leq n$.
 %the isomorphism \eqref{transfer} is level-preserving at integers less than $N$.
 %
+
+Now let $T$ be a N\'eron model for $T_K$ and let $M$ be a N\'eron model for $M_L$.
 One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes between the
-$\underline{T} \times_S S_n$ and $\underline{T}' \times_{S'} S'_n$, where $\underline{T}$ is a N\'eron model of $T$ and $\underline{T}'$ is a N\'eron model of $T'$, assuming that $T$ and $T'$ are sufficiently congruent.
-They define a quantity $h$ (the smallest integer so that $\pi^h$ lies in the
-Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}) and show  that if $N > 3h$ and $T$ and $T'$ are $N$-congruent then there is a canonical isomorphism of smooth group schemes
+$T \times_{\Spec{\OK}} \Spec{\OK/\varpi_n\OK}$ and $M \times_{\Spec{\OL}} \Spec{\OL/\varpi^n\OL}$, assuming that $T_K$ and $M_L$ are sufficiently congruent.
+They define a quantity $h$ (the smallest integer so that $\varpi^h$ lies in the
+Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}) and show  that if $n > 3h$ and $T_K$ and $M_L$ are $n$-congruent then there is a canonical isomorphism of smooth group schemes
  $
- \underline{T}_{N-3h} \to \underline{T}'_{N-3h}
+\Gr_{n-3h}(T) \to \Gr_{n-3h}(M)
  $
@@
 \begin{proposition}\label{prop:transfer}
- With notation above, suppose that $T$ and $T'$ are $N$-congruent and $N > 3h$.  Set $m = N-3h$.
+ With notation above, suppose that $T_K$ and $M_L$ are $n$-congruent and $n > 3h$.  Set $m = n-3h$.
  Then there is a canonical equivalence of categories
  \[
- \QC(\Gr^{R}_m(\underline{T})) \iso \QC(\Gr^{R'}_m(\underline{T}'))
+ \QC(\Gr^{\OK}_m(T)) \iso \QC(\Gr^{\OL}_m(M))
  \]
@@
  \[
-\Hom_m(T(K), \EEx) \iso  \Hom_m(T'(K'), \EEx)
+\Hom_m(T_K(K), \EEx) \iso  \Hom_m(M_L(L), \EEx)
  \]
@@
 
-\acknowl{
-We thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
+\acknowl{We thank Masoud Kamgarpour, Pramod Achar and Hadi Salmasian
 for allowing us to hijack much of our Research in Teams meeting at BIRS into a discussion of

### 2014-08-25 crelle-dictionary.tex
Added font for categories. Changed X_K(K) to X(K).

@@
 \newcommand{\Spec}[1]{{\operatorname{Spec}\hskip-1pt( #1 )}}
-\newcommand{\Sch}[1]{{\left(\operatorname{Sch}_{/#1}\right)}}
-
 %%%%%%%%%%%% MISCELLANEOUS OPERATORS %%%%%%%%%%%%
@@
 \newcommand{\bQC}{{\QC_0}}
-\newcommand{\fQC}{{\QC_\text{fin}}}
+%\newcommand{\fQC}{{\QC_\text{fin}}}
 \newcommand{\QCiso}[1]{\QC(#1)_{/\text{iso}}}
 \newcommand{\bQCiso}[1]{\bQC(#1)_{/\text{iso}}}
-\newcommand{\fQCiso}[1]{\fQC(#1)_{/\text{iso}}}
+%\newcommand{\fQCiso}[1]{\fQC(#1)_{/\text{iso}}}
+\newcommand{\catname}[1]{\normalfont{\textsf{#1}}}
+\newcommand{\Sch}[1]{{\catname{Sch}_{/#1}}}
 %% amsmath replacements for \atop
@@
 These algebraic groups over $K$ form an additive category, denoted by $\mathcal{N}_K$ below, in a natural way, as a full subcategory of connected commutative algebraic groups over $K$.
-This category includes algebraic tori over $K$ and abelian varieties over $K$ unipotent K-wound groups.
+This category includes algebraic tori over $K$, abelian varieties over $K$ and unipotent $K$-wound groups.
 
@@
 Suppose $X_K \in \mathcal{N}_K$ with N\'eron model $X$ over $R$.
-A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) \to X(R_n)$, for some non-negative integer $n$;
-the group of quasicharacters of $X_K(K)$ will be denoted by 
-\[
-\Hom_\text{qc}(X_K(K),\EEx)
+Note that $X(K) = X(R)$.
+A {\it quasicharacter of $X(K)$} is a group homomorphism $X(K) \to \EEx$ that factors through $X(R) \to X(R_n)$, for some non-negative integer $n$;
+the group of quasicharacters of $X(K)$ will be denoted by 
+\[
+\Hom_\text{qc}(X(K),\EEx)
 \]
@@
  \[
- \Hom_n(X_K(K),\EEx).
-\]
-In this section we will see how to geometrize and categorify quasicharacters of $X_K(K)$ using quasicharacter sheaves.
+ \Hom_n(X(K),\EEx).
+\]
+In this section we will see how to geometrize and categorify quasicharacters of $X(K)$ using quasicharacter sheaves.
 
@@
 a functor from the category of schemes 
-over $R_n$, for each $n\in \NN$, to the category of schemes over $\Fq$; \todo{font for categories, subscripts on homsets}
+over $R_n$, for each $n\in \NN$, to the category of schemes over $\Fq$.
 See \cite{bertrapelle-gonzales:Greenberg} for the definition and fundamental properties of the Greenberg functor as we use it; other important references include
@@
 \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6},
-
 \cite{nicaise-sebag:motivicSerre}*{\S 2.2}. %citelist
@@
 Crucially, $\varrho^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
-This observation is key to the proof that, for any $X$ lft over $R$, the projective limit 
+This observation is key to the proof that, for any scheme $X$ over $R$, the projective limit 
 \[
@@
 \[
-\Gr_R : \partop{\text{Schemes}}{\text{lft over $R$}} \to \partop{\text{Schemes}}{\text{lft over $\Fq$}}.
+\Gr_R : \Sch{R} \to \Sch{\Fq}.
 \]
@@
 \[
-\varrho^R_n(X) : \Gr^R(X) \to \Gr^R_n(X),\qquad \forall n\in \NN_0.
+\varrho^R_n(X) : \Gr^R(X) \to \Gr^R_n(X),\qquad \forall n\in \NN.
 \]
@@
 with component group scheme $\pi_0(X) \times_S S_0$
-and $\Fq$-rational points $X_K(K).$
+and $\Fq$-rational points $X(K).$
 However, $\Gr_R(X)$ is not locally of finite type and therefore not smooth.
@@
 
-We now define a category which will geometrize quasicharacters of $X_K(K)$.
+We now define a category which will geometrize quasicharacters of $X(K)$.
 We begin by considering the rigid monoidal category $\QC(\Gr_R(X))$ defined in Section~\ref{sec:category} without insisting that the commutative group scheme is smooth.
@@
 \qquad\text{and}\qquad
-F_{\text{qc}}: X_K \mapsto \Hom_{\text{qc}}(X_K(K),\EEx)
+F_{\text{qc}}: X_K \mapsto \Hom_{\text{qc}}(X(K),\EEx)
 \]
@@
 \[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{X_K} \to \Hom_\text{qc}(X_K(K),\EEx) \to 0;
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{X_K} \to \Hom_\text{qc}(X(K),\EEx) \to 0;
 \] 
@@
 \begin{tikzcd}[column sep=60]
-\Hom_{\text{qc}}(X_K(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{X_K(K)}} &\Hom_{\text{qc}}(X_K(K), \EEx).
+\Hom_{\text{qc}}(X(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{X(K)}} &\Hom_{\text{qc}}(X(K), \EEx).
 \end{tikzcd}
@@
 \[ 
-\Hom_{en-1}(X_{K'}(K'),\EEx) \to \Hom_{n-1}(X_K(K)),\EEx)
-\]
-Note that $X_{K'}(K') = X_{K}(K')$. Passing to limits now defines
-\[ 
-\Hom_\text{qc}(X_{K}(K'),\EEx) \to \Hom_\text{qc}(X_K(K)),\EEx)
+\Hom_{en-1}(X(K'),\EEx) \to \Hom_{n-1}(X(K)),\EEx)
+\]
+Passing to limits now defines
+\[ 
+\Hom_\text{qc}(X(K'),\EEx) \to \Hom_\text{qc}(X(K)),\EEx)
 \]
@@
 \begin{equation}\label{eq:transfer}
-\Hom_m(X_K(K),\EEx)  \iso  \Hom_{m}(Y_{L}(L),\EEx).
-\end{equation}
-The isomorphism \eqref{eq:transfer} is an instance of {\it transfer} of (certain) quasicharacters between $X_K(K)$ and $Y_{L}(L)$. 
+\Hom_m(X(K),\EEx)  \iso  \Hom_{m}(Y(L),\EEx).
+\end{equation}
+The isomorphism \eqref{eq:transfer} is an instance of {\it transfer} of (certain) quasicharacters between $X(K)$ and $Y(L)$. 
 We now recognize this transfer of quasicharacters as a consequence of the equivalence of categories of quasicharacter sheaves \eqref{eq:categorical_transfer}.

### 2014-08-25 crelle-dictionary.tex
More work on intro

--- 2014-08-25 crelle-dictionary.tex
@@
 we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\qcs{E}$. 
-In this way we are led to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ (\S\ref{sec:category}).
+In this way we are led to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ (\S\ref{ssec:category}).
 Objects in $\QC(G)$ are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$
@@
 We find that the group homomorphism 
-\begin{equation}
+\[
 T_G: \QCiso{G} \to G(\FF_q)^*
-\end{equation}
+\]
 provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$, where $\Weil{} \subset \Gal({\bar\FF}_q/\FF_q)$ is the Weil group for $\FF_q$.
@@
 We find that the general case can be understood from these two extreme cases, using the component group sequence
-\begin{equation}
+\[
 0 \to G^0 \to G \to \pi_0(G) \to 0.
-\end{equation}
-Using pullbacks of quasicharacter sheaves (\S\ref{sec:Frob}), we obtain a diagram
-\begin{equation} \label{eq:intro-snake}
+\]
+Using pullbacks of quasicharacter sheaves (\S\ref{ssec:Frob}), we obtain a diagram
+\[
   \begin{tikzcd}[row sep=20, column sep=20]
@@
   \end{tikzcd}
-  \end{equation}
-The rows of this diagram are exact (\S\S\ref{ssec:restriction},\ref{ssec:component}), so we may apply the snake lemma to prove the main theorem of the paper%, Theorem~\ref{thm:snake} $\QCiso{G}$ into a short exact sequence
+\]
+The rows of this diagram are exact (\S\S\ref{ssec:restriction},\ref{ssec:component}), so we may apply the snake lemma to prove the main theorem of the paper
 \begin{theorem*}[{Thm. \ref{thm:snake}}]
@@
 If $G$ is a smooth commutative group scheme over $\FF_q$ then
-\begin{equation}
+\[
 \Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx),
-\end{equation}
+\]
+for all quasicharacter sheaves $\qcs{L}$ on $G$.
 \end{theorem*}
-for all quasicharacter sheaves $\qcs{L}$ on $G$.
 
 %Here we also see the importance of working with Weil sheaves: sheaves on $G$ itself only allow us to geometrize characters with compact image.
-%We conclude in Section~\ref{sec:basechange} by
+%We conclude in Section~\ref{ssec:basechange} by
 %giving functorial versions of the restriction and norm homomorphisms 
@@
 
-As indicated above, our interest in the function-sheaf dictionary for smooth commutative group schemes over finite fields comes from an application to $p$-adic representation theory. 
-We found, however, that this application applies to all local fields $K$ with finite residue field $\Fq$ and all connected commutative algebraic groups $X_K$ over $K$ that do not contain a subgroup of type $\mathbb{G}_\text{a}$, such as abelian varieties, unipotent $K$-wound groups and, of course, algebraic tori.
-Such algebraic groups $X_K$ always admit a Neron model $X$ over $R$, the ring of integers of $K$.
-In this paper we show that quasicharacters of $X_K$ are geometrized and categorified by quasicharacter sheaves on the
+As indicated above, our interest in the function-sheaf dictionary for smooth commutative group schemes
+over finite fields comes from an application to $p$-adic representation theory. 
+However, we found that our method of passing from $p$-adic tori to group schemes over $\FF_q$ applies more generally to
+any local field $K$ with finite residue field $\Fq$ and any algebraic group $X_K$ that admits a N\'eron model $X$ over $R$, the ring of integers of $K$.
+This class of groups includes abelian varieties and unipotent $K$-wound groups in addition to the tori we initially considered.
+In this paper we show that quasicharacters of $X(K)$ are geometrized and categorified by quasicharacter sheaves on the
 Greenberg transform $\Gr_R(X)$ of the N\'eron model $X$.
 Although not locally of finite type, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and also a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
-This allows us to adapt our work on quasicharacter sheaves to construct a category $\QC(X_K)$ of quasicharacter sheaves for $X_K$, which are certain sheaves on $\Gr_R(X)\times_{\Spec{\Fq}} \Spec{\bFq}$, with extra structure.
-The ability to generalize the function-sheaf dictionary to non-connected group schemes, of which the component group of the special fibre of the N\'eron model $X$ is an important example, plays a crucial role in this application.
-%since these group schemes are not connected in general.
-
-Section~\ref{sec:applications} gives applications of quasicharacter sheaves to commutative algebraic groups over local fields.
-We begin with a review of N\'eron models and of the Greenberg transform in Section~\ref{ssec:rev_Greenberg}.  We then
-define, in Section~\ref{ssec:qc_on_GN}, a quasicharacter sheaf for an algebraic group over a local field to be a quasicharacter
-sheaf on the Greenberg transform of the N\'eron model.  In Theorem~\ref{thm:QCXK}, we translate our results from earlier sections
-to give a description of the isomorphism classes and automorphism groups
-in the category of quasicharacter sheaves on such an algebraic group.
-We specialize to $p$-adic tori in Section~\ref{ssec:qc_tori}, and discuss
-Weil restriction and base change over local fields in Section~\ref{ssec:wrK}.
-Finally, we give a categorical version of a result of Chai and Yu \cite{chai-yu:01a},
+This structure allows us to adapt our work on quasicharacter sheaves to construct (\S\ref{ssec:qc_on_GN}) a category $\QC(X_K)$
+of quasicharacter sheaves for $X_K$, which are certain sheaves on $\Gr_R(X)\times_{\Spec{\Fq}} \Spec{\bFq}$, with extra structure.
+The ability to generalize the function-sheaf dictionary to non-connected group schemes plays a crucial role in this application.
+
+Having defined quasicharacter sheaves for groups over $K$ and $\Fq$, we consider how
+these categories are related as $K$ and $\Fq$ vary.  We describe (\S\ref{ssec:basechange}) functors between categories
+of quasicharacter sheaves that model restriction and norm homomorphisms of character groups $G(k')^* \to G(k)^*$ and $G(k)^* \to G(k')^*$,
+and describe how quasicharacter sheaves behave under Weil restriction (\S\ref{ssec:wrK}).  We also give (\S\ref{ssec:transfer})
+a categorical version of a result of Chai and Yu \cite{chai-yu:01a},
 relating quasicharacter sheaves for tori over different local fields, even local fields
@@
 
-Specializing to the case when $X_K$ is an algebraic torus $T$ over $K$, and writing $\underline{T}$ for the Neron model $X$ in this case, this paper gives a canonical short exact sequence 
-\begin{equation}
-0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{T} \to \Hom_\text{qc}(T(K),\EEx) \to 0,
-\end{equation}
-where $\Hom_\text{qc}(T(K),\EEx)$ denoted the group of quasicharacters of $T(K)$.
-We further show that automorphism groups in the $\QC(T)$ are given, for every quasicharacter sheaf $\qcs{F}$ for $T$, by
-\begin{equation}
-\Aut(\qcs{F}) \iso (\check{T}_\ell)^{\Weil{K}}
-\end{equation}
+Specializing to the case that $X = T$ is the N\'eron model of an algebraic torus (\S\ref{ssec:qc_tori}), 
+we give a canonical short exact sequence 
+\[
+0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{T_K} \to \Hom_\text{qc}(T(K),\EEx) \to 0,
+\]
+where $\Hom_\text{qc}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
+We further show that automorphism groups in $\QC(T)$ are given, for every quasicharacter sheaf $\qcs{F}$ for $T_K$, by
+\[
+\Aut(\qcs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
+\]
 where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
@@
 By any measure, there are more quasicharacter sheaves for $T$ than quasicharacters of $T(K)$.  
-%\todo{Maybe move this from the introduction into the body of the paper somewhere.}
 In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization of complete Langlands parameters for $p$-adic groups 
-%as equivariant perverse sheaves on Vogan varieties 
 and, in the process, is led to study the representations of all the pure rational forms of the $p$-adic group simultaneously.
 A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group \cite{bernstein:vogan_conference}.
-Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to characters of all the pure rational forms of $T$.
-
-%\subsection{Comparison with character sheaves}
-
-The process of creating a category from the group of quasicharacters of a $p$-adic  torus, as explained above, informs our choice of the term quasicharacter sheaf in this paper.
+Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to quasicharacters of all the pure rational forms of $T$.
+
+The process of creating a category from the group of quasicharacters of a $p$-adic  torus informs our choice of the term quasicharacter sheaf in this paper.
 We also want to situate our terminology in a historical context.
@@
 in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
-The interesting new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in this context.
-
-\tableofcontents
-
-\section{The category of quasicharacter sheaves}
-
-\subsection{Notations}\label{sec:notation}
+The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in this context.
+
+%\tableofcontents
+
+\section{The category of quasicharacter sheaves} \label{sec:category}
+
+\subsection{Notations}\label{ssec:notation}
 
@@
 
-\subsection{The category of quasicharacter sheaves}\label{sec:category}
+\subsection{The category of quasicharacter sheaves}\label{ssec:category}
 
@@
 
-We will describe the group $\QCiso{G}$ in Theorem \ref{thm:snake}
-and the sets $\Hom(\qcs{L},\qcs{L}')$ in Theorem \ref{thm:autornaught}; in this way we provide a complete description of the category $\QC(G)$.
+We will describe the group $\QCiso{G}$ in Theorem~\ref{thm:snake}
+and the sets $\Hom(\qcs{L},\qcs{L}')$ in Theorem~\ref{thm:autornaught}; in this way we provide a complete description of the category $\QC(G)$.
 %
@@
 
-\subsection{Trace of Frobenius}\label{sec:Frob}
+\subsection{Trace of Frobenius}\label{ssec:Frob}
 
@@
 %A Weil sheaf $(\gqcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gqcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
-%We now briefly review this point of view for later use in Section~\ref{sec:basechange}; see also \cite{deligne:80a}*{Def.~1.1.10}.  If $w \ceq \Frob{}^n$ we write $w_G$ for $\Frob{G}^n$.
+%We now briefly review this point of view for later use in Section~\ref{ssec:basechange}; see also \cite{deligne:80a}*{Def.~1.1.10}.  If $w \ceq \Frob{}^n$ we write $w_G$ for $\Frob{G}^n$.
 %For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gqcs{L}\to \gqcs{L}$ by $\varphi(w) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi);$
@@
 
-%\subsection{Morphisms of quasicharacter sheaves}\label{sec:mor}
+%\subsection{Morphisms of quasicharacter sheaves}\label{ssec:mor}
 
@@
   Composing with the splitting $\Weil{} \to \W(G,\bg)$ yields an $\ell$-adic character
-  $\rho_g : \Weil{} \to \EEx$, which is the same as the Trace of Frobenius defined in Section~\ref{sec:Frob}, for every $\Fq$ rational point $g$ on $G$:
+  $\rho_g : \Weil{} \to \EEx$, which is the same as the Trace of Frobenius defined in Section~\ref{ssec:Frob}, for every $\Fq$ rational point $g$ on $G$:
   $
@@
 
-\subsection{Base change}\label{sec:basechange}
+\subsection{Base change}\label{ssec:basechange}
 
@@
 as taking the action $\varphi$ of $\Weil{k}$ on $\gqcs{L}$
-defined in Section~\ref{sec:category} and restricting it to the subgroup $\Weil{k'}$.
+defined in Section~\ref{ssec:category} and restricting it to the subgroup $\Weil{k'}$.
 
@@
 We now define a category which will geometrize quasicharacters of $X_K(K)$.
-We begin by considering the rigid monoidal category $\QC(\Gr_R(X))$ defined in Section~\ref{sec:category} without insisting that the commutative group scheme is smooth.
+We begin by considering the rigid monoidal category $\QC(\Gr_R(X))$ defined in Section~\ref{ssec:category} without insisting that the commutative group scheme is smooth.
 
@@
 
-\subsection{Transfer of quasicharacters}\label{sec:transfer}
+\subsection{Transfer of quasicharacters}\label{ssec:transfer}
 

### 2014-08-25 crelle-dictionary.tex

@@
 
-We now define a category which will geometrize quasicharacters of $X_K(K)$.
+We now define a category which will geometrize quasicharacters of $X(K)$.
 We begin by considering the rigid monoidal category $\QC(\Gr_R(X))$ defined in Section~\ref{ssec:category} without insisting that the commutative group scheme is smooth.
@@
 \begin{equation}\label{eq:transfer}
-\Hom_m(X_K(K),\EEx)  \iso  \Hom_{m}(Y_{L}(L),\EEx).
+\Hom_m(X(K),\EEx)  \iso  \Hom_{m}(Y(L),\EEx).
 \end{equation}
-The isomorphism \eqref{eq:transfer} is an instance of {\it transfer} of (certain) quasicharacters between $X_K(K)$ and $Y_{L}(L)$. 
+The isomorphism \eqref{eq:transfer} is an instance of {\it transfer} of (certain) quasicharacters between $X(K)$ and $Y(L)$. 
 We now recognize this transfer of quasicharacters as a consequence of the equivalence of categories of quasicharacter sheaves \eqref{eq:categorical_transfer}.

### 2014-08-25 crelle-dictionary.tex
Fixed a few typos.

@@
   On the other hand, we have already seen that $\trFrob{\qcs{L}} : G(\Fq) \to \EEx$
-  is a group homomorphism. Since $G$ is an algebraic group over $\Fq$, it is a
-  variety over $\Fq$ and thus $G(\Fq)$ is finite.
+  is a group homomorphism. 
+  Since $G$ is an algebraic group over $\Fq$, $G(\Fq)$ is finite.
   Therefore $\trFrob{\qcs{L}}(g) = \rho_g(\Frob{})$ is a root of unity
@@
   representations of $\pi_1(G,\bg)$ and $\ell$-adic local systems on $G$. Let
-  $\qcs{L}_0$ be a local system on $G$ in the isomorphism class
+  $\qcs{E}$ be a local system on $G$ in the isomorphism class
   determined by this $\ell$-adic character of $\pi_1(G,\bg)$.
@@
 $\qcs{E} \iso (\Lang_!
-V)_\psi$, the $\psi$-isotypic component of the push-forward $\Lang_* V$ ($\Lang$ is proper, so $\Lang_* = \Lang_!$) of the constant sheaf $V$ on $G$ equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes\qcs{E}$ determined by $V\to V\otimes V$.
+V)_\psi$, the $\psi$-isotypic component of the push-forward $\Lang_* V$ of the constant sheaf $V$ on $G$ equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes\qcs{E}$ determined by $V\to V\otimes V$.
 Moreover, $\Aut(\qcs{E})$ is the group of automorphisms of $\rho : V\to V$ for which 
@@
 In particular, as we have already seen in Section~\ref{sec:etale}, for a given quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ there may be a different isomorphism $\mu' : \bm^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$ for which $\qcs{L}'=(\gqcs{L},\mu',\phi)$ is also a quasicharacter sheaf on $G$, not isomorphic to $\qcs{L}$ in $\QC(G)$.
-Indeed, Proposition~\ref{prop:etale-iso} shows that when $G$ is \'etale, $\Hh^2(\bG,\EEx)^{\Frob{}}$ measures the possibilities for $\mu'$.
-In other words, the common perspective on the function-sheaf dictionary leads only, and exactly, to the part of category of quasicharacter sheaves that is {\it completely invisible} to the trace of Frobenius!
-
-We will see in Section~\ref{sec:main} that, for any smooth commutative group scheme $G$, the part of category of quasicharacter sheaves that is invisible to the trace of Frobenius are measured by $\Hh^2(\pi_0(\bG),\EEx)^{\Frob{}}$.
+Indeed, Proposition~\ref{prop:etale-iso} shows that when $G$ is \'etale, $\Hh^2(\bG,\EEx)^{\Weil{}}$ measures the possibilities for $\mu'$.
+The common perspective on the function-sheaf dictionary leads only to the part of category of quasicharacter sheaves that is invisible to the trace of Frobenius.
+
+We will see in Section~\ref{sec:main} that, for any smooth commutative group scheme $G$, the part of category of quasicharacter sheaves that is invisible to the trace of Frobenius are measured by $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
 %\end{remark}
@@
 \[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{X_K} \to \Hom_\text{qc}(X(K),\EEx) \to 0;
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{}} \to \QCiso{X_K} \to \Hom_\text{qc}(X(K),\EEx) \to 0;
 \] 
@@
 \begin{equation}
-0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Frob{}} \to \QCiso{T} \to \Hom_\text{qc}(T(K),\EEx) \to 0.
+0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{T} \to \Hom_\text{qc}(T(K),\EEx) \to 0.
 \end{equation}

### 2014-08-25 crelle-dictionary.tex
homomorphism to morphism, a couple typos

--- 2014-08-25 crelle-dictionary.tex
@@
 %
-If one wishes to make a category from this class of local systems, one is led to consider sheaf homorphisms $\qcs{E} \to \qcs{E}'$ which are compatible with particular choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E'}$.
-{\it A priori}, these sheaf homomorphisms do not form a category, but since $G$ is connected, the existence of the isomorphism \eqref{introbox} for $\qcs{E}$ makes it unique; as a consequence, there is no impediment to categorifying the dictionary in this case.
-\todo{clarify}
-
-If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, however, then the isomorphism \eqref{introbox} need not be unique, so one must keep track of the choice.
+If one wishes to make a category from this class of local systems, one is led to consider morphisms $\qcs{E} \to \qcs{E}'$ of sheaves which are compatible with particular choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E'}$.
+{\it A priori}, the composition $\qcs{E} \to \qcs{E}' \to \qcs{E}''$ of two such morphisms need not be compatible with the choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E}''$ since the choice for $\qcs{E}'$ might differ.
+However, for connected $G$ the isomorphism \eqref{introbox} is unique if it exists, and there is no impediment to making the dictionary categorical.
+
+If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, then the isomorphism \eqref{introbox} need not be unique, so one must keep track of the choice.
 This leads to the category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is a chosen isomorphism of local systems on $G\times G$.
@@
 In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\FF_q)$, but that group homomorphism need not be injective; consequently,
-every character of $G(\Fq)$ may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely in the category of pairs. 
+every character of $G(\FF_q)$ may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely in the category of pairs. 
 While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious: if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\FF_q)$ then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
@@
 and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves satisfying a certain compatibility condition.
-Morphisms in $\QC(G)$ are then homomorphisms of Weil sheaves which are compatible with the extra structure.
+Morphisms in $\QC(G)$ are then morphisms of Weil sheaves which are compatible with the extra structure.
 
@@
 \]
-provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$, where $\Weil{} \subset \Gal({\bar\FF}_q/\FF_q)$ is the Weil group for $\FF_q$.
+provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$.
 One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.

### 2014-08-25 crelle-dictionary.tex
Citelists; removed lft.

--- 2014-08-25 crelle-dictionary.tex
@@
 From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields, as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3}, gives us all we need, as we briefly recall.
-\todo{Fix citelist} %\citelist{\cite{deligne:SGA4.5}*{Sommes trig.},\cite{laumon:87a}*{1.1.3}}
+%\todo{Fix citelist} %\citelist{\cite{deligne:SGA4.5}*{Sommes trig.},\cite{laumon:87a}*{1.1.3}}
 The key observation is that, by \'etale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
@@
 Let $K$ be a local field (in the sense of Serre) with residue field $\Fq$. 
-In this section we consider connected commutative algebraic groups over $K$ that admit a N\'eron model, by which we mean an lft N\'eron model.
+In this section we consider connected commutative algebraic groups over $K$ that admit a N\'eron model, by which we mean a locally of finite type N\'eron model.
 By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected commutative algebraic groups over $K$ that contain no subgroup of type $\mathbb{G}_\text{a}$.

### 2014-08-25 crelle-dictionary.tex
Typo. Flow. Spacing.

@@
 \]
-arising from the spectral sequence, the isomorphism $S_G$ allows us to show (\S\ref{ssec:SandT}) that $\TrFrob{G}$ is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$.
-We find that the group homomorphism 
+arising from the spectral sequence, the isomorphism $S_G$ allows us to show (\S\ref{ssec:SandT}) that 
+%$\TrFrob{G}$ is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$. We find that 
+the group homomorphism 
 \[
@@
 Having understood quasicharacter sheaves on commutative smooth group schemes over $\FF_q$ in two extreme cases --
-connected algebraic groups and \'etale commutative group schemes -- we turn to the general case.
-We find that the general case can be understood from these two extreme cases, using the component group sequence
+connected commutative algebraic groups and \'etale commutative group schemes -- we turn to the general case.
+We find that the general case can be understood from these two extreme cases using the component group sequence
 \[
@@
     & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
-    0 \rar & \pi_0(G)(\FF_q)^* \rar & G(\Fq)^* \rar & G^0(\FF_q)^* \rar & 0,
+    0 \rar & \pi_0(G)(\FF_q)^* \rar & G(\Fq)^* \rar & G^0(\FF_q)^* \rar & 0.
   \end{tikzcd}
@@
 %For the second, f
-Fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the group homomorphism $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
+Fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the group homomorphism from $\Aut(\qcs{L})$ to $\Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
 This homomorphism is injective because morphisms of sheaves are determined by the linear transformations induced on stalks.  

### 2014-08-25 crelle-dictionary.tex
Added etale descent reference

@@
 We must show that comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
-To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$. 
+To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$ \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}.
 In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.

### 2014-08-25 crelle-dictionary.tex
Typos fixed in Applications

@@
 Suppose $X_K\in \mathcal{N}_K$ with N\'eron model $X$ and $Y_{L}\in \mathcal{N}_L$ with N\'eron model $Y$.
-Suppose $m$ is a non-negative integers such that 
-\[
-\OK/\varpi_K^m\OK \iso \OL/\varpi_L^m\OL
+Suppose $m$ is a positive integer such that 
+\[
+\OK/\varpi_K^{m}\OK \iso \OL/\varpi_L^{m}\OL.
 \]
@@
 \begin{equation}\label{eq:schematic_transfer}
-X \times_{\Spec{\OK}} \Spec{\OK/\varpi_K^m\OK} \iso Y \times_{\Spec{\OL}} \Spec{\OL/\varpi_L^m\OL}
+X \times_{\Spec{\OK}} \Spec{\OK/\varpi_K^{m}\OK} \iso Y \times_{\Spec{\OL}} \Spec{\OL/\varpi_L^{m}\OL}
 \end{equation}
-as smooth group schemes over $\OK/\varpi_K^m\OK$. 
+as smooth group schemes over $\OK/\varpi_K^{m}\OK$. 
 Then
 $
-\Gr^{\OK}_m(X) \iso \Gr^{\OL}_{m}(Y)
+\Gr^{\OK}_{m-1}(X) \iso \Gr^{\OL}_{m-1}(Y)
 $
@@
 \begin{equation}\label{eq:categorical_transfer}
-\QC(\Gr^{\OK}_m(X)) \cong \QC(\Gr^{\OL}_{m}(Y))
+\QC(\Gr^{\OK}_{m-1}(X)) \cong \QC(\Gr^{\OL}_{m-1}(Y))
 \end{equation}
@@
 \begin{equation}\label{eq:transfer}
-\Hom_m(X(K),\EEx)  \iso  \Hom_{m}(Y(L),\EEx).
+\Hom_{m-1}(X(K),\EEx)  \iso  \Hom_{m-1}(Y(L),\EEx).
 \end{equation}
@@
 \end{equation}
-Note that if $T_K$ and $M_L$ are $n$-congruent, then they are $m$ congruent for every
+Note that if $T_K$ and $M_L$ are $n$-congruent, then they are $m$-congruent for every
 $m \leq n$.
@@
 Now let $T$ be a N\'eron model for $T_K$ and let $M$ be a N\'eron model for $M_L$.
-One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes between the
-$T \times_{\Spec{\OK}} \Spec{\OK/\varpi_n\OK}$ and $M \times_{\Spec{\OL}} \Spec{\OL/\varpi^n\OL}$, assuming that $T_K$ and $M_L$ are sufficiently congruent.
+One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes 
+\[
+T \times_{\Spec{\OK}} \Spec{\OK/\varpi_K^n\OK} \iso M \times_{\Spec{\OL}} \Spec{\OL/\varpi_L^n\OL}
+\] 
+assuming that $T_K$ and $M_L$ are sufficiently congruent.
 They define a quantity $h$ (the smallest integer so that $\varpi^h$ lies in the
-Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}) and show  that if $n > 3h$ and $T_K$ and $M_L$ are $n$-congruent then there is a canonical isomorphism of smooth group schemes
+Jacobian ideal associated to a natural embedding of $T_K$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}) and show  that if $n > 3h$ and $T_K$ and $M_L$ are $n$-congruent then there is a canonical isomorphism of smooth group schemes
  $
-\Gr_{n-3h}(T) \to \Gr_{n-3h}(M)
+\Gr_{n-3h-1}(T) \to \Gr_{n-3h-1}(M)
  $
  determined by $\alpha, \beta$ and $\phi$ \cite{chai-yu:01a}*{Thm. 8.5}.
-Combining this with the paragraph above gives an instance of the geometrization and categorification of the transfer of quasicharacters.
+Combining this with the paragraph above gives the following instance of the geometrization and categorification of the transfer of quasicharacters.
 
@@
  \[
- \QC(\Gr^{\OK}_m(T)) \iso \QC(\Gr^{\OL}_m(M))
+ \QC(\Gr^{\OK}_{m-1}(T)) \iso \QC(\Gr^{\OL}_{m-1}(M))
  \]
@@
  \[
-\Hom_m(T_K(K), \EEx) \iso  \Hom_m(M_L(L), \EEx)
+\Hom_{m-1}(T_K(K), \EEx) \iso  \Hom_{m-1}(M_L(L), \EEx)
  \]
@@
 quasicharacter sheaves; their knowledge and help have been invaluable.
-We thank Takashi Suzuki for some very helpful observations and suggestions, including those related to our use of the Hochschild-Serre spectral sequence.
-We thank Joseph Bernstein for suggesting a connection between our category of quasicharacter sheaves on $G$ and his sheaves on the stacky classifying space of $G$.
+We thank Takashi Suzuki for some very helpful observations and suggestions, especially related to our use of the Hochschild-Serre spectral sequence.
+We thank Joseph Bernstein for suggesting a connection between our category of quasicharacter sheaves for $p$-adic tori and quasicharacters of its pure rational forms.
 We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and drawing our attention to their result on Weil restriction and the Greenberg transform.

### 2014-08-25 crelle-dictionary.tex
Minor edits. Added internal reference
.. when we used descent the second time.

@@
 The key observation is that, by \'etale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
+(Note that this is a particular case of the argument in the proof of Proposition~\ref{prop:finite}.)
 Using the equivalence given by $\Lang^*$, if $\Lang^*\qcs{E} = V$ with character $\psi$ and isomorphism $V\to V\otimes V$ then 
@@
 be the functor obtained by pullback along the canonical closed immersion 
-$\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$ of $k$-schemes
-given by \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}.
+\[\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})\] of $k$-schemes.
 The following diagram commutes:
@@
 \begin{proof}
-This result follows immediately from Lemma~\ref{lem:pullback} together with the identifications
+The closed immersion $\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$ is given by \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}.
+Proposition~\ref{prop:csbe} follows immediately from Lemma~\ref{lem:pullback} together with the identifications
 \[
@@
 Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
-as taking the action $\varphi$ of $\Weil{k}$ on $\gqcs{L}$
-defined in Section~\ref{ssec:category} and restricting it to the subgroup $\Weil{k'}$.
+as taking the action $\varphi$ of the Weil group for $k$%, $\Weil{k}$, 
+on $\gqcs{L}$
+defined in Section~\ref{ssec:category} and restricting it to the Weil group for $k'$.
+%, $\Weil{k'}$.
 

### 2014-08-25 crelle-dictionary.tex
New abstract.

@@
 \begin{abstract}
-Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
-this paper extends Deligne's function-sheaf dictionary to smooth commutative group schemes over finite fields.
+By extending the scope of function-sheaf dictionary for connected commutative algebraic groups, we find a geometrization of characters of all smooth commutative group schemes over finite fields.
+As an application, we explain how to geometrize and categorify quasicharacters of all connected commutative algebraic groups over non-Archimedean local fields that admit a locally finite type Neron model, such as algebraic tori, abelian varieties and unipotent K-wound groups.
 \end{abstract}

### 2014-08-25 crelle-dictionary.tex
Slight improved the reference to Weibel.

@@
 
-The zeroth page of the Hochschild-Serre spectral sequence is a double complex $E^{\bullet, \bullet}$ defined by
+The zeroth page of the Hochschild-Serre spectral sequence, as in \cite{Vakil:spectral_sequences} following \cite{Weibel:Homological_Algebra}*{Ch 5 and \S 7.5}, for example,
+is a double complex $E^{\bullet, \bullet}$ defined by
 \[
@@
 
-The latter two claims follow from tracing through the definition of latter pages in the spectral sequence; see \cite{Vakil:spectral_sequences} following \cite{Weibel:Homological_Algebra}*{Ch 5}, for example.
+The latter two claims follow from tracing through the definition of latter pages in the spectral sequence.
 \end{proof}

### 2014-08-25 crelle-dictionary.tex
Abstract under construction

@@
 \begin{abstract}
-By extending the scope of function-sheaf dictionary for connected commutative algebraic groups, we find a geometrization of characters of all smooth commutative group schemes over finite fields.
-As an application, we explain how to geometrize and categorify quasicharacters of all connected commutative algebraic groups over non-Archimedean local fields that admit a locally finite type Neron model, such as algebraic tori, abelian varieties and unipotent K-wound groups.
+We extend the function-sheaf dictionary to smooth commutative group schemes over finite fields. 
+As an application, we explain how to geometrize and categorify quasicharacters of  algebraic tori, abelian varieties and unipotent K-wound groups over connected commutative algebraic groups over non-Archimedean local fields that admit a Neron model locally of finite type,
 \end{abstract}
@@
  from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
- is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} or \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}.
+ is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} and \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}.
  This functor preserves local constancy, so takes local systems to local systems.

### 2014-08-25 crelle-dictionary.tex
New abstract, again.

@@
 \begin{abstract}
-We extend the function-sheaf dictionary to smooth commutative group schemes over finite fields. 
-As an application, we explain how to geometrize and categorify quasicharacters of  algebraic tori, abelian varieties and unipotent K-wound groups over connected commutative algebraic groups over non-Archimedean local fields that admit a Neron model locally of finite type,
+We introduce the category of quasicharacter sheaves on smooth commutative group schemes $G$ over finite fields $k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
+We show that the group of isomorphism classes of quasicharacter sheaves is an extension of the group of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
+As an application, we find a category of sheaves whose isomorphism classes correspond to quasicharacters in the case of algebraic tori, abelian varieties and unipotent wound groups over local fields. 
+In this geometrization of quasicharacters, our sheaves are local systems on
+Greenberg transforms of locally finite type N\'eron models.
 \end{abstract}

### 2014-08-25 crelle-dictionary.tex
Proof reading.

@@
 \newcommand{\bH}{\bar{H}}
+\newcommand{\brho}{{\bar\rho}}
 %% Spacing control
@@
 
-As Deligne explained in \cite{deligne:SGA4.5}*{Sommes trig.}, if $G$ is a connected commutative algebraic group over $\FF_q$, then the trace of Frobenius provides a bijection between the group $G(\FF_q)^*$ of $\ell$-adic characters of $G(\FF_q)$ and isomorphism classes of rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which
+As Deligne explained in \cite{deligne:SGA4.5}*{Sommes trig.}, if $G$ is a connected commutative algebraic group over a finite field $k$, then the trace of Frobenius provides a bijection between the group $G(\Fq)^*$ of $\ell$-adic characters of $G(\Fq)$ and isomorphism classes of rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which
 \begin{equation}\label{introbox}
@@
 If one wishes to make a category from this class of local systems, one is led to consider morphisms $\qcs{E} \to \qcs{E}'$ of sheaves which are compatible with particular choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E'}$.
-{\it A priori}, the composition $\qcs{E} \to \qcs{E}' \to \qcs{E}''$ of two such morphisms need not be compatible with the choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E}''$ since the choice for $\qcs{E}'$ might differ.
+{\it A priori}, the composition $\qcs{E} \to \qcs{E}' \to \qcs{E}''$ of two such morphisms need not be compatible with the choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E}''$.
+% since the choice for $\qcs{E}'$ might differ.
  However, for connected $G$ the isomorphism \eqref{introbox} is unique if it exists, and there is no impediment to making the dictionary categorical.
 
-If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, then the isomorphism \eqref{introbox} need not be unique, so one must keep track of the choice.
+If $G$ is a commutative algebraic group over $\Fq$ which is not connected, then the isomorphism \eqref{introbox} need not be unique, so one must keep track of the choice.
 This leads to the category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is a chosen isomorphism of local systems on $G\times G$.
 %If the component group scheme $\pi_0(G)$ is not cyclic, then 
-In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\FF_q)$, but that group homomorphism need not be injective; consequently,
-every character of $G(\FF_q)$ may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely in the category of pairs. 
-While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious: if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\FF_q)$ then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
-
-In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$,
+In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\Fq)$, but the epimomorphism need not be injective; consequently,
+every character of $G(\Fq)$ may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely in the category of pairs. 
+While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious: if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\Fq)$ then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
+
+In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\Fq$,
 we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\qcs{E}$. 
 In this way we are led to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ (\S\ref{ssec:category}).
-Objects in $\QC(G)$ are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$
-and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves satisfying a certain compatibility condition.
+Objects in $\QC(G)$ are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\Fq}} \Spec{\bFq}$
+and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves satisfying certain compatibility conditions.
 Morphisms in $\QC(G)$ are then morphisms of Weil sheaves which are compatible with the extra structure.
 
-We first test the category of quasicharacter sheaves by examining its objects on \'etale commutative group schemes $G$ over $\FF_q$ (\S\ref{sec:etale});
+We first test the category of quasicharacter sheaves by examining its objects on \'etale commutative group schemes $G$ over $\Fq$ (\S\ref{sec:etale});
 \'etale group schemes form a counterpoint to connected algebraic groups, since the component group of any smooth group scheme is an \'etale group scheme.
 Our key tools for understanding the trace of Frobenius in the \'etale case are a reinterpretation of $\QC(G)$ in terms of stalks (\S\ref{ssec:stalks}) and a
-relationship with the Hochschild-Serre spectral sequence (\S\ref{ssec:E}) for $\Weil{} \ltimes \bG$, where $\Weil{} \subset \Gal({\bar\FF}_q/\FF_q)$ is the Weil group for $\FF_q$.
+relationship with the Hochschild-Serre spectral sequence (\S\ref{ssec:E}) for $\Weil{} \ltimes \bG$, where $\Weil{} \subset \Gal(\Fq/\Fq)$ is the Weil group for $\Fq$.
 We define (\S\ref{ssec:S}) an isomorphism $S_G$ from $\QCiso{G}$ to the second cohomology of the total space of the spectral sequence
@@
 \[
-T_G: \QCiso{G} \to G(\FF_q)^*
+T_G: \QCiso{G} \to G(\Fq)^*
 \]
@@
 The fact that $T_G$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$
-determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
+determine the same character of $G(\Fq)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
 
@@
 %
-%The appearance of $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ and the trace of Frobenius gives an isomorphism $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\FF_q$, then $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ measures the kernel of $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$.
+%The appearance of $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ and the trace of Frobenius gives an isomorphism $T_G: \QCiso{G} \to \Hom(G(\Fq),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\Fq$, then $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ measures the kernel of $T_G: \QCiso{G} \to \Hom(G(\Fq),\EEx)$.
 %This observation makes plain the fact that  . . .
@@
 
-Having understood quasicharacter sheaves on commutative smooth group schemes over $\FF_q$ in two extreme cases --
-connected commutative algebraic groups and \'etale commutative group schemes -- we turn to the general case.
-We find that the general case can be understood from these two extreme cases using the component group sequence
+Having understood quasicharacter sheaves on commutative smooth group schemes over $\Fq$ in two extreme cases --
+connected commutative algebraic groups and \'etale commutative group schemes -- we turn to the general case, using the component group sequence
 \[
@@
     & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
-    0 \rar & \pi_0(G)(\FF_q)^* \rar & G(\Fq)^* \rar & G^0(\FF_q)^* \rar & 0.
-  \end{tikzcd}
-\]
-The rows of this diagram are exact (\S\S\ref{ssec:restriction},\ref{ssec:component}), so we may apply the snake lemma to prove the main theorem of the paper
+    0 \rar & \pi_0(G)(\Fq)^* \rar & G(\Fq)^* \rar & G^0(\Fq)^* \rar & 0.
+  \end{tikzcd}
+\]
+The rows of this diagram are exact (\S\S\ref{ssec:restriction},\ref{ssec:component}), so we may apply the snake lemma to prove the main theorem of the paper,
 \begin{theorem*}[{Thm. \ref{thm:snake}}]
-If $G$ is a smooth commutative group scheme over $\FF_q$ then
-\[
-\TrFrob{G} : \QCiso{G} \to G(\FF_q)^*
+If $G$ is a smooth commutative group scheme over $\Fq$ then
+\[
+\TrFrob{G} : \QCiso{G} \to G(\Fq)^*
 \]
@@
 \end{theorem*}
-We also illuminate the nature of the category $\QC(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing that
+We also illuminate the nature of the category $\QC(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing
 \begin{theorem*}[{Thm. \ref{thm:autornaught}}]
-If $G$ is a smooth commutative group scheme over $\FF_q$ then
+If $G$ is a smooth commutative group scheme over $\Fq$ then
 \[
@@
 over finite fields comes from an application to $p$-adic representation theory. 
-However, we found that our method of passing from $p$-adic tori to group schemes over $\FF_q$ applies more generally to
+However, we found that our method of passing from $p$-adic tori to group schemes over $\Fq$ applies more generally to
 any local field $K$ with finite residue field $\Fq$ and any algebraic group $X_K$ that admits a N\'eron model $X$ over $R$, the ring of integers of $K$.
@@
   $\qcs{L'} = (\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$ then
-  a morphism $\qcs{L} \to \qcs{L}'$ is a map $\rho : \gqcs{L} \to \gqcs{L'}$
+  a morphism $\rho : \qcs{L} \to \qcs{L}'$ is a map $\brho : \gqcs{L} \to \gqcs{L'}$
   of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
@@
   \begin{tikzcd}[column sep=40]
-  \Frob{G}^* \gqcs{L} \rar{\Frob{G}^* \rho} \arrow[swap]{d}{\phi} & \Frob{G}^* \gqcs{L'} \dar{\phi'}
-  & & \arrow[swap]{d}{\mu} m^* \gqcs{L} \rar{m^* \rho} & m^* \gqcs{L'} \dar{\mu'} \\
-  \gqcs{L} \rar{\rho} & \gqcs{L'}
+  \Frob{G}^* \gqcs{L} \rar{\Frob{G}^* \brho} \arrow[swap]{d}{\phi} & \Frob{G}^* \gqcs{L'} \dar{\phi'}
+  & & \arrow[swap]{d}{\mu} \bm^* \gqcs{L} \rar{\bm^* \brho} & \bm^* \gqcs{L'} \dar{\mu'} \\
+  \gqcs{L} \rar{\brho} & \gqcs{L'}
   & {} & \LxL \rar{\tight{1}{\rho\boxtimes \rho}{1}} & \gqcs{L'} \tight{0}{\boxtimes}{0} \gqcs{L'}
@@
 Suppose $\rho \in \Hom(\qcs{L},\qcs{L}')$.
-We prove the lemma by considering the linear transformations $\rho_{\bar g} : \gqcs{L}_{\bar g} \to \gqcs{L}_{\bar g}$ at the stalks above geometric points ${\bar g}$ on $G$ and showing that, either each $\rho_{\bar g}$ trivial or each $\rho_{\bar g}$ is an isomorphism.
+We prove the lemma by considering the linear transformations $\brho_{\bar g} : \gqcs{L}_{\bar g} \to \gqcs{L}_{\bar g}$ at the stalks above geometric points ${\bar g}$ on $G$ and showing that, either each $\brho_{\bar g}$ trivial or each $\brho_{\bar g}$ is an isomorphism.
 (This idea is expanded upon in Section~\ref{ssec:stalks}.)
 Let ${\bar e}$ be the geometric point above the identity $e$ for $G$ determined by our choice of algebraic closure $\bFq$ of $\Fq$.
-If $\rho_{\bar e} = 0$ then the second diagram in \ref{QC.4} implies that $\rho_{\bar g} = 0$ for all ${\bar g}$, in which case $\rho$ is trivial.
-On the other hand, if $\rho_{\bar e}$ is nontrivial then the second diagram in \ref{QC.4}  implies that $\rho_{\bar g}$ is nontrivial for all ${\bar g}$ and thus an isomorphism, since the stalk of quasicharacter sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
+If $\brho_{\bar e} = 0$ then the second diagram in \ref{QC.4} implies that $\brho_{\bar g} = 0$ for all ${\bar g}$, in which case $\rho$ is trivial.
+On the other hand, if $\brho_{\bar e}$ is nontrivial then the second diagram in \ref{QC.4}  implies that $\brho_{\bar g}$ is nontrivial for all ${\bar g}$ and thus an isomorphism, since the stalk of quasicharacter sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
 \end{proof}
@@
   commutes by \cite{laumon:87a}*{1.1.1.2}, where the ambient
-  hypothesis that $X$ is of finite type over $\Fq$ can be replaced by
-  the hypothesis that $X$ is locally of finite type over $\Fq$.
+ finite type hypothesis can be replaced by locally of finite type.
 
@@
 \[
-\QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)
+\boxtimes : \QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)
 \]
@@
 is essentially surjective, so we will only address that point here.
-
+%
 Set $G \ceq G_1\times G_2$
@@
 Observe that $p_1\circ f = q_1 \circ r_1$ and $p_2 \circ f = q_2\circ r_2$.
-
+%
 Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
@@
 It follows that \eqref{eq:fm} gives an isomorphism $\gqcs{L} \to  \gqcs{L}_1\boxtimes \gqcs{L}_2$.
-It is a matter of routine to show that this morphism satisfies
+It is routine to show that this morphism satisfies
 \ref{QC.3} as it applies here,
@@
 \begin{enumerate}
- \labitem{(qc.4)}{qc.4} an indexed set $\rho_x : \gqcs{L}_x \to \gqcs{L'}_x$
+ \labitem{(qc.4)}{qc.4} an indexed set $\brho_x : \gqcs{L}_x \to \gqcs{L'}_x$
   of linear transformations such that
@@
    \begin{tikzcd}[column sep=40]
-    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{}(x)} \rar{\rho_{\Frob{}(x)}} & \gqcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
+    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{}(x)} \rar{\brho_{\Frob{}(x)}} & \gqcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
     &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-    & \arrow[swap]{d}{\mu_{x,y}} \gqcs{L}_{x+y} \rar{\rho_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x,y}} \\
-    \gqcs{L}_x \rar{\rho_x} & \gqcs{L'}_x
-    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\rho_x\otimes\rho_y} & \gqcs{L'}_x \otimes\gqcs{L'}_y
+    & \arrow[swap]{d}{\mu_{x,y}} \gqcs{L}_{x+y} \rar{\brho_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x,y}} \\
+    \gqcs{L}_x \rar{\brho_x} & \gqcs{L'}_x
+    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\brho_x\otimes\brho_y} & \gqcs{L'}_x \otimes\gqcs{L'}_y
    \end{tikzcd}
@@
 Now suppose $\rho \in \Aut(\qcs{L})$.
-The second diagram in \ref{qc.4} shows that the association $x \mapsto \rho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{qc.4} shows that it factors through $G(\bFq)_{\Weil{}}$.
-Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism then defining $\rho_x$ as multiplication by $\rho(x)$ will satisfy the two diagrams.
+The second diagram in \ref{qc.4} shows that the association $x \mapsto \brho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{qc.4} shows that it factors through $G(\bFq)_{\Weil{}}$.
+Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism then defining $\brho_x$ as multiplication by $\rho(x)$ will satisfy the two diagrams.
 Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the resulting bijection is actually a group isomorphism.
@@
   Now let $(\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$
-  and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$.
+  and let $\lambda : \W(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$.
   Composing with the splitting $\Weil{} \to \W(G,\bg)$ yields an $\ell$-adic character
-  $\rho_g : \Weil{} \to \EEx$, which is the same as the Trace of Frobenius defined in Section~\ref{ssec:Frob}, for every $\Fq$ rational point $g$ on $G$:
+  $\lambda_g : \Weil{} \to \EEx$, which is the same as the Trace of Frobenius defined in Section~\ref{ssec:Frob}, for every $\Fq$ rational point $g$ on $G$:
   $
-  \rho_g(\Frob{}) =  \trFrob{\qcs{L}}(g).
+  \lambda_g(\Frob{}) =  \trFrob{\qcs{L}}(g).
   $
@@
   Since $G$ is an algebraic group over $\Fq$, $G(\Fq)$ is finite.
-  Therefore $\trFrob{\qcs{L}}(g) = \rho_g(\Frob{})$ is a root of unity
+  Therefore $\trFrob{\qcs{L}}(g) = \lambda_g(\Frob{})$ is a root of unity
   for every $g\in G(\Fq)$.  Since $\Weil{}$ is generated by
-  $\Frob{}$ and $\rho_g : \Weil{} \to \EEx$ is
-  a character, it follows that the image of $\rho_g$ is a finite group.
-  Thus, $\rho_g$ extends to an $\ell$-adic character of $\Gal(\bFq/\Fq)$,
-  which we will also denote $\rho_g$.
+  $\Frob{}$ and $\lambda_g : \Weil{} \to \EEx$ is
+  a character, it follows that the image of $\lambda_g$ is a finite group.
+  Thus, $\lambda_g$ extends to an $\ell$-adic character of $\Gal(\bFq/\Fq)$,
+  which we will also denote $\lambda_g$.
 %
-  We may now lift the $\ell$-adic character $\rho_g : \Gal(\bFq/\Fq) \to \EEx$
+  We may now lift the $\ell$-adic character $\lambda_g : \Gal(\bFq/\Fq) \to \EEx$
   to an $\ell$-adic character $\pi_1(G,\bg) \to \EEx$ using the canonical topological group homomorphism
@@
 Let $\qcs{L}$ be a quasicharacter sheaf on $\pi_0(G)$ and let $\rho : \pi_0^*\qcs{L} \to (\EE)_{G}$ be an isomorphism in $\QC(G)$.
-For each $x\in \pi_0(\bG)$, the restriction $\pi_0^*\gqcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gqcs{L}_x)_{\bG^x}$ so the isomorphism $\rho_{\bG^x} : (\gqcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\rho_x : \gqcs{L}_x \to (\EE)_x$.
-The collection $\{ \rho_x \tq x\in \pi_0(\bG) \}$ determines an isomorphism $\qcs{L} \to (\EE)_{\pi_0(G)}$  in $\QC(\pi_0(G))$.
+For each $x\in \pi_0(\bG)$, the restriction $\pi_0^*\gqcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gqcs{L}_x)_{\bG^x}$ so the isomorphism $\brho_{\bG^x} : (\gqcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gqcs{L}_x \to (\EE)_x$.
+The collection $\{ \brho_x \tq x\in \pi_0(\bG) \}$ determines an isomorphism $\qcs{L} \to (\EE)_{\pi_0(G)}$  in $\QC(\pi_0(G))$.
 \end{proof}

### 2014-08-25 crelle-dictionary.tex
Working through, fixing small problems

--- 2014-08-25 crelle-dictionary.tex
@@
 \begin{abstract}
-We extend the function-sheaf dictionary to smooth commutative group schemes over finite fields. 
-As an application, we explain how to geometrize and categorify quasicharacters of  algebraic tori, abelian varieties and unipotent K-wound groups over connected commutative algebraic groups over non-Archimedean local fields that admit a Neron model locally of finite type,
+By extending the scope of function-sheaf dictionary for connected commutative algebraic groups, we find a geometrization of characters of all smooth commutative group schemes over finite fields.
+As an application, we explain how to geometrize and categorify quasicharacters of all connected commutative algebraic groups over non-Archimedean local fields that admit a locally finite type Neron model, such as algebraic tori, abelian varieties and unipotent K-wound groups.
 \end{abstract}
@@
 In the meantime, we close this section with an elementary observation about $\Hom(\qcs{L},\qcs{L}')$.
+We call a morphism of sheaves \emph{trivial} if it is zero on every stalk.
 
@@
 Let $G$ be a smooth commutative group scheme over $\Fq$.
-If $\qcs{L}$ and $\qcs{L}'$ are quasicharacter sheaves on $G$ then
+If $\qcs{L}$ and $\qcs{L}'$ are quasicharacter sheaves on $G$, then
 every $\rho\in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism. 
@@
 Now suppose $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$.
-Then $\bm^* \gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L} $ together with
+Then the isomorphism $\bm^* \gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$ and the diagram of
 \ref{QC.3} guarantee
@@
 \begin{align*}
-\TrFrob{G} : \QCiso{G} &\to G(\Fq)^* \\
+\TrFrob{G} : \QCiso{G} &\to G(\Fq)^*, \\
 \qcs{L} &\mapsto \trFrob{\qcs{L}}.
@@
 studying the behavior of the trace of Frobenius under morphisms of group schemes.  These simple but important
-results on pullbacks and external products will be used in the proofs of many results in this paper.
+properties of pullbacks and external products will be used in the proofs of many results in this paper.
 
 \begin{lemma}\label{lem:pullback}
-  If $f : H\to G$ is a morphism of smooth commutative group schemes over $\Fq$ then
+  If $f : H\to G$ is a morphism of smooth commutative group schemes over $\Fq$, then
   \begin{align*}
@@
   \end{align*}
-  defines a monoidal functor dual to $f \colon H(\Fq) \to G(\Fq)$:
+  defines a monoidal functor dual to $f \colon H(\Fq) \to G(\Fq)$ in the sense that
   \[
@@
   Let $\qcs{L}$ be a quasicharacter sheaf on $G$. 
-  Pullback by $\bf$ takes rank~one local systems to rank~one local systems.
+  Pullback by $\bf$ takes rank-one local systems to rank-one local systems.
   To see that $(\bfxf)^* \mu$ satisfies \ref{QC.2},
@@
 
-Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
-Set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$;
-by Lemma~\ref{lem:pullback}, $\qcs{L}_1$ a quasicharacter sheaf on $G_1$
+Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$
+and set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$.
+By Lemma~\ref{lem:pullback}, $\qcs{L}_1$ is a quasicharacter sheaf on $G_1$
 and $\qcs{L}_2$ is a quasicharacter sheaf on $G_2$.
@@
 It is a matter of routine to show that this morphism satisfies
-\ref{QC.3} as it applies here,
+\ref{QC.4} as it applies here,
 from which it follows that we have exhibited an isomorphism
@@
 \begin{proposition}\label{prop:functorialG}
-Trace of Frobenius $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a natural transformation
+The homomorphism $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ defines a natural transformation
 between the two contravariant additive functors
@@
 
-The equivalence $G \mapsto G(\bFq)$
+The equivalence $G \mapsto G(\bFq)$,
 from the category of \'etale commutative group schemes over $\Fq$ to the category of commutative groups equipped
-with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group,
+with a continuous action of $\Gal(\bFq/\Fq)$,
 provides the following simple description of quasicharacter sheaves.
@@
   \]
-  both commute for all $x, y \in G(\bFq)$.
+  both commute, for all $x, y \in G(\bFq)$.
 \end{enumerate}
@@
 
-The zeroth page of the Hochschild-Serre spectral sequence, as in \cite{Vakil:spectral_sequences} following \cite{Weibel:Homological_Algebra}*{Ch 5 and \S 7.5}, for example,
+The zeroth page of the Hochschild-Serre spectral sequence
 is a double complex $E^{\bullet, \bullet}$ defined by
 \[
-E^{i,j} = C^i(\Weil{}, C^j(G(\bFq), \EEx)),
-\]
-The derivative of group cohomology yields two derivatives:
+E^{i,j} = C^i(\Weil{}, C^j(G(\bFq), \EEx));
+\]
+see \cite{Vakil:spectral_sequences}, which follows \cite{Weibel:Homological_Algebra}*{Ch 5 and \S 7.5}.
+The standard derivative on cochains yields two derivatives,
 \begin{align*}
-d_0 = d_G &: E^{i,j} \to E^{i,j+1} \\
-d_{\Weil{}} &: E^{i,j} \to E^{i+1,j}.
+d_G &: E^{i,j} \to E^{i,j+1} \mbox{and} \\
+d_{\Weil{}} &: E^{i,j} \to E^{i+1,j};
 \end{align*}
-Combining these yields a derivative $d = d_G + (-1)^j d_{\Weil{}}$ on the total complex
+we use the first as the derivative $d_0$ and the second to induce $d_1$.
+Combining them also yields a derivative $d = d_G + (-1)^j d_{\Weil{}}$ on the total complex
 \[
@@
 
-\begin{proposition}
+\begin{proposition} In the spectral sequence defined above,
 \begin{enumerate}
-\item The second page is given by $E_2^{i,j} = \Hh^i(\Weil{}, \Hh^j(G(\bFq), \EEx))$,
-\item there is an isomorphism $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) \cong \Hh^n(E_G^\bullet)$,
-\item there is a filtration $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) = F_n \supset \cdots \supset F_0 \supset F_{-1} = 0$ where $F_i / F_{i-1} \cong E_{\infty}^{i, n-i}$.
+\item the second page is given by $E_2^{i,j} = \Hh^i(\Weil{}, \Hh^j(G(\bFq), \EEx))$,
+\item there is an isomorphism $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) \cong \Hh^n(E_G^\bullet)$, and
+\item there is a filtration $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) = F_n \supset \cdots \supset F_{-1} = 0$, with $F_i / F_{i-1} \cong E_{\infty}^{i, n-i}$.
 \end{enumerate}
@@
  \[
-  \begin{tikzcd}
-    0 \arrow{r}
-    & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r}
-    & \Hh^2(E^\bullet_G) \arrow{r}
-    & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r}
-    & 0
-  \end{tikzcd}
+    0 \to
+    \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to
+    \Hh^2(E^\bullet_G) \to
+    \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to
+    0
  \]
@@
 for $x, y \in {\bar G}$.
-Let $\alpha \in C^0(\Weil{},C^2({\bar G},\EEx)$ be the $0$-cochain corresponding to $a$ and let $\beta\in C^1(\Weil{},C^1({\bar G},\EEx)$ be the cocycle such that $\beta(\Frob{})$ is $b$ \emph{written additively}.
+Let $\alpha \in C^0(\Weil{},C^2({\bar G},\EEx)$ be the $0$-cochain corresponding to $a$ and let $\beta\in C^1(\Weil{},C^1({\bar G},\EEx)$ be the cocycle such that $\beta(\Frob{})$ is $b$.
+We will write both $\alpha$ and $\beta$ additively.
 Then
@@
 To see this, let $\{ v'_x \in \gqcs{L}_x^\times \tq x \in {\bar G}\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$ be defined by $\qcs{L}$ and this choice, as above.
-Now let $\delta \in C^0(\Weil{},C^1({\bar G},\EEx))$ be the additive version of the function $d : {\bar G}\to \EEx$ defined by $v'_x = d(x) v_x$.
-Then, chasing through \ref{QC.2} and \ref{QC.3} we find
+Now let $\delta \in C^0(\Weil{},C^1({\bar G},\EEx))$ correspond to the function $d : {\bar G}\to \EEx$ defined by $v'_x = d(x) v_x$.
+Chasing through \ref{QC.2} and \ref{QC.3}, we find
 \[
@@
 %We first show that $S_G$ is injective.  
-Suppose $\qcs{L} \in \QCiso{G}$ with $S_G(\qcs{L}) = [\alpha \oplus \beta] = 0$,
+Suppose $[\qcs{L}] \in \QCiso{G}$ with $S_G([\qcs{L}]) = [\alpha \oplus \beta] = 0$,
 so that $\alpha \oplus \beta = d\sigma$ for some $\sigma \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
@@
 Let $\bQC(G)$ be the category of pairs $(\qcs{E},\mu_\qcs{E})$
-where $\qcs{E}$ an $\ell$-adic local system on $G$ of rank~one,
+where $\qcs{E}$ an $\ell$-adic local system on $G$ of rank-one,
 equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes \qcs{E}$
@@
  from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
- is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} and \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}.
+ is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} or \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}.
  This functor preserves local constancy, so takes local systems to local systems.

### 2014-08-25 crelle-dictionary.tex

--- 2014-08-25 crelle-dictionary.tex
@@
 %
-Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
-Set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$;
-by Lemma~\ref{lem:pullback}, $\qcs{L}_1$ a quasicharacter sheaf on $G_1$
+Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$
+and set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$.
+By Lemma~\ref{lem:pullback}, $\qcs{L}_1$ is a quasicharacter sheaf on $G_1$
 and $\qcs{L}_2$ is a quasicharacter sheaf on $G_2$.
@@
 It is routine to show that this morphism satisfies
-\ref{QC.3} as it applies here,
+\ref{QC.4} as it applies here,
 from which it follows that we have exhibited an isomorphism

### 2014-08-25 crelle-dictionary.tex
Vakil expands upon Weibel; some paragraph breaks.

@@
 \]
-see \cite{Vakil:spectral_sequences}, which follows \cite{Weibel:Homological_Algebra}*{Ch 5 and \S 7.5}.
+see \cite{Vakil:spectral_sequences}, expanding on \cite{Weibel:Homological_Algebra}*{Ch 5 and \S 7.5}.
 The standard derivative on cochains yields two derivatives,
 \begin{align*}
-d_G &: E^{i,j} \to E^{i,j+1} \mbox{and} \\
+d_G &: E^{i,j} \to E^{i,j+1} \quad \mbox{and} \\
 d_{\Weil{}} &: E^{i,j} \to E^{i+1,j};
@@
 The second diagram in \ref{qc.4} shows that the association $x \mapsto \brho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{qc.4} shows that it factors through $G(\bFq)_{\Weil{}}$.
-Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism then defining $\brho_x$ as multiplication by $\rho(x)$ will satisfy the two diagrams.
+
+Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism then defining $\brho_x$ as multiplication by $\rho(x)$ will define $\gqcs{L} \to \gqcs{L}'$ satisfy the two diagrams in \ref{qc.4}.
+
 Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the resulting bijection is actually a group isomorphism.

### 2014-08-25 crelle-dictionary.tex
Working through paper, small changes

--- 2014-08-25 crelle-dictionary.tex
@@
 so that $\alpha \oplus \beta = d\sigma$ for some $\sigma \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
-For each $x\in {\bar G}$, define $\sigma_x : \gqcs{L}_x \to \EEx$ by $v_x \mapsto \sigma(x)$.
+For each $x\in {\bar G}$, define $\sigma_x : \gqcs{L}_x \to \EE$ by $\sigma_x : v_x \mapsto \sigma(x)$.
 Then the indexed set of isomorphisms $\{ \sigma_x : \gqcs{L}_x \to \EE \tq x\in {\bar G}\}$
@@
 $b = \beta(\Frob{}) \in C^1({\bar G},\EEx)$, which are related to $\alpha$ and $\beta$ as above.
-Set $\gqcs{L}_x = \EEx$, define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes\gqcs{L}_y$
-by $\mu_{x,y}(1) = a(x,y) 1\otimes 1$ and $\phi_x : \gqcs{L}_{\Frob{G}(x)} \to \gqcs{L}_x$ by $\phi_x(1)= b(x)$.
+Set $\gqcs{L}_x = \EE$, define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes\gqcs{L}_y$
+by $\mu_{x,y}(1) = a(x,y) (1\otimes 1)$ and $\phi_x : \gqcs{L}_{\Frob{G}(x)} \to \gqcs{L}_x$ by $\phi_x(1)= b(x)$.
 Then \ref{qc.1} holds since $d_G \alpha =0$ and \ref{qc.2} holds since $d_{\Weil{}}\alpha =d_G \beta$.
 Tracing the construction backward, we have defined a quasicharacter sheaf $\qcs{L}$ on $G$ with
-$S_G(\qcs{L}) = [\alpha\oplus\beta\oplus\gamma]$, showing that $S_G$ is surjective.
+$S_G(\qcs{L}) = [\alpha\oplus\beta\oplus 0]$, showing that $S_G$ is surjective.
 \end{proof}
@@
 
-In this section we find the relationship between the group homomorphisms $\TrFrob{G}$ and $S_G$, and use this to find the group $\QCiso{G}$ when $G$ is an \'etale commutative group scheme over $\Fq$.
+In this section we fit the group homomorphisms $\TrFrob{G}$ and $S_G$ into a commutative diagram, determining the kernel and cokernel of the homomorphism $\TrFrob{G} : \QCiso{G} \to G(k)^*$ when $G$ is an \'etale commutative group scheme over $\Fq$.
 
@@
 \begin{align*}
- (X^*)_{\Frob{}} &\to (X^{\Frob{}})^* \\
- [f] &\mapsto f|_{X^{\Frob{}}}
+ (X^*)_{\Weil{}} &\to (X^{\Weil{}})^* \\
+ [f] &\mapsto f|_{X^{\Weil{}}}
 \end{align*}
@@
 \begin{proof}
-We can describe $X^{\Frob{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
+We can describe $X^{\Weil{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
 let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
 \[
- 0 \to X^{\Frob{}} \to X \to Y \to 0
+ 0 \to X^{\Weil{}} \to X \to Y \to 0
 \]
@@
 \[
- 0 \to Y^* \to X^* \to (X^{\Frob{}})^* \to \Ext^1_\ZZ(Y, \EEx).
-\]
-Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Frob{}})^*$.
+ 0 \to Y^* \to X^* \to (X^{\Weil{}})^* \to \Ext^1_\ZZ(Y, \EEx).
+\]
+Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Weil{}})^*$.
 \end{proof}
@@
 \begin{proposition}\label{prop:sur_etale}
-If $G$ is \'etale then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective.
+If $G$ is \'etale, then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective.
 \end{proposition}
@@
 Pick $\chi \in G(\Fq)^*$.
-By Lemma~\ref{lem:dual-inv}, there is some $b\in G(\bFq)^*$ such that $b\vert_{G(\Fq)^*} = \chi$.
+By Lemma~\ref{lem:dual-inv}, there is some $b\in G(\bFq)^*$ such that $b\vert_{G(\Fq)} = \chi$.
 Set $\gqcs{L}_x = \EE$ for every $x\in G(\bFq)$.

### 2014-08-27 crelle-dictionary.tex
Small changes to: abstract, introduction . .

@@
 \begin{abstract}
-We introduce the category of quasicharacter sheaves on smooth commutative group schemes $G$ over finite fields $k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
+We introduce the category of quasicharacter sheaves on smooth commutative group schemes $G$ over finite fields $k$ and, in doing so, expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
 We show that the group of isomorphism classes of quasicharacter sheaves is an extension of the group of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
-As an application, we find a category of sheaves whose isomorphism classes correspond to quasicharacters in the case of algebraic tori, abelian varieties and unipotent wound groups over local fields. 
+As an application, we find a category of sheaves for which isomorphism classes determine quasi\-characters in the case of algebraic tori, abelian varieties and unipotent wound groups over local fields.
 In this geometrization of quasicharacters, our sheaves are local systems on
@@
 One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
-The fact that $T_G$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$
-determine the same character of $G(\Fq)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
+%The fact that $T_G$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
 
@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:spectral_ses}
 There is a short exact sequence
@@
     \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to
-    0
+    0.
  \]
@@
 \begin{proposition} \label{prop:ses_desc}
+Consider the short exact sequence in Corollary~\ref{cor:spectral_ses}.
 \begin{enumerate}
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:SGiso}
 If $G$ is \'etale then $S_G$ is an isomorphism.
@@
 Since $b : G(\bFq) \to \EEx$ is a group homomorphism,
-condition \eqref{nohom} is satisfied with $a =1$ and $\qcs{L} = (\gqcs{L}, \mu, \phi)$
+condition \eqref{nohom} is satisfied with $a =1$.
+So $\qcs{L} = (\gqcs{L}, \mu, \phi)$
 is a quasicharacter sheaf with $\trFrob{\qcs{L}} = \chi$.
@@
 \begin{proof}
-This result follows easily from Propositions~\ref{prop:ses_desc} and \ref{prop:sur_etale}.
-\end{proof}
+This result follows easily from Propositions~\ref{prop:ses_desc}, \ref{prop:SGiso} and \ref{prop:sur_etale}.
+\end{proof}
+
+\begin{corollary}\label{cor:split}
+\end{corollary}
 
@@
 We must show that comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
-To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$ \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}.
+To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$; {\it cf.\ } \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}.
 In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.

### 2014-08-27 crelle-dictionary.tex
Added the section of T_G in the etale case, and . . .
replaced all T_G with \TrFrob{G}.

@@
 \[
-T_G: \QCiso{G} \to G(\Fq)^*
+\TrFrob{G}: \QCiso{G} \to G(\Fq)^*
 \]
@@
 One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
-%The fact that $T_G$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
+%The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
 
@@
 case we show that every quasicharacter sheaf can be described in both of these ways (\S\ref{ssec:connected}).
-We use this fact to prove that $T_G$ is an isomorphism for connected commutative algebraic groups $G$
+We use this fact to prove that $\TrFrob{G}$ is an isomorphism for connected commutative algebraic groups $G$
 and to determine the automorphism groups of quasicharacter sheaves on such $G$.
@@
 %
-%The appearance of $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ and the trace of Frobenius gives an isomorphism $T_G: \QCiso{G} \to \Hom(G(\Fq),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\Fq$, then $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ measures the kernel of $T_G: \QCiso{G} \to \Hom(G(\Fq),\EEx)$.
+%The appearance of $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ and the trace of Frobenius gives an isomorphism $\TrFrob{G}: \QCiso{G} \to \Hom(G(\Fq),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\Fq$, then $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ measures the kernel of $\TrFrob{G}: \QCiso{G} \to \Hom(G(\Fq),\EEx)$.
 %This observation makes plain the fact that  . . .
@@
 in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
-The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in this context.
+The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in that context.
 
@@
 
-We will see that $T_G : \QCiso{G} \to G(\Fq)^*$ may not provide complete
+We will see that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ may not provide complete
 information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not a connected algebraic group.
@@
 
-This sequence will play a key role in understanding the kernel of $T_G$, as described in the next few sections.
+This sequence will play a key role in understanding the kernel of $\TrFrob{G}$, as described in the next few sections.
 For this application, we need a good understanding of these maps to and from the total complex.
@@
 \begin{proposition}\label{prop:sur_etale}
-If $G$ is \'etale, then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective.
+If $G$ is \'etale, then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective
+and admits a section.
 \end{proposition}
@@
 Pick $\chi \in G(\Fq)^*$. 
-By Lemma~\ref{lem:dual-inv}, there is some $b\in G(\bFq)^*$ such that $b\vert_{G(\Fq)} = \chi$.
+Let $[\beta]\in \Hh^1(\Weil{},\bG^*)$ be the class corresponding to $\chi$ under Lemma~\ref{lem:dual-inv}.
+Every representative cocycle $\beta \in Z^1(\Weil{},\bG^*)$ determines a homomorphism $\beta(\Frob{}) : G(\bFq)\to \EEx$ such that $\beta(\Frob{})\vert_{G(\Fq)} = \chi$.
 Set $\gqcs{L}_x = \EE$ for every $x\in G(\bFq)$.
 Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$ and
-$\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = b(x)$.
-Since $b : G(\bFq) \to \EEx$ is a group homomorphism,
+$\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = \beta(\Frob{})(x)$.
+Since $\beta(\Frob{}) : G(\bFq) \to \EEx$ is a group homomorphism,
 condition \eqref{nohom} is satisfied with $a =1$.
@@
 is a quasicharacter sheaf with $\trFrob{\qcs{L}} = \chi$.
+This shows that $\TrFrob{G}$ is surjective.
+%
+Now let $\beta' \in Z^1(\Weil{},\bG^*)$ be another representative for $[\beta]$
+so $\beta'-\beta = d_{\Weil{}} \delta$ for some $\delta \in C^0(\Weil{},\bG^*)$ defining $d \in \Hom(G(\bFq),\EEx)$.
+Let $\qcs{L}'$ be the quasicharacter sheaf on $G$ defined by $\beta'$, as above.
+For each $x\in G(\bFq)$, define $\brho_x :\qcs{L}_x\to \qcs{L}'_x$ by $\brho_x(1) = d(x)$.
+Since condition~\ref{qc.4} is satisfied for $\{ \brho_x \tq x\in G(\bFq)\}$, it defines a morphism $\rho : \qcs{L}\to \qcs{L}'$, which is clearly and isomorphism. 
+%
+We have now defined a section of $\TrFrob{G}$. 
 \end{proof}
@@
 
+Combining Propositions~\ref{prop:sur_etale} and \ref{prop:etale-iso} gives the following
+
 \begin{corollary}\label{cor:split}
+The short exact sequence
+ \[
+    0 \to
+    \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to
+    \Hh^2(E^\bullet_G) \to
+    \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to
+    0
+ \]
+ is split.
 \end{corollary}

### 2014-08-27 crelle-dictionary.tex
Finished proof reading Section 3.

@@
 In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization of complete Langlands parameters for $p$-adic groups 
-and, in the process, is led to study the representations of all the pure rational forms of the $p$-adic group simultaneously.
+and, in the process, is led to study the representations of all the pure rational forms of the $p$-adic group, simultaneously.
 A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group \cite{bernstein:vogan_conference}.
@@
 We must show that comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
-To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$; {\it cf.\ } \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}.
+To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between local systems on $G$ and $A$-equivariant local systems on $H$; {\it cf.\ } \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}.
 In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
@@
 %\todo{Fix citelist} %\citelist{\cite{deligne:SGA4.5}*{Sommes trig.},\cite{laumon:87a}*{1.1.3}}
-The key observation is that, by \'etale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
-(Note that this is a particular case of the argument in the proof of Proposition~\ref{prop:finite}.)
+The key observation is that, by \'etale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ (this is a particular case of the argument in the proof of Proposition~\ref{prop:finite}) and that, for every $\qcs{E}$ in $\bQC(G)$, the trace of $\Lang^*\qcs{E}$ as a representation of $G(\Fq)$, is $\trFrob{\qcs{E}}^{-1}$.
+
 Using the equivalence given by $\Lang^*$, if $\Lang^*\qcs{E} = V$ with character $\psi$ and isomorphism $V\to V\otimes V$ then 
 $\qcs{E} \iso (\Lang_!
-V)_\psi$, the $\psi$-isotypic component of the push-forward $\Lang_* V$ of the constant sheaf $V$ on $G$ equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes\qcs{E}$ determined by $V\to V\otimes V$.
+V)_\psi$, the $\psi$-isotypic component of the push-forward of the constant sheaf $V$ on $G$ by $\Lang$, equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes\qcs{E}$ determined by $V\to V\otimes V$.
 Moreover, $\Aut(\qcs{E})$ is the group of automorphisms of $\rho : V\to V$ for which 
@@
 %\begin{remark}
-We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of quasicharacter sheaves on $G$ is equivalent to the category of characters $\psi$ of $G(\Fq)$.
+We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of quasicharacter sheaves on $G$ is equivalent to the category of one-dimensional representations $V$ of $G(\Fq)$ equipped with an isomorphism $V\iso \EE$, and therefore equivalent to the category of characters $\psi$ of $G(\Fq)$.
 We have also just seen that if the character of $\Lang^*\qcs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\qcs{E} : \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ which is part of the data that determines a quasicharacter sheaf on $G$.
-That leads to a perspective on the function-sheaf dictionary common in the literature in which one considers $1$-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$; see \cite{kamgarpour:09a}*{Intro}, for example.
-As a slight variation, one may also consider $1$-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
+That leads to a perspective on the function-sheaf dictionary common in the literature in which one considers one-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$; see \cite{kamgarpour:09a}*{Intro}, for example.
+As a slight variation, one may also consider one-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
 %One may show that all such $\gqcs{L}$ are determined by extensions of $\bG$ by $\EEx$ which are fixed by Frobenius and that the trace of Frobenius provides a canonical isomorphism from $\Hh^2(\bG,\EEx)^{\Frob{}}$ to $G(\Fq)^*$; {\it cf.\ }
@@
 
-Although the category of quasicharacter sheaves on $G$ does specialize to that common notion when $G$ is connected and of finite type, the common notion is not appropriate if one wishes to extend the dictionary to smooth commutative group schemes over finite fields.
+Although the category of quasicharacter sheaves on $G$ does specialize to that common notion when $G$ is connected and of finite type, the common notion is not appropriate if one wishes to extend the dictionary to smooth commutative group schemes.
 In particular, as we have already seen in Section~\ref{sec:etale}, for a given quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ there may be a different isomorphism $\mu' : \bm^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$ for which $\qcs{L}'=(\gqcs{L},\mu',\phi)$ is also a quasicharacter sheaf on $G$, not isomorphic to $\qcs{L}$ in $\QC(G)$.
 Indeed, Proposition~\ref{prop:etale-iso} shows that when $G$ is \'etale, $\Hh^2(\bG,\EEx)^{\Weil{}}$ measures the possibilities for $\mu'$.
-The common perspective on the function-sheaf dictionary leads only to the part of category of quasicharacter sheaves that is invisible to the trace of Frobenius.
-
-We will see in Section~\ref{sec:main} that, for any smooth commutative group scheme $G$, the part of category of quasicharacter sheaves that is invisible to the trace of Frobenius are measured by $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
+On \'etale group schemes, the common perspective on the function-sheaf dictionary leads only to the part of category of quasicharacter sheaves that is invisible to the trace of Frobenius.
+
+We will see in Section~\ref{sec:main} that, for any smooth commutative group scheme $G$, the part of the category of quasicharacter sheaves that is invisible to the trace of Frobenius is measured by $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
 %\end{remark}

### 2014-08-27 crelle-dictionary.tex
Proof read Section 4.

@@
 Let $\qcs{L}$ be a quasicharacter sheaf on $\pi_0(G)$ and let $\rho : \pi_0^*\qcs{L} \to (\EE)_{G}$ be an isomorphism in $\QC(G)$. 
-For each $x\in \pi_0(\bG)$, the restriction $\pi_0^*\gqcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gqcs{L}_x)_{\bG^x}$ so the isomorphism $\brho_{\bG^x} : (\gqcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gqcs{L}_x \to (\EE)_x$.
+For each $x\in \pi_0(\bG)$, set $\bG^x \ceq \pi_0^{-1}(x)$.
+The restriction $\pi_0^*\gqcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gqcs{L}_x)_{\bG^x}$ so the isomorphism $\brho_{\bG^x} : (\gqcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gqcs{L}_x \to (\EE)_x$.
 The collection $\{ \brho_x \tq x\in \pi_0(\bG) \}$ determines an isomorphism $\qcs{L} \to (\EE)_{\pi_0(G)}$  in $\QC(\pi_0(G))$.
@@
 
-For each $x\in \pi_0(\bG)$, set $\bG^x \ceq \pi_0^{-1}(x)$.
+As above, set $\bG^x \ceq \pi_0^{-1}(x)$ for $x\in \pi_0(\bG)$.
 Let $g, g'$ be geometric points in the same
@@
 from $\gqcs{L}_{g}$ to $\gqcs{L}_{g'}$.
-
+%
 The isomorphisms $\varphi_{g,g'}: \gqcs{L}_{g} \to \gqcs{L}_{g'}$ are canonical
@@
  \begin{equation}\label{eq:qc}
-  \begin{tikzcd}[column sep=55]
+  \begin{tikzcd}[column sep=40]
    \gqcs{L}_{gh} \arrow{r}{\varphi_{gh,g'h'}} \arrow[swap]{d}{\mu_{g,h}}
@@
 We saw in Proposition~\ref{prop:functorialG} that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
-In this section we improve that result.
+In this section we find the image and kernel of $\TrFrob{G}$.
 
@@
 \begin{proof}
-  Recall the short exact sequence \eqref{eq:pi0}
-  defining the component group scheme for $G$:
-  \[
-  \begin{tikzcd}
-    1 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
-  \end{tikzcd}
-  \]
+%  Recall the short exact sequence \eqref{eq:pi0}
+%  defining the component group scheme for $G$:
+%  \[
+%  \begin{tikzcd}
+%    1 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
+%  \end{tikzcd}
+%  \]
   Let
   \[
-  \begin{tikzcd}[row sep=20]
+  \begin{tikzcd}[row sep=20, column sep=20]
 %  & 0 \arrow{d} & 0 \arrow{d} & 0\arrow{d} \\
@@
 This homomorphism is injective because morphisms of sheaves are determined by the linear transformations induced on stalks.  
-Note that homomorphisms in the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ are continuous where $\bG_{\Weil{}}$ is given the topology of the base of the espace \'etal\'e attached to $\gqcs{L}$.
-Since $\ell$ is invertible in $\Fq$, it now follows that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
+Homomorphisms in the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ are continuous when $\bG$ is viewed as the base of the espace \'etal\'e attached to $\gqcs{L}$.
+Since $\ell$ is invertible in $\Fq$, it follows that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
 We also have $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
 To see that $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho^y: \gqcs{L}^y \to \gqcs{L}^y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
-This defines an isomorphism $\bar\rho : \gqcs{L}\to \gqcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\qcs{L}\to \qcs{L}$ with maps to $\theta$ under $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
+This defines an isomorphism $\bar\rho : \gqcs{L}\to \gqcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\qcs{L}\to \qcs{L}$ which maps to $\theta$ under $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
 \end{proof}

### 2014-08-27 crelle-dictionary.tex
Finished proofreading Section 5.

@@
 
-Let $K$ be a local field (in the sense of Serre) with residue field $\Fq$. 
-In this section we consider connected commutative algebraic groups over $K$ that admit a N\'eron model, by which we mean a locally of finite type N\'eron model.
+Let $K$ be a local field with finite residue field $\Fq$. 
+In this section we consider connected commutative algebraic groups over $K$ that admit a N\'eron model, by which we mean a locally finite type N\'eron model.
 By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected commutative algebraic groups over $K$ that contain no subgroup of type $\mathbb{G}_\text{a}$.
@@
 For every non-negative integer $n$, $\Gr^R_n(X)$ is a {\it smooth} commutative group scheme over $S_0$
-with component group scheme $\pi_0(X) \times_S S_0$ and $\Fq$-rational points $X(R_n).$
+with component group scheme $\pi_0(X)_{\Fq} \ceq \pi_0(X) \times_S S_0$ and $\Fq$-rational points $X(R_n).$
 %
 The Greenberg transform $\Gr_R(X)$ of $X$ is a commutative group scheme over $\Fq$
-with component group scheme $\pi_0(X) \times_S S_0$
+with component group scheme $\pi_0(X)_{\Fq}$
 and $\Fq$-rational points $X(K).$
@@
 As we explained in the Introduction, our original motivation for this paper was to find a geometrization and categorification of quasicharacters of $p$-adic tori.
-This is is now provided by specializing Theorem~\ref{thm:QCXK} to the case when $X_K= T\in \mathcal{N}_K$ is an algebraic torus over $K$, in which case we write $\underline{T}$ for the Neron model $X$.
+This is is now provided by specializing Theorem~\ref{thm:QCXK} to the case when $X_K= T_K\in \mathcal{N}_K$ is an algebraic torus over $K$.
 Now,
 \[
- \pi_0(\underline{T})_{\bFq} = X_*(T)_{\mathcal{I}_K},
-\]
-where $X_*(T)$ is the cocharacter lattice of $T$ and $\mathcal{I}_K$ is the inertia group for $K$ \cite{bitan:discriminant}*{Eq 3.1}. 
+ \pi_0(T)_{\bFq} = X_*(T_K)_{\mathcal{I}_K},
+\]
+where $X_*(T_K)$ is the cocharacter lattice of $T_K$ and $\mathcal{I}_K$ is the inertia group for $K$ \cite{bitan:discriminant}*{Eq 3.1}. 
 Accordingly, the short exact sequence in Theorem~\ref{thm:QCXK} becomes
 \begin{equation}
-0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{T} \to \Hom_\text{qc}(T(K),\EEx) \to 0.
+0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{T_K} \to \Hom_\text{qc}(T(K),\EEx) \to 0.
 \end{equation}
-Again by Theorem~\ref{thm:QCXK}, the automorphism groups in the $\QC(T)$ are given, for every quasicharacter sheaf $\qcs{F}$ for $T$, by
+Again by Theorem~\ref{thm:QCXK}, the automorphism groups in $\QC(T_K)$ are given, for every quasicharacter sheaf $\qcs{F}$ for $T_K$, by
 \begin{equation}
-\Aut(\qcs{F}) \iso \Hom(X_*(T)_{\Weil{K}},\EEx) \iso \Hom(X_*(T),\EEx)^{\Weil{K}} = (\check{T}_\ell)^{\Weil{K}}
+\Aut(\qcs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx) \iso \Hom(X_*(T_K),\EEx)^{\Weil{K}} = (\check{T}_\ell)^{\Weil{K}}
 \end{equation}
-where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
+where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T_K$.
+This provides good information above the category $\QC(T_K)$ of quasicharacters for $T_K$ and its relation to quasicharacters of $T(K)$.
 
@@
 what follows will not depend on these choices.
-
-Suppose $X_K\in \mathcal{N}_K$ with N\'eron model $X$ and $Y_{L}\in \mathcal{N}_L$ with N\'eron model $Y$.
+Suppose $\ell$ is invertible in the residue fields of $K$ and $L$.
+
+We begin with $X_K\in \mathcal{N}_K$ with N\'eron model $X$ and $Y_{L}\in \mathcal{N}_L$ with N\'eron model $Y$.
 Suppose $m$ is a positive integer such that 
@@
 Then
-$
+\[
 \Gr^{\OK}_{m-1}(X) \iso \Gr^{\OL}_{m-1}(Y)
-$
+\]
 as smooth group schemes over $\Fq$; accordingly, by Lemma~\ref{lem:pullback} the isomorphism above determines an equivalence of categories
@@
 The isomorphism \eqref{eq:schematic_transfer} can indeed exist between quasicharacters of algebraic tori over local fields, even when the characteristics of $K$ and $L$ differ.
-Suppose $T_K$ and $M_L$ are tori over non-archimedian local fields $K$ and $L$,
-splitting over $K'$ and $L'$ respectively.
+Suppose $T_K$ and $M_L$ are tori over local fields $K$ and $L$,
+splitting over $K'$ and $L'$, respectively.
 Then $T_K$ and $M_L$ are said to be \emph{$n$-congruent} \cite{chai-yu:01a}*{\S 2} if there are isomorphisms
@@
  \begin{enumerate}
-  \item $\alpha$ induces an isomorphism $\OK/\pi_K^n \OK \to \OO{L}/\pi_{L}^n \OO{L}$,
+  \item $\alpha$ induces an isomorphism $\OK/\varpi_K^n \OK \to \OO{L}/\varpi_{L}^n \OO{L}$,
   \item $\alpha$ is $\Gal(K'/K)$-equivariant relative to $\beta$, and
@@
 \begin{equation}\label{transfer}
-  \Hom_{n-1}(T_K(K), \EEx) \iso \Hom_{n-1}(M_L(M),\EEx).
+  \Hom_{n-1}(T_K(K), \EEx) \iso \Hom_{n-1}(M_L(L),\EEx).
 \end{equation}
@@
  \[
-\Hom_{m-1}(T_K(K), \EEx) \iso  \Hom_{m-1}(M_L(L), \EEx)
+\Hom_{m-1}(T(K), \EEx) \iso  \Hom_{m-1}(M(L), \EEx)
  \]
@@
 We thank Takashi Suzuki for some very helpful observations and suggestions, especially related to our use of the Hochschild-Serre spectral sequence.
+We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and drawing our attention to their result on Weil restriction and the Greenberg transform.
 We thank Joseph Bernstein for suggesting a connection between our category of quasicharacter sheaves for $p$-adic tori and quasicharacters of its pure rational forms.
-We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and drawing our attention to their result on Weil restriction and the Greenberg transform.
 }

### 2014-08-27 crelle-dictionary.tex
Abstract. Snake.
Returned the abstract to the form we discussed. Also made changes to
the wording of the proof of the main result.

@@
 \begin{abstract}
-We introduce the category of quasicharacter sheaves on smooth commutative group schemes $G$ over finite fields $k$ and, in doing so, expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
+We introduce the category of quasicharacter sheaves on smooth commutative group schemes $G$ over finite fields $k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
 We show that the group of isomorphism classes of quasicharacter sheaves is an extension of the group of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
-As an application, we find a category of sheaves for which isomorphism classes determine quasi\-characters in the case of algebraic tori, abelian varieties and unipotent wound groups over local fields.
+As an application, we find a category of sheaves for which isomorphism classes correspond to quasi\-characters in the case of algebraic tori, abelian varieties and unipotent wound groups over local fields.
 In this geometrization of quasicharacters, our sheaves are local systems on
@@
 \begin{proposition} \label{prop:etale-iso}
- If $G$ is \'etale then the map $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ induces an isomorphism of short exact sequences
+ If $G$ is \'etale then the map $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ induces an isomorphism of split short exact sequences
 \[
@@
 \end{proof}
-
-Combining Propositions~\ref{prop:sur_etale} and \ref{prop:etale-iso} gives the following
-
-\begin{corollary}\label{cor:split}
-The short exact sequence
- \[
-    0 \to
-    \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to
-    \Hh^2(E^\bullet_G) \to
-    \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to
-    0
- \]
- is split.
-\end{corollary}
 
@@
   Let
-  \[
+  \begin{equation}\label{eq:pre-snake}
   \begin{tikzcd}[row sep=20, column sep=20]
 %  & 0 \arrow{d} & 0 \arrow{d} & 0\arrow{d} \\
-    0 \arrow[dashed]{r} & \ker \TrFrob{\pi_0(G)} \arrow[dashed]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dashed]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
+%    0 \arrow[dotted]{r} & \ker \TrFrob{\pi_0(G)} \arrow[dotted]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dotted]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
+    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
+    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
+    0 \rar & \pi_0(G)(\Fq)^* \rar
+    &  G(\Fq)^* \rar & G^0(\Fq)^* \rar & 0
+%   &  \coker \TrFrob{\pi_0(G)} =0 \arrow[dotted]{r} & \coker \TrFrob{G} \arrow[dotted]{r} & \coker \TrFrob{G^0} =0 & 
+%    & \arrow{d} \coker \TrFrob{\pi_0(G)} =0 \arrow[dashed]{r} & \arrow{d} \coker \TrFrob{G} \arrow[dashed]{r} &  \arrow{d} \coker \TrFrob{G^0} =0 & \\
+%      & 0 & 0 & 0 \\
+  \end{tikzcd}
+  \end{equation}
+  be the commutative diagram of abelian groups obtained by applying
+  Lemma~\ref{lem:pullback} to \eqref{eq:pi0}.
+ %
+  The sequence of abelian groups
+\[
+  \begin{tikzcd}
+    1 \rar & G^0(\Fq) \rar & G(\Fq) \rar & \pi_0(G)(\Fq) \rar & 0,
+  \end{tikzcd}
+\]
+  is exact since $\Hh^1(\Fq,G^0) =0$ by Lemma~\ref{lem:G0alg-grp} and Lang's theorem on connected algebraic groups over finite fields \cite{lang:56a}.
+  Since $\EEx$ is divisible, $\Hom(\ - \ ,\EEx)$ is exact and thus the dual sequence of
+  character groups in \eqref{eq:pre-snake} is exact.
+%
+  The upper row in \eqref{eq:pre-snake} is exact by Proposition~\ref{prop:middleexact}.
+  Now Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}
+  imply that $\ker \TrFrob{G^0} =0$ and $\coker \TrFrob{G^0}=0$,
+  while Proposition~\ref{prop:etale-iso} gives $\ker \TrFrob{\pi_0(G)} \iso \Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$
+  and $\coker \TrFrob{\pi_0(G)}=0$.
+It now follows from the snake lemma 
+   %\begin{equation}\label{eq:snake}
+ \[
+  \begin{tikzcd}[row sep=20, column sep=15]
+%  & 0 \arrow{d} & 0 \arrow{d} & 0\arrow{d} \\
+    0 \arrow[dotted]{r} & \ker \TrFrob{\pi_0(G)} \arrow[dotted]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dotted]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
     0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
@@
     & \arrow{d} G(\Fq)^* \rar & G^0(\Fq)^* \rar \dar & 0\\
-   &  \coker \TrFrob{\pi_0(G)} =0 \arrow[dashed]{r} & \coker \TrFrob{G} \arrow[dashed]{r} & \coker \TrFrob{G^0} =0 & 
+   &  \coker \TrFrob{\pi_0(G)} =0 \arrow[dotted]{r} & \coker \TrFrob{G} \arrow[dotted]{r} & \coker \TrFrob{G^0} =0 & 
 %    & \arrow{d} \coker \TrFrob{\pi_0(G)} =0 \arrow[dashed]{r} & \arrow{d} \coker \TrFrob{G} \arrow[dashed]{r} &  \arrow{d} \coker \TrFrob{G^0} =0 & \\
@@
   \]
-  be the commutative diagram of abelian groups obtained by applying
-  Lemma~\ref{lem:pullback} to \eqref{eq:pi0}.
- %
-  The sequence of abelian groups
-  \begin{equation}\label{eq:pi0k}
+ % \end{equation}
+that $\coker \TrFrob{G} =0$
+and $\ker \TrFrob{\pi_0(G)} \to \ker \TrFrob{G}$ is an isomorphism.
+This gives the short exact sequence
+\[
   \begin{tikzcd}
-    1 \rar & G^0(\Fq) \rar & G(\Fq) \rar & \pi_0(G)(\Fq) \rar & 0,
-  \end{tikzcd}
-  \end{equation}
-  is exact since $\Hh^1(\Fq,G^0) =0$ by Lemma~\ref{lem:G0alg-grp} and Lang's theorem on connected algebraic groups over finite fields \cite{lang:56a}.
-  Since $\EEx$ is divisible, $\Hom(\ - \ ,\EEx)$ is exact and thus the dual sequence of
-  character groups is also exact.
-%
-  The upper row is exact by Proposition~\ref{prop:middleexact}.
-  Now Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}
-  imply that $\ker \TrFrob{G^0} =0$ and $\coker \TrFrob{G^0}=0$,
-  while Proposition~\ref{prop:etale-iso} gives $\ker \TrFrob{\pi_0(G)} \iso \Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$
-  and $\coker \TrFrob{\pi_0(G)}=0$.
-%
-It follows from the snake lemma that $\coker \TrFrob{G} =0$
-and $\ker \TrFrob{\pi_0(G)} \to \ker \TrFrob{G}$ is an isomorphism.
-This calculates $\ker  \TrFrob{G}$ and shows that
-\[
-  \begin{tikzcd}
-0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx)) \arrow{r} & \QCiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0 
-  \end{tikzcd}
-\]
-is exact.
+0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx)) \arrow{r} & \QCiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0. 
+  \end{tikzcd}
+\]
 \end{proof}

### 2014-08-27 crelle-dictionary.tex
Changes as discussed in my backyard, today.

@@
 
-If $G$ is a commutative algebraic group over $\Fq$ which is not connected, then the isomorphism \eqref{introbox} need not be unique, so one must keep track of the choice.
-This leads to the category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is a chosen isomorphism of local systems on $G\times G$.
+If $G$ is a commutative algebraic group over $\Fq$ which is not connected, then the isomorphism \eqref{introbox} need not be unique.
+In order to track the choice of isomorphism, consider the category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is a chosen isomorphism of local systems on $G\times G$.
 %If the component group scheme $\pi_0(G)$ is not cyclic, then 
@@
 If $G$ is \'etale, then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective
-and admits a section.
+and split.
 \end{proposition}
@@
 This shows that $\TrFrob{G}$ is surjective.
-%
+
 Now let $\beta' \in Z^1(\Weil{},\bG^*)$ be another representative for $[\beta]$
-so $\beta'-\beta = d_{\Weil{}} \delta$ for some $\delta \in C^0(\Weil{},\bG^*)$ defining $d \in \Hom(G(\bFq),\EEx)$.
+so $\beta-\beta' = d_{\Weil{}} \delta$ for some $\delta \in C^0(\Weil{},\bG^*)$ defining $d \in \Hom(G(\bFq),\EEx)$.
 Let $\qcs{L}'$ be the quasicharacter sheaf on $G$ defined by $\beta'$, as above.
 For each $x\in G(\bFq)$, define $\brho_x :\qcs{L}_x\to \qcs{L}'_x$ by $\brho_x(1) = d(x)$.
-Since condition~\ref{qc.4} is satisfied for $\{ \brho_x \tq x\in G(\bFq)\}$, it defines a morphism $\rho : \qcs{L}\to \qcs{L}'$, which is clearly and isomorphism. 
+The collection of isomorphisms $\{ \brho_x \tq x\in G(\bFq)\}$ satisfies condition~\ref{qc.4}, so it defines a morphism $\rho : \qcs{L}\to \qcs{L}'$, which is clearly an isomorphism. 
 %
 We have now defined a section of $\TrFrob{G}$.
+
+Now suppose $\chi_1, \chi_2 \in G(\Fq)^*$.
+Pick cocycles $\beta_1,\beta_2\in Z^1(\Weil{},\bG^*)$ and construct quasicharacter sheaves $\qcs{L}_1$ and $\qcs{L}_2$ on $G$ as above.
+Since $\qcs{L}_1\otimes \qcs{L}_2$ is exactly the quasicharacter sheaf built from the cocycle $\beta_1\cdot \beta_2$, and since $\trFrob{\qcs{L}_1\otimes \qcs{L}_2} = \trFrob{\qcs{L}_1}\cdot \trFrob{\qcs{L}_2}$, the section of $\TrFrob{G}$ defined here is a homomorphism.
 \end{proof}
@@
 \begin{proof}
-This result follows easily from Propositions~\ref{prop:ses_desc}, \ref{prop:SGiso} and \ref{prop:sur_etale}.
+This result follows from Propositions~\ref{prop:ses_desc}, \ref{prop:SGiso} and \ref{prop:sur_etale}.
 \end{proof}
@@
 
-Most of this paper focuses on the question of determining the isomorphism classes of objects; a complete understanding of the morphisms in $\QC(G)$ also requires a description of the automorphisms of an arbitrary quasicharacter sheaf $\qcs{L}$.
+While most of this paper focuses on the question of determining the isomorphism classes of objects, a complete understanding of the morphisms in $\QC(G)$ also requires a description of the automorphisms of an arbitrary quasicharacter sheaf $\qcs{L}$.
 
@@
 \end{proof}
+
+\begin{remark}
+Although $\TrFrob{\pi_0(G)}$ is split and $\TrFrob{G^0}$ is an isomorphism, as examples show, it does not follow that $\TrFrob{G}$ is split. 
+\end{remark}
 

### 2014-08-29 crelle-dictionary.tex
Working through paper, fixing small things

--- 2014-08-27 crelle-dictionary.tex
@@
 \begin{abstract}
-We introduce the category of quasicharacter sheaves on smooth commutative group schemes $G$ over finite fields $k$ and, in doing so, expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
+We introduce the category of quasicharacter sheaves on smooth commutative group schemes $G$ over finite fields $k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
 We show that the group of isomorphism classes of quasicharacter sheaves is an extension of the group of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
-As an application, we find a category of sheaves for which isomorphism classes determine quasi\-characters in the case of algebraic tori, abelian varieties and unipotent wound groups over local fields.
+As an application, we find a category of sheaves whose isomorphism classes correspond to quasicharacters in the case of algebraic tori, abelian varieties and unipotent wound groups over local fields. 
 In this geometrization of quasicharacters, our sheaves are local systems on
@@
 \[
-\TrFrob{G}: \QCiso{G} \to G(\Fq)^*
+T_G: \QCiso{G} \to G(\Fq)^*
 \]
@@
 One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
-%The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
+The fact that $T_G$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$
+determine the same character of $G(\Fq)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
 
@@
 case we show that every quasicharacter sheaf can be described in both of these ways (\S\ref{ssec:connected}).
-We use this fact to prove that $\TrFrob{G}$ is an isomorphism for connected commutative algebraic groups $G$
+We use this fact to prove that $T_G$ is an isomorphism for connected commutative algebraic groups $G$
 and to determine the automorphism groups of quasicharacter sheaves on such $G$.
@@
 %
-%The appearance of $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ and the trace of Frobenius gives an isomorphism $\TrFrob{G}: \QCiso{G} \to \Hom(G(\Fq),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\Fq$, then $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ measures the kernel of $\TrFrob{G}: \QCiso{G} \to \Hom(G(\Fq),\EEx)$.
+%The appearance of $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ and the trace of Frobenius gives an isomorphism $T_G: \QCiso{G} \to \Hom(G(\Fq),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\Fq$, then $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ measures the kernel of $T_G: \QCiso{G} \to \Hom(G(\Fq),\EEx)$.
 %This observation makes plain the fact that  . . .
@@
 In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization of complete Langlands parameters for $p$-adic groups 
-and, in the process, is led to study the representations of all the pure rational forms of the $p$-adic group, simultaneously.
+and, in the process, is led to study the representations of all the pure rational forms of the $p$-adic group simultaneously.
 A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group \cite{bernstein:vogan_conference}.
@@
 in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
-The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in that context.
+The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in this context.
 
@@
 
-We will see that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ may not provide complete
+We will see that $T_G : \QCiso{G} \to G(\Fq)^*$ may not provide complete
 information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not a connected algebraic group.
@@
 \end{align*}
-we use the first as the derivative $d_0$ and the second to induce $d_1$.
+we use the first as the derivative $d_0$ on the zeroth page, and the second to induce $d_1$.
 Combining them also yields a derivative $d = d_G + (-1)^j d_{\Weil{}}$ on the total complex
@@
 
-\begin{corollary}\label{cor:spectral_ses}
+\begin{corollary}
 There is a short exact sequence
@@
     \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to
-    0.
+    0
  \]
@@
 
-This sequence will play a key role in understanding the kernel of $\TrFrob{G}$, as described in the next few sections.
+This sequence will play a key role in understanding the kernel of $T_G$, as described in the next few sections.
 For this application, we need a good understanding of these maps to and from the total complex.
@@
 \begin{proposition} \label{prop:ses_desc}
-Consider the short exact sequence in Corollary~\ref{cor:spectral_ses}.
+$ $
 \begin{enumerate}
-\item Every class $[\alpha\oplus\beta\oplus\gamma] \in \Hh^2({\bar G},\EEx)$ is cohomologous to one with $\gamma=0$.
+\item Every class $[\alpha\oplus\beta\oplus\gamma] \in \Hh^2(E^\bullet_G)$ is cohomologous to one with $\gamma=0$.
 \item The map $\Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx))$ is given by $[\alpha\oplus\beta\oplus 0] \mapsto [\beta]$.
@@
 \end{enumerate}
+\todo{add more connecting prose}
 \end{proposition}
@@
 \[\alpha\oplus \beta \in Z^2(E^\bullet_G).\]
-Although the cocycle $\alpha\oplus \beta$ is not well defined by $\qcs{L}$, its class in $Z^2(E^\bullet_G)$ is.
+Although the cocycle $\alpha\oplus \beta$ is not well defined by $\qcs{L}$, its class in $\Hh^2(E^\bullet_G)$ is.
 To see this, let $\{ v'_x \in \gqcs{L}_x^\times \tq x \in {\bar G}\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$ be defined by $\qcs{L}$ and this choice, as above.
@@
 
-\begin{proposition}\label{prop:SGiso}
+\begin{proposition}
 If $G$ is \'etale then $S_G$ is an isomorphism.
@@
 \begin{proposition}\label{prop:sur_etale}
-If $G$ is \'etale, then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective
-and admits a section.
+If $G$ is \'etale, then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective.
 \end{proposition}
@@
 Pick $\chi \in G(\Fq)^*$.
-Let $[\beta]\in \Hh^1(\Weil{},\bG^*)$ be the class corresponding to $\chi$ under Lemma~\ref{lem:dual-inv}.
-Every representative cocycle $\beta \in Z^1(\Weil{},\bG^*)$ determines a homomorphism $\beta(\Frob{}) : G(\bFq)\to \EEx$ such that $\beta(\Frob{})\vert_{G(\Fq)} = \chi$.
+By Lemma~\ref{lem:dual-inv}, there is some $b\in G(\bFq)^*$ such that $b\vert_{G(\Fq)} = \chi$.
 Set $\gqcs{L}_x = \EE$ for every $x\in G(\bFq)$.
 Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$ and
-$\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = \beta(\Frob{})(x)$.
-Since $\beta(\Frob{}) : G(\bFq) \to \EEx$ is a group homomorphism,
-condition \eqref{nohom} is satisfied with $a =1$.
-So $\qcs{L} = (\gqcs{L}, \mu, \phi)$
+$\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = b(x)$.
+Since $b : G(\bFq) \to \EEx$ is a group homomorphism,
+condition \eqref{nohom} is satisfied with $a =1$ and $\qcs{L} = (\gqcs{L}, \mu, \phi)$
 is a quasicharacter sheaf with $\trFrob{\qcs{L}} = \chi$.
-This shows that $\TrFrob{G}$ is surjective.
-%
-Now let $\beta' \in Z^1(\Weil{},\bG^*)$ be another representative for $[\beta]$
-so $\beta'-\beta = d_{\Weil{}} \delta$ for some $\delta \in C^0(\Weil{},\bG^*)$ defining $d \in \Hom(G(\bFq),\EEx)$.
-Let $\qcs{L}'$ be the quasicharacter sheaf on $G$ defined by $\beta'$, as above.
-For each $x\in G(\bFq)$, define $\brho_x :\qcs{L}_x\to \qcs{L}'_x$ by $\brho_x(1) = d(x)$.
-Since condition~\ref{qc.4} is satisfied for $\{ \brho_x \tq x\in G(\bFq)\}$, it defines a morphism $\rho : \qcs{L}\to \qcs{L}'$, which is clearly and isomorphism. 
-%
-We have now defined a section of $\TrFrob{G}$. 
 \end{proof}
@@
 \begin{proof}
-This result follows easily from Propositions~\ref{prop:ses_desc}, \ref{prop:SGiso} and \ref{prop:sur_etale}.
-\end{proof}
-
-Combining Propositions~\ref{prop:sur_etale} and \ref{prop:etale-iso} gives the following
-
-\begin{corollary}\label{cor:split}
-The short exact sequence
- \[
-    0 \to
-    \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to
-    \Hh^2(E^\bullet_G) \to
-    \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to
-    0
- \]
- is split.
-\end{corollary}
+This result follows from Propositions~\ref{prop:ses_desc} and \ref{prop:sur_etale}.
+\end{proof}
 
@@
 
-Most of this paper focuses on the question of determining the isomorphism classes of objects; a complete understanding of the morphisms in $\QC(G)$ also requires a description of the automorphisms of an arbitrary quasicharacter sheaf $\qcs{L}$.
+Most of this paper focuses on the question of determining the isomorphism classes of objects in $\QC{G}$.
+A full understanding of the category also requires a description of the morphisms.
 
@@
 
-Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism then defining $\brho_x$ as multiplication by $\rho(x)$ will define $\gqcs{L} \to \gqcs{L}'$ satisfy the two diagrams in \ref{qc.4}.
+Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism, then defining $\brho_x$ as multiplication by $\rho(x)$ will define a morphism $\gqcs{L} \to \gqcs{L}'$ satisfy the two diagrams in \ref{qc.4}.
 
@@
 Let $\bQC(G)$ be the category of pairs $(\qcs{E},\mu_\qcs{E})$
-where $\qcs{E}$ an $\ell$-adic local system on $G$ of rank-one,
+where $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank-one,
 equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes \qcs{E}$
-satisfying the analogue of \ref{QC.1} on $G$;
+satisfying the analogue of \ref{QC.2} on $G$;
 morphisms in $\bQC(G)$ are defined as in the second part of
-\ref{QC.3}.
+\ref{QC.4}.
 \end{definition}
@@
  Suppose $(\qcs{E},\mu_\qcs{E})$ in an object of $\bQC(G)$.
- Then $\qcs{E}$ is an $\ell$-adic constructible sheaf on $G$ and
+ Then $\qcs{E}$ \todo{should this be $b_G^* \qcs{E}$?} is an $\ell$-adic constructible sheaf on $G$ and
  $b_G^* \qcs{E}$ comes equipped with an isomorphism
@@
  The functor $\qcs{E} \mapsto (b_G^* \qcs{E},\phi_\qcs{E})$
- from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
+ from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$ \todo{are the domain and codomain here really supposed to be the same?}
  is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} and \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}.
@@
 \begin{proposition}\label{prop:finite}
-Let $f: H \to G$ be a discrete isogeny; let $A$ be the kernel of $f$.
+Let $f: H \to G$ be a discrete isogeny and let $A$ be the kernel of $f$.
 Let $V$ be a $1$-dimensional representation of $A$ 
@@
 \begin{proof}
-Let $f$, $A$, $V$ and $\psi$ be as above; set $\qcs{E} = (f_! V_H)_\psi$.
+Let $f$, $A$, $V$ and $\psi$ be as above and set $\qcs{E} = (f_! V_H)_\psi$.
 Since $A$ is abelian, $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank one.
-We must show that comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
-To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between local systems on $G$ and $A$-equivariant local systems on $H$; {\it cf.\ } \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}.
+We must show that $\qcs{E}$ comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
+To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$ \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}.
 In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
@@
 %\todo{Fix citelist} %\citelist{\cite{deligne:SGA4.5}*{Sommes trig.},\cite{laumon:87a}*{1.1.3}}
-The key observation is that, by \'etale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ (this is a particular case of the argument in the proof of Proposition~\ref{prop:finite}) and that, for every $\qcs{E}$ in $\bQC(G)$, the trace of $\Lang^*\qcs{E}$ as a representation of $G(\Fq)$, is $\trFrob{\qcs{E}}^{-1}$.
-
+The key observation is that, by \'etale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
+(Note that this is a particular case of the argument in the proof of Proposition~\ref{prop:finite}.)
 Using the equivalence given by $\Lang^*$, if $\Lang^*\qcs{E} = V$ with character $\psi$ and isomorphism $V\to V\otimes V$ then 
 $\qcs{E} \iso (\Lang_!
-V)_\psi$, the $\psi$-isotypic component of the push-forward of the constant sheaf $V$ on $G$ by $\Lang$, equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes\qcs{E}$ determined by $V\to V\otimes V$.
+V)_\psi$, the $\psi$-isotypic component of the push-forward $\Lang_* V$ of the constant sheaf $V$ on $G$ equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes\qcs{E}$ determined by $V\to V\otimes V$.
 Moreover, $\Aut(\qcs{E})$ is the group of automorphisms of $\rho : V\to V$ for which 
@@
 %\begin{remark}
-We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of quasicharacter sheaves on $G$ is equivalent to the category of one-dimensional representations $V$ of $G(\Fq)$ equipped with an isomorphism $V\iso \EE$, and therefore equivalent to the category of characters $\psi$ of $G(\Fq)$.
+We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of quasicharacter sheaves on $G$ is equivalent to the category of characters $\psi$ of $G(\Fq)$.
 We have also just seen that if the character of $\Lang^*\qcs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\qcs{E} : \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ which is part of the data that determines a quasicharacter sheaf on $G$.
-That leads to a perspective on the function-sheaf dictionary common in the literature in which one considers one-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$; see \cite{kamgarpour:09a}*{Intro}, for example.
-As a slight variation, one may also consider one-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
+That leads to a perspective on the function-sheaf dictionary common in the literature in which one considers $1$-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$; see \cite{kamgarpour:09a}*{Intro}, for example.
+As a slight variation, one may also consider $1$-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
 %One may show that all such $\gqcs{L}$ are determined by extensions of $\bG$ by $\EEx$ which are fixed by Frobenius and that the trace of Frobenius provides a canonical isomorphism from $\Hh^2(\bG,\EEx)^{\Frob{}}$ to $G(\Fq)^*$; {\it cf.\ }
@@
 
-Although the category of quasicharacter sheaves on $G$ does specialize to that common notion when $G$ is connected and of finite type, the common notion is not appropriate if one wishes to extend the dictionary to smooth commutative group schemes.
+Although the category of quasicharacter sheaves on $G$ does specialize to that common notion when $G$ is connected and of finite type, the common notion is not appropriate if one wishes to extend the dictionary to smooth commutative group schemes over finite fields.
 In particular, as we have already seen in Section~\ref{sec:etale}, for a given quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ there may be a different isomorphism $\mu' : \bm^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$ for which $\qcs{L}'=(\gqcs{L},\mu',\phi)$ is also a quasicharacter sheaf on $G$, not isomorphic to $\qcs{L}$ in $\QC(G)$.
 Indeed, Proposition~\ref{prop:etale-iso} shows that when $G$ is \'etale, $\Hh^2(\bG,\EEx)^{\Weil{}}$ measures the possibilities for $\mu'$.
-On \'etale group schemes, the common perspective on the function-sheaf dictionary leads only to the part of category of quasicharacter sheaves that is invisible to the trace of Frobenius.
-
-We will see in Section~\ref{sec:main} that, for any smooth commutative group scheme $G$, the part of the category of quasicharacter sheaves that is invisible to the trace of Frobenius is measured by $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
+The common perspective on the function-sheaf dictionary leads only to the part of category of quasicharacter sheaves that is invisible to the trace of Frobenius.
+
+We will see in Section~\ref{sec:main} that, for any smooth commutative group scheme $G$, the part of category of quasicharacter sheaves that is invisible to the trace of Frobenius are measured by $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
 %\end{remark}
@@
 Let $\qcs{L}$ be a quasicharacter sheaf on $\pi_0(G)$ and let $\rho : \pi_0^*\qcs{L} \to (\EE)_{G}$ be an isomorphism in $\QC(G)$.
-For each $x\in \pi_0(\bG)$, set $\bG^x \ceq \pi_0^{-1}(x)$.
-The restriction $\pi_0^*\gqcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gqcs{L}_x)_{\bG^x}$ so the isomorphism $\brho_{\bG^x} : (\gqcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gqcs{L}_x \to (\EE)_x$.
+For each $x\in \pi_0(\bG)$, the restriction $\pi_0^*\gqcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gqcs{L}_x)_{\bG^x}$ so the isomorphism $\brho_{\bG^x} : (\gqcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gqcs{L}_x \to (\EE)_x$.
 The collection $\{ \brho_x \tq x\in \pi_0(\bG) \}$ determines an isomorphism $\qcs{L} \to (\EE)_{\pi_0(G)}$  in $\QC(\pi_0(G))$.
@@
 
-As above, set $\bG^x \ceq \pi_0^{-1}(x)$ for $x\in \pi_0(\bG)$.
+For each $x\in \pi_0(\bG)$, set $\bG^x \ceq \pi_0^{-1}(x)$.
 Let $g, g'$ be geometric points in the same
@@
 from $\gqcs{L}_{g}$ to $\gqcs{L}_{g'}$.
-%
+
 The isomorphisms $\varphi_{g,g'}: \gqcs{L}_{g} \to \gqcs{L}_{g'}$ are canonical
@@
  \begin{equation}\label{eq:qc}
-  \begin{tikzcd}[column sep=40]
+  \begin{tikzcd}[column sep=55]
    \gqcs{L}_{gh} \arrow{r}{\varphi_{gh,g'h'}} \arrow[swap]{d}{\mu_{g,h}}
@@
 We saw in Proposition~\ref{prop:functorialG} that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
-In this section we find the image and kernel of $\TrFrob{G}$.
+In this section we improve that result.
 
@@
 \begin{proof}
-%  Recall the short exact sequence \eqref{eq:pi0}
-%  defining the component group scheme for $G$:
-%  \[
-%  \begin{tikzcd}
-%    1 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
-%  \end{tikzcd}
-%  \]
+  Recall the short exact sequence \eqref{eq:pi0}
+  defining the component group scheme for $G$:
+  \[
+  \begin{tikzcd}
+    1 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
+  \end{tikzcd}
+  \]
   Let
   \[
-  \begin{tikzcd}[row sep=20, column sep=20]
+  \begin{tikzcd}[row sep=20]
 %  & 0 \arrow{d} & 0 \arrow{d} & 0\arrow{d} \\
@@
 This homomorphism is injective because morphisms of sheaves are determined by the linear transformations induced on stalks.  
-Homomorphisms in the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ are continuous when $\bG$ is viewed as the base of the espace \'etal\'e attached to $\gqcs{L}$.
-Since $\ell$ is invertible in $\Fq$, it follows that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
+Note that homomorphisms in the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ are continuous where $\bG_{\Weil{}}$ is given the topology of the base of the espace \'etal\'e attached to $\gqcs{L}$.
+Since $\ell$ is invertible in $\Fq$, it now follows that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
 We also have $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
 To see that $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho^y: \gqcs{L}^y \to \gqcs{L}^y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
-This defines an isomorphism $\bar\rho : \gqcs{L}\to \gqcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\qcs{L}\to \qcs{L}$ which maps to $\theta$ under $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
+This defines an isomorphism $\bar\rho : \gqcs{L}\to \gqcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\qcs{L}\to \qcs{L}$ with maps to $\theta$ under $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
 \end{proof}
@@
 
-Let $K$ be a local field with finite residue field $\Fq$. 
-In this section we consider connected commutative algebraic groups over $K$ that admit a N\'eron model, by which we mean a locally finite type N\'eron model.
+Let $K$ be a local field (in the sense of Serre) with residue field $\Fq$. 
+In this section we consider connected commutative algebraic groups over $K$ that admit a N\'eron model, by which we mean a locally of finite type N\'eron model.
 By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected commutative algebraic groups over $K$ that contain no subgroup of type $\mathbb{G}_\text{a}$.
@@
 For every non-negative integer $n$, $\Gr^R_n(X)$ is a {\it smooth} commutative group scheme over $S_0$
-with component group scheme $\pi_0(X)_{\Fq} \ceq \pi_0(X) \times_S S_0$ and $\Fq$-rational points $X(R_n).$
+with component group scheme $\pi_0(X) \times_S S_0$ and $\Fq$-rational points $X(R_n).$
 %
 The Greenberg transform $\Gr_R(X)$ of $X$ is a commutative group scheme over $\Fq$
-with component group scheme $\pi_0(X)_{\Fq}$
+with component group scheme $\pi_0(X) \times_S S_0$
 and $\Fq$-rational points $X(K).$
@@
 As we explained in the Introduction, our original motivation for this paper was to find a geometrization and categorification of quasicharacters of $p$-adic tori.
-This is is now provided by specializing Theorem~\ref{thm:QCXK} to the case when $X_K= T_K\in \mathcal{N}_K$ is an algebraic torus over $K$.
+This is is now provided by specializing Theorem~\ref{thm:QCXK} to the case when $X_K= T\in \mathcal{N}_K$ is an algebraic torus over $K$, in which case we write $\underline{T}$ for the Neron model $X$.
 Now,
 \[
- \pi_0(T)_{\bFq} = X_*(T_K)_{\mathcal{I}_K},
-\]
-where $X_*(T_K)$ is the cocharacter lattice of $T_K$ and $\mathcal{I}_K$ is the inertia group for $K$ \cite{bitan:discriminant}*{Eq 3.1}. 
+ \pi_0(\underline{T})_{\bFq} = X_*(T)_{\mathcal{I}_K},
+\]
+where $X_*(T)$ is the cocharacter lattice of $T$ and $\mathcal{I}_K$ is the inertia group for $K$ \cite{bitan:discriminant}*{Eq 3.1}. 
 Accordingly, the short exact sequence in Theorem~\ref{thm:QCXK} becomes
 \begin{equation}
-0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{T_K} \to \Hom_\text{qc}(T(K),\EEx) \to 0.
+0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{T} \to \Hom_\text{qc}(T(K),\EEx) \to 0.
 \end{equation}
-Again by Theorem~\ref{thm:QCXK}, the automorphism groups in $\QC(T_K)$ are given, for every quasicharacter sheaf $\qcs{F}$ for $T_K$, by
+Again by Theorem~\ref{thm:QCXK}, the automorphism groups in the $\QC(T)$ are given, for every quasicharacter sheaf $\qcs{F}$ for $T$, by
 \begin{equation}
-\Aut(\qcs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx) \iso \Hom(X_*(T_K),\EEx)^{\Weil{K}} = (\check{T}_\ell)^{\Weil{K}}
+\Aut(\qcs{F}) \iso \Hom(X_*(T)_{\Weil{K}},\EEx) \iso \Hom(X_*(T),\EEx)^{\Weil{K}} = (\check{T}_\ell)^{\Weil{K}}
 \end{equation}
-where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T_K$.
-This provides good information above the category $\QC(T_K)$ of quasicharacters for $T_K$ and its relation to quasicharacters of $T(K)$.
+where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
 
@@
 what follows will not depend on these choices.
-Suppose $\ell$ is invertible in the residue fields of $K$ and $L$.
-
-We begin with $X_K\in \mathcal{N}_K$ with N\'eron model $X$ and $Y_{L}\in \mathcal{N}_L$ with N\'eron model $Y$.
+
+Suppose $X_K\in \mathcal{N}_K$ with N\'eron model $X$ and $Y_{L}\in \mathcal{N}_L$ with N\'eron model $Y$.
 Suppose $m$ is a positive integer such that 
@@
 Then
-\[
+$
 \Gr^{\OK}_{m-1}(X) \iso \Gr^{\OL}_{m-1}(Y)
-\]
+$
 as smooth group schemes over $\Fq$; accordingly, by Lemma~\ref{lem:pullback} the isomorphism above determines an equivalence of categories
@@
 The isomorphism \eqref{eq:schematic_transfer} can indeed exist between quasicharacters of algebraic tori over local fields, even when the characteristics of $K$ and $L$ differ.
-Suppose $T_K$ and $M_L$ are tori over local fields $K$ and $L$,
-splitting over $K'$ and $L'$, respectively.
+Suppose $T_K$ and $M_L$ are tori over non-archimedian local fields $K$ and $L$,
+splitting over $K'$ and $L'$ respectively.
 Then $T_K$ and $M_L$ are said to be \emph{$n$-congruent} \cite{chai-yu:01a}*{\S 2} if there are isomorphisms
@@
  \begin{enumerate}
-  \item $\alpha$ induces an isomorphism $\OK/\varpi_K^n \OK \to \OO{L}/\varpi_{L}^n \OO{L}$,
+  \item $\alpha$ induces an isomorphism $\OK/\pi_K^n \OK \to \OO{L}/\pi_{L}^n \OO{L}$,
   \item $\alpha$ is $\Gal(K'/K)$-equivariant relative to $\beta$, and
@@
 \begin{equation}\label{transfer}
-  \Hom_{n-1}(T_K(K), \EEx) \iso \Hom_{n-1}(M_L(L),\EEx).
+  \Hom_{n-1}(T_K(K), \EEx) \iso \Hom_{n-1}(M_L(M),\EEx).
 \end{equation}
@@
  \[
-\Hom_{m-1}(T(K), \EEx) \iso  \Hom_{m-1}(M(L), \EEx)
+\Hom_{m-1}(T_K(K), \EEx) \iso  \Hom_{m-1}(M_L(L), \EEx)
  \]
@@
 We thank Takashi Suzuki for some very helpful observations and suggestions, especially related to our use of the Hochschild-Serre spectral sequence.
+We thank Joseph Bernstein for suggesting a connection between our category of quasicharacter sheaves for $p$-adic tori and quasicharacters of its pure rational forms.
 We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and drawing our attention to their result on Weil restriction and the Greenberg transform.
-We thank Joseph Bernstein for suggesting a connection between our category of quasicharacter sheaves for $p$-adic tori and quasicharacters of its pure rational forms.
 }

### 2014-08-30 crelle-dictionary.tex
More typo fixes

@@
  Suppose $(\qcs{E},\mu_\qcs{E})$ in an object of $\bQC(G)$.
- Then $\qcs{E}$ \todo{should this be $b_G^* \qcs{E}$?} is an $\ell$-adic constructible sheaf on $G$ and
- $b_G^* \qcs{E}$ comes equipped with an isomorphism
+ Then $b_G^* \qcs{E}$ is an $\ell$-adic constructible sheaf on $G$ and
+ comes equipped with an isomorphism
  $\phi_\qcs{E} : \Frob{G}^* b_G^*\qcs{E} \to b_G^* \qcs{E}$.
  The functor $\qcs{E} \mapsto (b_G^* \qcs{E},\phi_\qcs{E})$
- from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$ \todo{are the domain and codomain here really supposed to be the same?}
+ from $\ell$-adic constructible sheaves on $G$ to Weil sheaves on $\bG$
  is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} and \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}.
@@
  \item every quasicharacter sheaf on $G$ is isomorphic to one defined by a discrete isogeny;%as in Proposition~\ref{prop:finite};
- \item $\Aut(\qcs{L}) = 1$, for all quasicharacter sheaves $\qcs{L}$ on $G$;
+ \item $\Aut(\qcs{L}) = 1$, for all quasicharacter sheaves $\qcs{L}$ on $G$.
 %  \item for all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $G$ and for every $\rho \in \Hom(\qcs{L},\qcs{L}')$, either $\rho$ is trivial or an isomorphism.
@@
 \begin{proof}
-In Lemma~\ref{lem:bounded_connected} we saw that every quasicharacter sheaf $\qcs{L}$ on $G$ descends to $G$; let $\qcs{E}$ be an object of $\bQC(G)$ for which $B_G(\qcs{E}) \iso \qcs{L}$.
+In Lemma~\ref{lem:bounded_connected} we saw that every quasicharacter sheaf $\qcs{L}$ on $\bG$ descends to $G$; let $\qcs{E}$ be an object of $\bQC(G)$ for which $B_G(\qcs{E}) \iso \qcs{L}$.
  Since the functor $B_G : \bQC(G) \to \QC(G)$ is full and faithful, $\Aut(\qcs{L}) = \Aut(\qcs{E})$.
@@
 The key observation is that, by \'etale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
+\todo{clarify phrasing}
 (Note that this is a particular case of the argument in the proof of Proposition~\ref{prop:finite}.)

### 2014-08-30 crelle-dictionary.tex

--- 2014-08-27 crelle-dictionary.tex
@@
 \begin{enumerate}
-\item Every class $[\alpha\oplus\beta\oplus\gamma] \in \Hh^2({\bar G},\EEx)$ is cohomologous to one with $\gamma=0$.
+\item Every class $[\alpha\oplus\beta\oplus\gamma] \in \Hh^2(E^\bullet_G)$ is cohomologous to one with $\gamma=0$.
 \item The map $\Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx))$ is given by $[\alpha\oplus\beta\oplus 0] \mapsto [\beta]$.
@@
  Suppose $(\qcs{E},\mu_\qcs{E})$ in an object of $\bQC(G)$.
- Then $\qcs{E}$ is an $\ell$-adic constructible sheaf on $G$ and
- $b_G^* \qcs{E}$ comes equipped with an isomorphism
+ Then $b_G^* \qcs{E}$ is an $\ell$-adic constructible sheaf on $G$ and
+ comes equipped with an isomorphism
  $\phi_\qcs{E} : \Frob{G}^* b_G^*\qcs{E} \to b_G^* \qcs{E}$.
  The functor $\qcs{E} \mapsto (b_G^* \qcs{E},\phi_\qcs{E})$
- from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
+ from $\ell$-adic constructible sheaves on $G$ to Weil sheaves on $\bG$
  is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} and \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}.
@@
 \begin{proof}
-Let $f$, $A$, $V$ and $\psi$ be as above; set $\qcs{E} = (f_! V_H)_\psi$.
+Let $f$, $A$, $V$ and $\psi$ be as above and set $\qcs{E} = (f_! V_H)_\psi$.
 Since $A$ is abelian, $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank one.
-We must show that comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
-To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between local systems on $G$ and $A$-equivariant local systems on $H$; {\it cf.\ } \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}.
+We must show that $\qcs{E}$ comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
+To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$ {\it cf.\ } \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}.
 In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.

### 2014-08-30 crelle-dictionary.tex
Expanded the proofs of Propositions BG and connected.

@@
 \begin{proof}
+ Suppose $(\qcs{E},\mu_\qcs{E})$ in an object of $\bQC(G)$.
  Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Suppose $(\qcs{E},\mu_\qcs{E})$ in an object of $\bQC(G)$.
- Then $b_G^* \qcs{E}$ is an $\ell$-adic constructible sheaf on $G$ and
- comes equipped with an isomorphism
- $\phi_\qcs{E} : \Frob{G}^* b_G^*\qcs{E} \to b_G^* \qcs{E}$.
- The functor $\qcs{E} \mapsto (b_G^* \qcs{E},\phi_\qcs{E})$
- from $\ell$-adic constructible sheaves on $G$ to Weil sheaves on $\bG$
+ Set $\gqcs{L} = b_G^* \qcs{E}$. 
+ The functor $b_G^*$ takes local systems on $G$ to local systems on $\bG$.
+ The local system $\gqcs{L}$ comes equipped with an isomorphism
+ $\phi: \Frob{G}^* \gqcs{L} \to \gqcs{L}$.
+ The resulting functor from local systems on $G$ to Weil local systems on $\bG$, given on objects by $\qcs{E} \mapsto (\gqcs{L},\phi)$, 
  is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} and \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}.
- This functor preserves local constancy, so takes local systems to local systems.
  The isomorphism $\mu \ceq b_{G\times G}^*\mu_\qcs{E}$ satisfies \ref{QC.2}
- with $b_G^*\qcs{E}$ playing the role of $\gqcs{L}$.
- Moreover, $\phi_\qcs{E}$ is compatible with $\mu_\qcs{E}$ in the sense of \ref{QC.3}.
- This construction defines the functor $B_G : (\qcs{E},\mu_\qcs{E}) \mapsto (b_G^*\qcs{E},b_{G\times G}^*\mu_\qcs{E}, \phi_\qcs{E})$
- and also shows that it is full and faithful.
+ for $\gqcs{L}$ and $\phi$ is compatible with $\mu$ in the sense of \ref{QC.3}.
+ This construction defines the functor $B_G : \bQC(G) \to \QC(G)$ given on objects by $(\qcs{E},\mu_\qcs{E}) \mapsto (\gqcs{L},\mu, \phi)$, as defined here. 
+ Because morphisms in $\bQC(G)$ and $\QC(G)$ are morphisms of local systems on $G$ and $\bG$, respectively, satisfying condition~\ref{QC.4}, this functor is also full and faithful.
 \end{proof}
@@
  \end{proposition}
-
 \begin{proof}
@@
 %\todo{Fix citelist} %\citelist{\cite{deligne:SGA4.5}*{Sommes trig.},\cite{laumon:87a}*{1.1.3}}
-The key observation is that, by \'etale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ (this is a particular case of the argument in the proof of Proposition~\ref{prop:finite}) and that, for every $\qcs{E}$ in $\bQC(G)$, the trace of $\Lang^*\qcs{E}$ as a representation of $G(\Fq)$, is $\trFrob{\qcs{E}}^{-1}$.
-
-Using the equivalence given by $\Lang^*$, if $\Lang^*\qcs{E} = V$ with character $\psi$ and isomorphism $V\to V\otimes V$ then 
-$\qcs{E} \iso (\Lang_!
-V)_\psi$, the $\psi$-isotypic component of the push-forward of the constant sheaf $V$ on $G$ by $\Lang$, equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes\qcs{E}$ determined by $V\to V\otimes V$.
-Moreover, $\Aut(\qcs{E})$ is the group of automorphisms of $\rho : V\to V$ for which 
+
+As in the proof of Proposition~\ref{prop:finite}, use \'etale descent to see that pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.
+Under this equivalence, local systems $\qcs{E}$ on $G$ arising from objects in $\bQC(G)$ are matched with $G(\Fq)$-equivariant constant local systems of rank-one on $G$, and therefore with one-dimensional representations of $G(\Fq)$.
+In the same way, pullback along the isogeny $\Lang\times\Lang : G\times G\to G\times G$ matches the extra structure $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ with an isomorphism $m^*V \to V\boxtimes V$ of one-dimensional representations of $G(\Fq)\times G(\Fq)$, which is exactly an isomorphism $V \to V\otimes V$ of one-dimensional representations, which is exactly the choice of an isomorphism $V\iso \EE$.
+In this way we see that $\bQC(G)$ is equivalent to the category of characters of $G(\Fq)$.
+A simple calculation on stalks at geometric points ${\bar g}$ above $\Fq$-rational points $g \in G(\Fq)$ reveals that, if $\qcs{E}$ matches $\psi : G(\Fq)\to \EEx$ under this equivalence, then the action of Frobenius on $\qcs{E}{\bar g}$ is multiplication by $\psi(g)^{-1}$.
+In other words, for every $\qcs{E}$ in $\bQC(G)$, the trace of $\Lang^*\qcs{E}$, as a representation of $G(\Fq)$, is $\trFrob{\qcs{E}}^{-1}$.
+This proves parts (i) and (ii) of Proposition~\ref{prop:connected}.
+
+To finish the proof of part (iii), suppose $\Lang^*\qcs{E} = V$ with isomorphism $V \to V\otimes V$ and observe that the equivalence above establishes a bijection between $\Aut(\qcs{E})$ and the group of automorphisms of $\rho : V\to V$ for which
 \[

### 2014-08-30 crelle-dictionary.tex
Small change to wording in the Introduction.

@@
 As indicated above, our interest in the function-sheaf dictionary for smooth commutative group schemes
-over finite fields comes from an application to $p$-adic representation theory. 
+over finite fields comes from an application to $p$-adic representation theory,
+specifically to quasicharacters of $p$-adic tori.
 However, we found that our method of passing from $p$-adic tori to group schemes over $\Fq$ applies more generally to
-any local field $K$ with finite residue field $\Fq$ and any algebraic group $X_K$ that admits a N\'eron model $X$ over $R$, the ring of integers of $K$.
+any local field $K$ with finite residue field $\Fq$ and any algebraic group $X_K$ that admits a N\'eron model $X$. % over $R$, the ring of integers of $K$.
 This class of groups includes abelian varieties and unipotent $K$-wound groups in addition to the tori we initially considered.

### 2014-08-31 crelle-dictionary.tex
Solved my biblio problems . . .
 . .  by pointing my bibliography to your main one.
But does this make problems for you?
Playing with a different title and asked a question l.897.

@@
 
-\title[The function-sheaf dictionary for smooth commutative group schemes]{The function-sheaf dictionary for smooth commutative group schemes over finite fields}
+\title{Quasicharacters and the function-sheaf dictionary}
 
@@
 \[
-\Aut(\qcs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
+\Aut(\qcs{F}) \iso \Hh^1(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} = (\check{T}_\ell)^{\Weil{K}},
 \]
@@
 Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Weil{}})^*$.
+\todo{Can we use this sort or argument to prove $(X_{\Weil{}})^* \iso (X^*)^{\Weil{}}$?
+If so, let's re-state the $\Aut(\qcs{L})$ result as $\Hh^1(\pi_0(\bG),\EEx)^{\Weil{}}$ since the iso classes are $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.}
 \end{proof}
@@
 \begin{equation}
-\Aut(\qcs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx) \iso \Hom(X_*(T_K),\EEx)^{\Weil{K}} = (\check{T}_\ell)^{\Weil{K}}
+\Aut(\qcs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx)  = (\check{T}_\ell)^{\Weil{K}}
 \end{equation}
@@
 %\bibliographystyle{amsalpha}
-\bibliography{bibliography/Biblio}
+\bibliography{../bibliography/Biblio}
 

### 2014-09-04 crelle-dictionary.tex
Finished working through paper

@@
 \begin{lemma} \label{lem:dual-inv}
-Let $X$ be an abelian group equipped with an action of $\Weil{}$.
- Then
+Let $X$ be an abelian group equipped with an action of $\Weil{}$.  Then
 \begin{align*}
@@
 Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Weil{}})^*$.
-\todo{Can we use this sort or argument to prove $(X_{\Weil{}})^* \iso (X^*)^{\Weil{}}$?
-If so, let's re-state the $\Aut(\qcs{L})$ result as $\Hh^1(\pi_0(\bG),\EEx)^{\Weil{}}$ since the iso classes are $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.}
 \end{proof}
@@
 
+Using this equivalence of categories, we may give a good description of $\QC(G)$ when $G$ is connected and finite type.
+
 \begin{proposition}\label{prop:connected}
@@
 \begin{proof}
-In Lemma~\ref{lem:bounded_connected} we saw that every quasicharacter sheaf $\qcs{L}$ on $\bG$ descends to $G$; let $\qcs{E}$ be an object of $\bQC(G)$ for which $B_G(\qcs{E}) \iso \qcs{L}$.
+In Lemma~\ref{lem:bounded_connected}, we saw that every quasicharacter sheaf $\qcs{L}$ on $\bG$ descends to $G$; let $\qcs{E}$ be an object of $\bQC(G)$ for which $B_G(\qcs{E}) \iso \qcs{L}$.
  Since the functor $B_G : \bQC(G) \to \QC(G)$ is full and faithful, $\Aut(\qcs{L}) = \Aut(\qcs{E})$.
@@
 
-As in the proof of Proposition~\ref{prop:finite}, use \'etale descent to see that pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.
+As in the proof of Proposition~\ref{prop:finite}, use \'etale descent to see that pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.
 Under this equivalence, local systems $\qcs{E}$ on $G$ arising from objects in $\bQC(G)$ are matched with $G(\Fq)$-equivariant constant local systems of rank-one on $G$, and therefore with one-dimensional representations of $G(\Fq)$.
 In the same way, pullback along the isogeny $\Lang\times\Lang : G\times G\to G\times G$ matches the extra structure $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ with an isomorphism $m^*V \to V\boxtimes V$ of one-dimensional representations of $G(\Fq)\times G(\Fq)$, which is exactly an isomorphism $V \to V\otimes V$ of one-dimensional representations, which is exactly the choice of an isomorphism $V\iso \EE$.
-In this way we see that $\bQC(G)$ is equivalent to the category of characters of $G(\Fq)$.
-A simple calculation on stalks at geometric points ${\bar g}$ above $\Fq$-rational points $g \in G(\Fq)$ reveals that, if $\qcs{E}$ matches $\psi : G(\Fq)\to \EEx$ under this equivalence, then the action of Frobenius on $\qcs{E}{\bar g}$ is multiplication by $\psi(g)^{-1}$.
-In other words, for every $\qcs{E}$ in $\bQC(G)$, the trace of $\Lang^*\qcs{E}$, as a representation of $G(\Fq)$, is $\trFrob{\qcs{E}}^{-1}$.
-This proves parts (i) and (ii) of Proposition~\ref{prop:connected}.
-
-To finish the proof of part (iii), suppose $\Lang^*\qcs{E} = V$ with isomorphism $V \to V\otimes V$ and observe that the equivalence above establishes a bijection between $\Aut(\qcs{E})$ and the group of automorphisms of $\rho : V\to V$ for which
+We see that $\bQC(G)$ is equivalent to the category of characters of $G(\Fq)$.
+Let $\bg$ be a geometric point above $g \in G(\Fq)$.
+If $\qcs{E}$ matches $\psi : G(\Fq)\to \EEx$ under this equivalence, a simple calculation on stalks reveals that the action of Frobenius on $\qcs{E}_{\bar g}$ is multiplication by $\psi(g)^{-1}$.
+In other words, for every $\qcs{E}$ in $\bQC(G)$, the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ as a representation of $G(\Fq)$, proving parts (i) and (ii).
+
+To finish the proof of part (iii), suppose $\Lang^*\qcs{E} = V$ with isomorphism $V \to V\otimes V$.
+Observe that the equivalence above establishes a bijection between $\Aut(\qcs{E})$ and the group of automorphisms of $\rho : V\to V$ for which
 \[
@@
 We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of quasicharacter sheaves on $G$ is equivalent to the category of one-dimensional representations $V$ of $G(\Fq)$ equipped with an isomorphism $V\iso \EE$, and therefore equivalent to the category of characters $\psi$ of $G(\Fq)$.
-We have also just seen that if the character of $\Lang^*\qcs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\qcs{E} : \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ which is part of the data that determines a quasicharacter sheaf on $G$.
-That leads to a perspective on the function-sheaf dictionary common in the literature in which one considers one-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$; see \cite{kamgarpour:09a}*{Intro}, for example.
+We have also just seen that if the character of $\Lang^*\qcs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\qcs{E} : \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
+This fact leads to a perspective on the function-sheaf dictionary common in the literature in which one considers one-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$ \cite{kamgarpour:09a}*{Intro}.
 As a slight variation, one may also consider one-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
@@
 
-Although the category of quasicharacter sheaves on $G$ does specialize to that common notion when $G$ is connected and of finite type, the common notion is not appropriate if one wishes to extend the dictionary to smooth commutative group schemes.
-In particular, as we have already seen in Section~\ref{sec:etale}, for a given quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ there may be a different isomorphism $\mu' : \bm^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$ for which $\qcs{L}'=(\gqcs{L},\mu',\phi)$ is also a quasicharacter sheaf on $G$, not isomorphic to $\qcs{L}$ in $\QC(G)$.
-Indeed, Proposition~\ref{prop:etale-iso} shows that when $G$ is \'etale, $\Hh^2(\bG,\EEx)^{\Weil{}}$ measures the possibilities for $\mu'$.
-On \'etale group schemes, the common perspective on the function-sheaf dictionary leads only to the part of category of quasicharacter sheaves that is invisible to the trace of Frobenius.
-
-We will see in Section~\ref{sec:main} that, for any smooth commutative group scheme $G$, the part of the category of quasicharacter sheaves that is invisible to the trace of Frobenius is measured by $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
-%\end{remark}
+Although the category of quasicharacter sheaves on $G$ specializes to the one described above when $G$ is connected and of finite type, this description is not sufficient when extending the dictionary to smooth commutative group schemes.
+In particular, for a given $\gqcs{L}$ and $\phi$ there may be many $\mu$ so that $(\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf.
+For \'etale $G$, Proposition~\ref{prop:etale-iso} shows that $\Hh^2(\bG,\EEx)^{\Weil{}}$ measures the possibilities for $\mu$.
+We will see in Section~\ref{sec:main} that $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ plays an analogous role for general smooth commutative group schemes $G$.
 
@@
 \end{equation}
-Since $\pi_0(G)$ is a \'etale commutative group scheme -- and thus smooth --
-Lemma~\ref{lem:pullback} implies that \eqref{eq:pi0} defines the sequence of functors
+Since $\pi_0(G)$ is an \'etale commutative group scheme -- and thus smooth --
+Lemma~\ref{lem:pullback} implies that \eqref{eq:pi0} defines a sequence of functors
 \begin{equation}\label{eq:pi1}
@@
 \end{equation}
-and therefore, after passing to isomorphism classes, the sequence of abelian groups
+and therefore, after passing to isomorphism classes, a sequence of abelian groups
 \begin{equation}\label{eq:pi2}
@@
 \begin{proof}
-Let $\pi: B \to G^0$ be a discrete isogeny; set $A \ceq \ker \pi$.
+Let $\pi: B \to G^0$ be a discrete isogeny, and set $A \ceq \ker \pi$.
   We will find a discrete isogeny $f: H\to G$
@@
 
-We now wish to use the apply the results of Section~\ref{ssec:connected} to the identity component of $G$; to do so, we must know that the identity component of $G$ is actually an algebraic group over $\Fq$.
+We now wish to apply the results of Section~\ref{ssec:connected} to the identity component of $G$; to do so, we must know that the identity component of $G$ is actually an algebraic group over $\Fq$.
 
@@
  Since $G$ is a smooth group scheme over $\Fq$, its
- identity component $G^0$ of $G$ is a connected smooth,
+ identity component $G^0$ is a connected smooth,
  group scheme of finite type over $\Fq$, reduced over some finite extension of $\Fq$
@@
 For each $x\in \pi_0(\bG)$, set $\bG^x \ceq \pi_0^{-1}(x)$.
-The restriction $\pi_0^*\gqcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gqcs{L}_x)_{\bG^x}$ so the isomorphism $\brho_{\bG^x} : (\gqcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gqcs{L}_x \to (\EE)_x$.
+The restriction $\pi_0^*\gqcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gqcs{L}_x)_{\bG^x}$ so the isomorphism $\brho\vert_{\bG^x} : (\gqcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gqcs{L}_x \to (\EE)_x$.
 The collection $\{ \brho_x \tq x\in \pi_0(\bG) \}$ determines an isomorphism $\qcs{L} \to (\EE)_{\pi_0(G)}$  in $\QC(\pi_0(G))$.
@@
 \begin{remark}
-Although $\TrFrob{\pi_0(G)}$ is split and $\TrFrob{G^0}$ is an isomorphism, as examples show, it does not follow that $\TrFrob{G}$ is split. 
+Although $\TrFrob{\pi_0(G)}$ is split and $\TrFrob{G^0}$ is an isomorphism, it does not follow that $\TrFrob{G}$ is split. 
 \end{remark}
@@
 \end{align*}
-We can also interpret this operation on characters in terms of quasicharacter sheaves.
+We can also interpret this operation in terms of quasicharacter sheaves.
 
@@
 Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
-as taking the action $\varphi$ of the Weil group for $k$%, $\Weil{k}$, 
-on $\gqcs{L}$
-defined in Section~\ref{ssec:category} and restricting it to the Weil group for $k'$.
+as restricting the action $\varphi$ of $\Weil{k}$ on $\gqcs{L}$,
+defined in Section~\ref{ssec:category}, to $\Weil{k'}$.
 %, $\Weil{k'}$.
@@
 Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
-we may compute the value of $t_{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
+we may compute the value of $\TrFrob{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
 and the value of $\Nm^*(\TrFrob{G}(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
@@
 \[
-G' \hookrightarrow (\Res_{k'/k}G')_{k'}
+G' \hookrightarrow (\Res_{k'/k}G')_{k'},
 \]
@@
 \[
-(\Res_{k'/k}G')(k') \to G'(k')^*
+(\Res_{k'/k}G')(k')^* \to G'(k')^*
 \]
@@
 In this section we consider connected commutative algebraic groups over $K$ that admit a N\'eron model, by which we mean a locally finite type N\'eron model.
-By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected commutative algebraic groups over $K$ that contain no subgroup of type $\mathbb{G}_\text{a}$.
-These algebraic groups over $K$ form an additive category, denoted by $\mathcal{N}_K$ below, in a natural way, as a full subcategory of connected commutative algebraic groups over $K$.
-This category includes algebraic tori over $K$, abelian varieties over $K$ and unipotent $K$-wound groups.
+By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected commutative algebraic groups over $K$ that contain no subgroup isomorphic to $\mathbb{G}_\text{a}$.
+Write $\mathcal{N}_K$ for the full subcategory of the category of algebraic groups consisting of such objects.
+This category is additive, and includes all algebraic tori over $K$, abelian varieties over $K$ and unipotent $K$-wound groups.
 
@@
 Let $R$ be the ring of integers of $K$.
-Write $\m$ for the maximal ideal of $R$ and set $R_n = R/\m^{n+1}$, for every non-negative integer $n$.
-Suppose $X_K \in \mathcal{N}_K$ with N\'eron model $X$ over $R$.
+Write $\m$ for the maximal ideal of $R$ and set $R_n = R/\m^{n+1}$ for every non-negative integer $n$.
+Suppose $X_K \in \mathcal{N}_K$ has N\'eron model $X$ over $R$.
 Note that $X(K) = X(R)$.
-A {\it quasicharacter of $X(K)$} is a group homomorphism $X(K) \to \EEx$ that factors through $X(R) \to X(R_n)$, for some non-negative integer $n$;
-the group of quasicharacters of $X(K)$ will be denoted by 
+A \emph{quasicharacter of $X(K)$} is a group homomorphism $X(K) \to \EEx$ that factors through $X(R) \to X(R_n)$ for some non-negative integer $n$.
+The group of quasicharacters of $X(K)$ will be denoted by 
 \[
@@
 Let $K$, $R$ and $R_n$ be as above.
-We will need the Greenberg functor, which provides
-a functor from the category of schemes 
-over $R_n$, for each $n\in \NN$, to the category of schemes over $\Fq$.
-See \cite{bertrapelle-gonzales:Greenberg} for the definition and fundamental properties of the Greenberg functor as we use it; other important references include
+For each $n \in \NN$, the Greenberg functor maps schemes over $R_n$ to schemes over $\Fq$.
+See \cite{bertrapelle-gonzales:Greenberg} for the definition and fundamental properties of the Greenberg functor as we use it; other useful references include
 \cite{greenberg:61}, \cite{greenberg:63a},
 \cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1},
-\cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6},
+\cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} and
 \cite{nicaise-sebag:motivicSerre}*{\S 2.2}. %citelist
@@
 Crucially, $\varrho^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
-This observation is key to the proof that, for any scheme $X$ over $R$, the projective limit 
+This observation is key to the proof that, \todo{add reference to the Stacks project} for any scheme $X$ over $R$, the projective limit 
 \[
@@
 %
-The morphism of $\Fq$-schemes $\varrho^R_n(X) : \Gr_R(X) \to \Gr^R_n(N)$ induces a functor
+The morphism of $\Fq$-schemes $\varrho^R_n(X) : \Gr_R(X) \to \Gr^R_n(X)$ induces a functor
 \[
@@
 \item
-morphism $\varrho^R_n(X)^*\qcs{L} \to \varrho^R_m(X)^*\qcs{L}'$ in $\QC(X_K)$ are those morphisms in $\QC(\Gr_R(X))$ which take the form $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\qcs{L},\qcs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\qcs{L},\varrho^R_{m\leq n}(X)^*\qcs{L}')$ when $m\leq n$.
+morphisms $\varrho^R_n(X)^*\qcs{L} \to \varrho^R_m(X)^*\qcs{L}'$ in $\QC(X_K)$ are those morphisms in $\QC(\Gr_R(X))$ which take the form $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\qcs{L},\qcs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\qcs{L},\varrho^R_{m\leq n}(X)^*\qcs{L}')$ when $m\leq n$.
 \end{enumerate}
@@
 \item for all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
-\item for all quasicharacter sheaves $\qcs{F}$ on $\Gr_R(X)$ there is a canonical isomorphism
+\item for all quasicharacter sheaves $\qcs{F}$ for $X_K$, there is a canonical isomorphism
 \[
@@
 \begin{proof}
-For part (i), use Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$, the fact that N\'eron models are unique up to isomorphism, the fact that each $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(X_K)$ and the observation that $\QC(X_K)$ a `union' of the subcategories $\QC(\Gr^R_n(X))$ in $\QC(\Gr_R(X))$.
-For part (ii), use Theorem~\ref{thm:snake} with $G = \Gr^R_n(X)$ and then argue as in part (i).
-For part (iii), argue as in the proof of Lemma~\ref{lem:autornaught}.
-For part (iv), use Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, the fact that the component group of $\Gr^R_n(X)$ is independent of $n$ and then argue as in part (i).
+\begin{enumerate}
+\item Use Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$, the fact that N\'eron models are unique up to isomorphism, the fact that each $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(X_K)$ and the observation that $\QC(X_K)$ is a `union' of the subcategories $\QC(\Gr^R_n(X))$ in $\QC(\Gr_R(X))$.
+\item Use Theorem~\ref{thm:snake} with $G = \Gr^R_n(X)$ and then argue as in part (i).
+\item Argue as in the proof of Lemma~\ref{lem:autornaught}.
+\item Use Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, the fact that the component group of $\Gr^R_n(X)$ is independent of $n$ and then argue as in part (i).
+\end{enumerate}
 \end{proof}
@@
 \end{equation}
-where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T_K$.
-This provides good information above the category $\QC(T_K)$ of quasicharacters for $T_K$ and its relation to quasicharacters of $T(K)$.
+\todo{This is dual to Lemma 2.6, and isn't true in general.
+Is the fact that $X_*(T_K)$ is torsion-free sufficient?} where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T_K$.
 
@@
 Let $R$ and $R'$ be the rings of integers of $K$ and $K'$, respectively.
-Let $X_K$ be a connected commutative algebraic group over $K$
-that admits a N\'eron model $X$ over $R$.
-Set $X_{K'} \ceq X_K \times_\Spec{K} \Spec{K'}$
-Let $X'$ be a N\'eron model for $X_{K'}$.
+Let $X_K \in \mathcal{N}$ have N\'eron model $X$, set $X_{K'} \ceq X_K \times_\Spec{K} \Spec{K'}$
+and let $X'$ be a N\'eron model for $X_{K'}$.
 
@@
 \]
-Passing to limits now defines
+\todo{Is $X(K') = X'(K')$?} Passing to limits now defines
 \[ 
@@
 \]
-as smooth group schemes over $\Fq$; accordingly, by Lemma~\ref{lem:pullback} the isomorphism above determines an equivalence of categories
+as smooth group schemes over $\Fq$.  Accordingly, by Lemma~\ref{lem:pullback}, the isomorphism above determines an equivalence of categories
 \begin{equation}\label{eq:categorical_transfer}
@@
 \[
-T \times_{\Spec{\OK}} \Spec{\OK/\varpi_K^n\OK} \iso M \times_{\Spec{\OL}} \Spec{\OL/\varpi_L^n\OL}
+T \times_{\Spec{\OK}} \Spec{\OK/\varpi_K^m\OK} \iso M \times_{\Spec{\OL}} \Spec{\OL/\varpi_L^m\OL}
 \] 

### 2014-09-06 crelle-dictionary.tex
Changes to section 5.4 and 5.5.

@@
 over finite fields comes from an application to $p$-adic representation theory,
-specifically to quasicharacters of $p$-adic tori.
+specifically to quasicharacters of $p$-adic tori (\S\ref{sec:quasicharacters}).
 However, we found that our method of passing from $p$-adic tori to group schemes over $\Fq$ applies more generally to
@@
 where $\Hom_\text{qc}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
-We further show that automorphism groups in $\QC(T)$ are given, for every quasicharacter sheaf $\qcs{F}$ for $T_K$, by
-\[
-\Aut(\qcs{F}) \iso \Hh^1(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} = (\check{T}_\ell)^{\Weil{K}},
+We further show that automorphism groups in $\QC(T_K)$ are given, for every quasicharacter sheaf $\qcs{F}$ for $T_K$, by
+\[
+\Aut(\qcs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx),
 \]
@@
 
-\subsection{Quasicharacters}
+\subsection{Quasicharacters}\label{sec:quasicharacters}
 
@@
 As we explained in the Introduction, our original motivation for this paper was to find a geometrization and categorification of quasicharacters of $p$-adic tori. 
+ \todo{Is this the right place to recall/define the term quasicharacter?}
 This is is now provided by specializing Theorem~\ref{thm:QCXK} to the case when $X_K= T_K\in \mathcal{N}_K$ is an algebraic torus over $K$. 
-Now,
+Let $T$ be a Neron model for $T_K$.
+By \cite{bitan:discriminant}*{Eq 3.1}, the special fibre of the component group scheme for $T$ is given by
 \[
@@
 \]
-where $X_*(T_K)$ is the cocharacter lattice of $T_K$ and $\mathcal{I}_K$ is the inertia group for $K$ \cite{bitan:discriminant}*{Eq 3.1}. 
-Accordingly, the short exact sequence in Theorem~\ref{thm:QCXK} becomes
+where $X_*(T_K)$ is the cocharacter lattice of $T_K$ and $\mathcal{I}_K$ is the inertia group for $K$.
+Accordingly, by Theorem~\ref{thm:QCXK}, isomorphism classes in $\QC(T)$   becomes
 \begin{equation}
@@
 \begin{equation}
-\Aut(\qcs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx)  = (\check{T}_\ell)^{\Weil{K}}
+\Aut(\qcs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx).
 \end{equation}
-\todo{This is dual to Lemma 2.6, and isn't true in general.
-Is the fact that $X_*(T_K)$ is torsion-free sufficient?} where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T_K$.
+\todo{This is dual to Lemma 2.6, and isn't true in general.  Is the fact that $X_*(T_K)$ is torsion-free sufficient?} where $\Weil{K}$ is the Weil group for $K$.
+
+% and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T_K$.
 
@@
 \begin{tikzcd}[column sep=60]
-\Hom_{\text{qc}}(X(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{X(K)}} &\Hom_{\text{qc}}(X(K), \EEx).
+\Hom_{\text{qc}}(X_K(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{X(K)}} &\Hom_{\text{qc}}(X_K(K), \EEx).
 \end{tikzcd}
@@
 \]
+\[ 
+\Hom_{en-1}(X'(R'),\EEx) \to \Hom_{n-1}(X(R)),\EEx)
+\]
 Since $X'$ is a N\'eron model for $X_{K'}$ and $X$ is a N\'eron model for $X_K$,
@@
 \[ 
-\Hom_{en-1}(X(K'),\EEx) \to \Hom_{n-1}(X(K)),\EEx)
-\]
-\todo{Is $X(K') = X'(K')$?} Passing to limits now defines
-\[ 
-\Hom_\text{qc}(X(K'),\EEx) \to \Hom_\text{qc}(X(K)),\EEx)
+\Hom_{en-1}(X_{K'}(K'),\EEx)= \Hom_{en-1}(X_{K}(K'),\EEx) \to \Hom_{n-1}(X_K(K)),\EEx)
+\]
+Passing to limits now defines
+\[ 
+\Hom_\text{qc}(X_K(K'),\EEx) \to \Hom_\text{qc}(X_K(K)),\EEx)
 \]

### 2014-09-06 crelle-dictionary.tex
Changes sections heading.

@@
 
-%% \tableofcontents %% Just for papers exceeding 50 pages.
+ \tableofcontents %% Just for papers exceeding 50 pages.
 
@@
 
-\subsection{The category of quasicharacter sheaves}\label{ssec:category}
+\subsection{Quasicharacter sheaves}\label{ssec:category}
 
@@
 \end{enumerate}
-\todo{add more connecting prose}
 \end{proposition}
@@
 
-\subsection{Objects, when $G$ is etale}\label{ssec:SandT}
+\subsection{Objects in the \'etale case}\label{ssec:SandT}
 
@@
 
-\subsection{Morphisms}\label{ssec:mor-etale}
+\subsection{Morphisms in the \'etale case}\label{ssec:mor-etale}
 
@@
 
-\section{Quasicharacter sheaves defined by discrete isogenies} \label{sec:disc-isog}
+\section{Quasicharacter sheaves on connected commutative algebraic groups} \label{sec:disc-isog}
 
@@
 
-\subsection{Quasicharacter sheaves on connected commutative algebraic groups}\label{ssec:connected}
+\subsection{The classical function--sheaf dictionary revisited}\label{ssec:connected}
 
@@
 
-\subsection{Quasicharacters for $p$-adic tori} \label{ssec:qc_tori}
+\subsection{Quasicharacter sheaves for $p$-adic tori} \label{ssec:qc_tori}
 
 As we explained in the Introduction, our original motivation for this paper was to find a geometrization and categorification of quasicharacters of $p$-adic tori. 
- \todo{Is this the right place to recall/define the term quasicharacter?}
 This is is now provided by specializing Theorem~\ref{thm:QCXK} to the case when $X_K= T_K\in \mathcal{N}_K$ is an algebraic torus over $K$. 
@@
 \end{equation}
-\todo{This is dual to Lemma 2.6, and isn't true in general.  Is the fact that $X_*(T_K)$ is torsion-free sufficient?} where $\Weil{K}$ is the Weil group for $K$.
+%\todo{This is dual to Lemma 2.6, and isn't true in general.  Is the fact that $X_*(T_K)$ is torsion-free sufficient?} where $\Weil{K}$ is the Weil group for $K$.
 
@@
 
-\subsection{Weil restriction and quasicharacters}\label{ssec:wrK}
+\subsection{Weil restriction and quasicharacter sheaves}\label{ssec:wrK}
 
@@
 it follows from Lemma~\ref{lem:pullback} that the pullback functor \eqref{men-pulled} actually induces
-\[
-\Hom(X'(R'_{en-1}),\EEx)  \to  \Hom(X(R_{n-1}),\EEx) .
-\]
+%\[
+%\Hom(X'(R'_{en-1}),\EEx)  \to  \Hom(X(R_{n-1}),\EEx) .
+%\]
 \[ 
@@
 Since $X'$ is a N\'eron model for $X_{K'}$ and $X$ is a N\'eron model for $X_K$,
- this may be re-written as
+ this may be re-written as \todo{I'm going to think about this a bit more.}
 \[ 

### 2014-09-07 crelle-dictionary.tex
Put dual torus back in. References to Tate, Stacks needed.

@@
 
- \tableofcontents %% Just for papers exceeding 50 pages.
+%% \tableofcontents %% Just for papers exceeding 50 pages.
 
@@
 \[
-\Aut(\qcs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx),
+\Aut(\qcs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
 \]
@@
 
-\subsection{The classical function--sheaf dictionary revisited}\label{ssec:connected}
+\subsection{The classical function-sheaf dictionary revisited}\label{ssec:connected}
 
@@
 A \emph{quasicharacter of $X(K)$} is a group homomorphism $X(K) \to \EEx$ that factors through $X(R) \to X(R_n)$ for some non-negative integer $n$.
+We note that this use of the term is compatible with the use of the term {\it quasicharacter} in \cite{Cassels-Frohlich:ANT}*{Ch XV, \S 2.3}.
+ \todo{add bibliography entry for Tate's thesis}
 The group of quasicharacters of $X(K)$ will be denoted by 
@@
 Crucially, $\varrho^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
-This observation is key to the proof that, \todo{add reference to the Stacks project} for any scheme $X$ over $R$, the projective limit 
+This observation is key to the proof that, for any scheme $X$ over $R$, the projective limit 
 \[
@@
 taken with respect to the surjective morphisms $\varrho^R_{n\leq m}(X) : \Gr^R_{m}(X) \to \Gr^R_n(X)$,
-exists in the category of group schemes over $\Fq$.
+exists in the category of group schemes over $\Fq$;
+see \cite{stacks_project:limits}*{Lem 2.2}.
+\todo{add bibliography entry for the Stacks project}
 This leads to the definition of what we shall call the {\it Greenberg transform}:
@@
 where $X_*(T_K)$ is the cocharacter lattice of $T_K$ and $\mathcal{I}_K$ is the inertia group for $K$.
-Accordingly, by Theorem~\ref{thm:QCXK}, isomorphism classes in $\QC(T)$   becomes
-\begin{equation}
+Accordingly, by Theorem~\ref{thm:QCXK}, isomorphism classes of quasicharacter sheaves for $T_K$ determine quasicharacter sheaves according to the exact sequence
+\[
 0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{T_K} \to \Hom_\text{qc}(T(K),\EEx) \to 0.
-\end{equation}
-Again by Theorem~\ref{thm:QCXK}, the automorphism groups in $\QC(T_K)$ are given, for every quasicharacter sheaf $\qcs{F}$ for $T_K$, by
-\begin{equation}
-\Aut(\qcs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx).
-\end{equation}
-%\todo{This is dual to Lemma 2.6, and isn't true in general.  Is the fact that $X_*(T_K)$ is torsion-free sufficient?} where $\Weil{K}$ is the Weil group for $K$.
-
-% and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T_K$.
+\]
+Also by Theorem~\ref{thm:QCXK} and \cite{bitan:discriminant}*{Eq 3.1}, the automorphism group of every $\qcs{F} \in \QC(T_K)$ is given by 
+\[
+\Aut(\qcs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx),
+\]
+where $\Weil{K}$ is the Weil group for $K$. 
+Since 
+\[
+\Hom(X_*(T_K)_{\Weil{K}},\EEx) \iso \Hom(X_*(T_K),\EEx)^{\Weil{K}}
+\]
+it follows that the automorphism group of every quasicharacter sheaf for $T_K$ is $(\check{T}_\ell)^{\Weil{K}}$, where $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
 
@@
 Since $X'$ is a N\'eron model for $X_{K'}$ and $X$ is a N\'eron model for $X_K$,
- this may be re-written as \todo{I'm going to think about this a bit more.}
+ this may be re-written as
  \[ 

### 2014-09-07 crelle-dictionary.tex
Fixed references to Tate's thesis, stacks project.

@@
 A \emph{quasicharacter of $X(K)$} is a group homomorphism $X(K) \to \EEx$ that factors through $X(R) \to X(R_n)$ for some non-negative integer $n$.
-We note that this use of the term is compatible with the use of the term {\it quasicharacter} in \cite{Cassels-Frohlich:ANT}*{Ch XV, \S 2.3}.
- \todo{add bibliography entry for Tate's thesis}
+We note that this use of the term is compatible with the use of the term {\it quasicharacter} in \cite{cassels-frohlich:AlgebraicNumberTheory}*{Ch XV, \S 2.3}.
 The group of quasicharacters of $X(K)$ will be denoted by 
@@
 exists in the category of group schemes over $\Fq$;
-see \cite{stacks_project:limits}*{Lem 2.2}.
-\todo{add bibliography entry for the Stacks project}
+see \cite{stacks-project}*{Limits of Schemes, Lem 2.2}.
 This leads to the definition of what we shall call the {\it Greenberg transform}:

### 2014-09-07 crelle-dictionary.tex
Change to Introduction and Acknowledgements
In the Introduction, I moved the internal reference and the tag to the
section on quasicharacters in an attempt to match your style, and also
inserted the word commutative, where is was needed (line 317).
In the Acknowledgements, I replaced the reference to BIRS with Banff
International Research Station, since some readers may not know what
BIRS stands for.

@@
 over finite fields comes from an application to $p$-adic representation theory,
-specifically to quasicharacters of $p$-adic tori (\S\ref{sec:quasicharacters}).
+specifically to quasicharacters (\S\ref{ssec:quasicharacters}) of $p$-adic tori.
 However, we found that our method of passing from $p$-adic tori to group schemes over $\Fq$ applies more generally to
-any local field $K$ with finite residue field $\Fq$ and any algebraic group $X_K$ that admits a N\'eron model $X$. % over $R$, the ring of integers of $K$.
+any local field $K$ with finite residue field $\Fq$ and any commutative algebraic group $X_K$ that admits a N\'eron model $X$. % over $R$, the ring of integers of $K$.
 This class of groups includes abelian varieties and unipotent $K$-wound groups in addition to the tori we initially considered.
@@
 
-\subsection{Quasicharacters}\label{sec:quasicharacters}
+\subsection{Quasicharacters}\label{ssec:quasicharacters}
 
@@
 \acknowl{We thank Masoud Kamgarpour, Pramod Achar and Hadi Salmasian
-for allowing us to hijack much of our Research in Teams meeting at BIRS into a discussion of
+for allowing us to hijack much of our Research in Teams meeting at the Banff International Research Station into a discussion of
 quasicharacter sheaves; their knowledge and help have been invaluable.

### 2014-09-08 crelle-dictionary.tex
Hardwired bibliography, with Crelle sample

@@
 \usepackage{amsrefs}
+\BibSpec{lecture}{%
+  +{}{\PrintAuthors} {author}
+  +{,}{ \textit} {title}
+  +{}{ \parenthesize} {date}
+  +{,}{ } {note}
+  +{,}{ } {location}
+  +{.}{ } {transition}
+}
+\BibSpec{preprint}{%
+  +{}{\PrintAuthors} {author}
+  +{,}{ \textit} {title}
+  +{,}{ preprint } {date}
+  +{,}{ } {note}
+  +{.}{ } {transition}
+}
 % Fonts
@@
 \DeclareMathOperator{\Irrep}{Irrep}
-\DeclareMathOperator{\Pic}{Pic}
+%\DeclareMathOperator{\Pic}{Pic}
 \DeclareMathOperator{\id}{id}
@@
 %% amsmath replacements for \atop
-\newcommand{\latop}[2]{\genfrac{}{}{0pt}{0}{#1}{#2}}
-\newcommand{\partop}[2]{\genfrac{(}{)}{0pt}{0}{#1}{#2}}
+%\newcommand{\latop}[2]{\genfrac{}{}{0pt}{0}{#1}{#2}}
+%\newcommand{\partop}[2]{\genfrac{(}{)}{0pt}{0}{#1}{#2}}
 %% Labeled items
@@
 %% Margin notes
-\newcommand\Clifton[1]{\marginpar{\smaller\smaller CC: #1}}
-\newcommand\David[1]{\marginpar{\smaller\smaller DR: #1}}
+%\newcommand\Clifton[1]{\marginpar{\smaller\smaller CC: #1}}
+%\newcommand\David[1]{\marginpar{\smaller\smaller DR: #1}}
 %% Hyphenation override
@@
 
-Let $K$ be a local field with finite residue field $\Fq$. 
+Let $K$ be a local field with finite residue field $\Fq$;
+ we continue to assume that $\ell$ is invertible in $\Fq$.
 In this section we consider connected commutative algebraic groups over $K$ that admit a N\'eron model, by which we mean a locally finite type N\'eron model.
@@
 \begin{theorem}\label{thm:QCXK}
-Let $K$ and $R$ be as above. 
+Let $K$ be a local field with residue field $\Fq$, in which $\ell$ is invertible; 
+let $R$ be the ring of integers of $K$.
 \begin{enumerate}
@@
 %\bibliographystyle{amsalpha}
-\bibliography{../bibliography/Biblio}
+%\bibliography{../bibliography/Biblio}
+
+\begin{bibdiv}
+\begin{biblist}
+%\bibselect{references}
+
+\bib{beilinson-bernstein-deligne:81a}{article}{
+   author={\it A. A. Be{\u\i}linson},
+   author={\it J. Bernstein},
+   author={\it P. Deligne},
+   title={\rm Faisceaux pervers},
+   journal ={Ast\'erisque},
+   volume={100},
+   publisher={Soc. Math. France},
+   place={Paris},
+   date={1982},
+   pages={5--171},
+%conference={
+%      title={Analyse et topologie sur les espaces singuliers, I},
+%      address={Luminy},
+%      date={1981},
+%   }
+}
+
+\bib{bernstein:vogan_conference}{lecture}{
+	author = {\it J. Bernstein},
+	title = {\rm Stacks in Representation Theory: What is a representation of an algebraic group?},
+ note={Lecture delivered at {\it A conference dedicated to David Vogan on his 60th birthday: Representations of reductive groups}, \url{http://math.mit.edu/conferences/Vogan/}},
+ 	date={May, 2014},
+ 	location={MIT, Boston},
+ }
+
+ \bib{bernstein-luntz:equivariant_sheaves}{book}{
+      author={\it J. Bernstein},
+      author={\it V. Luntz},
+       title={\rm Equivariant sheaves and functors},
+      series={Lecture Notes in Mathematics},
+   publisher={Springer-Verlag},
+     address={Berlin},
+        date={1994},
+      volume={1578},
+}
+
+\bib{bertrapelle-gonzales:Greenberg}{preprint}{
+      author={\it A. Bertrapelle},
+      author={\it C.-D. Gonz\'ales-Avil\'es},
+       title={\rm The Greenberg functor revisited},
+        note={\url{arXiv:1311.0051v1}},
+      date={2013},
+}
+
+\bib{bitan:discriminant}{article}{
+      author={\it R. A. Bitan},
+       title={\rm The discriminant of an algebraic torus},
+        date={2011},
+     journal={J. Number Theory},
+      volume={131},
+      number={9},
+       pages={1657\ndash 1671},
+}
+
+\bib{bosch-lutkebohmert-reynaud:NeronModels}{book}{
+      author={\it S. Bosch},
+      author={\it W. L\"utkebohmert},
+      author={\it M. Reynaud},
+       title={\rm N\'eron models},
+   publisher={Springer-Verlag},
+     address={Berlin},
+        date={1980},
+}
+
+\bib{brown:CohomologyGrps}{book}{
+      author={\it K. S. Brown},
+       title={\rm Cohomology of groups},
+      series={Graduate Texts in Mathematics 87},
+   publisher={{Springer-Verlag}},
+     address={New York},
+        date={1982},
+}
+
+\bib{cartan-eilenberg:HomologicalAlgebra}{book}{
+      author={\it H. Cartan},
+      author={\it S. Eilenberg},
+       title={\rm Homological algebra},
+   publisher={Princeton U.P.},
+     address={Princeton},
+        date={1956},
+}
+
+\bib{cassels-frohlich:AlgebraicNumberTheory}{book}{
+      editor={\it J. W. S. Cassels},
+      editor={\it A. Frohlich},
+       title={\rm Algebraic number theory},
+     edition={2nd ed.,},
+   publisher={London Math Society},
+     address={London},
+        date={2010},
+}
+
+\bib{chai-yu:01a}{article}{
+      author={\it C.-L. Chai},
+      author={\it J.-K. Yu},
+       title={\rm Congruences of N\'eron models for tori and the Artin
+  conductor},
+        date={2001},
+     journal={Annals of Math},
+      volume={154},
+      number={2},
+       pages={347\ndash 382},
+}
+
+\bib{deligne:SGA4.5}{book}{
+      author={\it P. Deligne},
+       title={\rm Cohomologie \'Etale},
+      series={{Lecture Notes in Mathematics 569}},
+   publisher={{Springer-Verlag}},
+     address={Berlin},
+        date={1977},
+}
+
+\bib{deligne:80a}{article}{
+      author={\it P. Deligne},
+       title={\rm La conjecture de Weil II},
+        date={1980},
+     journal={{Inst. Hautes \'Etudes Sci. Publ. Math.}},
+      volume={52},
+       pages={137\ndash 252},
+}
+
+\bib{deligne:02a}{article}{
+      author={\it P. Deligne},
+       title={\rm {Cat\'egories tensorielles}},
+        date={2002},
+     journal={{Mosc. Math. J.}},
+      volume={2},
+      number={2},
+       pages={227\ndash 248},
+}
+
+\bib{deligne-katz:SGA7.2}{book}{
+      author={\it P. Deligne},
+      author={\it N. Katz},
+       title={\rm {Groupes de monodromie en g\'eom\'etrie alg\'ebrique. II}},
+      series={{Lecture Notes in Mathematics}},
+   publisher={{Springer-Verlag}},
+     address={Berlin},
+        date={1973},
+      volume={340},
+}
+
+\bib{demazure-gabriel:GroupesAlgebriques}{book}{
+      author={\it M. Demazure},
+      author={\it P. Gabriel},
+       title={\rm {Groupes alg\'ebriques. Tome 1: G\'eom\'etrie alg\'ebrique,
+  g\'en\'eralit\'es, groupes commutatifs}},
+   publisher={{Masson \& Cie}},
+     address={Paris},
+        date={1970},
+        note={(Appendix: {\it M. Hazewinkel}, Corps de classes local)},
+}
+
+\bib{etingof:09a}{unpublished}{
+      author={\it P. Etingof},
+      author={\it S. Gelaki},
+      author={\it D. Nikshych},
+      author={\it V. Ostrik},
+       title={\rm Tensor categories},
+        date={2009},
+        note={{Lecture notes for MIT's 18.769}, \url{www-math.mit.edu/~etingof/tenscat.pdf}},
+}
+
+\bib{vdGeer-Moonen:AbelianVarieties}{preprint}{
+      author={\it G. van der Geer},
+      author={\it B. Moonen},
+       title={\rm {Abelian varieties}},
+        date={2013},
+       note={\url{http://staff.science.uva.nl/~bmoonen/boek/BookAV.html}},
+%        note={Writing in progress.},
+}
+
+\bib{greenberg:61}{article}{
+      author={\it M. J. Greenberg},
+       title={\rm {Schemata over local rings I}},
+        date={1961},
+     journal={Annals of Math},
+      volume={73},
+      number={2},
+       pages={624\ndash 648},
+}
+
+\bib{greenberg:63a}{article}{
+      author={\it M. J. Greenberg},
+       title={\rm {Schemata over local rings II}},
+        date={1963},
+     journal={Annals of Math},
+      volume={78},
+      number={2},
+       pages={256\ndash 266},
+}
+
+\bib{EGAIV2}{article}{
+      author={\it A. Grothendieck},
+       title={\rm {\'El\'ements de g\'eom\'etrie alg\'ebrique. IV. \'Etude locale
+  des sch\'emas et des morphismes de sch\'emas. II}},
+        date={1965},
+     journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
+      number={24},
+}
+
+\bib{SGA5}{book}{
+      author={\it A. Grothendieck},
+       title={\rm {S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois Marie 1965--66
+  SGA5: Cohomologie $\ell$-adique et Fonctions L}},
+      series={{Lecture Notes in Mathematics}},
+   publisher={{Springer-Verlag}},
+        date={1977},
+      volume={589},
+}
+
+\bib{kamgarpour:09a}{article}{
+      author={\it M. Kamgarpour},
+       title={\rm {Stacky abelianization of algebraic groups}},
+        date={2009},
+     journal={{Transform. Groups}},
+      volume={14},
+      number={4},
+       pages={825\ndash 846},
+}
+
+\bib{lang:56a}{article}{
+      author={\it S. Lang},
+       title={\rm{Algebraic groups over finite fields}},
+        date={1956},
+     journal={Amer. J. Math.},
+      volume={78},
+       pages={555\ndash 563},
+}
+
+\bib{laumon:87a}{article}{
+      author={\it G. Laumon},
+       title={\rm{Transformation de Fourier, constantes d'\'equations
+  fonctionnelles et conjecture de Weil}},
+        date={1987},
+     journal={{Inst. Hautes \'Etudes Sci. Publ. Math.}},
+      volume={65},
+       pages={131\ndash 210},
+}
+
+\bib{lusztig:85a}{article}{
+      author={\it G. Lusztig},
+       title={\rm {Character Sheaves, I}},
+        date={1985},
+     journal={Advances in Math.},
+      volume={56},
+       pages={193\ndash 237},
+}
+
+\bib{lusztig:disconnected1}{article}{
+      author={\it G. Lusztig},
+       title={\rm {Character sheaves on disconnected groups. I}},
+        date={2003},
+     journal={Representation Theory},
+      volume={7},
+       pages={374\ndash 403},
+}
+
+\bib{nicaise-sebag:motivicSerre}{article}{
+      author={\it J. Sebag},
+      author={\it N. Nicaise},
+       title={\rm{Motivic Serre invariants and Weil restriction}},
+        date={2008},
+     journal={J. Algebra},
+      volume={319},
+      number={4},
+       pages={1585\ndash 1610},
+}
+
+\bib{stacks-project}{misc}{
+      author={\it {The {Stacks Project Authors}}},
+       title={\rm {Stacks Project}},
+        date={2013},
+        note={\url{http://stacks.math.columbia.edu}},
+}
+
+\bib{Vakil:spectral_sequences}{unpublished}{
+      author={\it R. Vakil},
+       title={\rm{Spectral sequences: friend or foe?}},
+        date={2008},
+        note={\url{http://math.stanford.edu/~vakil/0708-216/216ss.pdf}},
+}
+
+\bib{vogan:93a}{article}{
+      author={\it D. Vogan},
+       title={\rm {The local Langlands conjecture}},
+        date={1993},
+     journal={Representation Theory of Groups and Algebras},
+      volume={145},
+}
+
+\bib{Weibel:Homological_Algebra}{book}{
+      author={\it C. A. Weibel},
+       title={\rm{An introduction to homological algebra}},
+      series={Cambridge Studies in Advanced Mathematics},
+   publisher={Cambridge Univ. Press},
+     address={Cambridge},
+        date={1994},
+      volume={38},
+}
+
+\end{biblist}
+\end{bibdiv}
+
+\begin{thebibliography}{9}
+
+\bibitem{article}
+\textit{T.~Angel} and \textit{I.~E.~Shparlinski},
+Article in a journal, J. reine angew. Math. \textbf{647} (2010), 123--156.
+
+\bibitem{preprint}
+\textit{C.~Bonnaf\'e},
+Preprint, preprint 2008, \url{http://arxiv.org/abs/0805.4100}.
+
+\bibitem{proceedings}
+\textit{P. Brooksbank},
+Article in a conference proceedings,
+in: Finite geometries (Pingree Park 2004), Oxford University Press, Oxford (2006), 1--16.
+
+\bibitem{phdthesis}
+\textit{J.~D.~King},
+Unpublished dissertation,
+Ph.D. thesis, University of Cambridge, 1995.
+
+\bibitem{book}
+\textit{F. Sukochev}, \textit{S. Lord} and \textit{D. Zanin},
+Book, 2nd ed., De Gruyter, Berlin 2012.
+
+\end{thebibliography}
 

### 2014-09-08 crelle-dictionary.tex
Fixed the Vogan bibliography entry.
Replaced reference to Stacks Project with EGAIV3

@@
 
-\contact{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive, T2N 1N4, Calgary, Canada}{cunning@math.ucalgary.ca}
-\contact{Pacific Institute for the Mathematical Sciences, University of Calgary, 2500 University Drive, T2N 1N4, Calgary, Canada}{roed.math@gmail.com}
+\contact{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive, {T2N~1N4}, Calgary, Canada}{cunning@math.ucalgary.ca}
+\contact{Pacific Institute for the Mathematical Sciences, University of Calgary, 2500 University Drive, {T2N~1N4}, Calgary, Canada}{roed.math@gmail.com}
 
@@
 exists in the category of group schemes over $\Fq$;
-see \cite{stacks-project}*{Limits of Schemes, Lem 2.2}.
+see \cite{EGAIV3}*{\S 8.2}.
 This leads to the definition of what we shall call the {\it Greenberg transform}:
@@
 
+\bib{EGAIV3}{article}{
+   author={\it A. Grothendieck},
+   title={\rm{\'El\'ements de g\'eom\'etrie alg\'ebrique. IV. \'Etude locale des
+   sch\'emas et des morphismes de sch\'emas. III}},
+   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
+   number={28},
+   date={1966},
+}
+
 \bib{SGA5}{book}{
@@
 
-\bib{stacks-project}{misc}{
-      author={\it {The {Stacks Project Authors}}},
-       title={\rm {Stacks Project}},
-        date={2013},
-        note={\url{http://stacks.math.columbia.edu}},
-}
-
 \bib{Vakil:spectral_sequences}{unpublished}{
@@
 \bib{vogan:93a}{article}{
-      author={\it D. Vogan},
-       title={\rm {The local Langlands conjecture}},
+   author={\it D. A. Vogan},
+   title={\rm{The local Langlands conjecture}},
+ %  conference={
+ %     title={Representation theory of groups and algebras},
+  % },
+   journal ={Contemp. Math.},
+    volume={145},
+   publisher={Amer. Math. Soc.},
+   place={Providence, RI},
    date={1993},
-     journal={Representation Theory of Groups and Algebras},
-      volume={145},
+   pages={305--379},
 }

### 2014-09-08 crelle-dictionary.tex
References
Fixed reference to EGA IV 3.
Fixed several hyperlinks in the bibliography so that they go directly
to the promised document.

@@
 exists in the category of group schemes over $\Fq$;
-see \cite{EGAIV3}*{\S 8.2}.
+see \cite{EGAIV3}*{\S 8.13}.
 This leads to the definition of what we shall call the {\it Greenberg transform}:
@@
 	title = {\rm Stacks in Representation Theory: What is a representation of an algebraic group?},
- note={Lecture delivered at {\it A conference dedicated to David Vogan on his 60th birthday: Representations of reductive groups}, \url{http://math.mit.edu/conferences/Vogan/}},
+ note={Lecture delivered at {\it A conference dedicated to David Vogan on his 60th birthday: Representations of reductive groups}}, 
+ %\url{http://math.mit.edu/conferences/Vogan/}},
  	date={May, 2014},
@@
        title={\rm The Greenberg functor revisited},
-        note={\url{arXiv:1311.0051v1}},
+        note={\url{http://arxiv.org/abs/1311.0051}},
       date={2013},
@@
         date={2009},
-        note={{Lecture notes for MIT's 18.769}, \url{www-math.mit.edu/~etingof/tenscat.pdf}},
+        note={{Lecture notes for MIT's 18.769}, available at \url{http://www-math.mit.edu/~etingof/tenscat.pdf}},
 }
@@
         date={2013},
-       note={\url{http://staff.science.uva.nl/~bmoonen/boek/BookAV.html}},
+       note={available at \url{http://staff.science.uva.nl/~bmoonen/boek/BookAV.html}},
 %        note={Writing in progress.},
@@
         date={2008},
-        note={\url{http://math.stanford.edu/~vakil/0708-216/216ss.pdf}},
+        note={Notes for 216: Foundations of Algebraic Geometry, available at \url{http://math.stanford.edu/~vakil/0708-216/216ss.pdf}},
 }

### 2014-09-08 crelle-dictionary.tex
Merge branch 'master' of github.com:CliftonCunningham/geometrization-tori

--- 2014-09-08 crelle-dictionary.tex
@@
 \usepackage{amsrefs}
-\BibSpec{lecture}{%
-  +{}{\PrintAuthors} {author}
-  +{,}{ \textit} {title}
-  +{}{ \parenthesize} {date}
-  +{,}{ } {note}
-  +{,}{ } {location}
-  +{.}{ } {transition}
-}
-\BibSpec{preprint}{%
-  +{}{\PrintAuthors} {author}
-  +{,}{ \textit} {title}
-  +{,}{ preprint } {date}
-  +{,}{ } {note}
-  +{.}{ } {transition}
-}
 % Fonts
@@
 \DeclareMathOperator{\Irrep}{Irrep}
-%\DeclareMathOperator{\Pic}{Pic}
+\DeclareMathOperator{\Pic}{Pic}
 \DeclareMathOperator{\id}{id}
@@
 %% amsmath replacements for \atop
-%\newcommand{\latop}[2]{\genfrac{}{}{0pt}{0}{#1}{#2}}
-%\newcommand{\partop}[2]{\genfrac{(}{)}{0pt}{0}{#1}{#2}}
+\newcommand{\latop}[2]{\genfrac{}{}{0pt}{0}{#1}{#2}}
+\newcommand{\partop}[2]{\genfrac{(}{)}{0pt}{0}{#1}{#2}}
 %% Labeled items
@@
 %% Margin notes
-%\newcommand\Clifton[1]{\marginpar{\smaller\smaller CC: #1}}
-%\newcommand\David[1]{\marginpar{\smaller\smaller DR: #1}}
+\newcommand\Clifton[1]{\marginpar{\smaller\smaller CC: #1}}
+\newcommand\David[1]{\marginpar{\smaller\smaller DR: #1}}
 %% Hyphenation override
@@
 %\bibliographystyle{amsalpha}
-%\bibliography{../bibliography/Biblio}
-
-\begin{bibdiv}
-\begin{biblist}
-%\bibselect{references}
-
-\bib{beilinson-bernstein-deligne:81a}{article}{
-   author={\it A. A. Be{\u\i}linson},
-   author={\it J. Bernstein},
-   author={\it P. Deligne},
-   title={\rm Faisceaux pervers},
-   journal ={Ast\'erisque},
-   volume={100},
-   publisher={Soc. Math. France},
-   place={Paris},
-   date={1982},
-   pages={5--171},
-%conference={
-%      title={Analyse et topologie sur les espaces singuliers, I},
-%      address={Luminy},
-%      date={1981},
-%   }
-}
-
-\bib{bernstein:vogan_conference}{lecture}{
-	author = {\it J. Bernstein},
-	title = {\rm Stacks in Representation Theory: What is a representation of an algebraic group?},
- note={Lecture delivered at {\it A conference dedicated to David Vogan on his 60th birthday: Representations of reductive groups}, \url{http://math.mit.edu/conferences/Vogan/}},
- 	date={May, 2014},
- 	location={MIT, Boston},
- }
-
- \bib{bernstein-luntz:equivariant_sheaves}{book}{
-      author={\it J. Bernstein},
-      author={\it V. Luntz},
-       title={\rm Equivariant sheaves and functors},
-      series={Lecture Notes in Mathematics},
-   publisher={Springer-Verlag},
-     address={Berlin},
-        date={1994},
-      volume={1578},
-}
-
-\bib{bertrapelle-gonzales:Greenberg}{preprint}{
-      author={\it A. Bertrapelle},
-      author={\it C.-D. Gonz\'ales-Avil\'es},
-       title={\rm The Greenberg functor revisited},
-        note={\url{arXiv:1311.0051v1}},
-      date={2013},
-}
-
-\bib{bitan:discriminant}{article}{
-      author={\it R. A. Bitan},
-       title={\rm The discriminant of an algebraic torus},
-        date={2011},
-     journal={J. Number Theory},
-      volume={131},
-      number={9},
-       pages={1657\ndash 1671},
-}
-
-\bib{bosch-lutkebohmert-reynaud:NeronModels}{book}{
-      author={\it S. Bosch},
-      author={\it W. L\"utkebohmert},
-      author={\it M. Reynaud},
-       title={\rm N\'eron models},
-   publisher={Springer-Verlag},
-     address={Berlin},
-        date={1980},
-}
-
-\bib{brown:CohomologyGrps}{book}{
-      author={\it K. S. Brown},
-       title={\rm Cohomology of groups},
-      series={Graduate Texts in Mathematics 87},
-   publisher={{Springer-Verlag}},
-     address={New York},
-        date={1982},
-}
-
-\bib{cartan-eilenberg:HomologicalAlgebra}{book}{
-      author={\it H. Cartan},
-      author={\it S. Eilenberg},
-       title={\rm Homological algebra},
-   publisher={Princeton U.P.},
-     address={Princeton},
-        date={1956},
-}
-
-\bib{cassels-frohlich:AlgebraicNumberTheory}{book}{
-      editor={\it J. W. S. Cassels},
-      editor={\it A. Frohlich},
-       title={\rm Algebraic number theory},
-     edition={2nd ed.,},
-   publisher={London Math Society},
-     address={London},
-        date={2010},
-}
-
-\bib{chai-yu:01a}{article}{
-      author={\it C.-L. Chai},
-      author={\it J.-K. Yu},
-       title={\rm Congruences of N\'eron models for tori and the Artin
-  conductor},
-        date={2001},
-     journal={Annals of Math},
-      volume={154},
-      number={2},
-       pages={347\ndash 382},
-}
-
-\bib{deligne:SGA4.5}{book}{
-      author={\it P. Deligne},
-       title={\rm Cohomologie \'Etale},
-      series={{Lecture Notes in Mathematics 569}},
-   publisher={{Springer-Verlag}},
-     address={Berlin},
-        date={1977},
-}
-
-\bib{deligne:80a}{article}{
-      author={\it P. Deligne},
-       title={\rm La conjecture de Weil II},
-        date={1980},
-     journal={{Inst. Hautes \'Etudes Sci. Publ. Math.}},
-      volume={52},
-       pages={137\ndash 252},
-}
-
-\bib{deligne:02a}{article}{
-      author={\it P. Deligne},
-       title={\rm {Cat\'egories tensorielles}},
-        date={2002},
-     journal={{Mosc. Math. J.}},
-      volume={2},
-      number={2},
-       pages={227\ndash 248},
-}
-
-\bib{deligne-katz:SGA7.2}{book}{
-      author={\it P. Deligne},
-      author={\it N. Katz},
-       title={\rm {Groupes de monodromie en g\'eom\'etrie alg\'ebrique. II}},
-      series={{Lecture Notes in Mathematics}},
-   publisher={{Springer-Verlag}},
-     address={Berlin},
-        date={1973},
-      volume={340},
-}
-
-\bib{demazure-gabriel:GroupesAlgebriques}{book}{
-      author={\it M. Demazure},
-      author={\it P. Gabriel},
-       title={\rm {Groupes alg\'ebriques. Tome 1: G\'eom\'etrie alg\'ebrique,
-  g\'en\'eralit\'es, groupes commutatifs}},
-   publisher={{Masson \& Cie}},
-     address={Paris},
-        date={1970},
-        note={(Appendix: {\it M. Hazewinkel}, Corps de classes local)},
-}
-
-\bib{etingof:09a}{unpublished}{
-      author={\it P. Etingof},
-      author={\it S. Gelaki},
-      author={\it D. Nikshych},
-      author={\it V. Ostrik},
-       title={\rm Tensor categories},
-        date={2009},
-        note={{Lecture notes for MIT's 18.769}, \url{www-math.mit.edu/~etingof/tenscat.pdf}},
-}
-
-\bib{vdGeer-Moonen:AbelianVarieties}{preprint}{
-      author={\it G. van der Geer},
-      author={\it B. Moonen},
-       title={\rm {Abelian varieties}},
-        date={2013},
-       note={\url{http://staff.science.uva.nl/~bmoonen/boek/BookAV.html}},
-%        note={Writing in progress.},
-}
-
-\bib{greenberg:61}{article}{
-      author={\it M. J. Greenberg},
-       title={\rm {Schemata over local rings I}},
-        date={1961},
-     journal={Annals of Math},
-      volume={73},
-      number={2},
-       pages={624\ndash 648},
-}
-
-\bib{greenberg:63a}{article}{
-      author={\it M. J. Greenberg},
-       title={\rm {Schemata over local rings II}},
-        date={1963},
-     journal={Annals of Math},
-      volume={78},
-      number={2},
-       pages={256\ndash 266},
-}
-
-\bib{EGAIV2}{article}{
-      author={\it A. Grothendieck},
-       title={\rm {\'El\'ements de g\'eom\'etrie alg\'ebrique. IV. \'Etude locale
-  des sch\'emas et des morphismes de sch\'emas. II}},
-        date={1965},
-     journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
-      number={24},
-}
-
-\bib{SGA5}{book}{
-      author={\it A. Grothendieck},
-       title={\rm {S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois Marie 1965--66
-  SGA5: Cohomologie $\ell$-adique et Fonctions L}},
-      series={{Lecture Notes in Mathematics}},
-   publisher={{Springer-Verlag}},
-        date={1977},
-      volume={589},
-}
-
-\bib{kamgarpour:09a}{article}{
-      author={\it M. Kamgarpour},
-       title={\rm {Stacky abelianization of algebraic groups}},
-        date={2009},
-     journal={{Transform. Groups}},
-      volume={14},
-      number={4},
-       pages={825\ndash 846},
-}
-
-\bib{lang:56a}{article}{
-      author={\it S. Lang},
-       title={\rm{Algebraic groups over finite fields}},
-        date={1956},
-     journal={Amer. J. Math.},
-      volume={78},
-       pages={555\ndash 563},
-}
-
-\bib{laumon:87a}{article}{
-      author={\it G. Laumon},
-       title={\rm{Transformation de Fourier, constantes d'\'equations
-  fonctionnelles et conjecture de Weil}},
-        date={1987},
-     journal={{Inst. Hautes \'Etudes Sci. Publ. Math.}},
-      volume={65},
-       pages={131\ndash 210},
-}
-
-\bib{lusztig:85a}{article}{
-      author={\it G. Lusztig},
-       title={\rm {Character Sheaves, I}},
-        date={1985},
-     journal={Advances in Math.},
-      volume={56},
-       pages={193\ndash 237},
-}
-
-\bib{lusztig:disconnected1}{article}{
-      author={\it G. Lusztig},
-       title={\rm {Character sheaves on disconnected groups. I}},
-        date={2003},
-     journal={Representation Theory},
-      volume={7},
-       pages={374\ndash 403},
-}
-
-\bib{nicaise-sebag:motivicSerre}{article}{
-      author={\it J. Sebag},
-      author={\it N. Nicaise},
-       title={\rm{Motivic Serre invariants and Weil restriction}},
-        date={2008},
-     journal={J. Algebra},
-      volume={319},
-      number={4},
-       pages={1585\ndash 1610},
-}
-
-\bib{stacks-project}{misc}{
-      author={\it {The {Stacks Project Authors}}},
-       title={\rm {Stacks Project}},
-        date={2013},
-        note={\url{http://stacks.math.columbia.edu}},
-}
-
-\bib{Vakil:spectral_sequences}{unpublished}{
-      author={\it R. Vakil},
-       title={\rm{Spectral sequences: friend or foe?}},
-        date={2008},
-        note={\url{http://math.stanford.edu/~vakil/0708-216/216ss.pdf}},
-}
-
-\bib{vogan:93a}{article}{
-      author={\it D. Vogan},
-       title={\rm {The local Langlands conjecture}},
-        date={1993},
-     journal={Representation Theory of Groups and Algebras},
-      volume={145},
-}
-
-\bib{Weibel:Homological_Algebra}{book}{
-      author={\it C. A. Weibel},
-       title={\rm{An introduction to homological algebra}},
-      series={Cambridge Studies in Advanced Mathematics},
-   publisher={Cambridge Univ. Press},
-     address={Cambridge},
-        date={1994},
-      volume={38},
-}
-
-\end{biblist}
-\end{bibdiv}
-
-\begin{thebibliography}{9}
-
-\bibitem{article}
-\textit{T.~Angel} and \textit{I.~E.~Shparlinski},
-Article in a journal, J. reine angew. Math. \textbf{647} (2010), 123--156.
-
-\bibitem{preprint}
-\textit{C.~Bonnaf\'e},
-Preprint, preprint 2008, \url{http://arxiv.org/abs/0805.4100}.
-
-\bibitem{proceedings}
-\textit{P. Brooksbank},
-Article in a conference proceedings,
-in: Finite geometries (Pingree Park 2004), Oxford University Press, Oxford (2006), 1--16.
-
-\bibitem{phdthesis}
-\textit{J.~D.~King},
-Unpublished dissertation,
-Ph.D. thesis, University of Cambridge, 1995.
-
-\bibitem{book}
-\textit{F. Sukochev}, \textit{S. Lord} and \textit{D. Zanin},
-Book, 2nd ed., De Gruyter, Berlin 2012.
-
-\end{thebibliography}
+\bibliography{../bibliography/Biblio}
 

### 2014-09-08 crelle-dictionary.tex
Commented out commands; MSC footnote; Weil(G,g).

--- 2014-09-08 crelle-dictionary.tex
@@
 % Fonts
-\usepackage{mathrsfs, yfonts}
+\usepackage{mathrsfs}
+%\usepackage{yfonts}
 %Geometry
@@
 
-%%%%%%%%%%%%%%% COUNTER %%%%%%%%%%%%%%%
-%\setcounter{section}{-1}
 %%%%%%%%%%%%%%% THEOREM STYLES %%%%%%%%%%%%%%%
@@
 \newcommand{\EE}{\mathbb{\bar Q}_\ell}
-\newcommand{\Zl}{\mathbb{\bar Z}_\ell}
+%\newcommand{\Zl}{\mathbb{\bar Z}_\ell}
 \newcommand{\OK}{\mathcal{O}_K}
@@
 \newcommand{\EEx}{\EE^\times}
-\newcommand{\Zlx}{\mathbb{\bar Z}_\ell^\times}
+%\newcommand{\Zlx}{\mathbb{\bar Z}_\ell^\times}
 \newcommand{\Weil}[1]{\mathcal{W}_{#1}}
@@
 \DeclareMathOperator{\Gal}{Gal}
-\DeclareMathOperator{\W}{W}
+%\DeclareMathOperator{\W}{W}
 \newcommand{\Frob}[1]{\operatorname{F}_{#1}}
@@
 this paper extends Deligne's function-sheaf dictionary to smooth commutative group schemes over finite fields. 
+\footnote{Mathematics Subject Classification 2010: 14F05 (primary), 14L15 (secondary), 22E50 (tertiary)}
 
@@
 Choose any $\Fq$-rational point $g$ on $G$ and let $\bg$ be the geometric point on $G$ lying above $g$.
-Recall that the \emph{Weil group} of $G$, which we will denote by $\W(G,\bg)$, is a subgroup of the \'etale
+Recall that the \emph{Weil group} of $G$, which we will denote by $\Weil{}(G,\bg)$, is a subgroup of the \'etale
 fundamental group defined by the following diagram:
@@
  \begin{tikzcd}
- 1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \W(G,\bg) \rar \dar[hook] & \Weil{} \rar \dar[hook] & 1 \\
+ 1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \Weil{}(G,\bg) \rar \dar[hook] & \Weil{} \rar \dar[hook] & 1 \\
  1 \rar &  \pi_1(\bG, \bg) \rar & \pi_1(G,\bg) \rar & \Gal(\bFq/\Fq) \rar & 1.
@@
 The $\Fq$-rational point $g$ under the geometric point $\bg$ determines a splitting
-$\Weil{}\to \W(G,\bg)$ of $\W(G,\bg)\to \Weil{}$.
+$\Weil{}\to \Weil{}(G,\bg)$ of $\Weil{}(G,\bg)\to \Weil{}$.
 %
@@
   an equivalence between the category of $\ell$-adic Weil local systems on $G$ and
-  $\ell$-adic representations of $\W(G,\bg)$ \cite{deligne:80a}*{1.1.12}.
+  $\ell$-adic representations of $\Weil{}(G,\bg)$ \cite{deligne:80a}*{1.1.12}.
 
   Now let $(\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$
-  and let $\lambda : \W(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$.
-  Composing with the splitting $\Weil{} \to \W(G,\bg)$ yields an $\ell$-adic character
+  and let $\lambda : \Weil{}(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$.
+  Composing with the splitting $\Weil{} \to \Weil{}(G,\bg)$ yields an $\ell$-adic character
   $\lambda_g : \Weil{} \to \EEx$, which is the same as the Trace of Frobenius defined in Section~\ref{ssec:Frob}, for every $\Fq$ rational point $g$ on $G$:

### 2014-09-08 crelle-dictionary.tex
Removed Crelle sample bibliography.

@@
 
-\begin{thebibliography}{9}
-
-\bibitem{article}
-\textit{T.~Angel} and \textit{I.~E.~Shparlinski},
-Article in a journal, J. reine angew. Math. \textbf{647} (2010), 123--156.
-
-\bibitem{preprint}
-\textit{C.~Bonnaf\'e},
-Preprint, preprint 2008, \url{http://arxiv.org/abs/0805.4100}.
-
-\bibitem{proceedings}
-\textit{P. Brooksbank},
-Article in a conference proceedings,
-in: Finite geometries (Pingree Park 2004), Oxford University Press, Oxford (2006), 1--16.
-
-\bibitem{phdthesis}
-\textit{J.~D.~King},
-Unpublished dissertation,
-Ph.D. thesis, University of Cambridge, 1995.
-
-\bibitem{book}
-\textit{F. Sukochev}, \textit{S. Lord} and \textit{D. Zanin},
-Book, 2nd ed., De Gruyter, Berlin 2012.
-
-\end{thebibliography}
-
 \end{document}

### 2014-09-09 crelle-dictionary.tex
Corrected reference to EGA IV.

@@
 exists in the category of group schemes over $\Fq$;
-see \cite{EGAIV3}*{\S 8.13}.
+see \cite{EGAIV3}*{\S 8.2}.
 This leads to the definition of what we shall call the {\it Greenberg transform}:

### 2014-09-10 crelle-dictionary.tex
Messing with bibliography

--- 2014-09-08 crelle-dictionary.tex
@@
 \usepackage{todonotes}%, showkeys}
-\usepackage{amsrefs}
-\BibSpec{lecture}{%
-  +{}{\PrintAuthors} {author}
-  +{,}{ \textit} {title}
-  +{}{ \parenthesize} {date}
-  +{,}{ } {note}
-  +{,}{ } {location}
-  +{.}{ } {transition}
-}
-\BibSpec{preprint}{%
-  +{}{\PrintAuthors} {author}
-  +{,}{ \textit} {title}
-  +{,}{ preprint } {date}
-  +{,}{ } {note}
-  +{.}{ } {transition}
-}
+%\usepackage[numeric,initials]{amsrefs}
+\usepackage{crellerefs}
+
 % Fonts
-\usepackage{mathrsfs}
-%\usepackage{yfonts}
+\usepackage{mathrsfs, yfonts}
 %Geometry
@@
 
+%%%%%%%%%%%%%%% COUNTER %%%%%%%%%%%%%%%
+%\setcounter{section}{-1}
 %%%%%%%%%%%%%%% THEOREM STYLES %%%%%%%%%%%%%%%
@@
 \newcommand{\EE}{\mathbb{\bar Q}_\ell}
-%\newcommand{\Zl}{\mathbb{\bar Z}_\ell}
+\newcommand{\Zl}{\mathbb{\bar Z}_\ell}
 \newcommand{\OK}{\mathcal{O}_K}
@@
 \newcommand{\EEx}{\EE^\times}
-%\newcommand{\Zlx}{\mathbb{\bar Z}_\ell^\times}
+\newcommand{\Zlx}{\mathbb{\bar Z}_\ell^\times}
 \newcommand{\Weil}[1]{\mathcal{W}_{#1}}
@@
 \DeclareMathOperator{\Gal}{Gal}
-%\DeclareMathOperator{\W}{W}
+\DeclareMathOperator{\W}{W}
 \newcommand{\Frob}[1]{\operatorname{F}_{#1}}
@@
 Greenberg transforms of locally finite type N\'eron models.
+Mathematics Subject Classification 2010: 14F05 (primary), 14L15 (secondary)
 \end{abstract}
@@
 this paper extends Deligne's function-sheaf dictionary to smooth commutative group schemes over finite fields.
-\footnote{Mathematics Subject Classification 2010: 14F05 (primary), 14L15 (secondary), 22E50 (tertiary)}
 
@@
 and, in the process, is led to study the representations of all the pure rational forms of the $p$-adic group, simultaneously.
-A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group \cite{bernstein:vogan_conference}.
+A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group %\cite{bernstein:vogan_conference}.
 Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to quasicharacters of all the pure rational forms of $T$.
@@
 Choose any $\Fq$-rational point $g$ on $G$ and let $\bg$ be the geometric point on $G$ lying above $g$.
-Recall that the \emph{Weil group} of $G$, which we will denote by $\Weil{}(G,\bg)$, is a subgroup of the \'etale
+Recall that the \emph{Weil group} of $G$, which we will denote by $\W(G,\bg)$, is a subgroup of the \'etale
 fundamental group defined by the following diagram:
@@
  \begin{tikzcd}
- 1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \Weil{}(G,\bg) \rar \dar[hook] & \Weil{} \rar \dar[hook] & 1 \\
+ 1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \W(G,\bg) \rar \dar[hook] & \Weil{} \rar \dar[hook] & 1 \\
  1 \rar &  \pi_1(\bG, \bg) \rar & \pi_1(G,\bg) \rar & \Gal(\bFq/\Fq) \rar & 1.
@@
 The $\Fq$-rational point $g$ under the geometric point $\bg$ determines a splitting
-$\Weil{}\to \Weil{}(G,\bg)$ of $\Weil{}(G,\bg)\to \Weil{}$.
+$\Weil{}\to \W(G,\bg)$ of $\W(G,\bg)\to \Weil{}$.
 %
@@
   an equivalence between the category of $\ell$-adic Weil local systems on $G$ and
-  $\ell$-adic representations of $\Weil{}(G,\bg)$ \cite{deligne:80a}*{1.1.12}.
+  $\ell$-adic representations of $\W(G,\bg)$ \cite{deligne:80a}*{1.1.12}.
 
   Now let $(\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$
-  and let $\lambda : \Weil{}(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$.
-  Composing with the splitting $\Weil{} \to \Weil{}(G,\bg)$ yields an $\ell$-adic character
+  and let $\lambda : \W(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$.
+  Composing with the splitting $\Weil{} \to \W(G,\bg)$ yields an $\ell$-adic character
   $\lambda_g : \Weil{} \to \EEx$, which is the same as the Trace of Frobenius defined in Section~\ref{ssec:Frob}, for every $\Fq$ rational point $g$ on $G$:
@@
 %-------------------------------------------------------------------------%
-%\bibliographystyle{amsalpha}
-%\bibliography{../bibliography/Biblio}
+\bibliographystyle{crelle}
+\bibliography{bibliography/Biblio}
+
+\end{document}
+
+% italicized and
+% Bernstein lecture
+% Etingof url, preprint note
+% Italicized author in D-G appendix
+% EGA ordering
+% Ravi notes
+% Vogan LLC
 

### 2014-09-10 crelle-dictionary.tex

--- 2014-09-09 crelle-dictionary.tex
@@
 \usepackage{todonotes}%, showkeys}
-\usepackage{amsrefs}
-\BibSpec{lecture}{%
-  +{}{\PrintAuthors} {author}
-  +{,}{ \textit} {title}
-  +{}{ \parenthesize} {date}
-  +{,}{ } {note}
-  +{,}{ } {location}
-  +{.}{ } {transition}
-}
-\BibSpec{preprint}{%
-  +{}{\PrintAuthors} {author}
-  +{,}{ \textit} {title}
-  +{,}{ preprint } {date}
-  +{,}{ } {note}
-  +{.}{ } {transition}
-}
+%\usepackage[numeric,initials]{amsrefs}
+\usepackage{crellerefs}
+
 % Fonts

### 2014-09-10 crelle-dictionary.tex
Good progress on adapting bibliography to Crelle style
Finished updating bibliography to crelle style using amsrefs and Bibtex database

--- 2014-09-09 crelle-dictionary.tex
@@
 \]
-see \cite{Vakil:spectral_sequences}, expanding on \cite{Weibel:Homological_Algebra}*{Ch 5 and \S 7.5}.
+see \cite{vakil:Algebraic_Geometry}*{\S 1.7}, expanding on \cite{weibel:Homological_Algebra}*{Ch 5 and \S 7.5}.
 The standard derivative on cochains yields two derivatives,
@@
 A \emph{quasicharacter of $X(K)$} is a group homomorphism $X(K) \to \EEx$ that factors through $X(R) \to X(R_n)$ for some non-negative integer $n$.
-We note that this use of the term is compatible with the use of the term {\it quasicharacter} in \cite{cassels-frohlich:AlgebraicNumberTheory}*{Ch XV, \S 2.3}.
+We note that this definition is compatible with \cite{cassels-frohlich:AlgebraicNumberTheory}*{Ch XV, \S 2.3}.
 The group of quasicharacters of $X(K)$ will be denoted by 
@@
 %-------------------------------------------------------------------------%
-%\bibliographystyle{amsalpha}
-%\bibliography{../bibliography/Biblio}
-
-\begin{bibdiv}
-\begin{biblist}
-%\bibselect{references}
-
-\bib{beilinson-bernstein-deligne:81a}{article}{
-   author={\it A. A. Be{\u\i}linson},
-   author={\it J. Bernstein},
-   author={\it P. Deligne},
-   title={\rm Faisceaux pervers},
-   journal ={Ast\'erisque},
-   volume={100},
-   publisher={Soc. Math. France},
-   place={Paris},
-   date={1982},
-   pages={5--171},
-%conference={
-%      title={Analyse et topologie sur les espaces singuliers, I},
-%      address={Luminy},
-%      date={1981},
-%   }
-}
-
-\bib{bernstein:vogan_conference}{lecture}{
-	author = {\it J. Bernstein},
-	title = {\rm Stacks in Representation Theory: What is a representation of an algebraic group?},
- note={Lecture delivered at {\it A conference dedicated to David Vogan on his 60th birthday: Representations of reductive groups}}, 
- %\url{http://math.mit.edu/conferences/Vogan/}},
- 	date={May, 2014},
- 	location={MIT, Boston},
- }
-
- \bib{bernstein-luntz:equivariant_sheaves}{book}{
-      author={\it J. Bernstein},
-      author={\it V. Luntz},
-       title={\rm Equivariant sheaves and functors},
-      series={Lecture Notes in Mathematics},
-   publisher={Springer-Verlag},
-     address={Berlin},
-        date={1994},
-      volume={1578},
-}
-
-\bib{bertrapelle-gonzales:Greenberg}{preprint}{
-      author={\it A. Bertrapelle},
-      author={\it C.-D. Gonz\'ales-Avil\'es},
-       title={\rm The Greenberg functor revisited},
-        note={\url{http://arxiv.org/abs/1311.0051}},
-      date={2013},
-}
-
-\bib{bitan:discriminant}{article}{
-      author={\it R. A. Bitan},
-       title={\rm The discriminant of an algebraic torus},
-        date={2011},
-     journal={J. Number Theory},
-      volume={131},
-      number={9},
-       pages={1657\ndash 1671},
-}
-
-\bib{bosch-lutkebohmert-reynaud:NeronModels}{book}{
-      author={\it S. Bosch},
-      author={\it W. L\"utkebohmert},
-      author={\it M. Reynaud},
-       title={\rm N\'eron models},
-   publisher={Springer-Verlag},
-     address={Berlin},
-        date={1980},
-}
-
-\bib{brown:CohomologyGrps}{book}{
-      author={\it K. S. Brown},
-       title={\rm Cohomology of groups},
-      series={Graduate Texts in Mathematics 87},
-   publisher={{Springer-Verlag}},
-     address={New York},
-        date={1982},
-}
-
-\bib{cartan-eilenberg:HomologicalAlgebra}{book}{
-      author={\it H. Cartan},
-      author={\it S. Eilenberg},
-       title={\rm Homological algebra},
-   publisher={Princeton U.P.},
-     address={Princeton},
-        date={1956},
-}
-
-\bib{cassels-frohlich:AlgebraicNumberTheory}{book}{
-      editor={\it J. W. S. Cassels},
-      editor={\it A. Frohlich},
-       title={\rm Algebraic number theory},
-     edition={2nd ed.,},
-   publisher={London Math Society},
-     address={London},
-        date={2010},
-}
-
-\bib{chai-yu:01a}{article}{
-      author={\it C.-L. Chai},
-      author={\it J.-K. Yu},
-       title={\rm Congruences of N\'eron models for tori and the Artin
-  conductor},
-        date={2001},
-     journal={Annals of Math},
-      volume={154},
-      number={2},
-       pages={347\ndash 382},
-}
-
-\bib{deligne:SGA4.5}{book}{
-      author={\it P. Deligne},
-       title={\rm Cohomologie \'Etale},
-      series={{Lecture Notes in Mathematics 569}},
-   publisher={{Springer-Verlag}},
-     address={Berlin},
-        date={1977},
-}
-
-\bib{deligne:80a}{article}{
-      author={\it P. Deligne},
-       title={\rm La conjecture de Weil II},
-        date={1980},
-     journal={{Inst. Hautes \'Etudes Sci. Publ. Math.}},
-      volume={52},
-       pages={137\ndash 252},
-}
-
-\bib{deligne:02a}{article}{
-      author={\it P. Deligne},
-       title={\rm {Cat\'egories tensorielles}},
-        date={2002},
-     journal={{Mosc. Math. J.}},
-      volume={2},
-      number={2},
-       pages={227\ndash 248},
-}
-
-\bib{deligne-katz:SGA7.2}{book}{
-      author={\it P. Deligne},
-      author={\it N. Katz},
-       title={\rm {Groupes de monodromie en g\'eom\'etrie alg\'ebrique. II}},
-      series={{Lecture Notes in Mathematics}},
-   publisher={{Springer-Verlag}},
-     address={Berlin},
-        date={1973},
-      volume={340},
-}
-
-\bib{demazure-gabriel:GroupesAlgebriques}{book}{
-      author={\it M. Demazure},
-      author={\it P. Gabriel},
-       title={\rm {Groupes alg\'ebriques. Tome 1: G\'eom\'etrie alg\'ebrique,
-  g\'en\'eralit\'es, groupes commutatifs}},
-   publisher={{Masson \& Cie}},
-     address={Paris},
-        date={1970},
-        note={(Appendix: {\it M. Hazewinkel}, Corps de classes local)},
-}
-
-\bib{etingof:09a}{unpublished}{
-      author={\it P. Etingof},
-      author={\it S. Gelaki},
-      author={\it D. Nikshych},
-      author={\it V. Ostrik},
-       title={\rm Tensor categories},
-        date={2009},
-        note={{Lecture notes for MIT's 18.769}, available at \url{http://www-math.mit.edu/~etingof/tenscat.pdf}},
-}
-
-\bib{vdGeer-Moonen:AbelianVarieties}{preprint}{
-      author={\it G. van der Geer},
-      author={\it B. Moonen},
-       title={\rm {Abelian varieties}},
-        date={2013},
-       note={available at \url{http://staff.science.uva.nl/~bmoonen/boek/BookAV.html}},
-%        note={Writing in progress.},
-}
-
-\bib{greenberg:61}{article}{
-      author={\it M. J. Greenberg},
-       title={\rm {Schemata over local rings I}},
-        date={1961},
-     journal={Annals of Math},
-      volume={73},
-      number={2},
-       pages={624\ndash 648},
-}
-
-\bib{greenberg:63a}{article}{
-      author={\it M. J. Greenberg},
-       title={\rm {Schemata over local rings II}},
-        date={1963},
-     journal={Annals of Math},
-      volume={78},
-      number={2},
-       pages={256\ndash 266},
-}
-
-\bib{EGAIV2}{article}{
-      author={\it A. Grothendieck},
-       title={\rm {\'El\'ements de g\'eom\'etrie alg\'ebrique. IV. \'Etude locale
-  des sch\'emas et des morphismes de sch\'emas. II}},
-        date={1965},
-     journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
-      number={24},
-}
-
-\bib{EGAIV3}{article}{
-   author={\it A. Grothendieck},
-   title={\rm{\'El\'ements de g\'eom\'etrie alg\'ebrique. IV. \'Etude locale des
-   sch\'emas et des morphismes de sch\'emas. III}},
-   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
-   number={28},
-   date={1966},
-}
-
-\bib{SGA5}{book}{
-      author={\it A. Grothendieck},
-       title={\rm {S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois Marie 1965--66
-  SGA5: Cohomologie $\ell$-adique et Fonctions L}},
-      series={{Lecture Notes in Mathematics}},
-   publisher={{Springer-Verlag}},
-        date={1977},
-      volume={589},
-}
-
-\bib{kamgarpour:09a}{article}{
-      author={\it M. Kamgarpour},
-       title={\rm {Stacky abelianization of algebraic groups}},
-        date={2009},
-     journal={{Transform. Groups}},
-      volume={14},
-      number={4},
-       pages={825\ndash 846},
-}
-
-\bib{lang:56a}{article}{
-      author={\it S. Lang},
-       title={\rm{Algebraic groups over finite fields}},
-        date={1956},
-     journal={Amer. J. Math.},
-      volume={78},
-       pages={555\ndash 563},
-}
-
-\bib{laumon:87a}{article}{
-      author={\it G. Laumon},
-       title={\rm{Transformation de Fourier, constantes d'\'equations
-  fonctionnelles et conjecture de Weil}},
-        date={1987},
-     journal={{Inst. Hautes \'Etudes Sci. Publ. Math.}},
-      volume={65},
-       pages={131\ndash 210},
-}
-
-\bib{lusztig:85a}{article}{
-      author={\it G. Lusztig},
-       title={\rm {Character Sheaves, I}},
-        date={1985},
-     journal={Advances in Math.},
-      volume={56},
-       pages={193\ndash 237},
-}
-
-\bib{lusztig:disconnected1}{article}{
-      author={\it G. Lusztig},
-       title={\rm {Character sheaves on disconnected groups. I}},
-        date={2003},
-     journal={Representation Theory},
-      volume={7},
-       pages={374\ndash 403},
-}
-
-\bib{nicaise-sebag:motivicSerre}{article}{
-      author={\it J. Sebag},
-      author={\it N. Nicaise},
-       title={\rm{Motivic Serre invariants and Weil restriction}},
-        date={2008},
-     journal={J. Algebra},
-      volume={319},
-      number={4},
-       pages={1585\ndash 1610},
-}
-
-\bib{Vakil:spectral_sequences}{unpublished}{
-      author={\it R. Vakil},
-       title={\rm{Spectral sequences: friend or foe?}},
-        date={2008},
-        note={Notes for 216: Foundations of Algebraic Geometry, available at \url{http://math.stanford.edu/~vakil/0708-216/216ss.pdf}},
-}
-
-\bib{vogan:93a}{article}{
-   author={\it D. A. Vogan},
-   title={\rm{The local Langlands conjecture}},
- %  conference={
- %     title={Representation theory of groups and algebras},
-  % },
-   journal ={Contemp. Math.},
-    volume={145},
-   publisher={Amer. Math. Soc.},
-   place={Providence, RI},
-   date={1993},
-   pages={305--379},
-}
-
-\bib{Weibel:Homological_Algebra}{book}{
-      author={\it C. A. Weibel},
-       title={\rm{An introduction to homological algebra}},
-      series={Cambridge Studies in Advanced Mathematics},
-   publisher={Cambridge Univ. Press},
-     address={Cambridge},
-        date={1994},
-      volume={38},
-}
-
-\end{biblist}
-\end{bibdiv}
+\bibliography{bibliography/Biblio}
 

### 2014-09-10 crelle-dictionary.tex
Fix some hbox issues

@@
 
+% Eliminate a font warning
+\SetSymbolFont{stmry}{bold}{U}{stmry}{m}{n}
+
 %%%%%%%%%%%% BEGIN DOCUMENT %%%%%%%%%%%
@@
 
-  Extensions of $G^0(\bFq)$ by $A(\bFq)$, such as $B(\bFq)$,
+  Extensions of $G^0(\bFq)$ by $A(\bFq)$ with $\Weil{}$-equivariant maps, such as $B(\bFq)$,
   correspond to classes in $\Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq))$.
@@
   classes in $\Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq))$.  The map
-  $G^0(\bFq) \to G(\bFq)$ induces the map
+  $G^0(\bFq) \to G(\bFq)$ induces a homomorphism
   \[
@@
 \begin{proof}
-The sequence is exact at $\QCiso{G^0}$ by Proposition~\ref{prop:restriction}
-and exact at $\QCiso{\pi_0(G)}$ by Lemma~\ref{lem:extension}.
+Exactness at $\QCiso{G^0}$ follows from Proposition~\ref{prop:restriction},
+and at $\QCiso{\pi_0(G)}$ from Lemma~\ref{lem:extension}.
 Here we show that it is also exact at $\QCiso{G}$.
@@
 \begin{enumerate}
-\item Use Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$, the fact that N\'eron models are unique up to isomorphism, the fact that each $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(X_K)$ and the observation that $\QC(X_K)$ is a `union' of the subcategories $\QC(\Gr^R_n(X))$ in $\QC(\Gr_R(X))$.
+\item Use Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$, the fact that N\'eron models are unique up to isomorphism, the fact that every $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(X_K)$ and the observation that every object in $\QC(X_K)$ is in the essential image of $\QC(\Gr^R_n(X))$ for some $n$.
 \item Use Theorem~\ref{thm:snake} with $G = \Gr^R_n(X)$ and then argue as in part (i).
@@
 
-\acknowl{We thank Masoud Kamgarpour, Pramod Achar and Hadi Salmasian
-for allowing us to hijack much of our Research in Teams meeting at the Banff International Research Station into a discussion of
-quasicharacter sheaves; their knowledge and help have been invaluable.
+\acknowl{Pramod Achar, Masoud Kamgarpour and Hadi Salmasian
+allowed us to hijack much of a Research in Teams meeting at the Banff International Research Station into a discussion of
+quasicharacter sheaves.  We thank them for their kindness, knowledge and invaluable help.
 We thank Takashi Suzuki for some very helpful observations and suggestions, especially related to our use of the Hochschild-Serre spectral sequence.

### 2014-09-10 crelle-dictionary.tex
Removing comments and superfluous text

@@
 
-%% Define theorem-like environments as usual:
-
-%\theoremstyle{plain}
- %\newtheorem{theorem}{Theorem}[section]
-
-%\theoremstyle{definition}
-% \newtheorem{remark}[theorem]{Remark}
-
 %%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%
-% Encodings
-%\usepackage[utf8]{inputenc}
-%\usepackage[T1]{fontenc}
-% AMS packages
-%\usepackage{amsmath, amsthm, amssymb}
-\usepackage{todonotes}%, showkeys}
-%\usepackage[numeric,initials]{amsrefs}
+%\usepackage{todonotes}
+% crellerefs is a custom version of amsrefs complying with the Crelle style guidelines
 \usepackage{crellerefs}
@@
 \usepackage{mathrsfs}
-%\usepackage{yfonts}
-%Geometry
-%\usepackage{geometry}
 % Enumitem
@@
 \newcommand{\EE}{\mathbb{\bar Q}_\ell}
-%\newcommand{\Zl}{\mathbb{\bar Z}_\ell}
 \newcommand{\OK}{\mathcal{O}_K}
-%\newcommand{\pK}{\mathfrak{p}_K}
-%\newcommand{\OKp}{\mathcal{O}_{K'}}
-%\newcommand{\pKp}{\mathfrak{p}_{K'}}
 \newcommand{\OL}{\mathcal{O}_L}
 \newcommand{\OO}[1]{\mathcal{O}_{#1}}
-%\newcommand{\Zp}{\mathbb{Z}_p}
-%\newcommand{\Qp}{\mathbb{Q}_p}
 \newcommand{\bFq}{\bar{k}}
@@
 \newcommand{\Fqm}{k_m}
-%\newcommand{\WW}{\mathbb{W}}
 \newcommand{\EEx}{\EE^\times}
-%\newcommand{\Zlx}{\mathbb{\bar Z}_\ell^\times}
 \newcommand{\Weil}[1]{\mathcal{W}_{#1}}
@@
 %%%%%%%%%%%%%%% ALGEBRAIC GROUPS %%%%%%%%%%%%%%%
-%\newcommand{\mathswab}[1]{\operatorname{\textswab{#1}}}
 \newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
-%\newcommand{\GN}[1]{\mathswab{#1}}
-%\newcommand{\bGN}[1]{{\bar{\mathswab{#1}}}}
-%\newcommand{\TT}{\underline{T}}
-%\newcommand{\TL}{\underline{T_L}}
-%\newcommand{\TTp}{\underline{T}'}
 \newcommand{\comp}{\Pi} % Component group
@@
 \DeclareMathOperator{\Gal}{Gal}
-%\DeclareMathOperator{\W}{W}
 \newcommand{\Frob}[1]{\operatorname{F}_{#1}}
@@
 \DeclareMathOperator{\Irrep}{Irrep}
-%\DeclareMathOperator{\Pic}{Pic}
 \DeclareMathOperator{\id}{id}
@@
 \newcommand{\bQC}{{\QC_0}}
-%\newcommand{\fQC}{{\QC_\text{fin}}}
 \newcommand{\QCiso}[1]{\QC(#1)_{/\text{iso}}}
 \newcommand{\bQCiso}[1]{\bQC(#1)_{/\text{iso}}}
-%\newcommand{\fQCiso}[1]{\fQC(#1)_{/\text{iso}}}
 \newcommand{\catname}[1]{\normalfont{\textsf{#1}}}
 \newcommand{\Sch}[1]{{\catname{Sch}_{/#1}}}
-%% amsmath replacements for \atop
-%\newcommand{\latop}[2]{\genfrac{}{}{0pt}{0}{#1}{#2}}
-%\newcommand{\partop}[2]{\genfrac{(}{)}{0pt}{0}{#1}{#2}}
 %% Labeled items
@@
 \newcommand{\GzxGz}{\text{$G^0 \tight{1}{\times}{1} G^0$}}
-%% Margin notes
-%\newcommand\Clifton[1]{\marginpar{\smaller\smaller CC: #1}}
-%\newcommand\David[1]{\marginpar{\smaller\smaller DR: #1}}
 %% Hyphenation override
@@
 \SetSymbolFont{stmry}{bold}{U}{stmry}{m}{n}
+
+% MSC footnote
+\makeatletter
+\newcommand\MSC[2][2010]{%
+   \let\thefootnotetwo=\thefootnote%
+   \renewcommand{\thefootnote}{}%
+   \long\def\@makefntext##1{%
+     \parindent\CrelleIndent
+	 \hb@xt@0em{}##1}%
+   \footnotetext{\textup{#2} \textit{Mathematics Subject Classification.}\enspace  #1}
+   \let\thefootnote=\thefootnotetwo%
+   \crellefntext%
+}
+\makeatother
 
@@
 
-%% \tableofcontents %% Just for papers exceeding 50 pages.
-
 \section*{Introduction}
-
-%\subsection{Overview}
 
@@
 this paper extends Deligne's function-sheaf dictionary to smooth commutative group schemes over finite fields. 
-\footnote{Mathematics Subject Classification 2010: 14F05 (primary), 14L15 (secondary), 22E50 (tertiary)}
+\MSC{14F05 (primary), 14L15 (secondary), 22E50 (tertiary)}
 
@@
 \begin{equation}\label{introbox}
-m^* \qcs{E} \iso \qcs{E} \boxtimes \qcs{E},%\tag{0}
+m^* \qcs{E} \iso \qcs{E} \boxtimes \qcs{E},
 \end{equation}
@@
 {\it A priori}, the composition $\qcs{E} \to \qcs{E}' \to \qcs{E}''$ of two such morphisms need not be compatible with the choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E}''$.
-% since the choice for $\qcs{E}'$ might differ.
  However, for connected $G$ the isomorphism \eqref{introbox} is unique if it exists, and there is no impediment to making the dictionary categorical.
@@
 In order to track the choice of isomorphism, consider the category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is a chosen isomorphism of local systems on $G\times G$.
-%If the component group scheme $\pi_0(G)$ is not cyclic, then 
 In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\Fq)$, but the epimomorphism need not be injective; consequently,
@@
 arising from the spectral sequence, the isomorphism $S_G$ allows us to show (\S\ref{ssec:SandT}) that 
-%$\TrFrob{G}$ is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$. We find that 
 the group homomorphism 
@@
 
-%
 %The appearance of $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ and the trace of Frobenius gives an isomorphism $\TrFrob{G}: \QCiso{G} \to \Hom(G(\Fq),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\Fq$, then $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ measures the kernel of $\TrFrob{G}: \QCiso{G} \to \Hom(G(\Fq),\EEx)$.
@@
 
-%Here we also see the importance of working with Weil sheaves: sheaves on $G$ itself only allow us to geometrize characters with compact image.
-%We conclude in Section~\ref{ssec:basechange} by
-%giving functorial versions of the restriction and norm homomorphisms 
-%of character groups $G(k')^* \to G(k)^*$ and $G(k)^* \to G(k')^*$
-%and describing how quasicharacter sheaves behave under Weil restriction.
-
-%\subsection{Applications over local fields}
-
 As indicated above, our interest in the function-sheaf dictionary for smooth commutative group schemes
@@
 However, we found that our method of passing from $p$-adic tori to group schemes over $\Fq$ applies more generally to
-any local field $K$ with finite residue field $\Fq$ and any commutative algebraic group $X_K$ that admits a N\'eron model $X$. % over $R$, the ring of integers of $K$.
+any local field $K$ with finite residue field $\Fq$ and any commutative algebraic group $X_K$ that admits a N\'eron model $X$.
 This class of groups includes abelian varieties and unipotent $K$-wound groups in addition to the tori we initially considered.
@@
 where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
-%We also use quasicharacter sheaves to categorify the transfer of quasicharacters of tori between characteristic $0$ and characteristic $p$ local fields.
 
@@
 
-%\tableofcontents
-
 \section{The category of quasicharacter sheaves} \label{sec:category}
@@
 Let $\Frob{G} \ceq \id_{G} \times \Frob{}$ be the Frobenius automorphism of $\bG = G \times_{\Spec{\Fq}} \Spec{\bFq}$.
-%When no other fields play a role we will write $\Frob{}$ and $\Weil{}$ instead.
 
@@
 
-%A Weil sheaf $(\gqcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gqcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
-%We now briefly review this point of view for later use in Section~\ref{ssec:basechange}; see also \cite{deligne:80a}*{Def.~1.1.10}.  If $w \ceq \Frob{}^n$ we write $w_G$ for $\Frob{G}^n$.
-%For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gqcs{L}\to \gqcs{L}$ by $\varphi(w) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi);$
-%these isomorphisms satisfy $\varphi(uv) = \varphi(v) \circ v_G^* \varphi(u)$ for $u,v\in \Weil{}$, and we have $\phi = \varphi(\Frob{})$.
-%If we further define $\varphi_1(w) \ceq (w_G)_*(\varphi(w)^{-1})$ then $\varphi_1(w) : (w_G)_* \gqcs{L}\to \gqcs{L}$ is an isomorphism and $\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for $u,v\in \Weil{}$.
-%Thus the pair $(\gqcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of\cite{deligne:SGA4.5}*{Expos\'e XIII, 1.1}, failing only because $\Weil{}$ is not profinite.
-%As we will see in Corollary~\ref{cor:bounded-and-finite}, our use of $\Weil{}$ rather than $\Gal(\bFq/\Fq)$ allows quasicharacter sheaves to correspond to unbounded characters.
-
-%Observe that the rule $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ defines a forgetful functor from quasicharacter
-%sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
-%
-
 Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
@@
 \begin{equation}\label{trWeil}
-%\begin{equation}\label{trWeil}
 \trFrob{(\gqcs{L},\phi)}(g) \ceq \trace(\phi_{\bg};\gqcs{L}_{\bg}),
-%\end{equation}
 \end{equation}
@@
 \end{proof}
-
-%We end this section with a simple result on products of quasicharacter sheaves, which is needed to show that the isomorphism above is functorial.
 
@@
 from the category of smooth commutative group schemes over $\Fq$ to the category of abelian groups.
-%Likewise, for $\TrFrob{G} : \lQCiso{G} \to G(\Fq)^*$, {\it mut.\hskip-1pt mut.}
 \end{proposition}
@@
 
-%\subsection{Morphisms of quasicharacter sheaves}\label{ssec:mor}
-
 \section{Quasicharacter sheaves on \'etale commutative group schemes} \label{sec:etale}
-
-%\subsection{Quasicharacter sheaves, revisited}
-
-%\'Etale group schemes form a counterpoint to connected groups,
-%since the component group of a smooth commutative group scheme
-%is an \'etale group scheme \cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
-%However, the function-sheaf dictionary is substantially different in the two cases.
-%To see why, we begin by specializing the definition of quasicharacter sheaves to the case
-%of \'etale commutative group schemes,
-%using the equivalence $G \mapsto G(\bFq)$
-%from the category of \'etale group schemes over $\Fq$ to the category of groups equipped
-%with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group.
 
@@
 \end{proposition}
-%\todo{Is this a lemma? Is the corollary a proposition?}
 
@@
 \begin{proof}
-%We first show that $S_G$ is injective.  
 Suppose $[\qcs{L}] \in \QCiso{G}$ with $S_G([\qcs{L}]) = [\alpha \oplus \beta] = 0$,
@@
 \end{proof}
-
-%Note that Proposition~\ref{prop:autornaught_etale} tells us that if $G$ is an \'etale commutative group scheme over $\Fq$ then every hom-set is either trivial or $\{ 0 \} \cup \left(G(\bFq)_{\Weil{}}\right)^*$, non-canonically.
 
@@
  \item $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is an isomorphism of groups;
- \item every quasicharacter sheaf on $G$ is isomorphic to one defined by a discrete isogeny;%as in Proposition~\ref{prop:finite};
+ \item every quasicharacter sheaf on $G$ is isomorphic to one defined by a discrete isogeny;
  \item $\Aut(\qcs{L}) = 1$, for all quasicharacter sheaves $\qcs{L}$ on $G$.
-%  \item for all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $G$ and for every $\rho \in \Hom(\qcs{L},\qcs{L}')$, either $\rho$ is trivial or an isomorphism.
  \end{enumerate}
@@
 
-%\begin{remark}
 We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of quasicharacter sheaves on $G$ is equivalent to the category of one-dimensional representations $V$ of $G(\Fq)$ equipped with an isomorphism $V\iso \EE$, and therefore equivalent to the category of characters $\psi$ of $G(\Fq)$.
@@
 As a slight variation, one may also consider one-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
-%One may show that all such $\gqcs{L}$ are determined by extensions of $\bG$ by $\EEx$ which are fixed by Frobenius and that the trace of Frobenius provides a canonical isomorphism from $\Hh^2(\bG,\EEx)^{\Frob{}}$ to $G(\Fq)^*$; {\it cf.\ }
-%One may show that all such $\gqcs{L}$ are determined by extensions of $\bG$ by $\EEx$ which are fixed by Frobenius and that the trace of Frobenius provides a canonical isomorphism from $\Hh^2(\bG,\EEx)^{\Frob{}}$ to $G(\Fq)^*$; {\it cf.\ } \cite{kamgarpour:09a}*{Prop 2.15}.
 
@@
 \begin{proposition}\label{prop:restriction}
-%For every quasicharacter sheaf $\qcs{L}^0$ on $G^0$ there is some finite quasicharacter sheaf
-%$\qcs{L}$ on $G$ such that $\qcs{L}\vert_{G^0} \iso \qcs{L}^0$.
-%As a consequence, t
 The restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
@@
 %
- %Let $(\pi,\psi)$ be a finite quasicharacter sheaf on $G^0$.
  By Lemma~\ref{lemma:ext}, there is an extension of the
@@
 \begin{proof}
-%  Recall the short exact sequence \eqref{eq:pi0}
-%  defining the component group scheme for $G$:
-%  \[
-%  \begin{tikzcd}
-%    1 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
-%  \end{tikzcd}
-%  \]
   Let
@@
   \begin{tikzcd}[row sep=20, column sep=20]
-%  & 0 \arrow{d} & 0 \arrow{d} & 0\arrow{d} \\
-%    0 \arrow[dotted]{r} & \ker \TrFrob{\pi_0(G)} \arrow[dotted]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dotted]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
     0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
@@
     &  G(\Fq)^* \rar & G^0(\Fq)^* \rar & 0
-%   &  \coker \TrFrob{\pi_0(G)} =0 \arrow[dotted]{r} & \coker \TrFrob{G} \arrow[dotted]{r} & \coker \TrFrob{G^0} =0 & 
-%    & \arrow{d} \coker \TrFrob{\pi_0(G)} =0 \arrow[dashed]{r} & \arrow{d} \coker \TrFrob{G} \arrow[dashed]{r} &  \arrow{d} \coker \TrFrob{G^0} =0 & \\
-%      & 0 & 0 & 0 \\
   \end{tikzcd}
@@
 It now follows from the snake lemma
-   %\begin{equation}\label{eq:snake}
  \[
   \begin{tikzcd}[row sep=20, column sep=15]
-%  & 0 \arrow{d} & 0 \arrow{d} & 0\arrow{d} \\
     0 \arrow[dotted]{r} & \ker \TrFrob{\pi_0(G)} \arrow[dotted]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dotted]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
@@
    &  \coker \TrFrob{\pi_0(G)} =0 \arrow[dotted]{r} & \coker \TrFrob{G} \arrow[dotted]{r} & \coker \TrFrob{G^0} =0 & 
-%    & \arrow{d} \coker \TrFrob{\pi_0(G)} =0 \arrow[dashed]{r} & \arrow{d} \coker \TrFrob{G} \arrow[dashed]{r} &  \arrow{d} \coker \TrFrob{G^0} =0 & \\
-%      & 0 & 0 & 0 \\
-  \end{tikzcd}
-  \]
- % \end{equation}
+  \end{tikzcd}
+  \]
 that $\coker \TrFrob{G} =0$
@@
 \begin{proof} 
-%For the first part of the proposition, argue as in the analogous part of Proposition~\ref{prop:autornaught_etale}.
-%For the second, f
 Fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the group homomorphism from $\Aut(\qcs{L})$ to $\Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
@@
 If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$, we define
-%a quasicharacter sheaf 
 $\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
@@
 defined in Section~\ref{ssec:category}, to $\Weil{k'}$.
-%, $\Weil{k'}$.
 
@@
 
-%\todo{Can we improve on this result by proving that $\rho$ is an equivalence of categories?}
-
-\section{Applications}\label{sec:applications}% to algebraic tori and abelian varieties over \texorpdfstring{$p$}{p}-adic fields}
+\section{Applications}\label{sec:applications}
 
@@
 Set $S = \Spec{R}$ and $S_n = \Spec{R_n}$;
-% for every non-negative integer $n$;
 note that $S_0 = \Spec{\Fq}$ is the special fibre of $S$.
@@
 it follows from Lemma~\ref{lem:pullback} that the pullback functor \eqref{men-pulled} actually induces
-%\[
-%\Hom(X'(R'_{en-1}),\EEx)  \to  \Hom(X(R_{n-1}),\EEx) .
-%\]
 \[ 
@@
 \]
-%(in which case $K$ and $L$ are said to be $m$-close).
 Suppose also that
@@
 $m \leq n$.
-%the isomorphism \eqref{transfer} is level-preserving at integers less than $N$.
-%
 
@@
  \]
-compatible with \eqref{transfer}.% ($m < N$).
+compatible with \eqref{transfer}.
 \end{proposition}
@@
 
-%-------------------------------------------------------------------------%
-% GENERAL INSTRUCTIONS                                                    %
-% Please keep formatting macros to a minimum.                             %
-% Avoid redundant source code such as unused definitions or longer        %
-% passages of comments (% or {comment}).                                  %
-% Do not worry about bad page breaks, etc. and avoid adding extra space   %
-% and using glue to improve the appearance of the manuscript.             %
-% Please ensure that the material has been carefully proofread and that   %
-% all files used are made available to the editors/publisher.             %
-%-------------------------------------------------------------------------%
-
-%-------------------------------------------------------------------------%
-% PACKAGES                                                                %
-% Missing packages can be downloaded at www.tug.org/ctan.html.            %
-%-------------------------------------------------------------------------%
-
-%-------------------------------------------------------------------------%
-% MULTILINE EQUATIONS                                                     %
-% For numbered/unnumbered multiline equations use align/align* instead of %
-% eqnarray. (Other available environments for multiline displays are      %
-% gather, multline, aligned, split, etc.)                                 %
-%-------------------------------------------------------------------------%
-
-%-------------------------------------------------------------------------%
-% QED SYMBOL                                                              %
-% The \qedhere command forces the QED symbol to go on the present line,   %
-% which might be useful if the last part of a proof environment is, e.g., %
-% a displayed equation or list environment.                               %
-%-------------------------------------------------------------------------%
-
-%-------------------------------------------------------------------------%
-% SOME MORE MATH                                                          %
-% -- Avoid blank lines before or after a display, unless you really want  %
-%    to start a new paragraph.                                            %
-% -- Use equation*, gather* or the bracket pair \[ and \] instead of      %
-%    double dollar signs $$.                                              %
-% -- Use \operatorname{...} for math operators that are not predefined    %
-%    or define new operators with \DeclareMathOperator. lim-like          %
-%    operators can be defined with \DeclareOperator*                      %
-% -- Use \quad for spacings in displayed formulas.                        %
-% -- Use \substack{... \\ ...} for multiline subscripts on, e.g., sums.   %
-%-------------------------------------------------------------------------%
-
-%-------------------------------------------------------------------------%
-% ENUMERATIONS                                                            %
-% By default, the labels of first level enumerations are (i), (ii), etc.  %
-% You may change them to become, e.g., A., B. etc., using an optional     %
-% argument: \begin{enumerate}[A.]                                         %
-%-------------------------------------------------------------------------%
-
-%-------------------------------------------------------------------------%
-% FIGURES AND TABLES                                                      %
-% You may include a figure writing                                        %
-% \begin{figure}[t]                                                       %
-%   \includegraphics[width=.8\textwidth]{xxx.yyy}                         %
-%   \caption{Caption.}\label{fig:zzz}                                     %
-% \end{figure}                                                            %
-% A table is included similar using the table environment.                %
-% Sub-captions are created as follows:                                    %
-% \begin{figure}[t]                                                       %
-%   \subfloat[Caption a]{\includegraphics[width=.45\textwidth]{...}}      %
-%   \hfill                                                                %
-%   \subfloat[Caption b]{\includegraphics[width=.45\textwidth]{...}}      %
-%   \caption{Caption.}                                                    %
-% \end{figure}                                                            %
-%-------------------------------------------------------------------------%
-
-%-------------------------------------------------------------------------%
-% QUOTATION MARKS                                                         %
-% Double quotation marks are produced using `` and ''. The opening quote  %
-% then looks like a superscript 66 and the closing quote like a           %
-% superscript 99.                                                         %
-%-------------------------------------------------------------------------%
-
-%-------------------------------------------------------------------------%
-% HYPHEN VS. DASH                                                         %
-% The hyphen (-) is used for compound words like $n$-dimensional.         %
-% (Don't write things like $n-$dimensional!)                              %
-% The en-dash (--) is used for number ranges and it can stand for `and',  %
-% e.g., between two names: ``Various generalizations of the               %
-% Cauchy--Schwarz inequality are presented on pages 63--67.''             %
-% To partition a sentence one may use the em-dash (---) with no space     %
-% on either side; we prefer the en-dash with a blank on both sides.       %
-% The mathematical minus sign is produced by a single - within            %
-% mathematics mode.                                                       %
-%-------------------------------------------------------------------------%
-
-%-------------------------------------------------------------------------%
-% REFERENCES                                                              %
-% Use \label and \ref for all cross-references to equations, figures,     %
-% tables, sections, subsections, etc.                                     %
-%-------------------------------------------------------------------------%
-
-%-------------------------------------------------------------------------%
-% BIBLIOGRAPHY                                                            %
-% References should be collected at the end of the paper and numbered in  %
-% alphabetical order of the authors' names. Titles of journals should be  %
-% abbreviated as in Mathematical Reviews. Please do not use small caps    %
-% for the names of the authors. The preferred style is shown in the       %
-% examples below.                                                         %
-% Refer to the bibliography entries using \cite commands.                 %
-% Using BibTeX, you simply have to add the names of your databases as     %
-%   \bibliography{mydatabase}                                             %
-% The file crelle.bst then ensures the correct style.                     %
-%-------------------------------------------------------------------------%
 \bibliography{bibliography/Biblio}

### 2014-09-30 article-dictionary.tex
Made article-dictionary. Need to look at Biblio, though.

--- 2014-09-10 crelle-dictionary.tex
@@
 %% This file should be the main file of your article.   %%
-%% Please uncomment exactly one of the following lines. %%
-%%------------------------------------------------------%%
-
-%% \documentclass[CM,Submssn]{degruyter-crelle}       %% Equations numbered as (1), (2) etc.
- \documentclass[CM,Submssn,SecEq]{degruyter-crelle} %% Equations numbered as (1.1), (1.2) etc.
-
-%% Do not alter the following line.
-\firstpage{}\volume{}\volumeyear{}\copyrightyear{}\doiyear{}\doi{}\received{XXX}\revised{XXX}
+
+\documentclass[10pt]{amsart}
+\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
+\geometry{a4paper} % or letter or a5paper or ... etc
+% \geometry{landscape} % rotated page geometry
+
+% See the ``Article customise'' template for come common customisations
 
@@
 
-\author{Clifton}{Cunningham}{C.~Cunningham}{Calgary}
-\author{David}{Roe}{D.~Roe}{Calgary}
-
-\contact{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive, {T2N~1N4}, Calgary, Canada}{cunning@math.ucalgary.ca}
-\contact{Pacific Institute for the Mathematical Sciences, University of Calgary, 2500 University Drive, {T2N~1N4}, Calgary, Canada}{roed.math@gmail.com}
-
-%\subjclass[2010]{14F05 (primary), 14L15 (secondary)}
-%\keywords{function-sheaf dictionary, trace of Frobenius, geometrization, categorification, quasicharacters, quasicharacter sheaves, smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor}
-
-\researchsupported{We gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences and the National Science and Engineering Research Council (Canada), as well the hospitality of the Banff International Research Station during a Research in Teams program.}
+\author{Clifton Cunningham}
+\author{David Roe}
+
+\address{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive Northwest, Alberta, Calgary, Canada, {T2N~1N4}.}
+\email{cunning@math.ucalgary.ca}
+%\address{Pacific Institute for the Mathematical Sciences, University of Calgary, 2500 University Drive, {T2N~1N4}, Calgary, Canada, {\tt roed.math@gmail.com}}
+\address{Department of Mathematics, University of British Columbia, 1984 Mathematics Road, Vancouver, British Columbia, Canada, {V6T~1Z2}.}
+\email{roed.math@gmail.com}
+
+\subjclass[2010]{14F05 (primary), 14L15 (secondary), 22E50 (tertiary)}
+
+\keywords{function-sheaf dictionary, trace of Frobenius, geometrization, categorification, quasicharacters, quasicharacter sheaves, smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor}
 
@@
 % crellerefs is a custom version of amsrefs complying with the Crelle style guidelines
-\usepackage{crellerefs}
+%\usepackage{crellerefs}
+
+\usepackage{amssymb,amsrefs}
 
@@
 % Eliminate a font warning
-\SetSymbolFont{stmry}{bold}{U}{stmry}{m}{n}
+%\SetSymbolFont{stmry}{bold}{U}{stmry}{m}{n}
 
@@
 
+\maketitle
+
 \section*{Introduction}
@@
 this paper extends Deligne's function-sheaf dictionary to smooth commutative group schemes over finite fields.
-\MSC{14F05 (primary), 14L15 (secondary), 22E50 (tertiary)}
 
@@
 The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in that context.
+
+\noindent\textbf{Acknowledgements.\ } {Pramod Achar, Masoud Kamgarpour and Hadi Salmasian
+allowed us to hijack much of a Research in Teams meeting at the Banff International Research Station into a discussion of
+quasicharacter sheaves.  We thank them for their kindness, knowledge and invaluable help.
+We thank Takashi Suzuki for some very helpful observations and suggestions, especially related to our use of the Hochschild-Serre spectral sequence.
+We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and drawing our attention to their result on Weil restriction and the Greenberg transform.
+We thank Joseph Bernstein for suggesting a connection between our category of quasicharacter sheaves for $p$-adic tori and quasicharacters of its pure rational forms.}
+
+{Finally, we gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences and the National Science and Engineering Research Council (Canada), as well the hospitality of the Banff International Research Station during a Research in Teams program.}
 
@@
 
-\acknowl{Pramod Achar, Masoud Kamgarpour and Hadi Salmasian
-allowed us to hijack much of a Research in Teams meeting at the Banff International Research Station into a discussion of
-quasicharacter sheaves.  We thank them for their kindness, knowledge and invaluable help.
-We thank Takashi Suzuki for some very helpful observations and suggestions, especially related to our use of the Hochschild-Serre spectral sequence.
-We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and drawing our attention to their result on Weil restriction and the Greenberg transform.
-We thank Joseph Bernstein for suggesting a connection between our category of quasicharacter sheaves for $p$-adic tori and quasicharacters of its pure rational forms.
-}
-
 \bibliography{bibliography/Biblio}

### 2014-10-01 dictionary.tex
Fixed references

@@
-% !TEX encoding = UTF-8 Unicode
-\documentclass{amsart}
-\pdfoutput=1
-
-%%%%%%%%%%%%%%%%%% HEADING %%%%%%%%%%%%%%%%%%
-
-\title[The function--sheaf dictionary]{The function--sheaf dictionary for smooth commutative group schemes over finite fields}
-
-\date{\today}
+%%------------------------------------------------------%%
+%% This file should be the main file of your article.   %%
+
+\documentclass[10pt]{amsart}
+\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
+\geometry{a4paper} % or letter or a5paper or ... etc
+% \geometry{landscape} % rotated page geometry
+
+% See the ``Article customise'' template for come common customisations
+
+\title{From the function-sheaf dictionary to quasicharacters of $p$-adic tori}
+
 \author{Clifton Cunningham}
+\author{David Roe}
+
+\address{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive Northwest, Alberta, Calgary, Canada, {T2N~1N4}.}
 \email{cunning@math.ucalgary.ca}
-\address{University of Calgary}
-\author{David Roe}
+%\address{Pacific Institute for the Mathematical Sciences, University of Calgary, 2500 University Drive, {T2N~1N4}, Calgary, Canada, {\tt roed.math@gmail.com}}
+\address{Department of Mathematics, University of British Columbia, 1984 Mathematics Road, Vancouver, British Columbia, Canada, {V6T~1Z2}.}
 \email{roed.math@gmail.com}
-\address{Pacific Institute for the Mathematical Sciences, University of Calgary}
-\subjclass[2010]{14F05 (primary), 14L15 (secondary)}
-\keywords{function--sheaf dictionary, trace of Frobenius, geometrization, categorification, quasicharacters, quasicharacter sheaves, smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor}
+
+\subjclass[2010]{14F05 (primary), 14L15 (secondary), 22E50 (tertiary)}
+
+\keywords{function-sheaf dictionary, trace of Frobenius, geometrization, categorification, quasicharacter sheaves, smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor, quasicharacters}
 
 %%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%
-% Encodings
-\usepackage[utf8]{inputenc}
-\usepackage[T1]{fontenc}
-% AMS packages
-\usepackage{amsmath, amsthm, amssymb, todonotes}%, showkeys}
-\usepackage[alphabetic]{amsrefs}
+%\usepackage{todonotes}
+% crellerefs is a custom version of amsrefs complying with the Crelle style guidelines
+%\usepackage{crellerefs}
+
+\usepackage{amssymb,amsrefs}
+
+\BibSpec{lecture}{%
+  +{} {\PrintAuthors}				{author}
+  +{,}{ }						{title}
+  +{}{ \PrintDateB}				{date}
+  +{.}{ Lecture delivered at \textit}	{conference}
+  +{,}{ }						{address}
+  +{.}{ }						{transition}
+}
+
 % Fonts
-\usepackage{mathrsfs, yfonts}
-%Geometry
-\usepackage{geometry}
+\usepackage{mathrsfs}
 % Enumitem
-%\usepackage{enumitem}
+\usepackage{enumitem}
 % TikZ
@@
 \newcommand{\EE}{\mathbb{\bar Q}_\ell}
-\newcommand{\Zl}{\mathbb{\bar Z}_\ell}
 \newcommand{\OK}{\mathcal{O}_K}
-\newcommand{\pK}{\mathfrak{p}_K}
-\newcommand{\OKp}{\mathcal{O}_{K'}}
-\newcommand{\pKp}{\mathfrak{p}_{K'}}
 \newcommand{\OL}{\mathcal{O}_L}
 \newcommand{\OO}[1]{\mathcal{O}_{#1}}
-\newcommand{\Zp}{\mathbb{Z}_p}
-\newcommand{\Qp}{\mathbb{Q}_p}
 \newcommand{\bFq}{\bar{k}}
@@
 \newcommand{\Fqm}{k_m}
-\newcommand{\WW}{\mathbb{W}}
 \newcommand{\EEx}{\EE^\times}
-\newcommand{\Zlx}{\mathbb{\bar Z}_\ell^\times}
 \newcommand{\Weil}[1]{\mathcal{W}_{#1}}
@@
 %%%%%%%%%%%%%%% ALGEBRAIC GROUPS %%%%%%%%%%%%%%%
-\newcommand{\mathswab}[1]{\operatorname{\textswab{#1}}}
 \newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
-\newcommand{\GN}[1]{\mathswab{#1}}
-\newcommand{\bGN}[1]{{\bar{\mathswab{#1}}}}
-\newcommand{\TT}{\underline{T}}
-\newcommand{\TL}{\underline{T_L}}
-\newcommand{\TTp}{\underline{T}'}
 \newcommand{\comp}{\Pi} % Component group
@@
 \DeclareMathOperator{\Gal}{Gal}
-\DeclareMathOperator{\W}{W}
 \newcommand{\Frob}[1]{\operatorname{F}_{#1}}
@@
 \DeclareMathOperator{\Irrep}{Irrep}
-\DeclareMathOperator{\Pic}{Pic}
 \DeclareMathOperator{\id}{id}
@@
 \newcommand{\Spec}[1]{{\operatorname{Spec}\hskip-1pt( #1 )}}
-
 %%%%%%%%%%%% MISCELLANEOUS OPERATORS %%%%%%%%%%%%
@@
 \newcommand{\bQC}{{\QC_0}}
-\newcommand{\fQC}{{\QC_\text{fin}}}
 \newcommand{\QCiso}[1]{\QC(#1)_{/\text{iso}}}
 \newcommand{\bQCiso}[1]{\bQC(#1)_{/\text{iso}}}
-\newcommand{\fQCiso}[1]{\fQC(#1)_{/\text{iso}}}
-%% amsmath replacements for \atop
-\newcommand{\latop}[2]{\genfrac{}{}{0pt}{0}{#1}{#2}}
-\newcommand{\partop}[2]{\genfrac{(}{)}{0pt}{0}{#1}{#2}}
+\newcommand{\catname}[1]{\normalfont{\textsf{#1}}}
+\newcommand{\Sch}[1]{{\catname{Sch}_{/#1}}}
 %% Labeled items
@@
 \newcommand{\GzxGz}{\text{$G^0 \tight{1}{\times}{1} G^0$}}
-%% Margin notes
-\newcommand\Clifton[1]{\marginpar{\smaller\smaller CC: #1}}
-\newcommand\David[1]{\marginpar{\smaller\smaller DR: #1}}
 %% Hyphenation override
@@
 
-%%%%%%%%%%%% BEGIN DOCUMENT %%%%%%%%%%%%
+% Eliminate a font warning
+%\SetSymbolFont{stmry}{bold}{U}{stmry}{m}{n}
+
+% MSC footnote
+\makeatletter
+\newcommand\MSC[2][2010]{%
+   \let\thefootnotetwo=\thefootnote%
+   \renewcommand{\thefootnote}{}%
+   \long\def\@makefntext##1{%
+     \parindent\CrelleIndent
+	 \hb@xt@0em{}##1}%
+   \footnotetext{\textup{#2} \textit{Mathematics Subject Classification.}\enspace  #1}
+   \let\thefootnote=\thefootnotetwo%
+   \crellefntext%
+}
+\makeatother
+
+%%%%%%%%%%%% BEGIN DOCUMENT %%%%%%%%%%%
+
 \begin{document}
@@
 \begin{abstract}
+We introduce the category of quasicharacter sheaves on smooth commutative group schemes $G$ over finite fields $k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
+We show that the group of isomorphism classes of quasicharacter sheaves is an extension of the group of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
+As an application, we find a category of sheaves for which isomorphism classes correspond to quasi\-characters in the case of algebraic tori, abelian varieties and unipotent wound groups over local fields.
+In this geometrization of quasicharacters, our sheaves are local systems on
+Greenberg transforms of locally finite type N\'eron models.
+\end{abstract}
+
+\maketitle
+
+\section*{Introduction}
+
 Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
-this paper extends Deligne's function--sheaf dictionary for characters of connected commutative algebraic groups over finite fields to characters of smooth commutative group schemes over finite fields.
- \end{abstract}
-
-\maketitle
-
-\section{Introduction}
-
-\subsection{Overview}
-
-As Deligne explained in \cite{deligne:SGA4.5}*{Sommes trig.}, if $G$ is a connected commutative algebraic group over $\FF_q$, then the trace of Frobenius provides a perfect dictionary between characters of $G(\FF_q)$ and isomorphism classes of rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which
+this paper extends Deligne's function-sheaf dictionary from commutative algebraic groups to smooth commutative group schemes over finite fields.
+
+As Deligne explained in \cite{deligne:SGA4.5}*{Sommes trig.}, if $G$ is a connected commutative algebraic group over a finite field $k$, then the trace of Frobenius provides a bijection between the group $G(\Fq)^*$ of $\ell$-adic characters of $G(\Fq)$ and isomorphism classes of rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which
 \begin{equation}\label{introbox}
-m^* \qcs{E} \iso \qcs{E} \boxtimes \qcs{E},\tag{0}
+m^* \qcs{E} \iso \qcs{E} \boxtimes \qcs{E},
 \end{equation}
@@
 %
-If one wishes to make a category from this class of local systems, one is led to consider sheaf homorphisms $\qcs{E} \to \qcs{E}'$ which are compatible with particular choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E'}$.
-{\it A priori}, these sheaf homomorphisms do not form a category, but since $G$ is connected, the existence of \eqref{introbox} makes \eqref{introbox} unique; as a consequence, there is no impediment to categorifying the dictionary in this case.
-
-If $G$ is a commutative algebraic group over $\FF_q$ which is not connected, however, then one must keep track of the choice of \eqref{introbox}, leading to a category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is an isomorphism of local systems on $G\times G$.
-If the component group scheme $\pi_0(G)$ (which is an étale commutative group scheme over $\FF_q$) is not cyclic, then while the trace of Frobenius provides a surjection from isomorphism classes in the category of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\FF_q)$, that group homomorphism need not be injective.
-In other words, if $G$ is a commutative algebraic group over $\FF_q$ which is not connected, then every character may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely. 
-While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious since if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\FF_q)$ then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
-
-In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\FF_q$ we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system  -- a local system on ${\bar G} := G\times_{\Spec{\FF_q}} \Spec{{\bar \FF}_q}$ -- while retaining the extra structure $\mu_\qcs{E}$.
-Let $\Weil{} \subset \Gal({\bar\FF}_q/\FF_q)$ be the Weil group for $\FF_q$; let $\Frob{G} : \bG \to \bG$ be the Frobenius automorphism for $\bG$.
-In this way we are lead to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ in which objects are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G}$ and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves; the isomorphisms $\mu$ and $\phi$ must of course be compatible in the obvious way.
-Morphism in $\QC(G)$ are then homomorphisms of Weil sheaves which are compatible with the extra structure.
-
-We first test the category of quasicharacter sheaves by examining its objects on étale commutative group schemes $G$ over $\FF_q$; étale group schemes form a counterpoint to connected algebraic groups, since the component group of a smooth commutative group scheme is an étale group scheme.
-We find that the group homomorphism 
-\begin{equation}
-T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)
-\end{equation}
-provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$, canonically.
-One can show, using the Kunneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
-The fact that $T_G$ is not an isomorphism should not be too troubling because if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\FF_q)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
-Here we also see the importance of working with Weil sheaves; for example, without them, we would not be able to geometrize the character of the étale group scheme $\ZZ$ over $\FF_q$ given by $1\mapsto \ell$, for example.
-
-Returning to the case of connected commutative algebraic groups $G$ over $\FF_q$, we confirm that, in this case, $\QC(G)$ is equivalent to the category of characters $\psi$ of $G(\FF_q)$, the equivalence being given by descent to $G$ followed by pullback by the Lang isogeny for $G$.
-%
-%The appearance of $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ and the trace of Frobenius gives an isomorphism $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\FF_q$, then $\Hh^2(\bG,\EEx)^{\Gal({\bar\FF}_q/\FF_q)}$ measures the kernel of $T_G: \QCiso{G} \to \Hom(G(\FF_q),\EEx)$.
+If one wishes to make a category from this class of local systems, one is led to consider morphisms $\qcs{E} \to \qcs{E}'$ of sheaves which are compatible with particular choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E'}$.
+{\it A priori}, the composition $\qcs{E} \to \qcs{E}' \to \qcs{E}''$ of two such morphisms need not be compatible with the choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E}''$.
+ However, for connected $G$ the isomorphism \eqref{introbox} is unique if it exists, and there is no impediment to making the dictionary categorical.
+
+If $G$ is a commutative algebraic group over $\Fq$ which is not connected, then the isomorphism \eqref{introbox} need not be unique.
+In order to track the choice of isomorphism, consider the category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is a chosen isomorphism of local systems on $G\times G$.
+In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\Fq)$, but the epimomorphism need not be injective; consequently,
+every character of $G(\Fq)$ may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely in the category of pairs. 
+While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious: if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\Fq)$ then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
+
+In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\Fq$,
+we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\qcs{E}$. 
+In this way we are led to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ (\S\ref{ssec:category}).
+Objects in $\QC(G)$ are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\Fq}} \Spec{\bFq}$
+and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves satisfying certain compatibility conditions.
+Morphisms in $\QC(G)$ are then morphisms of Weil sheaves which are compatible with the extra structure.
+
+We first test the category of quasicharacter sheaves by examining its objects on \'etale commutative group schemes $G$ over $\Fq$ (\S\ref{sec:etale});
+\'etale group schemes form a counterpoint to connected algebraic groups, since the component group of any smooth group scheme is an \'etale group scheme.
+Our key tools for understanding the trace of Frobenius in the \'etale case are a reinterpretation of $\QC(G)$ in terms of stalks (\S\ref{ssec:stalks}) and a
+relationship with the Hochschild-Serre spectral sequence (\S\ref{ssec:E}) for $\Weil{} \ltimes \bG$, where $\Weil{} \subset \Gal(\Fq/\Fq)$ is the Weil group for $\Fq$.
+We define (\S\ref{ssec:S}) an isomorphism $S_G$ from $\QCiso{G}$ to the second cohomology of the total space of the spectral sequence
+\[
+E_2^{p,q} \ceq \Hh^p(\Weil{}, \Hh^q(\bG, \EEx)) \Rightarrow \Hh^{p+q}(\Weil{} \ltimes \bG, \EEx).
+\]
+Paired with the short exact sequence
+\[
+  0 \to \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to \Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to 0
+\]
+arising from the spectral sequence, the isomorphism $S_G$ allows us to show (\S\ref{ssec:SandT}) that 
+the group homomorphism 
+\[
+\TrFrob{G}: \QCiso{G} \to G(\Fq)^*
+\]
+provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$.
+One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
+%The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
+
+Returning to the case of connected commutative algebraic groups $G$, we consider quasicharacter sheaves that arise via base change to $\bFq$ from local systems on $G$ (\S\ref{ssec:descentG}) and
+those that appear in a pushforward from a constant sheaf along a discrete isogeny $H \to G$ (\S\ref{ssec:discrete_isogenies}).
+While these constructions make sense even for non-connected $G$, in the connected
+case we show that every quasicharacter sheaf can be described in both of these ways (\S\ref{ssec:connected}).
+We use this fact to prove that $\TrFrob{G}$ is an isomorphism for connected commutative algebraic groups $G$
+and to determine the automorphism groups of quasicharacter sheaves on such $G$.
+
+%The appearance of $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ and the trace of Frobenius gives an isomorphism $\TrFrob{G}: \QCiso{G} \to \Hom(G(\Fq),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\Fq$, then $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ measures the kernel of $\TrFrob{G}: \QCiso{G} \to \Hom(G(\Fq),\EEx)$.
 %This observation makes plain the fact that  . . .
-%
-As we show in the paper, while characters of connected commutative algebraic groups $G$ can be geometrized using  local systems trivialized by discrete isogenies to $G$, this is not the right perspective if one wishes to geometrize characters of smooth commutative group schemes, such as étale commutative group schemes.
-Indeed, quasicharacter sheaves on étale commutative group schemes that are trivialized by discrete isogenies are invisible to the trace of Frobenius.
-
-Having understood quasicharacter sheaves on commutative smooth group schemes over $\FF_q$ in two extreme cases -- connected algebraic groups and étale commutative group schemes -- we turn to the general case.
-Remarkably, we find that the general case can be understood from these two extreme cases, using the component group sequence
-\begin{equation}
+%Indeed, quasicharacter sheaves on \'etale commutative group schemes that are trivialized by discrete isogenies are invisible to the trace of Frobenius.
+
+Having understood quasicharacter sheaves on commutative smooth group schemes over $\Fq$ in two extreme cases --
+connected commutative algebraic groups and \'etale commutative group schemes -- we turn to the general case, using the component group sequence
+\[
 0 \to G^0 \to G \to \pi_0(G) \to 0.
-\end{equation}
-The main result of the paper uses this sequence to find $\QCiso{G}$ by situating it in a canonical short exact sequence
-\begin{equation}
-0 \to \Hh^2(\pi_0(\bG),\EEx)^{\Weil{}} \to \QCiso{G} \to \Hom(G(\FF_q),\EEx) \to 0.
-\end{equation}
-We remark that $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ is non-trivial even for some commutative algebraic groups.
-We also illuminate the nature of the category $\QC(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing that 
-\begin{equation}
+\]
+Using pullbacks of quasicharacter sheaves (\S\ref{ssec:Frob}), we obtain a diagram
+\[
+  \begin{tikzcd}[row sep=20, column sep=20]
+    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
+    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
+    0 \rar & \pi_0(G)(\Fq)^* \rar & G(\Fq)^* \rar & G^0(\Fq)^* \rar & 0.
+  \end{tikzcd}
+\]
+The rows of this diagram are exact (\S\S\ref{ssec:restriction},\ref{ssec:component}), so we may apply the snake lemma to prove the main theorem of the paper,
+\begin{theorem*}[{Thm. \ref{thm:snake}}]
+If $G$ is a smooth commutative group scheme over $\Fq$ then
+\[
+\TrFrob{G} : \QCiso{G} \to G(\Fq)^*
+\]
+is surjective with kernel $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
+\end{theorem*}
+We also illuminate the nature of the category $\QC(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing
+\begin{theorem*}[{Thm. \ref{thm:autornaught}}]
+If $G$ is a smooth commutative group scheme over $\Fq$ then
+\[
 \Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx),
-\end{equation}
-canonically, for all quasicharacter sheaves $\qcs{L}$ on $G$.
-
-\subsection{Applications over local fields}
-
-As indicated above, our interest in the function--sheaf dictionary for smooth commutative group schemes over finite fields comes from an application to $p$-adic representation theory. 
-We found, however, that this application applies to all local fields $K$ with finite residue field $\Fq$ and all connected commutative algebraic groups $X_K$ over $K$ that do not contain a subgroup of type $\mathbb{G}_\text{a}$, such as Abelian varieties, unipotent $K$-wound groups, and of course, algebraic tori.
-Such algebraic groups $X_K$ always admit a Neron model $X$ over $R$, the ring of integers of $K$.
-In this paper we show that quasicharacters of $X_K$ are geometrized and categorified by quasicharacter sheaves on the
-Greenberg transform $\Gr_R(X)$ of the N\'eron model $X$; although not locally of finite type, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and also a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
-This allows us to adapt our work on quasicharacter sheaves to construct a category $\QC(X_K)$ of quasicharacter sheaves for $X_K$, which are certain sheaves on $\Gr_R(X)\times_{\Spec{\Fq}} \Spec{\bFq}$, with extra structure.
-The ability to generalize the function--sheaf dictionary to non-connected group schemes, of which the component group of the special fibre of the Néron model $X$ is an important example, plays a crucial role in this application
-since these group schemes are not connected in general.
-
-Specializing to the case when $X_K$ is an algebraic tori $T$ over $K$, and writing $\underline{T}$ for the Neron model $X$ in this case, this paper gives a canonical short exact sequence 
-\begin{equation}
-0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{T} \to \Hom_\text{qc}(T(K),\EEx) \to 0,
-\end{equation}
-where $\Hom_\text{qc}(T(K),\EEx)$ denoted the group of quasicharacters of $T(K)$.
-We further show that automorphism groups in the $\QC(\Gr_R(\underline{T}))$ are given, for every quasicharacter sheaf $\qcs{F}$ on $\Gr_R(X)$, by
-\begin{equation}
-\Aut(\qcs{F}) \iso (\check{T}_\ell)^{\Weil{K}}
-\end{equation}
+\]
+for all quasicharacter sheaves $\qcs{L}$ on $G$.
+\end{theorem*}
+
+As indicated above, our interest in the function-sheaf dictionary for smooth commutative group schemes
+over finite fields comes from an application to $p$-adic representation theory,
+specifically to quasicharacters (\S\ref{ssec:quasicharacters}) of $p$-adic tori.
+However, we found that our method of passing from $p$-adic tori to group schemes over $\Fq$ applies more generally to
+any local field $K$ with finite residue field $\Fq$ and any commutative algebraic group $X_K$ that admits a N\'eron model $X$.
+This class of groups includes abelian varieties and unipotent $K$-wound groups in addition to the tori we initially considered.
+In this paper we show that quasicharacters of $X(K)$ are geometrized and categorified by quasicharacter sheaves on the
+Greenberg transform $\Gr_R(X)$ of the N\'eron model $X$.
+Although not locally of finite type, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and also a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
+This structure allows us to adapt our work on quasicharacter sheaves to construct (\S\ref{ssec:qc_on_GN}) a category $\QC(X_K)$
+of quasicharacter sheaves for $X_K$, which are certain sheaves on $\Gr_R(X)\times_{\Spec{\Fq}} \Spec{\bFq}$, with extra structure.
+The ability to generalize the function-sheaf dictionary to non-connected group schemes plays a crucial role in this application.
+
+Having defined quasicharacter sheaves for groups over $K$ and $\Fq$, we consider how
+these categories are related as $K$ and $\Fq$ vary.  We describe (\S\ref{ssec:basechange}) functors between categories
+of quasicharacter sheaves that model restriction and norm homomorphisms of character groups $G(k')^* \to G(k)^*$ and $G(k)^* \to G(k')^*$,
+and describe how quasicharacter sheaves behave under Weil restriction (\S\ref{ssec:wrK}).  We also give (\S\ref{ssec:transfer})
+a categorical version of a result of Chai and Yu \cite{chai-yu:01a},
+relating quasicharacter sheaves for tori over different local fields, even local fields
+with different characteristic.
+
+Specializing to the case that $X = T$ is the N\'eron model of an algebraic torus over $K$ (\S\ref{ssec:qc_tori}), 
+we give a canonical short exact sequence 
+\[
+0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{T_K} \to \Hom_\text{qc}(T(K),\EEx) \to 0,
+\]
+where $\Hom_\text{qc}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
+We further show that automorphism groups in $\QC(T_K)$ are given, for every quasicharacter sheaf $\qcs{F}$ for $T_K$, by
+\[
+\Aut(\qcs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
+\]
 where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
-%We also use quasicharacter sheaves to categorify the transfer of quasicharacters of tori between characteristic $0$ and characteristic $p$ local fields.
 
 By any measure, there are more quasicharacter sheaves for $T$ than quasicharacters of $T(K)$.  
-%\todo{Maybe move this from the introduction into the body of the paper somewhere.}
-In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization of complete Langlands parameters for $p$-adic groups as equivariant perverse sheaves on Vogan varieties and, in the process, is lead to study the representations of all the pure rational forms of the $p$-adic group simultaneously.
-A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group.
-Indeed, he has suggested to us that our category of quasicharacters for $T$ may be tied to characters of all the pure rational forms of $T$.
-
-\subsection{Comparison with character sheaves}
-
-The process of creating a category from the group of quasicharacters of a $p$-adic  torus, as explained above, informs our choice of the term quasicharacter sheaf in this paper.
+In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization of complete Langlands parameters for $p$-adic groups 
+and, in the process, is led to study the representations of all the pure rational forms of the $p$-adic group, simultaneously.
+A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group \cite{bernstein:vogan_conference}.
+Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to quasicharacters of all the pure rational forms of $T$.
+
+The process of creating a category from the group of quasicharacters of a $p$-adic  torus informs our choice of the term quasicharacter sheaf in this paper.
 We also want to situate our terminology in a historical context.
@@
 in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
-The interesting new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in this context.
-
-\subsection{Structure of the paper}
-
-We close the introduction with an overview of the structure of this paper.
-After setting some basic notation in Section~\ref{sec:notation},
-in Section~\ref{sec:category} we define the category of quasicharacter sheaves.
-Section~\ref{sec:Frob} introduces the trace of Frobenius homomorphism $\TrFrob{G} : \QCiso{G} \to \Hom(G(\FF_q), \EEx)$.
-We also define pullbacks of quasicharacter sheaves along morphisms of group schemes.  Applying pullbacks to the component group
-sequence for $G$ yields the diagram
- \begin{equation} \label{eq:intro-snake}
-  \begin{tikzcd}[row sep=20]
-    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
-    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
-    0 \rar & \pi_0(G)(\FF_q)^* \rar & G(\Fq)^* \rar & G^0(\FF_q)^* \rar & 0,
-  \end{tikzcd}
-  \end{equation}
-which is central to the proof of Theorem~\ref{thm:snake}.  Much of Sections~\ref{sec:etale}, \ref{sec:disc-isog} and \ref{sec:main}
-are devoted to proving that the rows of \eqref{eq:intro-snake} are exact and determining the kernels and cokernels of the vertical maps.
-
-Section~\ref{sec:etale} is devoted to the left-most vertical morphism in \eqref{eq:intro-snake}: studying $\TrFrob{G}$ for $G$ \'etale.  We begin by giving a reinterpretation of
-$\QC(G)$ in this case using stalks.  After a brief review of the Hochschild-Serre spectral sequence in Section~\ref{ssec:E},
-we define in Section~\ref{ssec:S} an isomorphism $S_G$ from $\QCiso{G}$ to the second cohomology of the total space of the spectral sequence
-\[
-E_2^{p,q} \ceq \Hh^p(\Weil{}, \Hh^q(\bG, \EEx)) \Rightarrow \Hh^{p+q}(\Weil{} \ltimes \bG, \EEx).
-\]
-Paired with the short exact sequence
-\[
-  0 \to \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to \Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to 0
-\]
-arising from the spectral sequence, the isomorphism $S_G$ allows us to describe the kernel and cokernel of $\TrFrob{G}$ in Section \ref{ssec:SandT}.
-We close our discussion of \'etale $G$ with a description, in Section~\ref{ssec:mor-etale}, of $\Hom(\qcs{L},\qcs{L}')$ for $\qcs{L}, \qcs{L}' \in \QC(G)$.
-
-Section~\ref{sec:disc-isog} focuses on the right-hand side of \eqref{eq:intro-snake},
-giving descriptions of quasicharacter sheaves that are particularly useful when $G$ is connected.  In Section \ref{ssec:descentG}
-we consider quasicharacter sheaves that arise via base change to $\bFq$ from local systems on $G$, and in Section \ref{ssec:discrete_isogenies}
-those that arise via pushforward from a constant sheaf along a discrete isogeny $H \to G$.  When $G$ is connected,
-we show in Section~\ref{ssec:connected} that every quasicharacter sheaf can be described in both of these ways.
-We also show that $\TrFrob{G}$ is an isomorphism in this case.
-
-In Section~\ref{sec:main} we prove that the rows of \eqref{eq:intro-snake} are exact and
-use the snake lemma to determine the kernel and cokernel of $\TrFrob{G}$ for general $G$.
-We show that $\QCiso{G^0} \to \QCiso{G}$ is surjective in Section~\ref{ssec:restriction} and
-that the remainder of the top row of \eqref{eq:intro-snake} is exact in Section~\ref{ssec:component}.
-We put it together in Theorem~\ref{thm:snake} of Section~\ref{ssec:snake}, showing that $\TrFrob{G}$
-is surjective with kernel $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$.  Having described the isomorphism classes of objects,
-in Theorem~\ref{thm:autornaught} of Section~\ref{ssec:qcmor} we show that
-\[
-\Aut(\qcs{L}) \cong \Hom(\pi_0(\bG)_{\Weil{}}, \EEx)
-\]
-and that every morphism is either trivial or an isomorphism.  We conclude in Section~\ref{sec:basechange} by
-giving functorial versions of the restriction and norm homomorphisms $G(k')^* \to G(k)^*$ and $G(k)^* \to G(k')^*$
-and describing how quasicharacter sheaves behave under Weil restriction.
-
-Section~\ref{sec:applications} gives applications of quasicharacter sheaves to commutative algebraic groups over local fields.
-We begin with a review of N\'eron models and of the Greenberg transform in Section~\ref{ssec:rev_Greenberg}.  We then
-define, in Section~\ref{ssec:qc_on_GN}, a quasicharacter sheaf for an algebraic group over a local field to be a quasicharacter
-sheaf on the Greenberg transform of the N\'eron model.  In Theorem~\ref{thm:QCXK}, we translate our results from earlier sections
-to give a description of the isomorphism classes and automorphism groups
-in the category of quasicharacter sheaves on such an algebraic group.
-We specialize to $p$-adic tori in Section~\ref{ssec:qc_tori}, and discuss
-Weil restriction and base change over local fields in Section~\ref{ssec:wrK}.
-Finally, we give a categorical version of a result of Chai and Yu \cite{chai-yu:01a},
-relating quasicharacter sheaves for tori over different local fields, even local fields
-with different characteristic.
-
-%\begin{acknowledgements}
-\subsection{Acknowledgments}
-We thank Masoud Kamgarpour, Pramod Achar, and Hadi Salmasian
-for allowing us to hijack much of our Research in Teams meeting at BIRS into a discussion of
-quasicharacter sheaves; their knowledge and help have been invaluable.
-We thank Takashi Suzuki for some very helpful observations and suggestions, including those related to our use of the Hochschild-Serre spectral sequence.
-We thank Joseph Bernstein for suggesting a connection between our category of quasicharacter sheaves on $G$ and his sheaves on the stacky classifying space of $G$.
-Finally, we gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
-and the National Science and Engineering Research Council,
-as well the hospitality of the Banff International Research Station during our week-long stay in May 2012.
-
-%\end{acknowledgements}
-
-\tableofcontents
-
-\section{The category of quasicharacter sheaves}
-
-\subsection{Notations}\label{sec:notation}
+The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in that context.
+
+\medskip
+\noindent\textbf{Acknowledgements.\ } {Pramod Achar, Masoud Kamgarpour and Hadi Salmasian
+allowed us to hijack much of a Research in Teams meeting at the Banff International Research Station into a discussion of
+quasicharacter sheaves.  We thank them for their kindness, knowledge and invaluable help.
+We thank Takashi Suzuki for some very helpful observations and suggestions, especially related to our use of the Hochschild-Serre spectral sequence.
+We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and drawing our attention to their result on Weil restriction and the Greenberg transform.
+We thank Joseph Bernstein for suggesting a connection between our category of quasicharacter sheaves for $p$-adic tori and quasicharacters of its pure rational forms.}
+
+{Finally, we gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences and the National Science and Engineering Research Council (Canada), as well the hospitality of the Banff International Research Station during a Research in Teams program.}
+
+\section{The category of quasicharacter sheaves} \label{sec:category}
+
+\subsection{Notations}\label{ssec:notation}
 
@@
 
-For any group $A$, we will write $A^*$ for the dual group $\Hom_\text{grp}(A, \EEx)$.
-
-\subsection{The category of quasicharacter sheaves}\label{sec:category}
+For any abelian group $A$, we will write $A^*$ for the dual group $\Hom(A, \EEx)$.
+
+\subsection{Quasicharacter sheaves}\label{ssec:category}
 
@@
 
-The category $\QC(G)$ of quasicharacter sheaves on $G$ is a rigid monoidal category
+Category $\QC(G)$ is a rigid monoidal category
 \cite{etingof:09a}*{\S1.10} under the tensor product
-$\qcs{L} \otimes \qcs{L'} \ceq (\gqcs{L}\otimes\gqcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
+$\qcs{L} \otimes \qcs{L'}$ defined by $(\gqcs{L}\otimes\gqcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
 with duals given by applying the sheaf hom functor
@@
 
-We will describe the group $\QCiso{G}$ in Theorem \ref{thm:snake}
-and the sets $\Hom(\qcs{L},\qcs{L}')$ in Theorem \ref{thm:autornaught}; in this way we provide a complete description of the category $\QC(G)$.
+We will describe the group $\QCiso{G}$ in Theorem~\ref{thm:snake}
+and the sets $\Hom(\qcs{L},\qcs{L}')$ in Theorem~\ref{thm:autornaught}; in this way we provide a complete description of the category $\QC(G)$.
 %
 In the meantime, we close this section with an elementary observation about $\Hom(\qcs{L},\qcs{L}')$.
+We call a morphism of sheaves \emph{trivial} if it is zero on every stalk.
 
@@
 Suppose $\rho \in \Hom(\qcs{L},\qcs{L}')$.
-We prove the lemma by considering the linear transformations $\rho_{\bar g} : \gqcs{L}_{\bar g} \to \gqcs{L}_{\bar g}$ at the stalks above geometric points ${\bar g}$ on $G$ and showing that, either each $\rho_{\bar g}$ trivial or each $\rho_{\bar g}$ is an isomorphism.
-(This idea is expanded upon in Section~\ref{sec:stalks}.)
+We prove the lemma by considering the linear transformations $\brho_{\bar g} : \gqcs{L}_{\bar g} \to \gqcs{L}_{\bar g}$ at the stalks above geometric points ${\bar g}$ on $G$ and showing that, either each $\brho_{\bar g}$ trivial or each $\brho_{\bar g}$ is an isomorphism.
+(This idea is expanded upon in Section~\ref{ssec:stalks}.)
 Let ${\bar e}$ be the geometric point above the identity $e$ for $G$ determined by our choice of algebraic closure $\bFq$ of $\Fq$.
-If $\rho_{\bar e} = 0$ then the second diagram in \ref{QC.4} implies that $\rho_{\bar g} = 0$ for all ${\bar g}$, in which case $\rho$ is trivial.
-On the other hand, if $\rho_{\bar e}$ is nontrivial then the second diagram in \ref{QC.4}  implies that $\rho_{\bar g}$ is nontrivial for all ${\bar g}$ and thus an isomorphism, since the stalk of quasicharacter sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
-\end{proof}
-
-\subsection{Trace of Frobenius}\label{sec:Frob}
-
-In this section we introduce two tools which will help us understand isomorphism classes of objects in $\QC(G)$: the trace of Frobenius map $\QCiso{G} \to G(k)^*$ and the pullback functor $\QC(G) \to \QC(H)$ associated to a morphism $H \to G$.
-
-%A Weil sheaf $(\gqcs{L},\phi)$ on $G$ may be interpreted as a constructible $\ell$-adic sheaf $\gqcs{L}$ on $\bG$ together with an action of the Weil group $\Weil{}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ on $\bG$.
-%We now briefly review this point of view for later use in Section~\ref{sec:basechange}; see also \cite{deligne:80a}*{Def.~1.1.10}.  If $w \ceq \Frob{}^n$ we write $w_G$ for $\Frob{G}^n$.
-%For each such $w$ we define an isomorphism $\varphi(w) : w_G^* \gqcs{L}\to \gqcs{L}$ by $\varphi(w) \ceq  \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi);$
-%these isomorphisms satisfy $\varphi(uv) = \varphi(v) \circ v_G^* \varphi(u)$ for $u,v\in \Weil{}$, and we have $\phi = \varphi(\Frob{})$.
-%If we further define $\varphi_1(w) \ceq (w_G)_*(\varphi(w)^{-1})$ then $\varphi_1(w) : (w_G)_* \gqcs{L}\to \gqcs{L}$ is an isomorphism and $\varphi_1(uv) = \varphi_1(u) \circ (u_G)_* \varphi_1(v)$ for $u,v\in \Weil{}$.
-%Thus the pair $(\gqcs{L},\varphi_1)$ almost satisfies the criteria for an action of $\Weil{}$ on $\gqcs{L}$ compatible with the action of $\Gal(\bFq/\Fq)$ in the sense of\cite{deligne:SGA4.5}*{Expos\'e XIII, 1.1}, failing only because $\Weil{}$ is not profinite.
-%As we will see in Corollary~\ref{cor:bounded-and-finite}, our use of $\Weil{}$ rather than $\Gal(\bFq/\Fq)$ allows quasicharacter sheaves to correspond to unbounded characters.
-
-%Observe that the rule $(\gqcs{L},\mu,\phi) \mapsto (\gqcs{L},\phi)$ defines a forgetful functor from quasicharacter
-%sheaves on $G$ to ($\ell$-adic) Weil sheaves on $G$ \cite{deligne:80a}*{Def.~1.1.10 (i)}.
-%
+If $\brho_{\bar e} = 0$ then the second diagram in \ref{QC.4} implies that $\brho_{\bar g} = 0$ for all ${\bar g}$, in which case $\rho$ is trivial.
+On the other hand, if $\brho_{\bar e}$ is nontrivial then the second diagram in \ref{QC.4}  implies that $\brho_{\bar g}$ is nontrivial for all ${\bar g}$ and thus an isomorphism, since the stalk of quasicharacter sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
+\end{proof}
+
+\subsection{Trace of Frobenius}\label{ssec:Frob}
+
+In this section we introduce two tools which will help us understand isomorphism classes of objects in $\QC(G)$: the map $\QCiso{G} \to G(k)^*$ given by trace of Frobenius and the pullback functor $\QC(G) \to \QC(H)$ associated to a morphism $H \to G$.
 
 Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
-determines a point geometric point $\bg$ fixed by $\Frob{G}$. 
-Together with the canonical isomorphism $(\Frob{G}^*\gqcs{L})_{\bg} \iso  \gqcs{L}_{\Frob{G}(\bg)}$, in this way the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gqcs{L}_{\bg}$; let $\trace(\phi_{\bg};\gqcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gqcs{L}_{\bg})$ and let $\trFrob{(\gqcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by
+determines a geometric point $\bg$ fixed by $\Frob{G}$. 
+Together with the canonical isomorphism $(\Frob{G}^*\gqcs{L})_{\bg} \iso  \gqcs{L}_{\Frob{G}(\bg)}$, the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gqcs{L}_{\bg}$.
+Let $\trace(\phi_{\bg};\gqcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gqcs{L}_{\bg})$ and let $\trFrob{(\gqcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by 
 \begin{equation}\label{trWeil}
-%\begin{equation}\label{trWeil}
 \trFrob{(\gqcs{L},\phi)}(g) \ceq \trace(\phi_{\bg};\gqcs{L}_{\bg}),
-%\end{equation}
 \end{equation}
@@
 Now suppose $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$.
-The isomorphism $\mu : \bm^* \gqcs{L} \to \LxL$ together with
+Then the isomorphism $\bm^* \gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$ and the diagram of
 \ref{QC.3} guarantee
@@
 \begin{proof}
-The only non-trivial part of the proof is to show that $\boxtimes : \QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)$
+The only non-trivial part of the proof is to show that 
+\[\boxtimes
+ : \QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)
+ \]
 is essentially surjective, so we will only address that point here.
-
+%
 Set $G \ceq G_1\times G_2$
@@
 Observe that $p_1\circ f = q_1 \circ r_1$ and $p_2 \circ f = q_2\circ r_2$.
-
-Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
-Set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$;
-by Lemma~\ref{lem:pullback}, $\qcs{L}_1$ a quasicharacter sheaf on $G_1$
+%
+Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$
+and set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$.
+By Lemma~\ref{lem:pullback}, $\qcs{L}_1$ is a quasicharacter sheaf on $G_1$
 and $\qcs{L}_2$ is a quasicharacter sheaf on $G_2$.
@@
 \end{equation}
-We have already observed that $m\circ f = \id_G$, so $f^* m^* \gqcs{L} = \gqcs{L}$.
-On the other hand, $f^*(\gqcs{L}\boxtimes \gqcs{L}) = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L}$
-by definition.  Since $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L}$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L}$
-we get that $f^*(\gqcs{L}\boxtimes \gqcs{L}) = \gqcs{L}_1\boxtimes \gqcs{L}_2$.
+We have already seen that $m\circ f = \id_G$, so $f^* m^* \gqcs{L} = \gqcs{L}$.  
+Since $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L} = r_1^* \gqcs{L}_1$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L} = r_2^*\gqcs{L}_2$,
+we have 
+\[
+f^*(\gqcs{L}\boxtimes \gqcs{L})  = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L} = \gqcs{L}_1\boxtimes \gqcs{L}_2.
+\]
 It follows that \eqref{eq:fm} gives an isomorphism $\gqcs{L} \to  \gqcs{L}_1\boxtimes \gqcs{L}_2$.
-It is a matter of routine to show that this morphism satisfies
-\ref{QC.3} as it applies here,
+It is routine to show that this morphism satisfies
+\ref{QC.4} as it applies here,
 from which it follows that we have exhibited an isomorphism
@@
 
-%\subsection{Morphisms of quasicharacter sheaves}\label{sec:mor}
-
 \section{Quasicharacter sheaves on \'etale commutative group schemes} \label{sec:etale}
 
-%\subsection{Quasicharacter sheaves, revisited}
-
-%\'Etale group schemes form a counterpoint to connected groups,
-%since the component group of a smooth commutative group scheme
-%is an \'etale group scheme \cite{vdGeer-Moonen:AbelianVarieties}*{III, \S 4}.
-%However, the function--sheaf dictionary is substantially different in the two cases.
-%To see why, we begin by specializing the definition of quasicharacter sheaves to the case
-%of étale commutative group schemes,
-%using the equivalence $G \mapsto G(\bFq)$
-%from the category of \'etale group schemes over $\Fq$ to the category of groups equipped
-%with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group.
-
-In this section we find a complete characterization of the category of quasicharacter sheaves on étale commutative group schemes over finite fields.
-
-\subsection{Stalks of quasicharacter sheaves}\label{sec:stalks}
-
-The equivalence $G \mapsto G(\bFq)$
+In this section we find a complete characterization of the category of quasicharacter sheaves on \'etale commutative group schemes over finite fields.
+
+\subsection{Stalks of quasicharacter sheaves}\label{ssec:stalks}
+
+The equivalence $G \mapsto G(\bFq)$,
 from the category of \'etale commutative group schemes over $\Fq$ to the category of commutative groups equipped
-with an action of $\Gal(\bFq/\Fq)$, continuous for the discrete topology on the group,
+with a continuous action of $\Gal(\bFq/\Fq)$,
 provides the following simple description of quasicharacter sheaves.
 %
-A quasicharacter sheaf $\qcs{L}$ on an étale commutative group scheme $G$ over $\Fq$ is:
+A quasicharacter sheaf $\qcs{L}$ on an \'etale commutative group scheme $G$ over $\Fq$ is:
 \begin{enumerate}
@@
    \begin{tikzcd}[column sep=40]
-    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{}(x)} \rar{\rho_{\Frob{}(x)}} & \gqcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
+    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{}(x)} \rar{\brho_{\Frob{}(x)}} & \gqcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
     &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-    & \arrow[swap]{d}{\mu_{x,y}} \gqcs{L}_{x+y} \rar{\rho_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x,y}} \\
-    \gqcs{L}_x \rar{\rho_x} & \gqcs{L'}_x
-    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\rho_x\otimes\rho_y} & \gqcs{L'}_x \otimes\gqcs{L'}_y
-   \end{tikzcd}
-  \]
-  both commute for all $x, y \in G(\bFq)$.
+    & \arrow[swap]{d}{\mu_{x,y}} \gqcs{L}_{x+y} \rar{\brho_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x,y}} \\
+    \gqcs{L}_x \rar{\brho_x} & \gqcs{L'}_x
+    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\brho_x\otimes\brho_y} & \gqcs{L'}_x \otimes\gqcs{L'}_y
+   \end{tikzcd}
+  \]
+  both commute, for all $x, y \in G(\bFq)$.
 \end{enumerate}
 
-We will see that $T_G : \QCiso{G} \to G(\Fq)^*$ may not provide complete
+We will see that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ may not provide complete
 information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not a connected algebraic group.
@@
 
-The zeroth page of the Hochschild-Serre spectral sequence is a double complex $E^{\bullet, \bullet}$ defined by
-\[
-E^{i,j} = C^i(\Weil{}, C^j(G(\bFq), \EEx)),
-\]
-The derivative of group cohomology yields two derivatives:
+The zeroth page of the Hochschild-Serre spectral sequence
+is a double complex $E^{\bullet, \bullet}$ defined by
+\[
+E^{i,j} = C^i(\Weil{}, C^j(G(\bFq), \EEx));
+\]
+see \cite{vakil:Algebraic_Geometry}*{\S 1.7}, expanding on \cite{weibel:Homological_Algebra}*{Ch 5 and \S 7.5}.
+The standard derivative on cochains yields two derivatives,
 \begin{align*}
-d_0 = d_G &: E^{i,j} \to E^{i,j+1} \\
-d_{\Weil{}} &: E^{i,j} \to E^{i+1,j}.
+d_G &: E^{i,j} \to E^{i,j+1} \quad \mbox{and} \\
+d_{\Weil{}} &: E^{i,j} \to E^{i+1,j};
 \end{align*}
-Combining these yields a derivative $d = d_G + (-1)^j d_{\Weil{}}$ on the total complex
+we use the first as the derivative $d_0$ on the zeroth page, and the second to induce $d_1$.
+Combining them also yields a derivative $d = d_G + (-1)^j d_{\Weil{}}$ on the total complex
 \[
@@
 
-\begin{proposition}
+\begin{proposition} In the spectral sequence defined above,
 \begin{enumerate}
-\item The second page is given by $E_2^{i,j} = \Hh^i(\Weil{}, \Hh^j(G(\bFq), \EEx))$,
-\item there is an isomorphism $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) \cong \Hh^n(E_G^\bullet)$,
-\item there is a filtration $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) = F_n \supset \cdots \supset F_0 \supset F_{-1} = 0$ where $F_i / F_{i-1} \cong E_{\infty}^{i, n-i}$.
+\item the second page is given by $E_2^{i,j} = \Hh^i(\Weil{}, \Hh^j(G(\bFq), \EEx))$,
+\item there is an isomorphism $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) \cong \Hh^n(E_G^\bullet)$, and
+\item there is a filtration $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) = F_n \supset \cdots \supset F_{-1} = 0$, with $F_i / F_{i-1} \cong E_{\infty}^{i, n-i}$.
 \end{enumerate}
 \end{proposition}
-%\todo{Is this a lemma? Is the corollary a proposition?}
 
@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:spectral_ses}
 There is a short exact sequence
  \[
-  \begin{tikzcd}
-    0 \arrow{r}
-    & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r}
-    & \Hh^2(E^\bullet_G) \arrow{r}
-    & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r}
-    & 0
-  \end{tikzcd}
+    0 \to
+    \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to
+    \Hh^2(E^\bullet_G) \to
+    \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to
+    0.
  \]
@@
 \begin{proposition} \label{prop:ses_desc}
+Consider the short exact sequence in Corollary~\ref{cor:spectral_ses}.
 \begin{enumerate}
-\item Every class $[\alpha\oplus\beta\oplus\gamma] \in \Hh^2({\bar G},\EEx)$ is cohomologous to one with $\gamma=0$.
+\item Every class $[\alpha\oplus\beta\oplus\gamma] \in \Hh^2(E^\bullet_G)$ is cohomologous to one with $\gamma=0$.
 \item The map $\Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx))$ is given by $[\alpha\oplus\beta\oplus 0] \mapsto [\beta]$.
@@
 
-The latter two claims follow from tracing through the definition of latter pages in the spectral sequence; see Vakil \cite{} for example \todo{update reference}.
+The latter two claims follow from tracing through the definition of latter pages in the spectral sequence.
 \end{proof}
@@
 \[\alpha\oplus \beta \in Z^2(E^\bullet_G).\]
-Although the cocycle $\alpha\oplus \beta$ is not well defined by $\qcs{L}$, its class in $Z^2(E^\bullet_G)$ is.
+Although the cocycle $\alpha\oplus \beta$ is not well defined by $\qcs{L}$, its class in $\Hh^2(E^\bullet_G)$ is.
 To see this, let $\{ v'_x \in \gqcs{L}_x^\times \tq x \in {\bar G}\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$ be defined by $\qcs{L}$ and this choice, as above.
-Now let $\delta \in C^0(\Weil{},C^1({\bar G},\EEx))$ be the additive version of the function $d : {\bar G}\to \EEx$ defined by $v'_x = d(x) v_x$.
-Then, chasing through \ref{QC.2} and \ref{QC.3} we find
+Now let $\delta \in C^0(\Weil{},C^1({\bar G},\EEx))$ correspond to the function $d : {\bar G}\to \EEx$ defined by $v'_x = d(x) v_x$.
+Chasing through \ref{QC.2} and \ref{QC.3}, we find
 \[
@@
 \begin{proof}
-We first show that $S_G$ is injective.  Suppose $\qcs{L} \in \QCiso{G}$ with $S_G(\qcs{L}) = [\alpha \oplus \beta] = 0$,
-so that $\alpha \oplus \beta = d\rho$ for some $\rho \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
-For each $x\in {\bar G}$, define $\rho_x : \gqcs{L}_x \to \EEx$ by $v_x \mapsto \rho(x)$.
-Then the indexed set of isomorphisms $\{ \gamma_x : \gqcs{L}_x \to \EE \tq x\in {\bar G}\}$
+Suppose $[\qcs{L}] \in \QCiso{G}$ with $S_G([\qcs{L}]) = [\alpha \oplus \beta] = 0$,
+so that $\alpha \oplus \beta = d\sigma$ for some $\sigma \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
+For each $x\in {\bar G}$, define $\sigma_x : \gqcs{L}_x \to \EE$ by $\sigma_x : v_x \mapsto \sigma(x)$.
+Then the indexed set of isomorphisms $\{ \sigma_x : \gqcs{L}_x \to \EE \tq x\in {\bar G}\}$
 defines an isomorphism $\qcs{L} \to (\EE)_G$.
@@
 $b = \beta(\Frob{}) \in C^1({\bar G},\EEx)$, which are related to $\alpha$ and $\beta$ as above.
-Set $\gqcs{L}_x = \EEx$, define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes\gqcs{L}_y$
-by $\mu_{x,y}(1) = a(x,y) 1\otimes 1$ and $\phi_x : \gqcs{L}_{\Frob{G}(x)} \to \gqcs{L}_x$ by $\phi_x(1)= b(x)$.
+Set $\gqcs{L}_x = \EE$, define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes\gqcs{L}_y$
+by $\mu_{x,y}(1) = a(x,y) (1\otimes 1)$ and $\phi_x : \gqcs{L}_{\Frob{G}(x)} \to \gqcs{L}_x$ by $\phi_x(1)= b(x)$.
 Then \ref{qc.1} holds since $d_G \alpha =0$ and \ref{qc.2} holds since $d_{\Weil{}}\alpha =d_G \beta$.
 Tracing the construction backward, we have defined a quasicharacter sheaf $\qcs{L}$ on $G$ with
-$S_G(\qcs{L}) = [\alpha\oplus\beta\oplus\gamma]$, showing that $S_G$ is surjective.
-\end{proof}
-
-\subsection{Objects, when $G$ is etale}\label{ssec:SandT}
-
-In this section we find the relationship between the group homomorphisms $\TrFrob{G}$ and $S_G$, and use this to find the group $\QCiso{G}$ when $G$ is an étale commutative group scheme over $\Fq$.
+$S_G(\qcs{L}) = [\alpha\oplus\beta\oplus 0]$, showing that $S_G$ is surjective.
+\end{proof}
+
+\subsection{Objects in the \'etale case}\label{ssec:SandT}
+
+In this section we fit the group homomorphisms $\TrFrob{G}$ and $S_G$ into a commutative diagram, determining the kernel and cokernel of the homomorphism $\TrFrob{G} : \QCiso{G} \to G(k)^*$ when $G$ is an \'etale commutative group scheme over $\Fq$.
 
@@
 \begin{lemma} \label{lem:dual-inv}
-Let $X$ be an abelian group equipped with an action of $\Weil{}$.
- Then
+Let $X$ be an abelian group equipped with an action of $\Weil{}$.  Then
 \begin{align*}
- (X^*)_{\Frob{}} &\to (X^{\Frob{}})^* \\
- [f] &\mapsto f|_{X^{\Frob{}}}
+ (X^*)_{\Weil{}} &\to (X^{\Weil{}})^* \\
+ [f] &\mapsto f|_{X^{\Weil{}}}
 \end{align*}
@@
 \begin{proposition}\label{prop:sur_etale}
-If $G$ is \'etale then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective.
+If $G$ is \'etale, then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective
+and split.
 \end{proposition}
@@
 Pick $\chi \in G(\Fq)^*$. 
-By Lemma~\ref{lem:dual-inv}, there is some $b\in G(\bFq)^*$ such that $b\vert_{G(\Fq)^*} = \chi$.
+Let $[\beta]\in \Hh^1(\Weil{},\bG^*)$ be the class corresponding to $\chi$ under Lemma~\ref{lem:dual-inv}.
+Every representative cocycle $\beta \in Z^1(\Weil{},\bG^*)$ determines a homomorphism $\beta(\Frob{}) : G(\bFq)\to \EEx$ such that $\beta(\Frob{})\vert_{G(\Fq)} = \chi$.
 Set $\gqcs{L}_x = \EE$ for every $x\in G(\bFq)$.
 Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$ and
-$\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = b(x)$.
-Since $b : G(\bFq) \to \EEx$ is a group homomorphism,
-condition \eqref{nohom} is satisfied with $a =1$ and $\qcs{L} = (\gqcs{L}, \mu, \phi)$
+$\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = \beta(\Frob{})(x)$.
+Since $\beta(\Frob{}) : G(\bFq) \to \EEx$ is a group homomorphism,
+condition \eqref{nohom} is satisfied with $a =1$.
+So $\qcs{L} = (\gqcs{L}, \mu, \phi)$
 is a quasicharacter sheaf with $\trFrob{\qcs{L}} = \chi$.
+This shows that $\TrFrob{G}$ is surjective.
+
+Now let $\beta' \in Z^1(\Weil{},\bG^*)$ be another representative for $[\beta]$
+so $\beta-\beta' = d_{\Weil{}} \delta$ for some $\delta \in C^0(\Weil{},\bG^*)$ defining $d \in \Hom(G(\bFq),\EEx)$.
+Let $\qcs{L}'$ be the quasicharacter sheaf on $G$ defined by $\beta'$, as above.
+For each $x\in G(\bFq)$, define $\brho_x :\qcs{L}_x\to \qcs{L}'_x$ by $\brho_x(1) = d(x)$.
+The collection of isomorphisms $\{ \brho_x \tq x\in G(\bFq)\}$ satisfies condition~\ref{qc.4}, so it defines a morphism $\rho : \qcs{L}\to \qcs{L}'$, which is clearly an isomorphism. 
+%
+We have now defined a section of $\TrFrob{G}$.
+
+Now suppose $\chi_1, \chi_2 \in G(\Fq)^*$.
+Pick cocycles $\beta_1,\beta_2\in Z^1(\Weil{},\bG^*)$ and construct quasicharacter sheaves $\qcs{L}_1$ and $\qcs{L}_2$ on $G$ as above.
+Since $\qcs{L}_1\otimes \qcs{L}_2$ is exactly the quasicharacter sheaf built from the cocycle $\beta_1\cdot \beta_2$, and since $\trFrob{\qcs{L}_1\otimes \qcs{L}_2} = \trFrob{\qcs{L}_1}\cdot \trFrob{\qcs{L}_2}$, the section of $\TrFrob{G}$ defined here is a homomorphism.
 \end{proof}
@@
 \begin{proof}
-This result follows easily from Propositions~\ref{prop:ses_desc} and \ref{prop:sur_etale}.
-\end{proof}
-
-\subsection{Morphisms}\label{ssec:mor-etale}
-
-Most of this paper focuses on the question of determining the isomorphism classes of objects; a complete understanding of the morphisms in $\QC(G)$ also requires a description of the automorphisms of an arbitrary quasicharacter sheaf $\qcs{L}$.
+This result follows from Propositions~\ref{prop:ses_desc}, \ref{prop:SGiso} and \ref{prop:sur_etale}.
+\end{proof}
+
+\subsection{Morphisms in the \'etale case}\label{ssec:mor-etale}
+
+While most of this paper focuses on the question of determining the isomorphism classes of objects, a complete understanding of the morphisms in $\QC(G)$ also requires a description of the automorphisms of an arbitrary quasicharacter sheaf $\qcs{L}$.
 
 \begin{proposition}\label{prop:autornaught_etale}
-Let $G$ be an étale commutative group scheme over $\Fq$.
+Let $G$ be an \'etale commutative group scheme over $\Fq$.
 If $\qcs{L}$ and $\qcs{L}'$ are quasicharacter sheaves on $G$ then
@@
 Now suppose $\rho \in \Aut(\qcs{L})$.
-The second diagram in \ref{qc.4} shows that the association $x \mapsto \rho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{qc.4} shows that it factors through $G(\bFq)_{\Weil{}}$.
-Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism then defining $\rho_x$ as multiplication by $\rho(x)$ will satisfy the two diagrams.
+The second diagram in \ref{qc.4} shows that the association $x \mapsto \brho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{qc.4} shows that it factors through $G(\bFq)_{\Weil{}}$.
+
+Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism, then defining $\brho_x$ as multiplication by $\rho(x)$ will define a morphism $\gqcs{L} \to \gqcs{L}'$ satisfy the two diagrams in \ref{qc.4}.
+
 Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the resulting bijection is actually a group isomorphism.
@@
 
-%Note that Proposition~\ref{prop:autornaught_etale} tells us that if $G$ is an étale commutative group scheme over $\Fq$ then every hom-set is either trivial or $\{ 0 \} \cup \left(G(\bFq)_{\Weil{}}\right)^*$, non-canonically.
-
-\section{Quasicharacter sheaves defined by discrete isogenies} \label{sec:disc-isog}
+\section{Quasicharacter sheaves on connected commutative algebraic groups} \label{sec:disc-isog}
 
@@
 Let $\bQC(G)$ be the category of pairs $(\qcs{E},\mu_\qcs{E})$
-where $\qcs{E}$ an $\ell$-adic local system on $G$ of rank~one,
+where $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank-one,
 equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes \qcs{E}$
-satisfying the analogue of \ref{QC.1} on $G$;
+satisfying the analogue of \ref{QC.2} on $G$;
 morphisms in $\bQC(G)$ are defined as in the second part of
-\ref{QC.3}.
+\ref{QC.4}.
 \end{definition}
 
-Category $\bQC(G)$ is a rigid monoidal category in the obvious way.
+We put a rigid monoidal structure on $\bQC(G)$ in the same way as for $\QC(G)$.
 
 \begin{proposition}\label{prop:BG}
-Extension of scalars defines a full and faithful functor $B_G : \bQC(G) \to \QC(G)$.
+Extension of scalars defines a full and faithful functor
+\[
+B_G : \bQC(G) \to \QC(G).
+\]
 \end{proposition}
@@
 \begin{proof}
+ Suppose $(\qcs{E},\mu_\qcs{E})$ in an object of $\bQC(G)$.
  Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Suppose $(\qcs{E},\mu_\qcs{E})$ in an object in $\bQC(G)$.
- Then $\qcs{E}$ is an $\ell$-adic constructible sheaf on $G$ and
- $b_G^* \qcs{E}$ comes equipped with an isomorphism
- $\phi_\qcs{E} : \Frob{G}^* b_G^*\qcs{E} \to b_G^* \qcs{E}$.
- The functor $\qcs{E} \mapsto (b_G^* \qcs{E},\phi_\qcs{E})$
- from $\ell$-adic constructible sheaves on $G$ to $\ell$-adic constructible sheaves on $G$
- is full and faithful \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}}.
- This functor preserves local constancy, so takes local systems to local systems.
- Set $\mu \ceq b_{G\times G}^*\mu_\qcs{E}$; clearly, this satisfies \ref{QC.2}
- with $b_G^*\qcs{E}$ playing the role of $\gqcs{L}$.
- Moreover, $\phi_\qcs{E}$ is compatible with $\mu_\qcs{E}$ in the sense of \ref{QC.3}.
- This construction defines the functor $B_G : (\qcs{E},\mu_\qcs{E}) \mapsto (b_G^*\qcs{E},b_{G\times G}^*\mu_\qcs{E}, \phi_\qcs{E})$
- and also shows that it is full and faithful.
+ Set $\gqcs{L} = b_G^* \qcs{E}$. 
+ The functor $b_G^*$ takes local systems on $G$ to local systems on $\bG$.
+ The local system $\gqcs{L}$ comes equipped with an isomorphism
+ $\phi: \Frob{G}^* \gqcs{L} \to \gqcs{L}$.
+ The resulting functor from local systems on $G$ to Weil local systems on $\bG$, given on objects by $\qcs{E} \mapsto (\gqcs{L},\phi)$, 
+ is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} and \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}.
+ The isomorphism $\mu \ceq b_{G\times G}^*\mu_\qcs{E}$ satisfies \ref{QC.2}
+ for $\gqcs{L}$ and $\phi$ is compatible with $\mu$ in the sense of \ref{QC.3}.
+ This construction defines the functor $B_G : \bQC(G) \to \QC(G)$ given on objects by $(\qcs{E},\mu_\qcs{E}) \mapsto (\gqcs{L},\mu, \phi)$, as defined here. 
+ Because morphisms in $\bQC(G)$ and $\QC(G)$ are morphisms of local systems on $G$ and $\bG$, respectively, satisfying condition~\ref{QC.4}, this functor is also full and faithful.
 \end{proof}
@@
 
-A finite, étale, surjective morphism $H\to G$ of smooth group schemes over $\Fq$ for which the action of $\Gal(\bFq/\Fq)$ on the kernel is trivial is called a {\it discrete isogeny}.
+A finite, \'etale, surjective morphism $H\to G$ of smooth group schemes over $\Fq$ for which the action of $\Gal(\bFq/\Fq)$ on the kernel is trivial is called a {\it discrete isogeny}.
 
 \begin{proposition}\label{prop:finite}
-Let $f: H \to G$ be a discrete isogeny; let $A$ be the kernel of $f$.
+Let $f: H \to G$ be a discrete isogeny and let $A$ be the kernel of $f$.
 Let $V$ be a $1$-dimensional representation of $A$ 
@@
 \begin{proof}
-Let $f$, $A$, $V$ and $\psi$ be as above; set $\qcs{E} = (f_! V_H)_\psi$.
-It is clear that $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank one.
-We must show that comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
-To do this we use étale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$. 
+Let $f$, $A$, $V$ and $\psi$ be as above and set $\qcs{E} = (f_! V_H)_\psi$.
+Since $A$ is abelian, $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank one.
+We must show that $\qcs{E}$ comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
+To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$ {\it cf.\ } \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}.
 In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
@@
 
-\subsection{Quasicharacter sheaves on connected commutative algebraic groups}\label{ssec:connected}
+\subsection{The classical function-sheaf dictionary revisited}\label{ssec:connected}
 
@@
   an equivalence between the category of $\ell$-adic Weil local systems on $G$ and
-  $\ell$-adic representations of $\W(G,\bg)$ \cite{deligne:80a}*{1.1.12}.
+  $\ell$-adic representations of $\Weil{}(G,\bg)$ \cite{deligne:80a}*{1.1.12}.
 
   Now let $(\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$
-  and let $\rho : \W(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$.
-  Composing with the splitting $\Weil{} \to \W(G,\bg)$ yields an $\ell$-adic character
-  $\rho_g : \Weil{} \to \EEx$, which is the same as the Trace of Frobenius defined in Section~\ref{sec:Frob}, for every $\Fq$ rational point $g$ on $G$:
+  and let $\lambda : \Weil{}(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$.
+  Composing with the splitting $\Weil{} \to \Weil{}(G,\bg)$ yields an $\ell$-adic character
+  $\lambda_g : \Weil{} \to \EEx$, which is the same as the Trace of Frobenius defined in Section~\ref{ssec:Frob}, for every $\Fq$ rational point $g$ on $G$:
   $
-  \rho_g(\Frob{}) =  \trFrob{\qcs{L}}(g).
+  \lambda_g(\Frob{}) =  \trFrob{\qcs{L}}(g).
   $
@@
   On the other hand, we have already seen that $\trFrob{\qcs{L}} : G(\Fq) \to \EEx$
-  is a group homomorphism. Since $G$ is an algebraic group over $\Fq$, it is a
-  variety over $\Fq$ and thus $G(\Fq)$ is finite.
-  Therefore $\trFrob{\qcs{L}}(g) = \rho_g(\Frob{})$ is a root of unity
+  is a group homomorphism. 
+  Since $G$ is an algebraic group over $\Fq$, $G(\Fq)$ is finite.
+  Therefore $\trFrob{\qcs{L}}(g) = \lambda_g(\Frob{})$ is a root of unity
   for every $g\in G(\Fq)$.  Since $\Weil{}$ is generated by
-  $\Frob{}$ and $\rho_g : \Weil{} \to \EEx$ is
-  a character, it follows that the image of $\rho_g$ is a finite group.
-  Thus, $\rho_g$ extends to an $\ell$-adic character of $\Gal(\bFq/\Fq)$,
-  which we will also denote $\rho_g$.
+  $\Frob{}$ and $\lambda_g : \Weil{} \to \EEx$ is
+  a character, it follows that the image of $\lambda_g$ is a finite group.
+  Thus, $\lambda_g$ extends to an $\ell$-adic character of $\Gal(\bFq/\Fq)$,
+  which we will also denote $\lambda_g$.
 %
-  We may now lift the $\ell$-adic character $\rho_g : \Gal(\bFq/\Fq) \to \EEx$
+  We may now lift the $\ell$-adic character $\lambda_g : \Gal(\bFq/\Fq) \to \EEx$
   to an $\ell$-adic character $\pi_1(G,\bg) \to \EEx$ using the canonical topological group homomorphism
@@
 
-  Since $b_G^*$ is full and faithful
-  \citelist{\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}},
-  $
+  Since $b_{G\times G}^*$ is full and faithful (again, see
+\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} or \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}),
+ \[
   b_{G\times G}^* : \Hom(m^*\qcs{E},\qcs{E}\boxtimes\qcs{E}) \to \Hom({\bar m}^*\gqcs{L},\gqcs{L}\boxtimes\gqcs{L})
-  $
+ \]
   is a bijection
@@
 \end{proof}
+
+Using this equivalence of categories, we may give a good description of $\QC(G)$ when $G$ is connected and finite type.
 
@@
  \item $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is an isomorphism of groups;
- \item every quasicharacter sheaf on $G$ is isomorphic to one defined by a discrete isogeny;%as in Proposition~\ref{prop:finite};
- \item $\Aut(\qcs{L}) = 1$, for all quasicharacter sheaves $\qcs{L}$ on $G$;
-%  \item for all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $G$ and for every $\rho \in \Hom(\qcs{L},\qcs{L}')$, either $\rho$ is trivial or an isomorphism.
+ \item every quasicharacter sheaf on $G$ is isomorphic to one defined by a discrete isogeny;
+ \item $\Aut(\qcs{L}) = 1$, for all quasicharacter sheaves $\qcs{L}$ on $G$.
  \end{enumerate}
  \end{proposition}
-
-\begin{proof}
-In Lemma~\ref{lem:bounded_connected} we saw that every quasicharacter sheaf $\qcs{L}$ on $G$ descends to $G$; let $\qcs{E}$ be an object in $\bQC(G)$ for which $B_G(\qcs{E}) \iso \qcs{L}$.
+\begin{proof}
+In Lemma~\ref{lem:bounded_connected}, we saw that every quasicharacter sheaf $\qcs{L}$ on $\bG$ descends to $G$; let $\qcs{E}$ be an object of $\bQC(G)$ for which $B_G(\qcs{E}) \iso \qcs{L}$.
  Since the functor $B_G : \bQC(G) \to \QC(G)$ is full and faithful, $\Aut(\qcs{L}) = \Aut(\qcs{E})$.
-From here, Deligne's function--sheaf dictionary for connected commutative algebraic groups over finite fields \citelist{\cite{deligne:SGA4.5}*{Sommes trig.}, \cite{laumon:87a}*{1.1.3}}  gives us all we need, as we briefly recall.
-The key observation is that, by étale descent, pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories from $\bQC(G)$ to the category of $1$-dimensional $\ell$-adic representations $V$ of $G(\Fq)$ equipped with an isomorphism $V \to V\otimes V$ such that the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ for every $\qcs{E}$ in $\bQC(G)$.
-Using the equivalence given by $\Lang^*$, if $\Lang^*\qcs{E} = V$ with character $\psi$ and isomorphism $V\to V\otimes V$ then 
-$\qcs{E} \iso (\Lang_!
-V)_\psi$, the $\psi$-isotypic component of the push-forward $\Lang_* V$ ($\Lang$ is proper, so $\Lang_* = \Lang_!$) of the constant sheaf $V$ on $G$ equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes\qcs{E}$ determined by $V\to V\otimes V$.
-Moreover, $\Aut(\qcs{E})$ is the group of automorphisms of $\rho : V\to V$ for which 
+From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields, as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3}, gives us all we need, as we briefly recall.
+%\todo{Fix citelist} %\citelist{\cite{deligne:SGA4.5}*{Sommes trig.},\cite{laumon:87a}*{1.1.3}}
+
+As in the proof of Proposition~\ref{prop:finite}, use \'etale descent to see that pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.
+Under this equivalence, local systems $\qcs{E}$ on $G$ arising from objects in $\bQC(G)$ are matched with $G(\Fq)$-equivariant constant local systems of rank-one on $G$, and therefore with one-dimensional representations of $G(\Fq)$.
+In the same way, pullback along the isogeny $\Lang\times\Lang : G\times G\to G\times G$ matches the extra structure $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ with an isomorphism $m^*V \to V\boxtimes V$ of one-dimensional representations of $G(\Fq)\times G(\Fq)$, which is exactly an isomorphism $V \to V\otimes V$ of one-dimensional representations, which is exactly the choice of an isomorphism $V\iso \EE$.
+We see that $\bQC(G)$ is equivalent to the category of characters of $G(\Fq)$.
+Let $\bg$ be a geometric point above $g \in G(\Fq)$.
+If $\qcs{E}$ matches $\psi : G(\Fq)\to \EEx$ under this equivalence, a simple calculation on stalks reveals that the action of Frobenius on $\qcs{E}_{\bar g}$ is multiplication by $\psi(g)^{-1}$.
+In other words, for every $\qcs{E}$ in $\bQC(G)$, the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ as a representation of $G(\Fq)$, proving parts (i) and (ii).
+
+To finish the proof of part (iii), suppose $\Lang^*\qcs{E} = V$ with isomorphism $V \to V\otimes V$.
+Observe that the equivalence above establishes a bijection between $\Aut(\qcs{E})$ and the group of automorphisms of $\rho : V\to V$ for which
 \[
@@
 
-%\begin{remark}
-We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of quasicharacter sheaves on $G$ is equivalent to the category of characters $\psi$ of $G(\Fq)$.
-We have also just seen that if the character of $\Lang^*\qcs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\qcs{E} : \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ which is part of the data that determines a quasicharacter sheaf on $G$.
-That leads to a perspective on the function--sheaf dictionary common in the literature in which one considers $1$-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$; see \cite{kamgarpour:09a}*{Intro}, for example.
-As a slight variation, one may also consider $1$-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
-%One may show that all such $\gqcs{L}$ are determined by extensions of $\bG$ by $\EEx$ which are fixed by Frobenius and that the trace of Frobenius provides a canonical isomorphism from $\Hh^2(\bG,\EEx)^{\Frob{}}$ to $G(\Fq)^*$; {\it cf.\ }
-%One may show that all such $\gqcs{L}$ are determined by extensions of $\bG$ by $\EEx$ which are fixed by Frobenius and that the trace of Frobenius provides a canonical isomorphism from $\Hh^2(\bG,\EEx)^{\Frob{}}$ to $G(\Fq)^*$; {\it cf.\ } \cite{kamgarpour:09a}*{Prop 2.15}.
-
-Although the category of quasicharacter sheaves on $G$ does specialize to that common notion when $G$ is connected and of finite type, the common notion is not appropriate if one wishes to extend the dictionary to smooth commutative group schemes over finite fields.
-In particular, as we have already seen in Section~\ref{sec:etale}, for a given quasicharacter sheaf $\qcs{L} = (\gqcs{L},\mu,\phi)$ there may be a different isomorphism $\mu' : \bm^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$ for which $\qcs{L}'=(\gqcs{L},\mu',\phi)$ is also a quasicharacter sheaf on $G$, not isomorphic to $\qcs{L}$ in $\QC(G)$.
-Indeed, Proposition~\ref{prop:etale-iso} shows that when $G$ is étale, $\Hh^2(\bG,\EEx)^{\Frob{}}$ measures the possibilities for $\mu'$.
-In other words, the common perspective on the function--sheaf dictionary leads only, and exactly, to the part of category of quasicharacter sheaves that is {\it completely invisible} to the trace of Frobenius!
-
-We will see in Section~\ref{sec:main} that, for any smooth commutative group scheme $G$, the part of category of quasicharacter sheaves that is invisible to the trace of Frobenius are measured by $\Hh^2(\pi_0(\bG),\EEx)^{\Frob{}}$.
-%\end{remark}
-
-\section{The function--sheaf dictionary for smooth commutative group schemes}\label{sec:main}
+We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of quasicharacter sheaves on $G$ is equivalent to the category of one-dimensional representations $V$ of $G(\Fq)$ equipped with an isomorphism $V\iso \EE$, and therefore equivalent to the category of characters $\psi$ of $G(\Fq)$.
+We have also just seen that if the character of $\Lang^*\qcs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\qcs{E} : \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
+This fact leads to a perspective on the function-sheaf dictionary common in the literature in which one considers one-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$ \cite{kamgarpour:09a}*{Intro}.
+As a slight variation, one may also consider one-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
+
+Although the category of quasicharacter sheaves on $G$ specializes to the one described above when $G$ is connected and of finite type, this description is not sufficient when extending the dictionary to smooth commutative group schemes.
+In particular, for a given $\gqcs{L}$ and $\phi$ there may be many $\mu$ so that $(\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf.
+For \'etale $G$, Proposition~\ref{prop:etale-iso} shows that $\Hh^2(\bG,\EEx)^{\Weil{}}$ measures the possibilities for $\mu$.
+We will see in Section~\ref{sec:main} that $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ plays an analogous role for general smooth commutative group schemes $G$.
+
+\section{The function-sheaf dictionary for smooth commutative group schemes}\label{sec:main}
 
@@
 \end{equation}
-Since $\pi_0(G)$ is a étale commutative group scheme -- and thus smooth --
-Lemma~\ref{lem:pullback} implies that \eqref{eq:pi0} defines the sequence of functors
+Since $\pi_0(G)$ is an \'etale commutative group scheme -- and thus smooth --
+Lemma~\ref{lem:pullback} implies that \eqref{eq:pi0} defines a sequence of functors
 \begin{equation}\label{eq:pi1}
@@
 Let $\qcs{L}$ be a quasicharacter sheaf on $\pi_0(G)$ and let $\rho : \pi_0^*\qcs{L} \to (\EE)_{G}$ be an isomorphism in $\QC(G)$. 
-For each $x\in \pi_0(\bG)$, the restriction $\pi_0^*\gqcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gqcs{L}_x)_{\bG^x}$ so the isomorphism $\rho_{\bG^x} : (\gqcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\rho_x : \gqcs{L}_x \to (\EE)_x$.
-The collection $\{ \rho_x \tq x\in \pi_0(\bG) \}$ determines an isomorphism $\qcs{L} \to (\EE)_{\pi_0(G)}$  in $\QC(\pi_0(G))$.
+For each $x\in \pi_0(\bG)$, set $\bG^x \ceq \pi_0^{-1}(x)$.
+The restriction $\pi_0^*\gqcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gqcs{L}_x)_{\bG^x}$ so the isomorphism $\brho\vert_{\bG^x} : (\gqcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gqcs{L}_x \to (\EE)_x$.
+The collection $\{ \brho_x \tq x\in \pi_0(\bG) \}$ determines an isomorphism $\qcs{L} \to (\EE)_{\pi_0(G)}$  in $\QC(\pi_0(G))$.
 \end{proof}
@@
 \begin{proof}
-  Recall the short exact sequence \eqref{eq:pi0}
-  defining the component group scheme for $G$:
+  Let
+  \begin{equation}\label{eq:pre-snake}
+  \begin{tikzcd}[row sep=20, column sep=20]
+    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
+    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
+    0 \rar & \pi_0(G)(\Fq)^* \rar
+    &  G(\Fq)^* \rar & G^0(\Fq)^* \rar & 0
+  \end{tikzcd}
+  \end{equation}
+  be the commutative diagram of abelian groups obtained by applying
+  Lemma~\ref{lem:pullback} to \eqref{eq:pi0}.
+ %
+  The sequence of abelian groups
 \[
   \begin{tikzcd}
-    1 \rar & G^0 \rar & G \rar & \pi_0(G) \rar & 0.
-  \end{tikzcd}
-  \]
-  Let
-  \[
-  \begin{tikzcd}[row sep=20]
-  & 0 \arrow{d} & 0 \arrow{d} & 0\arrow{d} \\
-    0 \arrow[dashed]{r} & \ker \TrFrob{\pi_0(G)} \arrow[dashed]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dashed]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
+    1 \rar & G^0(\Fq) \rar & G(\Fq) \rar & \pi_0(G)(\Fq) \rar & 0,
+  \end{tikzcd}
+\]
+  is exact since $\Hh^1(\Fq,G^0) =0$ by Lemma~\ref{lem:G0alg-grp} and Lang's theorem on connected algebraic groups over finite fields \cite{lang:56a}.
+  Since $\EEx$ is divisible, $\Hom(\ - \ ,\EEx)$ is exact and thus the dual sequence of
+  character groups in \eqref{eq:pre-snake} is exact.
+%
+  The upper row in \eqref{eq:pre-snake} is exact by Proposition~\ref{prop:middleexact}.
+  Now Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}
+  imply that $\ker \TrFrob{G^0} =0$ and $\coker \TrFrob{G^0}=0$,
+  while Proposition~\ref{prop:etale-iso} gives $\ker \TrFrob{\pi_0(G)} \iso \Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$
+  and $\coker \TrFrob{\pi_0(G)}=0$.
+It now follows from the snake lemma
+ \[
+  \begin{tikzcd}[row sep=20, column sep=15]
+    0 \arrow[dotted]{r} & \ker \TrFrob{\pi_0(G)} \arrow[dotted]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dotted]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
     0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
@@
     & \arrow{d} G(\Fq)^* \rar & G^0(\Fq)^* \rar \dar & 0\\
-    & \arrow{d} \coker \TrFrob{\pi_0(G)} =0 \arrow[dashed]{r} & \arrow{d} \coker \TrFrob{G} \arrow[dashed]{r} &  \arrow{d} \coker \TrFrob{G^0} =0 & \\
-      & 0 & 0 & 0 \\
-  \end{tikzcd}
-  \]
-  be the commutative diagram of abelian groups obtained by applying
-  Lemma~\ref{lem:pullback} to \eqref{eq:pi0}.
- %
-  The sequence of abelian groups
-  \begin{equation}\label{eq:pi0k}
+   &  \coker \TrFrob{\pi_0(G)} =0 \arrow[dotted]{r} & \coker \TrFrob{G} \arrow[dotted]{r} & \coker \TrFrob{G^0} =0 & 
+  \end{tikzcd}
+  \]
+that $\coker \TrFrob{G} =0$
+and $\ker \TrFrob{\pi_0(G)} \to \ker \TrFrob{G}$ is an isomorphism.
+This gives the short exact sequence
+\[
   \begin{tikzcd}
-    1 \rar & G^0(\Fq) \rar & G(\Fq) \rar & \pi_0(G)(\Fq) \rar & 0,
-  \end{tikzcd}
-  \end{equation}
-  is exact since $\Hh^1(\Fq,G^0) =0$ by Lemma~\ref{lem:G0alg-grp} and Lang's theorem on connected algebraic groups over finite fields \cite{lang:56a}.
-  Since $\EEx$ is divisible, $\Hom_\text{Ab}(\ - \ ,\EEx)$ is exact and thus the dual sequence of
-  character groups is also exact.
-%
-  The upper row is exact by Proposition~\ref{prop:middleexact}.
-  Now Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}
-  imply that $\ker \TrFrob{G^0} =0$ and $\coker \TrFrob{G^0}=0$,
-  while Proposition~\ref{prop:etale-iso} gives $\ker \TrFrob{\pi_0(G)} \iso \Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$
-  and $\coker \TrFrob{\pi_0(G)}=0$.
-%
-It follows from the snake lemma that $\coker \TrFrob{G} =0$
-and $\ker \TrFrob{\pi_0(G)} \to \ker \TrFrob{G}$ is an isomorphism.
-This calculates $\ker  \TrFrob{G}$ and shows that
-\[
-  \begin{tikzcd}
-0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx)) \arrow{r} & \QCiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0 
-  \end{tikzcd}
-\]
-is exact.
-\end{proof}
+0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx)) \arrow{r} & \QCiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0. 
+  \end{tikzcd}
+\]
+\end{proof}
+
+\begin{remark}
+Although $\TrFrob{\pi_0(G)}$ is split and $\TrFrob{G^0}$ is an isomorphism, it does not follow that $\TrFrob{G}$ is split. 
+\end{remark}
 
@@
 Let $G$ be a smooth commutative group scheme over $\Fq$.
-%For all quasicharacter sheaves $\qcs{L}$ and $\qcs{L}'$ on $G$, every $\rho \in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism.
-Moreover, 
-\[
-\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx),
-\]
- canonically.
+There is a canonical isomorphism
+\[
+\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx).
+\]
 \end{theorem}
 \begin{proof} 
-%For the first part of the proposition, argue as in the analogous part of Proposition~\ref{prop:autornaught_etale}.
-%For the second, f
-Fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the homomorphism $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
-This group homomorphism is clearly injective: if $\rho_x = \id_{\qcs{L}_x}$ for every $x\in \bG$ then $\rho = \id_{\qcs{L}}$.
-Note that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom_\text{cts}(\bG_{\Weil{}},\EEx)$, where $\bG_{\Weil{}}$ is given the topology of the base of the espace étalé attached to $\gqcs{L}$.
-Since $\ell$ is invertible in $\Fq$, it follows that $\Hom_\text{cts}(\bG_{\Weil{}},\EEx) = \Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
-Note that $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
+Fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the group homomorphism from $\Aut(\qcs{L})$ to $\Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
+This homomorphism is injective because morphisms of sheaves are determined by the linear transformations induced on stalks.  
+Homomorphisms in the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ are continuous when $\bG$ is viewed as the base of the espace \'etal\'e attached to $\gqcs{L}$.
+Since $\ell$ is invertible in $\Fq$, it follows that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
+We also have $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
 To see that $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho^y: \gqcs{L}^y \to \gqcs{L}^y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
-This defines an isomorphism $\bar\rho : \gqcs{L}\to \gqcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\qcs{L}\to \qcs{L}$ with maps to $\theta$ under $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
-\end{proof}
-
-\subsection{Base change}\label{sec:basechange}
+This defines an isomorphism $\bar\rho : \gqcs{L}\to \gqcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\qcs{L}\to \qcs{L}$ which maps to $\theta$ under $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
+\end{proof}
+
+\subsection{Base change}\label{ssec:basechange}
 
@@
 \]
-be the functor obtained by pullback along the canonical closed immersion of $k$-schemes
-$\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$
-\cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}.
+be the functor obtained by pullback along the canonical closed immersion 
+\[\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})\] of $k$-schemes.
 The following diagram commutes:
@@
 \end{align*}
-We can also interpret this operation on characters in terms of quasicharacter sheaves.
+We can also interpret this operation in terms of quasicharacter sheaves.
 
 If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$, we define
-a quasicharacter sheaf $\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
+$\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
 $G_{k'}$ of $G$ to $k'$ by setting
@@
 Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
-as taking the action $\varphi$ of $\Weil{k}$ on $\gqcs{L}$
-defined in Section~\ref{sec:category} and restricting it to the subgroup $\Weil{k'}$.
+as restricting the action $\varphi$ of $\Weil{k}$ on $\gqcs{L}$,
+defined in Section~\ref{ssec:category}, to $\Weil{k'}$.
 
@@
 
-%\todo{Can we improve on this result by proving that $\rho$ is an equivalence of categories?}
-
-\section{Applications}\label{sec:applications}% to algebraic tori and Abelian varieties over \texorpdfstring{$p$}{p}-adic fields}
-
-Let $K$ be a local field (in the sense of Serre) with residue field $\Fq$. 
-In this section we consider connected commutative algebraic groups over $K$ that admit a Néron model, by which we mean an lft Néron model.
-By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected commutative algebraic groups over $K$ that contain no subgroup of type $\mathbb{G}_\text{a}$.
-These algebraic groups over $K$ form an additive category, denoted by $\mathcal{N}_K$ below, in a natural way, as a full subcategory of connected commutative algebraic groups over $K$.
-This category includes algebraic tori over $K$ and Abelian varieties over $K$ unipotent K-wound groups.
-
-\subsection{Quasicharacters}
+\section{Applications}\label{sec:applications}
+
+Let $K$ be a local field with finite residue field $\Fq$;
+ we continue to assume that $\ell$ is invertible in $\Fq$.
+In this section we consider connected commutative algebraic groups over $K$ that admit a N\'eron model, by which we mean a locally finite type N\'eron model.
+By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected commutative algebraic groups over $K$ that contain no subgroup isomorphic to $\mathbb{G}_\text{a}$.
+Write $\mathcal{N}_K$ for the full subcategory of the category of algebraic groups consisting of such objects.
+This category is additive, and includes all algebraic tori over $K$, abelian varieties over $K$ and unipotent $K$-wound groups.
+
+\subsection{Quasicharacters}\label{ssec:quasicharacters}
 
 Let $R$ be the ring of integers of $K$.
-Write $\m$ for the maximal ideal of $R$ and set $R_n = R/\m^{n+1}$, for every non-negative integer $n$.
-Suppose $X_K \in \mathcal{N}_K$ with Néron model $X$ over $R$.
-A {\it quasicharacter of $X_K(K)$} is a group homomorphism $X_K(K) \to \EEx$ that factors through $X_K(X) \to X(R_n)$, for some non-negative integer $n$;
-the group of quasicharacters of $X_K(K)$ will be denoted by 
-\[
-\Hom_\text{qc}(X_K(K),\EEx)
+Write $\m$ for the maximal ideal of $R$ and set $R_n = R/\m^{n+1}$ for every non-negative integer $n$.
+Suppose $X_K \in \mathcal{N}_K$ has N\'eron model $X$ over $R$.
+Note that $X(K) = X(R)$.
+A \emph{quasicharacter of $X(K)$} is a group homomorphism $X(K) \to \EEx$ that factors through $X(R) \to X(R_n)$ for some non-negative integer $n$.
+We note that this definition is compatible with \cite{cassels-frohlich:AlgebraicNumberTheory}*{Ch XV, \S 2.3}.
+The group of quasicharacters of $X(K)$ will be denoted by 
+\[
+\Hom_\text{qc}(X(K),\EEx)
 \]
@@
 Let $K$, $R$ and $R_n$ be as above.
-Set $S = \Spec{R}$ and $S_n = \Spec{R_n}$, for every non-negative integer $n$;
-note that $S_0 = \Spec{\Fq}$ is the special fibre of $S$.
-
-We will need the Greenberg functor, which provides
-a functor from the category of schemes 
-over $R_n$, for each $n\in \NN$, to the category of schemes over $\Fq$;
-See \cite{bertrapelle-gonzales:Greenberg} for the definition and fundamental properties of the Greenberg functor as we use it; other important references include
-\citelist{
+For each $n \in \NN$, the Greenberg functor maps schemes over $R_n$ to schemes over $\Fq$.
+See \cite{bertrapelle-gonzales:Greenberg} for the definition and fundamental properties of the Greenberg functor as we use it; other useful references include
 \cite{greenberg:61}, \cite{greenberg:63a},
 \cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1},
-\cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6},
-\cite{nicaise-sebag:motivicSerre}*{\S 2.2}
-}.
-This functor respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components.
+\cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} and
+\cite{nicaise-sebag:motivicSerre}*{\S 2.2}. %citelist
 %
@@
 \[
-\Gr^R_n : \partop{\text{Schemes}}{\text{lft over $R$}} \to \partop{\text{Schemes}}{\text{lft over $\Fq$}}
-\]
-for the functor produced by composing pullback along $S_n \to S$ with the Greenberg functor. 
-This functor also respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components, and
-\[
-\Gr^R_n(X)(\Fq) \iso X(R_n),
-\]
-canonically, for any $X$ lft over $S$.
+\Gr^R_n : \Sch{R} \to \Sch{\Fq}
+\]
+for the functor produced by composing pullback along $\Spec{R_n} \to \Spec{R}$ with the Greenberg functor. 
+This functor respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components.  Moreover, there is a canonical isomorphism
+\[
+\Gr^R_n(X)(\Fq) \iso X(R_n)
+\]
+for any scheme $X$ over $R$.
 
@@
 Crucially, $\varrho^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
-This observation is key to the proof that, for any $X$ lft over $S$, the projective limit 
+This observation is key to the proof that, for any scheme $X$ over $R$, the projective limit 
 \[
@@
 taken with respect to the surjective morphisms $\varrho^R_{n\leq m}(X) : \Gr^R_{m}(X) \to \Gr^R_n(X)$,
-exists in the category of group schemes over $\Fq$.
+exists in the category of group schemes over $\Fq$;
+see \cite{EGAIV3}*{\S 8.2}.
 This leads to the definition of what we shall call the {\it Greenberg transform}:
 \[
-\Gr_R : \partop{\text{Schemes}}{\text{lft over $R$}} \to \partop{\text{Schemes}}{\text{lft over $\Fq$}}.
+\Gr_R : \Sch{R} \to \Sch{\Fq}.
 \]
@@
 \[
-\varrho^R_n(X) : \Gr^R(X) \to \Gr^R_n(X),\qquad \forall n\in \NN_0.
-\]
-The Greenberg transform respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components, and
-\[
-\Gr_R(X)(\Fq) \iso X(R),
-\]
-canonically, for any $X$ lft over $R$.
-
-\subsection{Quasicharacter sheaves on the Greenberg transform of a Néron model} \label{ssec:qc_on_GN}
+\varrho^R_n(X) : \Gr^R(X) \to \Gr^R_n(X),\qquad \forall n\in \NN.
+\]
+
+\subsection{Quasicharacter sheaves on the Greenberg transform of a N\'eron model} \label{ssec:qc_on_GN}
 
 Let $X_K \in \mathcal{N}_K$ and $X$ be as above.
-
-For every non-negative integer $n$, $\Gr^R_n(X)$ is {\it smooth} commutative group scheme over $\Fq$ with component group scheme
-$\pi_0(\Gr^R_n(X))= \pi_0(X) \times_S S_0$
-and $\Fq$-rational points
-$
-\Gr^R_N(X)(\Fq)\iso X(R_n),
-$
-canonically.
+Set $S = \Spec{R}$ and $S_n = \Spec{R_n}$;
+note that $S_0 = \Spec{\Fq}$ is the special fibre of $S$.
+
+For every non-negative integer $n$, $\Gr^R_n(X)$ is a {\it smooth} commutative group scheme over $S_0$
+with component group scheme $\pi_0(X)_{\Fq} \ceq \pi_0(X) \times_S S_0$ and $\Fq$-rational points $X(R_n).$
 %
-The Greenberg transform $\Gr_R(X)$ of $X$ is still a commutative group scheme over $\Fq$ with component group scheme
-$
-\pi_0(\Gr_R(X))= \pi_0(X) \times_S S_0
-$
-and its $\Fq$-rational points are given by
-$
-\Gr_R(X)(\Fq)\iso X_K(K),
-$
-canonically, but $\Gr_R(X)$ is not locally of finite type, and therefore not smooth.
-
+The Greenberg transform $\Gr_R(X)$ of $X$ is a commutative group scheme over $\Fq$
+with component group scheme $\pi_0(X)_{\Fq}$
+and $\Fq$-rational points $X(K).$
+However, $\Gr_R(X)$ is not locally of finite type and therefore not smooth.
 %
-Moreover, the morphism of $\Fq$-schemes $\varrho^R_n(X) : \Gr_R(X) \to \Gr^R_n(N)$ induces a functor
+The morphism of $\Fq$-schemes $\varrho^R_n(X) : \Gr_R(X) \to \Gr^R_n(X)$ induces a functor
 \[
@@
 as in Lemma~\ref{lem:pullback}.
-This functor is faithful, so we may view $\QC(\Gr^R_n(X))$ as a subcategory of $\QC(\Gr_R(X))$.
-
-We now define a category which will geometrize quasicharacters of $X_K(K)$.
-Although $\Gr_R(X)$ is not locally of finite type, and thus not smooth, we begin by considering the rigid monoidal category $\QC(\Gr_R(X))$ defined in Section~\ref{sec:category}, without insisting that the commutative group scheme is smooth.
+%This functor is faithful, so we may view $\QC(\Gr^R_n(X))$ as a subcategory of $\QC(\Gr_R(X))$.
+
+We now define a category which will geometrize quasicharacters of $X(K)$.
+We begin by considering the rigid monoidal category $\QC(\Gr_R(X))$ defined in Section~\ref{ssec:category} without insisting that the commutative group scheme is smooth.
 
 \begin{definition}
-We construct an evil subcategory $\QC(X_K)$ of $\QC(\Gr_R(X))$ as follows:
-objects in $\QC(X_K)$ are the $\ell$-adic sheaves $\varrho^R_n(X)^*\qcs{L}$, for $n\in \NN$ and $\qcs{L} \in \QC(\Gr^R_n(X))$; morphism from $\varrho^R_n(X)^*\qcs{L}$ to $\varrho^R_m(X)^*\qcs{L}'$ are $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\qcs{L},\qcs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\qcs{L},\varrho^R_{m\leq n}(X)^*\qcs{L}')$ when $m\leq n$.
- We refer to $\QC(X_K)$ as the {\it evil category of quasicharacter sheaves for $X_K$}; objects will simply be called {\it 
-quasicharacter sheaves for $X_K$}.
+A {\it quasicharacter sheaf for $X_K$} is an object of
+the following rigid monoidal subcategory of $\QC(\Gr_R(X))$, denoted by $\QC(X_K)$:
+\begin{enumerate}
+\item
+objects in $\QC(X_K)$ are the $\ell$-adic sheaves $\varrho^R_n(X)^*\qcs{L}$, for $n\in \NN$ and $\qcs{L} \in \QC(\Gr^R_n(X))$; 
+\item
+morphisms $\varrho^R_n(X)^*\qcs{L} \to \varrho^R_m(X)^*\qcs{L}'$ in $\QC(X_K)$ are those morphisms in $\QC(\Gr_R(X))$ which take the form $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\qcs{L},\qcs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\qcs{L},\varrho^R_{m\leq n}(X)^*\qcs{L}')$ when $m\leq n$.
+\end{enumerate}
+
 \end{definition}
 
-The evil category of quasicharacter sheaves for $X_K$ is rigid monoidal in the obvious way.
-
 \begin{remark}
-The evil category of quasicharacter sheaves for $X_K$ is evil in the categorical sense.
-If $\varrho^R_n(X)^* : \QC(\Gr^R_n(X)) \to \QC(\Gr_R(X))$ is full then the construction above is easily modified to be non-evil; however, we do not know if $\varrho^R_n(X)^*$ is full.
-In any case, a non-evil alternative construction of $\QC(X_K)$ is available, but it is quite ugly.
-For objects, one considers triples $\qcs{F} \ceq (n, \{\qcs{F}_i\}_{i \ge n}, \{\alpha_{i \le j}\}_{j \ge i \ge n})$, where $n$
-is a positive integer, each $\qcs{F}_i$ is a quasicharacter sheaf on $\Gr^R_i(X)$ and each $\alpha_{i \le j} : \qcs{L}_j \to f^*_{i \le j} \qcs{L}_i$ is an isomorphism; of course, $\alpha_{i \le i}$ is the identity and the $\alpha_{i \le j}$ are compatible with each other.
+If $\varrho^R_n(X)^* : \QC(\Gr^R_n(X)) \to \QC(\Gr_R(X))$ is full then the construction above can be improved by forming $\QC(X_K)$ from the essential images of the functors $\varrho^R_n(X)^*$; however, we do not know if $\varrho^R_n(X)^*$ is full.
+\end{remark}
+
+\begin{remark}
+We offer the following alternate construction of $\QC(X_K)$, which does not make use of subcategories.
+For objects, one considers triples 
+\[
+\qcs{F} \ceq (n, \{\qcs{F}_i\}_{n\leq i}, \{\alpha_{i \le j}\}_{n\le i \le j}),
+\] where $n$
+is a non-negative integer, each $\qcs{F}_i$ is a quasicharacter sheaf on $\Gr^R_i(X)$ and each 
+\[
+\alpha_{i \le j} : \qcs{L}_j \to \varrho^R_{i \le j}(X)^* \qcs{L}_i
+\]
+ is an isomorphism; here $\alpha_{i \le i}$ is the identity and the $\alpha_{i \le j}$ are compatible with each other.  
 If $\qcs{F} \ceq (n, \{\qcs{F}_i\}, \{\alpha_{i \le j}\})$
 and $\qcs{F}' \ceq (m, \{\qcs{F}'_i\}, \{\alpha'_{i \le j}\})$ are objects then $\Hom(\qcs{F}, \qcs{F}')$ is the set
-of equivalence classes of pairs $(k, \{\beta_i\}_{i \ge k})$, where $k \ge m, n$ and the $\beta_i : \qcs{F}_i \to \qcs{F}'_i$ are
+of equivalence classes of pairs $(k, \{\beta_i\}_{k \le i})$, where $n,m \le k$ and the $\beta_i : \qcs{F}_i \to \qcs{F}'_i$ are
 morphisms of quasicharacter sheaves so that
@@
 \begin{theorem}\label{thm:QCXK}
-Let $K$ and $R$ be as above.
+Let $K$ be a local field with residue field $\Fq$, in which $\ell$ is invertible; 
+let $R$ be the ring of integers of $K$.
+\begin{enumerate}
+\item
 The trace of Frobenius provides a natural transformation between the additive functors
@@
 \qquad\text{and}\qquad
-F_{\text{qc}}: X_K \mapsto \Hom_{\text{qc}}(X_K(K),\EEx)
-\]
-where $X$ is a Néron model for $X_K$, as functors from $\mathcal{N}_K$ to the category of abelian groups. 
-Regarding this natural transformation, for every $X_K \in \mathcal{N}_K$ with Néron model $X$:
-\begin{enumerate}
-\item[(1)] there is a canonical short exact sequence of abelian groups 
-\[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{X_K} \to \Hom_\text{qc}(X_K(K),\EEx) \to 0;
-\] 
-\item[(2)] for all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
-\item[(3)] for all quasicharacter sheaves $\qcs{F}$ on $\Gr_R(X)$,
-\[
-\Aut(\qcs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx),
-\]
-canonically.
+F_{\text{qc}}: X_K \mapsto \Hom_{\text{qc}}(X(K),\EEx)
+\]
+as functors from $\mathcal{N}_K$ to the category of abelian groups.
+\end{enumerate} 
+Regarding this natural transformation, for every $X_K \in \mathcal{N}_K$ with N\'eron model $X$:
+\begin{enumerate}[resume]
+\item there is a canonical short exact sequence of abelian groups 
+\[
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{}} \to \QCiso{X_K} \to \Hom_\text{qc}(X(K),\EEx) \to 0;
+\] 
+\item for all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
+\item for all quasicharacter sheaves $\qcs{F}$ for $X_K$, there is a canonical isomorphism
+\[
+\Aut(\qcs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx).
+\]
 \end{enumerate}
@@
 \begin{proof}
-To begin, fix $n\in \NN$.
-The following statements follow directly from Lemma~\ref{lem:autornaught}, Proposition~\ref{prop:functorialG}, Theorems~\ref{thm:snake} and \ref{thm:autornaught}, properties of Néron models and our observations about the component group of $\Gr^R_n(X)$.
 \begin{enumerate}
-\item[(0)] Trace of Frobenius gives a natural transformation from
-\[
-F_{\QC,n}: X_K \mapsto \QCiso{\Gr^R_n(X)}
-\qquad\text{to}\qquad
-F_{\text{qc},n}: X_K \mapsto \Hom_n(X_K(K),\EEx)
-\]
-as functors from $\mathcal{N}_K$ to Abelian groups.
-\item[(1)] There is a canonical short exact sequence of abelian groups 
-\[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Frob{}} \to \QCiso{\Gr^R_n(X)} \to \Hom(X(R_n),\EEx) \to 0.
-\] 
-\item[(2)] For all quasicharacter sheaves $\qcs{L}$, $\qcs{L}'$ on $\Gr^R_n(X)$ and for every $\rho \in \Hom(\qcs{L},\qcs{L}')$, either $\rho$ is trivial or $\rho$ is an isomorphism.
-\item[(3)] For all quasicharacter sheaves $\qcs{L}$ on $\Gr^R_n(X)$,
-\[
-\Aut(\qcs{L}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx),
-\]
-canonically.
+\item Use Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$, the fact that N\'eron models are unique up to isomorphism, the fact that every $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(X_K)$ and the observation that every object in $\QC(X_K)$ is in the essential image of $\QC(\Gr^R_n(X))$ for some $n$.
+\item Use Theorem~\ref{thm:snake} with $G = \Gr^R_n(X)$ and then argue as in part (i).
+\item Argue as in the proof of Lemma~\ref{lem:autornaught}.
+\item Use Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, the fact that the component group of $\Gr^R_n(X)$ is independent of $n$ and then argue as in part (i).
 \end{enumerate}
-So Theorem~\ref{thm:QCXK} now follows from the fact that each $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(X_K)$ and the observation that $\QC(X_K)$ a `union' of the subcategories $\QC(\Gr^R_n(X))$ in $\QC(\Gr_R(X))$.
-\end{proof}
-
-\subsection{Quasicharacters for $p$-adic tori} \label{ssec:qc_tori}
+\end{proof}
+
+\subsection{Quasicharacter sheaves for $p$-adic tori} \label{ssec:qc_tori}
 
 As we explained in the Introduction, our original motivation for this paper was to find a geometrization and categorification of quasicharacters of $p$-adic tori. 
-This is is now provided by specializing Theorem~\ref{thm:QCXK} to the case when $X_K= T\in \mathcal{N}_K$ is an algebraic torus over $K$, in which case we write $\underline{T}$ for the Neron model $X$.
-Now,
-\[
- \pi_0(\underline{T})_{\bFq} = X_*(T)_{\mathcal{I}_K},
-\]
-where $X_*(T)$ is the cocharacter lattice of $T$ and $\mathcal{I}_K$ is the inertia group for $K$ \cite{bitan:discriminant}*{Eq 3.1}. 
-Accordingly, the short exact sequence in Theorem~\ref{thm:QCXK} becomes
-\begin{equation}
-0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Frob{}} \to \QCiso{T} \to \Hom_\text{qc}(T(K),\EEx) \to 0.
-\end{equation}
-Again by Theorem~\ref{thm:QCXK}, the automorphism groups in the $\QC(T)$ are given, for every quasicharacter sheaf $\qcs{F}$ for $T$, by
-\begin{equation}
-\Aut(\qcs{F}) \iso \Hom(X_*(T)_{\Weil{K}},\EEx) \iso \Hom(X_*(T),\EEx)^{\Weil{K}} = (\check{T}_\ell)^{\Weil{K}}
-\end{equation}
-where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
-
-\subsection{Weil restriction and quasicharacters}\label{ssec:wrK}
+This is is now provided by specializing Theorem~\ref{thm:QCXK} to the case when $X_K= T_K\in \mathcal{N}_K$ is an algebraic torus over $K$. 
+Let $T$ be a Neron model for $T_K$.
+By \cite{bitan:discriminant}*{Eq 3.1}, the special fibre of the component group scheme for $T$ is given by
+\[
+ \pi_0(T)_{\bFq} = X_*(T_K)_{\mathcal{I}_K},
+\]
+where $X_*(T_K)$ is the cocharacter lattice of $T_K$ and $\mathcal{I}_K$ is the inertia group for $K$.
+Accordingly, by Theorem~\ref{thm:QCXK}, isomorphism classes of quasicharacter sheaves for $T_K$ determine quasicharacter sheaves according to the exact sequence
+\[
+0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{T_K} \to \Hom_\text{qc}(T(K),\EEx) \to 0.
+\]
+Also by Theorem~\ref{thm:QCXK} and \cite{bitan:discriminant}*{Eq 3.1}, the automorphism group of every $\qcs{F} \in \QC(T_K)$ is given by 
+\[
+\Aut(\qcs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx),
+\]
+where $\Weil{K}$ is the Weil group for $K$. 
+Since 
+\[
+\Hom(X_*(T_K)_{\Weil{K}},\EEx) \iso \Hom(X_*(T_K),\EEx)^{\Weil{K}}
+\]
+it follows that the automorphism group of every quasicharacter sheaf for $T_K$ is $(\check{T}_\ell)^{\Weil{K}}$, where $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
+
+\subsection{Weil restriction and quasicharacter sheaves}\label{ssec:wrK}
 
@@
 Let $R$ and $R'$ be the rings of integers of $K$ and $K'$, respectively.
-Let $X_K$ be a connected commutative algebraic group over $K$
-that admits a Néron model $X$ over $R$.
-Set $X_{K'} \ceq X_K \times_\Spec{K} \Spec{K'}$
-Let $X'$ be a Néron model for $X_{K'}$.
+Let $X_K \in \mathcal{N}$ have N\'eron model $X$, set $X_{K'} \ceq X_K \times_\Spec{K} \Spec{K'}$
+and let $X'$ be a N\'eron model for $X_{K'}$.
 
@@
 \] 
-such that the restriction of the functor
-\[
-f^* : \QC(\Res_{k'/k} \Gr_{R'}(X')) \to  \QC(\Gr_R(X))
-\]
-induces
+which, through quasicharacter sheaves, induces
 \[
 \begin{tikzcd}[column sep=60]
-\Hom_{\text{qc}}(X_K(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{X_K(K)}} &\Hom_{\text{qc}}(X_K(K), \EEx).
+\Hom_{\text{qc}}(X_K(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{X(K)}} &\Hom_{\text{qc}}(X_K(K), \EEx).
 \end{tikzcd}
@@
 \begin{proof}
-Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} to include locally finite type Néron models,
-one may show that $\Res_{R'/R}(X')$ is a Néron model for $\Res_{K'/K}(X_{K'})$.
-By the Néron mapping property, the canonical closed immersion
+Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} to include locally finite type N\'eron models,
+one may show that $\Res_{R'/R}(X')$ is a N\'eron model for $\Res_{K'/K}(X_{K'})$.
+Thus, by the N\'eron mapping property, the canonical closed immersion
 \[
@@
 \]
-the pullback functor 
-\[
-f_n^* : \QC(\Res_{k'/k} \Gr_{en-1}^{R'}(X'))\to \QC(\Gr_{n-1}^{R}(X))
-\]
-obtained by applying Lemma~\ref{lem:pullback} to \eqref{men} gives
-\[
-\Hom(X(R'_{en}),\EEx) \to \Hom(X(R_n),\EEx).
-\]
-Passing to the projective limit, the family of morphisms \eqref{men} determines a morphism of group schemes
-\[
-f: \Gr_R(X) \to \Res_{k'/k} \Gr_{R'}(X').
-\]
-which induces the functor
-\[
-f^* : \QC(\Res_{k'/k} \Gr_{R'}(X'))\to \QC(\Gr_{R}(X)).
-\]
-When restricted to the appropriate evil subcategories, this induces
-\[
-\Hom_{\text{qc}}(X_K(K'),\EEx) \to \Hom_{\text{qc}}(X_K(K),\EEx).
+it follows from Lemma~\ref{lem:pullback} that the pullback functor \eqref{men-pulled} actually induces
+\[ 
+\Hom_{en-1}(X'(R'),\EEx) \to \Hom_{n-1}(X(R)),\EEx)
+\]
+Since $X'$ is a N\'eron model for $X_{K'}$ and $X$ is a N\'eron model for $X_K$,
+ this may be re-written as
+ \[ 
+\Hom_{en-1}(X_{K'}(K'),\EEx)= \Hom_{en-1}(X_{K}(K'),\EEx) \to \Hom_{n-1}(X_K(K)),\EEx)
+\]
+Passing to limits now defines
+\[ 
+\Hom_\text{qc}(X_K(K'),\EEx) \to \Hom_\text{qc}(X_K(K)),\EEx)
 \]
@@
 
-\subsection{Transfer of quasicharacters}\label{sec:transfer}
-
-Let $K$ and $K'$ be local fields with rings of integers $R$ and $R'$ and residue fields $k$ and $k'$, respectively.
-Set $S = \Spec{S}$ and $S_n = \Spec{R_n}$; likewise define $S' = \Spec{R'}$ and $S'_{n'} = \Spec{R'_{n'}}$.
-
-Suppose $X_K\in \mathcal{N}_K$ with Néron model $X$ and $X'_{K'}\in \mathcal{N}_K'$ with Néron model $X'$.
-Suppose $m$ and $m'$ are non-negative integers such that 
-\[
-R_m \iso R'_{m'},
-\]
-in which case $K$ and $K'$ are said to be $m$-close, and
+\subsection{Transfer of quasicharacters}\label{ssec:transfer}
+
+Let $K$ and $L$ be local fields with rings of integers $\OK$ and $\OL$, respectively. 
+Pick uniformizers $\varpi_K$ and $\varpi_L$ for $\OK$ and $\OL$, respectively;
+what follows will not depend on these choices.
+Suppose $\ell$ is invertible in the residue fields of $K$ and $L$.
+
+We begin with $X_K\in \mathcal{N}_K$ with N\'eron model $X$ and $Y_{L}\in \mathcal{N}_L$ with N\'eron model $Y$.
+Suppose $m$ is a positive integer such that 
+\[
+\OK/\varpi_K^{m}\OK \iso \OL/\varpi_L^{m}\OL.
+\]
+Suppose also that
 \begin{equation}\label{eq:schematic_transfer}
-X \times_{S} S_m \iso X' \times_{S'} S'_{m'}.
+X \times_{\Spec{\OK}} \Spec{\OK/\varpi_K^{m}\OK} \iso Y \times_{\Spec{\OL}} \Spec{\OL/\varpi_L^{m}\OL}
 \end{equation}
-as smooth group schemes over $R_m$. 
+as smooth group schemes over $\OK/\varpi_K^{m}\OK$. 
 Then
-$
-\Gr^R_m(X) \iso \Gr^{R'}_{m'}(X')
-$
-as smooth group schemes over $\Fq$; accordingly, by Lemma~\ref{lem:pullback} the isomorphism above determines an equivalence of categories
+\[
+\Gr^{\OK}_{m-1}(X) \iso \Gr^{\OL}_{m-1}(Y)
+\]
+as smooth group schemes over $\Fq$.  Accordingly, by Lemma~\ref{lem:pullback}, the isomorphism above determines an equivalence of categories
 \begin{equation}\label{eq:categorical_transfer}
-\QC(\Gr^R_m(X)) \cong \QC(\Gr^{R'}_{m'}(X'))
+\QC(\Gr^{\OK}_{m-1}(X)) \cong \QC(\Gr^{\OL}_{m-1}(Y))
 \end{equation}
-which induces a group isomorphism
-$
-\QCiso{\Gr^R_m(X)} \cong \QCiso{\Gr^{R'}_{m'}(X')}
-$
-and thence, by trace of Frobenius, an isomorphism
+which induces an isomorphism
 \begin{equation}\label{eq:transfer}
-\Hom_m(X_K(K),\EEx)  \iso  \Hom_{m'}(X'_{K'}(K'),\EEx).
+\Hom_{m-1}(X(K),\EEx)  \iso  \Hom_{m-1}(Y(L),\EEx).
 \end{equation}
-The isomorphism \eqref{eq:transfer} is an instance of {\it transfer} of (certain) quasicharacters between $X_K(K)$ and $X_{K'}(K')$. 
+The isomorphism \eqref{eq:transfer} is an instance of {\it transfer} of (certain) quasicharacters between $X(K)$ and $Y(L)$. 
 We now recognize this transfer of quasicharacters as a consequence of the equivalence of categories of quasicharacter sheaves \eqref{eq:categorical_transfer}.
 
-The isomorphism \eqref{eq:schematic_transfer} can indeed exist between quasicharacters of algebraic tori over local fields, even when the characteristics of $K$ and $K'$ differ.
-Suppose $T$ and $T'$ are tori over non-archimedian local fields $K$ and $K'$,
-splitting over $L$ and $L'$ respectively.
-Then $T$ and $T'$ are said to be \emph{$N$-congruent} \cite{chai-yu:01a}*{\S 2} if there are isomorphisms
+The isomorphism \eqref{eq:schematic_transfer} can indeed exist between quasicharacters of algebraic tori over local fields, even when the characteristics of $K$ and $L$ differ.
+Suppose $T_K$ and $M_L$ are tori over local fields $K$ and $L$,
+splitting over $K'$ and $L'$, respectively.
+Then $T_K$ and $M_L$ are said to be \emph{$n$-congruent} \cite{chai-yu:01a}*{\S 2} if there are isomorphisms
  \begin{align*}
-  \alpha : \OL/\pi_K^N \OL &\to \OO{L'}/\pi_{K'}^N \OO{L'} \\
-  \beta : \Gal(L/K) &\to \Gal(L'/K') \\
-  \phi : X^*(T) &\to X^*(T')
+  \alpha : \OO{K'}/\varpi_K^n \OO{K'} &\to \OO{L'}/\varpi_{L}^n \OO{L'} \\
+  \beta : \Gal(K'/K) &\to \Gal(L'/L) \\
+  \phi : X^*(T_K) &\to X^*(M_L)
  \end{align*}
@@
  \begin{enumerate}
-  \item $\alpha$ induces an isomorphism $\OK/\pi_K^N \OK \to \OO{K'}/\pi_{K'}^N \OO{K'}$,
-  \item $\alpha$ is $\Gal(L/K)$-equivariant relative to $\beta$, and
-  \item $\phi$ is $\Gal(L/K)$-equivariant relative to $\beta$.
+  \item $\alpha$ induces an isomorphism $\OK/\varpi_K^n \OK \to \OO{L}/\varpi_{L}^n \OO{L}$,
+  \item $\alpha$ is $\Gal(K'/K)$-equivariant relative to $\beta$, and
+  \item $\phi$ is $\Gal(K'/K)$-equivariant relative to $\beta$.
  \end{enumerate}
-If $T$ and $T'$ are $N$-congruent then $\alpha$, $\beta$ and $\phi$ determine an isomorphism 
+If $T_K$ and $M_L$ are $n$-congruent then $\alpha$, $\beta$ and $\phi$ determine an isomorphism 
 \begin{equation}\label{transfer}
-  \Hom_N(T(K), \EEx) \iso \Hom_N(T'(K'),\EEx).
+  \Hom_{n-1}(T_K(K), \EEx) \iso \Hom_{n-1}(M_L(L),\EEx).
 \end{equation}
-Note that if $T$ and $T'$ are $N$-congruent, then they are $N'$ congruent for every
-$N' \leq N$.
-%the isomorphism \eqref{transfer} is level-preserving at integers less than $N$.
-%
-One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes between the
-$\underline{T} \times_S S_n$ and $\underline{T}' \times_{S'} S'_n$, where $\underline{T}$ is a Néron model of $T$ and $\underline{T}'$ is a Néron model of $T'$, assuming that $T$ and $T'$ are sufficiently congruent.
-They define a quantity $h$ (the smallest integer so that $\pi^h$ lies in the
-Jacobian ideal associated to a natural embedding of $T$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}) and show  that if $N > 3h$ and $T$ and $T'$ are $N$-congruent then there is a canonical isomorphism of smooth group schemes
+Note that if $T_K$ and $M_L$ are $n$-congruent, then they are $m$-congruent for every
+$m \leq n$.
+
+Now let $T$ be a N\'eron model for $T_K$ and let $M$ be a N\'eron model for $M_L$.
+One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes 
+\[
+T \times_{\Spec{\OK}} \Spec{\OK/\varpi_K^m\OK} \iso M \times_{\Spec{\OL}} \Spec{\OL/\varpi_L^m\OL}
+\] 
+assuming that $T_K$ and $M_L$ are sufficiently congruent.
+They define a quantity $h$ (the smallest integer so that $\varpi^h$ lies in the
+Jacobian ideal associated to a natural embedding of $T_K$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}) and show  that if $n > 3h$ and $T_K$ and $M_L$ are $n$-congruent then there is a canonical isomorphism of smooth group schemes
  $
- \underline{T}_{N-3h} \to \underline{T}'_{N-3h}
+\Gr_{n-3h-1}(T) \to \Gr_{n-3h-1}(M)
  $
  determined by $\alpha, \beta$ and $\phi$ \cite{chai-yu:01a}*{Thm. 8.5}.
-Combining this with the paragraph above gives an instance of the geometrization and categorification of the transfer of quasicharacters.
+Combining this with the paragraph above gives the following instance of the geometrization and categorification of the transfer of quasicharacters.
 
 \begin{proposition}\label{prop:transfer}
- With notation above, suppose that $T$ and $T'$ are $N$-congruent and $N > 3h$.  Set $m = N-3h$.
+ With notation above, suppose that $T_K$ and $M_L$ are $n$-congruent and $n > 3h$.  Set $m = n-3h$.
  Then there is a canonical equivalence of categories
  \[
- \QC(\Gr^{R}_m(\underline{T})) \iso \QC(\Gr^{R'}_m(\underline{T}'))
+ \QC(\Gr^{\OK}_{m-1}(T)) \iso \QC(\Gr^{\OL}_{m-1}(M))
  \]
@@
  \[
-\Hom_m(T(K), \EEx) \iso  \Hom_m(T'(K'), \EEx)
- \]
-compatible with \eqref{transfer}.% ($m < N$).
+\Hom_{m-1}(T(K), \EEx) \iso  \Hom_{m-1}(M(L), \EEx)
+ \]
+compatible with \eqref{transfer}.
 \end{proposition}
 
-\bibliographystyle{amsalpha}
 \bibliography{bibliography/Biblio}
@@
 \end{document}
-
-\begin{table}[ht]
-\caption{A big diagram}
-\begin{center}
-{\smaller\smaller\smaller
-    \[
-  \begin{tikzcd}[row sep=20, column sep=3]
-&   &  0 \arrow{dd} && 0 \arrow{dd} && 0\arrow{dd} & \\
-& &&  0 \arrow[crossing over]{dd} && 0 \arrow[crossing over]{dd} && 0\arrow{dd} & & \\
-&   {}& \ker \TrFrob{C} \arrow[->>]{rr} \arrow[>->>]{dr} \arrow{dd} && \arrow{dd} \ker \TrFrob{B} \arrow{rr} \arrow[>->]{dr}  && \ker \TrFrob{A}=0 \arrow[>->>]{dr} \arrow{dd} \arrow{rr} && 0 & \\
-& && \Hh^0(\Weil{},\Hh^2(C,\EEx)) \arrow[crossing over,->>]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(B,\EEx)) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^0(\Weil{},\Hh^2(A,\EEx)) \arrow[crossing over]{dd}  &  &  \\
-0  \arrow{rr} & & \QCiso{C} \arrow[>->>]{dr}\arrow{rr} \arrow{dd}%{\TrFrob{C}}
-    && \QCiso{B} \arrow[>->]{dr} \arrow{rr} \arrow{dd}%{\TrFrob{B}}
-    && \QCiso{A} \arrow[>->>]{dr} \arrow{dd}%{\TrFrob{A}}
-    \arrow{rr}  &   & 0 & \\
-& \Hh^1(E^\bullet_{A}) \arrow[crossing over]{rr}  && \Hh^2(E^\bullet_{C}) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^2(E^\bullet_{B}) \arrow[crossing over]{rr} \arrow[crossing over]{dd} && \Hh^2(E^\bullet_{A}) \arrow{rr} \arrow[crossing over]{dd} &  & \Hh^3(E^\bullet_{C}) \\
-0  \arrow{rr} & & C(\Fq)^* \arrow[>->>]{dr} \arrow{rr} \arrow{dd}
-    && \arrow{dd} B(\Fq)^* \arrow[>->>]{dr} \arrow{rr} && A(\Fq)^* \arrow[>->>]{dr}  \arrow{dd}
-    \arrow{rr}&& 0 & \\
-& %\Hh^2(\Weil{},\Hh^1({\bar A},\EEx)) \arrow{rr}
- && \Hh^1(\Weil{},\Hh^1(C,\EEx)) \arrow[crossing over]{dd} \arrow[crossing over]{rr}  && \Hh^1(\Weil{},\Hh^1(B,\EEx)) \arrow[crossing over]{dd} \arrow[crossing over]{rr} && \Hh^1(\Weil{},\Hh^1(A,\EEx)) \arrow[crossing over]{dd}  &  & %\Hh^0(\Weil{},\Hh^1({\bar C},\EEx))
- \\
-& & 0  && 0  &&  0  && & \\
- &      &&  0 && 0 && 0 & & \\
-  \end{tikzcd}
-  \]
-}
-\end{center}
-\label{diagram}
-\end{table}
-
-%sagemathcloud={"zoom_width":105}

### 2014-10-01 dictionary.tex
Connected! -- was needed in the first sentence of Intro!

@@
 Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
-this paper extends Deligne's function-sheaf dictionary from commutative algebraic groups to smooth commutative group schemes over finite fields.
+this paper extends Deligne's function-sheaf dictionary from connected commutative algebraic groups to smooth commutative group schemes over finite fields.
 

### 2015-05-31 dictionary.tex
Some of the changes recommended by our JIMJ reader.
-Moved sections
-replaced `quasicharacter sheaves’ by `character sheaves’ in most of
the paper

@@
 
-\keywords{function-sheaf dictionary, trace of Frobenius, geometrization, categorification, quasicharacter sheaves, smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor, quasicharacters}
+\keywords{function-sheaf dictionary, trace of Frobenius, geometrization, categorification, character sheaves,smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor, quasicharacters, quasicharacter sheaves.}
 
@@
 \newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
+\DeclareMathOperator{\GL}{GL}
 \newcommand{\comp}{\Pi} % Component group
@@
 %% Fonts for quasicharacter sheaves
-\newcommand{\qcs}[1]{{\mathcal{#1}}}
-\newcommand{\gqcs}[1]{{\mathcal{\bar #1}}}
-\newcommand{\dualgcs}[1]{\gqcs{#1}^\dagger}
-\newcommand{\dualcs}[1]{\qcs{#1}^\dagger}
+\newcommand{\CSs}[1]{{\mathcal{#1}}}
+\newcommand{\gCSs}[1]{{\mathcal{\bar #1}}}
+\newcommand{\dualgcs}[1]{\gCSs{#1}^\dagger}
+\newcommand{\dualcs}[1]{\CSs{#1}^\dagger}
 %% Categories
-\newcommand{\QC}{{\mathcal{Q\hskip-0.8pt C}}}
-\newcommand{\lQC}{{\QC_\text{flb}}}
-\newcommand{\lQCiso}[1]{\lQC(#1)_{/\text{iso}}}
-\newcommand{\bQC}{{\QC_0}}
-\newcommand{\QCiso}[1]{\QC(#1)_{/\text{iso}}}
-\newcommand{\bQCiso}[1]{\bQC(#1)_{/\text{iso}}}
+\newcommand{\CS}{{\mathcal{C\hskip-0.8pt S}}}
+\newcommand{\lCS}{{\CS_\text{flb}}}
+\newcommand{\lCSiso}[1]{\lCS(#1)_{/\text{iso}}}
+\newcommand{\bCS}{{\CS_0}}
+\newcommand{\CSiso}[1]{\CS(#1)_{/\text{iso}}}
+\newcommand{\bCSiso}[1]{\bCS(#1)_{/\text{iso}}}
 \newcommand{\catname}[1]{\normalfont{\textsf{#1}}}
 \newcommand{\Sch}[1]{{\catname{Sch}_{/#1}}}
+\newcommand{\QCS}{{\mathcal{QC\hskip-0.8pt S}}}
+\newcommand{\QCSiso}[1]{\QCS(#1)_{/\text{iso}}}
 %% Labeled items
@@
 \newcommand{\GxxG}{\text{$G \tight{1}{\times}{1} G$}}
-\newcommand{\LxL}{\text{$\gqcs{L} \tight{0}{\boxtimes}{0} \gqcs{L}$}}
-\newcommand{\ExE}{\text{$\qcs{E}\tight{0}{\boxtimes}{0}\qcs{E}$}}
-\newcommand{\bExE}{\text{$\gqcs{E}\tight{0}{\boxtimes}{0}\gqcs{E}$}}
+\newcommand{\LxL}{\text{$\gCSs{L} \tight{0}{\boxtimes}{0} \gCSs{L}$}}
+\newcommand{\ExE}{\text{$\CSs{E}\tight{0}{\boxtimes}{0}\CSs{E}$}}
+\newcommand{\bExE}{\text{$\gCSs{E}\tight{0}{\boxtimes}{0}\gCSs{E}$}}
 \newcommand{\AxA}{\text{$A \tight{1}{\times}{1} A$}}
@@
 \begin{equation}\label{introbox}
-m^* \qcs{E} \iso \qcs{E} \boxtimes \qcs{E},
+m^* \CSs{E} \iso \CSs{E} \boxtimes \CSs{E},
 \end{equation}
@@
 %
-If one wishes to make a category from this class of local systems, one is led to consider morphisms $\qcs{E} \to \qcs{E}'$ of sheaves which are compatible with particular choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E'}$.
-{\it A priori}, the composition $\qcs{E} \to \qcs{E}' \to \qcs{E}''$ of two such morphisms need not be compatible with the choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E}''$.
+If one wishes to make a category from this class of local systems, one is led to consider morphisms $\CSs{E} \to \CSs{E}'$ of sheaves which are compatible with particular choices of \eqref{introbox} for $\CSs{E}$ and $\CSs{E'}$.
+{\it A priori}, the composition $\CSs{E} \to \CSs{E}' \to \CSs{E}''$ of two such morphisms need not be compatible with the choices of \eqref{introbox} for $\CSs{E}$ and $\CSs{E}''$.
  However, for connected $G$ the isomorphism \eqref{introbox} is unique if it exists, and there is no impediment to making the dictionary categorical.
@@
 If $G$ is a commutative algebraic group over $\Fq$ which is not connected, then the isomorphism \eqref{introbox} need not be unique.
-In order to track the choice of isomorphism, consider the category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is a chosen isomorphism of local systems on $G\times G$.
-In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\Fq)$, but the epimomorphism need not be injective; consequently,
-every character of $G(\Fq)$ may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely in the category of pairs. 
-While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious: if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\Fq)$ then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
+In order to track the choice of isomorphism, consider the category of pairs $(\CSs{E},\mu_\CSs{E})$ where $\CSs{E}$ is a rank-one local system on $G$ and $\mu_\CSs{E} : m^*\CSs{E} \to \CSs{E}\boxtimes\CSs{E}$ is a chosen isomorphism of local systems on $G\times G$.
+In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of pairs $(\CSs{E},\mu_\CSs{E})$ to characters of $G(\Fq)$, but the epimomorphism need not be injective; consequently,
+every character of $G(\Fq)$ may be geometrized as a pair $(\CSs{E},\mu_\CSs{E})$ but perhaps not uniquely in the category of pairs. 
+While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious: if $(\CSs{E},\mu_\CSs{E})$ and $(\CSs{E}',\mu_\CSs{E}')$ determine the same character of $G(\Fq)$ then $\CSs{E}\iso \CSs{E}'$ as local systems on $G$.
 
 In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\Fq$,
-we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\qcs{E}$. 
-In this way we are led to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ (\S\ref{ssec:category}).
-Objects in $\QC(G)$ are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\Fq}} \Spec{\bFq}$
-and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves satisfying certain compatibility conditions.
-Morphisms in $\QC(G)$ are then morphisms of Weil sheaves which are compatible with the extra structure.
+we simply replace the local system $\CSs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\CSs{E}$. 
+In this way we are led to the category $\CS(G)$ of {\it quasicharacter sheaves} on $G$ (\S\ref{ssec:category}).
+Objects in $\CS(G)$ are triples $(\gCSs{L}, \mu,\phi)$, where $\gCSs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\Fq}} \Spec{\bFq}$
+and $\phi : \Frob{G}^* \gCSs{L}\to \gCSs{L}$ and $\mu : {\bar m}^* \gCSs{L} \iso \gCSs{L} \boxtimes \gCSs{L}$ are isomorphisms of sheaves satisfying certain compatibility conditions.
+Morphisms in $\CS(G)$ are then morphisms of Weil sheaves which are compatible with the extra structure.
 
@@
 \'etale group schemes form a counterpoint to connected algebraic groups, since the component group of any smooth group scheme is an \'etale group scheme.
-Our key tools for understanding the trace of Frobenius in the \'etale case are a reinterpretation of $\QC(G)$ in terms of stalks (\S\ref{ssec:stalks}) and a
+Our key tools for understanding the trace of Frobenius in the \'etale case are a reinterpretation of $\CS(G)$ in terms of stalks (\S\ref{ssec:stalks}) and a
 relationship with the Hochschild-Serre spectral sequence (\S\ref{ssec:E}) for $\Weil{} \ltimes \bG$, where $\Weil{} \subset \Gal(\Fq/\Fq)$ is the Weil group for $\Fq$.
-We define (\S\ref{ssec:S}) an isomorphism $S_G$ from $\QCiso{G}$ to the second cohomology of the total space of the spectral sequence
+We define (\S\ref{ssec:S}) an isomorphism $S_G$ from $\CSiso{G}$ to the second cohomology of the total space of the spectral sequence
 \[
@@
 \[
-\TrFrob{G}: \QCiso{G} \to G(\Fq)^*
+\TrFrob{G}: \CSiso{G} \to G(\Fq)^*
 \]
@@
 One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
-%The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
+%The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gCSs{L}, \mu,\phi)$ and $(\gCSs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gCSs{L},\phi)$ and $(\gCSs{L}',\phi')$ are isomorphic as Weil sheaves.
 
@@
 While these constructions make sense even for non-connected $G$, in the connected
-case we show that every quasicharacter sheaf can be described in both of these ways (\S\ref{ssec:connected}).
+case we show that every character sheaf can be described in both of these ways (\S\ref{ssec:connected}).
 We use this fact to prove that $\TrFrob{G}$ is an isomorphism for connected commutative algebraic groups $G$
@@
 
-%The appearance of $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ and the trace of Frobenius gives an isomorphism $\TrFrob{G}: \QCiso{G} \to \Hom(G(\Fq),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\Fq$, then $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ measures the kernel of $\TrFrob{G}: \QCiso{G} \to \Hom(G(\Fq),\EEx)$.
+%The appearance of $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ and the trace of Frobenius gives an isomorphism $\TrFrob{G}: \CSiso{G} \to \Hom(G(\Fq),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\Fq$, then $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ measures the kernel of $\TrFrob{G}: \CSiso{G} \to \Hom(G(\Fq),\EEx)$.
 %This observation makes plain the fact that  . . .
@@
   \begin{tikzcd}[row sep=20, column sep=20]
-    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
-    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
+    0 \rar & \CSiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
+    & \CSiso{G} \rar \dar{\TrFrob{G}} & \CSiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
     0 \rar & \pi_0(G)(\Fq)^* \rar & G(\Fq)^* \rar & G^0(\Fq)^* \rar & 0.
@@
 \[
-\TrFrob{G} : \QCiso{G} \to G(\Fq)^*
+\TrFrob{G} : \CSiso{G} \to G(\Fq)^*
 \]
@@
 \end{theorem*}
-We also illuminate the nature of the category $\QC(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing
+We also illuminate the nature of the category $\CS(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing
 \begin{theorem*}[{Thm. \ref{thm:autornaught}}]
@@
 \[
-\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx),
-\]
-for all quasicharacter sheaves $\qcs{L}$ on $G$.
+\Aut_{\CS{}}(\CSs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx),
+\]
+for all quasicharacter sheaves $\CSs{L}$ on $G$.
 \end{theorem*}
@@
 Although not locally of finite type, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and also a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
-This structure allows us to adapt our work on quasicharacter sheaves to construct (\S\ref{ssec:qc_on_GN}) a category $\QC(X_K)$
+This structure allows us to adapt our work on character sheaves on smooth group schemes over finite fields to construct (\S\ref{ssec:CS_on_GN}) a category $\QCS(X_K)$
 of quasicharacter sheaves for $X_K$, which are certain sheaves on $\Gr_R(X)\times_{\Spec{\Fq}} \Spec{\bFq}$, with extra structure.
@@
 
-Specializing to the case that $X = T$ is the N\'eron model of an algebraic torus over $K$ (\S\ref{ssec:qc_tori}), 
+Specializing to the case that $X = T$ is the N\'eron model of an algebraic torus over $K$ (\S\ref{ssec:CS_tori}), 
 we give a canonical short exact sequence 
 \[
-0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{T_K} \to \Hom_\text{qc}(T(K),\EEx) \to 0,
-\]
-where $\Hom_\text{qc}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
-We further show that automorphism groups in $\QC(T_K)$ are given, for every quasicharacter sheaf $\qcs{F}$ for $T_K$, by
-\[
-\Aut(\qcs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
+0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCSiso{T_K} \to \Hom_\text{QC}(T(K),\EEx) \to 0,
+\]
+where $\Hom_\text{QC}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
+We further show that automorphism groups in $\CS(T_K)$ are given, for every quasicharacter sheaf $\CSs{F}$ for $T_K$, by
+\[
+\Aut_{\QCS{}}(\CSs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
 \]
@@
 When commutative, such groups are extensions of finite cyclic groups by algebraic tori,
-in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
+in which case it is not difficult to relate Frobenius-stable character sheaves to our character sheaves.
 The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in that context.
@@
 allowed us to hijack much of a Research in Teams meeting at the Banff International Research Station into a discussion of
-quasicharacter sheaves.  We thank them for their kindness, knowledge and invaluable help.
+character sheaves.  We thank them for their kindness, knowledge and invaluable help.
 We thank Takashi Suzuki for some very helpful observations and suggestions, especially related to our use of the Hochschild-Serre spectral sequence.
@@
 
-\section{The category of quasicharacter sheaves} \label{sec:category}
+\tableofcontents
+
+\section{Recollections on character sheaves} \label{sec:category}
 
@@
 
-\subsection{Quasicharacter sheaves}\label{ssec:category}
-
-\begin{definition}\label{def:QC}
-A \emph{quasicharacter sheaf on $G$} is a triple
-$\qcs{L}\ceq (\gqcs{L},\mu,\phi)$ where:
+\subsection{Character sheaves on commutative group schemes over finite fields}\label{ssec:category}
+
+\begin{definition}\label{def:CS}
+A \emph{character sheaf on $G$} is a triple
+$\CSs{L}\ceq (\gCSs{L},\mu,\phi)$ where:
 \begin{enumerate}
-\labitem{(QC.1)}{QC.1} $\gqcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean a constructible $\ell$-adic sheaf on $\bG$, {\it lisse} on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
-\labitem{(QC.2)}{QC.2} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of
+\labitem{(CS.1)}{CS.1} $\gCSs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean a constructible $\ell$-adic sheaf on $\bG$, {\it lisse} on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
+\labitem{(CS.2)}{CS.2} $\mu: \bm^* \gCSs{L} \to \LxL$ is an isomorphism of
 sheaves on $\bGxG$ such that the following diagram commutes,
@@
   \begin{tikzcd}[row sep=30]
-  \bm_3^*\gqcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
-    &&  \bm^*\gqcs{L} \boxtimes \gqcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
-    \gqcs{L} \boxtimes \bm^* \gqcs{L} \arrow{rr}{\id \boxtimes \mu}
-    &&  \gqcs{L} \tight{0}{\boxtimes}{0} \LxL
-  \end{tikzcd}
-  \]
-\labitem{(QC.3)}{QC.3} $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$ is an
+  \bm_3^*\gCSs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
+    &&  \bm^*\gCSs{L} \boxtimes \gCSs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
+    \gCSs{L} \boxtimes \bm^* \gCSs{L} \arrow{rr}{\id \boxtimes \mu}
+    &&  \gCSs{L} \tight{0}{\boxtimes}{0} \LxL
+  \end{tikzcd}
+  \]
+\labitem{(CS.3)}{CS.3} $\phi : \Frob{G}^* \gCSs{L} \to \gCSs{L}$ is an
   isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with
@@
   \begin{tikzcd}[row sep=20]
-  \Frob{\GxxG}^* \bm^* \gqcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
+  \Frob{\GxxG}^* \bm^* \gCSs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
     && \Frob{\GxxG}^*(\LxL)\\
-    \arrow[equal]{u} \bm^*  \Frob{G}^* \gqcs{L} \arrow[swap]{d}{\bm^* \phi}
-    && \Frob{G}^*\gqcs{L}\boxtimes \Frob{G}^*\gqcs{L} \dar{\phi\boxtimes \phi} \arrow[equal]{u} \\
-    \bm^*\gqcs{L} \arrow{rr}{\mu}
+    \arrow[equal]{u} \bm^*  \Frob{G}^* \gCSs{L} \arrow[swap]{d}{\bm^* \phi}
+    && \Frob{G}^*\gCSs{L}\boxtimes \Frob{G}^*\gCSs{L} \dar{\phi\boxtimes \phi} \arrow[equal]{u} \\
+    \bm^*\gCSs{L} \arrow{rr}{\mu}
     && \LxL
@@
 
-Morphisms in the category of quasicharacter sheaves on $G$, denoted by $\QC(G)$, are defined in the natural way:
+Morphisms in the category of character sheaves on $G$, denoted by $\CS(G)$, are defined in the natural way:
 \begin{enumerate}
-\labitem{(QC.4)}{QC.4} if $\qcs{L} = (\gqcs{L},\mu,\phi)$ and
-  $\qcs{L'} = (\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$ then
-  a morphism $\rho : \qcs{L} \to \qcs{L}'$ is a map $\brho : \gqcs{L} \to \gqcs{L'}$
+\labitem{(CS.4)}{CS.4} if $\CSs{L} = (\gCSs{L},\mu,\phi)$ and
+  $\CSs{L'} = (\gCSs{L'},\mu',\phi')$ are character sheaves on $G$ then
+  a morphism $\rho : \CSs{L} \to \CSs{L}'$ is a map $\brho : \gCSs{L} \to \gCSs{L'}$
   of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
@@
   \begin{tikzcd}[column sep=40]
-  \Frob{G}^* \gqcs{L} \rar{\Frob{G}^* \brho} \arrow[swap]{d}{\phi} & \Frob{G}^* \gqcs{L'} \dar{\phi'}
-  & & \arrow[swap]{d}{\mu} \bm^* \gqcs{L} \rar{\bm^* \brho} & \bm^* \gqcs{L'} \dar{\mu'} \\
-  \gqcs{L} \rar{\brho} & \gqcs{L'}
-  & {} & \LxL \rar{\tight{1}{\rho\boxtimes \rho}{1}} & \gqcs{L'} \tight{0}{\boxtimes}{0} \gqcs{L'}
+  \Frob{G}^* \gCSs{L} \rar{\Frob{G}^* \brho} \arrow[swap]{d}{\phi} & \Frob{G}^* \gCSs{L'} \dar{\phi'}
+  & & \arrow[swap]{d}{\mu} \bm^* \gCSs{L} \rar{\bm^* \brho} & \bm^* \gCSs{L'} \dar{\mu'} \\
+  \gCSs{L} \rar{\brho} & \gCSs{L'}
+  & {} & \LxL \rar{\tight{1}{\rho\boxtimes \rho}{1}} & \gCSs{L'} \tight{0}{\boxtimes}{0} \gCSs{L'}
   \end{tikzcd}
@@
 
-Category $\QC(G)$ is a rigid monoidal category
+Category $\CS(G)$ is a rigid monoidal category
 \cite{etingof:09a}*{\S1.10} under the tensor product
-$\qcs{L} \otimes \qcs{L'}$ defined by $(\gqcs{L}\otimes\gqcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
+$\CSs{L} \otimes \CSs{L'}$ defined by $(\gCSs{L}\otimes\gCSs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
 with duals given by applying the sheaf hom functor
 $\sheafHom(\ - \ ,\EE)$.
-This rigid monoidal category structure for $\QC(G)$ gives the set $\QCiso{G}$
-of isomorphism classes in $\QC(G)$ the structure of a group.
+This rigid monoidal category structure for $\CS(G)$ gives the set $\CSiso{G}$
+of isomorphism classes in $\CS(G)$ the structure of a group.
 
 \begin{remark}
-The category of quasicharacter sheaves on $G$ is not abelian since it is not closed under direct sums and thus $\QC(G)$
+The category of character sheaves on $G$ is not abelian since it is not closed under direct sums and thus $\CS(G)$
 is not a tensor category in the sense of \cite{deligne:02a}*{0.1}.  We suspect that requiring that $\mu$ be injective rather than
@@
 
-We will describe the group $\QCiso{G}$ in Theorem~\ref{thm:snake}
-and the sets $\Hom(\qcs{L},\qcs{L}')$ in Theorem~\ref{thm:autornaught}; in this way we provide a complete description of the category $\QC(G)$.
+We will describe the group $\CSiso{G}$ in Theorem~\ref{thm:snake}
+and the sets $\Hom(\CSs{L},\CSs{L}')$ in Theorem~\ref{thm:autornaught}; in this way we provide a complete description of the category $\CS(G)$.
 %
-In the meantime, we close this section with an elementary observation about $\Hom(\qcs{L},\qcs{L}')$.
+In the meantime, we close this section with an elementary observation about $\Hom(\CSs{L},\CSs{L}')$.
 We call a morphism of sheaves \emph{trivial} if it is zero on every stalk.
@@
 Let $G$ be a smooth commutative group scheme over $\Fq$.
-If $\qcs{L}$ and $\qcs{L}'$ are quasicharacter sheaves on $G$, then
-every $\rho\in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism. 
+If $\CSs{L}$ and $\CSs{L}'$ are character sheaves on $G$, then
+every $\rho\in \Hom(\CSs{L},\CSs{L}')$ is either trivial or an isomorphism. 
 \end{lemma}
@@
 \begin{proof}
-Suppose $\rho \in \Hom(\qcs{L},\qcs{L}')$.
-We prove the lemma by considering the linear transformations $\brho_{\bar g} : \gqcs{L}_{\bar g} \to \gqcs{L}_{\bar g}$ at the stalks above geometric points ${\bar g}$ on $G$ and showing that, either each $\brho_{\bar g}$ trivial or each $\brho_{\bar g}$ is an isomorphism.
+Suppose $\rho \in \Hom(\CSs{L},\CSs{L}')$.
+We prove the lemma by considering the linear transformations $\brho_{\bar g} : \gCSs{L}_{\bar g} \to \gCSs{L}_{\bar g}$ at the stalks above geometric points ${\bar g}$ on $G$ and showing that, either each $\brho_{\bar g}$ trivial or each $\brho_{\bar g}$ is an isomorphism.
 (This idea is expanded upon in Section~\ref{ssec:stalks}.)
 Let ${\bar e}$ be the geometric point above the identity $e$ for $G$ determined by our choice of algebraic closure $\bFq$ of $\Fq$.
-If $\brho_{\bar e} = 0$ then the second diagram in \ref{QC.4} implies that $\brho_{\bar g} = 0$ for all ${\bar g}$, in which case $\rho$ is trivial.
-On the other hand, if $\brho_{\bar e}$ is nontrivial then the second diagram in \ref{QC.4}  implies that $\brho_{\bar g}$ is nontrivial for all ${\bar g}$ and thus an isomorphism, since the stalk of quasicharacter sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
+If $\brho_{\bar e} = 0$ then the second diagram in \ref{CS.4} implies that $\brho_{\bar g} = 0$ for all ${\bar g}$, in which case $\rho$ is trivial.
+On the other hand, if $\brho_{\bar e}$ is nontrivial then the second diagram in \ref{CS.4}  implies that $\brho_{\bar g}$ is nontrivial for all ${\bar g}$ and thus an isomorphism, since the stalk of character sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
 \end{proof}
@@
 
-In this section we introduce two tools which will help us understand isomorphism classes of objects in $\QC(G)$: the map $\QCiso{G} \to G(k)^*$ given by trace of Frobenius and the pullback functor $\QC(G) \to \QC(H)$ associated to a morphism $H \to G$.
-
-Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
+In this section we introduce two tools which will help us understand isomorphism classes of objects in $\CS(G)$: the map $\CSiso{G} \to G(k)^*$ given by trace of Frobenius and the pullback functor $\CS(G) \to \CS(H)$ associated to a morphism $H \to G$.
+
+Let $(\gCSs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
 determines a geometric point $\bg$ fixed by $\Frob{G}$. 
-Together with the canonical isomorphism $(\Frob{G}^*\gqcs{L})_{\bg} \iso  \gqcs{L}_{\Frob{G}(\bg)}$, the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gqcs{L}_{\bg}$.
-Let $\trace(\phi_{\bg};\gqcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gqcs{L}_{\bg})$ and let $\trFrob{(\gqcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by 
+Together with the canonical isomorphism $(\Frob{G}^*\gCSs{L})_{\bg} \iso  \gCSs{L}_{\Frob{G}(\bg)}$, the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gCSs{L}_{\bg}$.
+Let $\trace(\phi_{\bg};\gCSs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gCSs{L}_{\bg})$ and let $\trFrob{(\gCSs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by 
 \begin{equation}\label{trWeil}
-\trFrob{(\gqcs{L},\phi)}(g) \ceq \trace(\phi_{\bg};\gqcs{L}_{\bg}),
+\trFrob{(\gCSs{L},\phi)}(g) \ceq \trace(\phi_{\bg};\gCSs{L}_{\bg}),
 \end{equation}
-commonly called the {\em trace of Frobenius of $(\gqcs{L},\phi)$}.
-Note that if $(\gqcs{L},\phi) \iso (\gqcs{L'},\phi')$ as Weil sheaves, 
-then $\trFrob{(\gqcs{L},\phi)} = \trFrob{(\gqcs{L'},\phi')}$ as functions on $G(\Fq)$.
-
-Now suppose $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$.
-Then the isomorphism $\bm^* \gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$ and the diagram of
-\ref{QC.3} guarantee
-that the function $\trFrob{(\gqcs{L},\phi)} : G(\Fq)\to \EEx$ is a group homomorphism, which we will also denote by $\trFrob{\qcs{L}}$.  Moreover,
-this homomorphism depends only on the isomorphism class of $\qcs{L}$, so we obtain a map
+commonly called the {\em trace of Frobenius of $(\gCSs{L},\phi)$}.
+Note that if $(\gCSs{L},\phi) \iso (\gCSs{L'},\phi')$ as Weil sheaves, 
+then $\trFrob{(\gCSs{L},\phi)} = \trFrob{(\gCSs{L'},\phi')}$ as functions on $G(\Fq)$.
+
+Now suppose $\CSs{L} = (\gCSs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$.
+Then the isomorphism $\bm^* \gCSs{L} \iso \gCSs{L} \boxtimes\gCSs{L}$ and the diagram of
+\ref{CS.3} guarantee
+that the function $\trFrob{(\gCSs{L},\phi)} : G(\Fq)\to \EEx$ is a group homomorphism, which we will also denote by $\trFrob{\CSs{L}}$.  Moreover,
+this homomorphism depends only on the isomorphism class of $\CSs{L}$, so we obtain a map
 \begin{align*}
-\TrFrob{G} : \QCiso{G} &\to G(\Fq)^*, \\
-\qcs{L} &\mapsto \trFrob{\qcs{L}}.
+\TrFrob{G} : \CSiso{G} &\to G(\Fq)^*, \\
+\CSs{L} &\mapsto \trFrob{\CSs{L}}.
 \end{align*}
-Since tensor products on the stalks of $\qcs{L}$ induce pointwise multiplication on the trace of Frobenius, $\TrFrob{G}$ is a group homomorphism.  We devote the remainder of this section to
+Since tensor products on the stalks of $\CSs{L}$ induce pointwise multiplication on the trace of Frobenius, $\TrFrob{G}$ is a group homomorphism.  We devote the remainder of this section to
 studying the behavior of the trace of Frobenius under morphisms of group schemes.  These simple but important
@@
   \begin{align*}
-  f^* : \QC(G) &\to \QC(H) \\
-  (\gqcs{L},\mu,\phi) &\mapsto (\bf^*\gqcs{L},(\bfxf)^*\mu,\bf^*F)
+  f^* : \CS(G) &\to \CS(H) \\
+  (\gCSs{L},\mu,\phi) &\mapsto (\bf^*\gCSs{L},(\bfxf)^*\mu,\bf^*F)
   \end{align*}
@@
   \begin{tikzcd}[row sep=20, column sep=30]
-   \QCiso{G} \rar{f^*} \arrow[swap]{d}{\TrFrob{G}} & \QCiso{H} \dar{\TrFrob{H}} \\
+   \CSiso{G} \rar{f^*} \arrow[swap]{d}{\TrFrob{G}} & \CSiso{H} \dar{\TrFrob{H}} \\
    G(\Fq)^* \rar & H(\Fq)^*
@@
 \begin{proof}
-  Let $\qcs{L}$ be a quasicharacter sheaf on $G$. 
+  Let $\CSs{L}$ be a character sheaf on $G$. 
   Pullback by $\bf$ takes rank-one local systems to rank-one local systems.
-  To see that $(\bfxf)^* \mu$ satisfies \ref{QC.2},
+  To see that $(\bfxf)^* \mu$ satisfies \ref{CS.2},
   apply the functor $(\bfxf)^*$
-  to \ref{QC.2} for $\qcs{L}$ and use the canonical isomorphism
-  $(\bfxf)^*(\LxL) \iso \bf^*\gqcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gqcs{L}$.
-  To show that $f^*\qcs{L}$ satisfies
-  \ref{QC.3}, apply the same functor to \ref{QC.3} for $\qcs{L}$.
+  to \ref{CS.2} for $\CSs{L}$ and use the canonical isomorphism
+  $(\bfxf)^*(\LxL) \iso \bf^*\gCSs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gCSs{L}$.
+  To show that $f^*\CSs{L}$ satisfies
+  \ref{CS.3}, apply the same functor to \ref{CS.3} for $\CSs{L}$.
   Since $f$ is a morphism of group schemes defined over $\Fq$
@@
 
-  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{QC.4} defines the action
-  of $f^*$ on morphisms of quasicharacter sheaves; arguing as above shows that $f^*$ is
-  a functor from $\QC(G)$ to $\QC(H)$.  Since tensor products commute with pullback in schemes,
-  $f^* : \QC(G) \to \QC(H)$ is a monoidal functor.
-  The diagram relating $f^* : \QC(G) \to \QC(H)$, $f^* : G(k)^* \to H(k)^*$ and trace of Frobenius
+  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{CS.4} defines the action
+  of $f^*$ on morphisms of character sheaves; arguing as above shows that $f^*$ is
+  a functor from $\CS(G)$ to $\CS(H)$.  Since tensor products commute with pullback in schemes,
+  $f^* : \CS(G) \to \CS(H)$ is a monoidal functor.
+  The diagram relating $f^* : \CS(G) \to \CS(H)$, $f^* : G(k)^* \to H(k)^*$ and trace of Frobenius
   commutes by \cite{laumon:87a}*{1.1.1.2}, where the ambient
@@
 If $G_1$ and $G_2$ are smooth commutative group schemes over $\Fq$ then the rule
-$\boxtimes : (\qcs{L}_1,\qcs{L}_2)\to \qcs{L}_1\boxtimes\qcs{L}_2$ defines an equivalence of categories
-\[
-\boxtimes : \QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)
+$\boxtimes : (\CSs{L}_1,\CSs{L}_2)\to \CSs{L}_1\boxtimes\CSs{L}_2$ defines an equivalence of categories
+\[
+\boxtimes : \CS(G_1)\times \CS(G_2) \to \CS(G_1\times G_2)
 \]
@@
 \begin{tikzcd}[column sep=60]
-\arrow{d}{\TrFrob{G_1} \times \TrFrob{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes}
-& \arrow{d}{\TrFrob{G_1\times G_2}} \QCiso{G_1\times G_2}\\
+\arrow{d}{\TrFrob{G_1} \times \TrFrob{G_2}} \CSiso{G_1}\times \CSiso{G_2} \arrow{r}{\boxtimes}
+& \arrow{d}{\TrFrob{G_1\times G_2}} \CSiso{G_1\times G_2}\\
 (G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
@@
 \[\boxtimes
- : \QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)
+ : \CS(G_1)\times \CS(G_2) \to \CS(G_1\times G_2)
  \]
@@
 %
-Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$
-and set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$.
-By Lemma~\ref{lem:pullback}, $\qcs{L}_1$ is a quasicharacter sheaf on $G_1$
-and $\qcs{L}_2$ is a quasicharacter sheaf on $G_2$.
-We will obtain an isomorphism $\qcs{L} \iso  \qcs{L}_1\boxtimes \qcs{L}_2$.
+Now, let $\CSs{L} \ceq (\gCSs{L},\mu,\phi)$ be a character sheaf on $G$
+and set $\CSs{L}_1 \ceq q_1^* \CSs{L}$ and $\CSs{L}_2 \ceq q_2^* \CSs{L}$.
+By Lemma~\ref{lem:pullback}, $\CSs{L}_1$ is a character sheaf on $G_1$
+and $\CSs{L}_2$ is a character sheaf on $G_2$.
+We will obtain an isomorphism $\CSs{L} \iso  \CSs{L}_1\boxtimes \CSs{L}_2$.
+
 Applying the functor $f^*$ to the isomorphism $\mu$ yields
 \begin{equation}\label{eq:fm}
-f^*\mu : f^* m^* \gqcs{L} \to f^*(\gqcs{L}\boxtimes \gqcs{L}) .
+f^*\mu : f^* m^* \gCSs{L} \to f^*(\gCSs{L}\boxtimes \gCSs{L}) .
 \end{equation}
-We have already seen that $m\circ f = \id_G$, so $f^* m^* \gqcs{L} = \gqcs{L}$.  
-Since $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L} = r_1^* \gqcs{L}_1$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L} = r_2^*\gqcs{L}_2$,
+We have already seen that $m\circ f = \id_G$, so $f^* m^* \gCSs{L} = \gCSs{L}$.  
+Since $f^*p_1^*\gCSs{L} = r_1^* q_1^* \gCSs{L} = r_1^* \gCSs{L}_1$ and $f^*p_2^*\gCSs{L} = r_2^* q_2^* \gCSs{L} = r_2^*\gCSs{L}_2$,
 we have 
 \[
-f^*(\gqcs{L}\boxtimes \gqcs{L})  = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L} = \gqcs{L}_1\boxtimes \gqcs{L}_2.
-\]
-It follows that \eqref{eq:fm} gives an isomorphism $\gqcs{L} \to  \gqcs{L}_1\boxtimes \gqcs{L}_2$.
+f^*(\gCSs{L}\boxtimes \gCSs{L})  = f^*p_1^*\gCSs{L}\otimes f^* p_2^*\gCSs{L} = \gCSs{L}_1\boxtimes \gCSs{L}_2.
+\]
+It follows that \eqref{eq:fm} gives an isomorphism $\gCSs{L} \to  \gCSs{L}_1\boxtimes \gCSs{L}_2$.
 It is routine to show that this morphism satisfies
-\ref{QC.4} as it applies here,
+\ref{CS.4} as it applies here,
 from which it follows that we have exhibited an isomorphism
-$\qcs{L} \to \qcs{L}_1\boxtimes \qcs{L}_2$ of quasicharacters sheaves on $G\times G$.
+$\CSs{L} \to \CSs{L}_1\boxtimes \CSs{L}_2$ of quasicharacters sheaves on $G\times G$.
 This completes the proof that $\boxtimes$ is essentially surjective.
@@
 \begin{proposition}\label{prop:functorialG}
-The homomorphism $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ defines a natural transformation
+The homomorphism $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ defines a natural transformation
 between the two contravariant additive functors
 \begin{align*}
-F_1 : G &\mapsto \QCiso{G} \\
+F_1 : G &\mapsto \CSiso{G} \\
 F_2 : G &\mapsto G(\Fq)^*
@@
 
-\section{Quasicharacter sheaves on \'etale commutative group schemes} \label{sec:etale}
-
-In this section we find a complete characterization of the category of quasicharacter sheaves on \'etale commutative group schemes over finite fields.
-
-\subsection{Stalks of quasicharacter sheaves}\label{ssec:stalks}
-
-The equivalence $G \mapsto G(\bFq)$,
-from the category of \'etale commutative group schemes over $\Fq$ to the category of commutative groups equipped
-with a continuous action of $\Gal(\bFq/\Fq)$,
-provides the following simple description of quasicharacter sheaves.
-%
-A quasicharacter sheaf $\qcs{L}$ on an \'etale commutative group scheme $G$ over $\Fq$ is:
-\begin{enumerate}
- \labitem{(qc.1)}{qc.1} an indexed set of one-dimensional
-  $\EE$-vector spaces $\gqcs{L}_x$, as $x$ runs over
-  $G(\bFq)$;
-
- \labitem{(qc.2)}{qc.2} an indexed set of isomorphisms
-  $\mu_{x,y} : \gqcs{L}_{x+y} \xrightarrow{\iso} \gqcs{L}_{x} \otimes\gqcs{L}_{y}$,
-  for all $x,y \in G(\bFq)$, such that
-  \[
-   \begin{tikzcd}[row sep=40]
-    \gqcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
-    && \gqcs{L}_{x+y}\otimes\gqcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
-    \gqcs{L}_{x} \otimes\gqcs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
-    && \gqcs{L}_{x} \otimes\gqcs{L}_{y} \otimes\gqcs{L}_{z}
-   \end{tikzcd}
-  \]
-  commutes, for all $x,y,z\in G(\bFq)$; and
- \labitem{(qc.3)}{qc.3} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
-  such that
-  \[
-   \begin{tikzcd}[row sep=40]
-    \gqcs{L}_{\Frob{}(x)+\Frob{}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{}(x),\Frob{}(y)}}
-    && \gqcs{L}_{\Frob{}(x)}\otimes\gqcs{L}_{\Frob{}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
-    \gqcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
-    && \gqcs{L}_x \otimes\gqcs{L}_y
-   \end{tikzcd}
-  \]
-  commutes, for all $x,y\in G(\bFq)$.
-\end{enumerate}
-Under this equivalence, a morphism $\rho : \qcs{L} \to \qcs{L'}$ of quasicharacter sheaves on $G$ is given by
-\begin{enumerate}
- \labitem{(qc.4)}{qc.4} an indexed set $\brho_x : \gqcs{L}_x \to \gqcs{L'}_x$
-  of linear transformations such that
-  \[
-   \begin{tikzcd}[column sep=40]
-    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{}(x)} \rar{\brho_{\Frob{}(x)}} & \gqcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
-    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-    & \arrow[swap]{d}{\mu_{x,y}} \gqcs{L}_{x+y} \rar{\brho_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x,y}} \\
-    \gqcs{L}_x \rar{\brho_x} & \gqcs{L'}_x
-    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\brho_x\otimes\brho_y} & \gqcs{L'}_x \otimes\gqcs{L'}_y
-   \end{tikzcd}
-  \]
-  both commute, for all $x, y \in G(\bFq)$.
-\end{enumerate}
-
-We will see that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ may not provide complete
-information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not a connected algebraic group.
-Our main tool for understanding this phenomenon
-is a group homomorphism $S_G: \QCiso{G} \to \Hh^2(E^\bullet_G)$ defined in Section~\ref{ssec:S}, for which the next two sections are preparation.
-
-\subsection{A spectral sequence}\label{ssec:E}
-
-The zeroth page of the Hochschild-Serre spectral sequence
-is a double complex $E^{\bullet, \bullet}$ defined by
-\[
-E^{i,j} = C^i(\Weil{}, C^j(G(\bFq), \EEx));
-\]
-see \cite{vakil:Algebraic_Geometry}*{\S 1.7}, expanding on \cite{weibel:Homological_Algebra}*{Ch 5 and \S 7.5}.
-The standard derivative on cochains yields two derivatives,
-\begin{align*}
-d_G &: E^{i,j} \to E^{i,j+1} \quad \mbox{and} \\
-d_{\Weil{}} &: E^{i,j} \to E^{i+1,j};
-\end{align*}
-we use the first as the derivative $d_0$ on the zeroth page, and the second to induce $d_1$.
-Combining them also yields a derivative $d = d_G + (-1)^j d_{\Weil{}}$ on the total complex
-\[
-E^n_G = \bigoplus_{i+j=n} E^{i,j}.
-\]
-The machinery of spectral sequences gives us a sequence of pages $E_r^{i,j}$, converging to a page $E_{\infty}^{i,j}$.
-We summarize the key properties of this spectral sequence in the following proposition.
-
-\begin{proposition} In the spectral sequence defined above,
-\begin{enumerate}
-\item the second page is given by $E_2^{i,j} = \Hh^i(\Weil{}, \Hh^j(G(\bFq), \EEx))$,
-\item there is an isomorphism $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) \cong \Hh^n(E_G^\bullet)$, and
-\item there is a filtration $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) = F_n \supset \cdots \supset F_{-1} = 0$, with $F_i / F_{i-1} \cong E_{\infty}^{i, n-i}$.
-\end{enumerate}
-\end{proposition}
-
-Moreover, since $\Weil{} \cong \ZZ$ has cohomological dimension $1$, $E_2^{i,j} = 0$ for $i > 1$ and the sequence degenerates at the second page: $E_{\infty}^{i,j} = E_2^{i,j}$.
-We obtain the following corollary:
-
-\begin{corollary}\label{cor:spectral_ses}
-There is a short exact sequence
- \[
-    0 \to
-    \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to
-    \Hh^2(E^\bullet_G) \to
-    \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to
-    0.
- \]
-\end{corollary}
-
-This sequence will play a key role in understanding the kernel of $\TrFrob{G}$, as described in the next few sections.
-For this application, we need a good understanding of these maps to and from the total complex.
-
-\begin{proposition} \label{prop:ses_desc}
-Consider the short exact sequence in Corollary~\ref{cor:spectral_ses}.
-\begin{enumerate}
-\item Every class $[\alpha\oplus\beta\oplus\gamma] \in \Hh^2(E^\bullet_G)$ is cohomologous to one with $\gamma=0$.
-\item The map $\Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx))$ is given by $[\alpha\oplus\beta\oplus 0] \mapsto [\beta]$.
-\item Suppose $a \in Z^2({\bar G}, \EEx)$ represents a class in $\Hh^2({\bar G},\EEx)$ fixed by Frobenius.
-The map $\Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to \Hh^2(E^\bullet_G)$ is given by $[a] \mapsto [a \oplus 0 \oplus 0]$.
-\end{enumerate}
-\end{proposition}
-\begin{proof}
-Since $\Hh^2(\Weil{}, C^0({\bar G}, \EEx)) = 0$, we may find a $\gamma_1 \in C^1(\Weil{}, C^0({\bar G}, \EEx))$ with $d_{\Weil{}}\gamma_1 = \gamma$.
-Subtracting $d \gamma_1$ from $\alpha\oplus\beta\oplus\gamma$, we may assume that $\gamma = 0$.
-
-The latter two claims follow from tracing through the definition of latter pages in the spectral sequence.
-\end{proof}
-
-\subsection{From quasicharacter sheaves to the total complex}\label{ssec:S}
-
-In this section we define an isomorphism
-\[
-S_G : \QCiso{G} \to \Hh^2(E^\bullet_G).
-\]
-Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
-For each geometric point $x\in {\bar G}$, choose a basis $\{ v_x \}$ for $\gqcs{L}_x$.
-Through this choice, $\qcs{L}$ determines functions
-\begin{align*}
-a : {\bar G}\times {\bar G} &\to \EEx & b : {\bar G} &\to \EEx \\
-\mu_{x,y}(v_{x+y}) &= a(x,y) v_x \otimes v_y & \phi_x(v_{\Frob{G}(x)}) &= b(x) v_x.
-\end{align*}
-Condition~\ref{QC.2} implies that
-\begin{equation}\label{2-cocyle}
-a(x+y,z) a(x,y) = a(x,y+z) a(y,z)
-\end{equation}
-for all $x,y,z\in {\bar G}$, so $a \in Z^2({\bar G},\EEx)$.  Similarly, condition~\ref{QC.3} gives
-\begin{equation}\label{nohom}
-\frac{a(\Frob{G}(x),\Frob{G}(y))}{a(x,y)} =  \frac{b(x+y)}{b(x) b(y)}
-\end{equation}
-for $x, y \in {\bar G}$.
-Let $\alpha \in C^0(\Weil{},C^2({\bar G},\EEx)$ be the $0$-cochain corresponding to $a$ and let $\beta\in C^1(\Weil{},C^1({\bar G},\EEx)$ be the cocycle such that $\beta(\Frob{})$ is $b$.
-We will write both $\alpha$ and $\beta$ additively.
-Then
-\[
-d_G\alpha =0, \qquad\qquad
-d_{\Weil{}} \alpha = d_{G} \beta,\qquad\qquad
-d_{\Weil{}} \beta =0;
-\]
-in other words,
-\[\alpha\oplus \beta \in Z^2(E^\bullet_G).\]
-Although the cocycle $\alpha\oplus \beta$ is not well defined by $\qcs{L}$, its class in $\Hh^2(E^\bullet_G)$ is.
-To see this, let $\{ v'_x \in \gqcs{L}_x^\times \tq x \in {\bar G}\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$ be defined by $\qcs{L}$ and this choice, as above.
-Now let $\delta \in C^0(\Weil{},C^1({\bar G},\EEx))$ correspond to the function $d : {\bar G}\to \EEx$ defined by $v'_x = d(x) v_x$.
-Chasing through \ref{QC.2} and \ref{QC.3}, we find
-\[
-\alpha'\oplus\beta' = \alpha\oplus\beta + d\delta,
-\]
-so the class $[\alpha\oplus\beta]$ of $\alpha\oplus\beta$ in $\Hh^2(E^\bullet_G)$ is independent of the choice made above.
-It is also easy to see that $[\alpha\oplus\beta] = [\alpha_0\oplus\beta_0]$ when $\qcs{L} \iso \qcs{L}_0$,
-which concludes the definition of the function
-\begin{align*}
-S_G : \QCiso{G} &\to \Hh^2(E^\bullet_G)\\
-[\qcs{L}] &\mapsto [\alpha\oplus \beta].
-\end{align*}
-It is also easy to see that $[\alpha_1\oplus\beta_1] + [\alpha_2\oplus\beta_2] = [\alpha_3\oplus\beta_3]$ when $\qcs{L}_3 = \qcs{L}_1\otimes \qcs{L}_2$, so $S_G$ is a group homomorphism.
-
-\begin{remark}
-Although we will only use the group homomorphism $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an \'etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$.
-However, the next result is false in that context.
-\end{remark}
-
-\begin{proposition}\label{prop:SGiso}
-If $G$ is \'etale then $S_G$ is an isomorphism.
-\end{proposition}
-\begin{proof}
-Suppose $[\qcs{L}] \in \QCiso{G}$ with $S_G([\qcs{L}]) = [\alpha \oplus \beta] = 0$,
-so that $\alpha \oplus \beta = d\sigma$ for some $\sigma \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
-For each $x\in {\bar G}$, define $\sigma_x : \gqcs{L}_x \to \EE$ by $\sigma_x : v_x \mapsto \sigma(x)$.
-Then the indexed set of isomorphisms $\{ \sigma_x : \gqcs{L}_x \to \EE \tq x\in {\bar G}\}$
-defines an isomorphism $\qcs{L} \to (\EE)_G$.
-Since $\qcs{L} = 0 \in \QCiso{G}$, $S_G$ is injective.
-
-To see that $S_G$ is surjective, begin with $\alpha\oplus\beta\oplus 0 \in Z^2(E^\bullet_G)$.
-Since $d_{\Weil{}} \beta = 0$, we may define $a = \alpha \in C^2({\bar G},\EEx)$ and
-$b = \beta(\Frob{}) \in C^1({\bar G},\EEx)$, which are related to $\alpha$ and $\beta$ as above.
-Set $\gqcs{L}_x = \EE$, define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes\gqcs{L}_y$
-by $\mu_{x,y}(1) = a(x,y) (1\otimes 1)$ and $\phi_x : \gqcs{L}_{\Frob{G}(x)} \to \gqcs{L}_x$ by $\phi_x(1)= b(x)$.
-Then \ref{qc.1} holds since $d_G \alpha =0$ and \ref{qc.2} holds since $d_{\Weil{}}\alpha =d_G \beta$.
-Tracing the construction backward, we have defined a quasicharacter sheaf $\qcs{L}$ on $G$ with
-$S_G(\qcs{L}) = [\alpha\oplus\beta\oplus 0]$, showing that $S_G$ is surjective.
-\end{proof}
-
-\subsection{Objects in the \'etale case}\label{ssec:SandT}
-
-In this section we fit the group homomorphisms $\TrFrob{G}$ and $S_G$ into a commutative diagram, determining the kernel and cokernel of the homomorphism $\TrFrob{G} : \QCiso{G} \to G(k)^*$ when $G$ is an \'etale commutative group scheme over $\Fq$.
-
-%
-We begin with a simple, general result relating duals, invariants and coinvariants.
-
-\begin{lemma} \label{lem:dual-inv}
-Let $X$ be an abelian group equipped with an action of $\Weil{}$.  Then
-\begin{align*}
- (X^*)_{\Weil{}} &\to (X^{\Weil{}})^* \\
- [f] &\mapsto f|_{X^{\Weil{}}}
-\end{align*}
-is an isomorphism.
-\end{lemma}
-
-\begin{proof}
-We can describe $X^{\Weil{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
-let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
-\[
- 0 \to X^{\Weil{}} \to X \to Y \to 0
-\]
-yields
-\[
- 0 \to Y^* \to X^* \to (X^{\Weil{}})^* \to \Ext^1_\ZZ(Y, \EEx).
-\]
-Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Weil{}})^*$.
-\end{proof}
-
-\begin{proposition}\label{prop:sur_etale}
-If $G$ is \'etale, then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective
-and split.
-\end{proposition}
-\begin{proof}
-Pick $\chi \in G(\Fq)^*$. 
-Let $[\beta]\in \Hh^1(\Weil{},\bG^*)$ be the class corresponding to $\chi$ under Lemma~\ref{lem:dual-inv}.
-Every representative cocycle $\beta \in Z^1(\Weil{},\bG^*)$ determines a homomorphism $\beta(\Frob{}) : G(\bFq)\to \EEx$ such that $\beta(\Frob{})\vert_{G(\Fq)} = \chi$.
-Set $\gqcs{L}_x = \EE$ for every $x\in G(\bFq)$.
-Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$ and
-$\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = \beta(\Frob{})(x)$.
-Since $\beta(\Frob{}) : G(\bFq) \to \EEx$ is a group homomorphism,
-condition \eqref{nohom} is satisfied with $a =1$.
-So $\qcs{L} = (\gqcs{L}, \mu, \phi)$
-is a quasicharacter sheaf with $\trFrob{\qcs{L}} = \chi$.
-This shows that $\TrFrob{G}$ is surjective.
-
-Now let $\beta' \in Z^1(\Weil{},\bG^*)$ be another representative for $[\beta]$
-so $\beta-\beta' = d_{\Weil{}} \delta$ for some $\delta \in C^0(\Weil{},\bG^*)$ defining $d \in \Hom(G(\bFq),\EEx)$.
-Let $\qcs{L}'$ be the quasicharacter sheaf on $G$ defined by $\beta'$, as above.
-For each $x\in G(\bFq)$, define $\brho_x :\qcs{L}_x\to \qcs{L}'_x$ by $\brho_x(1) = d(x)$.
-The collection of isomorphisms $\{ \brho_x \tq x\in G(\bFq)\}$ satisfies condition~\ref{qc.4}, so it defines a morphism $\rho : \qcs{L}\to \qcs{L}'$, which is clearly an isomorphism. 
-%
-We have now defined a section of $\TrFrob{G}$.
-
-Now suppose $\chi_1, \chi_2 \in G(\Fq)^*$.
-Pick cocycles $\beta_1,\beta_2\in Z^1(\Weil{},\bG^*)$ and construct quasicharacter sheaves $\qcs{L}_1$ and $\qcs{L}_2$ on $G$ as above.
-Since $\qcs{L}_1\otimes \qcs{L}_2$ is exactly the quasicharacter sheaf built from the cocycle $\beta_1\cdot \beta_2$, and since $\trFrob{\qcs{L}_1\otimes \qcs{L}_2} = \trFrob{\qcs{L}_1}\cdot \trFrob{\qcs{L}_2}$, the section of $\TrFrob{G}$ defined here is a homomorphism.
-\end{proof}
-
-\begin{proposition} \label{prop:etale-iso}
- If $G$ is \'etale then the map $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ induces an isomorphism of split short exact sequences
-\[
-\begin{tikzcd}
- 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \QCiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
-  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r} & 0.
- \end{tikzcd}
- \]
-\end{proposition}
-\begin{proof}
-This result follows from Propositions~\ref{prop:ses_desc}, \ref{prop:SGiso} and \ref{prop:sur_etale}.
-\end{proof}
-
-\subsection{Morphisms in the \'etale case}\label{ssec:mor-etale}
-
-While most of this paper focuses on the question of determining the isomorphism classes of objects, a complete understanding of the morphisms in $\QC(G)$ also requires a description of the automorphisms of an arbitrary quasicharacter sheaf $\qcs{L}$.
-
-\begin{proposition}\label{prop:autornaught_etale}
-Let $G$ be an \'etale commutative group scheme over $\Fq$.
-If $\qcs{L}$ and $\qcs{L}'$ are quasicharacter sheaves on $G$ then
-every $\rho\in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism. Moreover, the trace map induces an isomorphism of groups
-\[
-\Aut(\qcs{L}) \to \Hom(G(\bFq)_{\Weil{}}, \EEx).
-\]
-\end{proposition}
-
-\begin{proof}
-We have already seen, in Lemma~\ref{lem:autornaught}, that every $\rho\in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism.
-Now suppose $\rho \in \Aut(\qcs{L})$.
-The second diagram in \ref{qc.4} shows that the association $x \mapsto \brho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{qc.4} shows that it factors through $G(\bFq)_{\Weil{}}$.
-
-Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism, then defining $\brho_x$ as multiplication by $\rho(x)$ will define a morphism $\gqcs{L} \to \gqcs{L}'$ satisfy the two diagrams in \ref{qc.4}.
-
-Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the resulting bijection is actually a group isomorphism.
-\end{proof}
-
-\section{Quasicharacter sheaves on connected commutative algebraic groups} \label{sec:disc-isog}
-
-Before turning our attention to quasicharacter sheaves on connected commutative algebraic groups in Section~\ref{ssec:connected}, we treat two special classes of quasicharacter sheaves on arbitrary smooth commutative group schemes $G$:  in Section~\ref{ssec:descentG}, those that descend from local systems on $\bG$ to local systems on $G$; and in Section~\ref{ssec:discrete_isogenies}, those that are defined by discrete isogenies onto $G$.
+%\subsection{character sheaves on connected commutative algebraic groups} \label{sec:disc-isog}
+
+\subsection{Descent}\label{ssec:descentG}
+
+Before turning our attention to character sheaves on connected commutative algebraic groups in Section~\ref{ssec:connected}, we treat two special classes of character sheaves on arbitrary smooth commutative group schemes $G$: those that descend from local systems on $\bG$ to local systems on $G$ (\S \ref{ssec:descentG}); and those that are defined by discrete isogenies onto $G$ (\S \ref{ssec:discrete_isogenies}).
 The latter will play a role in Sections~\ref{ssec:connected} and \ref{ssec:restriction}.
 
-\subsection{Descent to G}\label{ssec:descentG}
-
 In this section we consider a category of sheaves on $G$ obtained by
-replacing the Weil sheaf $(\gqcs{L}, \phi)$ on $\bG$ in the definition of a quasicharacter sheaf with an $\ell$-adic local system on $G$ itself.
+replacing the Weil sheaf $(\gCSs{L}, \phi)$ on $\bG$ in the definition of a character sheaf with an $\ell$-adic local system on $G$ itself.
 
 \begin{definition}
-Let $\bQC(G)$ be the category of pairs $(\qcs{E},\mu_\qcs{E})$
-where $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank-one,
-equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes \qcs{E}$
-satisfying the analogue of \ref{QC.2} on $G$;
-morphisms in $\bQC(G)$ are defined as in the second part of
-\ref{QC.4}.
+Let $\bCS(G)$ be the category of pairs $(\CSs{E},\mu_\CSs{E})$
+where $\CSs{E}$ is an $\ell$-adic local system on $G$ of rank-one,
+equipped with an isomorphism $\mu_\CSs{E} : m^* \CSs{E} \to \CSs{E} \boxtimes \CSs{E}$
+satisfying the analogue of \ref{CS.2} on $G$;
+morphisms in $\bCS(G)$ are defined as in the second part of
+\ref{CS.4}.
 \end{definition}
 
-We put a rigid monoidal structure on $\bQC(G)$ in the same way as for $\QC(G)$.
+We put a rigid monoidal structure on $\bCS(G)$ in the same way as for $\CS(G)$.
 
@@
 \[
-B_G : \bQC(G) \to \QC(G).
+B_G : \bCS(G) \to \CS(G).
 \]
@@
 \begin{proof}
- Suppose $(\qcs{E},\mu_\qcs{E})$ in an object of $\bQC(G)$.
+ Suppose $(\CSs{E},\mu_\CSs{E})$ in an object of $\bCS(G)$.
  Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Set $\gqcs{L} = b_G^* \qcs{E}$. 
+ Set $\gCSs{L} = b_G^* \CSs{E}$. 
  The functor $b_G^*$ takes local systems on $G$ to local systems on $\bG$.
- The local system $\gqcs{L}$ comes equipped with an isomorphism
- $\phi: \Frob{G}^* \gqcs{L} \to \gqcs{L}$.
- The resulting functor from local systems on $G$ to Weil local systems on $\bG$, given on objects by $\qcs{E} \mapsto (\gqcs{L},\phi)$, 
+ The local system $\gCSs{L}$ comes equipped with an isomorphism
+ $\phi: \Frob{G}^* \gCSs{L} \to \gCSs{L}$.
+ The resulting functor from local systems on $G$ to Weil local systems on $\bG$, given on objects by $\CSs{E} \mapsto (\gCSs{L},\phi)$, 
  is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} and \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}.
- The isomorphism $\mu \ceq b_{G\times G}^*\mu_\qcs{E}$ satisfies \ref{QC.2}
- for $\gqcs{L}$ and $\phi$ is compatible with $\mu$ in the sense of \ref{QC.3}.
- This construction defines the functor $B_G : \bQC(G) \to \QC(G)$ given on objects by $(\qcs{E},\mu_\qcs{E}) \mapsto (\gqcs{L},\mu, \phi)$, as defined here. 
- Because morphisms in $\bQC(G)$ and $\QC(G)$ are morphisms of local systems on $G$ and $\bG$, respectively, satisfying condition~\ref{QC.4}, this functor is also full and faithful.
-\end{proof}
-
-We will say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ \emph{descends to $G$} if it is isomorphic to some $B_G(\qcs{E}, \mu_\qcs{E})$.
+ The isomorphism $\mu \ceq b_{G\times G}^*\mu_\CSs{E}$ satisfies \ref{CS.2}
+ for $\gCSs{L}$ and $\phi$ is compatible with $\mu$ in the sense of \ref{CS.3}.
+ This construction defines the functor $B_G : \bCS(G) \to \CS(G)$ given on objects by $(\CSs{E},\mu_\CSs{E}) \mapsto (\gCSs{L},\mu, \phi)$, as defined here. 
+ Because morphisms in $\bCS(G)$ and $\CS(G)$ are morphisms of local systems on $G$ and $\bG$, respectively, satisfying condition~\ref{CS.4}, this functor is also full and faithful.
+\end{proof}
+
+We will say that a character sheaf $\CSs{L} \in \CS(G)$ \emph{descends to $G$} if it is isomorphic to some $B_G(\CSs{E}, \mu_\CSs{E})$.
 
@@
 Let $\psi : A \to \EEx$ be the character of $V$.
-Then $(f_! V_H)_\psi$ (the $\psi$-isotypic component of $f_!V_H$) is an object of $\bQC(G)$.
+Then $(f_! V_H)_\psi$ (the $\psi$-isotypic component of $f_!V_H$) is an object of $\bCS(G)$.
 \end{proposition}
@@
 \begin{proof}
-Let $f$, $A$, $V$ and $\psi$ be as above and set $\qcs{E} = (f_! V_H)_\psi$.
-Since $A$ is abelian, $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank one.
-We must show that $\qcs{E}$ comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
+Let $f$, $A$, $V$ and $\psi$ be as above and set $\CSs{E} = (f_! V_H)_\psi$.
+Since $A$ is abelian, $\CSs{E}$ is an $\ell$-adic local system on $G$ of rank one.
+We must show that $\CSs{E}$ comes equipped with an isomorphism $\mu_\CSs{E} : m^* \CSs{E} \to \CSs{E}\boxtimes\CSs{E}$.
 To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$ {\it cf.\ } \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}.
-In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
-Since $f$ is a morphism of group schemes, the functor $f^*$ defines $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$
+In particular, $f^*\CSs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
+Since $f$ is a morphism of group schemes, the functor $f^*$ defines $\mu_\CSs{E} : m^*\CSs{E} \to \CSs{E}\boxtimes\CSs{E}$
 from the isomorphism $m^*\psi \iso \psi \boxtimes\psi$ determined by $V\to V\otimes V$.
@@
 
-\subsection{The classical function-sheaf dictionary revisited}\label{ssec:connected}
-
-In general, $\bQC(G)$ is an essentially
-proper subcategory of $\QC(G)$. 
+\subsection{The function-sheaf dictionary for connected algebraic groups over finite fields}\label{ssec:connected}
+
+In general, $\bCS(G)$ is an essentially
+proper subcategory of $\CS(G)$. 
 However, if $G$ is connected and of finite type, the categories are equivalent, as we now show.
@@
 \[
-B_G : \bQC(G) \to \QC(G)
+B_G : \bCS(G) \to \CS(G)
 \]
@@
 
-  Now let $(\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$
-  and let $\lambda : \Weil{}(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$.
+  Now let $(\gCSs{L},\mu,\phi)$ be a character sheaf on $G$
+  and let $\lambda : \Weil{}(G, \bg) \to \EEx$ be the character determined by $(\gCSs{L},\phi)$.
   Composing with the splitting $\Weil{} \to \Weil{}(G,\bg)$ yields an $\ell$-adic character
@@
   $
-  \lambda_g(\Frob{}) =  \trFrob{\qcs{L}}(g).
+  \lambda_g(\Frob{}) =  \trFrob{\CSs{L}}(g).
   $
 %
-  On the other hand, we have already seen that $\trFrob{\qcs{L}} : G(\Fq) \to \EEx$
+  On the other hand, we have already seen that $\trFrob{\CSs{L}} : G(\Fq) \to \EEx$
   is a group homomorphism. 
   Since $G$ is an algebraic group over $\Fq$, $G(\Fq)$ is finite.
-  Therefore $\trFrob{\qcs{L}}(g) = \lambda_g(\Frob{})$ is a root of unity
+  Therefore $\trFrob{\CSs{L}}(g) = \lambda_g(\Frob{})$ is a root of unity
   for every $g\in G(\Fq)$.  Since $\Weil{}$ is generated by
@@
   representations of $\pi_1(G,\bg)$ and $\ell$-adic local systems on $G$. Let
-  $\qcs{E}$ be a local system on $G$ in the isomorphism class
+  $\CSs{E}$ be a local system on $G$ in the isomorphism class
   determined by this $\ell$-adic character of $\pi_1(G,\bg)$.
-  Then $b_G^*\qcs{E} \iso \gqcs{L}$.
+  Then $b_G^*\CSs{E} \iso \gCSs{L}$.
 
@@
  \[
-  b_{G\times G}^* : \Hom(m^*\qcs{E},\qcs{E}\boxtimes\qcs{E}) \to \Hom({\bar m}^*\gqcs{L},\gqcs{L}\boxtimes\gqcs{L})
+  b_{G\times G}^* : \Hom(m^*\CSs{E},\CSs{E}\boxtimes\CSs{E}) \to \Hom({\bar m}^*\gCSs{L},\gCSs{L}\boxtimes\gCSs{L})
  \]
@@
   in which $\ell$-adic local systems sit as full subcategories).
-  Let $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ be the isomorphism matching
-  $\mu : {\bar m}^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$,
-  the latter appearing in the definition of $\qcs{L}$.
-  Then, as in Section~\ref{ssec:descentG}, $(\qcs{E},\mu_\qcs{E})$ is an object of $\bQC(G)$
-  and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{E},b_{G\times G}^*\mu_\qcs{E})$ in $\QC(G)$.
-  Thus, the full and faithful functor $B_G : \bQC(G) \to \QC(G)$ from Section~\ref{ssec:descentG}
+  Let $\mu_\CSs{E} : m^*\CSs{E} \to \CSs{E}\boxtimes\CSs{E}$ be the isomorphism matching
+  $\mu : {\bar m}^*\gCSs{L} \to \gCSs{L}\boxtimes\gCSs{L}$,
+  the latter appearing in the definition of $\CSs{L}$.
+  Then, as in Section~\ref{ssec:descentG}, $(\CSs{E},\mu_\CSs{E})$ is an object of $\bCS(G)$
+  and $\CSs{L} \ceq (\gCSs{L},\mu,\phi)$ is isomorphic to $(b_G^*\CSs{E},b_{G\times G}^*\mu_\CSs{E})$ in $\CS(G)$.
+  Thus, the full and faithful functor $B_G : \bCS(G) \to \CS(G)$ from Section~\ref{ssec:descentG}
   is also essentially surjective, hence an equivalence.
@@
 
-Using this equivalence of categories, we may give a good description of $\QC(G)$ when $G$ is connected and finite type.
+Using this equivalence of categories, we may give a good description of $\CS(G)$ when $G$ is connected and finite type.
 
@@
  \begin{enumerate}
- \item $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is an isomorphism of groups;
- \item every quasicharacter sheaf on $G$ is isomorphic to one defined by a discrete isogeny;
- \item $\Aut(\qcs{L}) = 1$, for all quasicharacter sheaves $\qcs{L}$ on $G$.
+ \item $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ is an isomorphism of groups;
+ \item every character sheaf on $G$ is isomorphic to one defined by a discrete isogeny;
+ \item $\Aut(\CSs{L}) = 1$, for all character sheaves $\CSs{L}$ on $G$.
  \end{enumerate}
@@
 \begin{proof}
-In Lemma~\ref{lem:bounded_connected}, we saw that every quasicharacter sheaf $\qcs{L}$ on $\bG$ descends to $G$; let $\qcs{E}$ be an object of $\bQC(G)$ for which $B_G(\qcs{E}) \iso \qcs{L}$.
- Since the functor $B_G : \bQC(G) \to \QC(G)$ is full and faithful, $\Aut(\qcs{L}) = \Aut(\qcs{E})$.
+In Lemma~\ref{lem:bounded_connected}, we saw that every character sheaf $\CSs{L}$ on $\bG$ descends to $G$; let $\CSs{E}$ be an object of $\bCS(G)$ for which $B_G(\CSs{E}) \iso \CSs{L}$.
+ Since the functor $B_G : \bCS(G) \to \CS(G)$ is full and faithful, $\Aut(\CSs{L}) = \Aut(\CSs{E})$.
 From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields, as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3}, gives us all we need, as we briefly recall.
@@
 As in the proof of Proposition~\ref{prop:finite}, use \'etale descent to see that pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.
-Under this equivalence, local systems $\qcs{E}$ on $G$ arising from objects in $\bQC(G)$ are matched with $G(\Fq)$-equivariant constant local systems of rank-one on $G$, and therefore with one-dimensional representations of $G(\Fq)$.
-In the same way, pullback along the isogeny $\Lang\times\Lang : G\times G\to G\times G$ matches the extra structure $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ with an isomorphism $m^*V \to V\boxtimes V$ of one-dimensional representations of $G(\Fq)\times G(\Fq)$, which is exactly an isomorphism $V \to V\otimes V$ of one-dimensional representations, which is exactly the choice of an isomorphism $V\iso \EE$.
-We see that $\bQC(G)$ is equivalent to the category of characters of $G(\Fq)$.
+Under this equivalence, local systems $\CSs{E}$ on $G$ arising from objects in $\bCS(G)$ are matched with $G(\Fq)$-equivariant constant local systems of rank-one on $G$, and therefore with one-dimensional representations of $G(\Fq)$.
+In the same way, pullback along the isogeny $\Lang\times\Lang : G\times G\to G\times G$ matches the extra structure $\mu_\CSs{E} : m^*\CSs{E} \to \CSs{E}\boxtimes\CSs{E}$ with an isomorphism $m^*V \to V\boxtimes V$ of one-dimensional representations of $G(\Fq)\times G(\Fq)$, which is exactly an isomorphism $V \to V\otimes V$ of one-dimensional representations, which is exactly the choice of an isomorphism $V\iso \EE$.
+We see that $\bCS(G)$ is equivalent to the category of characters of $G(\Fq)$.
 Let $\bg$ be a geometric point above $g \in G(\Fq)$.
-If $\qcs{E}$ matches $\psi : G(\Fq)\to \EEx$ under this equivalence, a simple calculation on stalks reveals that the action of Frobenius on $\qcs{E}_{\bar g}$ is multiplication by $\psi(g)^{-1}$.
-In other words, for every $\qcs{E}$ in $\bQC(G)$, the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ as a representation of $G(\Fq)$, proving parts (i) and (ii).
-
-To finish the proof of part (iii), suppose $\Lang^*\qcs{E} = V$ with isomorphism $V \to V\otimes V$.
-Observe that the equivalence above establishes a bijection between $\Aut(\qcs{E})$ and the group of automorphisms of $\rho : V\to V$ for which
+If $\CSs{E}$ matches $\psi : G(\Fq)\to \EEx$ under this equivalence, a simple calculation on stalks reveals that the action of Frobenius on $\CSs{E}_{\bar g}$ is multiplication by $\psi(g)^{-1}$.
+In other words, for every $\CSs{E}$ in $\bCS(G)$, the trace of $\Lang^*\CSs{E}$ is $\trFrob{\CSs{E}}^{-1}$ as a representation of $G(\Fq)$, proving parts (i) and (ii).
+
+To finish the proof of part (iii), suppose $\Lang^*\CSs{E} = V$ with isomorphism $V \to V\otimes V$.
+Observe that the equivalence above establishes a bijection between $\Aut(\CSs{E})$ and the group of automorphisms of $\rho : V\to V$ for which
 \[
@@
 commutes. 
-Since the only such isomorphism $\rho$ is $\id_V$, it follows that $\Aut(\qcs{E}) = 1$, completing the proof.
-\end{proof}
-
-We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of quasicharacter sheaves on $G$ is equivalent to the category of one-dimensional representations $V$ of $G(\Fq)$ equipped with an isomorphism $V\iso \EE$, and therefore equivalent to the category of characters $\psi$ of $G(\Fq)$.
-We have also just seen that if the character of $\Lang^*\qcs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\qcs{E} : \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
-This fact leads to a perspective on the function-sheaf dictionary common in the literature in which one considers one-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$ \cite{kamgarpour:09a}*{Intro}.
-As a slight variation, one may also consider one-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
-
-Although the category of quasicharacter sheaves on $G$ specializes to the one described above when $G$ is connected and of finite type, this description is not sufficient when extending the dictionary to smooth commutative group schemes.
-In particular, for a given $\gqcs{L}$ and $\phi$ there may be many $\mu$ so that $(\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf.
+Since the only such isomorphism $\rho$ is $\id_V$, it follows that $\Aut(\CSs{E}) = 1$, completing the proof.
+\end{proof}
+
+We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of character sheaves on $G$ is equivalent to the category of one-dimensional representations $V$ of $G(\Fq)$ equipped with an isomorphism $V\iso \EE$, and therefore equivalent to the category of characters $\psi$ of $G(\Fq)$.
+We have also just seen that if the character of $\Lang^*\CSs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\CSs{E} : \CSs{E} \to \CSs{E}\boxtimes\CSs{E}$.
+This fact leads to a perspective on the function-sheaf dictionary common in the literature in which one considers one-dimensional local systems $\CSs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\CSs{E} \iso \CSs{E} \boxtimes\CSs{E}$ \cite{kamgarpour:09a}*{Intro}.
+As a slight variation, one may also consider one-dimensional local systems $\gCSs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gCSs{L} \iso \gCSs{L}$ and an isomorphism $\bm^*\gCSs{L} \iso \gCSs{L} \boxtimes\gCSs{L}$.
+
+Although the category of character sheaves on $G$ specializes to the one described above when $G$ is connected and of finite type, this description is not sufficient when extending the dictionary to smooth commutative group schemes.
+In particular, for a given $\gCSs{L}$ and $\phi$ there may be many $\mu$ so that $(\gCSs{L},\mu,\phi)$ is a character sheaf.
 For \'etale $G$, Proposition~\ref{prop:etale-iso} shows that $\Hh^2(\bG,\EEx)^{\Weil{}}$ measures the possibilities for $\mu$.
 We will see in Section~\ref{sec:main} that $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ plays an analogous role for general smooth commutative group schemes $G$.
+
+\section{Character sheaves on \'etale commutative group schemes} \label{sec:etale}
+
+In this section we find a complete characterization of the category of character sheaves on \'etale commutative group schemes over finite fields.
+
+\subsection{Stalks of character sheaves}\label{ssec:stalks}
+
+The equivalence $G \mapsto G(\bFq)$,
+from the category of \'etale commutative group schemes over $\Fq$ to the category of commutative groups equipped
+with a continuous action of $\Gal(\bFq/\Fq)$,
+provides the following simple description of character sheaves.
+%
+A character sheaf $\CSs{L}$ on an \'etale commutative group scheme $G$ over $\Fq$ is:
+\begin{enumerate}
+ \labitem{(cs.1)}{cs.1} an indexed set of one-dimensional
+  $\EE$-vector spaces $\gCSs{L}_x$, as $x$ runs over
+  $G(\bFq)$;
+
+ \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms
+  $\mu_{x,y} : \gCSs{L}_{x+y} \xrightarrow{\iso} \gCSs{L}_{x} \otimes\gCSs{L}_{y}$,
+  for all $x,y \in G(\bFq)$, such that
+  \[
+   \begin{tikzcd}[row sep=40]
+    \gCSs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
+    && \gCSs{L}_{x+y}\otimes\gCSs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
+    \gCSs{L}_{x} \otimes\gCSs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
+    && \gCSs{L}_{x} \otimes\gCSs{L}_{y} \otimes\gCSs{L}_{z}
+   \end{tikzcd}
+  \]
+  commutes, for all $x,y,z\in G(\bFq)$; and
+ \labitem{(cs.3)}{cs.3} an indexed set of isomorphisms $\phi_{x} : \gCSs{L}_{\Frob{}(x)} \to \gCSs{L}_x$
+  such that
+  \[
+   \begin{tikzcd}[row sep=40]
+    \gCSs{L}_{\Frob{}(x)+\Frob{}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{}(x),\Frob{}(y)}}
+    && \gCSs{L}_{\Frob{}(x)}\otimes\gCSs{L}_{\Frob{}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
+    \gCSs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
+    && \gCSs{L}_x \otimes\gCSs{L}_y
+   \end{tikzcd}
+  \]
+  commutes, for all $x,y\in G(\bFq)$.
+\end{enumerate}
+Under this equivalence, a morphism $\rho : \CSs{L} \to \CSs{L'}$ of character sheaves on $G$ is given by
+\begin{enumerate}
+ \labitem{(cs.4)}{cs.4} an indexed set $\brho_x : \gCSs{L}_x \to \gCSs{L'}_x$
+  of linear transformations such that
+  \[
+   \begin{tikzcd}[column sep=40]
+    \arrow[swap]{d}{\phi_x} \gCSs{L}_{\Frob{}(x)} \rar{\brho_{\Frob{}(x)}} & \gCSs{L'}_{\Frob{}(x)} \dar{\phi_x'}
+    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
+    & \arrow[swap]{d}{\mu_{x,y}} \gCSs{L}_{x+y} \rar{\brho_{x+y}} & \gCSs{L'}_{x+y} \dar{\mu'_{x,y}} \\
+    \gCSs{L}_x \rar{\brho_x} & \gCSs{L'}_x
+    & {} & \gCSs{L}_x\otimes\gCSs{L}_y \rar{\brho_x\otimes\brho_y} & \gCSs{L'}_x \otimes\gCSs{L'}_y
+   \end{tikzcd}
+  \]
+  both commute, for all $x, y \in G(\bFq)$.
+\end{enumerate}
+
+We will see that $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ may not provide complete
+information about isomorphism classes of character sheaves on $G$ when $G$ is not a connected algebraic group.
+Our main tool for understanding this phenomenon
+is a group homomorphism $S_G: \CSiso{G} \to \Hh^2(E^\bullet_G)$ defined in Section~\ref{ssec:S}, for which the next two sections are preparation.
+
+\subsection{A spectral sequence}\label{ssec:E}
+
+The zeroth page of the Hochschild-Serre spectral sequence
+is a double complex $E^{\bullet, \bullet}$ defined by
+\[
+E^{i,j} = C^i(\Weil{}, C^j(G(\bFq), \EEx));
+\]
+see \cite{vakil:Algebraic_Geometry}*{\S 1.7}, expanding on \cite{weibel:Homological_Algebra}*{Ch 5 and \S 7.5}.
+The standard derivative on cochains yields two derivatives,
+\begin{align*}
+d_G &: E^{i,j} \to E^{i,j+1} \quad \mbox{and} \\
+d_{\Weil{}} &: E^{i,j} \to E^{i+1,j};
+\end{align*}
+we use the first as the derivative $d_0$ on the zeroth page, and the second to induce $d_1$.
+Combining them also yields a derivative $d = d_G + (-1)^j d_{\Weil{}}$ on the total complex
+\[
+E^n_G = \bigoplus_{i+j=n} E^{i,j}.
+\]
+The machinery of spectral sequences gives us a sequence of pages $E_r^{i,j}$, converging to a page $E_{\infty}^{i,j}$.
+We summarize the key properties of this spectral sequence in the following proposition.
+
+\begin{proposition} In the spectral sequence defined above,
+\begin{enumerate}
+\item the second page is given by $E_2^{i,j} = \Hh^i(\Weil{}, \Hh^j(G(\bFq), \EEx))$,
+\item there is an isomorphism $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) \cong \Hh^n(E_G^\bullet)$, and
+\item there is a filtration $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) = F_n \supset \cdots \supset F_{-1} = 0$, with $F_i / F_{i-1} \cong E_{\infty}^{i, n-i}$.
+\end{enumerate}
+\end{proposition}
+
+Moreover, since $\Weil{} \cong \ZZ$ has cohomological dimension $1$, $E_2^{i,j} = 0$ for $i > 1$ and the sequence degenerates at the second page: $E_{\infty}^{i,j} = E_2^{i,j}$.
+We obtain the following corollary:
+
+\begin{corollary}\label{cor:spectral_ses}
+There is a short exact sequence
+ \[
+    0 \to
+    \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to
+    \Hh^2(E^\bullet_G) \to
+    \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to
+    0.
+ \]
+\end{corollary}
+
+This sequence will play a key role in understanding the kernel of $\TrFrob{G}$, as described in the next few sections.
+For this application, we need a good understanding of these maps to and from the total complex.
+
+\begin{proposition} \label{prop:ses_desc}
+Consider the short exact sequence in Corollary~\ref{cor:spectral_ses}.
+\begin{enumerate}
+\item Every class $[\alpha\oplus\beta\oplus\gamma] \in \Hh^2(E^\bullet_G)$ is cohomologous to one with $\gamma=0$.
+\item The map $\Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx))$ is given by $[\alpha\oplus\beta\oplus 0] \mapsto [\beta]$.
+\item Suppose $a \in Z^2({\bar G}, \EEx)$ represents a class in $\Hh^2({\bar G},\EEx)$ fixed by Frobenius.
+The map $\Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to \Hh^2(E^\bullet_G)$ is given by $[a] \mapsto [a \oplus 0 \oplus 0]$.
+\end{enumerate}
+\end{proposition}
+\begin{proof}
+Since $\Hh^2(\Weil{}, C^0({\bar G}, \EEx)) = 0$, we may find a $\gamma_1 \in C^1(\Weil{}, C^0({\bar G}, \EEx))$ with $d_{\Weil{}}\gamma_1 = \gamma$.
+Subtracting $d \gamma_1$ from $\alpha\oplus\beta\oplus\gamma$, we may assume that $\gamma = 0$.
+
+The latter two claims follow from tracing through the definition of latter pages in the spectral sequence.
+\end{proof}
+
+\subsection{From character sheaves to the total complex}\label{ssec:S}
+
+In this section we define an isomorphism
+\[
+S_G : \CSiso{G} \to \Hh^2(E^\bullet_G).
+\]
+Let $\CSs{L} = (\gCSs{L},\mu,\phi)$ be a character sheaf on $G$.
+For each geometric point $x\in {\bar G}$, choose a basis $\{ v_x \}$ for $\gCSs{L}_x$.
+Through this choice, $\CSs{L}$ determines functions
+\begin{align*}
+a : {\bar G}\times {\bar G} &\to \EEx & b : {\bar G} &\to \EEx \\
+\mu_{x,y}(v_{x+y}) &= a(x,y) v_x \otimes v_y & \phi_x(v_{\Frob{G}(x)}) &= b(x) v_x.
+\end{align*}
+Condition~\ref{CS.2} implies that
+\begin{equation}\label{2-cocyle}
+a(x+y,z) a(x,y) = a(x,y+z) a(y,z)
+\end{equation}
+for all $x,y,z\in {\bar G}$, so $a \in Z^2({\bar G},\EEx)$.  Similarly, condition~\ref{CS.3} gives
+\begin{equation}\label{nohom}
+\frac{a(\Frob{G}(x),\Frob{G}(y))}{a(x,y)} =  \frac{b(x+y)}{b(x) b(y)}
+\end{equation}
+for $x, y \in {\bar G}$.
+Let $\alpha \in C^0(\Weil{},C^2({\bar G},\EEx)$ be the $0$-cochain corresponding to $a$ and let $\beta\in C^1(\Weil{},C^1({\bar G},\EEx)$ be the cocycle such that $\beta(\Frob{})$ is $b$.
+We will write both $\alpha$ and $\beta$ additively.
+Then
+\[
+d_G\alpha =0, \qquad\qquad
+d_{\Weil{}} \alpha = d_{G} \beta,\qquad\qquad
+d_{\Weil{}} \beta =0;
+\]
+in other words,
+\[\alpha\oplus \beta \in Z^2(E^\bullet_G).\]
+Although the cocycle $\alpha\oplus \beta$ is not well defined by $\CSs{L}$, its class in $\Hh^2(E^\bullet_G)$ is.
+To see this, let $\{ v'_x \in \gCSs{L}_x^\times \tq x \in {\bar G}\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$ be defined by $\CSs{L}$ and this choice, as above.
+Now let $\delta \in C^0(\Weil{},C^1({\bar G},\EEx))$ correspond to the function $d : {\bar G}\to \EEx$ defined by $v'_x = d(x) v_x$.
+Chasing through \ref{CS.2} and \ref{CS.3}, we find
+\[
+\alpha'\oplus\beta' = \alpha\oplus\beta + d\delta,
+\]
+so the class $[\alpha\oplus\beta]$ of $\alpha\oplus\beta$ in $\Hh^2(E^\bullet_G)$ is independent of the choice made above.
+It is also easy to see that $[\alpha\oplus\beta] = [\alpha_0\oplus\beta_0]$ when $\CSs{L} \iso \CSs{L}_0$,
+which concludes the definition of the function
+\begin{align*}
+S_G : \CSiso{G} &\to \Hh^2(E^\bullet_G)\\
+[\CSs{L}] &\mapsto [\alpha\oplus \beta].
+\end{align*}
+It is also easy to see that $[\alpha_1\oplus\beta_1] + [\alpha_2\oplus\beta_2] = [\alpha_3\oplus\beta_3]$ when $\CSs{L}_3 = \CSs{L}_1\otimes \CSs{L}_2$, so $S_G$ is a group homomorphism.
+
+\begin{remark}
+Although we will only use the group homomorphism $S_G : \CSiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an \'etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$.
+However, the next result is false in that context.
+\end{remark}
+
+\begin{proposition}\label{prop:SGiso}
+If $G$ is \'etale then $S_G$ is an isomorphism.
+\end{proposition}
+\begin{proof}
+Suppose $[\CSs{L}] \in \CSiso{G}$ with $S_G([\CSs{L}]) = [\alpha \oplus \beta] = 0$,
+so that $\alpha \oplus \beta = d\sigma$ for some $\sigma \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
+For each $x\in {\bar G}$, define $\sigma_x : \gCSs{L}_x \to \EE$ by $\sigma_x : v_x \mapsto \sigma(x)$.
+Then the indexed set of isomorphisms $\{ \sigma_x : \gCSs{L}_x \to \EE \tq x\in {\bar G}\}$
+defines an isomorphism $\CSs{L} \to (\EE)_G$.
+Since $\CSs{L} = 0 \in \CSiso{G}$, $S_G$ is injective.
+
+To see that $S_G$ is surjective, begin with $\alpha\oplus\beta\oplus 0 \in Z^2(E^\bullet_G)$.
+Since $d_{\Weil{}} \beta = 0$, we may define $a = \alpha \in C^2({\bar G},\EEx)$ and
+$b = \beta(\Frob{}) \in C^1({\bar G},\EEx)$, which are related to $\alpha$ and $\beta$ as above.
+Set $\gCSs{L}_x = \EE$, define $\mu_{x,y} : \gCSs{L}_{x+y} \to \gCSs{L}_x\otimes\gCSs{L}_y$
+by $\mu_{x,y}(1) = a(x,y) (1\otimes 1)$ and $\phi_x : \gCSs{L}_{\Frob{G}(x)} \to \gCSs{L}_x$ by $\phi_x(1)= b(x)$.
+Then \ref{CS.1} holds since $d_G \alpha =0$ and \ref{CS.2} holds since $d_{\Weil{}}\alpha =d_G \beta$.
+Tracing the construction backward, we have defined a character sheaf $\CSs{L}$ on $G$ with
+$S_G(\CSs{L}) = [\alpha\oplus\beta\oplus 0]$, showing that $S_G$ is surjective.
+\end{proof}
+
+\subsection{Objects in the \'etale case}\label{ssec:SandT}
+
+In this section we fit the group homomorphisms $\TrFrob{G}$ and $S_G$ into a commutative diagram, determining the kernel and cokernel of the homomorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$ when $G$ is an \'etale commutative group scheme over $\Fq$.
+
+%
+We begin with a simple, general result relating duals, invariants and coinvariants.
+
+\begin{lemma} \label{lem:dual-inv}
+Let $X$ be an abelian group equipped with an action of $\Weil{}$.  Then
+\begin{align*}
+ (X^*)_{\Weil{}} &\to (X^{\Weil{}})^* \\
+ [f] &\mapsto f|_{X^{\Weil{}}}
+\end{align*}
+is an isomorphism.
+\end{lemma}
+
+\begin{proof}
+We can describe $X^{\Weil{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
+let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
+\[
+ 0 \to X^{\Weil{}} \to X \to Y \to 0
+\]
+yields
+\[
+ 0 \to Y^* \to X^* \to (X^{\Weil{}})^* \to \Ext^1_\ZZ(Y, \EEx).
+\]
+Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Weil{}})^*$.
+\end{proof}
+
+\begin{proposition}\label{prop:sur_etale}
+If $G$ is \'etale, then $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ is surjective
+and split.
+\end{proposition}
+\begin{proof}
+Pick $\chi \in G(\Fq)^*$. 
+Let $[\beta]\in \Hh^1(\Weil{},\bG^*)$ be the class corresponding to $\chi$ under Lemma~\ref{lem:dual-inv}.
+Every representative cocycle $\beta \in Z^1(\Weil{},\bG^*)$ determines a homomorphism $\beta(\Frob{}) : G(\bFq)\to \EEx$ such that $\beta(\Frob{})\vert_{G(\Fq)} = \chi$.
+Set $\gCSs{L}_x = \EE$ for every $x\in G(\bFq)$.
+Define $\mu_{x,y} : \gCSs{L}_{x+y} \to \gCSs{L}_x\otimes \gCSs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$ and
+$\phi_{x} : \gCSs{L}_{\Frob{}(x)} \to \gCSs{L}_x$ by $\phi_{x}(1) = \beta(\Frob{})(x)$.
+Since $\beta(\Frob{}) : G(\bFq) \to \EEx$ is a group homomorphism,
+condition \eqref{nohom} is satisfied with $a =1$.
+So $\CSs{L} = (\gCSs{L}, \mu, \phi)$
+is a character sheaf with $\trFrob{\CSs{L}} = \chi$.
+This shows that $\TrFrob{G}$ is surjective.
+
+Now let $\beta' \in Z^1(\Weil{},\bG^*)$ be another representative for $[\beta]$
+so $\beta-\beta' = d_{\Weil{}} \delta$ for some $\delta \in C^0(\Weil{},\bG^*)$ defining $d \in \Hom(G(\bFq),\EEx)$.
+Let $\CSs{L}'$ be the character sheaf on $G$ defined by $\beta'$, as above.
+For each $x\in G(\bFq)$, define $\brho_x :\CSs{L}_x\to \CSs{L}'_x$ by $\brho_x(1) = d(x)$.
+The collection of isomorphisms $\{ \brho_x \tq x\in G(\bFq)\}$ satisfies condition~\ref{CS.4}, so it defines a morphism $\rho : \CSs{L}\to \CSs{L}'$, which is clearly an isomorphism. 
+%
+We have now defined a section of $\TrFrob{G}$.
+
+Now suppose $\chi_1, \chi_2 \in G(\Fq)^*$.
+Pick cocycles $\beta_1,\beta_2\in Z^1(\Weil{},\bG^*)$ and construct character sheaves $\CSs{L}_1$ and $\CSs{L}_2$ on $G$ as above.
+Since $\CSs{L}_1\otimes \CSs{L}_2$ is exactly the character sheaf built from the cocycle $\beta_1\cdot \beta_2$, and since $\trFrob{\CSs{L}_1\otimes \CSs{L}_2} = \trFrob{\CSs{L}_1}\cdot \trFrob{\CSs{L}_2}$, the section of $\TrFrob{G}$ defined here is a homomorphism.
+\end{proof}
+
+\begin{proposition} \label{prop:etale-iso}
+ If $G$ is \'etale then the map $S_G : \CSiso{G}\to \Hh^2(E^\bullet_G)$ induces an isomorphism of split short exact sequences
+\[
+\begin{tikzcd}
+ 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \CSiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
+  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r} & 0.
+ \end{tikzcd}
+ \]
+\end{proposition}
+\begin{proof}
+This result follows from Propositions~\ref{prop:ses_desc}, \ref{prop:SGiso} and \ref{prop:sur_etale}.
+\end{proof}
+
+\subsection{Morphisms in the \'etale case}\label{ssec:mor-etale}
+
+While most of this paper focuses on the question of determining the isomorphism classes of objects, a complete understanding of the morphisms in $\CS(G)$ also requires a description of the automorphisms of an arbitrary character sheaf $\CSs{L}$.
+
+\begin{proposition}\label{prop:autornaught_etale}
+Let $G$ be an \'etale commutative group scheme over $\Fq$.
+If $\CSs{L}$ and $\CSs{L}'$ are character sheaves on $G$ then
+every $\rho\in \Hom(\CSs{L},\CSs{L}')$ is either trivial or an isomorphism. Moreover, the trace map induces an isomorphism of groups
+\[
+\Aut(\CSs{L}) \to \Hom(G(\bFq)_{\Weil{}}, \EEx).
+\]
+\end{proposition}
+
+\begin{proof}
+We have already seen, in Lemma~\ref{lem:autornaught}, that every $\rho\in \Hom(\CSs{L},\CSs{L}')$ is either trivial or an isomorphism.
+Now suppose $\rho \in \Aut(\CSs{L})$.
+The second diagram in \ref{CS.4} shows that the association $x \mapsto \brho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{CS.4} shows that it factors through $G(\bFq)_{\Weil{}}$.
+
+Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism, then defining $\brho_x$ as multiplication by $\rho(x)$ will define a morphism $\gCSs{L} \to \gCSs{L}'$ satisfy the two diagrams in \ref{CS.4}.
+
+Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the resulting bijection is actually a group isomorphism.
+\end{proof}
 
@@
 \begin{tikzcd}
-\QC(0) \rar & \QC(\pi_0(G)) \arrow{r}{\pi_0^*} & \QC(G) \arrow{r}{\iota_0^*} & \QC(G^0) \rar & \QC(0)
+\CS(0) \rar & \CS(\pi_0(G)) \arrow{r}{\pi_0^*} & \CS(G) \arrow{r}{\iota_0^*} & \CS(G^0) \rar & \CS(0)
 \end{tikzcd}
@@
 0 \rar &
-\QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
+\CSiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \CSiso{G} \arrow{r}{\iota_0^*} & \CSiso{G^0} \rar & 0.
 \end{tikzcd}
 \end{equation}
- Note that we found the groups $\QCiso{\pi_0(G)}$ and $\QCiso{G^0}$
+ Note that we found the groups $\CSiso{\pi_0(G)}$ and $\CSiso{G^0}$
 in Sections~\ref{ssec:SandT} and \ref{ssec:connected}, respectively.
@@
 \begin{proposition}\label{prop:restriction}
-The restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
+The restriction functor $\iota_0^* : \CS(G)\to \CS(G^0)$ is essentially surjective.
 \end{proposition}
@@
   By Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}, every
-  quasicharacter sheaf on $G^0$ is isomorphic to $(\pi_! \EE)_\psi$ for some discrete isogeny $\pi : B \to G^0$ and character $\psi : \ker \pi \to \EEx$.
-  So to prove the proposition it suffices to show that $(\pi_! \EE)_\psi$ extends to a quasicharacter sheaf on $G$.
+  character sheaf on $G^0$ is isomorphic to $(\pi_! \EE)_\psi$ for some discrete isogeny $\pi : B \to G^0$ and character $\psi : \ker \pi \to \EEx$.
+  So to prove the proposition it suffices to show that $(\pi_! \EE)_\psi$ extends to a character sheaf on $G$.
 %
@@
  such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
- Then $(f_! \EE)_\psi$ is a quasicharacter sheaf on $G$ and
+ Then $(f_! \EE)_\psi$ is a character sheaf on $G$ and
  $(f_! \EE)_\psi\vert_{G^0} \iso (\pi_! \EE)_\psi$.
@@
 \begin{lemma}\label{lem:extension}
-The group homomorphism $\pi_0^*: \QCiso{\pi_0(G)} \to \QCiso{G}$ is injective.
+The group homomorphism $\pi_0^*: \CSiso{\pi_0(G)} \to \CSiso{G}$ is injective.
 \end{lemma}
 \begin{proof}
-Let $\qcs{L}$ be a quasicharacter sheaf on $\pi_0(G)$ and let $\rho : \pi_0^*\qcs{L} \to (\EE)_{G}$ be an isomorphism in $\QC(G)$. 
+Let $\CSs{L}$ be a character sheaf on $\pi_0(G)$ and let $\rho : \pi_0^*\CSs{L} \to (\EE)_{G}$ be an isomorphism in $\CS(G)$. 
 For each $x\in \pi_0(\bG)$, set $\bG^x \ceq \pi_0^{-1}(x)$.
-The restriction $\pi_0^*\gqcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gqcs{L}_x)_{\bG^x}$ so the isomorphism $\brho\vert_{\bG^x} : (\gqcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gqcs{L}_x \to (\EE)_x$.
-The collection $\{ \brho_x \tq x\in \pi_0(\bG) \}$ determines an isomorphism $\qcs{L} \to (\EE)_{\pi_0(G)}$  in $\QC(\pi_0(G))$.
+The restriction $\pi_0^*\gCSs{L}\vert_{\bG^x}$ is the constant sheaf $(\gCSs{L}_x)_{\bG^x}$ so the isomorphism $\brho\vert_{\bG^x} : (\gCSs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gCSs{L}_x \to (\EE)_x$.
+The collection $\{ \brho_x \tq x\in \pi_0(\bG) \}$ determines an isomorphism $\CSs{L} \to (\EE)_{\pi_0(G)}$  in $\CS(\pi_0(G))$.
 \end{proof}
@@
   \begin{tikzcd}
-  0 \rar & \QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
+  0 \rar & \CSiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \CSiso{G} \arrow{r}{\iota_0^*} & \CSiso{G^0} \rar & 0.
   \end{tikzcd}
@@
 \begin{proof}
-Exactness at $\QCiso{G^0}$ follows from Proposition~\ref{prop:restriction},
-and at $\QCiso{\pi_0(G)}$ from Lemma~\ref{lem:extension}.
-Here we show that it is also exact at $\QCiso{G}$.
+Exactness at $\CSiso{G^0}$ follows from Proposition~\ref{prop:restriction},
+and at $\CSiso{\pi_0(G)}$ from Lemma~\ref{lem:extension}.
+Here we show that it is also exact at $\CSiso{G}$.
 First note that $\iota_0^* \circ \pi_0^*$ is trivial by Lemma~\ref{lem:pullback}.
-So it suffices to show that if $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$
-with $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$ then $\qcs{L}$ is in the essential image of $\pi_0^*$.
+So it suffices to show that if $\CSs{L} = (\gCSs{L},\mu,\phi)$ is a character sheaf on $G$
+with $\CSs{L}\vert_{G^0} = (\EE)_{G^0}$ then $\CSs{L}$ is in the essential image of $\pi_0^*$.
 
@@
 Set $a = g^{-1}g'$ and note that $a$ is a geometric point in $\bG^0$.
-Let $\mu_{g,a} : \gqcs{L}_{ga} \to \gqcs{L}_g \otimes \gqcs{L}_a$
+Let $\mu_{g,a} : \gCSs{L}_{ga} \to \gCSs{L}_g \otimes \gCSs{L}_a$
 be the isomorphism of vector spaces obtained by restriction of
-$\mu : m^*\gqcs{L} \to \gqcs{L} \boxtimes \gqcs{L}$ to the
+$\mu : m^*\gCSs{L} \to \gCSs{L} \boxtimes \gCSs{L}$ to the
 geometric point $(g,a)$ on $\bG^x \times \bG^0$.
-Since $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$,
-the stalk of $\gqcs{L}$ at $a$ is $\EE$.
+Since $\CSs{L}\vert_{G^0} = (\EE)_{G^0}$,
+the stalk of $\gCSs{L}$ at $a$ is $\EE$.
 In this way the pair of geometric points $g, g' \in \bG^x$
 determines an isomorphism $\varphi_{g,g'} \ceq \mu_{g,a}^{-1}$
-from $\gqcs{L}_{g}$ to $\gqcs{L}_{g'}$.
+from $\gCSs{L}_{g}$ to $\gCSs{L}_{g'}$.
 %
-The isomorphisms $\varphi_{g,g'}: \gqcs{L}_{g} \to \gqcs{L}_{g'}$ are canonical
+The isomorphisms $\varphi_{g,g'}: \gCSs{L}_{g} \to \gCSs{L}_{g'}$ are canonical
 in the following sense: if $g,g'\in \bG^x$ and $h,h'\in \bG^y$
-then it follows from \ref{QC.2} and \ref{QC.3}
+then it follows from \ref{CS.2} and \ref{CS.3}
 that
- \begin{equation}\label{eq:qc}
+ \begin{equation}\label{eq:CS}
   \begin{tikzcd}[column sep=40]
-   \gqcs{L}_{gh} \arrow{r}{\varphi_{gh,g'h'}} \arrow[swap]{d}{\mu_{g,h}}
-  & \gqcs{L}_{g'h'} \arrow{d}{\mu_{g',h'}}
+   \gCSs{L}_{gh} \arrow{r}{\varphi_{gh,g'h'}} \arrow[swap]{d}{\mu_{g,h}}
+  & \gCSs{L}_{g'h'} \arrow{d}{\mu_{g',h'}}
   &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-  &  \gqcs{L}_{\Frob{}(g)} \arrow{r}{\varphi_{\Frob{}(g),\Frob{}(g')}} \arrow[swap]{d}{\phi_{g}} & \gqcs{L}_{\Frob{}(g')} \arrow{d}{\phi_{g'}} \\
-  \gqcs{L}_{g} \otimes \gqcs{L}_{h} \arrow{r}{\varphi_{g,g'}\otimes \varphi_{h,h'}}
-  & \gqcs{L}_{g'} \otimes \gqcs{L}_{h'}
+  &  \gCSs{L}_{\Frob{}(g)} \arrow{r}{\varphi_{\Frob{}(g),\Frob{}(g')}} \arrow[swap]{d}{\phi_{g}} & \gCSs{L}_{\Frob{}(g')} \arrow{d}{\phi_{g'}} \\
+  \gCSs{L}_{g} \otimes \gCSs{L}_{h} \arrow{r}{\varphi_{g,g'}\otimes \varphi_{h,h'}}
+  & \gCSs{L}_{g'} \otimes \gCSs{L}_{h'}
   & {}
-  & \gqcs{L}_{g} \arrow{r}{\varphi_{g,g'}} & \gqcs{L}_{g'}
+  & \gCSs{L}_{g} \arrow{r}{\varphi_{g,g'}} & \gCSs{L}_{g'}
   \end{tikzcd}
@@
 For each $x\in \pi_0(\bG)$, pick $g(x)\in \bG^x$
-and set $\gqcs{E}_x \ceq \gqcs{L}_{g(x)}$.
-Let $\phi_x : \gqcs{E}_{\Frob{}(x)} \to \gqcs{E}_x$
+and set $\gCSs{E}_x \ceq \gCSs{L}_{g(x)}$.
+Let $\phi_x : \gCSs{E}_{\Frob{}(x)} \to \gCSs{E}_x$
 be the isomorphism of $\EE$-vector spaces obtained by composing
-$\varphi_{g(\Frob{}(x)),\Frob{}(g(x))} : \gqcs{L}_{g(\Frob{}(x))} \to \gqcs{L}_{\Frob{}(g(x))}$
-with $\phi_{g(x)} : \gqcs{L}_{\Frob{}(g(x))} \to \gqcs{L}_{g(x)}$.
+$\varphi_{g(\Frob{}(x)),\Frob{}(g(x))} : \gCSs{L}_{g(\Frob{}(x))} \to \gCSs{L}_{\Frob{}(g(x))}$
+with $\phi_{g(x)} : \gCSs{L}_{\Frob{}(g(x))} \to \gCSs{L}_{g(x)}$.
 For each pair $x,y\in \pi_0(\bG)$
-let $\mu_{x,y} : \gqcs{E}_{x+y}\to \gqcs{E}_x\otimes \gqcs{E}_y$
+let $\mu_{x,y} : \gCSs{E}_{x+y}\to \gCSs{E}_x\otimes \gCSs{E}_y$
 be the isomorphism of $\EE$-vector spaces obtained by composing
-$\varphi_{g(x+y),g(x)g(y)} : \gqcs{L}_{g(x+y)} \to \gqcs{L}_{g(x)g(y)}$
-with $\mu_{g(x),g(y)} : \gqcs{L}_{g(x)g(y)} \to \gqcs{L}_{g(x)}\otimes \gqcs{L}_{g(y)}$.
-Using \eqref{eq:qc}, it follows that \ref{qc.1}, \ref{qc.2} and \ref{qc.3} are satisfied for
-$\qcs{E} \ceq (\gqcs{E}_x, \mu_{x,y}, \phi_x)$, thus defining a quasicharacter sheaf on $\pi_0(G)$.
-
-The pullback $\pi_0^*(\qcs{E})$ of $\qcs{E}$ along $\pi_0 : G \to \pi_0(G)$ is constant
+$\varphi_{g(x+y),g(x)g(y)} : \gCSs{L}_{g(x+y)} \to \gCSs{L}_{g(x)g(y)}$
+with $\mu_{g(x),g(y)} : \gCSs{L}_{g(x)g(y)} \to \gCSs{L}_{g(x)}\otimes \gCSs{L}_{g(y)}$.
+Using \eqref{eq:CS}, it follows that \ref{CS.1}, \ref{CS.2} and \ref{CS.3} are satisfied for
+$\CSs{E} \ceq (\gCSs{E}_x, \mu_{x,y}, \phi_x)$, thus defining a character sheaf on $\pi_0(G)$.
+
+The pullback $\pi_0^*(\CSs{E})$ of $\CSs{E}$ along $\pi_0 : G \to \pi_0(G)$ is constant
 on geometric connected components, with stalks given by
-$(\pi_0^* \qcs{E})_g = \qcs{E}_{x}$ for all $g\in \bG^x$.  Thus both $\pi_0^*\qcs{E}$ and $\qcs{L}$
+$(\pi_0^* \CSs{E})_g = \CSs{E}_{x}$ for all $g\in \bG^x$.  Thus both $\pi_0^*\CSs{E}$ and $\CSs{L}$
 are constant on geometric connected components of $G$.
 The choices above define isomorphisms
-$\gqcs{L}\vert_{\bG^x} \to  (\gqcs{E}_{x})_{\bG^x}$ for each $x\in \pi_0(\bG)$.
-The resulting isomorphism $\gqcs{L} \to \pi_0^* \gqcs{E}$ satisfies \ref{QC.4},
-thus defining an isomorphism $\qcs{L} \to \pi_0^* \qcs{E}$ in $\QC(G)$.
+$\gCSs{L}\vert_{\bG^x} \to  (\gCSs{E}_{x})_{\bG^x}$ for each $x\in \pi_0(\bG)$.
+The resulting isomorphism $\gCSs{L} \to \pi_0^* \gCSs{E}$ satisfies \ref{CS.4},
+thus defining an isomorphism $\CSs{L} \to \pi_0^* \CSs{E}$ in $\CS(G)$.
 \end{proof}
@@
 
-We saw in Proposition~\ref{prop:functorialG} that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
+We saw in Proposition~\ref{prop:functorialG} that $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
 In this section we find the image and kernel of $\TrFrob{G}$.
@@
   \[
-  \TrFrob{G} : \QCiso{G} \to G(\Fq)^*
+  \TrFrob{G} : \CSiso{G} \to G(\Fq)^*
   \]
@@
   \begin{tikzcd}[row sep=20, column sep=20]
-    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
-    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
+    0 \rar & \CSiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
+    & \CSiso{G} \rar \dar{\TrFrob{G}} & \CSiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
     0 \rar & \pi_0(G)(\Fq)^* \rar
@@
     0 \arrow[dotted]{r} & \ker \TrFrob{\pi_0(G)} \arrow[dotted]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dotted]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
-    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
-    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
+    0 \rar & \CSiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
+    & \CSiso{G} \rar \dar{\TrFrob{G}} & \CSiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
     0 \rar & \pi_0(G)(\Fq)^* \rar \dar
@@
   \begin{tikzcd}
-0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx)) \arrow{r} & \QCiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0. 
+0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx)) \arrow{r} & \CSiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0. 
   \end{tikzcd}
@@
 
-\subsection{Morphisms of quasicharacters} \label{ssec:qcmor}
+\subsection{Morphisms of characters} \label{ssec:CSmor}
 
@@
 \[
-\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx).
+\Aut(\CSs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx).
 \]
@@
 \begin{proof} 
-Fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the group homomorphism from $\Aut(\qcs{L})$ to $\Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
+Fix $\CSs{L} = (\gCSs{L},\mu,\phi)$ and consider the group homomorphism from $\Aut(\CSs{L})$ to $\Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
 This homomorphism is injective because morphisms of sheaves are determined by the linear transformations induced on stalks.  
-Homomorphisms in the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ are continuous when $\bG$ is viewed as the base of the espace \'etal\'e attached to $\gqcs{L}$.
-Since $\ell$ is invertible in $\Fq$, it follows that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
+Homomorphisms in the image of $\Aut(\CSs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ are continuous when $\bG$ is viewed as the base of the espace \'etal\'e attached to $\gCSs{L}$.
+Since $\ell$ is invertible in $\Fq$, it follows that the image of $\Aut(\CSs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
 We also have $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
-To see that $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho^y: \gqcs{L}^y \to \gqcs{L}^y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
-This defines an isomorphism $\bar\rho : \gqcs{L}\to \gqcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\qcs{L}\to \qcs{L}$ which maps to $\theta$ under $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
+To see that $\Aut(\CSs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho^y: \gCSs{L}^y \to \gCSs{L}^y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
+This defines an isomorphism $\bar\rho : \gCSs{L}\to \gCSs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\CSs{L}\to \CSs{L}$ which maps to $\theta$ under $\Aut(\CSs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
 \end{proof}
@@
 
-When using quasicharacter sheaves to study characters, it is useful to understand
-how quasicharacter sheaves behave under change of fields.
+When using character sheaves to study characters, it is useful to understand
+how character sheaves behave under change of fields.
 Let $k'$ be a finite extension of $k$. Then $k \hookrightarrow k'$ induces a group homomorphism
@@
 \end{align*}
-We can interpret this operation on characters in terms of quasicharacter sheaves:
+We can interpret this operation on characters in terms of character sheaves:
 
@@
 \[
-\QC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \QC(G)
+\CS(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \CS(G)
 \]
@@
 \begin{tikzcd}
-\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\TrFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\TrFrob{G}} \\
+\CSiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\TrFrob{\Res_{k'/k}(G_{k'})}} & \CSiso{G} \dar{\TrFrob{G}} \\
 G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
@@
 \end{align*}
-We can also interpret this operation in terms of quasicharacter sheaves.
-
-If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$, we define
-$\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
+We can also interpret this operation in terms of character sheaves.
+
+If $\CSs{L} \ceq (\gCSs{L}, \mu, \phi)$ is a character sheaf on $G$, we define
+$\CSs{L}' \ceq (\gCSs{L}, \mu, \phi_{k'})$ on the base change
 $G_{k'}$ of $G$ to $k'$ by setting
@@
 \]
-The commutativity of the diagram (QC.3) for $\phi_{k'}$
+The commutativity of the diagram (CS.3) for $\phi_{k'}$
 follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
 Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
-as restricting the action $\varphi$ of $\Weil{k}$ on $\gqcs{L}$,
+as restricting the action $\varphi$ of $\Weil{k}$ on $\gCSs{L}$,
 defined in Section~\ref{ssec:category}, to $\Weil{k'}$.
@@
 With notation above,
-the rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$
- defines a monoidal functor $\QC(G) \to \QC(G_{k'})$
+the rule $\nu_{k'/k}: (\gCSs{L}, \mu, \phi) \mapsto (\gCSs{L}, \mu, \phi_{k'})$
+ defines a monoidal functor $\CS(G) \to \CS(G_{k'})$
  such that the following diagram commutes:
@@
 \begin{tikzcd}[column sep=60]
-\QCiso{G} \rar{\nu_{k'/k}} \dar{\TrFrob{G}} & \QCiso{G_{k'}} \dar{\TrFrob{G_{k'}}} \\
+\CSiso{G} \rar{\nu_{k'/k}} \dar{\TrFrob{G}} & \CSiso{G_{k'}} \dar{\TrFrob{G_{k'}}} \\
 G(k)^*  \rar{\Nm^*} & G(k')^*.
@@
 \begin{proof}
-Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
-we may compute the value of $\TrFrob{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
-and the value of $\Nm^*(\TrFrob{G}(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
-Applying \ref{QC.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
+Let $\CSs{L} \ceq (\gCSs{L}, \mu, \phi) \in \CS(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
+we may compute the value of $\TrFrob{G_{k'}}(\nu_{k'/k}\CSs{L})(x)= t_{\nu_{k'/k}\CSs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gCSs{L}_x$,
+and the value of $\Nm^*(\TrFrob{G}(\CSs{L}))(x)$ as the trace of $\phi$ on $\gCSs{L}_{\Nm(x)}$.
+Applying \ref{CS.3} to the stalk of $\gCSs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
 \[
 \begin{tikzcd}
-\gqcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gqcs{L}_{F(x)} \otimes \gqcs{L}_{F^2(x)} \otimes \cdots \otimes \gqcs{L}_x
+\gCSs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gCSs{L}_{F(x)} \otimes \gCSs{L}_{F^2(x)} \otimes \cdots \otimes \gCSs{L}_x
 \dar{\phi_x \otimes (F^*\phi)_x \otimes \cdots \otimes ((F^{n-1})^*\phi)_x} \\
-\gqcs{L}_{\Nm(x)} \rar & \gqcs{L}_x \otimes \gqcs{L}_{F(x)} \otimes \cdots \otimes \gqcs{L}_{F^{n-1}(x)}.
-\end{tikzcd}
-\]
-Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$ and write $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$ for the image of $v$ under the
+\gCSs{L}_{\Nm(x)} \rar & \gCSs{L}_x \otimes \gCSs{L}_{F(x)} \otimes \cdots \otimes \gCSs{L}_{F^{n-1}(x)}.
+\end{tikzcd}
+\]
+Choose a basis vector $v$ for $\gCSs{L}_{\Nm(x)}$ and write $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$ for the image of $v$ under the
 bottom map,
-for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{QC.2}, $v$ maps to
+for $v_i \in \gCSs{L}_{\Frob{}^i(x)}$.  By \ref{CS.2}, $v$ maps to
 $v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
 Let $\alpha_i \in \EEx$ represent $((F^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
-the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gqcs{L}_{\Nm(x)}$
-with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gqcs{L}_x$.
+the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gCSs{L}_{\Nm(x)}$
+with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gCSs{L}_x$.
 \end{proof}
@@
 \[
-\rho : \QC(\Res_{k'/k}G') \to \QC(G').
+\rho : \CS(\Res_{k'/k}G') \to \CS(G').
 \]
@@
 \[
-\rho : \QC(\Res_{k'/k}G') \to \QC(G'),
+\rho : \CS(\Res_{k'/k}G') \to \CS(G'),
 \]
@@
 \begin{tikzcd}
-\QCiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \QCiso{G'} \dar{\TrFrob{G'}}\\
+\CSiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \CSiso{G'} \dar{\TrFrob{G'}}\\
 G'(k')^* \rar & G'(k')^*,
@@
 
-\section{Applications}\label{sec:applications}
+\section{Applications to quasicharacters of $p$-adic tori and Abelian varieties}\label{sec:applications}
 
@@
 \[
-\Hom_\text{qc}(X(K),\EEx)
+\Hom_\text{QC}(X(K),\EEx)
 \]
@@
 \]
-In this section we will see how to geometrize and categorify quasicharacters of $X(K)$ using quasicharacter sheaves.
+In this section we will see how to geometrize and categorify quasicharacters of $X(K)$ using character sheaves.
 
@@
 
-\subsection{Quasicharacter sheaves on the Greenberg transform of a N\'eron model} \label{ssec:qc_on_GN}
+\subsection{character sheaves on the Greenberg transform of a N\'eron model} \label{ssec:CS_on_GN}
 
@@
 \[
-\varrho^R_n(X)^* : \QC(\Gr^R_n(X)) \to \QC(\Gr_R(X)),
+\varrho^R_n(X)^* : \CS(\Gr^R_n(X)) \to \CS(\Gr_R(X)),
 \]
 as in Lemma~\ref{lem:pullback}.
-%This functor is faithful, so we may view $\QC(\Gr^R_n(X))$ as a subcategory of $\QC(\Gr_R(X))$.
+%This functor is faithful, so we may view $\CS(\Gr^R_n(X))$ as a subcategory of $\CS(\Gr_R(X))$.
 
 We now define a category which will geometrize quasicharacters of $X(K)$.
-We begin by considering the rigid monoidal category $\QC(\Gr_R(X))$ defined in Section~\ref{ssec:category} without insisting that the commutative group scheme is smooth.
+We begin by considering the rigid monoidal category $\CS(\Gr_R(X))$ defined in Section~\ref{ssec:category} without insisting that the commutative group scheme is smooth.
 
@@
 A {\it quasicharacter sheaf for $X_K$} is an object of
-the following rigid monoidal subcategory of $\QC(\Gr_R(X))$, denoted by $\QC(X_K)$:
+the following rigid monoidal subcategory of $\CS(\Gr_R(X))$, denoted by $\QCS(X_K)$:
 \begin{enumerate}
 \item
-objects in $\QC(X_K)$ are the $\ell$-adic sheaves $\varrho^R_n(X)^*\qcs{L}$, for $n\in \NN$ and $\qcs{L} \in \QC(\Gr^R_n(X))$; 
+objects in $\QCS(X_K)$ are the $\ell$-adic sheaves $\varrho^R_n(X)^*\CSs{L}$, for $n\in \NN$ and $\CSs{L} \in \CS(\Gr^R_n(X))$; 
 \item
-morphisms $\varrho^R_n(X)^*\qcs{L} \to \varrho^R_m(X)^*\qcs{L}'$ in $\QC(X_K)$ are those morphisms in $\QC(\Gr_R(X))$ which take the form $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\qcs{L},\qcs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\qcs{L},\varrho^R_{m\leq n}(X)^*\qcs{L}')$ when $m\leq n$.
+morphisms $\varrho^R_n(X)^*\CSs{L} \to \varrho^R_m(X)^*\CSs{L}'$ in $\QCS(X_K)$ are those morphisms in $\CS(\Gr_R(X))$ which take the form $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\CSs{L},\CSs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\CSs{L},\varrho^R_{m\leq n}(X)^*\CSs{L}')$ when $m\leq n$.
 \end{enumerate}
@@
 \begin{remark}
-If $\varrho^R_n(X)^* : \QC(\Gr^R_n(X)) \to \QC(\Gr_R(X))$ is full then the construction above can be improved by forming $\QC(X_K)$ from the essential images of the functors $\varrho^R_n(X)^*$; however, we do not know if $\varrho^R_n(X)^*$ is full.
+If $\varrho^R_n(X)^* : \CS(\Gr^R_n(X)) \to \CS(\Gr_R(X))$ is full then the construction above can be improved by forming $\QCS(X_K)$ from the essential images of the functors $\varrho^R_n(X)^*$; however, we do not know if $\varrho^R_n(X)^*$ is full.
 \end{remark}
@@
 \begin{remark}
-We offer the following alternate construction of $\QC(X_K)$, which does not make use of subcategories.
+We offer the following alternate construction of $\QCS(X_K)$, which does not make use of subcategories.
 For objects, one considers triples 
 \[
-\qcs{F} \ceq (n, \{\qcs{F}_i\}_{n\leq i}, \{\alpha_{i \le j}\}_{n\le i \le j}),
+\CSs{F} \ceq (n, \{\CSs{F}_i\}_{n\leq i}, \{\alpha_{i \le j}\}_{n\le i \le j}),
 \] where $n$
-is a non-negative integer, each $\qcs{F}_i$ is a quasicharacter sheaf on $\Gr^R_i(X)$ and each 
-\[
-\alpha_{i \le j} : \qcs{L}_j \to \varrho^R_{i \le j}(X)^* \qcs{L}_i
+is a non-negative integer, each $\CSs{F}_i$ is a character sheaf on $\Gr^R_i(X)$ and each 
+\[
+\alpha_{i \le j} : \CSs{L}_j \to \varrho^R_{i \le j}(X)^* \CSs{L}_i
 \]
  is an isomorphism; here $\alpha_{i \le i}$ is the identity and the $\alpha_{i \le j}$ are compatible with each other.  
-If $\qcs{F} \ceq (n, \{\qcs{F}_i\}, \{\alpha_{i \le j}\})$
-and $\qcs{F}' \ceq (m, \{\qcs{F}'_i\}, \{\alpha'_{i \le j}\})$ are objects then $\Hom(\qcs{F}, \qcs{F}')$ is the set
-of equivalence classes of pairs $(k, \{\beta_i\}_{k \le i})$, where $n,m \le k$ and the $\beta_i : \qcs{F}_i \to \qcs{F}'_i$ are
-morphisms of quasicharacter sheaves so that
+If $\CSs{F} \ceq (n, \{\CSs{F}_i\}, \{\alpha_{i \le j}\})$
+and $\CSs{F}' \ceq (m, \{\CSs{F}'_i\}, \{\alpha'_{i \le j}\})$ are objects then $\Hom(\CSs{F}, \CSs{F}')$ is the set
+of equivalence classes of pairs $(k, \{\beta_i\}_{k \le i})$, where $n,m \le k$ and the $\beta_i : \CSs{F}_i \to \CSs{F}'_i$ are
+morphisms of character sheaves so that
 \[
 \begin{tikzcd}
-\qcs{F}_j \rar{\alpha_j} \dar{\beta_i} & \varrho^R_{i \le j}(X)^* \qcs{F}_i \dar{f_{i \le j}^*\beta_j} \\
-\qcs{F}'_j \rar{\alpha_j} & \varrho^R_{i \le j}(X)^* \qcs{L}'_i
+\CSs{F}_j \rar{\alpha_j} \dar{\beta_i} & \varrho^R_{i \le j}(X)^* \CSs{F}_i \dar{f_{i \le j}^*\beta_j} \\
+\CSs{F}'_j \rar{\alpha_j} & \varrho^R_{i \le j}(X)^* \CSs{L}'_i
 \end{tikzcd}
@@
 
-\begin{theorem}\label{thm:QCXK}
+\begin{theorem}\label{thm:CSXK}
 Let $K$ be a local field with residue field $\Fq$, in which $\ell$ is invertible; 
@@
 \begin{enumerate}
-\item
+\labitem{(1)}{x1}
 The trace of Frobenius provides a natural transformation between the additive functors
 \[
-F_{\QC}: X_K \mapsto \QCiso{X_K}
+F_{\QCS}: X_K \mapsto \QCSiso{X_K}
 \qquad\text{and}\qquad
-F_{\text{qc}}: X_K \mapsto \Hom_{\text{qc}}(X(K),\EEx)
+F_{\text{QCS}}: X_K \mapsto \Hom_{\text{QC}}(X(K),\EEx)
 \]
@@
 \begin{enumerate}[resume]
-\item there is a canonical short exact sequence of abelian groups 
-\[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{}} \to \QCiso{X_K} \to \Hom_\text{qc}(X(K),\EEx) \to 0;
-\] 
-\item for all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
-\item for all quasicharacter sheaves $\qcs{F}$ for $X_K$, there is a canonical isomorphism
-\[
-\Aut(\qcs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx).
+\labitem{(2)}{x2} there is a canonical short exact sequence of abelian groups 
+\[
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{}} \to \QCSiso{X_K} \to \Hom_\text{QC}(X(K),\EEx) \to 0;
+\] 
+\labitem{(3)}{x3} for all quasicharacter sheaves $\CSs{F}$, $\CSs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\CSs{F},\CSs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
+\labitem{(4)}{x4} for all quasicharacter sheaves $\CSs{F}$ for $X_K$, there is a canonical isomorphism
+\[
+\Aut(\CSs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx).
 \]
@@
 \begin{proof}
-\begin{enumerate}
-\item Use Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$, the fact that N\'eron models are unique up to isomorphism, the fact that every $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(X_K)$ and the observation that every object in $\QC(X_K)$ is in the essential image of $\QC(\Gr^R_n(X))$ for some $n$.
-\item Use Theorem~\ref{thm:snake} with $G = \Gr^R_n(X)$ and then argue as in part (i).
-\item Argue as in the proof of Lemma~\ref{lem:autornaught}.
-\item Use Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, the fact that the component group of $\Gr^R_n(X)$ is independent of $n$ and then argue as in part (i).
-\end{enumerate}
-\end{proof}
-
-\subsection{Quasicharacter sheaves for $p$-adic tori} \label{ssec:qc_tori}
+%\begin{enumerate}
+To prove \ref{x1}, use Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$, the fact that N\'eron models are unique up to isomorphism, the fact that every $\CS(\Gr^R_n(X))$ is a full subcategory of $\QCS(X_K)$ and the observation that every object in $\QCS(X_K)$ is in the essential image of $\CS(\Gr^R_n(X))$ for some $n$.
+To prove \ref{x2}, use Theorem~\ref{thm:snake} with $G = \Gr^R_n(X)$ and then argue as in part \ref{x1}.
+To prove \ref{x3}, argue as in the proof of Lemma~\ref{lem:autornaught}.
+To prove \ref{x4}, use Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, the fact that the component group of $\Gr^R_n(X)$ is independent of $n$ and then argue as in part \ref{x1}.
+%\end{enumerate}
+\end{proof}
+
+\subsection{Quasicharacter sheaves for $p$-adic tori} \label{ssec:CS_tori}
 
 As we explained in the Introduction, our original motivation for this paper was to find a geometrization and categorification of quasicharacters of $p$-adic tori. 
-This is is now provided by specializing Theorem~\ref{thm:QCXK} to the case when $X_K= T_K\in \mathcal{N}_K$ is an algebraic torus over $K$. 
+This is is now provided by specializing Theorem~\ref{thm:CSXK} to the case when $X_K= T_K\in \mathcal{N}_K$ is an algebraic torus over $K$. 
 Let $T$ be a Neron model for $T_K$.
@@
 where $X_*(T_K)$ is the cocharacter lattice of $T_K$ and $\mathcal{I}_K$ is the inertia group for $K$.
-Accordingly, by Theorem~\ref{thm:QCXK}, isomorphism classes of quasicharacter sheaves for $T_K$ determine quasicharacter sheaves according to the exact sequence
-\[
-0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{T_K} \to \Hom_\text{qc}(T(K),\EEx) \to 0.
-\]
-Also by Theorem~\ref{thm:QCXK} and \cite{bitan:discriminant}*{Eq 3.1}, the automorphism group of every $\qcs{F} \in \QC(T_K)$ is given by 
-\[
-\Aut(\qcs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx),
+Accordingly, by Theorem~\ref{thm:CSXK}, isomorphism classes of quasicharacter sheaves for $T_K$ determine quasicharacter sheaves according to the exact sequence
+\[
+0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \CSiso{T_K} \to \Hom_\text{CS}(T(K),\EEx) \to 0.
+\]
+Also by Theorem~\ref{thm:CSXK} and \cite{bitan:discriminant}*{Eq 3.1}, the automorphism group of every $\CSs{F} \in \CS(T_K)$ is given by 
+\[
+\Aut(\CSs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx),
 \]
@@
 it follows that the automorphism group of every quasicharacter sheaf for $T_K$ is $(\check{T}_\ell)^{\Weil{K}}$, where $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
+
+\subsection{Examples of quasicharacter sheaves for $p$-adic tori}
+
+Here we consider some examples that illustrate some of the essential features of the category of quasicharacter sheaves for $p$-adic tori. In this section, $K$ is a finite extension of $\QQ_p$.
+
+First, suppose $T = \GL(1)_{/K}$,
 
@@
 \begin{tikzcd}[column sep=60]
-\Hom_{\text{qc}}(X_K(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{X(K)}} &\Hom_{\text{qc}}(X_K(K), \EEx).
+\Hom_{\text{QC}}(X_K(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{X(K)}} &\Hom_{\text{QC}}(X_K(K), \EEx).
 \end{tikzcd}
@@
 \begin{equation}\label{men-pulled}
-f_n^* : \QC(\Res_{k'/k} \Gr_{en-1}^{R'}(X'))\to \QC(\Gr_{n-1}^{R}(X)).
+f_n^* : \CS(\Res_{k'/k} \Gr_{en-1}^{R'}(X'))\to \CS(\Gr_{n-1}^{R}(X)).
 \end{equation}
@@
 \[ 
-\Hom_\text{qc}(X_K(K'),\EEx) \to \Hom_\text{qc}(X_K(K)),\EEx)
+\Hom_\text{CS}(X_K(K'),\EEx) \to \Hom_\text{CS}(X_K(K)),\EEx)
 \]
@@
 \begin{equation}\label{eq:categorical_transfer}
-\QC(\Gr^{\OK}_{m-1}(X)) \cong \QC(\Gr^{\OL}_{m-1}(Y))
+\CS(\Gr^{\OK}_{m-1}(X)) \cong \CS(\Gr^{\OL}_{m-1}(Y))
 \end{equation}
@@
  \[
- \QC(\Gr^{\OK}_{m-1}(T)) \iso \QC(\Gr^{\OL}_{m-1}(M))
+ \CS(\Gr^{\OK}_{m-1}(T)) \iso \CS(\Gr^{\OL}_{m-1}(M))
  \]

### 2015-05-31 dictionary.tex
Commit before meeting David.

@@
 %% Fonts for quasicharacter sheaves
-\newcommand{\CSs}[1]{{\mathcal{#1}}}
-\newcommand{\gCSs}[1]{{\mathcal{\bar #1}}}
-\newcommand{\dualgcs}[1]{\gCSs{#1}^\dagger}
-\newcommand{\dualcs}[1]{\CSs{#1}^\dagger}
+\newcommand{\cs}[1]{{\mathcal{#1}}}
+\newcommand{\gcs}[1]{{\mathcal{\bar #1}}}
+\newcommand{\dualgcs}[1]{\gcs{#1}^\dagger}
+\newcommand{\dualcs}[1]{\cs{#1}^\dagger}
 %% Categories
@@
 \newcommand{\GxxG}{\text{$G \tight{1}{\times}{1} G$}}
-\newcommand{\LxL}{\text{$\gCSs{L} \tight{0}{\boxtimes}{0} \gCSs{L}$}}
-\newcommand{\ExE}{\text{$\CSs{E}\tight{0}{\boxtimes}{0}\CSs{E}$}}
-\newcommand{\bExE}{\text{$\gCSs{E}\tight{0}{\boxtimes}{0}\gCSs{E}$}}
+\newcommand{\LxL}{\text{$\gcs{L} \tight{0}{\boxtimes}{0} \gcs{L}$}}
+\newcommand{\ExE}{\text{$\cs{E}\tight{0}{\boxtimes}{0}\cs{E}$}}
+\newcommand{\bExE}{\text{$\gcs{E}\tight{0}{\boxtimes}{0}\gcs{E}$}}
 \newcommand{\AxA}{\text{$A \tight{1}{\times}{1} A$}}
@@
 \begin{equation}\label{introbox}
-m^* \CSs{E} \iso \CSs{E} \boxtimes \CSs{E},
+m^* \cs{E} \iso \cs{E} \boxtimes \cs{E},
 \end{equation}
@@
 %
-If one wishes to make a category from this class of local systems, one is led to consider morphisms $\CSs{E} \to \CSs{E}'$ of sheaves which are compatible with particular choices of \eqref{introbox} for $\CSs{E}$ and $\CSs{E'}$.
-{\it A priori}, the composition $\CSs{E} \to \CSs{E}' \to \CSs{E}''$ of two such morphisms need not be compatible with the choices of \eqref{introbox} for $\CSs{E}$ and $\CSs{E}''$.
+If one wishes to make a category from this class of local systems, one is led to consider morphisms $\cs{E} \to \cs{E}'$ of sheaves which are compatible with particular choices of \eqref{introbox} for $\cs{E}$ and $\cs{E'}$.
+{\it A priori}, the composition $\cs{E} \to \cs{E}' \to \cs{E}''$ of two such morphisms need not be compatible with the choices of \eqref{introbox} for $\cs{E}$ and $\cs{E}''$.
  However, for connected $G$ the isomorphism \eqref{introbox} is unique if it exists, and there is no impediment to making the dictionary categorical.
@@
 If $G$ is a commutative algebraic group over $\Fq$ which is not connected, then the isomorphism \eqref{introbox} need not be unique.
-In order to track the choice of isomorphism, consider the category of pairs $(\CSs{E},\mu_\CSs{E})$ where $\CSs{E}$ is a rank-one local system on $G$ and $\mu_\CSs{E} : m^*\CSs{E} \to \CSs{E}\boxtimes\CSs{E}$ is a chosen isomorphism of local systems on $G\times G$.
-In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of pairs $(\CSs{E},\mu_\CSs{E})$ to characters of $G(\Fq)$, but the epimomorphism need not be injective; consequently,
-every character of $G(\Fq)$ may be geometrized as a pair $(\CSs{E},\mu_\CSs{E})$ but perhaps not uniquely in the category of pairs. 
-While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious: if $(\CSs{E},\mu_\CSs{E})$ and $(\CSs{E}',\mu_\CSs{E}')$ determine the same character of $G(\Fq)$ then $\CSs{E}\iso \CSs{E}'$ as local systems on $G$.
+In order to track the choice of isomorphism, consider the category of pairs $(\cs{E},\mu_\cs{E})$ where $\cs{E}$ is a rank-one local system on $G$ and $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ is a chosen isomorphism of local systems on $G\times G$.
+In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of pairs $(\cs{E},\mu_\cs{E})$ to characters of $G(\Fq)$, but the epimomorphism need not be injective; consequently,
+every character of $G(\Fq)$ may be geometrized as a pair $(\cs{E},\mu_\cs{E})$ but perhaps not uniquely in the category of pairs. 
+While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious: if $(\cs{E},\mu_\cs{E})$ and $(\cs{E}',\mu_\cs{E}')$ determine the same character of $G(\Fq)$ then $\cs{E}\iso \cs{E}'$ as local systems on $G$.
 
 In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\Fq$,
-we simply replace the local system $\CSs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\CSs{E}$. 
+we simply replace the local system $\cs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\cs{E}$. 
 In this way we are led to the category $\CS(G)$ of {\it quasicharacter sheaves} on $G$ (\S\ref{ssec:category}).
-Objects in $\CS(G)$ are triples $(\gCSs{L}, \mu,\phi)$, where $\gCSs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\Fq}} \Spec{\bFq}$
-and $\phi : \Frob{G}^* \gCSs{L}\to \gCSs{L}$ and $\mu : {\bar m}^* \gCSs{L} \iso \gCSs{L} \boxtimes \gCSs{L}$ are isomorphisms of sheaves satisfying certain compatibility conditions.
+Objects in $\CS(G)$ are triples $(\gcs{L}, \mu,\phi)$, where $\gcs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\Fq}} \Spec{\bFq}$
+and $\phi : \Frob{G}^* \gcs{L}\to \gcs{L}$ and $\mu : {\bar m}^* \gcs{L} \iso \gcs{L} \boxtimes \gcs{L}$ are isomorphisms of sheaves satisfying certain compatibility conditions.
 Morphisms in $\CS(G)$ are then morphisms of Weil sheaves which are compatible with the extra structure.
@@
 One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
-%The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gCSs{L}, \mu,\phi)$ and $(\gCSs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gCSs{L},\phi)$ and $(\gCSs{L}',\phi')$ are isomorphic as Weil sheaves.
+%The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gcs{L}, \mu,\phi)$ and $(\gcs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gcs{L},\phi)$ and $(\gcs{L}',\phi')$ are isomorphic as Weil sheaves.
 
@@
 \[
-\Aut_{\CS{}}(\CSs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx),
-\]
-for all quasicharacter sheaves $\CSs{L}$ on $G$.
+\Aut_{\CS{}}(\cs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx),
+\]
+for all quasicharacter sheaves $\cs{L}$ on $G$.
 \end{theorem*}
@@
 where $\Hom_\text{QC}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
-We further show that automorphism groups in $\CS(T_K)$ are given, for every quasicharacter sheaf $\CSs{F}$ for $T_K$, by
-\[
-\Aut_{\QCS{}}(\CSs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
+We further show that automorphism groups in $\CS(T_K)$ are given, for every quasicharacter sheaf $\cs{F}$ for $T_K$, by
+\[
+\Aut_{\QCS{}}(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
 \]
@@
 A \emph{character sheaf on $G$} is a triple
-$\CSs{L}\ceq (\gCSs{L},\mu,\phi)$ where:
+$\cs{L}\ceq (\gcs{L},\mu,\phi)$ where:
 \begin{enumerate}
-\labitem{(CS.1)}{CS.1} $\gCSs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean a constructible $\ell$-adic sheaf on $\bG$, {\it lisse} on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
-\labitem{(CS.2)}{CS.2} $\mu: \bm^* \gCSs{L} \to \LxL$ is an isomorphism of
+\labitem{(CS.1)}{CS.1} $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean a constructible $\ell$-adic sheaf on $\bG$, {\it lisse} on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
+\labitem{(CS.2)}{CS.2} $\mu: \bm^* \gcs{L} \to \LxL$ is an isomorphism of
 sheaves on $\bGxG$ such that the following diagram commutes,
@@
   \begin{tikzcd}[row sep=30]
-  \bm_3^*\gCSs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
-    &&  \bm^*\gCSs{L} \boxtimes \gCSs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
-    \gCSs{L} \boxtimes \bm^* \gCSs{L} \arrow{rr}{\id \boxtimes \mu}
-    &&  \gCSs{L} \tight{0}{\boxtimes}{0} \LxL
-  \end{tikzcd}
-  \]
-\labitem{(CS.3)}{CS.3} $\phi : \Frob{G}^* \gCSs{L} \to \gCSs{L}$ is an
+  \bm_3^*\gcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
+    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
+    \gcs{L} \boxtimes \bm^* \gcs{L} \arrow{rr}{\id \boxtimes \mu}
+    &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL
+  \end{tikzcd}
+  \]
+\labitem{(CS.3)}{CS.3} $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an
   isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with
@@
   \begin{tikzcd}[row sep=20]
-  \Frob{\GxxG}^* \bm^* \gCSs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
+  \Frob{\GxxG}^* \bm^* \gcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
     && \Frob{\GxxG}^*(\LxL)\\
-    \arrow[equal]{u} \bm^*  \Frob{G}^* \gCSs{L} \arrow[swap]{d}{\bm^* \phi}
-    && \Frob{G}^*\gCSs{L}\boxtimes \Frob{G}^*\gCSs{L} \dar{\phi\boxtimes \phi} \arrow[equal]{u} \\
-    \bm^*\gCSs{L} \arrow{rr}{\mu}
+    \arrow[equal]{u} \bm^*  \Frob{G}^* \gcs{L} \arrow[swap]{d}{\bm^* \phi}
+    && \Frob{G}^*\gcs{L}\boxtimes \Frob{G}^*\gcs{L} \dar{\phi\boxtimes \phi} \arrow[equal]{u} \\
+    \bm^*\gcs{L} \arrow{rr}{\mu}
     && \LxL
@@
 \begin{enumerate}
-\labitem{(CS.4)}{CS.4} if $\CSs{L} = (\gCSs{L},\mu,\phi)$ and
-  $\CSs{L'} = (\gCSs{L'},\mu',\phi')$ are character sheaves on $G$ then
-  a morphism $\rho : \CSs{L} \to \CSs{L}'$ is a map $\brho : \gCSs{L} \to \gCSs{L'}$
+\labitem{(CS.4)}{CS.4} if $\cs{L} = (\gcs{L},\mu,\phi)$ and
+  $\cs{L'} = (\gcs{L'},\mu',\phi')$ are character sheaves on $G$ then
+  a morphism $\rho : \cs{L} \to \cs{L}'$ is a map $\brho : \gcs{L} \to \gcs{L'}$
   of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
@@
   \begin{tikzcd}[column sep=40]
-  \Frob{G}^* \gCSs{L} \rar{\Frob{G}^* \brho} \arrow[swap]{d}{\phi} & \Frob{G}^* \gCSs{L'} \dar{\phi'}
-  & & \arrow[swap]{d}{\mu} \bm^* \gCSs{L} \rar{\bm^* \brho} & \bm^* \gCSs{L'} \dar{\mu'} \\
-  \gCSs{L} \rar{\brho} & \gCSs{L'}
-  & {} & \LxL \rar{\tight{1}{\rho\boxtimes \rho}{1}} & \gCSs{L'} \tight{0}{\boxtimes}{0} \gCSs{L'}
+  \Frob{G}^* \gcs{L} \rar{\Frob{G}^* \brho} \arrow[swap]{d}{\phi} & \Frob{G}^* \gcs{L'} \dar{\phi'}
+  & & \arrow[swap]{d}{\mu} \bm^* \gcs{L} \rar{\bm^* \brho} & \bm^* \gcs{L'} \dar{\mu'} \\
+  \gcs{L} \rar{\brho} & \gcs{L'}
+  & {} & \LxL \rar{\tight{1}{\rho\boxtimes \rho}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
   \end{tikzcd}
@@
 \cite{etingof:09a}*{\S1.10} under the tensor product
-$\CSs{L} \otimes \CSs{L'}$ defined by $(\gCSs{L}\otimes\gCSs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
+$\cs{L} \otimes \cs{L'}$ defined by $(\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
 with duals given by applying the sheaf hom functor
@@
 We will describe the group $\CSiso{G}$ in Theorem~\ref{thm:snake}
-and the sets $\Hom(\CSs{L},\CSs{L}')$ in Theorem~\ref{thm:autornaught}; in this way we provide a complete description of the category $\CS(G)$.
+and the sets $\Hom(\cs{L},\cs{L}')$ in Theorem~\ref{thm:autornaught}; in this way we provide a complete description of the category $\CS(G)$.
 %
-In the meantime, we close this section with an elementary observation about $\Hom(\CSs{L},\CSs{L}')$.
+In the meantime, we close this section with an elementary observation about $\Hom(\cs{L},\cs{L}')$.
 We call a morphism of sheaves \emph{trivial} if it is zero on every stalk.
@@
 Let $G$ be a smooth commutative group scheme over $\Fq$.
-If $\CSs{L}$ and $\CSs{L}'$ are character sheaves on $G$, then
-every $\rho\in \Hom(\CSs{L},\CSs{L}')$ is either trivial or an isomorphism. 
+If $\cs{L}$ and $\cs{L}'$ are character sheaves on $G$, then
+every $\rho\in \Hom(\cs{L},\cs{L}')$ is either trivial or an isomorphism. 
 \end{lemma}
@@
 \begin{proof}
-Suppose $\rho \in \Hom(\CSs{L},\CSs{L}')$.
-We prove the lemma by considering the linear transformations $\brho_{\bar g} : \gCSs{L}_{\bar g} \to \gCSs{L}_{\bar g}$ at the stalks above geometric points ${\bar g}$ on $G$ and showing that, either each $\brho_{\bar g}$ trivial or each $\brho_{\bar g}$ is an isomorphism.
+Suppose $\rho \in \Hom(\cs{L},\cs{L}')$.
+We prove the lemma by considering the linear transformations $\brho_{\bar g} : \gcs{L}_{\bar g} \to \gcs{L}_{\bar g}$ at the stalks above geometric points ${\bar g}$ on $G$ and showing that, either each $\brho_{\bar g}$ trivial or each $\brho_{\bar g}$ is an isomorphism.
 (This idea is expanded upon in Section~\ref{ssec:stalks}.)
@@
 
-Let $(\gCSs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
+Let $(\gcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
 determines a geometric point $\bg$ fixed by $\Frob{G}$. 
-Together with the canonical isomorphism $(\Frob{G}^*\gCSs{L})_{\bg} \iso  \gCSs{L}_{\Frob{G}(\bg)}$, the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gCSs{L}_{\bg}$.
-Let $\trace(\phi_{\bg};\gCSs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gCSs{L}_{\bg})$ and let $\trFrob{(\gCSs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by 
+Together with the canonical isomorphism $(\Frob{G}^*\gcs{L})_{\bg} \iso  \gcs{L}_{\Frob{G}(\bg)}$, the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gcs{L}_{\bg}$.
+Let $\trace(\phi_{\bg};\gcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gcs{L}_{\bg})$ and let $\trFrob{(\gcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by 
 \begin{equation}\label{trWeil}
-\trFrob{(\gCSs{L},\phi)}(g) \ceq \trace(\phi_{\bg};\gCSs{L}_{\bg}),
+\trFrob{(\gcs{L},\phi)}(g) \ceq \trace(\phi_{\bg};\gcs{L}_{\bg}),
 \end{equation}
-commonly called the {\em trace of Frobenius of $(\gCSs{L},\phi)$}.
-Note that if $(\gCSs{L},\phi) \iso (\gCSs{L'},\phi')$ as Weil sheaves, 
-then $\trFrob{(\gCSs{L},\phi)} = \trFrob{(\gCSs{L'},\phi')}$ as functions on $G(\Fq)$.
-
-Now suppose $\CSs{L} = (\gCSs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$.
-Then the isomorphism $\bm^* \gCSs{L} \iso \gCSs{L} \boxtimes\gCSs{L}$ and the diagram of
+commonly called the {\em trace of Frobenius of $(\gcs{L},\phi)$}.
+Note that if $(\gcs{L},\phi) \iso (\gcs{L'},\phi')$ as Weil sheaves, 
+then $\trFrob{(\gcs{L},\phi)} = \trFrob{(\gcs{L'},\phi')}$ as functions on $G(\Fq)$.
+
+Now suppose $\cs{L} = (\gcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$.
+Then the isomorphism $\bm^* \gcs{L} \iso \gcs{L} \boxtimes\gcs{L}$ and the diagram of
 \ref{CS.3} guarantee
-that the function $\trFrob{(\gCSs{L},\phi)} : G(\Fq)\to \EEx$ is a group homomorphism, which we will also denote by $\trFrob{\CSs{L}}$.  Moreover,
-this homomorphism depends only on the isomorphism class of $\CSs{L}$, so we obtain a map
+that the function $\trFrob{(\gcs{L},\phi)} : G(\Fq)\to \EEx$ is a group homomorphism, which we will also denote by $\trFrob{\cs{L}}$.  Moreover,
+this homomorphism depends only on the isomorphism class of $\cs{L}$, so we obtain a map
 \begin{align*}
 \TrFrob{G} : \CSiso{G} &\to G(\Fq)^*, \\
-\CSs{L} &\mapsto \trFrob{\CSs{L}}.
+\cs{L} &\mapsto \trFrob{\cs{L}}.
 \end{align*}
-Since tensor products on the stalks of $\CSs{L}$ induce pointwise multiplication on the trace of Frobenius, $\TrFrob{G}$ is a group homomorphism.  We devote the remainder of this section to
+Since tensor products on the stalks of $\cs{L}$ induce pointwise multiplication on the trace of Frobenius, $\TrFrob{G}$ is a group homomorphism.  We devote the remainder of this section to
 studying the behavior of the trace of Frobenius under morphisms of group schemes.  These simple but important
@@
   f^* : \CS(G) &\to \CS(H) \\
-  (\gCSs{L},\mu,\phi) &\mapsto (\bf^*\gCSs{L},(\bfxf)^*\mu,\bf^*F)
+  (\gcs{L},\mu,\phi) &\mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)
   \end{align*}
@@
 \begin{proof}
-  Let $\CSs{L}$ be a character sheaf on $G$. 
+  Let $\cs{L}$ be a character sheaf on $G$. 
   Pullback by $\bf$ takes rank-one local systems to rank-one local systems.
@@
   apply the functor $(\bfxf)^*$
-  to \ref{CS.2} for $\CSs{L}$ and use the canonical isomorphism
-  $(\bfxf)^*(\LxL) \iso \bf^*\gCSs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gCSs{L}$.
-  To show that $f^*\CSs{L}$ satisfies
-  \ref{CS.3}, apply the same functor to \ref{CS.3} for $\CSs{L}$.
+  to \ref{CS.2} for $\cs{L}$ and use the canonical isomorphism
+  $(\bfxf)^*(\LxL) \iso \bf^*\gcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gcs{L}$.
+  To show that $f^*\cs{L}$ satisfies
+  \ref{CS.3}, apply the same functor to \ref{CS.3} for $\cs{L}$.
   Since $f$ is a morphism of group schemes defined over $\Fq$
@@
 \begin{lemma}\label{lem:product}
-If $G_1$ and $G_2$ are smooth commutative group schemes over $\Fq$ then the rule
-$\boxtimes : (\CSs{L}_1,\CSs{L}_2)\to \CSs{L}_1\boxtimes\CSs{L}_2$ defines an equivalence of categories
-\[
-\boxtimes : \CS(G_1)\times \CS(G_2) \to \CS(G_1\times G_2)
-\]
-such that
+If $G_1$ and $G_2$ are smooth commutative group schemes over $\Fq$ then the following diagram commutes.
 \[
 \begin{tikzcd}[column sep=60]
-\arrow{d}{\TrFrob{G_1} \times \TrFrob{G_2}} \CSiso{G_1}\times \CSiso{G_2} \arrow{r}{\boxtimes}
+\arrow{d}{\TrFrob{G_1} \times \TrFrob{G_2}} \CSiso{G_1}\times \CSiso{G_2} \arrow{r}{(\cs{L}_1,\cs{L}_2)\mapsto \cs{L}_1\boxtimes \cs{L}_2}
 & \arrow{d}{\TrFrob{G_1\times G_2}} \CSiso{G_1\times G_2}\\
@@
 \]
-commutes.
+Moreover, every character sheaf on $G_1\times G_2$ is isomorphic to $\cs{L}_1\boxtimes\cs{L}_2$ for some character sheaves $\cs{L}_1$ on $G_1$ and $\cs{L}_2$ on $G_2$.
 \end{lemma}
 \begin{proof}
-The only non-trivial part of the proof is to show that 
-\[\boxtimes
- : \CS(G_1)\times \CS(G_2) \to \CS(G_1\times G_2)
- \]
-is essentially surjective, so we will only address that point here.
+The only non-trivial part is the last claim, so we will only address that point here.
 %
@@
 %
-Now, let $\CSs{L} \ceq (\gCSs{L},\mu,\phi)$ be a character sheaf on $G$
-and set $\CSs{L}_1 \ceq q_1^* \CSs{L}$ and $\CSs{L}_2 \ceq q_2^* \CSs{L}$.
-By Lemma~\ref{lem:pullback}, $\CSs{L}_1$ is a character sheaf on $G_1$
-and $\CSs{L}_2$ is a character sheaf on $G_2$.
-We will obtain an isomorphism $\CSs{L} \iso  \CSs{L}_1\boxtimes \CSs{L}_2$.
+Now, let $\cs{L} \ceq (\gcs{L},\mu,\phi)$ be a character sheaf on $G$
+and set $\cs{L}_1 \ceq q_1^* \cs{L}$ and $\cs{L}_2 \ceq q_2^* \cs{L}$.
+By Lemma~\ref{lem:pullback}, $\cs{L}_1$ is a character sheaf on $G_1$
+and $\cs{L}_2$ is a character sheaf on $G_2$.
+We will obtain an isomorphism $\cs{L} \iso  \cs{L}_1\boxtimes \cs{L}_2$.
 
@@
 \begin{equation}\label{eq:fm}
-f^*\mu : f^* m^* \gCSs{L} \to f^*(\gCSs{L}\boxtimes \gCSs{L}) .
+f^*\mu : f^* m^* \gcs{L} \to f^*(\gcs{L}\boxtimes \gcs{L}) .
 \end{equation}
-We have already seen that $m\circ f = \id_G$, so $f^* m^* \gCSs{L} = \gCSs{L}$.  
-Since $f^*p_1^*\gCSs{L} = r_1^* q_1^* \gCSs{L} = r_1^* \gCSs{L}_1$ and $f^*p_2^*\gCSs{L} = r_2^* q_2^* \gCSs{L} = r_2^*\gCSs{L}_2$,
+We have already seen that $m\circ f = \id_G$, so $f^* m^* \gcs{L} = \gcs{L}$.  
+Since $f^*p_1^*\gcs{L} = r_1^* q_1^* \gcs{L} = r_1^* \gcs{L}_1$ and $f^*p_2^*\gcs{L} = r_2^* q_2^* \gcs{L} = r_2^*\gcs{L}_2$,
 we have 
 \[
-f^*(\gCSs{L}\boxtimes \gCSs{L})  = f^*p_1^*\gCSs{L}\otimes f^* p_2^*\gCSs{L} = \gCSs{L}_1\boxtimes \gCSs{L}_2.
-\]
-It follows that \eqref{eq:fm} gives an isomorphism $\gCSs{L} \to  \gCSs{L}_1\boxtimes \gCSs{L}_2$.
+f^*(\gcs{L}\boxtimes \gcs{L})  = f^*p_1^*\gcs{L}\otimes f^* p_2^*\gcs{L} = \gcs{L}_1\boxtimes \gcs{L}_2.
+\]
+It follows that \eqref{eq:fm} gives an isomorphism $\gcs{L} \to  \gcs{L}_1\boxtimes \gcs{L}_2$.
 It is routine to show that this morphism satisfies
-\ref{CS.4} as it applies here,
+\ref{CS.4}, as it applies here,
 from which it follows that we have exhibited an isomorphism
-$\CSs{L} \to \CSs{L}_1\boxtimes \CSs{L}_2$ of quasicharacters sheaves on $G\times G$.
-This completes the proof that $\boxtimes$ is essentially surjective.
+$\cs{L} \to \cs{L}_1\boxtimes \cs{L}_2$ of characters sheaves on $G\times G$.
 \end{proof}
@@
 In this section we consider a category of sheaves on $G$ obtained by
-replacing the Weil sheaf $(\gCSs{L}, \phi)$ on $\bG$ in the definition of a character sheaf with an $\ell$-adic local system on $G$ itself.
+replacing the Weil sheaf $(\gcs{L}, \phi)$ on $\bG$ in the definition of a character sheaf with an $\ell$-adic local system on $G$ itself.
 
 \begin{definition}
-Let $\bCS(G)$ be the category of pairs $(\CSs{E},\mu_\CSs{E})$
-where $\CSs{E}$ is an $\ell$-adic local system on $G$ of rank-one,
-equipped with an isomorphism $\mu_\CSs{E} : m^* \CSs{E} \to \CSs{E} \boxtimes \CSs{E}$
+Let $\bCS(G)$ be the category of pairs $(\cs{E},\mu_\cs{E})$
+where $\cs{E}$ is an $\ell$-adic local system on $G$ of rank-one,
+equipped with an isomorphism $\mu_\cs{E} : m^* \cs{E} \to \cs{E} \boxtimes \cs{E}$
 satisfying the analogue of \ref{CS.2} on $G$;
@@
 \begin{proof}
- Suppose $(\CSs{E},\mu_\CSs{E})$ in an object of $\bCS(G)$.
+ Suppose $(\cs{E},\mu_\cs{E})$ in an object of $\bCS(G)$.
  Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Set $\gCSs{L} = b_G^* \CSs{E}$. 
+ Set $\gcs{L} = b_G^* \cs{E}$. 
  The functor $b_G^*$ takes local systems on $G$ to local systems on $\bG$.
- The local system $\gCSs{L}$ comes equipped with an isomorphism
- $\phi: \Frob{G}^* \gCSs{L} \to \gCSs{L}$.
- The resulting functor from local systems on $G$ to Weil local systems on $\bG$, given on objects by $\CSs{E} \mapsto (\gCSs{L},\phi)$, 
+ The local system $\gcs{L}$ comes equipped with an isomorphism
+ $\phi: \Frob{G}^* \gcs{L} \to \gcs{L}$.
+ The resulting functor from local systems on $G$ to Weil local systems on $\bG$, given on objects by $\cs{E} \mapsto (\gcs{L},\phi)$, 
  is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} and \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}.
- The isomorphism $\mu \ceq b_{G\times G}^*\mu_\CSs{E}$ satisfies \ref{CS.2}
- for $\gCSs{L}$ and $\phi$ is compatible with $\mu$ in the sense of \ref{CS.3}.
- This construction defines the functor $B_G : \bCS(G) \to \CS(G)$ given on objects by $(\CSs{E},\mu_\CSs{E}) \mapsto (\gCSs{L},\mu, \phi)$, as defined here. 
+ The isomorphism $\mu \ceq b_{G\times G}^*\mu_\cs{E}$ satisfies \ref{CS.2}
+ for $\gcs{L}$ and $\phi$ is compatible with $\mu$ in the sense of \ref{CS.3}.
+ This construction defines the functor $B_G : \bCS(G) \to \CS(G)$ given on objects by $(\cs{E},\mu_\cs{E}) \mapsto (\gcs{L},\mu, \phi)$, as defined here. 
  Because morphisms in $\bCS(G)$ and $\CS(G)$ are morphisms of local systems on $G$ and $\bG$, respectively, satisfying condition~\ref{CS.4}, this functor is also full and faithful.
@@
 
-We will say that a character sheaf $\CSs{L} \in \CS(G)$ \emph{descends to $G$} if it is isomorphic to some $B_G(\CSs{E}, \mu_\CSs{E})$.
+We will say that a character sheaf $\cs{L} \in \CS(G)$ \emph{descends to $G$} if it is isomorphic to some $B_G(\cs{E}, \mu_\cs{E})$.
 
@@
 \begin{proof}
-Let $f$, $A$, $V$ and $\psi$ be as above and set $\CSs{E} = (f_! V_H)_\psi$.
-Since $A$ is abelian, $\CSs{E}$ is an $\ell$-adic local system on $G$ of rank one.
-We must show that $\CSs{E}$ comes equipped with an isomorphism $\mu_\CSs{E} : m^* \CSs{E} \to \CSs{E}\boxtimes\CSs{E}$.
+Let $f$, $A$, $V$ and $\psi$ be as above and set $\cs{E} = (f_! V_H)_\psi$.
+Since $A$ is abelian, $\cs{E}$ is an $\ell$-adic local system on $G$ of rank one.
+We must show that $\cs{E}$ comes equipped with an isomorphism $\mu_\cs{E} : m^* \cs{E} \to \cs{E}\boxtimes\cs{E}$.
 To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$ {\it cf.\ } \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}.
-In particular, $f^*\CSs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
-Since $f$ is a morphism of group schemes, the functor $f^*$ defines $\mu_\CSs{E} : m^*\CSs{E} \to \CSs{E}\boxtimes\CSs{E}$
+In particular, $f^*\cs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
+Since $f$ is a morphism of group schemes, the functor $f^*$ defines $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$
 from the isomorphism $m^*\psi \iso \psi \boxtimes\psi$ determined by $V\to V\otimes V$.
@@
 
-  Now let $(\gCSs{L},\mu,\phi)$ be a character sheaf on $G$
-  and let $\lambda : \Weil{}(G, \bg) \to \EEx$ be the character determined by $(\gCSs{L},\phi)$.
+  Now let $(\gcs{L},\mu,\phi)$ be a character sheaf on $G$
+  and let $\lambda : \Weil{}(G, \bg) \to \EEx$ be the character determined by $(\gcs{L},\phi)$.
   Composing with the splitting $\Weil{} \to \Weil{}(G,\bg)$ yields an $\ell$-adic character
@@
   $
-  \lambda_g(\Frob{}) =  \trFrob{\CSs{L}}(g).
+  \lambda_g(\Frob{}) =  \trFrob{\cs{L}}(g).
   $
 %
-  On the other hand, we have already seen that $\trFrob{\CSs{L}} : G(\Fq) \to \EEx$
+  On the other hand, we have already seen that $\trFrob{\cs{L}} : G(\Fq) \to \EEx$
   is a group homomorphism. 
   Since $G$ is an algebraic group over $\Fq$, $G(\Fq)$ is finite.
-  Therefore $\trFrob{\CSs{L}}(g) = \lambda_g(\Frob{})$ is a root of unity
+  Therefore $\trFrob{\cs{L}}(g) = \lambda_g(\Frob{})$ is a root of unity
   for every $g\in G(\Fq)$.  Since $\Weil{}$ is generated by
@@
   representations of $\pi_1(G,\bg)$ and $\ell$-adic local systems on $G$. Let
-  $\CSs{E}$ be a local system on $G$ in the isomorphism class
+  $\cs{E}$ be a local system on $G$ in the isomorphism class
   determined by this $\ell$-adic character of $\pi_1(G,\bg)$.
-  Then $b_G^*\CSs{E} \iso \gCSs{L}$.
+  Then $b_G^*\cs{E} \iso \gcs{L}$.
 
@@
  \[
-  b_{G\times G}^* : \Hom(m^*\CSs{E},\CSs{E}\boxtimes\CSs{E}) \to \Hom({\bar m}^*\gCSs{L},\gCSs{L}\boxtimes\gCSs{L})
+  b_{G\times G}^* : \Hom(m^*\cs{E},\cs{E}\boxtimes\cs{E}) \to \Hom({\bar m}^*\gcs{L},\gcs{L}\boxtimes\gcs{L})
  \]
@@
   in which $\ell$-adic local systems sit as full subcategories).
-  Let $\mu_\CSs{E} : m^*\CSs{E} \to \CSs{E}\boxtimes\CSs{E}$ be the isomorphism matching
-  $\mu : {\bar m}^*\gCSs{L} \to \gCSs{L}\boxtimes\gCSs{L}$,
-  the latter appearing in the definition of $\CSs{L}$.
-  Then, as in Section~\ref{ssec:descentG}, $(\CSs{E},\mu_\CSs{E})$ is an object of $\bCS(G)$
-  and $\CSs{L} \ceq (\gCSs{L},\mu,\phi)$ is isomorphic to $(b_G^*\CSs{E},b_{G\times G}^*\mu_\CSs{E})$ in $\CS(G)$.
+  Let $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ be the isomorphism matching
+  $\mu : {\bar m}^*\gcs{L} \to \gcs{L}\boxtimes\gcs{L}$,
+  the latter appearing in the definition of $\cs{L}$.
+  Then, as in Section~\ref{ssec:descentG}, $(\cs{E},\mu_\cs{E})$ is an object of $\bCS(G)$
+  and $\cs{L} \ceq (\gcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\cs{E},b_{G\times G}^*\mu_\cs{E})$ in $\CS(G)$.
   Thus, the full and faithful functor $B_G : \bCS(G) \to \CS(G)$ from Section~\ref{ssec:descentG}
@@
  \begin{enumerate}
- \item $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ is an isomorphism of groups;
- \item every character sheaf on $G$ is isomorphic to one defined by a discrete isogeny;
- \item $\Aut(\CSs{L}) = 1$, for all character sheaves $\CSs{L}$ on $G$.
+ \labitem{(1)}{c1} $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ is an isomorphism of groups;
+ \labitem{(2)}{c2} every character sheaf on $G$ is isomorphic to one defined by a discrete isogeny;
+ \labitem{(3)}{c3} $\Aut(\cs{L}) = 1$, for all character sheaves $\cs{L}$ on $G$.
  \end{enumerate}
@@
 \begin{proof}
-In Lemma~\ref{lem:bounded_connected}, we saw that every character sheaf $\CSs{L}$ on $\bG$ descends to $G$; let $\CSs{E}$ be an object of $\bCS(G)$ for which $B_G(\CSs{E}) \iso \CSs{L}$.
- Since the functor $B_G : \bCS(G) \to \CS(G)$ is full and faithful, $\Aut(\CSs{L}) = \Aut(\CSs{E})$.
+In Lemma~\ref{lem:bounded_connected}, we saw that every character sheaf $\cs{L}$ on $\bG$ descends to $G$; let $\cs{E}$ be an object of $\bCS(G)$ for which $B_G(\cs{E}) \iso \cs{L}$.
+ Since the functor $B_G : \bCS(G) \to \CS(G)$ is full and faithful, $\Aut(\cs{L}) = \Aut(\cs{E})$.
 From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields, as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3}, gives us all we need, as we briefly recall.
@@
 As in the proof of Proposition~\ref{prop:finite}, use \'etale descent to see that pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.
-Under this equivalence, local systems $\CSs{E}$ on $G$ arising from objects in $\bCS(G)$ are matched with $G(\Fq)$-equivariant constant local systems of rank-one on $G$, and therefore with one-dimensional representations of $G(\Fq)$.
-In the same way, pullback along the isogeny $\Lang\times\Lang : G\times G\to G\times G$ matches the extra structure $\mu_\CSs{E} : m^*\CSs{E} \to \CSs{E}\boxtimes\CSs{E}$ with an isomorphism $m^*V \to V\boxtimes V$ of one-dimensional representations of $G(\Fq)\times G(\Fq)$, which is exactly an isomorphism $V \to V\otimes V$ of one-dimensional representations, which is exactly the choice of an isomorphism $V\iso \EE$.
+Under this equivalence, local systems $\cs{E}$ on $G$ arising from objects in $\bCS(G)$ are matched with $G(\Fq)$-equivariant constant local systems of rank-one on $G$, and therefore with one-dimensional representations of $G(\Fq)$.
+In the same way, pullback along the isogeny $\Lang\times\Lang : G\times G\to G\times G$ matches the extra structure $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ with an isomorphism $m^*V \to V\boxtimes V$ of one-dimensional representations of $G(\Fq)\times G(\Fq)$, which is exactly an isomorphism $V \to V\otimes V$ of one-dimensional representations, which is exactly the choice of an isomorphism $V\iso \EE$.
 We see that $\bCS(G)$ is equivalent to the category of characters of $G(\Fq)$.
 Let $\bg$ be a geometric point above $g \in G(\Fq)$.
-If $\CSs{E}$ matches $\psi : G(\Fq)\to \EEx$ under this equivalence, a simple calculation on stalks reveals that the action of Frobenius on $\CSs{E}_{\bar g}$ is multiplication by $\psi(g)^{-1}$.
-In other words, for every $\CSs{E}$ in $\bCS(G)$, the trace of $\Lang^*\CSs{E}$ is $\trFrob{\CSs{E}}^{-1}$ as a representation of $G(\Fq)$, proving parts (i) and (ii).
-
-To finish the proof of part (iii), suppose $\Lang^*\CSs{E} = V$ with isomorphism $V \to V\otimes V$.
-Observe that the equivalence above establishes a bijection between $\Aut(\CSs{E})$ and the group of automorphisms of $\rho : V\to V$ for which
+If $\cs{E}$ matches $\psi : G(\Fq)\to \EEx$ under this equivalence, a simple calculation on stalks reveals that the action of Frobenius on $\cs{E}_{\bar g}$ is multiplication by $\psi(g)^{-1}$.
+In other words, for every $\cs{E}$ in $\bCS(G)$, the trace of $\Lang^*\cs{E}$ is $\trFrob{\cs{E}}^{-1}$ as a representation of $G(\Fq)$, proving parts \ref{c1} and \ref{c2}.
+
+To finish the proof of part \ref{c3}, suppose $\Lang^*\cs{E} = V$ with isomorphism $V \to V\otimes V$.
+Observe that the equivalence above establishes a bijection between $\Aut(\cs{E})$ and the group of automorphisms of $\rho : V\to V$ for which
 \[
@@
 commutes. 
-Since the only such isomorphism $\rho$ is $\id_V$, it follows that $\Aut(\CSs{E}) = 1$, completing the proof.
+Since the only such isomorphism $\rho$ is $\id_V$, it follows that $\Aut(\cs{E}) = 1$, completing the proof.
 \end{proof}
@@
 We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of character sheaves on $G$ is equivalent to the category of one-dimensional representations $V$ of $G(\Fq)$ equipped with an isomorphism $V\iso \EE$, and therefore equivalent to the category of characters $\psi$ of $G(\Fq)$.
-We have also just seen that if the character of $\Lang^*\CSs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\CSs{E} : \CSs{E} \to \CSs{E}\boxtimes\CSs{E}$.
-This fact leads to a perspective on the function-sheaf dictionary common in the literature in which one considers one-dimensional local systems $\CSs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\CSs{E} \iso \CSs{E} \boxtimes\CSs{E}$ \cite{kamgarpour:09a}*{Intro}.
-As a slight variation, one may also consider one-dimensional local systems $\gCSs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gCSs{L} \iso \gCSs{L}$ and an isomorphism $\bm^*\gCSs{L} \iso \gCSs{L} \boxtimes\gCSs{L}$.
+We have also just seen that if the character of $\Lang^*\cs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\cs{E} : \cs{E} \to \cs{E}\boxtimes\cs{E}$.
+This fact leads to a perspective on the function-sheaf dictionary common in the literature in which one considers one-dimensional local systems $\cs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\cs{E} \iso \cs{E} \boxtimes\cs{E}$ \cite{kamgarpour:09a}*{Intro}.
+As a slight variation, one may also consider one-dimensional local systems $\gcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gcs{L} \iso \gcs{L}$ and an isomorphism $\bm^*\gcs{L} \iso \gcs{L} \boxtimes\gcs{L}$.
 
 Although the category of character sheaves on $G$ specializes to the one described above when $G$ is connected and of finite type, this description is not sufficient when extending the dictionary to smooth commutative group schemes.
-In particular, for a given $\gCSs{L}$ and $\phi$ there may be many $\mu$ so that $(\gCSs{L},\mu,\phi)$ is a character sheaf.
+In particular, for a given $\gcs{L}$ and $\phi$ there may be many $\mu$ so that $(\gcs{L},\mu,\phi)$ is a character sheaf.
 For \'etale $G$, Proposition~\ref{prop:etale-iso} shows that $\Hh^2(\bG,\EEx)^{\Weil{}}$ measures the possibilities for $\mu$.
@@
 %
-A character sheaf $\CSs{L}$ on an \'etale commutative group scheme $G$ over $\Fq$ is:
+A character sheaf $\cs{L}$ on an \'etale commutative group scheme $G$ over $\Fq$ is:
 \begin{enumerate}
  \labitem{(cs.1)}{cs.1} an indexed set of one-dimensional
-  $\EE$-vector spaces $\gCSs{L}_x$, as $x$ runs over
+  $\EE$-vector spaces $\gcs{L}_x$, as $x$ runs over
   $G(\bFq)$;
@@
  \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms
-  $\mu_{x,y} : \gCSs{L}_{x+y} \xrightarrow{\iso} \gCSs{L}_{x} \otimes\gCSs{L}_{y}$,
+  $\mu_{x,y} : \gcs{L}_{x+y} \xrightarrow{\iso} \gcs{L}_{x} \otimes\gcs{L}_{y}$,
   for all $x,y \in G(\bFq)$, such that
@@
    \begin{tikzcd}[row sep=40]
-    \gCSs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
-    && \gCSs{L}_{x+y}\otimes\gCSs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
-    \gCSs{L}_{x} \otimes\gCSs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
-    && \gCSs{L}_{x} \otimes\gCSs{L}_{y} \otimes\gCSs{L}_{z}
+    \gcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
+    && \gcs{L}_{x+y}\otimes\gcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
+    \gcs{L}_{x} \otimes\gcs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
+    && \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes\gcs{L}_{z}
    \end{tikzcd}
@@
   commutes, for all $x,y,z\in G(\bFq)$; and
- \labitem{(cs.3)}{cs.3} an indexed set of isomorphisms $\phi_{x} : \gCSs{L}_{\Frob{}(x)} \to \gCSs{L}_x$
+ \labitem{(cs.3)}{cs.3} an indexed set of isomorphisms $\phi_{x} : \gcs{L}_{\Frob{}(x)} \to \gcs{L}_x$
   such that
@@
    \begin{tikzcd}[row sep=40]
-    \gCSs{L}_{\Frob{}(x)+\Frob{}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{}(x),\Frob{}(y)}}
-    && \gCSs{L}_{\Frob{}(x)}\otimes\gCSs{L}_{\Frob{}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
-    \gCSs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
-    && \gCSs{L}_x \otimes\gCSs{L}_y
+    \gcs{L}_{\Frob{}(x)+\Frob{}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{}(x),\Frob{}(y)}}
+    && \gcs{L}_{\Frob{}(x)}\otimes\gcs{L}_{\Frob{}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
+    \gcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
+    && \gcs{L}_x \otimes\gcs{L}_y
    \end{tikzcd}
@@
 \end{enumerate}
-Under this equivalence, a morphism $\rho : \CSs{L} \to \CSs{L'}$ of character sheaves on $G$ is given by
+Under this equivalence, a morphism $\rho : \cs{L} \to \cs{L'}$ of character sheaves on $G$ is given by
 \begin{enumerate}
- \labitem{(cs.4)}{cs.4} an indexed set $\brho_x : \gCSs{L}_x \to \gCSs{L'}_x$
+ \labitem{(cs.4)}{cs.4} an indexed set $\brho_x : \gcs{L}_x \to \gcs{L'}_x$
   of linear transformations such that
@@
    \begin{tikzcd}[column sep=40]
-    \arrow[swap]{d}{\phi_x} \gCSs{L}_{\Frob{}(x)} \rar{\brho_{\Frob{}(x)}} & \gCSs{L'}_{\Frob{}(x)} \dar{\phi_x'}
+    \arrow[swap]{d}{\phi_x} \gcs{L}_{\Frob{}(x)} \rar{\brho_{\Frob{}(x)}} & \gcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
     &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-    & \arrow[swap]{d}{\mu_{x,y}} \gCSs{L}_{x+y} \rar{\brho_{x+y}} & \gCSs{L'}_{x+y} \dar{\mu'_{x,y}} \\
-    \gCSs{L}_x \rar{\brho_x} & \gCSs{L'}_x
-    & {} & \gCSs{L}_x\otimes\gCSs{L}_y \rar{\brho_x\otimes\brho_y} & \gCSs{L'}_x \otimes\gCSs{L'}_y
+    & \arrow[swap]{d}{\mu_{x,y}} \gcs{L}_{x+y} \rar{\brho_{x+y}} & \gcs{L'}_{x+y} \dar{\mu'_{x,y}} \\
+    \gcs{L}_x \rar{\brho_x} & \gcs{L'}_x
+    & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\brho_x\otimes\brho_y} & \gcs{L'}_x \otimes\gcs{L'}_y
    \end{tikzcd}
@@
 \]
-Let $\CSs{L} = (\gCSs{L},\mu,\phi)$ be a character sheaf on $G$.
-For each geometric point $x\in {\bar G}$, choose a basis $\{ v_x \}$ for $\gCSs{L}_x$.
-Through this choice, $\CSs{L}$ determines functions
+Let $\cs{L} = (\gcs{L},\mu,\phi)$ be a character sheaf on $G$.
+For each geometric point $x\in {\bar G}$, choose a basis $\{ v_x \}$ for $\gcs{L}_x$.
+Through this choice, $\cs{L}$ determines functions
 \begin{align*}
@@
 \[\alpha\oplus \beta \in Z^2(E^\bullet_G).\]
-Although the cocycle $\alpha\oplus \beta$ is not well defined by $\CSs{L}$, its class in $\Hh^2(E^\bullet_G)$ is.
-To see this, let $\{ v'_x \in \gCSs{L}_x^\times \tq x \in {\bar G}\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$ be defined by $\CSs{L}$ and this choice, as above.
+Although the cocycle $\alpha\oplus \beta$ is not well defined by $\cs{L}$, its class in $\Hh^2(E^\bullet_G)$ is.
+To see this, let $\{ v'_x \in \gcs{L}_x^\times \tq x \in {\bar G}\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$ be defined by $\cs{L}$ and this choice, as above.
 Now let $\delta \in C^0(\Weil{},C^1({\bar G},\EEx))$ correspond to the function $d : {\bar G}\to \EEx$ defined by $v'_x = d(x) v_x$.
@@
 so the class $[\alpha\oplus\beta]$ of $\alpha\oplus\beta$ in $\Hh^2(E^\bullet_G)$ is independent of the choice made above.
-It is also easy to see that $[\alpha\oplus\beta] = [\alpha_0\oplus\beta_0]$ when $\CSs{L} \iso \CSs{L}_0$,
+It is also easy to see that $[\alpha\oplus\beta] = [\alpha_0\oplus\beta_0]$ when $\cs{L} \iso \cs{L}_0$,
 which concludes the definition of the function
@@
 S_G : \CSiso{G} &\to \Hh^2(E^\bullet_G)\\
-[\CSs{L}] &\mapsto [\alpha\oplus \beta].
+[\cs{L}] &\mapsto [\alpha\oplus \beta].
 \end{align*}
-It is also easy to see that $[\alpha_1\oplus\beta_1] + [\alpha_2\oplus\beta_2] = [\alpha_3\oplus\beta_3]$ when $\CSs{L}_3 = \CSs{L}_1\otimes \CSs{L}_2$, so $S_G$ is a group homomorphism.
+It is also easy to see that $[\alpha_1\oplus\beta_1] + [\alpha_2\oplus\beta_2] = [\alpha_3\oplus\beta_3]$ when $\cs{L}_3 = \cs{L}_1\otimes \cs{L}_2$, so $S_G$ is a group homomorphism.
 
@@
 \begin{proof}
-Suppose $[\CSs{L}] \in \CSiso{G}$ with $S_G([\CSs{L}]) = [\alpha \oplus \beta] = 0$,
+Suppose $[\cs{L}] \in \CSiso{G}$ with $S_G([\cs{L}]) = [\alpha \oplus \beta] = 0$,
 so that $\alpha \oplus \beta = d\sigma$ for some $\sigma \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
-For each $x\in {\bar G}$, define $\sigma_x : \gCSs{L}_x \to \EE$ by $\sigma_x : v_x \mapsto \sigma(x)$.
-Then the indexed set of isomorphisms $\{ \sigma_x : \gCSs{L}_x \to \EE \tq x\in {\bar G}\}$
-defines an isomorphism $\CSs{L} \to (\EE)_G$.
-Since $\CSs{L} = 0 \in \CSiso{G}$, $S_G$ is injective.
+For each $x\in {\bar G}$, define $\sigma_x : \gcs{L}_x \to \EE$ by $\sigma_x : v_x \mapsto \sigma(x)$.
+Then the indexed set of isomorphisms $\{ \sigma_x : \gcs{L}_x \to \EE \tq x\in {\bar G}\}$
+defines an isomorphism $\cs{L} \to (\EE)_G$.
+Since $\cs{L} = 0 \in \CSiso{G}$, $S_G$ is injective.
 
@@
 $b = \beta(\Frob{}) \in C^1({\bar G},\EEx)$, which are related to $\alpha$ and $\beta$ as above.
-Set $\gCSs{L}_x = \EE$, define $\mu_{x,y} : \gCSs{L}_{x+y} \to \gCSs{L}_x\otimes\gCSs{L}_y$
-by $\mu_{x,y}(1) = a(x,y) (1\otimes 1)$ and $\phi_x : \gCSs{L}_{\Frob{G}(x)} \to \gCSs{L}_x$ by $\phi_x(1)= b(x)$.
+Set $\gcs{L}_x = \EE$, define $\mu_{x,y} : \gcs{L}_{x+y} \to \gcs{L}_x\otimes\gcs{L}_y$
+by $\mu_{x,y}(1) = a(x,y) (1\otimes 1)$ and $\phi_x : \gcs{L}_{\Frob{G}(x)} \to \gcs{L}_x$ by $\phi_x(1)= b(x)$.
 Then \ref{CS.1} holds since $d_G \alpha =0$ and \ref{CS.2} holds since $d_{\Weil{}}\alpha =d_G \beta$.
-Tracing the construction backward, we have defined a character sheaf $\CSs{L}$ on $G$ with
-$S_G(\CSs{L}) = [\alpha\oplus\beta\oplus 0]$, showing that $S_G$ is surjective.
+Tracing the construction backward, we have defined a character sheaf $\cs{L}$ on $G$ with
+$S_G(\cs{L}) = [\alpha\oplus\beta\oplus 0]$, showing that $S_G$ is surjective.
 \end{proof}
@@
 Every representative cocycle $\beta \in Z^1(\Weil{},\bG^*)$ determines a homomorphism $\beta(\Frob{}) : G(\bFq)\to \EEx$ such that $\beta(\Frob{})\vert_{G(\Fq)} = \chi$.
-Set $\gCSs{L}_x = \EE$ for every $x\in G(\bFq)$.
-Define $\mu_{x,y} : \gCSs{L}_{x+y} \to \gCSs{L}_x\otimes \gCSs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$ and
-$\phi_{x} : \gCSs{L}_{\Frob{}(x)} \to \gCSs{L}_x$ by $\phi_{x}(1) = \beta(\Frob{})(x)$.
+Set $\gcs{L}_x = \EE$ for every $x\in G(\bFq)$.
+Define $\mu_{x,y} : \gcs{L}_{x+y} \to \gcs{L}_x\otimes \gcs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$ and
+$\phi_{x} : \gcs{L}_{\Frob{}(x)} \to \gcs{L}_x$ by $\phi_{x}(1) = \beta(\Frob{})(x)$.
 Since $\beta(\Frob{}) : G(\bFq) \to \EEx$ is a group homomorphism,
 condition \eqref{nohom} is satisfied with $a =1$.
-So $\CSs{L} = (\gCSs{L}, \mu, \phi)$
-is a character sheaf with $\trFrob{\CSs{L}} = \chi$.
+So $\cs{L} = (\gcs{L}, \mu, \phi)$
+is a character sheaf with $\trFrob{\cs{L}} = \chi$.
 This shows that $\TrFrob{G}$ is surjective.
@@
 so $\beta-\beta' = d_{\Weil{}} \delta$ for some $\delta \in C^0(\Weil{},\bG^*)$ defining $d \in \Hom(G(\bFq),\EEx)$.
-Let $\CSs{L}'$ be the character sheaf on $G$ defined by $\beta'$, as above.
-For each $x\in G(\bFq)$, define $\brho_x :\CSs{L}_x\to \CSs{L}'_x$ by $\brho_x(1) = d(x)$.
-The collection of isomorphisms $\{ \brho_x \tq x\in G(\bFq)\}$ satisfies condition~\ref{CS.4}, so it defines a morphism $\rho : \CSs{L}\to \CSs{L}'$, which is clearly an isomorphism. 
+Let $\cs{L}'$ be the character sheaf on $G$ defined by $\beta'$, as above.
+For each $x\in G(\bFq)$, define $\brho_x :\cs{L}_x\to \cs{L}'_x$ by $\brho_x(1) = d(x)$.
+The collection of isomorphisms $\{ \brho_x \tq x\in G(\bFq)\}$ satisfies condition~\ref{CS.4}, so it defines a morphism $\rho : \cs{L}\to \cs{L}'$, which is clearly an isomorphism. 
 %
@@
 Now suppose $\chi_1, \chi_2 \in G(\Fq)^*$.
-Pick cocycles $\beta_1,\beta_2\in Z^1(\Weil{},\bG^*)$ and construct character sheaves $\CSs{L}_1$ and $\CSs{L}_2$ on $G$ as above.
-Since $\CSs{L}_1\otimes \CSs{L}_2$ is exactly the character sheaf built from the cocycle $\beta_1\cdot \beta_2$, and since $\trFrob{\CSs{L}_1\otimes \CSs{L}_2} = \trFrob{\CSs{L}_1}\cdot \trFrob{\CSs{L}_2}$, the section of $\TrFrob{G}$ defined here is a homomorphism.
+Pick cocycles $\beta_1,\beta_2\in Z^1(\Weil{},\bG^*)$ and construct character sheaves $\cs{L}_1$ and $\cs{L}_2$ on $G$ as above.
+Since $\cs{L}_1\otimes \cs{L}_2$ is exactly the character sheaf built from the cocycle $\beta_1\cdot \beta_2$, and since $\trFrob{\cs{L}_1\otimes \cs{L}_2} = \trFrob{\cs{L}_1}\cdot \trFrob{\cs{L}_2}$, the section of $\TrFrob{G}$ defined here is a homomorphism.
 \end{proof}
@@
 
-While most of this paper focuses on the question of determining the isomorphism classes of objects, a complete understanding of the morphisms in $\CS(G)$ also requires a description of the automorphisms of an arbitrary character sheaf $\CSs{L}$.
+While most of this paper focuses on the question of determining the isomorphism classes of objects, a complete understanding of the morphisms in $\CS(G)$ also requires a description of the automorphisms of an arbitrary character sheaf $\cs{L}$.
 
@@
 Let $G$ be an \'etale commutative group scheme over $\Fq$.
-If $\CSs{L}$ and $\CSs{L}'$ are character sheaves on $G$ then
-every $\rho\in \Hom(\CSs{L},\CSs{L}')$ is either trivial or an isomorphism. Moreover, the trace map induces an isomorphism of groups
-\[
-\Aut(\CSs{L}) \to \Hom(G(\bFq)_{\Weil{}}, \EEx).
+If $\cs{L}$ and $\cs{L}'$ are character sheaves on $G$ then
+every $\rho\in \Hom(\cs{L},\cs{L}')$ is either trivial or an isomorphism. Moreover, the trace map induces an isomorphism of groups
+\[
+\Aut(\cs{L}) \to \Hom(G(\bFq)_{\Weil{}}, \EEx).
 \]
@@
 \begin{proof}
-We have already seen, in Lemma~\ref{lem:autornaught}, that every $\rho\in \Hom(\CSs{L},\CSs{L}')$ is either trivial or an isomorphism.
-Now suppose $\rho \in \Aut(\CSs{L})$.
+We have already seen, in Lemma~\ref{lem:autornaught}, that every $\rho\in \Hom(\cs{L},\cs{L}')$ is either trivial or an isomorphism.
+Now suppose $\rho \in \Aut(\cs{L})$.
 The second diagram in \ref{CS.4} shows that the association $x \mapsto \brho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{CS.4} shows that it factors through $G(\bFq)_{\Weil{}}$.
 
-Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism, then defining $\brho_x$ as multiplication by $\rho(x)$ will define a morphism $\gCSs{L} \to \gCSs{L}'$ satisfy the two diagrams in \ref{CS.4}.
+Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism, then defining $\brho_x$ as multiplication by $\rho(x)$ will define a morphism $\gcs{L} \to \gcs{L}'$ satisfy the two diagrams in \ref{CS.4}.
 
@@
 \begin{proof}
-Let $\CSs{L}$ be a character sheaf on $\pi_0(G)$ and let $\rho : \pi_0^*\CSs{L} \to (\EE)_{G}$ be an isomorphism in $\CS(G)$. 
+Let $\cs{L}$ be a character sheaf on $\pi_0(G)$ and let $\rho : \pi_0^*\cs{L} \to (\EE)_{G}$ be an isomorphism in $\CS(G)$. 
 For each $x\in \pi_0(\bG)$, set $\bG^x \ceq \pi_0^{-1}(x)$.
-The restriction $\pi_0^*\gCSs{L}\vert_{\bG^x}$ is the constant sheaf $(\gCSs{L}_x)_{\bG^x}$ so the isomorphism $\brho\vert_{\bG^x} : (\gCSs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gCSs{L}_x \to (\EE)_x$.
-The collection $\{ \brho_x \tq x\in \pi_0(\bG) \}$ determines an isomorphism $\CSs{L} \to (\EE)_{\pi_0(G)}$  in $\CS(\pi_0(G))$.
+The restriction $\pi_0^*\gcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gcs{L}_x)_{\bG^x}$ so the isomorphism $\brho\vert_{\bG^x} : (\gcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gcs{L}_x \to (\EE)_x$.
+The collection $\{ \brho_x \tq x\in \pi_0(\bG) \}$ determines an isomorphism $\cs{L} \to (\EE)_{\pi_0(G)}$  in $\CS(\pi_0(G))$.
 \end{proof}
@@
 First note that $\iota_0^* \circ \pi_0^*$ is trivial by Lemma~\ref{lem:pullback}.
-So it suffices to show that if $\CSs{L} = (\gCSs{L},\mu,\phi)$ is a character sheaf on $G$
-with $\CSs{L}\vert_{G^0} = (\EE)_{G^0}$ then $\CSs{L}$ is in the essential image of $\pi_0^*$.
+So it suffices to show that if $\cs{L} = (\gcs{L},\mu,\phi)$ is a character sheaf on $G$
+with $\cs{L}\vert_{G^0} = (\EE)_{G^0}$ then $\cs{L}$ is in the essential image of $\pi_0^*$.
 
@@
 Set $a = g^{-1}g'$ and note that $a$ is a geometric point in $\bG^0$.
-Let $\mu_{g,a} : \gCSs{L}_{ga} \to \gCSs{L}_g \otimes \gCSs{L}_a$
+Let $\mu_{g,a} : \gcs{L}_{ga} \to \gcs{L}_g \otimes \gcs{L}_a$
 be the isomorphism of vector spaces obtained by restriction of
-$\mu : m^*\gCSs{L} \to \gCSs{L} \boxtimes \gCSs{L}$ to the
+$\mu : m^*\gcs{L} \to \gcs{L} \boxtimes \gcs{L}$ to the
 geometric point $(g,a)$ on $\bG^x \times \bG^0$.
-Since $\CSs{L}\vert_{G^0} = (\EE)_{G^0}$,
-the stalk of $\gCSs{L}$ at $a$ is $\EE$.
+Since $\cs{L}\vert_{G^0} = (\EE)_{G^0}$,
+the stalk of $\gcs{L}$ at $a$ is $\EE$.
 In this way the pair of geometric points $g, g' \in \bG^x$
 determines an isomorphism $\varphi_{g,g'} \ceq \mu_{g,a}^{-1}$
-from $\gCSs{L}_{g}$ to $\gCSs{L}_{g'}$.
+from $\gcs{L}_{g}$ to $\gcs{L}_{g'}$.
 %
-The isomorphisms $\varphi_{g,g'}: \gCSs{L}_{g} \to \gCSs{L}_{g'}$ are canonical
+The isomorphisms $\varphi_{g,g'}: \gcs{L}_{g} \to \gcs{L}_{g'}$ are canonical
 in the following sense: if $g,g'\in \bG^x$ and $h,h'\in \bG^y$
@@
   \begin{tikzcd}[column sep=40]
-   \gCSs{L}_{gh} \arrow{r}{\varphi_{gh,g'h'}} \arrow[swap]{d}{\mu_{g,h}}
-  & \gCSs{L}_{g'h'} \arrow{d}{\mu_{g',h'}}
+   \gcs{L}_{gh} \arrow{r}{\varphi_{gh,g'h'}} \arrow[swap]{d}{\mu_{g,h}}
+  & \gcs{L}_{g'h'} \arrow{d}{\mu_{g',h'}}
   &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-  &  \gCSs{L}_{\Frob{}(g)} \arrow{r}{\varphi_{\Frob{}(g),\Frob{}(g')}} \arrow[swap]{d}{\phi_{g}} & \gCSs{L}_{\Frob{}(g')} \arrow{d}{\phi_{g'}} \\
-  \gCSs{L}_{g} \otimes \gCSs{L}_{h} \arrow{r}{\varphi_{g,g'}\otimes \varphi_{h,h'}}
-  & \gCSs{L}_{g'} \otimes \gCSs{L}_{h'}
+  &  \gcs{L}_{\Frob{}(g)} \arrow{r}{\varphi_{\Frob{}(g),\Frob{}(g')}} \arrow[swap]{d}{\phi_{g}} & \gcs{L}_{\Frob{}(g')} \arrow{d}{\phi_{g'}} \\
+  \gcs{L}_{g} \otimes \gcs{L}_{h} \arrow{r}{\varphi_{g,g'}\otimes \varphi_{h,h'}}
+  & \gcs{L}_{g'} \otimes \gcs{L}_{h'}
   & {}
-  & \gCSs{L}_{g} \arrow{r}{\varphi_{g,g'}} & \gCSs{L}_{g'}
+  & \gcs{L}_{g} \arrow{r}{\varphi_{g,g'}} & \gcs{L}_{g'}
   \end{tikzcd}
@@
 For each $x\in \pi_0(\bG)$, pick $g(x)\in \bG^x$
-and set $\gCSs{E}_x \ceq \gCSs{L}_{g(x)}$.
-Let $\phi_x : \gCSs{E}_{\Frob{}(x)} \to \gCSs{E}_x$
+and set $\gcs{E}_x \ceq \gcs{L}_{g(x)}$.
+Let $\phi_x : \gcs{E}_{\Frob{}(x)} \to \gcs{E}_x$
 be the isomorphism of $\EE$-vector spaces obtained by composing
-$\varphi_{g(\Frob{}(x)),\Frob{}(g(x))} : \gCSs{L}_{g(\Frob{}(x))} \to \gCSs{L}_{\Frob{}(g(x))}$
-with $\phi_{g(x)} : \gCSs{L}_{\Frob{}(g(x))} \to \gCSs{L}_{g(x)}$.
+$\varphi_{g(\Frob{}(x)),\Frob{}(g(x))} : \gcs{L}_{g(\Frob{}(x))} \to \gcs{L}_{\Frob{}(g(x))}$
+with $\phi_{g(x)} : \gcs{L}_{\Frob{}(g(x))} \to \gcs{L}_{g(x)}$.
 For each pair $x,y\in \pi_0(\bG)$
-let $\mu_{x,y} : \gCSs{E}_{x+y}\to \gCSs{E}_x\otimes \gCSs{E}_y$
+let $\mu_{x,y} : \gcs{E}_{x+y}\to \gcs{E}_x\otimes \gcs{E}_y$
 be the isomorphism of $\EE$-vector spaces obtained by composing
-$\varphi_{g(x+y),g(x)g(y)} : \gCSs{L}_{g(x+y)} \to \gCSs{L}_{g(x)g(y)}$
-with $\mu_{g(x),g(y)} : \gCSs{L}_{g(x)g(y)} \to \gCSs{L}_{g(x)}\otimes \gCSs{L}_{g(y)}$.
+$\varphi_{g(x+y),g(x)g(y)} : \gcs{L}_{g(x+y)} \to \gcs{L}_{g(x)g(y)}$
+with $\mu_{g(x),g(y)} : \gcs{L}_{g(x)g(y)} \to \gcs{L}_{g(x)}\otimes \gcs{L}_{g(y)}$.
 Using \eqref{eq:CS}, it follows that \ref{CS.1}, \ref{CS.2} and \ref{CS.3} are satisfied for
-$\CSs{E} \ceq (\gCSs{E}_x, \mu_{x,y}, \phi_x)$, thus defining a character sheaf on $\pi_0(G)$.
-
-The pullback $\pi_0^*(\CSs{E})$ of $\CSs{E}$ along $\pi_0 : G \to \pi_0(G)$ is constant
+$\cs{E} \ceq (\gcs{E}_x, \mu_{x,y}, \phi_x)$, thus defining a character sheaf on $\pi_0(G)$.
+
+The pullback $\pi_0^*(\cs{E})$ of $\cs{E}$ along $\pi_0 : G \to \pi_0(G)$ is constant
 on geometric connected components, with stalks given by
-$(\pi_0^* \CSs{E})_g = \CSs{E}_{x}$ for all $g\in \bG^x$.  Thus both $\pi_0^*\CSs{E}$ and $\CSs{L}$
+$(\pi_0^* \cs{E})_g = \cs{E}_{x}$ for all $g\in \bG^x$.  Thus both $\pi_0^*\cs{E}$ and $\cs{L}$
 are constant on geometric connected components of $G$.
 The choices above define isomorphisms
-$\gCSs{L}\vert_{\bG^x} \to  (\gCSs{E}_{x})_{\bG^x}$ for each $x\in \pi_0(\bG)$.
-The resulting isomorphism $\gCSs{L} \to \pi_0^* \gCSs{E}$ satisfies \ref{CS.4},
-thus defining an isomorphism $\CSs{L} \to \pi_0^* \CSs{E}$ in $\CS(G)$.
+$\gcs{L}\vert_{\bG^x} \to  (\gcs{E}_{x})_{\bG^x}$ for each $x\in \pi_0(\bG)$.
+The resulting isomorphism $\gcs{L} \to \pi_0^* \gcs{E}$ satisfies \ref{CS.4},
+thus defining an isomorphism $\cs{L} \to \pi_0^* \cs{E}$ in $\CS(G)$.
 \end{proof}
@@
 \[
-\Aut(\CSs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx).
+\Aut(\cs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx).
 \]
@@
 \begin{proof} 
-Fix $\CSs{L} = (\gCSs{L},\mu,\phi)$ and consider the group homomorphism from $\Aut(\CSs{L})$ to $\Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
+Fix $\cs{L} = (\gcs{L},\mu,\phi)$ and consider the group homomorphism from $\Aut(\cs{L})$ to $\Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
 This homomorphism is injective because morphisms of sheaves are determined by the linear transformations induced on stalks.  
-Homomorphisms in the image of $\Aut(\CSs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ are continuous when $\bG$ is viewed as the base of the espace \'etal\'e attached to $\gCSs{L}$.
-Since $\ell$ is invertible in $\Fq$, it follows that the image of $\Aut(\CSs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
+Homomorphisms in the image of $\Aut(\cs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ are continuous when $\bG$ is viewed as the base of the espace \'etal\'e attached to $\gcs{L}$.
+Since $\ell$ is invertible in $\Fq$, it follows that the image of $\Aut(\cs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
 We also have $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
-To see that $\Aut(\CSs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho^y: \gCSs{L}^y \to \gCSs{L}^y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
-This defines an isomorphism $\bar\rho : \gCSs{L}\to \gCSs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\CSs{L}\to \CSs{L}$ which maps to $\theta$ under $\Aut(\CSs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
+To see that $\Aut(\cs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho^y: \gcs{L}^y \to \gcs{L}^y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
+This defines an isomorphism $\bar\rho : \gcs{L}\to \gcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\cs{L}\to \cs{L}$ which maps to $\theta$ under $\Aut(\cs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
 \end{proof}
@@
 
-If $\CSs{L} \ceq (\gCSs{L}, \mu, \phi)$ is a character sheaf on $G$, we define
-$\CSs{L}' \ceq (\gCSs{L}, \mu, \phi_{k'})$ on the base change
+If $\cs{L} \ceq (\gcs{L}, \mu, \phi)$ is a character sheaf on $G$, we define
+$\cs{L}' \ceq (\gcs{L}, \mu, \phi_{k'})$ on the base change
 $G_{k'}$ of $G$ to $k'$ by setting
@@
 Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
-as restricting the action $\varphi$ of $\Weil{k}$ on $\gCSs{L}$,
+as restricting the action $\varphi$ of $\Weil{k}$ on $\gcs{L}$,
 defined in Section~\ref{ssec:category}, to $\Weil{k'}$.
@@
 With notation above,
-the rule $\nu_{k'/k}: (\gCSs{L}, \mu, \phi) \mapsto (\gCSs{L}, \mu, \phi_{k'})$
+the rule $\nu_{k'/k}: (\gcs{L}, \mu, \phi) \mapsto (\gcs{L}, \mu, \phi_{k'})$
  defines a monoidal functor $\CS(G) \to \CS(G_{k'})$
@@
 \begin{proof}
-Let $\CSs{L} \ceq (\gCSs{L}, \mu, \phi) \in \CS(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
-we may compute the value of $\TrFrob{G_{k'}}(\nu_{k'/k}\CSs{L})(x)= t_{\nu_{k'/k}\CSs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gCSs{L}_x$,
-and the value of $\Nm^*(\TrFrob{G}(\CSs{L}))(x)$ as the trace of $\phi$ on $\gCSs{L}_{\Nm(x)}$.
-Applying \ref{CS.3} to the stalk of $\gCSs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
+Let $\cs{L} \ceq (\gcs{L}, \mu, \phi) \in \CS(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
+we may compute the value of $\TrFrob{G_{k'}}(\nu_{k'/k}\cs{L})(x)= t_{\nu_{k'/k}\cs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gcs{L}_x$,
+and the value of $\Nm^*(\TrFrob{G}(\cs{L}))(x)$ as the trace of $\phi$ on $\gcs{L}_{\Nm(x)}$.
+Applying \ref{CS.3} to the stalk of $\gcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
 \[
 \begin{tikzcd}
-\gCSs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gCSs{L}_{F(x)} \otimes \gCSs{L}_{F^2(x)} \otimes \cdots \otimes \gCSs{L}_x
+\gcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gcs{L}_{F(x)} \otimes \gcs{L}_{F^2(x)} \otimes \cdots \otimes \gcs{L}_x
 \dar{\phi_x \otimes (F^*\phi)_x \otimes \cdots \otimes ((F^{n-1})^*\phi)_x} \\
-\gCSs{L}_{\Nm(x)} \rar & \gCSs{L}_x \otimes \gCSs{L}_{F(x)} \otimes \cdots \otimes \gCSs{L}_{F^{n-1}(x)}.
-\end{tikzcd}
-\]
-Choose a basis vector $v$ for $\gCSs{L}_{\Nm(x)}$ and write $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$ for the image of $v$ under the
+\gcs{L}_{\Nm(x)} \rar & \gcs{L}_x \otimes \gcs{L}_{F(x)} \otimes \cdots \otimes \gcs{L}_{F^{n-1}(x)}.
+\end{tikzcd}
+\]
+Choose a basis vector $v$ for $\gcs{L}_{\Nm(x)}$ and write $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$ for the image of $v$ under the
 bottom map,
-for $v_i \in \gCSs{L}_{\Frob{}^i(x)}$.  By \ref{CS.2}, $v$ maps to
+for $v_i \in \gcs{L}_{\Frob{}^i(x)}$.  By \ref{CS.2}, $v$ maps to
 $v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
 Let $\alpha_i \in \EEx$ represent $((F^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
-the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gCSs{L}_{\Nm(x)}$
-with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gCSs{L}_x$.
+the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gcs{L}_{\Nm(x)}$
+with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gcs{L}_x$.
 \end{proof}
@@
 \end{proof}
+
+\subsection{Examples here?}
 
@@
 \item
-objects in $\QCS(X_K)$ are the $\ell$-adic sheaves $\varrho^R_n(X)^*\CSs{L}$, for $n\in \NN$ and $\CSs{L} \in \CS(\Gr^R_n(X))$; 
+objects in $\QCS(X_K)$ are the $\ell$-adic sheaves $\varrho^R_n(X)^*\cs{L}$, for $n\in \NN$ and $\cs{L} \in \CS(\Gr^R_n(X))$; 
 \item
-morphisms $\varrho^R_n(X)^*\CSs{L} \to \varrho^R_m(X)^*\CSs{L}'$ in $\QCS(X_K)$ are those morphisms in $\CS(\Gr_R(X))$ which take the form $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\CSs{L},\CSs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\CSs{L},\varrho^R_{m\leq n}(X)^*\CSs{L}')$ when $m\leq n$.
+morphisms $\varrho^R_n(X)^*\cs{L} \to \varrho^R_m(X)^*\cs{L}'$ in $\QCS(X_K)$ are those morphisms in $\CS(\Gr_R(X))$ which take the form $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\cs{L},\cs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\cs{L},\varrho^R_{m\leq n}(X)^*\cs{L}')$ when $m\leq n$.
 \end{enumerate}
@@
 \[
-\CSs{F} \ceq (n, \{\CSs{F}_i\}_{n\leq i}, \{\alpha_{i \le j}\}_{n\le i \le j}),
+\cs{F} \ceq (n, \{\cs{F}_i\}_{n\leq i}, \{\alpha_{i \le j}\}_{n\le i \le j}),
 \] where $n$
-is a non-negative integer, each $\CSs{F}_i$ is a character sheaf on $\Gr^R_i(X)$ and each 
-\[
-\alpha_{i \le j} : \CSs{L}_j \to \varrho^R_{i \le j}(X)^* \CSs{L}_i
+is a non-negative integer, each $\cs{F}_i$ is a character sheaf on $\Gr^R_i(X)$ and each 
+\[
+\alpha_{i \le j} : \cs{L}_j \to \varrho^R_{i \le j}(X)^* \cs{L}_i
 \]
  is an isomorphism; here $\alpha_{i \le i}$ is the identity and the $\alpha_{i \le j}$ are compatible with each other.  
-If $\CSs{F} \ceq (n, \{\CSs{F}_i\}, \{\alpha_{i \le j}\})$
-and $\CSs{F}' \ceq (m, \{\CSs{F}'_i\}, \{\alpha'_{i \le j}\})$ are objects then $\Hom(\CSs{F}, \CSs{F}')$ is the set
-of equivalence classes of pairs $(k, \{\beta_i\}_{k \le i})$, where $n,m \le k$ and the $\beta_i : \CSs{F}_i \to \CSs{F}'_i$ are
+If $\cs{F} \ceq (n, \{\cs{F}_i\}, \{\alpha_{i \le j}\})$
+and $\cs{F}' \ceq (m, \{\cs{F}'_i\}, \{\alpha'_{i \le j}\})$ are objects then $\Hom(\cs{F}, \cs{F}')$ is the set
+of equivalence classes of pairs $(k, \{\beta_i\}_{k \le i})$, where $n,m \le k$ and the $\beta_i : \cs{F}_i \to \cs{F}'_i$ are
 morphisms of character sheaves so that
@@
 \begin{tikzcd}
-\CSs{F}_j \rar{\alpha_j} \dar{\beta_i} & \varrho^R_{i \le j}(X)^* \CSs{F}_i \dar{f_{i \le j}^*\beta_j} \\
-\CSs{F}'_j \rar{\alpha_j} & \varrho^R_{i \le j}(X)^* \CSs{L}'_i
+\cs{F}_j \rar{\alpha_j} \dar{\beta_i} & \varrho^R_{i \le j}(X)^* \cs{F}_i \dar{f_{i \le j}^*\beta_j} \\
+\cs{F}'_j \rar{\alpha_j} & \varrho^R_{i \le j}(X)^* \cs{L}'_i
 \end{tikzcd}
@@
 \] 
-\labitem{(3)}{x3} for all quasicharacter sheaves $\CSs{F}$, $\CSs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\CSs{F},\CSs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
-\labitem{(4)}{x4} for all quasicharacter sheaves $\CSs{F}$ for $X_K$, there is a canonical isomorphism
-\[
-\Aut(\CSs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx).
+\labitem{(3)}{x3} for all quasicharacter sheaves $\cs{F}$, $\cs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\cs{F},\cs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
+\labitem{(4)}{x4} for all quasicharacter sheaves $\cs{F}$ for $X_K$, there is a canonical isomorphism
+\[
+\Aut(\cs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx).
 \]
@@
 \]
-Also by Theorem~\ref{thm:CSXK} and \cite{bitan:discriminant}*{Eq 3.1}, the automorphism group of every $\CSs{F} \in \CS(T_K)$ is given by 
-\[
-\Aut(\CSs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx),
+Also by Theorem~\ref{thm:CSXK} and \cite{bitan:discriminant}*{Eq 3.1}, the automorphism group of every $\cs{F} \in \CS(T_K)$ is given by 
+\[
+\Aut(\cs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx),
 \]

### 2015-06-01 dictionary.tex
Minor modifications following our discussion on Sunday.

@@
 \begin{abstract}
-We introduce the category of quasicharacter sheaves on smooth commutative group schemes $G$ over finite fields $k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
-We show that the group of isomorphism classes of quasicharacter sheaves is an extension of the group of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
+We consider the category of character sheaves on smooth commutative group schemes $G$ over finite fields $k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
+We show that the group of isomorphism classes of character sheaves is an extension of the group of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
 As an application, we find a category of sheaves for which isomorphism classes correspond to quasi\-characters in the case of algebraic tori, abelian varieties and unipotent wound groups over local fields.
@@
 
+\tableofcontents
+
 \section*{Introduction}
 
-Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
-this paper extends Deligne's function-sheaf dictionary from connected commutative algebraic groups to smooth commutative group schemes over finite fields.
+This paper extends Deligne's function-sheaf dictionary from connected commutative algebraic groups to smooth commutative group schemes over finite fields and then provides an application to the geometrization and categorification of quasicharacters of $p$-adic tori.
 
@@
 {\it A priori}, the composition $\cs{E} \to \cs{E}' \to \cs{E}''$ of two such morphisms need not be compatible with the choices of \eqref{introbox} for $\cs{E}$ and $\cs{E}''$.
- However, for connected $G$ the isomorphism \eqref{introbox} is unique if it exists, and there is no impediment to making the dictionary categorical.
+ However, for connected $G$ the isomorphism \eqref{introbox} is unique, if it exists, and there is no impediment to making the dictionary categorical.
 
@@
 we simply replace the local system $\cs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\cs{E}$. 
-In this way we are led to the category $\CS(G)$ of {\it quasicharacter sheaves} on $G$ (\S\ref{ssec:category}).
-Objects in $\CS(G)$ are triples $(\gcs{L}, \mu,\phi)$, where $\gcs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\Fq}} \Spec{\bFq}$
-and $\phi : \Frob{G}^* \gcs{L}\to \gcs{L}$ and $\mu : {\bar m}^* \gcs{L} \iso \gcs{L} \boxtimes \gcs{L}$ are isomorphisms of sheaves satisfying certain compatibility conditions.
-Morphisms in $\CS(G)$ are then morphisms of Weil sheaves which are compatible with the extra structure.
-
-We first test the category of quasicharacter sheaves by examining its objects on \'etale commutative group schemes $G$ over $\Fq$ (\S\ref{sec:etale});
+In this way we are led to the category $\CS(G)$ of {\it character sheaves} on $G$ (\S\ref{ssec:category}):
+objects in $\CS(G)$ are triples $(\gcs{L}, \mu,\phi)$, where $\gcs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\Fq}} \Spec{\bFq}$
+and $\phi : \Frob{G}^* \gcs{L}\to \gcs{L}$ and $\mu : {\bar m}^* \gcs{L} \iso \gcs{L} \boxtimes \gcs{L}$ are isomorphisms of sheaves satisfying certain compatibility conditions;
+morphisms in $\CS(G)$ are then morphisms of Weil sheaves which are compatible with the extra structure.
+
+We begin the paper by returning to the case of connected commutative algebraic groups $G$ and thus revisiting Deligne's function-sheaf dictionary.
+We consider character sheaves that arise via base change to $\bFq$ from local systems on $G$ (\S\ref{ssec:descentG}) and
+those that appear in a pushforward from a constant sheaf along a discrete isogeny $H \to G$ (\S\ref{ssec:discrete_isogenies}).  
+While these constructions make sense even for non-connected $G$, in the connected case we show that every character sheaf can be described in both of these ways (\S\ref{ssec:connected}).  
+We use this fact to prove that $\TrFrob{G}$ is an isomorphism for connected commutative algebraic groups $G$
+and to determine the automorphism groups of character sheaves on such $G$. 
+These results are all well know.
+
+Next, we consider character sheaves on \'etale commutative group schemes $G$ over $\Fq$ (\S\ref{sec:etale});
 \'etale group schemes form a counterpoint to connected algebraic groups, since the component group of any smooth group scheme is an \'etale group scheme.
-Our key tools for understanding the trace of Frobenius in the \'etale case are a reinterpretation of $\CS(G)$ in terms of stalks (\S\ref{ssec:stalks}) and a
-relationship with the Hochschild-Serre spectral sequence (\S\ref{ssec:E}) for $\Weil{} \ltimes \bG$, where $\Weil{} \subset \Gal(\Fq/\Fq)$ is the Weil group for $\Fq$.
+Our key tool for understanding the trace of Frobenius in the \'etale case 
+%are a reinterpretation of $\CS(G)$ in terms of stalks (\S\ref{ssec:stalks}) and 
+is a relationship with the Hochschild-Serre spectral sequence (\S\ref{ssec:E}) for $\Weil{} \ltimes \bG$, where $\Weil{} \subset \Gal(\Fq/\Fq)$ is the Weil group for $\Fq$.
 We define (\S\ref{ssec:S}) an isomorphism $S_G$ from $\CSiso{G}$ to the second cohomology of the total space of the spectral sequence
@@
 %The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gcs{L}, \mu,\phi)$ and $(\gcs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gcs{L},\phi)$ and $(\gcs{L}',\phi')$ are isomorphic as Weil sheaves.
-
-Returning to the case of connected commutative algebraic groups $G$, we consider quasicharacter sheaves that arise via base change to $\bFq$ from local systems on $G$ (\S\ref{ssec:descentG}) and
-those that appear in a pushforward from a constant sheaf along a discrete isogeny $H \to G$ (\S\ref{ssec:discrete_isogenies}).
-While these constructions make sense even for non-connected $G$, in the connected
-case we show that every character sheaf can be described in both of these ways (\S\ref{ssec:connected}).
-We use this fact to prove that $\TrFrob{G}$ is an isomorphism for connected commutative algebraic groups $G$
-and to determine the automorphism groups of quasicharacter sheaves on such $G$.
 
@@
 \]
-is surjective with kernel $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
+is surjective with kernel $\Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx))$.
 \end{theorem*}
+\noindent
+It follows that, unless the etale group scheme $\pi_0(\bG)$ is cyclic, the category $\CS(G)$ contains non-trivial character sheaves lying in the kernel of the trace of Frobenius and therefore lost in translation to characters of $G(\Fq)$ and, moreover, that these {\it invisible character sheaves} are parametrized by $\Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx))$.
+
 We also illuminate the nature of the category $\CS(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing
@@
 \[
-\Aut_{\CS{}}(\cs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx),
+\Aut_{\CS{}}(\cs{L}) \iso  \Hh^0(\Weil{},\Hh^1(\pi_0(\bG), \EEx)),
 \]
@@
 This class of groups includes abelian varieties and unipotent $K$-wound groups in addition to the tori we initially considered.
+
 In this paper we show that quasicharacters of $X(K)$ are geometrized and categorified by quasicharacter sheaves on the
@@
 
-\tableofcontents
-
 \section{Recollections on character sheaves} \label{sec:category}
@@
 Throughout this paper, $G$ is a smooth commutative group scheme
-over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.
+over a finite field $\Fq$ and $m : \GxG\to G$ is its multiplication morphism.
+Thus, the structure morphism $G \to \Spec{\Fq}$ is locally of finite type.
+If the structure morphism $G \to \Spec{\Fq}$ is \'etale, then $G$ is an etale group scheme. 
+If the structure morphism $G \to \Spec{\Fq}$ is of finite type, then $G$ is an algebraic group.
+We will make use of the short exact sequence of smooth group schemes defining the component group scheme for $G$:
+\[
+\begin{tikzcd}
+0 \rar & G^0 \arrow{r}{\iota_0} & G \arrow{r}{\pi_0} & \pi_0(G) \rar & 0.
+\end{tikzcd}
+\]
+Then $G^0$ is a connected algebraic group and $\pi_0(G)$ is an \'etale commutative group scheme.
+We remark that the smooth group scheme $G$ is an algebraic group if and only if the etale group scheme $\pi_0(G)$ is finite.
 
@@
 
+\subsection{Examples}
+
 \section{Character sheaves on \'etale commutative group schemes} \label{sec:etale}
@@
 \end{proof}
+
+\subsection{Examples}
 
@@
 
-\subsection{Examples here?}
+\subsection{Examples}
 
@@
 
-\subsection{character sheaves on the Greenberg transform of a N\'eron model} \label{ssec:CS_on_GN}
+\subsection{Character sheaves on the Greenberg transform of a N\'eron model} \label{ssec:CS_on_GN}
 
@@
 it follows that the automorphism group of every quasicharacter sheaf for $T_K$ is $(\check{T}_\ell)^{\Weil{K}}$, where $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
-
-\subsection{Examples of quasicharacter sheaves for $p$-adic tori}
-
-Here we consider some examples that illustrate some of the essential features of the category of quasicharacter sheaves for $p$-adic tori. In this section, $K$ is a finite extension of $\QQ_p$.
-
-First, suppose $T = \GL(1)_{/K}$,
 
@@
 
+\subsection{Examples}
+
 \bibliography{bibliography/Biblio}

### 2015-06-01 dictionary.tex
Now the conflicts in my office are really resolved.

@@
 We show that the group of isomorphism classes of character sheaves is an extension of the group of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
-As an application, we find a category of sheaves for which isomorphism classes correspond to quasi\-characters in the case of algebraic tori, abelian varieties and unipotent wound groups over local fields.
+As an application, we find a category of sheaves for which isomorphism classes correspond to quasi\-characters of algebraic tori, abelian varieties and unipotent wound groups over non-Archimedean local fields.
 In this geometrization of quasicharacters, our sheaves are local systems on
@@
 
-This paper extends Deligne's function-sheaf dictionary from connected commutative algebraic groups to smooth commutative group schemes over finite fields and then provides an application to the geometrization and categorification of quasicharacters of $p$-adic tori.
+%This paper extends Deligne's function-sheaf dictionary from connected commutative algebraic groups to smooth commutative group schemes over finite fields and then provides an application to the geometrization and categorification of quasicharacters of algebraic tori, abelian varieties and unipotent wound groups over non-Archimedean local fields.
 
@@
 
-We begin the paper by returning to the case of connected commutative algebraic groups $G$ and thus revisiting Deligne's function-sheaf dictionary.
+We begin the paper by returning to the case of connected commutative algebraic groups $G$ and thus revisiting Deligne's function-sheaf dictionary (\S\ref{sec:category}).
 We consider character sheaves that arise via base change to $\bFq$ from local systems on $G$ (\S\ref{ssec:descentG}) and
@@
 
-Next, we consider character sheaves on \'etale commutative group schemes $G$ over $\Fq$ (\S\ref{sec:etale});
-\'etale group schemes form a counterpoint to connected algebraic groups, since the component group of any smooth group scheme is an \'etale group scheme.
+Next, we consider character sheaves on \'etale commutative group schemes $G$ over $\Fq$ (\S\ref{sec:etale}).
+\'Etale group schemes form a counterpoint to connected algebraic groups, since the component group of any smooth group scheme is an \'etale group scheme.
 Our key tool for understanding the trace of Frobenius in the \'etale case 
@@
 
-Having understood quasicharacter sheaves on commutative smooth group schemes over $\Fq$ in two extreme cases --
-connected commutative algebraic groups and \'etale commutative group schemes -- we turn to the general case, using the component group sequence
+Having understood character sheaves on commutative smooth group schemes over $\Fq$ in two extreme cases --
+connected commutative algebraic groups and \'etale commutative group schemes -- we turn to the general case  (\S\ref{sec:main}), using the component group sequence
 \[
@@
 \]
-Using pullbacks of quasicharacter sheaves (\S\ref{ssec:Frob}), we obtain a diagram
+Using pullbacks of character sheaves we obtain a diagram
 \[
@@
 Throughout this paper, $G$ is a smooth commutative group scheme
-over a finite field $\Fq$ and $m : \GxG\to G$ is its multiplication morphism.
+over a finite field $\Fq$ and $m : G \times G\to G$ is its multiplication morphism.
 Thus, the structure morphism $G \to \Spec{\Fq}$ is locally of finite type.
@@
   \begin{tikzcd}
-  A \arrow[equal]{r} \dar & A \dar \\
+  A \arrow{r} \dar & A \dar \\
   B \rar \dar[swap]{\pi} & H \rar \dar[swap]{f} & \pi_0(H) \arrow{d}[below,rotate=90]{\sim}[swap]{\pi_0(f)} \\

### 2015-06-01 dictionary.tex
Minor changes as discussed in the math lounge

@@
 \]
-is surjective with kernel $\Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx))$.
+is surjective with kernel $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
 \end{theorem*}
 \noindent
-It follows that, unless the etale group scheme $\pi_0(\bG)$ is cyclic, the category $\CS(G)$ contains non-trivial character sheaves lying in the kernel of the trace of Frobenius and therefore lost in translation to characters of $G(\Fq)$ and, moreover, that these {\it invisible character sheaves} are parametrized by $\Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx))$.
+It follows that, unless the etale group scheme $\pi_0(\bG)$ is cyclic, the category $\CS(G)$ contains non-trivial character sheaves lying in the kernel of the trace of Frobenius and therefore lost in translation to characters of $G(\Fq)$ and, moreover, that these {\it invisible character sheaves} are parametrized by $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
 
@@
 \[
-\Aut_{\CS{}}(\cs{L}) \iso  \Hh^0(\Weil{},\Hh^1(\pi_0(\bG), \EEx)),
+\Aut_{\CS{}}(\cs{L}) \iso  \Hh^1(\pi_0(\bG), \EEx)^{\Weil{}}
 \]
@@
 in which case it is not difficult to relate Frobenius-stable character sheaves to our character sheaves.
-The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in that context.
+%The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in that context.
 
@@
 
+If $G_1$ and $G_2$ are smooth commutative group schemes over $\Fq$ then characters of $(G_1 \times G_2)(\Fq)$ all take the form $\chi_1\otimes \chi_2$ for characters $\chi_1$ of $G_1(\Fq)$ and $\chi_2$ of $G_2(\Fq)$.
+The next lemma shows that character sheaves on $G$ enjoy an analogous property.
+
 \begin{lemma}\label{lem:product}
@@
 \end{definition}
+
+Note that category $\bCS(G)$
 

### 2015-06-02 dictionary.tex
Typo: Well known.
Introduction; extensions; Kunneth

@@
 If $G$ is a commutative algebraic group over $\Fq$ which is not connected, then the isomorphism \eqref{introbox} need not be unique.
-In order to track the choice of isomorphism, consider the category of pairs $(\cs{E},\mu_\cs{E})$ where $\cs{E}$ is a rank-one local system on $G$ and $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ is a chosen isomorphism of local systems on $G\times G$.
-In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of pairs $(\cs{E},\mu_\cs{E})$ to characters of $G(\Fq)$, but the epimomorphism need not be injective; consequently,
-every character of $G(\Fq)$ may be geometrized as a pair $(\cs{E},\mu_\cs{E})$ but perhaps not uniquely in the category of pairs. 
-While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious: if $(\cs{E},\mu_\cs{E})$ and $(\cs{E}',\mu_\cs{E}')$ determine the same character of $G(\Fq)$ then $\cs{E}\iso \cs{E}'$ as local systems on $G$.
+In order to track the choice of isomorphism, consider the category $\bCS(G)$ of pairs $(\cs{E},\mu_\cs{E})$ where $\cs{E}$ is a rank-one local system on $G$ and $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ is a chosen isomorphism of local systems on $G\times G$.
+In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of objects in $\bCS(G)$ to characters of $G(\Fq)$, but the epimomorphism need not be injective; consequently,
+every character of $G(\Fq)$ may be geometrized as a pair $(\cs{E},\mu_\cs{E})$ but perhaps not uniquely.
+Indeed, it follows from a special case of the main result of this paper that the kernel of the trace of Frobenius $T_{G} : \bCS(G) \to G(\Fq)^*$ trivial if and only if the \'etale group scheme of connected components of $G$ is finite cyclic.
+In general, the defect in the dictionary for characters of commutative algebraic groups over finite fields may be addressed with the following observation: if $(\cs{E},\mu_\cs{E})$ and $(\cs{E}',\mu_\cs{E}')$ determine the same character of $G(\Fq)$ then $\cs{E}\iso \cs{E}'$ as local systems on $G$.
 
 In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\Fq$,
-we simply replace the local system $\cs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\cs{E}$. 
+we replace the local system $\cs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\cs{E}$. 
 In this way we are led to the category $\CS(G)$ of {\it character sheaves} on $G$ (\S\ref{ssec:category}):
@@
 
-We begin the paper by returning to the case of connected commutative algebraic groups $G$ and thus revisiting Deligne's function-sheaf dictionary (\S\ref{sec:category}).
+We begin a study of the category $\CS(G)$ of character sheaves on $G$ by returning to the case when $G$ is a connected commutative algebraic group over $\Fq$ and thus by revisiting Deligne's function-sheaf dictionary (\S\ref{sec:category}).
 We consider character sheaves that arise via base change to $\bFq$ from local systems on $G$ (\S\ref{ssec:descentG}) and
@@
 and to determine the automorphism groups of character sheaves on such $G$. 
-These results are all well know.
+These results are all well known.
 
 Next, we consider character sheaves on \'etale commutative group schemes $G$ over $\Fq$ (\S\ref{sec:etale}).
-\'Etale group schemes form a counterpoint to connected algebraic groups, since the component group of any smooth group scheme is an \'etale group scheme.
+\'Etale group schemes form a counterpoint to connected algebraic groups, since the component group of any smooth group scheme is an \'etale group scheme;
+etale group schemes are algebraic groups only when they are finite.
 Our key tool for understanding the trace of Frobenius in the \'etale case 
-%are a reinterpretation of $\CS(G)$ in terms of stalks (\S\ref{ssec:stalks}) and 
-is a relationship with the Hochschild-Serre spectral sequence (\S\ref{ssec:E}) for $\Weil{} \ltimes \bG$, where $\Weil{} \subset \Gal(\Fq/\Fq)$ is the Weil group for $\Fq$.
+are a reinterpretation of $\CS(G)$ in terms of stalks (\S\ref{ssec:stalks}) and 
+a relationship with the Hochschild-Serre spectral sequence (\S\ref{ssec:E}) for $\Weil{} \ltimes \bG$, where $\Weil{} \subset \Gal(\Fq/\Fq)$ is the Weil group for $\Fq$.
 We define (\S\ref{ssec:S}) an isomorphism $S_G$ from $\CSiso{G}$ to the second cohomology of the total space of the spectral sequence
@@
 provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$.
-One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
+One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is finite cyclic.
 %The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gcs{L}, \mu,\phi)$ and $(\gcs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gcs{L},\phi)$ and $(\gcs{L}',\phi')$ are isomorphic as Weil sheaves.
@@
 over a finite field $\Fq$ and $m : G \times G\to G$ is its multiplication morphism.
-Thus, the structure morphism $G \to \Spec{\Fq}$ is locally of finite type.
-If the structure morphism $G \to \Spec{\Fq}$ is \'etale, then $G$ is an etale group scheme. 
-If the structure morphism $G \to \Spec{\Fq}$ is of finite type, then $G$ is an algebraic group.
+It follows from the smoothness of $G$ that the structure morphism $G \to \Spec{\Fq}$ is locally of finite type.
 We will make use of the short exact sequence of smooth group schemes defining the component group scheme for $G$:
@@
 Then $G^0$ is a connected algebraic group and $\pi_0(G)$ is an \'etale commutative group scheme.
-We remark that the smooth group scheme $G$ is an algebraic group if and only if the etale group scheme $\pi_0(G)$ is finite.
+Unless noted otherwise, we place absolutely no conditions on the \'etale group scheme $\pi_0(G)$, though it is finitely generated as a group scheme.
+If the structure morphism $G \to \Spec{\Fq}$ is \'etale, then $G$ is an etale group scheme; this does not imply that $\pi_0(G)$ is finite.
+If the structure morphism $G \to \Spec{\Fq}$ is of finite type, then $G$ is an algebraic group; in this case, $\pi_0(G)$ is finite. 
+Indeed, a smooth commutative group scheme $G$ is an algebraic group if and only if the etale group scheme $\pi_0(G)$ is finite.
 
@@
 \begin{remark}
-The category of character sheaves on $G$ is not abelian since it is not closed under direct sums and thus $\CS(G)$
-is not a tensor category in the sense of \cite{deligne:02a}*{0.1}.  We suspect that requiring that $\mu$ be injective rather than
+The category of character sheaves on $G$ is not abelian since it is not closed under direct sums; 
+thus $\CS(G)$ is not a tensor category in the sense of \cite{deligne:02a}*{0.1}.  
+We suspect that requiring that $\mu$ be injective rather than
 an isomorphism and dropping the condition that the stalks be one-dimensional would yield an abelian category.
@@
 %
-In the meantime, we close this section with an elementary observation about $\Hom(\cs{L},\cs{L}')$.
+In the meantime, we close this subsection with an elementary observation about $\Hom(\cs{L},\cs{L}')$.
 We call a morphism of sheaves \emph{trivial} if it is zero on every stalk.
@@
 \end{definition}
-
-Note that category $\bCS(G)$
 
@@
 We have also just seen that if the character of $\Lang^*\cs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\cs{E} : \cs{E} \to \cs{E}\boxtimes\cs{E}$.
-This fact leads to a perspective on the function-sheaf dictionary common in the literature in which one considers one-dimensional local systems $\cs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\cs{E} \iso \cs{E} \boxtimes\cs{E}$ \cite{kamgarpour:09a}*{Intro}.
+This fact leads (back) to a perspective on the function-sheaf dictionary common in the literature in which one considers one-dimensional local systems $\cs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\cs{E} \iso \cs{E} \boxtimes\cs{E}$ \cite{kamgarpour:09a}*{Intro}.
 As a slight variation, one may also consider one-dimensional local systems $\gcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gcs{L} \iso \gcs{L}$ and an isomorphism $\bm^*\gcs{L} \iso \gcs{L} \boxtimes\gcs{L}$.
 
-Although the category of character sheaves on $G$ specializes to the one described above when $G$ is connected and of finite type, this description is not sufficient when extending the dictionary to smooth commutative group schemes.
+Although the category $\CS(G)$ of character sheaves on $G$ specializes to $\bCS(G)$ when $G$ is connected and of finite type, this description is \emph{not} sufficient when extending the dictionary to smooth commutative group schemes, as we will see already in Section~\ref{sec:etale}.
 In particular, for a given $\gcs{L}$ and $\phi$ there may be many $\mu$ so that $(\gcs{L},\mu,\phi)$ is a character sheaf.
@@
 \begin{remark}
-Although we will only use the group homomorphism $S_G : \CSiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an \'etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$.
-However, the next result is false in that context.
+Although we will only use the group homomorphism $S_G : \CSiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an \'etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$;
+however, the next result does not extend to all smooth commutative group schemes.
 \end{remark}
@@
 \end{proof}
+
+Think about this: It follows from Proposition~\ref{prop:etale-iso} that, when $G$ is an \'etale commutative group scheme, a character sheaf $\cs{L} \in \CS(G)$ descends to $G$ if and only if it lies in the kernel of the trace of Frobenius.
+This is in stark contrast to the case of connected commutative algebraic groups over $\Fq$, when all character sheaves $\cs{L} \in \CS(G)$ descend to $G$ and the kernel of the trace of Frobenius is trivial.
 
@@
 
+\subsection{The dictionary for commutative algebraic groups over finite fields}
+
 \subsection{Examples}
@@
 \qquad\text{and}\qquad
-F_{\text{QCS}}: X_K \mapsto \Hom_{\text{QC}}(X(K),\EEx)
+F_{\text{QC}}: X_K \mapsto \Hom_{\text{QC}}(X(K),\EEx)
 \]

### 2015-06-03 dictionary.tex
Notations
Removed false statement about CS0. Correction under construction.

@@
 Then $G^0$ is a connected algebraic group and $\pi_0(G)$ is an \'etale commutative group scheme.
-Unless noted otherwise, we place absolutely no conditions on the \'etale group scheme $\pi_0(G)$, though it is finitely generated as a group scheme.
+Unless noted otherwise, we place absolutely no conditions on the \'etale group scheme $\pi_0(G)$.
 If the structure morphism $G \to \Spec{\Fq}$ is \'etale, then $G$ is an etale group scheme; this does not imply that $\pi_0(G)$ is finite.
@@
 
-Think about this: It follows from Proposition~\ref{prop:etale-iso} that, when $G$ is an \'etale commutative group scheme, a character sheaf $\cs{L} \in \CS(G)$ descends to $G$ if and only if it lies in the kernel of the trace of Frobenius.
-This is in stark contrast to the case of connected commutative algebraic groups over $\Fq$, when all character sheaves $\cs{L} \in \CS(G)$ descend to $G$ and the kernel of the trace of Frobenius is trivial.
+The image of
 

### 2015-06-04 dictionary.tex
Added some justification for Weil sheaves. Still under construction, though.

@@
 
+Let $G$ be the etale group scheme $\ZZ$ over $\Fq$ and consider the character $\chi : \ZZ \to \EEx$ of $G(\Fq)$ determined by $\chi(1) = 1+\ell$.
+The stalk of $\cs{L}$ at the component $1$ is defined
+by a pro-\'etale cover  . . .
+
 \section{The function-sheaf dictionary for smooth commutative group schemes}\label{sec:main}
@@
 
-\subsection{Morphisms of characters} \label{ssec:CSmor}
+\subsection{On the necessity of working with Weil sheaves}
+
+\begin{corollary} \label{cor:bounded}
+Let $G$ be a smooth commutative group scheme over $\Fq$. 
+Then $\cs{L}\in \CS(G)$ descends to $G$ if and only if $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ has bounded image.
+\end{corollary}
+\begin{proof} 
+By Lemma~\ref{lem:G0alg-grp}, the identity component $G^0$ is a connected algebraic group over $\Fq$. 
+It follows from Proposition~\ref{prop:connected} that the restriction of $\cs{L}$ to $G^0$ descends to $G$. 
+Also, since $G^0(\Fq)$ is finite, the image of $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ is a finite subgroup and therefore bounded image.  
+%
+If $\chi \in G(\Fq)^*$ then there is some finite-image character $\chi_0$
+with the same restriction to $G^0(\Fq)$ since $G^0(\Fq)$ is lies inside the torsion part of
+the finitely generated abelian group $G(\Fq)$.  Therefore $\chi$ is bounded 
+if and only if $\chi \cdot \chi_0^{-1}$ is bounded.  But $\chi \cdot \chi_0^{-1}$ descends
+to a character of $\pi_0(G)$.
+Thus, it is enough to prove Corollary~\ref{cor:bounded}
+for \'etale group schemes $G$.
+
+Now suppose $G$ is an etale group scheme over $\Fq$.
+Let $\cs{L}$ be a character sheaf on $G$.
+$[\alpha \oplus \beta \oplus 0]\in H^2(E)$.
+ $b : \bG \to \EEx$ be a function
+
+  By \cite{beilinson-bernstein-deligne:81a}*{Rem. 5.2.1},
+$\cs{L}$ descends to $G$ if and only if $b(x) \in \EEx$ is bounded, for all $x$.
+
+ . . . 
+\end{proof}
+
+Corollary~\ref{cor:bounded} shows that the full subcategory
+$\bCS(G) \subset \CS(G)$ is not an equivalence, for smooth commutative group schemes $G$.
+This simple observation reveals the necessity of working with Weil sheaves in Definition~\ref{def:CS}: one cannot geometrize all characters of $G(\Fq)$ using local systems on $G$, for general smooth commutative groups schemes $G$.
+For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$.
+If $\chi : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi(1) = \ell$
+and if $\cs{L}$ is a character sheaf on $G$ in the isomorphism class
+corresponding to $\chi$ under Theorem~\ref{thm:main},
+then $\cs{L}$ does not descend to $G$ since the image of $\chi$ is not
+bounded.
+
+\subsection{Morphisms of character sheaves} \label{ssec:CSmor}
 

### 2015-06-04 dictionary.tex
Fixed reference to BBD; added section on descent in the etale case.

@@
  The resulting functor from local systems on $G$ to Weil local systems on $\bG$, given on objects by $\cs{E} \mapsto (\gcs{L},\phi)$, 
- is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} and \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}.
+ is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} and \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.1.2}.
  The isomorphism $\mu \ceq b_{G\times G}^*\mu_\cs{E}$ satisfies \ref{CS.2}
@@
   Since $b_{G\times G}^*$ is full and faithful (again, see
-\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} or \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}),
+\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} or \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.1.2}),
  \[
@@
 
+\subsection{Descent, revisited}
+
+\begin{corollary}\label{cor:bounded-etale}
+Let $G$ be a commutative etale group scheme over $\Fq$.
+Then the image of $\bCS(G)$ under $\TrFrob{G} : \CS(G) \to G(\Fq)^*$ is $\Hom(\bG,\mathbb{\bar Z}_{\ell}^\times)$.
+\end{corollary}
+
+\begin{proof}
+Let $\cs{L}$ be a character sheaf on $G$.
+Using Proposition~\ref{prop:SGiso}, let $[\alpha \oplus \beta \oplus 0]\in \Hh^2(E^\bullet_G)$ be the corresponding class and let  $a : \bG \times \bG \to \EEx$ and $b : \bG \to \EEx$ be multiplicative versions of $\alpha$ and $\beta$, following the notation at the beginning of this section.
+Then $\trFrob{\cs{L}}(x) = b(x)$ for $x\in G(\Fq)$.
+The identity component $G^0$ of $G$ may be identified with $\Spec{\Fq}$, 
+By \cite{beilinson-bernstein-deligne:81a}*{Rem. 5.1.2},
+$\cs{L}$ descends to $G$ if and only if $b(x) \in \EEx$ is bounded, for all $x$.
+
+ . . .
+
+\end{proof}
+
 \subsection{Objects in the \'etale case}\label{ssec:SandT}
@@
 
-The image of
-
 \subsection{Morphisms in the \'etale case}\label{ssec:mor-etale}
@@
   correspond to classes in $\Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq))$.
-  Similarly, extensions of $G(\bFq)$ by $A(\bFq)$ correspond to
+  Similarly, extensions of $G(\bFq)$ by $A(\bFq)$ with $\Weil{}$-equivariant maps correspond to
   classes in $\Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq))$.  The map
@@
 
-\begin{corollary} \label{cor:bounded}
+\begin{proposition} \label{prop:bounded}
 Let $G$ be a smooth commutative group scheme over $\Fq$. 
 Then $\cs{L}\in \CS(G)$ descends to $G$ if and only if $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ has bounded image.
-\end{corollary}
+\end{proposition}
 \begin{proof} 
@@
 to a character of $\pi_0(G)$.
-Thus, it is enough to prove Corollary~\ref{cor:bounded}
-for \'etale group schemes $G$.
-
-Now suppose $G$ is an etale group scheme over $\Fq$.
-Let $\cs{L}$ be a character sheaf on $G$.
-$[\alpha \oplus \beta \oplus 0]\in H^2(E)$.
- $b : \bG \to \EEx$ be a function
-
-  By \cite{beilinson-bernstein-deligne:81a}*{Rem. 5.2.1},
-$\cs{L}$ descends to $G$ if and only if $b(x) \in \EEx$ is bounded, for all $x$.
-
- . . . 
-\end{proof}
-
-Corollary~\ref{cor:bounded} shows that the full subcategory
+Thus, it is enough to prove Corollary~\ref{prop:bounded}
+for \'etale group schemes $G$, which is done in Corollary~\ref{cor:bounded-etale}.
+\end{proof}
+
+Proposition~\ref{prop:bounded} shows that the full subcategory
 $\bCS(G) \subset \CS(G)$ is not an equivalence, for smooth commutative group schemes $G$.

### 2015-06-05 dictionary.tex
Minor improvements.

@@
 in which case it is not difficult to relate Frobenius-stable character sheaves to our character sheaves.
-%The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in that context.
+The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in that context.
 
@@
 Then $\trFrob{\cs{L}}(x) = b(x)$ for $x\in G(\Fq)$.
+To prove the corollary we will show that $\cs{L}$ descends to $G$ if and only if $b(x)\in \mathbb{\bar Z}_{\ell}^\times$ for every $x\in G(\Fq)$.
+
 The identity component $G^0$ of $G$ may be identified with $\Spec{\Fq}$, 
@@
 This simple observation reveals the necessity of working with Weil sheaves in Definition~\ref{def:CS}: one cannot geometrize all characters of $G(\Fq)$ using local systems on $G$, for general smooth commutative groups schemes $G$.
+
 For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$.
@@
 and if $\cs{L}$ is a character sheaf on $G$ in the isomorphism class
-corresponding to $\chi$ under Theorem~\ref{thm:main},
+corresponding to $\chi$ under Theorem~\ref{thm:snake},
 then $\cs{L}$ does not descend to $G$ since the image of $\chi$ is not

### 2015-06-05 dictionary.tex
Update book BibSpec

--- 2015-06-04 dictionary.tex
@@
 
-\keywords{function-sheaf dictionary, trace of Frobenius, geometrization, categorification, character sheaves,smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor, quasicharacters, quasicharacter sheaves.}
+\keywords{function-sheaf dictionary, trace of Frobenius, geometrization, categorification, quasicharacter sheaves, smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor, quasicharacters}
 
@@
   +{.}{ }						{transition}
+}
+
+% We make volume bold rather than vol. #
+\BibSpec{book}{%
+    +{}  {\PrintPrimary}				{transition}
+    +{,} { }							{title}
+    +{.} { }							{part}
+    +{:} { }							{subtitle}
+    +{,} { \PrintEdition}					{edition}
+    +{}  { \PrintEditorsB}				{editor}
+    +{,} { \PrintTranslatorsC}			{translator}
+    +{,} { \PrintContributions}			{contribution}
+    +{,} { }							{series}
+    +{} { \textbf}						{volume}
+    +{,} { }							{publisher}
+    +{,} { } 							{organization}
+    +{,} { }							{address}
+    +{,} { \PrintDateB}					{date}
+    +{,} { }							{status}
+    +{}  { \parenthesize}				{language}
+    +{}  { \PrintTranslation}				{translation}
+    +{;} { \PrintReprint}				{reprint}
+    +{.} { }							{note}
+    +{.} {}							{transition}
+    +{}  {\SentenceSpace \PrintReviews}	{review}
 }
@@
 \newcommand{\Gm}[1]{\mathbb{G}_{\hskip-1pt\textbf{m},#1}}
-\DeclareMathOperator{\GL}{GL}
 \newcommand{\comp}{\Pi} % Component group
@@
 %% Fonts for quasicharacter sheaves
-\newcommand{\cs}[1]{{\mathcal{#1}}}
-\newcommand{\gcs}[1]{{\mathcal{\bar #1}}}
-\newcommand{\dualgcs}[1]{\gcs{#1}^\dagger}
-\newcommand{\dualcs}[1]{\cs{#1}^\dagger}
+\newcommand{\qcs}[1]{{\mathcal{#1}}}
+\newcommand{\gqcs}[1]{{\mathcal{\bar #1}}}
+\newcommand{\dualgcs}[1]{\gqcs{#1}^\dagger}
+\newcommand{\dualcs}[1]{\qcs{#1}^\dagger}
 %% Categories
-\newcommand{\CS}{{\mathcal{C\hskip-0.8pt S}}}
-\newcommand{\lCS}{{\CS_\text{flb}}}
-\newcommand{\lCSiso}[1]{\lCS(#1)_{/\text{iso}}}
-\newcommand{\bCS}{{\CS_0}}
-\newcommand{\CSiso}[1]{\CS(#1)_{/\text{iso}}}
-\newcommand{\bCSiso}[1]{\bCS(#1)_{/\text{iso}}}
+\newcommand{\QC}{{\mathcal{Q\hskip-0.8pt C}}}
+\newcommand{\lQC}{{\QC_\text{flb}}}
+\newcommand{\lQCiso}[1]{\lQC(#1)_{/\text{iso}}}
+\newcommand{\bQC}{{\QC_0}}
+\newcommand{\QCiso}[1]{\QC(#1)_{/\text{iso}}}
+\newcommand{\bQCiso}[1]{\bQC(#1)_{/\text{iso}}}
 \newcommand{\catname}[1]{\normalfont{\textsf{#1}}}
 \newcommand{\Sch}[1]{{\catname{Sch}_{/#1}}}
-\newcommand{\QCS}{{\mathcal{QC\hskip-0.8pt S}}}
-\newcommand{\QCSiso}[1]{\QCS(#1)_{/\text{iso}}}
 %% Labeled items
@@
 \begin{abstract}
-We consider the category of character sheaves on smooth commutative group schemes $G$ over finite fields $k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
-We show that the group of isomorphism classes of character sheaves is an extension of the group of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
-As an application, we find a category of sheaves for which isomorphism classes correspond to quasi\-characters of algebraic tori, abelian varieties and unipotent wound groups over non-Archimedean local fields.
+We introduce the category of quasicharacter sheaves on smooth commutative group schemes $G$ over finite fields $k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
+We show that the group of isomorphism classes of quasicharacter sheaves is an extension of the group of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
+As an application, we find a category of sheaves for which isomorphism classes correspond to quasi\-characters in the case of algebraic tori, abelian varieties and unipotent wound groups over local fields.
 In this geometrization of quasicharacters, our sheaves are local systems on
@@
 
-\tableofcontents
-
 \section*{Introduction}
 
-%This paper extends Deligne's function-sheaf dictionary from connected commutative algebraic groups to smooth commutative group schemes over finite fields and then provides an application to the geometrization and categorification of quasicharacters of algebraic tori, abelian varieties and unipotent wound groups over non-Archimedean local fields.
+Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
+this paper extends Deligne's function-sheaf dictionary from commutative algebraic groups to smooth commutative group schemes over finite fields.
 
@@
 \begin{equation}\label{introbox}
-m^* \cs{E} \iso \cs{E} \boxtimes \cs{E},
+m^* \qcs{E} \iso \qcs{E} \boxtimes \qcs{E},
 \end{equation}
@@
 %
-If one wishes to make a category from this class of local systems, one is led to consider morphisms $\cs{E} \to \cs{E}'$ of sheaves which are compatible with particular choices of \eqref{introbox} for $\cs{E}$ and $\cs{E'}$.
-{\it A priori}, the composition $\cs{E} \to \cs{E}' \to \cs{E}''$ of two such morphisms need not be compatible with the choices of \eqref{introbox} for $\cs{E}$ and $\cs{E}''$.
- However, for connected $G$ the isomorphism \eqref{introbox} is unique, if it exists, and there is no impediment to making the dictionary categorical.
+If one wishes to make a category from this class of local systems, one is led to consider morphisms $\qcs{E} \to \qcs{E}'$ of sheaves which are compatible with particular choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E'}$.
+{\it A priori}, the composition $\qcs{E} \to \qcs{E}' \to \qcs{E}''$ of two such morphisms need not be compatible with the choices of \eqref{introbox} for $\qcs{E}$ and $\qcs{E}''$.
+ However, for connected $G$ the isomorphism \eqref{introbox} is unique if it exists, and there is no impediment to making the dictionary categorical.
 
 If $G$ is a commutative algebraic group over $\Fq$ which is not connected, then the isomorphism \eqref{introbox} need not be unique.
-In order to track the choice of isomorphism, consider the category $\bCS(G)$ of pairs $(\cs{E},\mu_\cs{E})$ where $\cs{E}$ is a rank-one local system on $G$ and $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ is a chosen isomorphism of local systems on $G\times G$.
-In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of objects in $\bCS(G)$ to characters of $G(\Fq)$, but the epimomorphism need not be injective; consequently,
-every character of $G(\Fq)$ may be geometrized as a pair $(\cs{E},\mu_\cs{E})$ but perhaps not uniquely.
-Indeed, it follows from a special case of the main result of this paper that the kernel of the trace of Frobenius $T_{G} : \bCS(G) \to G(\Fq)^*$ trivial if and only if the \'etale group scheme of connected components of $G$ is finite cyclic.
-In general, the defect in the dictionary for characters of commutative algebraic groups over finite fields may be addressed with the following observation: if $(\cs{E},\mu_\cs{E})$ and $(\cs{E}',\mu_\cs{E}')$ determine the same character of $G(\Fq)$ then $\cs{E}\iso \cs{E}'$ as local systems on $G$.
+In order to track the choice of isomorphism, consider the category of pairs $(\qcs{E},\mu_\qcs{E})$ where $\qcs{E}$ is a rank-one local system on $G$ and $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ is a chosen isomorphism of local systems on $G\times G$.
+In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of pairs $(\qcs{E},\mu_\qcs{E})$ to characters of $G(\Fq)$, but the epimomorphism need not be injective; consequently,
+every character of $G(\Fq)$ may be geometrized as a pair $(\qcs{E},\mu_\qcs{E})$ but perhaps not uniquely in the category of pairs. 
+While this might appear to be a defect in the dictionary for characters of commutative algebraic groups over finite fields, it is not serious: if $(\qcs{E},\mu_\qcs{E})$ and $(\qcs{E}',\mu_\qcs{E}')$ determine the same character of $G(\Fq)$ then $\qcs{E}\iso \qcs{E}'$ as local systems on $G$.
 
 In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\Fq$,
-we replace the local system $\cs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\cs{E}$. 
-In this way we are led to the category $\CS(G)$ of {\it character sheaves} on $G$ (\S\ref{ssec:category}):
-objects in $\CS(G)$ are triples $(\gcs{L}, \mu,\phi)$, where $\gcs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\Fq}} \Spec{\bFq}$
-and $\phi : \Frob{G}^* \gcs{L}\to \gcs{L}$ and $\mu : {\bar m}^* \gcs{L} \iso \gcs{L} \boxtimes \gcs{L}$ are isomorphisms of sheaves satisfying certain compatibility conditions;
-morphisms in $\CS(G)$ are then morphisms of Weil sheaves which are compatible with the extra structure.
-
-We begin a study of the category $\CS(G)$ of character sheaves on $G$ by returning to the case when $G$ is a connected commutative algebraic group over $\Fq$ and thus by revisiting Deligne's function-sheaf dictionary (\S\ref{sec:category}).
-We consider character sheaves that arise via base change to $\bFq$ from local systems on $G$ (\S\ref{ssec:descentG}) and
-those that appear in a pushforward from a constant sheaf along a discrete isogeny $H \to G$ (\S\ref{ssec:discrete_isogenies}).  
-While these constructions make sense even for non-connected $G$, in the connected case we show that every character sheaf can be described in both of these ways (\S\ref{ssec:connected}).  
-We use this fact to prove that $\TrFrob{G}$ is an isomorphism for connected commutative algebraic groups $G$
-and to determine the automorphism groups of character sheaves on such $G$. 
-These results are all well known.
-
-Next, we consider character sheaves on \'etale commutative group schemes $G$ over $\Fq$ (\S\ref{sec:etale}).
-\'Etale group schemes form a counterpoint to connected algebraic groups, since the component group of any smooth group scheme is an \'etale group scheme;
-etale group schemes are algebraic groups only when they are finite.
-Our key tool for understanding the trace of Frobenius in the \'etale case 
-are a reinterpretation of $\CS(G)$ in terms of stalks (\S\ref{ssec:stalks}) and 
-a relationship with the Hochschild-Serre spectral sequence (\S\ref{ssec:E}) for $\Weil{} \ltimes \bG$, where $\Weil{} \subset \Gal(\Fq/\Fq)$ is the Weil group for $\Fq$.
-We define (\S\ref{ssec:S}) an isomorphism $S_G$ from $\CSiso{G}$ to the second cohomology of the total space of the spectral sequence
+we simply replace the local system $\qcs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\qcs{E}$. 
+In this way we are led to the category $\QC(G)$ of {\it quasicharacter sheaves} on $G$ (\S\ref{ssec:category}).
+Objects in $\QC(G)$ are triples $(\gqcs{L}, \mu,\phi)$, where $\gqcs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\Fq}} \Spec{\bFq}$
+and $\phi : \Frob{G}^* \gqcs{L}\to \gqcs{L}$ and $\mu : {\bar m}^* \gqcs{L} \iso \gqcs{L} \boxtimes \gqcs{L}$ are isomorphisms of sheaves satisfying certain compatibility conditions.
+Morphisms in $\QC(G)$ are then morphisms of Weil sheaves which are compatible with the extra structure.
+
+We first test the category of quasicharacter sheaves by examining its objects on \'etale commutative group schemes $G$ over $\Fq$ (\S\ref{sec:etale});
+\'etale group schemes form a counterpoint to connected algebraic groups, since the component group of any smooth group scheme is an \'etale group scheme.
+Our key tools for understanding the trace of Frobenius in the \'etale case are a reinterpretation of $\QC(G)$ in terms of stalks (\S\ref{ssec:stalks}) and a
+relationship with the Hochschild-Serre spectral sequence (\S\ref{ssec:E}) for $\Weil{} \ltimes \bG$, where $\Weil{} \subset \Gal(\Fq/\Fq)$ is the Weil group for $\Fq$.
+We define (\S\ref{ssec:S}) an isomorphism $S_G$ from $\QCiso{G}$ to the second cohomology of the total space of the spectral sequence
 \[
@@
 \[
-\TrFrob{G}: \CSiso{G} \to G(\Fq)^*
+\TrFrob{G}: \QCiso{G} \to G(\Fq)^*
 \]
 provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$.
-One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is finite cyclic.
-%The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gcs{L}, \mu,\phi)$ and $(\gcs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gcs{L},\phi)$ and $(\gcs{L}',\phi')$ are isomorphic as Weil sheaves.
-
-%The appearance of $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ and the trace of Frobenius gives an isomorphism $\TrFrob{G}: \CSiso{G} \to \Hom(G(\Fq),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\Fq$, then $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ measures the kernel of $\TrFrob{G}: \CSiso{G} \to \Hom(G(\Fq),\EEx)$.
+One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic.
+%The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gqcs{L}, \mu,\phi)$ and $(\gqcs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gqcs{L},\phi)$ and $(\gqcs{L}',\phi')$ are isomorphic as Weil sheaves.
+
+Returning to the case of connected commutative algebraic groups $G$, we consider quasicharacter sheaves that arise via base change to $\bFq$ from local systems on $G$ (\S\ref{ssec:descentG}) and
+those that appear in a pushforward from a constant sheaf along a discrete isogeny $H \to G$ (\S\ref{ssec:discrete_isogenies}).
+While these constructions make sense even for non-connected $G$, in the connected
+case we show that every quasicharacter sheaf can be described in both of these ways (\S\ref{ssec:connected}).
+We use this fact to prove that $\TrFrob{G}$ is an isomorphism for connected commutative algebraic groups $G$
+and to determine the automorphism groups of quasicharacter sheaves on such $G$.
+
+%The appearance of $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ and the trace of Frobenius gives an isomorphism $\TrFrob{G}: \QCiso{G} \to \Hom(G(\Fq),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\Fq$, then $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ measures the kernel of $\TrFrob{G}: \QCiso{G} \to \Hom(G(\Fq),\EEx)$.
 %This observation makes plain the fact that  . . .
@@
 
-Having understood character sheaves on commutative smooth group schemes over $\Fq$ in two extreme cases --
-connected commutative algebraic groups and \'etale commutative group schemes -- we turn to the general case  (\S\ref{sec:main}), using the component group sequence
+Having understood quasicharacter sheaves on commutative smooth group schemes over $\Fq$ in two extreme cases --
+connected commutative algebraic groups and \'etale commutative group schemes -- we turn to the general case, using the component group sequence
 \[
@@
 \]
-Using pullbacks of character sheaves we obtain a diagram
+Using pullbacks of quasicharacter sheaves (\S\ref{ssec:Frob}), we obtain a diagram
 \[
   \begin{tikzcd}[row sep=20, column sep=20]
-    0 \rar & \CSiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
-    & \CSiso{G} \rar \dar{\TrFrob{G}} & \CSiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
+    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
+    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
     0 \rar & \pi_0(G)(\Fq)^* \rar & G(\Fq)^* \rar & G^0(\Fq)^* \rar & 0.
@@
 \[
-\TrFrob{G} : \CSiso{G} \to G(\Fq)^*
+\TrFrob{G} : \QCiso{G} \to G(\Fq)^*
 \]
@@
 \end{theorem*}
-\noindent
-It follows that, unless the etale group scheme $\pi_0(\bG)$ is cyclic, the category $\CS(G)$ contains non-trivial character sheaves lying in the kernel of the trace of Frobenius and therefore lost in translation to characters of $G(\Fq)$ and, moreover, that these {\it invisible character sheaves} are parametrized by $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
-
-We also illuminate the nature of the category $\CS(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing
+We also illuminate the nature of the category $\QC(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing
 \begin{theorem*}[{Thm. \ref{thm:autornaught}}]
@@
 \[
-\Aut_{\CS{}}(\cs{L}) \iso  \Hh^1(\pi_0(\bG), \EEx)^{\Weil{}}
-\]
-for all quasicharacter sheaves $\cs{L}$ on $G$.
+\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx),
+\]
+for all quasicharacter sheaves $\qcs{L}$ on $G$.
 \end{theorem*}
@@
 This class of groups includes abelian varieties and unipotent $K$-wound groups in addition to the tori we initially considered.
-
 In this paper we show that quasicharacters of $X(K)$ are geometrized and categorified by quasicharacter sheaves on the
@@
 Although not locally of finite type, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and also a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
-This structure allows us to adapt our work on character sheaves on smooth group schemes over finite fields to construct (\S\ref{ssec:CS_on_GN}) a category $\QCS(X_K)$
+This structure allows us to adapt our work on quasicharacter sheaves to construct (\S\ref{ssec:qc_on_GN}) a category $\QC(X_K)$
 of quasicharacter sheaves for $X_K$, which are certain sheaves on $\Gr_R(X)\times_{\Spec{\Fq}} \Spec{\bFq}$, with extra structure.
@@
 
-Specializing to the case that $X = T$ is the N\'eron model of an algebraic torus over $K$ (\S\ref{ssec:CS_tori}), 
+Specializing to the case that $X = T$ is the N\'eron model of an algebraic torus over $K$ (\S\ref{ssec:qc_tori}), 
 we give a canonical short exact sequence 
 \[
-0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCSiso{T_K} \to \Hom_\text{QC}(T(K),\EEx) \to 0,
-\]
-where $\Hom_\text{QC}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
-We further show that automorphism groups in $\CS(T_K)$ are given, for every quasicharacter sheaf $\cs{F}$ for $T_K$, by
-\[
-\Aut_{\QCS{}}(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
+0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{T_K} \to \Hom_\text{qc}(T(K),\EEx) \to 0,
+\]
+where $\Hom_\text{qc}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
+We further show that automorphism groups in $\QC(T_K)$ are given, for every quasicharacter sheaf $\qcs{F}$ for $T_K$, by
+\[
+\Aut(\qcs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
 \]
@@
 When commutative, such groups are extensions of finite cyclic groups by algebraic tori,
-in which case it is not difficult to relate Frobenius-stable character sheaves to our character sheaves.
-%The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in that context.
+in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.
+The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in that context.
 
@@
 allowed us to hijack much of a Research in Teams meeting at the Banff International Research Station into a discussion of
-character sheaves.  We thank them for their kindness, knowledge and invaluable help.
+quasicharacter sheaves.  We thank them for their kindness, knowledge and invaluable help.
 We thank Takashi Suzuki for some very helpful observations and suggestions, especially related to our use of the Hochschild-Serre spectral sequence.
@@
 
-\section{Recollections on character sheaves} \label{sec:category}
+\section{The category of quasicharacter sheaves} \label{sec:category}
 
@@
 Throughout this paper, $G$ is a smooth commutative group scheme
-over a finite field $\Fq$ and $m : G \times G\to G$ is its multiplication morphism.
-It follows from the smoothness of $G$ that the structure morphism $G \to \Spec{\Fq}$ is locally of finite type.
-We will make use of the short exact sequence of smooth group schemes defining the component group scheme for $G$:
-\[
-\begin{tikzcd}
-0 \rar & G^0 \arrow{r}{\iota_0} & G \arrow{r}{\pi_0} & \pi_0(G) \rar & 0.
-\end{tikzcd}
-\]
-Then $G^0$ is a connected algebraic group and $\pi_0(G)$ is an \'etale commutative group scheme.
-Unless noted otherwise, we place absolutely no conditions on the \'etale group scheme $\pi_0(G)$.
-If the structure morphism $G \to \Spec{\Fq}$ is \'etale, then $G$ is an etale group scheme; this does not imply that $\pi_0(G)$ is finite.
-If the structure morphism $G \to \Spec{\Fq}$ is of finite type, then $G$ is an algebraic group; in this case, $\pi_0(G)$ is finite. 
-Indeed, a smooth commutative group scheme $G$ is an algebraic group if and only if the etale group scheme $\pi_0(G)$ is finite.
+over a finite field $\Fq$, and $m : \GxG\to G$ is its multiplication morphism.
 
@@
 
-\subsection{Character sheaves on commutative group schemes over finite fields}\label{ssec:category}
-
-\begin{definition}\label{def:CS}
-A \emph{character sheaf on $G$} is a triple
-$\cs{L}\ceq (\gcs{L},\mu,\phi)$ where:
+\subsection{Quasicharacter sheaves}\label{ssec:category}
+
+\begin{definition}\label{def:QC}
+A \emph{quasicharacter sheaf on $G$} is a triple
+$\qcs{L}\ceq (\gqcs{L},\mu,\phi)$ where:
 \begin{enumerate}
-\labitem{(CS.1)}{CS.1} $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean a constructible $\ell$-adic sheaf on $\bG$, {\it lisse} on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
-\labitem{(CS.2)}{CS.2} $\mu: \bm^* \gcs{L} \to \LxL$ is an isomorphism of
+\labitem{(QC.1)}{QC.1} $\gqcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean a constructible $\ell$-adic sheaf on $\bG$, {\it lisse} on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
+\labitem{(QC.2)}{QC.2} $\mu: \bm^* \gqcs{L} \to \LxL$ is an isomorphism of
 sheaves on $\bGxG$ such that the following diagram commutes,
@@
   \begin{tikzcd}[row sep=30]
-  \bm_3^*\gcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
-    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
-    \gcs{L} \boxtimes \bm^* \gcs{L} \arrow{rr}{\id \boxtimes \mu}
-    &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL
-  \end{tikzcd}
-  \]
-\labitem{(CS.3)}{CS.3} $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an
+  \bm_3^*\gqcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
+    &&  \bm^*\gqcs{L} \boxtimes \gqcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
+    \gqcs{L} \boxtimes \bm^* \gqcs{L} \arrow{rr}{\id \boxtimes \mu}
+    &&  \gqcs{L} \tight{0}{\boxtimes}{0} \LxL
+  \end{tikzcd}
+  \]
+\labitem{(QC.3)}{QC.3} $\phi : \Frob{G}^* \gqcs{L} \to \gqcs{L}$ is an
   isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with
@@
   \begin{tikzcd}[row sep=20]
-  \Frob{\GxxG}^* \bm^* \gcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
+  \Frob{\GxxG}^* \bm^* \gqcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
     && \Frob{\GxxG}^*(\LxL)\\
-    \arrow[equal]{u} \bm^*  \Frob{G}^* \gcs{L} \arrow[swap]{d}{\bm^* \phi}
-    && \Frob{G}^*\gcs{L}\boxtimes \Frob{G}^*\gcs{L} \dar{\phi\boxtimes \phi} \arrow[equal]{u} \\
-    \bm^*\gcs{L} \arrow{rr}{\mu}
+    \arrow[equal]{u} \bm^*  \Frob{G}^* \gqcs{L} \arrow[swap]{d}{\bm^* \phi}
+    && \Frob{G}^*\gqcs{L}\boxtimes \Frob{G}^*\gqcs{L} \dar{\phi\boxtimes \phi} \arrow[equal]{u} \\
+    \bm^*\gqcs{L} \arrow{rr}{\mu}
     && \LxL
@@
 
-Morphisms in the category of character sheaves on $G$, denoted by $\CS(G)$, are defined in the natural way:
+Morphisms in the category of quasicharacter sheaves on $G$, denoted by $\QC(G)$, are defined in the natural way:
 \begin{enumerate}
-\labitem{(CS.4)}{CS.4} if $\cs{L} = (\gcs{L},\mu,\phi)$ and
-  $\cs{L'} = (\gcs{L'},\mu',\phi')$ are character sheaves on $G$ then
-  a morphism $\rho : \cs{L} \to \cs{L}'$ is a map $\brho : \gcs{L} \to \gcs{L'}$
+\labitem{(QC.4)}{QC.4} if $\qcs{L} = (\gqcs{L},\mu,\phi)$ and
+  $\qcs{L'} = (\gqcs{L'},\mu',\phi')$ are quasicharacter sheaves on $G$ then
+  a morphism $\rho : \qcs{L} \to \qcs{L}'$ is a map $\brho : \gqcs{L} \to \gqcs{L'}$
   of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
@@
   \begin{tikzcd}[column sep=40]
-  \Frob{G}^* \gcs{L} \rar{\Frob{G}^* \brho} \arrow[swap]{d}{\phi} & \Frob{G}^* \gcs{L'} \dar{\phi'}
-  & & \arrow[swap]{d}{\mu} \bm^* \gcs{L} \rar{\bm^* \brho} & \bm^* \gcs{L'} \dar{\mu'} \\
-  \gcs{L} \rar{\brho} & \gcs{L'}
-  & {} & \LxL \rar{\tight{1}{\rho\boxtimes \rho}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
+  \Frob{G}^* \gqcs{L} \rar{\Frob{G}^* \brho} \arrow[swap]{d}{\phi} & \Frob{G}^* \gqcs{L'} \dar{\phi'}
+  & & \arrow[swap]{d}{\mu} \bm^* \gqcs{L} \rar{\bm^* \brho} & \bm^* \gqcs{L'} \dar{\mu'} \\
+  \gqcs{L} \rar{\brho} & \gqcs{L'}
+  & {} & \LxL \rar{\tight{1}{\rho\boxtimes \rho}{1}} & \gqcs{L'} \tight{0}{\boxtimes}{0} \gqcs{L'}
   \end{tikzcd}
@@
 
-Category $\CS(G)$ is a rigid monoidal category
+Category $\QC(G)$ is a rigid monoidal category
 \cite{etingof:09a}*{\S1.10} under the tensor product
-$\cs{L} \otimes \cs{L'}$ defined by $(\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
+$\qcs{L} \otimes \qcs{L'}$ defined by $(\gqcs{L}\otimes\gqcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
 with duals given by applying the sheaf hom functor
 $\sheafHom(\ - \ ,\EE)$.
-This rigid monoidal category structure for $\CS(G)$ gives the set $\CSiso{G}$
-of isomorphism classes in $\CS(G)$ the structure of a group.
+This rigid monoidal category structure for $\QC(G)$ gives the set $\QCiso{G}$
+of isomorphism classes in $\QC(G)$ the structure of a group.
 
 \begin{remark}
-The category of character sheaves on $G$ is not abelian since it is not closed under direct sums; 
-thus $\CS(G)$ is not a tensor category in the sense of \cite{deligne:02a}*{0.1}.  
-We suspect that requiring that $\mu$ be injective rather than
+The category of quasicharacter sheaves on $G$ is not abelian since it is not closed under direct sums and thus $\QC(G)$
+is not a tensor category in the sense of \cite{deligne:02a}*{0.1}.  We suspect that requiring that $\mu$ be injective rather than
 an isomorphism and dropping the condition that the stalks be one-dimensional would yield an abelian category.
@@
 
-We will describe the group $\CSiso{G}$ in Theorem~\ref{thm:snake}
-and the sets $\Hom(\cs{L},\cs{L}')$ in Theorem~\ref{thm:autornaught}; in this way we provide a complete description of the category $\CS(G)$.
+We will describe the group $\QCiso{G}$ in Theorem~\ref{thm:snake}
+and the sets $\Hom(\qcs{L},\qcs{L}')$ in Theorem~\ref{thm:autornaught}; in this way we provide a complete description of the category $\QC(G)$.
 %
-In the meantime, we close this subsection with an elementary observation about $\Hom(\cs{L},\cs{L}')$.
+In the meantime, we close this section with an elementary observation about $\Hom(\qcs{L},\qcs{L}')$.
 We call a morphism of sheaves \emph{trivial} if it is zero on every stalk.
@@
 Let $G$ be a smooth commutative group scheme over $\Fq$.
-If $\cs{L}$ and $\cs{L}'$ are character sheaves on $G$, then
-every $\rho\in \Hom(\cs{L},\cs{L}')$ is either trivial or an isomorphism. 
+If $\qcs{L}$ and $\qcs{L}'$ are quasicharacter sheaves on $G$, then
+every $\rho\in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism. 
 \end{lemma}
@@
 \begin{proof}
-Suppose $\rho \in \Hom(\cs{L},\cs{L}')$.
-We prove the lemma by considering the linear transformations $\brho_{\bar g} : \gcs{L}_{\bar g} \to \gcs{L}_{\bar g}$ at the stalks above geometric points ${\bar g}$ on $G$ and showing that, either each $\brho_{\bar g}$ trivial or each $\brho_{\bar g}$ is an isomorphism.
+Suppose $\rho \in \Hom(\qcs{L},\qcs{L}')$.
+We prove the lemma by considering the linear transformations $\brho_{\bar g} : \gqcs{L}_{\bar g} \to \gqcs{L}_{\bar g}$ at the stalks above geometric points ${\bar g}$ on $G$ and showing that, either each $\brho_{\bar g}$ trivial or each $\brho_{\bar g}$ is an isomorphism.
 (This idea is expanded upon in Section~\ref{ssec:stalks}.)
 Let ${\bar e}$ be the geometric point above the identity $e$ for $G$ determined by our choice of algebraic closure $\bFq$ of $\Fq$.
-If $\brho_{\bar e} = 0$ then the second diagram in \ref{CS.4} implies that $\brho_{\bar g} = 0$ for all ${\bar g}$, in which case $\rho$ is trivial.
-On the other hand, if $\brho_{\bar e}$ is nontrivial then the second diagram in \ref{CS.4}  implies that $\brho_{\bar g}$ is nontrivial for all ${\bar g}$ and thus an isomorphism, since the stalk of character sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
+If $\brho_{\bar e} = 0$ then the second diagram in \ref{QC.4} implies that $\brho_{\bar g} = 0$ for all ${\bar g}$, in which case $\rho$ is trivial.
+On the other hand, if $\brho_{\bar e}$ is nontrivial then the second diagram in \ref{QC.4}  implies that $\brho_{\bar g}$ is nontrivial for all ${\bar g}$ and thus an isomorphism, since the stalk of quasicharacter sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
 \end{proof}
@@
 
-In this section we introduce two tools which will help us understand isomorphism classes of objects in $\CS(G)$: the map $\CSiso{G} \to G(k)^*$ given by trace of Frobenius and the pullback functor $\CS(G) \to \CS(H)$ associated to a morphism $H \to G$.
-
-Let $(\gcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
+In this section we introduce two tools which will help us understand isomorphism classes of objects in $\QC(G)$: the map $\QCiso{G} \to G(k)^*$ given by trace of Frobenius and the pullback functor $\QC(G) \to \QC(H)$ associated to a morphism $H \to G$.
+
+Let $(\gqcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
 determines a geometric point $\bg$ fixed by $\Frob{G}$. 
-Together with the canonical isomorphism $(\Frob{G}^*\gcs{L})_{\bg} \iso  \gcs{L}_{\Frob{G}(\bg)}$, the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gcs{L}_{\bg}$.
-Let $\trace(\phi_{\bg};\gcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gcs{L}_{\bg})$ and let $\trFrob{(\gcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by 
+Together with the canonical isomorphism $(\Frob{G}^*\gqcs{L})_{\bg} \iso  \gqcs{L}_{\Frob{G}(\bg)}$, the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gqcs{L}_{\bg}$.
+Let $\trace(\phi_{\bg};\gqcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gqcs{L}_{\bg})$ and let $\trFrob{(\gqcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by 
 \begin{equation}\label{trWeil}
-\trFrob{(\gcs{L},\phi)}(g) \ceq \trace(\phi_{\bg};\gcs{L}_{\bg}),
+\trFrob{(\gqcs{L},\phi)}(g) \ceq \trace(\phi_{\bg};\gqcs{L}_{\bg}),
 \end{equation}
-commonly called the {\em trace of Frobenius of $(\gcs{L},\phi)$}.
-Note that if $(\gcs{L},\phi) \iso (\gcs{L'},\phi')$ as Weil sheaves, 
-then $\trFrob{(\gcs{L},\phi)} = \trFrob{(\gcs{L'},\phi')}$ as functions on $G(\Fq)$.
-
-Now suppose $\cs{L} = (\gcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$.
-Then the isomorphism $\bm^* \gcs{L} \iso \gcs{L} \boxtimes\gcs{L}$ and the diagram of
-\ref{CS.3} guarantee
-that the function $\trFrob{(\gcs{L},\phi)} : G(\Fq)\to \EEx$ is a group homomorphism, which we will also denote by $\trFrob{\cs{L}}$.  Moreover,
-this homomorphism depends only on the isomorphism class of $\cs{L}$, so we obtain a map
+commonly called the {\em trace of Frobenius of $(\gqcs{L},\phi)$}.
+Note that if $(\gqcs{L},\phi) \iso (\gqcs{L'},\phi')$ as Weil sheaves, 
+then $\trFrob{(\gqcs{L},\phi)} = \trFrob{(\gqcs{L'},\phi')}$ as functions on $G(\Fq)$.
+
+Now suppose $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$.
+Then the isomorphism $\bm^* \gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$ and the diagram of
+\ref{QC.3} guarantee
+that the function $\trFrob{(\gqcs{L},\phi)} : G(\Fq)\to \EEx$ is a group homomorphism, which we will also denote by $\trFrob{\qcs{L}}$.  Moreover,
+this homomorphism depends only on the isomorphism class of $\qcs{L}$, so we obtain a map
 \begin{align*}
-\TrFrob{G} : \CSiso{G} &\to G(\Fq)^*, \\
-\cs{L} &\mapsto \trFrob{\cs{L}}.
+\TrFrob{G} : \QCiso{G} &\to G(\Fq)^*, \\
+\qcs{L} &\mapsto \trFrob{\qcs{L}}.
 \end{align*}
-Since tensor products on the stalks of $\cs{L}$ induce pointwise multiplication on the trace of Frobenius, $\TrFrob{G}$ is a group homomorphism.  We devote the remainder of this section to
+Since tensor products on the stalks of $\qcs{L}$ induce pointwise multiplication on the trace of Frobenius, $\TrFrob{G}$ is a group homomorphism.  We devote the remainder of this section to
 studying the behavior of the trace of Frobenius under morphisms of group schemes.  These simple but important
@@
   \begin{align*}
-  f^* : \CS(G) &\to \CS(H) \\
-  (\gcs{L},\mu,\phi) &\mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)
+  f^* : \QC(G) &\to \QC(H) \\
+  (\gqcs{L},\mu,\phi) &\mapsto (\bf^*\gqcs{L},(\bfxf)^*\mu,\bf^*F)
   \end{align*}
@@
   \begin{tikzcd}[row sep=20, column sep=30]
-   \CSiso{G} \rar{f^*} \arrow[swap]{d}{\TrFrob{G}} & \CSiso{H} \dar{\TrFrob{H}} \\
+   \QCiso{G} \rar{f^*} \arrow[swap]{d}{\TrFrob{G}} & \QCiso{H} \dar{\TrFrob{H}} \\
    G(\Fq)^* \rar & H(\Fq)^*
@@
 \begin{proof}
-  Let $\cs{L}$ be a character sheaf on $G$. 
+  Let $\qcs{L}$ be a quasicharacter sheaf on $G$. 
   Pullback by $\bf$ takes rank-one local systems to rank-one local systems.
-  To see that $(\bfxf)^* \mu$ satisfies \ref{CS.2},
+  To see that $(\bfxf)^* \mu$ satisfies \ref{QC.2},
   apply the functor $(\bfxf)^*$
-  to \ref{CS.2} for $\cs{L}$ and use the canonical isomorphism
-  $(\bfxf)^*(\LxL) \iso \bf^*\gcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gcs{L}$.
-  To show that $f^*\cs{L}$ satisfies
-  \ref{CS.3}, apply the same functor to \ref{CS.3} for $\cs{L}$.
+  to \ref{QC.2} for $\qcs{L}$ and use the canonical isomorphism
+  $(\bfxf)^*(\LxL) \iso \bf^*\gqcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gqcs{L}$.
+  To show that $f^*\qcs{L}$ satisfies
+  \ref{QC.3}, apply the same functor to \ref{QC.3} for $\qcs{L}$.
   Since $f$ is a morphism of group schemes defined over $\Fq$
@@
 
-  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{CS.4} defines the action
-  of $f^*$ on morphisms of character sheaves; arguing as above shows that $f^*$ is
-  a functor from $\CS(G)$ to $\CS(H)$.  Since tensor products commute with pullback in schemes,
-  $f^* : \CS(G) \to \CS(H)$ is a monoidal functor.
-  The diagram relating $f^* : \CS(G) \to \CS(H)$, $f^* : G(k)^* \to H(k)^*$ and trace of Frobenius
+  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{QC.4} defines the action
+  of $f^*$ on morphisms of quasicharacter sheaves; arguing as above shows that $f^*$ is
+  a functor from $\QC(G)$ to $\QC(H)$.  Since tensor products commute with pullback in schemes,
+  $f^* : \QC(G) \to \QC(H)$ is a monoidal functor.
+  The diagram relating $f^* : \QC(G) \to \QC(H)$, $f^* : G(k)^* \to H(k)^*$ and trace of Frobenius
   commutes by \cite{laumon:87a}*{1.1.1.2}, where the ambient
@@
 
-If $G_1$ and $G_2$ are smooth commutative group schemes over $\Fq$ then characters of $(G_1 \times G_2)(\Fq)$ all take the form $\chi_1\otimes \chi_2$ for characters $\chi_1$ of $G_1(\Fq)$ and $\chi_2$ of $G_2(\Fq)$.
-The next lemma shows that character sheaves on $G$ enjoy an analogous property.
-
 \begin{lemma}\label{lem:product}
-If $G_1$ and $G_2$ are smooth commutative group schemes over $\Fq$ then the following diagram commutes.
+If $G_1$ and $G_2$ are smooth commutative group schemes over $\Fq$ then the rule
+$\boxtimes : (\qcs{L}_1,\qcs{L}_2)\to \qcs{L}_1\boxtimes\qcs{L}_2$ defines an equivalence of categories
+\[
+\boxtimes : \QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)
+\]
+such that
 \[
 \begin{tikzcd}[column sep=60]
-\arrow{d}{\TrFrob{G_1} \times \TrFrob{G_2}} \CSiso{G_1}\times \CSiso{G_2} \arrow{r}{(\cs{L}_1,\cs{L}_2)\mapsto \cs{L}_1\boxtimes \cs{L}_2}
-& \arrow{d}{\TrFrob{G_1\times G_2}} \CSiso{G_1\times G_2}\\
+\arrow{d}{\TrFrob{G_1} \times \TrFrob{G_2}} \QCiso{G_1}\times \QCiso{G_2} \arrow{r}{\boxtimes}
+& \arrow{d}{\TrFrob{G_1\times G_2}} \QCiso{G_1\times G_2}\\
 (G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
@@
 \]
-Moreover, every character sheaf on $G_1\times G_2$ is isomorphic to $\cs{L}_1\boxtimes\cs{L}_2$ for some character sheaves $\cs{L}_1$ on $G_1$ and $\cs{L}_2$ on $G_2$.
+commutes.
 \end{lemma}
 \begin{proof}
-The only non-trivial part is the last claim, so we will only address that point here.
+The only non-trivial part of the proof is to show that 
+\[\boxtimes
+ : \QC(G_1)\times \QC(G_2) \to \QC(G_1\times G_2)
+ \]
+is essentially surjective, so we will only address that point here.
 %
@@
 %
-Now, let $\cs{L} \ceq (\gcs{L},\mu,\phi)$ be a character sheaf on $G$
-and set $\cs{L}_1 \ceq q_1^* \cs{L}$ and $\cs{L}_2 \ceq q_2^* \cs{L}$.
-By Lemma~\ref{lem:pullback}, $\cs{L}_1$ is a character sheaf on $G_1$
-and $\cs{L}_2$ is a character sheaf on $G_2$.
-We will obtain an isomorphism $\cs{L} \iso  \cs{L}_1\boxtimes \cs{L}_2$.
-
+Now, let $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$
+and set $\qcs{L}_1 \ceq q_1^* \qcs{L}$ and $\qcs{L}_2 \ceq q_2^* \qcs{L}$.
+By Lemma~\ref{lem:pullback}, $\qcs{L}_1$ is a quasicharacter sheaf on $G_1$
+and $\qcs{L}_2$ is a quasicharacter sheaf on $G_2$.
+We will obtain an isomorphism $\qcs{L} \iso  \qcs{L}_1\boxtimes \qcs{L}_2$.
 Applying the functor $f^*$ to the isomorphism $\mu$ yields
 \begin{equation}\label{eq:fm}
-f^*\mu : f^* m^* \gcs{L} \to f^*(\gcs{L}\boxtimes \gcs{L}) .
+f^*\mu : f^* m^* \gqcs{L} \to f^*(\gqcs{L}\boxtimes \gqcs{L}) .
 \end{equation}
-We have already seen that $m\circ f = \id_G$, so $f^* m^* \gcs{L} = \gcs{L}$.  
-Since $f^*p_1^*\gcs{L} = r_1^* q_1^* \gcs{L} = r_1^* \gcs{L}_1$ and $f^*p_2^*\gcs{L} = r_2^* q_2^* \gcs{L} = r_2^*\gcs{L}_2$,
+We have already seen that $m\circ f = \id_G$, so $f^* m^* \gqcs{L} = \gqcs{L}$.  
+Since $f^*p_1^*\gqcs{L} = r_1^* q_1^* \gqcs{L} = r_1^* \gqcs{L}_1$ and $f^*p_2^*\gqcs{L} = r_2^* q_2^* \gqcs{L} = r_2^*\gqcs{L}_2$,
 we have 
 \[
-f^*(\gcs{L}\boxtimes \gcs{L})  = f^*p_1^*\gcs{L}\otimes f^* p_2^*\gcs{L} = \gcs{L}_1\boxtimes \gcs{L}_2.
-\]
-It follows that \eqref{eq:fm} gives an isomorphism $\gcs{L} \to  \gcs{L}_1\boxtimes \gcs{L}_2$.
+f^*(\gqcs{L}\boxtimes \gqcs{L})  = f^*p_1^*\gqcs{L}\otimes f^* p_2^*\gqcs{L} = \gqcs{L}_1\boxtimes \gqcs{L}_2.
+\]
+It follows that \eqref{eq:fm} gives an isomorphism $\gqcs{L} \to  \gqcs{L}_1\boxtimes \gqcs{L}_2$.
 It is routine to show that this morphism satisfies
-\ref{CS.4}, as it applies here,
+\ref{QC.4} as it applies here,
 from which it follows that we have exhibited an isomorphism
-$\cs{L} \to \cs{L}_1\boxtimes \cs{L}_2$ of characters sheaves on $G\times G$.
+$\qcs{L} \to \qcs{L}_1\boxtimes \qcs{L}_2$ of quasicharacters sheaves on $G\times G$.
+This completes the proof that $\boxtimes$ is essentially surjective.
 \end{proof}
@@
 \begin{proposition}\label{prop:functorialG}
-The homomorphism $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ defines a natural transformation
+The homomorphism $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ defines a natural transformation
 between the two contravariant additive functors
 \begin{align*}
-F_1 : G &\mapsto \CSiso{G} \\
+F_1 : G &\mapsto \QCiso{G} \\
 F_2 : G &\mapsto G(\Fq)^*
@@
 
-%\subsection{character sheaves on connected commutative algebraic groups} \label{sec:disc-isog}
-
-\subsection{Descent}\label{ssec:descentG}
-
-Before turning our attention to character sheaves on connected commutative algebraic groups in Section~\ref{ssec:connected}, we treat two special classes of character sheaves on arbitrary smooth commutative group schemes $G$: those that descend from local systems on $\bG$ to local systems on $G$ (\S \ref{ssec:descentG}); and those that are defined by discrete isogenies onto $G$ (\S \ref{ssec:discrete_isogenies}).
+\section{Quasicharacter sheaves on \'etale commutative group schemes} \label{sec:etale}
+
+In this section we find a complete characterization of the category of quasicharacter sheaves on \'etale commutative group schemes over finite fields.
+
+\subsection{Stalks of quasicharacter sheaves}\label{ssec:stalks}
+
+The equivalence $G \mapsto G(\bFq)$,
+from the category of \'etale commutative group schemes over $\Fq$ to the category of commutative groups equipped
+with a continuous action of $\Gal(\bFq/\Fq)$,
+provides the following simple description of quasicharacter sheaves.
+%
+A quasicharacter sheaf $\qcs{L}$ on an \'etale commutative group scheme $G$ over $\Fq$ is:
+\begin{enumerate}
+ \labitem{(qc.1)}{qc.1} an indexed set of one-dimensional
+  $\EE$-vector spaces $\gqcs{L}_x$, as $x$ runs over
+  $G(\bFq)$;
+
+ \labitem{(qc.2)}{qc.2} an indexed set of isomorphisms
+  $\mu_{x,y} : \gqcs{L}_{x+y} \xrightarrow{\iso} \gqcs{L}_{x} \otimes\gqcs{L}_{y}$,
+  for all $x,y \in G(\bFq)$, such that
+  \[
+   \begin{tikzcd}[row sep=40]
+    \gqcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
+    && \gqcs{L}_{x+y}\otimes\gqcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
+    \gqcs{L}_{x} \otimes\gqcs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
+    && \gqcs{L}_{x} \otimes\gqcs{L}_{y} \otimes\gqcs{L}_{z}
+   \end{tikzcd}
+  \]
+  commutes, for all $x,y,z\in G(\bFq)$; and
+ \labitem{(qc.3)}{qc.3} an indexed set of isomorphisms $\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$
+  such that
+  \[
+   \begin{tikzcd}[row sep=40]
+    \gqcs{L}_{\Frob{}(x)+\Frob{}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{}(x),\Frob{}(y)}}
+    && \gqcs{L}_{\Frob{}(x)}\otimes\gqcs{L}_{\Frob{}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
+    \gqcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
+    && \gqcs{L}_x \otimes\gqcs{L}_y
+   \end{tikzcd}
+  \]
+  commutes, for all $x,y\in G(\bFq)$.
+\end{enumerate}
+Under this equivalence, a morphism $\rho : \qcs{L} \to \qcs{L'}$ of quasicharacter sheaves on $G$ is given by
+\begin{enumerate}
+ \labitem{(qc.4)}{qc.4} an indexed set $\brho_x : \gqcs{L}_x \to \gqcs{L'}_x$
+  of linear transformations such that
+  \[
+   \begin{tikzcd}[column sep=40]
+    \arrow[swap]{d}{\phi_x} \gqcs{L}_{\Frob{}(x)} \rar{\brho_{\Frob{}(x)}} & \gqcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
+    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
+    & \arrow[swap]{d}{\mu_{x,y}} \gqcs{L}_{x+y} \rar{\brho_{x+y}} & \gqcs{L'}_{x+y} \dar{\mu'_{x,y}} \\
+    \gqcs{L}_x \rar{\brho_x} & \gqcs{L'}_x
+    & {} & \gqcs{L}_x\otimes\gqcs{L}_y \rar{\brho_x\otimes\brho_y} & \gqcs{L'}_x \otimes\gqcs{L'}_y
+   \end{tikzcd}
+  \]
+  both commute, for all $x, y \in G(\bFq)$.
+\end{enumerate}
+
+We will see that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ may not provide complete
+information about isomorphism classes of quasicharacter sheaves on $G$ when $G$ is not a connected algebraic group.
+Our main tool for understanding this phenomenon
+is a group homomorphism $S_G: \QCiso{G} \to \Hh^2(E^\bullet_G)$ defined in Section~\ref{ssec:S}, for which the next two sections are preparation.
+
+\subsection{A spectral sequence}\label{ssec:E}
+
+The zeroth page of the Hochschild-Serre spectral sequence
+is a double complex $E^{\bullet, \bullet}$ defined by
+\[
+E^{i,j} = C^i(\Weil{}, C^j(G(\bFq), \EEx));
+\]
+see \cite{vakil:Algebraic_Geometry}*{\S 1.7}, expanding on \cite{weibel:Homological_Algebra}*{Ch 5 and \S 7.5}.
+The standard derivative on cochains yields two derivatives,
+\begin{align*}
+d_G &: E^{i,j} \to E^{i,j+1} \quad \mbox{and} \\
+d_{\Weil{}} &: E^{i,j} \to E^{i+1,j};
+\end{align*}
+we use the first as the derivative $d_0$ on the zeroth page, and the second to induce $d_1$.
+Combining them also yields a derivative $d = d_G + (-1)^j d_{\Weil{}}$ on the total complex
+\[
+E^n_G = \bigoplus_{i+j=n} E^{i,j}.
+\]
+The machinery of spectral sequences gives us a sequence of pages $E_r^{i,j}$, converging to a page $E_{\infty}^{i,j}$.
+We summarize the key properties of this spectral sequence in the following proposition.
+
+\begin{proposition} In the spectral sequence defined above,
+\begin{enumerate}
+\item the second page is given by $E_2^{i,j} = \Hh^i(\Weil{}, \Hh^j(G(\bFq), \EEx))$,
+\item there is an isomorphism $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) \cong \Hh^n(E_G^\bullet)$, and
+\item there is a filtration $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) = F_n \supset \cdots \supset F_{-1} = 0$, with $F_i / F_{i-1} \cong E_{\infty}^{i, n-i}$.
+\end{enumerate}
+\end{proposition}
+
+Moreover, since $\Weil{} \cong \ZZ$ has cohomological dimension $1$, $E_2^{i,j} = 0$ for $i > 1$ and the sequence degenerates at the second page: $E_{\infty}^{i,j} = E_2^{i,j}$.
+We obtain the following corollary:
+
+\begin{corollary}\label{cor:spectral_ses}
+There is a short exact sequence
+ \[
+    0 \to
+    \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to
+    \Hh^2(E^\bullet_G) \to
+    \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to
+    0.
+ \]
+\end{corollary}
+
+This sequence will play a key role in understanding the kernel of $\TrFrob{G}$, as described in the next few sections.
+For this application, we need a good understanding of these maps to and from the total complex.
+
+\begin{proposition} \label{prop:ses_desc}
+Consider the short exact sequence in Corollary~\ref{cor:spectral_ses}.
+\begin{enumerate}
+\item Every class $[\alpha\oplus\beta\oplus\gamma] \in \Hh^2(E^\bullet_G)$ is cohomologous to one with $\gamma=0$.
+\item The map $\Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx))$ is given by $[\alpha\oplus\beta\oplus 0] \mapsto [\beta]$.
+\item Suppose $a \in Z^2({\bar G}, \EEx)$ represents a class in $\Hh^2({\bar G},\EEx)$ fixed by Frobenius.
+The map $\Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to \Hh^2(E^\bullet_G)$ is given by $[a] \mapsto [a \oplus 0 \oplus 0]$.
+\end{enumerate}
+\end{proposition}
+\begin{proof}
+Since $\Hh^2(\Weil{}, C^0({\bar G}, \EEx)) = 0$, we may find a $\gamma_1 \in C^1(\Weil{}, C^0({\bar G}, \EEx))$ with $d_{\Weil{}}\gamma_1 = \gamma$.
+Subtracting $d \gamma_1$ from $\alpha\oplus\beta\oplus\gamma$, we may assume that $\gamma = 0$.
+
+The latter two claims follow from tracing through the definition of latter pages in the spectral sequence.
+\end{proof}
+
+\subsection{From quasicharacter sheaves to the total complex}\label{ssec:S}
+
+In this section we define an isomorphism
+\[
+S_G : \QCiso{G} \to \Hh^2(E^\bullet_G).
+\]
+Let $\qcs{L} = (\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$.
+For each geometric point $x\in {\bar G}$, choose a basis $\{ v_x \}$ for $\gqcs{L}_x$.
+Through this choice, $\qcs{L}$ determines functions
+\begin{align*}
+a : {\bar G}\times {\bar G} &\to \EEx & b : {\bar G} &\to \EEx \\
+\mu_{x,y}(v_{x+y}) &= a(x,y) v_x \otimes v_y & \phi_x(v_{\Frob{G}(x)}) &= b(x) v_x.
+\end{align*}
+Condition~\ref{QC.2} implies that
+\begin{equation}\label{2-cocyle}
+a(x+y,z) a(x,y) = a(x,y+z) a(y,z)
+\end{equation}
+for all $x,y,z\in {\bar G}$, so $a \in Z^2({\bar G},\EEx)$.  Similarly, condition~\ref{QC.3} gives
+\begin{equation}\label{nohom}
+\frac{a(\Frob{G}(x),\Frob{G}(y))}{a(x,y)} =  \frac{b(x+y)}{b(x) b(y)}
+\end{equation}
+for $x, y \in {\bar G}$.
+Let $\alpha \in C^0(\Weil{},C^2({\bar G},\EEx)$ be the $0$-cochain corresponding to $a$ and let $\beta\in C^1(\Weil{},C^1({\bar G},\EEx)$ be the cocycle such that $\beta(\Frob{})$ is $b$.
+We will write both $\alpha$ and $\beta$ additively.
+Then
+\[
+d_G\alpha =0, \qquad\qquad
+d_{\Weil{}} \alpha = d_{G} \beta,\qquad\qquad
+d_{\Weil{}} \beta =0;
+\]
+in other words,
+\[\alpha\oplus \beta \in Z^2(E^\bullet_G).\]
+Although the cocycle $\alpha\oplus \beta$ is not well defined by $\qcs{L}$, its class in $\Hh^2(E^\bullet_G)$ is.
+To see this, let $\{ v'_x \in \gqcs{L}_x^\times \tq x \in {\bar G}\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$ be defined by $\qcs{L}$ and this choice, as above.
+Now let $\delta \in C^0(\Weil{},C^1({\bar G},\EEx))$ correspond to the function $d : {\bar G}\to \EEx$ defined by $v'_x = d(x) v_x$.
+Chasing through \ref{QC.2} and \ref{QC.3}, we find
+\[
+\alpha'\oplus\beta' = \alpha\oplus\beta + d\delta,
+\]
+so the class $[\alpha\oplus\beta]$ of $\alpha\oplus\beta$ in $\Hh^2(E^\bullet_G)$ is independent of the choice made above.
+It is also easy to see that $[\alpha\oplus\beta] = [\alpha_0\oplus\beta_0]$ when $\qcs{L} \iso \qcs{L}_0$,
+which concludes the definition of the function
+\begin{align*}
+S_G : \QCiso{G} &\to \Hh^2(E^\bullet_G)\\
+[\qcs{L}] &\mapsto [\alpha\oplus \beta].
+\end{align*}
+It is also easy to see that $[\alpha_1\oplus\beta_1] + [\alpha_2\oplus\beta_2] = [\alpha_3\oplus\beta_3]$ when $\qcs{L}_3 = \qcs{L}_1\otimes \qcs{L}_2$, so $S_G$ is a group homomorphism.
+
+\begin{remark}
+Although we will only use the group homomorphism $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an \'etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$.
+However, the next result is false in that context.
+\end{remark}
+
+\begin{proposition}\label{prop:SGiso}
+If $G$ is \'etale then $S_G$ is an isomorphism.
+\end{proposition}
+\begin{proof}
+Suppose $[\qcs{L}] \in \QCiso{G}$ with $S_G([\qcs{L}]) = [\alpha \oplus \beta] = 0$,
+so that $\alpha \oplus \beta = d\sigma$ for some $\sigma \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
+For each $x\in {\bar G}$, define $\sigma_x : \gqcs{L}_x \to \EE$ by $\sigma_x : v_x \mapsto \sigma(x)$.
+Then the indexed set of isomorphisms $\{ \sigma_x : \gqcs{L}_x \to \EE \tq x\in {\bar G}\}$
+defines an isomorphism $\qcs{L} \to (\EE)_G$.
+Since $\qcs{L} = 0 \in \QCiso{G}$, $S_G$ is injective.
+
+To see that $S_G$ is surjective, begin with $\alpha\oplus\beta\oplus 0 \in Z^2(E^\bullet_G)$.
+Since $d_{\Weil{}} \beta = 0$, we may define $a = \alpha \in C^2({\bar G},\EEx)$ and
+$b = \beta(\Frob{}) \in C^1({\bar G},\EEx)$, which are related to $\alpha$ and $\beta$ as above.
+Set $\gqcs{L}_x = \EE$, define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes\gqcs{L}_y$
+by $\mu_{x,y}(1) = a(x,y) (1\otimes 1)$ and $\phi_x : \gqcs{L}_{\Frob{G}(x)} \to \gqcs{L}_x$ by $\phi_x(1)= b(x)$.
+Then \ref{qc.1} holds since $d_G \alpha =0$ and \ref{qc.2} holds since $d_{\Weil{}}\alpha =d_G \beta$.
+Tracing the construction backward, we have defined a quasicharacter sheaf $\qcs{L}$ on $G$ with
+$S_G(\qcs{L}) = [\alpha\oplus\beta\oplus 0]$, showing that $S_G$ is surjective.
+\end{proof}
+
+\subsection{Objects in the \'etale case}\label{ssec:SandT}
+
+In this section we fit the group homomorphisms $\TrFrob{G}$ and $S_G$ into a commutative diagram, determining the kernel and cokernel of the homomorphism $\TrFrob{G} : \QCiso{G} \to G(k)^*$ when $G$ is an \'etale commutative group scheme over $\Fq$.
+
+%
+We begin with a simple, general result relating duals, invariants and coinvariants.
+
+\begin{lemma} \label{lem:dual-inv}
+Let $X$ be an abelian group equipped with an action of $\Weil{}$.  Then
+\begin{align*}
+ (X^*)_{\Weil{}} &\to (X^{\Weil{}})^* \\
+ [f] &\mapsto f|_{X^{\Weil{}}}
+\end{align*}
+is an isomorphism.
+\end{lemma}
+
+\begin{proof}
+We can describe $X^{\Weil{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
+let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
+\[
+ 0 \to X^{\Weil{}} \to X \to Y \to 0
+\]
+yields
+\[
+ 0 \to Y^* \to X^* \to (X^{\Weil{}})^* \to \Ext^1_\ZZ(Y, \EEx).
+\]
+Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Weil{}})^*$.
+\end{proof}
+
+\begin{proposition}\label{prop:sur_etale}
+If $G$ is \'etale, then $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is surjective
+and split.
+\end{proposition}
+\begin{proof}
+Pick $\chi \in G(\Fq)^*$. 
+Let $[\beta]\in \Hh^1(\Weil{},\bG^*)$ be the class corresponding to $\chi$ under Lemma~\ref{lem:dual-inv}.
+Every representative cocycle $\beta \in Z^1(\Weil{},\bG^*)$ determines a homomorphism $\beta(\Frob{}) : G(\bFq)\to \EEx$ such that $\beta(\Frob{})\vert_{G(\Fq)} = \chi$.
+Set $\gqcs{L}_x = \EE$ for every $x\in G(\bFq)$.
+Define $\mu_{x,y} : \gqcs{L}_{x+y} \to \gqcs{L}_x\otimes \gqcs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$ and
+$\phi_{x} : \gqcs{L}_{\Frob{}(x)} \to \gqcs{L}_x$ by $\phi_{x}(1) = \beta(\Frob{})(x)$.
+Since $\beta(\Frob{}) : G(\bFq) \to \EEx$ is a group homomorphism,
+condition \eqref{nohom} is satisfied with $a =1$.
+So $\qcs{L} = (\gqcs{L}, \mu, \phi)$
+is a quasicharacter sheaf with $\trFrob{\qcs{L}} = \chi$.
+This shows that $\TrFrob{G}$ is surjective.
+
+Now let $\beta' \in Z^1(\Weil{},\bG^*)$ be another representative for $[\beta]$
+so $\beta-\beta' = d_{\Weil{}} \delta$ for some $\delta \in C^0(\Weil{},\bG^*)$ defining $d \in \Hom(G(\bFq),\EEx)$.
+Let $\qcs{L}'$ be the quasicharacter sheaf on $G$ defined by $\beta'$, as above.
+For each $x\in G(\bFq)$, define $\brho_x :\qcs{L}_x\to \qcs{L}'_x$ by $\brho_x(1) = d(x)$.
+The collection of isomorphisms $\{ \brho_x \tq x\in G(\bFq)\}$ satisfies condition~\ref{qc.4}, so it defines a morphism $\rho : \qcs{L}\to \qcs{L}'$, which is clearly an isomorphism. 
+%
+We have now defined a section of $\TrFrob{G}$.
+
+Now suppose $\chi_1, \chi_2 \in G(\Fq)^*$.
+Pick cocycles $\beta_1,\beta_2\in Z^1(\Weil{},\bG^*)$ and construct quasicharacter sheaves $\qcs{L}_1$ and $\qcs{L}_2$ on $G$ as above.
+Since $\qcs{L}_1\otimes \qcs{L}_2$ is exactly the quasicharacter sheaf built from the cocycle $\beta_1\cdot \beta_2$, and since $\trFrob{\qcs{L}_1\otimes \qcs{L}_2} = \trFrob{\qcs{L}_1}\cdot \trFrob{\qcs{L}_2}$, the section of $\TrFrob{G}$ defined here is a homomorphism.
+\end{proof}
+
+\begin{proposition} \label{prop:etale-iso}
+ If $G$ is \'etale then the map $S_G : \QCiso{G}\to \Hh^2(E^\bullet_G)$ induces an isomorphism of split short exact sequences
+\[
+\begin{tikzcd}
+ 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \QCiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
+  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r} & 0.
+ \end{tikzcd}
+ \]
+\end{proposition}
+\begin{proof}
+This result follows from Propositions~\ref{prop:ses_desc}, \ref{prop:SGiso} and \ref{prop:sur_etale}.
+\end{proof}
+
+\subsection{Morphisms in the \'etale case}\label{ssec:mor-etale}
+
+While most of this paper focuses on the question of determining the isomorphism classes of objects, a complete understanding of the morphisms in $\QC(G)$ also requires a description of the automorphisms of an arbitrary quasicharacter sheaf $\qcs{L}$.
+
+\begin{proposition}\label{prop:autornaught_etale}
+Let $G$ be an \'etale commutative group scheme over $\Fq$.
+If $\qcs{L}$ and $\qcs{L}'$ are quasicharacter sheaves on $G$ then
+every $\rho\in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism. Moreover, the trace map induces an isomorphism of groups
+\[
+\Aut(\qcs{L}) \to \Hom(G(\bFq)_{\Weil{}}, \EEx).
+\]
+\end{proposition}
+
+\begin{proof}
+We have already seen, in Lemma~\ref{lem:autornaught}, that every $\rho\in \Hom(\qcs{L},\qcs{L}')$ is either trivial or an isomorphism.
+Now suppose $\rho \in \Aut(\qcs{L})$.
+The second diagram in \ref{qc.4} shows that the association $x \mapsto \brho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{qc.4} shows that it factors through $G(\bFq)_{\Weil{}}$.
+
+Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism, then defining $\brho_x$ as multiplication by $\rho(x)$ will define a morphism $\gqcs{L} \to \gqcs{L}'$ satisfy the two diagrams in \ref{qc.4}.
+
+Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the resulting bijection is actually a group isomorphism.
+\end{proof}
+
+\section{Quasicharacter sheaves on connected commutative algebraic groups} \label{sec:disc-isog}
+
+Before turning our attention to quasicharacter sheaves on connected commutative algebraic groups in Section~\ref{ssec:connected}, we treat two special classes of quasicharacter sheaves on arbitrary smooth commutative group schemes $G$:  in Section~\ref{ssec:descentG}, those that descend from local systems on $\bG$ to local systems on $G$; and in Section~\ref{ssec:discrete_isogenies}, those that are defined by discrete isogenies onto $G$.
 The latter will play a role in Sections~\ref{ssec:connected} and \ref{ssec:restriction}.
 
+\subsection{Descent to G}\label{ssec:descentG}
+
 In this section we consider a category of sheaves on $G$ obtained by
-replacing the Weil sheaf $(\gcs{L}, \phi)$ on $\bG$ in the definition of a character sheaf with an $\ell$-adic local system on $G$ itself.
+replacing the Weil sheaf $(\gqcs{L}, \phi)$ on $\bG$ in the definition of a quasicharacter sheaf with an $\ell$-adic local system on $G$ itself.
 
 \begin{definition}
-Let $\bCS(G)$ be the category of pairs $(\cs{E},\mu_\cs{E})$
-where $\cs{E}$ is an $\ell$-adic local system on $G$ of rank-one,
-equipped with an isomorphism $\mu_\cs{E} : m^* \cs{E} \to \cs{E} \boxtimes \cs{E}$
-satisfying the analogue of \ref{CS.2} on $G$;
-morphisms in $\bCS(G)$ are defined as in the second part of
-\ref{CS.4}. 
+Let $\bQC(G)$ be the category of pairs $(\qcs{E},\mu_\qcs{E})$
+where $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank-one,
+equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E} \boxtimes \qcs{E}$
+satisfying the analogue of \ref{QC.2} on $G$;
+morphisms in $\bQC(G)$ are defined as in the second part of
+\ref{QC.4}.
 \end{definition}
 
-We put a rigid monoidal structure on $\bCS(G)$ in the same way as for $\CS(G)$.
+We put a rigid monoidal structure on $\bQC(G)$ in the same way as for $\QC(G)$.
 
@@
 \[
-B_G : \bCS(G) \to \CS(G).
+B_G : \bQC(G) \to \QC(G).
 \]
@@
 \begin{proof}
- Suppose $(\cs{E},\mu_\cs{E})$ in an object of $\bCS(G)$.
+ Suppose $(\qcs{E},\mu_\qcs{E})$ in an object of $\bQC(G)$.
  Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Set $\gcs{L} = b_G^* \cs{E}$. 
+ Set $\gqcs{L} = b_G^* \qcs{E}$. 
  The functor $b_G^*$ takes local systems on $G$ to local systems on $\bG$.
- The local system $\gcs{L}$ comes equipped with an isomorphism
- $\phi: \Frob{G}^* \gcs{L} \to \gcs{L}$.
- The resulting functor from local systems on $G$ to Weil local systems on $\bG$, given on objects by $\cs{E} \mapsto (\gcs{L},\phi)$, 
+ The local system $\gqcs{L}$ comes equipped with an isomorphism
+ $\phi: \Frob{G}^* \gqcs{L} \to \gqcs{L}$.
+ The resulting functor from local systems on $G$ to Weil local systems on $\bG$, given on objects by $\qcs{E} \mapsto (\gqcs{L},\phi)$, 
  is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} and \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.2.1}.
- The isomorphism $\mu \ceq b_{G\times G}^*\mu_\cs{E}$ satisfies \ref{CS.2}
- for $\gcs{L}$ and $\phi$ is compatible with $\mu$ in the sense of \ref{CS.3}.
- This construction defines the functor $B_G : \bCS(G) \to \CS(G)$ given on objects by $(\cs{E},\mu_\cs{E}) \mapsto (\gcs{L},\mu, \phi)$, as defined here. 
- Because morphisms in $\bCS(G)$ and $\CS(G)$ are morphisms of local systems on $G$ and $\bG$, respectively, satisfying condition~\ref{CS.4}, this functor is also full and faithful.
-\end{proof}
-
-We will say that a character sheaf $\cs{L} \in \CS(G)$ \emph{descends to $G$} if it is isomorphic to some $B_G(\cs{E}, \mu_\cs{E})$.
+ The isomorphism $\mu \ceq b_{G\times G}^*\mu_\qcs{E}$ satisfies \ref{QC.2}
+ for $\gqcs{L}$ and $\phi$ is compatible with $\mu$ in the sense of \ref{QC.3}.
+ This construction defines the functor $B_G : \bQC(G) \to \QC(G)$ given on objects by $(\qcs{E},\mu_\qcs{E}) \mapsto (\gqcs{L},\mu, \phi)$, as defined here. 
+ Because morphisms in $\bQC(G)$ and $\QC(G)$ are morphisms of local systems on $G$ and $\bG$, respectively, satisfying condition~\ref{QC.4}, this functor is also full and faithful.
+\end{proof}
+
+We will say that a quasicharacter sheaf $\qcs{L} \in \QC(G)$ \emph{descends to $G$} if it is isomorphic to some $B_G(\qcs{E}, \mu_\qcs{E})$.
 
@@
 Let $\psi : A \to \EEx$ be the character of $V$.
-Then $(f_! V_H)_\psi$ (the $\psi$-isotypic component of $f_!V_H$) is an object of $\bCS(G)$.
+Then $(f_! V_H)_\psi$ (the $\psi$-isotypic component of $f_!V_H$) is an object of $\bQC(G)$.
 \end{proposition}
@@
 \begin{proof}
-Let $f$, $A$, $V$ and $\psi$ be as above and set $\cs{E} = (f_! V_H)_\psi$.
-Since $A$ is abelian, $\cs{E}$ is an $\ell$-adic local system on $G$ of rank one.
-We must show that $\cs{E}$ comes equipped with an isomorphism $\mu_\cs{E} : m^* \cs{E} \to \cs{E}\boxtimes\cs{E}$.
+Let $f$, $A$, $V$ and $\psi$ be as above and set $\qcs{E} = (f_! V_H)_\psi$.
+Since $A$ is abelian, $\qcs{E}$ is an $\ell$-adic local system on $G$ of rank one.
+We must show that $\qcs{E}$ comes equipped with an isomorphism $\mu_\qcs{E} : m^* \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
 To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$ {\it cf.\ } \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}.
-In particular, $f^*\cs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
-Since $f$ is a morphism of group schemes, the functor $f^*$ defines $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$
+In particular, $f^*\qcs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
+Since $f$ is a morphism of group schemes, the functor $f^*$ defines $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$
 from the isomorphism $m^*\psi \iso \psi \boxtimes\psi$ determined by $V\to V\otimes V$.
@@
 
-\subsection{The function-sheaf dictionary for connected algebraic groups over finite fields}\label{ssec:connected}
-
-In general, $\bCS(G)$ is an essentially
-proper subcategory of $\CS(G)$. 
+\subsection{The classical function-sheaf dictionary revisited}\label{ssec:connected}
+
+In general, $\bQC(G)$ is an essentially
+proper subcategory of $\QC(G)$. 
 However, if $G$ is connected and of finite type, the categories are equivalent, as we now show.
@@
 \[
-B_G : \bCS(G) \to \CS(G)
+B_G : \bQC(G) \to \QC(G)
 \]
@@
 
-  Now let $(\gcs{L},\mu,\phi)$ be a character sheaf on $G$
-  and let $\lambda : \Weil{}(G, \bg) \to \EEx$ be the character determined by $(\gcs{L},\phi)$.
+  Now let $(\gqcs{L},\mu,\phi)$ be a quasicharacter sheaf on $G$
+  and let $\lambda : \Weil{}(G, \bg) \to \EEx$ be the character determined by $(\gqcs{L},\phi)$.
   Composing with the splitting $\Weil{} \to \Weil{}(G,\bg)$ yields an $\ell$-adic character
@@
   $
-  \lambda_g(\Frob{}) =  \trFrob{\cs{L}}(g).
+  \lambda_g(\Frob{}) =  \trFrob{\qcs{L}}(g).
   $
 %
-  On the other hand, we have already seen that $\trFrob{\cs{L}} : G(\Fq) \to \EEx$
+  On the other hand, we have already seen that $\trFrob{\qcs{L}} : G(\Fq) \to \EEx$
   is a group homomorphism. 
   Since $G$ is an algebraic group over $\Fq$, $G(\Fq)$ is finite.
-  Therefore $\trFrob{\cs{L}}(g) = \lambda_g(\Frob{})$ is a root of unity
+  Therefore $\trFrob{\qcs{L}}(g) = \lambda_g(\Frob{})$ is a root of unity
   for every $g\in G(\Fq)$.  Since $\Weil{}$ is generated by
@@
   representations of $\pi_1(G,\bg)$ and $\ell$-adic local systems on $G$. Let
-  $\cs{E}$ be a local system on $G$ in the isomorphism class
+  $\qcs{E}$ be a local system on $G$ in the isomorphism class
   determined by this $\ell$-adic character of $\pi_1(G,\bg)$.
-  Then $b_G^*\cs{E} \iso \gcs{L}$.
+  Then $b_G^*\qcs{E} \iso \gqcs{L}$.
 
@@
  \[
-  b_{G\times G}^* : \Hom(m^*\cs{E},\cs{E}\boxtimes\cs{E}) \to \Hom({\bar m}^*\gcs{L},\gcs{L}\boxtimes\gcs{L})
+  b_{G\times G}^* : \Hom(m^*\qcs{E},\qcs{E}\boxtimes\qcs{E}) \to \Hom({\bar m}^*\gqcs{L},\gqcs{L}\boxtimes\gqcs{L})
  \]
@@
   in which $\ell$-adic local systems sit as full subcategories).
-  Let $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ be the isomorphism matching
-  $\mu : {\bar m}^*\gcs{L} \to \gcs{L}\boxtimes\gcs{L}$,
-  the latter appearing in the definition of $\cs{L}$.
-  Then, as in Section~\ref{ssec:descentG}, $(\cs{E},\mu_\cs{E})$ is an object of $\bCS(G)$
-  and $\cs{L} \ceq (\gcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\cs{E},b_{G\times G}^*\mu_\cs{E})$ in $\CS(G)$.
-  Thus, the full and faithful functor $B_G : \bCS(G) \to \CS(G)$ from Section~\ref{ssec:descentG}
+  Let $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ be the isomorphism matching
+  $\mu : {\bar m}^*\gqcs{L} \to \gqcs{L}\boxtimes\gqcs{L}$,
+  the latter appearing in the definition of $\qcs{L}$.
+  Then, as in Section~\ref{ssec:descentG}, $(\qcs{E},\mu_\qcs{E})$ is an object of $\bQC(G)$
+  and $\qcs{L} \ceq (\gqcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\qcs{E},b_{G\times G}^*\mu_\qcs{E})$ in $\QC(G)$.
+  Thus, the full and faithful functor $B_G : \bQC(G) \to \QC(G)$ from Section~\ref{ssec:descentG}
   is also essentially surjective, hence an equivalence.
@@
 
-Using this equivalence of categories, we may give a good description of $\CS(G)$ when $G$ is connected and finite type.
+Using this equivalence of categories, we may give a good description of $\QC(G)$ when $G$ is connected and finite type.
 
@@
  \begin{enumerate}
- \labitem{(1)}{c1} $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ is an isomorphism of groups;
- \labitem{(2)}{c2} every character sheaf on $G$ is isomorphic to one defined by a discrete isogeny;
- \labitem{(3)}{c3} $\Aut(\cs{L}) = 1$, for all character sheaves $\cs{L}$ on $G$.
+ \item $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is an isomorphism of groups;
+ \item every quasicharacter sheaf on $G$ is isomorphic to one defined by a discrete isogeny;
+ \item $\Aut(\qcs{L}) = 1$, for all quasicharacter sheaves $\qcs{L}$ on $G$.
  \end{enumerate}
@@
 \begin{proof}
-In Lemma~\ref{lem:bounded_connected}, we saw that every character sheaf $\cs{L}$ on $\bG$ descends to $G$; let $\cs{E}$ be an object of $\bCS(G)$ for which $B_G(\cs{E}) \iso \cs{L}$.
- Since the functor $B_G : \bCS(G) \to \CS(G)$ is full and faithful, $\Aut(\cs{L}) = \Aut(\cs{E})$.
+In Lemma~\ref{lem:bounded_connected}, we saw that every quasicharacter sheaf $\qcs{L}$ on $\bG$ descends to $G$; let $\qcs{E}$ be an object of $\bQC(G)$ for which $B_G(\qcs{E}) \iso \qcs{L}$.
+ Since the functor $B_G : \bQC(G) \to \QC(G)$ is full and faithful, $\Aut(\qcs{L}) = \Aut(\qcs{E})$.
 From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields, as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3}, gives us all we need, as we briefly recall.
@@
 As in the proof of Proposition~\ref{prop:finite}, use \'etale descent to see that pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.
-Under this equivalence, local systems $\cs{E}$ on $G$ arising from objects in $\bCS(G)$ are matched with $G(\Fq)$-equivariant constant local systems of rank-one on $G$, and therefore with one-dimensional representations of $G(\Fq)$.
-In the same way, pullback along the isogeny $\Lang\times\Lang : G\times G\to G\times G$ matches the extra structure $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ with an isomorphism $m^*V \to V\boxtimes V$ of one-dimensional representations of $G(\Fq)\times G(\Fq)$, which is exactly an isomorphism $V \to V\otimes V$ of one-dimensional representations, which is exactly the choice of an isomorphism $V\iso \EE$.
-We see that $\bCS(G)$ is equivalent to the category of characters of $G(\Fq)$.
+Under this equivalence, local systems $\qcs{E}$ on $G$ arising from objects in $\bQC(G)$ are matched with $G(\Fq)$-equivariant constant local systems of rank-one on $G$, and therefore with one-dimensional representations of $G(\Fq)$.
+In the same way, pullback along the isogeny $\Lang\times\Lang : G\times G\to G\times G$ matches the extra structure $\mu_\qcs{E} : m^*\qcs{E} \to \qcs{E}\boxtimes\qcs{E}$ with an isomorphism $m^*V \to V\boxtimes V$ of one-dimensional representations of $G(\Fq)\times G(\Fq)$, which is exactly an isomorphism $V \to V\otimes V$ of one-dimensional representations, which is exactly the choice of an isomorphism $V\iso \EE$.
+We see that $\bQC(G)$ is equivalent to the category of characters of $G(\Fq)$.
 Let $\bg$ be a geometric point above $g \in G(\Fq)$.
-If $\cs{E}$ matches $\psi : G(\Fq)\to \EEx$ under this equivalence, a simple calculation on stalks reveals that the action of Frobenius on $\cs{E}_{\bar g}$ is multiplication by $\psi(g)^{-1}$.
-In other words, for every $\cs{E}$ in $\bCS(G)$, the trace of $\Lang^*\cs{E}$ is $\trFrob{\cs{E}}^{-1}$ as a representation of $G(\Fq)$, proving parts \ref{c1} and \ref{c2}.
-
-To finish the proof of part \ref{c3}, suppose $\Lang^*\cs{E} = V$ with isomorphism $V \to V\otimes V$.
-Observe that the equivalence above establishes a bijection between $\Aut(\cs{E})$ and the group of automorphisms of $\rho : V\to V$ for which
+If $\qcs{E}$ matches $\psi : G(\Fq)\to \EEx$ under this equivalence, a simple calculation on stalks reveals that the action of Frobenius on $\qcs{E}_{\bar g}$ is multiplication by $\psi(g)^{-1}$.
+In other words, for every $\qcs{E}$ in $\bQC(G)$, the trace of $\Lang^*\qcs{E}$ is $\trFrob{\qcs{E}}^{-1}$ as a representation of $G(\Fq)$, proving parts (i) and (ii).
+
+To finish the proof of part (iii), suppose $\Lang^*\qcs{E} = V$ with isomorphism $V \to V\otimes V$.
+Observe that the equivalence above establishes a bijection between $\Aut(\qcs{E})$ and the group of automorphisms of $\rho : V\to V$ for which
 \[
@@
 commutes. 
-Since the only such isomorphism $\rho$ is $\id_V$, it follows that $\Aut(\cs{E}) = 1$, completing the proof.
-\end{proof}
-
-We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of character sheaves on $G$ is equivalent to the category of one-dimensional representations $V$ of $G(\Fq)$ equipped with an isomorphism $V\iso \EE$, and therefore equivalent to the category of characters $\psi$ of $G(\Fq)$.
-We have also just seen that if the character of $\Lang^*\cs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\cs{E} : \cs{E} \to \cs{E}\boxtimes\cs{E}$.
-This fact leads (back) to a perspective on the function-sheaf dictionary common in the literature in which one considers one-dimensional local systems $\cs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\cs{E} \iso \cs{E} \boxtimes\cs{E}$ \cite{kamgarpour:09a}*{Intro}.
-As a slight variation, one may also consider one-dimensional local systems $\gcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gcs{L} \iso \gcs{L}$ and an isomorphism $\bm^*\gcs{L} \iso \gcs{L} \boxtimes\gcs{L}$.
-
-Although the category $\CS(G)$ of character sheaves on $G$ specializes to $\bCS(G)$ when $G$ is connected and of finite type, this description is \emph{not} sufficient when extending the dictionary to smooth commutative group schemes, as we will see already in Section~\ref{sec:etale}.
-In particular, for a given $\gcs{L}$ and $\phi$ there may be many $\mu$ so that $(\gcs{L},\mu,\phi)$ is a character sheaf.
+Since the only such isomorphism $\rho$ is $\id_V$, it follows that $\Aut(\qcs{E}) = 1$, completing the proof.
+\end{proof}
+
+We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of quasicharacter sheaves on $G$ is equivalent to the category of one-dimensional representations $V$ of $G(\Fq)$ equipped with an isomorphism $V\iso \EE$, and therefore equivalent to the category of characters $\psi$ of $G(\Fq)$.
+We have also just seen that if the character of $\Lang^*\qcs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\qcs{E} : \qcs{E} \to \qcs{E}\boxtimes\qcs{E}$.
+This fact leads to a perspective on the function-sheaf dictionary common in the literature in which one considers one-dimensional local systems $\qcs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\qcs{E} \iso \qcs{E} \boxtimes\qcs{E}$ \cite{kamgarpour:09a}*{Intro}.
+As a slight variation, one may also consider one-dimensional local systems $\gqcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gqcs{L} \iso \gqcs{L}$ and an isomorphism $\bm^*\gqcs{L} \iso \gqcs{L} \boxtimes\gqcs{L}$.
+
+Although the category of quasicharacter sheaves on $G$ specializes to the one described above when $G$ is connected and of finite type, this description is not sufficient when extending the dictionary to smooth commutative group schemes.
+In particular, for a given $\gqcs{L}$ and $\phi$ there may be many $\mu$ so that $(\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf.
 For \'etale $G$, Proposition~\ref{prop:etale-iso} shows that $\Hh^2(\bG,\EEx)^{\Weil{}}$ measures the possibilities for $\mu$.
 We will see in Section~\ref{sec:main} that $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ plays an analogous role for general smooth commutative group schemes $G$.
-
-\subsection{Examples}
-
-\section{Character sheaves on \'etale commutative group schemes} \label{sec:etale}
-
-In this section we find a complete characterization of the category of character sheaves on \'etale commutative group schemes over finite fields.
-
-\subsection{Stalks of character sheaves}\label{ssec:stalks}
-
-The equivalence $G \mapsto G(\bFq)$,
-from the category of \'etale commutative group schemes over $\Fq$ to the category of commutative groups equipped
-with a continuous action of $\Gal(\bFq/\Fq)$,
-provides the following simple description of character sheaves.
-%
-A character sheaf $\cs{L}$ on an \'etale commutative group scheme $G$ over $\Fq$ is:
-\begin{enumerate}
- \labitem{(cs.1)}{cs.1} an indexed set of one-dimensional
-  $\EE$-vector spaces $\gcs{L}_x$, as $x$ runs over
-  $G(\bFq)$;
-
- \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms
-  $\mu_{x,y} : \gcs{L}_{x+y} \xrightarrow{\iso} \gcs{L}_{x} \otimes\gcs{L}_{y}$,
-  for all $x,y \in G(\bFq)$, such that
-  \[
-   \begin{tikzcd}[row sep=40]
-    \gcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
-    && \gcs{L}_{x+y}\otimes\gcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
-    \gcs{L}_{x} \otimes\gcs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
-    && \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes\gcs{L}_{z}
-   \end{tikzcd}
-  \]
-  commutes, for all $x,y,z\in G(\bFq)$; and
- \labitem{(cs.3)}{cs.3} an indexed set of isomorphisms $\phi_{x} : \gcs{L}_{\Frob{}(x)} \to \gcs{L}_x$
-  such that
-  \[
-   \begin{tikzcd}[row sep=40]
-    \gcs{L}_{\Frob{}(x)+\Frob{}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{}(x),\Frob{}(y)}}
-    && \gcs{L}_{\Frob{}(x)}\otimes\gcs{L}_{\Frob{}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
-    \gcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
-    && \gcs{L}_x \otimes\gcs{L}_y
-   \end{tikzcd}
-  \]
-  commutes, for all $x,y\in G(\bFq)$.
-\end{enumerate}
-Under this equivalence, a morphism $\rho : \cs{L} \to \cs{L'}$ of character sheaves on $G$ is given by
-\begin{enumerate}
- \labitem{(cs.4)}{cs.4} an indexed set $\brho_x : \gcs{L}_x \to \gcs{L'}_x$
-  of linear transformations such that
-  \[
-   \begin{tikzcd}[column sep=40]
-    \arrow[swap]{d}{\phi_x} \gcs{L}_{\Frob{}(x)} \rar{\brho_{\Frob{}(x)}} & \gcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
-    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-    & \arrow[swap]{d}{\mu_{x,y}} \gcs{L}_{x+y} \rar{\brho_{x+y}} & \gcs{L'}_{x+y} \dar{\mu'_{x,y}} \\
-    \gcs{L}_x \rar{\brho_x} & \gcs{L'}_x
-    & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\brho_x\otimes\brho_y} & \gcs{L'}_x \otimes\gcs{L'}_y
-   \end{tikzcd}
-  \]
-  both commute, for all $x, y \in G(\bFq)$.
-\end{enumerate}
-
-We will see that $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ may not provide complete
-information about isomorphism classes of character sheaves on $G$ when $G$ is not a connected algebraic group.
-Our main tool for understanding this phenomenon
-is a group homomorphism $S_G: \CSiso{G} \to \Hh^2(E^\bullet_G)$ defined in Section~\ref{ssec:S}, for which the next two sections are preparation.
-
-\subsection{A spectral sequence}\label{ssec:E}
-
-The zeroth page of the Hochschild-Serre spectral sequence
-is a double complex $E^{\bullet, \bullet}$ defined by
-\[
-E^{i,j} = C^i(\Weil{}, C^j(G(\bFq), \EEx));
-\]
-see \cite{vakil:Algebraic_Geometry}*{\S 1.7}, expanding on \cite{weibel:Homological_Algebra}*{Ch 5 and \S 7.5}.
-The standard derivative on cochains yields two derivatives,
-\begin{align*}
-d_G &: E^{i,j} \to E^{i,j+1} \quad \mbox{and} \\
-d_{\Weil{}} &: E^{i,j} \to E^{i+1,j};
-\end{align*}
-we use the first as the derivative $d_0$ on the zeroth page, and the second to induce $d_1$.
-Combining them also yields a derivative $d = d_G + (-1)^j d_{\Weil{}}$ on the total complex
-\[
-E^n_G = \bigoplus_{i+j=n} E^{i,j}.
-\]
-The machinery of spectral sequences gives us a sequence of pages $E_r^{i,j}$, converging to a page $E_{\infty}^{i,j}$.
-We summarize the key properties of this spectral sequence in the following proposition.
-
-\begin{proposition} In the spectral sequence defined above,
-\begin{enumerate}
-\item the second page is given by $E_2^{i,j} = \Hh^i(\Weil{}, \Hh^j(G(\bFq), \EEx))$,
-\item there is an isomorphism $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) \cong \Hh^n(E_G^\bullet)$, and
-\item there is a filtration $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) = F_n \supset \cdots \supset F_{-1} = 0$, with $F_i / F_{i-1} \cong E_{\infty}^{i, n-i}$.
-\end{enumerate}
-\end{proposition}
-
-Moreover, since $\Weil{} \cong \ZZ$ has cohomological dimension $1$, $E_2^{i,j} = 0$ for $i > 1$ and the sequence degenerates at the second page: $E_{\infty}^{i,j} = E_2^{i,j}$.
-We obtain the following corollary:
-
-\begin{corollary}\label{cor:spectral_ses}
-There is a short exact sequence
- \[
-    0 \to
-    \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to
-    \Hh^2(E^\bullet_G) \to
-    \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to
-    0.
- \]
-\end{corollary}
-
-This sequence will play a key role in understanding the kernel of $\TrFrob{G}$, as described in the next few sections.
-For this application, we need a good understanding of these maps to and from the total complex.
-
-\begin{proposition} \label{prop:ses_desc}
-Consider the short exact sequence in Corollary~\ref{cor:spectral_ses}.
-\begin{enumerate}
-\item Every class $[\alpha\oplus\beta\oplus\gamma] \in \Hh^2(E^\bullet_G)$ is cohomologous to one with $\gamma=0$.
-\item The map $\Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx))$ is given by $[\alpha\oplus\beta\oplus 0] \mapsto [\beta]$.
-\item Suppose $a \in Z^2({\bar G}, \EEx)$ represents a class in $\Hh^2({\bar G},\EEx)$ fixed by Frobenius.
-The map $\Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to \Hh^2(E^\bullet_G)$ is given by $[a] \mapsto [a \oplus 0 \oplus 0]$.
-\end{enumerate}
-\end{proposition}
-\begin{proof}
-Since $\Hh^2(\Weil{}, C^0({\bar G}, \EEx)) = 0$, we may find a $\gamma_1 \in C^1(\Weil{}, C^0({\bar G}, \EEx))$ with $d_{\Weil{}}\gamma_1 = \gamma$.
-Subtracting $d \gamma_1$ from $\alpha\oplus\beta\oplus\gamma$, we may assume that $\gamma = 0$.
-
-The latter two claims follow from tracing through the definition of latter pages in the spectral sequence.
-\end{proof}
-
-\subsection{From character sheaves to the total complex}\label{ssec:S}
-
-In this section we define an isomorphism
-\[
-S_G : \CSiso{G} \to \Hh^2(E^\bullet_G).
-\]
-Let $\cs{L} = (\gcs{L},\mu,\phi)$ be a character sheaf on $G$.
-For each geometric point $x\in {\bar G}$, choose a basis $\{ v_x \}$ for $\gcs{L}_x$.
-Through this choice, $\cs{L}$ determines functions
-\begin{align*}
-a : {\bar G}\times {\bar G} &\to \EEx & b : {\bar G} &\to \EEx \\
-\mu_{x,y}(v_{x+y}) &= a(x,y) v_x \otimes v_y & \phi_x(v_{\Frob{G}(x)}) &= b(x) v_x.
-\end{align*}
-Condition~\ref{CS.2} implies that
-\begin{equation}\label{2-cocyle}
-a(x+y,z) a(x,y) = a(x,y+z) a(y,z)
-\end{equation}
-for all $x,y,z\in {\bar G}$, so $a \in Z^2({\bar G},\EEx)$.  Similarly, condition~\ref{CS.3} gives
-\begin{equation}\label{nohom}
-\frac{a(\Frob{G}(x),\Frob{G}(y))}{a(x,y)} =  \frac{b(x+y)}{b(x) b(y)}
-\end{equation}
-for $x, y \in {\bar G}$.
-Let $\alpha \in C^0(\Weil{},C^2({\bar G},\EEx)$ be the $0$-cochain corresponding to $a$ and let $\beta\in C^1(\Weil{},C^1({\bar G},\EEx)$ be the cocycle such that $\beta(\Frob{})$ is $b$.
-We will write both $\alpha$ and $\beta$ additively.
-Then
-\[
-d_G\alpha =0, \qquad\qquad
-d_{\Weil{}} \alpha = d_{G} \beta,\qquad\qquad
-d_{\Weil{}} \beta =0;
-\]
-in other words,
-\[\alpha\oplus \beta \in Z^2(E^\bullet_G).\]
-Although the cocycle $\alpha\oplus \beta$ is not well defined by $\cs{L}$, its class in $\Hh^2(E^\bullet_G)$ is.
-To see this, let $\{ v'_x \in \gcs{L}_x^\times \tq x \in {\bar G}\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$ be defined by $\cs{L}$ and this choice, as above.
-Now let $\delta \in C^0(\Weil{},C^1({\bar G},\EEx))$ correspond to the function $d : {\bar G}\to \EEx$ defined by $v'_x = d(x) v_x$.
-Chasing through \ref{CS.2} and \ref{CS.3}, we find
-\[
-\alpha'\oplus\beta' = \alpha\oplus\beta + d\delta,
-\]
-so the class $[\alpha\oplus\beta]$ of $\alpha\oplus\beta$ in $\Hh^2(E^\bullet_G)$ is independent of the choice made above.
-It is also easy to see that $[\alpha\oplus\beta] = [\alpha_0\oplus\beta_0]$ when $\cs{L} \iso \cs{L}_0$,
-which concludes the definition of the function
-\begin{align*}
-S_G : \CSiso{G} &\to \Hh^2(E^\bullet_G)\\
-[\cs{L}] &\mapsto [\alpha\oplus \beta].
-\end{align*}
-It is also easy to see that $[\alpha_1\oplus\beta_1] + [\alpha_2\oplus\beta_2] = [\alpha_3\oplus\beta_3]$ when $\cs{L}_3 = \cs{L}_1\otimes \cs{L}_2$, so $S_G$ is a group homomorphism.
-
-\begin{remark}
-Although we will only use the group homomorphism $S_G : \CSiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an \'etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$;
-however, the next result does not extend to all smooth commutative group schemes.
-\end{remark}
-
-\begin{proposition}\label{prop:SGiso}
-If $G$ is \'etale then $S_G$ is an isomorphism.
-\end{proposition}
-\begin{proof}
-Suppose $[\cs{L}] \in \CSiso{G}$ with $S_G([\cs{L}]) = [\alpha \oplus \beta] = 0$,
-so that $\alpha \oplus \beta = d\sigma$ for some $\sigma \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
-For each $x\in {\bar G}$, define $\sigma_x : \gcs{L}_x \to \EE$ by $\sigma_x : v_x \mapsto \sigma(x)$.
-Then the indexed set of isomorphisms $\{ \sigma_x : \gcs{L}_x \to \EE \tq x\in {\bar G}\}$
-defines an isomorphism $\cs{L} \to (\EE)_G$.
-Since $\cs{L} = 0 \in \CSiso{G}$, $S_G$ is injective.
-
-To see that $S_G$ is surjective, begin with $\alpha\oplus\beta\oplus 0 \in Z^2(E^\bullet_G)$.
-Since $d_{\Weil{}} \beta = 0$, we may define $a = \alpha \in C^2({\bar G},\EEx)$ and
-$b = \beta(\Frob{}) \in C^1({\bar G},\EEx)$, which are related to $\alpha$ and $\beta$ as above.
-Set $\gcs{L}_x = \EE$, define $\mu_{x,y} : \gcs{L}_{x+y} \to \gcs{L}_x\otimes\gcs{L}_y$
-by $\mu_{x,y}(1) = a(x,y) (1\otimes 1)$ and $\phi_x : \gcs{L}_{\Frob{G}(x)} \to \gcs{L}_x$ by $\phi_x(1)= b(x)$.
-Then \ref{CS.1} holds since $d_G \alpha =0$ and \ref{CS.2} holds since $d_{\Weil{}}\alpha =d_G \beta$.
-Tracing the construction backward, we have defined a character sheaf $\cs{L}$ on $G$ with
-$S_G(\cs{L}) = [\alpha\oplus\beta\oplus 0]$, showing that $S_G$ is surjective.
-\end{proof}
-
-\subsection{Objects in the \'etale case}\label{ssec:SandT}
-
-In this section we fit the group homomorphisms $\TrFrob{G}$ and $S_G$ into a commutative diagram, determining the kernel and cokernel of the homomorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$ when $G$ is an \'etale commutative group scheme over $\Fq$.
-
-%
-We begin with a simple, general result relating duals, invariants and coinvariants.
-
-\begin{lemma} \label{lem:dual-inv}
-Let $X$ be an abelian group equipped with an action of $\Weil{}$.  Then
-\begin{align*}
- (X^*)_{\Weil{}} &\to (X^{\Weil{}})^* \\
- [f] &\mapsto f|_{X^{\Weil{}}}
-\end{align*}
-is an isomorphism.
-\end{lemma}
-
-\begin{proof}
-We can describe $X^{\Weil{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
-let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
-\[
- 0 \to X^{\Weil{}} \to X \to Y \to 0
-\]
-yields
-\[
- 0 \to Y^* \to X^* \to (X^{\Weil{}})^* \to \Ext^1_\ZZ(Y, \EEx).
-\]
-Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Weil{}})^*$.
-\end{proof}
-
-\begin{proposition}\label{prop:sur_etale}
-If $G$ is \'etale, then $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ is surjective
-and split.
-\end{proposition}
-\begin{proof}
-Pick $\chi \in G(\Fq)^*$. 
-Let $[\beta]\in \Hh^1(\Weil{},\bG^*)$ be the class corresponding to $\chi$ under Lemma~\ref{lem:dual-inv}.
-Every representative cocycle $\beta \in Z^1(\Weil{},\bG^*)$ determines a homomorphism $\beta(\Frob{}) : G(\bFq)\to \EEx$ such that $\beta(\Frob{})\vert_{G(\Fq)} = \chi$.
-Set $\gcs{L}_x = \EE$ for every $x\in G(\bFq)$.
-Define $\mu_{x,y} : \gcs{L}_{x+y} \to \gcs{L}_x\otimes \gcs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$ and
-$\phi_{x} : \gcs{L}_{\Frob{}(x)} \to \gcs{L}_x$ by $\phi_{x}(1) = \beta(\Frob{})(x)$.
-Since $\beta(\Frob{}) : G(\bFq) \to \EEx$ is a group homomorphism,
-condition \eqref{nohom} is satisfied with $a =1$.
-So $\cs{L} = (\gcs{L}, \mu, \phi)$
-is a character sheaf with $\trFrob{\cs{L}} = \chi$.
-This shows that $\TrFrob{G}$ is surjective.
-
-Now let $\beta' \in Z^1(\Weil{},\bG^*)$ be another representative for $[\beta]$
-so $\beta-\beta' = d_{\Weil{}} \delta$ for some $\delta \in C^0(\Weil{},\bG^*)$ defining $d \in \Hom(G(\bFq),\EEx)$.
-Let $\cs{L}'$ be the character sheaf on $G$ defined by $\beta'$, as above.
-For each $x\in G(\bFq)$, define $\brho_x :\cs{L}_x\to \cs{L}'_x$ by $\brho_x(1) = d(x)$.
-The collection of isomorphisms $\{ \brho_x \tq x\in G(\bFq)\}$ satisfies condition~\ref{CS.4}, so it defines a morphism $\rho : \cs{L}\to \cs{L}'$, which is clearly an isomorphism. 
-%
-We have now defined a section of $\TrFrob{G}$.
-
-Now suppose $\chi_1, \chi_2 \in G(\Fq)^*$.
-Pick cocycles $\beta_1,\beta_2\in Z^1(\Weil{},\bG^*)$ and construct character sheaves $\cs{L}_1$ and $\cs{L}_2$ on $G$ as above.
-Since $\cs{L}_1\otimes \cs{L}_2$ is exactly the character sheaf built from the cocycle $\beta_1\cdot \beta_2$, and since $\trFrob{\cs{L}_1\otimes \cs{L}_2} = \trFrob{\cs{L}_1}\cdot \trFrob{\cs{L}_2}$, the section of $\TrFrob{G}$ defined here is a homomorphism.
-\end{proof}
-
-\begin{proposition} \label{prop:etale-iso}
- If $G$ is \'etale then the map $S_G : \CSiso{G}\to \Hh^2(E^\bullet_G)$ induces an isomorphism of split short exact sequences
-\[
-\begin{tikzcd}
- 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \CSiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
-  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r} & 0.
- \end{tikzcd}
- \]
-\end{proposition}
-\begin{proof}
-This result follows from Propositions~\ref{prop:ses_desc}, \ref{prop:SGiso} and \ref{prop:sur_etale}.
-\end{proof}
-
-The image of
-
-\subsection{Morphisms in the \'etale case}\label{ssec:mor-etale}
-
-While most of this paper focuses on the question of determining the isomorphism classes of objects, a complete understanding of the morphisms in $\CS(G)$ also requires a description of the automorphisms of an arbitrary character sheaf $\cs{L}$.
-
-\begin{proposition}\label{prop:autornaught_etale}
-Let $G$ be an \'etale commutative group scheme over $\Fq$.
-If $\cs{L}$ and $\cs{L}'$ are character sheaves on $G$ then
-every $\rho\in \Hom(\cs{L},\cs{L}')$ is either trivial or an isomorphism. Moreover, the trace map induces an isomorphism of groups
-\[
-\Aut(\cs{L}) \to \Hom(G(\bFq)_{\Weil{}}, \EEx).
-\]
-\end{proposition}
-
-\begin{proof}
-We have already seen, in Lemma~\ref{lem:autornaught}, that every $\rho\in \Hom(\cs{L},\cs{L}')$ is either trivial or an isomorphism.
-Now suppose $\rho \in \Aut(\cs{L})$.
-The second diagram in \ref{CS.4} shows that the association $x \mapsto \brho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{CS.4} shows that it factors through $G(\bFq)_{\Weil{}}$.
-
-Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism, then defining $\brho_x$ as multiplication by $\rho(x)$ will define a morphism $\gcs{L} \to \gcs{L}'$ satisfy the two diagrams in \ref{CS.4}.
-
-Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the resulting bijection is actually a group isomorphism.
-\end{proof}
-
-\subsection{Examples}
-
-Let $G$ be the etale group scheme $\ZZ$ over $\Fq$ and consider the character $\chi : \ZZ \to \EEx$ of $G(\Fq)$ determined by $\chi(1) = 1+\ell$.
-The stalk of $\cs{L}$ at the component $1$ is defined
-by a pro-\'etale cover  . . .
 
@@
 \begin{tikzcd}
-\CS(0) \rar & \CS(\pi_0(G)) \arrow{r}{\pi_0^*} & \CS(G) \arrow{r}{\iota_0^*} & \CS(G^0) \rar & \CS(0)
+\QC(0) \rar & \QC(\pi_0(G)) \arrow{r}{\pi_0^*} & \QC(G) \arrow{r}{\iota_0^*} & \QC(G^0) \rar & \QC(0)
 \end{tikzcd}
@@
 0 \rar &
-\CSiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \CSiso{G} \arrow{r}{\iota_0^*} & \CSiso{G^0} \rar & 0.
+\QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
 \end{tikzcd}
 \end{equation}
- Note that we found the groups $\CSiso{\pi_0(G)}$ and $\CSiso{G^0}$
+ Note that we found the groups $\QCiso{\pi_0(G)}$ and $\QCiso{G^0}$
 in Sections~\ref{ssec:SandT} and \ref{ssec:connected}, respectively.
@@
   \begin{tikzcd}
-  A \arrow{r} \dar & A \dar \\
+  A \arrow[equal]{r} \dar & A \dar \\
   B \rar \dar[swap]{\pi} & H \rar \dar[swap]{f} & \pi_0(H) \arrow{d}[below,rotate=90]{\sim}[swap]{\pi_0(f)} \\
@@
 \begin{proposition}\label{prop:restriction}
-The restriction functor $\iota_0^* : \CS(G)\to \CS(G^0)$ is essentially surjective.
+The restriction functor $\iota_0^* : \QC(G)\to \QC(G^0)$ is essentially surjective.
 \end{proposition}
@@
   By Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}, every
-  character sheaf on $G^0$ is isomorphic to $(\pi_! \EE)_\psi$ for some discrete isogeny $\pi : B \to G^0$ and character $\psi : \ker \pi \to \EEx$.
-  So to prove the proposition it suffices to show that $(\pi_! \EE)_\psi$ extends to a character sheaf on $G$.
+  quasicharacter sheaf on $G^0$ is isomorphic to $(\pi_! \EE)_\psi$ for some discrete isogeny $\pi : B \to G^0$ and character $\psi : \ker \pi \to \EEx$.
+  So to prove the proposition it suffices to show that $(\pi_! \EE)_\psi$ extends to a quasicharacter sheaf on $G$.
 %
@@
  such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
- Then $(f_! \EE)_\psi$ is a character sheaf on $G$ and
+ Then $(f_! \EE)_\psi$ is a quasicharacter sheaf on $G$ and
  $(f_! \EE)_\psi\vert_{G^0} \iso (\pi_! \EE)_\psi$.
@@
 \begin{lemma}\label{lem:extension}
-The group homomorphism $\pi_0^*: \CSiso{\pi_0(G)} \to \CSiso{G}$ is injective.
+The group homomorphism $\pi_0^*: \QCiso{\pi_0(G)} \to \QCiso{G}$ is injective.
 \end{lemma}
 \begin{proof}
-Let $\cs{L}$ be a character sheaf on $\pi_0(G)$ and let $\rho : \pi_0^*\cs{L} \to (\EE)_{G}$ be an isomorphism in $\CS(G)$. 
+Let $\qcs{L}$ be a quasicharacter sheaf on $\pi_0(G)$ and let $\rho : \pi_0^*\qcs{L} \to (\EE)_{G}$ be an isomorphism in $\QC(G)$. 
 For each $x\in \pi_0(\bG)$, set $\bG^x \ceq \pi_0^{-1}(x)$.
-The restriction $\pi_0^*\gcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gcs{L}_x)_{\bG^x}$ so the isomorphism $\brho\vert_{\bG^x} : (\gcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gcs{L}_x \to (\EE)_x$.
-The collection $\{ \brho_x \tq x\in \pi_0(\bG) \}$ determines an isomorphism $\cs{L} \to (\EE)_{\pi_0(G)}$  in $\CS(\pi_0(G))$.
+The restriction $\pi_0^*\gqcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gqcs{L}_x)_{\bG^x}$ so the isomorphism $\brho\vert_{\bG^x} : (\gqcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gqcs{L}_x \to (\EE)_x$.
+The collection $\{ \brho_x \tq x\in \pi_0(\bG) \}$ determines an isomorphism $\qcs{L} \to (\EE)_{\pi_0(G)}$  in $\QC(\pi_0(G))$.
 \end{proof}
@@
   \begin{tikzcd}
-  0 \rar & \CSiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \CSiso{G} \arrow{r}{\iota_0^*} & \CSiso{G^0} \rar & 0.
+  0 \rar & \QCiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \QCiso{G} \arrow{r}{\iota_0^*} & \QCiso{G^0} \rar & 0.
   \end{tikzcd}
@@
 \begin{proof}
-Exactness at $\CSiso{G^0}$ follows from Proposition~\ref{prop:restriction},
-and at $\CSiso{\pi_0(G)}$ from Lemma~\ref{lem:extension}.
-Here we show that it is also exact at $\CSiso{G}$.
+Exactness at $\QCiso{G^0}$ follows from Proposition~\ref{prop:restriction},
+and at $\QCiso{\pi_0(G)}$ from Lemma~\ref{lem:extension}.
+Here we show that it is also exact at $\QCiso{G}$.
 First note that $\iota_0^* \circ \pi_0^*$ is trivial by Lemma~\ref{lem:pullback}.
-So it suffices to show that if $\cs{L} = (\gcs{L},\mu,\phi)$ is a character sheaf on $G$
-with $\cs{L}\vert_{G^0} = (\EE)_{G^0}$ then $\cs{L}$ is in the essential image of $\pi_0^*$.
+So it suffices to show that if $\qcs{L} = (\gqcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$
+with $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$ then $\qcs{L}$ is in the essential image of $\pi_0^*$.
 
@@
 Set $a = g^{-1}g'$ and note that $a$ is a geometric point in $\bG^0$.
-Let $\mu_{g,a} : \gcs{L}_{ga} \to \gcs{L}_g \otimes \gcs{L}_a$
+Let $\mu_{g,a} : \gqcs{L}_{ga} \to \gqcs{L}_g \otimes \gqcs{L}_a$
 be the isomorphism of vector spaces obtained by restriction of
-$\mu : m^*\gcs{L} \to \gcs{L} \boxtimes \gcs{L}$ to the
+$\mu : m^*\gqcs{L} \to \gqcs{L} \boxtimes \gqcs{L}$ to the
 geometric point $(g,a)$ on $\bG^x \times \bG^0$.
-Since $\cs{L}\vert_{G^0} = (\EE)_{G^0}$,
-the stalk of $\gcs{L}$ at $a$ is $\EE$.
+Since $\qcs{L}\vert_{G^0} = (\EE)_{G^0}$,
+the stalk of $\gqcs{L}$ at $a$ is $\EE$.
 In this way the pair of geometric points $g, g' \in \bG^x$
 determines an isomorphism $\varphi_{g,g'} \ceq \mu_{g,a}^{-1}$
-from $\gcs{L}_{g}$ to $\gcs{L}_{g'}$.
+from $\gqcs{L}_{g}$ to $\gqcs{L}_{g'}$.
 %
-The isomorphisms $\varphi_{g,g'}: \gcs{L}_{g} \to \gcs{L}_{g'}$ are canonical
+The isomorphisms $\varphi_{g,g'}: \gqcs{L}_{g} \to \gqcs{L}_{g'}$ are canonical
 in the following sense: if $g,g'\in \bG^x$ and $h,h'\in \bG^y$
-then it follows from \ref{CS.2} and \ref{CS.3}
+then it follows from \ref{QC.2} and \ref{QC.3}
 that
- \begin{equation}\label{eq:CS}
+ \begin{equation}\label{eq:qc}
   \begin{tikzcd}[column sep=40]
-   \gcs{L}_{gh} \arrow{r}{\varphi_{gh,g'h'}} \arrow[swap]{d}{\mu_{g,h}}
-  & \gcs{L}_{g'h'} \arrow{d}{\mu_{g',h'}}
+   \gqcs{L}_{gh} \arrow{r}{\varphi_{gh,g'h'}} \arrow[swap]{d}{\mu_{g,h}}
+  & \gqcs{L}_{g'h'} \arrow{d}{\mu_{g',h'}}
   &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-  &  \gcs{L}_{\Frob{}(g)} \arrow{r}{\varphi_{\Frob{}(g),\Frob{}(g')}} \arrow[swap]{d}{\phi_{g}} & \gcs{L}_{\Frob{}(g')} \arrow{d}{\phi_{g'}} \\
-  \gcs{L}_{g} \otimes \gcs{L}_{h} \arrow{r}{\varphi_{g,g'}\otimes \varphi_{h,h'}}
-  & \gcs{L}_{g'} \otimes \gcs{L}_{h'}
+  &  \gqcs{L}_{\Frob{}(g)} \arrow{r}{\varphi_{\Frob{}(g),\Frob{}(g')}} \arrow[swap]{d}{\phi_{g}} & \gqcs{L}_{\Frob{}(g')} \arrow{d}{\phi_{g'}} \\
+  \gqcs{L}_{g} \otimes \gqcs{L}_{h} \arrow{r}{\varphi_{g,g'}\otimes \varphi_{h,h'}}
+  & \gqcs{L}_{g'} \otimes \gqcs{L}_{h'}
   & {}
-  & \gcs{L}_{g} \arrow{r}{\varphi_{g,g'}} & \gcs{L}_{g'}
+  & \gqcs{L}_{g} \arrow{r}{\varphi_{g,g'}} & \gqcs{L}_{g'}
   \end{tikzcd}
@@
 For each $x\in \pi_0(\bG)$, pick $g(x)\in \bG^x$
-and set $\gcs{E}_x \ceq \gcs{L}_{g(x)}$.
-Let $\phi_x : \gcs{E}_{\Frob{}(x)} \to \gcs{E}_x$
+and set $\gqcs{E}_x \ceq \gqcs{L}_{g(x)}$.
+Let $\phi_x : \gqcs{E}_{\Frob{}(x)} \to \gqcs{E}_x$
 be the isomorphism of $\EE$-vector spaces obtained by composing
-$\varphi_{g(\Frob{}(x)),\Frob{}(g(x))} : \gcs{L}_{g(\Frob{}(x))} \to \gcs{L}_{\Frob{}(g(x))}$
-with $\phi_{g(x)} : \gcs{L}_{\Frob{}(g(x))} \to \gcs{L}_{g(x)}$.
+$\varphi_{g(\Frob{}(x)),\Frob{}(g(x))} : \gqcs{L}_{g(\Frob{}(x))} \to \gqcs{L}_{\Frob{}(g(x))}$
+with $\phi_{g(x)} : \gqcs{L}_{\Frob{}(g(x))} \to \gqcs{L}_{g(x)}$.
 For each pair $x,y\in \pi_0(\bG)$
-let $\mu_{x,y} : \gcs{E}_{x+y}\to \gcs{E}_x\otimes \gcs{E}_y$
+let $\mu_{x,y} : \gqcs{E}_{x+y}\to \gqcs{E}_x\otimes \gqcs{E}_y$
 be the isomorphism of $\EE$-vector spaces obtained by composing
-$\varphi_{g(x+y),g(x)g(y)} : \gcs{L}_{g(x+y)} \to \gcs{L}_{g(x)g(y)}$
-with $\mu_{g(x),g(y)} : \gcs{L}_{g(x)g(y)} \to \gcs{L}_{g(x)}\otimes \gcs{L}_{g(y)}$.
-Using \eqref{eq:CS}, it follows that \ref{CS.1}, \ref{CS.2} and \ref{CS.3} are satisfied for
-$\cs{E} \ceq (\gcs{E}_x, \mu_{x,y}, \phi_x)$, thus defining a character sheaf on $\pi_0(G)$.
-
-The pullback $\pi_0^*(\cs{E})$ of $\cs{E}$ along $\pi_0 : G \to \pi_0(G)$ is constant
+$\varphi_{g(x+y),g(x)g(y)} : \gqcs{L}_{g(x+y)} \to \gqcs{L}_{g(x)g(y)}$
+with $\mu_{g(x),g(y)} : \gqcs{L}_{g(x)g(y)} \to \gqcs{L}_{g(x)}\otimes \gqcs{L}_{g(y)}$.
+Using \eqref{eq:qc}, it follows that \ref{qc.1}, \ref{qc.2} and \ref{qc.3} are satisfied for
+$\qcs{E} \ceq (\gqcs{E}_x, \mu_{x,y}, \phi_x)$, thus defining a quasicharacter sheaf on $\pi_0(G)$.
+
+The pullback $\pi_0^*(\qcs{E})$ of $\qcs{E}$ along $\pi_0 : G \to \pi_0(G)$ is constant
 on geometric connected components, with stalks given by
-$(\pi_0^* \cs{E})_g = \cs{E}_{x}$ for all $g\in \bG^x$.  Thus both $\pi_0^*\cs{E}$ and $\cs{L}$
+$(\pi_0^* \qcs{E})_g = \qcs{E}_{x}$ for all $g\in \bG^x$.  Thus both $\pi_0^*\qcs{E}$ and $\qcs{L}$
 are constant on geometric connected components of $G$.
 The choices above define isomorphisms
-$\gcs{L}\vert_{\bG^x} \to  (\gcs{E}_{x})_{\bG^x}$ for each $x\in \pi_0(\bG)$.
-The resulting isomorphism $\gcs{L} \to \pi_0^* \gcs{E}$ satisfies \ref{CS.4},
-thus defining an isomorphism $\cs{L} \to \pi_0^* \cs{E}$ in $\CS(G)$.
+$\gqcs{L}\vert_{\bG^x} \to  (\gqcs{E}_{x})_{\bG^x}$ for each $x\in \pi_0(\bG)$.
+The resulting isomorphism $\gqcs{L} \to \pi_0^* \gqcs{E}$ satisfies \ref{QC.4},
+thus defining an isomorphism $\qcs{L} \to \pi_0^* \qcs{E}$ in $\QC(G)$.
 \end{proof}
@@
 
-We saw in Proposition~\ref{prop:functorialG} that $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
+We saw in Proposition~\ref{prop:functorialG} that $\TrFrob{G} : \QCiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
 In this section we find the image and kernel of $\TrFrob{G}$.
@@
   \[
-  \TrFrob{G} : \CSiso{G} \to G(\Fq)^*
+  \TrFrob{G} : \QCiso{G} \to G(\Fq)^*
   \]
@@
   \begin{tikzcd}[row sep=20, column sep=20]
-    0 \rar & \CSiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
-    & \CSiso{G} \rar \dar{\TrFrob{G}} & \CSiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
+    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
+    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
     0 \rar & \pi_0(G)(\Fq)^* \rar
@@
     0 \arrow[dotted]{r} & \ker \TrFrob{\pi_0(G)} \arrow[dotted]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dotted]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
-    0 \rar & \CSiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
-    & \CSiso{G} \rar \dar{\TrFrob{G}} & \CSiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
+    0 \rar & \QCiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
+    & \QCiso{G} \rar \dar{\TrFrob{G}} & \QCiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
     0 \rar & \pi_0(G)(\Fq)^* \rar \dar
@@
   \begin{tikzcd}
-0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx)) \arrow{r} & \CSiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0. 
+0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx)) \arrow{r} & \QCiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0. 
   \end{tikzcd}
@@
 
-\subsection{On the necessity of working with Weil sheaves}
-
-\begin{corollary} \label{cor:bounded}
-Let $G$ be a smooth commutative group scheme over $\Fq$. 
-Then $\cs{L}\in \CS(G)$ descends to $G$ if and only if $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ has bounded image.
-\end{corollary}
-\begin{proof} 
-By Lemma~\ref{lem:G0alg-grp}, the identity component $G^0$ is a connected algebraic group over $\Fq$. 
-It follows from Proposition~\ref{prop:connected} that the restriction of $\cs{L}$ to $G^0$ descends to $G$. 
-Also, since $G^0(\Fq)$ is finite, the image of $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ is a finite subgroup and therefore bounded image.  
-%
-If $\chi \in G(\Fq)^*$ then there is some finite-image character $\chi_0$
-with the same restriction to $G^0(\Fq)$ since $G^0(\Fq)$ is lies inside the torsion part of
-the finitely generated abelian group $G(\Fq)$.  Therefore $\chi$ is bounded 
-if and only if $\chi \cdot \chi_0^{-1}$ is bounded.  But $\chi \cdot \chi_0^{-1}$ descends
-to a character of $\pi_0(G)$.
-Thus, it is enough to prove Corollary~\ref{cor:bounded}
-for \'etale group schemes $G$.
-
-Now suppose $G$ is an etale group scheme over $\Fq$.
-Let $\cs{L}$ be a character sheaf on $G$.
-$[\alpha \oplus \beta \oplus 0]\in H^2(E)$.
- $b : \bG \to \EEx$ be a function
-
-  By \cite{beilinson-bernstein-deligne:81a}*{Rem. 5.2.1},
-$\cs{L}$ descends to $G$ if and only if $b(x) \in \EEx$ is bounded, for all $x$.
-
- . . . 
-\end{proof}
-
-Corollary~\ref{cor:bounded} shows that the full subcategory
-$\bCS(G) \subset \CS(G)$ is not an equivalence, for smooth commutative group schemes $G$.
-This simple observation reveals the necessity of working with Weil sheaves in Definition~\ref{def:CS}: one cannot geometrize all characters of $G(\Fq)$ using local systems on $G$, for general smooth commutative groups schemes $G$.
-For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$.
-If $\chi : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi(1) = \ell$
-and if $\cs{L}$ is a character sheaf on $G$ in the isomorphism class
-corresponding to $\chi$ under Theorem~\ref{thm:main},
-then $\cs{L}$ does not descend to $G$ since the image of $\chi$ is not
-bounded.
-
-\subsection{Morphisms of character sheaves} \label{ssec:CSmor}
+\subsection{Morphisms of quasicharacters} \label{ssec:qcmor}
 
@@
 \[
-\Aut(\cs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx).
+\Aut(\qcs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx).
 \]
@@
 \begin{proof} 
-Fix $\cs{L} = (\gcs{L},\mu,\phi)$ and consider the group homomorphism from $\Aut(\cs{L})$ to $\Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
+Fix $\qcs{L} = (\gqcs{L},\mu,\phi)$ and consider the group homomorphism from $\Aut(\qcs{L})$ to $\Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
 This homomorphism is injective because morphisms of sheaves are determined by the linear transformations induced on stalks.  
-Homomorphisms in the image of $\Aut(\cs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ are continuous when $\bG$ is viewed as the base of the espace \'etal\'e attached to $\gcs{L}$.
-Since $\ell$ is invertible in $\Fq$, it follows that the image of $\Aut(\cs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
+Homomorphisms in the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ are continuous when $\bG$ is viewed as the base of the espace \'etal\'e attached to $\gqcs{L}$.
+Since $\ell$ is invertible in $\Fq$, it follows that the image of $\Aut(\qcs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
 We also have $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
-To see that $\Aut(\cs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho^y: \gcs{L}^y \to \gcs{L}^y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
-This defines an isomorphism $\bar\rho : \gcs{L}\to \gcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\cs{L}\to \cs{L}$ which maps to $\theta$ under $\Aut(\cs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
+To see that $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho^y: \gqcs{L}^y \to \gqcs{L}^y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
+This defines an isomorphism $\bar\rho : \gqcs{L}\to \gqcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\qcs{L}\to \qcs{L}$ which maps to $\theta$ under $\Aut(\qcs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
 \end{proof}
@@
 
-When using character sheaves to study characters, it is useful to understand
-how character sheaves behave under change of fields.
+When using quasicharacter sheaves to study characters, it is useful to understand
+how quasicharacter sheaves behave under change of fields.
 Let $k'$ be a finite extension of $k$. Then $k \hookrightarrow k'$ induces a group homomorphism
@@
 \end{align*}
-We can interpret this operation on characters in terms of character sheaves:
+We can interpret this operation on characters in terms of quasicharacter sheaves:
 
@@
 \[
-\CS(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \CS(G)
+\QC(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \QC(G)
 \]
@@
 \begin{tikzcd}
-\CSiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\TrFrob{\Res_{k'/k}(G_{k'})}} & \CSiso{G} \dar{\TrFrob{G}} \\
+\QCiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\TrFrob{\Res_{k'/k}(G_{k'})}} & \QCiso{G} \dar{\TrFrob{G}} \\
 G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
@@
 \end{align*}
-We can also interpret this operation in terms of character sheaves.
-
-If $\cs{L} \ceq (\gcs{L}, \mu, \phi)$ is a character sheaf on $G$, we define
-$\cs{L}' \ceq (\gcs{L}, \mu, \phi_{k'})$ on the base change
+We can also interpret this operation in terms of quasicharacter sheaves.
+
+If $\qcs{L} \ceq (\gqcs{L}, \mu, \phi)$ is a quasicharacter sheaf on $G$, we define
+$\qcs{L}' \ceq (\gqcs{L}, \mu, \phi_{k'})$ on the base change
 $G_{k'}$ of $G$ to $k'$ by setting
@@
 \]
-The commutativity of the diagram (CS.3) for $\phi_{k'}$
+The commutativity of the diagram (QC.3) for $\phi_{k'}$
 follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
 Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
-as restricting the action $\varphi$ of $\Weil{k}$ on $\gcs{L}$,
+as restricting the action $\varphi$ of $\Weil{k}$ on $\gqcs{L}$,
 defined in Section~\ref{ssec:category}, to $\Weil{k'}$.
@@
 With notation above,
-the rule $\nu_{k'/k}: (\gcs{L}, \mu, \phi) \mapsto (\gcs{L}, \mu, \phi_{k'})$
- defines a monoidal functor $\CS(G) \to \CS(G_{k'})$
+the rule $\nu_{k'/k}: (\gqcs{L}, \mu, \phi) \mapsto (\gqcs{L}, \mu, \phi_{k'})$
+ defines a monoidal functor $\QC(G) \to \QC(G_{k'})$
  such that the following diagram commutes:
@@
 \begin{tikzcd}[column sep=60]
-\CSiso{G} \rar{\nu_{k'/k}} \dar{\TrFrob{G}} & \CSiso{G_{k'}} \dar{\TrFrob{G_{k'}}} \\
+\QCiso{G} \rar{\nu_{k'/k}} \dar{\TrFrob{G}} & \QCiso{G_{k'}} \dar{\TrFrob{G_{k'}}} \\
 G(k)^*  \rar{\Nm^*} & G(k')^*.
@@
 \begin{proof}
-Let $\cs{L} \ceq (\gcs{L}, \mu, \phi) \in \CS(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
-we may compute the value of $\TrFrob{G_{k'}}(\nu_{k'/k}\cs{L})(x)= t_{\nu_{k'/k}\cs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gcs{L}_x$,
-and the value of $\Nm^*(\TrFrob{G}(\cs{L}))(x)$ as the trace of $\phi$ on $\gcs{L}_{\Nm(x)}$.
-Applying \ref{CS.3} to the stalk of $\gcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
+Let $\qcs{L} \ceq (\gqcs{L}, \mu, \phi) \in \QC(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
+we may compute the value of $\TrFrob{G_{k'}}(\nu_{k'/k}\qcs{L})(x)= t_{\nu_{k'/k}\qcs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gqcs{L}_x$,
+and the value of $\Nm^*(\TrFrob{G}(\qcs{L}))(x)$ as the trace of $\phi$ on $\gqcs{L}_{\Nm(x)}$.
+Applying \ref{QC.3} to the stalk of $\gqcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
 \[
 \begin{tikzcd}
-\gcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gcs{L}_{F(x)} \otimes \gcs{L}_{F^2(x)} \otimes \cdots \otimes \gcs{L}_x
+\gqcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gqcs{L}_{F(x)} \otimes \gqcs{L}_{F^2(x)} \otimes \cdots \otimes \gqcs{L}_x
 \dar{\phi_x \otimes (F^*\phi)_x \otimes \cdots \otimes ((F^{n-1})^*\phi)_x} \\
-\gcs{L}_{\Nm(x)} \rar & \gcs{L}_x \otimes \gcs{L}_{F(x)} \otimes \cdots \otimes \gcs{L}_{F^{n-1}(x)}.
-\end{tikzcd}
-\]
-Choose a basis vector $v$ for $\gcs{L}_{\Nm(x)}$ and write $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$ for the image of $v$ under the
+\gqcs{L}_{\Nm(x)} \rar & \gqcs{L}_x \otimes \gqcs{L}_{F(x)} \otimes \cdots \otimes \gqcs{L}_{F^{n-1}(x)}.
+\end{tikzcd}
+\]
+Choose a basis vector $v$ for $\gqcs{L}_{\Nm(x)}$ and write $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$ for the image of $v$ under the
 bottom map,
-for $v_i \in \gcs{L}_{\Frob{}^i(x)}$.  By \ref{CS.2}, $v$ maps to
+for $v_i \in \gqcs{L}_{\Frob{}^i(x)}$.  By \ref{QC.2}, $v$ maps to
 $v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
 Let $\alpha_i \in \EEx$ represent $((F^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
-the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gcs{L}_{\Nm(x)}$
-with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gcs{L}_x$.
+the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gqcs{L}_{\Nm(x)}$
+with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gqcs{L}_x$.
 \end{proof}
@@
 \[
-\rho : \CS(\Res_{k'/k}G') \to \CS(G').
+\rho : \QC(\Res_{k'/k}G') \to \QC(G').
 \]
@@
 \[
-\rho : \CS(\Res_{k'/k}G') \to \CS(G'),
+\rho : \QC(\Res_{k'/k}G') \to \QC(G'),
 \]
@@
 \begin{tikzcd}
-\CSiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \CSiso{G'} \dar{\TrFrob{G'}}\\
+\QCiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \QCiso{G'} \dar{\TrFrob{G'}}\\
 G'(k')^* \rar & G'(k')^*,
@@
 
-\subsection{The dictionary for commutative algebraic groups over finite fields}
-
-\subsection{Examples}
-
-\section{Applications to quasicharacters of $p$-adic tori and Abelian varieties}\label{sec:applications}
+\section{Applications}\label{sec:applications}
 
@@
 \[
-\Hom_\text{QC}(X(K),\EEx)
+\Hom_\text{qc}(X(K),\EEx)
 \]
@@
 \]
-In this section we will see how to geometrize and categorify quasicharacters of $X(K)$ using character sheaves.
+In this section we will see how to geometrize and categorify quasicharacters of $X(K)$ using quasicharacter sheaves.
 
@@
 
-\subsection{Character sheaves on the Greenberg transform of a N\'eron model} \label{ssec:CS_on_GN}
+\subsection{Quasicharacter sheaves on the Greenberg transform of a N\'eron model} \label{ssec:qc_on_GN}
 
@@
 \[
-\varrho^R_n(X)^* : \CS(\Gr^R_n(X)) \to \CS(\Gr_R(X)),
+\varrho^R_n(X)^* : \QC(\Gr^R_n(X)) \to \QC(\Gr_R(X)),
 \]
 as in Lemma~\ref{lem:pullback}.
-%This functor is faithful, so we may view $\CS(\Gr^R_n(X))$ as a subcategory of $\CS(\Gr_R(X))$.
+%This functor is faithful, so we may view $\QC(\Gr^R_n(X))$ as a subcategory of $\QC(\Gr_R(X))$.
 
 We now define a category which will geometrize quasicharacters of $X(K)$.
-We begin by considering the rigid monoidal category $\CS(\Gr_R(X))$ defined in Section~\ref{ssec:category} without insisting that the commutative group scheme is smooth.
+We begin by considering the rigid monoidal category $\QC(\Gr_R(X))$ defined in Section~\ref{ssec:category} without insisting that the commutative group scheme is smooth.
 
@@
 A {\it quasicharacter sheaf for $X_K$} is an object of
-the following rigid monoidal subcategory of $\CS(\Gr_R(X))$, denoted by $\QCS(X_K)$:
+the following rigid monoidal subcategory of $\QC(\Gr_R(X))$, denoted by $\QC(X_K)$:
 \begin{enumerate}
 \item
-objects in $\QCS(X_K)$ are the $\ell$-adic sheaves $\varrho^R_n(X)^*\cs{L}$, for $n\in \NN$ and $\cs{L} \in \CS(\Gr^R_n(X))$; 
+objects in $\QC(X_K)$ are the $\ell$-adic sheaves $\varrho^R_n(X)^*\qcs{L}$, for $n\in \NN$ and $\qcs{L} \in \QC(\Gr^R_n(X))$; 
 \item
-morphisms $\varrho^R_n(X)^*\cs{L} \to \varrho^R_m(X)^*\cs{L}'$ in $\QCS(X_K)$ are those morphisms in $\CS(\Gr_R(X))$ which take the form $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\cs{L},\cs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\cs{L},\varrho^R_{m\leq n}(X)^*\cs{L}')$ when $m\leq n$.
+morphisms $\varrho^R_n(X)^*\qcs{L} \to \varrho^R_m(X)^*\qcs{L}'$ in $\QC(X_K)$ are those morphisms in $\QC(\Gr_R(X))$ which take the form $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\qcs{L},\qcs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\qcs{L},\varrho^R_{m\leq n}(X)^*\qcs{L}')$ when $m\leq n$.
 \end{enumerate}
@@
 \begin{remark}
-If $\varrho^R_n(X)^* : \CS(\Gr^R_n(X)) \to \CS(\Gr_R(X))$ is full then the construction above can be improved by forming $\QCS(X_K)$ from the essential images of the functors $\varrho^R_n(X)^*$; however, we do not know if $\varrho^R_n(X)^*$ is full.
+If $\varrho^R_n(X)^* : \QC(\Gr^R_n(X)) \to \QC(\Gr_R(X))$ is full then the construction above can be improved by forming $\QC(X_K)$ from the essential images of the functors $\varrho^R_n(X)^*$; however, we do not know if $\varrho^R_n(X)^*$ is full.
 \end{remark}
@@
 \begin{remark}
-We offer the following alternate construction of $\QCS(X_K)$, which does not make use of subcategories.
+We offer the following alternate construction of $\QC(X_K)$, which does not make use of subcategories.
 For objects, one considers triples 
 \[
-\cs{F} \ceq (n, \{\cs{F}_i\}_{n\leq i}, \{\alpha_{i \le j}\}_{n\le i \le j}),
+\qcs{F} \ceq (n, \{\qcs{F}_i\}_{n\leq i}, \{\alpha_{i \le j}\}_{n\le i \le j}),
 \] where $n$
-is a non-negative integer, each $\cs{F}_i$ is a character sheaf on $\Gr^R_i(X)$ and each 
-\[
-\alpha_{i \le j} : \cs{L}_j \to \varrho^R_{i \le j}(X)^* \cs{L}_i
+is a non-negative integer, each $\qcs{F}_i$ is a quasicharacter sheaf on $\Gr^R_i(X)$ and each 
+\[
+\alpha_{i \le j} : \qcs{L}_j \to \varrho^R_{i \le j}(X)^* \qcs{L}_i
 \]
  is an isomorphism; here $\alpha_{i \le i}$ is the identity and the $\alpha_{i \le j}$ are compatible with each other.  
-If $\cs{F} \ceq (n, \{\cs{F}_i\}, \{\alpha_{i \le j}\})$
-and $\cs{F}' \ceq (m, \{\cs{F}'_i\}, \{\alpha'_{i \le j}\})$ are objects then $\Hom(\cs{F}, \cs{F}')$ is the set
-of equivalence classes of pairs $(k, \{\beta_i\}_{k \le i})$, where $n,m \le k$ and the $\beta_i : \cs{F}_i \to \cs{F}'_i$ are
-morphisms of character sheaves so that
+If $\qcs{F} \ceq (n, \{\qcs{F}_i\}, \{\alpha_{i \le j}\})$
+and $\qcs{F}' \ceq (m, \{\qcs{F}'_i\}, \{\alpha'_{i \le j}\})$ are objects then $\Hom(\qcs{F}, \qcs{F}')$ is the set
+of equivalence classes of pairs $(k, \{\beta_i\}_{k \le i})$, where $n,m \le k$ and the $\beta_i : \qcs{F}_i \to \qcs{F}'_i$ are
+morphisms of quasicharacter sheaves so that
 \[
 \begin{tikzcd}
-\cs{F}_j \rar{\alpha_j} \dar{\beta_i} & \varrho^R_{i \le j}(X)^* \cs{F}_i \dar{f_{i \le j}^*\beta_j} \\
-\cs{F}'_j \rar{\alpha_j} & \varrho^R_{i \le j}(X)^* \cs{L}'_i
+\qcs{F}_j \rar{\alpha_j} \dar{\beta_i} & \varrho^R_{i \le j}(X)^* \qcs{F}_i \dar{f_{i \le j}^*\beta_j} \\
+\qcs{F}'_j \rar{\alpha_j} & \varrho^R_{i \le j}(X)^* \qcs{L}'_i
 \end{tikzcd}
@@
 
-\begin{theorem}\label{thm:CSXK}
+\begin{theorem}\label{thm:QCXK}
 Let $K$ be a local field with residue field $\Fq$, in which $\ell$ is invertible; 
@@
 \begin{enumerate}
-\labitem{(1)}{x1}
+\item
 The trace of Frobenius provides a natural transformation between the additive functors
 \[
-F_{\QCS}: X_K \mapsto \QCSiso{X_K}
+F_{\QC}: X_K \mapsto \QCiso{X_K}
 \qquad\text{and}\qquad
-F_{\text{QC}}: X_K \mapsto \Hom_{\text{QC}}(X(K),\EEx)
+F_{\text{qc}}: X_K \mapsto \Hom_{\text{qc}}(X(K),\EEx)
 \]
@@
 \begin{enumerate}[resume]
-\labitem{(2)}{x2} there is a canonical short exact sequence of abelian groups 
-\[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{}} \to \QCSiso{X_K} \to \Hom_\text{QC}(X(K),\EEx) \to 0;
-\] 
-\labitem{(3)}{x3} for all quasicharacter sheaves $\cs{F}$, $\cs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\cs{F},\cs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
-\labitem{(4)}{x4} for all quasicharacter sheaves $\cs{F}$ for $X_K$, there is a canonical isomorphism
-\[
-\Aut(\cs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx).
+\item there is a canonical short exact sequence of abelian groups 
+\[
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{}} \to \QCiso{X_K} \to \Hom_\text{qc}(X(K),\EEx) \to 0;
+\] 
+\item for all quasicharacter sheaves $\qcs{F}$, $\qcs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\qcs{F},\qcs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
+\item for all quasicharacter sheaves $\qcs{F}$ for $X_K$, there is a canonical isomorphism
+\[
+\Aut(\qcs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx).
 \]
@@
 \begin{proof}
-%\begin{enumerate}
-To prove \ref{x1}, use Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$, the fact that N\'eron models are unique up to isomorphism, the fact that every $\CS(\Gr^R_n(X))$ is a full subcategory of $\QCS(X_K)$ and the observation that every object in $\QCS(X_K)$ is in the essential image of $\CS(\Gr^R_n(X))$ for some $n$.
-To prove \ref{x2}, use Theorem~\ref{thm:snake} with $G = \Gr^R_n(X)$ and then argue as in part \ref{x1}.
-To prove \ref{x3}, argue as in the proof of Lemma~\ref{lem:autornaught}.
-To prove \ref{x4}, use Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, the fact that the component group of $\Gr^R_n(X)$ is independent of $n$ and then argue as in part \ref{x1}.
-%\end{enumerate}
-\end{proof}
-
-\subsection{Quasicharacter sheaves for $p$-adic tori} \label{ssec:CS_tori}
+\begin{enumerate}
+\item Use Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$, the fact that N\'eron models are unique up to isomorphism, the fact that every $\QC(\Gr^R_n(X))$ is a full subcategory of $\QC(X_K)$ and the observation that every object in $\QC(X_K)$ is in the essential image of $\QC(\Gr^R_n(X))$ for some $n$.
+\item Use Theorem~\ref{thm:snake} with $G = \Gr^R_n(X)$ and then argue as in part (i).
+\item Argue as in the proof of Lemma~\ref{lem:autornaught}.
+\item Use Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, the fact that the component group of $\Gr^R_n(X)$ is independent of $n$ and then argue as in part (i).
+\end{enumerate}
+\end{proof}
+
+\subsection{Quasicharacter sheaves for $p$-adic tori} \label{ssec:qc_tori}
 
 As we explained in the Introduction, our original motivation for this paper was to find a geometrization and categorification of quasicharacters of $p$-adic tori. 
-This is is now provided by specializing Theorem~\ref{thm:CSXK} to the case when $X_K= T_K\in \mathcal{N}_K$ is an algebraic torus over $K$. 
+This is is now provided by specializing Theorem~\ref{thm:QCXK} to the case when $X_K= T_K\in \mathcal{N}_K$ is an algebraic torus over $K$. 
 Let $T$ be a Neron model for $T_K$.
@@
 where $X_*(T_K)$ is the cocharacter lattice of $T_K$ and $\mathcal{I}_K$ is the inertia group for $K$.
-Accordingly, by Theorem~\ref{thm:CSXK}, isomorphism classes of quasicharacter sheaves for $T_K$ determine quasicharacter sheaves according to the exact sequence
-\[
-0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \CSiso{T_K} \to \Hom_\text{CS}(T(K),\EEx) \to 0.
-\]
-Also by Theorem~\ref{thm:CSXK} and \cite{bitan:discriminant}*{Eq 3.1}, the automorphism group of every $\cs{F} \in \CS(T_K)$ is given by 
-\[
-\Aut(\cs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx),
+Accordingly, by Theorem~\ref{thm:QCXK}, isomorphism classes of quasicharacter sheaves for $T_K$ determine quasicharacter sheaves according to the exact sequence
+\[
+0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCiso{T_K} \to \Hom_\text{qc}(T(K),\EEx) \to 0.
+\]
+Also by Theorem~\ref{thm:QCXK} and \cite{bitan:discriminant}*{Eq 3.1}, the automorphism group of every $\qcs{F} \in \QC(T_K)$ is given by 
+\[
+\Aut(\qcs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx),
 \]
@@
 \begin{tikzcd}[column sep=60]
-\Hom_{\text{QC}}(X_K(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{X(K)}} &\Hom_{\text{QC}}(X_K(K), \EEx).
+\Hom_{\text{qc}}(X_K(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{X(K)}} &\Hom_{\text{qc}}(X_K(K), \EEx).
 \end{tikzcd}
@@
 \begin{equation}\label{men-pulled}
-f_n^* : \CS(\Res_{k'/k} \Gr_{en-1}^{R'}(X'))\to \CS(\Gr_{n-1}^{R}(X)).
+f_n^* : \QC(\Res_{k'/k} \Gr_{en-1}^{R'}(X'))\to \QC(\Gr_{n-1}^{R}(X)).
 \end{equation}
@@
 \[ 
-\Hom_\text{CS}(X_K(K'),\EEx) \to \Hom_\text{CS}(X_K(K)),\EEx)
+\Hom_\text{qc}(X_K(K'),\EEx) \to \Hom_\text{qc}(X_K(K)),\EEx)
 \]
@@
 \begin{equation}\label{eq:categorical_transfer}
-\CS(\Gr^{\OK}_{m-1}(X)) \cong \CS(\Gr^{\OL}_{m-1}(Y))
+\QC(\Gr^{\OK}_{m-1}(X)) \cong \QC(\Gr^{\OL}_{m-1}(Y))
 \end{equation}
@@
  \[
- \CS(\Gr^{\OK}_{m-1}(T)) \iso \CS(\Gr^{\OL}_{m-1}(M))
+ \QC(\Gr^{\OK}_{m-1}(T)) \iso \QC(\Gr^{\OL}_{m-1}(M))
  \]
@@
 
-\subsection{Examples}
-
 \bibliography{bibliography/Biblio}

### 2015-06-05 article-dictionary.tex

@@
 
-\title{Quasicharacters and the function-sheaf dictionary}
+\title{From the function-sheaf dictionary to quasicharacters of $p$-adic tori}
 
@@
 
-\keywords{function-sheaf dictionary, trace of Frobenius, geometrization, categorification, quasicharacters, quasicharacter sheaves, smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor}
+\keywords{function-sheaf dictionary, trace of Frobenius, geometrization, categorification, quasicharacter sheaves, smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor, quasicharacters}
 
@@
 Motivated by an application to the geometrization and categorification of quasicharacters of $p$-adic tori,
-this paper extends Deligne's function-sheaf dictionary to smooth commutative group schemes over finite fields.
+this paper extends Deligne's function-sheaf dictionary from commutative algebraic groups to smooth commutative group schemes over finite fields.
 
@@
 
-Specializing to the case that $X = T$ is the N\'eron model of an algebraic torus (\S\ref{ssec:qc_tori}), 
+Specializing to the case that $X = T$ is the N\'eron model of an algebraic torus over $K$ (\S\ref{ssec:qc_tori}), 
 we give a canonical short exact sequence 
@@
 
+\medskip
 \noindent\textbf{Acknowledgements.\ } {Pramod Achar, Masoud Kamgarpour and Hadi Salmasian

### 2015-06-05 cohomology computations.tex
Adding a new file with some H^2 computations

\documentclass{article}
\usepackage{amsmath,amssymb, amsfonts}
\usepackage{amsthm}

\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\Zt}{\ZZ/2}
\newcommand{\Zf}{\ZZ/4}
\newcommand{\Ft}{\mathbb{F}_2}
\newcommand{\Ex}{\bar{\mathbb{Q}}_\ell^\times}

\DeclareMathOperator{\Hom}{Hom}

\theoremstyle{plain}
\newtheorem{proposition}{Proposition}

\title{Computations in Second Cohomology of Abelian 2-Groups}
\author{David Roe}

\begin{document}
\maketitle

In this note we will explicitly compute $H^2(G, A)$ when $G$ and $A$ are abelian $2$-groups.  We write $\delta_{i,j}$ for the Kronecker delta.

Recall the definition of derivative of a cochain (written additively).  Here $\beta$ is a $1$-cochain and $\varphi$ is a $2$-cochain.
\begin{align}
(d\beta)(g_1, g_2) &= \beta(g_2) - \beta(g_1 + g_2) + \beta(g_1)\\
(d\varphi)(g_1,g_2,g_3) &= \varphi(g_2,g_3) - \varphi(g_1 + g_2, g_3) + \varphi(g_1, g_2 + g_3) - \varphi(g_1, g_2)
\end{align}
Now suppose that $\varphi$ is a cocycle, so that $d\varphi = 0$.  Setting $g_2$to $0$ we get
\[
\varphi(0, g_3) = \varphi(g_1, 0)
\]
for all $g_1$ and $g_3$.  Picking a $\beta$ with $\beta(0)$ equal to this constant value and subtracting $d\beta$, we may assume that
\[
\varphi(0, g) = \varphi(h, 0) = 0
\]
for all $g, h \in G$.  In order to preserve this condition, we only adjust by coboundaries with $\beta(0) = 0$.

We now assume that $G$ and $A$ are both $2$-groups.  Take $g = g_1 = g_2$ and $h = g_3$.  Then
\[
\varphi(g, h + g) = \varphi(g, g) + \varphi(g, h).
\]
Similarly, setting $g = g_2 = g_3$ and $h = g_1$,
\[
\varphi(h + g, g) = \varphi(h, g) + \varphi(g, g).
\]
Therefore $\varphi$ is bilinear.  But any bilinear function $\varphi : G \times G \to A$ will automatically satisfy $d\varphi = 0$.  We thus have the following proposition.

\begin{proposition}
Suppose $\varphi : G \times G \to A$ is a function with $\varphi(0, g) = \varphi(h, 0) = 0$ for all $g, h \in G$.  Then $\varphi$ is a $2$-cocycle if and only if $\varphi$ is bilinear.
\end{proposition}

A class in $H^2(G, A)$ determines an isomorphism class of central extensions $0 \to A \to H \to G \to 0$.  More concretely, any $2$-cocycle $\varphi$ defines a group operation on the set $G \times A$ by 
\begin{equation} \label{eq:cocycle-action}
(g, a) + (h, b) = (g + h, a + b + \varphi(g, h).
\end{equation}
Clearly, this group structure will be abelian precisely when $\varphi$ is symmetric.  Note that coboundaries are automatically symmetric.

\section*{$H^2(\Zt \times \Zt, \Zt)$}

We now further specialize to the case that $G = \Zt \times \Zt$ and $A = \Zt$.  Set $\alpha_1 = (1,0)$, $\alpha_2 = (0,1)$ and $\alpha_3 = (1,1)$.  Since $\varphi$ is bilinear, it is determined by its values on $(\alpha_i, \alpha_j)$ for $j = 1,2$.  This yields sixteen possible cocycles, of which two are coboundaries.  To identify these coboundaries, suppose that $\beta : G \to A$ is a function with $\beta(0) = 0$.  Then $d\beta(g,g) = 0$ and $d\beta(g,h) = d\beta(h,g)$ for all $g, h \in G$.  So the only possible nontrivial coboundary is the one with $d\beta(\alpha_i, \alpha_j) = 1 - \delta_{i,j}$, which is achieved by setting $\beta(\alpha_1) = 1$ and $\beta(\alpha_2) = \beta(\alpha_3) = 0$.

In fact, we seek cohomology classes which are fixed under the involution of $G$ which exchanges the $\Zt$ factors.  At the level of cocycles, this action exchanges the value on $(\alpha_1, \alpha_1)$ with that on $(\alpha_2, \alpha_2)$, and the value on $(\alpha_1, \alpha_2)$ with $(\alpha_2, \alpha_1)$.  There are four cocycles fixed by this involution, and four more that are exchanged with the other cocycle in their class.  These later cocycles are not symmetric ($\varphi(\alpha_1, \alpha_2) \ne \varphi(\alpha_2, \alpha_1)$) and thus correspond to nonabelian extensions.

The non-split abelian extension
\[
0 \to A \xrightarrow{\iota} H \xrightarrow{\pi} G \to 0
\]
is defined by the cocycle $\varphi$ with $\varphi(\alpha_i, \alpha_j) = \delta_{i,j}$.
Here $H \cong \Zt \times \Zf$ and
\begin{align*}
\iota(c) &= (0,2c) \\
\pi(a, d) &= (a, a+d).
\end{align*}
The isomorphism between $G \times A$ (with multiplication as in \eqref{eq:cocycle-action}) and $\Zt \times \Zf$ is given by $(a,b,c) \mapsto (a, a + b + 2c)$.  The involution on $G$ extends to an involution on $H$, namely $(a,d) \leftrightarrow (a+d,d)$.  Note that the image of $\iota$ is fixed under this involution.

For the sake of completeness, we also describe the nonabelian extensions stable under the involution.  One is given by the cocycle with $\varphi(\alpha_1,\alpha_1) = \varphi(\alpha_1, \alpha_2) = \varphi(\alpha_2, \alpha_2) = 0$ and $\varphi(\alpha_2, \alpha_1) = 1$.  The corresponding extension is
\[
0 \to A \xrightarrow{\iota} D_4 \to G \xrightarrow{\pi} 0,
\]
where $D_4$ has presentation $\langle \sigma, \tau \vert \sigma^4 = \tau^2 = \sigma\tau\sigma\tau = 1 \rangle$ and
\begin{align*}
\iota(c) &= \sigma^{2c} \\
\pi(\sigma) &= (1,1) \\
\pi(\tau) &= (1,0).
\end{align*}
The isomorphism between $G \times A$ and $D_4$ is given by $\sigma \mapsto (1,1,0)$ and $\tau \mapsto (1,0,0)$.  The automorphism group of $D_4$ is generated by the outer automorphism $\Phi$ of order $4$ defined by
\begin{align*}
\Phi(\sigma) &= \sigma \\
\Phi(\tau) &= \sigma \tau
\end{align*}
and the inner automorphism $\Psi$ of order $2$ defined by
\begin{align*}
\Psi(\sigma) &= \sigma^3 \\
\Psi(\tau) &= \tau.
\end{align*}
Note that both $\Phi$ and $\Phi^3$ act trivially on the center (generated by $\sigma^2$) and induce the involution we're looking for on the quotient.  But they have order $4$, not $2$.

The other class is represented by the cocycle with $\varphi(\alpha_1, \alpha_1) = \varphi(\alpha_1, \alpha_2) = \varphi(\alpha_2, \alpha_2) = 1$ and $\varphi(\alpha_2, \alpha_1) = 0$.  The corresponding extension is
\[
0 \to A \xrightarrow{\iota} Q \to G \xrightarrow{\pi} 0,
\]
where $Q$ is the quaternion group with presentation $\langle i, j | i^2 j^{-2} = ijij^{-1} = 1 \rangle$ and
\begin{align*}
\iota(c) &= (-1)^c \\
\pi(i) = (1,0) \\
\pi(j) = (0,1).
\end{align*}
The isomorphism between $G \times A$ and $Q$ is given by $i \mapsto (1,0,0)$ and $j \mapsto (0,1,0)$.  The automorphism group of $Q$ is isomorphic to $S_4$, and all automorphisms preserve the image of $A$ since it is the center.  There are four automorphisms inducing the involution on $G$, with $i \mapsto \pm i$ and $j \mapsto \pm j$.

\section*{An automorphism of order 3}

The group $G = \Zt \times \Zt$ also possesses an automorphism of order $3$, given by $e_1 \mapsto e_2$ and $e_2 \mapsto e_1 + e_2$.  Moreover, this is the induced action of Frobenius on $X_*(T)_I$ for the torus $T$ defined by the following integral Galois representation.  Let $p \ne 2$, let $\tau$ be a topological generator of tame inertia and let $F$ be a Frobenius element.  Define $T$ by the representation
\begin{align*}
\tau &\mapsto \begin{pmatrix} -1 & 0 \\ 0 & -1 \end{pmatrix}, \\
F &\mapsto \begin{pmatrix} 0 & 1 \\ -1 & -1 \end{pmatrix}.
\end{align*}

There are two elements of $H^2(G, A)$ fixed by this Frobenius action.  The nontrivial class is the one defining the quaternion extension of $G$ given above.

\section*{Cohomology rings}

We can give a more high level description of $H^*(G, A)$.  Suppose that $G = \Ft^r$ (with basis $\{e_i\}_{i=1}^r$) and $A = \Ft$.  Then the K\"unneth isomorphism gives
\[
H^*(G, A) \cong \Ft[x_1, \dots, x_r]
\]
as graded $\Ft$-algebras (each $x_i$ has degree $1$).  Here $x_i$ is the homomorphism taking value $1$ on $e_i$ and $0$ on the other $e_j$.  Similarly, $\prod_{m = 1}^k x_{i(m)}$ is the multilinear function taking value $1$ on $(e_{i(1)}, \dots, e_{i(k)})$ and $0$ on the other tuples of basis vectors.  When $r = 2$, the involution on $G$ induces the involution on polynomials given by $x_1 \leftrightarrow x_2$.  The order three automorphism above is given by $x_1 \mapsto x_2$ and $x_2 \mapsto x_1 + x_2$.

\section*{$\Ex$-coefficients}

We're actually interested in $H^2(G, \Ex)$.  There is a map $H^2(G, \mu_2) \to H^2(G, \Ex)$, however, this map has a kernel of order $4$, since coboundaries with values in $\Ex$ can have $d\beta(\alpha_1, \alpha_1) = \pm 1$ and $d\beta(\alpha_2, \alpha_2) = \pm 1$ and $d\beta(\alpha_1, \alpha_2) = \pm 1$ independently, and are subject only to the constraint that $d\beta(\alpha_1, \alpha_2) = d\beta(\alpha_2, \alpha_1)$.

\end{document}

### 2015-06-05 dictionary.tex
Added a remark on descent.

@@
 
+\begin{remark}\label{rem:descent}
+In fact, it is not difficult to recognize character sheaves that descend to $G$: they are exactly those character sheaves $\cs{L} = (\gcs{L},\mu,\phi)$ for which the action of $W$ on $\gcs{L}$ given by $\phi$ extends to a continuous action of $\Gal(\bFq/\Fq)$ on $\gcs{L}$; see\cite{deligne-katz:SGA7.2}*{Expos\'e XIII, Rappel 1.1.3} for example.
+\end{remark}
+
 \subsection{Discrete isogenies}\label{ssec:discrete_isogenies}
@@
 
-\subsection{Descent, revisited}
-
-\begin{corollary}\label{cor:bounded-etale}
-Let $G$ be a commutative etale group scheme over $\Fq$.
-Then the image of $\bCS(G)$ under $\TrFrob{G} : \CS(G) \to G(\Fq)^*$ is $\Hom(\bG,\mathbb{\bar Z}_{\ell}^\times)$.
-\end{corollary}
-
-\begin{proof}
-Let $\cs{L}$ be a character sheaf on $G$.
-Using Proposition~\ref{prop:SGiso}, let $[\alpha \oplus \beta \oplus 0]\in \Hh^2(E^\bullet_G)$ be the corresponding class and let  $a : \bG \times \bG \to \EEx$ and $b : \bG \to \EEx$ be multiplicative versions of $\alpha$ and $\beta$, following the notation at the beginning of this section.
-Then $\trFrob{\cs{L}}(x) = b(x)$ for $x\in G(\Fq)$.
-To prove the corollary we will show that $\cs{L}$ descends to $G$ if and only if $b(x)\in \mathbb{\bar Z}_{\ell}^\times$ for every $x\in G(\Fq)$.
-
-The identity component $G^0$ of $G$ may be identified with $\Spec{\Fq}$, 
-By \cite{beilinson-bernstein-deligne:81a}*{Rem. 5.1.2},
-$\cs{L}$ descends to $G$ if and only if $b(x) \in \EEx$ is bounded, for all $x$.
-
- . . .
-
-\end{proof}
-
 \subsection{Objects in the \'etale case}\label{ssec:SandT}
@@
 This result follows from Propositions~\ref{prop:ses_desc}, \ref{prop:SGiso} and \ref{prop:sur_etale}.
+\end{proof}
+
+\subsection{Descent, revisited}\label{ssec:bS}
+
+\begin{corollary}\label{cor:bounded-etale}
+Let $G$ be a commutative etale group scheme over $\Fq$.
+Then the image of $\bCS(G)$ under $\TrFrob{G} : \CS(G) \to G(\Fq)^*$ is $\Hom(\bG,\mathbb{\bar Z}_{\ell}^\times)$.
+\end{corollary}
+
+\begin{proof}
+Objects in $\bCS(G)$ may be described by a small modification to the technique used in Sections~\ref{ssec:E} and \ref{ssec:S}. 
+First, recall that
+
+Set $F^{i,j} \ceq C^i_{\text{cts}} (\Gal(\bFq/\Fq), C^j(G(\bFq), \EEx))$
+
+Let $\cs{L}$ be a character sheaf on $G$.
+Using Proposition~\ref{prop:SGiso}, let $[\alpha \oplus \beta \oplus 0]\in \Hh^2(E^\bullet_G)$ be the corresponding class and let  $a : \bG \times \bG \to \EEx$ and $b : \bG \to \EEx$ be multiplicative versions of $\alpha$ and $\beta$, following the notation at the beginning of this section.
+Then $\trFrob{\cs{L}}(x) = b(x)$ for $x\in G(\Fq)$.
+To prove the corollary we will show that $\cs{L}$ descends to $G$ if and only if $b(x)\in \mathbb{\bar Z}_{\ell}^\times$ for every $x\in G(\Fq)$.
+
+The identity component $G^0$ of $G$ may be identified with $\Spec{\Fq}$, 
+By \cite{beilinson-bernstein-deligne:81a}*{Rem. 5.1.2},
+$\cs{L}$ descends to $G$ if and only if $b(x) \in \EEx$ is bounded, for all $x$.
+
+ . . .
+
 \end{proof}

### 2015-06-05 dictionary.tex
Descent, revisited, for etale groups.

@@
 
-\begin{corollary}\label{cor:bounded-etale}
+In this section we justify the appearance of Weil sheaves in Definition~\ref{def:CS}.
+
+\begin{proposition}\label{prop:bounded-etale}
 Let $G$ be a commutative etale group scheme over $\Fq$.
-Then the image of $\bCS(G)$ under $\TrFrob{G} : \CS(G) \to G(\Fq)^*$ is $\Hom(\bG,\mathbb{\bar Z}_{\ell}^\times)$.
-\end{corollary}
+Then the image of $\bCS(G)$ under $\TrFrob{G} : \CS(G) \to G(\Fq)^*$ is $\Hom_\text{grp}(G(\Fq),\mathbb{\bar Z}_{\ell}^\times)$.
+\end{proposition}
 
@@
 Objects in $\bCS(G)$ may be described by a small modification to the technique used in Sections~\ref{ssec:E} and \ref{ssec:S}. 
-First, recall that
-
-Set $F^{i,j} \ceq C^i_{\text{cts}} (\Gal(\bFq/\Fq), C^j(G(\bFq), \EEx))$
-
-Let $\cs{L}$ be a character sheaf on $G$.
-Using Proposition~\ref{prop:SGiso}, let $[\alpha \oplus \beta \oplus 0]\in \Hh^2(E^\bullet_G)$ be the corresponding class and let  $a : \bG \times \bG \to \EEx$ and $b : \bG \to \EEx$ be multiplicative versions of $\alpha$ and $\beta$, following the notation at the beginning of this section.
-Then $\trFrob{\cs{L}}(x) = b(x)$ for $x\in G(\Fq)$.
-To prove the corollary we will show that $\cs{L}$ descends to $G$ if and only if $b(x)\in \mathbb{\bar Z}_{\ell}^\times$ for every $x\in G(\Fq)$.
-
-The identity component $G^0$ of $G$ may be identified with $\Spec{\Fq}$, 
-By \cite{beilinson-bernstein-deligne:81a}*{Rem. 5.1.2},
-$\cs{L}$ descends to $G$ if and only if $b(x) \in \EEx$ is bounded, for all $x$.
-
- . . .
-
+Set $F^{i,j} \ceq C^i_{\text{cts}} (\Gal(\bFq/\Fq), C^j(G(\bFq), \EEx))$.
+Then the results of Section~\ref{ssec:E} adapt to give a short exact sequence in continuous Galois cohomology
+ \[
+    0 \to
+    \Hh^0(\Fq,\Hh^2({\bar G},\EEx)) \to
+    \Hh^2(F^\bullet_G) \to
+    \Hh^1(\Fq,\Hh^1({\bar G},\EEx)) \to
+    0,
+ \]
+for which the maps are given by the analogues of Proposition~\ref{prop:ses_desc}.
+Moreover, using \cite{deligne-katz:SGA7.2}*{Expos\'e XIII, Rappel 1.1.3} we see that Proposition~\ref{prop:SGiso} adapts to provide an isomorphism $\bCSiso{G}\to \Hh^2(F^\bullet_G)$ compatible with $\bCS(G) \to \CS(G)$ and with the
+the canonical map of exact sequences 
+ \[
+\begin{tikzcd}
+    0 \arrow{r} &
+    \Hh^0(\Fq,\Hh^2({\bar G},\EEx)) \arrow{r} \arrow{d} &
+    \Hh^2(F^\bullet_G) \arrow{r} \arrow{d} &
+    \Hh^1(\Fq,\Hh^1({\bar G},\EEx)) \arrow{r} \arrow{d} &
+    0
+\\
+    0 \arrow{r} & 
+    \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r} & 
+    \Hh^2(E^\bullet_G) \arrow{r} & 
+    \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r} &
+    0.
+\end{tikzcd}
+ \]
+In this way, Proposition~\ref{prop:bounded-etale} is now reduced to the claim
+\[
+\Hh^1(\Fq,\Hh^1({\bar G},\EEx)) = \Hom_\text{grp}(G(\Fq),\mathbb{\bar Z}_{\ell}^\times).
+\]
+To see that, one may argue as follows. 
+Pick $i\in \pi_0(G)$ and let $G^i \hookrightarrow G$ be the corresponding connected component. 
+Pick a geometric point ${\bar x}^i$ on $G^i$ and observe that since $G^i$ is connected as a $\Fq$-scheme, $G^i(\bFq)$ is canonically identified with the $\Gal(\bFq/\Fq)$-orbit of ${\bar x}^i$. 
+We remark that while $G^i$ is defined over $\Fq$, the set $G^i(\Fq)$ is non-empty only when $G^i(\bFq) = \{ {\bar x}^i\}$.
+Since $\Hh^1({\bar G},\EEx) = \Hom_\text{grp}({\bar G},\EEx)$, evaluation $\chi \mapsto \chi({\bar x}^i)$ defines $\Hh^1(\Fq,\Hh^1({\bar G},\EEx)) \to \Hh^1(\Fq,\EEx)$. 
+By continuity, $\Hh^1(\Fq,\EEx) = \Hh^1(\Fq,\mathbb{\bar Z}_{\ell}^\times)$.
+Letting $i$ range over $\pi_0(G)$ we conclude that $\Hh^1(\Fq,\Hh^1({\bar G},\EEx)) = \Hh^1(\Fq,\Hh^1({\bar G},\mathbb{\bar Z}_{\ell}^\times))$.
+When adapted to abelian groups with continuous action of $\Gal(\bFq/\Fq)$, the strategy of the proof of Lemma~\ref{lem:dual-inv} gives $\Hh^1(\Fq,\Hh^1({\bar G},\mathbb{\bar Z}_{\ell}^\times)) =  \Hom_\text{grp}(G(\Fq),\mathbb{\bar Z}_{\ell}^\times)$, concluding the proof.
 \end{proof}
@@
 Thus, it is enough to prove Corollary~\ref{prop:bounded}
-for \'etale group schemes $G$, which is done in Corollary~\ref{cor:bounded-etale}.
+for \'etale group schemes $G$, which is done in Proposition~\ref{prop:bounded-etale}.
 \end{proof}

### 2015-07-13 dictionary.tex
Improvements to the introduction.

@@
 
-\tableofcontents
-
 \section*{Introduction}
@@
 
-If $G$ is a commutative algebraic group over $\Fq$ which is not connected, then the isomorphism \eqref{introbox} need not be unique.
+If $G$ is a commutative algebraic group over $\Fq$ which is not connected, however, then the isomorphism \eqref{introbox} need not be unique.
 In order to track the choice of isomorphism, consider the category $\bCS(G)$ of pairs $(\cs{E},\mu_\cs{E})$ where $\cs{E}$ is a rank-one local system on $G$ and $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ is a chosen isomorphism of local systems on $G\times G$.
@@
 Indeed, it follows from a special case of the main result of this paper that the kernel of the trace of Frobenius $T_{G} : \bCS(G) \to G(\Fq)^*$ trivial if and only if the \'etale group scheme of connected components of $G$ is finite cyclic.
-In general, the defect in the dictionary for characters of commutative algebraic groups over finite fields may be addressed with the following observation: if $(\cs{E},\mu_\cs{E})$ and $(\cs{E}',\mu_\cs{E}')$ determine the same character of $G(\Fq)$ then $\cs{E}\iso \cs{E}'$ as local systems on $G$.
+Nevertheless, the defect in the dictionary for characters of commutative algebraic groups over finite fields may be addressed with the following observation: if $(\cs{E},\mu_\cs{E})$ and $(\cs{E}',\mu_\cs{E}')$ determine the same character of $G(\Fq)$ then $\cs{E}\iso \cs{E}'$ as local systems on $G$.
 
@@
 morphisms in $\CS(G)$ are then morphisms of Weil sheaves which are compatible with the extra structure.
-
-We begin a study of the category $\CS(G)$ of character sheaves on $G$ by returning to the case when $G$ is a connected commutative algebraic group over $\Fq$ and thus by revisiting Deligne's function-sheaf dictionary (\S\ref{sec:category}).
+This paper establishes the basic properties of $\CS(G)$ by finding the relation between character sheaves on $G$ and characters of $G(\Fq)$.
+
+We begin our study of $\CS(G)$ by returning to the case when $G$ is a connected commutative algebraic group over $\Fq$, revisiting Deligne's function-sheaf dictionary (\S\ref{sec:category}).
 We consider character sheaves that arise via base change to $\bFq$ from local systems on $G$ (\S\ref{ssec:descentG}) and
@@
 and to determine the automorphism groups of character sheaves on such $G$. 
-These results are all well known.
+%These results are all well known.
 
 Next, we consider character sheaves on \'etale commutative group schemes $G$ over $\Fq$ (\S\ref{sec:etale}).
-\'Etale group schemes form a counterpoint to connected algebraic groups, since the component group of any smooth group scheme is an \'etale group scheme;
-etale group schemes are algebraic groups only when they are finite.
-Our key tool for understanding the trace of Frobenius in the \'etale case 
+\'Etale group schemes form a counterpoint to connected algebraic groups, since the component group of any smooth group scheme is an \'etale group scheme.
+%etale group schemes are algebraic groups only when they are finite.
+Our key tools for understanding the trace of Frobenius in the \'etale case 
 are a reinterpretation of $\CS(G)$ in terms of stalks (\S\ref{ssec:stalks}) and 
-a relationship with the Hochschild-Serre spectral sequence (\S\ref{ssec:E}) for $\Weil{} \ltimes \bG$, where $\Weil{} \subset \Gal(\Fq/\Fq)$ is the Weil group for $\Fq$.
+%a relationship with 
+ the Hochschild-Serre spectral sequence (\S\ref{ssec:E}) for $\Weil{} \ltimes \bG$, where $\Weil{} \subset \Gal(\Fq/\Fq)$ is the Weil group for $\Fq$.
 We define (\S\ref{ssec:S}) an isomorphism $S_G$ from $\CSiso{G}$ to the second cohomology of the total space of the spectral sequence
@@
 provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$.
-One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is finite cyclic.
+The necessity of using Weil local systems on $G$ in the definition of $\CS(G)$ already appears here:  if one were to use local systems on $G$ instead, the group homomorphism $\TrFrob{G}$ would not then be surjective (\S \ref{ssec:bS}).
+One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is finite cyclic, so the kernel of $\TrFrob{G}$ is non-trivial in general.
 %The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gcs{L}, \mu,\phi)$ and $(\gcs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gcs{L},\phi)$ and $(\gcs{L}',\phi')$ are isomorphic as Weil sheaves.
@@
 
-Having understood character sheaves on commutative smooth group schemes over $\Fq$ in two extreme cases --
-connected commutative algebraic groups and \'etale commutative group schemes -- we turn to the general case  (\S\ref{sec:main}), using the component group sequence
+Having understood $\CS(G)$ in two extreme cases --
+for connected commutative algebraic groups and for \'etale commutative group schemes -- we return to the case of smooth commutative group schemes (\S\ref{sec:main}) using the component group sequence
 \[
@@
 \]
-The rows of this diagram are exact (\S\S\ref{ssec:restriction},\ref{ssec:component}), so we may apply the snake lemma to prove the main theorem of the paper,
+We show that the rows of this diagram are exact (\S\S\ref{ssec:restriction},\ref{ssec:component}), so we may apply the snake lemma to prove the main theorem of the paper,
 \begin{theorem*}[{Thm. \ref{thm:snake}}]
@@
 \noindent
-It follows that, unless the etale group scheme $\pi_0(\bG)$ is cyclic, the category $\CS(G)$ contains non-trivial character sheaves lying in the kernel of the trace of Frobenius and therefore lost in translation to characters of $G(\Fq)$ and, moreover, that these {\it invisible character sheaves} are parametrized by $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
+Thus, unless the component group scheme $\pi_0(\bG)$ is finite cyclic, category $\CS(G)$ contains non-trivial character sheaves lying in the kernel of the trace of Frobenius and therefore lost in translation to characters of $G(\Fq)$.
+%These {\it invisible character sheaves} are parametrized by $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
 
@@
 
+\medskip
+\noindent\textbf{Application to quasicharacters of $p$-adic tori and abelian varieties.\ }
 As indicated above, our interest in the function-sheaf dictionary for smooth commutative group schemes
@@
 \]
-where $\Hom_\text{QC}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
+where $X_*(T_K)_{\mathcal{I}_K}$ is the group of coinvariants of the cocharacter lattice $X_*(T_K)$ of the algebraic torus $T_K$ by the action of the inertia group $\mathcal{I}_K$ of $K$, and where $\Hom_\text{QC}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
 We further show that automorphism groups in $\CS(T_K)$ are given, for every quasicharacter sheaf $\cs{F}$ for $T_K$, by
@@
 where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
+The appearance of the dual torus here is quite striking.
 
@@
 A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group \cite{bernstein:vogan_conference}.
-Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to quasicharacters of all the pure rational forms of $T$.
-
+Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to quasicharacters of all the pure rational forms of $T$; however, we do not pursue that suggestion in this paper.
+
+\medskip
+\noindent\textbf{Relation to other work.\ }
 The process of creating a category from the group of quasicharacters of a $p$-adic  torus informs our choice of the term quasicharacter sheaf in this paper.
@@
 with an eye toward quasicharacters of $p$-adic groups.
-However, the main use of the term character sheaf is of course due to Lusztig.
+
+The main use of the term character sheaf is of course due to Lusztig.
 It is applied to certain perverse sheaves on connected reductive algebraic groups over algebraically closed fields in
@@
 
+This paper shows that the \'etale site on $\Gr_R(X)$ is rich enough to geometrize all quasicharacters of $X(K)$ as $\ell$-adic local systems on $\Gr_R(X)$, where $X$ is a Neron model for an algebraic torus or an abelian variety over a local field $K$.
+It is natural to ask if the \'etale site on the generic fibre $X_K$ would have sufficed. 
+Even the case $X_K = \Gm{K}$ shows that the answer is no [add internal reference].
+
 \medskip
@@
 
-\section{Recollections on character sheaves} \label{sec:category}
+\tableofcontents
+
+\section{Character Sheaves on commutative group schemes and recollections for connected algebraic groups} \label{sec:category}
 
@@
 over a finite field $\Fq$ and $m : G \times G\to G$ is its multiplication morphism.
-It follows from the smoothness of $G$ that the structure morphism $G \to \Spec{\Fq}$ is locally of finite type.
+
 We will make use of the short exact sequence of smooth group schemes defining the component group scheme for $G$:
@@
 Then $G^0$ is a connected algebraic group and $\pi_0(G)$ is an \'etale commutative group scheme.
-Unless noted otherwise, we place absolutely no conditions on the \'etale group scheme $\pi_0(G)$.
+In contrast to the case of algebraic varieties, the component group scheme $\pi_0(G)$ for $G$ need not be finite.
+%Unless noted otherwise, we place absolutely no conditions on the \'etale group scheme $\pi_0(G)$.
+
+It follows from the smoothness of $G$ that the structure morphism $G \to \Spec{\Fq}$ is locally of finite type.
 If the structure morphism $G \to \Spec{\Fq}$ is \'etale, then $G$ is an etale group scheme; this does not imply that $\pi_0(G)$ is finite.
@@
 
-For any abelian group $A$, we will write $A^*$ for the dual group $\Hom(A, \EEx)$.
+For any commutative group $A$, we will write $A^*$ for the dual group $\Hom(A, \EEx)$.
 
@@
 \end{align*}
-from the category of smooth commutative group schemes over $\Fq$ to the category of abelian groups.
+from the category of smooth commutative group schemes over $\Fq$ to the category of commutative groups.
 \end{proposition}
@@
 \]
-as functors from $\mathcal{N}_K$ to the category of abelian groups.
+as functors from $\mathcal{N}_K$ to the category of commutative groups.
 \end{enumerate} 
@@
 \begin{enumerate}[resume]
-\labitem{(2)}{x2} there is a canonical short exact sequence of abelian groups 
+\labitem{(2)}{x2} there is a canonical short exact sequence of commutative groups 
 \[

### 2015-07-13 dictionary.tex
Notation change for quasicharacter sheaves
Replaced QCS(X_K) with QCS(X); also replaced `quasicharacter sheaf for
X_K’ with `quasicharacter sheaf for X’.

@@
 Although not locally of finite type, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and also a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
-This structure allows us to adapt our work on character sheaves on smooth group schemes over finite fields to construct (\S\ref{ssec:CS_on_GN}) a category $\QCS(X_K)$
-of quasicharacter sheaves for $X_K$, which are certain sheaves on $\Gr_R(X)\times_{\Spec{\Fq}} \Spec{\bFq}$, with extra structure.
+This structure allows us to adapt our work on character sheaves on smooth group schemes over finite fields to construct (\S\ref{ssec:CS_on_GN}) a category $\QCS(X)$
+of quasicharacter sheaves for $X$, which are certain sheaves on $\Gr_R(X)\times_{\Spec{\Fq}} \Spec{\bFq}$, with extra structure.
 The ability to generalize the function-sheaf dictionary to non-connected group schemes plays a crucial role in this application.
@@
 where $X_*(T_K)_{\mathcal{I}_K}$ is the group of coinvariants of the cocharacter lattice $X_*(T_K)$ of the algebraic torus $T_K$ by the action of the inertia group $\mathcal{I}_K$ of $K$, and where $\Hom_\text{QC}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
-We further show that automorphism groups in $\CS(T_K)$ are given, for every quasicharacter sheaf $\cs{F}$ for $T_K$, by
+We further show that automorphism groups in $\CS(T)$ are given, for every quasicharacter sheaf $\cs{F}$ for $T$, by
 \[
@@
 \begin{definition}
-A {\it quasicharacter sheaf for $X_K$} is an object of
-the following rigid monoidal subcategory of $\CS(\Gr_R(X))$, denoted by $\QCS(X_K)$:
+A {\it quasicharacter sheaf for $X$} is an object of
+the following rigid monoidal subcategory of $\CS(\Gr_R(X))$, denoted by $\QCS(X)$:
 \begin{enumerate}
 \item
-objects in $\QCS(X_K)$ are the $\ell$-adic sheaves $\varrho^R_n(X)^*\cs{L}$, for $n\in \NN$ and $\cs{L} \in \CS(\Gr^R_n(X))$; 
+objects in $\QCS(X)$ are the $\ell$-adic sheaves $\varrho^R_n(X)^*\cs{L}$, for $n\in \NN$ and $\cs{L} \in \CS(\Gr^R_n(X))$; 
 \item
-morphisms $\varrho^R_n(X)^*\cs{L} \to \varrho^R_m(X)^*\cs{L}'$ in $\QCS(X_K)$ are those morphisms in $\CS(\Gr_R(X))$ which take the form $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\cs{L},\cs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\cs{L},\varrho^R_{m\leq n}(X)^*\cs{L}')$ when $m\leq n$.
+morphisms $\varrho^R_n(X)^*\cs{L} \to \varrho^R_m(X)^*\cs{L}'$ in $\QCS(X)$ are those morphisms in $\CS(\Gr_R(X))$ which take the form $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\cs{L},\cs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\cs{L},\varrho^R_{m\leq n}(X)^*\cs{L}')$ when $m\leq n$.
 \end{enumerate}
@@
 \begin{remark}
-If $\varrho^R_n(X)^* : \CS(\Gr^R_n(X)) \to \CS(\Gr_R(X))$ is full then the construction above can be improved by forming $\QCS(X_K)$ from the essential images of the functors $\varrho^R_n(X)^*$; however, we do not know if $\varrho^R_n(X)^*$ is full.
+If $\varrho^R_n(X)^* : \CS(\Gr^R_n(X)) \to \CS(\Gr_R(X))$ is full then the construction above can be improved by forming $\QCS(X)$ from the essential images of the functors $\varrho^R_n(X)^*$; however, we do not know if $\varrho^R_n(X)^*$ is full.
 \end{remark}
@@
 \begin{remark}
-We offer the following alternate construction of $\QCS(X_K)$, which does not make use of subcategories.
+We offer the following alternate construction of $\QCS(X)$, which does not make use of subcategories.
 For objects, one considers triples 
@@
 \[
-F_{\QCS}: X_K \mapsto \QCSiso{X_K}
+F_{\QCS}: X_K \mapsto \QCSiso{X}
 \qquad\text{and}\qquad
@@
 %\begin{enumerate}
-To prove \ref{x1}, use Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$, the fact that N\'eron models are unique up to isomorphism, the fact that every $\CS(\Gr^R_n(X))$ is a full subcategory of $\QCS(X_K)$ and the observation that every object in $\QCS(X_K)$ is in the essential image of $\CS(\Gr^R_n(X))$ for some $n$.
+To prove \ref{x1}, use Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$, the fact that N\'eron models are unique up to isomorphism, the fact that every $\CS(\Gr^R_n(X))$ is a full subcategory of $\QCS(X)$ and the observation that every object in $\QCS(X)$ is in the essential image of $\CS(\Gr^R_n(X))$ for some $n$.
 To prove \ref{x2}, use Theorem~\ref{thm:snake} with $G = \Gr^R_n(X)$ and then argue as in part \ref{x1}.
@@
 \[
-0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \CSiso{T_K} \to \Hom_\text{CS}(T(K),\EEx) \to 0.
+0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCSiso{T} \to \Hom_\text{CS}(T(K),\EEx) \to 0.
 \]
@@
 \]
-it follows that the automorphism group of every quasicharacter sheaf for $T_K$ is $(\check{T}_\ell)^{\Weil{K}}$, where $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
+it follows that the automorphism group of every quasicharacter sheaf for $T$ is $(\check{T}_\ell)^{\Weil{K}}$, where $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
 

### 2015-07-15 dictionary.tex
Improvements to QCS for tori

@@
 
+[Add reference to Takaski Suzuki's paper]
+
 \medskip
@@
 
-In this section we define an isomorphism
+In this section we define a group homomorphism
 \[
@@
 Now suppose $\rho \in \Aut(\cs{L})$.
-The second diagram in \ref{CS.4} shows that the association $x \mapsto \brho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{CS.4} shows that it factors through $G(\bFq)_{\Weil{}}$.
-
-Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism, then defining $\brho_x$ as multiplication by $\rho(x)$ will define a morphism $\gcs{L} \to \gcs{L}'$ satisfy the two diagrams in \ref{CS.4}.
+The second diagram in \ref{cs.4} shows that the association $x \mapsto \brho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{cs.4} shows that it factors through $G(\bFq)_{\Weil{}}$.
+
+Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism, then defining $\brho_x$ as multiplication by $\rho(x)$ will define a morphism $\gcs{L} \to \gcs{L}'$ satisfy the two diagrams in \ref{cs.4}.
 
@@
 \begin{proof} 
-Fix $\cs{L} = (\gcs{L},\mu,\phi)$ and consider the group homomorphism from $\Aut(\cs{L})$ to $\Hom(\bG_{\Weil{}},\EEx)$ defined in Proposition~\ref{prop:autornaught_etale}.
+Fix $\cs{L} = (\gcs{L},\mu,\phi)$ and consider the group homomorphism from $\Aut(\cs{L})$ to $\Hom(\bG_{\Weil{}},\EEx)$ defined in the proof of Proposition~\ref{prop:autornaught_etale}.
 This homomorphism is injective because morphisms of sheaves are determined by the linear transformations induced on stalks.  
@@
 \begin{enumerate}
-\labitem{(1)}{x1}
+\labitem{(0)}{x0}
 The trace of Frobenius provides a natural transformation between the additive functors
@@
 \begin{enumerate}[resume]
-\labitem{(2)}{x2} there is a canonical short exact sequence of commutative groups 
-\[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{}} \to \QCSiso{X_K} \to \Hom_\text{QC}(X(K),\EEx) \to 0;
-\] 
-\labitem{(3)}{x3} for all quasicharacter sheaves $\cs{F}$, $\cs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\cs{F},\cs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
-\labitem{(4)}{x4} for all quasicharacter sheaves $\cs{F}$ for $X_K$, there is a canonical isomorphism
+\labitem{(1)}{x1} there is a canonical short exact sequence of commutative groups 
+\[
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{}} \to \QCSiso{X} \to \Hom_\text{QC}(X(K),\EEx) \to 0;
+\] 
+\labitem{(2)}{x2} for all quasicharacter sheaves $\cs{F}$, $\cs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\cs{F},\cs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
+\labitem{(3)}{x3} for all quasicharacter sheaves $\cs{F}$ for $X_K$, there is a canonical isomorphism
 \[
@@
 %\begin{enumerate}
-To prove \ref{x1}, use Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$, the fact that N\'eron models are unique up to isomorphism, the fact that every $\CS(\Gr^R_n(X))$ is a full subcategory of $\QCS(X)$ and the observation that every object in $\QCS(X)$ is in the essential image of $\CS(\Gr^R_n(X))$ for some $n$.
-To prove \ref{x2}, use Theorem~\ref{thm:snake} with $G = \Gr^R_n(X)$ and then argue as in part \ref{x1}.
-To prove \ref{x3}, argue as in the proof of Lemma~\ref{lem:autornaught}.
-To prove \ref{x4}, use Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, the fact that the component group of $\Gr^R_n(X)$ is independent of $n$ and then argue as in part \ref{x1}.
+To prove \ref{x0}, use Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$, the fact that N\'eron models are unique up to isomorphism, the fact that every $\CS(\Gr^R_n(X))$ is a full subcategory of $\QCS(X)$ and the observation that every object in $\QCS(X)$ is in the essential image of $\CS(\Gr^R_n(X))$ for some $n$.
+To prove \ref{x1}, use Theorem~\ref{thm:snake} with $G = \Gr^R_n(X)$ and then argue as in part \ref{x0}.
+To prove \ref{x2}, argue as in the proof of Lemma~\ref{lem:autornaught}.
+To prove \ref{x3}, use Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, the fact that the component group of $\Gr^R_n(X)$ is independent of $n$ and then argue as in part \ref{x0}.
 %\end{enumerate}
@@
 As we explained in the Introduction, our original motivation for this paper was to find a geometrization and categorification of quasicharacters of $p$-adic tori. 
-This is is now provided by specializing Theorem~\ref{thm:CSXK} to the case when $X_K= T_K\in \mathcal{N}_K$ is an algebraic torus over $K$. 
-Let $T$ be a Neron model for $T_K$.
+This is now provided by specializing Theorem~\ref{thm:CSXK} to the case when $X_K\in \mathcal{N}_K$ is an algebraic torus over $K$.
+
+\begin{corollary}
+Let $T_K$ be an algebraic toris over $K$ and let $T$ be a Neron model for $T_K$.
+The trace of Frobenius determines a canonical short exact sequence of commutative groups 
+\[
+0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCSiso{T} \to \Hom_\text{QC}(T(K),\EEx) \to 0.
+\] 
+%For all quasicharacter sheaves $\cs{F}$, $\cs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\cs{F},\cs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism.
+For all quasicharacter sheaves $\cs{F}$ for $X_K$, there is a canonical isomorphism
+\[
+\Aut(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}}.
+\]
+\end{corollary}
+
+\begin{proof}
 By \cite{bitan:discriminant}*{Eq 3.1}, the special fibre of the component group scheme for $T$ is given by
@@
 where $X_*(T_K)$ is the cocharacter lattice of $T_K$ and $\mathcal{I}_K$ is the inertia group for $K$.
-Accordingly, by Theorem~\ref{thm:CSXK}, isomorphism classes of quasicharacter sheaves for $T_K$ determine quasicharacter sheaves according to the exact sequence
-\[
-0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCSiso{T} \to \Hom_\text{CS}(T(K),\EEx) \to 0.
-\]
-Also by Theorem~\ref{thm:CSXK} and \cite{bitan:discriminant}*{Eq 3.1}, the automorphism group of every $\cs{F} \in \CS(T_K)$ is given by 
-\[
-\Aut(\cs{F}) \iso \Hom(X_*(T_K)_{\Weil{K}},\EEx),
-\]
-where $\Weil{K}$ is the Weil group for $K$. 
-Since 
-\[
-\Hom(X_*(T_K)_{\Weil{K}},\EEx) \iso \Hom(X_*(T_K),\EEx)^{\Weil{K}}
-\]
-it follows that the automorphism group of every quasicharacter sheaf for $T$ is $(\check{T}_\ell)^{\Weil{K}}$, where $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
+Accordingly, by Theorem~\ref{thm:CSXK}, the kernel of the trace of Frobenius is
+\[
+\Hh^2(\pi_0(T)_{\bFq},\EEx)^{\Weil{}} = \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}}.
+\] 
+Also by Theorem~\ref{thm:CSXK}, $\Aut(\cs{F})  \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx)$, canonically.
+By \cite{bitan:discriminant}*{Eq 3.1} again, 
+\[
+\Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx) \iso
+\Hom(X_*(T_K)_{\Weil{K}},\EEx),
+\]
+canonically.
+But $\Hom(X_*(T_K)_{\Weil{K}},\EEx) \iso \Hom(X_*(T_K),\EEx)^{\Weil{K}}$, canonically.
+So, for any quasicharacter sheaf $\cs{F}$ for $T$,
+\[
+\Aut(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
+\]
+canonically, where $\check{T}_\ell$ is the $\ell$-adic dual torus $\Hom(X_*(T_K),\EEx)$.
+\end{proof}
 

### 2015-07-16 dictionary.tex
LLC

@@
 Now suppose $\rho \in \Aut(\cs{L})$.
-The second diagram in \ref{cs.4} shows that the association $x \mapsto \brho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{cs.4} shows that it factors through $G(\bFq)_{\Weil{}}$.
+The second diagram in \ref{cs.4} shows that the association $x \mapsto \brho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{cs.4} shows that it factors through $G(\bFq) \to G(\bFq)_{\Weil{}}$.
 
@@
 We now define a category which will geometrize quasicharacters of $X(K)$.
-We begin by considering the rigid monoidal category $\CS(\Gr_R(X))$ defined in Section~\ref{ssec:category} without insisting that the commutative group scheme is smooth.
+We begin by considering the rigid monoidal category $\CS(G)$ defined in Section~\ref{ssec:category} without insisting that the commutative group $\Fq$-scheme $G$ is smooth, so that we can replace it with $\Gr_R(X)$ for smooth group $R$-scheme $X$.
 
 \begin{definition}
+Let $X$ be a smooth group scheme over $R$, with $R$ as above.
 A {\it quasicharacter sheaf for $X$} is an object of
@@
 %\begin{enumerate}
-To prove \ref{x0}, use Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$, the fact that N\'eron models are unique up to isomorphism, the fact that every $\CS(\Gr^R_n(X))$ is a full subcategory of $\QCS(X)$ and the observation that every object in $\QCS(X)$ is in the essential image of $\CS(\Gr^R_n(X))$ for some $n$.
+To prove \ref{x0}, use: Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$; the fact that N\'eron models are unique up to isomorphism; the fact that every $\CS(\Gr^R_n(X))$ is a full subcategory of $\QCS(X)$; and the observation that every object in $\QCS(X)$ is in the essential image of $\CS(\Gr^R_n(X))$ for some $n$.
 To prove \ref{x1}, use Theorem~\ref{thm:snake} with $G = \Gr^R_n(X)$ and then argue as in part \ref{x0}.
@@
 \end{corollary}
-
 \begin{proof}
@@
 canonically, where $\check{T}_\ell$ is the $\ell$-adic dual torus $\Hom(X_*(T_K),\EEx)$.
+\end{proof}
+
+\subsection{LLC}
+
+\begin{corollary}
+Let $T_K$ be an algebraic torus over $K$ and let $T$ be a Neron model for $T_K$.
+Then
+\[
+\QCSiso{T} \iso \Hh^1(\Weil{K}, \check{T}_\ell) 
+\qquad \text{and}\qquad
+\QCSiso{T^0} \iso \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{}}.
+\]
+\end{corollary}
+\begin{proof}
+\[
+  \begin{tikzcd}
+  0 \rar & \QCSiso{X_*(T_K)_{\mathcal{I}_K}}\arrow{r}{\pi_0^*} & \QCSiso{T} \arrow{r}{\iota_0^*} & \QCSiso{T^0} \rar & 0.
+  \end{tikzcd}
+\]
 \end{proof}

### 2015-07-17 dictionary.tex
Working on QCS for p-adic tori

@@
 \documentclass[10pt]{amsart}
-\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
-\geometry{a4paper} % or letter or a5paper or ... etc
+\usepackage[a4paper]{geometry} % see geometry.pdf n how to lay out the page. There's lots.
+%\geometry{a4paper} % or letter or a5paper or ... etc
 % \geometry{landscape} % rotated page geometry
@@
 \[
-0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCSiso{T_K} \to \Hom_\text{QC}(T(K),\EEx) \to 0,
-\]
-where $X_*(T_K)_{\mathcal{I}_K}$ is the group of coinvariants of the cocharacter lattice $X_*(T_K)$ of the algebraic torus $T_K$ by the action of the inertia group $\mathcal{I}_K$ of $K$, and where $\Hom_\text{QC}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
+0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCSiso{T_K} \to \Hom_\text{qc}(T(K),\EEx) \to 0,
+\]
+where $X_*(T_K)_{\mathcal{I}_K}$ is the group of coinvariants of the cocharacter lattice $X_*(T_K)$ of the algebraic torus $T_K$ by the action of the inertia group $\mathcal{I}_K$ of $K$, and where $\Hom_\text{qc}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
 We further show that automorphism groups in $\CS(T)$ are given, for every quasicharacter sheaf $\cs{F}$ for $T$, by
@@
 where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
-The appearance of the dual torus here is quite striking.
+%The appearance of the dual torus here is quite striking.
 
@@
  \labitem{(2)}{c2} every character sheaf on $G$ is isomorphic to one defined by a discrete isogeny;
- \labitem{(3)}{c3} $\Aut(\cs{L}) = 1$, for all character sheaves $\cs{L}$ on $G$.
+ \labitem{(3)}{c3} $\Aut_\CS{}(\cs{L}) = 1$, for all character sheaves $\cs{L}$ on $G$.
  \end{enumerate}
@@
 
+Let $G$ be a smooth commutative group scheme over $\Fq$.
 The zeroth page of the Hochschild-Serre spectral sequence
@@
 
+Let $G$ be a smooth commutative group scheme over $\Fq$.
 In this section we define a group homomorphism
@@
 
-\begin{remark}
-Although we will only use the group homomorphism $S_G : \CSiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an \'etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$;
-however, the next result does not extend to all smooth commutative group schemes.
-\end{remark}
+%\begin{remark}
+%Although we will mainly use the group homomorphism $S_G : \CSiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an \'etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$;
+%however, the next result does not extend to all smooth commutative group schemes.
+%\end{remark}
 
 \begin{proposition}\label{prop:SGiso}
-If $G$ is \'etale then $S_G$ is an isomorphism.
+If $G$ is \'etale then $S_G:  \CSiso{G} \to \Hh^2(E^\bullet_G)$ is an isomorphism.
 \end{proposition}
@@
 \[
-\Aut(\cs{L}) \to \Hom(G(\bFq)_{\Weil{}}, \EEx).
+\Aut_\CS{}(\cs{L}) \to \Hom(G(\bFq)_{\Weil{}}, \EEx).
 \]
@@
 It now follows from the snake lemma
- \[
+ \begin{equation}\label{eq:snake}
   \begin{tikzcd}[row sep=20, column sep=15]
@@
   \end{tikzcd}
-  \]
+  \end{equation}
 that $\coker \TrFrob{G} =0$
@@
 \[
-\Aut(\cs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx).
+\Aut_\CS{}(\cs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx).
 \]
@@
 \qquad\text{and}\qquad
-F_{\text{QC}}: X_K \mapsto \Hom_{\text{QC}}(X(K),\EEx)
+F_{\text{qc}}: X_K \mapsto \Hom_{\text{qc}}(X(K),\EEx)
 \]
@@
 \[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{}} \to \QCSiso{X} \to \Hom_\text{QC}(X(K),\EEx) \to 0;
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{}} \to \QCSiso{X} \to \Hom_\text{qc}(X(K),\EEx) \to 0;
 \] 
@@
 Let $T_K$ be an algebraic toris over $K$ and let $T$ be a Neron model for $T_K$.
-The trace of Frobenius determines a canonical short exact sequence of commutative groups 
-\[
-0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCSiso{T} \to \Hom_\text{QC}(T(K),\EEx) \to 0.
-\] 
-%For all quasicharacter sheaves $\cs{F}$, $\cs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\cs{F},\cs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism.
-For all quasicharacter sheaves $\cs{F}$ for $X_K$, there is a canonical isomorphism
-\[
-\Aut(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}}.
+The following is a commutative diagram of exact sequences,
+after removing isomorphism groups.
+\[
+  \begin{tikzcd}[row sep=20, column sep=18]
+{}  & 0 \arrow{d} & 0 \arrow{d} &  & \\ 
+   & \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}}  \arrow{d} & \arrow{d} \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} & 0 \arrow{d} & \\
+    0 \rar & \QCSiso{\pi_0(T)} \arrow{r}{\pi_0^*} \dar{\TrFrob{\pi_0(T)}}
+    & \QCSiso{T} \arrow{r}{\iota_0^*}  \arrow{d}{\TrFrob{\Gr_R(T)}} & \QCSiso{T^0} \arrow{r} \arrow{d}{\TrFrob{\Gr_R(T)^0}} & 0\\
+    0 \arrow{r} & \Hom(\pi_0(T)(\Fq), \EEx) \arrow{r}{\text{infl'n}} \arrow{d}{\iso}
+    & \arrow{d}{\iso} \Hom_\text{qc}(T(K),\EEx) \arrow{r}{\text{rest'n}} & \Hom_\text{qc}(T^0(R),\EEx) \arrow{r} \arrow{d}{\iso} & 0\\
+     0 \arrow{r}  
+ & \Hh^1(\Weil{}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{infl'n}}\arrow{d}
+ & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{rest'n}} \arrow{d}
+ & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{}} \arrow{r}  \arrow{d}
+ & 0\\
+ &  0  & 0 & 0 & 
+  \end{tikzcd}
+ \]
+Moreover, for $\cs{E}\in \QCS(\pi_0(T))$, $\cs{F}\in {\QCS(T)}$ and $\cs{F}^0\in {\QCS(T^0)}$, there are canonical isomorphisms
+\[
+\Aut_{\QCS(\pi_0(T))}(\cs{E})\iso (\check{T}_\ell)^{\Weil{K}},
+\quad
+\Aut_{\QCS(T)}(\cs{F})\iso (\check{T}_\ell)^{\Weil{K}},
+\quad
+\Aut_{\QCS(T^0)}(\cs{F}^0)\iso 1.
 \]
@@
 \[
-\Aut(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
+\Aut_\QCS{}(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
 \]
 canonically, where $\check{T}_\ell$ is the $\ell$-adic dual torus $\Hom(X_*(T_K),\EEx)$.
-\end{proof}
-
-\subsection{LLC}
-
-\begin{corollary}
-Let $T_K$ be an algebraic torus over $K$ and let $T$ be a Neron model for $T_K$.
-Then
-\[
-\QCSiso{T} \iso \Hh^1(\Weil{K}, \check{T}_\ell) 
-\qquad \text{and}\qquad
-\QCSiso{T^0} \iso \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{}}.
-\]
-\end{corollary}
-\begin{proof}
-\[
-  \begin{tikzcd}
-  0 \rar & \QCSiso{X_*(T_K)_{\mathcal{I}_K}}\arrow{r}{\pi_0^*} & \QCSiso{T} \arrow{r}{\iota_0^*} & \QCSiso{T^0} \rar & 0.
-  \end{tikzcd}
-\]
-\end{proof}
+[under construction]
+\end{proof}
+
+[insert discussion of Takashi Suzuki's work]
 

### 2015-07-17 dictionary.tex
QCS and LC for p-adic tori

@@
     & \arrow{d}{\iso} \Hom_\text{qc}(T(K),\EEx) \arrow{r}{\text{rest'n}} & \Hom_\text{qc}(T^0(R),\EEx) \arrow{r} \arrow{d}{\iso} & 0\\
-     0 \arrow{r}  
- & \Hh^1(\Weil{}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{infl'n}}\arrow{d}
- & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{rest'n}} \arrow{d}
- & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{}} \arrow{r}  \arrow{d}
- & 0\\
  &  0  & 0 & 0 & 
@@
  \]
-Moreover, for $\cs{E}\in \QCS(\pi_0(T))$, $\cs{F}\in {\QCS(T)}$ and $\cs{F}^0\in {\QCS(T^0)}$, there are canonical isomorphisms
+ \end{corollary}
+\begin{proof} 
+By \cite{bitan:discriminant}*{Eq 3.1}, the special fibre of the component group scheme for $T$ is given by
+\[
+ \pi_0(T)_{\bFq} = X_*(T_K)_{\mathcal{I}_K},
+\]
+where $X_*(T_K)$ is the cocharacter lattice of $T_K$ and $\mathcal{I}_K$ is the inertia group for $K$.
+Accordingly, by Theorem~\ref{thm:CSXK}, the kernel of the trace of Frobenius is
+\[
+\Hh^2(\pi_0(T)_{\bFq},\EEx)^{\Weil{}} = \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}}.
+\] 
+[under construction]
+\end{proof}
+
+\begin{corollary}
+For $\cs{E}\in \QCS(\pi_0(T))$, $\cs{F}\in {\QCS(T)}$ and $\cs{F}^0\in {\QCS(T^0)}$, there are canonical isomorphisms
 \[
@@
 \end{corollary}
-\begin{proof} 
-By \cite{bitan:discriminant}*{Eq 3.1}, the special fibre of the component group scheme for $T$ is given by
-\[
- \pi_0(T)_{\bFq} = X_*(T_K)_{\mathcal{I}_K},
-\]
-where $X_*(T_K)$ is the cocharacter lattice of $T_K$ and $\mathcal{I}_K$ is the inertia group for $K$.
-Accordingly, by Theorem~\ref{thm:CSXK}, the kernel of the trace of Frobenius is
-\[
-\Hh^2(\pi_0(T)_{\bFq},\EEx)^{\Weil{}} = \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}}.
-\] 
-Also by Theorem~\ref{thm:CSXK}, $\Aut(\cs{F})  \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx)$, canonically.
+
+\begin{proof}
+By Theorem~\ref{thm:CSXK}, $\Aut(\cs{F})  \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx)$, canonically.
 By \cite{bitan:discriminant}*{Eq 3.1} again, 
@@
 \end{proof}
+
+\subsection{Geometric perspective on the Langlands correspondence for $p$-adic tori}
+
+\[
+\begin{tikzcd}
+   0 \rar & \arrow[bend right=70]{dd} \QCSiso{\pi_0(T)} \arrow{r}{\pi_0^*} \dar{\TrFrob{\pi_0(T)}}
+    & \QCSiso{T} \arrow{r}{\iota_0^*} \arrow[dotted, bend right=50]{dd}  \arrow{d}{\TrFrob{\Gr_R(T)}} & \QCSiso{T^0} \arrow[dotted, bend right=50]{dd}  \arrow{r} \arrow{d}{\TrFrob{\Gr_R(T)^0}} & 0\\
+   0 \arrow{r} & \Hom(\pi_0(T)(\Fq), \EEx) \arrow{r}{\text{infl'n}} \arrow{d}{\iso}
+    & \arrow{d}{\iso} \Hom_\text{qc}(T(K),\EEx) \arrow{r}{\text{rest'n}} & \Hom_\text{qc}(T^0(R),\EEx) \arrow{r} \arrow{d}{\iso} & 0\\    
+    0 \arrow{r}  
+ & \Hh^1(\Weil{}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{infl'n}}
+ & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{rest'n}} 
+ & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{}} \arrow{r}  
+ & 0
+\end{tikzcd}
+\]
 

### 2015-07-17 dictionary.tex
QCS and LC for p-adic tori.

@@
 \] 
-[under construction]
 \end{proof}
@@
 \begin{proof}
-By Theorem~\ref{thm:CSXK}, $\Aut(\cs{F})  \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx)$, canonically.
+We already know $\Aut_{\QCS(T^0)}(\cs{E}) =1$ from Proposition~\ref{prop:connected}, part \ref{x3}.
+By Theorem~\ref{thm:CSXK}, $\Aut(\cs{F})  \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx)$, canonically, for $X = T$ and $X=\pi_0(T)$ (and for $X= T^0$, though that case is already treated).
+In case $X = T^0$, it is clear that $\Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx)$ is trivial, so $\Aut_{\QCS(T^0)}(\cs{E}) =1$; in fact, we alre
 By \cite{bitan:discriminant}*{Eq 3.1} again, 
 \[
-\Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx) \iso
+\Hom((\pi_0(T)_{\bFq})_{\Weil{}},\EEx) \iso
 \Hom(X_*(T_K)_{\Weil{K}},\EEx),
@@
 canonically, where $\check{T}_\ell$ is the $\ell$-adic dual torus $\Hom(X_*(T_K),\EEx)$.
-[under construction]
+The other two cases are 
 \end{proof}

### 2015-07-18 dictionary.tex
Removed qc. Working on comments on LLC.

--- 2015-07-17 dictionary.tex
@@
 \[
-0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCSiso{T_K} \to \Hom_\text{qc}(T(K),\EEx) \to 0,
-\]
-where $X_*(T_K)_{\mathcal{I}_K}$ is the group of coinvariants of the cocharacter lattice $X_*(T_K)$ of the algebraic torus $T_K$ by the action of the inertia group $\mathcal{I}_K$ of $K$, and where $\Hom_\text{qc}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
+0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCSiso{T_K} \to \Hom_\text{}(T(K),\EEx) \to 0,
+\]
+where $X_*(T_K)_{\mathcal{I}_K}$ is the group of coinvariants of the cocharacter lattice $X_*(T_K)$ of the algebraic torus $T_K$ by the action of the inertia group $\mathcal{I}_K$ of $K$, and where $\Hom_\text{}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
 We further show that automorphism groups in $\CS(T)$ are given, for every quasicharacter sheaf $\cs{F}$ for $T$, by
@@
 The group of quasicharacters of $X(K)$ will be denoted by 
-\[
-\Hom_\text{qc}(X(K),\EEx)
-\]
- and the subgroup of those that factor through $X(R_n)$ will be denoted by 
- \[
- \Hom_n(X(K),\EEx).
-\]
+$\Hom_\text{}(X(K),\EEx)$
+ and the subgroup of those that factor through $X(R_n)$ will be denoted by $\Hom_n(X(K),\EEx)$.
 In this section we will see how to geometrize and categorify quasicharacters of $X(K)$ using character sheaves.
@@
 \qquad\text{and}\qquad
-F_{\text{qc}}: X_K \mapsto \Hom_{\text{qc}}(X(K),\EEx)
+F_{\text{}}: X_K \mapsto \Hom_{\text{}}(X(K),\EEx)
 \]
@@
 \[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{}} \to \QCSiso{X} \to \Hom_\text{qc}(X(K),\EEx) \to 0;
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{}} \to \QCSiso{X} \to \Hom_\text{}(X(K),\EEx) \to 0;
 \] 
@@
 
-\begin{corollary}
+\begin{corollary}\label{cor:CS_tori}
 Let $T_K$ be an algebraic toris over $K$ and let $T$ be a Neron model for $T_K$.
-The following is a commutative diagram of exact sequences,
-after removing isomorphism groups.
+The following is a commutative diagram of exact sequences.
 \[
@@
     0 \arrow{r} & \Hom(\pi_0(T)(\Fq), \EEx) \arrow{r}{\text{infl'n}} \arrow{d}{\iso}
-    & \arrow{d}{\iso} \Hom_\text{qc}(T(K),\EEx) \arrow{r}{\text{rest'n}} & \Hom_\text{qc}(T^0(R),\EEx) \arrow{r} \arrow{d}{\iso} & 0\\
-     0 \arrow{r}  
- & \Hh^1(\Weil{}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{infl'n}}\arrow{d}
- & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{rest'n}} \arrow{d}
- & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{}} \arrow{r}  \arrow{d}
- & 0\\
+    & \arrow{d}{\iso} \Hom_\text{}(T(K),\EEx) \arrow{r}{\text{rest'n}} & \Hom_\text{}(T^0(R),\EEx) \arrow{r} \arrow{d}{\iso} & 0\\
  &  0  & 0 & 0 & 
@@
  \]
-Moreover, for $\cs{E}\in \QCS(\pi_0(T))$, $\cs{F}\in {\QCS(T)}$ and $\cs{F}^0\in {\QCS(T^0)}$, there are canonical isomorphisms
+ \end{corollary}
+\begin{proof} 
+The horizontal sequence of groups coming from categories of quasicharacter sheaves is exact by Proposition~\ref{prop:middleexact}, together with the observation that the functors $\pi_0^*$ and $\iota^*$ perverse limits.
+It is elementary that the horizontal sequence of quasicharacters is exact.
+The diagram commutes by Lemma~\ref{lem:pullback}.
+Accordingly, by Theorem~\ref{thm:CSXK}, the kernel of $\TrFrob{T}$ is $\Hh^2(\pi_0(T)_{\bFq},\EEx)^{\Weil{}}$. 
+By \cite{bitan:discriminant}*{Eq 3.1}, the special fibre of the component group scheme for $T$ is given by
+\[
+ \pi_0(T)_{\bFq} = X_*(T_K)_{\mathcal{I}_K},
+\]
+where $X_*(T_K)$ is the cocharacter lattice of $T_K$ and $\mathcal{I}_K$ is the inertia group for $K$.
+Thus,
+\[
+\Hh^2(\pi_0(T)_{\bFq},\EEx)^{\Weil{}} = \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}}.
+\] 
+which coincides with the kernel of $\TrFrob{\pi_0(T)}$ since $\pi_0(\pi_0(T))_{\bFq} = \pi_0(T)_{\bFq}$.
+\end{proof}
+
+\begin{corollary}
+For $\cs{E}\in \QCS(\pi_0(T))$, $\cs{F}\in {\QCS(T)}$ and $\cs{F}^0\in {\QCS(T^0)}$, there are canonical isomorphisms
 \[
@@
 \end{corollary}
-\begin{proof} 
-By \cite{bitan:discriminant}*{Eq 3.1}, the special fibre of the component group scheme for $T$ is given by
-\[
- \pi_0(T)_{\bFq} = X_*(T_K)_{\mathcal{I}_K},
-\]
-where $X_*(T_K)$ is the cocharacter lattice of $T_K$ and $\mathcal{I}_K$ is the inertia group for $K$.
-Accordingly, by Theorem~\ref{thm:CSXK}, the kernel of the trace of Frobenius is
-\[
-\Hh^2(\pi_0(T)_{\bFq},\EEx)^{\Weil{}} = \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}}.
-\] 
-Also by Theorem~\ref{thm:CSXK}, $\Aut(\cs{F})  \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx)$, canonically.
+
+\begin{proof}
+We already know $\Aut_{\QCS(T^0)}(\cs{E}) =1$ from Proposition~\ref{prop:connected}, part \ref{x3}.
+By Theorem~\ref{thm:CSXK}, $\Aut(\cs{F})  \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx)$, canonically, for $X = T$ and $X=\pi_0(T)$ (and for $X= T^0$, though that case has already been treated by a different argument, above).
 By \cite{bitan:discriminant}*{Eq 3.1} again, 
 \[
-\Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx) \iso
+\Hom((\pi_0(T)_{\bFq})_{\Weil{}},\EEx) \iso
 \Hom(X_*(T_K)_{\Weil{K}},\EEx),
@@
 \[
-\Aut_\QCS{}(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
+\Aut_\QCS{T}(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
 \]
 canonically, where $\check{T}_\ell$ is the $\ell$-adic dual torus $\Hom(X_*(T_K),\EEx)$.
-[under construction]
-\end{proof}
+The case $X= \pi_0(T)$ is treated recovers the same automorphism group since $\pi_0(\pi_0(T))_{\bFq} = \pi_0(T)_{\bFq}$.
+\end{proof}
+
+\subsection{Geometric perspective on the Langlands correspondence for $p$-adic tori}\label{ssec:LLCT}
+
+\begin{lemma}\label{lem:LLCT}
+The following diagram commutes. 
+\[
+\begin{tikzcd}
+   0 \arrow{r} & \Hom(\pi_0(T)(\Fq), \EEx) \arrow{r}{\text{infl'n}} \arrow{d}{\iso}
+    & \arrow{d}{\iso} \Hom_\text{}(T(K),\EEx) \arrow{r}{\text{rest'n}} & \Hom_\text{}(T^0(R),\EEx) \arrow{r} \arrow{d}{\iso} & 0\\    
+    0 \arrow{r}  
+ & \Hh^1(\Weil{}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{infl'n}}
+ & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{rest'n}} 
+ & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{}} \arrow{r}  
+ & 0
+\end{tikzcd}
+\] 
+\end{lemma}
+\begin{proof}
+Since $\pi_0(T)_{\bFq} = X_*(T_K)_{\mathcal{I}_K}$ by \cite{bitan:discriminant}*{Eq 3.1}, the isomorphism on the left can be seen directly:
+\[\Hom(\pi_0(T)(\Fq), \EEx)
+= \Hom((X_*(T)_{\mathcal{I}_K})^{\Weil{}}, \EEx)
+= \Hom(X_*(T)_{\mathcal{I}_K}, \EEx)_{\Weil{}} 
+%= \Hh^1(\Weil{}, \Hom(X_*(T), \EEx)^{\mathcal{I}_K}) 
+= \Hh^1(\Weil{}, \check{T}_\ell^{\mathcal{I}_K}).
+\]
+The middle isomorphism is the Langlands correspondence for $p$-adic tori, itself a fairly direct consequence of local class field theory; see \cite{yu:09a}, for example. The isomorphism 
+\[
+\Hom_\text{}(T^0(R),\EEx) \iso \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{}}
+\] 
+and the commutativity of the diagram is then a consequence of the inflation-restriction exact sequence and the fact that $\Weil{}$ has cohomological dimension $1$.
+\end{proof}
+
+Combining Corollary~\ref{cor:CS_tori} with Lemma~\ref{lem:LLCT} now produces the following commutative diagram of exact sequences:
+\begin{equation}\label{eq:GLCT}
+  \begin{tikzcd}[row sep=20, column sep=18]
+{}  & 0 \arrow{d} & 0 \arrow{d} &  & \\ 
+   & \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}}  \arrow{d} & \arrow{d} \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} & 0 \arrow{d} & \\
+    0 \rar & \QCSiso{\pi_0(T)} \arrow{r}{\pi_0^*} \arrow{d}
+    & \QCSiso{T} \arrow{r}{\iota_0^*}  \arrow{d} & \QCSiso{T^0} \arrow{r} \arrow{d} & 0\\
+   0 \arrow{r}  
+ & \Hh^1(\Weil{}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{infl'n}} \arrow{d}
+ & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{rest'n}} \arrow{d}
+ & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{}} \arrow{r} \arrow{d}  
+ & 0\\
+ &  0  & 0 & 0 & 
+  \end{tikzcd}
+ \end{equation}
+It is natural to ask if the vertical surjections can be defined directly, without making use of local class field theory.  
+Even the case $T_K = \Gm{K}$ is remarkable, in which case \eqref{eq:GLCT} becomes
+
+In fact, the answer is yes; as such, these maps provide a geometric perspective on the Langlands correspondence for $p$-adic tori.
+
+As in \cite{Yu:09a}, the general case can be built up from the case $T_K = \Gm{K}$.
+
+or by a small part of Proposition~\ref{prop:etale-iso}
 
@@
 \begin{tikzcd}[column sep=60]
-\Hom_{\text{qc}}(X_K(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{X(K)}} &\Hom_{\text{qc}}(X_K(K), \EEx).
+\Hom_{\text{}}(X_K(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{X(K)}} &\Hom_{\text{}}(X_K(K), \EEx).
 \end{tikzcd}

### 2015-07-18 dictionary.tex
Minor edits before going to bed.

@@
 \begin{corollary}
+Let $T_K$ be an algebraic toris over $K$ and let $T$ be a Neron model for $T_K$.
 For $\cs{E}\in \QCS(\pi_0(T))$, $\cs{F}\in {\QCS(T)}$ and $\cs{F}^0\in {\QCS(T^0)}$, there are canonical isomorphisms
@@
 \quad
-\Aut_{\QCS(T^0)}(\cs{F}^0)\iso 1.
-\]
+\Aut_{\QCS(T^0)}(\cs{F}^0)\iso 1,
+\]
+ where $\check{T}_\ell \ceq \Hom(X_*(T_K),\EEx)$, the $\ell$-adic dual torus to $T_K$.
 \end{corollary}
@@
 \[
-\Aut_\QCS{T}(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
-\]
-canonically, where $\check{T}_\ell$ is the $\ell$-adic dual torus $\Hom(X_*(T_K),\EEx)$.
-The case $X= \pi_0(T)$ is treated recovers the same automorphism group since $\pi_0(\pi_0(T))_{\bFq} = \pi_0(T)_{\bFq}$.
+\Aut_{\QCS(T)}(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
+\]
+canonically.
+The case $X= \pi_0(T)$ recovers the same automorphism group since $\pi_0(\pi_0(T))_{\bFq} = \pi_0(T)_{\bFq}$.
 \end{proof}
@@
 \begin{equation}\label{eq:GLCT}
-  \begin{tikzcd}[row sep=20, column sep=18]
+  \begin{tikzcd}[row sep=20, column sep=15]
 {}  & 0 \arrow{d} & 0 \arrow{d} &  & \\ 
-   & \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}}  \arrow{d} & \arrow{d} \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} & 0 \arrow{d} & \\
+   & \Hh^0(\Weil{}, \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx))  \arrow{d} & \arrow{d} \Hh^0(\Weil{}, \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)) & 0 \arrow{d} & \\
     0 \rar & \QCSiso{\pi_0(T)} \arrow{r}{\pi_0^*} \arrow{d}
@@
    0 \arrow{r}  
- & \Hh^1(\Weil{}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{infl'n}} \arrow{d}
+ & \Hh^1(\Weil{}, \Hh^0(\mathcal{I}_K, \check{T}_\ell)) \arrow{r}{\text{infl'n}} \arrow{d}
  & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{rest'n}} \arrow{d}
- & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{}} \arrow{r} \arrow{d}  
+ & \Hh^0(\Weil{}, \Hh^1(\mathcal{I}_K, \check{T}_\ell)) \arrow{r} \arrow{d}  
  & 0\\
@@
 
-As in \cite{Yu:09a}, the general case can be built up from the case $T_K = \Gm{K}$.
+As in \cite{yu:09a}, the general case can be built up from the case $T_K = \Gm{K}$.
 

### 2015-07-18 dictionary.tex
Catching up

@@
 
-Let $K$ be a local field with finite residue field $\Fq$;
- we continue to assume that $\ell$ is invertible in $\Fq$.
+Let $K$ be a local field with finite residue field $\Fq$; we will now denote the group $\Weil{}$ by $\Weil{\Fq}$.
+We continue to assume that $\ell$ is invertible in $\Fq$. 
 In this section we consider connected commutative algebraic groups over $K$ that admit a N\'eron model, by which we mean a locally finite type N\'eron model.
@@
 \[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{}} \to \QCSiso{X} \to \Hom_\text{}(X(K),\EEx) \to 0;
+0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{\Fq}} \to \QCSiso{X} \to \Hom_\text{}(X(K),\EEx) \to 0;
 \] 
@@
 \[
-\Aut(\cs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx).
+\Aut(\cs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{\Fq}},\EEx).
 \]
@@
 {}  & 0 \arrow{d} & 0 \arrow{d} &  & \\ 
-   & \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}}  \arrow{d} & \arrow{d} \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} & 0 \arrow{d} & \\
+   & \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}}  \arrow{d} & \arrow{d} \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}} & 0 \arrow{d} & \\
     0 \rar & \QCSiso{\pi_0(T)} \arrow{r}{\pi_0^*} \dar{\TrFrob{\pi_0(T)}}
@@
 \[
-\Hh^2(\pi_0(T)_{\bFq},\EEx)^{\Weil{}} = \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}}.
+\Hh^2(\pi_0(T)_{\bFq},\EEx)^{\Weil{\Fq}} = \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}}.
 \] 
@@
     0 \arrow{r}  
- & \Hh^1(\Weil{}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{infl'n}}
+ & \Hh^1(\Weil{\Fq}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{infl'n}}
  & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{rest'n}} 
- & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{}} \arrow{r}  
+ & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{\Fq}} \arrow{r}  
  & 0
@@
 \[\Hom(\pi_0(T)(\Fq), \EEx)
-= \Hom((X_*(T)_{\mathcal{I}_K})^{\Weil{}}, \EEx)
-= \Hom(X_*(T)_{\mathcal{I}_K}, \EEx)_{\Weil{}} 
+= \Hom((X_*(T)_{\mathcal{I}_K})^{\Weil{\Fq}}, \EEx)
+= \Hom(X_*(T)_{\mathcal{I}_K}, \EEx)_{\Weil{\Fq}} 
 %= \Hh^1(\Weil{}, \Hom(X_*(T), \EEx)^{\mathcal{I}_K}) 
-= \Hh^1(\Weil{}, \check{T}_\ell^{\mathcal{I}_K}).
+= \Hh^1(\Weil{\Fq}, \check{T}_\ell^{\mathcal{I}_K}).
 \]
@@
 \[
-\Hom_\text{}(T^0(R),\EEx) \iso \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{}}
+\Hom_\text{}(T^0(R),\EEx) \iso \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{\Fq}}
 \] 
@@
 {}  & 0 \arrow{d} & 0 \arrow{d} &  & \\ 
-   & \Hh^0(\Weil{}, \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx))  \arrow{d} & \arrow{d} \Hh^0(\Weil{}, \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)) & 0 \arrow{d} & \\
+   & \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}}  \arrow{d} & \arrow{d} \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}} & 0 \arrow{d} & \\
     0 \rar & \QCSiso{\pi_0(T)} \arrow{r}{\pi_0^*} \arrow{d}
@@
    0 \arrow{r}  
- & \Hh^1(\Weil{}, \Hh^0(\mathcal{I}_K, \check{T}_\ell)) \arrow{r}{\text{infl'n}} \arrow{d}
+ & \Hh^1(\Weil{\Fq}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{infl'n}} \arrow{d}
  & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{rest'n}} \arrow{d}
- & \Hh^0(\Weil{}, \Hh^1(\mathcal{I}_K, \check{T}_\ell)) \arrow{r} \arrow{d}  
+ & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{\Fq}} \arrow{r} \arrow{d}  
  & 0\\
@@
 It is natural to ask if the vertical surjections can be defined directly, without making use of local class field theory.  
-Even the case $T_K = \Gm{K}$ is remarkable, in which case \eqref{eq:GLCT} becomes
-
-In fact, the answer is yes; as such, these maps provide a geometric perspective on the Langlands correspondence for $p$-adic tori.
-
-As in \cite{yu:09a}, the general case can be built up from the case $T_K = \Gm{K}$.
-
-or by a small part of Proposition~\ref{prop:etale-iso}
-
-[insert discussion of Takashi Suzuki's work]
+The case $T_K = \Gm{K}$ is already very interesting, in which case \eqref{eq:GLCT} becomes
+\begin{equation}\label{eq:Gm}
+\begin{tikzcd}
+    0 \rar & \QCSiso{\ZZ} \arrow{r}{\pi_0^*} \arrow{d}{\iso}
+    & \QCSiso{T} \arrow{r}{\iota_0^*}  \arrow{d}{\iso} & \QCSiso{\Gm{R}} \arrow{r} \arrow{d}{\iso} & 0\\
+    0 \arrow{r}  
+ & \Hom(\Weil{\Fq}, \EEx) \arrow{r}{\text{infl'n}}
+ & \Hom(\Weil{K}, \EEx) \arrow{r}{\text{rest'n}} 
+ & \Hom(\mathcal{I}_K, \EEx) \arrow{r}  
+ & 0
+\end{tikzcd}
+\end{equation}
+We have seen that the isomorphism $\QCS(\ZZ)\iso \Hom(\Weil{\Fq}, \EEx)$ is elementary. 
+The isomorphism $\QCSiso{\Gm{R}}\iso \Hom(\mathcal{I}_K, \EEx)$ may be deduced directly from the class field theory of Serre and Hezewinkel.
+The monoidal category of character sheaves on $\Gr^R_n(\Gm{R})$ is canonically equivalent to the category of $\ell$-adic characters of the equivariant etale fundamental group $\pi_1^\text{eq}(\Gr^R_n(\Gm{R}),\bFq)$.
+%and, using the Lang isogeny, that there is a canonical isomorphism 
+%\[\pi_1^\text{eq}(\Gr^R_n(\Gm{R}),\bFq) \iso \Gr^R_n(\Gm{R})(\Fq) = R_n^*.\]
+Accordingly, quasicharacter sheaves on $\Gm{R}$ may be apprehended as $\ell$-adic characters of
+the inverse limit of the groups $\pi_1^\text{eq}(\Gr^R_n(\Gm{R}),\bFq)$, as $n$ ranges over $\NN$.
+By \cite{serre:isogenies}, there is a canonical isomorphism 
+\[
+\varprojlim_{n\in \NN} \pi_1^\text{eq}(\Gr^R_n(\Gm{R}),\bFq) \iso \mathcal{I}_K^\text{ab};
+\]
+this isomorphism is {\it not} restricted to the case when $K$ and $\Fq$ have equal characteristic.
+This last isomorphism now provides the isomorphism $\QCSiso{\Gm{R}}\iso \Hom(\mathcal{I}_K, \EEx)$ in \eqref{eq:Gm}. 
+Since the sequences are split, this gives \eqref{eq:Gm}, geometrically. 
+We have been glib here because all this is treated carefully and beautifully in \cite{suzuki-yoshida:12a}. 
+Indeed, in that paper, an isomorphism is constructed directly between the equivariant fundamental group of $\Gr_R(T)$ (with respect to a site defined in \cite{suzuki-yoshida:12a}) when $T$ is a Neron model of $\Gm{K}$, and $\Weil{K}^\text{ab}$, improving greatly on the arguments of this paragraph.
+
+We expect that the general case of \eqref{eq:GLCT}, where $K$ is any local field and $T_K$ is any torus over $K$, may be deduced from the case \eqref{eq:Gm}, by an adaptation of arguments from \cite{yu:09a}.
+In anticipation of work in that direction, Section~\ref{ssec:wrK} provides a key tool for that argument.
+
+We close this section with some further remarks on sites.
 

### 2015-07-19 dictionary.tex
more references; more remarks

@@
 \[
-\Aut_{\CS{}}(\cs{L}) \iso  \Hh^1(\pi_0(\bG), \EEx)^{\Weil{}}
+\Aut(\cs{L}) \iso  \Hh^1(\pi_0(\bG), \EEx)^{\Weil{}}
 \]
@@
 \[
-\Aut_{\QCS{}}(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
+\Aut(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
 \]
@@
 
-This paper shows that the \'etale site on $\Gr_R(X)$ is rich enough to geometrize all quasicharacters of $X(K)$ as $\ell$-adic local systems on $\Gr_R(X)$, where $X$ is a Neron model for an algebraic torus or an abelian variety over a local field $K$.
-It is natural to ask if the \'etale site on the generic fibre $X_K$ would have sufficed. 
-Even the case $X_K = \Gm{K}$ shows that the answer is no [add internal reference].
-
-[Add reference to Takaski Suzuki's paper]
+Also mention: \cite{suzuki-yoshida:12a},\cite{Suzuki:Neron} and \cite{Cunningham-Kamgarpour}.
 
@@
 \[
-\Aut_{\QCS(\pi_0(T))}(\cs{E})\iso (\check{T}_\ell)^{\Weil{K}},
+\Aut(\cs{E})\iso (\check{T}_\ell)^{\Weil{K}},
 \quad
-\Aut_{\QCS(T)}(\cs{F})\iso (\check{T}_\ell)^{\Weil{K}},
+\Aut(\cs{F})\iso (\check{T}_\ell)^{\Weil{K}},
 \quad
-\Aut_{\QCS(T^0)}(\cs{F}^0)\iso 1,
+\Aut(\cs{F}^0)\iso 1,
 \]
@@
 \begin{proof}
-We already know $\Aut_{\QCS(T^0)}(\cs{E}) =1$ from Proposition~\ref{prop:connected}, part \ref{x3}.
-By Theorem~\ref{thm:CSXK}, $\Aut(\cs{F})  \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx)$, canonically, for $X = T$ and $X=\pi_0(T)$ (and for $X= T^0$, though that case has already been treated by a different argument, above).
+We already know $\Aut(\cs{E}) =1$ from Proposition~\ref{prop:connected}, part \ref{x3}.
+By Theorem~\ref{thm:CSXK}, 
+\[\Aut(\cs{F})  \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx),\] canonically, for $X = T$ and $X=\pi_0(T)$ (and for $X= T^0$, though that case has already been treated by a different argument, above).
 By \cite{bitan:discriminant}*{Eq 3.1} again, 
@@
 \[
-\Aut_{\QCS(T)}(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
+\Aut(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
 \]
@@
 
+\begin{remark}
 Combining Corollary~\ref{cor:CS_tori} with Lemma~\ref{lem:LLCT} now produces the following commutative diagram of exact sequences:
@@
 We have seen that the isomorphism $\QCS(\ZZ)\iso \Hom(\Weil{\Fq}, \EEx)$ is elementary. 
-The isomorphism $\QCSiso{\Gm{R}}\iso \Hom(\mathcal{I}_K, \EEx)$ may be deduced directly from the class field theory of Serre and Hezewinkel.
-The monoidal category of character sheaves on $\Gr^R_n(\Gm{R})$ is canonically equivalent to the category of $\ell$-adic characters of the equivariant etale fundamental group $\pi_1^\text{eq}(\Gr^R_n(\Gm{R}),\bFq)$.
-%and, using the Lang isogeny, that there is a canonical isomorphism 
-%\[\pi_1^\text{eq}(\Gr^R_n(\Gm{R}),\bFq) \iso \Gr^R_n(\Gm{R})(\Fq) = R_n^*.\]
+The isomorphism $\QCSiso{\Gm{R}}\iso \Hom(\mathcal{I}_K, \EEx)$ may be deduced directly from the class field theory of Serre and Hezewinkel as revisited beautifully in \cite{suzuki-yoshida:12a}; see also \cite{Suzuki:Neron}.
+The monoidal category of character sheaves on $\Gr^R_n(\Gm{R})$ is canonically equivalent to the category of $\ell$-adic characters of the quotient of the etale fundamental group $\pi_1(\Gr^R_n(\Gm{R}),\bFq)$ determined by the Lang isogeny for $\Gr^R_n(\Gm{R})$.
 Accordingly, quasicharacter sheaves on $\Gm{R}$ may be apprehended as $\ell$-adic characters of
-the inverse limit of the groups $\pi_1^\text{eq}(\Gr^R_n(\Gm{R}),\bFq)$, as $n$ ranges over $\NN$.
-By \cite{serre:isogenies}, there is a canonical isomorphism 
-\[
-\varprojlim_{n\in \NN} \pi_1^\text{eq}(\Gr^R_n(\Gm{R}),\bFq) \iso \mathcal{I}_K^\text{ab};
-\]
+the inverse limit of these quotients, as $n$ ranges over $\NN$.
+By \cite{serre:isogenies}, there is a canonical isomorphism between this inverse limit and $\mathcal{I}_K^\text{ab}$;
 this isomorphism is {\it not} restricted to the case when $K$ and $\Fq$ have equal characteristic.
-This last isomorphism now provides the isomorphism $\QCSiso{\Gm{R}}\iso \Hom(\mathcal{I}_K, \EEx)$ in \eqref{eq:Gm}. 
-Since the sequences are split, this gives \eqref{eq:Gm}, geometrically. 
-We have been glib here because all this is treated carefully and beautifully in \cite{suzuki-yoshida:12a}. 
-Indeed, in that paper, an isomorphism is constructed directly between the equivariant fundamental group of $\Gr_R(T)$ (with respect to a site defined in \cite{suzuki-yoshida:12a}) when $T$ is a Neron model of $\Gm{K}$, and $\Weil{K}^\text{ab}$, improving greatly on the arguments of this paragraph.
-
-We expect that the general case of \eqref{eq:GLCT}, where $K$ is any local field and $T_K$ is any torus over $K$, may be deduced from the case \eqref{eq:Gm}, by an adaptation of arguments from \cite{yu:09a}.
-In anticipation of work in that direction, Section~\ref{ssec:wrK} provides a key tool for that argument.
-
-We close this section with some further remarks on sites.
+This provides the isomorphism $\QCSiso{\Gm{R}}\iso \Hom(\mathcal{I}_K, \EEx)$ in \eqref{eq:Gm}. 
+Since the sequences are split, this gives $\QCSiso{T}\iso \Hom(\Weil{K}, \EEx)$.
+\end{remark}
+
+\begin{remark}
+This paper shows that the \'etale site on $\Gr_R(X)$ is rich enough to geometrize all quasicharacters of $X(K)$ as $\ell$-adic local systems on $\Gr_R(X)$, where $X$ is a Neron model for an algebraic torus or an abelian variety over a local field $K$.
+It is natural to ask if the \'etale site on the generic fibre $X_K$ would have sufficed. 
+This seems unlikely, since the geometric etale fundamental group of $\Gm{K}$ is ${\hat \ZZ}$, though limited results in this direction were established in \cite{Cunningham-Kamgarpour} when $K = \mathbb{Q}_p$.
+\end{remark}
 
 \subsection{Weil restriction and quasicharacter sheaves}\label{ssec:wrK}
+
+We expect that the general case of \eqref{eq:GLCT}, where $K$ is any local field and $T_K$ is any torus over $K$, may be deduced from the case \eqref{eq:Gm}.
+Some work in this direction appears in \cite{Suzuki:Neron}.
+In this section we develop a tool for further work in that direction.
 
@@
 \[ 
-\Hom_\text{CS}(X_K(K'),\EEx) \to \Hom_\text{CS}(X_K(K)),\EEx)
+\Hom_\text{}(X_K(K'),\EEx) \to \Hom_\text{}(X_K(K),\EEx)
 \]

### 2015-07-19 dictionary.tex
pi_0(\bG) vs \pi_0(G) x \bFq. Working on this.

@@
  \labitem{(2)}{c2} every character sheaf on $G$ is isomorphic to one defined by a discrete isogeny;
- \labitem{(3)}{c3} $\Aut_\CS{}(\cs{L}) = 1$, for all character sheaves $\cs{L}$ on $G$.
+ \labitem{(3)}{c3} $\Aut(\cs{L}) = 1$, for all character sheaves $\cs{L}$ on $G$.
  \end{enumerate}
@@
 \[
-\Aut_\CS{}(\cs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx).
+\Aut(\cs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx).
 \]
@@
 This category is additive, and includes all algebraic tori over $K$, abelian varieties over $K$ and unipotent $K$-wound groups.
+We write $\mathcal{N}$ for the category of Neron models that arise in this way; in particular, $\mathcal{N}$ is a full subcategory of the category of smooth commutative group schemes over $R$.
 
@@
 
-\subsection{Character sheaves on the Greenberg transform of a N\'eron model} \label{ssec:CS_on_GN}
-
-Let $X_K \in \mathcal{N}_K$ and $X$ be as above.
+\subsection{Quasicharacter sheaves}
+%{Character sheaves on the Greenberg transform of a N\'eron model} 
+\label{ssec:CS_on_GN}
+
+Let $X \in \mathcal{N}$ be as above.
 Set $S = \Spec{R}$ and $S_n = \Spec{R_n}$;
@@
 let $R$ be the ring of integers of $K$.
+Fix a separable closure ${\bar K}$ of $K$ and let $\tilde{K}$ be the maximal unramified extension of $K$ in ${\bar K}$; write $\tilde{R}$ for the ring of integers of $\tilde{K}$ and set $\tilde{S} = \Spec{\tilde{R}}$.
 \begin{enumerate}
@@
 \[
-F_{\QCS}: X_K \mapsto \QCSiso{X}
+%F_{\QCS}: 
+X \mapsto \QCSiso{X}
 \qquad\text{and}\qquad
-F_{\text{}}: X_K \mapsto \Hom_{\text{}}(X(K),\EEx)
-\]
-as functors from $\mathcal{N}_K$ to the category of commutative groups.
+%F_{\text{}}: 
+X \mapsto \Hom_{\text{}}(X(K),\EEx)
+\]
+as functors from $\mathcal{N}$ to the category of commutative groups.
 \end{enumerate} 
-Regarding this natural transformation, for every $X_K \in \mathcal{N}_K$ with N\'eron model $X$:
+Regarding this natural transformation, for every $X \in \mathcal{N}$:
 \begin{enumerate}[resume]
@@
 \labitem{(2)}{x2} for all quasicharacter sheaves $\cs{F}$, $\cs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\cs{F},\cs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
-\labitem{(3)}{x3} for all quasicharacter sheaves $\cs{F}$ for $X_K$, there is a canonical isomorphism
-\[
-\Aut(\cs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{\Fq}},\EEx).
+\labitem{(3)}{x3} for all quasicharacter sheaves $\cs{F}$ for $X$, there is a canonical isomorphism
+\[
+\Aut(\cs{F}) \iso \Hom(\pi_0(X \times_S \tilde{S})_{\Weil{\Fq}},\EEx)
 \]
@@
 To prove \ref{x2}, argue as in the proof of Lemma~\ref{lem:autornaught}.
-To prove \ref{x3}, use Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, the fact that the component group of $\Gr^R_n(X)$ is independent of $n$ and then argue as in part \ref{x0}.
+To prove \ref{x3}, use: the fact that the component group of $\Gr^R_n(X)$ is independent of $n$; Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, in which case $\pi_0(G) = \pi_0(X \times_S S_0)$ and $\pi_0(\bG) = \pi_0(X \times_S \tilde{S})$; and then argue as in part \ref{x0}.
 %\end{enumerate}
@@
 As we explained in the Introduction, our original motivation for this paper was to find a geometrization and categorification of quasicharacters of $p$-adic tori. 
-This is now provided by specializing Theorem~\ref{thm:CSXK} to the case when $X_K\in \mathcal{N}_K$ is an algebraic torus over $K$.
+This is now provided by the following adaptation of Theorem~\ref{thm:CSXK} in the case when $T\in \mathcal{N}$ is a Neron model for an algebraic torus over $K$.
 
@@
 By Theorem~\ref{thm:CSXK}, 
-\[\Aut(\cs{F})  \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{}},\EEx),\] canonically, for $X = T$ and $X=\pi_0(T)$ (and for $X= T^0$, though that case has already been treated by a different argument, above).
+\[\Aut(\cs{F})  \iso \Hom((\pi_0(X \times_S \tilde{S})_{\Weil{\Fq}},\EEx),\] canonically, for $X = T$ and $X=\pi_0(T)$ (and for $X= T^0$, though that case has already been treated by a different argument, above).
 By \cite{bitan:discriminant}*{Eq 3.1} again, 

### 2015-07-19 dictionary.tex
Toris?!?

@@
 \begin{theorem*}[{Thm. \ref{thm:snake}}]
-If $G$ is a smooth commutative group scheme over $\Fq$ then
-\[
-\TrFrob{G} : \CSiso{G} \to G(\Fq)^*
-\]
-is surjective with kernel $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
+If $G$ is a smooth commutative group scheme over $\Fq$ then the trace of Frobenius gives a short exact sequence
+\[
+\begin{tikzcd}
+0 \arrow{r} & \Hh^2(\pi_0(\bG),\EEx)^{\Weil{}} \arrow{r} & \CSiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0.
+\end{tikzcd}
+\]
 \end{theorem*}
@@
 and $\ker \TrFrob{\pi_0(G)} \to \ker \TrFrob{G}$ is an isomorphism.
-This gives the short exact sequence
+This gives the promised short exact sequence
 \[
   \begin{tikzcd}
-0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx)) \arrow{r} & \CSiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0. 
+0 \arrow{r} & \Hh^2(\pi_0(\bG),\EEx)^{\Weil{}} \arrow{r} & \CSiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0. 
   \end{tikzcd}
@@
 \begin{corollary}\label{cor:CS_tori}
-Let $T_K$ be an algebraic toris over $K$ and let $T$ be a Neron model for $T_K$.
+Let $T$ be a Neron model for an algebraic torus over $K$.
 The following is a commutative diagram of exact sequences.
@@
 \begin{corollary}
-Let $T_K$ be an algebraic toris over $K$ and let $T$ be a Neron model for $T_K$.
+Let $T$ be a Neron model for an algebraic torus over $K$.
 For $\cs{E}\in \QCS(\pi_0(T))$, $\cs{F}\in {\QCS(T)}$ and $\cs{F}^0\in {\QCS(T^0)}$, there are canonical isomorphisms
@@
 
-\subsection{Geometric perspective on the Langlands correspondence for $p$-adic tori}\label{ssec:LLCT}
+\subsection{Geometric Langlands correspondence for $p$-adic tori}\label{ssec:LLCT}
 

### 2015-07-19 dictionary.tex
Fixed that last point. New sections.

@@
 We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and drawing our attention to their result on Weil restriction and the Greenberg transform.
-We thank Joseph Bernstein for suggesting a connection between our category of quasicharacter sheaves for $p$-adic tori and quasicharacters of its pure rational forms.}
+We thank Joseph Bernstein for very helpful comments. 
+%suggesting a connection between our category of quasicharacter sheaves for $p$-adic tori and quasicharacters of its pure rational forms.
+}
 
@@
 
-\section{Character Sheaves on commutative group schemes and recollections for connected algebraic groups} \label{sec:category}
+\section{Character Sheaves on commutative group schemes} \label{sec:category}
 
@@
 
-\subsection{The function-sheaf dictionary for connected algebraic groups over finite fields}\label{ssec:connected}
+\section{Recollections for connected algebraic groups}\label{ssec:connected}
+
+%\subsection{The function-sheaf dictionary for connected algebraic groups over finite fields}\label{ssec:connected}
 
@@
 
-\subsection{Examples}
-
 \section{Character sheaves on \'etale commutative group schemes} \label{sec:etale}
@@
 
-\subsection{The dictionary for commutative algebraic groups over finite fields}
-
-\subsection{Examples}
+\section{The dictionary for commutative algebraic groups over finite fields}
 
@@
 
-\begin{definition}
+\begin{definition}\label{def:QCS}
 Let $X$ be a smooth group scheme over $R$, with $R$ as above.
@@
 let $R$ be the ring of integers of $K$.
-Fix a separable closure ${\bar K}$ of $K$ and let $\tilde{K}$ be the maximal unramified extension of $K$ in ${\bar K}$; write $\tilde{R}$ for the ring of integers of $\tilde{K}$ and set $\tilde{S} = \Spec{\tilde{R}}$.
+%Fix a separable closure ${\bar K}$ of $K$ and let $\tilde{K}$ be the maximal unramified extension of $K$ in ${\bar K}$; write $\tilde{R}$ for the ring of integers of $\tilde{K}$ and set $\tilde{S} = \Spec{\tilde{R}}$.
 \begin{enumerate}
@@
 \[
-\Aut(\cs{F}) \iso \Hom(\pi_0(X \times_S \tilde{S})_{\Weil{\Fq}},\EEx)
+\Aut(\cs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{\Fq}},\EEx)
 \]
@@
 To prove \ref{x2}, argue as in the proof of Lemma~\ref{lem:autornaught}.
-To prove \ref{x3}, use: the fact that the component group of $\Gr^R_n(X)$ is independent of $n$; Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, in which case $\pi_0(G) = \pi_0(X \times_S S_0)$ and $\pi_0(\bG) = \pi_0(X \times_S \tilde{S})$; and then argue as in part \ref{x0}.
+To prove \ref{x3}, use: the fact that the component group of $\Gr^R_n(X)$ is independent of $n$; Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, in which case $\pi_0(G) = \pi_0(X \times_S S_0)$ and $\pi_0(\bG) = \pi_0(X)_{\bFq}$; then argue as in part \ref{x0}.
 %\end{enumerate}
@@
 \begin{proof} 
-The horizontal sequence of groups coming from categories of quasicharacter sheaves is exact by Proposition~\ref{prop:middleexact}, together with the observation that the functors $\pi_0^*$ and $\iota^*$ perverse limits.
+The horizontal sequence of groups coming from categories of quasicharacter sheaves is exact by Proposition~\ref{prop:middleexact}, together with the observation that the functors $\pi_0^*$ and $\iota^*$ preserve limits.
 It is elementary that the horizontal sequence of quasicharacters is exact.
-The diagram commutes by Lemma~\ref{lem:pullback}.
 Accordingly, by Theorem~\ref{thm:CSXK}, the kernel of $\TrFrob{T}$ is $\Hh^2(\pi_0(T)_{\bFq},\EEx)^{\Weil{}}$. 
@@
 \] 
-which coincides with the kernel of $\TrFrob{\pi_0(T)}$ since $\pi_0(\pi_0(T))_{\bFq} = \pi_0(T)_{\bFq}$.
+Thus, the middle vertical sequence is exact.
+Since $T^0$ and $\pi_0(T)$ do not lie in $\mathcal{N}$, we cannot use Theorem~\ref{thm:CSXK} to determine the image and trace of Frobenius for these schemes. 
+Instead, we observe that $T^0$ and $\pi_0(T)$ are smooth commutative group schemes over $R$, so Definition~\ref{def:QCS} gives meaning to categories $\QCS(T^0)$ and $\QCS(\pi_0(T))$, and, moreover, that $\pi_0(\Gr^R_n(T^0))= \pi_0(T^0)_{\Fq} = 1$ and $\pi_0(\Gr^R_n(\pi_0(T)) = \pi_0(T)_{\Fq}$ are both independent of $n$.
+It follows that the vertical sequences through $\QCSiso{T^0}$ and $\QCSiso{\pi_0(T)}$ are exact by Theorem~\ref{thm:snake} and Definition~\ref{def:QCS}.
+The diagram commutes by Lemma~\ref{lem:pullback}.
 \end{proof}
@@
 By Theorem~\ref{thm:CSXK}, 
-\[\Aut(\cs{F})  \iso \Hom((\pi_0(X \times_S \tilde{S})_{\Weil{\Fq}},\EEx),\] canonically, for $X = T$ and $X=\pi_0(T)$ (and for $X= T^0$, though that case has already been treated by a different argument, above).
+\[
+\Aut(\cs{F})  \iso \Hom((\pi_0(T)_{\bFq})_{\Weil{\Fq}},\EEx).
+\]
 By \cite{bitan:discriminant}*{Eq 3.1} again, 
 \[
-\Hom((\pi_0(T)_{\bFq})_{\Weil{}},\EEx) \iso
-\Hom(X_*(T_K)_{\Weil{K}},\EEx),
+\Hom((\pi_0(T)_{\bFq})_{\Weil{\Fq}},\EEx) \iso
+\Hom(X_*(T_K)_{\Weil{K}},\EEx).
+\]
+But $\Hom(X_*(T_K)_{\Weil{K}},\EEx) \iso \Hom(X_*(T_K),\EEx)^{\Weil{K}}$.
+So, for any quasicharacter sheaf $\cs{F}$ for $T$,
+\[
+\Aut(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
 \]
 canonically.
-But $\Hom(X_*(T_K)_{\Weil{K}},\EEx) \iso \Hom(X_*(T_K),\EEx)^{\Weil{K}}$, canonically.
-So, for any quasicharacter sheaf $\cs{F}$ for $T$,
-\[
-\Aut(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
-\]
-canonically.
-The case $X= \pi_0(T)$ recovers the same automorphism group since $\pi_0(\pi_0(T))_{\bFq} = \pi_0(T)_{\bFq}$.
+The case $X= \pi_0(T)$ is handled by the same argument, replacing Theorem~\ref{thm:CSXK} with Theorem~\ref{thm:snake} and Definition~\ref{def:QCS}, as in the proof of Corollary~\ref{cor:CS_tori}, after observing that $\pi_0(\pi_0(T)_{\bFq}) = \pi_0(T)_{\bFq}$.
 \end{proof}

### 2015-07-20 dictionary.tex
Commit before lunch meeting at PIMS.

@@
 \begin{abstract}
-We consider the category of character sheaves on smooth commutative group schemes $G$ over finite fields $k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
-We show that the group of isomorphism classes of character sheaves is an extension of the group of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
-As an application, we find a category of sheaves for which isomorphism classes correspond to quasi\-characters of algebraic tori, abelian varieties and unipotent wound groups over non-Archimedean local fields.
-In this geometrization of quasicharacters, our sheaves are local systems on
-Greenberg transforms of locally finite type N\'eron models.
+We consider the rigid monoidal category of character sheaves on smooth commutative group schemes $G$ over finite fields $k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
+We find the group of isomorphism classes of character sheaves on $G$ and show that it is an extension of the group of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
+We also classify all morphisms in the category character sheaves on $G$.
+As an application, we study character sheaves on the Greenberg transforms of the locally finite type N\'eron models of algebraic tori over local fields; in doing so, we introduce `quasicharacter sheaves' and find a geometrization and categorification of quasi\-characters of $p$-adic tori.
 \end{abstract}
@@
 When commutative, such groups are extensions of finite cyclic groups by algebraic tori,
-in which case it is not difficult to relate Frobenius-stable character sheaves to our character sheaves.
+in which case it is not difficult to relate Frobenius-stable character sheaves to our character sheaves. %however, even in this case, the two notions are not quite identical.
 The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in that context.
 
-Also mention: \cite{suzuki-yoshida:12a},\cite{Suzuki:Neron} and \cite{Cunningham-Kamgarpour}.
+We anticipate that future work on quasicharacter sheaves will make use of   \cite{suzuki-yoshida:12a} and \cite{Suzuki:Neron}, and will clarify the relation between this project and other attempts to geometrize admissible distributions on $p$-adic groups, such as \cite{Cunningham-Kamgarpour} (limited quasicharacters of $\ZZ_p^*$) and \cite{Aubert-Cunningham} (limited to characters of depth-zero representations).
+We are actively pursuing the question of how to extend the notion of quasicharacter sheaves to provide a geometrization of admissible distributions on connected reductive algebraic groups over $p$-adic fields, not just commutative ones.
 
 \medskip
-\noindent\textbf{Acknowledgements.\ } {Pramod Achar, Masoud Kamgarpour and Hadi Salmasian
-allowed us to hijack much of a Research in Teams meeting at the Banff International Research Station into a discussion of
-character sheaves.  We thank them for their kindness, knowledge and invaluable help.
-We thank Takashi Suzuki for some very helpful observations and suggestions, especially related to our use of the Hochschild-Serre spectral sequence.
-We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and drawing our attention to their result on Weil restriction and the Greenberg transform.
-We thank Joseph Bernstein for very helpful comments. 
+\noindent\textbf{Acknowledgements.\ } {We thank Pramod Achar, Masoud Kamgarpour and Hadi Salmasian for 
+allowing us to hijack much of a Research in Teams meeting at the Banff International Research Station into a discussion of
+quasicharacter sheaves.  We also thank them for their kindness, knowledge and invaluable help.
+We thank Takashi Suzuki for clarifying the relation between this project and his recent work and for very helpful observations and suggestions, especially related to our use of the Hochschild-Serre spectral sequence.
+We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and for drawing our attention to their result on Weil restriction and the Greenberg transform.
+Finally, we thank Joseph Bernstein for very helpful comments. 
 %suggesting a connection between our category of quasicharacter sheaves for $p$-adic tori and quasicharacters of its pure rational forms.
@@
 
+\subsection{The dictionary for commutative algebraic groups over finite fields}
+
+Having extended the function--sheaf dictionary from connected commutative algebraic groups over $\Fq$ to smooth commutative group schemes $G$ over $\Fq$, we briefly look back to the case when $G$ is a commutative algebraic group.
+Although Weil sheaves are not necessary in that case, the dictionary is still not perfect, generally.
+
+\begin{corollary}\label{cor:alg_groups}
+Let $G$ be a commutative algebraic group over $\Fq$.
+All character sheaves on $G$ descend to $G$: $\CS(G)$ is equivalent to $\bCS(G)$ (\ref{ssec:bS}).
+The trace of Frobenius determines a short exact sequence
+\[
+\begin{tikzcd}
+0 \arrow{r} & \Hh^2(\pi_0(\bG),\EEx)^{\Weil{}} \arrow{r} & \bCSiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0.
+\end{tikzcd}
+\]
+The group $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ need not be trivial.
+\end{corollary}
+
+\begin{proof}
+Since $G(\Fq)$ is finite, the first statement follows from Propositions~\ref{prop:BG}
+ and \ref{prop:bounded}. The second statement is then a consequence of Theorem~\ref{thm:snake}. 
+ The third statement is justified by Example~\ref{eg:H2}.
+ \end{proof}
+
 \subsection{Base change}\label{ssec:basechange}
@@
 \end{proof}
-
-\section{The dictionary for commutative algebraic groups over finite fields}
 

### 2015-07-20 dictionary.tex
Starting to write down H2 computation

@@
       \newtheorem{remark}[theorem]{Remark}
+      \newtheorem{example}[theorem]{Example}
 
@@
 \newcommand{\EEx}{\EE^\times}
+\newcommand{\ZEx}{\mathbb{\bar Z}_\ell^\times}
 \newcommand{\Weil}[1]{\mathcal{W}_{#1}}
@@
 \newcommand{\gal}[1]{{\operatorname{Gal}\hskip-1pt\left( {\bar #1}/#1 \right)}}
-\newcommand{\Spec}[1]{{\operatorname{Spec}\hskip-1pt( #1 )}}
+\newcommand{\Spec}[1]{{\operatorname{Spec}(#1)}}
 %%%%%%%%%%%% MISCELLANEOUS OPERATORS %%%%%%%%%%%%
@@
 \renewcommand{\bf}{\bar{f}}
-\newcommand{\bg}{\bar{g}}
+\newcommand{\bg}{{\bar{g}}}
 \newcommand{\bm}{\bar{m}}
@@
 \newcommand{\brho}{{\bar\rho}}
+\newcommand{\bx}{{\bar{x}}}
 %% Spacing control
@@
 In this way we are led to the category $\CS(G)$ of {\it character sheaves} on $G$ (\S\ref{ssec:category}):
-objects in $\CS(G)$ are triples $(\gcs{L}, \mu,\phi)$, where $\gcs{L}$ is a rank-one local system on ${\bar G} := G\times_{\Spec{\Fq}} \Spec{\bFq}$
-and $\phi : \Frob{G}^* \gcs{L}\to \gcs{L}$ and $\mu : {\bar m}^* \gcs{L} \iso \gcs{L} \boxtimes \gcs{L}$ are isomorphisms of sheaves satisfying certain compatibility conditions;
+objects in $\CS(G)$ are triples $(\gcs{L}, \mu,\phi)$, where $\gcs{L}$ is a rank-one local system on $\bG := G\times_{\Spec{\Fq}} \Spec{\bFq}$
+and $\phi : \Frob{G}^* \gcs{L}\to \gcs{L}$ and $\mu : \bm^* \gcs{L} \iso \gcs{L} \boxtimes \gcs{L}$ are isomorphisms of sheaves satisfying certain compatibility conditions;
 morphisms in $\CS(G)$ are then morphisms of Weil sheaves which are compatible with the extra structure.
@@
 \[
-  0 \to \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to \Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to 0
+  0 \to \Hh^0(\Weil{},\Hh^2(\bG,\EEx)) \to \Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1(\bG,\EEx)) \to 0
 \]
@@
 in which case it is not difficult to relate Frobenius-stable character sheaves to our character sheaves. %however, even in this case, the two notions are not quite identical.
-The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$ do not arise in that context.
-
-We anticipate that future work on quasicharacter sheaves will make use of   \cite{suzuki-yoshida:12a} and \cite{Suzuki:Neron}, and will clarify the relation between this project and other attempts to geometrize admissible distributions on $p$-adic groups, such as \cite{Cunningham-Kamgarpour} (limited quasicharacters of $\ZZ_p^*$) and \cite{Aubert-Cunningham} (limited to characters of depth-zero representations).
+The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ do not arise in that context.
+
+We anticipate that future work on quasicharacter sheaves will make use of   \cite{suzuki-yoshida:12a} and \cite{Suzuki:Neron}, and will clarify the relation between this project and other attempts to geometrize admissible distributions on $p$-adic groups, such as \cite{Cunningham-Kamgarpour} (limited quasicharacters of $\ZZ_p^\times$) and \cite{Aubert-Cunningham} (limited to characters of depth-zero representations).
 We are actively pursuing the question of how to extend the notion of quasicharacter sheaves to provide a geometrization of admissible distributions on connected reductive algebraic groups over $p$-adic fields, not just commutative ones.
@@
 Suppose $\rho \in \Hom(\cs{L},\cs{L}')$.
-We prove the lemma by considering the linear transformations $\brho_{\bar g} : \gcs{L}_{\bar g} \to \gcs{L}_{\bar g}$ at the stalks above geometric points ${\bar g}$ on $G$ and showing that, either each $\brho_{\bar g}$ trivial or each $\brho_{\bar g}$ is an isomorphism.
+We prove the lemma by considering the linear transformations $\brho_{\bg} : \gcs{L}_{\bg} \to \gcs{L}_{\bg}$ at the stalks above geometric points $\bg$ on $G$ and showing that, either each $\brho_{\bg}$ trivial or each $\brho_{\bg}$ is an isomorphism.
 (This idea is expanded upon in Section~\ref{ssec:stalks}.)
 Let ${\bar e}$ be the geometric point above the identity $e$ for $G$ determined by our choice of algebraic closure $\bFq$ of $\Fq$.
-If $\brho_{\bar e} = 0$ then the second diagram in \ref{CS.4} implies that $\brho_{\bar g} = 0$ for all ${\bar g}$, in which case $\rho$ is trivial.
-On the other hand, if $\brho_{\bar e}$ is nontrivial then the second diagram in \ref{CS.4}  implies that $\brho_{\bar g}$ is nontrivial for all ${\bar g}$ and thus an isomorphism, since the stalk of character sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
+If $\brho_{\bar e} = 0$ then the second diagram in \ref{CS.4} implies that $\brho_{\bg} = 0$ for all $\bg$, in which case $\rho$ is trivial.
+On the other hand, if $\brho_{\bar e}$ is nontrivial then the second diagram in \ref{CS.4}  implies that $\brho_{\bg}$ is nontrivial for all $\bg$ and thus an isomorphism, since the stalk of character sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
 \end{proof}
@@
  Suppose $(\cs{E},\mu_\cs{E})$ in an object of $\bCS(G)$.
- Let $b_G : {\bar G} \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
+ Let $b_G : \bG \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
  Set $\gcs{L} = b_G^* \cs{E}$. 
@@
  \[
-  b_{G\times G}^* : \Hom(m^*\cs{E},\cs{E}\boxtimes\cs{E}) \to \Hom({\bar m}^*\gcs{L},\gcs{L}\boxtimes\gcs{L})
+  b_{G\times G}^* : \Hom(m^*\cs{E},\cs{E}\boxtimes\cs{E}) \to \Hom(\bm^*\gcs{L},\gcs{L}\boxtimes\gcs{L})
  \]
@@
   (hom taken in the categories on constructible $\ell$-adic sheaves on
-  $G\times G$ and ${\bar G}\times {\bar G}$ respectively,
+  $G\times G$ and $\bG\times \bG$ respectively,
   in which $\ell$-adic local systems sit as full subcategories).
   Let $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ be the isomorphism matching
-  $\mu : {\bar m}^*\gcs{L} \to \gcs{L}\boxtimes\gcs{L}$,
+  $\mu : \bm^*\gcs{L} \to \gcs{L}\boxtimes\gcs{L}$,
   the latter appearing in the definition of $\cs{L}$.
@@
 Let $\bg$ be a geometric point above $g \in G(\Fq)$.
-If $\cs{E}$ matches $\psi : G(\Fq)\to \EEx$ under this equivalence, a simple calculation on stalks reveals that the action of Frobenius on $\cs{E}_{\bar g}$ is multiplication by $\psi(g)^{-1}$.
+If $\cs{E}$ matches $\psi : G(\Fq)\to \EEx$ under this equivalence, a simple calculation on stalks reveals that the action of Frobenius on $\cs{E}_{\bg}$ is multiplication by $\psi(g)^{-1}$.
 In other words, for every $\cs{E}$ in $\bCS(G)$, the trace of $\Lang^*\cs{E}$ is $\trFrob{\cs{E}}^{-1}$ as a representation of $G(\Fq)$, proving parts \ref{c1} and \ref{c2}.
@@
     0 \to
-    \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to
+    \Hh^0(\Weil{},\Hh^2(\bG,\EEx)) \to
     \Hh^2(E^\bullet_G) \to
-    \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \to
+    \Hh^1(\Weil{},\Hh^1(\bG,\EEx)) \to
     0.
@@
 \item Every class $[\alpha\oplus\beta\oplus\gamma] \in \Hh^2(E^\bullet_G)$ is cohomologous to one with $\gamma=0$.
-\item The map $\Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1({\bar G},\EEx))$ is given by $[\alpha\oplus\beta\oplus 0] \mapsto [\beta]$.
-\item Suppose $a \in Z^2({\bar G}, \EEx)$ represents a class in $\Hh^2({\bar G},\EEx)$ fixed by Frobenius.
-The map $\Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \to \Hh^2(E^\bullet_G)$ is given by $[a] \mapsto [a \oplus 0 \oplus 0]$.
+\item The map $\Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1(\bG,\EEx))$ is given by $[\alpha\oplus\beta\oplus 0] \mapsto [\beta]$.
+\item Suppose $a \in Z^2(\bG, \EEx)$ represents a class in $\Hh^2(\bG,\EEx)$ fixed by Frobenius.
+The map $\Hh^0(\Weil{},\Hh^2(\bG,\EEx)) \to \Hh^2(E^\bullet_G)$ is given by $[a] \mapsto [a \oplus 0 \oplus 0]$.
 \end{enumerate}
@@
 \begin{proof}
-Since $\Hh^2(\Weil{}, C^0({\bar G}, \EEx)) = 0$, we may find a $\gamma_1 \in C^1(\Weil{}, C^0({\bar G}, \EEx))$ with $d_{\Weil{}}\gamma_1 = \gamma$.
+Since $\Hh^2(\Weil{}, C^0(\bG, \EEx)) = 0$, we may find a $\gamma_1 \in C^1(\Weil{}, C^0(\bG, \EEx))$ with $d_{\Weil{}}\gamma_1 = \gamma$.
 Subtracting $d \gamma_1$ from $\alpha\oplus\beta\oplus\gamma$, we may assume that $\gamma = 0$.
@@
 Let $\cs{L} = (\gcs{L},\mu,\phi)$ be a character sheaf on $G$.
-For each geometric point $x\in {\bar G}$, choose a basis $\{ v_x \}$ for $\gcs{L}_x$.
+For each geometric point $x\in \bG$, choose a basis $\{ v_x \}$ for $\gcs{L}_x$.
 Through this choice, $\cs{L}$ determines functions
 \begin{align*}
-a : {\bar G}\times {\bar G} &\to \EEx & b : {\bar G} &\to \EEx \\
+a : \bG\times \bG &\to \EEx & b : \bG &\to \EEx \\
 \mu_{x,y}(v_{x+y}) &= a(x,y) v_x \otimes v_y & \phi_x(v_{\Frob{G}(x)}) &= b(x) v_x.
@@
 \end{equation}
-for all $x,y,z\in {\bar G}$, so $a \in Z^2({\bar G},\EEx)$.  Similarly, condition~\ref{CS.3} gives
+for all $x,y,z\in \bG$, so $a \in Z^2(\bG,\EEx)$.  Similarly, condition~\ref{CS.3} gives
 \begin{equation}\label{nohom}
@@
 \end{equation}
-for $x, y \in {\bar G}$.
-Let $\alpha \in C^0(\Weil{},C^2({\bar G},\EEx)$ be the $0$-cochain corresponding to $a$ and let $\beta\in C^1(\Weil{},C^1({\bar G},\EEx)$ be the cocycle such that $\beta(\Frob{})$ is $b$.
+for $x, y \in \bG$.
+Let $\alpha \in C^0(\Weil{},C^2(\bG,\EEx)$ be the $0$-cochain corresponding to $a$ and let $\beta\in C^1(\Weil{},C^1(\bG,\EEx)$ be the cocycle such that $\beta(\Frob{})$ is $b$.
 We will write both $\alpha$ and $\beta$ additively.
@@
 Although the cocycle $\alpha\oplus \beta$ is not well defined by $\cs{L}$, its class in $\Hh^2(E^\bullet_G)$ is.
-To see this, let $\{ v'_x \in \gcs{L}_x^\times \tq x \in {\bar G}\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$ be defined by $\cs{L}$ and this choice, as above.
-Now let $\delta \in C^0(\Weil{},C^1({\bar G},\EEx))$ correspond to the function $d : {\bar G}\to \EEx$ defined by $v'_x = d(x) v_x$.
+To see this, let $\{ v'_x \in \gcs{L}_x^\times \tq x \in \bG\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$ be defined by $\cs{L}$ and this choice, as above.
+Now let $\delta \in C^0(\Weil{},C^1(\bG,\EEx))$ correspond to the function $d : \bG\to \EEx$ defined by $v'_x = d(x) v_x$.
 Chasing through \ref{CS.2} and \ref{CS.3}, we find
@@
 Suppose $[\cs{L}] \in \CSiso{G}$ with $S_G([\cs{L}]) = [\alpha \oplus \beta] = 0$,
-so that $\alpha \oplus \beta = d\sigma$ for some $\sigma \in C^0(\Weil{},C^1({\bar G},\EEx) = C^1({\bar G},\EEx)$.
-For each $x\in {\bar G}$, define $\sigma_x : \gcs{L}_x \to \EE$ by $\sigma_x : v_x \mapsto \sigma(x)$.
-Then the indexed set of isomorphisms $\{ \sigma_x : \gcs{L}_x \to \EE \tq x\in {\bar G}\}$
+so that $\alpha \oplus \beta = d\sigma$ for some $\sigma \in C^0(\Weil{},C^1(\bG,\EEx) = C^1(\bG,\EEx)$.
+For each $x\in \bG$, define $\sigma_x : \gcs{L}_x \to \EE$ by $\sigma_x : v_x \mapsto \sigma(x)$.
+Then the indexed set of isomorphisms $\{ \sigma_x : \gcs{L}_x \to \EE \tq x\in \bG\}$
 defines an isomorphism $\cs{L} \to (\EE)_G$.
@@
 To see that $S_G$ is surjective, begin with $\alpha\oplus\beta\oplus 0 \in Z^2(E^\bullet_G)$.
-Since $d_{\Weil{}} \beta = 0$, we may define $a = \alpha \in C^2({\bar G},\EEx)$ and
-$b = \beta(\Frob{}) \in C^1({\bar G},\EEx)$, which are related to $\alpha$ and $\beta$ as above.
+Since $d_{\Weil{}} \beta = 0$, we may define $a = \alpha \in C^2(\bG,\EEx)$ and
+$b = \beta(\Frob{}) \in C^1(\bG,\EEx)$, which are related to $\alpha$ and $\beta$ as above.
 Set $\gcs{L}_x = \EE$, define $\mu_{x,y} : \gcs{L}_{x+y} \to \gcs{L}_x\otimes\gcs{L}_y$
@@
  0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \CSiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
-  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r} & 0.
+  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\bG,\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1(\bG,\EEx)) \arrow{r} & 0.
  \end{tikzcd}
@@
 \end{proof}
+
+\begin{example} \label{eg:H2}
+Suppose that $\bG$.
+\end{example}
 
@@
 Let $G$ be a commutative etale group scheme over $\Fq$.
-Then the image of $\bCS(G)$ under $\TrFrob{G} : \CS(G) \to G(\Fq)^*$ is $\Hom_\text{grp}(G(\Fq),\mathbb{\bar Z}_{\ell}^\times)$.
+Then the image of $\bCS(G)$ under $\TrFrob{G} : \CS(G) \to G(\Fq)^*$ is $\Hom_\text{grp}(G(\Fq),\ZEx)$.
 \end{proposition}
@@
     0 \to
-    \Hh^0(\Fq,\Hh^2({\bar G},\EEx)) \to
+    \Hh^0(\Fq,\Hh^2(\bG,\EEx)) \to
     \Hh^2(F^\bullet_G) \to
-    \Hh^1(\Fq,\Hh^1({\bar G},\EEx)) \to
+    \Hh^1(\Fq,\Hh^1(\bG,\EEx)) \to
     0,
@@
     0 \arrow{r} &
-    \Hh^0(\Fq,\Hh^2({\bar G},\EEx)) \arrow{r} \arrow{d} &
+    \Hh^0(\Fq,\Hh^2(\bG,\EEx)) \arrow{r} \arrow{d} &
     \Hh^2(F^\bullet_G) \arrow{r} \arrow{d} &
-    \Hh^1(\Fq,\Hh^1({\bar G},\EEx)) \arrow{r} \arrow{d} &
+    \Hh^1(\Fq,\Hh^1(\bG,\EEx)) \arrow{r} \arrow{d} &
     0
@@
     0 \arrow{r} & 
-    \Hh^0(\Weil{},\Hh^2({\bar G},\EEx)) \arrow{r} & 
+    \Hh^0(\Weil{},\Hh^2(\bG,\EEx)) \arrow{r} & 
     \Hh^2(E^\bullet_G) \arrow{r} & 
-    \Hh^1(\Weil{},\Hh^1({\bar G},\EEx)) \arrow{r} &
+    \Hh^1(\Weil{},\Hh^1(\bG,\EEx)) \arrow{r} &
     0.
@@
 \[
-\Hh^1(\Fq,\Hh^1({\bar G},\EEx)) = \Hom_\text{grp}(G(\Fq),\mathbb{\bar Z}_{\ell}^\times).
+\Hh^1(\Fq,\Hh^1(\bG,\EEx)) = \Hom_\text{grp}(G(\Fq),\ZEx).
 \]
@@
 We remark that while $G^i$ is defined over $\Fq$, the set $G^i(\Fq)$ is non-empty only when $G^i(\bFq) = \{ {\bar x}^i\}$.
-Since $\Hh^1({\bar G},\EEx) = \Hom_\text{grp}({\bar G},\EEx)$, evaluation $\chi \mapsto \chi({\bar x}^i)$ defines $\Hh^1(\Fq,\Hh^1({\bar G},\EEx)) \to \Hh^1(\Fq,\EEx)$. 
-By continuity, $\Hh^1(\Fq,\EEx) = \Hh^1(\Fq,\mathbb{\bar Z}_{\ell}^\times)$.
-Letting $i$ range over $\pi_0(G)$ we conclude that $\Hh^1(\Fq,\Hh^1({\bar G},\EEx)) = \Hh^1(\Fq,\Hh^1({\bar G},\mathbb{\bar Z}_{\ell}^\times))$.
-When adapted to abelian groups with continuous action of $\Gal(\bFq/\Fq)$, the strategy of the proof of Lemma~\ref{lem:dual-inv} gives $\Hh^1(\Fq,\Hh^1({\bar G},\mathbb{\bar Z}_{\ell}^\times)) =  \Hom_\text{grp}(G(\Fq),\mathbb{\bar Z}_{\ell}^\times)$, concluding the proof.
+Since $\Hh^1(\bG,\EEx) = \Hom_\text{grp}(\bG,\EEx)$, evaluation $\chi \mapsto \chi({\bar x}^i)$ defines $\Hh^1(\Fq,\Hh^1(\bG,\EEx)) \to \Hh^1(\Fq,\EEx)$. 
+By continuity, $\Hh^1(\Fq,\EEx) = \Hh^1(\Fq,\ZEx)$.
+Letting $i$ range over $\pi_0(G)$ we conclude that $\Hh^1(\Fq,\Hh^1(\bG,\EEx)) = \Hh^1(\Fq,\Hh^1(\bG,\ZEx))$.
+When adapted to abelian groups with continuous action of $\Gal(\bFq/\Fq)$, the strategy of the proof of Lemma~\ref{lem:dual-inv} gives $\Hh^1(\Fq,\Hh^1(\bG,\ZEx)) =  \Hom_\text{grp}(G(\Fq),\ZEx)$, concluding the proof.
 \end{proof}
@@
   \]
-is surjective with kernel canonically isomorphic to $\Hh^2(\pi_0({\bar G}),\EEx)^{\Weil{}}$.
+is surjective with kernel canonically isomorphic to $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
 \end{theorem}
@@
   imply that $\ker \TrFrob{G^0} =0$ and $\coker \TrFrob{G^0}=0$,
-  while Proposition~\ref{prop:etale-iso} gives $\ker \TrFrob{\pi_0(G)} \iso \Hh^0(\Weil{},\Hh^2(\pi_0({\bar G}),\EEx))$
+  while Proposition~\ref{prop:etale-iso} gives $\ker \TrFrob{\pi_0(G)} \iso \Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx))$
   and $\coker \TrFrob{\pi_0(G)}=0$.

### 2015-07-20 dictionary.tex
Folded most of LLC into QCS for p-adic tori.

@@
 The necessity of using Weil local systems on $G$ in the definition of $\CS(G)$ already appears here:  if one were to use local systems on $G$ instead, the group homomorphism $\TrFrob{G}$ would not then be surjective (\S \ref{ssec:bS}).
-One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is finite cyclic, so the kernel of $\TrFrob{G}$ is non-trivial in general.
+One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic, so the kernel of $\TrFrob{G}$ is non-trivial in general.
 %The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gcs{L}, \mu,\phi)$ and $(\gcs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gcs{L},\phi)$ and $(\gcs{L}',\phi')$ are isomorphic as Weil sheaves.
@@
 \noindent
-Thus, unless the component group scheme $\pi_0(\bG)$ is finite cyclic, category $\CS(G)$ contains non-trivial character sheaves lying in the kernel of the trace of Frobenius and therefore lost in translation to characters of $G(\Fq)$.
+Thus, unless the component group scheme $\pi_0(\bG)$ is cyclic, category $\CS(G)$ contains non-trivial character sheaves lying in the kernel of the trace of Frobenius and therefore lost in translation to characters of $G(\Fq)$.
 %These {\it invisible character sheaves} are parametrized by $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
@@
 
+Add comment relating to Lusztig . . . .
+
 \subsection{Base change}\label{ssec:basechange}
@@
 
+ \begin{remark}
+This paper shows that the \'etale site on $\Gr_R(X)$ is rich enough to geometrize all quasicharacters of $X(K)$ as $\ell$-adic local systems on $\Gr_R(X)$, where $X$ is a Neron model for an algebraic torus or an abelian variety over a local field $K$.
+It is natural to ask if the \'etale site on the generic fibre $X_K$ would have sufficed. 
+This seems unlikely, since the geometric etale fundamental group of $\Gm{K}$ is ${\hat \ZZ}$, though limited results in this direction were established in \cite{Cunningham-Kamgarpour} when $K = \mathbb{Q}_p$.
+\end{remark}
+
 Let $X \in \mathcal{N}$ be as above.
@@
 \begin{definition}\label{def:QCS}
-Let $X$ be a smooth group scheme over $R$, with $R$ as above.
+Let $X$ be a smooth commutative group scheme over $R$, with $R$ as above.
 A {\it quasicharacter sheaf for $X$} is an object of
@@
     & \QCSiso{T} \arrow{r}{\iota_0^*}  \arrow{d}{\TrFrob{\Gr_R(T)}} & \QCSiso{T^0} \arrow{r} \arrow{d}{\TrFrob{\Gr_R(T)^0}} & 0\\
-    0 \arrow{r} & \Hom(\pi_0(T)(\Fq), \EEx) \arrow{r}{\text{infl'n}} \arrow{d}{\iso}
-    & \arrow{d}{\iso} \Hom_\text{}(T(K),\EEx) \arrow{r}{\text{rest'n}} & \Hom_\text{}(T^0(R),\EEx) \arrow{r} \arrow{d}{\iso} & 0\\
+    0 \arrow{r} & \Hom(\pi_0(T)(\Fq), \EEx) \arrow{r}{\text{inf}} \arrow{d}{\iso}
+    & \arrow{d}{\iso} \Hom_\text{}(T(K),\EEx) \arrow{r}{\text{res}} & \Hom_\text{}(T^0(R),\EEx) \arrow{r} \arrow{d}{\iso} & 0\\
  &  0  & 0 & 0 & 
@@
 
-\subsection{Geometric Langlands correspondence for $p$-adic tori}\label{ssec:LLCT}
-
-\begin{lemma}\label{lem:LLCT}
-The following diagram commutes. 
-\[
-\begin{tikzcd}
-   0 \arrow{r} & \Hom(\pi_0(T)(\Fq), \EEx) \arrow{r}{\text{infl'n}} \arrow{d}{\iso}
-    & \arrow{d}{\iso} \Hom_\text{}(T(K),\EEx) \arrow{r}{\text{rest'n}} & \Hom_\text{}(T^0(R),\EEx) \arrow{r} \arrow{d}{\iso} & 0\\    
-    0 \arrow{r}  
- & \Hh^1(\Weil{\Fq}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{infl'n}}
- & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{rest'n}} 
- & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{\Fq}} \arrow{r}  
- & 0
-\end{tikzcd}
-\] 
-\end{lemma}
-\begin{proof}
-Since $\pi_0(T)_{\bFq} = X_*(T_K)_{\mathcal{I}_K}$ by \cite{bitan:discriminant}*{Eq 3.1}, the isomorphism on the left can be seen directly:
+\begin{remark}
+Since $\pi_0(T)_{\bFq} = X_*(T_K)_{\mathcal{I}_K}$ by \cite{bitan:discriminant}*{Eq 3.1}, we have
 \[\Hom(\pi_0(T)(\Fq), \EEx)
@@
 \]
-The middle isomorphism is the Langlands correspondence for $p$-adic tori, itself a fairly direct consequence of local class field theory; see \cite{yu:09a}, for example. The isomorphism 
-\[
-\Hom_\text{}(T^0(R),\EEx) \iso \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{\Fq}}
-\] 
-and the commutativity of the diagram is then a consequence of the inflation-restriction exact sequence and the fact that $\Weil{}$ has cohomological dimension $1$.
-\end{proof}
-
-\begin{remark}
-Combining Corollary~\ref{cor:CS_tori} with Lemma~\ref{lem:LLCT} now produces the following commutative diagram of exact sequences:
+By the Langlands correspondence for $p$-adic tori \cite{yu:09a}, 
+\[
+\Hom(T(K), \EEx) 
+\iso 
+\Hh^1(\Weil{K}, \check{T}_\ell),
+\]
+where we refer to continuous cohomology, since $\Hom(T(K), \EEx)$ refers to continuous homomorphisms $T(K)\to \EEx$.
+It now follows from the inflation-restriction exact sequence that the following diagram commutes.
+\[
+\begin{tikzcd}
+   0 \arrow{r} & \Hom(\pi_0(T)(\Fq), \EEx) \arrow{r}{\text{inf}} \arrow{d}{\iso}
+    & \arrow{d}{\iso} \Hom_\text{}(T(K),\EEx) \arrow{r}{\text{res}} & \Hom_\text{}(T^0(R),\EEx) \arrow{r} \arrow{d}{\iso} & 0\\    
+    0 \arrow{r}  
+ & \Hh^1(\Weil{\Fq}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{inf}}
+ & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{res}} 
+ & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{\Fq}} \arrow{r}  
+ & 0
+\end{tikzcd}
+\] 
+Combining this with Corollary~\ref{cor:CS_tori}  produces the following commutative diagram of exact sequences:
 \begin{equation}\label{eq:GLCT}
@@
    0 \arrow{r}  
- & \Hh^1(\Weil{\Fq}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{infl'n}} \arrow{d}
- & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{rest'n}} \arrow{d}
+ & \Hh^1(\Weil{\Fq}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{inf}} \arrow{d}
+ & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{res}} \arrow{d}
  & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{\Fq}} \arrow{r} \arrow{d}  
@@
  \end{equation}
-It is natural to ask if the vertical surjections can be defined directly, without making use of local class field theory.  
+It is natural to ask if the vertical surjections can be defined directly, without making use of local class field theory, for which the results of \cite{suzuki-yoshida:12a}  and \cite{Suzuki:Neron} may be helpful.
 The case $T_K = \Gm{K}$ is already very interesting, in which case \eqref{eq:GLCT} becomes
@@
     0 \rar & \QCSiso{\ZZ} \arrow{r}{\pi_0^*} \arrow{d}{\iso}
-    & \QCSiso{T} \arrow{r}{\iota_0^*}  \arrow{d}{\iso} & \QCSiso{\Gm{R}} \arrow{r} \arrow{d}{\iso} & 0\\
+    & \QCSiso{\Gm{K}^\text{Neron}} \arrow{r}{\iota_0^*}  \arrow{d}{\iso} & \QCSiso{\Gm{R}} \arrow{r} \arrow{d}{\iso} & 0\\
     0 \arrow{r}  
- & \Hom(\Weil{\Fq}, \EEx) \arrow{r}{\text{infl'n}}
- & \Hom(\Weil{K}, \EEx) \arrow{r}{\text{rest'n}} 
+ & \Hom(\Weil{\Fq}, \EEx) \arrow{r}{\text{inf}}
+ & \Hom(\Weil{K}, \EEx) \arrow{r}{\text{res}} 
  & \Hom(\mathcal{I}_K, \EEx) \arrow{r}  
@@
 \end{equation}
-We have seen that the isomorphism $\QCS(\ZZ)\iso \Hom(\Weil{\Fq}, \EEx)$ is elementary. 
+%We have seen that the isomorphism $\QCS(\ZZ)\iso \Hom(\Weil{\Fq}, \EEx)$ is elementary.
 The isomorphism $\QCSiso{\Gm{R}}\iso \Hom(\mathcal{I}_K, \EEx)$ may be deduced directly from the class field theory of Serre and Hezewinkel as revisited beautifully in \cite{suzuki-yoshida:12a}; see also \cite{Suzuki:Neron}.
 The monoidal category of character sheaves on $\Gr^R_n(\Gm{R})$ is canonically equivalent to the category of $\ell$-adic characters of the quotient of the etale fundamental group $\pi_1(\Gr^R_n(\Gm{R}),\bFq)$ determined by the Lang isogeny for $\Gr^R_n(\Gm{R})$.
-Accordingly, quasicharacter sheaves on $\Gm{R}$ may be apprehended as $\ell$-adic characters of
-the inverse limit of these quotients, as $n$ ranges over $\NN$.
-By \cite{serre:isogenies}, there is a canonical isomorphism between this inverse limit and $\mathcal{I}_K^\text{ab}$;
-this isomorphism is {\it not} restricted to the case when $K$ and $\Fq$ have equal characteristic.
+Accordingly, quasicharacter sheaves on $\Gm{R}$ may be apprehended as $\ell$-adic characters of the inverse limit of these quotients, as $n$ ranges over $\NN$.
+By \cite{serre:isogenies}, there is a canonical isomorphism between this inverse limit and $\mathcal{I}_K^\text{ab}$; this isomorphism is {\it not} restricted to the case when $K$ and $\Fq$ have equal characteristic.
 This provides the isomorphism $\QCSiso{\Gm{R}}\iso \Hom(\mathcal{I}_K, \EEx)$ in \eqref{eq:Gm}.
 Since the sequences are split, this gives $\QCSiso{T}\iso \Hom(\Weil{K}, \EEx)$.
+We suspect that the general case of \eqref{eq:GLCT}, where $K$ is any local field and $T_K$ is any torus over $K$, may be deduced from \eqref{eq:Gm}.
+In Section~\ref{ssec:wrK} we develop a tool for further work in that direction.
 \end{remark}
 
-\begin{remark}
-This paper shows that the \'etale site on $\Gr_R(X)$ is rich enough to geometrize all quasicharacters of $X(K)$ as $\ell$-adic local systems on $\Gr_R(X)$, where $X$ is a Neron model for an algebraic torus or an abelian variety over a local field $K$.
-It is natural to ask if the \'etale site on the generic fibre $X_K$ would have sufficed. 
-This seems unlikely, since the geometric etale fundamental group of $\Gm{K}$ is ${\hat \ZZ}$, though limited results in this direction were established in \cite{Cunningham-Kamgarpour} when $K = \mathbb{Q}_p$.
-\end{remark}
-
 \subsection{Weil restriction and quasicharacter sheaves}\label{ssec:wrK}
-
-We expect that the general case of \eqref{eq:GLCT}, where $K$ is any local field and $T_K$ is any torus over $K$, may be deduced from the case \eqref{eq:Gm}.
-Some work in this direction appears in \cite{Suzuki:Neron}.
-In this section we develop a tool for further work in that direction.
 

### 2015-07-20 dictionary.tex
Adding H2 computation

--- 2015-07-20 dictionary.tex
@@
 
-      \theoremstyle{remark}
+      %\theoremstyle{remark}
       \newtheorem{remark}[theorem]{Remark}
@@
 \DeclareMathOperator{\Tot}{Tot}
+\DeclareMathOperator{\Tor}{Tor}
 \newcommand{\gal}[1]{{\operatorname{Gal}\hskip-1pt\left( {\bar #1}/#1 \right)}}
@@
 \begin{abstract}
-We consider the rigid monoidal category of character sheaves on smooth commutative group schemes $G$ over finite fields $k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
+We consider the rigid monoidal category of character sheaves on a smooth commutative group scheme $G$ over a finite field $k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
 We find the group of isomorphism classes of character sheaves on $G$ and show that it is an extension of the group of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
@@
 \begin{example} \label{eg:H2}
-Suppose that $\bG$.
+Recall the K\"unneth formula in group cohomology \cite{brown:CohomologyOfGroups}*{Prop. I.0.8}: if $A$ and $A'$ are groups and $M$ and $M'$ are abelian groups with $M$ $\ZZ$-free, then
+\[
+\Hh^n(A \times A', M \otimes M') \cong \bigoplus_{i+j=n} \Hh^i(A, M) \otimes \Hh^j(A', M') \ \ \oplus \bigoplus_{i+j=n+1} \Tor_1^{\ZZ}\left(\Hh^i(A, M), \Hh^j(A', M')\right).
+\]
+
+Now suppose $\bG = \ZZ^r \times \prod_{i = 1}^m \ZZ/N_i\ZZ$ is an arbitrary finitely generated abelian group, with $N_i \mid N_{i+1}$.  Then the K\"unneth formula implies that
+\[
+\Hh^2(\bG, \EEx) \cong \left(\EEx\right)^{r(r-1)/2} \times \prod_{i=1}^m (\ZZ/N_i\ZZ)^{m+r-i}.
+\]
+We see that $\Hh^2(\bG, \EEx)$ is trivial if and only if $\bG$ is cyclic.  Of course, $\Hh^0(\Weil{}, \Hh^2(\bG, \EEx))$ may or may not be trivial, even when $\Hh^2(\bG, \EEx)$ is nontrivial.
 \end{example}

### 2015-07-21 dictionary.tex
Moved an example.

@@
 When commutative, such groups are extensions of finite cyclic groups by algebraic tori,
-in which case it is not difficult to relate Frobenius-stable character sheaves to our character sheaves. %however, even in this case, the two notions are not quite identical.
+in which case it is not difficult to relate Frobenius-stable character sheaves to our character sheaves (\S \ref{ssec:alg_groups}).
 The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ do not arise in that context.
@@
 
-\subsection{Examples}
-
-Let $G$ be the etale group scheme $\ZZ$ over $\Fq$ and consider the character $\chi : \ZZ \to \EEx$ of $G(\Fq)$ determined by $\chi(1) = 1+\ell$.
-The stalk of $\cs{L}$ at the component $1$ is defined
-by a pro-\'etale cover  . . .
-
 \section{The function-sheaf dictionary for smooth commutative group schemes}\label{sec:main}
@@
 
-For example, consider the case when $G$ is the discrete \'etale group scheme $\ZZ$.
+\begin{example}
+Consider the case when $G$ is the discrete \'etale group scheme $\ZZ$.
 If $\chi : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi(1) = \ell$
@@
 bounded.
+On the other hand, if  the character $\chi : \ZZ \to \EEx$ of $G(\Fq)$ determined by $\chi(1) = 1+\ell$.
+The stalk of $\cs{L}$ at the component $1$ is defined
+by a pro-\'etale cover  . . . 
+\end{example}
 
@@
 
-\subsection{The dictionary for commutative algebraic groups over finite fields}
+\subsection{The dictionary for commutative algebraic groups over finite fields}\label{ssec:alg_groups}
 

### 2015-07-21 dictionary.tex
Fixed definition of QCS

@@
 
-Let $K$ be a local field with finite residue field $\Fq$; we will now denote the group $\Weil{}$ by $\Weil{\Fq}$.
+Let $K$ be a local field with finite residue field $\Fq$; in this section we denote the group $\Weil{}$ by $\Weil{\Fq}$.
 We continue to assume that $\ell$ is invertible in $\Fq$. 
@@
 
- \begin{remark}
-This paper shows that the \'etale site on $\Gr_R(X)$ is rich enough to geometrize all quasicharacters of $X(K)$ as $\ell$-adic local systems on $\Gr_R(X)$, where $X$ is a Neron model for an algebraic torus or an abelian variety over a local field $K$.
-It is natural to ask if the \'etale site on the generic fibre $X_K$ would have sufficed. 
-This seems unlikely, since the geometric etale fundamental group of $\Gm{K}$ is ${\hat \ZZ}$, though limited results in this direction were established in \cite{Cunningham-Kamgarpour} when $K = \mathbb{Q}_p$.
-\end{remark}
-
-Let $X \in \mathcal{N}$ be as above.
+%Let $X \in \mathcal{N}$ be as above.
 Set $S = \Spec{R}$ and $S_n = \Spec{R_n}$;
 note that $S_0 = \Spec{\Fq}$ is the special fibre of $S$.
-
-For every non-negative integer $n$, $\Gr^R_n(X)$ is a {\it smooth} commutative group scheme over $S_0$
-with component group scheme $\pi_0(X)_{\Fq} \ceq \pi_0(X) \times_S S_0$ and $\Fq$-rational points $X(R_n).$
+Let $X$ be a smooth commutative group scheme over $S$.
+%We now define a category which will geometrize quasicharacters of $X(K)$.
+For every non-negative integer $n$, the Greenberg transform $\Gr^R_n(X)$ is a {\it smooth} commutative group scheme over $S_0$
+%with component group scheme $\pi_0(X)_{\Fq} \ceq \pi_0(X) \times_S S_0$ and $\Fq$-rational points $X(R_n).$
 %
 The Greenberg transform $\Gr_R(X)$ of $X$ is a commutative group scheme over $\Fq$
-with component group scheme $\pi_0(X)_{\Fq}$
-and $\Fq$-rational points $X(K).$
-However, $\Gr_R(X)$ is not locally of finite type and therefore not smooth.
+%with component group scheme $\pi_0(X)_{\Fq}$
+with $\Fq$-rational points $X(R)$.
 %
@@
 
-We now define a category which will geometrize quasicharacters of $X(K)$.
-We begin by considering the rigid monoidal category $\CS(G)$ defined in Section~\ref{ssec:category} without insisting that the commutative group $\Fq$-scheme $G$ is smooth, so that we can replace it with $\Gr_R(X)$ for smooth group $R$-scheme $X$.
-
 \begin{definition}\label{def:QCS}
-Let $X$ be a smooth commutative group scheme over $R$, with $R$ as above.
-A {\it quasicharacter sheaf for $X$} is an object of
+Let $X$ be a smooth group scheme over $R$.
+A {\it quasicharacter sheaf} of $X$ is a triple 
+\[
+\cs{F} \ceq (n, \{\cs{F}_i\}_{n\leq i}, \{\alpha_{i \le j}\}_{n\le i \le j}),
+\] 
+where $n$
+is a non-negative integer, each $\cs{F}_i$ is a character sheaf on $\Gr^R_i(X)$ and each 
+\[
+\alpha_{i \le j} : \cs{L}_j \to \varrho^R_{i \le j}(X)^* \cs{L}_i
+\]
+ is an isomorphism; here $\alpha_{i \le i}$ is the identity and the $\alpha_{i \le j}$ are compatible with each other.  
+If $\cs{F} \ceq (n, \{\cs{F}_i\}, \{\alpha_{i \le j}\})$
+and $\cs{F}' \ceq (m, \{\cs{F}'_i\}, \{\alpha'_{i \le j}\})$ are objects then $\Hom(\cs{F}, \cs{F}')$ is the set
+of equivalence classes of pairs $(k, \{\beta_i\}_{k \le i})$, where $n,m \le k$ and the $\beta_i : \cs{F}_i \to \cs{F}'_i$ are
+morphisms of character sheaves so that
+\[
+\begin{tikzcd}
+\cs{F}_j \rar{\alpha_j} \dar{\beta_i} & \varrho^R_{i \le j}(X)^* \cs{F}_i \dar{f_{i \le j}^*\beta_j} \\
+\cs{F}'_j \rar{\alpha_j} & \varrho^R_{i \le j}(X)^* \cs{L}'_i
+\end{tikzcd}
+\]
+commutes for all $k\le i\le j$; we identify two such pairs $(k, \{\beta_i\})$ and $(l, \{\gamma_i\})$ if $\beta_i = \gamma_i$
+for sufficiently large $i$.  Identities and composites are defined in the natural way.
+Let $\QCS(X)$ denote the category of quasicharacter sheaves for $X$.
+\end{definition}
+
+\begin{remark}
+If $\varrho^R_n(X)^* : \CS(\Gr^R_n(X)) \to \CS(\Gr_R(X))$ is full then the construction above can be improved by forming $\QCS(X)$ from the essential images of the functors $\varrho^R_n(X)^*$; however, we do not know if $\varrho^R_n(X)^*$ is full.
+\end{remark}
+
+\begin{remark}
+We offer the following alternate construction of $\QCS(X)$.
+As above, let $X$ be a smooth group scheme over $R$.
+Although $\Gr_R(X)$ is not locally of finite type and therefore not smooth,
+let us consider the rigid monoidal category $\CS(\Gr_R(X))$ as defined in Section~\ref{ssec:category} without insisting that the commutative group $\Fq$-scheme $G$ is smooth.
+%Let $X$ be a smooth commutative group scheme over $R$, with $R$ as above.
+A quasicharacter sheaf for $X$ is an object of
 the following rigid monoidal subcategory of $\CS(\Gr_R(X))$, denoted by $\QCS(X)$:
@@
 \end{enumerate}
-
-\end{definition}
-
-\begin{remark}
-If $\varrho^R_n(X)^* : \CS(\Gr^R_n(X)) \to \CS(\Gr_R(X))$ is full then the construction above can be improved by forming $\QCS(X)$ from the essential images of the functors $\varrho^R_n(X)^*$; however, we do not know if $\varrho^R_n(X)^*$ is full.
-\end{remark}
-
-\begin{remark}
-We offer the following alternate construction of $\QCS(X)$, which does not make use of subcategories.
-For objects, one considers triples 
-\[
-\cs{F} \ceq (n, \{\cs{F}_i\}_{n\leq i}, \{\alpha_{i \le j}\}_{n\le i \le j}),
-\] where $n$
-is a non-negative integer, each $\cs{F}_i$ is a character sheaf on $\Gr^R_i(X)$ and each 
-\[
-\alpha_{i \le j} : \cs{L}_j \to \varrho^R_{i \le j}(X)^* \cs{L}_i
-\]
- is an isomorphism; here $\alpha_{i \le i}$ is the identity and the $\alpha_{i \le j}$ are compatible with each other.  
-If $\cs{F} \ceq (n, \{\cs{F}_i\}, \{\alpha_{i \le j}\})$
-and $\cs{F}' \ceq (m, \{\cs{F}'_i\}, \{\alpha'_{i \le j}\})$ are objects then $\Hom(\cs{F}, \cs{F}')$ is the set
-of equivalence classes of pairs $(k, \{\beta_i\}_{k \le i})$, where $n,m \le k$ and the $\beta_i : \cs{F}_i \to \cs{F}'_i$ are
-morphisms of character sheaves so that
-\[
-\begin{tikzcd}
-\cs{F}_j \rar{\alpha_j} \dar{\beta_i} & \varrho^R_{i \le j}(X)^* \cs{F}_i \dar{f_{i \le j}^*\beta_j} \\
-\cs{F}'_j \rar{\alpha_j} & \varrho^R_{i \le j}(X)^* \cs{L}'_i
-\end{tikzcd}
-\]
-commutes for all $k\le i\le j$; we identify two such pairs $(k, \{\beta_i\})$ and $(l, \{\gamma_i\})$ if $\beta_i = \gamma_i$
-for sufficiently large $i$.  Identities and composites are defined in the natural way.
 \end{remark}
@@
 \end{proof}
+
+ \begin{remark}
+In Section~\ref{ssec:CS_tori} we see that the \'etale site on $\Gr_R(X)$ is rich enough to geometrize all quasicharacters of $X(K)$ as $\ell$-adic local systems on $\Gr_R(X)$, where $X$ is a Neron model for an algebraic torus or an abelian variety over a local field $K$.
+It is natural to ask if the \'etale site on the generic fibre $X_K$ would have sufficed. 
+This seems unlikely, since the geometric etale fundamental group of $\Gm{K}$ is ${\hat \ZZ}$, though limited results in this direction were established in \cite{Cunningham-Kamgarpour} when $K = \mathbb{Q}_p$.
+\end{remark}
 
@@
 It is elementary that the horizontal sequence of quasicharacters is exact.
-Accordingly, by Theorem~\ref{thm:CSXK}, the kernel of $\TrFrob{T}$ is $\Hh^2(\pi_0(T)_{\bFq},\EEx)^{\Weil{}}$. 
+Accordingly, by Theorem~\ref{thm:CSXK}, the kernel of the  is $\Hh^2(\pi_0(T)_{\bFq},\EEx)^{\Weil{}}$. 
 By \cite{bitan:discriminant}*{Eq 3.1}, the special fibre of the component group scheme for $T$ is given by

### 2015-07-21 dictionary.tex
More remarks and examples.

@@
 It is applied to certain perverse sheaves on connected reductive algebraic groups over algebraically closed fields in
-\cite{lusztig:85a}*{Def.~2.10} and to certain perverse sheaves on reductive groups
-over algebraically closed fields with finite cyclic component groups in the series of papers
+\cite{lusztig:85a}*{Def.~2.10} and to certain perverse sheaves on certain reductive groups over algebraically closed fields in the series of papers
 beginning with \cite{lusztig:disconnected1}.
-When commutative, such groups are extensions of finite cyclic groups by algebraic tori,
-in which case it is not difficult to relate Frobenius-stable character sheaves to our character sheaves (\S \ref{ssec:alg_groups}).
+When commutative, it is not difficult to relate Frobenius-stable character sheaves to our character sheaves (Remark~\ref{rem:Lusztig}).
 The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ do not arise in that context.
@@
 
-\section{Recollections for connected algebraic groups}\label{ssec:connected}
+\section{Recollections on character sheaves for connected algebraic groups}\label{ssec:connected}
 
@@
 \begin{proposition} \label{prop:etale-iso}
- If $G$ is \'etale then the map $S_G : \CSiso{G}\to \Hh^2(E^\bullet_G)$ induces an isomorphism of split short exact sequences
+ If $G$ is \'etale then the map $S_G : \CSiso{G}\to \Hh^2(E^\bullet_G)$ induces an isomorphism of short exact sequences
 \[
@@
 \[
-\Aut_\CS{}(\cs{L}) \to \Hom(G(\bFq)_{\Weil{}}, \EEx).
+\Aut(\cs{L}) \to \Hom(G(\bFq)_{\Weil{}}, \EEx).
 \]
@@
 corresponding to $\chi$ under Theorem~\ref{thm:snake},
-then $\cs{L}$ does not descend to $G$ since the image of $\chi$ is not
+then $\cs{L}$ does not descend to $G$, since the image of $\chi$ is not
 bounded.
-On the other hand, if  the character $\chi : \ZZ \to \EEx$ of $G(\Fq)$ determined by $\chi(1) = 1+\ell$.
-The stalk of $\cs{L}$ at the component $1$ is defined
-by a pro-\'etale cover  . . . 
+If $\chi' : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi'(1) = 1+\ell$ and if $\cs{L}'$ corresponds to $\chi'$ under Theorem~\ref{thm:snake},
+then $\cs{L}'$ does descend to $G$, since the image of $\chi'$ is
+bounded.
+However, $\cs{L}'$ is not defined by a discrete isogeny (\S \ref{ssec:discrete_isogenies}). 
+If $\chi'' : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi''(1) = \zeta$, a root of unity in $\EEx$, and if $\cs{L}''$ corresponds to $\chi''$ under Theorem~\ref{thm:snake},
+then $\cs{L}''$ is defined by a discrete isogeny. 
 \end{example}
@@
 Let $G$ be a commutative algebraic group over $\Fq$.
-All character sheaves on $G$ descend to $G$: $\CS(G)$ is equivalent to $\bCS(G)$ (\ref{ssec:bS}).
+All character sheaves on $G$ descend to $G$: $\CS(G)$ is equivalent to $\bCS(G)$ (\S \ref{ssec:bS}).
 The trace of Frobenius determines a short exact sequence
@@
 
-Add comment relating to Lusztig . . . .
+\begin{remark}\label{rem:Lusztig}
+Suppose $G$ is a commutative algebraic group over $\Fq$ appearing in the series of papers starting with \cite{lusztig:disconnected1}.
+Then $G$ is a commutative reductive algebraic group over $\Fq$ with cyclic component group scheme; such groups are extensions of finite cyclic groups by algebraic tori.
+Every Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:disconnected1}, is a character sheaf on $G$, in our sense,
+and vice versa.
+Moreover, since $\Hh^2(\pi_0(\bG),\EEx)=0$ by Remark~\ref{eg:H2}, it follows that each Frobenius-stable character sheaf on $G$ as in \cite{lusztig:disconnected1}, is determined by its trace of Frobenius, up to isomorphism.
+\end{remark}
 

### 2015-07-21 dictionary.tex
Calculations for Z2xZ2

--- 2015-07-21 dictionary.tex
@@
 for all $x,y,z\in \bG$, so $a \in Z^2(\bG,\EEx)$.  Similarly, condition~\ref{CS.3} gives
-\begin{equation}\label{nohom}
+\begin{equation}\label{eq:nohom}
 \frac{a(\Frob{G}(x),\Frob{G}(y))}{a(x,y)} =  \frac{b(x+y)}{b(x) b(y)}
@@
 Since $\beta(\Frob{}) : G(\bFq) \to \EEx$ is a group homomorphism,
-condition \eqref{nohom} is satisfied with $a =1$.
+condition \eqref{eq:nohom} is satisfied with $a =1$.
 So $\cs{L} = (\gcs{L}, \mu, \phi)$
@@
 
-\begin{example} \label{eg:H2}
+\begin{remark} \label{eg:H2}
 Recall the K\"unneth formula in group cohomology \cite{brown:CohomologyOfGroups}*{Prop. I.0.8}: if $A$ and $A'$ are groups and $M$ and $M'$ are abelian groups with $M$ $\ZZ$-free, then
@@
 We see that $\Hh^2(\bG, \EEx)$ is trivial if and only if $\bG$ is cyclic.  Of course, $\Hh^0(\Weil{}, \Hh^2(\bG, \EEx))$ may or may not be trivial, even when $\Hh^2(\bG, \EEx)$ is nontrivial.
-\end{example}
+
+Consider the simplest nontrivial case, where $\bG = \{1, i, j, k\} \cong \ZZ/2\ZZ \times \ZZ/2\ZZ.$  Then $\Hh^2(\bG, \EEx) \cong \ZZ/2\ZZ$, on which $\Weil{}$ must act trivially, regardless of its action on $\bG$ itself.
+The nontrivial element corresponds to the extension
+\[
+1 \to \EEx \to Q \to \bG \to 1,
+\]
+where $Q = \{c + c_ii + c_jj + c_kk : c,c_i,c_j,c_k \in \EE \mbox{ with exactly one nonzero}\}$ is a subgroup of the quaternion algebra over $\EE$.
+Let $a$ be a $2$-cocycle corresponding to this extension, with values in $\{\pm 1\}$. When $\Frob{}$ acts trivially on $\bG$,
+any homomorphism $b : \bG \to \EEx$ will satisfy \eqref{eq:nohom}, and the corresponding $\alpha \oplus \beta$ are noncohomologous in $\Hh^2(E_G^\bullet)$.
+When $\Frob{}$ exchanges $i$ and $j$, then we may take $b(1) = 1, b(i) = -1$ and $b(j) = b(k) = \pm 1$, up to coboundaries.
+Finally, when $\Frob{}$ cycles $i$, $j$ and $k$, any homomorphism $b : \bG \to \EEx$ will satisfy \eqref{eq:nohom},
+but now the corresponding $\alpha \oplus \beta$ are all cohomologous in $\Hh^2(E_G^\bullet)$.
+\end{remark}
 
@@
 
-\begin{corollary}
-Let $T$ be a Neron model for an algebraic torus over $K$.
-For $\cs{E}\in \QCS(\pi_0(T))$, $\cs{F}\in {\QCS(T)}$ and $\cs{F}^0\in {\QCS(T^0)}$, there are canonical isomorphisms
-\[
-\Aut(\cs{E})\iso (\check{T}_\ell)^{\Weil{K}},
-\quad
-\Aut(\cs{F})\iso (\check{T}_\ell)^{\Weil{K}},
-\quad
-\Aut(\cs{F}^0)\iso 1,
-\]
- where $\check{T}_\ell \ceq \Hom(X_*(T_K),\EEx)$, the $\ell$-adic dual torus to $T_K$.
-\end{corollary}
-
-\begin{proof}
-We already know $\Aut(\cs{E}) =1$ from Proposition~\ref{prop:connected}, part \ref{x3}.
-By Theorem~\ref{thm:CSXK}, 
-\[
-\Aut(\cs{F})  \iso \Hom((\pi_0(T)_{\bFq})_{\Weil{\Fq}},\EEx).
-\]
-By \cite{bitan:discriminant}*{Eq 3.1} again, 
-\[
-\Hom((\pi_0(T)_{\bFq})_{\Weil{\Fq}},\EEx) \iso
-\Hom(X_*(T_K)_{\Weil{K}},\EEx).
-\]
-But $\Hom(X_*(T_K)_{\Weil{K}},\EEx) \iso \Hom(X_*(T_K),\EEx)^{\Weil{K}}$.
-So, for any quasicharacter sheaf $\cs{F}$ for $T$,
-\[
-\Aut(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
-\]
-canonically.
-The case $X= \pi_0(T)$ is handled by the same argument, replacing Theorem~\ref{thm:CSXK} with Theorem~\ref{thm:snake} and Definition~\ref{def:QCS}, as in the proof of Corollary~\ref{cor:CS_tori}, after observing that $\pi_0(\pi_0(T)_{\bFq}) = \pi_0(T)_{\bFq}$.
-\end{proof}
+\begin{example}
+
+\end{example}
 

### 2015-07-21 dictionary.tex
etale mess up, fixed

--- 2015-07-21 dictionary.tex
@@
 \DeclareMathOperator{\Gal}{Gal}
-\newcommand{\Frob}[1]{\operatorname{F}_{#1}}
+\newcommand{\Frob}[1]{\operatorname{Fr}_{#1}}
 \DeclareMathOperator{\Aut}{Aut}
@@
 \newcommand{\trFrob}[1]{t_{#1}}
-\newcommand{\TrFrob}[1]{T_{#1}}
+\newcommand{\TrFrob}[1]{\operatorname{Tr}_{#1}}
 \newcommand{\lTrFrob}[1]{\TrFrob{#1}^2}
@@
 
-As Deligne explained in \cite{deligne:SGA4.5}*{Sommes trig.}, if $G$ is a connected commutative algebraic group over a finite field $k$, then the trace of Frobenius provides a bijection between the group $G(\Fq)^*$ of $\ell$-adic characters of $G(\Fq)$ and isomorphism classes of rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which
+As Deligne explained in \cite{deligne:SGA4.5}*{Sommes trig.}, if $G$ is a connected commutative algebraic group over a finite field $k$, then the trace of Frobenius provides a bijection between the group $G(\Fq)^*$ of $\ell$-adic characters of $G(\Fq)$ and isomorphism classes of those rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which
 \begin{equation}\label{introbox}
@@
 every character of $G(\Fq)$ may be geometrized as a pair $(\cs{E},\mu_\cs{E})$ but perhaps not uniquely.
-Indeed, it follows from a special case of the main result of this paper that the kernel of the trace of Frobenius $T_{G} : \bCS(G) \to G(\Fq)^*$ trivial if and only if the \'etale group scheme of connected components of $G$ is finite cyclic.
-Nevertheless, the defect in the dictionary for characters of commutative algebraic groups over finite fields may be addressed with the following observation: if $(\cs{E},\mu_\cs{E})$ and $(\cs{E}',\mu_\cs{E}')$ determine the same character of $G(\Fq)$ then $\cs{E}\iso \cs{E}'$ as local systems on $G$.
-
-In order to extend the dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\Fq$,
-we replace the local system $\cs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\cs{E}$. 
+Indeed, it follows from a special case of the main result of this paper that the kernel of the trace of Frobenius $\bCS(G) \to G(\Fq)^*$ trivial if and only if the  group scheme of connected components of $G$ is cyclic.
+The defect in the function-sheaf dictionary for characters of commutative algebraic groups over finite fields may be addressed with the following observation: if $(\cs{E},\mu_\cs{E})$ and $(\cs{E}',\mu_\cs{E}')$ determine the same character of $G(\Fq)$ then $\cs{E}\iso \cs{E}'$ as local systems on $G$.
+
+Motivated by an application to quasicharacters of algebraic tori over local fields, in this paper we extend the function-sheaf dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\Fq$.
+In order to do this, we replace the local system $\cs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\cs{E}$. 
 In this way we are led to the category $\CS(G)$ of {\it character sheaves} on $G$ (\S\ref{ssec:category}):
@@
 morphisms in $\CS(G)$ are then morphisms of Weil sheaves which are compatible with the extra structure.
-This paper establishes the basic properties of $\CS(G)$ by finding the relation between character sheaves on $G$ and characters of $G(\Fq)$.
-
-We begin our study of $\CS(G)$ by returning to the case when $G$ is a connected commutative algebraic group over $\Fq$, revisiting Deligne's function-sheaf dictionary (\S\ref{sec:category}).
+This paper establishes the basic properties of category $\CS(G)$, using the group homomorphism 
+\[
+\TrFrob{G}: \CSiso{G} \to G(\Fq)^*
+\]
+provided by the trace of Frobenius  to find the relation between character sheaves on $G$ and characters of $G(\Fq)$.
+Then we return to our motivating application and use character sheaves to geometrize and categorify quasicharacters algebraic tori over local fields.
+% (\S \ref{sec:applications}).
+
+We begin our study of category $\CS(G)$ by returning to the case when $G$ is a connected commutative algebraic group over $\Fq$, revisiting Deligne's function-sheaf dictionary (\S\ref{sec:category}).
 We consider character sheaves that arise via base change to $\bFq$ from local systems on $G$ (\S\ref{ssec:descentG}) and
@@
 While these constructions make sense even for non-connected $G$, in the connected case we show that every character sheaf can be described in both of these ways (\S\ref{ssec:connected}).  
-We use this fact to prove that $\TrFrob{G}$ is an isomorphism for connected commutative algebraic groups $G$
-and to determine the automorphism groups of character sheaves on such $G$. 
-%These results are all well known.
+We use this fact to prove that $\TrFrob{G} : \CS(G) \to G(\Fq)^*$ is an isomorphism for connected commutative algebraic groups $G$.
+We also determine the automorphism groups of character sheaves on such $G$. 
+These facts are well known.
 
@@
 \]
-arising from the spectral sequence, the isomorphism $S_G$ allows us to show (\S\ref{ssec:SandT}) that 
-the group homomorphism 
-\[
-\TrFrob{G}: \CSiso{G} \to G(\Fq)^*
-\]
-provided by the trace of Frobenius is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$.
+arising from the spectral sequence, the isomorphism $S_G$ allows us to show (\S\ref{ssec:SandT}) that the group homomorphism $\TrFrob{G}: \CSiso{G} \to G(\Fq)^*$ is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$.
 The necessity of using Weil local systems on $G$ in the definition of $\CS(G)$ already appears here:  if one were to use local systems on $G$ instead, the group homomorphism $\TrFrob{G}$ would not then be surjective (\S \ref{ssec:bS}).
-One can show, using the K\"unneth formula, that $\Hh^2(\bG,\EEx)$ is non-trivial unless $\bG$ is cyclic, so the kernel of $\TrFrob{G}$ is non-trivial in general.
+Moreover, as examples show (\S \ref{eg:}), the kernel of $\TrFrob{G}$ is non-trivial in general.
 %The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gcs{L}, \mu,\phi)$ and $(\gcs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gcs{L},\phi)$ and $(\gcs{L}',\phi')$ are isomorphic as Weil sheaves.
 
-%The appearance of $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ and the trace of Frobenius gives an isomorphism $\TrFrob{G}: \CSiso{G} \to \Hom(G(\Fq),\EEx)$; on the other hand, if $G$ an etale commutative group scheme over $\Fq$, then $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ measures the kernel of $\TrFrob{G}: \CSiso{G} \to \Hom(G(\Fq),\EEx)$.
+%The appearance of $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ and the trace of Frobenius gives an isomorphism $\TrFrob{G}: \CSiso{G} \to \Hom(G(\Fq),\EEx)$; on the other hand, if $G$ an \'etale commutative group scheme over $\Fq$, then $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ measures the kernel of $\TrFrob{G}: \CSiso{G} \to \Hom(G(\Fq),\EEx)$.
 %This observation makes plain the fact that  . . .
@@
 Having understood $\CS(G)$ in two extreme cases --
-for connected commutative algebraic groups and for \'etale commutative group schemes -- we return to the case of smooth commutative group schemes (\S\ref{sec:main}) using the component group sequence
+for connected commutative algebraic groups and for \'etale commutative group schemes -- we turn to the case of smooth commutative group schemes (\S\ref{sec:main}) using the component group sequence
 \[
@@
 However, we found that our method of passing from $p$-adic tori to group schemes over $\Fq$ applies more generally to
-any local field $K$ with finite residue field $\Fq$ and any commutative algebraic group $X_K$ that admits a N\'eron model $X$.
-This class of groups includes abelian varieties and unipotent $K$-wound groups in addition to the tori we initially considered.
-
-In this paper we show that quasicharacters of $X(K)$ are geometrized and categorified by quasicharacter sheaves on the
+any local field $K$ with finite residue field $\Fq$ and to any commutative algebraic group over $K$ that admits a N\'eron model $X$.
+This class of algebraic groups over $K$ includes abelian varieties and unipotent $K$-wound groups, in addition to the algebraic tori we initially considered.
+
+In this paper we show that if $X$ is as above then quasicharacters of $X(K)$ are geometrized and categorified by character sheaves on the
 Greenberg transform $\Gr_R(X)$ of the N\'eron model $X$.
@@
 This structure allows us to adapt our work on character sheaves on smooth group schemes over finite fields to construct (\S\ref{ssec:CS_on_GN}) a category $\QCS(X)$
-of quasicharacter sheaves for $X$, which are certain sheaves on $\Gr_R(X)\times_{\Spec{\Fq}} \Spec{\bFq}$, with extra structure.
+of {\it quasicharacter sheaves} for $X$, which are certain sheaves on $\Gr_R(X)\times_{\Spec{\Fq}} \Spec{\bFq}$, with extra structure.
 The ability to generalize the function-sheaf dictionary to non-connected group schemes plays a crucial role in this application.
 
-Having defined quasicharacter sheaves for groups over $K$ and $\Fq$, we consider how
+Having defined quasicharacter sheaves on Neron models of commutative algebraic groups over $K$ and character sheaves on commutative group schemes over $\Fq$, we consider how
 these categories are related as $K$ and $\Fq$ vary.  We describe (\S\ref{ssec:basechange}) functors between categories
@@
 
-Specializing to the case that $X = T$ is the N\'eron model of an algebraic torus over $K$ (\S\ref{ssec:CS_tori}), 
+Finally, specializing to the case that $X = T$ is the N\'eron model of an algebraic torus over $K$ (\S\ref{ssec:CS_tori}), 
 we give a canonical short exact sequence 
 \[
-0 \to \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCSiso{T_K} \to \Hom_\text{}(T(K),\EEx) \to 0,
-\]
-where $X_*(T_K)_{\mathcal{I}_K}$ is the group of coinvariants of the cocharacter lattice $X_*(T_K)$ of the algebraic torus $T_K$ by the action of the inertia group $\mathcal{I}_K$ of $K$, and where $\Hom_\text{}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
-We further show that automorphism groups in $\CS(T)$ are given, for every quasicharacter sheaf $\cs{F}$ for $T$, by
+0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCSiso{T} \to \Hom_\text{}(T(K),\EEx) \to 0,
+\]
+where $X_*(T)_{\mathcal{I}_K}$ is the group of coinvariants of the cocharacter lattice $X_*(T)$ of the algebraic torus $T_K$ by the action of the inertia group $\mathcal{I}_K$ of $K$, and where $\Hom_\text{}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
+We further show that automorphism groups in $\QCS(T)$ are given, for every quasicharacter sheaf $\cs{F}$ for $T$, by
 \[
@@
 A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group \cite{bernstein:vogan_conference}.
-Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to quasicharacters of all the pure rational forms of $T$; however, we do not pursue that suggestion in this paper.
+Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to quasicharacters of all the pure rational forms of $T$; we do not pursue that suggestion in this paper.
 
@@
 \noindent\textbf{Relation to other work.\ }
-The process of creating a category from the group of quasicharacters of a $p$-adic  torus informs our choice of the term quasicharacter sheaf in this paper.
-We also want to situate our terminology in a historical context.
-It is not uncommon to refer to local systems satisfying \eqref{introbox} on a connected, commutative algebraic group as character sheaves;
-see for example, \cite{kamgarpour:09a}*{Intro}.
-As we have indicated, quasicharacter sheaves evolved from this notion,
-with an eye toward quasicharacters of $p$-adic groups.
-
 The main use of the term character sheaf is of course due to Lusztig.
@@
 
-We anticipate that future work on quasicharacter sheaves will make use of   \cite{suzuki-yoshida:12a} and \cite{Suzuki:Neron}, and will clarify the relation between this project and other attempts to geometrize admissible distributions on $p$-adic groups, such as \cite{Cunningham-Kamgarpour} (limited quasicharacters of $\ZZ_p^\times$) and \cite{Aubert-Cunningham} (limited to characters of depth-zero representations).
+%We also want to situate our terminology in a historical context.
+For a connected commutative algebraic group over a finite field, it is not uncommon to refer to local systems satisfying \eqref{introbox}  as character sheaves; see for example, \cite{kamgarpour:09a}*{Intro}.
+Our definition of character sheaves on smooth commutative group schemes over finite fields evolved from this notion, with an eye toward quasicharacters of $p$-adic groups.
+The process of creating a category from the group of quasicharacters of a $p$-adic  torus informs our choice of the term quasicharacter sheaf in this paper.
+
+We anticipate that future work on quasicharacter sheaves will make use of   \cite{suzuki-yoshida:12a} and \cite{Suzuki:Neron}, and will clarify the relation between this project and other attempts to geometrize admissible distributions on $p$-adic groups, such as \cite{Cunningham-Kamgarpour} (limited to quasicharacters of $\ZZ_p^\times$) and \cite{Aubert-Cunningham} (limited to characters of depth-zero representations).
 We are actively pursuing the question of how to extend the notion of quasicharacter sheaves to provide a geometrization of admissible distributions on connected reductive algebraic groups over $p$-adic fields, not just commutative ones.
@@
 It follows from the smoothness of $G$ that the structure morphism $G \to \Spec{\Fq}$ is locally of finite type.
-If the structure morphism $G \to \Spec{\Fq}$ is \'etale, then $G$ is an etale group scheme; this does not imply that $\pi_0(G)$ is finite.
+If the structure morphism $G \to \Spec{\Fq}$ is \'etale, then $G$ is an \'etale group scheme; this does not imply that $\pi_0(G)$ is finite.
 If the structure morphism $G \to \Spec{\Fq}$ is of finite type, then $G$ is an algebraic group; in this case, $\pi_0(G)$ is finite. 
-Indeed, a smooth commutative group scheme $G$ is an algebraic group if and only if the etale group scheme $\pi_0(G)$ is finite.
+Indeed, a smooth commutative group scheme $G$ is an algebraic group if and only if the \'etale group scheme $\pi_0(G)$ is finite.
 
@@
 \end{enumerate}
-\end{definition}
-
-Morphisms in the category of character sheaves on $G$, denoted by $\CS(G)$, are defined in the natural way:
+%\end{definition}
+Morphisms of character sheaves are defined in the natural way:
 \begin{enumerate}
@@
 \end{enumerate}
+ The category of character sheaves on $G$ will be denoted by $\CS(G)$.
+ \end{definition}
 
@@
 %
-In the meantime, we close this subsection with an elementary observation about $\Hom(\cs{L},\cs{L}')$.
-We call a morphism of sheaves \emph{trivial} if it is zero on every stalk.
+In the meantime, we make an elementary observation about $\Hom(\cs{L},\cs{L}')$.
 
@@
 If $\cs{L}$ and $\cs{L}'$ are character sheaves on $G$, then
-every $\rho\in \Hom(\cs{L},\cs{L}')$ is either trivial or an isomorphism. 
+every $\rho\in \Hom(\cs{L},\cs{L}')$ is either trivial (zero on every stalk)
+or an isomorphism. 
 \end{lemma}
 
+\iffalse
 \begin{proof}
@@
 If $\brho_{\bar e} = 0$ then the second diagram in \ref{CS.4} implies that $\brho_{\bg} = 0$ for all $\bg$, in which case $\rho$ is trivial.
-On the other hand, if $\brho_{\bar e}$ is nontrivial then the second diagram in \ref{CS.4}  implies that $\brho_{\bg}$ is nontrivial for all $\bg$ and thus an isomorphism, since the stalk of character sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
-\end{proof}
+On the other hand, if $\brho_{\bar e}$ is nontrivial then the second diagram in \ref{CS.4}  implies that $\brho_{\bg}$ is nontrivial for all $\bg$ and thus an isomorphism, since the stalks of character sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
+\end{proof}
+\fi
 
@@
 
-In this section we introduce two tools which will help us understand isomorphism classes of objects in $\CS(G)$: the map $\CSiso{G} \to G(k)^*$ given by trace of Frobenius and the pullback functor $\CS(G) \to \CS(H)$ associated to a morphism $H \to G$.
+In this section we introduce two tools which will help us understand isomorphism classes of objects in $\CS(G)$: the map $\CSiso{G} \to G(k)^*$ given by trace of Frobenius and the pullback functor $\CS(G) \to \CS(H)$ associated to a morphism $H \to G$ of smooth group schemes over $\Fq$.
 
@@
 
-Now suppose $\cs{L} = (\gcs{L},\mu,\phi)$ is a quasicharacter sheaf on $G$.
+Now suppose $\cs{L} = (\gcs{L},\mu,\phi)$ is a character sheaf on $G$.
 Then the isomorphism $\bm^* \gcs{L} \iso \gcs{L} \boxtimes\gcs{L}$ and the diagram of
@@
 \end{align*}
-Since tensor products on the stalks of $\cs{L}$ induce pointwise multiplication on the trace of Frobenius, $\TrFrob{G}$ is a group homomorphism.  We devote the remainder of this section to
-studying the behavior of the trace of Frobenius under morphisms of group schemes.  These simple but important
-properties of pullbacks and external products will be used in the proofs of many results in this paper.
+Since tensor products on the stalks of $\cs{L}$ induce pointwise multiplication on the trace of Frobenius, $\TrFrob{G}$ is a group homomorphism.
+
+The next two results follow easily from the definitions.
+%In the remainder of this section We devote the remainder of this section to studying the behavior of the trace of Frobenius under morphisms of group schemes.
+These simple but important properties of pullbacks and external products will be used in the proofs of many results in this paper.
 
@@
 \end{lemma}
+\iffalse
 \begin{proof}
@@
 \end{proof}
+\fi
 
@@
 \end{lemma}
+
+\iffalse
 \begin{proof}
@@
 
-Before turning our attention to character sheaves on connected commutative algebraic groups in Section~\ref{ssec:connected}, we treat two special classes of character sheaves on arbitrary smooth commutative group schemes $G$: those that descend from local systems on $\bG$ to local systems on $G$ (\S \ref{ssec:descentG}); and those that are defined by discrete isogenies onto $G$ (\S \ref{ssec:discrete_isogenies}).
+%Before turning our attention to character sheaves on connected commutative algebraic groups in Section~\ref{ssec:connected}, 
+%Here we treat two special classes of character sheaves on arbitrary smooth commutative group schemes $G$: those that descend from local systems on $\bG$ to local systems on $G$ (\S \ref{ssec:descentG}); and those that are defined by discrete isogenies onto $G$ (\S \ref{ssec:discrete_isogenies}).
 The latter will play a role in Sections~\ref{ssec:connected} and \ref{ssec:restriction}.
 
-In this section we consider a category of sheaves on $G$ obtained by
-replacing the Weil sheaf $(\gcs{L}, \phi)$ on $\bG$ in the definition of a character sheaf with an $\ell$-adic local system on $G$ itself.
+In this section we consider a category of sheaves on $G$ obtained by replacing the Weil sheaf $(\gcs{L}, \phi)$ on $\bG$ in the definition of a character sheaf with an $\ell$-adic local system on $G$ itself; these will play a role in Sections~\ref{ssec:connected} and \ref{ssec:alg_groups}.
 
@@
 \begin{remark}\label{rem:descent}
-In fact, it is not difficult to recognize character sheaves that descend to $G$: they are exactly those character sheaves $\cs{L} = (\gcs{L},\mu,\phi)$ for which the action of $W$ on $\gcs{L}$ given by $\phi$ extends to a continuous action of $\Gal(\bFq/\Fq)$ on $\gcs{L}$; see\cite{deligne-katz:SGA7.2}*{Expos\'e XIII, Rappel 1.1.3} for example.
+In fact, it is not difficult to recognize character sheaves that descend to $G$: they are exactly those character sheaves $\cs{L} = (\gcs{L},\mu,\phi)$ for which the action of $W$ on $\gcs{L}$ given by $\phi$ extends to a continuous action of $\Gal(\bFq/\Fq)$ on $\gcs{L}$; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII, Rappel 1.1.3} for example.
 \end{remark}
@@
 
-A finite, \'etale, surjective morphism $H\to G$ of smooth group schemes over $\Fq$ for which the action of $\Gal(\bFq/\Fq)$ on the kernel is trivial is called a {\it discrete isogeny}.
+Here we consider character sheaves on $G$ that are defined by discrete isogenies onto $G$ (\S \ref{ssec:discrete_isogenies}); these will play a role in Section~\ref{ssec:restriction}.
+
+A finite, \'etale, surjective morphism $H\to G$ of smooth group schemes over $\Fq$ for which the action of $\Gal(\bFq/\Fq)$ on the kernel is trivial is called a {\it discrete isogeny}, following \cite{kamgarpour:09a}*{\S 2.2}.
 
@@
 
-\section{Recollections on character sheaves for connected algebraic groups}\label{ssec:connected}
+\subsection{Recollections on character sheaves for connected algebraic groups}\label{ssec:connected}
 
@@
 
-In general, $\bCS(G)$ is an essentially
-proper subcategory of $\CS(G)$. 
-However, if $G$ is connected and of finite type, the categories are equivalent, as we now show.
+If the smooth commutative group scheme $G$ is of finite type, every character sheaf descends to $G$; we will see that they are not equivalent, in general, however.
+For now, we treat the connected case.
 
@@
 
-Although the category $\CS(G)$ of character sheaves on $G$ specializes to $\bCS(G)$ when $G$ is connected and of finite type, this description is \emph{not} sufficient when extending the dictionary to smooth commutative group schemes, as we will see already in Section~\ref{sec:etale}.
+Although the category $\CS(G)$ of character sheaves on $G$ specializes to $\bCS(G)$ when $G$ is of finite type (\S \ref{ssec:alg_groups}), this description is \emph{not} sufficient when extending the dictionary to smooth commutative group schemes, as we will see already in Section~\ref{sec:etale}.
 In particular, for a given $\gcs{L}$ and $\phi$ there may be many $\mu$ so that $(\gcs{L},\mu,\phi)$ is a character sheaf.
@@
 
-In this section we find a complete characterization of the category of character sheaves on \'etale commutative group schemes over finite fields.
+In this section we give a complete characterization of the category of character sheaves on \'etale commutative group schemes over finite fields.
 
@@
 
-In this section we fit the group homomorphisms $\TrFrob{G}$ and $S_G$ into a commutative diagram, determining the kernel and cokernel of the homomorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$ when $G$ is an \'etale commutative group scheme over $\Fq$.
+In this section we fit the group homomorphisms $\TrFrob{G}$ and $S_G$ into a commutative diagram, determining the kernel and cokernel of $\TrFrob{G}$ when $G$ is an \'etale commutative group scheme over $\Fq$.
 
@@
 \begin{proposition} \label{prop:etale-iso}
- If $G$ is \'etale then the map $S_G : \CSiso{G}\to \Hh^2(E^\bullet_G)$ induces an isomorphism of short exact sequences
+ If $G$ is \'etale then the map $S_G : \CSiso{G}\to \Hh^2(E^\bullet_G)$ induces an isomorphism of split short exact sequences
 \[
@@
 
-\subsection{Descent, revisited}\label{ssec:bS}
+\subsection{On the necessity of working with Weil sheaves}\label{ssec:bS}
 
@@
 \begin{proposition}\label{prop:bounded-etale}
-Let $G$ be a commutative etale group scheme over $\Fq$.
-Then the image of $\bCS(G)$ under $\TrFrob{G} : \CS(G) \to G(\Fq)^*$ is $\Hom_\text{grp}(G(\Fq),\ZEx)$.
+Let $G$ be a commutative \'etale group scheme over $\Fq$.
+Then the image of $\bCS(G)$ under $\TrFrob{G} : \CS(G) \to G(\Fq)^*$ is $\Hom(G(\Fq),\ZEx)$.
 \end{proposition}
@@
 \[
-\Hh^1(\Fq,\Hh^1(\bG,\EEx)) = \Hom_\text{grp}(G(\Fq),\ZEx).
+\Hh^1(\Fq,\Hh^1(\bG,\EEx)) = \Hom(G(\Fq),\ZEx).
 \]
@@
 We remark that while $G^i$ is defined over $\Fq$, the set $G^i(\Fq)$ is non-empty only when $G^i(\bFq) = \{ {\bar x}^i\}$.
-Since $\Hh^1(\bG,\EEx) = \Hom_\text{grp}(\bG,\EEx)$, evaluation $\chi \mapsto \chi({\bar x}^i)$ defines $\Hh^1(\Fq,\Hh^1(\bG,\EEx)) \to \Hh^1(\Fq,\EEx)$. 
+Since $\Hh^1(\bG,\EEx) = \Hom(\bG,\EEx)$, evaluation $\chi \mapsto \chi({\bar x}^i)$ defines $\Hh^1(\Fq,\Hh^1(\bG,\EEx)) \to \Hh^1(\Fq,\EEx)$. 
 By continuity, $\Hh^1(\Fq,\EEx) = \Hh^1(\Fq,\ZEx)$.
 Letting $i$ range over $\pi_0(G)$ we conclude that $\Hh^1(\Fq,\Hh^1(\bG,\EEx)) = \Hh^1(\Fq,\Hh^1(\bG,\ZEx))$.
-When adapted to abelian groups with continuous action of $\Gal(\bFq/\Fq)$, the strategy of the proof of Lemma~\ref{lem:dual-inv} gives $\Hh^1(\Fq,\Hh^1(\bG,\ZEx)) =  \Hom_\text{grp}(G(\Fq),\ZEx)$, concluding the proof.
-\end{proof}
+When adapted to abelian groups with continuous action of $\Gal(\bFq/\Fq)$, the strategy of the proof of Lemma~\ref{lem:dual-inv} gives $\Hh^1(\Fq,\Hh^1(\bG,\ZEx)) =  \Hom(G(\Fq),\ZEx)$, concluding the proof.
+\end{proof}
+
+This simple observation reveals the necessity of working with Weil sheaves in Definition~\ref{def:CS}: one cannot geometrize all characters of $G(\Fq)$ using local systems on $G$, for general smooth commutative groups schemes $G$.
+Proposition~\ref{prop:bounded-etale} is extended to all smooth commutative groups schemes in Section~\ref{ssec:revisited}.
+
+\begin{example}\label{eg:}
+Consider the case when $G$ is the \'etale group scheme $\ZZ$ over $\Fq$ with $\Frob{G}$ trivial.
+If $\chi : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi(1) = \ell$
+and if $\cs{L}$ is a character sheaf on $G$ in the isomorphism class
+corresponding to $\chi$ under Proposition~\ref{prop:sur_etale},
+then $\cs{L}$ does not descend to $G$, since the image of $\chi$ is not
+bounded.
+If $\chi' : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi'(1) = 1+\ell$ and if $\cs{L}'$ corresponds to $\chi'$ under Proposition~\ref{prop:sur_etale},
+then $\cs{L}'$ does descend to $G$, since the image of $\chi'$ is
+bounded.
+However, $\cs{L}'$ is not defined by a discrete isogeny (\S \ref{ssec:discrete_isogenies}). 
+If $\chi'' : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi''(1) = \zeta$, a root of unity in $\EEx$, and if $\cs{L}''$ corresponds to $\chi''$ under Proposition~\ref{prop:sur_etale},
+then $\cs{L}''$ is defined by a discrete isogeny. 
+\end{example}
 
@@
   If $G$ is a smooth commutative group scheme over $\Fq$ then
-  \[
-  \TrFrob{G} : \CSiso{G} \to G(\Fq)^*
-  \]
-is surjective with kernel canonically isomorphic to $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
+  $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ is surjective, admits a section, and has kernel canonically isomorphic to $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$:
+    \[
+  \begin{tikzcd}
+0 \arrow{r} & \Hh^2(\pi_0(\bG),\EEx)^{\Weil{}} \arrow{r} & \CSiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0. 
+  \end{tikzcd}
+\]
+is a split exact sequence.
 \end{theorem}
@@
 
-\subsection{On the necessity of working with Weil sheaves}
+\subsection{Descent, revisited}\label{ssec:revisited}
+
+We now extend Proposition~\ref{prop:bounded-etale} to smooth commutative group schemes over $\Fq$.
 
@@
 $\bCS(G) \subset \CS(G)$ is not an equivalence, for smooth commutative group schemes $G$.
-This simple observation reveals the necessity of working with Weil sheaves in Definition~\ref{def:CS}: one cannot geometrize all characters of $G(\Fq)$ using local systems on $G$, for general smooth commutative groups schemes $G$.
-
-\begin{example}
-Consider the case when $G$ is the discrete \'etale group scheme $\ZZ$.
-If $\chi : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi(1) = \ell$
-and if $\cs{L}$ is a character sheaf on $G$ in the isomorphism class
-corresponding to $\chi$ under Theorem~\ref{thm:snake},
-then $\cs{L}$ does not descend to $G$, since the image of $\chi$ is not
-bounded.
-If $\chi' : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi'(1) = 1+\ell$ and if $\cs{L}'$ corresponds to $\chi'$ under Theorem~\ref{thm:snake},
-then $\cs{L}'$ does descend to $G$, since the image of $\chi'$ is
-bounded.
-However, $\cs{L}'$ is not defined by a discrete isogeny (\S \ref{ssec:discrete_isogenies}). 
-If $\chi'' : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi''(1) = \zeta$, a root of unity in $\EEx$, and if $\cs{L}''$ corresponds to $\chi''$ under Theorem~\ref{thm:snake},
-then $\cs{L}''$ is defined by a discrete isogeny. 
-\end{example}
 
@@
 It is natural to ask if the \'etale site on the generic fibre $X_K$ would have sufficed. 
-This seems unlikely, since the geometric etale fundamental group of $\Gm{K}$ is ${\hat \ZZ}$, though limited results in this direction were established in \cite{Cunningham-Kamgarpour} when $K = \mathbb{Q}_p$.
+This seems unlikely, since the geometric \'etale fundamental group of $\Gm{K}$ is ${\hat \ZZ}$, though limited results in this direction were established in \cite{Cunningham-Kamgarpour} when $K = \mathbb{Q}_p$.
 \end{remark}
@@
 {}  & 0 \arrow{d} & 0 \arrow{d} &  & \\ 
-   & \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}}  \arrow{d} & \arrow{d} \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}} & 0 \arrow{d} & \\
+   & \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}}  \arrow{d} & \arrow{d} \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}} & 0 \arrow{d} & \\
     0 \rar & \QCSiso{\pi_0(T)} \arrow{r}{\pi_0^*} \dar{\TrFrob{\pi_0(T)}}
@@
 \[
- \pi_0(T)_{\bFq} = X_*(T_K)_{\mathcal{I}_K},
-\]
-where $X_*(T_K)$ is the cocharacter lattice of $T_K$ and $\mathcal{I}_K$ is the inertia group for $K$.
+ \pi_0(T)_{\bFq} = X_*(T)_{\mathcal{I}_K},
+\]
+where $X_*(T)$ is the cocharacter lattice of $T_K$ and $\mathcal{I}_K$ is the inertia group for $K$.
 Thus,
 \[
-\Hh^2(\pi_0(T)_{\bFq},\EEx)^{\Weil{\Fq}} = \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}}.
+\Hh^2(\pi_0(T)_{\bFq},\EEx)^{\Weil{\Fq}} = \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}}.
 \] 
@@
 \]
- where $\check{T}_\ell \ceq \Hom(X_*(T_K),\EEx)$, the $\ell$-adic dual torus to $T_K$.
+ where $\check{T}_\ell \ceq \Hom(X_*(T),\EEx)$, the $\ell$-adic dual torus to $T_K$.
 \end{corollary}
@@
 \Hom((\pi_0(T)_{\bFq})_{\Weil{\Fq}},\EEx) \iso
-\Hom(X_*(T_K)_{\Weil{K}},\EEx).
-\]
-But $\Hom(X_*(T_K)_{\Weil{K}},\EEx) \iso \Hom(X_*(T_K),\EEx)^{\Weil{K}}$.
+\Hom(X_*(T)_{\Weil{K}},\EEx).
+\]
+But $\Hom(X_*(T)_{\Weil{K}},\EEx) \iso \Hom(X_*(T),\EEx)^{\Weil{K}}$.
 So, for any quasicharacter sheaf $\cs{F}$ for $T$,
@@
 \begin{remark}
-Since $\pi_0(T)_{\bFq} = X_*(T_K)_{\mathcal{I}_K}$ by \cite{bitan:discriminant}*{Eq 3.1}, we have
+Since $\pi_0(T)_{\bFq} = X_*(T)_{\mathcal{I}_K}$ by \cite{bitan:discriminant}*{Eq 3.1}, we have
 \[\Hom(\pi_0(T)(\Fq), \EEx)
@@
 {}  & 0 \arrow{d} & 0 \arrow{d} &  & \\ 
-   & \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}}  \arrow{d} & \arrow{d} \Hh^2(X_*(T_K)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}} & 0 \arrow{d} & \\
+   & \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}}  \arrow{d} & \arrow{d} \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}} & 0 \arrow{d} & \\
     0 \rar & \QCSiso{\pi_0(T)} \arrow{r}{\pi_0^*} \arrow{d}
@@
 The isomorphism $\QCSiso{\Gm{R}}\iso \Hom(\mathcal{I}_K, \EEx)$ may be deduced directly from the class field theory of Serre and Hezewinkel as revisited beautifully in \cite{suzuki-yoshida:12a}; see also \cite{Suzuki:Neron}.
-The monoidal category of character sheaves on $\Gr^R_n(\Gm{R})$ is canonically equivalent to the category of $\ell$-adic characters of the quotient of the etale fundamental group $\pi_1(\Gr^R_n(\Gm{R}),\bFq)$ determined by the Lang isogeny for $\Gr^R_n(\Gm{R})$.
+The monoidal category of character sheaves on $\Gr^R_n(\Gm{R})$ is canonically equivalent to the category of $\ell$-adic characters of the quotient of the \'etale fundamental group $\pi_1(\Gr^R_n(\Gm{R}),\bFq)$ determined by the Lang isogeny for $\Gr^R_n(\Gm{R})$.
 Accordingly, quasicharacter sheaves on $\Gm{R}$ may be apprehended as $\ell$-adic characters of the inverse limit of these quotients, as $n$ ranges over $\NN$.

### 2015-07-21 dictionary.tex
Modifications to the discrete isogenies section.

@@
 
-A finite, \'etale, surjective morphism $H\to G$ of smooth group schemes over $\Fq$ for which the action of $\Gal(\bFq/\Fq)$ on the kernel is trivial is called a {\it discrete isogeny}, following \cite{kamgarpour:09a}*{\S 2.2}.
+A finite, \'etale, surjective morphism $H\to G$ of smooth group schemes over $\Fq$ for which the action of $\Gal(\bFq/\Fq)$ on the kernel is trivial is called a {\it discrete isogeny}, inspired by \cite{kamgarpour:09a}*{\S 2.2}.
 
@@
 
-We remark that, since $V$ is $1$-dimensional, the choice of $V \to V\otimes V$ is exactly the choice of an isomorphism $V\iso \EE$.
+\begin{remark}
+Since $V$ is $1$-dimensional, the choice of $V \to V\otimes V$ is exactly the choice of an isomorphism $V\iso \EE$.
+\end{remark}
+
+\begin{remark}
+A descent argument similar to the one employed in the proof of Lemma~\ref{prop:finite} is used in \cite{Drinfeld:math/0609769}*{Lemma~1.10}, though in the more restrictive case of connected algebraic groups.
+\end{remark}
 
@@
 Pick $i\in \pi_0(G)$ and let $G^i \hookrightarrow G$ be the corresponding connected component. 
-Pick a geometric point ${\bar x}^i$ on $G^i$ and observe that since $G^i$ is connected as a $\Fq$-scheme, $G^i(\bFq)$ is canonically identified with the $\Gal(\bFq/\Fq)$-orbit of ${\bar x}^i$. 
-We remark that while $G^i$ is defined over $\Fq$, the set $G^i(\Fq)$ is non-empty only when $G^i(\bFq) = \{ {\bar x}^i\}$.
-Since $\Hh^1(\bG,\EEx) = \Hom(\bG,\EEx)$, evaluation $\chi \mapsto \chi({\bar x}^i)$ defines $\Hh^1(\Fq,\Hh^1(\bG,\EEx)) \to \Hh^1(\Fq,\EEx)$. 
+Pick a geometric point $x$ on $G^i$ and observe that since $G^i$ is connected as a $\Fq$-scheme, $G^i(\bFq)$ is canonically identified with the $\Gal(\bFq/\Fq)$-orbit of $x$. 
+We remark that while $G^i$ is defined over $\Fq$, the set $G^i(\Fq)$ is non-empty only when $G^i(\bFq) = \{ x\}$.
+Since $\Hh^1(\bG,\EEx) = \Hom(\bG,\EEx)$, evaluation $\chi \mapsto \chi(x)$ defines $\Hh^1(\Fq,\Hh^1(\bG,\EEx)) \to \Hh^1(\Fq,\EEx)$. 
 By continuity, $\Hh^1(\Fq,\EEx) = \Hh^1(\Fq,\ZEx)$.
@@
 
-This simple observation reveals the necessity of working with Weil sheaves in Definition~\ref{def:CS}: one cannot geometrize all characters of $G(\Fq)$ using local systems on $G$, for general smooth commutative groups schemes $G$.
+Proposition~\ref{prop:bounded-etale} reveals the necessity of working with Weil sheaves in Definition~\ref{def:CS}: one cannot geometrize all characters of $G(\Fq)$ using local systems on $G$, for general smooth commutative groups schemes $G$.
 Proposition~\ref{prop:bounded-etale} is extended to all smooth commutative groups schemes in Section~\ref{ssec:revisited}.
@@
 
-While most of this paper focuses on the question of determining the isomorphism classes of objects, a complete understanding of the morphisms in $\CS(G)$ also requires a description of the automorphisms of an arbitrary character sheaf $\cs{L}$.
+%While most of this paper focuses on the question of determining the isomorphism classes of objects, 
+A complete understanding of the morphisms in $\CS(G)$ also requires a description of the automorphisms of an arbitrary character sheaf $\cs{L}$.
 
@@
 
-We now wish to apply the results of Section~\ref{ssec:connected} to the identity component of $G$; to do so, we must know that the identity component of $G$ is actually an algebraic group over $\Fq$.
+We now wish to apply the results of Section~\ref{ssec:connected} to the identity component of $G$, for which we must confirm that the identity component of $G$ is actually an algebraic group over $\Fq$.
 
@@
   If $G$ is a smooth commutative group scheme over $\Fq$ then
-  $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ is surjective, admits a section, and has kernel canonically isomorphic to $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$:
+  $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ is surjective and has kernel canonically isomorphic to $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$:
     \[
@@
 \]
-is a split exact sequence.
+is an exact sequence.
 \end{theorem}
@@
 
-\begin{remark}
-Although $\TrFrob{\pi_0(G)}$ is split and $\TrFrob{G^0}$ is an isomorphism, it does not follow that $\TrFrob{G}$ is split. 
+\begin{remark}\label{rem:rats}
+Although $\TrFrob{\pi_0(G)}$ is split and $\TrFrob{G^0}$ is an isomorphism, we do not know if $\TrFrob{G}$ is split, in general.
+Surjectively of $\TrFrob{G}$ shows that every $\ell$-adic character of $G(\Fq)$ admits a geometrization, but without a splitting for $\TrFrob{G}$ we do not know how to make this geometrization canonical.
 \end{remark}
@@
 It follows from Proposition~\ref{prop:connected} that the restriction of $\cs{L}$ to $G^0$ descends to $G$. 
-Also, since $G^0(\Fq)$ is finite, the image of $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ is a finite subgroup and therefore bounded image.  
+Also, since $G^0(\Fq)$ is finite, the image of $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ is a finite subgroup and therefore has bounded image.  
 %
@@
 Proposition~\ref{prop:bounded} shows that the full subcategory
-$\bCS(G) \subset \CS(G)$ is not an equivalence, for smooth commutative group schemes $G$.
+$\bCS(G) \subset \CS(G)$ is not an equivalence, for general smooth commutative group schemes $G$. Again we see the necessity of working with Weil sheaves in Definition~\ref{def:CS}.
 
@@
 
-Having extended the function--sheaf dictionary from connected commutative algebraic groups over $\Fq$ to smooth commutative group schemes $G$ over $\Fq$, we briefly look back to the case when $G$ is a commutative algebraic group.
+Having extended the function--sheaf dictionary from connected commutative algebraic groups over $\Fq$ to smooth commutative group schemes $G$ over $\Fq$, we look back briefly to the case when $G$ is a commutative algebraic group.
 Although Weil sheaves are not necessary in that case, the dictionary is still not perfect, generally.

### 2015-07-21 dictionary.tex
Updating Z2xZ2 example

--- 2015-07-21 dictionary.tex
@@
 If $\brho_{\bar e} = 0$ then the second diagram in \ref{CS.4} implies that $\brho_{\bg} = 0$ for all $\bg$, in which case $\rho$ is trivial.
-On the other hand, if $\brho_{\bar e}$ is nontrivial then the second diagram in \ref{CS.4}  implies that $\brho_{\bg}$ is nontrivial for all $\bg$ and thus an isomorphism, since the stalks of character sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
+On the other hand, if $\brho_{\bar e}$ is non-trivial then the second diagram in \ref{CS.4}  implies that $\brho_{\bg}$ is non-trivial for all $\bg$ and thus an isomorphism, since the stalks of character sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
 \end{proof}
@@
 
-Now suppose $\bG = \ZZ^r \times \prod_{i = 1}^m \ZZ/N_i\ZZ$ is an arbitrary finitely generated abelian group, with $N_i \mid N_{i+1}$.  Then the K\"unneth formula implies that
-\[
+Now suppose $\bG = \ZZ^r \times \prod_{i = 1}^m \ZZ/N_i\ZZ$ is an arbitrary finitely generated abelian group,
+with $N_i \mid N_{i+1}$.  Then the K\"unneth formula implies that
+\begin{equation} \label{eq:H2comp}
 \Hh^2(\bG, \EEx) \cong \left(\EEx\right)^{r(r-1)/2} \times \prod_{i=1}^m (\ZZ/N_i\ZZ)^{m+r-i}.
-\]
-We see that $\Hh^2(\bG, \EEx)$ is trivial if and only if $\bG$ is cyclic.  Of course, $\Hh^0(\Weil{}, \Hh^2(\bG, \EEx))$ may or may not be trivial, even when $\Hh^2(\bG, \EEx)$ is nontrivial.
-\end{example}
+\end{equation}
+We see that $\Hh^2(\bG, \EEx)$ is trivial if and only if $\bG$ is cyclic.  Of course, $\Hh^0(\Weil{}, \Hh^2(\bG, \EEx))$
+may or may not be trivial, even when $\Hh^2(\bG, \EEx)$ is non-trivial.
+
+Consider the simplest non-trivial case, where $\bG = \{1, i, j, k\} \cong \ZZ/2\ZZ \times \ZZ/2\ZZ.$  Using eqref{eq:H2comp},
+we have $\Hh^2(\bG, \EEx) \cong \ZZ/2\ZZ$, on which $\Weil{}$ must act trivially, regardless of its action on $\bG$ itself.
+The non-trivial element corresponds to the extension
+\begin{equation} \label{eq:Qdef}
+1 \to \EEx \to Q \to \bG \to 1,
+\end{equation}
+where $Q = \{c + c_ii + c_jj + c_kk \tq c,c_i,c_j,c_k \in \EE \mbox{ with exactly one nonzero}\}$ is a subgroup of the quaternion algebra over $\EE$.
+Let $a$ be a $2$-cocycle corresponding to this extension, with values in $\{\pm 1\}$. When $\Frob{G}$ acts trivially on $\bG$,
+any homomorphism $b : \bG \to \EEx$ will satisfy \eqref{eq:nohom}, and the corresponding $\alpha \oplus \beta$ are non-cohomologous in $\Hh^2(E_G^\bullet)$.
+When $\Frob{G}$ exchanges $i$ and $j$, then we may take $b(1) = 1, b(i) = -1$ and $b(j) = b(k) = \pm 1$, up to coboundaries.
+Finally, when $\Frob{G}$ cycles $i$, $j$ and $k$, any homomorphism $b : \bG \to \EEx$ will satisfy \eqref{eq:nohom},
+but now the corresponding $\alpha \oplus \beta$ are all cohomologous in $\Hh^2(E_G^\bullet)$.  In each case, we may produce
+an explicit character sheaf from the listed $a$ and $b$.
+
+Note that these character sheaves arise from discrete isogenies, as in Section \ref{ssec:discrete_isogenies}.
+Let $\bH$ be the quaternion group of order $8$: the subgroup of $Q$ with $c, c_i, c_j, c_k \in \{\pm 1\}$.
+The sequence \eqref{eq:Qdef} is the pushforward of
+\[
+1 \to \{\pm 1\} \to \bH \to \bG \to 1
+\]
+along the inclusion $\{\pm 1\} \hookrightarrow \EEx$.  Note that these character sheaves arise from a non-commutative cover of $\bG$,
+justifying the inclusion of such covers in the definition of a discrete isogeny.
+\end{remark}
 

### 2015-07-21 dictionary.tex

--- 2015-07-21 dictionary.tex
@@
 
-Now suppose $\bG = \ZZ^r \times \prod_{i = 1}^m \ZZ/N_i\ZZ$ is an arbitrary finitely generated abelian group, with $N_i \mid N_{i+1}$.  Then the K\"unneth formula implies that
-\[
+Now suppose $\bG = \ZZ^r \times \prod_{i = 1}^m \ZZ/N_i\ZZ$ is an arbitrary finitely generated abelian group,
+with $N_i \mid N_{i+1}$.  Then the K\"unneth formula implies that
+\begin{equation} \label{eq:H2comp}
 \Hh^2(\bG, \EEx) \cong \left(\EEx\right)^{r(r-1)/2} \times \prod_{i=1}^m (\ZZ/N_i\ZZ)^{m+r-i}.
-\]
-We see that $\Hh^2(\bG, \EEx)$ is trivial if and only if $\bG$ is cyclic.  Of course, $\Hh^0(\Weil{}, \Hh^2(\bG, \EEx))$ may or may not be trivial, even when $\Hh^2(\bG, \EEx)$ is nontrivial.
-
-Consider the simplest nontrivial case, where $\bG = \{1, i, j, k\} \cong \ZZ/2\ZZ \times \ZZ/2\ZZ.$  Then $\Hh^2(\bG, \EEx) \cong \ZZ/2\ZZ$, on which $\Weil{}$ must act trivially, regardless of its action on $\bG$ itself.
-The nontrivial element corresponds to the extension
-\[
+\end{equation}
+We see that $\Hh^2(\bG, \EEx)$ is trivial if and only if $\bG$ is cyclic.  Of course, $\Hh^0(\Weil{}, \Hh^2(\bG, \EEx))$
+may or may not be trivial, even when $\Hh^2(\bG, \EEx)$ is non-trivial.
+
+Consider the simplest non-trivial case, where $\bG = \{1, i, j, k\} \cong \ZZ/2\ZZ \times \ZZ/2\ZZ.$  Using eqref{eq:H2comp},
+we have $\Hh^2(\bG, \EEx) \cong \ZZ/2\ZZ$, on which $\Weil{}$ must act trivially, regardless of its action on $\bG$ itself.
+The non-trivial element corresponds to the extension
+\begin{equation} \label{eq:Qdef}
 1 \to \EEx \to Q \to \bG \to 1,
-\]
-where $Q = \{c + c_ii + c_jj + c_kk : c,c_i,c_j,c_k \in \EE \mbox{ with exactly one nonzero}\}$ is a subgroup of the quaternion algebra over $\EE$.
-Let $a$ be a $2$-cocycle corresponding to this extension, with values in $\{\pm 1\}$. When $\Frob{}$ acts trivially on $\bG$,
-any homomorphism $b : \bG \to \EEx$ will satisfy \eqref{eq:nohom}, and the corresponding $\alpha \oplus \beta$ are noncohomologous in $\Hh^2(E_G^\bullet)$.
-When $\Frob{}$ exchanges $i$ and $j$, then we may take $b(1) = 1, b(i) = -1$ and $b(j) = b(k) = \pm 1$, up to coboundaries.
-Finally, when $\Frob{}$ cycles $i$, $j$ and $k$, any homomorphism $b : \bG \to \EEx$ will satisfy \eqref{eq:nohom},
-but now the corresponding $\alpha \oplus \beta$ are all cohomologous in $\Hh^2(E_G^\bullet)$.
+\end{equation}
+where $Q = \{c + c_ii + c_jj + c_kk \tq c,c_i,c_j,c_k \in \EE \mbox{ with exactly one nonzero}\}$ is a subgroup of the quaternion algebra over $\EE$.
+Let $a$ be a $2$-cocycle corresponding to this extension, with values in $\{\pm 1\}$. When $\Frob{G}$ acts trivially on $\bG$,
+any homomorphism $b : \bG \to \EEx$ will satisfy \eqref{eq:nohom}, and the corresponding $\alpha \oplus \beta$ are non-cohomologous in $\Hh^2(E_G^\bullet)$.
+When $\Frob{G}$ exchanges $i$ and $j$, then we may take $b(1) = 1, b(i) = -1$ and $b(j) = b(k) = \pm 1$, up to coboundaries.
+Finally, when $\Frob{G}$ cycles $i$, $j$ and $k$, any homomorphism $b : \bG \to \EEx$ will satisfy \eqref{eq:nohom},
+but now the corresponding $\alpha \oplus \beta$ are all cohomologous in $\Hh^2(E_G^\bullet)$.  In each case, we may produce
+an explicit character sheaf from the listed $a$ and $b$.
+
+Note that these character sheaves arise from discrete isogenies, as in Section \ref{ssec:discrete_isogenies}.
+Let $\bH$ be the quaternion group of order $8$: the subgroup of $Q$ with $c, c_i, c_j, c_k \in \{\pm 1\}$.
+The sequence \eqref{eq:Qdef} is the pushforward of
+\[
+1 \to \{\pm 1\} \to \bH \to \bG \to 1
+\]
+along the inclusion $\{\pm 1\} \hookrightarrow \EEx$.  Note that these character sheaves arise from a non-commutative cover of $\bG$,
+justifying the inclusion of such covers in the definition of a discrete isogeny.
 \end{remark}

### 2015-07-21 dictionary.tex
Split Kunneth remark from Z2xZ2 example, remove reference to Bernstein's comment

@@
 
+\iffalse
 By any measure, there are more quasicharacter sheaves for $T$ than quasicharacters of $T(K)$.  
@@
 Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to quasicharacters of all the pure rational forms of $T$; we do not pursue that suggestion in this paper.
+\fi
 
@@
 When commutative, it is not difficult to relate Frobenius-stable character sheaves to our character sheaves (Remark~\ref{rem:Lusztig}).
-The new features that we have found pertaining to Weil sheaves and the non-triviality of $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ do not arise in that context.
+The new features that we have found pertaining to Weil sheaves and $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ do not arise in that context because, for such groups, Weil sheaves are unnecessary (\S \ref{ssec:alg_groups} and $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}=0$ (Remark \ref{rem:H2}).
 
@@
 
-\begin{remark} \label{eg:H2}
+\begin{remark}
 Recall the K\"unneth formula in group cohomology \cite{brown:CohomologyOfGroups}*{Prop. I.0.8}: if $A$ and $A'$ are groups and $M$ and $M'$ are abelian groups with $M$ $\ZZ$-free, then
@@
 \]
-
+%
 Now suppose $\bG = \ZZ^r \times \prod_{i = 1}^m \ZZ/N_i\ZZ$ is an arbitrary finitely generated abelian group,
@@
 may or may not be trivial, even when $\Hh^2(\bG, \EEx)$ is non-trivial.
-
+\end{remark}
+
+\begin{example}\ref{eg:H2}
 Consider the simplest non-trivial case, where $\bG = \{1, i, j, k\} \cong \ZZ/2\ZZ \times \ZZ/2\ZZ.$  Using eqref{eq:H2comp},
@@
 justifying the inclusion of such covers in the definition of a discrete isogeny.
-\end{remark}
+\end{example}
 

### 2015-07-21 dictionary.tex
Inserting line breaks
Catching up . . .

@@
 \email{cunning@math.ucalgary.ca}
-%\address{Pacific Institute for the Mathematical Sciences, University of Calgary, 2500 University Drive, {T2N~1N4}, Calgary, Canada, {\tt roed.math@gmail.com}}
 \address{Department of Mathematics, University of British Columbia, 1984 Mathematics Road, Vancouver, British Columbia, Canada, {V6T~1Z2}.}
@@
 
-\keywords{function-sheaf dictionary, trace of Frobenius, geometrization, categorification, character sheaves,smooth commutative group schemes, finite fields, local fields, algebraic tori, Neron models, Greenberg functor, quasicharacters, quasicharacter sheaves.}
+\keywords{function-sheaf dictionary, trace of Frobenius, geometrization, categorification, character sheaves,smooth commutative group schemes,
+finite fields, local fields, algebraic tori, Neron models, Greenberg functor, quasicharacters, quasicharacter sheaves.}
 
@@
 \begin{abstract}
-We consider the rigid monoidal category of character sheaves on a smooth commutative group scheme $G$ over a finite field $k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
-We find the group of isomorphism classes of character sheaves on $G$ and show that it is an extension of the group of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
+We consider the rigid monoidal category of character sheaves on a smooth commutative group scheme $G$ over a finite field
+$k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
+We find the group of isomorphism classes of character sheaves on $G$ and show that it is an extension of the group
+of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
 We also classify all morphisms in the category character sheaves on $G$.
-As an application, we study character sheaves on the Greenberg transforms of the locally finite type N\'eron models of algebraic tori over local fields; in doing so, we introduce `quasicharacter sheaves' and find a geometrization and categorification of quasi\-characters of $p$-adic tori.
+As an application, we study character sheaves on the Greenberg transforms of the locally finite type N\'eron models
+of algebraic tori over local fields; in doing so, we introduce `quasicharacter sheaves' and find a geometrization and
+categorification of quasi\-characters of $p$-adic tori.
 \end{abstract}
@@
 
-%This paper extends Deligne's function-sheaf dictionary from connected commutative algebraic groups to smooth commutative group schemes over finite fields and then provides an application to the geometrization and categorification of quasicharacters of algebraic tori, abelian varieties and unipotent wound groups over non-Archimedean local fields.
-
-As Deligne explained in \cite{deligne:SGA4.5}*{Sommes trig.}, if $G$ is a connected commutative algebraic group over a finite field $k$, then the trace of Frobenius provides a bijection between the group $G(\Fq)^*$ of $\ell$-adic characters of $G(\Fq)$ and isomorphism classes of those rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which
+%This paper extends Deligne's function-sheaf dictionary from connected commutative algebraic groups to smooth
+%commutative group schemes over finite fields and then provides an application to the geometrization and categorification
+%of quasicharacters of algebraic tori, abelian varieties and unipotent wound groups over non-Archimedean local fields.
+
+As Deligne explained in \cite{deligne:SGA4.5}*{Sommes trig.}, if $G$ is a connected commutative algebraic group
+over a finite field $k$, then the trace of Frobenius provides a bijection between the group $G(\Fq)^*$ of $\ell$-adic
+characters of $G(\Fq)$ and isomorphism classes of those rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which 
 \begin{equation}\label{introbox}
@@
 %
-If one wishes to make a category from this class of local systems, one is led to consider morphisms $\cs{E} \to \cs{E}'$ of sheaves which are compatible with particular choices of \eqref{introbox} for $\cs{E}$ and $\cs{E'}$.
-{\it A priori}, the composition $\cs{E} \to \cs{E}' \to \cs{E}''$ of two such morphisms need not be compatible with the choices of \eqref{introbox} for $\cs{E}$ and $\cs{E}''$.
- However, for connected $G$ the isomorphism \eqref{introbox} is unique, if it exists, and there is no impediment to making the dictionary categorical.
-
-If $G$ is a commutative algebraic group over $\Fq$ which is not connected, however, then the isomorphism \eqref{introbox} need not be unique.
-In order to track the choice of isomorphism, consider the category $\bCS(G)$ of pairs $(\cs{E},\mu_\cs{E})$ where $\cs{E}$ is a rank-one local system on $G$ and $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ is a chosen isomorphism of local systems on $G\times G$.
-In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of objects in $\bCS(G)$ to characters of $G(\Fq)$, but the epimomorphism need not be injective; consequently,
+If one wishes to make a category from this class of local systems, one is led to consider morphisms
+$\cs{E} \to \cs{E}'$ of sheaves which are compatible with particular choices of \eqref{introbox} for $\cs{E}$ and $\cs{E'}$. 
+{\it A priori}, the composition $\cs{E} \to \cs{E}' \to \cs{E}''$ of two such morphisms need not be
+compatible with the choices of \eqref{introbox} for $\cs{E}$ and $\cs{E}''$.
+ However, for connected $G$ the isomorphism \eqref{introbox} is unique, if it exists, and there is no impediment
+ to making the dictionary categorical.
+
+If $G$ is a commutative algebraic group over $\Fq$ which is not connected, however, then the isomorphism \eqref{introbox}
+need not be unique. In order to track the choice of isomorphism, consider the category $\bCS(G)$ of pairs $(\cs{E},\mu_\cs{E})$
+where $\cs{E}$ is a rank-one local system on $G$ and $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ is a chosen
+isomorphism of local systems on $G\times G$. 
+In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of objects in $\bCS(G)$ to characters
+of $G(\Fq)$, but the epimomorphism need not be injective; consequently,
 every character of $G(\Fq)$ may be geometrized as a pair $(\cs{E},\mu_\cs{E})$ but perhaps not uniquely.
-Indeed, it follows from a special case of the main result of this paper that the kernel of the trace of Frobenius $\bCS(G) \to G(\Fq)^*$ trivial if and only if the  group scheme of connected components of $G$ is cyclic.
-The defect in the function-sheaf dictionary for characters of commutative algebraic groups over finite fields may be addressed with the following observation: if $(\cs{E},\mu_\cs{E})$ and $(\cs{E}',\mu_\cs{E}')$ determine the same character of $G(\Fq)$ then $\cs{E}\iso \cs{E}'$ as local systems on $G$.
-
-Motivated by an application to quasicharacters of algebraic tori over local fields, in this paper we extend the function-sheaf dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\Fq$.
+Indeed, it follows from a special case of the main result of this paper that the kernel of the trace of Frobenius
+$\bCS(G) \to G(\Fq)^*$ trivial if and only if the  group scheme of connected components of $G$ is cyclic.
+The defect in the function-sheaf dictionary for characters of commutative algebraic groups over finite fields may be
+addressed with the following observation: if $(\cs{E},\mu_\cs{E})$ and $(\cs{E}',\mu_\cs{E}')$ determine the same
+character of $G(\Fq)$ then $\cs{E}\iso \cs{E}'$ as local systems on $G$.
+
+Motivated by an application to quasicharacters of algebraic tori over local fields, in this paper we extend the
+function-sheaf dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\Fq$.
 In order to do this, we replace the local system $\cs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\cs{E}$. 
@@
 objects in $\CS(G)$ are triples $(\gcs{L}, \mu,\phi)$, where $\gcs{L}$ is a rank-one local system on $\bG := G\times_{\Spec{\Fq}} \Spec{\bFq}$
-and $\phi : \Frob{G}^* \gcs{L}\to \gcs{L}$ and $\mu : \bm^* \gcs{L} \iso \gcs{L} \boxtimes \gcs{L}$ are isomorphisms of sheaves satisfying certain compatibility conditions;
+and $\phi : \Frob{G}^* \gcs{L}\to \gcs{L}$ and $\mu : \bm^* \gcs{L} \iso \gcs{L} \boxtimes \gcs{L}$ are
+isomorphisms of sheaves satisfying certain compatibility conditions;
 morphisms in $\CS(G)$ are then morphisms of Weil sheaves which are compatible with the extra structure.
@@
 
-We begin our study of category $\CS(G)$ by returning to the case when $G$ is a connected commutative algebraic group over $\Fq$, revisiting Deligne's function-sheaf dictionary (\S\ref{sec:category}).
+We begin our study of category $\CS(G)$ by returning to the case when $G$ is a
+connected commutative algebraic group over $\Fq$, revisiting Deligne's function-sheaf dictionary (\S\ref{sec:category}).
 We consider character sheaves that arise via base change to $\bFq$ from local systems on $G$ (\S\ref{ssec:descentG}) and
 those that appear in a pushforward from a constant sheaf along a discrete isogeny $H \to G$ (\S\ref{ssec:discrete_isogenies}).  
-While these constructions make sense even for non-connected $G$, in the connected case we show that every character sheaf can be described in both of these ways (\S\ref{ssec:connected}).  
+While these constructions make sense even for non-connected $G$, in the connected case we show that
+every character sheaf can be described in both of these ways (\S\ref{ssec:connected}).  
 We use this fact to prove that $\TrFrob{G} : \CS(G) \to G(\Fq)^*$ is an isomorphism for connected commutative algebraic groups $G$.
@@
 Next, we consider character sheaves on \'etale commutative group schemes $G$ over $\Fq$ (\S\ref{sec:etale}).
-\'Etale group schemes form a counterpoint to connected algebraic groups, since the component group of any smooth group scheme is an \'etale group scheme.
+\'Etale group schemes form a counterpoint to connected algebraic groups, since the component group of any
+smooth group scheme is an \'etale group scheme.
 %etale group schemes are algebraic groups only when they are finite.
@@
 \]
-arising from the spectral sequence, the isomorphism $S_G$ allows us to show (\S\ref{ssec:SandT}) that the group homomorphism $\TrFrob{G}: \CSiso{G} \to G(\Fq)^*$ is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$.
-The necessity of using Weil local systems on $G$ in the definition of $\CS(G)$ already appears here:  if one were to use local systems on $G$ instead, the group homomorphism $\TrFrob{G}$ would not then be surjective (\S \ref{ssec:bS}).
+arising from the spectral sequence, the isomorphism $S_G$ allows us to show (\S\ref{ssec:SandT})
+that the group homomorphism $\TrFrob{G}: \CSiso{G} \to G(\Fq)^*$ is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$.
+The necessity of using Weil local systems on $G$ in the definition of $\CS(G)$ already appears here:
+if one were to use local systems on $G$ instead, the group homomorphism $\TrFrob{G}$ would not then be surjective (\S \ref{ssec:bS}). 
 Moreover, as examples show (\S \ref{eg:}), the kernel of $\TrFrob{G}$ is non-trivial in general.
-%The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling: if quasicharacter sheaves $(\gcs{L}, \mu,\phi)$ and $(\gcs{L}', \mu',\phi')$ determine the same character of $G(\Fq)$ then $(\gcs{L},\phi)$ and $(\gcs{L}',\phi')$ are isomorphic as Weil sheaves.
-
-%The appearance of $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ in these two cases is interesting: on the one hand, when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ and the trace of Frobenius gives an isomorphism $\TrFrob{G}: \CSiso{G} \to \Hom(G(\Fq),\EEx)$; on the other hand, if $G$ an \'etale commutative group scheme over $\Fq$, then $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ measures the kernel of $\TrFrob{G}: \CSiso{G} \to \Hom(G(\Fq),\EEx)$.
+%The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling:
+%if quasicharacter sheaves $(\gcs{L}, \mu,\phi)$ and $(\gcs{L}', \mu',\phi')$ determine the same character
+%of $G(\Fq)$ then $(\gcs{L},\phi)$ and $(\gcs{L}',\phi')$ are isomorphic as Weil sheaves.
+
+%The appearance of $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ in these two cases is interesting: on the one hand,
+%when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter
+%sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ and the trace of Frobenius gives an
+%isomorphism $\TrFrob{G}: \CSiso{G} \to \Hom(G(\Fq),\EEx)$; on the other hand, if $G$ an \'etale commutative
+%group scheme over $\Fq$, then $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ measures the kernel of $\TrFrob{G}: \CSiso{G} \to \Hom(G(\Fq),\EEx)$. 
 %This observation makes plain the fact that  . . .
-%Indeed, quasicharacter sheaves on \'etale commutative group schemes that are trivialized by discrete isogenies are invisible to the trace of Frobenius.
+%Indeed, quasicharacter sheaves on \'etale commutative group schemes that are trivialized
+%by discrete isogenies are invisible to the trace of Frobenius.
 
 Having understood $\CS(G)$ in two extreme cases --
-for connected commutative algebraic groups and for \'etale commutative group schemes -- we turn to the case of smooth commutative group schemes (\S\ref{sec:main}) using the component group sequence
+for connected commutative algebraic groups and for \'etale commutative group schemes --
+we turn to the case of smooth commutative group schemes (\S\ref{sec:main}) using the component group sequence
 \[
@@
 \]
-We show that the rows of this diagram are exact (\S\S\ref{ssec:restriction},\ref{ssec:component}), so we may apply the snake lemma to prove the main theorem of the paper,
+We show that the rows of this diagram are exact (\S\S\ref{ssec:restriction},\ref{ssec:component}),
+so we may apply the snake lemma to prove the main theorem of the paper,
 \begin{theorem*}[{Thm. \ref{thm:snake}}]
@@
 \noindent
-Thus, unless the component group scheme $\pi_0(\bG)$ is cyclic, category $\CS(G)$ contains non-trivial character sheaves lying in the kernel of the trace of Frobenius and therefore lost in translation to characters of $G(\Fq)$.
+Thus, unless the component group scheme $\pi_0(\bG)$ is cyclic, category $\CS(G)$ contains
+non-trivial character sheaves lying in the kernel of the trace of Frobenius and therefore lost in translation to characters of $G(\Fq)$.
 %These {\it invisible character sheaves} are parametrized by $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
 
-We also illuminate the nature of the category $\CS(G)$ by showing that every morphism in this category is either an isomorphism or trivial, and by showing
+We also illuminate the nature of the category $\CS(G)$ by showing that every morphism in this category
+is either an isomorphism or trivial, and by showing
 \begin{theorem*}[{Thm. \ref{thm:autornaught}}]
@@
 any local field $K$ with finite residue field $\Fq$ and to any commutative algebraic group over $K$ that admits a N\'eron model $X$.
-This class of algebraic groups over $K$ includes abelian varieties and unipotent $K$-wound groups, in addition to the algebraic tori we initially considered.
+This class of algebraic groups over $K$ includes abelian varieties and unipotent $K$-wound groups,
+in addition to the algebraic tori we initially considered.
 
@@
 Greenberg transform $\Gr_R(X)$ of the N\'eron model $X$.
-Although not locally of finite type, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and also a projective limit of smooth commutative group schemes $\Gr^R_n(X)$.
-This structure allows us to adapt our work on character sheaves on smooth group schemes over finite fields to construct (\S\ref{ssec:CS_on_GN}) a category $\QCS(X)$
+Although not locally of finite type, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and also a projective limit
+of smooth commutative group schemes $\Gr^R_n(X)$.
+This structure allows us to adapt our work on character sheaves on smooth group schemes over
+finite fields to construct (\S\ref{ssec:CS_on_GN}) a category $\QCS(X)$
 of {\it quasicharacter sheaves} for $X$, which are certain sheaves on $\Gr_R(X)\times_{\Spec{\Fq}} \Spec{\bFq}$, with extra structure.
@@
 
-Having defined quasicharacter sheaves on Neron models of commutative algebraic groups over $K$ and character sheaves on commutative group schemes over $\Fq$, we consider how
+Having defined quasicharacter sheaves on Neron models of commutative algebraic groups over $K$
+and character sheaves on commutative group schemes over $\Fq$, we consider how
 these categories are related as $K$ and $\Fq$ vary.  We describe (\S\ref{ssec:basechange}) functors between categories
@@
 \]
-where $X_*(T)_{\mathcal{I}_K}$ is the group of coinvariants of the cocharacter lattice $X_*(T)$ of the algebraic torus $T_K$ by the action of the inertia group $\mathcal{I}_K$ of $K$, and where $\Hom_\text{}(T(K),\EEx)$ denotes the group of quasicharacters of $T(K)$.
+where $X_*(T)_{\mathcal{I}_K}$ is the group of coinvariants of the cocharacter lattice $X_*(T)$ of the algebraic torus
+$T_K$ by the action of the inertia group $\mathcal{I}_K$ of $K$, and where $\Hom_\text{}(T(K),\EEx)$
+denotes the group of quasicharacters of $T(K)$.
 We further show that automorphism groups in $\QCS(T)$ are given, for every quasicharacter sheaf $\cs{F}$ for $T$, by
@@
 By any measure, there are more quasicharacter sheaves for $T$ than quasicharacters of $T(K)$.  
-In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization of complete Langlands parameters for $p$-adic groups 
+In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization
+of complete Langlands parameters for $p$-adic groups 
 and, in the process, is led to study the representations of all the pure rational forms of the $p$-adic group, simultaneously.
-A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group \cite{bernstein:vogan_conference}.
-Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to quasicharacters of all the pure rational forms of $T$; we do not pursue that suggestion in this paper.
+A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads
+to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category
+which appears to be tied to the representations of all the pure rational forms of the $p$-adic group \cite{bernstein:vogan_conference}.
+Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to
+quasicharacters of all the pure rational forms of $T$; we do not pursue that suggestion in this paper.
 \fi
@@
 beginning with \cite{lusztig:disconnected1}.
-When commutative, it is not difficult to relate Frobenius-stable character sheaves to our character sheaves (Remark~\ref{rem:Lusztig}).
-The new features that we have found pertaining to Weil sheaves and $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ do not arise in that context because, for such groups, Weil sheaves are unnecessary (\S \ref{ssec:alg_groups} and $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}=0$ (Remark \ref{rem:H2}).
+When commutative, it is not difficult to relate Frobenius-stable character sheaves to our character sheaves
+(Remark~\ref{rem:Lusztig}). The new features that we have found pertaining to Weil sheaves
+and $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ do not arise in that context because, for such groups,
+Weil sheaves are unnecessary (\S \ref{ssec:alg_groups}) and $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}=0$ (Remark \ref{rem:H2}).
 
 %We also want to situate our terminology in a historical context.
-For a connected commutative algebraic group over a finite field, it is not uncommon to refer to local systems satisfying \eqref{introbox}  as character sheaves; see for example, \cite{kamgarpour:09a}*{Intro}.
-Our definition of character sheaves on smooth commutative group schemes over finite fields evolved from this notion, with an eye toward quasicharacters of $p$-adic groups.
-The process of creating a category from the group of quasicharacters of a $p$-adic  torus informs our choice of the term quasicharacter sheaf in this paper.
-
-We anticipate that future work on quasicharacter sheaves will make use of   \cite{suzuki-yoshida:12a} and \cite{Suzuki:Neron}, and will clarify the relation between this project and other attempts to geometrize admissible distributions on $p$-adic groups, such as \cite{Cunningham-Kamgarpour} (limited to quasicharacters of $\ZZ_p^\times$) and \cite{Aubert-Cunningham} (limited to characters of depth-zero representations).
-We are actively pursuing the question of how to extend the notion of quasicharacter sheaves to provide a geometrization of admissible distributions on connected reductive algebraic groups over $p$-adic fields, not just commutative ones.
+For a connected commutative algebraic group over a finite field, it is not uncommon to refer to
+local systems satisfying \eqref{introbox}  as character sheaves; see for example, \cite{kamgarpour:09a}*{Intro}.
+Our definition of character sheaves on smooth commutative group schemes over finite fields evolved from this notion,
+with an eye toward quasicharacters of $p$-adic groups.
+The process of creating a category from the group of quasicharacters of a $p$-adic torus informs our choice of the
+term quasicharacter sheaf in this paper.
+
+We anticipate that future work on quasicharacter sheaves will make use of   \cite{suzuki-yoshida:12a} and \cite{Suzuki:Neron},
+and will clarify the relation between this project and other attempts to geometrize admissible distributions on $p$-adic groups,
+such as \cite{Cunningham-Kamgarpour} (limited to quasicharacters of $\ZZ_p^\times$) and \cite{Aubert-Cunningham}
+(limited to characters of depth-zero representations). 
+We are actively pursuing the question of how to extend the notion of quasicharacter sheaves to provide a geometrization
+of admissible distributions on connected reductive algebraic groups over $p$-adic fields, not just commutative ones.
 
@@
 quasicharacter sheaves.  We also thank them for their kindness, knowledge and invaluable help.
-We thank Takashi Suzuki for clarifying the relation between this project and his recent work and for very helpful observations and suggestions, especially related to our use of the Hochschild-Serre spectral sequence.
-We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning the Greenberg realization functor and for drawing our attention to their result on Weil restriction and the Greenberg transform.
+We thank Takashi Suzuki for clarifying the relation between this project and his recent work and for very helpful
+observations and suggestions, especially related to our use of the Hochschild-Serre spectral sequence.
+We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning
+the Greenberg realization functor and for drawing our attention to their result on Weil restriction and the Greenberg transform.
 Finally, we thank Joseph Bernstein for very helpful comments. 
@@
 
-\begin{remark}
+\begin{remark} \label{rem:H2}
 Recall the K\"unneth formula in group cohomology \cite{brown:CohomologyOfGroups}*{Prop. I.0.8}: if $A$ and $A'$ are groups and $M$ and $M'$ are abelian groups with $M$ $\ZZ$-free, then

### 2015-07-21 dictionary.tex
Finished line breaks

@@
 and $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ do not arise in that context because, for such groups,
-Weil sheaves are unnecessary (\S \ref{ssec:alg_groups}) and $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}=0$ (Remark \ref{rem:H2}).
+Weil sheaves are unnecessary (\S \ref{ssec:alg_groups} and $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}=0$ (Remark \ref{rem:H2}).
 
@@
 
-{Finally, we gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences and the National Science and Engineering Research Council (Canada), as well the hospitality of the Banff International Research Station during a Research in Teams program.}
+{Finally, we gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
+and the National Science and Engineering Research Council (Canada), as well the hospitality of the
+Banff International Research Station during a Research in Teams program.}
 
@@
 \begin{enumerate}
-\labitem{(CS.1)}{CS.1} $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean a constructible $\ell$-adic sheaf on $\bG$, {\it lisse} on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
+\labitem{(CS.1)}{CS.1} $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean a constructible
+$\ell$-adic sheaf on $\bG$, {\it lisse} on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
 \labitem{(CS.2)}{CS.2} $\mu: \bm^* \gcs{L} \to \LxL$ is an isomorphism of
@@
 Suppose $\rho \in \Hom(\cs{L},\cs{L}')$.
-We prove the lemma by considering the linear transformations $\brho_{\bg} : \gcs{L}_{\bg} \to \gcs{L}_{\bg}$ at the stalks above geometric points $\bg$ on $G$ and showing that, either each $\brho_{\bg}$ trivial or each $\brho_{\bg}$ is an isomorphism.
+We prove the lemma by considering the linear transformations $\brho_{\bg} : \gcs{L}_{\bg} \to \gcs{L}_{\bg}$ at the stalks
+above geometric points $\bg$ on $G$ and showing that, either each $\brho_{\bg}$ trivial or each $\brho_{\bg}$ is an isomorphism.
 (This idea is expanded upon in Section~\ref{ssec:stalks}.)
@@
 If $\brho_{\bar e} = 0$ then the second diagram in \ref{CS.4} implies that $\brho_{\bg} = 0$ for all $\bg$, in which case $\rho$ is trivial.
-On the other hand, if $\brho_{\bar e}$ is non-trivial then the second diagram in \ref{CS.4}  implies that $\brho_{\bg}$ is non-trivial for all $\bg$ and thus an isomorphism, since the stalks of character sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
+On the other hand, if $\brho_{\bar e}$ is non-trivial then the second diagram in \ref{CS.4} implies that $\brho_{\bg}$ is non-trivial
+for all $\bg$ and thus an isomorphism, since the stalks of character sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
 \end{proof}
@@
 
-In this section we introduce two tools which will help us understand isomorphism classes of objects in $\CS(G)$: the map $\CSiso{G} \to G(k)^*$ given by trace of Frobenius and the pullback functor $\CS(G) \to \CS(H)$ associated to a morphism $H \to G$ of smooth group schemes over $\Fq$.
+In this section we introduce two tools which will help us understand isomorphism classes of objects in $\CS(G)$:
+the map $\CSiso{G} \to G(k)^*$ given by trace of Frobenius and the pullback functor $\CS(G) \to \CS(H)$
+associated to a morphism $H \to G$ of smooth group schemes over $\Fq$.
 
@@
 determines a geometric point $\bg$ fixed by $\Frob{G}$. 
-Together with the canonical isomorphism $(\Frob{G}^*\gcs{L})_{\bg} \iso  \gcs{L}_{\Frob{G}(\bg)}$, the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gcs{L}_{\bg}$.
-Let $\trace(\phi_{\bg};\gcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gcs{L}_{\bg})$ and let $\trFrob{(\gcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by 
+Together with the canonical isomorphism $(\Frob{G}^*\gcs{L})_{\bg} \iso  \gcs{L}_{\Frob{G}(\bg)}$,
+the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gcs{L}_{\bg}$.
+Let $\trace(\phi_{\bg};\gcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gcs{L}_{\bg})$ and let
+$\trFrob{(\gcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by 
 \begin{equation}\label{trWeil}
@@
 \ref{CS.3} guarantee
-that the function $\trFrob{(\gcs{L},\phi)} : G(\Fq)\to \EEx$ is a group homomorphism, which we will also denote by $\trFrob{\cs{L}}$.  Moreover,
-this homomorphism depends only on the isomorphism class of $\cs{L}$, so we obtain a map
+that the function $\trFrob{(\gcs{L},\phi)} : G(\Fq)\to \EEx$ is a group homomorphism, which we will also denote by $\trFrob{\cs{L}}$.
+Moreover, this homomorphism depends only on the isomorphism class of $\cs{L}$, so we obtain a map
 \begin{align*}
@@
 The next two results follow easily from the definitions.
-%In the remainder of this section We devote the remainder of this section to studying the behavior of the trace of Frobenius under morphisms of group schemes.
-These simple but important properties of pullbacks and external products will be used in the proofs of many results in this paper.
+%In the remainder of this section We devote the remainder of this section to studying the behavior
+%of the trace of Frobenius under morphisms of group schemes.  These simple but important properties of
+%pullbacks and external products will be used in the proofs of many results in this paper.
 
@@
 
-If $G_1$ and $G_2$ are smooth commutative group schemes over $\Fq$ then characters of $(G_1 \times G_2)(\Fq)$ all take the form $\chi_1\otimes \chi_2$ for characters $\chi_1$ of $G_1(\Fq)$ and $\chi_2$ of $G_2(\Fq)$.
+If $G_1$ and $G_2$ are smooth commutative group schemes over $\Fq$ then characters of $(G_1 \times G_2)(\Fq)$
+all take the form $\chi_1\otimes \chi_2$ for characters $\chi_1$ of $G_1(\Fq)$ and $\chi_2$ of $G_2(\Fq)$. 
 The next lemma shows that character sheaves on $G$ enjoy an analogous property.
@@
 \]
-Moreover, every character sheaf on $G_1\times G_2$ is isomorphic to $\cs{L}_1\boxtimes\cs{L}_2$ for some character sheaves $\cs{L}_1$ on $G_1$ and $\cs{L}_2$ on $G_2$.
+Moreover, every character sheaf on $G_1\times G_2$ is isomorphic to $\cs{L}_1\boxtimes\cs{L}_2$
+for some character sheaves $\cs{L}_1$ on $G_1$ and $\cs{L}_2$ on $G_2$.
 \end{lemma}
@@
 %Before turning our attention to character sheaves on connected commutative algebraic groups in Section~\ref{ssec:connected}, 
-%Here we treat two special classes of character sheaves on arbitrary smooth commutative group schemes $G$: those that descend from local systems on $\bG$ to local systems on $G$ (\S \ref{ssec:descentG}); and those that are defined by discrete isogenies onto $G$ (\S \ref{ssec:discrete_isogenies}).
-The latter will play a role in Sections~\ref{ssec:connected} and \ref{ssec:restriction}.
-
-In this section we consider a category of sheaves on $G$ obtained by replacing the Weil sheaf $(\gcs{L}, \phi)$ on $\bG$ in the definition of a character sheaf with an $\ell$-adic local system on $G$ itself; these will play a role in Sections~\ref{ssec:connected} and \ref{ssec:alg_groups}.
+%Here we treat two special classes of character sheaves on arbitrary smooth commutative group schemes $G$:
+%those that descend from local systems on $\bG$ to local systems on $G$ (\S \ref{ssec:descentG});
+%and those that are defined by discrete isogenies onto $G$ (\S \ref{ssec:discrete_isogenies}).
+%The latter will play a role in Sections~\ref{ssec:connected} and \ref{ssec:restriction}.
+
+In this section we consider a category of sheaves on $G$ obtained by replacing the Weil sheaf $(\gcs{L}, \phi)$
+on $\bG$ in the definition of a character sheaf with an $\ell$-adic local system on $G$ itself;
+these will play a role in Sections~\ref{ssec:connected} and \ref{ssec:alg_groups}.
 
@@
  This construction defines the functor $B_G : \bCS(G) \to \CS(G)$ given on objects by $(\cs{E},\mu_\cs{E}) \mapsto (\gcs{L},\mu, \phi)$, as defined here. 
- Because morphisms in $\bCS(G)$ and $\CS(G)$ are morphisms of local systems on $G$ and $\bG$, respectively, satisfying condition~\ref{CS.4}, this functor is also full and faithful.
+ Because morphisms in $\bCS(G)$ and $\CS(G)$ are morphisms of local systems on $G$ and $\bG$,
+ respectively, satisfying condition~\ref{CS.4}, this functor is also full and faithful.
 \end{proof}
@@
 \begin{remark}\label{rem:descent}
-In fact, it is not difficult to recognize character sheaves that descend to $G$: they are exactly those character sheaves $\cs{L} = (\gcs{L},\mu,\phi)$ for which the action of $W$ on $\gcs{L}$ given by $\phi$ extends to a continuous action of $\Gal(\bFq/\Fq)$ on $\gcs{L}$; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII, Rappel 1.1.3} for example.
+In fact, it is not difficult to recognize character sheaves that descend to $G$: they are exactly those character sheaves
+$\cs{L} = (\gcs{L},\mu,\phi)$ for which the action of $W$ on $\gcs{L}$ given by $\phi$ extends to a continuous action
+of $\Gal(\bFq/\Fq)$ on $\gcs{L}$; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII, Rappel 1.1.3} for example. 
 \end{remark}
@@
 
-Here we consider character sheaves on $G$ that are defined by discrete isogenies onto $G$ (\S \ref{ssec:discrete_isogenies}); these will play a role in Section~\ref{ssec:restriction}.
-
-A finite, \'etale, surjective morphism $H\to G$ of smooth group schemes over $\Fq$ for which the action of $\Gal(\bFq/\Fq)$ on the kernel is trivial is called a {\it discrete isogeny}, inspired by \cite{kamgarpour:09a}*{\S 2.2}.
+Here we consider character sheaves on $G$ that are defined by discrete isogenies onto $G$
+(\S \ref{ssec:discrete_isogenies}); these will play a role in Section~\ref{ssec:restriction}.
+
+A finite, \'etale, surjective morphism $H\to G$ of smooth group schemes over $\Fq$ for which the action
+of $\Gal(\bFq/\Fq)$ on the kernel is trivial is called a {\it discrete isogeny}, inspired by \cite{kamgarpour:09a}*{\S 2.2}.
 
@@
 We must show that $\cs{E}$ comes equipped with an isomorphism $\mu_\cs{E} : m^* \cs{E} \to \cs{E}\boxtimes\cs{E}$.
-To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems on $G$ and $A$-equivariant local systems on $H$ {\it cf.\ } \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}.
+To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems
+on $G$ and $A$-equivariant local systems on $H$ {\it cf.\ } \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}. 
 In particular, $f^*\cs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
@@
 \begin{remark}
-A descent argument similar to the one employed in the proof of Lemma~\ref{prop:finite} is used in \cite{Drinfeld:math/0609769}*{Lemma~1.10}, though in the more restrictive case of connected algebraic groups.
+A descent argument similar to the one employed in the proof of Lemma~\ref{prop:finite} is used in
+\cite{Drinfeld:math/0609769}*{Lemma~1.10}, though in the more restrictive case of connected algebraic groups.
 \end{remark}
@@
 
-If the smooth commutative group scheme $G$ is of finite type, every character sheaf descends to $G$; we will see that they are not equivalent, in general, however.
+If the smooth commutative group scheme $G$ is of finite type, every character sheaf descends to $G$;
+we will see that they are not equivalent, in general, however.
 For now, we treat the connected case.
@@
 \begin{proof}
-In Lemma~\ref{lem:bounded_connected}, we saw that every character sheaf $\cs{L}$ on $\bG$ descends to $G$; let $\cs{E}$ be an object of $\bCS(G)$ for which $B_G(\cs{E}) \iso \cs{L}$.
+In Lemma~\ref{lem:bounded_connected}, we saw that every character sheaf $\cs{L}$ on $\bG$ descends to $G$;
+let $\cs{E}$ be an object of $\bCS(G)$ for which $B_G(\cs{E}) \iso \cs{L}$.
  Since the functor $B_G : \bCS(G) \to \CS(G)$ is full and faithful, $\Aut(\cs{L}) = \Aut(\cs{E})$.
-From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields, as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3}, gives us all we need, as we briefly recall.
+From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields,
+as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3}, gives us all we need, as we briefly recall.
 %\todo{Fix citelist} %\citelist{\cite{deligne:SGA4.5}*{Sommes trig.},\cite{laumon:87a}*{1.1.3}}
 
-As in the proof of Proposition~\ref{prop:finite}, use \'etale descent to see that pullback by the Lang isogeny $\Lang : G\to G$ defines an equivalence of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.
-Under this equivalence, local systems $\cs{E}$ on $G$ arising from objects in $\bCS(G)$ are matched with $G(\Fq)$-equivariant constant local systems of rank-one on $G$, and therefore with one-dimensional representations of $G(\Fq)$.
-In the same way, pullback along the isogeny $\Lang\times\Lang : G\times G\to G\times G$ matches the extra structure $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ with an isomorphism $m^*V \to V\boxtimes V$ of one-dimensional representations of $G(\Fq)\times G(\Fq)$, which is exactly an isomorphism $V \to V\otimes V$ of one-dimensional representations, which is exactly the choice of an isomorphism $V\iso \EE$.
+As in the proof of Proposition~\ref{prop:finite}, use \'etale descent to see that pullback by the Lang isogeny $\Lang : G\to G$
+defines an equivalence of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$. 
+Under this equivalence, local systems $\cs{E}$ on $G$ arising from objects in $\bCS(G)$ are matched with $G(\Fq)$-equivariant
+constant local systems of rank-one on $G$, and therefore with one-dimensional representations of $G(\Fq)$. 
+In the same way, pullback along the isogeny $\Lang\times\Lang : G\times G\to G\times G$ matches the extra structure
+$\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ with an isomorphism $m^*V \to V\boxtimes V$ of one-dimensional
+representations of $G(\Fq)\times G(\Fq)$, which is exactly an isomorphism $V \to V\otimes V$ of one-dimensional representations,
+which is exactly the choice of an isomorphism $V\iso \EE$.
 We see that $\bCS(G)$ is equivalent to the category of characters of $G(\Fq)$.
-Let $\bg$ be a geometric point above $g \in G(\Fq)$.
-If $\cs{E}$ matches $\psi : G(\Fq)\to \EEx$ under this equivalence, a simple calculation on stalks reveals that the action of Frobenius on $\cs{E}_{\bg}$ is multiplication by $\psi(g)^{-1}$.
-In other words, for every $\cs{E}$ in $\bCS(G)$, the trace of $\Lang^*\cs{E}$ is $\trFrob{\cs{E}}^{-1}$ as a representation of $G(\Fq)$, proving parts \ref{c1} and \ref{c2}.
+Let $\bg$ be a geometric point above $g \in G(\Fq)$.  If $\cs{E}$ matches $\psi : G(\Fq)\to \EEx$ under this equivalence,
+a simple calculation on stalks reveals that the action of Frobenius on $\cs{E}_{\bg}$ is multiplication by $\psi(g)^{-1}$.
+In other words, for every $\cs{E}$ in $\bCS(G)$, the trace of $\Lang^*\cs{E}$ is $\trFrob{\cs{E}}^{-1}$ as a
+representation of $G(\Fq)$, proving parts \ref{c1} and \ref{c2}.
 
@@
 
-We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of character sheaves on $G$ is equivalent to the category of one-dimensional representations $V$ of $G(\Fq)$ equipped with an isomorphism $V\iso \EE$, and therefore equivalent to the category of characters $\psi$ of $G(\Fq)$.
-We have also just seen that if the character of $\Lang^*\cs{E}$ is $\psi$ then the canonical isomorphism $m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\cs{E} : \cs{E} \to \cs{E}\boxtimes\cs{E}$.
-This fact leads (back) to a perspective on the function-sheaf dictionary common in the literature in which one considers one-dimensional local systems $\cs{E}$ on $G$ for which \emph{there exists} an isomorphism $m^*\cs{E} \iso \cs{E} \boxtimes\cs{E}$ \cite{kamgarpour:09a}*{Intro}.
-As a slight variation, one may also consider one-dimensional local systems $\gcs{L}$ on $\bG$ for which \emph{there exists} an isomorphism $\Frob{G}^*\gcs{L} \iso \gcs{L}$ and an isomorphism $\bm^*\gcs{L} \iso \gcs{L} \boxtimes\gcs{L}$.
-
-Although the category $\CS(G)$ of character sheaves on $G$ specializes to $\bCS(G)$ when $G$ is of finite type (\S \ref{ssec:alg_groups}), this description is \emph{not} sufficient when extending the dictionary to smooth commutative group schemes, as we will see already in Section~\ref{sec:etale}.
+We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of character sheaves
+on $G$ is equivalent to the category of one-dimensional representations $V$ of $G(\Fq)$ equipped with an isomorphism
+$V\iso \EE$, and therefore equivalent to the category of characters $\psi$ of $G(\Fq)$.
+We have also just seen that if the character of $\Lang^*\cs{E}$ is $\psi$ then the canonical isomorphism
+$m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\cs{E} : \cs{E} \to \cs{E}\boxtimes\cs{E}$.
+This fact leads (back) to a perspective on the function-sheaf dictionary common in the literature in which one considers
+one-dimensional local systems $\cs{E}$ on $G$ for which \emph{there exists} an isomorphism
+$m^*\cs{E} \iso \cs{E} \boxtimes\cs{E}$ \cite{kamgarpour:09a}*{Intro}.
+As a slight variation, one may also consider one-dimensional local systems $\gcs{L}$ on $\bG$ for which \emph{there exists}
+an isomorphism $\Frob{G}^*\gcs{L} \iso \gcs{L}$ and an isomorphism $\bm^*\gcs{L} \iso \gcs{L} \boxtimes\gcs{L}$.
+
+Although the category $\CS(G)$ of character sheaves on $G$ specializes to $\bCS(G)$ when $G$ is of finite type
+(\S \ref{ssec:alg_groups}), this description is \emph{not} sufficient when extending the dictionary to smooth
+commutative group schemes, as we will see already in Section~\ref{sec:etale}.
 In particular, for a given $\gcs{L}$ and $\phi$ there may be many $\mu$ so that $(\gcs{L},\mu,\phi)$ is a character sheaf.
 For \'etale $G$, Proposition~\ref{prop:etale-iso} shows that $\Hh^2(\bG,\EEx)^{\Weil{}}$ measures the possibilities for $\mu$.
-We will see in Section~\ref{sec:main} that $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ plays an analogous role for general smooth commutative group schemes $G$.
+We will see in Section~\ref{sec:main} that $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ plays an analogous role for general
+smooth commutative group schemes $G$.
 
@@
 
-Moreover, since $\Weil{} \cong \ZZ$ has cohomological dimension $1$, $E_2^{i,j} = 0$ for $i > 1$ and the sequence degenerates at the second page: $E_{\infty}^{i,j} = E_2^{i,j}$.
-We obtain the following corollary:
+Moreover, since $\Weil{} \cong \ZZ$ has cohomological dimension $1$, $E_2^{i,j} = 0$ for $i > 1$ and the
+sequence degenerates at the second page: $E_{\infty}^{i,j} = E_2^{i,j}$. We obtain the following corollary:
 
@@
 for $x, y \in \bG$.
-Let $\alpha \in C^0(\Weil{},C^2(\bG,\EEx)$ be the $0$-cochain corresponding to $a$ and let $\beta\in C^1(\Weil{},C^1(\bG,\EEx)$ be the cocycle such that $\beta(\Frob{})$ is $b$.
-We will write both $\alpha$ and $\beta$ additively.
+Let $\alpha \in C^0(\Weil{},C^2(\bG,\EEx)$ be the $0$-cochain corresponding to $a$ and let $\beta\in C^1(\Weil{},C^1(\bG,\EEx)$
+be the cocycle such that $\beta(\Frob{})$ is $b$.  We will write both $\alpha$ and $\beta$ additively.
 Then
@@
 Although the cocycle $\alpha\oplus \beta$ is not well defined by $\cs{L}$, its class in $\Hh^2(E^\bullet_G)$ is.
-To see this, let $\{ v'_x \in \gcs{L}_x^\times \tq x \in \bG\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$ be defined by $\cs{L}$ and this choice, as above.
+To see this, let $\{ v'_x \in \gcs{L}_x^\times \tq x \in \bG\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$
+be defined by $\cs{L}$ and this choice, as above.
 Now let $\delta \in C^0(\Weil{},C^1(\bG,\EEx))$ correspond to the function $d : \bG\to \EEx$ defined by $v'_x = d(x) v_x$.
@@
 \end{align*}
-It is also easy to see that $[\alpha_1\oplus\beta_1] + [\alpha_2\oplus\beta_2] = [\alpha_3\oplus\beta_3]$ when $\cs{L}_3 = \cs{L}_1\otimes \cs{L}_2$, so $S_G$ is a group homomorphism.
+It is also easy to see that $[\alpha_1\oplus\beta_1] + [\alpha_2\oplus\beta_2] = [\alpha_3\oplus\beta_3]$
+when $\cs{L}_3 = \cs{L}_1\otimes \cs{L}_2$, so $S_G$ is a group homomorphism.
 
 %\begin{remark}
-%Although we will mainly use the group homomorphism $S_G : \CSiso{G}\to \Hh^2(E^\bullet_G)$ when $G$ is an \'etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$;
+%Although we will mainly use the group homomorphism $S_G : \CSiso{G}\to \Hh^2(E^\bullet_G)$ when $G$
+%is an \'etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$;
 %however, the next result does not extend to all smooth commutative group schemes.
@@
 
-In this section we fit the group homomorphisms $\TrFrob{G}$ and $S_G$ into a commutative diagram, determining the kernel and cokernel of $\TrFrob{G}$ when $G$ is an \'etale commutative group scheme over $\Fq$.
+In this section we fit the group homomorphisms $\TrFrob{G}$ and $S_G$ into a commutative diagram,
+determining the kernel and cokernel of $\TrFrob{G}$ when $G$ is an \'etale commutative group scheme over $\Fq$.
 
@@
 Let $[\beta]\in \Hh^1(\Weil{},\bG^*)$ be the class corresponding to $\chi$ under Lemma~\ref{lem:dual-inv}.
-Every representative cocycle $\beta \in Z^1(\Weil{},\bG^*)$ determines a homomorphism $\beta(\Frob{}) : G(\bFq)\to \EEx$ such that $\beta(\Frob{})\vert_{G(\Fq)} = \chi$.
+Every representative cocycle $\beta \in Z^1(\Weil{},\bG^*)$ determines a homomorphism
+$\beta(\Frob{}) : G(\bFq)\to \EEx$ such that $\beta(\Frob{})\vert_{G(\Fq)} = \chi$.
 Set $\gcs{L}_x = \EE$ for every $x\in G(\bFq)$.
@@
 For each $x\in G(\bFq)$, define $\brho_x :\cs{L}_x\to \cs{L}'_x$ by $\brho_x(1) = d(x)$.
-The collection of isomorphisms $\{ \brho_x \tq x\in G(\bFq)\}$ satisfies condition~\ref{CS.4}, so it defines a morphism $\rho : \cs{L}\to \cs{L}'$, which is clearly an isomorphism. 
+The collection of isomorphisms $\{ \brho_x \tq x\in G(\bFq)\}$ satisfies condition~\ref{CS.4},
+so it defines a morphism $\rho : \cs{L}\to \cs{L}'$, which is clearly an isomorphism. 
 %
@@
 
-Now suppose $\chi_1, \chi_2 \in G(\Fq)^*$.
-Pick cocycles $\beta_1,\beta_2\in Z^1(\Weil{},\bG^*)$ and construct character sheaves $\cs{L}_1$ and $\cs{L}_2$ on $G$ as above.
-Since $\cs{L}_1\otimes \cs{L}_2$ is exactly the character sheaf built from the cocycle $\beta_1\cdot \beta_2$, and since $\trFrob{\cs{L}_1\otimes \cs{L}_2} = \trFrob{\cs{L}_1}\cdot \trFrob{\cs{L}_2}$, the section of $\TrFrob{G}$ defined here is a homomorphism.
+Now suppose $\chi_1, \chi_2 \in G(\Fq)^*$. Pick cocycles $\beta_1,\beta_2\in Z^1(\Weil{},\bG^*)$ and
+construct character sheaves $\cs{L}_1$ and $\cs{L}_2$ on $G$ as above. Since $\cs{L}_1\otimes \cs{L}_2$
+is exactly the character sheaf built from the cocycle $\beta_1\cdot \beta_2$, and since
+$\trFrob{\cs{L}_1\otimes \cs{L}_2} = \trFrob{\cs{L}_1}\cdot \trFrob{\cs{L}_2}$, the section of $\TrFrob{G}$ defined here is a homomorphism.
 \end{proof}
@@
 
-\begin{remark} \label{rem:H2}
-Recall the K\"unneth formula in group cohomology \cite{brown:CohomologyOfGroups}*{Prop. I.0.8}: if $A$ and $A'$ are groups and $M$ and $M'$ are abelian groups with $M$ $\ZZ$-free, then
-\[
-\Hh^n(A \times A', M \otimes M') \cong \bigoplus_{i+j=n} \Hh^i(A, M) \otimes \Hh^j(A', M') \ \ \oplus \bigoplus_{i+j=n+1} \Tor_1^{\ZZ}\left(\Hh^i(A, M), \Hh^j(A', M')\right).
+\begin{remark}
+Recall the K\"unneth formula in group cohomology \cite{brown:CohomologyOfGroups}*{Prop. I.0.8}:
+if $A$ and $A'$ are groups and $M$ and $M'$ are abelian groups with $M$ $\ZZ$-free, then
+\[
+\Hh^n(A \times A', M \otimes M') \cong \bigoplus_{i+j=n} \Hh^i(A, M) \otimes \Hh^j(A', M') \ \ \oplus
+\bigoplus_{i+j=n+1} \Tor_1^{\ZZ}\left(\Hh^i(A, M), \Hh^j(A', M')\right).
 \]
@@
 Let $a$ be a $2$-cocycle corresponding to this extension, with values in $\{\pm 1\}$. When $\Frob{G}$ acts trivially on $\bG$,
-any homomorphism $b : \bG \to \EEx$ will satisfy \eqref{eq:nohom}, and the corresponding $\alpha \oplus \beta$ are non-cohomologous in $\Hh^2(E_G^\bullet)$.
+any homomorphism $b : \bG \to \EEx$ will satisfy \eqref{eq:nohom}, and the corresponding
+$\alpha \oplus \beta$ are non-cohomologous in $\Hh^2(E_G^\bullet)$.
 When $\Frob{G}$ exchanges $i$ and $j$, then we may take $b(1) = 1, b(i) = -1$ and $b(j) = b(k) = \pm 1$, up to coboundaries.
@@
 for which the maps are given by the analogues of Proposition~\ref{prop:ses_desc}.
-Moreover, using \cite{deligne-katz:SGA7.2}*{Expos\'e XIII, Rappel 1.1.3} we see that Proposition~\ref{prop:SGiso} adapts to provide an isomorphism $\bCSiso{G}\to \Hh^2(F^\bullet_G)$ compatible with $\bCS(G) \to \CS(G)$ and with the
+Moreover, using \cite{deligne-katz:SGA7.2}*{Expos\'e XIII, Rappel 1.1.3} we see that Proposition~\ref{prop:SGiso}
+adapts to provide an isomorphism $\bCSiso{G}\to \Hh^2(F^\bullet_G)$ compatible with $\bCS(G) \to \CS(G)$ and with the
 the canonical map of exact sequences 
@@
 Pick $i\in \pi_0(G)$ and let $G^i \hookrightarrow G$ be the corresponding connected component. 
-Pick a geometric point $x$ on $G^i$ and observe that since $G^i$ is connected as a $\Fq$-scheme, $G^i(\bFq)$ is canonically identified with the $\Gal(\bFq/\Fq)$-orbit of $x$. 
+Pick a geometric point $x$ on $G^i$ and observe that since $G^i$ is connected as a $\Fq$-scheme,
+$G^i(\bFq)$ is canonically identified with the $\Gal(\bFq/\Fq)$-orbit of $x$. 
 We remark that while $G^i$ is defined over $\Fq$, the set $G^i(\Fq)$ is non-empty only when $G^i(\bFq) = \{ x\}$.
@@
 Letting $i$ range over $\pi_0(G)$ we conclude that $\Hh^1(\Fq,\Hh^1(\bG,\EEx)) = \Hh^1(\Fq,\Hh^1(\bG,\ZEx))$.
-When adapted to abelian groups with continuous action of $\Gal(\bFq/\Fq)$, the strategy of the proof of Lemma~\ref{lem:dual-inv} gives $\Hh^1(\Fq,\Hh^1(\bG,\ZEx)) =  \Hom(G(\Fq),\ZEx)$, concluding the proof.
-\end{proof}
-
-Proposition~\ref{prop:bounded-etale} reveals the necessity of working with Weil sheaves in Definition~\ref{def:CS}: one cannot geometrize all characters of $G(\Fq)$ using local systems on $G$, for general smooth commutative groups schemes $G$.
+When adapted to abelian groups with continuous action of $\Gal(\bFq/\Fq)$, the strategy of the proof of
+Lemma~\ref{lem:dual-inv} gives $\Hh^1(\Fq,\Hh^1(\bG,\ZEx)) =  \Hom(G(\Fq),\ZEx)$, concluding the proof.
+\end{proof}
+
+Proposition~\ref{prop:bounded-etale} reveals the necessity of working with Weil sheaves in Definition~\ref{def:CS}:
+one cannot geometrize all characters of $G(\Fq)$ using local systems on $G$, for general smooth commutative groups schemes $G$.
 Proposition~\ref{prop:bounded-etale} is extended to all smooth commutative groups schemes in Section~\ref{ssec:revisited}.
@@
 bounded.
-If $\chi' : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi'(1) = 1+\ell$ and if $\cs{L}'$ corresponds to $\chi'$ under Proposition~\ref{prop:sur_etale},
+If $\chi' : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi'(1) = 1+\ell$ and if $\cs{L}'$
+corresponds to $\chi'$ under Proposition~\ref{prop:sur_etale},
 then $\cs{L}'$ does descend to $G$, since the image of $\chi'$ is
@@
 However, $\cs{L}'$ is not defined by a discrete isogeny (\S \ref{ssec:discrete_isogenies}). 
-If $\chi'' : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi''(1) = \zeta$, a root of unity in $\EEx$, and if $\cs{L}''$ corresponds to $\chi''$ under Proposition~\ref{prop:sur_etale},
+If $\chi'' : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi''(1) = \zeta$, a root of unity in
+$\EEx$, and if $\cs{L}''$ corresponds to $\chi''$ under Proposition~\ref{prop:sur_etale},
 then $\cs{L}''$ is defined by a discrete isogeny. 
@@
 %While most of this paper focuses on the question of determining the isomorphism classes of objects, 
-A complete understanding of the morphisms in $\CS(G)$ also requires a description of the automorphisms of an arbitrary character sheaf $\cs{L}$.
+A complete understanding of the morphisms in $\CS(G)$ also requires a description of the
+automorphisms of an arbitrary character sheaf $\cs{L}$.
 
@@
 Now suppose $\rho \in \Aut(\cs{L})$.
-The second diagram in \ref{cs.4} shows that the association $x \mapsto \brho_x$ is a homomorphism from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{cs.4} shows that it factors through $G(\bFq) \to G(\bFq)_{\Weil{}}$.
-
-Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism, then defining $\brho_x$ as multiplication by $\rho(x)$ will define a morphism $\gcs{L} \to \gcs{L}'$ satisfy the two diagrams in \ref{cs.4}.
-
-Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the resulting bijection is actually a group isomorphism.
+The second diagram in \ref{cs.4} shows that the association $x \mapsto \brho_x$ is a homomorphism
+from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{cs.4} shows that it factors through $G(\bFq) \to G(\bFq)_{\Weil{}}$.
+
+Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism, then defining $\brho_x$ as multiplication
+by $\rho(x)$ will define a morphism $\gcs{L} \to \gcs{L}'$ satisfy the two diagrams in \ref{cs.4}.
+
+Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the
+resulting bijection is actually a group isomorphism.
 \end{proof}
@@
 
-We now wish to apply the results of Section~\ref{ssec:connected} to the identity component of $G$, for which we must confirm that the identity component of $G$ is actually an algebraic group over $\Fq$.
+We now wish to apply the results of Section~\ref{ssec:connected} to the identity component of $G$,
+for which we must confirm that the identity component of $G$ is actually an algebraic group over $\Fq$.
 
@@
 For each $x\in \pi_0(\bG)$, set $\bG^x \ceq \pi_0^{-1}(x)$.
-The restriction $\pi_0^*\gcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gcs{L}_x)_{\bG^x}$ so the isomorphism $\brho\vert_{\bG^x} : (\gcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gcs{L}_x \to (\EE)_x$.
+The restriction $\pi_0^*\gcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gcs{L}_x)_{\bG^x}$ so the isomorphism
+$\brho\vert_{\bG^x} : (\gcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gcs{L}_x \to (\EE)_x$.
 The collection $\{ \brho_x \tq x\in \pi_0(\bG) \}$ determines an isomorphism $\cs{L} \to (\EE)_{\pi_0(G)}$  in $\CS(\pi_0(G))$.
@@
   \begin{tikzcd}[row sep=20, column sep=15]
-    0 \arrow[dotted]{r} & \ker \TrFrob{\pi_0(G)} \arrow[dotted]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dotted]{r} & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
+    0 \arrow[dotted]{r} & \ker \TrFrob{\pi_0(G)} \arrow[dotted]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dotted]{r}
+    & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
     0 \rar & \CSiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
@@
 \begin{remark}\label{rem:rats}
-Although $\TrFrob{\pi_0(G)}$ is split and $\TrFrob{G^0}$ is an isomorphism, we do not know if $\TrFrob{G}$ is split, in general.
-Surjectively of $\TrFrob{G}$ shows that every $\ell$-adic character of $G(\Fq)$ admits a geometrization, but without a splitting for $\TrFrob{G}$ we do not know how to make this geometrization canonical.
+Although $\TrFrob{\pi_0(G)}$ is split and $\TrFrob{G^0}$ is an isomorphism, we do not know if $\TrFrob{G}$ is split,
+in general. Surjectively of $\TrFrob{G}$ shows that every $\ell$-adic character of $G(\Fq)$ admits a geometrization,
+but without a splitting for $\TrFrob{G}$ we do not know how to make this geometrization canonical.
 \end{remark}
@@
 Proposition~\ref{prop:bounded} shows that the full subcategory
-$\bCS(G) \subset \CS(G)$ is not an equivalence, for general smooth commutative group schemes $G$. Again we see the necessity of working with Weil sheaves in Definition~\ref{def:CS}.
+$\bCS(G) \subset \CS(G)$ is not an equivalence, for general smooth commutative group schemes $G$.
+Again we see the necessity of working with Weil sheaves in Definition~\ref{def:CS}.
 
@@
 \begin{proof} 
-Fix $\cs{L} = (\gcs{L},\mu,\phi)$ and consider the group homomorphism from $\Aut(\cs{L})$ to $\Hom(\bG_{\Weil{}},\EEx)$ defined in the proof of Proposition~\ref{prop:autornaught_etale}.
+Fix $\cs{L} = (\gcs{L},\mu,\phi)$ and consider the group homomorphism from $\Aut(\cs{L})$ to $\Hom(\bG_{\Weil{}},\EEx)$
+defined in the proof of Proposition~\ref{prop:autornaught_etale}.
 This homomorphism is injective because morphisms of sheaves are determined by the linear transformations induced on stalks.  
-Homomorphisms in the image of $\Aut(\cs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ are continuous when $\bG$ is viewed as the base of the espace \'etal\'e attached to $\gcs{L}$.
+Homomorphisms in the image of $\Aut(\cs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ are continuous when $\bG$ is
+viewed as the base of the espace \'etal\'e attached to $\gcs{L}$.
 Since $\ell$ is invertible in $\Fq$, it follows that the image of $\Aut(\cs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
 We also have $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
-To see that $\Aut(\cs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with $\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define $\bar\rho^y: \gcs{L}^y \to \gcs{L}^y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
-This defines an isomorphism $\bar\rho : \gcs{L}\to \gcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$, and thus an isomorphism $\rho :\cs{L}\to \cs{L}$ which maps to $\theta$ under $\Aut(\cs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
+To see that $\Aut(\cs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with
+$\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define
+$\bar\rho^y: \gcs{L}^y \to \gcs{L}^y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
+This defines an isomorphism $\bar\rho : \gcs{L}\to \gcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$,
+and thus an isomorphism $\rho :\cs{L}\to \cs{L}$ which maps to $\theta$ under $\Aut(\cs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
 \end{proof}
@@
 
-Having extended the function--sheaf dictionary from connected commutative algebraic groups over $\Fq$ to smooth commutative group schemes $G$ over $\Fq$, we look back briefly to the case when $G$ is a commutative algebraic group.
+Having extended the function--sheaf dictionary from connected commutative algebraic groups over $\Fq$ to smooth
+commutative group schemes $G$ over $\Fq$, we look back briefly to the case when $G$ is a commutative algebraic group. 
 Although Weil sheaves are not necessary in that case, the dictionary is still not perfect, generally.
@@
 Suppose $G$ is a commutative algebraic group over $\Fq$ appearing in the series of papers starting with \cite{lusztig:disconnected1}.
-Then $G$ is a commutative reductive algebraic group over $\Fq$ with cyclic component group scheme; such groups are extensions of finite cyclic groups by algebraic tori.
+Then $G$ is a commutative reductive algebraic group over $\Fq$ with cyclic component group scheme;
+such groups are extensions of finite cyclic groups by algebraic tori.
 Every Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:disconnected1}, is a character sheaf on $G$, in our sense,
 and vice versa.
-Moreover, since $\Hh^2(\pi_0(\bG),\EEx)=0$ by Remark~\ref{eg:H2}, it follows that each Frobenius-stable character sheaf on $G$ as in \cite{lusztig:disconnected1}, is determined by its trace of Frobenius, up to isomorphism.
+Moreover, since $\Hh^2(\pi_0(\bG),\EEx)=0$ by Remark~\ref{eg:H2}, it follows that each Frobenius-stable
+character sheaf on $G$ as in \cite{lusztig:disconnected1}, is determined by its trace of Frobenius, up to isomorphism. 
 \end{remark}
@@
 We continue to assume that $\ell$ is invertible in $\Fq$. 
-In this section we consider connected commutative algebraic groups over $K$ that admit a N\'eron model, by which we mean a locally finite type N\'eron model.
-By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected commutative algebraic groups over $K$ that contain no subgroup isomorphic to $\mathbb{G}_\text{a}$.
+In this section we consider connected commutative algebraic groups over $K$ that admit a N\'eron model,
+by which we mean a locally finite type N\'eron model.
+By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected
+commutative algebraic groups over $K$ that contain no subgroup isomorphic to $\mathbb{G}_\text{a}$.
 Write $\mathcal{N}_K$ for the full subcategory of the category of algebraic groups consisting of such objects.
 This category is additive, and includes all algebraic tori over $K$, abelian varieties over $K$ and unipotent $K$-wound groups.
-We write $\mathcal{N}$ for the category of Neron models that arise in this way; in particular, $\mathcal{N}$ is a full subcategory of the category of smooth commutative group schemes over $R$.
+We write $\mathcal{N}$ for the category of Neron models that arise in this way; in particular, $\mathcal{N}$
+is a full subcategory of the category of smooth commutative group schemes over $R$.
 
@@
 Note that $X(K) = X(R)$.
-A \emph{quasicharacter of $X(K)$} is a group homomorphism $X(K) \to \EEx$ that factors through $X(R) \to X(R_n)$ for some non-negative integer $n$.
+A \emph{quasicharacter of $X(K)$} is a group homomorphism $X(K) \to \EEx$ that factors through
+$X(R) \to X(R_n)$ for some non-negative integer $n$.
 We note that this definition is compatible with \cite{cassels-frohlich:AlgebraicNumberTheory}*{Ch XV, \S 2.3}.
@@
 For each $n \in \NN$, the Greenberg functor maps schemes over $R_n$ to schemes over $\Fq$.
-See \cite{bertrapelle-gonzales:Greenberg} for the definition and fundamental properties of the Greenberg functor as we use it; other useful references include
+See \cite{bertrapelle-gonzales:Greenberg} for the definition and fundamental properties of the
+Greenberg functor as we use it; other useful references include
 \cite{greenberg:61}, \cite{greenberg:63a},
@@
 for the functor produced by composing pullback along $\Spec{R_n} \to \Spec{R}$ with the Greenberg functor. 
-This functor respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and geometric components.  Moreover, there is a canonical isomorphism
+This functor respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and
+geometric components.  Moreover, there is a canonical isomorphism
 \[
@@
 between additive functors.
-Crucially, $\varrho^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes, for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
+Crucially, $\varrho^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes,
+for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
 This observation is key to the proof that, for any scheme $X$ over $R$, the projective limit 
@@
 \begin{remark}
-If $\varrho^R_n(X)^* : \CS(\Gr^R_n(X)) \to \CS(\Gr_R(X))$ is full then the construction above can be improved by forming $\QCS(X)$ from the essential images of the functors $\varrho^R_n(X)^*$; however, we do not know if $\varrho^R_n(X)^*$ is full.
+If $\varrho^R_n(X)^* : \CS(\Gr^R_n(X)) \to \CS(\Gr_R(X))$ is full then the construction above can be improved
+by forming $\QCS(X)$ from the essential images of the functors $\varrho^R_n(X)^*$; however, we do not know if $\varrho^R_n(X)^*$ is full.
 \end{remark}
@@
 Although $\Gr_R(X)$ is not locally of finite type and therefore not smooth,
-let us consider the rigid monoidal category $\CS(\Gr_R(X))$ as defined in Section~\ref{ssec:category} without insisting that the commutative group $\Fq$-scheme $G$ is smooth.
+let us consider the rigid monoidal category $\CS(\Gr_R(X))$ as defined in Section~\ref{ssec:category}
+without insisting that the commutative group $\Fq$-scheme $G$ is smooth.
 %Let $X$ be a smooth commutative group scheme over $R$, with $R$ as above.
@@
 \item
-morphisms $\varrho^R_n(X)^*\cs{L} \to \varrho^R_m(X)^*\cs{L}'$ in $\QCS(X)$ are those morphisms in $\CS(\Gr_R(X))$ which take the form $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\cs{L},\cs{L}')$ when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\cs{L},\varrho^R_{m\leq n}(X)^*\cs{L}')$ when $m\leq n$.
+morphisms $\varrho^R_n(X)^*\cs{L} \to \varrho^R_m(X)^*\cs{L}'$ in $\QCS(X)$ are those morphisms
+in $\CS(\Gr_R(X))$ which take the form $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\cs{L},\cs{L}')$
+when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\cs{L},\varrho^R_{m\leq n}(X)^*\cs{L}')$ when $m\leq n$.
 \end{enumerate}
@@
 let $R$ be the ring of integers of $K$.
-%Fix a separable closure ${\bar K}$ of $K$ and let $\tilde{K}$ be the maximal unramified extension of $K$ in ${\bar K}$; write $\tilde{R}$ for the ring of integers of $\tilde{K}$ and set $\tilde{S} = \Spec{\tilde{R}}$.
+%Fix a separable closure ${\bar K}$ of $K$ and let $\tilde{K}$ be the maximal unramified extension of $K$ in ${\bar K}$;
+%write $\tilde{R}$ for the ring of integers of $\tilde{K}$ and set $\tilde{S} = \Spec{\tilde{R}}$.
 \begin{enumerate}
@@
 \] 
-\labitem{(2)}{x2} for all quasicharacter sheaves $\cs{F}$, $\cs{F}'$ on $\Gr_R(X)$, and for every $\rho \in \Hom(\cs{F},\cs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
+\labitem{(2)}{x2} for all quasicharacter sheaves $\cs{F}$, $\cs{F}'$ on $\Gr_R(X)$, and for every
+$\rho \in \Hom(\cs{F},\cs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
 \labitem{(3)}{x3} for all quasicharacter sheaves $\cs{F}$ for $X$, there is a canonical isomorphism
@@
 %\begin{enumerate}
-To prove \ref{x0}, use: Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$; the fact that N\'eron models are unique up to isomorphism; the fact that every $\CS(\Gr^R_n(X))$ is a full subcategory of $\QCS(X)$; and the observation that every object in $\QCS(X)$ is in the essential image of $\CS(\Gr^R_n(X))$ for some $n$.
+To prove \ref{x0}, use: Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$; the fact that
+N\'eron models are unique up to isomorphism; the fact that every $\CS(\Gr^R_n(X))$ is a full subcategory
+of $\QCS(X)$; and the observation that every object in $\QCS(X)$ is in the essential image of $\CS(\Gr^R_n(X))$ for some $n$.
 To prove \ref{x1}, use Theorem~\ref{thm:snake} with $G = \Gr^R_n(X)$ and then argue as in part \ref{x0}.
 To prove \ref{x2}, argue as in the proof of Lemma~\ref{lem:autornaught}.
-To prove \ref{x3}, use: the fact that the component group of $\Gr^R_n(X)$ is independent of $n$; Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, in which case $\pi_0(G) = \pi_0(X \times_S S_0)$ and $\pi_0(\bG) = \pi_0(X)_{\bFq}$; then argue as in part \ref{x0}.
+To prove \ref{x3}, use: the fact that the component group of $\Gr^R_n(X)$ is independent of $n$;
+Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, in which case $\pi_0(G) = \pi_0(X \times_S S_0)$
+and $\pi_0(\bG) = \pi_0(X)_{\bFq}$; then argue as in part \ref{x0}.
 %\end{enumerate}
@@
  \begin{remark}
-In Section~\ref{ssec:CS_tori} we see that the \'etale site on $\Gr_R(X)$ is rich enough to geometrize all quasicharacters of $X(K)$ as $\ell$-adic local systems on $\Gr_R(X)$, where $X$ is a Neron model for an algebraic torus or an abelian variety over a local field $K$.
+In Section~\ref{ssec:CS_tori} we see that the \'etale site on $\Gr_R(X)$ is rich enough to geometrize all
+quasicharacters of $X(K)$ as $\ell$-adic local systems on $\Gr_R(X)$, where $X$ is a Neron model for an
+algebraic torus or an abelian variety over a local field $K$. 
 It is natural to ask if the \'etale site on the generic fibre $X_K$ would have sufficed. 
-This seems unlikely, since the geometric \'etale fundamental group of $\Gm{K}$ is ${\hat \ZZ}$, though limited results in this direction were established in \cite{Cunningham-Kamgarpour} when $K = \mathbb{Q}_p$.
+This seems unlikely, since the geometric \'etale fundamental group of $\Gm{K}$ is ${\hat \ZZ}$,
+though limited results in this direction were established in \cite{Cunningham-Kamgarpour} when $K = \mathbb{Q}_p$.
 \end{remark}
@@
 
-As we explained in the Introduction, our original motivation for this paper was to find a geometrization and categorification of quasicharacters of $p$-adic tori. 
-This is now provided by the following adaptation of Theorem~\ref{thm:CSXK} in the case when $T\in \mathcal{N}$ is a Neron model for an algebraic torus over $K$.
+As we explained in the Introduction, our original motivation for this paper was to find a
+geometrization and categorification of quasicharacters of $p$-adic tori. 
+This is now provided by the following adaptation of Theorem~\ref{thm:CSXK} in the case when
+$T\in \mathcal{N}$ is a Neron model for an algebraic torus over $K$.
 
@@
 \begin{proof} 
-The horizontal sequence of groups coming from categories of quasicharacter sheaves is exact by Proposition~\ref{prop:middleexact}, together with the observation that the functors $\pi_0^*$ and $\iota^*$ preserve limits.
+The horizontal sequence of groups coming from categories of quasicharacter sheaves is exact by
+Proposition~\ref{prop:middleexact}, together with the observation that the functors $\pi_0^*$ and $\iota^*$ preserve limits.
 It is elementary that the horizontal sequence of quasicharacters is exact.
@@
 Thus, the middle vertical sequence is exact.
-Since $T^0$ and $\pi_0(T)$ do not lie in $\mathcal{N}$, we cannot use Theorem~\ref{thm:CSXK} to determine the image and trace of Frobenius for these schemes. 
-Instead, we observe that $T^0$ and $\pi_0(T)$ are smooth commutative group schemes over $R$, so Definition~\ref{def:QCS} gives meaning to categories $\QCS(T^0)$ and $\QCS(\pi_0(T))$, and, moreover, that $\pi_0(\Gr^R_n(T^0))= \pi_0(T^0)_{\Fq} = 1$ and $\pi_0(\Gr^R_n(\pi_0(T)) = \pi_0(T)_{\Fq}$ are both independent of $n$.
-It follows that the vertical sequences through $\QCSiso{T^0}$ and $\QCSiso{\pi_0(T)}$ are exact by Theorem~\ref{thm:snake} and Definition~\ref{def:QCS}.
+Since $T^0$ and $\pi_0(T)$ do not lie in $\mathcal{N}$, we cannot use Theorem~\ref{thm:CSXK} to
+determine the image and trace of Frobenius for these schemes. 
+Instead, we observe that $T^0$ and $\pi_0(T)$ are smooth commutative group schemes over $R$,
+so Definition~\ref{def:QCS} gives meaning to categories $\QCS(T^0)$ and $\QCS(\pi_0(T))$, and,
+moreover, that $\pi_0(\Gr^R_n(T^0))= \pi_0(T^0)_{\Fq} = 1$ and $\pi_0(\Gr^R_n(\pi_0(T)) = \pi_0(T)_{\Fq}$ are both independent of $n$.
+It follows that the vertical sequences through $\QCSiso{T^0}$ and $\QCSiso{\pi_0(T)}$ are exact by
+Theorem~\ref{thm:snake} and Definition~\ref{def:QCS}.
 The diagram commutes by Lemma~\ref{lem:pullback}.
@@
 canonically.
-The case $X= \pi_0(T)$ is handled by the same argument, replacing Theorem~\ref{thm:CSXK} with Theorem~\ref{thm:snake} and Definition~\ref{def:QCS}, as in the proof of Corollary~\ref{cor:CS_tori}, after observing that $\pi_0(\pi_0(T)_{\bFq}) = \pi_0(T)_{\bFq}$.
+The case $X= \pi_0(T)$ is handled by the same argument, replacing Theorem~\ref{thm:CSXK} with
+Theorem~\ref{thm:snake} and Definition~\ref{def:QCS}, as in the proof of Corollary~\ref{cor:CS_tori},
+after observing that $\pi_0(\pi_0(T)_{\bFq}) = \pi_0(T)_{\bFq}$.
 \end{proof}
@@
  \end{equation}
-It is natural to ask if the vertical surjections can be defined directly, without making use of local class field theory, for which the results of \cite{suzuki-yoshida:12a}  and \cite{Suzuki:Neron} may be helpful.
+It is natural to ask if the vertical surjections can be defined directly, without making use of local class field theory,
+for which the results of \cite{suzuki-yoshida:12a}  and \cite{Suzuki:Neron} may be helpful.
 The case $T_K = \Gm{K}$ is already very interesting, in which case \eqref{eq:GLCT} becomes
@@
 %We have seen that the isomorphism $\QCS(\ZZ)\iso \Hom(\Weil{\Fq}, \EEx)$ is elementary.
-The isomorphism $\QCSiso{\Gm{R}}\iso \Hom(\mathcal{I}_K, \EEx)$ may be deduced directly from the class field theory of Serre and Hezewinkel as revisited beautifully in \cite{suzuki-yoshida:12a}; see also \cite{Suzuki:Neron}.
-The monoidal category of character sheaves on $\Gr^R_n(\Gm{R})$ is canonically equivalent to the category of $\ell$-adic characters of the quotient of the \'etale fundamental group $\pi_1(\Gr^R_n(\Gm{R}),\bFq)$ determined by the Lang isogeny for $\Gr^R_n(\Gm{R})$.
-Accordingly, quasicharacter sheaves on $\Gm{R}$ may be apprehended as $\ell$-adic characters of the inverse limit of these quotients, as $n$ ranges over $\NN$.
-By \cite{serre:isogenies}, there is a canonical isomorphism between this inverse limit and $\mathcal{I}_K^\text{ab}$; this isomorphism is {\it not} restricted to the case when $K$ and $\Fq$ have equal characteristic.
-This provides the isomorphism $\QCSiso{\Gm{R}}\iso \Hom(\mathcal{I}_K, \EEx)$ in \eqref{eq:Gm}.
-Since the sequences are split, this gives $\QCSiso{T}\iso \Hom(\Weil{K}, \EEx)$.
-We suspect that the general case of \eqref{eq:GLCT}, where $K$ is any local field and $T_K$ is any torus over $K$, may be deduced from \eqref{eq:Gm}.
+%The isomorphism $\QCSiso{\Gm{R}}\iso \Hom(\mathcal{I}_K, \EEx)$ may be deduced directly
+%from the class field theory of Serre and Hezewinkel as revisited beautifully in \cite{suzuki-yoshida:12a};
+%see also \cite{Suzuki:Neron}. The monoidal category of character sheaves on $\Gr^R_n(\Gm{R})$ is
+%canonically equivalent to the category of $\ell$-adic characters of the quotient of the \'etale fundamental
+%group $\pi_1(\Gr^R_n(\Gm{R}),\bFq)$ determined by the Lang isogeny for $\Gr^R_n(\Gm{R})$. Accordingly,
+%quasicharacter sheaves on $\Gm{R}$ may be apprehended as $\ell$-adic characters of the inverse limit
+%of these quotients, as $n$ ranges over $\NN$. By \cite{serre:isogenies}, there is a canonical isomorphism
+%between this inverse limit and $\mathcal{I}_K^\text{ab}$; this isomorphism is {\it not} restricted to the case
+%when $K$ and $\Fq$ have equal characteristic. This provides the isomorphism
+%$\QCSiso{\Gm{R}}\iso \Hom(\mathcal{I}_K, \EEx)$ in \eqref{eq:Gm}.
+%Since the sequences are split, this gives $\QCSiso{T}\iso \Hom(\Weil{K}, \EEx)$.
+We suspect that the general case of \eqref{eq:GLCT}, where $K$ is any local field and $T_K$ is any
+torus over $K$, may be deduced from \eqref{eq:Gm}.
 In Section~\ref{ssec:wrK} we develop a tool for further work in that direction.
@@
 \]
-as smooth group schemes over $\Fq$.  Accordingly, by Lemma~\ref{lem:pullback}, the isomorphism above determines an equivalence of categories
+as smooth group schemes over $\Fq$.  Accordingly, by Lemma~\ref{lem:pullback},
+the isomorphism above determines an equivalence of categories
 \begin{equation}\label{eq:categorical_transfer}
@@
 The isomorphism \eqref{eq:transfer} is an instance of {\it transfer} of (certain) quasicharacters between $X(K)$ and $Y(L)$. 
-We now recognize this transfer of quasicharacters as a consequence of the equivalence of categories of quasicharacter sheaves \eqref{eq:categorical_transfer}.
-
-The isomorphism \eqref{eq:schematic_transfer} can indeed exist between quasicharacters of algebraic tori over local fields, even when the characteristics of $K$ and $L$ differ.
+We now recognize this transfer of quasicharacters as a consequence of the
+equivalence of categories of quasicharacter sheaves \eqref{eq:categorical_transfer}.
+
+The isomorphism \eqref{eq:schematic_transfer} can indeed exist between quasicharacters of
+algebraic tori over local fields, even when the characteristics of $K$ and $L$ differ.
 Suppose $T_K$ and $M_L$ are tori over local fields $K$ and $L$,
@@
 They define a quantity $h$ (the smallest integer so that $\varpi^h$ lies in the
-Jacobian ideal associated to a natural embedding of $T_K$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}) and show  that if $n > 3h$ and $T_K$ and $M_L$ are $n$-congruent then there is a canonical isomorphism of smooth group schemes
+Jacobian ideal associated to a natural embedding of $T_K$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}) and show
+that if $n > 3h$ and $T_K$ and $M_L$ are $n$-congruent then there is a canonical isomorphism of smooth group schemes
  $

### 2015-07-21 dictionary.tex
Reading Section 4.

--- 2015-07-21 dictionary.tex
@@
 
-\begin{example}\ref{eg:H2}
-Consider the simplest non-trivial case, where $\bG = \{1, i, j, k\} \cong \ZZ/2\ZZ \times \ZZ/2\ZZ.$  Using eqref{eq:H2comp},
+\begin{example}\label{eg:H2}
+Consider the simplest non-trivial case, where $\bG = \{1, i, j, k\} \cong \ZZ/2\ZZ \times \ZZ/2\ZZ.$  Using \eqref{eq:H2comp},
 we have $\Hh^2(\bG, \EEx) \cong \ZZ/2\ZZ$, on which $\Weil{}$ must act trivially, regardless of its action on $\bG$ itself.
@@
 Write $\m$ for the maximal ideal of $R$ and set $R_n = R/\m^{n+1}$ for every non-negative integer $n$.
-Suppose $X_K \in \mathcal{N}_K$ has N\'eron model $X$ over $R$.
+Suppose $X \in \mathcal{N}$.
 Note that $X(K) = X(R)$.
@@
 see \cite{EGAIV3}*{\S 8.2}.
-This leads to the definition of what we shall call the {\it Greenberg transform}:
+This leads to the definition of the {\it Greenberg transform}:
 \[
@@
 %We now define a category which will geometrize quasicharacters of $X(K)$.
-For every non-negative integer $n$, the Greenberg transform $\Gr^R_n(X)$ is a {\it smooth} commutative group scheme over $S_0$
+For every non-negative integer $n$, the Greenberg transform $\Gr^R_n(X)$ is a {\it smooth} commutative group scheme over $S_0$.
 %with component group scheme $\pi_0(X)_{\Fq} \ceq \pi_0(X) \times_S S_0$ and $\Fq$-rational points $X(R_n).$
@@
 Although $\Gr_R(X)$ is not locally of finite type and therefore not smooth,
-let us consider the rigid monoidal category $\CS(\Gr_R(X))$ as defined in Section~\ref{ssec:category} without insisting that the commutative group $\Fq$-scheme $G$ is smooth.
+let us consider the rigid monoidal category $\CS(\Gr_R(X))$ as defined in Section~\ref{ssec:category}, though without insisting that the commutative group $\Fq$-scheme $G$ is smooth.
 %Let $X$ be a smooth commutative group scheme over $R$, with $R$ as above.
@@
 It is natural to ask if the \'etale site on the generic fibre $X_K$ would have sufficed. 
-This seems unlikely, since the geometric \'etale fundamental group of $\Gm{K}$ is ${\hat \ZZ}$, though limited results in this direction were established in \cite{Cunningham-Kamgarpour} when $K = \mathbb{Q}_p$.
+This seems unlikely, since the geometric \'etale fundamental group of $\Gm{K}$ is ${\hat \ZZ}$; however, limited results in this direction were established in \cite{Cunningham-Kamgarpour} when $K = \mathbb{Q}_p$.
 \end{remark}
@@
 \]
-where we refer to continuous cohomology, since $\Hom(T(K), \EEx)$ refers to continuous homomorphisms $T(K)\to \EEx$.
-It now follows from the inflation-restriction exact sequence that the following diagram commutes.
+where we refer to continuous cohomology, since $\Hom(T(K), \EEx)$ refers to continuous group homomorphisms $T(K)\to \EEx$.
+It now follows from the inflation-restriction exact sequence that the following diagram commutes:
 \[
@@
  & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{\Fq}} \arrow{r}  
- & 0
+ & 0.
 \end{tikzcd}
@@
 Let $R$ and $R'$ be the rings of integers of $K$ and $K'$, respectively.
-Let $X_K \in \mathcal{N}$ have N\'eron model $X$, set $X_{K'} \ceq X_K \times_\Spec{K} \Spec{K'}$
+Suppose $X \in \mathcal{N}$ and set $X_{K'} \ceq X_K \times_\Spec{K} \Spec{K'}$
 and let $X'$ be a N\'eron model for $X_{K'}$.

### 2015-07-21 dictionary.tex

--- 2015-07-21 dictionary.tex
@@
 and $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ do not arise in that context because, for such groups,
-Weil sheaves are unnecessary (\S \ref{ssec:alg_groups} and $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}=0$ (Remark \ref{rem:H2}).
+Weil sheaves are unnecessary (\S \ref{ssec:alg_groups}) and $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}=0$ (Remark \ref{rem:H2}).
 
@@
 
-\begin{remark}
+\begin{remark} \label{rem:H2}
 Recall the K\"unneth formula in group cohomology \cite{brown:CohomologyOfGroups}*{Prop. I.0.8}:
@@
 Although $\Gr_R(X)$ is not locally of finite type and therefore not smooth,
-let us consider the rigid monoidal category $\CS(\Gr_R(X))$ as defined in Section~\ref{ssec:category}
-without insisting that the commutative group $\Fq$-scheme $G$ is smooth.
+let us consider the rigid monoidal category $\CS(\Gr_R(X))$ as defined in Section~\ref{ssec:category},
+though without insisting that the commutative group $\Fq$-scheme $G$ is smooth.
 %Let $X$ be a smooth commutative group scheme over $R$, with $R$ as above.
@@
 It is natural to ask if the \'etale site on the generic fibre $X_K$ would have sufficed.
-This seems unlikely, since the geometric \'etale fundamental group of $\Gm{K}$ is ${\hat \ZZ}$,
-though limited results in this direction were established in \cite{Cunningham-Kamgarpour} when $K = \mathbb{Q}_p$.
+This seems unlikely, since the geometric \'etale fundamental group of $\Gm{K}$ is ${\hat \ZZ}$;
+however, limited results in this direction were established in \cite{Cunningham-Kamgarpour} when $K = \mathbb{Q}_p$.
 \end{remark}

### 2015-07-22 dictionary.tex
Removed section Examples, at the end.
Adding Neron model section

@@
 
-Let $K$ be a local field with finite residue field $\Fq$; in this section we denote the group $\Weil{}$ by $\Weil{\Fq}$.
+Let $K$ be a local field with ring of integers $R$ and finite residue field $\Fq$; in this section we denote the group $\Weil{}$ by $\Weil{\Fq}$.
 We continue to assume that $\ell$ is invertible in $\Fq$.
-In this section we consider connected commutative algebraic groups over $K$ that admit a N\'eron model,
+
+\subsection{N\'eron models}\label{ssec:neron}
+We will consider connected commutative algebraic groups over $K$ that admit a N\'eron model,
 by which we mean a locally finite type N\'eron model.
@@
 
+\begin{example}
+If $T_K = \Gm{K}$, then a N\'eron model can be obtained by gluing copies of $\Gm{R}$ (one for each $n \in \ZZ$) along their generic fibers,
+via the gluing morphisms $\Spec{\ZZ[t, t^{-1}]} \to \Spec{\ZZ[t, t^{-1}]}$ defined by $t \mapsto \pi^n t$
+\cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.1, Ex. 5}.
+
+Suppose that $K'/K$ is a quadratic extension and $T_K = U_1(K'/K)$ is the unitary group.
+When $K'/K$ is unramified, the N\'eron model of $T_K$ is a form of the N\'eron model for $\Gm{K}$, with the nontrivial automorphism
+$\sigma \in \Gal(K'/K)$ mapping $(x, n)$ to $(\sigma(x), -n)$ for $x \in R'^\times$ and $n \in \ZZ$ specifying the copy of $\Gm{R'}$.
+This example illustrates the compatibility between N\'eron models and unramified base change
+\cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.1, Prop. 3}.
+
+On the other hand, if $K' = K(\sqrt{\pi})$ is totally ramified over $K$ then the N'eron model of $U_1(K'/K)$ is affine, namely
+$\Spec{R[x,y] / (x^2 - \pi y^2 - 1)}$.  The special fiber is the the disjoint union of two affine lines.
+
+Finally, we remark that if $K'/K$ is any finite extension of local fields and $X'$ is a N\'eron model for $X_{K'}$ then
+$\Res_{R'/R}(X')$ is a N\'eron model for $\Res_{K'/K}(X_{K'}$ \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop. 6}.
+\end{example}
+
 \subsection{Quasicharacters}\label{ssec:quasicharacters}
 
-Let $R$ be the ring of integers of $K$.
 Write $\m$ for the maximal ideal of $R$ and set $R_n = R/\m^{n+1}$ for every non-negative integer $n$.
@@
 
+\begin{example}
+We give 
+\end{example}
+
 \begin{corollary}
@@
 \begin{proof}
-Adapting the argument in \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop 6} to include locally finite type N\'eron models,
-one may show that $\Res_{R'/R}(X')$ is a N\'eron model for $\Res_{K'/K}(X_{K'})$.
-Thus, by the N\'eron mapping property, the canonical closed immersion
+By the N\'eron mapping property, the canonical closed immersion
 \[

### 2015-07-22 dictionary.tex
Minor change in the Notations section.

--- 2015-07-21 dictionary.tex
@@
 
-It follows from the smoothness of $G$ that the structure morphism $G \to \Spec{\Fq}$ is locally of finite type.
-If the structure morphism $G \to \Spec{\Fq}$ is \'etale, then $G$ is an \'etale group scheme; this does not imply that $\pi_0(G)$ is finite.
-If the structure morphism $G \to \Spec{\Fq}$ is of finite type, then $G$ is an algebraic group; in this case, $\pi_0(G)$ is finite. 
-Indeed, a smooth commutative group scheme $G$ is an algebraic group if and only if the \'etale group scheme $\pi_0(G)$ is finite.
+It follows from the smoothness of $G$ that the structure morphism $G \to \Spec{\Fq}$ is locally of finite type, being smooth.
+If the structure morphism $G \to \Spec{\Fq}$ is also \'etale, then $G$ is an \'etale group scheme; this does not imply that $\pi_0(G)$ is finite.
+An algebraic group over $\Fq$ is a smooth group scheme of finite type, in which case its component group scheme is finite.
 

### 2015-07-22 dictionary.tex
Neron |--> N\'eron

@@
 \keywords{function-sheaf dictionary, trace of Frobenius, geometrization, categorification, character sheaves,smooth commutative group schemes,
-finite fields, local fields, algebraic tori, Neron models, Greenberg functor, quasicharacters, quasicharacter sheaves.}
+finite fields, local fields, algebraic tori, N\'eron models, Greenberg functor, quasicharacters, quasicharacter sheaves.}
 
@@
 
-Having defined quasicharacter sheaves on Neron models of commutative algebraic groups over $K$
+Having defined quasicharacter sheaves on N\'eron models of commutative algebraic groups over $K$
 and character sheaves on commutative group schemes over $\Fq$, we consider how
@@
 This category is additive, and includes all algebraic tori over $K$, abelian varieties over $K$ and unipotent $K$-wound groups.
-We write $\mathcal{N}$ for the category of Neron models that arise in this way; in particular, $\mathcal{N}$
+We write $\mathcal{N}$ for the category of N\'eron models that arise in this way; in particular, $\mathcal{N}$
 is a full subcategory of the category of smooth commutative group schemes over $R$.
@@
 
-On the other hand, if $K' = K(\sqrt{\pi})$ is totally ramified over $K$ then the N'eron model of $U_1(K'/K)$ is affine, namely
+On the other hand, if $K' = K(\sqrt{\pi})$ is totally ramified over $K$ then the N\'eron model of $U_1(K'/K)$ is affine, namely
 $\Spec{R[x,y] / (x^2 - \pi y^2 - 1)}$.  The special fiber is the the disjoint union of two affine lines.
@@
 Finally, we remark that if $K'/K$ is any finite extension of local fields and $X'$ is a N\'eron model for $X_{K'}$ then
-$\Res_{R'/R}(X')$ is a N\'eron model for $\Res_{K'/K}(X_{K'}$ \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop. 6}.
+$\Res_{R'/R}(X')$ is a N\'eron model for $\Res_{K'/K}(X_{K'})$ \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop. 6}.
 \end{example}
@@
 In Section~\ref{ssec:CS_tori} we see that the \'etale site on $\Gr_R(X)$ is rich enough to geometrize all
-quasicharacters of $X(K)$ as $\ell$-adic local systems on $\Gr_R(X)$, where $X$ is a Neron model for an
+quasicharacters of $X(K)$ as $\ell$-adic local systems on $\Gr_R(X)$, where $X$ is a N\'eron model for an
 algebraic torus or an abelian variety over a local field $K$. 
@@
 This is now provided by the following adaptation of Theorem~\ref{thm:CSXK} in the case when
-$T\in \mathcal{N}$ is a Neron model for an algebraic torus over $K$.
+$T\in \mathcal{N}$ is a N\'eron model for an algebraic torus over $K$.
 
 \begin{corollary}\label{cor:CS_tori}
-Let $T$ be a Neron model for an algebraic torus over $K$.
+Let $T$ be a N\'eron model for an algebraic torus over $K$.
 The following is a commutative diagram of exact sequences.
@@
 \begin{corollary}
-Let $T$ be a Neron model for an algebraic torus over $K$.
+Let $T$ be a N\'eron model for an algebraic torus over $K$.
 For $\cs{E}\in \QCS(\pi_0(T))$, $\cs{F}\in {\QCS(T)}$ and $\cs{F}^0\in {\QCS(T^0)}$, there are canonical isomorphisms

### 2015-07-22 dictionary.tex
Changed section titles.

@@
 
-\section{Character Sheaves on commutative group schemes} \label{sec:category}
+\section{Definitions and recollections} \label{sec:category}
 
@@
 
-\section{The function-sheaf dictionary for smooth commutative group schemes}\label{sec:main}
+\section{Character sheaves for smooth commutative group schemes}\label{sec:main}
 
@@
 
-\section{Applications to quasicharacters of $p$-adic tori and Abelian varieties}\label{sec:applications}
+\section{Quasicharacter sheaves for $p$-adic tori}\label{sec:applications}
 

### 2015-07-22 dictionary.tex
Fixed the section titles.

@@
 
-\section{Character sheaves on \'etale commutative group schemes} \label{sec:etale}
+\section{Character sheaves on \'etale commutative group schemes over finite fields} \label{sec:etale}
 
@@
 
-\section{Character sheaves for smooth commutative group schemes}\label{sec:main}
+\section{Character sheaves on smooth commutative group schemes over finite fields}\label{sec:main}
 

### 2015-07-22 dictionary.tex
Hid some proofs using \iffalse \fi

@@
 
-If the smooth commutative group scheme $G$ is of finite type, every character sheaf descends to $G$;
+If the smooth commutative group scheme $G$ is of finite type, then every character sheaf descends to $G$;
 we will see that they are not equivalent, in general, however.
-For now, we treat the connected case.
 
@@
 
+\iffalse
 \begin{proof}
@@
 \begin{proof}
-In Lemma~\ref{lem:bounded_connected}, we saw that every character sheaf $\cs{L}$ on $\bG$ descends to $G$;
+By Lemma~\ref{lem:bounded_connected}, we know that every character sheaf $\cs{L}$ on $\bG$ descends to $G$;
 let $\cs{E}$ be an object of $\bCS(G)$ for which $B_G(\cs{E}) \iso \cs{L}$.
@@
 From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields,
-as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3}, gives us all we need, as we briefly recall.
+as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3}, gives us all we need for points \ref{c1} and \ref{c2}.
+% as we briefly recall.
 %\todo{Fix citelist} %\citelist{\cite{deligne:SGA4.5}*{Sommes trig.},\cite{laumon:87a}*{1.1.3}}
-
+\iffalse
 As in the proof of Proposition~\ref{prop:finite}, use \'etale descent to see that pullback by the Lang isogeny $\Lang : G\to G$
@@
 representation of $G(\Fq)$, proving parts \ref{c1} and \ref{c2}.
-
-To finish the proof of part \ref{c3}, suppose $\Lang^*\cs{E} = V$ with isomorphism $V \to V\otimes V$.
+\fi
+For part \ref{c3}, suppose $\Lang^*\cs{E} = V$ with isomorphism $V \to V\otimes V$.
 Observe that the equivalence above establishes a bijection between $\Aut(\cs{E})$ and the group of automorphisms of $\rho : V\to V$ for which 

### 2015-07-22 dictionary.tex
Fixed references, overfull hboxes, texorpdfstring

--- 2015-07-22 dictionary.tex
@@
 \keywords{function-sheaf dictionary, trace of Frobenius, geometrization, categorification, character sheaves,smooth commutative group schemes,
-finite fields, local fields, algebraic tori, N\'eron models, Greenberg functor, quasicharacters, quasicharacter sheaves.}
+finite fields, local fields, algebraic tori, Neron models, Greenberg functor, quasicharacters, quasicharacter sheaves.}
 
@@
 
-Having defined quasicharacter sheaves on N\'eron models of commutative algebraic groups over $K$
+Having defined quasicharacter sheaves on Neron models of commutative algebraic groups over $K$
 and character sheaves on commutative group schemes over $\Fq$, we consider how
@@
 
-We anticipate that future work on quasicharacter sheaves will make use of   \cite{suzuki-yoshida:12a} and \cite{Suzuki:Neron},
+We anticipate that future work on quasicharacter sheaves will make use of   \cite{suzuki-yoshida:12a} and \cite{suzuki:14a},
 and will clarify the relation between this project and other attempts to geometrize admissible distributions on $p$-adic groups,
-such as \cite{Cunningham-Kamgarpour} (limited to quasicharacters of $\ZZ_p^\times$) and \cite{Aubert-Cunningham}
+such as \cite{cunningham-kamgarpour:13a} (limited to quasicharacters of $\ZZ_p^\times$) and \cite{aubert-cunningham:02a}
 (limited to characters of depth-zero representations). 
@@
 
-\section{Definitions and recollections} \label{sec:category}
+\section{Character Sheaves on commutative group schemes} \label{sec:category}
 
@@
 A descent argument similar to the one employed in the proof of Lemma~\ref{prop:finite} is used in
-\cite{Drinfeld:math/0609769}*{Lemma~1.10}, though in the more restrictive case of connected algebraic groups.
+\cite{boyarchenko-drinfeld:06a}*{Lemma~1.10}, though in the more restrictive case of connected algebraic groups.
 \end{remark}
@@
 \begin{remark} \label{rem:H2}
-Recall the K\"unneth formula in group cohomology \cite{brown:CohomologyOfGroups}*{Prop. I.0.8}:
+Recall the K\"unneth formula in group cohomology \cite{brown:CohomologyGrps}*{Prop. I.0.8}:
 if $A$ and $A'$ are groups and $M$ and $M'$ are abelian groups with $M$ $\ZZ$-free, then
@@
 
-\section{Character sheaves for smooth commutative group schemes}\label{sec:main}
+\section{The function-sheaf dictionary for smooth commutative group schemes}\label{sec:main}
 
@@
 Exactness at $\CSiso{G^0}$ follows from Proposition~\ref{prop:restriction},
-and at $\CSiso{\pi_0(G)}$ from Lemma~\ref{lem:extension}.
+and exactness at $\CSiso{\pi_0(G)}$ from Lemma~\ref{lem:extension}.
 Here we show that it is also exact at $\CSiso{G}$.
@@
 
-We now extend Proposition~\ref{prop:bounded-etale} to smooth commutative group schemes over $\Fq$.
+We now extend Proposition~\ref{prop:bounded-etale} to all smooth commutative group schemes over $\Fq$.
 
@@
 
-\section{Quasicharacter sheaves for $p$-adic tori}\label{sec:applications}
+\section{Applications to quasicharacters of \texorpdfstring{$p$}{p}-adic tori and Abelian varieties}\label{sec:applications}
 
@@
 This category is additive, and includes all algebraic tori over $K$, abelian varieties over $K$ and unipotent $K$-wound groups.
-We write $\mathcal{N}$ for the category of N\'eron models that arise in this way; in particular, $\mathcal{N}$
+We write $\mathcal{N}$ for the category of Neron models that arise in this way; in particular, $\mathcal{N}$
 is a full subcategory of the category of smooth commutative group schemes over $R$.
@@
 
-On the other hand, if $K' = K(\sqrt{\pi})$ is totally ramified over $K$ then the N\'eron model of $U_1(K'/K)$ is affine, namely
+On the other hand, if $K' = K(\sqrt{\pi})$ is totally ramified over $K$ then the N'eron model of $U_1(K'/K)$ is affine, namely
 $\Spec{R[x,y] / (x^2 - \pi y^2 - 1)}$.  The special fiber is the the disjoint union of two affine lines.
@@
 Finally, we remark that if $K'/K$ is any finite extension of local fields and $X'$ is a N\'eron model for $X_{K'}$ then
-$\Res_{R'/R}(X')$ is a N\'eron model for $\Res_{K'/K}(X_{K'})$ \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop. 6}.
+$\Res_{R'/R}(X')$ is a N\'eron model for $\Res_{K'/K}(X_{K'}$ \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop. 6}.
 \end{example}
@@
 In Section~\ref{ssec:CS_tori} we see that the \'etale site on $\Gr_R(X)$ is rich enough to geometrize all
-quasicharacters of $X(K)$ as $\ell$-adic local systems on $\Gr_R(X)$, where $X$ is a N\'eron model for an
+quasicharacters of $X(K)$ as $\ell$-adic local systems on $\Gr_R(X)$, where $X$ is a Neron model for an
 algebraic torus or an abelian variety over a local field $K$. 
@@
 This seems unlikely, since the geometric \'etale fundamental group of $\Gm{K}$ is ${\hat \ZZ}$;
-however, limited results in this direction were established in \cite{Cunningham-Kamgarpour} when $K = \mathbb{Q}_p$.
+however, limited results in this direction were established in \cite{cunningham-kamgarpour:13a} when $K = \mathbb{Q}_p$.
 \end{remark}
 
-\subsection{Quasicharacter sheaves for $p$-adic tori} \label{ssec:CS_tori}
+\subsection{Quasicharacter sheaves for \texorpdfstring{$p$}{p}-adic tori} \label{ssec:CS_tori}
 
@@
 This is now provided by the following adaptation of Theorem~\ref{thm:CSXK} in the case when
-$T\in \mathcal{N}$ is a N\'eron model for an algebraic torus over $K$.
+$T\in \mathcal{N}$ is a Neron model for an algebraic torus over $K$.
 
 \begin{corollary}\label{cor:CS_tori}
-Let $T$ be a N\'eron model for an algebraic torus over $K$.
+Let $T$ be a Neron model for an algebraic torus over $K$.
 The following is a commutative diagram of exact sequences.
@@
 \begin{example}
-We give 
+When $T_K = \Gm{K}$ or $T_K = U_1(K'/K)$, the geometric component group $\pi_0(T)_{\bar{k}}$ is cyclic,
+so $\TrFrob{\Gr_R(T)}$ is an isomorphism.  Conversely, when $T_K = \Gm{K}^2$ then
+\[
+\Hh^0(\Weil{\Fq}, \Hh^2(\pi_0(T), \EEx)) = \EEx,
+\]
+and there are uncountably many invisible quasicharacter sheaves for $T$.
+
+We may also give examples of tori whose N\'eron models have component groups appearing in Example \ref{eg:H2}.
+Let $L = K'(\sqrt{\pi})$ be a quadratic ramified extension of $K'$.  When $K = K'$ and $T_K = U_1(L/K) \times U_1(L/K)$,
+the component group $\pi_0(T)_{\bar{k}}$ is $\ZZ/2\ZZ \times \ZZ/2\ZZ$ with trivial Frobenius action.  When $K'/K$ is an unramified
+quadratic extension and $T_K = \Res_{K'/K} U_1(L/K')$, then $\pi_0(T)_{\bar{k}}$ is $\ZZ/2\ZZ \times \ZZ/2\ZZ$ with Frobenius
+exchanging the direct factors.  Finally, let $K'/K$ be a cubic unramified extension and $S_K = \Res_{K'/K} U_1(L/K')$.  If
+$T_K$ is the subtorus with character lattice $X^*(S_K) / \langle (1,1,1) \rangle$, then $\pi_0(T)_{\bar{k}}$ is $\ZZ/2\ZZ \times \ZZ/2\ZZ$
+with Frobenius of order $3$.  Each of these tori will have one invisible quasicharacter sheaf.
 \end{example}
 
+We may also extract information about the automorphism groups of quasicharacter sheaves from Theorem \ref{thm:CSXK}.
+
 \begin{corollary}
-Let $T$ be a N\'eron model for an algebraic torus over $K$.
+Let $T$ be a Neron model for an algebraic torus over $K$.
 For $\cs{E}\in \QCS(\pi_0(T))$, $\cs{F}\in {\QCS(T)}$ and $\cs{F}^0\in {\QCS(T^0)}$, there are canonical isomorphisms
@@
 It is natural to ask if the vertical surjections can be defined directly, without making use of local class field theory,
-for which the results of \cite{suzuki-yoshida:12a}  and \cite{Suzuki:Neron} may be helpful.
+for which the results of \cite{suzuki-yoshida:12a}  and \cite{suzuki:14a} may be helpful.
 The case $T_K = \Gm{K}$ is already very interesting, in which case \eqref{eq:GLCT} becomes
@@
 %from the class field theory of Serre and Hezewinkel as revisited beautifully in \cite{suzuki-yoshida:12a};
-%see also \cite{Suzuki:Neron}. The monoidal category of character sheaves on $\Gr^R_n(\Gm{R})$ is
+%see also \cite{suzuki:14a}. The monoidal category of character sheaves on $\Gr^R_n(\Gm{R})$ is
 %canonically equivalent to the category of $\ell$-adic characters of the quotient of the \'etale fundamental

### 2015-07-22 dictionary.tex

--- 2015-07-22 dictionary.tex
@@
 
-\section{Quasicharacter sheaves for $p$-adic tori}\label{sec:applications}
+\section{Quasicharacter sheaves for \texorpdfstring{$p$}{p}-adic tori}\label{sec:applications}
 
@@
 \begin{example}
-We give 
+When $T_K = \Gm{K}$ or $T_K = U_1(K'/K)$, the geometric component group $\pi_0(T)_{\bar{k}}$ is cyclic,
+so $\TrFrob{\Gr_R(T)}$ is an isomorphism.  Conversely, when $T_K = \Gm{K}^2$ then
+\[
+\Hh^0(\Weil{\Fq}, \Hh^2(\pi_0(T), \EEx)) = \EEx,
+\]
+and there are uncountably many invisible quasicharacter sheaves for $T$.
+
+We may also give examples of tori whose N\'eron models have component groups appearing in Example \ref{eg:H2}.
+Let $L = K'(\sqrt{\pi})$ be a quadratic ramified extension of $K'$.  When $K = K'$ and $T_K = U_1(L/K) \times U_1(L/K)$,
+the component group $\pi_0(T)_{\bar{k}}$ is $\ZZ/2\ZZ \times \ZZ/2\ZZ$ with trivial Frobenius action.  When $K'/K$ is an unramified
+quadratic extension and $T_K = \Res_{K'/K} U_1(L/K')$, then $\pi_0(T)_{\bar{k}}$ is $\ZZ/2\ZZ \times \ZZ/2\ZZ$ with Frobenius
+exchanging the direct factors.  Finally, let $K'/K$ be a cubic unramified extension and $S_K = \Res_{K'/K} U_1(L/K')$.  If
+$T_K$ is the subtorus with character lattice $X^*(S_K) / \langle (1,1,1) \rangle$, then $\pi_0(T)_{\bar{k}}$ is $\ZZ/2\ZZ \times \ZZ/2\ZZ$
+with Frobenius of order $3$.  Each of these tori will have one invisible quasicharacter sheaf.
 \end{example}
+
+We may also extract information about the automorphism groups of quasicharacter sheaves from Theorem \ref{thm:CSXK}.
 

### 2015-07-22 dictionary.tex
A few biblio changes, adding invisibility

@@
 
-\keywords{function-sheaf dictionary, trace of Frobenius, geometrization, categorification, character sheaves,smooth commutative group schemes,
-finite fields, local fields, algebraic tori, N\'eron models, Greenberg functor, quasicharacters, quasicharacter sheaves.}
+\keywords{character sheaves, p-adic tori, N\'eron models, Greenberg functor, geometrization, quasicharacter sheaves}
 
@@
 
-\usepackage{amssymb,amsrefs}
+\usepackage{amssymb}
+\usepackage[initials]{amsrefs}
 
@@
     +{,} { }							{status}
+    +{}  { \parenthesize}				{language}
+    +{}  { \PrintTranslation}				{translation}
+    +{;} { \PrintReprint}				{reprint}
+    +{.} { }							{note}
+    +{.} {}							{transition}
+    +{}  {\SentenceSpace \PrintReviews}	{review}
+}
+
+% The publisher wasn't appearing.
+\BibSpec{collection.article}{%
+    +{}  {\PrintAuthors}				{author}
+    +{,} { \textit}						{title}
+    +{.} { }							{part}
+    +{:} { \textit}						{subtitle}
+    +{,} { \PrintContributions}			{contribution}
+    +{,} { \PrintConference}				{conference}
+    +{}  {\PrintBook}					{book}
+    +{,} { }							{booktitle}
+    +{}  { \PrintEditorsB}				{editor}
+    +{,} { }							{series}
+    +{} { \textbf}						{volume}
+    +{,} { }							{publisher}
+    +{,} { }							{address}
+    +{,} { \PrintDateB}					{date}
+    +{,} { }							{pages}
+    +{,} { }							{status}
+    +{,} { \PrintDOI}					{doi}
+    +{,} { available at \eprint}			{eprint}
     +{}  { \parenthesize}				{language}
@@
 A descent argument similar to the one employed in the proof of Lemma~\ref{prop:finite} is used in
-\cite{boyarchenko-drinfeld:06a}*{Lemma~1.10}, though in the more restrictive case of connected algebraic groups.
+\cite{boyarchenko-drinfeld:10a}*{Lemma~1.10}, though in the more restrictive case of connected algebraic groups.
 \end{remark}
@@
 
+\begin{definition}
+We call a character sheaf $\cs{L}$ on $G$ \emph{invisible} if it is nontrivial and $\TrFrob{G}(\cs{L}) = 1$.
+\end{definition}
+
+The proposition gives a method for determining whether a given $G$ admits invisible character sheaves.
+
 \begin{remark} \label{rem:H2}

### 2015-07-22 dictionary.tex
bertrapelle -> bertapelle

@@
 For each $n \in \NN$, the Greenberg functor maps schemes over $R_n$ to schemes over $\Fq$.
-See \cite{bertrapelle-gonzales:Greenberg} for the definition and fundamental properties of the
+See \cite{bertapelle-gonzales:Greenberg} for the definition and fundamental properties of the
 Greenberg functor as we use it; other useful references include
@@
 Crucially, $\varrho^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes,
-for every $R$-scheme $X$ and every $n\leq m$ \cite{bertrapelle-gonzales:Greenberg}*{Prop 4.3}.
+for every $R$-scheme $X$ and every $n\leq m$ \cite{bertapelle-gonzales:Greenberg}*{Prop 4.3}.
 This observation is key to the proof that, for any scheme $X$ over $R$, the projective limit 
@@
 Applying the functor $\Gr^R_{n}$ to \eqref{me}
-and using \cite{bertrapelle-gonzales:Greenberg}*{Thm 1.1} defines the morphism of smooth group schemes
+and using \cite{bertapelle-gonzales:Greenberg}*{Thm 1.1} defines the morphism of smooth group schemes
 \begin{equation}\label{men}

### 2015-07-22 dictionary.tex
Subsections in intro

@@
-%%------------------------------------------------------%%
-%% This file should be the main file of your article.   %%
-
 \documentclass[10pt]{amsart}
-\usepackage[a4paper]{geometry} % see geometry.pdf n how to lay out the page. There's lots.
-%\geometry{a4paper} % or letter or a5paper or ... etc
-% \geometry{landscape} % rotated page geometry
-
-% See the ``Article customise'' template for come common customisations
-
+\usepackage[a4paper]{geometry}
 \title{From the function-sheaf dictionary to quasicharacters of $p$-adic tori}
@@
 %%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%
-%\usepackage{todonotes}
-% crellerefs is a custom version of amsrefs complying with the Crelle style guidelines
-%\usepackage{crellerefs}
 
@@
 
+%Customizations for amsrefs
 \BibSpec{lecture}{%
@@
 
-% Eliminate a font warning
-%\SetSymbolFont{stmry}{bold}{U}{stmry}{m}{n}
-
 % MSC footnote
@@
 
-\medskip
-\noindent\textbf{Application to quasicharacters of $p$-adic tori and abelian varieties.\ }
+\subsection*{Application to quasicharacters of \texorpdfstring{$p$}{p}-adic tori and abelian varieties}
 As indicated above, our interest in the function-sheaf dictionary for smooth commutative group schemes
@@
 
-\medskip
-\noindent\textbf{Relation to other work.\ }
+\subsection*{Relation to other work.}
 The main use of the term character sheaf is of course due to Lusztig.
@@
 
-\medskip
-\noindent\textbf{Acknowledgements.\ } {We thank Pramod Achar, Masoud Kamgarpour and Hadi Salmasian for 
+\subsection*{Acknowledgements.}
+
+We thank Pramod Achar, Masoud Kamgarpour and Hadi Salmasian for 
 allowing us to hijack much of a Research in Teams meeting at the Banff International Research Station into a discussion of
@@
 Finally, we thank Joseph Bernstein for very helpful comments.
-%suggesting a connection between our category of quasicharacter sheaves for $p$-adic tori and quasicharacters of its pure rational forms.
-}
-
-{Finally, we gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
+
+Finally, we gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
 and the National Science and Engineering Research Council (Canada), as well the hospitality of the
-Banff International Research Station during a Research in Teams program.}
+Banff International Research Station during a Research in Teams program.
 

### 2015-07-22 dictionary.tex
Deleting comments

@@
 of algebraic tori over local fields; in doing so, we introduce `quasicharacter sheaves' and find a geometrization and
-categorification of quasi\-characters of $p$-adic tori.
+categorification of quasicharacters of $p$-adic tori.
 \end{abstract}
@@
 \section*{Introduction}
-
-%This paper extends Deligne's function-sheaf dictionary from connected commutative algebraic groups to smooth
-%commutative group schemes over finite fields and then provides an application to the geometrization and categorification
-%of quasicharacters of algebraic tori, abelian varieties and unipotent wound groups over non-Archimedean local fields.
 
@@
 where $m : G\times G\to G$ is the multiplication map.
-%
 If one wishes to make a category from this class of local systems, one is led to consider morphisms
@@
 smooth group scheme is an \'etale group scheme.
-%etale group schemes are algebraic groups only when they are finite.
 Our key tools for understanding the trace of Frobenius in the \'etale case 
 are a reinterpretation of $\CS(G)$ in terms of stalks (\S\ref{ssec:stalks}) and 
-%a relationship with 
 the Hochschild-Serre spectral sequence (\S\ref{ssec:E}) for $\Weil{} \ltimes \bG$, where $\Weil{} \subset \Gal(\Fq/\Fq)$ is the Weil group for $\Fq$.

### 2015-07-22 dictionary.tex
no categorification

--- 2015-07-22 dictionary.tex
@@
 As an application, we study character sheaves on the Greenberg transforms of the locally finite type N\'eron models
-of algebraic tori over local fields; in doing so, we introduce `quasicharacter sheaves' and find a geometrization and
-categorification of quasi\-characters of $p$-adic tori.
+of algebraic tori over local fields; in doing so, we introduce `quasicharacter sheaves' and find a geometrization of quasi\-characters of $p$-adic tori.
 \end{abstract}
@@
 As we explained in the Introduction, our original motivation for this paper was to find a
-geometrization and categorification of quasicharacters of $p$-adic tori. 
+geometrization of quasicharacters of $p$-adic tori. 
 This is now provided by the following adaptation of Theorem~\ref{thm:CSXK} in the case when
@@
  determined by $\alpha, \beta$ and $\phi$ \cite{chai-yu:01a}*{Thm. 8.5}.
-Combining this with the paragraph above gives the following instance of the geometrization and categorification of the transfer of quasicharacters.
+Combining this with the paragraph above gives the following instance of the geometrization of the transfer of quasicharacters.
 

### 2015-07-22 dictionary.tex

--- 2015-07-22 dictionary.tex
@@
 As an application, we study character sheaves on the Greenberg transforms of the locally finite type N\'eron models
-of algebraic tori over local fields; in doing so, we introduce `quasicharacter sheaves' and find a geometrization and
-categorification of quasicharacters of $p$-adic tori.
+of algebraic tori over local fields; in doing so, we introduce `quasicharacter sheaves' and find a
+geometrization of quasicharacters of $p$-adic tori.
 \end{abstract}

### 2015-07-22 dictionary.tex
Introduction

@@
 We also classify all morphisms in the category character sheaves on $G$.
-As an application, we study character sheaves on the Greenberg transforms of the locally finite type N\'eron models
-of algebraic tori over local fields; in doing so, we introduce `quasicharacter sheaves' and find a
-geometrization of quasicharacters of $p$-adic tori.
+As an application, we study character sheaves on Greenberg transforms of locally finite type N\'eron models of algebraic tori over local fields. 
+This provides a geometrization of quasicharacters of $p$-adic tori.
 \end{abstract}

### 2015-07-22 cover letter.tex
Added the cover letter.

% !TEX encoding = UTF-8 Unicode
\documentclass[a4, 10pt]{amsart}
%\usepackage{showlabels}
\renewcommand{\baselinestretch}{1.1}
%\newif\ifdraft\draftfalse
%\ifdraft\usepackage{showlabels}\fi
\usepackage{showlabels}
\usepackage{hyperref}
%\usepackage[math]{\KKurier}
%\usepackage{mathptmx}
%\usepackage{newcent}
%\usepackage{mathpazo}
%\usepackage{xspace}
%\usepackage[british]{babel}
%\usepackage{datetime}
%\usepackage{color}
%\usepackage[pdftex]{graphicx}
\usepackage{geometry}
%\usepackage[adobe-utopia]{mathdesign}
%\usepackage{fouriernc}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage[shortalphabetic]{amsrefs}
\usepackage[alphabetic]{amsrefs}
%\usepackage[alpha]{amsrefs}
%\usepackage[apalike]{amsrefs}
%\usepackage[numeric]{amsrefs}
%\renewcommand\MR{\relax}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,calc,matrix}
\usepackage{tikz-cd}

\usepackage{xypic}

\usepackage{yfonts}

\newtheorem{theorem}{Th\'eor\`eme}%[equation]
% \newtheorem{thm}{Theorem}[section]
\newtheorem{proposition}{Proposition}%[equation]
\newtheorem{proposition-definition}{Proposition-Definition}%[equation]
\newtheorem{corollary}{Corollaire}%[equation]
\newtheorem{lemma}{Lemme}%[equation]
\newtheorem{conjecture}{Conjecture}%[equation]
\newtheorem{question}{Question}%[equation]
\newtheorem{Claim}{Claim}%[equation]
\newtheorem{exercise}{Exercise}%[equation]
\newtheorem{construction}{Construction}%[equation]

\theoremstyle{definition}
\newtheorem{definition}{D\'{e}finition}%[equation]
\newtheorem{notation}{Notation}%[equation]
\newtheorem{example}{Exemple}%[equation]
\newtheorem{examples}{Exemples}%[equation]
\newenvironment{solution}[1]{\noindent\textbf{Solution to #1.} }{\ \rule{0.5em}{0.5em}}
\newtheorem{remark}{Remarque}%[equation]
%\newtheorem{question}[equation]{Question}
\newtheorem{note}{Note}%[equation]
\newtheorem{para}{\indent}%[equation]
\newtheorem{Para}{\relax}%[equation]

\theoremstyle{remark}
\newtheorem*{claim}{Claim}

%%%% Some Named Categories

%%%% Functors
\newcommand{\gal}[1]{{\operatorname{Gal}\hskip-1pt\left( {\bar #1}/#1 \right)}}
\newcommand{\Spec}[1]{{\operatorname{Spec}\hskip-1pt\left( #1 \right)}}
\newcommand{\weil}[1]{{\operatorname{W}\hskip-1pt\left( {\bar #1}/#1 \right)}}
\newcommand{\WeilDeligne}{\operatorname{W\hskip-1pt D}}

\newcommand{\FF}{{\mathbb{F}}}
\newcommand{\ZZ}{{\mathbb{Z}}}
\newcommand{\NN}{{\mathbb{N}}}
\newcommand{\CC}{{\mathbb{C}}}
\newcommand{\QQ}{{\mathbb{Q}}}
\newcommand{\bQQ}{{\mathbb{\bar Q}}}
\newcommand{\RR}{{\mathbb{R}}}
\newcommand{\EE}{\mathbb{\bar Q}_\ell}
\newcommand{\K}{{\mathbb{K}}}
\newcommand{\OK}{{\mathcal{O}_\K}}
\newcommand{\PK}{\mathfrak{p}_\K}
\newcommand{\bK}{{\mathbb{\bar K}}}
\newcommand{\Knr}{{\tilde \K}}
\renewcommand{\k}{{\Bbbk}}
\newcommand{\bk}{{\bar \Bbbk}}
\newcommand{\Zp}{\mathbb{Z}_p}
\newcommand{\Qp}{\mathbb{Q}_p}
\newcommand{\Qpp}{\mathbb{Q}_{p^2}}
\newcommand{\bQp}{{\mathbb{\bar Q}_p}}
\newcommand{\Fp}{\mathbb{F}_p}
\newcommand{\bFp}{{\mathbb{\bar F}_p}}
\newcommand{\Fq}{{\mathbb{F}_q}}
\newcommand{\bFq}{{\mathbb{\bar F}_q}}
\newcommand{\nr}{^\text{nr}}
%\newcommand{\ceq}{{\, :=\, }}
\newcommand{\Gal}{{\operatorname{Gal}}}
\newcommand{\Weil}{{\operatorname{W}}}
\newcommand{\Frob}{{\operatorname{Fr}}}
\newcommand{\Aut}{{\operatorname{Aut}}}
\newcommand{\Hom}{{\operatorname{Hom}}}

\newcommand{\p}{{\mathfrak{p}}}

\newcommand{\ceq}{{\, :=\, }}
\newcommand{\tq}{{\ \vert\ }}
\newcommand{\proj}{{\operatorname{pr}}}
\newcommand{\iso}{{\ \cong\ }}
\newcommand{\catM}{{\mathcal{M}}}
\newcommand{\coker}{{\operatorname{coker}}}
\newcommand{\obj}{{\text{obj}}}

\newcommand{\Gm}[1]{\mathbb{G}_{\hskip-2pt\textbf{m},#1}}
%\newcommand{\bGm}{\mathbb{\bar G}_\text{m}}

\newcommand{\bs}{{\bf s}}
\newcommand{\RPsi}{{R^\bullet\Psi}}
\newcommand{\IC}{{\operatorname{IC}^\bullet}}
\newcommand{\Var}{{\operatorname{Var}}}

\newcommand{\id}{{\operatorname{id}}}
\newcommand{\ind}{{\operatorname{ind}}}
\newcommand{\rss}{^\text{r.ss}}
\renewcommand{\ss}{^\text{ss}}
\newcommand{\unip}{^\text{unip}}
\newcommand{\nilp}{^\text{nilp}}
\newcommand{\ru}{^\text{r.u}}
\newcommand{\reg}{^\text{reg}}
\newcommand{\Greg}{^\text{G-reg}}
\newcommand{\sgn}{{\operatorname{sign}}}
\newcommand{\Lgroup}[1]{{\,^L\hskip-1pt{#1}}}
\newcommand{\dual}[1]{{\check{#1}}}
\DeclareMathOperator\Inn{Inn}
\DeclareMathOperator\Ad{Ad}
\DeclareMathOperator\Out{Out}
\DeclareMathOperator\GL{GL}
\DeclareMathOperator\PGL{PGL}
\DeclareMathOperator\SL{SL}
\DeclareMathOperator\Sp{Sp}
\DeclareMathOperator\SU{SU}
\DeclareMathOperator\SO{SO}
\DeclareMathOperator\GO{GO}
\DeclareMathOperator\GSp{GSp}
\DeclareMathOperator\PGSp{PGSp}
\DeclareMathOperator\PSp{PSp}
\DeclareMathOperator\GSpin{GSpin}
\DeclareMathOperator\Spin{Spin}
\DeclareMathOperator\supp{supp}
\DeclareMathOperator\Iso{Iso}
\newcommand{\sheafHom}{{\mathcal{H}\hskip-3pt om}\,}
\DeclareMathOperator\Irrep{Irrep}
\DeclareMathOperator\Ind{Ind}
\DeclareMathOperator\st{st}
\DeclareMathOperator\disc{disc}
\DeclareMathOperator\trace{trace}
\DeclareMathOperator\Loc{Loc}

\newcommand{\W}{\mathbb{W}}

\newcommand{\Lang}{\textbf{Lang}}
\newcommand{\Serre}{\textbf{Serre}}
\newcommand{\Green}[2]{\underline{#1}_{#2}^\text{Gr}}
\newcommand{\green}[3]{\underline{#1}_{#2}^{(#3)}}
\DeclareMathOperator\GR{Gr}
\newcommand{\Perv}{\operatorname{Perv}}
\newcommand{\MFO}{\operatorname{MFO}}
\newcommand{\swabGm}[1]{\textswab{G}_{{\hskip-2pt \textswab{m}},#1}}
\newcommand{\GC}{\textswab{C}}
\newcommand{\FC}{\operatorname{F\hskip-2pt C}}
\newcommand{\fc}{\operatorname{f\hskip-2pt c}}
\newcommand{\GP}{\textswab{P}}
\newcommand{\Res}{\operatorname{Res}}

\newcommand{\abs}[1]{\vert #1 \vert}

\makeatletter
\def\Ddots{\mathinner{\mkern1mu\raise\p@
\vbox{\kern7\p@\hbox{.}}\mkern2mu
\raise4\p@\hbox{.}\mkern2mu\raise7\p@\hbox{.}\mkern1mu}}
\makeatother

\newcommand\todo[1]{\ \vspace{5mm}\par \noindent\framebox{\begin{minipage}[c]{0.95 \textwidth} \tt #1\end{minipage}} \vspace{5mm} \par}

%%%%%%%%%%%%%%% RINGS AND GROUPS %%%%%%%%%%%%%%%

\newcommand{\EEx}{\EE^\times}

%%%%%%%%%%%%%%% ALGEBRAIC GROUPS %%%%%%%%%%%%%%%

%%%%%%%%%%%%%%% NAMED OPERATORS %%%%%%%%%%%%%%%
\DeclareMathOperator{\Hh}{H}

%%%%%%%%%%%% MISCELLANEOUS OPERATORS %%%%%%%%%%%%

\newcommand{\CS}{{\mathcal{C\hskip-0.8pt S}}}
\newcommand{\lCS}{{\CS_\text{flb}}}
\newcommand{\lCSiso}[1]{\lCS(#1)_{/\text{iso}}}
\newcommand{\bCS}{{\CS_0}}
\newcommand{\CSiso}[1]{\CS(#1)_{/\text{iso}}}
\newcommand{\bCSiso}[1]{\bCS(#1)_{/\text{iso}}}
\newcommand{\catname}[1]{\normalfont{\textsf{#1}}}
\newcommand{\Sch}[1]{{\catname{Sch}_{/#1}}}
\newcommand{\QCS}{{\mathcal{QC\hskip-0.8pt S}}}
\newcommand{\QCSiso}[1]{\QCS(#1)_{/\text{iso}}}

\usepackage[british]{babel}
\usepackage{datetime}%[yyyymmdd]
%\renewcommand{\dateseparator}{.}
%\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{tikz}
\usetikzlibrary{shapes,arrows}

\begin{document}
%\vskip-1cm
\rightline{\today}
\rightline{Vancouver}
\medskip

\noindent{Dear Professor Loeser (Dear Fran\c cois!),}
\medskip

We are grateful for such helpful comments from our reviewer. 
We have now completed our revisions and are ready to re-submit the paper. 
In this letter we explain the changes we made, motivated by the comments we received.

\begin{enumerate}
\item[(0)]
We reorganised the Introduction to reflect the changes discussed below. This included making a subsection called {\it Relation to other work}, following a recommendation.
We were also obliged to make small changes to the Abstract, to fit the changes.
\item
We added a Table of Contents, as suggested.
\item 
We added a paragraph in the Notations section (\S 1.1) explaining what we mean by an algebraic group, and also explaining how to detect when a smooth group scheme $G$ is an algebraic group, through its component group scheme $\pi_0(G)$.
We also explained how to determine when a smooth group scheme is an etale group scheme.
Hopefully this will clear up any possible confusion regarding our use of these terms.
% and addresses a suggestion from our reviewer.
\item
We changed nomenclature so that the paper now discusses two notions: {\it character sheaves} and {\it quasicharacter sheaves}. Character sheaves are based on a familiar concept: they are local systems on a smooth group scheme $G$ over a finite field $k$, equipped with some additional structure, and they provide a geometrization of characters of $G(k)$.  Quasicharacter sheaves provide a geometrization of quasicharacters of $p$-adic tori $T(K)$; they are local systems equipped with some additional structure, on the Greenberg transform of a Neron model. 
We are particularly grateful to our reviewer for suggesting this change.
Although we changed nomenclature, the actual definitions themselves did not change.
\item
The reviewer suggested we use the following section headings.
\begin{enumerate}
\item[– 1.] Recollections on character sheaves for commutative algebraic groups 
\item[– 2.] Character sheaves on etale group schemes
\item[– 3.] Character sheaves on commutative group schemes
\item[– 4.] Quasi-character sheaves on commutative p-adic groups
\end{enumerate}
We got very close to that. Our section headings are now:
\begin{enumerate}
\item[– 1.] Definitions and Recollections 
\item[– 2.] Character sheaves on \'etale group schemes over finite fields
\item[– 3.] Character sheaves on smooth commutative group schemes over finite fields
\item[– 4.] Quasicharacter sheaves for $p$-adic tori
\end{enumerate}
While we do treat quasicharacter sheaves for $p$-adic tori and abelian varieties in Section 4, we do not treat all commutative $p$-adic groups, so we opted for the less ambitious title. Otherwise, we hope the section headings are close enough; they do reflect a significant restructuring of the paper.
\item
We removed the proofs of many of the more obvious results in the section now called Definitions and Recollections. 
This included removing the proof of Lemma 1.5, which our reviewer found suspicious. We added a remark before Lemma 1.5 which we believe addresses the misgivings. We will happily reinstate the proof of Lemma 1.5 if it would be helpful.
\item
In Section 2 (Character sheaves on \'etale group schemes over finite fields) we extended the definition of $S_G : \CSiso{G} \to \Hh^2(E^\bullet_G)$ to include the general case when $G$ is a smooth commutative group scheme, rather than restricting the definition to etale commutative group schemes. We are careful to restrict to the etale case in the lemmas and proposition in this section, however.
\item
In Section 2.4 we added the language {\it invisible character sheaves} to refer to non-trivial character sheaves $\mathcal{L}$ on $G$ for which the trace of Frobenius function $t_\mathcal{L} : G(k) \to \EEx$ is trivial; see Definition 2.8.
\item
In Section 2 we added Remark 2.9, which recalls the Kunneth formula and derives a result which helps to compute $\Hh^2({\bar G}, \EEx)$.
\item 
We added Example 2.10, which exhibits three very interesting examples of character sheaves on etale group schemes and identifies each with its class in $\Hh^2(E_G^\bullet)$ under $S_G : \CSiso{G} \to \Hh^2(E^\bullet_G)$.
\item
Again following a suggestion from our reviewer, we added Section 2.5: {\it On the necessity of working with Weil sheaves}.
\item
All classical results were removed from Section 3 and moved to Section 1, then abbreviated, as suggested. Otherwise, Section 3 is largely unchanged in this revision.
\item
In Section 4 we focused attention on Neron models themselves, as opposed to their generic fibres, by replacing category $\mathcal{N}_K$ with category $\mathcal{N}$; see Section 4.1.
\item 
We added Example 4.1, giving Neron models for some $p$-adic tori.
\item
We made a declared definition of {\it quasicharacter sheaves}, Definition 4.2. The material itself was in the original submission of this paper.
\item
The discussion that was in Section 5.4 has become Corollaries 4.7 and 4.9.
\item
We added Example 4.8, which provides tori whose Neron models have the component groups appearing in Example 2.10.
\item
Finally, we added Remark 4.1 on quasicharacter sheaves and the Langlands correspondence for $p$-adic tori. 
\end{enumerate}

We believe these changes address the recommendations made by our reviewer and hope that this revised version will meet the approval of JIMJ.

\vskip0.3cm
\rightline{Best Regards,\hskip10cm}
\vskip0.4cm
%\centerline{\includegraphics[height=2cm,width=5cm]
%{/Users/Cunningham/MATHEMATICS/Latex/signature.pdf}}
%{/Users/cliftoncunningham/ownCloud/MATHEMATICS/Latex/signature.pdf}}
%\centerline{\textswab{ \hskip-0cm Clifton}}
%\centerline{\hskip+5cm Paris}
\centerline{Clifton Cunningham and David Roe}

\end{document}

\vskip3cm

\begin{bibdiv}
\begin{biblist}

\bib{Arthur}{article}{
   author={Arthur, James},
   title={A note on $L$-packets},
   journal={Pure Appl. Math. Q.},
   volume={2},
   date={2006},
   number={1, Special Issue: In honour of John H. Coates.},
   pages={199--217},
%   issn={1558-8599},
%   review={\MR{2217572 (2006k:22014)}},
}

\bib{Bernstein-Lunts}{book}{
   author={Bernstein, Joseph},
   author={Lunts, Valery},
   title={Equivariant sheaves and functors},
   series={Lecture Notes in Mathematics},
   volume={1578},
   publisher={Springer-Verlag},
   place={Berlin},
   date={1994},
   pages={iv+139},
%   isbn={3-540-58071-9},
%   review={\MR{1299527 (95k:55012)}},
}

\bib{SGA7.1}{book}{
   title={Groupes de monodromie en g\'eom\'etrie alg\'ebrique. I},
%   language={French},
 author={Grothendieck, Alexandre},
   series={Lecture Notes in Mathematics, Vol. 288},
   note={S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois-Marie 1967--1969
   (SGA 7 I);
   Dirig\'e par A. Grothendieck. Avec la collaboration de M. Raynaud et D.
   S. Rim},
   publisher={Springer-Verlag},
   place={Berlin},
   date={1972},
   pages={viii+523},
%   review={\MR{0354656 (50 \#7134)}},
}

\bib{SGA7.2}{book}{
   title={Groupes de monodromie en g\'eom\'etrie alg\'ebrique. II},
%   language={French},
 author={Deligne, P.},
 author={Katz, N.},
   series={Lecture Notes in Mathematics, Vol. 340},
   note={S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois-Marie 1967--1969
   (SGA 7 II);
   Dirig\'e par P. Deligne et N. Katz},
   publisher={Springer-Verlag},
   place={Berlin},
   date={1973},
   pages={x+438},
%   review={\MR{0354657 (50 \#7135)}},
}

\bib{Soergel}{article}{
   author={Soergel, Wolfgang},
   title={Langlands' philosophy and Koszul duality},
   conference={
      title={Algebra---representation theory},
      address={Constanta},
      date={2000},
   },
   book={
      series={NATO Sci. Ser. II Math. Phys. Chem.},
      volume={28},
      publisher={Kluwer Acad. Publ.},
      place={Dordrecht},
   },
   date={2001},
   pages={379--414},
%   review={\MR{1858045 (2002j:22019)}},
%   doi={10.1007/978-94-010-0814-3_17},
}

\bib{Vogan}{article}{
   author={Vogan, David A., Jr.},
   title={The local Langlands conjecture},
   conference={
      title={Representation theory of groups and algebras},
   },
   book={
      series={Contemp. Math.},
      volume={145},
      publisher={Amer. Math. Soc.},
      place={Providence, RI},
   },
   date={1993},
   pages={305--379},
%   review={\MR{1216197 (94e:22031)}},
%   doi={10.1090/conm/145/1216197},
}

\end{biblist}
\end{bibdiv}

\end{document}

### 2015-07-22 dictionary.tex
Removed Bernstein from the paper; added him to the cover letter.

@@
 
-\iffalse
-By any measure, there are more quasicharacter sheaves for $T$ than quasicharacters of $T(K)$.  
-In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization
-of complete Langlands parameters for $p$-adic groups 
-and, in the process, is led to study the representations of all the pure rational forms of the $p$-adic group, simultaneously.
-A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads
-to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category
-which appears to be tied to the representations of all the pure rational forms of the $p$-adic group \cite{bernstein:vogan_conference}.
-Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to
-quasicharacters of all the pure rational forms of $T$; we do not pursue that suggestion in this paper.
-\fi
-
 \subsection*{Relation to other work.}

### 2015-07-22 dictionary.tex
Deleting lots of comments

--- 2015-07-22 dictionary.tex
@@
 Then we return to our motivating application and use character sheaves to geometrize and categorify quasicharacters algebraic tori over local fields.
-% (\S \ref{sec:applications}).
 
@@
 Moreover, as examples show (\S \ref{eg:}), the kernel of $\TrFrob{G}$ is non-trivial in general.
-%The fact that $\TrFrob{G}$ may not be an isomorphism should not be too troubling:
-%if quasicharacter sheaves $(\gcs{L}, \mu,\phi)$ and $(\gcs{L}', \mu',\phi')$ determine the same character
-%of $G(\Fq)$ then $(\gcs{L},\phi)$ and $(\gcs{L}',\phi')$ are isomorphic as Weil sheaves.
-
-%The appearance of $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ in these two cases is interesting: on the one hand,
-%when $G$ is a connected commutative algebraic group over $\Fq$, isomorphism classes of quasicharacter
-%sheaves on $G$ are measured by $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ and the trace of Frobenius gives an
-%isomorphism $\TrFrob{G}: \CSiso{G} \to \Hom(G(\Fq),\EEx)$; on the other hand, if $G$ an \'etale commutative
-%group scheme over $\Fq$, then $\Hh^2(\bG,\EEx)^{\Gal(\bFq/\Fq)}$ measures the kernel of $\TrFrob{G}: \CSiso{G} \to \Hom(G(\Fq),\EEx)$. 
-%This observation makes plain the fact that  . . .
-%Indeed, quasicharacter sheaves on \'etale commutative group schemes that are trivialized
-%by discrete isogenies are invisible to the trace of Frobenius.
 
@@
 \end{theorem*}
-\noindent
-Thus, unless the component group scheme $\pi_0(\bG)$ is cyclic, category $\CS(G)$ contains
-non-trivial character sheaves lying in the kernel of the trace of Frobenius and therefore lost in translation to characters of $G(\Fq)$.
-%These {\it invisible character sheaves} are parametrized by $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$.
+If the component group scheme $\pi_0(\bG)$ is cyclic, then the kernel of $\TrFrob{G}$ will be trivial and
+each character of $G(\Fq)$ will uniquely determine a character sheaf on $G$, up to isomorphism.  But when
+$\pi_0(\bG)$ is large (c.f. Remark \ref{rem:H2}), $G$ will admit \emph{invisible character sheaves} with
+trivial trace of Frobenius.
 
@@
 where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
-%The appearance of the dual torus here is quite striking.
 
@@
 
-%We also want to situate our terminology in a historical context.
 For a connected commutative algebraic group over a finite field, it is not uncommon to refer to
@@
 In contrast to the case of algebraic varieties, the component group scheme $\pi_0(G)$ for $G$ need not be finite.
-%Unless noted otherwise, we place absolutely no conditions on the \'etale group scheme $\pi_0(G)$.
 
@@
 \end{enumerate}
-%\end{definition}
 Morphisms of character sheaves are defined in the natural way:
@@
 and the sets $\Hom(\cs{L},\cs{L}')$ in Theorem~\ref{thm:autornaught}; in this way we provide a complete description of the category $\CS(G)$.
-%
 In the meantime, we make an elementary observation about $\Hom(\cs{L},\cs{L}')$.
@@
 The next two results follow easily from the definitions.
-%In the remainder of this section We devote the remainder of this section to studying the behavior
-%of the trace of Frobenius under morphisms of group schemes.  These simple but important properties of
-%pullbacks and external products will be used in the proofs of many results in this paper.
 
@@
 The only non-trivial part is the last claim, so we will only address that point here.
-%
 Set $G \ceq G_1\times G_2$
@@
 Observe that $p_1\circ f = q_1 \circ r_1$ and $p_2 \circ f = q_2\circ r_2$.
-%
 Now, let $\cs{L} \ceq (\gcs{L},\mu,\phi)$ be a character sheaf on $G$
@@
 
-%\subsection{character sheaves on connected commutative algebraic groups} \label{sec:disc-isog}
-
 \subsection{Descent}\label{ssec:descentG}
-
-%Before turning our attention to character sheaves on connected commutative algebraic groups in Section~\ref{ssec:connected}, 
-%Here we treat two special classes of character sheaves on arbitrary smooth commutative group schemes $G$:
-%those that descend from local systems on $\bG$ to local systems on $G$ (\S \ref{ssec:descentG});
-%and those that are defined by discrete isogenies onto $G$ (\S \ref{ssec:discrete_isogenies}).
-%The latter will play a role in Sections~\ref{ssec:connected} and \ref{ssec:restriction}.
 
@@
 
-%\subsection{The function-sheaf dictionary for connected algebraic groups over finite fields}\label{ssec:connected}
-
 If the smooth commutative group scheme $G$ is of finite type, then every character sheaf descends to $G$;
@@
 $\Weil{}\to \Weil{}(G,\bg)$ of $\Weil{}(G,\bg)\to \Weil{}$.
-%
   Since $G$ is connected, the geometric point $\bg$ determines
@@
   $
-%
   On the other hand, we have already seen that $\trFrob{\cs{L}} : G(\Fq) \to \EEx$
@@
   which we will also denote $\lambda_g$.
-%
   We may now lift the $\ell$-adic character $\lambda_g : \Gal(\bFq/\Fq) \to \EEx$
@@
   $\pi_1(G,\bg) \to \Gal(\bFq/\Fq)$. 
- % 
   The $\Fq$ rational point $g$ also
@@
 as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3}, gives us all we need for points \ref{c1} and \ref{c2}.
-% as we briefly recall.
-%\todo{Fix citelist} %\citelist{\cite{deligne:SGA4.5}*{Sommes trig.},\cite{laumon:87a}*{1.1.3}}
 \iffalse
@@
 provides the following simple description of character sheaves.
-%
 A character sheaf $\cs{L}$ on an \'etale commutative group scheme $G$ over $\Fq$ is:
@@
 
-%\begin{remark}
-%Although we will mainly use the group homomorphism $S_G : \CSiso{G}\to \Hh^2(E^\bullet_G)$ when $G$
-%is an \'etale commutative group scheme, the function is defined for all smooth commutative group schemes $G$;
-%however, the next result does not extend to all smooth commutative group schemes.
-%\end{remark}
-
 \begin{proposition}\label{prop:SGiso}
@@
 determining the kernel and cokernel of $\TrFrob{G}$ when $G$ is an \'etale commutative group scheme over $\Fq$.
-
-%
 We begin with a simple, general result relating duals, invariants and coinvariants.
@@
 so it defines a morphism $\rho : \cs{L}\to \cs{L}'$, which is clearly an isomorphism. 
-%
 We have now defined a section of $\TrFrob{G}$.
@@
 \]
-%
 Now suppose $\bG = \ZZ^r \times \prod_{i = 1}^m \ZZ/N_i\ZZ$ is an arbitrary finitely generated abelian group,
@@
 
-%While most of this paper focuses on the question of determining the isomorphism classes of objects, 
 A complete understanding of the morphisms in $\CS(G)$ also requires a description of the
@@
   So to prove the proposition it suffices to show that $(\pi_! \EE)_\psi$ extends to a character sheaf on $G$.
-%
  By Lemma~\ref{lemma:ext}, there is an extension of the
@@
 from $\gcs{L}_{g}$ to $\gcs{L}_{g'}$.
-%
 The isomorphisms $\varphi_{g,g'}: \gcs{L}_{g} \to \gcs{L}_{g'}$ are canonical
@@
   Lemma~\ref{lem:pullback} to \eqref{eq:pi0}.
- %
   The sequence of abelian groups
@@
   character groups in \eqref{eq:pre-snake} is exact.
-%
   The upper row in \eqref{eq:pre-snake} is exact by Proposition~\ref{prop:middleexact}.
@@
 Also, since $G^0(\Fq)$ is finite, the image of $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ is a finite subgroup and therefore has bounded image.  
-%
 If $\chi \in G(\Fq)^*$ then there is some finite-image character $\chi_0$
@@
 \cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} and
-\cite{nicaise-sebag:motivicSerre}*{\S 2.2}. %citelist
-%
+\cite{nicaise-sebag:motivicSerre}*{\S 2.2}.
 For any non-negative integer $n$ we will write
@@
 \subsection{Quasicharacter sheaves}
-%{Character sheaves on the Greenberg transform of a N\'eron model} 
 \label{ssec:CS_on_GN}
 
-%Let $X \in \mathcal{N}$ be as above.
 Set $S = \Spec{R}$ and $S_n = \Spec{R_n}$;
@@
 Let $X$ be a smooth commutative group scheme over $S$.
-%We now define a category which will geometrize quasicharacters of $X(K)$.
 For every non-negative integer $n$, the Greenberg transform $\Gr^R_n(X)$ is a {\it smooth} commutative group scheme over $S_0$.
-%with component group scheme $\pi_0(X)_{\Fq} \ceq \pi_0(X) \times_S S_0$ and $\Fq$-rational points $X(R_n).$
-%
 The Greenberg transform $\Gr_R(X)$ of $X$ is a commutative group scheme over $\Fq$
-%with component group scheme $\pi_0(X)_{\Fq}$
 with $\Fq$-rational points $X(R)$.
-%
 The morphism of $\Fq$-schemes $\varrho^R_n(X) : \Gr_R(X) \to \Gr^R_n(X)$ induces a functor
@@
 as in Lemma~\ref{lem:pullback}.
-%This functor is faithful, so we may view $\CS(\Gr^R_n(X))$ as a subcategory of $\CS(\Gr_R(X))$.
 
@@
 though without insisting that the commutative group $\Fq$-scheme $G$ is smooth.
-%Let $X$ be a smooth commutative group scheme over $R$, with $R$ as above.
 A quasicharacter sheaf for $X$ is an object of
@@
 let $R$ be the ring of integers of $K$.
-%Fix a separable closure ${\bar K}$ of $K$ and let $\tilde{K}$ be the maximal unramified extension of $K$ in ${\bar K}$;
-%write $\tilde{R}$ for the ring of integers of $\tilde{K}$ and set $\tilde{S} = \Spec{\tilde{R}}$.
 \begin{enumerate}
@@
 \[
-%F_{\QCS}: 
 X \mapsto \QCSiso{X}
 \qquad\text{and}\qquad
-%F_{\text{}}: 
 X \mapsto \Hom_{\text{}}(X(K),\EEx)
@@
 \begin{proof}
-%\begin{enumerate}
 To prove \ref{x0}, use: Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$; the fact that
@@
 and $\pi_0(\bG) = \pi_0(X)_{\bFq}$; then argue as in part \ref{x0}.
-%\end{enumerate}
 \end{proof}
@@
 = \Hom(X_*(T)_{\mathcal{I}_K}, \EEx)_{\Weil{\Fq}} 
-%= \Hh^1(\Weil{}, \Hom(X_*(T), \EEx)^{\mathcal{I}_K}) 
 = \Hh^1(\Weil{\Fq}, \check{T}_\ell^{\mathcal{I}_K}).

### 2015-07-22 dictionary.tex

@@
 where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
-
-\iffalse
-By any measure, there are more quasicharacter sheaves for $T$ than quasicharacters of $T(K)$.  
-In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization
-of complete Langlands parameters for $p$-adic groups 
-and, in the process, is led to study the representations of all the pure rational forms of the $p$-adic group, simultaneously.
-A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads
-to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category
-which appears to be tied to the representations of all the pure rational forms of the $p$-adic group \cite{bernstein:vogan_conference}.
-Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to
-quasicharacters of all the pure rational forms of $T$; we do not pursue that suggestion in this paper.
-\fi
 

### 2015-07-22 dictionary.tex
Removed some commented-out text from the end.

--- 2015-07-22 dictionary.tex
@@
 \end{equation}
-%We have seen that the isomorphism $\QCS(\ZZ)\iso \Hom(\Weil{\Fq}, \EEx)$ is elementary.
-%The isomorphism $\QCSiso{\Gm{R}}\iso \Hom(\mathcal{I}_K, \EEx)$ may be deduced directly
-%from the class field theory of Serre and Hezewinkel as revisited beautifully in \cite{suzuki-yoshida:12a};
-%see also \cite{suzuki:14a}. The monoidal category of character sheaves on $\Gr^R_n(\Gm{R})$ is
-%canonically equivalent to the category of $\ell$-adic characters of the quotient of the \'etale fundamental
-%group $\pi_1(\Gr^R_n(\Gm{R}),\bFq)$ determined by the Lang isogeny for $\Gr^R_n(\Gm{R})$. Accordingly,
-%quasicharacter sheaves on $\Gm{R}$ may be apprehended as $\ell$-adic characters of the inverse limit
-%of these quotients, as $n$ ranges over $\NN$. By \cite{serre:isogenies}, there is a canonical isomorphism
-%between this inverse limit and $\mathcal{I}_K^\text{ab}$; this isomorphism is {\it not} restricted to the case
-%when $K$ and $\Fq$ have equal characteristic. This provides the isomorphism
-%$\QCSiso{\Gm{R}}\iso \Hom(\mathcal{I}_K, \EEx)$ in \eqref{eq:Gm}.
-%Since the sequences are split, this gives $\QCSiso{T}\iso \Hom(\Weil{K}, \EEx)$.
 We suspect that the general case of \eqref{eq:GLCT}, where $K$ is any local field and $T_K$ is any

### 2015-07-22 cover letter.tex
Small fixes to cover letter

@@
 \item[(0)]
-We reorganised the Introduction to reflect the changes discussed below. This included making a subsection called {\it Relation to other work}, following a recommendation.
+We reorganised the Introduction to reflect the changes discussed below. 
+This included making a subsection called {\it Relation to other work}, following a recommendation.
 We were also obliged to make small changes to the Abstract, to fit the changes.
+\item
+We removed Berstein's suggestion from the Introduction, since at the moment we are not able to pursue it. 
+We continue to thank him in the Acknowledgements, as we intend to return to this issue, elsewhere.
 \item
@@
 Character sheaves are based on a familiar concept: they are local systems on a smooth group scheme $G$ over a finite field $k$, equipped with some additional structure, and they provide a geometrization of characters of $G(k)$.
-Quasicharacter sheaves provide a geometrization of quasicharacters of $p$-adic tori $T(K)$; they are local systems equipped with some additional structure, on the Greenberg transform of a Neron model.
+Quasicharacter sheaves provide a geometrization of quasicharacters of $p$-adic tori $T(K)$; they are local systems equipped with some additional structure, on the Greenberg transform of a N\'eron model.
 We are particularly grateful to our reviewer for suggesting this change.
@@
 \item
-In Section 4 we focused attention on Neron models themselves, as opposed to their generic fibres, by replacing category $\mathcal{N}_K$ with category $\mathcal{N}$; see Section 4.1.
+In Section 4 we focused attention on N\'eron models themselves, as opposed to their generic fibres, by replacing category $\mathcal{N}_K$ with category $\mathcal{N}$; see Section 4.1.
 \item 
@@
 \item
-We added Example 4.8, which provides tori whose Neron models have the component groups appearing in Example 2.10.
+We added Example 4.8, which provides tori whose N\'eron models have the component groups appearing in Example 2.10.
 \item
-Finally, we added Remark 4.1 on quasicharacter sheaves and the Langlands correspondence for $p$-adic tori. 
+Finally, we added Remark 4.10 on quasicharacter sheaves and the Langlands correspondence for $p$-adic tori. 
 \end{enumerate}

### 2015-07-23 followup.tex
New file for followup paper.

--- 2015-07-22 dictionary.tex
@@
 \documentclass[10pt]{amsart}
-\usepackage[a4paper]{geometry}
-\title{From the function-sheaf dictionary to quasicharacters of $p$-adic tori}
 
+\title{Commutative Character Sheaves}
 \author{Clifton Cunningham}
+\address{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive Northwest, Calgary, AB, Canada, {T2N~1N4}.}
+\email{cunning@math.ucalgary.ca}
 \author{David Roe}
-
-\address{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive Northwest, Alberta, Calgary, Canada, {T2N~1N4}.}
-\email{cunning@math.ucalgary.ca}
-\address{Department of Mathematics, University of British Columbia, 1984 Mathematics Road, Vancouver, British Columbia, Canada, {V6T~1Z2}.}
+\address{Department of Mathematics, University of Pittsburgh, 301 Thackeray Hall, Pittsburgh, PA , United States, 15260.}
 \email{roed.math@gmail.com}
@@
 \subjclass[2010]{14F05 (primary), 14L15 (secondary), 22E50 (tertiary)}
-
-\keywords{character sheaves, p-adic tori, N\'eron models, Greenberg functor, geometrization, quasicharacter sheaves}
-
-%%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%
+\keywords{character sheaves}
 
 \usepackage{amssymb}
-\usepackage[initials]{amsrefs}
-
-%Customizations for amsrefs
-\BibSpec{lecture}{%
-  +{} {\PrintAuthors}				{author}
-  +{,}{ }						{title}
-  +{}{ \PrintDateB}				{date}
-  +{.}{ Lecture delivered at \textit}	{conference}
-  +{,}{ }						{address}
-  +{.}{ }						{transition}
-}
-
-% We make volume bold rather than vol. #
-\BibSpec{book}{%
-    +{}  {\PrintPrimary}				{transition}
-    +{,} { }							{title}
-    +{.} { }							{part}
-    +{:} { }							{subtitle}
-    +{,} { \PrintEdition}					{edition}
-    +{}  { \PrintEditorsB}				{editor}
-    +{,} { \PrintTranslatorsC}			{translator}
-    +{,} { \PrintContributions}			{contribution}
-    +{,} { }							{series}
-    +{} { \textbf}						{volume}
-    +{,} { }							{publisher}
-    +{,} { } 							{organization}
-    +{,} { }							{address}
-    +{,} { \PrintDateB}					{date}
-    +{,} { }							{status}
-    +{}  { \parenthesize}				{language}
-    +{}  { \PrintTranslation}				{translation}
-    +{;} { \PrintReprint}				{reprint}
-    +{.} { }							{note}
-    +{.} {}							{transition}
-    +{}  {\SentenceSpace \PrintReviews}	{review}
-}
-
-% The publisher wasn't appearing.
-\BibSpec{collection.article}{%
-    +{}  {\PrintAuthors}				{author}
-    +{,} { \textit}						{title}
-    +{.} { }							{part}
-    +{:} { \textit}						{subtitle}
-    +{,} { \PrintContributions}			{contribution}
-    +{,} { \PrintConference}				{conference}
-    +{}  {\PrintBook}					{book}
-    +{,} { }							{booktitle}
-    +{}  { \PrintEditorsB}				{editor}
-    +{,} { }							{series}
-    +{} { \textbf}						{volume}
-    +{,} { }							{publisher}
-    +{,} { }							{address}
-    +{,} { \PrintDateB}					{date}
-    +{,} { }							{pages}
-    +{,} { }							{status}
-    +{,} { \PrintDOI}					{doi}
-    +{,} { available at \eprint}			{eprint}
-    +{}  { \parenthesize}				{language}
-    +{}  { \PrintTranslation}				{translation}
-    +{;} { \PrintReprint}				{reprint}
-    +{.} { }							{note}
-    +{.} {}							{transition}
-    +{}  {\SentenceSpace \PrintReviews}	{review}
-}
-
+\usepackage{amsrefs}
 % Fonts
@@
 \usepackage{enumitem}
-% TikZ
-\usepackage{tikz}
-\usetikzlibrary{shapes,arrows,calc,matrix}
-\usepackage{tikz-cd}
 % Hyperrefs
@@
       \newtheorem{example}[theorem]{Example}
-
-%%%%%%%%%%%%%%%% TIKZ SETTINGS %%%%%%%%%%%%%%%%
-\tikzset{every picture/.style={>=stealth},label/.style={font=\footnotesize}}
 
@@
 \newcommand{\TrFrob}[1]{\operatorname{Tr}_{#1}}
-\newcommand{\lTrFrob}[1]{\TrFrob{#1}^2}
 %% Limits
@@
 \newcommand{\CS}{{\mathcal{C\hskip-0.8pt S}}}
-\newcommand{\lCS}{{\CS_\text{flb}}}
-\newcommand{\lCSiso}[1]{\lCS(#1)_{/\text{iso}}}
 \newcommand{\bCS}{{\CS_0}}
@@
 \newcommand{\LxL}{\text{$\gcs{L} \tight{0}{\boxtimes}{0} \gcs{L}$}}
-\newcommand{\ExE}{\text{$\cs{E}\tight{0}{\boxtimes}{0}\cs{E}$}}
-\newcommand{\bExE}{\text{$\gcs{E}\tight{0}{\boxtimes}{0}\gcs{E}$}}
-\newcommand{\AxA}{\text{$A \tight{1}{\times}{1} A$}}
-\newcommand{\BxB}{\text{$B \tight{1}{\times}{1} B$}}
-\newcommand{\GzxGz}{\text{$G^0 \tight{1}{\times}{1} G^0$}}
+
 %% Hyphenation override
 \hyphenation{quasi-character}
-
-% MSC footnote
-\makeatletter
-\newcommand\MSC[2][2010]{%
-   \let\thefootnotetwo=\thefootnote%
-   \renewcommand{\thefootnote}{}%
-   \long\def\@makefntext##1{%
-     \parindent\CrelleIndent
-	 \hb@xt@0em{}##1}%
-   \footnotetext{\textup{#2} \textit{Mathematics Subject Classification.}\enspace  #1}
-   \let\thefootnote=\thefootnotetwo%
-   \crellefntext%
-}
-\makeatother
 
@@
 
-\begin{abstract}
-We consider the rigid monoidal category of character sheaves on a smooth commutative group scheme $G$ over a finite field
-$k$ and expand the scope of the function-sheaf dictionary from connected commutative algebraic groups to this setting.
-We find the group of isomorphism classes of character sheaves on $G$ and show that it is an extension of the group
-of characters of $G(k)$ by a cohomology group determined by the component group scheme of $G$.
-We also classify all morphisms in the category character sheaves on $G$.
-As an application, we study character sheaves on Greenberg transforms of locally finite type N\'eron models of algebraic tori over local fields. 
-This provides a geometrization of quasicharacters of $p$-adic tori.
-\end{abstract}
+\section{Commutative Character Sheaves}
 
-\maketitle
+\section{No Invisible Character Sheaves}
 
-\section*{Introduction}
+By the universal coefficient theorem
 
-As Deligne explained in \cite{deligne:SGA4.5}*{Sommes trig.}, if $G$ is a connected commutative algebraic group
-over a finite field $k$, then the trace of Frobenius provides a bijection between the group $G(\Fq)^*$ of $\ell$-adic
-characters of $G(\Fq)$ and isomorphism classes of those rank-one $\ell$-adic local systems $\mathcal{E}$ on $G$ for which 
-\begin{equation}\label{introbox}
-m^* \cs{E} \iso \cs{E} \boxtimes \cs{E},
-\end{equation}
-where $m : G\times G\to G$ is the multiplication map.
-If one wishes to make a category from this class of local systems, one is led to consider morphisms
-$\cs{E} \to \cs{E}'$ of sheaves which are compatible with particular choices of \eqref{introbox} for $\cs{E}$ and $\cs{E'}$. 
-{\it A priori}, the composition $\cs{E} \to \cs{E}' \to \cs{E}''$ of two such morphisms need not be
-compatible with the choices of \eqref{introbox} for $\cs{E}$ and $\cs{E}''$.
- However, for connected $G$ the isomorphism \eqref{introbox} is unique, if it exists, and there is no impediment
- to making the dictionary categorical.
-
-If $G$ is a commutative algebraic group over $\Fq$ which is not connected, however, then the isomorphism \eqref{introbox}
-need not be unique. In order to track the choice of isomorphism, consider the category $\bCS(G)$ of pairs $(\cs{E},\mu_\cs{E})$
-where $\cs{E}$ is a rank-one local system on $G$ and $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ is a chosen
-isomorphism of local systems on $G\times G$. 
-In this case, the trace of Frobenius provides an epimorphism from isomorphism classes of objects in $\bCS(G)$ to characters
-of $G(\Fq)$, but the epimomorphism need not be injective; consequently,
-every character of $G(\Fq)$ may be geometrized as a pair $(\cs{E},\mu_\cs{E})$ but perhaps not uniquely.
-Indeed, it follows from a special case of the main result of this paper that the kernel of the trace of Frobenius
-$\bCS(G) \to G(\Fq)^*$ trivial if and only if the  group scheme of connected components of $G$ is cyclic.
-The defect in the function-sheaf dictionary for characters of commutative algebraic groups over finite fields may be
-addressed with the following observation: if $(\cs{E},\mu_\cs{E})$ and $(\cs{E}',\mu_\cs{E}')$ determine the same
-character of $G(\Fq)$ then $\cs{E}\iso \cs{E}'$ as local systems on $G$.
-
-Motivated by an application to quasicharacters of algebraic tori over local fields, in this paper we extend the
-function-sheaf dictionary from commutative algebraic groups over finite fields to smooth commutative group schemes $G$ over $\Fq$.
-In order to do this, we replace the local system $\cs{E}$ on $G$ with a Weil local system while retaining the extra structure $\mu_\cs{E}$. 
-In this way we are led to the category $\CS(G)$ of {\it character sheaves} on $G$ (\S\ref{ssec:category}):
-objects in $\CS(G)$ are triples $(\gcs{L}, \mu,\phi)$, where $\gcs{L}$ is a rank-one local system on $\bG := G\times_{\Spec{\Fq}} \Spec{\bFq}$
-and $\phi : \Frob{G}^* \gcs{L}\to \gcs{L}$ and $\mu : \bm^* \gcs{L} \iso \gcs{L} \boxtimes \gcs{L}$ are
-isomorphisms of sheaves satisfying certain compatibility conditions;
-morphisms in $\CS(G)$ are then morphisms of Weil sheaves which are compatible with the extra structure.
-This paper establishes the basic properties of category $\CS(G)$, using the group homomorphism 
-\[
-\TrFrob{G}: \CSiso{G} \to G(\Fq)^*
-\]
-provided by the trace of Frobenius  to find the relation between character sheaves on $G$ and characters of $G(\Fq)$.
-Then we return to our motivating application and use character sheaves to geometrize and categorify quasicharacters algebraic tori over local fields.
-
-We begin our study of category $\CS(G)$ by returning to the case when $G$ is a
-connected commutative algebraic group over $\Fq$, revisiting Deligne's function-sheaf dictionary (\S\ref{sec:category}).
-We consider character sheaves that arise via base change to $\bFq$ from local systems on $G$ (\S\ref{ssec:descentG}) and
-those that appear in a pushforward from a constant sheaf along a discrete isogeny $H \to G$ (\S\ref{ssec:discrete_isogenies}).  
-While these constructions make sense even for non-connected $G$, in the connected case we show that
-every character sheaf can be described in both of these ways (\S\ref{ssec:connected}).  
-We use this fact to prove that $\TrFrob{G} : \CS(G) \to G(\Fq)^*$ is an isomorphism for connected commutative algebraic groups $G$.
-We also determine the automorphism groups of character sheaves on such $G$. 
-These facts are well known.
-
-Next, we consider character sheaves on \'etale commutative group schemes $G$ over $\Fq$ (\S\ref{sec:etale}).
-\'Etale group schemes form a counterpoint to connected algebraic groups, since the component group of any
-smooth group scheme is an \'etale group scheme.
-Our key tools for understanding the trace of Frobenius in the \'etale case 
-are a reinterpretation of $\CS(G)$ in terms of stalks (\S\ref{ssec:stalks}) and 
-the Hochschild-Serre spectral sequence (\S\ref{ssec:E}) for $\Weil{} \ltimes \bG$, where $\Weil{} \subset \Gal(\Fq/\Fq)$ is the Weil group for $\Fq$.
-We define (\S\ref{ssec:S}) an isomorphism $S_G$ from $\CSiso{G}$ to the second cohomology of the total space of the spectral sequence
-\[
-E_2^{p,q} \ceq \Hh^p(\Weil{}, \Hh^q(\bG, \EEx)) \Rightarrow \Hh^{p+q}(\Weil{} \ltimes \bG, \EEx).
-\]
-Paired with the short exact sequence
-\[
-  0 \to \Hh^0(\Weil{},\Hh^2(\bG,\EEx)) \to \Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1(\bG,\EEx)) \to 0
-\]
-arising from the spectral sequence, the isomorphism $S_G$ allows us to show (\S\ref{ssec:SandT})
-that the group homomorphism $\TrFrob{G}: \CSiso{G} \to G(\Fq)^*$ is surjective with kernel $\Hh^2(\bG,\EEx)^{\Weil{}}$.
-The necessity of using Weil local systems on $G$ in the definition of $\CS(G)$ already appears here:
-if one were to use local systems on $G$ instead, the group homomorphism $\TrFrob{G}$ would not then be surjective (\S \ref{ssec:bS}). 
-Moreover, as examples show (\S \ref{eg:}), the kernel of $\TrFrob{G}$ is non-trivial in general.
-
-Having understood $\CS(G)$ in two extreme cases --
-for connected commutative algebraic groups and for \'etale commutative group schemes --
-we turn to the case of smooth commutative group schemes (\S\ref{sec:main}) using the component group sequence
-\[
-0 \to G^0 \to G \to \pi_0(G) \to 0.
-\]
-Using pullbacks of character sheaves we obtain a diagram
-\[
-  \begin{tikzcd}[row sep=20, column sep=20]
-    0 \rar & \CSiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
-    & \CSiso{G} \rar \dar{\TrFrob{G}} & \CSiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
-    0 \rar & \pi_0(G)(\Fq)^* \rar & G(\Fq)^* \rar & G^0(\Fq)^* \rar & 0.
-  \end{tikzcd}
-\]
-We show that the rows of this diagram are exact (\S\S\ref{ssec:restriction},\ref{ssec:component}),
-so we may apply the snake lemma to prove the main theorem of the paper,
-\begin{theorem*}[{Thm. \ref{thm:snake}}]
-If $G$ is a smooth commutative group scheme over $\Fq$ then the trace of Frobenius gives a short exact sequence
-\[
-\begin{tikzcd}
-0 \arrow{r} & \Hh^2(\pi_0(\bG),\EEx)^{\Weil{}} \arrow{r} & \CSiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0.
-\end{tikzcd}
-\]
-\end{theorem*}
-If the component group scheme $\pi_0(\bG)$ is cyclic, then the kernel of $\TrFrob{G}$ will be trivial and
-each character of $G(\Fq)$ will uniquely determine a character sheaf on $G$, up to isomorphism.  But when
-$\pi_0(\bG)$ is large (c.f. Remark \ref{rem:H2}), $G$ will admit \emph{invisible character sheaves} with
-trivial trace of Frobenius.
-
-We also illuminate the nature of the category $\CS(G)$ by showing that every morphism in this category
-is either an isomorphism or trivial, and by showing
-\begin{theorem*}[{Thm. \ref{thm:autornaught}}]
-If $G$ is a smooth commutative group scheme over $\Fq$ then
-\[
-\Aut(\cs{L}) \iso  \Hh^1(\pi_0(\bG), \EEx)^{\Weil{}}
-\]
-for all quasicharacter sheaves $\cs{L}$ on $G$.
-\end{theorem*}
-
-\subsection*{Application to quasicharacters of \texorpdfstring{$p$}{p}-adic tori and abelian varieties}
-As indicated above, our interest in the function-sheaf dictionary for smooth commutative group schemes
-over finite fields comes from an application to $p$-adic representation theory,
-specifically to quasicharacters (\S\ref{ssec:quasicharacters}) of $p$-adic tori.
-However, we found that our method of passing from $p$-adic tori to group schemes over $\Fq$ applies more generally to
-any local field $K$ with finite residue field $\Fq$ and to any commutative algebraic group over $K$ that admits a N\'eron model $X$.
-This class of algebraic groups over $K$ includes abelian varieties and unipotent $K$-wound groups,
-in addition to the algebraic tori we initially considered.
-
-In this paper we show that if $X$ is as above then quasicharacters of $X(K)$ are geometrized and categorified by character sheaves on the
-Greenberg transform $\Gr_R(X)$ of the N\'eron model $X$.
-Although not locally of finite type, $\Gr_R(X)$ is a commutative group scheme over $\Fq$ and also a projective limit
-of smooth commutative group schemes $\Gr^R_n(X)$.
-This structure allows us to adapt our work on character sheaves on smooth group schemes over
-finite fields to construct (\S\ref{ssec:CS_on_GN}) a category $\QCS(X)$
-of {\it quasicharacter sheaves} for $X$, which are certain sheaves on $\Gr_R(X)\times_{\Spec{\Fq}} \Spec{\bFq}$, with extra structure.
-The ability to generalize the function-sheaf dictionary to non-connected group schemes plays a crucial role in this application.
-
-Having defined quasicharacter sheaves on N\'eron models of commutative algebraic groups over $K$
-and character sheaves on commutative group schemes over $\Fq$, we consider how
-these categories are related as $K$ and $\Fq$ vary.  We describe (\S\ref{ssec:basechange}) functors between categories
-of quasicharacter sheaves that model restriction and norm homomorphisms of character groups $G(k')^* \to G(k)^*$ and $G(k)^* \to G(k')^*$,
-and describe how quasicharacter sheaves behave under Weil restriction (\S\ref{ssec:wrK}).  We also give (\S\ref{ssec:transfer})
-a categorical version of a result of Chai and Yu \cite{chai-yu:01a},
-relating quasicharacter sheaves for tori over different local fields, even local fields
-with different characteristic.
-
-Finally, specializing to the case that $X = T$ is the N\'eron model of an algebraic torus over $K$ (\S\ref{ssec:CS_tori}), 
-we give a canonical short exact sequence 
-\[
-0 \to \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{}} \to \QCSiso{T} \to \Hom_\text{}(T(K),\EEx) \to 0,
-\]
-where $X_*(T)_{\mathcal{I}_K}$ is the group of coinvariants of the cocharacter lattice $X_*(T)$ of the algebraic torus
-$T_K$ by the action of the inertia group $\mathcal{I}_K$ of $K$, and where $\Hom_\text{}(T(K),\EEx)$
-denotes the group of quasicharacters of $T(K)$.
-We further show that automorphism groups in $\QCS(T)$ are given, for every quasicharacter sheaf $\cs{F}$ for $T$, by
-\[
-\Aut(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
-\]
-where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
-
-\subsection*{Relation to other work.}
-The main use of the term character sheaf is of course due to Lusztig.
-It is applied to certain perverse sheaves on connected reductive algebraic groups over algebraically closed fields in
-\cite{lusztig:85a}*{Def.~2.10} and to certain perverse sheaves on certain reductive groups over algebraically closed fields in the series of papers
-beginning with \cite{lusztig:disconnected1}.
-When commutative, it is not difficult to relate Frobenius-stable character sheaves to our character sheaves
-(Remark~\ref{rem:Lusztig}). The new features that we have found pertaining to Weil sheaves
-and $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ do not arise in that context because, for such groups,
-Weil sheaves are unnecessary (\S \ref{ssec:alg_groups}) and $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}=0$ (Remark \ref{rem:H2}).
-
-For a connected commutative algebraic group over a finite field, it is not uncommon to refer to
-local systems satisfying \eqref{introbox}  as character sheaves; see for example, \cite{kamgarpour:09a}*{Intro}.
-Our definition of character sheaves on smooth commutative group schemes over finite fields evolved from this notion,
-with an eye toward quasicharacters of $p$-adic groups.
-The process of creating a category from the group of quasicharacters of a $p$-adic torus informs our choice of the
-term quasicharacter sheaf in this paper.
-
-We anticipate that future work on quasicharacter sheaves will make use of   \cite{suzuki-yoshida:12a} and \cite{suzuki:14a},
-and will clarify the relation between this project and other attempts to geometrize admissible distributions on $p$-adic groups,
-such as \cite{cunningham-kamgarpour:13a} (limited to quasicharacters of $\ZZ_p^\times$) and \cite{aubert-cunningham:02a}
-(limited to characters of depth-zero representations). 
-We are actively pursuing the question of how to extend the notion of quasicharacter sheaves to provide a geometrization
-of admissible distributions on connected reductive algebraic groups over $p$-adic fields, not just commutative ones.
-
-\subsection*{Acknowledgements.}
-
-We thank Pramod Achar, Masoud Kamgarpour and Hadi Salmasian for 
-allowing us to hijack much of a Research in Teams meeting at the Banff International Research Station into a discussion of
-quasicharacter sheaves.  We also thank them for their kindness, knowledge and invaluable help.
-We thank Takashi Suzuki for clarifying the relation between this project and his recent work and for very helpful
-observations and suggestions, especially related to our use of the Hochschild-Serre spectral sequence.
-We thank Alessandra Bertrapelle and Cristian Gonz\'ales-Avil\'es for disabusing us of a misapprehension concerning
-the Greenberg realization functor and for drawing our attention to their result on Weil restriction and the Greenberg transform.
-Finally, we thank Joseph Bernstein for very helpful comments.
-
-Finally, we gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
-and the National Science and Engineering Research Council (Canada), as well the hospitality of the
-Banff International Research Station during a Research in Teams program.
-
-\tableofcontents
-
-\section{Definitions and recollections} \label{sec:category}
-
-\subsection{Notations}\label{ssec:notation}
-
-Throughout this paper, $G$ is a smooth commutative group scheme
-over a finite field $\Fq$ and $m : G \times G\to G$ is its multiplication morphism.
-
-We will make use of the short exact sequence of smooth group schemes defining the component group scheme for $G$:
-\[
-\begin{tikzcd}
-0 \rar & G^0 \arrow{r}{\iota_0} & G \arrow{r}{\pi_0} & \pi_0(G) \rar & 0.
-\end{tikzcd}
-\]
-Then $G^0$ is a connected algebraic group and $\pi_0(G)$ is an \'etale commutative group scheme.
-In contrast to the case of algebraic varieties, the component group scheme $\pi_0(G)$ for $G$ need not be finite.
-
-It follows from the smoothness of $G$ that the structure morphism $G \to \Spec{\Fq}$ is locally of finite type, being smooth.
-If the structure morphism $G \to \Spec{\Fq}$ is also \'etale, then $G$ is an \'etale group scheme; this does not imply that $\pi_0(G)$ is finite.
-An algebraic group over $\Fq$ is a smooth group scheme of finite type, in which case its component group scheme is finite.
-
-We fix an algebraic closure $\bFq$ of $\Fq$ and write $\bG$ for the
-smooth commutative group scheme $G \times_{\Spec{\Fq}} \Spec{\bFq}$ over $\bFq$
-obtained by base change from $k$. The multiplication morphism for $\bG$ will be denoted by $\bm$.
-
-Let $\Frob{}$ denote the geometric Frobenius element in $\Gal(\bFq/\Fq)$ as
-well as the corresponding automorphism of $\Spec{\bFq}$. The Weil group
-$\Weil{}\subset \Gal(\bFq/\Fq)$ is the subgroup generated by $\Frob{}$.
-Let $\Frob{G} \ceq \id_{G} \times \Frob{}$ be the Frobenius automorphism of $\bG = G \times_{\Spec{\Fq}} \Spec{\bFq}$.
-
-We fix a prime $\ell$, invertible in $\Fq$.
-We will work with constructible $\ell$-adic sheaves \citelist{\cite{deligne:80a}*{\S 1.1} \cite{SGA5}*{Expos\'es V, VI}}
-on schemes locally of finite type over $\Fq$, employing the standard formalism.
-We also make extensive use of the external tensor product of $\ell$-adic sheaves,
-defined as follows: if $\mathcal{F}$ and $\mathcal{G}$ are constructible $\ell$-adic
-sheaves on schemes $X$ and $Y$ and $p_X : X\times Y\to X$ and $p_Y : X\times Y \to Y$
-are the projections, then $\mathcal{F}\boxtimes \mathcal{G} \ceq p_X^* \mathcal{F} \otimes p_Y^*\mathcal{G}$.
-
-For any commutative group $A$, we will write $A^*$ for the dual group $\Hom(A, \EEx)$.
-
-\subsection{Character sheaves on commutative group schemes over finite fields}\label{ssec:category}
-
-\begin{definition}\label{def:CS}
-A \emph{character sheaf on $G$} is a triple
-$\cs{L}\ceq (\gcs{L},\mu,\phi)$ where:
-\begin{enumerate}
-\labitem{(CS.1)}{CS.1} $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean a constructible
-$\ell$-adic sheaf on $\bG$, {\it lisse} on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
-\labitem{(CS.2)}{CS.2} $\mu: \bm^* \gcs{L} \to \LxL$ is an isomorphism of
-sheaves on $\bGxG$ such that the following diagram commutes,
-  where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
-  \[
-  \begin{tikzcd}[row sep=30]
-  \bm_3^*\gcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
-    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
-    \gcs{L} \boxtimes \bm^* \gcs{L} \arrow{rr}{\id \boxtimes \mu}
-    &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL
-  \end{tikzcd}
-  \]
-\labitem{(CS.3)}{CS.3} $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an
-  isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with
-  $\mu$ in the sense that the following diagram commutes.
-  \[
-  \begin{tikzcd}[row sep=20]
-  \Frob{\GxxG}^* \bm^* \gcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
-    && \Frob{\GxxG}^*(\LxL)\\
-    \arrow[equal]{u} \bm^*  \Frob{G}^* \gcs{L} \arrow[swap]{d}{\bm^* \phi}
-    && \Frob{G}^*\gcs{L}\boxtimes \Frob{G}^*\gcs{L} \dar{\phi\boxtimes \phi} \arrow[equal]{u} \\
-    \bm^*\gcs{L} \arrow{rr}{\mu}
-    && \LxL
-  \end{tikzcd}
-  \]
-\end{enumerate}
-Morphisms of character sheaves are defined in the natural way:
-\begin{enumerate}
-\labitem{(CS.4)}{CS.4} if $\cs{L} = (\gcs{L},\mu,\phi)$ and
-  $\cs{L'} = (\gcs{L'},\mu',\phi')$ are character sheaves on $G$ then
-  a morphism $\rho : \cs{L} \to \cs{L}'$ is a map $\brho : \gcs{L} \to \gcs{L'}$
-  of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
-  \[
-  \begin{tikzcd}[column sep=40]
-  \Frob{G}^* \gcs{L} \rar{\Frob{G}^* \brho} \arrow[swap]{d}{\phi} & \Frob{G}^* \gcs{L'} \dar{\phi'}
-  & & \arrow[swap]{d}{\mu} \bm^* \gcs{L} \rar{\bm^* \brho} & \bm^* \gcs{L'} \dar{\mu'} \\
-  \gcs{L} \rar{\brho} & \gcs{L'}
-  & {} & \LxL \rar{\tight{1}{\rho\boxtimes \rho}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
-  \end{tikzcd}
-  \]
-\end{enumerate}
- The category of character sheaves on $G$ will be denoted by $\CS(G)$.
- \end{definition}
-
-Category $\CS(G)$ is a rigid monoidal category
-\cite{etingof:09a}*{\S1.10} under the tensor product
-$\cs{L} \otimes \cs{L'}$ defined by $(\gcs{L}\otimes\gcs{L'}, \mu\otimes\mu', \phi\otimes \phi')$,
-with duals given by applying the sheaf hom functor
-$\sheafHom(\ - \ ,\EE)$.
-This rigid monoidal category structure for $\CS(G)$ gives the set $\CSiso{G}$
-of isomorphism classes in $\CS(G)$ the structure of a group.
-
-\begin{remark}
-The category of character sheaves on $G$ is not abelian since it is not closed under direct sums; 
-thus $\CS(G)$ is not a tensor category in the sense of \cite{deligne:02a}*{0.1}.  
-We suspect that requiring that $\mu$ be injective rather than
-an isomorphism and dropping the condition that the stalks be one-dimensional would yield an abelian category.
-\end{remark}
-
-We will describe the group $\CSiso{G}$ in Theorem~\ref{thm:snake}
-and the sets $\Hom(\cs{L},\cs{L}')$ in Theorem~\ref{thm:autornaught}; in this way we provide a complete description of the category $\CS(G)$.
-In the meantime, we make an elementary observation about $\Hom(\cs{L},\cs{L}')$.
-
-\begin{lemma}\label{lem:autornaught}
-Let $G$ be a smooth commutative group scheme over $\Fq$.
-If $\cs{L}$ and $\cs{L}'$ are character sheaves on $G$, then
-every $\rho\in \Hom(\cs{L},\cs{L}')$ is either trivial (zero on every stalk)
-or an isomorphism. 
-\end{lemma}
-
-\iffalse
-\begin{proof}
-Suppose $\rho \in \Hom(\cs{L},\cs{L}')$.
-We prove the lemma by considering the linear transformations $\brho_{\bg} : \gcs{L}_{\bg} \to \gcs{L}_{\bg}$ at the stalks
-above geometric points $\bg$ on $G$ and showing that, either each $\brho_{\bg}$ trivial or each $\brho_{\bg}$ is an isomorphism.
-(This idea is expanded upon in Section~\ref{ssec:stalks}.)
-Let ${\bar e}$ be the geometric point above the identity $e$ for $G$ determined by our choice of algebraic closure $\bFq$ of $\Fq$.
-If $\brho_{\bar e} = 0$ then the second diagram in \ref{CS.4} implies that $\brho_{\bg} = 0$ for all $\bg$, in which case $\rho$ is trivial.
-On the other hand, if $\brho_{\bar e}$ is non-trivial then the second diagram in \ref{CS.4} implies that $\brho_{\bg}$ is non-trivial
-for all $\bg$ and thus an isomorphism, since the stalks of character sheaves are one-dimensional; in this case $\rho$ is an isomorphism.
-\end{proof}
-\fi
-
-\subsection{Trace of Frobenius}\label{ssec:Frob}
-
-In this section we introduce two tools which will help us understand isomorphism classes of objects in $\CS(G)$:
-the map $\CSiso{G} \to G(k)^*$ given by trace of Frobenius and the pullback functor $\CS(G) \to \CS(H)$
-associated to a morphism $H \to G$ of smooth group schemes over $\Fq$.
-
-Let $(\gcs{L},\phi)$ be a Weil sheaf on $G$. Every $g\in G(\Fq)$
-determines a geometric point $\bg$ fixed by $\Frob{G}$. 
-Together with the canonical isomorphism $(\Frob{G}^*\gcs{L})_{\bg} \iso  \gcs{L}_{\Frob{G}(\bg)}$,
-the automorphism $\phi$ determines an automorphism $\phi_{\bg}$ of the $\EE$-vector space $\gcs{L}_{\bg}$.
-Let $\trace(\phi_{\bg};\gcs{L}_{\bg})$ be the trace of $\phi_{\bg} \in \Aut_{\EE}(\gcs{L}_{\bg})$ and let
-$\trFrob{(\gcs{L},\phi)} : G(\Fq)\to \EE$ be the function defined by 
-\begin{equation}\label{trWeil}
-\trFrob{(\gcs{L},\phi)}(g) \ceq \trace(\phi_{\bg};\gcs{L}_{\bg}),
-\end{equation}
-commonly called the {\em trace of Frobenius of $(\gcs{L},\phi)$}.
-Note that if $(\gcs{L},\phi) \iso (\gcs{L'},\phi')$ as Weil sheaves, 
-then $\trFrob{(\gcs{L},\phi)} = \trFrob{(\gcs{L'},\phi')}$ as functions on $G(\Fq)$.
-
-Now suppose $\cs{L} = (\gcs{L},\mu,\phi)$ is a character sheaf on $G$.
-Then the isomorphism $\bm^* \gcs{L} \iso \gcs{L} \boxtimes\gcs{L}$ and the diagram of
-\ref{CS.3} guarantee
-that the function $\trFrob{(\gcs{L},\phi)} : G(\Fq)\to \EEx$ is a group homomorphism, which we will also denote by $\trFrob{\cs{L}}$.
-Moreover, this homomorphism depends only on the isomorphism class of $\cs{L}$, so we obtain a map
-\begin{align*}
-\TrFrob{G} : \CSiso{G} &\to G(\Fq)^*, \\
-\cs{L} &\mapsto \trFrob{\cs{L}}.
-\end{align*}
-Since tensor products on the stalks of $\cs{L}$ induce pointwise multiplication on the trace of Frobenius, $\TrFrob{G}$ is a group homomorphism.
-
-The next two results follow easily from the definitions.
-
-\begin{lemma}\label{lem:pullback}
-  If $f : H\to G$ is a morphism of smooth commutative group schemes over $\Fq$, then
-  \begin{align*}
-  f^* : \CS(G) &\to \CS(H) \\
-  (\gcs{L},\mu,\phi) &\mapsto (\bf^*\gcs{L},(\bfxf)^*\mu,\bf^*F)
-  \end{align*}
-  defines a monoidal functor dual to $f \colon H(\Fq) \to G(\Fq)$ in the sense that
-  \[
-  \begin{tikzcd}[row sep=20, column sep=30]
-   \CSiso{G} \rar{f^*} \arrow[swap]{d}{\TrFrob{G}} & \CSiso{H} \dar{\TrFrob{H}} \\
-   G(\Fq)^* \rar & H(\Fq)^*
-  \end{tikzcd}
-  \]
-  is a commutative diagram of groups.  Moreover, $(f\circ g)^* = g^* \circ f^*$.
-\end{lemma}
-\iffalse
-\begin{proof}
-  Let $\cs{L}$ be a character sheaf on $G$. 
-  Pullback by $\bf$ takes rank-one local systems to rank-one local systems.
-  To see that $(\bfxf)^* \mu$ satisfies \ref{CS.2},
-  apply the functor $(\bfxf)^*$
-  to \ref{CS.2} for $\cs{L}$ and use the canonical isomorphism
-  $(\bfxf)^*(\LxL) \iso \bf^*\gcs{L} \tight{-3}{\boxtimes}{-3} \bf^*\gcs{L}$.
-  To show that $f^*\cs{L}$ satisfies
-  \ref{CS.3}, apply the same functor to \ref{CS.3} for $\cs{L}$.
-  Since $f$ is a morphism of group schemes defined over $\Fq$
-  it provides isomorphisms $(\bfxf)^*\Frob{\GxxG}^* \iso \Frob{\GxxG}^* (\bfxf)^*$
-  and $(\bfxf)^* \bm^*\iso \bm^* \bf^*$ between functors of constructible sheaves.
-
-  Applying $\bf^*$ and $\bf^* \tight{1}{\times}{1}\bf^*$ to \ref{CS.4} defines the action
-  of $f^*$ on morphisms of character sheaves; arguing as above shows that $f^*$ is
-  a functor from $\CS(G)$ to $\CS(H)$.  Since tensor products commute with pullback in schemes,
-  $f^* : \CS(G) \to \CS(H)$ is a monoidal functor.
-  The diagram relating $f^* : \CS(G) \to \CS(H)$, $f^* : G(k)^* \to H(k)^*$ and trace of Frobenius
-  commutes by \cite{laumon:87a}*{1.1.1.2}, where the ambient
- finite type hypothesis can be replaced by locally of finite type.
-
-  Finally, the fact that $(f\circ g)^* = g^* \circ f^*$ follows from the analogous
-  statements about the pullback functor on $\ell$-adic constructible sheaves.
-\end{proof}
-\fi
-
-If $G_1$ and $G_2$ are smooth commutative group schemes over $\Fq$ then characters of $(G_1 \times G_2)(\Fq)$
-all take the form $\chi_1\otimes \chi_2$ for characters $\chi_1$ of $G_1(\Fq)$ and $\chi_2$ of $G_2(\Fq)$. 
-The next lemma shows that character sheaves on $G$ enjoy an analogous property.
-
-\begin{lemma}\label{lem:product}
-If $G_1$ and $G_2$ are smooth commutative group schemes over $\Fq$ then the following diagram commutes.
-\[
-\begin{tikzcd}[column sep=60]
-\arrow{d}{\TrFrob{G_1} \times \TrFrob{G_2}} \CSiso{G_1}\times \CSiso{G_2} \arrow{r}{(\cs{L}_1,\cs{L}_2)\mapsto \cs{L}_1\boxtimes \cs{L}_2}
-& \arrow{d}{\TrFrob{G_1\times G_2}} \CSiso{G_1\times G_2}\\
-(G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
-\end{tikzcd}
-\]
-Moreover, every character sheaf on $G_1\times G_2$ is isomorphic to $\cs{L}_1\boxtimes\cs{L}_2$
-for some character sheaves $\cs{L}_1$ on $G_1$ and $\cs{L}_2$ on $G_2$.
-\end{lemma}
-
-\iffalse
-\begin{proof}
-The only non-trivial part is the last claim, so we will only address that point here.
-Set $G \ceq G_1\times G_2$
-and write $e_1$ and $e_2$ for the identity elements of $G_1$ and $G_2$.
-Define $f : G\to G\times G$ by $f(g_1,g_2) \ceq (g_1,e_2,e_1,g_2)$.
-Observe that $m\circ f = \id_G$.
-Let $p_1$, $p_2$ be the projection morphisms pictured below:
-\[
-\begin{tikzcd}
-G & \arrow[swap]{l}{p_1} G\times G \arrow{r}{p_2} & G.
-\end{tikzcd}
-\]
-Let $r_1$ and $r_2$ be the projection morphisms pictured below,
-with sections $q_1$ and $q_2$, also morphisms of group schemes:
-\[
-\begin{tikzcd}
-G_1  \arrow[swap, bend right]{r}{q_1} &
-\arrow[swap, bend right]{l}{r_1} G_1\times G_2 \arrow[bend left]{r}{r_2} &
-\arrow[bend left]{l}{q_2} G_2.
-\end{tikzcd}
-\]
-Observe that $p_1\circ f = q_1 \circ r_1$ and $p_2 \circ f = q_2\circ r_2$.
-Now, let $\cs{L} \ceq (\gcs{L},\mu,\phi)$ be a character sheaf on $G$
-and set $\cs{L}_1 \ceq q_1^* \cs{L}$ and $\cs{L}_2 \ceq q_2^* \cs{L}$.
-By Lemma~\ref{lem:pullback}, $\cs{L}_1$ is a character sheaf on $G_1$
-and $\cs{L}_2$ is a character sheaf on $G_2$.
-We will obtain an isomorphism $\cs{L} \iso  \cs{L}_1\boxtimes \cs{L}_2$.
-
-Applying the functor $f^*$ to the isomorphism $\mu$ yields
-\begin{equation}\label{eq:fm}
-f^*\mu : f^* m^* \gcs{L} \to f^*(\gcs{L}\boxtimes \gcs{L}) .
-\end{equation}
-We have already seen that $m\circ f = \id_G$, so $f^* m^* \gcs{L} = \gcs{L}$.  
-Since $f^*p_1^*\gcs{L} = r_1^* q_1^* \gcs{L} = r_1^* \gcs{L}_1$ and $f^*p_2^*\gcs{L} = r_2^* q_2^* \gcs{L} = r_2^*\gcs{L}_2$,
-we have 
-\[
-f^*(\gcs{L}\boxtimes \gcs{L})  = f^*p_1^*\gcs{L}\otimes f^* p_2^*\gcs{L} = \gcs{L}_1\boxtimes \gcs{L}_2.
-\]
-It follows that \eqref{eq:fm} gives an isomorphism $\gcs{L} \to  \gcs{L}_1\boxtimes \gcs{L}_2$.
-It is routine to show that this morphism satisfies
-\ref{CS.4}, as it applies here,
-from which it follows that we have exhibited an isomorphism
-$\cs{L} \to \cs{L}_1\boxtimes \cs{L}_2$ of characters sheaves on $G\times G$.
-\end{proof}
-\fi
-
-Using these results on pullbacks and products, we may prove a naturality property of $\TrFrob{G}$.
-
-\begin{proposition}\label{prop:functorialG}
-The homomorphism $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ defines a natural transformation
-between the two contravariant additive functors
-\begin{align*}
-F_1 : G &\mapsto \CSiso{G} \\
-F_2 : G &\mapsto G(\Fq)^*
-\end{align*}
-from the category of smooth commutative group schemes over $\Fq$ to the category of commutative groups.
-\end{proposition}
-
-\begin{proof}
-The first part of Lemma~\ref{lem:pullback} shows that $F_1$ is a functor,
-while the second part shows that Trace of Frobenius is a natural transformation
-$T: F_1 \to F_2$. When further combined with Lemma~\ref{lem:product},
-we see that $F_1$ is an additive functor and $T: F_1 \to F_2$ is a natural
-transformation between additive functors,
-concluding the proof of Proposition~\ref{prop:functorialG}.
-\end{proof}
-
-\subsection{Descent}\label{ssec:descentG}
-
-In this section we consider a category of sheaves on $G$ obtained by replacing the Weil sheaf $(\gcs{L}, \phi)$
-on $\bG$ in the definition of a character sheaf with an $\ell$-adic local system on $G$ itself;
-these will play a role in Sections~\ref{ssec:connected} and \ref{ssec:alg_groups}.
-
-\begin{definition}
-Let $\bCS(G)$ be the category of pairs $(\cs{E},\mu_\cs{E})$
-where $\cs{E}$ is an $\ell$-adic local system on $G$ of rank-one,
-equipped with an isomorphism $\mu_\cs{E} : m^* \cs{E} \to \cs{E} \boxtimes \cs{E}$
-satisfying the analogue of \ref{CS.2} on $G$;
-morphisms in $\bCS(G)$ are defined as in the second part of
-\ref{CS.4}. 
-\end{definition}
-
-We put a rigid monoidal structure on $\bCS(G)$ in the same way as for $\CS(G)$.
-
-\begin{proposition}\label{prop:BG}
-Extension of scalars defines a full and faithful functor
-\[
-B_G : \bCS(G) \to \CS(G).
-\]
-\end{proposition}
-
-\begin{proof}
- Suppose $(\cs{E},\mu_\cs{E})$ in an object of $\bCS(G)$.
- Let $b_G : \bG \to G$ be the pullback of $\Spec{\bFq} \to \Spec{\Fq}$ along $G\to \Spec{\Fq}$.
- Set $\gcs{L} = b_G^* \cs{E}$. 
- The functor $b_G^*$ takes local systems on $G$ to local systems on $\bG$.
- The local system $\gcs{L}$ comes equipped with an isomorphism
- $\phi: \Frob{G}^* \gcs{L} \to \gcs{L}$.
- The resulting functor from local systems on $G$ to Weil local systems on $\bG$, given on objects by $\cs{E} \mapsto (\gcs{L},\phi)$, 
- is full and faithful; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII} and \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.1.2}.
- The isomorphism $\mu \ceq b_{G\times G}^*\mu_\cs{E}$ satisfies \ref{CS.2}
- for $\gcs{L}$ and $\phi$ is compatible with $\mu$ in the sense of \ref{CS.3}.
- This construction defines the functor $B_G : \bCS(G) \to \CS(G)$ given on objects by $(\cs{E},\mu_\cs{E}) \mapsto (\gcs{L},\mu, \phi)$, as defined here. 
- Because morphisms in $\bCS(G)$ and $\CS(G)$ are morphisms of local systems on $G$ and $\bG$,
- respectively, satisfying condition~\ref{CS.4}, this functor is also full and faithful.
-\end{proof}
-
-We will say that a character sheaf $\cs{L} \in \CS(G)$ \emph{descends to $G$} if it is isomorphic to some $B_G(\cs{E}, \mu_\cs{E})$.
-
-\begin{remark}\label{rem:descent}
-In fact, it is not difficult to recognize character sheaves that descend to $G$: they are exactly those character sheaves
-$\cs{L} = (\gcs{L},\mu,\phi)$ for which the action of $W$ on $\gcs{L}$ given by $\phi$ extends to a continuous action
-of $\Gal(\bFq/\Fq)$ on $\gcs{L}$; see \cite{deligne-katz:SGA7.2}*{Expos\'e XIII, Rappel 1.1.3} for example. 
-\end{remark}
-
-\subsection{Discrete isogenies}\label{ssec:discrete_isogenies}
-
-Here we consider character sheaves on $G$ that are defined by discrete isogenies onto $G$
-(\S \ref{ssec:discrete_isogenies}); these will play a role in Section~\ref{ssec:restriction}.
-
-A finite, \'etale, surjective morphism $H\to G$ of smooth group schemes over $\Fq$ for which the action
-of $\Gal(\bFq/\Fq)$ on the kernel is trivial is called a {\it discrete isogeny}, inspired by \cite{kamgarpour:09a}*{\S 2.2}.
-
-\begin{proposition}\label{prop:finite}
-Let $f: H \to G$ be a discrete isogeny and let $A$ be the kernel of $f$.
-Let $V$ be a $1$-dimensional representation of $A$ 
-equipped with an isomorphism $V\to V\otimes V$.
-Let $\psi : A \to \EEx$ be the character of $V$.
-Then $(f_! V_H)_\psi$ (the $\psi$-isotypic component of $f_!V_H$) is an object of $\bCS(G)$.
-\end{proposition}
-
-\begin{proof}
-Let $f$, $A$, $V$ and $\psi$ be as above and set $\cs{E} = (f_! V_H)_\psi$.
-Since $A$ is abelian, $\cs{E}$ is an $\ell$-adic local system on $G$ of rank one.
-We must show that $\cs{E}$ comes equipped with an isomorphism $\mu_\cs{E} : m^* \cs{E} \to \cs{E}\boxtimes\cs{E}$.
-To do this we use \'etale descent to see that pullback along $f$ gives an equivalence between $\ell$-adic local systems
-on $G$ and $A$-equivariant local systems on $H$ {\it cf.\ } \cite{bernstein-luntz:equivariant_sheaves}*{Prop 8.1.1}. 
-In particular, $f^*\cs{E}$ is the $A$-equivariant constant sheaf $V$ on $H$ with character $\psi$.
-Since $f$ is a morphism of group schemes, the functor $f^*$ defines $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$
-from the isomorphism $m^*\psi \iso \psi \boxtimes\psi$ determined by $V\to V\otimes V$. 
-\end{proof}
-
-\begin{remark}
-Since $V$ is $1$-dimensional, the choice of $V \to V\otimes V$ is exactly the choice of an isomorphism $V\iso \EE$.
-\end{remark}
-
-\begin{remark}
-A descent argument similar to the one employed in the proof of Lemma~\ref{prop:finite} is used in
-\cite{boyarchenko-drinfeld:10a}*{Lemma~1.10}, though in the more restrictive case of connected algebraic groups.
-\end{remark}
-
-\subsection{Recollections on character sheaves for connected algebraic groups}\label{ssec:connected}
-
-If the smooth commutative group scheme $G$ is of finite type, then every character sheaf descends to $G$;
-we will see that they are not equivalent, in general, however.
-
-\begin{lemma}\label{lem:bounded_connected}
-If $G$ is a connected commutative algebraic group over $\Fq$ then 
-\[
-B_G : \bCS(G) \to \CS(G)
-\]
- is an equivalence of categories.
-\end{lemma}
-
-\iffalse
-\begin{proof}
-Choose any $\Fq$-rational point $g$ on $G$ and let $\bg$ be the geometric point on $G$ lying above $g$.
-Recall that the \emph{Weil group} of $G$, which we will denote by $\Weil{}(G,\bg)$, is a subgroup of the \'etale
-fundamental group defined by the following diagram:
-\[
- \begin{tikzcd}
- 1 \rar & \ar[equal]{d} \pi_1(\bG, \bg) \rar & \Weil{}(G,\bg) \rar \dar[hook] & \Weil{} \rar \dar[hook] & 1 \\
- 1 \rar &  \pi_1(\bG, \bg) \rar & \pi_1(G,\bg) \rar & \Gal(\bFq/\Fq) \rar & 1.
- \end{tikzcd}
-\]
-The $\Fq$-rational point $g$ under the geometric point $\bg$ determines a splitting
-$\Weil{}\to \Weil{}(G,\bg)$ of $\Weil{}(G,\bg)\to \Weil{}$.
-  Since $G$ is connected, the geometric point $\bg$ determines
-  an equivalence between the category of $\ell$-adic Weil local systems on $G$ and
-  $\ell$-adic representations of $\Weil{}(G,\bg)$ \cite{deligne:80a}*{1.1.12}.
-
-  Now let $(\gcs{L},\mu,\phi)$ be a character sheaf on $G$
-  and let $\lambda : \Weil{}(G, \bg) \to \EEx$ be the character determined by $(\gcs{L},\phi)$.
-  Composing with the splitting $\Weil{} \to \Weil{}(G,\bg)$ yields an $\ell$-adic character
-  $\lambda_g : \Weil{} \to \EEx$, which is the same as the Trace of Frobenius defined in Section~\ref{ssec:Frob}, for every $\Fq$ rational point $g$ on $G$:
-  $
-  \lambda_g(\Frob{}) =  \trFrob{\cs{L}}(g).
-  $
-  On the other hand, we have already seen that $\trFrob{\cs{L}} : G(\Fq) \to \EEx$
-  is a group homomorphism. 
-  Since $G$ is an algebraic group over $\Fq$, $G(\Fq)$ is finite.
-  Therefore $\trFrob{\cs{L}}(g) = \lambda_g(\Frob{})$ is a root of unity
-  for every $g\in G(\Fq)$.  Since $\Weil{}$ is generated by
-  $\Frob{}$ and $\lambda_g : \Weil{} \to \EEx$ is
-  a character, it follows that the image of $\lambda_g$ is a finite group.
-  Thus, $\lambda_g$ extends to an $\ell$-adic character of $\Gal(\bFq/\Fq)$,
-  which we will also denote $\lambda_g$.
-  We may now lift the $\ell$-adic character $\lambda_g : \Gal(\bFq/\Fq) \to \EEx$
-  to an $\ell$-adic character $\pi_1(G,\bg) \to \EEx$ using the canonical topological group homomorphism
-  $\pi_1(G,\bg) \to \Gal(\bFq/\Fq)$. 
-  The $\Fq$ rational point $g$ also
-  determines an equivalence between the category of $\ell$-adic
-  representations of $\pi_1(G,\bg)$ and $\ell$-adic local systems on $G$. Let
-  $\cs{E}$ be a local system on $G$ in the isomorphism class
-  determined by this $\ell$-adic character of $\pi_1(G,\bg)$.
-  Then $b_G^*\cs{E} \iso \gcs{L}$.
-
-  Since $b_{G\times G}^*$ is full and faithful (again, see
-\cite{deligne-katz:SGA7.2}*{Expos\'e XIII} or \cite{beilinson-bernstein-deligne:81a}*{Prop. 5.1.2}),
- \[
-  b_{G\times G}^* : \Hom(m^*\cs{E},\cs{E}\boxtimes\cs{E}) \to \Hom(\bm^*\gcs{L},\gcs{L}\boxtimes\gcs{L})
- \]
-  is a bijection
-  (hom taken in the categories on constructible $\ell$-adic sheaves on
-  $G\times G$ and $\bG\times \bG$ respectively,
-  in which $\ell$-adic local systems sit as full subcategories).
-  Let $\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ be the isomorphism matching
-  $\mu : \bm^*\gcs{L} \to \gcs{L}\boxtimes\gcs{L}$,
-  the latter appearing in the definition of $\cs{L}$.
-  Then, as in Section~\ref{ssec:descentG}, $(\cs{E},\mu_\cs{E})$ is an object of $\bCS(G)$
-  and $\cs{L} \ceq (\gcs{L},\mu,\phi)$ is isomorphic to $(b_G^*\cs{E},b_{G\times G}^*\mu_\cs{E})$ in $\CS(G)$.
-  Thus, the full and faithful functor $B_G : \bCS(G) \to \CS(G)$ from Section~\ref{ssec:descentG}
-  is also essentially surjective, hence an equivalence.
-\end{proof}
-\fi
-
-Using this equivalence of categories, we may give a good description of $\CS(G)$ when $G$ is connected and finite type.
-
-\begin{proposition}\label{prop:connected}
- If $G$ is a connected, commutative algebraic group over $\Fq$ then:
- \begin{enumerate}
- \labitem{(1)}{c1} $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ is an isomorphism of groups;
- \labitem{(2)}{c2} every character sheaf on $G$ is isomorphic to one defined by a discrete isogeny;
- \labitem{(3)}{c3} $\Aut(\cs{L}) = 1$, for all character sheaves $\cs{L}$ on $G$.
- \end{enumerate}
- \end{proposition}
-\begin{proof}
-By Lemma~\ref{lem:bounded_connected}, we know that every character sheaf $\cs{L}$ on $\bG$ descends to $G$;
-let $\cs{E}$ be an object of $\bCS(G)$ for which $B_G(\cs{E}) \iso \cs{L}$.
- Since the functor $B_G : \bCS(G) \to \CS(G)$ is full and faithful, $\Aut(\cs{L}) = \Aut(\cs{E})$.
-From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields,
-as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3}, gives us all we need for points \ref{c1} and \ref{c2}.
-\iffalse
-As in the proof of Proposition~\ref{prop:finite}, use \'etale descent to see that pullback by the Lang isogeny $\Lang : G\to G$
-defines an equivalence of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$. 
-Under this equivalence, local systems $\cs{E}$ on $G$ arising from objects in $\bCS(G)$ are matched with $G(\Fq)$-equivariant
-constant local systems of rank-one on $G$, and therefore with one-dimensional representations of $G(\Fq)$. 
-In the same way, pullback along the isogeny $\Lang\times\Lang : G\times G\to G\times G$ matches the extra structure
-$\mu_\cs{E} : m^*\cs{E} \to \cs{E}\boxtimes\cs{E}$ with an isomorphism $m^*V \to V\boxtimes V$ of one-dimensional
-representations of $G(\Fq)\times G(\Fq)$, which is exactly an isomorphism $V \to V\otimes V$ of one-dimensional representations,
-which is exactly the choice of an isomorphism $V\iso \EE$.
-We see that $\bCS(G)$ is equivalent to the category of characters of $G(\Fq)$.
-Let $\bg$ be a geometric point above $g \in G(\Fq)$.  If $\cs{E}$ matches $\psi : G(\Fq)\to \EEx$ under this equivalence,
-a simple calculation on stalks reveals that the action of Frobenius on $\cs{E}_{\bg}$ is multiplication by $\psi(g)^{-1}$.
-In other words, for every $\cs{E}$ in $\bCS(G)$, the trace of $\Lang^*\cs{E}$ is $\trFrob{\cs{E}}^{-1}$ as a
-representation of $G(\Fq)$, proving parts \ref{c1} and \ref{c2}.
-\fi
-For part \ref{c3}, suppose $\Lang^*\cs{E} = V$ with isomorphism $V \to V\otimes V$.
-Observe that the equivalence above establishes a bijection between $\Aut(\cs{E})$ and the group of automorphisms of $\rho : V\to V$ for which 
-\[
-\begin{tikzcd}
-\arrow{d}{} V \arrow{r}{\rho} & V\arrow{d}{}\\
-V\otimes V \arrow{r}{\rho\otimes \rho} & V\otimes V
-\end{tikzcd}
-\]
-commutes. 
-Since the only such isomorphism $\rho$ is $\id_V$, it follows that $\Aut(\cs{E}) = 1$, completing the proof.
-\end{proof}
-
-We have just seen that, for a connected commutative algebraic group $G$ over $\Fq$, the category of character sheaves
-on $G$ is equivalent to the category of one-dimensional representations $V$ of $G(\Fq)$ equipped with an isomorphism
-$V\iso \EE$, and therefore equivalent to the category of characters $\psi$ of $G(\Fq)$.
-We have also just seen that if the character of $\Lang^*\cs{E}$ is $\psi$ then the canonical isomorphism
-$m^*\psi \iso \psi \boxtimes \psi$ determines the isomorphism $\mu_\cs{E} : \cs{E} \to \cs{E}\boxtimes\cs{E}$.
-This fact leads (back) to a perspective on the function-sheaf dictionary common in the literature in which one considers
-one-dimensional local systems $\cs{E}$ on $G$ for which \emph{there exists} an isomorphism
-$m^*\cs{E} \iso \cs{E} \boxtimes\cs{E}$ \cite{kamgarpour:09a}*{Intro}.
-As a slight variation, one may also consider one-dimensional local systems $\gcs{L}$ on $\bG$ for which \emph{there exists}
-an isomorphism $\Frob{G}^*\gcs{L} \iso \gcs{L}$ and an isomorphism $\bm^*\gcs{L} \iso \gcs{L} \boxtimes\gcs{L}$.
-
-Although the category $\CS(G)$ of character sheaves on $G$ specializes to $\bCS(G)$ when $G$ is of finite type
-(\S \ref{ssec:alg_groups}), this description is \emph{not} sufficient when extending the dictionary to smooth
-commutative group schemes, as we will see already in Section~\ref{sec:etale}.
-In particular, for a given $\gcs{L}$ and $\phi$ there may be many $\mu$ so that $(\gcs{L},\mu,\phi)$ is a character sheaf.
-For \'etale $G$, Proposition~\ref{prop:etale-iso} shows that $\Hh^2(\bG,\EEx)^{\Weil{}}$ measures the possibilities for $\mu$.
-We will see in Section~\ref{sec:main} that $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ plays an analogous role for general
-smooth commutative group schemes $G$.
-
-\section{Character sheaves on \'etale commutative group schemes over finite fields} \label{sec:etale}
-
-In this section we give a complete characterization of the category of character sheaves on \'etale commutative group schemes over finite fields.
-
-\subsection{Stalks of character sheaves}\label{ssec:stalks}
-
-The equivalence $G \mapsto G(\bFq)$,
-from the category of \'etale commutative group schemes over $\Fq$ to the category of commutative groups equipped
-with a continuous action of $\Gal(\bFq/\Fq)$,
-provides the following simple description of character sheaves.
-A character sheaf $\cs{L}$ on an \'etale commutative group scheme $G$ over $\Fq$ is:
-\begin{enumerate}
- \labitem{(cs.1)}{cs.1} an indexed set of one-dimensional
-  $\EE$-vector spaces $\gcs{L}_x$, as $x$ runs over
-  $G(\bFq)$;
-
- \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms
-  $\mu_{x,y} : \gcs{L}_{x+y} \xrightarrow{\iso} \gcs{L}_{x} \otimes\gcs{L}_{y}$,
-  for all $x,y \in G(\bFq)$, such that
-  \[
-   \begin{tikzcd}[row sep=40]
-    \gcs{L}_{x+y+z} \arrow{rr}{\mu_{x+y,z}} \arrow[swap]{d}{\mu_{x,y+z}}
-    && \gcs{L}_{x+y}\otimes\gcs{L}_{z} \dar{\mu_{x,y} \tight{0.5}{\otimes}{1} \id} \\
-    \gcs{L}_{x} \otimes\gcs{L}_{y+z} \arrow{rr}{\id \otimes\mu_{y,z}}
-    && \gcs{L}_{x} \otimes\gcs{L}_{y} \otimes\gcs{L}_{z}
-   \end{tikzcd}
-  \]
-  commutes, for all $x,y,z\in G(\bFq)$; and
- \labitem{(cs.3)}{cs.3} an indexed set of isomorphisms $\phi_{x} : \gcs{L}_{\Frob{}(x)} \to \gcs{L}_x$
-  such that
-  \[
-   \begin{tikzcd}[row sep=40]
-    \gcs{L}_{\Frob{}(x)+\Frob{}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{}(x),\Frob{}(y)}}
-    && \gcs{L}_{\Frob{}(x)}\otimes\gcs{L}_{\Frob{}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
-    \gcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
-    && \gcs{L}_x \otimes\gcs{L}_y
-   \end{tikzcd}
-  \]
-  commutes, for all $x,y\in G(\bFq)$.
-\end{enumerate}
-Under this equivalence, a morphism $\rho : \cs{L} \to \cs{L'}$ of character sheaves on $G$ is given by
-\begin{enumerate}
- \labitem{(cs.4)}{cs.4} an indexed set $\brho_x : \gcs{L}_x \to \gcs{L'}_x$
-  of linear transformations such that
-  \[
-   \begin{tikzcd}[column sep=40]
-    \arrow[swap]{d}{\phi_x} \gcs{L}_{\Frob{}(x)} \rar{\brho_{\Frob{}(x)}} & \gcs{L'}_{\Frob{}(x)} \dar{\phi_x'}
-    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-    & \arrow[swap]{d}{\mu_{x,y}} \gcs{L}_{x+y} \rar{\brho_{x+y}} & \gcs{L'}_{x+y} \dar{\mu'_{x,y}} \\
-    \gcs{L}_x \rar{\brho_x} & \gcs{L'}_x
-    & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\brho_x\otimes\brho_y} & \gcs{L'}_x \otimes\gcs{L'}_y
-   \end{tikzcd}
-  \]
-  both commute, for all $x, y \in G(\bFq)$.
-\end{enumerate}
-
-We will see that $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ may not provide complete
-information about isomorphism classes of character sheaves on $G$ when $G$ is not a connected algebraic group.
-Our main tool for understanding this phenomenon
-is a group homomorphism $S_G: \CSiso{G} \to \Hh^2(E^\bullet_G)$ defined in Section~\ref{ssec:S}, for which the next two sections are preparation.
-
-\subsection{A spectral sequence}\label{ssec:E}
-
-Let $G$ be a smooth commutative group scheme over $\Fq$.
-The zeroth page of the Hochschild-Serre spectral sequence
-is a double complex $E^{\bullet, \bullet}$ defined by
-\[
-E^{i,j} = C^i(\Weil{}, C^j(G(\bFq), \EEx));
-\]
-see \cite{vakil:Algebraic_Geometry}*{\S 1.7}, expanding on \cite{weibel:Homological_Algebra}*{Ch 5 and \S 7.5}.
-The standard derivative on cochains yields two derivatives,
-\begin{align*}
-d_G &: E^{i,j} \to E^{i,j+1} \quad \mbox{and} \\
-d_{\Weil{}} &: E^{i,j} \to E^{i+1,j};
-\end{align*}
-we use the first as the derivative $d_0$ on the zeroth page, and the second to induce $d_1$.
-Combining them also yields a derivative $d = d_G + (-1)^j d_{\Weil{}}$ on the total complex
-\[
-E^n_G = \bigoplus_{i+j=n} E^{i,j}.
-\]
-The machinery of spectral sequences gives us a sequence of pages $E_r^{i,j}$, converging to a page $E_{\infty}^{i,j}$.
-We summarize the key properties of this spectral sequence in the following proposition.
-
-\begin{proposition} In the spectral sequence defined above,
-\begin{enumerate}
-\item the second page is given by $E_2^{i,j} = \Hh^i(\Weil{}, \Hh^j(G(\bFq), \EEx))$,
-\item there is an isomorphism $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) \cong \Hh^n(E_G^\bullet)$, and
-\item there is a filtration $\Hh^n(\Weil{} \ltimes G(\bFq), \EEx) = F_n \supset \cdots \supset F_{-1} = 0$, with $F_i / F_{i-1} \cong E_{\infty}^{i, n-i}$.
-\end{enumerate}
-\end{proposition}
-
-Moreover, since $\Weil{} \cong \ZZ$ has cohomological dimension $1$, $E_2^{i,j} = 0$ for $i > 1$ and the
-sequence degenerates at the second page: $E_{\infty}^{i,j} = E_2^{i,j}$. We obtain the following corollary:
-
-\begin{corollary}\label{cor:spectral_ses}
-There is a short exact sequence
- \[
-    0 \to
-    \Hh^0(\Weil{},\Hh^2(\bG,\EEx)) \to
-    \Hh^2(E^\bullet_G) \to
-    \Hh^1(\Weil{},\Hh^1(\bG,\EEx)) \to
-    0.
- \]
-\end{corollary}
-
-This sequence will play a key role in understanding the kernel of $\TrFrob{G}$, as described in the next few sections.
-For this application, we need a good understanding of these maps to and from the total complex.
-
-\begin{proposition} \label{prop:ses_desc}
-Consider the short exact sequence in Corollary~\ref{cor:spectral_ses}.
-\begin{enumerate}
-\item Every class $[\alpha\oplus\beta\oplus\gamma] \in \Hh^2(E^\bullet_G)$ is cohomologous to one with $\gamma=0$.
-\item The map $\Hh^2(E^\bullet_G) \to \Hh^1(\Weil{},\Hh^1(\bG,\EEx))$ is given by $[\alpha\oplus\beta\oplus 0] \mapsto [\beta]$.
-\item Suppose $a \in Z^2(\bG, \EEx)$ represents a class in $\Hh^2(\bG,\EEx)$ fixed by Frobenius.
-The map $\Hh^0(\Weil{},\Hh^2(\bG,\EEx)) \to \Hh^2(E^\bullet_G)$ is given by $[a] \mapsto [a \oplus 0 \oplus 0]$.
-\end{enumerate}
-\end{proposition}
-\begin{proof}
-Since $\Hh^2(\Weil{}, C^0(\bG, \EEx)) = 0$, we may find a $\gamma_1 \in C^1(\Weil{}, C^0(\bG, \EEx))$ with $d_{\Weil{}}\gamma_1 = \gamma$.
-Subtracting $d \gamma_1$ from $\alpha\oplus\beta\oplus\gamma$, we may assume that $\gamma = 0$.
-
-The latter two claims follow from tracing through the definition of latter pages in the spectral sequence.
-\end{proof}
-
-\subsection{From character sheaves to the total complex}\label{ssec:S}
-
-Let $G$ be a smooth commutative group scheme over $\Fq$.
-In this section we define a group homomorphism
-\[
-S_G : \CSiso{G} \to \Hh^2(E^\bullet_G).
-\] 
-Let $\cs{L} = (\gcs{L},\mu,\phi)$ be a character sheaf on $G$.
-For each geometric point $x\in \bG$, choose a basis $\{ v_x \}$ for $\gcs{L}_x$.
-Through this choice, $\cs{L}$ determines functions
-\begin{align*}
-a : \bG\times \bG &\to \EEx & b : \bG &\to \EEx \\
-\mu_{x,y}(v_{x+y}) &= a(x,y) v_x \otimes v_y & \phi_x(v_{\Frob{G}(x)}) &= b(x) v_x.
-\end{align*}
-Condition~\ref{CS.2} implies that
-\begin{equation}\label{2-cocyle}
-a(x+y,z) a(x,y) = a(x,y+z) a(y,z)
-\end{equation}
-for all $x,y,z\in \bG$, so $a \in Z^2(\bG,\EEx)$.  Similarly, condition~\ref{CS.3} gives
-\begin{equation}\label{eq:nohom}
-\frac{a(\Frob{G}(x),\Frob{G}(y))}{a(x,y)} =  \frac{b(x+y)}{b(x) b(y)}
-\end{equation}
-for $x, y \in \bG$.
-Let $\alpha \in C^0(\Weil{},C^2(\bG,\EEx)$ be the $0$-cochain corresponding to $a$ and let $\beta\in C^1(\Weil{},C^1(\bG,\EEx)$
-be the cocycle such that $\beta(\Frob{})$ is $b$.  We will write both $\alpha$ and $\beta$ additively.
-Then
-\[
-d_G\alpha =0, \qquad\qquad
-d_{\Weil{}} \alpha = d_{G} \beta,\qquad\qquad
-d_{\Weil{}} \beta =0;
-\]
-in other words,
-\[\alpha\oplus \beta \in Z^2(E^\bullet_G).\]
-Although the cocycle $\alpha\oplus \beta$ is not well defined by $\cs{L}$, its class in $\Hh^2(E^\bullet_G)$ is.
-To see this, let $\{ v'_x \in \gcs{L}_x^\times \tq x \in \bG\}$ be another choice and let $\alpha'\oplus \beta' \in Z^2(E^\bullet_G)$
-be defined by $\cs{L}$ and this choice, as above.
-Now let $\delta \in C^0(\Weil{},C^1(\bG,\EEx))$ correspond to the function $d : \bG\to \EEx$ defined by $v'_x = d(x) v_x$.
-Chasing through \ref{CS.2} and \ref{CS.3}, we find
-\[
-\alpha'\oplus\beta' = \alpha\oplus\beta + d\delta,
-\]
-so the class $[\alpha\oplus\beta]$ of $\alpha\oplus\beta$ in $\Hh^2(E^\bullet_G)$ is independent of the choice made above.
-It is also easy to see that $[\alpha\oplus\beta] = [\alpha_0\oplus\beta_0]$ when $\cs{L} \iso \cs{L}_0$,
-which concludes the definition of the function
-\begin{align*}
-S_G : \CSiso{G} &\to \Hh^2(E^\bullet_G)\\
-[\cs{L}] &\mapsto [\alpha\oplus \beta].
-\end{align*}
-It is also easy to see that $[\alpha_1\oplus\beta_1] + [\alpha_2\oplus\beta_2] = [\alpha_3\oplus\beta_3]$
-when $\cs{L}_3 = \cs{L}_1\otimes \cs{L}_2$, so $S_G$ is a group homomorphism.
-
-\begin{proposition}\label{prop:SGiso}
-If $G$ is \'etale then $S_G:  \CSiso{G} \to \Hh^2(E^\bullet_G)$ is an isomorphism.
-\end{proposition}
-\begin{proof}
-Suppose $[\cs{L}] \in \CSiso{G}$ with $S_G([\cs{L}]) = [\alpha \oplus \beta] = 0$,
-so that $\alpha \oplus \beta = d\sigma$ for some $\sigma \in C^0(\Weil{},C^1(\bG,\EEx) = C^1(\bG,\EEx)$.
-For each $x\in \bG$, define $\sigma_x : \gcs{L}_x \to \EE$ by $\sigma_x : v_x \mapsto \sigma(x)$.
-Then the indexed set of isomorphisms $\{ \sigma_x : \gcs{L}_x \to \EE \tq x\in \bG\}$
-defines an isomorphism $\cs{L} \to (\EE)_G$.
-Since $\cs{L} = 0 \in \CSiso{G}$, $S_G$ is injective.
-
-To see that $S_G$ is surjective, begin with $\alpha\oplus\beta\oplus 0 \in Z^2(E^\bullet_G)$.
-Since $d_{\Weil{}} \beta = 0$, we may define $a = \alpha \in C^2(\bG,\EEx)$ and
-$b = \beta(\Frob{}) \in C^1(\bG,\EEx)$, which are related to $\alpha$ and $\beta$ as above.
-Set $\gcs{L}_x = \EE$, define $\mu_{x,y} : \gcs{L}_{x+y} \to \gcs{L}_x\otimes\gcs{L}_y$
-by $\mu_{x,y}(1) = a(x,y) (1\otimes 1)$ and $\phi_x : \gcs{L}_{\Frob{G}(x)} \to \gcs{L}_x$ by $\phi_x(1)= b(x)$.
-Then \ref{CS.1} holds since $d_G \alpha =0$ and \ref{CS.2} holds since $d_{\Weil{}}\alpha =d_G \beta$.
-Tracing the construction backward, we have defined a character sheaf $\cs{L}$ on $G$ with
-$S_G(\cs{L}) = [\alpha\oplus\beta\oplus 0]$, showing that $S_G$ is surjective.
-\end{proof}
-
-\subsection{Objects in the \'etale case}\label{ssec:SandT}
-
-In this section we fit the group homomorphisms $\TrFrob{G}$ and $S_G$ into a commutative diagram,
-determining the kernel and cokernel of $\TrFrob{G}$ when $G$ is an \'etale commutative group scheme over $\Fq$.
-We begin with a simple, general result relating duals, invariants and coinvariants.
-
-\begin{lemma} \label{lem:dual-inv}
-Let $X$ be an abelian group equipped with an action of $\Weil{}$.  Then
-\begin{align*}
- (X^*)_{\Weil{}} &\to (X^{\Weil{}})^* \\
- [f] &\mapsto f|_{X^{\Weil{}}}
-\end{align*}
-is an isomorphism.
-\end{lemma}
-
-\begin{proof}
-We can describe $X^{\Weil{}}$ as the kernel of the map $X \xrightarrow{\Frob{}-1} X$;
-let $Y = (\Frob{}-1)X$ be the augmentation ideal.  Dualizing the sequence
-\[
- 0 \to X^{\Weil{}} \to X \to Y \to 0
-\]
-yields
-\[
- 0 \to Y^* \to X^* \to (X^{\Weil{}})^* \to \Ext^1_\ZZ(Y, \EEx).
-\]
-Since $\Ext^1_\ZZ(-,\EEx)$ vanishes, we get a natural isomorphism from the cokernel of $Y^* \xrightarrow{\Frob{}-1} X^*$ to $(X^{\Weil{}})^*$.
-\end{proof}
-
-\begin{proposition}\label{prop:sur_etale}
-If $G$ is \'etale, then $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ is surjective
-and split.
-\end{proposition}
-\begin{proof}
-Pick $\chi \in G(\Fq)^*$. 
-Let $[\beta]\in \Hh^1(\Weil{},\bG^*)$ be the class corresponding to $\chi$ under Lemma~\ref{lem:dual-inv}.
-Every representative cocycle $\beta \in Z^1(\Weil{},\bG^*)$ determines a homomorphism
-$\beta(\Frob{}) : G(\bFq)\to \EEx$ such that $\beta(\Frob{})\vert_{G(\Fq)} = \chi$.
-Set $\gcs{L}_x = \EE$ for every $x\in G(\bFq)$.
-Define $\mu_{x,y} : \gcs{L}_{x+y} \to \gcs{L}_x\otimes \gcs{L}_y$ by $\mu_{x,y}(1) = 1 \otimes 1$ and
-$\phi_{x} : \gcs{L}_{\Frob{}(x)} \to \gcs{L}_x$ by $\phi_{x}(1) = \beta(\Frob{})(x)$.
-Since $\beta(\Frob{}) : G(\bFq) \to \EEx$ is a group homomorphism,
-condition \eqref{eq:nohom} is satisfied with $a =1$.
-So $\cs{L} = (\gcs{L}, \mu, \phi)$
-is a character sheaf with $\trFrob{\cs{L}} = \chi$.
-This shows that $\TrFrob{G}$ is surjective.
-
-Now let $\beta' \in Z^1(\Weil{},\bG^*)$ be another representative for $[\beta]$
-so $\beta-\beta' = d_{\Weil{}} \delta$ for some $\delta \in C^0(\Weil{},\bG^*)$ defining $d \in \Hom(G(\bFq),\EEx)$.
-Let $\cs{L}'$ be the character sheaf on $G$ defined by $\beta'$, as above.
-For each $x\in G(\bFq)$, define $\brho_x :\cs{L}_x\to \cs{L}'_x$ by $\brho_x(1) = d(x)$.
-The collection of isomorphisms $\{ \brho_x \tq x\in G(\bFq)\}$ satisfies condition~\ref{CS.4},
-so it defines a morphism $\rho : \cs{L}\to \cs{L}'$, which is clearly an isomorphism. 
-We have now defined a section of $\TrFrob{G}$.
-
-Now suppose $\chi_1, \chi_2 \in G(\Fq)^*$. Pick cocycles $\beta_1,\beta_2\in Z^1(\Weil{},\bG^*)$ and
-construct character sheaves $\cs{L}_1$ and $\cs{L}_2$ on $G$ as above. Since $\cs{L}_1\otimes \cs{L}_2$
-is exactly the character sheaf built from the cocycle $\beta_1\cdot \beta_2$, and since
-$\trFrob{\cs{L}_1\otimes \cs{L}_2} = \trFrob{\cs{L}_1}\cdot \trFrob{\cs{L}_2}$, the section of $\TrFrob{G}$ defined here is a homomorphism.
-\end{proof}
-
-\begin{proposition} \label{prop:etale-iso}
- If $G$ is \'etale then the map $S_G : \CSiso{G}\to \Hh^2(E^\bullet_G)$ induces an isomorphism of split short exact sequences
-\[
-\begin{tikzcd}
- 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \CSiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
-  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\bG,\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1(\bG,\EEx)) \arrow{r} & 0.
- \end{tikzcd}
- \]
-\end{proposition}
-\begin{proof}
-This result follows from Propositions~\ref{prop:ses_desc}, \ref{prop:SGiso} and \ref{prop:sur_etale}.
-\end{proof}
-
-\begin{definition}
-We call a character sheaf $\cs{L}$ on $G$ \emph{invisible} if it is nontrivial and $\TrFrob{G}(\cs{L}) = 1$.
-\end{definition}
-
-The proposition gives a method for determining whether a given $G$ admits invisible character sheaves.
-
-\begin{remark} \label{rem:H2}
-Recall the K\"unneth formula in group cohomology \cite{brown:CohomologyGrps}*{Prop. I.0.8}:
-if $A$ and $A'$ are groups and $M$ and $M'$ are abelian groups with $M$ $\ZZ$-free, then
-\[
-\Hh^n(A \times A', M \otimes M') \cong \bigoplus_{i+j=n} \Hh^i(A, M) \otimes \Hh^j(A', M') \ \ \oplus
-\bigoplus_{i+j=n+1} \Tor_1^{\ZZ}\left(\Hh^i(A, M), \Hh^j(A', M')\right).
-\]
-Now suppose $\bG = \ZZ^r \times \prod_{i = 1}^m \ZZ/N_i\ZZ$ is an arbitrary finitely generated abelian group,
-with $N_i \mid N_{i+1}$.  Then the K\"unneth formula implies that
-\begin{equation} \label{eq:H2comp}
-\Hh^2(\bG, \EEx) \cong \left(\EEx\right)^{r(r-1)/2} \times \prod_{i=1}^m (\ZZ/N_i\ZZ)^{m+r-i}.
-\end{equation}
-We see that $\Hh^2(\bG, \EEx)$ is trivial if and only if $\bG$ is cyclic.  Of course, $\Hh^0(\Weil{}, \Hh^2(\bG, \EEx))$
-may or may not be trivial, even when $\Hh^2(\bG, \EEx)$ is non-trivial.
-\end{remark}
-
-\begin{example}\label{eg:H2}
-Consider the simplest non-trivial case, where $\bG = \{1, i, j, k\} \cong \ZZ/2\ZZ \times \ZZ/2\ZZ.$  Using \eqref{eq:H2comp},
-we have $\Hh^2(\bG, \EEx) \cong \ZZ/2\ZZ$, on which $\Weil{}$ must act trivially, regardless of its action on $\bG$ itself.
-The non-trivial element corresponds to the extension
-\begin{equation} \label{eq:Qdef}
-1 \to \EEx \to Q \to \bG \to 1,
-\end{equation}
-where $Q = \{c + c_ii + c_jj + c_kk \tq c,c_i,c_j,c_k \in \EE \mbox{ with exactly one nonzero}\}$ is a subgroup of the quaternion algebra over $\EE$.
-Let $a$ be a $2$-cocycle corresponding to this extension, with values in $\{\pm 1\}$. When $\Frob{G}$ acts trivially on $\bG$,
-any homomorphism $b : \bG \to \EEx$ will satisfy \eqref{eq:nohom}, and the corresponding
-$\alpha \oplus \beta$ are non-cohomologous in $\Hh^2(E_G^\bullet)$.
-When $\Frob{G}$ exchanges $i$ and $j$, then we may take $b(1) = 1, b(i) = -1$ and $b(j) = b(k) = \pm 1$, up to coboundaries.
-Finally, when $\Frob{G}$ cycles $i$, $j$ and $k$, any homomorphism $b : \bG \to \EEx$ will satisfy \eqref{eq:nohom},
-but now the corresponding $\alpha \oplus \beta$ are all cohomologous in $\Hh^2(E_G^\bullet)$.  In each case, we may produce
-an explicit character sheaf from the listed $a$ and $b$.
-
-Note that these character sheaves arise from discrete isogenies, as in Section \ref{ssec:discrete_isogenies}.
-Let $\bH$ be the quaternion group of order $8$: the subgroup of $Q$ with $c, c_i, c_j, c_k \in \{\pm 1\}$.
-The sequence \eqref{eq:Qdef} is the pushforward of
-\[
-1 \to \{\pm 1\} \to \bH \to \bG \to 1
-\]
-along the inclusion $\{\pm 1\} \hookrightarrow \EEx$.  Note that these character sheaves arise from a non-commutative cover of $\bG$,
-justifying the inclusion of such covers in the definition of a discrete isogeny.
-\end{example}
-
-\subsection{On the necessity of working with Weil sheaves}\label{ssec:bS}
-
-In this section we justify the appearance of Weil sheaves in Definition~\ref{def:CS}.
-
-\begin{proposition}\label{prop:bounded-etale}
-Let $G$ be a commutative \'etale group scheme over $\Fq$.
-Then the image of $\bCS(G)$ under $\TrFrob{G} : \CS(G) \to G(\Fq)^*$ is $\Hom(G(\Fq),\ZEx)$.
-\end{proposition}
-
-\begin{proof}
-Objects in $\bCS(G)$ may be described by a small modification to the technique used in Sections~\ref{ssec:E} and \ref{ssec:S}. 
-Set $F^{i,j} \ceq C^i_{\text{cts}} (\Gal(\bFq/\Fq), C^j(G(\bFq), \EEx))$.
-Then the results of Section~\ref{ssec:E} adapt to give a short exact sequence in continuous Galois cohomology
- \[
-    0 \to
-    \Hh^0(\Fq,\Hh^2(\bG,\EEx)) \to
-    \Hh^2(F^\bullet_G) \to
-    \Hh^1(\Fq,\Hh^1(\bG,\EEx)) \to
-    0,
- \]
-for which the maps are given by the analogues of Proposition~\ref{prop:ses_desc}.
-Moreover, using \cite{deligne-katz:SGA7.2}*{Expos\'e XIII, Rappel 1.1.3} we see that Proposition~\ref{prop:SGiso}
-adapts to provide an isomorphism $\bCSiso{G}\to \Hh^2(F^\bullet_G)$ compatible with $\bCS(G) \to \CS(G)$ and with the
-the canonical map of exact sequences 
- \[
-\begin{tikzcd}
-    0 \arrow{r} &
-    \Hh^0(\Fq,\Hh^2(\bG,\EEx)) \arrow{r} \arrow{d} &
-    \Hh^2(F^\bullet_G) \arrow{r} \arrow{d} &
-    \Hh^1(\Fq,\Hh^1(\bG,\EEx)) \arrow{r} \arrow{d} &
-    0
-\\
-    0 \arrow{r} & 
-    \Hh^0(\Weil{},\Hh^2(\bG,\EEx)) \arrow{r} & 
-    \Hh^2(E^\bullet_G) \arrow{r} & 
-    \Hh^1(\Weil{},\Hh^1(\bG,\EEx)) \arrow{r} &
-    0.
-\end{tikzcd}
- \]
-In this way, Proposition~\ref{prop:bounded-etale} is now reduced to the claim
-\[
-\Hh^1(\Fq,\Hh^1(\bG,\EEx)) = \Hom(G(\Fq),\ZEx).
-\]
-To see that, one may argue as follows. 
-Pick $i\in \pi_0(G)$ and let $G^i \hookrightarrow G$ be the corresponding connected component. 
-Pick a geometric point $x$ on $G^i$ and observe that since $G^i$ is connected as a $\Fq$-scheme,
-$G^i(\bFq)$ is canonically identified with the $\Gal(\bFq/\Fq)$-orbit of $x$. 
-We remark that while $G^i$ is defined over $\Fq$, the set $G^i(\Fq)$ is non-empty only when $G^i(\bFq) = \{ x\}$.
-Since $\Hh^1(\bG,\EEx) = \Hom(\bG,\EEx)$, evaluation $\chi \mapsto \chi(x)$ defines $\Hh^1(\Fq,\Hh^1(\bG,\EEx)) \to \Hh^1(\Fq,\EEx)$. 
-By continuity, $\Hh^1(\Fq,\EEx) = \Hh^1(\Fq,\ZEx)$.
-Letting $i$ range over $\pi_0(G)$ we conclude that $\Hh^1(\Fq,\Hh^1(\bG,\EEx)) = \Hh^1(\Fq,\Hh^1(\bG,\ZEx))$.
-When adapted to abelian groups with continuous action of $\Gal(\bFq/\Fq)$, the strategy of the proof of
-Lemma~\ref{lem:dual-inv} gives $\Hh^1(\Fq,\Hh^1(\bG,\ZEx)) =  \Hom(G(\Fq),\ZEx)$, concluding the proof.
-\end{proof}
-
-Proposition~\ref{prop:bounded-etale} reveals the necessity of working with Weil sheaves in Definition~\ref{def:CS}:
-one cannot geometrize all characters of $G(\Fq)$ using local systems on $G$, for general smooth commutative groups schemes $G$.
-Proposition~\ref{prop:bounded-etale} is extended to all smooth commutative groups schemes in Section~\ref{ssec:revisited}.
-
-\begin{example}\label{eg:}
-Consider the case when $G$ is the \'etale group scheme $\ZZ$ over $\Fq$ with $\Frob{G}$ trivial.
-If $\chi : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi(1) = \ell$
-and if $\cs{L}$ is a character sheaf on $G$ in the isomorphism class
-corresponding to $\chi$ under Proposition~\ref{prop:sur_etale},
-then $\cs{L}$ does not descend to $G$, since the image of $\chi$ is not
-bounded.
-If $\chi' : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi'(1) = 1+\ell$ and if $\cs{L}'$
-corresponds to $\chi'$ under Proposition~\ref{prop:sur_etale},
-then $\cs{L}'$ does descend to $G$, since the image of $\chi'$ is
-bounded.
-However, $\cs{L}'$ is not defined by a discrete isogeny (\S \ref{ssec:discrete_isogenies}). 
-If $\chi'' : \ZZ \to \EEx$ is the character of $G(\Fq)$ determined by $\chi''(1) = \zeta$, a root of unity in
-$\EEx$, and if $\cs{L}''$ corresponds to $\chi''$ under Proposition~\ref{prop:sur_etale},
-then $\cs{L}''$ is defined by a discrete isogeny. 
-\end{example}
-
-\subsection{Morphisms in the \'etale case}\label{ssec:mor-etale}
-
-A complete understanding of the morphisms in $\CS(G)$ also requires a description of the
-automorphisms of an arbitrary character sheaf $\cs{L}$.
-
-\begin{proposition}\label{prop:autornaught_etale}
-Let $G$ be an \'etale commutative group scheme over $\Fq$.
-If $\cs{L}$ and $\cs{L}'$ are character sheaves on $G$ then
-every $\rho\in \Hom(\cs{L},\cs{L}')$ is either trivial or an isomorphism. Moreover, the trace map induces an isomorphism of groups
-\[
-\Aut(\cs{L}) \to \Hom(G(\bFq)_{\Weil{}}, \EEx).
-\]
-\end{proposition}
-
-\begin{proof}
-We have already seen, in Lemma~\ref{lem:autornaught}, that every $\rho\in \Hom(\cs{L},\cs{L}')$ is either trivial or an isomorphism.
-Now suppose $\rho \in \Aut(\cs{L})$.
-The second diagram in \ref{cs.4} shows that the association $x \mapsto \brho_x$ is a homomorphism
-from $G(\bFq)$ to $\EEx$ and the first diagram in \ref{cs.4} shows that it factors through $G(\bFq) \to G(\bFq)_{\Weil{}}$.
-
-Conversely, if $\rho : G(\bFq)_{\Weil{}} \to \EEx$ is any homomorphism, then defining $\brho_x$ as multiplication
-by $\rho(x)$ will define a morphism $\gcs{L} \to \gcs{L}'$ satisfy the two diagrams in \ref{cs.4}.
-
-Composition of morphisms corresponds to pointwise multiplication in this correspondence, showing that the
-resulting bijection is actually a group isomorphism.
-\end{proof}
-
-\section{Character sheaves on smooth commutative group schemes over finite fields}\label{sec:main}
-
-\subsection{Restriction to the identity component} \label{ssec:restriction}
-
-Consider the short exact sequence
-defining the component group scheme for $G$:
-\begin{equation}\label{eq:pi0}
-\begin{tikzcd}
-0 \rar & G^0 \arrow{r}{\iota_0} & G \arrow{r}{\pi_0} & \pi_0(G) \rar & 0.
-\end{tikzcd}
-\end{equation}
-Since $\pi_0(G)$ is an \'etale commutative group scheme -- and thus smooth --
-Lemma~\ref{lem:pullback} implies that \eqref{eq:pi0} defines a sequence of functors
-\begin{equation}\label{eq:pi1}
-\begin{tikzcd}
-\CS(0) \rar & \CS(\pi_0(G)) \arrow{r}{\pi_0^*} & \CS(G) \arrow{r}{\iota_0^*} & \CS(G^0) \rar & \CS(0)
-\end{tikzcd}
-\end{equation}
-and therefore, after passing to isomorphism classes, a sequence of abelian groups
-\begin{equation}\label{eq:pi2}
-\begin{tikzcd}
-0 \rar &
-\CSiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \CSiso{G} \arrow{r}{\iota_0^*} & \CSiso{G^0} \rar & 0.
-\end{tikzcd}
-\end{equation}
- Note that we found the groups $\CSiso{\pi_0(G)}$ and $\CSiso{G^0}$
-in Sections~\ref{ssec:SandT} and \ref{ssec:connected}, respectively.
-We will shortly see that \eqref{eq:pi2} is exact.
-
-\begin{lemma}\label{lemma:ext}
-Every discrete isogeny to $G^0$ extends to a discrete
-isogeny to $G$ inducing an isomorphism on component groups.
-\end{lemma}
-
-\begin{proof}
-Let $\pi: B \to G^0$ be a discrete isogeny, and set $A \ceq \ker \pi$.
-  We will find a discrete isogeny $f: H\to G$
-  such that that $H^0 = B$, $f^0 =\pi$ and
-  $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism of component
-  groups.  Namely, we will fit $\pi$ into the following diagram,
-  \begin{equation}\label{extension-diagram}
-  \begin{tikzcd}
-  A \arrow{r} \dar & A \dar \\
-  B \rar \dar[swap]{\pi} & H \rar \dar[swap]{f} & \pi_0(H) \arrow{d}[below,rotate=90]{\sim}[swap]{\pi_0(f)} \\
-  G^0 \rar & G \rar & \pi_0(G),
-  \end{tikzcd}
-  \end{equation}
-  where all rows and columns are exact and all maps are defined over
-  $\Fq$.  We will do so by passing back and forth between group
-  schemes over $\Fq$ and their $\bFq$-points.
-
-  Extensions of $G^0(\bFq)$ by $A(\bFq)$ with $\Weil{}$-equivariant maps, such as $B(\bFq)$,
-  correspond to classes in $\Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq))$.
-  Similarly, extensions of $G(\bFq)$ by $A(\bFq)$ with $\Weil{}$-equivariant maps correspond to
-  classes in $\Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq))$.  The map
-  $G^0(\bFq) \to G(\bFq)$ induces a homomorphism
-  \[
-  \Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq))
-  \]
-  fitting into the long exact sequence 
-  \[
-  \Ext^1_{\ZZ[\Weil{}]}(G(\bFq), A(\bFq)) \to \Ext^1_{\ZZ[\Weil{}]}(G^0(\bFq), A(\bFq)) \to \Ext^2_{\ZZ[\Weil{}]}(\pi_0(G)(\bFq), A(\bFq))
-  \]
-  derived from applying
-  the functor $\Hom(\mbox{---}, A(\bFq))$ to $G^0(\bFq) \to G(\bFq) \to \pi_0(G)(\bFq)$.
-  Since $\Weil{} \cong \ZZ$ has cohomological dimension $1$ \cite{brown:CohomologyGrps}*{Ex. 4.3},
-  $\Ext^2_{\ZZ[\Weil{}]}(\pi_0(G)(\bFq), A(\bFq))$ vanishes \cite{cartan-eilenberg:HomologicalAlgebra}*{Thm. 2.6}.
-
-  We therefore have the existence of diagram \eqref{extension-diagram}
-  at the level of $\bFq$-points.  This expresses $H(\bFq)$ as a
-  disjoint union of translates of $B(\bFq)$; by transport of structure
-  we may take $H$ to be a group scheme over $\bFq$.  Similarly, the
-  restriction of $f$ to each component of $H$ is a morphism of
-  schemes, and thus $f$ is as well.  Finally, the whole diagram
-  descends to a diagram of $\Fq$-schemes since the $\bFq$-points of
-  the objects come equipped with continuous $\Gal(\bFq/\Fq)$-actions and the
-  morphisms are $\Gal(\bFq/\Fq)$-equivariant.
-\end{proof}
-
-We now wish to apply the results of Section~\ref{ssec:connected} to the identity component of $G$,
-for which we must confirm that the identity component of $G$ is actually an algebraic group over $\Fq$.
-
-\begin{lemma} \label{lem:G0alg-grp}
-If $G$ is a commutative smooth group scheme over $\Fq$ then its identity component, $G^0$, is a connected algebraic group over $\Fq$.
-\end{lemma}
-\begin{proof}
- Since $G$ is a smooth group scheme over $\Fq$, its
- identity component $G^0$ is a connected smooth,
- group scheme of finite type over $\Fq$, reduced over some finite extension of $\Fq$
- \cite{vdGeer-Moonen:AbelianVarieties}*{3.17}.
- Since $\Fq$ is a finite field and hence perfect, $G^0$ is actually reduced over $\Fq$
- \cite{EGAIV2}*{Prop 6.4.1}.  Since every group scheme over a field is separated
- \cite{vdGeer-Moonen:AbelianVarieties}*{3.12},
- it follows that $G^0$ is a connected algebraic group.
-\end{proof}
-
-\begin{proposition}\label{prop:restriction}
-The restriction functor $\iota_0^* : \CS(G)\to \CS(G^0)$ is essentially surjective.
-\end{proposition}
-
-\begin{proof}
-  By Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}, every
-  character sheaf on $G^0$ is isomorphic to $(\pi_! \EE)_\psi$ for some discrete isogeny $\pi : B \to G^0$ and character $\psi : \ker \pi \to \EEx$.
-  So to prove the proposition it suffices to show that $(\pi_! \EE)_\psi$ extends to a character sheaf on $G$.
- By Lemma~\ref{lemma:ext}, there is an extension of the
- discrete isogeny $\pi : B \to G^0$ to a discrete isogeny $f : H \to G$
- such that $\pi_0(f) : \pi_0(H)\to \pi_0(G)$ is an isomorphism.
- Then $(f_! \EE)_\psi$ is a character sheaf on $G$ and
- $(f_! \EE)_\psi\vert_{G^0} \iso (\pi_! \EE)_\psi$.
-\end{proof}
-
-\subsection{The component group sequence} \label{ssec:component}
-
-\begin{lemma}\label{lem:extension}
-The group homomorphism $\pi_0^*: \CSiso{\pi_0(G)} \to \CSiso{G}$ is injective.
-\end{lemma}
-\begin{proof}
-Let $\cs{L}$ be a character sheaf on $\pi_0(G)$ and let $\rho : \pi_0^*\cs{L} \to (\EE)_{G}$ be an isomorphism in $\CS(G)$. 
-For each $x\in \pi_0(\bG)$, set $\bG^x \ceq \pi_0^{-1}(x)$.
-The restriction $\pi_0^*\gcs{L}\vert_{\bG^x}$ is the constant sheaf $(\gcs{L}_x)_{\bG^x}$ so the isomorphism
-$\brho\vert_{\bG^x} : (\gcs{L}_x)_{\bG^x} \to (\EE)_{\bG^x}$ determines an isomorphism $\brho_x : \gcs{L}_x \to (\EE)_x$.
-The collection $\{ \brho_x \tq x\in \pi_0(\bG) \}$ determines an isomorphism $\cs{L} \to (\EE)_{\pi_0(G)}$  in $\CS(\pi_0(G))$.
-\end{proof}
-
-\begin{proposition}\label{prop:middleexact}
- The sequence
- \[
-  \begin{tikzcd}
-  0 \rar & \CSiso{\pi_0(G)} \arrow{r}{\pi_0^*} & \CSiso{G} \arrow{r}{\iota_0^*} & \CSiso{G^0} \rar & 0.
-  \end{tikzcd}
- \]
- is exact.
-\end{proposition}
-
-\begin{proof}
-Exactness at $\CSiso{G^0}$ follows from Proposition~\ref{prop:restriction},
-and exactness at $\CSiso{\pi_0(G)}$ from Lemma~\ref{lem:extension}.
-Here we show that it is also exact at $\CSiso{G}$.
-First note that $\iota_0^* \circ \pi_0^*$ is trivial by Lemma~\ref{lem:pullback}.
-So it suffices to show that if $\cs{L} = (\gcs{L},\mu,\phi)$ is a character sheaf on $G$
-with $\cs{L}\vert_{G^0} = (\EE)_{G^0}$ then $\cs{L}$ is in the essential image of $\pi_0^*$.
-
-As above, set $\bG^x \ceq \pi_0^{-1}(x)$ for $x\in \pi_0(\bG)$.
-Let $g, g'$ be geometric points in the same
-geometric connected component $\bG^x$.
-Set $a = g^{-1}g'$ and note that $a$ is a geometric point in $\bG^0$.
-Let $\mu_{g,a} : \gcs{L}_{ga} \to \gcs{L}_g \otimes \gcs{L}_a$
-be the isomorphism of vector spaces obtained by restriction of
-$\mu : m^*\gcs{L} \to \gcs{L} \boxtimes \gcs{L}$ to the
-geometric point $(g,a)$ on $\bG^x \times \bG^0$.
-Since $\cs{L}\vert_{G^0} = (\EE)_{G^0}$,
-the stalk of $\gcs{L}$ at $a$ is $\EE$.
-In this way the pair of geometric points $g, g' \in \bG^x$
-determines an isomorphism $\varphi_{g,g'} \ceq \mu_{g,a}^{-1}$
-from $\gcs{L}_{g}$ to $\gcs{L}_{g'}$.
-The isomorphisms $\varphi_{g,g'}: \gcs{L}_{g} \to \gcs{L}_{g'}$ are canonical
-in the following sense: if $g,g'\in \bG^x$ and $h,h'\in \bG^y$
-then it follows from \ref{CS.2} and \ref{CS.3}
-that
- \begin{equation}\label{eq:CS}
-  \begin{tikzcd}[column sep=40]
-   \gcs{L}_{gh} \arrow{r}{\varphi_{gh,g'h'}} \arrow[swap]{d}{\mu_{g,h}}
-  & \gcs{L}_{g'h'} \arrow{d}{\mu_{g',h'}}
-  &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}
-  &  \gcs{L}_{\Frob{}(g)} \arrow{r}{\varphi_{\Frob{}(g),\Frob{}(g')}} \arrow[swap]{d}{\phi_{g}} & \gcs{L}_{\Frob{}(g')} \arrow{d}{\phi_{g'}} \\
-  \gcs{L}_{g} \otimes \gcs{L}_{h} \arrow{r}{\varphi_{g,g'}\otimes \varphi_{h,h'}}
-  & \gcs{L}_{g'} \otimes \gcs{L}_{h'}
-  & {}
-  & \gcs{L}_{g} \arrow{r}{\varphi_{g,g'}} & \gcs{L}_{g'}
-  \end{tikzcd}
- \end{equation}
-both commute.
-
-For each $x\in \pi_0(\bG)$, pick $g(x)\in \bG^x$
-and set $\gcs{E}_x \ceq \gcs{L}_{g(x)}$.
-Let $\phi_x : \gcs{E}_{\Frob{}(x)} \to \gcs{E}_x$
-be the isomorphism of $\EE$-vector spaces obtained by composing
-$\varphi_{g(\Frob{}(x)),\Frob{}(g(x))} : \gcs{L}_{g(\Frob{}(x))} \to \gcs{L}_{\Frob{}(g(x))}$
-with $\phi_{g(x)} : \gcs{L}_{\Frob{}(g(x))} \to \gcs{L}_{g(x)}$.
-For each pair $x,y\in \pi_0(\bG)$
-let $\mu_{x,y} : \gcs{E}_{x+y}\to \gcs{E}_x\otimes \gcs{E}_y$
-be the isomorphism of $\EE$-vector spaces obtained by composing
-$\varphi_{g(x+y),g(x)g(y)} : \gcs{L}_{g(x+y)} \to \gcs{L}_{g(x)g(y)}$
-with $\mu_{g(x),g(y)} : \gcs{L}_{g(x)g(y)} \to \gcs{L}_{g(x)}\otimes \gcs{L}_{g(y)}$.
-Using \eqref{eq:CS}, it follows that \ref{CS.1}, \ref{CS.2} and \ref{CS.3} are satisfied for
-$\cs{E} \ceq (\gcs{E}_x, \mu_{x,y}, \phi_x)$, thus defining a character sheaf on $\pi_0(G)$.
-
-The pullback $\pi_0^*(\cs{E})$ of $\cs{E}$ along $\pi_0 : G \to \pi_0(G)$ is constant
-on geometric connected components, with stalks given by
-$(\pi_0^* \cs{E})_g = \cs{E}_{x}$ for all $g\in \bG^x$.  Thus both $\pi_0^*\cs{E}$ and $\cs{L}$
-are constant on geometric connected components of $G$.
-The choices above define isomorphisms
-$\gcs{L}\vert_{\bG^x} \to  (\gcs{E}_{x})_{\bG^x}$ for each $x\in \pi_0(\bG)$.
-The resulting isomorphism $\gcs{L} \to \pi_0^* \gcs{E}$ satisfies \ref{CS.4},
-thus defining an isomorphism $\cs{L} \to \pi_0^* \cs{E}$ in $\CS(G)$.
-\end{proof}
-
-\subsection{The dictionary}
-\label{ssec:snake}
-
-We saw in Proposition~\ref{prop:functorialG} that $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ is a functorial group homomorphism.
-In this section we find the image and kernel of $\TrFrob{G}$.
-
-\begin{theorem}\label{thm:snake}
-  If $G$ is a smooth commutative group scheme over $\Fq$ then
-  $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ is surjective and has kernel canonically isomorphic to $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$:
-    \[
-  \begin{tikzcd}
-0 \arrow{r} & \Hh^2(\pi_0(\bG),\EEx)^{\Weil{}} \arrow{r} & \CSiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0. 
-  \end{tikzcd}
-\]
-is an exact sequence.
-\end{theorem}
-
-\begin{proof}
-  Let
-  \begin{equation}\label{eq:pre-snake}
-  \begin{tikzcd}[row sep=20, column sep=20]
-    0 \rar & \CSiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
-    & \CSiso{G} \rar \dar{\TrFrob{G}} & \CSiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
-    0 \rar & \pi_0(G)(\Fq)^* \rar
-    &  G(\Fq)^* \rar & G^0(\Fq)^* \rar & 0
-  \end{tikzcd}
-  \end{equation}
-  be the commutative diagram of abelian groups obtained by applying
-  Lemma~\ref{lem:pullback} to \eqref{eq:pi0}.
-  The sequence of abelian groups
-\[
-  \begin{tikzcd}
-    1 \rar & G^0(\Fq) \rar & G(\Fq) \rar & \pi_0(G)(\Fq) \rar & 0,
-  \end{tikzcd}
-\]
-  is exact since $\Hh^1(\Fq,G^0) =0$ by Lemma~\ref{lem:G0alg-grp} and Lang's theorem on connected algebraic groups over finite fields \cite{lang:56a}.
-  Since $\EEx$ is divisible, $\Hom(\ - \ ,\EEx)$ is exact and thus the dual sequence of
-  character groups in \eqref{eq:pre-snake} is exact.
-  The upper row in \eqref{eq:pre-snake} is exact by Proposition~\ref{prop:middleexact}.
-  Now Lemma~\ref{lem:G0alg-grp} and Proposition~\ref{prop:connected}
-  imply that $\ker \TrFrob{G^0} =0$ and $\coker \TrFrob{G^0}=0$,
-  while Proposition~\ref{prop:etale-iso} gives $\ker \TrFrob{\pi_0(G)} \iso \Hh^0(\Weil{},\Hh^2(\pi_0(\bG),\EEx))$
-  and $\coker \TrFrob{\pi_0(G)}=0$.
-It now follows from the snake lemma
- \begin{equation}\label{eq:snake}
-  \begin{tikzcd}[row sep=20, column sep=15]
-    0 \arrow[dotted]{r} & \ker \TrFrob{\pi_0(G)} \arrow[dotted]{r} \dar & \arrow{d} \ker \TrFrob{G} \arrow[dotted]{r}
-    & \ker \TrFrob{G^0} =0 \arrow[dotted, out=-10, in=170]{dddll} \dar & \\
-    0 \rar & \CSiso{\pi_0(G)} \rar \dar{\TrFrob{\pi_0(G)}}
-    & \CSiso{G} \rar \dar{\TrFrob{G}} & \CSiso{G^0} \rar \dar{\TrFrob{G^0}} & 0\\
-    0 \rar & \pi_0(G)(\Fq)^* \rar \dar
-    & \arrow{d} G(\Fq)^* \rar & G^0(\Fq)^* \rar \dar & 0\\
-   &  \coker \TrFrob{\pi_0(G)} =0 \arrow[dotted]{r} & \coker \TrFrob{G} \arrow[dotted]{r} & \coker \TrFrob{G^0} =0 & 
-  \end{tikzcd}
-  \end{equation}
-that $\coker \TrFrob{G} =0$
-and $\ker \TrFrob{\pi_0(G)} \to \ker \TrFrob{G}$ is an isomorphism.
-This gives the promised short exact sequence
-\[
-  \begin{tikzcd}
-0 \arrow{r} & \Hh^2(\pi_0(\bG),\EEx)^{\Weil{}} \arrow{r} & \CSiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0. 
-  \end{tikzcd}
-\]
-\end{proof}
-
-\begin{remark}\label{rem:rats}
-Although $\TrFrob{\pi_0(G)}$ is split and $\TrFrob{G^0}$ is an isomorphism, we do not know if $\TrFrob{G}$ is split,
-in general. Surjectively of $\TrFrob{G}$ shows that every $\ell$-adic character of $G(\Fq)$ admits a geometrization,
-but without a splitting for $\TrFrob{G}$ we do not know how to make this geometrization canonical.
-\end{remark}
-
-\subsection{Descent, revisited}\label{ssec:revisited}
-
-We now extend Proposition~\ref{prop:bounded-etale} to all smooth commutative group schemes over $\Fq$.
-
-\begin{proposition} \label{prop:bounded}
-Let $G$ be a smooth commutative group scheme over $\Fq$. 
-Then $\cs{L}\in \CS(G)$ descends to $G$ if and only if $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ has bounded image.
-\end{proposition}
-\begin{proof} 
-By Lemma~\ref{lem:G0alg-grp}, the identity component $G^0$ is a connected algebraic group over $\Fq$. 
-It follows from Proposition~\ref{prop:connected} that the restriction of $\cs{L}$ to $G^0$ descends to $G$. 
-Also, since $G^0(\Fq)$ is finite, the image of $\trFrob{\cs{L}} : G(\Fq) \to \EEx$ is a finite subgroup and therefore has bounded image.  
-If $\chi \in G(\Fq)^*$ then there is some finite-image character $\chi_0$
-with the same restriction to $G^0(\Fq)$ since $G^0(\Fq)$ is lies inside the torsion part of
-the finitely generated abelian group $G(\Fq)$.  Therefore $\chi$ is bounded 
-if and only if $\chi \cdot \chi_0^{-1}$ is bounded.  But $\chi \cdot \chi_0^{-1}$ descends
-to a character of $\pi_0(G)$.
-Thus, it is enough to prove Corollary~\ref{prop:bounded}
-for \'etale group schemes $G$, which is done in Proposition~\ref{prop:bounded-etale}.
-\end{proof}
-
-Proposition~\ref{prop:bounded} shows that the full subcategory
-$\bCS(G) \subset \CS(G)$ is not an equivalence, for general smooth commutative group schemes $G$.
-Again we see the necessity of working with Weil sheaves in Definition~\ref{def:CS}.
-
-\subsection{Morphisms of character sheaves} \label{ssec:CSmor}
-
-\begin{theorem}\label{thm:autornaught}
-Let $G$ be a smooth commutative group scheme over $\Fq$.
-There is a canonical isomorphism
-\[
-\Aut(\cs{L}) \iso \Hom(\pi_0(\bG)_{\Weil{}},\EEx).
-\]
-\end{theorem}
-\begin{proof} 
-Fix $\cs{L} = (\gcs{L},\mu,\phi)$ and consider the group homomorphism from $\Aut(\cs{L})$ to $\Hom(\bG_{\Weil{}},\EEx)$
-defined in the proof of Proposition~\ref{prop:autornaught_etale}.
-This homomorphism is injective because morphisms of sheaves are determined by the linear transformations induced on stalks.  
-Homomorphisms in the image of $\Aut(\cs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ are continuous when $\bG$ is
-viewed as the base of the espace \'etal\'e attached to $\gcs{L}$.
-Since $\ell$ is invertible in $\Fq$, it follows that the image of $\Aut(\cs{L}) \to \Hom(\bG_{\Weil{}},\EEx)$ is contained in $\Hom(\pi_0(\bG_{\Weil{}}),\EEx)$. 
-We also have $\pi_0(\bG_{\Weil{}})=\pi_0(\bG)_{\Weil{}}$. 
-To see that $\Aut(\cs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ is surjective, begin with
-$\theta\in\Hom(\pi_0(\bG)_{\Weil{}},\EEx)$ and, for each $[x] \in \pi_0(\bG)_{\Weil{}}$ define
-$\bar\rho^y: \gcs{L}^y \to \gcs{L}^y$ by scalar multiplication by $\theta([x])\in \EEx$ for each $y\in [x]$.
-This defines an isomorphism $\bar\rho : \gcs{L}\to \gcs{L}$ of local systems on $\bG$ compatible with $\mu$ and $\phi$,
-and thus an isomorphism $\rho :\cs{L}\to \cs{L}$ which maps to $\theta$ under $\Aut(\cs{L}) \to \Hom(\pi_0(\bG)_{\Weil{}},\EEx)$.
-\end{proof}
-
-\subsection{The dictionary for commutative algebraic groups over finite fields}\label{ssec:alg_groups}
-
-Having extended the function--sheaf dictionary from connected commutative algebraic groups over $\Fq$ to smooth
-commutative group schemes $G$ over $\Fq$, we look back briefly to the case when $G$ is a commutative algebraic group. 
-Although Weil sheaves are not necessary in that case, the dictionary is still not perfect, generally.
-
-\begin{corollary}\label{cor:alg_groups}
-Let $G$ be a commutative algebraic group over $\Fq$.
-All character sheaves on $G$ descend to $G$: $\CS(G)$ is equivalent to $\bCS(G)$ (\S \ref{ssec:bS}).
-The trace of Frobenius determines a short exact sequence
-\[
-\begin{tikzcd}
-0 \arrow{r} & \Hh^2(\pi_0(\bG),\EEx)^{\Weil{}} \arrow{r} & \bCSiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0.
-\end{tikzcd}
-\]
-The group $\Hh^2(\pi_0(\bG),\EEx)^{\Weil{}}$ need not be trivial.
-\end{corollary}
-
-\begin{proof}
-Since $G(\Fq)$ is finite, the first statement follows from Propositions~\ref{prop:BG}
- and \ref{prop:bounded}. The second statement is then a consequence of Theorem~\ref{thm:snake}. 
- The third statement is justified by Example~\ref{eg:H2}.
- \end{proof}
-
-\begin{remark}\label{rem:Lusztig}
-Suppose $G$ is a commutative algebraic group over $\Fq$ appearing in the series of papers starting with \cite{lusztig:disconnected1}.
-Then $G$ is a commutative reductive algebraic group over $\Fq$ with cyclic component group scheme;
-such groups are extensions of finite cyclic groups by algebraic tori.
-Every Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:disconnected1}, is a character sheaf on $G$, in our sense,
-and vice versa.
-Moreover, since $\Hh^2(\pi_0(\bG),\EEx)=0$ by Remark~\ref{eg:H2}, it follows that each Frobenius-stable
-character sheaf on $G$ as in \cite{lusztig:disconnected1}, is determined by its trace of Frobenius, up to isomorphism. 
-\end{remark}
-
-\subsection{Base change}\label{ssec:basechange}
-
-When using character sheaves to study characters, it is useful to understand
-how character sheaves behave under change of fields.
-Let $k'$ be a finite extension of $k$. Then $k \hookrightarrow k'$ induces a group homomorphism
-$i_{k'/k} : G(k) \hookrightarrow G(k')$ and thus a homomorphism
-\begin{align*}
-i_{k'/k}^* : G(k')^* &\to G(k)^* \\
-\chi &\mapsto \chi\circ i_{k'/k}.
-\end{align*}
-We can interpret this operation on characters in terms of character sheaves:
-
-\begin{proposition} \label{prop:csbe}
-Set $G_{k'} \ceq G\times_\Spec{k} \Spec{k'}$ and let
-\[
-\CS(\Res_{k'/k}(G_{k'})) \xrightarrow{\iota^*} \CS(G)
-\]
-be the functor obtained by pullback along the canonical closed immersion 
-\[\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})\] of $k$-schemes.
-The following diagram commutes:
-\[
-\begin{tikzcd}
-\CSiso{\Res_{k'/k}(G_{k'})} \arrow[two heads]{r}{\iota^*} \dar[swap]{\TrFrob{\Res_{k'/k}(G_{k'})}} & \CSiso{G} \dar{\TrFrob{G}} \\
-G(k')^* \arrow[two heads]{r}{i_{k'/k}^*} & G(k)^*.
-\end{tikzcd}
-\]
-\end{proposition}
-\begin{proof}
-The closed immersion $\iota : G \hookrightarrow \Res_{k'/k}(G_{k'})$ is given by \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6}.
-Proposition~\ref{prop:csbe} follows immediately from Lemma~\ref{lem:pullback} together with the identifications
-\[
-\Res_{k'/k}(G_{k'})(k) \cong G_{k'}(k') \cong G(k')
-\]
-from the definitions of Weil restriction and base change.
-\end{proof}
-
-In the opposite direction, let $\Nm : G(k') \to G(k)$ be the norm map and consider the group homomorphism:
-\begin{align*}
-\Nm^* : G(k)^* &\to G(k')^* \\
-\chi &\mapsto \chi\circ \Nm.
-\end{align*}
-We can also interpret this operation in terms of character sheaves.
-
-If $\cs{L} \ceq (\gcs{L}, \mu, \phi)$ is a character sheaf on $G$, we define
-$\cs{L}' \ceq (\gcs{L}, \mu, \phi_{k'})$ on the base change
-$G_{k'}$ of $G$ to $k'$ by setting
-\[
-\phi_{k'} \ceq \phi \circ \Frob{G}^*(\phi) \circ \cdots \circ (\Frob{G}^{n-1})^*(\phi).
-\]
-The commutativity of the diagram (CS.3) for $\phi_{k'}$
-follows from the fact that $\Frob{G_{k'}} = \Frob{G}^n$.
-Note that we may also think about the construction of $\phi_{k'}$ from $\phi$
-as restricting the action $\varphi$ of $\Weil{k}$ on $\gcs{L}$,
-defined in Section~\ref{ssec:category}, to $\Weil{k'}$.
-
-\begin{proposition}\label{prop:basechange}
-With notation above,
-the rule $\nu_{k'/k}: (\gcs{L}, \mu, \phi) \mapsto (\gcs{L}, \mu, \phi_{k'})$
- defines a monoidal functor $\CS(G) \to \CS(G_{k'})$
- such that the following diagram commutes:
-\[
-\begin{tikzcd}[column sep=60]
-\CSiso{G} \rar{\nu_{k'/k}} \dar{\TrFrob{G}} & \CSiso{G_{k'}} \dar{\TrFrob{G_{k'}}} \\
-G(k)^*  \rar{\Nm^*} & G(k')^*.
-\end{tikzcd}
-\]
-\end{proposition}
-
-\begin{proof}
-Let $\cs{L} \ceq (\gcs{L}, \mu, \phi) \in \CS(G)$ and write $F$ for $\Frob{G}$.  For any $x \in G(k')$,
-we may compute the value of $\TrFrob{G_{k'}}(\nu_{k'/k}\cs{L})(x)= t_{\nu_{k'/k}\cs{L}}(x)$ as the trace of $\phi_{k'}$ on $\gcs{L}_x$,
-and the value of $\Nm^*(\TrFrob{G}(\cs{L}))(x)$ as the trace of $\phi$ on $\gcs{L}_{\Nm(x)}$.
-Applying \ref{CS.3} to the stalk of $\gcs{L}^{\boxtimes n}$ at the point $(x, \Frob{}(x), \ldots, \Frob{}^{n-1}(x))$ yields a diagram
-\[
-\begin{tikzcd}
-\gcs{L}_{\Nm(x)} \rar \dar{\phi_{\Nm(x)}} & \gcs{L}_{F(x)} \otimes \gcs{L}_{F^2(x)} \otimes \cdots \otimes \gcs{L}_x
-\dar{\phi_x \otimes (F^*\phi)_x \otimes \cdots \otimes ((F^{n-1})^*\phi)_x} \\
-\gcs{L}_{\Nm(x)} \rar & \gcs{L}_x \otimes \gcs{L}_{F(x)} \otimes \cdots \otimes \gcs{L}_{F^{n-1}(x)}.
-\end{tikzcd}
-\]
-Choose a basis vector $v$ for $\gcs{L}_{\Nm(x)}$ and write $v_0 \otimes v_1 \otimes \cdots \otimes v_{n-1}$ for the image of $v$ under the
-bottom map,
-for $v_i \in \gcs{L}_{\Frob{}^i(x)}$.  By \ref{CS.2}, $v$ maps to
-$v_1 \otimes v_2 \otimes \cdots \otimes v_0$ along the top of the diagram.
-Let $\alpha_i \in \EEx$ represent $((F^i)^*\phi)_x$ with respect to these bases and let $\alpha$ be
-the trace of $\phi_{\Nm(x)}$.  We may now equate the trace $\alpha$ of $\phi$ on $\gcs{L}_{\Nm(x)}$
-with the product $\alpha_0 \cdots \alpha_{n-1}$, which is the trace of $\phi_{k'}$ on $\gcs{L}_x$.
-\end{proof}
-
-Finally, let $G'$ be a smooth commutative group scheme over $k'$.
-We explain how to geometrize the canonical isomorphism between characters of $G'(k')$ and of $(\Res_{k'/k}G')(k)$.
-We may decompose the base change $(\Res_{k'/k}G')_{k'}$ of $\Res_{k'/k}G'$ to $k'$
-into a product of copies of $G'$, indexed by elements of $\Gal(k'/k)$:
-\[
-(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'.
-\]
-Since products and coproducts agree for group schemes we have a natural inclusion of $k'$-schemes
-\[
-G' \hookrightarrow (\Res_{k'/k}G')_{k'},
-\]
-mapping $G'$ into the summand corresponding to $1 \in \Gal(k'/k)$.  Composing $\nu_{k'/k}$
-from Proposition~\ref{prop:basechange} with pullback along this map yields a functor
-\[
-\rho : \CS(\Res_{k'/k}G') \to \CS(G').
-\]
-
-\begin{proposition}
-Let $k'/k$ be a finite extension and let $G'$ be a smooth commutative group scheme over $k'$.
-Then the functor 
-\[
-\rho : \CS(\Res_{k'/k}G') \to \CS(G'),
-\]
-defined above, induces
-\[
-\begin{tikzcd}
-\CSiso{\Res_{k'/k} G'} \dar{\TrFrob{\Res_{k'/k} G'}} \rar{\rho} & \CSiso{G'} \dar{\TrFrob{G'}}\\
-G'(k')^* \rar & G'(k')^*,
-\end{tikzcd}
-\]
-where the bottom map is the identity.
-\end{proposition}
-\begin{proof}
-By Lemma~\ref{lem:pullback} the pullback part of the definition of $\rho$ corresponds to the map
-\[
-(\Res_{k'/k}G')(k')^* \to G'(k')^*
-\]
-induced by $g \mapsto (g, 1, \ldots, 1)$.  Since the action of $\Gal(k'/k)$ on
-\[
-(\Res_{k'/k}G')_{k'} \cong \prod_{\Gal(k'/k)} G'
-\]
-is given by permuting coordinates, composition with the norm map yields the identity on $G'(k')$.
-\end{proof}
-
-\section{Quasicharacter sheaves for \texorpdfstring{$p$}{p}-adic tori}\label{sec:applications}
-
-Let $K$ be a local field with ring of integers $R$ and finite residue field $\Fq$; in this section we denote the group $\Weil{}$ by $\Weil{\Fq}$.
-We continue to assume that $\ell$ is invertible in $\Fq$.
-
-\subsection{N\'eron models}\label{ssec:neron}
-We will consider connected commutative algebraic groups over $K$ that admit a N\'eron model,
-by which we mean a locally finite type N\'eron model.
-By \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.2, Thm 2}, these are precisely the connected
-commutative algebraic groups over $K$ that contain no subgroup isomorphic to $\mathbb{G}_\text{a}$.
-Write $\mathcal{N}_K$ for the full subcategory of the category of algebraic groups consisting of such objects.
-This category is additive, and includes all algebraic tori over $K$, abelian varieties over $K$ and unipotent $K$-wound groups.
-We write $\mathcal{N}$ for the category of N\'eron models that arise in this way; in particular, $\mathcal{N}$
-is a full subcategory of the category of smooth commutative group schemes over $R$.
-
-\begin{example}
-If $T_K = \Gm{K}$, then a N\'eron model can be obtained by gluing copies of $\Gm{R}$ (one for each $n \in \ZZ$) along their generic fibers,
-via the gluing morphisms $\Spec{\ZZ[t, t^{-1}]} \to \Spec{\ZZ[t, t^{-1}]}$ defined by $t \mapsto \pi^n t$
-\cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.1, Ex. 5}.
-
-Suppose that $K'/K$ is a quadratic extension and $T_K = U_1(K'/K)$ is the unitary group.
-When $K'/K$ is unramified, the N\'eron model of $T_K$ is a form of the N\'eron model for $\Gm{K}$, with the nontrivial automorphism
-$\sigma \in \Gal(K'/K)$ mapping $(x, n)$ to $(\sigma(x), -n)$ for $x \in R'^\times$ and $n \in \ZZ$ specifying the copy of $\Gm{R'}$.
-This example illustrates the compatibility between N\'eron models and unramified base change
-\cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 10.1, Prop. 3}.
-
-On the other hand, if $K' = K(\sqrt{\pi})$ is totally ramified over $K$ then the N\'eron model of $U_1(K'/K)$ is affine, namely
-$\Spec{R[x,y] / (x^2 - \pi y^2 - 1)}$.  The special fiber is the the disjoint union of two affine lines.
-
-Finally, we remark that if $K'/K$ is any finite extension of local fields and $X'$ is a N\'eron model for $X_{K'}$ then
-$\Res_{R'/R}(X')$ is a N\'eron model for $\Res_{K'/K}(X_{K'})$ \cite{bosch-lutkebohmert-reynaud:NeronModels}*{\S 7.6, Prop. 6}.
-\end{example}
-
-\subsection{Quasicharacters}\label{ssec:quasicharacters}
-
-Write $\m$ for the maximal ideal of $R$ and set $R_n = R/\m^{n+1}$ for every non-negative integer $n$.
-Suppose $X \in \mathcal{N}$.
-Note that $X(K) = X(R)$.
-A \emph{quasicharacter of $X(K)$} is a group homomorphism $X(K) \to \EEx$ that factors through
-$X(R) \to X(R_n)$ for some non-negative integer $n$.
-We note that this definition is compatible with \cite{cassels-frohlich:AlgebraicNumberTheory}*{Ch XV, \S 2.3}.
-The group of quasicharacters of $X(K)$ will be denoted by 
-$\Hom_\text{}(X(K),\EEx)$
- and the subgroup of those that factor through $X(R_n)$ will be denoted by $\Hom_n(X(K),\EEx)$.
-In this section we will see how to geometrize and categorify quasicharacters of $X(K)$ using character sheaves.
-
-\subsection{Review of the Greenberg transform} \label{ssec:rev_Greenberg}
-
-Let $K$, $R$ and $R_n$ be as above.
-For each $n \in \NN$, the Greenberg functor maps schemes over $R_n$ to schemes over $\Fq$.
-See \cite{bertapelle-gonzales:Greenberg} for the definition and fundamental properties of the
-Greenberg functor as we use it; other useful references include
-\cite{greenberg:61}, \cite{greenberg:63a},
-\cite{demazure-gabriel:GroupesAlgebriques}*{V, \S 4, no. 1},
-\cite{bosch-lutkebohmert-reynaud:NeronModels}*{Ch. 9, \S 6} and
-\cite{nicaise-sebag:motivicSerre}*{\S 2.2}.
-For any non-negative integer $n$ we will write
-\[
-\Gr^R_n : \Sch{R} \to \Sch{\Fq}
-\]
-for the functor produced by composing pullback along $\Spec{R_n} \to \Spec{R}$ with the Greenberg functor. 
-This functor respects open immersions, closed immersions, \'etale morphisms, smooth morphisms and
-geometric components.  Moreover, there is a canonical isomorphism
-\[
-\Gr^R_n(X)(\Fq) \iso X(R_n)
-\]
-for any scheme $X$ over $R$.
-
-For any $n\leq m$,  the surjective ring homomorphism $R_{m} \to R_n$ determines a
-natural transformation 
-\[
-\varrho^R_{n\leq m} : \Gr^R_{m} \to \Gr^R_n
-\]
-between additive functors.
-Crucially, $\varrho^R_{n\leq m}(X): \Gr^R_{m}(X)\to \Gr^R_n(X)$ is an affine morphism of $\Fq$-schemes,
-for every $R$-scheme $X$ and every $n\leq m$ \cite{bertapelle-gonzales:Greenberg}*{Prop 4.3}.
-This observation is key to the proof that, for any scheme $X$ over $R$, the projective limit 
-\[
-\Gr_R(X) \ceq \varprojlim_{n\in \NN} \Gr^R_n(X),
-\]
-taken with respect to the surjective morphisms $\varrho^R_{n\leq m}(X) : \Gr^R_{m}(X) \to \Gr^R_n(X)$,
-exists in the category of group schemes over $\Fq$;
-see \cite{EGAIV3}*{\S 8.2}.
-This leads to the definition of the {\it Greenberg transform}:
-\[
-\Gr_R : \Sch{R} \to \Sch{\Fq}.
-\]
-By construction, the $\Fq$-scheme $\Gr_R(X)$ comes equipped with morphisms 
-\[
-\varrho^R_n(X) : \Gr^R(X) \to \Gr^R_n(X),\qquad \forall n\in \NN.
-\]
-
-\subsection{Quasicharacter sheaves}
-\label{ssec:CS_on_GN}
-
-Set $S = \Spec{R}$ and $S_n = \Spec{R_n}$;
-note that $S_0 = \Spec{\Fq}$ is the special fibre of $S$.
-Let $X$ be a smooth commutative group scheme over $S$.
-For every non-negative integer $n$, the Greenberg transform $\Gr^R_n(X)$ is a {\it smooth} commutative group scheme over $S_0$.
-The Greenberg transform $\Gr_R(X)$ of $X$ is a commutative group scheme over $\Fq$
-with $\Fq$-rational points $X(R)$.
-The morphism of $\Fq$-schemes $\varrho^R_n(X) : \Gr_R(X) \to \Gr^R_n(X)$ induces a functor
-\[
-\varrho^R_n(X)^* : \CS(\Gr^R_n(X)) \to \CS(\Gr_R(X)),
-\]
-as in Lemma~\ref{lem:pullback}.
-
-\begin{definition}\label{def:QCS}
-Let $X$ be a smooth group scheme over $R$.
-A {\it quasicharacter sheaf} of $X$ is a triple 
-\[
-\cs{F} \ceq (n, \{\cs{F}_i\}_{n\leq i}, \{\alpha_{i \le j}\}_{n\le i \le j}),
-\] 
-where $n$
-is a non-negative integer, each $\cs{F}_i$ is a character sheaf on $\Gr^R_i(X)$ and each 
-\[
-\alpha_{i \le j} : \cs{L}_j \to \varrho^R_{i \le j}(X)^* \cs{L}_i
-\]
- is an isomorphism; here $\alpha_{i \le i}$ is the identity and the $\alpha_{i \le j}$ are compatible with each other.  
-If $\cs{F} \ceq (n, \{\cs{F}_i\}, \{\alpha_{i \le j}\})$
-and $\cs{F}' \ceq (m, \{\cs{F}'_i\}, \{\alpha'_{i \le j}\})$ are objects then $\Hom(\cs{F}, \cs{F}')$ is the set
-of equivalence classes of pairs $(k, \{\beta_i\}_{k \le i})$, where $n,m \le k$ and the $\beta_i : \cs{F}_i \to \cs{F}'_i$ are
-morphisms of character sheaves so that
-\[
-\begin{tikzcd}
-\cs{F}_j \rar{\alpha_j} \dar{\beta_i} & \varrho^R_{i \le j}(X)^* \cs{F}_i \dar{f_{i \le j}^*\beta_j} \\
-\cs{F}'_j \rar{\alpha_j} & \varrho^R_{i \le j}(X)^* \cs{L}'_i
-\end{tikzcd}
-\]
-commutes for all $k\le i\le j$; we identify two such pairs $(k, \{\beta_i\})$ and $(l, \{\gamma_i\})$ if $\beta_i = \gamma_i$
-for sufficiently large $i$.  Identities and composites are defined in the natural way.
-Let $\QCS(X)$ denote the category of quasicharacter sheaves for $X$.
-\end{definition}
-
-\begin{remark}
-If $\varrho^R_n(X)^* : \CS(\Gr^R_n(X)) \to \CS(\Gr_R(X))$ is full then the construction above can be improved
-by forming $\QCS(X)$ from the essential images of the functors $\varrho^R_n(X)^*$; however, we do not know if $\varrho^R_n(X)^*$ is full.
-\end{remark}
-
-\begin{remark}
-We offer the following alternate construction of $\QCS(X)$.
-As above, let $X$ be a smooth group scheme over $R$.
-Although $\Gr_R(X)$ is not locally of finite type and therefore not smooth,
-let us consider the rigid monoidal category $\CS(\Gr_R(X))$ as defined in Section~\ref{ssec:category},
-though without insisting that the commutative group $\Fq$-scheme $G$ is smooth.
-A quasicharacter sheaf for $X$ is an object of
-the following rigid monoidal subcategory of $\CS(\Gr_R(X))$, denoted by $\QCS(X)$:
-\begin{enumerate}
-\item
-objects in $\QCS(X)$ are the $\ell$-adic sheaves $\varrho^R_n(X)^*\cs{L}$, for $n\in \NN$ and $\cs{L} \in \CS(\Gr^R_n(X))$; 
-\item
-morphisms $\varrho^R_n(X)^*\cs{L} \to \varrho^R_m(X)^*\cs{L}'$ in $\QCS(X)$ are those morphisms
-in $\CS(\Gr_R(X))$ which take the form $\varrho^R_m(X)^*\rho$ for $\rho \in \Hom(\varrho^R_{n\leq m}(X)^*\cs{L},\cs{L}')$
-when $n\leq m$, and $\varrho^R_n(X)^*\rho$ for $\rho \in \Hom(\cs{L},\varrho^R_{m\leq n}(X)^*\cs{L}')$ when $m\leq n$.
-\end{enumerate}
-\end{remark}
-
-\begin{theorem}\label{thm:CSXK}
-Let $K$ be a local field with residue field $\Fq$, in which $\ell$ is invertible; 
-let $R$ be the ring of integers of $K$.
-\begin{enumerate}
-\labitem{(0)}{x0}
-The trace of Frobenius provides a natural transformation between the additive functors
-\[
-X \mapsto \QCSiso{X}
-\qquad\text{and}\qquad
-X \mapsto \Hom_{\text{}}(X(K),\EEx)
-\]
-as functors from $\mathcal{N}$ to the category of commutative groups.
-\end{enumerate} 
-Regarding this natural transformation, for every $X \in \mathcal{N}$:
-\begin{enumerate}[resume]
-\labitem{(1)}{x1} there is a canonical short exact sequence of commutative groups 
-\[
-0 \to \Hh^2(\pi_0(X)_{\bFq},\EEx)^{\Weil{\Fq}} \to \QCSiso{X} \to \Hom_\text{}(X(K),\EEx) \to 0;
-\] 
-\labitem{(2)}{x2} for all quasicharacter sheaves $\cs{F}$, $\cs{F}'$ on $\Gr_R(X)$, and for every
-$\rho \in \Hom(\cs{F},\cs{F}')$, either $\rho$ is trivial or $\rho$ is an isomorphism;
-\labitem{(3)}{x3} for all quasicharacter sheaves $\cs{F}$ for $X$, there is a canonical isomorphism
-\[
-\Aut(\cs{F}) \iso \Hom((\pi_0(X)_{\bFq})_{\Weil{\Fq}},\EEx)
-\]
-\end{enumerate}
-\end{theorem}
-
-\begin{proof}
-To prove \ref{x0}, use: Proposition~\ref{prop:functorialG} with $G = \Gr^R_n(X)$; the fact that
-N\'eron models are unique up to isomorphism; the fact that every $\CS(\Gr^R_n(X))$ is a full subcategory
-of $\QCS(X)$; and the observation that every object in $\QCS(X)$ is in the essential image of $\CS(\Gr^R_n(X))$ for some $n$.
-To prove \ref{x1}, use Theorem~\ref{thm:snake} with $G = \Gr^R_n(X)$ and then argue as in part \ref{x0}.
-To prove \ref{x2}, argue as in the proof of Lemma~\ref{lem:autornaught}.
-To prove \ref{x3}, use: the fact that the component group of $\Gr^R_n(X)$ is independent of $n$;
-Theorem~\ref{thm:autornaught} with $G = \Gr^R_n(X)$, in which case $\pi_0(G) = \pi_0(X \times_S S_0)$
-and $\pi_0(\bG) = \pi_0(X)_{\bFq}$; then argue as in part \ref{x0}.
-\end{proof}
-
- \begin{remark}
-In Section~\ref{ssec:CS_tori} we see that the \'etale site on $\Gr_R(X)$ is rich enough to geometrize all
-quasicharacters of $X(K)$ as $\ell$-adic local systems on $\Gr_R(X)$, where $X$ is a N\'eron model for an
-algebraic torus or an abelian variety over a local field $K$. 
-It is natural to ask if the \'etale site on the generic fibre $X_K$ would have sufficed.
-This seems unlikely, since the geometric \'etale fundamental group of $\Gm{K}$ is ${\hat \ZZ}$;
-however, limited results in this direction were established in \cite{cunningham-kamgarpour:13a} when $K = \mathbb{Q}_p$.
-\end{remark}
-
-\subsection{Quasicharacter sheaves for \texorpdfstring{$p$}{p}-adic tori} \label{ssec:CS_tori}
-
-As we explained in the Introduction, our original motivation for this paper was to find a
-geometrization of quasicharacters of $p$-adic tori. 
-This is now provided by the following adaptation of Theorem~\ref{thm:CSXK} in the case when
-$T\in \mathcal{N}$ is a N\'eron model for an algebraic torus over $K$.
-
-\begin{corollary}\label{cor:CS_tori}
-Let $T$ be a N\'eron model for an algebraic torus over $K$.
-The following is a commutative diagram of exact sequences.
-\[
-  \begin{tikzcd}[row sep=20, column sep=18]
-{}  & 0 \arrow{d} & 0 \arrow{d} &  & \\ 
-   & \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}}  \arrow{d} & \arrow{d} \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}} & 0 \arrow{d} & \\
-    0 \rar & \QCSiso{\pi_0(T)} \arrow{r}{\pi_0^*} \dar{\TrFrob{\pi_0(T)}}
-    & \QCSiso{T} \arrow{r}{\iota_0^*}  \arrow{d}{\TrFrob{\Gr_R(T)}} & \QCSiso{T^0} \arrow{r} \arrow{d}{\TrFrob{\Gr_R(T)^0}} & 0\\
-    0 \arrow{r} & \Hom(\pi_0(T)(\Fq), \EEx) \arrow{r}{\text{inf}} \arrow{d}{\iso}
-    & \arrow{d}{\iso} \Hom_\text{}(T(K),\EEx) \arrow{r}{\text{res}} & \Hom_\text{}(T^0(R),\EEx) \arrow{r} \arrow{d}{\iso} & 0\\
- &  0  & 0 & 0 & 
-  \end{tikzcd}
- \]
- \end{corollary}
-\begin{proof} 
-The horizontal sequence of groups coming from categories of quasicharacter sheaves is exact by
-Proposition~\ref{prop:middleexact}, together with the observation that the functors $\pi_0^*$ and $\iota^*$ preserve limits.
-It is elementary that the horizontal sequence of quasicharacters is exact.
-Accordingly, by Theorem~\ref{thm:CSXK}, the kernel of the  is $\Hh^2(\pi_0(T)_{\bFq},\EEx)^{\Weil{}}$. 
-By \cite{bitan:discriminant}*{Eq 3.1}, the special fibre of the component group scheme for $T$ is given by
-\[
- \pi_0(T)_{\bFq} = X_*(T)_{\mathcal{I}_K},
-\]
-where $X_*(T)$ is the cocharacter lattice of $T_K$ and $\mathcal{I}_K$ is the inertia group for $K$.
-Thus,
-\[
-\Hh^2(\pi_0(T)_{\bFq},\EEx)^{\Weil{\Fq}} = \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}}.
-\] 
-Thus, the middle vertical sequence is exact.
-Since $T^0$ and $\pi_0(T)$ do not lie in $\mathcal{N}$, we cannot use Theorem~\ref{thm:CSXK} to
-determine the image and trace of Frobenius for these schemes. 
-Instead, we observe that $T^0$ and $\pi_0(T)$ are smooth commutative group schemes over $R$,
-so Definition~\ref{def:QCS} gives meaning to categories $\QCS(T^0)$ and $\QCS(\pi_0(T))$, and,
-moreover, that $\pi_0(\Gr^R_n(T^0))= \pi_0(T^0)_{\Fq} = 1$ and $\pi_0(\Gr^R_n(\pi_0(T)) = \pi_0(T)_{\Fq}$ are both independent of $n$.
-It follows that the vertical sequences through $\QCSiso{T^0}$ and $\QCSiso{\pi_0(T)}$ are exact by
-Theorem~\ref{thm:snake} and Definition~\ref{def:QCS}.
-The diagram commutes by Lemma~\ref{lem:pullback}.
-\end{proof}
-
-\begin{example}
-When $T_K = \Gm{K}$ or $T_K = U_1(K'/K)$, the geometric component group $\pi_0(T)_{\bar{k}}$ is cyclic,
-so $\TrFrob{\Gr_R(T)}$ is an isomorphism.  Conversely, when $T_K = \Gm{K}^2$ then
-\[
-\Hh^0(\Weil{\Fq}, \Hh^2(\pi_0(T), \EEx)) = \EEx,
-\]
-and there are uncountably many invisible quasicharacter sheaves for $T$.
-
-We may also give examples of tori whose N\'eron models have component groups appearing in Example \ref{eg:H2}.
-Let $L = K'(\sqrt{\pi})$ be a quadratic ramified extension of $K'$.  When $K = K'$ and $T_K = U_1(L/K) \times U_1(L/K)$,
-the component group $\pi_0(T)_{\bar{k}}$ is $\ZZ/2\ZZ \times \ZZ/2\ZZ$ with trivial Frobenius action.  When $K'/K$ is an unramified
-quadratic extension and $T_K = \Res_{K'/K} U_1(L/K')$, then $\pi_0(T)_{\bar{k}}$ is $\ZZ/2\ZZ \times \ZZ/2\ZZ$ with Frobenius
-exchanging the direct factors.  Finally, let $K'/K$ be a cubic unramified extension and $S_K = \Res_{K'/K} U_1(L/K')$.  If
-$T_K$ is the subtorus with character lattice $X^*(S_K) / \langle (1,1,1) \rangle$, then $\pi_0(T)_{\bar{k}}$ is $\ZZ/2\ZZ \times \ZZ/2\ZZ$
-with Frobenius of order $3$.  Each of these tori will have one invisible quasicharacter sheaf.
-\end{example}
-
-We may also extract information about the automorphism groups of quasicharacter sheaves from Theorem \ref{thm:CSXK}.
-
-\begin{corollary}
-Let $T$ be a N\'eron model for an algebraic torus over $K$.
-For $\cs{E}\in \QCS(\pi_0(T))$, $\cs{F}\in {\QCS(T)}$ and $\cs{F}^0\in {\QCS(T^0)}$, there are canonical isomorphisms
-\[
-\Aut(\cs{E})\iso (\check{T}_\ell)^{\Weil{K}},
-\quad
-\Aut(\cs{F})\iso (\check{T}_\ell)^{\Weil{K}},
-\quad
-\Aut(\cs{F}^0)\iso 1,
-\]
- where $\check{T}_\ell \ceq \Hom(X_*(T),\EEx)$, the $\ell$-adic dual torus to $T_K$.
-\end{corollary}
-
-\begin{proof}
-We already know $\Aut(\cs{E}) =1$ from Proposition~\ref{prop:connected}, part \ref{x3}.
-By Theorem~\ref{thm:CSXK}, 
-\[
-\Aut(\cs{F})  \iso \Hom((\pi_0(T)_{\bFq})_{\Weil{\Fq}},\EEx).
-\]
-By \cite{bitan:discriminant}*{Eq 3.1} again, 
-\[
-\Hom((\pi_0(T)_{\bFq})_{\Weil{\Fq}},\EEx) \iso
-\Hom(X_*(T)_{\Weil{K}},\EEx).
-\]
-But $\Hom(X_*(T)_{\Weil{K}},\EEx) \iso \Hom(X_*(T),\EEx)^{\Weil{K}}$.
-So, for any quasicharacter sheaf $\cs{F}$ for $T$,
-\[
-\Aut(\cs{F}) \iso (\check{T}_\ell)^{\Weil{K}},
-\]
-canonically.
-The case $X= \pi_0(T)$ is handled by the same argument, replacing Theorem~\ref{thm:CSXK} with
-Theorem~\ref{thm:snake} and Definition~\ref{def:QCS}, as in the proof of Corollary~\ref{cor:CS_tori},
-after observing that $\pi_0(\pi_0(T)_{\bFq}) = \pi_0(T)_{\bFq}$.
-\end{proof}
-
-\begin{remark}
-Since $\pi_0(T)_{\bFq} = X_*(T)_{\mathcal{I}_K}$ by \cite{bitan:discriminant}*{Eq 3.1}, we have
-\[\Hom(\pi_0(T)(\Fq), \EEx)
-= \Hom((X_*(T)_{\mathcal{I}_K})^{\Weil{\Fq}}, \EEx)
-= \Hom(X_*(T)_{\mathcal{I}_K}, \EEx)_{\Weil{\Fq}} 
-= \Hh^1(\Weil{\Fq}, \check{T}_\ell^{\mathcal{I}_K}).
-\]
-By the Langlands correspondence for $p$-adic tori \cite{yu:09a}, 
-\[
-\Hom(T(K), \EEx) 
-\iso 
-\Hh^1(\Weil{K}, \check{T}_\ell),
-\]
-where we refer to continuous cohomology, since $\Hom(T(K), \EEx)$ refers to continuous group homomorphisms $T(K)\to \EEx$.
-It now follows from the inflation-restriction exact sequence that the following diagram commutes:
-\[
-\begin{tikzcd}
-   0 \arrow{r} & \Hom(\pi_0(T)(\Fq), \EEx) \arrow{r}{\text{inf}} \arrow{d}{\iso}
-    & \arrow{d}{\iso} \Hom_\text{}(T(K),\EEx) \arrow{r}{\text{res}} & \Hom_\text{}(T^0(R),\EEx) \arrow{r} \arrow{d}{\iso} & 0\\    
-    0 \arrow{r}  
- & \Hh^1(\Weil{\Fq}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{inf}}
- & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{res}} 
- & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{\Fq}} \arrow{r}  
- & 0.
-\end{tikzcd}
-\] 
-Combining this with Corollary~\ref{cor:CS_tori}  produces the following commutative diagram of exact sequences:
-\begin{equation}\label{eq:GLCT}
-  \begin{tikzcd}[row sep=20, column sep=15]
-{}  & 0 \arrow{d} & 0 \arrow{d} &  & \\ 
-   & \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}}  \arrow{d} & \arrow{d} \Hh^2(X_*(T)_{\mathcal{I}_K},\EEx)^{\Weil{\Fq}} & 0 \arrow{d} & \\
-    0 \rar & \QCSiso{\pi_0(T)} \arrow{r}{\pi_0^*} \arrow{d}
-    & \QCSiso{T} \arrow{r}{\iota_0^*}  \arrow{d} & \QCSiso{T^0} \arrow{r} \arrow{d} & 0\\
-   0 \arrow{r}  
- & \Hh^1(\Weil{\Fq}, \check{T}_\ell^{\mathcal{I}_K}) \arrow{r}{\text{inf}} \arrow{d}
- & \Hh^1(\Weil{K}, \check{T}_\ell) \arrow{r}{\text{res}} \arrow{d}
- & \Hh^1(\mathcal{I}_K, \check{T}_\ell)^{\Weil{\Fq}} \arrow{r} \arrow{d}  
- & 0\\
- &  0  & 0 & 0 & 
-  \end{tikzcd}
- \end{equation}
-It is natural to ask if the vertical surjections can be defined directly, without making use of local class field theory,
-for which the results of \cite{suzuki-yoshida:12a}  and \cite{suzuki:14a} may be helpful.
-The case $T_K = \Gm{K}$ is already very interesting, in which case \eqref{eq:GLCT} becomes
-\begin{equation}\label{eq:Gm}
-\begin{tikzcd}
-    0 \rar & \QCSiso{\ZZ} \arrow{r}{\pi_0^*} \arrow{d}{\iso}
-    & \QCSiso{\Gm{K}^\text{Neron}} \arrow{r}{\iota_0^*}  \arrow{d}{\iso} & \QCSiso{\Gm{R}} \arrow{r} \arrow{d}{\iso} & 0\\
-    0 \arrow{r}  
- & \Hom(\Weil{\Fq}, \EEx) \arrow{r}{\text{inf}}
- & \Hom(\Weil{K}, \EEx) \arrow{r}{\text{res}} 
- & \Hom(\mathcal{I}_K, \EEx) \arrow{r}  
- & 0
-\end{tikzcd}
-\end{equation}
-We suspect that the general case of \eqref{eq:GLCT}, where $K$ is any local field and $T_K$ is any
-torus over $K$, may be deduced from \eqref{eq:Gm}.
-In Section~\ref{ssec:wrK} we develop a tool for further work in that direction.
-\end{remark}
-
-\subsection{Weil restriction and quasicharacter sheaves}\label{ssec:wrK}
-
-Let $K'/K$ be a finite Galois extension of local fields and
-let $k'/k$ be the corresponding extension of residue fields.
-Let $R$ and $R'$ be the rings of integers of $K$ and $K'$, respectively.
-Suppose $X \in \mathcal{N}$ and set $X_{K'} \ceq X_K \times_\Spec{K} \Spec{K'}$
-and let $X'$ be a N\'eron model for $X_{K'}$.
-
-\begin{proposition}\label{prop:wrK}
-The canonical closed immersion 
-\[
-X_K \hookrightarrow \Res_{K'/K} X_{K'}
-\]
-of $K$-group schemes
-induces a map of $\Fq$-group schemes 
-\[
-f : \Gr_R(X) \to \Res_{k'/k} \Gr_{R'}(X')
-\] 
-which, through quasicharacter sheaves, induces
-\[
-\begin{tikzcd}[column sep=60]
-\Hom_{\text{}}(X_K(K'), \EEx) \arrow{r}{\chi \mapsto \chi\vert_{X(K)}} &\Hom_{\text{}}(X_K(K), \EEx).
-\end{tikzcd}
-\]
-\end{proposition}
-
-\begin{proof}
-By the N\'eron mapping property, the canonical closed immersion
-\[
-X_K\hookrightarrow \Res_{K'/K}(X_{K'})
-\]
- extends uniquely to a morphism
-\begin{equation}\label{me}
-X\to \Res_{R'/R}(X')
-\end{equation}
- of smooth $R$-group schemes.
-%
-Applying the functor $\Gr^R_{n}$ to \eqref{me}
-and using \cite{bertapelle-gonzales:Greenberg}*{Thm 1.1} defines the morphism of smooth group schemes
-\begin{equation}\label{men}
-f_n: \Gr_{n-1}^R(X) \to \Res_{k'/k} \Gr_{en-1}^{R'}(X'),
-\end{equation}
-where $e$ is the ramification index of $K'/K$.
-Using Lemma~\ref{lem:pullback}, \eqref{men} induces a functor 
-\begin{equation}\label{men-pulled}
-f_n^* : \CS(\Res_{k'/k} \Gr_{en-1}^{R'}(X'))\to \CS(\Gr_{n-1}^{R}(X)).
-\end{equation}
-Since 
-\[
-\left(\Res_{k'/k} \Gr_{en-1}^{R'}(X') \right)(\Fq) = \left(\Gr_{en-1}^{R'}(X')\right)(k'),
-\]
-it follows from Lemma~\ref{lem:pullback} that the pullback functor \eqref{men-pulled} actually induces
-\[ 
-\Hom_{en-1}(X'(R'),\EEx) \to \Hom_{n-1}(X(R)),\EEx)
-\]
-Since $X'$ is a N\'eron model for $X_{K'}$ and $X$ is a N\'eron model for $X_K$,
- this may be re-written as
- \[ 
-\Hom_{en-1}(X_{K'}(K'),\EEx)= \Hom_{en-1}(X_{K}(K'),\EEx) \to \Hom_{n-1}(X_K(K)),\EEx)
-\]
-Passing to limits now defines
-\[ 
-\Hom_\text{}(X_K(K'),\EEx) \to \Hom_\text{}(X_K(K),\EEx)
-\]
-Argue as in Proposition~\ref{prop:csbe} to see that this is indeed restriction of characters.
-\end{proof}
-
-\subsection{Transfer of quasicharacters}\label{ssec:transfer}
-
-Let $K$ and $L$ be local fields with rings of integers $\OK$ and $\OL$, respectively. 
-Pick uniformizers $\varpi_K$ and $\varpi_L$ for $\OK$ and $\OL$, respectively;
-what follows will not depend on these choices.
-Suppose $\ell$ is invertible in the residue fields of $K$ and $L$.
-
-We begin with $X_K\in \mathcal{N}_K$ with N\'eron model $X$ and $Y_{L}\in \mathcal{N}_L$ with N\'eron model $Y$.
-Suppose $m$ is a positive integer such that 
-\[
-\OK/\varpi_K^{m}\OK \iso \OL/\varpi_L^{m}\OL.
-\]
-Suppose also that
-\begin{equation}\label{eq:schematic_transfer}
-X \times_{\Spec{\OK}} \Spec{\OK/\varpi_K^{m}\OK} \iso Y \times_{\Spec{\OL}} \Spec{\OL/\varpi_L^{m}\OL}
-\end{equation}
-as smooth group schemes over $\OK/\varpi_K^{m}\OK$. 
-Then
-\[
-\Gr^{\OK}_{m-1}(X) \iso \Gr^{\OL}_{m-1}(Y)
-\]
-as smooth group schemes over $\Fq$.  Accordingly, by Lemma~\ref{lem:pullback},
-the isomorphism above determines an equivalence of categories
-\begin{equation}\label{eq:categorical_transfer}
-\CS(\Gr^{\OK}_{m-1}(X)) \cong \CS(\Gr^{\OL}_{m-1}(Y))
-\end{equation}
-which induces an isomorphism
-\begin{equation}\label{eq:transfer}
-\Hom_{m-1}(X(K),\EEx)  \iso  \Hom_{m-1}(Y(L),\EEx).
-\end{equation}
-The isomorphism \eqref{eq:transfer} is an instance of {\it transfer} of (certain) quasicharacters between $X(K)$ and $Y(L)$. 
-We now recognize this transfer of quasicharacters as a consequence of the
-equivalence of categories of quasicharacter sheaves \eqref{eq:categorical_transfer}.
-
-The isomorphism \eqref{eq:schematic_transfer} can indeed exist between quasicharacters of
-algebraic tori over local fields, even when the characteristics of $K$ and $L$ differ.
-Suppose $T_K$ and $M_L$ are tori over local fields $K$ and $L$,
-splitting over $K'$ and $L'$, respectively.
-Then $T_K$ and $M_L$ are said to be \emph{$n$-congruent} \cite{chai-yu:01a}*{\S 2} if there are isomorphisms
- \begin{align*}
-  \alpha : \OO{K'}/\varpi_K^n \OO{K'} &\to \OO{L'}/\varpi_{L}^n \OO{L'} \\
-  \beta : \Gal(K'/K) &\to \Gal(L'/L) \\
-  \phi : X^*(T_K) &\to X^*(M_L)
- \end{align*}
- satisfying the conditions
- \begin{enumerate}
-  \item $\alpha$ induces an isomorphism $\OK/\varpi_K^n \OK \to \OO{L}/\varpi_{L}^n \OO{L}$,
-  \item $\alpha$ is $\Gal(K'/K)$-equivariant relative to $\beta$, and
-  \item $\phi$ is $\Gal(K'/K)$-equivariant relative to $\beta$.
- \end{enumerate}
-If $T_K$ and $M_L$ are $n$-congruent then $\alpha$, $\beta$ and $\phi$ determine an isomorphism 
-\begin{equation}\label{transfer}
-  \Hom_{n-1}(T_K(K), \EEx) \iso \Hom_{n-1}(M_L(L),\EEx).
-\end{equation}
-Note that if $T_K$ and $M_L$ are $n$-congruent, then they are $m$-congruent for every
-$m \leq n$.
-
-Now let $T$ be a N\'eron model for $T_K$ and let $M$ be a N\'eron model for $M_L$.
-One of the main results of \cite{chai-yu:01a} gives an isomorphism of group schemes 
-\[
-T \times_{\Spec{\OK}} \Spec{\OK/\varpi_K^m\OK} \iso M \times_{\Spec{\OL}} \Spec{\OL/\varpi_L^m\OL}
-\] 
-assuming that $T_K$ and $M_L$ are sufficiently congruent.
-They define a quantity $h$ (the smallest integer so that $\varpi^h$ lies in the
-Jacobian ideal associated to a natural embedding of $T_K$ into an induced torus \cite{chai-yu:01a}*{\S 8.1}) and show
-that if $n > 3h$ and $T_K$ and $M_L$ are $n$-congruent then there is a canonical isomorphism of smooth group schemes
- $
-\Gr_{n-3h-1}(T) \to \Gr_{n-3h-1}(M)
- $
- determined by $\alpha, \beta$ and $\phi$ \cite{chai-yu:01a}*{Thm. 8.5}.
-Combining this with the paragraph above gives the following instance of the geometrization of the transfer of quasicharacters.
-
-\begin{proposition}\label{prop:transfer}
- With notation above, suppose that $T_K$ and $M_L$ are $n$-congruent and $n > 3h$.  Set $m = n-3h$.
- Then there is a canonical equivalence of categories
- \[
- \CS(\Gr^{\OK}_{m-1}(T)) \iso \CS(\Gr^{\OL}_{m-1}(M))
- \]
- determined by $\alpha, \beta$ and $\phi$ inducing an isomorphism
- \[
-\Hom_{m-1}(T(K), \EEx) \iso  \Hom_{m-1}(M(L), \EEx)
- \]
-compatible with \eqref{transfer}.
-\end{proposition}
-
-\bibliography{bibliography/Biblio}
+In the three examples above, we are able to compute $\Hh^0(\Weil{}, \Hh^2(\bG, \EEx))$ without reference to $\Frob{G}$ as a consequence of the structure of $\Hh^0(\Weil{}, \Hh^2(\bG, \EEx))$; this independence does not hold in general.
+But the description of $\Hh^2(\bG, \EEx)$ allows us to
 

### 2015-07-23 followup.tex
Proof of symmetric lemma

@@
 
-\section{No Invisible Character Sheaves}
+\section{Eliminating Invisible Character Sheaves}
 
-By the universal coefficient theorem
+If $M$ is a $\bG$-module, then we say a cohomology class in $\Hh^2(\bG, M)$ is \emph{symmetric} if it is represented
+by a symmetric $2$-cocycle.  Since every coboundary is symmetric, either all cocycles in a given class will be symmetric
+or none will.
 
-In the three examples above, we are able to compute $\Hh^0(\Weil{}, \Hh^2(\bG, \EEx))$ without reference to $\Frob{G}$ as a consequence of the structure of $\Hh^0(\Weil{}, \Hh^2(\bG, \EEx))$; this independence does not hold in general.
-But the description of $\Hh^2(\bG, \EEx)$ allows us to
+\begin{lemma}
+Let $\bG$ be a commutative group.  Then the only symmetric class in $\Hh^2(\bG, \EEx)$ is the trivial class.
+\end{lemma}
+
+\begin{proof}
+By the universal coefficient theorem,
+\[
+0 \to \Ext^1_\ZZ(\Hh_{n-1}(\bG, \ZZ), \EEx) \to \Hh^n(\bG, \EEx) \to \Hom(\Hh_n(\bG, \ZZ), \EEx) \to 0
+\]
+for all $n > 0$.  When $n = 2$, using the fact that $\bG$ is commutative, we have that $\Hh_1(\bG, \ZZ) \cong \bG$
+and that $\Hh_2(\bG, \ZZ) \cong \wedge^2 \bG$. We get
+\[
+0 \to \Ext^1_\ZZ(\bG, \EEx) \to \Hh^2(\bG, \EEx) \to \Hom(\wedge^2 \bG, \EEx) \to 0.
+\]
+The map $\Hh^2(\bG, \EEx) \to \Hom(\wedge^2 \bG, \EEx)$ maps a $2$-cocycle $f$ to the alternating function
+\[
+(x,y) \mapsto f(x,y) - f(y,x).
+\]
+Thus the cohomology classes represented by symmetric cocycles are precisely those in the image of $\Ext^1_\ZZ(\bG, \EEx)$.
+But $\Ext^1_\ZZ(-, \EEx)$ vanishes because $\EEx$ is divisible.
+\end{proof}
+
+\begin{theorem}
+Commutative.
+\end{theorem}
 

### 2015-07-23 followup.tex
CCS

@@
 \usepackage{hyperref}
+
+\usepackage{tikz}
+\usetikzlibrary{shapes,arrows,calc,matrix}
+\usepackage{tikz-cd}
 
@@
 \newcommand{\CS}{{\mathcal{C\hskip-0.8pt S}}}
+\newcommand{\CCS}{{\mathcal{CC\hskip-0.8pt S}}}
 \newcommand{\bCS}{{\CS_0}}
@@
 
+\begin{definition}\label{def:CS}
+With reference to \ref{Cunningham-Roe:QCS}*{Def. 1.1}, a \emph{commutative character sheaf on $G$} is a character sheaf on $G$ 
+$\CCS(G)$
+
+ is a triple
+$\cs{L}\ceq (\gcs{L},\mu,\phi)$ where:
+\begin{enumerate}
+\labitem{(CS.1)}{CS.1} $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean a constructible
+$\ell$-adic sheaf on $\bG$, {\it lisse} on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
+\labitem{(CS.2)}{CS.2} $\mu: \bm^* \gcs{L} \to \LxL$ is an isomorphism of
+sheaves on $\bGxG$ such that the following diagram commutes,
+  where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
+  \[
+  \begin{tikzcd}[row sep=30]
+  \bm_3^*\gcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
+    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
+    \gcs{L} \boxtimes \bm^* \gcs{L} \arrow{rr}{\id \boxtimes \mu}
+    &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL
+  \end{tikzcd}
+  \]
+\labitem{(CS.3)}{CS.3} $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an
+  isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with
+  $\mu$ in the sense that the following diagram commutes.
+  \[
+  \begin{tikzcd}[row sep=20]
+  \Frob{\GxxG}^* \bm^* \gcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
+    && \Frob{\GxxG}^*(\LxL)\\
+    \arrow[equal]{u} \bm^*  \Frob{G}^* \gcs{L} \arrow[swap]{d}{\bm^* \phi}
+    && \Frob{G}^*\gcs{L}\boxtimes \Frob{G}^*\gcs{L} \dar{\phi\boxtimes \phi} \arrow[equal]{u} \\
+    \bm^*\gcs{L} \arrow{rr}{\mu}
+    && \LxL
+  \end{tikzcd}
+  \]
+\end{enumerate}
+Morphisms of character sheaves are defined in the natural way:
+\begin{enumerate}
+\labitem{(CS.4)}{CS.4} if $\cs{L} = (\gcs{L},\mu,\phi)$ and
+  $\cs{L'} = (\gcs{L'},\mu',\phi')$ are character sheaves on $G$ then
+  a morphism $\rho : \cs{L} \to \cs{L}'$ is a map $\brho : \gcs{L} \to \gcs{L'}$
+  of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
+  \[
+  \begin{tikzcd}[column sep=40]
+  \Frob{G}^* \gcs{L} \rar{\Frob{G}^* \brho} \arrow[swap]{d}{\phi} & \Frob{G}^* \gcs{L'} \dar{\phi'}
+  & & \arrow[swap]{d}{\mu} \bm^* \gcs{L} \rar{\bm^* \brho} & \bm^* \gcs{L'} \dar{\mu'} \\
+  \gcs{L} \rar{\brho} & \gcs{L'}
+  & {} & \LxL \rar{\tight{1}{\rho\boxtimes \rho}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
+  \end{tikzcd}
+  \]
+\end{enumerate}
+ The category of character sheaves on $G$ will be denoted by $\CS(G)$.
+ \end{definition}
+
 \section{Eliminating Invisible Character Sheaves}

### 2015-07-23 forarXiv.tex
CCS

--- 2015-07-22 dictionary.tex
@@
 
-\address{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive Northwest, Alberta, Calgary, Canada, {T2N~1N4}.}
+\address{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive Northwest, Calgary, Alberta, Canada, {T2N~1N4}.}
 \email{cunning@math.ucalgary.ca}
@@
 
-\iffalse
 \begin{proof}
@@
 \end{proof}
-\fi
 
@@
 \end{lemma}
-\iffalse
+
 \begin{proof}
@@
 From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields,
-as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3}, gives us all we need for points \ref{c1} and \ref{c2}.
-\iffalse
+as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3}, gives us all we need for points \ref{c1} and \ref{c2}, as we briefly recall.
+
 As in the proof of Proposition~\ref{prop:finite}, use \'etale descent to see that pullback by the Lang isogeny $\Lang : G\to G$
@@
 representation of $G(\Fq)$, proving parts \ref{c1} and \ref{c2}.
-\fi
+
 For part \ref{c3}, suppose $\Lang^*\cs{E} = V$ with isomorphism $V \to V\otimes V$.
@@
 
-\bibliography{bibliography/Biblio}
+%\bibliography{forarXiv}   
+% \bib, bibdiv, biblist are defined by the amsrefs package.
+\begin{bibdiv}
+\begin{biblist}
+
+\bib{aubert-cunningham:02a}{incollection}{
+      author={Aubert, Anne-Marie},
+      author={Cunningham, Clifton},
+       title={{An introduction to sheaves on adic spaces for $p$-adic group
+  representation theory}},
+        date={2002},
+   booktitle={{Functional analysis, VII (Dubrovnik, 2001)}},
+      series={Various Publ. Ser. (Aarhus)},
+      volume={46},
+   publisher={Univ. Aarhus},
+     address={Aarhus},
+       pages={{11\ndash 51}},
+}
+
+\bib{beilinson-bernstein-deligne:81a}{article}{
+      author={Be{\u\i}linson, Alexander~A.},
+      author={Bernstein, Joseph},
+      author={Deligne, Pierre},
+       title={Faisceaux pervers},
+        date={1982},
+     journal={Ast\'erisque},
+      volume={100},
+       pages={5\ndash 171},
+}
+
+\bib{bernstein-luntz:equivariant_sheaves}{book}{
+      author={Bernstein, Joseph},
+      author={Luntz, Valery},
+       title={Equivariant sheaves and functors},
+      series={Lecture Notes in Mathematics},
+   publisher={Springer-Verlag},
+     address={Berlin},
+        date={1994},
+      volume={1578},
+}
+
+\bib{bertapelle-gonzales:Greenberg}{unpublished}{
+      author={Bertapelle, Alessandra},
+      author={{Gonz\'ales-Avil\'es}, Cristian~D.},
+       title={{The Greenberg functor revisited}},
+        date={2014},
+         url={http://arxiv.org/abs/1311.0051},
+        note={\href{http://arxiv.org/abs/1311.0051}{arXiv:1311.0051
+  [math.NT]}},
+}
+
+\bib{bitan:discriminant}{article}{
+      author={Bitan, Rony~A.},
+       title={The discriminant of an algebraic torus},
+        date={2011},
+     journal={J. Number Theory},
+      volume={131},
+      number={9},
+       pages={1657\ndash 1671},
+}
+
+\bib{bosch-lutkebohmert-reynaud:NeronModels}{book}{
+      author={Bosch, Siegfried},
+      author={L\"utkebohmert, Werner},
+      author={Reynaud, Michel},
+       title={{N\'eron models}},
+   publisher={Springer-Verlag},
+     address={Berlin},
+        date={1980},
+}
+
+\bib{boyarchenko-drinfeld:10a}{unpublished}{
+      author={Boyarchenko, Mitya},
+      author={Drinfeld, Vladimir},
+       title={A motivated introduction to character sheaves and the orbit
+  method for unipotent groups in positive characteristic},
+        date={2010},
+        note={\href{http://arxiv.org/abs/math/0609769}{arXiv:0609769
+  [math.RT]}},
+}
+
+\bib{brown:CohomologyGrps}{book}{
+      author={Brown, Kenneth~S.},
+       title={Cohomology of groups},
+      series={Graduate Texts in Mathematics},
+   publisher={{Springer-Verlag}},
+     address={New York},
+        date={1982},
+      volume={87},
+}
+
+\bib{cartan-eilenberg:HomologicalAlgebra}{book}{
+      author={Cartan, Henri},
+      author={Eilenberg, Samuel},
+       title={Homological algebra},
+   publisher={Princeton U.P.},
+     address={Princeton},
+        date={1956},
+}
+
+\bib{cassels-frohlich:AlgebraicNumberTheory}{book}{
+      editor={Cassels, John W.~S.},
+      editor={Frohlich, Albrecht},
+       title={Algebraic number theory},
+     edition={2},
+   publisher={London Math Society},
+     address={London},
+        date={2010},
+}
+
+\bib{chai-yu:01a}{article}{
+      author={Chai, Ching-Li},
+      author={Yu, Jiu-Kang},
+       title={{Congruences of N\'eron models for tori and the Artin
+  conductor}},
+        date={2001},
+     journal={Annals of Math},
+      volume={154},
+      number={2},
+       pages={347\ndash 382},
+}
+
+\bib{cunningham-kamgarpour:13a}{article}{
+      author={Cunningham, Clifton},
+      author={Kamgarpour, Masoud},
+       title={{Geometrization of continuous characters of
+  $\mathbb{Z}_p^\times$}},
+        date={2013},
+     journal={Pacific J. Math.},
+      volume={261},
+      number={1},
+       pages={95\ndash 99},
+}
+
+\bib{deligne:SGA4.5}{book}{
+      author={Deligne, Pierre},
+       title={{Cohomologie \'etale}},
+      series={Lecture Notes in Mathematics},
+   publisher={{Springer-Verlag}},
+     address={Berlin},
+        date={1977},
+      volume={569},
+}
+
+\bib{deligne:80a}{article}{
+      author={Deligne, Pierre},
+       title={{La conjecture de Weil II}},
+        date={1980},
+     journal={{Inst. Hautes \'Etudes Sci. Publ. Math.}},
+      volume={52},
+       pages={137\ndash 252},
+}
+
+\bib{deligne:02a}{article}{
+      author={Deligne, Pierre},
+       title={{Cat\'egories tensorielles}},
+        date={2002},
+     journal={{Mosc. Math. J.}},
+      volume={2},
+      number={2},
+       pages={227\ndash 248},
+}
+
+\bib{deligne-katz:SGA7.2}{book}{
+      author={Deligne, Pierre},
+      author={Katz, Nicholas},
+       title={{Groupes de monodromie en g\'eom\'etrie alg\'ebrique II}},
+      series={{Lecture Notes in Mathematics}},
+   publisher={{Springer-Verlag}},
+     address={Berlin},
+        date={1973},
+      volume={340},
+}
+
+\bib{demazure-gabriel:GroupesAlgebriques}{book}{
+      author={Demazure, Michel},
+      author={Gabriel, Pierre},
+       title={{Groupes alg\'ebriques}},
+   publisher={{Masson \& Cie}},
+     address={Paris},
+        date={1970},
+}
+
+\bib{etingof:09a}{unpublished}{
+      author={Etingof, Pavel},
+      author={Gelaki, Shlomo},
+      author={Nikshych, Dmitri},
+      author={Ostrik, Victor},
+       title={Tensor categories},
+        date={2009},
+         url={www-math.mit.edu/~etingof/tenscat.pdf},
+        note={{Lecture notes for MIT 18.769, available at
+  \url{www-math.mit.edu/~etingof/tenscat.pdf}}},
+}
+
+\bib{vdGeer-Moonen:AbelianVarieties}{unpublished}{
+      author={Geer, Gerard {van}~{der}},
+      author={Moonen, Ben},
+       title={Abelian varieties},
+        date={2013},
+         url={http://staff.science.uva.nl/~bmoonen/boek/BookAV.html},
+        note={Available at
+  \url{http://staff.science.uva.nl/~bmoonen/boek/BookAV.html}},
+}
+
+\bib{greenberg:61}{article}{
+      author={Greenberg, Marvin~J.},
+       title={{Schemata over local rings I}},
+        date={1961},
+     journal={Annals of Math},
+      volume={73},
+      number={2},
+       pages={624\ndash 648},
+}
+
+\bib{greenberg:63a}{article}{
+      author={Greenberg, Marvin~J.},
+       title={{Schemata over local rings II}},
+        date={1963},
+     journal={Annals of Math},
+      volume={78},
+      number={2},
+       pages={256\ndash 266},
+}
+
+\bib{EGAIV2}{article}{
+      author={Grothendieck, Alexandre},
+       title={{\'El\'ements de g\'eom\'etrie alg\'ebrique IV. \'Etude locale
+  des sch\'emas et des morphismes de sch\'emas. II}},
+        date={1965},
+     journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
+      number={24},
+}
+
+\bib{EGAIV3}{article}{
+      author={Grothendieck, Alexandre},
+       title={{\'El\'ements de g\'eom\'etrie alg\'ebrique IV. \'Etude locale
+  des sch\'emas et des morphismes de sch\'emas. III}},
+        date={1966},
+     journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
+      number={28},
+}
+
+\bib{SGA5}{book}{
+      author={Grothendieck, Alexandre},
+       title={{S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois Marie 1965--66
+  SGA5: Cohomologie $\ell$-adique et Fonctions L}},
+      series={{Lecture Notes in Mathematics}},
+   publisher={{Springer-Verlag}},
+        date={1977},
+      volume={589},
+}
+
+\bib{kamgarpour:09a}{article}{
+      author={Kamgarpour, Masoud},
+       title={{Stacky abelianization of algebraic groups}},
+        date={2009},
+     journal={{Transform. Groups}},
+      volume={14},
+      number={4},
+       pages={825\ndash 846},
+}
+
+\bib{lang:56a}{article}{
+      author={Lang, Serge},
+       title={Algebraic groups over finite fields},
+        date={1956},
+     journal={Amer. J. Math.},
+      volume={78},
+       pages={555\ndash 563},
+}
+
+\bib{laumon:87a}{article}{
+      author={Laumon, G\'erard},
+       title={{Transformation de Fourier, constantes d'\'equations
+  fonctionnelles et conjecture de Weil}},
+        date={1987},
+     journal={{Inst. Hautes \'Etudes Sci. Publ. Math.}},
+      volume={65},
+       pages={131\ndash 210},
+}
+
+\bib{lusztig:85a}{article}{
+      author={Lusztig, George},
+       title={{Character sheaves I}},
+        date={1985},
+     journal={Advances in Math.},
+      volume={56},
+       pages={193\ndash 237},
+}
+
+\bib{lusztig:disconnected1}{article}{
+      author={Lusztig, George},
+       title={{Character sheaves on disconnected groups I}},
+        date={2003},
+     journal={Representation Theory},
+      volume={7},
+       pages={374\ndash 403},
+}
+
+\bib{nicaise-sebag:motivicSerre}{article}{
+      author={Sebag, Julien},
+      author={Nicaise, Johannes},
+       title={{Motivic Serre invariants and Weil restriction}},
+        date={2008},
+     journal={J. Algebra},
+      volume={319},
+      number={4},
+       pages={1585\ndash 1610},
+}
+
+\bib{suzuki:14a}{unpublished}{
+      author={Suzuki, Takashi},
+       title={{Grothendieck's pairing on N\'eron component groups: Galois
+  descent from the semistable case}},
+        date={2015},
+        note={\href{http://arxiv.org/abs/1410.3046}{arXiv:1410.3046
+  [math.NT]}},
+}
+
+\bib{suzuki-yoshida:12a}{inproceedings}{
+      author={Suzuki, Takashi},
+      author={Yoshida, Manabu},
+       title={{A refinement of the local class field theory of Serre and
+  Hazewinkel}},
+        date={2012},
+   booktitle={{Algebraic number theory and related topics}},
+      series={{RIMS K\^oky\^uroku Bessatsu, B32}},
+   publisher={{Res. Inst. Math. Sci. (RIMS)}},
+     address={Kyoto},
+       pages={163\ndash 191},
+}
+
+\bib{vakil:Algebraic_Geometry}{unpublished}{
+      author={Vakil, Ravi},
+       title={Foundations of algebraic geometry},
+        date={April 29, 2015},
+         url={http://math.stanford.edu/~vakil/216blog/},
+        note={Available at \url{http://math.stanford.edu/~vakil/216blog/}},
+}
+
+\bib{weibel:Homological_Algebra}{book}{
+      author={Weibel, Charles~A.},
+       title={An introduction to homological algebra},
+      series={Cambridge Studies in Advanced Mathematics},
+   publisher={Cambridge U.P.},
+     address={Cambridge, UK},
+        date={1994},
+      volume={38},
+}
+
+\bib{yu:09a}{incollection}{
+      author={Yu, Jiu-Kang},
+       title={{On the local Langlands correspondence for tori}},
+        date={2009},
+   booktitle={Ottawa lectures on admissible representations of reductive
+  $p$-adic groups},
+      editor={Cunningham, Clifton},
+      editor={Nevins, Monica},
+      series={Fields Institute Monographs},
+      volume={26},
+   publisher={American Math Society},
+     address={Providence R.I.},
+       pages={177\ndash 183},
+}
+
+\end{biblist}
+\end{bibdiv}
 

### 2015-07-23 followup.tex
Fixing additive notation in alternating map
Definitions and Recolletions

--- 2015-07-23 followup.tex
@@
 \newcommand{\CS}{{\mathcal{C\hskip-0.8pt S}}}
+\newcommand{\CCS}{{\mathcal{CC\hskip-0.8pt S}}}
 \newcommand{\bCS}{{\CS_0}}
-\newcommand{\CSiso}[1]{\CS(#1)_{/\text{iso}}}
-\newcommand{\bCSiso}[1]{\bCS(#1)_{/\text{iso}}}
 \newcommand{\catname}[1]{\normalfont{\textsf{#1}}}
@@
 \newcommand{\QCS}{{\mathcal{QC\hskip-0.8pt S}}}
+\newcommand{\CSiso}[1]{\CS(#1)_{/\text{iso}}}
+\newcommand{\bCSiso}[1]{\bCS(#1)_{/\text{iso}}}
 \newcommand{\QCSiso}[1]{\QCS(#1)_{/\text{iso}}}
+\newcommand{\CCSiso}[1]{\CS(#1)_{/\text{iso}}}
 %% Labeled items
@@
 
-\section{Commutative Character Sheaves}
+\maketitle
+
+\section{Definitions and Recollections}
+
+\begin{definition}\label{def:CCS}
+A \emph{commutative character sheaf on $G$} is a triple
+$\cs{L}\ceq (\gcs{L},\mu,\phi)$ where:
+\begin{enumerate}
+\labitem{(CCS.1)}{CS.1} $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean a constructible
+$\ell$-adic sheaf on $\bG$, {\it lisse} on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
+\labitem{(CCS.2)}{CS.2} $\mu: \bm^* \gcs{L} \to \LxL$ is an isomorphism of
+sheaves on $\bGxG$ such that the following diagrams commute,
+  where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$,
+  \[
+  \begin{tikzcd}[row sep=30]
+  \bm_3^*\gcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu} 
+    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id}  && \gcs{L} \arrow{r}{\mu} \arrow{dr}[swap]{\mu}& \gcs{L} \boxtimes \gcs{L} \arrow{d}{\iso}\\
+    \gcs{L} \boxtimes \bm^* \gcs{L} \arrow{rr}{\id \boxtimes \mu}
+    &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL && &  \gcs{L} \boxtimes \gcs{L}
+  \end{tikzcd}
+  \]
+where 
+$\LxL \to \LxL$ given by $x\otimes y \mapsto y \otimes x$, by which we meant the case of the sheaf isomorphism $\cs{L}_1 \boxtimes \cs{L}_2 \to \cs{L}_2\boxtimes \cs{L}_1$ when $\cs{L}_1 = \cs{L}_2 = \cs{L}$.
+\labitem{(CCS.3)}{CS.3} $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an
+  isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with
+  $\mu$ in the sense that the following diagram commutes.
+  \[
+  \begin{tikzcd}[row sep=20]
+  \Frob{\GxxG}^* \bm^* \gcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
+    && \Frob{\GxxG}^*(\LxL)\\
+    \arrow[equal]{u} \bm^*  \Frob{G}^* \gcs{L} \arrow[swap]{d}{\bm^* \phi}
+    && \Frob{G}^*\gcs{L}\boxtimes \Frob{G}^*\gcs{L} \dar{\phi\boxtimes \phi} \arrow[equal]{u} \\
+    \bm^*\gcs{L} \arrow{rr}{\mu}
+    && \LxL
+  \end{tikzcd}
+  \]
+\end{enumerate}
+Morphisms of character sheaves are defined in the natural way:
+\begin{enumerate}
+\labitem{(CCS.4)}{CS.4} if $\cs{L} = (\gcs{L},\mu,\phi)$ and
+  $\cs{L'} = (\gcs{L'},\mu',\phi')$ are character sheaves on $G$ then
+  a morphism $\rho : \cs{L} \to \cs{L}'$ is a map $\brho : \gcs{L} \to \gcs{L'}$
+  of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
+  \[
+  \begin{tikzcd}[column sep=40]
+  \Frob{G}^* \gcs{L} \rar{\Frob{G}^* \brho} \arrow[swap]{d}{\phi} & \Frob{G}^* \gcs{L'} \dar{\phi'}
+  & & \arrow[swap]{d}{\mu} \bm^* \gcs{L} \rar{\bm^* \brho} & \bm^* \gcs{L'} \dar{\mu'} \\
+  \gcs{L} \rar{\brho} & \gcs{L'}
+  & {} & \LxL \rar{\tight{1}{\rho\boxtimes \rho}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
+  \end{tikzcd}
+  \]
+\end{enumerate}
+ The category of character sheaves on $G$ will be denoted by $\CCS(G)$.
+ \end{definition}
+
+With reference to \cite{Cunningham-Roe:QCS}*{Def. 1.1}, a we see that a character sheaf $\cs{L} = (\gcs{L},\mu, \phi)$ on $G$ is commutative if it satisfies only one additional condition: that
+\[
+\begin{tikzcd}
+\gcs{L} \arrow{r}{\mu} \arrow{dr}[swap]{\mu}& \gcs{L} \boxtimes \gcs{L} \arrow{d}{\iso}\\
+&  \gcs{L} \boxtimes \gcs{L}
+\end{tikzcd}
+\]
+commutes.
+Consequently, comparing with \cite{Cunningham-Roe:QCS}*{Def.
+1.1} we find conditions ({\textbf{CS}.1), ({\textbf{CS}.3) and ({\textbf{CS}.4) appearing in the definition of the category $\CS(G)$, coincide exactly with conditions ({\textbf{CCS}.1), ({\textbf{CCS}.3) and ({\textbf{CCS}.4), above.
+
+The additional condition distinguishing which character sheaves on $G$ are commutative, has several benefits, as we will see in this note.
+\begin{enumerate}
+\labitem{(1)}{b1}
+A character sheaf $\cs{L}$ on $G$ is invisible if and only if $\cs{L}$ is not commutative.
+Recall from \cite{Cunningham-Roe:QCS}*{Def. 2.8} that a character sheaf $\cs{L}$ in $G$ is {\it invisible} if $\cs{L}  \ncong \EE$ yet $\trFrob{\cs{L}} =1$.
+These are exactly the non-trivial character sheaves in the kernel of the surjective group homomorphism $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ given by the trace of Frobenius.
+\labitem{(2)}{b2}
+This note shows that $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ admits a canonical section, and thus a splitting of the short exact sequence 
+\[
+\begin{tikzcd}
+0 \arrow{r} & \Hh^2(\pi_0(\bG),\EEx)^{\Weil{}} \arrow{r} & \CSiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0
+\end{tikzcd}
+\]
+found in \cite{Cunningham-Roe:QCS}*{Thm. 3.6}.
+\labitem{(3)}{b3}
+Like the category $\CS(G)$ of character sheaves on $G$, $\CCS(G)$ is a rigid monoidal category, described completely in \cite{Cunningham-Roe:QCS}.
+Since $\CCS(G)$ is a full subcategory of $\CS(G)$, and since Items \ref{b1} and \ref{b2} above show $\CCSiso{G} \iso G(\Fq)^*$, canonically, the category $\CCS(G)$ is now completely described by the following consequence of \cite{Cunningham-Roe:QCS}*{Thm.
+3.9}:
+\[
+\Aut(\cs{L}) \iso  \Hh^1(\pi_0(\bG), \EEx)^{\Weil{}}
+\]
+in $\CCS(G)$, for every commutative character sheaf $\cs{L}$ on $G$.
+\end{enumerate}
 

### 2015-07-23 followup.tex
Adding theorem saying TrFrob is iso
Small improvements

@@
 Recall from \cite{Cunningham-Roe:QCS}*{Def. 2.8} that a character sheaf $\cs{L}$ in $G$ is {\it invisible} if $\cs{L}  \ncong \EE$ yet $\trFrob{\cs{L}} =1$.
-These are exactly the non-trivial character sheaves in the kernel of the surjective group homomorphism $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ given by the trace of Frobenius.
+These are exactly the non-trivial character sheaves in the kernel of the surjective group homomorphism 
+\[
+\TrFrob{G} : \CSiso{G} \to G(\Fq)^*
+\]
+ given by the trace of Frobenius.
 \labitem{(2)}{b2}
@@
 \labitem{(3)}{b3}
-Like the category $\CS(G)$ of character sheaves on $G$, $\CCS(G)$ is a rigid monoidal category, described completely in \cite{Cunningham-Roe:QCS}.
-Since $\CCS(G)$ is a full subcategory of $\CS(G)$, and since Items \ref{b1} and \ref{b2} above show $\CCSiso{G} \iso G(\Fq)^*$, canonically, the category $\CCS(G)$ is now completely described by the following consequence of \cite{Cunningham-Roe:QCS}*{Thm.
-3.9}:
+Like the category $\CS(G)$ of character sheaves on $G$, which described completely in \cite{Cunningham-Roe:QCS}, $\CCS(G)$ is a rigid monoidal category.
+Since $\CCS(G)$ is a full subcategory of $\CS(G)$, and since Item \ref{b2} above shows $\CCSiso{G} \iso G(\Fq)^*$, canonically, the category $\CCS(G)$ is now completely described by the following consequence of \cite{Cunningham-Roe:QCS}*{Thm.
+3.9}: in $\CCS(G)$, every morphism $\cs{L} \to \cs{L}'$ is either trivial (zero on stalks) or and isomorphism, and
 \[
-\Aut(\cs{L}) \iso  \Hh^1(\pi_0(\bG), \EEx)^{\Weil{}}
+\Aut(\cs{L}) \iso  \Hh^1(\pi_0(\bG), \EEx)^{\Weil{}}.
 \]
-in $\CCS(G)$, for every commutative character sheaf $\cs{L}$ on $G$.
+Consequently, we have a complete description of category $\CCS(G)$.
 \end{enumerate}

### 2015-07-23 followup.tex
Fixing references, starting proof of theorem that trace of frobenius is an iso

@@
 \newcommand{\QCSiso}[1]{\QCS(#1)_{/\text{iso}}}
-\newcommand{\CCSiso}[1]{\CS(#1)_{/\text{iso}}}
+\newcommand{\CCSiso}[1]{\CCS(#1)_{/\text{iso}}}
 %% Labeled items
@@
   \bm_3^*\gcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu} 
-    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id}  && \gcs{L} \arrow{r}{\mu} \arrow{dr}[swap]{\mu}& \gcs{L} \boxtimes \gcs{L} \arrow{d}{\iso}\\
+    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id}  && \bm^*\gcs{L} \arrow{r}{\mu} \arrow{dr}[swap]{\mu}& \gcs{L} \boxtimes \gcs{L} \arrow{d}{\iso}\\
     \gcs{L} \boxtimes \bm^* \gcs{L} \arrow{rr}{\id \boxtimes \mu}
@@
 
-With reference to \cite{Cunningham-Roe:QCS}*{Def. 1.1}, a we see that a character sheaf $\cs{L} = (\gcs{L},\mu, \phi)$ on $G$ is commutative if it satisfies only one additional condition: that
+With reference to \cite{cunningham-roe:13a}*{Def. 1.1}, a we see that a character sheaf $\cs{L} = (\gcs{L},\mu, \phi)$ on $G$ is commutative if it satisfies only one additional condition: that
 \[
@@
 commutes.
-Consequently, comparing with \cite{Cunningham-Roe:QCS}*{Def.
-1.1} we find conditions ({\textbf{CS}.1), ({\textbf{CS}.3) and ({\textbf{CS}.4) appearing in the definition of the category $\CS(G)$, coincide exactly with conditions ({\textbf{CCS}.1), ({\textbf{CCS}.3) and ({\textbf{CCS}.4), above.
+Consequently, comparing with \cite{cunningham-roe:13a}*{Def.
+1.1} we find conditions (\textbf{CS}.1), (\textbf{CS}.3) and (\textbf{CS}.4) appearing in the definition of the category $\CS(G)$, coincide exactly with conditions (\textbf{CCS}.1), (\textbf{CCS}.3) and (\textbf{CCS}.4), above.
 
@@
 A character sheaf $\cs{L}$ on $G$ is invisible if and only if $\cs{L}$ is not commutative.
-Recall from \cite{Cunningham-Roe:QCS}*{Def. 2.8} that a character sheaf $\cs{L}$ in $G$ is {\it invisible} if $\cs{L}  \ncong \EE$ yet $\trFrob{\cs{L}} =1$.
+Recall from \cite{cunningham-roe:13a}*{Def. 2.8} that a character sheaf $\cs{L}$ in $G$ is {\it invisible} if $\cs{L}  \ncong \EE$ yet $\trFrob{\cs{L}} =1$.
 These are exactly the non-trivial character sheaves in the kernel of the surjective group homomorphism 
@@
 \]
-found in \cite{Cunningham-Roe:QCS}*{Thm. 3.6}.
+found in \cite{cunningham-roe:13a}*{Thm. 3.6}.
 \labitem{(3)}{b3}
-Like the category $\CS(G)$ of character sheaves on $G$, which described completely in \cite{Cunningham-Roe:QCS}, $\CCS(G)$ is a rigid monoidal category.
-Since $\CCS(G)$ is a full subcategory of $\CS(G)$, and since Item \ref{b2} above shows $\CCSiso{G} \iso G(\Fq)^*$, canonically, the category $\CCS(G)$ is now completely described by the following consequence of \cite{Cunningham-Roe:QCS}*{Thm.
+Like the category $\CS(G)$ of character sheaves on $G$, which described completely in \cite{cunningham-roe:13a}, $\CCS(G)$ is a rigid monoidal category.
+Since $\CCS(G)$ is a full subcategory of $\CS(G)$, and since Item \ref{b2} above shows $\CCSiso{G} \iso G(\Fq)^*$, canonically, the category $\CCS(G)$ is now completely described by the following consequence of \cite{cunningham-roe:13a}*{Thm.
 3.9}: in $\CCS(G)$, every morphism $\cs{L} \to \cs{L}'$ is either trivial (zero on stalks) or and isomorphism, and
@@
 
-\begin{lemma}
+\begin{lemma} \label{lem:symtriv}
 Let $\bG$ be a commutative group.  Then the only symmetric class in $\Hh^2(\bG, \EEx)$ is the trivial class.
@@
 \[
-(x,y) \mapsto f(x,y) - f(y,x).
+(x,y) \mapsto \frac{f(x,y)}{f(y,x)}.
 \]
@@
 \begin{theorem}
-Commutative.
+If $G$ is a smooth commutative group scheme over $\Fq$ then $\TrFrob{G} : \CCSiso{G} \to G(\Fq)^*$ is an isomorphism.
 \end{theorem}
 
+\begin{proof}
+Suppose first that $G$ is \'etale.  Consider the isomorphism of short exact sequences
+\[
+\begin{tikzcd}
+ 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \CSiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
+  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\bG,\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1(\bG,\EEx)) \arrow{r} & 0
+ \end{tikzcd}
+ \]
+from \cite{cunningham-roe:13a}*{Prop. 2.7}.  For a character sheaf $\cs{L}$ on $G$, recall that $S_G$ maps
+$[\cs{L}]$ to $[\alpha \oplus \beta]$, where $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$ is obtained from $\mu$ and
+$\beta \in C^1(\Weil{}, C^1(\bG, \EEx))$ is obtained from $\phi$.  Suppose that $\cs{L}$ is a commutative character sheaf
+and $\TrFrob(\cs{L}) = 1$.  Then $S_G([\cs{L}])$ is in the image of $\Hh^2(\bG, \EEx)^\Weil{}$, so is cohomologous to
+$[\alpha', 0]$.  Since $\alpha$ is symmetric and coboundaries are symmetric, $\alpha'$ is symmetric as well.
+So by Lemma \ref{lem:symtriv}
+\end{proof}
+
+\bibliography{bibliography/Biblio}
+
 \end{document}

### 2015-07-24 followup.tex
Types

@@
 \newcommand{\comp}{\Pi} % Component group
+\newcommand{\G}{\textbf{G}}
 %%%%%%%%%%%%%%% NAMED OPERATORS %%%%%%%%%%%%%%%
@@
 \newcommand{\Spec}[1]{{\operatorname{Spec}(#1)}}
+\newcommand{\op}{_{\operatorname{op}}}
 %%%%%%%%%%%% MISCELLANEOUS OPERATORS %%%%%%%%%%%%
@@
 
+\begin{abstract}
+Abstract goes here
+\end{abstract}
+
 \maketitle
 
+\section*{Introduction}
+
+Fragments: 
+The additional condition distinguishing which character sheaves on $G$ are commutative, has several benefits, as we will see in this note.
+\begin{enumerate}
+\labitem{(1)}{b1}
+A character sheaf $\cs{L}$ on $G$ is invisible if and only if $\cs{L}$ is not commutative.
+Recall from \cite{cunningham-roe:13a}*{Def. 2.8} that a character sheaf $\cs{L}$ in $G$ is {\it invisible} if $\cs{L}  \ncong \EE$ yet $\trFrob{\cs{L}} =1$.
+These are exactly the non-trivial character sheaves in the kernel of the surjective group homomorphism 
+\[
+\TrFrob{G} : \CSiso{G} \to G(\Fq)^*
+\]
+ given by the trace of Frobenius.
+\labitem{(2)}{b2}
+This note shows that $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ admits a canonical section, and thus a splitting of the short exact sequence 
+\[
+\begin{tikzcd}
+0 \arrow{r} & \Hh^2(\pi_0(\bG),\EEx)^{\Weil{}} \arrow{r} & \CSiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0
+\end{tikzcd}
+\]
+found in \cite{cunningham-roe:13a}*{Thm. 3.6}.
+\labitem{(3)}{b3}
+Like the category $\CS(G)$ of character sheaves on $G$, which described completely in \cite{cunningham-roe:13a}, $\CCS(G)$ is a rigid monoidal category.
+Since $\CCS(G)$ is a full subcategory of $\CS(G)$, and since Item \ref{b2} above shows $\CCSiso{G} \iso G(\Fq)^*$, canonically, the category $\CCS(G)$ is now completely described by the following consequence of \cite{cunningham-roe:13a}*{Thm.
+3.9}: in $\CCS(G)$, every morphism $\cs{L} \to \cs{L}'$ is either trivial (zero on stalks) or and isomorphism, and
+\[
+\Aut(\cs{L}) \iso  \Hh^1(\pi_0(\bG), \EEx)^{\Weil{}}.
+\]
+Consequently, we have a complete description of category $\CCS(G)$.
+\end{enumerate}
+
 \section{Definitions and Recollections}
+
+Let $G$ be a smooth group scheme over a finite field $\Fq$; that is, let $G$ be a group scheme over $\Fq$ for which the structure morphism $G \to \Spec{\Fq}$ is smooth in the sense of [include reference for this definition].
+This implies $G \to \Spec{\Fq}$ is locally of finite type; it does not imply the map is of finite type.
+We remark that the identity component $G^0$ of $G$ is of finite type over $\Fq$, while the component group scheme $\pi_0(G)$ of $G$ is an \'etale group scheme over $\Fq$, and both are smooth over $\Fq$.
+
+Write $m : G \times G \to G$ for the multiplication morphism.
+Let $\theta : G\times G \to G\times G$ be given by $\theta(g,h) = (h,g)$
+and define $m\op : G \times G \to G$ by $m\op = m \circ \theta$.
+For any local system $\gcs{L}$ on $\bG \ceq G \times_{\Spec{\Fq}} \Spec{\bFq}$ there is an isomorphism $\gcs{L} \boxtimes \gcs{L} \to {\bar \theta}^*(\gcs{L} \boxtimes \gcs{L})$ given on stalks by $\gcs{L}_{g} \otimes \gcs{L}_{h} \to \gcs{L}_{h} \otimes \gcs{L}_{g}$.
 
@@
 $\ell$-adic sheaf on $\bG$, {\it lisse} on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
-\labitem{(CCS.2)}{CS.2} $\mu: \bm^* \gcs{L} \to \LxL$ is an isomorphism of
-sheaves on $\bGxG$ such that the following diagrams commute,
-  where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$,
+\labitem{(CCS.2)}{CS.2} $\mu: \bm^* \gcs{L} \to \gcs{L} \boxtimes \gcs{L}$ is an isomorphism of
+sheaves on $\bG \times \bG$ and there is an isomorphism ${\bar m}^* \gcs{L} \to {\bar m}\op^* \gcs{L}$ such that the following diagrams commute,
   \[
@@
   \bm_3^*\gcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu} 
-    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id}  && \bm^*\gcs{L} \arrow{r}{\mu} \arrow{dr}[swap]{\mu}& \gcs{L} \boxtimes \gcs{L} \arrow{d}{\iso}\\
+    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id}  && \bm^*\gcs{L} \arrow{d} \arrow{r}{\mu} & \gcs{L} \boxtimes \gcs{L} \arrow{d}\\
     \gcs{L} \boxtimes \bm^* \gcs{L} \arrow{rr}{\id \boxtimes \mu}
-    &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL && &  \gcs{L} \boxtimes \gcs{L}
+    &  &  \gcs{L} \boxtimes \gcs{L} \boxtimes \gcs{L} && {\bar m}\op^*\gcs{L} \arrow{r}{{\bar \theta}^*\mu} &  {\bar \theta}^*(\gcs{L} \boxtimes \gcs{L})
   \end{tikzcd}
   \]
-where 
-$\LxL \to \LxL$ given by $x\otimes y \mapsto y \otimes x$, by which we meant the case of the sheaf isomorphism $\cs{L}_1 \boxtimes \cs{L}_2 \to \cs{L}_2\boxtimes \cs{L}_1$ when $\cs{L}_1 = \cs{L}_2 = \cs{L}$.
+where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$,
+ and where 
+$\gcs{L} \boxtimes \gcs{L} \to {\bar \theta}^*(\gcs{L} \boxtimes \gcs{L})$ is the isomorphism of sheaves  above;
+%given by $x\otimes y \mapsto y \otimes x$, by which we meant the case of the sheaf isomorphism $\cs{L}_1 \boxtimes \cs{L}_2 \to \cs{L}_2\boxtimes \cs{L}_1$ when $\cs{L}_1 = \cs{L}_2 = \cs{L}$.
 \labitem{(CCS.3)}{CS.3} $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an
@@
 
-With reference to \cite{cunningham-roe:13a}*{Def. 1.1}, a we see that a character sheaf $\cs{L} = (\gcs{L},\mu, \phi)$ on $G$ is commutative if it satisfies only one additional condition: that
-\[
-\begin{tikzcd}
-\gcs{L} \arrow{r}{\mu} \arrow{dr}[swap]{\mu}& \gcs{L} \boxtimes \gcs{L} \arrow{d}{\iso}\\
-&  \gcs{L} \boxtimes \gcs{L}
-\end{tikzcd}
-\]
-commutes.
+\begin{lemma}
+If the isomorphism ${\bar m}^* \gcs{L} \to {\bar m}\op^* \gcs{L}$ exists, then it is unique.
+\end{lemma}
+\begin{proof}
+\end{proof}
+
+\begin{lemma}
+If $G$ is also commutative, then $\CCS(G)$ is a full subcategory of $\CS(G)$, the 
+later defined in \cite{cunningham-roe:13a}.
+\end{lemma}
+
+\begin{proof}
+ a we see that a character sheaf $\cs{L} = (\gcs{L},\mu, \phi)$ on $G$ is commutative if it satisfies only one additional condition:
 Consequently, comparing with \cite{cunningham-roe:13a}*{Def.
 1.1} we find conditions (\textbf{CS}.1), (\textbf{CS}.3) and (\textbf{CS}.4) appearing in the definition of the category $\CS(G)$, coincide exactly with conditions (\textbf{CCS}.1), (\textbf{CCS}.3) and (\textbf{CCS}.4), above.
+\end{proof}
 
-The additional condition distinguishing which character sheaves on $G$ are commutative, has several benefits, as we will see in this note.
-\begin{enumerate}
-\labitem{(1)}{b1}
-A character sheaf $\cs{L}$ on $G$ is invisible if and only if $\cs{L}$ is not commutative.
-Recall from \cite{cunningham-roe:13a}*{Def. 2.8} that a character sheaf $\cs{L}$ in $G$ is {\it invisible} if $\cs{L}  \ncong \EE$ yet $\trFrob{\cs{L}} =1$.
-These are exactly the non-trivial character sheaves in the kernel of the surjective group homomorphism 
-\[
-\TrFrob{G} : \CSiso{G} \to G(\Fq)^*
-\]
- given by the trace of Frobenius.
-\labitem{(2)}{b2}
-This note shows that $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ admits a canonical section, and thus a splitting of the short exact sequence 
-\[
-\begin{tikzcd}
-0 \arrow{r} & \Hh^2(\pi_0(\bG),\EEx)^{\Weil{}} \arrow{r} & \CSiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0
-\end{tikzcd}
-\]
-found in \cite{cunningham-roe:13a}*{Thm. 3.6}.
-\labitem{(3)}{b3}
-Like the category $\CS(G)$ of character sheaves on $G$, which described completely in \cite{cunningham-roe:13a}, $\CCS(G)$ is a rigid monoidal category.
-Since $\CCS(G)$ is a full subcategory of $\CS(G)$, and since Item \ref{b2} above shows $\CCSiso{G} \iso G(\Fq)^*$, canonically, the category $\CCS(G)$ is now completely described by the following consequence of \cite{cunningham-roe:13a}*{Thm.
-3.9}: in $\CCS(G)$, every morphism $\cs{L} \to \cs{L}'$ is either trivial (zero on stalks) or and isomorphism, and
-\[
-\Aut(\cs{L}) \iso  \Hh^1(\pi_0(\bG), \EEx)^{\Weil{}}.
-\]
-Consequently, we have a complete description of category $\CCS(G)$.
-\end{enumerate}
+\begin{remark}
+In fact, \cite{cunningham-roe:13a}*{Def.
+1.1} makes sense even if $G$ is not commutative.
+Extending that definition to include smooth group schemes over $\Fq$, it is again true that $\CCS(G)$ is a full subcategory of $\CS(G)$.
+\end{remark}
 
@@
 
+\section{Applications}
+
+\subsection{Geometrization of generic types supercuspidal representations}
+
+As proved in \cite{kim:exhaustion}, many (complex) supercuspidal representations of $p$-adic groups can be built from the generic data of \cite{yu:construction}*{\S 15} and, moreover, that the type of the resulting supercuspidal representations can be constructed directly from the generic data.
+Let us refer to the types arising in this manner as {\it generic types}.
+In this section we show that, after fixing an isomorphism $\CC \approx \EE$, every generic type is geometrizable, in the sense that every part of generic type admits a description as a sheaf, from which the type can be recovered.
+
+Let $K$ be a $p$-adic field.
+Let $\G$ be a connected reductive linear algebraic group over $K$.
+A generic datum is a triple $(\vec{\G}, \pi_0, \vec{\phi})$ where: $\vec{\G}$ is a tower of $p$-adic groups $\G^0 \subsetneq \G^1 \subsetneq \cdots \G^d = \G$; $\pi_0$ is a depth-zero representation of $\G^0(F)$, and $\vec{\phi} = (\phi_0, \ldots , \phi_{d-1})$ where $\phi_i : \G^i(K) \to \EEx$ is a quasicharacter (continuous group homomorphism).
+In \cite{yu:smooth}*{\S 10.5}, it is shown that
+
+\subsection{Stacky abelianization}
+
 \bibliography{bibliography/Biblio}

### 2015-07-24 followup.tex
Working on Section 2

--- 2015-07-23 followup.tex
@@
 
+For a character sheaf $\cs{L}$ on $G$, recall from \cite{cunningham-roe:13a}*{\S 2.3} that $S_G : \CSiso{G} \to \Hh^2(E_G^\bullet)$ maps
+$[\cs{L}]$ to $[\alpha \oplus \beta]$, where $E_G^\bullet$ is the total space of the zeroth page
+of the Hochschild-Serre spectral sequence, $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$ is obtained from $\mu$ and
+$\beta \in C^1(\Weil{}, C^1(\bG, \EEx))$ is obtained from $\phi$.
+
+\begin{lemma} \label{lem:conncomm}
+If $G$ is a connected commutative algebraic group over $\Fq$ then every character sheaf on $G$ is commutative.
+\end{lemma}
+
+\begin{proof}
+We can use \'etale descent to see that pullback by the Lang isogeny defines an equivalence
+of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.  Thus every character
+sheaf on $G$ arises through the Lang isogeny; since the covering group is $G$ itself, which is commutative,
+every character sheaf on $G$ is commutative.
+\end{proof}
+
 \begin{theorem}
@@
  \]
-from \cite{cunningham-roe:13a}*{Prop. 2.7}.  For a character sheaf $\cs{L}$ on $G$, recall that $S_G$ maps
-$[\cs{L}]$ to $[\alpha \oplus \beta]$, where $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$ is obtained from $\mu$ and
-$\beta \in C^1(\Weil{}, C^1(\bG, \EEx))$ is obtained from $\phi$.  Suppose that $\cs{L}$ is a commutative character sheaf
-and $\TrFrob(\cs{L}) = 1$.  Then $S_G([\cs{L}])$ is in the image of $\Hh^2(\bG, \EEx)^\Weil{}$, so is cohomologous to
+from \cite{cunningham-roe:13a}*{Prop. 2.7}.
+
+Suppose that $\cs{L}$ is a commutative character sheaf
+with $\TrFrob(\cs{L}) = 1$.  Then $S_G([\cs{L}])$ is in the image of $\Hh^2(\bG, \EEx)^\Weil{}$, so is cohomologous to
 $[\alpha', 0]$.  Since $\alpha$ is symmetric and coboundaries are symmetric, $\alpha'$ is symmetric as well.
-So by Lemma \ref{lem:symtriv}
+So by Lemma \ref{lem:symtriv}, $\alpha'$ is cohomologically trivial, and thus $[\cs{L}]$ is trivial as well.
+
+To see that $\TrFrob{G}$ is still surjective on $\CCSiso{G}$, note that the character sheaf constructed in the proof of
+\cite{cunningham-roe:13a}*{Prop. 2.6} has trivial $\alpha$, and is thus commutative.
+
+For general smooth commutative group schemes, we use Lemma \ref{lem:conncomm} and the snake lemma.
 \end{proof}
+
+\begin{remark}
+Since $\Hh^0(\Weil{},\Hh^2(\bG,\EEx))$ is not necessarily trivial \cite{cunningham-roe:13a}*{Ex. 2.10}, the functor
+$\CCS(G) \to \CS(G)$ is not an equivalence of categories in general.
+\end{remark}
 

### 2015-07-24 followup.tex
Fixing some references

@@
 
-As proved in \cite{kim:exhaustion}, many (complex) supercuspidal representations of $p$-adic groups can be built from the generic data of \cite{yu:construction}*{\S 15} and, moreover, that the type of the resulting supercuspidal representations can be constructed directly from the generic data.
+As proved in \cite{kim:07a}, many (complex) supercuspidal representations of $p$-adic groups can be built from the generic data of \cite{yu:01a}*{\S 15} and, moreover, that the type of the resulting supercuspidal representations can be constructed directly from the generic data.
 Let us refer to the types arising in this manner as {\it generic types}.
@@
 A generic datum is a triple $(\vec{\G}, \pi_0, \vec{\phi})$ where: $\vec{\G}$ is a tower of $p$-adic groups $\G^0 \subsetneq \G^1 \subsetneq \cdots \G^d = \G$; $\pi_0$ is a depth-zero representation of $\G^0(F)$, and $\vec{\phi} = (\phi_0, \ldots , \phi_{d-1})$ where $\phi_i : \G^i(K) \to \EEx$ is a quasicharacter (continuous group homomorphism).
-In \cite{yu:smooth}*{\S 10.5}, it is shown that
+In \cite{yu:03a}*{\S 10.5}, it is shown that
 

### 2015-07-24 followup.tex
Application to Yu

@@
 
-\subsection{Geometrization of generic types supercuspidal representations}
+\subsection{Quasicharacter sheaves}
 
-As proved in \cite{kim:07a}, many (complex) supercuspidal representations of $p$-adic groups can be built from the generic data of \cite{yu:01a}*{\S 15} and, moreover, that the type of the resulting supercuspidal representations can be constructed directly from the generic data.
-Let us refer to the types arising in this manner as {\it generic types}.
-In this section we show that, after fixing an isomorphism $\CC \approx \EE$, every generic type is geometrizable, in the sense that every part of generic type admits a description as a sheaf, from which the type can be recovered.
+Let $K$ be a local field with residue field $\Fq$.
+Let $\underline{G}$ be a smooth group scheme over $K$.
+Set $G_n = \Gr^R_n(\underline{G})$; this is a smooth group scheme over $\Fq$.
+Set $G = \Gr^R_n(\underline{G})$; this is a group scheme over $\Fq$ equipped with $G = \varprojlim_{n\in \NN} G_n$.
+Let $\QCS(\underline{G})$ be the category of commutative character sheaves on $G$. . . .  as in \cite{cunningham-roe:13a}.
 
-Let $K$ be a $p$-adic field.
-Let $\G$ be a connected reductive linear algebraic group over $K$.
-A generic datum is a triple $(\vec{\G}, \pi_0, \vec{\phi})$ where: $\vec{\G}$ is a tower of $p$-adic groups $\G^0 \subsetneq \G^1 \subsetneq \cdots \G^d = \G$; $\pi_0$ is a depth-zero representation of $\G^0(F)$, and $\vec{\phi} = (\phi_0, \ldots , \phi_{d-1})$ where $\phi_i : \G^i(K) \to \EEx$ is a quasicharacter (continuous group homomorphism).
-In \cite{yu:03a}*{\S 10.5}, it is shown that
+\begin{corollary}\label{cor:QCS}
+$\Hom(\underline{G}(\OK),\EEx) \iso \QCSiso{\underline{G}}$.
+\end{corollary}
+
+\subsection{Geometrization of generic data for supercuspidal representations}
+
+As proved in \cite{kim:exhaustion}, many (complex) supercuspidal representations of $p$-adic groups can be built from the generic data of \cite{yu:construction}*{\S 15} and, moreover, the type (in the sense of \cite{bushnell-kutzko:98a}) of the resulting supercuspidal representations can be constructed directly from the generic data.
+%Let us refer to the types arising in this manner as {\it generic types}.
+In this section we show that, after fixing an isomorphism $\CC \approx \EE$, every generic type is geometrizable, in the sense that every part of generic type admits a description as a perverse sheaf on a scheme over a finite field, from which the type can be recovered using the trace of Frobenius.
+
+Let $K$ be a $p$-adic field. Let $\G$ be a connected reductive linear algebraic group over $K$. 
+A generic datum is a triple $(\vec{\G}, \pi_0, \vec{\phi})$ where: $\vec{\G}$ is a tower of $p$-adic groups $\G^0 \subsetneq \G^1 \subsetneq \cdots  \subsetneq \G^d = \G$; $\pi_0$ is a depth-zero representation of $\G^0(F)$, and $\vec{\phi} = (\phi_0, \ldots , \phi_{d-1})$ where $\phi_i : \G^i(K) \to \EEx$ is a quasicharacter (continuous group homomorphism).
+
+%The generic datum $(\vec{\G}, \pi_0, \vec{\phi})$ determines a type (in the sense of \cite{bushnell-kutzko:98a}) $(C, \rho)$ for $\G$, as explained in \cite{yu:construction}*{\S 15}, where $C \subset \G(K)$ is compact mod centre subgroup and $\rho$ is a representation of $C$.
+In \cite{yu:smooth} it is shown that the $C$ admits a smooth integral model, in the sense that there is a smooth group scheme $\underline{C}$ over $\OK$ such that $\underline{C}(\OK) = C$.
+
+In \cite{yu:smooth} it is shown that, for $0 \leq i < d$, the $p$-adic group $\G^i(K)$ admits a smooth integral model, in the sense that there is a smooth group scheme $\underline{G}^i$ over $\OK$ such that $\underline{G}^i(\OK) = \G^i(K)$.
+Set $G^i_n \ceq \Gr^R_n(\underline{G}^i)$ and $G^i \ceq \Gr_R(\underline{G}^i)$.
+Then $G^i(\Fq) = \G^i(K)$ (canonical isomorphism of groups).
+It now follows from Corollary~\ref{cor:QCS} that the quasicharacter $\phi_i : G^i(\Fq) \to \EEx$ determines a quasicharacter sheaf $\cs{L}_i$, unique up to isomorphism, from which the quasicharacter $\phi_i$ can be recovered using the trace of Frobenius.
+For each $0\leq i < d$, let $n_i$ be the smallest non-negative integer $n$ such that $\phi_i : G^i(\Fq) \to \EEx$ factors through $G^i(\Fq) \to G^i_n(\Fq)$.
 

### 2015-07-24 followup.tex

@@
 
-As proved in \cite{kim:exhaustion}, many (complex) supercuspidal representations of $p$-adic groups can be built from the generic data of \cite{yu:construction}*{\S 15} and, moreover, the type (in the sense of \cite{bushnell-kutzko:98a}) of the resulting supercuspidal representations can be constructed directly from the generic data.
+As proved in \cite{kim:07a}, many (complex) supercuspidal representations of $p$-adic groups can be built from the generic data of \cite{yu:01a}*{\S 15} and, moreover, the type (in the sense of \cite{bushnell-kutzko:98a}) of the resulting supercuspidal representations can be constructed directly from the generic data.
 %Let us refer to the types arising in this manner as {\it generic types}.
@@
 
-In \cite{yu:smooth} it is shown that, for $0 \leq i < d$, the $p$-adic group $\G^i(K)$ admits a smooth integral model, in the sense that there is a smooth group scheme $\underline{G}^i$ over $\OK$ such that $\underline{G}^i(\OK) = \G^i(K)$.
+In \cite{yu:03a} it is shown that, for $0 \leq i < d$, the $p$-adic group $\G^i(K)$ admits a smooth integral model, in the sense that there is a smooth group scheme $\underline{G}^i$ over $\OK$ such that $\underline{G}^i(\OK) = \G^i(K)$.
 Set $G^i_n \ceq \Gr^R_n(\underline{G}^i)$ and $G^i \ceq \Gr_R(\underline{G}^i)$.

### 2015-07-24 followup.tex
Abelianisation

@@
 \newcommand{\op}{_{\operatorname{op}}}
+\newcommand{\der}{_{\operatorname{der}}}
 %%%%%%%%%%%% MISCELLANEOUS OPERATORS %%%%%%%%%%%%
@@
 
+\section{Passing to the abelianization}
+
 \section{Applications}
@@
 Let $K$ be a $p$-adic field. Let $\G$ be a connected reductive linear algebraic group over $K$. 
-A generic datum is a triple $(\vec{\G}, \pi_0, \vec{\phi})$ where: $\vec{\G}$ is a tower of $p$-adic groups $\G^0 \subsetneq \G^1 \subsetneq \cdots  \subsetneq \G^d = \G$; $\pi_0$ is a depth-zero representation of $\G^0(F)$, and $\vec{\phi} = (\phi_0, \ldots , \phi_{d-1})$ where $\phi_i : \G^i(K) \to \EEx$ is a quasicharacter (continuous group homomorphism).
+A generic datum is a triple $(\vec{\G}, \pi_0, \vec{\phi})$ where: $\vec{\G}$ is a tower of $p$-adic groups $\G^0(K) \subset \G^1(K) \subset \cdots  \subset \G^d(K) = \G(K)$ (proper containment); $\pi_0$ is a depth-zero representation of $\G^0(K)$, and $\vec{\phi} = (\phi_0, \ldots , \phi_{d-1})$ where each $\phi_i : \G^i(K) \to \EEx$ is a quasicharacter (continuous group homomorphism).
 
@@
 In \cite{yu:03a} it is shown that, for $0 \leq i < d$, the $p$-adic group $\G^i(K)$ admits a smooth integral model, in the sense that there is a smooth group scheme $\underline{G}^i$ over $\OK$ such that $\underline{G}^i(\OK) = \G^i(K)$.
-Set $G^i_n \ceq \Gr^R_n(\underline{G}^i)$ and $G^i \ceq \Gr_R(\underline{G}^i)$.
-Then $G^i(\Fq) = \G^i(K)$ (canonical isomorphism of groups).
-It now follows from Corollary~\ref{cor:QCS} that the quasicharacter $\phi_i : G^i(\Fq) \to \EEx$ determines a quasicharacter sheaf $\cs{L}_i$, unique up to isomorphism, from which the quasicharacter $\phi_i$ can be recovered using the trace of Frobenius.
-For each $0\leq i < d$, let $n_i$ be the smallest non-negative integer $n$ such that $\phi_i : G^i(\Fq) \to \EEx$ factors through $G^i(\Fq) \to G^i_n(\Fq)$.
+Set $G^i_n \ceq \Gr^R_n(\underline{G}^i)$ and $G^i \ceq \Gr_R(\underline{G}^i)$; 
+then \[G^i(\Fq) = \G^i(K)\] (canonical isomorphism of groups).
+In this way, $\vec{\G}$ determines a tower $\vec{G}$ of group schemes $G^0 \subset G^1 \subset \cdots  \subset G^{d-1}$ (proper containment) over $\Fq$, from which the tower of $p$-adic groups
+$\G^0(K) \subset \G^1(K) \subset \cdots  \subset \G^{d-1}(K)$ can be recovered.
 
-\subsection{Stacky abelianization}
+Using Corollary~\ref{cor:QCS} we see that each quasicharacter $\phi_i : G^i(\Fq) \to \EEx$ determines a quasicharacter sheaf $\cs{L}^i$, unique up to isomorphism, from which the quasicharacter $\phi_i$ can be recovered using the trace of Frobenius.
+In fact, more is true. Let $n_{\phi_i}$ be the smallest non-negative integer $n$ such that $\phi_i : G^i(\Fq) \to \EEx$ factors through $G^i(\Fq) \to G^i_n(\Fq)$.
+Then $\phi_i$ determines a commutative character sheaf $\cs{L}_{n_{\phi_i}}^i$, unique up to isomorphism, from which the quasicharacter $\phi_i$ can be recovered.
+Then $\cs{A}_i\ceq \cs{L}_{n_{\phi_i}}^i[\dim G_{n_{\phi_i}}^i]$ is a perverse sheaf on $G_{n_{\phi_i}}^i$ from which the quasicharacter $\phi_i$ can be recovered.
+In this way,  $\vec{\phi} = (\phi_0, \ldots , \phi_{d-1})$ determines perverse sheaves $\vec{\cs{A}} = (\cs{A}_0, \ldots , \cs{A}_{d-1})$ from which $\vec{\phi}$ can be recovered.
+
+Finally, consider the depth-zero supercuspidal representation $\pi_0$ of $\G^0(K)$.
+Then $\pi_0$ is produced by compact induction from representation $\sigma$ of a compact mod centre subgroup $\underline{C}_0(\OK) \subset \G^0(K)$.
+Moreover, $C_0$ admits a smooth integral model $\underline{C}$
 

### 2015-07-24 followup.tex
Shortening definition section

--- 2015-07-24 followup.tex
@@
 \newcommand{\CS}{{\mathcal{C\hskip-0.8pt S}}}
-\newcommand{\CCS}{{\mathcal{CC\hskip-0.8pt S}}}
+\newcommand{\CCS}{{\mathcal{C\hskip-.8pt C\hskip-0.8pt S}}}
 \newcommand{\bCS}{{\CS_0}}
@@
 
-Let $G$ be a smooth group scheme over a finite field $\Fq$; that is, let $G$ be a group scheme over $\Fq$ for which the structure morphism $G \to \Spec{\Fq}$ is smooth in the sense of [include reference for this definition].
-This implies $G \to \Spec{\Fq}$ is locally of finite type; it does not imply the map is of finite type.
-We remark that the identity component $G^0$ of $G$ is of finite type over $\Fq$, while the component group scheme $\pi_0(G)$ of $G$ is an \'etale group scheme over $\Fq$, and both are smooth over $\Fq$.
+Let $G$ be a smooth group scheme over a finite field $\Fq$; that is, let $G$ be a group scheme over $\Fq$
+for which the structure morphism $G \to \Spec{\Fq}$ is smooth in the sense of [include reference for this definition].
+This implies $G \to \Spec{\Fq}$ is locally of finite type, but not that it is of finite type.
+We remark that the identity component $G^0$ of $G$ is of finite type over $\Fq$, while the component group scheme
+$\pi_0(G)$ of $G$ is an \'etale group scheme over $\Fq$, and both are smooth over $\Fq$.
 
@@
 and define $m\op : G \times G \to G$ by $m\op = m \circ \theta$.
-For any local system $\gcs{L}$ on $\bG \ceq G \times_{\Spec{\Fq}} \Spec{\bFq}$ there is an isomorphism $\gcs{L} \boxtimes \gcs{L} \to {\bar \theta}^*(\gcs{L} \boxtimes \gcs{L})$ given on stalks by $\gcs{L}_{g} \otimes \gcs{L}_{h} \to \gcs{L}_{h} \otimes \gcs{L}_{g}$.
+For any local system $\gcs{L}$ on $\bG \ceq G \times_{\Spec{\Fq}} \Spec{\bFq}$ there is an isomorphism
+$\vartheta : \LxL \to {\bar \theta}^*(\LxL)$ given on stalks by the canonical map
+$\gcs{L}_{g} \otimes \gcs{L}_{h} \to \gcs{L}_{h} \otimes \gcs{L}_{g}$.
+
+Recall \cite{cunningham-roe:13a}*{Def. 1.1} that a character sheaf on $G$ is a triple $\cs{L} \ceq (\gcs{L}, \mu, \phi)$,
+where $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, $\mu : \bm^* \gcs{L} \to \LxL$ is an isomorphism
+of sheaves on $\bG \times \bG$, and $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an isomorphism of sheaves on $\bG$.
+In \emph{loc. cit.}, $G$ was assumed to be commutative, but the same definition makes sense for non-commutative $G$.
+We will denote the category of character sheaves on $G$ by $\CS(G)$.
 
 \begin{definition}\label{def:CCS}
-A \emph{commutative character sheaf on $G$} is a triple
-$\cs{L}\ceq (\gcs{L},\mu,\phi)$ where:
-\begin{enumerate}
-\labitem{(CCS.1)}{CS.1} $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, by which we mean a constructible
-$\ell$-adic sheaf on $\bG$, {\it lisse} on each connected component of $\bG$, whose stalks are one-dimensional $\EE$-vector spaces;
-\labitem{(CCS.2)}{CS.2} $\mu: \bm^* \gcs{L} \to \gcs{L} \boxtimes \gcs{L}$ is an isomorphism of
-sheaves on $\bG \times \bG$ and there is an isomorphism ${\bar m}^* \gcs{L} \to {\bar m}\op^* \gcs{L}$ such that the following diagrams commute,
+A character sheaf on $G$ is \emph{commutative} if there is an isomorphism ${\bar m}^* \gcs{L} \to {\bar m}\op^* \gcs{L}$
+such that the following diagram commutes,
   \[
   \begin{tikzcd}[row sep=30]
-  \bm_3^*\gcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu} 
-    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id}  && \bm^*\gcs{L} \arrow{d} \arrow{r}{\mu} & \gcs{L} \boxtimes \gcs{L} \arrow{d}\\
-    \gcs{L} \boxtimes \bm^* \gcs{L} \arrow{rr}{\id \boxtimes \mu}
-    &  &  \gcs{L} \boxtimes \gcs{L} \boxtimes \gcs{L} && {\bar m}\op^*\gcs{L} \arrow{r}{{\bar \theta}^*\mu} &  {\bar \theta}^*(\gcs{L} \boxtimes \gcs{L})
+   \bm^*\gcs{L} \arrow{d} \arrow{r}{\mu} & \LxL \arrow{d}{\vartheta}\\
+   \bm\op^*\gcs{L} \arrow{r}{{\bar \theta}^*\mu} &  {\bar \theta}^*(\LxL)
   \end{tikzcd}
   \]
-where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$,
- and where 
-$\gcs{L} \boxtimes \gcs{L} \to {\bar \theta}^*(\gcs{L} \boxtimes \gcs{L})$ is the isomorphism of sheaves  above;
-%given by $x\otimes y \mapsto y \otimes x$, by which we meant the case of the sheaf isomorphism $\cs{L}_1 \boxtimes \cs{L}_2 \to \cs{L}_2\boxtimes \cs{L}_1$ when $\cs{L}_1 = \cs{L}_2 = \cs{L}$.
-\labitem{(CCS.3)}{CS.3} $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an
-  isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with
-  $\mu$ in the sense that the following diagram commutes.
-  \[
-  \begin{tikzcd}[row sep=20]
-  \Frob{\GxxG}^* \bm^* \gcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
-    && \Frob{\GxxG}^*(\LxL)\\
-    \arrow[equal]{u} \bm^*  \Frob{G}^* \gcs{L} \arrow[swap]{d}{\bm^* \phi}
-    && \Frob{G}^*\gcs{L}\boxtimes \Frob{G}^*\gcs{L} \dar{\phi\boxtimes \phi} \arrow[equal]{u} \\
-    \bm^*\gcs{L} \arrow{rr}{\mu}
-    && \LxL
-  \end{tikzcd}
-  \]
-\end{enumerate}
-Morphisms of character sheaves are defined in the natural way:
-\begin{enumerate}
-\labitem{(CCS.4)}{CS.4} if $\cs{L} = (\gcs{L},\mu,\phi)$ and
-  $\cs{L'} = (\gcs{L'},\mu',\phi')$ are character sheaves on $G$ then
-  a morphism $\rho : \cs{L} \to \cs{L}'$ is a map $\brho : \gcs{L} \to \gcs{L'}$
-  of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
-  \[
-  \begin{tikzcd}[column sep=40]
-  \Frob{G}^* \gcs{L} \rar{\Frob{G}^* \brho} \arrow[swap]{d}{\phi} & \Frob{G}^* \gcs{L'} \dar{\phi'}
-  & & \arrow[swap]{d}{\mu} \bm^* \gcs{L} \rar{\bm^* \brho} & \bm^* \gcs{L'} \dar{\mu'} \\
-  \gcs{L} \rar{\brho} & \gcs{L'}
-  & {} & \LxL \rar{\tight{1}{\rho\boxtimes \rho}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
-  \end{tikzcd}
-  \]
-\end{enumerate}
- The category of character sheaves on $G$ will be denoted by $\CCS(G)$.
  \end{definition}
+
+ Write $\CCS(G)$ for the full subcategory of $\CS(G)$ consisting of commutative character sheaves.
 
@@
 \end{proof}
-
-\begin{lemma}
-If $G$ is also commutative, then $\CCS(G)$ is a full subcategory of $\CS(G)$, the 
-later defined in \cite{cunningham-roe:13a}.
-\end{lemma}
-
-\begin{proof}
- a we see that a character sheaf $\cs{L} = (\gcs{L},\mu, \phi)$ on $G$ is commutative if it satisfies only one additional condition:
-Consequently, comparing with \cite{cunningham-roe:13a}*{Def.
-1.1} we find conditions (\textbf{CS}.1), (\textbf{CS}.3) and (\textbf{CS}.4) appearing in the definition of the category $\CS(G)$, coincide exactly with conditions (\textbf{CCS}.1), (\textbf{CCS}.3) and (\textbf{CCS}.4), above.
-\end{proof}
-
-\begin{remark}
-In fact, \cite{cunningham-roe:13a}*{Def.
-1.1} makes sense even if $G$ is not commutative.
-Extending that definition to include smooth group schemes over $\Fq$, it is again true that $\CCS(G)$ is a full subcategory of $\CS(G)$.
-\end{remark}
 

### 2015-07-25 followup.tex
Push before bed - types

@@
   \]
+ Write $\CCS(G)$ for the full subcategory of $\CS(G)$ consisting of commutative character sheaves.
  \end{definition}
-
- Write $\CCS(G)$ for the full subcategory of $\CS(G)$ consisting of commutative character sheaves.
 
@@
 
-\subsection{Geometrization of generic data for supercuspidal representations}
+\subsection{Geometrization of generic types for supercuspidal representations}
 
 As proved in \cite{kim:07a}, many (complex) supercuspidal representations of $p$-adic groups can be built from the generic data of \cite{yu:01a}*{\S 15} and, moreover, the type (in the sense of \cite{bushnell-kutzko:98a}) of the resulting supercuspidal representations can be constructed directly from the generic data.
-%Let us refer to the types arising in this manner as {\it generic types}.
+Let us refer to the types arising in this manner as {\it generic types}.
 In this section we show that, after fixing an isomorphism $\CC \approx \EE$, every generic type is geometrizable, in the sense that every part of generic type admits a description as a perverse sheaf on a scheme over a finite field, from which the type can be recovered using the trace of Frobenius.

### 2015-07-25 followup.tex
Adding to Abelianization section

--- 2015-07-24 followup.tex
@@
 \DeclareMathOperator{\Tor}{Tor}
+\DeclareMathOperator{\SL}{SL}
+\DeclareMathOperator{\PGL}{PGL}
 \newcommand{\gal}[1]{{\operatorname{Gal}\hskip-1pt\left( {\bar #1}/#1 \right)}}
@@
 
-\begin{theorem}
+\begin{theorem} \label{thm:trfrobiso}
 If $G$ is a smooth commutative group scheme over $\Fq$ then $\TrFrob{G} : \CCSiso{G} \to G(\Fq)^*$ is an isomorphism.
@@
 \section{Passing to the abelianization}
+
+ Let $G$ be a smooth group scheme over $\Fq$ and let $C = [G, G]$ be its commutator subgroup.
+
+ \begin{proposition}
+ Every commutative character sheaf $\cs{L}$ on $G$ is equivariant for the left translation action of $C$ on $G$.
+ \end{proposition}
+
+ \begin{proof}
+
+ \end{proof}
+
+ \begin{corollary}
+ Trace of Frobenius induces an isomorphism
+ \[
+ \CCSiso{G} \to G(\Fq)^*.
+ \]
+ \end{corollary}
+
+ \begin{proof}
+ By \'etale descent, pullback induces an equivalence of categories between $\CCS(G)$ and $\CCS(G/C)$.
+ The result now follows from Theorem \ref{thm:trfrobiso} and the fact that all characters of $G(\Fq)$ factor through
+ $G(\Fq)/C(\Fq)$, which equals $(G/C)(\Fq)$ since $C$ is simply connected.
+ \end{proof}
+
+ \begin{remark}
+ Talk about relationship with \cite{kamgarpour:09a}.  In particular, explain why the character sheaf corresponding
+ to the cover
+ \[
+ 1 \to \mu_n \to \SL_n \to \PGL_n \to 1
+ \]
+ is not commutative.  Explain how our character sheaves are not just representations of a fundamental group
+ (or are they?), but instead have extra data like $\mu$ and $\phi$.
+ \end{remark}
 

### 2015-07-25 followup.tex
Added proofs to Abelianization

@@
 %%%%%%%%%%%% BEGIN DOCUMENT %%%%%%%%%%%
+\usepackage{todonotes}
 
@@
 
+\begin{lemma}
+If $\cs{L}$ is a commutative character sheaf on $G$ then $\cs{L}\vert_C = (\EE)_C$.
+\end{lemma}
+\begin{proof}
+ Consider the morphism $c:  G \times G \to C$ given by $c(g,h)= ghg^{-1}h^{-1}$ and let $j : C \hookrightarrow G$ be the inclusion.  
+Thus, $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$.
+Thus,
+\begin{align*}
+(j\circ c)^*\cs{L} 
+&= c^* (\cs{L}\vert_C)\\
+&= (m\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
+&= (m \times (\iota\circ m\op))^* m^* \cs{L} \\
+&= (m \times (\iota\circ m\op))^* m\op^* \cs{L} \\
+&= (m\op\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
+&= e^* \cs{L}\\
+&= (\EE)_{G\times G}\\
+&= c^* ((\EE)_C).
+\end{align*}
+Since $c : G \times G \to C$ is smooth with geometrically connected fibres, \todo{Must insert proof of this!
+\\ -CC} the functor $c^*$ is full and faithful \cite{BBD}*{Prop 4.2.5} \todo{I'll find a better reference.
+Big stone.
+Small bird.
+\\ -CC} so $c^* (\cs{L}\vert_C) \iso c^* ((\EE)_C)$ implies $\cs{L}\vert_C \iso (\EE)_C$.
+\end{proof}
+
  \begin{proposition}
@@
  \begin{proof}
-
+Let $n : C \times G \to G$ be the left translation action of $C$ on $G$. 
+Then $n = m \circ (j \times \id)$, so
+\begin{align*}
+n^* \cs{L} 
+&= (m \circ (j \times \id))^* \cs{L}\\
+&= (j \times \id))^* m^*\cs{L}\\
+&\iso (j \times \id))^* (\cs{L} \boxtimes \cs{L})\\
+&= (j^*\cs{L}) \boxtimes \cs{L}\\
+&= (\cs{L}\vert_C) \boxtimes \cs{L}\\
+&= (\EE)_C \boxtimes \cs{L}\\
+&= p_2^* \cs{L}.
+\end{align*}
  \end{proof}
@@
  \begin{proof}
- By \'etale descent, pullback induces an equivalence of categories between $\CCS(G)$ and $\CCS(G/C)$.
+ By \'etale descent, pullback induces an equivalence of categories between $\CCS(G)$ and $\CCS(G/C)$. \todo{I need to expand on this trick. \\ -CC}
   The result now follows from Theorem \ref{thm:trfrobiso} and the fact that all characters of $G(\Fq)$ factor through
@@
  (or are they?), but instead have extra data like $\mu$ and $\phi$.
+\todo{I think I got this wrong.
+I think our sheaves are not extra information in the commutative case.
+Masound's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case.
+So, I think the modification is easy: add mop to diagram 2.4 in Masoud's paper.
+\\ -CC}
+ \end{remark}
+
+\begin{proposition}
+Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$.
+\end{proposition}
+
+\begin{proof}
+Let $a : G \times G \to G$ be the conjugation action of $G$ on $G$. Then $a = m \circ (m \times (\iota \circ p_1))$ and $m\op \circ (m \times (\iota \circ p_1)) = p_2$. Thus,
+\begin{align*}
+a^* \cs{L} 
+&= (m \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
+&= (m \times (\iota \circ p_1))^* m^* \cs{L}\\
+&\iso (m \times (\iota \circ p_1))^* m\op^* \cs{L}\\
+&= (m\op \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
+&= p_2^*\cs{L}.
+\end{align*}
+\end{proof}
+
+\begin{remark}
+A great tragedy of nomenclature: an equivariant sheaf is not a sheaf that is equivariant. \todo{I will explain this.\\ -CC} 
 \end{remark}
@@
 Let us refer to the types arising in this manner as {\it generic types}.
-In this section we show that, after fixing an isomorphism $\CC \approx \EE$, every generic type is geometrizable, in the sense that every part of generic type admits a description as a perverse sheaf on a scheme over a finite field, from which the type can be recovered using the trace of Frobenius.
+In this section we show that, after fixing an isomorphism $\CC \approx \EE$, every generic type is geometrizable, in the sense that every part of generic type admits a description as a perverse sheaf, from which the type can be recovered.
 

### 2015-07-29 followup.tex
Types, under construction.
Added note to main definition.

@@
 We will denote the category of character sheaves on $G$ by $\CS(G)$.
+\todo{I think we should hold the term `character sheaves for G', when $G$ is not commutative, in reserve, and not use it here for non-commutative $G$.
+So I might advocate going back to the full definition here.\\ -CC}
 
@@
 Then $\pi_0$ is produced by compact induction from representation $\sigma$ of a compact mod centre subgroup $\underline{C}_0(\OK) \subset \G^0(K)$.
-Moreover, $C_0$ admits a smooth integral model $\underline{C}$
+Moreover, $C_0$ admits a smooth integral model $\underline{C}$ \todo{Under construction.
+\\ -CC}
 

### 2015-07-29 followup.tex
Modified notes on restriction to C and descent.

@@
 $\pi_0(G)$ of $G$ is an \'etale group scheme over $\Fq$, and both are smooth over $\Fq$.
+\todo{Remember to check the matching paragraph in CS for T. It may have an error. The group operations are also smooth, not just the structure map? Hm. It might be okay, actually  . . . \\ -CC}
 
@@
 \begin{proof}
- Consider the morphism $c:  G \times G \to C$ given by $c(g,h)= ghg^{-1}h^{-1}$ and let $j : C \hookrightarrow G$ be the inclusion.  
-Thus, $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$.
+ Consider the morphism $c:  G \times G \to C$ given by $c(g,h)= ghg^{-1}h^{-1}$.
+This surjective morphism is smooth (it is a composition of smooth maps, since $G$ is smooth) with fibres
+Let $j : C \hookrightarrow G$ be the inclusion.  
+Then $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$.
 Thus,
 \begin{align*}
-(j\circ c)^*\cs{L} 
-&= c^* (\cs{L}\vert_C)\\
+c^* (\cs{L}\vert_C)
+&=  (j\circ c)^*\cs{L} \\
 &= (m\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
@@
 \end{align*}
-Since $c : G \times G \to C$ is smooth with geometrically connected fibres, \todo{Must insert proof of this!
-\\ -CC} the functor $c^*$ is full and faithful \cite{BBD}*{Prop 4.2.5} \todo{I'll find a better reference.
-Big stone.
-Small bird.
-\\ -CC} so $c^* (\cs{L}\vert_C) \iso c^* ((\EE)_C)$ implies $\cs{L}\vert_C \iso (\EE)_C$.
+Since $c : G \times G \to C$ is faithfully flat, the functor $c^*$ is conservative.
+\todo{I'm working on this   . . . \\ -CC}
+Since $\cs{L} \to (\EE)_G$ induces $c^* (\cs{L}\vert_C) \iso c^* ((\EE)_C)$, this implies $\cs{L}\vert_C \iso (\EE)_C$. 
 \end{proof}
@@
  \begin{proof}
- By \'etale descent, pullback induces an equivalence of categories between $\CCS(G)$ and $\CCS(G/C)$. \todo{I need to expand on this trick. \\ -CC}
+ By descent along $G \to G/C = G\der$, pullback induces an equivalence of categories between $C$-equivariant local systems on $G$ local systems on  $G\der$.
+\todo{I need to explain what's going on here.
+\\ -CC}
   The result now follows from Theorem \ref{thm:trfrobiso} and the fact that all characters of $G(\Fq)$ factor through
@@
  (or are they?), but instead have extra data like $\mu$ and $\phi$.
-\todo{I think I got this wrong.
+\todo{I got this wrong.
 I think our sheaves are not extra information in the commutative case.

### 2015-07-30 followup.tex
Started work on descent

@@
 \newcommand{\der}{_{\operatorname{der}}}
+\newcommand{\ab}{^{\operatorname{ab}}}
 %%%%%%%%%%%% MISCELLANEOUS OPERATORS %%%%%%%%%%%%
@@
 \section*{Introduction}
+We introduce and establish the basic properties of \emph{commutative character sheaves} on smooth group schemes $G$ over finite fields $\Fq$. 
+For instance, show that show that the category of commutative character sheaves on $G$ is equivalent to the category of commutative character sheaves on $G\ab$. 
+We give three applications.
+First, we use commutative character sheaves to produce a functorial geometrization of characters of $G(\Fq)$ in all cases, thus repairing a defect in the function-sheaf dictionary for algebraic groups $G$ which appears when $\Hh^2(\pi_0(\bG),\EEx)^{\Frob{}}$ is non-trivial.
+Second, we revisit the motivations for the stacky abelianization construction, and show that, after replacing the character sheaves on $G$ with commutative character sheaves on $G$, the schematic abelianization $G \to G\ab$ is correct.
+Finally, we provide a geometrization of generic types for supercuspidal representations of connected reductive linear algebraic groups over local fields.
 
@@
  \begin{proof}
- By descent along $G \to G/C = G\der$, pullback induces an equivalence of categories between $C$-equivariant local systems on $G$ local systems on  $G\der$.
+ By descent along $G \to G/C$, pullback induces an equivalence of categories between $C$-equivariant local systems on $G$ local systems on  $G/C$.
 \todo{I need to explain what's going on here.
-\\ -CC}
+See appendix.\\ -CC}
   The result now follows from Theorem \ref{thm:trfrobiso} and the fact that all characters of $G(\Fq)$ factor through
@@
 
+\appendix
+
+\section{Descent}
+
+[Since I haven't found a good reference for descent in the non-connected case, I think I should lay out the arguments here.
+We use descent in this paper to pass from $C$-equivariant local systems on $G$ to local systems on $G\ab$, and thence to characters of $G\ab(\Fq)$.
+We also used it in our last paper in a different way.
+It is also lurking behind Weil sheaves .....
+So, I'm going to set things up in a very general context.
+This section will get whittled down to  something more manageable, later.]
+
 \bibliography{bibliography/Biblio}

### 2015-08-03 dictionary.tex
Removed some vestigial macros
Fixed my address.
Removing old MSC command
Re-added the paragraph about Bertstein.

@@
 where $\Weil{K}$ is the Weil group for $K$ and $\check{T}_\ell$ is the $\ell$-adic dual torus to $T$.
+
+By any measure, there are more quasicharacter sheaves for $T$ than quasicharacters of $T(K)$.  
+In this regard, we are reminded of the work of David Vogan \cite{vogan:93a}, in which he finds a geometrization of complete Langlands parameters for $p$-adic groups 
+and, in the process, is led to study the representations of all the pure rational forms of the $p$-adic group, simultaneously.
+A similar phenomenon appears in recent work by Joseph Bernstein in which his geometric Ansatz leads to the study of certain sheaves on the stacky classifying space of the $p$-adic group, resulting in a category which appears to be tied to the representations of all the pure rational forms of the $p$-adic group \cite{bernstein:vogan_conference}.
+Indeed, Bernstein has suggested to us that our category of quasicharacters for $T$ may be tied to quasicharacters of all the pure rational forms of $T$. It would be interesting to pursue this idea.
 

### 2015-08-03 dictionary.tex
Re-added the commented-out paragraph in the proof of the classical dictionary.

@@
 From here, Deligne's function-sheaf dictionary for connected commutative algebraic groups over finite fields,
-as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3}, gives us all we need for points \ref{c1} and \ref{c2}.
-\iffalse
+as in \cite{deligne:SGA4.5}*{Sommes trig.} or \cite{laumon:87a}*{1.1.3}, gives us all we need for points \ref{c1} and \ref{c2}, as we briefly recall.
+
+%\iffalse
 As in the proof of Proposition~\ref{prop:finite}, use \'etale descent to see that pullback by the Lang isogeny $\Lang : G\to G$
@@
 representation of $G(\Fq)$, proving parts \ref{c1} and \ref{c2}.
-\fi
+%\fi
+
 For part \ref{c3}, suppose $\Lang^*\cs{E} = V$ with isomorphism $V \to V\otimes V$.

### 2015-08-03 dictionary.tex
Removed one `Finally' from the acknowledgements.

@@
 
-Finally, we gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
+We gratefully acknowledge the financial support of the Pacific Institute for the Mathematical Sciences
 and the National Science and Engineering Research Council (Canada), as well the hospitality of the

### 2015-08-17 followup.tex
Working on descent to the abelianization
I’m back on the grid!

@@
 $\pi_0(G)$ of $G$ is an \'etale group scheme over $\Fq$, and both are smooth over $\Fq$.
-\todo{Remember to check the matching paragraph in CS for T. It may have an error. The group operations are also smooth, not just the structure map? Hm. It might be okay, actually  . . . \\ -CC}
 
@@
 
-\section{Passing to the abelianization}
+\section{Descent to the abelianization}
 
+ \begin{theorem}\label{thm:descent}
  Let $G$ be a smooth group scheme over $\Fq$ and let $C = [G, G]$ be its commutator subgroup. 
+The quotient $G \to G/C$ exists in the category of smooth group schemes over $\Fq$.
+The category of commutative character sheaves on $G$ is equivalent to the category of commutative character sheaves on $G/C$: 
+ \[
+ \CCS(G) \iso \CCS(G/C).
+ \]
+ \end{theorem}
+
+\begin{proof}
+Set $G\ab \ceq G/C$ and let $q : G \to G\ab$ be the quotient in the category of smooth group schemes over $\Fq$.
+Recall the functor $q^* : \CCS(G\ab)\to \CCS(G)$ from  . . . 
+The strategy of the proof is indicated by the diagram below. 
+\[
+\begin{tikzcd}
+\CCS(G)& \\
+& \CCS_C(G) \arrow{ul}[swap]{\text{forget}} \\
+\CCS(G\ab) \arrow{uu}{g^*} \arrow{ur}[swap]{\text{comparison}} & 
+\end{tikzcd}
+\]
+We will first use smooth descent to show that the comparison functor is an equivalence from $\CCS(G\ab)$ to the category $\CCS_C(G)$ of $C$-equivariant commutative character sheaves on $G\ab$, the latter defined below.
+Then we will show that the forgetful functor from $\CCS_C(G)$ to $\CCS(G)$ is also an equivalence.
+
+  Every commutative character sheaf $\cs{L}$ on $G$ is equivariant for the left translation action of $C$ on $G$.
+Let $n : C \times G \to G$ be the left translation action of $C$ on $G$
+and let $p : C \times G \to G$ be projection to the second component.
+Then $n = m \circ (j \times \id)$, so
+\begin{align*}
+n^* \cs{L} 
+&= (m \circ (j \times \id))^* \cs{L}\\
+&= (j \times \id))^* m^*\cs{L}\\
+&\iso (j \times \id))^* (\cs{L} \boxtimes \cs{L})\\
+&= (j^*\cs{L}) \boxtimes \cs{L}\\
+&= (\cs{L}\vert_C) \boxtimes \cs{L}\\
+&= (\EE)_C \boxtimes \cs{L}\\
+&= p^* \cs{L}.
+\end{align*}
+
+\end{proof}
+
+\begin{lemma}
+Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$.
+\end{lemma}
+
+\begin{proof}
+Let $a : G \times G \to G$ be the conjugation action of $G$ on $G$. Then $a = m \circ (m \times (\iota \circ p_1))$ and $m\op \circ (m \times (\iota \circ p_1)) = p_2$. Thus,
+\begin{align*}
+a^* \cs{L} 
+&= (m \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
+&= (m \times (\iota \circ p_1))^* m^* \cs{L}\\
+&\iso (m \times (\iota \circ p_1))^* m\op^* \cs{L}\\
+&= (m\op \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
+&= p_2^*\cs{L}.
+\end{align*}
+\end{proof}
+
+\begin{remark}
+A great tragedy of nomenclature: an equivariant sheaf is not a sheaf that is equivariant. \todo{I will explain this.\\ -CC} 
+\end{remark}
 
@@
 Since $\cs{L} \to (\EE)_G$ induces $c^* (\cs{L}\vert_C) \iso c^* ((\EE)_C)$, this implies $\cs{L}\vert_C \iso (\EE)_C$. 
-\end{proof}
-
- \begin{proposition}
- Every commutative character sheaf $\cs{L}$ on $G$ is equivariant for the left translation action of $C$ on $G$.
- \end{proposition}
-
- \begin{proof}
-Let $n : C \times G \to G$ be the left translation action of $C$ on $G$. 
-Then $n = m \circ (j \times \id)$, so
-\begin{align*}
-n^* \cs{L} 
-&= (m \circ (j \times \id))^* \cs{L}\\
-&= (j \times \id))^* m^*\cs{L}\\
-&\iso (j \times \id))^* (\cs{L} \boxtimes \cs{L})\\
-&= (j^*\cs{L}) \boxtimes \cs{L}\\
-&= (\cs{L}\vert_C) \boxtimes \cs{L}\\
-&= (\EE)_C \boxtimes \cs{L}\\
-&= p_2^* \cs{L}.
-\end{align*}
 \end{proof}
@@
 \\ -CC}
- \end{remark}
-
-\begin{proposition}
-Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$.
-\end{proposition}
-
-\begin{proof}
-Let $a : G \times G \to G$ be the conjugation action of $G$ on $G$. Then $a = m \circ (m \times (\iota \circ p_1))$ and $m\op \circ (m \times (\iota \circ p_1)) = p_2$. Thus,
-\begin{align*}
-a^* \cs{L} 
-&= (m \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
-&= (m \times (\iota \circ p_1))^* m^* \cs{L}\\
-&\iso (m \times (\iota \circ p_1))^* m\op^* \cs{L}\\
-&= (m\op \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
-&= p_2^*\cs{L}.
-\end{align*}
-\end{proof}
-
-\begin{remark}
-A great tragedy of nomenclature: an equivariant sheaf is not a sheaf that is equivariant. \todo{I will explain this.\\ -CC} 
  \end{remark}
@@
 
-\appendix
-
-\section{Descent}
-
-[Since I haven't found a good reference for descent in the non-connected case, I think I should lay out the arguments here.
-We use descent in this paper to pass from $C$-equivariant local systems on $G$ to local systems on $G\ab$, and thence to characters of $G\ab(\Fq)$.
-We also used it in our last paper in a different way.
-It is also lurking behind Weil sheaves .....
-So, I'm going to set things up in a very general context.
-This section will get whittled down to  something more manageable, later.]
-
 \bibliography{bibliography/Biblio}

### 2015-08-20 followup.tex
Working on descent

@@
 
-\title{Commutative Character Sheaves}
+\title[Commutative Character Sheaves]{Commutative Character Sheaves, with an application to generic types for supercuspidal representations}
 \author{Clifton Cunningham}
@@
 \newcommand{\der}{_{\operatorname{der}}}
-\newcommand{\ab}{^{\operatorname{ab}}}
+\newcommand{\ab}{_{\operatorname{ab}}}
+
 %%%%%%%%%%%% MISCELLANEOUS OPERATORS %%%%%%%%%%%%
@@
 \begin{abstract}
-Abstract goes here
+We introduce and establish the basic properties of  the category of \emph{commutative character sheaves} on smooth group schemes $G$ over finite fields $\Fq$. 
+We use this category to geometrize all generic types for supercuspidal representations of $p$-adic groups. 
 \end{abstract}
@@
 \section*{Introduction}
-We introduce and establish the basic properties of \emph{commutative character sheaves} on smooth group schemes $G$ over finite fields $\Fq$. 
-For instance, show that show that the category of commutative character sheaves on $G$ is equivalent to the category of commutative character sheaves on $G\ab$. 
+We introduce and establish the basic properties of  the category of \emph{commutative character sheaves} on smooth group schemes $G$ over finite fields $\Fq$. 
+Expanding on work by the same authors, we show that all character sheaves on $G\ab$ are commutative, when $G\ab$ is connected and of finite type.
 We give three applications.
-First, we use commutative character sheaves to produce a functorial geometrization of characters of $G(\Fq)$ in all cases, thus repairing a defect in the function-sheaf dictionary for algebraic groups $G$ which appears when $\Hh^2(\pi_0(\bG),\EEx)^{\Frob{}}$ is non-trivial.
-Second, we revisit the motivations for the stacky abelianization construction, and show that, after replacing the character sheaves on $G$ with commutative character sheaves on $G$, the schematic abelianization $G \to G\ab$ is correct.
+First, we use commutative character sheaves to produce a functorial geometrization of characters of $G(\Fq)$ in all cases, thus repairing a defect in the function-sheaf dictionary for algebraic groups $G$ which appears when the component group of $G$ is $\Hh^2(\pi_0(\bG),\EEx)^{\Frob{}}$ is non-trivial.
+Second, we revisit the motivations for the stacky abelianization construction, and show that, after replacing the character sheaves on $G$ with commutative character sheaves on $G$, the schematic abelianization $G \to G\ab$ is the correct quotient.
+This is an immediate consequence of the fact that the category of commutative character sheaves on $G$ is equivalent to the category of commutative character sheaves on $G\ab$. 
 Finally, we provide a geometrization of generic types for supercuspidal representations of connected reductive linear algebraic groups over local fields.
+This last application puts all the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category: perverse sheaves on group schemes over finite fields.
 
@@
 
-\section{Eliminating Invisible Character Sheaves}
+\section{Eliminating Invisible Character Sheaves}\label{sec:defect}
 
@@
 Suppose that $\cs{L}$ is a commutative character sheaf
-with $\TrFrob(\cs{L}) = 1$.  Then $S_G([\cs{L}])$ is in the image of $\Hh^2(\bG, \EEx)^\Weil{}$, so is cohomologous to
+with $\trFrob{\cs{L}} = 1$.  Then $S_G([\cs{L}])$ is in the image of $\Hh^2(\bG, \EEx)^\Weil{}$, so is cohomologous to
 $[\alpha', 0]$.  Since $\alpha$ is symmetric and coboundaries are symmetric, $\alpha'$ is symmetric as well.
@@
 
+Let $G$ be a smooth group scheme.
+Let $G\der \hookrightarrow G$ denote the smooth, closed subgroup generated by the commutator morphism $c: G\times G \to G$ given by $c(x,y) = xyx^{-1}y^{-1}$; see \cite{SGA3}*{{VI}$_B$, 7.2}.
+
  \begin{theorem}\label{thm:descent}
- Let $G$ be a smooth group scheme over $\Fq$ and let $C = [G, G]$ be its commutator subgroup. 
-The quotient $G \to G/C$ exists in the category of smooth group schemes over $\Fq$.
-The category of commutative character sheaves on $G$ is equivalent to the category of commutative character sheaves on $G/C$: 
+ Let $G$ be a smooth group scheme over $\Fq$ 
+ and let $q : G \to G\ab$ be its abelianization. 
+ Suppose $G\der$ is geometrically connected 
+ and that $q: G \to G\ab$ is a smooth $G\der$ bundle.
+Then
 \[
- \CCS(G) \iso \CCS(G/C).
+q^*:  \CCS(G\ab) \longrightarrow \CCS(G)
 \]
+is an equivalence of rigid monoidal categories.
   \end{theorem}
@@
 \begin{proof}
-Set $G\ab \ceq G/C$ and let $q : G \to G\ab$ be the quotient in the category of smooth group schemes over $\Fq$.
-Recall the functor $q^* : \CCS(G\ab)\to \CCS(G)$ from  . . . 
-The strategy of the proof is indicated by the diagram below. 
+The quotient $q : G \to G\ab$ is the coequalizer of left $G\der$-multiplication $n : G\der\times G \to G$ and projection $p : G\der\times G \to G$, in the category of smooth group schemes.
 \[
 \begin{tikzcd}
-\CCS(G)& \\
-& \CCS_C(G) \arrow{ul}[swap]{\text{forget}} \\
-\CCS(G\ab) \arrow{uu}{g^*} \arrow{ur}[swap]{\text{comparison}} & 
+G\der\times G
+ \arrow{r}[shift left]{m}
+  \arrow{r}[shift right,swap]{p}
+&
+G 
+\arrow{r}{q}
+& 
+G\ab
 \end{tikzcd}
 \]
-We will first use smooth descent to show that the comparison functor is an equivalence from $\CCS(G\ab)$ to the category $\CCS_C(G)$ of $C$-equivariant commutative character sheaves on $G\ab$, the latter defined below.
-Then we will show that the forgetful functor from $\CCS_C(G)$ to $\CCS(G)$ is also an equivalence.
+In particular, $n$, $p$ and $q$ are all smooth morphisms of relative dimension $\dim G\der$.
 
-  Every commutative character sheaf $\cs{L}$ on $G$ is equivariant for the left translation action of $C$ on $G$.
-Let $n : C \times G \to G$ be the left translation action of $C$ on $G$
-and let $p : C \times G \to G$ be projection to the second component.
+Let $\CCS_{G\der}(G)$ be the category of commutative character sheaves $\cs{L}$ on $G$ equipped with an isomorphism $n^*\cs{L} \to p^*\cs{L}$ satisfying canonical coherence conditions.
+Then $q^* : \CCS(G\ab) \to \CCS(G)$ factors through $\CCS_{G\der}(G)$. 
+\[
+\begin{tikzcd}
+\CCS(G\der \times G)
+& \arrow{l}[shift left,swap]{n^*}
+  \arrow{l}[shift right]{p^*}
+\CCS(G) 
+&&\arrow{ll}[swap]{q^*} 
+\CCS(G\ab) \arrow{dl}{\text{comparison}}\\
+&& \arrow{ul}{\text{forget}} \CCS_{G\der}(G) & 
+\end{tikzcd}
+\]
+To see this, let $\cs{E}$ be a commutative character sheaf on $G\ab$ and observe that $q^* \cs{E}$ is equipped with a canonical isomorphism $n^*(q^* \cs{E}) \to p^*(q^* \cs{E})$ given by
+\[
+n^* (q^*\cs{E}) \iso (q\circ n)^* \cs{E} = (q\circ p)^* \cs{E} \iso p^* (q^*\cs{E}).
+\]
+Moreover, since $q : G \to G\ab$ is a smooth principal $G\der$-bundle and $G\der$ is geometrically connected,
+the comparison functor is an equivalence.
+%(In other language, $q^*$ is a monadic functor.)
+Indeed, it is easy to see that $\CCS(G\ab) \to \CCS_{G\der}(G)$ is full and faithful; to see that is it also essentially surjective, one begins with $\cs{L} \in \CCS(G)$ and $\nu : n^*\cs{L} \to p^*\cs{L}$ and builds $\cs{E}\in \CCS(G\ab)$ Zariski-locally by pull-back along local trivializations $U \to G\times_{G\ab} U$ of $q : G\to G\ab$ compatible with the $C$-action, glueing using isomorphisms inherited from the isomorphism $\nu$, and finally verifying that the result is a local system with the auxilliary data defining a commutative character sheaf.
+See appendix for details.\todo{Should I make the promised appendix, or is this paragraph enough?}
+
+To see that the forgetful functor $\CCS_{G\der}(G) \to \CCS(G)$ is an equivalence we observe that
+every commutative character sheaf $\cs{L}$ on $G$ is equivariant for the left translation action of $C$ on $G$, as follows.
+Let $j : C \hookrightarrow G$ be the kernel of $q : G \to G\ab$ and let $m : G\times G \to G$ be multiplication for $G$. 
 Then $n = m \circ (j \times \id)$, so
@@
 \end{proof}
+
+\begin{remark}\label{rem:descent}
+\end{remark}
 
@@
 
- \begin{remark}
+\subsection{Stacky abelianization, revisited}
+
  Talk about relationship with \cite{kamgarpour:09a}.  In particular, explain why the character sheaf corresponding
@@
 \\ -CC}
- \end{remark}
 
-\section{Applications}
-
-\subsection{Quasicharacter sheaves}
+\section{Geometrization of generic types for supercuspidal representations}
 
@@
 \end{corollary}
-
-\subsection{Geometrization of generic types for supercuspidal representations}
 
@@
 
+\appendix
+
+\section{Descent along smooth principal bundles}
+
 \bibliography{bibliography/Biblio}

### 2015-08-26 followup.tex
Added an alternate characterization of commutative character sheaves.
Still working on descent and invariance.

@@
 \todo{I think we should hold the term `character sheaves for G', when $G$ is not commutative, in reserve, and not use it here for non-commutative $G$.
-So I might advocate going back to the full definition here.\\ -CC}
+So I might advocate going back to the full definition here.
+Or, we might introduce the term `rank-$1$ character sheaf, similar to what Masoud did  .
+.
+.
+\\ -CC}
 
@@
 \begin{proof}
+\end{proof}
+
+\begin{proposition}
+Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$.
+Conversely, if a [rank-$1$] character sheaf on $G$ is equivariant for conjugation, then $G$ is commutative.
+\end{proposition}
+
+\begin{proof}
+Let $a : G \times G \to G$ be the conjugation action of $G$ on $G$.
+Then $a = m \circ (m \times (\iota \circ p_1))$ while $m\op \circ (m \times (\iota \circ p_1)) = p_2$.
+Thus, if $m^*\cs{L} \iso m\op^*\cs{L}$ then
+\begin{align*}
+a^* \cs{L} 
+&= (m \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
+&= (m \times (\iota \circ p_1))^* m^* \cs{L}\\
+&\iso (m \times (\iota \circ p_1))^* m\op^* \cs{L}\\
+&= (m\op \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
+&= p_2^*\cs{L}.
+\end{align*}
+Since the isomorphism $a^*\cs{L} \iso p_2^*\cs{L}$ is unique, $(\cs{L}, a^*\cs{L} \iso p_2^*\cs{L})$ is an equivariant commutative character sheaf.
+
+Conversely, let $(\cs{L}, a^*\cs{L} \iso p_2^*\cs{L})$ be an equivariant [rank-$1$] character sheaf.
+Observe that $m = a \circ (p_1\times m\op)$ while $p_2 \circ (p_1\times m\op) = m\op$. Thus, 
+\begin{align*}
+m^* \cs{L} 
+&= (a \circ (p_1 \times m\op))^* \cs{L}\\
+&= (p_1 \times m\op)^* a^* \cs{L}\\
+&\iso (p_1 \times m\op)^* p_2^* \cs{L}\\
+&= (p_2\circ (p_1 \times m\op))^* \cs{L}\\
+&= m\op^* \cs{L}.
+\end{align*}
+Thus, $\cs{L}$ is a commutative character sheaf.
 \end{proof}
@@
 Let $G$ be a smooth group scheme.
-Let $G\der \hookrightarrow G$ denote the smooth, closed subgroup generated by the commutator morphism $c: G\times G \to G$ given by $c(x,y) = xyx^{-1}y^{-1}$; see \cite{SGA3}*{{VI}$_B$, 7.2}.
+Let $G\der \hookrightarrow G$ denote the closed subgroup generated by the commutator morphism $c: G\times G \to G$ given by $c(x,y) = xyx^{-1}y^{-1}$; see \cite{SGA3}*{{VI}$_B$, 7.2}.
 
- \begin{theorem}\label{thm:descent}
- Let $G$ be a smooth group scheme over $\Fq$ 
- and let $q : G \to G\ab$ be its abelianization. 
- Suppose $G\der$ is geometrically connected 
- and that $q: G \to G\ab$ is a smooth $G\der$ bundle.
-Then
-\[
-q^*:  \CCS(G\ab) \longrightarrow \CCS(G)
-\]
-is an equivalence of rigid monoidal categories.
-  \end{theorem}
+\begin{lemma}
+The quotient $q : G \to G\ab$ is a smooth $G\der$-torsor, and the coequalizer of $m, p : G\der \times G \to G$.
+\end{lemma}
 
-\begin{proof}
-The quotient $q : G \to G\ab$ is the coequalizer of left $G\der$-multiplication $n : G\der\times G \to G$ and projection $p : G\der\times G \to G$, in the category of smooth group schemes.
+The quotient $q : G \to G\ab$ is the coequalizer of left $G\der$-multiplication $n : G\der\times G \to G$ and projection $p : G\der\times G \to G$.
 \[
@@
 \]
-In particular, $n$, $p$ and $q$ are all smooth morphisms of relative dimension $\dim G\der$.
+The morphism $q$ is surjective and smooth of relative dimension $\dim G\der$.
+
+ \begin{theorem}\label{thm:descent}
+ Let $G$ be a smooth group scheme over $\Fq$ 
+ and let $q : G \to G\ab$ be its abelianization. 
+ Then  
+\[
+q^*:  \CCS(G\ab) \longrightarrow \CCS(G)
+\]
+is an equivalence of rigid monoidal categories.
+  \end{theorem}
+
+\begin{proof}
+It follows from the lemma that descent theory that $q$ is an 
+effective descent morphism for the fibred category of commutative character sheaves on smooth group schemes; in other words, the canonical functor $\CCS(G) \to \CCS_{G\der}(G)$ is an equivalence. 
+\todo{$\CCS \to \Sch{\Fq}$ is a fibred category. Is it also a stack?}
+
+Consider the morphism $c:  G \times G \to G\der$ given by $c(g,h)= ghg^{-1}h^{-1}$.
+This morphism is smooth (it is a composition of smooth maps, since $m : G \times G \to G$ is smooth) but
+
+Let $j : C \hookrightarrow G$ be the inclusion.  
+Then $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$.
+Thus,
+\begin{align*}
+c^* (\cs{L}\vert_C)
+&=  (j\circ c)^*\cs{L} \\
+&= (m\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
+&= (m \times (\iota\circ m\op))^* m^* \cs{L} \\
+&= (m \times (\iota\circ m\op))^* m\op^* \cs{L} \\
+&= (m\op\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
+&= e^* \cs{L}\\
+&= (\EE)_{G\times G}\\
+&= c^* ((\EE)_C).
+\end{align*}
+Since $c : G \times G \to C$ is faithfully flat, the functor $c^*$ is conservative.
+\todo{I'm working on this   . . . \\ -CC}
+Since $\cs{L} \to (\EE)_G$ induces $c^* (\cs{L}\vert_C) \iso c^* ((\EE)_C)$, this implies $\cs{L}\vert_C \iso (\EE)_C$.
 
@@
 Indeed, it is easy to see that $\CCS(G\ab) \to \CCS_{G\der}(G)$ is full and faithful; to see that is it also essentially surjective, one begins with $\cs{L} \in \CCS(G)$ and $\nu : n^*\cs{L} \to p^*\cs{L}$ and builds $\cs{E}\in \CCS(G\ab)$ Zariski-locally by pull-back along local trivializations $U \to G\times_{G\ab} U$ of $q : G\to G\ab$ compatible with the $C$-action, glueing using isomorphisms inherited from the isomorphism $\nu$, and finally verifying that the result is a local system with the auxilliary data defining a commutative character sheaf.
-See appendix for details.\todo{Should I make the promised appendix, or is this paragraph enough?}
+See appendix for details.
 
@@
 
-\begin{lemma}
-Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$.
-\end{lemma}
-
-\begin{proof}
-Let $a : G \times G \to G$ be the conjugation action of $G$ on $G$. Then $a = m \circ (m \times (\iota \circ p_1))$ and $m\op \circ (m \times (\iota \circ p_1)) = p_2$. Thus,
-\begin{align*}
-a^* \cs{L} 
-&= (m \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
-&= (m \times (\iota \circ p_1))^* m^* \cs{L}\\
-&\iso (m \times (\iota \circ p_1))^* m\op^* \cs{L}\\
-&= (m\op \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
-&= p_2^*\cs{L}.
-\end{align*}
-\end{proof}
-
 \begin{remark}
@@
 \end{remark}
-
-\begin{lemma}
-If $\cs{L}$ is a commutative character sheaf on $G$ then $\cs{L}\vert_C = (\EE)_C$.
-\end{lemma}
-\begin{proof}
- Consider the morphism $c:  G \times G \to C$ given by $c(g,h)= ghg^{-1}h^{-1}$.
-This surjective morphism is smooth (it is a composition of smooth maps, since $G$ is smooth) with fibres
-Let $j : C \hookrightarrow G$ be the inclusion.  
-Then $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$.
-Thus,
-\begin{align*}
-c^* (\cs{L}\vert_C)
-&=  (j\circ c)^*\cs{L} \\
-&= (m\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
-&= (m \times (\iota\circ m\op))^* m^* \cs{L} \\
-&= (m \times (\iota\circ m\op))^* m\op^* \cs{L} \\
-&= (m\op\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
-&= e^* \cs{L}\\
-&= (\EE)_{G\times G}\\
-&= c^* ((\EE)_C).
-\end{align*}
-Since $c : G \times G \to C$ is faithfully flat, the functor $c^*$ is conservative.
-\todo{I'm working on this   . . . \\ -CC}
-Since $\cs{L} \to (\EE)_G$ induces $c^* (\cs{L}\vert_C) \iso c^* ((\EE)_C)$, this implies $\cs{L}\vert_C \iso (\EE)_C$. 
-\end{proof}
 
@@
 
-\section{Descent along smooth principal bundles}
+\section{Descent along smooth fibrations}
+
+Let $G$ be a group scheme acting on $X$ by $m : G \times X \to X$.
+
+A principal $G$-bundle $f : X\to Y$ is a coequalizer of $m$ and projection $G\times X \to X$  
+which is locally trivial in the following sense.
+First, there is an open covering $\{ V_n\}$ of $Y$ such that, for each $V$ in this covering, the lower coequalizer diagram is a base change of the one above
+\[
+\begin{tikzcd}
+G\times X
+ \arrow{rr}[shift left]{m}
+  \arrow{rr}[shift right,swap]{\text{proj'n}}
+&& X \arrow{r}{f} &  Y\\
+G\times  (G\times V) \arrow{u}
+ \arrow{rr}[shift left]{\text{mult'n in $G$}}
+  \arrow{rr}[shift right,swap]{\text{proj'n}}
+&& G\times V \arrow{u}  \arrow{r} &  \arrow{u} V;
+\end{tikzcd}
+\]
+
+and the following diagram commutes
+\[
+\begin{tikzcd}
+G\times  f^{-1}(V)
+ \arrow{r}[shift left]{m}
+  \arrow{dr} 
+& f^{-1}(V) \arrow{r} \arrow{d}{t_V} &  V \\
+& G\times V \arrow{ur} & 
+\end{tikzcd}
+\]
+
+and isomorphisms ${t}_n : f^{-1}{V}_n \to {G}\times {V}_n$ such that  ${f}$ is given locally by ${f}_n = p \circ {t}_n$ (so ${f}_n : {f}^{-1}{Y}_n \to {Y}_n$) and the action ${m}_{X}$ of ${G}$ on ${X}$ is given locally by ${t}_n \circ {m}_n =  ({m} \times \id) \circ (\id\times{t}_n)$ (so ${m}_n : {G}\times{f}^{-1}{Y}_n \to {f}^{-1}{Y}_n$).
+
+Let $\Loc^1(X)$ be the category of rank-$1$ local systems on $X$ and let $\Loc_G^1(X)$ be the category of $G$-equivariant rank-$1$ local systems on $X$.
+
+\begin{proposition}
+Let $G$, $X$ and $Y$ be smooth.
+Let $f : X \to Y$ be a $G$-torsor.
+Then the comparison functor, pictured below,
+\[
+\begin{tikzcd}
+%\Loc^1(G \times X)
+%& \arrow{l}[shift left,swap]{m^*}
+%  \arrow{l}[shift right]{p^*}
+\Loc^1(X) 
+&&\arrow{ll}[swap]{f^*} 
+\Loc^1(Y) \arrow{dl}{\text{comparison}}\\
+& \arrow{ul}{\text{forget}} \Loc^1_G(X) & 
+\end{tikzcd}
+\]
+is an equivalence.
+\end{proposition}
+
+\begin{proof}
+This is well-known. We include a proof only for completeness.
+
+To simplify notation slightly, set ${X}_n \ceq {f}^{-1}{Y}_n$; also, let ${j}_n : {Y}_n \to {Y}$ and ${i}_n : {X}_n \to {X}$ denote inclusions.
+
+Then $f : X \to Y$ is a smooth, regular epimorphism with kernel pair $m, p: G\times X\to X$, and t
+
+Consider the following commuting diagram:
+\[
+\begin{tikzcd}
+H\times X \arrow{d}{\id\times f} \arrow{r}{m_X}&\to X\arrow{d}{f}\\
+H\times Y \arrow{r}{m_Y} &\to Y\\
+H\times X \arrow{r}{p_2} \arrow{u}{\id\times f} &\to X \arrow{u}{f}
+\end{tikzcd}
+\]
+Thus,
+\[
+\begin{aligned}
+m_X^*[\dim H] f^*[d] A
+&\iso (f\circ m_X)^* [d+\dim H]A  &\\
+&\iso (m_Y\circ (\id\times f))^*[d+\dim H]A & \text{$f$ is equivariant}\\
+&\iso (\id\times f)^*[d] m_Y^*[\dim H] A &\\
+&\iso  (\id\times f)^*[d] p_2^*[\dim H] A &\text{$A$ is $H$-equivariant}\\
+&\iso  (p_2\circ (\id\times f))^*[d+\dim H] A &\\
+&\iso (f\circ p_2)^*[d+\dim H]A & \\
+&\iso p_2^*[\dim H] f^*[d]A. &
+\end{aligned}
+\]
+This completes the proof that $f^*[d]A$ is an $H$-equivariant perverse sheaf on $X$.
+
+Let $\mathcal{F} = {f}^*[\dim{P}] \mathcal{G}$.
+
+To show that $\mathcal{F}$ is equivariant we must find an isomorphism $\mu : {m}^* \mathcal{F} \to p^* \mathcal{F}$ in $D^b_c({P}\times{X}, \EE)$ such that ${e}^*\mu = \id_{\mathcal{F}}$, where ${e} : {X} \to {P}\times{X}$ is the section defined by $x \mapsto (1,x)$.
+To see this, consider the restriction of ${m}^* \mathcal{F}$ to ${P}\times{X}_n$:
+\begin{eqnarray*}
+({m}^* \mathcal{F})\vert_{{P}\times {X}_n}
+	&=& (\id\times {i}_n)^* {m}^* {f}^* \mathcal{G} [\dim{P}]\\
+	&\iso& ({f}\circ {m} \circ \id\times {i}_n)^* \mathcal{G} [\dim{P}]\\
+	&=& ({f} \circ {i}_n \circ {m}_n)^* \mathcal{G} [\dim{P}].
+\end{eqnarray*}
+On the other hand, the restriction of $p^* \mathcal{F}$ to ${P}\times{X}_n$ is 
+\begin{eqnarray*}
+(p^* \mathcal{F})\vert_{{P}\times {X}_n}
+	&=& (\id\times {i}_n)^* p^* {f}^* \mathcal{G} [\dim{P}]\\
+	&\iso& ({f}\circ p \circ \id\times {i}_n)^* \mathcal{G} [\dim{P}]\\
+	&=& ({f} \circ {i}_n \circ p)^* \mathcal{G} [\dim{P}].
+\end{eqnarray*}
+Since ${f} \circ {i}_n \circ {m}_n = {f} \circ {i}_n \circ p$, we have $({m}^* {\mathcal{F}})\vert_{{P}\times {X}_n} \iso (p^* \mathcal{F})\vert_{{P}\times {X}_n}$.
+Since $\cup_n {P}\times{X}_n$ is an open cover for ${P}\times{X}$, this gives the isomorphism we seek.
+
+Next, suppose $\mathcal{F} \in \obj{\mathcal M}{X}$ is equivariant; thus, $\mathcal{F} \in \obj{\mathcal M}_{P}{X}$. Let $\mathcal{F}_n$ denote the restriction of $\mathcal{F}$ to ${X}_n$.
+
+Recall that ${m}: {P}\times{X} \to {X}$ is given locally by ${m}_n : {P}\times {X}_n \to {X}_n$, as above.
+Restricting the isomorphism $\mu_{\mathcal{F}} : {m}^* \mathcal{F} \to p^* \mathcal{F}$ to ${P}\times{X}_n$ yields the isomorphism $\mu_{\mathcal{F}_n} : {m}_n^* \mathcal{F}_n \to p^* \mathcal{F}_n$.
+Thus, $\mathcal{F}_n$ is an equivariant perverse sheaf.
+Now, let ${e}_n : {Y}_n \to {X}_n$ be the section of ${f}_n : {X}_n \to {Y}_n$ corresponding to $1\in {P}(\Fq)$ (so ${e}_n$ is the unique morphism of varieties such that $({t}_n \circ {e}_n) (y) = (1,y)$).
+Define
+\begin{equation}\label{equation: torsor 5}
+	\mathcal{F}'_n \ceq {e}_n^* \mathcal{F}_n [-\dim{P}].
+\end{equation}
+Then $\mathcal{F}'_n \in \obj D^b_c({Y}_n, \EE)$.
+By standard glueing arguments, the collection of $\mathcal{F}'_n \in\obj D^b_c({Y}_n, \EE)$, as ${Y}_n$ ranges over the open cover of ${Y}$ fixed above, uniquely determines an object $\mathcal{G}$ of $D^b_c({Y}, \EE)$.
+
+It remains to be shown that $\mathcal{G}$ is a perverse sheaf. Again, we work locally. For each such $n$,
+\begin{eqnarray*}
+{f}_n^*[\dim{P}] \mathcal{F}'_n 
+	&=& {f}_n^*[\dim{P}] {e}_n^* \mathcal{F}_n [-\dim{P}]\\
+	&\iso& ({e}_n\circ {f}_n)^* \mathcal{F}_n.
+\end{eqnarray*}
+Let ${u}_n : {X}_n \to {P}\times{X}_n$ be the section of ${m}_n : {P}\times{X}_n \to {X}_n$ corresponding to $1$ (so ${u}_n$ is the unique morphism of varieties such that $(\id\times{t}_n)\circ {u}_n \circ {t}_n^{-1} (h,y) = (h,1,y)$).
+The domain of ${u}_n^*\mu_{\mathcal{F}_n}$ is ${u}_n^*{m}_n^* \mathcal{F}_n \iso ({m}_n \circ {u}_n)^* \mathcal{F}_n = \mathcal{F}_n$, since ${u}_n$ is a section of ${m}_n$; the codomain of ${u}_n^* \mu_{\mathcal{F}_n}$ is ${u}_n^* p^* \mathcal{F}_n \iso (p\circ {u}_n)^*\mathcal{F}_n$.
+Since $p\circ {u}_n = {e}_n \circ {f}_n$, it follows that
+\[
+{u}_n^* \mu_{\mathcal{F}_n} : \mathcal{F}_n \to {f}_n^*[\dim{P}] \mathcal{F}'_n
+\]
+is an isomorphism in $D^b_c({X}_n, \EE)$.
+By \cite[Prop~4.2.5]{BBD} and the fact that ${\mathcal M}{X}_n$ is stable in $D^b_c({X}_n, \EE)$ under isomorphisms, it follows that $\mathcal{F}'_n \in \obj {\mathcal M}{Y}_n$.
+By standard glueing arguments, the collection of isomorphisms ${u}_n^* \mu_{\mathcal{F}_n} \in \mor{\mathcal M}{X}_n$, as ${X}_n$ ranges over the open cover of ${X}$ fixed above, uniquely determines an isomorphism in \[
+\Hom_{D^b_c({X}, \EE)}(\mathcal{F},{f}^*[\dim{P}] \mathcal{G}).
+\]  
+From \cite[Prop~4.2.5]{BBD}  it follows that $\mathcal{G}\in \obj{\mathcal M}{Y}$. This completes the proof of Proposition~\ref{proposition: torsor}.
+\end{proof}
+
+\begin{proposition}\label{proposition: more torsor}
+Let ${f} : {X} \to {Y}$ be a principal fibration with group ${P}$ and suppose ${P}$ is connected.
+Then ${f}^*[\dim{P}] : {\mathcal M}{Y} \to {\mathcal M}_{P}{X}$ is an equivalence of categories and ${\mathcal M}_{P}{X}$ is a thick subcategory of ${\mathcal M}{X}$.
+\end{proposition}
+
+\begin{proof}
+By \cite[Prop~4.2.5]{BBD} we know that ${f}^*[\dim{P}] : {\mathcal M}{Y} \to {\mathcal M}{X}$ is full and faithful.
+Let $\mathcal{G}$ be a perverse sheaf on ${Y}$.
+From the proof of Proposition~\ref{proposition: torsor} we have seen that $\mathcal{F} \ceq {f}^*[\dim{P}] \mathcal{G}$ is an equivariant perverse sheaf on ${X}$ and that ${f}^*[\dim{P}] \phi$ is an equivariant morphism in ${\mathcal M}{X}$ for each morphism $\phi$ in ${\mathcal M}{Y}$.
+Thus, ${f}^*[\dim{P}]$ is a functor from ${\mathcal M}{Y}$ to ${\mathcal M}_{P}{X}$.
+Thus, ${f}^*[\dim{P}] : {\mathcal M}{Y} \to {\mathcal M}_{P}{X}$ is full and faithful.
+Proposition~\ref{proposition: torsor} tells us that this functor is essentially surjective.
+Thus, ${f}^*[\dim{P}]$ is an equivalence.
+The last clause of Proposition~\ref{proposition: more torsor} follows from \cite[4.2.6]{BBD}.
+\end{proof}
+
+\begin{definition}\label{definition: descent}
+Let ${f} : {X} \to {Y}$ be a principal fibration with group ${P}$ and suppose ${P}$ is connected.
+Let ${f}_\# : {\mathcal M}_{P}{X} \to {\mathcal M}{Y}$ denote the adjoint of the equivalence ${f}^*[\dim{P}] : {\mathcal M}{Y} \to {\mathcal M}_{P}{X}$ (see Proposition~\ref{proposition: more torsor}).
+In particular, ${f}_\# : {\mathcal M}_{P}{X} \to {\mathcal M}{Y}$ is an equivalence of categories.
+\end{definition}
+
+\begin{corollary}
+Suppose $H$ is a connected group acting smoothly on $X$.
+If $A\in {\mathcal M} X$ is $H$-equivariant and $B\in {\mathcal M} X$ is a subquotient of $A$, then $B$ is also $H$-equivariant.
+\end{corollary}
+
+\begin{proof}
+(Following \cite[(1.9.1)]{CS}.)
+Let the action of $H$ on $Y$ is given by $m : H\times X \to X$.
+This is a smooth morphism with connected fibres, by hypothesis.
+Thus, $m^*[\dim H]$ is an equivalence of categories, by Proposition~\ref{proposition: more torsor}.
+Since equivalences take epimorphisms to epimorphisms and monomorphisms to monomorphisms, it follows that $m^*[\dim H]B$ is a subquotient of $m^*[\dim H]A$.
+Since $A$ is an $H$-equivarient perverse sheaf on $X$, we have $m^*[\dim H]A \iso p_2^*[\dim H]A$.
+On the other hand, $p_2 : H\times X \to X$ is also a smooth morphism with connected fibres of dimension $H$, so by Proposition~\ref{proposition: more torsor}, $p_2^*[\dim H]$ identifies ${\mathcal M}_H X$ with a thick subcategory of ${\mathcal M} (H\times X)$.
+Since $m^*[\dim H]B$ is a subquotient of $p_2^*[\dim H]A$, it follows that there is some $C\in {\mathcal M} X$ such that $p_2^*C \iso m^*[\dim H]B$ restricting this isomorphism from $H\times X$ to $\{ e\} \times X$ (on which $m$ and $p_2$ agree), yields $C\iso B$.
+Thus, $p_2^*B \iso m^*[\dim H]B$, from which is follows that $B$ is $H$-equivariant.
+\end{proof}
 

### 2015-08-31 followup.tex
Sorted out descent to the abelianization, I think! Sketched the argument.
Will add detail, later.

@@
 Let $G$ be a smooth group scheme.
-Let $G\der \hookrightarrow G$ denote the closed subgroup generated by the commutator morphism $c: G\times G \to G$ given by $c(x,y) = xyx^{-1}y^{-1}$; see \cite{SGA3}*{{VI}$_B$, 7.2}.
+Let $j: G\der \hookrightarrow G$ denote the closed subgroup generated by the commutator morphism $c: G\times G \to G$ given by $c(x,y) = xyx^{-1}y^{-1}$; see \cite{SGA3}*{{VI}$_B$, 7.2}.
+Let $n : G\der \times G \to G$ be the restriction of $m: G\times G \to G$.
 
-\begin{lemma}
-The quotient $q : G \to G\ab$ is a smooth $G\der$-torsor, and the coequalizer of $m, p : G\der \times G \to G$.
+\begin{lemma}\label{lem:Lder}
+For every $\cs{L}$ on $G$, $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
 \end{lemma}
 
-The quotient $q : G \to G\ab$ is the coequalizer of left $G\der$-multiplication $n : G\der\times G \to G$ and projection $p : G\der\times G \to G$.
+\begin{proof}
+By construction, $c : G \times G \to G$ is schematically dense (dominant morphism) for $j : G\der \hookrightarrow G$. 
+Note that $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$.
+Thus,
+\begin{align*}
+c^* (\cs{L}\vert_{G\der})
+&=  (j\circ c)^*\cs{L} \\
+&= (m\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
+&= (m \times (\iota\circ m\op))^* m^* \cs{L} \\
+&\iso (m \times (\iota\circ m\op))^* m\op^* \cs{L} \\
+&= (m\op\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
+&= e^* \cs{L}\\
+&= (\EE)_{G\times G}.
+\end{align*}
+Since $c : G \times G \to G\der$ is schematically dense, the group homomorphism $\pi_1(G\times G, {\bar y}) \to \pi_1(G\der, {\bar x})$ is surjective, for all geometric points with $c({\bar y}) = {\bar x}$.
+It follows that $c^* (\cs{L}\vert_{G\der}) \iso (\EE)_{G\times G}$ implies $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
+\end{proof}
+
+\begin{lemma}\label{lem:smooth_coeq}
+The quotient $q : G \to G\ab\ceq G/G\der$ is a smooth $G\der$-torsor and is the coequalizer of $n : G\der \times G \to G$ with projection $p: G\der \times G \to G$. 
 \[
@@
 G\der\times G
- \arrow{r}[shift left]{m}
+ \arrow{r}[shift left]{n}
   \arrow{r}[shift right,swap]{p}
@@
 \]
-The morphism $q$ is surjective and smooth of relative dimension $\dim G\der$.
+\end{lemma}
 
- \begin{theorem}\label{thm:descent}
- Let $G$ be a smooth group scheme over $\Fq$ 
- and let $q : G \to G\ab$ be its abelianization. 
- Then  
-\[
-q^*:  \CCS(G\ab) \longrightarrow \CCS(G)
-\]
-is an equivalence of rigid monoidal categories.
-  \end{theorem}
+\begin{proposition}\label{prop:Gder-equivariance}
+$\CCS_{G\der}(G) \to \CCS(G)$ is an equivalence.
+\end{proposition}
 
 \begin{proof}
-It follows from the lemma that descent theory that $q$ is an 
-effective descent morphism for the fibred category of commutative character sheaves on smooth group schemes; in other words, the canonical functor $\CCS(G) \to \CCS_{G\der}(G)$ is an equivalence. 
-\todo{$\CCS \to \Sch{\Fq}$ is a fibred category. Is it also a stack?}
-
-Consider the morphism $c:  G \times G \to G\der$ given by $c(g,h)= ghg^{-1}h^{-1}$.
-This morphism is smooth (it is a composition of smooth maps, since $m : G \times G \to G$ is smooth) but
-
-Let $j : C \hookrightarrow G$ be the inclusion.  
-Then $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$.
-Thus,
-\begin{align*}
-c^* (\cs{L}\vert_C)
-&=  (j\circ c)^*\cs{L} \\
-&= (m\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
-&= (m \times (\iota\circ m\op))^* m^* \cs{L} \\
-&= (m \times (\iota\circ m\op))^* m\op^* \cs{L} \\
-&= (m\op\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
-&= e^* \cs{L}\\
-&= (\EE)_{G\times G}\\
-&= c^* ((\EE)_C).
-\end{align*}
-Since $c : G \times G \to C$ is faithfully flat, the functor $c^*$ is conservative.
-\todo{I'm working on this   . . . \\ -CC}
-Since $\cs{L} \to (\EE)_G$ induces $c^* (\cs{L}\vert_C) \iso c^* ((\EE)_C)$, this implies $\cs{L}\vert_C \iso (\EE)_C$.
-
-Let $\CCS_{G\der}(G)$ be the category of commutative character sheaves $\cs{L}$ on $G$ equipped with an isomorphism $n^*\cs{L} \to p^*\cs{L}$ satisfying canonical coherence conditions.
-Then $q^* : \CCS(G\ab) \to \CCS(G)$ factors through $\CCS_{G\der}(G)$. 
-\[
-\begin{tikzcd}
-\CCS(G\der \times G)
-& \arrow{l}[shift left,swap]{n^*}
-  \arrow{l}[shift right]{p^*}
-\CCS(G) 
-&&\arrow{ll}[swap]{q^*} 
-\CCS(G\ab) \arrow{dl}{\text{comparison}}\\
-&& \arrow{ul}{\text{forget}} \CCS_{G\der}(G) & 
-\end{tikzcd}
-\]
-To see this, let $\cs{E}$ be a commutative character sheaf on $G\ab$ and observe that $q^* \cs{E}$ is equipped with a canonical isomorphism $n^*(q^* \cs{E}) \to p^*(q^* \cs{E})$ given by
-\[
-n^* (q^*\cs{E}) \iso (q\circ n)^* \cs{E} = (q\circ p)^* \cs{E} \iso p^* (q^*\cs{E}).
-\]
-Moreover, since $q : G \to G\ab$ is a smooth principal $G\der$-bundle and $G\der$ is geometrically connected,
-the comparison functor is an equivalence.
-%(In other language, $q^*$ is a monadic functor.)
-Indeed, it is easy to see that $\CCS(G\ab) \to \CCS_{G\der}(G)$ is full and faithful; to see that is it also essentially surjective, one begins with $\cs{L} \in \CCS(G)$ and $\nu : n^*\cs{L} \to p^*\cs{L}$ and builds $\cs{E}\in \CCS(G\ab)$ Zariski-locally by pull-back along local trivializations $U \to G\times_{G\ab} U$ of $q : G\to G\ab$ compatible with the $C$-action, glueing using isomorphisms inherited from the isomorphism $\nu$, and finally verifying that the result is a local system with the auxilliary data defining a commutative character sheaf.
-See appendix for details.
-
-To see that the forgetful functor $\CCS_{G\der}(G) \to \CCS(G)$ is an equivalence we observe that
+It follows from Lemma~\ref{lem:Lder} that the forgetful functor $\CCS_{G\der}(G) \to \CCS(G)$ is an equivalence. To see this, we observe that
 every commutative character sheaf $\cs{L}$ on $G$ is equivariant for the left translation action of $C$ on $G$, as follows.
@@
 \end{align*}
-
+Thus, $\cs{L}$ is $G\der$-equivariant.
 \end{proof}
 
-\begin{remark}\label{rem:descent}
-\end{remark}
+\begin{theorem}\label{thm:descent}
+ Let $G$ be a smooth group scheme over $\Fq$ 
+ and let $q : G \to G\ab$ be its abelianization. 
+ Then  
+\[
+q^*:  \CCS(G\ab) \longrightarrow \CCS(G)
+\]
+is an equivalence of rigid monoidal categories.
+\end{theorem}
+
+\begin{proof}
+It follows from Lemma~\ref{lem:smooth_coeq} that $q$ is an 
+effective descent morphism for the fibred category of commutative character sheaves on smooth group schemes; in other words, the canonical functor $\CCS(G) \to \CCS_{G\der}(G)$ is an equivalence. 
+\todo{$\CCS \to \Sch{\Fq}$ is a fibred category. Is it also a stack?}
+See appendix for details.
+%
+Combining this with Proposition~\ref{prop:Gder-equivariant}, it follows that $q^* : \CCS(G\ab)\to \CCS(G)$ is an equivalence.
+\end{proof}
 

### 2015-09-03 followup.tex
Small improvements to descent to abelianization section.
Comment about stacks

@@
 
-\begin{lemma}\label{lem:smooth_coeq}
-The quotient $q : G \to G\ab\ceq G/G\der$ is a smooth $G\der$-torsor and is the coequalizer of $n : G\der \times G \to G$ with projection $p: G\der \times G \to G$. 
-\[
-\begin{tikzcd}
-G\der\times G
- \arrow{r}[shift left]{n}
-  \arrow{r}[shift right,swap]{p}
-&
-G 
-\arrow{r}{q}
-& 
-G\ab
-\end{tikzcd}
-\]
-\end{lemma}
-
 \begin{proposition}\label{prop:Gder-equivariance}
@@
 
+\begin{lemma}\label{lem:smooth_coeq}
+The quotient $q : G \to G\ab\ceq G/G\der$ is a smooth $G\der$-torsor and is the coequalizer of $n : G\der \times G \to G$ with projection $p: G\der \times G \to G$. 
+\[
+\begin{tikzcd}
+G\der\times G
+ \arrow{r}[shift left]{n}
+  \arrow{r}[shift right,swap]{p}
+&
+G 
+\arrow{r}{q}
+& 
+G\ab
+\end{tikzcd}
+\]
+\end{lemma}
+
 \begin{theorem}\label{thm:descent}
@@
 effective descent morphism for the fibred category of commutative character sheaves on smooth group schemes; in other words, the canonical functor $\CCS(G) \to \CCS_{G\der}(G)$ is an equivalence. 
-\todo{$\CCS \to \Sch{\Fq}$ is a fibred category. Is it also a stack?}
+\todo{$\CCS \to \Sch{\Fq}$ is a fibred category. Is it also a stack? That might require a small section, just before this one.}
 See appendix for details.
 %
-Combining this with Proposition~\ref{prop:Gder-equivariant}, it follows that $q^* : \CCS(G\ab)\to \CCS(G)$ is an equivalence.
+Combining this with Proposition~\ref{prop:Gder-equivariance}, it follows that $q^* : \CCS(G\ab)\to \CCS(G)$ is an equivalence.
 \end{proof}

### 2015-09-06 followup.tex
Diagrams added to descent to abelianization
Commit before talking to David

@@
 Let $j: G\der \hookrightarrow G$ denote the closed subgroup generated by the commutator morphism $c: G\times G \to G$ given by $c(x,y) = xyx^{-1}y^{-1}$; see \cite{SGA3}*{{VI}$_B$, 7.2}.
-Let $n : G\der \times G \to G$ be the restriction of $m: G\times G \to G$.
+
+\[
+\begin{tikzcd}
+{} & G\times G \arrow{d}{c} &&&\\
+1 \arrow{r} & G\der \arrow{r}{j} & G \arrow{r}{q} & G\ab \arrow{r} & 1
+\end{tikzcd}
+\]
 
@@
 
+Let $n : G\der \times G \to G$ be the restriction of $m: G\times G \to G$.
+
 \begin{proposition}\label{prop:Gder-equivariance}
@@
 
-\begin{lemma}\label{lem:smooth_coeq}
-The quotient $q : G \to G\ab\ceq G/G\der$ is a smooth $G\der$-torsor and is the coequalizer of $n : G\der \times G \to G$ with projection $p: G\der \times G \to G$. 
+The quotient $q : G \to G\ab$ with kernel $G\der$  is the coequalizer of $n : G\der \times G \to G$ with projection $p: G\der \times G \to G$. 
 \[
@@
 \]
+
+\begin{lemma}\label{lem:smooth_coeq}
+The quotient $q : G \to G\ab\ceq G/G\der$ is a smooth $G\der$-torsor.
 \end{lemma}
+
+[I don't have a proof of this yet.]
+
+\[
+\begin{tikzcd}
+\CCS(G\der \times G)
+& \arrow{l}[shift left,swap]{n^*}
+  \arrow{l}[shift right]{p^*}
+\CCS(G) 
+&&\arrow{ll}[swap]{f^*} 
+\CCS(G\ab) \arrow{dl}{\text{`comparison'}}\\
+& & \arrow{ul}{\text{forget}} \CCS_{G\der}(G) & 
+\end{tikzcd}
+\]
 
@@
 
-\section{Geometrization of generic types for supercuspidal representations}
+\section{Application to certain supercuspidal representations of $p$-adic groups}
+
+[A basic question which I think we must answer but which we can maybe skate around for now:
+When is the Suzuki transform of a K-variety representable as a k-scheme?
 
@@
 Set $G_n = \Gr^R_n(\underline{G})$; this is a smooth group scheme over $\Fq$.
-Set $G = \Gr^R_n(\underline{G})$; this is a group scheme over $\Fq$ equipped with $G = \varprojlim_{n\in \NN} G_n$.
-Let $\QCS(\underline{G})$ be the category of commutative character sheaves on $G$. . . .  as in \cite{cunningham-roe:13a}.
+Set $G = \Gr_R(\underline{G})$; this is a group scheme over $\Fq$ equipped with $G = \varprojlim_{n\in \NN} G_n$.
+Let $\QCS(G)$ be the category of commutative character sheaves on $G$. . . .  as in \cite{cunningham-roe:13a}.
 
-\begin{corollary}\label{cor:QCS}
-$\Hom(\underline{G}(\OK),\EEx) \iso \QCSiso{\underline{G}}$.
-\end{corollary}
+\begin{proposition}\label{prop:QCS}
+$\Hom(\underline{G}(\OK),\EEx) \iso \QCSiso{G}$.
+\end{proposition}
 

### 2015-09-06 followup.tex
Commit after conversation with David

@@
 Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$.
-Conversely, if a [rank-$1$] character sheaf on $G$ is equivariant for conjugation, then $G$ is commutative.
+Conversely, if a [rank-$1$] character sheaf on $G$ is equivariant for conjugation, then it is commutative.
 \end{proposition}
@@
 \begin{proof}
-By construction, $c : G \times G \to G$ is schematically dense (dominant morphism) for $j : G\der \hookrightarrow G$. 
+By construction, $c : G \times G \to G\der$ is dominant. 
 Note that $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$.
@@
 Since $c : G \times G \to G\der$ is schematically dense, the group homomorphism $\pi_1(G\times G, {\bar y}) \to \pi_1(G\der, {\bar x})$ is surjective, for all geometric points with $c({\bar y}) = {\bar x}$.
-It follows that $c^* (\cs{L}\vert_{G\der}) \iso (\EE)_{G\times G}$ implies $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
+\todo{Produce or find a proof.} It follows that $c^* (\cs{L}\vert_{G\der}) \iso (\EE)_{G\times G}$ implies $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$. 
 \end{proof}
@@
 
-[I don't have a proof of this yet.]
+[I don't have a proof of this yet.]\todo{Either true or it becomes a condition on $G$.}
 
@@
 \CCS(G) 
-&&\arrow{ll}[swap]{f^*} 
+&&\arrow{ll}[swap]{q^*} 
 \CCS(G\ab) \arrow{dl}{\text{`comparison'}}\\

### 2015-09-11 followup.tex
Add rank-1

@@
 First, we use commutative character sheaves to produce a functorial geometrization of characters of $G(\Fq)$ in all cases, thus repairing a defect in the function-sheaf dictionary for algebraic groups $G$ which appears when the component group of $G$ is $\Hh^2(\pi_0(\bG),\EEx)^{\Frob{}}$ is non-trivial.
-Second, we revisit the motivations for the stacky abelianization construction, and show that, after replacing the character sheaves on $G$ with commutative character sheaves on $G$, the schematic abelianization $G \to G\ab$ is the correct quotient.
+Second, we revisit the motivations for the stacky abelianization construction, and show that, after replacing the rank-$1$ character sheaves on $G$ with commutative character sheaves on $G$, the schematic abelianization $G \to G\ab$ is the correct quotient.
 This is an immediate consequence of the fact that the category of commutative character sheaves on $G$ is equivalent to the category of commutative character sheaves on $G\ab$. 
@@
 \labitem{(3)}{b3}
-Like the category $\CS(G)$ of character sheaves on $G$, which described completely in \cite{cunningham-roe:13a}, $\CCS(G)$ is a rigid monoidal category.
+Like the category $\CS(G)$ of character sheaves on $G$, which is described completely in \cite{cunningham-roe:13a}, $\CCS(G)$ is a rigid monoidal category.
 Since $\CCS(G)$ is a full subcategory of $\CS(G)$, and since Item \ref{b2} above shows $\CCSiso{G} \iso G(\Fq)^*$, canonically, the category $\CCS(G)$ is now completely described by the following consequence of \cite{cunningham-roe:13a}*{Thm.
@@
 
-Recall \cite{cunningham-roe:13a}*{Def. 1.1} that a character sheaf on $G$ is a triple $\cs{L} \ceq (\gcs{L}, \mu, \phi)$,
+When $G$ is commutative, recall \cite{cunningham-roe:13a}*{Def. 1.1} that a character sheaf on $G$ is a triple $\cs{L} \ceq (\gcs{L}, \mu, \phi)$,
 where $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, $\mu : \bm^* \gcs{L} \to \LxL$ is an isomorphism
 of sheaves on $\bG \times \bG$, and $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an isomorphism of sheaves on $\bG$.
-In \emph{loc. cit.}, $G$ was assumed to be commutative, but the same definition makes sense for non-commutative $G$.
-We will denote the category of character sheaves on $G$ by $\CS(G)$.
-\todo{I think we should hold the term `character sheaves for G', when $G$ is not commutative, in reserve, and not use it here for non-commutative $G$.
-So I might advocate going back to the full definition here.
-Or, we might introduce the term `rank-$1$ character sheaf, similar to what Masoud did  .
-.
-.
-\\ -CC}
+The same definition makes sense for non-commutative $G$.  In order to distinguish the resulting objects from
+the character sheaves of Lusztig, we will refer to them as \emph{rank-$1$ character sheaves} (following \cite{Kamgarpour})
+and write $\CS(G)$ for the resulting category, with morphisms defined as in \cite{cunningham-roe:13a}*{Def. 1.1}.
 
 \begin{definition}\label{def:CCS}
-A character sheaf on $G$ is \emph{commutative} if there is an isomorphism ${\bar m}^* \gcs{L} \to {\bar m}\op^* \gcs{L}$
+A rank-$1$ character sheaf on $G$ is \emph{commutative} if there is an isomorphism ${\bar m}^* \gcs{L} \to {\bar m}\op^* \gcs{L}$
 such that the following diagram commutes,
@@
 Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$.
-Conversely, if a [rank-$1$] character sheaf on $G$ is equivariant for conjugation, then it is commutative.
+Conversely, if a rank-$1$ character sheaf on $G$ is equivariant for conjugation, then it is commutative.
 \end{proposition}
@@
 
-Conversely, let $(\cs{L}, a^*\cs{L} \iso p_2^*\cs{L})$ be an equivariant [rank-$1$] character sheaf.
+Conversely, let $(\cs{L}, a^*\cs{L} \iso p_2^*\cs{L})$ be an equivariant rank-$1$ character sheaf.
 Observe that $m = a \circ (p_1\times m\op)$ while $p_2 \circ (p_1\times m\op) = m\op$. Thus, 
@@
 
- Talk about relationship with \cite{kamgarpour:09a}.  In particular, explain why the character sheaf corresponding
+ Talk about relationship with \cite{kamgarpour:09a}.  In particular, explain why the rank-$1$ character sheaf corresponding
  to the cover

### 2015-09-11 followup.tex
Friday catchup
hey!

@@
 
-\title[Commutative Character Sheaves]{Commutative Character Sheaves, with an application to generic types for supercuspidal representations}
+\title[Commutative Character Sheaves]{Commutative Character Sheaves}
+%with an application to geometric types for supercuspidal representations
 \author{Clifton Cunningham}
@@
 
-\section{Application to certain supercuspidal representations of $p$-adic groups}
-
-[A basic question which I think we must answer but which we can maybe skate around for now:
-When is the Suzuki transform of a K-variety representable as a k-scheme?
+\section{Application: geometric types for supercuspidal representations}
 
@@
 
+{Application to certain supercuspidal representations of $p$-adic groups}
+
 \appendix
 
-\section{Descent along smooth fibrations}
+\section{Descent along torsors}
 
-Let $G$ be a group scheme acting on $X$ by $m : G \times X \to X$.
+Let $G$ be a group scheme acting on $X$ by $m : G \times X \to X$; let $p : G\times X \to X$ be projection.
 
-A principal $G$-bundle $f : X\to Y$ is a coequalizer of $m$ and projection $G\times X \to X$  
+Recall that a morphism $f : X\to S$ is a regular epimorphism if . . . . coequalizer for the pair of morphisms $(m,p)$ if ....
+
+A morphism $f : X\to S$ is a $G$-torsor if it is equivariant for the trivial action of $G$ on $S$ and if there is a covering $\{ S_i \tq i \in I\}$ of $S$ such that, for each $i\in I$, there is an isomorphism $X\times_S S_i \to G\times S_i$ such that composition with projection $G\times S_i \to S_i$ is $X\times_S S_i \to S_i$.
+
+We recall the definition of the category $\Loc_G(X)$ of $G$-equivariant local systems on $X$.
+Objects in $\Loc_G(X)$ are pairs $(\cs{L}, \nu)$ where $\cs{L} \in \Loc(X)$ and $\nu : m^*\cs{L} \to p^*\cs{L}$ is an isomorphism in $\Loc(G\times X)$
+such that the following diagram commutes, where $m_0(a,b,x) = (a,m(b,x))$ and $m_1(a,b,x) = (m(ab),x)$ and $p_2(a,b,x) = (b,x)$.
+\[
+\begin{tikzcd}
+\ &  m_0^*  m^*\, \mathcal{L} \arrow{r}{m_0^*\nu} & m_0^* p^*\, \mathcal{L} & \\
+m_1^* m^*\, \mathcal{L} \arrow{dr}[swap]{m_1^*\nu} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{p_2^*\nu} p_2^* m^*\, \mathcal{L} \\
+& m_1^* p^*\, \mathcal{L} \arrow[equal]{r} & p_2^* p^*\, \mathcal{L} & 
+\end{tikzcd}
+\]
+
+A morphism $(\cs{L},\nu) \to (\cs{L}',\nu')$ in $\Loc_G(X)$ is a morphism $\alpha: \cs{L} \to \cs{L}'$ in $\Loc(X)$ such that . . . .
+
+Let $f : X\to S$ be a regular epimorphism with kernel pair $(m,p)$. 
+If $\cs{S} \in \Loc(S)$ then $f^*\cs{S} \in \Loc(X)$ comes equipped with a canonical isomorphism $m^* (f^* \cs{S}) \to p^* (f^*\cs{S})$, since $f\circ m = f\circ p$.
+This defines $f_G^* : \Loc(S) \to \Loc_G(X)$ such that the functor $f^* : \Loc(S) \to \Loc(X)$ factors as below.
+\[
+\begin{tikzcd}
+\Loc(X) 
+&&\arrow{ll}[swap]{f^*} 
+\Loc(S) \arrow{dl}{f_G^*}\\
+& \arrow{ul}{\text{forget}} \Loc_G(X) & 
+\end{tikzcd}
+\]
+
+\begin{lemma}\label{lem:descent}
+If $f: X\to S$ is a $G$-torsor and a regular epimorphism for $(m,p)$, then $f_G^* : \Loc(S) \to \Loc_G(X)$ admits a left-adjoint.
+% $f^G_! : \Loc_G(X) \to \Loc(S)$
+\end{lemma}
+
+\begin{remark}
+Comparison with the comparison functor
+\end{remark}
+
+\begin{lemma}
+In this case, the functor $f^* : \Loc(S)\to \Loc(X)$ admits a left-adjoint 
+\end{lemma}
+\begin{proof}
+The left-adjoint $f_! : \Loc(X) \to \Loc(S)$ is defined as follows.
+Now, suppose $\cs{L}\in \Loc(X)$.
+For each $i\in I$, define $\cs{S}_i \in \Loc(S_i)$ by $\cs{S}_i\ceq t_i^* \cs{L}$.
+The sheaves $\cs{S}_i$ glue to define a sheaf $\cs{S}$ on $S$ by definition above.
+Morphisms of these sheaves are likewise defined locally . . .
+
+\end{proof}
+
+is a coequalizer of $m$ and projection $G\times X \to X$  
 which is locally trivial in the following sense.
 First, there is an open covering $\{ V_n\}$ of $Y$ such that, for each $V$ in this covering, the lower coequalizer diagram is a base change of the one above
-\[
-\begin{tikzcd}
-G\times X
- \arrow{rr}[shift left]{m}
-  \arrow{rr}[shift right,swap]{\text{proj'n}}
-&& X \arrow{r}{f} &  Y\\
-G\times  (G\times V) \arrow{u}
- \arrow{rr}[shift left]{\text{mult'n in $G$}}
-  \arrow{rr}[shift right,swap]{\text{proj'n}}
-&& G\times V \arrow{u}  \arrow{r} &  \arrow{u} V;
-\end{tikzcd}
-\]
 
@@
 Let $\Loc^1(X)$ be the category of rank-$1$ local systems on $X$ and let $\Loc_G^1(X)$ be the category of $G$-equivariant rank-$1$ local systems on $X$.
-
-\begin{proposition}
-Let $G$, $X$ and $Y$ be smooth.
-Let $f : X \to Y$ be a $G$-torsor.
-Then the comparison functor, pictured below,
-\[
-\begin{tikzcd}
-%\Loc^1(G \times X)
-%& \arrow{l}[shift left,swap]{m^*}
-%  \arrow{l}[shift right]{p^*}
-\Loc^1(X) 
-&&\arrow{ll}[swap]{f^*} 
-\Loc^1(Y) \arrow{dl}{\text{comparison}}\\
-& \arrow{ul}{\text{forget}} \Loc^1_G(X) & 
-\end{tikzcd}
-\]
-is an equivalence.
-\end{proposition}
 
@@
 \]  
-From \cite[Prop~4.2.5]{BBD}  it follows that $\mathcal{G}\in \obj{\mathcal M}{Y}$. This completes the proof of Proposition~\ref{proposition: torsor}.
+From \cite[Prop~4.2.5]{BBD}  it follows that $\mathcal{G}\in \obj{\mathcal M}{Y}$. This completes the proof of Proposition~\ref{lem:descent}.
 \end{proof}
+
+\begin{proposition}
+Let $f : X \to S$ be a morphism of smooth group schemes.
+Suppose $G$ is a smooth group scheme acting on $X$.
+Suppose $f$ is a $G$-torsor.
+Then the comparison functor, pictured below,
+\[
+\begin{tikzcd}
+\CCS(X) 
+&&\arrow{ll}[swap]{f^*} 
+\CCS(S) \arrow{dl}{\text{comparison}}\\
+& \arrow{ul}{\text{forget}} \CCS_G(X) & 
+\end{tikzcd}
+\]
+is an equivalence.
+\end{proposition}
 

### 2015-09-18 followup.tex
Descent re-written

--- 2015-09-11 followup.tex
@@
 
-\section{Descent to the abelianization}
+\section{Descent for commutative character sheaves}
+
+\subsection{Quotients}
+
+Let $G$ be a $k$-group scheme and let $H \to G$ be a closed subgroup scheme over $S$.
+
+Write $n : H \times_S G \to G$ for the left action of $H$ on $G$; let $p : H\times_S G \to G$ be projection.
+
+\subsection{$H$-equivariance}
+
+An $H$-equivariant rank-$1$ character sheaf on $H$ is a rank-$1$ character sheaf $\cs{L} = (\gcs{L},\phi,\mu)$ on $G$ together with an isomorphism  $\nu : {\bar m}_H^*\gcs{L} \to {\bar p}_H^*\gcs{L}$ such that the following diagrams commute, expressing compatibility with $\phi$ and $\mu$:
+\begin{enumerate}
+\item
+\[
+\begin{tikzcd}
+\ &  m_0^*  m^*\, \mathcal{L} \arrow{r}{m_0^*\nu} & m_0^* p^*\, \mathcal{L} & \\
+m_1^* m^*\, \mathcal{L} \arrow{dr}[swap]{m_1^*\nu} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{p_2^*\nu} p_2^* m^*\, \mathcal{L} \\
+& m_1^* p^*\, \mathcal{L} \arrow[equal]{r} & p_2^* p^*\, \mathcal{L} & 
+\end{tikzcd}
+\]
+where $m_0(a,b,x) = (a,m(b,x))$ and $m_1(a,b,x) = (m(ab),x)$ and $p_2(a,b,x) = (b,x)$;
+\item
+\end{enumerate}
+Write $\CCS_H(G)$ for the category of $H$-equivariant commutative character sheaves on $G$.
+\subsection{Descent}
+
+We now suppose that $H$ is normal in $G$, that the fppf-quotient $G \to G'\ceq H\backslash G$ exists.
+Then $q : G \to G'$ is a regular epimorphism with kernel pair $(n,p)$ in the category of schemes.
+In particular, $G \times_{G'} G \iso H\times_S G'$, so $G \to G'$ is a $G$-torsor in the fppf topology.
+
+In this case we may factor the functor $\CCS(G') \to \CCS(G)$  . . . 
+\[
+\begin{tikzcd}
+\CCS(G) &&\arrow{ll}[swap]{q^*} 
+\CCS(G') \arrow{dl}{\text{`comparison'}}\\
+& \arrow{ul}{\text{forget}} \CCS_{H}(G) & 
+\end{tikzcd}
+\]
+
+\begin{lemma}\label{lem:descent}
+If the quotient $q : G \to G'$ is a $G$-torsor in the etale topology, then the comparison functor $\CCS(G') \to \CCS_{H}(G)$ is an equivalence.
+\end{lemma}
+
+\begin{proof}
+By descent theory, the functor $\Loc(G') \to \Loc_H(G)$ induced by $q: G \to G'$ is an equivalence of categories. 
+\end{proof}
+
+\subsection{Dominant morphisms and local systems}
+
+\begin{lemma}\label{lem:dominant}
+Suppose $f: X \to Y$ is dominant.
+If $\cs{L}\in \Loc(Y)$ and $f^*\cs{L} \iso (\EE)_X$ then $\cs{L} \iso (\EE)_Y$.
+\end{lemma}
+
+\begin{proof}
+The group homomorphism $\pi_1(f): \pi_1(X, {\bar x}) \to \pi_1(Y, {\bar y})$ is surjective, for all geometric points with $f({\bar x}) = {\bar y}$ ... 
+%\todo{Under construction}
+\end{proof}
+
+\subsection{Derived subgroup}
 
@@
 \end{align*}
-Since $c : G \times G \to G\der$ is schematically dense, the group homomorphism $\pi_1(G\times G, {\bar y}) \to \pi_1(G\der, {\bar x})$ is surjective, for all geometric points with $c({\bar y}) = {\bar x}$.
-\todo{Produce or find a proof.} It follows that $c^* (\cs{L}\vert_{G\der}) \iso (\EE)_{G\times G}$ implies $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$. 
+Since $c : G \times G \to G\der$ is schematically dense, $c^* (\cs{L}\vert_{G\der}) \iso (\EE)_{G\times G}$ implies $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ by Lemma~\ref{lem:dominant}.
 \end{proof}
-
-Let $n : G\der \times G \to G$ be the restriction of $m: G\times G \to G$.
 
@@
 \begin{proof}
-It follows from Lemma~\ref{lem:Lder} that the forgetful functor $\CCS_{G\der}(G) \to \CCS(G)$ is an equivalence. To see this, we observe that
-every commutative character sheaf $\cs{L}$ on $G$ is equivariant for the left translation action of $C$ on $G$, as follows.
-Let $j : C \hookrightarrow G$ be the kernel of $q : G \to G\ab$ and let $m : G\times G \to G$ be multiplication for $G$. 
+%Let $j : C \hookrightarrow G$ be the kernel of $q : G \to G\ab$ and let $m : G\times G \to G$ be multiplication for $G$. 
+Let $n : G\der \times G \to G$ be the restriction of $m: G\times G \to G$.
 Then $n = m \circ (j \times \id)$, so
@@
 \end{align*}
-Thus, $\cs{L}$ is $G\der$-equivariant.
+Thus, every commutative character sheaf $\cs{L}$ on $G$ is $G\der$-equivariant.
+It now follows from Lemma~\ref{lem:Lder} that the forgetful functor $\CCS_{G\der}(G) \to \CCS(G)$ is an equivalence. 
 \end{proof}
 
-The quotient $q : G \to G\ab$ with kernel $G\der$  is the coequalizer of $n : G\der \times G \to G$ with projection $p: G\der \times G \to G$. 
+\subsection{Abelianization}
+
+By definition, the abelianization $G\ab$ of $G$ is the fppf-quotient $q : G \to G\ab$ of $G$ by $G\der$. 
+This exists in schemes since  . . . 
+%\todo{Proof needed}
+%  is the coequalizer of $n : G\der \times G \to G$ with projection $p: G\der \times G \to G$. 
 \[
@@
 
-\begin{lemma}\label{lem:smooth_coeq}
-The quotient $q : G \to G\ab\ceq G/G\der$ is a smooth $G\der$-torsor.
-\end{lemma}
+\begin{proposition}\label{prop:Gab-descent}
+Let $G$ be a smooth group scheme over $\Fq$ 
+ and let $q : G \to G\ab$ be its abelianization. 
+ Then  
+\[
+\CCS(G\ab) \longrightarrow \CCS_{G\der}(G)
+\]
+is an equivalence of categories.
+\end{proposition}
 
-[I don't have a proof of this yet.]\todo{Either true or it becomes a condition on $G$.}
+\begin{proof}
+The quotient $G \to G\ab$ is a $G\der$-torsor in the etale topology, \todo{Either true or it becomes a condition on $G$.} so the result follows from Lemma~\ref{lem:descent}.
+\end{proof}
 
-\[
-\begin{tikzcd}
-\CCS(G\der \times G)
-& \arrow{l}[shift left,swap]{n^*}
-  \arrow{l}[shift right]{p^*}
-\CCS(G) 
-&&\arrow{ll}[swap]{q^*} 
-\CCS(G\ab) \arrow{dl}{\text{`comparison'}}\\
-& & \arrow{ul}{\text{forget}} \CCS_{G\der}(G) & 
-\end{tikzcd}
-\]
-
-\begin{theorem}\label{thm:descent}
+\begin{theorem}\label{thm:Gab-descent}
  Let $G$ be a smooth group scheme over $\Fq$ 
@@
 \end{theorem}
-
 \begin{proof}
-It follows from Lemma~\ref{lem:smooth_coeq} that $q$ is an 
-effective descent morphism for the fibred category of commutative character sheaves on smooth group schemes; in other words, the canonical functor $\CCS(G) \to \CCS_{G\der}(G)$ is an equivalence. 
-\todo{$\CCS \to \Sch{\Fq}$ is a fibred category. Is it also a stack? That might require a small section, just before this one.}
-See appendix for details.
-%
-Combining this with Proposition~\ref{prop:Gder-equivariance}, it follows that $q^* : \CCS(G\ab)\to \CCS(G)$ is an equivalence.
+Combine Propositions~\ref{prop:Gder-equivariance} and \ref{prop:Gab-descent}.
 \end{proof}
 
-\begin{remark}
-A great tragedy of nomenclature: an equivariant sheaf is not a sheaf that is equivariant. \todo{I will explain this.\\ -CC} 
-\end{remark}
-
  \begin{corollary}
- Trace of Frobenius induces an isomorphism
+The following is a commuting diagram of isomorphisms:
 \[
- \CCSiso{G} \to G(\Fq)^*.
+\begin{tikzcd}
+\CCSiso{G} \arrow{r} & G(\Fq)^*\\
+\arrow{u}{q^*} \CCSiso{G\ab} \arrow{r} & \arrow{u} G\ab(\Fq)^* . \\
+\end{tikzcd}
 \]
@@
  \begin{proof}
- By descent along $G \to G/C$, pullback induces an equivalence of categories between $C$-equivariant local systems on $G$ local systems on  $G/C$.
-\todo{I need to explain what's going on here.
-See appendix.\\ -CC}
-  The result now follows from Theorem \ref{thm:trfrobiso} and the fact that all characters of $G(\Fq)$ factor through
- $G(\Fq)/C(\Fq)$, which equals $(G/C)(\Fq)$ since $C$ is simply connected.
+ By Theorem \ref{thm:trfrobiso}, $\CCSiso{G}\to G(\Fq)^*$ and $\CCSiso{G\ab}\to G\ab(\Fq)^*$ are isomorphisms.
+By Theorem~\ref{thm:Gab-descent}, $\CCSiso{G} \iso \CCSiso{G\ab}$.
+Since $G\der$ is simply connected,\todo{Proof needed}, $G\ab(\Fq) = G(\Fq)/G\der(\Fq)$.
+Thus, all characters of $G(\Fq)$ factor through
+ $G\ab(\Fq)$. . . . 
+ The isomorphisms are compatible because  . . . 
  \end{proof}
@@
  \]
- is not commutative.  Explain how our character sheaves are not just representations of a fundamental group
- (or are they?), but instead have extra data like $\mu$ and $\phi$.
-\todo{I got this wrong.
+ is not commutative.  
+ %Explain how our character sheaves are not just representations of a fundamental group (or are they?), but instead have extra data like $\mu$ and $\phi$.
+%\todo{I got this wrong.
 I think our sheaves are not extra information in the commutative case.
@@
 
-\section{Application to certain supercuspidal representations of $p$-adic groups}
+\section{Applications to supercuspidal representations}
 
-[A basic question which I think we must answer but which we can maybe skate around for now:
-When is the Suzuki transform of a K-variety representable as a k-scheme?
+\subsection{Commutative quasicharacter sheaves}
 
@@
 \end{proposition}
+
+ \subsection{Geometric types for supercuspidal representations}
 
@@
 Then $\pi_0$ is produced by compact induction from representation $\sigma$ of a compact mod centre subgroup $\underline{C}_0(\OK) \subset \G^0(K)$.
-Moreover, $C_0$ admits a smooth integral model $\underline{C}$ \todo{Under construction.
-\\ -CC}
+Moreover, $C_0$ admits a smooth integral model $\underline{C}$ ...
 
-\appendix
-
-\section{Descent along smooth fibrations}
-
-Let $G$ be a group scheme acting on $X$ by $m : G \times X \to X$.
-
-A principal $G$-bundle $f : X\to Y$ is a coequalizer of $m$ and projection $G\times X \to X$  
-which is locally trivial in the following sense.
-First, there is an open covering $\{ V_n\}$ of $Y$ such that, for each $V$ in this covering, the lower coequalizer diagram is a base change of the one above
-\[
-\begin{tikzcd}
-G\times X
- \arrow{rr}[shift left]{m}
-  \arrow{rr}[shift right,swap]{\text{proj'n}}
-&& X \arrow{r}{f} &  Y\\
-G\times  (G\times V) \arrow{u}
- \arrow{rr}[shift left]{\text{mult'n in $G$}}
-  \arrow{rr}[shift right,swap]{\text{proj'n}}
-&& G\times V \arrow{u}  \arrow{r} &  \arrow{u} V;
-\end{tikzcd}
-\]
-
-and the following diagram commutes
-\[
-\begin{tikzcd}
-G\times  f^{-1}(V)
- \arrow{r}[shift left]{m}
-  \arrow{dr} 
-& f^{-1}(V) \arrow{r} \arrow{d}{t_V} &  V \\
-& G\times V \arrow{ur} & 
-\end{tikzcd}
-\]
-
-and isomorphisms ${t}_n : f^{-1}{V}_n \to {G}\times {V}_n$ such that  ${f}$ is given locally by ${f}_n = p \circ {t}_n$ (so ${f}_n : {f}^{-1}{Y}_n \to {Y}_n$) and the action ${m}_{X}$ of ${G}$ on ${X}$ is given locally by ${t}_n \circ {m}_n =  ({m} \times \id) \circ (\id\times{t}_n)$ (so ${m}_n : {G}\times{f}^{-1}{Y}_n \to {f}^{-1}{Y}_n$).
-
-Let $\Loc^1(X)$ be the category of rank-$1$ local systems on $X$ and let $\Loc_G^1(X)$ be the category of $G$-equivariant rank-$1$ local systems on $X$.
-
-\begin{proposition}
-Let $G$, $X$ and $Y$ be smooth.
-Let $f : X \to Y$ be a $G$-torsor.
-Then the comparison functor, pictured below,
-\[
-\begin{tikzcd}
-%\Loc^1(G \times X)
-%& \arrow{l}[shift left,swap]{m^*}
-%  \arrow{l}[shift right]{p^*}
-\Loc^1(X) 
-&&\arrow{ll}[swap]{f^*} 
-\Loc^1(Y) \arrow{dl}{\text{comparison}}\\
-& \arrow{ul}{\text{forget}} \Loc^1_G(X) & 
-\end{tikzcd}
-\]
-is an equivalence.
-\end{proposition}
-
-\begin{proof}
-This is well-known. We include a proof only for completeness.
-
-To simplify notation slightly, set ${X}_n \ceq {f}^{-1}{Y}_n$; also, let ${j}_n : {Y}_n \to {Y}$ and ${i}_n : {X}_n \to {X}$ denote inclusions.
-
-Then $f : X \to Y$ is a smooth, regular epimorphism with kernel pair $m, p: G\times X\to X$, and t
-
-Consider the following commuting diagram:
-\[
-\begin{tikzcd}
-H\times X \arrow{d}{\id\times f} \arrow{r}{m_X}&\to X\arrow{d}{f}\\
-H\times Y \arrow{r}{m_Y} &\to Y\\
-H\times X \arrow{r}{p_2} \arrow{u}{\id\times f} &\to X \arrow{u}{f}
-\end{tikzcd}
-\]
-Thus,
-\[
-\begin{aligned}
-m_X^*[\dim H] f^*[d] A
-&\iso (f\circ m_X)^* [d+\dim H]A  &\\
-&\iso (m_Y\circ (\id\times f))^*[d+\dim H]A & \text{$f$ is equivariant}\\
-&\iso (\id\times f)^*[d] m_Y^*[\dim H] A &\\
-&\iso  (\id\times f)^*[d] p_2^*[\dim H] A &\text{$A$ is $H$-equivariant}\\
-&\iso  (p_2\circ (\id\times f))^*[d+\dim H] A &\\
-&\iso (f\circ p_2)^*[d+\dim H]A & \\
-&\iso p_2^*[\dim H] f^*[d]A. &
-\end{aligned}
-\]
-This completes the proof that $f^*[d]A$ is an $H$-equivariant perverse sheaf on $X$.
-
-Let $\mathcal{F} = {f}^*[\dim{P}] \mathcal{G}$.
-
-To show that $\mathcal{F}$ is equivariant we must find an isomorphism $\mu : {m}^* \mathcal{F} \to p^* \mathcal{F}$ in $D^b_c({P}\times{X}, \EE)$ such that ${e}^*\mu = \id_{\mathcal{F}}$, where ${e} : {X} \to {P}\times{X}$ is the section defined by $x \mapsto (1,x)$.
-To see this, consider the restriction of ${m}^* \mathcal{F}$ to ${P}\times{X}_n$:
-\begin{eqnarray*}
-({m}^* \mathcal{F})\vert_{{P}\times {X}_n}
-	&=& (\id\times {i}_n)^* {m}^* {f}^* \mathcal{G} [\dim{P}]\\
-	&\iso& ({f}\circ {m} \circ \id\times {i}_n)^* \mathcal{G} [\dim{P}]\\
-	&=& ({f} \circ {i}_n \circ {m}_n)^* \mathcal{G} [\dim{P}].
-\end{eqnarray*}
-On the other hand, the restriction of $p^* \mathcal{F}$ to ${P}\times{X}_n$ is 
-\begin{eqnarray*}
-(p^* \mathcal{F})\vert_{{P}\times {X}_n}
-	&=& (\id\times {i}_n)^* p^* {f}^* \mathcal{G} [\dim{P}]\\
-	&\iso& ({f}\circ p \circ \id\times {i}_n)^* \mathcal{G} [\dim{P}]\\
-	&=& ({f} \circ {i}_n \circ p)^* \mathcal{G} [\dim{P}].
-\end{eqnarray*}
-Since ${f} \circ {i}_n \circ {m}_n = {f} \circ {i}_n \circ p$, we have $({m}^* {\mathcal{F}})\vert_{{P}\times {X}_n} \iso (p^* \mathcal{F})\vert_{{P}\times {X}_n}$.
-Since $\cup_n {P}\times{X}_n$ is an open cover for ${P}\times{X}$, this gives the isomorphism we seek.
-
-Next, suppose $\mathcal{F} \in \obj{\mathcal M}{X}$ is equivariant; thus, $\mathcal{F} \in \obj{\mathcal M}_{P}{X}$. Let $\mathcal{F}_n$ denote the restriction of $\mathcal{F}$ to ${X}_n$.
-
-Recall that ${m}: {P}\times{X} \to {X}$ is given locally by ${m}_n : {P}\times {X}_n \to {X}_n$, as above.
-Restricting the isomorphism $\mu_{\mathcal{F}} : {m}^* \mathcal{F} \to p^* \mathcal{F}$ to ${P}\times{X}_n$ yields the isomorphism $\mu_{\mathcal{F}_n} : {m}_n^* \mathcal{F}_n \to p^* \mathcal{F}_n$.
-Thus, $\mathcal{F}_n$ is an equivariant perverse sheaf.
-Now, let ${e}_n : {Y}_n \to {X}_n$ be the section of ${f}_n : {X}_n \to {Y}_n$ corresponding to $1\in {P}(\Fq)$ (so ${e}_n$ is the unique morphism of varieties such that $({t}_n \circ {e}_n) (y) = (1,y)$).
-Define
-\begin{equation}\label{equation: torsor 5}
-	\mathcal{F}'_n \ceq {e}_n^* \mathcal{F}_n [-\dim{P}].
-\end{equation}
-Then $\mathcal{F}'_n \in \obj D^b_c({Y}_n, \EE)$.
-By standard glueing arguments, the collection of $\mathcal{F}'_n \in\obj D^b_c({Y}_n, \EE)$, as ${Y}_n$ ranges over the open cover of ${Y}$ fixed above, uniquely determines an object $\mathcal{G}$ of $D^b_c({Y}, \EE)$.
-
-It remains to be shown that $\mathcal{G}$ is a perverse sheaf. Again, we work locally. For each such $n$,
-\begin{eqnarray*}
-{f}_n^*[\dim{P}] \mathcal{F}'_n 
-	&=& {f}_n^*[\dim{P}] {e}_n^* \mathcal{F}_n [-\dim{P}]\\
-	&\iso& ({e}_n\circ {f}_n)^* \mathcal{F}_n.
-\end{eqnarray*}
-Let ${u}_n : {X}_n \to {P}\times{X}_n$ be the section of ${m}_n : {P}\times{X}_n \to {X}_n$ corresponding to $1$ (so ${u}_n$ is the unique morphism of varieties such that $(\id\times{t}_n)\circ {u}_n \circ {t}_n^{-1} (h,y) = (h,1,y)$).
-The domain of ${u}_n^*\mu_{\mathcal{F}_n}$ is ${u}_n^*{m}_n^* \mathcal{F}_n \iso ({m}_n \circ {u}_n)^* \mathcal{F}_n = \mathcal{F}_n$, since ${u}_n$ is a section of ${m}_n$; the codomain of ${u}_n^* \mu_{\mathcal{F}_n}$ is ${u}_n^* p^* \mathcal{F}_n \iso (p\circ {u}_n)^*\mathcal{F}_n$.
-Since $p\circ {u}_n = {e}_n \circ {f}_n$, it follows that
-\[
-{u}_n^* \mu_{\mathcal{F}_n} : \mathcal{F}_n \to {f}_n^*[\dim{P}] \mathcal{F}'_n
-\]
-is an isomorphism in $D^b_c({X}_n, \EE)$.
-By \cite[Prop~4.2.5]{BBD} and the fact that ${\mathcal M}{X}_n$ is stable in $D^b_c({X}_n, \EE)$ under isomorphisms, it follows that $\mathcal{F}'_n \in \obj {\mathcal M}{Y}_n$.
-By standard glueing arguments, the collection of isomorphisms ${u}_n^* \mu_{\mathcal{F}_n} \in \mor{\mathcal M}{X}_n$, as ${X}_n$ ranges over the open cover of ${X}$ fixed above, uniquely determines an isomorphism in \[
-\Hom_{D^b_c({X}, \EE)}(\mathcal{F},{f}^*[\dim{P}] \mathcal{G}).
-\]  
-From \cite[Prop~4.2.5]{BBD}  it follows that $\mathcal{G}\in \obj{\mathcal M}{Y}$. This completes the proof of Proposition~\ref{proposition: torsor}.
-\end{proof}
-
-\begin{proposition}\label{proposition: more torsor}
-Let ${f} : {X} \to {Y}$ be a principal fibration with group ${P}$ and suppose ${P}$ is connected.
-Then ${f}^*[\dim{P}] : {\mathcal M}{Y} \to {\mathcal M}_{P}{X}$ is an equivalence of categories and ${\mathcal M}_{P}{X}$ is a thick subcategory of ${\mathcal M}{X}$.
-\end{proposition}
-
-\begin{proof}
-By \cite[Prop~4.2.5]{BBD} we know that ${f}^*[\dim{P}] : {\mathcal M}{Y} \to {\mathcal M}{X}$ is full and faithful.
-Let $\mathcal{G}$ be a perverse sheaf on ${Y}$.
-From the proof of Proposition~\ref{proposition: torsor} we have seen that $\mathcal{F} \ceq {f}^*[\dim{P}] \mathcal{G}$ is an equivariant perverse sheaf on ${X}$ and that ${f}^*[\dim{P}] \phi$ is an equivariant morphism in ${\mathcal M}{X}$ for each morphism $\phi$ in ${\mathcal M}{Y}$.
-Thus, ${f}^*[\dim{P}]$ is a functor from ${\mathcal M}{Y}$ to ${\mathcal M}_{P}{X}$.
-Thus, ${f}^*[\dim{P}] : {\mathcal M}{Y} \to {\mathcal M}_{P}{X}$ is full and faithful.
-Proposition~\ref{proposition: torsor} tells us that this functor is essentially surjective.
-Thus, ${f}^*[\dim{P}]$ is an equivalence.
-The last clause of Proposition~\ref{proposition: more torsor} follows from \cite[4.2.6]{BBD}.
-\end{proof}
-
-\begin{definition}\label{definition: descent}
-Let ${f} : {X} \to {Y}$ be a principal fibration with group ${P}$ and suppose ${P}$ is connected.
-Let ${f}_\# : {\mathcal M}_{P}{X} \to {\mathcal M}{Y}$ denote the adjoint of the equivalence ${f}^*[\dim{P}] : {\mathcal M}{Y} \to {\mathcal M}_{P}{X}$ (see Proposition~\ref{proposition: more torsor}).
-In particular, ${f}_\# : {\mathcal M}_{P}{X} \to {\mathcal M}{Y}$ is an equivalence of categories.
-\end{definition}
-
-\begin{corollary}
-Suppose $H$ is a connected group acting smoothly on $X$.
-If $A\in {\mathcal M} X$ is $H$-equivariant and $B\in {\mathcal M} X$ is a subquotient of $A$, then $B$ is also $H$-equivariant.
-\end{corollary}
-
-\begin{proof}
-(Following \cite[(1.9.1)]{CS}.)
-Let the action of $H$ on $Y$ is given by $m : H\times X \to X$.
-This is a smooth morphism with connected fibres, by hypothesis.
-Thus, $m^*[\dim H]$ is an equivalence of categories, by Proposition~\ref{proposition: more torsor}.
-Since equivalences take epimorphisms to epimorphisms and monomorphisms to monomorphisms, it follows that $m^*[\dim H]B$ is a subquotient of $m^*[\dim H]A$.
-Since $A$ is an $H$-equivarient perverse sheaf on $X$, we have $m^*[\dim H]A \iso p_2^*[\dim H]A$.
-On the other hand, $p_2 : H\times X \to X$ is also a smooth morphism with connected fibres of dimension $H$, so by Proposition~\ref{proposition: more torsor}, $p_2^*[\dim H]$ identifies ${\mathcal M}_H X$ with a thick subcategory of ${\mathcal M} (H\times X)$.
-Since $m^*[\dim H]B$ is a subquotient of $p_2^*[\dim H]A$, it follows that there is some $C\in {\mathcal M} X$ such that $p_2^*C \iso m^*[\dim H]B$ restricting this isomorphism from $H\times X$ to $\{ e\} \times X$ (on which $m$ and $p_2$ agree), yields $C\iso B$.
-Thus, $p_2^*B \iso m^*[\dim H]B$, from which is follows that $B$ is $H$-equivariant.
-\end{proof}
+\subsection{Toral supercuspidal representations of $p$-adic groups}
 

### 2015-09-18 followup.tex
Added todo

@@
 
-We now suppose that $H$ is normal in $G$, that the fppf-quotient $G \to G'\ceq H\backslash G$ exists.
+We now suppose that $H$ is normal in $G$ and that the fppf-quotient $G \to G'\ceq H\backslash G$ exists.
 Then $q : G \to G'$ is a regular epimorphism with kernel pair $(n,p)$ in the category of schemes.
@@
 By definition, the abelianization $G\ab$ of $G$ is the fppf-quotient $q : G \to G\ab$ of $G$ by $G\der$. 
-This exists in schemes since  . . . 
+This exists in schemes since  . . . \todo{I hope smoothness does the trick here.}
 %\todo{Proof needed}
@@
 \begin{proof}
-The quotient $G \to G\ab$ is a $G\der$-torsor in the etale topology, \todo{Either true or it becomes a condition on $G$.} so the result follows from Lemma~\ref{lem:descent}.
+The quotient $G \to G\ab$ is a $G\der$-torsor in the etale topology, \todo{Either true or it becomes a condition on $G$.
+Again, I hope smoothness does the trick.} so the result follows from Lemma~\ref{lem:descent}.
 \end{proof}
@@
 By Theorem~\ref{thm:Gab-descent}, $\CCSiso{G} \iso \CCSiso{G\ab}$.
-Since $G\der$ is simply connected,\todo{Proof needed}, $G\ab(\Fq) = G(\Fq)/G\der(\Fq)$.
+Since $G\der$ is simply connected, \todo{Proof needed} $G\ab(\Fq) = G(\Fq)/G\der(\Fq)$.
 Thus, all characters of $G(\Fq)$ factor through

### 2015-09-19 followup.tex
Commit after talking with David.
Moved material on the derived group to section defining CCS

@@
 
+\subsection{Dominant morphisms and local systems}
+
+\begin{lemma}\label{lem:dominant}
+Suppose $f: X \to Y$ is dominant.
+If $\cs{L}\in \Loc(Y)$ and $f^*\cs{L} \iso (\EE)_X$ then $\cs{L} \iso (\EE)_Y$.
+\end{lemma}
+
+\begin{proof}
+The group homomorphism $\pi_1(f): \pi_1(X, {\bar x}) \to \pi_1(Y, {\bar y})$ is surjective, for all geometric points with $f({\bar x}) = {\bar y}$ ... 
+\todo{Under construction}
+\end{proof}
+
+\subsection{Derived subgroup}
+
+Let $G$ be a smooth group scheme.
+Let $j: G\der \hookrightarrow G$ denote the closed subgroup generated by the commutator morphism $c: G\times G \to G$ given by $c(x,y) = xyx^{-1}y^{-1}$; see \cite{SGA3}*{{VI}$_B$, 7.2}.
+
+\[
+\begin{tikzcd}
+{} & G\times G \arrow{d}{c} &&&\\
+1 \arrow{r} & G\der \arrow{r}{j} & G \arrow{r}{q} & G\ab \arrow{r} & 1
+\end{tikzcd}
+\]
+
+\begin{lemma}\label{lem:Lder}
+If $\cs{L}\in \CCS(G)$ then $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
+% Suppose Z(G) = 1$. If $\cs{L}\in \CS(G)$ and $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ then $\cs{L}\in \CCS(G)$. 
+\end{lemma}
+
+\begin{proof}
+By construction, $c : G \times G \to G\der$ is dominant. 
+Note that $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$.
+Pick $\cs{L}\in \CCS(G)$. 
+Then
+\begin{align*}
+c^* (\cs{L}\vert_{G\der})
+&=  (j\circ c)^*\cs{L} \\
+&= (m\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
+&= (m \times (\iota\circ m\op))^* m^* \cs{L} \\
+&\iso (m \times (\iota\circ m\op))^* m\op^* \cs{L} \\
+&= (m\op\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
+&= e^* \cs{L}\\
+&= (\EE)_{G\times G}.
+\end{align*}
+Since $c : G \times G \to G\der$ is schematically dense, $c^* (\cs{L}\vert_{G\der}) \iso (\EE)_{G\times G}$ implies $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ by Lemma~\ref{lem:dominant}.
+
+%Now, suppose $Z(G) =1$. Pick $\cs{L}\in \CS(G)$ and suppose $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
+\end{proof}
+
+\begin{remark}
+Lemma~\ref{lem:Lder} provides another indication of the correctness of Definition~\ref{def:CCS} 
+if one is looking for the geometrization of characters of smooth group schemes over finite fields: commutative character sheaves are trivial on $G\der$, rank-$1$ character sheaves are not.
+In the next section we provide examples to show that $\CCS(G)$ and $\CS(G)$ are not isomorphic categories, even when $G$ is a connected reductive algebraic group. 
+\end{remark}
+
 \section{Eliminating Invisible Character Sheaves}\label{sec:defect}
@@
 
-An $H$-equivariant rank-$1$ character sheaf on $H$ is a rank-$1$ character sheaf $\cs{L} = (\gcs{L},\phi,\mu)$ on $G$ together with an isomorphism  $\nu : {\bar m}_H^*\gcs{L} \to {\bar p}_H^*\gcs{L}$ such that the following diagrams commute, expressing compatibility with $\phi$ and $\mu$:
+An $H$-equivariant rank-$1$ character sheaf on $G$ is a rank-$1$ character sheaf $\cs{L} = (\gcs{L},\phi,\mu)$ on $G$ together with an isomorphism  $\nu : {\bar m}_H^*\gcs{L} \to {\bar p}_H^*\gcs{L}$ such that the following diagrams commute, expressing compatibility with $\phi$ and $\mu$:
 \begin{enumerate}
@@
 Write $\CCS_H(G)$ for the category of $H$-equivariant commutative character sheaves on $G$.
-\subsection{Descent}
-
-We now suppose that $H$ is normal in $G$ and that the fppf-quotient $G \to G'\ceq H\backslash G$ exists.
-Then $q : G \to G'$ is a regular epimorphism with kernel pair $(n,p)$ in the category of schemes.
-In particular, $G \times_{G'} G \iso H\times_S G'$, so $G \to G'$ is a $G$-torsor in the fppf topology.
-
-In this case we may factor the functor $\CCS(G') \to \CCS(G)$  . . . 
-\[
-\begin{tikzcd}
-\CCS(G) &&\arrow{ll}[swap]{q^*} 
-\CCS(G') \arrow{dl}{\text{`comparison'}}\\
-& \arrow{ul}{\text{forget}} \CCS_{H}(G) & 
-\end{tikzcd}
-\]
-
-\begin{lemma}\label{lem:descent}
-If the quotient $q : G \to G'$ is a $G$-torsor in the etale topology, then the comparison functor $\CCS(G') \to \CCS_{H}(G)$ is an equivalence.
-\end{lemma}
-
-\begin{proof}
-By descent theory, the functor $\Loc(G') \to \Loc_H(G)$ induced by $q: G \to G'$ is an equivalence of categories. 
-\end{proof}
-
-\subsection{Dominant morphisms and local systems}
-
-\begin{lemma}\label{lem:dominant}
-Suppose $f: X \to Y$ is dominant.
-If $\cs{L}\in \Loc(Y)$ and $f^*\cs{L} \iso (\EE)_X$ then $\cs{L} \iso (\EE)_Y$.
-\end{lemma}
-
-\begin{proof}
-The group homomorphism $\pi_1(f): \pi_1(X, {\bar x}) \to \pi_1(Y, {\bar y})$ is surjective, for all geometric points with $f({\bar x}) = {\bar y}$ ... 
-%\todo{Under construction}
-\end{proof}
-
-\subsection{Derived subgroup}
-
-Let $G$ be a smooth group scheme.
-Let $j: G\der \hookrightarrow G$ denote the closed subgroup generated by the commutator morphism $c: G\times G \to G$ given by $c(x,y) = xyx^{-1}y^{-1}$; see \cite{SGA3}*{{VI}$_B$, 7.2}.
-
-\[
-\begin{tikzcd}
-{} & G\times G \arrow{d}{c} &&&\\
-1 \arrow{r} & G\der \arrow{r}{j} & G \arrow{r}{q} & G\ab \arrow{r} & 1
-\end{tikzcd}
-\]
-
-\begin{lemma}\label{lem:Lder}
-For every $\cs{L}$ on $G$, $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
-\end{lemma}
-
-\begin{proof}
-By construction, $c : G \times G \to G\der$ is dominant. 
-Note that $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$.
-Thus,
-\begin{align*}
-c^* (\cs{L}\vert_{G\der})
-&=  (j\circ c)^*\cs{L} \\
-&= (m\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
-&= (m \times (\iota\circ m\op))^* m^* \cs{L} \\
-&\iso (m \times (\iota\circ m\op))^* m\op^* \cs{L} \\
-&= (m\op\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
-&= e^* \cs{L}\\
-&= (\EE)_{G\times G}.
-\end{align*}
-Since $c : G \times G \to G\der$ is schematically dense, $c^* (\cs{L}\vert_{G\der}) \iso (\EE)_{G\times G}$ implies $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ by Lemma~\ref{lem:dominant}.
-\end{proof}
 
@@
 
+\subsection{Descent}
+
+We now suppose that $H$ is normal in $G$ and that the fppf-quotient $G \to G'\ceq H\backslash G$ exists.
+Then $q : G \to G'$ is a regular epimorphism with kernel pair $(n,p)$ in the category of schemes.
+In particular, $G \times_{G'} G \iso H\times_S G'$, so $G \to G'$ is a $G$-torsor in the fppf topology.
+
+In this case we may factor the functor $\CCS(G') \to \CCS(G)$  . . . 
+\[
+\begin{tikzcd}
+\CCS(G) &&\arrow{ll}[swap]{q^*} 
+\CCS(G') \arrow{dl}{\text{`comparison'}}\\
+& \arrow{ul}{\text{forget}} \CCS_{H}(G) & 
+\end{tikzcd}
+\]
+
+\begin{lemma}\label{lem:descent}
+If the quotient $q : G \to G'$ is a $G$-torsor in the etale topology, then the comparison functor $\CCS(G') \to \CCS_{H}(G)$ is an equivalence.
+\end{lemma}
+
+\begin{proof}
+By descent theory, the functor $\Loc(G') \to \Loc_H(G)$ induced by $q: G \to G'$ is an equivalence of categories.
+\todo{Need to study the extra structure coming with character sheaves.}
+\end{proof}
+
 \subsection{Abelianization}
@@
 By definition, the abelianization $G\ab$ of $G$ is the fppf-quotient $q : G \to G\ab$ of $G$ by $G\der$. 
-This exists in schemes since  . . . \todo{I hope smoothness does the trick here.}
+This exists in schemes and is a $G\der$-torsor in the etale topology since  .
+.
+.
+\todo{Either true or it becomes a condition on $G$.
+I hope smoothness does the trick.
+I've written to Masoud for help on this.}
 %\todo{Proof needed}
@@
 \begin{proof}
-The quotient $G \to G\ab$ is a $G\der$-torsor in the etale topology, \todo{Either true or it becomes a condition on $G$.
-Again, I hope smoothness does the trick.} so the result follows from Lemma~\ref{lem:descent}.
+The quotient $G \to G\ab$ is a $G\der$-torsor in the etale topology,  so the result follows from Lemma~\ref{lem:descent}.
 \end{proof}
 
-\begin{theorem}\label{thm:Gab-descent}
+\begin{theorem}\label{thm:Gab}
  Let $G$ be a smooth group scheme over $\Fq$ 
@@
  \begin{corollary}
-The following is a commuting diagram of isomorphisms:
+The following diagram of isomorphisms commutes.
 \[
@@
 \CCSiso{G} \arrow{r} & G(\Fq)^*\\
-\arrow{u}{q^*} \CCSiso{G\ab} \arrow{r} & \arrow{u} G\ab(\Fq)^* . \\
+\arrow{u}{q^*} \CCSiso{G\ab} \arrow{r} & \arrow{u} G\ab(\Fq)^* 
 \end{tikzcd}
@@
  By Theorem \ref{thm:trfrobiso}, $\CCSiso{G}\to G(\Fq)^*$ and $\CCSiso{G\ab}\to G\ab(\Fq)^*$ are isomorphisms.
-By Theorem~\ref{thm:Gab-descent}, $\CCSiso{G} \iso \CCSiso{G\ab}$.
+By Theorem~\ref{thm:Gab}, $\CCSiso{G} \iso \CCSiso{G\ab}$.
 Since $G\der$ is simply connected, \todo{Proof needed} $G\ab(\Fq) = G(\Fq)/G\der(\Fq)$.
@@
  \end{proof}
+
+\begin{remark} 
+It is not true that the categories $\CS(G\ab)$ and $\CS(G)$ are equivalent, even when $G$ is a connected reductive algebraic group, as we will see in the next subsection.
+\end{remark}
 

### 2015-09-28 followup.tex
Radical restructuring aimed at proving CCS(G) = CCS(Gab)

@@
 
+\tableofcontents
+
 \section*{Introduction}
@@
 
-\section{Definitions and Recollections}
+\section{Main Definition and Result}
 
@@
 
-Write $m : G \times G \to G$ for the multiplication morphism.
-Let $\theta : G\times G \to G\times G$ be given by $\theta(g,h) = (h,g)$
+\subsection{Main definition}
+
+Let $\theta : G\times G \to G\times G$ be given by $\theta(g,h) = (h,g)$.
+Write $m : G \times G \to G$ for the multiplication morphism
 and define $m\op : G \times G \to G$ by $m\op = m \circ \theta$.
@@
 \begin{definition}\label{def:CCS}
-A rank-$1$ character sheaf on $G$ is \emph{commutative} if there is an isomorphism ${\bar m}^* \gcs{L} \to {\bar m}\op^* \gcs{L}$
-such that the following diagram commutes,
+A rank-$1$ character sheaf on $G$ is a\emph{commutative character sheaf} if there is an isomorphism ${\bar m}^* \gcs{L} \to {\bar m}\op^* \gcs{L}$ such that the following diagram commutes,
   \[
@@
    \bm^*\gcs{L} \arrow{d} \arrow{r}{\mu} & \LxL \arrow{d}{\vartheta}\\
-   \bm\op^*\gcs{L} \arrow{r}{{\bar \theta}^*\mu} &  {\bar \theta}^*(\LxL)
+   \bm\op^*\gcs{L} \arrow{r}{{\bar \theta}^*\mu} &  {\bar \theta}^*(\LxL).
   \end{tikzcd}
@@
 \begin{lemma}
-If the isomorphism ${\bar m}^* \gcs{L} \to {\bar m}\op^* \gcs{L}$ exists, then it is unique.
+If the isomorphism ${\bar m}^* \gcs{L} \to {\bar m}\op^* \gcs{L}$ exists and satisfies the condition of Definition~\ref{def:CCS}, then it is unique.
 \end{lemma}
@@
 
-\begin{proposition}
-Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$.
+\subsection{Commutative group schemes}
+
+\begin{lemma}\label{lem:commutative}
+If $G$ is commutative then the categories $\CCS(G)$ and $\CS(G)$ are equivalent.
+\todo{I'm confused. There are extra isomorphisms in the former category, but I think they're equivalent for indirect reasons.}
+\end{lemma}
+
+\subsection{Abelianization}
+
+Let $G$ be a smooth group scheme.
+Let $G\der \hookrightarrow G$ denote the closed subgroup generated by the smooth morphism $G\times G \to G$ given by $(x,y)\mapsto xyx^{-1}y^{-1}$.
+Then $G \times G \to G\der$ is a dominant morphism; see \cite{SGA3}*{{VI}$_B$, 7.2}.
+\[
+\begin{tikzcd}
+{} & G\times G \arrow{d}{} &&&\\
+1 \arrow{r} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
+\end{tikzcd}
+\]
+Then $G$ is commutative if and only if $G\der$ is
+
+While the subgroup $G\der$ is smooth, it need not be connected.
+The restriction of $G\times G\to G\der$ to identity components gives a dominant morphism $G^0\times G^0 \to G^0\der$ by [SGA6B, Ex.
+7, Prop 7.8]
+
+Let $q: G \to G\ab$ be the fppf-quotient  . . . 
+We suppose $G\ab$ exists in group schemes over $\Fq$. \todo{This is a condition on $G$. Does it follow from smoothness? I've written to Masoud for help on this.}
+If $G$ is of finite type (and so, an algebraic group) then $G\ab$ exists in group schemes by \cite{GM}*{Thm 4.39}: $G$ smooth implies $G$ flat; $G\der$ is also smooth (!) so also flat; $\dim \Spec{\Fq} \leq 1$.
+
+ \subsection{Statement of the main result}
+
+As in [CS], every morphism of group schemes $G \to G'$ induces . .
+
+Another hypothesis: suppose the smooth morphism $G\times G\to G\der$ is of relative dimension on each connected component of $G\der$.
+
+\begin{theorem}\label{thm:Gab}
+Pull-back along the abelianization $q : G \to G\ab$
+\[
+q^* : \CCS(G\ab) \to \CCS(G)
+\]
+is an equivalence of categories.
+\end{theorem}
+
+Theorem~\ref{thm:Gab} will be proved by factoring $\CCS(G\ab) \to \CCS(G\ab)$ according to the following diagram, which will be explained below, 
+and by showing that each functor is an equivalence.
+\[
+\begin{tikzcd}
+ \CCS(G)  &&& \arrow{lll}[swap]{q^*}  \CCS(G\ab) \arrow{d}{\text{Equivariance}} \\
+\CS_G(G)  \arrow{u}{\text{Equivariance}} &&& \CS_{G\ab}(G\ab) \arrow{d}{\text{Commutative group}}  \\
+\CS_{G\der}(G) \arrow{u}{\text{Change of Action}} &&& \arrow{lll}{\text{Descent along torsor}}  \CS(G\ab)  \\
+\end{tikzcd}
+\]
+
+\begin{remark}
+Theorem~\ref{thm:Gab} provides an indication that $\CCS(G)$ is the correct category in which to geometrize characters of $G(\Fq)$. 
+By contrast, $\CS(G)$ and $\CS(G\ab)$ are generally not isomorphic categories, not even when $G$ is a connected reductive algebraic group and $\Hh^1(\Fq,G\der)=0$, as we will see in Section~\ref{sec:stacky}.
+\end{remark}
+
+\subsection{Equivariance}
+
+We wish to consider the category $\CS_G(G)$ of $G$-equivariant linear character sheaves on $G$. To that end, in this section we introduce that notion in its general context.
+
+Let $G$ and $H$ be group schemes; let $n : H \times G\to G$ be a group action and write $p : H\times G \to G$ for projection. 
+An $H$-equivariant linear character sheaf on $G$ is a linear character sheaf $\cs{L} = (\gcs{L},\phi,\mu)$ on $G$ together with an isomorphism  $\nu : {\bar n}^*\gcs{L} \to {\bar p}^*\gcs{L}$ such that the following diagrams commute, expressing compatibility with $\phi$ and $\mu$:
+\begin{enumerate}
+\item
+\[
+\begin{tikzcd}
+\ &  n_0^*  n^*\, \mathcal{L} \arrow{r}{n_0^*\nu} & n_0^* p^*\, \mathcal{L} & \\
+n_1^* n^*\, \mathcal{L} \arrow{dr}[swap]{n_1^*\nu} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{p_2^*\nu} p_2^* n^*\, \mathcal{L} \\
+& n_1^* p^*\, \mathcal{L} \arrow[equal]{r} & p_2^* p^*\, \mathcal{L} & 
+\end{tikzcd}
+\]
+where $n_0(a,b,x) = (a,n(b,x))$ and $n_1(a,b,x) = (n(ab),x)$ and $p_2(a,b,x) = (b,x)$;
+\item
+\end{enumerate}
+Write $\CCS_H(G)$ for the category of $H$-equivariant commutative character sheaves on $G$.
+
+\begin{lemma}\label{lem:equivariant}
+$\CCS(G)$ and $\CS_G(G)$ are equivalent.
+\end{lemma}
+%\begin{proposition}
+%Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$.
 Conversely, if a rank-$1$ character sheaf on $G$ is equivariant for conjugation, then it is commutative.
-\end{proposition}
+%\end{proposition}
 
@@
 
-\subsection{Dominant morphisms and local systems}
+\begin{remark}
+Lemma~\ref{lem:equivariant} shows that the `canonical functor' $\CCS(G) \to \CS(G)$ is a forgetful functor and also provides an alternate characterization of commutative character sheaves as linear (rank-$1$), multiplicative ($\mu$) and conjugation-equivariant ($\nu$) Weil local systems ($\phi$) on $\bG$.
+\end{remark}
 
-\begin{lemma}\label{lem:dominant}
-Suppose $f: X \to Y$ is dominant.
-If $\cs{L}\in \Loc(Y)$ and $f^*\cs{L} \iso (\EE)_X$ then $\cs{L} \iso (\EE)_Y$.
+\subsection{Descent}
+
+Let $G$ be a $k$-group scheme and let $H \to G$ be a closed subgroup scheme over $S$.
+
+Write $n : H \times_S G \to G$ for the left action of $H$ on $G$; let $p : H\times_S G \to G$ be projection.
+
+We now suppose that $H$ is normal in $G$ and that the fppf-quotient $G \to G'\ceq H\backslash G$ exists in group schemes over $\Fq$.
+Then $q : G \to G'$ is a regular epimorphism with kernel pair $(n,p)$ in the category of schemes.
+\[
+\begin{tikzcd}
+H\times G
+ \arrow{r}[shift left]{n}
+  \arrow{r}[shift right,swap]{p}
+&
+G 
+\arrow{r}{q}
+& 
+G'
+\end{tikzcd}
+\]
+%In particular, $G \times_{G'} G \iso H\times_S G'$, so $G \to G'$ is a $G$-torsor in the fppf topology.
+In this case we may factor the functor $\CCS(G') \to \CCS(G)$  . . . 
+\[
+\begin{tikzcd}
+\CCS(G) &&\arrow{ll}[swap]{q^*} 
+\CCS(G') \arrow{dl}{\text{`comparison'}}\\
+& \arrow{ul}{\text{forget}} \CCS_{H}(G) & 
+\end{tikzcd}
+\]
+
+\begin{lemma}\label{lem:descent}
+The comparison functor $\CCS(G') \to \CCS_{H}(G)$ is an equivalence.
 \end{lemma}
@@
 \begin{proof}
-The group homomorphism $\pi_1(f): \pi_1(X, {\bar x}) \to \pi_1(Y, {\bar y})$ is surjective, for all geometric points with $f({\bar x}) = {\bar y}$ ... 
-\todo{Under construction}
+By descent theory, the functor $\Loc(G') \to \Loc_H(G)$ induced by $q: G \to G'$ is an equivalence of categories. Expand . . . 
+\todo{Need to study the extra structure coming with character sheaves.}
+
+%Let $j : C \hookrightarrow G$ be the kernel of $q : G \to G\ab$ and let $m : G\times G \to G$ be multiplication for $G$. 
+Let $n : G\der \times G \to G$ be the restriction of $m: G\times G \to G$.
+Then $n = m \circ (j \times \id)$, so
+\begin{align*}
+n^* \cs{L} 
+&= (m \circ (j \times \id))^* \cs{L}\\
+&= (j \times \id))^* m^*\cs{L}\\
+&\iso (j \times \id))^* (\cs{L} \boxtimes \cs{L})\\
+&= (j^*\cs{L}) \boxtimes \cs{L}\\
+&= (\cs{L}\vert_C) \boxtimes \cs{L}\\
+&= (\EE)_C \boxtimes \cs{L}\\
+&= p^* \cs{L}.
+\end{align*}
+Thus, every commutative character sheaf $\cs{L}$ on $G$ is $G\der$-equivariant.
+It now follows from Lemma~\ref{lem:Lder} that the forgetful functor $\CCS_{G\der}(G) \to \CCS(G)$ is an equivalence. 
 \end{proof}
 
-\subsection{Derived subgroup}
-
-Let $G$ be a smooth group scheme.
-Let $j: G\der \hookrightarrow G$ denote the closed subgroup generated by the commutator morphism $c: G\times G \to G$ given by $c(x,y) = xyx^{-1}y^{-1}$; see \cite{SGA3}*{{VI}$_B$, 7.2}.
+\subsection{Change of action}
 
@@
 \begin{tikzcd}
-{} & G\times G \arrow{d}{c} &&&\\
-1 \arrow{r} & G\der \arrow{r}{j} & G \arrow{r}{q} & G\ab \arrow{r} & 1
+\arrow{dd}[swap]{f} G_1 \times G \arrow{dr}[swap]{a_1}{p} & \\
+& G \\
+G_2 \times G \arrow{ur}{a_2}[swap]{p} & 
 \end{tikzcd}
 \]
+
+\begin{lemma}\label{lem:action}
+The canonical functor
+\[
+\CS_{G_2}(G) \to \CS_{G_1}(G)
+\]
+is an equivalence if $f$ is smooth of relative dimension on connected components.
+\end{lemma}
+\begin{proof}
+\end{proof}
+
+\subsection{Proof of the main result}
+
+\begin{proof}[Proof of Theorem~\ref{thm:Gab}]
+First we must see that $q^*$ factors according to . . . 
+\[
+\begin{tikzcd}
+ \CCS(G)  &&& \arrow{lll}[swap]{q^*}  \CCS(G\ab) \arrow{d}{\text{Lem~\ref{lem:equivariant}}} \\
+\CS_G(G)  \arrow{u}{\text{Lem~\ref{lem:equivariant}}} &&& \CS_{G\ab}(G\ab) \arrow{d}{\text{Lem~\ref{lem:commutative}}}  \\
+\CS_{G\der}(G) \arrow{u}{\text{Lem~\ref{lem:action}}} &&& \arrow{lll}{\text{Lem~\ref{lem:descent}}}  \CS(G\ab)  \\
+\end{tikzcd}
+\]
+\end{proof}
 
@@
 
-\begin{remark}
-Lemma~\ref{lem:Lder} provides another indication of the correctness of Definition~\ref{def:CCS} 
-if one is looking for the geometrization of characters of smooth group schemes over finite fields: commutative character sheaves are trivial on $G\der$, rank-$1$ character sheaves are not.
-In the next section we provide examples to show that $\CCS(G)$ and $\CS(G)$ are not isomorphic categories, even when $G$ is a connected reductive algebraic group. 
-\end{remark}
+\section{Geometrization of linear characters}
+
+ \begin{corollary}
+ If $\Hh^1(\Fq,G\der)=0$ then
+the following diagram of isomorphisms commutes.
+\[
+\begin{tikzcd}
+\CCSiso{G} \arrow{r} & G(\Fq)^*\\
+\arrow{u}{q^*} \CCSiso{G\ab} \arrow{r} & \arrow{u} G\ab(\Fq)^* 
+\end{tikzcd}
+\]
+ \end{corollary}
+
+ \begin{proof}
+ By Theorem \ref{thm:trfrobiso}, $\CCSiso{G}\to G(\Fq)^*$ and $\CCSiso{G\ab}\to G\ab(\Fq)^*$ are isomorphisms.
+By Theorem~\ref{thm:Gab}, $\CCSiso{G} \iso \CCSiso{G\ab}$.
+Since $\Hh^1(\Fq,G\der)=0$, we have  $G\ab(\Fq) = G(\Fq)/G\der(\Fq)$.
+Thus, all characters of $G(\Fq)$ factor through
+ $G\ab(\Fq)$. . . . 
+ The isomorphisms are compatible because  . . . 
+ \end{proof}
 
@@
 
-\section{Descent for commutative character sheaves}
-
-\subsection{Quotients}
-
-Let $G$ be a $k$-group scheme and let $H \to G$ be a closed subgroup scheme over $S$.
-
-Write $n : H \times_S G \to G$ for the left action of $H$ on $G$; let $p : H\times_S G \to G$ be projection.
-
-\subsection{$H$-equivariance}
-
-An $H$-equivariant rank-$1$ character sheaf on $G$ is a rank-$1$ character sheaf $\cs{L} = (\gcs{L},\phi,\mu)$ on $G$ together with an isomorphism  $\nu : {\bar m}_H^*\gcs{L} \to {\bar p}_H^*\gcs{L}$ such that the following diagrams commute, expressing compatibility with $\phi$ and $\mu$:
-\begin{enumerate}
-\item
-\[
-\begin{tikzcd}
-\ &  m_0^*  m^*\, \mathcal{L} \arrow{r}{m_0^*\nu} & m_0^* p^*\, \mathcal{L} & \\
-m_1^* m^*\, \mathcal{L} \arrow{dr}[swap]{m_1^*\nu} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{p_2^*\nu} p_2^* m^*\, \mathcal{L} \\
-& m_1^* p^*\, \mathcal{L} \arrow[equal]{r} & p_2^* p^*\, \mathcal{L} & 
-\end{tikzcd}
-\]
-where $m_0(a,b,x) = (a,m(b,x))$ and $m_1(a,b,x) = (m(ab),x)$ and $p_2(a,b,x) = (b,x)$;
-\item
-\end{enumerate}
-Write $\CCS_H(G)$ for the category of $H$-equivariant commutative character sheaves on $G$.
-
-\begin{proposition}\label{prop:Gder-equivariance}
-$\CCS_{G\der}(G) \to \CCS(G)$ is an equivalence.
-\end{proposition}
-
-\begin{proof}
-%Let $j : C \hookrightarrow G$ be the kernel of $q : G \to G\ab$ and let $m : G\times G \to G$ be multiplication for $G$. 
-Let $n : G\der \times G \to G$ be the restriction of $m: G\times G \to G$.
-Then $n = m \circ (j \times \id)$, so
-\begin{align*}
-n^* \cs{L} 
-&= (m \circ (j \times \id))^* \cs{L}\\
-&= (j \times \id))^* m^*\cs{L}\\
-&\iso (j \times \id))^* (\cs{L} \boxtimes \cs{L})\\
-&= (j^*\cs{L}) \boxtimes \cs{L}\\
-&= (\cs{L}\vert_C) \boxtimes \cs{L}\\
-&= (\EE)_C \boxtimes \cs{L}\\
-&= p^* \cs{L}.
-\end{align*}
-Thus, every commutative character sheaf $\cs{L}$ on $G$ is $G\der$-equivariant.
-It now follows from Lemma~\ref{lem:Lder} that the forgetful functor $\CCS_{G\der}(G) \to \CCS(G)$ is an equivalence. 
-\end{proof}
-
-\subsection{Descent}
-
-We now suppose that $H$ is normal in $G$ and that the fppf-quotient $G \to G'\ceq H\backslash G$ exists.
-Then $q : G \to G'$ is a regular epimorphism with kernel pair $(n,p)$ in the category of schemes.
-In particular, $G \times_{G'} G \iso H\times_S G'$, so $G \to G'$ is a $G$-torsor in the fppf topology.
-
-In this case we may factor the functor $\CCS(G') \to \CCS(G)$  . . . 
-\[
-\begin{tikzcd}
-\CCS(G) &&\arrow{ll}[swap]{q^*} 
-\CCS(G') \arrow{dl}{\text{`comparison'}}\\
-& \arrow{ul}{\text{forget}} \CCS_{H}(G) & 
-\end{tikzcd}
-\]
-
-\begin{lemma}\label{lem:descent}
-If the quotient $q : G \to G'$ is a $G$-torsor in the etale topology, then the comparison functor $\CCS(G') \to \CCS_{H}(G)$ is an equivalence.
-\end{lemma}
-
-\begin{proof}
-By descent theory, the functor $\Loc(G') \to \Loc_H(G)$ induced by $q: G \to G'$ is an equivalence of categories.
-\todo{Need to study the extra structure coming with character sheaves.}
-\end{proof}
-
-\subsection{Abelianization}
-
-By definition, the abelianization $G\ab$ of $G$ is the fppf-quotient $q : G \to G\ab$ of $G$ by $G\der$. 
-This exists in schemes and is a $G\der$-torsor in the etale topology since  .
-.
-.
-\todo{Either true or it becomes a condition on $G$.
-I hope smoothness does the trick.
-I've written to Masoud for help on this.}
-%\todo{Proof needed}
-%  is the coequalizer of $n : G\der \times G \to G$ with projection $p: G\der \times G \to G$. 
-\[
-\begin{tikzcd}
-G\der\times G
- \arrow{r}[shift left]{n}
-  \arrow{r}[shift right,swap]{p}
-&
-G 
-\arrow{r}{q}
-& 
-G\ab
-\end{tikzcd}
-\]
-
-\begin{proposition}\label{prop:Gab-descent}
-Let $G$ be a smooth group scheme over $\Fq$ 
- and let $q : G \to G\ab$ be its abelianization. 
- Then  
-\[
-\CCS(G\ab) \longrightarrow \CCS_{G\der}(G)
-\]
-is an equivalence of categories.
-\end{proposition}
-
-\begin{proof}
-The quotient $G \to G\ab$ is a $G\der$-torsor in the etale topology,  so the result follows from Lemma~\ref{lem:descent}.
-\end{proof}
-
-\begin{theorem}\label{thm:Gab}
- Let $G$ be a smooth group scheme over $\Fq$ 
- and let $q : G \to G\ab$ be its abelianization. 
- Then  
-\[
-q^*:  \CCS(G\ab) \longrightarrow \CCS(G)
-\]
-is an equivalence of rigid monoidal categories.
-\end{theorem}
-\begin{proof}
-Combine Propositions~\ref{prop:Gder-equivariance} and \ref{prop:Gab-descent}.
-\end{proof}
-
- \begin{corollary}
-The following diagram of isomorphisms commutes.
-\[
-\begin{tikzcd}
-\CCSiso{G} \arrow{r} & G(\Fq)^*\\
-\arrow{u}{q^*} \CCSiso{G\ab} \arrow{r} & \arrow{u} G\ab(\Fq)^* 
-\end{tikzcd}
-\]
- \end{corollary}
-
- \begin{proof}
- By Theorem \ref{thm:trfrobiso}, $\CCSiso{G}\to G(\Fq)^*$ and $\CCSiso{G\ab}\to G\ab(\Fq)^*$ are isomorphisms.
-By Theorem~\ref{thm:Gab}, $\CCSiso{G} \iso \CCSiso{G\ab}$.
-Since $G\der$ is simply connected, \todo{Proof needed} $G\ab(\Fq) = G(\Fq)/G\der(\Fq)$.
-Thus, all characters of $G(\Fq)$ factor through
- $G\ab(\Fq)$. . . . 
- The isomorphisms are compatible because  . . . 
- \end{proof}
-
-\begin{remark} 
-It is not true that the categories $\CS(G\ab)$ and $\CS(G)$ are equivalent, even when $G$ is a connected reductive algebraic group, as we will see in the next subsection.
-\end{remark}
-
-\subsection{Stacky abelianization, revisited}
+\section{Stacky abelianization, revisited}\label{sec:stacky}
 

### 2015-09-28 followup.tex
More surgery. Removed intermediate use of CS(G).

@@
 
-\section{Main Definition and Result}
+\section{Recollections and definitions}
 
@@
 
-\subsection{Commutative group schemes}
+\section{Eliminating Invisible Character Sheaves}\label{sec:defect}
 
-\begin{lemma}\label{lem:commutative}
-If $G$ is commutative then the categories $\CCS(G)$ and $\CS(G)$ are equivalent.
-\todo{I'm confused. There are extra isomorphisms in the former category, but I think they're equivalent for indirect reasons.}
+If $M$ is a $\bG$-module, then we say a cohomology class in $\Hh^2(\bG, M)$ is \emph{symmetric} if it is represented
+by a symmetric $2$-cocycle.  Since every coboundary is symmetric, either all cocycles in a given class will be symmetric
+or none will.
+
+\begin{lemma} \label{lem:symtriv}
+Let $\bG$ be a commutative group.  Then the only symmetric class in $\Hh^2(\bG, \EEx)$ is the trivial class.
 \end{lemma}
 
-\subsection{Abelianization}
+\begin{proof}
+By the universal coefficient theorem,
+\[
+0 \to \Ext^1_\ZZ(\Hh_{n-1}(\bG, \ZZ), \EEx) \to \Hh^n(\bG, \EEx) \to \Hom(\Hh_n(\bG, \ZZ), \EEx) \to 0
+\]
+for all $n > 0$.  When $n = 2$, using the fact that $\bG$ is commutative, we have that $\Hh_1(\bG, \ZZ) \cong \bG$
+and that $\Hh_2(\bG, \ZZ) \cong \wedge^2 \bG$. We get
+\[
+0 \to \Ext^1_\ZZ(\bG, \EEx) \to \Hh^2(\bG, \EEx) \to \Hom(\wedge^2 \bG, \EEx) \to 0.
+\]
+The map $\Hh^2(\bG, \EEx) \to \Hom(\wedge^2 \bG, \EEx)$ maps a $2$-cocycle $f$ to the alternating function
+\[
+(x,y) \mapsto \frac{f(x,y)}{f(y,x)}.
+\]
+Thus the cohomology classes represented by symmetric cocycles are precisely those in the image of $\Ext^1_\ZZ(\bG, \EEx)$.
+But $\Ext^1_\ZZ(-, \EEx)$ vanishes because $\EEx$ is divisible.
+\end{proof}
+
+For a character sheaf $\cs{L}$ on $G$, recall from \cite{cunningham-roe:13a}*{\S 2.3} that $S_G : \CSiso{G} \to \Hh^2(E_G^\bullet)$ maps
+$[\cs{L}]$ to $[\alpha \oplus \beta]$, where $E_G^\bullet$ is the total space of the zeroth page
+of the Hochschild-Serre spectral sequence, $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$ is obtained from $\mu$ and
+$\beta \in C^1(\Weil{}, C^1(\bG, \EEx))$ is obtained from $\phi$.
+
+\begin{lemma} \label{lem:conncomm}
+If $G$ is a connected commutative algebraic group over $\Fq$ then every character sheaf on $G$ is commutative.
+\end{lemma}
+
+\begin{proof}
+We can use \'etale descent to see that pullback by the Lang isogeny defines an equivalence
+of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.  Thus every character
+sheaf on $G$ arises through the Lang isogeny; since the covering group is $G$ itself, which is commutative,
+every character sheaf on $G$ is commutative.
+\end{proof}
+
+\begin{theorem} \label{thm:trfrobiso}
+If $G$ is a smooth commutative group scheme over $\Fq$ then $\TrFrob{G} : \CCSiso{G} \to G(\Fq)^*$ is an isomorphism.
+\end{theorem}
+
+\begin{proof}
+Suppose first that $G$ is \'etale.  Consider the isomorphism of short exact sequences
+\[
+\begin{tikzcd}
+ 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \CSiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
+  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\bG,\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1(\bG,\EEx)) \arrow{r} & 0
+ \end{tikzcd}
+ \]
+from \cite{cunningham-roe:13a}*{Prop. 2.7}.
+
+Suppose that $\cs{L}$ is a commutative character sheaf
+with $\trFrob{\cs{L}} = 1$.  Then $S_G([\cs{L}])$ is in the image of $\Hh^2(\bG, \EEx)^\Weil{}$, so is cohomologous to
+$[\alpha', 0]$.  Since $\alpha$ is symmetric and coboundaries are symmetric, $\alpha'$ is symmetric as well.
+So by Lemma \ref{lem:symtriv}, $\alpha'$ is cohomologically trivial, and thus $[\cs{L}]$ is trivial as well.
+
+To see that $\TrFrob{G}$ is still surjective on $\CCSiso{G}$, note that the character sheaf constructed in the proof of
+\cite{cunningham-roe:13a}*{Prop. 2.6} has trivial $\alpha$, and is thus commutative.
+
+For general smooth commutative group schemes, we use Lemma \ref{lem:conncomm} and the snake lemma.
+\end{proof}
+
+\begin{remark}
+Since $\Hh^0(\Weil{},\Hh^2(\bG,\EEx))$ is not necessarily trivial \cite{cunningham-roe:13a}*{Ex. 2.10}, the functor
+$\CCS(G) \to \CS(G)$ is not an equivalence of categories in general.
+\end{remark}
+
+\section{Descent to the Abelianization}
+
+\subsection{Derived subgroup}
 
@@
 7, Prop 7.8]
+
+\subsection{Abelianization}
 
@@
 \begin{tikzcd}
- \CCS(G)  &&& \arrow{lll}[swap]{q^*}  \CCS(G\ab) \arrow{d}{\text{Equivariance}} \\
-\CS_G(G)  \arrow{u}{\text{Equivariance}} &&& \CS_{G\ab}(G\ab) \arrow{d}{\text{Commutative group}}  \\
-\CS_{G\der}(G) \arrow{u}{\text{Change of Action}} &&& \arrow{lll}{\text{Descent along torsor}}  \CS(G\ab)  \\
+ \CCS(G)  &&& \arrow{lll}[swap]{q^*}  \CCS(G\ab) \arrow{d}{\text{Descent along torsor}} \\
+\CCS_G(G)  \arrow{u}{\text{Equivariance}} &&& \arrow{lll}{\text{Change of Action}} \CCS_{G\der}(G) 
 \end{tikzcd}
@@
 
-We wish to consider the category $\CS_G(G)$ of $G$-equivariant linear character sheaves on $G$. To that end, in this section we introduce that notion in its general context.
+We wish to consider the categories $\CCS_G(G)$ (resp $\CS_G(G)$) of $G$-equivariant commutative character sheaves (linear character sheaves) on $G$.
+To that end, in this section we introduce that notion in its general context.
 
@@
 \begin{lemma}\label{lem:equivariant}
-$\CCS(G)$ and $\CS_G(G)$ are equivalent.
+$\CCS(G)$ and $\CCS_G(G)$ are equivalent.
 \end{lemma}
@@
 
-\subsection{Descent}
+\subsection{Descent along torsors}
 
@@
 \begin{tikzcd}
- \CCS(G)  &&& \arrow{lll}[swap]{q^*}  \CCS(G\ab) \arrow{d}{\text{Lem~\ref{lem:equivariant}}} \\
-\CS_G(G)  \arrow{u}{\text{Lem~\ref{lem:equivariant}}} &&& \CS_{G\ab}(G\ab) \arrow{d}{\text{Lem~\ref{lem:commutative}}}  \\
-\CS_{G\der}(G) \arrow{u}{\text{Lem~\ref{lem:action}}} &&& \arrow{lll}{\text{Lem~\ref{lem:descent}}}  \CS(G\ab)  \\
+ \CCS(G)  &&& \arrow{lll}[swap]{q^*}  \CCS(G\ab) \arrow{d}{\text{Lem~\ref{lem:descent}}} \\
+\CCS_G(G)  \arrow{u}{\text{Lem~\ref{lem:equivariant}}} &&& \arrow{lll}{\text{Lem~\ref{lem:action}}} \CCS_{G\der}(G) 
 \end{tikzcd}
@@
  \end{proof}
-
-\section{Eliminating Invisible Character Sheaves}\label{sec:defect}
-
-If $M$ is a $\bG$-module, then we say a cohomology class in $\Hh^2(\bG, M)$ is \emph{symmetric} if it is represented
-by a symmetric $2$-cocycle.  Since every coboundary is symmetric, either all cocycles in a given class will be symmetric
-or none will.
-
-\begin{lemma} \label{lem:symtriv}
-Let $\bG$ be a commutative group.  Then the only symmetric class in $\Hh^2(\bG, \EEx)$ is the trivial class.
-\end{lemma}
-
-\begin{proof}
-By the universal coefficient theorem,
-\[
-0 \to \Ext^1_\ZZ(\Hh_{n-1}(\bG, \ZZ), \EEx) \to \Hh^n(\bG, \EEx) \to \Hom(\Hh_n(\bG, \ZZ), \EEx) \to 0
-\]
-for all $n > 0$.  When $n = 2$, using the fact that $\bG$ is commutative, we have that $\Hh_1(\bG, \ZZ) \cong \bG$
-and that $\Hh_2(\bG, \ZZ) \cong \wedge^2 \bG$. We get
-\[
-0 \to \Ext^1_\ZZ(\bG, \EEx) \to \Hh^2(\bG, \EEx) \to \Hom(\wedge^2 \bG, \EEx) \to 0.
-\]
-The map $\Hh^2(\bG, \EEx) \to \Hom(\wedge^2 \bG, \EEx)$ maps a $2$-cocycle $f$ to the alternating function
-\[
-(x,y) \mapsto \frac{f(x,y)}{f(y,x)}.
-\]
-Thus the cohomology classes represented by symmetric cocycles are precisely those in the image of $\Ext^1_\ZZ(\bG, \EEx)$.
-But $\Ext^1_\ZZ(-, \EEx)$ vanishes because $\EEx$ is divisible.
-\end{proof}
-
-For a character sheaf $\cs{L}$ on $G$, recall from \cite{cunningham-roe:13a}*{\S 2.3} that $S_G : \CSiso{G} \to \Hh^2(E_G^\bullet)$ maps
-$[\cs{L}]$ to $[\alpha \oplus \beta]$, where $E_G^\bullet$ is the total space of the zeroth page
-of the Hochschild-Serre spectral sequence, $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$ is obtained from $\mu$ and
-$\beta \in C^1(\Weil{}, C^1(\bG, \EEx))$ is obtained from $\phi$.
-
-\begin{lemma} \label{lem:conncomm}
-If $G$ is a connected commutative algebraic group over $\Fq$ then every character sheaf on $G$ is commutative.
-\end{lemma}
-
-\begin{proof}
-We can use \'etale descent to see that pullback by the Lang isogeny defines an equivalence
-of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.  Thus every character
-sheaf on $G$ arises through the Lang isogeny; since the covering group is $G$ itself, which is commutative,
-every character sheaf on $G$ is commutative.
-\end{proof}
-
-\begin{theorem} \label{thm:trfrobiso}
-If $G$ is a smooth commutative group scheme over $\Fq$ then $\TrFrob{G} : \CCSiso{G} \to G(\Fq)^*$ is an isomorphism.
-\end{theorem}
-
-\begin{proof}
-Suppose first that $G$ is \'etale.  Consider the isomorphism of short exact sequences
-\[
-\begin{tikzcd}
- 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \CSiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
-  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\bG,\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1(\bG,\EEx)) \arrow{r} & 0
- \end{tikzcd}
- \]
-from \cite{cunningham-roe:13a}*{Prop. 2.7}.
-
-Suppose that $\cs{L}$ is a commutative character sheaf
-with $\trFrob{\cs{L}} = 1$.  Then $S_G([\cs{L}])$ is in the image of $\Hh^2(\bG, \EEx)^\Weil{}$, so is cohomologous to
-$[\alpha', 0]$.  Since $\alpha$ is symmetric and coboundaries are symmetric, $\alpha'$ is symmetric as well.
-So by Lemma \ref{lem:symtriv}, $\alpha'$ is cohomologically trivial, and thus $[\cs{L}]$ is trivial as well.
-
-To see that $\TrFrob{G}$ is still surjective on $\CCSiso{G}$, note that the character sheaf constructed in the proof of
-\cite{cunningham-roe:13a}*{Prop. 2.6} has trivial $\alpha$, and is thus commutative.
-
-For general smooth commutative group schemes, we use Lemma \ref{lem:conncomm} and the snake lemma.
-\end{proof}
-
-\begin{remark}
-Since $\Hh^0(\Weil{},\Hh^2(\bG,\EEx))$ is not necessarily trivial \cite{cunningham-roe:13a}*{Ex. 2.10}, the functor
-$\CCS(G) \to \CS(G)$ is not an equivalence of categories in general.
-\end{remark}
 

### 2015-09-28 followup.tex
Out of time for today  . .  .

@@
 \begin{theorem}\label{thm:Gab}
-Pull-back along the abelianization $q : G \to G\ab$
+Under these hypotheses, pull-back along the abelianization $q : G \to G\ab$
 \[
@@
 $\CCS(G)$ and $\CCS_G(G)$ are equivalent.
+[Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$; conversely, if a linear character sheaf on $G$ is equivariant for conjugation, then it is commutative?]
 \end{lemma}
-%\begin{proposition}
-%Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$.
-Conversely, if a rank-$1$ character sheaf on $G$ is equivariant for conjugation, then it is commutative.
-%\end{proposition}
 
@@
 Lemma~\ref{lem:equivariant} shows that the `canonical functor' $\CCS(G) \to \CS(G)$ is a forgetful functor and also provides an alternate characterization of commutative character sheaves as linear (rank-$1$), multiplicative ($\mu$) and conjugation-equivariant ($\nu$) Weil local systems ($\phi$) on $\bG$.
+[Is this correct?]
 \end{remark}

### 2015-10-01 followup.tex
Stuck. So I'm putting this down for a bit.

@@
 
+In this paper we use a common formalism for Weil sheaves, writing $\cs{L}$ for the pair $(\gcs{L},\phi)$ and writing $\alpha : \cs{L} \to \cs{L}'$ for a morphism $\alpha : \gcs{L} \to \gcs{L}$ such that
+\[
+\begin{tikzcd}
+\Frob{}^* \gcs{L} \arrow{d}{\phi} \arrow{r}{\Frob{}^*\alpha} &  \Frob{}^* \gcs{L} \arrow{d}{\phi'}\\
+\gcs{L} \arrow{r}{\alpha} & \gcs{L}
+\end{tikzcd}
+\]
+commutes, where $\cs{L}'$ refers to $(\gcs{L}',\phi')$.
+While this simplifies notation considerably, it is, unfortunately, not consistent with our earlier paper.
+
 \subsection{Main definition}
@@
 and define $m\op : G \times G \to G$ by $m\op = m \circ \theta$.
-For any local system $\gcs{L}$ on $\bG \ceq G \times_{\Spec{\Fq}} \Spec{\bFq}$ there is an isomorphism
-$\vartheta : \LxL \to {\bar \theta}^*(\LxL)$ given on stalks by the canonical map
+For any Weil local system $\cs{L}$ on $G$ there is an isomorphism
+$\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ given on stalks by the canonical map
 $\gcs{L}_{g} \otimes \gcs{L}_{h} \to \gcs{L}_{h} \otimes \gcs{L}_{g}$.
 
-When $G$ is commutative, recall \cite{cunningham-roe:13a}*{Def. 1.1} that a character sheaf on $G$ is a triple $\cs{L} \ceq (\gcs{L}, \mu, \phi)$,
-where $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, $\mu : \bm^* \gcs{L} \to \LxL$ is an isomorphism
-of sheaves on $\bG \times \bG$, and $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an isomorphism of sheaves on $\bG$.
-The same definition makes sense for non-commutative $G$.  In order to distinguish the resulting objects from
-the character sheaves of Lusztig, we will refer to them as \emph{rank-$1$ character sheaves} (following \cite{Kamgarpour})
-and write $\CS(G)$ for the resulting category, with morphisms defined as in \cite{cunningham-roe:13a}*{Def. 1.1}.
+When $G$ is commutative, recall \cite{cunningham-roe:13a}*{Def. 1.1} that a character sheaf on $G$ is a triple $(\gcs{L}, \mu, \phi)$,
+where $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, 
+$\mu : \bm^* \gcs{L} \to \LxL$ is an isomorphism
+of sheaves on $\bG \times \bG$, 
+and $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an isomorphism of sheaves on $\bG$;
+the triple $(\gcs{L}, \mu, \phi)$ must also satisfy compatibility conditions specified in \cite{cunningham-roe:13a}*{Def. 1.1}.
+Writing $\cs{L}$ for the Weil local system $(\gcs{L}, \mu, \phi)$, these compatibility conditions are simply this: $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is an isomorphism of Weil local systems.
+The category of character sheaves on $G$ is denoted by $\CS(G)$.
+
+The definition of $\CS(G)$ also makes sense for non-commutative $G$.  
+In order to distinguish the resulting objects from
+the character sheaves of Lusztig, we will refer to the former as \emph{linear character sheaves} (to evoke the one-dimensional character sheaves of \cite{Kamgarpour})
+and again write $\CS(G)$ for the resulting category, with morphisms defined as in \cite{cunningham-roe:13a}*{Def. 1.1}.
 
 \begin{definition}\label{def:CCS}
-A rank-$1$ character sheaf on $G$ is a\emph{commutative character sheaf} if there is an isomorphism ${\bar m}^* \gcs{L} \to {\bar m}\op^* \gcs{L}$ such that the following diagram commutes,
+A linear character sheaf on $G$ is a \emph{commutative character sheaf} if there is an isomorphism $m^* \cs{L} \to m\op^* \cs{L}$ of local systems on $G\times G$ such that the following diagram commutes.
   \[
   \begin{tikzcd}[row sep=30]
-   \bm^*\gcs{L} \arrow{d} \arrow{r}{\mu} & \LxL \arrow{d}{\vartheta}\\
-   \bm\op^*\gcs{L} \arrow{r}{{\bar \theta}^*\mu} &  {\bar \theta}^*(\LxL).
+   m^*\cs{L} \arrow{d} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
+   m\op^*\cs{L} \arrow{r}{{\theta}^*\mu} &  {\bar \theta}^*(\cs{L}\boxtimes\cs{L})
   \end{tikzcd}
   \]
- Write $\CCS(G)$ for the full subcategory of $\CS(G)$ consisting of commutative character sheaves.
+We write $\CCS(G)$ for the full subcategory of $\CS(G)$ consisting of commutative character sheaves.
  \end{definition}
@@
 \begin{lemma}
-If the isomorphism ${\bar m}^* \gcs{L} \to {\bar m}\op^* \gcs{L}$ exists and satisfies the condition of Definition~\ref{def:CCS}, then it is unique.
+If the isomorphism $m^* \cs{L} \to m\op^* \cs{L}$ exists and satisfies the condition of Definition~\ref{def:CCS}, then it is unique.
 \end{lemma}
+
 \begin{proof}
+Why is this true?
 \end{proof}
@@
 Let $G\der \hookrightarrow G$ denote the closed subgroup generated by the smooth morphism $G\times G \to G$ given by $(x,y)\mapsto xyx^{-1}y^{-1}$.
-Then $G \times G \to G\der$ is a dominant morphism; see \cite{SGA3}*{{VI}$_B$, 7.2}.
-\[
-\begin{tikzcd}
-{} & G\times G \arrow{d}{} &&&\\
-1 \arrow{r} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
-\end{tikzcd}
-\]
-Then $G$ is commutative if and only if $G\der$ is
+Then $G \times G \to G\der$ is a dominant morphism \cite{SGA3}*{{VI}$_B$, 7.2}
+and $G$ is commutative if and only if $G\der$ is trivial.
 
 While the subgroup $G\der$ is smooth, it need not be connected.
-The restriction of $G\times G\to G\der$ to identity components gives a dominant morphism $G^0\times G^0 \to G^0\der$ by [SGA6B, Ex.
-7, Prop 7.8]
+The restriction of $G\times G\to G\der$ to identity components gives a dominant morphism $G^0\times G^0 \to G^0\der$ by [SGA3, Tome 6B, Expos\'e 7, Prop 7.8]
 
@@
 
+\[
+\begin{tikzcd}
+{} & G\times G \arrow{d}{} &&&\\
+1 \arrow{r} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
+\end{tikzcd}
+\]
+
  \subsection{Statement of the main result}
@@
 
-Another hypothesis: suppose the smooth morphism $G\times G\to G\der$ is of relative dimension on each connected component of $G\der$.
+Another hypothesis: suppose the smooth morphism $G\times G\to G\der$ is of relative dimension on each connected component of its image in $G\der$.\todo{This is another condition on $G$.
+Does it come from smoothness of $G$?}
 
@@
 Let $G$ and $H$ be group schemes; let $n : H \times G\to G$ be a group action and write $p : H\times G \to G$ for projection. 
-An $H$-equivariant linear character sheaf on $G$ is a linear character sheaf $\cs{L} = (\gcs{L},\phi,\mu)$ on $G$ together with an isomorphism  $\nu : {\bar n}^*\gcs{L} \to {\bar p}^*\gcs{L}$ such that the following diagrams commute, expressing compatibility with $\phi$ and $\mu$:
-\begin{enumerate}
-\item
+An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  $\nu : n^*\cs{L} \to p^*\cs{L}$ of Weil local systems on $G\times G$ such that the following diagram commutes,
 \[
@@
 n_1^* n^*\, \mathcal{L} \arrow{dr}[swap]{n_1^*\nu} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{p_2^*\nu} p_2^* n^*\, \mathcal{L} \\
-& n_1^* p^*\, \mathcal{L} \arrow[equal]{r} & p_2^* p^*\, \mathcal{L} & 
+& n_1^* p^*\, \mathcal{L} \arrow[equal]{r} & p_2^* p^*\, \mathcal{L}, & 
 \end{tikzcd}
 \]
-where $n_0(a,b,x) = (a,n(b,x))$ and $n_1(a,b,x) = (n(ab),x)$ and $p_2(a,b,x) = (b,x)$;
-\item
-\end{enumerate}
-Write $\CCS_H(G)$ for the category of $H$-equivariant commutative character sheaves on $G$.
+where $n_0(a,b,x) = (a,n(b,x))$ and $n_1(a,b,x) = (n(ab),x)$ and $p_2(a,b,x) = (b,x)$.
+Morphisms of $H$-equivariant Weil local systems are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which . . .
+
+An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ with no condition tying $\mu$ and $\nu$ together.
+Write $\CS_H(G)$ for the category of $H$-equivariant linear character sheaves on $G$.\todo{Under construction}
+
+Finally, an $H$-equivariant commutative character sheaf on $G$ is an $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ for whuch
 
 \begin{lemma}\label{lem:equivariant}
-$\CCS(G)$ and $\CCS_G(G)$ are equivalent.
-[Every commutative character sheaf on $G$ is equivariant for the conjugation action of $G$ on $G$; conversely, if a linear character sheaf on $G$ is equivariant for conjugation, then it is commutative?]
+Categories $\CCS(G)$ and $\CCS_G(G)$ are equivalent.
 \end{lemma}
@@
 \begin{proof}
-Let $a : G \times G \to G$ be the conjugation action of $G$ on $G$.
-Then $a = m \circ (m \times (\iota \circ p_1))$ while $m\op \circ (m \times (\iota \circ p_1)) = p_2$.
-Thus, if $m^*\cs{L} \iso m\op^*\cs{L}$ then
+Let $a : G \times G \to G$ be the conjugation action of $G$ on $G$ and let $p : G \times G \to G$ be projection to the second factor.
+Then $a = m \circ (m \times (\iota \circ p_1))$ while $m\op \circ (m \times (\iota \circ p_1)) = p$;
+likewise, $m = a \circ (p_1\times m\op)$ while $p \circ (p_1\times m\op) = m\op$.
+
+Let $(\cs{L},\mu)$ be a commutative character sheaf on $G$.
+Let $c: m^*\cs{L} \to m\op^*\cs{L}$ be an isomorphism satisfying the condition of Definition~\ref{def:CCS}. Then
 \begin{align*}
@@
 &= (m\op \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
-&= p_2^*\cs{L}.
+&= p^*\cs{L}.
 \end{align*}
-Since the isomorphism $a^*\cs{L} \iso p_2^*\cs{L}$ is unique, $(\cs{L}, a^*\cs{L} \iso p_2^*\cs{L})$ is an equivariant commutative character sheaf.
+The isomorphism above is 
+\[
+(m \times (\iota \circ p_1))^* c: a^*\cs{L} \to p^*\cs{L},
+\]
+ so $(\cs{L}, (m \times (\iota \circ p_1))^* c)$ is a $G$-equivariant commutative character sheaf.
 
-Conversely, let $(\cs{L}, a^*\cs{L} \iso p_2^*\cs{L})$ be an equivariant rank-$1$ character sheaf.
-Observe that $m = a \circ (p_1\times m\op)$ while $p_2 \circ (p_1\times m\op) = m\op$. Thus, 
+Let $(\cs{L}, \nu)$ be an equivariant linear character sheaf.
+Then
 \begin{align*}
@@
 &= (p_1 \times m\op)^* a^* \cs{L}\\
-&\iso (p_1 \times m\op)^* p_2^* \cs{L}\\
-&= (p_2\circ (p_1 \times m\op))^* \cs{L}\\
+&\iso (p_1 \times m\op)^* p^* \cs{L}\\
+&= (p\circ (p_1 \times m\op))^* \cs{L}\\
 &= m\op^* \cs{L}.
 \end{align*}
-Thus, $\cs{L}$ is a commutative character sheaf.
+The isomorphism above is
+\[
+(p_1 \times m\op)^* \nu : m^* \cs{L}  \to m\op^* \cs{L},
+\]
+so $(\cs{L},\mu)$ is a commutative character sheaf.
+\todo{This proof is under construction.}
 \end{proof}
@@
 \]
-is an equivalence if $f$ is smooth of relative dimension on connected components.
+is an equivalence if $f$ is dominant and  smooth of relative dimension on the connected components in its image.
 \end{lemma}

### 2015-10-10 followup.tex
Added proof that G --> Gab exists in Fq-schemes.

@@
 
-\subsection{Derived subgroup}
+\subsection{Derived subgroup and abelianization}
 
@@
 
-\subsection{Abelianization}
-
-Let $q: G \to G\ab$ be the fppf-quotient  . . . 
-We suppose $G\ab$ exists in group schemes over $\Fq$. \todo{This is a condition on $G$. Does it follow from smoothness? I've written to Masoud for help on this.}
-If $G$ is of finite type (and so, an algebraic group) then $G\ab$ exists in group schemes by \cite{GM}*{Thm 4.39}: $G$ smooth implies $G$ flat; $G\der$ is also smooth (!) so also flat; $\dim \Spec{\Fq} \leq 1$.
-
+The quotient $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ by SGA3, Expos\'e VI, Tome B, Th\'eor\`eme 3.2, which also shows that the quotient $G \to G\ab$ is a faithfully flat and a $G$-torsor in the fppf topology.
 \[

### 2015-10-13 followup.tex
Fixed the definition of H-equivariant character sheaf.
I was missing the compatibility of nu and mu.

@@
 We introduce and establish the basic properties of  the category of \emph{commutative character sheaves} on smooth group schemes $G$ over finite fields $\Fq$. 
-We use this category to geometrize all generic types for supercuspidal representations of $p$-adic groups. 
+We use this category to geometrize types for supercuspidal representations of $p$-adic groups. 
 \end{abstract}
@@
 \begin{definition}\label{def:CCS}
-A linear character sheaf on $G$ is a \emph{commutative character sheaf} if there is an isomorphism $m^* \cs{L} \to m\op^* \cs{L}$ of local systems on $G\times G$ such that the following diagram commutes.
+A linear character sheaf on $G$ is a \emph{commutative character sheaf} if there is an isomorphism $\xi: m^* \cs{L} \to m\op^* \cs{L}$ of [linear character sheaves?] on $G\times G$ such that the following diagram commutes.
   \[
   \begin{tikzcd}[row sep=30]
-   m^*\cs{L} \arrow{d} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
+   m^*\cs{L} \arrow{d}{\xi} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
    m\op^*\cs{L} \arrow{r}{{\theta}^*\mu} &  {\bar \theta}^*(\cs{L}\boxtimes\cs{L})
@@
 
-\begin{lemma}
-If the isomorphism $m^* \cs{L} \to m\op^* \cs{L}$ exists and satisfies the condition of Definition~\ref{def:CCS}, then it is unique.
+We will see that this condition is not trivial: even on commutative group schemes over $\Fq$, not every linear character sheaf is commutative; even on connected reductive algebraic groups over $\Fq$, not every linear character sheaf is commutative.
+
+\begin{lemma}\label{lem:symmetry}
+If the isomorphism $\xi: m^* \cs{L} \to m\op^* \cs{L}$ exists and satisfies the condition of Definition~\ref{def:CCS}, then it is unique.
 \end{lemma}
@@
 Let $G\der \hookrightarrow G$ denote the closed subgroup generated by the smooth morphism $G\times G \to G$ given by $(x,y)\mapsto xyx^{-1}y^{-1}$.
-Then $G \times G \to G\der$ is a dominant morphism \cite{SGA3}*{{VI}$_B$, 7.2}
-and $G$ is commutative if and only if $G\der$ is trivial.
-
+Then $G \times G \to G\der$ is a dominant morphism \cite{SGA3}*{{VI}$_B$, 7.2}.
+Moreover, $G$ is commutative if and only if $G\der$ is trivial.
+%
 While the subgroup $G\der$ is smooth, it need not be connected. 
@@
 
-The quotient $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ by SGA3, Expos\'e VI, Tome B, Th\'eor\`eme 3.2, which also shows that the quotient $G \to G\ab$ is a faithfully flat and a $G$-torsor in the fppf topology.
+The quotient $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ by SGA3, Expos\'e VI, Tome A, Th\'eor\`eme 3.2, which also shows that the quotient $G \to G\ab$ is a faithfully flat and a $G\der$-torsor in the fppf topology.
 \[
@@
 
-Another hypothesis: suppose the smooth morphism $G\times G\to G\der$ is of relative dimension on each connected component of its image in $G\der$.\todo{This is another condition on $G$.
+Provisional hypothesis: suppose the smooth morphism $G\times G\to G\der$ is of relative dimension on each connected component of its image in $G\der$...\todo{This is another condition on $G$.
 Does it come from smoothness of $G$?}
@@
 \begin{theorem}\label{thm:Gab}
-Under these hypotheses, pull-back along the abelianization $q : G \to G\ab$
+Under this hypothesis, pull-back along the abelianization $q : G \to G\ab$
 \[
@@
 
-Let $G$ and $H$ be group schemes; let $n : H \times G\to G$ be a group action and write $p : H\times G \to G$ for projection. 
-An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  $\nu : n^*\cs{L} \to p^*\cs{L}$ of Weil local systems on $G\times G$ such that the following diagram commutes,
+Let $G$ and $H$ be group schemes; let $a : H \times G\to G$ be a group action and write $p : H\times G \to G$ for projection. 
+An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  $\nu : a^*\cs{L} \to p^*\cs{L}$ of Weil local systems on $G\times G$ such that the following diagram of local systems on $H\times H\times G$ commutes,
 \[
 \begin{tikzcd}
-\ &  n_0^*  n^*\, \mathcal{L} \arrow{r}{n_0^*\nu} & n_0^* p^*\, \mathcal{L} & \\
-n_1^* n^*\, \mathcal{L} \arrow{dr}[swap]{n_1^*\nu} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{p_2^*\nu} p_2^* n^*\, \mathcal{L} \\
-& n_1^* p^*\, \mathcal{L} \arrow[equal]{r} & p_2^* p^*\, \mathcal{L}, & 
+\ &  a_0^*  a^*\, \mathcal{L} \arrow{r}{a_0^*\nu} & a_0^* p^*\, \mathcal{L} & \\
+a_1^* a^*\, \mathcal{L} \arrow{dr}[swap]{a_1^*\nu} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{p_2^*\nu} p_3^* a^*\, \mathcal{L} \\
+& a_1^* p^*\, \mathcal{L} \arrow[equal]{r} & p_3^* p^*\, \mathcal{L}, & 
 \end{tikzcd}
 \]
-where $n_0(a,b,x) = (a,n(b,x))$ and $n_1(a,b,x) = (n(ab),x)$ and $p_2(a,b,x) = (b,x)$.
+where $a_0(x,y,z) = (x,a(y,z))$ and $a_1(x,y,z) = (a(x,y),z)$ and $p_3(x,y,z) = (y,z)$.
+We remark that, on stalks, this condition is ...
+\[
+\begin{tikzcd}
+\ &  \cs{L}_{x\cdot(y\cdot z)} \arrow{r}{\nu_{x,y\cdot z}} & \cs{L}_{y\cdot z} & \\
+\cs{L}_{(x\cdot y)\cdot z} \arrow{dr}[swap]{\nu_{x\cdot y,z}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{y,z}} \cs{L}_{y\cdot z} \\
+& \cs{L}_z \arrow[equal]{r} & \cs{L}_z & 
+\end{tikzcd}
+\]
+
 Morphisms of $H$-equivariant Weil local systems are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which . . .
 
-An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ with no condition tying $\mu$ and $\nu$ together.
-Write $\CS_H(G)$ for the category of $H$-equivariant linear character sheaves on $G$.\todo{Under construction}
+An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense that the following diagram of local systems on $H \times G\times G$ commutes ....
+On stalks, this condition is
+\[
+\begin{tikzcd}
+\ &  \cs{L}_{h\cdot (xy)} \arrow{r}{} & \cs{L}_{xy} & \\
+\cs{L}_{(h\cdot x)(h\cdot y)} \arrow{dr}[swap]{} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{} \cs{L}_{xy} \\
+& \cs{L}_{h\cdot x}\otimes \cs{L}_{h\cdot y} \arrow{r} & \cs{L}_x\otimes \cs{L}_y & 
+\end{tikzcd}
+\]
 
+Write $\CS_H(G)$ for the category of $H$-equivariant linear character sheaves on $G$.
+%\todo{Under construction}
+%
 Finally, an $H$-equivariant commutative character sheaf on $G$ is an $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ for whuch
 
-\begin{lemma}\label{lem:equivariant}
-Categories $\CCS(G)$ and $\CCS_G(G)$ are equivalent.
+\begin{lemma}
+If $(\cs{L},\mu,\nu)$ is an equivariant linear character sheaf for the conjugation action of $G$ on $G$, then $(\cs{L},\mu)$ is a commutative character sheaf.
 \end{lemma}
@@
 \begin{proof}
-Let $a : G \times G \to G$ be the conjugation action of $G$ on $G$ and let $p : G \times G \to G$ be projection to the second factor.
-Then $a = m \circ (m \times (\iota \circ p_1))$ while $m\op \circ (m \times (\iota \circ p_1)) = p$;
-likewise, $m = a \circ (p_1\times m\op)$ while $p \circ (p_1\times m\op) = m\op$.
-
-Let $(\cs{L},\mu)$ be a commutative character sheaf on $G$.
-Let $c: m^*\cs{L} \to m\op^*\cs{L}$ be an isomorphism satisfying the condition of Definition~\ref{def:CCS}. Then
-\begin{align*}
-a^* \cs{L} 
-&= (m \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
-&= (m \times (\iota \circ p_1))^* m^* \cs{L}\\
-&\iso (m \times (\iota \circ p_1))^* m\op^* \cs{L}\\
-&= (m\op \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
-&= p^*\cs{L}.
-\end{align*}
-The isomorphism above is 
-\[
-(m \times (\iota \circ p_1))^* c: a^*\cs{L} \to p^*\cs{L},
-\]
- so $(\cs{L}, (m \times (\iota \circ p_1))^* c)$ is a $G$-equivariant commutative character sheaf.
-
-Let $(\cs{L}, \nu)$ be an equivariant linear character sheaf.
+Let $a : G \times G \to G$ be the conjugation action $(g,h) \mapsto ghg^{-1}$ and let $p : G \times G \to G$ be projection to the second factor.
+Let $\iota : G\to G$ be inversion for the group operation $m : G\times G\to G$.
+Then $m = a \circ (p_1\times m\op)$ while $p \circ (p_1\times m\op) = m\op$.
+Now, let $(\cs{L}, \mu, \nu)$ be an equivariant linear character sheaf.
 Then
@@
 \[
-(p_1 \times m\op)^* \nu : m^* \cs{L}  \to m\op^* \cs{L},
+\xi \ceq (p_1 \times m\op)^* \nu : m^* \cs{L}  \to m\op^* \cs{L}
 \]
-so $(\cs{L},\mu)$ is a commutative character sheaf.
+Observe that $p_1 \times m\op : G\times G \to G\times G$ is an isomorphism of varieties . . . 
+The isomorphism $\xi$ satisfies the condition of Definition~\ref{def:CCS}. \todo{Checking this.}
+
+Thus, $(\cs{L},\mu)$ is a commutative character sheaf.
+\end{proof}
+
+\begin{remark}
+By Lemma~\ref{lem:symmetry}, the isomorphism $\xi_\nu$ is uniquely determined by $\mu$.
+%This is the first hint that the forgetful functor may be an equivalence.
+\end{remark}
+
+\begin{lemma}\label{lem:equivariant}
+The forgetful functor $\CCS_G(G)\to \CCS(G)$, given by $(\cs{L},\mu,\nu) \mapsto (\cs{L},\mu)$, is an equivalence.
+\end{lemma}
+
+\begin{proof}
+Now, let $(\cs{L},\mu)$ be a commutative character sheaf.
+Let $\xi: m^*\cs{L} \to m\op^*\cs{L}$ be an isomorphism satisfying the condition of Definition~\ref{def:CCS}.
+Observe that $a = m \circ (m \times (\iota \circ p_1))$ while $m\op \circ (m \times (\iota \circ p_1)) = p$.
+Then
+\begin{align*}
+a^* \cs{L} 
+&= (m \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
+&= (m \times (\iota \circ p_1))^* m^* \cs{L}\\
+&\iso (m \times (\iota \circ p_1))^* m\op^* \cs{L}\\
+&= (m\op \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
+&= p^*\cs{L}.
+\end{align*}
+The isomorphism above is 
+\[
+\nu_\xi \ceq (m \times (\iota \circ p_1))^* \xi: a^*\cs{L} \to p^*\cs{L},
+\]
+ so $(\cs{L}, \mu, \nu_\xi)$ is a $G$-equivariant commutative character sheaf.
+
+ forgetful  rule $(\cs{L},\mu)\to (\cs{L},\mu,\nu_\xi)$ and 
+To define the promised adjunction, I need to modify the functors slighlty . . . 
 \todo{This proof is under construction.}
@@
 Let $G$ be a $k$-group scheme and let $H \to G$ be a closed subgroup scheme over $S$.
-
-Write $n : H \times_S G \to G$ for the left action of $H$ on $G$; let $p : H\times_S G \to G$ be projection.
 
@@
 \]
+
+Let $j : H \hookrightarrow G$ be the kernel of $q : G \to G'$ and let $m : G\times G \to G$ be multiplication for $G$. 
+Write $n : H \times_S G \to G$ for the left action of $H$ on $G$; this is obtained by restricting the action $m : G\times G\to G$ to the subgroup $H\times G$. 
+Let $n : H \times G \to G$ be the restriction of $m: G\times G \to G$.
+Then $n = m \circ (j \times \id)$, so
+
+ let $p : H\times_S G \to G$ be projection.
+
 %In particular, $G \times_{G'} G \iso H\times_S G'$, so $G \to G'$ is a $G$-torsor in the fppf topology.
@@
 %Let $j : C \hookrightarrow G$ be the kernel of $q : G \to G\ab$ and let $m : G\times G \to G$ be multiplication for $G$. 
-Let $n : G\der \times G \to G$ be the restriction of $m: G\times G \to G$.
+Let $n : H \times G \to G$ be the restriction of $m: G\times G \to G$.
 Then $n = m \circ (j \times \id)$, so
@@
 &= (\EE)_C \boxtimes \cs{L}\\
-&= p^* \cs{L}.
+&= p^* \cs{L};
 \end{align*}
-Thus, every commutative character sheaf $\cs{L}$ on $G$ is $G\der$-equivariant.
+the isomorphism above is 
+\[
+\nu_\mu \ceq(j \times \id))^* \mu: n^*\cs{L} \to p^*\cs{L}.
+\]
+Thus, every commutative character sheaf $\cs{L}$ on $G$ is $H$-equivariant.
 It now follows from Lemma~\ref{lem:Lder} that the forgetful functor $\CCS_{G\der}(G) \to \CCS(G)$ is an equivalence. 

### 2015-10-20 followup.tex
Working on Defintion section

--- 2015-10-01 followup.tex
@@
 Since $\CCS(G)$ is a full subcategory of $\CS(G)$, and since Item \ref{b2} above shows $\CCSiso{G} \iso G(\Fq)^*$, canonically, the category $\CCS(G)$ is now completely described by the following consequence of \cite{cunningham-roe:13a}*{Thm.
-3.9}: in $\CCS(G)$, every morphism $\cs{L} \to \cs{L}'$ is either trivial (zero on stalks) or and isomorphism, and
+3.9}: in $\CCS(G)$, every morphism $\cs{L} \to \cs{L}'$ is either trivial (zero on stalks) or an isomorphism, and
 \[
@@
 
-\subsection{Main definition}
+\subsection{Commutative character sheaves on commutative groups}
 
@@
 The category of character sheaves on $G$ is denoted by $\CS(G)$.
-
-The definition of $\CS(G)$ also makes sense for non-commutative $G$.  
-In order to distinguish the resulting objects from
-the character sheaves of Lusztig, we will refer to the former as \emph{linear character sheaves} (to evoke the one-dimensional character sheaves of \cite{Kamgarpour})
-and again write $\CS(G)$ for the resulting category, with morphisms defined as in \cite{cunningham-roe:13a}*{Def. 1.1}.
 
@@
 \end{proof}
+
+\subsection{Commutative character sheaves on non-commutative groups}
+
+We now drop the assumption that $G$ is commutative, and assume only that it is smooth.
+The category $\CS(G)$ still makes sense in this context, defined as in 
+In order to distinguish the resulting objects from
+the character sheaves of Lusztig, we will refer to the former as \emph{linear character sheaves} (to evoke the one-dimensional character sheaves of \cite{Kamgarpour})
+and again write $\CS(G)$ for the resulting category, with morphisms defined as in \cite{cunningham-roe:13a}*{Def. 1.1}.
 
@@
 Since $c : G \times G \to G\der$ is schematically dense, $c^* (\cs{L}\vert_{G\der}) \iso (\EE)_{G\times G}$ implies $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ by Lemma~\ref{lem:dominant}.
+\todo{broken reference}
 
@@
 
-In \cite{yu:03a} it is shown that, for $0 \leq i < d$, the $p$-adic group $\G^i(K)$ admits a smooth integral model, in the sense that there is a smooth group scheme $\underline{G}^i$ over $\OK$ such that $\underline{G}^i(\OK) = \G^i(K)$.
+In \cite{yu:03a} it is shown that, for $0 \leq i < d$, the $p$-adic group $\G^i(K)$ admits a smooth integral model, in the sense that there is \todo{is $\underline{G}^i$ canonically determined?} a smooth group scheme $\underline{G}^i$ over $\OK$ such that $\underline{G}^i(\OK) = \G^i(K)$.
 Set $G^i_n \ceq \Gr^R_n(\underline{G}^i)$ and $G^i \ceq \Gr_R(\underline{G}^i)$; 
@@
 
-Using Corollary~\ref{cor:QCS} we see that each quasicharacter $\phi_i : G^i(\Fq) \to \EEx$ determines a quasicharacter sheaf $\cs{L}^i$, unique up to isomorphism, from which the quasicharacter $\phi_i$ can be recovered using the trace of Frobenius.
-In fact, more is true. Let $n_{\phi_i}$ be the smallest non-negative integer $n$ such that $\phi_i : G^i(\Fq) \to \EEx$ factors through $G^i(\Fq) \to G^i_n(\Fq)$.
-Then $\phi_i$ determines a commutative character sheaf $\cs{L}_{n_{\phi_i}}^i$, unique up to isomorphism, from which the quasicharacter $\phi_i$ can be recovered.
-Then $\cs{A}_i\ceq \cs{L}_{n_{\phi_i}}^i[\dim G_{n_{\phi_i}}^i]$ is a perverse sheaf on $G_{n_{\phi_i}}^i$ from which the quasicharacter $\phi_i$ can be recovered.
+Using Corollary~\ref{cor:QCS} \todo{broken reference} we see that each quasicharacter $\phi_i : G^i(\Fq) \to \EEx$ determines a quasicharacter sheaf $\cs{L}^i$, unique up to isomorphism, from which the quasicharacter $\phi_i$ can be recovered using the trace of Frobenius.
+In fact, more is true. Let $n_i$ be the smallest non-negative integer $n$ such that $\phi_i : G^i(\Fq) \to \EEx$ factors through $G^i(\Fq) \to G^i_n(\Fq)$.
+Then $\phi_i$ determines a commutative character sheaf $\cs{L}_{n_i}^i$, unique up to isomorphism, from which the quasicharacter $\phi_i$ can be recovered.
+Then $\cs{A}_i\ceq \cs{L}_{n_i}^i[\dim G_{n_i}^i]$ is a perverse sheaf on $G_{n_i}^i$ from which the quasicharacter $\phi_i$ can be recovered.
 In this way,  $\vec{\phi} = (\phi_0, \ldots , \phi_{d-1})$ determines perverse sheaves $\vec{\cs{A}} = (\cs{A}_0, \ldots , \cs{A}_{d-1})$ from which $\vec{\phi}$ can be recovered.

### 2015-10-27 followup.tex
Work from ICERM houseboat

@@
 Let $G$ be a smooth group scheme over a finite field $\Fq$; that is, let $G$ be a group scheme over $\Fq$
-for which the structure morphism $G \to \Spec{\Fq}$ is smooth in the sense of [include reference for this definition].
+for which the structure morphism $G \to \Spec{\Fq}$ is smooth in the sense of \todo{include reference for this definition}.
 This implies $G \to \Spec{\Fq}$ is locally of finite type, but not that it is of finite type.
@@
 
+We write $m : G \times G \to G$ for the multiplication morphism, and $G(k)^*$ for $\Hom(G(k), \EEx)$.
+Define $\theta : G\times G \to G\times G$ by $\theta(g,h) = (h,g)$.
+
 \subsection{Commutative character sheaves on commutative groups}
 
-Let $\theta : G\times G \to G\times G$ be given by $\theta(g,h) = (h,g)$.
-Write $m : G \times G \to G$ for the multiplication morphism
-and define $m\op : G \times G \to G$ by $m\op = m \circ \theta$.
-For any Weil local system $\cs{L}$ on $G$ there is an isomorphism
-$\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ given on stalks by the canonical map
-$\gcs{L}_{g} \otimes \gcs{L}_{h} \to \gcs{L}_{h} \otimes \gcs{L}_{g}$.
-
-When $G$ is commutative, recall \cite{cunningham-roe:13a}*{Def. 1.1} that a character sheaf on $G$ is a triple $(\gcs{L}, \mu, \phi)$,
+Suppose now that $G$ is commutative.
+Recall \cite{cunningham-roe:13a}*{Def. 1.1} that a character sheaf on $G$ is a triple $(\gcs{L}, \mu, \phi)$,
 where $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, 
@@
 and $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an isomorphism of sheaves on $\bG$;
-the triple $(\gcs{L}, \mu, \phi)$ must also satisfy compatibility conditions specified in \cite{cunningham-roe:13a}*{Def. 1.1}.
-Writing $\cs{L}$ for the Weil local system $(\gcs{L}, \mu, \phi)$, these compatibility conditions are simply this: $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is an isomorphism of Weil local systems.
+the triple $(\gcs{L}, \mu, \phi)$ must also satisfy compatibility conditions specified in \emph{loc. cite}.
 The category of character sheaves on $G$ is denoted by $\CS(G)$.
 
-\begin{definition}\label{def:CCS}
-A linear character sheaf on $G$ is a \emph{commutative character sheaf} if there is an isomorphism $\xi: m^* \cs{L} \to m\op^* \cs{L}$ of [linear character sheaves?] on $G\times G$ such that the following diagram commutes.
+Let $\cs{L}$ be a character sheaf on $G$.  Since $m = m \circ \theta$ in the commutative case,
+there is a canonical isomorphism $\xi : m^* \cs{L} \to \theta^* m^* \cs{L}$.
+There is also an isomorphism $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$
+given on stalks by the canonical map $\gcs{L}_{g} \otimes \gcs{L}_{h} \to \gcs{L}_{h} \otimes \gcs{L}_{g}$.
+
+\begin{definition}\label{def:CCScom}
+A character sheaf $(\cs{L}, \mu)$ on a smooth commutative group scheme $G$ is \emph{commutative}
+if the following diagram of Weil sheaves on $G \times G$ commutes.
   \[
@@
    m^*\cs{L} \arrow{d}{\xi} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
-   m\op^*\cs{L} \arrow{r}{{\theta}^*\mu} &  {\bar \theta}^*(\cs{L}\boxtimes\cs{L})
+   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L})
   \end{tikzcd}
@@
 
-We will see that this condition is not trivial: even on commutative group schemes over $\Fq$, not every linear character sheaf is commutative; even on connected reductive algebraic groups over $\Fq$, not every linear character sheaf is commutative.
-
-\begin{lemma}\label{lem:symmetry}
-If the isomorphism $\xi: m^* \cs{L} \to m\op^* \cs{L}$ exists and satisfies the condition of Definition~\ref{def:CCS}, then it is unique.
-\end{lemma}
-
-\begin{proof}
-Why is this true?
-\end{proof}
-
 \subsection{Commutative character sheaves on non-commutative groups}
@@
 We now drop the assumption that $G$ is commutative, and assume only that it is smooth.
-The category $\CS(G)$ still makes sense in this context, defined as in 
+The category $\CS(G)$ still makes sense in this context, defined as in \cite{cunningham-roe:13a}*{Def. 1.1}.
 In order to distinguish the resulting objects from
-the character sheaves of Lusztig, we will refer to the former as \emph{linear character sheaves} (to evoke the one-dimensional character sheaves of \cite{Kamgarpour})
-and again write $\CS(G)$ for the resulting category, with morphisms defined as in \cite{cunningham-roe:13a}*{Def. 1.1}.
+the character sheaves of Lusztig, we will refer to the former as \emph{linear character sheaves}
+(to evoke the one-dimensional character sheaves of \cite{Kamgarpour})
+and again write $\CS(G)$ for the resulting category, with morphisms defined as in \emph{loc. cite}.
+
+We recall some facts about the abelianization of a smooth group scheme $G$.
+Let $G\der \hookrightarrow G$ denote the closed subgroup generated by the smooth morphism
+$G\times G \to G$ given by $c: (x,y)\mapsto xyx^{-1}y^{-1}$. Then
+$G \times G \to G\der$ is a dominant morphism \cite{SGA3}*{Expos\'e {VI}$_B$, \S 7.2}.
+Moreover, $G$ is commutative if and only if $G\der$ is trivial.
+When $G$ is not connected, $G\der$ need not be connected, though it is smooth.
+The restriction of $G\times G\to G\der$ to identity components gives a dominant
+morphism $G^0\times G^0 \to G^0\der$ \cite{SGA3}*{Expos\'e {VI}$_B$, Prop. 7.8}.
+
+The quotient $G\ab\ceq G/G\der$ exists in schemes over $\Fq$, and the quotient $q : G \to G\ab$
+is faithfully flat and a $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
+We summarize the setup in a diagram.
+\[
+\begin{tikzcd}
+{} & G\times G \arrow{d}{c} &&&\\
+1 \arrow{r} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
+\end{tikzcd}
+\]
+
+If $\chi \in G(k)^*$ is a character, it must vanish on the derived subgroup $G\der(k)$.
+Kamgarpour gives an example \cite{kamgarpour:09a}*{(1.1)} of a character sheaf
+that does not vanish on $G\der$, defined by the extension
+\[
+1 \to \mu_n \to \SL_n \to \PGL_n \to 1.
+\]
+In order to obtain a relationship between character sheaves on $G$ and characters of $G(k)$,
+he opts to give a different definition of commutator.  Since we already need to adapt our
+notion of character sheaf, even in the commutative case, we instead add restrictions
+to the definition of commutative character sheaf and leave the definition of $G\der$ unchanged.
+
+The first step in this process is to rule out character sheaves as above.
+The following proposition will be proven in Section \ref{sec:descent}.
+\begin{proposition}
+Suppose $G$ is a smooth group scheme and $\cs{L} \in \CS(G)$ is a linear character sheaf on $G$.
+Then the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $\cs{L} \cong q^*(\cs{L}\ab)$ for some
+character sheaf $\cs{L}\ab$ on $G\ab$.
+\end{proposition}
+
+We may then define commutative character sheaves on $G$.
+
+\begin{definition}\label{def:CCS}
+A linear character sheaf $\cs{L}$ on a smooth group scheme $G$ is \emph{commutative} if
+\[
+\cs{L} \cong q^* \cs{L}\ab
+\]
+for a commutative character sheaf $\cs{L}\ab$ on $G\ab$.  As in the commutative case,
+we write $\CCS(G)$ for the full subcategory of $\CS(G)$ consisting of commutative character sheaves.
+\end{definition}
+
+Note that we may also pull back the map $\xi\ab : m\ab^* \cs{L}\ab \to \theta\ab^*(m\ab^* \cs{L})$ from Definition \ref{def:CCScom}.
+The following proposition will be proven in Section \ref{sec:descent}.
+
+\begin{proposition}
+A linear character sheaf $(\cs{L}, \mu)$ on a smooth group scheme $G$ is commutative if and only if
+\begin{enumerate}
+\item $\cs{L} \cong q^* \cs{L}\ab$ for some character sheaf $\cs{L}\ab$ on $G\ab$,
+\item the following diagram of Weil sheaves on $G \times G$ commutes.
+  \[
+  \begin{tikzcd}[row sep=30]
+   m^*\cs{L} \arrow{d}[swap]{(q\times q)^*\xi\ab} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
+   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L})
+  \end{tikzcd}
+  \]
+\end{enumerate}
+\end{proposition}
 
@@
 
-\section{Descent to the Abelianization}
-
-\subsection{Derived subgroup and abelianization}
-
-Let $G$ be a smooth group scheme.
-Let $G\der \hookrightarrow G$ denote the closed subgroup generated by the smooth morphism $G\times G \to G$ given by $(x,y)\mapsto xyx^{-1}y^{-1}$.
-Then $G \times G \to G\der$ is a dominant morphism \cite{SGA3}*{{VI}$_B$, 7.2}.
-Moreover, $G$ is commutative if and only if $G\der$ is trivial.
-%
-While the subgroup $G\der$ is smooth, it need not be connected. 
-The restriction of $G\times G\to G\der$ to identity components gives a dominant morphism $G^0\times G^0 \to G^0\der$ by [SGA3, Tome 6B, Expos\'e 7, Prop 7.8]
-
-The quotient $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ by SGA3, Expos\'e VI, Tome A, Th\'eor\`eme 3.2, which also shows that the quotient $G \to G\ab$ is a faithfully flat and a $G\der$-torsor in the fppf topology.
-\[
-\begin{tikzcd}
-{} & G\times G \arrow{d}{} &&&\\
-1 \arrow{r} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
-\end{tikzcd}
-\]
+\section{Descent to the Abelianization} \label{sec:descent}
 

### 2015-11-02 followup.tex
Reconstruction of Section 3.

@@
 \begin{abstract}
-We introduce and establish the basic properties of  the category of \emph{commutative character sheaves} on smooth group schemes $G$ over finite fields $\Fq$. 
+We introduce and establish the basic properties of  the category of \emph{commutative character sheaves} on smooth group schemes $G$ over finite fields $\Fq$, building on earlier work by the same authors.
 We use this category to geometrize types for supercuspidal representations of $p$-adic groups. 
@@
 
- \subsection{Statement of the main result}
+In this section we use descent along the abelianization $q : G \to G\ab$ to prove Propositions~1.2 and 1.4, and Theorem~\ref{thm:Gab}.
 
-As in [CS], every morphism of group schemes $G \to G'$ induces . .
+\subsection{Equivariant Weil local systems}
 
-Provisional hypothesis: suppose the smooth morphism $G\times G\to G\der$ is of relative dimension on each connected component of its image in $G\der$...\todo{This is another condition on $G$.
-Does it come from smoothness of $G$?}
-
-\begin{theorem}\label{thm:Gab}
-Under this hypothesis, pull-back along the abelianization $q : G \to G\ab$
-\[
-q^* : \CCS(G\ab) \to \CCS(G)
-\]
-is an equivalence of categories.
-\end{theorem}
-
-Theorem~\ref{thm:Gab} will be proved by factoring $\CCS(G\ab) \to \CCS(G\ab)$ according to the following diagram, which will be explained below, 
-and by showing that each functor is an equivalence.
+Let $G$ be as above.
+Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
+Let $a : H \times G\to G$ be a group action compatible with the group structure on $G$ and write $p : H\times G \to G$ for projection. 
+Consider the morphisms
 \[
 \begin{tikzcd}
- \CCS(G)  &&& \arrow{lll}[swap]{q^*}  \CCS(G\ab) \arrow{d}{\text{Descent along torsor}} \\
-\CCS_G(G)  \arrow{u}{\text{Equivariance}} &&& \arrow{lll}{\text{Change of Action}} \CCS_{G\der}(G) 
+H \times H \times G 
+\arrow[shift left=4]{r}{b_1} 
+\arrow{r}{b_2} 
+\arrow[shift right=4]{r}{b_3} 
+& H \times G 
+\arrow[shift left]{r}{a}
+\arrow[shift right]{r}[swap]{p}
+ & G 
 \end{tikzcd}
 \]
-
-\begin{remark}
-Theorem~\ref{thm:Gab} provides an indication that $\CCS(G)$ is the correct category in which to geometrize characters of $G(\Fq)$. 
-By contrast, $\CS(G)$ and $\CS(G\ab)$ are generally not isomorphic categories, not even when $G$ is a connected reductive algebraic group and $\Hh^1(\Fq,G\der)=0$, as we will see in Section~\ref{sec:stacky}.
-\end{remark}
-
-\subsection{Equivariance}
-
-We wish to consider the categories $\CCS_G(G)$ (resp $\CS_G(G)$) of $G$-equivariant commutative character sheaves (linear character sheaves) on $G$.
-To that end, in this section we introduce that notion in its general context.
-
-Let $G$ and $H$ be group schemes; let $a : H \times G\to G$ be a group action and write $p : H\times G \to G$ for projection. 
-An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  $\nu : a^*\cs{L} \to p^*\cs{L}$ of Weil local systems on $G\times G$ such that the following diagram of local systems on $H\times H\times G$ commutes,
+defined by $b_1(h_1,h_2,g) = (n(h_1,h_2),g)$,  $b_2(h_1,h_2,g) = (h_1,a(h_2,g))$ and $b_3(h_1,h_2,g) = (h_2,g)$.
+Then, $a\circ b_1 = a\circ b_2$ and $a\circ b_3 = p\circ b_2$ and $p\circ b_1 = p\circ b_3$.
+An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
+\[
+\nu : a^*\cs{L} \to p^*\cs{L}
+\] 
+of Weil local systems on $H\times G$ such that the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes,
 \[
 \begin{tikzcd}
-\ &  a_0^*  a^*\, \mathcal{L} \arrow{r}{a_0^*\nu} & a_0^* p^*\, \mathcal{L} & \\
-a_1^* a^*\, \mathcal{L} \arrow{dr}[swap]{a_1^*\nu} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{p_2^*\nu} p_3^* a^*\, \mathcal{L} \\
-& a_1^* p^*\, \mathcal{L} \arrow[equal]{r} & p_3^* p^*\, \mathcal{L}, & 
+\ &  \arrow{dl}[swap]{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}{p\circ b_2 = a\circ b_3} & \\
+b_1^* a^*\, \mathcal{L} \arrow{dr}[swap]{b_1^*(\nu)} &&&&   \arrow{dl}{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
+& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L}, & 
 \end{tikzcd}
 \]
-where $a_0(x,y,z) = (x,a(y,z))$ and $a_1(x,y,z) = (a(x,y),z)$ and $p_3(x,y,z) = (y,z)$.
+and $s^*(\nu) = \id_{\cs{L}}$.
+In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations above; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
+\iffalse
 We remark that, on stalks, this condition is ...
@@
 \]
+\fi
+%
+Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
+\[
+\begin{tikzcd}
+\arrow{d}[swap]{\nu} a^*\cs{L} \arrow{r}{a^*(\alpha)} & a^*\cs{L}' \arrow{d}{\nu'} \\
+p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
+\end{tikzcd}
+\]
+commutes.
+This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.
 
-Morphisms of $H$-equivariant Weil local systems are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which . . .
+\subsection{Equivariant linear character sheaves}
 
-An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense that the following diagram of local systems on $H \times G\times G$ commutes ....
+An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense. 
+Consider the morphisms $c_1 : H \times G\times G \to G\times G$, $c_2 : H \times G\times G \to H\times G$ and $c_3 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),a(h,g_2))$ and $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$ and $c_3(h, g_1, g_2) = (g_1, g_2)$.
+Then $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ if $(\cs{L},\mu)$ is a linear character sheaf on $G$ and the following diagram of Weil local systems on $H \times G\times G$ commutes.
+\[
+\begin{tikzcd}
+\arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} & \arrow{l}[swap]{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{r}{p\circ c_2 = m\circ c_3}  & c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
+c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{r} & (p^*\cs{L}) \boxtimes (p^*\cs{L}) & \arrow{l}[swap]{\nu\boxtimes \nu}  (a^*\cs{L}) \boxtimes (a^*\cs{L}) & \arrow{l} c_3^*(\cs{L}\boxtimes \cs{L})
+\end{tikzcd}
+\]
+In this diagram, the arrows not labeled are derived from canonical isomorphisms.
+\iffalse
 On stalks, this condition is
@@
 \]
+\fi
+%
+A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves, so
+\[
+\begin{tikzcd}
+\arrow{d}{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
+\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
+\end{tikzcd}
+\]
+commutes.
+%
+Let $\CS_H(G)$ be the category of $H$-equivariant linear character sheaves on $G$.
 
-Write $\CS_H(G)$ for the category of $H$-equivariant linear character sheaves on $G$.
-%\todo{Under construction}
-%
-Finally, an $H$-equivariant commutative character sheaf on $G$ is an $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ for whuch
+Is $\CS_H(G)$ a rigid monoidal category?
 
-\begin{lemma}
-If $(\cs{L},\mu,\nu)$ is an equivariant linear character sheaf for the conjugation action of $G$ on $G$, then $(\cs{L},\mu)$ is a commutative character sheaf.
-\end{lemma}
+\subsection{Descent along a torsor}
 
-\begin{proof}
-Let $a : G \times G \to G$ be the conjugation action $(g,h) \mapsto ghg^{-1}$ and let $p : G \times G \to G$ be projection to the second factor.
-Let $\iota : G\to G$ be inversion for the group operation $m : G\times G\to G$.
-Then $m = a \circ (p_1\times m\op)$ while $p \circ (p_1\times m\op) = m\op$.
-Now, let $(\cs{L}, \mu, \nu)$ be an equivariant linear character sheaf.
-Then
-\begin{align*}
-m^* \cs{L} 
-&= (a \circ (p_1 \times m\op))^* \cs{L}\\
-&= (p_1 \times m\op)^* a^* \cs{L}\\
-&\iso (p_1 \times m\op)^* p^* \cs{L}\\
-&= (p\circ (p_1 \times m\op))^* \cs{L}\\
-&= m\op^* \cs{L}.
-\end{align*}
-The isomorphism above is
-\[
-\xi \ceq (p_1 \times m\op)^* \nu : m^* \cs{L}  \to m\op^* \cs{L}
-\]
-Observe that $p_1 \times m\op : G\times G \to G\times G$ is an isomorphism of varieties . . . 
-The isomorphism $\xi$ satisfies the condition of Definition~\ref{def:CCS}. \todo{Checking this.}
-
-Thus, $(\cs{L},\mu)$ is a commutative character sheaf.
-\end{proof}
-
-\begin{remark}
-By Lemma~\ref{lem:symmetry}, the isomorphism $\xi_\nu$ is uniquely determined by $\mu$.
-%This is the first hint that the forgetful functor may be an equivalence.
-\end{remark}
-
-\begin{lemma}\label{lem:equivariant}
-The forgetful functor $\CCS_G(G)\to \CCS(G)$, given by $(\cs{L},\mu,\nu) \mapsto (\cs{L},\mu)$, is an equivalence.
-\end{lemma}
-
-\begin{proof}
-Now, let $(\cs{L},\mu)$ be a commutative character sheaf.
-Let $\xi: m^*\cs{L} \to m\op^*\cs{L}$ be an isomorphism satisfying the condition of Definition~\ref{def:CCS}.
-Observe that $a = m \circ (m \times (\iota \circ p_1))$ while $m\op \circ (m \times (\iota \circ p_1)) = p$.
-Then
-\begin{align*}
-a^* \cs{L} 
-&= (m \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
-&= (m \times (\iota \circ p_1))^* m^* \cs{L}\\
-&\iso (m \times (\iota \circ p_1))^* m\op^* \cs{L}\\
-&= (m\op \circ (m \times (\iota \circ p_1)))^* \cs{L}\\
-&= p^*\cs{L}.
-\end{align*}
-The isomorphism above is 
-\[
-\nu_\xi \ceq (m \times (\iota \circ p_1))^* \xi: a^*\cs{L} \to p^*\cs{L},
-\]
- so $(\cs{L}, \mu, \nu_\xi)$ is a $G$-equivariant commutative character sheaf.
-
- forgetful  rule $(\cs{L},\mu)\to (\cs{L},\mu,\nu_\xi)$ and 
-To define the promised adjunction, I need to modify the functors slighlty . . . 
-\todo{This proof is under construction.}
-\end{proof}
-
-\begin{remark}
-Lemma~\ref{lem:equivariant} shows that the `canonical functor' $\CCS(G) \to \CS(G)$ is a forgetful functor and also provides an alternate characterization of commutative character sheaves as linear (rank-$1$), multiplicative ($\mu$) and conjugation-equivariant ($\nu$) Weil local systems ($\phi$) on $\bG$.
-[Is this correct?]
-\end{remark}
-
-\subsection{Descent along torsors}
-
-Let $G$ be a $k$-group scheme and let $H \to G$ be a closed subgroup scheme over $S$.
-
-We now suppose that $H$ is normal in $G$ and that the fppf-quotient $G \to G'\ceq H\backslash G$ exists in group schemes over $\Fq$.
-Then $q : G \to G'$ is a regular epimorphism with kernel pair $(n,p)$ in the category of schemes.
+Now suppose $q : G \to G'$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
 \[
@@
 H\times G
- \arrow{r}[shift left]{n}
-  \arrow{r}[shift right,swap]{p}
+ \arrow[shift left]{r}{a}
+  \arrow[shift right,swap]{r}{p}
 &
@@
 \]
-
-Let $j : H \hookrightarrow G$ be the kernel of $q : G \to G'$ and let $m : G\times G \to G$ be multiplication for $G$. 
-Write $n : H \times_S G \to G$ for the left action of $H$ on $G$; this is obtained by restricting the action $m : G\times G\to G$ to the subgroup $H\times G$. 
-Let $n : H \times G \to G$ be the restriction of $m: G\times G \to G$.
-Then $n = m \circ (j \times \id)$, so
-
- let $p : H\times_S G \to G$ be projection.
-
-%In particular, $G \times_{G'} G \iso H\times_S G'$, so $G \to G'$ is a $G$-torsor in the fppf topology.
-In this case we may factor the functor $\CCS(G') \to \CCS(G)$  . . . 
+Let $\cs{L}'$ be a linear character sheaf on $G'$.
+Consider the functor
+\[
+q^* : \CS(G') \to \CS(G)
+\]
+given on objects by $(\cs{L}',\mu') \mapsto (q^*\cs{L}', (q\times q)^* \mu', \nu_{\cs{L}'})$; cf [Dictionary].
+Then $q^*\cs{L}'$ is an $H$-equivariant linear character sheaf on $G$ when equipped with the canonical isomorphism
+\[
+\nu_{\cs{L}'} : a^* q^* \cs{L}' \mathop{\longrightarrow}\limits^{\iso} (q\circ a)^* \cs{L}' = (q\circ p)^*\cs{L}' \mathop{\longrightarrow}\limits^{\iso} p^* q^*\cs{L}.
+\]
+This simple observation shows that the functor $q^* : \CS(G') \to \CS(G)$  factors according to the following commuting diagram of functors
 \[
 \begin{tikzcd}
-\CCS(G) &&\arrow{ll}[swap]{q^*} 
-\CCS(G') \arrow{dl}{\text{`comparison'}}\\
-& \arrow{ul}{\text{forget}} \CCS_{H}(G) & 
+\CS(G) &&\arrow{ll}[swap]{q^*} 
+\CS(G') \arrow{dl}{\text{`comparison'}}\\
+& \arrow{ul}{\text{forget}} \CS_{H}(G). & 
 \end{tikzcd}
@@
 
-\begin{lemma}\label{lem:descent}
-The comparison functor $\CCS(G') \to \CCS_{H}(G)$ is an equivalence.
+\begin{lemma}
+If $q : G \to G'$ is an $H$-torsor in the fppf topology then the comparison functor $\CS(G') \to \CS_H(G)$ is an equivalence.
 \end{lemma}
@@
 \begin{proof}
-By descent theory, the functor $\Loc(G') \to \Loc_H(G)$ induced by $q: G \to G'$ is an equivalence of categories. Expand . . . 
-\todo{Need to study the extra structure coming with character sheaves.}
+. . . 
+So the lemma reduces to the claim: the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence. 
+To see this, observe first that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
+Moreover, if $Y \to X$ is a flat surjective morphism of affine schemes over $\Fq$, then the comparison functor $\Loc(X) \to \Loc(Y\to X)$ is an equivalence, with $\Loc(Y\to X)$ defined as in [].
+It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fppf topology.
+(This is a small variation on the proof of the fact that quasicoherent sheaves form a stack on sheaves in the fppf topology.)
+Since $q : G\to G'$ is an $H$-torsor in the fppf topology, is now follows immediately that the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence.
+\end{proof}
 
-%Let $j : C \hookrightarrow G$ be the kernel of $q : G \to G\ab$ and let $m : G\times G \to G$ be multiplication for $G$. 
-Let $n : H \times G \to G$ be the restriction of $m: G\times G \to G$.
-Then $n = m \circ (j \times \id)$, so
-\begin{align*}
-n^* \cs{L} 
-&= (m \circ (j \times \id))^* \cs{L}\\
-&= (j \times \id))^* m^*\cs{L}\\
-&\iso (j \times \id))^* (\cs{L} \boxtimes \cs{L})\\
-&= (j^*\cs{L}) \boxtimes \cs{L}\\
-&= (\cs{L}\vert_C) \boxtimes \cs{L}\\
-&= (\EE)_C \boxtimes \cs{L}\\
-&= p^* \cs{L};
-\end{align*}
-the isomorphism above is 
+\subsection{Forget}
+
+In this section we find a subcategory $\CS'(G)$ of $\CS(G)$ such that the forgetful functor $\CS_H(G) \to \CS(G)$ induces an equivalence $\CS_H(G) \to \CS'(G)$, in the case required to prove Proposition~1.2.
+
+Suppose there is some $H\times G\to G\times G$ such that the following diagram commutes.
 \[
-\nu_\mu \ceq(j \times \id))^* \mu: n^*\cs{L} \to p^*\cs{L}.
+\begin{tikzcd}
+&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
+G & & G \\
+& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p} & 
+\end{tikzcd}
 \]
-Thus, every commutative character sheaf $\cs{L}$ on $G$ is $H$-equivariant.
-It now follows from Lemma~\ref{lem:Lder} that the forgetful functor $\CCS_{G\der}(G) \to \CCS(G)$ is an equivalence. 
+Then $f_1 : H\times G \to G$ and $f_0 : H \to G$ . . .
+
+\begin{lemma}
+If $f: H\times G \to G$ exists as above and $f_1$ is proper, then the forgetful functor $\CS_H(G) \to \CS(G)$ is full and faithful, with essential image
+$\CS'(G)$ consisting of those $(\cs{L},\mu,\nu) \in \CS_H(G)$ such that $f_0^*\cs{L} \iso (\EE)_{H}$. 
+\end{lemma}
+
+\begin{proof}
 \end{proof}
+
+\subsection{Proof of Proposition~1.2}
+
+We now consider a special case of the lemmas above. 
+Suppose $H = G$ and the action $a$ is $m: G\times G\to G$.
+Suppose $H' = G\der$ and let $a'$, be the restriction of $m$ to $G\der\times G$.
+Let $d : G\der \hookrightarrow G$ and set $k(h,g) = d(h)$. 
+Then $f : G\der \times G\to G\times G$ is simply the inclusion.
+
+As we have seen above, the fppf quotient $q : G\to G\ab = G/G\der$ exists in schemes and is a $G\der$-torsor in the fppf topology. 
+%(In fact, it's a trivial torsor in that topology.)
+It follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
+On the other hand, by Lemma~[], the forgetful functor $\CS_{G\der}(G)\to \CS(G)$ defines an equivalence $\CS_{G\der}(G)\to \CS'(G)$, where $\CS'(G)$ is the category of $(\cs{L},\mu,\nu)\in \CS_{G\der}(G)$ such that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
+It now follows that $q^* : \CS(G\ab) \to \CS(G)$ is fll and faithful with essential image $\CS'(G)$.
+This concludes the proof of Proposition~1.2.
+
+\subsection{Commutative character sheaves}
+
+Move this statement to Section 1?
+
+\begin{theorem}\label{thm:Gab}
+Pull-back along the abelianization $q : G \to G\ab$
+\[
+q^* : \CCS(G\ab) \to \CCS(G)
+\]
+is an equivalence of categories.
+\end{theorem}
+
+\begin{proof}
+Combining Lemmas~[] and [] we see that $q^* : \CS(G\ab) \to \CS(G)$ is full and faithful.
+% with essential image $\CS'(G)$, the category of linear character sheaves $\cs{L}$ on $G$ for which $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$. 
+By Definition~[], this induces an equivalence between $\CCS(G\ab)$ and $\CCS(G)$. 
+\end{proof}
+
+\subsection{Proof of Proposition~1.4}
+
+\iffalse
 
@@
 
+Now, let $a' : H'\times G \to G$ be another group action on $G$ and suppose $f: H \times G \to H'\times G$ makes the following diagram commute.
 \[
 \begin{tikzcd}
-\arrow{dd}[swap]{f} G_1 \times G \arrow{dr}[swap]{a_1}{p} & \\
-& G \\
-G_2 \times G \arrow{ur}{a_2}[swap]{p} & 
+&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
+G & & G \\
+& \arrow{ul}{a'} H' \times G \arrow{ur}[swap]{p} & 
 \end{tikzcd}
 \]
+Then pull-back along $f: H\times G \to H'\times G$ defines a monoidal functor 
+\[
+\CS_{H'}(G) \to \CS_{H}(G).
+\]
+
+Then $f : H\times G \to H'\times G$ is given by $f(h,g) = (k(h,g),g)$ for some $k : H\times G\to H'$. 
+Define $d : H\to H'$ by $d(h) = k(h,1)$.
 
@@
 \[
-\CS_{G_2}(G) \to \CS_{G_1}(G)
+\CS_{H}(G) \to \CS_{H'}(G)
 \]
-is an equivalence if $f$ is dominant and  smooth of relative dimension on the connected components in its image.
+is an equivalence if ...
 \end{lemma}
@@
 
-\subsection{Proof of the main result}
+\subsection{Conjugation}
 
-\begin{proof}[Proof of Theorem~\ref{thm:Gab}]
-First we must see that $q^*$ factors according to . . . 
-\[
-\begin{tikzcd}
- \CCS(G)  &&& \arrow{lll}[swap]{q^*}  \CCS(G\ab) \arrow{d}{\text{Lem~\ref{lem:descent}}} \\
-\CCS_G(G)  \arrow{u}{\text{Lem~\ref{lem:equivariant}}} &&& \arrow{lll}{\text{Lem~\ref{lem:action}}} \CCS_{G\der}(G) 
-\end{tikzcd}
-\]
-\end{proof}
+We close this section with an alternate characterization of $\CS'(G)$, the category of linear character sheaves $\cs{L}$ on $G$ for which $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
+Recall that $\CS'(G)$ is a full subcategory of $\CS(G)$ and that $\CCS(G)$ is a full subcategory of $\CS'(G)$.
 
-\begin{lemma}\label{lem:Lder}
-If $\cs{L}\in \CCS(G)$ then $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
-% Suppose Z(G) = 1$. If $\cs{L}\in \CS(G)$ and $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ then $\cs{L}\in \CCS(G)$. 
-\end{lemma}
+Consider the following case of Section~\ref{ssec:action}.
 
-\begin{proof}
-By construction, $c : G \times G \to G\der$ is dominant. 
-Note that $j\circ c = m\circ (m \times (\iota\circ m\op)) : G \times G \to G$ is $(g,h) \mapsto gh g^{-1}h^{-1}$ while $m\op\circ (m \times (\iota\circ m\op))= e : G \times G \to G$ is $(g,h) \mapsto 1_G$.
-Pick $\cs{L}\in \CCS(G)$. 
-Then
-\begin{align*}
-c^* (\cs{L}\vert_{G\der})
-&=  (j\circ c)^*\cs{L} \\
-&= (m\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
-&= (m \times (\iota\circ m\op))^* m^* \cs{L} \\
-&\iso (m \times (\iota\circ m\op))^* m\op^* \cs{L} \\
-&= (m\op\circ (m \times (\iota\circ m\op)))^* \cs{L} \\
-&= e^* \cs{L}\\
-&= (\EE)_{G\times G}.
-\end{align*}
-Since $c : G \times G \to G\der$ is schematically dense, $c^* (\cs{L}\vert_{G\der}) \iso (\EE)_{G\times G}$ implies $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ by Lemma~\ref{lem:dominant}.
-\todo{broken reference}
-
-%Now, suppose $Z(G) =1$. Pick $\cs{L}\in \CS(G)$ and suppose $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
-\end{proof}
+\fi
 

### 2015-11-03 followup.tex
Corrections to the essential image of the forgetful functor CS_H(G) --> CS(G).

@@
 
-Suppose there is some $H\times G\to G\times G$ such that the following diagram commutes.
+Suppose there is some $f : H\times G\to G\times G$ such that the following diagram commutes.
 \[
@@
 \]
-Then $f_1 : H\times G \to G$ and $f_0 : H \to G$ . . .
+Then $f(h,g) = (f_1(h,g),p)$ for $f_1 : H\times G \to G$.
+Let $\CS'(G)$ be the full subcategory of $\CS(G)$ consisting of those $(\cs{L},\mu,\nu) \in \CS_H(G)$ such that $f_1^*\cs{L} \iso (\EE)_{H\times G}$.
 
 \begin{lemma}
-If $f: H\times G \to G$ exists as above and $f_1$ is proper, then the forgetful functor $\CS_H(G) \to \CS(G)$ is full and faithful, with essential image
-$\CS'(G)$ consisting of those $(\cs{L},\mu,\nu) \in \CS_H(G)$ such that $f_0^*\cs{L} \iso (\EE)_{H}$. 
-\end{lemma}
+The forgetful functor $\CS_H(G) \to \CS(G)$ is full and faithful with essential image $\CS'(G)$.\end{lemma}
 
@@
 We now consider a special case of the lemmas above. 
-Suppose $H = G$ and the action $a$ is $m: G\times G\to G$.
-Suppose $H' = G\der$ and let $a'$, be the restriction of $m$ to $G\der\times G$.
-Let $d : G\der \hookrightarrow G$ and set $k(h,g) = d(h)$. 
-Then $f : G\der \times G\to G\times G$ is simply the inclusion.
+Suppose $H = G\der$ and the action $a$ is the restriction of $m$ to $G\der\times G$.
+Then $f : G\der \times G\to G\times G$ is simply the inclusion and $f_1: G\der\times G \to G$ is projection to the first coordinate followed by inclusion $G\der \hookrightarrow G$.
 

### 2015-11-03 followup.tex
Working on later sections

--- 2015-10-27 followup.tex
@@
 \end{proposition}
+
+%\todo{I got this wrong.
+I think our sheaves are not extra information in the commutative case.
+Masound's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case.
+So, I think the modification is easy: add mop to diagram 2.4 in Masoud's paper.
+\\ -CC}
 
@@
 
-\section{Geometrization of linear characters}
+\section{Applications to supercuspidal representations}
 
- \begin{corollary}
- If $\Hh^1(\Fq,G\der)=0$ then
-the following diagram of isomorphisms commutes.
+\subsection{Linear Characters}
+
+For non-commutative $G$, we aim to model homomorphisms from $G(k)$ to $\EEx$ using the category $\CCS(G)$.
+The precise nature of the relationship between $G(k)^*$ and $\CCSiso{G}$ is described by Galois cohomology.
+Let $\Delta$ be the image of the boundary homomorphism $\delta$ in the sequence
 \[
-\begin{tikzcd}
-\CCSiso{G} \arrow{r} & G(\Fq)^*\\
-\arrow{u}{q^*} \CCSiso{G\ab} \arrow{r} & \arrow{u} G\ab(\Fq)^* 
-\end{tikzcd}
+1 \to G\der(k) \to G(k) \to G\ab(k) \xrightarrow{\delta} \Hh^1(k, G\der),
 \]
- \end{corollary}
+yielding a short exact sequence
+\[
+1 \to G(k) / G\der(k) \to G\ab(k) \to \Delta \to 1.
+\]
+Applying $\Hom(-, \EEx)$ and using the fact that every homomorphism $G(k) \to \EEx$ vanishes on $G\der(k)$, we get
+\[
+1 \to \Delta^* \to G\ab(k)^* \to G(k)^* \to 1.
+\]
 
- \begin{proof}
- By Theorem \ref{thm:trfrobiso}, $\CCSiso{G}\to G(\Fq)^*$ and $\CCSiso{G\ab}\to G\ab(\Fq)^*$ are isomorphisms.
-By Theorem~\ref{thm:Gab}, $\CCSiso{G} \iso \CCSiso{G\ab}$.
-Since $\Hh^1(\Fq,G\der)=0$, we have  $G\ab(\Fq) = G(\Fq)/G\der(\Fq)$.
-Thus, all characters of $G(\Fq)$ factor through
- $G\ab(\Fq)$. . . . 
- The isomorphisms are compatible because  . . . 
- \end{proof}
+Combining Theorems \ref{thm:trfrobiso} and \ref{thm:Gab} gives an isomorphism $\CCSiso{G} \to G\ab(k)^*$.
+We may thus ask for a condition on a commutative character sheaf on $G$ that corresponds to having trivial
+trace of Frobenius, with the expectation that the isomorphism classes of such commutative character sheaves
+should be in natural bijection with $\Delta^*$.
 
-\section{Stacky abelianization, revisited}\label{sec:stacky}
+Note that when $\Hh^1(k,G\der) = 0$, as is the case when $G\der(\bFq)$ ``is simply connected,'' then
+we succeed in geometrizing characters of $G(k)$ on the nose.
 
- Talk about relationship with \cite{kamgarpour:09a}.  In particular, explain why the rank-$1$ character sheaf corresponding
- to the cover
- \[
- 1 \to \mu_n \to \SL_n \to \PGL_n \to 1
- \]
- is not commutative.  
- %Explain how our character sheaves are not just representations of a fundamental group (or are they?), but instead have extra data like $\mu$ and $\phi$.
-%\todo{I got this wrong.
-I think our sheaves are not extra information in the commutative case.
-Masound's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case.
-So, I think the modification is easy: add mop to diagram 2.4 in Masoud's paper.
-\\ -CC}
-
-\section{Applications to supercuspidal representations}
+% \begin{corollary}
+% If $\Hh^1(\Fq,G\der)=0$ then
+%the following diagram of isomorphisms commutes.
+%\[
+%\begin{tikzcd}
+%\CCSiso{G} \arrow{r} & G(\Fq)^*\\
+%\arrow{u}{q^*} \CCSiso{G\ab} \arrow{r} & \arrow{u} G\ab(\Fq)^* 
+%\end{tikzcd}
+%\]
+% \end{corollary}
+% 
+% \begin{proof}
+% By Theorem \ref{thm:trfrobiso}, $\CCSiso{G}\to G(\Fq)^*$ and $\CCSiso{G\ab}\to G\ab(\Fq)^*$ are isomorphisms.
+%By Theorem~\ref{thm:Gab}, $\CCSiso{G} \iso \CCSiso{G\ab}$.
+%Since $\Hh^1(\Fq,G\der)=0$, we have  $G\ab(\Fq) = G(\Fq)/G\der(\Fq)$.
+%Thus, all characters of $G(\Fq)$ factor through
+% $G\ab(\Fq)$. . . . 
+% The isomorphisms are compatible because  . . . 
+% \end{proof}
 

### 2015-11-03 followup.tex

--- 2015-11-03 followup.tex
@@
 
+%\todo{I got this wrong.
+I think our sheaves are not extra information in the commutative case.
+Masound's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case.
+So, I think the modification is easy: add mop to diagram 2.4 in Masoud's paper.
+\\ -CC}
+
 \section{Eliminating Invisible Character Sheaves}\label{sec:defect}

### 2015-11-03 followup.tex
Fixing/skipping some tikzcd problems
Formating of equalizer arrows, moving Theorem 1.5 into section 1

@@
 
-\section{Recollections and definitions}
+\section{Recollections and definitions} \label{sec:defs}
 
@@
 The following proposition will be proven in Section \ref{sec:descent}.
-\begin{proposition}
+\begin{proposition} \label{prop:Gder_triv}
 Suppose $G$ is a smooth group scheme and $\cs{L} \in \CS(G)$ is a linear character sheaf on $G$.
@@
 
-\begin{proposition}
+\begin{proposition} \label{prop:Gdiagram}
 A linear character sheaf $(\cs{L}, \mu)$ on a smooth group scheme $G$ is commutative if and only if
@@
 \end{proposition}
+
+\begin{theorem}\label{thm:Gab}
+Pull-back along the abelianization $q : G \to G\ab$
+\[
+q^* : \CCS(G\ab) \to \CCS(G)
+\]
+is an equivalence of categories.
+\end{theorem}
 
@@
 H \times H \times G 
-\arrow[shift left=4]{r}{b_1} 
-\arrow{r}{b_2} 
-\arrow[shift right=4]{r}{b_3} 
+\arrow[shift left=4]{r}{b_1, b_2, b_3} 
+\arrow{r}{}
+\arrow[shift right=4]{r}{} 
 & H \times G 
-\arrow[shift left]{r}{a}
-\arrow[shift right]{r}[swap]{p}
+\arrow[shift left=4]{r}{a}
+\arrow[shift right=4]{r}[swap]{p}
  & G 
@@
 H\times G
- \arrow[shift left]{r}{a}
-  \arrow[shift right,swap]{r}{p}
+ \arrow[shift left=4]{r}{a}
+  \arrow[shift right=4,swap]{r}{p}
 &
@@
 Suppose there is some $f : H\times G\to G\times G$ such that the following diagram commutes.
-\[
-\begin{tikzcd}
-&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
-G & & G \\
-& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p} & 
-\end{tikzcd}
-\]
+%%%%%%%% FIX!!!! %%%%%%%%%%
+%\[
+%\begin{tikzcd}
+%&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
+%G & & G \\
+%& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p} & 
+%\end{tikzcd}
+%\]
 Then $f(h,g) = (f_1(h,g),p)$ for $f_1 : H\times G \to G$.
@@
 
-\subsection{Proof of Proposition~1.2}
+\subsection{Proofs}
 
+We can now give the missing proofs from Section \ref{sec:defs}.
+
+\begin{proof}[Proof of Proposition~\ref{prop:Gder_triv}]
 We now consider a special case of the lemmas above. 
@@
 It now follows that $q^* : \CS(G\ab) \to \CS(G)$ is fll and faithful with essential image $\CS'(G)$.
-This concludes the proof of Proposition~1.2.
+\end{proof}
 
-\subsection{Commutative character sheaves}
+\begin{proof}[Proof of Proposition~\ref{prop:Gdiagram}]
 
-Move this statement to Section 1?
+\end{proof}
 
-\begin{theorem}\label{thm:Gab}
-Pull-back along the abelianization $q : G \to G\ab$
-\[
-q^* : \CCS(G\ab) \to \CCS(G)
-\]
-is an equivalence of categories.
-\end{theorem}
-
-\begin{proof}
+\begin{proof}[Proof of Theorem~\ref{thm:Gab}]
 Combining Lemmas~[] and [] we see that $q^* : \CS(G\ab) \to \CS(G)$ is full and faithful.
@@
 \end{proof}
-
-\subsection{Proof of Proposition~1.4}
 

### 2015-11-03 followup.tex
Minor changes/commit to move to uni

@@
 We recall some facts about the abelianization of a smooth group scheme $G$.
-Let $G\der \hookrightarrow G$ denote the closed subgroup generated by the smooth morphism
-$G\times G \to G$ given by $c: (x,y)\mapsto xyx^{-1}y^{-1}$. Then
-$G \times G \to G\der$ is a dominant morphism \cite{SGA3}*{Expos\'e {VI}$_B$, \S 7.2}.
-Moreover, $G$ is commutative if and only if $G\der$ is trivial.
+Let $G\der \hookrightarrow G$ denote the closed subgroup generated by the family of smooth morphisms
+$c_n: (G\times G)^n \to G$ given by $c_1: (x,y)\mapsto xyx^{-1}y^{-1}$ and ...
+%Then $G \times G \to G\der$ is a dominant morphism \cite{SGA3}*{Expos\'e {VI}$_B$, \S 7.2}.
+The group scheme $G$ is commutative if and only if $G\der$ is trivial.
 When $G$ is not connected, $G\der$ need not be connected, though it is smooth.
-The restriction of $G\times G\to G\der$ to identity components gives a dominant
-morphism $G^0\times G^0 \to G^0\der$ \cite{SGA3}*{Expos\'e {VI}$_B$, Prop. 7.8}.
+%The restriction of $G\times G\to G\der$ to identity components gives a dominant morphism $G^0\times G^0 \to G^0\der$ \cite{SGA3}*{Expos\'e {VI}$_B$, Prop. 7.8}.
 
-The quotient $G\ab\ceq G/G\der$ exists in schemes over $\Fq$, and the quotient $q : G \to G\ab$
-is faithfully flat and a $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
+The quotient $G\ab\ceq G/G\der$ exists in schemes over $\Fq$.
+%and the quotient $q : G \to G\ab$ is faithfully flat and a $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
 We summarize the setup in a diagram.
@@
 & H \times G 
-\arrow[shift left=4]{r}{a}
-\arrow[shift right=4]{r}[swap]{p}
+\arrow[shift left=2]{r}{a}
+\arrow[shift right=2]{r}[swap]{p}
  & G 
@@
 An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense. 
-Consider the morphisms $c_1 : H \times G\times G \to G\times G$, $c_2 : H \times G\times G \to H\times G$ and $c_3 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),a(h,g_2))$ and $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$ and $c_3(h, g_1, g_2) = (g_1, g_2)$.
+Consider the following morphisms: $c_0 : H\times G \times G\to H\times G \times H \times G$ defined by $c_0(h,g_1,g_2)\ceq(h,g_1,h,g_2)$;
+$c_1 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),a(h,g_2))$;  $c_2 : H \times G\times G \to H\times G$ defined by $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$; and $c_3 : H \times G\times G \to G\times G$ defined by $c_3(h, g_1, g_2) = (g_1, g_2)$.
 Then $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ if $(\cs{L},\mu)$ is a linear character sheaf on $G$ and the following diagram of Weil local systems on $H \times G\times G$ commutes.
@@
 \arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} & \arrow{l}[swap]{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{r}{p\circ c_2 = m\circ c_3}  & c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
-c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{r} & (p^*\cs{L}) \boxtimes (p^*\cs{L}) & \arrow{l}[swap]{\nu\boxtimes \nu}  (a^*\cs{L}) \boxtimes (a^*\cs{L}) & \arrow{l} c_3^*(\cs{L}\boxtimes \cs{L})
+c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_i\circ c_1 = a\circ p_i\circ c_0} & c_0^*(a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{c_0^*(\nu\boxtimes \nu)} & c_0^*(p^*\cs{L} \boxtimes p^*\cs{L}) & \arrow{l}[swap]{p\circ p_i\circ c_0 = p_i \circ c_3}c_3^*(\cs{L}\boxtimes \cs{L})
 \end{tikzcd}
 \]
-In this diagram, the arrows not labeled are derived from canonical isomorphisms.
+%In this diagram, the arrows not labeled are derived from canonical isomorphisms.
 \iffalse
@@
 H\times G
- \arrow[shift left=4]{r}{a}
-  \arrow[shift right=4,swap]{r}{p}
+ \arrow[shift left=2]{r}{a}
+  \arrow[shift right=2,swap]{r}{p}
 &
@@
 (This is a small variation on the proof of the fact that quasicoherent sheaves form a stack on sheaves in the fppf topology.)
-Since $q : G\to G'$ is an $H$-torsor in the fppf topology, is now follows immediately that the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence.
+Since $q : G\to G'$ is an $H$-torsor in the fppf topology, is now follows from descent theory that the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence.
 \end{proof}
@@
 %%%%%%%% FIX!!!! %%%%%%%%%%
-%\[
-%\begin{tikzcd}
-%&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
-%G & & G \\
-%& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p} & 
-%\end{tikzcd}
-%\]
+\[
+\begin{tikzcd}
+\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
+G & & G \\
+& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p} & 
+\end{tikzcd}
+\]
 Then $f(h,g) = (f_1(h,g),p)$ for $f_1 : H\times G \to G$.
@@
 
-As we have seen above, the fppf quotient $q : G\to G\ab = G/G\der$ exists in schemes and is a $G\der$-torsor in the fppf topology. 
+As we have seen above, the fppf quotient $q : G\to G\ab = G/G\der$ exists in schemes.
+Moreover, the quotient $q : G \to G\ab$ is faithfully flat and a $G\der$-torsor in the fppf topology, by\cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}
 %(In fact, it's a trivial torsor in that topology.)
-It follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
+It now follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
 On the other hand, by Lemma~[], the forgetful functor $\CS_{G\der}(G)\to \CS(G)$ defines an equivalence $\CS_{G\der}(G)\to \CS'(G)$, where $\CS'(G)$ is the category of $(\cs{L},\mu,\nu)\in \CS_{G\der}(G)$ such that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.

### 2015-11-04 followup.tex
Added stalks. Still working on Forget.
Added beta

@@
 In this section we use descent along the abelianization $q : G \to G\ab$ to prove Propositions~1.2 and 1.4, and Theorem~\ref{thm:Gab}.
+This approach requires introducing equivariant linear character sheaves, as defined in Section~[].
 
@@
 %In this diagram, the arrows not labeled are derived from canonical isomorphisms.
-\iffalse
+%\iffalse
 On stalks, this condition is
@@
 \begin{tikzcd}
-\ &  \cs{L}_{h\cdot (xy)} \arrow{r}{} & \cs{L}_{xy} & \\
-\cs{L}_{(h\cdot x)(h\cdot y)} \arrow{dr}[swap]{} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{} \cs{L}_{xy} \\
-& \cs{L}_{h\cdot x}\otimes \cs{L}_{h\cdot y} \arrow{r} & \cs{L}_x\otimes \cs{L}_y & 
+\arrow{d}[swap]{\mu_{(h\cdot g_1, h\cdot g_2)}} \cs{L}_{(h\cdot g_1)(h\cdot g_2)} & \arrow[equal]{l}  \cs{L}_{h\cdot(g_1 g_2)} \arrow{r}{\nu_{(h, g_2 g_2)}} & \cs{L}_{g_1 g_2} \arrow[equal]{r} & \cs{L}_{g_1 g_2} \arrow{d}{\mu_{(g_1,g_2)}} \\
+\cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow[equal]{r} & \cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow{r}{\nu_{(h,g_1)}\otimes \nu_{(h,g_2)}} & \cs{L}_{g_1}\otimes \cs{L}_{g_2} & \arrow[equal]{l} \cs{L}_{g_1} \otimes \cs{L}_{g_2},
 \end{tikzcd}
 \]
-\fi
+for all $(h,g_1,g_2)\in H\times G\times G$.
+%\fi
 %
@@
 Is $\CS_H(G)$ a rigid monoidal category?
+
+If $(\cs{L},\mu,\nu)$ and $(\cs{L},\mu,\nu')$ in $\CS_H(G)$, then $\nu = \nu'$?
 
@@
 
-In this section we find a subcategory $\CS'(G)$ of $\CS(G)$ such that the forgetful functor $\CS_H(G) \to \CS(G)$ induces an equivalence $\CS_H(G) \to \CS'(G)$, in the case required to prove Proposition~1.2.
+In this section we consider a different perspective on $\CS_H(G)$ of $\CS(G)$ which will help us understand how the forgetful functor $\CS_H(G) \to \CS(G)$ induces an equivalence $\CS_H(G) \to \CS'(G)$, in the case required to prove Proposition~1.2.
 
@@
 \]
-Then $f(h,g) = (f_1(h,g),p)$ for $f_1 : H\times G \to G$.
+Then $f(h,g) = (a(h,g) g^{-1}, g)$.
+Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq a(h,g) g^{-1}$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
+
+Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ defines an isomorphism $\beta : f_1^*\cs{L} \to (\EE)_{H\times G}$ by $\beta \boxtimes \id = \nu \circ f^*(\mu)^{-1}$ from which $\nu$ may be recovered.
+In this way we see we may replace $(\cs{L},\mu,\nu)$ with another triple, $(\cs{L},\mu,\beta)$.
+What are the defining properties of $\beta$?
+
+Now,
+
 Let $\CS'(G)$ be the full subcategory of $\CS(G)$ consisting of those $(\cs{L},\mu,\nu) \in \CS_H(G)$ such that $f_1^*\cs{L} \iso (\EE)_{H\times G}$.

### 2015-11-05 followup.tex
Properties of beta, then special case.

@@
 \iffalse
-We remark that, on stalks, this condition is ...
+On stalks, this condition is ...
 \[
 \begin{tikzcd}
-\ &  \cs{L}_{x\cdot(y\cdot z)} \arrow{r}{\nu_{x,y\cdot z}} & \cs{L}_{y\cdot z} & \\
-\cs{L}_{(x\cdot y)\cdot z} \arrow{dr}[swap]{\nu_{x\cdot y,z}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{y,z}} \cs{L}_{y\cdot z} \\
-& \cs{L}_z \arrow[equal]{r} & \cs{L}_z & 
+\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
+\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
+& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
 \end{tikzcd}
@@
 \fi
-%
 Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
@@
 Consider the following morphisms: $c_0 : H\times G \times G\to H\times G \times H \times G$ defined by $c_0(h,g_1,g_2)\ceq(h,g_1,h,g_2)$;
-$c_1 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),a(h,g_2))$;  $c_2 : H \times G\times G \to H\times G$ defined by $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$; and $c_3 : H \times G\times G \to G\times G$ defined by $c_3(h, g_1, g_2) = (g_1, g_2)$.
+$c_1 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),g_2)$;  $c_2 : H \times G\times G \to H\times G$ defined by $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$; and $c_3 : H \times G\times G \to G\times G$ defined by $c_3(h, g_1, g_2) = (g_1, g_2)$.
 Then $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ if $(\cs{L},\mu)$ is a linear character sheaf on $G$ and the following diagram of Weil local systems on $H \times G\times G$ commutes.
@@
 \]
+\todo{Check this.}
 %In this diagram, the arrows not labeled are derived from canonical isomorphisms.
-%\iffalse
+\iffalse
 On stalks, this condition is
@@
 for all $(h,g_1,g_2)\in H\times G\times G$.
-%\fi
-%
+\fi
+
 A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves, so
@@
 
-\subsection{Forget}
-
-In this section we consider a different perspective on $\CS_H(G)$ of $\CS(G)$ which will help us understand how the forgetful functor $\CS_H(G) \to \CS(G)$ induces an equivalence $\CS_H(G) \to \CS'(G)$, in the case required to prove Proposition~1.2.
+\subsection{Change of action/perspective}
 
@@
 G & & G \\
-& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p} & 
+& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
 \end{tikzcd}
@@
 
-Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ defines an isomorphism $\beta : f_1^*\cs{L} \to (\EE)_{H\times G}$ by $\beta \boxtimes \id = \nu \circ f^*(\mu)^{-1}$ from which $\nu$ may be recovered.
-In this way we see we may replace $(\cs{L},\mu,\nu)$ with another triple, $(\cs{L},\mu,\beta)$.
-What are the defining properties of $\beta$?
+Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
+\[
+\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}
+\]
+by $\beta \otimes \id_{p^*\cs{L}} = \nu \circ f^*(\mu)^{-1}$, or more precisely, by the following diagram of isomorphisms,
+\[
+\begin{tikzcd}
+a^*\cs{L} \arrow{d}{m\circ f = a} \arrow{rrr}{\nu}
+&&& p^*\cs{L}\\
+f^* m^*\cs{L} \arrow{r}{f^*\mu} & 
+f^*(\cs{L}\boxtimes \cs{L}) \arrow{d} & 
+f_1^*\cs{L} \otimes p^*\cs{L} \arrow{r}{\beta\otimes \id_{p^*\cs{L}}} & 
+(\EE)_{H\times G} \otimes p^*\cs{L} \arrow{u} \\
+& f^*(p_1^*\cs{L}\otimes p_2^*\cs{L}) \arrow{r} & f^*p_1^*\cs{L}\otimes f^* p_2^*\cs{L} \arrow{u}{f_1 = p_1\circ f}[swap]{p = p_2\circ f} &
+\end{tikzcd}
+\]
+In this way we see we may replace $(\cs{L},\mu,\nu)$ with an alternate triple, $(\cs{L},\mu,\beta_1)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
+The isomorphism $\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}$ is constrained by two properties, corresponding to the diagrams in Sections [] and [].
 
-Now,
+\subsection{Forget}
 
-Let $\CS'(G)$ be the full subcategory of $\CS(G)$ consisting of those $(\cs{L},\mu,\nu) \in \CS_H(G)$ such that $f_1^*\cs{L} \iso (\EE)_{H\times G}$.
+Let us know specialize Section [] to the following case: $H = G\der$ and the action $a$ is the restriction of $m$ to $G\der\times G$.
+Then $f : G\der \times G\to G\times G$ is simply the inclusion and $f_1: G\der\times G \to G$ is projection to the first coordinate followed by inclusion $G\der \hookrightarrow G$, so $f_1^*\cs{L} = \cs{L}\vert_{G\der} \boxtimes (\EE)_G$.
+Then $\beta : f_1^*\cs{L} \to (\EE)_{H\times G}$ determines an isomorphism $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$, and vice versa.
+
+\todo{Under construction}
 

### 2015-11-09 followup.tex
Commit for conversation with David

@@
 Consider the following morphisms: $c_0 : H\times G \times G\to H\times G \times H \times G$ defined by $c_0(h,g_1,g_2)\ceq(h,g_1,h,g_2)$;
-$c_1 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),g_2)$;  $c_2 : H \times G\times G \to H\times G$ defined by $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$; and $c_3 : H \times G\times G \to G\times G$ defined by $c_3(h, g_1, g_2) = (g_1, g_2)$.
+$c_1 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),a(h,g_2))$;  $c_2 : H \times G\times G \to H\times G$ defined by $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$; and $c_3 : H \times G\times G \to G\times G$ defined by $c_3(h, g_1, g_2) = (g_1, g_2)$.
 Then $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ if $(\cs{L},\mu)$ is a linear character sheaf on $G$ and the following diagram of Weil local systems on $H \times G\times G$ commutes.
@@
 \]
-\todo{Check this.}
-%In this diagram, the arrows not labeled are derived from canonical isomorphisms.
 \iffalse
@@
 \begin{tikzcd}
-\CS(G) &&\arrow{ll}[swap]{q^*} 
+\CS(G) &\arrow{l}[swap]{q^*} 
 \CS(G') \arrow{dl}{\text{`comparison'}}\\
-& \arrow{ul}{\text{forget}} \CS_{H}(G). & 
+\arrow{u}{\text{forget}} \CS_{H}(G). & 
 \end{tikzcd}
@@
 
-\subsection{Forget}
+\subsection{Quotient and restriction}
 
-Let us know specialize Section [] to the following case: $H = G\der$ and the action $a$ is the restriction of $m$ to $G\der\times G$.
-Then $f : G\der \times G\to G\times G$ is simply the inclusion and $f_1: G\der\times G \to G$ is projection to the first coordinate followed by inclusion $G\der \hookrightarrow G$, so $f_1^*\cs{L} = \cs{L}\vert_{G\der} \boxtimes (\EE)_G$.
-Then $\beta : f_1^*\cs{L} \to (\EE)_{H\times G}$ determines an isomorphism $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$, and vice versa.
+We now combine the material of the last two sections, by specializing to the following case: $H$ is a closed subgroup of $G$ and $q : G \to G/H$ is the fppf quotient.
 
-\todo{Under construction}
+\[
+\begin{tikzcd}
+\CS(H) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
+\CS(G/H) \arrow{dl}{\text{`comparison'}} \\
+ & \CS_{H}(G) \arrow{u}{\text{forget}}  & 
+\end{tikzcd}
+\]
 
 \begin{lemma}
-The forgetful functor $\CS_H(G) \to \CS(G)$ is full and faithful with essential image $\CS'(G)$.\end{lemma}
+$\CS(G/H)$ is equivalent to the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$.
+\end{lemma}
 
-\begin{proof}
-\end{proof}
+In this case, the action $a$ is the restriction of $m$ to $H\times G$ and $f : H \times G\to G\times G$ is simply the inclusion and $f_1: H\times G \to G$ is projection to the first coordinate followed by inclusion $H \hookrightarrow G$, so $f_1^*\cs{L} = \cs{L}\vert_{H} \boxtimes (\EE)_G$.
+Then $\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}$ determines an isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$, and vice versa.
+Moreover, in this case, the constraint on $\beta$ is only this: $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is an isomorphism in $\CS(H)$. 
+%Let $\CS^H(G)$ denote the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$.
 
@@
 It now follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
-On the other hand, by Lemma~[], the forgetful functor $\CS_{G\der}(G)\to \CS(G)$ defines an equivalence $\CS_{G\der}(G)\to \CS'(G)$, where $\CS'(G)$ is the category of $(\cs{L},\mu,\nu)\in \CS_{G\der}(G)$ such that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
-It now follows that $q^* : \CS(G\ab) \to \CS(G)$ is fll and faithful with essential image $\CS'(G)$.
+On the other hand, by Lemma~[], the forgetful functor $\CS_{G\der}(G)\to \CS(G)$ defines an equivalence $\CS_{G\der}(G)\to \CS'(G)$, where $\CS'(G)$ is the category of $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ in $\CS(G\der)$.
 \end{proof}
@@
 \begin{proof}[Proof of Theorem~\ref{thm:Gab}] 
-Combining Lemmas~[] and [] we see that $q^* : \CS(G\ab) \to \CS(G)$ is full and faithful.
-% with essential image $\CS'(G)$, the category of linear character sheaves $\cs{L}$ on $G$ for which $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$. 
-By Definition~[], this induces an equivalence between $\CCS(G\ab)$ and $\CCS(G)$. 
 \end{proof}

### 2015-11-09 followup.tex
Working on Section 2

--- 2015-11-04 followup.tex
@@
 We recall some facts about the abelianization of a smooth group scheme $G$.
-Let $G\der \hookrightarrow G$ denote the closed subgroup generated by the family of smooth morphisms
-$c_n: (G\times G)^n \to G$ given by $c_1: (x,y)\mapsto xyx^{-1}y^{-1}$ and ...
-%Then $G \times G \to G\der$ is a dominant morphism \cite{SGA3}*{Expos\'e {VI}$_B$, \S 7.2}.
-The group scheme $G$ is commutative if and only if $G\der$ is trivial.
+Let $G\der \hookrightarrow G$ denote the closed subgroup generated by the smooth morphism
+$G\times G \to G$ given by $c: (x,y)\mapsto xyx^{-1}y^{-1}$. Then
+$G \times G \to G\der$ is a dominant morphism \cite{SGA3}*{Expos\'e {VI}$_B$, \S 7.2}.
+Moreover, $G$ is commutative if and only if $G\der$ is trivial.
 When $G$ is not connected, $G\der$ need not be connected, though it is smooth.
-%The restriction of $G\times G\to G\der$ to identity components gives a dominant morphism $G^0\times G^0 \to G^0\der$ \cite{SGA3}*{Expos\'e {VI}$_B$, Prop. 7.8}.
+The restriction of $G\times G\to G\der$ to identity components gives a dominant
+morphism $G^0\times G^0 \to G^0\der$ \cite{SGA3}*{Expos\'e {VI}$_B$, Prop. 7.8}.
 
-The quotient $G\ab\ceq G/G\der$ exists in schemes over $\Fq$.
-%and the quotient $q : G \to G\ab$ is faithfully flat and a $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
+The quotient $G\ab\ceq G/G\der$ exists in schemes over $\Fq$, and the quotient $q : G \to G\ab$
+is faithfully flat and a $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
 We summarize the setup in a diagram.
@@
 I think our sheaves are not extra information in the commutative case.
-Masound's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case.
+Masoud's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case.
 So, I think the modification is easy: add mop to diagram 2.4 in Masoud's paper.
@@
 \section{Eliminating Invisible Character Sheaves}\label{sec:defect}
+
+In this section we show that trace of Frobenius is an isomorphism for commutative character sheaves on a
+smooth commutative group scheme $G$.  We begin by reinterpreting Definition \ref{def:CCScom} in terms of
+cocycles.
+
+For a character sheaf $\cs{L}$ on $G$, recall from \cite{cunningham-roe:13a}*{\S 2.3} that $S_G : \CSiso{G} \to \Hh^2(E_G^\bullet)$ maps
+$[\cs{L}]$ to $[\alpha \oplus \beta]$, where $E_G^\bullet$ is the total space of the zeroth page
+of the Hochschild-Serre spectral sequence, $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$ is obtained from $\mu$ and
+$\beta \in C^1(\Weil{}, C^1(\bG, \EEx))$ is obtained from $\phi$.
 
@@
 \end{proof}
-
-For a character sheaf $\cs{L}$ on $G$, recall from \cite{cunningham-roe:13a}*{\S 2.3} that $S_G : \CSiso{G} \to \Hh^2(E_G^\bullet)$ maps
-$[\cs{L}]$ to $[\alpha \oplus \beta]$, where $E_G^\bullet$ is the total space of the zeroth page
-of the Hochschild-Serre spectral sequence, $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$ is obtained from $\mu$ and
-$\beta \in C^1(\Weil{}, C^1(\bG, \EEx))$ is obtained from $\phi$.
 
@@
 In this section we use descent along the abelianization $q : G \to G\ab$ to prove Propositions~1.2 and 1.4, and Theorem~\ref{thm:Gab}.
-This approach requires introducing equivariant linear character sheaves, as defined in Section~[].
 
@@
 & H \times G 
-\arrow[shift left=2]{r}{a}
-\arrow[shift right=2]{r}[swap]{p}
+\arrow[shift left=4]{r}{a}
+\arrow[shift right=4]{r}[swap]{p}
  & G 
@@
 An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense. 
-Consider the following morphisms: $c_0 : H\times G \times G\to H\times G \times H \times G$ defined by $c_0(h,g_1,g_2)\ceq(h,g_1,h,g_2)$;
-$c_1 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),a(h,g_2))$;  $c_2 : H \times G\times G \to H\times G$ defined by $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$; and $c_3 : H \times G\times G \to G\times G$ defined by $c_3(h, g_1, g_2) = (g_1, g_2)$.
+Consider the morphisms $c_1 : H \times G\times G \to G\times G$, $c_2 : H \times G\times G \to H\times G$ and $c_3 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),a(h,g_2))$ and $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$ and $c_3(h, g_1, g_2) = (g_1, g_2)$.
 Then $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ if $(\cs{L},\mu)$ is a linear character sheaf on $G$ and the following diagram of Weil local systems on $H \times G\times G$ commutes.
@@
 \arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} & \arrow{l}[swap]{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{r}{p\circ c_2 = m\circ c_3}  & c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
-c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_i\circ c_1 = a\circ p_i\circ c_0} & c_0^*(a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{c_0^*(\nu\boxtimes \nu)} & c_0^*(p^*\cs{L} \boxtimes p^*\cs{L}) & \arrow{l}[swap]{p\circ p_i\circ c_0 = p_i \circ c_3}c_3^*(\cs{L}\boxtimes \cs{L})
+c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{r} & (p^*\cs{L}) \boxtimes (p^*\cs{L}) & \arrow{l}[swap]{\nu\boxtimes \nu}  (a^*\cs{L}) \boxtimes (a^*\cs{L}) & \arrow{l} c_3^*(\cs{L}\boxtimes \cs{L})
 \end{tikzcd}
 \]
-%In this diagram, the arrows not labeled are derived from canonical isomorphisms.
-%\iffalse
+In this diagram, the arrows not labeled are derived from canonical isomorphisms.
+\iffalse
 On stalks, this condition is
@@
 \begin{tikzcd}
-\arrow{d}[swap]{\mu_{(h\cdot g_1, h\cdot g_2)}} \cs{L}_{(h\cdot g_1)(h\cdot g_2)} & \arrow[equal]{l}  \cs{L}_{h\cdot(g_1 g_2)} \arrow{r}{\nu_{(h, g_2 g_2)}} & \cs{L}_{g_1 g_2} \arrow[equal]{r} & \cs{L}_{g_1 g_2} \arrow{d}{\mu_{(g_1,g_2)}} \\
-\cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow[equal]{r} & \cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow{r}{\nu_{(h,g_1)}\otimes \nu_{(h,g_2)}} & \cs{L}_{g_1}\otimes \cs{L}_{g_2} & \arrow[equal]{l} \cs{L}_{g_1} \otimes \cs{L}_{g_2},
+\ &  \cs{L}_{h\cdot (xy)} \arrow{r}{} & \cs{L}_{xy} & \\
+\cs{L}_{(h\cdot x)(h\cdot y)} \arrow{dr}[swap]{} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{} \cs{L}_{xy} \\
+& \cs{L}_{h\cdot x}\otimes \cs{L}_{h\cdot y} \arrow{r} & \cs{L}_x\otimes \cs{L}_y & 
 \end{tikzcd}
 \]
-for all $(h,g_1,g_2)\in H\times G\times G$.
-%\fi
+\fi
 %
@@
 
-If $(\cs{L},\mu,\nu)$ and $(\cs{L},\mu,\nu')$ in $\CS_H(G)$, then $\nu = \nu'$?
-
 \subsection{Descent along a torsor}
@@
 H\times G
- \arrow[shift left=2]{r}{a}
-  \arrow[shift right=2,swap]{r}{p}
+ \arrow[shift left=4]{r}{a}
+  \arrow[shift right=4,swap]{r}{p}
 &
@@
 (This is a small variation on the proof of the fact that quasicoherent sheaves form a stack on sheaves in the fppf topology.)
-Since $q : G\to G'$ is an $H$-torsor in the fppf topology, is now follows from descent theory that the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence.
+Since $q : G\to G'$ is an $H$-torsor in the fppf topology, is now follows immediately that the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence.
 \end{proof}
@@
 
-In this section we consider a different perspective on $\CS_H(G)$ of $\CS(G)$ which will help us understand how the forgetful functor $\CS_H(G) \to \CS(G)$ induces an equivalence $\CS_H(G) \to \CS'(G)$, in the case required to prove Proposition~1.2.
+In this section we find a subcategory $\CS'(G)$ of $\CS(G)$ such that the forgetful functor $\CS_H(G) \to \CS(G)$ induces an equivalence $\CS_H(G) \to \CS'(G)$, in the case required to prove Proposition~1.2.
 
@@
 %%%%%%%% FIX!!!! %%%%%%%%%%
-\[
-\begin{tikzcd}
-\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
-G & & G \\
-& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p} & 
-\end{tikzcd}
-\]
-Then $f(h,g) = (a(h,g) g^{-1}, g)$.
-Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq a(h,g) g^{-1}$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
-
-Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ defines an isomorphism $\beta : f_1^*\cs{L} \to (\EE)_{H\times G}$ by $\beta \boxtimes \id = \nu \circ f^*(\mu)^{-1}$ from which $\nu$ may be recovered.
-In this way we see we may replace $(\cs{L},\mu,\nu)$ with another triple, $(\cs{L},\mu,\beta)$.
-What are the defining properties of $\beta$?
-
-Now,
-
+%\[
+%\begin{tikzcd}
+%&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
+%G & & G \\
+%& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p} & 
+%\end{tikzcd}
+%\]
+Then $f(h,g) = (f_1(h,g),p)$ for $f_1 : H\times G \to G$.
 Let $\CS'(G)$ be the full subcategory of $\CS(G)$ consisting of those $(\cs{L},\mu,\nu) \in \CS_H(G)$ such that $f_1^*\cs{L} \iso (\EE)_{H\times G}$.
@@
 
-As we have seen above, the fppf quotient $q : G\to G\ab = G/G\der$ exists in schemes.
-Moreover, the quotient $q : G \to G\ab$ is faithfully flat and a $G\der$-torsor in the fppf topology, by\cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}
+As we have seen above, the fppf quotient $q : G\to G\ab = G/G\der$ exists in schemes and is a $G\der$-torsor in the fppf topology. 
 %(In fact, it's a trivial torsor in that topology.)
-It now follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
+It follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
 On the other hand, by Lemma~[], the forgetful functor $\CS_{G\der}(G)\to \CS(G)$ defines an equivalence $\CS_{G\der}(G)\to \CS'(G)$, where $\CS'(G)$ is the category of $(\cs{L},\mu,\nu)\in \CS_{G\der}(G)$ such that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.

### 2015-11-09 followup.tex
Added morphisms to (L,mu,beta). Not much else.

--- 2015-11-09 followup.tex
@@
 \]
-by $\beta \otimes \id_{p^*\cs{L}} = \nu \circ f^*(\mu)^{-1}$, or more precisely, by the following diagram of isomorphisms,
+by $\beta \otimes \id_{p^*\cs{L}} = \nu \circ f^*\mu^{-1}$, or more precisely, by the following diagram of isomorphisms,
 \[
@@
 \begin{lemma}
-$\CS(G/H)$ is equivalent to the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$.
+$\CS(G/H)$ is equivalent to the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$, with morphisms $\alpha : (\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ defined by the condition
+$\alpha : (\cs{L},\mu) \to (\cs{L}',\mu')$ is a morphism in $\CS(G)$ and $\beta = \beta' \circ \alpha\vert_{H}$.
 \end{lemma}

### 2015-11-10 followup.tex
Added new definition of CCS(G) and made some other changes to Section 1.

@@
 
+\todo{Add some remarks and/or promise examples showing that $\CCS(G)$ need not be $\CS(G)$, even in the Abelian case.}
+I'm wondering about the structure of the paper. 
+Would it make sense to really explore the Abelian case, before moving to the non-Abelian case?
+That would mean moving the material from Section~Invisible up to here.
+
 \subsection{Commutative character sheaves on non-commutative groups}
@@
 
-We recall some facts about the abelianization of a smooth group scheme $G$.
-Let $G\der \hookrightarrow G$ denote the closed subgroup generated by the family of smooth morphisms
+\iffalse
+In order to define the category of commutative character sheaves on $G$ in this generality, we need to review ... 
+Let $G\der \hookrightarrow G$ be the derived subgroup scheme.
+We recall that this closed normal subgroup scheme is generated by a family of smooth morphisms
 $c_n: (G\times G)^n \to G$ given by $c_1: (x,y)\mapsto xyx^{-1}y^{-1}$ and ...
@@
 %The restriction of $G\times G\to G\der$ to identity components gives a dominant morphism $G^0\times G^0 \to G^0\der$ \cite{SGA3}*{Expos\'e {VI}$_B$, Prop. 7.8}.
-
-The quotient $G\ab\ceq G/G\der$ exists in schemes over $\Fq$.
-%and the quotient $q : G \to G\ab$ is faithfully flat and a $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
-We summarize the setup in a diagram.
-\[
-\begin{tikzcd}
-{} & G\times G \arrow{d}{c} &&&\\
-1 \arrow{r} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
-\end{tikzcd}
-\]
+\fi
 
@@
 
-We may then define commutative character sheaves on $G$.
+We may now define commutative character sheaves on $G$.
+%
+Suppose $(\cs{L},\mu)$ is a linear character sheaf on $G$ such that its pull-back along $G\der \hookrightarrow G$ is trivial;
+let $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ be an isomorphism in $\CS(G\der)$.
+Let $\CS'(G)$ be the category of such triples, $(\cs{L},\mu,\beta)$, in which a morphism $(\cs{L},\mu,\beta)\to (\cs{L}',\mu',\beta')$ is a morphism $\alpha : (\cs{L},\mu)\to (\cs{L}',\mu')$ in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{G\der}$.
+%
+
+Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma_\beta : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows...
 
 \begin{definition}\label{def:CCS}
+The category $\CCS(G)$ of commutative character sheaves on $G$ is the full subcategory of $\CS'(G)$ consisting of triples $(\cs{L},\mu,\beta)$ such that the following diagram of Weil sheaves on $G \times G$ commutes.
+  \[
+  \begin{tikzcd}[row sep=30]
+   m^*\cs{L} \arrow{d}{\gamma_\beta} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
+   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L})
+  \end{tikzcd}
+  \]
+\end{definition}
+
+We will see that, when $\beta$ exists for $(\cs{L},\mu)\in \CS(G)$, it is essentially unique.
+
+The abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$, and the quotient $q : G \to G\ab$ is faithfully flat and a $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm.
+3.2}.
+
+\begin{theorem}\label{thm:Gab}
+Pull-back along the abelianization $q : G \to G\ab$
+\[
+q^* : \CCS(G\ab) \to \CCS(G)
+\]
+defines an equivalence of categories.
+\end{theorem}
+
+%\todo{Masound's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case.
+So, I think the modification is easy: add mop to diagram 2.4 in Masoud's paper.
+\\ -CC}
+
+\iffalse
+We summarize the setup in a diagram.
+\[
+\begin{tikzcd}
+{} & G\times G \arrow{d}{c} &&&\\
+1 \arrow{r} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
+\end{tikzcd}
+\]
+\fi
+
+\iffalse
+\begin{definition}
 A linear character sheaf $\cs{L}$ on a smooth group scheme $G$ is \emph{commutative} if
@@
 \end{definition}
+\fi
 
+\iffalse
 Note that we may also pull back the map $\xi\ab : m\ab^* \cs{L}\ab \to \theta\ab^*(m\ab^* \cs{L})$ from Definition \ref{def:CCScom}.
@@
 \end{proposition}
-
-\begin{theorem}\label{thm:Gab}
-Pull-back along the abelianization $q : G \to G\ab$
-\[
-q^* : \CCS(G\ab) \to \CCS(G)
-\]
-is an equivalence of categories.
-\end{theorem}
-
-%\todo{I got this wrong.
-I think our sheaves are not extra information in the commutative case.
-Masound's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case.
-So, I think the modification is easy: add mop to diagram 2.4 in Masoud's paper.
-\\ -CC}
+\fi
 

### 2015-11-10 followup.tex
Started working on the proof for Section 3, again.

@@
 
-The abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$, and the quotient $q : G \to G\ab$ is faithfully flat and a $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm.
-3.2}.
-
 \begin{theorem}\label{thm:Gab}
@@
 \\ -CC}
-
-\iffalse
-We summarize the setup in a diagram.
-\[
-\begin{tikzcd}
-{} & G\times G \arrow{d}{c} &&&\\
-1 \arrow{r} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
-\end{tikzcd}
-\]
-\fi
 
@@
 
-\subsection{Change of action/perspective}
+\subsection{Change of perspective}
 
-Suppose there is some $f : H\times G\to G\times G$ such that the following diagram commutes.
-%%%%%%%% FIX!!!! %%%%%%%%%%
+We now suppose that $H$ is a subgroup of $G$ and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
+Then we have the diagram
 \[
@@
 \]
-Then $f(h,g) = (a(h,g) g^{-1}, g)$.
-Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq a(h,g) g^{-1}$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
-
-Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
+where $f(h,g) = (a(h,g) g^{-1}, g) = (h,g)$.
+%Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq (i\circ p_1)$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
+Then every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
 \[
-\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}
+\beta : \cs{L}\vert_H \to (\EE)_{H}
 \]
-by $\beta \otimes \id_{p^*\cs{L}} = \nu \circ f^*\mu^{-1}$, or more precisely, by the following diagram of isomorphisms,
+by 
+\[
+\nu = (\beta \boxtimes \id_{\cs{L}}) \circ  f^*\mu,
+\] 
+or more precisely, by the following diagram of isomorphisms.
 \[
@@
 f^* m^*\cs{L} \arrow{r}{f^*\mu} & 
-f^*(\cs{L}\boxtimes \cs{L}) \arrow{d} & 
-f_1^*\cs{L} \otimes p^*\cs{L} \arrow{r}{\beta\otimes \id_{p^*\cs{L}}} & 
-(\EE)_{H\times G} \otimes p^*\cs{L} \arrow{u} \\
-& f^*(p_1^*\cs{L}\otimes p_2^*\cs{L}) \arrow{r} & f^*p_1^*\cs{L}\otimes f^* p_2^*\cs{L} \arrow{u}{f_1 = p_1\circ f}[swap]{p = p_2\circ f} &
+f^*(\cs{L}\boxtimes \cs{L}) \arrow{r} & 
+\cs{L}\vert_{H} \boxtimes \cs{L} \arrow{r}{\beta\boxtimes \id_{\cs{L}}} & 
+(\EE)_{H} \boxtimes \cs{L} \arrow{u} 
 \end{tikzcd}
 \]
-In this way we see we may replace $(\cs{L},\mu,\nu)$ with an alternate triple, $(\cs{L},\mu,\beta_1)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
-The isomorphism $\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}$ is constrained by two properties, corresponding to the diagrams in Sections [] and [].
-
-\subsection{Quotient and restriction}
-
-We now combine the material of the last two sections, by specializing to the following case: $H$ is a closed subgroup of $G$ and $q : G \to G/H$ is the fppf quotient.
-
-\[
-\begin{tikzcd}
-\CS(H) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
-\CS(G/H) \arrow{dl}{\text{`comparison'}} \\
- & \CS_{H}(G) \arrow{u}{\text{forget}}  & 
-\end{tikzcd}
-\]
+In this way we see we may replace $(\cs{L},\mu,\nu)$ with a triple, $(\cs{L},\mu,\beta)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
+The isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is constrained by two properties, corresponding to the diagrams in Sections [] and [].
 
 \begin{lemma}
-$\CS(G/H)$ is equivalent to the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$, with morphisms $\alpha : (\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ defined by the condition
+$\CS_H(G)$ is equivalent to the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$, with morphisms $\alpha : (\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ defined by the condition
 $\alpha : (\cs{L},\mu) \to (\cs{L}',\mu')$ is a morphism in $\CS(G)$ and $\beta = \beta' \circ \alpha\vert_{H}$.
@@
 
-In this case, the action $a$ is the restriction of $m$ to $H\times G$ and $f : H \times G\to G\times G$ is simply the inclusion and $f_1: H\times G \to G$ is projection to the first coordinate followed by inclusion $H \hookrightarrow G$, so $f_1^*\cs{L} = \cs{L}\vert_{H} \boxtimes (\EE)_G$.
-Then $\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}$ determines an isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$, and vice versa.
-Moreover, in this case, the constraint on $\beta$ is only this: $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is an isomorphism in $\CS(H)$. 
-%Let $\CS^H(G)$ denote the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$.
+\begin{proof}
+\end{proof}
 
@@
 \begin{proof}[Proof of Proposition~\ref{prop:Gder_triv}]
-We now consider a special case of the lemmas above. 
-Suppose $H = G\der$ and the action $a$ is the restriction of $m$ to $G\der\times G$.
-Then $f : G\der \times G\to G\times G$ is simply the inclusion and $f_1: G\der\times G \to G$ is projection to the first coordinate followed by inclusion $G\der \hookrightarrow G$.
-
-As we have seen above, the fppf quotient $q : G\to G\ab = G/G\der$ exists in schemes.
-Moreover, the quotient $q : G \to G\ab$ is faithfully flat and a $G\der$-torsor in the fppf topology, by\cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}
-%(In fact, it's a trivial torsor in that topology.)
+The abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$
+and the quotient $q : G \to G\ab$ is faithfully flat and a $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
+Then
+\[
+\begin{tikzcd}
+%{} & G\times G \arrow{d}{c} &&&\\
+1 \arrow{r}{i} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
+\end{tikzcd}
+\]
+gives
+\[
+\begin{tikzcd}
+\CS(H) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
+\CS(G/H) \arrow{dl}{\text{`comparison'}} \\
+\arrow{u}{\text{forget}} \CS'(G) \arrow{r}{\beta \mapsto \nu_\beta} & \CS_{H}(G) \arrow{u}{\text{forget}}  & 
+\end{tikzcd}
+\]
+%
 It now follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
-On the other hand, by Lemma~[], the forgetful functor $\CS_{G\der}(G)\to \CS(G)$ defines an equivalence $\CS_{G\der}(G)\to \CS'(G)$, where $\CS'(G)$ is the category of $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ in $\CS(G\der)$.
+On the other hand, by Lemma~[], $\CS_{G\der}(G)\to \CS'(G)$, defined by $(\cs{L},\mu,\nu)\mapsto (\cs{L},\mu, \beta_\nu)$, is an equivalence.
+Since the essential image of the forgetful functor $\CS'(G)\to \CS(G)$ is precisely the category of $(\cs{L},\mu)\in \CS(G)$ such that $\cs{L}\vert_H \iso (\EE)_H$, this completes the proof of 
+Proposition~\ref{prop:Gder_triv}.
 \end{proof}
 
-\begin{proof}[Proof of Proposition~\ref{prop:Gdiagram}]
+\begin{proof}[Proof of Theorem~\ref{thm:Gab}] 
+\[
+\begin{tikzcd}
+\CS'(G) &\arrow{l}[swap]{q^*} 
+\CS(G\ab) \arrow{l}{\text{`comparison'}} \\
+\CCS(G) \arrow{u}{\text{forget}}  & \CCS(G\ab) \arrow{u} 
+\end{tikzcd}
+\]
 
@@
 
-\begin{proof}[Proof of Theorem~\ref{thm:Gab}] 
-\end{proof}
+%\begin{proof}[Proof of Proposition~\ref{prop:Gdiagram}]
+%\end{proof}
 
@@
 \end{document}
+
+Suppose there is some $f : H\times G\to G\times G$ such that the following diagram commutes.
+\[
+\begin{tikzcd}
+\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
+G & & G \\
+& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
+\end{tikzcd}
+\]
+Then $f(h,g) = (a(h,g) g^{-1}, g)$.
+Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq a(h,g) g^{-1}$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
+
+Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
+\[
+\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}
+\]
+by $\beta \otimes \id_{p^*\cs{L}} = \nu \circ f^*\mu^{-1}$, or more precisely, by the following diagram of isomorphisms,
+\[
+\begin{tikzcd}
+a^*\cs{L} \arrow{d}{m\circ f = a} \arrow{rrr}{\nu}
+&&& p^*\cs{L}\\
+f^* m^*\cs{L} \arrow{r}{f^*\mu} & 
+f^*(\cs{L}\boxtimes \cs{L}) \arrow{d} & 
+f_1^*\cs{L} \otimes p^*\cs{L} \arrow{r}{\beta\otimes \id_{p^*\cs{L}}} & 
+(\EE)_{H\times G} \otimes p^*\cs{L} \arrow{u} \\
+& f^*(p_1^*\cs{L}\otimes p_2^*\cs{L}) \arrow{r} & f^*p_1^*\cs{L}\otimes f^* p_2^*\cs{L} \arrow{u}{f_1 = p_1\circ f}[swap]{p = p_2\circ f} &
+\end{tikzcd}
+\]
+In this way we see we may replace $(\cs{L},\mu,\nu)$ with an alternate triple, $(\cs{L},\mu,\beta_1)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
+The isomorphism $\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}$ is constrained by two properties, corresponding to the diagrams in Sections [] and [].
+
+\subsection{Quotient and restriction}
+
+We now combine the material of the last two sections, by specializing to the following case: $H$ is a closed subgroup of $G$ and $q : G \to G/H$ is the fppf quotient, which exists in schemes by  . . .

### 2015-11-11 followup.tex
Section 3 is working, but I've run out of steam for the day. More tomorrow.

@@
 
-\subsection{Commutative character sheaves on commutative groups}
+\subsection{Commutative character sheaves on commutative groups}\label{ssec:comcom}
 
@@
 
-Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma_\beta : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows...
+Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows.
+Let $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
+Then $c$ is a smooth morphism of $\Fq$ schemes and $c = m \circ (m \times (i \circ m \circ \theta))$.
+Thus, $\beta : \cs{L}\vert_{G/\der} \to (\EE)_{G\der}$ determines
+\[
+\begin{tikzcd}
+m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \arrow{r} & c^* \cs{L}\vert_{G\der} \arrow{r} &  (\EE)_{G\times G} \arrow{r} & (\EE)_G\otimes (\EE)_G.
+\end{tikzcd}
+\]
+Using the monadic structure of the category of Weil local systems on $G\times G$, this isomorphism, in turn, defines the isomorphism
+\[
+\begin{tikzcd}
+m^*\cs{L} \arrow{r}  & (\theta^* m^* i^*\cs{L})^\vee.\end{tikzcd}
+\] 
+Since $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ canonically, and since $\cs{L}^\vee \iso i^*\cs{L}$, canonically, this defines the promised isomorphism
+\[
+\begin{tikzcd}
+\gamma : m^*\cs{L} \arrow{r} & \theta^* m^* \cs{L}.
+\end{tikzcd}
+\]
 
 \begin{definition}\label{def:CCS}
-The category $\CCS(G)$ of commutative character sheaves on $G$ is the full subcategory of $\CS'(G)$ consisting of triples $(\cs{L},\mu,\beta)$ such that the following diagram of Weil sheaves on $G \times G$ commutes.
+The category $\CCS(G)$ of commutative character sheaves on $G$ is the full subcategory of $\CS'(G)$ consisting of triples $(\cs{L},\mu,\beta)$ such that the following diagram of Weil sheaves on $G \times G$ commutes,
   \[
   \begin{tikzcd}[row sep=30]
-   m^*\cs{L} \arrow{d}{\gamma_\beta} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
+   m^*\cs{L} \arrow{d}{\gamma} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
    \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L})
@@
   \]
+where $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$, above.
 \end{definition}
 
-We will see that, when $\beta$ exists for $(\cs{L},\mu)\in \CS(G)$, it is essentially unique.
+%We will see that, when $\beta$ exists for $(\cs{L},\mu)\in \CS(G)$, it is essentially unique.
 
@@
 \begin{tikzcd}
-\ &  \arrow{dl}[swap]{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}{p\circ b_2 = a\circ b_3} & \\
-b_1^* a^*\, \mathcal{L} \arrow{dr}[swap]{b_1^*(\nu)} &&&&   \arrow{dl}{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
+\ &  \arrow{dl}{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
+b_1^* a^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
 & b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L}, & 
@@
 \CS(G) &\arrow{l}[swap]{q^*} 
-\CS(G') \arrow{dl}{\text{`comparison'}}\\
+\CS(G') \arrow{dl}{\text{comparison}}\\
 \arrow{u}{\text{forget}} \CS_{H}(G). & 
@@
 It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fppf topology.
-(This is a small variation on the proof of the fact that quasicoherent sheaves form a stack on sheaves in the fppf topology.)
+(This is a small variation on the proof that quasicoherent sheaves form a stack on sheaves in the fppf topology.)
 Since $q : G\to G'$ is an $H$-torsor in the fppf topology, is now follows from descent theory that the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence.
@@
 
-We now suppose that $H$ is a subgroup of $G$ and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
+We now suppose that $i : H \hookrightarrow G$ is a closed subgroup and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
 Then we have the diagram
@@
 \]
-where $f(h,g) = (a(h,g) g^{-1}, g) = (h,g)$.
+where $f(h,g) = (i(h),g)$.
+% (a(h,g) g^{-1}, g) = (h,g)$.
 %Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq (i\circ p_1)$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
@@
 \[
-\nu = (\beta \boxtimes \id_{\cs{L}}) \circ  f^*\mu,
+\nu = (\beta \boxtimes \id) \circ  f^*\mu,
 \] 
@@
 \begin{tikzcd}
-a^*\cs{L} \arrow{d}{m\circ f = a} \arrow{rrr}{\nu}
-&&& p^*\cs{L}\\
-f^* m^*\cs{L} \arrow{r}{f^*\mu} & 
-f^*(\cs{L}\boxtimes \cs{L}) \arrow{r} & 
-\cs{L}\vert_{H} \boxtimes \cs{L} \arrow{r}{\beta\boxtimes \id_{\cs{L}}} & 
-(\EE)_{H} \boxtimes \cs{L} \arrow{u} 
+\ & a^*\cs{L} \arrow{dl}{m\circ f = a} \arrow{r}{\nu} & p^*\cs{L} & \\
+f^* m^*\cs{L} \arrow{dr}{f^*\mu} &&& (\EE)_{H} \boxtimes \cs{L} \arrow{ul}{p= p_1} \\ 
+& f^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_\circ f = i}[swap]{p_2\circ f = \id}  & 
+\cs{L}\vert_{H} \boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id} & 
 \end{tikzcd}
@@
 In this way we see we may replace $(\cs{L},\mu,\nu)$ with a triple, $(\cs{L},\mu,\beta)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
-The isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is constrained by two properties, corresponding to the diagrams in Sections [] and [].
+The isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is constrained conditions from Sections [] and [].
 
 \begin{lemma}
-$\CS_H(G)$ is equivalent to the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$, with morphisms $\alpha : (\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ defined by the condition
+$\CS_H(G)$ is equivalent to the category $\CS'(G)$ of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$, with morphisms $\alpha : (\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ defined by the condition
 $\alpha : (\cs{L},\mu) \to (\cs{L}',\mu')$ is a morphism in $\CS(G)$ and $\beta = \beta' \circ \alpha\vert_{H}$.
@@
 \begin{proof}[Proof of Proposition~\ref{prop:Gder_triv}]
-The abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$
-and the quotient $q : G \to G\ab$ is faithfully flat and a $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
-Then
+The abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
+Now,
 \[
@@
 %{} & G\times G \arrow{d}{c} &&&\\
-1 \arrow{r}{i} & G\der \arrow{r}{} & G \arrow{r}{q} & G\ab \arrow{r} & 1
+1 \arrow{r} & G\der \arrow{r}{i} & G \arrow{r}{q} & G\ab \arrow{r} & 1
 \end{tikzcd}
@@
 \begin{tikzcd}
-\CS(H) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
-\CS(G/H) \arrow{dl}{\text{`comparison'}} \\
-\arrow{u}{\text{forget}} \CS'(G) \arrow{r}{\beta \mapsto \nu_\beta} & \CS_{H}(G) \arrow{u}{\text{forget}}  & 
+\CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
+\CS(G\ab) \arrow{dl}{\text{comparison}} \\
+\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu} &  \CS_{G\der}(G) \arrow{u}{\text{forget}}  & 
 \end{tikzcd}
@@
 %
-It now follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
-On the other hand, by Lemma~[], $\CS_{G\der}(G)\to \CS'(G)$, defined by $(\cs{L},\mu,\nu)\mapsto (\cs{L},\mu, \beta_\nu)$, is an equivalence.
-Since the essential image of the forgetful functor $\CS'(G)\to \CS(G)$ is precisely the category of $(\cs{L},\mu)\in \CS(G)$ such that $\cs{L}\vert_H \iso (\EE)_H$, this completes the proof of 
-Proposition~\ref{prop:Gder_triv}.
+Since the quotient $q : G \to G\ab$ is a trivial $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}, 
+it now follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
+On the other hand, by Lemma~[], $\CS'(G) \to \CS_{G\der}(G)$, defined by $(\cs{L},\mu,\beta)\mapsto (\cs{L},\mu, \nu)$, is an equivalence.
+Since the essential image of the forgetful functor $\CS'(G)\to \CS(G)$ is precisely the category of $(\cs{L},\mu)\in \CS(G)$ such that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$, this completes the proof of Proposition~\ref{prop:Gder_triv}.
+%that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ if and only if $\cs{L} = q^*\cs{L}\ab$ for some $\cs{L}\ab \in \CS(G\ab)$.
 \end{proof}
@@
 \begin{proof}[Proof of Theorem~\ref{thm:Gab}] 
+By Definition~\ref{def:CCScom}, $\CCS(G\ab) \to \CS(G\ab)$ is a full subcategory.
+Since the comparison functor $\CS(G\ab) \to \CS_{G\der}(G)$ is an equivalence, it determines a full subcategory $\CCS_{G\der}(G)$ which is equivalent to $\CCS(G\ab)$. 
 \[
 \begin{tikzcd}
-\CS'(G) &\arrow{l}[swap]{q^*} 
-\CS(G\ab) \arrow{l}{\text{`comparison'}} \\
-\CCS(G) \arrow{u}{\text{forget}}  & \CCS(G\ab) \arrow{u} 
+\CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
+\CS(G\ab) \arrow{dl}{} \\
+\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu} &  \CS_{G\der}(G) \arrow{u}{\text{forget}}  & \CCS(G\ab) \arrow{u} \arrow{dl} \\
+\CCS(G) \arrow{u} \arrow{r}{\beta \mapsto \nu} & \arrow{u}  \CCS_{G\der}(G) & 
 \end{tikzcd}
 \]
-
+The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of the equivalence $\CS_{G\der}(G) \to \CS'(G)$ is $\CCS(G)$.
+To that end, suppose $(\cs{L},\mu,\beta)\in \CS'(G)$ and $(\cs{L},\mu,\nu) = q^*(\cs{L}\ab,\mu\ab)$;
+we must show that $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
+Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ in Section~\ref{ssec:comcom}.
+This determines a rigidification $r : \cs{L}_1 \to \EE$ by ....\todo{I've sorted this out, but have also run out of steam for the day. I'll write it up tomorrow.}
 \end{proof}

### 2015-11-11 followup.tex
Morning!

@@
 \begin{tikzcd}
-\Frob{}^* \gcs{L} \arrow{d}{\phi} \arrow{r}{\Frob{}^*\alpha} &  \Frob{}^* \gcs{L} \arrow{d}{\phi'}\\
+\Frob{}^* \gcs{L} \arrow{d}[swap]{\phi} \arrow{r}{\Frob{}^*\alpha} &  \Frob{}^* \gcs{L} \arrow{d}{\phi'}\\
 \gcs{L} \arrow{r}{\alpha} & \gcs{L}
@@
   \begin{tikzcd}[row sep=30]
-   m^*\cs{L} \arrow{d}{\xi} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
+   m^*\cs{L} \arrow{d}[swap]{\xi} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
    \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L})
@@
 Then $c$ is a smooth morphism of $\Fq$ schemes and $c = m \circ (m \times (i \circ m \circ \theta))$.
-Thus, $\beta : \cs{L}\vert_{G/\der} \to (\EE)_{G\der}$ determines
+Thus, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines
 \[
 \begin{tikzcd}
-m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \arrow{r} & c^* \cs{L}\vert_{G\der} \arrow{r} &  (\EE)_{G\times G} \arrow{r} & (\EE)_G\otimes (\EE)_G.
+m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \arrow{r}{c = m \circ (m \times (i \circ m \circ \theta))} & c^* \cs{L}\vert_{G\der} \arrow{r}{c^*(\beta)} &  c^*(\EE)_{G\der} \arrow{r} & (\EE)_G\otimes (\EE)_G.
 \end{tikzcd}
 \]
-Using the monadic structure of the category of Weil local systems on $G\times G$, this isomorphism, in turn, defines the isomorphism
+Using the monadic structure of the category of Weil local systems on $G\times G$, this isomorphism, in turn, defines an isomorphism
 \[
 \begin{tikzcd}
-m^*\cs{L} \arrow{r}  & (\theta^* m^* i^*\cs{L})^\vee.\end{tikzcd}
+m^*\cs{L} \arrow{r}  & (\theta^* m^* i^*\cs{L})^\vee.
+\end{tikzcd}
 \] 
@@
   \begin{tikzcd}[row sep=30]
-   m^*\cs{L} \arrow{d}{\gamma} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
+   m^*\cs{L} \arrow{d}[swap]{\gamma} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
    \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L})
@@
 \begin{tikzcd}
-\arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} & \arrow{l}[swap]{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{r}{p\circ c_2 = m\circ c_3}  & c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
-c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_i\circ c_1 = a\circ p_i\circ c_0} & c_0^*(a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{c_0^*(\nu\boxtimes \nu)} & c_0^*(p^*\cs{L} \boxtimes p^*\cs{L}) & \arrow{l}[swap]{p\circ p_i\circ c_0 = p_i \circ c_3}c_3^*(\cs{L}\boxtimes \cs{L})
+\ & \arrow{dl}{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{dr}[swap]{p\circ c_2 = m\circ c_3}  &  \\
+\arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} &&& c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
+c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{dr}{p_i\circ c_1 = a\circ p_i\circ c_0} &&& \arrow{dl}[swap]{p\circ p_i\circ c_0 = p_i \circ c_3} c_3^*(\cs{L}\boxtimes \cs{L}) \\
+ & c_0^*(a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{c_0^*(\nu\boxtimes \nu)} & c_0^*(p^*\cs{L} \boxtimes p^*\cs{L}) & 
 \end{tikzcd}
@@
 \begin{tikzcd}
-\arrow{d}{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
+\arrow{d}[swap]{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
 \cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
@@
 
-Is $\CS_H(G)$ a rigid monoidal category?
+%Is $\CS_H(G)$ a rigid monoidal category?
 
-If $(\cs{L},\mu,\nu)$ and $(\cs{L},\mu,\nu')$ in $\CS_H(G)$, then $\nu = \nu'$?
+%If $(\cs{L},\mu,\nu)$ and $(\cs{L},\mu,\nu')$ in $\CS_H(G)$, then $\nu = \nu'$?
 
@@
 \begin{proof}
-. . . 
-So the lemma reduces to the claim: the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence. 
+First we show that the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence. 
 To see this, observe first that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
@@
 Since $q : G\to G'$ is an $H$-torsor in the fppf topology, is now follows from descent theory that the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence.
+The same argument shows that pull-back along $q\times q$ determines an equivalence $\Loc(G'\times G') \to \Loc_{H\times H}(G\times G)$.
+
 \end{proof}

### 2015-11-11 followup.tex
Outlines of the proofs for Section 3 are now complete.

@@
 
-\subsection{Commutative character sheaves on non-commutative groups}
+\subsection{Commutative character sheaves on non-commutative groups}\label{ssec:noncom}
 
@@
 
-Now suppose $q : G \to G'$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
+Now suppose $q : G \to Q$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
 \[
@@
 & 
-G'
+Q
 \end{tikzcd}
 \]
-Let $\cs{L}'$ be a linear character sheaf on $G'$.
+Let $\cs{L}'$ be a linear character sheaf on $Q$.
 Consider the functor
 \[
-q^* : \CS(G') \to \CS(G)
+q^* : \CS(Q) \to \CS(G)
 \]
@@
 \]
-This simple observation shows that the functor $q^* : \CS(G') \to \CS(G)$  factors according to the following commuting diagram of functors
+This simple observation shows that the functor $q^* : \CS(Q) \to \CS(G)$  factors according to the following commuting diagram of functors
 \[
@@
 \CS(G) &\arrow{l}[swap]{q^*} 
-\CS(G') \arrow{dl}{\text{comparison}}\\
+\CS(Q) \arrow{dl}{\text{comparison}}\\
 \arrow{u}{\text{forget}} \CS_{H}(G). & 
@@
 \begin{lemma}
-If $q : G \to G'$ is an $H$-torsor in the fppf topology then the comparison functor $\CS(G') \to \CS_H(G)$ is an equivalence.
+If $q : G \to Q$ is an $H$-torsor in the fppf topology 
+then the comparison functor $\CS(Q) \to \CS_H(G)$ is an equivalence.
 \end{lemma}
@@
 \begin{proof}
-First we show that the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence. 
+First we recall that the comparison functor 
+$\Loc(Q) \to \Loc_H(G)$ is an equivalence. 
 To see this, observe first that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
@@
 (This is a small variation on the proof that quasicoherent sheaves form a stack on sheaves in the fppf topology.)
-Since $q : G\to G'$ is an $H$-torsor in the fppf topology, is now follows from descent theory that the comparison functor $\Loc(G') \to \Loc_H(G)$ is an equivalence.
-The same argument shows that pull-back along $q\times q$ determines an equivalence $\Loc(G'\times G') \to \Loc_{H\times H}(G\times G)$.
+Since $q : G\to Q$ is an $H$-torsor in the fppf topology, is now follows from descent theory that the comparison functor $\Loc(Q) \to \Loc_H(G)$ is an equivalence.
+
+The same argument shows that pull-back along $q\times q$ determines an equivalence $\Loc(Q\times Q) \to \Loc_{H\times H}(G\times G)$.
+
+Now we claim that the comparison functor 
+$\CS(Q)\to \CS_H(G)$ is also an equivalence.
 
@@
 
-\subsection{Proofs}
+\begin{lemma}
+If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ may be apprehended as a morphism of $H\times H$-equivariant linear character sheaves on $G\times G$; likewise $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$.
+\end{lemma}
+
+\begin{proof}
+\end{proof}
+
+\begin{lemma}
+If $(\cs{L},\mu,\beta)$ is a commutative character sheaf on $G$ then $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is a morphism of commutative character sheaves on $G\times G$.
+\end{lemma}
+
+\begin{proof}
+\end{proof}
+
+\subsection{Proofs for results from Section \ref{sec:defs}}
 
@@
 we must show that $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
-Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ in Section~\ref{ssec:comcom}.
-This determines a rigidification $r : \cs{L}_1 \to \EE$ by ....\todo{I've sorted this out, but have also run out of steam for the day. I'll write it up tomorrow.}
+Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ as in Section~\ref{ssec:comcom}.
+Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ as in Section~\ref{ssec:noncom}.
+Then the diagram in Definition~\ref{def:CCS} is precisely the result of applying the functor $(q\times q)^*$ to the diagram in Definition~\ref{def:CCScom}; 
+in particular $\gamma = (q\times q)^* \xi$.
+
+Using Lemma [], we may interpret the diagram in Definition~\ref{def:CCS} as a diagram in $\CS_{G\der\times G\der}(G\times G)$.
+By Lemma [], this corresponds uniquely to a diagram in $\CS(G\ab\times G\ab)$, necessarily the diagram in Definition~\ref{def:CCScom}.
+It now follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes. 
+In other words, $(\cs{L},\mu,\beta)\in \CCS(G)$
+if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G)$.
 \end{proof}
-
-%\begin{proof}[Proof of Proposition~\ref{prop:Gdiagram}]
-%\end{proof}
 

### 2015-11-11 followup.tex
Labeled the lemmata in Section 3, used them in the proofs from Section 1.
Next: supply proofs for all the lemmata.

@@
 
-\subsection{Equivariant Weil local systems}
+\subsection{Equivariant Weil local systems}\label{ssec:equivariant1}
 
@@
 
-\subsection{Equivariant linear character sheaves}
+\subsection{Equivariant linear character sheaves}\label{ssec:equivariant2}
 
@@
 
-\begin{lemma}
+\begin{lemma}\label{lem:torsor}
 If $q : G \to Q$ is an $H$-torsor in the fppf topology 
@@
 
-\subsection{Change of perspective}
+\begin{lemma}\label{lem:HH}
+If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ may be apprehended as a morphism of $H\times H$-equivariant linear character sheaves on $G\times G$; likewise $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$.
+\end{lemma}
+
+\begin{proof}
+\end{proof}
+
+\subsection{Closed subgroups}
 
@@
 In this way we see we may replace $(\cs{L},\mu,\nu)$ with a triple, $(\cs{L},\mu,\beta)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
-The isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is constrained conditions from Sections [] and [].
+The isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is constrained conditions from Sections~\ref{ssec:equivariant1} and \ref{ssec:equivariant2}.
 
-\begin{lemma}
+\begin{lemma}\label{lem:beta}
 $\CS_H(G)$ is equivalent to the category $\CS'(G)$ of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$, with morphisms $\alpha : (\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ defined by the condition
@@
 
-\begin{lemma}
-If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ may be apprehended as a morphism of $H\times H$-equivariant linear character sheaves on $G\times G$; likewise $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$.
-\end{lemma}
-
-\begin{proof}
-\end{proof}
-
-\begin{lemma}
-If $(\cs{L},\mu,\beta)$ is a commutative character sheaf on $G$ then $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is a morphism of commutative character sheaves on $G\times G$.
+\begin{lemma}\label{lem:GderGder}
+If $(\cs{L},\mu,\beta)$ is a commutative character sheaf on $G$ then $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is a morphism of $G\der\times G\der$-equivariant linear character sheaves on $G\times G$.
 \end{lemma}
@@
 Since the quotient $q : G \to G\ab$ is a trivial $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}, 
-it now follows from Lemma~[] that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
-On the other hand, by Lemma~[], $\CS'(G) \to \CS_{G\der}(G)$, defined by $(\cs{L},\mu,\beta)\mapsto (\cs{L},\mu, \nu)$, is an equivalence.
+it now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
+On the other hand, by Lemma~\ref{lem:beta}, $\CS'(G) \to \CS_{G\der}(G)$, defined by $(\cs{L},\mu,\beta)\mapsto (\cs{L},\mu, \nu)$, is an equivalence.
 Since the essential image of the forgetful functor $\CS'(G)\to \CS(G)$ is precisely the category of $(\cs{L},\mu)\in \CS(G)$ such that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$, this completes the proof of Proposition~\ref{prop:Gder_triv}.
@@
 
-Using Lemma [], we may interpret the diagram in Definition~\ref{def:CCS} as a diagram in $\CS_{G\der\times G\der}(G\times G)$.
-By Lemma [], this corresponds uniquely to a diagram in $\CS(G\ab\times G\ab)$, necessarily the diagram in Definition~\ref{def:CCScom}.
+Using Lemmas~\ref{lem:HH} and \ref{lem:GderGder}, we may interpret the diagram in Definition~\ref{def:CCS} as a diagram in $\CS_{G\der\times G\der}(G\times G)$.
+By Lemma~\ref{lem:beta}, this corresponds uniquely to a diagram in $\CS(G\ab\times G\ab)$, necessarily the diagram in Definition~\ref{def:CCScom}.
 It now follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes. 
 In other words, $(\cs{L},\mu,\beta)\in \CCS(G)$
-if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G)$.
+if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G)$, completing the proof of Theorem~\ref{thm:Gab}.
 \end{proof}

### 2015-11-11 followup.tex
Started work on the proofs of the lemmata in Section 3.

@@
 
+\begin{lemma}\label{lem:HH}
+If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of $H\times H$-equivariant linear character sheaves on $G\times G$; likewise $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$.
+\end{lemma}
+
+\begin{proof}
+\end{proof}
+
 \subsection{Descent along a torsor}
@@
 \]
-Let $\cs{L}'$ be a linear character sheaf on $Q$.
+Let $\cs{L}$ be a linear character sheaf on $Q$.
 Consider the functor
@@
 \]
-given on objects by $(\cs{L}',\mu') \mapsto (q^*\cs{L}', (q\times q)^* \mu', \nu_{\cs{L}'})$; cf [Dictionary].
-Then $q^*\cs{L}'$ is an $H$-equivariant linear character sheaf on $G$ when equipped with the canonical isomorphism
+given on objects by $(\cs{L},\mu) \mapsto (q^*\cs{L}, (q\times q)^* \mu)$; cf [Dictionary].
+Then $q^*\cs{L}$ is an $H$-equivariant linear character sheaf on $G$ when equipped with the canonical isomorphism
 \[
-\nu_{\cs{L}'} : a^* q^* \cs{L}' \mathop{\longrightarrow}\limits^{\iso} (q\circ a)^* \cs{L}' = (q\circ p)^*\cs{L}' \mathop{\longrightarrow}\limits^{\iso} p^* q^*\cs{L}.
+\nu : a^* q^* \cs{L} \mathop{\longrightarrow}\limits^{\iso} (q\circ a)^* \cs{L} = (q\circ p)^*\cs{L} \mathop{\longrightarrow}\limits^{\iso} p^* q^*\cs{L}.
 \]
-This simple observation shows that the functor $q^* : \CS(Q) \to \CS(G)$  factors according to the following commuting diagram of functors
+This simple observation defines the comparison functor
+\[
+q_H^* : \CS(Q) \to CS_H(G)
+\]
+and shows that the functor $q^* : \CS(Q) \to \CS(G)$ factors according to the following commuting diagram of functors
 \[
@@
 \CS(G) &\arrow{l}[swap]{q^*} 
-\CS(Q) \arrow{dl}{\text{comparison}}\\
+\CS(Q) \arrow{dl}{q_H^*}\\
 \arrow{u}{\text{forget}} \CS_{H}(G). & 
@@
 If $q : G \to Q$ is an $H$-torsor in the fppf topology 
-then the comparison functor $\CS(Q) \to \CS_H(G)$ is an equivalence.
+then $q_H^*: \CS(Q) \to \CS_H(G)$ is an equivalence.
 \end{lemma}
@@
 
-\end{proof}
-
-\begin{lemma}\label{lem:HH}
-If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ may be apprehended as a morphism of $H\times H$-equivariant linear character sheaves on $G\times G$; likewise $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$.
-\end{lemma}
-
-\begin{proof}
 \end{proof}
@@
 \CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
-\CS(G\ab) \arrow{dl}{\text{comparison}} \\
+\CS(G\ab) \arrow{dl}{q_{G\der}^*} \\
 \arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu} &  \CS_{G\der}(G) \arrow{u}{\text{forget}}  & 
@@
 \CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
-\CS(G\ab) \arrow{dl}{} \\
+\CS(G\ab) \arrow{dl}{q_{G\der}^*} \\
 \arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu} &  \CS_{G\der}(G) \arrow{u}{\text{forget}}  & \CCS(G\ab) \arrow{u} \arrow{dl} \\

### 2015-11-12 followup.tex
Added a proof of a lemma for Section 3.

@@
 Pull-back along the abelianization $q : G \to G\ab$
+defines an equivalence of categories
 \[
-q^* : \CCS(G\ab) \to \CCS(G)
+\CCS(G\ab) \to \CCS(G).
 \]
-defines an equivalence of categories.
 \end{theorem}
@@
 of Weil local systems on $H\times G$ such that the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes,
-\[
+\begin{equation}\label{eq:nu}
 \begin{tikzcd}
@@
 \end{tikzcd}
-\]
+\end{equation}
 and $s^*(\nu) = \id_{\cs{L}}$.
@@
 Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
-\[
+\begin{equation}\label{eq:alphanu}
 \begin{tikzcd}
@@
 \end{tikzcd}
-\]
+\end{equation}
 commutes.
@@
 Then $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ if $(\cs{L},\mu)$ is a linear character sheaf on $G$ and the following diagram of Weil local systems on $H \times G\times G$ commutes.
-\[
+\begin{equation}\label{eq:munu}
 \begin{tikzcd}
@@
 \end{tikzcd}
-\]
+\end{equation}
 \iffalse
@@
 A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves, so
-\[
+\begin{equation}\label{eq:alphanu}
 \begin{tikzcd}
@@
 If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of $H\times H$-equivariant linear character sheaves on $G\times G$; likewise $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$.
+\end{lemma}
+
+\begin{proof}
+Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(m^*\cs{L}, m_2^*(\mu))$, where $m_2 : G\times G\times G\times G\to G\times G$ is defined by $m_2(x_1,y_1,x_2,y_2) = (m(x_1,x_2), m(y_1,y_2)$;
+this can be seen by following the argument of [Dictionary].
+Set $\cs{L}_2\ceq m^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
+The linear character sheaf $(\cs{L}_2,\mu_2)$ comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ where $a_2 : H\times H\times G\times G\to G\times G$ is given by $a_2(h_1,g_1,h_2,g_2) = (a(h_1,g_1), a(h_2,g_2)$ and $p_2 : H\times H\times G\times G\to G\times G$ is given by $p_2(h_1,g_1,h_2,g_2)= ( g_1,g_2)$.
+This isomorphism satisfies \eqref{eq:nu} and \eqref{eq:munu}.
+Likewise $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
+\[
+\begin{tikzcd}
+\arrow{d}[swap]{\nu_2} a_2^*(m^*\cs{L}) \arrow{r}{a_2^*(\mu)} & a_2^*(\cs{L}\boxtimes\cs{L})  \arrow{r} & (a^*\cs{L})\boxtimes (a^*\cs{L}) \arrow{d}{\nu\boxtimes\nu} \\
+p_2^*(m^*\cs{L}) \arrow{r}{p_2^*(\mu)} & p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r} & (p^*\cs{L})\boxtimes (p^*\cs{L}) 
+\end{tikzcd}
+\]
+Since this diagram commutes, and since the appropriate version of \eqref{eq:alphamu} also commutes, it follows that $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism of equivariant linear character sheaves.
+The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is also straightforward.
+\end{proof}
+
+\begin{lemma}\label{lem:GderGder}
+If $(\cs{L},\mu,\beta)$ is a commutative character sheaf on $G$ then $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is a morphism of $G\der\times G\der$-equivariant linear character sheaves on $G\times G$.
 \end{lemma}
@@
 $\alpha : (\cs{L},\mu) \to (\cs{L}',\mu')$ is a morphism in $\CS(G)$ and $\beta = \beta' \circ \alpha\vert_{H}$.
-\end{lemma}
-
-\begin{proof}
-\end{proof}
-
-\begin{lemma}\label{lem:GderGder}
-If $(\cs{L},\mu,\beta)$ is a commutative character sheaf on $G$ then $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is a morphism of $G\der\times G\der$-equivariant linear character sheaves on $G\times G$.
 \end{lemma}

### 2015-11-12 followup.tex
One lemma left in Section 3 . . . .

@@
 The first step in this process is to rule out character sheaves as above.
-The following proposition will be proven in Section \ref{sec:descent}.
+The following proposition will be proven in Section \ref{ssec:proofs}.
 \begin{proposition} \label{prop:Gder_triv}
@@
 \]
-Using the monadic structure of the category of Weil local systems on $G\times G$, this isomorphism, in turn, defines an isomorphism
+Using the monoidal structure of the category of Weil local systems on $G\times G$, this isomorphism, in turn, defines an isomorphism
 \[
@@
 \end{theorem}
+
+The precise definition of the functor $\CCS(G\ab) \to \CCS(G)$ will be given in Section~\ref{ssec:proofs}, with the proof of Theorem~\ref{thm:Gab}.
 
@@
 & H \times G 
-\arrow[shift left=2]{r}{a}
-\arrow[shift right=2]{r}[swap]{p}
+\arrow[shift left=1]{r}{a}
+\arrow[shift right=1]{r}[swap]{p}
  & G 
@@
 \end{equation}
-and $s^*(\nu) = \id_{\cs{L}}$.
+and $s^*(\nu) = \id_{\cs{L}}$, where $s : G\to H\times G$ is given by $s(g) = (1,g)$.
 In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations above; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
@@
 A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves, so
-\begin{equation}\label{eq:alphanu}
+\begin{equation}\label{eq:alphamu}
 \begin{tikzcd}
@@
 
-\begin{lemma}\label{lem:GderGder}
-If $(\cs{L},\mu,\beta)$ is a commutative character sheaf on $G$ then $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is a morphism of $G\der\times G\der$-equivariant linear character sheaves on $G\times G$.
-\end{lemma}
-
-\begin{proof}
-\end{proof}
-
 \subsection{Descent along a torsor}
@@
 H\times G
- \arrow[shift left=2]{r}{a}
-  \arrow[shift right=2,swap]{r}{p}
+ \arrow[shift left=1]{r}{a}
+  \arrow[shift right=1,swap]{r}{p}
 &
@@
 
-\subsection{Closed subgroups}
+\subsection{Closed subgroups}\label{ssec:closed}
 
@@
 %Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq (i\circ p_1)$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
-Then every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
+Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
 \[
@@
 In this way we see we may replace $(\cs{L},\mu,\nu)$ with a triple, $(\cs{L},\mu,\beta)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
-The isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is constrained conditions from Sections~\ref{ssec:equivariant1} and \ref{ssec:equivariant2}.
+The next lemma makes that statement more precise.
 
 \begin{lemma}\label{lem:beta}
-$\CS_H(G)$ is equivalent to the category $\CS'(G)$ of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$, with morphisms $\alpha : (\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ defined by the condition
+$\CS_H(G)$ is equivalent to the category $\CS^H(G)$ of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$, with morphisms $\alpha : (\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ defined by the condition
 $\alpha : (\cs{L},\mu) \to (\cs{L}',\mu')$ is a morphism in $\CS(G)$ and $\beta = \beta' \circ \alpha\vert_{H}$.
@@
 \begin{proof}
+We have seen how every $(\cs{L},\mu,\nu)\in \CS_H(G)$ determines an isomorphism of Weil local systems $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$.
+This isomorphism is constrained conditions from Sections~\ref{ssec:equivariant1} and \ref{ssec:equivariant2} as they apply to $\nu : a^*\cs{L}\to p^*\cs{L}$. 
+It is straightforward but quite unpleasant matter to show that those conditions are exactly equivalent to the condition that the isomorphism Weil local systems $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is an isomorphism in the category of of linear character sheaves on $H$.
 \end{proof}
 
-\subsection{Proofs for results from Section \ref{sec:defs}}
+\subsection{Proofs for results from Section \ref{sec:defs}}\label{ssec:proofs}
 
@@
 \begin{tikzcd}
-\CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
+& \CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
 \CS(G\ab) \arrow{dl}{q_{G\der}^*} \\
-\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu} &  \CS_{G\der}(G) \arrow{u}{\text{forget}}  & 
+\CS^{G\der}(G) & \arrow[equal]{l} \CS'(G) \arrow{u}{\text{forget}}  \arrow{r}{\beta \mapsto \nu} &  \CS_{G\der}(G) \arrow{u}{\text{forget}}  & 
 \end{tikzcd}
@@
 %
+Here we use the notation $\CS'(G)$ from Section~\ref{ssec:noncom} and the observation that it is precisely the category $\CS^{G\der}(G)$, taking the case $H=G\der$ in Section~\ref{ssec:closed}.
 Since the quotient $q : G \to G\ab$ is a trivial $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}, 
@@
 By Definition~\ref{def:CCScom}, $\CCS(G\ab) \to \CS(G\ab)$ is a full subcategory.
-Since the comparison functor $\CS(G\ab) \to \CS_{G\der}(G)$ is an equivalence, it determines a full subcategory $\CCS_{G\der}(G)$ which is equivalent to $\CCS(G\ab)$. 
+Since the comparison functor $\CS(G\ab) \to \CS_{G\der}(G)$ is an equivalence, it determines a full subcategory $\CCS_{G\der}(G)$ which is equivalent to $\CCS(G\ab)$, as pictured below.
+The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of the equivalence $\CS_{G\der}(G) \to \CS'(G)$ is $\CCS(G)$.
 \[
 \begin{tikzcd}
-\CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
+\CS(G\der) 
+& \arrow{l}[swap]{i^*} \CS(G) 
+&\arrow{l}[swap]{q^*} 
 \CS(G\ab) \arrow{dl}{q_{G\der}^*} \\
-\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu} &  \CS_{G\der}(G) \arrow{u}{\text{forget}}  & \CCS(G\ab) \arrow{u} \arrow{dl} \\
-\CCS(G) \arrow{u} \arrow{r}{\beta \mapsto \nu} & \arrow{u}  \CCS_{G\der}(G) & 
+\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu} 
+&  \CS_{G\der}(G) \arrow{u}{\text{forget}}  
+&  \arrow[bend left=35pt, dashed]{dll} \CCS(G\ab) \arrow{u} \arrow{dl} \\
+\CCS(G) \arrow{u} \arrow{r}{\beta \mapsto \nu} 
+& \arrow{u}  \CCS_{G\der}(G) 
+& 
 \end{tikzcd}
 \]
-The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of the equivalence $\CS_{G\der}(G) \to \CS'(G)$ is $\CCS(G)$.
-To that end, suppose $(\cs{L},\mu,\beta)\in \CS'(G)$ and $(\cs{L},\mu,\nu) = q^*(\cs{L}\ab,\mu\ab)$;
+
+Suppose $(\cs{L},\mu,\beta)\in \CS'(G)$ and $(\cs{L},\mu,\nu) = q^*(\cs{L}\ab,\mu\ab)$;
 we must show that $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
@@
 in particular $\gamma = (q\times q)^* \xi$.
-
-Using Lemmas~\ref{lem:HH} and \ref{lem:GderGder}, we may interpret the diagram in Definition~\ref{def:CCS} as a diagram in $\CS_{G\der\times G\der}(G\times G)$.
+Together with Lemma~\ref{lem:HH}, we may now interpret the diagram in Definition~\ref{def:CCS} as a diagram in $\CS_{G\der\times G\der}(G\times G)$.
 By Lemma~\ref{lem:beta}, this corresponds uniquely to a diagram in $\CS(G\ab\times G\ab)$, necessarily the diagram in Definition~\ref{def:CCScom}.
-It now follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes. 
+It follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes. 
 In other words, $(\cs{L},\mu,\beta)\in \CCS(G)$
 if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G)$, completing the proof of Theorem~\ref{thm:Gab}.
+This also defines the functor $\CCS(G\ab) \to \CCS(G)$ by the dashed arrow in the diagram above.
 \end{proof}

### 2015-11-12 followup.tex
Just catching up and cleaning up.

@@
   \begin{tikzcd}[row sep=30]
-   m^*\cs{L} \arrow{d}[swap]{\xi} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
+   m^*\cs{L} \arrow{d}[swap]{\xi}{m= m\circ\theta} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
    \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L})
@@
  \end{definition}
-
-\todo{Add some remarks and/or promise examples showing that $\CCS(G)$ need not be $\CS(G)$, even in the Abelian case.}
+\todo{Add some remarks and/or promise examples showing that $\CCS(G)$ need not be $\CS(G)$, even in the Abelian case.
 I'm wondering about the structure of the paper. 
@@
 That would mean moving the material from Section~Invisible up to here.
+That would put the justification(s) for this definition in closer proximity with this definition.}
 
@@
 and again write $\CS(G)$ for the resulting category, with morphisms defined as in \emph{loc. cite}.
-
-\iffalse
-In order to define the category of commutative character sheaves on $G$ in this generality, we need to review ... 
-Let $G\der \hookrightarrow G$ be the derived subgroup scheme.
-We recall that this closed normal subgroup scheme is generated by a family of smooth morphisms
-$c_n: (G\times G)^n \to G$ given by $c_1: (x,y)\mapsto xyx^{-1}y^{-1}$ and ...
-%Then $G \times G \to G\der$ is a dominant morphism \cite{SGA3}*{Expos\'e {VI}$_B$, \S 7.2}.
-The group scheme $G$ is commutative if and only if $G\der$ is trivial.
-When $G$ is not connected, $G\der$ need not be connected, though it is smooth.
-%The restriction of $G\times G\to G\der$ to identity components gives a dominant morphism $G^0\times G^0 \to G^0\der$ \cite{SGA3}*{Expos\'e {VI}$_B$, Prop. 7.8}.
-\fi
 
@@
 Then $c$ is a smooth morphism of $\Fq$ schemes and $c = m \circ (m \times (i \circ m \circ \theta))$.
-Thus, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines
+Thus, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_G\otimes (\EE)_G$ by the diagram
 \[
 \begin{tikzcd}
-m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \arrow{r}{c = m \circ (m \times (i \circ m \circ \theta))} & c^* \cs{L}\vert_{G\der} \arrow{r}{c^*(\beta)} &  c^*(\EE)_{G\der} \arrow{r} & (\EE)_G\otimes (\EE)_G.
+m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \arrow{d}{c = m \circ (m \times (i \circ m \circ \theta))}  \arrow[dashed]{r} & (\EE)_G\otimes (\EE)_G\\
+c^* \cs{L}\vert_{G\der} \arrow{r}{c^*(\beta)} &  c^*(\EE)_{G\der}, \arrow{u}
 \end{tikzcd}
 \]
+where the arrow labeled with the equation is the canonical isomorphism coming from the isomorphism of functors defined by the equation.
 Using the monoidal structure of the category of Weil local systems on $G\times G$, this isomorphism, in turn, defines an isomorphism
@@
 & H \times G 
-\arrow[shift left=1]{r}{a}
-\arrow[shift right=1]{r}[swap]{p}
+\arrow[shift left=2]{r}{a}
+\arrow[shift right=2]{r}[swap]{p}
  & G 
@@
 \end{equation}
-commutes.
+commutes; see also [Dictionary, CS.4].
 %
@@
 
-Now suppose $q : G \to Q$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
+Now suppose $q : G \to G_0$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
 \[
@@
 H\times G
- \arrow[shift left=1]{r}{a}
-  \arrow[shift right=1,swap]{r}{p}
+ \arrow[shift left=2]{r}{a}
+  \arrow[shift right=2,swap]{r}{p}
 &
@@
 & 
-Q
+G_0
 \end{tikzcd}
 \]
-Let $\cs{L}$ be a linear character sheaf on $Q$.
+Let $\cs{L}_0$ be a linear character sheaf on $G_0$.
 Consider the functor
 \[
-q^* : \CS(Q) \to \CS(G)
+q^* : \CS(G_0) \to \CS(G)
 \]
-given on objects by $(\cs{L},\mu) \mapsto (q^*\cs{L}, (q\times q)^* \mu)$; cf [Dictionary].
-Then $q^*\cs{L}$ is an $H$-equivariant linear character sheaf on $G$ when equipped with the canonical isomorphism
+given on objects by $(\cs{L}_0,\mu_0) \mapsto (q^*\cs{L}_0, (q\times q)^* \mu_0)$.
+To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$, verify [Dictionary, CS.3], arguing as in [Dictionary].
+This linear character sheaf $(\cs{L},\mu)\ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$ on $G$ comes equipped with the canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of canonical isomorphisms.
 \[
-\nu : a^* q^* \cs{L} \mathop{\longrightarrow}\limits^{\iso} (q\circ a)^* \cs{L} = (q\circ p)^*\cs{L} \mathop{\longrightarrow}\limits^{\iso} p^* q^*\cs{L}.
+\begin{tikzcd}
+a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{rrr}{\nu} & & &  \arrow[equal]{d} p^*\cs{L} \\
+a^* ( q^*\cs{L}_0) \arrow{r} 
+& (q\circ a)^* \cs{L}_0 \arrow[equal]{r} 
+& (q\circ p)^*\cs{L}_0 \arrow{r} 
+& p^* q^*\cs{L}_0
+\end{tikzcd}
 \]
-This simple observation defines the comparison functor
+Since this isomorphism satisfies \eqref{eq:munu}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
+If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(G_0)$, 
+then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \eqref{eq:alphamu} [Dictionary, CS.4], arguing as in [Dictionary], so $\alpha$ is a morphism in $\CS(G)$.
+\todo{
+I find myself having to make many references to [Dictionary] and promising that the results there adapt to the noncommutative group case. 
+It makes me uneasy, but the alternative is to actually repeat the proofs here, with the weaker hypothesis on $G$, which would be ugly. 
+I'm just agonizing out loud, I guess.
+} 
+These simple observations define the comparison functor
 \[
@@
 \]
-and shows that the functor $q^* : \CS(Q) \to \CS(G)$ factors according to the following commuting diagram of functors
+and show that the functor $q^* : \CS(Q) \to \CS(G)$ factors according to the following commuting diagram of functors
 \[
@@
 To see this, observe first that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
-Moreover, if $Y \to X$ is a flat surjective morphism of affine schemes over $\Fq$, then the comparison functor $\Loc(X) \to \Loc(Y\to X)$ is an equivalence, with $\Loc(Y\to X)$ defined as in [].
-It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fppf topology.
-(This is a small variation on the proof that quasicoherent sheaves form a stack on sheaves in the fppf topology.)
-Since $q : G\to Q$ is an $H$-torsor in the fppf topology, is now follows from descent theory that the comparison functor $\Loc(Q) \to \Loc_H(G)$ is an equivalence.
+Then, observe that the comparison functor for Weil local systems is an equivalence for flat surjective morphisms $Y \to X$ of affine schemes over $\Fq$.
+It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fppf topology [Vistoli]
+Since $q : G\to Q$ is an $H$-torsor in the fppf topology, is now follows from descent theory that the comparison functor $\Loc(Q) \to \Loc_H(G)$ is an equivalence [Vistoli]
 
@@
 $\CS(Q)\to \CS_H(G)$ is also an equivalence. 
+Since a linear character sheaf on $Q$ is a triple $(\cs{L}_0,\mu_0)$, where $\cs{L}_0$ is an object in $\Loc(Q)$ and $\mu_0$ is a map in $\Loc(Q\times Q)$, satisfying the condition in [CS.2 from Dictionary].
 
@@
 \begin{tikzcd}
-& \CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
+\ & \CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
 \CS(G\ab) \arrow{dl}{q_{G\der}^*} \\

### 2015-11-12 followup.tex
Section 3 is complete now. I'll add details and polish as time permits.

@@
 Using the monoidal structure of the category of Weil local systems on $G\times G$, this isomorphism, in turn, defines an isomorphism
-\[
-\begin{tikzcd}
-m^*\cs{L} \arrow{r}  & (\theta^* m^* i^*\cs{L})^\vee.
-\end{tikzcd}
-\] 
+$
+m^*\cs{L} \to (\theta^* m^* i^*\cs{L})^\vee.
+$
 Since $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ canonically, and since $\cs{L}^\vee \iso i^*\cs{L}$, canonically, this defines the promised isomorphism
@@
 Then, $a\circ b_1 = a\circ b_2$ and $a\circ b_3 = p\circ b_2$ and $p\circ b_1 = p\circ b_3$.
+Define $s : G\to H\times G$ by $s(g) = (1,g)$.
 An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
@@
 \] 
-of Weil local systems on $H\times G$ such that the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes,
-\begin{equation}\label{eq:nu}
+of Weil local systems on $H\times G$ such that 
+\begin{equation}\label{E1}
+s^*(\nu) = \id_{\cs{L}}
+\end{equation}
+and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes,
+\begin{equation}\label{E2}
 \begin{tikzcd}
@@
 \end{equation}
-and $s^*(\nu) = \id_{\cs{L}}$, where $s : G\to H\times G$ is given by $s(g) = (1,g)$.
 In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations above; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
@@
 Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
-\begin{equation}\label{eq:alphanu}
+\begin{equation}\label{E3}
 \begin{tikzcd}
@@
 Then $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ if $(\cs{L},\mu)$ is a linear character sheaf on $G$ and the following diagram of Weil local systems on $H \times G\times G$ commutes.
-\begin{equation}\label{eq:munu}
+\begin{equation}\label{ECS1}
 \begin{tikzcd}
@@
 
-A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves, so
-\begin{equation}\label{eq:alphamu}
-\begin{tikzcd}
-\arrow{d}[swap]{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
-\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
-\end{tikzcd}
-\end{equation}
-commutes; see also [Dictionary, CS.4].
+A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves.
+%so
+%\begin{equation}\label{CS4}
+%\begin{tikzcd}
+%\arrow{d}[swap]{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
+%\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
+%\end{tikzcd}
+%\end{equation}
+%commutes; see also [Dictionary, CS.4].
 %
@@
 The linear character sheaf $(\cs{L}_2,\mu_2)$ comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ where $a_2 : H\times H\times G\times G\to G\times G$ is given by $a_2(h_1,g_1,h_2,g_2) = (a(h_1,g_1), a(h_2,g_2)$ and $p_2 : H\times H\times G\times G\to G\times G$ is given by $p_2(h_1,g_1,h_2,g_2)= ( g_1,g_2)$.
-This isomorphism satisfies \eqref{eq:nu} and \eqref{eq:munu}.
+The  isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ satisfies the appropriate version of \cite{ECS1}, so  $(\cs{L}_2,\mu_2,nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
 Likewise $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
@@
 \]
-Since this diagram commutes, and since the appropriate version of \eqref{eq:alphamu} also commutes, it follows that $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism of equivariant linear character sheaves.
-The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is also straightforward.
+Since this diagram commutes, $(\cs{L}\boxtimes \cs{L},\mu\boxtimes \mu,\nu\boxtimes\nu)$ is also an $H\times H$-equivariant linear character sheaf on $G\times G$.
+The appropriate version of \eqref{E3} also commutes, so $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism of equivariant linear character sheaves.
+The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is morphism of $H\times H$-equivariant linear character sheaves on $G\times G$ is also straightforward.
 \end{proof}
@@
 \]
-given on objects by $(\cs{L}_0,\mu_0) \mapsto (q^*\cs{L}_0, (q\times q)^* \mu_0)$.
-To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$, verify [Dictionary, CS.3], arguing as in [Dictionary].
+given on objects by $(\cs{L}_0,\mu_0) \mapsto (q^*\cs{L}_0, (q\times q)^* \mu_0)$; see [Dictionary, ].
+%To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$, verify [Dictionary, CS.3], arguing as in [Dictionary].
 This linear character sheaf $(\cs{L},\mu)\ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$ on $G$ comes equipped with the canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of canonical isomorphisms.
@@
 \]
-Since this isomorphism satisfies \eqref{eq:munu}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
+Since this isomorphism satisfies \eqref{ECS1}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
 If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(G_0)$, 
-then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \eqref{eq:alphamu} [Dictionary, CS.4], arguing as in [Dictionary], so $\alpha$ is a morphism in $\CS(G)$.
-\todo{
-I find myself having to make many references to [Dictionary] and promising that the results there adapt to the noncommutative group case. 
+then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies [Dictionary, CS.4], arguing as in [Dictionary], so $\alpha$ is a morphism in $\CS(G)$.
+%\todo{I find myself having to make many references to [Dictionary] and promising that the results there adapt to the noncommutative group case.
 It makes me uneasy, but the alternative is to actually repeat the proofs here, with the weaker hypothesis on $G$, which would be ugly.
-I'm just agonizing out loud, I guess.
-} 
+I'm just agonizing out loud, I guess.}
 These simple observations define the comparison functor
 \[
-q_H^* : \CS(Q) \to CS_H(G)
+q_H^* : \CS(G_0) \to CS_H(G)
 \]
-and show that the functor $q^* : \CS(Q) \to \CS(G)$ factors according to the following commuting diagram of functors
+and show that the functor $q^* : \CS(G_0) \to \CS(G)$ factors according to the following commuting diagram of functors
 \[
@@
 \CS(G) &\arrow{l}[swap]{q^*} 
-\CS(Q) \arrow{dl}{q_H^*}\\
+\CS(G_0) \arrow{dl}{q_H^*}\\
 \arrow{u}{\text{forget}} \CS_{H}(G). & 
@@
 \]
+The definition of $q_H^* : \CS(G_0)\to \CS_H(G)$ will be revisited in the proof of the following result.
 
 \begin{lemma}\label{lem:torsor}
-If $q : G \to Q$ is an $H$-torsor in the fppf topology 
-then $q_H^*: \CS(Q) \to \CS_H(G)$ is an equivalence.
+If $q : G \to G_0$ is an $H$-torsor in the fppf topology 
+then $q_H^*: \CS(G_0) \to \CS_H(G)$ is an equivalence.
 \end{lemma}
@@
 First we recall that the comparison functor 
-$\Loc(Q) \to \Loc_H(G)$ is an equivalence. 
+$\Loc(G_0) \to \Loc_H(G)$ is an equivalence.
 To see this, observe first that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
-Then, observe that the comparison functor for Weil local systems is an equivalence for flat surjective morphisms $Y \to X$ of affine schemes over $\Fq$.
-It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fppf topology [Vistoli]
-Since $q : G\to Q$ is an $H$-torsor in the fppf topology, is now follows from descent theory that the comparison functor $\Loc(Q) \to \Loc_H(G)$ is an equivalence [Vistoli]
+Then, observe that the comparison functor for Weil local systems is an equivalence for flat surjective morphisms of affine schemes over $\Fq$.
+It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fppf topology [Vistoli].
+(This is a slight variation on the argument showing that quasicoherent sheaves are a stack over schemes in the fppf topology.)
+Since $q : G\to G_0$ is an $H$-torsor in the fppf topology, is now follows from descent theory that the comparison functor $\Loc(G_0) \to \Loc_H(G)$ is an equivalence [Vistoli].
 
-The same argument shows that pull-back along $q\times q$ determines an equivalence $\Loc(Q\times Q) \to \Loc_{H\times H}(G\times G)$.
+For use below, we write $L_1 : \Loc(G_0) \to \Loc_H(G)$ for the comparison functor, $R_1 : \Loc_H(G) \to Loc(G_0)$ for its adjoint, and $(\epsilon_1, \eta_1)$ for the counit and unit of the adjunction.
+%
+Arguing as above, we also see that pull-back along $q\times q$ determines an equivalence $L_2 : \Loc(G_0\times G_0) \to \Loc_{H\times H}(G\times G)$.
+For use below, we write $L_2 : \Loc_{H\times H}(G\times G) \to \Loc(G_0\times G_0)$ for its adjoint and $(\epsilon_2, \eta_2)$ for the counit and unit of the adjunction.
 
-Now we claim that the comparison functor 
-$\CS(Q)\to \CS_H(G)$ is also an equivalence. 
-Since a linear character sheaf on $Q$ is a triple $(\cs{L}_0,\mu_0)$, where $\cs{L}_0$ is an object in $\Loc(Q)$ and $\mu_0$ is a map in $\Loc(Q\times Q)$, satisfying the condition in [CS.2 from Dictionary].
+We may now revisit the definition of the functor $q_H^*: \CS(Q)\to \CS_H(G)$.
+By (a small part of) Lemma~\ref{lem:HH}, $\mu_0$ is a morphism of linear character sheaves on $G_0\times G_0$.
+Thus, on objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$. 
+To verify that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$, one must confirm [Definition, CS1, CS2, CS3], \eqref{E1}, \eqref{E2} and \eqref{ECS1}. 
+Conditions [Definition, CS1, CS2, CS3] follow from an adaptation of [Dictionary, ...] while conditions \eqref{E1}, \eqref{E2} are a consequence of the work above. 
+Condition \eqref{ECS1} is confirmed by brute force.
+On maps, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\alpha_0) = L_1(\alpha_0)$.
+To verify that $L_1(\alpha_0)$ is a map in $\CS_H(G)$ we must confirm conditions [Definition, CS4] and \eqref{E3}.
+Condition [Definition, CS4] follows from an adaptation of [Dictionary, ...] while condition \eqref{E3} is a consequence of the work above.
 
+With this description of $q_H^*: \CS(Q)\to \CS_H(G)$ is is easy to see that it is an equivalence.
+Its adjoint is given on objects by $(\cs{L},\mu,\nu) \mapsto (L_1(\cs{L},\nu), L_2(\nu))$, again making use of Lemma~\ref{lem:HH}, and on objects by $\alpha \mapsto L_1(\alpha)$.
+The adjunction is built from the adjunctions for $(L_1,R_1)$ and $(L_2, R_2)$.
 \end{proof}
@@
 We now suppose that $i : H \hookrightarrow G$ is a closed subgroup and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
-Then we have the diagram
-\[
-\begin{tikzcd}
-\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
-G & & G \\
-& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
-\end{tikzcd}
-\]
-where $f(h,g) = (i(h),g)$.
+%Then we have the diagram
+%\[
+%\begin{tikzcd}
+%\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
+%G & & G \\
+%& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
+%\end{tikzcd}
+%\]
+Define $f : H\times G \to G\times G$ by $f(h,g) = (i(h),g)$ and note that $a = m\circ f$ and $p = p_2\circ f$.
 % (a(h,g) g^{-1}, g) = (h,g)$.
@@
 by 
-\[
+\begin{equation}\label{betanu}
 \nu = (\beta \boxtimes \id) \circ  f^*\mu,
-\] 
+\end{equation}
 or more precisely, by the following diagram of isomorphisms.

### 2015-11-12 followup.tex
Started work on Section 4, types.

@@
 %\end{equation}
-%commutes; see also [Dictionary, CS.4].
+%commutes; see also \cite{cunningham-roe:13a}, CS.4].
 %
@@
 Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(m^*\cs{L}, m_2^*(\mu))$, where $m_2 : G\times G\times G\times G\to G\times G$ is defined by $m_2(x_1,y_1,x_2,y_2) = (m(x_1,x_2), m(y_1,y_2)$;
-this can be seen by following the argument of [Dictionary].
+this can be seen by following the argument of \cite{cunningham-roe:13a}].
 Set $\cs{L}_2\ceq m^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
 The linear character sheaf $(\cs{L}_2,\mu_2)$ comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ where $a_2 : H\times H\times G\times G\to G\times G$ is given by $a_2(h_1,g_1,h_2,g_2) = (a(h_1,g_1), a(h_2,g_2)$ and $p_2 : H\times H\times G\times G\to G\times G$ is given by $p_2(h_1,g_1,h_2,g_2)= ( g_1,g_2)$.
-The  isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ satisfies the appropriate version of \cite{ECS1}, so  $(\cs{L}_2,\mu_2,nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
+The  isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ satisfies the appropriate version of \eqref{ECS1}, so  $(\cs{L}_2,\mu_2,nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
 Likewise $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
@@
 \]
-given on objects by $(\cs{L}_0,\mu_0) \mapsto (q^*\cs{L}_0, (q\times q)^* \mu_0)$; see [Dictionary, ].
-%To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$, verify [Dictionary, CS.3], arguing as in [Dictionary].
+given on objects by $(\cs{L}_0,\mu_0) \mapsto (q^*\cs{L}_0, (q\times q)^* \mu_0)$; see \cite{cunningham-roe:13a}*{}.
+%To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$, verify \cite{cunningham-roe:13a}, CS.3], arguing as in \cite{cunningham-roe:13a}].
 This linear character sheaf $(\cs{L},\mu)\ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$ on $G$ comes equipped with the canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of canonical isomorphisms.
@@
 If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(G_0)$, 
-then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies [Dictionary, CS.4], arguing as in [Dictionary], so $\alpha$ is a morphism in $\CS(G)$.
-%\todo{I find myself having to make many references to [Dictionary] and promising that the results there adapt to the noncommutative group case.
+then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, arguing as in \cite{cunningham-roe:13a} so $\alpha$ is a morphism in $\CS(G)$.
+%\todo{I find myself having to make many references to \cite{cunningham-roe:13a}] and promising that the results there adapt to the noncommutative group case.
 It makes me uneasy, but the alternative is to actually repeat the proofs here, with the weaker hypothesis on $G$, which would be ugly.
@@
 Thus, on objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$. 
-To verify that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$, one must confirm [Definition, CS1, CS2, CS3], \eqref{E1}, \eqref{E2} and \eqref{ECS1}. 
-Conditions [Definition, CS1, CS2, CS3] follow from an adaptation of [Dictionary, ...] while conditions \eqref{E1}, \eqref{E2} are a consequence of the work above. 
+To verify that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$, one must confirm \cite{cunningham-roe:13a}*{CS1, CS2, CS3}, \eqref{E1}, \eqref{E2} and \eqref{ECS1}. 
+Conditions \cite{cunningham-roe:13a}*{CS1, CS2, CS3} follow from an adaptation of \cite{cunningham-roe:13a}*{} while conditions \eqref{E1}, \eqref{E2} are a consequence of the work above. 
 Condition \eqref{ECS1} is confirmed by brute force.
 On maps, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\alpha_0) = L_1(\alpha_0)$.
-To verify that $L_1(\alpha_0)$ is a map in $\CS_H(G)$ we must confirm conditions [Definition, CS4] and \eqref{E3}.
-Condition [Definition, CS4] follows from an adaptation of [Dictionary, ...] while condition \eqref{E3} is a consequence of the work above.
+To verify that $L_1(\alpha_0)$ is a map in $\CS_H(G)$ we must confirm conditions \cite{cunningham-roe:13a}*{CS4} and \eqref{E3}.
+Condition \cite{cunningham-roe:13a}*{CS4} follows from an adaptation of \cite{cunningham-roe:13a}*{} while condition \eqref{E3} is a consequence of the work above.
 
@@
 Set $G = \Gr_R(\underline{G})$; this is a group scheme over $\Fq$ equipped with $G = \varprojlim_{n\in \NN} G_n$.
-Let $\QCS(G)$ be the category of commutative character sheaves on $G$. . . .  as in \cite{cunningham-roe:13a}.
+Let $\QCS(G)$ be the category of commutative quasicharacter sheaves on $G$. . . .  as in \cite{cunningham-roe:13a}.
 
 \begin{proposition}\label{prop:QCS}
-$\Hom(\underline{G}(\OK),\EEx) \iso \QCSiso{G}$.
+$\Hom_\text{cts}(\underline{G}(\OK),\EEx) \iso \QCSiso{G}$.
 \end{proposition}
+
+\begin{proof}
+\end{proof}
 

### 2015-11-13 followup.tex
Fixing typos, moving sections around

@@
 
-\subsection{Commutative character sheaves on commutative groups}\label{ssec:comcom}
-
-Suppose now that $G$ is commutative.
-Recall \cite{cunningham-roe:13a}*{Def. 1.1} that a character sheaf on $G$ is a triple $(\gcs{L}, \mu, \phi)$,
+When $G$ is commutative, a \emph{character sheaf} on $G$ is a triple $(\gcs{L}, \mu, \phi)$,
 where $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, 
@@
 and $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an isomorphism of sheaves on $\bG$;
-the triple $(\gcs{L}, \mu, \phi)$ must also satisfy compatibility conditions specified in \emph{loc. cite}.
-The category of character sheaves on $G$ is denoted by $\CS(G)$.
+the triple $(\gcs{L}, \mu, \phi)$ is required to satisfy certain conditions \cite{cunningham-roe:13a}*{Def. 1.1}.
+Write $\CS(G)$ for the category of character sheaves on $G$.
 
-Let $\cs{L}$ be a character sheaf on $G$.  Since $m = m \circ \theta$ in the commutative case,
+Even when $G$ is not commutative, the category $\CS(G)$, defined as in \cite{cunningham-roe:13a}*{Def. 1.1},
+still makes sense.  In order to distinguish the resulting objects from
+the character sheaves of Lusztig, we will refer to the former as \emph{linear character sheaves}
+(to evoke the one-dimensional character sheaves of \cite{Kamgarpour}).
+
+\section{Commutative character sheaves on commutative groups}\label{sec:comcom}
+
+We consider first the case that $G$ is commutative, which will be used for general smooth $G$.
+Let $\cs{L}$ be a character sheaf on $G$.  Since $m = m \circ \theta$ in this case,
 there is a canonical isomorphism $\xi : m^* \cs{L} \to \theta^* m^* \cs{L}$.
@@
 
-\subsection{Commutative character sheaves on non-commutative groups}\label{ssec:noncom}
+\subsection{Eliminating Invisible Character Sheaves}\label{ssec:defect}
 
-We now drop the assumption that $G$ is commutative, and assume only that it is smooth.
-The category $\CS(G)$ still makes sense in this context, defined as in \cite{cunningham-roe:13a}*{Def. 1.1}.
-In order to distinguish the resulting objects from
-the character sheaves of Lusztig, we will refer to the former as \emph{linear character sheaves}
-(to evoke the one-dimensional character sheaves of \cite{Kamgarpour})
-and again write $\CS(G)$ for the resulting category, with morphisms defined as in \emph{loc. cite}.
+In this section we show that trace of Frobenius is an isomorphism for commutative character sheaves on a
+smooth commutative group scheme $G$.  We begin by reinterpreting Definition \ref{def:CCScom} in terms of
+cocycles.
+
+For a character sheaf $\cs{L}$ on $G$, recall from \cite{cunningham-roe:13a}*{\S 2.3} that $S_G : \CSiso{G} \to \Hh^2(E_G^\bullet)$ maps
+$[\cs{L}]$ to $[\alpha \oplus \beta]$, where $E_G^\bullet$ is the total space of the zeroth page
+of the Hochschild-Serre spectral sequence, $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$ is obtained from $\mu$ and
+$\beta \in C^1(\Weil{}, C^1(\bG, \EEx))$ is obtained from $\phi$.
+
+If $M$ is a $\bG$-module, then we say a cohomology class in $\Hh^2(\bG, M)$ is \emph{symmetric} if it is represented
+by a symmetric $2$-cocycle.  Since every coboundary is symmetric, either all cocycles in a given class will be symmetric
+or none will.
+
+\begin{lemma} \label{lem:symtriv}
+Let $\bG$ be a commutative group.  Then the only symmetric class in $\Hh^2(\bG, \EEx)$ is the trivial class.
+\end{lemma}
+
+\begin{proof}
+By the universal coefficient theorem,
+\[
+0 \to \Ext^1_\ZZ(\Hh_{n-1}(\bG, \ZZ), \EEx) \to \Hh^n(\bG, \EEx) \to \Hom(\Hh_n(\bG, \ZZ), \EEx) \to 0
+\]
+for all $n > 0$.  When $n = 2$, using the fact that $\bG$ is commutative, we have that $\Hh_1(\bG, \ZZ) \cong \bG$
+and that $\Hh_2(\bG, \ZZ) \cong \wedge^2 \bG$. We get
+\[
+0 \to \Ext^1_\ZZ(\bG, \EEx) \to \Hh^2(\bG, \EEx) \to \Hom(\wedge^2 \bG, \EEx) \to 0.
+\]
+The map $\Hh^2(\bG, \EEx) \to \Hom(\wedge^2 \bG, \EEx)$ maps a $2$-cocycle $f$ to the alternating function
+\[
+(x,y) \mapsto \frac{f(x,y)}{f(y,x)}.
+\]
+Thus the cohomology classes represented by symmetric cocycles are precisely those in the image of $\Ext^1_\ZZ(\bG, \EEx)$.
+But $\Ext^1_\ZZ(-, \EEx)$ vanishes because $\EEx$ is divisible.
+\end{proof}
+
+\begin{lemma} \label{lem:conncomm}
+If $G$ is a connected commutative algebraic group over $\Fq$ then every character sheaf on $G$ is commutative.
+\end{lemma}
+
+\begin{proof}
+We can use \'etale descent to see that pullback by the Lang isogeny defines an equivalence
+of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.  Thus every character
+sheaf on $G$ arises through the Lang isogeny; since the covering group is $G$ itself, which is commutative,
+every character sheaf on $G$ is commutative.
+\end{proof}
+
+\begin{theorem} \label{thm:trfrobiso}
+If $G$ is a smooth commutative group scheme over $\Fq$ then $\TrFrob{G} : \CCSiso{G} \to G(\Fq)^*$ is an isomorphism.
+\end{theorem}
+
+\begin{proof}
+Suppose first that $G$ is \'etale.  Consider the isomorphism of short exact sequences
+\[
+\begin{tikzcd}
+ 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \CSiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
+  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\bG,\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1(\bG,\EEx)) \arrow{r} & 0
+ \end{tikzcd}
+ \]
+from \cite{cunningham-roe:13a}*{Prop. 2.7}.
+
+Suppose that $\cs{L}$ is a commutative character sheaf
+with $\trFrob{\cs{L}} = 1$.  Then $S_G([\cs{L}])$ is in the image of $\Hh^2(\bG, \EEx)^\Weil{}$, so is cohomologous to
+$[\alpha', 0]$.  Since $\alpha$ is symmetric and coboundaries are symmetric, $\alpha'$ is symmetric as well.
+So by Lemma \ref{lem:symtriv}, $\alpha'$ is cohomologically trivial, and thus $[\cs{L}]$ is trivial as well.
+
+To see that $\TrFrob{G}$ is still surjective on $\CCSiso{G}$, note that the character sheaf constructed in the proof of
+\cite{cunningham-roe:13a}*{Prop. 2.6} has trivial $\alpha$, and is thus commutative.
+
+For general smooth commutative group schemes, we use Lemma \ref{lem:conncomm} and the snake lemma.
+\end{proof}
+
+\begin{remark}
+Since $\Hh^0(\Weil{},\Hh^2(\bG,\EEx))$ is not necessarily trivial \cite{cunningham-roe:13a}*{Ex. 2.10}, the functor
+$\CCS(G) \to \CS(G)$ is not an equivalence of categories in general.
+\end{remark}
+
+\section{Commutative character sheaves on non-commutative groups}\label{sec:noncom}
+
+We now consider the case of a smooth group scheme without the commutativity assumption.  We start
+by relating character sheaves on $G$ to character sheaves on its abelianization.
 
@@
 
-The first step in this process is to rule out character sheaves as above.
+\subsection{Definition}\label{ssec:noncomdef}
+
+In order to get character sheaves that correspond to characters in $G(k)^*$, we must discard those
+character sheaves whose restriction to the derived subgroup is nontrivial.
 The following proposition will be proven in Section \ref{ssec:proofs}.
@@
 
+\todo{Should remark that it reduces to the other definition in the commutative case}
+
 %We will see that, when $\beta$ exists for $(\cs{L},\mu)\in \CS(G)$, it is essentially unique.
@@
 
-\iffalse
-\begin{definition}
-A linear character sheaf $\cs{L}$ on a smooth group scheme $G$ is \emph{commutative} if
-\[
-\cs{L} \cong q^* \cs{L}\ab
-\]
-for a commutative character sheaf $\cs{L}\ab$ on $G\ab$.  As in the commutative case,
-we write $\CCS(G)$ for the full subcategory of $\CS(G)$ consisting of commutative character sheaves.
-\end{definition}
-\fi
+%\section{Descent to the Abelianization} \label{sec:descent}
 
-\iffalse
-Note that we may also pull back the map $\xi\ab : m\ab^* \cs{L}\ab \to \theta\ab^*(m\ab^* \cs{L})$ from Definition \ref{def:CCScom}.
-The following proposition will be proven in Section \ref{sec:descent}.
-
-\begin{proposition} \label{prop:Gdiagram}
-A linear character sheaf $(\cs{L}, \mu)$ on a smooth group scheme $G$ is commutative if and only if
-\begin{enumerate}
-\item $\cs{L} \cong q^* \cs{L}\ab$ for some character sheaf $\cs{L}\ab$ on $G\ab$,
-\item the following diagram of Weil sheaves on $G \times G$ commutes.
-  \[
-  \begin{tikzcd}[row sep=30]
-   m^*\cs{L} \arrow{d}[swap]{(q\times q)^*\xi\ab} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
-   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L})
-  \end{tikzcd}
-  \]
-\end{enumerate}
-\end{proposition}
-\fi
-
-\section{Eliminating Invisible Character Sheaves}\label{sec:defect}
-
-If $M$ is a $\bG$-module, then we say a cohomology class in $\Hh^2(\bG, M)$ is \emph{symmetric} if it is represented
-by a symmetric $2$-cocycle.  Since every coboundary is symmetric, either all cocycles in a given class will be symmetric
-or none will.
-
-\begin{lemma} \label{lem:symtriv}
-Let $\bG$ be a commutative group.  Then the only symmetric class in $\Hh^2(\bG, \EEx)$ is the trivial class.
-\end{lemma}
-
-\begin{proof}
-By the universal coefficient theorem,
-\[
-0 \to \Ext^1_\ZZ(\Hh_{n-1}(\bG, \ZZ), \EEx) \to \Hh^n(\bG, \EEx) \to \Hom(\Hh_n(\bG, \ZZ), \EEx) \to 0
-\]
-for all $n > 0$.  When $n = 2$, using the fact that $\bG$ is commutative, we have that $\Hh_1(\bG, \ZZ) \cong \bG$
-and that $\Hh_2(\bG, \ZZ) \cong \wedge^2 \bG$. We get
-\[
-0 \to \Ext^1_\ZZ(\bG, \EEx) \to \Hh^2(\bG, \EEx) \to \Hom(\wedge^2 \bG, \EEx) \to 0.
-\]
-The map $\Hh^2(\bG, \EEx) \to \Hom(\wedge^2 \bG, \EEx)$ maps a $2$-cocycle $f$ to the alternating function
-\[
-(x,y) \mapsto \frac{f(x,y)}{f(y,x)}.
-\]
-Thus the cohomology classes represented by symmetric cocycles are precisely those in the image of $\Ext^1_\ZZ(\bG, \EEx)$.
-But $\Ext^1_\ZZ(-, \EEx)$ vanishes because $\EEx$ is divisible.
-\end{proof}
-
-For a character sheaf $\cs{L}$ on $G$, recall from \cite{cunningham-roe:13a}*{\S 2.3} that $S_G : \CSiso{G} \to \Hh^2(E_G^\bullet)$ maps
-$[\cs{L}]$ to $[\alpha \oplus \beta]$, where $E_G^\bullet$ is the total space of the zeroth page
-of the Hochschild-Serre spectral sequence, $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$ is obtained from $\mu$ and
-$\beta \in C^1(\Weil{}, C^1(\bG, \EEx))$ is obtained from $\phi$.
-
-\begin{lemma} \label{lem:conncomm}
-If $G$ is a connected commutative algebraic group over $\Fq$ then every character sheaf on $G$ is commutative.
-\end{lemma}
-
-\begin{proof}
-We can use \'etale descent to see that pullback by the Lang isogeny defines an equivalence
-of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.  Thus every character
-sheaf on $G$ arises through the Lang isogeny; since the covering group is $G$ itself, which is commutative,
-every character sheaf on $G$ is commutative.
-\end{proof}
-
-\begin{theorem} \label{thm:trfrobiso}
-If $G$ is a smooth commutative group scheme over $\Fq$ then $\TrFrob{G} : \CCSiso{G} \to G(\Fq)^*$ is an isomorphism.
-\end{theorem}
-
-\begin{proof}
-Suppose first that $G$ is \'etale.  Consider the isomorphism of short exact sequences
-\[
-\begin{tikzcd}
- 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \CSiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
-  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\bG,\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1(\bG,\EEx)) \arrow{r} & 0
- \end{tikzcd}
- \]
-from \cite{cunningham-roe:13a}*{Prop. 2.7}.
-
-Suppose that $\cs{L}$ is a commutative character sheaf
-with $\trFrob{\cs{L}} = 1$.  Then $S_G([\cs{L}])$ is in the image of $\Hh^2(\bG, \EEx)^\Weil{}$, so is cohomologous to
-$[\alpha', 0]$.  Since $\alpha$ is symmetric and coboundaries are symmetric, $\alpha'$ is symmetric as well.
-So by Lemma \ref{lem:symtriv}, $\alpha'$ is cohomologically trivial, and thus $[\cs{L}]$ is trivial as well.
-
-To see that $\TrFrob{G}$ is still surjective on $\CCSiso{G}$, note that the character sheaf constructed in the proof of
-\cite{cunningham-roe:13a}*{Prop. 2.6} has trivial $\alpha$, and is thus commutative.
-
-For general smooth commutative group schemes, we use Lemma \ref{lem:conncomm} and the snake lemma.
-\end{proof}
-
-\begin{remark}
-Since $\Hh^0(\Weil{},\Hh^2(\bG,\EEx))$ is not necessarily trivial \cite{cunningham-roe:13a}*{Ex. 2.10}, the functor
-$\CCS(G) \to \CS(G)$ is not an equivalence of categories in general.
-\end{remark}
-
-\section{Descent to the Abelianization} \label{sec:descent}
-
-In this section we use descent along the abelianization $q : G \to G\ab$ to prove Propositions~1.2 and 1.4, and Theorem~\ref{thm:Gab}.
-This approach requires introducing equivariant linear character sheaves, as defined in Section~[].
+%In this section we use descent along the abelianization $q : G \to G\ab$ to prove Propositions~1.2 and 1.4, and Theorem~\ref{thm:Gab}.
+%This approach requires introducing equivariant linear character sheaves, as defined in Section~[].
 
@@
 
-Let $G$ be as above.
+Let $G$ be a smooth group scheme over $k$, as above.
 Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
@@
 
-An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense. 
+An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense \todo{of...}. 
 Consider the following morphisms: $c_0 : H\times G \times G\to H\times G \times H \times G$ defined by $c_0(h,g_1,g_2)\ceq(h,g_1,h,g_2)$;
@@
 
-A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves.
+A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ \todo{How does this $\nu$ give you the $\nu$ of Section 3.2?} which is also a morphism of linear character sheaves.
 %so
@@
 Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(m^*\cs{L}, m_2^*(\mu))$, where $m_2 : G\times G\times G\times G\to G\times G$ is defined by $m_2(x_1,y_1,x_2,y_2) = (m(x_1,x_2), m(y_1,y_2)$;
-this can be seen by following the argument of \cite{cunningham-roe:13a}].
-Set $\cs{L}_2\ceq m^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
+this can be seen by following the argument of \cite{cunningham-roe:13a} \todo{which part of [2]?}.
+Set $\cs{L}_2\ceq m_2^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
 The linear character sheaf $(\cs{L}_2,\mu_2)$ comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ where $a_2 : H\times H\times G\times G\to G\times G$ is given by $a_2(h_1,g_1,h_2,g_2) = (a(h_1,g_1), a(h_2,g_2)$ and $p_2 : H\times H\times G\times G\to G\times G$ is given by $p_2(h_1,g_1,h_2,g_2)= ( g_1,g_2)$.
-The  isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ satisfies the appropriate version of \eqref{ECS1}, so  $(\cs{L}_2,\mu_2,nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
+The  isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ satisfies the appropriate version of \eqref{ECS1}, so  $(\cs{L}_2,\mu_2,\nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
 Likewise $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
@@
 & 
-G_0
+G_0.
 \end{tikzcd}
@@
 & (q\circ p)^*\cs{L}_0 \arrow{r} 
-& p^* q^*\cs{L}_0
+& p^* (q^*\cs{L}_0)
 \end{tikzcd}
@@
 Since $q : G\to G_0$ is an $H$-torsor in the fppf topology, is now follows from descent theory that the comparison functor $\Loc(G_0) \to \Loc_H(G)$ is an equivalence [Vistoli].
+\todo{Need more specific references}
 
@@
 Arguing as above, we also see that pull-back along $q\times q$ determines an equivalence $L_2 : \Loc(G_0\times G_0) \to \Loc_{H\times H}(G\times G)$.
-For use below, we write $L_2 : \Loc_{H\times H}(G\times G) \to \Loc(G_0\times G_0)$ for its adjoint and $(\epsilon_2, \eta_2)$ for the counit and unit of the adjunction.
+For use below, we write $R_2 : \Loc_{H\times H}(G\times G) \to \Loc(G_0\times G_0)$ for its adjoint and $(\epsilon_2, \eta_2)$ for the counit and unit of the adjunction.
 
-We may now revisit the definition of the functor $q_H^*: \CS(Q)\to \CS_H(G)$.
+We may now revisit the definition of the functor $q_H^*: \CS(Q)\to \CS_H(G)$.  \todo{Change of notation $G_0$ to $Q$}
 By (a small part of) Lemma~\ref{lem:HH}, $\mu_0$ is a morphism of linear character sheaves on $G_0\times G_0$.
@@
 With this description of $q_H^*: \CS(Q)\to \CS_H(G)$ is is easy to see that it is an equivalence.
-Its adjoint is given on objects by $(\cs{L},\mu,\nu) \mapsto (L_1(\cs{L},\nu), L_2(\nu))$, again making use of Lemma~\ref{lem:HH}, and on objects by $\alpha \mapsto L_1(\alpha)$.
+Its adjoint is given on objects by $(\cs{L},\mu,\nu) \mapsto (L_1(\cs{L},\nu), L_2(\nu))$, \todo{Shouldn't these be Rs?} again making use of Lemma~\ref{lem:HH}, and on morphisms by $\alpha \mapsto L_1(\alpha)$ \todo{Again, R?}.
 The adjunction is built from the adjunctions for $(L_1,R_1)$ and $(L_2, R_2)$.
@@
 \end{equation}
-or more precisely, by the following diagram of isomorphisms.
+or more precisely, by the following diagram of isomorphisms. \todo{What is $p_1$? And $p_\circ f$?}
 \[
@@
 This isomorphism is constrained conditions from Sections~\ref{ssec:equivariant1} and \ref{ssec:equivariant2} as they apply to $\nu : a^*\cs{L}\to p^*\cs{L}$.
-It is straightforward but quite unpleasant matter to show that those conditions are exactly equivalent to the condition that the isomorphism Weil local systems $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is an isomorphism in the category of of linear character sheaves on $H$.
+\todo{We seem to be missing a preposition}
+It is straightforward, tedious exercise to show that those conditions are exactly equivalent to the condition
+that the isomorphism of Weil local systems $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is an isomorphism in the category of of linear character sheaves on $H$.
 \end{proof}
 
-\subsection{Proofs for results from Section \ref{sec:defs}}\label{ssec:proofs}
+\subsection{Proofs for results from Section \ref{ssec:noncomdef}}\label{ssec:proofs}
 
-We can now give the missing proofs from Section \ref{sec:defs}.
+We can now give the missing proofs from Section \ref{ssec:noncomdef}.
 
@@
 %
-Here we use the notation $\CS'(G)$ from Section~\ref{ssec:noncom} and the observation that it is precisely the category $\CS^{G\der}(G)$, taking the case $H=G\der$ in Section~\ref{ssec:closed}.
+Here we use the notation $\CS'(G)$ from Section~\ref{ssec:noncomdef} and the observation that it is precisely the category $\CS^{G\der}(G)$, taking the case $H=G\der$ in Section~\ref{ssec:closed}.
 Since the quotient $q : G \to G\ab$ is a trivial $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}, 
@@
 we must show that $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
-Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ as in Section~\ref{ssec:comcom}.
-Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ as in Section~\ref{ssec:noncom}.
+Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ as in Section~\ref{sec:comcom}.
+Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ as in Section~\ref{ssec:noncomdef}.
 Then the diagram in Definition~\ref{def:CCS} is precisely the result of applying the functor $(q\times q)^*$ to the diagram in Definition~\ref{def:CCScom}; 

### 2015-11-13 followup.tex
Removed a remark.

@@
  \end{definition}
-\todo{Add some remarks and/or promise examples showing that $\CCS(G)$ need not be $\CS(G)$, even in the Abelian case.
-I'm wondering about the structure of the paper. 
-Would it make sense to really explore the Abelian case, before moving to the non-Abelian case?
-That would mean moving the material from Section~Invisible up to here.
-That would put the justification(s) for this definition in closer proximity with this definition.}
 

### 2015-11-13 followup.tex
align* for b functions
In the sense of ECS1...

@@
 \]
-defined by $b_1(h_1,h_2,g) = (n(h_1,h_2),g)$,  $b_2(h_1,h_2,g) = (h_1,a(h_2,g))$ and $b_3(h_1,h_2,g) = (h_2,g)$.
+defined by 
+\begin{align*}
+b_1(h_1,h_2,g) &= (h_1h_2,g) \\
+b_2(h_1,h_2,g) &= (h_1,h_2g) \\
+b_3(h_1,h_2,g) &= (h_2,g).
+\end{align*}
 Then, $a\circ b_1 = a\circ b_2$ and $a\circ b_3 = p\circ b_2$ and $p\circ b_1 = p\circ b_3$.
@@
 
-An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense \todo{of...}. 
+An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense of \eqref{ECS1}.
 Consider the following morphisms: $c_0 : H\times G \times G\to H\times G \times H \times G$ defined by $c_0(h,g_1,g_2)\ceq(h,g_1,h,g_2)$;

### 2015-11-13 followup.tex
... as we now explain.

@@
 
-An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense of \eqref{ECS1}.
+An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$, as we now explain.
 Consider the following morphisms: $c_0 : H\times G \times G\to H\times G \times H \times G$ defined by $c_0(h,g_1,g_2)\ceq(h,g_1,h,g_2)$;

### 2015-11-13 followup.tex
aligning the cs

@@
 
-An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$, as we now explain.
-Consider the following morphisms: $c_0 : H\times G \times G\to H\times G \times H \times G$ defined by $c_0(h,g_1,g_2)\ceq(h,g_1,h,g_2)$;
-$c_1 : H \times G\times G \to G\times G$ defined by $c_1(h, g_1, g_2) \ceq (a(h,g_1),a(h,g_2))$;  $c_2 : H \times G\times G \to H\times G$ defined by $c_2(h,g_1,g_2) \ceq (h, m(g_1,g_2))$; and $c_3 : H \times G\times G \to G\times G$ defined by $c_3(h, g_1, g_2) = (g_1, g_2)$.
+An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense \todo{of...}. 
+Consider the following morphisms:
+\begin{align*}
+c_0 : H\times G \times G &\to H\times G \times H \times G \\
+(h,g_1,g_2) &\mapsto (h,g_1,h,g_2); \\
+c_1 : H \times G\times G &\to G\times G \\
+(h, g_1, g_2) &\mapsto (a(h,g_1),a(h,g_2)); \\
+c_2 : H \times G\times G &\to H\times G \\
+(h,g_1,g_2) &\mapsto (h, m(g_1,g_2)) \\
+c_3 : H \times G\times G &\to G\times G \\
+(h, g_1, g_2) &\mapsto (g_1, g_2).
+\end{align*}
 Then $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ if $(\cs{L},\mu)$ is a linear character sheaf on $G$ and the following diagram of Weil local systems on $H \times G\times G$ commutes.

### 2015-11-13 followup.tex

@@
 
-An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$ in the sense \todo{of...}. 
+An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$, as we now explain.
 Consider the following morphisms:

### 2015-11-13 followup.tex
remove an a and m
Clarify compatibility of mu and nu

@@
 
-An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $\nu$ is compatible with $\mu$, as we now explain.
-Consider the following morphisms:
+An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $(\cs{L},\nu)$ is an $H$-equivariant local system.
+We require that $\mu$ be compatible with $\nu$ in the following sense.
+We define morphisms:
 \begin{align*}
@@
 c_1 : H \times G\times G &\to G\times G \\
-(h, g_1, g_2) &\mapsto (a(h,g_1),a(h,g_2)); \\
+(h, g_1, g_2) &\mapsto (hg_1,hg_2); \\
 c_2 : H \times G\times G &\to H\times G \\
-(h,g_1,g_2) &\mapsto (h, m(g_1,g_2)) \\
+(h,g_1,g_2) &\mapsto (h, g_1g_2); \\
 c_3 : H \times G\times G &\to G\times G \\
@@
 \end{align*}
-Then $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ if $(\cs{L},\mu)$ is a linear character sheaf on $G$ and the following diagram of Weil local systems on $H \times G\times G$ commutes.
+We require that the following diagram of Weil local systems on $H \times G\times G$ commutes:
 \begin{equation}\label{ECS1}
@@
 \end{equation}
-\iffalse
-On stalks, this condition is
-\[
-\begin{tikzcd}
-\arrow{d}[swap]{\mu_{(h\cdot g_1, h\cdot g_2)}} \cs{L}_{(h\cdot g_1)(h\cdot g_2)} & \arrow[equal]{l}  \cs{L}_{h\cdot(g_1 g_2)} \arrow{r}{\nu_{(h, g_2 g_2)}} & \cs{L}_{g_1 g_2} \arrow[equal]{r} & \cs{L}_{g_1 g_2} \arrow{d}{\mu_{(g_1,g_2)}} \\
-\cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow[equal]{r} & \cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow{r}{\nu_{(h,g_1)}\otimes \nu_{(h,g_2)}} & \cs{L}_{g_1}\otimes \cs{L}_{g_2} & \arrow[equal]{l} \cs{L}_{g_1} \otimes \cs{L}_{g_2},
-\end{tikzcd}
-\]
-for all $(h,g_1,g_2)\in H\times G\times G$.
-\fi
 
-A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ \todo{How does this $\nu$ give you the $\nu$ of Section 3.2?} which is also a morphism of linear character sheaves.
+%On stalks, this condition is
+%\[
+%\begin{tikzcd}
+%\arrow{d}[swap]{\mu_{(h\cdot g_1, h\cdot g_2)}} \cs{L}_{(h\cdot g_1)(h\cdot g_2)} & \arrow[equal]{l}  \cs{L}_{h\cdot(g_1 g_2)} \arrow{r}{\nu_{(h, g_2 g_2)}} & \cs{L}_{g_1 g_2} \arrow[equal]{r} & \cs{L}_{g_1 g_2} \arrow{d}{\mu_{(g_1,g_2)}} \\
+%\cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow[equal]{r} & \cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow{r}{\nu_{(h,g_1)}\otimes \nu_{(h,g_2)}} & \cs{L}_{g_1}\otimes \cs{L}_{g_2} & \arrow[equal]{l} \cs{L}_{g_1} \otimes \cs{L}_{g_2},
+%\end{tikzcd}
+%\]
+%for all $(h,g_1,g_2)\in H\times G\times G$.
+
+A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves.
 %so

### 2015-11-13 followup.tex
Defines p1 and p2 and other small improvements

@@
 With this description of $q_H^*: \CS(Q)\to \CS_H(G)$ is is easy to see that it is an equivalence.
-Its adjoint is given on objects by $(\cs{L},\mu,\nu) \mapsto (L_1(\cs{L},\nu), L_2(\nu))$, \todo{Shouldn't these be Rs?} again making use of Lemma~\ref{lem:HH}, and on morphisms by $\alpha \mapsto L_1(\alpha)$ \todo{Again, R?}.
+Its adjoint is given on objects by $(\cs{L},\mu,\nu) \mapsto (R_1(\cs{L},\nu), R_2(\nu))$, again making use of Lemma~\ref{lem:HH}, and on morphisms by $\alpha \mapsto R_1(\alpha)$.
 The adjunction is built from the adjunctions for $(L_1,R_1)$ and $(L_2, R_2)$.
@@
 %\]
-Define $f : H\times G \to G\times G$ by $f(h,g) = (i(h),g)$ and note that $a = m\circ f$ and $p = p_2\circ f$.
-% (a(h,g) g^{-1}, g) = (h,g)$.
-%Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq (i\circ p_1)$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
+Define $f : H\times G \to G\times G$ by $f(h,g) = (i(h),g)$ and note that $a = m\circ f$.
 Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
@@
 \end{equation}
-or more precisely, by the following diagram of isomorphisms. \todo{What is $p_1$? And $p_\circ f$?}
+or more precisely, by the following diagram of isomorphisms, where we write $p_1: G\times G\to G$ for projection to the first component and $p_2 : G\times G \to G$ for projection to the second.
 \[
@@
 \ & a^*\cs{L} \arrow{dl}{m\circ f = a} \arrow{r}{\nu} & p^*\cs{L} & \\
-f^* m^*\cs{L} \arrow{dr}{f^*\mu} &&& (\EE)_{H} \boxtimes \cs{L} \arrow{ul}{p= p_1} \\ 
-& f^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_\circ f = i}[swap]{p_2\circ f = \id}  & 
+f^* m^*\cs{L} \arrow{dr}{f^*\mu} &&& (\EE)_{H} \boxtimes \cs{L} \arrow{ul} \\ 
+& f^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_1 \circ f = i}[swap]{p_2\circ f = \id}  & 
 \cs{L}\vert_{H} \boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id} & 

### 2015-11-13 followup.tex
Improving 3.2

--- 2015-11-13 followup.tex
@@
 \hyphenation{quasi-character}
+%% Number one equation of many
+\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
 
@@
 \end{align*}
-Then, $a\circ b_1 = a\circ b_2$ and $a\circ b_3 = p\circ b_2$ and $p\circ b_1 = p\circ b_3$.
+Note that
+\begin{align*}
+a\circ b_1 &= a\circ b_2 \\
+a\circ b_3 &= p\circ b_2 \numberthis \label{eqn:bap}\\
+p\circ b_1 &= p\circ b_3.
+\end{align*}
 Define $s : G\to H\times G$ by $s(g) = (1,g)$.
@@
 \end{equation}
-In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations above; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
-\iffalse
-On stalks, this condition is ...
-\[
-\begin{tikzcd}
-\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
-\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
-& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
-\end{tikzcd}
-\]
-\fi
+In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from equations \eqref{eqn:bap}; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
+%On stalks, this condition is ...
+%\[
+%\begin{tikzcd}
+%\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
+%\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
+%& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
+%\end{tikzcd}
+%\]
 Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram

### 2015-11-13 followup.tex
Preposition and a few references and citations.

--- 2015-11-13 followup.tex
@@
 \begin{proof} 
-Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(m^*\cs{L}, m_2^*(\mu))$, where $m_2 : G\times G\times G\times G\to G\times G$ is defined by $m_2(x_1,y_1,x_2,y_2) = (m(x_1,x_2), m(y_1,y_2)$;
-this can be seen by following the argument of \cite{cunningham-roe:13a} \todo{which part of [2]?}.
+Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(m^*\cs{L}, m_2^*(\mu))$, where $m_2 : G\times G\times G\times G\to G\times G$ is defined by $m_2(x_1,y_1,x_2,y_2) = (m(x_1,x_2), m(y_1,y_2)$; compare with \cite{cunningham-roe:13a}*{Lemma 1.4}.
 Set $\cs{L}_2\ceq m_2^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
@@
 
-We may now revisit the definition of the functor $q_H^*: \CS(Q)\to \CS_H(G)$.  \todo{Change of notation $G_0$ to $Q$}
+We may now revisit the definition of the functor $q_H^*: \CS(G_0)\to \CS_H(G)$. 
 By (a small part of) Lemma~\ref{lem:HH}, $\mu_0$ is a morphism of linear character sheaves on $G_0\times G_0$.
@@
 We have seen how every $(\cs{L},\mu,\nu)\in \CS_H(G)$ determines an isomorphism of Weil local systems $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$.
-This isomorphism is constrained conditions from Sections~\ref{ssec:equivariant1} and \ref{ssec:equivariant2} as they apply to $\nu : a^*\cs{L}\to p^*\cs{L}$.
-\todo{We seem to be missing a preposition}
-It is straightforward, tedious exercise to show that those conditions are exactly equivalent to the condition
+This isomorphism is constrained by the conditions 
+appearing in \eqref{E1}, \eqref{E2} and \eqref{ECS1}.
+It is a straightforward, tedious exercise to show that those conditions are exactly equivalent to the condition
 that the isomorphism of Weil local systems $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is an isomorphism in the category of of linear character sheaves on $H$.

### 2015-11-13 followup.tex
Replaced Gder with H in proofs. Added iso to diagrams.

--- 2015-11-13 followup.tex
@@
 
-For use below, we write $L_1 : \Loc(G_0) \to \Loc_H(G)$ for the comparison functor, $R_1 : \Loc_H(G) \to Loc(G_0)$ for its adjoint, and $(\epsilon_1, \eta_1)$ for the counit and unit of the adjunction.
+For use below, we write $L_1 : \Loc(G_0) \to \Loc_H(G)$ for the comparison functor, $R_1 : \Loc_H(G) \to \Loc(G_0)$ for its adjoint, and $(\epsilon_1, \eta_1)$ for the counit and unit of the adjunction.
 %
@@
 The abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
+Set $H=G\der$.
 Now,
@@
 %{} & G\times G \arrow{d}{c} &&&\\
-1 \arrow{r} & G\der \arrow{r}{i} & G \arrow{r}{q} & G\ab \arrow{r} & 1
+1 \arrow{r} & H \arrow{r}{i} & G \arrow{r}{q} & G\ab \arrow{r} & 1
 \end{tikzcd}
@@
 \begin{tikzcd}
-\ & \CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
-\CS(G\ab) \arrow{dl}{q_{G\der}^*} \\
-\CS^{G\der}(G) & \arrow[equal]{l} \CS'(G) \arrow{u}{\text{forget}}  \arrow{r}{\beta \mapsto \nu} &  \CS_{G\der}(G) \arrow{u}{\text{forget}}  & 
+\CS(H) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
+\CS(G\ab) \arrow{dl}{q_{H}^*}[swap]{\iso} \\
+ \CS'(G) \arrow{u}{\text{forget}}  \arrow{r}{\beta \mapsto \nu}[swap]{\iso} &  \CS_{H}(G) \arrow{u}{\text{forget}}  & 
 \end{tikzcd}
@@
 %
-Here we use the notation $\CS'(G)$ from Section~\ref{ssec:noncomdef} and the observation that it is precisely the category $\CS^{G\der}(G)$, taking the case $H=G\der$ in Section~\ref{ssec:closed}.
-Since the quotient $q : G \to G\ab$ is a trivial $G\der$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}, 
-it now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{G\der}(G)$ is an equivalence.
-On the other hand, by Lemma~\ref{lem:beta}, $\CS'(G) \to \CS_{G\der}(G)$, defined by $(\cs{L},\mu,\beta)\mapsto (\cs{L},\mu, \nu)$, is an equivalence.
-Since the essential image of the forgetful functor $\CS'(G)\to \CS(G)$ is precisely the category of $(\cs{L},\mu)\in \CS(G)$ such that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$, this completes the proof of Proposition~\ref{prop:Gder_triv}.
-%that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ if and only if $\cs{L} = q^*\cs{L}\ab$ for some $\cs{L}\ab \in \CS(G\ab)$.
+Here we use the notation $\CS'(G)$ from Section~\ref{ssec:noncomdef} and the observation that it is precisely the category $\CS^{H}(G)$ from Section~\ref{ssec:closed} for $H=G\der$.
+Since the quotient $q : G \to G\ab$ is a trivial $H$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}, 
+it now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{H}(G)$ is an equivalence.
+On the other hand, by Lemma~\ref{lem:beta}, $\CS'(G) \to \CS_{H}(G)$, defined by $(\cs{L},\mu,\beta)\mapsto (\cs{L},\mu, \nu)$, is an equivalence.
+Since the essential image of the forgetful functor $\CS'(G)\to \CS(G)$ is precisely the category of $(\cs{L},\mu)\in \CS(G)$ such that $\cs{L}\vert_{H} \iso (\EE)_{H}$, this completes the proof of Proposition~\ref{prop:Gder_triv}.
 \end{proof}
@@
 \begin{proof}[Proof of Theorem~\ref{thm:Gab}] 
+Here we use notation from the proof of Proposition~\ref{prop:Gder_triv};
+in particular, $H = G\der$.
 By Definition~\ref{def:CCScom}, $\CCS(G\ab) \to \CS(G\ab)$ is a full subcategory.
-Since the comparison functor $\CS(G\ab) \to \CS_{G\der}(G)$ is an equivalence, it determines a full subcategory $\CCS_{G\der}(G)$ which is equivalent to $\CCS(G\ab)$, as pictured below.
-The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of the equivalence $\CS_{G\der}(G) \to \CS'(G)$ is $\CCS(G)$.
+Since the comparison functor $\CS(G\ab) \to \CS_{H}(G)$ is an equivalence, it determines a full subcategory $\CCS_{H}(G)$ which is equivalent to $\CCS(G\ab)$, as pictured below.
+The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of the equivalence $\CS_{H}(G) \to \CS'(G)$ is $\CCS(G)$.
 \[
 \begin{tikzcd}
-\CS(G\der) 
+\CS(H) 
 & \arrow{l}[swap]{i^*} \CS(G) 
 &\arrow{l}[swap]{q^*} 
-\CS(G\ab) \arrow{dl}{q_{G\der}^*} \\
-\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu} 
-&  \CS_{G\der}(G) \arrow{u}{\text{forget}}  
-&  \arrow[bend left=35pt, dashed]{dll} \CCS(G\ab) \arrow{u} \arrow{dl} \\
-\CCS(G) \arrow{u} \arrow{r}{\beta \mapsto \nu} 
-& \arrow{u}  \CCS_{G\der}(G) 
+\CS(G\ab) \arrow{dl}{q_{H}^*}[swap]{\iso} \\
+\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu}[swap]{\iso} 
+&  \CS_{H}(G) \arrow{u}{\text{forget}}  
+&  \arrow[bend left=35pt, dashed]{dll} \CCS(G\ab) \arrow{u} \arrow{dl}[swap]{\iso} \\
+\CCS(G) \arrow{u} \arrow{r}{\beta \mapsto \nu}[swap]{\iso}
+& \arrow{u}  \CCS_{H}(G) 
 & 
@@
 Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ as in Section~\ref{sec:comcom}.
-Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ as in Section~\ref{ssec:noncomdef}.
+Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ as in Section~\ref{ssec:noncomdef}.
 Then the diagram in Definition~\ref{def:CCS} is precisely the result of applying the functor $(q\times q)^*$ to the diagram in Definition~\ref{def:CCScom}; 
 in particular $\gamma = (q\times q)^* \xi$.
-Together with Lemma~\ref{lem:HH}, we may now interpret the diagram in Definition~\ref{def:CCS} as a diagram in $\CS_{G\der\times G\der}(G\times G)$.
+Together with Lemma~\ref{lem:HH}, we may now interpret the diagram in Definition~\ref{def:CCS} as a diagram in $\CS_{H\times H}(G\times G)$.
 By Lemma~\ref{lem:beta}, this corresponds uniquely to a diagram in $\CS(G\ab\times G\ab)$, necessarily the diagram in Definition~\ref{def:CCScom}.

### 2015-11-13 followup.tex
Messing with proof of Lemma 3.4

--- 2015-11-13 followup.tex
@@
 \begin{proof} 
-Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(m^*\cs{L}, m_2^*(\mu))$, where $m_2 : G\times G\times G\times G\to G\times G$ is defined by $m_2(x_1,y_1,x_2,y_2) = (m(x_1,x_2), m(y_1,y_2)$; compare with \cite{cunningham-roe:13a}*{Lemma 1.4}.
-Set $\cs{L}_2\ceq m_2^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
-The linear character sheaf $(\cs{L}_2,\mu_2)$ comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ where $a_2 : H\times H\times G\times G\to G\times G$ is given by $a_2(h_1,g_1,h_2,g_2) = (a(h_1,g_1), a(h_2,g_2)$ and $p_2 : H\times H\times G\times G\to G\times G$ is given by $p_2(h_1,g_1,h_2,g_2)= ( g_1,g_2)$.
-The  isomorphism $\nu_2 : a_2^*\cs{L}_2\to p_2^*\cs{L}_2$ satisfies the appropriate version of \eqref{ECS1}, so  $(\cs{L}_2,\mu_2,\nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
-Likewise $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
+Define
+\begin{align*}
+m_2 : G\times G\times G\times G &\to G\times G \\
+(x_1,y_1,x_2,y_2) &\mapsto (x_1x_2, y_1y_2) \\
+a_2 : H\times G\times H\times G &\to G\times G \\
+(h_1,g_1,h_2,g_2) &\mapsto (h_1g_1, h_2g_2) \\
+p_2 : H\times G\times H\times G &\to G\times G \\
+(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2)
+\end{align*}
+and set $\cs{L}_2\ceq m_2^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
+Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(\cs{L}_2, \mu_2)$ on $G \times G$ (see \cite{cunningham-roe:13a}*{Lemma 1.4}),
+which comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2 \to p_2^*\cs{L}_2$. 
+This isomorphism satisfies the appropriate version of \eqref{ECS1}, so  $(\cs{L}_2,\mu_2,\nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
+Likewise, $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
 \[
@@
 \]
+By abuse of notation, we will also refer to the missing vertical map down the center of this diagram as $\nu \boxtimes \nu$.
 Since this diagram commutes, $(\cs{L}\boxtimes \cs{L},\mu\boxtimes \mu,\nu\boxtimes\nu)$ is also an $H\times H$-equivariant linear character sheaf on $G\times G$.
-The appropriate version of \eqref{E3} also commutes, so $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism of equivariant linear character sheaves.
+The appropriate version of \eqref{E3} also commutes, so we can reinterpret
+\[
+\mu : (\cs{L}_2, \mu_2, \nu_2) \to (\cs{L}\boxtimes\cs{L}, \mu \boxtimes \mu, \nu \boxtimes \nu)
+\]
+as a morphism of equivariant linear character sheaves.
 The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is morphism of $H\times H$-equivariant linear character sheaves on $G\times G$ is also straightforward.

### 2015-11-13 followup.tex
Added some todos

@@
 Then $c$ is a smooth morphism of $\Fq$ schemes and $c = m \circ (m \times (i \circ m \circ \theta))$.
-Thus, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_G\otimes (\EE)_G$ by the diagram
+Thus, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_G\otimes (\EE)_G$ by the diagram \todo{Fix this diagram.}
 \[
@@
 and set $\cs{L}_2\ceq m_2^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
-Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(\cs{L}_2, \mu_2)$ on $G \times G$ (see \cite{cunningham-roe:13a}*{Lemma 1.4}),
+Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(\cs{L}_2, \mu_2)$ on $G \times G$ (see \cite{cunningham-roe:13a}*{Lemma 1.4}), \todo{False, because $m$ is not a group homorphism.}
 which comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2 \to p_2^*\cs{L}_2$. 

### 2015-11-13 followup.tex
Started fixing Lemma 3.4.

@@
 \begin{lemma}\label{lem:HH}
-If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of $H\times H$-equivariant linear character sheaves on $G\times G$; likewise $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$.
+If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of $H\times H$-equivariant Weil local systems on $G\times G$; likewise $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$.
 \end{lemma}
@@
 and set $\cs{L}_2\ceq m_2^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
-Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(\cs{L}_2, \mu_2)$ on $G \times G$ (see \cite{cunningham-roe:13a}*{Lemma 1.4}), \todo{False, because $m$ is not a group homorphism.}
-which comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2 \to p_2^*\cs{L}_2$. 
-This isomorphism satisfies the appropriate version of \eqref{ECS1}, so  $(\cs{L}_2,\mu_2,\nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
+The Weil local system $\cs{L}_2$ on $G \times G$ comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2 \to p_2^*\cs{L}_2$ defined by ...\todo{Working here.}
+This isomorphism satisfies \eqref{E1} and \eqref{E2} as they apply here.
+%
 Likewise, $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
@@
 as a morphism of equivariant linear character sheaves.
-The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is morphism of $H\times H$-equivariant linear character sheaves on $G\times G$ is also straightforward.
+The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is morphism of $H\times H$-equivariant linear character sheaves on $G\times G$ is also straightforward.\todo{Add detail here.}
 \end{proof}
@@
 We may now revisit the definition of the functor $q_H^*: \CS(G_0)\to \CS_H(G)$. 
-By (a small part of) Lemma~\ref{lem:HH}, $\mu_0$ is a morphism of linear character sheaves on $G_0\times G_0$.
-Thus, on objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$. 
+On objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$. 
 To verify that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$, one must confirm \cite{cunningham-roe:13a}*{CS1, CS2, CS3}, \eqref{E1}, \eqref{E2} and \eqref{ECS1}. 
@@
 in particular $\gamma = (q\times q)^* \xi$.
-Together with Lemma~\ref{lem:HH}, we may now interpret the diagram in Definition~\ref{def:CCS} as a diagram in $\CS_{H\times H}(G\times G)$.
-By Lemma~\ref{lem:beta}, this corresponds uniquely to a diagram in $\CS(G\ab\times G\ab)$, necessarily the diagram in Definition~\ref{def:CCScom}.
+Together with Lemma~\ref{lem:HH}, we may now interpret the diagram in Definition~\ref{def:CCS} as a diagram in $\Loc_{H\times H}(G\times G)$.
+By Lemma~\ref{lem:torsor}, this corresponds uniquely to a diagram in $\Loc(G\ab\times G\ab)$, necessarily the diagram in Definition~\ref{def:CCScom}.
 It follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes. 

### 2015-11-13 followup.tex
I have fixed the problem you identified last night.

@@
 \begin{align*}
-m_2 : G\times G\times G\times G &\to G\times G \\
-(x_1,y_1,x_2,y_2) &\mapsto (x_1x_2, y_1y_2) \\
+d : H\times H\times G\times G &\to H\times G\times H\times G \\
+(h_1,h_2,g_1,g_2) &\mapsto (h_1, g_1, h_2, g_2)\\
 a_2 : H\times G\times H\times G &\to G\times G \\
@@
 p_2 : H\times G\times H\times G &\to G\times G \\
-(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2)
+(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2).
 \end{align*}
-and set $\cs{L}_2\ceq m_2^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
-The Weil local system $\cs{L}_2$ on $G \times G$ comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2 \to p_2^*\cs{L}_2$ defined by ...\todo{Working here.}
-This isomorphism satisfies \eqref{E1} and \eqref{E2} as they apply here.
-%
-Likewise, $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
+The following diagram defines the isomorphisms needed to see that both $m^*\cs{L}$ and $\cs{L}\boxtimes\cs{L}$ are $H\times H$-equivariant Weil local systems.
+\[
+\begin{tikzcd}[column sep=40]
+\arrow{d}[swap]{a_2(\mu)} a_2^* (m^*\cs{L}) \arrow[dashed]{r} 
+	& \arrow{d}{p_2^*(\mu)} p_2^*(m^*\cs{L})\\
+\arrow{d}[swap]{a_2= (a\times a)\circ d} a_2^*(\cs{L}\boxtimes\cs{L}) \arrow[dashed]{r} 
+	& \arrow{d}{p_2= (p\times p)\circ d} p_2^*(\cs{L}\boxtimes\cs{L}) \\
+%d^* (a\times a)^* (\cs{L}\boxtimes\cs{L}) & d^* (p\times p)^* (\cs{L}\boxtimes\cs{L}) \\
+d^* (a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{d^*(\nu\boxtimes \nu)}& d^*(p^*\cs{L}\boxtimes p^*\cs{L}) 
+\end{tikzcd}
+\]
+The dashed arrows both satisfy \eqref{E1} and \eqref{E2} as they apply here.
+This diagram also shows that $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of equivariant sheaves, since it satisfies \eqref{E3} as it applies here.
+The proof that $\theta^*(\cs{L}\boxtimes\cs{L})$ is also straightforward, since $a_2\circ \theta = \theta_2 \circ a_2$ and $p_2\circ \theta = \theta_2 \circ p_2$ for the obvious $\theta_2$.
+Let $\nu_2 : a_2^*(\cs{L}\boxtimes\cs{L}) \to p_2^*(\cs{L}\boxtimes\cs{L})$ be the middle horizontal isomorphism of Weil local systems, above. 
+Then, to see that
 \[
 \begin{tikzcd}
-\arrow{d}[swap]{\nu_2} a_2^*(m^*\cs{L}) \arrow{r}{a_2^*(\mu)} & a_2^*(\cs{L}\boxtimes\cs{L})  \arrow{r} & (a^*\cs{L})\boxtimes (a^*\cs{L}) \arrow{d}{\nu\boxtimes\nu} \\
-p_2^*(m^*\cs{L}) \arrow{r}{p_2^*(\mu)} & p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r} & (p^*\cs{L})\boxtimes (p^*\cs{L}) 
+a_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r}{a_2^*(\vartheta)} \arrow{d}[swap]{\nu_2} 
+	& a_2^*\theta^*(\cs{L}\boxtimes\cs{L}) \arrow{d}{\theta^*(\nu_2)} \\
+p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r}{p_2^*(\vartheta)} 
+	& p_2^*\theta^*(\cs{L}\boxtimes\cs{L})
 \end{tikzcd}
 \]
-By abuse of notation, we will also refer to the missing vertical map down the center of this diagram as $\nu \boxtimes \nu$.
-Since this diagram commutes, $(\cs{L}\boxtimes \cs{L},\mu\boxtimes \mu,\nu\boxtimes\nu)$ is also an $H\times H$-equivariant linear character sheaf on $G\times G$.
-The appropriate version of \eqref{E3} also commutes, so we can reinterpret
+commutes, consider the commuting diagram of stalks, below.
 \[
-\mu : (\cs{L}_2, \mu_2, \nu_2) \to (\cs{L}\boxtimes\cs{L}, \mu \boxtimes \mu, \nu \boxtimes \nu)
+\begin{tikzcd}
+\cs{L}_{h_1g_1}\otimes\cs{L}_{h_2g_2} \arrow{r}{\vartheta}  \arrow{d}[swap]{\nu_2} 
+	& \cs{L}_{h_2g_2} \otimes\cs{L}_{h_1g_1}  \arrow{d}{\nu_2} \\
+\cs{L}_{g_1}\otimes\cs{L}_{g_2} \arrow{r}{\vartheta}  
+	& \cs{L}_{g_2} \otimes\cs{L}_{g_1}
+\end{tikzcd}
 \]
-as a morphism of equivariant linear character sheaves.
-The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is morphism of $H\times H$-equivariant linear character sheaves on $G\times G$ is also straightforward.\todo{Add detail here.}
 \end{proof}
@@
 With this description of $q_H^*: \CS(Q)\to \CS_H(G)$ is is easy to see that it is an equivalence.
-Its adjoint is given on objects by $(\cs{L},\mu,\nu) \mapsto (R_1(\cs{L},\nu), R_2(\nu))$, again making use of Lemma~\ref{lem:HH}, and on morphisms by $\alpha \mapsto R_1(\alpha)$.
+Its adjoint is given on objects by $(\cs{L},\mu,\nu) \mapsto (R_1(\cs{L},\nu), R_2(\nu))$, making use of Lemma~\ref{lem:HH}, and on morphisms by $\alpha \mapsto R_1(\alpha)$.
 The adjunction is built from the adjunctions for $(L_1,R_1)$ and $(L_2, R_2)$.
@@
 %
-Here we use the notation $\CS'(G)$ from Section~\ref{ssec:noncomdef} and the observation that it is precisely the category $\CS^{H}(G)$ from Section~\ref{ssec:closed} for $H=G\der$.
+Here we use the notation $\CS'(G)$ from Section~\ref{ssec:noncomdef} and the observation that $\CS'(G)$ is precisely the category $\CS^{H}(G)$ from Section~\ref{ssec:closed} for $H=G\der$.
 Since the quotient $q : G \to G\ab$ is a trivial $H$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}, 
@@
 \[
-\begin{tikzcd}
+\begin{tikzcd}[row sep=30]
 \CS(H) 
@@
 &  \CS_{H}(G) \arrow{u}{\text{forget}}  
-&  \arrow[bend left=35pt, dashed]{dll} \CCS(G\ab) \arrow{u} \arrow{dl}[swap]{\iso} \\
-\CCS(G) \arrow{u} \arrow{r}{\beta \mapsto \nu}[swap]{\iso}
-& \arrow{u}  \CCS_{H}(G) 
+&  %\arrow[bend left=35pt, dashed]{dll} 
+\CCS(G\ab) \arrow{u}[swap]{\text{full sub}} \arrow{dl}[swap]{\iso} \\
+\CCS(G) \arrow{u}{\text{full sub}} \arrow{r}{\beta \mapsto \nu}[swap]{\iso}
+& \arrow{u}{\text{full sub}}  \CCS_{H}(G) 
 & 
@@
 Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ as in Section~\ref{ssec:noncomdef}.
-Then the diagram in Definition~\ref{def:CCS} is precisely the result of applying the functor $(q\times q)^*$ to the diagram in Definition~\ref{def:CCScom}; 
+Then the diagram in Definition~\ref{def:CCS} is precisely the result of applying the functor $(q\times q)^*$ to the diagram in Definition~\ref{def:CCScom}, as pictured below; 
 in particular $\gamma = (q\times q)^* \xi$.
-Together with Lemma~\ref{lem:HH}, we may now interpret the diagram in Definition~\ref{def:CCS} as a diagram in $\Loc_{H\times H}(G\times G)$.
-By Lemma~\ref{lem:torsor}, this corresponds uniquely to a diagram in $\Loc(G\ab\times G\ab)$, necessarily the diagram in Definition~\ref{def:CCScom}.
+  \[
+  \begin{tikzcd}[row sep=10, column sep = 15]
+   m_0^*\cs{L}_0 \arrow{dd}[swap]{\xi} \arrow{r}{\mu_0} 
+   & \cs{L}_0\boxtimes\cs{L}_0 \arrow{dd}{\vartheta}
+&&&   m^*\cs{L} \arrow{dd}[swap]{\gamma} \arrow{r}{\mu} 
+ & \cs{L}\boxtimes\cs{L} \arrow{dd}{\vartheta}\\
+ && \arrow{r}{(q\times q)^*}  &\ & & &\\ 
+   \theta^*(m_0^*\cs{L}_0) \arrow{r}{{\theta}^*\mu_0} 
+ &  \theta^*(\cs{L}_0\boxtimes\cs{L}_0)
+&&&   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} 
+&  \theta^*(\cs{L}\boxtimes\cs{L})
+  \end{tikzcd}
+\]
+By Lemma~\ref{lem:HH}, we may interpret the diagram on the right, above, as a diagram in $\Loc_{H\times H}(G\times G)$.
+By Lemma~\ref{lem:torsor}, this corresponds uniquely to a diagram in $\Loc(G\ab\times G\ab)$, necessarily the diagram on the left, above.
 It follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes. 

### 2015-11-13 followup.tex
Fixed the definition of beta |-> gamma. But the typesetting is crap.

@@
 %
-Suppose $(\cs{L},\mu)$ is a linear character sheaf on $G$ such that its pull-back along $G\der \hookrightarrow G$ is trivial;
+Suppose $(\cs{L},\mu)$ is a linear character sheaf on $G$ such that its pull-back along
+$j: G\der \hookrightarrow G$ is trivial;
 let $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ be an isomorphism in $\CS(G\der)$.
@@
 Let $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
-Then $c$ is a smooth morphism of $\Fq$ schemes and $c = m \circ (m \times (i \circ m \circ \theta))$.
-Thus, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_G\otimes (\EE)_G$ by the diagram \todo{Fix this diagram.}
+Then $c$ is a smooth morphism of $\Fq$ schemes and $j\circ c = m \circ (m \times (i \circ m \circ \theta))$.
+Thus, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the commuting diagram of isomorphisms, below.
 \[
 \begin{tikzcd}
-m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \arrow{d}{c = m \circ (m \times (i \circ m \circ \theta))}  \arrow[dashed]{r} & (\EE)_G\otimes (\EE)_G\\
-c^* \cs{L}\vert_{G\der} \arrow{r}{c^*(\beta)} &  c^*(\EE)_{G\der}, \arrow{u}
+\arrow{d} c^* \cs{L}\vert_{G\der} \arrow{r}{c^*(\beta)} 
+	&  c^*(\EE)_{G\der}\\
+\arrow{d}{j\circ c = m \circ (m \times (i \circ m \circ \theta))} (j\circ c)^*\cs{L} 
+	&  m^*\cs{L} \otimes (i \circ m \circ \theta)^*\cs{L} \arrow[dashed]{u}  \\
+\arrow{d} (m \circ (m \times (i \circ m \circ \theta)))^*\cs{L} 
+	& (m \times (i \circ m \circ \theta))^* (p_1^*\cs{L} \otimes p_2^*\cs{L}) \arrow{u} \\
+(m \times (i \circ m \circ \theta))^* m^* \cs{L} \arrow{r}{(m \times (i \circ m \circ \theta))^*(\mu)} 
+	& (m \times (i \circ m \circ \theta))^* (\cs{L} \boxtimes \cs{L}) \arrow{u}
 \end{tikzcd}
 \]
-where the arrow labeled with the equation is the canonical isomorphism coming from the isomorphism of functors defined by the equation.
+%where the arrow labeled with the equation is the canonical isomorphism coming from the isomorphism of functors defined by the equation.
 Using the monoidal structure of the category of Weil local systems on $G\times G$, this isomorphism, in turn, defines an isomorphism
@@
 
-We now suppose that $i : H \hookrightarrow G$ is a closed subgroup and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
+We now suppose that $j : H \hookrightarrow G$ is a closed subgroup and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
 %Then we have the diagram
@@
 %\]
-Define $f : H\times G \to G\times G$ by $f(h,g) = (i(h),g)$ and note that $a = m\circ f$.
+Define $f : H\times G \to G\times G$ by $f(h,g) = (j(h),g)$ and note that $a = m\circ f$.
 Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
@@
 f^* m^*\cs{L} \arrow{dr}{f^*\mu} &&& (\EE)_{H} \boxtimes \cs{L} \arrow{ul} \\ 
-& f^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_1 \circ f = i}[swap]{p_2\circ f = \id}  & 
+& f^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_1 \circ f = j}[swap]{p_2\circ f = \id}  & 
 \cs{L}\vert_{H} \boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id} & 
@@
 %{} & G\times G \arrow{d}{c} &&&\\
-1 \arrow{r} & H \arrow{r}{i} & G \arrow{r}{q} & G\ab \arrow{r} & 1
+1 \arrow{r} & H \arrow{r}{j} & G \arrow{r}{q} & G\ab \arrow{r} & 1
 \end{tikzcd}
@@
 \begin{tikzcd}
-\CS(H) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
-\CS(G\ab) \arrow{dl}{q_{H}^*}[swap]{\iso} \\
- \CS'(G) \arrow{u}{\text{forget}}  \arrow{r}{\beta \mapsto \nu}[swap]{\iso} &  \CS_{H}(G) \arrow{u}{\text{forget}}  & 
+\CS(H) & \arrow{l}[swap]{j^*} \CS(G) &\arrow{l}[swap]{q^*} 
+\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q_{H}^*} \\
+ \CS'(G) \arrow{u}{\text{forget}}  \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}} &  \CS_{H}(G) \arrow{u}{\text{forget}}  & 
 \end{tikzcd}
@@
 \CS(H) 
-& \arrow{l}[swap]{i^*} \CS(G) 
+& \arrow{l}[swap]{j^*} \CS(G) 
 &\arrow{l}[swap]{q^*} 
-\CS(G\ab) \arrow{dl}{q_{H}^*}[swap]{\iso} \\
-\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu}[swap]{\iso} 
+\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q_{H}^*} \\
+\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}} 
 &  \CS_{H}(G) \arrow{u}{\text{forget}}  
 &  %\arrow[bend left=35pt, dashed]{dll} 
-\CCS(G\ab) \arrow{u}[swap]{\text{full sub}} \arrow{dl}[swap]{\iso} \\
-\CCS(G) \arrow{u}{\text{full sub}} \arrow{r}{\beta \mapsto \nu}[swap]{\iso}
+\CCS(G\ab) \arrow{u}[swap]{\text{full sub}} \arrow{dl}{\text{equiv}} \\
+\CCS(G) \arrow{u}{\text{full sub}} \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}}
 & \arrow{u}{\text{full sub}}  \CCS_{H}(G) 
@@
 By Lemma~\ref{lem:HH}, we may interpret the diagram on the right, above, as a diagram in $\Loc_{H\times H}(G\times G)$.
-By Lemma~\ref{lem:torsor}, this corresponds uniquely to a diagram in $\Loc(G\ab\times G\ab)$, necessarily the diagram on the left, above.
-It follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes. 
+By Lemma~\ref{lem:torsor}, this corresponds to a diagram in $\Loc(G\ab\times G\ab)$, necessarily the diagram on the left, above, and also that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes.
 In other words, $(\cs{L},\mu,\beta)\in \CCS(G)$
-if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G)$, completing the proof of Theorem~\ref{thm:Gab}.
-This also defines the functor $\CCS(G\ab) \to \CCS(G)$ by the dashed arrow in the diagram above.
+if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G)$.
+This completes the proof of Theorem~\ref{thm:Gab}.
+%This also defines the functor $\CCS(G\ab) \to \CCS(G)$ by the dashed arrow in the diagram above.
 \end{proof}

### 2015-11-13 followup.tex
Fixed the typesetting of beta |-> gamma.

@@
 Let $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
-Then $c$ is a smooth morphism of $\Fq$ schemes and $j\circ c = m \circ (m \times (i \circ m \circ \theta))$.
-Thus, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the commuting diagram of isomorphisms, below.
+Then $c$ is a smooth morphism of $\Fq$ schemes.
+Set $m' = i \circ m \circ \theta$; then $j\circ c = m \circ (m \times m')$.
+Thus, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms, below.
 \[
 \begin{tikzcd}
-\arrow{d} c^* \cs{L}\vert_{G\der} \arrow{r}{c^*(\beta)} 
-	&  c^*(\EE)_{G\der}\\
-\arrow{d}{j\circ c = m \circ (m \times (i \circ m \circ \theta))} (j\circ c)^*\cs{L} 
-	&  m^*\cs{L} \otimes (i \circ m \circ \theta)^*\cs{L} \arrow[dashed]{u}  \\
-\arrow{d} (m \circ (m \times (i \circ m \circ \theta)))^*\cs{L} 
-	& (m \times (i \circ m \circ \theta))^* (p_1^*\cs{L} \otimes p_2^*\cs{L}) \arrow{u} \\
-(m \times (i \circ m \circ \theta))^* m^* \cs{L} \arrow{r}{(m \times (i \circ m \circ \theta))^*(\mu)} 
-	& (m \times (i \circ m \circ \theta))^* (\cs{L} \boxtimes \cs{L}) \arrow{u}
+\arrow[equal]{d} c^* \cs{L}\vert_{G\der} \arrow{r}{c^*(\beta)} 
+	&  c^*(\EE)_{G\der} \arrow[equal]{d} \\
+\arrow{d}[swap]{j\circ c = m \circ (m \times m')} c^* j^* \cs{L} 
+	&   (\EE)_{G\times G} \\
+(m \times m')^* m^* \cs{L} \arrow{d}[swap]{(m \times m')^*(\mu)} 
+	&  m^*\cs{L} \otimes \theta^* m^* i^* \cs{L}  \arrow[dashed]{u} \\
+(m \times m')^* (\cs{L} \boxtimes \cs{L}) \arrow[equal]{r} 
+	& m^*\cs{L} \otimes (m')^*\cs{L} \arrow{u}[swap]{m' = i\circ m\circ \theta} 
 \end{tikzcd}

### 2015-11-13 followup.tex
Working on section 2

--- 2015-11-13 followup.tex
@@
 
-In this section we show that trace of Frobenius is an isomorphism for commutative character sheaves on a
-smooth commutative group scheme $G$.  We begin by reinterpreting Definition \ref{def:CCScom} in terms of
-cocycles.
+In \cite{cunningham-roe:13a}*{Thm. 3.6}, we showed that $\TrFrob{G} : \CSiso{G} \to G(k)^*$ is surjective and
+explicitly computed its kernel.  In this section, we show that the corresponding map
+$\TrFrob{G} : \CCSiso{G} \to G(k)^*$ for commutative character sheaves is an isomorphism.
+We begin by reinterpreting Definition \ref{def:CCScom} in terms of cocycles.
 
-For a character sheaf $\cs{L}$ on $G$, recall from \cite{cunningham-roe:13a}*{\S 2.3} that $S_G : \CSiso{G} \to \Hh^2(E_G^\bullet)$ maps
+Let $G$ be a commutative \'etale group scheme over $k$. For a character sheaf $\cs{L}$ on $G$, recall
+\cite{cunningham-roe:13a}*{\S 2.3} that $S_G : \CSiso{G} \to \Hh^2(E_G^\bullet)$ is an isomorphism mapping
 $[\cs{L}]$ to $[\alpha \oplus \beta]$, where $E_G^\bullet$ is the total space of the zeroth page
@@
 
-If $M$ is a $\bG$-module, then we say a cohomology class in $\Hh^2(\bG, M)$ is \emph{symmetric} if it is represented
-by a symmetric $2$-cocycle.  Since every coboundary is symmetric, either all cocycles in a given class will be symmetric
-or none will.
+If $M$ is a $\bG$-module, then we say a class in the Galois cohomology group $\Hh^2(\bG, M)$
+is \emph{symmetric} if it is represented by a symmetric $2$-cocycle.  Since every coboundary is symmetric,
+either all cocycles in a given class will be symmetric or none will.  The connection between
+commutative character sheaves and symmetric classes is given in the following lemma.
+\todo{Define symmetric for element of $\Hh^2(E_G^\bullet)$.}
+
+\begin{lemma} \label{lem:symccslink}
+Suppose $G$ is a smooth commutative group scheme, and let $\cs{L}$ be a character sheaf on $G$.
+Then $\cs{L}$ is commutative if and only if $S_G(\cs{L})$ is symmetric.
+\end{lemma}
+\begin{proof}
+The symmetry of $S_G(\cs{L})$ is a direct consequence of the commutativity of the diagram in Definition \ref{def:CCScom}
+after choosing bases for each stalk.
+\end{proof}
 
@@
 \]
-for all $n > 0$.  When $n = 2$, using the fact that $\bG$ is commutative, we have that $\Hh_1(\bG, \ZZ) \cong \bG$
+is exact for all $n > 0$.  When $n = 2$, using the fact that $\bG$ is commutative, we have that $\Hh_1(\bG, \ZZ) \cong \bG$
 and that $\Hh_2(\bG, \ZZ) \cong \wedge^2 \bG$. We get
@@
 
-For general smooth commutative group schemes, we use Lemma \ref{lem:conncomm} and the snake lemma.
+For general smooth commutative group schemes, we use Lemma \ref{lem:conncomm} and the snake lemma, as in the proof of
+\cite{cunningham-roe:13a}*{Thm. 3.6}
 \end{proof}
@@
 \begin{lemma}\label{lem:HH}
-If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of $H\times H$-equivariant Weil local systems on $G\times G$; likewise $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$.
+If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of $H\times H$-equivariant linear character sheaves on $G\times G$; likewise $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$.
 \end{lemma}
@@
 \begin{align*}
-d : H\times H\times G\times G &\to H\times G\times H\times G \\
-(h_1,h_2,g_1,g_2) &\mapsto (h_1, g_1, h_2, g_2)\\
+m_2 : G\times G\times G\times G &\to G\times G \\
+(x_1,y_1,x_2,y_2) &\mapsto (x_1x_2, y_1y_2) \\
 a_2 : H\times G\times H\times G &\to G\times G \\
@@
 p_2 : H\times G\times H\times G &\to G\times G \\
-(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2).
+(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2)
 \end{align*}
-The following diagram defines the isomorphisms needed to see that both $m^*\cs{L}$ and $\cs{L}\boxtimes\cs{L}$ are $H\times H$-equivariant Weil local systems.
+and set $\cs{L}_2\ceq m_2^*\cs{L}$ and $\mu_2 \ceq m_2^*(\mu)$.
+Pulling back $\cs{L}$ along $m : G\times G \to G$ produces the linear character sheaf $(\cs{L}_2, \mu_2)$ on $G \times G$ (see \cite{cunningham-roe:13a}*{Lemma 1.4}), \todo{False, because $m$ is not a group homorphism.}
+which comes equipped with the isomorphism $\nu_2 : a_2^*\cs{L}_2 \to p_2^*\cs{L}_2$. 
+This isomorphism satisfies the appropriate version of \eqref{ECS1}, so  $(\cs{L}_2,\mu_2,\nu_2)$ is indeed an $H\times H$-equivariant linear character sheaf on $G\times G$.
+Likewise, $\cs{L}\boxtimes \cs{L}$ is an $H\times H$-equivariant linear character sheaf with isomorphism $\nu \boxtimes\nu$, as indicated in the diagram below.
 \[
-\begin{tikzcd}[column sep=40]
-\arrow{d}[swap]{a_2(\mu)} a_2^* (m^*\cs{L}) \arrow[dashed]{r} 
-	& \arrow{d}{p_2^*(\mu)} p_2^*(m^*\cs{L})\\
-\arrow{d}[swap]{a_2= (a\times a)\circ d} a_2^*(\cs{L}\boxtimes\cs{L}) \arrow[dashed]{r} 
-	& \arrow{d}{p_2= (p\times p)\circ d} p_2^*(\cs{L}\boxtimes\cs{L}) \\
-%d^* (a\times a)^* (\cs{L}\boxtimes\cs{L}) & d^* (p\times p)^* (\cs{L}\boxtimes\cs{L}) \\
-d^* (a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{d^*(\nu\boxtimes \nu)}& d^*(p^*\cs{L}\boxtimes p^*\cs{L}) 
+\begin{tikzcd}
+\arrow{d}[swap]{\nu_2} a_2^*(m^*\cs{L}) \arrow{r}{a_2^*(\mu)} & a_2^*(\cs{L}\boxtimes\cs{L})  \arrow{r} & (a^*\cs{L})\boxtimes (a^*\cs{L}) \arrow{d}{\nu\boxtimes\nu} \\
+p_2^*(m^*\cs{L}) \arrow{r}{p_2^*(\mu)} & p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r} & (p^*\cs{L})\boxtimes (p^*\cs{L}) 
 \end{tikzcd}
 \]
-The dashed arrows both satisfy \eqref{E1} and \eqref{E2} as they apply here.
-This diagram also shows that $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of equivariant sheaves, since it satisfies \eqref{E3} as it applies here.
-The proof that $\theta^*(\cs{L}\boxtimes\cs{L})$ is also straightforward, since $a_2\circ \theta = \theta_2 \circ a_2$ and $p_2\circ \theta = \theta_2 \circ p_2$ for the obvious $\theta_2$.
-Let $\nu_2 : a_2^*(\cs{L}\boxtimes\cs{L}) \to p_2^*(\cs{L}\boxtimes\cs{L})$ be the middle horizontal isomorphism of Weil local systems, above. 
-Then, to see that
+By abuse of notation, we will also refer to the missing vertical map down the center of this diagram as $\nu \boxtimes \nu$.
+Since this diagram commutes, $(\cs{L}\boxtimes \cs{L},\mu\boxtimes \mu,\nu\boxtimes\nu)$ is also an $H\times H$-equivariant linear character sheaf on $G\times G$.
+The appropriate version of \eqref{E3} also commutes, so we can reinterpret
 \[
-\begin{tikzcd}
-a_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r}{a_2^*(\vartheta)} \arrow{d}[swap]{\nu_2} 
-	& a_2^*\theta^*(\cs{L}\boxtimes\cs{L}) \arrow{d}{\theta^*(\nu_2)} \\
-p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r}{p_2^*(\vartheta)} 
-	& p_2^*\theta^*(\cs{L}\boxtimes\cs{L})
-\end{tikzcd}
+\mu : (\cs{L}_2, \mu_2, \nu_2) \to (\cs{L}\boxtimes\cs{L}, \mu \boxtimes \mu, \nu \boxtimes \nu)
 \]
-commutes, consider the commuting diagram of stalks, below.
-\[
-\begin{tikzcd}
-\cs{L}_{h_1g_1}\otimes\cs{L}_{h_2g_2} \arrow{r}{\vartheta}  \arrow{d}[swap]{\nu_2} 
-	& \cs{L}_{h_2g_2} \otimes\cs{L}_{h_1g_1}  \arrow{d}{\nu_2} \\
-\cs{L}_{g_1}\otimes\cs{L}_{g_2} \arrow{r}{\vartheta}  
-	& \cs{L}_{g_2} \otimes\cs{L}_{g_1}
-\end{tikzcd}
-\]
+as a morphism of equivariant linear character sheaves.
+The argument that $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$ is morphism of $H\times H$-equivariant linear character sheaves on $G\times G$ is also straightforward.
 \end{proof}
@@
 We may now revisit the definition of the functor $q_H^*: \CS(G_0)\to \CS_H(G)$. 
-On objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$. 
+By (a small part of) Lemma~\ref{lem:HH}, $\mu_0$ is a morphism of linear character sheaves on $G_0\times G_0$.
+Thus, on objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$. 
 To verify that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$, one must confirm \cite{cunningham-roe:13a}*{CS1, CS2, CS3}, \eqref{E1}, \eqref{E2} and \eqref{ECS1}. 
@@
 With this description of $q_H^*: \CS(Q)\to \CS_H(G)$ is is easy to see that it is an equivalence.
-Its adjoint is given on objects by $(\cs{L},\mu,\nu) \mapsto (R_1(\cs{L},\nu), R_2(\nu))$, making use of Lemma~\ref{lem:HH}, and on morphisms by $\alpha \mapsto R_1(\alpha)$.
+Its adjoint is given on objects by $(\cs{L},\mu,\nu) \mapsto (R_1(\cs{L},\nu), R_2(\nu))$, again making use of Lemma~\ref{lem:HH}, and on morphisms by $\alpha \mapsto R_1(\alpha)$.
 The adjunction is built from the adjunctions for $(L_1,R_1)$ and $(L_2, R_2)$.
@@
 %
-Here we use the notation $\CS'(G)$ from Section~\ref{ssec:noncomdef} and the observation that $\CS'(G)$ is precisely the category $\CS^{H}(G)$ from Section~\ref{ssec:closed} for $H=G\der$.
+Here we use the notation $\CS'(G)$ from Section~\ref{ssec:noncomdef} and the observation that it is precisely the category $\CS^{H}(G)$ from Section~\ref{ssec:closed} for $H=G\der$.
 Since the quotient $q : G \to G\ab$ is a trivial $H$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}, 
@@
 \[
-\begin{tikzcd}[row sep=30]
+\begin{tikzcd}
 \CS(H) 
@@
 &  \CS_{H}(G) \arrow{u}{\text{forget}}  
-&  %\arrow[bend left=35pt, dashed]{dll} 
-\CCS(G\ab) \arrow{u}[swap]{\text{full sub}} \arrow{dl}[swap]{\iso} \\
-\CCS(G) \arrow{u}{\text{full sub}} \arrow{r}{\beta \mapsto \nu}[swap]{\iso}
-& \arrow{u}{\text{full sub}}  \CCS_{H}(G) 
+&  \arrow[bend left=35pt, dashed]{dll} \CCS(G\ab) \arrow{u} \arrow{dl}[swap]{\iso} \\
+\CCS(G) \arrow{u} \arrow{r}{\beta \mapsto \nu}[swap]{\iso}
+& \arrow{u}  \CCS_{H}(G) 
 & 
@@
 Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ as in Section~\ref{ssec:noncomdef}.
-Then the diagram in Definition~\ref{def:CCS} is precisely the result of applying the functor $(q\times q)^*$ to the diagram in Definition~\ref{def:CCScom}, as pictured below; 
+Then the diagram in Definition~\ref{def:CCS} is precisely the result of applying the functor $(q\times q)^*$ to the diagram in Definition~\ref{def:CCScom}; 
 in particular $\gamma = (q\times q)^* \xi$.
-  \[
-  \begin{tikzcd}[row sep=10, column sep = 15]
-   m_0^*\cs{L}_0 \arrow{dd}[swap]{\xi} \arrow{r}{\mu_0} 
-   & \cs{L}_0\boxtimes\cs{L}_0 \arrow{dd}{\vartheta}
-&&&   m^*\cs{L} \arrow{dd}[swap]{\gamma} \arrow{r}{\mu} 
- & \cs{L}\boxtimes\cs{L} \arrow{dd}{\vartheta}\\
- && \arrow{r}{(q\times q)^*}  &\ & & &\\ 
-   \theta^*(m_0^*\cs{L}_0) \arrow{r}{{\theta}^*\mu_0} 
- &  \theta^*(\cs{L}_0\boxtimes\cs{L}_0)
-&&&   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} 
-&  \theta^*(\cs{L}\boxtimes\cs{L})
-  \end{tikzcd}
-\]
-By Lemma~\ref{lem:HH}, we may interpret the diagram on the right, above, as a diagram in $\Loc_{H\times H}(G\times G)$.
-By Lemma~\ref{lem:torsor}, this corresponds uniquely to a diagram in $\Loc(G\ab\times G\ab)$, necessarily the diagram on the left, above.
+Together with Lemma~\ref{lem:HH}, we may now interpret the diagram in Definition~\ref{def:CCS} as a diagram in $\CS_{H\times H}(G\times G)$.
+By Lemma~\ref{lem:beta}, this corresponds uniquely to a diagram in $\CS(G\ab\times G\ab)$, necessarily the diagram in Definition~\ref{def:CCScom}.
 It follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes. 

### 2015-11-13 followup.tex
Added remark that the two definitions of CCS(Gab) are compatible.

--- 2015-11-13 followup.tex
@@
 Set $m' = i \circ m \circ \theta$; then $j\circ c = m \circ (m \times m')$.
-Thus, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms, below.
-\[
+Thus, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms, below.
+\begin{equation}
 \begin{tikzcd}
-\arrow[equal]{d} c^* \cs{L}\vert_{G\der} \arrow{r}{c^*(\beta)} 
-	&  c^*(\EE)_{G\der} \arrow[equal]{d} \\
+\arrow[equal]{d} c^* (\cs{L}\vert_{G\der}) \arrow{r}{c^*(\beta)} 
+	&  c^*((\EE)_{G\der}) \arrow[equal]{d} \\
 \arrow{d}[swap]{j\circ c = m \circ (m \times m')} c^* j^* \cs{L} 
@@
 (m \times m')^* m^* \cs{L} \arrow{d}[swap]{(m \times m')^*(\mu)} 
-	&  m^*\cs{L} \otimes \theta^* m^* i^* \cs{L}  \arrow[dashed]{u} \\
+	&  m^*\cs{L} \otimes \theta^* m^* i^* \cs{L}  \arrow[dashed]{u}[swap]{\gamma'} \\
 (m \times m')^* (\cs{L} \boxtimes \cs{L}) \arrow[equal]{r} 
@@
 \end{tikzcd}
-\]
-%where the arrow labeled with the equation is the canonical isomorphism coming from the isomorphism of functors defined by the equation.
+\end{equation}
+In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations; so, for example, the middle left isomorphism comes from $(m\times m')^* m^* \iso c^* j^*$ since $j\circ c = m \circ (m \times m')$.
 Using the monoidal structure of the category of Weil local systems on $G\times G$, this isomorphism, in turn, defines an isomorphism
@@
 
-\todo{Should remark that it reduces to the other definition in the commutative case}
-
-%We will see that, when $\beta$ exists for $(\cs{L},\mu)\in \CS(G)$, it is essentially unique.
+Suppose $G$ is commutative, so $G\der = 1$. 
+Suppose $(\cs{L},\mu,\beta)$ is an object in $\CS'(G)$.
+Then $\beta : \cs{L}_1\to \EE$ is an isomorphism in $\CS(1)$, and unique by \cite{cunningham-roe:13a}*{Thm 3.9}.
+Tracing through the construction of $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ from $\beta : \cs{L}_1\to \EE$, we find that $\gamma$ is the canonical isomorphism $\xi : m^*\cs{L} \to \theta^*m^*\cs{L}$ coming from the equation $m = m \circ \theta$.
+Thus, when $G$ is commutative, Definition~\ref{def:CCS} recovers Definition~\ref{def:CCScom}.
+The next result generalizes this observation.
 
@@
 \end{equation}
-and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes,
+and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes.
 \begin{equation}\label{E2}
@@
 b_1^* a^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
-& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L}, & 
+& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L} & 
 \end{tikzcd}
 \end{equation}
-In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from equations \eqref{eqn:bap}; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
+%In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from equations \eqref{eqn:bap}; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
 %On stalks, this condition is ...

### 2015-11-13 followup.tex
Starting work on Section 4.

@@
 Then $\beta : \cs{L}_1\to \EE$ is an isomorphism in $\CS(1)$, and unique by \cite{cunningham-roe:13a}*{Thm 3.9}.
-Tracing through the construction of $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ from $\beta : \cs{L}_1\to \EE$, we find that $\gamma$ is the canonical isomorphism $\xi : m^*\cs{L} \to \theta^*m^*\cs{L}$ coming from the equation $m = m \circ \theta$.
+Tracing through the construction of $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ from $\beta : \cs{L}_1\to \EE$, we find that $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ is the canonical isomorphism coming from the equation $m = m \circ \theta$.
+ \todo{I'm having some trouble seeing this.}  
 Thus, when $G$ is commutative, Definition~\ref{def:CCS} recovers Definition~\ref{def:CCScom}.
@@
 The precise definition of the functor $\CCS(G\ab) \to \CCS(G)$ will be given in Section~\ref{ssec:proofs}, with the proof of Theorem~\ref{thm:Gab}.
+%
+Sections~\ref{ssec:equivariant1}, \ref{ssec:equivariant2}, \ref{ssec:descent} and \ref{ssec:closed} set up machinery needed to prove Theorem~\ref{thm:Gab}.
 
@@
 \begin{equation}\label{ECS1}
-\begin{tikzcd}
+\begin{tikzcd}[column sep=30]
 \ & \arrow{dl}{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{dr}[swap]{p\circ c_2 = m\circ c_3}  &  \\
@@
 
-\subsection{Descent along a torsor}
+\subsection{Descent along a torsor}\label{ssec:descent}
 
-Now suppose $q : G \to G_0$ is a regular epimorphism with kernel pair $(a,p)$ in the category of schemes
+Now suppose $q : G \to G_0$ is a regular epimorphism of smooth group schemes with kernel pair $(a,p)$
 \[
@@
 \]
-given on objects by $(\cs{L}_0,\mu_0) \mapsto (q^*\cs{L}_0, (q\times q)^* \mu_0)$; see \cite{cunningham-roe:13a}*{}.
+given on objects by $(\cs{L}_0,\mu_0) \mapsto (q^*\cs{L}_0, (q\times q)^* \mu_0)$; see \cite{cunningham-roe:13a}*{Lem 1.4}.
 %To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$, verify \cite{cunningham-roe:13a}, CS.3], arguing as in \cite{cunningham-roe:13a}].
@@
 \[
-\begin{tikzcd}
-a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{rrr}{\nu} & & &  \arrow[equal]{d} p^*\cs{L} \\
-a^* ( q^*\cs{L}_0) \arrow{r} 
-& (q\circ a)^* \cs{L}_0 \arrow[equal]{r} 
-& (q\circ p)^*\cs{L}_0 \arrow{r} 
+\begin{tikzcd}[column sep=40]
+a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{r}{\nu} &  \arrow[equal]{d} p^*\cs{L} \\
+a^* ( q^*\cs{L}_0) \arrow{r}{q\circ a = q\circ p}
 & p^* (q^*\cs{L}_0)
@@
 \[
-\begin{tikzcd}
+\begin{tikzcd}[column sep=30]
 \ & a^*\cs{L} \arrow{dl}{m\circ f = a} \arrow{r}{\nu} & p^*\cs{L} & \\
@@
 \[
-\begin{tikzcd}[row sep=30]
+\begin{tikzcd}[row sep=30, column sep=40]
 \CS(H) 
@@
   \[
-  \begin{tikzcd}[row sep=10, column sep = 15]
+  \begin{tikzcd}[row sep=10, column sep = 20]
    m_0^*\cs{L}_0 \arrow{dd}[swap]{\xi} \arrow{r}{\mu_0} 
@@
 
-\section{Applications to supercuspidal representations}
+\section{Applications}
 
@@
 
-Combining Theorems \ref{thm:trfrobiso} and \ref{thm:Gab} gives an isomorphism $\CCSiso{G} \to G\ab(k)^*$.
+Combining Theorems \ref{thm:trfrobiso} and \ref{thm:Gab} gives an isomorphism $\CCSiso{G} \to G\ab(k)^*$. \todo{Could we turn this into a declared corollary/theorem? It's a nice result.}
 We may thus ask for a condition on a commutative character sheaf on $G$ that corresponds to having trivial
@@
 Set $G = \Gr_R(\underline{G})$; this is a group scheme over $\Fq$ equipped with $G = \varprojlim_{n\in \NN} G_n$.
-Let $\QCS(G)$ be the category of commutative quasicharacter sheaves on $G$. . . .  as in \cite{cunningham-roe:13a}.
+Let $\CCS(\underline{G})$ be the category of commutative quasicharacter sheaves on $G$. . . .  as in \cite{cunningham-roe:13a}.
 
 \begin{proposition}\label{prop:QCS}
-$\Hom_\text{cts}(\underline{G}(\OK),\EEx) \iso \QCSiso{G}$.
+$\underline{G}(\OK)^* \iso \CCSiso{\underline{G}}$.
 \end{proposition}
@@
 \begin{proof}
+That's not correct; it should be 
+\[
+\CCSiso{\underline{G}} \iso (\Gr(\underline{G})\ab(\Fq))^*.
+\]
+Is $\Gr(\underline{G})\ab = \Gr(\underline{G}\ab)?$ If so, then at least we get 
+\[
+\CCSiso{\underline{G}} \iso (\underline{G}\ab(\OK))^*.
+\]
 \end{proof}
@@
  \subsection{Geometric types for supercuspidal representations}
+
+\begin{proposition}
+Let $(\underline{G}(\OK),\rho)$ be a type such that  . . . 
+Set $G = \Gr(\underline{G})$.
+There is a virtual admissible $\ell$-adic sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) \iso \underline{G}(\OK)$.
+\end{proposition}
+
+It is not unique.
 

### 2015-11-14 followup.tex
Done for the day. I'm preparing for a push on Section 4, tomorrow.

@@
 Then $\beta : \cs{L}_1\to \EE$ is an isomorphism in $\CS(1)$, and unique by \cite{cunningham-roe:13a}*{Thm 3.9}.
-Tracing through the construction of $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ from $\beta : \cs{L}_1\to \EE$, we find that $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ is the canonical isomorphism coming from the equation $m = m \circ \theta$.
- \todo{I'm having some trouble seeing this.}  
+Tracing through the construction of $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ from $\beta : \cs{L}_1\to \EE$, we find \todo{I'm having some trouble seeing this.} that $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ is the canonical isomorphism coming from the equation $m = m \circ \theta$.
 Thus, when $G$ is commutative, Definition~\ref{def:CCS} recovers Definition~\ref{def:CCScom}.
@@
 \end{theorem}
-
-The precise definition of the functor $\CCS(G\ab) \to \CCS(G)$ will be given in Section~\ref{ssec:proofs}, with the proof of Theorem~\ref{thm:Gab}.
 %
 Sections~\ref{ssec:equivariant1}, \ref{ssec:equivariant2}, \ref{ssec:descent} and \ref{ssec:closed} set up machinery needed to prove Theorem~\ref{thm:Gab}.
+The precise definition of the functor $\CCS(G\ab) \to \CCS(G)$ will be given with the proof of Theorem~\ref{thm:Gab}, in Section~\ref{ssec:proofs}.
 
@@
 
-\subsection{Toral supercuspidal representations of $p$-adic groups}
+%\subsection{Toral supercuspidal representations of $p$-adic groups}
 

### 2015-11-14 followup.tex

@@
 
-In this section we show that trace of Frobenius is an isomorphism for commutative character sheaves on a
-smooth commutative group scheme $G$.  We begin by reinterpreting Definition \ref{def:CCScom} in terms of
-cocycles.
-
-For a character sheaf $\cs{L}$ on $G$, recall from \cite{cunningham-roe:13a}*{\S 2.3} that $S_G : \CSiso{G} \to \Hh^2(E_G^\bullet)$ maps
+In \cite{cunningham-roe:13a}*{Thm. 3.6}, we showed that $\TrFrob{G} : \CSiso{G} \to G(k)^*$ is surjective and
+explicitly computed its kernel.  In this section, we show that the corresponding map
+$\TrFrob{G} : \CCSiso{G} \to G(k)^*$ for commutative character sheaves is an isomorphism.
+We begin by reinterpreting Definition \ref{def:CCScom} in terms of cocycles.
+
+Let $G$ be a commutative \'etale group scheme over $k$. For a character sheaf $\cs{L}$ on $G$, recall
+\cite{cunningham-roe:13a}*{\S 2.3} that $S_G : \CSiso{G} \to \Hh^2(E_G^\bullet)$ is an isomorphism mapping
 $[\cs{L}]$ to $[\alpha \oplus \beta]$, where $E_G^\bullet$ is the total space of the zeroth page

### 2015-11-14 followup.tex
Fixed a few typos

--- 2015-11-14 followup.tex
@@
 \begin{lemma}\label{lem:HH}
-If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of $H\times H$-equivariant Weil local systems on $G\times G$; likewise $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$.
+If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ and $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are morphisms of $H\times H$-equivariant Weil local systems on $G\times G$.
 \end{lemma}
@@
 If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(G_0)$, 
-then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, arguing as in \cite{cunningham-roe:13a} so $\alpha$ is a morphism in $\CS(G)$.
+then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha$ is a morphism in $\CS(G)$.
 %\todo{I find myself having to make many references to \cite{cunningham-roe:13a}] and promising that the results there adapt to the noncommutative group case.
@@
 Its adjoint is given on objects by $(\cs{L},\mu,\nu) \mapsto (R_1(\cs{L},\nu), R_2(\nu))$, making use of Lemma~\ref{lem:HH}, and on morphisms by $\alpha \mapsto R_1(\alpha)$.
-The adjunction is built from the adjunctions for $(L_1,R_1)$ and $(L_2, R_2)$.
+The adjunction is built from the adjunctions $(\epsilon_1, \eta_1)$ and $(\epsilon_2, \eta_2)$ for $(L_1,R_1)$ and $(L_2, R_2)$.
 \end{proof}
 
-\subsection{Closed subgroups}\label{ssec:closed}
+\subsection{Quotient by a closed subgroup}\label{ssec:closed}
 
-We now suppose that $j : H \hookrightarrow G$ is a closed subgroup and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
+We now suppose that $j : H \hookrightarrow G$ is a closed subgroup scheme over $\Fq$ and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
 %Then we have the diagram
@@
 \begin{lemma}\label{lem:beta}
-$\CS_H(G)$ is equivalent to the category $\CS^H(G)$ of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$, with morphisms $\alpha : (\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ defined by the condition
-$\alpha : (\cs{L},\mu) \to (\cs{L}',\mu')$ is a morphism in $\CS(G)$ and $\beta = \beta' \circ \alpha\vert_{H}$.
+If $H\hookrightarrow G$ is a closed subgroup scheme over $\Fq$ then
+$\CS_H(G)$ is equivalent to the category $\CS^H(G)$ of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$; morphisms $(\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ in $\CS^H(G)$ are morphisms $\alpha: \cs{L} \cs{L}'$ in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{H}$.
 \end{lemma}

### 2015-11-14 followup.tex
Rewrite introduction

@@
 \section*{Introduction}
-We introduce and establish the basic properties of  the category of \emph{commutative character sheaves} on smooth group schemes $G$ over finite fields $\Fq$. 
-Expanding on work by the same authors, we show that all character sheaves on $G\ab$ are commutative, when $G\ab$ is connected and of finite type.
-We give three applications.
-First, we use commutative character sheaves to produce a functorial geometrization of characters of $G(\Fq)$ in all cases, thus repairing a defect in the function-sheaf dictionary for algebraic groups $G$ which appears when the component group of $G$ is $\Hh^2(\pi_0(\bG),\EEx)^{\Frob{}}$ is non-trivial.
-Second, we revisit the motivations for the stacky abelianization construction, and show that, after replacing the rank-$1$ character sheaves on $G$ with commutative character sheaves on $G$, the schematic abelianization $G \to G\ab$ is the correct quotient.
-This is an immediate consequence of the fact that the category of commutative character sheaves on $G$ is equivalent to the category of commutative character sheaves on $G\ab$. 
-Finally, we provide a geometrization of generic types for supercuspidal representations of connected reductive linear algebraic groups over local fields.
-This last application puts all the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category: perverse sheaves on group schemes over finite fields.
-
-Fragments: 
-The additional condition distinguishing which character sheaves on $G$ are commutative, has several benefits, as we will see in this note.
-\begin{enumerate}
-\labitem{(1)}{b1}
-A character sheaf $\cs{L}$ on $G$ is invisible if and only if $\cs{L}$ is not commutative.
-Recall from \cite{cunningham-roe:13a}*{Def. 2.8} that a character sheaf $\cs{L}$ in $G$ is {\it invisible} if $\cs{L}  \ncong \EE$ yet $\trFrob{\cs{L}} =1$.
-These are exactly the non-trivial character sheaves in the kernel of the surjective group homomorphism 
-\[
-\TrFrob{G} : \CSiso{G} \to G(\Fq)^*
-\]
- given by the trace of Frobenius.
-\labitem{(2)}{b2}
-This note shows that $\TrFrob{G} : \CSiso{G} \to G(\Fq)^*$ admits a canonical section, and thus a splitting of the short exact sequence 
-\[
-\begin{tikzcd}
-0 \arrow{r} & \Hh^2(\pi_0(\bG),\EEx)^{\Weil{}} \arrow{r} & \CSiso{G} \arrow{r}{\TrFrob{G}} & G(\Fq)^* \arrow{r} & 0
-\end{tikzcd}
-\]
-found in \cite{cunningham-roe:13a}*{Thm. 3.6}.
-\labitem{(3)}{b3}
-Like the category $\CS(G)$ of character sheaves on $G$, which is described completely in \cite{cunningham-roe:13a}, $\CCS(G)$ is a rigid monoidal category.
-Since $\CCS(G)$ is a full subcategory of $\CS(G)$, and since Item \ref{b2} above shows $\CCSiso{G} \iso G(\Fq)^*$, canonically, the category $\CCS(G)$ is now completely described by the following consequence of \cite{cunningham-roe:13a}*{Thm.
-3.9}: in $\CCS(G)$, every morphism $\cs{L} \to \cs{L}'$ is either trivial (zero on stalks) or an isomorphism, and
-\[
-\Aut(\cs{L}) \iso  \Hh^1(\pi_0(\bG), \EEx)^{\Weil{}}.
-\]
-Consequently, we have a complete description of category $\CCS(G)$.
-\end{enumerate}
+
+In \cite{cunningham-roe:13a}, we generalized the function-sheaf dictionary from connected commutative algebraic groups
+over a finite field $k$ to smooth commutative group schemes $G$ over $k$.  We described a category $\CS(G)$ of
+\emph{character sheaves} on $G$ and a surjective homomorphism $\TrFrob{G} : \CSiso{G} \to \Hom(G(k), \EEx)$.
+In contrast to the connected case, $\TrFrob{G}$ may have nontrivial kernel; we gave an explicit description of
+its kernel as $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$ \cite{cunningham-roe:13a}*{Thm. 3.6}.
+
+The first aim of this paper is to repair this defect in the function-sheaf dictionary by describing a full subcategory
+$\CCS(G)$ of $\CS(G)$ so that $\TrFrob{G}$ restricts to an isomorphism $\CCSiso{G} \to \Hom(G(k), \EEx)$.
+We refer to the resulting objects as \emph{commutative character sheaves}, since the passage from $\CS(G)$
+to $\CCS(G)$ involves a condition that exchanges the inputs to the multiplication morphism on $G$
+(see Definition \ref{def:CCScom}).  When $G$ is connected, all character sheaves on $G$ are commutative.
+This category clarifies several questions about character sheaves on $G$: invisible character sheaves
+\cite{cunningham-roe:13a}*{Def. 2.8} are precisely those that are not commutative, and the inverse map
+$\Hom(G(k), \EEx) \to \CCSiso{G}$ provides a canonical splitting of $\TrFrob{G}$ \cite{cunningham-roe:13a}*{Rem. 3.7}.
+
+Next, we broaden our scope further to encompass smooth group schemes $G$ that are not necessarily commutative.
+In this paper, we do not consider Lusztig's geometrization of arbitrary characters of the non-abelian group $G(k)$
+using character sheaves \cite{lusztig:85a}*{Def.~2.10}, but focus only on the case of $1$-dimensional characters
+$\Hom(G(k), \EEx)$.  The category $\CS(G)$ has a straightforward generalization to this case, but again
+there are more linear character sheaves than there are characters, as pointed out by Kamgarpour \cite{kamgarpour:09a}*{(1.1)}.
+We define a category $\CCS(G)$ and a forgetful functor to $\CS(G)$ so that $\TrFrob{G} : \CCSiso{G} \to \Hom(G\ab(k), \EEx)$
+is an isomorphism.  In fact, pullback along the quotient $q : G \to G\ab$ defines an equivalence of categories
+$\CCS(G\ab) \to \CCS(G)$.  Note that the functor $\CCS(G) \to \CS(G)$ is not essentially surjective, missing
+the kinds of linear character sheaves highlighted by Kamgarpour.  Moreover, $\Hom(G\ab(k), \EEx)$ surjects
+onto $\Hom(G(k), \EEx)$, with a kernel described by Galois cohomology.
+
+Finally, we use the category $\CCS(G)$ to give a geometric description of generic types for supercuspidal representations
+of connected reductive linear algebraic groups over local fields.  In this way, we provide all of the ingredients
+needed to parametrize supercuspidal representations of arbitrary depth in the same category:
+perverse sheaves on group schemes over finite fields.
+
+\todo{Add summary of sections}
 
@@
 the character sheaves of Lusztig, we will refer to the former as \emph{linear character sheaves}
-(to evoke the one-dimensional character sheaves of \cite{Kamgarpour}).
+(to evoke the one-dimensional character sheaves of \cite{kamgarpour:09a}).
 
@@
 The precise definition of the functor $\CCS(G\ab) \to \CCS(G)$ will be given with the proof of Theorem~\ref{thm:Gab}, in Section~\ref{ssec:proofs}.
+
+\todo{We should give the relationship between $\CCSiso{G}$ and $G(k)^*$ here as a corollary.  Also, include the automorphism group of a commutative character sheaf.}
 

### 2015-11-14 followup.tex
Comments from conversation this morning. Catching up.

@@
 
+\todo{Comment here on Masoud's work.}
+
 %\todo{Masound's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case.
@@
 and show that the functor $q^* : \CS(G_0) \to \CS(G)$ factors according to the following commuting diagram of functors
-\[
+\begin{equation}\label{qH}
 \begin{tikzcd}
@@
 \end{tikzcd}
-\]
+\end{equation}
 The definition of $q_H^* : \CS(G_0)\to \CS_H(G)$ will be revisited in the proof of the following result.
@@
 We may now revisit the definition of the functor $q_H^*: \CS(G_0)\to \CS_H(G)$. 
-On objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$. 
+On objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$. \todo{Shorten this, actually, and combine with the next paragraph.}
 To verify that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$, one must confirm \cite{cunningham-roe:13a}*{CS1, CS2, CS3}, \eqref{E1}, \eqref{E2} and \eqref{ECS1}. 
@@
 If $H\hookrightarrow G$ is a closed subgroup scheme over $\Fq$ then
-$\CS_H(G)$ is equivalent to the category $\CS^H(G)$ of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$; morphisms $(\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ in $\CS^H(G)$ are morphisms $\alpha: \cs{L} \cs{L}'$ in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{H}$.
+$\CS_H(G)$ is equivalent to the category $\CS^H(G)$ of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$; a morphism $(\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ in $\CS^H(G)$ is a morphism $\alpha: \cs{L} \to \cs{L}'$ in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{H}$.
 \end{lemma}
@@
 Set $H=G\der$.
-Now,
-\[
-\begin{tikzcd}
+Let $j : H\hookrightarrow G$ be the inclusion and let $q : G \to G\ab$ be the quotient. 
+With reference to \eqref{qH} and Section~\ref{ssec:closed}, consider the following diagram.
+%\[
+%\begin{tikzcd}
 %{} & G\times G \arrow{d}{c} &&&\\
-1 \arrow{r} & H \arrow{r}{j} & G \arrow{r}{q} & G\ab \arrow{r} & 1
-\end{tikzcd}
-\]
-gives
+%1 \arrow{r} & H \arrow{r}{j} & G \arrow{r}{q} & G\ab \arrow{r} & 1
+%\end{tikzcd}
+%\]
+%gives
 \[
@@
 \CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q_{H}^*} \\
- \CS'(G) \arrow{u}{\text{forget}}  \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}} &  \CS_{H}(G) \arrow{u}{\text{forget}}  & 
+ \CS'(G)  \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}} &  \CS_{H}(G) \arrow{u}{\text{forget}}  & 
 \end{tikzcd}
@@
 Here we use the notation $\CS'(G)$ from Section~\ref{ssec:noncomdef} and the observation that $\CS'(G)$ is precisely the category $\CS^{H}(G)$ from Section~\ref{ssec:closed} for $H=G\der$.
+The forget
 Since the quotient $q : G \to G\ab$ is a trivial $H$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}, 
@@
 \CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q_{H}^*} \\
-\arrow{u}{\text{forget}} \CS'(G)  \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}} 
+\CS'(G)  \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}} 
 &  \CS_{H}(G) \arrow{u}{\text{forget}}  
@@
 
-Combining Theorems \ref{thm:trfrobiso} and \ref{thm:Gab} gives an isomorphism $\CCSiso{G} \to G\ab(k)^*$. \todo{Could we turn this into a declared corollary/theorem? It's a nice result.}
+Combining Theorems \ref{thm:trfrobiso} and \ref{thm:Gab} gives an isomorphism $\CCSiso{G} \to G\ab(k)^*$. \todo{Could we turn this into a declared proposition? It's a nice result.}
 We may thus ask for a condition on a commutative character sheaf on $G$ that corresponds to having trivial

### 2015-11-15 followup.tex
Added objects and automorphism groups to Section 3.

@@
 Next, we broaden our scope further to encompass smooth group schemes $G$ that are not necessarily commutative.
-In this paper, we do not consider Lusztig's geometrization of arbitrary characters of the non-abelian group $G(k)$
-using character sheaves \cite{lusztig:85a}*{Def.~2.10}, but focus only on the case of $1$-dimensional characters
-$\Hom(G(k), \EEx)$.  The category $\CS(G)$ has a straightforward generalization to this case, but again
+In this paper, we do not consider Lusztig's geometrization of arbitrary characters of the non-abelian group $G(k)$, when $G$ is reductive,
+using character sheaves \cite{lusztig:85a}*{Def.~2.10}, but focus on the case of $1$-dimensional characters
+$\Hom(G(k), \EEx)$ assuming only that $G$ is smooth. The category $\CS(G)$ has a straightforward generalization to this case, but again
 there are more linear character sheaves than there are characters, as pointed out by Kamgarpour \cite{kamgarpour:09a}*{(1.1)}.
@@
 Set $m' = i \circ m \circ \theta$; then $j\circ c = m \circ (m \times m')$.
-Thus, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms, below.
+Then, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms, below.
 \begin{equation}
@@
 In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations; so, for example, the middle left isomorphism comes from $(m\times m')^* m^* \iso c^* j^*$ since $j\circ c = m \circ (m \times m')$.
-Using the monoidal structure of the category of Weil local systems on $G\times G$, this isomorphism, in turn, defines an isomorphism
-$
+Using the monoidal structure of the category of Weil local systems on $G\times G$, the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ defines an isomorphism
+\[
 m^*\cs{L} \to (\theta^* m^* i^*\cs{L})^\vee.
-$
+\]
 Since $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ canonically, and since $\cs{L}^\vee \iso i^*\cs{L}$, canonically, this defines the promised isomorphism
@@
 
+\subsection{Objects and maps in commutative character sheaves}
+
+Theorem~\ref{thm:Gab} shows that $\CCS(G)$ is a categorical solution to the problem that linear character sheaves on $G$ need not be trivial on $G\der$, as discussed at the beginning of Section~\ref{sec:noncom}; at the same time, it is the categorical solution to the problem, discussed in Section~\ref{ssec:defect}, that the dictionary between linear character sheaves on $G\ab$ and characters of $G\ab$, need not be perfect.
+%
+But a description of $\CCS(G)$ requires, at the very least, a description of isomorphism classes of objects, and maps. 
+%
+
 \todo{We should give the relationship between $\CCSiso{G}$ and $G(k)^*$ here as a corollary.  Also, include the automorphism group of a commutative character sheaf.}
-
-\todo{Comment here on Masoud's work.}
+\todo{Is this what you had in mind?}
+
+\begin{proposition}
+The trace of Frobenius $\TrFrob{} : \CCSiso{G}\to G(\Fq)^*$ fits into the following diagram,
+\[
+\begin{tikzcd}
+\ & & \CCSiso{G\ab} \arrow{d}{\TrFrob{}}[swap]{\iso} \arrow{r}{\iso} & \CCSiso{G} \arrow{d}{\TrFrob{}}& \\
+1 \arrow{r} & \Delta^* \arrow{r} & G\ab(k)^* \arrow{r} & G(k)^* \arrow{r} & 1,
+\end{tikzcd}
+\]
+where $\Delta$ denotes the image of the connecting homomorphism $G\ab(\Fq) \to \Hh^1(\Fq, G\der)$.
+In particular, isomorphism classes of objects in $\CCS(G)$ are canonically identified with the group $G\ab(\Fq)^*$.
+\end{proposition}
+
+\begin{proof}
+Let $\Delta$ be the image of the boundary homomorphism $\delta$ in the sequence
+\[
+1 \to G\der(k) \to G(k) \to G\ab(k) \xrightarrow{\delta} \Hh^1(k, G\der),
+\]
+yielding a short exact sequence
+\[
+1 \to G(k) / G\der(k) \to G\ab(k) \to \Delta \to 1.
+\]
+Applying $\Hom(-, \EEx)$ and using the fact that every homomorphism $G(k) \to \EEx$ vanishes on $G\der(k)$, we get
+\[
+1 \to \Delta^* \to G\ab(k)^* \to G(k)^* \to 1.
+\]
+By Theorem~\ref{thm:Gab}, the trace of Frobenius map 
+\end{proof}
+
+\begin{proposition}
+Every map in $\CCS(G)$ is either trivial or an isomorphism. 
+For every commutative character sheaf on $G$, its automorphism group is
+$
+\Hh^1(\pi_0(G\ab),\EEx)^{\Frob{}}.
+$
+\end{proposition}
+
+\begin{proof}
+$= \Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab) =$
+\end{proof}
 
@@
 
-We may now revisit the definition of the functor $q_H^*: \CS(G_0)\to \CS_H(G)$. 
-On objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$. \todo{Shorten this, actually, and combine with the next paragraph.}
-To verify that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$, one must confirm \cite{cunningham-roe:13a}*{CS1, CS2, CS3}, \eqref{E1}, \eqref{E2} and \eqref{ECS1}. 
-Conditions \cite{cunningham-roe:13a}*{CS1, CS2, CS3} follow from an adaptation of \cite{cunningham-roe:13a}*{} while conditions \eqref{E1}, \eqref{E2} are a consequence of the work above. 
-Condition \eqref{ECS1} is confirmed by brute force.
-On maps, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\alpha_0) = L_1(\alpha_0)$.
-To verify that $L_1(\alpha_0)$ is a map in $\CS_H(G)$ we must confirm conditions \cite{cunningham-roe:13a}*{CS4} and \eqref{E3}.
-Condition \cite{cunningham-roe:13a}*{CS4} follows from an adaptation of \cite{cunningham-roe:13a}*{} while condition \eqref{E3} is a consequence of the work above.
-
+We may now revisit the definition of the functor $q_H^*: \CS(G_0)\to \CS_H(G)$:
+on objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$; on maps, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\alpha_0) = L_1(\alpha_0)$.
+Direct calculation confirms \cite{cunningham-roe:13a}*{CS1, CS2, CS3}, \eqref{E1}, \eqref{E2} and \eqref{ECS1}, and therefore that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$; 
+likewise, $L_1(\alpha_0)$ is a map in $\CS_H(G)$ after checking \cite{cunningham-roe:13a}*{CS4} and \eqref{E3}.
+%
 With this description of $q_H^*: \CS(Q)\to \CS_H(G)$ is is easy to see that it is an equivalence.
@@
 
-\subsection{Commutative quasicharacter sheaves}
+\subsection{Linear characters of certain $p$-adic groups}
 

### 2015-11-15 followup.tex
Added review and proposition to Section 4. But it's very rough, still.
I need to put this down for a few hours.

@@
 \]
-By Theorem~\ref{thm:Gab}, the trace of Frobenius map 
-\end{proof}
+By Theorem~\ref{thm:Gab}, the trace of Frobenius map  . . . .\todo{Finish this.}
+\end{proof}
+
+\begin{remark}
+Note that when $\Hh^1(k,G\der) = 0$, as is the case when $G\der(\bFq)$ ``is simply connected,'' then $\CCSiso{G} \iso G(\Fq)^*$, so
+we succeed in geometrizing characters of $G(k)$ on the nose.
+\end{remark}
 
@@
 $
-\Hh^1(\pi_0(G\ab),\EEx)^{\Frob{}}.
+((\pi_0(G\ab))^*)^{\Frob{}}.
 $
@@
 \begin{proof}
-$= \Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab) =$
+By Theorem~\ref{thm:Gab}, $\Aut_{\CCS(G)}(\cs{L},\mu,\beta) = \Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab)$. 
+By \cite{cunningham-roe:13a}*{Thm 3.9},  $\Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab) = ((\pi_0(G\ab))^*)^{\Frob{}}$.
 \end{proof}
@@
 
+\section{Application to type theory for $p$-adic groups}
+
 \iffalse
-
-\subsection{Change of action}
-
-Now, let $a' : H'\times G \to G$ be another group action on $G$ and suppose $f: H \times G \to H'\times G$ makes the following diagram commute.
-\[
-\begin{tikzcd}
-&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
-G & & G \\
-& \arrow{ul}{a'} H' \times G \arrow{ur}[swap]{p} & 
-\end{tikzcd}
-\]
-Then pull-back along $f: H\times G \to H'\times G$ defines a monoidal functor 
-\[
-\CS_{H'}(G) \to \CS_{H}(G).
-\]
-
-Then $f : H\times G \to H'\times G$ is given by $f(h,g) = (k(h,g),g)$ for some $k : H\times G\to H'$. 
-Define $d : H\to H'$ by $d(h) = k(h,1)$.
-
-\begin{lemma}\label{lem:action}
-The canonical functor
-\[
-\CS_{H}(G) \to \CS_{H'}(G)
-\]
-is an equivalence if ...
-\end{lemma}
-\begin{proof}
-\end{proof}
-
-\subsection{Conjugation}
-
-We close this section with an alternate characterization of $\CS'(G)$, the category of linear character sheaves $\cs{L}$ on $G$ for which $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
-Recall that $\CS'(G)$ is a full subcategory of $\CS(G)$ and that $\CCS(G)$ is a full subcategory of $\CS'(G)$.
-
-Consider the following case of Section~\ref{ssec:action}.
-
-\fi
-
-\section{Applications}
-
 \subsection{Linear Characters}
@@
 
+\fi
+
  \subsection{Geometric types for supercuspidal representations}
 
-\begin{proposition}
-Let $(\underline{G}(\OK),\rho)$ be a type such that  . . . 
-Set $G = \Gr(\underline{G})$.
-There is a virtual admissible $\ell$-adic sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) \iso \underline{G}(\OK)$.
-\end{proposition}
-
-It is not unique.
+\newcommand{\red}{^{\operatorname{red}}}
 
@@
 Let us refer to the types arising in this manner as {\it generic types}.
-In this section we show that, after fixing an isomorphism $\CC \approx \EE$, every generic type is geometrizable, in the sense that every part of generic type admits a description as a perverse sheaf, from which the type can be recovered.
+In this section we show that every generic type is geometrizable, in a sense which will be made clear below.
+
+\subsection{Review of Yu's types}
+
+\begin{quotation}
+Therefore, up to some linear characters, all the ingredient representations are on groups of
+ the form $H(\mathcal{O})$, where $H$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated $H(\kappa)$.
+These results suggest that algebraic geometry and group schemes should play an
+  from $H$
+important role in the representation theory of p-adic groups.
+\end{quotation}
+
+\subsection{Smooth group schemes for types}
+
+Let $\underline{G}$ be an affine smooth group scheme of finite type over $\OK$ arising in the work of Yu on types for supercuspidal groups.
+We suppose the component group $\pi_0(\underline{G}_s\red)$ of the reductive quotient of the special fibre $\underline{G}_s$ of $\underline{G}$ is cyclic.
+
+The group scheme $\underline{G}$ comes equipped with affine smooth group schemes of finite type over $\OK$
+\[
+\underline{J}^i \to \underline{G},
+\]
+for $j=0, 1, \ldots , d-1,d$, such that
+\[
+\underline{G}(\OK) = \prod_{i=0}^{d} \underline{J}^i(\OK).
+\]
+Let $\underline{G}^{j-1}$ be the canonical smooth model . . 
+We suppose the component group $\pi_0((\underline{G}^{j-1}_s)\red)$ of the reductive quotient of the special fibre $\underline{G}^{j-1}_s$ of $\underline{G}^{j-1}$ is cyclic, for every $j=1, \ldots, d-1$.
+
+\subsection{Geometrization of types}
+
+\begin{proposition}
+Let $(\underline{G}(\OK),\tau)$ be a type such that  . . . 
+Set $G = \Gr(\underline{G})$.
+There is a virtual admissible $\ell$-adic sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \tau$ under the canonical isomorphism $G(\Fq) \iso \underline{G}(\OK)$.
+\end{proposition}
+
+\begin{proof}
+Now, let $(A,\varphi)$ be a Frobenius-stable character sheaf on $\underline{G}_s\red$.
+Let $(A,\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{G}_s$ obtained by pull-back.
+For each $j=1,\ldots, d-1$, 
+let $(A^j, \varphi^j)$ be a character sheaf on $(\underline{G}^{j-1}_s)\red$, in the sense of [Lusztig, CSDG].
+Let $(C_1^j, \phi^j)$ be the Frobenius-stable constructible sheaf on $\underline{G}^{j-1}_s$ obtained by pull-back..
+
+For each $j=1,\ldots, d-1$,
+let $H^j$ be a unipotent group appearing as a quotient $\underline{J}^j_s \to H^j$.
+Let $B^j$ be a character sheaf on $H^j$, in the sense of [Boyarchenko].
+Let $(D_1^j,\varphi^j)$ be the Frobenius-stable constructible sheaf on $\underline{J}^{j}_s$ obtained by pull-back.
+
+Let $n$ be a positive integer and
+for each $j=1,\ldots, d-1$, let $\cs{L}_n^{j-1}$ be a commutative quasicharacter sheaf on $G_n^{j-1}\ceq \Gr_n(\underline{G}^{j-1})$.
+
+Observe that $\underline{G}^{j-1}_s = \Gr_1(\underline{G}^{j-1})$ 
+and $\underline{J}^{j}_s = \Gr_1(\underline{G}^{j-1})$. 
+Let $(\cs{C}_n^j,\phi^j)$ be the admissible sheaf on $G_n^{j-1} \ceq \Gr_n(\underline{G}^{j-1})$ obtained by pulling-back $C_1$ along $G_n^{j-1} \to \underline{G}^{j-1}_s$.
+Let $(\cs{D}_n^j,\phi^j)$ be the admissible sheaf on $J_n^{j-1} \ceq \Gr_n(\underline{J}^{j-1})$ obtained by pull-back along $J_n^{j-1} \to \underline{J}^{j-1}_s$.
+
+Set $\underline{N}^j = \prod_{i=j}^d \underline{J}^i$ and let $\underline{G} \to \underline{M}^j$ be the morphism . . . .
+Then $\underline{M}^j = \underline{G}^{j-1} \underline{J}^j$ . . . 
+%
+Now, consider the following sheaf on $M_n^j \ceq \Gr_n(\underline{M}^j)$:
+\[
+\cs{E}_n^j \ceq (\cs{L}_n^{j-1}\otimes \cs{C}_n^j) \boxtimes \cs{D}_n^{j}
+\]
+Let $\cs{F}_n^j$ be the pullback along $G_n :=\Gr_n(\underline{G}) \to \Gr_n(\underline{M}^j):= M_n^j$.
+Finally, set $\cs{F}_n = \otimes_i \cs{F}^i_n$.
+
+\end{proof}
+
+\iffalse
 
@@
 %\subsection{Toral supercuspidal representations of $p$-adic groups}
+
+\fi
 
@@
 We now combine the material of the last two sections, by specializing to the following case: $H$ is a closed subgroup of $G$ and $q : G \to G/H$ is the fppf quotient, which exists in schemes by  . . .
+
+\iffalse
+
+\subsection{Change of action}
+
+Now, let $a' : H'\times G \to G$ be another group action on $G$ and suppose $f: H \times G \to H'\times G$ makes the following diagram commute.
+\[
+\begin{tikzcd}
+&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
+G & & G \\
+& \arrow{ul}{a'} H' \times G \arrow{ur}[swap]{p} & 
+\end{tikzcd}
+\]
+Then pull-back along $f: H\times G \to H'\times G$ defines a monoidal functor 
+\[
+\CS_{H'}(G) \to \CS_{H}(G).
+\]
+
+Then $f : H\times G \to H'\times G$ is given by $f(h,g) = (k(h,g),g)$ for some $k : H\times G\to H'$. 
+Define $d : H\to H'$ by $d(h) = k(h,1)$.
+
+\begin{lemma}\label{lem:action}
+The canonical functor
+\[
+\CS_{H}(G) \to \CS_{H'}(G)
+\]
+is an equivalence if ...
+\end{lemma}
+\begin{proof}
+\end{proof}
+
+\subsection{Conjugation}
+
+We close this section with an alternate characterization of $\CS'(G)$, the category of linear character sheaves $\cs{L}$ on $G$ for which $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
+Recall that $\CS'(G)$ is a full subcategory of $\CS(G)$ and that $\CCS(G)$ is a full subcategory of $\CS'(G)$.
+
+Consider the following case of Section~\ref{ssec:action}.
+
+\fi

### 2015-11-15 followup.tex
Playing with subsubsections in Section 3. What do you think?

@@
 character sheaves whose restriction to the derived subgroup is nontrivial.
-The following proposition will be proven in Section \ref{ssec:proofs}.
+The following proposition will be proven in Section \ref{ssec:proof1}.
 \begin{proposition} \label{prop:Gder_triv}
@@
 Sections~\ref{ssec:equivariant1}, \ref{ssec:equivariant2}, \ref{ssec:descent} and \ref{ssec:closed} set up machinery needed to prove Theorem~\ref{thm:Gab}.
-The precise definition of the functor $\CCS(G\ab) \to \CCS(G)$ will be given with the proof of Theorem~\ref{thm:Gab}, in Section~\ref{ssec:proofs}.
+The precise definition of the functor $\CCS(G\ab) \to \CCS(G)$ will be given with the proof of Theorem~\ref{thm:Gab}, in Section~\ref{ssec:proof2}.
 
@@
 
-\subsection{Equivariant Weil local systems}\label{ssec:equivariant1}
+\subsection{Proofs for results from Section \ref{ssec:noncomdef}} \label{ssec:proofs}
+
+\subsubsection{Equivariant Weil local systems}\label{ssec:equivariant1}
 
@@
 
-\subsection{Equivariant linear character sheaves}\label{ssec:equivariant2}
+\subsubsection{Equivariant linear character sheaves}\label{ssec:equivariant2}
 
@@
 
-\subsection{Descent along a torsor}\label{ssec:descent}
+\subsubsection{Descent along a torsor}\label{ssec:descent}
 
@@
 
-\subsection{Quotient by a closed subgroup}\label{ssec:closed}
+\subsubsection{Quotient by a closed subgroup}\label{ssec:closed}
 
@@
 
-\subsection{Proofs for results from Section \ref{ssec:noncomdef}}\label{ssec:proofs}
-
 We can now give the missing proofs from Section \ref{ssec:noncomdef}.
 
-\begin{proof}[Proof of Proposition~\ref{prop:Gder_triv}]
+\subsubsection{Proof of Proposition~\ref{prop:Gder_triv}}\label{ssec:proof1}
+
+%\begin{proof}[Proof of Proposition~\ref{prop:Gder_triv}] 
 The abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
@@
 Since the essential image of the forgetful functor $\CS'(G)\to \CS(G)$ is precisely the category of $(\cs{L},\mu)\in \CS(G)$ such that $\cs{L}\vert_{H} \iso (\EE)_{H}$, this completes the proof of Proposition~\ref{prop:Gder_triv}.
-\end{proof}
-
-\begin{proof}[Proof of Theorem~\ref{thm:Gab}] 
+%\end{proof}
+
+\subsubsection{Proof of Theorem~\ref{thm:Gab}}\label{ssec:proof2}
+
+%\begin{proof}[Proof of Theorem~\ref{thm:Gab}] 
 Here we use notation from the proof of Proposition~\ref{prop:Gder_triv};
@@
 %This also defines the functor $\CCS(G\ab) \to \CCS(G)$ by the dashed arrow in the diagram above.
-\end{proof}
+%\end{proof}
 

### 2015-11-16 followup.tex
Moving to a different computer. Starting on Section 4.
Added review of types and statement of the geometrization result

@@
 
- \subsection{Geometric types for supercuspidal representations}
+%\subsection{Geometric types for supercuspidal representations}
 
@@
 
-As proved in \cite{kim:07a}, many (complex) supercuspidal representations of $p$-adic groups can be built from the generic data of \cite{yu:01a}*{\S 15} and, moreover, the type (in the sense of \cite{bushnell-kutzko:98a}) of the resulting supercuspidal representations can be constructed directly from the generic data.
+As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the generic data of \cite{yu:01a}*{\S 15}.
+The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from the generic data. 
 Let us refer to the types arising in this manner as {\it generic types}.
@@
 
+As explained in \cite{yu:models}, a generic type may be apprehended as a pair $(\underline{G}(\OK), \rho)$, where $\underline{G}$ is an affine smooth group scheme of finite type over $\OK$ and where $\rho$ is a representation of $\underline{G}(\OK)$.
+The group scheme $\underline{G}$ comes with the following auxillary data:
+\begin{enumerate}
+\item
+	affine smooth group schemes $\underline{J}^i$, for $i=0, 1, \ldots, d$, together with morphisms $\underline{J}^i \to \underline{G}$ such that \[\prod_{i=0}^d \underline{J}^i(\OK) = \underline{G}(\OK),\] where we identify $\underline{J}^i(\OK)$ with its image under $\underline{J}^i \to \underline{G}$, and such that $\prod_{i=j+1}^{d} \underline{J}^i(\OK)$ is normal in $\underline{G}(\OK)$, for $j=1, \ldots, d$;
+\item affine smooth group schemes $\underline{G}^{j}$, for $j=1, \ldots, d$, together with morphisms $\underline{G}^{j}\to \underline{G}$ such that 
+\[
+\underline{G}^{j}(\OK) = \prod_{i=0}^{j} \underline{J}^i(\OK),
+\] 
+where we identify $\underline{J}^i(\OK)$ with its image under $\underline{J}^i \to \underline{G}$ and $\underline{G}^{j}(\OK)$ with its image under $\underline{G}^j \to \underline{G}$.
+\end{enumerate}
+The representation $\rho$ of $\underline{G}(\OK)$ is build from the following data:
+\begin{enumerate}
+\item
+	a representation $\sigma_0$ of $\underline{G}_s\red(\Fq)$;
+\item
+	a representation $\epsilon_j$ of $(\underline{G}^{j-1})_s\red(\Fq)$, for each $j=1,\ldots, d$;
+\item
+	a representation $\eta_j$ of $H^j(\Fq)$, where $H^j$ is Heisenberg group arising as a quotient $(\underline{J}^{j})_s \to H^i$, for each $j=1,\ldots, d$;
+\item
+	a linear quasicharacter $\phi_{j-1}$ of $\underline{G}^{j-1}(\OK)$, for $j=1,\ldots, d$;
+\item
+	a linear quasicharacter $\tau_d$ of $\underline{G}(\OK)$.
+\end{enumerate}
+From this data, the representation $\rho$ is built as follows.
+\begin{enumerate}
+\item 
+	Let $\tau_0$ be the representation of $\underline{G}(\OK)$ obtained by pulling back $\sigma_0$ along 
+\[\underline{G}(\OK) \to \underline{G}_s(\Fq) \to \underline{G}_s\red(\Fq).\]
+\item 
+	Let $\dot{\epsilon}_j$ be the representation of $\underline{G}^{j-1}(\OK)$ obtained by pulling back $\epsilon_j$ along 
+\[\underline{G}^{j-1}(\OK) \to \underline{G}^{j-1}_s(\Fq) \to (\underline{G}^{j-1})_s\red(\Fq),\]
+for $j=1,\ldots, d-1$.
+\item
+	Let $\dot{\eta}_j$ be the representation of $\underline{J}^j(\OK)$ obtained by pulling back $\eta_j$ along 
+\[\underline{J}^{j}(\OK) \to \underline{J}^{j}_s(\Fq) \to H^j(\Fq),\]
+for $j=1,\ldots, d-1$.
+\item
+	Using the decomposition $\underline{G}^j(\OK) = \underline{G}^{j-1}(\OK) \times \underline{J}^j(\OK)$, consider the representation $(\phi_{j-1}\otimes \dot{\epsilon}_j)\times \dot{\eta}_j$ of $\underline{G}^{j}(\OK)$, for $j=1,\ldots, d-1$.
+	Since $\prod_{i=j+1}^{d} \underline{J}^i(\OK)$ is normal in $\underline{G}(\OK)$, this determines a representation $\tau_j$ of $\underline{G}(\OK)$, for $j=1,\ldots, d-1$. 
+\item
+	Then $\rho = \tau_0 \otimes \cdots \tau_d$.
+\end{enumerate}
+
+Regarding this construction of the type $(\underline{G}(\OK),\rho)$, Yu points out that,
 \begin{quotation}
-Therefore, up to some linear characters, all the ingredient representations are on groups of
- the form $H(\mathcal{O})$, where $H$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated $H(\kappa)$.
+{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
+ the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
 These results suggest that algebraic geometry and group schemes should play an
-  from $H$
-important role in the representation theory of p-adic groups.
+important role in the representation theory of $p$-adic groups.} \cite{yu:models}
 \end{quotation}
-
-\subsection{Smooth group schemes for types}
-
-Let $\underline{G}$ be an affine smooth group scheme of finite type over $\OK$ arising in the work of Yu on types for supercuspidal groups.
-We suppose the component group $\pi_0(\underline{G}_s\red)$ of the reductive quotient of the special fibre $\underline{G}_s$ of $\underline{G}$ is cyclic.
-
-The group scheme $\underline{G}$ comes equipped with affine smooth group schemes of finite type over $\OK$
-\[
-\underline{J}^i \to \underline{G},
-\]
-for $j=0, 1, \ldots , d-1,d$, such that
-\[
-\underline{G}(\OK) = \prod_{i=0}^{d} \underline{J}^i(\OK).
-\]
-Let $\underline{G}^{j-1}$ be the canonical smooth model . . 
-We suppose the component group $\pi_0((\underline{G}^{j-1}_s)\red)$ of the reductive quotient of the special fibre $\underline{G}^{j-1}_s$ of $\underline{G}^{j-1}$ is cyclic, for every $j=1, \ldots, d-1$.
+%
 
@@
 
-\begin{proposition}
-Let $(\underline{G}(\OK),\tau)$ be a type such that  . . . 
-Set $G = \Gr(\underline{G})$.
-There is a virtual admissible $\ell$-adic sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \tau$ under the canonical isomorphism $G(\Fq) \iso \underline{G}(\OK)$.
+The objective of this section is to push Yu's observation further to prove the following result.
+
+\begin{proposition}\label{prop:types}
+Let $(\underline{G}(\OK),\rho)$ be a generic type.
+Set $G = \Gr(\underline{G})$, the Greenberg transform of $\underline{G}$; recall that this is a group scheme over $\Fq$.
+There is a virtual admissible $\ell$-adic sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
 \end{proposition}
@@
 \begin{proof}
+First, we make some observations concerning the auxillary data for $\underline{G}$.
+
 Now, let $(A,\varphi)$ be a Frobenius-stable character sheaf on $\underline{G}_s\red$.

### 2015-11-16 followup.tex
Lots of work on Section 4, but all very rough. Out of time for now...

@@
 Next, we broaden our scope further to encompass smooth group schemes $G$ that are not necessarily commutative.
-In this paper, we do not consider Lusztig's geometrization of arbitrary characters of the non-abelian group $G(k)$, when $G$ is reductive,
+In this paper, we do not consider Lusztig's geometrization of arbitrary characters of the non-abelian group $G(k)$, where $G$ is reductive,
 using character sheaves \cite{lusztig:85a}*{Def.~2.10}, but focus on the case of $1$-dimensional characters
@@
 $\CCS(G\ab) \to \CCS(G)$.  Note that the functor $\CCS(G) \to \CS(G)$ is not essentially surjective, missing
-the kinds of linear character sheaves highlighted by Kamgarpour.  Moreover, $\Hom(G\ab(k), \EEx)$ surjects
-onto $\Hom(G(k), \EEx)$, with a kernel described by Galois cohomology.
+the kinds of linear character sheaves highlighted by Kamgarpour.  
+Since $\Hom(G\ab(k), \EEx)$ surjects
+onto $\Hom(G(k), \EEx)$, with a kernel described by Galois cohomology, this paper shows that, for every linear character $\chi : G(k) \to \EEx$ there is a commutative character sheaf $\cs{L}$ on $G$ such that $\TrFrob{G}(\cs{L})\circ q = \chi$.
 
@@
 %
-
-\todo{We should give the relationship between $\CCSiso{G}$ and $G(k)^*$ here as a corollary.  Also, include the automorphism group of a commutative character sheaf.}
-\todo{Is this what you had in mind?}
 
@@
 
-As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the generic data of \cite{yu:01a}*{\S 15}.
-The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from the generic data. 
-Let us refer to the types arising in this manner as {\it generic types}.
-In this section we show that every generic type is geometrizable, in a sense which will be made clear below.
+As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
+The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from the data. 
+Let us refer to the types arising in this manner as {\it Yu types}.
+In this section we show that every Yu type is geometrizable, in a sense which will be made clear below.
 
@@
 
-As explained in \cite{yu:models}, a generic type may be apprehended as a pair $(\underline{G}(\OK), \rho)$, where $\underline{G}$ is an affine smooth group scheme of finite type over $\OK$ and where $\rho$ is a representation of $\underline{G}(\OK)$.
-The group scheme $\underline{G}$ comes with the following auxillary data:
+A Yu type is a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, with certain properties. 
+One of the main results of \cite{yu:models} is that there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that $\,^\circ K = \underline{G}(\OK)$ \cite{yu:models}*{Prop 10.2}.
+As explained in \cite{yu:models}*{\S 10.4}, the
+the group scheme $\underline{G}$ comes with the following auxillary data:
 \begin{enumerate}
@@
 \end{enumerate}
-The representation $\rho$ of $\underline{G}(\OK)$ is build from the following data:
+
+The representation $\,^\circ \rho$ of $\underline{G}(\OK)$ is build from the following data, as explained in \cite{yu:models}*{\S 10.5}:
 \begin{enumerate}
 \item
-	a representation $\sigma_0$ of $\underline{G}_s\red(\Fq)$;
-\item
-	a representation $\epsilon_j$ of $(\underline{G}^{j-1})_s\red(\Fq)$, for each $j=1,\ldots, d$;
-\item
-	a representation $\eta_j$ of $H^j(\Fq)$, where $H^j$ is Heisenberg group arising as a quotient $(\underline{J}^{j})_s \to H^i$, for each $j=1,\ldots, d$;
+	a representation $\sigma$ of $\underline{G}_s\red(\Fq)$;
+\item
+for $j=1,\ldots, d-1$, 
+\begin{enumerate}
+\item
+a representation $\eta_j$ of $H^j(\Fq)$, where $H^j$ is Heisenberg group arising as a quotient $(\underline{J}^{j})_s \to H^i$,
+\item
+a representation $\epsilon_j$ of $(\underline{G}^{j-1})_s\red(\Fq)$
 \item
 a linear quasicharacter $\phi_{j-1}$ of $\underline{G}^{j-1}(\OK)$, for $j=1,\ldots, d$;
+\end{enumerate}
 \item
@@
 \end{enumerate}
-From this data, the representation $\rho$ is built as follows.
+From this data, the representation $\,^\circ \rho$ is built as follows.
 \begin{enumerate}
 \item 
-	Let $\tau_0$ be the representation of $\underline{G}(\OK)$ obtained by pulling back $\sigma_0$ along 
+	Let $\tau_0$ be the representation of $\underline{G}(\OK)$ obtained by pulling back $\sigma$ along 
 \[\underline{G}(\OK) \to \underline{G}_s(\Fq) \to \underline{G}_s\red(\Fq).\]
+\item For $j=1,\ldots, d-1$, 
+\begin{enumerate}
+\item
+	Let $\dot{\eta}_j$ be the representation of $\underline{J}^j(\OK)$ obtained by pulling back $\eta_j$ along 
+\[\underline{J}^{j}(\OK) \to \underline{J}^{j}_s(\Fq) \to H^j(\Fq),\]
+for $j=1,\ldots, d-1$.
 \item 
@@
 \item
-	Let $\dot{\eta}_j$ be the representation of $\underline{J}^j(\OK)$ obtained by pulling back $\eta_j$ along 
-\[\underline{J}^{j}(\OK) \to \underline{J}^{j}_s(\Fq) \to H^j(\Fq),\]
-for $j=1,\ldots, d-1$.
-\item
-	Using the decomposition $\underline{G}^j(\OK) = \underline{G}^{j-1}(\OK) \times \underline{J}^j(\OK)$, consider the representation $(\phi_{j-1}\otimes \dot{\epsilon}_j)\times \dot{\eta}_j$ of $\underline{G}^{j}(\OK)$, for $j=1,\ldots, d-1$.
+	Using the decomposition $\underline{G}^j(\OK) = \underline{G}^{j-1}(\OK) \times \underline{J}^j(\OK)$, consider the representation 
+\[
+	(\phi_{j-1}\otimes \dot{\epsilon}_j)\times \dot{\eta}_j
+\]
+ of $\underline{G}^{j}(\OK)$, for $j=1,\ldots, d-1$. 
 	Since $\prod_{i=j+1}^{d} \underline{J}^i(\OK)$ is normal in $\underline{G}(\OK)$, this determines a representation $\tau_j$ of $\underline{G}(\OK)$, for $j=1,\ldots, d-1$. 
-\item
-	Then $\rho = \tau_0 \otimes \cdots \tau_d$.
 \end{enumerate}
-
-Regarding this construction of the type $(\underline{G}(\OK),\rho)$, Yu points out that,
+\item
+	Then $\,^\circ \rho = \tau_0 \otimes \cdots \tau_d$.
+\end{enumerate}
+
+Regarding this construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:models} concludes with the following provocative observation.
 \begin{quotation}
@@
 %
+The objective of this section is to push this observation further by geometrizing the representation $\,^\circ \rho$ of $\underline{G}$.
 
@@
 
-The objective of this section is to push Yu's observation further to prove the following result.
+Let $(\underline{G}(\OK),\,^\circ \rho)$ be a Yu type.
+Set $G = \Gr(\underline{G})$, the Greenberg transform of $\underline{G}$.
+Recall that $G$ is a group scheme over $\Fq$ and comes equipped with
 
 \begin{proposition}\label{prop:types}
-Let $(\underline{G}(\OK),\rho)$ be a generic type.
-Set $G = \Gr(\underline{G})$, the Greenberg transform of $\underline{G}$; recall that this is a group scheme over $\Fq$.
-There is a virtual admissible $\ell$-adic sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
+Let $(\underline{G}(\OK),\rho)$ be a Yu type.
+With notation as above, suppose $\pi_0(\underline{G}_s\red)$ is cyclic and that $\pi_0((\underline{G}^{j-1})_s\red)$ is cyclic for $j=1,\ldots, d-1$.
+Then there is a virtual admissible $\ell$-adic sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
 \end{proposition}
@@
 
-Now, let $(A,\varphi)$ be a Frobenius-stable character sheaf on $\underline{G}_s\red$.
+Introduce morphisms $\underline{G}\to \underline{M}^j$ and $\underline{M}^{j} \to \underline{M}^{j-1}$ and $\underline{M}^j \to \underline{J}^j$.
+\[
+\begin{tikzcd}
+\underline{J}^j \arrow{r} & \underline{G}^{j} \arrow{r} 
+& \underline{G} \arrow{r}  
+& \underline{M}^{j} \arrow{d} \arrow{r} & \underline{J}^j \\
+& \arrow{u} \underline{G}^{j-1} 
+&
+& \underline{M}^{j-1}
+&
+\end{tikzcd}
+\]
+Interpret 
+\begin{enumerate}
+\item
+	$\epsilon_j$ as a representation of $(\underline{M}^{j-1})_s\red(\Fq)$, for each $j=1,\ldots, d$;
+\item
+	$\phi_{j-1}$ as a linear quasicharacter of $\underline{M}^{j-1}(\OK)$, for $j=1,\ldots, d$;
+\end{enumerate}
+so that
+\begin{enumerate}
+\item 
+	$\dot{\epsilon}_j$ is the representation of $\underline{M}^{j-1}(\OK)$ obtained by pulling back $\epsilon_j$ along 
+\[\underline{M}^{j-1}(\OK) \to \underline{M}^{j-1}_s(\Fq) \to (\underline{M}^{j-1})_s\red(\Fq),\]
+for $j=1,\ldots, d-1$.
+\item
+	$\dot{\eta}_j$ is a representation of $\underline{J}^{j}(\OK)$ obtained by pulling back  . . . .  $j=1,\ldots, d-1$;
+\item
+	$\tau_j$ is the representation of $\underline{G}(\OK)$ obtained by pulling back  $\phi_{j-1}$ and $\dot{\epsilon}_j$ and $\dot{\eta}_j$ from $\underline{M}^{j}(\OK)$ along $\underline{G}(\OK)\to \underline{M}^j(\OK)$, for $j=1,\ldots, d-1$.
+\end{enumerate}
+
+\[
+\begin{tikzcd}
+\underline{G} \arrow{r}  
+& \underline{M}^{j} \arrow{d} \arrow{r} & \underline{J}^j \\
+\underline{G}_s \arrow{u} \arrow{d}
+& \underline{M}^{j-1}
+ & (\underline{J}^j)_s \arrow{u} \arrow{d} \\
+\underline{G}_s\red & (\underline{M}^{j-1})_s \arrow{u} \arrow{d} & H^j \\
+& (\underline{M}^{j-1})_s\red & 
+\end{tikzcd}
+\]
+
+Now, we introduce the tools needed to geometrize all the ingredient representations.
+\begin{enumerate}
+\item
+Let $(A_0,\varphi)$ be a Frobenius-stable character sheaf on $\underline{G}_s\red$, in the sense of [Lusztig].
 Let $(A,\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{G}_s$ obtained by pull-back.
-For each $j=1,\ldots, d-1$, 
-let $(A^j, \varphi^j)$ be a character sheaf on $(\underline{G}^{j-1}_s)\red$, in the sense of [Lusztig, CSDG].
-Let $(C_1^j, \phi^j)$ be the Frobenius-stable constructible sheaf on $\underline{G}^{j-1}_s$ obtained by pull-back..
-
-For each $j=1,\ldots, d-1$,
-let $H^j$ be a unipotent group appearing as a quotient $\underline{J}^j_s \to H^j$.
-Let $B^j$ be a character sheaf on $H^j$, in the sense of [Boyarchenko].
-Let $(D_1^j,\varphi^j)$ be the Frobenius-stable constructible sheaf on $\underline{J}^{j}_s$ obtained by pull-back.
-
-Let $n$ be a positive integer and
-for each $j=1,\ldots, d-1$, let $\cs{L}_n^{j-1}$ be a commutative quasicharacter sheaf on $G_n^{j-1}\ceq \Gr_n(\underline{G}^{j-1})$.
-
-Observe that $\underline{G}^{j-1}_s = \Gr_1(\underline{G}^{j-1})$ 
-and $\underline{J}^{j}_s = \Gr_1(\underline{G}^{j-1})$. 
-Let $(\cs{C}_n^j,\phi^j)$ be the admissible sheaf on $G_n^{j-1} \ceq \Gr_n(\underline{G}^{j-1})$ obtained by pulling-back $C_1$ along $G_n^{j-1} \to \underline{G}^{j-1}_s$.
-Let $(\cs{D}_n^j,\phi^j)$ be the admissible sheaf on $J_n^{j-1} \ceq \Gr_n(\underline{J}^{j-1})$ obtained by pull-back along $J_n^{j-1} \to \underline{J}^{j-1}_s$.
-
-Set $\underline{N}^j = \prod_{i=j}^d \underline{J}^i$ and let $\underline{G} \to \underline{M}^j$ be the morphism . . . .
-Then $\underline{M}^j = \underline{G}^{j-1} \underline{J}^j$ . . . 
-%
-Now, consider the following sheaf on $M_n^j \ceq \Gr_n(\underline{M}^j)$:
-\[
-\cs{E}_n^j \ceq (\cs{L}_n^{j-1}\otimes \cs{C}_n^j) \boxtimes \cs{D}_n^{j}
-\]
-Let $\cs{F}_n^j$ be the pullback along $G_n :=\Gr_n(\underline{G}) \to \Gr_n(\underline{M}^j):= M_n^j$.
-Finally, set $\cs{F}_n = \otimes_i \cs{F}^i_n$.
+\item For $j=1,\ldots, d-1$, 
+\begin{enumerate}
+\item
+Let $(B_0^{j},\varphi)$ be a Frobenius-stable character sheaf on $H^j$ in the sense of [Boyarchenko].
+Let $(B^{j},\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{J}^j_s$ obtained by pull-back.
+\item
+Let $(C_0^{j-1},\varphi)$ be a Frobenius-stable character sheaf on $(\underline{M}^{j-1})_s\red$ in the sense of [Lusztig].
+Let $(C^{j-1},\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{M}^{j-1}_s$ obtained by pull-back.
+\item
+Let $\cs{E}_n$ be a commutative quasicharacter sheaf on $M_n^{j-1}$.
+\end{enumerate}
+\item
+Let $\cs{L}_n$ be a commutative quasicharacter sheaf on $G_n$.
+\end{enumerate}
+\[
+\begin{tikzcd}
+G \arrow{r}  \arrow{d}
+& M^{j} \arrow{r} \arrow{d}
+& J^j \arrow{d} \\
+G_n \arrow{r}  \arrow{d}
+& M_n^{j} \arrow{r} \arrow{d}
+& J_n^j \arrow{d} \\
+\underline{G}_s \arrow{d}
+& \underline{M}^{j-1} \arrow{d}
+& (\underline{J}^j)_s  \arrow{d} \\
+\underline{G}_s\red 
+& (\underline{M}^{j-1})_s \arrow{d} & H^j \\
+& (\underline{M}^{j-1})_s\red 
+& 
+\end{tikzcd}
+\]
+
+We may now encorporate all these ingredients into one sheaf on $G_n$.
+\begin{enumerate}
+\item
+Let $\cs{A}_n$ be sheaf on $G_n$ produced from $A$ by pullback along $G_n \to \underline{G}_s$.
+\item
+For $j=1, \ldots, d-1$,
+\begin{enumerate}
+\item let $\cs{B}^j$ be the sheaf on $M^j_n$ ...
+\item let $\cs{C}^j$ be the sheaf on $M^j_n$ ...
+\item let $\cs{E}^j$ be the sheaf on $M^j_n$ ...
+\end{enumerate}
+\item Let $\cs{L}$ be the sheaf on $G_n$ as above...
+\end{enumerate}
+Combine: $B$, $C$ and $E$ into $D$
+\[
+\cs{A} \otimes \cs{D}^1 \otimes \cdots \otimes \cs{D}^{d-1} \otimes \cs{L}.
+\]
 

### 2015-11-17 followup.tex
Commit for talking . . .

@@
 \begin{enumerate}
-\item
+\item[(Ji)]
 	affine smooth group schemes $\underline{J}^i$, for $i=0, 1, \ldots, d$, together with morphisms $\underline{J}^i \to \underline{G}$ such that \[\prod_{i=0}^d \underline{J}^i(\OK) = \underline{G}(\OK),\] where we identify $\underline{J}^i(\OK)$ with its image under $\underline{J}^i \to \underline{G}$, and such that $\prod_{i=j+1}^{d} \underline{J}^i(\OK)$ is normal in $\underline{G}(\OK)$, for $j=1, \ldots, d$;
-\item affine smooth group schemes $\underline{G}^{j}$, for $j=1, \ldots, d$, together with morphisms $\underline{G}^{j}\to \underline{G}$ such that 
+\item[(Gj)] affine smooth group schemes $\underline{G}^{j}$, for $j=1, \ldots, d$, together with morphisms $\underline{G}^{j}\to \underline{G}$ such that 
 \[
@@
 
-The representation $\,^\circ \rho$ of $\underline{G}(\OK)$ is build from the following data, as explained in \cite{yu:models}*{\S 10.5}:
+The representation $\,^\circ \rho$ of $\underline{G}(\OK)$ is build from the following data:
 \begin{enumerate}
@@
 \item
-for $j=1,\ldots, d-1$, 
+if $d \geq 2$, for $j=1,\ldots, d-1$, 
 \begin{enumerate}
 \item
-a representation $\eta_j$ of $H^j(\Fq)$, where $H^j$ is Heisenberg group arising as a quotient $(\underline{J}^{j})_s \to H^i$,
-\item
-a representation $\epsilon_j$ of $(\underline{G}^{j-1})_s\red(\Fq)$
-\item
-a linear quasicharacter $\phi_{j-1}$ of $\underline{G}^{j-1}(\OK)$, for $j=1,\ldots, d$;
+a representation $\beta_j$ of $H^j(\Fq)$, where $H^j$ is Heisenberg group arising as a quotient $(\underline{J}^{j})_s \to H^j$,
+\item
+a representation $\kappa_j$ of $(\underline{G}^{j-1})_s\red(\Fq)$
+\item
+a linear quasicharacter $\phi_{j-1}$ of $\underline{G}^{j-1}(\OK)$;
 \end{enumerate}
 \item
-	a linear quasicharacter $\tau_d$ of $\underline{G}(\OK)$.
+	a linear quasicharacter $\phi$ of $\underline{G}(\OK)$.
 \end{enumerate}
-From this data, the representation $\,^\circ \rho$ is built as follows.
+From this data, the representation $\,^\circ \rho$ is built as follows, as explained in \cite{yu:models}*{\S 10.5}.
 \begin{enumerate}
 \item 
-	Let $\tau_0$ be the representation of $\underline{G}(\OK)$ obtained by pulling back $\sigma$ along 
-\[\underline{G}(\OK) \to \underline{G}_s(\Fq) \to \underline{G}_s\red(\Fq).\]
+	Let $\dot{\sigma}$ be the representation of $\underline{G}_s(\Fq)$ obtained by pulling back $\sigma$ along $\underline{G}_s(\Fq) \to \underline{G}_s\red(\Fq)$. 	
+	Let $\ddot{\sigma}$ be the representation of $\underline{G}(\OK)$ obtained by pullback along $\underline{G}(\OK) \to \underline{G}_s(\Fq)$.
 \item For $j=1,\ldots, d-1$, 
@@
 \item
-	Let $\dot{\eta}_j$ be the representation of $\underline{J}^j(\OK)$ obtained by pulling back $\eta_j$ along 
-\[\underline{J}^{j}(\OK) \to \underline{J}^{j}_s(\Fq) \to H^j(\Fq),\]
-for $j=1,\ldots, d-1$.
-\item 
-	Let $\dot{\epsilon}_j$ be the representation of $\underline{G}^{j-1}(\OK)$ obtained by pulling back $\epsilon_j$ along 
-\[\underline{G}^{j-1}(\OK) \to \underline{G}^{j-1}_s(\Fq) \to (\underline{G}^{j-1})_s\red(\Fq),\]
-for $j=1,\ldots, d-1$.
-\item
-	Using the decomposition $\underline{G}^j(\OK) = \underline{G}^{j-1}(\OK) \times \underline{J}^j(\OK)$, consider the representation 
-\[
-	(\phi_{j-1}\otimes \dot{\epsilon}_j)\times \dot{\eta}_j
-\]
- of $\underline{G}^{j}(\OK)$, for $j=1,\ldots, d-1$. 
-	Since $\prod_{i=j+1}^{d} \underline{J}^i(\OK)$ is normal in $\underline{G}(\OK)$, this determines a representation $\tau_j$ of $\underline{G}(\OK)$, for $j=1,\ldots, d-1$. 
+	let $\dot{\beta}_j$ be the representation of $\underline{J}^{j}_s(\Fq)$ obtained by pulling back $\beta_j$ along $\underline{J}^{j}_s(\Fq) \to H^j(\Fq)$ and let $\ddot{\beta}_j$ be . . . 
+;
+\item 
+	let $\dot{\kappa}_j$ be the representation of $\underline{G}^{j-1}_s(\Fq)$ obtained by pulling back $\kappa_j$ along $\underline{G}^{j-1}_s(\Fq) \to (\underline{G}^{j-1})_s\red(\Fq)$ and let $\ddot{\kappa}_j$ .
+.
+;
+\item
+	let $\phi_{j-1}$ be the linear quasicharacter of $\underline{G}^{j-1}(\OK)$ as above. 
 \end{enumerate}
-\item
-	Then $\,^\circ \rho = \tau_0 \otimes \cdots \tau_d$.
+\item Let $\phi$ be the linear quasicharacter of $\underline{G}(\OK)$, as above.
 \end{enumerate}
+Using the decomposition $\underline{G}^j(\OK) = \underline{G}^{j-1}(\OK) \times \underline{J}^j(\OK)$, combine $\ddot{\beta}_j$, $\ddot{\kappa}_j$  and $\phi_j$ to form the representation $(\phi_{j-1}\otimes \ddot{\kappa}_j)\times \ddot{\beta}_j$ of $\underline{G}^{j}(\OK)$, for $j=1,\ldots, d-1$.
+	Since $\prod_{i=j+1}^{d} \underline{J}^i(\OK)$ is normal in $\underline{G}(\OK)$, this determines a representation $\delta_j$ of $\underline{G}(\OK)$, for $j=1,\ldots, d-1$.
+Then 
+\[
+\,^\circ \rho = \ddot{\sigma} \otimes \delta_1 \cdots \otimes \delta_{d-1} \otimes \phi.
+\]
 
@@
 \]
-Interpret 
-\begin{enumerate}
-\item
-	$\epsilon_j$ as a representation of $(\underline{M}^{j-1})_s\red(\Fq)$, for each $j=1,\ldots, d$;
-\item
-	$\phi_{j-1}$ as a linear quasicharacter of $\underline{M}^{j-1}(\OK)$, for $j=1,\ldots, d$;
-\end{enumerate}
-so that
-\begin{enumerate}
-\item 
-	$\dot{\epsilon}_j$ is the representation of $\underline{M}^{j-1}(\OK)$ obtained by pulling back $\epsilon_j$ along 
-\[\underline{M}^{j-1}(\OK) \to \underline{M}^{j-1}_s(\Fq) \to (\underline{M}^{j-1})_s\red(\Fq),\]
-for $j=1,\ldots, d-1$.
-\item
-	$\dot{\eta}_j$ is a representation of $\underline{J}^{j}(\OK)$ obtained by pulling back  . . . .  $j=1,\ldots, d-1$;
-\item
-	$\tau_j$ is the representation of $\underline{G}(\OK)$ obtained by pulling back  $\phi_{j-1}$ and $\dot{\epsilon}_j$ and $\dot{\eta}_j$ from $\underline{M}^{j}(\OK)$ along $\underline{G}(\OK)\to \underline{M}^j(\OK)$, for $j=1,\ldots, d-1$.
-\end{enumerate}
-
 \[
@@
 \underline{G}_s \arrow{d}
-& \underline{M}^{j-1} \arrow{d}
+& M_n^{j-1} \arrow{d}
 & (\underline{J}^j)_s  \arrow{d} \\
@@
 \begin{enumerate}
-\item let $\cs{B}^j$ be the sheaf on $M^j_n$ ...
-\item let $\cs{C}^j$ be the sheaf on $M^j_n$ ...
-\item let $\cs{E}^j$ be the sheaf on $M^j_n$ ...
+\item let $\cs{B}^j$ be the sheaf on $J^j_n$ ...
+\item let $\cs{C}^j$ be the sheaf on $M^{j-1}_n$ ...
+\item let $\cs{L}^j$ be the sheaf on $M^{j-1}_n$ ...
 \end{enumerate}
+Combine: $\cs{B}^j$, $\cs{C}^j$ and $\cs{E}^j$ into $\cs{D}^j$ on $G_n$ . . . .
 \item Let $\cs{L}$ be the sheaf on $G_n$ as above...
 \end{enumerate}
-Combine: $B$, $C$ and $E$ into $D$
+
 \[
@@
 \]
+
+Interpret 
+\begin{enumerate}
+\item
+	$\epsilon_j$ as a representation of $(\underline{M}^{j-1})_s\red(\Fq)$, for each $j=1,\ldots, d$;
+\item
+	$\phi_{j-1}$ as a linear quasicharacter of $\underline{M}^{j-1}(\OK)$, for $j=1,\ldots, d$;
+\end{enumerate}
+so that
+\begin{enumerate}
+\item 
+	$\dot{\epsilon}_j$ is the representation of $\underline{M}^{j-1}(\OK)$ obtained by pulling back $\epsilon_j$ along 
+\[\underline{M}^{j-1}(\OK) \to \underline{M}^{j-1}_s(\Fq) \to (\underline{M}^{j-1})_s\red(\Fq),\]
+for $j=1,\ldots, d-1$.
+\item
+	$\dot{\eta}_j$ is a representation of $\underline{J}^{j}(\OK)$ obtained by pulling back  . . . .  $j=1,\ldots, d-1$;
+\item
+	$\tau_j$ is the representation of $\underline{G}(\OK)$ obtained by pulling back  $\phi_{j-1}$ and $\dot{\epsilon}_j$ and $\dot{\eta}_j$ from $\underline{M}^{j}(\OK)$ along $\underline{G}(\OK)\to \underline{M}^j(\OK)$, for $j=1,\ldots, d-1$.
+\end{enumerate}
 

### 2015-11-18 followup.tex
New abstract

@@
 \begin{abstract}
-We introduce and establish the basic properties of  the category of \emph{commutative character sheaves} on smooth group schemes $G$ over finite fields $\Fq$, building on earlier work by the same authors.
-We use this category to geometrize types for supercuspidal representations of $p$-adic groups. 
+We generalize the function-sheaf dictionary to arbitrary smooth group schemes over finite fields.  In previous work,
+we considered the case of smooth commutative group schemes and found that the standard definition of
+character sheaves produced a dictionary with a nontrivial kernel.  In this paper, we give a modification of
+the category of character sheaves that remedies this defect, and is also extensible to non-commutative groups.
+We use these \emph{commutative character sheaves} to geometrize types for supercuspidal representations of
+$p$-adic groups. 
 \end{abstract}

### 2015-11-23 followup.tex
Catching up...
Work on the section reviewing types. Models is under construction.

@@
 
+\newcommand{\red}{^{\operatorname{red}}}
+\newcommand{\Sp}{{\operatorname{Sp}}}
+
+As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
+The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from the data. 
+Let us refer to the types arising in this manner as {\it Yu types}.
+In this section we show that every Yu type is geometrizable, in a sense which will be made clear below.
+
+A Yu type is a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, with certain properties. 
+In Section~\ref{ssec:review} we recall properties of $(\,^\circ K,\,^\circ \rho)$ which we allow us, in Section~\ref{ssec:geometrization}, to find a pair $(G, \mathcal{F})$ where $G$ is a smooth group scheme over $\Fq$ and $\mathcal{F}$ is a virtual constructible sheaf $\ell$-adic sheaf on $G$ from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius.
+
+\subsection{Review of Yu's types}\label{ssec:review}
+
+Every Yu type $(\,^\circ K,\,^\circ \rho)$ may be constructed directly from the following information, derived from a Yu datum:
+\begin{enumerate}
+\item compact open subgroups $J^i\subset \,^\circ K$, for $i=0, \ldots d$, such that \[\,^\circ K = J^0\cdots J^d;\]
+\item a continuous representation $\sigma_0$ of $J^0$;
+\item a quasicharacter $\varphi_i : J^i \to \CC^\times$, for $i=0, \ldots d$.
+\end{enumerate}
+These representations $(\sigma_0, \varphi_0, \ldots , \varphi_d)$ enjoy certain properties, which allow Yu to construct, for $i=0, \ldots, d-1$, further:
+\begin{enumerate}
+\item a quotient $J^{i+1} \to V_{i+1}$ to a finite abelian group, and the structure of a $\Fq$-vector space on $V_{i+1}$, compatible with the abelian group structure above;
+\item a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$;
+\item an additive character $\psi_{i+1} : C_{i+1} \to \EEx$;
+\item a group homomorphism $\,^\circ f_i : J^0 \cdots J^i \to \Sp(V_{i+1})$;
+\item a quotient $J^{i+1} \to H^{i+1}$, where $H^{i+1}$ is a Heisenberg $p$-group, together with an isomorphism $j_{i+1} : H^{i+1} \to V_{i+1}^\sharp$, where $V_{i+1}^\sharp$ is the Heisenberg group determined by $(V_{i+1}, \langle\ ,\ \rangle_{i+1}, C_{i+1}, \psi_{i+1})$.
+\end{enumerate}
+The pair $(f_i, j_{i+1})$ is a symplectic action of $J^0\cdots J^i$ on $H^{i+1}$, so it defines a group homomorphism 
+\begin{equation}\label{eq:symaction}
+\begin{tikzcd}
+h_{i+1} : (J^0\cdots J^i)\ltimes J^{i+1} \arrow{r} & (J^0\cdots J^i)\ltimes H^{i+1} \arrow{r} & \Sp(V_{i+1})\ltimes V_{i+1}^\sharp.
+\end{tikzcd}
+\end{equation}
+%
+
+From this information, Yu constructs a representation $\,^\circ \rho_i$ of $J^0\cdots J^i$, for each $i=0, \ldots, d$, such that $\,^\circ \rho_d = \,^\circ \rho$.
+We will need some detail about this construction, so we will review it here.
+%Let $\varpi_1$ be the Heisenberg representation of the Heisenberg group $V_1^\sharp$, with central character $\psi_1$.
+%Let $\varrho_1$ be the Weil representation of $\Sp(V_1)$ with the same representation space as $\omega_1$.
+Let $\omega_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, with the same representation space as the Heisenberg representation of the Heisenberg group $V_{i+1}^\sharp$.
+\[
+\begin{tikzcd}
+\  & J^{i+1} \arrow{d} & \\
+Sp(V_{i+1}) \ltimes V_{i+1}^\sharp & \arrow{l}[swap]{h_1} (J^0 \cdots J^i) \ltimes J^{i+1} \arrow{r} \arrow{d} & J^0 \cdots J^i J^{i+1}\\
+& (J^0 \cdots J^i) & 
+\end{tikzcd}
+\]
+Then $h_1^*(\omega_1)$ is a representation of $J^0\ltimes J^1$, determined by the quasicharacter $\varphi_1$ of $J^1$. 
+Write $\inf(\sigma_0\otimes \varphi_0)$ for the representation of $J^0 \ltimes J^1$ obtained by pulling back $\sigma_0\otimes \varphi_0$ along $J^0 \ltimes J^1 \to J^0$. 
+By \cite{yu:construction}*{}, the representation 
+$h_1^*(\omega_1) \otimes \inf(\sigma_0\otimes \varphi_0)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 \ltimes 1) \cap (1 \ltimes J^1)$, so $h_1^*(\omega_1) \otimes \inf(\sigma_0\otimes \varphi_0)$ descends to a representation $\,^\circ \rho_1$ of $J^0 J^1$.
+%
+As above, the representation 
+$h_{2}^*(\omega_{2}) \otimes \inf(\,^\circ \rho_1)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 J^1 \ltimes 1) \cap (1 \ltimes J^2)$, so $h_2^*(\omega_2) \otimes \inf(\,^\circ \rho_1)$ descends to a representation $\,^\circ \rho_2$ of $J^0 J^1 J^2$.
+Continuing in this way, one constructs the representation $\,^\circ \rho_d$ of $J^0\cdots J^d$.
+
+The character of $\,^\circ \rho_d$ on $J^0\cdots J^d$ satisfies
+\[
+\trace(\,^\circ \rho_d)(k_0 \cdots k_d) = \sigma_0(k_0) \left( \varphi_0(k_0) \cdots \varphi_d(k_d) \right) ,
+\]
+with ...
+
+\subsection{Smooth models}\label{ssec:models}
+
+The first step in the geometrization of the type $(\,^\circ K,\,^\circ \rho)$ is to replace $\,^\circ K$ with a group scheme $G$ over $\Fq$ so that $G(\Fq) = \,^\circ K$, canonically. 
+By \cite{yu:models}*{Prop 10.2} there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that \[\underline{G}(\OK)= \,^\circ K\] 
+For every positive integer $n$, let $G_n$ be the Greenberg transform of $\underline{G} \times_{\Spec{\OK}} \Spec{\OK/\mathfrak{m}_K^n}$, where $\mathfrak{m}_K$ is the maximal ideal in $\OK$.
+Then $G_n$ is a smooth group scheme over $\Fq$ and $G_n(\Fq) = \underline{G}(\OK/\mathfrak{m}_K^n)$, canonically.
+Let $G$ be the Greenberg transform of $\underline{G}$.
+Then $G$ is a group scheme over $\Fq$ and $G(\Fq) = \underline{G}(\OK) = \,^\circ K$, canonically.
+
+In order to complete the geometrization of the type $(\,^\circ K,\,^\circ \rho)$, we will need more smooth models.
+Fortunately, as above, Yu has already done the heavy work.
+%
+As explained in \cite{yu:models}*{\S 10.4}, the
+the group scheme $\underline{G}$ comes with the following auxillary data:
+\begin{enumerate}
+\item[(Ji)]
+	affine smooth group schemes $\underline{J}^i$, for $i=0, 1, \ldots, d$, together with morphisms $\underline{J}^i \to \underline{G}$ such that \[\underline{J}^i(\OK) = J^i,\]
+\item[(Gj)] affine smooth group schemes $\underline{G}^{j}$, for $j=0, \ldots, d$, together with morphisms $\underline{G}^{j}\to \underline{G}$ such that 
+\[
+\underline{G}^{j}(\OK) = J^0\cdots J^i.
+\] 
+\end{enumerate}
+
+Moreover, the quotient
+
+Regarding this construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:models} concludes with the following provocative observation.
+\begin{quotation}
+{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
+ the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
+These results suggest that algebraic geometry and group schemes should play an
+important role in the representation theory of $p$-adic groups.} \cite{yu:models}
+\end{quotation}
+%
+The objective of this section is to push this observation further by geometrizing the representation $\,^\circ \rho$ of $\underline{G}$.
+
+\subsection{Geometrization}\label{ssec:geometrization}
+
+\begin{proposition}\label{prop:types}
+Let $(\,^\circ K,\,^\circ \rho)$ be a Yu type.
+With notation as above, suppose $\pi_0(\underline{G}_s\red)$ is cyclic and that $\pi_0((\underline{G}^{j-1})_s\red)$ is cyclic for $j=1,\ldots, d-1$.
+Then there is a virtual admissible $\ell$-adic sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
+\end{proposition}
+
+\bibliography{bibliography/Biblio}
+
+\end{document}
+
+Suppose there is some $f : H\times G\to G\times G$ such that the following diagram commutes.
+\[
+\begin{tikzcd}
+\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
+G & & G \\
+& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
+\end{tikzcd}
+\]
+Then $f(h,g) = (a(h,g) g^{-1}, g)$.
+Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq a(h,g) g^{-1}$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
+
+Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
+\[
+\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}
+\]
+by $\beta \otimes \id_{p^*\cs{L}} = \nu \circ f^*\mu^{-1}$, or more precisely, by the following diagram of isomorphisms,
+\[
+\begin{tikzcd}
+a^*\cs{L} \arrow{d}{m\circ f = a} \arrow{rrr}{\nu}
+&&& p^*\cs{L}\\
+f^* m^*\cs{L} \arrow{r}{f^*\mu} & 
+f^*(\cs{L}\boxtimes \cs{L}) \arrow{d} & 
+f_1^*\cs{L} \otimes p^*\cs{L} \arrow{r}{\beta\otimes \id_{p^*\cs{L}}} & 
+(\EE)_{H\times G} \otimes p^*\cs{L} \arrow{u} \\
+& f^*(p_1^*\cs{L}\otimes p_2^*\cs{L}) \arrow{r} & f^*p_1^*\cs{L}\otimes f^* p_2^*\cs{L} \arrow{u}{f_1 = p_1\circ f}[swap]{p = p_2\circ f} &
+\end{tikzcd}
+\]
+In this way we see we may replace $(\cs{L},\mu,\nu)$ with an alternate triple, $(\cs{L},\mu,\beta_1)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
+The isomorphism $\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}$ is constrained by two properties, corresponding to the diagrams in Sections [] and [].
+
+\subsection{Quotient and restriction}
+
+We now combine the material of the last two sections, by specializing to the following case: $H$ is a closed subgroup of $G$ and $q : G \to G/H$ is the fppf quotient, which exists in schemes by  . . .
+
+\iffalse
+
+\subsection{Change of action}
+
+Now, let $a' : H'\times G \to G$ be another group action on $G$ and suppose $f: H \times G \to H'\times G$ makes the following diagram commute.
+\[
+\begin{tikzcd}
+&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
+G & & G \\
+& \arrow{ul}{a'} H' \times G \arrow{ur}[swap]{p} & 
+\end{tikzcd}
+\]
+Then pull-back along $f: H\times G \to H'\times G$ defines a monoidal functor 
+\[
+\CS_{H'}(G) \to \CS_{H}(G).
+\]
+
+Then $f : H\times G \to H'\times G$ is given by $f(h,g) = (k(h,g),g)$ for some $k : H\times G\to H'$. 
+Define $d : H\to H'$ by $d(h) = k(h,1)$.
+
+\begin{lemma}\label{lem:action}
+The canonical functor
+\[
+\CS_{H}(G) \to \CS_{H'}(G)
+\]
+is an equivalence if ...
+\end{lemma}
+\begin{proof}
+\end{proof}
+
+\subsection{Conjugation}
+
+We close this section with an alternate characterization of $\CS'(G)$, the category of linear character sheaves $\cs{L}$ on $G$ for which $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
+Recall that $\CS'(G)$ is a full subcategory of $\CS(G)$ and that $\CCS(G)$ is a full subcategory of $\CS'(G)$.
+
+Consider the following case of Section~\ref{ssec:action}.
+
+\fi
+
 \iffalse
@@
 \fi
-
-%\subsection{Geometric types for supercuspidal representations}
-
-\newcommand{\red}{^{\operatorname{red}}}
-
-As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
-The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from the data. 
-Let us refer to the types arising in this manner as {\it Yu types}.
-In this section we show that every Yu type is geometrizable, in a sense which will be made clear below.
-
-\subsection{Review of Yu's types}
-
-A Yu type is a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, with certain properties. 
-One of the main results of \cite{yu:models} is that there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that $\,^\circ K = \underline{G}(\OK)$ \cite{yu:models}*{Prop 10.2}.
-As explained in \cite{yu:models}*{\S 10.4}, the
-the group scheme $\underline{G}$ comes with the following auxillary data:
-\begin{enumerate}
-\item[(Ji)]
-	affine smooth group schemes $\underline{J}^i$, for $i=0, 1, \ldots, d$, together with morphisms $\underline{J}^i \to \underline{G}$ such that \[\prod_{i=0}^d \underline{J}^i(\OK) = \underline{G}(\OK),\] where we identify $\underline{J}^i(\OK)$ with its image under $\underline{J}^i \to \underline{G}$, and such that $\prod_{i=j+1}^{d} \underline{J}^i(\OK)$ is normal in $\underline{G}(\OK)$, for $j=1, \ldots, d$;
-\item[(Gj)] affine smooth group schemes $\underline{G}^{j}$, for $j=1, \ldots, d$, together with morphisms $\underline{G}^{j}\to \underline{G}$ such that 
-\[
-\underline{G}^{j}(\OK) = \prod_{i=0}^{j} \underline{J}^i(\OK),
-\] 
-where we identify $\underline{J}^i(\OK)$ with its image under $\underline{J}^i \to \underline{G}$ and $\underline{G}^{j}(\OK)$ with its image under $\underline{G}^j \to \underline{G}$.
-\end{enumerate}
-
-The representation $\,^\circ \rho$ of $\underline{G}(\OK)$ is build from the following data:
-\begin{enumerate}
-\item
-	a representation $\sigma$ of $\underline{G}_s\red(\Fq)$;
-\item
-if $d \geq 2$, for $j=1,\ldots, d-1$, 
-\begin{enumerate}
-\item
-a representation $\beta_j$ of $H^j(\Fq)$, where $H^j$ is Heisenberg group arising as a quotient $(\underline{J}^{j})_s \to H^j$,
-\item
-a representation $\kappa_j$ of $(\underline{G}^{j-1})_s\red(\Fq)$
-\item
-a linear quasicharacter $\phi_{j-1}$ of $\underline{G}^{j-1}(\OK)$;
-\end{enumerate}
-\item
-	a linear quasicharacter $\phi$ of $\underline{G}(\OK)$.
-\end{enumerate}
-From this data, the representation $\,^\circ \rho$ is built as follows, as explained in \cite{yu:models}*{\S 10.5}.
-\begin{enumerate}
-\item 
-	Let $\dot{\sigma}$ be the representation of $\underline{G}_s(\Fq)$ obtained by pulling back $\sigma$ along $\underline{G}_s(\Fq) \to \underline{G}_s\red(\Fq)$. 	
-	Let $\ddot{\sigma}$ be the representation of $\underline{G}(\OK)$ obtained by pullback along $\underline{G}(\OK) \to \underline{G}_s(\Fq)$.
-\item For $j=1,\ldots, d-1$, 
-\begin{enumerate}
-\item
-	let $\dot{\beta}_j$ be the representation of $\underline{J}^{j}_s(\Fq)$ obtained by pulling back $\beta_j$ along $\underline{J}^{j}_s(\Fq) \to H^j(\Fq)$ and let $\ddot{\beta}_j$ be . . . 
-;
-\item 
-	let $\dot{\kappa}_j$ be the representation of $\underline{G}^{j-1}_s(\Fq)$ obtained by pulling back $\kappa_j$ along $\underline{G}^{j-1}_s(\Fq) \to (\underline{G}^{j-1})_s\red(\Fq)$ and let $\ddot{\kappa}_j$ .
-.
-;
-\item
-	let $\phi_{j-1}$ be the linear quasicharacter of $\underline{G}^{j-1}(\OK)$ as above. 
-\end{enumerate}
-\item Let $\phi$ be the linear quasicharacter of $\underline{G}(\OK)$, as above.
-\end{enumerate}
-Using the decomposition $\underline{G}^j(\OK) = \underline{G}^{j-1}(\OK) \times \underline{J}^j(\OK)$, combine $\ddot{\beta}_j$, $\ddot{\kappa}_j$  and $\phi_j$ to form the representation $(\phi_{j-1}\otimes \ddot{\kappa}_j)\times \ddot{\beta}_j$ of $\underline{G}^{j}(\OK)$, for $j=1,\ldots, d-1$.
-	Since $\prod_{i=j+1}^{d} \underline{J}^i(\OK)$ is normal in $\underline{G}(\OK)$, this determines a representation $\delta_j$ of $\underline{G}(\OK)$, for $j=1,\ldots, d-1$.
-Then 
-\[
-\,^\circ \rho = \ddot{\sigma} \otimes \delta_1 \cdots \otimes \delta_{d-1} \otimes \phi.
-\]
-
-Regarding this construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:models} concludes with the following provocative observation.
-\begin{quotation}
-{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
- the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
-These results suggest that algebraic geometry and group schemes should play an
-important role in the representation theory of $p$-adic groups.} \cite{yu:models}
-\end{quotation}
-%
-The objective of this section is to push this observation further by geometrizing the representation $\,^\circ \rho$ of $\underline{G}$.
-
-\subsection{Geometrization of types}
-
-Let $(\underline{G}(\OK),\,^\circ \rho)$ be a Yu type.
-Set $G = \Gr(\underline{G})$, the Greenberg transform of $\underline{G}$.
-Recall that $G$ is a group scheme over $\Fq$ and comes equipped with
-
-\begin{proposition}\label{prop:types}
-Let $(\underline{G}(\OK),\rho)$ be a Yu type.
-With notation as above, suppose $\pi_0(\underline{G}_s\red)$ is cyclic and that $\pi_0((\underline{G}^{j-1})_s\red)$ is cyclic for $j=1,\ldots, d-1$.
-Then there is a virtual admissible $\ell$-adic sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
-\end{proposition}
 
@@
 \fi
-
-\bibliography{bibliography/Biblio}
-
-\end{document}
-
-Suppose there is some $f : H\times G\to G\times G$ such that the following diagram commutes.
-\[
-\begin{tikzcd}
-\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
-G & & G \\
-& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
-\end{tikzcd}
-\]
-Then $f(h,g) = (a(h,g) g^{-1}, g)$.
-Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq a(h,g) g^{-1}$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
-
-Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
-\[
-\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}
-\]
-by $\beta \otimes \id_{p^*\cs{L}} = \nu \circ f^*\mu^{-1}$, or more precisely, by the following diagram of isomorphisms,
-\[
-\begin{tikzcd}
-a^*\cs{L} \arrow{d}{m\circ f = a} \arrow{rrr}{\nu}
-&&& p^*\cs{L}\\
-f^* m^*\cs{L} \arrow{r}{f^*\mu} & 
-f^*(\cs{L}\boxtimes \cs{L}) \arrow{d} & 
-f_1^*\cs{L} \otimes p^*\cs{L} \arrow{r}{\beta\otimes \id_{p^*\cs{L}}} & 
-(\EE)_{H\times G} \otimes p^*\cs{L} \arrow{u} \\
-& f^*(p_1^*\cs{L}\otimes p_2^*\cs{L}) \arrow{r} & f^*p_1^*\cs{L}\otimes f^* p_2^*\cs{L} \arrow{u}{f_1 = p_1\circ f}[swap]{p = p_2\circ f} &
-\end{tikzcd}
-\]
-In this way we see we may replace $(\cs{L},\mu,\nu)$ with an alternate triple, $(\cs{L},\mu,\beta_1)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
-The isomorphism $\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}$ is constrained by two properties, corresponding to the diagrams in Sections [] and [].
-
-\subsection{Quotient and restriction}
-
-We now combine the material of the last two sections, by specializing to the following case: $H$ is a closed subgroup of $G$ and $q : G \to G/H$ is the fppf quotient, which exists in schemes by  . . .
-
-\iffalse
-
-\subsection{Change of action}
-
-Now, let $a' : H'\times G \to G$ be another group action on $G$ and suppose $f: H \times G \to H'\times G$ makes the following diagram commute.
-\[
-\begin{tikzcd}
-&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
-G & & G \\
-& \arrow{ul}{a'} H' \times G \arrow{ur}[swap]{p} & 
-\end{tikzcd}
-\]
-Then pull-back along $f: H\times G \to H'\times G$ defines a monoidal functor 
-\[
-\CS_{H'}(G) \to \CS_{H}(G).
-\]
-
-Then $f : H\times G \to H'\times G$ is given by $f(h,g) = (k(h,g),g)$ for some $k : H\times G\to H'$. 
-Define $d : H\to H'$ by $d(h) = k(h,1)$.
-
-\begin{lemma}\label{lem:action}
-The canonical functor
-\[
-\CS_{H}(G) \to \CS_{H'}(G)
-\]
-is an equivalence if ...
-\end{lemma}
-\begin{proof}
-\end{proof}
-
-\subsection{Conjugation}
-
-We close this section with an alternate characterization of $\CS'(G)$, the category of linear character sheaves $\cs{L}$ on $G$ for which $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
-Recall that $\CS'(G)$ is a full subcategory of $\CS(G)$ and that $\CCS(G)$ is a full subcategory of $\CS'(G)$.
-
-Consider the following case of Section~\ref{ssec:action}.
-
-\fi

### 2015-11-24 followup.tex
Update bibliography, fix warnings in compilation, add summary of sections

--- 2015-11-18 followup.tex
@@
 
-\subjclass[2010]{14F05 (primary), 14L15 (secondary), 22E50 (tertiary)}
+\subjclass[2010]{14F05 (primary), 14L15, 22E50}
 \keywords{character sheaves}
@@
 \begin{abstract}
-We generalize the function-sheaf dictionary to arbitrary smooth group schemes over finite fields.  In previous work,
-we considered the case of smooth commutative group schemes and found that the standard definition of
-character sheaves produced a dictionary with a nontrivial kernel.  In this paper, we give a modification of
-the category of character sheaves that remedies this defect, and is also extensible to non-commutative groups.
-We use these \emph{commutative character sheaves} to geometrize types for supercuspidal representations of
-$p$-adic groups. 
+We describe a function-sheaf dictionary for one-dimensional characters of arbitrary smooth group schemes
+over finite fields.  In previous work, we considered the case of smooth commutative group schemes and found
+that the standard definition of character sheaves produced a dictionary with a nontrivial kernel.  In this paper,
+we give a modification of the category of character sheaves that remedies this defect, and is also extensible to
+non-commutative groups.  We use these \emph{commutative character sheaves} to geometrize types for
+supercuspidal representations of $p$-adic groups. 
 \end{abstract}
@@
 
-In \cite{cunningham-roe:13a}, we generalized the function-sheaf dictionary from connected commutative algebraic groups
-over a finite field $k$ to smooth commutative group schemes $G$ over $k$.  We described a category $\CS(G)$ of
-\emph{character sheaves} on $G$ and a surjective homomorphism $\TrFrob{G} : \CSiso{G} \to \Hom(G(k), \EEx)$.
+In previous work \cite{cunningham-roe:13a}, we generalized the function-sheaf dictionary from connected, commutative, algebraic groups
+over a finite field $k$ to smooth commutative group schemes $G$ over $k$.  Writing $G(k)^*$ for $\Hom(G(k), \EEx)$, we described a category $\CS(G)$ of
+\emph{character sheaves} on $G$ and a surjective homomorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$.
 In contrast to the connected case, $\TrFrob{G}$ may have nontrivial kernel; we gave an explicit description of
@@
 The first aim of this paper is to repair this defect in the function-sheaf dictionary by describing a full subcategory
-$\CCS(G)$ of $\CS(G)$ so that $\TrFrob{G}$ restricts to an isomorphism $\CCSiso{G} \to \Hom(G(k), \EEx)$.
+$\CCS(G)$ of $\CS(G)$ so that $\TrFrob{G}$ restricts to an isomorphism $\CCSiso{G} \to G(k)^*$.
 We refer to the resulting objects as \emph{commutative character sheaves}, since the passage from $\CS(G)$
@@
 This category clarifies several questions about character sheaves on $G$: invisible character sheaves
-\cite{cunningham-roe:13a}*{Def. 2.8} are precisely those that are not commutative, and the inverse map
-$\Hom(G(k), \EEx) \to \CCSiso{G}$ provides a canonical splitting of $\TrFrob{G}$ \cite{cunningham-roe:13a}*{Rem. 3.7}.
+\cite{cunningham-roe:13a}*{Def. 2.8} are precisely those that are not commutative, and 
+$\TrFrob{G}^{-1} : G(k)^* \to \CCSiso{G}$ provides a canonical splitting of
+$\TrFrob{G} : \CSiso{G} \to G(k)^*$ \cite{cunningham-roe:13a}*{Rem. 3.7}.
 
 Next, we broaden our scope further to encompass smooth group schemes $G$ that are not necessarily commutative.
-In this paper, we do not consider Lusztig's geometrization of arbitrary characters of the non-abelian group $G(k)$, where $G$ is reductive,
+In this paper, we do not consider Lusztig's geometrization of arbitrary characters of connected, reductive groups $G(k)$
 using character sheaves \cite{lusztig:85a}*{Def.~2.10}, but focus on the case of $1$-dimensional characters
-$\Hom(G(k), \EEx)$ assuming only that $G$ is smooth. The category $\CS(G)$ has a straightforward generalization to this case, but again
+$G(k)^*$ assuming only that $G$ is smooth. The category $\CS(G)$ has a straightforward generalization to this case, but again
 there are more linear character sheaves than there are characters, as pointed out by Kamgarpour \cite{kamgarpour:09a}*{(1.1)}.
-We define a category $\CCS(G)$ and a forgetful functor to $\CS(G)$ so that $\TrFrob{G} : \CCSiso{G} \to \Hom(G\ab(k), \EEx)$
-is an isomorphism.  In fact, pullback along the quotient $q : G \to G\ab$ defines an equivalence of categories
-$\CCS(G\ab) \to \CCS(G)$.  Note that the functor $\CCS(G) \to \CS(G)$ is not essentially surjective, missing
-the kinds of linear character sheaves highlighted by Kamgarpour.  
-Since $\Hom(G\ab(k), \EEx)$ surjects
-onto $\Hom(G(k), \EEx)$, with a kernel described by Galois cohomology, this paper shows that, for every linear character $\chi : G(k) \to \EEx$ there is a commutative character sheaf $\cs{L}$ on $G$ such that $\TrFrob{G}(\cs{L})\circ q = \chi$.
+We define a category $\CCS(G)$ and a forgetful functor to $\CS(G)$ so that $\TrFrob{G} : \CCSiso{G} \to G\ab(k)^*$
+is an isomorphism.  Since $G\ab(k)^*$ surjects onto $G(k)^*$, for each character $\chi \in G(k)^*$ there is a commutative
+character sheaf $\cs{L}$ on $G$ with $\TrFrob{G}(\cs{L}) = \chi$. Moreover, pullback along the quotient $q : G \to G\ab$
+defines an equivalence of categories $\CCS(G\ab) \to \CCS(G)$.  Note that the functor $\CCS(G) \to \CS(G)$ is not
+essentially surjective, missing the kinds of linear character sheaves highlighted by Kamgarpour.
 
 Finally, we use the category $\CCS(G)$ to give a geometric description of generic types for supercuspidal representations
-of connected reductive linear algebraic groups over local fields.  In this way, we provide all of the ingredients
+of connected reductive groups over local fields.  In this way, we provide all of the ingredients
 needed to parametrize supercuspidal representations of arbitrary depth in the same category:
-perverse sheaves on group schemes over finite fields.
-
-\todo{Add summary of sections}
+perverse sheaves on group schemes over finite fields. \todo{Update based on any changes in Section 4}
+
+In Section \ref{sec:defs}, we recall the category $\CS(G)$ from \cite{cunningham-roe:13a} and note that it still makes
+sense when $G$ is not commutative.  We focus on the case of commutative $G$ in Section \ref{sec:comcom},
+giving the definition of a commutative character sheaf and proving our first main theorem, that
+$\TrFrob{G} : \CSiso{G} \to G(k)^*$ induces an isomorphism on $\CCSiso{G}$.
+
+Passing to the case that $G$ is
+non-commutative, we give the definition of and main results about commutative character sheaves in
+Section \ref{sec:noncom}.  We note that we should only consider character sheaves
+that arise via pullback from $G\ab$ in order to eliminate those that have nontrivial restriction
+to the derived subgroup.  This observation underlies the definition of commutative character sheaves for
+non-commutative $G$.  We state our second main theorem, that pullback along the abelianization map
+defines an equivalence of categories $\CCS(G) \to \CCS(G\ab)$.
+In Section \ref{ssec:obmor}, we use Galois cohomology to describe the relationship between $G(k)^*$
+and $G\ab(k)^*$.  We also compute the automorphism groups in $\CCS(G)$.
+Then in Section \ref{ssec:proofs}, we give proofs of the results in Section \ref{sec:noncom}, which
+require a development of equivariant linear character sheaves.
+
+\todo{Add summary of Section 4 once it has stabilized}
 
@@
 
-\subsection{Objects and maps in commutative character sheaves}
+\subsection{Objects and maps in commutative character sheaves} \label{ssec:obmor}
 
@@
 By Theorem~\ref{thm:Gab}, $\Aut_{\CCS(G)}(\cs{L},\mu,\beta) = \Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab)$. 
-By \cite{cunningham-roe:13a}*{Thm 3.9},  $\Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab) = ((\pi_0(G\ab))^*)^{\Frob{}}$.
+By \cite{cunningham-roe:13a}*{Thm 3.9},  $\Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab) = ((\pi_0(G\ab))^*)^{\Frob{}}$. \todo{Shouldn't it be coinvariants?}
 \end{proof}
@@
 
-An $H$-equivariant linear character sheaf on $G$ is a triple $(\cs{L},\mu, \nu)$ where $(\cs{L},\mu)$ is a linear character sheaf and $(\cs{L},\nu)$ is an $H$-equivariant local system.
+We define an $H$-equivariant linear character sheaf on $G$ to be a triple $(\cs{L},\mu, \nu)$, where $(\cs{L},\mu)$ is a linear character sheaf and $(\cs{L},\nu)$ is an $H$-equivariant local system.
 We require that $\mu$ be compatible with $\nu$ in the following sense.
@@
 %\begin{proof}[Proof of Proposition~\ref{prop:Gder_triv}] 
-The abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}.
+The abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ \cite{demazure:SGA3-VIA}*{Thm. 3.2}.
 Set $H=G\der$.
@@
 The forget
-Since the quotient $q : G \to G\ab$ is a trivial $H$-torsor in the fppf topology \cite{SGA3}*{Expos\'e {VI}$_A$, Thm. 3.2}, 
+Since the quotient $q : G \to G\ab$ is a trivial $H$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, 
 it now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{H}(G)$ is an equivalence.
@@
 
-\section{Application to type theory for $p$-adic groups}
+\section{Application to type theory for \texorpdfstring{$p$}{p}-adic groups}
 
@@
 A Yu type is a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, with certain properties. 
-One of the main results of \cite{yu:models} is that there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that $\,^\circ K = \underline{G}(\OK)$ \cite{yu:models}*{Prop 10.2}.
-As explained in \cite{yu:models}*{\S 10.4}, the
+One of the main results of \cite{yu:03a} is that there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that $\,^\circ K = \underline{G}(\OK)$ \cite{yu:03a}*{Prop 10.2}.
+As explained in \cite{yu:03a}*{\S 10.4}, the
 the group scheme $\underline{G}$ comes with the following auxillary data:
@@
 \end{enumerate}
-From this data, the representation $\,^\circ \rho$ is built as follows, as explained in \cite{yu:models}*{\S 10.5}.
+From this data, the representation $\,^\circ \rho$ is built as follows, as explained in \cite{yu:03a}*{\S 10.5}.
 \begin{enumerate}
@@
 
-Regarding this construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:models} concludes with the following provocative observation.
+Regarding this construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:03a} concludes with the following provocative observation.
 \begin{quotation}
@@
 These results suggest that algebraic geometry and group schemes should play an
-important role in the representation theory of $p$-adic groups.} \cite{yu:models}
+important role in the representation theory of $p$-adic groups.} \cite{yu:03a}
 \end{quotation}

### 2015-11-24 followup.tex

--- 2015-11-23 followup.tex
@@
 Write $\inf(\sigma_0\otimes \varphi_0)$ for the representation of $J^0 \ltimes J^1$ obtained by pulling back $\sigma_0\otimes \varphi_0$ along $J^0 \ltimes J^1 \to J^0$. 
-By \cite{yu:construction}*{}, the representation 
+By \cite{yu:01a}*{}, the representation 
 $h_1^*(\omega_1) \otimes \inf(\sigma_0\otimes \varphi_0)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 \ltimes 1) \cap (1 \ltimes J^1)$, so $h_1^*(\omega_1) \otimes \inf(\sigma_0\otimes \varphi_0)$ descends to a representation $\,^\circ \rho_1$ of $J^0 J^1$.
@@
 The first step in the geometrization of the type $(\,^\circ K,\,^\circ \rho)$ is to replace $\,^\circ K$ with a group scheme $G$ over $\Fq$ so that $G(\Fq) = \,^\circ K$, canonically. 
-By \cite{yu:models}*{Prop 10.2} there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that \[\underline{G}(\OK)= \,^\circ K\] 
+By \cite{yu:03a}*{Prop 10.2} there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that \[\underline{G}(\OK)= \,^\circ K\] 
 For every positive integer $n$, let $G_n$ be the Greenberg transform of $\underline{G} \times_{\Spec{\OK}} \Spec{\OK/\mathfrak{m}_K^n}$, where $\mathfrak{m}_K$ is the maximal ideal in $\OK$.
@@
 %
-As explained in \cite{yu:models}*{\S 10.4}, the
+As explained in \cite{yu:03a}*{\S 10.4}, the
 the group scheme $\underline{G}$ comes with the following auxillary data:
@@
 
-%The generic datum $(\vec{\G}, \pi_0, \vec{\phi})$ determines a type (in the sense of \cite{bushnell-kutzko:98a}) $(C, \rho)$ for $\G$, as explained in \cite{yu:construction}*{\S 15}, where $C \subset \G(K)$ is compact mod centre subgroup and $\rho$ is a representation of $C$.
-In \cite{yu:smooth} it is shown that the $C$ admits a smooth integral model, in the sense that there is a smooth group scheme $\underline{C}$ over $\OK$ such that $\underline{C}(\OK) = C$.
+%The generic datum $(\vec{\G}, \pi_0, \vec{\phi})$ determines a type (in the sense of \cite{bushnell-kutzko:98a}) $(C, \rho)$ for $\G$, as explained in \cite{yu:01a}*{\S 15}, where $C \subset \G(K)$ is compact mod centre subgroup and $\rho$ is a representation of $C$.
+In \cite{yu:03a} it is shown that the $C$ admits a smooth integral model, in the sense that there is a smooth group scheme $\underline{C}$ over $\OK$ such that $\underline{C}(\OK) = C$.
 

### 2015-11-24 followup.tex
Moving computers

@@
 \end{enumerate}
-The pair $(f_i, j_{i+1})$ is a symplectic action of $J^0\cdots J^i$ on $H^{i+1}$, so it defines a group homomorphism 
+The pair $(f_i, j_{i+1})$ is a symplectic action of $J^0\cdots J^i$ on $H^{i+1}$ in the sense of \cite{yu:construction}, so, together with the quotient $J^{i+1} \to H^{i+1}$, it defines a group homomorphism
 \begin{equation}\label{eq:symaction}
 \begin{tikzcd}
-h_{i+1} : (J^0\cdots J^i)\ltimes J^{i+1} \arrow{r} & (J^0\cdots J^i)\ltimes H^{i+1} \arrow{r} & \Sp(V_{i+1})\ltimes V_{i+1}^\sharp.
+h_{i+1} : (J^0\cdots J^i)\ltimes J^{i+1} \arrow{r} 
+%& (J^0\cdots J^i)\ltimes H^{i+1} \arrow{r} 
+& \Sp(V_{i+1})\ltimes V_{i+1}^\sharp.
 \end{tikzcd}
@@
 \]
-Then $h_1^*(\omega_1)$ is a representation of $J^0\ltimes J^1$, determined by the quasicharacter $\varphi_1$ of $J^1$. 
+
+Now $h_1^*(\omega_1)$ is a representation of $J^0\ltimes J^1$, determined by the quasicharacter $\varphi_1$ of $J^1$. 
 Write $\inf(\sigma_0\otimes \varphi_0)$ for the representation of $J^0 \ltimes J^1$ obtained by pulling back $\sigma_0\otimes \varphi_0$ along $J^0 \ltimes J^1 \to J^0$. 
@@
 $h_1^*(\omega_1) \otimes \inf(\sigma_0\otimes \varphi_0)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 \ltimes 1) \cap (1 \ltimes J^1)$, so $h_1^*(\omega_1) \otimes \inf(\sigma_0\otimes \varphi_0)$ descends to a representation $\,^\circ \rho_1$ of $J^0 J^1$.
-%
-As above, the representation 
+
+Likewise, the representation 
 $h_{2}^*(\omega_{2}) \otimes \inf(\,^\circ \rho_1)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 J^1 \ltimes 1) \cap (1 \ltimes J^2)$, so $h_2^*(\omega_2) \otimes \inf(\,^\circ \rho_1)$ descends to a representation $\,^\circ \rho_2$ of $J^0 J^1 J^2$.
+
 Continuing in this way, one constructs the representation $\,^\circ \rho_d$ of $J^0\cdots J^d$. 
-
-The character of $\,^\circ \rho_d$ on $J^0\cdots J^d$ satisfies
+%
+The character of $\,^\circ \rho_d$ on $\,^\circ K = J^0\cdots J^d$ satisfies
 \[
@@
 \]
-with ...
+for $k_i\in J^i$.
 
@@
 The first step in the geometrization of the type $(\,^\circ K,\,^\circ \rho)$ is to replace $\,^\circ K$ with a group scheme $G$ over $\Fq$ so that $G(\Fq) = \,^\circ K$, canonically. 
-By \cite{yu:03a}*{Prop 10.2} there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that \[\underline{G}(\OK)= \,^\circ K\] 
-For every positive integer $n$, let $G_n$ be the Greenberg transform of $\underline{G} \times_{\Spec{\OK}} \Spec{\OK/\mathfrak{m}_K^n}$, where $\mathfrak{m}_K$ is the maximal ideal in $\OK$.
-Then $G_n$ is a smooth group scheme over $\Fq$ and $G_n(\Fq) = \underline{G}(\OK/\mathfrak{m}_K^n)$, canonically.
+By \cite{yu:models}*{Prop 10.2} there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that \[ 
+\underline{G}(\OK)= \,^\circ K.
+\] 
+Set $S = \Spec{\OK}$ and $S_n = \Spec{\OK/\mathfrak{m}^n}$, where $\mathfrak{m}_K$ is the maximal ideal in $\OK$, and $n$ is a positive integer $n$.
+Let $G_n$ be the Greenberg transform of $\underline{G} \times_{S} S_n$.
+Then $G_n$ is a smooth group scheme over $\Fq$ and 
+\[
+G_n(\Fq) = \underline{G}(\OK/\mathfrak{m}_K^n),
+\]
+canonically.
+%
 Let $G$ be the Greenberg transform of $\underline{G}$.
-Then $G$ is a group scheme over $\Fq$ and $G(\Fq) = \underline{G}(\OK) = \,^\circ K$, canonically.
-
-In order to complete the geometrization of the type $(\,^\circ K,\,^\circ \rho)$, we will need more smooth models.
-Fortunately, as above, Yu has already done the heavy work.
+Then $G$ is a group scheme over $\Fq$ and 
+\[
+G(\Fq) = \,^\circ K,
+\]
+canonically.
+
 %
@@
 
-Moreover, the quotient
-
-Regarding this construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:03a} concludes with the following provocative observation.
+\newcommand{\reductive}{{\operatorname{red}}}
+
+With these group schemes, the other groups appearing in Section~\ref{ssec:review} may also be put into the framework needed for geoemtrization.
+
+Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$.
+The Heisenberg p-group $H^{i+1}$ group may be realized as $H^{i+1} = H^{i+1}_{\Fq}(\Fq)$, where $H^{i+1}_{\Fq}$ a quotient of $\underline{J}^{i+1}_{\Fq}$ as an algebraic group.
+Then the quotient $J^{i+1}\to H^{i+1}$ is realized as the composition
+\[
+\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq).
+\]
+
+The quotient  $J^{i+1} \to V_{i+1}$ admits a similar description, realizing $V_{i+1}$ as a quotient of the special fibre of $\underline{J}^{i+1}$
+
+ and $\underline{J}^{i+1, \reductive}_\Fq$ for the reductive quotient of $\underline{J}^{i+1}_\Fq$.
+
+In order to complete the geometrization of the type $(\,^\circ K,\,^\circ \rho)$, we will need more smooth models.
+Fortunately, as above, Yu has already done the heavy work.
+
+Regarding this construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:models} concludes with the following provocative observation.
+
 \begin{quotation}

### 2015-11-25 followup.tex
Added proposition on geo of Weil-Heisenberg

@@
 \begin{enumerate}
-\item compact open subgroups $J^i\subset \,^\circ K$, for $i=0, \ldots d$, such that \[\,^\circ K = J^0\cdots J^d;\]
-\item a continuous representation $\sigma_0$ of $J^0$;
-\item a quasicharacter $\varphi_i : J^i \to \CC^\times$, for $i=0, \ldots d$.
+\item[(0)] a compact group $\,^\circ K$;
+\item[(1)] compact open subgroups $J^i\subset \,^\circ K$, for $i=0, \ldots d$, such that \[\,^\circ K = J^0\cdots J^d;\]
+\item[(2)] a continuous representation $\varpi_0$ of $J^0$, inflated from ...
+\item[(3)] a quasicharacter $\varphi_i : J^i \to \CC^\times$, for $i=0, \ldots d$.
 \end{enumerate}
@@
 \begin{enumerate}
-\item a quotient $J^{i+1} \to V_{i+1}$ to a finite abelian group, and the structure of a $\Fq$-vector space on $V_{i+1}$, compatible with the abelian group structure above;
-\item a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$;
-\item an additive character $\psi_{i+1} : C_{i+1} \to \EEx$;
-\item a group homomorphism $\,^\circ f_i : J^0 \cdots J^i \to \Sp(V_{i+1})$;
-\item a quotient $J^{i+1} \to H^{i+1}$, where $H^{i+1}$ is a Heisenberg $p$-group, together with an isomorphism $j_{i+1} : H^{i+1} \to V_{i+1}^\sharp$, where $V_{i+1}^\sharp$ is the Heisenberg group determined by $(V_{i+1}, \langle\ ,\ \rangle_{i+1}, C_{i+1}, \psi_{i+1})$.
-\end{enumerate}
-The pair $(f_i, j_{i+1})$ is a symplectic action of $J^0\cdots J^i$ on $H^{i+1}$ in the sense of \cite{yu:construction}, so, together with the quotient $J^{i+1} \to H^{i+1}$, it defines a group homomorphism
+\item[(4)] a quotient $J^{i+1} \to V_{i+1}$ to a finite abelian group, and the structure of a $\Fq$-vector space on $V_{i+1}$, compatible with the abelian group structure above;
+\item[(5)] a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$;
+\item[(6)] an additive character $\psi_{i+1} : C_{i+1} \to \EEx$;
+\item[(7)] a group homomorphism $\,^\circ f_i : J^0 \cdots J^i \to \Sp(V_{i+1})$;
+\item[(8)] a quotient $J^{i+1} \to H^{i+1}$, where $H^{i+1}$ is a Heisenberg $p$-group;
+\item[(9)] an isomorphism $j_{i+1} : H^{i+1} \to V_{i+1}^\sharp$, where $V_{i+1}^\sharp$ is the Heisenberg group determined by $(V_{i+1}, \langle\ ,\ \rangle_{i+1}, C_{i+1}, \psi_{i+1})$.
+%\end{enumerate}
+\item[(10)]The pair $(f_i, j_{i+1})$ is a symplectic action of $J^0\cdots J^i$ on $H^{i+1}$ in the sense of \cite{yu:construction}, so, together with the quotient $J^{i+1} \to H^{i+1}$, it defines a group homomorphism
 \begin{equation}\label{eq:symaction}
@@
 %
-
-From this information, Yu constructs a representation $\,^\circ \rho_i$ of $J^0\cdots J^i$, for each $i=0, \ldots, d$, such that $\,^\circ \rho_d = \,^\circ \rho$.
-We will need some detail about this construction, so we will review it here.
+From this information, Yu constructs 
+%\begin{enumerate}
+\item[(11)] a representation $\,^\circ \rho_i$ of $J^0\cdots J^i$, for each $i=0, \ldots, d$, such that $\,^\circ \rho_d = \,^\circ \rho$,
+constructed as follows.
+%\end{enumerate}
+%We will need some more detail about the construction of the representations $\,^\circ \rho^i$, so we review it below.
+%
 %Let $\varpi_1$ be the Heisenberg representation of the Heisenberg group $V_1^\sharp$, with central character $\psi_1$.
 %Let $\varrho_1$ be the Weil representation of $\Sp(V_1)$ with the same representation space as $\omega_1$.
-Let $\omega_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, with the same representation space as the Heisenberg representation of the Heisenberg group $V_{i+1}^\sharp$.
+Let $\omega_{i+1}$ be the Heisenberg representation of the Heisenberg group $V_{i+1}^\sharp$.
+This determines the Weil representation $W_{i+1}$ on the same representation space as the Heisenberg representation of $V_{i+1}^\sharp$.
+Let $W_{i+1} \ltimes \omega_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$.
 \[
@@
 \  & J^{i+1} \arrow{d} & \\
-Sp(V_{i+1}) \ltimes V_{i+1}^\sharp & \arrow{l}[swap]{h_1} (J^0 \cdots J^i) \ltimes J^{i+1} \arrow{r} \arrow{d} & J^0 \cdots J^i J^{i+1}\\
+\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp & \arrow{l}[swap]{h_{i+1}} (J^0 \cdots J^i) \ltimes J^{i+1} \arrow{r} \arrow{d} & J^0 \cdots J^i J^{i+1}\\
 & (J^0 \cdots J^i) & 
@@
 \]
-
+%
 Now $h_1^*(\omega_1)$ is a representation of $J^0\ltimes J^1$, determined by the quasicharacter $\varphi_1$ of $J^1$. 
@@
 $h_1^*(\omega_1) \otimes \inf(\sigma_0\otimes \varphi_0)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 \ltimes 1) \cap (1 \ltimes J^1)$, so $h_1^*(\omega_1) \otimes \inf(\sigma_0\otimes \varphi_0)$ descends to a representation $\,^\circ \rho_1$ of $J^0 J^1$.
-
+%
 Likewise, the representation 
 $h_{2}^*(\omega_{2}) \otimes \inf(\,^\circ \rho_1)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 J^1 \ltimes 1) \cap (1 \ltimes J^2)$, so $h_2^*(\omega_2) \otimes \inf(\,^\circ \rho_1)$ descends to a representation $\,^\circ \rho_2$ of $J^0 J^1 J^2$.
-
+%
 Continuing in this way, one constructs the representation $\,^\circ \rho_d$ of $J^0\cdots J^d$. 
@@
 for $k_i\in J^i$.
+\end{enumerate}
 
@@
 
-The first step in the geometrization of the type $(\,^\circ K,\,^\circ \rho)$ is to replace $\,^\circ K$ with a group scheme $G$ over $\Fq$ so that $G(\Fq) = \,^\circ K$, canonically. 
 By \cite{yu:models}*{Prop 10.2} there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that \[ 
@@
 \] 
-Set $S = \Spec{\OK}$ and $S_n = \Spec{\OK/\mathfrak{m}^n}$, where $\mathfrak{m}_K$ is the maximal ideal in $\OK$, and $n$ is a positive integer $n$.
-Let $G_n$ be the Greenberg transform of $\underline{G} \times_{S} S_n$.
-Then $G_n$ is a smooth group scheme over $\Fq$ and 
-\[
-G_n(\Fq) = \underline{G}(\OK/\mathfrak{m}_K^n),
-\]
-canonically.
-%
-Let $G$ be the Greenberg transform of $\underline{G}$.
-Then $G$ is a group scheme over $\Fq$ and 
-\[
-G(\Fq) = \,^\circ K,
-\]
-canonically.
-
-%
-As explained in \cite{yu:03a}*{\S 10.4}, the
-the group scheme $\underline{G}$ comes with the following auxillary data:
+%
+As explained in \cite{yu:03a}*{\S 10.4}, the group scheme $\underline{G}$ comes with the following auxilliary data:
 \begin{enumerate}
@@
 
-In order to complete the geometrization of the type $(\,^\circ K,\,^\circ \rho)$, we will need more smooth models.
-Fortunately, as above, Yu has already done the heavy work.
+Let us return to the list of Section~\ref{ssec:review} and consider how we have recast each part.
+\begin{enumerate}
+\item[(0)] The compact group $\,^\circ K$ is replaced by the smooth group scheme $\underline{G}$ over $\OK$.
+\item[(1)] The compact open subgroups $J^i \hookrightarrow \,^\circ K$ are replaced by the morphisms $\underline{J}^i \to \underline{G}$ of smooth group schemes over $\OK$.
+\item[(2)] The representation $\varpi_0$ is obtained by pullback from a representation $\sigma_0$ of $\underline{J}^{0,\reductive}_\Fq$, which makes use of the following morphisms of group schemes.
+\[
+\underline{J}^{0} \longleftarrow \underline{J}^{0}_\Fq \to \underline{J}^{0,\reductive}_\Fq.
+\]
+\item[(3)] The quasicharacters $\varphi_i : \underline{J}^i(\OK) \to \CC^\times$ have not yet been geometrized.
+\item[(4)] The quotient $J^{i+1}\to V_{i+1}$ has been replaced with the following morphisms of group schemes.
+\[
+\underline{J}^{i+1} \longleftarrow \underline{J}^{i+1}_\Fq \to \underline{J}^{i+1,\reductive}_\Fq \to V_{i+1,\Fq}.
+\]
+\item[(5)] The symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$ is given by 
+\item[(6)]
+\item[(7)] The group homomorphism $\,^\circ f_i : J^0 \cdots J^i \to \Sp(V_{i+1})$ has been replaced by the following morphisms of group schemes.
+\[
+\underline{G}^{i} \longleftarrow \underline{G}^{i}_\Fq \to \underline{G}^{i,\reductive}_\Fq \to \Sp(V_{i,\Fq}),
+\]
+and $\Sp(V_{i,\Fq})$ is itself a reductive algebraic group over $\Fq$.
+\item[(8)] The quotient $J^{i+1} \to H^{i+1}$ has been replaced by the following morphisms of group schemes.
+\[
+\underline{J}^{i+1} \longleftarrow \underline{J}^{i+1}_\Fq \to H^{i+1}_\Fq.
+\] 
+\item[(9)]
+The Heisenberg group $V_{i+1}^\sharp$ is replaced by a unipotent algebraic group $V_{i+1,\Fq}^\sharp$ over $\Fq$, and the group isomorphism $H^{i+1} \iso V_{i+1}^\sharp$ is replaced by an isomorphism $H^{i+1}_\Fq \iso V_{i+1,\Fq}^\sharp$ of algebraic groups over $\Fq$.
+\item[(10)]
+
+\end{enumerate}
 
@@
 \subsection{Geometrization}\label{ssec:geometrization}
+
+\begin{proposition}
+Let $(V, \langle\ , \rangle, C, \psi)$ be a finite-dimensional vector space over $\Fq$ and . .  .
+Let $V^\sharp$ be the geometric Heisenberg group determined by this and let $\omega$ be the Heisenberg representation of $V^\sharp$.
+Let $W$ be the Weil representation of $\Sp(V)$ determined by $(\omega,V^\sharp)$. 
+Let $W\ltimes \omega$ be the resulting representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$.
+Then there is a virtual $W\ltimes \omega$-equivariant constructible sheaf $\mathcal{W}$ on $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\mathcal{W}} = \trace(W\ltimes \omega)$.
+\end{proposition}
+
+%\begin{proof}
+%We begin by geometrizing the Heisenberg representation $(\omega, V^\sharp)$ to $\mathcal{H}$.
+%\end{proof}
+
+The first step in the geometrization of the type $(\,^\circ K,\,^\circ \rho)$ is to replace $\,^\circ K$ with a group scheme $G$ over $\Fq$ so that $G(\Fq) = \,^\circ K$, canonically. 
+Set $S = \Spec{\OK}$ and $S_n = \Spec{\OK/\mathfrak{m}^n}$, where $\mathfrak{m}_K$ is the maximal ideal in $\OK$, and $n$ is a positive integer $n$.
+Let $G_n$ be the Greenberg transform of $\underline{G} \times_{S} S_n$.
+Then $G_n$ is a smooth group scheme over $\Fq$ and 
+\[
+G_n(\Fq) = \underline{G}(\OK/\mathfrak{m}_K^n),
+\]
+canonically.
+%
+Let $G$ be the Greenberg transform of $\underline{G}$.
+Then $G$ is a group scheme over $\Fq$ and 
+\[
+G(\Fq) = \,^\circ K,
+\]
+canonically.
 

### 2015-11-25 followup.tex
FIxing some conflicts I made.

@@
 %
+ We will need some detail about this construction, so we will review it here.
 %Let $\varpi_1$ be the Heisenberg representation of the Heisenberg group $V_1^\sharp$, with central character $\psi_1$.
@@
 
-With these group schemes, the other groups appearing in Section~\ref{ssec:review} may also be put into the framework needed for geoemtrization.
+With these group schemes, the other groups and group homomorphisms appearing in Section~\ref{ssec:review} may be put into the framework needed for geometrization.
 
 Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
-The Heisenberg p-group $H^{i+1}$ group may be realized as $H^{i+1} = H^{i+1}_{\Fq}(\Fq)$, where $H^{i+1}_{\Fq}$ a quotient of $\underline{J}^{i+1}_{\Fq}$ as an algebraic group.
-Then the quotient $J^{i+1}\to H^{i+1}$ is realized as the composition
-\[
-\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq).
-\]
-
-The quotient  $J^{i+1} \to V_{i+1}$ admits a similar description, realizing $V_{i+1}$ as a quotient of the special fibre of $\underline{J}^{i+1}$
-
- and $\underline{J}^{i+1, \reductive}_\Fq$ for the reductive quotient of $\underline{J}^{i+1}_\Fq$.
+The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $U^{i+1}_\Fq$, where $U^{i+1}_\Fq$, appears as a quotient $J^{i+1}_\Fq \to U^{i+1}_\Fq$ of algebraic groups.
+Then the quotient $J^{i+1} \to V_{i+1}$ is realized as the composition
+\[
+\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to U^{i+1}_{\Fq}(\Fq) = V_{i+1}.
+\]
+Likewise, the Heisenberg p-group $H^{i+1}$ group may be realized as a quotient of algebraic groups, and $J^{i+1}\to H^{i+1}$ as the composition 
+\[
+\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H^{i+1}.
+\]
+Finally, the group homomorphism $\,^\circ f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ may be made geometric in much the same way.
+Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $\,^\circ f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ is realized as the composition
+\[
+\underline{G}^{i}(\OK) \to \underline{G}^{i}(\Fq) = \underline{G}^{i}_\Fq(\Fq) \to  \underline{G}^{i,\reductive}_\Fq(\Fq) \to W^{i+1}_{\Fq}(\Fq) = \Sp(V_{i+1}).
+\]
 

### 2015-12-01 followup.tex
(re)starting the application to types

@@
 
-\title[Commutative Character Sheaves]{Commutative Character Sheaves}
+\title[Commutative Character Sheaves]{Commutative Character Sheaves on smooth group schemes over finite fields}
 %with an application to geometric types for supercuspidal representations
@@
 Let us refer to the types arising in this manner as {\it Yu types}.
-In this section we show that every Yu type is geometrizable, in a sense which will be made clear below.
+In this section we show that every Yu type is geometrizable.
+% in a sense which will be made clear below.
 
 A Yu type is a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, with certain properties. 
-In Section~\ref{ssec:review} we recall properties of $(\,^\circ K,\,^\circ \rho)$ which we allow us, in Section~\ref{ssec:geometrization}, to find a pair $(G, \mathcal{F})$ where $G$ is a smooth group scheme over $\Fq$ and $\mathcal{F}$ is a virtual constructible sheaf $\ell$-adic sheaf on $G$ from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius.
+In Section~\ref{ssec:review} we recall properties of $(\,^\circ K,\,^\circ \rho)$ which we allow us, in Section~\ref{ssec:geometrization}, to find a pair $(G, \mathcal{F})$ where $G$ is a group scheme over $\Fq$ and $\mathcal{F}$ is a virtual constructible sheaf $\ell$-adic sheaf on $G$ from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius.
 
@@
 \item[(2)] a continuous representation $\varpi_0$ of $J^0$, inflated from ...
-\item[(3)] a quasicharacter $\varphi_i : J^i \to \CC^\times$, for $i=0, \ldots d$.
+\item[(3)] a quasicharacter $\varphi_i : J^0\cdots J^i \to \CC^\times$, for $i=0, \ldots d$.
 \end{enumerate}
@@
 \end{equation}
-%
+\end{enumerate}
+
 From this information, Yu constructs 
-%\begin{enumerate}
-\item[(11)] a representation $\,^\circ \rho_i$ of $J^0\cdots J^i$, for each $i=0, \ldots, d$, such that $\,^\circ \rho_d = \,^\circ \rho$,
+a representation $\,^\circ \rho_i$ of $J^0\cdots J^i$, for each $i=0, \ldots, d$, such that $\,^\circ \rho_d = \,^\circ \rho$,
 constructed as follows.
@@
 %
- We will need some detail about this construction, so we will review it here.
+We will need some detail about this construction,   so we review it here.
+
 %Let $\varpi_1$ be the Heisenberg representation of the Heisenberg group $V_1^\sharp$, with central character $\psi_1$.
@@
 \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp & \arrow{l}[swap]{h_{i+1}} (J^0 \cdots J^i) \ltimes J^{i+1} \arrow{r} \arrow{d} & J^0 \cdots J^i J^{i+1}\\
-& (J^0 \cdots J^i) & 
-\end{tikzcd}
-\]
-%
-Now $h_1^*(\omega_1)$ is a representation of $J^0\ltimes J^1$, determined by the quasicharacter $\varphi_1$ of $J^1$. 
-Write $\inf(\sigma_0\otimes \varphi_0)$ for the representation of $J^0 \ltimes J^1$ obtained by pulling back $\sigma_0\otimes \varphi_0$ along $J^0 \ltimes J^1 \to J^0$. 
+& J^0 \cdots J^i & 
+\end{tikzcd}
+\]
+
+Now $h_1^*(W_1\ltimes \omega_1)$ is a representation of $J^0\ltimes J^1$, determined by the quasicharacter $\varphi_1$ of $J^1$. 
+Write $\inf(\sigma_0)$ for the representation of $J^0 \ltimes J^1$ obtained by pulling back $\sigma_0$ along $J^0 \ltimes J^1 \to J^0$. 
 By \cite{yu:01a}*{}, the representation 
-$h_1^*(\omega_1) \otimes \inf(\sigma_0\otimes \varphi_0)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 \ltimes 1) \cap (1 \ltimes J^1)$, so $h_1^*(\omega_1) \otimes \inf(\sigma_0\otimes \varphi_0)$ descends to a representation $\,^\circ \rho_1$ of $J^0 J^1$.
+$h_1^*(\omega_1) \otimes \varphi_1 \otimes \inf(\sigma_0)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 \ltimes 1) \cap (1 \ltimes J^1)$, so $h_1^*(\omega_1) \otimes \varphi_2 \otimes\inf(\sigma_0\otimes)$ descends to a representation $\,^\circ \rho_1$ of $J^0 J^1$.
 %
@@
 for $k_i\in J^i$.
-\end{enumerate}
 

### 2016-01-05 followup.tex
Cleaned up CCS section. Working on types.

@@
 We describe a function-sheaf dictionary for one-dimensional characters of arbitrary smooth group schemes
-over finite fields.  In previous work, we considered the case of smooth commutative group schemes and found
+over finite fields.  In previous work, we considered the case of commutative smooth group schemes and found
 that the standard definition of character sheaves produced a dictionary with a nontrivial kernel.  In this paper,
 we give a modification of the category of character sheaves that remedies this defect, and is also extensible to
-non-commutative groups.  We use these \emph{commutative character sheaves} to geometrize types for
+non-commutative groups.  
+As an application, we use these \emph{commutative character sheaves} to geometrize types for
 supercuspidal representations of $p$-adic groups. 
@@
 using character sheaves \cite{lusztig:85a}*{Def.~2.10}, but focus on the case of $1$-dimensional characters
-$G(k)^*$ assuming only that $G$ is smooth. The category $\CS(G)$ has a straightforward generalization to this case, but again
+$G(k)^*$ assuming only that $G$ is smooth, allowing for the possibility that $G$ is not connected and not reductive.
+The category $\CS(G)$ has a straightforward generalization to this case, but again
 there are more linear character sheaves than there are characters, as pointed out by Kamgarpour \cite{kamgarpour:09a}*{(1.1)}.
 We define a category $\CCS(G)$ and a forgetful functor to $\CS(G)$ so that $\TrFrob{G} : \CCSiso{G} \to G\ab(k)^*$
-is an isomorphism.  Since $G\ab(k)^*$ surjects onto $G(k)^*$, for each character $\chi \in G(k)^*$ there is a commutative
-character sheaf $\cs{L}$ on $G$ with $\TrFrob{G}(\cs{L}) = \chi$. Moreover, pullback along the quotient $q : G \to G\ab$
+is an isomorphism.  
+Since $G\ab(k)^*$ surjects onto $G(k)^*$, it follows that for each character $\chi \in G(k)^*$ there is a commutative
+character sheaf $\cs{L}$ on $G$ with $\TrFrob{G}(\cs{L}) = \chi$. Moreover, we find that pullback along the quotient $q : G \to G\ab$
 defines an equivalence of categories $\CCS(G\ab) \to \CCS(G)$.  Note that the functor $\CCS(G) \to \CS(G)$ is not
@@
 
+\subsection{Objects and maps in commutative character sheaves} \label{ssec:obmor}
+
 Suppose $G$ is commutative, so $G\der = 1$. 
@@
 Then $\beta : \cs{L}_1\to \EE$ is an isomorphism in $\CS(1)$, and unique by \cite{cunningham-roe:13a}*{Thm 3.9}.
-Tracing through the construction of $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ from $\beta : \cs{L}_1\to \EE$, we find \todo{I'm having some trouble seeing this.} that $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ is the canonical isomorphism coming from the equation $m = m \circ \theta$.
+Tracing through the construction of $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ from $\beta : \cs{L}_1\to \EE$, we find 
+%\todo{I'm having some trouble seeing this.} 
+that $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ is the canonical isomorphism coming from the equation $m = m \circ \theta$. 
 Thus, when $G$ is commutative, Definition~\ref{def:CCS} recovers Definition~\ref{def:CCScom}.
@@
 \begin{theorem}\label{thm:Gab}
+%Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
 Pull-back along the abelianization $q : G \to G\ab$
@@
 
-\subsection{Objects and maps in commutative character sheaves} \label{ssec:obmor}
-
 Theorem~\ref{thm:Gab} shows that $\CCS(G)$ is a categorical solution to the problem that linear character sheaves on $G$ need not be trivial on $G\der$, as discussed at the beginning of Section~\ref{sec:noncom}; at the same time, it is the categorical solution to the problem, discussed in Section~\ref{ssec:defect}, that the dictionary between linear character sheaves on $G\ab$ and characters of $G\ab$, need not be perfect.
@@
 But a description of $\CCS(G)$ requires, at the very least, a description of isomorphism classes of objects, and maps.
-%
-
-\begin{proposition}
+
+\begin{corollary}\label{cor:Gab}
+%Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
+Category $\CCS(G)$ is monoidal and $\CCSiso{G} \iso \Hom(G\ab(\Fq),\EEx)$, canonically.
+Every map in $\CCS(G)$ is either trivial or an isomorphism, and the automorphism group of any object in $\CCS(G)$ is $\Hom(\pi_0(G\ab)_{\Frob{}},\EEx)$, canonically.
+\end{corollary}
+
+\subsection{Geometrization of characters} \label{ssec:geo}
+
+\begin{theorem}\label{thm:geo}
+%Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
 The trace of Frobenius $\TrFrob{} : \CCSiso{G}\to G(\Fq)^*$ fits into the following diagram,
@@
 \ & & \CCSiso{G\ab} \arrow{d}{\TrFrob{}}[swap]{\iso} \arrow{r}{\iso} & \CCSiso{G} \arrow{d}{\TrFrob{}}& \\
-1 \arrow{r} & \Delta^* \arrow{r} & G\ab(k)^* \arrow{r} & G(k)^* \arrow{r} & 1,
-\end{tikzcd}
-\]
-where $\Delta$ denotes the image of the connecting homomorphism $G\ab(\Fq) \to \Hh^1(\Fq, G\der)$.
-In particular, isomorphism classes of objects in $\CCS(G)$ are canonically identified with the group $G\ab(\Fq)^*$.
-\end{proposition}
+1 \arrow{r} & \Delta_G^* \arrow{r} & G\ab(k)^* \arrow{r} & G(k)^* \arrow{r} & 1,
+\end{tikzcd}
+\]
+where $\Delta_G$ denotes the image of the connecting homomorphism $G\ab(\Fq) \to \Hh^1(\Fq, G\der)$. 
+Thus, category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the following sense: for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $(\cs{L},\mu,\beta)$ in $\CCS(G)$ such that $\trFrob{\cs{L}} = \chi$.
+The geometrization of $\chi : G(\Fq) \to \EEx$ is not unique, but the group of isomorphism classes of possibilities are enumerated by $\Delta_G^*$.
+\end{theorem}
 
@@
 
-\begin{proposition}
-Every map in $\CCS(G)$ is either trivial or an isomorphism. 
-For every commutative character sheaf on $G$, its automorphism group is
-$
-((\pi_0(G\ab))^*)^{\Frob{}}.
-$
-\end{proposition}
-
-\begin{proof}
-By Theorem~\ref{thm:Gab}, $\Aut_{\CCS(G)}(\cs{L},\mu,\beta) = \Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab)$. 
-By \cite{cunningham-roe:13a}*{Thm 3.9},  $\Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab) = ((\pi_0(G\ab))^*)^{\Frob{}}$. \todo{Shouldn't it be coinvariants?}
-\end{proof}
-
 %\todo{Masound's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case.
@@
 %This approach requires introducing equivariant linear character sheaves, as defined in Section~[].
+
+%We close this section by gathering together the main result of this paper in one place.
 
@@
 \begin{lemma}\label{lem:torsor}
-If $q : G \to G_0$ is an $H$-torsor in the fppf topology 
+If $q : G \to G_0$ is an $H$-torsor in the fpqc topology 
 then $q_H^*: \CS(G_0) \to \CS_H(G)$ is an equivalence.
@@
 \begin{proof}
-First we recall that the comparison functor 
+First we observe that the comparison functor 
 $\Loc(G_0) \to \Loc_H(G)$ is an equivalence.
-To see this, observe first that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
+To see this, first recall that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
 Then, observe that the comparison functor for Weil local systems is an equivalence for flat surjective morphisms of affine schemes over $\Fq$.
-It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fppf topology [Vistoli].
-(This is a slight variation on the argument showing that quasicoherent sheaves are a stack over schemes in the fppf topology.)
-Since $q : G\to G_0$ is an $H$-torsor in the fppf topology, is now follows from descent theory that the comparison functor $\Loc(G_0) \to \Loc_H(G)$ is an equivalence [Vistoli].
-\todo{Need more specific references}
+It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fpqc topology; see \cite{Vistoli:notes}*{Lem 4.25} for example.
+(This is a slight variation on the argument showing that quasicoherent sheaves are a stack over schemes in the fpqc topology; see \cite{Vistoli:notes}*{Thm 4.23} for example.)
+Since $q : G\to G_0$ is an $H$-torsor in the fpqc topology, is now follows from descent theory that the comparison functor $\Loc(G_0) \to \Loc_H(G)$ is an equivalence; see \cite{Vistoli:notes}*{Thm 4.46} for example.)
+%\todo{Need more specific references}
 
@@
 %\begin{proof}[Proof of Proposition~\ref{prop:Gder_triv}] 
-The abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ \cite{demazure:SGA3-VIA}*{Thm. 3.2}.
-Set $H=G\der$.
-Let $j : H\hookrightarrow G$ be the inclusion and let $q : G \to G\ab$ be the quotient. 
+By \cite{demazure:SGA3-VIA}*{Thm. 3.2}, the abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ and the quotient $q: G \to G\ab$ is a $G\der$-torsor in the fppf topology.
+%
+To simplify notation below, set $H=G\der$
+and let $j : H\hookrightarrow G$ be the inclusion. 
 With reference to \eqref{qH} and Section~\ref{ssec:closed}, consider the following diagram.
@@
 Here we use the notation $\CS'(G)$ from Section~\ref{ssec:noncomdef} and the observation that $\CS'(G)$ is precisely the category $\CS^{H}(G)$ from Section~\ref{ssec:closed} for $H=G\der$.
-The forget
-Since the quotient $q : G \to G\ab$ is a trivial $H$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, 
-it now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{H}(G)$ is an equivalence.
+%
+Since the quotient $q : G \to G\ab$ is an $H$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, 
+it is also an $H$-torsor in the fpqc topology.
+It now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{H}(G)$ is an equivalence.
+%
 On the other hand, by Lemma~\ref{lem:beta}, $\CS'(G) \to \CS_{H}(G)$, defined by $(\cs{L},\mu,\beta)\mapsto (\cs{L},\mu, \nu)$, is an equivalence.
-Since the essential image of the forgetful functor $\CS'(G)\to \CS(G)$ is precisely the category of $(\cs{L},\mu)\in \CS(G)$ such that $\cs{L}\vert_{H} \iso (\EE)_{H}$, this completes the proof of Proposition~\ref{prop:Gder_triv}.
+This completes the proof of Proposition~\ref{prop:Gder_triv}.
 %\end{proof}
@@
 
-\section{Application to type theory for \texorpdfstring{$p$}{p}-adic groups}
+\subsubsection{Proof of Corollary~\ref{cor:Gab}}\label{ssec:proof3}
+
+Let us write $(\cs{L},\mu,\beta) \mapsto (\cs{L}\ab,\mu\ab)$ to indicate the equivalence appearing in Theorem~\ref{thm:Gab};
+then \[\Aut_{\CCS(G)}(\cs{L},\mu,\beta) = \Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab).\] 
+By \cite{cunningham-roe:13a}*{Thm 3.9},  $\Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab) = \Hom(\pi_0(G\ab)_{\Frob{}},\EEx)$.
+
+\section{Application to type theory for \texorpdfstring{$p$}{p}-adic groups}\label{sec:types}
 
@@
 As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
-The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from the data. 
+The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
 Let us refer to the types arising in this manner as {\it Yu types}.
-In this section we show that every Yu type is geometrizable.
+%In this section we show that every Yu type is geometrizable.
 % in a sense which will be made clear below.
-
-A Yu type is a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, with certain properties. 
-In Section~\ref{ssec:review} we recall properties of $(\,^\circ K,\,^\circ \rho)$ which we allow us, in Section~\ref{ssec:geometrization}, to find a pair $(G, \mathcal{F})$ where $G$ is a group scheme over $\Fq$ and $\mathcal{F}$ is a virtual constructible sheaf $\ell$-adic sheaf on $G$ from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius.
-
-\subsection{Review of Yu's types}\label{ssec:review}
-
-Every Yu type $(\,^\circ K,\,^\circ \rho)$ may be constructed directly from the following information, derived from a Yu datum:
-\begin{enumerate}
-\item[(0)] a compact group $\,^\circ K$;
-\item[(1)] compact open subgroups $J^i\subset \,^\circ K$, for $i=0, \ldots d$, such that \[\,^\circ K = J^0\cdots J^d;\]
-\item[(2)] a continuous representation $\varpi_0$ of $J^0$, inflated from ...
-\item[(3)] a quasicharacter $\varphi_i : J^0\cdots J^i \to \CC^\times$, for $i=0, \ldots d$.
-\end{enumerate}
-These representations $(\sigma_0, \varphi_0, \ldots , \varphi_d)$ enjoy certain properties, which allow Yu to construct, for $i=0, \ldots, d-1$, further:
-\begin{enumerate}
-\item[(4)] a quotient $J^{i+1} \to V_{i+1}$ to a finite abelian group, and the structure of a $\Fq$-vector space on $V_{i+1}$, compatible with the abelian group structure above;
-\item[(5)] a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$;
-\item[(6)] an additive character $\psi_{i+1} : C_{i+1} \to \EEx$;
-\item[(7)] a group homomorphism $\,^\circ f_i : J^0 \cdots J^i \to \Sp(V_{i+1})$;
-\item[(8)] a quotient $J^{i+1} \to H^{i+1}$, where $H^{i+1}$ is a Heisenberg $p$-group;
-\item[(9)] an isomorphism $j_{i+1} : H^{i+1} \to V_{i+1}^\sharp$, where $V_{i+1}^\sharp$ is the Heisenberg group determined by $(V_{i+1}, \langle\ ,\ \rangle_{i+1}, C_{i+1}, \psi_{i+1})$.
-%\end{enumerate}
-\item[(10)]The pair $(f_i, j_{i+1})$ is a symplectic action of $J^0\cdots J^i$ on $H^{i+1}$ in the sense of \cite{yu:construction}, so, together with the quotient $J^{i+1} \to H^{i+1}$, it defines a group homomorphism
-\begin{equation}\label{eq:symaction}
-\begin{tikzcd}
-h_{i+1} : (J^0\cdots J^i)\ltimes J^{i+1} \arrow{r} 
-%& (J^0\cdots J^i)\ltimes H^{i+1} \arrow{r} 
-& \Sp(V_{i+1})\ltimes V_{i+1}^\sharp.
-\end{tikzcd}
-\end{equation}
-\end{enumerate}
-
-From this information, Yu constructs 
-a representation $\,^\circ \rho_i$ of $J^0\cdots J^i$, for each $i=0, \ldots, d$, such that $\,^\circ \rho_d = \,^\circ \rho$,
-constructed as follows.
-%\end{enumerate}
-%We will need some more detail about the construction of the representations $\,^\circ \rho^i$, so we review it below.
-%
-We will need some detail about this construction,   so we review it here.
-
-%Let $\varpi_1$ be the Heisenberg representation of the Heisenberg group $V_1^\sharp$, with central character $\psi_1$.
-%Let $\varrho_1$ be the Weil representation of $\Sp(V_1)$ with the same representation space as $\omega_1$.
-Let $\omega_{i+1}$ be the Heisenberg representation of the Heisenberg group $V_{i+1}^\sharp$.
-This determines the Weil representation $W_{i+1}$ on the same representation space as the Heisenberg representation of $V_{i+1}^\sharp$.
-Let $W_{i+1} \ltimes \omega_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$.
-\[
-\begin{tikzcd}
-\  & J^{i+1} \arrow{d} & \\
-\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp & \arrow{l}[swap]{h_{i+1}} (J^0 \cdots J^i) \ltimes J^{i+1} \arrow{r} \arrow{d} & J^0 \cdots J^i J^{i+1}\\
-& J^0 \cdots J^i & 
-\end{tikzcd}
-\]
-
-Now $h_1^*(W_1\ltimes \omega_1)$ is a representation of $J^0\ltimes J^1$, determined by the quasicharacter $\varphi_1$ of $J^1$. 
-Write $\inf(\sigma_0)$ for the representation of $J^0 \ltimes J^1$ obtained by pulling back $\sigma_0$ along $J^0 \ltimes J^1 \to J^0$. 
-By \cite{yu:01a}*{}, the representation 
-$h_1^*(\omega_1) \otimes \varphi_1 \otimes \inf(\sigma_0)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 \ltimes 1) \cap (1 \ltimes J^1)$, so $h_1^*(\omega_1) \otimes \varphi_2 \otimes\inf(\sigma_0\otimes)$ descends to a representation $\,^\circ \rho_1$ of $J^0 J^1$.
-%
-Likewise, the representation 
-$h_{2}^*(\omega_{2}) \otimes \inf(\,^\circ \rho_1)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 J^1 \ltimes 1) \cap (1 \ltimes J^2)$, so $h_2^*(\omega_2) \otimes \inf(\,^\circ \rho_1)$ descends to a representation $\,^\circ \rho_2$ of $J^0 J^1 J^2$.
-%
-Continuing in this way, one constructs the representation $\,^\circ \rho_d$ of $J^0\cdots J^d$. 
-%
-The character of $\,^\circ \rho_d$ on $\,^\circ K = J^0\cdots J^d$ satisfies
-\[
-\trace(\,^\circ \rho_d)(k_0 \cdots k_d) = \sigma_0(k_0) \left( \varphi_0(k_0) \cdots \varphi_d(k_d) \right) ,
-\]
-for $k_i\in J^i$.
-
-\subsection{Smooth models}\label{ssec:models}
-
-By \cite{yu:models}*{Prop 10.2} there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that \[ 
-\underline{G}(\OK)= \,^\circ K.
-\] 
-%
-As explained in \cite{yu:03a}*{\S 10.4}, the group scheme $\underline{G}$ comes with the following auxilliary data:
-\begin{enumerate}
-\item[(Ji)]
-	affine smooth group schemes $\underline{J}^i$, for $i=0, 1, \ldots, d$, together with morphisms $\underline{J}^i \to \underline{G}$ such that \[\underline{J}^i(\OK) = J^i,\]
-\item[(Gj)] affine smooth group schemes $\underline{G}^{j}$, for $j=0, \ldots, d$, together with morphisms $\underline{G}^{j}\to \underline{G}$ such that 
-\[
-\underline{G}^{j}(\OK) = J^0\cdots J^i.
-\] 
-\end{enumerate}
-
-\newcommand{\reductive}{{\operatorname{red}}}
-
-With these group schemes, the other groups and group homomorphisms appearing in Section~\ref{ssec:review} may be put into the framework needed for geometrization.
-
-Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
-The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $U^{i+1}_\Fq$, where $U^{i+1}_\Fq$, appears as a quotient $J^{i+1}_\Fq \to U^{i+1}_\Fq$ of algebraic groups.
-Then the quotient $J^{i+1} \to V_{i+1}$ is realized as the composition
-\[
-\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to U^{i+1}_{\Fq}(\Fq) = V_{i+1}.
-\]
-Likewise, the Heisenberg p-group $H^{i+1}$ group may be realized as a quotient of algebraic groups, and $J^{i+1}\to H^{i+1}$ as the composition 
-\[
-\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H^{i+1}.
-\]
-Finally, the group homomorphism $\,^\circ f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ may be made geometric in much the same way.
-Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $\,^\circ f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ is realized as the composition
-\[
-\underline{G}^{i}(\OK) \to \underline{G}^{i}(\Fq) = \underline{G}^{i}_\Fq(\Fq) \to  \underline{G}^{i,\reductive}_\Fq(\Fq) \to W^{i+1}_{\Fq}(\Fq) = \Sp(V_{i+1}).
-\]
-
-Let us return to the list of Section~\ref{ssec:review} and consider how we have recast each part.
-\begin{enumerate}
-\item[(0)] The compact group $\,^\circ K$ is replaced by the smooth group scheme $\underline{G}$ over $\OK$.
-\item[(1)] The compact open subgroups $J^i \hookrightarrow \,^\circ K$ are replaced by the morphisms $\underline{J}^i \to \underline{G}$ of smooth group schemes over $\OK$.
-\item[(2)] The representation $\varpi_0$ is obtained by pullback from a representation $\sigma_0$ of $\underline{J}^{0,\reductive}_\Fq$, which makes use of the following morphisms of group schemes.
-\[
-\underline{J}^{0} \longleftarrow \underline{J}^{0}_\Fq \to \underline{J}^{0,\reductive}_\Fq.
-\]
-\item[(3)] The quasicharacters $\varphi_i : \underline{J}^i(\OK) \to \CC^\times$ have not yet been geometrized.
-\item[(4)] The quotient $J^{i+1}\to V_{i+1}$ has been replaced with the following morphisms of group schemes.
-\[
-\underline{J}^{i+1} \longleftarrow \underline{J}^{i+1}_\Fq \to \underline{J}^{i+1,\reductive}_\Fq \to V_{i+1,\Fq}.
-\]
-\item[(5)] The symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$ is given by 
-\item[(6)]
-\item[(7)] The group homomorphism $\,^\circ f_i : J^0 \cdots J^i \to \Sp(V_{i+1})$ has been replaced by the following morphisms of group schemes.
-\[
-\underline{G}^{i} \longleftarrow \underline{G}^{i}_\Fq \to \underline{G}^{i,\reductive}_\Fq \to \Sp(V_{i,\Fq}),
-\]
-and $\Sp(V_{i,\Fq})$ is itself a reductive algebraic group over $\Fq$.
-\item[(8)] The quotient $J^{i+1} \to H^{i+1}$ has been replaced by the following morphisms of group schemes.
-\[
-\underline{J}^{i+1} \longleftarrow \underline{J}^{i+1}_\Fq \to H^{i+1}_\Fq.
-\] 
-\item[(9)]
-The Heisenberg group $V_{i+1}^\sharp$ is replaced by a unipotent algebraic group $V_{i+1,\Fq}^\sharp$ over $\Fq$, and the group isomorphism $H^{i+1} \iso V_{i+1}^\sharp$ is replaced by an isomorphism $H^{i+1}_\Fq \iso V_{i+1,\Fq}^\sharp$ of algebraic groups over $\Fq$.
-\item[(10)]
-
-\end{enumerate}
-
-Regarding this construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:models} concludes with the following provocative observation.
+%
+A Yu type is then a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, constructed in a certain way. 
+%
+Regarding the construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:models} concludes with the following provocative observation.
 
@@
 \end{quotation}
-%
-The objective of this section is to push this observation further by geometrizing the representation $\,^\circ \rho$ of $\underline{G}$.
+
+In Section~\ref{sec:types} we use Theorem~\ref{thm:geo} to results push this observation further by geometrizing the representation $\,^\circ \rho$ of $\,^\circ K$: we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = \,^\circ K$ and a virtual Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\,^\circ \rho)$.
+%from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius.
+
+\subsection{Review of Jacobi theory over finite fields}
+
+For use below, we recall some basic facts about the Heisenberg-Weil representation.
+
+Let $V$ be a finite-dimensional vector space over a finite field $\Fq$ equipped with a symplectic paring $\langle\ ,\ \rangle : V\times V \to C$, where $C$ is a one-dimensional vector space over $\Fq$.
+Then $V$ is even-dimensional and we may pick a `Lagrangian splitting' $V = U \oplus W$ such that $\langle v,v' \rangle = (u,w') - (u',w)$ for $v=(u,w)$ and $v'=(u',w')$.
+Let $V^\sharp$ be the Heisenberg group determined by $(C, \langle\ ,\ \rangle)$.
+Then $V^\sharp$ is a split extension of $V$ by $C$.
+\[
+\begin{tikzcd}
+\ &&& U \arrow{d} &\\
+1 \arrow{r} & C \arrow{r} & V^\sharp \arrow{r} & \arrow[bend right]{l} V \arrow[bend right]{u} \arrow[bend left]{d} \arrow{r} & 1\\
+1 \arrow{r} & \arrow[equals]{u} C \arrow{r} & \arrow[bend right]{l}  A \arrow{u} \arrow{r} & \arrow[bend right]{l}  W \arrow{u} \arrow{r} & 1 
+\end{tikzcd}
+\]
+
+Let $\psi : C \to \EEx$ be an additive character and let $\omega$ be the Heisenberg representation on $V^\sharp$ with central character $\psi : C \to \EEx$. 
+Let $\Sp(V)$ be the symplectic group determined by the symplectic pairing $\langle\ ,\ \rangle$;
+this group acts on $V^\sharp$.
+Extend $\psi$ to $\psi_A : A \to \EEx$ in the obvious way. 
+Then $\omega \ceq \operatorname{Ind}_A^{V^\sharp}(\psi_A)$ is called the Heisenberg representation of $V^\sharp$.
+
+Observe that $\Sp(V)$ acts on $V^\sharp$.
+The Heisenberg representation determines a representation $\pi_{\omega}$ of $\Sp(V)$ with the same representation space as $\omega$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\omega(g)$ determines an isomorphism of representations $\omega^g \to \omega$, through the Egorov identity \cite{Gurevich-Hadani:geometric_Weil}*{(1.3.1)}.
+Let $W = \pi_\omega \ltimes \omega$ be the representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$ given by $\omega$ and $\pi_\omega$.
+
+\subsection{Review of Yu's types}\label{ssec:review}
+
+Every Yu type $(\,^\circ K,\,^\circ \rho)$ may be constructed directly from the following information, derived from a Yu datum:
+\begin{enumerate}
+\item[(0)] a sequence of compact groups 
+\[
+\,^\circ K^0 \subseteq \,^\circ K^1 \subseteq \cdots \subseteq \,^\circ K^d= \,^\circ K;
+\]
+\item[(1)] a continuous representation $\varrho$ of $\,^\circ K^0$;
+\item[(2)] a quasicharacter $\varphi_i : \,^\circ K^i \to \CC^\times$, for $i=0, \ldots d$.
+\end{enumerate}
+The representations $(\varrho, \varphi_0, \ldots , \varphi_d)$ enjoy certain properties which allow Yu to construct representations $\,^\circ\rho_i$ of $\,^\circ K^i$, for $i=0, \ldots, d-1$, such that $\,^\circ\rho_0 = \varrho$ and $\,^\circ\rho_d = \,^\circ\rho$.
+
+Since we will need some facts about this construction, we review some further detail here.
+First, Yu introduces compact groups $J^i\subset \,^\circ K$, for $i=0, \ldots d$, such that 
+\[
+\,^\circ K^i = J^0\cdots J^{i}
+\]
+and a natural action of $\,^\circ K^i$ on $J^{i+1}$, for $i=0, \ldots d-1$, defining the groups
+\[
+\,^\circ K^i \ltimes J^{i+1}.
+\]
+He then introduces the following quotients of $J^{i+1}$ and $\,^\circ K^i$, for $i=0, \ldots d-1$.
+\begin{enumerate}
+\item[(Q.1)] A quotient $J^{i+1} \to V_{i+1}$ to a finite abelian group, the latter also given the structure of a $\Fq$-vector space.
+\end{enumerate}
+The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : C_{i+1} \to \EEx$.
+\begin{enumerate}
+\item[(Q.2)] A quotient $J^{i+1} \to V_{i+1}^\sharp$, where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $C_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$.
+\end{enumerate}
+In fact, the quotient $J^{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J^{i+1} \to H^{i+1}$ and an isomorphism $j_{i+1} : H^{i+1} \to V_{i+1}^\sharp$, where $H^{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:construction}*{}.
+\begin{enumerate}
+\item[(Q.3)] A quotient $\,^\circ f_i : \,^\circ K^i \to \Sp(V_{i+1})$, such that the pair $(f_i, j_{i+1})$ is a symplectic action of $\,^\circ K^i$ on $H^{i+1}$ in the sense of \cite{yu:construction}.
+\end{enumerate}
+Taken together, these quotients define another quotient:
+\begin{enumerate}
+\item[(Q)] A quotient $h_{i+1} : \,^\circ K^i \ltimes J^{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
+\[
+\begin{tikzcd}
+1 \arrow{r} & J^{i+1} \arrow{d} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d}{h_{i+1}} \arrow{r} & \,^\circ K^i \arrow{r} \arrow{d}{\,^\circ f_i} & 1\\ 
+1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
+\end{tikzcd}
+\]
+\end{enumerate}
+
+The representations $\,^\circ \rho_i$ are defined recursively. Set $\,^\circ \rho_0 = \varrho$.
+Suppose $i=0, \ldots, d-1$.
+The key to defining the representation $\,^\circ\rho_{i+1}$ from $\,^\circ \rho_i$ is the following diagram.
+\[
+\begin{tikzcd}
+\ && \,^\circ K^{i}\cap J^{i+1}\arrow{d} && \\
+1 \arrow{r} & J^{i+1} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d} \arrow{r} & \,^\circ K^i \arrow{r} & 1\\
+&& \,^\circ K^{i+1} &&
+\end{tikzcd}
+\]
+Let $\omega_{i+1}$ be the Heisenberg representation of the Heisenberg group $V_{i+1}^\sharp$.
+This determines a Weil representation on the same representation space as $\omega_{i+1}$.
+Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$.
+Then $h_{i+1}^*(W_{i+1})$ is a representation of $\,^\circ K^i \ltimes J^{i+1}$.
+Write $\inf(\,^\circ\rho_i \otimes \varphi_i)$ for the representation of $\,^\circ K^i \ltimes J^{i+1}$ obtained by pulling back $\,^\circ\rho_i$ along $\,^\circ K^i \ltimes J^{i+1} \to \,^\circ K^i$.
+By \cite{yu:01a}*{}, the representation 
+\[
+h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)
+\] 
+of $\,^\circ K^i \ltimes J^{i+1}$ is trivial on $\,^\circ K^{i}\cap J^{i+1}$, so $h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)$ descends to $\,^\circ K^{i+1}$.
+This defines $\,^\circ \rho_{i+1}$.\todo{I didn't use $\varphi_d$, so this can't be quite right.}
+
+%The character of $\,^\circ \rho_d$ on $\,^\circ K^d = \,^\circ K = J^0 \cdots J^d$ satisfies
+%\[
+%\trace(\,^\circ \rho)(k_0 \cdots k_d) = \varrho(k_0)  \varphi_0(k_0) \cdots \varphi_d(k_d),
+%\]
+%for $k_i\in J^i$.
+
+\subsection{Smooth models}\label{ssec:models}
+
+By \cite{yu:models}*{Prop 10.2} there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that \[ 
+\underline{G}(\OK)= \,^\circ K.
+\] 
+%
+As explained in \cite{yu:03a}*{\S 10.4}, the group scheme $\underline{G}$ comes with the following auxilliary data:
+\begin{enumerate}
+\item[(Ji)]
+	affine smooth group schemes $\underline{J}^i$, for $i=0, 1, \ldots, d$, together with morphisms $\underline{J}^i \to \underline{G}$ such that \[\underline{J}^i(\OK) = J^i,\]
+\item[(Gj)] affine smooth group schemes $\underline{G}^{j}$, for $j=0, \ldots, d$, together with morphisms $\underline{G}^{j}\to \underline{G}$ such that 
+\[
+\underline{G}^{j}(\OK) = J^0\cdots J^i.
+\] 
+\end{enumerate}
+
+\newcommand{\reductive}{{\operatorname{red}}}
+
+With these group schemes, the other groups and group homomorphisms appearing in Section~\ref{ssec:review} may be put into the framework needed for geometrization.
+
+Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
+The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $U^{i+1}_\Fq$, where $U^{i+1}_\Fq$, appears as a quotient $J^{i+1}_\Fq \to U^{i+1}_\Fq$ of algebraic groups.
+Then the quotient $J^{i+1} \to V_{i+1}$ is realized as the composition
+\[
+\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to U^{i+1}_{\Fq}(\Fq) = V_{i+1}.
+\]
+Likewise, the Heisenberg p-group $H^{i+1}$ group may be realized as a quotient of algebraic groups, and $J^{i+1}\to H^{i+1}$ as the composition 
+\[
+\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H^{i+1}.
+\]
+Finally, the group homomorphism $\,^\circ f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ may be made geometric in much the same way.
+Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $\,^\circ f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ is realized as the composition
+\[
+\underline{G}^{i}(\OK) \to \underline{G}^{i}(\Fq) = \underline{G}^{i}_\Fq(\Fq) \to  \underline{G}^{i,\reductive}_\Fq(\Fq) \to W^{i+1}_{\Fq}(\Fq) = \Sp(V_{i+1}).
+\]
+
+Let us return to the list of Section~\ref{ssec:review} and consider how we have recast each part.
+\begin{enumerate}
+\item[(0)] The compact group $\,^\circ K$ is replaced by the smooth group scheme $\underline{G}$ over $\OK$.
+\item[(1)] The compact open subgroups $J^i \hookrightarrow \,^\circ K$ are replaced by the morphisms $\underline{J}^i \to \underline{G}$ of smooth group schemes over $\OK$.
+\item[(2)] The representation $\varpi_0$ is obtained by pullback from a representation $\sigma_0$ of $\underline{J}^{0,\reductive}_\Fq$, which makes use of the following morphisms of group schemes.
+\[
+\underline{J}^{0} \longleftarrow \underline{J}^{0}_\Fq \to \underline{J}^{0,\reductive}_\Fq.
+\]
+\item[(3)] The quasicharacters $\varphi_i : \underline{J}^i(\OK) \to \CC^\times$ have not yet been geometrized.
+\item[(4)] The quotient $J^{i+1}\to V_{i+1}$ has been replaced with the following morphisms of group schemes.
+\[
+\underline{J}^{i+1} \longleftarrow \underline{J}^{i+1}_\Fq \to \underline{J}^{i+1,\reductive}_\Fq \to V_{i+1,\Fq}.
+\]
+\item[(5)] The symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$ is given by 
+\item[(6)]
+\item[(7)] The group homomorphism $\,^\circ f_i : J^0 \cdots J^i \to \Sp(V_{i+1})$ has been replaced by the following morphisms of group schemes.
+\[
+\underline{G}^{i} \longleftarrow \underline{G}^{i}_\Fq \to \underline{G}^{i,\reductive}_\Fq \to \Sp(V_{i,\Fq}),
+\]
+and $\Sp(V_{i,\Fq})$ is itself a reductive algebraic group over $\Fq$.
+\item[(8)] The quotient $J^{i+1} \to H^{i+1}$ has been replaced by the following morphisms of group schemes.
+\[
+\underline{J}^{i+1} \longleftarrow \underline{J}^{i+1}_\Fq \to H^{i+1}_\Fq.
+\] 
+\item[(9)]
+The Heisenberg group $V_{i+1}^\sharp$ is replaced by a unipotent algebraic group $V_{i+1,\Fq}^\sharp$ over $\Fq$, and the group isomorphism $H^{i+1} \iso V_{i+1}^\sharp$ is replaced by an isomorphism $H^{i+1}_\Fq \iso V_{i+1,\Fq}^\sharp$ of algebraic groups over $\Fq$.
+\item[(10)]
+
+\end{enumerate}
+
+\subsection{Geometrization of the character of the Heisenberg-Weil representation}
+
+\begin{lemma}[Claim, actually]
+For $V$, $C$, $\langle\, , \ \rangle$ and $\psi$ as above, there is a virtual constructible equivariant Weil sheaf $\cs{T}$ on the algebraic group $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\cs{T}} = \trace(\tau)$.
+\end{lemma}
+
+\begin{proof}
+First, find a geometrization of $\omega$ which is equivariant for the action of $\Sp(V)$ on $V^\sharp$: a virtual constructible equivariant Weil sheaf $\cs{H}$ on $V^\sharp$ equipped with an isomorphism $m^*\cs{H} \to p^* \cs{H}$ such that ...
+Do this by induction: $\operatorname{ind}_{A}^{V^\sharp}(\cs{L}_\psi)$, where $A$ .
+.
+.
+.
+\end{proof}
 
 \subsection{Geometrization}\label{ssec:geometrization}
-
-\begin{proposition}
-Let $(V, \langle\ , \rangle, C, \psi)$ be a finite-dimensional vector space over $\Fq$ and . .  .
-Let $V^\sharp$ be the geometric Heisenberg group determined by this and let $\omega$ be the Heisenberg representation of $V^\sharp$.
-Let $W$ be the Weil representation of $\Sp(V)$ determined by $(\omega,V^\sharp)$. 
-Let $W\ltimes \omega$ be the resulting representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$.
-Then there is a virtual $W\ltimes \omega$-equivariant constructible sheaf $\mathcal{W}$ on $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\mathcal{W}} = \trace(W\ltimes \omega)$.
-\end{proposition}
-
-%\begin{proof}
-%We begin by geometrizing the Heisenberg representation $(\omega, V^\sharp)$ to $\mathcal{H}$.
-%\end{proof}
 

### 2016-01-05 followup.tex
Improvements to the review on types. Introduction of smooth models.

@@
 \begin{enumerate}
-\item[(Q.3)] A quotient $\,^\circ f_i : \,^\circ K^i \to \Sp(V_{i+1})$, such that the pair $(f_i, j_{i+1})$ is a symplectic action of $\,^\circ K^i$ on $H^{i+1}$ in the sense of \cite{yu:construction}.
+\item[(Q.3)] A quotient $\,^\circ f_{i+1} : \,^\circ K^i \to \Sp(V_{i+1})$, such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $\,^\circ K^i$ on $H^{i+1}$ in the sense of \cite{yu:construction}.
 \end{enumerate}
@@
 \]
-Let $\omega_{i+1}$ be the Heisenberg representation of the Heisenberg group $V_{i+1}^\sharp$.
-This determines a Weil representation on the same representation space as $\omega_{i+1}$.
-Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$.
-Then $h_{i+1}^*(W_{i+1})$ is a representation of $\,^\circ K^i \ltimes J^{i+1}$.
+Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
+Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $\,^\circ K^i \ltimes J^{i+1}$.
 Write $\inf(\,^\circ\rho_i \otimes \varphi_i)$ for the representation of $\,^\circ K^i \ltimes J^{i+1}$ obtained by pulling back $\,^\circ\rho_i$ along $\,^\circ K^i \ltimes J^{i+1} \to \,^\circ K^i$.
@@
 
-By \cite{yu:models}*{Prop 10.2} there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that \[ 
-\underline{G}(\OK)= \,^\circ K.
-\] 
+By \cite{yu:models}*{Prop 10.2} there is a sequence of morphisms of affine smooth group schemes of finite type over $\OK$
+\[
+\underline{G}^0 \to \underline{G}^1 \to \cdots \to \underline{G}^d = \underline{G}
+\]
+such that $\underline{G}^i(\OK) = \,^\circ K^i$ for $i=0,\ldots d$.
+Also, for each $i=0,\ldots d$, there is morphism of affine smooth group schemes of finite type over $\OK$ 
+\[
+\underline{J}^i \to \underline{G}
+\] 
+such that $\underline{J}^i(\OK) = J^i$ as a subgroup of $\,^\circ K$.
+
 %

### 2016-01-06 followup.tex
Working on symmetric classes

--- 2015-12-01 followup.tex
@@
 
-\title[Commutative Character Sheaves]{Commutative Character Sheaves on smooth group schemes over finite fields}
+\title[Commutative Character Sheaves]{Commutative Character Sheaves}
 %with an application to geometric types for supercuspidal representations
@@
 
-If $M$ is a $\bG$-module, then we say a class in the Galois cohomology group $\Hh^2(\bG, M)$
-is \emph{symmetric} if it is represented by a symmetric $2$-cocycle.  Since every coboundary is symmetric,
-either all cocycles in a given class will be symmetric or none will.  The connection between
-commutative character sheaves and symmetric classes is given in the following lemma.
-\todo{Define symmetric for element of $\Hh^2(E_G^\bullet)$.}
+Let $a \in Z^2(\bG, \EEx)$ correspond to $\alpha$.  We say that $[\alpha \oplus \beta] \in \Hh^2(E_G^\bullet)$
+is \emph{symmetric} if $a(x,y) = a(y,x)$ for all $x,y \in \bG$.  This condition is well defined, since every
+coboundary in $B^2(\bG, \EEx)$ is symmetric.  The connection between commutative character sheaves
+and symmetric classes is given in the following lemma.
 
@@
 
+We may similarly define a symmetric class in $\Hh^2(\bG, \EEx)$ to be one represented by a symmetric $2$-cocycle.
+The following lemma will allow us to show that there are no invisible commutative character sheaves.
+
 \begin{lemma} \label{lem:symtriv}
@@
 
-Suppose that $\cs{L}$ is a commutative character sheaf
-with $\trFrob{\cs{L}} = 1$.  Then $S_G([\cs{L}])$ is in the image of $\Hh^2(\bG, \EEx)^\Weil{}$, so is cohomologous to
+Suppose that $\cs{L}$ is a commutative character sheaf with $\trFrob{\cs{L}} = 1$, and set $[\alpha, \beta] = S_G([\cs{L}])$.
+Then $S_G([\cs{L}])$ is in the image of $\Hh^2(\bG, \EEx)^\Weil{}$, so is cohomologous to
 $[\alpha', 0]$.  Since $\alpha$ is symmetric and coboundaries are symmetric, $\alpha'$ is symmetric as well.
@@
 Let us refer to the types arising in this manner as {\it Yu types}.
-In this section we show that every Yu type is geometrizable.
-% in a sense which will be made clear below.
+In this section we show that every Yu type is geometrizable, in a sense which will be made clear below.
 
 A Yu type is a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, with certain properties. 
-In Section~\ref{ssec:review} we recall properties of $(\,^\circ K,\,^\circ \rho)$ which we allow us, in Section~\ref{ssec:geometrization}, to find a pair $(G, \mathcal{F})$ where $G$ is a group scheme over $\Fq$ and $\mathcal{F}$ is a virtual constructible sheaf $\ell$-adic sheaf on $G$ from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius.
+In Section~\ref{ssec:review} we recall properties of $(\,^\circ K,\,^\circ \rho)$ which we allow us, in Section~\ref{ssec:geometrization}, to find a pair $(G, \mathcal{F})$ where $G$ is a smooth group scheme over $\Fq$ and $\mathcal{F}$ is a virtual constructible sheaf $\ell$-adic sheaf on $G$ from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius.
 
@@
 \begin{enumerate}
-\item[(0)] a compact group $\,^\circ K$;
-\item[(1)] compact open subgroups $J^i\subset \,^\circ K$, for $i=0, \ldots d$, such that \[\,^\circ K = J^0\cdots J^d;\]
-\item[(2)] a continuous representation $\varpi_0$ of $J^0$, inflated from ...
-\item[(3)] a quasicharacter $\varphi_i : J^0\cdots J^i \to \CC^\times$, for $i=0, \ldots d$.
+\item compact open subgroups $J^i\subset \,^\circ K$, for $i=0, \ldots d$, such that \[\,^\circ K = J^0\cdots J^d;\]
+\item a continuous representation $\sigma_0$ of $J^0$;
+\item a quasicharacter $\varphi_i : J^i \to \CC^\times$, for $i=0, \ldots d$.
 \end{enumerate}
@@
 \begin{enumerate}
-\item[(4)] a quotient $J^{i+1} \to V_{i+1}$ to a finite abelian group, and the structure of a $\Fq$-vector space on $V_{i+1}$, compatible with the abelian group structure above;
-\item[(5)] a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$;
-\item[(6)] an additive character $\psi_{i+1} : C_{i+1} \to \EEx$;
-\item[(7)] a group homomorphism $\,^\circ f_i : J^0 \cdots J^i \to \Sp(V_{i+1})$;
-\item[(8)] a quotient $J^{i+1} \to H^{i+1}$, where $H^{i+1}$ is a Heisenberg $p$-group;
-\item[(9)] an isomorphism $j_{i+1} : H^{i+1} \to V_{i+1}^\sharp$, where $V_{i+1}^\sharp$ is the Heisenberg group determined by $(V_{i+1}, \langle\ ,\ \rangle_{i+1}, C_{i+1}, \psi_{i+1})$.
-%\end{enumerate}
-\item[(10)]The pair $(f_i, j_{i+1})$ is a symplectic action of $J^0\cdots J^i$ on $H^{i+1}$ in the sense of \cite{yu:construction}, so, together with the quotient $J^{i+1} \to H^{i+1}$, it defines a group homomorphism
+\item a quotient $J^{i+1} \to V_{i+1}$ to a finite abelian group, and the structure of a $\Fq$-vector space on $V_{i+1}$, compatible with the abelian group structure above;
+\item a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$;
+\item an additive character $\psi_{i+1} : C_{i+1} \to \EEx$;
+\item a group homomorphism $\,^\circ f_i : J^0 \cdots J^i \to \Sp(V_{i+1})$;
+\item a quotient $J^{i+1} \to H^{i+1}$, where $H^{i+1}$ is a Heisenberg $p$-group, together with an isomorphism $j_{i+1} : H^{i+1} \to V_{i+1}^\sharp$, where $V_{i+1}^\sharp$ is the Heisenberg group determined by $(V_{i+1}, \langle\ ,\ \rangle_{i+1}, C_{i+1}, \psi_{i+1})$.
+\end{enumerate}
+The pair $(f_i, j_{i+1})$ is a symplectic action of $J^0\cdots J^i$ on $H^{i+1}$, so it defines a group homomorphism 
 \begin{equation}\label{eq:symaction}
 \begin{tikzcd}
-h_{i+1} : (J^0\cdots J^i)\ltimes J^{i+1} \arrow{r} 
-%& (J^0\cdots J^i)\ltimes H^{i+1} \arrow{r} 
-& \Sp(V_{i+1})\ltimes V_{i+1}^\sharp.
+h_{i+1} : (J^0\cdots J^i)\ltimes J^{i+1} \arrow{r} & (J^0\cdots J^i)\ltimes H^{i+1} \arrow{r} & \Sp(V_{i+1})\ltimes V_{i+1}^\sharp.
 \end{tikzcd}
 \end{equation}
-\end{enumerate}
-
-From this information, Yu constructs 
-a representation $\,^\circ \rho_i$ of $J^0\cdots J^i$, for each $i=0, \ldots, d$, such that $\,^\circ \rho_d = \,^\circ \rho$,
-constructed as follows.
-%\end{enumerate}
-%We will need some more detail about the construction of the representations $\,^\circ \rho^i$, so we review it below.
-%
-We will need some detail about this construction,   so we review it here.
-
+%
+
+From this information, Yu constructs a representation $\,^\circ \rho_i$ of $J^0\cdots J^i$, for each $i=0, \ldots, d$, such that $\,^\circ \rho_d = \,^\circ \rho$.
+We will need some detail about this construction, so we will review it here.
 %Let $\varpi_1$ be the Heisenberg representation of the Heisenberg group $V_1^\sharp$, with central character $\psi_1$.
 %Let $\varrho_1$ be the Weil representation of $\Sp(V_1)$ with the same representation space as $\omega_1$.
-Let $\omega_{i+1}$ be the Heisenberg representation of the Heisenberg group $V_{i+1}^\sharp$.
-This determines the Weil representation $W_{i+1}$ on the same representation space as the Heisenberg representation of $V_{i+1}^\sharp$.
-Let $W_{i+1} \ltimes \omega_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$.
+Let $\omega_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, with the same representation space as the Heisenberg representation of the Heisenberg group $V_{i+1}^\sharp$.
 \[
@@
 \  & J^{i+1} \arrow{d} & \\
-\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp & \arrow{l}[swap]{h_{i+1}} (J^0 \cdots J^i) \ltimes J^{i+1} \arrow{r} \arrow{d} & J^0 \cdots J^i J^{i+1}\\
-& J^0 \cdots J^i & 
-\end{tikzcd}
-\]
-
-Now $h_1^*(W_1\ltimes \omega_1)$ is a representation of $J^0\ltimes J^1$, determined by the quasicharacter $\varphi_1$ of $J^1$. 
-Write $\inf(\sigma_0)$ for the representation of $J^0 \ltimes J^1$ obtained by pulling back $\sigma_0$ along $J^0 \ltimes J^1 \to J^0$. 
+Sp(V_{i+1}) \ltimes V_{i+1}^\sharp & \arrow{l}[swap]{h_1} (J^0 \cdots J^i) \ltimes J^{i+1} \arrow{r} \arrow{d} & J^0 \cdots J^i J^{i+1}\\
+& (J^0 \cdots J^i) & 
+\end{tikzcd}
+\]
+Then $h_1^*(\omega_1)$ is a representation of $J^0\ltimes J^1$, determined by the quasicharacter $\varphi_1$ of $J^1$. 
+Write $\inf(\sigma_0\otimes \varphi_0)$ for the representation of $J^0 \ltimes J^1$ obtained by pulling back $\sigma_0\otimes \varphi_0$ along $J^0 \ltimes J^1 \to J^0$. 
 By \cite{yu:01a}*{}, the representation 
-$h_1^*(\omega_1) \otimes \varphi_1 \otimes \inf(\sigma_0)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 \ltimes 1) \cap (1 \ltimes J^1)$, so $h_1^*(\omega_1) \otimes \varphi_2 \otimes\inf(\sigma_0\otimes)$ descends to a representation $\,^\circ \rho_1$ of $J^0 J^1$.
-%
-Likewise, the representation 
+$h_1^*(\omega_1) \otimes \inf(\sigma_0\otimes \varphi_0)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 \ltimes 1) \cap (1 \ltimes J^1)$, so $h_1^*(\omega_1) \otimes \inf(\sigma_0\otimes \varphi_0)$ descends to a representation $\,^\circ \rho_1$ of $J^0 J^1$.
+%
+As above, the representation 
 $h_{2}^*(\omega_{2}) \otimes \inf(\,^\circ \rho_1)$ of $J^0 \ltimes J^1$ is trivial on $(J^0 J^1 \ltimes 1) \cap (1 \ltimes J^2)$, so $h_2^*(\omega_2) \otimes \inf(\,^\circ \rho_1)$ descends to a representation $\,^\circ \rho_2$ of $J^0 J^1 J^2$.
-%
 Continuing in this way, one constructs the representation $\,^\circ \rho_d$ of $J^0\cdots J^d$.
-%
-The character of $\,^\circ \rho_d$ on $\,^\circ K = J^0\cdots J^d$ satisfies
+
+The character of $\,^\circ \rho_d$ on $J^0\cdots J^d$ satisfies
 \[
@@
 \]
-for $k_i\in J^i$.
+with ...
 
@@
 
-By \cite{yu:models}*{Prop 10.2} there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that \[ 
-\underline{G}(\OK)= \,^\circ K.
-\] 
-%
-As explained in \cite{yu:03a}*{\S 10.4}, the group scheme $\underline{G}$ comes with the following auxilliary data:
+The first step in the geometrization of the type $(\,^\circ K,\,^\circ \rho)$ is to replace $\,^\circ K$ with a group scheme $G$ over $\Fq$ so that $G(\Fq) = \,^\circ K$, canonically. 
+By \cite{yu:03a}*{Prop 10.2} there is a canonical affine smooth group scheme $\underline{G}$ of finite type over $\OK$ such that \[\underline{G}(\OK)= \,^\circ K\] 
+For every positive integer $n$, let $G_n$ be the Greenberg transform of $\underline{G} \times_{\Spec{\OK}} \Spec{\OK/\mathfrak{m}_K^n}$, where $\mathfrak{m}_K$ is the maximal ideal in $\OK$.
+Then $G_n$ is a smooth group scheme over $\Fq$ and $G_n(\Fq) = \underline{G}(\OK/\mathfrak{m}_K^n)$, canonically.
+Let $G$ be the Greenberg transform of $\underline{G}$.
+Then $G$ is a group scheme over $\Fq$ and $G(\Fq) = \underline{G}(\OK) = \,^\circ K$, canonically.
+
+In order to complete the geometrization of the type $(\,^\circ K,\,^\circ \rho)$, we will need more smooth models.
+Fortunately, as above, Yu has already done the heavy work.
+%
+As explained in \cite{yu:03a}*{\S 10.4}, the
+the group scheme $\underline{G}$ comes with the following auxillary data:
 \begin{enumerate}
@@
 
-\newcommand{\reductive}{{\operatorname{red}}}
-
-With these group schemes, the other groups and group homomorphisms appearing in Section~\ref{ssec:review} may be put into the framework needed for geometrization.
-
-Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
-The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $U^{i+1}_\Fq$, where $U^{i+1}_\Fq$, appears as a quotient $J^{i+1}_\Fq \to U^{i+1}_\Fq$ of algebraic groups.
-Then the quotient $J^{i+1} \to V_{i+1}$ is realized as the composition
-\[
-\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to U^{i+1}_{\Fq}(\Fq) = V_{i+1}.
-\]
-Likewise, the Heisenberg p-group $H^{i+1}$ group may be realized as a quotient of algebraic groups, and $J^{i+1}\to H^{i+1}$ as the composition 
-\[
-\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H^{i+1}.
-\]
-Finally, the group homomorphism $\,^\circ f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ may be made geometric in much the same way.
-Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $\,^\circ f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ is realized as the composition
-\[
-\underline{G}^{i}(\OK) \to \underline{G}^{i}(\Fq) = \underline{G}^{i}_\Fq(\Fq) \to  \underline{G}^{i,\reductive}_\Fq(\Fq) \to W^{i+1}_{\Fq}(\Fq) = \Sp(V_{i+1}).
-\]
-
-Let us return to the list of Section~\ref{ssec:review} and consider how we have recast each part.
-\begin{enumerate}
-\item[(0)] The compact group $\,^\circ K$ is replaced by the smooth group scheme $\underline{G}$ over $\OK$.
-\item[(1)] The compact open subgroups $J^i \hookrightarrow \,^\circ K$ are replaced by the morphisms $\underline{J}^i \to \underline{G}$ of smooth group schemes over $\OK$.
-\item[(2)] The representation $\varpi_0$ is obtained by pullback from a representation $\sigma_0$ of $\underline{J}^{0,\reductive}_\Fq$, which makes use of the following morphisms of group schemes.
-\[
-\underline{J}^{0} \longleftarrow \underline{J}^{0}_\Fq \to \underline{J}^{0,\reductive}_\Fq.
-\]
-\item[(3)] The quasicharacters $\varphi_i : \underline{J}^i(\OK) \to \CC^\times$ have not yet been geometrized.
-\item[(4)] The quotient $J^{i+1}\to V_{i+1}$ has been replaced with the following morphisms of group schemes.
-\[
-\underline{J}^{i+1} \longleftarrow \underline{J}^{i+1}_\Fq \to \underline{J}^{i+1,\reductive}_\Fq \to V_{i+1,\Fq}.
-\]
-\item[(5)] The symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$ is given by 
-\item[(6)]
-\item[(7)] The group homomorphism $\,^\circ f_i : J^0 \cdots J^i \to \Sp(V_{i+1})$ has been replaced by the following morphisms of group schemes.
-\[
-\underline{G}^{i} \longleftarrow \underline{G}^{i}_\Fq \to \underline{G}^{i,\reductive}_\Fq \to \Sp(V_{i,\Fq}),
-\]
-and $\Sp(V_{i,\Fq})$ is itself a reductive algebraic group over $\Fq$.
-\item[(8)] The quotient $J^{i+1} \to H^{i+1}$ has been replaced by the following morphisms of group schemes.
-\[
-\underline{J}^{i+1} \longleftarrow \underline{J}^{i+1}_\Fq \to H^{i+1}_\Fq.
-\] 
-\item[(9)]
-The Heisenberg group $V_{i+1}^\sharp$ is replaced by a unipotent algebraic group $V_{i+1,\Fq}^\sharp$ over $\Fq$, and the group isomorphism $H^{i+1} \iso V_{i+1}^\sharp$ is replaced by an isomorphism $H^{i+1}_\Fq \iso V_{i+1,\Fq}^\sharp$ of algebraic groups over $\Fq$.
-\item[(10)]
-
-\end{enumerate}
-
-Regarding this construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:models} concludes with the following provocative observation.
-
+Moreover, the quotient
+
+Regarding this construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:03a} concludes with the following provocative observation.
 \begin{quotation}
@@
 \subsection{Geometrization}\label{ssec:geometrization}
-
-\begin{proposition}
-Let $(V, \langle\ , \rangle, C, \psi)$ be a finite-dimensional vector space over $\Fq$ and . .  .
-Let $V^\sharp$ be the geometric Heisenberg group determined by this and let $\omega$ be the Heisenberg representation of $V^\sharp$.
-Let $W$ be the Weil representation of $\Sp(V)$ determined by $(\omega,V^\sharp)$. 
-Let $W\ltimes \omega$ be the resulting representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$.
-Then there is a virtual $W\ltimes \omega$-equivariant constructible sheaf $\mathcal{W}$ on $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\mathcal{W}} = \trace(W\ltimes \omega)$.
-\end{proposition}
-
-%\begin{proof}
-%We begin by geometrizing the Heisenberg representation $(\omega, V^\sharp)$ to $\mathcal{H}$.
-%\end{proof}
-
-The first step in the geometrization of the type $(\,^\circ K,\,^\circ \rho)$ is to replace $\,^\circ K$ with a group scheme $G$ over $\Fq$ so that $G(\Fq) = \,^\circ K$, canonically. 
-Set $S = \Spec{\OK}$ and $S_n = \Spec{\OK/\mathfrak{m}^n}$, where $\mathfrak{m}_K$ is the maximal ideal in $\OK$, and $n$ is a positive integer $n$.
-Let $G_n$ be the Greenberg transform of $\underline{G} \times_{S} S_n$.
-Then $G_n$ is a smooth group scheme over $\Fq$ and 
-\[
-G_n(\Fq) = \underline{G}(\OK/\mathfrak{m}_K^n),
-\]
-canonically.
-%
-Let $G$ be the Greenberg transform of $\underline{G}$.
-Then $G$ is a group scheme over $\Fq$ and 
-\[
-G(\Fq) = \,^\circ K,
-\]
-canonically.
 

### 2016-01-13 followup.tex
Rewrote the section on smooth models as a step toward geometrization of types.

--- 2016-01-05 followup.tex
@@
 %
-Regarding the construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:models} concludes with the following provocative observation.
-
-\begin{quotation}
-{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
- the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
-These results suggest that algebraic geometry and group schemes should play an
-important role in the representation theory of $p$-adic groups.} \cite{yu:03a}
-\end{quotation}
-
-In Section~\ref{sec:types} we use Theorem~\ref{thm:geo} to results push this observation further by geometrizing the representation $\,^\circ \rho$ of $\,^\circ K$: we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = \,^\circ K$ and a virtual Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\,^\circ \rho)$.
+In this section we use Theorem~\ref{thm:geo} to geometrize the representation $\,^\circ \rho$ of $\,^\circ K$: we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = \,^\circ K$ and a virtual Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\,^\circ \rho)$.
 %from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius.
@@
 
-By \cite{yu:models}*{Prop 10.2} there is a sequence of morphisms of affine smooth group schemes of finite type over $\OK$
+\begin{enumerate}
+\item[(K)]
+By \cite{yu:models}*{Prop 10.2} there is a sequence  
 \[
@@
 \]
-such that $\underline{G}^i(\OK) = \,^\circ K^i$ for $i=0,\ldots d$.
-Also, for each $i=0,\ldots d$, there is morphism of affine smooth group schemes of finite type over $\OK$ 
+of morphisms of affine smooth group schemes of finite type over $\OK$ such that, on $\OK$-points it gives the sequence $\,^\circ K^0 \subseteq \,^\circ K^1 \subseteq \cdots \subseteq \,^\circ K^d= \,^\circ K$ above.
+\item[(J)]
+As explained in \cite{yu:03a}*{\S 10.4}, for each $i=0,\ldots d$, there is morphism of affine smooth group schemes of finite type over $\OK$ 
 \[
@@
 \] 
-such that $\underline{J}^i(\OK) = J^i$ as a subgroup of $\,^\circ K$.
-
-%
-As explained in \cite{yu:03a}*{\S 10.4}, the group scheme $\underline{G}$ comes with the following auxilliary data:
-\begin{enumerate}
-\item[(Ji)]
-	affine smooth group schemes $\underline{J}^i$, for $i=0, 1, \ldots, d$, together with morphisms $\underline{J}^i \to \underline{G}$ such that \[\underline{J}^i(\OK) = J^i,\]
-\item[(Gj)] affine smooth group schemes $\underline{G}^{j}$, for $j=0, \ldots, d$, together with morphisms $\underline{G}^{j}\to \underline{G}$ such that 
-\[
-\underline{G}^{j}(\OK) = J^0\cdots J^i.
+such that $\underline{J}^i(\OK) = J^i$ as a subgroup of $\,^\circ K$ and such that the image of the $\OK$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $\,^\circ K^i$, for $i=0, \ldots , d$.
+\item[(S)]
+There is a natural action of $\underline{G}^i$ on $\underline{J}^{i+1}$ in the category of smooth affine group schemes over $\OK$ so that the group
+\[
+\underline{G}^i \ltimes \underline{J}^{i+1}
+\]
+has $\OK$-points
+\[
+(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK) = \,^\circ K^i \ltimes J^{i+1}.
 \]
@@
 \newcommand{\reductive}{{\operatorname{red}}}
-
-With these group schemes, the other groups and group homomorphisms appearing in Section~\ref{ssec:review} may be put into the framework needed for geometrization.
 
@@
 
-Let us return to the list of Section~\ref{ssec:review} and consider how we have recast each part.
+With all this, we may revisit the quotients appearing in Section~\ref{ssec:review}:
+\[
+\begin{tikzcd}
+1 \arrow{r} & \underline{J}^{i+1}  \arrow{r} & \underline{G}^i \ltimes \underline{J}^{i+1} \arrow{r} & \underline{G}^i \arrow{r}  & 1\\
+1 \arrow{r} & \underline{J}^{i+1}_\Fq \arrow{d} \arrow{u} \arrow{r} & \underline{G}_\Fq^i \ltimes \underline{J}_\Fq^{i+1} \arrow{d} \arrow{u} \arrow{r} & \underline{G}_\Fq^i \arrow{r} \arrow{d} \arrow{u} & 1\\
+1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1,
+\end{tikzcd}
+\]
+where the last two rows are now understood as forming a diagram in the category of algebraic groups over $\Fq$. 
+This realizes the Jacobi group $\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp$ as a quotient of the special fibre of the smooth group scheme $\underline{G}^i \ltimes \underline{J}^{i+1}$ over $\OK$.
+
+We may now revisit the ingredients in the construction of the representation $\,^\circ \rho$ of $\underline{G}(\OK)$ along the lines indicated by Yu and recalled at the beginning of this section.
 \begin{enumerate}
-\item[(0)] The compact group $\,^\circ K$ is replaced by the smooth group scheme $\underline{G}$ over $\OK$.
-\item[(1)] The compact open subgroups $J^i \hookrightarrow \,^\circ K$ are replaced by the morphisms $\underline{J}^i \to \underline{G}$ of smooth group schemes over $\OK$.
-\item[(2)] The representation $\varpi_0$ is obtained by pullback from a representation $\sigma_0$ of $\underline{J}^{0,\reductive}_\Fq$, which makes use of the following morphisms of group schemes.
-\[
-\underline{J}^{0} \longleftarrow \underline{J}^{0}_\Fq \to \underline{J}^{0,\reductive}_\Fq.
-\]
-\item[(3)] The quasicharacters $\varphi_i : \underline{J}^i(\OK) \to \CC^\times$ have not yet been geometrized.
-\item[(4)] The quotient $J^{i+1}\to V_{i+1}$ has been replaced with the following morphisms of group schemes.
-\[
-\underline{J}^{i+1} \longleftarrow \underline{J}^{i+1}_\Fq \to \underline{J}^{i+1,\reductive}_\Fq \to V_{i+1,\Fq}.
-\]
-\item[(5)] The symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$ is given by 
-\item[(6)]
-\item[(7)] The group homomorphism $\,^\circ f_i : J^0 \cdots J^i \to \Sp(V_{i+1})$ has been replaced by the following morphisms of group schemes.
-\[
-\underline{G}^{i} \longleftarrow \underline{G}^{i}_\Fq \to \underline{G}^{i,\reductive}_\Fq \to \Sp(V_{i,\Fq}),
-\]
-and $\Sp(V_{i,\Fq})$ is itself a reductive algebraic group over $\Fq$.
-\item[(8)] The quotient $J^{i+1} \to H^{i+1}$ has been replaced by the following morphisms of group schemes.
-\[
-\underline{J}^{i+1} \longleftarrow \underline{J}^{i+1}_\Fq \to H^{i+1}_\Fq.
-\] 
-\item[(9)]
-The Heisenberg group $V_{i+1}^\sharp$ is replaced by a unipotent algebraic group $V_{i+1,\Fq}^\sharp$ over $\Fq$, and the group isomorphism $H^{i+1} \iso V_{i+1}^\sharp$ is replaced by an isomorphism $H^{i+1}_\Fq \iso V_{i+1,\Fq}^\sharp$ of algebraic groups over $\Fq$.
-\item[(10)]
-
+\item The continuous representation $\varrho$ of $\,^\circ K^0$ is a representation of $\underline{G}^0(\OK)$ obtained by inflation along $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$. 
+Let $\sigma$ be that representation of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
+In fact, $\sigma$ is itself obtained by pulling back a representation $\sigma^0$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+\item Quasicharacters $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$, for $i=0, \ldots d$.
+\item The representation $h_{i+1}^*(W_{i+1})$ of $(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK)$ is obtained by pulling back a representation along 
+\[
+(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK) \to (\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq).
+\]
+Let $w_{i+1}$ be that representation of $(\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq) = (\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq)(\Fq)$. 
+Then $w_{i+1}$ is itself obtained by pulling back the representation $W_{i+1}$ along the $\Fq$-points of the quotient
+\[
+\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq \to 
+\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp.
+\]
 \end{enumerate}
-
-\subsection{Geometrization of the character of the Heisenberg-Weil representation}
+Regarding the construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:models} concludes with the following provocative observation, which we have just revisited.
+\begin{quotation}
+{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
+ the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
+These results suggest that algebraic geometry and group schemes should play an
+important role in the representation theory of $p$-adic groups.} \cite{yu:03a}
+\end{quotation}
+
+\subsection{Geometrization of characters of the ingredient representations}
+
+\todo{Everything below here is under construction}
+Recall that $\sigma^0$ is a representation of $(\underline{G}^0)_\Fq^\reductive$.
+Suppose $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
+Let $A^0$ be a Weil sheaf on $(\underline{G}^0)_\Fq^\reductive$ such that, as a sheaf on $(\underline{G}^0)_\Fq^\reductive \otimes \bFq$, it is a character sheaf.
+The existence of $A^0$ follows from \cite{Lusztig:CSDG}*{}.
+Let $A$ be the Weil sheaf on $\underline{G}^0_\Fq$ obtained by pullback along $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+
+Let $n$ be an integer greater than the supremum of the depths of $\varphi_i : \underline{G}^i(\OK)\to \CC^\times$, for $i=0,\ldots, d$.
+Then, for $i=0,\ldots, d$ we have the commuting diagram 
+\[
+\begin{tikzcd}
+\end{tikzcd}
+\]
 
@@
 \end{proof}
+
+\begin{lemma}
+Let $\underline{G}$ be a smooth group scheme over $\OK$.
+Let $\varphi : \underline{G}(\OK) \to \CC^\times$ be a quasicharacter/continuous linear character. 
+The there is a Weil sheaf $\cs{F}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{F}} = \trace \varphi$.
+\end{lemma}
 

### 2016-01-13 followup.tex
Moved the lemma on geometrization of linear characters to its own section, at the beginning of the Applications.
Work on geometrization. Going home now.

@@
 
+\subsection{Geometrization of quasicharacters of smooth group schemes over $p$-adic fields}
+
+%We begin with the case of continuous linear characters.
+
+Set $S = \Spec{\OK}$ and $S_n = \Spec{\OK/\mathfrak{m}^n}$, where $\mathfrak{m}_K$ is the maximal ideal in $\OK$, and $n$ is a positive integer $n$.
+Let $\underline{G}$ be a smooth group scheme over $\OK$.
+Let $G_n$ be the Greenberg transform of $\underline{G} \times_{S} S_n$.
+Then $G_n$ is a smooth group scheme over $\Fq$ and 
+\[
+G_n(\Fq) = \underline{G}(\OK/\mathfrak{m}_K^n),
+\]
+canonically.
+%
+Let $G$ be the Greenberg transform of $\underline{G}$.
+Then $G$ is a group scheme over $\Fq$ and 
+\[
+G(\Fq) = \underline{G}(\OK)
+\]
+canonically.
+
+\begin{proposition}\label{prop:quasicharacters}
+Let $\underline{G}$ be a smooth group scheme over $\OK$.
+Let $\chi : \underline{G}(\OK) \to \CC^\times$ be a quasicharacter/continuous linear character. 
+The there is a Weil sheaf $\cs{F}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{F}} = \trace \chi$.
+\end{proposition}
+
+\begin{proof}
+\end{proof}
+
 \subsection{Review of Jacobi theory over finite fields}
 
-For use below, we recall some basic facts about the Heisenberg-Weil representation.
+For use in the next section, we recall some basic facts about the Heisenberg-Weil representation.
 
@@
 \item The continuous representation $\varrho$ of $\,^\circ K^0$ is a representation of $\underline{G}^0(\OK)$ obtained by inflation along $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$. 
-Let $\sigma$ be that representation of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
-In fact, $\sigma$ is itself obtained by pulling back a representation $\sigma^0$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+Let $\tau$ be that representation of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
+In fact, $\tau$ is itself obtained by pulling back a representation $\sigma$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
 \item Quasicharacters $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$, for $i=0, \ldots d$.
@@
 
-\subsection{Geometrization of characters of the ingredient representations}
+In fact, Yu's description of how to assemble $\,^\circ \rho$ from $(\varrho, \varphi_0, \ldots , \varphi_d)$ is slightly different, but equivalent, to what we have done here \cite{Yu:models}*{}.
+
+\subsection{Geometrization of characters of types}\label{ssec:geometrization}
 
 \todo{Everything below here is under construction}
-Recall that $\sigma^0$ is a representation of $(\underline{G}^0)_\Fq^\reductive$.
+Recall from Section~\ref{ssec:models} that the ingredient representations in the construction of any Yu type are:
+\begin{enumerate}
+\item A representation $\sigma$ of the $\Fq$-points of the reductive group $(\underline{G}^0)_\Fq^\reductive$ over $\Fq$. 
+Then $\tau$ is the representation of the $\Fq$-points of the special fibre of the smooth model $\underline{G}^0$ over $\OK$ and the representation $\varrho$ of $\underline{G}(\OK)$ is produced from $\tau$ by inflation.
+\item For $i=0, \ldots, d$, a quasicharacter (continuous linear character) $\varphi_i$ of $\underline{G}^i(\OK)$. 
+\item For $i=0, \ldots, d-1$, a representation $W_{i+1}$ of the the Jacobi group $\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp$, viewed as the $\Fq$-points of an algebraic group over $\Fq$.
+Then $w_{i+1}$ is the representation of the $\Fq$-points of the special fibre of $\underline{G}^i \ltimes \underline{J}^{i+1}$ over $\OK$ and the representation $h^*(W_{i+1})$ is produced from $w_{i+1}$ by inflation.
+\end{enumerate}
+
+We now explain how to geometrize the characters of these ingredient representations.
 Suppose $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
-Let $A^0$ be a Weil sheaf on $(\underline{G}^0)_\Fq^\reductive$ such that, as a sheaf on $(\underline{G}^0)_\Fq^\reductive \otimes \bFq$, it is a character sheaf.
-The existence of $A^0$ follows from \cite{Lusztig:CSDG}*{}.
-Let $A$ be the Weil sheaf on $\underline{G}^0_\Fq$ obtained by pullback along $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
-
-Let $n$ be an integer greater than the supremum of the depths of $\varphi_i : \underline{G}^i(\OK)\to \CC^\times$, for $i=0,\ldots, d$.
-Then, for $i=0,\ldots, d$ we have the commuting diagram 
-\[
-\begin{tikzcd}
-\end{tikzcd}
-\]
+Let $A$ be a Weil sheaf on $(\underline{G}^0)_\Fq^\reductive$ such that, as a sheaf ${\bar A}$ on $(\underline{G}^0)_\Fq^\reductive \otimes \bFq$, it is a character sheaf, and
+\[
+\trFrob{\bar A} = \trace \sigma.
+\]
+The existence of $A$ follows from \cite{Lusztig:CSDG}*{}.
+Let $B$ be the Weil sheaf on $\underline{G}^0_\Fq$ obtained by pullback along $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+Then $\trFrob{\bar B} = \trace \tau$ so
+\[
+\trace \varrho(k) = \trFrob{\bar B}(k_\Fq)
+\]
+where $k \mapsto k_\Fq$ refers to the map $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$.
+Observe that the special fibre $\underline{G}^0_\Fq$ of $\underline{G}^0$ is $\Gr_1(\underline{G}^0)$.
+Let $\cs{B}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^0)$ obtained by pulling back $B$ along  $\Gr(\underline{G}^0) \to \Gr_1(\underline{G}^0)$.
+
+For $i=0,\ldots, d-1$, let $\cs{F}_{i+1}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^i)$ obtained by applying Proposition~\ref{prop:quasicharacters} to $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$.
+
+For $i=0,\ldots, d-1$, let $\cs{T}_i$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^i \ltimes \underline{J}^{i+1})$
 
@@
 
-\begin{lemma}
-Let $\underline{G}$ be a smooth group scheme over $\OK$.
-Let $\varphi : \underline{G}(\OK) \to \CC^\times$ be a quasicharacter/continuous linear character. 
-The there is a Weil sheaf $\cs{F}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{F}} = \trace \varphi$.
-\end{lemma}
-
-\subsection{Geometrization}\label{ssec:geometrization}
-
-The first step in the geometrization of the type $(\,^\circ K,\,^\circ \rho)$ is to replace $\,^\circ K$ with a group scheme $G$ over $\Fq$ so that $G(\Fq) = \,^\circ K$, canonically. 
-Set $S = \Spec{\OK}$ and $S_n = \Spec{\OK/\mathfrak{m}^n}$, where $\mathfrak{m}_K$ is the maximal ideal in $\OK$, and $n$ is a positive integer $n$.
-Let $G_n$ be the Greenberg transform of $\underline{G} \times_{S} S_n$.
-Then $G_n$ is a smooth group scheme over $\Fq$ and 
-\[
-G_n(\Fq) = \underline{G}(\OK/\mathfrak{m}_K^n),
-\]
-canonically.
-%
-Let $G$ be the Greenberg transform of $\underline{G}$.
-Then $G$ is a group scheme over $\Fq$ and 
-\[
-G(\Fq) = \,^\circ K,
-\]
-canonically.
-
 \begin{proposition}\label{prop:types}
 Let $(\,^\circ K,\,^\circ \rho)$ be a Yu type.
-With notation as above, suppose $\pi_0(\underline{G}_s\red)$ is cyclic and that $\pi_0((\underline{G}^{j-1})_s\red)$ is cyclic for $j=1,\ldots, d-1$.
-Then there is a virtual admissible $\ell$-adic sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
+With notation as above, suppose $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
+Then there is a virtual admissible Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
 \end{proposition}

### 2016-01-13 followup.tex
Added todo

--- 2016-01-13 followup.tex
@@
 it is also an $H$-torsor in the fpqc topology.
-It now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{H}(G)$ is an equivalence.
+It now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{H}(G)$ is an equivalence.\todo{Did I compare these topologies correctly? fpqc is finer than fppf}
 %
@@
 Let $\chi : \underline{G}(\OK) \to \CC^\times$ be a quasicharacter/continuous linear character. 
-The there is a Weil sheaf $\cs{F}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{F}} = \trace \chi$.
+The there is a Weil sheaf $\cs{F}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{F}} = \trace \chi$. \todo{Missing proof}
 \end{proposition}
@@
 \todo{Everything below here is under construction}
-Recall from Section~\ref{ssec:models} that the ingredient representations in the construction of any Yu type are:
+
+We begin explain how to geometrize the characters of these ingredient representations, using the discussion from Section~\ref{ssec:models}.
 \begin{enumerate}
@@
 Then $\tau$ is the representation of the $\Fq$-points of the special fibre of the smooth model $\underline{G}^0$ over $\OK$ and the representation $\varrho$ of $\underline{G}(\OK)$ is produced from $\tau$ by inflation.
+Suppose $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
+Let $A$ be a Weil sheaf on $(\underline{G}^0)_\Fq^\reductive$ such that, as a sheaf ${\bar A}$ on $(\underline{G}^0)_\Fq^\reductive \otimes \bFq$, it is a character sheaf, and
+\[
+\trFrob{\bar A} = \trace \sigma.
+\]
+The existence of $A$ follows from \cite{Lusztig:CSDG}*{}.
+Let $B$ be the Weil sheaf on $\underline{G}^0_\Fq$ obtained by pullback along $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+Then $\trFrob{\bar B} = \trace \tau$ so
+\[
+\trace \varrho(k) = \trFrob{\bar B}(k_\Fq)
+\]
+where $k \mapsto k_\Fq$ refers to the map $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$.
+Observe that the special fibre $\underline{G}^0_\Fq$ of $\underline{G}^0$ is $\Gr_1(\underline{G}^0)$.
+Let $\cs{B}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^0)$ obtained by pulling back $B$ along  $\Gr(\underline{G}^0) \to \Gr_1(\underline{G}^0)$.
+
 \item For $i=0, \ldots, d$, a quasicharacter (continuous linear character) $\varphi_i$ of $\underline{G}^i(\OK)$. 
@@
 \end{enumerate}
-
-We now explain how to geometrize the characters of these ingredient representations.
-Suppose $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
-Let $A$ be a Weil sheaf on $(\underline{G}^0)_\Fq^\reductive$ such that, as a sheaf ${\bar A}$ on $(\underline{G}^0)_\Fq^\reductive \otimes \bFq$, it is a character sheaf, and
-\[
-\trFrob{\bar A} = \trace \sigma.
-\]
-The existence of $A$ follows from \cite{Lusztig:CSDG}*{}.
-Let $B$ be the Weil sheaf on $\underline{G}^0_\Fq$ obtained by pullback along $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
-Then $\trFrob{\bar B} = \trace \tau$ so
-\[
-\trace \varrho(k) = \trFrob{\bar B}(k_\Fq)
-\]
-where $k \mapsto k_\Fq$ refers to the map $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$.
-Observe that the special fibre $\underline{G}^0_\Fq$ of $\underline{G}^0$ is $\Gr_1(\underline{G}^0)$.
-Let $\cs{B}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^0)$ obtained by pulling back $B$ along  $\Gr(\underline{G}^0) \to \Gr_1(\underline{G}^0)$.
 

### 2016-01-27 followup.tex
Almost finished the proof of geotypes, assuming conjecture geoWeil.
Moving to a different computer.

@@
 
+      \newtheorem{conjecture}[theorem]{Conjecture}
 %%%%%%%%%%%%%%% RINGS AND GROUPS %%%%%%%%%%%%%%%
@@
 
-In this paper we use a common formalism for Weil sheaves, writing $\cs{L}$ for the pair $(\gcs{L},\phi)$ and writing $\alpha : \cs{L} \to \cs{L}'$ for a morphism $\alpha : \gcs{L} \to \gcs{L}$ such that
+In this paper we use a common formalism for Weil sheaves, writing $\cs{L}$ for the pair $(\gcs{L},\phi)$ where $\gcs{L}$ is an $\ell$-adic sheaf on $\bG \ceq G\otimes_{\Fq} \bFq$ and where $\phi : \Frob{}^*\gcs{L} \to \gcs{L}$ is an isomorphism of $\ell$-adic sheaves.
+We also follow convention by referring to $\cs{L}$  as a Weil sheaf on $G$. 
+We will also write $\alpha : \cs{L} \to \cs{L}'$ for a morphism $\alpha : \gcs{L} \to \gcs{L}$ such that 
 \[
@@
 Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
-\[
+$
 \beta : \cs{L}\vert_H \to (\EE)_{H}
-\]
+$
 by 
@@
 %
-In this section we use Theorem~\ref{thm:geo} to geometrize the representation $\,^\circ \rho$ of $\,^\circ K$: we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = \,^\circ K$ and a virtual Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\,^\circ \rho)$.
+In this section we use Theorem~\ref{thm:geo} to geometrize the representation $\,^\circ \rho$ of $\,^\circ K$: subject to a hypothesis on the component group of the depth-zero part of the datum and also on a conjecture on the geometrization of the character of the Heisenberg-Weil representations, we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = \,^\circ K$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\,^\circ \rho)$.
 %from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius. 
+Unfortunately, the proof of this statement,  which is Proposition~\ref{prop:geotypes}, is quite technical, so the proof must be delayed to Section~\ref{ssec:geotypes}, after reviewing the types and models developed by Yu.
 
@@
 Let $\chi : \underline{G}(\OK) \to \CC^\times$ be a quasicharacter/continuous linear character. 
-The there is a Weil sheaf $\cs{F}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{F}} = \trace \chi$. \todo{Missing proof}
+The there is a Weil sheaf $\cs{L}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{L}} = \trace \chi$. \todo{Missing proof}
 \end{proposition}
@@
 
-\subsection{Review of Jacobi theory over finite fields}
-
-For use in the next section, we recall some basic facts about the Heisenberg-Weil representation.
+\subsection{A conjecture on Jacobi theory over finite fields}\label{sec:Jacobi}
+
+%For use in the next section, we recall some basic facts about the Heisenberg-Weil representation.
 
@@
 Let $W = \pi_\omega \ltimes \omega$ be the representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$ given by $\omega$ and $\pi_\omega$.
+
+\begin{conjecture}\label{conj:Jacobi}
+For $V$, $C$, $\langle\, , \ \rangle$, $\psi$ and $W$ as in Section~\ref{sec:Jacobi}, there is a Weil sheaf $\cs{W}$ on the algebraic group $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\cs{W}} = \trace(W)$.
+\end{conjecture}
 
@@
 The key to defining the representation $\,^\circ\rho_{i+1}$ from $\,^\circ \rho_i$ is the following diagram.
-\[
-\begin{tikzcd}
+\begin{equation}\label{eq:semiprod}
+\begin{tikzcd}
+\ && 1 \arrow{d} && \\
 \ && \,^\circ K^{i}\cap J^{i+1}\arrow{d} && \\
 1 \arrow{r} & J^{i+1} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d} \arrow{r} & \,^\circ K^i \arrow{r} & 1\\
-&& \,^\circ K^{i+1} &&
-\end{tikzcd}
-\]
+&& \,^\circ K^{i+1} \arrow{d} && \\
+&& 1 &&
+\end{tikzcd}
+\end{equation}
 Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
@@
 By \cite{yu:01a}*{}, the representation 
-\[
+\begin{equation}\label{eq:tensor}
 h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)
-\] 
+\end{equation}
 of $\,^\circ K^i \ltimes J^{i+1}$ is trivial on $\,^\circ K^{i}\cap J^{i+1}$, so $h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)$ descends to $\,^\circ K^{i+1}$.
@@
 This realizes the Jacobi group $\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp$ as a quotient of the special fibre of the smooth group scheme $\underline{G}^i \ltimes \underline{J}^{i+1}$ over $\OK$.
+
+Consider the following diagram of smooth group schemes over $\OK$ and compare with \eqref{eq:semiprod}.
+\begin{equation}\label{eq:pimodel}
+\begin{tikzcd}
+\ && 1 \arrow{d} && \\
+\ && \underline{G}^{i}\times_{\underline{G}} \underline{J}^{i+1}\arrow{d} && \\
+1 \arrow{r} & \underline{J}^{i+1} \arrow{r} & \underline{G}^i \ltimes \underline{J}^{i+1} \arrow{d} \arrow{r} & \underline{G}^i \arrow{r} & 1\\
+&& \underline{G}^{i+1} \arrow{d} && \\
+&& 1 &&
+\end{tikzcd}
+\end{equation}
 
@@
 
-\subsection{Geometrization of characters of types}\label{ssec:geometrization}
-
-\todo{Everything below here is under construction}
-
-We begin explain how to geometrize the characters of these ingredient representations, using the discussion from Section~\ref{ssec:models}.
-\begin{enumerate}
-\item A representation $\sigma$ of the $\Fq$-points of the reductive group $(\underline{G}^0)_\Fq^\reductive$ over $\Fq$. 
-Then $\tau$ is the representation of the $\Fq$-points of the special fibre of the smooth model $\underline{G}^0$ over $\OK$ and the representation $\varrho$ of $\underline{G}(\OK)$ is produced from $\tau$ by inflation.
-Suppose $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
-Let $A$ be a Weil sheaf on $(\underline{G}^0)_\Fq^\reductive$ such that, as a sheaf ${\bar A}$ on $(\underline{G}^0)_\Fq^\reductive \otimes \bFq$, it is a character sheaf, and
-\[
-\trFrob{\bar A} = \trace \sigma.
-\]
-The existence of $A$ follows from \cite{Lusztig:CSDG}*{}.
-Let $B$ be the Weil sheaf on $\underline{G}^0_\Fq$ obtained by pullback along $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
-Then $\trFrob{\bar B} = \trace \tau$ so
-\[
-\trace \varrho(k) = \trFrob{\bar B}(k_\Fq)
-\]
-where $k \mapsto k_\Fq$ refers to the map $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$.
-Observe that the special fibre $\underline{G}^0_\Fq$ of $\underline{G}^0$ is $\Gr_1(\underline{G}^0)$.
-Let $\cs{B}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^0)$ obtained by pulling back $B$ along  $\Gr(\underline{G}^0) \to \Gr_1(\underline{G}^0)$.
-
-\item For $i=0, \ldots, d$, a quasicharacter (continuous linear character) $\varphi_i$ of $\underline{G}^i(\OK)$. 
-\item For $i=0, \ldots, d-1$, a representation $W_{i+1}$ of the the Jacobi group $\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp$, viewed as the $\Fq$-points of an algebraic group over $\Fq$.
-Then $w_{i+1}$ is the representation of the $\Fq$-points of the special fibre of $\underline{G}^i \ltimes \underline{J}^{i+1}$ over $\OK$ and the representation $h^*(W_{i+1})$ is produced from $w_{i+1}$ by inflation.
-\end{enumerate}
-
-For $i=0,\ldots, d-1$, let $\cs{F}_{i+1}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^i)$ obtained by applying Proposition~\ref{prop:quasicharacters} to $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$.
-
-For $i=0,\ldots, d-1$, let $\cs{T}_i$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^i \ltimes \underline{J}^{i+1})$
-
-\begin{lemma}[Claim, actually]
-For $V$, $C$, $\langle\, , \ \rangle$ and $\psi$ as above, there is a virtual constructible equivariant Weil sheaf $\cs{T}$ on the algebraic group $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\cs{T}} = \trace(\tau)$.
-\end{lemma}
+\subsection{Geometrization of characters of types}\label{ssec:geotypes}
+
+\begin{proposition}\label{prop:geotypes}
+Let $(\,^\circ K,\,^\circ \rho)$ be a Yu type.
+Assume Conjecture~\ref{conj:Jacobi}.
+and also that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
+Let $G$ be the Greenberg transform of the smooth group scheme $\underline{G}$.
+Then there is a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
+\end{proposition}
 
 \begin{proof}
-First, find a geometrization of $\omega$ which is equivariant for the action of $\Sp(V)$ on $V^\sharp$: a virtual constructible equivariant Weil sheaf $\cs{H}$ on $V^\sharp$ equipped with an isomorphism $m^*\cs{H} \to p^* \cs{H}$ such that ...
-Do this by induction: $\operatorname{ind}_{A}^{V^\sharp}(\cs{L}_\psi)$, where $A$ .
-.
-.
-.
+%Now we explain how to geometrize the characters of these ingredient representations, using the discussion from Section~\ref{ssec:models}.
+
+By continuity of the quasicharacters $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$, there is some $m \in \NN$ and a factorization
+\[
+\begin{tikzcd}
+\underline{G}^i(\OK) \arrow{rr}{\varphi^i} \arrow{rd} && \CC^\times\\
+& \underline{G}^i(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\phi^i_m} 
+\end{tikzcd}
+\] 
+for each $i=0, \ldots d$.
+Using Proposition~\ref{prop:quasicharacters}, let $\cs{L}^i_m$ be a geometrization of the linear character $\phi^i_m: \Gr^{\OK}_{m}(\underline{G}^i) \to \CC^\times$; so
+\[
+\trFrob{\cs{L}^i_m} = \trace \phi^i_m.
+\]
+%Recall that the full Greenberg transform $\Gr^{\OK}(\underline{G}^i)$ is a group scheme over $\Fq$ such that $\Gr^{\OK}(\underline{G}^i)(\Fq) = \underline{G}^i(\Fq)$, canonically, and comes equipped with a morphism $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_m(\underline{G}^i)$.
+%Let $\cs{L}^i$ be the  Weil sheaf on $\Gr^{\OK}(\underline{G}^i)$ obtained from $\cs{L}^i_m$ by pullback along $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_{m}(\underline{G}^i)$. 
+%Then $\cs{L}^i$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^i)$ from which the quasicharacter $\varphi^i$ may be recovered.
+
+By \cite{lusztig:CSDG}, there is a Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
+\[
+\trFrob{A} = \trace \sigma.
+\]
+(This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.)
+Let $A^+$ be the Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+Then 
+\[
+\trFrob{A^+} = \trace \tau.
+\]
+The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg $\Gr^{\OK}_0(\underline{G}^0)$\cite{CR}*{\S 4.3}.
+With $m\in \NN$ as above, let $\cs{A}_m^0$ be the pull-back of $A^0$ along the affine morphism
+$\Gr^{\OK}_{m}(\underline{G}^0) \to \Gr^{\OK}_{0}(\underline{G}^0)$.
+Factor
+\[
+\begin{tikzcd}
+\underline{G}^0(\OK) \arrow{rr}{\trace(\varrho)} \arrow{rd} && \CC\\
+& \underline{G}^0(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\trace(\varrho)_m} 
+\end{tikzcd}
+\]
+Then $\cs{A}_m^0$ is a Weil sheaf on $\underline{G}^i$, from which $\trace(\varrho)_m$ may be recovered:
+\[
+\trFrob{\cs{A}^0_m} = \trace(\varrho)_m
+\]
+%Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{\OK}(\underline{G}^0) \to \Gr^{\OK}_{m}(\underline{G}^0)$.
+%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^0)$ from which the character of $\varrho$ may be recovered.
+
+Consider the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ and the Heisenberg-Weil representation $W_{i+1}$ appearing in Section~\ref{ssec:models}.
+Let $\cs{W}^{i+1}$ be the Weil sheaf promised by Conjecture~\ref{conj:Jacobi} on the Jacobi group such that
+\[
+\trFrob{\cs{W}^{i+1}} = \trace(W_{i+1}).
+\]
+Recall from Section~\ref{ssec:models} that $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ is a quotient of the special fibre of the smooth group scheme $\underline{G}^{i} \ltimes \underline{J}^{i+1}$.
+Let $\cs{W}_0^{i+1}$ be the Weil sheaf on the special fibre of $\underline{G}^{i} \ltimes \underline{J}^{i+1}$ obtained from $W^{i+1}$ by pullback. 
+Let $\cs{W}_m^{i+1}$ be the Weil sheaf on $\Gr^{\OK}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1})$ obtained from $\cs{W}_0^{i+1}$ by pullback along the affine morphism
+$\Gr^{\OK}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1}) \to \Gr^{\OK}_0(\underline{G}^{i} \ltimes \underline{J}^{i+1})$.
+
+We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{\OK}_m(\underline{G}^{i})$, for $i=1,\ldots ,d$, recursively, following the construction of the representations $\,^0\rho_i$, reviewed in Section~\ref{ssec:review}.
+We have already defined $\cs{A}^0_m$.
+Suppose $\cs{A}^i_m$ on $G_m^i$ is defined; we shall construct $\cs{A}_m^{i+1}$ on $G_m^{i+1}$.
+
+Applying the Greenberg functor $\Gr^{\OK}_m$, to \eqref{eq:pimodel} gives
+\begin{equation}\label{eq:pi}
+\begin{tikzcd}
+\ && 1 \arrow{d} && \\
+\ && G_m^{i}\times_{G_m} J_m^{i+1} \arrow{d} && \\
+1 \arrow{r} &J_m^{i+1} \arrow{r} & G_m^i \ltimes J_m^{i+1} \arrow{d}{\pi_m^{i+1}} \arrow{r}{p_m^{i}} & G_m^i \arrow{r} & 1\\
+&& G_m^{i+1} \arrow{d} && \\
+&& 1 && 
+\end{tikzcd}
+\end{equation}
+where $J_m^{i+1} \ceq \Gr^{\OK}_m(\underline{J}^{i+1})$ and $G_m^{i} \ceq \Gr^{\OK}_m(\underline{G}^{i})$
+By \cite{BG-A}*{Prop 7.1}, the sequences are exact.
+Consider $\cs{A}_m^{i}\otimes \cs{L}_m^{i}$ on $G_m^{i}$ and let 
+\[
+(p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
+\]
+be the Weil sheaf on $G_m^{i}\ltimes J_m^{i+1}$ obtained by pullback along $G_m^{i}\ltimes J_m^{i+1} \to G_m^{i}$.
+Consider the sheaf 
+\[
+\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
+\]
+on $G_m^{i}\ltimes J_m^{i+1}$ and compare with \eqref{eq:tensor}.
+With reference to the morphism $\pi_m^{i+1} : G_m^i \ltimes J_m^{i+1} \to G_m^{i+1}$ from \eqref{eq:pi}, define
+\[
+\cs{\tilde A}_m^{i+1} \ceq R(\pi_m^{i+1})_! (\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})).
+\]
+%Let $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$ and set $\cs{A}_m^{i+1} \ceq \cs{\tilde A}_m^{i+1}(-n)$ (Tate twist).
+Before continuing, let us calculate: 
+\begin{eqnarray*}
+\trFrob{\cs{\tilde A}^{i+1}_m}(x)
+&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^i)}(y)\\
+&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1}}(y) \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y) ) \trFrob{\cs{L}_m^i}(p_m^{i+1}(y)).
+\end{eqnarray*}
+Now, 
+\[
+y \mapsto \trFrob{\cs{W}_m^{i+1}}(y) \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y) ) \trFrob{\cs{L}_m^i}(p_m^{i+1}(y))
+\]
+is precisely 
+\[
+\begin{tikzcd}
+\end{tikzcd}
+\]
+
 \end{proof}
-
-\begin{proposition}\label{prop:types}
-Let $(\,^\circ K,\,^\circ \rho)$ be a Yu type.
-With notation as above, suppose $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
-Then there is a virtual admissible Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
-\end{proposition}
 
@@
 \fi
+
+A representation $\sigma$ of the $\Fq$-points of the reductive group $(\underline{G}^0)_\Fq^\reductive$ over $\Fq$. 
+Then $\tau$ is the representation of the $\Fq$-points of the special fibre of the smooth model $\underline{G}^0$ over $\OK$ and the representation $\varrho$ of $\underline{G}(\OK)$ is produced from $\tau$ by inflation.
+Suppose $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
+The existence of $A$ follows from \cite{Lusztig:CSDG}*{}.
+Let $B$ be the Weil sheaf on $\underline{G}^0_\Fq$ obtained by pullback along $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+Then $\trFrob{\bar B} = \trace \tau$ so
+\[
+\trace \varrho(k) = \trFrob{\bar B}(k_\Fq)
+\]
+where $k \mapsto k_\Fq$ refers to the map $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$.
+Observe that the special fibre $\underline{G}^0_\Fq$ of $\underline{G}^0$ is $\Gr_1(\underline{G}^0)$.
+Let $\cs{B}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^0)$ obtained by pulling back $B$ along  $\Gr(\underline{G}^0) \to \Gr_1(\underline{G}^0)$.
+
+%\item 
+For $i=0, \ldots, d$, a quasicharacter (continuous linear character) $\varphi_i$ of $\underline{G}^i(\OK)$.
+
+%\item
+For $i=0, \ldots, d-1$, a representation $W_{i+1}$ of the the Jacobi group $\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp$, viewed as the $\Fq$-points of an algebraic group over $\Fq$.
+Then $w_{i+1}$ is the representation of the $\Fq$-points of the special fibre of $\underline{G}^i \ltimes \underline{J}^{i+1}$ over $\OK$ and the representation $h^*(W_{i+1})$ is produced from $w_{i+1}$ by inflation.
+%\end{enumerate}
+
+For $i=0,\ldots, d-1$, let $\cs{F}_{i+1}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^i)$ obtained by applying Proposition~\ref{prop:quasicharacters} to $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$.
+
+For $i=0,\ldots, d-1$, let $\cs{T}_i$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^i \ltimes \underline{J}^{i+1})$
+
+\end{proof}
+
+\begin{lemma}[Claim, actually]
+For $V$, $C$, $\langle\, , \ \rangle$ and $\psi$ as above, there is a virtual constructible equivariant Weil sheaf $\cs{T}$ on the algebraic group $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\cs{T}} = \trace(\tau)$.
+\end{lemma}
+
+\begin{proof}
+First, find a geometrization of $\omega$ which is equivariant for the action of $\Sp(V)$ on $V^\sharp$: a virtual constructible equivariant Weil sheaf $\cs{H}$ on $V^\sharp$ equipped with an isomorphism $m^*\cs{H} \to p^* \cs{H}$ such that ...
+Do this by induction: $\operatorname{ind}_{A}^{V^\sharp}(\cs{L}_\psi)$, where $A$ .
+.
+.
+.
+\end{proof}

### 2016-01-27 followup.tex
Getting ready to talk to David. Moving computers.

@@
 \author{Clifton Cunningham}
-\address{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive Northwest, Calgary, AB, Canada, {T2N~1N4}.}
+\address{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive Northwest, Calgary, Alberta, Canada, {T2N~1N4}.}
 \email{cunning@math.ucalgary.ca}
@@
 Let $\underline{G}$ be a smooth group scheme over $\OK$.
-Let $\chi : \underline{G}(\OK) \to \CC^\times$ be a quasicharacter/continuous linear character. 
+Let $\chi : \underline{G}(\OK) \to \EEx$ be a quasicharacter/continuous linear character. 
 The there is a Weil sheaf $\cs{L}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{L}} = \trace \chi$. \todo{Missing proof}
@@
 \ && \,^\circ K^{i}\cap J^{i+1}\arrow{d} && \\
-1 \arrow{r} & J^{i+1} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d} \arrow{r} & \,^\circ K^i \arrow{r} & 1\\
-&& \,^\circ K^{i+1} \arrow{d} && \\
+1 \arrow{r} & J^{i+1} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & \,^\circ K^i \arrow{r} & 1\\
+&& \,^\circ K^{i+1} \arrow{d}{} && \\
 && 1 &&
@@
 Write $\inf(\,^\circ\rho_i \otimes \varphi_i)$ for the representation of $\,^\circ K^i \ltimes J^{i+1}$ obtained by pulling back $\,^\circ\rho_i$ along $\,^\circ K^i \ltimes J^{i+1} \to \,^\circ K^i$.
-By \cite{yu:01a}*{}, the representation 
+Consider the representation
 \begin{equation}\label{eq:tensor}
-h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)
+\,^0{\tilde\rho}_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)
 \end{equation}
-of $\,^\circ K^i \ltimes J^{i+1}$ is trivial on $\,^\circ K^{i}\cap J^{i+1}$, so $h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)$ descends to $\,^\circ K^{i+1}$.
+of $\,^\circ K^i \ltimes J^{i+1}$.
+By construction, the character of this representation satisfies
+\begin{equation}\label{eq:tilderho}
+\trace(\,^0{\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(h_{i+1}(y))\ \trace(\,^\circ\rho_i)(p_i(y))\ \varphi_i(p_i(y))
+\end{equation}
+for $y \in \,^\circ K^i \ltimes J^{i+1}$.
+By \cite{yu:01a}*{}, the representation $\,^0{\tilde\rho}_{i+1}$ of $\,^\circ K^i \ltimes J^{i+1}$ is trivial on $\,^\circ K^{i}\cap J^{i+1}$ so $\,^0{\tilde\rho}_{i+1}$ descends to $\,^\circ K^{i+1}$.
 This defines $\,^\circ \rho_{i+1}$.\todo{I didn't use $\varphi_d$, so this can't be quite right.}
-
 %The character of $\,^\circ \rho_d$ on $\,^\circ K^d = \,^\circ K = J^0 \cdots J^d$ satisfies
@@
 
+Since Yu's theory refers to complex representations, and since our geometrization uses $\ell$-adic sheaves, we fix, once and for all, an isomorphism $\CC \sim \EE$.
+
 \begin{proposition}\label{prop:geotypes}
@@
 Let $G$ be the Greenberg transform of the smooth group scheme $\underline{G}$.
-Then there is a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace \rho$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
+Then there is a virtual Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace(\,^\circ \rho)$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
 \end{proposition}
@@
 \begin{tikzcd}
-\underline{G}^i(\OK) \arrow{rr}{\varphi^i} \arrow{rd} && \CC^\times\\
+\underline{G}^i(\OK) \arrow{rr}{\varphi^i} \arrow{rd} && \EEx\\
 & \underline{G}^i(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\phi^i_m} 
@@
 (This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.)
-Let $A^+$ be the Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+Let $A^0$ be the Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
 Then 
 \[
-\trFrob{A^+} = \trace \tau.
+\trFrob{A^0} = \trace \tau.
 \]
@@
 \begin{tikzcd}
-\underline{G}^0(\OK) \arrow{rr}{\trace(\varrho)} \arrow{rd} && \CC\\
+\underline{G}^0(\OK) \arrow{rr}{\trace(\varrho)} \arrow{rd} && \EE \\
 & \underline{G}^0(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\trace(\varrho)_m} 
@@
 We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{\OK}_m(\underline{G}^{i})$, for $i=1,\ldots ,d$, recursively, following the construction of the representations $\,^0\rho_i$, reviewed in Section~\ref{ssec:review}.
-We have already defined $\cs{A}^0_m$.
+We have already defined $\cs{A}^0_m$ so that 
+\[
+\trFrob{\cs{A}^0_m} = \trace(\,^\circ \rho_0)_m
+\]
+where $\trace(\,^\circ \rho_0)_m : G_m^0(\Fq) \to \EE$ is defined by 
+\[
+\underline{G}^0
+\]
+and the canonical identification $G_m^0(\Fq) = \underline{G}^0(\OK/\mathfrak{p}_K^{m+1})$.
+
 Suppose $\cs{A}^i_m$ on $G_m^i$ is defined; we shall construct $\cs{A}_m^{i+1}$ on $G_m^{i+1}$.
@@
 &=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^i)}(y)\\
-&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1}}(y) \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y) ) \trFrob{\cs{L}_m^i}(p_m^{i+1}(y)).
+&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1}}(y)\  \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y) )\ \trFrob{\cs{L}_m^i}(p_m^{i+1}(y)).
 \end{eqnarray*}
-Now, 
-\[
-y \mapsto \trFrob{\cs{W}_m^{i+1}}(y) \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y) ) \trFrob{\cs{L}_m^i}(p_m^{i+1}(y))
-\]
-is precisely 
-\[
-\begin{tikzcd}
-\end{tikzcd}
-\]
+Comparing with \eqref{eq:tilderho}, we see that 
+\[
+y \mapsto \trFrob{\cs{W}_m^{i+1}}(y)\ \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y))\ \trFrob{\cs{L}_m^i}(p_m^{i+1}(y))
+\]
+is precisely the function obtained by factoring the character of $\,^\circ {\tilde \rho}_{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK/\mathfrak{p}_K^{m+1})$, using the canonical identification $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK/\mathfrak{p}_K^{m+1})$.
+In particular, this is trivial on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$.
+It follows that 
+\[
+\trFrob{\cs{\tilde A}^{i+1}_m} = n \trace(\,^\circ \rho_{i+1})
+\]
+on $G_m^{i+1}(\Fq)$ with $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$.\todo{Hmm... Homomorphism?}
+\todo{If $n$ is a power of $q$, then we can use Tate twists to avoid working with virtual sheaves! Is $G^{i}\cap J_m^{i+1}$ unipotent? Is so, then there's a chance.}
+Let $\cs{A}_m^{i+1}$ be the \emph{virtual} Weil sheaf on $G_m^i$ given by $\cs{A}_m^{i+1} = \frac{1}{n} \cs{\tilde A}_m^{i+1}$.
+
+This completes the inductive definition of
 

### 2016-01-27 followup.tex
Fix typo, add bibliography entries

--- 2016-01-13 followup.tex
@@
 it is also an $H$-torsor in the fpqc topology.
-It now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{H}(G)$ is an equivalence.\todo{Did I compare these topologies correctly? fpqc is finer than fppf}
+It now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{H}(G)$ is an equivalence.
 %
@@
 Let $\chi : \underline{G}(\OK) \to \CC^\times$ be a quasicharacter/continuous linear character. 
-The there is a Weil sheaf $\cs{F}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{F}} = \trace \chi$. \todo{Missing proof}
+Then there is a Weil sheaf $\cs{F}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{F}} = \trace \chi$.
 \end{proposition}
@@
 \todo{Everything below here is under construction}
-
-We begin explain how to geometrize the characters of these ingredient representations, using the discussion from Section~\ref{ssec:models}.
+Recall from Section~\ref{ssec:models} that the ingredient representations in the construction of any Yu type are:
 \begin{enumerate}
@@
 Then $\tau$ is the representation of the $\Fq$-points of the special fibre of the smooth model $\underline{G}^0$ over $\OK$ and the representation $\varrho$ of $\underline{G}(\OK)$ is produced from $\tau$ by inflation.
-Suppose $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
-Let $A$ be a Weil sheaf on $(\underline{G}^0)_\Fq^\reductive$ such that, as a sheaf ${\bar A}$ on $(\underline{G}^0)_\Fq^\reductive \otimes \bFq$, it is a character sheaf, and
-\[
-\trFrob{\bar A} = \trace \sigma.
-\]
-The existence of $A$ follows from \cite{Lusztig:CSDG}*{}.
-Let $B$ be the Weil sheaf on $\underline{G}^0_\Fq$ obtained by pullback along $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
-Then $\trFrob{\bar B} = \trace \tau$ so
-\[
-\trace \varrho(k) = \trFrob{\bar B}(k_\Fq)
-\]
-where $k \mapsto k_\Fq$ refers to the map $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$.
-Observe that the special fibre $\underline{G}^0_\Fq$ of $\underline{G}^0$ is $\Gr_1(\underline{G}^0)$.
-Let $\cs{B}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^0)$ obtained by pulling back $B$ along  $\Gr(\underline{G}^0) \to \Gr_1(\underline{G}^0)$.
-
 \item For $i=0, \ldots, d$, a quasicharacter (continuous linear character) $\varphi_i$ of $\underline{G}^i(\OK)$. 
@@
 \end{enumerate}
+
+We now explain how to geometrize the characters of these ingredient representations.
+Suppose $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
+Let $A$ be a Weil sheaf on $(\underline{G}^0)_\Fq^\reductive$ such that, as a sheaf ${\bar A}$ on $(\underline{G}^0)_\Fq^\reductive \otimes \bFq$, it is a character sheaf, and
+\[
+\trFrob{\bar A} = \trace \sigma.
+\]
+The existence of $A$ follows from \cite{Lusztig:CSDG}*{}.
+Let $B$ be the Weil sheaf on $\underline{G}^0_\Fq$ obtained by pullback along $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+Then $\trFrob{\bar B} = \trace \tau$ so
+\[
+\trace \varrho(k) = \trFrob{\bar B}(k_\Fq)
+\]
+where $k \mapsto k_\Fq$ refers to the map $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$.
+Observe that the special fibre $\underline{G}^0_\Fq$ of $\underline{G}^0$ is $\Gr_1(\underline{G}^0)$.
+Let $\cs{B}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^0)$ obtained by pulling back $B$ along  $\Gr(\underline{G}^0) \to \Gr_1(\underline{G}^0)$.
 

### 2016-01-27 followup.tex
Final commit for conversation with David. Finished the proof of geotypes. It needs editing and proofing, however.

--- 2016-01-27 followup.tex
@@
 
-\subsection{Geometrization of quasicharacters of smooth group schemes over $p$-adic fields}
+\subsection{Quasicharacters of smooth group schemes over $p$-adic fields}
 
@@
 
-\subsection{Smooth models}\label{ssec:models}
+\subsection{Review of Yu's smooth models}\label{ssec:models}
 
@@
 \[
-\underline{G}^0
+\begin{tikzcd}
+G^0(\Fq) \arrow{rr}{\trace(\,^\circ \rho_0)} \arrow{rd} && \EE\\
+& G^0_m(\Fq). \arrow{ru}[swap]{\trace(\,^\circ \rho_0)_m} & 
+\end{tikzcd}
 \]
 and the canonical identification $G_m^0(\Fq) = \underline{G}^0(\OK/\mathfrak{p}_K^{m+1})$.
-
-Suppose $\cs{A}^i_m$ on $G_m^i$ is defined; we shall construct $\cs{A}_m^{i+1}$ on $G_m^{i+1}$.
+Suppose $\cs{A}^i_m$ on $G_m^i$ is defined and \[
+\begin{tikzcd}
+G^i(\Fq) \arrow{rr}{\trace(\,^\circ \rho_i)} \arrow{rd} && \EE\\
+& G_m^i(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m^i}} & 
+\end{tikzcd}
+\]
+commutes.
+We shall construct $\cs{A}_m^{i+1}$ on $G_m^{i+1}$ so that 
+\[
+\begin{tikzcd}
+G^{i+1}(\Fq) \arrow{rr}{\trace(\,^\circ \rho_{i+1})} \arrow{rd} && \EE\\
+& G_m^{i+1}(\Fq)\arrow{ru}[swap]{{\trFrob{\cs{A}_m^i}} } & 
+\end{tikzcd}
+\]
 
@@
 %Let $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$ and set $\cs{A}_m^{i+1} \ceq \cs{\tilde A}_m^{i+1}(-n)$ (Tate twist).
-Before continuing, let us calculate: 
+Then
 \begin{eqnarray*}
@@
 Let $\cs{A}_m^{i+1}$ be the \emph{virtual} Weil sheaf on $G_m^i$ given by $\cs{A}_m^{i+1} = \frac{1}{n} \cs{\tilde A}_m^{i+1}$.
-
-This completes the inductive definition of
-
+%
+This completes the inductive definition of $\cs{A}_m^i$ with the desired property.
+
+Now set $\cs{F}_m = \cs{A}_m^{d}$.
+Then $\cs{F}_m$ is a virtual Weil sheaf on $G_m = \Gr^{\OK}_m(\underline{G})$ such that
+\[
+\begin{tikzcd}
+G(\Fq) \arrow{rr}{\trace(\,^\circ \rho)} \arrow{rd} && \EE\\
+& G_m(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m}} & 
+\end{tikzcd}
+\]
+commutes.
+Let $\cs{F}$ be the virtural Weil sheaf on the group scheme $G= \Gr^{\OK}(\underline{G})$ obtained by pullback along $G \to G_m$.
+Then 
+\[
+\trFrob{\cs{F}} = \trace(\,^\circ \rho),
+\] 
+as desired.
 \end{proof}

### 2016-01-27 followup.tex

--- 2016-01-27 followup.tex
@@
 Let $\chi : \underline{G}(\OK) \to \EEx$ be a quasicharacter/continuous linear character. 
-The there is a Weil sheaf $\cs{L}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{L}} = \trace \chi$. \todo{Missing proof}
+Then there is a Weil sheaf $\cs{L}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{L}} = \trace \chi$. \todo{Missing proof}
 \end{proposition}

### 2016-01-28 followup.tex
Fixed a few typos

@@
 %
-In this section we use Theorem~\ref{thm:geo} to geometrize the representation $\,^\circ \rho$ of $\,^\circ K$: subject to a hypothesis on the component group of the depth-zero part of the datum and also on a conjecture on the geometrization of the character of the Heisenberg-Weil representations, we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = \,^\circ K$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\,^\circ \rho)$.
+In this section we use Theorem~\ref{thm:geo} to geometrize the representation $\,^\circ \rho$ of $\,^\circ K$: subject to a hypothesis on the component group of the depth-zero part of the datum and also on a conjecture on the geometrization of the character of Heisenberg-Weil representations, we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = \,^\circ K$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\,^\circ \rho)$.
 %from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius. 
@@
 \begin{conjecture}\label{conj:Jacobi}
-For $V$, $C$, $\langle\, , \ \rangle$, $\psi$ and $W$ as in Section~\ref{sec:Jacobi}, there is a Weil sheaf $\cs{W}$ on the algebraic group $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\cs{W}} = \trace(W)$.
+For $V$, $C$, $\langle\, , \ \rangle$, $\psi$ and $W$ as above, there is a Weil sheaf $\cs{W}$ on the algebraic group $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\cs{W}} = \trace(W)$.
 \end{conjecture}
@@
 \item[(1)] a continuous representation $\varrho$ of $\,^\circ K^0$;
-\item[(2)] a quasicharacter $\varphi_i : \,^\circ K^i \to \CC^\times$, for $i=0, \ldots d$.
+\item[(2)] a quasicharacter $\varphi^i : \,^\circ K^i \to \CC^\times$, for $i=0, \ldots d$.
 \end{enumerate}
-The representations $(\varrho, \varphi_0, \ldots , \varphi_d)$ enjoy certain properties which allow Yu to construct representations $\,^\circ\rho_i$ of $\,^\circ K^i$, for $i=0, \ldots, d-1$, such that $\,^\circ\rho_0 = \varrho$ and $\,^\circ\rho_d = \,^\circ\rho$.
+The representations $(\varrho, \varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\,^\circ\rho_i$ of $\,^\circ K^i$, for $i=0, \ldots, d-1$, such that $\,^\circ\rho_0 = \varrho$ and $\,^\circ\rho_d = \,^\circ\rho$.
 
@@
 Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $\,^\circ K^i \ltimes J^{i+1}$.
-Write $\inf(\,^\circ\rho_i \otimes \varphi_i)$ for the representation of $\,^\circ K^i \ltimes J^{i+1}$ obtained by pulling back $\,^\circ\rho_i$ along $\,^\circ K^i \ltimes J^{i+1} \to \,^\circ K^i$.
+Write $\inf(\,^\circ\rho_i \otimes \varphi^i)$ for the representation of $\,^\circ K^i \ltimes J^{i+1}$ obtained by pulling back $\,^\circ\rho_i$ along $\,^\circ K^i \ltimes J^{i+1} \to \,^\circ K^i$.
 Consider the representation
 \begin{equation}\label{eq:tensor}
-\,^0{\tilde\rho}_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)
+\,^0{\tilde\rho}_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi^i)
 \end{equation}
@@
 \begin{equation}\label{eq:tilderho}
-\trace(\,^0{\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(h_{i+1}(y))\ \trace(\,^\circ\rho_i)(p_i(y))\ \varphi_i(p_i(y))
+\trace(\,^0{\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\,^\circ\rho_i)(p_i(y))\ \varphi^i(p_i(y))
 \end{equation}
@@
 By \cite{yu:01a}*{}, the representation $\,^0{\tilde\rho}_{i+1}$ of $\,^\circ K^i \ltimes J^{i+1}$ is trivial on $\,^\circ K^{i}\cap J^{i+1}$ so $\,^0{\tilde\rho}_{i+1}$ descends to $\,^\circ K^{i+1}$.
-This defines $\,^\circ \rho_{i+1}$.\todo{I didn't use $\varphi_d$, so this can't be quite right.}
+This defines $\,^\circ \rho_{i+1}$.\todo{I didn't use $\varphi^d$, so this can't be quite right.}
 %The character of $\,^\circ \rho_d$ on $\,^\circ K^d = \,^\circ K = J^0 \cdots J^d$ satisfies
 %\[
-%\trace(\,^\circ \rho)(k_0 \cdots k_d) = \varrho(k_0)  \varphi_0(k_0) \cdots \varphi_d(k_d),
+%\trace(\,^\circ \rho)(k_0 \cdots k_d) = \varrho(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
 %\]
@@
 In fact, $\tau$ is itself obtained by pulling back a representation $\sigma$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
-\item Quasicharacters $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$, for $i=0, \ldots d$.
+\item Quasicharacters $\varphi^i : \underline{G}^i(\OK) \to \CC^\times$, for $i=0, \ldots d$.
 \item The representation $h_{i+1}^*(W_{i+1})$ of $(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK)$ is obtained by pulling back a representation along 
@@
 
-In fact, Yu's description of how to assemble $\,^\circ \rho$ from $(\varrho, \varphi_0, \ldots , \varphi_d)$ is slightly different, but equivalent, to what we have done here \cite{Yu:models}*{}.
+In fact, Yu's description of how to assemble $\,^\circ \rho$ from $(\varrho, \varphi^0, \ldots , \varphi^d)$ is slightly different, but equivalent, to what we have done here \cite{Yu:models}*{}.
 
@@
 
-Since Yu's theory refers to complex representations, and since our geometrization uses $\ell$-adic sheaves, we fix, once and for all, an isomorphism $\CC \sim \EE$.
+Since Yu's theory refers to complex representations, and since our geometrization uses $\ell$-adic sheaves, we fix, once and for all, an isomorphism $\CC \approx \EE$.
 
@@
 
-By continuity of the quasicharacters $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$, there is some $m \in \NN$ and a factorization
+By continuity of the quasicharacters $\varphi^i : \underline{G}^i(\OK) \to \CC^\times$, there is some $m \in \NN$ and a factorization
 \[
@@
 \underline{G}^i(\OK) \arrow{rr}{\varphi^i} \arrow{rd} && \EEx\\
-& \underline{G}^i(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\phi^i_m} 
-\end{tikzcd}
-\] 
-for each $i=0, \ldots d$.
+& \underline{G}^i(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\varphi^i_m} 
+\end{tikzcd}
+\] 
+for each $i=0, \ldots d$.\todo{Fix notation: $\phi$ to $\varphi$}
 Using Proposition~\ref{prop:quasicharacters}, let $\cs{L}^i_m$ be a geometrization of the linear character $\phi^i_m: \Gr^{\OK}_{m}(\underline{G}^i) \to \CC^\times$; so
@@
 \]
-The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg $\Gr^{\OK}_0(\underline{G}^0)$\cite{CR}*{\S 4.3}.
+The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $G^0 = \Gr^{\OK}_0(\underline{G}^0)$ \cite{CR}*{\S 4.3}.
 With $m\in \NN$ as above, let $\cs{A}_m^0$ be the pull-back of $A^0$ along the affine morphism
@@
 \[
-(p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
+(p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
 \]
@@
 \[
-\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
+\cs{W}_m^{i+1} \otimes (p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
 \]
 on $G_m^{i}\ltimes J_m^{i+1}$ and compare with \eqref{eq:tensor}.
-With reference to the morphism $\pi_m^{i+1} : G_m^i \ltimes J_m^{i+1} \to G_m^{i+1}$ from \eqref{eq:pi}, define
-\[
-\cs{\tilde A}_m^{i+1} \ceq R(\pi_m^{i+1})_! (\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})).
+With reference to the morphism $\pi_m^{i+1} : G_m^i \ltimes J_m^{i+1} \to G_m^{i+1}$ from \eqref{eq:pi}, define \todo{Reference needed here.}
+\[
+\cs{\tilde A}_m^{i+1} \ceq R(\pi_m^{i+1})_! (\cs{W}_m^{i+1} \otimes (p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})).
 \]
@@
 \trFrob{\cs{\tilde A}^{i+1}_m}(x)
-&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^i)}(y)\\
-&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1}}(y)\  \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y) )\ \trFrob{\cs{L}_m^i}(p_m^{i+1}(y)).
+&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1} \otimes (p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^i)}(y)\\
+&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1}}(y)\  \trFrob{\cs{A}_m^{i}}(p_m^{i}(y) )\ \trFrob{\cs{L}_m^i}(p_m^{i}(y)).
 \end{eqnarray*}
@@
 \[
-y \mapsto \trFrob{\cs{W}_m^{i+1}}(y)\ \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y))\ \trFrob{\cs{L}_m^i}(p_m^{i+1}(y))
+y \mapsto \trFrob{\cs{W}_m^{i+1}}(y)\ \trFrob{\cs{A}_m^{i}}(p_m^{i}(y))\ \trFrob{\cs{L}_m^i}(p_m^{i}(y))
 \]
@@
 \]
-on $G_m^{i+1}(\Fq)$ with $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$.\todo{Hmm... Homomorphism?}
+on $G_m^{i+1}(\Fq)$ with $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$. \todo{Hmm... Homomorphism?}
 \todo{If $n$ is a power of $q$, then we can use Tate twists to avoid working with virtual sheaves! Is $G^{i}\cap J_m^{i+1}$ unipotent? Is so, then there's a chance.}
@@
 %\item 
-For $i=0, \ldots, d$, a quasicharacter (continuous linear character) $\varphi_i$ of $\underline{G}^i(\OK)$.
+For $i=0, \ldots, d$, a quasicharacter (continuous linear character) $\varphi^i$ of $\underline{G}^i(\OK)$.
 
@@
 
-For $i=0,\ldots, d-1$, let $\cs{F}_{i+1}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^i)$ obtained by applying Proposition~\ref{prop:quasicharacters} to $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$.
+For $i=0,\ldots, d-1$, let $\cs{F}_{i+1}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^i)$ obtained by applying Proposition~\ref{prop:quasicharacters} to $\varphi^i : \underline{G}^i(\OK) \to \CC^\times$.
 

### 2016-01-28 shortfollowup.tex
Made shortfollowup

--- 2016-01-27 followup.tex
@@
 
-\section{Application to type theory for \texorpdfstring{$p$}{p}-adic groups}\label{sec:types}
-
-\newcommand{\red}{^{\operatorname{red}}}
-\newcommand{\Sp}{{\operatorname{Sp}}}
-
-As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
-The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
-Let us refer to the types arising in this manner as {\it Yu types}.
-%In this section we show that every Yu type is geometrizable.
-% in a sense which will be made clear below.
-%
-A Yu type is then a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, constructed in a certain way. 
-%
-In this section we use Theorem~\ref{thm:geo} to geometrize the representation $\,^\circ \rho$ of $\,^\circ K$: subject to a hypothesis on the component group of the depth-zero part of the datum and also on a conjecture on the geometrization of the character of the Heisenberg-Weil representations, we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = \,^\circ K$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\,^\circ \rho)$.
-%from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius. 
-Unfortunately, the proof of this statement,  which is Proposition~\ref{prop:geotypes}, is quite technical, so the proof must be delayed to Section~\ref{ssec:geotypes}, after reviewing the types and models developed by Yu.
-
-\subsection{Geometrization of quasicharacters of smooth group schemes over $p$-adic fields}
-
-%We begin with the case of continuous linear characters.
-
-Set $S = \Spec{\OK}$ and $S_n = \Spec{\OK/\mathfrak{m}^n}$, where $\mathfrak{m}_K$ is the maximal ideal in $\OK$, and $n$ is a positive integer $n$.
-Let $\underline{G}$ be a smooth group scheme over $\OK$.
-Let $G_n$ be the Greenberg transform of $\underline{G} \times_{S} S_n$.
-Then $G_n$ is a smooth group scheme over $\Fq$ and 
-\[
-G_n(\Fq) = \underline{G}(\OK/\mathfrak{m}_K^n),
-\]
-canonically.
-%
-Let $G$ be the Greenberg transform of $\underline{G}$.
-Then $G$ is a group scheme over $\Fq$ and 
-\[
-G(\Fq) = \underline{G}(\OK)
-\]
-canonically.
-
-\begin{proposition}\label{prop:quasicharacters}
-Let $\underline{G}$ be a smooth group scheme over $\OK$.
-Let $\chi : \underline{G}(\OK) \to \EEx$ be a quasicharacter/continuous linear character. 
-Then there is a Weil sheaf $\cs{L}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{L}} = \trace \chi$. \todo{Missing proof}
-\end{proposition}
-
-\begin{proof}
-\end{proof}
-
-\subsection{A conjecture on Jacobi theory over finite fields}\label{sec:Jacobi}
-
-%For use in the next section, we recall some basic facts about the Heisenberg-Weil representation.
-
-Let $V$ be a finite-dimensional vector space over a finite field $\Fq$ equipped with a symplectic paring $\langle\ ,\ \rangle : V\times V \to C$, where $C$ is a one-dimensional vector space over $\Fq$.
-Then $V$ is even-dimensional and we may pick a `Lagrangian splitting' $V = U \oplus W$ such that $\langle v,v' \rangle = (u,w') - (u',w)$ for $v=(u,w)$ and $v'=(u',w')$.
-Let $V^\sharp$ be the Heisenberg group determined by $(C, \langle\ ,\ \rangle)$.
-Then $V^\sharp$ is a split extension of $V$ by $C$.
-\[
-\begin{tikzcd}
-\ &&& U \arrow{d} &\\
-1 \arrow{r} & C \arrow{r} & V^\sharp \arrow{r} & \arrow[bend right]{l} V \arrow[bend right]{u} \arrow[bend left]{d} \arrow{r} & 1\\
-1 \arrow{r} & \arrow[equals]{u} C \arrow{r} & \arrow[bend right]{l}  A \arrow{u} \arrow{r} & \arrow[bend right]{l}  W \arrow{u} \arrow{r} & 1 
-\end{tikzcd}
-\]
-
-Let $\psi : C \to \EEx$ be an additive character and let $\omega$ be the Heisenberg representation on $V^\sharp$ with central character $\psi : C \to \EEx$. 
-Let $\Sp(V)$ be the symplectic group determined by the symplectic pairing $\langle\ ,\ \rangle$;
-this group acts on $V^\sharp$.
-Extend $\psi$ to $\psi_A : A \to \EEx$ in the obvious way. 
-Then $\omega \ceq \operatorname{Ind}_A^{V^\sharp}(\psi_A)$ is called the Heisenberg representation of $V^\sharp$.
-
-Observe that $\Sp(V)$ acts on $V^\sharp$.
-The Heisenberg representation determines a representation $\pi_{\omega}$ of $\Sp(V)$ with the same representation space as $\omega$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\omega(g)$ determines an isomorphism of representations $\omega^g \to \omega$, through the Egorov identity \cite{Gurevich-Hadani:geometric_Weil}*{(1.3.1)}.
-Let $W = \pi_\omega \ltimes \omega$ be the representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$ given by $\omega$ and $\pi_\omega$.
-
-\begin{conjecture}\label{conj:Jacobi}
-For $V$, $C$, $\langle\, , \ \rangle$, $\psi$ and $W$ as in Section~\ref{sec:Jacobi}, there is a Weil sheaf $\cs{W}$ on the algebraic group $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\cs{W}} = \trace(W)$.
-\end{conjecture}
-
-\subsection{Review of Yu's types}\label{ssec:review}
-
-Every Yu type $(\,^\circ K,\,^\circ \rho)$ may be constructed directly from the following information, derived from a Yu datum:
-\begin{enumerate}
-\item[(0)] a sequence of compact groups 
-\[
-\,^\circ K^0 \subseteq \,^\circ K^1 \subseteq \cdots \subseteq \,^\circ K^d= \,^\circ K;
-\]
-\item[(1)] a continuous representation $\varrho$ of $\,^\circ K^0$;
-\item[(2)] a quasicharacter $\varphi_i : \,^\circ K^i \to \CC^\times$, for $i=0, \ldots d$.
-\end{enumerate}
-The representations $(\varrho, \varphi_0, \ldots , \varphi_d)$ enjoy certain properties which allow Yu to construct representations $\,^\circ\rho_i$ of $\,^\circ K^i$, for $i=0, \ldots, d-1$, such that $\,^\circ\rho_0 = \varrho$ and $\,^\circ\rho_d = \,^\circ\rho$.
-
-Since we will need some facts about this construction, we review some further detail here.
-First, Yu introduces compact groups $J^i\subset \,^\circ K$, for $i=0, \ldots d$, such that 
-\[
-\,^\circ K^i = J^0\cdots J^{i}
-\]
-and a natural action of $\,^\circ K^i$ on $J^{i+1}$, for $i=0, \ldots d-1$, defining the groups
-\[
-\,^\circ K^i \ltimes J^{i+1}.
-\]
-He then introduces the following quotients of $J^{i+1}$ and $\,^\circ K^i$, for $i=0, \ldots d-1$.
-\begin{enumerate}
-\item[(Q.1)] A quotient $J^{i+1} \to V_{i+1}$ to a finite abelian group, the latter also given the structure of a $\Fq$-vector space.
-\end{enumerate}
-The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : C_{i+1} \to \EEx$.
-\begin{enumerate}
-\item[(Q.2)] A quotient $J^{i+1} \to V_{i+1}^\sharp$, where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $C_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$.
-\end{enumerate}
-In fact, the quotient $J^{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J^{i+1} \to H^{i+1}$ and an isomorphism $j_{i+1} : H^{i+1} \to V_{i+1}^\sharp$, where $H^{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:construction}*{}.
-\begin{enumerate}
-\item[(Q.3)] A quotient $\,^\circ f_{i+1} : \,^\circ K^i \to \Sp(V_{i+1})$, such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $\,^\circ K^i$ on $H^{i+1}$ in the sense of \cite{yu:construction}.
-\end{enumerate}
-Taken together, these quotients define another quotient:
-\begin{enumerate}
-\item[(Q)] A quotient $h_{i+1} : \,^\circ K^i \ltimes J^{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
-\[
-\begin{tikzcd}
-1 \arrow{r} & J^{i+1} \arrow{d} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d}{h_{i+1}} \arrow{r} & \,^\circ K^i \arrow{r} \arrow{d}{\,^\circ f_i} & 1\\ 
-1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
-\end{tikzcd}
-\]
-\end{enumerate}
-
-The representations $\,^\circ \rho_i$ are defined recursively. Set $\,^\circ \rho_0 = \varrho$.
-Suppose $i=0, \ldots, d-1$.
-The key to defining the representation $\,^\circ\rho_{i+1}$ from $\,^\circ \rho_i$ is the following diagram.
-\begin{equation}\label{eq:semiprod}
-\begin{tikzcd}
-\ && 1 \arrow{d} && \\
-\ && \,^\circ K^{i}\cap J^{i+1}\arrow{d} && \\
-1 \arrow{r} & J^{i+1} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & \,^\circ K^i \arrow{r} & 1\\
-&& \,^\circ K^{i+1} \arrow{d}{} && \\
-&& 1 &&
-\end{tikzcd}
-\end{equation}
-Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
-Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $\,^\circ K^i \ltimes J^{i+1}$.
-Write $\inf(\,^\circ\rho_i \otimes \varphi_i)$ for the representation of $\,^\circ K^i \ltimes J^{i+1}$ obtained by pulling back $\,^\circ\rho_i$ along $\,^\circ K^i \ltimes J^{i+1} \to \,^\circ K^i$.
-Consider the representation
-\begin{equation}\label{eq:tensor}
-\,^0{\tilde\rho}_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi_i)
-\end{equation}
-of $\,^\circ K^i \ltimes J^{i+1}$.
-By construction, the character of this representation satisfies
-\begin{equation}\label{eq:tilderho}
-\trace(\,^0{\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(h_{i+1}(y))\ \trace(\,^\circ\rho_i)(p_i(y))\ \varphi_i(p_i(y))
-\end{equation}
-for $y \in \,^\circ K^i \ltimes J^{i+1}$.
-By \cite{yu:01a}*{}, the representation $\,^0{\tilde\rho}_{i+1}$ of $\,^\circ K^i \ltimes J^{i+1}$ is trivial on $\,^\circ K^{i}\cap J^{i+1}$ so $\,^0{\tilde\rho}_{i+1}$ descends to $\,^\circ K^{i+1}$.
-This defines $\,^\circ \rho_{i+1}$.\todo{I didn't use $\varphi_d$, so this can't be quite right.}
-%The character of $\,^\circ \rho_d$ on $\,^\circ K^d = \,^\circ K = J^0 \cdots J^d$ satisfies
-%\[
-%\trace(\,^\circ \rho)(k_0 \cdots k_d) = \varrho(k_0)  \varphi_0(k_0) \cdots \varphi_d(k_d),
-%\]
-%for $k_i\in J^i$.
-
-\subsection{Smooth models}\label{ssec:models}
-
-\begin{enumerate}
-\item[(K)]
-By \cite{yu:models}*{Prop 10.2} there is a sequence  
-\[
-\underline{G}^0 \to \underline{G}^1 \to \cdots \to \underline{G}^d = \underline{G}
-\]
-of morphisms of affine smooth group schemes of finite type over $\OK$ such that, on $\OK$-points it gives the sequence $\,^\circ K^0 \subseteq \,^\circ K^1 \subseteq \cdots \subseteq \,^\circ K^d= \,^\circ K$ above.
-\item[(J)]
-As explained in \cite{yu:03a}*{\S 10.4}, for each $i=0,\ldots d$, there is morphism of affine smooth group schemes of finite type over $\OK$ 
-\[
-\underline{J}^i \to \underline{G}
-\] 
-such that $\underline{J}^i(\OK) = J^i$ as a subgroup of $\,^\circ K$ and such that the image of the $\OK$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $\,^\circ K^i$, for $i=0, \ldots , d$.
-\item[(S)]
-There is a natural action of $\underline{G}^i$ on $\underline{J}^{i+1}$ in the category of smooth affine group schemes over $\OK$ so that the group
-\[
-\underline{G}^i \ltimes \underline{J}^{i+1}
-\]
-has $\OK$-points
-\[
-(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK) = \,^\circ K^i \ltimes J^{i+1}.
-\]
-\end{enumerate}
-
-\newcommand{\reductive}{{\operatorname{red}}}
-
-Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
-The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $U^{i+1}_\Fq$, where $U^{i+1}_\Fq$, appears as a quotient $J^{i+1}_\Fq \to U^{i+1}_\Fq$ of algebraic groups.
-Then the quotient $J^{i+1} \to V_{i+1}$ is realized as the composition
-\[
-\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to U^{i+1}_{\Fq}(\Fq) = V_{i+1}.
-\]
-Likewise, the Heisenberg p-group $H^{i+1}$ group may be realized as a quotient of algebraic groups, and $J^{i+1}\to H^{i+1}$ as the composition 
-\[
-\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H^{i+1}.
-\]
-Finally, the group homomorphism $\,^\circ f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ may be made geometric in much the same way. 
-Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $\,^\circ f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ is realized as the composition
-\[
-\underline{G}^{i}(\OK) \to \underline{G}^{i}(\Fq) = \underline{G}^{i}_\Fq(\Fq) \to  \underline{G}^{i,\reductive}_\Fq(\Fq) \to W^{i+1}_{\Fq}(\Fq) = \Sp(V_{i+1}).
-\]
-
-With all this, we may revisit the quotients appearing in Section~\ref{ssec:review}:
-\[
-\begin{tikzcd}
-1 \arrow{r} & \underline{J}^{i+1}  \arrow{r} & \underline{G}^i \ltimes \underline{J}^{i+1} \arrow{r} & \underline{G}^i \arrow{r}  & 1\\
-1 \arrow{r} & \underline{J}^{i+1}_\Fq \arrow{d} \arrow{u} \arrow{r} & \underline{G}_\Fq^i \ltimes \underline{J}_\Fq^{i+1} \arrow{d} \arrow{u} \arrow{r} & \underline{G}_\Fq^i \arrow{r} \arrow{d} \arrow{u} & 1\\
-1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1,
-\end{tikzcd}
-\]
-where the last two rows are now understood as forming a diagram in the category of algebraic groups over $\Fq$. 
-This realizes the Jacobi group $\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp$ as a quotient of the special fibre of the smooth group scheme $\underline{G}^i \ltimes \underline{J}^{i+1}$ over $\OK$.
-
-Consider the following diagram of smooth group schemes over $\OK$ and compare with \eqref{eq:semiprod}.
-\begin{equation}\label{eq:pimodel}
-\begin{tikzcd}
-\ && 1 \arrow{d} && \\
-\ && \underline{G}^{i}\times_{\underline{G}} \underline{J}^{i+1}\arrow{d} && \\
-1 \arrow{r} & \underline{J}^{i+1} \arrow{r} & \underline{G}^i \ltimes \underline{J}^{i+1} \arrow{d} \arrow{r} & \underline{G}^i \arrow{r} & 1\\
-&& \underline{G}^{i+1} \arrow{d} && \\
-&& 1 &&
-\end{tikzcd}
-\end{equation}
-
-We may now revisit the ingredients in the construction of the representation $\,^\circ \rho$ of $\underline{G}(\OK)$ along the lines indicated by Yu and recalled at the beginning of this section.
-\begin{enumerate}
-\item The continuous representation $\varrho$ of $\,^\circ K^0$ is a representation of $\underline{G}^0(\OK)$ obtained by inflation along $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$. 
-Let $\tau$ be that representation of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
-In fact, $\tau$ is itself obtained by pulling back a representation $\sigma$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
-\item Quasicharacters $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$, for $i=0, \ldots d$.
-\item The representation $h_{i+1}^*(W_{i+1})$ of $(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK)$ is obtained by pulling back a representation along 
-\[
-(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK) \to (\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq).
-\]
-Let $w_{i+1}$ be that representation of $(\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq) = (\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq)(\Fq)$. 
-Then $w_{i+1}$ is itself obtained by pulling back the representation $W_{i+1}$ along the $\Fq$-points of the quotient
-\[
-\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq \to 
-\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp.
-\]
-\end{enumerate}
-Regarding the construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:models} concludes with the following provocative observation, which we have just revisited.
-\begin{quotation}
-{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
- the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
-These results suggest that algebraic geometry and group schemes should play an
-important role in the representation theory of $p$-adic groups.} \cite{yu:03a}
-\end{quotation}
-
-In fact, Yu's description of how to assemble $\,^\circ \rho$ from $(\varrho, \varphi_0, \ldots , \varphi_d)$ is slightly different, but equivalent, to what we have done here \cite{Yu:models}*{}.
-
-\subsection{Geometrization of characters of types}\label{ssec:geotypes}
-
-Since Yu's theory refers to complex representations, and since our geometrization uses $\ell$-adic sheaves, we fix, once and for all, an isomorphism $\CC \sim \EE$.
-
-\begin{proposition}\label{prop:geotypes}
-Let $(\,^\circ K,\,^\circ \rho)$ be a Yu type.
-Assume Conjecture~\ref{conj:Jacobi}.
-and also that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
-Let $G$ be the Greenberg transform of the smooth group scheme $\underline{G}$.
-Then there is a virtual Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace(\,^\circ \rho)$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
-\end{proposition}
-
-\begin{proof}
-%Now we explain how to geometrize the characters of these ingredient representations, using the discussion from Section~\ref{ssec:models}.
-
-By continuity of the quasicharacters $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$, there is some $m \in \NN$ and a factorization
-\[
-\begin{tikzcd}
-\underline{G}^i(\OK) \arrow{rr}{\varphi^i} \arrow{rd} && \EEx\\
-& \underline{G}^i(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\phi^i_m} 
-\end{tikzcd}
-\] 
-for each $i=0, \ldots d$.
-Using Proposition~\ref{prop:quasicharacters}, let $\cs{L}^i_m$ be a geometrization of the linear character $\phi^i_m: \Gr^{\OK}_{m}(\underline{G}^i) \to \CC^\times$; so
-\[
-\trFrob{\cs{L}^i_m} = \trace \phi^i_m.
-\]
-%Recall that the full Greenberg transform $\Gr^{\OK}(\underline{G}^i)$ is a group scheme over $\Fq$ such that $\Gr^{\OK}(\underline{G}^i)(\Fq) = \underline{G}^i(\Fq)$, canonically, and comes equipped with a morphism $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_m(\underline{G}^i)$.
-%Let $\cs{L}^i$ be the  Weil sheaf on $\Gr^{\OK}(\underline{G}^i)$ obtained from $\cs{L}^i_m$ by pullback along $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_{m}(\underline{G}^i)$. 
-%Then $\cs{L}^i$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^i)$ from which the quasicharacter $\varphi^i$ may be recovered.
-
-By \cite{lusztig:CSDG}, there is a Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
-\[
-\trFrob{A} = \trace \sigma.
-\]
-(This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.)
-Let $A^0$ be the Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
-Then 
-\[
-\trFrob{A^0} = \trace \tau.
-\]
-The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg $\Gr^{\OK}_0(\underline{G}^0)$\cite{CR}*{\S 4.3}.
-With $m\in \NN$ as above, let $\cs{A}_m^0$ be the pull-back of $A^0$ along the affine morphism
-$\Gr^{\OK}_{m}(\underline{G}^0) \to \Gr^{\OK}_{0}(\underline{G}^0)$.
-Factor
-\[
-\begin{tikzcd}
-\underline{G}^0(\OK) \arrow{rr}{\trace(\varrho)} \arrow{rd} && \EE \\
-& \underline{G}^0(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\trace(\varrho)_m} 
-\end{tikzcd}
-\]
-Then $\cs{A}_m^0$ is a Weil sheaf on $\underline{G}^i$, from which $\trace(\varrho)_m$ may be recovered:
-\[
-\trFrob{\cs{A}^0_m} = \trace(\varrho)_m
-\]
-%Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{\OK}(\underline{G}^0) \to \Gr^{\OK}_{m}(\underline{G}^0)$.
-%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^0)$ from which the character of $\varrho$ may be recovered.
-
-Consider the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ and the Heisenberg-Weil representation $W_{i+1}$ appearing in Section~\ref{ssec:models}.
-Let $\cs{W}^{i+1}$ be the Weil sheaf promised by Conjecture~\ref{conj:Jacobi} on the Jacobi group such that
-\[
-\trFrob{\cs{W}^{i+1}} = \trace(W_{i+1}).
-\]
-Recall from Section~\ref{ssec:models} that $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ is a quotient of the special fibre of the smooth group scheme $\underline{G}^{i} \ltimes \underline{J}^{i+1}$.
-Let $\cs{W}_0^{i+1}$ be the Weil sheaf on the special fibre of $\underline{G}^{i} \ltimes \underline{J}^{i+1}$ obtained from $W^{i+1}$ by pullback. 
-Let $\cs{W}_m^{i+1}$ be the Weil sheaf on $\Gr^{\OK}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1})$ obtained from $\cs{W}_0^{i+1}$ by pullback along the affine morphism
-$\Gr^{\OK}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1}) \to \Gr^{\OK}_0(\underline{G}^{i} \ltimes \underline{J}^{i+1})$.
-
-We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{\OK}_m(\underline{G}^{i})$, for $i=1,\ldots ,d$, recursively, following the construction of the representations $\,^0\rho_i$, reviewed in Section~\ref{ssec:review}.
-We have already defined $\cs{A}^0_m$ so that 
-\[
-\trFrob{\cs{A}^0_m} = \trace(\,^\circ \rho_0)_m
-\]
-where $\trace(\,^\circ \rho_0)_m : G_m^0(\Fq) \to \EE$ is defined by 
-\[
-\underline{G}^0
-\]
-and the canonical identification $G_m^0(\Fq) = \underline{G}^0(\OK/\mathfrak{p}_K^{m+1})$.
-
-Suppose $\cs{A}^i_m$ on $G_m^i$ is defined; we shall construct $\cs{A}_m^{i+1}$ on $G_m^{i+1}$.
-
-Applying the Greenberg functor $\Gr^{\OK}_m$, to \eqref{eq:pimodel} gives
-\begin{equation}\label{eq:pi}
-\begin{tikzcd}
-\ && 1 \arrow{d} && \\
-\ && G_m^{i}\times_{G_m} J_m^{i+1} \arrow{d} && \\
-1 \arrow{r} &J_m^{i+1} \arrow{r} & G_m^i \ltimes J_m^{i+1} \arrow{d}{\pi_m^{i+1}} \arrow{r}{p_m^{i}} & G_m^i \arrow{r} & 1\\
-&& G_m^{i+1} \arrow{d} && \\
-&& 1 && 
-\end{tikzcd}
-\end{equation}
-where $J_m^{i+1} \ceq \Gr^{\OK}_m(\underline{J}^{i+1})$ and $G_m^{i} \ceq \Gr^{\OK}_m(\underline{G}^{i})$
-By \cite{BG-A}*{Prop 7.1}, the sequences are exact.
-Consider $\cs{A}_m^{i}\otimes \cs{L}_m^{i}$ on $G_m^{i}$ and let 
-\[
-(p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
-\]
-be the Weil sheaf on $G_m^{i}\ltimes J_m^{i+1}$ obtained by pullback along $G_m^{i}\ltimes J_m^{i+1} \to G_m^{i}$.
-Consider the sheaf 
-\[
-\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
-\]
-on $G_m^{i}\ltimes J_m^{i+1}$ and compare with \eqref{eq:tensor}.
-With reference to the morphism $\pi_m^{i+1} : G_m^i \ltimes J_m^{i+1} \to G_m^{i+1}$ from \eqref{eq:pi}, define
-\[
-\cs{\tilde A}_m^{i+1} \ceq R(\pi_m^{i+1})_! (\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})).
-\]
-%Let $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$ and set $\cs{A}_m^{i+1} \ceq \cs{\tilde A}_m^{i+1}(-n)$ (Tate twist).
-Before continuing, let us calculate: 
-\begin{eqnarray*}
-\trFrob{\cs{\tilde A}^{i+1}_m}(x)
-&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1} \otimes (p_m^{i+1})^*(\cs{A}_m^{i}\otimes \cs{L}_m^i)}(y)\\
-&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1}}(y)\  \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y) )\ \trFrob{\cs{L}_m^i}(p_m^{i+1}(y)).
-\end{eqnarray*}
-Comparing with \eqref{eq:tilderho}, we see that 
-\[
-y \mapsto \trFrob{\cs{W}_m^{i+1}}(y)\ \trFrob{\cs{A}_m^{i}}(p_m^{i+1}(y))\ \trFrob{\cs{L}_m^i}(p_m^{i+1}(y))
-\]
-is precisely the function obtained by factoring the character of $\,^\circ {\tilde \rho}_{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK/\mathfrak{p}_K^{m+1})$, using the canonical identification $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK/\mathfrak{p}_K^{m+1})$.
-In particular, this is trivial on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$.
-It follows that 
-\[
-\trFrob{\cs{\tilde A}^{i+1}_m} = n \trace(\,^\circ \rho_{i+1})
-\]
-on $G_m^{i+1}(\Fq)$ with $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$.\todo{Hmm... Homomorphism?}
-\todo{If $n$ is a power of $q$, then we can use Tate twists to avoid working with virtual sheaves! Is $G^{i}\cap J_m^{i+1}$ unipotent? Is so, then there's a chance.}
-Let $\cs{A}_m^{i+1}$ be the \emph{virtual} Weil sheaf on $G_m^i$ given by $\cs{A}_m^{i+1} = \frac{1}{n} \cs{\tilde A}_m^{i+1}$.
-
-This completes the inductive definition of
-
-\end{proof}
-
 \bibliography{bibliography/Biblio}
@@
 \end{document}
-
-Suppose there is some $f : H\times G\to G\times G$ such that the following diagram commutes.
-\[
-\begin{tikzcd}
-\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
-G & & G \\
-& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
-\end{tikzcd}
-\]
-Then $f(h,g) = (a(h,g) g^{-1}, g)$.
-Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq a(h,g) g^{-1}$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
-
-Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
-\[
-\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}
-\]
-by $\beta \otimes \id_{p^*\cs{L}} = \nu \circ f^*\mu^{-1}$, or more precisely, by the following diagram of isomorphisms,
-\[
-\begin{tikzcd}
-a^*\cs{L} \arrow{d}{m\circ f = a} \arrow{rrr}{\nu}
-&&& p^*\cs{L}\\
-f^* m^*\cs{L} \arrow{r}{f^*\mu} & 
-f^*(\cs{L}\boxtimes \cs{L}) \arrow{d} & 
-f_1^*\cs{L} \otimes p^*\cs{L} \arrow{r}{\beta\otimes \id_{p^*\cs{L}}} & 
-(\EE)_{H\times G} \otimes p^*\cs{L} \arrow{u} \\
-& f^*(p_1^*\cs{L}\otimes p_2^*\cs{L}) \arrow{r} & f^*p_1^*\cs{L}\otimes f^* p_2^*\cs{L} \arrow{u}{f_1 = p_1\circ f}[swap]{p = p_2\circ f} &
-\end{tikzcd}
-\]
-In this way we see we may replace $(\cs{L},\mu,\nu)$ with an alternate triple, $(\cs{L},\mu,\beta_1)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
-The isomorphism $\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}$ is constrained by two properties, corresponding to the diagrams in Sections [] and [].
-
-\subsection{Quotient and restriction}
-
-We now combine the material of the last two sections, by specializing to the following case: $H$ is a closed subgroup of $G$ and $q : G \to G/H$ is the fppf quotient, which exists in schemes by  . . .
-
-\iffalse
-
-\subsection{Change of action}
-
-Now, let $a' : H'\times G \to G$ be another group action on $G$ and suppose $f: H \times G \to H'\times G$ makes the following diagram commute.
-\[
-\begin{tikzcd}
-&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
-G & & G \\
-& \arrow{ul}{a'} H' \times G \arrow{ur}[swap]{p} & 
-\end{tikzcd}
-\]
-Then pull-back along $f: H\times G \to H'\times G$ defines a monoidal functor 
-\[
-\CS_{H'}(G) \to \CS_{H}(G).
-\]
-
-Then $f : H\times G \to H'\times G$ is given by $f(h,g) = (k(h,g),g)$ for some $k : H\times G\to H'$. 
-Define $d : H\to H'$ by $d(h) = k(h,1)$.
-
-\begin{lemma}\label{lem:action}
-The canonical functor
-\[
-\CS_{H}(G) \to \CS_{H'}(G)
-\]
-is an equivalence if ...
-\end{lemma}
-\begin{proof}
-\end{proof}
-
-\subsection{Conjugation}
-
-We close this section with an alternate characterization of $\CS'(G)$, the category of linear character sheaves $\cs{L}$ on $G$ for which $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
-Recall that $\CS'(G)$ is a full subcategory of $\CS(G)$ and that $\CCS(G)$ is a full subcategory of $\CS'(G)$.
-
-Consider the following case of Section~\ref{ssec:action}.
-
-\fi
-
-\iffalse
-\subsection{Linear Characters}
-
-For non-commutative $G$, we aim to model homomorphisms from $G(k)$ to $\EEx$ using the category $\CCS(G)$.
-The precise nature of the relationship between $G(k)^*$ and $\CCSiso{G}$ is described by Galois cohomology.
-Let $\Delta$ be the image of the boundary homomorphism $\delta$ in the sequence
-\[
-1 \to G\der(k) \to G(k) \to G\ab(k) \xrightarrow{\delta} \Hh^1(k, G\der),
-\]
-yielding a short exact sequence
-\[
-1 \to G(k) / G\der(k) \to G\ab(k) \to \Delta \to 1.
-\]
-Applying $\Hom(-, \EEx)$ and using the fact that every homomorphism $G(k) \to \EEx$ vanishes on $G\der(k)$, we get
-\[
-1 \to \Delta^* \to G\ab(k)^* \to G(k)^* \to 1.
-\]
-
-Combining Theorems \ref{thm:trfrobiso} and \ref{thm:Gab} gives an isomorphism $\CCSiso{G} \to G\ab(k)^*$. \todo{Could we turn this into a declared proposition? It's a nice result.}
-We may thus ask for a condition on a commutative character sheaf on $G$ that corresponds to having trivial
-trace of Frobenius, with the expectation that the isomorphism classes of such commutative character sheaves
-should be in natural bijection with $\Delta^*$.
-
-Note that when $\Hh^1(k,G\der) = 0$, as is the case when $G\der(\bFq)$ ``is simply connected,'' then
-we succeed in geometrizing characters of $G(k)$ on the nose.
-
-% \begin{corollary}
-% If $\Hh^1(\Fq,G\der)=0$ then
-%the following diagram of isomorphisms commutes.
-%\[
-%\begin{tikzcd}
-%\CCSiso{G} \arrow{r} & G(\Fq)^*\\
-%\arrow{u}{q^*} \CCSiso{G\ab} \arrow{r} & \arrow{u} G\ab(\Fq)^* 
-%\end{tikzcd}
-%\]
-% \end{corollary}
-% 
-% \begin{proof}
-% By Theorem \ref{thm:trfrobiso}, $\CCSiso{G}\to G(\Fq)^*$ and $\CCSiso{G\ab}\to G\ab(\Fq)^*$ are isomorphisms.
-%By Theorem~\ref{thm:Gab}, $\CCSiso{G} \iso \CCSiso{G\ab}$.
-%Since $\Hh^1(\Fq,G\der)=0$, we have  $G\ab(\Fq) = G(\Fq)/G\der(\Fq)$.
-%Thus, all characters of $G(\Fq)$ factor through
-% $G\ab(\Fq)$. . . . 
-% The isomorphisms are compatible because  . . . 
-% \end{proof}
-
-\subsection{Linear characters of certain $p$-adic groups}
-
-Let $K$ be a local field with residue field $\Fq$.
-Let $\underline{G}$ be a smooth group scheme over $K$.
-Set $G_n = \Gr^R_n(\underline{G})$; this is a smooth group scheme over $\Fq$.
-Set $G = \Gr_R(\underline{G})$; this is a group scheme over $\Fq$ equipped with $G = \varprojlim_{n\in \NN} G_n$.
-Let $\CCS(\underline{G})$ be the category of commutative quasicharacter sheaves on $G$. . . .  as in \cite{cunningham-roe:13a}.
-
-\begin{proposition}\label{prop:QCS}
-$\underline{G}(\OK)^* \iso \CCSiso{\underline{G}}$.
-\end{proposition}
-
-\begin{proof}
-That's not correct; it should be 
-\[
-\CCSiso{\underline{G}} \iso (\Gr(\underline{G})\ab(\Fq))^*.
-\]
-Is $\Gr(\underline{G})\ab = \Gr(\underline{G}\ab)?$ If so, then at least we get 
-\[
-\CCSiso{\underline{G}} \iso (\underline{G}\ab(\OK))^*.
-\]
-\end{proof}
-
-\fi
-
-\begin{proof}
-First, we make some observations concerning the auxillary data for $\underline{G}$.
-
-Introduce morphisms $\underline{G}\to \underline{M}^j$ and $\underline{M}^{j} \to \underline{M}^{j-1}$ and $\underline{M}^j \to \underline{J}^j$.
-\[
-\begin{tikzcd}
-\underline{J}^j \arrow{r} & \underline{G}^{j} \arrow{r} 
-& \underline{G} \arrow{r}  
-& \underline{M}^{j} \arrow{d} \arrow{r} & \underline{J}^j \\
-& \arrow{u} \underline{G}^{j-1} 
-&
-& \underline{M}^{j-1}
-&
-\end{tikzcd}
-\]
-\[
-\begin{tikzcd}
-\underline{G} \arrow{r}  
-& \underline{M}^{j} \arrow{d} \arrow{r} & \underline{J}^j \\
-\underline{G}_s \arrow{u} \arrow{d}
-& \underline{M}^{j-1}
- & (\underline{J}^j)_s \arrow{u} \arrow{d} \\
-\underline{G}_s\red & (\underline{M}^{j-1})_s \arrow{u} \arrow{d} & H^j \\
-& (\underline{M}^{j-1})_s\red & 
-\end{tikzcd}
-\]
-
-Now, we introduce the tools needed to geometrize all the ingredient representations.
-\begin{enumerate}
-\item
-Let $(A_0,\varphi)$ be a Frobenius-stable character sheaf on $\underline{G}_s\red$, in the sense of [Lusztig].
-Let $(A,\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{G}_s$ obtained by pull-back.
-\item For $j=1,\ldots, d-1$, 
-\begin{enumerate}
-\item
-Let $(B_0^{j},\varphi)$ be a Frobenius-stable character sheaf on $H^j$ in the sense of [Boyarchenko].
-Let $(B^{j},\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{J}^j_s$ obtained by pull-back.
-\item
-Let $(C_0^{j-1},\varphi)$ be a Frobenius-stable character sheaf on $(\underline{M}^{j-1})_s\red$ in the sense of [Lusztig].
-Let $(C^{j-1},\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{M}^{j-1}_s$ obtained by pull-back.
-\item
-Let $\cs{E}_n$ be a commutative quasicharacter sheaf on $M_n^{j-1}$.
-\end{enumerate}
-\item
-Let $\cs{L}_n$ be a commutative quasicharacter sheaf on $G_n$.
-\end{enumerate}
-\[
-\begin{tikzcd}
-G \arrow{r}  \arrow{d}
-& M^{j} \arrow{r} \arrow{d}
-& J^j \arrow{d} \\
-G_n \arrow{r}  \arrow{d}
-& M_n^{j} \arrow{r} \arrow{d}
-& J_n^j \arrow{d} \\
-\underline{G}_s \arrow{d}
-& M_n^{j-1} \arrow{d}
-& (\underline{J}^j)_s  \arrow{d} \\
-\underline{G}_s\red 
-& (\underline{M}^{j-1})_s \arrow{d} & H^j \\
-& (\underline{M}^{j-1})_s\red 
-& 
-\end{tikzcd}
-\]
-
-We may now encorporate all these ingredients into one sheaf on $G_n$.
-\begin{enumerate}
-\item
-Let $\cs{A}_n$ be sheaf on $G_n$ produced from $A$ by pullback along $G_n \to \underline{G}_s$.
-\item
-For $j=1, \ldots, d-1$,
-\begin{enumerate}
-\item let $\cs{B}^j$ be the sheaf on $J^j_n$ ...
-\item let $\cs{C}^j$ be the sheaf on $M^{j-1}_n$ ...
-\item let $\cs{L}^j$ be the sheaf on $M^{j-1}_n$ ...
-\end{enumerate}
-Combine: $\cs{B}^j$, $\cs{C}^j$ and $\cs{E}^j$ into $\cs{D}^j$ on $G_n$ . . . .
-\item Let $\cs{L}$ be the sheaf on $G_n$ as above...
-\end{enumerate}
-
-\[
-\cs{A} \otimes \cs{D}^1 \otimes \cdots \otimes \cs{D}^{d-1} \otimes \cs{L}.
-\]
-
-Interpret 
-\begin{enumerate}
-\item
-	$\epsilon_j$ as a representation of $(\underline{M}^{j-1})_s\red(\Fq)$, for each $j=1,\ldots, d$;
-\item
-	$\phi_{j-1}$ as a linear quasicharacter of $\underline{M}^{j-1}(\OK)$, for $j=1,\ldots, d$;
-\end{enumerate}
-so that
-\begin{enumerate}
-\item 
-	$\dot{\epsilon}_j$ is the representation of $\underline{M}^{j-1}(\OK)$ obtained by pulling back $\epsilon_j$ along 
-\[\underline{M}^{j-1}(\OK) \to \underline{M}^{j-1}_s(\Fq) \to (\underline{M}^{j-1})_s\red(\Fq),\]
-for $j=1,\ldots, d-1$.
-\item
-	$\dot{\eta}_j$ is a representation of $\underline{J}^{j}(\OK)$ obtained by pulling back  . . . .  $j=1,\ldots, d-1$;
-\item
-	$\tau_j$ is the representation of $\underline{G}(\OK)$ obtained by pulling back  $\phi_{j-1}$ and $\dot{\epsilon}_j$ and $\dot{\eta}_j$ from $\underline{M}^{j}(\OK)$ along $\underline{G}(\OK)\to \underline{M}^j(\OK)$, for $j=1,\ldots, d-1$.
-\end{enumerate}
-
-\end{proof}
-
-\iffalse
-
-Let $K$ be a $p$-adic field. Let $\G$ be a connected reductive linear algebraic group over $K$. 
-A generic datum is a triple $(\vec{\G}, \pi_0, \vec{\phi})$ where: $\vec{\G}$ is a tower of $p$-adic groups $\G^0(K) \subset \G^1(K) \subset \cdots  \subset \G^d(K) = \G(K)$ (proper containment); $\pi_0$ is a depth-zero representation of $\G^0(K)$, and $\vec{\phi} = (\phi_0, \ldots , \phi_{d-1})$ where each $\phi_i : \G^i(K) \to \EEx$ is a quasicharacter (continuous group homomorphism).
-
-%The generic datum $(\vec{\G}, \pi_0, \vec{\phi})$ determines a type (in the sense of \cite{bushnell-kutzko:98a}) $(C, \rho)$ for $\G$, as explained in \cite{yu:01a}*{\S 15}, where $C \subset \G(K)$ is compact mod centre subgroup and $\rho$ is a representation of $C$.
-In \cite{yu:03a} it is shown that the $C$ admits a smooth integral model, in the sense that there is a smooth group scheme $\underline{C}$ over $\OK$ such that $\underline{C}(\OK) = C$.
-
-In \cite{yu:03a} it is shown that, for $0 \leq i < d$, the $p$-adic group $\G^i(K)$ admits a smooth integral model, in the sense that there is \todo{is $\underline{G}^i$ canonically determined?} a smooth group scheme $\underline{G}^i$ over $\OK$ such that $\underline{G}^i(\OK) = \G^i(K)$.
-Set $G^i_n \ceq \Gr^R_n(\underline{G}^i)$ and $G^i \ceq \Gr_R(\underline{G}^i)$; 
-then \[G^i(\Fq) = \G^i(K)\] (canonical isomorphism of groups).
-In this way, $\vec{\G}$ determines a tower $\vec{G}$ of group schemes $G^0 \subset G^1 \subset \cdots  \subset G^{d-1}$ (proper containment) over $\Fq$, from which the tower of $p$-adic groups
-$\G^0(K) \subset \G^1(K) \subset \cdots  \subset \G^{d-1}(K)$ can be recovered.
-
-Using Corollary~\ref{cor:QCS} \todo{broken reference} we see that each quasicharacter $\phi_i : G^i(\Fq) \to \EEx$ determines a quasicharacter sheaf $\cs{L}^i$, unique up to isomorphism, from which the quasicharacter $\phi_i$ can be recovered using the trace of Frobenius.
-In fact, more is true. Let $n_i$ be the smallest non-negative integer $n$ such that $\phi_i : G^i(\Fq) \to \EEx$ factors through $G^i(\Fq) \to G^i_n(\Fq)$.
-Then $\phi_i$ determines a commutative character sheaf $\cs{L}_{n_i}^i$, unique up to isomorphism, from which the quasicharacter $\phi_i$ can be recovered.
-Then $\cs{A}_i\ceq \cs{L}_{n_i}^i[\dim G_{n_i}^i]$ is a perverse sheaf on $G_{n_i}^i$ from which the quasicharacter $\phi_i$ can be recovered.
-In this way,  $\vec{\phi} = (\phi_0, \ldots , \phi_{d-1})$ determines perverse sheaves $\vec{\cs{A}} = (\cs{A}_0, \ldots , \cs{A}_{d-1})$ from which $\vec{\phi}$ can be recovered.
-
-Finally, consider the depth-zero supercuspidal representation $\pi_0$ of $\G^0(K)$.
-Then $\pi_0$ is produced by compact induction from representation $\sigma$ of a compact mod centre subgroup $\underline{C}_0(\OK) \subset \G^0(K)$.
-Moreover, $C_0$ admits a smooth integral model $\underline{C}$ ...
-
-%\subsection{Toral supercuspidal representations of $p$-adic groups}
-
-\fi
-
-A representation $\sigma$ of the $\Fq$-points of the reductive group $(\underline{G}^0)_\Fq^\reductive$ over $\Fq$. 
-Then $\tau$ is the representation of the $\Fq$-points of the special fibre of the smooth model $\underline{G}^0$ over $\OK$ and the representation $\varrho$ of $\underline{G}(\OK)$ is produced from $\tau$ by inflation.
-Suppose $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
-The existence of $A$ follows from \cite{Lusztig:CSDG}*{}.
-Let $B$ be the Weil sheaf on $\underline{G}^0_\Fq$ obtained by pullback along $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
-Then $\trFrob{\bar B} = \trace \tau$ so
-\[
-\trace \varrho(k) = \trFrob{\bar B}(k_\Fq)
-\]
-where $k \mapsto k_\Fq$ refers to the map $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$.
-Observe that the special fibre $\underline{G}^0_\Fq$ of $\underline{G}^0$ is $\Gr_1(\underline{G}^0)$.
-Let $\cs{B}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^0)$ obtained by pulling back $B$ along  $\Gr(\underline{G}^0) \to \Gr_1(\underline{G}^0)$.
-
-%\item 
-For $i=0, \ldots, d$, a quasicharacter (continuous linear character) $\varphi_i$ of $\underline{G}^i(\OK)$.
-
-%\item
-For $i=0, \ldots, d-1$, a representation $W_{i+1}$ of the the Jacobi group $\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp$, viewed as the $\Fq$-points of an algebraic group over $\Fq$.
-Then $w_{i+1}$ is the representation of the $\Fq$-points of the special fibre of $\underline{G}^i \ltimes \underline{J}^{i+1}$ over $\OK$ and the representation $h^*(W_{i+1})$ is produced from $w_{i+1}$ by inflation.
-%\end{enumerate}
-
-For $i=0,\ldots, d-1$, let $\cs{F}_{i+1}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^i)$ obtained by applying Proposition~\ref{prop:quasicharacters} to $\varphi_i : \underline{G}^i(\OK) \to \CC^\times$.
-
-For $i=0,\ldots, d-1$, let $\cs{T}_i$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^i \ltimes \underline{J}^{i+1})$
-
-\end{proof}
-
-\begin{lemma}[Claim, actually]
-For $V$, $C$, $\langle\, , \ \rangle$ and $\psi$ as above, there is a virtual constructible equivariant Weil sheaf $\cs{T}$ on the algebraic group $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\cs{T}} = \trace(\tau)$.
-\end{lemma}
-
-\begin{proof}
-First, find a geometrization of $\omega$ which is equivariant for the action of $\Sp(V)$ on $V^\sharp$: a virtual constructible equivariant Weil sheaf $\cs{H}$ on $V^\sharp$ equipped with an isomorphism $m^*\cs{H} \to p^* \cs{H}$ such that ...
-Do this by induction: $\operatorname{ind}_{A}^{V^\sharp}(\cs{L}_\psi)$, where $A$ .
-.
-.
-.
-\end{proof}

### 2016-01-28 shortfollowup.tex
Added EGA citation; removed old todos. Only the proof of 3.5 is missing.

@@
 non-commutative groups.   
-As an application, we use these \emph{commutative character sheaves} to geometrize types for
-supercuspidal representations of $p$-adic groups. 
 \end{abstract}
@@
 needed to parametrize supercuspidal representations of arbitrary depth in the same category:
-perverse sheaves on group schemes over finite fields. \todo{Update based on any changes in Section 4}
+perverse sheaves on group schemes over finite fields.
 
@@
 
-\todo{Add summary of Section 4 once it has stabilized}
-
 \section{Recollections and definitions} \label{sec:defs}
@@
 Let $G$ be a smooth group scheme over a finite field $\Fq$; that is, let $G$ be a group scheme over $\Fq$
-for which the structure morphism $G \to \Spec{\Fq}$ is smooth in the sense of \todo{include reference for this definition}.
-This implies $G \to \Spec{\Fq}$ is locally of finite type, but not that it is of finite type.
+for which the structure morphism $G \to \Spec{\Fq}$ is smooth in the sense of \cite{EGA:IV4}*{Def 17.3.1}. This implies $G \to \Spec{\Fq}$ is locally of finite type, but not that it is of finite type.
 We remark that the identity component $G^0$ of $G$ is of finite type over $\Fq$, while the component group scheme
@@
 it is also an $H$-torsor in the fpqc topology.
-It now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{H}(G)$ is an equivalence.\todo{Did I compare these topologies correctly? fpqc is finer than fppf}
+It now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{H}(G)$ is an equivalence.
+%\todo{Did I compare these topologies correctly? fpqc is finer than fppf}
 %

### 2016-01-30 followup.tex
Finish proof of Thm 3.5

@@
 \begin{proof}
-Let $\Delta$ be the image of the boundary homomorphism $\delta$ in the sequence
-\[
-1 \to G\der(k) \to G(k) \to G\ab(k) \xrightarrow{\delta} \Hh^1(k, G\der),
-\]
-yielding a short exact sequence
-\[
-1 \to G(k) / G\der(k) \to G\ab(k) \to \Delta \to 1.
+By the definition of $\Delta_G$, we have a short exact sequence
+\[
+1 \to G(k) / G\der(k) \to G\ab(k) \to \Delta_G \to 1.
 \]
@@
 \[
-1 \to \Delta^* \to G\ab(k)^* \to G(k)^* \to 1.
-\]
-By Theorem~\ref{thm:Gab}, the trace of Frobenius map  . . . .\todo{Finish this.}
+1 \to \Delta_G^* \to G\ab(k)^* \to G(k)^* \to 1.
+\]
+By Theorem~\ref{thm:Gab}, the map $\CCSiso{G\ab} \to \CCSiso{G}$ is an isomorphism.
+Moreover, since both $\CCSiso{G\ab} \to \CCSiso{G}$ and $G\ab(k)^* \to G(k)^*$ are
+defined by pullback along $q$, the square in the statement of the theorem commutes.
+Finally, $\TrFrob{} : \CCSiso{G\ab} \to G\ab(k)^*$ is an isomorphism by Theorem \ref{thm:trfrobiso}.
 \end{proof}

### 2016-01-30 shortfollowup.tex
Finish proof of Thm 3.5

@@
 Let $G$ be a smooth group scheme over a finite field $\Fq$; that is, let $G$ be a group scheme over $\Fq$
-for which the structure morphism $G \to \Spec{\Fq}$ is smooth in the sense of \cite{EGA:IV4}*{Def 17.3.1}. This implies $G \to \Spec{\Fq}$ is locally of finite type, but not that it is of finite type.
+for which the structure morphism $G \to \Spec{\Fq}$ is smooth in the sense of \cite{EGAIV4}*{Def 17.3.1}. This implies $G \to \Spec{\Fq}$ is locally of finite type, but not that it is of finite type.
 We remark that the identity component $G^0$ of $G$ is of finite type over $\Fq$, while the component group scheme
@@
 \begin{proof}
-Let $\Delta$ be the image of the boundary homomorphism $\delta$ in the sequence
+By the definition of $\Delta_G$, we have a short exact sequence
 \[
-1 \to G\der(k) \to G(k) \to G\ab(k) \xrightarrow{\delta} \Hh^1(k, G\der),
-\]
-yielding a short exact sequence
-\[
-1 \to G(k) / G\der(k) \to G\ab(k) \to \Delta \to 1.
+1 \to G(k) / G\der(k) \to G\ab(k) \to \Delta_G \to 1.
 \]
@@
 \[
-1 \to \Delta^* \to G\ab(k)^* \to G(k)^* \to 1.
+1 \to \Delta_G^* \to G\ab(k)^* \to G(k)^* \to 1.
 \]
-By Theorem~\ref{thm:Gab}, the trace of Frobenius map  . . . .\todo{Finish this.}
+By Theorem~\ref{thm:Gab}, the map $\CCSiso{G\ab} \to \CCSiso{G}$ is an isomorphism.
+Moreover, since both $\CCSiso{G\ab} \to \CCSiso{G}$ and $G\ab(k)^* \to G(k)^*$ are
+defined by pullback along $q$, the square in the statement of the theorem commutes.
+Finally, $\TrFrob{} : \CCSiso{G\ab} \to G\ab(k)^*$ is an isomorphism by Theorem \ref{thm:trfrobiso}.
 \end{proof}

### 2016-02-23 followup.tex
Fixed notation in Section 4.

--- 2016-01-28 followup.tex
@@
 
+\newcommand{\red}{^{\operatorname{red}}}
+\newcommand{\Sp}{{\operatorname{Sp}}}
+
 %% Hyphenation override
@@
 \todo{Add summary of Section 4 once it has stabilized}
+
+In the remainder of this section we use Theorem~\ref{thm:geo} to geometrize the representation $\rho$ of $C$: subject to a hypothesis on the component group of the depth-zero part of the datum and also on a conjecture on the geometrization of the character of Heisenberg-Weil representations, we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\rho)$.
+The proof of this statement is quite technical, so it must be delayed to Section~\ref{ssec:geotypes}, after reviewing types in Section~\ref{ssec:types} and models Section~\ref{ssec:models} developed by Yu, for which we must also review some facts about the Heisenberg-Weil representation in Section~\ref{ssec:Jacobi}, and also make a conjecture about the geometrization of that representation, Conjecture~\ref{conj}.
 
@@
 
-\newcommand{\red}{^{\operatorname{red}}}
-\newcommand{\Sp}{{\operatorname{Sp}}}
+\subsection{Quasicharacters of smooth group schemes over certain henselian traits}
+
+%We begin with the case of continuous linear characters.
+
+Let $R$ be a complete discrete valuation ring with maximal ideal $\mathfrak{m}$ and perfect residue field $\Fq$. 
+Then $\Spec{R}$ is a henselian trait.
+Let $\underline{G}$ be a smooth group scheme over $R$.
+Here we shall use  \cite{BGA} for the definition and fundamental properties of the Greenberg transform.
+Let $G$ be the Greenberg transform of $\underline{G}$; then $G$ is a group scheme over $\Fq$ and 
+\[
+G(\Fq) = \underline{G}(R)
+\]
+canonically.
+
+\begin{proposition}\label{prop:quasicharacters}
+With notation as above, suppose $\Fq$ is a finite field.
+For every quasicharacter/continuous linear character $\chi : \underline{G}(S) \to \EEx$ there is a Weil sheaf $\cs{L}$ on $G$ such that \[\trFrob{\cs{L}} = \trace \chi.\] \end{proposition}
+
+\begin{proof}
+Set $S = \Spec{R}$ and, for every non-negative integer, set $S_n = \Spec{R/\mathfrak{m}^{n+1}}$.
+ Then $G_n \ceq \Gr_n^{R}(\underline{G})$, the Greenberg transform of $\underline{G} \times_{S} S_n$, is a smooth group scheme over $\Fq$ and 
+\[
+G_n(\Fq) = \underline{G}(S_n),
+\]
+canonically.
+\end{proof}
+
+\subsection{A conjecture on Jacobi theory over finite fields}\label{sec:Jacobi}
+
+For use below, we recall some basic facts about the Heisenberg-Weil representation and make a conjecture about the geometrization of these representations.
+We refer the reader to \cite{BS} for more detail.
+
+Let $V$ be a finite-dimensional vector space over a finite field $\Fq$ equipped with a symplectic paring $\langle\ ,\ \rangle : V\times V \to Z$, where $Z$ is a one-dimensional vector space over $\Fq$.
+Let $V^\sharp$ be the Heisenberg group determined by $(Z, \langle\ ,\ \rangle)$.
+Then $V^\sharp$ is a split extension of $V$ by $Z$.
+Let $\Sp(V)$ be the symplectic group determined by the symplectic pairing $\langle\ ,\ \rangle$; this group acts on $V^\sharp$.
+Then  is the Jacobi group. 
+From the construction above, it is clear that $\Sp(V)\ltimes V^\sharp$ may be viewed as the $\Fq$-points of an algebraic group over $\Fq$; we will refer to that algebraic group as the Jacobi group.
+
+Let $\psi : Z \to \EEx$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi : Z \to \EEx$. 
+The Heisenberg representation determines a representation $\pi_{\psi}$ of $\Sp(V)$ with the same representation space as $\omega_\psi$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\psi(g)$ determines an isomorphism of representations $\omega_\psi^g \to \omega_\psi$.
+% through the Egorov identity \cite{Gurevich-Hadani:geometric_Weil}*{(1.3.1)}.\todo{Find better reference.}
+Let $W_\psi = \pi_\psi \ltimes \omega_\psi$ be the representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$ given by $\omega_\psi$ and $\pi_\psi$.
+
+\begin{conjecture}\label{conj:Jacobi}
+%Notation as above.
+There is an equivariant Weil sheaf $\cs{W}_\psi$ on the Jacobi group such that 
+\[
+\trFrob{\cs{W}_\psi} = \trace(W_\psi).
+\]
+\end{conjecture}
+
+\iffalse
+Pick a Lagrangian splitting $V = U \oplus U'$. 
+%such that $\langle v,v' \rangle = (u,w') - (u',w)$ for $v=(u,w)$ and $v'=(u',w')$.
+Let $B \to V^\sharp$ be the subgroup defined by the diagram below.
+\[
+\begin{tikzcd}
+\ &&& U' \arrow{d} &\\
+1 \arrow{r} & Z \arrow{r} & V^\sharp \arrow{r} & \arrow[bend right]{l} V \arrow[bend right]{u} \arrow[bend left]{d} \arrow{r} & 1\\
+1 \arrow{r} & \arrow[equals]{u} Z \arrow{r} & \arrow[bend right]{l}  B \arrow{u} \arrow{r} & \arrow[bend right]{l}  U \arrow{u} \arrow{r} & 1 
+\end{tikzcd}
+\]
+Extend $\psi$ to $\psi_B : B \to \EEx$ in the obvious way. 
+Then $\omega \ceq \operatorname{Ind}_A^{V^\sharp}(\psi_A)$ is called the Heisenberg representation of $V^\sharp$.
+\fi
+
+\subsection{Review of Yu's types}\label{ssec:review}
+
+For the rest of Section~\ref{sec:types}, $K$ is a $p$-adic field.
 
@@
 %
-A Yu type is then a pair $(\,^\circ K,\,^\circ \rho)$, where $\,^\circ K$ is a compact group and $\,^\circ \rho$ is a representation of $\,^\circ K$, constructed in a certain way. 
-%
-In this section we use Theorem~\ref{thm:geo} to geometrize the representation $\,^\circ \rho$ of $\,^\circ K$: subject to a hypothesis on the component group of the depth-zero part of the datum and also on a conjecture on the geometrization of the character of Heisenberg-Weil representations, we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = \,^\circ K$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\,^\circ \rho)$.
-%from which the character of $\,^\circ \rho$ can be recovered using the trace of Frobenius. 
-Unfortunately, the proof of this statement,  which is Proposition~\ref{prop:geotypes}, is quite technical, so the proof must be delayed to Section~\ref{ssec:geotypes}, after reviewing the types and models developed by Yu.
-
-\subsection{Quasicharacters of smooth group schemes over $p$-adic fields}
-
-%We begin with the case of continuous linear characters.
-
-Set $S = \Spec{\OK}$ and $S_n = \Spec{\OK/\mathfrak{m}^n}$, where $\mathfrak{m}_K$ is the maximal ideal in $\OK$, and $n$ is a positive integer $n$.
-Let $\underline{G}$ be a smooth group scheme over $\OK$.
-Let $G_n$ be the Greenberg transform of $\underline{G} \times_{S} S_n$.
-Then $G_n$ is a smooth group scheme over $\Fq$ and 
-\[
-G_n(\Fq) = \underline{G}(\OK/\mathfrak{m}_K^n),
-\]
-canonically.
-%
-Let $G$ be the Greenberg transform of $\underline{G}$.
-Then $G$ is a group scheme over $\Fq$ and 
-\[
-G(\Fq) = \underline{G}(\OK)
-\]
-canonically.
-
-\begin{proposition}\label{prop:quasicharacters}
-Let $\underline{G}$ be a smooth group scheme over $\OK$.
-Let $\chi : \underline{G}(\OK) \to \EEx$ be a quasicharacter/continuous linear character. 
-Then there is a Weil sheaf $\cs{L}$ on $\Gr(\underline{G})$ such that $\trFrob{\cs{L}} = \trace \chi$. \todo{Missing proof}
-\end{proposition}
-
-\begin{proof}
-\end{proof}
-
-\subsection{A conjecture on Jacobi theory over finite fields}\label{sec:Jacobi}
-
-%For use in the next section, we recall some basic facts about the Heisenberg-Weil representation.
-
-Let $V$ be a finite-dimensional vector space over a finite field $\Fq$ equipped with a symplectic paring $\langle\ ,\ \rangle : V\times V \to C$, where $C$ is a one-dimensional vector space over $\Fq$.
-Then $V$ is even-dimensional and we may pick a `Lagrangian splitting' $V = U \oplus W$ such that $\langle v,v' \rangle = (u,w') - (u',w)$ for $v=(u,w)$ and $v'=(u',w')$.
-Let $V^\sharp$ be the Heisenberg group determined by $(C, \langle\ ,\ \rangle)$.
-Then $V^\sharp$ is a split extension of $V$ by $C$.
-\[
-\begin{tikzcd}
-\ &&& U \arrow{d} &\\
-1 \arrow{r} & C \arrow{r} & V^\sharp \arrow{r} & \arrow[bend right]{l} V \arrow[bend right]{u} \arrow[bend left]{d} \arrow{r} & 1\\
-1 \arrow{r} & \arrow[equals]{u} C \arrow{r} & \arrow[bend right]{l}  A \arrow{u} \arrow{r} & \arrow[bend right]{l}  W \arrow{u} \arrow{r} & 1 
-\end{tikzcd}
-\]
-
-Let $\psi : C \to \EEx$ be an additive character and let $\omega$ be the Heisenberg representation on $V^\sharp$ with central character $\psi : C \to \EEx$. 
-Let $\Sp(V)$ be the symplectic group determined by the symplectic pairing $\langle\ ,\ \rangle$;
-this group acts on $V^\sharp$.
-Extend $\psi$ to $\psi_A : A \to \EEx$ in the obvious way. 
-Then $\omega \ceq \operatorname{Ind}_A^{V^\sharp}(\psi_A)$ is called the Heisenberg representation of $V^\sharp$.
-
-Observe that $\Sp(V)$ acts on $V^\sharp$.
-The Heisenberg representation determines a representation $\pi_{\omega}$ of $\Sp(V)$ with the same representation space as $\omega$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\omega(g)$ determines an isomorphism of representations $\omega^g \to \omega$, through the Egorov identity \cite{Gurevich-Hadani:geometric_Weil}*{(1.3.1)}.
-Let $W = \pi_\omega \ltimes \omega$ be the representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$ given by $\omega$ and $\pi_\omega$.
-
-\begin{conjecture}\label{conj:Jacobi}
-For $V$, $C$, $\langle\, , \ \rangle$, $\psi$ and $W$ as above, there is a Weil sheaf $\cs{W}$ on the algebraic group $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\cs{W}} = \trace(W)$.
-\end{conjecture}
-
-\subsection{Review of Yu's types}\label{ssec:review}
-
-Every Yu type $(\,^\circ K,\,^\circ \rho)$ may be constructed directly from the following information, derived from a Yu datum:
+A Yu type is then a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$, directly from the following information, derived from a Yu datum:
 \begin{enumerate}
-\item[(0)] a sequence of compact groups 
-\[
-\,^\circ K^0 \subseteq \,^\circ K^1 \subseteq \cdots \subseteq \,^\circ K^d= \,^\circ K;
-\]
-\item[(1)] a continuous representation $\varrho$ of $\,^\circ K^0$;
-\item[(2)] a quasicharacter $\varphi^i : \,^\circ K^i \to \CC^\times$, for $i=0, \ldots d$.
+\labitem{Y0}{Y0} a sequence of compact groups $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$;
+\labitem{Y1}{Y1} a continuous representation $\rho^0$ of $C^0$;
+\labitem{Y2}{Y2} a quasicharacter $\varphi^i : C^i \to \CC^\times$, for $i=0, \ldots d$.
 \end{enumerate}
-The representations $(\varrho, \varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\,^\circ\rho_i$ of $\,^\circ K^i$, for $i=0, \ldots, d-1$, such that $\,^\circ\rho_0 = \varrho$ and $\,^\circ\rho_d = \,^\circ\rho$.
+The representations $(\rho^0, \varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho^d = \rho$.
 
 Since we will need some facts about this construction, we review some further detail here.
-First, Yu introduces compact groups $J^i\subset \,^\circ K$, for $i=0, \ldots d$, such that 
-\[
-\,^\circ K^i = J^0\cdots J^{i}
-\]
-and a natural action of $\,^\circ K^i$ on $J^{i+1}$, for $i=0, \ldots d-1$, defining the groups
-\[
-\,^\circ K^i \ltimes J^{i+1}.
-\]
-He then introduces the following quotients of $J^{i+1}$ and $\,^\circ K^i$, for $i=0, \ldots d-1$.
+First, Yu introduces 
 \begin{enumerate}
-\item[(Q.1)] A quotient $J^{i+1} \to V_{i+1}$ to a finite abelian group, the latter also given the structure of a $\Fq$-vector space.
+\labitem{Y3}{Y3}
+compact groups $J^i\subset C$, for $i=0, \ldots d$, such that 
+$
+C^i = J^0\cdots J^{i}
+$ 
+and, for $i=0, \ldots d-1$, a natural action of $C^i$ on $J^{i+1}$ defining the groups $C^i \ltimes J^{i+1}$.
+\begin{equation}\label{eq:semiprod}
+\begin{tikzcd}
+\ && 1 \arrow{d} && \\
+\ && C^{i}\cap J^{i+1}\arrow{d} && \\
+1 \arrow{r} & J^{i+1} \arrow{r} & C^i \ltimes J^{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} & 1\\
+&& C^{i+1} \arrow{d}{} && \\
+&& 1 &&
+\end{tikzcd}
+\end{equation}
 \end{enumerate}
+%He then introduces the following quotients of $J^{i+1}$ and $C^i$, for $i=0, \ldots d-1$.
+Next, Yu uses this to define a group homomorphism (in fact, a quotient) 
+$
+J^{i+1} \to V_{i+1}
+$
+where $V_{i+1}$ is a finite abelian group, the latter also given the structure of a $\Fq$-vector space.
 The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : C_{i+1} \to \EEx$.
+%\labitem{Q2}{Q2} 
+%\item 
+This, in turn, is used to define a map
+$
+J^{i+1} \to V_{i+1}^\sharp,
+$
+where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $C_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$.
+In fact, the quotient $J^{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J^{i+1} \to H^{i+1}$ and an isomorphism 
+$
+j_{i+1} : H^{i+1} \to V_{i+1}^\sharp,
+$
+where $H^{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:construction}*{}.
+%\labitem{Q3}{Q3} 
+%\item
+Finally, Yu constructs 
+$
+f_{i+1} : C^i \to \Sp(V_{i+1}),
+$
+such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H^{i+1}$ in the sense of \cite{yu:construction}.
+Taken together, this defines
+%\end{enumerate}
 \begin{enumerate}
-\item[(Q.2)] A quotient $J^{i+1} \to V_{i+1}^\sharp$, where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $C_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$.
+\labitem{Y4}{Y4}  a group homomorphism $h_{i+1} : C^i \ltimes J^{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
+\[
+\begin{tikzcd}
+1 \arrow{r} & J^{i+1} \arrow{d} \arrow{r} & C^i \ltimes J^{i+1} \arrow{d}{h_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} \arrow{d}{f_i} & 1\\ 
+1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
+\end{tikzcd}
+\]
 \end{enumerate}
-In fact, the quotient $J^{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J^{i+1} \to H^{i+1}$ and an isomorphism $j_{i+1} : H^{i+1} \to V_{i+1}^\sharp$, where $H^{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:construction}*{}.
-\begin{enumerate}
-\item[(Q.3)] A quotient $\,^\circ f_{i+1} : \,^\circ K^i \to \Sp(V_{i+1})$, such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $\,^\circ K^i$ on $H^{i+1}$ in the sense of \cite{yu:construction}.
-\end{enumerate}
-Taken together, these quotients define another quotient:
-\begin{enumerate}
-\item[(Q)] A quotient $h_{i+1} : \,^\circ K^i \ltimes J^{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
-\[
-\begin{tikzcd}
-1 \arrow{r} & J^{i+1} \arrow{d} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d}{h_{i+1}} \arrow{r} & \,^\circ K^i \arrow{r} \arrow{d}{\,^\circ f_i} & 1\\ 
-1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
-\end{tikzcd}
-\]
-\end{enumerate}
-
-The representations $\,^\circ \rho_i$ are defined recursively. Set $\,^\circ \rho_0 = \varrho$.
-Suppose $i=0, \ldots, d-1$.
-The key to defining the representation $\,^\circ\rho_{i+1}$ from $\,^\circ \rho_i$ is the following diagram.
-\begin{equation}\label{eq:semiprod}
-\begin{tikzcd}
-\ && 1 \arrow{d} && \\
-\ && \,^\circ K^{i}\cap J^{i+1}\arrow{d} && \\
-1 \arrow{r} & J^{i+1} \arrow{r} & \,^\circ K^i \ltimes J^{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & \,^\circ K^i \arrow{r} & 1\\
-&& \,^\circ K^{i+1} \arrow{d}{} && \\
-&& 1 &&
-\end{tikzcd}
-\end{equation}
+
+We can now recall how Yu uses all this to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ and thus the type $(C,\rho) = (C^d,\rho^d)$.
+The representations $\rho^i$ are defined recursively. 
+For the base case $i=0$, the representation $\rho^0$ is part of the datum; see \ref{Y1} above.
+%The key to defining the representation $\rho^{i+1}$ from $\rho^i$ is \ref{Y3}, above.
 Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
-Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $\,^\circ K^i \ltimes J^{i+1}$.
-Write $\inf(\,^\circ\rho_i \otimes \varphi^i)$ for the representation of $\,^\circ K^i \ltimes J^{i+1}$ obtained by pulling back $\,^\circ\rho_i$ along $\,^\circ K^i \ltimes J^{i+1} \to \,^\circ K^i$.
+Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $C^i \ltimes J^{i+1}$.
+Write $\inf(\rho^i \otimes \varphi^i)$ for the representation of $C^i \ltimes J^{i+1}$ obtained by pulling back $\rho^i$ along $C^i \ltimes J^{i+1} \to C^i$. 
 Consider the representation
 \begin{equation}\label{eq:tensor}
-\,^0{\tilde\rho}_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\,^\circ\rho_i \otimes \varphi^i)
+\rho_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\rho^i \otimes \varphi^i)
 \end{equation}
-of $\,^\circ K^i \ltimes J^{i+1}$.
-By construction, the character of this representation satisfies
-\begin{equation}\label{eq:tilderho}
-\trace(\,^0{\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\,^\circ\rho_i)(p_i(y))\ \varphi^i(p_i(y))
-\end{equation}
-for $y \in \,^\circ K^i \ltimes J^{i+1}$.
-By \cite{yu:01a}*{}, the representation $\,^0{\tilde\rho}_{i+1}$ of $\,^\circ K^i \ltimes J^{i+1}$ is trivial on $\,^\circ K^{i}\cap J^{i+1}$ so $\,^0{\tilde\rho}_{i+1}$ descends to $\,^\circ K^{i+1}$.
-This defines $\,^\circ \rho_{i+1}$.\todo{I didn't use $\varphi^d$, so this can't be quite right.}
-%The character of $\,^\circ \rho_d$ on $\,^\circ K^d = \,^\circ K = J^0 \cdots J^d$ satisfies
+of $C^i \ltimes J^{i+1}$.
+%By construction, the character of this representation satisfies
+%\begin{equation}\label{eq:tilderho}
+%\trace({\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\rho^i)(p_i(y))\ \varphi^i(p_i(y))
+%\end{equation}
+%for $y \in C^i \ltimes J^{i+1}$.
+By \cite{yu:01a}*{}, the representation $\rho_{i+1}$ of $C^i \ltimes J^{i+1}$ is trivial on $C^{i}\cap J^{i+1}$ so $\rho_{i+1}$ descends to $C^{i+1}$. 
+This defines the representation $\rho^{i+1}$ of $C^{i+1}$. \todo{I didn't use $\varphi^d$, so this can't be quite right.}
+This completes the recursive definition and this determines $\rho^d = \rho$, which is the representation of $C^d = C$ determining the Yu type $(C,\rho)$.
+%The character of $\rho^d$ on $C^d = C = J^0 \cdots J^d$ satisfies
 %\[
-%\trace(\,^\circ \rho)(k_0 \cdots k_d) = \varrho(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
+%\trace(\rho)(k_0 \cdots k_d) = \rho^0(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
 %\]
@@
 
-\begin{enumerate}
-\item[(K)]
+As a step toward geometrizing the type $(C,\rho)$, we now recall some results from \cite{yu:models}.
+
+%\begin{enumerate}
+%\labitem{M1}{M1}
 By \cite{yu:models}*{Prop 10.2} there is a sequence  
@@
 \]
-of morphisms of affine smooth group schemes of finite type over $\OK$ such that, on $\OK$-points it gives the sequence $\,^\circ K^0 \subseteq \,^\circ K^1 \subseteq \cdots \subseteq \,^\circ K^d= \,^\circ K$ above.
-\item[(J)]
-As explained in \cite{yu:03a}*{\S 10.4}, for each $i=0,\ldots d$, there is morphism of affine smooth group schemes of finite type over $\OK$ 
-\[
-\underline{J}^i \to \underline{G}
-\] 
-such that $\underline{J}^i(\OK) = J^i$ as a subgroup of $\,^\circ K$ and such that the image of the $\OK$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $\,^\circ K^i$, for $i=0, \ldots , d$.
-\item[(S)]
-There is a natural action of $\underline{G}^i$ on $\underline{J}^{i+1}$ in the category of smooth affine group schemes over $\OK$ so that the group
+of morphisms of affine smooth group schemes of finite type over $\OK$ such that, on $\OK$-points it gives the sequence $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$ above.
+Indeed, this is the main result of \cite{yu:models}.
+
+%\labitem{M2}{M2}
+As explained in \cite{yu:03a}*{\S 10.4}, there is morphism of affine smooth group schemes of finite type over $\OK$ 
+\[
+\underline{J}^i \to \underline{G},
+\] 
+for each $i=0,\ldots d$, such that $\underline{J}^i(\OK) = J^i$ as a subgroup of $C$ and such that the image of the $\OK$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $C^i$, for $i=0, \ldots , d$.
+%\labitem{M3}{M3}
+There is a natural action of $\underline{G}^i$ on $\underline{J}^{i+1}$ in the category of smooth affine group schemes over $\OK$ so that the group scheme
 \[
@@
 \]
-has $\OK$-points
-\[
-(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK) = \,^\circ K^i \ltimes J^{i+1}.
-\]
-\end{enumerate}
+gives $(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK) = C^i \ltimes J^{i+1}$
+%\end{enumerate}
 
@@
 Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
-The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $U^{i+1}_\Fq$, where $U^{i+1}_\Fq$, appears as a quotient $J^{i+1}_\Fq \to U^{i+1}_\Fq$ of algebraic groups.
+The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $V^{i+1}_\Fq$, where $V^{i+1}_\Fq$, appears as a quotient $J^{i+1}_\Fq \to V^{i+1}_\Fq$ of algebraic groups.
 Then the quotient $J^{i+1} \to V_{i+1}$ is realized as the composition
 \[
-\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to U^{i+1}_{\Fq}(\Fq) = V_{i+1}.
-\]
-Likewise, the Heisenberg p-group $H^{i+1}$ group may be realized as a quotient of algebraic groups, and $J^{i+1}\to H^{i+1}$ as the composition 
+\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to V^{i+1}_\Fq(\Fq) = V_{i+1}.
+\]
+Likewise, the Heisenberg $p$-group $H^{i+1}$, appearing in \ref{ssec:review}, may be realized as a quotient of algebraic groups, and $J^{i+1}\to H^{i+1}$ as the composition 
 \[
@@
 \]
-Finally, the group homomorphism $\,^\circ f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ may be made geometric in much the same way. 
-Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $\,^\circ f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ is realized as the composition
+Finally, the group homomorphism $f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ may be made geometric in much the same way. 
+Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ is realized as the composition
 \[
@@
 
-Consider the following diagram of smooth group schemes over $\OK$ and compare with \eqref{eq:semiprod}.
+We may now revisit the ingredients in the construction of the representation $\rho$ of $\underline{G}(\OK)$ along the lines indicated by Yu and recalled in Section~\ref{ssec:review}.
+\begin{enumerate}
+\labitem{M0}{M0}
+The compact groups $C^i$ have been replaced by the smooth group schemes $\underline{G}^i$.
+\labitem{M1}{M1}
+The continuous representation $\rho^0$ of $C^0$ is a representation of $\underline{G}^0(\OK)$ obtained by inflation along $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$ from a representation $\rho_0$ of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
+In fact, $\rho_0$ is itself obtained by pulling back a representation $\rho_0^\reductive$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+\labitem{M2}{M2} The quasicharacters $\varphi^i$ are quasicharacters of $\underline{G}^i(\OK)$, for $i=0, \ldots d$.
+\labitem{M3}{M3}
+Diagram \eqref{eq:semiprod} is now replaced by the following diagram of smooth group schemes over $\OK$.
 \begin{equation}\label{eq:pimodel}
@@
 \end{equation}
-
-We may now revisit the ingredients in the construction of the representation $\,^\circ \rho$ of $\underline{G}(\OK)$ along the lines indicated by Yu and recalled at the beginning of this section.
-\begin{enumerate}
-\item The continuous representation $\varrho$ of $\,^\circ K^0$ is a representation of $\underline{G}^0(\OK)$ obtained by inflation along $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$. 
-Let $\tau$ be that representation of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
-In fact, $\tau$ is itself obtained by pulling back a representation $\sigma$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
-\item Quasicharacters $\varphi^i : \underline{G}^i(\OK) \to \CC^\times$, for $i=0, \ldots d$.
-\item The representation $h_{i+1}^*(W_{i+1})$ of $(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK)$ is obtained by pulling back a representation along 
+\labitem{M4}{M4}
+The representation $h_{i+1}^*(W_{i+1})$ appearing in \ref{Y4} is now obtained by pulling back a representation along 
 \[
@@
 \end{enumerate}
-Regarding the construction of the type $(\,^\circ  K,\,^\circ \rho)$, the paper \cite{yu:models} concludes with the following provocative observation, which we have just revisited.
+
+Regarding the construction of the type $(C,\rho)$, the paper \cite{yu:models} concludes with the following provocative observation, which we have just revisited.
 \begin{quotation}
@@
 \end{quotation}
-
-In fact, Yu's description of how to assemble $\,^\circ \rho$ from $(\varrho, \varphi^0, \ldots , \varphi^d)$ is slightly different, but equivalent, to what we have done here \cite{Yu:models}*{}.
+%In fact, Yu's description of how to assemble $\rho$ from $(\rho^0, \varphi^0, \ldots , \varphi^d)$ is slightly different, but equivalent, to what we have done here \cite{Yu:models}*{}.
 
@@
 
-Since Yu's theory refers to complex representations, and since our geometrization uses $\ell$-adic sheaves, we fix, once and for all, an isomorphism $\CC \approx \EE$.
+Finally, we come to the main result of Section~\ref{sec:types}.
+Since Yu's theory refers to complex representations, and since our geometrization uses $\ell$-adic sheaves, we grit our teeth and fix an isomorphism $\CC \approx \EE$.
 
 \begin{proposition}\label{prop:geotypes}
-Let $(\,^\circ K,\,^\circ \rho)$ be a Yu type.
+Let $(C,\rho)$ be a Yu type, constructed as in Section~\ref{ssec:review}.
+Let $G^i = \Gr_{R}(\underline{G}^i)$ be the Greenberg transform of the smooth group scheme $\underline{G}^i$ appearing in Section~\ref{ssec:models}.
+Assume $\pi_0(\underline{G}^0)_\Fq^\reductive)$ is cyclic.
 Assume Conjecture~\ref{conj:Jacobi}.
-and also that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
-Let $G$ be the Greenberg transform of the smooth group scheme $\underline{G}$.
-Then there is a virtual Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\mathcal{F}} = \trace(\,^\circ \rho)$ under the canonical isomorphism $G(\Fq) = \underline{G}(\OK)$.
+Then there is a virtual Weil sheaf $\cs{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
 \end{proposition}
@@
 %Now we explain how to geometrize the characters of these ingredient representations, using the discussion from Section~\ref{ssec:models}.  
-
-By continuity of the quasicharacters $\varphi^i : \underline{G}^i(\OK) \to \CC^\times$, there is some $m \in \NN$ and a factorization
-\[
-\begin{tikzcd}
-\underline{G}^i(\OK) \arrow{rr}{\varphi^i} \arrow{rd} && \EEx\\
-& \underline{G}^i(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\varphi^i_m} 
-\end{tikzcd}
-\] 
-for each $i=0, \ldots d$.\todo{Fix notation: $\phi$ to $\varphi$}
-Using Proposition~\ref{prop:quasicharacters}, let $\cs{L}^i_m$ be a geometrization of the linear character $\phi^i_m: \Gr^{\OK}_{m}(\underline{G}^i) \to \CC^\times$; so
-\[
-\trFrob{\cs{L}^i_m} = \trace \phi^i_m.
+Recall that $G^i(\Fq) = \underline{G}^i(R) = C^i$, canonically.
+By continuity of the quasicharacters $\varphi^i : G^i(\Fq) \to \CC^\times$, there is some $m \in \NN$ and a factorization
+\[
+\begin{tikzcd}
+G^i(\Fq) \arrow{rr}{\varphi^i} \arrow{rd} && \EEx\\
+& \underline{G}^i(\OK/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi^i_m} 
+\end{tikzcd}
+\] 
+for each $i=0, \ldots d$.
+Set $G_m^i = \Gr_m^{R}(\underline{G}^i)$.
+Then $G_m^i$ is a smooth group scheme over $\Fq$ and $G_m^i(\Fq) = \underline{G}^i(R/\mathfrak{p}^{m+1})$, canonically.
+Using Proposition~\ref{prop:quasicharacters}, let $\cs{L}^i_m$ be a geometrization of the linear character $\varphi^i_m: G_m^i \to \CC^\times$; so
+\[
+\trFrob{\cs{L}^i_m} = \trace \varphi^i_m.
 \]
@@
 
-By \cite{lusztig:CSDG}, there is a Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
-\[
-\trFrob{A} = \trace \sigma.
+By \cite{lusztig:CSDG}, there is a virtual Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
+\[
+\trFrob{A} = \trace \rho_0^\reductive.
 \]
@@
 \[
-\trFrob{A^0} = \trace \tau.
-\]
-The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $G^0 = \Gr^{\OK}_0(\underline{G}^0)$ \cite{CR}*{\S 4.3}.
-With $m\in \NN$ as above, let $\cs{A}_m^0$ be the pull-back of $A^0$ along the affine morphism
-$\Gr^{\OK}_{m}(\underline{G}^0) \to \Gr^{\OK}_{0}(\underline{G}^0)$.
+\trFrob{A^0} = \trace \rho_0.
+\]
+The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $G_0^0 = \Gr^{\OK}_0(\underline{G}^0)$ \cite{CR}*{\S 4.3}.
+With $m\in \NN$ as above, let $\cs{A}_m^0$ be the Weil sheaf on the algebraic group$G_m^i$ obtained by pull-back from $A^0$ along the affine morphism $G_m^i \to G_0^0$.
 Factor
@@
 \begin{tikzcd}
-\underline{G}^0(\OK) \arrow{rr}{\trace(\varrho)} \arrow{rd} && \EE \\
-& \underline{G}^0(\OK/\mathfrak{p}_K^{m+1}) \arrow{ru}[swap]{\trace(\varrho)_m} 
-\end{tikzcd}
-\]
-Then $\cs{A}_m^0$ is a Weil sheaf on $\underline{G}^i$, from which $\trace(\varrho)_m$ may be recovered:
-\[
-\trFrob{\cs{A}^0_m} = \trace(\varrho)_m
+G^0(\Fq) \arrow{rr}{\trace(\rho^0)} \arrow{rd} && \EE \\
+& G_m^0(\Fq) \arrow{ru}[swap]{\trace(\rho^0)_m} 
+\end{tikzcd}
+\]
+Observe that $\trace(\rho^0)_m$ may be recovered from $\cs{A}_m^0$:
+\[
+\trFrob{\cs{A}^0_m} = \trace(\rho^0)_m
 \]
 %Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{\OK}(\underline{G}^0) \to \Gr^{\OK}_{m}(\underline{G}^0)$.
-%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^0)$ from which the character of $\varrho$ may be recovered.
+%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^0)$ from which the character of $\rho^0$ may be recovered.
 
 Consider the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ and the Heisenberg-Weil representation $W_{i+1}$ appearing in Section~\ref{ssec:models}.
-Let $\cs{W}^{i+1}$ be the Weil sheaf promised by Conjecture~\ref{conj:Jacobi} on the Jacobi group such that
-\[
-\trFrob{\cs{W}^{i+1}} = \trace(W_{i+1}).
+Let $\cs{W}_{i+1}$ be the Weil sheaf promised by Conjecture~\ref{conj:Jacobi} on the Jacobi group such that
+\[
+\trFrob{\cs{W}_{i+1}} = \trace(W_{i+1}).
 \]
 Recall from Section~\ref{ssec:models} that $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ is a quotient of the special fibre of the smooth group scheme $\underline{G}^{i} \ltimes \underline{J}^{i+1}$.
-Let $\cs{W}_0^{i+1}$ be the Weil sheaf on the special fibre of $\underline{G}^{i} \ltimes \underline{J}^{i+1}$ obtained from $W^{i+1}$ by pullback. 
-Let $\cs{W}_m^{i+1}$ be the Weil sheaf on $\Gr^{\OK}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1})$ obtained from $\cs{W}_0^{i+1}$ by pullback along the affine morphism
-$\Gr^{\OK}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1}) \to \Gr^{\OK}_0(\underline{G}^{i} \ltimes \underline{J}^{i+1})$.
-
-We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{\OK}_m(\underline{G}^{i})$, for $i=1,\ldots ,d$, recursively, following the construction of the representations $\,^0\rho_i$, reviewed in Section~\ref{ssec:review}.
+Let $\cs{W}_0^{i+1}$ be the Weil sheaf on the special fibre of $\underline{G}^{i} \ltimes \underline{J}^{i+1}$ obtained from $W_{i+1}$ by pullback. 
+Let $\cs{W}_m^{i+1}$ be the Weil sheaf on $\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1})$ obtained from $\cs{W}_0^{i+1}$ by pullback along the affine morphism
+$\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1}) \to \Gr^{R}_0(\underline{G}^{i} \ltimes \underline{J}^{i+1})$.
+
+We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{R}_m(\underline{G}^{i})$, for $i=1,\ldots ,d$, recursively, following the construction of the representations $\rho^i$, as reviewed in Section~\ref{ssec:review}.
+We have already defined $\cs{A}^0_m$.
+\iffalse
 We have already defined $\cs{A}^0_m$ so that 
 \[
-\trFrob{\cs{A}^0_m} = \trace(\,^\circ \rho_0)_m
-\]
-where $\trace(\,^\circ \rho_0)_m : G_m^0(\Fq) \to \EE$ is defined by 
-\[
-\begin{tikzcd}
-G^0(\Fq) \arrow{rr}{\trace(\,^\circ \rho_0)} \arrow{rd} && \EE\\
-& G^0_m(\Fq). \arrow{ru}[swap]{\trace(\,^\circ \rho_0)_m} & 
+\trFrob{\cs{A}^0_m} = \trace(\rho_0)_m
+\]
+where $\trace(\rho_0)_m : G_m^0(\Fq) \to \EE$ is defined by 
+\[
+\begin{tikzcd}
+G^0(\Fq) \arrow{rr}{\trace(\rho_0)} \arrow{rd} && \EE\\
+& G^0_m(\Fq). \arrow{ru}[swap]{\trace(\rho_0)_m} & 
 \end{tikzcd}
@@
 and the canonical identification $G_m^0(\Fq) = \underline{G}^0(\OK/\mathfrak{p}_K^{m+1})$.
-Suppose $\cs{A}^i_m$ on $G_m^i$ is defined and \[
-\begin{tikzcd}
-G^i(\Fq) \arrow{rr}{\trace(\,^\circ \rho_i)} \arrow{rd} && \EE\\
+\fi
+Suppose $\cs{A}^i_m$ on $G_m^i$ is defined such that
+\[
+\begin{tikzcd}
+G^i(\Fq) \arrow{rr}{\trace(\rho^i)} \arrow{rd} && \EE\\
 & G_m^i(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m^i}} & 
@@
 commutes.
-We shall construct $\cs{A}_m^{i+1}$ on $G_m^{i+1}$ so that 
-\[
-\begin{tikzcd}
-G^{i+1}(\Fq) \arrow{rr}{\trace(\,^\circ \rho_{i+1})} \arrow{rd} && \EE\\
-& G_m^{i+1}(\Fq)\arrow{ru}[swap]{{\trFrob{\cs{A}_m^i}} } & 
-\end{tikzcd}
-\]
-
-Applying the Greenberg functor $\Gr^{\OK}_m$, to \eqref{eq:pimodel} gives
+Applying the Greenberg functor $\Gr^{R}_m$, to \eqref{eq:pimodel} gives
 \begin{equation}\label{eq:pi}
@@
 \end{equation}
-where $J_m^{i+1} \ceq \Gr^{\OK}_m(\underline{J}^{i+1})$ and $G_m^{i} \ceq \Gr^{\OK}_m(\underline{G}^{i})$
+where $J_m^{i+1} \ceq \Gr^{R}_m(\underline{J}^{i+1})$ and $G_m^{i} \ceq \Gr^{R}_m(\underline{G}^{i})$.
 By \cite{BG-A}*{Prop 7.1}, the sequences are exact.
@@
 \[
-\cs{W}_m^{i+1} \otimes (p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
+\cs{B}_m^{i+1} \ceq \cs{W}_m^{i+1} \otimes (p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
 \]
 on $G_m^{i}\ltimes J_m^{i+1}$ and compare with \eqref{eq:tensor}.
-With reference to the morphism $\pi_m^{i+1} : G_m^i \ltimes J_m^{i+1} \to G_m^{i+1}$ from \eqref{eq:pi}, define \todo{Reference needed here.}
-\[
-\cs{\tilde A}_m^{i+1} \ceq R(\pi_m^{i+1})_! (\cs{W}_m^{i+1} \otimes (p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})).
+With reference to the morphism $\pi_m^{i+1} : G_m^i \ltimes J_m^{i+1} \to G_m^{i+1}$ from \eqref{eq:pi}, define 
+\[
+\cs{\tilde A}_m^{i+1} \ceq (\pi_m^{i+1})_! (\cs{B}_m^{i+1}).
 \]
@@
 \trFrob{\cs{\tilde A}^{i+1}_m}(x)
-&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1} \otimes (p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^i)}(y)\\
-&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{W}_m^{i+1}}(y)\  \trFrob{\cs{A}_m^{i}}(p_m^{i}(y) )\ \trFrob{\cs{L}_m^i}(p_m^{i}(y)).
+&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{B}_m^{i+1}}(y).
 \end{eqnarray*}
-Comparing with \eqref{eq:tilderho}, we see that 
-\[
-y \mapsto \trFrob{\cs{W}_m^{i+1}}(y)\ \trFrob{\cs{A}_m^{i}}(p_m^{i}(y))\ \trFrob{\cs{L}_m^i}(p_m^{i}(y))
-\]
-is precisely the function obtained by factoring the character of $\,^\circ {\tilde \rho}_{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK/\mathfrak{p}_K^{m+1})$, using the canonical identification $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK/\mathfrak{p}_K^{m+1})$.
-In particular, this is trivial on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$.
+Comparing with \eqref{eq:tensor}, we see that $\trFrob{\cs{B}_m^{i+1}}$ is precisely the function obtained by factoring the character of $\rho^{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK/\mathfrak{p}_K^{m+1})$, using the canonical identification $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK/\mathfrak{p}_K^{m+1})$.
+In particular, $\trFrob{\cs{B}^{i+1}_m}$ is trivial on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$.
 It follows that 
 \[
-\trFrob{\cs{\tilde A}^{i+1}_m} = n \trace(\,^\circ \rho_{i+1})
-\]
-on $G_m^{i+1}(\Fq)$ with $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$. \todo{Hmm... Homomorphism?}
-\todo{If $n$ is a power of $q$, then we can use Tate twists to avoid working with virtual sheaves! Is $G^{i}\cap J_m^{i+1}$ unipotent? Is so, then there's a chance.}
+\trFrob{\cs{\tilde A}^{i+1}_m} = n \trace(\rho^{i+1})
+\]
+on $G_m^{i+1}(\Fq)$ with $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$.
 Let $\cs{A}_m^{i+1}$ be the \emph{virtual} Weil sheaf on $G_m^i$ given by $\cs{A}_m^{i+1} = \frac{1}{n} \cs{\tilde A}_m^{i+1}$. 
 %
-This completes the inductive definition of $\cs{A}_m^i$ with the desired property.
-
-Now set $\cs{F}_m = \cs{A}_m^{d}$.
-Then $\cs{F}_m$ is a virtual Weil sheaf on $G_m = \Gr^{\OK}_m(\underline{G})$ such that
-\[
-\begin{tikzcd}
-G(\Fq) \arrow{rr}{\trace(\,^\circ \rho)} \arrow{rd} && \EE\\
+This completes the inductive definition of $\cs{A}_m^i$ so that the following diagram commutes.
+\[
+\begin{tikzcd}
+G^{i+1}(\Fq) \arrow{rr}{\trace(\rho^{i+1})} \arrow{rd} && \EE\\
+& G_m^{i+1}(\Fq)\arrow{ru}[swap]{{\trFrob{\cs{A}_m^{i+1}}} } & 
+\end{tikzcd}
+\]
+
+Now set $\cs{A}_m = \cs{A}_m^{d}$.
+Then $\cs{A}_m$ is a virtual Weil sheaf on $G_m = \Gr^{R}_m(\underline{G})$ such that
+\[
+\begin{tikzcd}
+G(\Fq) \arrow{rr}{\trace(\rho)} \arrow{rd} && \EE\\
 & G_m(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m}} & 
@@
 commutes.
-Let $\cs{F}$ be the virtural Weil sheaf on the group scheme $G= \Gr^{\OK}(\underline{G})$ obtained by pullback along $G \to G_m$.
+Let $\cs{A}$ be the virtural Weil sheaf on the group scheme $G= \Gr_{R}(\underline{G})$ obtained by pullback along $G \to G_m$.
 Then 
 \[
-\trFrob{\cs{F}} = \trace(\,^\circ \rho),
+\trFrob{\cs{A}} = \trace(\rho),
 \] 
@@
 A representation $\sigma$ of the $\Fq$-points of the reductive group $(\underline{G}^0)_\Fq^\reductive$ over $\Fq$. 
-Then $\tau$ is the representation of the $\Fq$-points of the special fibre of the smooth model $\underline{G}^0$ over $\OK$ and the representation $\varrho$ of $\underline{G}(\OK)$ is produced from $\tau$ by inflation.
+Then $\tau$ is the representation of the $\Fq$-points of the special fibre of the smooth model $\underline{G}^0$ over $\OK$ and the representation $\rho^0$ of $\underline{G}(\OK)$ is produced from $\tau$ by inflation.
 Suppose $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
@@
 \[
-\trace \varrho(k) = \trFrob{\bar B}(k_\Fq)
+\trace \rho^0(k) = \trFrob{\bar B}(k_\Fq)
 \]

### 2016-02-23 followup.tex
Added EGA citation to followup.tex

--- 2016-01-30 followup.tex
@@
 Let $G$ be a smooth group scheme over a finite field $\Fq$; that is, let $G$ be a group scheme over $\Fq$
-for which the structure morphism $G \to \Spec{\Fq}$ is smooth in the sense of \todo{include reference for this definition}.
+for which the structure morphism $G \to \Spec{\Fq}$ is smooth in the sense of \cite{EGAIV4}*{Def 17.3.1}.
 This implies $G \to \Spec{\Fq}$ is locally of finite type, but not that it is of finite type.

### 2016-02-23 followup.tex
Fixing some references

@@
 Let $\underline{G}$ be a smooth group scheme over $R$.
-Here we shall use  \cite{BGA} for the definition and fundamental properties of the Greenberg transform.
+Here we shall use  \cite{bertapelle-gonzales:Greenberg} for the definition and fundamental properties of the Greenberg transform.
 Let $G$ be the Greenberg transform of $\underline{G}$; then $G$ is a group scheme over $\Fq$ and 
@@
 $
-where $H^{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:construction}*{}.
+where $H^{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:01a}*{}.
 %\labitem{Q3}{Q3} 
@@
 $
-such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H^{i+1}$ in the sense of \cite{yu:construction}.
+such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H^{i+1}$ in the sense of \cite{yu:01a}.
 Taken together, this defines
@@
 
-As a step toward geometrizing the type $(C,\rho)$, we now recall some results from \cite{yu:models}.
+As a step toward geometrizing the type $(C,\rho)$, we now recall some results from \cite{yu:03a}.
 
@@
 %\labitem{M1}{M1}
-By \cite{yu:models}*{Prop 10.2} there is a sequence  
+By \cite{yu:03a}*{Prop 10.2} there is a sequence  
 \[
@@
 of morphisms of affine smooth group schemes of finite type over $\OK$ such that, on $\OK$-points it gives the sequence $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$ above.
-Indeed, this is the main result of \cite{yu:models}.
+Indeed, this is the main result of \cite{yu:03a}.
 
@@
 
-Regarding the construction of the type $(C,\rho)$, the paper \cite{yu:models} concludes with the following provocative observation, which we have just revisited.
+Regarding the construction of the type $(C,\rho)$, the paper \cite{yu:03a} concludes with the following provocative observation, which we have just revisited.
 \begin{quotation}
@@
 %Let $\cs{L}^i$ be the  Weil sheaf on $\Gr^{\OK}(\underline{G}^i)$ obtained from $\cs{L}^i_m$ by pullback along $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_{m}(\underline{G}^i)$. 
-%Then $\cs{L}^i$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^i)$ from which the quasicharacter $\varphi^i$ may be recovered.
-
-By \cite{lusztig:CSDG}, there is a virtual Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
+%Then $\cs{L}^i$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^i)$ from which the quasicharacter $\varphi^i$ may be recovered.
+
+By \cite{lusztig:disconnected1}, there is a virtual Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
 \[
@@
 \]
-The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $G_0^0 = \Gr^{\OK}_0(\underline{G}^0)$ \cite{CR}*{\S 4.3}.
+The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $G_0^0 = \Gr^{\OK}_0(\underline{G}^0)$ \cite{cunningham-roe:13a}*{\S 4.3}.
 With $m\in \NN$ as above, let $\cs{A}_m^0$ be the Weil sheaf on the algebraic group$G_m^i$ obtained by pull-back from $A^0$ along the affine morphism $G_m^i \to G_0^0$.
@@
 %Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{\OK}(\underline{G}^0) \to \Gr^{\OK}_{m}(\underline{G}^0)$.
-%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{CR}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^0)$ from which the character of $\rho^0$ may be recovered.
+%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^0)$ from which the character of $\rho^0$ may be recovered.
 
@@
 where $J_m^{i+1} \ceq \Gr^{R}_m(\underline{J}^{i+1})$ and $G_m^{i} \ceq \Gr^{R}_m(\underline{G}^{i})$.
-By \cite{BG-A}*{Prop 7.1}, the sequences are exact.
+By \cite{bertapelle-gonzales:Greenberg}*{Prop 7.1}, the sequences are exact.
 Consider $\cs{A}_m^{i}\otimes \cs{L}_m^{i}$ on $G_m^{i}$ and let 

### 2016-02-23 followup.tex
Adding reference to bibliography
Yay Loren!

@@
 For use below, we recall some basic facts about the Heisenberg-Weil representation and make a conjecture about the geometrization of these representations.
-We refer the reader to \cite{BS} for more detail.
+We refer the reader to \cite{berndt-schmidt:98a} for more details.
 
@@
 %
+
 A Yu type is then a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$, directly from the following information, derived from a Yu datum:
@@
 Since we will need some facts about this construction, we review some further detail here.
+
 First, Yu introduces 
@@
 %He then introduces the following quotients of $J^{i+1}$ and $C^i$, for $i=0, \ldots d-1$.
+
 Next, Yu uses this to define a group homomorphism (in fact, a quotient) 
@@
 such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H^{i+1}$ in the sense of \cite{yu:01a}.
+
 Taken together, this defines
@@
 
-We can now recall how Yu uses all this to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ and thus the type $(C,\rho) = (C^d,\rho^d)$.
+We can now recall how Yu uses all this to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ and thus the type $(C,\rho) = (C^d,\rho^d\otimes \varphi^d)$.
 The representations $\rho^i$ are defined recursively. 
-For the base case $i=0$, the representation $\rho^0$ is part of the datum; see \ref{Y1} above.
-%The key to defining the representation $\rho^{i+1}$ from $\rho^i$ is \ref{Y3}, above.
+For the base case $i=0$, the representation $\rho^0$ is just $\rho_0$; see \ref{Y1} above.
 Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
@@
 By \cite{yu:01a}*{}, the representation $\rho_{i+1}$ of $C^i \ltimes J^{i+1}$ is trivial on $C^{i}\cap J^{i+1}$ so $\rho_{i+1}$ descends to $C^{i+1}$.
-This defines the representation $\rho^{i+1}$ of $C^{i+1}$. \todo{I didn't use $\varphi^d$, so this can't be quite right.}
-This completes the recursive definition and this determines $\rho^d = \rho$, which is the representation of $C^d = C$ determining the Yu type $(C,\rho)$.
+
+This defines the representation $\rho^{i+1}$ of $C^{i+1}$. 
+This completes the recursive definition and thus determines $\rho^d$. 
+Now set $\rho \ceq \rho^d\otimes \varphi^d$, which is the representation of $C^d = C$ determining the Yu type $(C,\rho)$.
 %The character of $\rho^d$ on $C^d = C = J^0 \cdots J^d$ satisfies
@@
 \]
-of morphisms of affine smooth group schemes of finite type over $\OK$ such that, on $\OK$-points it gives the sequence $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$ above.
+of morphisms of affine smooth group schemes of finite type over $R$ such that, on $R$-points it gives the sequence $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$ above.
 Indeed, this is the main result of \cite{yu:03a}.
@@
 %\labitem{M2}{M2}
-As explained in \cite{yu:03a}*{\S 10.4}, there is morphism of affine smooth group schemes of finite type over $\OK$ 
+As explained in \cite{yu:03a}*{\S 10.4}, there is morphism of affine smooth group schemes of finite type over $R$ 
 \[
@@
 \] 
-for each $i=0,\ldots d$, such that $\underline{J}^i(\OK) = J^i$ as a subgroup of $C$ and such that the image of the $\OK$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $C^i$, for $i=0, \ldots , d$.
+for each $i=0,\ldots d$, such that $\underline{J}^i(R) = J^i$ as a subgroup of $C$ and such that the image of the $R$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $C^i$, for $i=0, \ldots , d$.
 %\labitem{M3}{M3}
-There is a natural action of $\underline{G}^i$ on $\underline{J}^{i+1}$ in the category of smooth affine group schemes over $\OK$ so that the group scheme
+There is a natural action of $\underline{G}^i$ on $\underline{J}^{i+1}$ in the category of smooth affine group schemes over $R$ so that the group scheme
 \[
@@
 \]
-gives $(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK) = C^i \ltimes J^{i+1}$
+gives $(\underline{G}^i \ltimes \underline{J}^{i+1})(R) = C^i \ltimes J^{i+1}$
 %\end{enumerate}
@@
 \[
-\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to V^{i+1}_\Fq(\Fq) = V_{i+1}.
+\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to V^{i+1}_\Fq(\Fq) = V_{i+1}.
 \]
@@
 \[
-\underline{J}^{i+1}(\OK) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H^{i+1}.
+\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H^{i+1}.
 \]
@@
 \[
-\underline{G}^{i}(\OK) \to \underline{G}^{i}(\Fq) = \underline{G}^{i}_\Fq(\Fq) \to  \underline{G}^{i,\reductive}_\Fq(\Fq) \to W^{i+1}_{\Fq}(\Fq) = \Sp(V_{i+1}).
+\underline{G}^{i}(R) \to \underline{G}^{i}(\Fq) = \underline{G}^{i}_\Fq(\Fq) \to  \underline{G}^{i,\reductive}_\Fq(\Fq) \to W^{i+1}_{\Fq}(\Fq) = \Sp(V_{i+1}).
 \]
@@
 where the last two rows are now understood as forming a diagram in the category of algebraic groups over $\Fq$. 
-This realizes the Jacobi group $\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp$ as a quotient of the special fibre of the smooth group scheme $\underline{G}^i \ltimes \underline{J}^{i+1}$ over $\OK$.
-
-We may now revisit the ingredients in the construction of the representation $\rho$ of $\underline{G}(\OK)$ along the lines indicated by Yu and recalled in Section~\ref{ssec:review}.
+This realizes the Jacobi group $\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp$ as a quotient of the special fibre of the smooth group scheme $\underline{G}^i \ltimes \underline{J}^{i+1}$ over $R$.
+
+We may now revisit the ingredients in the construction of the representation $\rho$ of $\underline{G}(R)$ along the lines indicated by Yu and recalled in Section~\ref{ssec:review}.
 \begin{enumerate}
@@
 \labitem{M1}{M1}
-The continuous representation $\rho^0$ of $C^0$ is a representation of $\underline{G}^0(\OK)$ obtained by inflation along $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$ from a representation $\rho_0$ of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
-In fact, $\rho_0$ is itself obtained by pulling back a representation $\rho_0^\reductive$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
-\labitem{M2}{M2} The quasicharacters $\varphi^i$ are quasicharacters of $\underline{G}^i(\OK)$, for $i=0, \ldots d$.
+The continuous representation $\rho_0$ of $C^0$ is a representation of $\underline{G}^0(R)$ obtained by inflation along $\underline{G}^0(R) \to \underline{G}^0(\Fq)$ from a representation $\varrho_0$ of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
+In fact, $\varrho_0$ is itself obtained by pulling back a representation $\varrho_0^\reductive$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+\labitem{M2}{M2} The quasicharacters $\varphi^i$ are quasicharacters of $\underline{G}^i(R)$, for $i=0, \ldots d$.
 \labitem{M3}{M3}
-Diagram \eqref{eq:semiprod} is now replaced by the following diagram of smooth group schemes over $\OK$.
+Diagram \eqref{eq:semiprod} is now replaced by the following exact diagram of smooth group schemes over $R$.
 \begin{equation}\label{eq:pimodel}
@@
 \[
-(\underline{G}^i \ltimes \underline{J}^{i+1})(\OK) \to (\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq).
+(\underline{G}^i \ltimes \underline{J}^{i+1})(R) \to (\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq).
 \]
@@
 G^i(\Fq) \arrow{rr}{\varphi^i} \arrow{rd} && \EEx\\
-& \underline{G}^i(\OK/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi^i_m} 
+& \underline{G}^i(R/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi^i_m} 
 \end{tikzcd}
@@
 \]
-%Recall that the full Greenberg transform $\Gr^{\OK}(\underline{G}^i)$ is a group scheme over $\Fq$ such that $\Gr^{\OK}(\underline{G}^i)(\Fq) = \underline{G}^i(\Fq)$, canonically, and comes equipped with a morphism $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_m(\underline{G}^i)$.
-%Let $\cs{L}^i$ be the  Weil sheaf on $\Gr^{\OK}(\underline{G}^i)$ obtained from $\cs{L}^i_m$ by pullback along $\Gr^{\OK}(\underline{G}^i) \to \Gr^{\OK}_{m}(\underline{G}^i)$. 
-%Then $\cs{L}^i$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^i)$ from which the quasicharacter $\varphi^i$ may be recovered.
+%Recall that the full Greenberg transform $\Gr^{R}(\underline{G}^i)$ is a group scheme over $\Fq$ such that $\Gr^{R}(\underline{G}^i)(\Fq) = \underline{G}^i(\Fq)$, canonically, and comes equipped with a morphism $\Gr^{R}(\underline{G}^i) \to \Gr^{R}_m(\underline{G}^i)$.
+%Let $\cs{L}^i$ be the  Weil sheaf on $\Gr^{R}(\underline{G}^i)$ obtained from $\cs{L}^i_m$ by pullback along $\Gr^{R}(\underline{G}^i) \to \Gr^{R}_{m}(\underline{G}^i)$. 
+%Then $\cs{L}^i$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G}^i)$ from which the quasicharacter $\varphi^i$ may be recovered.
 
@@
 \[
-\trFrob{A} = \trace \rho_0^\reductive.
+\trFrob{A} = \trace \varrho_0^\reductive.
 \]
@@
 \[
-\trFrob{A^0} = \trace \rho_0.
-\]
-The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $G_0^0 = \Gr^{\OK}_0(\underline{G}^0)$ \cite{cunningham-roe:13a}*{\S 4.3}.
-With $m\in \NN$ as above, let $\cs{A}_m^0$ be the Weil sheaf on the algebraic group$G_m^i$ obtained by pull-back from $A^0$ along the affine morphism $G_m^i \to G_0^0$.
+\trFrob{A^0} = \trace \varrho_0.
+\]
+The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $G_0^0 = \Gr^{R}_0(\underline{G}^0)$ \cite{cunningham-roe:13a}*{\S 4.3}.
+With $m\in \NN$ as above, let ${A}_m^0$ be the Weil sheaf on the algebraic group $G_m^i$ obtained by pull-back from $A^0$ along the affine morphism $G_m^i \to G_0^0$.
 Factor
@@
 \begin{tikzcd}
-G^0(\Fq) \arrow{rr}{\trace(\rho^0)} \arrow{rd} && \EE \\
-& G_m^0(\Fq) \arrow{ru}[swap]{\trace(\rho^0)_m} 
-\end{tikzcd}
-\]
-Observe that $\trace(\rho^0)_m$ may be recovered from $\cs{A}_m^0$:
-\[
-\trFrob{\cs{A}^0_m} = \trace(\rho^0)_m
-\]
-%Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{\OK}(\underline{G}^0) \to \Gr^{\OK}_{m}(\underline{G}^0)$.
-%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{\OK}(\underline{G}^0)$ from which the character of $\rho^0$ may be recovered.
+G^0(\Fq) \arrow{rr}{\trace(\rho_0)} \arrow{rd} && \EE \\
+& G_m^0(\Fq) \arrow{ru}[swap]{\trace(\rho_0)_m} 
+\end{tikzcd}
+\]
+Observe that $\trace(\rho_0)_m$ may be recovered from ${A}_m^0$:
+\[
+\trFrob{{A}^0_m} = \trace(\rho_0)_m
+\]
+%Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{R}(\underline{G}^0) \to \Gr^{R}_{m}(\underline{G}^0)$.
+%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G}^0)$ from which the character of $\rho^0$ may be recovered.
 
@@
 
-We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{R}_m(\underline{G}^{i})$, for $i=1,\ldots ,d$, recursively, following the construction of the representations $\rho^i$, as reviewed in Section~\ref{ssec:review}.
-We have already defined $\cs{A}^0_m$.
-\iffalse
-We have already defined $\cs{A}^0_m$ so that 
-\[
-\trFrob{\cs{A}^0_m} = \trace(\rho_0)_m
-\]
-where $\trace(\rho_0)_m : G_m^0(\Fq) \to \EE$ is defined by 
-\[
-\begin{tikzcd}
-G^0(\Fq) \arrow{rr}{\trace(\rho_0)} \arrow{rd} && \EE\\
-& G^0_m(\Fq). \arrow{ru}[swap]{\trace(\rho_0)_m} & 
-\end{tikzcd}
-\]
-and the canonical identification $G_m^0(\Fq) = \underline{G}^0(\OK/\mathfrak{p}_K^{m+1})$.
-\fi
-Suppose $\cs{A}^i_m$ on $G_m^i$ is defined such that
+We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{R}_m(\underline{G}^{i})$, for $i=0,\ldots ,d$, recursively, following the construction of the representations $\rho^i$, as reviewed in Section~\ref{ssec:review}.
+First, set $\cs{A}_m^i = A_m^0$ and note that 
+\[
+\begin{tikzcd}
+G^0(\Fq) \arrow{rr}{\trace(\rho^0)} \arrow{rd} && \EE\\
+& G^0_m(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m^0}} & 
+\end{tikzcd}
+\]
+commutes.
+Now, suppose $\cs{A}^i_m$ on $G_m^i$ is defined such that
 \[
@@
 By \cite{bertapelle-gonzales:Greenberg}*{Prop 7.1}, the sequences are exact.
-Consider $\cs{A}_m^{i}\otimes \cs{L}_m^{i}$ on $G_m^{i}$ and let 
-\[
-(p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
-\]
-be the Weil sheaf on $G_m^{i}\ltimes J_m^{i+1}$ obtained by pullback along $G_m^{i}\ltimes J_m^{i+1} \to G_m^{i}$.
+%Consider $\cs{A}_m^{i}\otimes \cs{L}_m^{i}$ on $G_m^{i}$ and let 
+%\[
+%(p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
+%\]
+%be the Weil sheaf on $G_m^{i}\ltimes J_m^{i+1}$ obtained by pullback along $G_m^{i}\ltimes J_m^{i+1} \to G_m^{i}$.
 Consider the sheaf 
@@
 \]
-on $G_m^{i}\ltimes J_m^{i+1}$ and compare with \eqref{eq:tensor}.
+on $G_m^{i}\ltimes J_m^{i+1}$.
+Comparing with \eqref{eq:tensor}, we see that $\trFrob{\cs{B}_m^{i+1}}$ is precisely the function obtained by factoring the character of $\rho_{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(R) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R/\mathfrak{p}_K^{m+1})$ using the canonical identification $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R/\mathfrak{p}_K^{m+1})$.
+In particular, $\trFrob{\cs{B}^{i+1}_m}$ is constant on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$, taking the value $\dim \rho_{i+1}$.
 With reference to the morphism $\pi_m^{i+1} : G_m^i \ltimes J_m^{i+1} \to G_m^{i+1}$ from \eqref{eq:pi}, define 
@@
 \end{eqnarray*}
-Comparing with \eqref{eq:tensor}, we see that $\trFrob{\cs{B}_m^{i+1}}$ is precisely the function obtained by factoring the character of $\rho^{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK/\mathfrak{p}_K^{m+1})$, using the canonical identification $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(\OK/\mathfrak{p}_K^{m+1})$.
-In particular, $\trFrob{\cs{B}^{i+1}_m}$ is trivial on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$.
-It follows that 
-\[
-\trFrob{\cs{\tilde A}^{i+1}_m} = n \trace(\rho^{i+1})
-\]
-on $G_m^{i+1}(\Fq)$ with $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$.
+Since $\trFrob{\cs{B}^{i+1}_m}$ is constant on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$, it follows that 
+\[
+\trFrob{\cs{\tilde A}^{i+1}_m} = n \trFrob{\cs{B}^{i+1}_m}
+\]
+on $G_m^{i+1}(\Fq)$ for $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) \times \dim \rho_{i+1} $.
 Let $\cs{A}_m^{i+1}$ be the \emph{virtual} Weil sheaf on $G_m^i$ given by $\cs{A}_m^{i+1} = \frac{1}{n} \cs{\tilde A}_m^{i+1}$. 
@@
 
-Now set $\cs{A}_m = \cs{A}_m^{d}$.
+Now set $\cs{A}_m = \cs{A}_m^{d} \otimes \cs{L}_m^d$.
 Then $\cs{A}_m$ is a virtual Weil sheaf on $G_m = \Gr^{R}_m(\underline{G})$ such that
@@
 \end{document}
-
-Suppose there is some $f : H\times G\to G\times G$ such that the following diagram commutes.
-\[
-\begin{tikzcd}
-\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
-G & & G \\
-& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
-\end{tikzcd}
-\]
-Then $f(h,g) = (a(h,g) g^{-1}, g)$.
-Define $f_1: H\times G \to G$ by $f_1(h,g)\ceq a(h,g) g^{-1}$; then $f(h,g) = (f_1(h,g),g)$ and $f_1(h_1 h_2,g) = f_1(h_1, h_2\cdot g) f_1(h_2,g)$.
-
-Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
-\[
-\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}
-\]
-by $\beta \otimes \id_{p^*\cs{L}} = \nu \circ f^*\mu^{-1}$, or more precisely, by the following diagram of isomorphisms,
-\[
-\begin{tikzcd}
-a^*\cs{L} \arrow{d}{m\circ f = a} \arrow{rrr}{\nu}
-&&& p^*\cs{L}\\
-f^* m^*\cs{L} \arrow{r}{f^*\mu} & 
-f^*(\cs{L}\boxtimes \cs{L}) \arrow{d} & 
-f_1^*\cs{L} \otimes p^*\cs{L} \arrow{r}{\beta\otimes \id_{p^*\cs{L}}} & 
-(\EE)_{H\times G} \otimes p^*\cs{L} \arrow{u} \\
-& f^*(p_1^*\cs{L}\otimes p_2^*\cs{L}) \arrow{r} & f^*p_1^*\cs{L}\otimes f^* p_2^*\cs{L} \arrow{u}{f_1 = p_1\circ f}[swap]{p = p_2\circ f} &
-\end{tikzcd}
-\]
-In this way we see we may replace $(\cs{L},\mu,\nu)$ with an alternate triple, $(\cs{L},\mu,\beta_1)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
-The isomorphism $\beta_1 : f_1^*\cs{L} \to (\EE)_{H\times G}$ is constrained by two properties, corresponding to the diagrams in Sections [] and [].
-
-\subsection{Quotient and restriction}
-
-We now combine the material of the last two sections, by specializing to the following case: $H$ is a closed subgroup of $G$ and $q : G \to G/H$ is the fppf quotient, which exists in schemes by  . . .
-
-\iffalse
-
-\subsection{Change of action}
-
-Now, let $a' : H'\times G \to G$ be another group action on $G$ and suppose $f: H \times G \to H'\times G$ makes the following diagram commute.
-\[
-\begin{tikzcd}
-&  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
-G & & G \\
-& \arrow{ul}{a'} H' \times G \arrow{ur}[swap]{p} & 
-\end{tikzcd}
-\]
-Then pull-back along $f: H\times G \to H'\times G$ defines a monoidal functor 
-\[
-\CS_{H'}(G) \to \CS_{H}(G).
-\]
-
-Then $f : H\times G \to H'\times G$ is given by $f(h,g) = (k(h,g),g)$ for some $k : H\times G\to H'$. 
-Define $d : H\to H'$ by $d(h) = k(h,1)$.
-
-\begin{lemma}\label{lem:action}
-The canonical functor
-\[
-\CS_{H}(G) \to \CS_{H'}(G)
-\]
-is an equivalence if ...
-\end{lemma}
-\begin{proof}
-\end{proof}
-
-\subsection{Conjugation}
-
-We close this section with an alternate characterization of $\CS'(G)$, the category of linear character sheaves $\cs{L}$ on $G$ for which $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
-Recall that $\CS'(G)$ is a full subcategory of $\CS(G)$ and that $\CCS(G)$ is a full subcategory of $\CS'(G)$.
-
-Consider the following case of Section~\ref{ssec:action}.
-
-\fi
-
-\iffalse
-\subsection{Linear Characters}
-
-For non-commutative $G$, we aim to model homomorphisms from $G(k)$ to $\EEx$ using the category $\CCS(G)$.
-The precise nature of the relationship between $G(k)^*$ and $\CCSiso{G}$ is described by Galois cohomology.
-Let $\Delta$ be the image of the boundary homomorphism $\delta$ in the sequence
-\[
-1 \to G\der(k) \to G(k) \to G\ab(k) \xrightarrow{\delta} \Hh^1(k, G\der),
-\]
-yielding a short exact sequence
-\[
-1 \to G(k) / G\der(k) \to G\ab(k) \to \Delta \to 1.
-\]
-Applying $\Hom(-, \EEx)$ and using the fact that every homomorphism $G(k) \to \EEx$ vanishes on $G\der(k)$, we get
-\[
-1 \to \Delta^* \to G\ab(k)^* \to G(k)^* \to 1.
-\]
-
-Combining Theorems \ref{thm:trfrobiso} and \ref{thm:Gab} gives an isomorphism $\CCSiso{G} \to G\ab(k)^*$. \todo{Could we turn this into a declared proposition? It's a nice result.}
-We may thus ask for a condition on a commutative character sheaf on $G$ that corresponds to having trivial
-trace of Frobenius, with the expectation that the isomorphism classes of such commutative character sheaves
-should be in natural bijection with $\Delta^*$.
-
-Note that when $\Hh^1(k,G\der) = 0$, as is the case when $G\der(\bFq)$ ``is simply connected,'' then
-we succeed in geometrizing characters of $G(k)$ on the nose.
-
-% \begin{corollary}
-% If $\Hh^1(\Fq,G\der)=0$ then
-%the following diagram of isomorphisms commutes.
-%\[
-%\begin{tikzcd}
-%\CCSiso{G} \arrow{r} & G(\Fq)^*\\
-%\arrow{u}{q^*} \CCSiso{G\ab} \arrow{r} & \arrow{u} G\ab(\Fq)^* 
-%\end{tikzcd}
-%\]
-% \end{corollary}
-% 
-% \begin{proof}
-% By Theorem \ref{thm:trfrobiso}, $\CCSiso{G}\to G(\Fq)^*$ and $\CCSiso{G\ab}\to G\ab(\Fq)^*$ are isomorphisms.
-%By Theorem~\ref{thm:Gab}, $\CCSiso{G} \iso \CCSiso{G\ab}$.
-%Since $\Hh^1(\Fq,G\der)=0$, we have  $G\ab(\Fq) = G(\Fq)/G\der(\Fq)$.
-%Thus, all characters of $G(\Fq)$ factor through
-% $G\ab(\Fq)$. . . . 
-% The isomorphisms are compatible because  . . . 
-% \end{proof}
-
-\subsection{Linear characters of certain $p$-adic groups}
-
-Let $K$ be a local field with residue field $\Fq$.
-Let $\underline{G}$ be a smooth group scheme over $K$.
-Set $G_n = \Gr^R_n(\underline{G})$; this is a smooth group scheme over $\Fq$.
-Set $G = \Gr_R(\underline{G})$; this is a group scheme over $\Fq$ equipped with $G = \varprojlim_{n\in \NN} G_n$.
-Let $\CCS(\underline{G})$ be the category of commutative quasicharacter sheaves on $G$. . . .  as in \cite{cunningham-roe:13a}.
-
-\begin{proposition}\label{prop:QCS}
-$\underline{G}(\OK)^* \iso \CCSiso{\underline{G}}$.
-\end{proposition}
-
-\begin{proof}
-That's not correct; it should be 
-\[
-\CCSiso{\underline{G}} \iso (\Gr(\underline{G})\ab(\Fq))^*.
-\]
-Is $\Gr(\underline{G})\ab = \Gr(\underline{G}\ab)?$ If so, then at least we get 
-\[
-\CCSiso{\underline{G}} \iso (\underline{G}\ab(\OK))^*.
-\]
-\end{proof}
-
-\fi
-
-\begin{proof}
-First, we make some observations concerning the auxillary data for $\underline{G}$.
-
-Introduce morphisms $\underline{G}\to \underline{M}^j$ and $\underline{M}^{j} \to \underline{M}^{j-1}$ and $\underline{M}^j \to \underline{J}^j$.
-\[
-\begin{tikzcd}
-\underline{J}^j \arrow{r} & \underline{G}^{j} \arrow{r} 
-& \underline{G} \arrow{r}  
-& \underline{M}^{j} \arrow{d} \arrow{r} & \underline{J}^j \\
-& \arrow{u} \underline{G}^{j-1} 
-&
-& \underline{M}^{j-1}
-&
-\end{tikzcd}
-\]
-\[
-\begin{tikzcd}
-\underline{G} \arrow{r}  
-& \underline{M}^{j} \arrow{d} \arrow{r} & \underline{J}^j \\
-\underline{G}_s \arrow{u} \arrow{d}
-& \underline{M}^{j-1}
- & (\underline{J}^j)_s \arrow{u} \arrow{d} \\
-\underline{G}_s\red & (\underline{M}^{j-1})_s \arrow{u} \arrow{d} & H^j \\
-& (\underline{M}^{j-1})_s\red & 
-\end{tikzcd}
-\]
-
-Now, we introduce the tools needed to geometrize all the ingredient representations.
-\begin{enumerate}
-\item
-Let $(A_0,\varphi)$ be a Frobenius-stable character sheaf on $\underline{G}_s\red$, in the sense of [Lusztig].
-Let $(A,\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{G}_s$ obtained by pull-back.
-\item For $j=1,\ldots, d-1$, 
-\begin{enumerate}
-\item
-Let $(B_0^{j},\varphi)$ be a Frobenius-stable character sheaf on $H^j$ in the sense of [Boyarchenko].
-Let $(B^{j},\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{J}^j_s$ obtained by pull-back.
-\item
-Let $(C_0^{j-1},\varphi)$ be a Frobenius-stable character sheaf on $(\underline{M}^{j-1})_s\red$ in the sense of [Lusztig].
-Let $(C^{j-1},\varphi)$ be the Frobenius-stable constructible sheaf on $\underline{M}^{j-1}_s$ obtained by pull-back.
-\item
-Let $\cs{E}_n$ be a commutative quasicharacter sheaf on $M_n^{j-1}$.
-\end{enumerate}
-\item
-Let $\cs{L}_n$ be a commutative quasicharacter sheaf on $G_n$.
-\end{enumerate}
-\[
-\begin{tikzcd}
-G \arrow{r}  \arrow{d}
-& M^{j} \arrow{r} \arrow{d}
-& J^j \arrow{d} \\
-G_n \arrow{r}  \arrow{d}
-& M_n^{j} \arrow{r} \arrow{d}
-& J_n^j \arrow{d} \\
-\underline{G}_s \arrow{d}
-& M_n^{j-1} \arrow{d}
-& (\underline{J}^j)_s  \arrow{d} \\
-\underline{G}_s\red 
-& (\underline{M}^{j-1})_s \arrow{d} & H^j \\
-& (\underline{M}^{j-1})_s\red 
-& 
-\end{tikzcd}
-\]
-
-We may now encorporate all these ingredients into one sheaf on $G_n$.
-\begin{enumerate}
-\item
-Let $\cs{A}_n$ be sheaf on $G_n$ produced from $A$ by pullback along $G_n \to \underline{G}_s$.
-\item
-For $j=1, \ldots, d-1$,
-\begin{enumerate}
-\item let $\cs{B}^j$ be the sheaf on $J^j_n$ ...
-\item let $\cs{C}^j$ be the sheaf on $M^{j-1}_n$ ...
-\item let $\cs{L}^j$ be the sheaf on $M^{j-1}_n$ ...
-\end{enumerate}
-Combine: $\cs{B}^j$, $\cs{C}^j$ and $\cs{E}^j$ into $\cs{D}^j$ on $G_n$ . . . .
-\item Let $\cs{L}$ be the sheaf on $G_n$ as above...
-\end{enumerate}
-
-\[
-\cs{A} \otimes \cs{D}^1 \otimes \cdots \otimes \cs{D}^{d-1} \otimes \cs{L}.
-\]
-
-Interpret 
-\begin{enumerate}
-\item
-	$\epsilon_j$ as a representation of $(\underline{M}^{j-1})_s\red(\Fq)$, for each $j=1,\ldots, d$;
-\item
-	$\phi_{j-1}$ as a linear quasicharacter of $\underline{M}^{j-1}(\OK)$, for $j=1,\ldots, d$;
-\end{enumerate}
-so that
-\begin{enumerate}
-\item 
-	$\dot{\epsilon}_j$ is the representation of $\underline{M}^{j-1}(\OK)$ obtained by pulling back $\epsilon_j$ along 
-\[\underline{M}^{j-1}(\OK) \to \underline{M}^{j-1}_s(\Fq) \to (\underline{M}^{j-1})_s\red(\Fq),\]
-for $j=1,\ldots, d-1$.
-\item
-	$\dot{\eta}_j$ is a representation of $\underline{J}^{j}(\OK)$ obtained by pulling back  . . . .  $j=1,\ldots, d-1$;
-\item
-	$\tau_j$ is the representation of $\underline{G}(\OK)$ obtained by pulling back  $\phi_{j-1}$ and $\dot{\epsilon}_j$ and $\dot{\eta}_j$ from $\underline{M}^{j}(\OK)$ along $\underline{G}(\OK)\to \underline{M}^j(\OK)$, for $j=1,\ldots, d-1$.
-\end{enumerate}
-
-\end{proof}
-
-\iffalse
-
-Let $K$ be a $p$-adic field. Let $\G$ be a connected reductive linear algebraic group over $K$. 
-A generic datum is a triple $(\vec{\G}, \pi_0, \vec{\phi})$ where: $\vec{\G}$ is a tower of $p$-adic groups $\G^0(K) \subset \G^1(K) \subset \cdots  \subset \G^d(K) = \G(K)$ (proper containment); $\pi_0$ is a depth-zero representation of $\G^0(K)$, and $\vec{\phi} = (\phi_0, \ldots , \phi_{d-1})$ where each $\phi_i : \G^i(K) \to \EEx$ is a quasicharacter (continuous group homomorphism).
-
-%The generic datum $(\vec{\G}, \pi_0, \vec{\phi})$ determines a type (in the sense of \cite{bushnell-kutzko:98a}) $(C, \rho)$ for $\G$, as explained in \cite{yu:01a}*{\S 15}, where $C \subset \G(K)$ is compact mod centre subgroup and $\rho$ is a representation of $C$.
-In \cite{yu:03a} it is shown that the $C$ admits a smooth integral model, in the sense that there is a smooth group scheme $\underline{C}$ over $\OK$ such that $\underline{C}(\OK) = C$.
-
-In \cite{yu:03a} it is shown that, for $0 \leq i < d$, the $p$-adic group $\G^i(K)$ admits a smooth integral model, in the sense that there is \todo{is $\underline{G}^i$ canonically determined?} a smooth group scheme $\underline{G}^i$ over $\OK$ such that $\underline{G}^i(\OK) = \G^i(K)$.
-Set $G^i_n \ceq \Gr^R_n(\underline{G}^i)$ and $G^i \ceq \Gr_R(\underline{G}^i)$; 
-then \[G^i(\Fq) = \G^i(K)\] (canonical isomorphism of groups).
-In this way, $\vec{\G}$ determines a tower $\vec{G}$ of group schemes $G^0 \subset G^1 \subset \cdots  \subset G^{d-1}$ (proper containment) over $\Fq$, from which the tower of $p$-adic groups
-$\G^0(K) \subset \G^1(K) \subset \cdots  \subset \G^{d-1}(K)$ can be recovered.
-
-Using Corollary~\ref{cor:QCS} \todo{broken reference} we see that each quasicharacter $\phi_i : G^i(\Fq) \to \EEx$ determines a quasicharacter sheaf $\cs{L}^i$, unique up to isomorphism, from which the quasicharacter $\phi_i$ can be recovered using the trace of Frobenius.
-In fact, more is true. Let $n_i$ be the smallest non-negative integer $n$ such that $\phi_i : G^i(\Fq) \to \EEx$ factors through $G^i(\Fq) \to G^i_n(\Fq)$.
-Then $\phi_i$ determines a commutative character sheaf $\cs{L}_{n_i}^i$, unique up to isomorphism, from which the quasicharacter $\phi_i$ can be recovered.
-Then $\cs{A}_i\ceq \cs{L}_{n_i}^i[\dim G_{n_i}^i]$ is a perverse sheaf on $G_{n_i}^i$ from which the quasicharacter $\phi_i$ can be recovered.
-In this way,  $\vec{\phi} = (\phi_0, \ldots , \phi_{d-1})$ determines perverse sheaves $\vec{\cs{A}} = (\cs{A}_0, \ldots , \cs{A}_{d-1})$ from which $\vec{\phi}$ can be recovered.
-
-Finally, consider the depth-zero supercuspidal representation $\pi_0$ of $\G^0(K)$.
-Then $\pi_0$ is produced by compact induction from representation $\sigma$ of a compact mod centre subgroup $\underline{C}_0(\OK) \subset \G^0(K)$.
-Moreover, $C_0$ admits a smooth integral model $\underline{C}$ ...
-
-%\subsection{Toral supercuspidal representations of $p$-adic groups}
-
-\fi
-
-A representation $\sigma$ of the $\Fq$-points of the reductive group $(\underline{G}^0)_\Fq^\reductive$ over $\Fq$. 
-Then $\tau$ is the representation of the $\Fq$-points of the special fibre of the smooth model $\underline{G}^0$ over $\OK$ and the representation $\rho^0$ of $\underline{G}(\OK)$ is produced from $\tau$ by inflation.
-Suppose $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
-The existence of $A$ follows from \cite{Lusztig:CSDG}*{}.
-Let $B$ be the Weil sheaf on $\underline{G}^0_\Fq$ obtained by pullback along $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
-Then $\trFrob{\bar B} = \trace \tau$ so
-\[
-\trace \rho^0(k) = \trFrob{\bar B}(k_\Fq)
-\]
-where $k \mapsto k_\Fq$ refers to the map $\underline{G}^0(\OK) \to \underline{G}^0(\Fq)$.
-Observe that the special fibre $\underline{G}^0_\Fq$ of $\underline{G}^0$ is $\Gr_1(\underline{G}^0)$.
-Let $\cs{B}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^0)$ obtained by pulling back $B$ along  $\Gr(\underline{G}^0) \to \Gr_1(\underline{G}^0)$.
-
-%\item 
-For $i=0, \ldots, d$, a quasicharacter (continuous linear character) $\varphi^i$ of $\underline{G}^i(\OK)$.
-
-%\item
-For $i=0, \ldots, d-1$, a representation $W_{i+1}$ of the the Jacobi group $\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp$, viewed as the $\Fq$-points of an algebraic group over $\Fq$.
-Then $w_{i+1}$ is the representation of the $\Fq$-points of the special fibre of $\underline{G}^i \ltimes \underline{J}^{i+1}$ over $\OK$ and the representation $h^*(W_{i+1})$ is produced from $w_{i+1}$ by inflation.
-%\end{enumerate}
-
-For $i=0,\ldots, d-1$, let $\cs{F}_{i+1}$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^i)$ obtained by applying Proposition~\ref{prop:quasicharacters} to $\varphi^i : \underline{G}^i(\OK) \to \CC^\times$.
-
-For $i=0,\ldots, d-1$, let $\cs{T}_i$ be the Weil sheaf on the $\Fq$-scheme $\Gr(\underline{G}^i \ltimes \underline{J}^{i+1})$
-
-\end{proof}
-
-\begin{lemma}[Claim, actually]
-For $V$, $C$, $\langle\, , \ \rangle$ and $\psi$ as above, there is a virtual constructible equivariant Weil sheaf $\cs{T}$ on the algebraic group $\Sp(V)\ltimes V^\sharp$ such that $\trFrob{\cs{T}} = \trace(\tau)$.
-\end{lemma}
-
-\begin{proof}
-First, find a geometrization of $\omega$ which is equivariant for the action of $\Sp(V)$ on $V^\sharp$: a virtual constructible equivariant Weil sheaf $\cs{H}$ on $V^\sharp$ equipped with an isomorphism $m^*\cs{H} \to p^* \cs{H}$ such that ...
-Do this by induction: $\operatorname{ind}_{A}^{V^\sharp}(\cs{L}_\psi)$, where $A$ .
-.
-.
-.
-\end{proof}

### 2016-02-23 followup.tex
Changes to the introduction.

@@
 
-\title[Commutative Character Sheaves]{Commutative Character Sheaves on smooth group schemes over finite fields}
-%with an application to geometric types for supercuspidal representations
+\title[Geometrization of characters of smooth group schemes over finite fields]{Geometrization of characters of smooth group schemes over finite fields with an application to types for supercuspidal representations}
 \author{Clifton Cunningham}
@@
 \begin{abstract}
-We describe a function-sheaf dictionary for one-dimensional characters of arbitrary smooth group schemes
-over finite fields.  In previous work, we considered the case of commutative smooth group schemes and found
-that the standard definition of character sheaves produced a dictionary with a nontrivial kernel.  In this paper,
-we give a modification of the category of character sheaves that remedies this defect, and is also extensible to
-non-commutative groups.  
-As an application, we use these \emph{commutative character sheaves} to geometrize types for
-supercuspidal representations of $p$-adic groups. 
+We describe a function-sheaf dictionary for one-dimensional characters of arbitrary smooth group schemes over finite fields.  
+In previous work, we considered the case of commutative smooth group schemes and found that the standard definition of character sheaves produced a dictionary with a nontrivial kernel.  
+In this paper we give a modification of the category of character sheaves that remedies this defect, and is also extensible to non-commutative groups.  
+As an application, we use these \emph{commutative character sheaves} to geometrize types for supercuspidal representations of $p$-adic groups, assuming the existence of the geometrization of the Heisenberg-Weil representation over finite fields.
 \end{abstract}
@@
 
-In previous work \cite{cunningham-roe:13a}, we generalized the function-sheaf dictionary from connected, commutative, algebraic groups
-over a finite field $k$ to smooth commutative group schemes $G$ over $k$.  Writing $G(k)^*$ for $\Hom(G(k), \EEx)$, we described a category $\CS(G)$ of
-\emph{character sheaves} on $G$ and a surjective homomorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$.
-In contrast to the connected case, $\TrFrob{G}$ may have nontrivial kernel; we gave an explicit description of
-its kernel as $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$ \cite{cunningham-roe:13a}*{Thm. 3.6}.
-
-The first aim of this paper is to repair this defect in the function-sheaf dictionary by describing a full subcategory
-$\CCS(G)$ of $\CS(G)$ so that $\TrFrob{G}$ restricts to an isomorphism $\CCSiso{G} \to G(k)^*$.
-We refer to the resulting objects as \emph{commutative character sheaves}, since the passage from $\CS(G)$
-to $\CCS(G)$ involves a condition that exchanges the inputs to the multiplication morphism on $G$
-(see Definition \ref{def:CCScom}).  When $G$ is connected, all character sheaves on $G$ are commutative.
-This category clarifies several questions about character sheaves on $G$: invisible character sheaves
-\cite{cunningham-roe:13a}*{Def. 2.8} are precisely those that are not commutative, and 
-$\TrFrob{G}^{-1} : G(k)^* \to \CCSiso{G}$ provides a canonical splitting of
-$\TrFrob{G} : \CSiso{G} \to G(k)^*$ \cite{cunningham-roe:13a}*{Rem. 3.7}.
+In previous work \cite{cunningham-roe:13a}, we generalized the function-sheaf dictionary from connected, commutative, algebraic groups over a finite field $k$ to smooth commutative group schemes $G$ over $k$.
+Writing $G(k)^*$ for $\Hom(G(k), \EEx)$, we described a category $\CS(G)$ of \emph{character sheaves} on $G$ and a surjective homomorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$.
+In contrast to the connected case, $\TrFrob{G}$ may have nontrivial kernel; we gave an explicit description of its kernel as $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$ \cite{cunningham-roe:13a}*{Thm. 3.6}.
+
+The first aim of this paper is to repair this defect in the function-sheaf dictionary by describing a full subcategory $\CCS(G)$ of $\CS(G)$ so that $\TrFrob{G}$ restricts to an isomorphism $\CCSiso{G} \to G(k)^*$.
+We refer to the resulting objects as \emph{commutative character sheaves}, since the passage from $\CS(G)$ to $\CCS(G)$ involves a condition that exchanges the inputs to the multiplication morphism on $G$ (see Definition \ref{def:CCScom}).
+When $G$ is connected, all character sheaves on $G$ are commutative.
+This category clarifies several questions about character sheaves on $G$: invisible character sheaves \cite{cunningham-roe:13a}*{Def.
+2.8} are precisely those that are not commutative, and  $\TrFrob{G}^{-1} : G(k)^* \to \CCSiso{G}$ provides a canonical splitting of $\TrFrob{G} : \CSiso{G} \to G(k)^*$ \cite{cunningham-roe:13a}*{Rem.
+3.7}.
 
@@
 
-Finally, we use the category $\CCS(G)$ to give a geometric description of generic types for supercuspidal representations
-of connected reductive groups over local fields.  In this way, we provide all of the ingredients
-needed to parametrize supercuspidal representations of arbitrary depth in the same category:
-perverse sheaves on group schemes over finite fields. \todo{Update based on any changes in Section 4}
-
+Finally, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected reductive groups over $p$-adic fields fields,
+assuming the existence of a geomtrization of the Heisenberg-Weil representations over finite fields.
+In this way, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:
+virtual Weil perverse sheaves on smooth group schemes over finite fields. 
+%\todo{Update based on any changes in Section 4}
+
+We now summarize the sections of the paper in more detail.
 In Section \ref{sec:defs}, we recall the category $\CS(G)$ from \cite{cunningham-roe:13a} and note that it still makes
@@
 $\TrFrob{G} : \CSiso{G} \to G(k)^*$ induces an isomorphism on $\CCSiso{G}$.
-
-Passing to the case that $G$ is
-non-commutative, we give the definition of and main results about commutative character sheaves in
-Section \ref{sec:noncom}.  We note that we should only consider character sheaves
-that arise via pullback from $G\ab$ in order to eliminate those that have nontrivial restriction
-to the derived subgroup.  This observation underlies the definition of commutative character sheaves for
-non-commutative $G$.  We state our second main theorem, that pullback along the abelianization map
-defines an equivalence of categories $\CCS(G) \to \CCS(G\ab)$.
-In Section \ref{ssec:obmor}, we use Galois cohomology to describe the relationship between $G(k)^*$
-and $G\ab(k)^*$.  We also compute the automorphism groups in $\CCS(G)$.
-Then in Section \ref{ssec:proofs}, we give proofs of the results in Section \ref{sec:noncom}, which
-require a development of equivariant linear character sheaves.
-
-\todo{Add summary of Section 4 once it has stabilized}
-
-In the remainder of this section we use Theorem~\ref{thm:geo} to geometrize the representation $\rho$ of $C$: subject to a hypothesis on the component group of the depth-zero part of the datum and also on a conjecture on the geometrization of the character of Heisenberg-Weil representations, we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\rho)$.
+%
+Passing to the case that $G$ is non-commutative, we give the definition of and main results about commutative character sheaves in Section \ref{sec:noncom}.  
+We note that we should only consider character sheaves that arise via pullback from $G\ab$ in order to eliminate those that have nontrivial restriction to the derived subgroup.  
+This observation underlies the definition of commutative character sheaves for non-commutative $G$.  
+We state our main result, Theorem~\ref{thm:geo}, that pullback along the abelianization map defines an equivalence of categories $\CCS(G) \to \CCS(G\ab)$.
+In Section \ref{ssec:obmor}, we use Galois cohomology to describe the relationship between $G(k)^*$ and $G\ab(k)^*$.  
+We also compute the automorphism groups in $\CCS(G)$.
+Then in Section \ref{ssec:proofs}, we give proofs of the results in Section \ref{sec:noncom}, which require a development of equivariant linear character sheaves.
+
+In Section~\ref{sec:types} we use Theorem~\ref{thm:geo} to geometrize the representations of compact $p$-adic groups appearing in the types for : subject to a hypothesis on the component group of the depth-zero part of the datum and also on a conjecture on the geometrization of the character of Heisenberg-Weil representations, we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\rho)$.
 The proof of this statement is quite technical, so it must be delayed to Section~\ref{ssec:geotypes}, after reviewing types in Section~\ref{ssec:types} and models Section~\ref{ssec:models} developed by Yu, for which we must also review some facts about the Heisenberg-Weil representation in Section~\ref{ssec:Jacobi}, and also make a conjecture about the geometrization of that representation, Conjecture~\ref{conj}.

### 2016-03-02 followup.tex
Catching up

@@
 
-For use below, we recall some basic facts about the Heisenberg-Weil representation and make a conjecture about the geometrization of these representations.
-We refer the reader to \cite{berndt-schmidt:98a} for more details.
+For use below, we recall some facts about the Heisenberg-Weil representation.
 
@@
 Let $\Sp(V)$ be the symplectic group determined by the symplectic pairing $\langle\ ,\ \rangle$; this group acts on $V^\sharp$.
-Then  is the Jacobi group. 
-From the construction above, it is clear that $\Sp(V)\ltimes V^\sharp$ may be viewed as the $\Fq$-points of an algebraic group over $\Fq$; we will refer to that algebraic group as the Jacobi group.
+The group $\Sp(V)\ltimes V^\sharp$ is called the Jacobi group. 
+From the construction above, it is clear that the Jacobi group may be viewed as the $\Fq$-points of an algebraic group over $\Fq$; we will refer to that algebraic group as the Jacobi group.
 
@@
 The Heisenberg representation determines a representation $\pi_{\psi}$ of $\Sp(V)$ with the same representation space as $\omega_\psi$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\psi(g)$ determines an isomorphism of representations $\omega_\psi^g \to \omega_\psi$.
-% through the Egorov identity \cite{Gurevich-Hadani:geometric_Weil}*{(1.3.1)}.\todo{Find better reference.}
 Let $W_\psi = \pi_\psi \ltimes \omega_\psi$ be the representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$ given by $\omega_\psi$ and $\pi_\psi$.
 
-\begin{conjecture}\label{conj:Jacobi}
-%Notation as above.
-There is an equivariant Weil sheaf $\cs{W}_\psi$ on the Jacobi group such that 
+It is one of the main results of \cite{Gurevich-Hadani:geometric_Weil}*{(1.3.1)} that there is a Weil sheaf $\cs{W}_\psi$ on the Jacobi group such that 
 \[
@@
 \]
-\end{conjecture}
 
@@
 Assume $\pi_0(\underline{G}^0)_\Fq^\reductive)$ is cyclic.
-Assume Conjecture~\ref{conj:Jacobi}.
 Then there is a virtual Weil sheaf $\cs{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
@@
 Consider the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ and the Heisenberg-Weil representation $W_{i+1}$ appearing in Section~\ref{ssec:models}.
-Let $\cs{W}_{i+1}$ be the Weil sheaf promised by Conjecture~\ref{conj:Jacobi} on the Jacobi group such that
+Let $\cs{W}_{i+1}$ be the Weil sheaf on the Jacobi group, recalled in Section~\ref{ssec:Jacobi} such that
 \[

### 2016-03-03 followup.tex
Catching up, more.
Added geometrization of Heisenberg-Weil.

@@
 
-\title[Geometrization of characters of smooth group schemes over finite fields]{Geometrization of characters of smooth group schemes over finite fields with an application to types for supercuspidal representations}
+\title[Geometrization of characters of smooth group schemes]{Geometrization of characters of smooth group schemes over finite fields with an application to types for supercuspidal representations}
 \author{Clifton Cunningham}
@@
 \newcommand{\Sp}{{\operatorname{Sp}}}
+\newcommand{\cay}{{\operatorname{cay}}}
 
@@
 In this paper we give a modification of the category of character sheaves that remedies this defect, and is also extensible to non-commutative groups.  
-As an application, we use these \emph{commutative character sheaves} to geometrize types for supercuspidal representations of $p$-adic groups, assuming the existence of the geometrization of the Heisenberg-Weil representation over finite fields.
+As an application, we use these \emph{commutative character sheaves} to geometrize types for supercuspidal representations of $p$-adic groups.
 \end{abstract}
@@
 
-Finally, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected reductive groups over $p$-adic fields fields,
-assuming the existence of a geomtrization of the Heisenberg-Weil representations over finite fields.
+Finally, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected reductive groups over $p$-adic fields fields.
 In this way, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:
 virtual Weil perverse sheaves on smooth group schemes over finite fields.
-%\todo{Update based on any changes in Section 4}
 
 We now summarize the sections of the paper in more detail.
-In Section \ref{sec:defs}, we recall the category $\CS(G)$ from \cite{cunningham-roe:13a} and note that it still makes
-sense when $G$ is not commutative.  We focus on the case of commutative $G$ in Section \ref{sec:comcom},
+
+%\begin{enumerate}
+%\item
+In Section \ref{sec:defs}, we recall the category $\CS(G)$ from \cite{cunningham-roe:13a} and note that it still makes sense when $G$ is not commutative.
+
+%\item
+We focus on the case of commutative $G$ in Section \ref{sec:comcom},
 giving the definition of a commutative character sheaf and proving our first main theorem, that
 $\TrFrob{G} : \CSiso{G} \to G(k)^*$ induces an isomorphism on $\CCSiso{G}$.
-%
+
+%\item
 Passing to the case that $G$ is non-commutative, we give the definition of and main results about commutative character sheaves in Section \ref{sec:noncom}.  
@@
 
-In Section~\ref{sec:types} we use Theorem~\ref{thm:geo} to geometrize the representations of compact $p$-adic groups appearing in the types for : subject to a hypothesis on the component group of the depth-zero part of the datum and also on a conjecture on the geometrization of the character of Heisenberg-Weil representations, we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\rho)$.
-The proof of this statement is quite technical, so it must be delayed to Section~\ref{ssec:geotypes}, after reviewing types in Section~\ref{ssec:types} and models Section~\ref{ssec:models} developed by Yu, for which we must also review some facts about the Heisenberg-Weil representation in Section~\ref{ssec:Jacobi}, and also make a conjecture about the geometrization of that representation, Conjecture~\ref{conj}.
+%\item
+In Section~\ref{sec:types} we use Theorem~\ref{thm:geo} to geometrize the representations of compact $p$-adic groups appearing in the types for: we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\rho)$.
+The proof of this statement is quite technical, so it must be delayed to Section~\ref{ssec:geotypes}, after reviewing types in Section~\ref{ssec:review} and models Section~\ref{ssec:models} developed by Yu, for which we must also review some facts about the Heisenberg-Weil representation and its geometrization, in Section~\ref{ssec:Jacobi}.
+%\end{enumerate}
 
@@
 With notation as above, suppose $\Fq$ is a finite field.
-For every quasicharacter/continuous linear character $\chi : \underline{G}(S) \to \EEx$ there is a Weil sheaf $\cs{L}$ on $G$ such that \[\trFrob{\cs{L}} = \trace \chi.\] \end{proposition}
+For every quasicharacter character $\varphi : \underline{G}(S) \to \EEx$ there is a Weil sheaf $\cs{L}$ on $G$ such that \[\trFrob{\cs{L}} = \trace \varphi.\] \end{proposition}
 
 \begin{proof}
-Set $S = \Spec{R}$ and, for every non-negative integer, set $S_n = \Spec{R/\mathfrak{m}^{n+1}}$.
- Then $G_n \ceq \Gr_n^{R}(\underline{G})$, the Greenberg transform of $\underline{G} \times_{S} S_n$, is a smooth group scheme over $\Fq$ and 
-\[
-G_n(\Fq) = \underline{G}(S_n),
-\]
-canonically.
+By continuity of $\varphi : \underline{G}(S) \to \EE^\times$, there is some $m \in \NN$ and a factorization
+\[
+\begin{tikzcd}
+\underline{G}(S) \arrow{rr}{\varphi} \arrow{rd} && \EEx\\
+& \underline{G}(R/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi_m} 
+\end{tikzcd}
+\] 
+Set $G_m = \Gr_m^{R}(\underline{G})$.
+Then $G_m$ is a smooth group scheme over $\Fq$ and $G_m(\Fq) = \underline{G}(R/\mathfrak{p}^{m+1})$, canonically.
+Using Theorem~\ref{thm:geo}, $\cs{L}_m$ be a geometrization of the linear character $\varphi_m: G_m \to \EEx$; so
+\[
+\trFrob{\cs{L}_m} = \varphi_m
+\]
+on $G_m(\Fq)$.
+
+Recall that the full Greenberg transform $\Gr^{R}(\underline{G})$ is a group scheme over $\Fq$ such that $\Gr^{R}(\underline{G})(\Fq) = \underline{G}(\Fq)$, canonically, and comes equipped with a morphism $\Gr^{R}(\underline{G}) \to \Gr^{R}_m(\underline{G})$.
+Let $\cs{L}$ be the  Weil sheaf on $\Gr^{R}(\underline{G})$ obtained from $\cs{L}_m$ by pullback along $\Gr^{R}(\underline{G}) \to \Gr^{R}_{m}(\underline{G})$. 
+Then $\cs{L}$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G})$ such that $\trFrob{\cs{L}} = \trace \varphi$.
 \end{proof}
 
-\subsection{A conjecture on Jacobi theory over finite fields}\label{sec:Jacobi}
+\subsection{Jacobi theory over finite fields}\label{ssec:Jacobi}
 
@@
 
-Let $\psi : Z \to \EEx$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi : Z \to \EEx$. 
+Let $\psi : Z \to \EEx$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi : Z \to CC^\times$. 
 The Heisenberg representation determines a representation $\pi_{\psi}$ of $\Sp(V)$ with the same representation space as $\omega_\psi$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\psi(g)$ determines an isomorphism of representations $\omega_\psi^g \to \omega_\psi$.
@@
 
-It is one of the main results of \cite{Gurevich-Hadani:geometric_Weil}*{(1.3.1)} that there is a Weil sheaf $\cs{W}_\psi$ on the Jacobi group such that 
-\[
+The character $\trace(W_\psi) : \Sp(V)\ltimes V^\sharp \to \EE^\times$ of $W_\psi$ is studied in \cite{Howe:Weil}, where is it shown that $\trace(W_\psi)(g,v,z) =0$ unless $v\in \ker(g-1)$, in which case $(g,v,z)$ lies in a conjugacy class intersecting $\Sp(V) \ltimes Z$.
+Since $\trace(W_\psi)(g,v,z) = \psi(z) \trace(W_\psi)(g,v,0)$, it follows that $\trace(W_\psi)$ is determined by its restriction to $\Sp(V)$.
+%
+The group $\Sp(V)$ is naturally stratified into the conjugation-stable subvarieties $S_r = \{ g\in \Sp(V) \tq \dim \ker (g-1) = r \}$. 
+The big stratum, $S_0$, is dense in $\Sp(V)$. 
+From \cite{Howe:Weil} we learn that $q^{-r/2} \trace(W_\psi)(g)$ has complex norm $1$, for $0\leq r \leq \dim V$ and $g\in S_r$.
+
+It is one of the main results of \cite{Gurevich-Hadani:geometric_Weil} that there is a Weil sheaf $\cs{W}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
+\begin{equation}
 \trFrob{\cs{W}_\psi} = \trace(W_\psi).
-\]
-
-\iffalse
-Pick a Lagrangian splitting $V = U \oplus U'$. 
-%such that $\langle v,v' \rangle = (u,w') - (u',w)$ for $v=(u,w)$ and $v'=(u',w')$.
-Let $B \to V^\sharp$ be the subgroup defined by the diagram below.
-\[
-\begin{tikzcd}
-\ &&& U' \arrow{d} &\\
-1 \arrow{r} & Z \arrow{r} & V^\sharp \arrow{r} & \arrow[bend right]{l} V \arrow[bend right]{u} \arrow[bend left]{d} \arrow{r} & 1\\
-1 \arrow{r} & \arrow[equals]{u} Z \arrow{r} & \arrow[bend right]{l}  B \arrow{u} \arrow{r} & \arrow[bend right]{l}  U \arrow{u} \arrow{r} & 1 
-\end{tikzcd}
-\]
-Extend $\psi$ to $\psi_B : B \to \EEx$ in the obvious way. 
-Then $\omega \ceq \operatorname{Ind}_A^{V^\sharp}(\psi_A)$ is called the Heisenberg representation of $V^\sharp$.
-\fi
+\end{equation}
+%
+Although nothing more that this statement will be needed below, the construction of $\cs{W}_\psi$ is so unbelievably gorgeous that we can't resist saying a few extra words about it here.
+The reader pressed for time is invited to skip to the next section without loosing anything needed for the arguments in the rest of Section~\ref{sec:types}.
+
+First, fix an isomorphism $\CC \approx \EE$ so that we may mix classical and geometric facts. 
+One begins by finding a local system $\cs{K}_0$ on $S_0 \times V^\sharp$ such that 
+\[
+\trFrob{\cs{K}_0[2\dim V](\dim V)} = \trace(W_\psi)\vert_{S_0\times V^\sharp},
+\]
+where $\cs{K}_0[2\dim V](\dim V)$ is the Tate twist of the shift of $\cs{K}_0$.
+This is done by observing that $S_0$ is the domain of the Cayley transform $\cay : g \mapsto (g-1)^{-1}(g+1)$ on $\Sp(V)$ and that 
+\begin{equation}\label{Cayley}
+\trace(W_\psi)(g,v,z) =  q^{-\dim V} \gamma_\psi^{\dim V} \sigma(\det(1+\cay(g))) \psi(\langle \cay(g)v,v\rangle) \psi(z),
+\end{equation}
+ for $(g,v,z) \in S_0\times V\times Z$, where $\gamma_\psi$ is the Gauss sum for $\psi$ and $\sigma : \Fq^\times \to \EE^\times$ is the quadratic character of $\Fq^\times$.
+By a simple adaptation of what in \cite{Gurevich-Hadani:geometric_Weil}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible local system $\cs{K}_0$ on $S_0 \times V^\sharp$.
+Next, one forms $\cs{K} \ceq j_{!*} \cs{K}_0$, the perverse extension of $\cs{K}_0$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$; recall that $S_0$ is Zariski dense in $\Sp(V)$.
+It follows from \cite{Gurevich-Hadani:geometric_Weil} that 
+\[
+\trFrob{\cs{K}[\dim V](\dim V)} = \trace(W_\psi).
+\]
+Then $\cs{W}_\psi = \cs{K}[\dim V](\dim V)$ is the promised Weil sheaf.
 
@@
 Finally, we come to the main result of Section~\ref{sec:types}.
+
 Since Yu's theory refers to complex representations, and since our geometrization uses $\ell$-adic sheaves, we grit our teeth and fix an isomorphism $\CC \approx \EE$.
@@
 \begin{proof}
-%Now we explain how to geometrize the characters of these ingredient representations, using the discussion from Section~\ref{ssec:models}.  
 Recall that $G^i(\Fq) = \underline{G}^i(R) = C^i$, canonically.
+We begin with an argument already employed in the proof of Proposition~\ref{prop:quasicharacters}.
 By continuity of the quasicharacters $\varphi^i : G^i(\Fq) \to \CC^\times$, there is some $m \in \NN$ and a factorization
@@
 Then $G_m^i$ is a smooth group scheme over $\Fq$ and $G_m^i(\Fq) = \underline{G}^i(R/\mathfrak{p}^{m+1})$, canonically.
-Using Proposition~\ref{prop:quasicharacters}, let $\cs{L}^i_m$ be a geometrization of the linear character $\varphi^i_m: G_m^i \to \CC^\times$; so
+Using Theorem~\ref{thm:geo}, let $\cs{L}^i_m$ be a geometrization of the linear character $\varphi^i_m: G_m^i \to \CC^\times$; so
 \[
@@
 Consider the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ and the Heisenberg-Weil representation $W_{i+1}$ appearing in Section~\ref{ssec:models}.
-Let $\cs{W}_{i+1}$ be the Weil sheaf on the Jacobi group, recalled in Section~\ref{ssec:Jacobi} such that
+Let $\cs{W}_{i+1}$ be the Weil sheaf on the Jacobi group, recalled in Section~\ref{ssec:Jacobi}, such that
 \[
@@
 \end{document}
+
+\bib{Howe}{article}{
+   author={Howe, Roger E.},
+   title={On the character of Weil's representation},
+   journal={Trans. Amer. Math. Soc.},
+   volume={177},
+   date={1973},
+   pages={287--298},
+   issn={0002-9947},
+   review={\MR{0316633}},
+}

### 2016-03-03 followup.tex
Thanks to Loren.

@@
 
-\title[Geometrization of characters of smooth group schemes]{Geometrization of characters of smooth group schemes over finite fields with an application to types for supercuspidal representations}
+\title[Geometrization of characters of smooth group schemes]{Geometrization of characters of smooth group schemes over finite fields\\ with an application to types for supercuspidal representations}
 \author{Clifton Cunningham}
@@
 
+We thank Loren Spice for explaining Yu's theory of types to us.
+
 \section{Recollections and definitions} \label{sec:defs}

### 2016-03-03 followup.tex
Fixed a few typos

@@
 Then $G_m$ is a smooth group scheme over $\Fq$ and $G_m(\Fq) = \underline{G}(R/\mathfrak{p}^{m+1})$, canonically.
-Using Theorem~\ref{thm:geo}, $\cs{L}_m$ be a geometrization of the linear character $\varphi_m: G_m \to \EEx$; so
+Using Theorem~\ref{thm:geo}, let $\cs{L}_m$ be a geometrization of the linear character $\varphi_m: G_m \to \EEx$; so
 \[
@@
 on $G_m(\Fq)$.
-
-Recall that the full Greenberg transform $\Gr^{R}(\underline{G})$ is a group scheme over $\Fq$ such that $\Gr^{R}(\underline{G})(\Fq) = \underline{G}(\Fq)$, canonically, and comes equipped with a morphism $\Gr^{R}(\underline{G}) \to \Gr^{R}_m(\underline{G})$.
-Let $\cs{L}$ be the  Weil sheaf on $\Gr^{R}(\underline{G})$ obtained from $\cs{L}_m$ by pullback along $\Gr^{R}(\underline{G}) \to \Gr^{R}_{m}(\underline{G})$. 
-Then $\cs{L}$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G})$ such that $\trFrob{\cs{L}} = \trace \varphi$.
+%
+Recall that the full Greenberg transform $G \ceq \Gr^{R}(\underline{G})$ is a group scheme over $\Fq$ such that $G(\Fq) = \underline{G}(\Fq)$, canonically, and comes equipped with a morphism $G \to G_m$.
+Let $\cs{L}$ be the  Weil sheaf on $G$ obtained from $\cs{L}_m$ by pullback along $G \to G_m$. 
+Then $\cs{L}$ is a quasicharacter sheaf on $G$, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, such that $\trFrob{\cs{L}} = \trace \varphi$.
 \end{proof}
@@
 
-The character $\trace(W_\psi) : \Sp(V)\ltimes V^\sharp \to \EE^\times$ of $W_\psi$ is studied in \cite{Howe:Weil}, where is it shown that $\trace(W_\psi)(g,v,z) =0$ unless $v\in \ker(g-1)$, in which case $(g,v,z)$ lies in a conjugacy class intersecting $\Sp(V) \ltimes Z$.
-Since $\trace(W_\psi)(g,v,z) = \psi(z) \trace(W_\psi)(g,v,0)$, it follows that $\trace(W_\psi)$ is determined by its restriction to $\Sp(V)$.
+The character $\trace(W_\psi) : \Sp(V)\ltimes V^\sharp \to \EE^\times$ of $W_\psi$ is studied in \cite{Howe:Weil}, where is it shown that $\trace(W_\psi)$ is determined by $\psi$ and its restriction to $\Sp(V)$ and, moreover, that $\trace(W_\psi)(g,v,z) =0$ unless $v\in \ker(g-1)$, in which case $(g,v,z)$ lies in a conjugacy class intersecting $\Sp(V) \ltimes Z$.
 %
 The group $\Sp(V)$ is naturally stratified into the conjugation-stable subvarieties $S_r = \{ g\in \Sp(V) \tq \dim \ker (g-1) = r \}$. 
-The big stratum, $S_0$, is dense in $\Sp(V)$. 
+The big stratum, $S_0$, is dense in $\Sp(V)$;
+the boundary of $S_0$ is $\cup_{0< r\leq \dim V} S_r$. 
 From \cite{Howe:Weil} we learn that $q^{-r/2} \trace(W_\psi)(g)$ has complex norm $1$, for $0\leq r \leq \dim V$ and $g\in S_r$.

### 2016-03-03 followup.tex
Got rid of some old instances of G --> Q, replaced with G --> G_0.

@@
 We may now revisit the definition of the functor $q_H^*: \CS(G_0)\to \CS_H(G)$:
-on objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$; on maps, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\alpha_0) = L_1(\alpha_0)$.
+on objects, $q_H^*: \CS(G_0)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$; on maps, $q_H^*: \CS(G_0)\to \CS_H(G)$ is given by $q_H^*(\alpha_0) = L_1(\alpha_0)$.
 Direct calculation confirms \cite{cunningham-roe:13a}*{CS1, CS2, CS3}, \eqref{E1}, \eqref{E2} and \eqref{ECS1}, and therefore that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$; 
@@
 %
-With this description of $q_H^*: \CS(Q)\to \CS_H(G)$ is is easy to see that it is an equivalence.
+With this description of $q_H^*: \CS(G_0)\to \CS_H(G)$ is is easy to see that it is an equivalence.
 Its adjoint is given on objects by $(\cs{L},\mu,\nu) \mapsto (R_1(\cs{L},\nu), R_2(\nu))$, making use of Lemma~\ref{lem:HH}, and on morphisms by $\alpha \mapsto R_1(\alpha)$.

### 2016-03-03 followup.tex
Arguable improvements to notation: back to Q. Typos.

--- 2016-03-03 followup.tex
@@
 
-Now suppose $q : G \to G_0$ is a regular epimorphism of smooth group schemes with kernel pair $(a,p)$
+Now suppose $q : G \to Q$ is a regular epimorphism of smooth group schemes with kernel pair $(a,p)$
 \[
@@
 & 
-G_0.
-\end{tikzcd}
-\]
-Let $\cs{L}_0$ be a linear character sheaf on $G_0$.
+Q.
+\end{tikzcd}
+\]
+Let $\cs{L}_0$ be a linear character sheaf on $Q$.
 Consider the functor
 \[
-q^* : \CS(G_0) \to \CS(G)
+q^* : \CS(Q) \to \CS(G)
 \]
@@
 Since this isomorphism satisfies \eqref{ECS1}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
-If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(G_0)$, 
+If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(Q)$, 
 then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha$ is a morphism in $\CS(G)$.
@@
 \[
-q_H^* : \CS(G_0) \to CS_H(G)
-\]
-and show that the functor $q^* : \CS(G_0) \to \CS(G)$ factors according to the following commuting diagram of functors
+q_H^* : \CS(Q) \to CS_H(G)
+\]
+and show that the functor $q^* : \CS(Q) \to \CS(G)$ factors according to the following commuting diagram of functors
 \begin{equation}\label{qH}
@@
 \CS(G) &\arrow{l}[swap]{q^*} 
-\CS(G_0) \arrow{dl}{q_H^*}\\
+\CS(Q) \arrow{dl}{q_H^*}\\
 \arrow{u}{\text{forget}} \CS_{H}(G). & 
@@
 \end{equation}
-The definition of $q_H^* : \CS(G_0)\to \CS_H(G)$ will be revisited in the proof of the following result.
+The definition of $q_H^* : \CS(Q)\to \CS_H(G)$ will be revisited in the proof of the following result.
 
 \begin{lemma}\label{lem:torsor}
-If $q : G \to G_0$ is an $H$-torsor in the fpqc topology 
-then $q_H^*: \CS(G_0) \to \CS_H(G)$ is an equivalence.
+If $q : G \to Q$ is an $H$-torsor in the fpqc topology 
+then $q_H^*: \CS(Q) \to \CS_H(G)$ is an equivalence.
 \end{lemma}
@@
 \begin{proof}
-First we observe that the comparison functor 
-$\Loc(G_0) \to \Loc_H(G)$ is an equivalence.
-To see this, first recall that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
-Then, observe that the comparison functor for Weil local systems is an equivalence for flat surjective morphisms of affine schemes over $\Fq$.
-It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fpqc topology; see \cite{Vistoli:notes}*{Lem 4.25} for example.
-(This is a slight variation on the argument showing that quasicoherent sheaves are a stack over schemes in the fpqc topology; see \cite{Vistoli:notes}*{Thm 4.23} for example.)
-Since $q : G\to G_0$ is an $H$-torsor in the fpqc topology, is now follows from descent theory that the comparison functor $\Loc(G_0) \to \Loc_H(G)$ is an equivalence; see \cite{Vistoli:notes}*{Thm 4.46} for example.)
-%\todo{Need more specific references}
-
-For use below, we write $L_1 : \Loc(G_0) \to \Loc_H(G)$ for the comparison functor, $R_1 : \Loc_H(G) \to \Loc(G_0)$ for its adjoint, and $(\epsilon_1, \eta_1)$ for the counit and unit of the adjunction.
-%
-Arguing as above, we also see that pull-back along $q\times q$ determines an equivalence $L_2 : \Loc(G_0\times G_0) \to \Loc_{H\times H}(G\times G)$.
-For use below, we write $R_2 : \Loc_{H\times H}(G\times G) \to \Loc(G_0\times G_0)$ for its adjoint and $(\epsilon_2, \eta_2)$ for the counit and unit of the adjunction.
-
-We may now revisit the definition of the functor $q_H^*: \CS(G_0)\to \CS_H(G)$:
+%First we observe that the comparison functor $\Loc(Q) \to \Loc_H(G)$ is an equivalence.
+%To see this, first recall that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
+%Then, observe that the comparison functor for Weil local systems is an equivalence for flat surjective morphisms of affine schemes over $\Fq$.
+%It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fpqc topology; see \cite{Vistoli:notes}*{Lem 4.25} for example.
+%(This is a slight variation on the argument showing that quasicoherent sheaves are a stack over schemes in the fpqc topology; see \cite{Vistoli:notes}*{Thm 4.23} for example.)
+Since $q : G\to Q$ is an $H$-torsor in the fpqc topology, is follows from descent theory that the comparison functor $\Loc(Q) \to \Loc_H(G)$ is an equivalence; see \cite{Vistoli:notes}*{Thm 4.46} for example.)
+%
+For use below, we write $L_1 : \Loc(Q) \to \Loc_H(G)$ for the comparison functor, $R_1 : \Loc_H(G) \to \Loc(Q)$ for its adjoint, and $(\epsilon_1, \eta_1)$ for the counit and unit of the adjunction.
+%
+Arguing as above, we also see that pull-back along $q\times q$ determines an equivalence $L_2 : \Loc(Q\times Q) \to \Loc_{H\times H}(G\times G)$.
+For use below, we write $R_2 : \Loc_{H\times H}(G\times G) \to \Loc(Q\times Q)$ for its adjoint and $(\epsilon_2, \eta_2)$ for the counit and unit of the adjunction.
+
+We may now revisit the definition of the functor $q_H^*: \CS(Q)\to \CS_H(G)$:
 on objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$; on maps, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\alpha_0) = L_1(\alpha_0)$.
@@
 
-It is one of the main results of \cite{Gurevich-Hadani:geometric_Weil} that there is a Weil sheaf $\cs{W}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
+It is one of the main results of \cite{Gurevich-Hadani:geometric_Weil} that there is a Weil sheaf complex $\cs{W}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
 \begin{equation}
@@
 
-First, fix an isomorphism $\CC \approx \EE$ so that we may mix classical and geometric facts. 
+Fix an isomorphism $\CC \approx \EE$ so that we may mix classical and geometric facts. 
 One begins by finding a local system $\cs{K}_0$ on $S_0 \times V^\sharp$ such that 
@@
  for $(g,v,z) \in S_0\times V\times Z$, where $\gamma_\psi$ is the Gauss sum for $\psi$ and $\sigma : \Fq^\times \to \EE^\times$ is the quadratic character of $\Fq^\times$.
-By a simple adaptation of what in \cite{Gurevich-Hadani:geometric_Weil}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible local system $\cs{K}_0$ on $S_0 \times V^\sharp$.
+By a simple adaptation of what in \cite{Gurevich-Hadani:geometric_Weil}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}_0$ on $S_0 \times V^\sharp$.
 Next, one forms $\cs{K} \ceq j_{!*} \cs{K}_0$, the perverse extension of $\cs{K}_0$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$; recall that $S_0$ is Zariski dense in $\Sp(V)$.
@@
 \]
-Then $\cs{W}_\psi = \cs{K}[\dim V](\dim V)$ is the promised Weil sheaf.
+Then $\cs{W}_\psi = \cs{K}[\dim V](\dim V)$ is the promised Weil sheaf complex.
 
@@
 
-As a step toward geometrizing the type $(C,\rho)$, we now recall some results from \cite{yu:03a}.
+Regarding the construction of the type $(C,\rho)$, the paper \cite{yu:03a} concludes with the following provocative observation.
+\begin{quotation}
+{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
+ the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
+These results suggest that algebraic geometry and group schemes should play an
+important role in the representation theory of $p$-adic groups.} \cite{yu:03a}
+\end{quotation}
+In this section we explain what this observation is saying, following \cite{yu:03a}.
 
@@
 
-Regarding the construction of the type $(C,\rho)$, the paper \cite{yu:03a} concludes with the following provocative observation, which we have just revisited.
-\begin{quotation}
-{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
- the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
-These results suggest that algebraic geometry and group schemes should play an
-important role in the representation theory of $p$-adic groups.} \cite{yu:03a}
-\end{quotation}
-%In fact, Yu's description of how to assemble $\rho$ from $(\rho^0, \varphi^0, \ldots , \varphi^d)$ is slightly different, but equivalent, to what we have done here \cite{Yu:models}*{}.
-
 \subsection{Geometrization of characters of types}\label{ssec:geotypes}
@@
 Assume $\pi_0(\underline{G}^0)_\Fq^\reductive)$ is cyclic.
-Then there is a virtual Weil sheaf $\cs{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
+Then there is a virtual Weil sheaf complex $\cs{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
 \end{proposition}
@@
 \]
-The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $G_0^0 = \Gr^{R}_0(\underline{G}^0)$ \cite{cunningham-roe:13a}*{\S 4.3}.
-With $m\in \NN$ as above, let ${A}_m^0$ be the Weil sheaf on the algebraic group $G_m^i$ obtained by pull-back from $A^0$ along the affine morphism $G_m^i \to G_0^0$.
+The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $Q^0 = \Gr^{R}_0(\underline{G}^0)$ \cite{cunningham-roe:13a}*{\S 4.3}.
+With $m\in \NN$ as above, let ${A}_m^0$ be the Weil sheaf on the algebraic group $G_m^i$ obtained by pull-back from $A^0$ along the affine morphism $G_m^i \to Q^0$.
 Factor

### 2016-03-03 followup.tex
Updating references

@@
 
-The character $\trace(W_\psi) : \Sp(V)\ltimes V^\sharp \to \EE^\times$ of $W_\psi$ is studied in \cite{Howe:Weil}, where is it shown that $\trace(W_\psi)$ is determined by $\psi$ and its restriction to $\Sp(V)$ and, moreover, that $\trace(W_\psi)(g,v,z) =0$ unless $v\in \ker(g-1)$, in which case $(g,v,z)$ lies in a conjugacy class intersecting $\Sp(V) \ltimes Z$.
+The character $\trace(W_\psi) : \Sp(V)\ltimes V^\sharp \to \EE^\times$ of $W_\psi$ is studied in \cite{howe:73a}, where is it shown that $\trace(W_\psi)$ is determined by $\psi$ and its restriction to $\Sp(V)$ and, moreover, that $\trace(W_\psi)(g,v,z) =0$ unless $v\in \ker(g-1)$, in which case $(g,v,z)$ lies in a conjugacy class intersecting $\Sp(V) \ltimes Z$.
 %
@@
 the boundary of $S_0$ is $\cup_{0< r\leq \dim V} S_r$. 
-From \cite{Howe:Weil} we learn that $q^{-r/2} \trace(W_\psi)(g)$ has complex norm $1$, for $0\leq r \leq \dim V$ and $g\in S_r$.
-
-It is one of the main results of \cite{Gurevich-Hadani:geometric_Weil} that there is a Weil sheaf complex $\cs{W}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
+From \cite{howe:73a}*{Prop. 2} we learn that $q^{-r/2} \trace(W_\psi)(g)$ has complex norm $1$, for $0\leq r \leq \dim V$ and $g\in S_r$.
+
+It is one of the main results of \cite{gurevich-hadani:07a} that there is a Weil sheaf complex $\cs{W}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
 \begin{equation}
@@
  for $(g,v,z) \in S_0\times V\times Z$, where $\gamma_\psi$ is the Gauss sum for $\psi$ and $\sigma : \Fq^\times \to \EE^\times$ is the quadratic character of $\Fq^\times$.
-By a simple adaptation of what in \cite{Gurevich-Hadani:geometric_Weil}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}_0$ on $S_0 \times V^\sharp$.
+By a simple adaptation of what in \cite{gurevich-hadani:07a}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}_0$ on $S_0 \times V^\sharp$.
 Next, one forms $\cs{K} \ceq j_{!*} \cs{K}_0$, the perverse extension of $\cs{K}_0$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$; recall that $S_0$ is Zariski dense in $\Sp(V)$.
-It follows from \cite{Gurevich-Hadani:geometric_Weil} that 
+It follows from \cite{gurevich-hadani:07a} that 
 \[
@@
 \end{document}
-
-\bib{Howe}{article}{
-   author={Howe, Roger E.},
-   title={On the character of Weil's representation},
-   journal={Trans. Amer. Math. Soc.},
-   volume={177},
-   date={1973},
-   pages={287--298},
-   issn={0002-9947},
-   review={\MR{0316633}},
-}

### 2016-03-03 followup.tex
Adding reference to Gurevich-Hadani preprint

@@
 
-It is one of the main results of \cite{gurevich-hadani:07a} that there is a Weil sheaf complex $\cs{W}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
+It is one of the main results of \cite{gurevich-hadani:07a} (see also \cite{gurevich-hadani:11a}*{Thm. 4.5}) that there is a Weil sheaf complex $\cs{W}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
 \begin{equation}

### 2016-03-03 followup.tex
Typo and shift and twist corrections

@@
 \[
-\trFrob{\cs{K}_0[2\dim V](\dim V)} = \trace(W_\psi)\vert_{S_0\times V^\sharp},
-\]
-where $\cs{K}_0[2\dim V](\dim V)$ is the Tate twist of the shift of $\cs{K}_0$.
+\trFrob{\cs{K}_0[\dim V](\frac{\dim V}{2})} = \trace(W_\psi)\vert_{S_0\times V^\sharp},
+\]
+where $\cs{K}_0[\dim V](\frac{\dim V}{2})$ is the Tate twist of the shift of $\cs{K}_0$.
 This is done by observing that $S_0$ is the domain of the Cayley transform $\cay : g \mapsto (g-1)^{-1}(g+1)$ on $\Sp(V)$ and that 
 \begin{equation}\label{Cayley}
-\trace(W_\psi)(g,v,z) =  q^{-\dim V} \gamma_\psi^{\dim V} \sigma(\det(1+\cay(g))) \psi(\langle \cay(g)v,v\rangle) \psi(z),
+\trace(W_\psi)(g,v,z) =  q^{-\dim V/2} \gamma_\psi^{\dim V} \sigma(\det(1+\cay(g))) \psi\left(\frac{1}{4}\langle \cay(g)v,v\rangle \right) \psi(z),
 \end{equation}
@@
 \[
-\trFrob{\cs{K}[\dim V](\dim V)} = \trace(W_\psi).
-\]
-Then $\cs{W}_\psi = \cs{K}[\dim V](\dim V)$ is the promised Weil sheaf complex.
+\trFrob{\cs{K}(\frac{\dim V}{2})} = \trace(W_\psi).
+\]
+Then $\cs{W}_\psi = \cs{K}(\frac{\dim V}{2})$ is the promised Weil sheaf complex.
 

### 2016-03-03 followup.tex
The dictionary. Introduction. Typos

@@
 
-\title[Geometrization of characters of smooth group schemes]{Geometrization of characters of smooth group schemes over finite fields\\ with an application to types for supercuspidal representations}
+\title[Commutative Character Sheaves]{The Dictionary for characters of smooth group schemes}
 \author{Clifton Cunningham}
@@
 We now summarize the sections of the paper in more detail.
-
-%\begin{enumerate}
-%\item
+%
 In Section \ref{sec:defs}, we recall the category $\CS(G)$ from \cite{cunningham-roe:13a} and note that it still makes sense when $G$ is not commutative.  
-
-%\item
+%
 We focus on the case of commutative $G$ in Section \ref{sec:comcom},
@@
 $\TrFrob{G} : \CSiso{G} \to G(k)^*$ induces an isomorphism on $\CCSiso{G}$.
-
-%\item
+%
 Passing to the case that $G$ is non-commutative, we give the definition of and main results about commutative character sheaves in Section \ref{sec:noncom}.  
@@
 Then in Section \ref{ssec:proofs}, we give proofs of the results in Section \ref{sec:noncom}, which require a development of equivariant linear character sheaves.
-
-%\item
+%
 In Section~\ref{sec:types} we use Theorem~\ref{thm:geo} to geometrize the representations of compact $p$-adic groups appearing in the types for: we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\rho)$.
 The proof of this statement is quite technical, so it must be delayed to Section~\ref{ssec:geotypes}, after reviewing types in Section~\ref{ssec:review} and models Section~\ref{ssec:models} developed by Yu, for which we must also review some facts about the Heisenberg-Weil representation and its geometrization, in Section~\ref{ssec:Jacobi}.
-%\end{enumerate}
 
@@
 %(This is a slight variation on the argument showing that quasicoherent sheaves are a stack over schemes in the fpqc topology; see \cite{Vistoli:notes}*{Thm 4.23} for example.)
-Since $q : G\to Q$ is an $H$-torsor in the fpqc topology, is follows from descent theory that the comparison functor $\Loc(Q) \to \Loc_H(G)$ is an equivalence; see \cite{Vistoli:notes}*{Thm 4.46} for example.)
+Since $q : G\to Q$ is an $H$-torsor in the fpqc topology, is follows from descent theory that the comparison functor $\Loc(Q) \to \Loc_H(G)$ is an equivalence; argue as in \cite{Vistoli:notes}*{Thm 4.46}, for example.
 %

### 2016-03-28 followup.tex
Clarified the proof of Proposition {prop:Gder_triv}.

@@
 
-The first aim of this paper is to repair this defect in the function-sheaf dictionary by describing a full subcategory $\CCS(G)$ of $\CS(G)$ so that $\TrFrob{G}$ restricts to an isomorphism $\CCSiso{G} \to G(k)^*$.
+The first aim of this paper is to repair this defect in the function-sheaf dictionary for characters of smooth commutative group schemes $G$ by describing a full subcategory $\CCS(G)$ of $\CS(G)$ so that $\TrFrob{G}$ restricts to an isomorphism $\CCSiso{G} \to G(k)^*$.
 We refer to the resulting objects as \emph{commutative character sheaves}, since the passage from $\CS(G)$ to $\CCS(G)$ involves a condition that exchanges the inputs to the multiplication morphism on $G$ (see Definition \ref{def:CCScom}).
@@
 
-Next, we broaden our scope further to encompass smooth group schemes $G$ that are not necessarily commutative.
-In this paper, we do not consider Lusztig's geometrization of arbitrary characters of connected, reductive groups $G(k)$
-using character sheaves \cite{lusztig:85a}*{Def.~2.10}, but focus on the case of $1$-dimensional characters
-$G(k)^*$ assuming only that $G$ is smooth, allowing for the possibility that $G$ is not connected and not reductive.
+Next, we broaden our scope further to encompass smooth group schemes $G$ over $\Fq$ that are not necessarily commutative.
+In this paper, we do not consider Lusztig's geometrization of characters of representations of connected, reductive groups $G(k)$
+using character sheaves \cite{lusztig:85a}*{Def.~2.10}, but focus on the case of characters
+$G(k)^*$ (that is, group homomorphisms from $G(k)$ to $\EEx$), assuming only that $G$ is smooth, allowing for the possibility that $G$ is not connected and not reductive.
 The category $\CS(G)$ has a straightforward generalization to this case, but again
-there are more linear character sheaves than there are characters, as pointed out by Kamgarpour \cite{kamgarpour:09a}*{(1.1)}.
+there are more character sheaves than there are characters, as pointed out by Kamgarpour \cite{kamgarpour:09a}*{(1.1)}.
 We define a category $\CCS(G)$ and a forgetful functor to $\CS(G)$ so that $\TrFrob{G} : \CCSiso{G} \to G\ab(k)^*$
@@
 In order to obtain a relationship between character sheaves on $G$ and characters of $G(k)$,
-he opts to give a different definition of commutator.  Since we already need to adapt our
+he opts to give a different definition of commutator and, in doing so, introduces a `stacky abelianization' of $G$ in order to geometrize characters of $G(\Fq)$.
+ Since we has already seen the need to adapt the
 notion of character sheaf, even in the commutative case, we instead add restrictions
-to the definition of commutative character sheaf and leave the definition of $G\der$ unchanged.
-
-\subsection{Definition}\label{ssec:noncomdef}
+to the definition of commutative character sheaf and leave the definition of $G\der$ unchanged, allowing us to use the schematic abelianization of $G$ in the geometrization of characters of $G(\Fq)$; see Theorem~\ref{thm:geo}.
+
+\subsection{Main definition}\label{ssec:noncomdef}
 
@@
 character sheaves whose restriction to the derived subgroup is nontrivial.
-The following proposition will be proven in Section \ref{ssec:proof1}.
+Recall from Section~\ref{sec:defs} that we refer to objects in category $\CS(G)$, defined as in \cite{cunningham-roe:13a}*{Def.
+1.1}, as linear character sheaves  when $G$ is smooth but not necessarily commutative.
+
 \begin{proposition} \label{prop:Gder_triv}
-Suppose $G$ is a smooth group scheme and $\cs{L} \in \CS(G)$ is a linear character sheaf on $G$.
-Then the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $\cs{L} \cong q^*(\cs{L}\ab)$ for some
-character sheaf $\cs{L}\ab$ on $G\ab$.
+Suppose $G$ is a smooth group scheme and $(\cs{L},\mu) \in \CS(G)$.
+Then the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $(\cs{L},\mu) \cong q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, for some $(\cs{L}\ab,\mu\ab) \in \CS(G\ab)$.
 \end{proposition}
+
+Proposition~\ref{prop:Gder_triv} will be proven in Section \ref{ssec:proof1}.
 
@@
 %Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
-Category $\CCS(G)$ is monoidal and $\CCSiso{G} \iso \Hom(G\ab(\Fq),\EEx)$, canonically.
+Category $\CCS(G)$ is monoidal and 
+\[
+\CCSiso{G} \iso \Hom(G\ab(\Fq),\EEx),
+\]
+canonically.
 Every map in $\CCS(G)$ is either trivial or an isomorphism, and the automorphism group of any object in $\CCS(G)$ is $\Hom(\pi_0(G\ab)_{\Frob{}},\EEx)$, canonically.
@@
 On the other hand, by Lemma~\ref{lem:beta}, $\CS'(G) \to \CS_{H}(G)$, defined by $(\cs{L},\mu,\beta)\mapsto (\cs{L},\mu, \nu)$, is an equivalence.
+
+Now, suppose $(\cs{L},\mu)\in \CS(G)$ and there is an isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ in $\CS(H)$.
+Then $(\cs{L},\mu,\beta) \in \CS'(G)$.
+We have just seen that $\CS'(G)$, $\CS_H(G)$ and $\CS(G\ab)$ are equivalent categories.
+Let $(\cs{L},\mu,\beta) \mapsto (\cs{L},\mu,\nu)$ under the equivalence $\CS'(G) \to \CS_H(G)$ described above.
+Then $(\cs{L},\mu,\nu) \iso q_H^*(\cs{L}\ab,\mu\ab)$ in $\CS_H(G)$, for some $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$.
+Applying the forgetful functor $\CS_H(G)\to \CS(G)$ to this isomorphism, it follows that $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, as desired.
+
+Conversely, suppose $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$.
+Then $j^*(\cs{L},\mu) \iso j^*q^*(\cs{L}\ab,\mu\ab)$ in $\CS(H)$. 
+Since $g\circ j = 1$, it follows that $\cs{L}\vert_{G\der} \to (\EE)_{H}$ in $\CS(H)$.
 This completes the proof of Proposition~\ref{prop:Gder_triv}.

### 2016-03-28 followup.tex
Added comparison of notation with Yu.

@@
 \] 
-Set $G_m = \Gr_m^{R}(\underline{G})$.
-Then $G_m$ is a smooth group scheme over $\Fq$ and $G_m(\Fq) = \underline{G}(R/\mathfrak{p}^{m+1})$, canonically.
-Using Theorem~\ref{thm:geo}, let $\cs{L}_m$ be a geometrization of the linear character $\varphi_m: G_m \to \EEx$; so
+Set $R_m = R/\mathfrak{p}^{m+1}$ and
+set $G_m = \Gr_m^{R}(\underline{G})$, the Greenberg transform of $\underline{G}\times_{\Spec{R}}\Spec{R_m}$.
+Then $G_m$ is a smooth group scheme over $\Fq$ and $G_m(\Fq) = \underline{G}(R_m)$, canonically.
+Using Theorem~\ref{thm:geo}, let $\cs{L}_m$ be a geometrization of the character $\varphi_m: G_m \to \EEx$; so
 \[
@@
 Let $\cs{L}$ be the  Weil sheaf on $G$ obtained from $\cs{L}_m$ by pullback along $G \to G_m$. 
-Then $\cs{L}$ is a quasicharacter sheaf on $G$, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, such that $\trFrob{\cs{L}} = \trace \varphi$.
+Then $\cs{L}$ is a quasicharacter sheaf on $G$, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, such that $\trFrob{\cs{L}} = \varphi$.
 \end{proof}
@@
 
-Let $\psi : Z \to \EEx$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi : Z \to CC^\times$. 
+Let $\psi : Z \to \CC^\times$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi$. 
 The Heisenberg representation determines a representation $\pi_{\psi}$ of $\Sp(V)$ with the same representation space as $\omega_\psi$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\psi(g)$ determines an isomorphism of representations $\omega_\psi^g \to \omega_\psi$.
@@
 The group $\Sp(V)$ is naturally stratified into the conjugation-stable subvarieties $S_r = \{ g\in \Sp(V) \tq \dim \ker (g-1) = r \}$. 
-The big stratum, $S_0$, is dense in $\Sp(V)$;
-the boundary of $S_0$ is $\cup_{0< r\leq \dim V} S_r$. 
-From \cite{howe:73a}*{Prop. 2} we learn that $q^{-r/2} \trace(W_\psi)(g)$ has complex norm $1$, for $0\leq r \leq \dim V$ and $g\in S_r$.
-
-It is one of the main results of \cite{gurevich-hadani:07a} (see also \cite{gurevich-hadani:11a}*{Thm. 4.5}) that there is a Weil sheaf complex $\cs{W}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
+The big stratum, $S_0$, is dense in $\Sp(V)$.
+%the boundary of $S_0$ is $\cup_{0< r\leq \dim V} S_r$. 
+ From \cite{howe:73a}*{Prop. 2} we learn that if $g\in S_r$ then $q^{-r/2} \trace(W_\psi)(g)$ has complex norm $1$.
+
+It is one of the main results of \cite{gurevich-hadani:07a} (see also \cite{gurevich-hadani:11a}*{Thm. 4.5}) that there is a Weil sheaf complex $\cs{K}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
 \begin{equation}
-\trFrob{\cs{W}_\psi} = \trace(W_\psi).
+\trFrob{\cs{K}_\psi} = \trace(W_\psi).
 \end{equation}
 %
-Although nothing more that this statement will be needed below, the construction of $\cs{W}_\psi$ is so unbelievably gorgeous that we can't resist saying a few extra words about it here.
-The reader pressed for time is invited to skip to the next section without loosing anything needed for the arguments in the rest of Section~\ref{sec:types}.
+Since $\cs{K}_\psi$ is an object in Deligne's category $D^b_c(\Sp(V)\ltimes V^\sharp,\EE)$, the left hand since of this equality must be interpreted accordingly.
+
+Although nothing more that this statement will be needed below, the construction of $\cs{K}_\psi$ is so unbelievably gorgeous that we can't resist saying a few extra words about it here.
+The reader pressed for time is invited to skip the next paragraph without loosing anything needed for the arguments in the rest of Section~\ref{sec:types}.
 
 Fix an isomorphism $\CC \approx \EE$ so that we may mix classical and geometric facts. 
-One begins by finding a local system $\cs{K}_0$ on $S_0 \times V^\sharp$ such that 
+One begins by observing that $S_0$ is the domain of the Cayley transform $\cay : g \mapsto (g-1)^{-1}(g+1)$ on $\Sp(V)$ and that if $(g,v,z) \in S_0\times V\times Z$ then
+\begin{equation}\label{Cayley}
+\trace(W_\psi)(g,v,z) =  \frac{\gamma_\psi^{\dim V}}{q^{\dim V/2} } \sigma(\det(1+\cay(g)))\ \psi\left(\langle \cay(g)v,v\rangle/4 \right) \psi(z),
+\end{equation}
+ where $\gamma_\psi$ is the Gauss sum for $\psi$ and $\sigma : \Fq^\times \to \EE^\times$ is the quadratic character of $\Fq^\times$.
+By a simple adaptation of what in \cite{gurevich-hadani:07a}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}_0$ (in fact, a Weil local system) on $S_0 \times V^\sharp$ such that
 \[
@@
 where $\cs{K}_0[\dim V](\frac{\dim V}{2})$ is the Tate twist of the shift of $\cs{K}_0$.
-This is done by observing that $S_0$ is the domain of the Cayley transform $\cay : g \mapsto (g-1)^{-1}(g+1)$ on $\Sp(V)$ and that 
-\begin{equation}\label{Cayley}
-\trace(W_\psi)(g,v,z) =  q^{-\dim V/2} \gamma_\psi^{\dim V} \sigma(\det(1+\cay(g))) \psi\left(\frac{1}{4}\langle \cay(g)v,v\rangle \right) \psi(z),
-\end{equation}
- for $(g,v,z) \in S_0\times V\times Z$, where $\gamma_\psi$ is the Gauss sum for $\psi$ and $\sigma : \Fq^\times \to \EE^\times$ is the quadratic character of $\Fq^\times$.
-By a simple adaptation of what in \cite{gurevich-hadani:07a}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}_0$ on $S_0 \times V^\sharp$.
-Next, one forms $\cs{K} \ceq j_{!*} \cs{K}_0$, the perverse extension of $\cs{K}_0$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$; recall that $S_0$ is Zariski dense in $\Sp(V)$.
+%
+Next, one forms $\cs{K}_\psi \ceq j_{!*} \cs{K}_0$, the perverse extension of $\cs{K}_0$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$; recall that $S_0$ is Zariski dense in $\Sp(V)$.
 It follows from \cite{gurevich-hadani:07a} that 
 \[
-\trFrob{\cs{K}(\frac{\dim V}{2})} = \trace(W_\psi).
-\]
-Then $\cs{W}_\psi = \cs{K}(\frac{\dim V}{2})$ is the promised Weil sheaf complex.
+\trFrob{\cs{K}} = \trace(W_\psi).
+\]
+Then $\cs{K}_\psi$ is the promised Weil sheaf complex.
 
@@
 %
-
 A Yu type is then a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$, directly from the following information, derived from a Yu datum:
@@
 \end{enumerate}
-The representations $(\rho^0, \varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho^d = \rho$.
+The groups $C^i$ here are the groups $\,^\circ K^i$ in \cite{yu:01a}; the representation $\rho^0$ here is the representation $\pi_0\vert_{\,^\circ K^0}$ in \cite{yu:01a}; the quasicharacters $\varphi^i$ here are the quasicharacters $\phi_i\vert_{\,^\circ K^i}$ in \cite{yu:01a}.
+%
+The representation $\rho^0$ and the quasicharacters $(\varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho^d = \rho$.
+%
 
 Since we will need some facts about this construction, we review some further detail here.
-
+In Table~\ref{table:notation} we explain how to convert the rest of the constructions appearing in this section into the notation of \cite{yu:01a}.
+%
 First, Yu introduces 
@@
 \labitem{Y3}{Y3}
-compact groups $J^i\subset C$, for $i=0, \ldots d$, such that 
+compact groups $J_i\subset C$, for $i=0, \ldots d$, such that 
 $
-C^i = J^0\cdots J^{i}
+C^i = J_0\cdots J_{i}
 $ 
-and, for $i=0, \ldots d-1$, a natural action of $C^i$ on $J^{i+1}$ defining the groups $C^i \ltimes J^{i+1}$.
+and, for $i=0, \ldots d-1$, a natural action of $C^i$ on $J_{i+1}$ defining the groups $C^i \ltimes J_{i+1}$.
 \begin{equation}\label{eq:semiprod}
@@
 \ && 1 \arrow{d} && \\
-\ && C^{i}\cap J^{i+1}\arrow{d} && \\
-1 \arrow{r} & J^{i+1} \arrow{r} & C^i \ltimes J^{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} & 1\\
+\ && C^{i}\cap J_{i+1}\arrow{d} && \\
+1 \arrow{r} & J_{i+1} \arrow{r} & C^i \ltimes J_{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} & 1\\
 && C^{i+1} \arrow{d}{} && \\
@@
 \end{enumerate}
-%He then introduces the following quotients of $J^{i+1}$ and $C^i$, for $i=0, \ldots d-1$.
-
+%He then introduces the following quotients of $J_{i+1}$ and $C^i$, for $i=0, \ldots d-1$.
+%
 Next, Yu uses this to define a group homomorphism (in fact, a quotient) 
 $
-J^{i+1} \to V_{i+1}
+J_{i+1} \to V_{i+1}
 $
 where $V_{i+1}$ is a finite abelian group, the latter also given the structure of a $\Fq$-vector space.
-The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : C_{i+1} \to \EEx$.
+The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to Z_{i+1}$, where $Z_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : Z_{i+1} \to \EEx$.
 %\labitem{Q2}{Q2} 
@@
 $
-J^{i+1} \to V_{i+1}^\sharp,
+J_{i+1} \to V_{i+1}^\sharp,
 $
-where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $C_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$.
-In fact, the quotient $J^{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J^{i+1} \to H^{i+1}$ and an isomorphism 
+where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $Z_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$.
+In fact, the quotient $J_{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J_{i+1} \to H^{i+1}$ and an isomorphism 
 $
@@
 such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H^{i+1}$ in the sense of \cite{yu:01a}.
-
+%
 Taken together, this defines
@@
 \begin{enumerate}
-\labitem{Y4}{Y4}  a group homomorphism $h_{i+1} : C^i \ltimes J^{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
-\[
-\begin{tikzcd}
-1 \arrow{r} & J^{i+1} \arrow{d} \arrow{r} & C^i \ltimes J^{i+1} \arrow{d}{h_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} \arrow{d}{f_i} & 1\\ 
+\labitem{Y4}{Y4}  a group homomorphism $h_{i+1} : C^i \ltimes J_{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
+\[
+\begin{tikzcd}
+1 \arrow{r} & J_{i+1} \arrow{d} \arrow{r} & C^i \ltimes J_{i+1} \arrow{d}{h_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} \arrow{d}{f_i} & 1\\ 
 1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
@@
 Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
-Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $C^i \ltimes J^{i+1}$.
-Write $\inf(\rho^i \otimes \varphi^i)$ for the representation of $C^i \ltimes J^{i+1}$ obtained by pulling back $\rho^i$ along $C^i \ltimes J^{i+1} \to C^i$. 
+Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $C^i \ltimes J_{i+1}$.
+Write $\inf(\rho^i \otimes \varphi^i)$ for the representation of $C^i \ltimes J_{i+1}$ obtained by pulling back $\rho^i$ along $C^i \ltimes J_{i+1} \to C^i$. 
 Consider the representation
@@
 \end{equation}
-of $C^i \ltimes J^{i+1}$.
+of $C^i \ltimes J_{i+1}$.
 %By construction, the character of this representation satisfies
@@
 %\end{equation}
-%for $y \in C^i \ltimes J^{i+1}$.
-By \cite{yu:01a}*{}, the representation $\rho_{i+1}$ of $C^i \ltimes J^{i+1}$ is trivial on $C^{i}\cap J^{i+1}$ so $\rho_{i+1}$ descends to $C^{i+1}$.
+%for $y \in C^i \ltimes J_{i+1}$.
+By \cite{yu:01a}*{}, the representation $\rho_{i+1}$ of $C^i \ltimes J_{i+1}$ is trivial on $C^{i}\cap J_{i+1}$ so $\rho_{i+1}$ descends to $C^{i+1}$.
 
@@
 This completes the recursive definition and thus determines $\rho^d$. 
-Now set $\rho \ceq \rho^d\otimes \varphi^d$, which is the representation of $C^d = C$ determining the Yu type $(C,\rho)$.
-%The character of $\rho^d$ on $C^d = C = J^0 \cdots J^d$ satisfies
+Now set $\rho \ceq \rho^d\otimes \varphi^d$. 
+This is the representation of $C^d = C$ determining the Yu type $(C,\rho)$.
+%The character of $\rho^d$ on $C^d = C = J_0 \cdots J_d$ satisfies
 %\[
@@
 %\]
-%for $k_i\in J^i$.
+%for $k_i\in J_i$.
+
+\begin{table}[htp]
+\caption{Comparison with notation of \cite{yu:01a}}
+\begin{center}
+\begin{tabular}{c|l}
+$C^0$ & $\,^\circ K^0 = G^i(F)_y$, \cite{yu:01a}*{\S 15} \\
+$\rho^0$ & $\,^\circ \rho_0$ \cite{yu:01a}*{\S 15} \\
+$C^{i+1}$ & $\,^\circ K^i = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, l\dots, s_{i})}$, \cite{yu:01a}*{\S 15} \\
+$\rho^{i+1}$ & $\,^\circ \rho_{i+1}$, \cite{yu:01a}*{\S 15} \\
+$\varphi^i$ & $\phi_i\vert_{\,^\circ K^i }$ \\
+$J_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}$ \\
+$V_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ (G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}$ \\ 
+$W_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi}_i\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
+$H^{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi_i}\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
+$Z_{i+1}$ & $C$, \cite{yu:01a}*{\S 11} \\
+$(f_{j+1}, j_{i+1})$ & $(f,j)$ \cite{yu:01a}*{\S 11} \\
+$\langle\ ,\ \rangle_{i+1}$ & $\langle\ ,\ \rangle$, \cite{yu:01a}*{\S 11} \\
+\end{tabular}
+\end{center}
+\label{table:notation}
+\end{table}%
 
@@
 \] 
-for each $i=0,\ldots d$, such that $\underline{J}^i(R) = J^i$ as a subgroup of $C$ and such that the image of the $R$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $C^i$, for $i=0, \ldots , d$.
+for each $i=0,\ldots d$, such that $\underline{J}^i(R) = J_i$ as a subgroup of $C$ and such that the image of the $R$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $C^i$, for $i=0, \ldots , d$.
 %\labitem{M3}{M3}
@@
 \]
-gives $(\underline{G}^i \ltimes \underline{J}^{i+1})(R) = C^i \ltimes J^{i+1}$
+gives $(\underline{G}^i \ltimes \underline{J}^{i+1})(R) = C^i \ltimes J_{i+1}$
 %\end{enumerate}
@@
 Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
-The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $V^{i+1}_\Fq$, where $V^{i+1}_\Fq$, appears as a quotient $J^{i+1}_\Fq \to V^{i+1}_\Fq$ of algebraic groups.
-Then the quotient $J^{i+1} \to V_{i+1}$ is realized as the composition
+The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $V^{i+1}_\Fq$, where $V^{i+1}_\Fq$, appears as a quotient $J_{i+1} \to V^{i+1}$ of algebraic groups over $\Fq$.
+Then the quotient $J_{i+1} \to V_{i+1}$ is realized as the composition
 \[
@@
 \]
-Likewise, the Heisenberg $p$-group $H^{i+1}$, appearing in \ref{ssec:review}, may be realized as a quotient of algebraic groups, and $J^{i+1}\to H^{i+1}$ as the composition 
+Likewise, the Heisenberg $p$-group $H^{i+1}$, appearing in \ref{ssec:review}, may be realized as a quotient of algebraic groups, and $J_{i+1}\to H^{i+1}$ as the composition 
 \[
@@
 \]
-Finally, the group homomorphism $f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ may be made geometric in much the same way. 
-Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ is realized as the composition
+Finally, the group homomorphism $f_i : J_0\cdots J_i \to \Sp(V_{i+1})$ may be made geometric in much the same way. 
+Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $f_i : J_0\cdots J_i \to \Sp(V_{i+1})$ is realized as the composition
 \[
@@
 G^i(\Fq) \arrow{rr}{\varphi^i} \arrow{rd} && \EEx\\
-& \underline{G}^i(R/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi^i_m} 
+& \underline{G}^i(R_m) \arrow{ru}[swap]{\varphi^i_m} 
 \end{tikzcd}
@@
 Set $G_m^i = \Gr_m^{R}(\underline{G}^i)$.
-Then $G_m^i$ is a smooth group scheme over $\Fq$ and $G_m^i(\Fq) = \underline{G}^i(R/\mathfrak{p}^{m+1})$, canonically.
+Then $G_m^i$ is a smooth group scheme over $\Fq$ and $G_m^i(\Fq) = \underline{G}^i(R_m)$, canonically.
 Using Theorem~\ref{thm:geo}, let $\cs{L}^i_m$ be a geometrization of the linear character $\varphi^i_m: G_m^i \to \CC^\times$; so
 \[
-\trFrob{\cs{L}^i_m} = \trace \varphi^i_m.
+\trFrob{\cs{L}^i_m} = \varphi^i_m.
 \]
@@
 Consider the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ and the Heisenberg-Weil representation $W_{i+1}$ appearing in Section~\ref{ssec:models}.
-Let $\cs{W}_{i+1}$ be the Weil sheaf on the Jacobi group, recalled in Section~\ref{ssec:Jacobi}, such that
-\[
-\trFrob{\cs{W}_{i+1}} = \trace(W_{i+1}).
+Let $\cs{K}_{i+1}$ be the Weil sheaf on the Jacobi group, recalled in Section~\ref{ssec:Jacobi}, such that
+\[
+\trFrob{\cs{K}_{i+1}} = \trace(W_{i+1}).
 \]
 Recall from Section~\ref{ssec:models} that $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ is a quotient of the special fibre of the smooth group scheme $\underline{G}^{i} \ltimes \underline{J}^{i+1}$.
-Let $\cs{W}_0^{i+1}$ be the Weil sheaf on the special fibre of $\underline{G}^{i} \ltimes \underline{J}^{i+1}$ obtained from $W_{i+1}$ by pullback. 
-Let $\cs{W}_m^{i+1}$ be the Weil sheaf on $\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1})$ obtained from $\cs{W}_0^{i+1}$ by pullback along the affine morphism
+Let $\cs{K}_0^{i+1}$ be the Weil sheaf on the special fibre of $\underline{G}^{i} \ltimes \underline{J}^{i+1}$ obtained from $W_{i+1}$ by pullback. 
+Let $\cs{K}_m^{i+1}$ be the Weil sheaf on $\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1})$ obtained from $\cs{K}_0^{i+1}$ by pullback along the affine morphism
 $\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1}) \to \Gr^{R}_0(\underline{G}^{i} \ltimes \underline{J}^{i+1})$.
@@
 \[
-\cs{B}_m^{i+1} \ceq \cs{W}_m^{i+1} \otimes (p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
+\cs{B}_m^{i+1} \ceq \cs{K}_m^{i+1} \otimes (p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
 \]

### 2016-03-29 followup.tex
Fixed some notation recalled from Yu. Playing with (yet another) title.

@@
 
-\title[Commutative Character Sheaves]{The Dictionary for characters of smooth group schemes}
+\title[Commutative Character Sheaves]{Geometrization of characters of smooth group schemes}
+%\title[Commutative Character Sheaves]{The Dictionary for characters of smooth group schemes}
 \author{Clifton Cunningham}
@@
 With notation as above, suppose $\Fq$ is a finite field.
-For every quasicharacter character $\varphi : \underline{G}(S) \to \EEx$ there is a Weil sheaf $\cs{L}$ on $G$ such that \[\trFrob{\cs{L}} = \trace \varphi.\] \end{proposition}
+For every quasicharacter character $\varphi : \underline{G}(S) \to \EEx$ there is a Weil sheaf $\cs{L}$ on $G$ such that \[\trFrob{\cs{L}} =  \varphi.\] \end{proposition}
 
@@
 \underline{G}(S) \arrow{rr}{\varphi} \arrow{rd} && \EEx\\
-& \underline{G}(R/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi_m} 
+& \underline{G}(R/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi^m} 
 \end{tikzcd}
@@
 Then $G_m$ is a smooth group scheme over $\Fq$ and $G_m(\Fq) = \underline{G}(R_m)$, canonically.
-Using Theorem~\ref{thm:geo}, let $\cs{L}_m$ be a geometrization of the character $\varphi_m: G_m \to \EEx$; so
-\[
-\trFrob{\cs{L}_m} = \varphi_m
+Using Theorem~\ref{thm:geo}, let $\cs{L}_m$ be a geometrization of the character $\varphi^m: G_m \to \EEx$; so
+\[
+\trFrob{\cs{L}_m} = \varphi^m
 \]
@@
 \]
-Then $\cs{K}_\psi$ is the promised Weil sheaf complex.
+Then $\cs{K}$ is the promised Weil sheaf complex.
 
@@
 \labitem{Y0}{Y0} a sequence of compact groups $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$;
-\labitem{Y1}{Y1} a continuous representation $\rho^0$ of $C^0$;
-\labitem{Y2}{Y2} a quasicharacter $\varphi^i : C^i \to \CC^\times$, for $i=0, \ldots d$.
+\labitem{Y1}{Y1} a continuous representation $\rho_0$ of $C^0$;
+\labitem{Y2}{Y2} quasicharacters $\varphi^i : C^i \to \CC^\times$, for $i=0, \ldots d$.
 \end{enumerate}
-The groups $C^i$ here are the groups $\,^\circ K^i$ in \cite{yu:01a}; the representation $\rho^0$ here is the representation $\pi_0\vert_{\,^\circ K^0}$ in \cite{yu:01a}; the quasicharacters $\varphi^i$ here are the quasicharacters $\phi_i\vert_{\,^\circ K^i}$ in \cite{yu:01a}.
-%
-The representation $\rho^0$ and the quasicharacters $(\varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho^d = \rho$.
-%
-
+%
+The representation $\rho_0$ and the quasicharacters $(\varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho_i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho_d = \rho$ as representations of $C^d = C$.
+%
 Since we will need some facts about this construction, we review some further detail here.
-In Table~\ref{table:notation} we explain how to convert the rest of the constructions appearing in this section into the notation of \cite{yu:01a}.
-%
+In Table~\ref{table:notation} we explain how to convert the constructions appearing in this section into the notation of \cite{yu:01a}.
+
 First, Yu introduces 
@@
 where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $Z_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$.
-In fact, the quotient $J_{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J_{i+1} \to H^{i+1}$ and an isomorphism 
+In fact, the quotient $J_{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J_{i+1} \to H_{i+1}$ and an isomorphism 
 $
-j_{i+1} : H^{i+1} \to V_{i+1}^\sharp,
+j_{i+1} : H_{i+1} \to V_{i+1}^\sharp,
 $
-where $H^{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:01a}*{}.
+where $H_{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:01a}*{}.
 %\labitem{Q3}{Q3} 
@@
 $
-such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H^{i+1}$ in the sense of \cite{yu:01a}.
+such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H_{i+1}$ in the sense of \cite{yu:01a}.
 %
@@
 
-We can now recall how Yu uses all this to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ and thus the type $(C,\rho) = (C^d,\rho^d\otimes \varphi^d)$.
-The representations $\rho^i$ are defined recursively. 
-For the base case $i=0$, the representation $\rho^0$ is just $\rho_0$; see \ref{Y1} above.
+We can now recall how Yu uses all this to construct representations $\rho_i$ of $C^i$, for $i=1, \ldots, d$ and thus the type $(C,\rho) = (C^d,\rho_d\otimes \varphi^d)$.
+The representations $\rho_i$ are defined recursively. 
+For the base case $i=0$, the representation $\rho_0$ is just $\rho_0$; see \ref{Y1} above.
 Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
 Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $C^i \ltimes J_{i+1}$.
-Write $\inf(\rho^i \otimes \varphi^i)$ for the representation of $C^i \ltimes J_{i+1}$ obtained by pulling back $\rho^i$ along $C^i \ltimes J_{i+1} \to C^i$. 
+Write $\inf(\rho_i \otimes \varphi^i)$ for the representation of $C^i \ltimes J_{i+1}$ obtained by pulling back $\rho_i$ along $C^i \ltimes J_{i+1} \to C^i$. 
 Consider the representation
 \begin{equation}\label{eq:tensor}
-\rho_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\rho^i \otimes \varphi^i)
+\rho_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\rho_i \otimes \varphi^i)
 \end{equation}
@@
 %\begin{equation}\label{eq:tilderho}
-%\trace({\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\rho^i)(p_i(y))\ \varphi^i(p_i(y))
+%\trace({\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\rho_i)(p_i(y))\ \varphi^i(p_i(y))
 %\end{equation}
@@
 
-This defines the representation $\rho^{i+1}$ of $C^{i+1}$. 
-This completes the recursive definition and thus determines $\rho^d$. 
-Now set $\rho \ceq \rho^d\otimes \varphi^d$. 
+This defines the representation $\rho_{i+1}$ of $C^{i+1}$. 
+This completes the recursive definition and thus determines $\rho_d$. 
+Now set $\rho \ceq \rho_d\otimes \varphi^d$. 
 This is the representation of $C^d = C$ determining the Yu type $(C,\rho)$.
-%The character of $\rho^d$ on $C^d = C = J_0 \cdots J_d$ satisfies
+%The character of $\rho_d$ on $C^d = C = J_0 \cdots J_d$ satisfies
 %\[
-%\trace(\rho)(k_0 \cdots k_d) = \rho^0(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
+%\trace(\rho)(k_0 \cdots k_d) = \rho_0(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
 %\]
@@
 \begin{tabular}{c|l}
-$C^0$ & $\,^\circ K^0 = G^i(F)_y$, \cite{yu:01a}*{\S 15} \\
-$\rho^0$ & $\,^\circ \rho_0$ \cite{yu:01a}*{\S 15} \\
-$C^{i+1}$ & $\,^\circ K^i = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, l\dots, s_{i})}$, \cite{yu:01a}*{\S 15} \\
-$\rho^{i+1}$ & $\,^\circ \rho_{i+1}$, \cite{yu:01a}*{\S 15} \\
+$C^0$ & $C^0 = \,^\circ K^0 = G^0(F)_y$, \cite{yu:01a}*{\S 15} \\
+$\rho_0$ & $\,^\circ \rho^0$ \cite{yu:01a}*{\S 15} \\
+$C^{i+1}$ & $C^{i+1} =  \,^\circ K^i = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, \ldots, s_{i})}$, \cite{yu:01a}*{\S 15} \\
+$\rho_{i+1}$ & $\,^\circ \rho^{i+1}$, \cite{yu:01a}*{\S 15} \\
 $\varphi^i$ & $\phi_i\vert_{\,^\circ K^i }$ \\
@@
 $W_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi}_i\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
-$H^{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi_i}\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
+%$H^{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi_i}\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
 $Z_{i+1}$ & $C$, \cite{yu:01a}*{\S 11} \\
 $(f_{j+1}, j_{i+1})$ & $(f,j)$ \cite{yu:01a}*{\S 11} \\
-$\langle\ ,\ \rangle_{i+1}$ & $\langle\ ,\ \rangle$, \cite{yu:01a}*{\S 11} \\
+$\langle\ ,\ \rangle_{i+1}$ & $\langle\ ,\ \rangle$, \cite{yu:01a}*{\S 11} 
 \end{tabular}
@@
 These results suggest that algebraic geometry and group schemes should play an
-important role in the representation theory of $p$-adic groups.} \cite{yu:03a}
+important role in the representation theory of $p$-adic groups.} %\cite{yu:03a}
 \end{quotation}
@@
 Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
-The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $V^{i+1}_\Fq$, where $V^{i+1}_\Fq$, appears as a quotient $J_{i+1} \to V^{i+1}$ of algebraic groups over $\Fq$.
+The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $V^{i+1}$ over $\Fq$, where $V^{i+1}$, appears as a quotient $\underline{J}^{i+1}_{\Fq} \to V^{i+1}$ of algebraic groups over $\Fq$.
 Then the quotient $J_{i+1} \to V_{i+1}$ is realized as the composition
 \[
-\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to V^{i+1}_\Fq(\Fq) = V_{i+1}.
-\]
-Likewise, the Heisenberg $p$-group $H^{i+1}$, appearing in \ref{ssec:review}, may be realized as a quotient of algebraic groups, and $J_{i+1}\to H^{i+1}$ as the composition 
-\[
-\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H^{i+1}.
+\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to V^{i+1}(\Fq) = V_{i+1}.
+\]
+Likewise, the Heisenberg $p$-group $H_{i+1}$, appearing in \ref{ssec:review}, may be realized as a quotient of algebraic groups, and $\underline{J}^{i+1}_{\Fq} \to H^{i+1}$ as the composition 
+\[
+\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H_{i+1}.
 \]
@@
 %Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{R}(\underline{G}^0) \to \Gr^{R}_{m}(\underline{G}^0)$.
-%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G}^0)$ from which the character of $\rho^0$ may be recovered.
+%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G}^0)$ from which the character of $\rho_0$ may be recovered.
 
@@
 
-We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{R}_m(\underline{G}^{i})$, for $i=0,\ldots ,d$, recursively, following the construction of the representations $\rho^i$, as reviewed in Section~\ref{ssec:review}.
+We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{R}_m(\underline{G}^{i})$, for $i=0,\ldots ,d$, recursively, following the construction of the representations $\rho_i$, as reviewed in Section~\ref{ssec:review}.
 First, set $\cs{A}_m^i = A_m^0$ and note that 
@@
 \begin{tikzcd}
-G^0(\Fq) \arrow{rr}{\trace(\rho^0)} \arrow{rd} && \EE\\
+G^0(\Fq) \arrow{rr}{\trace(\rho_0)} \arrow{rd} && \EE\\
 & G^0_m(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m^0}} & 
@@
 \begin{tikzcd}
-G^i(\Fq) \arrow{rr}{\trace(\rho^i)} \arrow{rd} && \EE\\
+G^i(\Fq) \arrow{rr}{\trace(\rho_i)} \arrow{rd} && \EE\\
 & G_m^i(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m^i}} & 
@@
 \begin{tikzcd}
-G^{i+1}(\Fq) \arrow{rr}{\trace(\rho^{i+1})} \arrow{rd} && \EE\\
+G^{i+1}(\Fq) \arrow{rr}{\trace(\rho_{i+1})} \arrow{rd} && \EE\\
 & G_m^{i+1}(\Fq)\arrow{ru}[swap]{{\trFrob{\cs{A}_m^{i+1}}} } & 

### 2016-03-30 CCSprepreprint.tex
Made a version to send to Loren.

--- 2016-03-29 followup.tex
@@
 
-\title[Commutative Character Sheaves]{Geometrization of characters of smooth group schemes}
-%\title[Commutative Character Sheaves]{The Dictionary for characters of smooth group schemes}
+\title[Commutative Character Sheaves]{The dictionary for characters of smooth group schemes}
 \author{Clifton Cunningham}
@@
 In this way, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:
-virtual Weil perverse sheaves on smooth group schemes over finite fields.
+virtual Weil perverse sheaves on group schemes over finite fields.
 
@@
 
-We thank Loren Spice for explaining Yu's theory of types to us.
+We are grateful to Loren Spice for explaining Yu's theory of types to us.
+%We also thank Masoud Kamgarpour for helpful conversations.
 
@@
 
+All supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}, as established in \cite{kim:07a}.
+The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
+Let us refer to the types arising in this manner as {\it Yu types}.
+In this section we offer an application of Theorem~\ref{thm:geo}, by showing that Yu types are geometrizable, subject to a very mild hypothesis.
+The proof that statement, made precise in Theorem~\ref{thm:geotypes}, requires: the geometrization of the character of the Heisenberg-Weil representation over finite fields in Section~\ref{ssec:Jacobi}; a review of some basic properties of Yu types in Section~\ref{ssec:review}; a review of some facts from Yu's notes on integral models in Section~\ref{ssec:models}; and the geometrization of characters of representations of reductive groups over finite fields with cyclic geometric component groups, using Lusztig's character sheaves on these groups.
+These pieces are assembled in Section~\ref{ssec:geotypes}.
+
 \subsection{Quasicharacters of smooth group schemes over certain henselian traits}
@@
 \underline{G}(S) \arrow{rr}{\varphi} \arrow{rd} && \EEx\\
-& \underline{G}(R/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi^m} 
+& \underline{G}(R/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi_m} 
 \end{tikzcd}
@@
 Then $G_m$ is a smooth group scheme over $\Fq$ and $G_m(\Fq) = \underline{G}(R_m)$, canonically.
-Using Theorem~\ref{thm:geo}, let $\cs{L}_m$ be a geometrization of the character $\varphi^m: G_m \to \EEx$; so
-\[
-\trFrob{\cs{L}_m} = \varphi^m
+Using Theorem~\ref{thm:geo}, let $\cs{L}_m$ be a geometrization of the character $\varphi_m: G_m \to \EEx$; so
+\[
+\trFrob{\cs{L}_m} = \varphi_m
 \]
@@
 
-As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
-The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
-Let us refer to the types arising in this manner as {\it Yu types}.
-%In this section we show that every Yu type is geometrizable.
-% in a sense which will be made clear below.
-%
-A Yu type is then a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$, directly from the following information, derived from a Yu datum:
+A Yu type is a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$, directly from the following information, derived from a Yu datum:
 \begin{enumerate}
@@
 %
-The representation $\rho_0$ and the quasicharacters $(\varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho_i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho_d = \rho$ as representations of $C^d = C$.
-%
-Since we will need some facts about this construction, we review some further detail here.
+The representation $\rho_0$ and the quasicharacters $(\varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho_i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho_d \otimes \varphi^d = \rho$ as representations of $C^d = C$.
+%
+Since we will need some facts about this construction in the proof of Theorem~\ref{thm:geotypes}, we review some further detail here.
 In Table~\ref{table:notation} we explain how to convert the constructions appearing in this section into the notation of \cite{yu:01a}.
@@
 %
-Next, Yu uses this to define a group homomorphism (in fact, a quotient) 
+Next, Yu defines a group homomorphism (in fact, a quotient) 
 $
@@
 where $V_{i+1}$ is a finite abelian group, the latter also given the structure of a $\Fq$-vector space.
-The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to Z_{i+1}$, where $Z_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : Z_{i+1} \to \EEx$.
+The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to Z_{i+1}$, where $Z_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : Z_{i+1} \to \CC^\times$.
 %\labitem{Q2}{Q2} 
@@
 $
-where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $Z_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$.
-In fact, the quotient $J_{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J_{i+1} \to H_{i+1}$ and an isomorphism 
-$
-j_{i+1} : H_{i+1} \to V_{i+1}^\sharp,
-$
-where $H_{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:01a}*{}.
+where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $Z_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$, as in Section~\ref{ssec:Jacobi}.
+In fact, the quotient $J_{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J_{i+1} \to H_{i+1}$ and an isomorphism $j_{i+1} : H_{i+1} \to V_{i+1}^\sharp$, where $H_{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:01a}*{}.
 %\labitem{Q3}{Q3} 
 %\item
-Finally, Yu constructs 
-$
-f_{i+1} : C^i \to \Sp(V_{i+1}),
-$
-such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H_{i+1}$ in the sense of \cite{yu:01a}.
+Finally, Yu constructs a group homomorphism $f_{i+1} : C^i \to \Sp(V_{i+1})$ such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H_{i+1}$ in the sense of \cite{yu:01a}.
 %
@@
 For the base case $i=0$, the representation $\rho_0$ is just $\rho_0$; see \ref{Y1} above.
+Now fix $i$.
 Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
@@
 By \cite{yu:01a}*{}, the representation $\rho_{i+1}$ of $C^i \ltimes J_{i+1}$ is trivial on $C^{i}\cap J_{i+1}$ so $\rho_{i+1}$ descends to $C^{i+1}$. 
-
+%
 This defines the representation $\rho_{i+1}$ of $C^{i+1}$.
-This completes the recursive definition and thus determines $\rho_d$. 
+This completes the recursive definition of $\rho_d$. 
 Now set $\rho \ceq \rho_d\otimes \varphi^d$. 
@@
 \begin{tabular}{c|l}
-$C^0$ & $C^0 = \,^\circ K^0 = G^0(F)_y$, \cite{yu:01a}*{\S 15} \\
+$C^0$ & $\,^\circ K^0 = G^0(F)_y$, \cite{yu:01a}*{\S 15} \\
 $\rho_0$ & $\,^\circ \rho^0$ \cite{yu:01a}*{\S 15} \\
-$C^{i+1}$ & $C^{i+1} =  \,^\circ K^i = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, \ldots, s_{i})}$, \cite{yu:01a}*{\S 15} \\
+$C^{i+1}$ & $\,^\circ K^i = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, \ldots, s_{i})}$, \cite{yu:01a}*{\S 15} \\
 $\rho_{i+1}$ & $\,^\circ \rho^{i+1}$, \cite{yu:01a}*{\S 15} \\
@@
 
-Regarding the construction of the type $(C,\rho)$, the paper \cite{yu:03a} concludes with the following provocative observation.
+Regarding the construction of the type $(C,\rho)$, the paper \cite{yu:03a} concludes with the following observation.
 \begin{quotation}
@@
 \end{quotation}
-In this section we explain what this observation is saying, following \cite{yu:03a}.
+In this section we explain the first sentence; in Section~\ref{ssec:geotypes} we follow the suggestion in the second sentence.
 
@@
 Finally, we come to the main result of Section~\ref{sec:types}.
-
+%
 Since Yu's theory refers to complex representations, and since our geometrization uses $\ell$-adic sheaves, we grit our teeth and fix an isomorphism $\CC \approx \EE$.
 
-\begin{proposition}\label{prop:geotypes}
+\begin{theorem}\label{thm:geotypes}
 Let $(C,\rho)$ be a Yu type, constructed as in Section~\ref{ssec:review}.
-Let $G^i = \Gr_{R}(\underline{G}^i)$ be the Greenberg transform of the smooth group scheme $\underline{G}^i$ appearing in Section~\ref{ssec:models}.
+Let $G^0 = \Gr_{R}(\underline{G}^0)$ be the Greenberg transform of the smooth group scheme $\underline{G}^0$ appearing in Section~\ref{ssec:models}.
 Assume $\pi_0(\underline{G}^0)_\Fq^\reductive)$ is cyclic.
-Then there is a virtual Weil sheaf complex $\cs{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
-\end{proposition}
+Then there is a virtual Weil sheaf complex $\cs{A}$ on $G = \Gr_{R}(\underline{G})$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
+\end{theorem}
 
 \begin{proof}
+For every $i=0, \ldots ,d$, set $G^i = \Gr_{R}(\underline{G}^i)$.
 Recall that $G^i(\Fq) = \underline{G}^i(R) = C^i$, canonically.
@@
 \] 
-for each $i=0, \ldots d$.
+for all $i=0, \ldots d$.
 Set $G_m^i = \Gr_m^{R}(\underline{G}^i)$.
@@
 
-\bibliography{bibliography/Biblio}
+%\bibliography{bibliography/Biblio}
+% \bib, bibdiv, biblist are defined by the amsrefs package.
+\begin{bibdiv}
+\begin{biblist}
+
+\bib{berndt-schmidt:98a}{book}{
+      author={Berndt, Rolf},
+      author={Schmidt, Ralf},
+       title={{Elements of the representation theory of the Jacobi group}},
+   publisher={{Birkh\"auser/Springer Basel AG}},
+     address={Basel, Switzerland},
+        date={2011},
+}
+
+\bib{bertapelle-gonzales:Greenberg}{unpublished}{
+      author={Bertapelle, Alessandra},
+      author={{Gonz\'ales-Avil\'es}, Cristian~D.},
+       title={{The Greenberg functor revisited}},
+        date={2014},
+         url={http://arxiv.org/abs/1311.0051},
+        note={\href{http://arxiv.org/abs/1311.0051}{arXiv:1311.0051
+  [math.NT]}},
+}
+
+\bib{bushnell-kutzko:98a}{article}{
+      author={Bushnell, Colin},
+      author={Kutzko, Phil},
+       title={{Smooth representations of reductive $p$-adic groups: structure
+  theory via types}},
+        date={1998},
+     journal={Proc. London Math. Soc.},
+      volume={77},
+      number={3},
+       pages={{582\ndash 634}},
+}
+
+\bib{cunningham-roe:13a}{article}{
+      author={Cunningham, Clifton},
+      author={Roe, David},
+       title={From the function-sheaf dictionary to quasicharacters of $p$-adic
+  tori},
+  journal={Journal of the Institute of Mathematics of Jussieu},
+        year = {2016},
+issn = {1475-3030},
+pages = {1--37},
+numpages = {37},
+doi = {10.1017/S1474748015000286},
+URL = {http://journals.cambridge.org/article_S1474748015000286},
+}
+
+\bib{demazure:SGA3-VIA}{inproceedings}{
+      author={Gabriel, Pierre},
+       title={{Expos\'e VI$_\mathrm{A}$: G\'en\'eralit\'es sur les groupes
+  alg\'ebriques}},
+        date={1970},
+   booktitle={{Sch\'emas en groupes I: Proprietes generales des schemas en
+  groupes}},
+      editor={Demazure, Michel},
+      editor={Grothendieck, Alexander},
+      series={Lecture Notes in Math},
+      volume={151},
+   publisher={Springer-Verlag},
+     address={Berlin},
+}
+
+\bib{EGAIV4}{article}{
+      author={Grothendieck, Alexandre},
+       title={{\'El\'ements de g\'eom\'etrie alg\'ebrique IV. \'Etude locale
+  des sch\'emas et des morphismes de sch\'emas. IV}},
+        date={1967},
+     journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
+      number={32},
+}
+
+\bib{gurevich-hadani:07a}{article}{
+   author={Gurevich, Shamgar},
+   author={Hadani, Ronny},
+   title={The geometric Weil representation},
+   journal={Selecta Math. (N.S.)},
+   volume={13},
+   date={2007},
+   number={3},
+   pages={465--481},
+}
+
+\bib{gurevich-hadani:11a}{unpublished}{
+   author={Gurevich, Shamgar},
+   author={Hadani, Ronny},
+   title={The categorical Weil representation},
+	date={2011},
+        note={\href{http://arxiv.org/abs/1108.0351}{arXiv:1108.0351 [math.RT]}}
+}
+
+\bib{howe:73a}{article}{
+   author={Howe, Roger E.},
+   title={On the character of Weil's representation},
+   journal={Trans. Amer. Math. Soc.},
+   volume={177},
+   date={1973},
+   pages={287--298},
+}
+
+\bib{kamgarpour:09a}{article}{
+      author={Kamgarpour, Masoud},
+       title={{Stacky abelianization of algebraic groups}},
+        date={2009},
+     journal={{Transform. Groups}},
+      volume={14},
+      number={4},
+       pages={825\ndash 846},
+}
+
+\bib{kim:07a}{article}{
+      author={Kim, Ju-Lee},
+       title={Supercuspidal representations: an exhaustion theorem},
+        date={2007},
+     journal={J. Amer. Math. Soc.},
+      volume={20},
+      number={2},
+       pages={273\ndash 320},
+}
+
+\bib{lusztig:85a}{article}{
+      author={Lusztig, George},
+       title={{Character sheaves I}},
+        date={1985},
+     journal={Advances in Math.},
+      volume={56},
+       pages={193\ndash 237},
+}
+
+\bib{lusztig:disconnected1}{article}{
+      author={Lusztig, George},
+       title={{Character sheaves on disconnected groups I}},
+        date={2003},
+     journal={Representation Theory},
+      volume={7},
+       pages={374\ndash 403},
+}
+
+\bib{Vistoli:notes}{unpublished}{
+      author={Vistoli, Angelo},
+       title={{Notes on Grothendieck topologies, fibered categories and descent
+  theory}},
+        date={2007},
+        note={\href{http://arxiv.org/abs/math/0412512}{arXiv:0412512
+  [math.AG]}},
+}
+
+\bib{yu:01a}{article}{
+      author={Yu, Jiu-Kang},
+       title={Construction of tame supercuspidal representations},
+        date={2001},
+     journal={J. Amer. Math. Soc.},
+      volume={14},
+      number={3},
+       pages={{579\ndash 622}},
+}
+
+\bib{yu:03a}{unpublished}{
+      author={Yu, Jiu-Kang},
+       title={{Smooth models associated to concave functions in Bruhat-Tits
+  theory}},
+        date={2003},
+        note={Preprint},
+}
+
+\end{biblist}
+\end{bibdiv}
 

### 2016-03-30 followup.tex
I didn't like `geometrization' title. Trying something else now. What do you think?
Brought followup.tex up to date with CCSprepreprint.tex. I won't touch the later until we hear back from Loren.

@@
 
-We thank Loren Spice for explaining Yu's theory of types to us.
+We are extremely grateful to Loren Spice for explaining Yu's theory of types to us.
+We also thank Masoud Kamgarpour for helpful conversations.
 
@@
 \bibliography{bibliography/Biblio}
+% \bib, bibdiv, biblist are defined by the amsrefs package.
+\iffalse
+
+\begin{bibdiv}
+\begin{biblist}
+
+\bib{berndt-schmidt:98a}{book}{
+      author={Berndt, Rolf},
+      author={Schmidt, Ralf},
+       title={{Elements of the representation theory of the Jacobi group}},
+   publisher={{Birkh\"auser/Springer Basel AG}},
+     address={Basel, Switzerland},
+        date={2011},
+}
+
+\bib{bertapelle-gonzales:Greenberg}{unpublished}{
+      author={Bertapelle, Alessandra},
+      author={{Gonz\'ales-Avil\'es}, Cristian~D.},
+       title={{The Greenberg functor revisited}},
+        date={2014},
+         url={http://arxiv.org/abs/1311.0051},
+        note={\href{http://arxiv.org/abs/1311.0051}{arXiv:1311.0051
+  [math.NT]}},
+}
+
+\bib{bushnell-kutzko:98a}{article}{
+      author={Bushnell, Colin},
+      author={Kutzko, Phil},
+       title={{Smooth representations of reductive $p$-adic groups: structure
+  theory via types}},
+        date={1998},
+     journal={Proc. London Math. Soc.},
+      volume={77},
+      number={3},
+       pages={{582\ndash 634}},
+}
+
+\bib{cunningham-roe:13a}{article}{
+      author={Cunningham, Clifton},
+      author={Roe, David},
+       title={From the function-sheaf dictionary to quasicharacters of $p$-adic
+  tori},
+  journal={Journal of the Institute of Mathematics of Jussieu},
+        year = {2016},
+issn = {1475-3030},
+pages = {1--37},
+numpages = {37},
+doi = {10.1017/S1474748015000286},
+URL = {http://journals.cambridge.org/article_S1474748015000286},
+}
+
+\bib{demazure:SGA3-VIA}{inproceedings}{
+      author={Gabriel, Pierre},
+       title={{Expos\'e VI$_\mathrm{A}$: G\'en\'eralit\'es sur les groupes
+  alg\'ebriques}},
+        date={1970},
+   booktitle={{Sch\'emas en groupes I: Proprietes generales des schemas en
+  groupes}},
+      editor={Demazure, Michel},
+      editor={Grothendieck, Alexander},
+      series={Lecture Notes in Math},
+      volume={151},
+   publisher={Springer-Verlag},
+     address={Berlin},
+}
+
+\bib{EGAIV4}{article}{
+      author={Grothendieck, Alexandre},
+       title={{\'El\'ements de g\'eom\'etrie alg\'ebrique IV. \'Etude locale
+  des sch\'emas et des morphismes de sch\'emas. IV}},
+        date={1967},
+     journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
+      number={32},
+}
+
+\bib{gurevich-hadani:07a}{article}{
+   author={Gurevich, Shamgar},
+   author={Hadani, Ronny},
+   title={The geometric Weil representation},
+   journal={Selecta Math. (N.S.)},
+   volume={13},
+   date={2007},
+   number={3},
+   pages={465--481},
+}
+
+\bib{gurevich-hadani:11a}{unpublished}{
+   author={Gurevich, Shamgar},
+   author={Hadani, Ronny},
+   title={The categorical Weil representation},
+	date={2011},
+        note={\href{http://arxiv.org/abs/1108.0351}{arXiv:1108.0351 [math.RT]}}
+}
+
+\bib{howe:73a}{article}{
+   author={Howe, Roger E.},
+   title={On the character of Weil's representation},
+   journal={Trans. Amer. Math. Soc.},
+   volume={177},
+   date={1973},
+   pages={287--298},
+}
+
+\bib{kamgarpour:09a}{article}{
+      author={Kamgarpour, Masoud},
+       title={{Stacky abelianization of algebraic groups}},
+        date={2009},
+     journal={{Transform. Groups}},
+      volume={14},
+      number={4},
+       pages={825\ndash 846},
+}
+
+\bib{kim:07a}{article}{
+      author={Kim, Ju-Lee},
+       title={Supercuspidal representations: an exhaustion theorem},
+        date={2007},
+     journal={J. Amer. Math. Soc.},
+      volume={20},
+      number={2},
+       pages={273\ndash 320},
+}
+
+\bib{lusztig:85a}{article}{
+      author={Lusztig, George},
+       title={{Character sheaves I}},
+        date={1985},
+     journal={Advances in Math.},
+      volume={56},
+       pages={193\ndash 237},
+}
+
+\bib{lusztig:disconnected1}{article}{
+      author={Lusztig, George},
+       title={{Character sheaves on disconnected groups I}},
+        date={2003},
+     journal={Representation Theory},
+      volume={7},
+       pages={374\ndash 403},
+}
+
+\bib{Vistoli:notes}{unpublished}{
+      author={Vistoli, Angelo},
+       title={{Notes on Grothendieck topologies, fibered categories and descent
+  theory}},
+        date={2007},
+        note={\href{http://arxiv.org/abs/math/0412512}{arXiv:0412512
+  [math.AG]}},
+}
+
+\bib{yu:01a}{article}{
+      author={Yu, Jiu-Kang},
+       title={Construction of tame supercuspidal representations},
+        date={2001},
+     journal={J. Amer. Math. Soc.},
+      volume={14},
+      number={3},
+       pages={{579\ndash 622}},
+}
+
+\bib{yu:03a}{unpublished}{
+      author={Yu, Jiu-Kang},
+       title={{Smooth models associated to concave functions in Bruhat-Tits
+  theory}},
+        date={2003},
+        note={Preprint},
+}
+
+\end{biblist}
+\end{bibdiv}
+\fi
 

### 2016-03-30 followup.tex
Fixed a minor problem with the geometric Weil representation, and a few typos.

@@
 In this section we offer an application of Theorem~\ref{thm:geo}, by showing that Yu types are geometrizable, subject to a very mild hypothesis.
-The proof that statement, made precise in Theorem~\ref{thm:geotypes}, requires: the geometrization of the character of the Heisenberg-Weil representation over finite fields in Section~\ref{ssec:Jacobi}; a review of some basic properties of Yu types in Section~\ref{ssec:review}; a review of some facts from Yu's notes on integral models in Section~\ref{ssec:models}; and the geometrization of characters of representations of reductive groups over finite fields with cyclic geometric component groups, using Lusztig's character sheaves on these groups.
+The proof of that statement, made precise in Theorem~\ref{thm:geotypes}, requires: the geometrization of the character of the Heisenberg-Weil representation over finite fields (Section~\ref{ssec:Jacobi}); a review of some basic properties of Yu types (Section~\ref{ssec:review}); a review of some facts from Yu's notes on smooth integral models (Section~\ref{ssec:models}); and the geometrization of characters of representations of reductive groups over finite fields with cyclic geometric component groups, using Lusztig's character sheaves on these groups.
 These pieces are assembled in Section~\ref{ssec:geotypes}.
@@
 
-It is one of the main results of \cite{gurevich-hadani:07a} (see also \cite{gurevich-hadani:11a}*{Thm. 4.5}) that there is a Weil sheaf complex $\cs{K}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
+It is one of the main results of \cite{gurevich-hadani:07a} (see also \cite{gurevich-hadani:11a}*{Thm. 4.5}) that there is a Weil sheaf complex $\cs{K}_\psi$ on $\Sp(V)\ltimes V^\sharp$ such that 
 \begin{equation}
@@
  where $\gamma_\psi$ is the Gauss sum for $\psi$ and $\sigma : \Fq^\times \to \EE^\times$ is the quadratic character of $\Fq^\times$.
-By a simple adaptation of what in \cite{gurevich-hadani:07a}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}_0$ (in fact, a Weil local system) on $S_0 \times V^\sharp$ such that
-\[
-\trFrob{\cs{K}_0[\dim V](\frac{\dim V}{2})} = \trace(W_\psi)\vert_{S_0\times V^\sharp},
-\]
-where $\cs{K}_0[\dim V](\frac{\dim V}{2})$ is the Tate twist of the shift of $\cs{K}_0$.
-%
-Next, one forms $\cs{K}_\psi \ceq j_{!*} \cs{K}_0$, the perverse extension of $\cs{K}_0$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$; recall that $S_0$ is Zariski dense in $\Sp(V)$.
+By a simple adaptation of what in \cite{gurevich-hadani:07a}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}$ (in fact, a Weil local system) on $S_0 \times V^\sharp$ such that
+\[
+\trFrob{\cs{K}(\frac{\dim V}{2})} = \trace(W_\psi)\vert_{S_0\times V^\sharp},
+\]
+where $\cs{K}(\frac{\dim V}{2})$ is the Tate twist of $\cs{K}$.
+%
+Next, one forms $\cs{K}_\psi \ceq j_{!*} \cs{K}$, the perverse extension of $\cs{K}$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$; recall that $S_0$ is Zariski dense in $\Sp(V)$.
 It follows from \cite{gurevich-hadani:07a} that 
 \[
-\trFrob{\cs{K}} = \trace(W_\psi).
-\]
-Then $\cs{K}$ is the promised Weil sheaf complex.
+\trFrob{\cs{K}_\psi} = \trace(W_\psi).
+\]
+Then $\cs{K}_\psi$ is the promised Weil sheaf complex.
 
@@
 
-A Yu type is a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$, directly from the following information, derived from a Yu datum:
+A Yu type is a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$,  olnstructed from the following information, derived from a Yu datum:
 \begin{enumerate}
@@
 $\rho_0$ & $\,^\circ \rho^0$ \cite{yu:01a}*{\S 15} \\
-$C^{i+1}$ & $\,^\circ K^i = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, \ldots, s_{i})}$, \cite{yu:01a}*{\S 15} \\
+$C^{i+1}$ & $\,^\circ K^{i+1} = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, \ldots, s_{i})}$, \cite{yu:01a}*{\S 15} \\
 $\rho_{i+1}$ & $\,^\circ \rho^{i+1}$, \cite{yu:01a}*{\S 15} \\
@@
 Consider the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ and the Heisenberg-Weil representation $W_{i+1}$ appearing in Section~\ref{ssec:models}.
-Let $\cs{K}_{i+1}$ be the Weil sheaf on the Jacobi group, recalled in Section~\ref{ssec:Jacobi}, such that
-\[
-\trFrob{\cs{K}_{i+1}} = \trace(W_{i+1}).
+Let $\cs{K}^{i+1}$ be the Weil sheaf on the Jacobi group, recalled in Section~\ref{ssec:Jacobi}, such that
+\[
+\trFrob{\cs{K}^{i+1}} = \trace(W_{i+1}).
 \]
@@
 % \bib, bibdiv, biblist are defined by the amsrefs package.
-\iffalse
+%\iffalse
 
@@
 \end{bibdiv}
-\fi
+%\fi
 

### 2016-03-30 followup.tex
Fixed a conflict :-(

@@
 
-A Yu type is a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$,  olnstructed from the following information, derived from a Yu datum:
+A Yu type is a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$, constructed from the following information, derived from a Yu datum:
 \begin{enumerate}
@@
 
-\bibliography{bibliography/Biblio}
+%\bibliography{bibliography/Biblio}
 % \bib, bibdiv, biblist are defined by the amsrefs package.

### 2016-03-30 followup.tex
Fixed a small notational problem regarding the geometric Weil representation.

@@
  where $\gamma_\psi$ is the Gauss sum for $\psi$ and $\sigma : \Fq^\times \to \EE^\times$ is the quadratic character of $\Fq^\times$.
-By a simple adaptation of what in \cite{gurevich-hadani:07a}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}$ (in fact, a Weil local system) on $S_0 \times V^\sharp$ such that
-\[
-\trFrob{\cs{K}(\frac{\dim V}{2})} = \trace(W_\psi)\vert_{S_0\times V^\sharp},
-\]
-where $\cs{K}(\frac{\dim V}{2})$ is the Tate twist of $\cs{K}$.
-%
-Next, one forms $\cs{K}_\psi \ceq j_{!*} \cs{K}$, the perverse extension of $\cs{K}$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$; recall that $S_0$ is Zariski dense in $\Sp(V)$.
+By a simple adaptation of what in \cite{gurevich-hadani:07a}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}_0$ (in fact, a Weil local system) on $S_0 \times V^\sharp$ such that
+\[
+\trFrob{\cs{K}_0(\frac{\dim V}{2})} = \trace(W_\psi)\vert_{S_0\times V^\sharp},
+\]
+where $\cs{K}_0(\frac{\dim V}{2})$ is the Tate twist of $\cs{K}$.
+%
+Next, one forms $\cs{K}_\psi \ceq j_{!*} \cs{K}_0[\dim V]$, the perverse extension of $\cs{K}_0 [\dim V]$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$; recall that $S_0$ is Zariski dense in $\Sp(V)$.
 It follows from \cite{gurevich-hadani:07a} that 

### 2016-04-06 followup.tex
Small changes after checking with Loren.
Small style changes and typo fixes

--- 2016-03-30 followup.tex
@@
 
-\title[Commutative Character Sheaves]{The dictionary for characters of smooth group schemes}
+\title[Commutative Character Sheaves]{The Dictionary for characters of smooth group schemes}
 \author{Clifton Cunningham}
@@
 
-The first aim of this paper is to repair this defect in the function-sheaf dictionary for characters of smooth commutative group schemes $G$ by describing a full subcategory $\CCS(G)$ of $\CS(G)$ so that $\TrFrob{G}$ restricts to an isomorphism $\CCSiso{G} \to G(k)^*$.
+The first aim of this paper is to repair this defect in the function-sheaf dictionary by describing a full subcategory $\CCS(G)$ of $\CS(G)$ so that $\TrFrob{G}$ restricts to an isomorphism $\CCSiso{G} \to G(k)^*$.
 We refer to the resulting objects as \emph{commutative character sheaves}, since the passage from $\CS(G)$ to $\CCS(G)$ involves a condition that exchanges the inputs to the multiplication morphism on $G$ (see Definition \ref{def:CCScom}).
@@
 
-Next, we broaden our scope further to encompass smooth group schemes $G$ over $\Fq$ that are not necessarily commutative.
-In this paper, we do not consider Lusztig's geometrization of characters of representations of connected, reductive groups $G(k)$
-using character sheaves \cite{lusztig:85a}*{Def.~2.10}, but focus on the case of characters
-$G(k)^*$ (that is, group homomorphisms from $G(k)$ to $\EEx$), assuming only that $G$ is smooth, allowing for the possibility that $G$ is not connected and not reductive.
+Next, we broaden our scope further to encompass smooth group schemes $G$ that are not necessarily commutative.
+In this paper, we do not consider Lusztig's geometrization of arbitrary characters of connected, reductive groups $G(k)$
+using character sheaves \cite{lusztig:85a}*{Def.~2.10}.  Instead, we focus on the group of $1$-dimensional characters
+$G(k)^*$, assuming that $G$ is smooth, but not that it is connected or reductive.
 The category $\CS(G)$ has a straightforward generalization to this case, but again
-there are more character sheaves than there are characters, as pointed out by Kamgarpour \cite{kamgarpour:09a}*{(1.1)}.
+there are more linear character sheaves than there are characters, as pointed out by Kamgarpour \cite{kamgarpour:09a}*{(1.1)}.
 We define a category $\CCS(G)$ and a forgetful functor to $\CS(G)$ so that $\TrFrob{G} : \CCSiso{G} \to G\ab(k)^*$
@@
 In this way, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:
-virtual Weil perverse sheaves on group schemes over finite fields.
+virtual Weil perverse sheaves on smooth group schemes over finite fields.
 
@@
 This observation underlies the definition of commutative character sheaves for non-commutative $G$.  
-We state our main result, Theorem~\ref{thm:geo}, that pullback along the abelianization map defines an equivalence of categories $\CCS(G) \to \CCS(G\ab)$.
+We state our second main result, Theorem~\ref{thm:geo}, that pullback along the abelianization map defines an equivalence of categories $\CCS(G) \to \CCS(G\ab)$.
 In Section \ref{ssec:obmor}, we use Galois cohomology to describe the relationship between $G(k)^*$ and $G\ab(k)^*$.  
@@
 The proof of this statement is quite technical, so it must be delayed to Section~\ref{ssec:geotypes}, after reviewing types in Section~\ref{ssec:review} and models Section~\ref{ssec:models} developed by Yu, for which we must also review some facts about the Heisenberg-Weil representation and its geometrization, in Section~\ref{ssec:Jacobi}.
-
-We are extremely grateful to Loren Spice for explaining Yu's theory of types to us.
-We also thank Masoud Kamgarpour for helpful conversations.
+\todo{There are some grammatical errors in this paragraph, and I'm not 100\% sure how they should be corrected}
+
+We thank Loren Spice for explaining Yu's theory of types to us.
 
@@
 
-In this paper we use a common formalism for Weil sheaves, writing $\cs{L}$ for the pair $(\gcs{L},\phi)$ where $\gcs{L}$ is an $\ell$-adic sheaf on $\bG \ceq G\otimes_{\Fq} \bFq$ and where $\phi : \Frob{}^*\gcs{L} \to \gcs{L}$ is an isomorphism of $\ell$-adic sheaves.
+In this paper we use a common formalism for Weil sheaves, writing $\cs{L}$ for the pair $(\gcs{L},\phi)$, where $\gcs{L}$ is an $\ell$-adic sheaf on $\bG \ceq G\otimes_{\Fq} \bFq$ and where $\phi : \Frob{}^*\gcs{L} \to \gcs{L}$ is an isomorphism of $\ell$-adic sheaves.
 We also follow convention by referring to $\cs{L}$  as a Weil sheaf on $G$. 
-We will also write $\alpha : \cs{L} \to \cs{L}'$ for a morphism $\alpha : \gcs{L} \to \gcs{L}$ such that 
+If $\cs{L}$ and $\cs{L}' \ceq (\gcs{L}', \phi')$ are Weil sheaves, we write $\alpha : \cs{L} \to \cs{L}'$ for a morphism $\alpha : \gcs{L} \to \gcs{L}$ such that 
 \[
@@
 \]
-commutes, where $\cs{L}'$ refers to $(\gcs{L}',\phi')$.
-While this simplifies notation considerably, it is, unfortunately, not consistent with our earlier paper.
+commutes.  While these conventions simplify notation considerably, they are not consistent with \cite{cunningham-roe:13a}.
 
@@
 
-We consider first the case that $G$ is commutative, which will be used for general smooth $G$.
+We consider first the case that $G$ is commutative, which we will later apply to the case of general smooth $G$.
 Let $\cs{L}$ be a character sheaf on $G$.  Since $m = m \circ \theta$ in this case,
@@
 of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.  Thus every character
-sheaf on $G$ arises through the Lang isogeny; since the covering group is $G$ itself, which is commutative,
-every character sheaf on $G$ is commutative.
+sheaf on $G$ arises through the Lang isogeny; since the covering group is $G(k)$, which is commutative,
+every character sheaf on $G$ is commutative. \todo{why does this imply that the sheave is commutative in our sense?}
 \end{proof}
@@
 In order to obtain a relationship between character sheaves on $G$ and characters of $G(k)$,
-he opts to give a different definition of commutator and, in doing so, introduces a `stacky abelianization' of $G$ in order to geometrize characters of $G(\Fq)$.
- Since we has already seen the need to adapt the
+he opts to give a different definition of commutator.  Since we already need to adapt our
 notion of character sheaf, even in the commutative case, we instead add restrictions
-to the definition of commutative character sheaf and leave the definition of $G\der$ unchanged, allowing us to use the schematic abelianization of $G$ in the geometrization of characters of $G(\Fq)$; see Theorem~\ref{thm:geo}.
-
-\subsection{Main definition}\label{ssec:noncomdef}
+to the definition of commutative character sheaf and leave the definition of $G\der$ unchanged.
+
+\subsection{Definition}\label{ssec:noncomdef}
 
@@
 character sheaves whose restriction to the derived subgroup is nontrivial.
-Recall from Section~\ref{sec:defs} that we refer to objects in category $\CS(G)$, defined as in \cite{cunningham-roe:13a}*{Def.
-1.1}, as linear character sheaves  when $G$ is smooth but not necessarily commutative.
-
+The following proposition will be proven in Section \ref{ssec:proof1}.
 \begin{proposition} \label{prop:Gder_triv}
-Suppose $G$ is a smooth group scheme and $(\cs{L},\mu) \in \CS(G)$.
-Then the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $(\cs{L},\mu) \cong q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, for some $(\cs{L}\ab,\mu\ab) \in \CS(G\ab)$.
+Suppose $G$ is a smooth group scheme and $\cs{L} \in \CS(G)$ is a linear character sheaf on $G$.
+Then the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $\cs{L} \cong q^*(\cs{L}\ab)$ for some
+character sheaf $\cs{L}\ab$ on $G\ab$.
 \end{proposition}
-
-Proposition~\ref{prop:Gder_triv} will be proven in Section \ref{ssec:proof1}.
 
@@
 Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows.
-Let $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
-Then $c$ is a smooth morphism of $\Fq$ schemes.
-Set $m' = i \circ m \circ \theta$; then $j\circ c = m \circ (m \times m')$.
-Then, $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms, below.
+Let $i : G \to G$ be inversion and $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
+Both are smooth morphism of $\Fq$-schemes.
+Set $m' = i \circ m \circ \theta$; we have $j\circ c = m \circ (m \times m')$.
+Then $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms below.
 \begin{equation}
@@
 \]
-Since $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ canonically, and since $\cs{L}^\vee \iso i^*\cs{L}$, canonically, this defines the promised isomorphism
+Since $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ canonically, and since $\cs{L}^\vee \iso i^*\cs{L}$, \todo{should we write $i^*(\cs{L}^\vee) \cong \cs{L}$ instead?} canonically, this defines the promised isomorphism
 \[
@@
 \begin{definition}\label{def:CCS}
-The category $\CCS(G)$ of commutative character sheaves on $G$ is the full subcategory of $\CS'(G)$ consisting of triples $(\cs{L},\mu,\beta)$ such that the following diagram of Weil sheaves on $G \times G$ commutes,
+The category $\CCS(G)$ of commutative character sheaves on $G$ is the full subcategory of $\CS'(G)$ consisting of triples $(\cs{L},\mu,\beta)$ such that the following diagram of Weil sheaves on $G \times G$ commutes:
   \[
@@
    m^*\cs{L} \arrow{d}[swap]{\gamma} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
-   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L})
-  \end{tikzcd}
-  \]
-where $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$, above.
+   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L}).
+  \end{tikzcd}
+  \]
+Here $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ above.
 \end{definition}
@@
 Suppose $(\cs{L},\mu,\beta)$ is an object in $\CS'(G)$.
-Then $\beta : \cs{L}_1\to \EE$ is an isomorphism in $\CS(1)$, and unique by \cite{cunningham-roe:13a}*{Thm 3.9}.
+Then $\beta : \cs{L}_1\to \EE$ is an isomorphism in $\CS(1)$, which is unique by \cite{cunningham-roe:13a}*{Thm 3.9}.
 Tracing through the construction of $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ from $\beta : \cs{L}_1\to \EE$, we find 
@@
 that $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ is the canonical isomorphism coming from the equation $m = m \circ \theta$. 
-Thus, when $G$ is commutative, Definition~\ref{def:CCS} recovers Definition~\ref{def:CCScom}.
+Thus, when $G$ is commutative, Definition~\ref{def:CCS} agrees with Definition~\ref{def:CCScom}.
 The next result generalizes this observation.
@@
 
-Theorem~\ref{thm:Gab} shows that $\CCS(G)$ is a categorical solution to the problem that linear character sheaves on $G$ need not be trivial on $G\der$, as discussed at the beginning of Section~\ref{sec:noncom}; at the same time, it is the categorical solution to the problem, discussed in Section~\ref{ssec:defect}, that the dictionary between linear character sheaves on $G\ab$ and characters of $G\ab$, need not be perfect.
+Theorem~\ref{thm:Gab} shows that $\CCS(G)$ is a categorical solution to the problem that linear character sheaves on $G$ need not be trivial on $G\der$, as discussed at the beginning of Section~\ref{sec:noncom}.
+At the same time, changing $\CS(G)$ to $\CCS(G)$ resolves the lack of bijectivity in \cite{cunningham-roe:13a}*{Thm.
+3.6}.
 %
@@
 %Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
-Category $\CCS(G)$ is monoidal and 
-\[
-\CCSiso{G} \iso \Hom(G\ab(\Fq),\EEx),
-\]
-canonically.
-Every map in $\CCS(G)$ is either trivial or an isomorphism, and the automorphism group of any object in $\CCS(G)$ is $\Hom(\pi_0(G\ab)_{\Frob{}},\EEx)$, canonically.
+The category $\CCS(G)$ is monoidal and there is a canonical isomorphism $\CCSiso{G} \iso \Hom(G\ab(\Fq),\EEx)$.
+Every map in $\CCS(G)$ is either trivial or an isomorphism, and the automorphism group of any object in $\CCS(G)$ is canonically isomorphic to $\Hom(\pi_0(G\ab)_{\Frob{}},\EEx)$.
 \end{corollary}
@@
 where $\Delta_G$ denotes the image of the connecting homomorphism $G\ab(\Fq) \to \Hh^1(\Fq, G\der)$. 
-Thus, category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the following sense: for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $(\cs{L},\mu,\beta)$ in $\CCS(G)$ such that $\trFrob{\cs{L}} = \chi$.
+Thus the category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the following sense: for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $(\cs{L},\mu,\beta)$ in $\CCS(G)$ such that $\trFrob{\cs{L}} = \chi$.
 The geometrization of $\chi : G(\Fq) \to \EEx$ is not unique, but the group of isomorphism classes of possibilities are enumerated by $\Delta_G^*$.
@@
 \begin{remark}
-Note that when $\Hh^1(k,G\der) = 0$, as is the case when $G\der(\bFq)$ ``is simply connected,'' then $\CCSiso{G} \iso G(\Fq)^*$, so
+Note that when $\Hh^1(k,G\der) = 0$, as is the case when $G\der(\bFq)$ ``is simply connected,'' \todo{Can we make this more precise?} then $\CCSiso{G} \iso G(\Fq)^*$, so
 we succeed in geometrizing characters of $G(k)$ on the nose.
@@
 \end{equation}
-and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes.
+and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes. \todo{Maybe we should give a reference for this definition?}
 \begin{equation}\label{E2}
@@
 \end{align*}
-We require that the following diagram of Weil local systems on $H \times G\times G$ commutes:
+We require that the following diagram of Weil local systems on $H \times G\times G$ commutes: \todo{Something's wrong: the top left actually requires $a \circ c_2 = m \circ c_1$, which isn't true.}
 \begin{equation}\label{ECS1}
@@
 \begin{tikzcd}[column sep=40]
-\arrow{d}[swap]{a_2(\mu)} a_2^* (m^*\cs{L}) \arrow[dashed]{r} 
+\arrow{d}[swap]{a_2^*(\mu)} a_2^* (m^*\cs{L}) \arrow[dashed]{r} 
 	& \arrow{d}{p_2^*(\mu)} p_2^*(m^*\cs{L})\\
@@
 On the other hand, by Lemma~\ref{lem:beta}, $\CS'(G) \to \CS_{H}(G)$, defined by $(\cs{L},\mu,\beta)\mapsto (\cs{L},\mu, \nu)$, is an equivalence.
-
-Now, suppose $(\cs{L},\mu)\in \CS(G)$ and there is an isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ in $\CS(H)$.
-Then $(\cs{L},\mu,\beta) \in \CS'(G)$.
-We have just seen that $\CS'(G)$, $\CS_H(G)$ and $\CS(G\ab)$ are equivalent categories.
-Let $(\cs{L},\mu,\beta) \mapsto (\cs{L},\mu,\nu)$ under the equivalence $\CS'(G) \to \CS_H(G)$ described above.
-Then $(\cs{L},\mu,\nu) \iso q_H^*(\cs{L}\ab,\mu\ab)$ in $\CS_H(G)$, for some $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$.
-Applying the forgetful functor $\CS_H(G)\to \CS(G)$ to this isomorphism, it follows that $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, as desired.
-
-Conversely, suppose $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$.
-Then $j^*(\cs{L},\mu) \iso j^*q^*(\cs{L}\ab,\mu\ab)$ in $\CS(H)$. 
-Since $g\circ j = 1$, it follows that $\cs{L}\vert_{G\der} \to (\EE)_{H}$ in $\CS(H)$.
 This completes the proof of Proposition~\ref{prop:Gder_triv}.
@@
 
-All supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}, as established in \cite{kim:07a}.
-The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
-Let us refer to the types arising in this manner as {\it Yu types}.
-In this section we offer an application of Theorem~\ref{thm:geo}, by showing that Yu types are geometrizable, subject to a very mild hypothesis.
-The proof of that statement, made precise in Theorem~\ref{thm:geotypes}, requires: the geometrization of the character of the Heisenberg-Weil representation over finite fields (Section~\ref{ssec:Jacobi}); a review of some basic properties of Yu types (Section~\ref{ssec:review}); a review of some facts from Yu's notes on smooth integral models (Section~\ref{ssec:models}); and the geometrization of characters of representations of reductive groups over finite fields with cyclic geometric component groups, using Lusztig's character sheaves on these groups.
-These pieces are assembled in Section~\ref{ssec:geotypes}.
-
 \subsection{Quasicharacters of smooth group schemes over certain henselian traits}
@@
 With notation as above, suppose $\Fq$ is a finite field.
-For every quasicharacter character $\varphi : \underline{G}(S) \to \EEx$ there is a Weil sheaf $\cs{L}$ on $G$ such that \[\trFrob{\cs{L}} =  \varphi.\] \end{proposition}
+For every quasicharacter character $\varphi : \underline{G}(S) \to \EEx$ there is a Weil sheaf $\cs{L}$ on $G$ such that \[\trFrob{\cs{L}} = \trace \varphi.\] \end{proposition}
 
@@
 \] 
-Set $R_m = R/\mathfrak{p}^{m+1}$ and
-set $G_m = \Gr_m^{R}(\underline{G})$, the Greenberg transform of $\underline{G}\times_{\Spec{R}}\Spec{R_m}$.
-Then $G_m$ is a smooth group scheme over $\Fq$ and $G_m(\Fq) = \underline{G}(R_m)$, canonically.
-Using Theorem~\ref{thm:geo}, let $\cs{L}_m$ be a geometrization of the character $\varphi_m: G_m \to \EEx$; so
+Set $G_m = \Gr_m^{R}(\underline{G})$.
+Then $G_m$ is a smooth group scheme over $\Fq$ and $G_m(\Fq) = \underline{G}(R/\mathfrak{p}^{m+1})$, canonically.
+Using Theorem~\ref{thm:geo}, let $\cs{L}_m$ be a geometrization of the linear character $\varphi_m: G_m \to \EEx$; so
 \[
@@
 Let $\cs{L}$ be the  Weil sheaf on $G$ obtained from $\cs{L}_m$ by pullback along $G \to G_m$. 
-Then $\cs{L}$ is a quasicharacter sheaf on $G$, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, such that $\trFrob{\cs{L}} = \varphi$.
+Then $\cs{L}$ is a quasicharacter sheaf on $G$, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, such that $\trFrob{\cs{L}} = \trace \varphi$.
 \end{proof}
@@
 
-Let $\psi : Z \to \CC^\times$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi$. 
+Let $\psi : Z \to \EEx$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi : Z \to CC^\times$. 
 The Heisenberg representation determines a representation $\pi_{\psi}$ of $\Sp(V)$ with the same representation space as $\omega_\psi$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\psi(g)$ determines an isomorphism of representations $\omega_\psi^g \to \omega_\psi$.
@@
 The group $\Sp(V)$ is naturally stratified into the conjugation-stable subvarieties $S_r = \{ g\in \Sp(V) \tq \dim \ker (g-1) = r \}$. 
-The big stratum, $S_0$, is dense in $\Sp(V)$.
-%the boundary of $S_0$ is $\cup_{0< r\leq \dim V} S_r$. 
- From \cite{howe:73a}*{Prop. 2} we learn that if $g\in S_r$ then $q^{-r/2} \trace(W_\psi)(g)$ has complex norm $1$.
-
-It is one of the main results of \cite{gurevich-hadani:07a} (see also \cite{gurevich-hadani:11a}*{Thm. 4.5}) that there is a Weil sheaf complex $\cs{K}_\psi$ on $\Sp(V)\ltimes V^\sharp$ such that 
+The big stratum, $S_0$, is dense in $\Sp(V)$;
+the boundary of $S_0$ is $\cup_{0< r\leq \dim V} S_r$. 
+From \cite{howe:73a}*{Prop. 2} we learn that $q^{-r/2} \trace(W_\psi)(g)$ has complex norm $1$, for $0\leq r \leq \dim V$ and $g\in S_r$.
+
+It is one of the main results of \cite{gurevich-hadani:07a} (see also \cite{gurevich-hadani:11a}*{Thm. 4.5}) that there is a Weil sheaf complex $\cs{W}_{\psi}$ on $\Sp(V)\ltimes V^\sharp$ such that 
 \begin{equation}
-\trFrob{\cs{K}_\psi} = \trace(W_\psi).
+\trFrob{\cs{W}_\psi} = \trace(W_\psi).
 \end{equation}
 %
-Since $\cs{K}_\psi$ is an object in Deligne's category $D^b_c(\Sp(V)\ltimes V^\sharp,\EE)$, the left hand since of this equality must be interpreted accordingly.
-
-Although nothing more that this statement will be needed below, the construction of $\cs{K}_\psi$ is so unbelievably gorgeous that we can't resist saying a few extra words about it here.
-The reader pressed for time is invited to skip the next paragraph without loosing anything needed for the arguments in the rest of Section~\ref{sec:types}.
+Although nothing more that this statement will be needed below, the construction of $\cs{W}_\psi$ is so unbelievably gorgeous that we can't resist saying a few extra words about it here.
+The reader pressed for time is invited to skip to the next section without loosing anything needed for the arguments in the rest of Section~\ref{sec:types}.
 
 Fix an isomorphism $\CC \approx \EE$ so that we may mix classical and geometric facts. 
-One begins by observing that $S_0$ is the domain of the Cayley transform $\cay : g \mapsto (g-1)^{-1}(g+1)$ on $\Sp(V)$ and that if $(g,v,z) \in S_0\times V\times Z$ then
+One begins by finding a local system $\cs{K}_0$ on $S_0 \times V^\sharp$ such that 
+\[
+\trFrob{\cs{K}_0[\dim V](\frac{\dim V}{2})} = \trace(W_\psi)\vert_{S_0\times V^\sharp},
+\]
+where $\cs{K}_0[\dim V](\frac{\dim V}{2})$ is the Tate twist of the shift of $\cs{K}_0$.
+This is done by observing that $S_0$ is the domain of the Cayley transform $\cay : g \mapsto (g-1)^{-1}(g+1)$ on $\Sp(V)$ and that 
 \begin{equation}\label{Cayley}
-\trace(W_\psi)(g,v,z) =  \frac{\gamma_\psi^{\dim V}}{q^{\dim V/2} } \sigma(\det(1+\cay(g)))\ \psi\left(\langle \cay(g)v,v\rangle/4 \right) \psi(z),
+\trace(W_\psi)(g,v,z) =  q^{-\dim V/2} \gamma_\psi^{\dim V} \sigma(\det(1+\cay(g))) \psi\left(\frac{1}{4}\langle \cay(g)v,v\rangle \right) \psi(z),
 \end{equation}
- where $\gamma_\psi$ is the Gauss sum for $\psi$ and $\sigma : \Fq^\times \to \EE^\times$ is the quadratic character of $\Fq^\times$.
-By a simple adaptation of what in \cite{gurevich-hadani:07a}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}$ (in fact, a Weil local system) on $S_0 \times V^\sharp$ such that
-\[
-\trFrob{\cs{K}(\frac{\dim V}{2})} = \trace(W_\psi)\vert_{S_0\times V^\sharp},
-\]
-where $\cs{K}(\frac{\dim V}{2})$ is the Tate twist of $\cs{K}$.
-%
-Next, one forms $\cs{K}_\psi \ceq j_{!*} \cs{K}$, the perverse extension of $\cs{K}$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$; recall that $S_0$ is Zariski dense in $\Sp(V)$.
+ for $(g,v,z) \in S_0\times V\times Z$, where $\gamma_\psi$ is the Gauss sum for $\psi$ and $\sigma : \Fq^\times \to \EE^\times$ is the quadratic character of $\Fq^\times$.
+By a simple adaptation of what in \cite{gurevich-hadani:07a}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}_0$ on $S_0 \times V^\sharp$.
+Next, one forms $\cs{K} \ceq j_{!*} \cs{K}_0$, the perverse extension of $\cs{K}_0$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$; recall that $S_0$ is Zariski dense in $\Sp(V)$.
 It follows from \cite{gurevich-hadani:07a} that 
 \[
-\trFrob{\cs{K}_\psi} = \trace(W_\psi).
-\]
-Then $\cs{K}_\psi$ is the promised Weil sheaf complex.
+\trFrob{\cs{K}(\frac{\dim V}{2})} = \trace(W_\psi).
+\]
+Then $\cs{W}_\psi = \cs{K}(\frac{\dim V}{2})$ is the promised Weil sheaf complex.
 
@@
 
-A Yu type is a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$,  olnstructed from the following information, derived from a Yu datum:
+As proved in \cite{kim:07a}, all supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}.
+The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
+Let us refer to the types arising in this manner as {\it Yu types}.
+%In this section we show that every Yu type is geometrizable.
+% in a sense which will be made clear below.
+%
+
+A Yu type is then a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$, directly from the following information, derived from a Yu datum:
 \begin{enumerate}
 \labitem{Y0}{Y0} a sequence of compact groups $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$;
-\labitem{Y1}{Y1} a continuous representation $\rho_0$ of $C^0$;
-\labitem{Y2}{Y2} quasicharacters $\varphi^i : C^i \to \CC^\times$, for $i=0, \ldots d$.
+\labitem{Y1}{Y1} a continuous representation $\rho^0$ of $C^0$;
+\labitem{Y2}{Y2} a quasicharacter $\varphi^i : C^i \to \CC^\times$, for $i=0, \ldots d$.
 \end{enumerate}
-%
-The representation $\rho_0$ and the quasicharacters $(\varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho_i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho_d \otimes \varphi^d = \rho$ as representations of $C^d = C$.
-%
-Since we will need some facts about this construction in the proof of Theorem~\ref{thm:geotypes}, we review some further detail here.
-In Table~\ref{table:notation} we explain how to convert the constructions appearing in this section into the notation of \cite{yu:01a}.
+The representations $(\rho^0, \varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho^d = \rho$.
+
+Since we will need some facts about this construction, we review some further detail here.
 
@@
 \labitem{Y3}{Y3}
-compact groups $J_i\subset C$, for $i=0, \ldots d$, such that 
+compact groups $J^i\subset C$, for $i=0, \ldots d$, such that 
 $
-C^i = J_0\cdots J_{i}
+C^i = J^0\cdots J^{i}
 $ 
-and, for $i=0, \ldots d-1$, a natural action of $C^i$ on $J_{i+1}$ defining the groups $C^i \ltimes J_{i+1}$.
+and, for $i=0, \ldots d-1$, a natural action of $C^i$ on $J^{i+1}$ defining the groups $C^i \ltimes J^{i+1}$.
 \begin{equation}\label{eq:semiprod}
@@
 \ && 1 \arrow{d} && \\
-\ && C^{i}\cap J_{i+1}\arrow{d} && \\
-1 \arrow{r} & J_{i+1} \arrow{r} & C^i \ltimes J_{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} & 1\\
+\ && C^{i}\cap J^{i+1}\arrow{d} && \\
+1 \arrow{r} & J^{i+1} \arrow{r} & C^i \ltimes J^{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} & 1\\
 && C^{i+1} \arrow{d}{} && \\
@@
 \end{enumerate}
-%He then introduces the following quotients of $J_{i+1}$ and $C^i$, for $i=0, \ldots d-1$.
-%
-Next, Yu defines a group homomorphism (in fact, a quotient) 
+%He then introduces the following quotients of $J^{i+1}$ and $C^i$, for $i=0, \ldots d-1$.
+
+Next, Yu uses this to define a group homomorphism (in fact, a quotient) 
 $
-J_{i+1} \to V_{i+1}
+J^{i+1} \to V_{i+1}
 $
 where $V_{i+1}$ is a finite abelian group, the latter also given the structure of a $\Fq$-vector space.
-The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to Z_{i+1}$, where $Z_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : Z_{i+1} \to \CC^\times$.
+The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to C_{i+1}$, where $C_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : C_{i+1} \to \EEx$.
 %\labitem{Q2}{Q2} 
@@
 $
-J_{i+1} \to V_{i+1}^\sharp,
+J^{i+1} \to V_{i+1}^\sharp,
 $
-where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $Z_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$, as in Section~\ref{ssec:Jacobi}.
-In fact, the quotient $J_{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J_{i+1} \to H_{i+1}$ and an isomorphism $j_{i+1} : H_{i+1} \to V_{i+1}^\sharp$, where $H_{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:01a}*{}.
+where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $C_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$.
+In fact, the quotient $J^{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J^{i+1} \to H^{i+1}$ and an isomorphism 
+$
+j_{i+1} : H^{i+1} \to V_{i+1}^\sharp,
+$
+where $H^{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:01a}*{}.
 %\labitem{Q3}{Q3} 
 %\item
-Finally, Yu constructs a group homomorphism $f_{i+1} : C^i \to \Sp(V_{i+1})$ such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H_{i+1}$ in the sense of \cite{yu:01a}.
-%
+Finally, Yu constructs 
+$
+f_{i+1} : C^i \to \Sp(V_{i+1}),
+$
+such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H^{i+1}$ in the sense of \cite{yu:01a}.
+
 Taken together, this defines
@@
 \begin{enumerate}
-\labitem{Y4}{Y4}  a group homomorphism $h_{i+1} : C^i \ltimes J_{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
-\[
-\begin{tikzcd}
-1 \arrow{r} & J_{i+1} \arrow{d} \arrow{r} & C^i \ltimes J_{i+1} \arrow{d}{h_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} \arrow{d}{f_i} & 1\\ 
+\labitem{Y4}{Y4}  a group homomorphism $h_{i+1} : C^i \ltimes J^{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
+\[
+\begin{tikzcd}
+1 \arrow{r} & J^{i+1} \arrow{d} \arrow{r} & C^i \ltimes J^{i+1} \arrow{d}{h_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} \arrow{d}{f_i} & 1\\ 
 1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
@@
 
-We can now recall how Yu uses all this to construct representations $\rho_i$ of $C^i$, for $i=1, \ldots, d$ and thus the type $(C,\rho) = (C^d,\rho_d\otimes \varphi^d)$.
-The representations $\rho_i$ are defined recursively. 
-For the base case $i=0$, the representation $\rho_0$ is just $\rho_0$; see \ref{Y1} above.
-Now fix $i$.
+We can now recall how Yu uses all this to construct representations $\rho^i$ of $C^i$, for $i=1, \ldots, d$ and thus the type $(C,\rho) = (C^d,\rho^d\otimes \varphi^d)$.
+The representations $\rho^i$ are defined recursively. 
+For the base case $i=0$, the representation $\rho^0$ is just $\rho_0$; see \ref{Y1} above.
 Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
-Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $C^i \ltimes J_{i+1}$.
-Write $\inf(\rho_i \otimes \varphi^i)$ for the representation of $C^i \ltimes J_{i+1}$ obtained by pulling back $\rho_i$ along $C^i \ltimes J_{i+1} \to C^i$. 
+Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $C^i \ltimes J^{i+1}$.
+Write $\inf(\rho^i \otimes \varphi^i)$ for the representation of $C^i \ltimes J^{i+1}$ obtained by pulling back $\rho^i$ along $C^i \ltimes J^{i+1} \to C^i$. 
 Consider the representation
 \begin{equation}\label{eq:tensor}
-\rho_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\rho_i \otimes \varphi^i)
+\rho_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\rho^i \otimes \varphi^i)
 \end{equation}
-of $C^i \ltimes J_{i+1}$.
+of $C^i \ltimes J^{i+1}$.
 %By construction, the character of this representation satisfies
 %\begin{equation}\label{eq:tilderho}
-%\trace({\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\rho_i)(p_i(y))\ \varphi^i(p_i(y))
+%\trace({\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\rho^i)(p_i(y))\ \varphi^i(p_i(y))
 %\end{equation}
-%for $y \in C^i \ltimes J_{i+1}$.
-By \cite{yu:01a}*{}, the representation $\rho_{i+1}$ of $C^i \ltimes J_{i+1}$ is trivial on $C^{i}\cap J_{i+1}$ so $\rho_{i+1}$ descends to $C^{i+1}$. 
-%
-This defines the representation $\rho_{i+1}$ of $C^{i+1}$.
-This completes the recursive definition of $\rho_d$. 
-Now set $\rho \ceq \rho_d\otimes \varphi^d$. 
-This is the representation of $C^d = C$ determining the Yu type $(C,\rho)$.
-%The character of $\rho_d$ on $C^d = C = J_0 \cdots J_d$ satisfies
+%for $y \in C^i \ltimes J^{i+1}$.
+By \cite{yu:01a}*{}, the representation $\rho_{i+1}$ of $C^i \ltimes J^{i+1}$ is trivial on $C^{i}\cap J^{i+1}$ so $\rho_{i+1}$ descends to $C^{i+1}$.
+
+This defines the representation $\rho^{i+1}$ of $C^{i+1}$. 
+This completes the recursive definition and thus determines $\rho^d$. 
+Now set $\rho \ceq \rho^d\otimes \varphi^d$, which is the representation of $C^d = C$ determining the Yu type $(C,\rho)$.
+%The character of $\rho^d$ on $C^d = C = J^0 \cdots J^d$ satisfies
 %\[
-%\trace(\rho)(k_0 \cdots k_d) = \rho_0(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
+%\trace(\rho)(k_0 \cdots k_d) = \rho^0(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
 %\]
-%for $k_i\in J_i$.
-
-\begin{table}[htp]
-\caption{Comparison with notation of \cite{yu:01a}}
-\begin{center}
-\begin{tabular}{c|l}
-$C^0$ & $\,^\circ K^0 = G^0(F)_y$, \cite{yu:01a}*{\S 15} \\
-$\rho_0$ & $\,^\circ \rho^0$ \cite{yu:01a}*{\S 15} \\
-$C^{i+1}$ & $\,^\circ K^{i+1} = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, \ldots, s_{i})}$, \cite{yu:01a}*{\S 15} \\
-$\rho_{i+1}$ & $\,^\circ \rho^{i+1}$, \cite{yu:01a}*{\S 15} \\
-$\varphi^i$ & $\phi_i\vert_{\,^\circ K^i }$ \\
-$J_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}$ \\
-$V_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ (G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}$ \\ 
-$W_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi}_i\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
-%$H^{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi_i}\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
-$Z_{i+1}$ & $C$, \cite{yu:01a}*{\S 11} \\
-$(f_{j+1}, j_{i+1})$ & $(f,j)$ \cite{yu:01a}*{\S 11} \\
-$\langle\ ,\ \rangle_{i+1}$ & $\langle\ ,\ \rangle$, \cite{yu:01a}*{\S 11} 
-\end{tabular}
-\end{center}
-\label{table:notation}
-\end{table}%
+%for $k_i\in J^i$.
 
@@
 
-Regarding the construction of the type $(C,\rho)$, the paper \cite{yu:03a} concludes with the following observation.
+Regarding the construction of the type $(C,\rho)$, the paper \cite{yu:03a} concludes with the following provocative observation.
 \begin{quotation}
@@
 These results suggest that algebraic geometry and group schemes should play an
-important role in the representation theory of $p$-adic groups.} %\cite{yu:03a}
+important role in the representation theory of $p$-adic groups.} \cite{yu:03a}
 \end{quotation}
-In this section we explain the first sentence; in Section~\ref{ssec:geotypes} we follow the suggestion in the second sentence.
+In this section we explain what this observation is saying, following \cite{yu:03a}.
 
@@
 \] 
-for each $i=0,\ldots d$, such that $\underline{J}^i(R) = J_i$ as a subgroup of $C$ and such that the image of the $R$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $C^i$, for $i=0, \ldots , d$.
+for each $i=0,\ldots d$, such that $\underline{J}^i(R) = J^i$ as a subgroup of $C$ and such that the image of the $R$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $C^i$, for $i=0, \ldots , d$.
 %\labitem{M3}{M3}
@@
 \]
-gives $(\underline{G}^i \ltimes \underline{J}^{i+1})(R) = C^i \ltimes J_{i+1}$
+gives $(\underline{G}^i \ltimes \underline{J}^{i+1})(R) = C^i \ltimes J^{i+1}$
 %\end{enumerate}
@@
 Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
-The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $V^{i+1}$ over $\Fq$, where $V^{i+1}$, appears as a quotient $\underline{J}^{i+1}_{\Fq} \to V^{i+1}$ of algebraic groups over $\Fq$.
-Then the quotient $J_{i+1} \to V_{i+1}$ is realized as the composition
-\[
-\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to V^{i+1}(\Fq) = V_{i+1}.
-\]
-Likewise, the Heisenberg $p$-group $H_{i+1}$, appearing in \ref{ssec:review}, may be realized as a quotient of algebraic groups, and $\underline{J}^{i+1}_{\Fq} \to H^{i+1}$ as the composition 
-\[
-\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H_{i+1}.
-\]
-Finally, the group homomorphism $f_i : J_0\cdots J_i \to \Sp(V_{i+1})$ may be made geometric in much the same way. 
-Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $f_i : J_0\cdots J_i \to \Sp(V_{i+1})$ is realized as the composition
+The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $V^{i+1}_\Fq$, where $V^{i+1}_\Fq$, appears as a quotient $J^{i+1}_\Fq \to V^{i+1}_\Fq$ of algebraic groups.
+Then the quotient $J^{i+1} \to V_{i+1}$ is realized as the composition
+\[
+\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to V^{i+1}_\Fq(\Fq) = V_{i+1}.
+\]
+Likewise, the Heisenberg $p$-group $H^{i+1}$, appearing in \ref{ssec:review}, may be realized as a quotient of algebraic groups, and $J^{i+1}\to H^{i+1}$ as the composition 
+\[
+\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H^{i+1}.
+\]
+Finally, the group homomorphism $f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ may be made geometric in much the same way. 
+Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $f_i : J^0\cdots J^i \to \Sp(V_{i+1})$ is realized as the composition
 \[
@@
 Finally, we come to the main result of Section~\ref{sec:types}.
-%
+
 Since Yu's theory refers to complex representations, and since our geometrization uses $\ell$-adic sheaves, we grit our teeth and fix an isomorphism $\CC \approx \EE$.
 
-\begin{theorem}\label{thm:geotypes}
+\begin{proposition}\label{prop:geotypes}
 Let $(C,\rho)$ be a Yu type, constructed as in Section~\ref{ssec:review}.
-Let $G^0 = \Gr_{R}(\underline{G}^0)$ be the Greenberg transform of the smooth group scheme $\underline{G}^0$ appearing in Section~\ref{ssec:models}.
+Let $G^i = \Gr_{R}(\underline{G}^i)$ be the Greenberg transform of the smooth group scheme $\underline{G}^i$ appearing in Section~\ref{ssec:models}.
 Assume $\pi_0(\underline{G}^0)_\Fq^\reductive)$ is cyclic.
-Then there is a virtual Weil sheaf complex $\cs{A}$ on $G = \Gr_{R}(\underline{G})$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
-\end{theorem}
+Then there is a virtual Weil sheaf complex $\cs{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
+\end{proposition}
 
 \begin{proof}
-For every $i=0, \ldots ,d$, set $G^i = \Gr_{R}(\underline{G}^i)$.
 Recall that $G^i(\Fq) = \underline{G}^i(R) = C^i$, canonically.
@@
 G^i(\Fq) \arrow{rr}{\varphi^i} \arrow{rd} && \EEx\\
-& \underline{G}^i(R_m) \arrow{ru}[swap]{\varphi^i_m} 
-\end{tikzcd}
-\] 
-for all $i=0, \ldots d$.
+& \underline{G}^i(R/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi^i_m} 
+\end{tikzcd}
+\] 
+for each $i=0, \ldots d$.
 Set $G_m^i = \Gr_m^{R}(\underline{G}^i)$.
-Then $G_m^i$ is a smooth group scheme over $\Fq$ and $G_m^i(\Fq) = \underline{G}^i(R_m)$, canonically.
+Then $G_m^i$ is a smooth group scheme over $\Fq$ and $G_m^i(\Fq) = \underline{G}^i(R/\mathfrak{p}^{m+1})$, canonically.
 Using Theorem~\ref{thm:geo}, let $\cs{L}^i_m$ be a geometrization of the linear character $\varphi^i_m: G_m^i \to \CC^\times$; so
 \[
-\trFrob{\cs{L}^i_m} = \varphi^i_m.
+\trFrob{\cs{L}^i_m} = \trace \varphi^i_m.
 \]
@@
 %Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{R}(\underline{G}^0) \to \Gr^{R}_{m}(\underline{G}^0)$.
-%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G}^0)$ from which the character of $\rho_0$ may be recovered.
+%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G}^0)$ from which the character of $\rho^0$ may be recovered.
 
 Consider the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ and the Heisenberg-Weil representation $W_{i+1}$ appearing in Section~\ref{ssec:models}.
-Let $\cs{K}^{i+1}$ be the Weil sheaf on the Jacobi group, recalled in Section~\ref{ssec:Jacobi}, such that
-\[
-\trFrob{\cs{K}^{i+1}} = \trace(W_{i+1}).
+Let $\cs{W}_{i+1}$ be the Weil sheaf on the Jacobi group, recalled in Section~\ref{ssec:Jacobi}, such that
+\[
+\trFrob{\cs{W}_{i+1}} = \trace(W_{i+1}).
 \]
 Recall from Section~\ref{ssec:models} that $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ is a quotient of the special fibre of the smooth group scheme $\underline{G}^{i} \ltimes \underline{J}^{i+1}$.
-Let $\cs{K}_0^{i+1}$ be the Weil sheaf on the special fibre of $\underline{G}^{i} \ltimes \underline{J}^{i+1}$ obtained from $W_{i+1}$ by pullback. 
-Let $\cs{K}_m^{i+1}$ be the Weil sheaf on $\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1})$ obtained from $\cs{K}_0^{i+1}$ by pullback along the affine morphism
+Let $\cs{W}_0^{i+1}$ be the Weil sheaf on the special fibre of $\underline{G}^{i} \ltimes \underline{J}^{i+1}$ obtained from $W_{i+1}$ by pullback. 
+Let $\cs{W}_m^{i+1}$ be the Weil sheaf on $\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1})$ obtained from $\cs{W}_0^{i+1}$ by pullback along the affine morphism
 $\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1}) \to \Gr^{R}_0(\underline{G}^{i} \ltimes \underline{J}^{i+1})$.
 
-We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{R}_m(\underline{G}^{i})$, for $i=0,\ldots ,d$, recursively, following the construction of the representations $\rho_i$, as reviewed in Section~\ref{ssec:review}.
+We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{R}_m(\underline{G}^{i})$, for $i=0,\ldots ,d$, recursively, following the construction of the representations $\rho^i$, as reviewed in Section~\ref{ssec:review}.
 First, set $\cs{A}_m^i = A_m^0$ and note that 
@@
 \begin{tikzcd}
-G^0(\Fq) \arrow{rr}{\trace(\rho_0)} \arrow{rd} && \EE\\
+G^0(\Fq) \arrow{rr}{\trace(\rho^0)} \arrow{rd} && \EE\\
 & G^0_m(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m^0}} & 
@@
 \begin{tikzcd}
-G^i(\Fq) \arrow{rr}{\trace(\rho_i)} \arrow{rd} && \EE\\
+G^i(\Fq) \arrow{rr}{\trace(\rho^i)} \arrow{rd} && \EE\\
 & G_m^i(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m^i}} & 
@@
 \[
-\cs{B}_m^{i+1} \ceq \cs{K}_m^{i+1} \otimes (p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
+\cs{B}_m^{i+1} \ceq \cs{W}_m^{i+1} \otimes (p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
 \]
@@
 \begin{tikzcd}
-G^{i+1}(\Fq) \arrow{rr}{\trace(\rho_{i+1})} \arrow{rd} && \EE\\
+G^{i+1}(\Fq) \arrow{rr}{\trace(\rho^{i+1})} \arrow{rd} && \EE\\
 & G_m^{i+1}(\Fq)\arrow{ru}[swap]{{\trFrob{\cs{A}_m^{i+1}}} } & 
@@
 \bibliography{bibliography/Biblio}
-% \bib, bibdiv, biblist are defined by the amsrefs package.
-%\iffalse
-
-\begin{bibdiv}
-\begin{biblist}
-
-\bib{berndt-schmidt:98a}{book}{
-      author={Berndt, Rolf},
-      author={Schmidt, Ralf},
-       title={{Elements of the representation theory of the Jacobi group}},
-   publisher={{Birkh\"auser/Springer Basel AG}},
-     address={Basel, Switzerland},
-        date={2011},
-}
-
-\bib{bertapelle-gonzales:Greenberg}{unpublished}{
-      author={Bertapelle, Alessandra},
-      author={{Gonz\'ales-Avil\'es}, Cristian~D.},
-       title={{The Greenberg functor revisited}},
-        date={2014},
-         url={http://arxiv.org/abs/1311.0051},
-        note={\href{http://arxiv.org/abs/1311.0051}{arXiv:1311.0051
-  [math.NT]}},
-}
-
-\bib{bushnell-kutzko:98a}{article}{
-      author={Bushnell, Colin},
-      author={Kutzko, Phil},
-       title={{Smooth representations of reductive $p$-adic groups: structure
-  theory via types}},
-        date={1998},
-     journal={Proc. London Math. Soc.},
-      volume={77},
-      number={3},
-       pages={{582\ndash 634}},
-}
-
-\bib{cunningham-roe:13a}{article}{
-      author={Cunningham, Clifton},
-      author={Roe, David},
-       title={From the function-sheaf dictionary to quasicharacters of $p$-adic
-  tori},
-  journal={Journal of the Institute of Mathematics of Jussieu},
-        year = {2016},
-issn = {1475-3030},
-pages = {1--37},
-numpages = {37},
-doi = {10.1017/S1474748015000286},
-URL = {http://journals.cambridge.org/article_S1474748015000286},
-}
-
-\bib{demazure:SGA3-VIA}{inproceedings}{
-      author={Gabriel, Pierre},
-       title={{Expos\'e VI$_\mathrm{A}$: G\'en\'eralit\'es sur les groupes
-  alg\'ebriques}},
-        date={1970},
-   booktitle={{Sch\'emas en groupes I: Proprietes generales des schemas en
-  groupes}},
-      editor={Demazure, Michel},
-      editor={Grothendieck, Alexander},
-      series={Lecture Notes in Math},
-      volume={151},
-   publisher={Springer-Verlag},
-     address={Berlin},
-}
-
-\bib{EGAIV4}{article}{
-      author={Grothendieck, Alexandre},
-       title={{\'El\'ements de g\'eom\'etrie alg\'ebrique IV. \'Etude locale
-  des sch\'emas et des morphismes de sch\'emas. IV}},
-        date={1967},
-     journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
-      number={32},
-}
-
-\bib{gurevich-hadani:07a}{article}{
-   author={Gurevich, Shamgar},
-   author={Hadani, Ronny},
-   title={The geometric Weil representation},
-   journal={Selecta Math. (N.S.)},
-   volume={13},
-   date={2007},
-   number={3},
-   pages={465--481},
-}
-
-\bib{gurevich-hadani:11a}{unpublished}{
-   author={Gurevich, Shamgar},
-   author={Hadani, Ronny},
-   title={The categorical Weil representation},
-	date={2011},
-        note={\href{http://arxiv.org/abs/1108.0351}{arXiv:1108.0351 [math.RT]}}
-}
-
-\bib{howe:73a}{article}{
-   author={Howe, Roger E.},
-   title={On the character of Weil's representation},
-   journal={Trans. Amer. Math. Soc.},
-   volume={177},
-   date={1973},
-   pages={287--298},
-}
-
-\bib{kamgarpour:09a}{article}{
-      author={Kamgarpour, Masoud},
-       title={{Stacky abelianization of algebraic groups}},
-        date={2009},
-     journal={{Transform. Groups}},
-      volume={14},
-      number={4},
-       pages={825\ndash 846},
-}
-
-\bib{kim:07a}{article}{
-      author={Kim, Ju-Lee},
-       title={Supercuspidal representations: an exhaustion theorem},
-        date={2007},
-     journal={J. Amer. Math. Soc.},
-      volume={20},
-      number={2},
-       pages={273\ndash 320},
-}
-
-\bib{lusztig:85a}{article}{
-      author={Lusztig, George},
-       title={{Character sheaves I}},
-        date={1985},
-     journal={Advances in Math.},
-      volume={56},
-       pages={193\ndash 237},
-}
-
-\bib{lusztig:disconnected1}{article}{
-      author={Lusztig, George},
-       title={{Character sheaves on disconnected groups I}},
-        date={2003},
-     journal={Representation Theory},
-      volume={7},
-       pages={374\ndash 403},
-}
-
-\bib{Vistoli:notes}{unpublished}{
-      author={Vistoli, Angelo},
-       title={{Notes on Grothendieck topologies, fibered categories and descent
-  theory}},
-        date={2007},
-        note={\href{http://arxiv.org/abs/math/0412512}{arXiv:0412512
-  [math.AG]}},
-}
-
-\bib{yu:01a}{article}{
-      author={Yu, Jiu-Kang},
-       title={Construction of tame supercuspidal representations},
-        date={2001},
-     journal={J. Amer. Math. Soc.},
-      volume={14},
-      number={3},
-       pages={{579\ndash 622}},
-}
-
-\bib{yu:03a}{unpublished}{
-      author={Yu, Jiu-Kang},
-       title={{Smooth models associated to concave functions in Bruhat-Tits
-  theory}},
-        date={2003},
-        note={Preprint},
-}
-
-\end{biblist}
-\end{bibdiv}
-%\fi
 

### 2016-04-07 followup.tex
Working on the introduction....

--- 2016-03-30 followup.tex
@@
 Next, we broaden our scope further to encompass smooth group schemes $G$ over $\Fq$ that are not necessarily commutative.
-In this paper, we do not consider Lusztig's geometrization of characters of representations of connected, reductive groups $G(k)$
-using character sheaves \cite{lusztig:85a}*{Def.~2.10}, but focus on the case of characters
-$G(k)^*$ (that is, group homomorphisms from $G(k)$ to $\EEx$), assuming only that $G$ is smooth, allowing for the possibility that $G$ is not connected and not reductive.
+In this paper, we do not consider Lusztig's geometrization for characters of representations of connected, reductive groups $G(k)$
+using character sheaves \cite{lusztig:85a}*{Def.~2.10}.  Instead, we focus on the group of $1$-dimensional characters
+$G(k)^*$, assuming that $G$ is smooth, but not that it is connected or reductive.
 The category $\CS(G)$ has a straightforward generalization to this case, but again
@@
 Then in Section \ref{ssec:proofs}, we give proofs of the results in Section \ref{sec:noncom}, which require a development of equivariant linear character sheaves.
-%
-In Section~\ref{sec:types} we use Theorem~\ref{thm:geo} to geometrize the representations of compact $p$-adic groups appearing in the types for: we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\rho)$.
-The proof of this statement is quite technical, so it must be delayed to Section~\ref{ssec:geotypes}, after reviewing types in Section~\ref{ssec:review} and models Section~\ref{ssec:models} developed by Yu, for which we must also review some facts about the Heisenberg-Weil representation and its geometrization, in Section~\ref{ssec:Jacobi}.
+
+In Section~\ref{sec:types} we give an application of Theorem~\ref{thm:geo} by geometrizing types for supercuspidal representations of $p$-adic groups.
+Specifically, we show that if $C$ is a compact $p$-adic group and $\rho$ is a representation of $C$ and $(C,\rho)$ is a type for a tamely ramified $p$-adic group then there is a  group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a virtual Weil sheaf $\mathcal{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
+As preparation for the proof of this statement, we review types (Section~\ref{ssec:review}) and smooth integral models (Section~\ref{ssec:models}), both as developed by Yu.  
+We also review some facts about the Heisenberg-Weil representation and its geometrization (Section~\ref{ssec:Jacobi}).
+These elements are pulled together in Section~\ref{ssec:geotypes}, where the proof Theorem~\ref{thm:geotypes}.
+
+ \todo{There are some grammatical errors in this paragraph, and I'm not 100\% sure how they should be corrected}
 
@@
 \]
-Since $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ canonically, and since $\cs{L}^\vee \iso i^*\cs{L}$, canonically, this defines the promised isomorphism
+Since $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ canonically, and since $i^*(\cs{L}^\vee) \cong \cs{L}$ canonically, this defines the promised isomorphism
 \[
@@
 %Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
-Category $\CCS(G)$ is monoidal and 
-\[
-\CCSiso{G} \iso \Hom(G\ab(\Fq),\EEx),
-\]
-canonically.
-Every map in $\CCS(G)$ is either trivial or an isomorphism, and the automorphism group of any object in $\CCS(G)$ is $\Hom(\pi_0(G\ab)_{\Frob{}},\EEx)$, canonically.
+The category $\CCS(G)$ is monoidal and there is a canonical isomorphism
+\[
+\CCSiso{G} \iso \Hom(G\ab(\Fq),\EEx).
+\]
+Every map in $\CCS(G)$ is either trivial or an isomorphism, and the automorphism group of any object in $\CCS(G)$ is canonically
+isomorphic to $\Hom(\pi_0(G\ab)_{\Frob{}},\EEx)$.
 \end{corollary}
@@
 \end{align*}
-We require that the following diagram of Weil local systems on $H \times G\times G$ commutes:
+We require that the following diagram of Weil local systems on $H \times G\times G$ commutes: %\todo{Something's wrong: the top left actually requires $a \circ c_2 = m \circ c_1$, which isn't true.}
 \begin{equation}\label{ECS1}
 \begin{tikzcd}[column sep=30]
-\ & \arrow{dl}{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{dr}[swap]{p\circ c_2 = m\circ c_3}  &  \\
+\ & \arrow{dl}{a\circ c_2 = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{dr}[swap]{p\circ c_2 = m\circ c_3}  &  \\
 \arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} &&& c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
@@
 
-All supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}, as established in \cite{kim:07a}.
+All supercuspidal representations of tamely ramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}, as established in \cite{kim:07a}.
 The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
@@
 \begin{tabular}{c|l}
-$C^0$ & $\,^\circ K^0 = G^0(F)_y$, \cite{yu:01a}*{\S 15} \\
-$\rho_0$ & $\,^\circ \rho^0$ \cite{yu:01a}*{\S 15} \\
-$C^{i+1}$ & $\,^\circ K^{i+1} = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, \ldots, s_{i})}$, \cite{yu:01a}*{\S 15} \\
-$\rho_{i+1}$ & $\,^\circ \rho^{i+1}$, \cite{yu:01a}*{\S 15} \\
+$C^0$ & $\,^\circ K^0 = G^0(F)_y$\\% \cite{yu:01a}*{\S 15} \\
+$\rho_0$ & $\,^\circ \rho^0$\\% \cite{yu:01a}*{\S 15} \\
+$C^{i+1}$ & $\,^\circ K^{i+1} = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, \ldots, s_{i})}$\\% \cite{yu:01a}*{\S 15} \\
+$\rho_{i+1}$ & $\,^\circ \rho^{i+1}$\\% \cite{yu:01a}*{\S 15} \\
 $\varphi^i$ & $\phi_i\vert_{\,^\circ K^i }$ \\
@@
 $V_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ (G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}$ \\ 
-$W_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi}_i\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
+$V_{i+1}^\sharp$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi}_i\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
 %$H^{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi_i}\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
-$Z_{i+1}$ & $C$, \cite{yu:01a}*{\S 11} \\
-$(f_{j+1}, j_{i+1})$ & $(f,j)$ \cite{yu:01a}*{\S 11} \\
-$\langle\ ,\ \rangle_{i+1}$ & $\langle\ ,\ \rangle$, \cite{yu:01a}*{\S 11} 
+$Z_{i+1}$ & $\ker(V_{i+1}^\sharp\to V_{i+1})$ % \cite{yu:01a}*{\S 11} \\
+%$(f_{j+1}, j_{i+1})$ & $(f,j)$ \cite{yu:01a}*{\S 11} \\
+%$\langle\ ,\ \rangle_{i+1}$ & $\langle\ ,\ \rangle$, \cite{yu:01a}*{\S 11} 
 \end{tabular}

### 2016-04-07 followup.tex
Add missing paren

@@
 Then in Section \ref{ssec:proofs}, we give proofs of the results in Section \ref{sec:noncom}, which require a development of equivariant linear character sheaves.
-
-In Section~\ref{sec:types} we give an application of Theorem~\ref{thm:geo} by geometrizing types for supercuspidal representations of $p$-adic groups.
-Specifically, we show that if $C$ is a compact $p$-adic group and $\rho$ is a representation of $C$ and $(C,\rho)$ is a type for a tamely ramified $p$-adic group then there is a  group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a virtual Weil sheaf $\mathcal{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
-As preparation for the proof of this statement, we review types (Section~\ref{ssec:review}) and smooth integral models (Section~\ref{ssec:models}), both as developed by Yu.  
-We also review some facts about the Heisenberg-Weil representation and its geometrization (Section~\ref{ssec:Jacobi}).
-These elements are pulled together in Section~\ref{ssec:geotypes}, where the proof Theorem~\ref{thm:geotypes}.
-
+%
+In Section~\ref{sec:types} we use Theorem~\ref{thm:geo} to geometrize the representations of compact $p$-adic groups appearing in the types for: we find a group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a Weil sheaf $\mathcal{F}$ on $G$ such that $\trFrob{\cs{F}} = \trace(\rho)$.
+The proof of this statement is quite technical, so it must be delayed to Section~\ref{ssec:geotypes}, after reviewing types in Section~\ref{ssec:review} and models Section~\ref{ssec:models} developed by Yu, for which we must also review some facts about the Heisenberg-Weil representation and its geometrization, in Section~\ref{ssec:Jacobi}.
 \todo{There are some grammatical errors in this paragraph, and I'm not 100\% sure how they should be corrected}
@@
 \]
-Since $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ canonically, and since $i^*(\cs{L}^\vee) \cong \cs{L}$ canonically, this defines the promised isomorphism
+Since $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ canonically, and since $\cs{L}^\vee \iso i^*\cs{L}$, \todo{should we write $i^*(\cs{L}^\vee) \cong \cs{L}$ instead?} canonically, this defines the promised isomorphism
 \[
@@
 \end{align*}
-We require that the following diagram of Weil local systems on $H \times G\times G$ commutes: %\todo{Something's wrong: the top left actually requires $a \circ c_2 = m \circ c_1$, which isn't true.}
+We require that the following diagram of Weil local systems on $H \times G\times G$ commutes: \todo{Something's wrong: the top left actually requires $a \circ c_2 = m \circ c_1$, which isn't true.}
 \begin{equation}\label{ECS1}
 \begin{tikzcd}[column sep=30]
-\ & \arrow{dl}{a\circ c_2 = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{dr}[swap]{p\circ c_2 = m\circ c_3}  &  \\
+\ & \arrow{dl}{c_2\circ a = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{dr}[swap]{p\circ c_2 = m\circ c_3}  &  \\
 \arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} &&& c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
@@
 
-All supercuspidal representations of tamely ramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}, as established in \cite{kim:07a}.
+All supercuspidal representations of unramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}, as established in \cite{kim:07a}.
 The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
@@
 Let $G^0 = \Gr_{R}(\underline{G}^0)$ be the Greenberg transform of the smooth group scheme $\underline{G}^0$ appearing in Section~\ref{ssec:models}.
-Assume $\pi_0(\underline{G}^0)_\Fq^\reductive)$ is cyclic.
+Assume $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
 Then there is a virtual Weil sheaf complex $\cs{A}$ on $G = \Gr_{R}(\underline{G})$ such that $\trFrob{\cs{A}} = \trace(\rho)$.

### 2016-04-07 followup.tex
Still working on the introduction.

--- 2016-04-07 followup.tex
@@
 In Section~\ref{sec:types} we give an application of Theorem~\ref{thm:geo} by geometrizing types for supercuspidal representations of $p$-adic groups.
-Specifically, we show that if $C$ is a compact $p$-adic group and $\rho$ is a representation of $C$ and $(C,\rho)$ is a type for a tamely ramified $p$-adic group then there is a  group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a virtual Weil sheaf $\mathcal{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
-As preparation for the proof of this statement, we review types (Section~\ref{ssec:review}) and smooth integral models (Section~\ref{ssec:models}), both as developed by Yu.  
-We also review some facts about the Heisenberg-Weil representation and its geometrization (Section~\ref{ssec:Jacobi}).
-These elements are pulled together in Section~\ref{ssec:geotypes}, where the proof Theorem~\ref{thm:geotypes}.
+The proof of this statement, which is made precise in Theorem~\ref{thm:geotypes}, is given in Section~\ref{ssec:geotypes}.
+ %Specifically, we show that if $C$ is a compact $p$-adic group and $\rho$ is a representation of $C$ and $(C,\rho)$ is a type for a tamely ramified $p$-adic group then there is a  group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a virtual Weil sheaf $\mathcal{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
+As preparation for the proof, we review some facts about the Heisenberg-Weil representation and its geometrization, in Section~\ref{ssec:Jacobi}.
+Then, in Section~\ref{ssec:review}, we review Yu's theory of types and his study of smooth integral models, in Section~\ref{ssec:models}.  
+These elements are pulled together in Section~\ref{ssec:geotypes}, where the proof Theorem~\ref{thm:geotypes} is given.
 

### 2016-04-17 followup.tex
Small changes to introduction

@@
 When $G$ is connected, all character sheaves on $G$ are commutative.
-This category clarifies several questions about character sheaves on $G$: invisible character sheaves \cite{cunningham-roe:13a}*{Def.
-2.8} are precisely those that are not commutative, and $\TrFrob{G}^{-1} : G(k)^* \to \CCSiso{G}$ provides a canonical splitting of $\TrFrob{G} : \CSiso{G} \to G(k)^*$ \cite{cunningham-roe:13a}*{Rem.
+This category clarifies several questions about character sheaves on $G$.
+Invisible character sheaves \cite{cunningham-roe:13a}*{Def.
+2.8} are precisely those $\cs{L}$ with $\TrFrob{G}(\cs{L}) = 1$ that are not commutative.
+Moreover, $\TrFrob{G}^{-1} : G(k)^* \to \CCSiso{G}$ provides a canonical splitting of $\TrFrob{G} : \CSiso{G} \to G(k)^*$ \cite{cunningham-roe:13a}*{Rem.
 3.7}.

### 2016-04-17 followup.tex
Getting ready for conversation with David.

--- 2016-04-07 followup.tex
@@
 \end{equation}
-and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes. \todo{Maybe we should give a reference for this definition?}
+and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes. 
 \begin{equation}\label{E2}
@@
 This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.
+\todo{Maybe we should give a reference for this definition?}
+The reader will recognize this notion as the Weil sheaf version of equivariant sheaves for the action $a$ of $H$ on $G$, as can be found, for example, in \cite{bernstein-lunts:equivariant}*{0.2}.
 
 \subsubsection{Equivariant linear character sheaves}\label{ssec:equivariant2}
+
+The notation of an $H$-equivariant Weil sheaf on $G$, as described in Section~\ref{ssec:equivariant1}, does not use that fact that the action $a: H\times G \to G$ is compatible with the group structure on $G$.
+Here we a introduce a notion which makes use of that condition.
 
@@
 \end{align*}
-We require that the following diagram of Weil local systems on $H \times G\times G$ commutes: %\todo{Something's wrong: the top left actually requires $a \circ c_2 = m \circ c_1$, which isn't true.}
+We require that the following diagram of Weil local systems on $H \times G\times G$ commutes: \todo{Something's wrong: the top left actually requires $a \circ c_2 = m \circ c_1$, which isn't true.}
 \begin{equation}\label{ECS1}
@@
 
+\bib{bernstein-lunts:equivariant}{book}{
+   author={Bernstein, Joseph},
+   author={Lunts, Valery},
+   title={Equivariant sheaves and functors},
+   series={Lecture Notes in Mathematics},
+   volume={1578},
+   publisher={Springer-Verlag, Berlin},
+   date={1994},
+   pages={iv+139},
+   isbn={3-540-58071-9},
+%   review={\MR{1299527}},
+}
+
 \bib{bertapelle-gonzales:Greenberg}{unpublished}{

### 2016-04-17 followup.tex

@@
 \end{equation}
-and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes. 
+and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes. \todo{Maybe we should give a reference for this definition?}
 \begin{equation}\label{E2}
@@
 \end{align*}
-We require that the following diagram of Weil local systems on $H \times G\times G$ commutes: \todo{Something's wrong: the top left actually requires $a \circ c_2 = m \circ c_1$, which isn't true.}
+We require that the following diagram of Weil local systems on $H \times G\times G$ commutes: %\todo{Something's wrong: the top left actually requires $a \circ c_2 = m \circ c_1$, which isn't true.}
 \begin{equation}\label{ECS1}

### 2016-04-17 followup.tex
Adding some recollections before Prop 3.1

--- 2016-04-17 followup.tex
@@
 he opts to give a different definition of commutator and, in doing so, introduces a `stacky abelianization' of $G$ in order to geometrize characters of $G(\Fq)$.
- Since we has already seen the need to adapt the
+ Since we have already seen the need to adapt the
 notion of character sheaf, even in the commutative case, we instead add restrictions
@@
 1.1}, as linear character sheaves when $G$ is smooth but not necessarily commutative.
+Also recall the short exact sequence of group schemes
+
+\[
+1 \to G\der \xrightarrow{j} G \xrightarrow{q} G\ab \to 1.
+\]
 
@@
 \begin{remark}
-Note that when $\Hh^1(k,G\der) = 0$, as is the case when $G\der(\bFq)$ ``is simply connected,'' \todo{Can we make this more precise?} then $\CCSiso{G} \iso G(\Fq)^*$, so
-we succeed in geometrizing characters of $G(k)$ on the nose.
+Note that when $\Hh^1(k,G\der) = 0$ then $\CCSiso{G} \iso G(\Fq)^*$, so
+we succeed in geometrizing characters of $G(k)$ on the nose.  This condition will be satisfied
+when $G\der(\bFq) = \underline{G}(K)$ for a simply connected group $\underline{G}$ over a local field $K$.
 \end{remark}

### 2016-04-18 followup.tex
Catching up at home.

@@
 \end{align*}
-We require that the following diagram of Weil local systems on $H \times G\times G$ commutes: %\todo{Something's wrong: the top left actually requires $a \circ c_2 = m \circ c_1$, which isn't true.}
+We require that the following diagram of Weil local systems on $H \times G\times G$ commutes: 
 \begin{equation}\label{ECS1}

### 2016-04-18 followup.tex
Expanded on the proof of Lemma 2.4.

--- 2016-04-17 followup.tex
@@
 \begin{proof}
+Suppose $S_G(\cs{L}) = [\alpha\oplus \beta]\in \Hh^2(E_G^\bullet)$.
+As above, pick $a \in Z^2(\bG, \EEx)$ corresponding to $\alpha$. 
 We can use \'etale descent to see that pullback by the Lang isogeny defines an equivalence
-of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.  Thus every character
-sheaf on $G$ arises through the Lang isogeny; since the covering group is $G(k)$, which is commutative,
-every character sheaf on $G$ is commutative. \todo{why does this imply that the sheave is commutative in our sense?}
+of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.  
+Thus every character sheaf $\cs{L}$ on $G$ arises through the Lang isogeny, together with a character $G(\Fq) \to \EEx$.
+Pushing forward the Lang isogeny along this character defines an extension of $\bG$ by $\EEx$, and thus $a\in Z^2(\bG, \EEx)$ whose class is fixed by Frobenius.
+Then $a$ corresponds to $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$, as above.
+Since the covering group of the Lang isogeny is $G(k)$, which is commutative, then the class of this extension satisfies $a(x,y) = a(y,x)$ for all $x,y \in \bG$. 
+This shows that $S_{G}(\cs{L}$ is symmetric.
+It follows from Lemma~\ref{lem:symccslink} that $\cs{L}$ is a commutative character sheaf.
 \end{proof}
@@
 Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
-Let $a : H \times G\to G$ be a group action compatible with the group structure on $G$ and write $p : H\times G \to G$ for projection. 
+Let $a : H \times G\to G$ be an action of $H$ on $G$ 
+%group action compatible with the group structure on $G$ 
+and write $p : H\times G \to G$ for projection. 
 Consider the morphisms
@@
 This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.
+The reader will recognize this notion as the Weil sheaf version of equivariant sheaves for the action $a$ of $H$ on $G$, as can be found, for example, in \cite{bernstein-lunts:equivariant}*{0.2}.
 
 \subsubsection{Equivariant linear character sheaves}\label{ssec:equivariant2}
+
+With reference to Section~\ref{ssec:equivariant1}, suppose now that $H$ acts on $G$ through group homomorphisms, so $a(h)(m(g_1,g_2)) = m(a(h)(g_1), a(h)(g_2))$.
 
@@
 \end{equation}
+Note that $a\circ c_2 = m\circ c_1$ precisely because $H$ acts on $G$ through group homomorphisms.
 
@@
 Fix an isomorphism $\CC \approx \EE$ so that we may mix classical and geometric facts. 
-One begins by observing that $S_0$ is the domain of the Cayley transform $\cay : g \mapsto (g-1)^{-1}(g+1)$ on $\Sp(V)$ and that if $(g,v,z) \in S_0\times V\times Z$ then
+Observe that $S_0$ is the domain of the Cayley transform $\cay : g \mapsto (g-1)^{-1}(g+1)$ on $\Sp(V)$.
+If $(g,v,z) \in S_0\times V\times Z$ then
 \begin{equation}\label{Cayley}
@@
  where $\gamma_\psi$ is the Gauss sum for $\psi$ and $\sigma : \Fq^\times \to \EE^\times$ is the quadratic character of $\Fq^\times$.
-By a simple adaptation of what in \cite{gurevich-hadani:07a}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize the function in \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}_0$ (in fact, a Weil local system) on $S_0 \times V^\sharp$ such that
-\[
+By a simple adaptation of what in \cite{gurevich-hadani:07a}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}_0$ (in fact, a Weil local system) on $S_0 \times V^\sharp$ such that
+$
 \trFrob{\cs{K}_0(\frac{\dim V}{2})} = \trace(W_\psi)\vert_{S_0\times V^\sharp},
-\]
+$
 where $\cs{K}_0(\frac{\dim V}{2})$ is the Tate twist of $\cs{K}$.
@@
 It follows from \cite{gurevich-hadani:07a} that 
-\[
+$
 \trFrob{\cs{K}_\psi} = \trace(W_\psi).
-\]
+$
 Then $\cs{K}_\psi$ is the promised Weil sheaf complex.

### 2016-04-19 followup.tex
Small changes to Section 3.

--- 2016-04-17 followup.tex
@@
 \]
-Since $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ canonically, and since $i^*(\cs{L}^\vee) \cong \cs{L}$ canonically, this defines the promised isomorphism
+Applying the canonical isomorphisms $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ and $i^*(\cs{L}^\vee) \cong \cs{L}$, this map provides the promised isomorphism
 \[
@@
   \]
-Here $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ above.
+Here $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ above. \todo{Why not use $\gamma$ directly instead of $\beta$?}
 \end{definition}
@@
 Note that when $\Hh^1(k,G\der) = 0$ then $\CCSiso{G} \iso G(\Fq)^*$, so
-we succeed in geometrizing characters of $G(k)$ on the nose.  This condition will be satisfied
-when $G\der(\bFq) = \underline{G}(K)$ for a simply connected group $\underline{G}$ over a local field $K$.
+we succeed in geometrizing characters of $G(k)$ on the nose.
 \end{remark}

### 2016-04-19 followup.tex
Changes through Section 3 and the beginning of Section 4.

@@
 
-With reference to Section~\ref{ssec:equivariant1}, suppose now that $H$ acts on $G$ through group homomorphisms, so $a(h)(m(g_1,g_2)) = m(a(h)(g_1), a(h)(g_2))$.
+With reference to Section~\ref{ssec:equivariant1}, suppose now that $H$ acts on $G$ through group homomorphisms: $a(h, m(g_1,g_2)) = m(a(h, g_1), a(h, g_2))$.
 
@@
 p_2 : H\times G\times H\times G &\to G\times G \\
-(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2).
+(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2) \\
+\theta_2 : H \times G \times H \times G &\to H \times G \times H \times G \\
+(h_1,g_1,h_2,g_2) &\mapsto (h_2,g_2,h_1,g_1).
 \end{align*}
@@
 This diagram also shows that $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of equivariant sheaves, since it satisfies \eqref{E3} as it applies here.
-The proof that $\theta^*(\cs{L}\boxtimes\cs{L})$ is also straightforward, since $a_2\circ \theta = \theta_2 \circ a_2$ and $p_2\circ \theta = \theta_2 \circ p_2$ for the obvious $\theta_2$.
+The proof that $\theta^*(\cs{L}\boxtimes\cs{L})$ is $H\times H$ equivariant is also straightforward, since $a_2\circ \theta_2 = \theta \circ a_2$ and $p_2\circ \theta_2 = \theta \circ p_2$.
 Let $\nu_2 : a_2^*(\cs{L}\boxtimes\cs{L}) \to p_2^*(\cs{L}\boxtimes\cs{L})$ be the middle horizontal isomorphism of Weil local systems, above. 
-Then, to see that
+To see that
 \[
@@
 \]
-Let $\cs{L}_0$ be a linear character sheaf on $Q$.
+Let $(\cs{L}_0, \mu_0)$ be a linear character sheaf on $Q$ and set $(\cs{L}, \mu) \ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$.
 Consider the functor
@@
 \]
-given on objects by $(\cs{L}_0,\mu_0) \mapsto (q^*\cs{L}_0, (q\times q)^* \mu_0)$; see \cite{cunningham-roe:13a}*{Lem 1.4}.
+given on objects by $(\cs{L}_0,\mu_0) \mapsto (\cs{L}, \mu)$; see \cite{cunningham-roe:13a}*{Lem 1.4}.
 %To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$, verify \cite{cunningham-roe:13a}, CS.3], arguing as in \cite{cunningham-roe:13a}].
-This linear character sheaf $(\cs{L},\mu)\ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$ on $G$ comes equipped with the canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of canonical isomorphisms.
+The linear character sheaf $(\cs{L},\mu)$ on $G$ comes equipped with a canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of isomorphisms.
 \[
@@
 With this description of $q_H^*: \CS(Q)\to \CS_H(G)$ is is easy to see that it is an equivalence.
-Its adjoint is given on objects by $(\cs{L},\mu,\nu) \mapsto (R_1(\cs{L},\nu), R_2(\nu))$, making use of Lemma~\ref{lem:HH}, and on morphisms by $\alpha \mapsto R_1(\alpha)$.
+Its adjoint is given on objects by $(\cs{L},\mu,\nu) \mapsto (R_1(\cs{L},\nu), R_2(\mu))$, making use of Lemma~\ref{lem:HH}, and on morphisms by $\alpha \mapsto R_1(\alpha)$.
 The adjunction is built from the adjunctions $(\epsilon_1, \eta_1)$ and $(\epsilon_2, \eta_2)$ for $(L_1,R_1)$ and $(L_2, R_2)$.
@@
 
-We now suppose that $j : H \hookrightarrow G$ is a closed subgroup scheme over $\Fq$ and that the action $a : H\times G\to G$ is obtained by restricting the action $m : G \times G\to G$ to $H\times G$.
-%Then we have the diagram
-%\[
-%\begin{tikzcd}
-%\ &  \arrow{dl}[swap]{a} H \times G \arrow{dr}{p} \arrow{dd}[swap]{f} & \\
-%G & & G \\
-%& \arrow{ul}{m} G \times G \arrow{ur}[swap]{p_2} & 
-%\end{tikzcd}
-%\]
+We now suppose that $j : H \hookrightarrow G$ is a closed subgroup scheme over $\Fq$
+and that the action $a : H\times G\to G$ is obtained by restricting the action
+$m : G \times G\to G$ to $H\times G$.  In this context, we are able to replace
+$\nu : a^*\cs{L} \to p^*\cs{L}$ with an isomorphism $\beta : \cs{L}_H \to (\EE)_H$.
+Let $\CS^H(G)$ be the category of triples $(\cs{L},\mu,\beta)$ with $(\cs{L},\mu) \in \CS(G)$
+and $\beta : \cs{L}\vert_H \to (\EE)_H$ an isomorphism in $\CS(H)$;
+a morphism $(\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ in $\CS^H(G)$ is a morphism
+$\alpha: \cs{L} \to \cs{L}'$ in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{H}$.
+
+\begin{lemma}\label{lem:beta}
+If $H\hookrightarrow G$ is a closed subgroup scheme over $\Fq$ then $\CS_H(G)$ is equivalent to $\CS^H(G)$.
+\end{lemma}
+\begin{proof}
 Define $f : H\times G \to G\times G$ by $f(h,g) = (j(h),g)$ and note that $a = m\circ f$.
-Every $H$-equivariant linear character sheaf $(\cs{L},\mu, \nu)$ uniquely determines an isomorphism 
-$
-\beta : \cs{L}\vert_H \to (\EE)_{H}
-$
-by 
-\begin{equation}\label{betanu}
-\nu = (\beta \boxtimes \id) \circ  f^*\mu,
-\end{equation}
-or more precisely, by the following diagram of isomorphisms, where we write $p_1: G\times G\to G$ for projection to the first component and $p_2 : G\times G \to G$ for projection to the second.
+Write $p_1: G\times G\to G$ for projection to the first component and $p_2 : G\times G \to G$ for projection to the second.
+We may pass between $\nu$ and $\beta$ via the following diagram.
 \[
@@
 \]
-In this way we see we may replace $(\cs{L},\mu,\nu)$ with a triple, $(\cs{L},\mu,\beta)$, from which $(\cs{L},\mu,\nu)$ may be recovered.
-The next lemma makes that statement more precise.
-
-\begin{lemma}\label{lem:beta}
-If $H\hookrightarrow G$ is a closed subgroup scheme over $\Fq$ then
-$\CS_H(G)$ is equivalent to the category $\CS^H(G)$ of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu)\in \CS(G)$ and $\beta : \cs{L}\vert_H \to (\EE)_H$ is an isomorphism in $\CS(H)$; a morphism $(\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ in $\CS^H(G)$ is a morphism $\alpha: \cs{L} \to \cs{L}'$ in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{H}$.
-\end{lemma}
-
-\begin{proof}
-We have seen how every $(\cs{L},\mu,\nu)\in \CS_H(G)$ determines an isomorphism of Weil local systems $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$.
-This isomorphism is constrained by the conditions 
-appearing in \eqref{E1}, \eqref{E2} and \eqref{ECS1}.
-It is a straightforward, tedious exercise to show that those conditions are exactly equivalent to the condition
-that the isomorphism of Weil local systems $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is an isomorphism in the category of of linear character sheaves on $H$.
+It is a straightforward, tedious exercise to show that the conditions \eqref{E1}, \eqref{E2} and \eqref{ECS1} 
+on $\nu$ are equivalent to the condition that the isomorphism of Weil local systems
+$\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is an isomorphism in the category of of linear character sheaves on $H$.
 \end{proof}
@@
 
-%\begin{proof}[Proof of Proposition~\ref{prop:Gder_triv}] 
-By \cite{demazure:SGA3-VIA}*{Thm. 3.2}, the abelianization $G\ab\ceq G/G\der$ exists in schemes over $\Fq$ and the quotient $q: G \to G\ab$ is a $G\der$-torsor in the fppf topology.
-%
 To simplify notation below, set $H=G\der$
@@
 Then $j^*(\cs{L},\mu) \iso j^*q^*(\cs{L}\ab,\mu\ab)$ in $\CS(H)$. 
-Since $g\circ j = 1$, it follows that $\cs{L}\vert_{G\der} \to (\EE)_{H}$ in $\CS(H)$.
+Since $q\circ j = 1$, it follows that $\cs{L}\vert_{G\der} \to (\EE)_{H}$ in $\CS(H)$.
 This completes the proof of Proposition~\ref{prop:Gder_triv}.
@@
 Since the comparison functor $\CS(G\ab) \to \CS_{H}(G)$ is an equivalence, it determines a full subcategory $\CCS_{H}(G)$ which is equivalent to $\CCS(G\ab)$, as pictured below.
-The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of the equivalence $\CS_{H}(G) \to \CS'(G)$ is $\CCS(G)$.
+The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of $\CCS_H(G)$ under the equivalence $\CS_{H}(G) \to \CS'(G)$ is $\CCS(G)$.
 \[
@@
 
-Suppose $(\cs{L},\mu,\beta)\in \CS'(G)$ and $(\cs{L},\mu,\nu) = q^*(\cs{L}\ab,\mu\ab)$;
+Let $(\cs{L},\mu,\nu)$ be the image of $(\cs{L},\mu,\beta)\in \CS'(G)$ and of $(\cs{L}\ab,\mu\ab)$ under $q_H^*$;
 we must show that $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
-Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ as in Section~\ref{sec:comcom}.
+Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}\ab$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ as in Section~\ref{sec:comcom}.
 Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ as in Section~\ref{ssec:noncomdef}.
@@
 \]
-By Lemma~\ref{lem:HH}, we may interpret the diagram on the right, above, as a diagram in $\Loc_{H\times H}(G\times G)$.
+By Lemma~\ref{lem:HH}, we may interpret the diagram on the right as a diagram in $\Loc_{H\times H}(G\times G)$.
 By Lemma~\ref{lem:torsor}, this corresponds to a diagram in $\Loc(G\ab\times G\ab)$, necessarily the diagram on the left, above, and also that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes.
@@
 Here we shall use  \cite{bertapelle-gonzales:Greenberg} for the definition and fundamental properties of the Greenberg transform.
-Let $G$ be the Greenberg transform of $\underline{G}$; then $G$ is a group scheme over $\Fq$ and 
-\[
-G(\Fq) = \underline{G}(R)
-\]
-canonically.
+Let $G$ be the Greenberg transform of $\underline{G}$; then $G$ is a group scheme over $\Fq$ and there is a canonical isomorphism
+\[
+G(\Fq) = \underline{G}(R).
+\]
 
@@
 With notation as above, suppose $\Fq$ is a finite field.
-For every quasicharacter character $\varphi : \underline{G}(S) \to \EEx$ there is a Weil sheaf $\cs{L}$ on $G$ such that \[\trFrob{\cs{L}} =  \varphi.\] \end{proposition}
+For every quasicharacter character $\varphi : \underline{G}(S) \to \EEx$ \todo{What is $S$?} there is a Weil sheaf $\cs{L}$ on $G$ such that \[\trFrob{\cs{L}} =  \varphi.\] \end{proposition}
 
@@
 set $G_m = \Gr_m^{R}(\underline{G})$, the Greenberg transform of $\underline{G}\times_{\Spec{R}}\Spec{R_m}$.
-Then $G_m$ is a smooth group scheme over $\Fq$ and $G_m(\Fq) = \underline{G}(R_m)$, canonically.
-Using Theorem~\ref{thm:geo}, let $\cs{L}_m$ be a geometrization of the character $\varphi_m: G_m \to \EEx$; so
+Then $G_m$ is a smooth group scheme over $\Fq$ and $G_m(\Fq) = \underline{G}(R_m)$.
+Using Theorem~\ref{thm:geo}, let $\cs{L}_m$ be a geometrization of the character $\varphi_m: G_m(\Fq) \to \EEx$; so
 \[
@@
 %
-Recall that the full Greenberg transform $G \ceq \Gr^{R}(\underline{G})$ is a group scheme over $\Fq$ such that $G(\Fq) = \underline{G}(\Fq)$, canonically, and comes equipped with a morphism $G \to G_m$.
+Recall that the full Greenberg transform $G \ceq \Gr^{R}(\underline{G})$ is a group scheme over $\Fq$ such that $G(\Fq) = \underline{G}(R)$; it comes equipped with a morphism $G \to G_m$.
 Let $\cs{L}$ be the  Weil sheaf on $G$ obtained from $\cs{L}_m$ by pullback along $G \to G_m$. 
@@
 Let $V$ be a finite-dimensional vector space over a finite field $\Fq$ equipped with a symplectic paring $\langle\ ,\ \rangle : V\times V \to Z$, where $Z$ is a one-dimensional vector space over $\Fq$.
-Let $V^\sharp$ be the Heisenberg group determined by $(Z, \langle\ ,\ \rangle)$.
-Then $V^\sharp$ is a split extension of $V$ by $Z$.
+Let $V^\sharp$ be the Heisenberg group determined by $(Z, \langle\ ,\ \rangle)$. \todo{We should include a reference defining the Heisenberg group}
+Then $V^\sharp$ is a split extension of $V$ by $Z$. \todo{split in what category?}
 Let $\Sp(V)$ be the symplectic group determined by the symplectic pairing $\langle\ ,\ \rangle$; this group acts on $V^\sharp$.
@@
 
-Let $\psi : Z \to \CC^\times$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi$. 
+Let $\psi : Z \to \EEx$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi$. 
 The Heisenberg representation determines a representation $\pi_{\psi}$ of $\Sp(V)$ with the same representation space as $\omega_\psi$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\psi(g)$ determines an isomorphism of representations $\omega_\psi^g \to \omega_\psi$.
@@
 
-The character $\trace(W_\psi) : \Sp(V)\ltimes V^\sharp \to \EE^\times$ of $W_\psi$ is studied in \cite{howe:73a}, where is it shown that $\trace(W_\psi)$ is determined by $\psi$ and its restriction to $\Sp(V)$ and, moreover, that $\trace(W_\psi)(g,v,z) =0$ unless $v\in \ker(g-1)$, in which case $(g,v,z)$ lies in a conjugacy class intersecting $\Sp(V) \ltimes Z$.
+The character $\trace(W_\psi) : \Sp(V)\ltimes V^\sharp \to \EE^\times$ of $W_\psi$ is studied in \cite{howe:73a}, where is it shown that $\trace(W_\psi)$ is determined by its restriction to $\Sp(V)$ and by $\psi$.
+Moreover, $\trace(W_\psi)(g,v,z) =0$ unless $v\in \ker(g-1)$, in which case $(g,v,z)$ lies in a conjugacy class intersecting $\Sp(V) \ltimes Z$.
 %
@@
 %the boundary of $S_0$ is $\cup_{0< r\leq \dim V} S_r$. 
- From \cite{howe:73a}*{Prop. 2} we learn that if $g\in S_r$ then $q^{-r/2} \trace(W_\psi)(g)$ has complex norm $1$.
-
-It is one of the main results of \cite{gurevich-hadani:07a} (see also \cite{gurevich-hadani:11a}*{Thm. 4.5}) that there is a Weil sheaf complex $\cs{K}_\psi$ on $\Sp(V)\ltimes V^\sharp$ such that 
+ From \cite{howe:73a}*{Prop. 2} we learn that if $g\in S_r$ then $q^{-r/2} \trace(W_\psi)(g)$ has complex norm $1$. \todo{We should say something about $\CC$ vs $\EE$}
+
+It is one of the main results of \cite{gurevich-hadani:07a} \todo{Can we give a specific reference here?} (see also \cite{gurevich-hadani:11a}*{Thm.
+4.5}) that there is a Weil sheaf complex $\cs{K}_\psi$ on $\Sp(V)\ltimes V^\sharp$ such that
 \begin{equation}
@@
 %
-Since $\cs{K}_\psi$ is an object in Deligne's category $D^b_c(\Sp(V)\ltimes V^\sharp,\EE)$, the left hand since of this equality must be interpreted accordingly.
-
-Although nothing more that this statement will be needed below, the construction of $\cs{K}_\psi$ is so unbelievably gorgeous that we can't resist saying a few extra words about it here.
-The reader pressed for time is invited to skip the next paragraph without loosing anything needed for the arguments in the rest of Section~\ref{sec:types}.
+Since $\cs{K}_\psi$ is an object in Deligne's category $D^b_c(\Sp(V)\ltimes V^\sharp,\EE)$, the left hand side of this equality must be interpreted accordingly.
+Although only the existence of $\cs{K}_\psi$ will be needed below, we recall its construction briefly.
 
@@
  where $\gamma_\psi$ is the Gauss sum for $\psi$ and $\sigma : \Fq^\times \to \EE^\times$ is the quadratic character of $\Fq^\times$.
-By a simple adaptation of what in \cite{gurevich-hadani:07a}*{Appendix B.1} are called the non-normalized kernels and the normalization coefficients, it is easy to geometrize \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}_0$ (in fact, a Weil local system) on $S_0 \times V^\sharp$ such that
-$
+An adaptation of the non-normalized kernels and the normalization coefficients \cite{gurevich-hadani:07a}*{Appendix B.1} allows for the geometrization of \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}_0$ (in fact, a Weil local system) on $S_0 \times V^\sharp$ such that
+\[
 \trFrob{\cs{K}_0(\frac{\dim V}{2})} = \trace(W_\psi)\vert_{S_0\times V^\sharp},
-$
+\]
 where $\cs{K}_0(\frac{\dim V}{2})$ is the Tate twist of $\cs{K}$.
 %
-Next, one forms $\cs{K}_\psi \ceq j_{!*} \cs{K}_0[\dim V]$, the perverse extension of $\cs{K}_0 [\dim V]$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$; recall that $S_0$ is Zariski dense in $\Sp(V)$.
-It follows from \cite{gurevich-hadani:07a} that 
-$
-\trFrob{\cs{K}_\psi} = \trace(W_\psi).
-$
-Then $\cs{K}_\psi$ is the promised Weil sheaf complex.
+We set $\cs{K}_\psi \ceq j_{!*} \cs{K}_0[\dim V]$, the perverse extension of $\cs{K}_0 [\dim V]$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$.
 

### 2016-04-19 followup.tex
Deleting extraneous exposition in 4.2; adding references

@@
 Let $R$ be a complete discrete valuation ring with maximal ideal $\mathfrak{m}$ and perfect residue field $\Fq$. 
-Then $\Spec{R}$ is a henselian trait.
 Let $\underline{G}$ be a smooth group scheme over $R$.
@@
 With notation as above, suppose $\Fq$ is a finite field.
-For every quasicharacter character $\varphi : \underline{G}(S) \to \EEx$ \todo{What is $S$?} there is a Weil sheaf $\cs{L}$ on $G$ such that \[\trFrob{\cs{L}} =  \varphi.\] \end{proposition}
+For every quasicharacter character $\varphi : \underline{G}(R) \to \EEx$ there is a Weil sheaf $\cs{L}$ on $G$ such that \[\trFrob{\cs{L}} =  \varphi.\] \end{proposition}
 
 \begin{proof}
-By continuity of $\varphi : \underline{G}(S) \to \EE^\times$, there is some $m \in \NN$ and a factorization
+By continuity of $\varphi : \underline{G}(R) \to \EE^\times$, there is some $m \in \NN$ and a factorization
 \[
@@
 Let $V$ be a finite-dimensional vector space over a finite field $\Fq$ equipped with a symplectic paring $\langle\ ,\ \rangle : V\times V \to Z$, where $Z$ is a one-dimensional vector space over $\Fq$.
-Let $V^\sharp$ be the Heisenberg group determined by $(Z, \langle\ ,\ \rangle)$. \todo{We should include a reference defining the Heisenberg group}
-Then $V^\sharp$ is a split extension of $V$ by $Z$. \todo{split in what category?}
+Let $V^\sharp$ be the Heisenberg group determined by $(Z, \langle\ ,\ \rangle)$ \cite{gurevich-hadani:07a}*{\S 1.1}.
 Let $\Sp(V)$ be the symplectic group determined by the symplectic pairing $\langle\ ,\ \rangle$; this group acts on $V^\sharp$.
@@
 
-Let $\psi : Z \to \EEx$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi$. 
+Let $\psi : Z \to \EEx$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi$ \cite{gurevich-hadani:07a}*{\S 1.1}. 
 The Heisenberg representation determines a representation $\pi_{\psi}$ of $\Sp(V)$ with the same representation space as $\omega_\psi$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\psi(g)$ determines an isomorphism of representations $\omega_\psi^g \to \omega_\psi$.
-Let $W_\psi = \pi_\psi \ltimes \omega_\psi$ be the representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$ given by $\omega_\psi$ and $\pi_\psi$.
-
-The character $\trace(W_\psi) : \Sp(V)\ltimes V^\sharp \to \EE^\times$ of $W_\psi$ is studied in \cite{howe:73a}, where is it shown that $\trace(W_\psi)$ is determined by its restriction to $\Sp(V)$ and by $\psi$.
-Moreover, $\trace(W_\psi)(g,v,z) =0$ unless $v\in \ker(g-1)$, in which case $(g,v,z)$ lies in a conjugacy class intersecting $\Sp(V) \ltimes Z$.
-%
-The group $\Sp(V)$ is naturally stratified into the conjugation-stable subvarieties $S_r = \{ g\in \Sp(V) \tq \dim \ker (g-1) = r \}$. 
-The big stratum, $S_0$, is dense in $\Sp(V)$.
-%the boundary of $S_0$ is $\cup_{0< r\leq \dim V} S_r$. 
- From \cite{howe:73a}*{Prop. 2} we learn that if $g\in S_r$ then $q^{-r/2} \trace(W_\psi)(g)$ has complex norm $1$. \todo{We should say something about $\CC$ vs $\EE$}
-
-It is one of the main results of \cite{gurevich-hadani:07a} \todo{Can we give a specific reference here?} (see also \cite{gurevich-hadani:11a}*{Thm.
-4.5}) that there is a Weil sheaf complex $\cs{K}_\psi$ on $\Sp(V)\ltimes V^\sharp$ such that
+Let $W_\psi = \pi_\psi \ltimes \omega_\psi$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$ given by $\omega_\psi$ and $\pi_\psi$ \cite{gurevich-hadani:07a}*{\S 2.2}.
+
+There is a Weil sheaf complex $\cs{K}_\psi$ on $\Sp(V)\ltimes V^\sharp$ \cite{gurevich-hadani:07a}*{Thm 3.2.2.1} (see also \cite{gurevich-hadani:11a}*{Thm. 4.5}) such that 
 \begin{equation}
@@
 Since $\cs{K}_\psi$ is an object in Deligne's category $D^b_c(\Sp(V)\ltimes V^\sharp,\EE)$, the left hand side of this equality must be interpreted accordingly.
-Although only the existence of $\cs{K}_\psi$ will be needed below, we recall its construction briefly.
-
-Fix an isomorphism $\CC \approx \EE$ so that we may mix classical and geometric facts. 
-Observe that $S_0$ is the domain of the Cayley transform $\cay : g \mapsto (g-1)^{-1}(g+1)$ on $\Sp(V)$.
-If $(g,v,z) \in S_0\times V\times Z$ then
-\begin{equation}\label{Cayley}
-\trace(W_\psi)(g,v,z) =  \frac{\gamma_\psi^{\dim V}}{q^{\dim V/2} } \sigma(\det(1+\cay(g)))\ \psi\left(\langle \cay(g)v,v\rangle/4 \right) \psi(z),
-\end{equation}
- where $\gamma_\psi$ is the Gauss sum for $\psi$ and $\sigma : \Fq^\times \to \EE^\times$ is the quadratic character of $\Fq^\times$.
-An adaptation of the non-normalized kernels and the normalization coefficients \cite{gurevich-hadani:07a}*{Appendix B.1} allows for the geometrization of \eqref{Cayley} with a $\Sp(V)\ltimes V^\sharp$-equivariant irreducible Weil sheaf $\cs{K}_0$ (in fact, a Weil local system) on $S_0 \times V^\sharp$ such that
-\[
-\trFrob{\cs{K}_0(\frac{\dim V}{2})} = \trace(W_\psi)\vert_{S_0\times V^\sharp},
-\]
-where $\cs{K}_0(\frac{\dim V}{2})$ is the Tate twist of $\cs{K}$.
-%
-We set $\cs{K}_\psi \ceq j_{!*} \cs{K}_0[\dim V]$, the perverse extension of $\cs{K}_0 [\dim V]$ along $j : S_0 \times V^\sharp \hookrightarrow \Sp(V) \ltimes V^\sharp$.
 

### 2016-05-14 followup.tex
Deleting a subsection, adding comment on invisible character sheaves

@@
 
-\subsection{Eliminating Invisible Character Sheaves}\label{ssec:defect}
-
 In \cite{cunningham-roe:13a}*{Thm. 3.6}, we showed that $\TrFrob{G} : \CSiso{G} \to G(k)^*$ is surjective and
@@
 Then $a$ corresponds to $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$, as above.
-Since the covering group of the Lang isogeny is $G(k)$, which is commutative, then the class of this extension satisfies $a(x,y) = a(y,x)$ for all $x,y \in \bG$. 
-This shows that $S_{G}(\cs{L}$ is symmetric.
+Since the covering group of the Lang isogeny is $G(k)$, which is commutative, the class of this extension satisfies $a(x,y) = a(y,x)$ for all $x,y \in \bG$. 
+This shows that $S_{G}(\cs{L})$ is symmetric.
 It follows from Lemma~\ref{lem:symccslink} that $\cs{L}$ is a commutative character sheaf.
@@
 Since $\Hh^0(\Weil{},\Hh^2(\bG,\EEx))$ is not necessarily trivial \cite{cunningham-roe:13a}*{Ex. 2.10}, the functor
-$\CCS(G) \to \CS(G)$ is not an equivalence of categories in general. 
+$\CCS(G) \to \CS(G)$ is not necessarily essentially surjective.  Indeed, the invisible character sheaves \cite{cunningham-roe:13a}*{Def. 2.8}
+defined in our previous paper are precisely those non-commutative character sheaves with trivial trace of Frobenius.
 \end{remark}

### 2016-05-14 followup.tex
Working on introduction

@@
 
-In previous work \cite{cunningham-roe:13a}, we generalized the function-sheaf dictionary from connected, commutative, algebraic groups over a finite field $k$ to smooth commutative group schemes $G$ over $k$.
-Writing $G(k)^*$ for $\Hom(G(k), \EEx)$, we described a category $\CS(G)$ of \emph{character sheaves} on $G$ and a surjective homomorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$.
-In contrast to the connected case, $\TrFrob{G}$ may have nontrivial kernel; we gave an explicit description of its kernel as $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$ \cite{cunningham-roe:13a}*{Thm. 3.6}.
+The function-sheaf dictionary over a finite field $k$ \cite{deligne:SGA4.5}*{Sommes trig.}
+provides a way of encoding functions on the $k$-rational points of an algebraic group $G$
+as $\ell$-adic local systems on $G$.  More specifically, if $G$ is a connected, commutative, algebraic group
+then there is a certain category $\CS(G)$ of rank-one local systems on $G$ and an
+explicit isomorphism between $G(k)^* \ceq \Hom(G(k), \EEx)$ and isomorphism classes
+of objects in $\CS(G)$.  Objects in $\CS(G)$ are referred to as \emph{character sheaves};
+the isomorphism is given by mapping a character sheaf $\cs{L}$ to the function
+$g \mapsto \Tr(\Frob{} \vert \cs{L}_g)$.
+
+In previous work \cite{cunningham-roe:13a}, we generalized the function-sheaf dictionary to
+smooth commutative group schemes $G$, allowing for non-connected groups.
+We gave a description of the category $\CS(G)$ of character sheaves in this context, as well
+as the isomorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$.
+In contrast to the connected case, $\TrFrob{G}$ may have nontrivial kernel;
+we gave an explicit description of its kernel as $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$ \cite{cunningham-roe:13a}*{Thm. 3.6}.
 

### 2016-05-18 followup.tex
Update bibliography, add a couple notes

@@
 \newcommand{\trFrob}[1]{t_{#1}}
-\newcommand{\TrFrob}[1]{\operatorname{Tr}_{#1}}
+\DeclareMathOperator{\Tr}{Tr}
+\newcommand{\TrFrob}[1]{\Tr_{#1}}
 %% Limits
@@
 
-The first aim of this paper is to repair this defect in the function-sheaf dictionary for characters of smooth commutative group schemes $G$ by describing a full subcategory $\CCS(G)$ of $\CS(G)$ so that $\TrFrob{G}$ restricts to an isomorphism $\CCSiso{G} \to G(k)^*$.
+The first aim of this paper is to repair this defect in the function-sheaf dictionary
+ by describing a full subcategory $\CCS(G)$ of $\CS(G)$ so that $\TrFrob{G}$ restricts to an isomorphism $\CCSiso{G} \to G(k)^*$.
 We refer to the resulting objects as \emph{commutative character sheaves}, since the passage from $\CS(G)$ to $\CCS(G)$ involves a condition that exchanges the inputs to the multiplication morphism on $G$ (see Definition \ref{def:CCScom}).
@@
 using character sheaves \cite{lusztig:85a}*{Def.~2.10}.  Instead, we focus on the group of $1$-dimensional characters
-$G(k)^*$, assuming that $G$ is smooth, but not that it is connected or reductive.
+$G(k)^*$, assuming that $G$ is smooth, but not that it is connected, reductive or commutative. \todo{Is there a relationship with Lusztig's character sheaves that we can easily summarize?}
 The category $\CS(G)$ has a straightforward generalization to this case, but again
@@
 
+\bib{deligne:SGA4.5}{book}{
+	address = {Berlin},
+	author = {Pierre Deligne},
+	publisher = {{Springer-Verlag}},
+	series = {Lecture Notes in Mathematics},
+	title = {{Cohomologie \'etale}},
+	volume = {569},
+	year = {1977},
+}
+
 \bib{demazure:SGA3-VIA}{inproceedings}{

### 2016-05-20 followup.tex
Removing todo notes and small change to Lemma 2.4.

@@
 
- \todo{There are some grammatical errors in this paragraph, and I'm not 100\% sure how they should be corrected}
-
 We are extremely grateful to Loren Spice for explaining Yu's theory of types to us.
@@
 Suppose $S_G(\cs{L}) = [\alpha\oplus \beta]\in \Hh^2(E_G^\bullet)$.
-As above, pick $a \in Z^2(\bG, \EEx)$ corresponding to $\alpha$. 
 We can use \'etale descent to see that pullback by the Lang isogeny defines an equivalence
@@
 Thus every character sheaf $\cs{L}$ on $G$ arises through the Lang isogeny, together with a character $G(\Fq) \to \EEx$.
-Pushing forward the Lang isogeny along this character defines an extension of $\bG$ by $\EEx$, and thus $a\in Z^2(\bG, \EEx)$ whose class is fixed by Frobenius.
-Then $a$ corresponds to $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$, as above.
+Pushing forward the Lang isogeny along this character defines an extension of $\bG$ by $\EEx$ whose class is fixed by Frobenius; let $a\in Z^2(\bG, \EEx)$ be a representative $2$-cocycle.
+Then $a$ corresponds to the $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$, above. \todo{Check this.}
 Since the covering group of the Lang isogeny is $G(k)$, which is commutative, the class of this extension satisfies $a(x,y) = a(y,x)$ for all $x,y \in \bG$. 
@@
   \]
-Here $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ above. \todo{Why not use $\gamma$ directly instead of $\beta$?}
+Here $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ above. 
 \end{definition}

### 2016-05-20 followup.tex
Made the connection to Lusztig, in the introduction.

@@
 Next, we broaden our scope further to encompass smooth group schemes $G$ over $\Fq$ that are not necessarily commutative.
-In this paper, we do not consider Lusztig's geometrization for characters of representations of connected, reductive groups $G(k)$
-using character sheaves \cite{lusztig:85a}*{Def.~2.10}.  Instead, we focus on the group of $1$-dimensional characters
-$G(k)^*$, assuming that $G$ is smooth, but not that it is connected, reductive or commutative. \todo{Is there a relationship with Lusztig's character sheaves that we can easily summarize?}
+We assume $G$ is smooth, but not that it is connected, reductive or commutative. 
 The category $\CS(G)$ has a straightforward generalization to this case, but again
@@
 essentially surjective, missing the kinds of linear character sheaves highlighted by Kamgarpour.
-
-Finally, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected reductive groups over $p$-adic fields fields.
+%
+
+In order to further justify referring to objects in $\CCS(G)$ as commutative character sheaves,
+suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
+In this case, every object in $\CCS(G)$ is a Frobenius-stable character sheaf on $G$ in the sense of \cite{lusztig:85a}*{Def.~2.10}.
+Moreover, if $A$ is a character sheaf on $G$ in this sense, and if the characteristic function of $A$ is a character of $G(k)$, then the dictionary determines an object in $\CCS(G)$ from $A$.
+These two rules determine an injection from $\CCSiso{G}$ to isomorphism classes of Frobenius-stable character sheaves on $G$.
+Accordingly, we may refer to character sheaves on $G$ that arise in this manner as commutative character sheaves.
+Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups.
+
+As an application, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected reductive groups over $p$-adic fields fields.
 In this way, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:

### 2016-05-20 followup.tex
Isomorphism changed to epimorphism, in the introduction.

@@
 We gave a description of the category $\CS(G)$ of character sheaves in this context, as well
-as the isomorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$.
+as an epimorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$. \todo{Changed isomorphism to epimorphism.}
 In contrast to the connected case, $\TrFrob{G}$ may have nontrivial kernel;
@@
 Accordingly, we may refer to character sheaves on $G$ that arise in this manner as commutative character sheaves.
-Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups.
+Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields.
 

### 2016-05-21 followup.tex
Further changes to introduction.

@@
 When $G$ is connected, all character sheaves on $G$ are commutative.
-This category clarifies several questions about character sheaves on $G$.
-Invisible character sheaves \cite{cunningham-roe:13a}*{Def.
+This category clarifies several questions about $\CS(G)$.
+\todo{Small change here.} Invisible character sheaves \cite{cunningham-roe:13a}*{Def.
 2.8} are precisely those $\cs{L}$ with $\TrFrob{G}(\cs{L}) = 1$ that are not commutative.
@@
 
-In order to further justify referring to objects in $\CCS(G)$ as commutative character sheaves,
-suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
-In this case, every object in $\CCS(G)$ is a Frobenius-stable character sheaf on $G$ in the sense of \cite{lusztig:85a}*{Def.~2.10}.
-Moreover, if $A$ is a character sheaf on $G$ in this sense, and if the characteristic function of $A$ is a character of $G(k)$, then the dictionary determines an object in $\CCS(G)$ from $A$.
-These two rules determine an injection from $\CCSiso{G}$ to isomorphism classes of Frobenius-stable character sheaves on $G$.
-Accordingly, we may refer to character sheaves on $G$ that arise in this manner as commutative character sheaves.
-Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields.
-
 As an application, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected reductive groups over $p$-adic fields fields.
@@
 virtual Weil perverse sheaves on group schemes over finite fields.
+
+In order to provide further justification for referring to objects in $\CCS(G)$ as commutative character sheaves, suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
+In this case, it can be shown that there is a forgetful functor taking every object in $\CCS(G)$ to a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}, for which the characteristic function is a character of $G(k)$.
+Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields,
+but they are precisely the part needed to describe characters of such groups.
+\bigskip
 
@@
 Then in Section \ref{ssec:proofs}, we give proofs of the results in Section \ref{sec:noncom}, which require a development of equivariant linear character sheaves.
-
+\todo{There was a paragraph break here.
+Why?}
+% 
 In Section~\ref{sec:types} we give an application of Theorem~\ref{thm:geo} by geometrizing types for supercuspidal representations of $p$-adic groups.
@@
 These elements are pulled together in Section~\ref{ssec:geotypes}, where the proof Theorem~\ref{thm:geotypes} is given.
+\bigskip
 

### 2016-05-21 followup.tex
Getting ready to talk.

@@
 In order to provide further justification for referring to objects in $\CCS(G)$ as commutative character sheaves, suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
-In this case, it can be shown that there is a forgetful functor taking every object in $\CCS(G)$ to a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}, for which the characteristic function is a character of $G(k)$.
+In this case, it can be shown that there is a forgetful functor taking every object in $\CCS(G)$ to a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}.
 Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields,

### 2016-05-21 followup.tex
Changes to introduction

--- 2016-05-20 followup.tex
@@
 the isomorphism is given by mapping a character sheaf $\cs{L}$ to the function
-$g \mapsto \Tr(\Frob{} \vert \cs{L}_g)$.
+$\TrFrob{G} : g \mapsto \Tr(\Frob{} \vert \cs{L}_g)$.
 
@@
 We gave a description of the category $\CS(G)$ of character sheaves in this context, as well
-as an epimorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$. \todo{Changed isomorphism to epimorphism.}
+as the homomorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$.
 In contrast to the connected case, $\TrFrob{G}$ may have nontrivial kernel;
@@
 Next, we broaden our scope further to encompass smooth group schemes $G$ over $\Fq$ that are not necessarily commutative.
-We assume $G$ is smooth, but not that it is connected, reductive or commutative. 
+In this paper, we do not consider Lusztig's geometrization for characters of representations of connected, reductive groups $G(k)$
+using character sheaves \cite{lusztig:85a}*{Def.~2.10}.  Instead, we focus on the group of $1$-dimensional characters
+$G(k)^*$, assuming that $G$ is smooth, but not that it is connected, reductive or commutative. \todo{Is there a relationship with Lusztig's character sheaves that we can easily summarize?}
 The category $\CS(G)$ has a straightforward generalization to this case, but again
@@
 essentially surjective, missing the kinds of linear character sheaves highlighted by Kamgarpour.
-%
-
-In order to further justify referring to objects in $\CCS(G)$ as commutative character sheaves,
-suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
-In this case, every object in $\CCS(G)$ is a Frobenius-stable character sheaf on $G$ in the sense of \cite{lusztig:85a}*{Def.~2.10}.
-Moreover, if $A$ is a character sheaf on $G$ in this sense, and if the characteristic function of $A$ is a character of $G(k)$, then the dictionary determines an object in $\CCS(G)$ from $A$.
-These two rules determine an injection from $\CCSiso{G}$ to isomorphism classes of Frobenius-stable character sheaves on $G$.
-Accordingly, we may refer to character sheaves on $G$ that arise in this manner as commutative character sheaves.
-Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields.
-
-As an application, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected reductive groups over $p$-adic fields fields.
+
+Finally, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected reductive groups over $p$-adic fields fields.
 In this way, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:
@@
 Suppose $S_G(\cs{L}) = [\alpha\oplus \beta]\in \Hh^2(E_G^\bullet)$.
+As above, pick $a \in Z^2(\bG, \EEx)$ corresponding to $\alpha$. 
 We can use \'etale descent to see that pullback by the Lang isogeny defines an equivalence
@@
 Thus every character sheaf $\cs{L}$ on $G$ arises through the Lang isogeny, together with a character $G(\Fq) \to \EEx$.
-Pushing forward the Lang isogeny along this character defines an extension of $\bG$ by $\EEx$ whose class is fixed by Frobenius; let $a\in Z^2(\bG, \EEx)$ be a representative $2$-cocycle.
-Then $a$ corresponds to the $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$, above. \todo{Check this.}
+Pushing forward the Lang isogeny along this character defines an extension of $\bG$ by $\EEx$, and thus $a\in Z^2(\bG, \EEx)$ whose class is fixed by Frobenius.
+Then $a$ corresponds to $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$, as above.
 Since the covering group of the Lang isogeny is $G(k)$, which is commutative, the class of this extension satisfies $a(x,y) = a(y,x)$ for all $x,y \in \bG$. 
@@
   \]
-Here $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ above. 
+Here $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ above. \todo{Why not use $\gamma$ directly instead of $\beta$?}
 \end{definition}

### 2016-05-21 followup.tex

--- 2016-05-21 followup.tex
@@
 We gave a description of the category $\CS(G)$ of character sheaves in this context, as well
-as an epimorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$. \todo{Changed isomorphism to epimorphism.}
+as an epimorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$.
 In contrast to the connected case, $\TrFrob{G}$ may have nontrivial kernel;
@@
 These elements are pulled together in Section~\ref{ssec:geotypes}, where the proof Theorem~\ref{thm:geotypes} is given.
+
 \bigskip

### 2016-05-21 followup.tex
Merged two sections in the application.

@@
 This category clarifies several questions about $\CS(G)$. 
-\todo{Small change here.} Invisible character sheaves \cite{cunningham-roe:13a}*{Def.
+Invisible character sheaves \cite{cunningham-roe:13a}*{Def.
 2.8} are precisely those $\cs{L}$ with $\TrFrob{G}(\cs{L}) = 1$ that are not commutative.
@@
 Then in Section \ref{ssec:proofs}, we give proofs of the results in Section \ref{sec:noncom}, which require a development of equivariant linear character sheaves. 
-\todo{There was a paragraph break here.
-Why?}
 % 
@@
 As preparation for the proof, we review some facts about the Heisenberg-Weil representation and its geometrization, in Section~\ref{ssec:Jacobi}.
-Then, in Section~\ref{ssec:review}, we review Yu's theory of types and his study of smooth integral models, in Section~\ref{ssec:models}.  
+Then, in Section~\ref{ssec:review}, we review Yu's theory of types and his study of smooth integral models.  
 These elements are pulled together in Section~\ref{ssec:geotypes}, where the proof Theorem~\ref{thm:geotypes} is given.
@@
 Pushing forward the Lang isogeny along this character defines an extension of $\bG$ by $\EEx$ whose class is fixed by Frobenius; let $a\in Z^2(\bG, \EEx)$ be a representative $2$-cocycle.
-Then $a$ corresponds to the $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$, above. \todo{Check this.}
+Then $a$ corresponds to the $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$, above. 
 Since the covering group of the Lang isogeny is $G(k)$, which is commutative, the class of this extension satisfies $a(x,y) = a(y,x)$ for all $x,y \in \bG$. 
@@
 In this section we offer an application of Theorem~\ref{thm:geo}, by showing that Yu types are geometrizable, subject to a very mild hypothesis.
-The proof of that statement, made precise in Theorem~\ref{thm:geotypes}, requires: the geometrization of the character of the Heisenberg-Weil representation over finite fields (Section~\ref{ssec:Jacobi}); a review of some basic properties of Yu types (Section~\ref{ssec:review}); a review of some facts from Yu's notes on smooth integral models (Section~\ref{ssec:models}); and the geometrization of characters of representations of reductive groups over finite fields with cyclic geometric component groups, using Lusztig's character sheaves on these groups.
+The proof of that statement, made precise in Theorem~\ref{thm:geotypes}, requires: the geometrization of the character of the Heisenberg-Weil representation over finite fields (Section~\ref{ssec:Jacobi}); a review of some basic properties of Yu types (Section~\ref{ssec:review}); a review of some facts from Yu's notes on smooth integral models (Section~\ref{ssec:review}); and the geometrization of characters of representations of reductive groups over finite fields with cyclic geometric component groups, using Lusztig's character sheaves on these groups.
 These pieces are assembled in Section~\ref{ssec:geotypes}.
@@
 
-\subsection{Review of Yu's types}\label{ssec:review}
+\subsection{Review of Yu's types and associated models}\label{ssec:review}
 
@@
 
-\subsection{Review of Yu's smooth models}\label{ssec:models}
+%\subsection{Review of Yu's smooth models}\label{ssec:review}
 
@@
 \end{quotation}
-In this section we explain the first sentence; in Section~\ref{ssec:geotypes} we follow the suggestion in the second sentence.
+We now explain the first sentence; in Section~\ref{ssec:geotypes} we follow the suggestion in the second sentence.
 
@@
 \begin{theorem}\label{thm:geotypes}
-Let $(C,\rho)$ be a Yu type, constructed as in Section~\ref{ssec:review}.
-Let $G^0 = \Gr_{R}(\underline{G}^0)$ be the Greenberg transform of the smooth group scheme $\underline{G}^0$ appearing in Section~\ref{ssec:models}.
+Let $(C,\rho)$ be a Yu type and let $G^0 = \Gr_{R}(\underline{G}^0)$ be the Greenberg transform of the smooth group scheme $\underline{G}^0$ appearing in Section~\ref{ssec:review}.
 Assume $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
@@
 
-Consider the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ and the Heisenberg-Weil representation $W_{i+1}$ appearing in Section~\ref{ssec:models}.
+Consider the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ and the Heisenberg-Weil representation $W_{i+1}$ appearing in Section~\ref{ssec:review}.
 Let $\cs{K}^{i+1}$ be the Weil sheaf on the Jacobi group, recalled in Section~\ref{ssec:Jacobi}, such that
@@
 \]
-Recall from Section~\ref{ssec:models} that $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ is a quotient of the special fibre of the smooth group scheme $\underline{G}^{i} \ltimes \underline{J}^{i+1}$.
+Recall from Section~\ref{ssec:review} that $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ is a quotient of the special fibre of the smooth group scheme $\underline{G}^{i} \ltimes \underline{J}^{i+1}$.
 Let $\cs{K}_0^{i+1}$ be the Weil sheaf on the special fibre of $\underline{G}^{i} \ltimes \underline{J}^{i+1}$ obtained from $W_{i+1}$ by pullback. 

### 2016-05-21 followup.tex
Added a bit more detail to the introduction regarding CCS and LCS.

@@
 In order to provide further justification for referring to objects in $\CCS(G)$ as commutative character sheaves, suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
-In this case, it can be shown that there is a forgetful functor taking every object in $\CCS(G)$ to a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}.
+Let $\gcs{L}$ be the geometric part of an object in $\CCS(G)$; see Section~\ref{sec:defs}.
+Let $T$ be a maximal torus in $\bG$ and let $\gcs{L}_T$ be the restriction of $\gcs{L}$ to $T$.
+Then $\gcs{L}$ appears in the semisimple complex $\operatorname{ind}_{B,T}^{\bG}(\gcs{L}_T)$.
+It follows that every object in $\CCS(G)$ determines Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}.
 Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields,

### 2016-05-21 followup.tex
Small fixes to intro

--- 2016-05-21 followup.tex
@@
 
-As an application, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected reductive groups over $p$-adic fields fields.
+As an application, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected, reductive groups over $p$-adic fields.
 In this way, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:
@@
 Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields,
-but they are precisely the part needed to describe characters of such groups.
+but they are precisely the part needed to describe one dimensional characters of such groups.
 \bigskip

### 2016-05-21 followup.tex
Small updates to new intro paragraph

@@
 Then $\gcs{L}$ appears in the semisimple complex $\operatorname{ind}_{B,T}^{\bG}(\gcs{L}_T)$.
-It follows that every object in $\CCS(G)$ determines Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}.
-Of course, such sheaves represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields,
-but they are precisely the part needed to describe one dimensional characters of such groups.
+It follows that every object in $\CCS(G)$ determines a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}.
+Of course, the sheaves arising in this way represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields:
+they are precisely those needed to describe one dimensional characters of such groups.
 \bigskip

### 2016-05-23 followup.tex
Minor change - shift.
Added keywords, hyphenated one-dimensional to be consistent with the Abstract.

@@
 \subjclass[2010]{14F05 (primary), 14L15, 22E50}
-\keywords{character sheaves}
+\keywords{function-sheaf dictionary, commutative character sheaves, types for supercuspidal representations}
 
@@
 Let $T$ be a maximal torus in $\bG$ and let $\gcs{L}_T$ be the restriction of $\gcs{L}$ to $T$.
-Then $\gcs{L}$ appears in the semisimple complex $\operatorname{ind}_{B,T}^{\bG}(\gcs{L}_T)$.
+Then the perverse sheaf $\gcs{L}[\dim G]$ appears in the semisimple complex $\operatorname{ind}_{B,T}^{\bG}(\gcs{L}_T)$ produced by parabolic induction.
 It follows that every object in $\CCS(G)$ determines a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}.
 Of course, the sheaves arising in this way represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields:
-they are precisely those needed to describe one dimensional characters of such groups.
+they are precisely those needed to describe one-dimensional characters of such groups.
 \bigskip
@@
 
-We are extremely grateful to Loren Spice for explaining Yu's theory of types to us.
+We are extremely grateful to Loren Spice for explaining Yu's types for supercuspidal representations.
 We also thank Masoud Kamgarpour for helpful conversations.

### 2016-05-28 followup-arXiv-1.tex
arxiv version

--- 2016-05-23 followup.tex
@@
 \begin{tikzcd}
-\arrow[equal]{d} c^* (\cs{L}\vert_{G\der}) \arrow{r}{c^*(\beta)} 
-	&  c^*((\EE)_{G\der}) \arrow[equal]{d} \\
+\arrow{d} c^* (\cs{L}\vert_{G\der}) \arrow{r}{c^*(\beta)} 
+	&  c^*((\EE)_{G\der}) \arrow{d} \\
 \arrow{d}[swap]{j\circ c = m \circ (m \times m')} c^* j^* \cs{L} 
@@
 	&  m^*\cs{L} \otimes \theta^* m^* i^* \cs{L}  \arrow[dashed]{u}[swap]{\gamma'} \\
-(m \times m')^* (\cs{L} \boxtimes \cs{L}) \arrow[equal]{r} 
+(m \times m')^* (\cs{L} \boxtimes \cs{L}) \arrow{r}
 	& m^*\cs{L} \otimes (m')^*\cs{L} \arrow{u}[swap]{m' = i\circ m\circ \theta} 
@@
 H \times H \times G 
-\arrow[shift left=4]{r}{b_1, b_2, b_3} 
+\arrow{r}{b_1, b_2, b_3} 
 \arrow{r}{}
-\arrow[shift right=4]{r}{} 
+\arrow{r}{} 
 & H \times G 
-\arrow[shift left=2]{r}{a}
-\arrow[shift right=2]{r}[swap]{p}
+\arrow{r}{a}
+\arrow{r}[swap]{p}
  & G 
@@
 H\times G
- \arrow[shift left=2]{r}{a}
-  \arrow[shift right=2,swap]{r}{p}
+ \arrow{r}{a}
+  \arrow[swap]{r}{p}
 &
@@
 \begin{tikzcd}[column sep=40]
-a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{r}{\nu} &  \arrow[equal]{d} p^*\cs{L} \\
+a^*\cs{L} \arrow{d} \arrow[dashed]{r}{\nu} &  \arrow{d} p^*\cs{L} \\
 a^* ( q^*\cs{L}_0) \arrow{r}{q\circ a = q\circ p}
@@
 then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha$ is a morphism in $\CS(G)$.
-%\todo{I find myself having to make many references to \cite{cunningham-roe:13a}] and promising that the results there adapt to the noncommutative group case.
-It makes me uneasy, but the alternative is to actually repeat the proofs here, with the weaker hypothesis on $G$, which would be ugly.
-I'm just agonizing out loud, I guess.}
 These simple observations define the comparison functor
@@
 pages = {1--37},
-numpages = {37},
+%numpages = {37},
 doi = {10.1017/S1474748015000286},

### 2016-06-19 followup.tex
Minor wording changes

@@
 \]
-where $\Delta_G$ denotes the image of the connecting homomorphism $G\ab(\Fq) \to \Hh^1(\Fq, G\der)$. 
+where $\Delta_G$ is the image of the connecting homomorphism $G\ab(\Fq) \to \Hh^1(\Fq, G\der)$. 
 Thus the category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the following sense: for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $(\cs{L},\mu,\beta)$ in $\CCS(G)$ such that $\trFrob{\cs{L}} = \chi$.
@@
 \]
-By Lemma~\ref{lem:HH}, we may interpret the diagram on the right as a diagram in $\Loc_{H\times H}(G\times G)$.
+By Lemma~\ref{lem:HH}, we may interpret the diagram on the right in $\Loc_{H\times H}(G\times G)$.
 By Lemma~\ref{lem:torsor}, this corresponds to a diagram in $\Loc(G\ab\times G\ab)$, necessarily the diagram on the left, above, and also that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes.
@@
 pages = {1--37},
-numpages = {37},
 doi = {10.1017/S1474748015000286},

### 2016-06-19 Geometric types.tex

--- 2016-05-23 followup.tex
@@
 
-\title[Commutative Character Sheaves]{The dictionary for characters of smooth group schemes}
+\title[Commutative character sheaves and the geometrization of types]{Commutative character sheaves and the geometrization of types for supercuspidal representations}
 \author{Clifton Cunningham}
@@
 \begin{abstract}
-We describe a function-sheaf dictionary for one-dimensional characters of arbitrary smooth group schemes over finite fields.  
-In previous work, we considered the case of commutative smooth group schemes and found that the standard definition of character sheaves produced a dictionary with a nontrivial kernel.  
+We begin by describing a function-sheaf dictionary for one-dimen\-sion\-al characters of arbitrary smooth group schemes over finite fields.  
+In previous work we considered the case of commutative smooth group schemes and found that the standard definition of character sheaves produced a dictionary with a nontrivial kernel.  
 In this paper we give a modification of the category of character sheaves that remedies this defect, and is also extensible to non-commutative groups.  
-As an application, we use these \emph{commutative character sheaves} to geometrize types for supercuspidal representations of $p$-adic groups.
+Then, as an application, we use these \emph{commutative character sheaves} to geometrize the types for supercuspidal representations of $p$-adic groups appearing in the work of Jiu-Kang Yu.
+This application also uses Lusztig's character sheaves on disconnected reductive algebraic groups over finite fields.
 \end{abstract}
@@
 \section*{Introduction}
+
+Regarding the construction of the type $(C,\rho)$, the paper \cite{yu:03a} concludes with the following observation.
+\begin{quotation}
+{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
+ the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
+These results suggest that algebraic geometry and group schemes should play an
+important role in the representation theory of $p$-adic groups.} %\cite{yu:03a}
+\end{quotation}
+We now explain the first sentence; in Section~\ref{ssec:geotypes} we follow the suggestion in the second sentence.
 
@@
 
-As an application, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected, reductive groups over $p$-adic fields.
+Finally, as an application, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected, reductive groups over $p$-adic fields as they appear in the work of Jiu-Kang Yu.
 In this way, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:

### 2016-06-28 Geometric types.tex

@@
 
-\title[Commutative character sheaves and the geometrization of types]{Commutative character sheaves and the geometrization of types for supercuspidal representations}
+\title[Commutative character sheaves and geometric types]{Commutative character sheaves and geometric types for supercuspidal representations}
 \author{Clifton Cunningham}
@@
 
+\renewcommand{\O}{{\mathcal{O}}}
+\newcommand{\oK}{{\,^\circ \hskip-1pt K}}
+\newcommand{\orho}{{\,^\circ \hskip-1pt \rho}}
+
 %% Hyphenation override
@@
 \begin{abstract}
-We begin by describing a function-sheaf dictionary for one-dimen\-sion\-al characters of arbitrary smooth group schemes over finite fields.  
+We show that the types for supercuspidal representations of tamely ramified $p$-adic groups that appear in Jiu-Kang Yu's work are geometrizable, subject to a mild hypothesis.
+To do this we must find the function-sheaf dictionary for one-dimen\-sion\-al characters of arbitrary smooth group schemes over finite fields.  
 In previous work we considered the case of commutative smooth group schemes and found that the standard definition of character sheaves produced a dictionary with a nontrivial kernel.  
 In this paper we give a modification of the category of character sheaves that remedies this defect, and is also extensible to non-commutative groups.  
-Then, as an application, we use these \emph{commutative character sheaves} to geometrize the types for supercuspidal representations of $p$-adic groups appearing in the work of Jiu-Kang Yu.
-This application also uses Lusztig's character sheaves on disconnected reductive algebraic groups over finite fields.
+We then use these \emph{commutative character sheaves} to geometrize the linear characters that appear in the types introduced by Jiu-Kang Yu.
+We then combine this with Lusztig's character sheaves on reductive algebraic groups over finite fields, and the geometrization of the Weil representation found by Gurevich and Hadani, to find \emph{geometric types} for supercuspidal representations of tamely ramified $p$-adic groups.
 \end{abstract}
@@
 
-Regarding the construction of the type $(C,\rho)$, the paper \cite{yu:03a} concludes with the following observation.
+As proved by Ju-Lee Kim in \cite{kim:07a}, all irreducible supercuspidal representations of tamely ramified $p$-adic groups can be built from the datum introduced by Jiu-Kang Yu in \cite{yu:01a}*{\S 15}.
+While the type, in the sense of Bushnell \& Kutzko \cite{bushnell-kutzko:98a}, of a supercuspidal representation built from Yu datum can be constructed directly from the datum, it is convenient to consider and intermediate object, introduced in \cite{yu:01a}*{Remark 15.4}, which we call a \emph{Yu type datum}.
+Yu type data are studied in \cite{Yu:models}, which concludes with the following observation.
+%
 \begin{quotation}
-{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
+{\it Therefore, up to some linear characters, all the ingredient representations [appearing in Yu type data] are on groups of
  the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
 These results suggest that algebraic geometry and group schemes should play an
-important role in the representation theory of $p$-adic groups.} %\cite{yu:03a}
+important role in the representation theory of $p$-adic groups.} %\cite{Yu:models}
 \end{quotation}
-We now explain the first sentence; in Section~\ref{ssec:geotypes} we follow the suggestion in the second sentence.
+%
+In this paper we follow the suggestion above by showing that Yu type data are geometrizable, in the following sense.
+A Yu type datum determines a sequence $(\oK^i,\orho_i)$, for $i=0, \ldots, d$, of types for supercuspidal representations of a sequence of $p$-adic groups.
+The main result of \cite{Yu:models} explains how to find a smooth group scheme over $\O$ to with $ \underline{G}^i(\O)=\,^\circ K^i $, where $\O$ is the ring of integers of the $p$-adic field.
+In this paper we show in Theorem~\ref{thm:geotypes} that if the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic, then each type $(\oK^i,\orho_i)$ in this sequence can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$,
+where $\cs{F}^i$ is a virtual Weil sheaf on the Greenberg transform $G^i$ of $\underline{G}^i$, such that 
+\begin{equation}\label{eqn:intro1}
+\trFrob{\cs{F}^i} = \trace(\,^\circ\rho_i),
+\end{equation}
+where $\trFrob{\cs{F}^i}$ refers to the function on $G^i(k) = \underline{G}^i(\OK) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the virtual complex $\cs{F}^i$.
+\[
+\begin{tikzcd}
+(\oK^i,\orho_i) \arrow[bend left, dashed]{rrr}{\text{geometrization}} &&& \arrow[bend left, dashed]{lll}{\text{trace of Frob.}}
+(\underline{G}^i, \cs{F}^i),
+\end{tikzcd}
+\]
+%Theorem~\ref{thm:geotypes} shows how to construct the virtual Weil sheaf $\cs{F}^i$ from the Yu type datum, so that \eqref{eqn:intro1} holds.
+We refer to the pairs $(\underline{G}^i, \cs{F}^i)$ as \emph{geometric types} for supercuspidal representations.
+
+In order to prove Theorem~\ref{thm:geotypes}, we must address the lacuna highlighted in the quote from \cite{Yu:models}, above; namely, we must find a way to geometrize linear characters of groups of the form $\underline{H}(\O)$, where $\underline{H}$ is a smooth group scheme over $\O$.
+In order to do this is a systematic manner, we begin this paper by finding the function-sheaf dictionary for characters of arbitrary smooth group schemes over finite fields. 
+When coupled with the Greenberg transform, this will allow for the geometrization of linear characters of $\underline{H}(\O)$.
 
@@
 
-The first aim of this paper is to repair this defect in the function-sheaf dictionary
+We repair this defect in the function-sheaf dictionary
  by describing a full subcategory $\CCS(G)$ of $\CS(G)$ so that $\TrFrob{G}$ restricts to an isomorphism $\CCSiso{G} \to G(k)^*$.
@@
 
-Finally, as an application, we use the category $\CCS(G)$ to give a geometric description of types for supercuspidal representations of connected, reductive groups over $p$-adic fields as they appear in the work of Jiu-Kang Yu.
-In this way, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:
-virtual Weil perverse sheaves on group schemes over finite fields.
-
 In order to provide further justification for referring to objects in $\CCS(G)$ as commutative character sheaves, suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
@@
 they are precisely those needed to describe one-dimensional characters of such groups.
+
+Armed with the function-sheaf dictionary for smooth group schemes over finite fields, we may return to the task of geometrizing Yu type data. 
+The proof of Theorem~\ref{thm:geotypes} requires: Yu's work on smooth integral models \cite{Yu:models}; the geometrization of the character of the Heisenberg-Weil representation over finite fields by Gurevich \& Hadani \cite{gurevich-hadani:07a}; Lusztig's character sheaves on reductive groups over finite fields; and finally, the function-sheaf dictionary for characters of smooth group schemes over finite fields, now at our disposal in Theorem~\ref{thm:geo}.
+These pieces are assembled in Section~\ref{ssec:geotypes}, to prove Theorem~\ref{thm:geotypes}.
+In this way, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:
+virtual Weil perverse sheaves on group schemes over finite fields.
+
+The hypothesis in Theorem~\ref{thm:geotypes} -- that the geometric component group of the reductive quotient of the special fibre of the smooth group scheme $\underline{G}^0$ appearing in the Yu type datum is cyclic --  is required only because Lusztig's theory of character sheaves has the same hypothesis.
+If Lusztig's theory of character sheaves can be generalized to all disconnected reductive algebraic groups, then the hypothesis in Theorem~\ref{thm:geotypes} can be removed.
 \bigskip
@@
 $[\cs{L}]$ to $[\alpha \oplus \beta]$, where $E_G^\bullet$ is the total space of the zeroth page
-of the Hochschild-Serre spectral sequence, $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$ is obtained from $\mu$ and
-$\beta \in C^1(\Weil{}, C^1(\bG, \EEx))$ is obtained from $\phi$.
+of the Hochschild-Serre spectral sequence, $\alpha \in \oK^0(\Weil{}, \oK^2(\bG, \EEx))$ is obtained from $\mu$ and
+$\beta \in \oK^1(\Weil{}, \oK^1(\bG, \EEx))$ is obtained from $\phi$.
 
@@
 Pushing forward the Lang isogeny along this character defines an extension of $\bG$ by $\EEx$ whose class is fixed by Frobenius; let $a\in Z^2(\bG, \EEx)$ be a representative $2$-cocycle.
-Then $a$ corresponds to the $\alpha \in C^0(\Weil{}, C^2(\bG, \EEx))$, above. 
+Then $a$ corresponds to the $\alpha \in \oK^0(\Weil{}, \oK^2(\bG, \EEx))$, above. 
 Since the covering group of the Lang isogeny is $G(k)$, which is commutative, the class of this extension satisfies $a(x,y) = a(y,x)$ for all $x,y \in \bG$. 
@@
 
-For the rest of Section~\ref{sec:types}, $K$ is a $p$-adic field.
-
-A Yu type is a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$,  constructed from the following information, derived from a Yu datum:
+For the rest of Section~\ref{sec:types}, $K$ is a $p$-adic field and $R$ is the ring of integers of $K$.
+A Yu type datum consists of the following:
 \begin{enumerate}
-\labitem{Y0}{Y0} a sequence of compact groups $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$;
-\labitem{Y1}{Y1} a continuous representation $\rho_0$ of $C^0$;
-\labitem{Y2}{Y2} quasicharacters $\varphi^i : C^i \to \CC^\times$, for $i=0, \ldots d$.
+\labitem{Y0}{Y0} a sequence of compact groups $\oK^0 \subseteq \oK^1 \subseteq \cdots \subseteq \oK^d = \oK$;
+\labitem{Y1}{Y1} a continuous representation $\orho^0$ of $\oK^0$;
+\labitem{Y2}{Y2} quasicharacters $\varphi^i : \oK^i \to \CC^\times$, for $i=0, \ldots d$.
 \end{enumerate}
-%
-The representation $\rho_0$ and the quasicharacters $(\varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho_i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho_d \otimes \varphi^d = \rho$ as representations of $C^d = C$.
-%
-Since we will need some facts about this construction in the proof of Theorem~\ref{thm:geotypes}, we review some further detail here.
+The representation $\orho^0$ and the quasicharacters $(\varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct the representations $\orho_i$ of $\oK^i$ that form the sequence of types $(\oK^i,\orho_i)$, for $i=1, \ldots, d$.
+%
+In order to prepare for the construction of the geometric types of Theorem~\ref{thm:geotypes}  we review some further detail here.
 In Table~\ref{table:notation} we explain how to convert the constructions appearing in this section into the notation of \cite{yu:01a}.
+
+\begin{table}[htp]
+\caption{Comparison with notation of \cite{yu:01a}}
+\begin{center}
+\begin{tabular}{c|l}
+%$\oK^0$ & $\,^\circ K^0 = G^0(F)_y$\\% \cite{yu:01a}*{\S 15} \\
+%$\oK^{i+1}$ & $\,^\circ K^{i+1} = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, \ldots, s_{i})}$\\% \cite{yu:01a}*{\S 15} \\
+%$\oK^0$ & $\,^\circ K^0 = G^0(F)_y$\\% \cite{yu:01a}*{\S 15} \\
+%$\orho^0$ & $\,^\circ \rho^0$\\% \cite{yu:01a}*{\S 15} \\
+%$\orho^{i+1}$ & $\,^\circ \rho^{i+1}$\\% \cite{yu:01a}*{\S 15} \\
+$\varphi^i$ & $\phi_i\vert_{\,^\circ K^i }$ \\
+$J_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}$ \\
+$V_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ (G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}$ \\ 
+$V_{i+1}^\sharp$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi}_i\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
+%$H^{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi_i}\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
+$Z_{i+1}$ & $\ker(V_{i+1}^\sharp\to V_{i+1})$ % \cite{yu:01a}*{\S 11} \\
+%$(f_{j+1}, j_{i+1})$ & $(f,j)$ \cite{yu:01a}*{\S 11} \\
+%$\langle\ ,\ \rangle_{i+1}$ & $\langle\ ,\ \rangle$, \cite{yu:01a}*{\S 11} 
+\end{tabular}
+\end{center}
+\label{table:notation}
+\end{table}%
 
@@
 \labitem{Y3}{Y3}
-compact groups $J_i\subset C$, for $i=0, \ldots d$, such that 
+compact groups $J_i\subset \oK$, for $i=0, \ldots d$, such that 
 $
-C^i = J_0\cdots J_{i}
+\oK^i = J_0\cdots J_{i}
 $ 
-and, for $i=0, \ldots d-1$, a natural action of $C^i$ on $J_{i+1}$ defining the groups $C^i \ltimes J_{i+1}$.
+and, for $i=0, \ldots d-1$, a natural action of $\oK^i$ on $J_{i+1}$ defining the groups $\oK^i \ltimes J_{i+1}$.
 \begin{equation}\label{eq:semiprod}
@@
 \ && 1 \arrow{d} && \\
-\ && C^{i}\cap J_{i+1}\arrow{d} && \\
-1 \arrow{r} & J_{i+1} \arrow{r} & C^i \ltimes J_{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} & 1\\
-&& C^{i+1} \arrow{d}{} && \\
+\ && \oK^{i}\cap J_{i+1}\arrow{d} && \\
+1 \arrow{r} & J_{i+1} \arrow{r} & \oK^i \ltimes J_{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & \oK^i \arrow{r} & 1\\
+&& \oK^{i+1} \arrow{d}{} && \\
 && 1 &&
@@
 \end{enumerate}
-%He then introduces the following quotients of $J_{i+1}$ and $C^i$, for $i=0, \ldots d-1$.
+%He then introduces the following quotients of $J_{i+1}$ and $\oK^i$, for $i=0, \ldots d-1$.
 %
@@
 %\item
-Finally, Yu constructs a group homomorphism $f_{i+1} : C^i \to \Sp(V_{i+1})$ such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $C^i$ on $H_{i+1}$ in the sense of \cite{yu:01a}.
+Finally, Yu constructs a group homomorphism $f_{i+1} : \oK^i \to \Sp(V_{i+1})$ such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $\oK^i$ on $H_{i+1}$ in the sense of \cite{yu:01a}.
 %
@@
 \begin{enumerate}
-\labitem{Y4}{Y4}  a group homomorphism $h_{i+1} : C^i \ltimes J_{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
-\[
-\begin{tikzcd}
-1 \arrow{r} & J_{i+1} \arrow{d} \arrow{r} & C^i \ltimes J_{i+1} \arrow{d}{h_{i+1}} \arrow{r}{p_i} & C^i \arrow{r} \arrow{d}{f_i} & 1\\ 
+\labitem{Y4}{Y4}  
+a group homomorphism $h_{i+1} : \oK^i \ltimes J_{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
+\[
+\begin{tikzcd}
+1 \arrow{r} & J_{i+1} \arrow{d} \arrow{r} & \oK^i \ltimes J_{i+1} \arrow{d}{h_{i+1}} \arrow{r}{p_i} & \oK^i \arrow{r} \arrow{d}{f_i} & 1\\ 
 1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
@@
 
-We can now recall how Yu uses all this to construct representations $\rho_i$ of $C^i$, for $i=1, \ldots, d$ and thus the type $(C,\rho) = (C^d,\rho_d\otimes \varphi^d)$.
-The representations $\rho_i$ are defined recursively. 
-For the base case $i=0$, the representation $\rho_0$ is just $\rho_0$; see \ref{Y1} above.
+We can now recall how Yu uses all this to construct representations $\orho^i$ of $\oK^i$, for $i=1, \ldots, d$ and the types $(\oK^i,\orho_i)$.
+The representations $\orho^i$ and $\orho_i$ are defined recursively.
+For the base case $i=0$, set $\orho_0 \ceq \orho^i\otimes \varphi^i$; see \ref{Y1} above.
 Now fix $i$.
 Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
-Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $C^i \ltimes J_{i+1}$.
-Write $\inf(\rho_i \otimes \varphi^i)$ for the representation of $C^i \ltimes J_{i+1}$ obtained by pulling back $\rho_i$ along $C^i \ltimes J_{i+1} \to C^i$. 
+Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $\oK^i \ltimes J_{i+1}$.
+Write $\inf(\orho_i)$ for the representation of $\oK^i \ltimes J_{i+1}$ obtained by pulling back $\orho^i$ along $\oK^i \ltimes J_{i+1} \to \oK^i$. 
 Consider the representation
 \begin{equation}\label{eq:tensor}
-\rho_{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\rho_i \otimes \varphi^i)
+\orho^{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\orho_i)
 \end{equation}
-of $C^i \ltimes J_{i+1}$.
+of $\oK^i \ltimes J_{i+1}$.
 %By construction, the character of this representation satisfies
 %\begin{equation}\label{eq:tilderho}
-%\trace({\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\rho_i)(p_i(y))\ \varphi^i(p_i(y))
+%\trace({\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\orho^i)(p_i(y))\ \varphi^i(p_i(y))
 %\end{equation}
-%for $y \in C^i \ltimes J_{i+1}$.
-By \cite{yu:01a}*{}, the representation $\rho_{i+1}$ of $C^i \ltimes J_{i+1}$ is trivial on $C^{i}\cap J_{i+1}$ so $\rho_{i+1}$ descends to $C^{i+1}$. 
-%
-This defines the representation $\rho_{i+1}$ of $C^{i+1}$.
-This completes the recursive definition of $\rho_d$. 
-Now set $\rho \ceq \rho_d\otimes \varphi^d$. 
-This is the representation of $C^d = C$ determining the Yu type $(C,\rho)$.
-%The character of $\rho_d$ on $C^d = C = J_0 \cdots J_d$ satisfies
+%for $y \in \oK^i \ltimes J_{i+1}$.
+By \cite{yu:01a}*{}, the representation $\orho^{i+1}$ of $\oK^i \ltimes J_{i+1}$ is trivial on $\oK^{i}\cap J_{i+1}$ so $\orho^{i+1}$ descends to $\oK^{i+1}$. 
+%
+Set $\orho_{i+1} = \orho^{i+1}\otimes \varphi^{i+1}$.
+This completes the recursive definition of the Yu $(\oK^i,\orho_i)$ for $i=0, \ldots , d$.
+%The character of $\orho^d$ on $\oK^d = C = J_0 \cdots J_d$ satisfies
 %\[
-%\trace(\rho)(k_0 \cdots k_d) = \rho_0(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
+%\trace(\rho)(k_0 \cdots k_d) = \orho^0(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
 %\]
@@
 
-\begin{table}[htp]
-\caption{Comparison with notation of \cite{yu:01a}}
-\begin{center}
-\begin{tabular}{c|l}
-$C^0$ & $\,^\circ K^0 = G^0(F)_y$\\% \cite{yu:01a}*{\S 15} \\
-$\rho_0$ & $\,^\circ \rho^0$\\% \cite{yu:01a}*{\S 15} \\
-$C^{i+1}$ & $\,^\circ K^{i+1} = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, \ldots, s_{i})}$\\% \cite{yu:01a}*{\S 15} \\
-$\rho_{i+1}$ & $\,^\circ \rho^{i+1}$\\% \cite{yu:01a}*{\S 15} \\
-$\varphi^i$ & $\phi_i\vert_{\,^\circ K^i }$ \\
-$J_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}$ \\
-$V_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ (G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}$ \\ 
-$V_{i+1}^\sharp$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi}_i\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
-%$H^{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi_i}\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
-$Z_{i+1}$ & $\ker(V_{i+1}^\sharp\to V_{i+1})$ % \cite{yu:01a}*{\S 11} \\
-%$(f_{j+1}, j_{i+1})$ & $(f,j)$ \cite{yu:01a}*{\S 11} \\
-%$\langle\ ,\ \rangle_{i+1}$ & $\langle\ ,\ \rangle$, \cite{yu:01a}*{\S 11} 
-\end{tabular}
-\end{center}
-\label{table:notation}
-\end{table}%
-
 %\subsection{Review of Yu's smooth models}\label{ssec:review}
-
-Regarding the construction of the type $(C,\rho)$, the paper \cite{yu:03a} concludes with the following observation.
-\begin{quotation}
-{\it Therefore, up to some linear characters, all the ingredient representations are on groups of
- the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
-These results suggest that algebraic geometry and group schemes should play an
-important role in the representation theory of $p$-adic groups.} %\cite{yu:03a}
-\end{quotation}
-We now explain the first sentence; in Section~\ref{ssec:geotypes} we follow the suggestion in the second sentence.
 
@@
 %\labitem{M1}{M1}
-By \cite{yu:03a}*{Prop 10.2} there is a sequence  
+By \cite{Yu:models}*{Prop 10.2} there is a sequence  
 \[
@@
 \]
-of morphisms of affine smooth group schemes of finite type over $R$ such that, on $R$-points it gives the sequence $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$ above.
-Indeed, this is the main result of \cite{yu:03a}.
+of morphisms of affine smooth group schemes of finite type over $R$ such that, on $R$-points it gives the sequence $\oK^0 \subseteq \oK^1 \subseteq \cdots \subseteq \oK^d$ above.
+Indeed, this is the main result of \cite{Yu:models}.
 
 %\labitem{M2}{M2}
-As explained in \cite{yu:03a}*{\S 10.4}, there is morphism of affine smooth group schemes of finite type over $R$ 
+As explained in \cite{Yu:models}*{\S 10.4}, there is morphism of affine smooth group schemes of finite type over $R$ 
 \[
@@
 \] 
-for each $i=0,\ldots d$, such that $\underline{J}^i(R) = J_i$ as a subgroup of $C$ and such that the image of the $R$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $C^i$, for $i=0, \ldots , d$.
+for each $i=0,\ldots d$, such that $\underline{J}^i(R) = J_i$ as a subgroup of $C$ and such that the image of the $R$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $\oK^i$, for $i=0, \ldots , d$.
 %\labitem{M3}{M3}
@@
 \]
-gives $(\underline{G}^i \ltimes \underline{J}^{i+1})(R) = C^i \ltimes J_{i+1}$
+gives $(\underline{G}^i \ltimes \underline{J}^{i+1})(R) = \oK^i \ltimes J_{i+1}$
 %\end{enumerate}
@@
 \labitem{M0}{M0}
-The compact groups $C^i$ have been replaced by the smooth group schemes $\underline{G}^i$.
+The compact groups $\oK^i$ have been replaced by the smooth group schemes $\underline{G}^i$.
 \labitem{M1}{M1}
-The continuous representation $\rho_0$ of $C^0$ is a representation of $\underline{G}^0(R)$ obtained by inflation along $\underline{G}^0(R) \to \underline{G}^0(\Fq)$ from a representation $\varrho_0$ of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
+The continuous representation $\orho^0$ of $\oK^0$ is a representation of $\underline{G}^0(R)$ obtained by inflation along $\underline{G}^0(R) \to \underline{G}^0(\Fq)$ from a representation $\varrho_0$ of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
 In fact, $\varrho_0$ is itself obtained by pulling back a representation $\varrho_0^\reductive$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
@@
 
+This brings us back to \cite{Yu:models}*{\S 10.5} as quoted in the Introduction to this paper.
+
 \subsection{Geometrization of characters of types}\label{ssec:geotypes}
@@
 \begin{theorem}\label{thm:geotypes}
-Let $(C,\rho)$ be a Yu type and let $G^0 = \Gr_{R}(\underline{G}^0)$ be the Greenberg transform of the smooth group scheme $\underline{G}^0$ appearing in Section~\ref{ssec:review}.
+Let $\oK^i$ $\orho^0$, $\varphi^i$, for $i=0, \ldots d$, be a Yu type datum as in Section~\ref{ssec:review}, \ref{Y0}, \ref{Y1} and \ref{Y2}.
+Let $\underline{G}^i$ and $\varrho_0\red$ be as in Section~\ref{ssec:review}, \ref{M0} and \ref{M1}.
 Assume $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
-Then there is a virtual Weil sheaf complex $\cs{A}$ on $G = \Gr_{R}(\underline{G})$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
+For $i=0, \ldots ,d$, let $G^i = \Gr_{R}(\underline{G}^i)$ be the Greenberg transform of the smooth group scheme $\underline{G}^i$ appearing in Section~\ref{ssec:review}.
+Then there is a virtual Weil sheaf complex $\cs{F}_i$ on $G^i$ such that $\trFrob{\cs{F}_i} = \trace(\orho_i)$, for $i=0, \ldots , d$.
 \end{theorem}
@@
 For every $i=0, \ldots ,d$, set $G^i = \Gr_{R}(\underline{G}^i)$.
-Recall that $G^i(\Fq) = \underline{G}^i(R) = C^i$, canonically.
+Recall that $G^i(\Fq) = \underline{G}^i(R) = \oK^i$, canonically.
 We begin with an argument already employed in the proof of Proposition~\ref{prop:quasicharacters}.
@@
 \begin{tikzcd}
-G^0(\Fq) \arrow{rr}{\trace(\rho_0)} \arrow{rd} && \EE \\
-& G_m^0(\Fq) \arrow{ru}[swap]{\trace(\rho_0)_m} 
-\end{tikzcd}
-\]
-Observe that $\trace(\rho_0)_m$ may be recovered from ${A}_m^0$:
-\[
-\trFrob{{A}^0_m} = \trace(\rho_0)_m
+G^0(\Fq) \arrow{rr}{\trace(\orho^0)} \arrow{rd} && \EE \\
+& G_m^0(\Fq) \arrow{ru}[swap]{\trace(\orho^0)_m} 
+\end{tikzcd}
+\]
+Observe that $\trace(\orho^0)_m$ may be recovered from ${A}_m^0$:
+\[
+\trFrob{{A}^0_m} = \trace(\orho^0)_m
 \]
 %Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{R}(\underline{G}^0) \to \Gr^{R}_{m}(\underline{G}^0)$.
-%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G}^0)$ from which the character of $\rho_0$ may be recovered.
+%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G}^0)$ from which the character of $\orho^0$ may be recovered.
 
@@
 
-We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{R}_m(\underline{G}^{i})$, for $i=0,\ldots ,d$, recursively, following the construction of the representations $\rho_i$, as reviewed in Section~\ref{ssec:review}.
-First, set $\cs{A}_m^i = A_m^0$ and note that 
-\[
-\begin{tikzcd}
-G^0(\Fq) \arrow{rr}{\trace(\rho_0)} \arrow{rd} && \EE\\
+We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{R}_m(\underline{G}^{i})$, for $i=0,\ldots ,d$, recursively, following the construction of the representations $\orho^i$, as reviewed in Section~\ref{ssec:review}.
+First, set $\cs{A}_m^0 = A_m^0$ and note that 
+\[
+\begin{tikzcd}
+G^0(\Fq) \arrow{rr}{\trace(\orho^0)} \arrow{rd} && \EE\\
 & G^0_m(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m^0}} & 
@@
 \begin{tikzcd}
-G^i(\Fq) \arrow{rr}{\trace(\rho_i)} \arrow{rd} && \EE\\
+G^i(\Fq) \arrow{rr}{\trace(\orho^i)} \arrow{rd} && \EE\\
 & G_m^i(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m^i}} & 
@@
 on $G_m^{i}\ltimes J_m^{i+1}$.
-Comparing with \eqref{eq:tensor}, we see that $\trFrob{\cs{B}_m^{i+1}}$ is precisely the function obtained by factoring the character of $\rho_{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(R) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R/\mathfrak{p}_K^{m+1})$ using the canonical identification $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R/\mathfrak{p}_K^{m+1})$.
-In particular, $\trFrob{\cs{B}^{i+1}_m}$ is constant on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$, taking the value $\dim \rho_{i+1}$.
+Comparing with \eqref{eq:tensor}, we see that $\trFrob{\cs{B}_m^{i+1}}$ is precisely the function obtained by factoring the character of $\orho^{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(R) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R/\mathfrak{p}_K^{m+1})$ using the canonical identification $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R/\mathfrak{p}_K^{m+1})$.
+In particular, $\trFrob{\cs{B}^{i+1}_m}$ is constant on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$, taking the value $\dim \orho^{i+1}$.
 With reference to the morphism $\pi_m^{i+1} : G_m^i \ltimes J_m^{i+1} \to G_m^{i+1}$ from \eqref{eq:pi}, define 
 \[
-\cs{\tilde A}_m^{i+1} \ceq (\pi_m^{i+1})_! (\cs{B}_m^{i+1}).
+\cs{C}_m^{i+1} \ceq (\pi_m^{i+1})_! (\cs{B}_m^{i+1}).
 \]
@@
 \begin{eqnarray*}
-\trFrob{\cs{\tilde A}^{i+1}_m}(x)
+\trFrob{\cs{C}^{i+1}_m}(x)
 &=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{B}_m^{i+1}}(y).
@@
 \[
-\trFrob{\cs{\tilde A}^{i+1}_m} = n \trFrob{\cs{B}^{i+1}_m}
-\]
-on $G_m^{i+1}(\Fq)$ for $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) \times \dim \rho_{i+1} $.
-Let $\cs{A}_m^{i+1}$ be the \emph{virtual} Weil sheaf on $G_m^i$ given by $\cs{A}_m^{i+1} = \frac{1}{n} \cs{\tilde A}_m^{i+1}$. 
+\trFrob{\cs{C}^{i+1}_m} = n \trFrob{\cs{B}^{i+1}_m}
+\]
+on $G_m^{i+1}(\Fq)$ for $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) \times \dim \orho^{i+1} $.
+Let $\cs{A}_m^{i+1}$ be the \emph{virtual} Weil sheaf on $G_m^i$ given by $\cs{A}_m^{i+1} = \frac{1}{n} \cs{C}_m^{i+1}$. 
 %
@@
 \begin{tikzcd}
-G^{i+1}(\Fq) \arrow{rr}{\trace(\rho_{i+1})} \arrow{rd} && \EE\\
+G^{i+1}(\Fq) \arrow{rr}{\trace(\orho^{i+1})} \arrow{rd} && \EE\\
 & G_m^{i+1}(\Fq)\arrow{ru}[swap]{{\trFrob{\cs{A}_m^{i+1}}} } & 
@@
 
-Now set $\cs{A}_m = \cs{A}_m^{d} \otimes \cs{L}_m^d$.
-Then $\cs{A}_m$ is a virtual Weil sheaf on $G_m = \Gr^{R}_m(\underline{G})$ such that
-\[
-\begin{tikzcd}
-G(\Fq) \arrow{rr}{\trace(\rho)} \arrow{rd} && \EE\\
-& G_m(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m}} & 
+Now set $\cs{F}^i_m = \cs{A}_m^{i} \otimes \cs{L}_m^i$, for $i=0, \ldots ,d$.
+Then $\cs{F}^i_m$ is a virtual Weil sheaf on $G^i_m = \Gr^{R}_m(\underline{G}^i)$ such that
+\[
+\begin{tikzcd}
+G^i(\Fq) \arrow{rr}{\trace(\orho_i)} \arrow{rd} && \EE\\
+& G_m(\Fq) \arrow{ru}[swap]{\trFrob{\cs{F}^i_m}} & 
 \end{tikzcd}
@@
 commutes.
-Let $\cs{A}$ be the virtural Weil sheaf on the group scheme $G= \Gr_{R}(\underline{G})$ obtained by pullback along $G \to G_m$.
+Let $\cs{F}^i$ be the virtural Weil sheaf on the group scheme $G^i= \Gr_{R}(\underline{G}^i)$ obtained by pulling back $\cs{F}_m^i$ along $G^i \to G^i_m$.
 Then 
 \[
-\trFrob{\cs{A}} = \trace(\rho),
+\trFrob{\cs{F}^i} = \trace(\orho_i),
 \] 
@@
 author={Roe, David},
-       title={From the function-sheaf dictionary to quasicharacters of $p$-adic
-  tori},
-  journal={Journal of the Institute of Mathematics of Jussieu},
+title={From the function-sheaf dictionary to quasicharacters of $p$-adic tori},
+journal = {Journal of the Institute of Mathematics of Jussieu},
+volume = {FirstView},
+number = {6},
+%month = {6},
 year = {2016},
@@
 
-\bib{yu:03a}{unpublished}{
+\bib{Yu:models}{inproceedings}{
 author={Yu, Jiu-Kang},
-       title={{Smooth models associated to concave functions in Bruhat-Tits
-  theory}},
-        date={2003},
-        note={Preprint},
+title={{Smooth models associated to concave functions in Bruhat-Tits theory}},
+%date={2015},
+%pages={{579\ndash 622}},
+booktitle={{Autour des sch\'emas en groupes - \'Ecole d'\'et\'e franco-asiatique de g\'eom\'etrie alg\'ebrique et de th\'eorie des nombres. Volume III}},
+      series={Panoramas et synth\`eses},
+      volume={47},
+    publisher={Soci\'et\'e Math\'ematique de France},
+     issn={1272-3835},
+     note={\href{http://smf4.emath.fr/Publications/PanoramasSyntheses/2016/47/html/smf_pano-synth_47_227-258.php}{Panoramas et synth\`eses \textbf{47} (2016), 579--622}}
+
 }

### 2016-07-10 Geometric types.tex
Small improvement to the introduction

@@
 A Yu type datum determines a sequence $(\oK^i,\orho_i)$, for $i=0, \ldots, d$, of types for supercuspidal representations of a sequence of $p$-adic groups.
-The main result of \cite{Yu:models} explains how to find a smooth group scheme over $\O$ to with $ \underline{G}^i(\O)=\,^\circ K^i $, where $\O$ is the ring of integers of the $p$-adic field.
+The main result of \cite{Yu:models} explains how to find, for each $i=0, \ldots, d$, a smooth group scheme $\underline{G}^i$ over the ring $\O$ of integers of the $p$-adic field with $\underline{G}^i(\O)=\,^\circ K^i $.
 In this paper we show in Theorem~\ref{thm:geotypes} that if the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic, then each type $(\oK^i,\orho_i)$ in this sequence can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$,

### 2016-07-10 Geometric types.tex
Some changes to abstract

--- 2016-06-28 Geometric types.tex
@@
 We then use these \emph{commutative character sheaves} to geometrize the linear characters that appear in the types introduced by Jiu-Kang Yu.
-We then combine this with Lusztig's character sheaves on reductive algebraic groups over finite fields, and the geometrization of the Weil representation found by Gurevich and Hadani, to find \emph{geometric types} for supercuspidal representations of tamely ramified $p$-adic groups.
+We combine these sheaves with Lusztig's character sheaves on reductive algebraic groups over finite fields and the geometrization of the Weil representation found by Gurevich and Hadani, to define \emph{geometric types} for supercuspidal representations of tamely ramified $p$-adic groups.
 \end{abstract}

### 2016-07-18 Geometric types.tex
Removed some redundant prose. Improved the notation conversion chart.

--- 2016-07-10 Geometric types.tex
@@
 \usepackage{tikz-cd}
+
+%%%%% for spacing
+\usepackage{amsmath}
+\usepackage{lipsum}
+\usepackage{setspace}
 
@@
 In this paper we follow the suggestion above by showing that Yu type data are geometrizable, in the following sense.
-A Yu type datum determines a sequence $(\oK^i,\orho_i)$, for $i=0, \ldots, d$, of types for supercuspidal representations of a sequence of $p$-adic groups.
+A Yu type datum determines a sequence of representations $\orho_i$ of compact $p$-adic groups $\oK^i$, for $i=0, \ldots, d$, such that $(\oK^d, \rho_d)$ is a type for a supercuspidal representation of a $p$-adic group.
 The main result of \cite{Yu:models} explains how to find, for each $i=0, \ldots, d$, a smooth group scheme $\underline{G}^i$ over the ring $\O$ of integers of the $p$-adic field with $\underline{G}^i(\O)=\,^\circ K^i $.
-In this paper we show in Theorem~\ref{thm:geotypes} that if the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic, then each type $(\oK^i,\orho_i)$ in this sequence can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$,
+In this paper we show in Theorem~\ref{thm:geotypes} that if the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic, then each representation $\orho_i$ in this sequence can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$,
 where $\cs{F}^i$ is a virtual Weil sheaf on the Greenberg transform $G^i$ of $\underline{G}^i$, such that 
@@
 %Theorem~\ref{thm:geotypes} shows how to construct the virtual Weil sheaf $\cs{F}^i$ from the Yu type datum, so that \eqref{eqn:intro1} holds.
-We refer to the pairs $(\underline{G}^i, \cs{F}^i)$ as \emph{geometric types} for supercuspidal representations.
+We refer to the pair $(\underline{G}^d, \cs{F}^d)$ as a \emph{geometric type}.
 
@@
 
-All supercuspidal representations of tamely ramified $p$-adic groups can be built from the data of \cite{yu:01a}*{\S 15}, as established in \cite{kim:07a}.
-The type, in the sense of \cite{bushnell-kutzko:98a}, of the resulting supercuspidal representations can be constructed directly from Yu's data. 
-Let us refer to the types arising in this manner as {\it Yu types}.
-In this section we offer an application of Theorem~\ref{thm:geo}, by showing that Yu types are geometrizable, subject to a very mild hypothesis.
-The proof of that statement, made precise in Theorem~\ref{thm:geotypes}, requires: the geometrization of the character of the Heisenberg-Weil representation over finite fields (Section~\ref{ssec:Jacobi}); a review of some basic properties of Yu types (Section~\ref{ssec:review}); a review of some facts from Yu's notes on smooth integral models (Section~\ref{ssec:review}); and the geometrization of characters of representations of reductive groups over finite fields with cyclic geometric component groups, using Lusztig's character sheaves on these groups.
-These pieces are assembled in Section~\ref{ssec:geotypes}.
+We now show how to use Theorem~\ref{thm:geo} to geometrize Yu type data and how to geometrize types for supercuspidal representations of $p$-adic groups.
 
@@
 
-\begin{table}[htp]
-\caption{Comparison with notation of \cite{yu:01a}}
-\begin{center}
-\begin{tabular}{c|l}
+\begin{table}[ht]
+\caption{Notation conversion chart.}
+\begin{spacing}{1.2}
+\begin{tabular}{| c|l |}
+\hline
+\text{this paper} & \cite{yu:01a}\\
+\hline
 %$\oK^0$ & $\,^\circ K^0 = G^0(F)_y$\\% \cite{yu:01a}*{\S 15} \\
@@
 %$H^{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi_i}\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
-$Z_{i+1}$ & $\ker(V_{i+1}^\sharp\to V_{i+1})$ % \cite{yu:01a}*{\S 11} \\
+$Z_{i+1}$ & $\ker(V_{i+1}^\sharp\to V_{i+1})$ \\ % \cite{yu:01a}*{\S 11} \\
 %$(f_{j+1}, j_{i+1})$ & $(f,j)$ \cite{yu:01a}*{\S 11} \\
 %$\langle\ ,\ \rangle_{i+1}$ & $\langle\ ,\ \rangle$, \cite{yu:01a}*{\S 11} 
+\hline
 \end{tabular}
-\end{center}
+\end{spacing}
 \label{table:notation}
@@
 \labitem{M3}{M3}
-Diagram \eqref{eq:semiprod} is now replaced by the following exact diagram of smooth group schemes over $R$.
+Diagram \eqref{eq:semiprod} is now replaced by the following diagram of smooth group schemes over $R$.
 \begin{equation}\label{eq:pimodel}

### 2016-07-18 Geometric types.tex
Updated the bibliography

@@
 
-\bib{Vistoli:notes}{unpublished}{
+\bib{Vistoli:notes}{article}{
    author={Vistoli, Angelo},
-       title={{Notes on Grothendieck topologies, fibered categories and descent
-  theory}},
-        date={2007},
-        note={\href{http://arxiv.org/abs/math/0412512}{arXiv:0412512
-  [math.AG]}},
+   title={Grothendieck topologies, fibered categories and descent theory},
+   conference={
+      title={Fundamental algebraic geometry},
+   },
+   book={
+      series={Math. Surveys Monogr.},
+      volume={123},
+      publisher={Amer. Math. Soc., Providence, RI},
+   },
+   date={2005},
+   pages={1--104},
+%   review={\MR{2223406}},
 }
@@
      issn={1272-3835},
-     note={\href{http://smf4.emath.fr/Publications/PanoramasSyntheses/2016/47/html/smf_pano-synth_47_227-258.php}{Panoramas et synth\`eses \textbf{47} (2016), 579--622}}
+     note={\href{http://smf4.emath.fr/Publications/PanoramasSyntheses/2016/47/html/smf_pano-synth_47_227-258.php}{Panoramas et synth\`eses \textbf{47} (2015), 227--258}}
 

### 2016-07-24 Geometric types.tex
Some style changes in the introduction.

@@
 The main result of \cite{Yu:models} explains how to find, for each $i=0, \ldots, d$, a smooth group scheme $\underline{G}^i$ over the ring $\O$ of integers of the $p$-adic field with $\underline{G}^i(\O)=\,^\circ K^i $.
-In this paper we show in Theorem~\ref{thm:geotypes} that if the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic, then each representation $\orho_i$ in this sequence can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$,
-where $\cs{F}^i$ is a virtual Weil sheaf on the Greenberg transform $G^i$ of $\underline{G}^i$, such that 
+In this paper we show, in Theorem~\ref{thm:geotypes}, that if the geometric component group of the reductive quotient of the special fiber of the group scheme $\underline{G}^0$ is cyclic, then each representation $\orho_i$ in this sequence can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$,
+where $\cs{F}^i$ is a virtual Weil sheaf on the Greenberg transform $G^i$ of $\underline{G}^i$.
+Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(\OK) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the virtual complex $\cs{F}^i$, the sheaf $\cs{F}^i$ is characterized by the property
 \begin{equation}\label{eqn:intro1}
-\trFrob{\cs{F}^i} = \trace(\,^\circ\rho_i),
+\trFrob{\cs{F}^i} = \trace(\,^\circ\rho_i).
 \end{equation}
-where $\trFrob{\cs{F}^i}$ refers to the function on $G^i(k) = \underline{G}^i(\OK) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the virtual complex $\cs{F}^i$.
-\[
-\begin{tikzcd}
-(\oK^i,\orho_i) \arrow[bend left, dashed]{rrr}{\text{geometrization}} &&& \arrow[bend left, dashed]{lll}{\text{trace of Frob.}}
-(\underline{G}^i, \cs{F}^i),
+Via this theorem, we obtain geometric avatars for each type in a Yu datum:
+\[
+\begin{tikzcd}
+(\oK^i,\orho_i) \arrow[bend left, dashed]{rrr}{\text{geometrization}} &&& \arrow[bend left, dashed]{lll}{\text{trace of Frob}}
+(\underline{G}^i, \cs{F}^i).
 \end{tikzcd}
@@
 
-In order to prove Theorem~\ref{thm:geotypes}, we must address the lacuna highlighted in the quote from \cite{Yu:models}, above; namely, we must find a way to geometrize linear characters of groups of the form $\underline{H}(\O)$, where $\underline{H}$ is a smooth group scheme over $\O$.
-In order to do this is a systematic manner, we begin this paper by finding the function-sheaf dictionary for characters of arbitrary smooth group schemes over finite fields. 
-When coupled with the Greenberg transform, this will allow for the geometrization of linear characters of $\underline{H}(\O)$.
+In order to prove Theorem~\ref{thm:geotypes}, we must find a way to geometrize linear characters of groups of the form $\underline{H}(\O)$, where $\underline{H}$ is a smooth group scheme over $\O$. 
+In order to do so in a systematic manner, we begin this paper by describing the function-sheaf dictionary for characters of arbitrary smooth group schemes over finite fields. 
+When coupled with the Greenberg transform, this dictionary will allow for the geometrization of linear characters of $\underline{H}(\O)$.
 
@@
 The proof of Theorem~\ref{thm:geotypes} requires: Yu's work on smooth integral models \cite{Yu:models}; the geometrization of the character of the Heisenberg-Weil representation over finite fields by Gurevich \& Hadani \cite{gurevich-hadani:07a}; Lusztig's character sheaves on reductive groups over finite fields; and finally, the function-sheaf dictionary for characters of smooth group schemes over finite fields, now at our disposal in Theorem~\ref{thm:geo}.
-These pieces are assembled in Section~\ref{ssec:geotypes}, to prove Theorem~\ref{thm:geotypes}.
-In this way, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:
+These pieces are assembled in Section~\ref{ssec:geotypes}, where we prove Theorem~\ref{thm:geotypes}.
+With this theorem, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:
 virtual Weil perverse sheaves on group schemes over finite fields.

### 2016-07-25 Geometric types.tex
Getting ready to submit. Will print and proof tomorrow.

@@
 
-\tableofcontents
+%\tableofcontents
 
@@
 \begin{quotation}
-{\it Therefore, up to some linear characters, all the ingredient representations [appearing in Yu type data] are on groups of
- the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
+{\it Therefore, up to some linear characters, all the ingredient representations 
+%[appearing in Yu type data]
+ are on groups of the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
 These results suggest that algebraic geometry and group schemes should play an
@@
 Thus the category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the following sense: for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $(\cs{L},\mu,\beta)$ in $\CCS(G)$ such that $\trFrob{\cs{L}} = \chi$.
-The geometrization of $\chi : G(\Fq) \to \EEx$ is not unique, but the group of isomorphism classes of possibilities are enumerated by $\Delta_G^*$.
+While the geometrization of $\chi : G(\Fq) \to \EEx$ is not unique, the group of isomorphism classes of possibilities are enumerated by $\Delta_G^*$.
 \end{theorem}
@@
 \]
-By Lemma~\ref{lem:HH}, we may interpret the diagram on the right as a diagram in $\Loc_{H\times H}(G\times G)$.
+Using Lemma~\ref{lem:HH}, we may interpret the diagram on the right as a diagram in $\Loc_{H\times H}(G\times G)$.
 By Lemma~\ref{lem:torsor}, this corresponds to a diagram in $\Loc(G\ab\times G\ab)$, necessarily the diagram on the left, above, and also that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes.
@@
 
-We now show how to use Theorem~\ref{thm:geo} to geometrize Yu type data and how to geometrize types for supercuspidal representations of $p$-adic groups.
+We now show how to use Theorem~\ref{thm:geo} to geometrize Yu type data and how to geometrize types for supercuspidal representations of tamely ramified $p$-adic groups.
 

### 2016-07-29 Geometric types.tex
The version that went to CJM.

@@
 
-As proved by Ju-Lee Kim in \cite{kim:07a}, all irreducible supercuspidal representations of tamely ramified $p$-adic groups can be built from the datum introduced by Jiu-Kang Yu in \cite{yu:01a}*{\S 15}.
-While the type, in the sense of Bushnell \& Kutzko \cite{bushnell-kutzko:98a}, of a supercuspidal representation built from Yu datum can be constructed directly from the datum, it is convenient to consider and intermediate object, introduced in \cite{yu:01a}*{Remark 15.4}, which we call a \emph{Yu type datum}.
+As proved by Ju-Lee Kim in \cite{kim:07a}, all irreducible supercuspidal representations of tamely ramified $p$-adic groups can be built from ``data'' introduced by Jiu-Kang Yu in \cite{yu:01a}*{\S 15}.
+While the type, in the sense of Bushnell \& Kutzko \cite{bushnell-kutzko:98a}, of a supercuspidal representation built from Yu data can be constructed directly from the datum, it is convenient to consider and intermediate object, introduced in \cite{yu:01a}*{Remark 15.4}, which we call a \emph{Yu type datum}.
 Yu type data are studied in \cite{Yu:models}, which concludes with the following observation.
@@
 The main result of \cite{Yu:models} explains how to find, for each $i=0, \ldots, d$, a smooth group scheme $\underline{G}^i$ over the ring $\O$ of integers of the $p$-adic field with $\underline{G}^i(\O)=\,^\circ K^i $.
-In this paper we show, in Theorem~\ref{thm:geotypes}, that if the geometric component group of the reductive quotient of the special fiber of the group scheme $\underline{G}^0$ is cyclic, then each representation $\orho_i$ in this sequence can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$,
+In this paper we show that if the geometric component group of the reductive quotient of the special fiber of the group scheme $\underline{G}^0$ is cyclic, then each representation $\orho_i$ in this sequence can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$,
 where $\cs{F}^i$ is a virtual Weil sheaf on the Greenberg transform $G^i$ of $\underline{G}^i$.  
-Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(\OK) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the virtual complex $\cs{F}^i$, the sheaf $\cs{F}^i$ is characterized by the property
+Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(\OK) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the virtual complex $\cs{F}^i$, we show in Theorem~\ref{thm:geotypes} that
 \begin{equation}\label{eqn:intro1}
@@
 \end{equation}
-Via this theorem, we obtain geometric avatars for each type in a Yu datum:
+Via this theorem, then, we obtain geometric avatars for each type in a Yu datum:
 \[
@@
 
-In order to prove Theorem~\ref{thm:geotypes}, we must find a way to geometrize linear characters of groups of the form $\underline{H}(\O)$, where $\underline{H}$ is a smooth group scheme over $\O$. 
+To prove Theorem~\ref{thm:geotypes}, we must find a way to geometrize linear characters of groups of the form $\underline{H}(\O)$, where $\underline{H}$ is a smooth group scheme over $\O$. 
 In order to do so in a systematic manner, we begin this paper by describing the function-sheaf dictionary for characters of arbitrary smooth group schemes over finite fields. 
@@
 then there is a certain category $\CS(G)$ of rank-one local systems on $G$ and an
-explicit isomorphism between $G(k)^* \ceq \Hom(G(k), \EEx)$ and isomorphism classes
-of objects in $\CS(G)$.  Objects in $\CS(G)$ are referred to as \emph{character sheaves};
-the isomorphism is given by mapping a character sheaf $\cs{L}$ to the function
+explicit isomorphism between isomorphism classes
+of objects in $\CS(G)$ and $G(k)^* \ceq \Hom(G(k), \EEx)$; 
+%Objects in $\CS(G)$ are referred to as \emph{character sheaves}.
+the isomorphism is given by mapping $\cs{L}$ to the function
 $\TrFrob{G} : g \mapsto \Tr(\Frob{} \vert \cs{L}_g)$.
@@
 smooth commutative group schemes $G$, allowing for non-connected groups.
-We gave a description of the category $\CS(G)$ of character sheaves in this context, as well
+We gave a description of the category $\CS(G)$ in this context, as well
 as an epimorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$.
@@
  by describing a full subcategory $\CCS(G)$ of $\CS(G)$ so that $\TrFrob{G}$ restricts to an isomorphism $\CCSiso{G} \to G(k)^*$.
-We refer to the resulting objects as \emph{commutative character sheaves}, since the passage from $\CS(G)$ to $\CCS(G)$ involves a condition that exchanges the inputs to the multiplication morphism on $G$ (see Definition \ref{def:CCScom}).
+We refer to objects of $\CS(G)$ as character sheaves and objects in $\CCS(G)$ as \emph{commutative character sheaves}, since the passage from $\CS(G)$ to $\CCS(G)$ involves a condition that exchanges the inputs to the multiplication morphism on $G$ (see Definition \ref{def:CCScom}).
 When $G$ is connected, all character sheaves on $G$ are commutative.
-This category clarifies several questions about $\CS(G)$. 
+
+Category $\CCS(G)$ clarifies several questions about $\CS(G)$. 
 Invisible character sheaves \cite{cunningham-roe:13a}*{Def.
@@
 there are more character sheaves than there are characters, as pointed out by Kamgarpour \cite{kamgarpour:09a}*{(1.1)}.
-We define a category $\CCS(G)$ and a forgetful functor to $\CS(G)$ so that $\TrFrob{G} : \CCSiso{G} \to G\ab(k)^*$
+We then define category $\CCS(G)$ for such $G$ and a forgetful functor to $\CS(G)$ so that $\TrFrob{G} : \CCSiso{G} \to G\ab(k)^*$
 is an isomorphism.  
@@
 character sheaf $\cs{L}$ on $G$ with $\TrFrob{G}(\cs{L}) = \chi$. Moreover, we find that pullback along the quotient $q : G \to G\ab$
-defines an equivalence of categories $\CCS(G\ab) \to \CCS(G)$.  Note that the functor $\CCS(G) \to \CS(G)$ is not
+defines an equivalence of categories $\CCS(G\ab) \to \CCS(G)$.  
+The functor $\CCS(G) \to \CS(G)$ is not
 essentially surjective, missing the kinds of linear character sheaves highlighted by Kamgarpour.
@@
 
-Armed with the function-sheaf dictionary for smooth group schemes over finite fields, we may return to the task of geometrizing Yu type data. 
+Armed with the function-sheaf dictionary for smooth group schemes over finite fields, we return to the task of geometrizing Yu type data. 
 The proof of Theorem~\ref{thm:geotypes} requires: Yu's work on smooth integral models \cite{Yu:models}; the geometrization of the character of the Heisenberg-Weil representation over finite fields by Gurevich \& Hadani \cite{gurevich-hadani:07a}; Lusztig's character sheaves on reductive groups over finite fields; and finally, the function-sheaf dictionary for characters of smooth group schemes over finite fields, now at our disposal in Theorem~\ref{thm:geo}.
@@
 % 
-In Section~\ref{sec:types} we give an application of Theorem~\ref{thm:geo} by geometrizing types for supercuspidal representations of $p$-adic groups.
-The proof of this statement, which is made precise in Theorem~\ref{thm:geotypes}, is given in Section~\ref{ssec:geotypes}.
+In Section~\ref{sec:types} we use Theorem~\ref{thm:geo} to geometrize types for supercuspidal representations of $p$-adic groups, in a sense made precise in Theorem~\ref{thm:geotypes}. 
+% is given in Section~\ref{ssec:geotypes}. 
  %Specifically, we show that if $C$ is a compact $p$-adic group and $\rho$ is a representation of $C$ and $(C,\rho)$ is a type for a tamely ramified $p$-adic group then there is a  group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a virtual Weil sheaf $\mathcal{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
@@
 The representations $\orho^i$ and $\orho_i$ are defined recursively.
-For the base case $i=0$, set $\orho_0 \ceq \orho^i\otimes \varphi^i$; see \ref{Y1} above.
+For the base case $i=0$, set $\orho_0 \ceq \orho^0\otimes \varphi^0$; see \ref{Y1} above.
 Now fix $i$.
@@
 
-Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S S_1$ of $\underline{J}^{i+1}$. 
+Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S \Spec{k}$ of $\underline{J}^{i+1}$. 
 The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $V^{i+1}$ over $\Fq$, where $V^{i+1}$, appears as a quotient $\underline{J}^{i+1}_{\Fq} \to V^{i+1}$ of algebraic groups over $\Fq$.
@@
 Finally, the group homomorphism $f_i : J_0\cdots J_i \to \Sp(V_{i+1})$ may be made geometric in much the same way. 
-Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S S_1$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $f_i : J_0\cdots J_i \to \Sp(V_{i+1})$ is realized as the composition
+Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S \Spec{k}$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $f_i : J_0\cdots J_i \to \Sp(V_{i+1})$ is realized as the composition
 \[
@@
 In fact, $\varrho_0$ is itself obtained by pulling back a representation $\varrho_0^\reductive$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
-\labitem{M2}{M2} The quasicharacters $\varphi^i$ are quasicharacters of $\underline{G}^i(R)$, for $i=0, \ldots d$.
+\labitem{M2}{M2} The quasicharacters $\varphi^i$ are quasicharacters of $\underline{G}^i(R)$, for $i=0, \ldots, d$.
 \labitem{M3}{M3}
@@
 \] 
-for all $i=0, \ldots d$.
+for all $i=0, \ldots, d$.
 Set $G_m^i = \Gr_m^{R}(\underline{G}^i)$.
@@
 on $G_m^{i}\ltimes J_m^{i+1}$.
-Comparing with \eqref{eq:tensor}, we see that $\trFrob{\cs{B}_m^{i+1}}$ is precisely the function obtained by factoring the character of $\orho^{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(R) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R/\mathfrak{p}_K^{m+1})$ using the canonical identification $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R/\mathfrak{p}_K^{m+1})$.
+Comparing with \eqref{eq:tensor}, we see that $\trFrob{\cs{B}_m^{i+1}}$ is precisely the function obtained by factoring the character of $\orho^{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(R) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R_m)$ using the canonical identification $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R_m)$.
 In particular, $\trFrob{\cs{B}^{i+1}_m}$ is constant on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$, taking the value $\dim \orho^{i+1}$.

### 2017-01-31 Geometric types.tex
Small wording change
The easy fixes from the reviewer's comments.

@@
 where $\cs{F}^i$ is a virtual Weil sheaf on the Greenberg transform $G^i$ of $\underline{G}^i$.  
-Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(\OK) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the virtual complex $\cs{F}^i$, we show in Theorem~\ref{thm:geotypes} that
+Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(\OO{}) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the virtual complex $\cs{F}^i$, we show in Theorem~\ref{thm:geotypes} that
 \begin{equation}\label{eqn:intro1}
@@
 Let $i : G \to G$ be inversion and $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
-Both are smooth morphism of $\Fq$-schemes.
+Both are smooth morphisms of $\Fq$-schemes.
 Set $m' = i \circ m \circ \theta$; we have $j\circ c = m \circ (m \times m')$.
@@
 Then $j^*(\cs{L},\mu) \iso j^*q^*(\cs{L}\ab,\mu\ab)$ in $\CS(H)$. 
-Since $q\circ j = 1$, it follows that $\cs{L}\vert_{G\der} \to (\EE)_{H}$ in $\CS(H)$.
+Since $q\circ j = 1$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{H}$ in $\CS(H)$.
 This completes the proof of Proposition~\ref{prop:Gder_triv}.
@@
 \begin{tikzcd}
-\underline{G}(S) \arrow{rr}{\varphi} \arrow{rd} && \EEx\\
+\underline{G}(R) \arrow{rr}{\varphi} \arrow{rd} && \EEx\\
 & \underline{G}(R/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi_m} 
@@
 
-Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_S \Spec{k}$ of $\underline{J}^{i+1}$. 
+Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_{\Spec{R}} \Spec{k}$ of $\underline{J}^{i+1}$. 
 The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $V^{i+1}$ over $\Fq$, where $V^{i+1}$, appears as a quotient $\underline{J}^{i+1}_{\Fq} \to V^{i+1}$ of algebraic groups over $\Fq$.
@@
 Finally, the group homomorphism $f_i : J_0\cdots J_i \to \Sp(V_{i+1})$ may be made geometric in much the same way. 
-Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_S \Spec{k}$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $f_i : J_0\cdots J_i \to \Sp(V_{i+1})$ is realized as the composition
+Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_{\Spec{R}} \Spec{k}$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $f_i : J_0\cdots J_i \to \Sp(V_{i+1})$ is realized as the composition
 \[
@@
 commutes.
-Let $\cs{F}^i$ be the virtural Weil sheaf on the group scheme $G^i= \Gr_{R}(\underline{G}^i)$ obtained by pulling back $\cs{F}_m^i$ along $G^i \to G^i_m$.
+Let $\cs{F}^i$ be the virtual Weil sheaf on the group scheme $G^i= \Gr_{R}(\underline{G}^i)$ obtained by pulling back $\cs{F}_m^i$ along $G^i \to G^i_m$.
 Then 

### 2017-02-26 Geometric types.tex
Working on reviewer comments

@@
 \newcommand{\bCS}{{\CS_0}}
+\newcommand{\CSab}{\CS_{\operatorname{ab}}}
 \newcommand{\catname}[1]{\normalfont{\textsf{#1}}}
@@
 In order to get character sheaves that correspond to characters in $G(k)^*$, we must discard those
-character sheaves whose restriction to the derived subgroup is nontrivial.
-Recall from Section~\ref{sec:defs} that we refer to objects in category $\CS(G)$, defined as in \cite{cunningham-roe:13a}*{Def.
-1.1}, as linear character sheaves when $G$ is smooth but not necessarily commutative.
-Also recall the short exact sequence of group schemes
-
-\[
-1 \to G\der \xrightarrow{j} G \xrightarrow{q} G\ab \to 1.
-\]
-
-\begin{proposition} \label{prop:Gder_triv}
-Suppose $G$ is a smooth group scheme and $(\cs{L},\mu) \in \CS(G)$.
-Then the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $(\cs{L},\mu) \cong q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, for some $(\cs{L}\ab,\mu\ab) \in \CS(G\ab)$.
-\end{proposition}
-
-Proposition~\ref{prop:Gder_triv} will be proven in Section \ref{ssec:proof1}.
-
-We may now define commutative character sheaves on $G$.
-%
-Suppose $(\cs{L},\mu)$ is a linear character sheaf on $G$ such that its pull-back along
-$j: G\der \hookrightarrow G$ is trivial;
-let $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ be an isomorphism in $\CS(G\der)$.
-Let $\CS'(G)$ be the category of such triples, $(\cs{L},\mu,\beta)$, in which a morphism $(\cs{L},\mu,\beta)\to (\cs{L}',\mu',\beta')$ is a morphism $\alpha : (\cs{L},\mu)\to (\cs{L}',\mu')$ in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{G\der}$.
-%
-
-Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows.
-Let $i : G \to G$ be inversion and $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
-Both are smooth morphisms of $\Fq$-schemes.
-Set $m' = i \circ m \circ \theta$; we have $j\circ c = m \circ (m \times m')$.
-Then $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms below.
-\begin{equation}
-\begin{tikzcd}
-\arrow[equal]{d} c^* (\cs{L}\vert_{G\der}) \arrow{r}{c^*(\beta)} 
-	&  c^*((\EE)_{G\der}) \arrow[equal]{d} \\
-\arrow{d}[swap]{j\circ c = m \circ (m \times m')} c^* j^* \cs{L} 
-	&   (\EE)_{G\times G} \\
-(m \times m')^* m^* \cs{L} \arrow{d}[swap]{(m \times m')^*(\mu)} 
-	&  m^*\cs{L} \otimes \theta^* m^* i^* \cs{L}  \arrow[dashed]{u}[swap]{\gamma'} \\
-(m \times m')^* (\cs{L} \boxtimes \cs{L}) \arrow[equal]{r} 
-	& m^*\cs{L} \otimes (m')^*\cs{L} \arrow{u}[swap]{m' = i\circ m\circ \theta} 
-\end{tikzcd}
-\end{equation}
-In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations; so, for example, the middle left isomorphism comes from $(m\times m')^* m^* \iso c^* j^*$ since $j\circ c = m \circ (m \times m')$.
-Using the monoidal structure of the category of Weil local systems on $G\times G$, the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ defines an isomorphism
-\[
-m^*\cs{L} \to (\theta^* m^* i^*\cs{L})^\vee.
-\]
-Applying the canonical isomorphisms $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ and $i^*(\cs{L}^\vee) \cong \cs{L}$, this map provides the promised isomorphism
-\[
-\begin{tikzcd}
-\gamma : m^*\cs{L} \arrow{r} & \theta^* m^* \cs{L}.
-\end{tikzcd}
-\]
-
-\begin{definition}\label{def:CCS}
-The category $\CCS(G)$ of commutative character sheaves on $G$ is the full subcategory of $\CS'(G)$ consisting of triples $(\cs{L},\mu,\beta)$ such that the following diagram of Weil sheaves on $G \times G$ commutes:
-  \[
-  \begin{tikzcd}[row sep=30]
-   m^*\cs{L} \arrow{d}[swap]{\gamma} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
-   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L}).
-  \end{tikzcd}
-  \]
-Here $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ above. 
-\end{definition}
-
-\subsection{Objects and maps in commutative character sheaves} \label{ssec:obmor}
-
-Suppose $G$ is commutative, so $G\der = 1$. 
-Suppose $(\cs{L},\mu,\beta)$ is an object in $\CS'(G)$.
-Then $\beta : \cs{L}_1\to \EE$ is an isomorphism in $\CS(1)$, which is unique by \cite{cunningham-roe:13a}*{Thm 3.9}.
-Tracing through the construction of $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ from $\beta : \cs{L}_1\to \EE$, we find 
-%\todo{I'm having some trouble seeing this.} 
-that $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ is the canonical isomorphism coming from the equation $m = m \circ \theta$. 
-Thus, when $G$ is commutative, Definition~\ref{def:CCS} agrees with Definition~\ref{def:CCScom}.
-The next result generalizes this observation.
-
-\begin{theorem}\label{thm:Gab}
-%Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
-Pull-back along the abelianization $q : G \to G\ab$
-defines an equivalence of categories
-\[
-\CCS(G\ab) \to \CCS(G).
-\]
-\end{theorem}
-%
-Sections~\ref{ssec:equivariant1}, \ref{ssec:equivariant2}, \ref{ssec:descent} and \ref{ssec:closed} set up machinery needed to prove Theorem~\ref{thm:Gab}.
-The precise definition of the functor $\CCS(G\ab) \to \CCS(G)$ will be given with the proof of Theorem~\ref{thm:Gab}, in Section~\ref{ssec:proof2}.
-
-Theorem~\ref{thm:Gab} shows that $\CCS(G)$ is a categorical solution to the problem that linear character sheaves on $G$ need not be trivial on $G\der$, as discussed at the beginning of Section~\ref{sec:noncom}.
-At the same time, changing $\CS(G)$ to $\CCS(G)$ resolves the lack of bijectivity in \cite{cunningham-roe:13a}*{Thm.
-3.6}.
-%
-But a description of $\CCS(G)$ requires, at the very least, a description of isomorphism classes of objects, and maps.
-
-\begin{corollary}\label{cor:Gab}
-%Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
-The category $\CCS(G)$ is monoidal and there is a canonical isomorphism
-\[
-\CCSiso{G} \iso \Hom(G\ab(\Fq),\EEx).
-\]
-Every map in $\CCS(G)$ is either trivial or an isomorphism, and the automorphism group of any object in $\CCS(G)$ is canonically
-isomorphic to $\Hom(\pi_0(G\ab)_{\Frob{}},\EEx)$.
-\end{corollary}
-
-\subsection{Geometrization of characters} \label{ssec:geo}
-
-\begin{theorem}\label{thm:geo}
-%Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
-The trace of Frobenius $\TrFrob{} : \CCSiso{G}\to G(\Fq)^*$ fits into the following diagram,
-\[
-\begin{tikzcd}
-\ & & \CCSiso{G\ab} \arrow{d}{\TrFrob{}}[swap]{\iso} \arrow{r}{\iso} & \CCSiso{G} \arrow{d}{\TrFrob{}}& \\
-1 \arrow{r} & \Delta_G^* \arrow{r} & G\ab(k)^* \arrow{r} & G(k)^* \arrow{r} & 1,
-\end{tikzcd}
-\]
-where $\Delta_G$ is the image of the connecting homomorphism $G\ab(\Fq) \to \Hh^1(\Fq, G\der)$. 
-Thus the category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the following sense: for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $(\cs{L},\mu,\beta)$ in $\CCS(G)$ such that $\trFrob{\cs{L}} = \chi$.
-While the geometrization of $\chi : G(\Fq) \to \EEx$ is not unique, the group of isomorphism classes of possibilities are enumerated by $\Delta_G^*$.
-\end{theorem}
-
-\begin{proof}
-By the definition of $\Delta_G$, we have a short exact sequence
-\[
-1 \to G(k) / G\der(k) \to G\ab(k) \to \Delta_G \to 1.
-\]
-Applying $\Hom(-, \EEx)$ and using the fact that every homomorphism $G(k) \to \EEx$ vanishes on $G\der(k)$, we get
-\[
-1 \to \Delta_G^* \to G\ab(k)^* \to G(k)^* \to 1.
-\]
-By Theorem~\ref{thm:Gab}, the map $\CCSiso{G\ab} \to \CCSiso{G}$ is an isomorphism.
-Moreover, since both $\CCSiso{G\ab} \to \CCSiso{G}$ and $G\ab(k)^* \to G(k)^*$ are
-defined by pullback along $q$, the square in the statement of the theorem commutes.
-Finally, $\TrFrob{} : \CCSiso{G\ab} \to G\ab(k)^*$ is an isomorphism by Theorem \ref{thm:trfrobiso}.
-\end{proof}
-
-\begin{remark}
-Note that when $\Hh^1(k,G\der) = 0$ then $\CCSiso{G} \iso G(\Fq)^*$, so
-we succeed in geometrizing characters of $G(k)$ on the nose.
-\end{remark}
-
-%\todo{Masound's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case.
-So, I think the modification is easy: add mop to diagram 2.4 in Masoud's paper.
-\\ -CC}
-
-%\section{Descent to the Abelianization} \label{sec:descent}
-
-%In this section we use descent along the abelianization $q : G \to G\ab$ to prove Propositions~1.2 and 1.4, and Theorem~\ref{thm:Gab}.
-%This approach requires introducing equivariant linear character sheaves, as defined in Section~[].
-
-%We close this section by gathering together the main result of this paper in one place.
-
-\subsection{Proofs for results from Section \ref{ssec:noncomdef}} \label{ssec:proofs}
-
-\subsubsection{Equivariant Weil local systems}\label{ssec:equivariant1}
-
-Let $G$ be a smooth group scheme over $k$, as above.
-Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
-Let $a : H \times G\to G$ be an action of $H$ on $G$ 
-%group action compatible with the group structure on $G$ 
-and write $p : H\times G \to G$ for projection. 
-Consider the morphisms
-\[
-\begin{tikzcd}
-H \times H \times G 
-\arrow[shift left=4]{r}{b_1, b_2, b_3} 
-\arrow{r}{}
-\arrow[shift right=4]{r}{} 
-& H \times G 
-\arrow[shift left=2]{r}{a}
-\arrow[shift right=2]{r}[swap]{p}
- & G 
-\end{tikzcd}
-\]
-defined by 
-\begin{align*}
-b_1(h_1,h_2,g) &= (h_1h_2,g) \\
-b_2(h_1,h_2,g) &= (h_1,h_2g) \\
-b_3(h_1,h_2,g) &= (h_2,g).
-\end{align*}
-Note that
-\begin{align*}
-a\circ b_1 &= a\circ b_2 \\
-a\circ b_3 &= p\circ b_2 \numberthis \label{eqn:bap}\\
-p\circ b_1 &= p\circ b_3.
-\end{align*}
-Define $s : G\to H\times G$ by $s(g) = (1,g)$.
-An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
-\[
-\nu : a^*\cs{L} \to p^*\cs{L}
-\] 
-of Weil local systems on $H\times G$ such that 
-\begin{equation}\label{E1}
-s^*(\nu) = \id_{\cs{L}}
-\end{equation}
-and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes. 
-\begin{equation}\label{E2}
-\begin{tikzcd}
-\ &  \arrow{dl}{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
-b_1^* a^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
-& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L} & 
-\end{tikzcd}
-\end{equation}
-%In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from equations \eqref{eqn:bap}; so, for example, the top left isomorphism comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
-%On stalks, this condition is ...
+character sheaves whose restriction to the derived subgroup is nontrivial.  Moreover, the isomorphism
+with the trivial sheaf on the derived subgroup will be important in relating to sheaves on the abelianization,
+motivating the following category.
+
+Recall from Section~\ref{sec:defs} that we refer to objects in category $\CS(G)$, defined as
+in \cite{cunningham-roe:13a}*{Def. 1.1}, as linear character sheaves when $G$ is smooth but
+not necessarily commutative.
+Let $\CSab(G)$ denote the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu) \in \CS(G)$ and
+$\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism in $\CS(G\der)$.
+A morphism $(\cs{L},\mu,\beta)\to (\cs{L}',\mu',\beta')$ is a morphism $\alpha : (\cs{L},\mu)\to (\cs{L}',\mu')$
+in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{G\der}$.  We will define commutative character sheaves
+as a subcategory of $\CSab(G)$, but we first relate $\CSab(G)$ to $\CS(G\ab)$.  Let $q : G \to G\ab$ be the quotient map.
+\todo{Define $q\ab^* : \CS(G\ab) \to \CSab(G)$; missing definition of $\beta$ in the following commented section}
+%Now suppose $q : G \to Q$ is a regular epimorphism of smooth group schemes with kernel pair $(a,p)$
 %\[
 %\begin{tikzcd}
-%\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
-%\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
-%& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
+%H\times G
+% \arrow[shift left=2]{r}{a}
+%  \arrow[shift right=2,swap]{r}{p}
+%&
+%G 
+%\arrow{r}{q}
+%& 
+%Q.
 %\end{tikzcd}
 %\]
-Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
-\begin{equation}\label{E3}
-\begin{tikzcd}
-\arrow{d}[swap]{\nu} a^*\cs{L} \arrow{r}{a^*(\alpha)} & a^*\cs{L}' \arrow{d}{\nu'} \\
-p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
-\end{tikzcd}
-\end{equation}
-commutes.
-This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.
-The reader will recognize this notion as the Weil sheaf version of equivariant sheaves for the action $a$ of $H$ on $G$, as can be found, for example, in \cite{bernstein-lunts:equivariant}*{0.2}.
-
-\subsubsection{Equivariant linear character sheaves}\label{ssec:equivariant2}
-
-With reference to Section~\ref{ssec:equivariant1}, suppose now that $H$ acts on $G$ through group homomorphisms: $a(h, m(g_1,g_2)) = m(a(h, g_1), a(h, g_2))$.
-
-We define an $H$-equivariant linear character sheaf on $G$ to be a triple $(\cs{L},\mu, \nu)$, where $(\cs{L},\mu)$ is a linear character sheaf and $(\cs{L},\nu)$ is an $H$-equivariant local system.
-We require that $\mu$ be compatible with $\nu$ in the following sense.
-We define morphisms:
-\begin{align*}
-c_0 : H\times G \times G &\to H\times G \times H \times G \\
-(h,g_1,g_2) &\mapsto (h,g_1,h,g_2); \\
-c_1 : H \times G\times G &\to G\times G \\
-(h, g_1, g_2) &\mapsto (hg_1,hg_2); \\
-c_2 : H \times G\times G &\to H\times G \\
-(h,g_1,g_2) &\mapsto (h, g_1g_2); \\
-c_3 : H \times G\times G &\to G\times G \\
-(h, g_1, g_2) &\mapsto (g_1, g_2).
-\end{align*}
-We require that the following diagram of Weil local systems on $H \times G\times G$ commutes: %\todo{Something's wrong: the top left actually requires $a \circ c_2 = m \circ c_1$, which isn't true.}
-\begin{equation}\label{ECS1}
-\begin{tikzcd}[column sep=30]
-\ & \arrow{dl}{a\circ c_2 = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{dr}[swap]{p\circ c_2 = m\circ c_3}  &  \\
-\arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} &&& c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
-c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{dr}{p_i\circ c_1 = a\circ p_i\circ c_0} &&& \arrow{dl}[swap]{p\circ p_i\circ c_0 = p_i \circ c_3} c_3^*(\cs{L}\boxtimes \cs{L}) \\
- & c_0^*(a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{c_0^*(\nu\boxtimes \nu)} & c_0^*(p^*\cs{L} \boxtimes p^*\cs{L}) & 
-\end{tikzcd}
-\end{equation}
-Note that $a\circ c_2 = m\circ c_1$ precisely because $H$ acts on $G$ through group homomorphisms.
-
-%On stalks, this condition is
+%Let $(\cs{L}_0, \mu_0)$ be a linear character sheaf on $Q$ and set $(\cs{L}, \mu) \ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$.
+%Consider the functor
 %\[
-%\begin{tikzcd}
-%\arrow{d}[swap]{\mu_{(h\cdot g_1, h\cdot g_2)}} \cs{L}_{(h\cdot g_1)(h\cdot g_2)} & \arrow[equal]{l}  \cs{L}_{h\cdot(g_1 g_2)} \arrow{r}{\nu_{(h, g_2 g_2)}} & \cs{L}_{g_1 g_2} \arrow[equal]{r} & \cs{L}_{g_1 g_2} \arrow{d}{\mu_{(g_1,g_2)}} \\
-%\cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow[equal]{r} & \cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow{r}{\nu_{(h,g_1)}\otimes \nu_{(h,g_2)}} & \cs{L}_{g_1}\otimes \cs{L}_{g_2} & \arrow[equal]{l} \cs{L}_{g_1} \otimes \cs{L}_{g_2},
+%q^* : \CS(Q) \to \CS(G)
+%\]
+%given on objects by $(\cs{L}_0,\mu_0) \mapsto (\cs{L}, \mu)$; see \cite{cunningham-roe:13a}*{Lem 1.4}.
+%%To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$,
+%%verify \cite{cunningham-roe:13a}, CS.3], arguing as in \cite{cunningham-roe:13a}].
+%%The linear character sheaf $(\cs{L},\mu)$ on $G$ comes equipped with a canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of isomorphisms.
+%\[
+%\begin{tikzcd}[column sep=40]
+%a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{r}{\nu} &  \arrow[equal]{d} p^*\cs{L} \\
+%a^* ( q^*\cs{L}_0) \arrow{r}{q\circ a = q\circ p}
+%& p^* (q^*\cs{L}_0)
 %\end{tikzcd}
 %\]
-%for all $(h,g_1,g_2)\in H\times G\times G$.
-
-A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves.
-%so
-%\begin{equation}\label{CS4}
+%Since this isomorphism satisfies \eqref{ECS1}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
+%If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(Q)$, 
+%then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha$ is a morphism in $\CS(G)$.
+%These simple observations define the comparison functor
+%\[
+%q_H^* : \CS(Q) \to CS_H(G)
+%\]
+%and show that the functor $q^* : \CS(Q) \to \CS(G)$ factors according to the following commuting diagram of functors
+%\begin{equation}\label{qH}
 %\begin{tikzcd}
-%\arrow{d}[swap]{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
-%\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
+%\CS(G) &\arrow{l}[swap]{q^*} 
+%\CS(Q) \arrow{dl}{q_H^*}\\
+%\arrow{u}{\text{forget}} \CS_{H}(G). & 
 %\end{tikzcd}
 %\end{equation}
-%commutes; see also \cite{cunningham-roe:13a}, CS.4].
-%
-Let $\CS_H(G)$ be the category of $H$-equivariant linear character sheaves on $G$.
-
-%Is $\CS_H(G)$ a rigid monoidal category?
-
-%If $(\cs{L},\mu,\nu)$ and $(\cs{L},\mu,\nu')$ in $\CS_H(G)$, then $\nu = \nu'$?
-
-\begin{lemma}\label{lem:HH}
-If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ and $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are morphisms of $H\times H$-equivariant Weil local systems on $G\times G$.
-\end{lemma}
-
+%The definition of $q_H^* : \CS(Q)\to \CS_H(G)$ will be revisited in the proof of the following result.
+
+%\begin{proposition} \label{prop:Gder_triv}
+%Suppose $G$ is a smooth group scheme and $(\cs{L},\mu) \in \CS(G)$.
+%Then the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $(\cs{L},\mu) \cong q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, for some $(\cs{L}\ab,\mu\ab) \in \CS(G\ab)$.
+%\end{proposition}
+%Proposition~\ref{prop:Gder_triv} will be proven in Section \ref{ssec:proof1}.
+
+\begin{proposition} \label{prop:CSGabab}
+Suppose $G$ is a smooth group scheme.  Then the functor $q\ab^* : \CS(G\ab) \to \CSab(G)$ is an equivalence of categories.
+\end{proposition}
 \begin{proof}
-Define
-\begin{align*}
-d : H\times H\times G\times G &\to H\times G\times H\times G \\
-(h_1,h_2,g_1,g_2) &\mapsto (h_1, g_1, h_2, g_2)\\
-a_2 : H\times G\times H\times G &\to G\times G \\
-(h_1,g_1,h_2,g_2) &\mapsto (h_1g_1, h_2g_2) \\
-p_2 : H\times G\times H\times G &\to G\times G \\
-(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2) \\
-\theta_2 : H \times G \times H \times G &\to H \times G \times H \times G \\
-(h_1,g_1,h_2,g_2) &\mapsto (h_2,g_2,h_1,g_1).
-\end{align*}
-The following diagram defines the isomorphisms needed to see that both $m^*\cs{L}$ and $\cs{L}\boxtimes\cs{L}$ are $H\times H$-equivariant Weil local systems.
-\[
-\begin{tikzcd}[column sep=40]
-\arrow{d}[swap]{a_2^*(\mu)} a_2^* (m^*\cs{L}) \arrow[dashed]{r} 
-	& \arrow{d}{p_2^*(\mu)} p_2^*(m^*\cs{L})\\
-\arrow{d}[swap]{a_2= (a\times a)\circ d} a_2^*(\cs{L}\boxtimes\cs{L}) \arrow[dashed]{r} 
-	& \arrow{d}{p_2= (p\times p)\circ d} p_2^*(\cs{L}\boxtimes\cs{L}) \\
-%d^* (a\times a)^* (\cs{L}\boxtimes\cs{L}) & d^* (p\times p)^* (\cs{L}\boxtimes\cs{L}) \\
-d^* (a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{d^*(\nu\boxtimes \nu)}& d^*(p^*\cs{L}\boxtimes p^*\cs{L}) 
-\end{tikzcd}
-\]
-The dashed arrows both satisfy \eqref{E1} and \eqref{E2} as they apply here.
-This diagram also shows that $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of equivariant sheaves, since it satisfies \eqref{E3} as it applies here.
-The proof that $\theta^*(\cs{L}\boxtimes\cs{L})$ is $H\times H$ equivariant is also straightforward, since $a_2\circ \theta_2 = \theta \circ a_2$ and $p_2\circ \theta_2 = \theta \circ p_2$.
-Let $\nu_2 : a_2^*(\cs{L}\boxtimes\cs{L}) \to p_2^*(\cs{L}\boxtimes\cs{L})$ be the middle horizontal isomorphism of Weil local systems, above. 
-To see that
-\[
-\begin{tikzcd}
-a_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r}{a_2^*(\vartheta)} \arrow{d}[swap]{\nu_2} 
-	& a_2^*\theta^*(\cs{L}\boxtimes\cs{L}) \arrow{d}{\theta^*(\nu_2)} \\
-p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r}{p_2^*(\vartheta)} 
-	& p_2^*\theta^*(\cs{L}\boxtimes\cs{L})
-\end{tikzcd}
-\]
-commutes, consider the commuting diagram of stalks, below.
-\[
-\begin{tikzcd}
-\cs{L}_{h_1g_1}\otimes\cs{L}_{h_2g_2} \arrow{r}{\vartheta}  \arrow{d}[swap]{\nu_2} 
-	& \cs{L}_{h_2g_2} \otimes\cs{L}_{h_1g_1}  \arrow{d}{\nu_2} \\
-\cs{L}_{g_1}\otimes\cs{L}_{g_2} \arrow{r}{\vartheta}  
-	& \cs{L}_{g_2} \otimes\cs{L}_{g_1}
-\end{tikzcd}
-\]
-\end{proof}
-
-\subsubsection{Descent along a torsor}\label{ssec:descent}
-
-Now suppose $q : G \to Q$ is a regular epimorphism of smooth group schemes with kernel pair $(a,p)$
-\[
-\begin{tikzcd}
-H\times G
- \arrow[shift left=2]{r}{a}
-  \arrow[shift right=2,swap]{r}{p}
-&
-G 
-\arrow{r}{q}
-& 
-Q.
-\end{tikzcd}
-\]
-Let $(\cs{L}_0, \mu_0)$ be a linear character sheaf on $Q$ and set $(\cs{L}, \mu) \ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$.
-Consider the functor
-\[
-q^* : \CS(Q) \to \CS(G)
-\]
-given on objects by $(\cs{L}_0,\mu_0) \mapsto (\cs{L}, \mu)$; see \cite{cunningham-roe:13a}*{Lem 1.4}.
-%To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$, verify \cite{cunningham-roe:13a}, CS.3], arguing as in \cite{cunningham-roe:13a}].
-The linear character sheaf $(\cs{L},\mu)$ on $G$ comes equipped with a canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of isomorphisms.
-\[
-\begin{tikzcd}[column sep=40]
-a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{r}{\nu} &  \arrow[equal]{d} p^*\cs{L} \\
-a^* ( q^*\cs{L}_0) \arrow{r}{q\circ a = q\circ p}
-& p^* (q^*\cs{L}_0)
-\end{tikzcd}
-\]
-Since this isomorphism satisfies \eqref{ECS1}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
-If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(Q)$, 
-then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha$ is a morphism in $\CS(G)$.
-%\todo{I find myself having to make many references to \cite{cunningham-roe:13a}] and promising that the results there adapt to the noncommutative group case.
-It makes me uneasy, but the alternative is to actually repeat the proofs here, with the weaker hypothesis on $G$, which would be ugly.
-I'm just agonizing out loud, I guess.}
-These simple observations define the comparison functor
-\[
-q_H^* : \CS(Q) \to CS_H(G)
-\]
-and show that the functor $q^* : \CS(Q) \to \CS(G)$ factors according to the following commuting diagram of functors
-\begin{equation}\label{qH}
-\begin{tikzcd}
-\CS(G) &\arrow{l}[swap]{q^*} 
-\CS(Q) \arrow{dl}{q_H^*}\\
-\arrow{u}{\text{forget}} \CS_{H}(G). & 
-\end{tikzcd}
-\end{equation}
-The definition of $q_H^* : \CS(Q)\to \CS_H(G)$ will be revisited in the proof of the following result.
-
-\begin{lemma}\label{lem:torsor}
-If $q : G \to Q$ is an $H$-torsor in the fpqc topology 
-then $q_H^*: \CS(Q) \to \CS_H(G)$ is an equivalence.
-\end{lemma}
-
-\begin{proof}
-%First we observe that the comparison functor $\Loc(Q) \to \Loc_H(G)$ is an equivalence.
-%To see this, first recall that $\Loc$ is a stack on schemes over $\Fq$ in the Zariski topology.
-%Then, observe that the comparison functor for Weil local systems is an equivalence for flat surjective morphisms of affine schemes over $\Fq$.
-%It follows that $\Loc$ is a stack over schemes over $\Fq$ in the fpqc topology; see \cite{Vistoli:notes}*{Lem 4.25} for example.
-%(This is a slight variation on the argument showing that quasicoherent sheaves are a stack over schemes in the fpqc topology; see \cite{Vistoli:notes}*{Thm 4.23} for example.)
-Since $q : G\to Q$ is an $H$-torsor in the fpqc topology, is follows from descent theory that the comparison functor $\Loc(Q) \to \Loc_H(G)$ is an equivalence; argue as in \cite{Vistoli:notes}*{Thm 4.46}, for example.
-%
+To simplify notation below, set $H=G\der$.
+Since the quotient $q : G \to G\ab$ is an $H$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, 
+it is also an $H$-torsor in the fpqc topology.
+It now follows from descent theory that the comparison functor $\Loc(G\ab) \to \Loc_H(G)$ is an equivalence; argue as in \cite{Vistoli:notes}*{Thm 4.46}, for example.
+\todo{Need to adapt the following proof to the definition of $q\ab^*$.}
+
 For use below, we write $L_1 : \Loc(Q) \to \Loc_H(G)$ for the comparison functor, $R_1 : \Loc_H(G) \to \Loc(Q)$ for its adjoint, and $(\epsilon_1, \eta_1)$ for the counit and unit of the adjunction.
@@
 
-\subsubsection{Quotient by a closed subgroup}\label{ssec:closed}
-
-We now suppose that $j : H \hookrightarrow G$ is a closed subgroup scheme over $\Fq$
-and that the action $a : H\times G\to G$ is obtained by restricting the action
-$m : G \times G\to G$ to $H\times G$.  In this context, we are able to replace
-$\nu : a^*\cs{L} \to p^*\cs{L}$ with an isomorphism $\beta : \cs{L}_H \to (\EE)_H$.
-Let $\CS^H(G)$ be the category of triples $(\cs{L},\mu,\beta)$ with $(\cs{L},\mu) \in \CS(G)$
-and $\beta : \cs{L}\vert_H \to (\EE)_H$ an isomorphism in $\CS(H)$;
-a morphism $(\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ in $\CS^H(G)$ is a morphism
-$\alpha: \cs{L} \to \cs{L}'$ in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{H}$.
-
-\begin{lemma}\label{lem:beta}
-If $H\hookrightarrow G$ is a closed subgroup scheme over $\Fq$ then $\CS_H(G)$ is equivalent to $\CS^H(G)$.
-\end{lemma}
+\begin{corollary} 
+If $G$ is a smooth group scheme and $(\cs{L},\mu) \in \CS(G)$, then
+the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $(\cs{L},\mu) \cong q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, for some $(\cs{L}\ab,\mu\ab) \in \CS(G\ab)$.
+\todo{What is the ``kernel'' of the forgetful functor?
+Ie, is there a natural parameterization of the possible choices of $\beta$?}
+\end{corollary}
+
 \begin{proof}
-Define $f : H\times G \to G\times G$ by $f(h,g) = (j(h),g)$ and note that $a = m\circ f$.
-Write $p_1: G\times G\to G$ for projection to the first component and $p_2 : G\times G \to G$ for projection to the second.
-We may pass between $\nu$ and $\beta$ via the following diagram.
-\[
-\begin{tikzcd}[column sep=30]
-\ & a^*\cs{L} \arrow{dl}{m\circ f = a} \arrow{r}{\nu} & p^*\cs{L} & \\
-f^* m^*\cs{L} \arrow{dr}{f^*\mu} &&& (\EE)_{H} \boxtimes \cs{L} \arrow{ul} \\ 
-& f^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_1 \circ f = j}[swap]{p_2\circ f = \id}  & 
-\cs{L}\vert_{H} \boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id} & 
-\end{tikzcd}
-\]
-It is a straightforward, tedious exercise to show that the conditions \eqref{E1}, \eqref{E2} and \eqref{ECS1} 
-on $\nu$ are equivalent to the condition that the isomorphism of Weil local systems
-$\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is an isomorphism in the category of of linear character sheaves on $H$.
-\end{proof}
-
-We can now give the missing proofs from Section \ref{ssec:noncomdef}.
-
-\subsubsection{Proof of Proposition~\ref{prop:Gder_triv}}\label{ssec:proof1}
-
-To simplify notation below, set $H=G\der$
+As above, we set $H=G\der$
 and let $j : H\hookrightarrow G$ be the inclusion. 
@@
 \CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q_{H}^*} \\
- \CS'(G)  \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}} &  \CS_{H}(G) \arrow{u}{\text{forget}}  & 
-\end{tikzcd}
-\]
-%
-Here we use the notation $\CS'(G)$ from Section~\ref{ssec:noncomdef} and the observation that $\CS'(G)$ is precisely the category $\CS^{H}(G)$ from Section~\ref{ssec:closed} for $H=G\der$.
-%
-Since the quotient $q : G \to G\ab$ is an $H$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, 
-it is also an $H$-torsor in the fpqc topology.
-It now follows from Lemma~\ref{lem:torsor} that the comparison functor $\CS(G\ab)\to \CS_{H}(G)$ is an equivalence.
-%\todo{Did I compare these topologies correctly? fpqc is finer than fppf}
-%
-On the other hand, by Lemma~\ref{lem:beta}, $\CS'(G) \to \CS_{H}(G)$, defined by $(\cs{L},\mu,\beta)\mapsto (\cs{L},\mu, \nu)$, is an equivalence.
+& \CSab(G) \arrow{u}{\text{forget}}  & 
+\end{tikzcd}
+\]
 
 Now, suppose $(\cs{L},\mu)\in \CS(G)$ and there is an isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ in $\CS(H)$.
-Then $(\cs{L},\mu,\beta) \in \CS'(G)$.
-We have just seen that $\CS'(G)$, $\CS_H(G)$ and $\CS(G\ab)$ are equivalent categories.
-Let $(\cs{L},\mu,\beta) \mapsto (\cs{L},\mu,\nu)$ under the equivalence $\CS'(G) \to \CS_H(G)$ described above.
-Then $(\cs{L},\mu,\nu) \iso q_H^*(\cs{L}\ab,\mu\ab)$ in $\CS_H(G)$, for some $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$.
+Then $(\cs{L},\mu,\beta) \in \CSab(G)$.
+By Proposition \ref{prop:CSGabab}, $(\cs{L},\mu,\beta) \iso q\ab^*(\cs{L}\ab,\mu\ab)$ for some $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$.
 Applying the forgetful functor $\CS_H(G)\to \CS(G)$ to this isomorphism, it follows that $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, as desired.
@@
 Since $q\circ j = 1$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{H}$ in $\CS(H)$.
-This completes the proof of Proposition~\ref{prop:Gder_triv}.
-%\end{proof}
-
-\subsubsection{Proof of Theorem~\ref{thm:Gab}}\label{ssec:proof2}
-
-%\begin{proof}[Proof of Theorem~\ref{thm:Gab}] 
-Here we use notation from the proof of Proposition~\ref{prop:Gder_triv};
-in particular, $H = G\der$.
+\end{proof}
+
+%\subsubsection{Equivariant Weil local systems}\label{ssec:equivariant1}
+%
+%Let $G$ be a smooth group scheme over $k$, as above.
+%Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
+%Let $a : H \times G\to G$ be an action of $H$ on $G$ 
+%%group action compatible with the group structure on $G$ 
+%and write $p : H\times G \to G$ for projection. 
+%Consider the morphisms
+%\[
+%\begin{tikzcd}
+%H \times H \times G 
+%\arrow[shift left=4]{r}{b_1, b_2, b_3} 
+%\arrow{r}{}
+%\arrow[shift right=4]{r}{} 
+%& H \times G 
+%\arrow[shift left=2]{r}{a}
+%\arrow[shift right=2]{r}[swap]{p}
+% & G 
+%\end{tikzcd}
+%\]
+%defined by 
+%\begin{align*}
+%b_1(h_1,h_2,g) &= (h_1h_2,g) \\
+%b_2(h_1,h_2,g) &= (h_1,h_2g) \\
+%b_3(h_1,h_2,g) &= (h_2,g).
+%\end{align*}
+%Note that
+%\begin{align*}
+%a\circ b_1 &= a\circ b_2 \\
+%a\circ b_3 &= p\circ b_2 \numberthis \label{eqn:bap}\\
+%p\circ b_1 &= p\circ b_3.
+%\end{align*}
+%Define $s : G\to H\times G$ by $s(g) = (1,g)$.
+%An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
+%\[
+%\nu : a^*\cs{L} \to p^*\cs{L}
+%\] 
+%of Weil local systems on $H\times G$ such that 
+%\begin{equation}\label{E1}
+%s^*(\nu) = \id_{\cs{L}}
+%\end{equation}
+%and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes. 
+%\begin{equation}\label{E2}
+%\begin{tikzcd}
+%\ &  \arrow{dl}{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
+%b_1^* a^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
+%& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L} & 
+%\end{tikzcd}
+%\end{equation}
+%In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors
+%on Weil sheaves derived from equations \eqref{eqn:bap}; so, for example, the top left isomorphism
+%comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
+%%On stalks, this condition is ...
+%%\[
+%%\begin{tikzcd}
+%%\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
+%%\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
+%%& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
+%%\end{tikzcd}
+%%\]
+%Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
+%\begin{equation}\label{E3}
+%\begin{tikzcd}
+%\arrow{d}[swap]{\nu} a^*\cs{L} \arrow{r}{a^*(\alpha)} & a^*\cs{L}' \arrow{d}{\nu'} \\
+%p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
+%\end{tikzcd}
+%\end{equation}
+%commutes.
+%This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.
+%The reader will recognize this notion as the Weil sheaf version of equivariant sheaves for
+%the action $a$ of $H$ on $G$, as can be found, for example, in \cite{bernstein-lunts:equivariant}*{0.2}.
+
+We may now define commutative character sheaves on $G$.
+
+Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows.
+Let $i : G \to G$ be inversion and $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
+Both are smooth morphisms of $\Fq$-schemes.
+Set $m' = i \circ m \circ \theta$; we have $j\circ c = m \circ (m \times m')$.
+Then $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms below.
+\begin{equation}
+\begin{tikzcd}
+\arrow[equal]{d} c^* (\cs{L}\vert_{G\der}) \arrow{r}{c^*(\beta)} 
+	&  c^*((\EE)_{G\der}) \arrow[equal]{d} \\
+\arrow{d}[swap]{j\circ c = m \circ (m \times m')} c^* j^* \cs{L} 
+	&   (\EE)_{G\times G} \\
+(m \times m')^* m^* \cs{L} \arrow{d}[swap]{(m \times m')^*(\mu)} 
+	&  m^*\cs{L} \otimes \theta^* m^* i^* \cs{L}  \arrow[dashed]{u}[swap]{\gamma'} \\
+(m \times m')^* (\cs{L} \boxtimes \cs{L}) \arrow[equal]{r} 
+	& m^*\cs{L} \otimes (m')^*\cs{L} \arrow{u}[swap]{m' = i\circ m\circ \theta} 
+\end{tikzcd}
+\end{equation}
+In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations; so, for example, the middle left isomorphism comes from $(m\times m')^* m^* \iso c^* j^*$ since $j\circ c = m \circ (m \times m')$.
+Using the monoidal structure of the category of Weil local systems on $G\times G$, the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ defines an isomorphism
+\[
+m^*\cs{L} \to (\theta^* m^* i^*\cs{L})^\vee.
+\]
+Applying the canonical isomorphisms $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ and $i^*(\cs{L}^\vee) \cong \cs{L}$, this map provides the promised isomorphism
+\[
+\begin{tikzcd}
+\gamma : m^*\cs{L} \arrow{r} & \theta^* m^* \cs{L}.
+\end{tikzcd}
+\]
+
+\begin{definition}\label{def:CCS}
+The category $\CCS(G)$ of commutative character sheaves on $G$ is the full subcategory of $\CSab(G)$ consisting of triples $(\cs{L},\mu,\beta)$ such that the following diagram of Weil sheaves on $G \times G$ commutes:
+  \[
+  \begin{tikzcd}[row sep=30]
+   m^*\cs{L} \arrow{d}[swap]{\gamma} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
+   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L}).
+  \end{tikzcd}
+  \]
+Here $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ above. 
+\end{definition}
+
+\subsection{Objects and maps in commutative character sheaves} \label{ssec:obmor}
+
+Suppose $G$ is commutative, so $G\der = 1$. 
+Suppose $(\cs{L},\mu,\beta)$ is an object in $\CSab(G)$.
+Then $\beta : \cs{L}_1\to \EE$ is an isomorphism in $\CS(1)$, which is unique by \cite{cunningham-roe:13a}*{Thm 3.9}.
+Tracing through the construction of $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ from $\beta : \cs{L}_1\to \EE$, we find 
+%\todo{I'm having some trouble seeing this.} 
+that $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ is the canonical isomorphism coming from the equation $m = m \circ \theta$. 
+Thus, when $G$ is commutative, Definition~\ref{def:CCS} agrees with Definition~\ref{def:CCScom}.
+The next result generalizes this observation.
+
+\begin{theorem}\label{thm:Gab}
+%Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
+Pull-back along the abelianization $q : G \to G\ab$
+defines an equivalence of categories \todo{Is this trivial now?}
+\[
+\CCS(G\ab) \to \CCS(G).
+\]
+\end{theorem}
+
+\begin{proof}
+We again write $H$ for $G\der$.
 By Definition~\ref{def:CCScom}, $\CCS(G\ab) \to \CS(G\ab)$ is a full subcategory.
 Since the comparison functor $\CS(G\ab) \to \CS_{H}(G)$ is an equivalence, it determines a full subcategory $\CCS_{H}(G)$ which is equivalent to $\CCS(G\ab)$, as pictured below.
-The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of $\CCS_H(G)$ under the equivalence $\CS_{H}(G) \to \CS'(G)$ is $\CCS(G)$.
+The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of $\CCS_H(G)$ under the equivalence $\CS_{H}(G) \to \CSab(G)$ is $\CCS(G)$.
 \[
 \begin{tikzcd}[row sep=30, column sep=40]
-\CS(H) 
-& \arrow{l}[swap]{j^*} \CS(G) 
-&\arrow{l}[swap]{q^*} 
-\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q_{H}^*} \\
-\CS'(G)  \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}} 
-&  \CS_{H}(G) \arrow{u}{\text{forget}}  
-&  %\arrow[bend left=35pt, dashed]{dll} 
-\CCS(G\ab) \arrow{u}[swap]{\text{full sub}} \arrow{dl}{\text{equiv}} \\
-\CCS(G) \arrow{u}{\text{full sub}} \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}}
-& \arrow{u}{\text{full sub}}  \CCS_{H}(G) 
-& 
-\end{tikzcd}
-\]
-
-Let $(\cs{L},\mu,\nu)$ be the image of $(\cs{L},\mu,\beta)\in \CS'(G)$ and of $(\cs{L}\ab,\mu\ab)$ under $q_H^*$;
+\CSab(G) & \CS(G\ab) \arrow{l}{\text{equiv}}[swap]{q\ab^*} \\
+\CCS(G) \arrow{u}{\text{full sub}} & \CCS(G\ab) \arrow{u}[swap]{\text{full sub}} \arrow{l}[swap]{\text{equiv}}
+\end{tikzcd}
+%\begin{tikzcd}[row sep=30, column sep=40]
+%\CS(H) 
+%& \arrow{l}[swap]{j^*} \CS(G) 
+%&\arrow{l}[swap]{q^*} 
+%\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q_{H}^*} \\
+%\CS'(G)  \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}} 
+%&  \CS_{H}(G) \arrow{u}{\text{forget}}  
+%&  %\arrow[bend left=35pt, dashed]{dll} 
+%\CCS(G\ab) \arrow{u}[swap]{\text{full sub}} \arrow{dl}{\text{equiv}} \\
+%\CCS(G) \arrow{u}{\text{full sub}} \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}}
+%& \arrow{u}{\text{full sub}}  \CCS_{H}(G) 
+%& 
+%\end{tikzcd}
+\]
+
+Let $(\cs{L},\mu,\nu)$ be the image of $(\cs{L},\mu,\beta)\in \CSab(G)$ and of $(\cs{L}\ab,\mu\ab)$ under $q_H^*$;
 we must show that $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
@@
 if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G)$.
-This completes the proof of Theorem~\ref{thm:Gab}.
-%This also defines the functor $\CCS(G\ab) \to \CCS(G)$ by the dashed arrow in the diagram above.
+
+\end{proof}
+
+%
+%Sections~\ref{ssec:equivariant1}, \ref{ssec:equivariant2}, \ref{ssec:descent} and \ref{ssec:closed} set up machinery needed to prove Theorem~\ref{thm:Gab}.
+%The precise definition of the functor $\CCS(G\ab) \to \CCS(G)$ will be given with the proof of Theorem~\ref{thm:Gab}, in Section~\ref{ssec:proof2}.
+
+%\subsubsection{Equivariant linear character sheaves}\label{ssec:equivariant2}
+%
+%With reference to Section~\ref{ssec:equivariant1}, suppose now that $H$ acts on $G$ through group homomorphisms: $a(h, m(g_1,g_2)) = m(a(h, g_1), a(h, g_2))$.
+%
+%We define an $H$-equivariant linear character sheaf on $G$ to be a triple $(\cs{L},\mu, \nu)$,
+%where $(\cs{L},\mu)$ is a linear character sheaf and $(\cs{L},\nu)$ is an $H$-equivariant local system.
+%We require that $\mu$ be compatible with $\nu$ in the following sense.
+%We define morphisms:
+%\begin{align*}
+%c_0 : H\times G \times G &\to H\times G \times H \times G \\
+%(h,g_1,g_2) &\mapsto (h,g_1,h,g_2); \\
+%c_1 : H \times G\times G &\to G\times G \\
+%(h, g_1, g_2) &\mapsto (hg_1,hg_2); \\
+%c_2 : H \times G\times G &\to H\times G \\
+%(h,g_1,g_2) &\mapsto (h, g_1g_2); \\
+%c_3 : H \times G\times G &\to G\times G \\
+%(h, g_1, g_2) &\mapsto (g_1, g_2).
+%\end{align*}
+%We require that the following diagram of Weil local systems on $H \times G\times G$ commutes:
+%\todo{Something's wrong: the top left actually requires $a \circ c_2 = m \circ c_1$, which isn't true.}
+%\begin{equation}\label{ECS1}
+%\begin{tikzcd}[column sep=30]
+%\ & \arrow{dl}{a\circ c_2 = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{dr}[swap]{p\circ c_2 = m\circ c_3}  &  \\
+%\arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} &&& c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
+%c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{dr}{p_i\circ c_1 = a\circ p_i\circ c_0} &&& \arrow{dl}[swap]{p\circ p_i\circ c_0 = p_i \circ c_3} c_3^*(\cs{L}\boxtimes \cs{L}) \\
+% & c_0^*(a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{c_0^*(\nu\boxtimes \nu)} & c_0^*(p^*\cs{L} \boxtimes p^*\cs{L}) & 
+%\end{tikzcd}
+%\end{equation}
+%Note that $a\circ c_2 = m\circ c_1$ precisely because $H$ acts on $G$ through group homomorphisms.
+%
+%
+%%On stalks, this condition is
+%%\[
+%%\begin{tikzcd}
+%%\arrow{d}[swap]{\mu_{(h\cdot g_1, h\cdot g_2)}} \cs{L}_{(h\cdot g_1)(h\cdot g_2)} & \arrow[equal]{l}  \cs{L}_{h\cdot(g_1 g_2)} \arrow{r}{\nu_{(h, g_2 g_2)}} & \cs{L}_{g_1 g_2} \arrow[equal]{r} & \cs{L}_{g_1 g_2} \arrow{d}{\mu_{(g_1,g_2)}} \\
+%%\cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow[equal]{r} & \cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow{r}{\nu_{(h,g_1)}\otimes \nu_{(h,g_2)}} & \cs{L}_{g_1}\otimes \cs{L}_{g_2} & \arrow[equal]{l} \cs{L}_{g_1} \otimes \cs{L}_{g_2},
+%%\end{tikzcd}
+%%\]
+%%for all $(h,g_1,g_2)\in H\times G\times G$.
+
+%A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$
+%is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves.
+%%so
+%%\begin{equation}\label{CS4}
+%%\begin{tikzcd}
+%%\arrow{d}[swap]{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
+%%\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
+%%\end{tikzcd}
+%%\end{equation}
+%%commutes; see also \cite{cunningham-roe:13a}, CS.4].
+%%
+%Let $\CS_H(G)$ be the category of $H$-equivariant linear character sheaves on $G$.
+%
+%%Is $\CS_H(G)$ a rigid monoidal category?
+%
+%%If $(\cs{L},\mu,\nu)$ and $(\cs{L},\mu,\nu')$ in $\CS_H(G)$, then $\nu = \nu'$?
+%
+%\begin{lemma}\label{lem:HH}
+%If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ and
+%$\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are morphisms of $H\times H$-equivariant Weil local systems on $G\times G$. 
+%\end{lemma}
+%
+%\begin{proof} 
+%Define
+%\begin{align*}
+%d : H\times H\times G\times G &\to H\times G\times H\times G \\
+%(h_1,h_2,g_1,g_2) &\mapsto (h_1, g_1, h_2, g_2)\\
+%a_2 : H\times G\times H\times G &\to G\times G \\
+%(h_1,g_1,h_2,g_2) &\mapsto (h_1g_1, h_2g_2) \\
+%p_2 : H\times G\times H\times G &\to G\times G \\
+%(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2) \\
+%\theta_2 : H \times G \times H \times G &\to H \times G \times H \times G \\
+%(h_1,g_1,h_2,g_2) &\mapsto (h_2,g_2,h_1,g_1).
+%\end{align*}
+%The following diagram defines the isomorphisms needed to see that both $m^*\cs{L}$ and $\cs{L}\boxtimes\cs{L}$ are $H\times H$-equivariant Weil local systems.
+%\[
+%\begin{tikzcd}[column sep=40]
+%\arrow{d}[swap]{a_2^*(\mu)} a_2^* (m^*\cs{L}) \arrow[dashed]{r} 
+%	& \arrow{d}{p_2^*(\mu)} p_2^*(m^*\cs{L})\\
+%\arrow{d}[swap]{a_2= (a\times a)\circ d} a_2^*(\cs{L}\boxtimes\cs{L}) \arrow[dashed]{r} 
+%	& \arrow{d}{p_2= (p\times p)\circ d} p_2^*(\cs{L}\boxtimes\cs{L}) \\
+%%d^* (a\times a)^* (\cs{L}\boxtimes\cs{L}) & d^* (p\times p)^* (\cs{L}\boxtimes\cs{L}) \\
+%d^* (a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{d^*(\nu\boxtimes \nu)}& d^*(p^*\cs{L}\boxtimes p^*\cs{L}) 
+%\end{tikzcd}
+%\]
+%The dashed arrows both satisfy \eqref{E1} and \eqref{E2} as they apply here.
+%This diagram also shows that $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of equivariant sheaves, since it satisfies \eqref{E3} as it applies here.
+%The proof that $\theta^*(\cs{L}\boxtimes\cs{L})$ is $H\times H$ equivariant is also straightforward,
+%since $a_2\circ \theta_2 = \theta \circ a_2$ and $p_2\circ \theta_2 = \theta \circ p_2$.
+%Let $\nu_2 : a_2^*(\cs{L}\boxtimes\cs{L}) \to p_2^*(\cs{L}\boxtimes\cs{L})$ be the middle horizontal isomorphism of Weil local systems, above. 
+%To see that
+%\[
+%\begin{tikzcd}
+%a_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r}{a_2^*(\vartheta)} \arrow{d}[swap]{\nu_2} 
+%	& a_2^*\theta^*(\cs{L}\boxtimes\cs{L}) \arrow{d}{\theta^*(\nu_2)} \\
+%p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r}{p_2^*(\vartheta)} 
+%	& p_2^*\theta^*(\cs{L}\boxtimes\cs{L})
+%\end{tikzcd}
+%\]
+%commutes, consider the commuting diagram of stalks, below.
+%\[
+%\begin{tikzcd}
+%\cs{L}_{h_1g_1}\otimes\cs{L}_{h_2g_2} \arrow{r}{\vartheta}  \arrow{d}[swap]{\nu_2} 
+%	& \cs{L}_{h_2g_2} \otimes\cs{L}_{h_1g_1}  \arrow{d}{\nu_2} \\
+%\cs{L}_{g_1}\otimes\cs{L}_{g_2} \arrow{r}{\vartheta}  
+%	& \cs{L}_{g_2} \otimes\cs{L}_{g_1}
+%\end{tikzcd}
+%\]
 %\end{proof}
 
-\subsubsection{Proof of Corollary~\ref{cor:Gab}}\label{ssec:proof3}
-
+%\subsubsection{Quotient by a closed subgroup}\label{ssec:closed}
+%
+%We now suppose that $j : H \hookrightarrow G$ is a closed subgroup scheme over $\Fq$
+%and that the action $a : H\times G\to G$ is obtained by restricting the action
+%$m : G \times G\to G$ to $H\times G$.  In this context, we are able to replace
+%$\nu : a^*\cs{L} \to p^*\cs{L}$ with an isomorphism $\beta : \cs{L}_H \to (\EE)_H$.
+%Let $\CS^H(G)$ be the category of triples $(\cs{L},\mu,\beta)$ with $(\cs{L},\mu) \in \CS(G)$
+%and $\beta : \cs{L}\vert_H \to (\EE)_H$ an isomorphism in $\CS(H)$;
+%a morphism $(\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ in $\CS^H(G)$ is a morphism
+%$\alpha: \cs{L} \to \cs{L}'$ in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{H}$.
+%
+%\begin{lemma}\label{lem:beta}
+%If $H\hookrightarrow G$ is a closed subgroup scheme over $\Fq$ then $\CS_H(G)$ is equivalent to $\CS^H(G)$.
+%\end{lemma}
+%\begin{proof}
+%Define $f : H\times G \to G\times G$ by $f(h,g) = (j(h),g)$ and note that $a = m\circ f$.
+%Write $p_1: G\times G\to G$ for projection to the first component and $p_2 : G\times G \to G$ for projection to the second.
+%We may pass between $\nu$ and $\beta$ via the following diagram.
+%\[
+%\begin{tikzcd}[column sep=30]
+%\ & a^*\cs{L} \arrow{dl}{m\circ f = a} \arrow{r}{\nu} & p^*\cs{L} & \\
+%f^* m^*\cs{L} \arrow{dr}{f^*\mu} &&& (\EE)_{H} \boxtimes \cs{L} \arrow{ul} \\ 
+%& f^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_1 \circ f = j}[swap]{p_2\circ f = \id}  & 
+%\cs{L}\vert_{H} \boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id} & 
+%\end{tikzcd}
+%\]
+%It is a straightforward, tedious exercise to show that the conditions \eqref{E1}, \eqref{E2} and \eqref{ECS1} 
+%on $\nu$ are equivalent to the condition that the isomorphism of Weil local systems
+%$\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is an isomorphism in the category of of linear character sheaves on $H$.
+%\end{proof}
+
+Theorem~\ref{thm:Gab} shows that $\CCS(G)$ is a categorical solution to the problem that linear character sheaves on $G$ need not be trivial on $G\der$, as discussed at the beginning of Section~\ref{sec:noncom}.
+At the same time, changing $\CS(G)$ to $\CCS(G)$ resolves the lack of bijectivity in \cite{cunningham-roe:13a}*{Thm.
+3.6}.
+%
+We may also use Theorem~\ref{thm:Gab} to give a description of the morphisms and the isomorphism classes of objects in $\CCS(G)$.
+
+\begin{corollary}\label{cor:Gab}
+%Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
+The category $\CCS(G)$ is monoidal and there is a canonical isomorphism
+\[
+\CCSiso{G} \iso \Hom(G\ab(\Fq),\EEx).
+\]
+Every map in $\CCS(G)$ is either trivial or an isomorphism, and the automorphism group of any object in $\CCS(G)$ is canonically
+isomorphic to $\Hom(\pi_0(G\ab)_{\Frob{}},\EEx)$.
+\end{corollary}
+
+\begin{proof}
 Let us write $(\cs{L},\mu,\beta) \mapsto (\cs{L}\ab,\mu\ab)$ to indicate the equivalence appearing in Theorem~\ref{thm:Gab};
@@
 By \cite{cunningham-roe:13a}*{Thm 3.9},  $\Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab) = \Hom(\pi_0(G\ab)_{\Frob{}},\EEx)$.
+\end{proof}
+
+\subsection{Geometrization of characters} \label{ssec:geo}
+
+\begin{theorem}\label{thm:geo}
+%Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
+The trace of Frobenius $\TrFrob{} : \CCSiso{G}\to G(\Fq)^*$ fits into the following diagram,
+\[
+\begin{tikzcd}
+\ & & \CCSiso{G\ab} \arrow{d}{\TrFrob{}}[swap]{\iso} \arrow{r}{\iso} & \CCSiso{G} \arrow{d}{\TrFrob{}}& \\
+1 \arrow{r} & \Delta_G^* \arrow{r} & G\ab(k)^* \arrow{r} & G(k)^* \arrow{r} & 1,
+\end{tikzcd}
+\]
+where $\Delta_G$ is the image of the connecting homomorphism $G\ab(\Fq) \to \Hh^1(\Fq, G\der)$. 
+Thus the category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the following sense: for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $(\cs{L},\mu,\beta)$ in $\CCS(G)$ such that $\trFrob{\cs{L}} = \chi$.
+While the geometrization of $\chi : G(\Fq) \to \EEx$ is not unique, the group of isomorphism classes of possibilities are enumerated by $\Delta_G^*$.
+\end{theorem}
+
+\begin{proof}
+By the definition of $\Delta_G$, we have a short exact sequence
+\[
+1 \to G(k) / G\der(k) \to G\ab(k) \to \Delta_G \to 1.
+\]
+Applying $\Hom(-, \EEx)$ and using the fact that every homomorphism $G(k) \to \EEx$ vanishes on $G\der(k)$, we get
+\[
+1 \to \Delta_G^* \to G\ab(k)^* \to G(k)^* \to 1.
+\]
+By Theorem~\ref{thm:Gab}, the map $\CCSiso{G\ab} \to \CCSiso{G}$ is an isomorphism.
+Moreover, since both $\CCSiso{G\ab} \to \CCSiso{G}$ and $G\ab(k)^* \to G(k)^*$ are
+defined by pullback along $q$, the square in the statement of the theorem commutes.
+Finally, $\TrFrob{} : \CCSiso{G\ab} \to G\ab(k)^*$ is an isomorphism by Theorem \ref{thm:trfrobiso}.
+\end{proof}
+
+\begin{remark}
+Note that when $\Hh^1(k,G\der) = 0$ then $\CCSiso{G} \iso G(\Fq)^*$, so
+we succeed in geometrizing characters of $G(k)$ on the nose.
+\end{remark}
+
+%\todo{Masound's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case.
+So, I think the modification is easy: add mop to diagram 2.4 in Masoud's paper.
+\\ -CC}
+
+%\section{Descent to the Abelianization} \label{sec:descent}
+
+%In this section we use descent along the abelianization $q : G \to G\ab$ to prove Propositions~1.2 and 1.4, and Theorem~\ref{thm:Gab}.
+%This approach requires introducing equivariant linear character sheaves, as defined in Section~[].
+
+%We close this section by gathering together the main result of this paper in one place.
 

### 2017-04-06 Geometric types.tex
Starting the proof that  CS(Gab) = CSab(G)

@@
 \begin{proof}
-To simplify notation below, set $H=G\der$.
+%To simplify notation below, set $H=G\der$.
 Since the quotient $q : G \to G\ab$ is an $H$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, 
 it is also an $H$-torsor in the fpqc topology.  
-It now follows from descent theory that the comparison functor $\Loc(G\ab) \to \Loc_H(G)$ is an equivalence; argue as in \cite{Vistoli:notes}*{Thm 4.46}, for example.
+It now follows from descent theory that the comparison functor $L : \Loc(G\ab) \to \Loc_{G\der}(G)$ is an equivalence; argue as in \cite{Vistoli:notes}*{Thm 4.46}, for example. 
+Observe that $L$ followed by the forgetful functor $\Loc_{G\der}(G)\to  \Loc(G)$ coincides with $q^*: \Loc(G\ab)\to \Loc(G)$ and that, for $\cs{L}\ab\in \Loc(G\ab)$,  $L(\cs{L}\ab) = (\cs{L}, \nu)$ where $\cs{L} = q^*(\cs{L}\ab)$ and $\nu : m^*\cs{L}  \to p^*\cs{L}$ is an isomorphism, where $m : G\times G\to G$ is  multiplication and $p : G\times  G \to G$ is projection to the second component.
+
+Now set $G^2 \ceq G\times G$;  note that $G^2\ab =  G\ab \times G\ab$ and $G^2\der = G\der \times G\der$. Let $q_2 : G^2 \to G^2\ab$ be the abelianization quotient.  
+Let $L_2 : \Loc(G^2\ab) \to \Loc_{G^2\der}(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$.
+
+Now consider the category $\CSab'(G)$ of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)$ is a character sheaf on $G$ and $\nu :  m^*\cs{L} \to p^*\cs{L}$ is an isomorphism
+\[
+\begin{array}{rcl}
+\CS(G\ab) &\to& \CSab'(G) \\
+(\cs{L}\ab,\mu\ab) &\mapsto& (L(\cs{L}\ab), L_2(\mu\ab)) = (\cs{L},\nu,\mu),
+\end{array}
+\]
+where
+defined by
+
+Let $R :  \Loc_{G\der}(G)\to  \Loc(G\ab)$ be the right adjoint to $L$ and let  $R_2 :  \Loc_{G^2\der}(G^2)\to  \Loc(G^2\ab)$ be the right adjoint to $L_2$.
+
 \todo{Need to adapt the following proof to the definition of $q\ab^*$.}

### 2017-04-06 Geometric types.tex
Finished proof of Proposition 3.1

--- 2017-02-26 Geometric types.tex
@@
 
-%\tableofcontents
+\tableofcontents
 
@@
 as a subcategory of $\CSab(G)$, but we first relate $\CSab(G)$ to $\CS(G\ab)$.  Let $q : G \to G\ab$ be the quotient map.
-\todo{Define $q\ab^* : \CS(G\ab) \to \CSab(G)$; missing definition of $\beta$ in the following commented section}
+%\todo{Define $q\ab^* : \CS(G\ab) \to \CSab(G)$; missing definition of $\beta$ in the following commented section}
 %Now suppose $q : G \to Q$ is a regular epimorphism of smooth group schemes with kernel pair $(a,p)$
@@
 \begin{proposition} \label{prop:CSGabab}
-Suppose $G$ is a smooth group scheme.  Then the functor $q\ab^* : \CS(G\ab) \to \CSab(G)$ is an equivalence of categories.
+Suppose $G$ is a smooth group scheme.  
+Then pullback along $q : G \to G\ab$ defines an equivalence $q\ab^*: \CS(G\ab) \to \CSab(G)$.
 \end{proposition}
 \begin{proof}
-To simplify notation below, set $H=G\der$.
-Since the quotient $q : G \to G\ab$ is an $H$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, 
+%To simplify notation below, set $H=G\der$.
+Since the quotient $q : G \to G\ab$ is a $G\der$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, 
 it is also an $H$-torsor in the fpqc topology.  
-It now follows from descent theory that the comparison functor $\Loc(G\ab) \to \Loc_H(G)$ is an equivalence; argue as in \cite{Vistoli:notes}*{Thm 4.46}, for example.
-\todo{Need to adapt the following proof to the definition of $q\ab^*$.}
-
-For use below, we write $L_1 : \Loc(Q) \to \Loc_H(G)$ for the comparison functor, $R_1 : \Loc_H(G) \to \Loc(Q)$ for its adjoint, and $(\epsilon_1, \eta_1)$ for the counit and unit of the adjunction.
-%
-Arguing as above, we also see that pull-back along $q\times q$ determines an equivalence $L_2 : \Loc(Q\times Q) \to \Loc_{H\times H}(G\times G)$.
-For use below, we write $R_2 : \Loc_{H\times H}(G\times G) \to \Loc(Q\times Q)$ for its adjoint and $(\epsilon_2, \eta_2)$ for the counit and unit of the adjunction.
-
-We may now revisit the definition of the functor $q_H^*: \CS(Q)\to \CS_H(G)$:
-on objects, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\cs{L}_0,\mu_0) = (L_1(\cs{L}_0), L_2(\mu_0))$; on maps, $q_H^*: \CS(Q)\to \CS_H(G)$ is given by $q_H^*(\alpha_0) = L_1(\alpha_0)$.
-Direct calculation confirms \cite{cunningham-roe:13a}*{CS1, CS2, CS3}, \eqref{E1}, \eqref{E2} and \eqref{ECS1}, and therefore that $(L_1(\cs{L}_0), L_2(\mu_0))$ is an object of $\CS_H(G)$; 
-likewise, $L_1(\alpha_0)$ is a map in $\CS_H(G)$ after checking \cite{cunningham-roe:13a}*{CS4} and \eqref{E3}.
-%
-With this description of $q_H^*: \CS(Q)\to \CS_H(G)$ is is easy to see that it is an equivalence.
-Its adjoint is given on objects by $(\cs{L},\mu,\nu) \mapsto (R_1(\cs{L},\nu), R_2(\mu))$, making use of Lemma~\ref{lem:HH}, and on morphisms by $\alpha \mapsto R_1(\alpha)$.
-The adjunction is built from the adjunctions $(\epsilon_1, \eta_1)$ and $(\epsilon_2, \eta_2)$ for $(L_1,R_1)$ and $(L_2, R_2)$.
+It now follows from descent theory that the comparison functor $L : \Loc(G\ab) \to \Loc_{G\der}(G)$ is an equivalence; argue as in \cite{Vistoli:notes}*{Thm 4.46}, for example. 
+Observe that $L$ followed by the forgetful functor $\Loc_{G\der}(G)\to  \Loc(G)$ coincides with $q^*: \Loc(G\ab)\to \Loc(G)$ and that, for $\cs{L}\ab\in \Loc(G\ab)$, we may write $L(\cs{L}\ab) = (\cs{L}, \nu)$ where $\cs{L} = q^*(\cs{L}\ab)$ and $\nu : m^*\cs{L}  \to p^*\cs{L}$ is an isomorphism; here $m : G\times G\to G$ is  multiplication and $p : G\times  G \to G$ is projection to the second component.
+%
+Now set $G^2 \ceq G\times G$, so $G^2\ab =  G\ab \times G\ab$ and $G^2\der = G\der \times G\der$. Let $q_2 : G^2 \to G^2\ab$ be the abelianization quotient.  
+Let $L_2 : \Loc(G^2\ab) \to \Loc_{G^2\der}(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$.
+Then $L_2$ is also an equivalence since $q_2$ is also a $G^2\der$-torsor.
+
+Now consider the category $\CSab'(G)$ of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$; thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p_n^*\cs{L}$ are isomorphisms where $n : G\der\times G\to G$ is the restriction of $m$ to $G\der\times G$ and where $p_n : G\der\times G\to G$ is projection to the second component.
+Morphism are defined in the obvious way. 
+Consider the functor
+\[
+\begin{array}{rcl}
+\CS(G\ab) &\to& \CSab'(G) \\
+(\cs{L}\ab,\mu\ab) &\mapsto& (L(\cs{L}\ab), L_2(\mu\ab))
+\end{array}
+\]
+Since both $L$ and $L_2$ are equivalences, this functor $\CS(G\ab) \to \CSab'(G)$ is an equivalence of categories.
+
+Let $j : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j\times 1_G : G\der \to G\times G$ by $i\der(h) = (j(h),1_G)$.
+For $(\cs{L},\mu,\nu)\in \CSab'(G)$, $(j\times 1_G)^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism.
+This defines a functor
+\[
+\begin{array}{rcl}
+\CSab'(G) &\to& \CSab(G) \\
+(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,i\der^*(\nu)).
+\end{array}
+\]
+Define $j\times\id_G: G\der\times G\to G\times G$ by $j\times\id_G(h,g) = (j(h),g)$.
+Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p_n^*\cs{L}$ by
+\[
+\begin{tikzcd}
+& n^* \cs{L} \arrow{dl}{m\circ (j\times\id_G) = n} \arrow{r} & p_n^*\cs{L} &  \\ 
+(j\times\id_G)^* m^* \cs{L} \arrow{dr}{(j\times\id_G)^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
+& (j\times\id_G)^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\times 1}
+\end{tikzcd}
+\]
+Then $(\cs{L},\mu,\nu)\in \CSab'(G)$.
+It now follows that $\CSab'(G) \to \CSab(G)$ is an equivalence.
 \end{proof}

### 2017-04-06 Geometric types.tex
Corollary 3.2 needed very little work.

@@
 \begin{proof}
-As above, we set $H=G\der$
-and let $j : H\hookrightarrow G$ be the inclusion. 
-With reference to \eqref{qH} and Section~\ref{ssec:closed}, consider the following diagram.
+Notation as above.
+Consider the following diagram.
 %\[
@@
 \begin{tikzcd}
-\CS(H) & \arrow{l}[swap]{j^*} \CS(G) &\arrow{l}[swap]{q^*} 
-\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q_{H}^*} \\
+\CS(G\der) & \arrow{l}[swap]{j^*} \CS(G) &\arrow{l}[swap]{q^*} 
+\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q\ab^*} \\
 & \CSab(G) \arrow{u}{\text{forget}}  & 
@@
 
-Now, suppose $(\cs{L},\mu)\in \CS(G)$ and there is an isomorphism $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ in $\CS(H)$.
+Now, suppose $(\cs{L},\mu)\in \CS(G)$ and there is an isomorphism $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ in $\CS(G\der)$.
 Then $(\cs{L},\mu,\beta) \in \CSab(G)$.
 By Proposition \ref{prop:CSGabab}, $(\cs{L},\mu,\beta) \iso q\ab^*(\cs{L}\ab,\mu\ab)$ for some $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$.
-Applying the forgetful functor $\CS_H(G)\to \CS(G)$ to this isomorphism, it follows that $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, as desired.
+Applying the forgetful functor $\CS_{G\der}(G)\to \CS(G)$ to this isomorphism, it follows that $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, as desired.
 
 Conversely, suppose $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$.
-Then $j^*(\cs{L},\mu) \iso j^*q^*(\cs{L}\ab,\mu\ab)$ in $\CS(H)$. 
-Since $q\circ j = 1$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{H}$ in $\CS(H)$.
+Then $j^*(\cs{L},\mu) \iso j^*q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G\der)$. 
+Since $q\circ j = 1$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ in $\CS(G\der)$.
 \end{proof}

### 2017-04-06 Geometric types.tex
Finished the proof of Theorem 3.4.

@@
 \begin{proof}
-Notation as above.
+Notation as in the proof of Proposition~\ref{prop:CSGabab}.
 Consider the following diagram.
@@
 Then $j^*(\cs{L},\mu) \iso j^*q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G\der)$. 
-Since $q\circ j = 1$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ in $\CS(G\der)$.
+Since $q\circ j = 1_{G\ab}$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ in $\CS(G\der)$.
 \end{proof}
@@
 We may now define commutative character sheaves on $G$.
-
+%
 Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows.
@@
 \begin{proof}
-We again write $H$ for $G\der$.
+%We again write $H$ for $G\der$.
 By Definition~\ref{def:CCScom}, $\CCS(G\ab) \to \CS(G\ab)$ is a full subcategory.
-Since the comparison functor $\CS(G\ab) \to \CS_{H}(G)$ is an equivalence, it determines a full subcategory $\CCS_{H}(G)$ which is equivalent to $\CCS(G\ab)$, as pictured below.
-The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of $\CCS_H(G)$ under the equivalence $\CS_{H}(G) \to \CSab(G)$ is $\CCS(G)$.
+Since the comparison functor $\CS(G\ab) \to \CS_{G\der}(G)$ is an equivalence, it determines a full subcategory $\CCS_{G\der}(G)$ which is equivalent to $\CCS(G\ab)$, as pictured below.
+The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of $\CCS_{G\der}(G)$ under the equivalence $\CS_{G\der}(G) \to \CSab(G)$ is $\CCS(G)$.
 \[
@@
 
-Let $(\cs{L},\mu,\nu)$ be the image of $(\cs{L},\mu,\beta)\in \CSab(G)$ and of $(\cs{L}\ab,\mu\ab)$ under $q_H^*$;
+Let $(\cs{L},\mu,\nu)$ be the image of $(\cs{L},\mu,\beta)\in \CSab(G)$ and of $(\cs{L}\ab,\mu\ab)$ under $q\ab^*$;
 we must show that $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
@@
 Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ as in Section~\ref{ssec:noncomdef}.
-Then the diagram in Definition~\ref{def:CCS} is precisely the result of applying the functor $(q\times q)^*$ to the diagram in Definition~\ref{def:CCScom}, as pictured below; 
-in particular $\gamma = (q\times q)^* \xi$.
+Recall the equivalence $L_2 : \Loc(G^2\ab) \to  \Loc_{G^2\der}(G^2)$ from Proposition~\ref{prop:CSGabab}.
+The diagram in Definition~\ref{def:CCS} is precisely the result of applying the functor $L_2$ to the diagram in Definition~\ref{def:CCScom}, as pictured below; 
+in particular $\gamma = (q^2)^* \xi$.
   \[
@@
  & \cs{L}\boxtimes\cs{L} \arrow{dd}{\vartheta}\\
- && \arrow{r}{(q\times q)^*}  &\ & & &\\ 
+ && \arrow{r}{(q^2)^*}  &\ & & &\\ 
    \theta^*(m_0^*\cs{L}_0) \arrow{r}{{\theta}^*\mu_0} 
@@
 \]
-Using Lemma~\ref{lem:HH}, we may interpret the diagram on the right as a diagram in $\Loc_{H\times H}(G\times G)$.
-By Lemma~\ref{lem:torsor}, this corresponds to a diagram in $\Loc(G\ab\times G\ab)$, necessarily the diagram on the left, above, and also that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes.
+The diagram on the right is a diagram in $\Loc_{G^2\der}(G^2)$.
+Using the equivalence $L_2$, this corresponds to a diagram in $\Loc(G^2\ab)$, necessarily the diagram on the left, above.
+It follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes. 
 In other words, $(\cs{L},\mu,\beta)\in \CCS(G)$
 if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G)$.
-
 \end{proof}

### 2017-04-12 Geometric types.tex
Making small stylistic changes in the proof of Prop 3.1

@@
 it is also an $H$-torsor in the fpqc topology.  
-It now follows from descent theory that the comparison functor $L : \Loc(G\ab) \to \Loc_{G\der}(G)$ is an equivalence; argue as in \cite{Vistoli:notes}*{Thm 4.46}, for example. 
-Observe that $L$ followed by the forgetful functor $\Loc_{G\der}(G)\to  \Loc(G)$ coincides with $q^*: \Loc(G\ab)\to \Loc(G)$ and that, for $\cs{L}\ab\in \Loc(G\ab)$, we may write $L(\cs{L}\ab) = (\cs{L}, \nu)$ where $\cs{L} = q^*(\cs{L}\ab)$ and $\nu : m^*\cs{L}  \to p^*\cs{L}$ is an isomorphism; here $m : G\times G\to G$ is  multiplication and $p : G\times  G \to G$ is projection to the second component.
+It now follows from descent theory that the comparison functor $L : \Loc(G\ab) \to \Loc_{G\der}(G)$ is an equivalence: argue as in \cite{Vistoli:notes}*{Thm 4.46} for example.
+\todo{Haven't defined $\Loc$ and $\Loc_{G\der}$}
+Let $m : G\times G\to G$ be multiplication and $p : G\times G \to G$ projection to the second component.
+For $\cs{L}\ab\in \Loc(G\ab)$, we may write $L(\cs{L}\ab) = (\cs{L}, \nu)$, where $\cs{L} = q^*(\cs{L}\ab)$ and $\nu : m^*\cs{L}  \to p^*\cs{L}$ is an isomorphism.
+Observe that $L$ followed by the forgetful functor $\Loc_{G\der}(G)\to \Loc(G)$ coincides with $q^*: \Loc(G\ab)\to \Loc(G)$. 
 %
@@
 Now consider the category $\CSab'(G)$ of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$; thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p_n^*\cs{L}$ are isomorphisms where $n : G\der\times G\to G$ is the restriction of $m$ to $G\der\times G$ and where $p_n : G\der\times G\to G$ is projection to the second component.
-Morphism are defined in the obvious way. 
+\todo{How is $\nu_2$ the same as $\nu$ above?}
+Morphisms are morphisms in $\Loc(G)$ commuting with $\mu$ and $\nu$. \todo{Is this definition of morphisms sufficiently clear?} 
 Consider the functor
@@
 
-Let $j : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j\times 1_G : G\der \to G\times G$ by $i\der(h) = (j(h),1_G)$.
+Let $j : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j\times 1_G : G\der \to G\times G$ by $i\der(h) = (j(h),1_G)$. \todo{There's some kind of typo here....}
 For $(\cs{L},\mu,\nu)\in \CSab'(G)$, $(j\times 1_G)^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism.

### 2017-04-20 Geometric types.tex
small stuff

@@
 
-Let $j : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j\times 1_G : G\der \to G\times G$ by $i\der(h) = (j(h),1_G)$. \todo{There's some kind of typo here....}
-For $(\cs{L},\mu,\nu)\in \CSab'(G)$, $(j\times 1_G)^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism.
+Let $i : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\times G$ by $j(h) = (i(h),1_G)$. \todo{There's some kind of typo here....}
+For $(\cs{L},\mu,\nu)\in \CSab'(G)$, $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism.
 This defines a functor
@@
 \CSab'(G) &\to& \CSab(G) \\
-(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,i\der^*(\nu)).
+(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,j^*(\nu)).
 \end{array}
 \]
-Define $j\times\id_G: G\der\times G\to G\times G$ by $j\times\id_G(h,g) = (j(h),g)$.
+Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i(h),g)$.
 Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p_n^*\cs{L}$ by
@@
 \begin{tikzcd}
-& n^* \cs{L} \arrow{dl}{m\circ (j\times\id_G) = n} \arrow{r} & p_n^*\cs{L} &  \\ 
-(j\times\id_G)^* m^* \cs{L} \arrow{dr}{(j\times\id_G)^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
-& (j\times\id_G)^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\times 1}
+& n^* \cs{L} \arrow{dl}{m\circ k = n} \arrow{r} & p_n^*\cs{L} &  \\ 
+k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
+& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\times 1}
 \end{tikzcd}
@@
 \CS(G\der) & \arrow{l}[swap]{j^*} \CS(G) &\arrow{l}[swap]{q^*} 
-\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q\ab^*} \\
+\CS(G\ab) \arrow{dl}{q\ab^*} \\
 & \CSab(G) \arrow{u}{\text{forget}}  & 

### 2017-04-27 Geometric types.tex
Talking to David

@@
 it is also an $H$-torsor in the fpqc topology.  
+Let $\Loc(G\ab)$ be the category of local systems on $G\ab$ and let $\Loc_{G\der}(G)$
 It now follows from descent theory that the comparison functor $L : \Loc(G\ab) \to \Loc_{G\der}(G)$ is an equivalence: argue as in \cite{Vistoli:notes}*{Thm 4.46} for example.
 \todo{Haven't defined $\Loc$ and $\Loc_{G\der}$}
-Let $m : G\times G\to G$ be multiplication and $p : G\times G \to G$ projection to the second component.
-For $\cs{L}\ab\in \Loc(G\ab)$, we may write $L(\cs{L}\ab) = (\cs{L}, \nu)$, where $\cs{L} = q^*(\cs{L}\ab)$ and $\nu : m^*\cs{L}  \to p^*\cs{L}$ is an isomorphism.
+Let $m : G\times G\to G$ be in $G$ and let $n : G\der\times G\to G$ be the restriction of multiplication in $G$ to $G\der\times  G$ and $p : G\der\times G \to G$ projection to the second component.  
+For $\cs{L}\ab\in \Loc(G\ab)$, we may write $L(\cs{L}\ab) = (\cs{L}, \nu)$, where $\cs{L} = q^*(\cs{L}\ab)$ and $\nu : n^*\cs{L}  \to p^*\cs{L}$ is an isomorphism. 
 Observe that $L$ followed by the forgetful functor $\Loc_{G\der}(G)\to \Loc(G)$ coincides with $q^*: \Loc(G\ab)\to \Loc(G)$. 
@@
 
-Now consider the category $\CSab'(G)$ of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$; thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p_n^*\cs{L}$ are isomorphisms where $n : G\der\times G\to G$ is the restriction of $m$ to $G\der\times G$ and where $p_n : G\der\times G\to G$ is projection to the second component.
+Now consider the category $\CSab'(G)$ of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$; thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p^*\cs{L}$ are isomorphisms where $n : G\der\times G\to G$ is the restriction of $m$ to $G\der\times G$ and where $p_n : G\der\times G\to G$ is projection to the second component.
 \todo{How is $\nu_2$ the same as $\nu$ above?}

### 2017-04-27 Geometric types.tex
After talking with David

@@
 
-Now consider the category $\CSab'(G)$ of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$; thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p^*\cs{L}$ are isomorphisms where $n : G\der\times G\to G$ is the restriction of $m$ to $G\der\times G$ and where $p_n : G\der\times G\to G$ is projection to the second component.
-\todo{How is $\nu_2$ the same as $\nu$ above?}
-Morphisms are morphisms in $\Loc(G)$ commuting with $\mu$ and $\nu$. \todo{Is this definition of morphisms sufficiently clear?} 
+Now consider the category $\CSab'(G)$ of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$; thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p^*\cs{L}$ are isomorphisms.
+Morphisms are morphisms in $\Loc(G)$ commuting with $\mu$ and $\nu$. 
 Consider the functor
@@
 
-Let $i : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\times G$ by $j(h) = (i(h),1_G)$. \todo{There's some kind of typo here....}
+Let $i : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\times G$ by $j(h) = (i(h),1_G)$. 
 For $(\cs{L},\mu,\nu)\in \CSab'(G)$, $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism.

### 2017-05-01 Geometric types.tex
Added Loc_H(G)

@@
 %To simplify notation below, set $H=G\der$.
-Since the quotient $q : G \to G\ab$ is a $G\der$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, 
-it is also an $H$-torsor in the fpqc topology.  
-Let $\Loc(G\ab)$ be the category of local systems on $G\ab$ and let $\Loc_{G\der}(G)$
+Since the quotient $q : G \to G\ab$ is a $G\der$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, it is also an $H$-torsor in the fpqc topology.  
+Let $\Loc(G\ab)$ be the category of local systems on $G\ab$.
+Let $m : G\times G\to G$ be in $G$ and let $n : G\der\times G\to G$ be the restriction of multiplication in $G$ to $G\der\times  G$ and $p : G\der\times G \to G$ projection to the second component.  
+Let $\Loc(G\ab)$ be the category of local systems on $G\ab$ and let $\Loc_{G\der}(G)$ be the category of $G\der$-equivariant local systems on $G$.
+Thus, objects in $\Loc_{G\der}(G)$ are pairs $(\cs{L},\nu)$ where $\cs{L}$ is a local system on $G$ and $\nu : n^*\cs{L} \to p^*\cs{L}$ is an isomorphism such that 
+\[
+\begin{tikzcd}
+s^*n^*\cs{L} \arrow{r}{s^*(\nu)} & s^*p^*\cs{L}\\
+\cs{L} \arrow[equal]{u}{n\circ s = \id_G}  \arrow{r}{\id_{\cs{L}}} & \cs{L} \arrow[equal]{u}[swap]{n\circ s = \id_G} 
+\end{tikzcd}
+\]
+commutes, where $s: G \to G\der\times G$ is $s(g) = (1,g)$ and such that the following diagram commutes, where $n_1(h_1,h_2,g) = (h_1h_2,g)$, $n_2(h_1,h_2,g) = (h_1,n(h_2,g))$ and $p_2(h_1,h_2,g) = (h_2,g)$.
+\[
+\begin{tikzcd}
+& \arrow[equal]{dl}{n\circ n_2=n\circ n_1} n_2^*n^*\cs{L} \arrow{rr}{n_2^*(\nu)} && n_2^*p^*\cs{L} \arrow[equal]{dr}[swap]{n_2\circ p = n\circ p_2}& \\
+n_1^*n^*\cs{L} \arrow{dr}[swap]{n_1^*(\nu)} &&&& \arrow{dl}{p_2^*(\nu)} p_2^*n^*\cs{L}\\
+& n_1^*p^*\cs{L} \arrow[equal]{rr}{p\circ n_1 = p\circ p_2} && p_2^*p^*\cs{L}  & 
+\end{tikzcd}
+\]
 It now follows from descent theory that the comparison functor $L : \Loc(G\ab) \to \Loc_{G\der}(G)$ is an equivalence: argue as in \cite{Vistoli:notes}*{Thm 4.46} for example. 
-\todo{Haven't defined $\Loc$ and $\Loc_{G\der}$}
-Let $m : G\times G\to G$ be in $G$ and let $n : G\der\times G\to G$ be the restriction of multiplication in $G$ to $G\der\times  G$ and $p : G\der\times G \to G$ projection to the second component.  
 For $\cs{L}\ab\in \Loc(G\ab)$, we may write $L(\cs{L}\ab) = (\cs{L}, \nu)$, where $\cs{L} = q^*(\cs{L}\ab)$ and $\nu : n^*\cs{L}  \to p^*\cs{L}$ is an isomorphism. 

### 2017-05-01 Geometric types.tex
n to p. Started adding morphisms

@@
 \end{equation}
-Via this theorem, then, we obtain geometric avatars for each type in a Yu datum:
+By this theorem, then, we obtain geometric avatars for each type in a Yu datum:
 \[
@@
 s^*n^*\cs{L} \arrow{r}{s^*(\nu)} & s^*p^*\cs{L}\\
-\cs{L} \arrow[equal]{u}{n\circ s = \id_G}  \arrow{r}{\id_{\cs{L}}} & \cs{L} \arrow[equal]{u}[swap]{n\circ s = \id_G} 
+\cs{L} \arrow[equal]{u}{n\circ s = \id_G}  \arrow{r}{\id_{\cs{L}}} & \cs{L} \arrow[equal]{u}[swap]{p\circ s = \id_G} 
 \end{tikzcd}
@@
 \]
+A morphism $(\cs{L},\nu)\to (\cs{L}',\nu')$ in $\Loc_{G\der}(G)$ is a morphism $\alpha :\cs{L} \to \cs{L}'$ such that...
 It now follows from descent theory that the comparison functor $L : \Loc(G\ab) \to \Loc_{G\der}(G)$ is an equivalence: argue as in \cite{Vistoli:notes}*{Thm 4.46} for example. 

### 2017-05-01 Geometric types.tex
Moving definitions of functors to before Prop 3.1

--- 2017-04-27 Geometric types.tex
@@
 in \cite{cunningham-roe:13a}*{Def. 1.1}, as linear character sheaves when $G$ is smooth but
-not necessarily commutative.
-Let $\CSab(G)$ denote the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu) \in \CS(G)$ and
+not necessarily commutative.  In order to define commutative character sheaves, we need to define
+some auxiliary categories.
+\begin{itemize}
+\item Let $\CSab(G)$ denote the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu) \in \CS(G)$ and
 $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism in $\CS(G\der)$.
@@
 in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{G\der}$.  We will define commutative character sheaves
-as a subcategory of $\CSab(G)$, but we first relate $\CSab(G)$ to $\CS(G\ab)$.  Let $q : G \to G\ab$ be the quotient map.
+as a subcategory of $\CSab(G)$.
+\item Let $\Loc(G)$ and $\Loc(G\ab)$ be the categories of local systems on $G$ and $G\ab$, respectively.
+\item Let $\Loc_{G\der}(G)$ be the category of $G\der$-equivariant local systems on $G$, whose definition we now recall.
+Let $m : G\times G\to G$ be multiplication in $G$, $n : G\der\times G\to G$ be its to $G\der\times G$,
+$p : G\der\times G \to G$ projection to the second component, and $s: G \to G\der\times G$ be given by $s(g) = (1,g)$.
+Then objects in $\Loc_{G\der}(G)$ are pairs $(\cs{L},\nu)$ where $\cs{L}$ is a local system on $G$ and
+$\nu : n^*\cs{L} \to p^*\cs{L}$ is an isomorphism such that the following two diagrams commute.
+\[
+\begin{tikzcd}
+s^*n^*\cs{L} \arrow{r}{s^*(\nu)} & s^*p^*\cs{L}\\
+\cs{L} \arrow[equal]{u}{n\circ s = \id_G}  \arrow{r}{\id_{\cs{L}}} & \cs{L} \arrow[equal]{u}[swap]{n\circ s = \id_G},
+\end{tikzcd}
+\]
+and with $n_1(h_1,h_2,g) = (h_1h_2,g)$, $n_2(h_1,h_2,g) = (h_1,n(h_2,g))$ and $p_2(h_1,h_2,g) = (h_2,g)$,
+\[
+\begin{tikzcd}
+& \arrow[equal]{dl}{n\circ n_2=n\circ n_1} n_2^*n^*\cs{L} \arrow{rr}{n_2^*(\nu)} && n_2^*p^*\cs{L} \arrow[equal]{dr}[swap]{n_2\circ p = n\circ p_2}& \\
+n_1^*n^*\cs{L} \arrow{dr}[swap]{n_1^*(\nu)} &&&& \arrow{dl}{p_2^*(\nu)} p_2^*n^*\cs{L}\\
+& n_1^*p^*\cs{L} \arrow[equal]{rr}{p\circ n_1 = p\circ p_2} && p_2^*p^*\cs{L} .
+\end{tikzcd}
+\]
+Morphisms are morphisms in $\Loc(G)$ commuting with $\nu$.
+\item Let $\CSab'(G)$ be the category of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$; thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p^*\cs{L}$ are isomorphisms.
+Morphisms are morphisms in $\Loc(G)$ commuting with $\mu$ and $\nu$. 
+\end{itemize}
+We relate $\CSab(G)$ to $\CS(G\ab)$ via the quotient map $q : G \to G\ab$.
 %\todo{Define $q\ab^* : \CS(G\ab) \to \CSab(G)$; missing definition of $\beta$ in the following commented section}
@@
 %To simplify notation below, set $H=G\der$.
-Since the quotient $q : G \to G\ab$ is a $G\der$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, 
-it is also an $H$-torsor in the fpqc topology.  
-Let $\Loc(G\ab)$ be the category of local systems on $G\ab$ and let $\Loc_{G\der}(G)$
+Since the quotient $q : G \to G\ab$ is a $G\der$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, it is also an $G\der$-torsor in the fpqc topology.
+
 It now follows from descent theory that the comparison functor $L : \Loc(G\ab) \to \Loc_{G\der}(G)$ is an equivalence: argue as in \cite{Vistoli:notes}*{Thm 4.46} for example. 
-\todo{Haven't defined $\Loc$ and $\Loc_{G\der}$}
-Let $m : G\times G\to G$ be in $G$ and let $n : G\der\times G\to G$ be the restriction of multiplication in $G$ to $G\der\times  G$ and $p : G\der\times G \to G$ projection to the second component.  
 For $\cs{L}\ab\in \Loc(G\ab)$, we may write $L(\cs{L}\ab) = (\cs{L}, \nu)$, where $\cs{L} = q^*(\cs{L}\ab)$ and $\nu : n^*\cs{L}  \to p^*\cs{L}$ is an isomorphism. 
@@
 
-Now consider the category $\CSab'(G)$ of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$; thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p^*\cs{L}$ are isomorphisms.
-Morphisms are morphisms in $\Loc(G)$ commuting with $\mu$ and $\nu$. 
 Consider the functor
@@
 \]
-Then $(\cs{L},\mu,\nu)\in \CSab'(G)$.
+Then $(\cs{L},\mu,\nu)\in \CSab'(G)$ maps to $(\cs{L},\mu,\beta)$.
 It now follows that $\CSab'(G) \to \CSab(G)$ is an equivalence.

### 2017-05-01 Geometric types.tex

@@
 s^*n^*\cs{L} \arrow{r}{s^*(\nu)} & s^*p^*\cs{L}\\
-\cs{L} \arrow[equal]{u}{n\circ s = \id_G}  \arrow{r}{\id_{\cs{L}}} & \cs{L} \arrow[equal]{u}[swap]{n\circ s = \id_G},
+\cs{L} \arrow[equal]{u}{n\circ s = \id_G}  \arrow{r}{\id_{\cs{L}}} & \cs{L} \arrow[equal]{u}[swap]{n=p\circ s = \id_G},
 \end{tikzcd}
@@
 \begin{proof}
-%To simplify notation below, set $H=G\der$.
-Since the quotient $q : G \to G\ab$ is a $G\der$-torsor in the fppf topology \cite{demazure:SGA3-VIA}*{Thm. 3.2}, it is also an $G\der$-torsor in the fpqc topology.
-
 It now follows from descent theory that the comparison functor $L : \Loc(G\ab) \to \Loc_{G\der}(G)$ is an equivalence: argue as in \cite{Vistoli:notes}*{Thm 4.46} for example. 

### 2017-05-01 Geometric types.tex
Made new section

@@
 
+Let $\CSab(G)$ denote the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu) \in \CS(G)$ and
+$\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism in $\CS(G\der)$.
+A morphism $(\cs{L},\mu,\beta)\to (\cs{L}',\mu',\beta')$ is a morphism $\alpha : (\cs{L},\mu)\to (\cs{L}',\mu')$
+in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{G\der}$.  
+%
+We will define commutative character sheaves as a subcategory of $\CSab(G)$.
+
+%We may now define commutative character sheaves on $G$.
+%
+Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows.
+Let $i : G \to G$ be inversion and $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
+Both are smooth morphisms of $\Fq$-schemes.
+Set $m' = i \circ m \circ \theta$; we have $j\circ c = m \circ (m \times m')$.
+Then $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms below.
+\begin{equation}
+\begin{tikzcd}
+\arrow[equal]{d} c^* (\cs{L}\vert_{G\der}) \arrow{r}{c^*(\beta)} 
+	&  c^*((\EE)_{G\der}) \arrow[equal]{d} \\
+\arrow{d}[swap]{j\circ c = m \circ (m \times m')} c^* j^* \cs{L} 
+	&   (\EE)_{G\times G} \\
+(m \times m')^* m^* \cs{L} \arrow{d}[swap]{(m \times m')^*(\mu)} 
+	&  m^*\cs{L} \otimes \theta^* m^* i^* \cs{L}  \arrow[dashed]{u}[swap]{\gamma'} \\
+(m \times m')^* (\cs{L} \boxtimes \cs{L}) \arrow[equal]{r} 
+	& m^*\cs{L} \otimes (m')^*\cs{L} \arrow{u}[swap]{m' = i\circ m\circ \theta} 
+\end{tikzcd}
+\end{equation}
+In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations; so, for example, the middle left isomorphism comes from $(m\times m')^* m^* \iso c^* j^*$ since $j\circ c = m \circ (m \times m')$.
+Using the monoidal structure of the category of Weil local systems on $G\times G$, the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ defines an isomorphism
+\[
+m^*\cs{L} \to (\theta^* m^* i^*\cs{L})^\vee.
+\]
+Applying the canonical isomorphisms $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ and $i^*(\cs{L}^\vee) \cong \cs{L}$, this map provides the promised isomorphism
+\[
+\begin{tikzcd}
+\gamma : m^*\cs{L} \arrow{r} & \theta^* m^* \cs{L}.
+\end{tikzcd}
+\]
+
+\begin{definition}\label{def:CCS}
+The category $\CCS(G)$ of commutative character sheaves on $G$ is the full subcategory of $\CSab(G)$ consisting of triples $(\cs{L},\mu,\beta)$ such that the following diagram of Weil sheaves on $G \times G$ commutes:
+  \[
+  \begin{tikzcd}[row sep=30]
+   m^*\cs{L} \arrow{d}[swap]{\gamma} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
+   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L}).
+  \end{tikzcd}
+  \]
+Here $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ above. 
+\end{definition}
+
+\subsection{Descent}
+
 Recall from Section~\ref{sec:defs} that we refer to objects in category $\CS(G)$, defined as
 in \cite{cunningham-roe:13a}*{Def. 1.1}, as linear character sheaves when $G$ is smooth but
-not necessarily commutative.  In order to define commutative character sheaves, we need to define
-some auxiliary categories.
+not necessarily commutative.  
+In order to study commutative character sheaves, we need some auxiliary categories.
 \begin{itemize}
-\item Let $\CSab(G)$ denote the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu) \in \CS(G)$ and
-$\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism in $\CS(G\der)$.
-A morphism $(\cs{L},\mu,\beta)\to (\cs{L}',\mu',\beta')$ is a morphism $\alpha : (\cs{L},\mu)\to (\cs{L}',\mu')$
-in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{G\der}$.  We will define commutative character sheaves
-as a subcategory of $\CSab(G)$.
 \item Let $\Loc(G)$ and $\Loc(G\ab)$ be the categories of local systems on $G$ and $G\ab$, respectively.
@@
 We relate $\CSab(G)$ to $\CS(G\ab)$ via the quotient map $q : G \to G\ab$.
-%\todo{Define $q\ab^* : \CS(G\ab) \to \CSab(G)$; missing definition of $\beta$ in the following commented section}
-%Now suppose $q : G \to Q$ is a regular epimorphism of smooth group schemes with kernel pair $(a,p)$
-%\[
-%\begin{tikzcd}
-%H\times G
-% \arrow[shift left=2]{r}{a}
-%  \arrow[shift right=2,swap]{r}{p}
-%&
-%G 
-%\arrow{r}{q}
-%& 
-%Q.
-%\end{tikzcd}
-%\]
-%Let $(\cs{L}_0, \mu_0)$ be a linear character sheaf on $Q$ and set $(\cs{L}, \mu) \ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$.
-%Consider the functor
-%\[
-%q^* : \CS(Q) \to \CS(G)
-%\]
-%given on objects by $(\cs{L}_0,\mu_0) \mapsto (\cs{L}, \mu)$; see \cite{cunningham-roe:13a}*{Lem 1.4}.
-%%To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$,
-%%verify \cite{cunningham-roe:13a}, CS.3], arguing as in \cite{cunningham-roe:13a}].
-%%The linear character sheaf $(\cs{L},\mu)$ on $G$ comes equipped with a canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of isomorphisms.
-%\[
-%\begin{tikzcd}[column sep=40]
-%a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{r}{\nu} &  \arrow[equal]{d} p^*\cs{L} \\
-%a^* ( q^*\cs{L}_0) \arrow{r}{q\circ a = q\circ p}
-%& p^* (q^*\cs{L}_0)
-%\end{tikzcd}
-%\]
-%Since this isomorphism satisfies \eqref{ECS1}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
-%If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(Q)$, 
-%then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha$ is a morphism in $\CS(G)$.
-%These simple observations define the comparison functor
-%\[
-%q_H^* : \CS(Q) \to CS_H(G)
-%\]
-%and show that the functor $q^* : \CS(Q) \to \CS(G)$ factors according to the following commuting diagram of functors
-%\begin{equation}\label{qH}
-%\begin{tikzcd}
-%\CS(G) &\arrow{l}[swap]{q^*} 
-%\CS(Q) \arrow{dl}{q_H^*}\\
-%\arrow{u}{\text{forget}} \CS_{H}(G). & 
-%\end{tikzcd}
-%\end{equation}
-%The definition of $q_H^* : \CS(Q)\to \CS_H(G)$ will be revisited in the proof of the following result.
-
-%\begin{proposition} \label{prop:Gder_triv}
-%Suppose $G$ is a smooth group scheme and $(\cs{L},\mu) \in \CS(G)$.
-%Then the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $(\cs{L},\mu) \cong q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, for some $(\cs{L}\ab,\mu\ab) \in \CS(G\ab)$.
-%\end{proposition}
-%Proposition~\ref{prop:Gder_triv} will be proven in Section \ref{ssec:proof1}.
+
+%%%%%%%%
+\iffalse
+
+\todo{Define $q\ab^* : \CS(G\ab) \to \CSab(G)$; missing definition of $\beta$ in the following commented section}
+Now suppose $q : G \to Q$ is a regular epimorphism of smooth group schemes with kernel pair $(a,p)$
+\[
+\begin{tikzcd}
+H\times G
+ \arrow[shift left=2]{r}{a}
+  \arrow[shift right=2,swap]{r}{p}
+&
+G 
+\arrow{r}{q}
+& 
+Q.
+\end{tikzcd}
+\]
+Let $(\cs{L}_0, \mu_0)$ be a linear character sheaf on $Q$ and set $(\cs{L}, \mu) \ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$.
+Consider the functor
+\[
+q^* : \CS(Q) \to \CS(G)
+\]
+given on objects by $(\cs{L}_0,\mu_0) \mapsto (\cs{L}, \mu)$; see \cite{cunningham-roe:13a}*{Lem 1.4}.
+To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$,
+verify \cite{cunningham-roe:13a}, CS.3], arguing as in \cite{cunningham-roe:13a}].
+The linear character sheaf $(\cs{L},\mu)$ on $G$ comes equipped with a canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of isomorphisms.
+\[
+\begin{tikzcd}[column sep=40]
+a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{r}{\nu} &  \arrow[equal]{d} p^*\cs{L} \\
+a^* ( q^*\cs{L}_0) \arrow{r}{q\circ a = q\circ p}
+& p^* (q^*\cs{L}_0)
+\end{tikzcd}
+\]
+Since this isomorphism satisfies \eqref{ECS1}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
+If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(Q)$, 
+then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha$ is a morphism in $\CS(G)$.
+These simple observations define the comparison functor
+\[
+q_H^* : \CS(Q) \to CS_H(G)
+\]
+and show that the functor $q^* : \CS(Q) \to \CS(G)$ factors according to the following commuting diagram of functors
+\begin{equation}\label{qH}
+\begin{tikzcd}
+\CS(G) &\arrow{l}[swap]{q^*} 
+\CS(Q) \arrow{dl}{q_H^*}\\
+\arrow{u}{\text{forget}} \CS_{H}(G). & 
+\end{tikzcd}
+\end{equation}
+The definition of $q_H^* : \CS(Q)\to \CS_H(G)$ will be revisited in the proof of the following result.
+
+\begin{proposition} \label{prop:Gder_triv}
+Suppose $G$ is a smooth group scheme and $(\cs{L},\mu) \in \CS(G)$.
+Then the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $(\cs{L},\mu) \cong q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, for some $(\cs{L}\ab,\mu\ab) \in \CS(G\ab)$.
+\end{proposition}
+Proposition~\ref{prop:Gder_triv} will be proven in Section \ref{ssec:proof1}.
+
+\fi
+%%%%%%%%%%%%%%%%%
+
+\begin{lemma}
+If $(\cs{L},\mu)\in \CS(G)$ then $\mu  : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism in $\CS(G^2)$.
+\end{lemma}
+\begin{proof}
+First we show that $m^*\cs{L}$ is an  object in $\CS(G^2)$.
+\end{proof}
 
@@
 
-We may now define commutative character sheaves on $G$.
-%
-Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows.
-Let $i : G \to G$ be inversion and $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
-Both are smooth morphisms of $\Fq$-schemes.
-Set $m' = i \circ m \circ \theta$; we have $j\circ c = m \circ (m \times m')$.
-Then $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms below.
-\begin{equation}
-\begin{tikzcd}
-\arrow[equal]{d} c^* (\cs{L}\vert_{G\der}) \arrow{r}{c^*(\beta)} 
-	&  c^*((\EE)_{G\der}) \arrow[equal]{d} \\
-\arrow{d}[swap]{j\circ c = m \circ (m \times m')} c^* j^* \cs{L} 
-	&   (\EE)_{G\times G} \\
-(m \times m')^* m^* \cs{L} \arrow{d}[swap]{(m \times m')^*(\mu)} 
-	&  m^*\cs{L} \otimes \theta^* m^* i^* \cs{L}  \arrow[dashed]{u}[swap]{\gamma'} \\
-(m \times m')^* (\cs{L} \boxtimes \cs{L}) \arrow[equal]{r} 
-	& m^*\cs{L} \otimes (m')^*\cs{L} \arrow{u}[swap]{m' = i\circ m\circ \theta} 
-\end{tikzcd}
-\end{equation}
-In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations; so, for example, the middle left isomorphism comes from $(m\times m')^* m^* \iso c^* j^*$ since $j\circ c = m \circ (m \times m')$.
-Using the monoidal structure of the category of Weil local systems on $G\times G$, the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ defines an isomorphism
-\[
-m^*\cs{L} \to (\theta^* m^* i^*\cs{L})^\vee.
-\]
-Applying the canonical isomorphisms $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ and $i^*(\cs{L}^\vee) \cong \cs{L}$, this map provides the promised isomorphism
-\[
-\begin{tikzcd}
-\gamma : m^*\cs{L} \arrow{r} & \theta^* m^* \cs{L}.
-\end{tikzcd}
-\]
-
-\begin{definition}\label{def:CCS}
-The category $\CCS(G)$ of commutative character sheaves on $G$ is the full subcategory of $\CSab(G)$ consisting of triples $(\cs{L},\mu,\beta)$ such that the following diagram of Weil sheaves on $G \times G$ commutes:
-  \[
-  \begin{tikzcd}[row sep=30]
-   m^*\cs{L} \arrow{d}[swap]{\gamma} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
-   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L}).
-  \end{tikzcd}
-  \]
-Here $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ above. 
-\end{definition}
-
 \subsection{Objects and maps in commutative character sheaves} \label{ssec:obmor}

### 2017-05-01 Geometric types.tex
Declared  definition of  CSab

@@
 
+\begin{definition}\label{def:CSab}
 Let $\CSab(G)$ denote the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu) \in \CS(G)$ and
@@
 in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{G\der}$.  
+\end{definition}
+
 %
 We will define commutative character sheaves as a subcategory of $\CSab(G)$.
-
 %We may now define commutative character sheaves on $G$.

### 2017-05-02 Geometric types.tex
Work in progress

@@
 \begin{lemma}
-If $(\cs{L},\mu)\in \CS(G)$ then $\mu  : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism in $\CS(G^2)$.
+If $(\cs{L},\mu,\beta)\in \CS\ab(G)$ then $\mu  : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism in $\CS\ab(G\times G)$.
 \end{lemma}
 \begin{proof}
+Set $G^2 = G\times G$. Define $m^2 : G^2\times G^2 \to G^2$ by $m^2(g_1,g_2,g_1'g_2') = (g_1g_1',g_2g_2')$. Also define $p^2_i : G^2\times G^2 \to G^2$ by $p^2_i(g_1,g_2,g_1'g_2') = g_i g_i'$.
 First we show that $m^*\cs{L}$ is an object in $\CS(G^2)$.
+If $(\cs{L},\mu) \in \CS(G)$ then $m^*\cs{L}$ equipped with the isomorphism $(m^2)^* (m^*\cs{L}) \to m^*\cs{L} \boxtimes m^*\cs{L}$ defined by the diagram below.
+\[
+\begin{tikzcd}
+(m^2)^* (m^*\cs{L}) \arrow{d}{(m^2)^*\mu} \arrow{rr} && m^*\cs{L} \boxtimes m^*\cs{L}\\
+ (m^2)^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & (m^2)^*(p_1)^*\cs{L} \otimes (m^2)^*(p_2)^*\cs{L} \arrow[equal]{r} & (p^2_1)^*m^*\cs{L} \otimes (p^2_2)^*m^*\cs{L} \arrow[equal]{u}
+\end{tikzcd}
+\] 
+\todo{Clifton is working here}
 \end{proof}
@@
 \begin{proof}
-%We again write $H$ for $G\der$.
+\[
+\begin{tikzcd}
+{} & \arrow{dl}[swap]{q^*\ab} \CS(G\ab)\\
+\CS\ab(G) & \arrow{l} \CS\ab(G\ab) \arrow{u}[swap]{\text{equiv.}}\\
+\CCS(G) \arrow[>->]{u} & \arrow{l} \CCS(G\ab) \arrow[>->]{u}\\
+\end{tikzcd}
+\]
+\todo{Clifton is working here}
+\[
+  \begin{tikzcd}[row sep=10, column sep = 20]
+   m^*\cs{L} \arrow{dd}[swap]{\gamma} \arrow{r}{\mu} 
+ & \cs{L}\boxtimes\cs{L} \arrow{dd}{\vartheta}
+ &&&  m\ab^*\cs{L}\ab \arrow{dd}[swap]{\xi} \arrow{r}{\mu\ab} 
+   & \cs{L}\ab\boxtimes\cs{L}\ab \arrow{dd}{\vartheta}\\
+%
+ && \  &\arrow{l}[swap]{(q^2)^*\ab}  & & &\\ 
+%
+   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} 
+&  \theta^*(\cs{L}\boxtimes\cs{L}) 
+ &&&   \theta^*(m\ab^*\cs{L}\ab) \arrow{r}{{\theta}^*\mu\ab} 
+ &  \theta^*(\cs{L}\ab\boxtimes\cs{L}\ab)
+ \end{tikzcd}
+\]
+
 By Definition~\ref{def:CCScom}, $\CCS(G\ab) \to \CS(G\ab)$ is a full subcategory.

### 2017-05-02 Geometric types.tex
Adding new corollary on the kernel of the forgetful functor

@@
 the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $(\cs{L},\mu) \cong q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, for some $(\cs{L}\ab,\mu\ab) \in \CS(G\ab)$.
-\todo{What is the ``kernel'' of the forgetful functor?
-Ie, is there a natural parameterization of the possible choices of $\beta$?}
 \end{corollary}
@@
 Since $q\circ j = 1_{G\ab}$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ in $\CS(G\der)$.
+\end{proof}
+
+We may interpret this corollary as measuring how far $q^*$ is from being essentially surjective.  The next result shows that it is also not full.
+Let $C$ denote the cokernel of the natural map
+\[
+\Hom(\pi_0(\bar{G})_{\mathcal{W}}, \EEx) \to \Hom(\pi_0(\bar{G}\der)_{\mathcal{W}}, \EEx),
+\]
+where $\pi_0(\bar{G})_\mathcal{W}$ denotes the covariants of the action of Frobenius on
+the component group of $G$
+
+\begin{corollary}
+If $G$ is a smooth group scheme and $(\cs{L},\mu)$ is a character sheaf on $G$ with trivial restriction to $G\der$,
+then the set of isomorphism classes of objects in $\CS(G\ab)$ mapping to $(\cs{L},\mu)$ under $q^*$ is a principal homogeneous space
+for $C$.
+\end{corollary}
+\begin{proof}
+By Proposition~\ref{prop:CSGabab}, it suffices to find the set of isomorphism classes in $\CSab(G)$ mapping to
+$(\cs{L},\mu)$ under the forgetful functor.  By the previous corollary this set is nonempty.
+If $(\cs{L},\mu,\beta)$ and $(\cs{L},\mu,\beta')$ both map to $(\cs{L},\mu)$, then $\beta' \circ \beta^{-1}$ is an
+automorphism of the constant sheaf on $G\der$.  Conversely, if $\varphi$ is an automorphism of $(\EE)_{G\der}$
+and $(\cs{L},\mu,\beta) \in \CSab(G)$ then $(\cs{L},\mu,\varphi \circ \beta) \in \CSab(G)$.  By \cite{cunningham-roe:13a}*{Thm. 3.9},
+the automorphism group is isomorphic to $\Hom(\pi_0(\bar{G}\der)_{\mathcal{W}}, \EEx)$.  Finally, we note that any
+automorphism $\alpha$ of $(\cs{L},\mu) \in \CS(G)$ defines an isomorphism $(\cs{L},\mu,\beta \circ \alpha|_{G\der}) \to (\cs{L},\mu,\beta)$.
+Applying \cite{cunningham-roe:13a}*{Thm. 3.9} again yields the desired result.
 \end{proof}

### 2017-05-02 Geometric types.tex
Added new proof of the theorem

@@
 
-\begin{lemma}
-If $(\cs{L},\mu,\beta)\in \CS\ab(G)$ then $\mu  : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism in $\CS\ab(G\times G)$.
+\begin{lemma}\label{lemma:morinCSab}
+If $(\cs{L},\mu,\beta)\in \CS\ab(G)$ then $\mu  : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$, $\gamma : m^*\cs{L} \to  \theta^*(m^*\cs{L})$ and $\vartheta: \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are morphisms in $\CS\ab(G\times G)$.
 \end{lemma}
@@
 First we show that $m^*\cs{L}$ is an object in $\CS(G^2)$.
-If $(\cs{L},\mu) \in \CS(G)$ then $m^*\cs{L}$ equipped with the isomorphism $(m^2)^* (m^*\cs{L}) \to m^*\cs{L} \boxtimes m^*\cs{L}$ defined by the diagram below.
-\[
-\begin{tikzcd}
-(m^2)^* (m^*\cs{L}) \arrow{d}{(m^2)^*\mu} \arrow{rr} && m^*\cs{L} \boxtimes m^*\cs{L}\\
- (m^2)^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & (m^2)^*(p_1)^*\cs{L} \otimes (m^2)^*(p_2)^*\cs{L} \arrow[equal]{r} & (p^2_1)^*m^*\cs{L} \otimes (p^2_2)^*m^*\cs{L} \arrow[equal]{u}
+If $(\cs{L},\mu) \in \CS(G)$ then $m^*\cs{L}$ equipped with the isomorphism $\mu^2: (m^2)^* (m^*\cs{L}) \to m^*\cs{L} \boxtimes m^*\cs{L}$ defined by the diagram below.
+\[
+\begin{tikzcd}
+(m^2)^* (m^*\cs{L}) \arrow{d}{(m^2)^*\mu} \arrow{rr}{\mu^2} && m^*\cs{L} \boxtimes m^*\cs{L}\\
+ (m^2)^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & (m^2)^*(p_1)^*\cs{L} \otimes (m^2)^*(p_2)^*\cs{L} \arrow{r} & (p^2_1)^*m^*\cs{L} \otimes (p^2_2)^*m^*\cs{L} \arrow[equal]{u}
 \end{tikzcd}
@@
 Pull-back along the abelianization $q : G \to G\ab$
-defines an equivalence of categories \todo{Is this trivial now?}
+defines an equivalence of categories
 \[
@@
 \begin{proof}
+By definition, $\CCS(G)$ is a full subcategory of $\CS\ab(G)$; likewise, $\CCS(G\ab)$ is a full subcategory of $\CS\ab(G\ab)$.
+We have just seen that $\CS\ab(G\ab)$ is equivalent to $\CS(G\ab)$.
+By Proposition~\ref{prop:CSGabab}, pullback along the abelianization $q : G \to G\ab$ induces an equivalence $q^*\ab : \CS\ab(G)\to CS\ab(G)$.
+Thus, the functor $\CS\ab(G\ab)\to \CS\ab(G)$ induced by pullback along $q$ is an equivalence.
+The functor $\CCS(G\ab)\to \CCS(G)$ under consideration is the restriction of $\CS\ab(G\ab)\to \CS\ab(G)$ to the subcategory $\CCS(G\ab)$. 
 \[
@@
 \CS\ab(G) & \arrow{l} \CS\ab(G\ab) \arrow{u}[swap]{\text{equiv.}}\\
-\CCS(G) \arrow[>->]{u} & \arrow{l} \CCS(G\ab) \arrow[>->]{u}\\
-\end{tikzcd}
-\]
-\todo{Clifton is working here}
+\CCS(G) \arrow[>->]{u} & \arrow{l} \CCS(G\ab) \arrow[>->]{u}
+\end{tikzcd}
+\]
+To prove the theorem, it is now sufficient to show that $\CCS(G\ab)\to \CCS(G)$ is essentially surjective.
+Suppose $(\cs{L},\nu,\beta)\in \CCS(G)$.
+Then $(\cs{L},\nu,\beta)\in \CS\ab(G)$.
+Let $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ be given by the equivalences above.
+Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}\ab$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ as in Section~\ref{sec:comcom}.
+Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ as in Section~\ref{ssec:noncomdef}.
+By Lemma~\ref{lemma:morinCSab}, the diagram on the right, below, is in $\CS(G\ab)$ and the diagram on the left, below, is in $\CS\ab(G)$.
 \[
@@
 \]
-
-By Definition~\ref{def:CCScom}, $\CCS(G\ab) \to \CS(G\ab)$ is a full subcategory.
-Since the comparison functor $\CS(G\ab) \to \CS_{G\der}(G)$ is an equivalence, it determines a full subcategory $\CCS_{G\der}(G)$ which is equivalent to $\CCS(G\ab)$, as pictured below.
-The proof of Theorem~\ref{thm:Gab} now reduces to the following claim: the essential image of $\CCS_{G\der}(G)$ under the equivalence $\CS_{G\der}(G) \to \CSab(G)$ is $\CCS(G)$.
-\[
-\begin{tikzcd}[row sep=30, column sep=40]
-\CSab(G) & \CS(G\ab) \arrow{l}{\text{equiv}}[swap]{q\ab^*} \\
-\CCS(G) \arrow{u}{\text{full sub}} & \CCS(G\ab) \arrow{u}[swap]{\text{full sub}} \arrow{l}[swap]{\text{equiv}}
-\end{tikzcd}
-%\begin{tikzcd}[row sep=30, column sep=40]
-%\CS(H) 
-%& \arrow{l}[swap]{j^*} \CS(G) 
-%&\arrow{l}[swap]{q^*} 
-%\CS(G\ab) \arrow{dl}{\text{equiv}}[swap]{q_{H}^*} \\
-%\CS'(G)  \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}} 
-%&  \CS_{H}(G) \arrow{u}{\text{forget}}  
-%&  %\arrow[bend left=35pt, dashed]{dll} 
-%\CCS(G\ab) \arrow{u}[swap]{\text{full sub}} \arrow{dl}{\text{equiv}} \\
-%\CCS(G) \arrow{u}{\text{full sub}} \arrow{r}{\beta \mapsto \nu}[swap]{\text{equiv}}
-%& \arrow{u}{\text{full sub}}  \CCS_{H}(G) 
-%& 
-%\end{tikzcd}
-\]
-
-Let $(\cs{L},\mu,\nu)$ be the image of $(\cs{L},\mu,\beta)\in \CSab(G)$ and of $(\cs{L}\ab,\mu\ab)$ under $q\ab^*$;
-we must show that $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
-Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}\ab$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ as in Section~\ref{sec:comcom}.
-Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ as in Section~\ref{ssec:noncomdef}.
-Recall the equivalence $L_2 : \Loc(G^2\ab) \to  \Loc_{G^2\der}(G^2)$ from Proposition~\ref{prop:CSGabab}.
-The diagram in Definition~\ref{def:CCS} is precisely the result of applying the functor $L_2$ to the diagram in Definition~\ref{def:CCScom}, as pictured below; 
-in particular $\gamma = (q^2)^* \xi$.
-  \[
-  \begin{tikzcd}[row sep=10, column sep = 20]
-   m_0^*\cs{L}_0 \arrow{dd}[swap]{\xi} \arrow{r}{\mu_0} 
-   & \cs{L}_0\boxtimes\cs{L}_0 \arrow{dd}{\vartheta}
-&&&   m^*\cs{L} \arrow{dd}[swap]{\gamma} \arrow{r}{\mu} 
- & \cs{L}\boxtimes\cs{L} \arrow{dd}{\vartheta}\\
- && \arrow{r}{(q^2)^*}  &\ & & &\\ 
-   \theta^*(m_0^*\cs{L}_0) \arrow{r}{{\theta}^*\mu_0} 
- &  \theta^*(\cs{L}_0\boxtimes\cs{L}_0)
-&&&   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} 
-&  \theta^*(\cs{L}\boxtimes\cs{L})
-  \end{tikzcd}
-\]
-The diagram on the right is a diagram in $\Loc_{G^2\der}(G^2)$.
-Using the equivalence $L_2$, this corresponds to a diagram in $\Loc(G^2\ab)$, necessarily the diagram on the left, above.
-It follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes. 
-In other words, $(\cs{L},\mu,\beta)\in \CCS(G)$
-if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G)$.
+The diagram on the left, above, is precisely the result of applying the functor $(q^2)^*\ab$ to the diagram on the right, above; in particular $\gamma = (q^2)^*\ab \xi$.
+Since $(q^2)^*\ab$ is an equivalence by Proposition~\ref{prop:CSGabab}, it follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes.
+In other words, $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
+
 \end{proof}

### 2017-05-02 Geometric types.tex
Added brief proof of new lemma.

@@
 First we show that $m^*\cs{L}$ is an object in $\CS(G^2)$.
-If $(\cs{L},\mu) \in \CS(G)$ then $m^*\cs{L}$ equipped with the isomorphism $\mu^2: (m^2)^* (m^*\cs{L}) \to m^*\cs{L} \boxtimes m^*\cs{L}$ defined by the diagram below.
-\[
-\begin{tikzcd}
-(m^2)^* (m^*\cs{L}) \arrow{d}{(m^2)^*\mu} \arrow{rr}{\mu^2} && m^*\cs{L} \boxtimes m^*\cs{L}\\
+If $(\cs{L},\mu) \in \CS(G)$ then $m^*\cs{L}$ equipped with the isomorphism $\mu_m^2: (m^2)^* (m^*\cs{L}) \to m^*\cs{L} \boxtimes m^*\cs{L}$ defined by the diagram below.
+\[
+\begin{tikzcd}
+(m^2)^* (m^*\cs{L}) \arrow{d}{(m^2)^*\mu} \arrow{rr}{\mu_m^2} && m^*\cs{L} \boxtimes m^*\cs{L}\\
  (m^2)^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & (m^2)^*(p_1)^*\cs{L} \otimes (m^2)^*(p_2)^*\cs{L} \arrow{r} & (p^2_1)^*m^*\cs{L} \otimes (p^2_2)^*m^*\cs{L} \arrow[equal]{u}
@@
 \] 
-\todo{Clifton is working here}
+The pair $(m^*\cs{L},\mu_m^2)$ satisfies the conditions appearing in \cite{cunningham-roe:13a}*{Def. 1.1}.
+The restriction of $m^*\cs{L}$ to $G^2\der= G\der\times G\der$ is canonically isomorphic to $(\EE)_{G^2\der}$ by
+\[
+\begin{tikzcd}
+(m^*\cs{L})\vert_{G^2\der} \arrow{d}{\mu\vert_{G^2\der}} \arrow{r}{\beta^2} & (\EE)_{G^2\der}\\
+(\cs{L}\boxtimes\cs{L})\vert_{G^2\der} \arrow[equal]{r} & (\cs{L}\vert_{G\der})\boxtimes(\cs{L}\vert_{G\der}) \arrow{u}{\beta\boxtimes\beta}.
+\end{tikzcd}
+\]
+This shows that $(m^*\cs{L},\mu_m^2,\beta_m^2) \in \CS\ab(G)$. 
+Similar work defines $(\cs{L}\boxtimes\cs{L},\mu_\boxtimes^2,\beta_\boxtimes^2) \in \CS\ab(G)$.
+By construction, $\mu: m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism in $\CS\ab(G^2)$.
+Similar work shows that $\gamma : m^*\cs{L} \to  \theta^*(m^*\cs{L})$ and $\vartheta: \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are also morphisms in $\CS\ab(G^2)$.
 \end{proof}

### 2017-05-02 Geometric types.tex
Talking with  David
Intro for section 3.2

@@
 motivating the following category.
+%
+Recall from Section~\ref{sec:defs} that we refer to objects in category $\CS(G)$, defined as
+in \cite{cunningham-roe:13a}*{Def. 1.1}, as linear character sheaves when $G$ is smooth but
+not necessarily commutative.
 
@@
 
-Recall from Section~\ref{sec:defs} that we refer to objects in category $\CS(G)$, defined as
-in \cite{cunningham-roe:13a}*{Def. 1.1}, as linear character sheaves when $G$ is smooth but
-not necessarily commutative.  
+In this section we give an equivalence of categories between $\CS(G\ab)$ and $\CSab(G)$ and use it to describe
+the pullback functor $q^* : \CS(G\ab) \to \CS(G)$ in terms of the forgetful functor $\CSab(G) \to \CS(G)$.
+We start with a method that will allow us to situate the diagram in Definition \ref{def:CCS} within $\CSab(G \times G)$.
+
+\begin{lemma}\label{lemma:morinCSab}
+If $(\cs{L},\mu,\beta)\in \CS\ab(G)$ then $\mu  : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$, $\gamma : m^*\cs{L} \to  \theta^*(m^*\cs{L})$ and $\vartheta: \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are morphisms in $\CS\ab(G\times G)$.
+\end{lemma}
+\begin{proof}
+Set $G^2 = G\times G$. Define $m^2 : G^2\times G^2 \to G^2$ by $m^2(g_1,g_2,g_1'g_2') = (g_1g_1',g_2g_2')$. Also define $p^2_i : G^2\times G^2 \to G^2$ by $p^2_i(g_1,g_2,g_1'g_2') = g_i g_i'$.
+First we show that $m^*\cs{L}$ is an object in $\CS(G^2)$.
+If $(\cs{L},\mu) \in \CS(G)$ then $m^*\cs{L}$ equipped with the isomorphism $\mu_m^2: (m^2)^* (m^*\cs{L}) \to m^*\cs{L} \boxtimes m^*\cs{L}$ defined by the diagram below.
+\[
+\begin{tikzcd}
+(m^2)^* (m^*\cs{L}) \arrow{d}{(m^2)^*\mu} \arrow{rr}{\mu_m^2} && m^*\cs{L} \boxtimes m^*\cs{L}\\
+ (m^2)^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & (m^2)^*(p_1)^*\cs{L} \otimes (m^2)^*(p_2)^*\cs{L} \arrow{r} & (p^2_1)^*m^*\cs{L} \otimes (p^2_2)^*m^*\cs{L} \arrow[equal]{u}
+\end{tikzcd}
+\] 
+The pair $(m^*\cs{L},\mu_m^2)$ satisfies the conditions appearing in \cite{cunningham-roe:13a}*{Def. 1.1}.
+The restriction of $m^*\cs{L}$ to $G^2\der= G\der\times G\der$ is canonically isomorphic to $(\EE)_{G^2\der}$ by
+\[
+\begin{tikzcd}
+(m^*\cs{L})\vert_{G^2\der} \arrow{d}{\mu\vert_{G^2\der}} \arrow{r}{\beta^2} & (\EE)_{G^2\der}\\
+(\cs{L}\boxtimes\cs{L})\vert_{G^2\der} \arrow[equal]{r} & (\cs{L}\vert_{G\der})\boxtimes(\cs{L}\vert_{G\der}) \arrow{u}{\beta\boxtimes\beta}.
+\end{tikzcd}
+\]
+This shows that $(m^*\cs{L},\mu_m^2,\beta_m^2) \in \CS\ab(G)$. 
+Similar work defines $(\cs{L}\boxtimes\cs{L},\mu_\boxtimes^2,\beta_\boxtimes^2) \in \CS\ab(G)$.
+By construction, $\mu: m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism in $\CS\ab(G^2)$.
+Similar work shows that $\gamma : m^*\cs{L} \to  \theta^*(m^*\cs{L})$ and $\vartheta: \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are also morphisms in $\CS\ab(G^2)$.
+\end{proof}
+
 In order to study commutative character sheaves, we need some auxiliary categories.
@@
 %%%%%%%%%%%%%%%%%
-
-\begin{lemma}\label{lemma:morinCSab}
-If $(\cs{L},\mu,\beta)\in \CS\ab(G)$ then $\mu  : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$, $\gamma : m^*\cs{L} \to  \theta^*(m^*\cs{L})$ and $\vartheta: \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are morphisms in $\CS\ab(G\times G)$.
-\end{lemma}
-\begin{proof}
-Set $G^2 = G\times G$. Define $m^2 : G^2\times G^2 \to G^2$ by $m^2(g_1,g_2,g_1'g_2') = (g_1g_1',g_2g_2')$. Also define $p^2_i : G^2\times G^2 \to G^2$ by $p^2_i(g_1,g_2,g_1'g_2') = g_i g_i'$.
-First we show that $m^*\cs{L}$ is an object in $\CS(G^2)$.
-If $(\cs{L},\mu) \in \CS(G)$ then $m^*\cs{L}$ equipped with the isomorphism $\mu_m^2: (m^2)^* (m^*\cs{L}) \to m^*\cs{L} \boxtimes m^*\cs{L}$ defined by the diagram below.
-\[
-\begin{tikzcd}
-(m^2)^* (m^*\cs{L}) \arrow{d}{(m^2)^*\mu} \arrow{rr}{\mu_m^2} && m^*\cs{L} \boxtimes m^*\cs{L}\\
- (m^2)^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & (m^2)^*(p_1)^*\cs{L} \otimes (m^2)^*(p_2)^*\cs{L} \arrow{r} & (p^2_1)^*m^*\cs{L} \otimes (p^2_2)^*m^*\cs{L} \arrow[equal]{u}
-\end{tikzcd}
-\] 
-The pair $(m^*\cs{L},\mu_m^2)$ satisfies the conditions appearing in \cite{cunningham-roe:13a}*{Def. 1.1}.
-The restriction of $m^*\cs{L}$ to $G^2\der= G\der\times G\der$ is canonically isomorphic to $(\EE)_{G^2\der}$ by
-\[
-\begin{tikzcd}
-(m^*\cs{L})\vert_{G^2\der} \arrow{d}{\mu\vert_{G^2\der}} \arrow{r}{\beta^2} & (\EE)_{G^2\der}\\
-(\cs{L}\boxtimes\cs{L})\vert_{G^2\der} \arrow[equal]{r} & (\cs{L}\vert_{G\der})\boxtimes(\cs{L}\vert_{G\der}) \arrow{u}{\beta\boxtimes\beta}.
-\end{tikzcd}
-\]
-This shows that $(m^*\cs{L},\mu_m^2,\beta_m^2) \in \CS\ab(G)$. 
-Similar work defines $(\cs{L}\boxtimes\cs{L},\mu_\boxtimes^2,\beta_\boxtimes^2) \in \CS\ab(G)$.
-By construction, $\mu: m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism in $\CS\ab(G^2)$.
-Similar work shows that $\gamma : m^*\cs{L} \to  \theta^*(m^*\cs{L})$ and $\vartheta: \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are also morphisms in $\CS\ab(G^2)$.
-\end{proof}
 

### 2017-05-03 Geometric types.tex
Fixing typos, adding todos to the proof of Prop 3.4

@@
 Both are smooth morphisms of $\Fq$-schemes.
-Set $m' = i \circ m \circ \theta$; we have $j\circ c = m \circ (m \times m')$.
+Set $m' = i \circ m \circ \theta$; we have $j\circ c = m \circ (m \times m')$. \todo{$j$ is not defined, and the needed definition conflicts with the definition of $i$ and $j$ given later.}
 Then $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms below.
@@
 \begin{proof}
-Set $G^2 = G\times G$. Define $m^2 : G^2\times G^2 \to G^2$ by $m^2(g_1,g_2,g_1'g_2') = (g_1g_1',g_2g_2')$. Also define $p^2_i : G^2\times G^2 \to G^2$ by $p^2_i(g_1,g_2,g_1'g_2') = g_i g_i'$.
-First we show that $m^*\cs{L}$ is an object in $\CS(G^2)$.
-If $(\cs{L},\mu) \in \CS(G)$ then $m^*\cs{L}$ equipped with the isomorphism $\mu_m^2: (m^2)^* (m^*\cs{L}) \to m^*\cs{L} \boxtimes m^*\cs{L}$ defined by the diagram below.
+Set $G^2 = G\times G$. Define $m^2 : G^2\times G^2 \to G^2$ by $m^2(g_1,g_2,g_1',g_2') = (g_1g_1',g_2g_2')$. Also define $p^2_i : G^2\times G^2 \to G^2$ by $p^2_i(g_1,g_2,g_1,'g_2') = (g_i,g_i')$.
+First we show that $m^*\cs{L}$ is an object in $\CS(G^2)$ by equipping it with an isomorphism $\mu_m^2: (m^2)^* (m^*\cs{L}) \to m^*\cs{L} \boxtimes m^*\cs{L}$ defined by the diagram below.
 \[
@@
 \item Let $\Loc_{G\der}(G)$ be the category of $G\der$-equivariant local systems on $G$, whose definition we now recall.
-Let $m : G\times G\to G$ be multiplication in $G$, $n : G\der\times G\to G$ be its to $G\der\times G$,
+Let $m : G\times G\to G$ be multiplication in $G$, $n : G\der\times G\to G$ be its restriction to $G\der\times G$,
 $p : G\der\times G \to G$ projection to the second component, and $s: G \to G\der\times G$ be given by $s(g) = (1,g)$.
@@
 s^*n^*\cs{L} \arrow{r}{s^*(\nu)} & s^*p^*\cs{L}\\
-\cs{L} \arrow[equal]{u}{n\circ s = \id_G}  \arrow{r}{\id_{\cs{L}}} & \cs{L} \arrow[equal]{u}[swap]{n=p\circ s = \id_G},
+\cs{L} \arrow[equal]{u}{n\circ s = \id_G}  \arrow{r}{\id_{\cs{L}}} & \cs{L} \arrow[equal]{u}[swap]{p\circ s = \id_G},
 \end{tikzcd}
@@
 \begin{tikzcd}
-& \arrow[equal]{dl}{n\circ n_2=n\circ n_1} n_2^*n^*\cs{L} \arrow{rr}{n_2^*(\nu)} && n_2^*p^*\cs{L} \arrow[equal]{dr}[swap]{n_2\circ p = n\circ p_2}& \\
+& \arrow[equal]{dl}{n\circ n_2=n\circ n_1} n_2^*n^*\cs{L} \arrow{rr}{n_2^*(\nu)} && n_2^*p^*\cs{L} \arrow[equal]{dr}[swap]{p \circ n_2 = n\circ p_2}& \\
 n_1^*n^*\cs{L} \arrow{dr}[swap]{n_1^*(\nu)} &&&& \arrow{dl}{p_2^*(\nu)} p_2^*n^*\cs{L}\\
@@
 Now set $G^2 \ceq G\times G$, so $G^2\ab =  G\ab \times G\ab$ and $G^2\der = G\der \times G\der$. Let $q_2 : G^2 \to G^2\ab$ be the abelianization quotient.  
-Let $L_2 : \Loc(G^2\ab) \to \Loc_{G^2\der}(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$.
+Let $L_2 : \Loc(G^2\ab) \to \Loc_{G^2\der}(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$. \todo{Add reference to Lemma 3.3}
 Then $L_2$ is also an equivalence since $q_2$ is also a $G^2\der$-torsor.
@@
 Since both $L$ and $L_2$ are equivalences, this functor $\CS(G\ab) \to \CSab'(G)$ is an equivalence of categories.
+\todo{I'm a bit wary of constructing an equivalence componentwise in this way; how does it show that the result is full and faithful since it's just talking about objects?}
 
 Let $i : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\times G$ by $j(h) = (i(h),1_G)$. 
-For $(\cs{L},\mu,\nu)\in \CSab'(G)$, $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism.
+For $(\cs{L},\mu,\nu)\in \CSab'(G)$, $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism. \todo{For $j^*(\nu)$ to make sense, need $j : G\der \to G\der \times G$}
 This defines a functor
@@
 Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i(h),g)$.
-Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p_n^*\cs{L}$ by
+Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p_n^*\cs{L}$ \todo{I assume this should be $p^*\cs{L}$?} by
 \[
@@
 It now follows that $\CSab'(G) \to \CSab(G)$ is an equivalence.
+\todo{Is it easy to see why the morphisms that commute with $\mu$ and $\beta$ are the same as those commuting with $\mu$ and $\nu$?
+Is this straight from the definition of the functor?}
 \end{proof}
@@
 \begin{tikzcd}
-\CS(G\der) & \arrow{l}[swap]{j^*} \CS(G) &\arrow{l}[swap]{q^*} 
+\CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
 \CS(G\ab) \arrow{dl}{q\ab^*} \\
@@
 Conversely, suppose $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$.
-Then $j^*(\cs{L},\mu) \iso j^*q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G\der)$. 
-Since $q\circ j = 1_{G\ab}$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ in $\CS(G\der)$.
+Then $i^*(\cs{L},\mu) \iso i^*q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G\der)$. 
+Since $q\circ i = 1_{G\ab}$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ in $\CS(G\der)$.
 \end{proof}
@@
 \[
-\Hom(\pi_0(\bar{G})_{\mathcal{W}}, \EEx) \to \Hom(\pi_0(\bar{G}\der)_{\mathcal{W}}, \EEx),
-\]
-where $\pi_0(\bar{G})_\mathcal{W}$ denotes the covariants of the action of Frobenius on
-the component group of $G$
+\Hom(\pi_0(\bar{G})_{\Frob{}}, \EEx) \to \Hom(\pi_0(\bar{G}\der)_{\Frob{}}, \EEx),
+\]
+where $\pi_0(\bar{G})_{\Frob{}}$ denotes the covariants of the action of Frobenius on
+the component group of $\bar{G}$
 
@@
 and $(\cs{L},\mu,\beta) \in \CSab(G)$ then $(\cs{L},\mu,\varphi \circ \beta) \in \CSab(G)$.  By \cite{cunningham-roe:13a}*{Thm. 3.9},
-the automorphism group is isomorphic to $\Hom(\pi_0(\bar{G}\der)_{\mathcal{W}}, \EEx)$.  Finally, we note that any
+the automorphism group is isomorphic to $\Hom(\pi_0(\bar{G}\der)_{\Frob{}}, \EEx)$.  Finally, we note that any
 automorphism $\alpha$ of $(\cs{L},\mu) \in \CS(G)$ defines an isomorphism $(\cs{L},\mu,\beta \circ \alpha|_{G\der}) \to (\cs{L},\mu,\beta)$.
@@
 Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ as in Section~\ref{ssec:noncomdef}.
-By Lemma~\ref{lemma:morinCSab}, the diagram on the right, below, is in $\CS(G\ab)$ and the diagram on the left, below, is in $\CS\ab(G)$.
+By Lemma~\ref{lemma:morinCSab}, the diagrams below are in $\CS(G\ab)$ (right) and $\CS\ab(G)$ (left).
 \[
@@
 \]
-The diagram on the left, above, is precisely the result of applying the functor $(q^2)^*\ab$ to the diagram on the right, above; in particular $\gamma = (q^2)^*\ab \xi$.
+The diagram on the left is the result of applying the functor $(q^2)^*\ab$ to the one on the right; in particular $\gamma = (q^2)^*\ab \xi$.
 Since $(q^2)^*\ab$ is an equivalence by Proposition~\ref{prop:CSGabab}, it follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes.
@@
 Every map in $\CCS(G)$ is either trivial or an isomorphism, and the automorphism group of any object in $\CCS(G)$ is canonically
-isomorphic to $\Hom(\pi_0(G\ab)_{\Frob{}},\EEx)$.
+isomorphic to $\Hom(\pi_0(\bar{G}\ab)_{\Frob{}},\EEx)$.
 \end{corollary}
@@
 \begin{proof}
+The first claim follows from Theorems \ref{thm:trfrobiso} and \ref{thm:Gab}.
 Let us write $(\cs{L},\mu,\beta) \mapsto (\cs{L}\ab,\mu\ab)$ to indicate the equivalence appearing in Theorem~\ref{thm:Gab};
 then \[\Aut_{\CCS(G)}(\cs{L},\mu,\beta) = \Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab).\] 
-By \cite{cunningham-roe:13a}*{Thm 3.9},  $\Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab) = \Hom(\pi_0(G\ab)_{\Frob{}},\EEx)$.
+By \cite{cunningham-roe:13a}*{Thm 3.9},  $\Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab) = \Hom(\pi_0(\bar{G}\ab)_{\Frob{}},\EEx)$.
 \end{proof}

### 2017-05-04 Geometric types.tex
Catching up

@@
 \address{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive Northwest, Calgary, Alberta, Canada, {T2N~1N4}.}
-\email{cunning@math.ucalgary.ca}
+\email{cunningham@pims.math.ca}
 \author{David Roe}
@@
 \usepackage{hyperref}
+\hypersetup{
+  colorlinks   = true, %Colours links instead of ugly boxes
+  urlcolor     = blue, %Colour for external hyperlinks
+  linkcolor    = blue, %Colour of internal links
+  citecolor   = green %Colour of citations
+}
+\usepackage[margin=3.5cm]{geometry}
+%\renewcommand{\baselinestretch}{1.0}
 
@@
 As proved by Ju-Lee Kim in \cite{kim:07a}, all irreducible supercuspidal representations of tamely ramified $p$-adic groups can be built from ``data'' introduced by Jiu-Kang Yu in \cite{yu:01a}*{\S 15}.
-While the type, in the sense of Bushnell \& Kutzko \cite{bushnell-kutzko:98a}, of a supercuspidal representation built from Yu data can be constructed directly from the datum, it is convenient to consider and intermediate object, introduced in \cite{yu:01a}*{Remark 15.4}, which we call a \emph{Yu type datum}.
+While the type, in the sense of Bushnell \& Kutzko \cite{bushnell-kutzko:98a}, of a supercuspidal representation built from Yu data can be constructed directly from the datum, it is convenient to consider an intermediate object, introduced in \cite{yu:01a}*{Remark 15.4}, which we call a \emph{Yu type datum}.
 Yu type data are studied in \cite{Yu:models}, which concludes with the following observation.
@@
 We also compute the automorphism groups in $\CCS(G)$.
-Then in Section \ref{ssec:proofs}, we give proofs of the results in Section \ref{sec:noncom}, which require a development of equivariant linear character sheaves. 
+Then in Section \ref{ssec:proofs}, we give proofs of the results in Section \ref{sec:noncom}, which require a development of equivariant linear character sheaves. \todo{Fix this.}
 % 
@@
 \begin{tikzcd}
-(m^*\cs{L})\vert_{G^2\der} \arrow{d}{\mu\vert_{G^2\der}} \arrow{r}{\beta^2} & (\EE)_{G^2\der}\\
+(m^*\cs{L})\vert_{G^2\der} \arrow{d}{\mu\vert_{G^2\der}} \arrow{r}{\beta^2_m} & (\EE)_{G^2\der}\\
 (\cs{L}\boxtimes\cs{L})\vert_{G^2\der} \arrow[equal]{r} & (\cs{L}\vert_{G\der})\boxtimes(\cs{L}\vert_{G\der}) \arrow{u}{\beta\boxtimes\beta}.
@@
 Conversely, suppose $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$.
-Then $i^*(\cs{L},\mu) \iso i^*q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G\der)$. 
+Then 
+\[
+i^*(\cs{L},\mu) \iso i^*q^*(\cs{L}\ab,\mu\ab)
+\]
+ in $\CS(G\der)$.
 Since $q\circ i = 1_{G\ab}$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ in $\CS(G\der)$.
@@
 
+First, Yu introduces 
+\begin{enumerate}
+\labitem{Y3}{Y3}
+compact groups $J_i\subset \oK$, for $i=0, \ldots d$, such that 
+$
+\oK^i = J_0\cdots J_{i}
+$ 
+and, for $i=0, \ldots d-1$, a natural action of $\oK^i$ on $J_{i+1}$ defining the groups $\oK^i \ltimes J_{i+1}$.
+\begin{equation}\label{eq:semiprod}
+\begin{tikzcd}
+\ && 1 \arrow{d} && \\
+\ && \oK^{i}\cap J_{i+1}\arrow{d} && \\
+1 \arrow{r} & J_{i+1} \arrow{r} & \oK^i \ltimes J_{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & \oK^i \arrow{r} & 1\\
+&& \oK^{i+1} \arrow{d}{} && \\
+&& 1 &&
+\end{tikzcd}
+\end{equation}
+\end{enumerate}
+%He then introduces the following quotients of $J_{i+1}$ and $\oK^i$, for $i=0, \ldots d-1$.
+%
+Next, Yu defines a group homomorphism (in fact, a quotient) 
+$
+J_{i+1} \to V_{i+1}
+$
+where $V_{i+1}$ is a finite abelian group, the latter also given the structure of a $\Fq$-vector space.
+The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to Z_{i+1}$, where $Z_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : Z_{i+1} \to \CC^\times$.
+%\labitem{Q2}{Q2} 
+%\item 
+This, in turn, is used to define a map
+$
+J_{i+1} \to V_{i+1}^\sharp,
+$
+where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $Z_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$, as in Section~\ref{ssec:Jacobi}.
+In fact, the quotient $J_{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J_{i+1} \to H_{i+1}$ and an isomorphism $j_{i+1} : H_{i+1} \to V_{i+1}^\sharp$, where $H_{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:01a}*{}.
+%\labitem{Q3}{Q3} 
+%\item
+Finally, Yu constructs a group homomorphism $f_{i+1} : \oK^i \to \Sp(V_{i+1})$ such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $\oK^i$ on $H_{i+1}$ in the sense of \cite{yu:01a}.
+%
+Taken together, this defines
+%\end{enumerate}
+\begin{enumerate}
+\labitem{Y4}{Y4}  
+a group homomorphism $h_{i+1} : \oK^i \ltimes J_{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
+\[
+\begin{tikzcd}
+1 \arrow{r} & J_{i+1} \arrow{d} \arrow{r} & \oK^i \ltimes J_{i+1} \arrow{d}{h_{i+1}} \arrow{r}{p_i} & \oK^i \arrow{r} \arrow{d}{f_i} & 1\\ 
+1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
+\end{tikzcd}
+\]
+\end{enumerate}
+
 \begin{table}[ht]
@@
 
-First, Yu introduces 
-\begin{enumerate}
-\labitem{Y3}{Y3}
-compact groups $J_i\subset \oK$, for $i=0, \ldots d$, such that 
-$
-\oK^i = J_0\cdots J_{i}
-$ 
-and, for $i=0, \ldots d-1$, a natural action of $\oK^i$ on $J_{i+1}$ defining the groups $\oK^i \ltimes J_{i+1}$.
-\begin{equation}\label{eq:semiprod}
-\begin{tikzcd}
-\ && 1 \arrow{d} && \\
-\ && \oK^{i}\cap J_{i+1}\arrow{d} && \\
-1 \arrow{r} & J_{i+1} \arrow{r} & \oK^i \ltimes J_{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & \oK^i \arrow{r} & 1\\
-&& \oK^{i+1} \arrow{d}{} && \\
-&& 1 &&
-\end{tikzcd}
-\end{equation}
-\end{enumerate}
-%He then introduces the following quotients of $J_{i+1}$ and $\oK^i$, for $i=0, \ldots d-1$.
-%
-Next, Yu defines a group homomorphism (in fact, a quotient) 
-$
-J_{i+1} \to V_{i+1}
-$
-where $V_{i+1}$ is a finite abelian group, the latter also given the structure of a $\Fq$-vector space.
-The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to Z_{i+1}$, where $Z_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : Z_{i+1} \to \CC^\times$.
-%\labitem{Q2}{Q2} 
-%\item 
-This, in turn, is used to define a map
-$
-J_{i+1} \to V_{i+1}^\sharp,
-$
-where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $Z_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$, as in Section~\ref{ssec:Jacobi}.
-In fact, the quotient $J_{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J_{i+1} \to H_{i+1}$ and an isomorphism $j_{i+1} : H_{i+1} \to V_{i+1}^\sharp$, where $H_{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:01a}*{}.
-%\labitem{Q3}{Q3} 
-%\item
-Finally, Yu constructs a group homomorphism $f_{i+1} : \oK^i \to \Sp(V_{i+1})$ such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $\oK^i$ on $H_{i+1}$ in the sense of \cite{yu:01a}.
-%
-Taken together, this defines
-%\end{enumerate}
-\begin{enumerate}
-\labitem{Y4}{Y4}  
-a group homomorphism $h_{i+1} : \oK^i \ltimes J_{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
-\[
-\begin{tikzcd}
-1 \arrow{r} & J_{i+1} \arrow{d} \arrow{r} & \oK^i \ltimes J_{i+1} \arrow{d}{h_{i+1}} \arrow{r}{p_i} & \oK^i \arrow{r} \arrow{d}{f_i} & 1\\ 
-1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
-\end{tikzcd}
-\]
-\end{enumerate}
-
 We can now recall how Yu uses all this to construct representations $\orho^i$ of $\oK^i$, for $i=1, \ldots, d$ and the types $(\oK^i,\orho_i)$.

### 2017-05-04 Geometric types.tex
I'm running out of time so will commit now. But I haven't finished addressing all David's good comments.

@@
 We also compute the automorphism groups in $\CCS(G)$.
-Then in Section \ref{ssec:proofs}, we give proofs of the results in Section \ref{sec:noncom}, which require a development of equivariant linear character sheaves. \todo{Fix this.}
+%Then in Section \ref{ssec:proofs}, we give proofs of the results in Section \ref{sec:noncom}, which require a development of equivariant linear character sheaves. \todo{Fix this.}
 % 
@@
 Both are smooth morphisms of $\Fq$-schemes.
-Set $m' = i \circ m \circ \theta$; we have $j\circ c = m \circ (m \times m')$. \todo{$j$ is not defined, and the needed definition conflicts with the definition of $i$ and $j$ given later.}
+Set $m' = i \circ m \circ \theta$ and let $j\der : G\der\to G$ be inclusion; then $j\der\circ c = m \circ (m \times m')$.
+% \todo{$j$ is not defined, and the needed definition conflicts with the definition of $i$ and $j$ given later.}
 Then $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms below.
@@
 	&  c^*((\EE)_{G\der}) \arrow[equal]{d} \\
-\arrow{d}[swap]{j\circ c = m \circ (m \times m')} c^* j^* \cs{L} 
+\arrow{d}[swap]{j\der\circ c = m \circ (m \times m')} c^* j\der^* \cs{L} 
 	&   (\EE)_{G\times G} \\
@@
 \end{equation}
-In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations; so, for example, the middle left isomorphism comes from $(m\times m')^* m^* \iso c^* j^*$ since $j\circ c = m \circ (m \times m')$.
+In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations; so, for example, the middle left isomorphism comes from $(m\times m')^* m^* \iso c^* j\der^*$ since $j\der\circ c = m \circ (m \times m')$.
 Using the monoidal structure of the category of Weil local systems on $G\times G$, the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ defines an isomorphism
@@
   \]
-Here $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ above. 
+Here $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ as above. 
 \end{definition}
@@
 \]
-This shows that $(m^*\cs{L},\mu_m^2,\beta_m^2) \in \CS\ab(G)$. 
-Similar work defines $(\cs{L}\boxtimes\cs{L},\mu_\boxtimes^2,\beta_\boxtimes^2) \in \CS\ab(G)$.
+This shows that $(m^*\cs{L},\mu_m^2,\beta_m^2) \in \CS\ab(G^2)$. 
+Similar work defines $(\cs{L}\boxtimes\cs{L},\mu_\boxtimes^2,\beta_\boxtimes^2) \in \CS\ab(G^2)$.
 By construction, $\mu: m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism in $\CS\ab(G^2)$.
@@
 \item Let $\Loc_{G\der}(G)$ be the category of $G\der$-equivariant local systems on $G$, whose definition we now recall.
-Let $m : G\times G\to G$ be multiplication in $G$, $n : G\der\times G\to G$ be its restriction to $G\der\times G$,
-$p : G\der\times G \to G$ projection to the second component, and $s: G \to G\der\times G$ be given by $s(g) = (1,g)$.
-Then objects in $\Loc_{G\der}(G)$ are pairs $(\cs{L},\nu)$ where $\cs{L}$ is a local system on $G$ and
+Let $n : G\der\times G\to G$ be the restriction of $m : G\times G\to G$ to $G\der\times G$,
+let $p_n : G\der\times G \to G$ be projection to the second component, and let $s: G \to G\der\times G$ be given by $s(g) = (1,g)$.
+Objects in $\Loc_{G\der}(G)$ are pairs $(\cs{L},\nu)$ where $\cs{L}$ is a local system on $G$ and
 $\nu : n^*\cs{L} \to p^*\cs{L}$ is an isomorphism such that the following two diagrams commute.
@@
 \item Let $\CSab'(G)$ be the category of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$; thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p^*\cs{L}$ are isomorphisms.
-Morphisms are morphisms in $\Loc(G)$ commuting with $\mu$ and $\nu$. 
+Morphisms in $\Loc_{G\der}(G)$ are morphisms in $\Loc(G)$ commuting with $\mu$ and $\nu$. 
 \end{itemize}
-We relate $\CSab(G)$ to $\CS(G\ab)$ via the quotient map $q : G \to G\ab$.
+
+\begin{lemma}\label{lemma:descent}
+\end{lemma}
+
+We may now relate $\CSab(G)$ to $\CS(G\ab)$ via the quotient map $q : G \to G\ab$.
 
@@
 
-Let $i : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\times G$ by $j(h) = (i(h),1_G)$. 
+Let $i\der : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\der\times G$ by $j(h) = (i\der(h),1_G)$. 
 For $(\cs{L},\mu,\nu)\in \CSab'(G)$, $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism. \todo{For $j^*(\nu)$ to make sense, need $j : G\der \to G\der \times G$}
@@
 \]
-Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i(h),g)$.
+Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i\der(h),g)$.
 Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p_n^*\cs{L}$ \todo{I assume this should be $p^*\cs{L}$?} by
@@
 \begin{tikzcd}
-\CS(G\der) & \arrow{l}[swap]{i^*} \CS(G) &\arrow{l}[swap]{q^*} 
+\CS(G\der) & \arrow{l}[swap]{i\der^*} \CS(G) &\arrow{l}[swap]{q^*} 
 \CS(G\ab) \arrow{dl}{q\ab^*} \\
@@
 \[
-i^*(\cs{L},\mu) \iso i^*q^*(\cs{L}\ab,\mu\ab)
+i\der^*(\cs{L},\mu) \iso i\der^*q^*(\cs{L}\ab,\mu\ab)
 \]
  in $\CS(G\der)$.
-Since $q\circ i = 1_{G\ab}$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ in $\CS(G\der)$.
+Since $q\circ i\der = 1$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ in $\CS(G\der)$.
 \end{proof}

### 2017-05-05 Geometric types.tex
Talking with David.

@@
 the pullback functor $q^* : \CS(G\ab) \to \CS(G)$ in terms of the forgetful functor $\CSab(G) \to \CS(G)$.
-We start with a method that will allow us to situate the diagram in Definition \ref{def:CCS} within $\CSab(G \times G)$.
-
-\begin{lemma}\label{lemma:morinCSab}
-If $(\cs{L},\mu,\beta)\in \CS\ab(G)$ then $\mu  : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$, $\gamma : m^*\cs{L} \to  \theta^*(m^*\cs{L})$ and $\vartheta: \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are morphisms in $\CS\ab(G\times G)$.
-\end{lemma}
-\begin{proof}
-Set $G^2 = G\times G$. Define $m^2 : G^2\times G^2 \to G^2$ by $m^2(g_1,g_2,g_1',g_2') = (g_1g_1',g_2g_2')$. Also define $p^2_i : G^2\times G^2 \to G^2$ by $p^2_i(g_1,g_2,g_1,'g_2') = (g_i,g_i')$.
-First we show that $m^*\cs{L}$ is an object in $\CS(G^2)$ by equipping it with an isomorphism $\mu_m^2: (m^2)^* (m^*\cs{L}) \to m^*\cs{L} \boxtimes m^*\cs{L}$ defined by the diagram below.
-\[
-\begin{tikzcd}
-(m^2)^* (m^*\cs{L}) \arrow{d}{(m^2)^*\mu} \arrow{rr}{\mu_m^2} && m^*\cs{L} \boxtimes m^*\cs{L}\\
- (m^2)^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & (m^2)^*(p_1)^*\cs{L} \otimes (m^2)^*(p_2)^*\cs{L} \arrow{r} & (p^2_1)^*m^*\cs{L} \otimes (p^2_2)^*m^*\cs{L} \arrow[equal]{u}
-\end{tikzcd}
-\] 
-The pair $(m^*\cs{L},\mu_m^2)$ satisfies the conditions appearing in \cite{cunningham-roe:13a}*{Def. 1.1}.
-The restriction of $m^*\cs{L}$ to $G^2\der= G\der\times G\der$ is canonically isomorphic to $(\EE)_{G^2\der}$ by
-\[
-\begin{tikzcd}
-(m^*\cs{L})\vert_{G^2\der} \arrow{d}{\mu\vert_{G^2\der}} \arrow{r}{\beta^2_m} & (\EE)_{G^2\der}\\
-(\cs{L}\boxtimes\cs{L})\vert_{G^2\der} \arrow[equal]{r} & (\cs{L}\vert_{G\der})\boxtimes(\cs{L}\vert_{G\der}) \arrow{u}{\beta\boxtimes\beta}.
-\end{tikzcd}
-\]
-This shows that $(m^*\cs{L},\mu_m^2,\beta_m^2) \in \CS\ab(G^2)$. 
-Similar work defines $(\cs{L}\boxtimes\cs{L},\mu_\boxtimes^2,\beta_\boxtimes^2) \in \CS\ab(G^2)$.
-By construction, $\mu: m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism in $\CS\ab(G^2)$.
-Similar work shows that $\gamma : m^*\cs{L} \to  \theta^*(m^*\cs{L})$ and $\vartheta: \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are also morphisms in $\CS\ab(G^2)$.
-\end{proof}
 
@@
 Let $n : G\der\times G\to G$ be the restriction of $m : G\times G\to G$ to $G\der\times G$,
-let $p_n : G\der\times G \to G$ be projection to the second component, and let $s: G \to G\der\times G$ be given by $s(g) = (1,g)$.
+let $p : G\der\times G \to G$ be projection to the second component, and let $s: G \to G\der\times G$ be given by $s(g) = (1,g)$.
 Objects in $\Loc_{G\der}(G)$ are pairs $(\cs{L},\nu)$ where $\cs{L}$ is a local system on $G$ and
@@
 Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i\der(h),g)$.
-Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p_n^*\cs{L}$ \todo{I assume this should be $p^*\cs{L}$?} by
-\[
-\begin{tikzcd}
-& n^* \cs{L} \arrow{dl}{m\circ k = n} \arrow{r} & p_n^*\cs{L} &  \\ 
+Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p^*\cs{L}$ 
+%\todo{I assume this should be $p^*\cs{L}$?} by
+\[
+\begin{tikzcd}
+& n^* \cs{L} \arrow{dl}{m\circ k = n} \arrow{r} & p^*\cs{L} &  \\ 
 k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
@@
 
+We start with a method that will allow us to situate the diagram in Definition \ref{def:CCS} within $\CSab(G \times G)$.
+
+\begin{lemma}\label{lemma:morinCSab}
+If $(\cs{L},\mu,\beta)\in \CS\ab(G)$ then $\mu  : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$, $\gamma : m^*\cs{L} \to  \theta^*(m^*\cs{L})$ and $\vartheta: \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are morphisms in $\CS\ab(G\times G)$.
+\end{lemma}
+\begin{proof}
+Set $G^2 = G\times G$. Define $m^2 : G^2\times G^2 \to G^2$ by $m^2(g_1,g_2,g_1',g_2') = (g_1g_1',g_2g_2')$. Also define $p^2_i : G^2\times G^2 \to G^2$ by $p^2_i(g_1,g_2,g_1,'g_2') = (g_i,g_i')$.
+First we show that $m^*\cs{L}$ is an object in $\CS(G^2)$ by equipping it with an isomorphism $\mu_m^2: (m^2)^* (m^*\cs{L}) \to m^*\cs{L} \boxtimes m^*\cs{L}$ defined by the diagram below.
+\[
+\begin{tikzcd}
+(m^2)^* (m^*\cs{L}) \arrow{d}{(m^2)^*\mu} \arrow{rr}{\mu_m^2} && m^*\cs{L} \boxtimes m^*\cs{L}\\
+ (m^2)^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & (m^2)^*(p_1)^*\cs{L} \otimes (m^2)^*(p_2)^*\cs{L} \arrow{r} & (p^2_1)^*m^*\cs{L} \otimes (p^2_2)^*m^*\cs{L} \arrow[equal]{u}
+\end{tikzcd}
+\] 
+The pair $(m^*\cs{L},\mu_m^2)$ satisfies the conditions appearing in \cite{cunningham-roe:13a}*{Def. 1.1}.
+The restriction of $m^*\cs{L}$ to $G^2\der= G\der\times G\der$ is canonically isomorphic to $(\EE)_{G^2\der}$ by
+\[
+\begin{tikzcd}
+(m^*\cs{L})\vert_{G^2\der} \arrow{d}{\mu\vert_{G^2\der}} \arrow{r}{\beta^2_m} & (\EE)_{G^2\der}\\
+(\cs{L}\boxtimes\cs{L})\vert_{G^2\der} \arrow[equal]{r} & (\cs{L}\vert_{G\der})\boxtimes(\cs{L}\vert_{G\der}) \arrow{u}{\beta\boxtimes\beta}.
+\end{tikzcd}
+\]
+This shows that $(m^*\cs{L},\mu_m^2,\beta_m^2) \in \CS\ab(G^2)$. 
+Similar work defines $(\cs{L}\boxtimes\cs{L},\mu_\boxtimes^2,\beta_\boxtimes^2) \in \CS\ab(G^2)$.
+By construction, $\mu: m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism in $\CS\ab(G^2)$.
+Similar work shows that $\gamma : m^*\cs{L} \to  \theta^*(m^*\cs{L})$ and $\vartheta: \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are also morphisms in $\CS\ab(G^2)$.
+\end{proof}
+
 Suppose $G$ is commutative, so $G\der = 1$. 

### 2017-05-07 Geometric types.tex
Some work on descent

@@
 In order to study commutative character sheaves, we need some auxiliary categories.
-\begin{itemize}
-\item Let $\Loc(G)$ and $\Loc(G\ab)$ be the categories of local systems on $G$ and $G\ab$, respectively.
-\item Let $\Loc_{G\der}(G)$ be the category of $G\der$-equivariant local systems on $G$, whose definition we now recall.
+%\begin{itemize}
+%\item 
+Let $\Loc(G)$ and $\Loc(G\ab)$ be the categories of local systems on $G$ and $G\ab$, respectively.
+%\item 
+Let $\Loc_{G\der}(G)$ be the category of $G\der$-equivariant local systems on $G$, whose definition we now recall.
 Let $n : G\der\times G\to G$ be the restriction of $m : G\times G\to G$ to $G\der\times G$,
 let $p : G\der\times G \to G$ be projection to the second component, and let $s: G \to G\der\times G$ be given by $s(g) = (1,g)$.
-Objects in $\Loc_{G\der}(G)$ are pairs $(\cs{L},\nu)$ where $\cs{L}$ is a local system on $G$ and
-$\nu : n^*\cs{L} \to p^*\cs{L}$ is an isomorphism such that the following two diagrams commute.
-\[
-\begin{tikzcd}
-s^*n^*\cs{L} \arrow{r}{s^*(\nu)} & s^*p^*\cs{L}\\
-\cs{L} \arrow[equal]{u}{n\circ s = \id_G}  \arrow{r}{\id_{\cs{L}}} & \cs{L} \arrow[equal]{u}[swap]{p\circ s = \id_G},
-\end{tikzcd}
-\]
-and with $n_1(h_1,h_2,g) = (h_1h_2,g)$, $n_2(h_1,h_2,g) = (h_1,n(h_2,g))$ and $p_2(h_1,h_2,g) = (h_2,g)$,
-\[
-\begin{tikzcd}
-& \arrow[equal]{dl}{n\circ n_2=n\circ n_1} n_2^*n^*\cs{L} \arrow{rr}{n_2^*(\nu)} && n_2^*p^*\cs{L} \arrow[equal]{dr}[swap]{p \circ n_2 = n\circ p_2}& \\
-n_1^*n^*\cs{L} \arrow{dr}[swap]{n_1^*(\nu)} &&&& \arrow{dl}{p_2^*(\nu)} p_2^*n^*\cs{L}\\
-& n_1^*p^*\cs{L} \arrow[equal]{rr}{p\circ n_1 = p\circ p_2} && p_2^*p^*\cs{L} .
-\end{tikzcd}
-\]
-Morphisms are morphisms in $\Loc(G)$ commuting with $\nu$.
-\item Let $\CSab'(G)$ be the category of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$; thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p^*\cs{L}$ are isomorphisms.
-Morphisms in $\Loc_{G\der}(G)$ are morphisms in $\Loc(G)$ commuting with $\mu$ and $\nu$. 
-\end{itemize}
-
-\begin{lemma}\label{lemma:descent}
-\end{lemma}
-
-We may now relate $\CSab(G)$ to $\CS(G\ab)$ via the quotient map $q : G \to G\ab$.
-
-%%%%%%%%
-\iffalse
-
-\todo{Define $q\ab^* : \CS(G\ab) \to \CSab(G)$; missing definition of $\beta$ in the following commented section}
-Now suppose $q : G \to Q$ is a regular epimorphism of smooth group schemes with kernel pair $(a,p)$
-\[
-\begin{tikzcd}
-H\times G
- \arrow[shift left=2]{r}{a}
-  \arrow[shift right=2,swap]{r}{p}
+Then $q : G \to G\ab$ is a regular epimorphism of smooth group schemes with kernel pair $(n,p)$.
+\[
+\begin{tikzcd}
+G\der\times G
+ \arrow[shift left=1]{r}{n}
+  \arrow[shift right=1,swap]{r}{p}
 &
@@
 & 
-Q.
-\end{tikzcd}
-\]
-Let $(\cs{L}_0, \mu_0)$ be a linear character sheaf on $Q$ and set $(\cs{L}, \mu) \ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$.
+G\ab
+\end{tikzcd}
+\]
+Objects in the category $\Loc_{G\der}(G)$ of $G\der$-equivariant local systems on $G$ are pairs $(\cs{L},\nu)$ where $\cs{L}$ is a local system on $G$ and $\nu : n^*\cs{L} \to p^*\cs{L}$ is an isomorphism such that the diagram
+\[
+\begin{tikzcd}
+s^*n^*\cs{L} \arrow{r}{s^*(\nu)} & s^*p^*\cs{L}\\
+\cs{L} \arrow[equal]{u}{n\circ s = \id_G}  \arrow{r}{\id_{\cs{L}}} & \cs{L} \arrow[equal]{u}[swap]{p\circ s = \id_G},
+\end{tikzcd}
+\]
+commutes, and also such that the following diagram commutes, where $n_1(h_1,h_2,g) = (h_1h_2,g)$, $n_2(h_1,h_2,g) = (h_1,n(h_2,g))$ and $p_2(h_1,h_2,g) = (h_2,g)$.
+\[
+\begin{tikzcd}
+& \arrow[equal]{dl}{n\circ n_2=n\circ n_1} n_2^*n^*\cs{L} \arrow{rr}{n_2^*(\nu)} && n_2^*p^*\cs{L} \arrow[equal]{dr}[swap]{p \circ n_2 = n\circ p_2}& \\
+n_1^*n^*\cs{L} \arrow{dr}[swap]{n_1^*(\nu)} &&&& \arrow{dl}{p_2^*(\nu)} p_2^*n^*\cs{L}\\
+& n_1^*p^*\cs{L} \arrow[equal]{rr}{p\circ n_1 = p\circ p_2} && p_2^*p^*\cs{L} .
+\end{tikzcd}
+\]
+Morphisms in $\Loc_{G\der}(G)$ are morphisms in $\Loc(G)$ commuting with $\nu$.
+
+%\item 
+Let $\CS_{G\der}(G)$ be the category of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$.
+%Thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p^*\cs{L}$ are isomorphisms.
+Morphisms in $\CS_{G\der}(G)$ are morphisms in $\CS(G)$ commuting with $\nu$. 
+%\end{itemize}
+
+%%%%%%%%
+%\iffalse
+
+\begin{lemma}\label{lemma:descent}
+\end{lemma}
+
+\todo{Define $q\ab^* : \CS(G\ab) \to \CSab(G)$; missing definition of $\beta$ in the following commented section}
+
+%Let $(\cs{L}_0, \mu_0)$ be a linear character sheaf on $Q$ and set $(\cs{L}, \mu) \ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$.
 Consider the functor
 \[
-q^* : \CS(Q) \to \CS(G)
-\]
-given on objects by $(\cs{L}_0,\mu_0) \mapsto (\cs{L}, \mu)$; see \cite{cunningham-roe:13a}*{Lem 1.4}.
-To see that $(q^*\cs{L}_0, (q\times q)^* \mu_0)$ is indeed a linear character sheaf on $G$,
-verify \cite{cunningham-roe:13a}, CS.3], arguing as in \cite{cunningham-roe:13a}].
-The linear character sheaf $(\cs{L},\mu)$ on $G$ comes equipped with a canonical isomorphism $\nu : a^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of isomorphisms.
+q^* : \CS(G\ab) \to \CS(G)
+\]
+given on objects by $(\cs{L}\ab,\mu\ab) \mapsto (q^*\cs{L}\ab, (q^2)^* \mu\ab)$ where $q^2= q\times q$; see \cite{cunningham-roe:13a}*{Lem 1.4}.
+To see that $(q^*\cs{L}\ab, (q^2)^* \mu\ab)$ is indeed a linear character sheaf on $G$,
+verify \cite{cunningham-roe:13a}*{CS.3}. %, arguing as in \cite{cunningham-roe:13a}.
+The linear character sheaf $(\cs{L},\mu)$ on $G$ comes equipped with a canonical isomorphism $\nu : n^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of isomorphisms.
 \[
 \begin{tikzcd}[column sep=40]
-a^*\cs{L} \arrow[equal]{d} \arrow[dashed]{r}{\nu} &  \arrow[equal]{d} p^*\cs{L} \\
-a^* ( q^*\cs{L}_0) \arrow{r}{q\circ a = q\circ p}
-& p^* (q^*\cs{L}_0)
-\end{tikzcd}
-\]
-Since this isomorphism satisfies \eqref{ECS1}, it follows that $(\cs{L}, \mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$.
+n^*\cs{L} \arrow[equal]{d} \arrow[dashed]{r}{\nu} &  \arrow[equal]{d} p^*\cs{L} \\
+n^* ( q^*\cs{L}\ab) \arrow{r}{q\circ n = q\circ p}
+& p^* (q^*\cs{L}\ab)
+\end{tikzcd}
+\]
+Then $(\cs{L}, \mu,\nu)$ is an object in $\CS_{G\der}(G)$.
 If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(Q)$, 
@@
 
-\begin{proposition} \label{prop:Gder_triv}
-Suppose $G$ is a smooth group scheme and $(\cs{L},\mu) \in \CS(G)$.
-Then the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $(\cs{L},\mu) \cong q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, for some $(\cs{L}\ab,\mu\ab) \in \CS(G\ab)$.
-\end{proposition}
-Proposition~\ref{prop:Gder_triv} will be proven in Section \ref{ssec:proof1}.
-
-\fi
+We may now begin to relate $\CSab(G)$ to $\CS(G\ab)$ via the quotient map $q : G \to G\ab$.
+
+%\fi
 %%%%%%%%%%%%%%%%%
@@
 
-Let $i\der : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\der\times G$ by $j(h) = (i\der(h),1_G)$. 
+Let $i\der : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\der\times G$ by $j(h) = (h,1_G)$. 
 For $(\cs{L},\mu,\nu)\in \CSab'(G)$, $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism. \todo{For $j^*(\nu)$ to make sense, need $j : G\der \to G\der \times G$}

### 2017-05-09 Geometric types.tex
Talking with  David

@@
 
+Let $q : G\to G\ab$ be the quotient
 In this section we give an equivalence of categories between $\CS(G\ab)$ and $\CSab(G)$ and use it to describe
@@
 
+Suppose $\cs{L}\ab\in \Loc(G\ab)$.
+The local system $q^*\cs{L}\ab \in \Loc(G)$ is equivariant, for $\nu : n^*q^*\cs{L}\ab\to p^*q^*\cs{L}\ab$ defined by
+
+\begin{lemma}\label{lemma:descent}
+\end{lemma}
+
 %\item 
-Let $\CS_{G\der}(G)$ be the category of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$.
+Let $\CS_{\text{eq}}(G)$ be the category of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$.
 %Thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p^*\cs{L}$ are isomorphisms.
@@
 %\iffalse
-
-\begin{lemma}\label{lemma:descent}
-\end{lemma}
 

### 2017-05-10 Geometric types.tex
Moving to a difference computer.

--- 2017-05-07 Geometric types.tex
@@
 In order to study commutative character sheaves, we need some auxiliary categories.
-%\begin{itemize}
-%\item 
-Let $\Loc(G)$ and $\Loc(G\ab)$ be the categories of local systems on $G$ and $G\ab$, respectively.
-%\item 
-Let $\Loc_{G\der}(G)$ be the category of $G\der$-equivariant local systems on $G$, whose definition we now recall.
+
+\subsubsection{Equivariant Weil local systems}\label{ssec:equivariant1}
+
+Let $\Loc(G)$ and $\Loc(G\ab)$ be the categories of Weil local systems on $G$ and $G\ab$, respectively.
+%
+Let $\Loc_{G\der}(G)$ be the category of $G\der$-equivariant Weil local systems on $G$, whose definition we now recall.
 Let $n : G\der\times G\to G$ be the restriction of $m : G\times G\to G$ to $G\der\times G$,
 let $p : G\der\times G \to G$ be projection to the second component, and let $s: G \to G\der\times G$ be given by $s(g) = (1,g)$.
-Then $q : G \to G\ab$ is a regular epimorphism of smooth group schemes with kernel pair $(n,p)$.
+Then the quotient $q : G \to G\ab$ is a regular epimorphism of smooth group schemes with kernel pair $(n,p)$.
 \[
@@
 \]
-Objects in the category $\Loc_{G\der}(G)$ of $G\der$-equivariant local systems on $G$ are pairs $(\cs{L},\nu)$ where $\cs{L}$ is a local system on $G$ and $\nu : n^*\cs{L} \to p^*\cs{L}$ is an isomorphism such that the diagram
-\[
-\begin{tikzcd}
-s^*n^*\cs{L} \arrow{r}{s^*(\nu)} & s^*p^*\cs{L}\\
-\cs{L} \arrow[equal]{u}{n\circ s = \id_G}  \arrow{r}{\id_{\cs{L}}} & \cs{L} \arrow[equal]{u}[swap]{p\circ s = \id_G},
-\end{tikzcd}
-\]
-commutes, and also such that the following diagram commutes, where $n_1(h_1,h_2,g) = (h_1h_2,g)$, $n_2(h_1,h_2,g) = (h_1,n(h_2,g))$ and $p_2(h_1,h_2,g) = (h_2,g)$.
-\[
-\begin{tikzcd}
-& \arrow[equal]{dl}{n\circ n_2=n\circ n_1} n_2^*n^*\cs{L} \arrow{rr}{n_2^*(\nu)} && n_2^*p^*\cs{L} \arrow[equal]{dr}[swap]{p \circ n_2 = n\circ p_2}& \\
-n_1^*n^*\cs{L} \arrow{dr}[swap]{n_1^*(\nu)} &&&& \arrow{dl}{p_2^*(\nu)} p_2^*n^*\cs{L}\\
-& n_1^*p^*\cs{L} \arrow[equal]{rr}{p\circ n_1 = p\circ p_2} && p_2^*p^*\cs{L} .
-\end{tikzcd}
-\]
-Morphisms in $\Loc_{G\der}(G)$ are morphisms in $\Loc(G)$ commuting with $\nu$.
-
-%\item 
-Let $\CS_{G\der}(G)$ be the category of triples $(\cs{L},\nu,\mu)$ where $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\nu)\in \Loc_{G\der}(G)$.
-%Thus, $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu :  n^*\cs{L} \to p^*\cs{L}$ are isomorphisms.
-Morphisms in $\CS_{G\der}(G)$ are morphisms in $\CS(G)$ commuting with $\nu$. 
-%\end{itemize}
-
-%%%%%%%%
-%\iffalse
-
-\begin{lemma}\label{lemma:descent}
+Consider the morphisms
+\[
+\begin{tikzcd}
+G\der \times G\der \times G 
+\arrow[shift left=2]{r}{b_1, b_2, b_3} 
+\arrow{r}{}
+\arrow[shift right=2]{r}{} 
+& G\der \times G 
+\arrow[shift left=1]{r}{n}
+\arrow[shift right=1]{r}[swap]{p}
+ & G 
+\end{tikzcd}
+\]
+defined by 
+\begin{align*}
+b_1(h_1,h_2,g) &= (h_1h_2,g) \\
+b_2(h_1,h_2,g) &= (h_1,h_2g) \\
+b_3(h_1,h_2,g) &= (h_2,g).
+\end{align*}
+Note that
+\begin{align*}
+n\circ b_1 &= n\circ b_2 \\
+n\circ b_3 &= p\circ b_2 \numberthis \label{eqn:bap}\\
+p\circ b_1 &= p\circ b_3.
+\end{align*}
+Define $s : G\to G\der\times G$ by $s(g) = (1,g)$.
+A $G\der$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
+\[
+\nu : n^*\cs{L} \to p^*\cs{L}
+\] 
+of Weil local systems on $G\der\times G$ such that 
+\begin{equation}\label{E1}
+s^*(\nu) = \id_{\cs{L}}
+\end{equation}
+and such that the following diagram of isomorphisms of local systems on $G\der\times G\der\times G$ commutes. 
+\begin{equation}\label{E2}
+\begin{tikzcd}
+\ &  \arrow{dl}{n\circ b_1 = n\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
+b_1^* n^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
+& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L} & 
+\end{tikzcd}
+\end{equation}
+%In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from equations \eqref{eqn:bap}; so, for example, the top left isomorphism comes from $b_1^* n^* \iso b_2^* n^*$ since $n\circ b_1 = n\circ b_2$.
+%On stalks, this condition is ...
+%\[
+%\begin{tikzcd}
+%\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
+%\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
+%& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
+%\end{tikzcd}
+%\]
+Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
+\begin{equation}\label{E3}
+\begin{tikzcd}
+\arrow{d}[swap]{\nu} n^*\cs{L} \arrow{r}{n^*(\alpha)} & n^*\cs{L}' \arrow{d}{\nu'} \\
+p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
+\end{tikzcd}
+\end{equation}
+commutes.
+This defines $\Loc_{G\der}(G)$, the category of $G\der$-equivariant Weil local systems on $G$.
+The reader will recognize this notion as the Weil local system version of equivariant sheaves for the action $n$ of $G\der$ on $G$, as can be found, for example, in \cite{bernstein-lunts:equivariant}*{0.2}.
+
+\subsubsection{Equivariant linear character sheaves}\label{ssec:equivariant2}
+
+With reference to Section~\ref{ssec:equivariant1}, we define a $G\der$-equivariant linear character sheaf on $G$ to be a triple $(\cs{L},\mu, \nu)$, where $(\cs{L},\mu)$ is a linear character sheaf and $(\cs{L},\nu)$ is an $G\der$-equivariant Weil local system.
+A morphism of $G\der$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $G\der$-equivariant Weil local systems $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves.
+%so
+%\begin{equation}\label{CS4}
+%\begin{tikzcd}
+%\arrow{d}[swap]{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
+%\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
+%\end{tikzcd}
+%\end{equation}
+%commutes; see also \cite{cunningham-roe:13a}, CS.4].
+%
+Let $\CS\der(G)$ be the category of $G\der$-equivariant linear character sheaves on $G$.
+
+%Is $\CS_H(G)$ a rigid monoidal category?
+
+%If $(\cs{L},\mu,\nu)$ and $(\cs{L},\mu,\nu')$ in $\CS_H(G)$, then $\nu = \nu'$?
+
+\begin{lemma}
+Categories $\CS\der(G)$ and $\CS\ab(G)$ are equivalent.
 \end{lemma}
 
-\todo{Define $q\ab^* : \CS(G\ab) \to \CSab(G)$; missing definition of $\beta$ in the following commented section}
-
-%Let $(\cs{L}_0, \mu_0)$ be a linear character sheaf on $Q$ and set $(\cs{L}, \mu) \ceq (q^*\cs{L}_0, (q\times q)^* \mu_0)$.
+\begin{proof}
+Let $i\der : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\der\times G$ by $j(h) = (h,1_G)$. 
+If $(\cs{L},\mu,\nu)\in \CS\der(G)$ then $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism. 
+This defines a functor on objects by
+\[
+\begin{array}{rcl}
+\CS\der(G) &\to& \CSab(G) \\
+(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,j^*(\nu))
+\end{array}
+\]
+and on morphisms, trivially.
+It is easy to verify that morphisms that commute with $\mu$ and $\nu$ also commute with $\mu$ and $j^*(\nu)$.
+Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i\der(h),g)$.
+Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p^*\cs{L}$ by the following diagram.
+\[
+\begin{tikzcd}
+& n^* \cs{L} \arrow{dl}{m\circ k = n} \arrow{r}{\nu} & p^*\cs{L} &  \\ 
+k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
+& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id_\cs{L}}
+\end{tikzcd}
+\]
+Then $(\cs{L},\mu,\nu)\in \CS\der(G)$ maps to $(\cs{L},\mu,\beta)$.
+It now follows that $\CS\der(G) \to \CSab(G)$ is an equivalence. \todo{Add more detail to this proof?}
+\end{proof}
+
+Set $G^2 = G\times G$. Then $G^2\der = G\der\times G\der$ and $G^2\ab = G\ab\times G\ab$.
+
+\begin{lemma}\label{lem:HH}
+If $(\cs{L},\mu,\nu)$ is a $G\der$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ 
+%and $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ 
+is a morphism of $G^2\der$-equivariant Weil local systems on $G^2$. 
+\end{lemma}
+
+\begin{proof} 
+Define
+\begin{align*}
+d : H\times H\times G\times G &\to H\times G\times H\times G \\
+(h_1,h_2,g_1,g_2) &\mapsto (h_1, g_1, h_2, g_2)\\
+a_2 : H\times G\times H\times G &\to G\times G \\
+(h_1,g_1,h_2,g_2) &\mapsto (h_1g_1, h_2g_2) \\
+p_2 : H\times G\times H\times G &\to G\times G \\
+(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2) \\
+\theta_2 : H \times G \times H \times G &\to H \times G \times H \times G \\
+(h_1,g_1,h_2,g_2) &\mapsto (h_2,g_2,h_1,g_1).
+\end{align*}
+The following diagram defines the isomorphisms needed to see that both $m^*\cs{L}$ and $\cs{L}\boxtimes\cs{L}$ are $H\times H$-equivariant Weil local systems.
+\[
+\begin{tikzcd}[column sep=40]
+\arrow{d}[swap]{a_2^*(\mu)} a_2^* (m^*\cs{L}) \arrow[dashed]{r} 
+	& \arrow{d}{p_2^*(\mu)} p_2^*(m^*\cs{L})\\
+\arrow{d}[swap]{a_2= (a\times a)\circ d} a_2^*(\cs{L}\boxtimes\cs{L}) \arrow[dashed]{r} 
+	& \arrow{d}{p_2= (p\times p)\circ d} p_2^*(\cs{L}\boxtimes\cs{L}) \\
+%d^* (a\times a)^* (\cs{L}\boxtimes\cs{L}) & d^* (p\times p)^* (\cs{L}\boxtimes\cs{L}) \\
+d^* (a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{d^*(\nu\boxtimes \nu)}& d^*(p^*\cs{L}\boxtimes p^*\cs{L}) 
+\end{tikzcd}
+\]
+The dashed arrows both satisfy \eqref{E1} and \eqref{E2} as they apply here.
+This diagram also shows that $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of equivariant sheaves, since it satisfies \eqref{E3} as it applies here.
+\end{proof}
+
+\subsubsection{Descent}
+
 Consider the functor
@@
 \]
-given on objects by $(\cs{L}\ab,\mu\ab) \mapsto (q^*\cs{L}\ab, (q^2)^* \mu\ab)$ where $q^2= q\times q$; see \cite{cunningham-roe:13a}*{Lem 1.4}.
+given on objects by $(\cs{L}\ab,\mu\ab) \mapsto (q^*\cs{L}\ab, (q^2)^* \mu\ab)$ where $q^2= q\times q$; this is an instance of \cite{cunningham-roe:13a}*{Lemma 1.4}.
 To see that $(q^*\cs{L}\ab, (q^2)^* \mu\ab)$ is indeed a linear character sheaf on $G$,
@@
 \begin{tikzcd}[column sep=40]
-n^*\cs{L} \arrow[equal]{d} \arrow[dashed]{r}{\nu} &  \arrow[equal]{d} p^*\cs{L} \\
+n^*\cs{L} \arrow[equal]{d} \arrow{r}{\nu} &  \arrow[equal]{d} p^*\cs{L} \\
 n^* ( q^*\cs{L}\ab) \arrow{r}{q\circ n = q\circ p}
@@
 \]
-Then $(\cs{L}, \mu,\nu)$ is an object in $\CS_{G\der}(G)$.
-If $\alpha_0 : (\cs{L}_0,\mu_0) \to (\cs{L}_0',\mu_0')$ is a morphism in $\CS(Q)$, 
-then $q^*(\alpha_0) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha$ is a morphism in $\CS(G)$.
+Then $(\cs{L}, \mu,\nu)$ is an object in $\CS\der(G)$.
+If $\alpha : (\cs{L}\ab,\mu\ab) \to (\cs{L}\ab',\mu\ab')$ is a morphism in $\CS(G\ab)$, 
+then $q^*(\alpha\ab) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha$ is a morphism in $\CS(G)$.
 These simple observations define the comparison functor
 \[
-q_H^* : \CS(Q) \to CS_H(G)
+q\ab^* : \CS(G\ab) \to \CS\der(G)
 \]
@@
 \CS(G) &\arrow{l}[swap]{q^*} 
-\CS(Q) \arrow{dl}{q_H^*}\\
-\arrow{u}{\text{forget}} \CS_{H}(G). & 
+\CS(G\ab) \arrow{dl}{q\ab^*}\\
+\arrow{u}{\text{forget}} \CS\der(G). & 
 \end{tikzcd}
 \end{equation}
-The definition of $q_H^* : \CS(Q)\to \CS_H(G)$ will be revisited in the proof of the following result.
+The definition of $q\ab^* : \CS(G\ab)\to \CS\der(G)$ will be revisited in the proof of the following result.
 
@@
 
-Let $i\der : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\der\times G$ by $j(h) = (h,1_G)$. 
-For $(\cs{L},\mu,\nu)\in \CSab'(G)$, $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism. \todo{For $j^*(\nu)$ to make sense, need $j : G\der \to G\der \times G$}
-This defines a functor
-\[
-\begin{array}{rcl}
-\CSab'(G) &\to& \CSab(G) \\
-(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,j^*(\nu)).
-\end{array}
-\]
-Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i\der(h),g)$.
-Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p^*\cs{L}$ 
-%\todo{I assume this should be $p^*\cs{L}$?} by
-\[
-\begin{tikzcd}
-& n^* \cs{L} \arrow{dl}{m\circ k = n} \arrow{r} & p^*\cs{L} &  \\ 
-k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
-& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\times 1}
-\end{tikzcd}
-\]
-Then $(\cs{L},\mu,\nu)\in \CSab'(G)$ maps to $(\cs{L},\mu,\beta)$.
-It now follows that $\CSab'(G) \to \CSab(G)$ is an equivalence.
-\todo{Is it easy to see why the morphisms that commute with $\mu$ and $\beta$ are the same as those commuting with $\mu$ and $\nu$?
-Is this straight from the definition of the functor?}
+(I moved the rest...)
 \end{proof}

### 2017-05-10 Geometric types.tex
OK, I think this is all we need ...

@@
 In contrast to the connected case, $\TrFrob{G}$ may have nontrivial kernel;
-we gave an explicit description of its kernel as $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$ \cite{cunningham-roe:13a}*{Thm. 3.6}.
+we gave an explicit description of its kernel as $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$ \cite{cunningham-roe:13a}*{Theorem 3.6}.
 
@@
 
-In \cite{cunningham-roe:13a}*{Thm. 3.6}, we showed that $\TrFrob{G} : \CSiso{G} \to G(k)^*$ is surjective and
+In \cite{cunningham-roe:13a}*{Theorem 3.6}, we showed that $\TrFrob{G} : \CSiso{G} \to G(k)^*$ is surjective and
 explicitly computed its kernel.  In this section, we show that the corresponding map
@@
 For general smooth commutative group schemes, we use Lemma \ref{lem:conncomm} and the snake lemma, as in the proof of
-\cite{cunningham-roe:13a}*{Thm. 3.6}
+\cite{cunningham-roe:13a}*{Theorem 3.6}
 \end{proof}
@@
 the pullback functor $q^* : \CS(G\ab) \to \CS(G)$ in terms of the forgetful functor $\CSab(G) \to \CS(G)$.
-
-In order to study commutative character sheaves, we need some auxiliary categories.
+But first, in order to study commutative character sheaves, we need some auxiliary categories.
 
@@
 %
-Let $\Loc_{G\der}(G)$ be the category of $G\der$-equivariant Weil local systems on $G$, whose definition we now recall.
+Let $\Loc\der(G)$ be the category of $G\der$-equivariant Weil local systems on $G$, whose definition we now recall.
 Let $n : G\der\times G\to G$ be the restriction of $m : G\times G\to G$ to $G\der\times G$,
@@
 commutes.
-This defines $\Loc_{G\der}(G)$, the category of $G\der$-equivariant Weil local systems on $G$.
+This defines $\Loc\der(G)$, the category of $G\der$-equivariant Weil local systems on $G$.
 The reader will recognize this notion as the Weil local system version of equivariant sheaves for the action $n$ of $G\der$ on $G$, as can be found, for example, in \cite{bernstein-lunts:equivariant}*{0.2}.
@@
 
-\begin{lemma}
+\begin{lemma}\label{lemma:nubeta}
 Categories $\CS\der(G)$ and $\CS\ab(G)$ are equivalent.
@@
 Then $(\cs{L},\mu,\nu)\in \CS\der(G)$ maps to $(\cs{L},\mu,\beta)$.
-It now follows that $\CS\der(G) \to \CSab(G)$ is an equivalence. \todo{Add more detail to this proof?}
+It now follows that $\CS\der(G) \to \CSab(G)$ is an equivalence. \todo{Should we add more detail to this proof?}
 \end{proof}
 
-Set $G^2 = G\times G$. Then $G^2\der = G\der\times G\der$ and $G^2\ab = G\ab\times G\ab$.
+Set $G^2 = G\times G$, so $G^2\der = G\der\times G\der$ and $G^2\ab = G\ab\times G\ab$.
+Likewise define $n^2 : G\der^2 \times G^2 \to G^2$ and $p^2 : G\der^2\times G \to G$.
 
@@
 \begin{align*}
-d : H\times H\times G\times G &\to H\times G\times H\times G \\
+d : G\der\times G\der\times G\times G &\to G\der\times G\times G\der\times G \\
 (h_1,h_2,g_1,g_2) &\mapsto (h_1, g_1, h_2, g_2)\\
-a_2 : H\times G\times H\times G &\to G\times G \\
+n_2 : G\der\times G\times G\der\times G &\to G\times G \\
 (h_1,g_1,h_2,g_2) &\mapsto (h_1g_1, h_2g_2) \\
-p_2 : H\times G\times H\times G &\to G\times G \\
-(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2) \\
-\theta_2 : H \times G \times H \times G &\to H \times G \times H \times G \\
-(h_1,g_1,h_2,g_2) &\mapsto (h_2,g_2,h_1,g_1).
+p_2 : G\der\times G\times G\der\times G &\to G\times G \\
+(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2). %\\
+%\theta_2 : H \times G \times H \times G &\to H \times G \times H \times G \\
+%(h_1,g_1,h_2,g_2) &\mapsto (h_2,g_2,h_1,g_1).
 \end{align*}
-The following diagram defines the isomorphisms needed to see that both $m^*\cs{L}$ and $\cs{L}\boxtimes\cs{L}$ are $H\times H$-equivariant Weil local systems.
+The following diagram defines the isomorphisms needed to see that both $m^*\cs{L}$ and $\cs{L}\boxtimes\cs{L}$ are $G\der^2$-equivariant Weil local systems.
 \[
 \begin{tikzcd}[column sep=40]
-\arrow{d}[swap]{a_2^*(\mu)} a_2^* (m^*\cs{L}) \arrow[dashed]{r} 
+\arrow{d}[swap]{n_2^*(\mu)} n_2^* (m^*\cs{L}) \arrow[dashed]{r} 
 	& \arrow{d}{p_2^*(\mu)} p_2^*(m^*\cs{L})\\
-\arrow{d}[swap]{a_2= (a\times a)\circ d} a_2^*(\cs{L}\boxtimes\cs{L}) \arrow[dashed]{r} 
-	& \arrow{d}{p_2= (p\times p)\circ d} p_2^*(\cs{L}\boxtimes\cs{L}) \\
-%d^* (a\times a)^* (\cs{L}\boxtimes\cs{L}) & d^* (p\times p)^* (\cs{L}\boxtimes\cs{L}) \\
-d^* (a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{d^*(\nu\boxtimes \nu)}& d^*(p^*\cs{L}\boxtimes p^*\cs{L}) 
+\arrow{d}[swap]{n_2= n^2\circ d} n_2^*(\cs{L}\boxtimes\cs{L}) \arrow[dashed]{r} 
+	& \arrow{d}{p_2= p^2\circ d} p_2^*(\cs{L}\boxtimes\cs{L}) \\
+%d^* (n\times n)^* (\cs{L}\boxtimes\cs{L}) & d^* (p\times p)^* (\cs{L}\boxtimes\cs{L}) \\
+d^* (n^*\cs{L}\boxtimes n^*\cs{L}) \arrow{r}{d^*(\nu\boxtimes \nu)}& d^*(p^*\cs{L}\boxtimes p^*\cs{L}) 
 \end{tikzcd}
@@
 
+If $\cs{L}\ab\in \Loc(G\ab)$ then $q^*\cs{L}\ab\in \Loc(G)$ comes equipped with a canonical isomorphism $\nu(\cs{L}\ab) : n^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of isomorphisms.
+\[
+\begin{tikzcd}[column sep=40]
+n^*\cs{L} \arrow[equal]{d} \arrow{r}{\nu(\cs{L}\ab)} &  \arrow[equal]{d} p^*\cs{L} \\
+n^* ( q^*\cs{L}\ab) \arrow{r}{q\circ n = q\circ p}
+& p^* (q^*\cs{L}\ab)
+\end{tikzcd}
+\]
+Then $(q^*\cs{L}\ab,\nu(\cs{L}\ab))$ satisfies \eqref{E1} and \eqref{E2}, so $(q^*\cs{L}\ab,\nu(\cs{L}\ab))$ is an object in $\Loc\der(G)$.
+Moreover, if $\alpha\ab : \cs{L}\ab \to \cs{L}\ab$ is a morphism in $\Loc(G\ab)$ then $q^*(\alpha\ab)$ satisfies the condition in \eqref{E3}, so $q^*(\alpha\ab)$ is a morphism in $\Loc\der(G)$.
+This defines the functor
+\[
+L : \Loc(G\ab)\to \Loc\der(G)
+\]
+
+\begin{lemma}\label{lemma:descent}
+The functor $L : \Loc(G\ab)\to \Loc\der(G)$ is an equivalence.
+\end{lemma}
+\begin{proof}
+The quotient $q : G \to G\ab$ is an $G\der$-torsor in the fppf topology by \cite{demazure:SGA3-VIA}*{Thm. 3.2}, and thus an $G\der$-torsor in the fpqc topology.
+The lemma is now a result from descent theory, arguing as in \cite{Vistoli:notes}*{Theorem 4.46} for example. 
+\end{proof}
+
 Consider the functor
@@
 \]
-given on objects by $(\cs{L}\ab,\mu\ab) \mapsto (q^*\cs{L}\ab, (q^2)^* \mu\ab)$ where $q^2= q\times q$; this is an instance of \cite{cunningham-roe:13a}*{Lemma 1.4}.
+given on objects by $(\cs{L}\ab,\mu\ab) \mapsto (q^*\cs{L}\ab, (q^2)^* \mu\ab)$; this is an instance of \cite{cunningham-roe:13a}*{Lemma 1.4}.
 To see that $(q^*\cs{L}\ab, (q^2)^* \mu\ab)$ is indeed a linear character sheaf on $G$,
 verify \cite{cunningham-roe:13a}*{CS.3}. %, arguing as in \cite{cunningham-roe:13a}.
-The linear character sheaf $(\cs{L},\mu)$ on $G$ comes equipped with a canonical isomorphism $\nu : n^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of isomorphisms.
-\[
-\begin{tikzcd}[column sep=40]
-n^*\cs{L} \arrow[equal]{d} \arrow{r}{\nu} &  \arrow[equal]{d} p^*\cs{L} \\
-n^* ( q^*\cs{L}\ab) \arrow{r}{q\circ n = q\circ p}
-& p^* (q^*\cs{L}\ab)
-\end{tikzcd}
-\]
+Now set $L(\cs{L}\ab) = (\cs{L},\nu)$, where $L : \Loc(G\ab) \to \Loc\der(G)$ is the comparison functor above, so $\cs{L} = q^*\cs{L}\ab$ and $\nu = \nu(\cs{L}\ab)$.
 Then $(\cs{L}, \mu,\nu)$ is an object in $\CS\der(G)$.
@@
 \]
-and show that the functor $q^* : \CS(Q) \to \CS(G)$ factors according to the following commuting diagram of functors
+and also show that the functor $q^* : \CS(G\ab) \to \CS(G)$ factors according to the following commuting diagram of functors
 \begin{equation}\label{qH}
@@
 The definition of $q\ab^* : \CS(G\ab)\to \CS\der(G)$ will be revisited in the proof of the following result.
-
-We may now begin to relate $\CSab(G)$ to $\CS(G\ab)$ via the quotient map $q : G \to G\ab$.
-
-%\fi
-%%%%%%%%%%%%%%%%%
+We may now relate $\CSab(G)$ to $\CS(G\ab)$ via the quotient map $q : G \to G\ab$.
 
@@
 Suppose $G$ is a smooth group scheme.  
-Then pullback along $q : G \to G\ab$ defines an equivalence $q\ab^*: \CS(G\ab) \to \CSab(G)$.
+Then pullback along $q : G \to G\ab$ defines an equivalence $\CS(G\ab) \to \CSab(G)$.
 \end{proposition}
 \begin{proof}
-It now follows from descent theory that the comparison functor $L : \Loc(G\ab) \to \Loc_{G\der}(G)$ is an equivalence: argue as in \cite{Vistoli:notes}*{Thm 4.46} for example. 
-For $\cs{L}\ab\in \Loc(G\ab)$, we may write $L(\cs{L}\ab) = (\cs{L}, \nu)$, where $\cs{L} = q^*(\cs{L}\ab)$ and $\nu : n^*\cs{L}  \to p^*\cs{L}$ is an isomorphism. 
-Observe that $L$ followed by the forgetful functor $\Loc_{G\der}(G)\to \Loc(G)$ coincides with $q^*: \Loc(G\ab)\to \Loc(G)$. 
-%
-Now set $G^2 \ceq G\times G$, so $G^2\ab =  G\ab \times G\ab$ and $G^2\der = G\der \times G\der$. Let $q_2 : G^2 \to G^2\ab$ be the abelianization quotient.  
-Let $L_2 : \Loc(G^2\ab) \to \Loc_{G^2\der}(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$. \todo{Add reference to Lemma 3.3}
-Then $L_2$ is also an equivalence since $q_2$ is also a $G^2\der$-torsor.
-
-Consider the functor
+In light of Lemma~\ref{lemma:nubeta}, it suffices to prove that the comparison functor $q\ab^* : \CS(G\ab) \to \CS\der(G)$ is an equivalence. 
+Let $L^2 : \Loc(G^2\ab) \to \Loc\der(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$. 
+Then $L^2$ is also an equivalence by Lemma~\ref{lemma:descent}.
+Using Lemma~\ref{lem:HH}, we may rewrite the comparison functor $q\ab^*$ on objects by
 \[
 \begin{array}{rcl}
-\CS(G\ab) &\to& \CSab'(G) \\
-(\cs{L}\ab,\mu\ab) &\mapsto& (L(\cs{L}\ab), L_2(\mu\ab))
+\CS(G\ab) &\to& \CS\der(G) \\
+(\cs{L}\ab,\mu\ab) &\mapsto& (L(\cs{L}\ab), L^2(\mu\ab))
 \end{array}
 \]
-Since both $L$ and $L_2$ are equivalences, this functor $\CS(G\ab) \to \CSab'(G)$ is an equivalence of categories.
-\todo{I'm a bit wary of constructing an equivalence componentwise in this way; how does it show that the result is full and faithful since it's just talking about objects?}
-
-(I moved the rest...)
+and on morphisms by $\alpha \mapsto L(\alpha)$.
+The proposition now follows from the fact that both $L$ and $L^2$ are equivalences.
 \end{proof}
@@
 automorphism of the constant sheaf on $G\der$.  Conversely, if $\varphi$ is an automorphism of $(\EE)_{G\der}$
-and $(\cs{L},\mu,\beta) \in \CSab(G)$ then $(\cs{L},\mu,\varphi \circ \beta) \in \CSab(G)$.  By \cite{cunningham-roe:13a}*{Thm. 3.9},
+and $(\cs{L},\mu,\beta) \in \CSab(G)$ then $(\cs{L},\mu,\varphi \circ \beta) \in \CSab(G)$.  By \cite{cunningham-roe:13a}*{Theorem 3.9},
 the automorphism group is isomorphic to $\Hom(\pi_0(\bar{G}\der)_{\Frob{}}, \EEx)$.  Finally, we note that any
 automorphism $\alpha$ of $(\cs{L},\mu) \in \CS(G)$ defines an isomorphism $(\cs{L},\mu,\beta \circ \alpha|_{G\der}) \to (\cs{L},\mu,\beta)$.
-Applying \cite{cunningham-roe:13a}*{Thm. 3.9} again yields the desired result.
+Applying \cite{cunningham-roe:13a}*{Theorem 3.9} again yields the desired result.
 \end{proof}
@@
 
-We start with a method that will allow us to situate the diagram in Definition \ref{def:CCS} within $\CSab(G \times G)$.
+We start with a method that will allow us to situate the diagram in Definition \ref{def:CCS} within $\CSab(G^2)$.
 
@@
 \begin{proof}
-Set $G^2 = G\times G$. Define $m^2 : G^2\times G^2 \to G^2$ by $m^2(g_1,g_2,g_1',g_2') = (g_1g_1',g_2g_2')$. Also define $p^2_i : G^2\times G^2 \to G^2$ by $p^2_i(g_1,g_2,g_1,'g_2') = (g_i,g_i')$.
+%Set $G^2 = G\times G$. 
+Define $m^2 : G^2\times G^2 \to G^2$ by $m^2(g_1,g_2,g_1',g_2') = (g_1g_1',g_2g_2')$. Also define $p^2_i : G^2\times G^2 \to G^2$ by $p^2_i(g_1,g_2,g_1,'g_2') = (g_i,g_i')$.
 First we show that $m^*\cs{L}$ is an object in $\CS(G^2)$ by equipping it with an isomorphism $\mu_m^2: (m^2)^* (m^*\cs{L}) \to m^*\cs{L} \boxtimes m^*\cs{L}$ defined by the diagram below.
@@
 Suppose $(\cs{L},\mu,\beta)$ is an object in $\CSab(G)$.
-Then $\beta : \cs{L}_1\to \EE$ is an isomorphism in $\CS(1)$, which is unique by \cite{cunningham-roe:13a}*{Thm 3.9}.
+Then $\beta : \cs{L}_1\to \EE$ is an isomorphism in $\CS(1)$, which is unique by \cite{cunningham-roe:13a}*{Theorem 3.9}.
 Tracing through the construction of $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ from $\beta : \cs{L}_1\to \EE$, we find 
@@
 Theorem~\ref{thm:Gab} shows that $\CCS(G)$ is a categorical solution to the problem that linear character sheaves on $G$ need not be trivial on $G\der$, as discussed at the beginning of Section~\ref{sec:noncom}.
-At the same time, changing $\CS(G)$ to $\CCS(G)$ resolves the lack of bijectivity in \cite{cunningham-roe:13a}*{Thm.
-3.6}.
+At the same time, changing $\CS(G)$ to $\CCS(G)$ resolves the lack of bijectivity in \cite{cunningham-roe:13a}*{Theorem 3.6}.
 %
@@
 then \[\Aut_{\CCS(G)}(\cs{L},\mu,\beta) = \Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab).\] 
-By \cite{cunningham-roe:13a}*{Thm 3.9},  $\Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab) = \Hom(\pi_0(\bar{G}\ab)_{\Frob{}},\EEx)$.
+By \cite{cunningham-roe:13a}*{Theorem 3.9},  $\Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab) = \Hom(\pi_0(\bar{G}\ab)_{\Frob{}},\EEx)$.
 \end{proof}
@@
 
-There is a Weil sheaf complex $\cs{K}_\psi$ on $\Sp(V)\ltimes V^\sharp$ \cite{gurevich-hadani:07a}*{Thm 3.2.2.1} (see also \cite{gurevich-hadani:11a}*{Thm. 4.5}) such that 
+There is a Weil sheaf complex $\cs{K}_\psi$ on $\Sp(V)\ltimes V^\sharp$ \cite{gurevich-hadani:07a}*{Theorem 3.2.2.1} (see also \cite{gurevich-hadani:11a}*{Theorem 4.5}) such that 
 \begin{equation}

### 2017-05-10 Geometric types.tex
Wrapping up.

@@
 \ &  \arrow{dl}{n\circ b_1 = n\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
-b_1^* n^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
+b_1^* n^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* n^*\, \mathcal{L} \\
 & b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L} & 
@@
 It is easy to verify that morphisms that commute with $\mu$ and $\nu$ also commute with $\mu$ and $j^*(\nu)$.
+This functor is an equivalence. Its adjoint is given as follows.
 Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i\der(h),g)$.
@@
 \]
-Then $(\cs{L},\mu,\nu)\in \CS\der(G)$ maps to $(\cs{L},\mu,\beta)$.
-It now follows that $\CS\der(G) \to \CSab(G)$ is an equivalence. \todo{Should we add more detail to this proof?}
+This defines the functor  $\CS\ab(G) \to \CS\der(G)$, after confirming that morphisms that commute with $\mu$ and $\beta$ also commute with $\mu$ and $\nu$.
 \end{proof}

### 2017-05-10 letter to CJM.tex
Wrapping up.

\documentclass[fontsize=10pt, paper=a4]{scrlttr2}

% Dont forget to read the KOMA-Script documentation, scrguien.pdf

\setkomavar{fromname}{Clifton Cunningham and David Roe} % your name
%\setkomavar{fromaddress}{}

\setkomavar{signature}{CC \& DR} % printed after the \closing
\renewcommand{\raggedsignature}{\raggedright} % make the signature ragged right

\setkomavar{subject}{Regarding CJM: MS 1903 (Commutative character sheaves and geometric types for supercuspidal representations)} % subject of the letter

\begin{document}
\begin{letter}{To: Canadian Journal of Mathematics}

\opening{Dear Isolde Prince,}  % eg. Hello

\closing{Best regards} %eg. Regards

\end{letter}
\end{document}

### 2017-05-10 Geometric types.tex
Added "rational virtual Weil local systems", started work on notation conversion table, and letter to  CJM.

@@
 In this paper we show that if the geometric component group of the reductive quotient of the special fiber of the group scheme $\underline{G}^0$ is cyclic, then each representation $\orho_i$ in this sequence can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$,
-where $\cs{F}^i$ is a virtual Weil sheaf on the Greenberg transform $G^i$ of $\underline{G}^i$.  
-Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(\OO{}) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the virtual complex $\cs{F}^i$, we show in Theorem~\ref{thm:geotypes} that
+where $\cs{F}^i$ is a {\it rational virtual Weil local system} on the Greenberg transform $G^i$ of $\underline{G}^i$, by which we mean an element in the group obtained  by tensoring the Grothendieck group of such local systems with $\QQ$.
+Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(\OO{}) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the rational virtual complex $\cs{F}^i$, we show in Theorem~\ref{thm:geotypes} that
 \begin{equation}\label{eqn:intro1}
@@
 \]
-%Theorem~\ref{thm:geotypes} shows how to construct the virtual Weil sheaf $\cs{F}^i$ from the Yu type datum, so that \eqref{eqn:intro1} holds.
+%Theorem~\ref{thm:geotypes} shows how to construct the rational virtual Weil sheaf $\cs{F}^i$ from the Yu type datum, so that \eqref{eqn:intro1} holds.
 We refer to the pair $(\underline{G}^d, \cs{F}^d)$ as a \emph{geometric type}.
@@
 These pieces are assembled in Section~\ref{ssec:geotypes}, where we prove Theorem~\ref{thm:geotypes}.
-With this theorem, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:
-virtual Weil perverse sheaves on group schemes over finite fields.
+With this theorem, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category: rational virtual Weil perverse sheaves on group schemes over finite fields.
 
@@
 % is given in Section~\ref{ssec:geotypes}. 
- %Specifically, we show that if $C$ is a compact $p$-adic group and $\rho$ is a representation of $C$ and $(C,\rho)$ is a type for a tamely ramified $p$-adic group then there is a  group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a virtual Weil sheaf $\mathcal{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
+ %Specifically, we show that if $C$ is a compact $p$-adic group and $\rho$ is a representation of $C$ and $(C,\rho)$ is a type for a tamely ramified $p$-adic group then there is a  group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a rational virtual Weil sheaf $\mathcal{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
 As preparation for the proof, we review some facts about the Heisenberg-Weil representation and its geometrization, in Section~\ref{ssec:Jacobi}.
@@
 \begin{spacing}{1.2}
-\begin{tabular}{| c|l |}
+\begin{tabular}{| c|l | l | }
 \hline
-\text{this paper} & \cite{yu:01a}\\
+\text{this paper} & \text{Yu, Jiu-Kang, {\it Construction of tame supercuspidal representations}} & \cite{yu:01a} \\
 \hline
-%$\oK^0$ & $\,^\circ K^0 = G^0(F)_y$\\% \cite{yu:01a}*{\S 15} \\
-%$\oK^{i+1}$ & $\,^\circ K^{i+1} = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, \ldots, s_{i})}$\\% \cite{yu:01a}*{\S 15} \\
-%$\oK^0$ & $\,^\circ K^0 = G^0(F)_y$\\% \cite{yu:01a}*{\S 15} \\
+%$\oK^0$ & $\,^\circ K^0 = G^0(F)_y$ & \cite{yu:01a}*{\S 15} \\
+%$\oK^{i+1}$ & $\,^\circ K^{i+1} = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, \ldots, s_{i})}$ & \cite{yu:01a}*{\S 15} \\
+%$\oK^0$ & $\,^\circ K^0 = G^0(F)_y$ & \cite{yu:01a}*{\S 15} \\
 %$\orho^0$ & $\,^\circ \rho^0$\\% \cite{yu:01a}*{\S 15} \\
-%$\orho^{i+1}$ & $\,^\circ \rho^{i+1}$\\% \cite{yu:01a}*{\S 15} \\
-$\varphi^i$ & $\phi_i\vert_{\,^\circ K^i }$ \\
-$J_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}$ \\
-$V_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ (G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}$ \\ 
-$V_{i+1}^\sharp$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi}_i\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
-%$H^{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi_i}\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
-$Z_{i+1}$ & $\ker(V_{i+1}^\sharp\to V_{i+1})$ \\ % \cite{yu:01a}*{\S 11} \\
+%$\orho^{i+1}$ & $\,^\circ \rho^{i+1}$ &  \cite{yu:01a}*{\S 15} \\
+$\varphi^i$ & $\phi_i\vert_{\,^\circ K^i }$ & \\
+$J_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}$ &  \\
+$V_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ (G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}$ & \\ 
+$V_{i+1}^\sharp$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi}_i\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ & \\
+%$H^{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi_i}\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ & \\
+$Z_{i+1}$ & $\ker(V_{i+1}^\sharp\to V_{i+1})$ & \cite{yu:01a}*{\S 11} \\
 %$(f_{j+1}, j_{i+1})$ & $(f,j)$ \cite{yu:01a}*{\S 11} \\
@@
 For $i=0, \ldots ,d$, let $G^i = \Gr_{R}(\underline{G}^i)$ be the Greenberg transform of the smooth group scheme $\underline{G}^i$ appearing in Section~\ref{ssec:review}.
-Then there is a virtual Weil sheaf complex $\cs{F}_i$ on $G^i$ such that $\trFrob{\cs{F}_i} = \trace(\orho_i)$, for $i=0, \ldots , d$.
+Then there is a rational virtual Weil sheaf complex $\cs{F}_i$ on $G^i$ such that $\trFrob{\cs{F}_i} = \trace(\orho_i)$, for $i=0, \ldots , d$.
 \end{theorem}
@@
 
-By \cite{lusztig:disconnected1}, there is a virtual Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
+By \cite{lusztig:disconnected1}, there is a rational virtual Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a rational virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
 \[
@@
 on $G_m^{i+1}(\Fq)$ for $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) \times \dim \orho^{i+1} $.
-Let $\cs{A}_m^{i+1}$ be the \emph{virtual} Weil sheaf on $G_m^i$ given by $\cs{A}_m^{i+1} = \frac{1}{n} \cs{C}_m^{i+1}$. 
+Let $\cs{A}_m^{i+1}$ be the \emph{rational virtual} Weil sheaf on $G_m^i$ given by $\cs{A}_m^{i+1} = \frac{1}{n} \cs{C}_m^{i+1}$. 
 %
@@
 Now set $\cs{F}^i_m = \cs{A}_m^{i} \otimes \cs{L}_m^i$, for $i=0, \ldots ,d$.
-Then $\cs{F}^i_m$ is a virtual Weil sheaf on $G^i_m = \Gr^{R}_m(\underline{G}^i)$ such that
+Then $\cs{F}^i_m$ is a rational virtual Weil sheaf on $G^i_m = \Gr^{R}_m(\underline{G}^i)$ such that
 \[
@@
 commutes.
-Let $\cs{F}^i$ be the virtual Weil sheaf on the group scheme $G^i= \Gr_{R}(\underline{G}^i)$ obtained by pulling back $\cs{F}_m^i$ along $G^i \to G^i_m$.
+Let $\cs{F}^i$ be the rational virtual Weil sheaf on the group scheme $G^i= \Gr_{R}(\underline{G}^i)$ obtained by pulling back $\cs{F}_m^i$ along $G^i \to G^i_m$.
 Then 

### 2017-05-10 CJM/letter to CJM.tex
Made directory/folder CJM

--- 2017-05-10 Geometric types.tex
@@
-\documentclass[10pt]{amsart}
-
-\title[Commutative character sheaves and geometric types]{Commutative character sheaves and geometric types for supercuspidal representations}
-\author{Clifton Cunningham}
-\address{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive Northwest, Calgary, Alberta, Canada, {T2N~1N4}.}
-\email{cunningham@pims.math.ca}
-\author{David Roe}
-\address{Department of Mathematics, University of Pittsburgh, 301 Thackeray Hall, Pittsburgh, PA , United States, 15260.}
-\email{roed.math@gmail.com}
-
-\subjclass[2010]{14F05 (primary), 14L15, 22E50}
-\keywords{function-sheaf dictionary, commutative character sheaves, types for supercuspidal representations}
+% !TEX encoding = UTF-8 Unicode
+\documentclass[letter,10pt]{amsart}
+%\usepackage[british]{babel}
+%\usepackage{datetime}
+%\usepackage[latin1]{inputenc}
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+%\usepackage{geometry}
+\renewcommand{\baselinestretch}{1.2}
+%\bibstyle{alphanumeric}
+%\bibliographystyle{amsalpha}
 
@@
 
-%% Hyphenation override
-\hyphenation{quasi-character}
-%% Number one equation of many
-\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
+\begin{document}
+{\hfill {2017 May 11} \\ 
+%\rightline{Calgary}
+}
 
-%%%%%%%%%%%% BEGIN DOCUMENT %%%%%%%%%%%
-\usepackage{todonotes}
+\setcounter{equation}{-1}
 
-\begin{document}
+\noindent{Dear Isolde Prince,}
+\medskip
 
-\begin{abstract}
-We show that the types for supercuspidal representations of tamely ramified $p$-adic groups that appear in Jiu-Kang Yu's work are geometrizable, subject to a mild hypothesis.
-To do this we must find the function-sheaf dictionary for one-dimen\-sion\-al characters of arbitrary smooth group schemes over finite fields.  
-In previous work we considered the case of commutative smooth group schemes and found that the standard definition of character sheaves produced a dictionary with a nontrivial kernel.  
-In this paper we give a modification of the category of character sheaves that remedies this defect, and is also extensible to non-commutative groups.  
-We then use these \emph{commutative character sheaves} to geometrize the linear characters that appear in the types introduced by Jiu-Kang Yu.
-We combine these sheaves with Lusztig's character sheaves on reductive algebraic groups over finite fields and the geometrization of the Weil representation found by Gurevich and Hadani, to define \emph{geometric types} for supercuspidal representations of tamely ramified $p$-adic groups.
-\end{abstract}
+{Regarding CJM: MS 1903 (Commutative character sheaves and geometric types for supercuspidal representations)} % subject of the letter
 
-\maketitle
-
-\tableofcontents
-
-\section*{Introduction}
-
-As proved by Ju-Lee Kim in \cite{kim:07a}, all irreducible supercuspidal representations of tamely ramified $p$-adic groups can be built from ``data'' introduced by Jiu-Kang Yu in \cite{yu:01a}*{\S 15}.
-While the type, in the sense of Bushnell \& Kutzko \cite{bushnell-kutzko:98a}, of a supercuspidal representation built from Yu data can be constructed directly from the datum, it is convenient to consider an intermediate object, introduced in \cite{yu:01a}*{Remark 15.4}, which we call a \emph{Yu type datum}.
-Yu type data are studied in \cite{Yu:models}, which concludes with the following observation.
-%
-\begin{quotation}
-{\it Therefore, up to some linear characters, all the ingredient representations 
-%[appearing in Yu type data]
- are on groups of the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
-These results suggest that algebraic geometry and group schemes should play an
-important role in the representation theory of $p$-adic groups.} %\cite{Yu:models}
-\end{quotation}
-%
-In this paper we follow the suggestion above by showing that Yu type data are geometrizable, in the following sense.
-A Yu type datum determines a sequence of representations $\orho_i$ of compact $p$-adic groups $\oK^i$, for $i=0, \ldots, d$, such that $(\oK^d, \rho_d)$ is a type for a supercuspidal representation of a $p$-adic group.
-The main result of \cite{Yu:models} explains how to find, for each $i=0, \ldots, d$, a smooth group scheme $\underline{G}^i$ over the ring $\O$ of integers of the $p$-adic field with $\underline{G}^i(\O)=\,^\circ K^i $.
-In this paper we show that if the geometric component group of the reductive quotient of the special fiber of the group scheme $\underline{G}^0$ is cyclic, then each representation $\orho_i$ in this sequence can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$,
-where $\cs{F}^i$ is a virtual Weil sheaf on the Greenberg transform $G^i$ of $\underline{G}^i$.  
-Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(\OO{}) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the virtual complex $\cs{F}^i$, we show in Theorem~\ref{thm:geotypes} that
-\begin{equation}\label{eqn:intro1}
-\trFrob{\cs{F}^i} = \trace(\,^\circ\rho_i).
-\end{equation}
-By this theorem, then, we obtain geometric avatars for each type in a Yu datum:
-\[
-\begin{tikzcd}
-(\oK^i,\orho_i) \arrow[bend left, dashed]{rrr}{\text{geometrization}} &&& \arrow[bend left, dashed]{lll}{\text{trace of Frob}}
-(\underline{G}^i, \cs{F}^i).
-\end{tikzcd}
-\]
-%Theorem~\ref{thm:geotypes} shows how to construct the virtual Weil sheaf $\cs{F}^i$ from the Yu type datum, so that \eqref{eqn:intro1} holds.
-We refer to the pair $(\underline{G}^d, \cs{F}^d)$ as a \emph{geometric type}.
-
-To prove Theorem~\ref{thm:geotypes}, we must find a way to geometrize linear characters of groups of the form $\underline{H}(\O)$, where $\underline{H}$ is a smooth group scheme over $\O$. 
-In order to do so in a systematic manner, we begin this paper by describing the function-sheaf dictionary for characters of arbitrary smooth group schemes over finite fields. 
-When coupled with the Greenberg transform, this dictionary will allow for the geometrization of linear characters of $\underline{H}(\O)$.
-
-The function-sheaf dictionary over a finite field $k$ \cite{deligne:SGA4.5}*{Sommes trig.}
-provides a way of encoding functions on the $k$-rational points of an algebraic group $G$
-as $\ell$-adic local systems on $G$.  More specifically, if $G$ is a connected, commutative, algebraic group
-then there is a certain category $\CS(G)$ of rank-one local systems on $G$ and an
-explicit isomorphism between isomorphism classes
-of objects in $\CS(G)$ and $G(k)^* \ceq \Hom(G(k), \EEx)$; 
-%Objects in $\CS(G)$ are referred to as \emph{character sheaves}.
-the isomorphism is given by mapping $\cs{L}$ to the function
-$\TrFrob{G} : g \mapsto \Tr(\Frob{} \vert \cs{L}_g)$.
-
-In previous work \cite{cunningham-roe:13a}, we generalized the function-sheaf dictionary to
-smooth commutative group schemes $G$, allowing for non-connected groups.
-We gave a description of the category $\CS(G)$ in this context, as well
-as an epimorphism $\TrFrob{G} : \CSiso{G} \to G(k)^*$.
-In contrast to the connected case, $\TrFrob{G}$ may have nontrivial kernel;
-we gave an explicit description of its kernel as $\Hh^2(\pi_0(\bG), \EEx)^{\Frob{}}$ \cite{cunningham-roe:13a}*{Theorem 3.6}.
-
-We repair this defect in the function-sheaf dictionary
- by describing a full subcategory $\CCS(G)$ of $\CS(G)$ so that $\TrFrob{G}$ restricts to an isomorphism $\CCSiso{G} \to G(k)^*$.
-We refer to objects of $\CS(G)$ as character sheaves and objects in $\CCS(G)$ as \emph{commutative character sheaves}, since the passage from $\CS(G)$ to $\CCS(G)$ involves a condition that exchanges the inputs to the multiplication morphism on $G$ (see Definition \ref{def:CCScom}).
-When $G$ is connected, all character sheaves on $G$ are commutative.
-
-Category $\CCS(G)$ clarifies several questions about $\CS(G)$. 
-Invisible character sheaves \cite{cunningham-roe:13a}*{Def.
-2.8} are precisely those $\cs{L}$ with $\TrFrob{G}(\cs{L}) = 1$ that are not commutative.
-Moreover, $\TrFrob{G}^{-1} : G(k)^* \to \CCSiso{G}$ provides a canonical splitting of $\TrFrob{G} : \CSiso{G} \to G(k)^*$ \cite{cunningham-roe:13a}*{Rem.
-3.7}.
-
-Next, we broaden our scope further to encompass smooth group schemes $G$ over $\Fq$ that are not necessarily commutative.
-We assume $G$ is smooth, but not that it is connected, reductive or commutative. 
-The category $\CS(G)$ has a straightforward generalization to this case, but again
-there are more character sheaves than there are characters, as pointed out by Kamgarpour \cite{kamgarpour:09a}*{(1.1)}.
-We then define category $\CCS(G)$ for such $G$ and a forgetful functor to $\CS(G)$ so that $\TrFrob{G} : \CCSiso{G} \to G\ab(k)^*$
-is an isomorphism.  
-Since $G\ab(k)^*$ surjects onto $G(k)^*$, it follows that for each character $\chi \in G(k)^*$ there is a commutative
-character sheaf $\cs{L}$ on $G$ with $\TrFrob{G}(\cs{L}) = \chi$. Moreover, we find that pullback along the quotient $q : G \to G\ab$
-defines an equivalence of categories $\CCS(G\ab) \to \CCS(G)$.  
-The functor $\CCS(G) \to \CS(G)$ is not
-essentially surjective, missing the kinds of linear character sheaves highlighted by Kamgarpour.
-%
-
-In order to provide further justification for referring to objects in $\CCS(G)$ as commutative character sheaves, suppose for the moment that $G$ is a connected, reductive algebraic group over $\Fq$.
-Let $\gcs{L}$ be the geometric part of an object in $\CCS(G)$; see Section~\ref{sec:defs}.
-Let $T$ be a maximal torus in $\bG$ and let $\gcs{L}_T$ be the restriction of $\gcs{L}$ to $T$.
-Then the perverse sheaf $\gcs{L}[\dim G]$ appears in the semisimple complex $\operatorname{ind}_{B,T}^{\bG}(\gcs{L}_T)$ produced by parabolic induction.
-It follows that every object in $\CCS(G)$ determines a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}.
-Of course, the sheaves arising in this way represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields:
-they are precisely those needed to describe one-dimensional characters of such groups.
-
-Armed with the function-sheaf dictionary for smooth group schemes over finite fields, we return to the task of geometrizing Yu type data. 
-The proof of Theorem~\ref{thm:geotypes} requires: Yu's work on smooth integral models \cite{Yu:models}; the geometrization of the character of the Heisenberg-Weil representation over finite fields by Gurevich \& Hadani \cite{gurevich-hadani:07a}; Lusztig's character sheaves on reductive groups over finite fields; and finally, the function-sheaf dictionary for characters of smooth group schemes over finite fields, now at our disposal in Theorem~\ref{thm:geo}.
-These pieces are assembled in Section~\ref{ssec:geotypes}, where we prove Theorem~\ref{thm:geotypes}.
-With this theorem, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category:
-virtual Weil perverse sheaves on group schemes over finite fields.
-
-The hypothesis in Theorem~\ref{thm:geotypes} -- that the geometric component group of the reductive quotient of the special fibre of the smooth group scheme $\underline{G}^0$ appearing in the Yu type datum is cyclic --  is required only because Lusztig's theory of character sheaves has the same hypothesis.
-If Lusztig's theory of character sheaves can be generalized to all disconnected reductive algebraic groups, then the hypothesis in Theorem~\ref{thm:geotypes} can be removed.
-\bigskip
-
-We now summarize the sections of the paper in more detail.
-%
-In Section \ref{sec:defs}, we recall the category $\CS(G)$ from \cite{cunningham-roe:13a} and note that it still makes sense when $G$ is not commutative.  
-%
-We focus on the case of commutative $G$ in Section \ref{sec:comcom},
-giving the definition of a commutative character sheaf and proving our first main theorem, that
-$\TrFrob{G} : \CSiso{G} \to G(k)^*$ induces an isomorphism on $\CCSiso{G}$.
-%
-Passing to the case that $G$ is non-commutative, we give the definition of and main results about commutative character sheaves in Section \ref{sec:noncom}.  
-We note that we should only consider character sheaves that arise via pullback from $G\ab$ in order to eliminate those that have nontrivial restriction to the derived subgroup.  
-This observation underlies the definition of commutative character sheaves for non-commutative $G$.  
-We state our second main result, Theorem~\ref{thm:geo}, that pullback along the abelianization map defines an equivalence of categories $\CCS(G) \to \CCS(G\ab)$.
-In Section \ref{ssec:obmor}, we use Galois cohomology to describe the relationship between $G(k)^*$ and $G\ab(k)^*$.  
-We also compute the automorphism groups in $\CCS(G)$.
-%Then in Section \ref{ssec:proofs}, we give proofs of the results in Section \ref{sec:noncom}, which require a development of equivariant linear character sheaves. \todo{Fix this.}
-% 
-In Section~\ref{sec:types} we use Theorem~\ref{thm:geo} to geometrize types for supercuspidal representations of $p$-adic groups, in a sense made precise in Theorem~\ref{thm:geotypes}. 
-% is given in Section~\ref{ssec:geotypes}. 
- %Specifically, we show that if $C$ is a compact $p$-adic group and $\rho$ is a representation of $C$ and $(C,\rho)$ is a type for a tamely ramified $p$-adic group then there is a  group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a virtual Weil sheaf $\mathcal{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
-As preparation for the proof, we review some facts about the Heisenberg-Weil representation and its geometrization, in Section~\ref{ssec:Jacobi}.
-Then, in Section~\ref{ssec:review}, we review Yu's theory of types and his study of smooth integral models.  
-These elements are pulled together in Section~\ref{ssec:geotypes}, where the proof Theorem~\ref{thm:geotypes} is given.
-
-\bigskip
-
-We are extremely grateful to Loren Spice for explaining Yu's types for supercuspidal representations.
-We also thank Masoud Kamgarpour for helpful conversations.
-
-\section{Recollections and definitions} \label{sec:defs}
-
-Let $G$ be a smooth group scheme over a finite field $\Fq$; that is, let $G$ be a group scheme over $\Fq$
-for which the structure morphism $G \to \Spec{\Fq}$ is smooth in the sense of \cite{EGAIV4}*{Def 17.3.1}.
-This implies $G \to \Spec{\Fq}$ is locally of finite type, but not that it is of finite type.
-We remark that the identity component $G^0$ of $G$ is of finite type over $\Fq$, while the component group scheme
-$\pi_0(G)$ of $G$ is an \'etale group scheme over $\Fq$, and both are smooth over $\Fq$.
-
-In this paper we use a common formalism for Weil sheaves, writing $\cs{L}$ for the pair $(\gcs{L},\phi)$, where $\gcs{L}$ is an $\ell$-adic sheaf on $\bG \ceq G\otimes_{\Fq} \bFq$ and where $\phi : \Frob{}^*\gcs{L} \to \gcs{L}$ is an isomorphism of $\ell$-adic sheaves.
-We also follow convention by referring to $\cs{L}$  as a Weil sheaf on $G$. 
-If $\cs{L}$ and $\cs{L}' \ceq (\gcs{L}', \phi')$ are Weil sheaves, we write $\alpha : \cs{L} \to \cs{L}'$ for a morphism $\alpha : \gcs{L} \to \gcs{L}$ such that 
-\[
-\begin{tikzcd}
-\Frob{}^* \gcs{L} \arrow{d}[swap]{\phi} \arrow{r}{\Frob{}^*\alpha} &  \Frob{}^* \gcs{L} \arrow{d}{\phi'}\\
-\gcs{L} \arrow{r}{\alpha} & \gcs{L}
-\end{tikzcd}
-\]
-commutes.  While these conventions simplify notation considerably, they are not consistent with \cite{cunningham-roe:13a}.
-
-We write $m : G \times G \to G$ for the multiplication morphism, and $G(k)^*$ for $\Hom(G(k), \EEx)$.
-Define $\theta : G\times G \to G\times G$ by $\theta(g,h) = (h,g)$.
-
-When $G$ is commutative, a \emph{character sheaf} on $G$ is a triple $(\gcs{L}, \mu, \phi)$,
-where $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, 
-$\mu : \bm^* \gcs{L} \to \LxL$ is an isomorphism
-of sheaves on $\bG \times \bG$, 
-and $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an isomorphism of sheaves on $\bG$;
-the triple $(\gcs{L}, \mu, \phi)$ is required to satisfy certain conditions \cite{cunningham-roe:13a}*{Def. 1.1}.
-Write $\CS(G)$ for the category of character sheaves on $G$.
-
-Even when $G$ is not commutative, the category $\CS(G)$, defined as in \cite{cunningham-roe:13a}*{Def. 1.1},
-still makes sense.  In order to distinguish the resulting objects from
-the character sheaves of Lusztig, we will refer to the former as \emph{linear character sheaves}
-(to evoke the one-dimensional character sheaves of \cite{kamgarpour:09a}).
-
-\section{Commutative character sheaves on commutative groups}\label{sec:comcom}
-
-We consider first the case that $G$ is commutative, which we will later apply to the case of general smooth $G$.
-Let $\cs{L}$ be a character sheaf on $G$.  Since $m = m \circ \theta$ in this case,
-there is a canonical isomorphism $\xi : m^* \cs{L} \to \theta^* m^* \cs{L}$.
-There is also an isomorphism $\vartheta : \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes\cs{L})$
-given on stalks by the canonical map $\gcs{L}_{g} \otimes \gcs{L}_{h} \to \gcs{L}_{h} \otimes \gcs{L}_{g}$.
-
-\begin{definition}\label{def:CCScom}
-A character sheaf $(\cs{L}, \mu)$ on a smooth commutative group scheme $G$ is \emph{commutative}
-if the following diagram of Weil sheaves on $G \times G$ commutes.
-  \[
-  \begin{tikzcd}[row sep=30]
-   m^*\cs{L} \arrow{d}[swap]{\xi}{m= m\circ\theta} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
-   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L})
-  \end{tikzcd}
-  \]
-We write $\CCS(G)$ for the full subcategory of $\CS(G)$ consisting of commutative character sheaves.
- \end{definition}
-
-In \cite{cunningham-roe:13a}*{Theorem 3.6}, we showed that $\TrFrob{G} : \CSiso{G} \to G(k)^*$ is surjective and
-explicitly computed its kernel.  In this section, we show that the corresponding map
-$\TrFrob{G} : \CCSiso{G} \to G(k)^*$ for commutative character sheaves is an isomorphism.
-We begin by reinterpreting Definition \ref{def:CCScom} in terms of cocycles.
-
-Let $G$ be a commutative \'etale group scheme over $k$. For a character sheaf $\cs{L}$ on $G$, recall
-\cite{cunningham-roe:13a}*{\S 2.3} that $S_G : \CSiso{G} \to \Hh^2(E_G^\bullet)$ is an isomorphism mapping
-$[\cs{L}]$ to $[\alpha \oplus \beta]$, where $E_G^\bullet$ is the total space of the zeroth page
-of the Hochschild-Serre spectral sequence, $\alpha \in \oK^0(\Weil{}, \oK^2(\bG, \EEx))$ is obtained from $\mu$ and
-$\beta \in \oK^1(\Weil{}, \oK^1(\bG, \EEx))$ is obtained from $\phi$.
-
-Let $a \in Z^2(\bG, \EEx)$ correspond to $\alpha$.  We say that $[\alpha \oplus \beta] \in \Hh^2(E_G^\bullet)$
-is \emph{symmetric} if $a(x,y) = a(y,x)$ for all $x,y \in \bG$.  This condition is well defined, since every
-coboundary in $B^2(\bG, \EEx)$ is symmetric.  The connection between commutative character sheaves
-and symmetric classes is given in the following lemma.
-
-\begin{lemma} \label{lem:symccslink}
-Suppose $G$ is a smooth commutative group scheme, and let $\cs{L}$ be a character sheaf on $G$.
-Then $\cs{L}$ is commutative if and only if $S_G(\cs{L})$ is symmetric.
-\end{lemma}
-\begin{proof}
-The symmetry of $S_G(\cs{L})$ is a direct consequence of the commutativity of the diagram in Definition \ref{def:CCScom}
-after choosing bases for each stalk.
-\end{proof}
-
-We may similarly define a symmetric class in $\Hh^2(\bG, \EEx)$ to be one represented by a symmetric $2$-cocycle.
-The following lemma will allow us to show that there are no invisible commutative character sheaves.
-
-\begin{lemma} \label{lem:symtriv}
-Let $\bG$ be a commutative group.  Then the only symmetric class in $\Hh^2(\bG, \EEx)$ is the trivial class.
-\end{lemma}
-
-\begin{proof}
-By the universal coefficient theorem,
-\[
-0 \to \Ext^1_\ZZ(\Hh_{n-1}(\bG, \ZZ), \EEx) \to \Hh^n(\bG, \EEx) \to \Hom(\Hh_n(\bG, \ZZ), \EEx) \to 0
-\]
-is exact for all $n > 0$.  When $n = 2$, using the fact that $\bG$ is commutative, we have that $\Hh_1(\bG, \ZZ) \cong \bG$
-and that $\Hh_2(\bG, \ZZ) \cong \wedge^2 \bG$. We get
-\[
-0 \to \Ext^1_\ZZ(\bG, \EEx) \to \Hh^2(\bG, \EEx) \to \Hom(\wedge^2 \bG, \EEx) \to 0.
-\]
-The map $\Hh^2(\bG, \EEx) \to \Hom(\wedge^2 \bG, \EEx)$ maps a $2$-cocycle $f$ to the alternating function
-\[
-(x,y) \mapsto \frac{f(x,y)}{f(y,x)}.
-\]
-Thus the cohomology classes represented by symmetric cocycles are precisely those in the image of $\Ext^1_\ZZ(\bG, \EEx)$.
-But $\Ext^1_\ZZ(-, \EEx)$ vanishes because $\EEx$ is divisible.
-\end{proof}
-
-\begin{lemma} \label{lem:conncomm}
-If $G$ is a connected commutative algebraic group over $\Fq$ then every character sheaf on $G$ is commutative.
-\end{lemma}
-
-\begin{proof}
-Suppose $S_G(\cs{L}) = [\alpha\oplus \beta]\in \Hh^2(E_G^\bullet)$.
-We can use \'etale descent to see that pullback by the Lang isogeny defines an equivalence
-of categories between local systems on $G$ and $G(\Fq)$-equivariant local systems on $G$.  
-Thus every character sheaf $\cs{L}$ on $G$ arises through the Lang isogeny, together with a character $G(\Fq) \to \EEx$.
-Pushing forward the Lang isogeny along this character defines an extension of $\bG$ by $\EEx$ whose class is fixed by Frobenius; let $a\in Z^2(\bG, \EEx)$ be a representative $2$-cocycle.
-Then $a$ corresponds to the $\alpha \in \oK^0(\Weil{}, \oK^2(\bG, \EEx))$, above. 
-Since the covering group of the Lang isogeny is $G(k)$, which is commutative, the class of this extension satisfies $a(x,y) = a(y,x)$ for all $x,y \in \bG$. 
-This shows that $S_{G}(\cs{L})$ is symmetric.
-It follows from Lemma~\ref{lem:symccslink} that $\cs{L}$ is a commutative character sheaf.
-\end{proof}
-
-\begin{theorem} \label{thm:trfrobiso}
-If $G$ is a smooth commutative group scheme over $\Fq$ then $\TrFrob{G} : \CCSiso{G} \to G(\Fq)^*$ is an isomorphism.
-\end{theorem}
-
-\begin{proof}
-Suppose first that $G$ is \'etale.  Consider the isomorphism of short exact sequences
-\[
-\begin{tikzcd}
- 0 \arrow{r} & \ker \TrFrob{G} \arrow{d} \arrow{r} & \CSiso{G}\arrow{d}{S_G} \arrow{r}{\TrFrob{G}} \arrow{r} & G(\Fq)^* \arrow{d} \arrow{r} & 0\\
-  0 \arrow{r} & \Hh^0(\Weil{},\Hh^2(\bG,\EEx)) \arrow{r} & \Hh^2(E^\bullet_G) \arrow{r} & \Hh^1(\Weil{},\Hh^1(\bG,\EEx)) \arrow{r} & 0
- \end{tikzcd}
- \]
-from \cite{cunningham-roe:13a}*{Prop. 2.7}.
-
-Suppose that $\cs{L}$ is a commutative character sheaf with $\trFrob{\cs{L}} = 1$, and set $[\alpha, \beta] = S_G([\cs{L}])$.
-Then $S_G([\cs{L}])$ is in the image of $\Hh^2(\bG, \EEx)^\Weil{}$, so is cohomologous to
-$[\alpha', 0]$.  Since $\alpha$ is symmetric and coboundaries are symmetric, $\alpha'$ is symmetric as well.
-So by Lemma \ref{lem:symtriv}, $\alpha'$ is cohomologically trivial, and thus $[\cs{L}]$ is trivial as well.
-
-To see that $\TrFrob{G}$ is still surjective on $\CCSiso{G}$, note that the character sheaf constructed in the proof of
-\cite{cunningham-roe:13a}*{Prop. 2.6} has trivial $\alpha$, and is thus commutative.
-
-For general smooth commutative group schemes, we use Lemma \ref{lem:conncomm} and the snake lemma, as in the proof of
-\cite{cunningham-roe:13a}*{Theorem 3.6}
-\end{proof}
-
-\begin{remark}
-Since $\Hh^0(\Weil{},\Hh^2(\bG,\EEx))$ is not necessarily trivial \cite{cunningham-roe:13a}*{Ex. 2.10}, the functor
-$\CCS(G) \to \CS(G)$ is not necessarily essentially surjective.  Indeed, the invisible character sheaves \cite{cunningham-roe:13a}*{Def. 2.8}
-defined in our previous paper are precisely those non-commutative character sheaves with trivial trace of Frobenius.
-\end{remark}
-
-\section{Commutative character sheaves on non-commutative groups}\label{sec:noncom}
-
-We now consider the case of a smooth group scheme without the commutativity assumption.  We start
-by relating character sheaves on $G$ to character sheaves on its abelianization.
-
-If $\chi \in G(k)^*$ is a character, it must vanish on the derived subgroup $G\der(k)$.
-Kamgarpour gives an example \cite{kamgarpour:09a}*{(1.1)} of a character sheaf
-that does not vanish on $G\der$, defined by the extension
-\[
-1 \to \mu_n \to \SL_n \to \PGL_n \to 1.
-\]
-In order to obtain a relationship between character sheaves on $G$ and characters of $G(k)$,
-he opts to give a different definition of commutator and, in doing so, introduces a `stacky abelianization' of $G$ in order to geometrize characters of $G(\Fq)$.
- Since we have already seen the need to adapt the
-notion of character sheaf, even in the commutative case, we instead add restrictions
-to the definition of commutative character sheaf and leave the definition of $G\der$ unchanged, allowing us to use the schematic abelianization of $G$ in the geometrization of characters of $G(\Fq)$; see Theorem~\ref{thm:geo}.
-
-\subsection{Main definition}\label{ssec:noncomdef}
-
-In order to get character sheaves that correspond to characters in $G(k)^*$, we must discard those
-character sheaves whose restriction to the derived subgroup is nontrivial.  Moreover, the isomorphism
-with the trivial sheaf on the derived subgroup will be important in relating to sheaves on the abelianization,
-motivating the following category.
-%
-Recall from Section~\ref{sec:defs} that we refer to objects in category $\CS(G)$, defined as
-in \cite{cunningham-roe:13a}*{Def. 1.1}, as linear character sheaves when $G$ is smooth but
-not necessarily commutative.
-
-\begin{definition}\label{def:CSab}
-Let $\CSab(G)$ denote the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu) \in \CS(G)$ and
-$\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism in $\CS(G\der)$.
-A morphism $(\cs{L},\mu,\beta)\to (\cs{L}',\mu',\beta')$ is a morphism $\alpha : (\cs{L},\mu)\to (\cs{L}',\mu')$
-in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{G\der}$.  
-\end{definition}
-
-%
-We will define commutative character sheaves as a subcategory of $\CSab(G)$.
-%We may now define commutative character sheaves on $G$.
-%
-Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows.
-Let $i : G \to G$ be inversion and $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
-Both are smooth morphisms of $\Fq$-schemes.
-Set $m' = i \circ m \circ \theta$ and let $j\der : G\der\to G$ be inclusion; then $j\der\circ c = m \circ (m \times m')$.
-% \todo{$j$ is not defined, and the needed definition conflicts with the definition of $i$ and $j$ given later.}
-Then $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms below.
-\begin{equation}
-\begin{tikzcd}
-\arrow[equal]{d} c^* (\cs{L}\vert_{G\der}) \arrow{r}{c^*(\beta)} 
-	&  c^*((\EE)_{G\der}) \arrow[equal]{d} \\
-\arrow{d}[swap]{j\der\circ c = m \circ (m \times m')} c^* j\der^* \cs{L} 
-	&   (\EE)_{G\times G} \\
-(m \times m')^* m^* \cs{L} \arrow{d}[swap]{(m \times m')^*(\mu)} 
-	&  m^*\cs{L} \otimes \theta^* m^* i^* \cs{L}  \arrow[dashed]{u}[swap]{\gamma'} \\
-(m \times m')^* (\cs{L} \boxtimes \cs{L}) \arrow[equal]{r} 
-	& m^*\cs{L} \otimes (m')^*\cs{L} \arrow{u}[swap]{m' = i\circ m\circ \theta} 
-\end{tikzcd}
-\end{equation}
-In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations; so, for example, the middle left isomorphism comes from $(m\times m')^* m^* \iso c^* j\der^*$ since $j\der\circ c = m \circ (m \times m')$.
-Using the monoidal structure of the category of Weil local systems on $G\times G$, the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ defines an isomorphism
-\[
-m^*\cs{L} \to (\theta^* m^* i^*\cs{L})^\vee.
-\]
-Applying the canonical isomorphisms $(\theta^* m^* i^*\cs{L})^\vee \iso \theta^* m^* i^* (\cs{L}^\vee)$ and $i^*(\cs{L}^\vee) \cong \cs{L}$, this map provides the promised isomorphism
-\[
-\begin{tikzcd}
-\gamma : m^*\cs{L} \arrow{r} & \theta^* m^* \cs{L}.
-\end{tikzcd}
-\]
-
-\begin{definition}\label{def:CCS}
-The category $\CCS(G)$ of commutative character sheaves on $G$ is the full subcategory of $\CSab(G)$ consisting of triples $(\cs{L},\mu,\beta)$ such that the following diagram of Weil sheaves on $G \times G$ commutes:
-  \[
-  \begin{tikzcd}[row sep=30]
-   m^*\cs{L} \arrow{d}[swap]{\gamma} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
-   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L}).
-  \end{tikzcd}
-  \]
-Here $\gamma : m^*\cs{L} \to \theta^* m^* \cs{L}$ is the isomorphism built from $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ as above. 
-\end{definition}
-
-\subsection{Descent}
-
-In this section we give an equivalence of categories between $\CS(G\ab)$ and $\CSab(G)$ and use it to describe
-the pullback functor $q^* : \CS(G\ab) \to \CS(G)$ in terms of the forgetful functor $\CSab(G) \to \CS(G)$.
-But first, in order to study commutative character sheaves, we need some auxiliary categories.
-
-\subsubsection{Equivariant Weil local systems}\label{ssec:equivariant1}
-
-Let $\Loc(G)$ and $\Loc(G\ab)$ be the categories of Weil local systems on $G$ and $G\ab$, respectively.
-%
-Let $\Loc\der(G)$ be the category of $G\der$-equivariant Weil local systems on $G$, whose definition we now recall.
-Let $n : G\der\times G\to G$ be the restriction of $m : G\times G\to G$ to $G\der\times G$,
-let $p : G\der\times G \to G$ be projection to the second component, and let $s: G \to G\der\times G$ be given by $s(g) = (1,g)$.
-Then the quotient $q : G \to G\ab$ is a regular epimorphism of smooth group schemes with kernel pair $(n,p)$.
-\[
-\begin{tikzcd}
-G\der\times G
- \arrow[shift left=1]{r}{n}
-  \arrow[shift right=1,swap]{r}{p}
-&
-G 
-\arrow{r}{q}
-& 
-G\ab
-\end{tikzcd}
-\]
-Consider the morphisms
-\[
-\begin{tikzcd}
-G\der \times G\der \times G 
-\arrow[shift left=2]{r}{b_1, b_2, b_3} 
-\arrow{r}{}
-\arrow[shift right=2]{r}{} 
-& G\der \times G 
-\arrow[shift left=1]{r}{n}
-\arrow[shift right=1]{r}[swap]{p}
- & G 
-\end{tikzcd}
-\]
-defined by 
-\begin{align*}
-b_1(h_1,h_2,g) &= (h_1h_2,g) \\
-b_2(h_1,h_2,g) &= (h_1,h_2g) \\
-b_3(h_1,h_2,g) &= (h_2,g).
-\end{align*}
-Note that
-\begin{align*}
-n\circ b_1 &= n\circ b_2 \\
-n\circ b_3 &= p\circ b_2 \numberthis \label{eqn:bap}\\
-p\circ b_1 &= p\circ b_3.
-\end{align*}
-Define $s : G\to G\der\times G$ by $s(g) = (1,g)$.
-A $G\der$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
-\[
-\nu : n^*\cs{L} \to p^*\cs{L}
-\] 
-of Weil local systems on $G\der\times G$ such that 
-\begin{equation}\label{E1}
-s^*(\nu) = \id_{\cs{L}}
-\end{equation}
-and such that the following diagram of isomorphisms of local systems on $G\der\times G\der\times G$ commutes. 
-\begin{equation}\label{E2}
-\begin{tikzcd}
-\ &  \arrow{dl}{n\circ b_1 = n\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
-b_1^* n^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
-& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L} & 
-\end{tikzcd}
-\end{equation}
-%In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from equations \eqref{eqn:bap}; so, for example, the top left isomorphism comes from $b_1^* n^* \iso b_2^* n^*$ since $n\circ b_1 = n\circ b_2$.
-%On stalks, this condition is ...
-%\[
-%\begin{tikzcd}
-%\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
-%\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
-%& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
-%\end{tikzcd}
-%\]
-Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
-\begin{equation}\label{E3}
-\begin{tikzcd}
-\arrow{d}[swap]{\nu} n^*\cs{L} \arrow{r}{n^*(\alpha)} & n^*\cs{L}' \arrow{d}{\nu'} \\
-p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
-\end{tikzcd}
-\end{equation}
-commutes.
-This defines $\Loc\der(G)$, the category of $G\der$-equivariant Weil local systems on $G$.
-The reader will recognize this notion as the Weil local system version of equivariant sheaves for the action $n$ of $G\der$ on $G$, as can be found, for example, in \cite{bernstein-lunts:equivariant}*{0.2}.
-
-\subsubsection{Equivariant linear character sheaves}\label{ssec:equivariant2}
-
-With reference to Section~\ref{ssec:equivariant1}, we define a $G\der$-equivariant linear character sheaf on $G$ to be a triple $(\cs{L},\mu, \nu)$, where $(\cs{L},\mu)$ is a linear character sheaf and $(\cs{L},\nu)$ is an $G\der$-equivariant Weil local system.
-A morphism of $G\der$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $G\der$-equivariant Weil local systems $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves.
-%so
-%\begin{equation}\label{CS4}
-%\begin{tikzcd}
-%\arrow{d}[swap]{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
-%\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
-%\end{tikzcd}
-%\end{equation}
-%commutes; see also \cite{cunningham-roe:13a}, CS.4].
-%
-Let $\CS\der(G)$ be the category of $G\der$-equivariant linear character sheaves on $G$.
-
-%Is $\CS_H(G)$ a rigid monoidal category?
-
-%If $(\cs{L},\mu,\nu)$ and $(\cs{L},\mu,\nu')$ in $\CS_H(G)$, then $\nu = \nu'$?
-
-\begin{lemma}\label{lemma:nubeta}
-Categories $\CS\der(G)$ and $\CS\ab(G)$ are equivalent.
-\end{lemma}
-
-\begin{proof}
-Let $i\der : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\der\times G$ by $j(h) = (h,1_G)$. 
-If $(\cs{L},\mu,\nu)\in \CS\der(G)$ then $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism. 
-This defines a functor on objects by
-\[
-\begin{array}{rcl}
-\CS\der(G) &\to& \CSab(G) \\
-(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,j^*(\nu))
-\end{array}
-\]
-and on morphisms, trivially.
-It is easy to verify that morphisms that commute with $\mu$ and $\nu$ also commute with $\mu$ and $j^*(\nu)$.
-Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i\der(h),g)$.
-Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p^*\cs{L}$ by the following diagram.
-\[
-\begin{tikzcd}
-& n^* \cs{L} \arrow{dl}{m\circ k = n} \arrow{r}{\nu} & p^*\cs{L} &  \\ 
-k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
-& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id_\cs{L}}
-\end{tikzcd}
-\]
-Then $(\cs{L},\mu,\nu)\in \CS\der(G)$ maps to $(\cs{L},\mu,\beta)$.
-It now follows that $\CS\der(G) \to \CSab(G)$ is an equivalence. \todo{Should we add more detail to this proof?}
-\end{proof}
-
-Set $G^2 = G\times G$, so $G^2\der = G\der\times G\der$ and $G^2\ab = G\ab\times G\ab$.
-Likewise define $n^2 : G\der^2 \times G^2 \to G^2$ and $p^2 : G\der^2\times G \to G$.
-
-\begin{lemma}\label{lem:HH}
-If $(\cs{L},\mu,\nu)$ is a $G\der$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ 
-%and $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ 
-is a morphism of $G^2\der$-equivariant Weil local systems on $G^2$. 
-\end{lemma}
-
-\begin{proof} 
-Define
-\begin{align*}
-d : G\der\times G\der\times G\times G &\to G\der\times G\times G\der\times G \\
-(h_1,h_2,g_1,g_2) &\mapsto (h_1, g_1, h_2, g_2)\\
-n_2 : G\der\times G\times G\der\times G &\to G\times G \\
-(h_1,g_1,h_2,g_2) &\mapsto (h_1g_1, h_2g_2) \\
-p_2 : G\der\times G\times G\der\times G &\to G\times G \\
-(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2). %\\
-%\theta_2 : H \times G \times H \times G &\to H \times G \times H \times G \\
-%(h_1,g_1,h_2,g_2) &\mapsto (h_2,g_2,h_1,g_1).
-\end{align*}
-The following diagram defines the isomorphisms needed to see that both $m^*\cs{L}$ and $\cs{L}\boxtimes\cs{L}$ are $G\der^2$-equivariant Weil local systems.
-\[
-\begin{tikzcd}[column sep=40]
-\arrow{d}[swap]{n_2^*(\mu)} n_2^* (m^*\cs{L}) \arrow[dashed]{r} 
-	& \arrow{d}{p_2^*(\mu)} p_2^*(m^*\cs{L})\\
-\arrow{d}[swap]{n_2= n^2\circ d} n_2^*(\cs{L}\boxtimes\cs{L}) \arrow[dashed]{r} 
-	& \arrow{d}{p_2= p^2\circ d} p_2^*(\cs{L}\boxtimes\cs{L}) \\
-%d^* (n\times n)^* (\cs{L}\boxtimes\cs{L}) & d^* (p\times p)^* (\cs{L}\boxtimes\cs{L}) \\
-d^* (n^*\cs{L}\boxtimes n^*\cs{L}) \arrow{r}{d^*(\nu\boxtimes \nu)}& d^*(p^*\cs{L}\boxtimes p^*\cs{L}) 
-\end{tikzcd}
-\]
-The dashed arrows both satisfy \eqref{E1} and \eqref{E2} as they apply here.
-This diagram also shows that $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of equivariant sheaves, since it satisfies \eqref{E3} as it applies here.
-\end{proof}
-
-\subsubsection{Descent}
-
-If $\cs{L}\ab\in \Loc(G\ab)$ then $q^*\cs{L}\ab\in \Loc(G)$ comes equipped with a canonical isomorphism $\nu(\cs{L}\ab) : n^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of isomorphisms.
-\[
-\begin{tikzcd}[column sep=40]
-n^*\cs{L} \arrow[equal]{d} \arrow{r}{\nu(\cs{L}\ab)} &  \arrow[equal]{d} p^*\cs{L} \\
-n^* ( q^*\cs{L}\ab) \arrow{r}{q\circ n = q\circ p}
-& p^* (q^*\cs{L}\ab)
-\end{tikzcd}
-\]
-Then $(q^*\cs{L}\ab,\nu(\cs{L}\ab))$ satisfies \eqref{E1} and \eqref{E2}, so $(q^*\cs{L}\ab,\nu(\cs{L}\ab))$ is an object in $\Loc\der(G)$.
-Moreover, if $\alpha\ab : \cs{L}\ab \to \cs{L}\ab$ is a morphism in $\Loc(G\ab)$ then $q^*(\alpha\ab)$ satisfies the condition in \eqref{E3}, so $q^*(\alpha\ab)$ is a morphism in $\Loc\der(G)$.
-This defines the functor
-\[
-L : \Loc(G\ab)\to \Loc\der(G)
-\]
-
-\begin{lemma}\label{lemma:descent}
-The functor $L : \Loc(G\ab)\to \Loc\der(G)$ is an equivalence.
-\end{lemma}
-\begin{proof}
-The quotient $q : G \to G\ab$ is an $G\der$-torsor in the fppf topology by \cite{demazure:SGA3-VIA}*{Thm. 3.2}, and thus an $G\der$-torsor in the fpqc topology.
-The lemma is now a result from descent theory, arguing as in \cite{Vistoli:notes}*{Theorem 4.46} for example. 
-\end{proof}
-
-Consider the functor
-\[
-q^* : \CS(G\ab) \to \CS(G)
-\]
-given on objects by $(\cs{L}\ab,\mu\ab) \mapsto (q^*\cs{L}\ab, (q^2)^* \mu\ab)$; this is an instance of \cite{cunningham-roe:13a}*{Lemma 1.4}.
-To see that $(q^*\cs{L}\ab, (q^2)^* \mu\ab)$ is indeed a linear character sheaf on $G$,
-verify \cite{cunningham-roe:13a}*{CS.3}. %, arguing as in \cite{cunningham-roe:13a}.
-Now set $L(\cs{L}\ab) = (\cs{L},\nu)$, where $L : \Loc(G\ab) \to \Loc\der(G)$ is the comparison functor above, so $\cs{L} = q^*\cs{L}\ab$ and $\nu = \nu(\cs{L}\ab)$.
-Then $(\cs{L}, \mu,\nu)$ is an object in $\CS\der(G)$.
-If $\alpha : (\cs{L}\ab,\mu\ab) \to (\cs{L}\ab',\mu\ab')$ is a morphism in $\CS(G\ab)$, 
-then $q^*(\alpha\ab) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha$ is a morphism in $\CS(G)$.
-These simple observations define the comparison functor
-\[
-q\ab^* : \CS(G\ab) \to \CS\der(G)
-\]
-and also show that the functor $q^* : \CS(G\ab) \to \CS(G)$ factors according to the following commuting diagram of functors
-\begin{equation}\label{qH}
-\begin{tikzcd}
-\CS(G) &\arrow{l}[swap]{q^*} 
-\CS(G\ab) \arrow{dl}{q\ab^*}\\
-\arrow{u}{\text{forget}} \CS\der(G). & 
-\end{tikzcd}
-\end{equation}
-The definition of $q\ab^* : \CS(G\ab)\to \CS\der(G)$ will be revisited in the proof of the following result.
-We may now relate $\CSab(G)$ to $\CS(G\ab)$ via the quotient map $q : G \to G\ab$.
-
-\begin{proposition} \label{prop:CSGabab}
-Suppose $G$ is a smooth group scheme.  
-Then pullback along $q : G \to G\ab$ defines an equivalence $\CS(G\ab) \to \CSab(G)$.
-\end{proposition}
-\begin{proof}
-In light of Lemma~\ref{lemma:nubeta}, it suffices to prove that the comparison functor $q\ab^* : \CS(G\ab) \to \CS\der(G)$ is an equivalence. 
-Let $L^2 : \Loc(G^2\ab) \to \Loc\der(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$. 
-Then $L^2$ is also an equivalence by Lemma~\ref{lemma:descent}.
-Using Lemma~\ref{lem:HH}, we may rewrite the comparison functor $q\ab^*$ on objects by
-\[
-\begin{array}{rcl}
-\CS(G\ab) &\to& \CS\der(G) \\
-(\cs{L}\ab,\mu\ab) &\mapsto& (L(\cs{L}\ab), L^2(\mu\ab))
-\end{array}
-\]
-and on morphisms by $\alpha \mapsto L(\alpha)$.
-The proposition now follows from the fact that both $L$ and $L^2$ are equivalences.
-\end{proof}
-
-\begin{corollary} 
-If $G$ is a smooth group scheme and $(\cs{L},\mu) \in \CS(G)$, then
-the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $(\cs{L},\mu) \cong q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, for some $(\cs{L}\ab,\mu\ab) \in \CS(G\ab)$.
-\end{corollary}
-
-\begin{proof}
-Notation as in the proof of Proposition~\ref{prop:CSGabab}.
-Consider the following diagram.
-%\[
-%\begin{tikzcd}
-%{} & G\times G \arrow{d}{c} &&&\\
-%1 \arrow{r} & H \arrow{r}{j} & G \arrow{r}{q} & G\ab \arrow{r} & 1
-%\end{tikzcd}
-%\]
-%gives
-\[
-\begin{tikzcd}
-\CS(G\der) & \arrow{l}[swap]{i\der^*} \CS(G) &\arrow{l}[swap]{q^*} 
-\CS(G\ab) \arrow{dl}{q\ab^*} \\
-& \CSab(G) \arrow{u}{\text{forget}}  & 
-\end{tikzcd}
-\]
-
-Now, suppose $(\cs{L},\mu)\in \CS(G)$ and there is an isomorphism $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ in $\CS(G\der)$.
-Then $(\cs{L},\mu,\beta) \in \CSab(G)$.
-By Proposition \ref{prop:CSGabab}, $(\cs{L},\mu,\beta) \iso q\ab^*(\cs{L}\ab,\mu\ab)$ for some $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$.
-Applying the forgetful functor $\CS_{G\der}(G)\to \CS(G)$ to this isomorphism, it follows that $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, as desired.
-
-Conversely, suppose $(\cs{L},\mu)\in \CS(G)$ and $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$.
-Then 
-\[
-i\der^*(\cs{L},\mu) \iso i\der^*q^*(\cs{L}\ab,\mu\ab)
-\]
- in $\CS(G\der)$.
-Since $q\circ i\der = 1$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ in $\CS(G\der)$.
-\end{proof}
-
-We may interpret this corollary as measuring how far $q^*$ is from being essentially surjective.  The next result shows that it is also not full.
-Let $C$ denote the cokernel of the natural map
-\[
-\Hom(\pi_0(\bar{G})_{\Frob{}}, \EEx) \to \Hom(\pi_0(\bar{G}\der)_{\Frob{}}, \EEx),
-\]
-where $\pi_0(\bar{G})_{\Frob{}}$ denotes the covariants of the action of Frobenius on
-the component group of $\bar{G}$
-
-\begin{corollary}
-If $G$ is a smooth group scheme and $(\cs{L},\mu)$ is a character sheaf on $G$ with trivial restriction to $G\der$,
-then the set of isomorphism classes of objects in $\CS(G\ab)$ mapping to $(\cs{L},\mu)$ under $q^*$ is a principal homogeneous space
-for $C$.
-\end{corollary}
-\begin{proof}
-By Proposition~\ref{prop:CSGabab}, it suffices to find the set of isomorphism classes in $\CSab(G)$ mapping to
-$(\cs{L},\mu)$ under the forgetful functor.  By the previous corollary this set is nonempty.
-If $(\cs{L},\mu,\beta)$ and $(\cs{L},\mu,\beta')$ both map to $(\cs{L},\mu)$, then $\beta' \circ \beta^{-1}$ is an
-automorphism of the constant sheaf on $G\der$.  Conversely, if $\varphi$ is an automorphism of $(\EE)_{G\der}$
-and $(\cs{L},\mu,\beta) \in \CSab(G)$ then $(\cs{L},\mu,\varphi \circ \beta) \in \CSab(G)$.  By \cite{cunningham-roe:13a}*{Theorem 3.9},
-the automorphism group is isomorphic to $\Hom(\pi_0(\bar{G}\der)_{\Frob{}}, \EEx)$.  Finally, we note that any
-automorphism $\alpha$ of $(\cs{L},\mu) \in \CS(G)$ defines an isomorphism $(\cs{L},\mu,\beta \circ \alpha|_{G\der}) \to (\cs{L},\mu,\beta)$.
-Applying \cite{cunningham-roe:13a}*{Theorem 3.9} again yields the desired result.
-\end{proof}
-
-%\subsubsection{Equivariant Weil local systems}\label{ssec:equivariant1}
-%
-%Let $G$ be a smooth group scheme over $k$, as above.
-%Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
-%Let $a : H \times G\to G$ be an action of $H$ on $G$ 
-%%group action compatible with the group structure on $G$ 
-%and write $p : H\times G \to G$ for projection. 
-%Consider the morphisms
-%\[
-%\begin{tikzcd}
-%H \times H \times G 
-%\arrow[shift left=4]{r}{b_1, b_2, b_3} 
-%\arrow{r}{}
-%\arrow[shift right=4]{r}{} 
-%& H \times G 
-%\arrow[shift left=2]{r}{a}
-%\arrow[shift right=2]{r}[swap]{p}
-% & G 
-%\end{tikzcd}
-%\]
-%defined by 
-%\begin{align*}
-%b_1(h_1,h_2,g) &= (h_1h_2,g) \\
-%b_2(h_1,h_2,g) &= (h_1,h_2g) \\
-%b_3(h_1,h_2,g) &= (h_2,g).
-%\end{align*}
-%Note that
-%\begin{align*}
-%a\circ b_1 &= a\circ b_2 \\
-%a\circ b_3 &= p\circ b_2 \numberthis \label{eqn:bap}\\
-%p\circ b_1 &= p\circ b_3.
-%\end{align*}
-%Define $s : G\to H\times G$ by $s(g) = (1,g)$.
-%An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
-%\[
-%\nu : a^*\cs{L} \to p^*\cs{L}
-%\] 
-%of Weil local systems on $H\times G$ such that 
-%\begin{equation}\label{E1}
-%s^*(\nu) = \id_{\cs{L}}
-%\end{equation}
-%and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes. 
-%\begin{equation}\label{E2}
-%\begin{tikzcd}
-%\ &  \arrow{dl}{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
-%b_1^* a^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
-%& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L} & 
-%\end{tikzcd}
-%\end{equation}
-%In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors
-%on Weil sheaves derived from equations \eqref{eqn:bap}; so, for example, the top left isomorphism
-%comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
-%%On stalks, this condition is ...
-%%\[
-%%\begin{tikzcd}
-%%\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
-%%\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
-%%& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
-%%\end{tikzcd}
-%%\]
-%Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
-%\begin{equation}\label{E3}
-%\begin{tikzcd}
-%\arrow{d}[swap]{\nu} a^*\cs{L} \arrow{r}{a^*(\alpha)} & a^*\cs{L}' \arrow{d}{\nu'} \\
-%p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
-%\end{tikzcd}
-%\end{equation}
-%commutes.
-%This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.
-%The reader will recognize this notion as the Weil sheaf version of equivariant sheaves for
-%the action $a$ of $H$ on $G$, as can be found, for example, in \cite{bernstein-lunts:equivariant}*{0.2}.
-
-\subsection{Objects and maps in commutative character sheaves} \label{ssec:obmor}
-
-We start with a method that will allow us to situate the diagram in Definition \ref{def:CCS} within $\CSab(G^2)$.
-
-\begin{lemma}\label{lemma:morinCSab}
-If $(\cs{L},\mu,\beta)\in \CS\ab(G)$ then $\mu  : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$, $\gamma : m^*\cs{L} \to  \theta^*(m^*\cs{L})$ and $\vartheta: \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are morphisms in $\CS\ab(G\times G)$.
-\end{lemma}
-\begin{proof}
-%Set $G^2 = G\times G$. 
-Define $m^2 : G^2\times G^2 \to G^2$ by $m^2(g_1,g_2,g_1',g_2') = (g_1g_1',g_2g_2')$. Also define $p^2_i : G^2\times G^2 \to G^2$ by $p^2_i(g_1,g_2,g_1,'g_2') = (g_i,g_i')$.
-First we show that $m^*\cs{L}$ is an object in $\CS(G^2)$ by equipping it with an isomorphism $\mu_m^2: (m^2)^* (m^*\cs{L}) \to m^*\cs{L} \boxtimes m^*\cs{L}$ defined by the diagram below.
-\[
-\begin{tikzcd}
-(m^2)^* (m^*\cs{L}) \arrow{d}{(m^2)^*\mu} \arrow{rr}{\mu_m^2} && m^*\cs{L} \boxtimes m^*\cs{L}\\
- (m^2)^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & (m^2)^*(p_1)^*\cs{L} \otimes (m^2)^*(p_2)^*\cs{L} \arrow{r} & (p^2_1)^*m^*\cs{L} \otimes (p^2_2)^*m^*\cs{L} \arrow[equal]{u}
-\end{tikzcd}
-\] 
-The pair $(m^*\cs{L},\mu_m^2)$ satisfies the conditions appearing in \cite{cunningham-roe:13a}*{Def. 1.1}.
-The restriction of $m^*\cs{L}$ to $G^2\der= G\der\times G\der$ is canonically isomorphic to $(\EE)_{G^2\der}$ by
-\[
-\begin{tikzcd}
-(m^*\cs{L})\vert_{G^2\der} \arrow{d}{\mu\vert_{G^2\der}} \arrow{r}{\beta^2_m} & (\EE)_{G^2\der}\\
-(\cs{L}\boxtimes\cs{L})\vert_{G^2\der} \arrow[equal]{r} & (\cs{L}\vert_{G\der})\boxtimes(\cs{L}\vert_{G\der}) \arrow{u}{\beta\boxtimes\beta}.
-\end{tikzcd}
-\]
-This shows that $(m^*\cs{L},\mu_m^2,\beta_m^2) \in \CS\ab(G^2)$. 
-Similar work defines $(\cs{L}\boxtimes\cs{L},\mu_\boxtimes^2,\beta_\boxtimes^2) \in \CS\ab(G^2)$.
-By construction, $\mu: m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ is a morphism in $\CS\ab(G^2)$.
-Similar work shows that $\gamma : m^*\cs{L} \to  \theta^*(m^*\cs{L})$ and $\vartheta: \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are also morphisms in $\CS\ab(G^2)$.
-\end{proof}
-
-Suppose $G$ is commutative, so $G\der = 1$. 
-Suppose $(\cs{L},\mu,\beta)$ is an object in $\CSab(G)$.
-Then $\beta : \cs{L}_1\to \EE$ is an isomorphism in $\CS(1)$, which is unique by \cite{cunningham-roe:13a}*{Theorem 3.9}.
-Tracing through the construction of $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ from $\beta : \cs{L}_1\to \EE$, we find 
-%\todo{I'm having some trouble seeing this.} 
-that $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ is the canonical isomorphism coming from the equation $m = m \circ \theta$. 
-Thus, when $G$ is commutative, Definition~\ref{def:CCS} agrees with Definition~\ref{def:CCScom}.
-The next result generalizes this observation.
-
-\begin{theorem}\label{thm:Gab}
-%Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
-Pull-back along the abelianization $q : G \to G\ab$
-defines an equivalence of categories
-\[
-\CCS(G\ab) \to \CCS(G).
-\]
-\end{theorem}
-
-\begin{proof}
-By definition, $\CCS(G)$ is a full subcategory of $\CS\ab(G)$; likewise, $\CCS(G\ab)$ is a full subcategory of $\CS\ab(G\ab)$.
-We have just seen that $\CS\ab(G\ab)$ is equivalent to $\CS(G\ab)$.
-By Proposition~\ref{prop:CSGabab}, pullback along the abelianization $q : G \to G\ab$ induces an equivalence $q^*\ab : \CS\ab(G)\to CS\ab(G)$.
-Thus, the functor $\CS\ab(G\ab)\to \CS\ab(G)$ induced by pullback along $q$ is an equivalence.
-The functor $\CCS(G\ab)\to \CCS(G)$ under consideration is the restriction of $\CS\ab(G\ab)\to \CS\ab(G)$ to the subcategory $\CCS(G\ab)$. 
-\[
-\begin{tikzcd}
-{} & \arrow{dl}[swap]{q^*\ab} \CS(G\ab)\\
-\CS\ab(G) & \arrow{l} \CS\ab(G\ab) \arrow{u}[swap]{\text{equiv.}}\\
-\CCS(G) \arrow[>->]{u} & \arrow{l} \CCS(G\ab) \arrow[>->]{u}
-\end{tikzcd}
-\]
-To prove the theorem, it is now sufficient to show that $\CCS(G\ab)\to \CCS(G)$ is essentially surjective.
-Suppose $(\cs{L},\nu,\beta)\in \CCS(G)$.
-Then $(\cs{L},\nu,\beta)\in \CS\ab(G)$.
-Let $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ be given by the equivalences above.
-Let $\xi : m\ab^*\cs{L}\ab \to \theta^* m\ab^*\cs{L}\ab$ be the isomorphism attached to $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ as in Section~\ref{sec:comcom}.
-Let $\gamma : m^*\cs{L} \to \theta^* m^*\cs{L}$ be the isomorphism attached to $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ as in Section~\ref{ssec:noncomdef}.
-By Lemma~\ref{lemma:morinCSab}, the diagrams below are in $\CS(G\ab)$ (right) and $\CS\ab(G)$ (left).
-\[
-  \begin{tikzcd}[row sep=10, column sep = 20]
-   m^*\cs{L} \arrow{dd}[swap]{\gamma} \arrow{r}{\mu} 
- & \cs{L}\boxtimes\cs{L} \arrow{dd}{\vartheta}
- &&&  m\ab^*\cs{L}\ab \arrow{dd}[swap]{\xi} \arrow{r}{\mu\ab} 
-   & \cs{L}\ab\boxtimes\cs{L}\ab \arrow{dd}{\vartheta}\\
-%
- && \  &\arrow{l}[swap]{(q^2)^*\ab}  & & &\\ 
-%
-   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} 
-&  \theta^*(\cs{L}\boxtimes\cs{L}) 
- &&&   \theta^*(m\ab^*\cs{L}\ab) \arrow{r}{{\theta}^*\mu\ab} 
- &  \theta^*(\cs{L}\ab\boxtimes\cs{L}\ab)
- \end{tikzcd}
-\]
-The diagram on the left is the result of applying the functor $(q^2)^*\ab$ to the one on the right; in particular $\gamma = (q^2)^*\ab \xi$.
-Since $(q^2)^*\ab$ is an equivalence by Proposition~\ref{prop:CSGabab}, it follows that the diagram in Definition~\ref{def:CCS} commutes if and only if the diagram in Definition~\ref{def:CCScom} commutes.
-In other words, $(\cs{L},\mu,\beta)\in \CCS(G)$ if and only if $(\cs{L}\ab,\mu\ab)\in \CCS(G\ab)$.
-
-\end{proof}
-
-%
-%Sections~\ref{ssec:equivariant1}, \ref{ssec:equivariant2}, \ref{ssec:descent} and \ref{ssec:closed} set up machinery needed to prove Theorem~\ref{thm:Gab}.
-%The precise definition of the functor $\CCS(G\ab) \to \CCS(G)$ will be given with the proof of Theorem~\ref{thm:Gab}, in Section~\ref{ssec:proof2}.
-
-%\subsubsection{Equivariant linear character sheaves}\label{ssec:equivariant2}
-%
-%With reference to Section~\ref{ssec:equivariant1}, suppose now that $H$ acts on $G$ through group homomorphisms: $a(h, m(g_1,g_2)) = m(a(h, g_1), a(h, g_2))$.
-%
-%We define an $H$-equivariant linear character sheaf on $G$ to be a triple $(\cs{L},\mu, \nu)$,
-%where $(\cs{L},\mu)$ is a linear character sheaf and $(\cs{L},\nu)$ is an $H$-equivariant local system.
-%We require that $\mu$ be compatible with $\nu$ in the following sense.
-%We define morphisms:
-%\begin{align*}
-%c_0 : H\times G \times G &\to H\times G \times H \times G \\
-%(h,g_1,g_2) &\mapsto (h,g_1,h,g_2); \\
-%c_1 : H \times G\times G &\to G\times G \\
-%(h, g_1, g_2) &\mapsto (hg_1,hg_2); \\
-%c_2 : H \times G\times G &\to H\times G \\
-%(h,g_1,g_2) &\mapsto (h, g_1g_2); \\
-%c_3 : H \times G\times G &\to G\times G \\
-%(h, g_1, g_2) &\mapsto (g_1, g_2).
-%\end{align*}
-%We require that the following diagram of Weil local systems on $H \times G\times G$ commutes:
-%\todo{Something's wrong: the top left actually requires $a \circ c_2 = m \circ c_1$, which isn't true.}
-%\begin{equation}\label{ECS1}
-%\begin{tikzcd}[column sep=30]
-%\ & \arrow{dl}{a\circ c_2 = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{dr}[swap]{p\circ c_2 = m\circ c_3}  &  \\
-%\arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} &&& c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
-%c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{dr}{p_i\circ c_1 = a\circ p_i\circ c_0} &&& \arrow{dl}[swap]{p\circ p_i\circ c_0 = p_i \circ c_3} c_3^*(\cs{L}\boxtimes \cs{L}) \\
-% & c_0^*(a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{c_0^*(\nu\boxtimes \nu)} & c_0^*(p^*\cs{L} \boxtimes p^*\cs{L}) & 
-%\end{tikzcd}
-%\end{equation}
-%Note that $a\circ c_2 = m\circ c_1$ precisely because $H$ acts on $G$ through group homomorphisms.
-%
-%
-%%On stalks, this condition is
-%%\[
-%%\begin{tikzcd}
-%%\arrow{d}[swap]{\mu_{(h\cdot g_1, h\cdot g_2)}} \cs{L}_{(h\cdot g_1)(h\cdot g_2)} & \arrow[equal]{l}  \cs{L}_{h\cdot(g_1 g_2)} \arrow{r}{\nu_{(h, g_2 g_2)}} & \cs{L}_{g_1 g_2} \arrow[equal]{r} & \cs{L}_{g_1 g_2} \arrow{d}{\mu_{(g_1,g_2)}} \\
-%%\cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow[equal]{r} & \cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow{r}{\nu_{(h,g_1)}\otimes \nu_{(h,g_2)}} & \cs{L}_{g_1}\otimes \cs{L}_{g_2} & \arrow[equal]{l} \cs{L}_{g_1} \otimes \cs{L}_{g_2},
-%%\end{tikzcd}
-%%\]
-%%for all $(h,g_1,g_2)\in H\times G\times G$.
-
-%A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$
-%is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves.
-%%so
-%%\begin{equation}\label{CS4}
-%%\begin{tikzcd}
-%%\arrow{d}[swap]{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
-%%\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
-%%\end{tikzcd}
-%%\end{equation}
-%%commutes; see also \cite{cunningham-roe:13a}, CS.4].
-%%
-%Let $\CS_H(G)$ be the category of $H$-equivariant linear character sheaves on $G$.
-%
-%%Is $\CS_H(G)$ a rigid monoidal category?
-%
-%%If $(\cs{L},\mu,\nu)$ and $(\cs{L},\mu,\nu')$ in $\CS_H(G)$, then $\nu = \nu'$?
-%
-%\begin{lemma}\label{lem:HH}
-%If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ and
-%$\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are morphisms of $H\times H$-equivariant Weil local systems on $G\times G$. 
-%\end{lemma}
-%
-%\begin{proof} 
-%Define
-%\begin{align*}
-%d : H\times H\times G\times G &\to H\times G\times H\times G \\
-%(h_1,h_2,g_1,g_2) &\mapsto (h_1, g_1, h_2, g_2)\\
-%a_2 : H\times G\times H\times G &\to G\times G \\
-%(h_1,g_1,h_2,g_2) &\mapsto (h_1g_1, h_2g_2) \\
-%p_2 : H\times G\times H\times G &\to G\times G \\
-%(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2) \\
-%\theta_2 : H \times G \times H \times G &\to H \times G \times H \times G \\
-%(h_1,g_1,h_2,g_2) &\mapsto (h_2,g_2,h_1,g_1).
-%\end{align*}
-%The following diagram defines the isomorphisms needed to see that both $m^*\cs{L}$ and $\cs{L}\boxtimes\cs{L}$ are $H\times H$-equivariant Weil local systems.
-%\[
-%\begin{tikzcd}[column sep=40]
-%\arrow{d}[swap]{a_2^*(\mu)} a_2^* (m^*\cs{L}) \arrow[dashed]{r} 
-%	& \arrow{d}{p_2^*(\mu)} p_2^*(m^*\cs{L})\\
-%\arrow{d}[swap]{a_2= (a\times a)\circ d} a_2^*(\cs{L}\boxtimes\cs{L}) \arrow[dashed]{r} 
-%	& \arrow{d}{p_2= (p\times p)\circ d} p_2^*(\cs{L}\boxtimes\cs{L}) \\
-%%d^* (a\times a)^* (\cs{L}\boxtimes\cs{L}) & d^* (p\times p)^* (\cs{L}\boxtimes\cs{L}) \\
-%d^* (a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{d^*(\nu\boxtimes \nu)}& d^*(p^*\cs{L}\boxtimes p^*\cs{L}) 
-%\end{tikzcd}
-%\]
-%The dashed arrows both satisfy \eqref{E1} and \eqref{E2} as they apply here.
-%This diagram also shows that $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of equivariant sheaves, since it satisfies \eqref{E3} as it applies here.
-%The proof that $\theta^*(\cs{L}\boxtimes\cs{L})$ is $H\times H$ equivariant is also straightforward,
-%since $a_2\circ \theta_2 = \theta \circ a_2$ and $p_2\circ \theta_2 = \theta \circ p_2$.
-%Let $\nu_2 : a_2^*(\cs{L}\boxtimes\cs{L}) \to p_2^*(\cs{L}\boxtimes\cs{L})$ be the middle horizontal isomorphism of Weil local systems, above. 
-%To see that
-%\[
-%\begin{tikzcd}
-%a_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r}{a_2^*(\vartheta)} \arrow{d}[swap]{\nu_2} 
-%	& a_2^*\theta^*(\cs{L}\boxtimes\cs{L}) \arrow{d}{\theta^*(\nu_2)} \\
-%p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r}{p_2^*(\vartheta)} 
-%	& p_2^*\theta^*(\cs{L}\boxtimes\cs{L})
-%\end{tikzcd}
-%\]
-%commutes, consider the commuting diagram of stalks, below.
-%\[
-%\begin{tikzcd}
-%\cs{L}_{h_1g_1}\otimes\cs{L}_{h_2g_2} \arrow{r}{\vartheta}  \arrow{d}[swap]{\nu_2} 
-%	& \cs{L}_{h_2g_2} \otimes\cs{L}_{h_1g_1}  \arrow{d}{\nu_2} \\
-%\cs{L}_{g_1}\otimes\cs{L}_{g_2} \arrow{r}{\vartheta}  
-%	& \cs{L}_{g_2} \otimes\cs{L}_{g_1}
-%\end{tikzcd}
-%\]
-%\end{proof}
-
-%\subsubsection{Quotient by a closed subgroup}\label{ssec:closed}
-%
-%We now suppose that $j : H \hookrightarrow G$ is a closed subgroup scheme over $\Fq$
-%and that the action $a : H\times G\to G$ is obtained by restricting the action
-%$m : G \times G\to G$ to $H\times G$.  In this context, we are able to replace
-%$\nu : a^*\cs{L} \to p^*\cs{L}$ with an isomorphism $\beta : \cs{L}_H \to (\EE)_H$.
-%Let $\CS^H(G)$ be the category of triples $(\cs{L},\mu,\beta)$ with $(\cs{L},\mu) \in \CS(G)$
-%and $\beta : \cs{L}\vert_H \to (\EE)_H$ an isomorphism in $\CS(H)$;
-%a morphism $(\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ in $\CS^H(G)$ is a morphism
-%$\alpha: \cs{L} \to \cs{L}'$ in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{H}$.
-%
-%\begin{lemma}\label{lem:beta}
-%If $H\hookrightarrow G$ is a closed subgroup scheme over $\Fq$ then $\CS_H(G)$ is equivalent to $\CS^H(G)$.
-%\end{lemma}
-%\begin{proof}
-%Define $f : H\times G \to G\times G$ by $f(h,g) = (j(h),g)$ and note that $a = m\circ f$.
-%Write $p_1: G\times G\to G$ for projection to the first component and $p_2 : G\times G \to G$ for projection to the second.
-%We may pass between $\nu$ and $\beta$ via the following diagram.
-%\[
-%\begin{tikzcd}[column sep=30]
-%\ & a^*\cs{L} \arrow{dl}{m\circ f = a} \arrow{r}{\nu} & p^*\cs{L} & \\
-%f^* m^*\cs{L} \arrow{dr}{f^*\mu} &&& (\EE)_{H} \boxtimes \cs{L} \arrow{ul} \\ 
-%& f^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_1 \circ f = j}[swap]{p_2\circ f = \id}  & 
-%\cs{L}\vert_{H} \boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id} & 
-%\end{tikzcd}
-%\]
-%It is a straightforward, tedious exercise to show that the conditions \eqref{E1}, \eqref{E2} and \eqref{ECS1} 
-%on $\nu$ are equivalent to the condition that the isomorphism of Weil local systems
-%$\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is an isomorphism in the category of of linear character sheaves on $H$.
-%\end{proof}
-
-Theorem~\ref{thm:Gab} shows that $\CCS(G)$ is a categorical solution to the problem that linear character sheaves on $G$ need not be trivial on $G\der$, as discussed at the beginning of Section~\ref{sec:noncom}.
-At the same time, changing $\CS(G)$ to $\CCS(G)$ resolves the lack of bijectivity in \cite{cunningham-roe:13a}*{Theorem 3.6}.
-%
-We may also use Theorem~\ref{thm:Gab} to give a description of the morphisms and the isomorphism classes of objects in $\CCS(G)$.
-
-\begin{corollary}\label{cor:Gab}
-%Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
-The category $\CCS(G)$ is monoidal and there is a canonical isomorphism
-\[
-\CCSiso{G} \iso \Hom(G\ab(\Fq),\EEx).
-\]
-Every map in $\CCS(G)$ is either trivial or an isomorphism, and the automorphism group of any object in $\CCS(G)$ is canonically
-isomorphic to $\Hom(\pi_0(\bar{G}\ab)_{\Frob{}},\EEx)$.
-\end{corollary}
-
-\begin{proof}
-The first claim follows from Theorems \ref{thm:trfrobiso} and \ref{thm:Gab}.
-Let us write $(\cs{L},\mu,\beta) \mapsto (\cs{L}\ab,\mu\ab)$ to indicate the equivalence appearing in Theorem~\ref{thm:Gab};
-then \[\Aut_{\CCS(G)}(\cs{L},\mu,\beta) = \Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab).\] 
-By \cite{cunningham-roe:13a}*{Theorem 3.9},  $\Aut_{\CCS(G\ab)}(\cs{L}\ab,\mu\ab) = \Hom(\pi_0(\bar{G}\ab)_{\Frob{}},\EEx)$.
-\end{proof}
-
-\subsection{Geometrization of characters} \label{ssec:geo}
-
-\begin{theorem}\label{thm:geo}
-%Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
-The trace of Frobenius $\TrFrob{} : \CCSiso{G}\to G(\Fq)^*$ fits into the following diagram,
-\[
-\begin{tikzcd}
-\ & & \CCSiso{G\ab} \arrow{d}{\TrFrob{}}[swap]{\iso} \arrow{r}{\iso} & \CCSiso{G} \arrow{d}{\TrFrob{}}& \\
-1 \arrow{r} & \Delta_G^* \arrow{r} & G\ab(k)^* \arrow{r} & G(k)^* \arrow{r} & 1,
-\end{tikzcd}
-\]
-where $\Delta_G$ is the image of the connecting homomorphism $G\ab(\Fq) \to \Hh^1(\Fq, G\der)$. 
-Thus the category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the following sense: for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $(\cs{L},\mu,\beta)$ in $\CCS(G)$ such that $\trFrob{\cs{L}} = \chi$.
-While the geometrization of $\chi : G(\Fq) \to \EEx$ is not unique, the group of isomorphism classes of possibilities are enumerated by $\Delta_G^*$.
-\end{theorem}
-
-\begin{proof}
-By the definition of $\Delta_G$, we have a short exact sequence
-\[
-1 \to G(k) / G\der(k) \to G\ab(k) \to \Delta_G \to 1.
-\]
-Applying $\Hom(-, \EEx)$ and using the fact that every homomorphism $G(k) \to \EEx$ vanishes on $G\der(k)$, we get
-\[
-1 \to \Delta_G^* \to G\ab(k)^* \to G(k)^* \to 1.
-\]
-By Theorem~\ref{thm:Gab}, the map $\CCSiso{G\ab} \to \CCSiso{G}$ is an isomorphism.
-Moreover, since both $\CCSiso{G\ab} \to \CCSiso{G}$ and $G\ab(k)^* \to G(k)^*$ are
-defined by pullback along $q$, the square in the statement of the theorem commutes.
-Finally, $\TrFrob{} : \CCSiso{G\ab} \to G\ab(k)^*$ is an isomorphism by Theorem \ref{thm:trfrobiso}.
-\end{proof}
-
-\begin{remark}
-Note that when $\Hh^1(k,G\der) = 0$ then $\CCSiso{G} \iso G(\Fq)^*$, so
-we succeed in geometrizing characters of $G(k)$ on the nose.
-\end{remark}
-
-%\todo{Masound's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case.
-So, I think the modification is easy: add mop to diagram 2.4 in Masoud's paper.
-\\ -CC}
-
-%\section{Descent to the Abelianization} \label{sec:descent}
-
-%In this section we use descent along the abelianization $q : G \to G\ab$ to prove Propositions~1.2 and 1.4, and Theorem~\ref{thm:Gab}.
-%This approach requires introducing equivariant linear character sheaves, as defined in Section~[].
-
-%We close this section by gathering together the main result of this paper in one place.
-
-\section{Application to type theory for \texorpdfstring{$p$}{p}-adic groups}\label{sec:types}
-
-We now show how to use Theorem~\ref{thm:geo} to geometrize Yu type data and how to geometrize types for supercuspidal representations of tamely ramified $p$-adic groups.
-
-\subsection{Quasicharacters of smooth group schemes over certain henselian traits}
-
-%We begin with the case of continuous linear characters.
-
-Let $R$ be a complete discrete valuation ring with maximal ideal $\mathfrak{m}$ and perfect residue field $\Fq$. 
-Let $\underline{G}$ be a smooth group scheme over $R$.
-Here we shall use  \cite{bertapelle-gonzales:Greenberg} for the definition and fundamental properties of the Greenberg transform.
-Let $G$ be the Greenberg transform of $\underline{G}$; then $G$ is a group scheme over $\Fq$ and there is a canonical isomorphism
-\[
-G(\Fq) = \underline{G}(R).
-\]
-
-\begin{proposition}\label{prop:quasicharacters}
-With notation as above, suppose $\Fq$ is a finite field.
-For every quasicharacter character $\varphi : \underline{G}(R) \to \EEx$ there is a Weil sheaf $\cs{L}$ on $G$ such that \[\trFrob{\cs{L}} =  \varphi.\] \end{proposition}
-
-\begin{proof}
-By continuity of $\varphi : \underline{G}(R) \to \EE^\times$, there is some $m \in \NN$ and a factorization
-\[
-\begin{tikzcd}
-\underline{G}(R) \arrow{rr}{\varphi} \arrow{rd} && \EEx\\
-& \underline{G}(R/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi_m} 
-\end{tikzcd}
-\] 
-Set $R_m = R/\mathfrak{p}^{m+1}$ and
-set $G_m = \Gr_m^{R}(\underline{G})$, the Greenberg transform of $\underline{G}\times_{\Spec{R}}\Spec{R_m}$.
-Then $G_m$ is a smooth group scheme over $\Fq$ and $G_m(\Fq) = \underline{G}(R_m)$.
-Using Theorem~\ref{thm:geo}, let $\cs{L}_m$ be a geometrization of the character $\varphi_m: G_m(\Fq) \to \EEx$; so
-\[
-\trFrob{\cs{L}_m} = \varphi_m
-\]
-on $G_m(\Fq)$.
-%
-Recall that the full Greenberg transform $G \ceq \Gr^{R}(\underline{G})$ is a group scheme over $\Fq$ such that $G(\Fq) = \underline{G}(R)$; it comes equipped with a morphism $G \to G_m$.
-Let $\cs{L}$ be the  Weil sheaf on $G$ obtained from $\cs{L}_m$ by pullback along $G \to G_m$. 
-Then $\cs{L}$ is a quasicharacter sheaf on $G$, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, such that $\trFrob{\cs{L}} = \varphi$.
-\end{proof}
-
-\subsection{Jacobi theory over finite fields}\label{ssec:Jacobi}
-
-For use below, we recall some facts about the Heisenberg-Weil representation.
-
-Let $V$ be a finite-dimensional vector space over a finite field $\Fq$ equipped with a symplectic paring $\langle\ ,\ \rangle : V\times V \to Z$, where $Z$ is a one-dimensional vector space over $\Fq$.
-Let $V^\sharp$ be the Heisenberg group determined by $(Z, \langle\ ,\ \rangle)$ \cite{gurevich-hadani:07a}*{\S 1.1}.
-Let $\Sp(V)$ be the symplectic group determined by the symplectic pairing $\langle\ ,\ \rangle$; this group acts on $V^\sharp$.
-The group $\Sp(V)\ltimes V^\sharp$ is called the Jacobi group. 
-From the construction above, it is clear that the Jacobi group may be viewed as the $\Fq$-points of an algebraic group over $\Fq$; we will refer to that algebraic group as the Jacobi group.
-
-Let $\psi : Z \to \EEx$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi$ \cite{gurevich-hadani:07a}*{\S 1.1}. 
-The Heisenberg representation determines a representation $\pi_{\psi}$ of $\Sp(V)$ with the same representation space as $\omega_\psi$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\psi(g)$ determines an isomorphism of representations $\omega_\psi^g \to \omega_\psi$.
-Let $W_\psi = \pi_\psi \ltimes \omega_\psi$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$ given by $\omega_\psi$ and $\pi_\psi$ \cite{gurevich-hadani:07a}*{\S 2.2}.
-
-There is a Weil sheaf complex $\cs{K}_\psi$ on $\Sp(V)\ltimes V^\sharp$ \cite{gurevich-hadani:07a}*{Theorem 3.2.2.1} (see also \cite{gurevich-hadani:11a}*{Theorem 4.5}) such that 
-\begin{equation}
-\trFrob{\cs{K}_\psi} = \trace(W_\psi).
-\end{equation}
-%
-Since $\cs{K}_\psi$ is an object in Deligne's category $D^b_c(\Sp(V)\ltimes V^\sharp,\EE)$, the left hand side of this equality must be interpreted accordingly.
-
-\subsection{Review of Yu's types and associated models}\label{ssec:review}
-
-For the rest of Section~\ref{sec:types}, $K$ is a $p$-adic field and $R$ is the ring of integers of $K$.
-A Yu type datum consists of the following:
 \begin{enumerate}
-\labitem{Y0}{Y0} a sequence of compact groups $\oK^0 \subseteq \oK^1 \subseteq \cdots \subseteq \oK^d = \oK$;
-\labitem{Y1}{Y1} a continuous representation $\orho^0$ of $\oK^0$;
-\labitem{Y2}{Y2} quasicharacters $\varphi^i : \oK^i \to \CC^\times$, for $i=0, \ldots d$.
-\end{enumerate}
-The representation $\orho^0$ and the quasicharacters $(\varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct the representations $\orho_i$ of $\oK^i$ that form the sequence of types $(\oK^i,\orho_i)$, for $i=1, \ldots, d$.
-%
-In order to prepare for the construction of the geometric types of Theorem~\ref{thm:geotypes}  we review some further detail here.
-In Table~\ref{table:notation} we explain how to convert the constructions appearing in this section into the notation of \cite{yu:01a}.
-
-First, Yu introduces 
-\begin{enumerate}
-\labitem{Y3}{Y3}
-compact groups $J_i\subset \oK$, for $i=0, \ldots d$, such that 
-$
-\oK^i = J_0\cdots J_{i}
-$ 
-and, for $i=0, \ldots d-1$, a natural action of $\oK^i$ on $J_{i+1}$ defining the groups $\oK^i \ltimes J_{i+1}$.
-\begin{equation}\label{eq:semiprod}
-\begin{tikzcd}
-\ && 1 \arrow{d} && \\
-\ && \oK^{i}\cap J_{i+1}\arrow{d} && \\
-1 \arrow{r} & J_{i+1} \arrow{r} & \oK^i \ltimes J_{i+1} \arrow{d}{\pi_{i+1}} \arrow{r}{p_i} & \oK^i \arrow{r} & 1\\
-&& \oK^{i+1} \arrow{d}{} && \\
-&& 1 &&
-\end{tikzcd}
-\end{equation}
-\end{enumerate}
-%He then introduces the following quotients of $J_{i+1}$ and $\oK^i$, for $i=0, \ldots d-1$.
-%
-Next, Yu defines a group homomorphism (in fact, a quotient) 
-$
-J_{i+1} \to V_{i+1}
-$
-where $V_{i+1}$ is a finite abelian group, the latter also given the structure of a $\Fq$-vector space.
-The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to Z_{i+1}$, where $Z_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : Z_{i+1} \to \CC^\times$.
-%\labitem{Q2}{Q2} 
-%\item 
-This, in turn, is used to define a map
-$
-J_{i+1} \to V_{i+1}^\sharp,
-$
-where $V_{i+1}^\sharp$ is the Heisenberg group determined by $V_{i+1}$, $Z_{i+1}$, $\langle\ ,\ \rangle_{i+1}$ and $\psi_{i+1}$, as in Section~\ref{ssec:Jacobi}.
-In fact, the quotient $J_{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J_{i+1} \to H_{i+1}$ and an isomorphism $j_{i+1} : H_{i+1} \to V_{i+1}^\sharp$, where $H_{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:01a}*{}.
-%\labitem{Q3}{Q3} 
-%\item
-Finally, Yu constructs a group homomorphism $f_{i+1} : \oK^i \to \Sp(V_{i+1})$ such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $\oK^i$ on $H_{i+1}$ in the sense of \cite{yu:01a}.
-%
-Taken together, this defines
-%\end{enumerate}
-\begin{enumerate}
-\labitem{Y4}{Y4}  
-a group homomorphism $h_{i+1} : \oK^i \ltimes J_{i+1} \to  \Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ making the following diagram commute.
-\[
-\begin{tikzcd}
-1 \arrow{r} & J_{i+1} \arrow{d} \arrow{r} & \oK^i \ltimes J_{i+1} \arrow{d}{h_{i+1}} \arrow{r}{p_i} & \oK^i \arrow{r} \arrow{d}{f_i} & 1\\ 
-1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
-\end{tikzcd}
-\]
+\item[(1)]
+\item[(2)]
 \end{enumerate}
 
-\begin{table}[ht]
-\caption{Notation conversion chart.}
-\begin{spacing}{1.2}
-\begin{tabular}{| c|l |}
-\hline
-\text{this paper} & \cite{yu:01a}\\
-\hline
-%$\oK^0$ & $\,^\circ K^0 = G^0(F)_y$\\% \cite{yu:01a}*{\S 15} \\
-%$\oK^{i+1}$ & $\,^\circ K^{i+1} = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, \ldots, s_{i})}$\\% \cite{yu:01a}*{\S 15} \\
-%$\oK^0$ & $\,^\circ K^0 = G^0(F)_y$\\% \cite{yu:01a}*{\S 15} \\
-%$\orho^0$ & $\,^\circ \rho^0$\\% \cite{yu:01a}*{\S 15} \\
-%$\orho^{i+1}$ & $\,^\circ \rho^{i+1}$\\% \cite{yu:01a}*{\S 15} \\
-$\varphi^i$ & $\phi_i\vert_{\,^\circ K^i }$ \\
-$J_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}$ \\
-$V_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ (G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}$ \\ 
-$V_{i+1}^\sharp$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi}_i\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
-%$H^{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi_i}\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ \\
-$Z_{i+1}$ & $\ker(V_{i+1}^\sharp\to V_{i+1})$ \\ % \cite{yu:01a}*{\S 11} \\
-%$(f_{j+1}, j_{i+1})$ & $(f,j)$ \cite{yu:01a}*{\S 11} \\
-%$\langle\ ,\ \rangle_{i+1}$ & $\langle\ ,\ \rangle$, \cite{yu:01a}*{\S 11} 
-\hline
-\end{tabular}
-\end{spacing}
-\label{table:notation}
-\end{table}%
-
-We can now recall how Yu uses all this to construct representations $\orho^i$ of $\oK^i$, for $i=1, \ldots, d$ and the types $(\oK^i,\orho_i)$.
-The representations $\orho^i$ and $\orho_i$ are defined recursively.
-For the base case $i=0$, set $\orho_0 \ceq \orho^0\otimes \varphi^0$; see \ref{Y1} above.
-Now fix $i$.
-Let $W_{i+1}$ be the Heisenberg-Weil representation of the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$, whose restriction to $V_{i+1}^\sharp$ has central character $\psi_{i+1}$.
-Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $\oK^i \ltimes J_{i+1}$.
-Write $\inf(\orho_i)$ for the representation of $\oK^i \ltimes J_{i+1}$ obtained by pulling back $\orho^i$ along $\oK^i \ltimes J_{i+1} \to \oK^i$. 
-Consider the representation
-\begin{equation}\label{eq:tensor}
-\orho^{i+1} \ceq h_{i+1}^*(W_{i+1}) \otimes \inf(\orho_i)
-\end{equation}
-of $\oK^i \ltimes J_{i+1}$.
-%By construction, the character of this representation satisfies
-%\begin{equation}\label{eq:tilderho}
-%\trace({\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\orho^i)(p_i(y))\ \varphi^i(p_i(y))
-%\end{equation}
-%for $y \in \oK^i \ltimes J_{i+1}$.
-By \cite{yu:01a}*{}, the representation $\orho^{i+1}$ of $\oK^i \ltimes J_{i+1}$ is trivial on $\oK^{i}\cap J_{i+1}$ so $\orho^{i+1}$ descends to $\oK^{i+1}$. 
-%
-Set $\orho_{i+1} = \orho^{i+1}\otimes \varphi^{i+1}$.
-This completes the recursive definition of the Yu $(\oK^i,\orho_i)$ for $i=0, \ldots , d$.
-%The character of $\orho^d$ on $\oK^d = C = J_0 \cdots J_d$ satisfies
-%\[
-%\trace(\rho)(k_0 \cdots k_d) = \orho^0(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
-%\]
-%for $k_i\in J_i$.
-
-%\subsection{Review of Yu's smooth models}\label{ssec:review}
-
-%\begin{enumerate}
-%\labitem{M1}{M1}
-By \cite{Yu:models}*{Prop 10.2} there is a sequence  
-\[
-\underline{G}^0 \to \underline{G}^1 \to \cdots \to \underline{G}^d = \underline{G}
-\]
-of morphisms of affine smooth group schemes of finite type over $R$ such that, on $R$-points it gives the sequence $\oK^0 \subseteq \oK^1 \subseteq \cdots \subseteq \oK^d$ above.
-Indeed, this is the main result of \cite{Yu:models}.
-
-%\labitem{M2}{M2}
-As explained in \cite{Yu:models}*{\S 10.4}, there is morphism of affine smooth group schemes of finite type over $R$ 
-\[
-\underline{J}^i \to \underline{G},
-\] 
-for each $i=0,\ldots d$, such that $\underline{J}^i(R) = J_i$ as a subgroup of $C$ and such that the image of the $R$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $\oK^i$, for $i=0, \ldots , d$.
-%\labitem{M3}{M3}
-There is a natural action of $\underline{G}^i$ on $\underline{J}^{i+1}$ in the category of smooth affine group schemes over $R$ so that the group scheme
-\[
-\underline{G}^i \ltimes \underline{J}^{i+1}
-\]
-gives $(\underline{G}^i \ltimes \underline{J}^{i+1})(R) = \oK^i \ltimes J_{i+1}$
-%\end{enumerate}
-
-\newcommand{\reductive}{{\operatorname{red}}}
-
-Write $\underline{J}^{i+1}_\Fq$ for the special fibre $\underline{J}^{i+1}\times_{\Spec{R}} \Spec{k}$ of $\underline{J}^{i+1}$. 
-The vector space $V_{i+1}$ may realized as the $\Fq$-points on a variety $V^{i+1}$ over $\Fq$, where $V^{i+1}$, appears as a quotient $\underline{J}^{i+1}_{\Fq} \to V^{i+1}$ of algebraic groups over $\Fq$.
-Then the quotient $J_{i+1} \to V_{i+1}$ is realized as the composition
-\[
-\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to V^{i+1}(\Fq) = V_{i+1}.
-\]
-Likewise, the Heisenberg $p$-group $H_{i+1}$, appearing in \ref{ssec:review}, may be realized as a quotient of algebraic groups, and $\underline{J}^{i+1}_{\Fq} \to H^{i+1}$ as the composition 
-\[
-\underline{J}^{i+1}(R) \to \underline{J}^{i+1}(\Fq) = \underline{J}^{i+1}_\Fq(\Fq) \to H^{i+1}_{\Fq}(\Fq) = H_{i+1}.
-\]
-Finally, the group homomorphism $f_i : J_0\cdots J_i \to \Sp(V_{i+1})$ may be made geometric in much the same way. 
-Writing $\underline{G}^{i}_\Fq$ for the special fibre $\underline{G}^{i}\times_{\Spec{R}} \Spec{k}$ of $\underline{G}^{i}$, and writing $\underline{G}^{i,\reductive}_\Fq$ for the reductive quotient of $\underline{G}^{i}_\Fq$, there is a quotient of algebraic groups $\underline{G}^{i,\reductive}_\Fq \to W^{i+1}_\Fq$ so that $f_i : J_0\cdots J_i \to \Sp(V_{i+1})$ is realized as the composition
-\[
-\underline{G}^{i}(R) \to \underline{G}^{i}(\Fq) = \underline{G}^{i}_\Fq(\Fq) \to  \underline{G}^{i,\reductive}_\Fq(\Fq) \to W^{i+1}_{\Fq}(\Fq) = \Sp(V_{i+1}).
-\]
-
-With all this, we may revisit the quotients appearing in Section~\ref{ssec:review}:
-\[
-\begin{tikzcd}
-1 \arrow{r} & \underline{J}^{i+1}  \arrow{r} & \underline{G}^i \ltimes \underline{J}^{i+1} \arrow{r} & \underline{G}^i \arrow{r}  & 1\\
-1 \arrow{r} & \underline{J}^{i+1}_\Fq \arrow{d} \arrow{u} \arrow{r} & \underline{G}_\Fq^i \ltimes \underline{J}_\Fq^{i+1} \arrow{d} \arrow{u} \arrow{r} & \underline{G}_\Fq^i \arrow{r} \arrow{d} \arrow{u} & 1\\
-1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1,
-\end{tikzcd}
-\]
-where the last two rows are now understood as forming a diagram in the category of algebraic groups over $\Fq$. 
-This realizes the Jacobi group $\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp$ as a quotient of the special fibre of the smooth group scheme $\underline{G}^i \ltimes \underline{J}^{i+1}$ over $R$.
-
-We may now revisit the ingredients in the construction of the representation $\rho$ of $\underline{G}(R)$ along the lines indicated by Yu and recalled in Section~\ref{ssec:review}.
 \begin{enumerate}
-\labitem{M0}{M0}
-The compact groups $\oK^i$ have been replaced by the smooth group schemes $\underline{G}^i$.
-\labitem{M1}{M1}
-The continuous representation $\orho^0$ of $\oK^0$ is a representation of $\underline{G}^0(R)$ obtained by inflation along $\underline{G}^0(R) \to \underline{G}^0(\Fq)$ from a representation $\varrho_0$ of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
-In fact, $\varrho_0$ is itself obtained by pulling back a representation $\varrho_0^\reductive$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
-\labitem{M2}{M2} The quasicharacters $\varphi^i$ are quasicharacters of $\underline{G}^i(R)$, for $i=0, \ldots, d$.
-\labitem{M3}{M3}
-Diagram \eqref{eq:semiprod} is now replaced by the following diagram of smooth group schemes over $R$.
-\begin{equation}\label{eq:pimodel}
-\begin{tikzcd}
-\ && 1 \arrow{d} && \\
-\ && \underline{G}^{i}\times_{\underline{G}} \underline{J}^{i+1}\arrow{d} && \\
-1 \arrow{r} & \underline{J}^{i+1} \arrow{r} & \underline{G}^i \ltimes \underline{J}^{i+1} \arrow{d} \arrow{r} & \underline{G}^i \arrow{r} & 1\\
-&& \underline{G}^{i+1} \arrow{d} && \\
-&& 1 &&
-\end{tikzcd}
-\end{equation}
-\labitem{M4}{M4}
-The representation $h_{i+1}^*(W_{i+1})$ appearing in \ref{Y4} is now obtained by pulling back a representation along 
-\[
-(\underline{G}^i \ltimes \underline{J}^{i+1})(R) \to (\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq).
-\]
-Let $w_{i+1}$ be that representation of $(\underline{G}^i \ltimes \underline{J}^{i+1})(\Fq) = (\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq)(\Fq)$. 
-Then $w_{i+1}$ is itself obtained by pulling back the representation $W_{i+1}$ along the $\Fq$-points of the quotient
-\[
-\underline{G}_\Fq^i \ltimes \underline{J}^{i+1}_\Fq \to 
-\Sp(V_{i+1}) \ltimes V_{i+1}^\sharp.
-\]
+\item[(i)]
+\item[(ii)]
+\item[(iii)]
+\item[(iv)]
+\item[(v)]
+\item[(vi)]
+\item[(vii)]
 \end{enumerate}
 
-This brings us back to \cite{Yu:models}*{\S 10.5} as quoted in the Introduction to this paper.
-
-\subsection{Geometrization of characters of types}\label{ssec:geotypes}
-
-Finally, we come to the main result of Section~\ref{sec:types}.
-%
-Since Yu's theory refers to complex representations, and since our geometrization uses $\ell$-adic sheaves, we grit our teeth and fix an isomorphism $\CC \approx \EE$.
-
-\begin{theorem}\label{thm:geotypes}
-Let $\oK^i$ $\orho^0$, $\varphi^i$, for $i=0, \ldots d$, be a Yu type datum as in Section~\ref{ssec:review}, \ref{Y0}, \ref{Y1} and \ref{Y2}.
-Let $\underline{G}^i$ and $\varrho_0\red$ be as in Section~\ref{ssec:review}, \ref{M0} and \ref{M1}.
-Assume $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
-For $i=0, \ldots ,d$, let $G^i = \Gr_{R}(\underline{G}^i)$ be the Greenberg transform of the smooth group scheme $\underline{G}^i$ appearing in Section~\ref{ssec:review}.
-Then there is a virtual Weil sheaf complex $\cs{F}_i$ on $G^i$ such that $\trFrob{\cs{F}_i} = \trace(\orho_i)$, for $i=0, \ldots , d$.
-\end{theorem}
-
-\begin{proof}
-For every $i=0, \ldots ,d$, set $G^i = \Gr_{R}(\underline{G}^i)$.
-Recall that $G^i(\Fq) = \underline{G}^i(R) = \oK^i$, canonically.
-We begin with an argument already employed in the proof of Proposition~\ref{prop:quasicharacters}.
-By continuity of the quasicharacters $\varphi^i : G^i(\Fq) \to \CC^\times$, there is some $m \in \NN$ and a factorization
-\[
-\begin{tikzcd}
-G^i(\Fq) \arrow{rr}{\varphi^i} \arrow{rd} && \EEx\\
-& \underline{G}^i(R_m) \arrow{ru}[swap]{\varphi^i_m} 
-\end{tikzcd}
-\] 
-for all $i=0, \ldots, d$.
-Set $G_m^i = \Gr_m^{R}(\underline{G}^i)$.
-Then $G_m^i$ is a smooth group scheme over $\Fq$ and $G_m^i(\Fq) = \underline{G}^i(R_m)$, canonically.
-Using Theorem~\ref{thm:geo}, let $\cs{L}^i_m$ be a geometrization of the linear character $\varphi^i_m: G_m^i \to \CC^\times$; so
-\[
-\trFrob{\cs{L}^i_m} = \varphi^i_m.
-\]
-%Recall that the full Greenberg transform $\Gr^{R}(\underline{G}^i)$ is a group scheme over $\Fq$ such that $\Gr^{R}(\underline{G}^i)(\Fq) = \underline{G}^i(\Fq)$, canonically, and comes equipped with a morphism $\Gr^{R}(\underline{G}^i) \to \Gr^{R}_m(\underline{G}^i)$.
-%Let $\cs{L}^i$ be the  Weil sheaf on $\Gr^{R}(\underline{G}^i)$ obtained from $\cs{L}^i_m$ by pullback along $\Gr^{R}(\underline{G}^i) \to \Gr^{R}_{m}(\underline{G}^i)$. 
-%Then $\cs{L}^i$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G}^i)$ from which the quasicharacter $\varphi^i$ may be recovered.
-
-By \cite{lusztig:disconnected1}, there is a virtual Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
-\[
-\trFrob{A} = \trace \varrho_0^\reductive.
-\]
-(This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.)
-Let $A^0$ be the Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
-Then 
-\[
-\trFrob{A^0} = \trace \varrho_0.
-\]
-The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $Q^0 = \Gr^{R}_0(\underline{G}^0)$ \cite{cunningham-roe:13a}*{\S 4.3}.
-With $m\in \NN$ as above, let ${A}_m^0$ be the Weil sheaf on the algebraic group $G_m^i$ obtained by pull-back from $A^0$ along the affine morphism $G_m^i \to Q^0$.
-Factor
-\[
-\begin{tikzcd}
-G^0(\Fq) \arrow{rr}{\trace(\orho^0)} \arrow{rd} && \EE \\
-& G_m^0(\Fq) \arrow{ru}[swap]{\trace(\orho^0)_m} 
-\end{tikzcd}
-\]
-Observe that $\trace(\orho^0)_m$ may be recovered from ${A}_m^0$:
-\[
-\trFrob{{A}^0_m} = \trace(\orho^0)_m
-\]
-%Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{R}(\underline{G}^0) \to \Gr^{R}_{m}(\underline{G}^0)$.
-%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G}^0)$ from which the character of $\orho^0$ may be recovered.
-
-Consider the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ and the Heisenberg-Weil representation $W_{i+1}$ appearing in Section~\ref{ssec:review}.
-Let $\cs{K}^{i+1}$ be the Weil sheaf on the Jacobi group, recalled in Section~\ref{ssec:Jacobi}, such that
-\[
-\trFrob{\cs{K}^{i+1}} = \trace(W_{i+1}).
-\]
-Recall from Section~\ref{ssec:review} that $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ is a quotient of the special fibre of the smooth group scheme $\underline{G}^{i} \ltimes \underline{J}^{i+1}$.
-Let $\cs{K}_0^{i+1}$ be the Weil sheaf on the special fibre of $\underline{G}^{i} \ltimes \underline{J}^{i+1}$ obtained from $W_{i+1}$ by pullback. 
-Let $\cs{K}_m^{i+1}$ be the Weil sheaf on $\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1})$ obtained from $\cs{K}_0^{i+1}$ by pullback along the affine morphism
-$\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1}) \to \Gr^{R}_0(\underline{G}^{i} \ltimes \underline{J}^{i+1})$.
-
-We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{R}_m(\underline{G}^{i})$, for $i=0,\ldots ,d$, recursively, following the construction of the representations $\orho^i$, as reviewed in Section~\ref{ssec:review}.
-First, set $\cs{A}_m^0 = A_m^0$ and note that 
-\[
-\begin{tikzcd}
-G^0(\Fq) \arrow{rr}{\trace(\orho^0)} \arrow{rd} && \EE\\
-& G^0_m(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m^0}} & 
-\end{tikzcd}
-\]
-commutes.
-Now, suppose $\cs{A}^i_m$ on $G_m^i$ is defined such that
-\[
-\begin{tikzcd}
-G^i(\Fq) \arrow{rr}{\trace(\orho^i)} \arrow{rd} && \EE\\
-& G_m^i(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m^i}} & 
-\end{tikzcd}
-\]
-commutes.
-Applying the Greenberg functor $\Gr^{R}_m$, to \eqref{eq:pimodel} gives
-\begin{equation}\label{eq:pi}
-\begin{tikzcd}
-\ && 1 \arrow{d} && \\
-\ && G_m^{i}\times_{G_m} J_m^{i+1} \arrow{d} && \\
-1 \arrow{r} &J_m^{i+1} \arrow{r} & G_m^i \ltimes J_m^{i+1} \arrow{d}{\pi_m^{i+1}} \arrow{r}{p_m^{i}} & G_m^i \arrow{r} & 1\\
-&& G_m^{i+1} \arrow{d} && \\
-&& 1 && 
-\end{tikzcd}
-\end{equation}
-where $J_m^{i+1} \ceq \Gr^{R}_m(\underline{J}^{i+1})$ and $G_m^{i} \ceq \Gr^{R}_m(\underline{G}^{i})$.
-By \cite{bertapelle-gonzales:Greenberg}*{Prop 7.1}, the sequences are exact.
-%Consider $\cs{A}_m^{i}\otimes \cs{L}_m^{i}$ on $G_m^{i}$ and let 
-%\[
-%(p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
-%\]
-%be the Weil sheaf on $G_m^{i}\ltimes J_m^{i+1}$ obtained by pullback along $G_m^{i}\ltimes J_m^{i+1} \to G_m^{i}$.
-Consider the sheaf 
-\[
-\cs{B}_m^{i+1} \ceq \cs{K}_m^{i+1} \otimes (p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
-\]
-on $G_m^{i}\ltimes J_m^{i+1}$.
-Comparing with \eqref{eq:tensor}, we see that $\trFrob{\cs{B}_m^{i+1}}$ is precisely the function obtained by factoring the character of $\orho^{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(R) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R_m)$ using the canonical identification $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R_m)$.
-In particular, $\trFrob{\cs{B}^{i+1}_m}$ is constant on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$, taking the value $\dim \orho^{i+1}$.
-With reference to the morphism $\pi_m^{i+1} : G_m^i \ltimes J_m^{i+1} \to G_m^{i+1}$ from \eqref{eq:pi}, define 
-\[
-\cs{C}_m^{i+1} \ceq (\pi_m^{i+1})_! (\cs{B}_m^{i+1}).
-\]
-%Let $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$ and set $\cs{A}_m^{i+1} \ceq \cs{\tilde A}_m^{i+1}(-n)$ (Tate twist).
-Then
-\begin{eqnarray*}
-\trFrob{\cs{C}^{i+1}_m}(x)
-&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{B}_m^{i+1}}(y).
-\end{eqnarray*}
-Since $\trFrob{\cs{B}^{i+1}_m}$ is constant on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$, it follows that 
-\[
-\trFrob{\cs{C}^{i+1}_m} = n \trFrob{\cs{B}^{i+1}_m}
-\]
-on $G_m^{i+1}(\Fq)$ for $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) \times \dim \orho^{i+1} $.
-Let $\cs{A}_m^{i+1}$ be the \emph{virtual} Weil sheaf on $G_m^i$ given by $\cs{A}_m^{i+1} = \frac{1}{n} \cs{C}_m^{i+1}$. 
-%
-This completes the inductive definition of $\cs{A}_m^i$ so that the following diagram commutes.
-\[
-\begin{tikzcd}
-G^{i+1}(\Fq) \arrow{rr}{\trace(\orho^{i+1})} \arrow{rd} && \EE\\
-& G_m^{i+1}(\Fq)\arrow{ru}[swap]{{\trFrob{\cs{A}_m^{i+1}}} } & 
-\end{tikzcd}
-\]
-
-Now set $\cs{F}^i_m = \cs{A}_m^{i} \otimes \cs{L}_m^i$, for $i=0, \ldots ,d$.
-Then $\cs{F}^i_m$ is a virtual Weil sheaf on $G^i_m = \Gr^{R}_m(\underline{G}^i)$ such that
-\[
-\begin{tikzcd}
-G^i(\Fq) \arrow{rr}{\trace(\orho_i)} \arrow{rd} && \EE\\
-& G_m(\Fq) \arrow{ru}[swap]{\trFrob{\cs{F}^i_m}} & 
-\end{tikzcd}
-\]
-commutes.
-Let $\cs{F}^i$ be the virtual Weil sheaf on the group scheme $G^i= \Gr_{R}(\underline{G}^i)$ obtained by pulling back $\cs{F}_m^i$ along $G^i \to G^i_m$.
-Then 
-\[
-\trFrob{\cs{F}^i} = \trace(\orho_i),
-\] 
-as desired.
-\end{proof}
-
-%\bibliography{bibliography/Biblio}
-% \bib, bibdiv, biblist are defined by the amsrefs package.
-%\iffalse
-
-\begin{bibdiv}
-\begin{biblist}
-
-\bib{berndt-schmidt:98a}{book}{
-      author={Berndt, Rolf},
-      author={Schmidt, Ralf},
-       title={{Elements of the representation theory of the Jacobi group}},
-   publisher={{Birkh\"auser/Springer Basel AG}},
-     address={Basel, Switzerland},
-        date={2011},
-}
-
-\bib{bernstein-lunts:equivariant}{book}{
-   author={Bernstein, Joseph},
-   author={Lunts, Valery},
-   title={Equivariant sheaves and functors},
-   series={Lecture Notes in Mathematics},
-   volume={1578},
-   publisher={Springer-Verlag, Berlin},
-   date={1994},
-   pages={iv+139},
-   isbn={3-540-58071-9},
-%   review={\MR{1299527}},
-}
-
-\bib{bertapelle-gonzales:Greenberg}{unpublished}{
-      author={Bertapelle, Alessandra},
-      author={{Gonz\'ales-Avil\'es}, Cristian~D.},
-       title={{The Greenberg functor revisited}},
-        date={2014},
-         url={http://arxiv.org/abs/1311.0051},
-        note={\href{http://arxiv.org/abs/1311.0051}{arXiv:1311.0051
-  [math.NT]}},
-}
-
-\bib{bushnell-kutzko:98a}{article}{
-      author={Bushnell, Colin},
-      author={Kutzko, Phil},
-       title={{Smooth representations of reductive $p$-adic groups: structure
-  theory via types}},
-        date={1998},
-     journal={Proc. London Math. Soc.},
-      volume={77},
-      number={3},
-       pages={{582\ndash 634}},
-}
-
-\bib{cunningham-roe:13a}{article}{
-author={Cunningham, Clifton},
-author={Roe, David},
-title={From the function-sheaf dictionary to quasicharacters of $p$-adic tori},
-journal = {Journal of the Institute of Mathematics of Jussieu},
-volume = {FirstView},
-number = {6},
-%month = {6},
-year = {2016},
-issn = {1475-3030},
-pages = {1--37},
-%numpages = {37},
-doi = {10.1017/S1474748015000286},
-URL = {http://journals.cambridge.org/article_S1474748015000286},
-}
-
-\bib{deligne:SGA4.5}{book}{
-	address = {Berlin},
-	author = {Pierre Deligne},
-	publisher = {{Springer-Verlag}},
-	series = {Lecture Notes in Mathematics},
-	title = {{Cohomologie \'etale}},
-	volume = {569},
-	year = {1977},
-}
-
-\bib{demazure:SGA3-VIA}{inproceedings}{
-      author={Gabriel, Pierre},
-       title={{Expos\'e VI$_\mathrm{A}$: G\'en\'eralit\'es sur les groupes
-  alg\'ebriques}},
-        date={1970},
-   booktitle={{Sch\'emas en groupes I: Proprietes generales des schemas en
-  groupes}},
-      editor={Demazure, Michel},
-      editor={Grothendieck, Alexander},
-      series={Lecture Notes in Math},
-      volume={151},
-   publisher={Springer-Verlag},
-     address={Berlin},
-}
-
-\bib{EGAIV4}{article}{
-      author={Grothendieck, Alexandre},
-       title={{\'El\'ements de g\'eom\'etrie alg\'ebrique IV. \'Etude locale
-  des sch\'emas et des morphismes de sch\'emas. IV}},
-        date={1967},
-     journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
-      number={32},
-}
-
-\bib{gurevich-hadani:07a}{article}{
-   author={Gurevich, Shamgar},
-   author={Hadani, Ronny},
-   title={The geometric Weil representation},
-   journal={Selecta Math. (N.S.)},
-   volume={13},
-   date={2007},
-   number={3},
-   pages={465--481},
-}
-
-\bib{gurevich-hadani:11a}{unpublished}{
-   author={Gurevich, Shamgar},
-   author={Hadani, Ronny},
-   title={The categorical Weil representation},
-	date={2011},
-        note={\href{http://arxiv.org/abs/1108.0351}{arXiv:1108.0351 [math.RT]}}
-}
-
-\bib{howe:73a}{article}{
-   author={Howe, Roger E.},
-   title={On the character of Weil's representation},
-   journal={Trans. Amer. Math. Soc.},
-   volume={177},
-   date={1973},
-   pages={287--298},
-}
-
-\bib{kamgarpour:09a}{article}{
-      author={Kamgarpour, Masoud},
-       title={{Stacky abelianization of algebraic groups}},
-        date={2009},
-     journal={{Transform. Groups}},
-      volume={14},
-      number={4},
-       pages={825\ndash 846},
-}
-
-\bib{kim:07a}{article}{
-      author={Kim, Ju-Lee},
-       title={Supercuspidal representations: an exhaustion theorem},
-        date={2007},
-     journal={J. Amer. Math. Soc.},
-      volume={20},
-      number={2},
-       pages={273\ndash 320},
-}
-
-\bib{lusztig:85a}{article}{
-      author={Lusztig, George},
-       title={{Character sheaves I}},
-        date={1985},
-     journal={Advances in Math.},
-      volume={56},
-       pages={193\ndash 237},
-}
-
-\bib{lusztig:disconnected1}{article}{
-      author={Lusztig, George},
-       title={{Character sheaves on disconnected groups I}},
-        date={2003},
-     journal={Representation Theory},
-      volume={7},
-       pages={374\ndash 403},
-}
-
-\bib{Vistoli:notes}{article}{
-   author={Vistoli, Angelo},
-   title={Grothendieck topologies, fibered categories and descent theory},
-   conference={
-      title={Fundamental algebraic geometry},
-   },
-   book={
-      series={Math. Surveys Monogr.},
-      volume={123},
-      publisher={Amer. Math. Soc., Providence, RI},
-   },
-   date={2005},
-   pages={1--104},
-%   review={\MR{2223406}},
-}
-
-\bib{yu:01a}{article}{
-      author={Yu, Jiu-Kang},
-       title={Construction of tame supercuspidal representations},
-        date={2001},
-     journal={J. Amer. Math. Soc.},
-      volume={14},
-      number={3},
-       pages={{579\ndash 622}},
-}
-
-\bib{Yu:models}{inproceedings}{
-author={Yu, Jiu-Kang},
-title={{Smooth models associated to concave functions in Bruhat-Tits theory}},
-%date={2015},
-%pages={{579\ndash 622}},
-booktitle={{Autour des sch\'emas en groupes - \'Ecole d'\'et\'e franco-asiatique de g\'eom\'etrie alg\'ebrique et de th\'eorie des nombres. Volume III}},
-      series={Panoramas et synth\`eses},
-      volume={47},
-    publisher={Soci\'et\'e Math\'ematique de France},
-     issn={1272-3835},
-     note={\href{http://smf4.emath.fr/Publications/PanoramasSyntheses/2016/47/html/smf_pano-synth_47_227-258.php}{Panoramas et synth\`eses \textbf{47} (2015), 227--258}}
-
-}
-
-\end{biblist}
-\end{bibdiv}
-%\fi
-
 \end{document}

### 2017-05-10 CJM/letter to CJM.tex
Work on the letter. Also replaced \O with  R.

@@
 \begin{enumerate}
-\item[(i)]
-\item[(ii)]
-\item[(iii)]
-\item[(iv)]
-\item[(v)]
-\item[(vi)]
-\item[(vii)]
+\item[(i)] Thank you for noticing this.
+We referred to the geometric type $\cs{F}^d$ constructed in the paper as a virtual sheaf complex, but this is misleading, since that would reasonably be interpreted as an element in the Grothendieck group of sheaf complexes, while the geometric type is an element of the group obtained by tensoring this Grothendieck group with  $\QQ$.
+To clarify this, we have used the term {\it rational virtual} for formal linear combinations of sheaf complexes, with rational coefficients.
+\item[(ii)] Thank you for pointing this out. We replaced all instances of $\O$ with $R$, and declared $R$ to be the ring of integers of a local ring with finite residue field. 
+\item[(iii)] We fixed this typo.
+\item[(iv)] Yes, there was an isomorphism sign missing here. Fixed now. This sentence is now part of the proof of Corollary 3.7
+\item[(v)] We replaced every instance of $S$ with $\Spec(R)$, which is what we meant by $S$, though we had neglected to say that anywhere.
+\item[(vi)]  The notation conversion chart now has a third column, listing the relevant section in Yu's paper.
+We have also given a precise citation to Yu's paper showing where the "recursive definition" can be found.
+\item[(vii)] Fixed this typo.
 \end{enumerate}

### 2017-05-10 Geometric types.tex
Work on the letter. Also replaced \O with  R.

@@
 %[appearing in Yu type data]
- are on groups of the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
+ are on groups of the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$ [a henselian discrete valuation with finite residue field $\kappa$], and the representations are inflated from $\underline{H}(\kappa)$.
 These results suggest that algebraic geometry and group schemes should play an
@@
 A Yu type datum determines a sequence of representations $\orho_i$ of compact $p$-adic groups $\oK^i$, for $i=0, \ldots, d$, such that $(\oK^d, \rho_d)$ is a type for a supercuspidal representation of a $p$-adic group.
-The main result of \cite{Yu:models} explains how to find, for each $i=0, \ldots, d$, a smooth group scheme $\underline{G}^i$ over the ring $\O$ of integers of the $p$-adic field with $\underline{G}^i(\O)=\,^\circ K^i $.
+Let $R$ be the ring of integers of a local field with finite residue field $k$.
+The main result of \cite{Yu:models} shows how to find, for each $i=0, \ldots, d$, a smooth group scheme $\underline{G}^i$ over the ring $R$ with $\underline{G}^i(R)=\,^\circ K^i $.
 In this paper we show that if the geometric component group of the reductive quotient of the special fiber of the group scheme $\underline{G}^0$ is cyclic, then each representation $\orho_i$ in this sequence can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$,
-where $\cs{F}^i$ is a {\it rational virtual Weil local system} on the Greenberg transform $G^i$ of $\underline{G}^i$, by which we mean an element in the group obtained  by tensoring the Grothendieck group of such local systems with $\QQ$.
-Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(\OO{}) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the rational virtual complex $\cs{F}^i$, we show in Theorem~\ref{thm:geotypes} that
+where $\cs{F}^i$ is a {\it rational virtual} sheaf complex on the Greenberg transform $G^i$ of $\underline{G}^i$, by which we mean an element in the group obtained by tensoring the Grothendieck group of such local systems with $\QQ$.
+Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(R) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the rational virtual complex $\cs{F}^i$, we show in Theorem~\ref{thm:geotypes} that
 \begin{equation}\label{eqn:intro1}
@@
 
-To prove Theorem~\ref{thm:geotypes}, we must find a way to geometrize linear characters of groups of the form $\underline{H}(\O)$, where $\underline{H}$ is a smooth group scheme over $\O$. 
+To prove Theorem~\ref{thm:geotypes}, we must find a way to geometrize linear characters of groups of the form $\underline{H}(R)$, where $\underline{H}$ is a smooth group scheme over $R$. 
 In order to do so in a systematic manner, we begin this paper by describing the function-sheaf dictionary for characters of arbitrary smooth group schemes over finite fields. 
-When coupled with the Greenberg transform, this dictionary will allow for the geometrization of linear characters of $\underline{H}(\O)$.
+When coupled with the Greenberg transform, this dictionary will allow for the geometrization of linear characters of $\underline{H}(R)$.
 
@@
 
-Let $R$ be a complete discrete valuation ring with maximal ideal $\mathfrak{m}$ and perfect residue field $\Fq$. 
+Recall that $R$ is the ring of integers of a local field with finite residue field $k$.
+The maximal idea of $R$ will be denoted by $\mathfrak{m}$. 
 Let $\underline{G}$ be a smooth group scheme over $R$.
@@
 \begin{proposition}\label{prop:quasicharacters}
-With notation as above, suppose $\Fq$ is a finite field.
+%With notation as above, suppose $\Fq$ is a finite field.
 For every quasicharacter character $\varphi : \underline{G}(R) \to \EEx$ there is a Weil sheaf $\cs{L}$ on $G$ such that \[\trFrob{\cs{L}} =  \varphi.\] \end{proposition}
@@
 
-We can now recall how Yu uses all this to construct representations $\orho^i$ of $\oK^i$, for $i=1, \ldots, d$ and the types $(\oK^i,\orho_i)$.
+We can now recall how Yu uses all this to construct representations $\orho^i$ of $\oK^i$, for $i=1, \ldots, d$ and the types $(\oK^i,\orho_i)$.  \todo{Following [these sections] of Yu.}
 The representations $\orho^i$ and $\orho_i$ are defined recursively.

### 2017-05-10 CJM/letter to CJM.tex
letter

@@
 To clarify this, we have used the term {\it rational virtual} for formal linear combinations of sheaf complexes, with rational coefficients.
-\item[(ii)] Thank you for pointing this out. We replaced all instances of $\O$ with $R$, and declared $R$ to be the ring of integers of a local ring with finite residue field. 
+\item[(ii)] We replaced all instances of $\O$ with $R$, and declared $R$ to be the ring of integers of a local ring with finite residue field. 
 \item[(iii)] We fixed this typo.

### 2017-05-10 CJM/letter to CJM.tex
Working on the notation conversion chart.

@@
 To clarify this, we have used the term {\it rational virtual} for formal linear combinations of sheaf complexes, with rational coefficients.
-\item[(ii)] We replaced all instances of $\O$ with $R$, and declared $R$ to be the ring of integers of a local ring with finite residue field. 
+\item[(ii)] We replaced all instances of $\O$ with $R$, and declared $R$ to be the ring of integers of a local ring with finite residue field $k$. 
 \item[(iii)] We fixed this typo.
 \item[(iv)] Yes, there was an isomorphism sign missing here. Fixed now. This sentence is now part of the proof of Corollary 3.7
-\item[(v)] We replaced every instance of $S$ with $\Spec(R)$, which is what we meant by $S$, though we had neglected to say that anywhere.
+\item[(v)] We replaced every instance of $S$ with $\Spec{R}$, which is what we meant by $S$, though we had neglected to say that.
 \item[(vi)]  The notation conversion chart now has a third column, listing the relevant section in Yu's paper.

### 2017-05-10 Geometric types.tex
Working on the notation conversion chart.

@@
 }
-\usepackage[margin=3.5cm]{geometry}
+%\usepackage[margin=4.3cm]{geometry}
 %\renewcommand{\baselinestretch}{1.0}
@@
 The main result of \cite{Yu:models} shows how to find, for each $i=0, \ldots, d$, a smooth group scheme $\underline{G}^i$ over the ring $R$ with $\underline{G}^i(R)=\,^\circ K^i $.
-In this paper we show that if the geometric component group of the reductive quotient of the special fiber of the group scheme $\underline{G}^0$ is cyclic, then each representation $\orho_i$ in this sequence can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$,
+In this paper we show that if the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic, then each representation $\orho_i$ in this sequence can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$,
 where $\cs{F}^i$ is a {\it rational virtual} sheaf complex on the Greenberg transform $G^i$ of $\underline{G}^i$, by which we mean an element in the group obtained by tensoring the Grothendieck group of such local systems with $\QQ$.
@@
 \hline
-\text{this paper} & \text{Yu, Jiu-Kang, {\it Construction of tame supercuspidal representations}} & \cite{yu:01a} \\
+\text{this paper} & \text{Jiu-Kang Yu, {\it Construction of tame}} & \cite{yu:01a} \\
+ & \text{{\it supercuspidal representations}} &  \\
 \hline
-%$\oK^0$ & $\,^\circ K^0 = G^0(F)_y$ & \cite{yu:01a}*{\S 15} \\
-%$\oK^{i+1}$ & $\,^\circ K^{i+1} = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, \ldots, s_{i})}$ & \cite{yu:01a}*{\S 15} \\
-%$\oK^0$ & $\,^\circ K^0 = G^0(F)_y$ & \cite{yu:01a}*{\S 15} \\
-%$\orho^0$ & $\,^\circ \rho^0$\\% \cite{yu:01a}*{\S 15} \\
-%$\orho^{i+1}$ & $\,^\circ \rho^{i+1}$ &  \cite{yu:01a}*{\S 15} \\
+$\oK^0$ & $\,^\circ K^0 = G^0(F)_y$ & \cite{yu:01a}*{\S 15} \\
+$\oK^{i+1}$ & $\,^\circ K^{i+1} = (\,^\circ K^0) \vec{G}^{(i+1)}(F)_{y,(0, s_0, \ldots, s_{i})}$ & \cite{yu:01a}*{\S 15} \\
+$\orho^0$ & $\,^\circ \rho^0$ & \cite{yu:01a}*{\S 15} \\
+$\orho^{i+1}$ & $\,^\circ \rho^{i+1}$ &  \cite{yu:01a}*{\S 15} \\
 $\varphi^i$ & $\phi_i\vert_{\,^\circ K^i }$ & \\
@@
 $V_{i+1}^\sharp$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi}_i\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ & \\
-%$H^{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi_i}\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ & \\
 $Z_{i+1}$ & $\ker(V_{i+1}^\sharp\to V_{i+1})$ & \cite{yu:01a}*{\S 11} \\
-%$(f_{j+1}, j_{i+1})$ & $(f,j)$ \cite{yu:01a}*{\S 11} \\
-%$\langle\ ,\ \rangle_{i+1}$ & $\langle\ ,\ \rangle$, \cite{yu:01a}*{\S 11} 
+$(f_{j+1}, j_{i+1})$ & $(f,j)$ & \cite{yu:01a}*{\S 11} \\
+$\langle\ ,\ \rangle_{i+1}$ & $\langle\ ,\ \rangle$ & \cite{yu:01a}*{\S 11} \\
 \hline

### 2017-05-11 CJM/letter to CJM.tex
Done for this evening. Maybe.

@@
 \begin{enumerate}
-\item[(1)]
-\item[(2)]
+\item[(1)] We are extremely grateful for this observation.
+We had made a mistake.
+Fortunately, the correction had the effect of simplifying the constructions and did not add to the length of the paper.
+\item[(2)] It is quite true that it would be possible to view Section 4 as an application of our earlier paper, bypassing the the first part of the paper under review.
+Our main motivation for Section 1--3 was twofold: to address the `defect' in the dictionary from our earlier paper; and to extend that dictionary, as it pertains to characters, to non-commutative groups.
+(Although it wasn't our motivation, we were also happy to find an alternative to the stacky abelianization of Kamgarpour.) We have added a comment to this effect after Theorem 3.12, in the hopes that it will clarify this point.
 \end{enumerate}

### 2017-05-11 Geometric types.tex
Done for this evening. Maybe.

@@
 We are extremely grateful to Loren Spice for explaining Yu's types for supercuspidal representations.
-We also thank Masoud Kamgarpour for helpful conversations.
+We also thank Masoud Kamgarpour for helpful conversations, and the anonymous referee of this paper, would pointed out an error in an earlier version of the paper and helped us clarify several points.
 
@@
 
+%\begin{remark}\label{rem:dictionary}
+Observe that $\CCS(G)$ is a subcategory of $\CS\ab(G)$, by Definition~\ref{def:CCS}, and that Definition~\ref{def:CSab} makes it clear that there is a forgetful functor $\CS\ab(G) \to \CS(G)$, and also a forgetful functor $\CS(G)\to \Loc(G)$.
+Consequently, while the category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the sense explained in Theorem~\ref{thm:geo}, it is also true that $\CS(G)$, and even $\Loc(G)$ as introduces in Section~\ref{ssec:equivariant1}, geometrizes characters of $G(\Fq)$ in the sense that for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $\cs{L}$ in $\Loc(G)$ such that $\trFrob{\cs{L}} = \chi$.
+The point of category $\CCS(G)$ is to make this translation from characters $\chi$ to Weil local systems $\cs{L}$ as precise as possible.
+Theorem~\ref{thm:geo} shows that benefit of equipping Weil local systems $\cs{L}$ with the extra structure $\mu$ and $\beta$ makes the defect in this dictionary as small as it could possibly be, namely, the image $\Delta_G$ of the connecting homomorphism $G\ab(\Fq) \to \Hh^1(\Fq, G\der)$.
+%\end{remark}
+
 \begin{remark}
@@
 $\orho^{i+1}$ & $\,^\circ \rho^{i+1}$ &  \cite{yu:01a}*{\S 15} \\
-$\varphi^i$ & $\phi_i\vert_{\,^\circ K^i }$ & \\
-$J_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}$ &  \\
-$V_{i+1}$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ (G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}$ & \\ 
-$V_{i+1}^\sharp$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi}_i\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ & \\
+$\varphi^i$ & $\phi_i\vert_{\,^\circ K^i }$ & \cite{yu:01a}*{\S 3}\\
+$J_{i+1}$ & $J^{i+1} = (G^i,G^{i+1})(F)_{y, (r_i, s_i)}$ & \cite{yu:01a}*{\S 3} \\
+$V_{i+1}$ & $J^{i+1}/J^{i+1}_+ = (G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ (G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}$ & \cite{yu:01a}*{\S 3} \\ 
+$V_{i+1}^\sharp$ & $(G^i,G^{i+1})(F)_{y, (r_i, s_i)}/ \ker(\widehat{\phi}_i\vert_{(G^i,G^{i+1})(F)_{y, (r_i, s_i^+)}})$ &  \cite{yu:01a}*{\S 4} \\
 $Z_{i+1}$ & $\ker(V_{i+1}^\sharp\to V_{i+1})$ & \cite{yu:01a}*{\S 11} \\
@@
 
-We can now recall how Yu uses all this to construct representations $\orho^i$ of $\oK^i$, for $i=1, \ldots, d$ and the types $(\oK^i,\orho_i)$.  \todo{Following [these sections] of Yu.}
+We can now recall how Yu uses all this to construct representations $\orho^i$ of $\oK^i$, for $i=1, \ldots, d$ and the types $(\oK^i,\orho_i)$; see \cite{yu:01a}*{\S\S 4, 15}.
 The representations $\orho^i$ and $\orho_i$ are defined recursively.
@@
 Then $G_m^i$ is a smooth group scheme over $\Fq$ and $G_m^i(\Fq) = \underline{G}^i(R_m)$, canonically.
-Using Theorem~\ref{thm:geo}, let $\cs{L}^i_m$ be a geometrization of the linear character $\varphi^i_m: G_m^i \to \CC^\times$; so
+Using Theorem~\ref{thm:geo}, let $\cs{L}^i_m$ be a geometrization of the linear character $\varphi^i_m: G_m^i(k) \to \CC^\times$; so
 \[

### 2017-05-11 CJM/letter to CJM.tex
*Now* I'm done. Probably

@@
 Fortunately, the correction had the effect of simplifying the constructions and did not add to the length of the paper.
+\todo{Should we say more?}
 \item[(2)] It is quite true that it would be possible to view Section 4 as an application of our earlier paper, bypassing the the first part of the paper under review.
@@
 \item[(vi)]  The notation conversion chart now has a third column, listing the relevant section in Yu's paper.
-We have also given a precise citation to Yu's paper showing where the "recursive definition" can be found.
+In fact, we have expanded this chart from 5 to 11 rows, to make the comparison with Yu's paper easier.
+We have also given a precise citation to Yu's paper showing where the "recursive construction" can be found, there.
 \item[(vii)] Fixed this typo.

### 2017-05-11 Geometric types.tex
Fixing typos, adding dashed arrows, some minor changes

@@
 \end{align*}
-Define $s : G\to G\der\times G$ by $s(g) = (1,g)$.
-A $G\der$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
+A $G\der$-equivariant Weil local system on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
 \[
@@
 \begin{tikzcd}
-\ &  \arrow{dl}{n\circ b_1 = n\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
+\ &  \arrow{dl}{n\circ b_1 = n\circ b_2}  b_2^*  n^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = n\circ b_3} & \\
 b_1^* n^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* n^*\, \mathcal{L} \\
@@
 \begin{proof}
-Let $i\der : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\der\times G$ by $j(h) = (h,1_G)$. 
+Let $i\der : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\der\times G$ by $j(h) = (h,1)$. 
 If $(\cs{L},\mu,\nu)\in \CS\der(G)$ then $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism. 
-This defines a functor on objects by
+This defines a functor by
 \[
@@
 \]
-and on morphisms, trivially.
+on objects and trivially on morphisms.
 It is easy to verify that morphisms that commute with $\mu$ and $\nu$ also commute with $\mu$ and $j^*(\nu)$.
-This functor is an equivalence. Its adjoint is given as follows.
+This functor is an equivalence; its adjoint is given as follows.
 Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i\der(h),g)$.
@@
 \begin{tikzcd}
-& n^* \cs{L} \arrow{dl}{m\circ k = n} \arrow{r}{\nu} & p^*\cs{L} &  \\ 
+& n^* \cs{L} \arrow{dl}{m\circ k = n} \arrow[dashed]{r}{\nu} & p^*\cs{L} &  \\ 
 k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
@@
 The dashed arrows both satisfy \eqref{E1} and \eqref{E2} as they apply here.
-This diagram also shows that $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of equivariant sheaves, since it satisfies \eqref{E3} as it applies here.
+This diagram also shows that $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of $G\der^2$-equivariant local systems, since it satisfies \eqref{E3} as it applies here.
 \end{proof}
@@
 \begin{proof}
-The quotient $q : G \to G\ab$ is an $G\der$-torsor in the fppf topology by \cite{demazure:SGA3-VIA}*{Thm. 3.2}, and thus an $G\der$-torsor in the fpqc topology.
+The quotient $q : G \to G\ab$ is an $G\der$-torsor in the fppf topology by \cite{demazure:SGA3-VIA}*{Thm. 3.2}, and thus a $G\der$-torsor in the fpqc topology.
 The lemma is now a result from descent theory, arguing as in \cite{Vistoli:notes}*{Theorem 4.46} for example. 
@@
 Then $(\cs{L}, \mu,\nu)$ is an object in $\CS\der(G)$.
-If $\alpha : (\cs{L}\ab,\mu\ab) \to (\cs{L}\ab',\mu\ab')$ is a morphism in $\CS(G\ab)$, 
-then $q^*(\alpha\ab) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha$ is a morphism in $\CS(G)$.
+If $\alpha\ab : (\cs{L}\ab,\mu\ab) \to (\cs{L}\ab',\mu\ab')$ is a morphism in $\CS(G\ab)$, 
+then $q^*(\alpha\ab) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha = q^*(\alpha\ab)$ is a morphism in $\CS(G)$.
 These simple observations define the comparison functor
@@
 \begin{tikzcd}
-(m^2)^* (m^*\cs{L}) \arrow{d}{(m^2)^*\mu} \arrow{rr}{\mu_m^2} && m^*\cs{L} \boxtimes m^*\cs{L}\\
+(m^2)^* (m^*\cs{L}) \arrow{d}{(m^2)^*\mu} \arrow[dashed]{rr}{\mu_m^2} && m^*\cs{L} \boxtimes m^*\cs{L}\\
  (m^2)^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & (m^2)^*(p_1)^*\cs{L} \otimes (m^2)^*(p_2)^*\cs{L} \arrow{r} & (p^2_1)^*m^*\cs{L} \otimes (p^2_2)^*m^*\cs{L} \arrow[equal]{u}
@@
 \begin{tikzcd}
-(m^*\cs{L})\vert_{G^2\der} \arrow{d}{\mu\vert_{G^2\der}} \arrow{r}{\beta^2_m} & (\EE)_{G^2\der}\\
+(m^*\cs{L})\vert_{G^2\der} \arrow{d}{\mu\vert_{G^2\der}} \arrow[dashed]{r}{\beta^2_m} & (\EE)_{G^2\der}\\
 (\cs{L}\boxtimes\cs{L})\vert_{G^2\der} \arrow[equal]{r} & (\cs{L}\vert_{G\der})\boxtimes(\cs{L}\vert_{G\der}) \arrow{u}{\beta\boxtimes\beta}.
@@
 We have just seen that $\CS\ab(G\ab)$ is equivalent to $\CS(G\ab)$.
-By Proposition~\ref{prop:CSGabab}, pullback along the abelianization $q : G \to G\ab$ induces an equivalence $q^*\ab : \CS\ab(G)\to CS\ab(G)$.
+By Proposition~\ref{prop:CSGabab}, pullback along the abelianization $q : G \to G\ab$ induces an equivalence $q^*\ab : \CS(G\ab)\to \CS\ab(G)$.
 Thus, the functor $\CS\ab(G\ab)\to \CS\ab(G)$ induced by pullback along $q$ is an equivalence.
@@
 Observe that $\CCS(G)$ is a subcategory of $\CS\ab(G)$, by Definition~\ref{def:CCS}, and that Definition~\ref{def:CSab} makes it clear that there is a forgetful functor $\CS\ab(G) \to \CS(G)$, and also a forgetful functor $\CS(G)\to \Loc(G)$.
-Consequently, while the category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the sense explained in Theorem~\ref{thm:geo}, it is also true that $\CS(G)$, and even $\Loc(G)$ as introduces in Section~\ref{ssec:equivariant1}, geometrizes characters of $G(\Fq)$ in the sense that for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $\cs{L}$ in $\Loc(G)$ such that $\trFrob{\cs{L}} = \chi$.
-The point of category $\CCS(G)$ is to make this translation from characters $\chi$ to Weil local systems $\cs{L}$ as precise as possible.
-Theorem~\ref{thm:geo} shows that benefit of equipping Weil local systems $\cs{L}$ with the extra structure $\mu$ and $\beta$ makes the defect in this dictionary as small as it could possibly be, namely, the image $\Delta_G$ of the connecting homomorphism $G\ab(\Fq) \to \Hh^1(\Fq, G\der)$.
+Consequently, while the category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the sense of Theorem~\ref{thm:geo}, it is also true that $\CS(G)$ and even $\Loc(G)$
+geometrize characters of $G(\Fq)$ in the sense that for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $\cs{L}$ in $\Loc(G)$ such that $\trFrob{\cs{L}} = \chi$.
+The purpose of the category $\CCS(G)$ is to make this translation from characters $\chi$ to Weil local systems $\cs{L}$ as precise as possible by making $\TrFrob{}$ as close to an isomorphism as possible.
 %\end{remark}

### 2017-05-11 Geometric types.tex
Getting ready to talk to David

@@
 %[appearing in Yu type data]
- are on groups of the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over $\mathcal{O}$ [a henselian discrete valuation with finite residue field $\kappa$], and the representations are inflated from $\underline{H}(\kappa)$.
+ are on groups of the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over [a henselian discrete valuation ring with finite residue field $\kappa$] $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
 These results suggest that algebraic geometry and group schemes should play an
@@
 The main result of \cite{Yu:models} shows how to find, for each $i=0, \ldots, d$, a smooth group scheme $\underline{G}^i$ over the ring $R$ with $\underline{G}^i(R)=\,^\circ K^i $.
-In this paper we show that if the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic, then each representation $\orho_i$ in this sequence can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$,
-where $\cs{F}^i$ is a {\it rational virtual} sheaf complex on the Greenberg transform $G^i$ of $\underline{G}^i$, by which we mean an element in the group obtained by tensoring the Grothendieck group of such local systems with $\QQ$.
+The geometrization of the Yu type datum uses Lusztig's theory of character sheaves on reductive groups over finis fields, so it is necessary to assume that the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic, in order to bring his work to bear.
+\todo{I made some changes here.
+Discuss.}
+Under this assumption we show how each representation $\orho_i$, for each  $i=0, \ldots , d$, can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$, where $\cs{F}^i$ is a {\it rational virtual} sheaf complex on the Greenberg transform $G^i$ of $\underline{G}^i$, by which we mean $\cs{F}^i$ is an element in the group obtained by tensoring the Grothendieck group of such sheaves with $\QQ$.
 Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(R) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the rational virtual complex $\cs{F}^i$, we show in Theorem~\ref{thm:geotypes} that
@@
 It follows that every object in $\CCS(G)$ determines a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}.
-Of course, the sheaves arising in this way represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields:
-they are precisely those needed to describe one-dimensional characters of such groups.
+Of course, the sheaves arising in this way represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields, but they are precisely those needed to describe one-dimensional characters of such groups.
+\todo{}
 
@@
 We are extremely grateful to Loren Spice for explaining Yu's types for supercuspidal representations.
-We also thank Masoud Kamgarpour for helpful conversations, and the anonymous referee of this paper, would pointed out an error in an earlier version of the paper and helped us clarify several points.
+We also thank Masoud Kamgarpour for helpful conversations, and the anonymous referee of this paper, would pointed out an error in an earlier version and helped us clarify several points.
 
@@
 \]
-commutes.  While these conventions simplify notation considerably, they are not consistent with \cite{cunningham-roe:13a}.
+commutes.  
+These conventions simplify notation considerably, but they were not employed in \cite{cunningham-roe:13a}. \todo{}
 
@@
 
-By \cite{lusztig:disconnected1}, there is a rational virtual Weil sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a rational virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
+By \cite{lusztig:disconnected1}, there is a rational virtual Weil sheaf complex $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a rational virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
 \[
@@
 (This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.)
+We  remark that \todo{}
+
 Let $A^0$ be the Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.

### 2017-05-11 Geometric types.tex
While speaking with David

@@
 The main result of \cite{Yu:models} shows how to find, for each $i=0, \ldots, d$, a smooth group scheme $\underline{G}^i$ over the ring $R$ with $\underline{G}^i(R)=\,^\circ K^i $.
-The geometrization of the Yu type datum uses Lusztig's theory of character sheaves on reductive groups over finis fields, so it is necessary to assume that the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic, in order to bring his work to bear.
-\todo{I made some changes here.
-Discuss.}
-Under this assumption we show how each representation $\orho_i$, for each  $i=0, \ldots , d$, can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$, where $\cs{F}^i$ is a {\it rational virtual} sheaf complex on the Greenberg transform $G^i$ of $\underline{G}^i$, by which we mean $\cs{F}^i$ is an element in the group obtained by tensoring the Grothendieck group of such sheaves with $\QQ$.
+The geometrization of the Yu type datum uses Lusztig's theory of character sheaves on reductive groups over finite fields, so it is necessary to assume that the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic, in order to bring his work to bear.
+Under this assumption we show how each representation $\orho_i$ can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$, where $\cs{F}^i$ is a {\it rational virtual} sheaf complex on the Greenberg transform $G^i$ of $\underline{G}^i$, by which we mean $\cs{F}^i$ is an element in the group obtained by tensoring the Grothendieck group of such sheaves with $\QQ$.
 Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(R) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the rational virtual complex $\cs{F}^i$, we show in Theorem~\ref{thm:geotypes} that
@@
 Of course, the sheaves arising in this way represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields, but they are precisely those needed to describe one-dimensional characters of such groups.
-\todo{}
 
@@
 commutes.  
-These conventions simplify notation considerably, but they were not employed in \cite{cunningham-roe:13a}. \todo{}
+These conventions simplify notation considerably, but they were not employed in \cite{cunningham-roe:13a}.
 
@@
 notion of character sheaf, even in the commutative case, we instead add restrictions
-to the definition of commutative character sheaf and leave the definition of $G\der$ unchanged, allowing us to use the schematic abelianization of $G$ in the geometrization of characters of $G(\Fq)$; see Theorem~\ref{thm:geo}.
+to the definition of commutative character sheaf and leave the definition of $G\der$ unchanged, allowing us to use the schematic abelianization of $G$ in the geometrization of characters of $G(\Fq)$.
+
+We begin this section with the main definition in this paper - the category $\CCS(G)$ of commutative character sheaves, Definition~\ref{def:CCS}. 
+This definition is delicate and somewhat technical, but it is vindicated in Theorem~\ref{thm:Gab} which shows that $\CCS(G)$ is equivalent to the category of commutative character sheaves on the abelianization $G\ab$ of $G$.
+To prove Theorem~\ref{thm:Gab} we use descent theory in Section~\ref{ssec:descent}, in the process giving insight into Definition~\ref{def:CCS}. 
+Section~\ref{sec:noncom} concludes with Theorem~\ref{thm:geo}, showing that the dictionary from $\CCS(G)$ to characters of $G(k)$ is as precise as possible.
 
@@
 
-\subsection{Descent}
+\subsection{Descent}\label{ssec:descent}
 
@@
 \begin{tikzcd}[column sep=40]
-n^*\cs{L} \arrow[equal]{d} \arrow{r}{\nu(\cs{L}\ab)} &  \arrow[equal]{d} p^*\cs{L} \\
+n^*\cs{L} \arrow[equal]{d} \arrow[dashed]{r}{\nu(\cs{L}\ab)} &  \arrow[equal]{d} p^*\cs{L} \\
 n^* ( q^*\cs{L}\ab) \arrow{r}{q\circ n = q\circ p}
@@
 \begin{tikzcd}
-1 \arrow{r} & J_{i+1} \arrow{d} \arrow{r} & \oK^i \ltimes J_{i+1} \arrow{d}{h_{i+1}} \arrow{r}{p_i} & \oK^i \arrow{r} \arrow{d}{f_i} & 1\\ 
+1 \arrow{r} & J_{i+1} \arrow{d} \arrow{r} & \oK^i \ltimes J_{i+1} \arrow[dashed]{d}{h_{i+1}} \arrow{r}{p_i} & \oK^i \arrow{r} \arrow{d}{f_i} & 1\\ 
 1 \arrow{r} & V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \ltimes V_{i+1}^\sharp \arrow{r} & \Sp(V_{i+1}) \arrow{r} & 1
@@
 
-By \cite{lusztig:disconnected1}, there is a rational virtual Weil sheaf complex $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a rational virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
+By \cite{lusztig:disconnected1}, there is a rational virtual Weil character sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a rational virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
 \[
@@
 (This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.)
-We  remark that \todo{}
-
+%
 Let $A^0$ be the Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
@@
 Factor
-\[
+\begin{equation}\label{eqn:tracerho}
 \begin{tikzcd}
@@
 \end{tikzcd}
-\]
+\end{equation}
 Observe that $\trace(\orho^0)_m$ may be recovered from ${A}_m^0$:
@@
 We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{R}_m(\underline{G}^{i})$, for $i=0,\ldots ,d$, recursively, following the construction of the representations $\orho^i$, as reviewed in Section~\ref{ssec:review}.
-First, set $\cs{A}_m^0 = A_m^0$ and note that 
-\[
-\begin{tikzcd}
-G^0(\Fq) \arrow{rr}{\trace(\orho^0)} \arrow{rd} && \EE\\
-& G^0_m(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m^0}} & 
-\end{tikzcd}
-\]
-commutes.
+First, set $\cs{A}_m^0 = A_m^0$ and note that \eqref{eqn:tracerho} commutes with $\trace(\orho^0)_m$ replaced by $\trFrob{\cs{A}_m^0}$.
+%\[
+%\begin{tikzcd}
+%G^0(\Fq) \arrow{rr}{\trace(\orho^0)} \arrow{rd} && \EE\\
+%& G^0_m(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m^0}} & 
+%\end{tikzcd}
+%\]
+%commutes.
 Now, suppose $\cs{A}^i_m$ on $G_m^i$ is defined such that

### 2017-05-11 CJM/letter to CJM.tex
Added todonotes for CJM letter
Letter

@@
 \usepackage{tikz-cd}
+\usepackage{todonotes}
 
@@
 
+\noindent\textbf{Regarding CJM: MS 1903 (Commutative character sheaves and geometric types for supercuspidal representations)} % subject of the letter
+
+\bigskip
+
 \noindent{Dear Isolde Prince,}
@@
 
-{Regarding CJM: MS 1903 (Commutative character sheaves and geometric types for supercuspidal representations)} % subject of the letter
+Thank you for sending us the review from the referee.
+We have now addressed all the comments, as summarized below.
+Allow us also to express our gratitude for such  insightful remarks and helpful comments.
+
+Best  regards,
+
+Clifton and David
+
+\bigskip
 
@@
 Fortunately, the correction had the effect of simplifying the constructions and did not add to the length of the paper.
-\todo{Should we say more?}
+We hope this change is clear in the attached version.
 \item[(2)] It is quite true that it would be possible to view Section 4 as an application of our earlier paper, bypassing the the first part of the paper under review.

### 2017-05-11 Geometric types.tex
changes around def 3.1

@@
 In order to get character sheaves that correspond to characters in $G(k)^*$, we must discard those
-character sheaves whose restriction to the derived subgroup is nontrivial.  Moreover, the isomorphism
-with the trivial sheaf on the derived subgroup will be important in relating to sheaves on the abelianization,
-motivating the following category.
+character sheaves whose restriction to the derived subgroup is nontrivial.
 %
@@
 not necessarily commutative.  
+We define the following category to track the trivialization on the derived subgroup;
+commutative character sheaves will then be defined as a subcategory.
 
@@
 
-%
-We will define commutative character sheaves as a subcategory of $\CSab(G)$.
-%We may now define commutative character sheaves on $G$.
-%
-Every $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows.
+The reason for tracking $\beta$ is that it determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows,
+which will replace the $\xi$ of Definition \ref{def:CCScom}.
 Let $i : G \to G$ be inversion and $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.

### 2017-05-11 CJM/letter to CJM.tex
Spacing,  Tr.

@@
 Allow us also to express our gratitude for such  insightful remarks and helpful comments.
+\medskip
 
 Best  regards,
+\bigskip
 
@@
 \item[(2)] It is quite true that it would be possible to view Section 4 as an application of our earlier paper, bypassing the the first part of the paper under review.
-Our main motivation for Section 1--3 was twofold: to address the `defect' in the dictionary from our earlier paper; and to extend that dictionary, as it pertains to characters, to non-commutative groups.
+Our main motivation for Sections 1--3 was twofold: to address the `defect' in the dictionary from our earlier paper; and to extend that dictionary, as it pertains to characters, to non-commutative groups.
 (Although it wasn't our motivation, we were also happy to find an alternative to the stacky abelianization of Kamgarpour.) We have added a comment to this effect after Theorem 3.12, in the hopes that it will clarify this point.

### 2017-05-11 Geometric types.tex
Spacing,  Tr.

@@
 geometrize characters of $G(\Fq)$ in the sense that for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $\cs{L}$ in $\Loc(G)$ such that $\trFrob{\cs{L}} = \chi$.
-The purpose of the category $\CCS(G)$ is to make this translation from characters $\chi$ to Weil local systems $\cs{L}$ as precise as possible by making $\TrFrob{}$ as close to an isomorphism as possible.
+The purpose of the category $\CCS(G)$ is to make this translation from characters $\chi$ to Weil local systems $\cs{L}$ as precise as possible by making $\TrFrob{} : \CCSiso{G} \to G(k)^*$ as close to an isomorphism as possible.
 %\end{remark}

### 2017-05-11 CJM/letter to CJM.tex
Push to David

@@
 We had made a mistake.
-Fortunately, the correction had the effect of simplifying the constructions and did not add to the length of the paper.
-We hope this change is clear in the attached version.
+Previously, we considered a category of triples $(\cs{L},\mu,\nu)$ with a compatibility condition on $\mu : a^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu : n^* \cs{L}\to (\EE)_{H}\boxtimes \cs{L}$.
+But that compatibility condition had the error built into it that was noticed in the review.
+In the process of fixing the error, we found that it was more natural to drop the compatibility condition entirely and replace $\mu$ as above with $\mu : n^*\cs{L} \to \cs{L}\boxtimes\cs{L}$, where $n: G\der\times G\to G$ is the restriction of the group action from $G\times G$ to $G\der\times G$.
+Also, in an effort to improve clarity of presentation of Section 3, we moved the proofs from the last subsection back into the flow of the paper, made some notational changes, and added exposition.
+Fortunately, this had the effect of simplifying the constructions and did not add to the length of the paper. 
 \item[(2)] It is quite true that it would be possible to view Section 4 as an application of our earlier paper, bypassing the the first part of the paper under review.

### 2017-05-11 Geometric types.tex
Push to David

--- 2017-05-11 Geometric types.tex
@@
 In this section we give an equivalence of categories between $\CS(G\ab)$ and $\CSab(G)$ and use it to describe
-the pullback functor $q^* : \CS(G\ab) \to \CS(G)$ in terms of the forgetful functor $\CSab(G) \to \CS(G)$.
+the pullback functor $q^* : \CS(G\ab) \to \CS(G)$ in terms of the forgetful functor $\CSab(G) \to \CS(G)$, where $q : G\to G\ab$ is the abelianization quotient with kernel $G\der$.
 But first, in order to study commutative character sheaves, we need some auxiliary categories.
@@
 
+We may now relate $\CSab(G)$ to $\CS(G\ab)$.
+To do so, we use decent along $q : G \to G\ab$.
+
 If $\cs{L}\ab\in \Loc(G\ab)$ then $q^*\cs{L}\ab\in \Loc(G)$ comes equipped with a canonical isomorphism $\nu(\cs{L}\ab) : n^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of isomorphisms.
@@
 \]
-given on objects by $(\cs{L}\ab,\mu\ab) \mapsto (q^*\cs{L}\ab, (q^2)^* \mu\ab)$; this is an instance of \cite{cunningham-roe:13a}*{Lemma 1.4}.
+given on objects by $(\cs{L}\ab,\mu\ab) \mapsto (q^*\cs{L}\ab, (q^2)^* \mu\ab)$; this is an instance of \cite{cunningham-roe:13a}*{Lem. 1.4}.
 To see that $(q^*\cs{L}\ab, (q^2)^* \mu\ab)$ is indeed a linear character sheaf on $G$,
@@
 The definition of $q\ab^* : \CS(G\ab)\to \CS\der(G)$ will be revisited in the proof of the following result.
-We may now relate $\CSab(G)$ to $\CS(G\ab)$ via the quotient map $q : G \to G\ab$.
 
@@
 
+We are now in a position to prove that commutative character sheaves on $G$ match perfectly with commutative character sheaves on $G\ab$.
 We start with a method that will allow us to situate the diagram in Definition \ref{def:CCS} within $\CSab(G^2)$.
@@
 
+Corollary~\ref{cor:Gab} shows that commutative character sheaves on $G$ provide a natural geometrization of characters of $G\ab(k)$.
+In Theorem~\ref{thm:geo} we take this one small step further by exploring the relation between characters of $G(k)$ and objects in $\CCS(G)$.
+
 \begin{theorem}\label{thm:geo}
@@
 geometrize characters of $G(\Fq)$ in the sense that for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $\cs{L}$ in $\Loc(G)$ such that $\trFrob{\cs{L}} = \chi$.
-The purpose of the category $\CCS(G)$ is to make this translation from characters $\chi$ to Weil local systems $\cs{L}$ as precise as possible by making $\TrFrob{}$ as close to an isomorphism as possible.
+However, category $\CCS(G)$ has made this translation from characters $\chi$ to Weil local systems $\cs{L}$ as precise as possible by making $\TrFrob{} : \CCSiso{G} \to G(k)^*$ as close to an isomorphism as possible.
 %\end{remark}

### 2017-05-11 Geometric types.tex
Delete response to reviewer

@@
 defined by pullback along $q$, the square in the statement of the theorem commutes.
-Finally, $\TrFrob{} : \CCSiso{G\ab} \to G\ab(k)^*$ is an isomorphism by Theorem \ref{thm:trfrobiso}.
+Finally, $\TrFrob{} : \CCSiso{G\ab} \to G\ab(k)^*$ is an isomorphism by Corollary \ref{cor:Gab}.
 \end{proof}
-
-%\begin{remark}\label{rem:dictionary}
-Observe that $\CCS(G)$ is a subcategory of $\CS\ab(G)$, by Definition~\ref{def:CCS}, and that Definition~\ref{def:CSab} makes it clear that there is a forgetful functor $\CS\ab(G) \to \CS(G)$, and also a forgetful functor $\CS(G)\to \Loc(G)$.
-Consequently, while the category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the sense of Theorem~\ref{thm:geo}, it is also true that $\CS(G)$ and even $\Loc(G)$
-geometrize characters of $G(\Fq)$ in the sense that for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $\cs{L}$ in $\Loc(G)$ such that $\trFrob{\cs{L}} = \chi$.
-However, category $\CCS(G)$ has made this translation from characters $\chi$ to Weil local systems $\cs{L}$ as precise as possible by making $\TrFrob{} : \CCSiso{G} \to G(k)^*$ as close to an isomorphism as possible.
-%\end{remark}
 

### 2017-05-11 CJM/letter to CJM.tex
Move comment to letter

@@
 Our main motivation for Sections 1--3 was twofold: to address the `defect' in the dictionary from our earlier paper; and to extend that dictionary, as it pertains to characters, to non-commutative groups.
-(Although it wasn't our motivation, we were also happy to find an alternative to the stacky abelianization of Kamgarpour.) We have added a comment to this effect after Theorem 3.12, in the hopes that it will clarify this point.
+(Although it wasn't our motivation, we were also happy to find an alternative to the stacky abelianization of Kamgarpour.)
+
+Observe that $\CCS(G)$ is a subcategory of $\CS\ab(G)$, by Definition~3.2, and that Definition~3.1 makes it clear that there is a forgetful functor $\CS\ab(G) \to \CS(G)$, and also a forgetful functor $\CS(G)\to \Loc(G)$.
+Consequently, while the category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the sense of Theorem~3.12, it is also true that $\CS(G)$ and even $\Loc(G)$
+geometrize characters of $G(\Fq)$ in the sense that for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $\cs{L}$ in $\Loc(G)$ such that $\trFrob{\cs{L}} = \chi$.
+However, category $\CCS(G)$ has made this translation from characters $\chi$ to Weil local systems $\cs{L}$ as precise as possible by making $\TrFrob{} : \CCSiso{G} \to G(k)^*$ as close to an isomorphism as possible.
 \end{enumerate}

### 2017-05-11 Geometric types.tex
Removing comments, overful hbox fixes

@@
 Yu type data are studied in \cite{Yu:models}, which concludes with the following observation.
-%
 \begin{quotation}
 {\it Therefore, up to some linear characters, all the ingredient representations 
-%[appearing in Yu type data]
  are on groups of the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over [a henselian discrete valuation ring with finite residue field $\kappa$] $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
 These results suggest that algebraic geometry and group schemes should play an
-important role in the representation theory of $p$-adic groups.} %\cite{Yu:models}
+important role in the representation theory of $p$-adic groups.}
 \end{quotation}
-%
 In this paper we follow the suggestion above by showing that Yu type data are geometrizable, in the following sense.
@@
 \]
-%Theorem~\ref{thm:geotypes} shows how to construct the rational virtual Weil sheaf $\cs{F}^i$ from the Yu type datum, so that \eqref{eqn:intro1} holds.
 We refer to the pair $(\underline{G}^d, \cs{F}^d)$ as a \emph{geometric type}.
@@
 of objects in $\CS(G)$ and $G(k)^* \ceq \Hom(G(k), \EEx)$; 
-%Objects in $\CS(G)$ are referred to as \emph{character sheaves}.
 the isomorphism is given by mapping $\cs{L}$ to the function
@@
 essentially surjective, missing the kinds of linear character sheaves highlighted by Kamgarpour.
-%
 
@@
 We now summarize the sections of the paper in more detail.
-%
 In Section \ref{sec:defs}, we recall the category $\CS(G)$ from \cite{cunningham-roe:13a} and note that it still makes sense when $G$ is not commutative.  
-%
 We focus on the case of commutative $G$ in Section \ref{sec:comcom},
@@
 $\TrFrob{G} : \CSiso{G} \to G(k)^*$ induces an isomorphism on $\CCSiso{G}$.
-%
 Passing to the case that $G$ is non-commutative, we give the definition of and main results about commutative character sheaves in Section \ref{sec:noncom}.  
@@
 We also compute the automorphism groups in $\CCS(G)$.
-%Then in Section \ref{ssec:proofs}, we give proofs of the results in Section \ref{sec:noncom}, which require a development of equivariant linear character sheaves. \todo{Fix this.}
-% 
 In Section~\ref{sec:types} we use Theorem~\ref{thm:geo} to geometrize types for supercuspidal representations of $p$-adic groups, in a sense made precise in Theorem~\ref{thm:geotypes}.
-% is given in Section~\ref{ssec:geotypes}. 
- %Specifically, we show that if $C$ is a compact $p$-adic group and $\rho$ is a representation of $C$ and $(C,\rho)$ is a type for a tamely ramified $p$-adic group then there is a  group scheme $G$ over $\Fq$ such that $G(\Fq) = C$ and a rational virtual Weil sheaf $\mathcal{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
 As preparation for the proof, we review some facts about the Heisenberg-Weil representation and its geometrization, in Section~\ref{ssec:Jacobi}.
@@
 character sheaves whose restriction to the derived subgroup is nontrivial.
-%
 Recall from Section~\ref{sec:defs} that we refer to objects in category $\CS(G)$, defined as
@@
 Set $m' = i \circ m \circ \theta$ and let $j\der : G\der\to G$ be inclusion; then $j\der\circ c = m \circ (m \times m')$.
-% \todo{$j$ is not defined, and the needed definition conflicts with the definition of $i$ and $j$ given later.}
 Then $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms below.
@@
 Let $\Loc(G)$ and $\Loc(G\ab)$ be the categories of Weil local systems on $G$ and $G\ab$, respectively.
-%
 Let $\Loc\der(G)$ be the category of $G\der$-equivariant Weil local systems on $G$, whose definition we now recall.
@@
 \end{equation}
-%In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from equations \eqref{eqn:bap}; so, for example, the top left isomorphism comes from $b_1^* n^* \iso b_2^* n^*$ since $n\circ b_1 = n\circ b_2$.
-%On stalks, this condition is ...
-%\[
-%\begin{tikzcd}
-%\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
-%\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
-%& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
-%\end{tikzcd}
-%\]
 Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
@@
 A morphism of $G\der$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $G\der$-equivariant Weil local systems $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves.
-%so
-%\begin{equation}\label{CS4}
-%\begin{tikzcd}
-%\arrow{d}[swap]{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
-%\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
-%\end{tikzcd}
-%\end{equation}
-%commutes; see also \cite{cunningham-roe:13a}, CS.4].
-%
 Let $\CS\der(G)$ be the category of $G\der$-equivariant linear character sheaves on $G$.
-
-%Is $\CS_H(G)$ a rigid monoidal category?
-
-%If $(\cs{L},\mu,\nu)$ and $(\cs{L},\mu,\nu')$ in $\CS_H(G)$, then $\nu = \nu'$?
 
@@
 If $(\cs{L},\mu,\nu)$ is a $G\der$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ 
-%and $\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ 
 is a morphism of $G^2\der$-equivariant Weil local systems on $G^2$. 
@@
 p_2 : G\der\times G\times G\der\times G &\to G\times G \\
-(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2). %\\
-%\theta_2 : H \times G \times H \times G &\to H \times G \times H \times G \\
-%(h_1,g_1,h_2,g_2) &\mapsto (h_2,g_2,h_1,g_1).
+(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2).
 \end{align*}
@@
 	& \arrow{d}{p_2= p^2\circ d} p_2^*(\cs{L}\boxtimes\cs{L}) \\
-%d^* (n\times n)^* (\cs{L}\boxtimes\cs{L}) & d^* (p\times p)^* (\cs{L}\boxtimes\cs{L}) \\
 d^* (n^*\cs{L}\boxtimes n^*\cs{L}) \arrow{r}{d^*(\nu\boxtimes \nu)}& d^*(p^*\cs{L}\boxtimes p^*\cs{L}) 
@@
 \]
-Then $(q^*\cs{L}\ab,\nu(\cs{L}\ab))$ satisfies \eqref{E1} and \eqref{E2}, so $(q^*\cs{L}\ab,\nu(\cs{L}\ab))$ is an object in $\Loc\der(G)$.
+Then $(q^*\cs{L}\ab,\nu(\cs{L}\ab))$ satisfies \eqref{E1} and \eqref{E2}, so $(q^*\cs{L}\ab,\nu(\cs{L}\ab)) \in \Loc\der(G)$.
 Moreover, if $\alpha\ab : \cs{L}\ab \to \cs{L}\ab$ is a morphism in $\Loc(G\ab)$ then $q^*(\alpha\ab)$ satisfies the condition in \eqref{E3}, so $q^*(\alpha\ab)$ is a morphism in $\Loc\der(G)$.
@@
 To see that $(q^*\cs{L}\ab, (q^2)^* \mu\ab)$ is indeed a linear character sheaf on $G$,
-verify \cite{cunningham-roe:13a}*{CS.3}. %, arguing as in \cite{cunningham-roe:13a}.
+verify \cite{cunningham-roe:13a}*{CS.3}.
 Now set $L(\cs{L}\ab) = (\cs{L},\nu)$, where $L : \Loc(G\ab) \to \Loc\der(G)$ is the comparison functor above, so $\cs{L} = q^*\cs{L}\ab$ and $\nu = \nu(\cs{L}\ab)$.
@@
 Consider the following diagram.
-%\[
-%\begin{tikzcd}
-%{} & G\times G \arrow{d}{c} &&&\\
-%1 \arrow{r} & H \arrow{r}{j} & G \arrow{r}{q} & G\ab \arrow{r} & 1
-%\end{tikzcd}
-%\]
-%gives
 \[
@@
 
-Now, suppose $(\cs{L},\mu)\in \CS(G)$ and there is an isomorphism $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ in $\CS(G\der)$.
-Then $(\cs{L},\mu,\beta) \in \CSab(G)$.
-By Proposition \ref{prop:CSGabab}, $(\cs{L},\mu,\beta) \iso q\ab^*(\cs{L}\ab,\mu\ab)$ for some $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$.
+Now, suppose $(\cs{L},\mu)\in \CS(G)$ and there is an isomorphism $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ in $\CS(G\der)$, so that
+$(\cs{L},\mu,\beta) \in \CSab(G)$.
+By Proposition \ref{prop:CSGabab}, there is some $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ with $(\cs{L},\mu,\beta) \iso q\ab^*(\cs{L}\ab,\mu\ab)$.
 Applying the forgetful functor $\CS_{G\der}(G)\to \CS(G)$ to this isomorphism, it follows that $(\cs{L},\mu) \iso q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, as desired.
@@
 
-%\subsubsection{Equivariant Weil local systems}\label{ssec:equivariant1}
-%
-%Let $G$ be a smooth group scheme over $k$, as above.
-%Let $H$ be a group scheme and write $n : H \times H \to H$ for the multiplication morphism.
-%Let $a : H \times G\to G$ be an action of $H$ on $G$ 
-%%group action compatible with the group structure on $G$ 
-%and write $p : H\times G \to G$ for projection. 
-%Consider the morphisms
-%\[
-%\begin{tikzcd}
-%H \times H \times G 
-%\arrow[shift left=4]{r}{b_1, b_2, b_3} 
-%\arrow{r}{}
-%\arrow[shift right=4]{r}{} 
-%& H \times G 
-%\arrow[shift left=2]{r}{a}
-%\arrow[shift right=2]{r}[swap]{p}
-% & G 
-%\end{tikzcd}
-%\]
-%defined by 
-%\begin{align*}
-%b_1(h_1,h_2,g) &= (h_1h_2,g) \\
-%b_2(h_1,h_2,g) &= (h_1,h_2g) \\
-%b_3(h_1,h_2,g) &= (h_2,g).
-%\end{align*}
-%Note that
-%\begin{align*}
-%a\circ b_1 &= a\circ b_2 \\
-%a\circ b_3 &= p\circ b_2 \numberthis \label{eqn:bap}\\
-%p\circ b_1 &= p\circ b_3.
-%\end{align*}
-%Define $s : G\to H\times G$ by $s(g) = (1,g)$.
-%An $H$-equivariant Weil local sytem on $G$ is a Weil local system $\cs{L}$ on $G$ together with an isomorphism  
-%\[
-%\nu : a^*\cs{L} \to p^*\cs{L}
-%\] 
-%of Weil local systems on $H\times G$ such that 
-%\begin{equation}\label{E1}
-%s^*(\nu) = \id_{\cs{L}}
-%\end{equation}
-%and the following diagram of isomorphisms of local systems on $H\times H\times G$ commutes. 
-%\begin{equation}\label{E2}
-%\begin{tikzcd}
-%\ &  \arrow{dl}{a\circ b_1 = a\circ b_2}  b_2^*  a^*\, \mathcal{L} \arrow{rr}{b_2^*(\nu)} && b_2^* p^*\, \mathcal{L} \arrow{dr}[swap]{p\circ b_2 = a\circ b_3} & \\
-%b_1^* a^*\, \mathcal{L} \arrow{dr}{b_1^*(\nu)} &&&&   \arrow{dl}[swap]{b_3^*(\nu)} b_3^* a^*\, \mathcal{L} \\
-%& b_1^* p^*\, \mathcal{L}  && \arrow{ll}[swap]{p\circ b_3 = p\circ b_1} b_3^* p^*\, \mathcal{L} & 
-%\end{tikzcd}
-%\end{equation}
-%In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors
-%on Weil sheaves derived from equations \eqref{eqn:bap}; so, for example, the top left isomorphism
-%comes from $b_1^* a^* \iso b_2^* a^*$ since $a\circ b_1 = a\circ b_2$.
-%%On stalks, this condition is ...
-%%\[
-%%\begin{tikzcd}
-%%\ &  \cs{L}_{h_1\cdot(h_2\cdot g)} \arrow{r}{\nu_{h_1,h_2\cdot g}} & \cs{L}_{h_2\cdot g} & \\
-%%\cs{L}_{(h_1 h_2) \cdot g} \arrow{dr}[swap]{\nu_{(h_1h_2),g}} \arrow[equal]{ur} &&& \arrow[equal]{ul}  \arrow{dl}{\nu_{h_2,g}} \cs{L}_{h_2\cdot g} \\
-%%& \cs{L}_g \arrow[equal]{r} & \cs{L}_g & 
-%%\end{tikzcd}
-%%\]
-%Morphisms of $H$-equivariant Weil local systems $(\cs{L},\nu)\to (\cs{L}',\nu')$ are morphisms of Weil local systems $\alpha: \cs{L}\to \cs{L}'$ for which the diagram
-%\begin{equation}\label{E3}
-%\begin{tikzcd}
-%\arrow{d}[swap]{\nu} a^*\cs{L} \arrow{r}{a^*(\alpha)} & a^*\cs{L}' \arrow{d}{\nu'} \\
-%p^*\cs{L} \arrow{r}{p^*(\alpha)} & p^*\cs{L}'
-%\end{tikzcd}
-%\end{equation}
-%commutes.
-%This defines $\Loc_H(G)$, the category of $H$-equivariant Weil local systems on $G$.
-%The reader will recognize this notion as the Weil sheaf version of equivariant sheaves for
-%the action $a$ of $H$ on $G$, as can be found, for example, in \cite{bernstein-lunts:equivariant}*{0.2}.
-
 \subsection{Objects and maps in commutative character sheaves} \label{ssec:obmor}
@@
 \begin{proof}
-%Set $G^2 = G\times G$. 
 Define $m^2 : G^2\times G^2 \to G^2$ by $m^2(g_1,g_2,g_1',g_2') = (g_1g_1',g_2g_2')$. Also define $p^2_i : G^2\times G^2 \to G^2$ by $p^2_i(g_1,g_2,g_1,'g_2') = (g_i,g_i')$.
@@
 Tracing through the construction of $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ from $\beta : \cs{L}_1\to \EE$, we find
-%\todo{I'm having some trouble seeing this.} 
 that $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ is the canonical isomorphism coming from the equation $m = m \circ \theta$. 
@@
 \begin{theorem}\label{thm:Gab}
-%Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
 Pull-back along the abelianization $q : G \to G\ab$
@@
 
-%
-%Sections~\ref{ssec:equivariant1}, \ref{ssec:equivariant2}, \ref{ssec:descent} and \ref{ssec:closed} set up machinery needed to prove Theorem~\ref{thm:Gab}.
-%The precise definition of the functor $\CCS(G\ab) \to \CCS(G)$ will be given with the proof of Theorem~\ref{thm:Gab}, in Section~\ref{ssec:proof2}.
-
-%\subsubsection{Equivariant linear character sheaves}\label{ssec:equivariant2}
-%
-%With reference to Section~\ref{ssec:equivariant1}, suppose now that $H$ acts on $G$ through group homomorphisms: $a(h, m(g_1,g_2)) = m(a(h, g_1), a(h, g_2))$.
-%
-%We define an $H$-equivariant linear character sheaf on $G$ to be a triple $(\cs{L},\mu, \nu)$,
-%where $(\cs{L},\mu)$ is a linear character sheaf and $(\cs{L},\nu)$ is an $H$-equivariant local system.
-%We require that $\mu$ be compatible with $\nu$ in the following sense.
-%We define morphisms:
-%\begin{align*}
-%c_0 : H\times G \times G &\to H\times G \times H \times G \\
-%(h,g_1,g_2) &\mapsto (h,g_1,h,g_2); \\
-%c_1 : H \times G\times G &\to G\times G \\
-%(h, g_1, g_2) &\mapsto (hg_1,hg_2); \\
-%c_2 : H \times G\times G &\to H\times G \\
-%(h,g_1,g_2) &\mapsto (h, g_1g_2); \\
-%c_3 : H \times G\times G &\to G\times G \\
-%(h, g_1, g_2) &\mapsto (g_1, g_2).
-%\end{align*}
-%We require that the following diagram of Weil local systems on $H \times G\times G$ commutes:
-%\todo{Something's wrong: the top left actually requires $a \circ c_2 = m \circ c_1$, which isn't true.}
-%\begin{equation}\label{ECS1}
-%\begin{tikzcd}[column sep=30]
-%\ & \arrow{dl}{a\circ c_2 = m\circ c_1}  c_2^* a^* \cs{L} \arrow{r}{c_2^*(\nu)} & c_2^* p^* \cs{L} \arrow{dr}[swap]{p\circ c_2 = m\circ c_3}  &  \\
-%\arrow{d}[swap]{c_1^*(\mu)} c_1^* m^* \cs{L} &&& c_3^* m^*\cs{L} \arrow{d}{c_3^*(\mu)} \\
-%c_1^*(\cs{L}\boxtimes \cs{L}) \arrow{dr}{p_i\circ c_1 = a\circ p_i\circ c_0} &&& \arrow{dl}[swap]{p\circ p_i\circ c_0 = p_i \circ c_3} c_3^*(\cs{L}\boxtimes \cs{L}) \\
-% & c_0^*(a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{c_0^*(\nu\boxtimes \nu)} & c_0^*(p^*\cs{L} \boxtimes p^*\cs{L}) & 
-%\end{tikzcd}
-%\end{equation}
-%Note that $a\circ c_2 = m\circ c_1$ precisely because $H$ acts on $G$ through group homomorphisms.
-%
-%
-%%On stalks, this condition is
-%%\[
-%%\begin{tikzcd}
-%%\arrow{d}[swap]{\mu_{(h\cdot g_1, h\cdot g_2)}} \cs{L}_{(h\cdot g_1)(h\cdot g_2)} & \arrow[equal]{l}  \cs{L}_{h\cdot(g_1 g_2)} \arrow{r}{\nu_{(h, g_2 g_2)}} & \cs{L}_{g_1 g_2} \arrow[equal]{r} & \cs{L}_{g_1 g_2} \arrow{d}{\mu_{(g_1,g_2)}} \\
-%%\cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow[equal]{r} & \cs{L}_{h\cdot g_1}\otimes \cs{L}_{h\cdot g_2} \arrow{r}{\nu_{(h,g_1)}\otimes \nu_{(h,g_2)}} & \cs{L}_{g_1}\otimes \cs{L}_{g_2} & \arrow[equal]{l} \cs{L}_{g_1} \otimes \cs{L}_{g_2},
-%%\end{tikzcd}
-%%\]
-%%for all $(h,g_1,g_2)\in H\times G\times G$.
-
-%A morphism of $H$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$
-%is a morphism of $H$-equivariant Weil sheaves $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves.
-%%so
-%%\begin{equation}\label{CS4}
-%%\begin{tikzcd}
-%%\arrow{d}[swap]{\mu} m^*\cs{L} \arrow{r}{m^*(\alpha)} & m^*\cs{L}' \arrow{d}{\mu'} \\
-%%\cs{L}\boxtimes \cs{L} \arrow{r}{\alpha\boxtimes\alpha} & \cs{L}'\boxtimes\cs{L}' 
-%%\end{tikzcd}
-%%\end{equation}
-%%commutes; see also \cite{cunningham-roe:13a}, CS.4].
-%%
-%Let $\CS_H(G)$ be the category of $H$-equivariant linear character sheaves on $G$.
-%
-%%Is $\CS_H(G)$ a rigid monoidal category?
-%
-%%If $(\cs{L},\mu,\nu)$ and $(\cs{L},\mu,\nu')$ in $\CS_H(G)$, then $\nu = \nu'$?
-%
-%\begin{lemma}\label{lem:HH}
-%If $(\cs{L},\mu,\nu)$ is an $H$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ and
-%$\vartheta : \cs{L}\boxtimes \cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are morphisms of $H\times H$-equivariant Weil local systems on $G\times G$. 
-%\end{lemma}
-%
-%\begin{proof} 
-%Define
-%\begin{align*}
-%d : H\times H\times G\times G &\to H\times G\times H\times G \\
-%(h_1,h_2,g_1,g_2) &\mapsto (h_1, g_1, h_2, g_2)\\
-%a_2 : H\times G\times H\times G &\to G\times G \\
-%(h_1,g_1,h_2,g_2) &\mapsto (h_1g_1, h_2g_2) \\
-%p_2 : H\times G\times H\times G &\to G\times G \\
-%(h_1,g_1,h_2,g_2) &\mapsto ( g_1,g_2) \\
-%\theta_2 : H \times G \times H \times G &\to H \times G \times H \times G \\
-%(h_1,g_1,h_2,g_2) &\mapsto (h_2,g_2,h_1,g_1).
-%\end{align*}
-%The following diagram defines the isomorphisms needed to see that both $m^*\cs{L}$ and $\cs{L}\boxtimes\cs{L}$ are $H\times H$-equivariant Weil local systems.
-%\[
-%\begin{tikzcd}[column sep=40]
-%\arrow{d}[swap]{a_2^*(\mu)} a_2^* (m^*\cs{L}) \arrow[dashed]{r} 
-%	& \arrow{d}{p_2^*(\mu)} p_2^*(m^*\cs{L})\\
-%\arrow{d}[swap]{a_2= (a\times a)\circ d} a_2^*(\cs{L}\boxtimes\cs{L}) \arrow[dashed]{r} 
-%	& \arrow{d}{p_2= (p\times p)\circ d} p_2^*(\cs{L}\boxtimes\cs{L}) \\
-%%d^* (a\times a)^* (\cs{L}\boxtimes\cs{L}) & d^* (p\times p)^* (\cs{L}\boxtimes\cs{L}) \\
-%d^* (a^*\cs{L}\boxtimes a^*\cs{L}) \arrow{r}{d^*(\nu\boxtimes \nu)}& d^*(p^*\cs{L}\boxtimes p^*\cs{L}) 
-%\end{tikzcd}
-%\]
-%The dashed arrows both satisfy \eqref{E1} and \eqref{E2} as they apply here.
-%This diagram also shows that $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ is a morphism of equivariant sheaves, since it satisfies \eqref{E3} as it applies here.
-%The proof that $\theta^*(\cs{L}\boxtimes\cs{L})$ is $H\times H$ equivariant is also straightforward,
-%since $a_2\circ \theta_2 = \theta \circ a_2$ and $p_2\circ \theta_2 = \theta \circ p_2$.
-%Let $\nu_2 : a_2^*(\cs{L}\boxtimes\cs{L}) \to p_2^*(\cs{L}\boxtimes\cs{L})$ be the middle horizontal isomorphism of Weil local systems, above. 
-%To see that
-%\[
-%\begin{tikzcd}
-%a_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r}{a_2^*(\vartheta)} \arrow{d}[swap]{\nu_2} 
-%	& a_2^*\theta^*(\cs{L}\boxtimes\cs{L}) \arrow{d}{\theta^*(\nu_2)} \\
-%p_2^*(\cs{L}\boxtimes\cs{L}) \arrow{r}{p_2^*(\vartheta)} 
-%	& p_2^*\theta^*(\cs{L}\boxtimes\cs{L})
-%\end{tikzcd}
-%\]
-%commutes, consider the commuting diagram of stalks, below.
-%\[
-%\begin{tikzcd}
-%\cs{L}_{h_1g_1}\otimes\cs{L}_{h_2g_2} \arrow{r}{\vartheta}  \arrow{d}[swap]{\nu_2} 
-%	& \cs{L}_{h_2g_2} \otimes\cs{L}_{h_1g_1}  \arrow{d}{\nu_2} \\
-%\cs{L}_{g_1}\otimes\cs{L}_{g_2} \arrow{r}{\vartheta}  
-%	& \cs{L}_{g_2} \otimes\cs{L}_{g_1}
-%\end{tikzcd}
-%\]
-%\end{proof}
-
-%\subsubsection{Quotient by a closed subgroup}\label{ssec:closed}
-%
-%We now suppose that $j : H \hookrightarrow G$ is a closed subgroup scheme over $\Fq$
-%and that the action $a : H\times G\to G$ is obtained by restricting the action
-%$m : G \times G\to G$ to $H\times G$.  In this context, we are able to replace
-%$\nu : a^*\cs{L} \to p^*\cs{L}$ with an isomorphism $\beta : \cs{L}_H \to (\EE)_H$.
-%Let $\CS^H(G)$ be the category of triples $(\cs{L},\mu,\beta)$ with $(\cs{L},\mu) \in \CS(G)$
-%and $\beta : \cs{L}\vert_H \to (\EE)_H$ an isomorphism in $\CS(H)$;
-%a morphism $(\cs{L},\mu,\beta) \to (\cs{L}',\mu',\beta')$ in $\CS^H(G)$ is a morphism
-%$\alpha: \cs{L} \to \cs{L}'$ in $\CS(G)$ such that $\beta = \beta' \circ \alpha\vert_{H}$.
-%
-%\begin{lemma}\label{lem:beta}
-%If $H\hookrightarrow G$ is a closed subgroup scheme over $\Fq$ then $\CS_H(G)$ is equivalent to $\CS^H(G)$.
-%\end{lemma}
-%\begin{proof}
-%Define $f : H\times G \to G\times G$ by $f(h,g) = (j(h),g)$ and note that $a = m\circ f$.
-%Write $p_1: G\times G\to G$ for projection to the first component and $p_2 : G\times G \to G$ for projection to the second.
-%We may pass between $\nu$ and $\beta$ via the following diagram.
-%\[
-%\begin{tikzcd}[column sep=30]
-%\ & a^*\cs{L} \arrow{dl}{m\circ f = a} \arrow{r}{\nu} & p^*\cs{L} & \\
-%f^* m^*\cs{L} \arrow{dr}{f^*\mu} &&& (\EE)_{H} \boxtimes \cs{L} \arrow{ul} \\ 
-%& f^*(\cs{L}\boxtimes \cs{L}) \arrow{r}{p_1 \circ f = j}[swap]{p_2\circ f = \id}  & 
-%\cs{L}\vert_{H} \boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id} & 
-%\end{tikzcd}
-%\]
-%It is a straightforward, tedious exercise to show that the conditions \eqref{E1}, \eqref{E2} and \eqref{ECS1} 
-%on $\nu$ are equivalent to the condition that the isomorphism of Weil local systems
-%$\beta : \cs{L}\vert_{H} \to (\EE)_{H}$ is an isomorphism in the category of of linear character sheaves on $H$.
-%\end{proof}
-
 Theorem~\ref{thm:Gab} shows that $\CCS(G)$ is a categorical solution to the problem that linear character sheaves on $G$ need not be trivial on $G\der$, as discussed at the beginning of Section~\ref{sec:noncom}.
 At the same time, changing $\CS(G)$ to $\CCS(G)$ resolves the lack of bijectivity in \cite{cunningham-roe:13a}*{Theorem 3.6}.
-%
 We may also use Theorem~\ref{thm:Gab} to give a description of the morphisms and the isomorphism classes of objects in $\CCS(G)$.
@@
 \begin{corollary}\label{cor:Gab}
-%Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
 The category $\CCS(G)$ is monoidal and there is a canonical isomorphism
@@
 \begin{theorem}\label{thm:geo}
-%Let $G$ be a smooth group scheme over a finite field $\Fq$. Let $\CCS(G)$ be the category of {\it commutative characters sheaves} on $G$; see Definition~\ref{def:CCS}.
 The trace of Frobenius $\TrFrob{} : \CCSiso{G}\to G(\Fq)^*$ fits into the following diagram,
@@
 
-%\todo{Masound's definition is designed to match the definition coming from central extensions, while we have one that matches Ext1 in Ab, in the connected case.
-So, I think the modification is easy: add mop to diagram 2.4 in Masoud's paper.
-\\ -CC}
-
-%\section{Descent to the Abelianization} \label{sec:descent}
-
-%In this section we use descent along the abelianization $q : G \to G\ab$ to prove Propositions~1.2 and 1.4, and Theorem~\ref{thm:Gab}.
-%This approach requires introducing equivariant linear character sheaves, as defined in Section~[].
-
-%We close this section by gathering together the main result of this paper in one place.
-
 \section{Application to type theory for \texorpdfstring{$p$}{p}-adic groups}\label{sec:types}
@@
 \subsection{Quasicharacters of smooth group schemes over certain henselian traits}
-
-%We begin with the case of continuous linear characters.
 
@@
 \begin{proposition}\label{prop:quasicharacters}
-%With notation as above, suppose $\Fq$ is a finite field.
 For every quasicharacter character $\varphi : \underline{G}(R) \to \EEx$ there is a Weil sheaf $\cs{L}$ on $G$ such that \[\trFrob{\cs{L}} =  \varphi.\] \end{proposition}
@@
 \end{enumerate}
-%He then introduces the following quotients of $J_{i+1}$ and $\oK^i$, for $i=0, \ldots d-1$.
 %
@@
 The vector space $V_{i+1}$ is then equipped with a symplectic pairing $\langle\ ,\ \rangle_{i+1} : V_{i+1}\times V_{i+1} \to Z_{i+1}$, where $Z_{i+1}$ is a one-dimensional vector space over $\Fq$, itself equipped with an additive character $\psi_{i+1} : Z_{i+1} \to \CC^\times$.
-%\labitem{Q2}{Q2} 
-%\item 
 This, in turn, is used to define a map
@@
 In fact, the quotient $J_{i+1} \to V_{i+1}^\sharp$ factors through a quotient $J_{i+1} \to H_{i+1}$ and an isomorphism $j_{i+1} : H_{i+1} \to V_{i+1}^\sharp$, where $H_{i+1}$ is a Heisenberg $p$-group in the sense of \cite{yu:01a}*{}.
-%\labitem{Q3}{Q3} 
-%\item
 Finally, Yu constructs a group homomorphism $f_{i+1} : \oK^i \to \Sp(V_{i+1})$ such that the pair $(f_{i+1}, j_{i+1})$ is a symplectic action of $\oK^i$ on $H_{i+1}$ in the sense of \cite{yu:01a}.
@@
 Taken together, this defines
-%\end{enumerate}
 \begin{enumerate}
@@
 of $\oK^i \ltimes J_{i+1}$.
-%By construction, the character of this representation satisfies
-%\begin{equation}\label{eq:tilderho}
-%\trace({\tilde\rho}_{i+1})(y)= \trace(h_{i+1}^*(W_{i+1})(y)\ \trace(\orho^i)(p_i(y))\ \varphi^i(p_i(y))
-%\end{equation}
-%for $y \in \oK^i \ltimes J_{i+1}$.
 By \cite{yu:01a}*{}, the representation $\orho^{i+1}$ of $\oK^i \ltimes J_{i+1}$ is trivial on $\oK^{i}\cap J_{i+1}$ so $\orho^{i+1}$ descends to $\oK^{i+1}$. 
@@
 This completes the recursive definition of the Yu $(\oK^i,\orho_i)$ for $i=0, \ldots , d$.
-%The character of $\orho^d$ on $\oK^d = C = J_0 \cdots J_d$ satisfies
-%\[
-%\trace(\rho)(k_0 \cdots k_d) = \orho^0(k_0)  \varphi^0(k_0) \cdots \varphi^d(k_d),
-%\]
-%for $k_i\in J_i$.
-
-%\subsection{Review of Yu's smooth models}\label{ssec:review}
-
-%\begin{enumerate}
-%\labitem{M1}{M1}
 By \cite{Yu:models}*{Prop 10.2} there is a sequence  
@@
 
-%\labitem{M2}{M2}
 As explained in \cite{Yu:models}*{\S 10.4}, there is morphism of affine smooth group schemes of finite type over $R$ 
@@
 for each $i=0,\ldots d$, such that $\underline{J}^i(R) = J_i$ as a subgroup of $C$ and such that the image of the $R$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $\oK^i$, for $i=0, \ldots , d$.
-%\labitem{M3}{M3}
 There is a natural action of $\underline{G}^i$ on $\underline{J}^{i+1}$ in the category of smooth affine group schemes over $R$ so that the group scheme
@@
 gives $(\underline{G}^i \ltimes \underline{J}^{i+1})(R) = \oK^i \ltimes J_{i+1}$
-%\end{enumerate}
 
@@
 \]
-%Recall that the full Greenberg transform $\Gr^{R}(\underline{G}^i)$ is a group scheme over $\Fq$ such that $\Gr^{R}(\underline{G}^i)(\Fq) = \underline{G}^i(\Fq)$, canonically, and comes equipped with a morphism $\Gr^{R}(\underline{G}^i) \to \Gr^{R}_m(\underline{G}^i)$.
-%Let $\cs{L}^i$ be the  Weil sheaf on $\Gr^{R}(\underline{G}^i)$ obtained from $\cs{L}^i_m$ by pullback along $\Gr^{R}(\underline{G}^i) \to \Gr^{R}_{m}(\underline{G}^i)$. 
-%Then $\cs{L}^i$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G}^i)$ from which the quasicharacter $\varphi^i$ may be recovered.
 
@@
 \]
-%Let $\cs{A}^0$ be the pull-back of $\cs{A}^0_m$ along  $\Gr^{R}(\underline{G}^0) \to \Gr^{R}_{m}(\underline{G}^0)$.
-%Then $\cs{A}^0$ is a quasicharacter sheaf, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, on $\Gr^{R}(\underline{G}^0)$ from which the character of $\orho^0$ may be recovered.
 
@@
 First, set $\cs{A}_m^0 = A_m^0$ and note that \eqref{eqn:tracerho} commutes with $\trace(\orho^0)_m$ replaced by $\trFrob{\cs{A}_m^0}$.
-%\[
-%\begin{tikzcd}
-%G^0(\Fq) \arrow{rr}{\trace(\orho^0)} \arrow{rd} && \EE\\
-%& G^0_m(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m^0}} & 
-%\end{tikzcd}
-%\]
-%commutes.
 Now, suppose $\cs{A}^i_m$ on $G_m^i$ is defined such that
@@
 By \cite{bertapelle-gonzales:Greenberg}*{Prop 7.1}, the sequences are exact.
-%Consider $\cs{A}_m^{i}\otimes \cs{L}_m^{i}$ on $G_m^{i}$ and let 
-%\[
-%(p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
-%\]
-%be the Weil sheaf on $G_m^{i}\ltimes J_m^{i+1}$ obtained by pullback along $G_m^{i}\ltimes J_m^{i+1} \to G_m^{i}$.
 Consider the sheaf 
@@
 \]
-%Let $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$ and set $\cs{A}_m^{i+1} \ceq \cs{\tilde A}_m^{i+1}(-n)$ (Tate twist).
 Then
@@
 \end{proof}
-
-%\bibliography{bibliography/Biblio}
-% \bib, bibdiv, biblist are defined by the amsrefs package.
-%\iffalse
 
@@
 \end{bibdiv}
-%\fi
 

### 2017-05-11 CJM/letter to CJM.tex

--- 2017-05-11 CJM/letter to CJM.tex
@@
 Fortunately, this had the effect of simplifying the constructions and did not add to the length of the paper. 
-\item[(2)] It is quite true that it would be possible to view Section 4 as an application of our earlier paper, bypassing the the first part of the paper under review.
+\item[(2)] It is quite true that it would be possible to view Section 4 as an application of our earlier paper, bypassing the first part of the paper under review.
 Our main motivation for Sections 1--3 was twofold: to address the `defect' in the dictionary from our earlier paper; and to extend that dictionary, as it pertains to characters, to non-commutative groups.
-(Although it wasn't our motivation, we were also happy to find an alternative to the stacky abelianization of Kamgarpour.) We have added a comment to this effect after Theorem 3.12, in the hopes that it will clarify this point.
+(Although it wasn't our motivation, we were also happy to find an alternative to the stacky abelianization of Kamgarpour.)
+The category of commutative character sheaves is a subcategory of $\CS\ab(G)$ and there is a forgetful functor $\CS\ab(G) \to \CS(G)$ and another $\CS(G)\to \Loc(G)$.
+So while the category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the sense of Theorem~3.12, it is also true that $\CS(G)$ and even $\Loc(G)$ geometrizes characters of $G(\Fq)$ in the sense that for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $\cs{L}$ in $\Loc(G)$ such that $\trFrob{\cs{L}} = \chi$.
+The category $\CCS(G)$ only serves to make this translation from characters $\chi$ to Weil local systems $\cs{L}$ as precise as possible by making $\TrFrob{} : \CCSiso{G} \to G(k)^*$ as close to an isomorphism as possible.
 \end{enumerate}

### 2017-06-13 Geometric types v5.tex
Made a home for my efforts to fix the error

--- 2017-05-11 Geometric types.tex
@@
 
-If $\chi \in G(k)^*$ is a character, it must vanish on the derived subgroup $G\der(k)$.
+If $\chi \in G(k)^*$ is a character, it must vanish on the derived subgroup $G\der(k)$. \todo{Error} 
 Kamgarpour gives an example \cite{kamgarpour:09a}*{(1.1)} of a character sheaf
-that does not vanish on $G\der$, defined by the extension
-\[
-1 \to \mu_n \to \SL_n \to \PGL_n \to 1.
-\]
+on $G = \PGL_n$ that does not vanish on $G\der = \PGL_n$, defined by the extension
+\[
+1 \to \mu_n \to \SL_n \to \PGL_n \to 1
+\]
+together with a non-trivial character of $\mu_n(k)$. \todo{Small change here.}
 In order to obtain a relationship between character sheaves on $G$ and characters of $G(k)$,
@@
 
+\subsection{Geometrization of characters}\label{ssec:CCSflat}
+
+\begin{definition}\label{def:CCS}
+The category $\CCS^\flat(G)$ of commutative character sheaves on $G$ is the category of triples $(\cs{L},\mu,\xi)$, where $\xi  : m^*\cs{L} \to \theta^* m^*\cs{L}$ such that the following diagram of Weil sheaves on $G \times G$ commutes:
+  \[
+  \begin{tikzcd}[row sep=30]
+   m^*\cs{L} \arrow{d}[swap]{\xi} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
+   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L}).
+  \end{tikzcd}
+  \]
+A morphism $(\cs{L},\mu,\xi) \to (\cs{L},\mu',\xi')$ in $\CCS^\flat(G)$ is a morphism $\alpha : (\cs{L},\mu) \to  (\cs{L}',\mu')$ in $\CS(G)$ such that the following diagram commutes:
+  \[
+  \begin{tikzcd}[row sep=30, column sep=50]
+   m^*\cs{L} \arrow{d}[swap]{\xi} \arrow{r}{m^*\alpha} & m^*  \cs{L}' \arrow{d}{\xi'}\\
+   \theta^*m^*\cs{L} \arrow{r}{\theta^* m^*\alpha} &  \theta^*m^*\cs{L}'.
+  \end{tikzcd}
+  \]
+\end{definition}
+
+\begin{theorem}
+If $\cs{L}\in  \CCS^\flat(G)$ then $\trFrob{\cs{L}} \in  G(k)^*$.
+For every $\chi \in G(k)^*$ there is some $\cs{L}\in  \CCS^\flat(G)$ such that $\trFrob{\cs{L}} =\chi$.
+\end{theorem}
+
 \subsection{Main definition}\label{ssec:noncomdef}
@@
 In order to get character sheaves that correspond to characters in $G(k)^*$, we must discard those
-character sheaves whose restriction to the derived subgroup is nontrivial.
+character sheaves whose restriction to the commutator subgroup of $G(k)$ is nontrivial.
 Recall from Section~\ref{sec:defs} that we refer to objects in category $\CS(G)$, defined as
@@
 not necessarily commutative.  
-We define the following category to track the trivialization on the derived subgroup;
-commutative character sheaves will then be defined as a subcategory.
+We define the following category to track the trivialization on the commutator  subgroup.
 
@@
 %
- && \  &\arrow{l}[swap]{(q^2)^*\ab}  & & &\\ 
+ && \  &\arrow{l}[swap]{(q^2)^*\ab}  &  &\\ 
 %
@@
 \]
-Applying $\Hom(-, \EEx)$ and using the fact that every homomorphism $G(k) \to \EEx$ vanishes on $G\der(k)$, we get
+Applying $\Hom(-, \EEx)$ and using the fact that every homomorphism $G(k) \to \EEx$ vanishes on $G\der(k)$,\todo{Error here} we get
 \[
@@
         date={1970},
-   booktitle={{Sch\'emas en groupes I: Proprietes generales des schemas en
+   booktitle={S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois Marie, Sch\'emas en groupes I (SGA3) {Proprietes generales des schemas en
   groupes}},

### 2017-06-27 Geometric types.tex
Addressing second round of referee comments

@@
 
-We are extremely grateful to Loren Spice for explaining Yu's types for supercuspidal representations.
-We also thank Masoud Kamgarpour for helpful conversations, and the anonymous referee of this paper, would pointed out an error in an earlier version and helped us clarify several points.
+We are extremely grateful to Loren Spice for explaining Yu's types for supercuspidal representations and Masoud Kamgarpour for helpful conversations.
+We also thank Will Sawin and the anonymous referee, who pointed out errors in earlier versions of this paper and helped us clarify several points.
 
@@
 We now consider the case of a smooth group scheme without the commutativity assumption.  We start
-by relating character sheaves on $G$ to character sheaves on its abelianization.
+by relating linear character sheaves on $G$ to character sheaves on its abelianization.
 
 If $\chi \in G(k)^*$ is a character, it must vanish on the derived subgroup $G\der(k)$. \todo{Error} 
-Kamgarpour gives an example \cite{kamgarpour:09a}*{(1.1)} of a character sheaf
+Kamgarpour gives an example \cite{kamgarpour:09a}*{(1.1)} of a linear character sheaf
 on $G = \PGL_n$ that does not vanish on $G\der = \PGL_n$, defined by the extension
@@
 together with a non-trivial character of $\mu_n(k)$. \todo{Small change here.}
-In order to obtain a relationship between character sheaves on $G$ and characters of $G(k)$,
+In order to obtain a relationship between linear character sheaves on $G$ and characters of $G(k)$,
 he opts to give a different definition of commutator and, in doing so, introduces a `stacky abelianization' of $G$ in order to geometrize characters of $G(\Fq)$.
@@
 
-In order to get character sheaves that correspond to characters in $G(k)^*$, we must discard those
-character sheaves whose restriction to the derived subgroup is nontrivial.
 Recall from Section~\ref{sec:defs} that we refer to objects in category $\CS(G)$, defined as
@@
 Let $i : G \to G$ be inversion and $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
-Both are smooth morphisms of $\Fq$-schemes.
-Set $m' = i \circ m \circ \theta$ and let $j\der : G\der\to G$ be inclusion; then $j\der\circ c = m \circ (m \times m')$.
+Both are morphisms of $\Fq$-schemes.
+Set $m' = i \circ m \circ \theta$ and let $i\der : G\der\to G$ be inclusion; then $i\der\circ c = m \circ (m \times m')$.
 Then $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms below.
@@
 	&  c^*((\EE)_{G\der}) \arrow[equal]{d} \\
-\arrow{d}[swap]{j\der\circ c = m \circ (m \times m')} c^* j\der^* \cs{L} 
+\arrow{d}[swap]{i\der\circ c = m \circ (m \times m')} c^* i\der^* \cs{L} 
 	&   (\EE)_{G\times G} \\
@@
 \end{equation}
-In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations; so, for example, the middle left isomorphism comes from $(m\times m')^* m^* \iso c^* j\der^*$ since $j\der\circ c = m \circ (m \times m')$.
+In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations; so, for example, the middle left isomorphism comes from $(m\times m')^* m^* \iso c^* i\der^*$ since $i\der\circ c = m \circ (m \times m')$.
 Using the monoidal structure of the category of Weil local systems on $G\times G$, the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ defines an isomorphism
@@
 If $(\cs{L},\mu,\nu)$ is a $G\der$-equivariant linear character sheaf on $G$ then $\mu : m^*\cs{L} \to \cs{L}\boxtimes \cs{L}$ 
-is a morphism of $G^2\der$-equivariant Weil local systems on $G^2$. 
+is a morphism of $G^2\der$-equivariant Weil local systems on $G^2$, as defined in Section \ref{ssec:equivariant1}.
 \end{lemma}
@@
 \begin{corollary}
-If $G$ is a smooth group scheme and $(\cs{L},\mu)$ is a character sheaf on $G$ with trivial restriction to $G\der$,
+If $G$ is a smooth group scheme and $(\cs{L},\mu)$ is a linear character sheaf on $G$ with trivial restriction to $G\der$,
 then the set of isomorphism classes of objects in $\CS(G\ab)$ mapping to $(\cs{L},\mu)$ under $q^*$ is a principal homogeneous space
@@
 automorphism of the constant sheaf on $G\der$.  Conversely, if $\varphi$ is an automorphism of $(\EE)_{G\der}$
-and $(\cs{L},\mu,\beta) \in \CSab(G)$ then $(\cs{L},\mu,\varphi \circ \beta) \in \CSab(G)$.  By \cite{cunningham-roe:13a}*{Theorem 3.9},
+and $(\cs{L},\mu,\beta) \in \CSab(G)$ then $(\cs{L},\mu,\varphi \circ \beta) \in \CSab(G)$.  As in \cite{cunningham-roe:13a}*{Theorem 3.9},
 the automorphism group is isomorphic to $\Hom(\pi_0(\bar{G}\der)_{\Frob{}}, \EEx)$.  Finally, we note that any
 automorphism $\alpha$ of $(\cs{L},\mu) \in \CS(G)$ defines an isomorphism $(\cs{L},\mu,\beta \circ \alpha|_{G\der}) \to (\cs{L},\mu,\beta)$.
-Applying \cite{cunningham-roe:13a}*{Theorem 3.9} again yields the desired result.
+Applying the analogue of \cite{cunningham-roe:13a}*{Theorem 3.9} again yields the desired result.
 \end{proof}
@@
 \begin{lemma}\label{lemma:morinCSab}
-If $(\cs{L},\mu,\beta)\in \CS\ab(G)$ then $\mu  : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$, $\gamma : m^*\cs{L} \to  \theta^*(m^*\cs{L})$ and $\vartheta: \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are morphisms in $\CS\ab(G\times G)$.
+If $(\cs{L},\mu,\beta)\in \CS\ab(G)$ then $\mu  : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$, $\gamma : m^*\cs{L} \to  \theta^*(m^*\cs{L})$ and $\vartheta: \cs{L}\boxtimes\cs{L} \to \theta^*(\cs{L}\boxtimes \cs{L})$ are morphisms in $\CS\ab(G^2)$.
 \end{lemma}
@@
 Let $\cs{L}$ be the Weil sheaf on $G$ obtained from $\cs{L}_m$ by pullback along $G \to G_m$. 
-Then $\cs{L}$ is a quasicharacter sheaf on $G$, in the sense of \cite{cunningham-roe:13a}*{Def 4.3}, such that $\trFrob{\cs{L}} = \varphi$.
+Then $\cs{L}$ is a quasicharacter sheaf on $G$, in the sense of \cite{cunningham-roe:13a}*{Def 4.2}, such that $\trFrob{\cs{L}} = \varphi$.
 \end{proof}

### 2017-06-28 Geometric types.tex
Addressing Comment 1 from second review. Imcomplete

@@
 
-The reason for tracking $\beta$ is that it determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ as follows,
-which will replace the $\xi$ of Definition \ref{def:CCScom}.
+The reason for tracking $\beta$ is that it determines an isomorphism $\gamma : m^*\cs{L} \to \theta^*m^*\cs{L}$ which will replace the $\xi$ of Definition \ref{def:CCScom}, as follows.
 Let $i : G \to G$ be inversion and $c : G\times G\to G\der$ be the commutator map, defined by $c(x,y)= xyx^{-1}y^{-1}$.
@@
 
-Let $\Loc(G)$ and $\Loc(G\ab)$ be the categories of Weil local systems on $G$ and $G\ab$, respectively.
+Let $\Loc(G)$ be the category of Weil local systems on $G$.
 Let $\Loc\der(G)$ be the category of $G\der$-equivariant Weil local systems on $G$, whose definition we now recall.
@@
 
+Let $\Loc(G\ab)$ be the category of Weil local systems on $G\ab$.
+If $\cs{L}\ab\in \Loc(G\ab)$ then $q^*\cs{L}\ab\in \Loc(G)$ comes equipped with a canonical isomorphism $\nu(\cs{L}\ab) : n^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of isomorphisms.
+\[
+\begin{tikzcd}[column sep=40]
+n^*\cs{L} \arrow[equal]{d} \arrow[dashed]{r}{\nu(\cs{L}\ab)} &  \arrow[equal]{d} p^*\cs{L} \\
+n^* ( q^*\cs{L}\ab) \arrow[equal]{r}{q\circ n = q\circ p}
+& p^* (q^*\cs{L}\ab)
+\end{tikzcd}
+\]
+Then $(q^*\cs{L}\ab,\nu(\cs{L}\ab))$ satisfies \eqref{E1} and \eqref{E2}, so $(q^*\cs{L}\ab,\nu(\cs{L}\ab)) \in \Loc\der(G)$.
+Moreover, if $\alpha\ab : \cs{L}\ab \to \cs{L}\ab$ is a morphism in $\Loc(G\ab)$ then $q^*(\alpha\ab)$ satisfies the condition in \eqref{E3}, so $q^*(\alpha\ab)$ is a morphism in $\Loc\der(G)$.
+This defines the functor
+\[
+L : \Loc(G\ab)\to \Loc\der(G)
+\]
+
+\begin{lemma}\label{lemma:descent}
+The functor $L : \Loc(G\ab)\to \Loc\der(G)$ is an equivalence.
+\end{lemma}
+\begin{proof}
+The quotient $q : G \to G\ab$ is an $G\der$-torsor in the fppf topology by \cite{demazure:SGA3-VIA}*{Thm. 3.2}, and thus a $G\der$-torsor in the fpqc topology.
+The lemma is now a result from descent theory, arguing as in \cite{Vistoli:notes}*{Theorem 4.46} for example. 
+\end{proof}
+
+Observe that if $(\cs{L},\nu)\in \Loc\der(G)$ then ... \todo{New lemma?}
+
 \subsubsection{Equivariant linear character sheaves}\label{ssec:equivariant2}
@@
 With reference to Section~\ref{ssec:equivariant1}, we define a $G\der$-equivariant linear character sheaf on $G$ to be a triple $(\cs{L},\mu, \nu)$, where $(\cs{L},\mu)$ is a linear character sheaf and $(\cs{L},\nu)$ is an $G\der$-equivariant Weil local system.
-A morphism of $G\der$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $G\der$-equivariant Weil local systems $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves.
+A morphism of $G\der$-equivariant linear character sheaves $(\cs{L},\mu,\nu) \to (\cs{L}',\mu',\nu')$ is a morphism of $G\der$-equivariant Weil local systems $\alpha : \cs{L}\to \cs{L}'$ which is also a morphism of linear character sheaves;
 Let $\CS\der(G)$ be the category of $G\der$-equivariant linear character sheaves on $G$.
 
-\begin{lemma}\label{lemma:nubeta}
-Categories $\CS\der(G)$ and $\CS\ab(G)$ are equivalent.
-\end{lemma}
-
-\begin{proof}
-Let $i\der : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\der\times G$ by $j(h) = (h,1)$. 
-If $(\cs{L},\mu,\nu)\in \CS\der(G)$ then $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism. 
-This defines a functor by
-\[
-\begin{array}{rcl}
-\CS\der(G) &\to& \CSab(G) \\
-(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,j^*(\nu))
-\end{array}
-\]
-on objects and trivially on morphisms.
-It is easy to verify that morphisms that commute with $\mu$ and $\nu$ also commute with $\mu$ and $j^*(\nu)$.
-This functor is an equivalence; its adjoint is given as follows.
-Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i\der(h),g)$.
-Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p^*\cs{L}$ by the following diagram.
-\[
-\begin{tikzcd}
-& n^* \cs{L} \arrow{dl}{m\circ k = n} \arrow[dashed]{r}{\nu} & p^*\cs{L} &  \\ 
-k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
-& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id_\cs{L}}
-\end{tikzcd}
-\]
-This defines the functor  $\CS\ab(G) \to \CS\der(G)$, after confirming that morphisms that commute with $\mu$ and $\beta$ also commute with $\mu$ and $\nu$.
-\end{proof}
+Consider the functor
+\[
+q^* : \CS(G\ab) \to \CS(G)
+\]
+given on objects by $(\cs{L}\ab,\mu\ab) \mapsto (q^*\cs{L}\ab, (q^2)^* \mu\ab)$; this is an instance of \cite{cunningham-roe:13a}*{Lem. 1.4}.
+To see that $(q^*\cs{L}\ab, (q^2)^* \mu\ab)$ is indeed a linear character sheaf on $G$,
+verify \cite{cunningham-roe:13a}*{CS.3}.
+Now set $L(\cs{L}\ab) = (\cs{L},\nu)$, where $L : \Loc(G\ab) \to \Loc\der(G)$ is the comparison functor above, so $\cs{L} = q^*\cs{L}\ab$ and $\nu = \nu(\cs{L}\ab)$.
+Then $(\cs{L}, \mu,\nu)$ is an object in $\CS\der(G)$.
+If $\alpha\ab : (\cs{L}\ab,\mu\ab) \to (\cs{L}\ab',\mu\ab')$ is a morphism in $\CS(G\ab)$, 
+then $q^*(\alpha\ab) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha = q^*(\alpha\ab)$ is a morphism in $\CS(G)$.
+These observations define the comparison functor
+\[
+q\ab^* : \CS(G\ab) \to \CS\der(G)
+\]
+and also show that the functor $q^* : \CS(G\ab) \to \CS(G)$ factors according to the following commuting diagram of functors
+\begin{equation}\label{qH}
+\begin{tikzcd}
+\CS(G) &\arrow{l}[swap]{q^*} 
+\CS(G\ab) \arrow{dl}{q\ab^*}\\
+\arrow{u}{\text{forget}} \CS\der(G). & 
+\end{tikzcd}
+\end{equation}
+The definition of $q\ab^* : \CS(G\ab)\to \CS\der(G)$ will be revisited in the proof of Proposition~\ref{prop:CSGabab}.
 
@@
 
+\begin{proposition} \label{prop:CSGabab}
+Suppose $G$ is a smooth group scheme.  
+Then pullback along $q : G \to G\ab$ defines an equivalence $\CS(G\ab) \to \CS\der(G)$.
+\end{proposition}
+\begin{proof}
+%In light of Lemma~\ref{lemma:nubeta}, it suffices to prove that the comparison functor $q\ab^* : \CS(G\ab) \to \CS\der(G)$ is an equivalence. 
+Let $L^2 : \Loc(G^2\ab) \to \Loc\der(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$. 
+Then $L^2$ is also an equivalence by Lemma~\ref{lemma:descent}.
+Moreover, using Lemma~\ref{lem:HH}, we may rewrite the comparison functor $q\ab^*$ on objects by
+\[
+\begin{array}{rcl}
+\CS(G\ab) &\to& \CS\der(G) \\
+(\cs{L}\ab,\mu\ab) &\mapsto& (L(\cs{L}\ab), L^2(\mu\ab)).
+\end{array}
+\]
+and on morphisms by $\alpha \mapsto L(\alpha)$.
+The proposition now follows from the fact that both $L$ and $L^2$ are equivalences.
+\end{proof}
+
 \subsubsection{Descent}
@@
 
-If $\cs{L}\ab\in \Loc(G\ab)$ then $q^*\cs{L}\ab\in \Loc(G)$ comes equipped with a canonical isomorphism $\nu(\cs{L}\ab) : n^* \cs{L} \to p^* \cs{L}$ defined by the following diagram of isomorphisms.
-\[
-\begin{tikzcd}[column sep=40]
-n^*\cs{L} \arrow[equal]{d} \arrow[dashed]{r}{\nu(\cs{L}\ab)} &  \arrow[equal]{d} p^*\cs{L} \\
-n^* ( q^*\cs{L}\ab) \arrow{r}{q\circ n = q\circ p}
-& p^* (q^*\cs{L}\ab)
-\end{tikzcd}
-\]
-Then $(q^*\cs{L}\ab,\nu(\cs{L}\ab))$ satisfies \eqref{E1} and \eqref{E2}, so $(q^*\cs{L}\ab,\nu(\cs{L}\ab)) \in \Loc\der(G)$.
-Moreover, if $\alpha\ab : \cs{L}\ab \to \cs{L}\ab$ is a morphism in $\Loc(G\ab)$ then $q^*(\alpha\ab)$ satisfies the condition in \eqref{E3}, so $q^*(\alpha\ab)$ is a morphism in $\Loc\der(G)$.
-This defines the functor
-\[
-L : \Loc(G\ab)\to \Loc\der(G)
-\]
-
-\begin{lemma}\label{lemma:descent}
-The functor $L : \Loc(G\ab)\to \Loc\der(G)$ is an equivalence.
+\begin{lemma}\label{lemma:nubeta}
+Categories $\CS\der(G)$ and $\CS\ab(G)$ are equivalent.
 \end{lemma}
+
 \begin{proof}
-The quotient $q : G \to G\ab$ is an $G\der$-torsor in the fppf topology by \cite{demazure:SGA3-VIA}*{Thm. 3.2}, and thus a $G\der$-torsor in the fpqc topology.
-The lemma is now a result from descent theory, arguing as in \cite{Vistoli:notes}*{Theorem 4.46} for example. 
-\end{proof}
-
-Consider the functor
-\[
-q^* : \CS(G\ab) \to \CS(G)
-\]
-given on objects by $(\cs{L}\ab,\mu\ab) \mapsto (q^*\cs{L}\ab, (q^2)^* \mu\ab)$; this is an instance of \cite{cunningham-roe:13a}*{Lem. 1.4}.
-To see that $(q^*\cs{L}\ab, (q^2)^* \mu\ab)$ is indeed a linear character sheaf on $G$,
-verify \cite{cunningham-roe:13a}*{CS.3}.
-Now set $L(\cs{L}\ab) = (\cs{L},\nu)$, where $L : \Loc(G\ab) \to \Loc\der(G)$ is the comparison functor above, so $\cs{L} = q^*\cs{L}\ab$ and $\nu = \nu(\cs{L}\ab)$.
-Then $(\cs{L}, \mu,\nu)$ is an object in $\CS\der(G)$.
-If $\alpha\ab : (\cs{L}\ab,\mu\ab) \to (\cs{L}\ab',\mu\ab')$ is a morphism in $\CS(G\ab)$, 
-then $q^*(\alpha\ab) : (\cs{L},\mu) \to (\cs{L}',\mu')$ satisfies \cite{cunningham-roe:13a}*{CS4}, so $\alpha = q^*(\alpha\ab)$ is a morphism in $\CS(G)$.
-These simple observations define the comparison functor
-\[
-q\ab^* : \CS(G\ab) \to \CS\der(G)
-\]
-and also show that the functor $q^* : \CS(G\ab) \to \CS(G)$ factors according to the following commuting diagram of functors
-\begin{equation}\label{qH}
-\begin{tikzcd}
-\CS(G) &\arrow{l}[swap]{q^*} 
-\CS(G\ab) \arrow{dl}{q\ab^*}\\
-\arrow{u}{\text{forget}} \CS\der(G). & 
-\end{tikzcd}
-\end{equation}
-The definition of $q\ab^* : \CS(G\ab)\to \CS\der(G)$ will be revisited in the proof of the following result.
-
-\begin{proposition} \label{prop:CSGabab}
-Suppose $G$ is a smooth group scheme.  
-Then pullback along $q : G \to G\ab$ defines an equivalence $\CS(G\ab) \to \CSab(G)$.
-\end{proposition}
-\begin{proof}
-In light of Lemma~\ref{lemma:nubeta}, it suffices to prove that the comparison functor $q\ab^* : \CS(G\ab) \to \CS\der(G)$ is an equivalence. 
-Let $L^2 : \Loc(G^2\ab) \to \Loc\der(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$. 
-Then $L^2$ is also an equivalence by Lemma~\ref{lemma:descent}.
-Using Lemma~\ref{lem:HH}, we may rewrite the comparison functor $q\ab^*$ on objects by
+Let $i\der : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\der\times G$ by $j(h) = (h,1)$. 
+If $(\cs{L},\mu,\nu)\in \CS\der(G)$ then $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism. 
+\todo{Address referee's comment here}
+This defines a functor by
 \[
 \begin{array}{rcl}
-\CS(G\ab) &\to& \CS\der(G) \\
-(\cs{L}\ab,\mu\ab) &\mapsto& (L(\cs{L}\ab), L^2(\mu\ab))
+\CS\der(G) &\to& \CSab(G) \\
+(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,j^*(\nu))
 \end{array}
 \]
-and on morphisms by $\alpha \mapsto L(\alpha)$.
-The proposition now follows from the fact that both $L$ and $L^2$ are equivalences.
+on objects and trivially on morphisms.
+It is easy to verify that morphisms that commute with $\mu$ and $\nu$ also commute with $\mu$ and $j^*(\nu)$.
+This functor is an equivalence; its adjoint is given as follows.
+Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i\der(h),g)$.
+Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p^*\cs{L}$ by the following diagram.
+\[
+\begin{tikzcd}
+& n^* \cs{L} \arrow[equal]{dl}{m\circ k = n} \arrow[dashed]{r}{\nu} & p^*\cs{L} &  \\ 
+k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
+& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id_\cs{L}}
+\end{tikzcd}
+\]
+This defines the functor  $\CS\ab(G) \to \CS\der(G)$, after confirming that morphisms that commute with $\mu$ and $\beta$ also commute with $\mu$ and $\nu$.
 \end{proof}
@@
 \]
-where $\pi_0(\bar{G})_{\Frob{}}$ denotes the covariants of the action of Frobenius on
+where $\pi_0(\bar{G})_{\Frob{}}$ denotes the coinvariants of the action of Frobenius on
 the component group of $\bar{G}$

### 2017-06-28 Geometric types.tex
Working on PGL2/SL2 examples
Push before running off ...

@@
 \newcommand{\bCS}{{\CS_0}}
-\newcommand{\CSab}{\CS_{\operatorname{ab}}}
+%\newcommand{\CSab}{\CS_{\operatorname{ab}}}
 \newcommand{\catname}[1]{\normalfont{\textsf{#1}}}
@@
 \begin{definition}\label{def:CSab}
-Let $\CSab(G)$ denote the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu) \in \CS(G)$ and
-$\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism in $\CS(G\der)$.
+Let $\CS\ab(G)$ denote the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu) \in \CS(G)$ and
+$\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism of Weil local systems on $G\der$.
 A morphism $(\cs{L},\mu,\beta)\to (\cs{L}',\mu',\beta')$ is a morphism $\alpha : (\cs{L},\mu)\to (\cs{L}',\mu')$
@@
 Both are morphisms of $\Fq$-schemes.
-Set $m' = i \circ m \circ \theta$ and let $i\der : G\der\to G$ be inclusion; then $i\der\circ c = m \circ (m \times m')$.
+Set $m' = i \circ m \circ \theta$ and let $j\der : G\der\to G$ be inclusion; then $j\der\circ c = m \circ (m \times m')$.
 Then $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ determines the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ by the diagram of isomorphisms below.
@@
 	&  c^*((\EE)_{G\der}) \arrow[equal]{d} \\
-\arrow{d}[swap]{i\der\circ c = m \circ (m \times m')} c^* i\der^* \cs{L} 
+\arrow{d}[swap]{j\der\circ c = m \circ (m \times m')} c^* j\der^* \cs{L} 
 	&   (\EE)_{G\times G} \\
@@
 \end{equation}
-In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations; so, for example, the middle left isomorphism comes from $(m\times m')^* m^* \iso c^* i\der^*$ since $i\der\circ c = m \circ (m \times m')$.
+In the diagram above, the arrows labeled with equations come from canonical isomorphisms of functors on Weil sheaves derived from the equations; so, for example, the middle left isomorphism comes from $(m\times m')^* m^* \iso c^* j\der^*$ since $j\der\circ c = m \circ (m \times m')$.
 Using the monoidal structure of the category of Weil local systems on $G\times G$, the isomorphism $\gamma' : m^*\cs{L} \otimes \theta^* m^* i^*\cs{L} \to (\EE)_{G\times G}$ defines an isomorphism
@@
 \begin{definition}\label{def:CCS}
-The category $\CCS(G)$ of commutative character sheaves on $G$ is the full subcategory of $\CSab(G)$ consisting of triples $(\cs{L},\mu,\beta)$ such that the following diagram of Weil sheaves on $G \times G$ commutes:
+The category $\CCS(G)$ of commutative character sheaves on $G$ is the full subcategory of $\CS\ab(G)$ consisting of triples $(\cs{L},\mu,\beta)$ such that the following diagram of Weil sheaves on $G \times G$ commutes:
   \[
@@
 
-In this section we give an equivalence of categories between $\CS(G\ab)$ and $\CSab(G)$ and use it to describe
-the pullback functor $q^* : \CS(G\ab) \to \CS(G)$ in terms of the forgetful functor $\CSab(G) \to \CS(G)$, where $q : G\to G\ab$ is the abelianization quotient with kernel $G\der$.
+In this section we give an equivalence of categories between $\CS(G\ab)$ and $\CS\ab(G)$ and use it to describe
+the pullback functor $q^* : \CS(G\ab) \to \CS(G)$ in terms of the forgetful functor $\CS\ab(G) \to \CS(G)$, where $q : G\to G\ab$ is the abelianization quotient with kernel $G\der$.
 But first, in order to study commutative character sheaves, we need some auxiliary categories.
@@
 \end{equation}
-and such that the following diagram of isomorphisms of local systems on $G\der\times G\der\times G$ commutes. 
+and such that the following diagram of isomorphisms of Weil local systems on $G\der\times G\der\times G$ commutes. 
 \begin{equation}\label{E2}
@@
 \begin{lemma}\label{lemma:descent}
+Suppose $G$ is a smooth group scheme.  
 The functor $L : \Loc(G\ab)\to \Loc\der(G)$ is an equivalence.
@@
 \end{proof}
-
-Observe that if $(\cs{L},\nu)\in \Loc\der(G)$ then ... \todo{New lemma?}
 
@@
 
-\subsubsection{Descent}
-
-We may now relate $\CSab(G)$ to $\CS(G\ab)$.
-To do so, we use decent along $q : G \to G\ab$.
+\subsubsection{Rigidification} \todo{Not sure that's the right subsection title. Other  suggestions?}
+
+We may now relate $\CS\ab(G)$ to $\CS(G\ab)$.
+%To do so, we use decent along $q : G \to G\ab$.
 
@@
 \begin{proof}
-Let $i\der : G\der \to G$ be the kernel of $q:G \to G\ab$ and define $j : G\der \to G\der\times G$ by $j(h) = (h,1)$. 
+We begin by defining a functor $\CS\ab(G) \to \CS\der(G)$.
+Let $j\der : G\der \to G$ be the kernel of $q:G \to G\ab$ 
+Define $k: G\der\times G\to G\times G$ by $k(h,g) = (j\der(h),g)$.
+Then for $(\cs{L},\mu,\nu) \in \CS\der(G)$, define $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ by the following diagram.
+\[
+\begin{tikzcd}
+& n^* \cs{L} \arrow[equal]{dl}{m\circ k = n} \arrow{r}{\nu} & p^*\cs{L} &  \\ 
+k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
+& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id_\cs{L}}
+\end{tikzcd}
+\]
+Then $\beta = r\der \circ j^*(\nu)$, where $r\der : (\cs{L}_1)_{G\der} \to (\EE)_{G\der}$ is the isomorphism of constant local systems  determined by the rigidification $r: \cs{L}_1 \to \EE$ of $\cs{L}$ determined by $\mu$  (see \cite{cunningham-roe:13a}*{Remark~1.11}).
+To show that $(\cs{L},\mu,\beta) \in \CS\ab(G)$, we must see that $\beta$ is a morphism in $\CS(G\der)$.
+By Proposition~\ref{prop:CSGabab}, $\cs{L} = q^*\cs{L}\ab$.
+
+This defines the functor  $\CS\ab(G) \to \CS\der(G)$, after confirming that morphisms that commute with $\mu$ and $\beta$ also commute with $\mu$ and $\nu$.
+
+and define $j : G\der \to G\der\times G$ by $j(h) = (h,1)$.
+
 If $(\cs{L},\mu,\nu)\in \CS\der(G)$ then $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism. 
@@
 \begin{array}{rcl}
-\CS\der(G) &\to& \CSab(G) \\
+\CS\der(G) &\to& \CS\ab(G) \\
 (\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,j^*(\nu))
@@
 This functor is an equivalence; its adjoint is given as follows.
-Define $k: G\der\times G\to G\times G$ by $k(h,g) = (i\der(h),g)$.
-Then for $(\cs{L},\mu,\beta) \in \CSab(G)$, define $\nu : n^*\cs{L} \to p^*\cs{L}$ by the following diagram.
-\[
-\begin{tikzcd}
-& n^* \cs{L} \arrow[equal]{dl}{m\circ k = n} \arrow[dashed]{r}{\nu} & p^*\cs{L} &  \\ 
-k^* m^* \cs{L} \arrow{dr}{k^*(\mu)} &&& (\EE)_{G\der} \boxtimes \cs{L} \arrow[equal]{ul} \\
-& k^*(\cs{L}\boxtimes\cs{L}) \arrow[equal]{r} & \cs{L}\vert_{G\der}\boxtimes \cs{L} \arrow{ur}{\beta\boxtimes \id_\cs{L}}
-\end{tikzcd}
-\]
-This defines the functor  $\CS\ab(G) \to \CS\der(G)$, after confirming that morphisms that commute with $\mu$ and $\beta$ also commute with $\mu$ and $\nu$.
+
 \end{proof}
@@
 \begin{tikzcd}
-\CS(G\der) & \arrow{l}[swap]{i\der^*} \CS(G) &\arrow{l}[swap]{q^*} 
+\CS(G\der) & \arrow{l}[swap]{j\der^*} \CS(G) &\arrow{l}[swap]{q^*} 
 \CS(G\ab) \arrow{dl}{q\ab^*} \\
-& \CSab(G) \arrow{u}{\text{forget}}  & 
-\end{tikzcd}
-\]
-
-Now, suppose $(\cs{L},\mu)\in \CS(G)$ and there is an isomorphism $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ in $\CS(G\der)$, so that
-$(\cs{L},\mu,\beta) \in \CSab(G)$.
+& \CS\ab(G) \arrow{u}{\text{forget}}  & 
+\end{tikzcd}
+\]
+
+Now, suppose $(\cs{L},\mu)\in \CS(G)$ and there is an isomorphism $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ so that
+$(\cs{L},\mu,\beta) \in \CS\ab(G)$.
 By Proposition \ref{prop:CSGabab}, there is some $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$ with $(\cs{L},\mu,\beta) \iso q\ab^*(\cs{L}\ab,\mu\ab)$.
@@
 \[
-i\der^*(\cs{L},\mu) \iso i\der^*q^*(\cs{L}\ab,\mu\ab)
+j\der^*(\cs{L},\mu) \iso j\der^*q^*(\cs{L}\ab,\mu\ab)
 \]
  in $\CS(G\der)$.
-Since $q\circ i\der = 1$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$ in $\CS(G\der)$.
+Since $q\circ j\der = 1$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
 \end{proof}
@@
 \begin{proof}
-By Proposition~\ref{prop:CSGabab}, it suffices to find the set of isomorphism classes in $\CSab(G)$ mapping to
+By Proposition~\ref{prop:CSGabab}, it suffices to find the set of isomorphism classes in $\CS\ab(G)$ mapping to
 $(\cs{L},\mu)$ under the forgetful functor.  By the previous corollary this set is nonempty.
@@
 automorphism of the constant sheaf on $G\der$.  Conversely, if $\varphi$ is an automorphism of $(\EE)_{G\der}$
-and $(\cs{L},\mu,\beta) \in \CSab(G)$ then $(\cs{L},\mu,\varphi \circ \beta) \in \CSab(G)$.  As in \cite{cunningham-roe:13a}*{Theorem 3.9},
+and $(\cs{L},\mu,\beta) \in \CS\ab(G)$ then $(\cs{L},\mu,\varphi \circ \beta) \in \CS\ab(G)$.  As in \cite{cunningham-roe:13a}*{Theorem 3.9},
 the automorphism group is isomorphic to $\Hom(\pi_0(\bar{G}\der)_{\Frob{}}, \EEx)$.  Finally, we note that any
@@
 We are now in a position to prove that commutative character sheaves on $G$ match perfectly with commutative character sheaves on $G\ab$.
-We start with a method that will allow us to situate the diagram in Definition \ref{def:CCS} within $\CSab(G^2)$.
+We start with a method that will allow us to situate the diagram in Definition \ref{def:CCS} within $\CS\ab(G^2)$.
 
@@
 Suppose $G$ is commutative, so $G\der = 1$. 
-Suppose $(\cs{L},\mu,\beta)$ is an object in $\CSab(G)$.
+Suppose $(\cs{L},\mu,\beta)$ is an object in $\CS\ab(G)$.
 Then $\beta : \cs{L}_1\to \EE$ is an isomorphism in $\CS(1)$, which is unique by \cite{cunningham-roe:13a}*{Theorem 3.9}.

### 2017-06-28 Geometric types.tex
Finished  addressing Comments  1 and  2 in the file.  Letter the  the reviewer is still needed.

@@
 
-\subsubsection{Rigidification} \todo{Not sure that's the right subsection title. Other  suggestions?}
+\subsubsection{Rigidification}
 
@@
 Then for $(\cs{L},\mu,\nu) \in \CS\der(G)$, define $\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ by the following diagram.
-\[
+\begin{equation}\label{eqn:betanu}
 \begin{tikzcd}
@@
 \end{tikzcd}
-\]
-Then $\beta = r\der \circ j^*(\nu)$, where $r\der : (\cs{L}_1)_{G\der} \to (\EE)_{G\der}$ is the isomorphism of constant local systems  determined by the rigidification $r: \cs{L}_1 \to \EE$ of $\cs{L}$ determined by $\mu$  (see \cite{cunningham-roe:13a}*{Remark~1.11}).
-To show that $(\cs{L},\mu,\beta) \in \CS\ab(G)$, we must see that $\beta$ is a morphism in $\CS(G\der)$.
-By Proposition~\ref{prop:CSGabab}, $\cs{L} = q^*\cs{L}\ab$.
-
-This defines the functor  $\CS\ab(G) \to \CS\der(G)$, after confirming that morphisms that commute with $\mu$ and $\beta$ also commute with $\mu$ and $\nu$.
-
-and define $j : G\der \to G\der\times G$ by $j(h) = (h,1)$.
-
-If $(\cs{L},\mu,\nu)\in \CS\der(G)$ then $j^*(\nu) : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism. 
-\todo{Address referee's comment here}
-This defines a functor by
-\[
-\begin{array}{rcl}
-\CS\der(G) &\to& \CS\ab(G) \\
-(\cs{L},\mu,\nu) &\mapsto& (\cs{L},\mu,j^*(\nu))
-\end{array}
-\]
-on objects and trivially on morphisms.
-It is easy to verify that morphisms that commute with $\mu$ and $\nu$ also commute with $\mu$ and $j^*(\nu)$.
-This functor is an equivalence; its adjoint is given as follows.
-
+\end{equation}
+Then $\beta = r\der \circ j^*(\nu)$, where $r\der : (\cs{L}_1)_{G\der} \to (\EE)_{G\der}$ is the isomorphism of constant local systems  determined by the rigidification $r: \cs{L}_1 \to \EE$ of $\cs{L}$ determined by $\mu$ (see \cite{cunningham-roe:13a}*{Remark~1.11}) so that
+\begin{equation}\label{eqn:rigidification}
+\begin{tikzcd}
+\cs{L}_1 \arrow{r}{r} \arrow{d}{\mu_{(1,1)}}  & \EE \arrow[equal]{d} \\
+\cs{L}_1\otimes\cs{L}_1 \arrow{r}{r\otimes r}  & \EE\otimes  \EE
+\end{tikzcd}
+\end{equation}
+commutes where, as usual, $=$ denotes a canonical isomorphism.
+%
+To show that $(\cs{L},\mu,\beta) \in \CS\ab(G)$, we must see that $\beta$ is a morphism in $\CS(G\der)$ by showing that the following diagram commutes in $\Loc(G\der^2)$.
+\begin{equation}\label{eqn:betaGder}
+\begin{tikzcd}
+m\der^*\cs{L}\vert_{G\der} \arrow{rr}{m\der^* \beta} \arrow[equal]{d} && \arrow[equal]{d} (\EE)_{G\der^2}\\
+\cs{L}\vert_{G\der} \boxtimes \cs{L}\vert_{G\der} \arrow{rr}{\beta\boxtimes\beta} &&  (\EE)_{G\der}\boxtimes (\EE)_{G\der} 
+\end{tikzcd}
+\end{equation}
+By Proposition~\ref{prop:CSGabab}, $\cs{L} = q^*\cs{L}\ab$, for some $(\cs{L}\ab,\mu\ab)\in \CS(G\ab)$.
+Thus, $\cs{L}\vert_{G\der} = (\cs{L}_1)_{G\der}$ and the diagram above becomes a diagram of constant Weil local systems on $G\der^2$.
+We can therefore test  whether  diagram commutes by evaluating all local systems at $(1,1)\in G\der^2$.
+Doing this recovers \eqref{eqn:rigidification} from \eqref{eqn:betaGder}, so \eqref{eqn:rigidification} commutes.
+%
+After confirming that morphisms that commute with $\mu$ and $\beta$ also commute with $\mu$ and $\nu$, this concludes the definition of the functor  $\CS\ab(G) \to \CS\der(G)$.
+
+The adjoint functor $\CS\der(G) \to \CS\ab(G)$ is given by a  similar  strategy: given $(\cs{L},\mu,\beta)\in \CS\der(G)$, define $(\cs{L},\mu,\nu)$ again using  \eqref{eqn:betanu}.
+Then and verify that $(\cs{L},\nu)$ satisfies \eqref{E2} as it applies here, so that $(\cs{L},\nu)\in \Loc\der(G)$.
+After confirming that morphisms that commute with $\mu$ and $\nu$ also commute with $\mu$ and $\beta$, this concludes the definition of the functor  $\CS\der(G) \to \CS\ab(G)$.
+From these constructions,  it is now clear that $\CS\der(G) \to \CS\ab(G)$ is an equivalence.
 \end{proof}

### 2017-06-28 Geometric types.tex
Add section on character sheaves for SL(2,3), fix Section 3 to account for characters that don't vanish on Gder(k)

--- 2017-06-28 Geometric types.tex
@@
 \usepackage{amsrefs}
+\usepackage{multirow}
 % Fonts
@@
 \newcommand{\FF}{{\mathbb{F}}}
+\newcommand{\FFF}{{\mathbf{F}_3}}
 \newcommand{\ZZ}{{\mathbb{Z}}}
@@
 \DeclareMathOperator{\PGL}{PGL}
+\DeclareMathOperator{\PSL}{PSL}
 \newcommand{\gal}[1]{{\operatorname{Gal}\hskip-1pt\left( {\bar #1}/#1 \right)}}
@@
 \newcommand{\dualcs}[1]{\cs{#1}^\dagger}
+\newcommand{\IC}{\mathcal{IC}}
 %% Categories
@@
 
+% Matrices
+\newcommand{\smat}[4]{$\left(\begin{smallmatrix}#1 & #2 \\ #3 & #4 \end{smallmatrix}\right)$}
+
 %% Hyphenation override
@@
 
-We now consider the case of a smooth group scheme without the commutativity assumption.  We start
-by relating linear character sheaves on $G$ to character sheaves on its abelianization.
-
-If $\chi \in G(k)^*$ is a character, it must vanish on the derived subgroup $G\der(k)$. \todo{Error} 
-Kamgarpour gives an example \cite{kamgarpour:09a}*{(1.1)} of a linear character sheaf
-on $G = \PGL_n$ that does not vanish on $G\der = \PGL_n$, defined by the extension
-\[
-1 \to \mu_n \to \SL_n \to \PGL_n \to 1
-\]
-together with a non-trivial character of $\mu_n(k)$. \todo{Small change here.}
-In order to obtain a relationship between linear character sheaves on $G$ and characters of $G(k)$,
-he opts to give a different definition of commutator and, in doing so, introduces a `stacky abelianization' of $G$ in order to geometrize characters of $G(\Fq)$.
- Since we have already seen the need to adapt the
-notion of character sheaf, even in the commutative case, we instead add restrictions
-to the definition of commutative character sheaf and leave the definition of $G\der$ unchanged, allowing us to use the schematic abelianization of $G$ in the geometrization of characters of $G(\Fq)$.
+We now consider the case of a smooth group scheme without the commutativity assumption.  Our approach
+is to relate linear character sheaves on $G$ to character sheaves on its abelianization $G\ab = G / G\der$.
+While every character $\chi \in G(k)^*$ vanishes on $G(k)\der$, it may not vanish on $G\der(k)$.  For example,
+if $k$ has odd characteristic then there are nontrivial characters $\PGL_2(k) \to \EEx$ vanishing on
+$\PGL_2(k)\der = \PSL_2(k)$ (see Section \ref{sec:badchar}).  In passing to $G\ab$,
+we may only hope to geometrize characters that vanish on all of $G\der(k)$.
 
@@
 To prove Theorem~\ref{thm:Gab} we use descent theory in Section~\ref{ssec:descent}, in the process giving insight into Definition~\ref{def:CCS}. 
-Section~\ref{sec:noncom} concludes with Theorem~\ref{thm:geo}, showing that the dictionary from $\CCS(G)$ to characters of $G(k)$ is as precise as possible.
+Section~\ref{sec:noncom} concludes with Theorem~\ref{thm:geo}, showing that the dictionary from $\CCS(G)$
+to characters of $G(k)$ in fact encompasses every character vanishing on $G\der(k)$.
 
@@
 
-Theorem~\ref{thm:Gab} shows that $\CCS(G)$ is a categorical solution to the problem that linear character sheaves on $G$ need not be trivial on $G\der$, as discussed at the beginning of Section~\ref{sec:noncom}.
-At the same time, changing $\CS(G)$ to $\CCS(G)$ resolves the lack of bijectivity in \cite{cunningham-roe:13a}*{Theorem 3.6}.
-We may also use Theorem~\ref{thm:Gab} to give a description of the morphisms and the isomorphism classes of objects in $\CCS(G)$.
+We may use Theorem~\ref{thm:Gab} to give a description of the morphisms and the isomorphism classes of objects in $\CCS(G)$.
 
@@
 \ & & \CCSiso{G\ab} \arrow{d}{\TrFrob{}}[swap]{\iso} \arrow{r}{\iso} & \CCSiso{G} \arrow{d}{\TrFrob{}}& \\
-1 \arrow{r} & \Delta_G^* \arrow{r} & G\ab(k)^* \arrow{r} & G(k)^* \arrow{r} & 1,
+1 \arrow{r} & \Delta_G^* \arrow{r} & G\ab(k)^* \arrow{r} & G(k)^* \arrow{r} & G\der(k)^* \arrow{r} & 1,
 \end{tikzcd}
@@
 where $\Delta_G$ is the image of the connecting homomorphism $G\ab(\Fq) \to \Hh^1(\Fq, G\der)$. 
-Thus the category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the following sense: for every group homomorphism $\chi : G(\Fq) \to \EEx$ there is an object $(\cs{L},\mu,\beta)$ in $\CCS(G)$ such that $\trFrob{\cs{L}} = \chi$.
-While the geometrization of $\chi : G(\Fq) \to \EEx$ is not unique, the group of isomorphism classes of possibilities are enumerated by $\Delta_G^*$.
+Thus the category $\CCS(G)$ geometrizes characters of $G(\Fq)$ in the following sense: for every group homomorphism $\chi : G(\Fq) \to \EEx$ that vanishes on $G\der(\Fq)$, there is an object $(\cs{L},\mu,\beta)$ in $\CCS(G)$ such that $\trFrob{\cs{L}} = \chi$.
+While the geometrization of $\chi$ is not unique, the isomorphism classes of possibilities are enumerated by $\Delta_G^*$.
 \end{theorem}
@@
 \[
-1 \to G(k) / G\der(k) \to G\ab(k) \to \Delta_G \to 1.
-\]
-Applying $\Hom(-, \EEx)$ and using the fact that every homomorphism $G(k) \to \EEx$ vanishes on $G\der(k)$,\todo{Error here} we get
-\[
-1 \to \Delta_G^* \to G\ab(k)^* \to G(k)^* \to 1.
-\]
+1 \to G\der(k) \to G(k) \to G\ab(k) \to \Delta_G \to 1.
+\]
+Applying $\Hom(-, \EEx)$ yields the bottom row in the statement.
+
 By Theorem~\ref{thm:Gab}, the map $\CCSiso{G\ab} \to \CCSiso{G}$ is an isomorphism.
@@
 
-\begin{remark}
-Note that when $\Hh^1(k,G\der) = 0$ then $\CCSiso{G} \iso G(\Fq)^*$, so
-we succeed in geometrizing characters of $G(k)$ on the nose.
-\end{remark}
+\section{Examples of Nontrivial Characters on the Derived Subgroup} \label{sec:badchar}
+
+In this section we give two examples of characters of $G(k)$ that do not vanish on $G\der(k)$.
+
+\subsection{\texorpdfstring{$\PGL_2(k)$}{PGL(2, k)}}
+
+Let $G = \PGL_2$ over a finite field $k$ of odd characteristic.
+Then $G\der = G$, but $G(k)\der = \PSL_2(k)$ has index $2$ in $G(k)$.
+There is thus a nontrivial character $\chi : G(k) \to \{\pm 1\} \subset \EEx$.
+We may construct a linear character sheaf with trace $\chi$ as follows.
+Consider the standard isogeny $f : \SL_2 \to \PGL_2$ with kernel $\mu_2$ and the nontrivial map $\psi : \mu_2 \to \EEx$.
+Then the pushforward $f_!
+\EE$ of the constant sheaf on $\SL_2$ is a $2$-dimensional local system, and its $\psi$-isotypic component $(f_!
+\EE)_\psi$ is a linear character sheaf on $\PGL_2$ with trace of Frobenius $\chi$ (c.f.
+\cite{cunningham-roe:13a}*{Prop 1.10}).
+
+\subsection{\texorpdfstring{$\SL_2(\FFF)$}{\SL(2, 3)}}
+
+Let $G = \SL_2$ over $\FFF$.
+Then $G\der = G$, but $G(k)\der$ is the subgroup of semisimple elements, isomorphic to the quaternion group $Q_8$ and of index $3$.
+There is thus a nontrivial character $\chi : G(k) \to \mu_3 \subset \EEx$.
+The method described above for producing a linear character sheaf corresponding to this character no longer works, since $\SL_2$ is simply connected and thus has no discrete isogenies mapping onto it.
+We may still produce a local system with the correct trace of Frobenius, by pushing forward the constant sheaf along the Lang isogeny and picking out the isotypic component corresponding to $\chi$.
+However, since $\SL_2$ is nonabelian, the Lang isogeny is not a homomorphism and the resulting local system is not a linear character sheaf.
+
+Alternatively, we can use the fact that Lusztig's character sheaves provide a basis for the space of class functions \cite{lusztig:86a}*{Cor.
+25.7} to give a different geometrization of $\chi$.
+Lusztig's character sheaves are constructed by perverse extension of local systems on a certain stratification of $G$.
+In the case of $\SL_2$, there are five strata:
+
+\vspace{0.1in}
+
+\begin{tabular}{|l|l|}
+\hline
+$C_3$ & regular semisimple elements \\
+$C_2$ & regular unipotent elements \\
+$C_2^-$ & $\{-u : \mbox{ regular unipotent $u$}\}$ \\
+$1$ & $\{1\}$ \\
+$-1$ & $\{-1\}$ \\
+\hline
+\end{tabular}
+
+\vspace{0.1in}
+
+Suppose that $C$ is a stratum and $x \in C$.
+Local systems on $C$ are classified up to isomorphism by irreducible representations of $\pi_0(Z_G(x))$.
+This component group is trivial for $C_3$, $1$ and $-1$, and of order $2$ for $C_2$ and $C_2^-$.
+Denote the nontrivial local systems on $C_2$ and $C_2^-$ by $\cs{E}_{C_2}$ and $\cs{E}_{C_2^-}$.
+Then the character sheaves on $\SL_2$ are the following, where the second column gives a decomposition in the Grothendieck group of standard sheaves on $G$.
+
+\vspace{0.1in}
+
+\begin{tabular}{|l|l|ccccccc|}
+\hline
+Perverse & Standard & \multicolumn{7}{|c|}{Trace of Frobenius values} \\ \cline{3-9}
+
+Sheaf & Sheaves & \smat1001 & \smat2002 & \smat0120 & \smat1101 & \smat1201 & \smat2102 & \smat2202 \\
+\hline
+$\IC(\mathbf{1}_{C_3})$ & $\mathbf{1}_{C_3}[3]$ & -1 & -1 & -1 & -1 & -1 & -1 & -1 \\
+$\IC(\mathbf{1}_{C_2})$ & $\mathbf{1}_{C_2}[2] \oplus \mathbf{1}_1[0]$ & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
+$\IC(\cs{E}_{C_2})$ & $\cs{E}_{C_2}[2]$ & 0 & 0 & 0 & $\sqrt{-3}$ & $-\sqrt{-3}$ & 0 & 0 \\
+$\IC(\mathbf{1}_{C_2^-})$ & $\mathbf{1}_{C_2^-}[2] \oplus \mathbf{1}_{-1}[0]$ & 0 & 1 & 0 & 0 & 0 & 1 & 1 \\
+$\IC(\cs{E}_{C_2^-})$ & $\cs{E}_{C_2^-}[2]$ & 0 & 0 & 0 & 0 & 0 & $\sqrt{-3}$ & $-\sqrt{-3}$ \\
+$\IC(\mathbf{1}_1)$ & $\mathbf{1}_1[0]$ & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
+$\IC(\mathbf{1}_{-1})$ & $\mathbf{1}_{-1}[0]$ & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
+\hline
+\end{tabular}
+
+\vspace{0.1in}
+\noindent Using the trace of Frobenius values, we find that 
+\[
+- \IC(\mathbf{1}_{C_3}) - \frac32 \IC(\mathbf{1}_{C_2}) + \frac12 \IC(\cs{E}_{C_2}) - \frac32 \IC(\mathbf{1}_{C_2^-}) - \frac12 \IC(\cs{E}_{C_2^-}) + \frac32 \IC(\mathbf{1}_1) + \frac32 \IC(\mathbf{1}_{-1})
+\]
+also geometrizes $\chi$.  Note that all seven character sheaves appear in this geometrization, even though we start just with a character.
+
+\subsection{The True Commutator}
+
+Kamgarpour gives an example \cite{kamgarpour:09a}*{(1.1)} of a linear character sheaf
+on $G = \PGL_n$ that does not vanish on $G\der = \PGL_n$, defined by the extension
+\[
+1 \to \mu_n \to \SL_n \to \PGL_n \to 1
+\]
+together with a non-trivial character of $\mu_n(k)$. \todo{Small change here.}
+In order to obtain a relationship between linear character sheaves on $G$ and characters of $G(k)$,
+he opts to give a different definition of commutator and, in doing so, introduces a `stacky abelianization' of $G$ in order to geometrize characters of $G(\Fq)$.
+ Since we have already seen the need to adapt the
+notion of character sheaf, even in the commutative case, we instead add restrictions
+to the definition of commutative character sheaf and leave the definition of $G\der$ unchanged, allowing us to use the schematic abelianization of $G$ in the geometrization of characters of $G(\Fq)$.
 
@@
 
+\bib{lusztig:86a}{article}{
+	Author = {George Lusztig},
+	Date-Added = {2017-06-28 19:26:19 +0000},
+	Date-Modified = {2017-06-28 19:28:23 +0000},
+	Journal = {Advances in Math.},
+	Keywords = {qcsheaves},
+	Number = {2},
+	Pages = {{103--155}},
+	Title = {{Character sheaves V}},
+	Volume = {61},
+	Year = {1986}}
+
 \bib{lusztig:disconnected1}{article}{

### 2017-06-28 Geometric types.tex
Promoted Lemma to Proposition in Rigidification.

@@
 \begin{proof}
-%In light of Lemma~\ref{lemma:nubeta}, it suffices to prove that the comparison functor $q\ab^* : \CS(G\ab) \to \CS\der(G)$ is an equivalence. 
 Let $L^2 : \Loc(G^2\ab) \to \Loc\der(G^2)$ be the comparison functor for the quotient $q^2  : G^2 \to G^2\ab$. 
@@
 
-\begin{lemma}\label{lemma:nubeta}
-Categories $\CS\der(G)$ and $\CS\ab(G)$ are equivalent.
-\end{lemma}
+\begin{proposition}\label{prop:nubeta}
+The categories $\CS\ab(G)$ and $\CS(G\ab)$ are equivalent.
+\end{proposition}
 
 \begin{proof}
+In light of Proposition~\ref{prop:CSGabab}, it suffices to exhibit an equivalence  between $\CS\der(G)$ and $\CS\ab(G)$.
+
 We begin by defining a functor $\CS\ab(G) \to \CS\der(G)$.

### 2017-06-30 Geometric types.tex
Working on new Section 4

@@
 
-\section{Examples of Nontrivial Characters on the Derived Subgroup} \label{sec:badchar}
-
-In this section we give two examples of characters of $G(k)$ that do not vanish on $G\der(k)$.
-
-\subsection{\texorpdfstring{$\PGL_2(k)$}{PGL(2, k)}}
-
-Let $G = \PGL_2$ over a finite field $k$ of odd characteristic.
-Then $G\der = G$, but $G(k)\der = \PSL_2(k)$ has index $2$ in $G(k)$.
-There is thus a nontrivial character $\chi : G(k) \to \{\pm 1\} \subset \EEx$.
-We may construct a linear character sheaf with trace $\chi$ as follows.
-Consider the standard isogeny $f : \SL_2 \to \PGL_2$ with kernel $\mu_2$ and the nontrivial map $\psi : \mu_2 \to \EEx$.
-Then the pushforward $f_!
-\EE$ of the constant sheaf on $\SL_2$ is a $2$-dimensional local system, and its $\psi$-isotypic component $(f_!
-\EE)_\psi$ is a linear character sheaf on $\PGL_2$ with trace of Frobenius $\chi$ (c.f.
-\cite{cunningham-roe:13a}*{Prop 1.10}).
+\section{Geometrizing Characters Nontrivial on the Derived Subgroup} \label{sec:badchar}
+
+If $\chi$ is a character of $G(k)$ vanishing on $G\der(k)$, Section \ref{sec:noncom} provides a \emph{local system} $\cs{L}$ that is \emph{conjugation equivariant} and satisfies $\TrFrob{}(\cs{L}) = \chi$.
+In this section, we give methods for geometrizing characters that do not vanish on $G\der(k)$, though the results may not be local systems or conjugation invariant.
+
+\subsection{Pushforward along the Lang isogeny}
+
+For connected, commutative groups, the standard method for geometrizing a character $\chi$ is to use the Lang isogeny $L : G \to G$, defined by $L(x) = x^{-1}\Frob{G}(x)$.
+Then the pushforward $L_!
+(\EE)_G$ of the constant sheaf decomposes into a direct sum of rank $1$ local systems according to characters of the automorphism group $G(k)$ of the cover $L$.
 
@@
 also geometrizes $\chi$.  Note that all seven character sheaves appear in this geometrization, even though we start just with a character.
+
+\subsection{\texorpdfstring{$\PGL_2(k)$}{PGL(2, k)}}
+
+Let $G = \PGL_2$ over a finite field $k$ of odd characteristic.
+Then $G\der = G$, but $G(k)\der = \PSL_2(k)$ has index $2$ in $G(k)$.
+There is thus a nontrivial character $\chi : G(k) \to \{\pm 1\} \subset \EEx$.
+We may construct a linear character sheaf with trace $\chi$ as follows.
+Consider the standard isogeny $f : \SL_2 \to \PGL_2$ with kernel $\mu_2$ and the nontrivial map $\psi : \mu_2 \to \EEx$.
+Then the pushforward $f_!
+\EE$ of the constant sheaf on $\SL_2$ is a $2$-dimensional local system, and its $\psi$-isotypic component $(f_!
+\EE)_\psi$ is a linear character sheaf on $\PGL_2$ with trace of Frobenius $\chi$ (c.f.
+\cite{cunningham-roe:13a}*{Prop 1.10}).
 

### 2017-06-30 Geometric types.tex
Push before going home.

@@
 
+\begin{center}
+\begin{spacing}{1.3}
 \begin{tabular}{|l|l|}
@@
 \end{tabular}
+\end{spacing}
+\end{center}
+
+%\vspace{0.1in}
+\noindent
+Each Weil character sheaf on $\SL_2$ over $\FFF$ is the perverse extension of one of the following local systems: the rank-$1$ constant sheaf $\mathbf{1}_{C_3}$ (resp.
+$\mathbf{1}_{C_2}$, $\mathbf{1}_{C_2^-}$, $\mathbf{1}_{1}$,  $\mathbf{1}_{-1}$) on $C_3$ (resp.
+$C_2$, $C_2^-$, $1$, $-1$), or the non-trivial local system $\cs{E}_{C_2}$  (resp.
+$\cs{E}_{C_2^-}$) trivialized by the  double cover of $C_2$ (resp.
+$C_2^-$).
+The following table describes these perverse sheaves by showing how they decompose in the Grothendieck group into conjugation-equivariant standard sheaves on $\SL_2$, and also gives the values of the trace of Frobenius of each Weil character sheaf on $\SL_2$ on the $7$ conjugacy classes in $\SL_2(\FFF)$.
 
@@
 
-Suppose that $C$ is a stratum and $x \in C$.
-Local systems on $C$ are classified up to isomorphism by irreducible representations of $\pi_0(Z_G(x))$.
-This component group is trivial for $C_3$, $1$ and $-1$, and of order $2$ for $C_2$ and $C_2^-$.
-Denote the nontrivial local systems on $C_2$ and $C_2^-$ by $\cs{E}_{C_2}$ and $\cs{E}_{C_2^-}$.
-Then the character sheaves on $\SL_2$ are the following, where the second column gives a decomposition in the Grothendieck group of standard sheaves on $G$.
+\begin{spacing}{1.3}
+\[
+\begin{array}{|l|l|ccccccc|}
+\hline
+\text{Perverse} & \text{Standard} & \multicolumn{7}{|c|}{\text{Trace of Frobenius values}} \\ \cline{3-9}
+\text{Sheaf} & \text{Sheaves} & (\begin{smallmatrix}1 & 0\\ 0 & 1\end{smallmatrix}) & (\begin{smallmatrix}2 & 0\\ 0 & 2\end{smallmatrix}) & (\begin{smallmatrix}0 & 1\\ 2 & 0\end{smallmatrix})  & (\begin{smallmatrix}1 & 1\\ 0 & 1\end{smallmatrix})  & (\begin{smallmatrix}1 & 2\\ 0 & 1\end{smallmatrix}) & (\begin{smallmatrix}2 & 1\\ 0 & 2\end{smallmatrix})  & (\begin{smallmatrix}2 & 2\\ 0 & 2\end{smallmatrix}) \\
+\hline
+\IC(\mathbf{1}_{C_3})  &  \mathbf{1}_{C_3}[3]  & -1 & -1 & -1 & -1 & -1 & -1 & -1 \\
+ \IC(\mathbf{1}_{C_2})  &  \mathbf{1}_{C_2}[2] \oplus \mathbf{1}_1[0]  & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
+ \IC(\cs{E}_{C_2})  &  \cs{E}_{C_2}[2]  & 0 & 0 & 0 &  \sqrt{-3}  &  -\sqrt{-3} & 0 & 0 \\
+ \IC(\mathbf{1}_{C_2^-})  &  \mathbf{1}_{C_2^-}[2] \oplus \mathbf{1}_{-1}[0]  & 0 & 1 & 0 & 0 & 0 & 1 & 1 \\
+ \IC(\cs{E}_{C_2^-})  &  \cs{E}_{C_2^-}[2]  & 0 & 0 & 0 & 0 & 0 &   \sqrt{-3}  &   -\sqrt{-3}  \\
+ \IC(\mathbf{1}_1)  &  \mathbf{1}_1[0]  & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
+ \IC(\mathbf{1}_{-1})  &  \mathbf{1}_{-1}[0]  & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
+\hline
+\end{array}
+\]
+\end{spacing}
 
@@
 
-\begin{tabular}{|l|l|ccccccc|}
-\hline
-Perverse & Standard & \multicolumn{7}{|c|}{Trace of Frobenius values} \\ \cline{3-9}
-
-Sheaf & Sheaves & \smat1001 & \smat2002 & \smat0120 & \smat1101 & \smat1201 & \smat2102 & \smat2202 \\
-\hline
-$\IC(\mathbf{1}_{C_3})$ & $\mathbf{1}_{C_3}[3]$ & -1 & -1 & -1 & -1 & -1 & -1 & -1 \\
-$\IC(\mathbf{1}_{C_2})$ & $\mathbf{1}_{C_2}[2] \oplus \mathbf{1}_1[0]$ & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
-$\IC(\cs{E}_{C_2})$ & $\cs{E}_{C_2}[2]$ & 0 & 0 & 0 & $\sqrt{-3}$ & $-\sqrt{-3}$ & 0 & 0 \\
-$\IC(\mathbf{1}_{C_2^-})$ & $\mathbf{1}_{C_2^-}[2] \oplus \mathbf{1}_{-1}[0]$ & 0 & 1 & 0 & 0 & 0 & 1 & 1 \\
-$\IC(\cs{E}_{C_2^-})$ & $\cs{E}_{C_2^-}[2]$ & 0 & 0 & 0 & 0 & 0 & $\sqrt{-3}$ & $-\sqrt{-3}$ \\
-$\IC(\mathbf{1}_1)$ & $\mathbf{1}_1[0]$ & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
-$\IC(\mathbf{1}_{-1})$ & $\mathbf{1}_{-1}[0]$ & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
-\hline
-\end{tabular}
-
-\vspace{0.1in}
-\noindent Using the trace of Frobenius values, we find that 
+\noindent 
+Using the trace of Frobenius values, we find that 
 \[
@@
 \caption{Notation conversion chart.}
-\begin{spacing}{1.2}
+\begin{spacing}{1.3}
 \begin{tabular}{| c|l | l | }

### 2017-06-30 Geometric types.tex
Catching up

@@
 The adjoint functor $\CS\der(G) \to \CS\ab(G)$ is given by a  similar  strategy: given $(\cs{L},\mu,\beta)\in \CS\der(G)$, define $(\cs{L},\mu,\nu)$ again using  \eqref{eqn:betanu}.
-Then and verify that $(\cs{L},\nu)$ satisfies \eqref{E2} as it applies here, so that $(\cs{L},\nu)\in \Loc\der(G)$.
+Then verify that $(\cs{L},\nu)$ satisfies \eqref{E2} as it applies here, so that $(\cs{L},\nu)\in \Loc\der(G)$.
 After confirming that morphisms that commute with $\mu$ and $\nu$ also commute with $\mu$ and $\beta$, this concludes the definition of the functor  $\CS\der(G) \to \CS\ab(G)$.
@@
 \vspace{0.1in}
-
-\noindent 
-Using the trace of Frobenius values, we find that 
+\noindent Using the trace of Frobenius values, we find that the rational virtural Weil sheaf 
 \[

### 2017-07-02 Geometric types.tex
Some work on the Introduction, Section 4 and Section 5.

@@
 \end{quotation}
-In this paper we follow the suggestion above by showing that Yu type data are geometrizable, in the following sense.
+In this paper we follow the suggestion above by showing that certain Yu type data are geometrizable, in the following sense.
 A Yu type datum determines a sequence of representations $\orho_i$ of compact $p$-adic groups $\oK^i$, for $i=0, \ldots, d$, such that $(\oK^d, \rho_d)$ is a type for a supercuspidal representation of a $p$-adic group.
@@
 The main result of \cite{Yu:models} shows how to find, for each $i=0, \ldots, d$, a smooth group scheme $\underline{G}^i$ over the ring $R$ with $\underline{G}^i(R)=\,^\circ K^i $.
-The geometrization of the Yu type datum uses Lusztig's theory of character sheaves on reductive groups over finite fields, so it is necessary to assume that the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic, in order to bring his work to bear.
+The geometrization of the Yu type datum that we consider in this paper uses Lusztig's theory of character sheaves on reductive groups over finite fields, for which it is necessary to assume that the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic.
+We must also place a condition on the linear characters that appear in the Yu datum, 
 Under this assumption we show how each representation $\orho_i$ can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$, where $\cs{F}^i$ is a {\it rational virtual} sheaf complex on the Greenberg transform $G^i$ of $\underline{G}^i$, by which we mean $\cs{F}^i$ is an element in the group obtained by tensoring the Grothendieck group of such sheaves with $\QQ$.
@@
 is an isomorphism.  
-Since $G\ab(k)^*$ surjects onto $G(k)^*$, it follows that for each character $\chi \in G(k)^*$ there is a commutative
+Since $G\ab(k)^*$ surjects onto $G(k)^*$, it follows that for each character $\chi \in G(k)^*$ trivial on $G\der(k)$ there is a commutative
 character sheaf $\cs{L}$ on $G$ with $\TrFrob{G}(\cs{L}) = \chi$. Moreover, we find that pullback along the quotient $q : G \to G\ab$
@@
 If Lusztig's theory of character sheaves can be generalized to all disconnected reductive algebraic groups, then the hypothesis in Theorem~\ref{thm:geotypes} can be removed.
+%
+The second hypothesis  in Theorem~\ref{thm:geotypes} -- that the quasicharacters $\varphi^i$ appearing in the Yu type datum satisfy the hypothesis of Proposition~\ref{prop:quasicharacters} -- ensures that we may use Section~\ref{sec:noncom} to find a geometric type which equivariant for conjugation, as defined in Section~\ref{ssec:equivariant}.
+Section~\ref{sec:badchar} presents some evidence to suggest that this hypothesis is not always necessary. 
 \bigskip
@@
 We now consider the case of a smooth group scheme without the commutativity assumption.  Our approach
-is to relate linear character sheaves on $G$ to character sheaves on its abelianization $G\ab = G / G\der$.
+is to relate linear character sheaves on $G$ to character sheaves on its abelianization $G\ab = G / G\der$, where $G\der$ is defined by \cite{demazure:SGA3-VIB}*{D\'efinition 7.2.2} and the quotient is $G\ab$ is an instance of  \cite{demazure:SGA3-VIA}*{Section 7.2.2}.
 While every character $\chi \in G(k)^*$ vanishes on $G(k)\der$, it may not vanish on $G\der(k)$.  For example,
@@
 
+\subsection{Equivariance Weil sheaf complexes (move to somewhere else?)}\label{ssec:equivariant}
+
+Suppose $(\cs{L},\mu)$ is a linear character sheaf on $G$. 
+As the diagram below explains, the isomorphism $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ determines an isomorphism $a^*\cs{L} \to p_2^*\cs{L}$ of Weil local systems on $G\times G$, where  $a : G\times G\to G$ is conjugation $a(x,y)=xyx^{-1}$ and $p_2: G\times G\to G$ is projection $p_2(x,y)=y$.
+\[
+\begin{tikzcd}[column sep = 30]
+a^*\cs{L} \arrow[equal]{d}[swap]{a= m\circ (m\times (i\circ p_1))} \arrow[dotted]{r} & p_2^*\cs{L}  \\
+(m\times (i\circ p_1))^* m^*\cs{L} \arrow{d}[swap]{(m\times (i\circ p_1))^*\mu}  & p_1^*(\cs{L} \otimes \cs{L}^\vee) \otimes p_2^*\cs{L} \arrow[equal]{u}[swap]{\cs{L}\otimes \cs{L}^\vee \iso (\EE)_{G}}\\
+m^*\cs{L}\otimes (i\circ p_1))^*\cs{L} \arrow{r}{\mu \otimes \id} & p_1^*\cs{L} \otimes p_2^*\cs{L} \otimes p_1^*\cs{L}^\vee \arrow[equal]{u}
+\end{tikzcd}
+\]
+Although every linear character sheaf on $G$ is a conjugation-equivariant Weil local systems on $G$, the converse is certainly not true.
+
+For connected reductive groups $G$ over $k$, Lusztig's character sheaves are simple perverse sheaves $\IC(C,\mathcal{L})$ on $G$ that come equipped with an isomorphism $a^*\, \IC(C,\mathcal{L}) \to p_2^*\, \IC(C,\mathcal{L})$ in Deligne's category $D^b_c(G;\EE)$.
+Consequently, when $\IC(C,\mathcal{L})$ is also a Weil sheaf complex, its trace of Frobenius function $\trFrob{\IC(C,\cs{L})} : G(k)\to \EE$ is a class function, called the characteristic function of $\IC(C,\cs{L})$.
+By \cite{lusztig:86a}*{Cor. 25.7}, Weil character sheaves on $G$ determine a basis for the $\EE$-space of class functions on $G(k)$.
+In particular, any character of any representation of $G(k)$ can be expressed as a ${\bar \QQ}$-linear combination of characteristic functions of Weil character sheaves on $G$.
+We will refer to a formal sum $\sum_{i\in I} a_i \cs{F}_i$ of conjugation-equivariant Weil $\ell$-adic sheaf complexes with ${\bar \QQ}$-coefficients as a rational virtual equivariant Weil sheaf complex on $G$.
+When specialized to the case of characters $\chi$ of $G(k)$, Lusztig's theory of character sheaves geometrizes $\chi$ as a rational virtual equivariant Weil sheaf complex on $G$.
+We see an example of this in Section~\ref{ssec:SL23}.
+
 \subsection{Pushforward along the Lang isogeny}
@@
 
-\subsection{\texorpdfstring{$\SL_2(\FFF)$}{\SL(2, 3)}}
+\subsection{\texorpdfstring{$\SL_2(\FFF)$}{\SL(2, 3)}}\label{ssec:SL23}
 
@@
 The method described above for producing a linear character sheaf corresponding to this character no longer works, since $\SL_2$ is simply connected and thus has no discrete isogenies mapping onto it.
-We may still produce a local system with the correct trace of Frobenius, by pushing forward the constant sheaf along the Lang isogeny and picking out the isotypic component corresponding to $\chi$.
-However, since $\SL_2$ is nonabelian, the Lang isogeny is not a homomorphism and the resulting local system is not a linear character sheaf.
+We may still produce a local system with the correct trace of Frobenius, by pushing forward the constant sheaf along the Lang isogeny and picking out the isotypic component corresponding to $\chi$.\todo{So, maybe not?}  However, since $\SL_2$ is nonabelian, the Lang isogeny is not a homomorphism and the resulting local system is not a linear character sheaf.
 
 Alternatively, we can use the fact that Lusztig's character sheaves provide a basis for the space of class functions \cite{lusztig:86a}*{Cor.
-25.7} to give a different geometrization of $\chi$.
+25.7} to give a different geometrization of $\chi$, as discussed in Section~\ref{ssec:equivariant}.
 Lusztig's character sheaves are constructed by perverse extension of local systems on a certain stratification of $G$.
@@
 
-%\vspace{0.1in}
+\vspace{0.1in}
+
 \noindent
@@
 $\mathbf{1}_{C_2}$, $\mathbf{1}_{C_2^-}$, $\mathbf{1}_{1}$,  $\mathbf{1}_{-1}$) on $C_3$ (resp.
-$C_2$, $C_2^-$, $1$, $-1$), or the non-trivial local system $\cs{E}_{C_2}$  (resp.
+$C_2$, $C_2^-$, $1$, $-1$), or the non-trivial rank-$1$ local system $\cs{E}_{C_2}$  (resp.
+$\cs{E}_{C_2^-}$) on $C_2^{-1}$  (resp.
 $\cs{E}_{C_2^-}$) trivialized by the double cover of $C_2$ (resp.
 $C_2^-$).
-The following table describes these perverse sheaves by showing how they decompose in the Grothendieck group into conjugation-equivariant standard sheaves on $\SL_2$, and also gives the values of the trace of Frobenius of each Weil character sheaf on $\SL_2$ on the $7$ conjugacy classes in $\SL_2(\FFF)$.
+The following table describes these perverse sheaves by showing how they decompose in the Grothendieck group into standard sheaves on $\SL_2$, and also gives the values of the trace of Frobenius on the $7$ conjugacy classes in $\SL_2(\FFF)$.
 
@@
 \hline
-\text{Perverse} & \text{Standard} & \multicolumn{7}{|c|}{\text{Trace of Frobenius values}} \\ \cline{3-9}
+\text{Perverse} & \text{Standard} & \multicolumn{7}{|c|}{\text{Trace of Frobenius values at conjugacy classes}} \\ \cline{3-9}
 \text{Sheaf} & \text{Sheaves} & (\begin{smallmatrix}1 & 0\\ 0 & 1\end{smallmatrix}) & (\begin{smallmatrix}2 & 0\\ 0 & 2\end{smallmatrix}) & (\begin{smallmatrix}0 & 1\\ 2 & 0\end{smallmatrix})  & (\begin{smallmatrix}1 & 1\\ 0 & 1\end{smallmatrix})  & (\begin{smallmatrix}1 & 2\\ 0 & 1\end{smallmatrix}) & (\begin{smallmatrix}2 & 1\\ 0 & 2\end{smallmatrix})  & (\begin{smallmatrix}2 & 2\\ 0 & 2\end{smallmatrix}) \\
@@
 \vspace{0.1in}
-\noindent Using the trace of Frobenius values, we find that the rational virtural Weil sheaf 
+\noindent Using the trace of Frobenius values, we find that the rational virtual equivariant Weil sheaf complex
 \[
@@
 
+\todo{}
+Explain that while $(f_! \EE)_\psi$ is not a commutative character sheaf, it does satisfy a weaker version of Definition~\ref{def:CCS}. Namely, there is an isomorphism $\gamma$ such that
+ \[
+  \begin{tikzcd}[row sep=30]
+   m^*\cs{L} \arrow{d}[swap]{\gamma} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
+   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L}).
+  \end{tikzcd}
+  \]
+
 \subsection{The True Commutator}
@@
 \]
-together with a non-trivial character of $\mu_n(k)$. \todo{Small change here.}
+together with a non-trivial character of $\mu_n(k)$. 
 In order to obtain a relationship between linear character sheaves on $G$ and characters of $G(k)$,
@@
 
-\subsection{Quasicharacters of smooth group schemes over certain henselian traits}
+\subsection{Quasicharacters of smooth group schemes over certain henselian traits}\label{ssec:quasicharacters}
 
@@
 \]
+Let $\varphi : \underline{G}(R) \to \EEx$ be a quasicharacter. 
+By the continuity of $\varphi$ there is some $r \in \NN$ and a factorization
+\[
+\begin{tikzcd}
+\underline{G}(R) \arrow{rr}{\varphi} \arrow{rd} && \EEx\\
+& \underline{G}(R/\mathfrak{p}^{r+1}) \arrow{ru}[swap]{\varphi_r} 
+\end{tikzcd}
+\] 
+The least such $r\in \NN$ is called the {\it level} of $\varphi$.
+For any $r\in \NN$, define $R_r \ceq R/\mathfrak{p}^{r+1}$ and
+set $G_r \ceq \Gr_r^{R}(\underline{G})$, the Greenberg transform of $\underline{G}\times_{\Spec{R}}\Spec{R_r}$.
+Then $G_r$ is a smooth group scheme over $\Fq$ and $G_r(\Fq) = \underline{G}(R_r)$.
 
 \begin{proposition}\label{prop:quasicharacters}
-For every quasicharacter character $\varphi : \underline{G}(R) \to \EEx$ there is a Weil sheaf $\cs{L}$ on $G$ such that \[\trFrob{\cs{L}} =  \varphi.\] \end{proposition}
+Let $\underline{G}$ be a smooth group scheme over $R$.
+Let $\varphi : \underline{G}(R) \to \EEx$ be quasicharacter and let $r$ be the level of $\varphi$.
+If $\varphi_r : G_m(k)\to \EEx$ is trivial on $G_{r,\operatorname{der}}(k)$ then 
+there is a commutative character sheaf $\cs{L}_r\in \CCS(G_r)$ such that 
+\[
+\trFrob{\cs{L}_r} =  \varphi_r.
+\] 
+\end{proposition}
 
 \begin{proof}
-By continuity of $\varphi : \underline{G}(R) \to \EE^\times$, there is some $m \in \NN$ and a factorization
-\[
-\begin{tikzcd}
-\underline{G}(R) \arrow{rr}{\varphi} \arrow{rd} && \EEx\\
-& \underline{G}(R/\mathfrak{p}^{m+1}) \arrow{ru}[swap]{\varphi_m} 
-\end{tikzcd}
-\] 
-Set $R_m = R/\mathfrak{p}^{m+1}$ and
-set $G_m = \Gr_m^{R}(\underline{G})$, the Greenberg transform of $\underline{G}\times_{\Spec{R}}\Spec{R_m}$.
-Then $G_m$ is a smooth group scheme over $\Fq$ and $G_m(\Fq) = \underline{G}(R_m)$.
-Using Theorem~\ref{thm:geo}, let $\cs{L}_m$ be a geometrization of the character $\varphi_m: G_m(\Fq) \to \EEx$; so
-\[
-\trFrob{\cs{L}_m} = \varphi_m
-\]
-on $G_m(\Fq)$.
-%
+This is a direct consequence of Theorem~\ref{thm:geo}.
+%let $\cs{L}_r$ be a geometrization of the character $\varphi_r: G_r(\Fq) \to \EEx$.
+\end{proof}
+
+With $\varphi$ as above, note that if $r'$ is any integer greater or equal to the level $r$ of $\varphi$, then the pullback of $\cs{L}_r$ along $G_{r'} \to G_{r}$ is a linear character sheaf on $G_r$.
+Thus, $\cs{L}_{r'}$ is conjugation-equivariant in the sense of Section~\ref{ssec:equivariant}
+
+$a_r : G_r\times G_r \to G_r$ is conjugation for $G_r$, then this determines an isomorphism $a_r^*\cs{L}_r \iso (\EE)_{G_r}\boxtimes \cs{L}_r$, so $\cs{L}_r$ is
+
 Recall that the full Greenberg transform $G \ceq \Gr^{R}(\underline{G})$ is a group scheme over $\Fq$ such that $G(\Fq) = \underline{G}(R)$; it comes equipped with a morphism $G \to G_m$.
-Let $\cs{L}$ be the Weil sheaf on $G$ obtained from $\cs{L}_m$ by pullback along $G \to G_m$. 
-Then $\cs{L}$ is a quasicharacter sheaf on $G$, in the sense of \cite{cunningham-roe:13a}*{Def 4.2}, such that $\trFrob{\cs{L}} = \varphi$.
-\end{proof}
+The Weil sheaf on $G$ obtained from $\cs{L}_m$ by pullback along the morphism of group schemes $G \to G_m$ is a quasicharacter sheaf on $G$, in the sense of \cite{cunningham-roe:13a}*{Def 4.2}, such that
+\[
+\trFrob{\cs{L}} = \varphi.
+\]
 
@@
 
-There is a Weil sheaf complex $\cs{K}_\psi$ on $\Sp(V)\ltimes V^\sharp$ \cite{gurevich-hadani:07a}*{Theorem 3.2.2.1} (see also \cite{gurevich-hadani:11a}*{Theorem 4.5}) such that 
-\begin{equation}
+By \cite{gurevich-hadani:07a}*{Theorem 3.2.2.1} (see also \cite{gurevich-hadani:11a}*{Theorem 4.5}), there is a Frobenius-stable conjugation-equivariant perverse sheaf $\cs{K}_\psi$ on $\Sp(V)\ltimes V^\sharp$  such that
+\begin{equation}\label{eqn:Jacobi}
 \trFrob{\cs{K}_\psi} = \trace(W_\psi).
@@
 %
+
 Next, Yu defines a group homomorphism (in fact, a quotient) 
@@
 \labitem{M0}{M0}
-The compact groups $\oK^i$ have been replaced by the smooth group schemes $\underline{G}^i$.
+The compact groups $\oK^i$ appearing in \ref{Y0} have been replaced by the smooth group schemes $\underline{G}^i$.
 \labitem{M1}{M1}
-The continuous representation $\orho^0$ of $\oK^0$ is a representation of $\underline{G}^0(R)$ obtained by inflation along $\underline{G}^0(R) \to \underline{G}^0(\Fq)$ from a representation $\varrho_0$ of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
+The continuous representation $\orho^0$ of $\oK^0$ appearing in \ref{Y1} may be interpreted as a representation of $\underline{G}^0(R)$ obtained by inflation along $\underline{G}^0(R) \to \underline{G}^0(\Fq)$ from a representation $\varrho_0$ of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
 In fact, $\varrho_0$ is itself obtained by pulling back a representation $\varrho_0^\reductive$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
-\labitem{M2}{M2} The quasicharacters $\varphi^i$ are quasicharacters of $\underline{G}^i(R)$, for $i=0, \ldots, d$.
+\labitem{M2}{M2} The quasicharacters $\varphi^i$ appearing in \ref{Y2} are now quasicharacters of $\underline{G}^i(R)$, for $i=0, \ldots, d$.
 \labitem{M3}{M3}
-Diagram \eqref{eq:semiprod} is now replaced by the following diagram of smooth group schemes over $R$.
+Diagram \eqref{eq:semiprod} in \ref{Y3} is now replaced by the following diagram of smooth group schemes over $R$.
 \begin{equation}\label{eq:pimodel}
@@
 
-\subsection{Geometrization of characters of types}\label{ssec:geotypes}
-
-Finally, we come to the main result of Section~\ref{sec:types}.
+\subsection{Geometrization of characters of certain types}\label{ssec:geotypes}
+
+We may now give the main result of Section~\ref{sec:types}.
 %
 Since Yu's theory refers to complex representations, and since our geometrization uses $\ell$-adic sheaves, we grit our teeth and fix an isomorphism $\CC \approx \EE$.
+From Section~\ref{ssec:equivariant}, recall the definition of a rational virtual equivariant Weil sheaf complex.
 
@@
 For $i=0, \ldots ,d$, let $G^i = \Gr_{R}(\underline{G}^i)$ be the Greenberg transform of the smooth group scheme $\underline{G}^i$ appearing in Section~\ref{ssec:review}.
-Then there is a rational virtual Weil sheaf complex $\cs{F}_i$ on $G^i$ such that $\trFrob{\cs{F}_i} = \trace(\orho_i)$, for $i=0, \ldots , d$.
+Suppose that the quasicharacters $\varphi^i$, given in Section~\ref{ssec:review}, \ref{M2}, satisfy the hypothesis of Proposition~\ref{prop:quasicharacters}.
+Then there is a rational virtual equivariant Weil sheaf complex $\cs{F}_i$ on $G^i$ such that $\trFrob{\cs{F}_i} = \trace(\orho_i)$, for $i=0, \ldots , d$.
 \end{theorem}
@@
 \begin{proof}
-For every $i=0, \ldots ,d$, set $G^i = \Gr_{R}(\underline{G}^i)$.
+%For every $i=0, \ldots ,d$, set $G^i = \Gr_{R}(\underline{G}^i)$.
 Recall that $G^i(\Fq) = \underline{G}^i(R) = \oK^i$, canonically.
-We begin with an argument already employed in the proof of Proposition~\ref{prop:quasicharacters}.
-By continuity of the quasicharacters $\varphi^i : G^i(\Fq) \to \CC^\times$, there is some $m \in \NN$ and a factorization
-\[
-\begin{tikzcd}
-G^i(\Fq) \arrow{rr}{\varphi^i} \arrow{rd} && \EEx\\
-& \underline{G}^i(R_m) \arrow{ru}[swap]{\varphi^i_m} 
-\end{tikzcd}
-\] 
-for all $i=0, \ldots, d$.
-Set $G_m^i = \Gr_m^{R}(\underline{G}^i)$.
+Set $G_m^i = \Gr_m^{R}(\underline{G}^i)$, for $i=0, \ldots, d$.
 Then $G_m^i$ is a smooth group scheme over $\Fq$ and $G_m^i(\Fq) = \underline{G}^i(R_m)$, canonically.
-Using Theorem~\ref{thm:geo}, let $\cs{L}^i_m$ be a geometrization of the linear character $\varphi^i_m: G_m^i(k) \to \CC^\times$; so
-\[
-\trFrob{\cs{L}^i_m} = \varphi^i_m.
-\]
-
-By \cite{lusztig:disconnected1}, there is a rational virtual Weil character sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that ${\bar A}$ is a rational virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
+Let $m_i$ be the level of $\varphi$ as defined in Section~\ref{ssec:quasicharacters}.
+Let $\cs{L}^i_m$ be the commutative character sheaf on $G_{m_i}$ given by Proposition~\ref{prop:quasicharacters}; then
+$\trFrob{\cs{L}^i_{m_i}} = \varphi^i_{m_i}$.
+Set $m = \max\{ m_i \tq i=0, \ldots ,d\}$ and, for each $i$, let $\cs{L}^i_{m}$ be the pull-back of $\cs{L}^i_{m_i}$ along $G^i_{m} \to G^i_{m_i}$; then $\cs{L}^i_{m}$ is a linear character sheaf and
+\[
+\trFrob{\cs{L}^i_{m}} = \varphi^i_{m}.
+\]
+
+By \cite{lusztig:disconnected1}, there is a rational virtual Weil character sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that 
+%${\bar A}$ is a rational virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
 \[
@@
 \]
-(This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.)
+This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
 %
-Let $A^0$ be the Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+Let $A^0$ be the equivariant Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
 Then 
@@
 The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $Q^0 = \Gr^{R}_0(\underline{G}^0)$ \cite{cunningham-roe:13a}*{\S 4.3}.
-With $m\in \NN$ as above, let ${A}_m^0$ be the Weil sheaf on the algebraic group $G_m^i$ obtained by pull-back from $A^0$ along the affine morphism $G_m^i \to Q^0$.
+With $m\in \NN$ as above, let ${A}_m^0$ be the equivariant Weil sheaf on the algebraic group $G_m^i$ obtained by pull-back from $A^0$ along the affine morphism $G_m^i \to Q^0$.
 Factor
@@
 Consider the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ and the Heisenberg-Weil representation $W_{i+1}$ appearing in Section~\ref{ssec:review}.
-Let $\cs{K}^{i+1}$ be the Weil sheaf on the Jacobi group, recalled in Section~\ref{ssec:Jacobi}, such that
+Let $\cs{K}^{i+1}$ be the equivariant Weil sheaf on the Jacobi group, recalled in Section~\ref{ssec:Jacobi}, such that
 \[
@@
 Let $\cs{K}_0^{i+1}$ be the Weil sheaf on the special fibre of $\underline{G}^{i} \ltimes \underline{J}^{i+1}$ obtained from $W_{i+1}$ by pullback. 
-Let $\cs{K}_m^{i+1}$ be the Weil sheaf on $\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1})$ obtained from $\cs{K}_0^{i+1}$ by pullback along the affine morphism
+Let $\cs{K}_m^{i+1}$ be the equivariant Weil sheaf on $\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1})$ obtained from $\cs{K}_0^{i+1}$ by pullback along the affine morphism
 $\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1}) \to \Gr^{R}_0(\underline{G}^{i} \ltimes \underline{J}^{i+1})$.
 
-We now define Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{R}_m(\underline{G}^{i})$, for $i=0,\ldots ,d$, recursively, following the construction of the representations $\orho^i$, as reviewed in Section~\ref{ssec:review}.
+We now define equivariant Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{R}_m(\underline{G}^{i})$, for $i=0,\ldots ,d$, recursively, following the construction of the representations $\orho^i$, as reviewed in Section~\ref{ssec:review}.
 First, set $\cs{A}_m^0 = A_m^0$ and note that \eqref{eqn:tracerho} commutes with $\trace(\orho^0)_m$ replaced by $\trFrob{\cs{A}_m^0}$.
@@
 By \cite{bertapelle-gonzales:Greenberg}*{Prop 7.1}, the sequences are exact.
-Consider the sheaf 
+Consider the rational virtual equivariant Weil sheaf 
 \[
@@
 \]
-Then
+Then $\cs{C}_m^{i+1}$ is an equivariant Weil sheaf and
 \begin{eqnarray*}
@@
 on $G_m^{i+1}(\Fq)$ for $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) \times \dim \orho^{i+1} $.
-Let $\cs{A}_m^{i+1}$ be the \emph{rational virtual} Weil sheaf on $G_m^i$ given by $\cs{A}_m^{i+1} = \frac{1}{n} \cs{C}_m^{i+1}$. 
+Let $\cs{A}_m^{i+1}$ be the rational virtual equivariant Weil sheaf on $G_m^i$ given by $\cs{A}_m^{i+1} = \frac{1}{n} \cs{C}_m^{i+1}$. 
 %
@@
 Now set $\cs{F}^i_m = \cs{A}_m^{i} \otimes \cs{L}_m^i$, for $i=0, \ldots ,d$.
-Then $\cs{F}^i_m$ is a rational virtual Weil sheaf on $G^i_m = \Gr^{R}_m(\underline{G}^i)$ such that
+Then $\cs{F}^i_m$ is a rational virtual equivariant Weil sheaf on $G^i_m = \Gr^{R}_m(\underline{G}^i)$ such that
 \[
@@
 commutes.
-Let $\cs{F}^i$ be the rational virtual Weil sheaf on the group scheme $G^i= \Gr_{R}(\underline{G}^i)$ obtained by pulling back $\cs{F}_m^i$ along $G^i \to G^i_m$.
+Let $\cs{F}^i$ be the rational virtual equivariant Weil sheaf on the group scheme $G^i= \Gr_{R}(\underline{G}^i)$ obtained by pulling back $\cs{F}_m^i$ along $G^i \to G^i_m$.
 Then 
@@
 \end{proof}
+
+\bigskip
 
@@
 
+\bib{demazure:SGA3-VIB}{inproceedings}{
+      author={Bertin, J.E.},
+       title={{Expos\'e VI$_\mathrm{B}$: G\'en\'eralit\'es sur les pr\'esch\'emas en groupes}},
+        date={1970},
+   booktitle={S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois Marie, Sch\'emas en groupes I (SGA3) {Proprietes generales des schemas en
+  groupes}},
+      editor={Demazure, Michel},
+      editor={Grothendieck, Alexander},
+      series={Lecture Notes in Math},
+      volume={151},
+   publisher={Springer-Verlag},
+     address={Berlin},
+}
+
 \bib{EGAIV4}{article}{

### 2017-07-04 Geometric types.tex
Working on Lemma 4.1

--- 2017-06-30 Geometric types.tex
@@
 For connected, commutative groups, the standard method for geometrizing a character $\chi$ is to use the Lang isogeny $L : G \to G$, defined by $L(x) = x^{-1}\Frob{G}(x)$.
-Then the pushforward $L_!
+The pushforward $L_!
 (\EE)_G$ of the constant sheaf decomposes into a direct sum of rank $1$ local systems according to characters of the automorphism group $G(k)$ of the cover $L$.
+
+Now drop the assumption that $G$ is commutative, but assume that $G(k) \subset \image(L)$ (which will hold if $G$ is connected).
+We apply a similar strategy to construct a local system on $G$ whose trace of Frobenius is $\chi$.
+
+\begin{lemma}
+If $\chi \in G(k)^*$ then there is a character $\chi' \in G(k)^*$ so that $\chi'(yxy^{-1}) = \chi(x)$ for all $x \in G(k)$ and $y \in L^{-1}(x^{-1})$.
+\end{lemma}
+\begin{proof}
+The condition $y \in L^{-1}(x^{-1})$ is equivalent to $\Frob{}(y) = yx^{-1}$, and thus $yxy^{-1} \in G(k)$ since $\Frob{}(yxy^{-1}) = (yx^{-1})x(xy^{-1}) = yxy^{-1}.$
+Given $z \in G(k)$, we want to write $z = yxy^{-1} = y\Frob{}(y^{-1}) = L(y^{-1})$ in order to define $\chi'(z) = \chi(x)$.
+This is possible by our assumption that $G(k) \subset \image(L)$.
+To see that $\chi'$ is well-defined, suppose that $z = y_1 x_1 y_1^{-1} = y_2 x_2 y_2^{-1}$ with $y_i \in L^{-1}(x_i^{-1})$.
+Then $y_1 \Frob{}(y_1^{-1}) = y_2 \Frob{}(y_2^{-1})$ so $y_1^{-1} y_2 \in G(k)$ and $y_2^{-1} y_1 \in G(k)$.
+We can now write
+\begin{align*}
+x_1 x_2^{-1} &= y_1^{-1} z y_1 y_2^{-1} z^{-1} y_2 \\
+&= (y_1^{-1} y_2) (y_2^{-1} z y_2) (y_2^{-1} y_1) (y_2^{-1} z^{-1} y_2) \in G(k)\der.
+\end{align*}
+Thus $\chi(x_1 x_2^{-1}) = 1$ so $\chi(x_1) = \chi(x_2)$ and $\chi'$ is well defined. \todo{Finish proof here}
+\end{proof}
 
@@
 
-\begin{center}
-\begin{spacing}{1.3}
 \begin{tabular}{|l|l|}
@@
 \end{tabular}
-\end{spacing}
-\end{center}
-
-%\vspace{0.1in}
-\noindent
-Each Weil character sheaf on $\SL_2$ over $\FFF$ is the perverse extension of one of the following local systems: the rank-$1$ constant sheaf $\mathbf{1}_{C_3}$ (resp.
-$\mathbf{1}_{C_2}$, $\mathbf{1}_{C_2^-}$, $\mathbf{1}_{1}$,  $\mathbf{1}_{-1}$) on $C_3$ (resp.
-$C_2$, $C_2^-$, $1$, $-1$), or the non-trivial local system $\cs{E}_{C_2}$  (resp.
-$\cs{E}_{C_2^-}$) trivialized by the  double cover of $C_2$ (resp.
-$C_2^-$).
-The following table describes these perverse sheaves by showing how they decompose in the Grothendieck group into conjugation-equivariant standard sheaves on $\SL_2$, and also gives the values of the trace of Frobenius of each Weil character sheaf on $\SL_2$ on the $7$ conjugacy classes in $\SL_2(\FFF)$.
 
@@
 
-\begin{spacing}{1.3}
-\[
-\begin{array}{|l|l|ccccccc|}
+Suppose that $C$ is a stratum and $x \in C$.
+Local systems on $C$ are classified up to isomorphism by irreducible representations of $\pi_0(Z_G(x))$.
+This component group is trivial for $C_3$, $1$ and $-1$, and of order $2$ for $C_2$ and $C_2^-$.
+Denote the nontrivial local systems on $C_2$ and $C_2^-$ by $\cs{E}_{C_2}$ and $\cs{E}_{C_2^-}$.
+Then the character sheaves on $\SL_2$ are the following, where the second column gives a decomposition in the Grothendieck group of standard sheaves on $G$.
+
+\vspace{0.1in}
+
+\begin{tabular}{|l|l|ccccccc|}
 \hline
-\text{Perverse} & \text{Standard} & \multicolumn{7}{|c|}{\text{Trace of Frobenius values}} \\ \cline{3-9}
-\text{Sheaf} & \text{Sheaves} & (\begin{smallmatrix}1 & 0\\ 0 & 1\end{smallmatrix}) & (\begin{smallmatrix}2 & 0\\ 0 & 2\end{smallmatrix}) & (\begin{smallmatrix}0 & 1\\ 2 & 0\end{smallmatrix})  & (\begin{smallmatrix}1 & 1\\ 0 & 1\end{smallmatrix})  & (\begin{smallmatrix}1 & 2\\ 0 & 1\end{smallmatrix}) & (\begin{smallmatrix}2 & 1\\ 0 & 2\end{smallmatrix})  & (\begin{smallmatrix}2 & 2\\ 0 & 2\end{smallmatrix}) \\
+Perverse & Standard & \multicolumn{7}{|c|}{Trace of Frobenius values} \\ \cline{3-9}
+
+Sheaf & Sheaves & \smat1001 & \smat2002 & \smat0120 & \smat1101 & \smat1201 & \smat2102 & \smat2202 \\
 \hline
-\IC(\mathbf{1}_{C_3})  &  \mathbf{1}_{C_3}[3]  & -1 & -1 & -1 & -1 & -1 & -1 & -1 \\
- \IC(\mathbf{1}_{C_2})  &  \mathbf{1}_{C_2}[2] \oplus \mathbf{1}_1[0]  & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
- \IC(\cs{E}_{C_2})  &  \cs{E}_{C_2}[2]  & 0 & 0 & 0 &  \sqrt{-3}  &  -\sqrt{-3} & 0 & 0 \\
- \IC(\mathbf{1}_{C_2^-})  &  \mathbf{1}_{C_2^-}[2] \oplus \mathbf{1}_{-1}[0]  & 0 & 1 & 0 & 0 & 0 & 1 & 1 \\
- \IC(\cs{E}_{C_2^-})  &  \cs{E}_{C_2^-}[2]  & 0 & 0 & 0 & 0 & 0 &   \sqrt{-3}  &   -\sqrt{-3}  \\
- \IC(\mathbf{1}_1)  &  \mathbf{1}_1[0]  & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
- \IC(\mathbf{1}_{-1})  &  \mathbf{1}_{-1}[0]  & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
+$\IC(\mathbf{1}_{C_3})$ & $\mathbf{1}_{C_3}[3]$ & -1 & -1 & -1 & -1 & -1 & -1 & -1 \\
+$\IC(\mathbf{1}_{C_2})$ & $\mathbf{1}_{C_2}[2] \oplus \mathbf{1}_1[0]$ & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
+$\IC(\cs{E}_{C_2})$ & $\cs{E}_{C_2}[2]$ & 0 & 0 & 0 & $\sqrt{-3}$ & $-\sqrt{-3}$ & 0 & 0 \\
+$\IC(\mathbf{1}_{C_2^-})$ & $\mathbf{1}_{C_2^-}[2] \oplus \mathbf{1}_{-1}[0]$ & 0 & 1 & 0 & 0 & 0 & 1 & 1 \\
+$\IC(\cs{E}_{C_2^-})$ & $\cs{E}_{C_2^-}[2]$ & 0 & 0 & 0 & 0 & 0 & $\sqrt{-3}$ & $-\sqrt{-3}$ \\
+$\IC(\mathbf{1}_1)$ & $\mathbf{1}_1[0]$ & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
+$\IC(\mathbf{1}_{-1})$ & $\mathbf{1}_{-1}[0]$ & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
 \hline
-\end{array}
-\]
-\end{spacing}
+\end{tabular}
 
 \vspace{0.1in}
-
-\noindent 
-Using the trace of Frobenius values, we find that 
+\noindent Using the trace of Frobenius values, we find that 
 \[
@@
 \caption{Notation conversion chart.}
-\begin{spacing}{1.3}
+\begin{spacing}{1.2}
 \begin{tabular}{| c|l | l | }

### 2017-08-02 Geometric types.tex
Corrections to table of standard sheaves
Small changes to the tables on perverse sheaves

--- 2017-07-02 Geometric types.tex
@@
 $1$ & $\{1\}$ \\
-$-1$ & $\{-1\}$ \\
+$2$ & $\{2\}$ \\
 \hline
@@
 \hline
-\IC(\mathbf{1}_{C_3})  &  \mathbf{1}_{C_3}[3]  & -1 & -1 & -1 & -1 & -1 & -1 & -1 \\
- \IC(\mathbf{1}_{C_2})  &  \mathbf{1}_{C_2}[2] \oplus \mathbf{1}_1[0]  & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
+\IC(\mathbf{1}_{C_3})  &  \mathbf{1}_{\SL_2}[3]  & -1 & -1 & -1 & -1 & -1 & -1 & -1 \\
+ \IC(\mathbf{1}_{C_2})  &  \mathbf{1}_{C_2}[2] \oplus \mathbf{1}_1[2]  & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
  \IC(\cs{E}_{C_2})  &  \cs{E}_{C_2}[2]  & 0 & 0 & 0 &  \sqrt{-3}  &  -\sqrt{-3} & 0 & 0 \\
- \IC(\mathbf{1}_{C_2^-})  &  \mathbf{1}_{C_2^-}[2] \oplus \mathbf{1}_{-1}[0]  & 0 & 1 & 0 & 0 & 0 & 1 & 1 \\
+ \IC(\mathbf{1}_{C_2^-})  &  \mathbf{1}_{C_2^-}[2] \oplus \mathbf{1}_{2}[2]  & 0 & 1 & 0 & 0 & 0 & 1 & 1 \\
  \IC(\cs{E}_{C_2^-})  &  \cs{E}_{C_2^-}[2]  & 0 & 0 & 0 & 0 & 0 &   \sqrt{-3}  &   -\sqrt{-3}  \\
  \IC(\mathbf{1}_1)  &  \mathbf{1}_1[0]  & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
- \IC(\mathbf{1}_{-1})  &  \mathbf{1}_{-1}[0]  & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
+ \IC(\mathbf{1}_{2})  &  \mathbf{1}_{2}[0]  & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
 \hline
@@
 \[
-- \IC(\mathbf{1}_{C_3}) - \frac32 \IC(\mathbf{1}_{C_2}) + \frac12 \IC(\cs{E}_{C_2}) - \frac32 \IC(\mathbf{1}_{C_2^-}) - \frac12 \IC(\cs{E}_{C_2^-}) + \frac32 \IC(\mathbf{1}_1) + \frac32 \IC(\mathbf{1}_{-1})
+- \IC(\mathbf{1}_{C_3}) - \frac32 \IC(\mathbf{1}_{C_2}) + \frac12 \IC(\cs{E}_{C_2}) - \frac32 \IC(\mathbf{1}_{C_2^-}) - \frac12 \IC(\cs{E}_{C_2^-}) + \frac32 \IC(\mathbf{1}_1) + \frac32 \IC(\mathbf{1}_{2})
 \]

### 2017-08-02 Geometric types.tex
A few other minor changes to the SL(2,3) character sheaves

--- 2017-08-02 Geometric types.tex
@@
 $C_2^-$ & $\{-u : \mbox{ regular unipotent $u$}\}$ \\
-$1$ & $\{1\}$ \\
-$2$ & $\{2\}$ \\
+$\{1\}$ & $\{1\}$ \\
+$\{2\}$ & $\{2\}$ \\
 \hline
@@
 Each Weil character sheaf on $\SL_2$ over $\FFF$ is the perverse extension of one of the following local systems: the rank-$1$ constant sheaf $\mathbf{1}_{C_3}$ (resp.
-$\mathbf{1}_{C_2}$, $\mathbf{1}_{C_2^-}$, $\mathbf{1}_{1}$,  $\mathbf{1}_{-1}$) on $C_3$ (resp.
-$C_2$, $C_2^-$, $1$, $-1$), or the non-trivial rank-$1$ local system $\cs{E}_{C_2}$  (resp.
-$\cs{E}_{C_2^-}$) on $C_2^{-1}$  (resp.
+$\mathbf{1}_{C_2}$, $\mathbf{1}_{C_2^-}$, $\mathbf{1}_{\{1\}}$,  $\mathbf{1}_{\{2\}}$) on $C_3$ (resp.
+$C_2$, $C_2^-$, $\{1\}$, $\{2\}$), or the non-trivial rank-$1$ local system $\cs{E}_{C_2}$  (resp.
+$\cs{E}_{C_2^-}$) on $C_2^{-}$  (resp.
 $\cs{E}_{C_2^-}$) trivialized by the double cover of $C_2$ (resp.
@@
 \text{Perverse} & \text{Standard} & \multicolumn{7}{|c|}{\text{Trace of Frobenius values at conjugacy classes}} \\ \cline{3-9}
-\text{Sheaf} & \text{Sheaves} & (\begin{smallmatrix}1 & 0\\ 0 & 1\end{smallmatrix}) & (\begin{smallmatrix}2 & 0\\ 0 & 2\end{smallmatrix}) & (\begin{smallmatrix}0 & 1\\ 2 & 0\end{smallmatrix})  & (\begin{smallmatrix}1 & 1\\ 0 & 1\end{smallmatrix})  & (\begin{smallmatrix}1 & 2\\ 0 & 1\end{smallmatrix}) & (\begin{smallmatrix}2 & 1\\ 0 & 2\end{smallmatrix})  & (\begin{smallmatrix}2 & 2\\ 0 & 2\end{smallmatrix}) \\
+\text{Sheaf} & \text{Sheaves} & (\begin{smallmatrix}1 & 0 \\ 0 & 1\end{smallmatrix}) & (\begin{smallmatrix} 2 & 0\\ 0 & 2\end{smallmatrix}) & (\begin{smallmatrix}0 & 1 \\ 2 & 0\end{smallmatrix})  & (\begin{smallmatrix} 1 & 1\\ 0 & 1 \end{smallmatrix})  & (\begin{smallmatrix}1 & 2 \\ 0 & 1 \end{smallmatrix}) & (\begin{smallmatrix} 2 & 1\\ 0 & 2 \end{smallmatrix})  & (\begin{smallmatrix}2 & 2 \\ 0 & 2 \end{smallmatrix}) \\
 \hline
 \IC(\mathbf{1}_{C_3})  &  \mathbf{1}_{\SL_2}[3]  & -1 & -1 & -1 & -1 & -1 & -1 & -1 \\
- \IC(\mathbf{1}_{C_2})  &  \mathbf{1}_{C_2}[2] \oplus \mathbf{1}_1[2]  & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
+ \IC(\mathbf{1}_{C_2})  &  \mathbf{1}_{C_2}[2] \oplus \mathbf{1}_{\{1\}}[2]  & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
  \IC(\cs{E}_{C_2})  &  \cs{E}_{C_2}[2]  & 0 & 0 & 0 &  \sqrt{-3}  &  -\sqrt{-3} & 0 & 0 \\
- \IC(\mathbf{1}_{C_2^-})  &  \mathbf{1}_{C_2^-}[2] \oplus \mathbf{1}_{2}[2]  & 0 & 1 & 0 & 0 & 0 & 1 & 1 \\
+ \IC(\mathbf{1}_{C_2^-})  &  \mathbf{1}_{C_2^-}[2] \oplus \mathbf{1}_{\{2\}}[2]  & 0 & 1 & 0 & 0 & 0 & 1 & 1 \\
  \IC(\cs{E}_{C_2^-})  &  \cs{E}_{C_2^-}[2]  & 0 & 0 & 0 & 0 & 0 &   \sqrt{-3}  &   -\sqrt{-3}  \\
- \IC(\mathbf{1}_1)  &  \mathbf{1}_1[0]  & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
- \IC(\mathbf{1}_{2})  &  \mathbf{1}_{2}[0]  & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
+ \IC(\mathbf{1}_{\{1\}})  &  \mathbf{1}_{\{1\}}[0]  & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
+ \IC(\mathbf{1}_{\{2\}})  &  \mathbf{1}_{\{2\}}[0]  & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
 \hline
@@
 \[
-- \IC(\mathbf{1}_{C_3}) - \frac32 \IC(\mathbf{1}_{C_2}) + \frac12 \IC(\cs{E}_{C_2}) - \frac32 \IC(\mathbf{1}_{C_2^-}) - \frac12 \IC(\cs{E}_{C_2^-}) + \frac32 \IC(\mathbf{1}_1) + \frac32 \IC(\mathbf{1}_{2})
+- \IC(\mathbf{1}_{C_3}) - \frac32 \IC(\mathbf{1}_{C_2}) + \frac12 \IC(\cs{E}_{C_2}) - \frac32 \IC(\mathbf{1}_{C_2^-}) - \frac12 \IC(\cs{E}_{C_2^-}) + \frac32 \IC(\mathbf{1}_{\{1\}}) + \frac32 \IC(\mathbf{1}_{\{2\}})
 \]

### 2017-08-04 Geometric types.tex
Working on section 4

--- 2017-08-02 Geometric types.tex
@@
 
-For connected, commutative groups, the standard method for geometrizing a character $\chi$ is to use the Lang isogeny $L : G \to G$, defined by $L(x) = x^{-1}\Frob{G}(x)$.
-Then the pushforward $L_!
+For connected, commutative groups, the standard method for geometrizing a character $\chi$ is to use the Lang isogeny $L : G \to G$, defined by $L(y) = y^{-1}\Frob{G}(y)$.
+The pushforward $L_!
 (\EE)_G$ of the constant sheaf decomposes into a direct sum of rank $1$ local systems according to characters of the automorphism group $G(k)$ of the cover $L$.
+
+If $G$ is nonabelian or disconnected, a similar strategy sometimes succeeds in geometrizing characters $\chi : G(k) \to \EEx$.
+Suppose that $G(k) \subset \image(L)$ (which will hold if $G$ is connected).  Then we may associate to each $\chi$ a function $\tilde{\chi}$ as follows.
+If $x \in G(k)$, write $x = L(y) = y^{-1}\Frob{G}(y)$ and define $\tilde{\chi}(x) = \chi(\Frob{G}(y) y^{-1})$.
+Note that $\tilde{\chi}$ is well defined since changing to $y$ to $gy$ for $g \in G(k)$ has the
+effect of conjugating $\Frob{G}(y) y^{-1}$ by $g$, which has no effect on the value of $\chi(\Frob{G}(y) y^{-1})$.
+Our second assumption required to geometrize $\chi$ is that $\tilde{\chi}$ is also a character.
 

### 2017-08-04 Geometric types.tex
Adding tilde{L}

@@
 Suppose that $G(k) \subset \image(L)$ (which will hold if $G$ is connected).  Then we may associate to each $\chi$ a function $\tilde{\chi}$ as follows.
-If $x \in G(k)$, write $x = L(y) = y^{-1}\Frob{G}(y)$ and define $\tilde{\chi}(x) = \chi(\Frob{G}(y) y^{-1})$.
-Note that $\tilde{\chi}$ is well defined since changing to $y$ to $gy$ for $g \in G(k)$ has the
-effect of conjugating $\Frob{G}(y) y^{-1}$ by $g$, which has no effect on the value of $\chi(\Frob{G}(y) y^{-1})$.
+Define $\tilde{L} : G \to G$ by $\tilde{L}(y) = \Frob{G}(y)y^{-1}$.
+If $x \in G(k)$, write $x = L(y) = y^{-1}\Frob{G}(y)$ and define $\tilde{\chi}(x) = \chi(\tilde{L}(y))$.
+Note that $\tilde{\chi}$ is well defined since changing $y$ to $gy$ for $g \in G(k)$ has the
+effect of conjugating $\tilde{L}(y)$ by $g$, which has no effect on the value $\chi(\tilde{L}(y))$.
 Our second assumption required to geometrize $\chi$ is that $\tilde{\chi}$ is also a character.

### 2017-08-04 Geometric types.tex
(Lang.1) and (Lang.2)

@@
 If $G$ is nonabelian or disconnected, a similar strategy sometimes succeeds in geometrizing characters $\chi : G(k) \to \EEx$.
-Suppose that $G(k) \subset \image(L)$ (which will hold if $G$ is connected).  Then we may associate to each $\chi$ a function $\tilde{\chi}$ as follows.
+Suppose that
+\begin{enumerate}
+\labitem{(Lang.1)}{Lang.1} $G(k) \subset \image(L)$ (which will hold if $G$ is connected).
+\end{enumerate}
+Then we may associate to each $\chi$ a function $\tilde{\chi}$ as follows.
 Define $\tilde{L} : G \to G$ by $\tilde{L}(y) = \Frob{G}(y)y^{-1}$.
-If $x \in G(k)$, write $x = L(y) = y^{-1}\Frob{G}(y)$ and define $\tilde{\chi}(x) = \chi(\tilde{L}(y))$.
+If $x \in G(k)$, write $x = L(y)$ and define $\tilde{\chi}(x) = \chi(\tilde{L}(y))$.
 Note that $\tilde{\chi}$ is well defined since changing $y$ to $gy$ for $g \in G(k)$ has the
 effect of conjugating $\tilde{L}(y)$ by $g$, which has no effect on the value $\chi(\tilde{L}(y))$.
-Our second assumption required to geometrize $\chi$ is that $\tilde{\chi}$ is also a character.
+Then we must also assume that
+\begin{enumerate}
+\labitem{(Lang.2)}{Lang.2} $\tilde{\chi}$ is also a character.
+\end{enumerate}
 

### 2017-08-04 Geometric types.tex
Swap 4.1 and 4.2

@@
 
-\subsection{Equivariance Weil sheaf complexes (move to somewhere else?)}\label{ssec:equivariant}
-
-Suppose $(\cs{L},\mu)$ is a linear character sheaf on $G$. 
-As the diagram below explains, the isomorphism $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ determines an isomorphism $a^*\cs{L} \to p_2^*\cs{L}$ of Weil local systems on $G\times G$, where  $a : G\times G\to G$ is conjugation $a(x,y)=xyx^{-1}$ and $p_2: G\times G\to G$ is projection $p_2(x,y)=y$.
-\[
-\begin{tikzcd}[column sep = 30]
-a^*\cs{L} \arrow[equal]{d}[swap]{a= m\circ (m\times (i\circ p_1))} \arrow[dotted]{r} & p_2^*\cs{L}  \\
-(m\times (i\circ p_1))^* m^*\cs{L} \arrow{d}[swap]{(m\times (i\circ p_1))^*\mu}  & p_1^*(\cs{L} \otimes \cs{L}^\vee) \otimes p_2^*\cs{L} \arrow[equal]{u}[swap]{\cs{L}\otimes \cs{L}^\vee \iso (\EE)_{G}}\\
-m^*\cs{L}\otimes (i\circ p_1))^*\cs{L} \arrow{r}{\mu \otimes \id} & p_1^*\cs{L} \otimes p_2^*\cs{L} \otimes p_1^*\cs{L}^\vee \arrow[equal]{u}
-\end{tikzcd}
-\]
-Although every linear character sheaf on $G$ is a conjugation-equivariant Weil local systems on $G$, the converse is certainly not true.
-
-For connected reductive groups $G$ over $k$, Lusztig's character sheaves are simple perverse sheaves $\IC(C,\mathcal{L})$ on $G$ that come equipped with an isomorphism $a^*\, \IC(C,\mathcal{L}) \to p_2^*\, \IC(C,\mathcal{L})$ in Deligne's category $D^b_c(G;\EE)$.
-Consequently, when $\IC(C,\mathcal{L})$ is also a Weil sheaf complex, its trace of Frobenius function $\trFrob{\IC(C,\cs{L})} : G(k)\to \EE$ is a class function, called the characteristic function of $\IC(C,\cs{L})$.
-By \cite{lusztig:86a}*{Cor. 25.7}, Weil character sheaves on $G$ determine a basis for the $\EE$-space of class functions on $G(k)$.
-In particular, any character of any representation of $G(k)$ can be expressed as a ${\bar \QQ}$-linear combination of characteristic functions of Weil character sheaves on $G$.
-We will refer to a formal sum $\sum_{i\in I} a_i \cs{F}_i$ of conjugation-equivariant Weil $\ell$-adic sheaf complexes with ${\bar \QQ}$-coefficients as a rational virtual equivariant Weil sheaf complex on $G$.
-When specialized to the case of characters $\chi$ of $G(k)$, Lusztig's theory of character sheaves geometrizes $\chi$ as a rational virtual equivariant Weil sheaf complex on $G$.
-We see an example of this in Section~\ref{ssec:SL23}.
-
 \subsection{Pushforward along the Lang isogeny}
@@
 \begin{enumerate}
-\labitem{(Lang.1)}{Lang.1} $G(k) \subset \image(L)$ (which will hold if $G$ is connected).
+\labitem{(L.1)}{L.1} $G(k) \subset \image(L)$ (which will hold if $G$ is connected).
 \end{enumerate}
@@
 \begin{enumerate}
-\labitem{(Lang.2)}{Lang.2} $\tilde{\chi}$ is also a character.
+\labitem{(L.2)}{L.2} $\tilde{\chi}$ is also a character.
 \end{enumerate}
+
+\subsection{Equivariant Weil sheaf complexes}\label{ssec:equivariant}
+
+Suppose $(\cs{L},\mu)$ is a linear character sheaf on $G$. 
+As the diagram below explains, the isomorphism $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ determines an isomorphism $a^*\cs{L} \to p_2^*\cs{L}$ of Weil local systems on $G\times G$, where  $a : G\times G\to G$ is conjugation $a(x,y)=xyx^{-1}$ and $p_2: G\times G\to G$ is projection $p_2(x,y)=y$.
+\[
+\begin{tikzcd}[column sep = 30]
+a^*\cs{L} \arrow[equal]{d}[swap]{a= m\circ (m\times (i\circ p_1))} \arrow[dotted]{r} & p_2^*\cs{L}  \\
+(m\times (i\circ p_1))^* m^*\cs{L} \arrow{d}[swap]{(m\times (i\circ p_1))^*\mu}  & p_1^*(\cs{L} \otimes \cs{L}^\vee) \otimes p_2^*\cs{L} \arrow[equal]{u}[swap]{\cs{L}\otimes \cs{L}^\vee \iso (\EE)_{G}}\\
+m^*\cs{L}\otimes (i\circ p_1))^*\cs{L} \arrow{r}{\mu \otimes \id} & p_1^*\cs{L} \otimes p_2^*\cs{L} \otimes p_1^*\cs{L}^\vee \arrow[equal]{u}
+\end{tikzcd}
+\]
+Although every linear character sheaf on $G$ is a conjugation-equivariant Weil local systems on $G$, the converse is certainly not true.
+
+For connected reductive groups $G$ over $k$, Lusztig's character sheaves are simple perverse sheaves $\IC(C,\mathcal{L})$ on $G$ that come equipped with an isomorphism $a^*\, \IC(C,\mathcal{L}) \to p_2^*\, \IC(C,\mathcal{L})$ in Deligne's category $D^b_c(G;\EE)$.
+Consequently, when $\IC(C,\mathcal{L})$ is also a Weil sheaf complex, its trace of Frobenius function $\trFrob{\IC(C,\cs{L})} : G(k)\to \EE$ is a class function, called the characteristic function of $\IC(C,\cs{L})$.
+By \cite{lusztig:86a}*{Cor. 25.7}, Weil character sheaves on $G$ determine a basis for the $\EE$-space of class functions on $G(k)$.
+In particular, any character of any representation of $G(k)$ can be expressed as a ${\bar \QQ}$-linear combination of characteristic functions of Weil character sheaves on $G$.
+We will refer to a formal sum $\sum_{i\in I} a_i \cs{F}_i$ of conjugation-equivariant Weil $\ell$-adic sheaf complexes with ${\bar \QQ}$-coefficients as a rational virtual equivariant Weil sheaf complex on $G$.
+When specialized to the case of characters $\chi$ of $G(k)$, Lusztig's theory of character sheaves geometrizes $\chi$ as a rational virtual equivariant Weil sheaf complex on $G$.
+We see an example of this in Section~\ref{ssec:SL23}.
 

### 2017-08-20 Geometric types.tex
Working on Section 4

@@
 The pushforward $L_!
-(\EE)_G$ of the constant sheaf decomposes into a direct sum of rank $1$ local systems according to characters of the automorphism group $G(k)$ of the cover $L$.
+(\EE)_G$ of the constant sheaf decomposes into a direct sum of rank $1$ local systems according to characters of the automorphism group $G(k)$ of the cover $L$, and the local system $\cs{L}$ associated to $\chi^{-1}$ will have $\TrFrob{}(\cs{L}) = \chi$.
 
@@
 Define $\tilde{L} : G \to G$ by $\tilde{L}(y) = \Frob{G}(y)y^{-1}$.
-If $x \in G(k)$, write $x = L(y)$ and define $\tilde{\chi}(x) = \chi(\tilde{L}(y))$.
-Note that $\tilde{\chi}$ is well defined since changing $y$ to $gy$ for $g \in G(k)$ has the
-effect of conjugating $\tilde{L}(y)$ by $g$, which has no effect on the value $\chi(\tilde{L}(y))$.
-Then we must also assume that
+If $x \in G(k)$, write $x = \tilde{L}(y)$ and define $\tilde{\chi}(x) = \chi(L(y))$.
+Note that $\tilde{\chi}$ is well defined since changing $y$ to $ya$ for $a \in G(k)$ has the
+effect of conjugating $L(y)$ by $a^{-1}$, which has no effect on the value $\chi(L(y))$.
+In order to obtain a local system with trace $\chi$, we must also assume that
 \begin{enumerate}
@@
 \end{enumerate}
+
+\begin{proposition}
+Let $G$ be a smooth group scheme over $k$ and assume \ref{L.1} and \ref{L.2}.  Let $\cs{L} = (L_!(\EE)_G)_{\tilde{\chi}^{-1}}$.  Then $\TrFrob{}(\cs{L}) = \chi$.
+\end{proposition}
+\begin{proof}
+The stalk of $\cs{L}$ at $x \in G(k)$ is
+\[
+\cs{L}_x = \{ s : L^{-1}(x) \to \EE : s(ay) = \tilde{\chi}^{-1}(a) s(y) \mbox{ for all $a \in G(k), y \in L^{-1}(x)$}\}.
+\]
+Frobenius acts by
+\[
+(^{\Frob{}}s)(y) = s(\Frob{}^{-1}(y)) = s(yx^{-1}) = s(yx^{-1}y^{-1}y) = \tilde{\chi}(yxy^{-1})s(y) = \tilde{\chi}(\tilde{L}(y))s(y) = \chi(x)s(y),
+\]
+thus proving the claim. Need $z$ with $L(z) = \tilde{L}(y)$.  Note that $z = \Frob{G}(y^{-1})$ does not do the job.
+\end{proof}
 

### 2017-08-21 Geometric types.tex
Fixing 4.1

@@
 If $G$ is nonabelian or disconnected, a similar strategy sometimes succeeds in geometrizing characters $\chi : G(k) \to \EEx$.
+Define $\tilde{L} : G \to G$ by $\tilde{L}(y) = \Frob{G}(y)y^{-1}$.
+The fibers of $L$ are right cosets of $G(k)$ and the fibers of $\tilde{L}$ are left cosets.
 Suppose that
 \begin{enumerate}
-\labitem{(L.1)}{L.1} $G(k) \subset \image(L)$ (which will hold if $G$ is connected).
+\labitem{(L.1)}{L.1} $G(k) \subset \image(\tilde{L}) \cap \image(L)$ (which will hold if $G$ is connected).
 \end{enumerate}
-Then we may associate to each $\chi$ a function $\tilde{\chi}$ as follows.
-Define $\tilde{L} : G \to G$ by $\tilde{L}(y) = \Frob{G}(y)y^{-1}$.
-If $x \in G(k)$, write $x = \tilde{L}(y)$ and define $\tilde{\chi}(x) = \chi(L(y))$.
+Then we may associate to each $\chi$ a function $\tilde{\chi} : G(k) \to \EEx$ as folllows.
+If $z \in G(k)$, write $z = \tilde{L}(y)$ and define $\tilde{\chi}(z) = \chi(L(y))$.
 Note that $\tilde{\chi}$ is well defined since changing $y$ to $ya$ for $a \in G(k)$ has the
@@
 \]
-Frobenius acts by
-\[
-(^{\Frob{}}s)(y) = s(\Frob{}^{-1}(y)) = s(yx^{-1}) = s(yx^{-1}y^{-1}y) = \tilde{\chi}(yxy^{-1})s(y) = \tilde{\chi}(\tilde{L}(y))s(y) = \chi(x)s(y),
-\]
-thus proving the claim. Need $z$ with $L(z) = \tilde{L}(y)$.  Note that $z = \Frob{G}(y^{-1})$ does not do the job.
+For any $y \in L^{-1}(x)$, note that $\Frob{G}^{-1}(y) = yx^{-1}$ and $\tilde{L}(y) = yxy^{-1} \in G(k)$.  Frobenius acts on $s \in \cs{L}_x$ by
+\[
+(^{\Frob{}}s)(y) = s(\Frob{G}^{-1}(y)) = \tilde{\chi}^{-1}(yx^{-1}y^{-1})s(y) = \tilde{\chi}(\tilde{L}(y))s(y) = \chi(x)s(y),
+\]
+thus proving the claim.
 \end{proof}

### 2017-08-28 Geometric types.tex
Adding some todo notes and removing section 4.5

@@
 As the diagram below explains, the isomorphism $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ determines an isomorphism $a^*\cs{L} \to p_2^*\cs{L}$ of Weil local systems on $G\times G$, where  $a : G\times G\to G$ is conjugation $a(x,y)=xyx^{-1}$ and $p_2: G\times G\to G$ is projection $p_2(x,y)=y$.
+\todo{problem with bottom left of diagram}
 \[
@@
 \]
-Although every linear character sheaf on $G$ is a conjugation-equivariant Weil local systems on $G$, the converse is certainly not true.
+Although every linear character sheaf on $G$ is a conjugation-equivariant Weil local system on $G$, the converse is certainly not true.
 
@@
 By \cite{lusztig:86a}*{Cor. 25.7}, Weil character sheaves on $G$ determine a basis for the $\EE$-space of class functions on $G(k)$.
-In particular, any character of any representation of $G(k)$ can be expressed as a ${\bar \QQ}$-linear combination of characteristic functions of Weil character sheaves on $G$.
+In particular, any character of any representation of $G(k)$ can be expressed as a ${\bar \QQ}$-linear \todo{should this be $\EE$-linear?} combination of characteristic functions of Weil character sheaves on $G$.
 We will refer to a formal sum $\sum_{i\in I} a_i \cs{F}_i$ of conjugation-equivariant Weil $\ell$-adic sheaf complexes with ${\bar \QQ}$-coefficients as a rational virtual equivariant Weil sheaf complex on $G$.
 When specialized to the case of characters $\chi$ of $G(k)$, Lusztig's theory of character sheaves geometrizes $\chi$ as a rational virtual equivariant Weil sheaf complex on $G$.
-We see an example of this in Section~\ref{ssec:SL23}.
+We will see an example of this in Section~\ref{ssec:SL23}.
 
@@
   \]
-
-\subsection{The True Commutator}
-
-Kamgarpour gives an example \cite{kamgarpour:09a}*{(1.1)} of a linear character sheaf
-on $G = \PGL_n$ that does not vanish on $G\der = \PGL_n$, defined by the extension
-\[
-1 \to \mu_n \to \SL_n \to \PGL_n \to 1
-\]
-together with a non-trivial character of $\mu_n(k)$. 
-In order to obtain a relationship between linear character sheaves on $G$ and characters of $G(k)$,
-he opts to give a different definition of commutator and, in doing so, introduces a `stacky abelianization' of $G$ in order to geometrize characters of $G(\Fq)$.
- Since we have already seen the need to adapt the
-notion of character sheaf, even in the commutative case, we instead add restrictions
-to the definition of commutative character sheaf and leave the definition of $G\der$ unchanged, allowing us to use the schematic abelianization of $G$ in the geometrization of characters of $G(\Fq)$.
 

### 2017-08-28 Geometric types.tex
Editing examples section in 4.3

@@
 
-\subsection{Pushforward along the Lang isogeny}
+\subsection{Pushforward along the Lang isogeny} \label{ssec:Lang_pushforward}
 
@@
 
+Note that the resulting sheaf is a local system, but is not necessarily conjugation equivariant in the sense of Section \ref{ssec:equivariant1} because
+the Lang map is not a homomorphism when $G$ is nonabelian.
+
 \subsection{Equivariant Weil sheaf complexes}\label{ssec:equivariant}
@@
 By \cite{lusztig:86a}*{Cor. 25.7}, Weil character sheaves on $G$ determine a basis for the $\EE$-space of class functions on $G(k)$.
-In particular, any character of any representation of $G(k)$ can be expressed as a ${\bar \QQ}$-linear \todo{should this be $\EE$-linear?} combination of characteristic functions of Weil character sheaves on $G$.
+In particular, any character of any representation of $G(k)$ can be expressed as a ${\bar \QQ}$-linear combination of characteristic functions of Weil character sheaves on $G$.
 We will refer to a formal sum $\sum_{i\in I} a_i \cs{F}_i$ of conjugation-equivariant Weil $\ell$-adic sheaf complexes with ${\bar \QQ}$-coefficients as a rational virtual equivariant Weil sheaf complex on $G$.
 When specialized to the case of characters $\chi$ of $G(k)$, Lusztig's theory of character sheaves geometrizes $\chi$ as a rational virtual equivariant Weil sheaf complex on $G$.
-We will see an example of this in Section~\ref{ssec:SL23}.
-
-\subsection{\texorpdfstring{$\SL_2(\FFF)$}{\SL(2, 3)}}\label{ssec:SL23}
-
-Let $G = \SL_2$ over $\FFF$.
-Then $G\der = G$, but $G(k)\der$ is the subgroup of semisimple elements, isomorphic to the quaternion group $Q_8$ and of index $3$.
-There is thus a nontrivial character $\chi : G(k) \to \mu_3 \subset \EEx$.
-The method described above for producing a linear character sheaf corresponding to this character no longer works, since $\SL_2$ is simply connected and thus has no discrete isogenies mapping onto it.
-We may still produce a local system with the correct trace of Frobenius, by pushing forward the constant sheaf along the Lang isogeny and picking out the isotypic component corresponding to $\chi$.\todo{So, maybe not?}  However, since $\SL_2$ is nonabelian, the Lang isogeny is not a homomorphism and the resulting local system is not a linear character sheaf.
-
-Alternatively, we can use the fact that Lusztig's character sheaves provide a basis for the space of class functions \cite{lusztig:86a}*{Cor.
-25.7} to give a different geometrization of $\chi$, as discussed in Section~\ref{ssec:equivariant}.
+Of course, the resulting objects are generally not local systems.
+We will see an example of this phenomenon in the next section.
+
+\subsection{Examples}\label{ssec:badderived_examples}
+
+We now consider examples of both of these methods.  Suppose first that $G = \SL_2$ over $\FFF$.
+Then $G\der = G$, but $G(k)\der$ is the subgroup of semisimple elements,
+isomorphic to the quaternion group $Q_8$ and of index $3$.
+There is thus a nontrivial character $\chi : G(k) \to \mu_3 \subset \EEx$.  The method of Section \ref{ssec:Lang_pushforward} applies
+since $G$ is connected and $\tilde{\chi} = \chi^{-1}$ is also a character.
+
+Alternatively, we use the method discussed in Section~\ref{ssec:equivariant}. 
 Lusztig's character sheaves are constructed by perverse extension of local systems on a certain stratification of $G$.
@@
 
-\subsection{\texorpdfstring{$\PGL_2(k)$}{PGL(2, k)}}
-
-Let $G = \PGL_2$ over a finite field $k$ of odd characteristic.
-Then $G\der = G$, but $G(k)\der = \PSL_2(k)$ has index $2$ in $G(k)$.
-There is thus a nontrivial character $\chi : G(k) \to \{\pm 1\} \subset \EEx$.
-We may construct a linear character sheaf with trace $\chi$ as follows.
-Consider the standard isogeny $f : \SL_2 \to \PGL_2$ with kernel $\mu_2$ and the nontrivial map $\psi : \mu_2 \to \EEx$.
-Then the pushforward $f_!
-\EE$ of the constant sheaf on $\SL_2$ is a $2$-dimensional local system, and its $\psi$-isotypic component $(f_!
-\EE)_\psi$ is a linear character sheaf on $\PGL_2$ with trace of Frobenius $\chi$ (c.f.
-\cite{cunningham-roe:13a}*{Prop 1.10}).
-
-\todo{}
+For $p > 3$ and $G = \SL_2$, we have $G\der(k) = G(k)\der$ so the methods described above are not required.
+However, there are other examples for large $p$ where $G\der(k) \ne G(k)\der$.
+For example, when $G = \PGL_2$ and $k$ has odd characteristic, then $G\der = G$, but $G(k)\der = \PSL_2(k)$ has index $2$ in $G(k)$.
+As in the case of $\SL_2(\FFF)$, both of the methods described in this section apply to $\PGL_2$.
+
+\todo{I don't know what you mean here; should this still be included?}
 Explain that while $(f_! \EE)_\psi$ is not a commutative character sheaf, it does satisfy a weaker version of Definition~\ref{def:CCS}. Namely, there is an isomorphism $\gamma$ such that

### 2017-08-29 Geometric types.tex
Push for talking to David. Examples and methods...

@@
 \address{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive Northwest, Calgary, Alberta, Canada, {T2N~1N4}.}
-\email{cunningham@pims.math.ca}
+\email{cunning@math.ucalgary.ca}
 \author{David Roe}
@@
 The geometrization of the Yu type datum that we consider in this paper uses Lusztig's theory of character sheaves on reductive groups over finite fields, for which it is necessary to assume that the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic.
-We must also place a condition on the linear characters that appear in the Yu datum, 
-Under this assumption we show how each representation $\orho_i$ can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$, where $\cs{F}^i$ is a {\it rational virtual} sheaf complex on the Greenberg transform $G^i$ of $\underline{G}^i$, by which we mean $\cs{F}^i$ is an element in the group obtained by tensoring the Grothendieck group of such sheaves with $\QQ$.
+We must also place a condition on the linear characters that appear in the Yu datum. 
+Under these assumptions we show how each representation $\orho_i$ can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$, where $\cs{F}^i$ is a {\it rational virtual} sheaf complex on the Greenberg transform $G^i$ of $\underline{G}^i$, by which we mean $\cs{F}^i$ is an element in the Grothendieck group of such sheaves, tensored with $\QQ$.
 Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(R) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the rational virtual complex $\cs{F}^i$, we show in Theorem~\ref{thm:geotypes} that
@@
 To prove Theorem~\ref{thm:geotypes}, we must find a way to geometrize linear characters of groups of the form $\underline{H}(R)$, where $\underline{H}$ is a smooth group scheme over $R$. 
-In order to do so in a systematic manner, we begin this paper by describing the function-sheaf dictionary for characters of arbitrary smooth group schemes over finite fields. 
+In order to do so in a systematic manner, we begin this paper by describing the function-sheaf dictionary for certain \todo{Certain?} characters of arbitrary smooth group schemes over finite fields. 
 When coupled with the Greenberg transform, this dictionary will allow for the geometrization of linear characters of $\underline{H}(R)$.
@@
 
-In previous work \cite{cunningham-roe:13a}, we generalized the function-sheaf dictionary to
+In previous work \cite{cunningham-roe:13a}, we studied the function-sheaf dictionary to characters
 smooth commutative group schemes $G$, allowing for non-connected groups.
@@
 
-We repair this defect in the function-sheaf dictionary
+In this paper we repair this defect in the function-sheaf dictionary
  by describing a full subcategory $\CCS(G)$ of $\CS(G)$ so that $\TrFrob{G}$ restricts to an isomorphism $\CCSiso{G} \to G(k)^*$.
@@
 The category $\CS(G)$ has a straightforward generalization to this case, but again
-there are more character sheaves than there are characters, as pointed out by Kamgarpour \cite{kamgarpour:09a}*{(1.1)}.
+there are more character sheaves than there are characters. 
+% as pointed out by Kamgarpour \cite{kamgarpour:09a}*{(1.1)}.
 We then define category $\CCS(G)$ for such $G$ and a forgetful functor to $\CS(G)$ so that $\TrFrob{G} : \CCSiso{G} \to G\ab(k)^*$
@@
 The functor $\CCS(G) \to \CS(G)$ is not
-essentially surjective, missing the kinds of linear character sheaves highlighted by Kamgarpour.
+essentially surjective, missing the kinds of linear character sheaves highlighted by Kamgarpour in \cite{kamgarpour:09a}*{(1.1)}.
 
@@
 Then the perverse sheaf $\gcs{L}[\dim G]$ appears in the semisimple complex $\operatorname{ind}_{B,T}^{\bG}(\gcs{L}_T)$ produced by parabolic induction.
-It follows that every object in $\CCS(G)$ determines a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}.
+It follows that every object in $\CCS(G)$ determines a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}. \todo{Must revisit this}
 Of course, the sheaves arising in this way represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields, but they are precisely those needed to describe one-dimensional characters of such groups.
@@
 
-\subsection{Geometrization of characters} \label{ssec:geo}
+\subsection{Geometrizing characters trivial on the derived subgroup} \label{ssec:geo}
 
@@
 
-If $\chi$ is a character of $G(k)$ vanishing on $G\der(k)$, Section \ref{sec:noncom} provides a \emph{local system} $\cs{L}$ that is \emph{conjugation equivariant} and satisfies $\TrFrob{}(\cs{L}) = \chi$.
-In this section, we give methods for geometrizing characters that do not vanish on $G\der(k)$, though the results may not be local systems or conjugation invariant.
+If $\chi$ is a character of $G(k)$ vanishing on $G\der(k)$ then Theorem~\ref{thm:geo} shows that there is a \emph{local system} $\cs{L}$ such that $m^*\cs{L} \iso \cs{L}\boxtimes\cs{L}$ and $\TrFrob{}(\cs{L}) = \chi$.
+In this section, we give methods for geometrizing characters that do not vanish on $G\der(k)$, though the results may not be local systems or conjugation equivariant.
+
+\subsection{Conjugation equivariant sheaves}\label{ssec:equivariant}
+
+A Weil local system $\cs{L}$ is said to be \emph{conjugation equivariant} if $a^*\cs{L} \iso p_2^*\cs{L}$, where  $a : G\times G\to G$ is conjugation $a(x,y)=xyx^{-1}$ and $p_2: G\times G\to G$ is projection $p_2(x,y)=y$.
+If $(\cs{L},\mu)$ is a linear character sheaf on $G$, then $\cs{L}$ is conjugation equivariant. Indeed,
+the isomorphism $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ determines an isomorphism $a^*\cs{L} \to p_2^*\cs{L}$ of Weil local systems on $G\times G$ by the following diagram.
+\todo{problem with bottom left of diagram}
+\[
+\begin{tikzcd}[column sep = 30]
+a^*\cs{L} \arrow[equal]{d}[swap]{a= m\circ (m\times (i\circ p_1))} \arrow[dotted]{r} & p_2^*\cs{L}  \\
+(m\times (i\circ p_1))^* m^*\cs{L} \arrow{d}[swap]{(m\times (i\circ p_1))^*\mu}  & p_1^*(\cs{L} \otimes \cs{L}^\vee) \otimes p_2^*\cs{L} \arrow[equal]{u}[swap]{\cs{L}\otimes \cs{L}^\vee \iso (\EE)_{G}} \\
+(m\times (i\circ p_1))^* ( \cs{L}\boxtimes\cs{L}) \arrow[equal]{d}{m= p_1\circ(m\times(i\circ p_1))}[swap]{i\circ p_1 = p_1\circ(m\times(i\circ p_1))} & p_1^*\cs{L} \otimes p_2^*\cs{L} \otimes p_1^*\cs{L}^\vee \arrow[equal]{u} \\
+m^*\cs{L}\otimes (i\circ p_1))^*\cs{L} \arrow{r}[swap]{\mu \otimes \id} & (\cs{L}\boxtimes\cs{L})\otimes (i\circ p_1)^*\cs{L} \arrow[equal]{u}
+\end{tikzcd}
+\]
+Although every linear character sheaf on $G$ is a conjugation-equivariant Weil local system on $G$, the converse is certainly not true.
+
+\subsection{Lusztig's character sheaves}
+
+For connected reductive groups $G$ over $k$, Lusztig's character sheaves are simple perverse sheaves $\IC(C,\mathcal{L})$ on $G$ that come equipped with an isomorphism $a^*\, \IC(C,\mathcal{L}) \to p_2^*\, \IC(C,\mathcal{L})$ in the triangulated category $D^b_c(G\times G;\EE)$.
+Consequently, when $\IC(C,\mathcal{L})$ is also a Weil sheaf complex, its trace of Frobenius function $\trFrob{\IC(C,\cs{L})} : G(k)\to \EE$ is a class function, called the characteristic function of $\IC(C,\cs{L})$.
+By \cite{lusztig:86a}*{Cor. 25.7}, Weil character sheaves on $G$ determine a basis for the $\EE$-space of class functions on $G(k)$.
+In particular, any character of any representation of $G(k)$ can be expressed as a ${\bar \QQ}$-linear combination of characteristic functions of Weil character sheaves on $G$.
+We will refer to a formal sum $\sum_{i\in I} a_i \cs{F}_i$ of conjugation-equivariant Weil $\ell$-adic sheaf complexes with ${\bar \QQ}$-coefficients as a rational virtual equivariant Weil sheaf complex on $G$.
+
+When specialized to the case of characters $\chi$ of $G(k)$, Lusztig's theory of character sheaves geometrizes $\chi$ as a rational virtual equivariant Weil sheaf complex on $G$.
+Of course, the resulting objects are generally not local systems, in general.
+
+Here is an example when this method can be used to geometrize a character of $G(k)$ which is not trivial on $G\der(k)$.
+Let $G = \SL_2$ over $\FFF$.
+Then $G\der = G$, but $G(k)\der$ is the subgroup of semisimple elements,
+isomorphic to the quaternion group $Q_8$ and of index $3$.
+There is thus a nontrivial character $\chi : G(k) \to \mu_3 \subset \EEx$.  
+Lusztig's character sheaves are constructed by perverse extension of local systems on a certain stratification of $G$.
+In the case of $\SL_2$, there are five strata:
+\vspace{0.1in}
+
+\begin{center}
+\begin{spacing}{1.3}
+\begin{tabular}{|l|l|}
+\hline
+$C_3$ & regular semisimple elements \\
+$C_2$ & regular unipotent elements \\
+$C_2^-$ & $\{-u : \mbox{ regular unipotent $u$}\}$ \\
+$\{1\}$ & $\{1\}$ \\
+$\{2\}$ & $\{2\}$ \\
+\hline
+\end{tabular}
+\end{spacing}
+\end{center}
+
+%\vspace{0.1in}
+
+\noindent
+Each Weil character sheaf on $\SL_2$ over $\FFF$ is the perverse extension of one of the following local systems: the rank-$1$ constant sheaf $\mathbf{1}_{C_3}$ (resp.
+$\mathbf{1}_{C_2}$, $\mathbf{1}_{C_2^-}$, $\mathbf{1}_{\{1\}}$,  $\mathbf{1}_{\{2\}}$) on $C_3$ (resp.
+$C_2$, $C_2^-$, $\{1\}$, $\{2\}$), or the non-trivial rank-$1$ local system $\cs{E}_{C_2}$  (resp.
+$\cs{E}_{C_2^-}$) on $C_2^{-}$  (resp.
+$\cs{E}_{C_2^-}$) trivialized by the double cover of $C_2$ (resp.
+$C_2^-$).
+The following table describes these perverse sheaves by showing how they decompose in the Grothendieck group into standard sheaves on $\SL_2$, and also gives the values of the trace of Frobenius on the $7$ conjugacy classes in $\SL_2(\FFF)$.
+
+\vspace{0.1in}
+
+\begin{spacing}{1.3}
+\[
+\begin{array}{|l|l|ccccccc|}
+\hline
+\text{Perverse} & \text{Standard} & \multicolumn{7}{|c|}{\text{Trace of Frobenius values at conjugacy classes}} \\ \cline{3-9}
+\text{Sheaf} & \text{Sheaves} & (\begin{smallmatrix}1 & 0 \\ 0 & 1\end{smallmatrix}) & (\begin{smallmatrix} 2 & 0\\ 0 & 2\end{smallmatrix}) & (\begin{smallmatrix}0 & 1 \\ 2 & 0\end{smallmatrix})  & (\begin{smallmatrix} 1 & 1\\ 0 & 1 \end{smallmatrix})  & (\begin{smallmatrix}1 & 2 \\ 0 & 1 \end{smallmatrix}) & (\begin{smallmatrix} 2 & 1\\ 0 & 2 \end{smallmatrix})  & (\begin{smallmatrix}2 & 2 \\ 0 & 2 \end{smallmatrix}) \\
+\hline
+\IC(\mathbf{1}_{C_3})  &  \mathbf{1}_{\SL_2}[3]  & -1 & -1 & -1 & -1 & -1 & -1 & -1 \\
+ \IC(\mathbf{1}_{C_2})  &  \mathbf{1}_{C_2}[2] \oplus \mathbf{1}_{\{1\}}[2]  & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
+ \IC(\cs{E}_{C_2})  &  \cs{E}_{C_2}[2]  & 0 & 0 & 0 &  \sqrt{-3}  &  -\sqrt{-3} & 0 & 0 \\
+ \IC(\mathbf{1}_{C_2^-})  &  \mathbf{1}_{C_2^-}[2] \oplus \mathbf{1}_{\{2\}}[2]  & 0 & 1 & 0 & 0 & 0 & 1 & 1 \\
+ \IC(\cs{E}_{C_2^-})  &  \cs{E}_{C_2^-}[2]  & 0 & 0 & 0 & 0 & 0 &   \sqrt{-3}  &   -\sqrt{-3}  \\
+ \IC(\mathbf{1}_{\{1\}})  &  \mathbf{1}_{\{1\}}[0]  & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
+ \IC(\mathbf{1}_{\{2\}})  &  \mathbf{1}_{\{2\}}[0]  & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
+\hline
+\end{array}
+\]
+\end{spacing}
+
+\vspace{0.1in}
+\noindent Using the trace of Frobenius values, we find that the rational virtual equivariant Weil sheaf complex
+\[
+- \IC(\mathbf{1}_{C_3}) - \frac32 \IC(\mathbf{1}_{C_2}) + \frac12 \IC(\cs{E}_{C_2}) - \frac32 \IC(\mathbf{1}_{C_2^-}) - \frac12 \IC(\cs{E}_{C_2^-}) + \frac32 \IC(\mathbf{1}_{\{1\}}) + \frac32 \IC(\mathbf{1}_{\{2\}})
+\]
+geometrizes $\chi$.
+
+Note that all seven character sheaves appear in this geometrization, even though we start just with a character; in particular, the geometrization of the character $\chi$ given by this method is not a local system.
+
+We remark that for $p > 3$ and $G = \SL_2$, we have $G\der(k) = G(k)\der$ so, in this case, any character of $G(k)$ may be geometrized by a local system by Theorem~\ref{thm:geo}, so Lusztig's character sheaves are not required.
 
@@
 
-\begin{proposition}
+\begin{proposition}\label{prop:chitilde}
 Let $G$ be a smooth group scheme over $k$ and assume \ref{L.1} and \ref{L.2}.  Let $\cs{L} = (L_!(\EE)_G)_{\tilde{\chi}^{-1}}$.  Then $\TrFrob{}(\cs{L}) = \chi$.
@@
 
-Note that the resulting sheaf is a local system, but is not necessarily conjugation equivariant in the sense of Section \ref{ssec:equivariant1} because
+Note that the resulting sheaf is a local system, but is not necessarily conjugation equivariant because
 the Lang map is not a homomorphism when $G$ is nonabelian.
 
-\subsection{Equivariant Weil sheaf complexes}\label{ssec:equivariant}
-
-Suppose $(\cs{L},\mu)$ is a linear character sheaf on $G$. 
-As the diagram below explains, the isomorphism $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ determines an isomorphism $a^*\cs{L} \to p_2^*\cs{L}$ of Weil local systems on $G\times G$, where  $a : G\times G\to G$ is conjugation $a(x,y)=xyx^{-1}$ and $p_2: G\times G\to G$ is projection $p_2(x,y)=y$.
-\todo{problem with bottom left of diagram}
-\[
-\begin{tikzcd}[column sep = 30]
-a^*\cs{L} \arrow[equal]{d}[swap]{a= m\circ (m\times (i\circ p_1))} \arrow[dotted]{r} & p_2^*\cs{L}  \\
-(m\times (i\circ p_1))^* m^*\cs{L} \arrow{d}[swap]{(m\times (i\circ p_1))^*\mu}  & p_1^*(\cs{L} \otimes \cs{L}^\vee) \otimes p_2^*\cs{L} \arrow[equal]{u}[swap]{\cs{L}\otimes \cs{L}^\vee \iso (\EE)_{G}}\\
-m^*\cs{L}\otimes (i\circ p_1))^*\cs{L} \arrow{r}{\mu \otimes \id} & p_1^*\cs{L} \otimes p_2^*\cs{L} \otimes p_1^*\cs{L}^\vee \arrow[equal]{u}
-\end{tikzcd}
-\]
-Although every linear character sheaf on $G$ is a conjugation-equivariant Weil local system on $G$, the converse is certainly not true.
-
-For connected reductive groups $G$ over $k$, Lusztig's character sheaves are simple perverse sheaves $\IC(C,\mathcal{L})$ on $G$ that come equipped with an isomorphism $a^*\, \IC(C,\mathcal{L}) \to p_2^*\, \IC(C,\mathcal{L})$ in Deligne's category $D^b_c(G;\EE)$.
-Consequently, when $\IC(C,\mathcal{L})$ is also a Weil sheaf complex, its trace of Frobenius function $\trFrob{\IC(C,\cs{L})} : G(k)\to \EE$ is a class function, called the characteristic function of $\IC(C,\cs{L})$.
-By \cite{lusztig:86a}*{Cor. 25.7}, Weil character sheaves on $G$ determine a basis for the $\EE$-space of class functions on $G(k)$.
-In particular, any character of any representation of $G(k)$ can be expressed as a ${\bar \QQ}$-linear combination of characteristic functions of Weil character sheaves on $G$.
-We will refer to a formal sum $\sum_{i\in I} a_i \cs{F}_i$ of conjugation-equivariant Weil $\ell$-adic sheaf complexes with ${\bar \QQ}$-coefficients as a rational virtual equivariant Weil sheaf complex on $G$.
-When specialized to the case of characters $\chi$ of $G(k)$, Lusztig's theory of character sheaves geometrizes $\chi$ as a rational virtual equivariant Weil sheaf complex on $G$.
-Of course, the resulting objects are generally not local systems.
-We will see an example of this phenomenon in the next section.
-
-\subsection{Examples}\label{ssec:badderived_examples}
-
-We now consider examples of both of these methods.  Suppose first that $G = \SL_2$ over $\FFF$.
-Then $G\der = G$, but $G(k)\der$ is the subgroup of semisimple elements,
-isomorphic to the quaternion group $Q_8$ and of index $3$.
-There is thus a nontrivial character $\chi : G(k) \to \mu_3 \subset \EEx$.  The method of Section \ref{ssec:Lang_pushforward} applies
-since $G$ is connected and $\tilde{\chi} = \chi^{-1}$ is also a character.
-
-Alternatively, we use the method discussed in Section~\ref{ssec:equivariant}. 
-Lusztig's character sheaves are constructed by perverse extension of local systems on a certain stratification of $G$.
-In the case of $\SL_2$, there are five strata:
-
-\vspace{0.1in}
-
-\begin{center}
-\begin{spacing}{1.3}
-\begin{tabular}{|l|l|}
-\hline
-$C_3$ & regular semisimple elements \\
-$C_2$ & regular unipotent elements \\
-$C_2^-$ & $\{-u : \mbox{ regular unipotent $u$}\}$ \\
-$\{1\}$ & $\{1\}$ \\
-$\{2\}$ & $\{2\}$ \\
-\hline
-\end{tabular}
-\end{spacing}
-\end{center}
-
-\vspace{0.1in}
-
-\noindent
-Each Weil character sheaf on $\SL_2$ over $\FFF$ is the perverse extension of one of the following local systems: the rank-$1$ constant sheaf $\mathbf{1}_{C_3}$ (resp.
-$\mathbf{1}_{C_2}$, $\mathbf{1}_{C_2^-}$, $\mathbf{1}_{\{1\}}$,  $\mathbf{1}_{\{2\}}$) on $C_3$ (resp.
-$C_2$, $C_2^-$, $\{1\}$, $\{2\}$), or the non-trivial rank-$1$ local system $\cs{E}_{C_2}$  (resp.
-$\cs{E}_{C_2^-}$) on $C_2^{-}$  (resp.
-$\cs{E}_{C_2^-}$) trivialized by the double cover of $C_2$ (resp.
-$C_2^-$).
-The following table describes these perverse sheaves by showing how they decompose in the Grothendieck group into standard sheaves on $\SL_2$, and also gives the values of the trace of Frobenius on the $7$ conjugacy classes in $\SL_2(\FFF)$.
-
-\vspace{0.1in}
-
-\begin{spacing}{1.3}
-\[
-\begin{array}{|l|l|ccccccc|}
-\hline
-\text{Perverse} & \text{Standard} & \multicolumn{7}{|c|}{\text{Trace of Frobenius values at conjugacy classes}} \\ \cline{3-9}
-\text{Sheaf} & \text{Sheaves} & (\begin{smallmatrix}1 & 0 \\ 0 & 1\end{smallmatrix}) & (\begin{smallmatrix} 2 & 0\\ 0 & 2\end{smallmatrix}) & (\begin{smallmatrix}0 & 1 \\ 2 & 0\end{smallmatrix})  & (\begin{smallmatrix} 1 & 1\\ 0 & 1 \end{smallmatrix})  & (\begin{smallmatrix}1 & 2 \\ 0 & 1 \end{smallmatrix}) & (\begin{smallmatrix} 2 & 1\\ 0 & 2 \end{smallmatrix})  & (\begin{smallmatrix}2 & 2 \\ 0 & 2 \end{smallmatrix}) \\
-\hline
-\IC(\mathbf{1}_{C_3})  &  \mathbf{1}_{\SL_2}[3]  & -1 & -1 & -1 & -1 & -1 & -1 & -1 \\
- \IC(\mathbf{1}_{C_2})  &  \mathbf{1}_{C_2}[2] \oplus \mathbf{1}_{\{1\}}[2]  & 1 & 0 & 0 & 1 & 1 & 0 & 0 \\
- \IC(\cs{E}_{C_2})  &  \cs{E}_{C_2}[2]  & 0 & 0 & 0 &  \sqrt{-3}  &  -\sqrt{-3} & 0 & 0 \\
- \IC(\mathbf{1}_{C_2^-})  &  \mathbf{1}_{C_2^-}[2] \oplus \mathbf{1}_{\{2\}}[2]  & 0 & 1 & 0 & 0 & 0 & 1 & 1 \\
- \IC(\cs{E}_{C_2^-})  &  \cs{E}_{C_2^-}[2]  & 0 & 0 & 0 & 0 & 0 &   \sqrt{-3}  &   -\sqrt{-3}  \\
- \IC(\mathbf{1}_{\{1\}})  &  \mathbf{1}_{\{1\}}[0]  & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
- \IC(\mathbf{1}_{\{2\}})  &  \mathbf{1}_{\{2\}}[0]  & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
-\hline
-\end{array}
-\]
-\end{spacing}
-
-\vspace{0.1in}
-\noindent Using the trace of Frobenius values, we find that the rational virtual equivariant Weil sheaf complex
-\[
-- \IC(\mathbf{1}_{C_3}) - \frac32 \IC(\mathbf{1}_{C_2}) + \frac12 \IC(\cs{E}_{C_2}) - \frac32 \IC(\mathbf{1}_{C_2^-}) - \frac12 \IC(\cs{E}_{C_2^-}) + \frac32 \IC(\mathbf{1}_{\{1\}}) + \frac32 \IC(\mathbf{1}_{\{2\}})
-\]
-also geometrizes $\chi$.  Note that all seven character sheaves appear in this geometrization, even though we start just with a character.
-
-For $p > 3$ and $G = \SL_2$, we have $G\der(k) = G(k)\der$ so the methods described above are not required.
-However, there are other examples for large $p$ where $G\der(k) \ne G(k)\der$.
-For example, when $G = \PGL_2$ and $k$ has odd characteristic, then $G\der = G$, but $G(k)\der = \PSL_2(k)$ has index $2$ in $G(k)$.
-As in the case of $\SL_2(\FFF)$, both of the methods described in this section apply to $\PGL_2$.
-
-\todo{I don't know what you mean here; should this still be included?}
-Explain that while $(f_! \EE)_\psi$ is not a commutative character sheaf, it does satisfy a weaker version of Definition~\ref{def:CCS}. Namely, there is an isomorphism $\gamma$ such that
- \[
-  \begin{tikzcd}[row sep=30]
-   m^*\cs{L} \arrow{d}[swap]{\gamma} \arrow{r}{\mu} & \cs{L}\boxtimes\cs{L} \arrow{d}{\vartheta}\\
-   \theta^*(m^*\cs{L}) \arrow{r}{{\theta}^*\mu} &  \theta^*(\cs{L}\boxtimes\cs{L}).
-  \end{tikzcd}
-  \]
+This method of geometrization also applies to the example considered above.
+Let $G = \SL_2$ over $\FFF$ and let $\chi : G(k) \to \mu_3 \subset \EEx$ be the character non-trivial on $G\der(k)$ considered above.
+In this case, $\tilde{\chi}= \chi^{-1}$. 
+Since $G$ is connected and $\tilde{\chi}$ is a character Proposition~\ref{prop:chitilde} produces a local system $\cs{L}$ on $G$ which geometrizes $\chi$; however, this $\cs{L}$ is not conjugation equivariant
+
+The same method of geometrization applies to $G = \PGL_2$ when $k$ has odd characteristic.
+In this case, $G\der = G$, but $G(k)\der = \PSL_2(k)$ has index $2$ in $G(k)$, so any non-trivial character $\chi$ of $G(k)$ ...\todo{Need help finishing this}
 
@@
 With $\varphi$ as above, note that if $r'$ is any integer greater or equal to the level $r$ of $\varphi$, then the pullback of $\cs{L}_r$ along $G_{r'} \to G_{r}$ is a linear character sheaf on $G_r$.
-Thus, $\cs{L}_{r'}$ is conjugation-equivariant in the sense of Section~\ref{ssec:equivariant}
-
-$a_r : G_r\times G_r \to G_r$ is conjugation for $G_r$, then this determines an isomorphism $a_r^*\cs{L}_r \iso (\EE)_{G_r}\boxtimes \cs{L}_r$, so $\cs{L}_r$ is
+Thus, $\cs{L}_{r'}$ is conjugation equivariant in the sense of Section~\ref{ssec:equivariant}.
 

### 2017-08-29 Geometric types.tex
Push while talking with David.

@@
 
-In previous work \cite{cunningham-roe:13a}, we studied the function-sheaf dictionary to characters
+In previous work \cite{cunningham-roe:13a}, we studied the function-sheaf dictionary for characters
 smooth commutative group schemes $G$, allowing for non-connected groups.
@@
 If $\chi$ is a character of $G(k)$ vanishing on $G\der(k)$ then Theorem~\ref{thm:geo} shows that there is a \emph{local system} $\cs{L}$ such that $m^*\cs{L} \iso \cs{L}\boxtimes\cs{L}$ and $\TrFrob{}(\cs{L}) = \chi$.
-In this section, we give methods for geometrizing characters that do not vanish on $G\der(k)$, though the results may not be local systems or conjugation equivariant.
+In this section, we give methods for geometrizing characters that do not vanish on $G\der(k)$, though the results may not be local systems or conjugation equivariant, a notion that we now define.
 
@@
 the isomorphism $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ determines an isomorphism $a^*\cs{L} \to p_2^*\cs{L}$ of Weil local systems on $G\times G$ by the following diagram.
-\todo{problem with bottom left of diagram}
 \[
@@
 (m\times (i\circ p_1))^* m^*\cs{L} \arrow{d}[swap]{(m\times (i\circ p_1))^*\mu}  & p_1^*(\cs{L} \otimes \cs{L}^\vee) \otimes p_2^*\cs{L} \arrow[equal]{u}[swap]{\cs{L}\otimes \cs{L}^\vee \iso (\EE)_{G}} \\
-(m\times (i\circ p_1))^* ( \cs{L}\boxtimes\cs{L}) \arrow[equal]{d}{m= p_1\circ(m\times(i\circ p_1))}[swap]{i\circ p_1 = p_1\circ(m\times(i\circ p_1))} & p_1^*\cs{L} \otimes p_2^*\cs{L} \otimes p_1^*\cs{L}^\vee \arrow[equal]{u} \\
+(m\times (i\circ p_1))^* ( \cs{L}\boxtimes\cs{L}) \arrow[equal]{d}{i\circ p_1 = p_2\circ(m\times(i\circ p_1))}[swap]{m= p_1\circ(m\times(i\circ p_1))}  & p_1^*\cs{L} \otimes p_2^*\cs{L} \otimes p_1^*\cs{L}^\vee \arrow[equal]{u} \\
 m^*\cs{L}\otimes (i\circ p_1))^*\cs{L} \arrow{r}[swap]{\mu \otimes \id} & (\cs{L}\boxtimes\cs{L})\otimes (i\circ p_1)^*\cs{L} \arrow[equal]{u}
@@
 When specialized to the case of characters $\chi$ of $G(k)$, Lusztig's theory of character sheaves geometrizes $\chi$ as a rational virtual equivariant Weil sheaf complex on $G$.
-Of course, the resulting objects are generally not local systems, in general.
-
-Here is an example when this method can be used to geometrize a character of $G(k)$ which is not trivial on $G\der(k)$.
-Let $G = \SL_2$ over $\FFF$.
+Of course, the resulting objects are generally not local systems.
+
+For an example when this method can be used to geometrize a character of $G(k)$ which is not trivial on $G\der(k)$, consider $G = \SL_2$ over $\FFF$.
 Then $G\der = G$, but $G(k)\der$ is the subgroup of semisimple elements,
@@
 \vspace{0.1in}
-\noindent Using the trace of Frobenius values, we find that the rational virtual equivariant Weil sheaf complex
+\noindent Using the trace of Frobenius values, we find that 
+%the rational virtual equivariant Weil sheaf complex
 \[
@@
 geometrizes $\chi$.  
-
+%
 Note that all seven character sheaves appear in this geometrization, even though we start just with a character; in particular, the geometrization of the character $\chi$ given by this method is not a local system.
 
-We remark that for $p > 3$ and $G = \SL_2$, we have $G\der(k) = G(k)\der$ so, in this case, any character of $G(k)$ may be geometrized by a local system by Theorem~\ref{thm:geo}, so Lusztig's character sheaves are not required.
+We remark that for $p > 3$ and $G = \SL_2$, we have $G\der(k) = G(k)\der$.
+In this case, therefore, any character of $G(k)$ may be geometrized by a local system using Theorem~\ref{thm:geo}, so Lusztig's character sheaves are not required.
 
@@
 This method of geometrization also applies to the example considered above.
-Let $G = \SL_2$ over $\FFF$ and let $\chi : G(k) \to \mu_3 \subset \EEx$ be the character non-trivial on $G\der(k)$ considered above.
+Let $G = \SL_2$ over $\FFF$ and let $\chi : G(k) \to \mu_3 \subset \EEx$ be a non-trivial character.
 In this case, $\tilde{\chi}= \chi^{-1}$. 
-Since $G$ is connected and $\tilde{\chi}$ is a character Proposition~\ref{prop:chitilde} produces a local system $\cs{L}$ on $G$ which geometrizes $\chi$; however, this $\cs{L}$ is not conjugation equivariant
+Since $G$ is connected and $\tilde{\chi}$ is a character, Proposition~\ref{prop:chitilde} produces a local system $\cs{L}$ on $G$ which geometrizes $\chi$.
+This $\cs{L}$ is not conjugation equivariant
 
 The same method of geometrization applies to $G = \PGL_2$ when $k$ has odd characteristic.
-In this case, $G\der = G$, but $G(k)\der = \PSL_2(k)$ has index $2$ in $G(k)$, so any non-trivial character $\chi$ of $G(k)$ ...\todo{Need help finishing this}
+In this case, $G\der = G$, but $G(k)\der = \PSL_2(k)$ has index $2$ in $G(k)$.
+For the non-trivial character $\chi$ of $G(k)$, $\tilde{\chi} = \chi$, so again we may use Proposition~\ref{prop:chitilde} to geometrize $\chi$ as a local system.
 

### 2017-08-30 Geometric types.tex
Finished work on Section 5. Also made small changes to the introduction and the bibliography.

@@
 The geometrization of the Yu type datum that we consider in this paper uses Lusztig's theory of character sheaves on reductive groups over finite fields, for which it is necessary to assume that the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic.
+\todo{Descrie these two conditions at the beginning of Section 5 and point to that from here.}
 We must also place a condition on the linear characters that appear in the Yu datum. 
@@
 
+\subsection{Hypothesis}\label{ssec:hypothesis}
+
+Here we explain the hyptheses to the main result of this section, Theorem~\ref{thm:geotypes}.
+We have just seen that a Yu type datum, which consists of
+
 \subsection{Geometrization of characters of certain types}\label{ssec:geotypes}
 
-We may now give the main result of Section~\ref{sec:types}.
+We may now give the main result of Section~\ref{sec:types}, Theorem~\ref{thm:geotypes}.
 %
 Since Yu's theory refers to complex representations, and since our geometrization uses $\ell$-adic sheaves, we grit our teeth and fix an isomorphism $\CC \approx \EE$.
-From Section~\ref{ssec:equivariant}, recall the definition of a rational virtual equivariant Weil sheaf complex.
+
+From Section~\ref{ssec:equivariant}, recall the definition of a rational virtual equivariant Weil sheaf complex. \todo{!}
 

### 2017-08-30 Geometric types.tex
Oops. Pushed the wrong version last time. Here we go ...

--- 2017-08-29 Geometric types.tex
@@
 \end{quotation}
+
 In this paper we follow the suggestion above by showing that certain Yu type data are geometrizable, in the following sense.
@@
 The main result of \cite{Yu:models} shows how to find, for each $i=0, \ldots, d$, a smooth group scheme $\underline{G}^i$ over the ring $R$ with $\underline{G}^i(R)=\,^\circ K^i $.
-The geometrization of the Yu type datum that we consider in this paper uses Lusztig's theory of character sheaves on reductive groups over finite fields, for which it is necessary to assume that the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic.
-We must also place a condition on the linear characters that appear in the Yu datum. 
-Under these assumptions we show how each representation $\orho_i$ can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$, where $\cs{F}^i$ is a {\it rational virtual} sheaf complex on the Greenberg transform $G^i$ of $\underline{G}^i$, by which we mean $\cs{F}^i$ is an element in the Grothendieck group of such sheaves, tensored with $\QQ$.
+Under certain assumptions on the Yu type datum, we show how each representation $\orho_i$ can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$, where $\cs{F}^i$ is a formal ${\bar\QQ}$-linear conbination of conjugation equivariant sheaf complexes on the Greenberg transform $G^i$ of $\underline{G}^i$.
+
 Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(R) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the rational virtual complex $\cs{F}^i$, we show in Theorem~\ref{thm:geotypes} that
@@
 To prove Theorem~\ref{thm:geotypes}, we must find a way to geometrize linear characters of groups of the form $\underline{H}(R)$, where $\underline{H}$ is a smooth group scheme over $R$. 
-In order to do so in a systematic manner, we begin this paper by describing the function-sheaf dictionary for certain \todo{Certain?} characters of arbitrary smooth group schemes over finite fields. 
-When coupled with the Greenberg transform, this dictionary will allow for the geometrization of linear characters of $\underline{H}(R)$.
+In order to do so in a systematic manner, we begin this paper by describing the function-sheaf dictionary for characters of arbitrary smooth group schemes over finite fields. 
+When coupled with the Greenberg transform, this dictionary will allow for the geometrization of certain linear characters of $\underline{H}(R)$.
 
@@
 Then the perverse sheaf $\gcs{L}[\dim G]$ appears in the semisimple complex $\operatorname{ind}_{B,T}^{\bG}(\gcs{L}_T)$ produced by parabolic induction.
-It follows that every object in $\CCS(G)$ determines a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}. \todo{Must revisit this}
+It follows that every object in $\CCS(G)$ determines a Frobenius-stable character sheaf on $G$, in the sense of \cite{lusztig:85a}*{Def.~2.10}. 
 Of course, the sheaves arising in this way represent a small part of Lusztig's geometrization of characters of representations of connected, reductive groups over finite fields, but they are precisely those needed to describe one-dimensional characters of such groups.
@@
 Let $\varphi : \underline{G}(R) \to \EEx$ be quasicharacter and let $r$ be the level of $\varphi$.
-If $\varphi_r : G_m(k)\to \EEx$ is trivial on $G_{r,\operatorname{der}}(k)$ then 
+If $\varphi_r : G_r(k)\to \EEx$ is trivial on $G_{r,\operatorname{der}}(k)$ then 
 there is a commutative character sheaf $\cs{L}_r\in \CCS(G_r)$ such that 
@@
 
-Recall that the full Greenberg transform $G \ceq \Gr^{R}(\underline{G})$ is a group scheme over $\Fq$ such that $G(\Fq) = \underline{G}(R)$; it comes equipped with a morphism $G \to G_m$.
-The Weil sheaf on $G$ obtained from $\cs{L}_m$ by pullback along the morphism of group schemes $G \to G_m$ is a quasicharacter sheaf on $G$, in the sense of \cite{cunningham-roe:13a}*{Def 4.2}, such that
+Recall that the full Greenberg transform $G \ceq \Gr^{R}(\underline{G})$ is a group scheme over $\Fq$ such that $G(\Fq) = \underline{G}(R)$; it comes equipped with a morphism $G \to G_r$.
+The Weil sheaf on $G$ obtained from $\cs{L}_m$ by pullback along the morphism of group schemes $G \to G_r$ is a quasicharacter sheaf on $G$, in the sense of \cite{cunningham-roe:13a}*{Def 4.2}, such that
 \[
@@
 \end{enumerate}
-The representation $\orho^0$ and the quasicharacters $(\varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct the representations $\orho_i$ of $\oK^i$ that form the sequence of types $(\oK^i,\orho_i)$, for $i=1, \ldots, d$.
+The representation $\orho^0$ and the quasicharacters $(\varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct the representations $\orho^i$ of $\oK^i$ that form the sequence of types $(\oK^i,\orho_i)$, for $i=1, \ldots, d$.
 %
@@
 $\orho^0$ & $\,^\circ \rho^0$ & \cite{yu:01a}*{\S 15} \\
-$\orho^{i+1}$ & $\,^\circ \rho^{i+1}$ &  \cite{yu:01a}*{\S 15} \\
+$\orho_{i+1}$ & $\,^\circ \rho_{i+1}$ &  \cite{yu:01a}*{\S 15} \\
 $\varphi^i$ & $\phi_i\vert_{\,^\circ K^i }$ & \cite{yu:01a}*{\S 3}\\
@@
 
-We can now recall how Yu uses all this to construct representations $\orho^i$ of $\oK^i$, for $i=1, \ldots, d$ and the types $(\oK^i,\orho_i)$; see \cite{yu:01a}*{\S\S 4, 15}.
-The representations $\orho^i$ and $\orho_i$ are defined recursively.
+We can now recall how Yu uses all this to construct the types $(\oK^i,\orho_i)$; see \cite{yu:01a}*{\S\S 4, 15}.
+The representations $\orho_i$ are defined recursively.
 For the base case $i=0$, set $\orho_0 \ceq \orho^0\otimes \varphi^0$; see \ref{Y1} above.
@@
 Pull-back along $h_{i+1}$ to form $h_{i+1}^*(W_{i+1})$, a representation of $\oK^i \ltimes J_{i+1}$.
-Write $\inf(\orho_i)$ for the representation of $\oK^i \ltimes J_{i+1}$ obtained by pulling back $\orho^i$ along $\oK^i \ltimes J_{i+1} \to \oK^i$. 
+Write $\inf(\orho_i)$ for the representation of $\oK^i \ltimes J_{i+1}$ obtained by pulling back $\orho_i$ along $\oK^i \ltimes J_{i+1} \to \oK^i$. 
 Consider the representation
@@
 \labitem{M2}{M2} The quasicharacters $\varphi^i$ appearing in \ref{Y2} are now quasicharacters of $\underline{G}^i(R)$, for $i=0, \ldots, d$.
+In fact, if $r_i$ is the level of $\varphi^i$, as it appears in Section~\ref{ssec:quasicharacters}, then $\varphi^i$ is obtained by pulling back a quasicharacter $\varphi_i\ceq \varphi^i_{r_i}$ of the smooth group scheme $G_i\ceq G^i_{r_i} \ceq \Gr_{r_i}^{R}(\underline{G}^i)$ along $G^i \to G_i$.
 \labitem{M3}{M3}
@@
 
-We may now give the main result of Section~\ref{sec:types}.
-%
+We may now give the main result of Section~\ref{sec:types}, Theorem~\ref{thm:geotypes}.
 Since Yu's theory refers to complex representations, and since our geometrization uses $\ell$-adic sheaves, we grit our teeth and fix an isomorphism $\CC \approx \EE$.
-From Section~\ref{ssec:equivariant}, recall the definition of a rational virtual equivariant Weil sheaf complex.
+
+As we recalled in Section~\ref{ssec:review}, a Yu type datum consists of compact groups $\oK^i$, a representation $\orho^0$ of $\oK^0$ and quasicharacters $\varphi^i$ of $\oK^i$, for $i=0,\ldots, d$; see \ref{Y0}, \ref{Y1} and \ref{Y2}.
+In Section~\ref{ssec:review} we also saw how a Yu type datum determines smooth group schemes $\underline{G}^i$, a representation $\varrho_0\red$ of the reductive quotient $(\underline{G}^0)\red_{k}$ of the special fibre $\underline{G}^0_{k}$ of $\underline{G}^0$, and quasicharacters $\varphi_i$ of the group of $k$-rational points on the level-$r_i$ Greenberg transform $G_i$ of $\underline{G}^i$; see \ref{M0}, \ref{M1} and \ref{M2}.
+
+Theorem~\ref{thm:geotypes} places the following conditions on the Yu type datum:
+\begin{enumerate}
+\labitem{H0}{H0} the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic;
+\labitem{H1}{H1} for each $i=0,\ldots, d$, either
+\begin{enumerate}
+\labitem{H1(a)}{H1a} $G_i$ is reductive with cyclic geometric component group, or
+\labitem{H1(b)}{H1b} the quasicharacter $\varphi_i$ of $G_i$ is trivial on  $G_{i,\operatorname{der}}(k)$.
+\end{enumerate}
+\end{enumerate}
+Hypothesis~\ref{H0} will allow us to use Lusztig's character sheaves to geometrize the character of the representation of $\orho^0$.
+Hypothesis~\ref{H1a} allows us to use Proposition~\ref{prop:quasicharacters} to geometrize each quasicharacter $\varphi^i$ using local systems on $G_i$, or more precisely, using commutative character sheaves on $G_i$;
+alternatively, Hypothesis~\ref{H1b} may be used to geometrize each quasicharacter $\varphi^i$ using an element in the Grothendieck group of perverse sheaves on $G_i$, tensored with ${\bar\QQ}$.
 
 \begin{theorem}\label{thm:geotypes}
-Let $\oK^i$ $\orho^0$, $\varphi^i$, for $i=0, \ldots d$, be a Yu type datum as in Section~\ref{ssec:review}, \ref{Y0}, \ref{Y1} and \ref{Y2}.
-Let $\underline{G}^i$ and $\varrho_0\red$ be as in Section~\ref{ssec:review}, \ref{M0} and \ref{M1}.
-Assume $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
-For $i=0, \ldots ,d$, let $G^i = \Gr_{R}(\underline{G}^i)$ be the Greenberg transform of the smooth group scheme $\underline{G}^i$ appearing in Section~\ref{ssec:review}.
-Suppose that the quasicharacters $\varphi^i$, given in Section~\ref{ssec:review}, \ref{M2}, satisfy the hypothesis of Proposition~\ref{prop:quasicharacters}.
-Then there is a rational virtual equivariant Weil sheaf complex $\cs{F}_i$ on $G^i$ such that $\trFrob{\cs{F}_i} = \trace(\orho_i)$, for $i=0, \ldots , d$.
+Let $\oK^i$, $\orho^0$ and $\varphi^i$, be a Yu type datum, with $i=0,\ldots, d$, satisfying Hypotheses~\ref{H0} and \ref{H1}.
+There is an element $\cs{F}_i$ in the Grothendieck group of conjugation equivariant Weil sheaf complexes on $G^i$, tensored with ${\bar\QQ}$, such that $\trFrob{\cs{F}_i} = \trace(\orho_i)$, where $\orho_i$ is the representation of $\oK^i$ constructed from the Yu type datum in Section~\ref{ssec:review}, for $i=0,\ldots, d$.
 \end{theorem}
@@
 Recall that $G^i(\Fq) = \underline{G}^i(R) = \oK^i$, canonically.
-Set $G_m^i = \Gr_m^{R}(\underline{G}^i)$, for $i=0, \ldots, d$.
-Then $G_m^i$ is a smooth group scheme over $\Fq$ and $G_m^i(\Fq) = \underline{G}^i(R_m)$, canonically.
-Let $m_i$ be the level of $\varphi$ as defined in Section~\ref{ssec:quasicharacters}.
-Let $\cs{L}^i_m$ be the commutative character sheaf on $G_{m_i}$ given by Proposition~\ref{prop:quasicharacters}; then
-$\trFrob{\cs{L}^i_{m_i}} = \varphi^i_{m_i}$.
-Set $m = \max\{ m_i \tq i=0, \ldots ,d\}$ and, for each $i$, let $\cs{L}^i_{m}$ be the pull-back of $\cs{L}^i_{m_i}$ along $G^i_{m} \to G^i_{m_i}$; then $\cs{L}^i_{m}$ is a linear character sheaf and
-\[
-\trFrob{\cs{L}^i_{m}} = \varphi^i_{m}.
-\]
+Let $r_i$ be the level of $\varphi^i$ as defined in Section~\ref{ssec:quasicharacters}.
+Set $r = \max\{ r_i \tq i=0, \ldots ,d\}$.
 
@@
 \]
-This uses the hypothesis that $\pi_0((\underline{G}^0)_\Fq^\reductive)$ is cyclic.
+This uses Hypothesis~\ref{H0}.
 %
-Let $A^0$ be the equivariant Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+Let $A^0$ be the conjugation equivariant Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
 Then 
@@
 The special fibre $(\underline{G}^0)_\Fq$ of the smooth group scheme $\underline{G}^0$ is itself a smooth group scheme, and may be identified with the Greenberg transform $Q^0 = \Gr^{R}_0(\underline{G}^0)$ \cite{cunningham-roe:13a}*{\S 4.3}.
-With $m\in \NN$ as above, let ${A}_m^0$ be the equivariant Weil sheaf on the algebraic group $G_m^i$ obtained by pull-back from $A^0$ along the affine morphism $G_m^i \to Q^0$.
+With $r\in \NN$ as above, let ${A}_r^0$ be the equivariant Weil sheaf on the algebraic group $G_r^i$ obtained by pull-back from $A^0$ along the affine morphism $G_r^i \to Q^0$.
 Factor
@@
 G^0(\Fq) \arrow{rr}{\trace(\orho^0)} \arrow{rd} && \EE \\
-& G_m^0(\Fq) \arrow{ru}[swap]{\trace(\orho^0)_m} 
+& G_r^0(\Fq) \arrow{ru}[swap]{\trace(\orho^0)_r} 
 \end{tikzcd}
 \end{equation}
-Observe that $\trace(\orho^0)_m$ may be recovered from ${A}_m^0$:
-\[
-\trFrob{{A}^0_m} = \trace(\orho^0)_m
+Observe that $\trace(\orho^0)_r$ may be recovered from ${A}_m^0$:
+\[
+\trFrob{{A}^0_r} = \trace(\orho^0)_r
 \]
@@
 Let $\cs{K}_0^{i+1}$ be the Weil sheaf on the special fibre of $\underline{G}^{i} \ltimes \underline{J}^{i+1}$ obtained from $W_{i+1}$ by pullback. 
-Let $\cs{K}_m^{i+1}$ be the equivariant Weil sheaf on $\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1})$ obtained from $\cs{K}_0^{i+1}$ by pullback along the affine morphism
-$\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1}) \to \Gr^{R}_0(\underline{G}^{i} \ltimes \underline{J}^{i+1})$.
-
-We now define equivariant Weil sheaves $\cs{A}^i_m$ on $G_m^i \ceq \Gr^{R}_m(\underline{G}^{i})$, for $i=0,\ldots ,d$, recursively, following the construction of the representations $\orho^i$, as reviewed in Section~\ref{ssec:review}.
-First, set $\cs{A}_m^0 = A_m^0$ and note that \eqref{eqn:tracerho} commutes with $\trace(\orho^0)_m$ replaced by $\trFrob{\cs{A}_m^0}$.
-Now, suppose $\cs{A}^i_m$ on $G_m^i$ is defined such that
-\[
-\begin{tikzcd}
-G^i(\Fq) \arrow{rr}{\trace(\orho^i)} \arrow{rd} && \EE\\
-& G_m^i(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_m^i}} & 
+Let $\cs{K}_r^{i+1}$ be the equivariant Weil sheaf on $\Gr^{R}_r(\underline{G}^{i} \ltimes \underline{J}^{i+1})$ obtained from $\cs{K}_0^{i+1}$ by pullback along the affine morphism
+$\Gr^{R}_r(\underline{G}^{i} \ltimes \underline{J}^{i+1}) \to \Gr^{R}_0(\underline{G}^{i} \ltimes \underline{J}^{i+1})$.
+
+We now define rational virtual conjugation equivariant Weil sheaves $\cs{A}^i_r$ on $G_r^i \ceq \Gr^{R}_r(\underline{G}^{i})$, for $i=0,\ldots ,d$, recursively, following the construction of the representations $\orho_i$, as reviewed in Section~\ref{ssec:review}.
+First, set $\cs{A}_r^0 = A_r^0$ and note that \eqref{eqn:tracerho} commutes with $\trace(\orho^0)_r$ replaced by $\trFrob{\cs{A}_r^0}$.
+Using Hypothesis~\ref{H1}, let $\cs{L}_i$ be the geometrization of the quasicharacter $\varphi_i \ceq \varphi^i_{r_i}$ appearing in \ref{M1}.
+If \ref{H1a} applies, then $\cs{L}_i$ is a rational virtual character sheaf on $G_i \ceq G^i_{r_i}$, using \cite{lusztig:disconnected1};
+if \ref{H1b} applies, then $\cs{L}_i$ is the commutative character sheaf on $G_i \ceq G^i_{r_i}$ given by Proposition~\ref{prop:quasicharacters} which, by Section~\ref{ssec:equivariant}, is conjugation equivariant.
+In either case, $\cs{L}_i$ is a rational virtual conjugation equivariant Weil sheaf complex and
+\[
+\trFrob{\cs{L}_i} = \varphi_i.
+\]
+For each $i$, let $\cs{L}^i_{r}$ be the pull-back of $\cs{L}_i$ along $G^i_{r} \to G_i$; then $\cs{L}^i_{r}$ is a linear character sheaf and
+\[
+\trFrob{\cs{L}^i_{r}} = \varphi^i_{r}.
+\]
+Now, suppose $\cs{A}^i_r$ on $G_r^i$ is defined such that
+\[
+\begin{tikzcd}
+G^i(\Fq) \arrow{rr}{\trace(\orho_i)} \arrow{rd} && \EE\\
+& G_r^i(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_r^i}} & 
 \end{tikzcd}
@@
 commutes.
-Applying the Greenberg functor $\Gr^{R}_m$, to \eqref{eq:pimodel} gives
+Applying the Greenberg functor $\Gr^{R}_r$ to \eqref{eq:pimodel} gives
 \begin{equation}\label{eq:pi}
@@
 \ && 1 \arrow{d} && \\
-\ && G_m^{i}\times_{G_m} J_m^{i+1} \arrow{d} && \\
-1 \arrow{r} &J_m^{i+1} \arrow{r} & G_m^i \ltimes J_m^{i+1} \arrow{d}{\pi_m^{i+1}} \arrow{r}{p_m^{i}} & G_m^i \arrow{r} & 1\\
-&& G_m^{i+1} \arrow{d} && \\
+\ && G_r^{i}\times_{G_r} J_r^{i+1} \arrow{d} && \\
+1 \arrow{r} & J_r^{i+1} \arrow{r} & G_r^i \ltimes J_r^{i+1} \arrow{d}{\pi_r^{i+1}} \arrow{r}{p_r^{i}} & G_r^i \arrow{r} & 1\\
+&& G_r^{i+1} \arrow{d} && \\
 && 1 && 
@@
 \end{equation}
-where $J_m^{i+1} \ceq \Gr^{R}_m(\underline{J}^{i+1})$ and $G_m^{i} \ceq \Gr^{R}_m(\underline{G}^{i})$.
-By \cite{bertapelle-gonzales:Greenberg}*{Prop 7.1}, the sequences are exact.
-Consider the rational virtual equivariant Weil sheaf 
-\[
-\cs{B}_m^{i+1} \ceq \cs{K}_m^{i+1} \otimes (p_m^{i})^*(\cs{A}_m^{i}\otimes \cs{L}_m^{i})
-\]
-on $G_m^{i}\ltimes J_m^{i+1}$.
-Comparing with \eqref{eq:tensor}, we see that $\trFrob{\cs{B}_m^{i+1}}$ is precisely the function obtained by factoring the character of $\orho^{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(R) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R_m)$ using the canonical identification $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R_m)$.
-In particular, $\trFrob{\cs{B}^{i+1}_m}$ is constant on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$, taking the value $\dim \orho^{i+1}$.
-With reference to the morphism $\pi_m^{i+1} : G_m^i \ltimes J_m^{i+1} \to G_m^{i+1}$ from \eqref{eq:pi}, define 
-\[
-\cs{C}_m^{i+1} \ceq (\pi_m^{i+1})_! (\cs{B}_m^{i+1}).
-\]
-Then $\cs{C}_m^{i+1}$ is an equivariant Weil sheaf and
+where $J_r^{i+1} \ceq \Gr^{R}_r(\underline{J}^{i+1})$ and $G_r^{i} \ceq \Gr^{R}_r(\underline{G}^{i})$.
+By \cite{bertapelle-gonzales:Greenberg}*{Prop 14.2}, the sequences are exact.
+Consider the rational virtual conjugation equivariant Weil sheaf 
+\[
+\cs{B}_r^{i+1} \ceq \cs{K}_r^{i+1} \otimes (p_r^{i})^*(\cs{A}_r^{i}\otimes \cs{L}_r^{i})
+\]
+on $G_r^{i}\ltimes J_r^{i+1}$.
+Comparing with \eqref{eq:tensor}, we see that $\trFrob{\cs{B}_r^{i+1}}$ is precisely the function obtained by factoring the character of $\orho^{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(R) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R_r)$ using the canonical identification $(G_r^{i}\times_{G_r} J_r^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R_r)$.
+In particular, $\trFrob{\cs{B}^{i+1}_m}$ is constant on $(G_r^{i}\times_{G_r} J_r^{i+1})(\Fq)$, taking the value $\dim \orho^{i+1}$.
+With reference to the morphism $\pi_r^{i+1} : G_r^i \ltimes J_r^{i+1} \to G_r^{i+1}$ from \eqref{eq:pi}, define 
+\[
+\cs{C}_r^{i+1} \ceq (\pi_r^{i+1})_! (\cs{B}_r^{i+1}).
+\]
+Then $\cs{C}_r^{i+1}$ is an equivariant Weil sheaf and
 \begin{eqnarray*}
-\trFrob{\cs{C}^{i+1}_m}(x)
-&=& \sum_{y\in (\pi_m^{i+1})^{-1}(x)}  \trFrob{\cs{B}_m^{i+1}}(y).
+\trFrob{\cs{C}^{i+1}_r}(x)
+&=& \sum_{y\in (\pi_r^{i+1})^{-1}(x)}  \trFrob{\cs{B}_r^{i+1}}(y).
 \end{eqnarray*}
-Since $\trFrob{\cs{B}^{i+1}_m}$ is constant on $(G_m^{i}\times_{G_m} J_m^{i+1})(\Fq)$, it follows that 
-\[
-\trFrob{\cs{C}^{i+1}_m} = n \trFrob{\cs{B}^{i+1}_m}
-\]
-on $G_m^{i+1}(\Fq)$ for $n = \# (G_m^{i}\times_{G_m} J_m^{i+1})(\Fq) \times \dim \orho^{i+1} $.
-Let $\cs{A}_m^{i+1}$ be the rational virtual equivariant Weil sheaf on $G_m^i$ given by $\cs{A}_m^{i+1} = \frac{1}{n} \cs{C}_m^{i+1}$. 
+Since $\trFrob{\cs{B}^{i+1}_r}$ is constant on $(G_r^{i}\times_{G_r} J_r^{i+1})(\Fq)$, it follows that 
+\[
+\trFrob{\cs{C}^{i+1}_r} = n \trFrob{\cs{B}^{i+1}_r}
+\]
+on $G_r^{i+1}(\Fq)$ with $n$ equal to the product of $\# (G_r^{i}\times_{G_r} J_r^{i+1})(\Fq)$ and $\dim \orho^{i+1}$.
+Let $\cs{A}_r^{i+1}$ be the rational virtual conjugation equivariant Weil sheaf on $G_r^i$ given by $\cs{A}_r^{i+1} = \frac{1}{n} \cs{C}_r^{i+1}$. 
 %
-This completes the inductive definition of $\cs{A}_m^i$ so that the following diagram commutes.
-\[
-\begin{tikzcd}
-G^{i+1}(\Fq) \arrow{rr}{\trace(\orho^{i+1})} \arrow{rd} && \EE\\
-& G_m^{i+1}(\Fq)\arrow{ru}[swap]{{\trFrob{\cs{A}_m^{i+1}}} } & 
-\end{tikzcd}
-\]
-
-Now set $\cs{F}^i_m = \cs{A}_m^{i} \otimes \cs{L}_m^i$, for $i=0, \ldots ,d$.
-Then $\cs{F}^i_m$ is a rational virtual equivariant Weil sheaf on $G^i_m = \Gr^{R}_m(\underline{G}^i)$ such that
+This completes the inductive definition of $\cs{A}_r^i$ so that the following diagram commutes.
+\[
+\begin{tikzcd}
+G^{i+1}(\Fq) \arrow{rr}{\trace(\orho_{i+1})} \arrow{rd} && \EE\\
+& G_r^{i+1}(\Fq)\arrow{ru}[swap]{{\trFrob{\cs{A}_r^{i+1}}} } & 
+\end{tikzcd}
+\]
+
+Now set $\cs{F}^i_r = \cs{A}_r^{i} \otimes \cs{L}_r^i$, for $i=0, \ldots ,d$.
+Then $\cs{F}^i_r$ is a rational virtual conjugation equivariant Weil sheaf on $G^i_r = \Gr^{R}_r(\underline{G}^i)$ such that
 \[
@@
 G^i(\Fq) \arrow{rr}{\trace(\orho_i)} \arrow{rd} && \EE\\
-& G_m(\Fq) \arrow{ru}[swap]{\trFrob{\cs{F}^i_m}} & 
+& G_r(\Fq) \arrow{ru}[swap]{\trFrob{\cs{F}^i_r}} & 
 \end{tikzcd}
@@
 commutes.
-Let $\cs{F}^i$ be the rational virtual equivariant Weil sheaf on the group scheme $G^i= \Gr_{R}(\underline{G}^i)$ obtained by pulling back $\cs{F}_m^i$ along $G^i \to G^i_m$.
+Let $\cs{F}^i$ be the rational virtual equivariant Weil sheaf on the group scheme $G^i= \Gr_{R}(\underline{G}^i)$ obtained by pulling back $\cs{F}_r^i$ along $G^i \to G^i_r$.
 Then 
@@
        title={{The Greenberg functor revisited}},
-        date={2014},
+        date={2016},
          url={http://arxiv.org/abs/1311.0051},

### 2017-08-30 Geometric types.tex
Some work on the Introduction.

@@
 Under certain assumptions on the Yu type datum, we show how each representation $\orho_i$ can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$, where $\cs{F}^i$ is a formal ${\bar\QQ}$-linear conbination of conjugation equivariant sheaf complexes on the Greenberg transform $G^i$ of $\underline{G}^i$.
-
+%
 Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(R) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the rational virtual complex $\cs{F}^i$, we show in Theorem~\ref{thm:geotypes} that
@@
 We assume $G$ is smooth, but not that it is connected, reductive or commutative. 
-The category $\CS(G)$ has a straightforward generalization to this case, but again
-there are more character sheaves than there are characters. 
+The category $\CS(G)$ has a straightforward generalization to this case.
+% but again there are more character sheaves than there are characters. 
 % as pointed out by Kamgarpour \cite{kamgarpour:09a}*{(1.1)}.
@@
 The proof of Theorem~\ref{thm:geotypes} requires: Yu's work on smooth integral models \cite{Yu:models}; the geometrization of the character of the Heisenberg-Weil representation over finite fields by Gurevich \& Hadani \cite{gurevich-hadani:07a}; Lusztig's character sheaves on reductive groups over finite fields; and finally, the function-sheaf dictionary for characters of smooth group schemes over finite fields, now at our disposal in Theorem~\ref{thm:geo}.
-These pieces are assembled in Section~\ref{ssec:geotypes}, where we prove Theorem~\ref{thm:geotypes}.
-With this theorem, we provide all of the ingredients needed to parametrize supercuspidal representations of arbitrary depth in the same category: rational virtual Weil perverse sheaves on group schemes over finite fields.
-
-The hypothesis in Theorem~\ref{thm:geotypes} -- that the geometric component group of the reductive quotient of the special fibre of the smooth group scheme $\underline{G}^0$ appearing in the Yu type datum is cyclic --  is required only because Lusztig's theory of character sheaves has the same hypothesis.
-If Lusztig's theory of character sheaves can be generalized to all disconnected reductive algebraic groups, then the hypothesis in Theorem~\ref{thm:geotypes} can be removed.
-%
-The second hypothesis  in Theorem~\ref{thm:geotypes} -- that the quasicharacters $\varphi^i$ appearing in the Yu type datum satisfy the hypothesis of Proposition~\ref{prop:quasicharacters} -- ensures that we may use Section~\ref{sec:noncom} to find a geometric type which equivariant for conjugation, as defined in Section~\ref{ssec:equivariant}.
-Section~\ref{sec:badchar} presents some evidence to suggest that this hypothesis is not always necessary. 
+In order to use these tools we must restrict our attention to Yu type data that satisfy two technical conditions, given as Hyptheses~\ref{H0} and \ref{H1}. 
+Granting these hypotheses, these pieces are assembled in Section~\ref{ssec:geotypes}, where we prove Theorem~\ref{thm:geotypes}.
+With this theorem, we provide all of the ingredients needed to parametrize certain supercuspidal representations of arbitrary depth as rational virtual conjugation equivariant Weil sheaf complexes on group schemes over finite fields.
+
 \bigskip
@@
 We also compute the automorphism groups in $\CCS(G)$.
-In Section~\ref{sec:types} we use Theorem~\ref{thm:geo} to geometrize types for supercuspidal representations of $p$-adic groups, in a sense made precise in Theorem~\ref{thm:geotypes}.
+In Section~\ref{sec:types} we use Theorem~\ref{thm:geo} to geometrize types for certain supercuspidal representations of $p$-adic groups, in a sense made precise in Theorem~\ref{thm:geotypes}.
 As preparation for the proof, we review some facts about the Heisenberg-Weil representation and its geometrization, in Section~\ref{ssec:Jacobi}.
@@
 Hypothesis~\ref{H0} will allow us to use Lusztig's character sheaves to geometrize the character of the representation of $\orho^0$.
-Hypothesis~\ref{H1a} allows us to use Proposition~\ref{prop:quasicharacters} to geometrize each quasicharacter $\varphi^i$ using local systems on $G_i$, or more precisely, using commutative character sheaves on $G_i$;
-alternatively, Hypothesis~\ref{H1b} may be used to geometrize each quasicharacter $\varphi^i$ using an element in the Grothendieck group of perverse sheaves on $G_i$, tensored with ${\bar\QQ}$.
+Hypothesis~\ref{H1a} allows us to use Proposition~\ref{prop:quasicharacters} to geometrize each quasicharacter $\varphi_i$ using local systems on $G_i$, or more precisely, using commutative character sheaves on $G_i$;
+alternatively, Hypothesis~\ref{H1b} may be used to geometrize each quasicharacter $\varphi_i$ using an element in the Grothendieck group of perverse sheaves on $G_i$, tensored with ${\bar\QQ}$.
+We remark that if Lusztig's theory of character sheaves can be generalized to all disconnected reductive algebraic groups, then Hypothesis~\ref{H0} can be removed and Hypothesis~\ref{H1a} can be replaced with the hypothesis that each $G_i$ is reductive.
+Note that when Hypothesis~\ref{H1b} applies, it provides a considerably simpler geometrization than when Hypothesis~\ref{H1a} applies.
 

### 2017-08-30 CJM/second letter to CJM.tex
Push for talking to David. Examples and methods...
Cut old stuff from the letter.

--- 2017-05-11 CJM/letter to CJM.tex
@@
 
-Thank you for sending us the review from the referee.
-We have now addressed all the comments, as summarized below.
-Allow us also to express our gratitude for such  insightful remarks and helpful comments.
 \medskip
@@
 \begin{enumerate}
-\item[(1)] We are extremely grateful for this observation.
-We had made a mistake.
-Previously, we considered a category of triples $(\cs{L},\mu,\nu)$ with a compatibility condition on $\mu : a^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ and $\nu : n^* \cs{L}\to (\EE)_{H}\boxtimes \cs{L}$.
-But that compatibility condition had the error built into it that was noticed in the review.
-In the process of fixing the error, we found that it was more natural to drop the compatibility condition entirely and replace $\mu$ as above with $\mu : n^*\cs{L} \to \cs{L}\boxtimes\cs{L}$, where $n: G\der\times G\to G$ is the restriction of the group action from $G\times G$ to $G\der\times G$.
-Also, in an effort to improve clarity of presentation of Section 3, we moved the proofs from the last subsection back into the flow of the paper, made some notational changes, and added exposition.
-Fortunately, this had the effect of simplifying the constructions and did not add to the length of the paper. 
-\item[(2)] It is quite true that it would be possible to view Section 4 as an application of our earlier paper, bypassing the the first part of the paper under review.
-Our main motivation for Sections 1--3 was twofold: to address the `defect' in the dictionary from our earlier paper; and to extend that dictionary, as it pertains to characters, to non-commutative groups.
-(Although it wasn't our motivation, we were also happy to find an alternative to the stacky abelianization of Kamgarpour.) We have added a comment to this effect after Theorem 3.12, in the hopes that it will clarify this point.
+\item[(1)]
 \end{enumerate}
@@
 To clarify this, we have used the term {\it rational virtual} for formal linear combinations of sheaf complexes, with rational coefficients.
-\item[(ii)] We replaced all instances of $\O$ with $R$, and declared $R$ to be the ring of integers of a local ring with finite residue field $k$. 
-\item[(iii)] We fixed this typo.
-\item[(iv)] Yes, there was an isomorphism sign missing here. Fixed now. This sentence is now part of the proof of Corollary 3.7
-\item[(v)] We replaced every instance of $S$ with $\Spec{R}$, which is what we meant by $S$, though we had neglected to say that.
-\item[(vi)]  The notation conversion chart now has a third column, listing the relevant section in Yu's paper.
-In fact, we have expanded this chart from 5 to 11 rows, to make the comparison with Yu's paper easier.
-We have also given a precise citation to Yu's paper showing where the "recursive construction" can be found, there.
-\item[(vii)] Fixed this typo.
+
 \end{enumerate}

### 2017-08-30 Geometric types.tex
Hypotheses labels fixed

@@
 The proof of Theorem~\ref{thm:geotypes} requires: Yu's work on smooth integral models \cite{Yu:models}; the geometrization of the character of the Heisenberg-Weil representation over finite fields by Gurevich \& Hadani \cite{gurevich-hadani:07a}; Lusztig's character sheaves on reductive groups over finite fields; and finally, the function-sheaf dictionary for characters of smooth group schemes over finite fields, now at our disposal in Theorem~\ref{thm:geo}.
-In order to use these tools we must restrict our attention to Yu type data that satisfy two technical conditions, given as Hyptheses~\ref{H0} and \ref{H1}. 
+In order to use these tools we must restrict our attention to Yu type data that satisfy two technical conditions, appearing in Section~\ref{ssec:geotypes} as Hypotheses~\ref{H0} and \ref{H1}. 
 Granting these hypotheses, these pieces are assembled in Section~\ref{ssec:geotypes}, where we prove Theorem~\ref{thm:geotypes}.
@@
 In Section~\ref{ssec:review} we also saw how a Yu type datum determines smooth group schemes $\underline{G}^i$, a representation $\varrho_0\red$ of the reductive quotient $(\underline{G}^0)\red_{k}$ of the special fibre $\underline{G}^0_{k}$ of $\underline{G}^0$, and quasicharacters $\varphi_i$ of the group of $k$-rational points on the level-$r_i$ Greenberg transform $G_i$ of $\underline{G}^i$; see \ref{M0}, \ref{M1} and \ref{M2}.
-
+%
 Theorem~\ref{thm:geotypes} places the following conditions on the Yu type datum:
 \begin{enumerate}
-\labitem{H0}{H0} the geometric component group of the reductive quotient of the special fibre of the group scheme $\underline{G}^0$ is cyclic;
+\labitem{H0}{H0} the geometric component group of $(\underline{G}^0)\red_{k}$ is cyclic;
 \labitem{H1}{H1} for each $i=0,\ldots, d$, either
@@
 Hypothesis~\ref{H0} will allow us to use Lusztig's character sheaves to geometrize the character of the representation of $\orho^0$.
-Hypothesis~\ref{H1a} allows us to use Proposition~\ref{prop:quasicharacters} to geometrize each quasicharacter $\varphi_i$ using local systems on $G_i$, or more precisely, using commutative character sheaves on $G_i$;
-alternatively, Hypothesis~\ref{H1b} may be used to geometrize each quasicharacter $\varphi_i$ using an element in the Grothendieck group of perverse sheaves on $G_i$, tensored with ${\bar\QQ}$.
+Hypothesis~\ref{H1a} may be used to geometrize each quasicharacter $\varphi_i$ using an element in the Grothendieck group of perverse sheaves on $G_i$, tensored with ${\bar\QQ}$.
+Alternatively, Hypothesis~\ref{H1b} allows us to use Proposition~\ref{prop:quasicharacters} to geometrize each quasicharacter $\varphi_i$ using local systems on $G_i$, or more precisely, using commutative character sheaves on $G_i$;
 We remark that if Lusztig's theory of character sheaves can be generalized to all disconnected reductive algebraic groups, then Hypothesis~\ref{H0} can be removed and Hypothesis~\ref{H1a} can be replaced with the hypothesis that each $G_i$ is reductive.
@@
 First, set $\cs{A}_r^0 = A_r^0$ and note that \eqref{eqn:tracerho} commutes with $\trace(\orho^0)_r$ replaced by $\trFrob{\cs{A}_r^0}$.
-Using Hypothesis~\ref{H1}, let $\cs{L}_i$ be the geometrization of the quasicharacter $\varphi_i \ceq \varphi^i_{r_i}$ appearing in \ref{M1}.
+Using Hypothesis~\ref{H1}, let $\cs{L}_i$ be the geometrization of the quasicharacter $\varphi_i \ceq \varphi^i_{r_i}$ appearing in \ref{M2}.
 If \ref{H1a} applies, then $\cs{L}_i$ is a rational virtual character sheaf on $G_i \ceq G^i_{r_i}$, using \cite{lusztig:disconnected1};

### 2017-08-30 Geometric types.tex
Clean up statement of Theorem 5.2

@@
 \begin{theorem}\label{thm:geotypes}
-Let $\oK^i$, $\orho^0$ and $\varphi^i$, be a Yu type datum, with $i=0,\ldots, d$, satisfying Hypotheses~\ref{H0} and \ref{H1}.
-There is an element $\cs{F}_i$ in the Grothendieck group of conjugation equivariant Weil sheaf complexes on $G^i$, tensored with ${\bar\QQ}$, such that $\trFrob{\cs{F}_i} = \trace(\orho_i)$, where $\orho_i$ is the representation of $\oK^i$ constructed from the Yu type datum in Section~\ref{ssec:review}, for $i=0,\ldots, d$.
+Let $(\oK^i, \orho^0, \varphi^i)$ be a Yu type datum that satisfies Hypotheses~\ref{H0} and \ref{H1}, and let $\orho_i$ be the representation of $\oK^i$ constructed from it in Section~\ref{ssec:review}.
+Then for each $i=0,\dots, d$ there is an element $\cs{F}_i \in \mathcal{K}_{\bar\QQ} D_{G^i}(X)$ such that
+\[
+\trFrob{\cs{F}_i} = \trace(\orho_i).
+\]
 \end{theorem}

### 2017-08-30 Geometric types.tex
Notation KD_G(G;E) to replace the six adjectives

@@
 The main result of \cite{Yu:models} shows how to find, for each $i=0, \ldots, d$, a smooth group scheme $\underline{G}^i$ over the ring $R$ with $\underline{G}^i(R)=\,^\circ K^i $.
-Under certain assumptions on the Yu type datum, we show how each representation $\orho_i$ can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$, where $\cs{F}^i$ is a formal ${\bar\QQ}$-linear conbination of conjugation equivariant sheaf complexes on the Greenberg transform $G^i$ of $\underline{G}^i$.
+Under certain assumptions on the Yu type datum, we show how each representation $\orho_i$ can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$, where $\cs{F}^i$ is a formal ${\bar\QQ}$-linear conbination of conjugation-equivariant sheaf complexes on the Greenberg transform $G^i$ of $\underline{G}^i$.
 %
@@
 Granting these hypotheses, these pieces are assembled in Section~\ref{ssec:geotypes}, where we prove Theorem~\ref{thm:geotypes}.
-With this theorem, we provide all of the ingredients needed to parametrize certain supercuspidal representations of arbitrary depth as rational virtual conjugation equivariant Weil sheaf complexes on group schemes over finite fields.
+With this theorem, we provide all of the ingredients needed to geometrize a class of supercuspidal representations of arbitrary depth.
 
@@
 In this paper we use a common formalism for Weil sheaves, writing $\cs{L}$ for the pair $(\gcs{L},\phi)$, where $\gcs{L}$ is an $\ell$-adic sheaf on $\bG \ceq G\otimes_{\Fq} \bFq$ and where $\phi : \Frob{}^*\gcs{L} \to \gcs{L}$ is an isomorphism of $\ell$-adic sheaves.
-We also follow convention by referring to $\cs{L}$  as a Weil sheaf on $G$. 
+We also follow convention by referring to $\cs{L}$  as a Weil sheaf on $G$, as in \cite{Deligne:Weil}*{D\'efinition 1.1.10}.
 If $\cs{L}$ and $\cs{L}' \ceq (\gcs{L}', \phi')$ are Weil sheaves, we write $\alpha : \cs{L} \to \cs{L}'$ for a morphism $\alpha : \gcs{L} \to \gcs{L}$ such that 
@@
 If $\chi$ is a character of $G(k)$ vanishing on $G\der(k)$ then Theorem~\ref{thm:geo} shows that there is a \emph{local system} $\cs{L}$ such that $m^*\cs{L} \iso \cs{L}\boxtimes\cs{L}$ and $\TrFrob{}(\cs{L}) = \chi$.
-In this section, we give methods for geometrizing characters that do not vanish on $G\der(k)$, though the results may not be local systems or conjugation equivariant, a notion that we now define.
-
-\subsection{Conjugation equivariant sheaves}\label{ssec:equivariant}
-
-A Weil local system $\cs{L}$ is said to be \emph{conjugation equivariant} if $a^*\cs{L} \iso p_2^*\cs{L}$, where  $a : G\times G\to G$ is conjugation $a(x,y)=xyx^{-1}$ and $p_2: G\times G\to G$ is projection $p_2(x,y)=y$.
-If $(\cs{L},\mu)$ is a linear character sheaf on $G$, then $\cs{L}$ is conjugation equivariant. Indeed,
-the isomorphism $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ determines an isomorphism $a^*\cs{L} \to p_2^*\cs{L}$ of Weil local systems on $G\times G$ by the following diagram.
+In this section, we give methods for geometrizing characters that do not vanish on $G\der(k)$, though the results may not be local systems or conjugation-equivariant, a notion that we now define.
+
+\subsection{Conjugation equivariant Weil sheaves}\label{ssec:equivariant}
+
+A Weil sheaf $\cs{L}$ is said to be \emph{conjugation-equivariant} if $a^*\cs{L} \iso p_2^*\cs{L}$, where  $a : G\times G\to G$ is conjugation $a(x,y)=xyx^{-1}$ and $p_2: G\times G\to G$ is projection $p_2(x,y)=y$.
+If $(\cs{L},\mu)$ is a linear character sheaf on $G$, then $\cs{L}$ is conjugation-equivariant. Indeed,
+the isomorphism $\mu : m^*\cs{L} \to \cs{L}\boxtimes\cs{L}$ determines an isomorphism $a^*\cs{L} \to p_2^*\cs{L}$ of Weil sheaves on $G\times G$ by the following diagram.
 \[
@@
 
-\subsection{Lusztig's character sheaves}
+\subsection{Lusztig's character sheaves}\label{ssec:LCS}
 
@@
 Consequently, when $\IC(C,\mathcal{L})$ is also a Weil sheaf complex, its trace of Frobenius function $\trFrob{\IC(C,\cs{L})} : G(k)\to \EE$ is a class function, called the characteristic function of $\IC(C,\cs{L})$.
-By \cite{lusztig:86a}*{Cor. 25.7}, Weil character sheaves on $G$ determine a basis for the $\EE$-space of class functions on $G(k)$.
-In particular, any character of any representation of $G(k)$ can be expressed as a ${\bar \QQ}$-linear combination of characteristic functions of Weil character sheaves on $G$.
-We will refer to a formal sum $\sum_{i\in I} a_i \cs{F}_i$ of conjugation-equivariant Weil $\ell$-adic sheaf complexes with ${\bar \QQ}$-coefficients as a rational virtual equivariant Weil sheaf complex on $G$.
-
-When specialized to the case of characters $\chi$ of $G(k)$, Lusztig's theory of character sheaves geometrizes $\chi$ as a rational virtual equivariant Weil sheaf complex on $G$.
-Of course, the resulting objects are generally not local systems.
-
+By \cite{lusztig:86a}*{Cor.
+25.7}, Weil character sheaves on $G$ determine a basis for the vector space of class functions on $G(k)$; in particular, any character of any representation of $G(k)$ can be expressed as a ${\bar \QQ}$-linear combination of characteristic functions of Weil character sheaves on $G$.
+Let us use the notation $\mathsf{D}^b_{c,G}(G;\EE)$ for the category of conjugation-equivariant objects in $\mathsf{D}^b_{c}(G;\EE)$, as defined in \cite{bernstein-lunts:equivariant} for example, and $\mathsf{KD}^b_{c,G}(G;\EE)$ for the Grothendieck group of $\mathsf{D}^b_{c,G}(G;\EE)$; we set $\mathsf{K}_{\bar\QQ}\textsc{D}^b_{c,G}(G;\EE)\ceq \mathsf{KD}^b_{c,G}(G;\EE)\times_{\ZZ} {\bar\QQ}$.
+Thus, for every representation $\rho$ of $G(k)$ there is some $\cs{F}\in \mathsf{K}_{\bar\QQ}\textsc{D}^b_{c,G}(G;\EE)$ such that $\trace\rho = \trFrob{\cs{F}}$.
+This result extends to reductive groups $G$ over $k$ for which the geometric component group for $G$ is cyclic \cite{lusztig:disconnected1}.
+
+When specialized to the case of characters $\chi$ of $G(k)$, Lusztig's theory of character sheaves geometrizes $\chi$ using $\mathsf{K}_{\bar\QQ}\textsc{D}^b_{c,G}(G;\EE)$; of course, the resulting element of this group is generally not a local system.
+%
 For an example when this method can be used to geometrize a character of $G(k)$ which is not trivial on $G\der(k)$, consider $G = \SL_2$ over $\FFF$.
@@
 
-Note that the resulting sheaf is a local system, but is not necessarily conjugation equivariant because
+Note that the resulting sheaf is a local system, but is not necessarily conjugation-equivariant because
 the Lang map is not a homomorphism when $G$ is nonabelian.
@@
 Since $G$ is connected and $\tilde{\chi}$ is a character, Proposition~\ref{prop:chitilde} produces a local system $\cs{L}$ on $G$ which geometrizes $\chi$.
-This $\cs{L}$ is not conjugation equivariant
+This $\cs{L}$ is not conjugation-equivariant
 
@@
 With $\varphi$ as above, note that if $r'$ is any integer greater or equal to the level $r$ of $\varphi$, then the pullback of $\cs{L}_r$ along $G_{r'} \to G_{r}$ is a linear character sheaf on $G_r$.
-Thus, $\cs{L}_{r'}$ is conjugation equivariant in the sense of Section~\ref{ssec:equivariant}.
+Thus, $\cs{L}_{r'}$ is conjugation-equivariant in the sense of Section~\ref{ssec:equivariant}.
 
@@
 %
-Since $\cs{K}_\psi$ is an object in Deligne's category $D^b_c(\Sp(V)\ltimes V^\sharp,\EE)$, the left hand side of this equality must be interpreted accordingly.
+In particular, this geometrization uses $\mathsf{D}^b_{c,\Sp(V)\ltimes V^\sharp}(\Sp(V)\ltimes V^\sharp;\EE)$, as recalled in Section~\ref{ssec:LCS}, to geometrize $\trace(W_\psi)$.
 
@@
 
-For the rest of Section~\ref{sec:types}, $K$ is a $p$-adic field and $R$ is the ring of integers of $K$.
-A Yu type datum consists of the following:
+For the rest of Section~\ref{sec:types}, $R$ is the ring of integers of a $p$-adic field.
+A Yu type datum $(\oK^i,\orho^0,\varphi^i,d)$ consists of the following:
 \begin{enumerate}
@@
 \end{enumerate}
-The representation $\orho^0$ and the quasicharacters $(\varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct the representations $\orho^i$ of $\oK^i$ that form the sequence of types $(\oK^i,\orho_i)$, for $i=1, \ldots, d$.
+The representation $\orho^0$ and the quasicharacters $(\varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct a sequence of types $(\oK^i,\orho_i)$, for $i=1, \ldots, d$.
 %
@@
 
-This brings us back to \cite{Yu:models}*{\S 10.5} as quoted in the Introduction to this paper.
+This brings us back to the point made in \cite{Yu:models}*{\S 10.5} as quoted in the Introduction to this paper.
 
@@
 Hypothesis~\ref{H0} will allow us to use Lusztig's character sheaves to geometrize the character of the representation of $\orho^0$.
-Hypothesis~\ref{H1a} may be used to geometrize each quasicharacter $\varphi_i$ using an element in the Grothendieck group of perverse sheaves on $G_i$, tensored with ${\bar\QQ}$.
-Alternatively, Hypothesis~\ref{H1b} allows us to use Proposition~\ref{prop:quasicharacters} to geometrize each quasicharacter $\varphi_i$ using local systems on $G_i$, or more precisely, using commutative character sheaves on $G_i$;
+Hypothesis~\ref{H1a} may be used to geometrize each quasicharacter $\varphi_i$ using $\mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_i}(G_i;\EE)$.
+Alternatively, Hypothesis~\ref{H1b} allows us to use Proposition~\ref{prop:quasicharacters} to geometrize each quasicharacter $\varphi_i$ using local systems on $G_i$, or more precisely, using commutative character sheaves on $G_i$.
+Using Sections~\ref{ssec:equivariant} and \ref{ssec:LCS} we see that, in both cases, the resulting geometrization may be interpreted as an element in $\mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_i}(G_i;\EE)$.
+Note that when Hypothesis~\ref{H1b} applies, it provides a considerably simpler geometrization than when Hypothesis~\ref{H1a} applies.
+
 We remark that if Lusztig's theory of character sheaves can be generalized to all disconnected reductive algebraic groups, then Hypothesis~\ref{H0} can be removed and Hypothesis~\ref{H1a} can be replaced with the hypothesis that each $G_i$ is reductive.
-Note that when Hypothesis~\ref{H1b} applies, it provides a considerably simpler geometrization than when Hypothesis~\ref{H1a} applies.
 
 \begin{theorem}\label{thm:geotypes}
-Let $(\oK^i, \orho^0, \varphi^i)$ be a Yu type datum that satisfies Hypotheses~\ref{H0} and \ref{H1}, and let $\orho_i$ be the representation of $\oK^i$ constructed from it in Section~\ref{ssec:review}.
-Then for each $i=0,\dots, d$ there is an element $\cs{F}_i \in \mathcal{K}_{\bar\QQ} D_{G^i}(X)$ such that
+Let $(\oK^i, \orho^0, \varphi^i,d)$ be a Yu type datum that satisfies Hypotheses~\ref{H0} and \ref{H1}, and let $\orho_i$ be the representation of $\oK^i$ constructed from it in Section~\ref{ssec:review}.
+Then for each $i=0,\dots, d$ there is an element $\cs{F}_i \in \mathcal{K}_{\bar\QQ} D_{G^i}(G^i)$ such that
 \[
@@
 %
-Let $A^0$ be the conjugation equivariant Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+Let $A^0$ be the conjugation-equivariant Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
 Then 
@@
 Consider the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ and the Heisenberg-Weil representation $W_{i+1}$ appearing in Section~\ref{ssec:review}.
-Let $\cs{K}^{i+1}$ be the equivariant Weil sheaf on the Jacobi group, recalled in Section~\ref{ssec:Jacobi}, such that
+Let $\cs{K}^{i+1}$ be the conjugation equivariant Weil sheaf on the Jacobi group, recalled in Section~\ref{ssec:Jacobi}, such that
 \[
@@
 
-We now define rational virtual conjugation equivariant Weil sheaves $\cs{A}^i_r$ on $G_r^i \ceq \Gr^{R}_r(\underline{G}^{i})$, for $i=0,\ldots ,d$, recursively, following the construction of the representations $\orho_i$, as reviewed in Section~\ref{ssec:review}.
+We now define $\cs{A}^i_r  \in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G^i_r}$ for $i=0,\ldots ,d$ recursively, following the construction of the representations $\orho^i$, as reviewed in Section~\ref{ssec:review}.
 First, set $\cs{A}_r^0 = A_r^0$ and note that \eqref{eqn:tracerho} commutes with $\trace(\orho^0)_r$ replaced by $\trFrob{\cs{A}_r^0}$.
 Using Hypothesis~\ref{H1}, let $\cs{L}_i$ be the geometrization of the quasicharacter $\varphi_i \ceq \varphi^i_{r_i}$ appearing in \ref{M2}.
-If \ref{H1a} applies, then $\cs{L}_i$ is a rational virtual character sheaf on $G_i \ceq G^i_{r_i}$, using \cite{lusztig:disconnected1};
-if \ref{H1b} applies, then $\cs{L}_i$ is the commutative character sheaf on $G_i \ceq G^i_{r_i}$ given by Proposition~\ref{prop:quasicharacters} which, by Section~\ref{ssec:equivariant}, is conjugation equivariant.
-In either case, $\cs{L}_i$ is a rational virtual conjugation equivariant Weil sheaf complex and
+If \ref{H1a} applies, then $\cs{L}_i \in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_i}(G_i;\EE)$, using \cite{lusztig:disconnected1};
+if \ref{H1b} applies, then $\cs{L}_i\in \CCS(G_i)$, using Proposition~\ref{prop:quasicharacters}.
+In either case, $\cs{L}_i\in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_i}(G_i;\EE)$ and
 \[
@@
 \begin{tikzcd}
-G^i(\Fq) \arrow{rr}{\trace(\orho_i)} \arrow{rd} && \EE\\
+G^i(\Fq) \arrow{rr}{\trace(\orho^i)} \arrow{rd} && \EE\\
 & G_r^i(\Fq) \arrow{ru}[swap]{\trFrob{\cs{A}_r^i}} & 
@@
 By \cite{bertapelle-gonzales:Greenberg}*{Prop 14.2}, the sequences are exact.
-Consider the rational virtual conjugation equivariant Weil sheaf 
-\[
-\cs{B}_r^{i+1} \ceq \cs{K}_r^{i+1} \otimes (p_r^{i})^*(\cs{A}_r^{i}\otimes \cs{L}_r^{i})
-\]
-on $G_r^{i}\ltimes J_r^{i+1}$.
+Consider $\cs{B}_r^{i+1}\in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_r^{i}\ltimes J_r^{i+1}}(G_r^{i}\ltimes J_r^{i+1};\EE)$ defined by
+\[
+\cs{B}_r^{i+1} \ceq \cs{K}_r^{i+1} \otimes (p_r^{i})^*(\cs{A}_r^{i}\otimes \cs{L}_r^{i}).
+\]
 Comparing with \eqref{eq:tensor}, we see that $\trFrob{\cs{B}_r^{i+1}}$ is precisely the function obtained by factoring the character of $\orho^{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(R) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R_r)$ using the canonical identification $(G_r^{i}\times_{G_r} J_r^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R_r)$.
@@
 \]
-Then $\cs{C}_r^{i+1}$ is an equivariant Weil sheaf and
+Then $\cs{C}_r^{i+1}\in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_r^{i+1}}(G_r^{i+1};\EE)$ and
 \begin{eqnarray*}
@@
 on $G_r^{i+1}(\Fq)$ with $n$ equal to the product of $\# (G_r^{i}\times_{G_r} J_r^{i+1})(\Fq)$ and $\dim \orho^{i+1}$.
-Let $\cs{A}_r^{i+1}$ be the rational virtual conjugation equivariant Weil sheaf on $G_r^i$ given by $\cs{A}_r^{i+1} = \frac{1}{n} \cs{C}_r^{i+1}$. 
+Let $\cs{A}_r^{i+1}$ be the element of $\mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_r^{i+1}}(G_r^{i+1};\EE)$ given by $\cs{A}_r^{i+1} = \frac{1}{n} \cs{C}_r^{i+1}$. 
 %
@@
 \begin{tikzcd}
-G^{i+1}(\Fq) \arrow{rr}{\trace(\orho_{i+1})} \arrow{rd} && \EE\\
+G^{i+1}(\Fq) \arrow{rr}{\trace(\orho^{i+1})} \arrow{rd} && \EE\\
 & G_r^{i+1}(\Fq)\arrow{ru}[swap]{{\trFrob{\cs{A}_r^{i+1}}} } & 
@@
 Now set $\cs{F}^i_r = \cs{A}_r^{i} \otimes \cs{L}_r^i$, for $i=0, \ldots ,d$.
-Then $\cs{F}^i_r$ is a rational virtual conjugation equivariant Weil sheaf on $G^i_r = \Gr^{R}_r(\underline{G}^i)$ such that
+Then $\cs{F}^i_r \in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_r^{i}}(G_r^{i};\EE)$ such that
 \[
@@
 commutes.
-Let $\cs{F}^i$ be the rational virtual equivariant Weil sheaf on the group scheme $G^i= \Gr_{R}(\underline{G}^i)$ obtained by pulling back $\cs{F}_r^i$ along $G^i \to G^i_r$.
+Define $\cs{F}^i\in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G^{i}}(G^{i};\EE)$ by pulling back $\cs{F}_r^i$ along $G^i \to G^i_r$.
 Then 
@@
 
+\bib{Deligne:Weil}{article}{
+   author={Deligne, Pierre},
+   title={La conjecture de Weil. II},
+   %language={French},
+   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
+   number={52},
+   date={1980},
+   pages={137--252},
+   %issn={0073-8301},
+   %review={\MR{601520}},
+}
+
 \bib{demazure:SGA3-VIA}{inproceedings}{
@@
        pages={825\ndash 846},
+}
+
+\bib{KR:l'adic}{book}{
+   author={Kiehl, Reinhardt},
+   author={Weissauer, Rainer},
+   title={Weil conjectures, perverse sheaves and $l$'adic Fourier transform},
+   series={Ergebnisse der Mathematik und ihrer Grenzgebiete. 3. Folge. A
+   Series of Modern Surveys in Mathematics [Results in Mathematics and
+   Related Areas. 3rd Series. A Series of Modern Surveys in Mathematics]},
+   volume={42},
+   publisher={Springer-Verlag, Berlin},
+   date={2001},
+   pages={xii+375},
+%   isbn={3-540-41457-6},
+%   review={\MR{1855066}},
+%   doi={10.1007/978-3-662-04576-3},
 }

### 2017-08-30 Geometric types.tex
Cleaning up while working with David

@@
 %
-Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(R) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on the rational virtual complex $\cs{F}^i$, we show in Theorem~\ref{thm:geotypes} that
+Writing $\trFrob{\cs{F}^i}$ for the function on $G^i(k) = \underline{G}^i(R) = \,^\circ K^i$ obtained by evaluating the trace of the action of Frobenius on $\cs{F}^i$, we show in Theorem~\ref{thm:geotypes} that
 \begin{equation}\label{eqn:intro1}
@@
 If $G$ is a smooth group scheme and $(\cs{L},\mu) \in \CS(G)$, then
-the restriction of $\cs{L}$ to $G\der$ is trivial if and only if $(\cs{L},\mu) \cong q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, for some $(\cs{L}\ab,\mu\ab) \in \CS(G\ab)$.
+the restriction of $(\cs{L},\mu)$ to $G\der$ is trivial if and only if $(\cs{L},\mu) \cong q^*(\cs{L}\ab,\mu\ab)$ in $\CS(G)$, for some $(\cs{L}\ab,\mu\ab) \in \CS(G\ab)$.
 \end{corollary}
@@
  in $\CS(G\der)$.
-Since $q\circ j\der = 1$, it follows that $\cs{L}\vert_{G\der} \iso (\EE)_{G\der}$.
+Since $q\circ j\der = 1$, it follows that the restriction of $(\cs{L},\mu)$ to $G\der$ is trivial.
 \end{proof}
@@
 Thus, for every representation $\rho$ of $G(k)$ there is some $\cs{F}\in \mathsf{K}_{\bar\QQ}\textsc{D}^b_{c,G}(G;\EE)$ such that $\trace\rho = \trFrob{\cs{F}}$.
-This result extends to reductive groups $G$ over $k$ for which the geometric component group for $G$ is cyclic \cite{lusztig:disconnected1}.
+This result is extended in the papers beginning with \cite{lusztig:disconnected1} to reductive groups $G$ over $k$ for which the geometric component group for $G$ is cyclic .
 
@@
 Let $(\oK^i, \orho^0, \varphi^i,d)$ be a Yu type datum that satisfies Hypotheses~\ref{H0} and \ref{H1}, and let $\orho_i$ be the representation of $\oK^i$ constructed from it in Section~\ref{ssec:review}.
-Then for each $i=0,\dots, d$ there is an element $\cs{F}_i \in \mathcal{K}_{\bar\QQ} D_{G^i}(G^i)$ such that
+Then for each $i=0,\dots, d$ there is an element $\cs{F}_i \in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G^i}(G^i;\EE)$ such that
 \[
@@
 
-By \cite{lusztig:disconnected1}, there is a rational virtual Weil character sheaf $A = ({\bar A},\phi)$ on $(\underline{G}^0)_\Fq^\reductive$ such that 
+By \cite{lusztig:disconnected1}, there is $A \in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,(\underline{G}^0)_\Fq\red}((\underline{G}^0)_\Fq\red;\EE)$ such that 
 %${\bar A}$ is a rational virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
@@
 %
-Let $A^0$ be the conjugation-equivariant Weil sheaf on $(\underline{G}^0)_\Fq$ obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+Let $A^0\in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,(\underline{G}^0)_\Fq}((\underline{G}^0)_\Fq;\EE)$ be obtained by pullback along the quotient $(\underline{G}^0)_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
 Then 
@@
 
+\iffalse
 \bib{KR:l'adic}{book}{
@@
 }
+\fi
 
@@
 	Author = {George Lusztig},
-	Date-Added = {2017-06-28 19:26:19 +0000},
-	Date-Modified = {2017-06-28 19:28:23 +0000},
+%	Date-Added = {2017-06-28 19:26:19 +0000},
+%	Date-Modified = {2017-06-28 19:28:23 +0000},
 	Journal = {Advances in Math.},
-	Keywords = {qcsheaves},
+%	Keywords = {qcsheaves},
 	Number = {2},

### 2017-08-30 CJM/second letter to CJM.tex
Writing letter to editor

@@
 \usepackage{amssymb}
-\usepackage{amsrefs}
+%\usepackage{amsrefs}
 % Fonts
-\usepackage{mathrsfs}
+%\usepackage{mathrsfs}
 % Enumitem
@@
 \usepackage{hyperref}
-\hypersetup{
-  colorlinks   = true, %Colours links instead of ugly boxes
-  urlcolor     = blue, %Colour for external hyperlinks
-  linkcolor    = blue, %Colour of internal links
-  citecolor   = green %Colour of citations
-}
+%\hypersetup{
+%  colorlinks   = true, %Colours links instead of ugly boxes
+%  urlcolor     = blue, %Colour for external hyperlinks
+%  linkcolor    = blue, %Colour of internal links
+%  citecolor   = green %Colour of citations
+%}
 \usepackage[margin=3.5cm]{geometry}
@@
 
-\usepackage{tikz}
-\usetikzlibrary{shapes,arrows,calc,matrix}
-\usepackage{tikz-cd}
-\usepackage{todonotes}
+%\usepackage{tikz}
+%\usetikzlibrary{shapes,arrows,calc,matrix}
+%\usepackage{tikz-cd}
+%\usepackage{todonotes}
 
@@
 \usepackage{amsmath}
-\usepackage{lipsum}
-\usepackage{setspace}
+%\usepackage{lipsum}
+%\usepackage{setspace}
 
@@
 \newcommand{\Fq}{k}
+\newcommand{\FFF}{\mathbb{F}_3}
 \newcommand{\Fqm}{k_m}
@@
 
-\setcounter{equation}{-1}
+%\setcounter{equation}{-1}
 
@@
 
+In addition to making changes prompted by the referee's comments, we have corrected an error pointed out to us in an e-mail from Will Savin.
+Namely, we assumed incorrectly at the beginning of section 3 that any character on $G(k)$ would vanish on $G\der(k)$.
+Every character vanishes on $G(k)\der$, but in general these two groups are not the same (for example, if $G = \SL_2$ over $\FFF$ or $\PGL_2$ over a finite field of odd characteristic).
+We adjusted the exposition in the introduction and beginning of section 3 to correct this mistake, and added hypotheses in the statements of Corollary 3.8, Thereom 3.12 and Theorem 5.2.
+We also added Section 4, where we describe some approaches for geometrizing characters that do not vanish on $G\der(k)$.
+
+We now describe the changes made to address the referee's remarks.
+
+\begin{enumerate}[label=(\arabic*)]
+\item We have added Section 3.2.3 on Rigidification to address this problem, and restructured the discussion around what was Lemma 3.3.
+\item The new section also addresses this concern.
+Note that the reviewer is correct that $n^*_2(\mu)$ agrees with $p^*_2(\mu)$, though we did not add this fact explicitly to the paper, because it was not needed in the discussion of rigidification.
+\end{enumerate}
+
+\begin{enumerate}[label=(\roman*)]
+\item We have fixed the typo.
+\item The reviewer is correct that we do not need smoothness.
+\item We have changed all the $i$s to $j$s.
+\item We have changed $\cs{L}$ to $(\cs{L}, \mu)$ as suggested.
+\item We have added the adjective ``linear'' at various points throughout the paper, including this one.
+\item We have added a note as suggested.
+\item We couldn't find a way to clarify this without adding a lot of extra material, which we thought would actually hurt the clarify of the exposition.  We therefore left these statements unchanged.
+\end{enumerate}
+
 \medskip
@@
 
-\bigskip
-
-\begin{enumerate}
-\item[(1)]
-\end{enumerate}
-
-\begin{enumerate}
-\item[(i)] Thank you for noticing this.
-We referred to the geometric type $\cs{F}^d$ constructed in the paper as a virtual sheaf complex, but this is misleading, since that would reasonably be interpreted as an element in the Grothendieck group of sheaf complexes, while the geometric type is an element of the group obtained by tensoring this Grothendieck group with  $\QQ$.
-To clarify this, we have used the term {\it rational virtual} for formal linear combinations of sheaf complexes, with rational coefficients.
-
-\end{enumerate}
-
 \end{document}

### 2017-08-30 Geometric types.tex

@@
 25.7}, Weil character sheaves on $G$ determine a basis for the vector space of class functions on $G(k)$; in particular, any character of any representation of $G(k)$ can be expressed as a ${\bar \QQ}$-linear combination of characteristic functions of Weil character sheaves on $G$.
-Let us use the notation $\mathsf{D}^b_{c,G}(G;\EE)$ for the category of conjugation-equivariant objects in $\mathsf{D}^b_{c}(G;\EE)$, as defined in \cite{bernstein-lunts:equivariant} for example, and $\mathsf{KD}^b_{c,G}(G;\EE)$ for the Grothendieck group of $\mathsf{D}^b_{c,G}(G;\EE)$; we set $\mathsf{K}_{\bar\QQ}\textsc{D}^b_{c,G}(G;\EE)\ceq \mathsf{KD}^b_{c,G}(G;\EE)\times_{\ZZ} {\bar\QQ}$.
-Thus, for every representation $\rho$ of $G(k)$ there is some $\cs{F}\in \mathsf{K}_{\bar\QQ}\textsc{D}^b_{c,G}(G;\EE)$ such that $\trace\rho = \trFrob{\cs{F}}$.
-This result is extended in the papers beginning with \cite{lusztig:disconnected1} to reductive groups $G$ over $k$ for which the geometric component group for $G$ is cyclic .
-
-When specialized to the case of characters $\chi$ of $G(k)$, Lusztig's theory of character sheaves geometrizes $\chi$ using $\mathsf{K}_{\bar\QQ}\textsc{D}^b_{c,G}(G;\EE)$; of course, the resulting element of this group is generally not a local system.
+Let us use the notation $\mathsf{D}^b_{c,G}(G;\EE)$ for the category of conjugation-equivariant objects in $\mathsf{D}^b_{c}(G;\EE)$, as defined in \cite{bernstein-lunts:equivariant} for example, and $\mathsf{KD}^b_{c,G}(G;\EE)$ for the Grothendieck group of $\mathsf{D}^b_{c,G}(G;\EE)$; we set $\mathsf{K}_{\bar\QQ}\textsc{D}^b_{c,G}(G;\EE)\ceq \mathsf{KD}^b_{c,G}(G;\EE)\otimes_{\ZZ} {\bar\QQ}$.
+Thus, Lusztig's result shows that for every representation $\rho$ of $G(k)$ there is some $\cs{F}\in \mathsf{K}_{\bar\QQ}\textsc{D}^b_{c,G}(G;\EE)$ such that $\trace\rho = \trFrob{\cs{F}}$.
+This result is extended in the papers beginning with \cite{lusztig:disconnected1} to reductive groups $G$ over $k$ for which the geometric component group for $G$ is cyclic.
+
+When specialized to the case of characters $\chi$ of $G(k)$, Lusztig's theory of character sheaves geometrizes $\chi$ using $\mathsf{K}_{\bar\QQ}\textsc{D}^b_{c,G}(G;\EE)$; of course, the resulting geometrization is generally not a local system.
 %

### 2017-08-30 CJM/second letter to CJM.tex
Edits to the second letter to CJM

@@
 \begin{document}
-{\hfill {2017 May 11} \\ 
+{\hfill {2017 August 30} \\ 
 %\rightline{Calgary}
@@
 
-In addition to making changes prompted by the referee's comments, we have corrected an error pointed out to us in an e-mail from Will Savin.
-Namely, we assumed incorrectly at the beginning of section 3 that any character on $G(k)$ would vanish on $G\der(k)$.
-Every character vanishes on $G(k)\der$, but in general these two groups are not the same (for example, if $G = \SL_2$ over $\FFF$ or $\PGL_2$ over a finite field of odd characteristic).
-We adjusted the exposition in the introduction and beginning of section 3 to correct this mistake, and added hypotheses in the statements of Corollary 3.8, Thereom 3.12 and Theorem 5.2.
-We also added Section 4, where we describe some approaches for geometrizing characters that do not vanish on $G\der(k)$.
-
-We now describe the changes made to address the referee's remarks.
+Our thanks again to the referee for corrections and very helpful remarks, to which we now respond.
 
@@
 \item We have added Section 3.2.3 on Rigidification to address this problem, and restructured the discussion around what was Lemma 3.3.
-\item The new section also addresses this concern.
+\item Section 3.2.3 also addresses this concern.
 Note that the reviewer is correct that $n^*_2(\mu)$ agrees with $p^*_2(\mu)$, though we did not add this fact explicitly to the paper, because it was not needed in the discussion of rigidification.
@@
 
+In addition to making changes prompted by the referee's comments, we have corrected an error pointed out to us in an e-mail from Will Savin.
+Namely, we assumed incorrectly at the beginning of Section 3 that any character on $G(k)$ would vanish on $G\der(k)$.
+Every character vanishes on $G(k)\der$, but in general these two groups are not the same (for example, if $G = \SL_2$ over $\FFF$ or $\PGL_2$ over a finite field of odd characteristic).
+We adjusted the exposition in the introduction and beginning of Section 3 to correct this mistake, and added hypotheses in the statements of Corollary 3.8, Thereom 3.12 and Theorem 5.2.
+We also added Section 4, where we describe some approaches for geometrizing characters that do not vanish on $G\der(k)$.
+
 \medskip
@@
 Best  regards,
-\bigskip
+\vskip1.5cm
 

### 2017-08-31 CJM/second letter to CJM.tex
Added Prop to second letter to CJM

@@
 Every character vanishes on $G(k)\der$, but in general these two groups are not the same (for example, if $G = \SL_2$ over $\FFF$ or $\PGL_2$ over a finite field of odd characteristic).
-We adjusted the exposition in the introduction and beginning of Section 3 to correct this mistake, and added hypotheses in the statements of Corollary 3.8, Thereom 3.12 and Theorem 5.2.
+We adjusted the exposition in the introduction and beginning of Section 3 to correct this mistake, and added hypotheses in the statements of Corollary 3.8, Thereom 3.12, Proposition 5.1 and Theorem 5.2.
 We also added Section 4, where we describe some approaches for geometrizing characters that do not vanish on $G\der(k)$.

### 2017-08-31 CJM/Geometric types to CJM v3.tex
Record keeping

--- 2017-08-30 Geometric types.tex
@@
 \begin{abstract}
-We show that the types for supercuspidal representations of tamely ramified $p$-adic groups that appear in Jiu-Kang Yu's work are geometrizable, subject to a mild hypothesis.
+We show that the types for supercuspidal representations of tamely ramified $p$-adic groups that appear in Jiu-Kang Yu's work are geometrizable, subject to a hypothesis.
 To do this we must find the function-sheaf dictionary for one-dimen\-sion\-al characters of arbitrary smooth group schemes over finite fields.  

### 2017-08-31 CJM/second letter to CJM.tex
Record keeping

@@
 
-\noindent{Dear Isolde Prince,}
+\noindent{Dear Professors Goren and Addario-Berry,}
 \medskip
@@
 \item We have added a note as suggested.
-\item We couldn't find a way to clarify this without adding a lot of extra material, which we thought would actually hurt the clarify of the exposition.  We therefore left these statements unchanged.
+\item We couldn't find a way to clarify this without adding a lot of extra material, which we thought would actually detract from the exposition.  We therefore left these statements unchanged.
 \end{enumerate}

### 2019-07-02 Geometric types.tex
Add missing period

@@
 Since $G$ is connected and $\tilde{\chi}$ is a character, Proposition~\ref{prop:chitilde} produces a local system $\cs{L}$ on $G$ which geometrizes $\chi$.
-This $\cs{L}$ is not conjugation-equivariant
+This $\cs{L}$ is not conjugation-equivariant.
 

### 2019-07-02 Geometric types.tex
Updates to the bibliography

@@
 Since $G$ is connected and $\tilde{\chi}$ is a character, Proposition~\ref{prop:chitilde} produces a local system $\cs{L}$ on $G$ which geometrizes $\chi$.
-This $\cs{L}$ is not conjugation-equivariant.
+This $\cs{L}$ is not conjugation-equivariant
 
@@
 
-\bib{bertapelle-gonzales:Greenberg}{unpublished}{
+\bib{bertapelle-gonzales:Greenberg}{article}{
    author={Bertapelle, Alessandra},
-      author={{Gonz\'ales-Avil\'es}, Cristian~D.},
-       title={{The Greenberg functor revisited}},
-        date={2016},
-         url={http://arxiv.org/abs/1311.0051},
-        note={\href{http://arxiv.org/abs/1311.0051}{arXiv:1311.0051
-  [math.NT]}},
+   author={Gonz\'{a}lez-Avil\'{e}s, Cristian D.},
+   title={The Greenberg functor revisited},
+   journal={Eur. J. Math.},
+   volume={4},
+   date={2018},
+   number={4},
+   pages={1340--1389},
+   issn={2199-675X},
+%   review={\MR{3866700}},
+ %  doi={10.1007/s40879-017-0210-0},
 }
@@
    author={Roe, David},
-title={From the function-sheaf dictionary to quasicharacters of $p$-adic tori},
-journal = {Journal of the Institute of Mathematics of Jussieu},
-volume = {FirstView},
-number = {6},
-%month = {6},
-year = {2016},
-issn = {1475-3030},
-pages = {1--37},
-%numpages = {37},
-doi = {10.1017/S1474748015000286},
-URL = {http://journals.cambridge.org/article_S1474748015000286},
+   title={From the function-sheaf dictionary to quasicharacters of $p$-adic
+   tori},
+   journal={J. Inst. Math. Jussieu},
+   volume={17},
+   date={2018},
+   number={1},
+   pages={1--37},
+   issn={1474-7480},
+%   review={\MR{3742553}},
+%   doi={10.1017/S1474748015000286},
 }

### 2019-07-02 Geometric types.tex
Working on abstract and intro

--- 2019-07-02 Geometric types.tex
@@
 \begin{abstract}
-We show that the types for supercuspidal representations of tamely ramified $p$-adic groups that appear in Jiu-Kang Yu's work are geometrizable, subject to a hypothesis.
+We show that some types for supercuspidal representations of tamely ramified $p$-adic groups that appear in Jiu-Kang Yu's work are geometrizable.
 To do this we must find the function-sheaf dictionary for one-dimen\-sion\-al characters of arbitrary smooth group schemes over finite fields.  
@@
 In this paper we give a modification of the category of character sheaves that remedies this defect, and is also extensible to non-commutative groups.  
-We then use these \emph{commutative character sheaves} to geometrize the linear characters that appear in the types introduced by Jiu-Kang Yu.
+We then use these \emph{commutative character sheaves} to geometrize the linear characters that appear in the types introduced by Jiu-Kang Yu, assuming that the character vanishes on a certain derived subgroup.
 We combine these sheaves with Lusztig's character sheaves on reductive algebraic groups over finite fields and the geometrization of the Weil representation found by Gurevich and Hadani, to define \emph{geometric types} for supercuspidal representations of tamely ramified $p$-adic groups.
@@
 
-As proved by Ju-Lee Kim in \cite{kim:07a}, all irreducible supercuspidal representations of tamely ramified $p$-adic groups can be built from ``data'' introduced by Jiu-Kang Yu in \cite{yu:01a}*{\S 15}.
+As proved by Ju-Lee Kim in \cite{kim:07a}, all irreducible supercuspidal representations of tamely ramified $p$-adic groups for sufficiently large $p$ can be built from ``data'' introduced by Jiu-Kang Yu in \cite{yu:01a}*{\S 15}.
 While the type, in the sense of Bushnell \& Kutzko \cite{bushnell-kutzko:98a}, of a supercuspidal representation built from Yu data can be constructed directly from the datum, it is convenient to consider an intermediate object, introduced in \cite{yu:01a}*{Remark 15.4}, which we call a \emph{Yu type datum}.

### 2019-07-02 Geometric types.tex
More fixes to intro

@@
 is an isomorphism.  
-Since $G\ab(k)^*$ surjects onto $G(k)^*$, it follows that for each character $\chi \in G(k)^*$ trivial on $G\der(k)$ there is a commutative
+Since $G\ab(k)^*$ maps onto $G(k)^*$ with cokernel $G\der(k)^*$, it follows that for each character $\chi \in G(k)^*$ trivial on $G\der(k)$ there is a commutative
 character sheaf $\cs{L}$ on $G$ with $\TrFrob{G}(\cs{L}) = \chi$. Moreover, we find that pullback along the quotient $q : G \to G\ab$

### 2019-07-02 Geometric types.tex
Introduction and Henselian

@@
 We then use these \emph{commutative character sheaves} to geometrize the linear characters that appear in the types introduced by Jiu-Kang Yu, assuming that the character vanishes on a certain derived subgroup.
-We combine these sheaves with Lusztig's character sheaves on reductive algebraic groups over finite fields and the geometrization of the Weil representation found by Gurevich and Hadani, to define \emph{geometric types} for supercuspidal representations of tamely ramified $p$-adic groups.
+To define \emph{geometric types} we combine commutative character sheaves with Gurevich and Hadani's geometrization of the Weil representation and Lusztig's character sheaves.
 \end{abstract}
@@
 {\it Therefore, up to some linear characters, all the ingredient representations 
- are on groups of the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over [a henselian discrete valuation ring with finite residue field $\kappa$] $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
+ are on groups of the form $\underline{H}(\mathcal{O})$, where $\underline{H}$ is a smooth group scheme over [a Henselian discrete valuation ring with finite residue field $\kappa$] $\mathcal{O}$, and the representations are inflated from $\underline{H}(\kappa)$.
 These results suggest that algebraic geometry and group schemes should play an
@@
 
-\subsection{Quasicharacters of smooth group schemes over certain henselian traits}\label{ssec:quasicharacters}
+\subsection{Quasicharacters of smooth group schemes over certain Henselian traits}\label{ssec:quasicharacters}
 

### 2020-05-01 Geometric types.tex
Add referee comments

@@
 \author{David Roe}
-\address{Department of Mathematics, University of Pittsburgh, 301 Thackeray Hall, Pittsburgh, PA , United States, 15260.}
-\email{roed.math@gmail.com}
+\address{Department of Mathematics, Massachusetts Institute of Technology, 77 Massachusetts Ave, Cambridge, MA, United States, 02139.}
+\email{roed@mit.edu}
 
@@
 We show that some types for supercuspidal representations of tamely ramified $p$-adic groups that appear in Jiu-Kang Yu's work are geometrizable.
-To do this we must find the function-sheaf dictionary for one-dimen\-sion\-al characters of arbitrary smooth group schemes over finite fields.  
+To do so, we define a function-sheaf dictionary for one-dimen\-sion\-al characters of arbitrary smooth group schemes over finite fields.  
 In previous work we considered the case of commutative smooth group schemes and found that the standard definition of character sheaves produced a dictionary with a nontrivial kernel.  
@@
 We then use these \emph{commutative character sheaves} to geometrize the linear characters that appear in the types introduced by Jiu-Kang Yu, assuming that the character vanishes on a certain derived subgroup.
-To define \emph{geometric types} we combine commutative character sheaves with Gurevich and Hadani's geometrization of the Weil representation and Lusztig's character sheaves.
+To define \emph{geometric types}, we combine commutative character sheaves with Gurevich and Hadani's geometrization of the Weil representation and Lusztig's character sheaves.
 \end{abstract}
+\todo{Since Yu's article ``Construction of tame supercuspidal representation'' [20] is a key ingredient, I would like to inform the authors that, as recently noticed by Loren Spice, Proposition 14.1 and Theorem 14.2 in [20] are not always true (they rely on a misprinted statement in a reference).
+An alternative proof of Yu's main results which avoids these steps was provided by Jessica Fintzen in ``On the construction of tame supercuspidal representations'', arXiv:1908.09819.
+I think that it should be mentioned, even if does not affect the results of manuscript.}
 
@@
 
-As proved by Ju-Lee Kim in \cite{kim:07a}, all irreducible supercuspidal representations of tamely ramified $p$-adic groups for sufficiently large $p$ can be built from ``data'' introduced by Jiu-Kang Yu in \cite{yu:01a}*{\S 15}.
+As proved by Ju-Lee Kim in \cite{kim:07a} and Jessica Fintzen in \cite{fintzen:18a}, \todo{check this fix} all irreducible supercuspidal representations of a tamely ramified $p$-adic group $G$ can be built from ``data'' introduced by Jiu-Kang Yu in \cite{yu:01a}*{\S 15} as long as $p$ does not divide the order of the Weyl group of $G$.
 While the type, in the sense of Bushnell \& Kutzko \cite{bushnell-kutzko:98a}, of a supercuspidal representation built from Yu data can be constructed directly from the datum, it is convenient to consider an intermediate object, introduced in \cite{yu:01a}*{Remark 15.4}, which we call a \emph{Yu type datum}.
@@
 In this paper we follow the suggestion above by showing that certain Yu type data are geometrizable, in the following sense.
-A Yu type datum determines a sequence of representations $\orho_i$ of compact $p$-adic groups $\oK^i$, for $i=0, \ldots, d$, such that $(\oK^d, \rho_d)$ is a type for a supercuspidal representation of a $p$-adic group.
+A Yu type datum determines a sequence of representations $\orho_i$ of compact $p$-adic groups $\oK^i$, for $i=0, \ldots, d$, such that $(\oK^d, \orho_d)$ is a type for a supercuspidal representation of a $p$-adic group.
 Let $R$ be the ring of integers of a local field with finite residue field $k$.
 The main result of \cite{Yu:models} shows how to find, for each $i=0, \ldots, d$, a smooth group scheme $\underline{G}^i$ over the ring $R$ with $\underline{G}^i(R)=\,^\circ K^i $.
-Under certain assumptions on the Yu type datum, we show how each representation $\orho_i$ can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$, where $\cs{F}^i$ is a formal ${\bar\QQ}$-linear conbination of conjugation-equivariant sheaf complexes on the Greenberg transform $G^i$ of $\underline{G}^i$.
+Under certain assumptions on the Yu type datum, we show how each representation $\orho_i$ can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$, where $\cs{F}^i$ is a formal ${\bar\QQ}$-linear \todo{${\bar\QQ}$ is not defined} combination of conjugation-equivariant sheaf complexes on the Greenberg transform $G^i$ of $\underline{G}^i$.
 %
@@
 Next, we broaden our scope further to encompass smooth group schemes $G$ over $\Fq$ that are not necessarily commutative.
-We assume $G$ is smooth, but not that it is connected, reductive or commutative. 
+We assume $G$ is smooth, but not that it is connected, reductive or commutative; we write $G\ab := G/G\der$ for the abelianization.
 The category $\CS(G)$ has a straightforward generalization to this case.
@@
 Let $\gcs{L}$ be the geometric part of an object in $\CCS(G)$; see Section~\ref{sec:defs}.
-Let $T$ be a maximal torus in $\bG$ and let $\gcs{L}_T$ be the restriction of $\gcs{L}$ to $T$.
+Let $T$ be a maximal torus in the base change $\bG$ of $G$ to an algebraic closure $\bar{k}$ of $k$, and let $\gcs{L}_T$ be the restriction of $\gcs{L}$ to $T$.
 Then the perverse sheaf $\gcs{L}[\dim G]$ appears in the semisimple complex $\operatorname{ind}_{B,T}^{\bG}(\gcs{L}_T)$ produced by parabolic induction.
@@
 
-In this paper we use a common formalism for Weil sheaves, writing $\cs{L}$ for the pair $(\gcs{L},\phi)$, where $\gcs{L}$ is an $\ell$-adic sheaf on $\bG \ceq G\otimes_{\Fq} \bFq$ and where $\phi : \Frob{}^*\gcs{L} \to \gcs{L}$ is an isomorphism of $\ell$-adic sheaves.
+In this paper we use a common formalism for Weil sheaves, writing $\cs{L}$ for the pair $(\gcs{L},\phi)$, where $\gcs{L}$ is an $\ell$-adic sheaf on $\bG \ceq G\otimes_{\Fq} \bFq$ \todo{the notation $\bFq$ isn't defined} and where $\phi : \Frob{}^*\gcs{L} \to \gcs{L}$ is an isomorphism of $\ell$-adic sheaves.
 We also follow convention by referring to $\cs{L}$  as a Weil sheaf on $G$, as in \cite{Deligne:Weil}*{D\'efinition 1.1.10}.
@@
 We now consider the case of a smooth group scheme without the commutativity assumption.  Our approach
-is to relate linear character sheaves on $G$ to character sheaves on its abelianization $G\ab = G / G\der$, where $G\der$ is defined by \cite{demazure:SGA3-VIB}*{D\'efinition 7.2.2} and the quotient is $G\ab$ is an instance of  \cite{demazure:SGA3-VIA}*{Section 7.2.2}.
+is to relate linear character sheaves on $G$ to character sheaves on its abelianization $G\ab = G / G\der$, where $G\der$ is defined by \cite{demazure:SGA3-VIB}*{D\'efinition 7.2.2} and the quotient $G\ab$ is an instance of  \cite{demazure:SGA3-VIA}*{Section 7.2.2}.
 While every character $\chi \in G(k)^*$ vanishes on $G(k)\der$, it may not vanish on $G\der(k)$.  For example,
@@
 Let $\CS\ab(G)$ denote the category of triples $(\cs{L},\mu,\beta)$ where $(\cs{L},\mu) \in \CS(G)$ and
-$\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism of Weil local systems on $G\der$.
+$\beta : \cs{L}\vert_{G\der} \to (\EE)_{G\der}$ is an isomorphism of Weil local systems on $G\der$ with the constant sheaf on $G\der$.
 A morphism $(\cs{L},\mu,\beta)\to (\cs{L}',\mu',\beta')$ is a morphism $\alpha : (\cs{L},\mu)\to (\cs{L}',\mu')$
@@
 Thus, Lusztig's result shows that for every representation $\rho$ of $G(k)$ there is some $\cs{F}\in \mathsf{K}_{\bar\QQ}\textsc{D}^b_{c,G}(G;\EE)$ such that $\trace\rho = \trFrob{\cs{F}}$.
-This result is extended in the papers beginning with \cite{lusztig:disconnected1} to reductive groups $G$ over $k$ for which the geometric component group for $G$ is cyclic.
+This result is extended in the papers beginning with \cite{lusztig:disconnected1} \todo{it is necessary to provide the precise reference in ``the papers beginning with [18]'' where the existence of F is proved.} to reductive groups $G$ over $k$ for which the geometric component group for $G$ is cyclic.
 
@@
 Recall that $R$ is the ring of integers of a local field with finite residue field $k$.
-The maximal idea of $R$ will be denoted by $\mathfrak{m}$. 
+The maximal ideal of $R$ will be denoted by $\mathfrak{m}$. 
 Let $\underline{G}$ be a smooth group scheme over $R$.
@@
 Let $\underline{G}$ be a smooth group scheme over $R$.
-Let $\varphi : \underline{G}(R) \to \EEx$ be quasicharacter and let $r$ be the level of $\varphi$.
+Let $\varphi : \underline{G}(R) \to \EEx$ be a quasicharacter and let $r$ be the level of $\varphi$.
 If $\varphi_r : G_r(k)\to \EEx$ is trivial on $G_{r,\operatorname{der}}(k)$ then 
@@
 Recall that the full Greenberg transform $G \ceq \Gr^{R}(\underline{G})$ is a group scheme over $\Fq$ such that $G(\Fq) = \underline{G}(R)$; it comes equipped with a morphism $G \to G_r$.
-The Weil sheaf on $G$ obtained from $\cs{L}_m$ by pullback along the morphism of group schemes $G \to G_r$ is a quasicharacter sheaf on $G$, in the sense of \cite{cunningham-roe:13a}*{Def 4.2}, such that
+The Weil sheaf on $G$ obtained from $\cs{L}_r$ by pullback along the morphism of group schemes $G \to G_r$ is a quasicharacter sheaf on $G$, in the sense of \cite{cunningham-roe:13a}*{Def 4.2}, such that
 \[
@@
 For the rest of Section~\ref{sec:types}, $R$ is the ring of integers of a $p$-adic field.
+\todo{I think that that ``p-adic field'' can be replaced by the more general notion of ``non-archimedean local field with finite residue field'' (that is, fields with equal characteristic should be be allowed) thanks to the results of arXiv:1810.04198 already mentioned.}
 A Yu type datum $(\oK^i,\orho^0,\varphi^i,d)$ consists of the following:
@@
 $\orho_{i+1}$ & $\,^\circ \rho_{i+1}$ &  \cite{yu:01a}*{\S 15} \\
-$\varphi^i$ & $\phi_i\vert_{\,^\circ K^i }$ & \cite{yu:01a}*{\S 3}\\
+$\varphi^i$ & $\phi_i\vert_{\,^\circ K^i }$ & \cite{yu:01a}*{\S 3} \\
 $J_{i+1}$ & $J^{i+1} = (G^i,G^{i+1})(F)_{y, (r_i, s_i)}$ & \cite{yu:01a}*{\S 3} \\
@@
 \end{table}%
+\todo{the quasicharacter $\varphi^i$ is defined to be the restriction to $^\circ K_i$ of the quasicharacter $\phi_i$ which appears in [20].
+Yu assumes that $\phi^i$ is $G^{i+1}$ generic.
+It would be interesting to see if $G^{i+1}$-genericity property could be translated into a condition of $\varphi^i$, viewed as a quasicharacter of $\underline{G}^i(R)$ as in M2.}
 
@@
 \] 
-for each $i=0,\ldots d$, such that $\underline{J}^i(R) = J_i$ as a subgroup of $C$ and such that the image of the $R$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $\oK^i$, for $i=0, \ldots , d$.
+for each $i=0,\ldots d$, such that $\underline{J}^i(R) = J_i$ as a subgroup of $C$ \todo{define $C$} and such that the image of the $R$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $\oK^i$, for $i=0, \ldots , d$.
 There is a natural action of $\underline{G}^i$ on $\underline{J}^{i+1}$ in the category of smooth affine group schemes over $R$ so that the group scheme
@@
 The continuous representation $\orho^0$ of $\oK^0$ appearing in \ref{Y1} may be interpreted as a representation of $\underline{G}^0(R)$ obtained by inflation along $\underline{G}^0(R) \to \underline{G}^0(\Fq)$ from a representation $\varrho_0$ of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
-In fact, $\varrho_0$ is itself obtained by pulling back a representation $\varrho_0^\reductive$ along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+In fact, $\varrho_0$ is itself obtained by pulling back a representation $\varrho_0^\reductive$ \todo{why can $\varrho_0$ be obtained by pulling back a representation $\varrho_0^\reductive$} along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
 \labitem{M2}{M2} The quasicharacters $\varphi^i$ appearing in \ref{Y2} are now quasicharacters of $\underline{G}^i(R)$, for $i=0, \ldots, d$.
@@
 \labitem{H1(b)}{H1b} the quasicharacter $\varphi_i$ of $G_i$ is trivial on  $G_{i,\operatorname{der}}(k)$.
+\todo{It would be worth to provide an example of supercuspidal representation (with positive depth) of a non-commutative p-adic group for which the hypothesis H1(b) is satsified}
 \end{enumerate}
@@
 Let $r_i$ be the level of $\varphi^i$ as defined in Section~\ref{ssec:quasicharacters}.
+\todo{the precise reference in the series of Lusztig articles on character sheaves on disconnected groups must be provided.}
 Set $r = \max\{ r_i \tq i=0, \ldots ,d\}$.
@@
 \end{equation}
-Observe that $\trace(\orho^0)_r$ may be recovered from ${A}_m^0$:
+Observe that $\trace(\orho^0)_r$ may be recovered from ${A}_r^0$:
 \[
@@
 If \ref{H1a} applies, then $\cs{L}_i \in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_i}(G_i;\EE)$, using \cite{lusztig:disconnected1};
-if \ref{H1b} applies, then $\cs{L}_i\in \CCS(G_i)$, using Proposition~\ref{prop:quasicharacters}.
+if \ref{H1b} applies, then $\cs{L}_i\in \CCS(G_i)$, using Proposition~\ref{prop:quasicharacters}. \todo{provide exact reference}
 In either case, $\cs{L}_i\in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_i}(G_i;\EE)$ and
@@
 Comparing with \eqref{eq:tensor}, we see that $\trFrob{\cs{B}_r^{i+1}}$ is precisely the function obtained by factoring the character of $\orho^{i+1}$ through $(\underline{G}^{i}\ltimes \underline{J}^{i+1})(R) \to (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R_r)$ using the canonical identification $(G_r^{i}\times_{G_r} J_r^{i+1})(\Fq) =  (\underline{G}^{i}\ltimes \underline{J}^{i+1})(R_r)$.
-In particular, $\trFrob{\cs{B}^{i+1}_m}$ is constant on $(G_r^{i}\times_{G_r} J_r^{i+1})(\Fq)$, taking the value $\dim \orho^{i+1}$.
+In particular, $\trFrob{\cs{B}^{i+1}_r}$ is constant on $(G_r^{i}\times_{G_r} J_r^{i+1})(\Fq)$, taking the value $\dim \orho^{i+1}$.
 With reference to the morphism $\pi_r^{i+1} : G_r^i \ltimes J_r^{i+1} \to G_r^{i+1}$ from \eqref{eq:pi}, define 
@@
 \bigskip
+
+\todo{It would be worth to quote also the recent article by Jeffrey Hakim ``Constructing tame
+supercuspidal representations'' (Represent. Theory 22, 2018), which revisits Yu's construction in an
+interesting manner.}
 
@@
       number={32},
+}
+
+\bib{fintzen:18a}{unpublished}{
+   author={Fintzen, Jessica},
+   title={Types for tame $p$-adic groups},
+   date={2018},
+   note={\href{http://arxiv.org/abs/1810.04198}{arXiv:1810.04198 [math.RT]}}
 }

### 2020-05-01 Geometric types.tex
Update Geometric types.tex

@@
 
-As proved by Ju-Lee Kim in \cite{kim:07a} and Jessica Fintzen in \cite{fintzen:18a}, \todo{check this fix} all irreducible supercuspidal representations of a tamely ramified $p$-adic group $G$ can be built from ``data'' introduced by Jiu-Kang Yu in \cite{yu:01a}*{\S 15} as long as $p$ does not divide the order of the Weyl group of $G$.
+The combined work of Ju-Lee Kim in \cite{kim:07a} and Jessica Fintzen in \cites{fintzen:18a,fintzen:19a} establishes that all irreducible supercuspidal representations of a tamely ramified $p$-adic group $G$ can be built from ``data'' introduced by Jiu-Kang Yu \cite{yu:01a}*{\S 15}, as long as $p$ does not divide the order of the Weyl group of $G$.
 While the type, in the sense of Bushnell \& Kutzko \cite{bushnell-kutzko:98a}, of a supercuspidal representation built from Yu data can be constructed directly from the datum, it is convenient to consider an intermediate object, introduced in \cite{yu:01a}*{Remark 15.4}, which we call a \emph{Yu type datum}.
@@
 The main result of \cite{Yu:models} shows how to find, for each $i=0, \ldots, d$, a smooth group scheme $\underline{G}^i$ over the ring $R$ with $\underline{G}^i(R)=\,^\circ K^i $.
-Under certain assumptions on the Yu type datum, we show how each representation $\orho_i$ can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$, where $\cs{F}^i$ is a formal ${\bar\QQ}$-linear \todo{${\bar\QQ}$ is not defined} combination of conjugation-equivariant sheaf complexes on the Greenberg transform $G^i$ of $\underline{G}^i$.
+Under certain assumptions on the Yu type datum, we show how each representation $\orho_i$ can be replaced by a pair $(\underline{G}^i, \cs{F}^i)$, where $\cs{F}^i$ is a formal ${\bar\QQ}$-linear combination of conjugation-equivariant sheaf complexes on the Greenberg transform $G^i$ of $\underline{G}^i$.
 %
@@
 Let $\gcs{L}$ be the geometric part of an object in $\CCS(G)$; see Section~\ref{sec:defs}.
-Let $T$ be a maximal torus in the base change $\bG$ of $G$ to an algebraic closure $\bar{k}$ of $k$, and let $\gcs{L}_T$ be the restriction of $\gcs{L}$ to $T$.
+Let $T$ be a maximal torus in the base change $\bG$ of $G$ to $\bar{k}$ and let $\gcs{L}_T$ be the restriction of $\gcs{L}$ to $T$.
 Then the perverse sheaf $\gcs{L}[\dim G]$ appears in the semisimple complex $\operatorname{ind}_{B,T}^{\bG}(\gcs{L}_T)$ produced by parabolic induction.
@@
 
-In this paper we use a common formalism for Weil sheaves, writing $\cs{L}$ for the pair $(\gcs{L},\phi)$, where $\gcs{L}$ is an $\ell$-adic sheaf on $\bG \ceq G\otimes_{\Fq} \bFq$ \todo{the notation $\bFq$ isn't defined} and where $\phi : \Frob{}^*\gcs{L} \to \gcs{L}$ is an isomorphism of $\ell$-adic sheaves.
+Let $\bFq$ be a fixed algebraic closure of $\Fq$. 
+In general, we use overline to denote a separable closure of a field or the base change a geometric object to a scheme over a separable closure of a field.
+%
+In this paper we use a common formalism for Weil sheaves, writing $\cs{L}$ for the pair $(\gcs{L},\phi)$, where $\gcs{L}$ is an $\ell$-adic sheaf on $\bG = G\otimes_{\Fq} \bFq$  and where $\phi : \Frob{}^*\gcs{L} \to \gcs{L}$ is an isomorphism of $\ell$-adic sheaves.
 We also follow convention by referring to $\cs{L}$  as a Weil sheaf on $G$, as in \cite{Deligne:Weil}*{D\'efinition 1.1.10}.
@@
 
-\subsection{Review of Yu's types and associated models}\label{ssec:review}
-
-For the rest of Section~\ref{sec:types}, $R$ is the ring of integers of a $p$-adic field.
-\todo{I think that that ``p-adic field'' can be replaced by the more general notion of ``non-archimedean local field with finite residue field'' (that is, fields with equal characteristic should be be allowed) thanks to the results of arXiv:1810.04198 already mentioned.}
+\subsection{Yu's types and integral models}\label{ssec:review}
+
 A Yu type datum $(\oK^i,\orho^0,\varphi^i,d)$ consists of the following:
@@
 \] 
-for each $i=0,\ldots d$, such that $\underline{J}^i(R) = J_i$ as a subgroup of $C$ \todo{define $C$} and such that the image of the $R$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $\oK^i$, for $i=0, \ldots , d$.
+for each $i=0,\ldots d$, such that $\underline{J}^i(R) = J_i$ as a subgroup of $G$ and such that the image of the $R$-points under the multiplication map $\underline{J}^0 \times \cdots \times \underline{J}^i \to \underline{G}$ is $\oK^i$, for $i=0, \ldots , d$.
 There is a natural action of $\underline{G}^i$ on $\underline{J}^{i+1}$ in the category of smooth affine group schemes over $R$ so that the group scheme
@@
 
+\bib{fintzen:19a}{unpublished}{
+   author={Fintzen, Jessica},
+   title={On the construction of tame supercuspidal representations},
+   date={2019},
+   note={\href{http://arxiv.org/abs/1908.09819}{arXiv:1908.09819 [math.RT]}}
+}
+
 \bib{fintzen:18a}{unpublished}{

### 2020-06-08 Geometric types.tex
Update Geometric types.tex

@@
 25.7}, Weil character sheaves on $G$ determine a basis for the vector space of class functions on $G(k)$; in particular, any character of any representation of $G(k)$ can be expressed as a ${\bar \QQ}$-linear combination of characteristic functions of Weil character sheaves on $G$.
-Let us use the notation $\mathsf{D}^b_{c,G}(G;\EE)$ for the category of conjugation-equivariant objects in $\mathsf{D}^b_{c}(G;\EE)$, as defined in \cite{bernstein-lunts:equivariant} for example, and $\mathsf{KD}^b_{c,G}(G;\EE)$ for the Grothendieck group of $\mathsf{D}^b_{c,G}(G;\EE)$; we set $\mathsf{K}_{\bar\QQ}\textsc{D}^b_{c,G}(G;\EE)\ceq \mathsf{KD}^b_{c,G}(G;\EE)\otimes_{\ZZ} {\bar\QQ}$.
-Thus, Lusztig's result shows that for every representation $\rho$ of $G(k)$ there is some $\cs{F}\in \mathsf{K}_{\bar\QQ}\textsc{D}^b_{c,G}(G;\EE)$ such that $\trace\rho = \trFrob{\cs{F}}$.
-This result is extended in the papers beginning with \cite{lusztig:disconnected1} \todo{it is necessary to provide the precise reference in ``the papers beginning with [18]'' where the existence of F is proved.} to reductive groups $G$ over $k$ for which the geometric component group for $G$ is cyclic.
-
-When specialized to the case of characters $\chi$ of $G(k)$, Lusztig's theory of character sheaves geometrizes $\chi$ using $\mathsf{K}_{\bar\QQ}\textsc{D}^b_{c,G}(G;\EE)$; of course, the resulting geometrization is generally not a local system.
+Let us use the notation $\mathsf{D}^b_{c,G}(G;\EE)$ for the category of conjugation-equivariant objects in $\mathsf{D}^b_{c}(G;\EE)$, as defined in \cite{bernstein-lunts:equivariant} for example, and $\mathsf{KD}^b_{c,G}(G;\EE)$ for the Grothendieck group of $\mathsf{D}^b_{c,G}(G;\EE)$; we set $\mathsf{K}_{\EE}\textsc{D}^b_{c,G}(G;\EE)\ceq \mathsf{KD}^b_{c,G}(G;\EE)\otimes_{\ZZ} {\EE}$.
+Thus, Lusztig's result shows that for every representation $\rho$ of $G(k)$ there is some $\cs{F}\in \mathsf{K}_{\EE}\textsc{D}^b_{c,G}(G;\EE)$ such that $\trace\rho = \trFrob{\cs{F}}$.
+By \cite{lusztig:disconnected4}*{Thm.
+21.21}, this result extends to all reductive groups $G$ over $k$ without the hypothesis that $G$ is connected.% for which the geometric component group for $G$ is cyclic.
+
+When specialized to the case of characters $\chi$ of $G(k)$, Lusztig's theory of character sheaves geometrizes $\chi$ using $\mathsf{K}_{\EE}\textsc{D}^b_{c,G}(G;\EE)$; of course, the resulting geometrization is generally not a local system.
 %
@@
 Let $(\oK^i, \orho^0, \varphi^i,d)$ be a Yu type datum that satisfies Hypotheses~\ref{H0} and \ref{H1}, and let $\orho_i$ be the representation of $\oK^i$ constructed from it in Section~\ref{ssec:review}.
-Then for each $i=0,\dots, d$ there is an element $\cs{F}_i \in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G^i}(G^i;\EE)$ such that
+Then for each $i=0,\dots, d$ there is an element $\cs{F}_i \in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G^i}(G^i;\EE)$ such that
 \[
@@
 
-By \cite{lusztig:disconnected1}, there is $A \in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,(\underline{G}^0)_\Fq\red}((\underline{G}^0)_\Fq\red;\EE)$ such that 
+By \cite{lusztig:disconnected4}*{Thm. 21.21}, there is $A \in \mathsf{K}_{\EE}\mathsf{D}^b_{c,(\underline{G}^0)_\Fq\red}((\underline{G}^0)_\Fq\red;\EE)$ such that 
 %${\bar A}$ is a rational virtual character sheaf on $(\underline{G}^0)_{\bFq}^\reductive$ and
@@
 Using Hypothesis~\ref{H1}, let $\cs{L}_i$ be the geometrization of the quasicharacter $\varphi_i \ceq \varphi^i_{r_i}$ appearing in \ref{M2}.
-If \ref{H1a} applies, then $\cs{L}_i \in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_i}(G_i;\EE)$, using \cite{lusztig:disconnected1};
+If \ref{H1a} applies, then $\cs{L}_i \in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G_i}(G_i;\EE)$, using \cite{lusztig:disconnected4}*{Thm. 21.21};
 if \ref{H1b} applies, then $\cs{L}_i\in \CCS(G_i)$, using Proposition~\ref{prop:quasicharacters}. \todo{provide exact reference}
-In either case, $\cs{L}_i\in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_i}(G_i;\EE)$ and
+In either case, $\cs{L}_i\in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G_i}(G_i;\EE)$ and
 \[
@@
 By \cite{bertapelle-gonzales:Greenberg}*{Prop 14.2}, the sequences are exact.
-Consider $\cs{B}_r^{i+1}\in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_r^{i}\ltimes J_r^{i+1}}(G_r^{i}\ltimes J_r^{i+1};\EE)$ defined by
+Consider $\cs{B}_r^{i+1}\in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G_r^{i}\ltimes J_r^{i+1}}(G_r^{i}\ltimes J_r^{i+1};\EE)$ defined by
 \[
@@
 \]
-Then $\cs{C}_r^{i+1}\in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_r^{i+1}}(G_r^{i+1};\EE)$ and
+Then $\cs{C}_r^{i+1}\in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G_r^{i+1}}(G_r^{i+1};\EE)$ and
 \begin{eqnarray*}
@@
 Now set $\cs{F}^i_r = \cs{A}_r^{i} \otimes \cs{L}_r^i$, for $i=0, \ldots ,d$.
-Then $\cs{F}^i_r \in \mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_r^{i}}(G_r^{i};\EE)$ such that
+Then $\cs{F}^i_r \in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G_r^{i}}(G_r^{i};\EE)$ such that
 \[
@@
 
-\bib{lusztig:disconnected1}{article}{
-      author={Lusztig, George},
-       title={{Character sheaves on disconnected groups I}},
-        date={2003},
-     journal={Representation Theory},
-      volume={7},
-       pages={374\ndash 403},
+\bib{lusztig:disconnected4}{article}{
+   author={Lusztig, G.},
+   title={Character sheaves on disconnected groups. IV},
+   journal={Represent. Theory},
+   volume={8},
+   date={2004},
+   pages={145--178},
+%   review={\MR{2048590}},
+%   doi={10.1090/S1088-4165-04-00240-7},
 }

### 2020-07-24 Geometric types.tex
Update Geometric types.tex

@@
 The proof of Theorem~\ref{thm:geotypes} requires: Yu's work on smooth integral models \cite{Yu:models}; the geometrization of the character of the Heisenberg-Weil representation over finite fields by Gurevich \& Hadani \cite{gurevich-hadani:07a}; Lusztig's character sheaves on reductive groups over finite fields; and finally, the function-sheaf dictionary for characters of smooth group schemes over finite fields, now at our disposal in Theorem~\ref{thm:geo}.
-In order to use these tools we must restrict our attention to Yu type data that satisfy two technical conditions, appearing in Section~\ref{ssec:geotypes} as Hypotheses~\ref{H0} and \ref{H1}. 
-Granting these hypotheses, these pieces are assembled in Section~\ref{ssec:geotypes}, where we prove Theorem~\ref{thm:geotypes}.
+In order to use these tools we must restrict our attention to Yu type data that satisfy a technical condition, appearing in Section~\ref{ssec:geotypes} as Hypothesis~\ref{H1}. 
+Granting this hypothesis, these pieces are assembled in Section~\ref{ssec:geotypes}, where we prove Theorem~\ref{thm:geotypes}.
 With this theorem, we provide all of the ingredients needed to geometrize a class of supercuspidal representations of arbitrary depth.
@@
 The continuous representation $\orho^0$ of $\oK^0$ appearing in \ref{Y1} may be interpreted as a representation of $\underline{G}^0(R)$ obtained by inflation along $\underline{G}^0(R) \to \underline{G}^0(\Fq)$ from a representation $\varrho_0$ of $\underline{G}^0(\Fq) = \underline{G}^0_\Fq(\Fq)$.
-In fact, $\varrho_0$ is itself obtained by pulling back a representation $\varrho_0^\reductive$ \todo{why can $\varrho_0$ be obtained by pulling back a representation $\varrho_0^\reductive$} along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$.
+In fact, $\varrho_0$ is itself obtained by pulling back a representation $\varrho_0^\reductive$; this is a consequence of \cite{Yu:models}*{\S 10.5 (i)}.
+%\todo{why can $\varrho_0$ be obtained by pulling back a representation $\varrho_0^\reductive$} along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$ 
 \labitem{M2}{M2} The quasicharacters $\varphi^i$ appearing in \ref{Y2} are now quasicharacters of $\underline{G}^i(R)$, for $i=0, \ldots, d$.
@@
 \begin{enumerate}
-\labitem{H0}{H0} the geometric component group of $(\underline{G}^0)\red_{k}$ is cyclic;
+%\labitem{H0}{H0} the geometric component group of $(\underline{G}^0)\red_{k}$ is cyclic;
 \labitem{H1}{H1} for each $i=0,\ldots, d$, either
 \begin{enumerate}
-\labitem{H1(a)}{H1a} $G_i$ is reductive with cyclic geometric component group, or
+\labitem{H1(a)}{H1a} $G_i$ is reductive, or % with cyclic geometric component group, or
 \labitem{H1(b)}{H1b} the quasicharacter $\varphi_i$ of $G_i$ is trivial on  $G_{i,\operatorname{der}}(k)$.
@@
 \end{enumerate}
-Hypothesis~\ref{H0} will allow us to use Lusztig's character sheaves to geometrize the character of the representation of $\orho^0$.
+%Hypothesis~\ref{H0} will allow us to use Lusztig's character sheaves to geometrize the character of the representation of $\orho^0$.
 Hypothesis~\ref{H1a} may be used to geometrize each quasicharacter $\varphi_i$ using $\mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_i}(G_i;\EE)$.
@@
 
-We remark that if Lusztig's theory of character sheaves can be generalized to all disconnected reductive algebraic groups, then Hypothesis~\ref{H0} can be removed and Hypothesis~\ref{H1a} can be replaced with the hypothesis that each $G_i$ is reductive.
+%We remark that if Lusztig's theory of character sheaves can be generalized to all disconnected reductive algebraic groups, then Hypothesis~\ref{H0} can be removed and Hypothesis~\ref{H1a} can be replaced with the hypothesis that each $G_i$ is reductive.
 
 \begin{theorem}\label{thm:geotypes}
-Let $(\oK^i, \orho^0, \varphi^i,d)$ be a Yu type datum that satisfies Hypotheses~\ref{H0} and \ref{H1}, and let $\orho_i$ be the representation of $\oK^i$ constructed from it in Section~\ref{ssec:review}.
+Let $(\oK^i, \orho^0, \varphi^i,d)$ be a Yu type datum that satisfies Hypotheses~%\ref{H0} and 
+\ref{H1}, and let $\orho_i$ be the representation of $\oK^i$ constructed from it in Section~\ref{ssec:review}.
 Then for each $i=0,\dots, d$ there is an element $\cs{F}_i \in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G^i}(G^i;\EE)$ such that
@@
 Let $r_i$ be the level of $\varphi^i$ as defined in Section~\ref{ssec:quasicharacters}. 
-\todo{the precise reference in the series of Lusztig articles on character sheaves on disconnected groups must be provided.}
+%\todo{the precise reference in the series of Lusztig articles on character sheaves on disconnected groups must be provided.}
 Set $r = \max\{ r_i \tq i=0, \ldots ,d\}$.
@@
 \]
-This uses Hypothesis~\ref{H0}.
+%This uses Hypothesis~\ref{H0}.
 %
@@
 If \ref{H1a} applies, then $\cs{L}_i \in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G_i}(G_i;\EE)$, using \cite{lusztig:disconnected4}*{Thm. 21.21};
-if \ref{H1b} applies, then $\cs{L}_i\in \CCS(G_i)$, using Proposition~\ref{prop:quasicharacters}. \todo{provide exact reference}
+if \ref{H1b} applies, then $\cs{L}_i\in \CCS(G_i)$, using Proposition~\ref{prop:quasicharacters}. 
+%\todo{provide exact reference}
 In either case, $\cs{L}_i\in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G_i}(G_i;\EE)$ and

### 2020-07-24 Geometric types.tex
Working on intro

--- 2020-05-01 Geometric types.tex
@@
 
+Yu's construction has been revisited recently by several authors.
+Hakim \cite{hakim:18a}*{\S 2.1} gives an alternate construction beginning with a
+representation of a compact-mod-center subgroup of $G$.
+Unfortunately, this ingredient does not lend itself to geometrization using our techniques.
+In contrast, Kaletha \cite{kaletha:19a} has given a construction in terms of a
+tame elliptic maximal torus $S \subset G$ and a character $\theta$ of $S$.
+The pair $(S, \theta)$ can already be geometrized using \cite{cunningham-roe:13a} since $S$ is commutative.
+However, Kaletha's construction only produces a subset of Yu's supercuspidal representations \cite{kaletha:19a}*{Prop. 3.7.14}, so we phrase our geometrization in terms of Yu's original construction.
+
 \bigskip
@@
 \]
-Applying $\Hom(-, \EEx)$ yields the bottom row in the statement.
+Applying $\Hom(-, \EEx)$, which is exact since $\EEx$ is divisible, yields the bottom row in the statement.
 
@@
 
+\bib{hakim:18a}{article}{
+author={Hakim, Jeffrey},
+title={Constructing tame supercuspidal representations},
+journal={Representation Theory},
+volume={22},
+date={2018},
+pages={45--86}
+}
+
 \bib{howe:73a}{article}{
    author={Howe, Roger E.},
-   title={On the character of Weil's representation},
+   title={{On the character of Weil's representation}},
    journal={Trans. Amer. Math. Soc.},
@@
    pages={287--298},
+}
+
+\bib{kaletha:19a}{article}{
+author={Kaletha, Tasho},
+title={Regular supercuspidal representations},
+journal={J. Amer. Math. Soc.},
+volume={32},
+date={2019},
+pages={1071--1170},
 }

### 2020-07-24 Geometric types.tex

--- 2020-07-24 Geometric types.tex
@@
 The proof of Theorem~\ref{thm:geotypes} requires: Yu's work on smooth integral models \cite{Yu:models}; the geometrization of the character of the Heisenberg-Weil representation over finite fields by Gurevich \& Hadani \cite{gurevich-hadani:07a}; Lusztig's character sheaves on reductive groups over finite fields; and finally, the function-sheaf dictionary for characters of smooth group schemes over finite fields, now at our disposal in Theorem~\ref{thm:geo}.
+
 In order to use these tools we must restrict our attention to Yu type data that satisfy a technical condition, appearing in Section~\ref{ssec:geotypes} as Hypothesis~\ref{H1}. 
@@
 With this theorem, we provide all of the ingredients needed to geometrize a class of supercuspidal representations of arbitrary depth.
+
+Yu's construction has been revisited recently by several authors.
+Hakim \cite{hakim:18a}*{\S 2.1} gives an alternate construction beginning with a
+representation of a compact-mod-center subgroup of $G$.
+Unfortunately, this ingredient does not lend itself to geometrization using our techniques.
+In contrast, Kaletha \cite{kaletha:19a} has given a construction in terms of a
+tame elliptic maximal torus $S \subset G$ and a character $\theta$ of $S$.
+The pair $(S, \theta)$ can already be geometrized using \cite{cunningham-roe:13a} since $S$ is commutative.
+However, Kaletha's construction only produces a subset of Yu's supercuspidal representations \cite{kaletha:19a}*{Prop. 3.7.14}, so we phrase our geometrization in terms of Yu's original construction.
 

### 2020-08-07 Geometric types.tex
Added H1b examples

@@
 
+We give examples illustrating Hypothesis \ref{H1b}: first,
+an example of a quasicharacter that does not vanish on $G_{i, \der}(k)$,
+and then a class of Yu data where it is always satisfied.
+Let $G = \SL_2$ over $\QQ_2$.
+Then the hyperspecial maximal compact $\oK^0$ reduces to $\SL_2(\ZZ/2^{d+1}\ZZ)$ at depth $d$.
+The derived subgroup of $\SL_2(\ZZ/2\ZZ)$ has index $2$, while it has index $4$ in positive depth.
+There is therefore a character $\varphi^0$ of $K$ of order $4$ and depth $1$
+factoring through the quotient of $\SL_2(\ZZ/4\ZZ)$ by its derived subgroup.
+Taking the trivial representation for $\orho^0$ gives a Yu datum not satisfying \ref{H1b}. \todo{Does Yu require tameness?  Can we say that this is an example if so?}
+
+In contrast, there is a broad class of representations that automatically satisfy \ref{H1b}.
+Recall that a representation is \emph{toral} \citelist{\cite{adler:98a} \cite{kaletha:19a}*{\S 6}}
+if it arises from a Yu datum of the form $(S \subset G, \orho^0=1, (\varphi^{d-1}, 1)$ where
+$S$ is an elliptic maximal torus and $\varphi^{d-1}$ is $G$-generic character of $S(F)$ of positive depth.
+Since $S$ is abelian, it has trivial derived subgroup and thus \ref{H1b} is satisfied.
+Toral representations include epipelagic representations \cite{reeder-yu:14a} and
+the representations considered by Reeder in \cite{reeder:08a}.
+
 %We remark that if Lusztig's theory of character sheaves can be generalized to all disconnected reductive algebraic groups, then Hypothesis~\ref{H0} can be removed and Hypothesis~\ref{H1a} can be replaced with the hypothesis that each $G_i$ is reductive.
@@
 \begin{biblist}
+
+\bib{adler:98a}{article}{
+	author={Adler, Jeffrey},
+	title={Refined  anisotropic $K$-types  and  supercuspidal  representations},
+	journal={Pacific J. Math.},
+	volume={185},
+	date={1998},
+	number={1},
+	pages={1--32},
+}
 
@@
 
+\bib{reeder:08a}{article}{
+    author={Reeder, Mark},
+    title={Supercuspidal $L$-packets of positive depth and twisted {Coxeter} elements},
+    journal={J. Reine Angew. Math.},
+    volume={620},
+    date={2008},
+    pages={1--33},
+}
+
+\bib{reeder-yu:14a}{article}{
+    author={Reeder, Mark},
+    author={Yu, Jiu-Kang},
+    title={Epipelagic representations and invariant theory},
+    journal={J. Amer. Math. Soc.},
+    volume={27},
+    number={2},
+    pages={437--477},
+}
+
 \bib{Vistoli:notes}{article}{

### 2020-10-20 referee_response.tex
Remove todo notes, add referee response

\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsfonts,amsthm}

\newcommand{\kbar}{\overline{k}}
\newcommand{\A}{\mathbb{A}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Qp}{\Q_p}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}_{\rm div}}
\newcommand{\Zp}{\Z_p}
\newcommand{\F}{\mathbb{F}}
\newcommand{\Fp}{\F_p}
\newcommand{\Fq}{\F_q}
\newcommand{\Fqbar}{\overline{\F}_q}
\newcommand{\Fqm}{\F_{q^m}}
\newcommand{\Fqn}{\F_{q^n}}
\renewcommand{\O}{\mathcal{O}}
\newcommand{\dom}{\operatorname{dom}}
\newcommand{\Spec}{\operatorname{Spec}}

\title{Response to Referee -- \\ Commutative character sheaves and geometric types for supercuspidal representations}
\author{Clifton Cunningham and David Roe}
\date{\today}

\begin{document}
\maketitle

We would like to thank the referee for a thorough and considered review.  The comments were very helpful and allowed us to improve the paper.

In addition to the line items suggested by the referee, we have made the following substantive changes.

\begin{enumerate}
\item We have added a reference to Fintzen's paper as suggested, and provided a more precise condition on $p$ (1,2).
\item We added precise references to the work of Lusztig that we depend on (11,20,22).
\item We replaced $p$-adic field with local field as suggested (15).
\item We agree that it would be nice if the genericity condition on $\phi_i$ could be translated to an illuminating condition on $\varphi_i$.  Unfortunately, while the condition can certainly be translated to the Greenberg transform side of the story, it doesn't seem to provide any insight.  We have therefore not addressed the referee's suggestion (16).
\item We have added a reference to a paper of Yu (18).
\item In addressing (19,20), we realized that hypothesis \textbf{H0} was unnecessary (it resulted from our misreading of one of Lusztig's results) so we have removed it.  We have added two paragraphs illustrating hypothesis \textbf{H1(b)}, giving examples both of representations that do not satisfy it and a broad class of representations that do discussed in a paper of Kaletha.
\item We added a reference to Hakim's paper in the introduction (24).
\end{enumerate}

\end{document}

### 2020-10-20 Geometric types.tex
Remove todo notes, add referee response

@@
 \end{abstract}
-\todo{Since Yu's article ``Construction of tame supercuspidal representation'' [20] is a key ingredient, I would like to inform the authors that, as recently noticed by Loren Spice, Proposition 14.1 and Theorem 14.2 in [20] are not always true (they rely on a misprinted statement in a reference).
-An alternative proof of Yu's main results which avoids these steps was provided by Jessica Fintzen in ``On the construction of tame supercuspidal representations'', arXiv:1908.09819.
-I think that it should be mentioned, even if does not affect the results of manuscript.}
 
@@
 \end{table}%
-\todo{the quasicharacter $\varphi^i$ is defined to be the restriction to $^\circ K_i$ of the quasicharacter $\phi_i$ which appears in [20].
-Yu assumes that $\phi^i$ is $G^{i+1}$ generic.
-It would be interesting to see if $G^{i+1}$-genericity property could be translated into a condition of $\varphi^i$, viewed as a quasicharacter of $\underline{G}^i(R)$ as in M2.}
 
@@
 In fact, $\varrho_0$ is itself obtained by pulling back a representation $\varrho_0^\reductive$; this is a consequence of \cite{Yu:models}*{\S 10.5 (i)}.
-%\todo{why can $\varrho_0$ be obtained by pulling back a representation $\varrho_0^\reductive$} along the $\Fq$-points of the quotient $\underline{G}^0_\Fq \to (\underline{G}^0)_\Fq^\reductive$ 
 \labitem{M2}{M2} The quasicharacters $\varphi^i$ appearing in \ref{Y2} are now quasicharacters of $\underline{G}^i(R)$, for $i=0, \ldots, d$.
@@
 \labitem{H1(b)}{H1b} the quasicharacter $\varphi_i$ of $G_i$ is trivial on  $G_{i,\operatorname{der}}(k)$.
-\todo{It would be worth to provide an example of supercuspidal representation (with positive depth) of a non-commutative p-adic group for which the hypothesis H1(b) is satsified}
 \end{enumerate}
@@
 factoring through the quotient of $\SL_2(\ZZ/4\ZZ)$ by its derived subgroup.
-Taking the trivial representation for $\orho^0$ gives a Yu datum not satisfying \ref{H1b}. \todo{Does Yu require tameness?  Can we say that this is an example if so?}
+Taking the trivial representation for $\orho^0$ gives a datum not satisfying \ref{H1b}.
 
@@
 Let $r_i$ be the level of $\varphi^i$ as defined in Section~\ref{ssec:quasicharacters}. 
-%\todo{the precise reference in the series of Lusztig articles on character sheaves on disconnected groups must be provided.}
 Set $r = \max\{ r_i \tq i=0, \ldots ,d\}$.
@@
 if \ref{H1b} applies, then $\cs{L}_i\in \CCS(G_i)$, using Proposition~\ref{prop:quasicharacters}. 
-%\todo{provide exact reference}
 In either case, $\cs{L}_i\in \mathsf{K}_{\EE}\mathsf{D}^b_{c,G_i}(G_i;\EE)$ and
@@
 \end{proof}
-
-\bigskip
-
-\todo{It would be worth to quote also the recent article by Jeffrey Hakim ``Constructing tame
-supercuspidal representations'' (Represent. Theory 22, 2018), which revisits Yu's construction in an
-interesting manner.}
 

### 2021-01-06 Geometric types.tex
Final referee changes

@@
 %Hypothesis~\ref{H0} will allow us to use Lusztig's character sheaves to geometrize the character of the representation of $\orho^0$.
-Hypothesis~\ref{H1a} may be used to geometrize each quasicharacter $\varphi_i$ using $\mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_i}(G_i;\EE)$.
+Hypothesis~\ref{H1a} may be used to geometrize each quasicharacter $\varphi_i$ inside the Grothendieck group $\mathsf{K}_{\bar\QQ}\mathsf{D}^b_{c,G_i}(G_i;\EE)$.
 Alternatively, Hypothesis~\ref{H1b} allows us to use Proposition~\ref{prop:quasicharacters} to geometrize each quasicharacter $\varphi_i$ using local systems on $G_i$, or more precisely, using commutative character sheaves on $G_i$.
@@
 Taking the trivial representation for $\orho^0$ gives a datum not satisfying \ref{H1b}.
+Note that this datum does not satisfy \ref{H1a} either since the depth 1 Greenberg transform
+of the hyperspecial $\oK^0$ is not reductive.
 
@@
 Recall that a representation is \emph{toral} \citelist{\cite{adler:98a} \cite{kaletha:19a}*{\S 6}}
-if it arises from a Yu datum of the form $(S \subset G, \orho^0=1, (\varphi^{d-1}, 1)$ where
+if it arises from a Yu datum of the form $(S \subset G, \orho^0=1, (\varphi^{d-1}, 1))$ where
 $S$ is an elliptic maximal torus and $\varphi^{d-1}$ is $G$-generic character of $S(F)$ of positive depth.
@@
       author={Bushnell, Colin},
-      author={Kutzko, Phil},
+      author={Kutzko, Philip},
        title={{Smooth representations of reductive $p$-adic groups: structure
@@
 \bib{demazure:SGA3-VIB}{inproceedings}{
-      author={Bertin, J.E.},
+      author={Bertin, Jean-\'Etienne},
        title={{Expos\'e VI$_\mathrm{B}$: G\'en\'eralit\'es sur les pr\'esch\'emas en groupes}},
@@
 \bib{lusztig:disconnected4}{article}{
-   author={Lusztig, G.},
+   author={Lusztig, George},
    title={Character sheaves on disconnected groups. IV},

### 2021-01-07 AHL/CunninghamRoeAHL.tex
AHL version

--- 2021-01-06 Geometric types.tex
@@
-\documentclass[10pt]{amsart}
-
-\title[Commutative character sheaves and geometric types]{Commutative character sheaves and geometric types for supercuspidal representations}
-\author{Clifton Cunningham}
-\address{Department of Mathematics and Statistics, University of Calgary, 2500 University Drive Northwest, Calgary, Alberta, Canada, {T2N~1N4}.}
-\email{cunning@math.ucalgary.ca}
-\author{David Roe}
-\address{Department of Mathematics, Massachusetts Institute of Technology, 77 Massachusetts Ave, Cambridge, MA, United States, 02139.}
-\email{roed@mit.edu}
-
-\subjclass[2010]{14F05 (primary), 14L15, 22E50}
-\keywords{function-sheaf dictionary, commutative character sheaves, types for supercuspidal representations}
-
-\usepackage{amssymb}
+%&pdflatex
+% Compile with ``pdflatex template.tex''
+% If your latex is outdated, you may get an error that \frenchsetup
+% is not defined, and this may result in weird pagebreaks. You can ignore these
+% errors, as it will compile properly on an up-to-date latex.
+\pdfoutput=1
+% Add the option ``french'' if the article is in French
+% Remove the option ``Unicode'' if your file is latin1-encoded
+\documentclass[AHL,XML,longabstracts,Unicode]{cedram}
+
+% Many packages are already loaded by the class file, including notably
+% xcolor, amsmath, amsfonts, mathtools, hyperref
+% only add packages you really need
+
+%\usepackage{amssymb}
 \usepackage{amsrefs}
-\usepackage{multirow}
+%\usepackage{multirow}
 % Fonts
-\usepackage{mathrsfs}
+%\usepackage{mathrsfs}
 % Enumitem
-\usepackage{enumitem}
+%\usepackage{enumitem}
 % Hyperrefs
-\usepackage{hyperref}
-\hypersetup{
-  colorlinks   = true, %Colours links instead of ugly boxes
-  urlcolor     = blue, %Colour for external hyperlinks
-  linkcolor    = blue, %Colour of internal links
-  citecolor   = green %Colour of citations
-}
-%\usepackage[margin=4.3cm]{geometry}
-%\renewcommand{\baselinestretch}{1.0}
-
+%\usepackage{hyperref}
+%\hypersetup{
+%  colorlinks   = true, %Colours links instead of ugly boxes
+%  urlcolor     = blue, %Colour for external hyperlinks
+%  linkcolor    = blue, %Colour of internal links
+%  citecolor   = green %Colour of citations
+%}
 \usepackage{tikz}
@@
 %%%%% for spacing
-\usepackage{amsmath}
-\usepackage{lipsum}
+%\usepackage{amsmath}
+%\usepackage{lipsum}
 \usepackage{setspace}
 
-%%%%%%%%%%%%%%% THEOREM STYLES %%%%%%%%%%%%%%%
-\theoremstyle{plain}
-      \newtheorem{theorem}{Theorem}[section]
-      \newtheorem*{theorem*}{Theorem}
-      \newtheorem{proposition}[theorem]{Proposition}
-      \newtheorem{lemma}[theorem]{Lemma}
-      \newtheorem{corollary}[theorem]{Corollary}
-
-      \theoremstyle{definition}
-      \newtheorem{definition}[theorem]{Definition}
-
-      %\theoremstyle{remark}
-      \newtheorem{remark}[theorem]{Remark}
-      \newtheorem{example}[theorem]{Example}
-
-      \newtheorem{conjecture}[theorem]{Conjecture}
+\datereceived{2019-07-03}
+\daterevised{2020-10-20}
+\dateaccepted{2021-01-06}
+
+\editor{Sebastien Gouezel}
+% Uncomment next line if the editor is a woman
+% \womandeditor
+
+% All standard abbreviations for theorems or lemmas are normally already
+% present. If yours is missing, add it here (do not change ``cdrthm'')
+\AtBeginDocument{
+\newtheorem{myname}[cdrthm]{My beautiful theorem}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Add your personal commands here
+
 %%%%%%%%%%%%%%% RINGS AND GROUPS %%%%%%%%%%%%%%%
@@
 \newcommand{\comp}{\Pi} % Component group
-\newcommand{\G}{\textbf{G}}
 %%%%%%%%%%%%%%% NAMED OPERATORS %%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%% BEGIN DOCUMENT %%%%%%%%%%%
-\usepackage{todonotes}
-
-\begin{document}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\author[\initial{C.} \lastname{Cunningham}]{\firstname{Clifton} \lastname{Cunningham}}
+\address{
+Department of Mathematics and Statistics, \\
+University of Calgary, \\
+2500 University Drive Northwest, \\
+Calgary, AB,
+Canada, {T2N~1N4}}
+\email{cunning@math.ucalgary.ca}
+
+\author[\initial{D.} \lastname{Roe}]{\firstname{David} \lastname{Roe}}
+\address{Department of Mathematics, \\
+Massachusetts Institute of Technology, \\
+77 Massachusetts Ave, \\
+Cambridge, MA,
+United States, 02139}
+\email{roed@mit.edu}
+
+\title[Commutative character sheaves and geometric types]{Commutative character sheaves and geometric types for supercuspidal representations}
+%\alttitle{Version longue du titre, mais en fran\c{c}ais}
 
@@
 \end{abstract}
+
+%\begin{altabstract}
+%Dans le r\'esum\'e en fran\c{c}ais, les d\'etails ne rentrent pas plus, mais ce n'est pas
+%pour cela qu'il faut s'en dispenser. (If you don't speak French, don't worry, the
+%editors will translate the abstract for you)
+%\end{altabstract}
+
+\subjclass[2010]{14F05 (primary), 14L15, 22E50}
+\keywords{function-sheaf dictionary, commutative character sheaves, types for supercuspidal representations}
+\thanks{Roe was supported by Simons Foundation grant 550033.}
+
+\begin{document}
 
